### 2016-08-31 paper/paper.tex
+ paper format

% This is "sig-alternate.tex" V2.1 April 2013
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate-05-2015}

\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
%\doi{10.475/123_4}

% ISBN
%\isbn{123-4567-24-567/08/06}

%Conference
%\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

%\acmPrice{\$15.00}

%
% --- Author Metadata here ---
%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{TBD}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

%\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
%% \author{
%% % You can go ahead and credit any number of authors here,
%% % e.g. one 'row of three' or two rows (consisting of one row of three
%% % and a second row of one, two or three).
%% %
%% % The command \alignauthor (no curly braces needed) should
%% % precede each author name, affiliation/snail-mail address and
%% % e-mail address. Additionally, tag each line of
%% % affiliation/address with \affaddr, and tag the
%% % e-mail address with \email.
%% %
%% % 1st. author
%% \alignauthor
%% Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
%%        \affaddr{Institute for Clarity in Documentation}\\
%%        \affaddr{1932 Wallamaloo Lane}\\
%%        \affaddr{Wallamaloo, New Zealand}\\
%%        \email{trovato@corporation.com}
%% % 2nd. author
%% \alignauthor
%% G.K.M. Tobin\titlenote{The secretary disavows
%% any knowledge of this author's actions.}\\
%%        \affaddr{Institute for Clarity in Documentation}\\
%%        \affaddr{P.O. Box 1212}\\
%%        \affaddr{Dublin, Ohio 43017-6221}\\
%%        \email{webmaster@marysville-ohio.com}
%% }

\maketitle
\begin{abstract}

\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
%% \begin{CCSXML}
%% <ccs2012>
%%  <concept>
%%   <concept_id>10010520.10010553.10010562</concept_id>
%%   <concept_desc>Computer systems organization~Embedded systems</concept_desc>
%%   <concept_significance>500</concept_significance>
%%  </concept>
%%  <concept>
%%   <concept_id>10010520.10010575.10010755</concept_id>
%%   <concept_desc>Computer systems organization~Redundancy</concept_desc>
%%   <concept_significance>300</concept_significance>
%%  </concept>
%%  <concept>
%%   <concept_id>10010520.10010553.10010554</concept_id>
%%   <concept_desc>Computer systems organization~Robotics</concept_desc>
%%   <concept_significance>100</concept_significance>
%%  </concept>
%%  <concept>
%%   <concept_id>10003033.10003083.10003095</concept_id>
%%   <concept_desc>Networks~Network reliability</concept_desc>
%%   <concept_significance>100</concept_significance>
%%  </concept>
%% </ccs2012>  
%% \end{CCSXML}

%% \ccsdesc[500]{Computer systems organization~Embedded systems}
%% \ccsdesc[300]{Computer systems organization~Redundancy}
%% \ccsdesc{Computer systems organization~Robotics}
%% \ccsdesc[100]{Networks~Network reliability}

%
% End generated code
%

%
%  Use this command to print the description
%
\printccsdesc

% We no longer use \terms command
%\terms{Theory}

\keywords{}

\section{Introduction}
\section{Overview}
\section{Running Example}
\section{Program Synthesis}
\section{Experiments}
\section{Related Works}
\section{Conclusions}

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
%\appendix
%Appendix A
\end{document}

### 2016-08-31 paper/paper.tex
+ CEGIS figure

@@
 \documentclass{sig-alternate-05-2015}
+
+\usepackage{url}                  % format URLs
+\usepackage{listings}          % format code
+\lstset{
+  mathescape, 
+  language={Java},
+  basicstyle=\small
+}
+\usepackage{enumitem}      % adjust spacing in enums
+\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   
+\usepackage{graphicx}
+\usepackage{float,subfig}
+\usepackage{xspace,framed}
+\usepackage{colortbl}
+\usepackage{calc}
+
+\usepackage{algorithm}
+\usepackage{amsfonts}
+\usepackage{amsmath}
+\usepackage{multicol}
+\usepackage{multirow}
+\usepackage{tikz}
+\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
+\usepackage[justification=centering]{caption}
+\usepackage{stmaryrd}
+\usepackage{hhline}
+\usepackage{pifont}
+%\usepackage{cite}
+\usepackage{pdflscape} % Experiments table is landscape
+\usepackage{longtable}
+\usepackage{afterpage}
+\usepackage{wasysym}
 
@@
 \section{Program Synthesis}
+
+We use CounterExample-Guided Inductive Synthesis (CEGIS), as illustrated in Fig~\ref{fig:CEGIS}.
+
+\begin{figure*}
+\centering
+\resizebox{.6\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto,
+ semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
+},
+          row sep=1cm, column sep=1cm] {
+   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}}; \\
+   \node[fill=yellow!20] (synth) {{\sc Synthesise}};
+   \&
+   \node[fill=yellow!20] (verif) {{\sc Verify}}; \\
+   %% \&
+
+   \& \\
+   \& \\
+   \node (gp) {~~~~~~~~~~~~~~Program Search~~~~~~~~~~~~~~~};
+   \&
+   \node (bmc) {~~~~~~~~~~~~~~~BMC-based Verifier~~~~~~~~~~~~~~~};
+
+    \\
+  };
+
+   \path
+    ([yshift=2em]synth.east) edge node {Candidate solution} ([yshift=2em]verif.west)
+    ([yshift=-2em]verif.west) edge node {Counter-ex} ([yshift=-2em]synth.east)
+    ([xshift=5em]verif.south) edge node {Candidate $P$} ([xshift=5em]bmc.north)
+    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif.south)
+    (verif) edge node {} (done)
+    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
+    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south);
+ \end{tikzpicture}
+}
+ \caption{Counterexample-Guided Inductive Synthesis. \label{fig:CEGIS}}
+\end{figure*}
+
 \section{Experiments}

### 2016-08-31 paper/paper.tex
closed-loop system

@@
   mathescape, 
-  language={Java},
+  language={C},
   basicstyle=\small
@@
 % DOI
-%\doi{10.475/123_4}
+\doi{}
 
 % ISBN
-%\isbn{123-4567-24-567/08/06}
+\isbn{}
 
@@
 \section{Introduction}
+
+\begin{figure*}
+\centering
+\resizebox{.5\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
+     semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=1cm, column sep=1cm] {
+   \coordinate (aux0);
+   \& \node[circle] (circle) {}; 
+   \& \node[fill=yellow!20] (da) {{\sc D/A}}; 
+   \& \node[fill=yellow!20] (p) {{\sc P}};
+   \& \node[fill=yellow!20] (ad) {{\sc A/D}}; 
+   \& \coordinate (aux1);\\
+   \& \coordinate (aux3); 
+   \&
+   \&
+   \node[fill=yellow!20] (c) {C};
+   \& 
+   \& \coordinate (aux2);\\
+  };
+
+  \path[->] (aux0) edge (circle.west);
+  \path  
+   (circle.east) edge (da.west)
+   (da.east) edge (p.west)
+   (p.east) edge (ad.west)
+   (ad.east) edge (aux1.west)
+   (aux1.south) edge (aux2.north)
+   (aux2.west) edge (c.east)
+   (c.west) edge (aux3.east); 
+  \path[->]  (aux3.north) edge (circle.south);
+ \end{tikzpicture}
+}
+ \caption{Closed Loop System. \label{fig:control}}
+\end{figure*}
+
 \section{Overview}
@@
 \centering
-\resizebox{.6\textwidth}{!}{
- \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto,
- semithick, initial text=, ampersand replacement=\&,]
-
+\resizebox{.7\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
   \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
@@
    \node[fill=yellow!20] (verif) {{\sc Verify}}; \\
-   %% \&
 

### 2016-08-31 paper/paper.tex
+ some related works

@@
 
+We are interested in the stability of closed loop systems, i.e., controllers along with a
+model of their physical environment, the plant, as shown in Fig.~\ref{fig:closed-system}.
+
 \begin{figure*}
@@
 }
- \caption{Closed Loop System. \label{fig:control}}
+ \caption{Closed Loop System. \label{fig:closed-system}}
 \end{figure*}
@@
 \section{Related Works}
+Robustness analyses: \cite{DBLP:conf/hybrid/WangGRJF16}
+
+Stability analyses of closed loop systems: \cite{DBLP:conf/hybrid/RouxJG15}.
+This analysis is performed in the state space
+domain using Lyapunov-based quadratic invariants.
 \section{Conclusions}

### 2016-08-31 paper/paper.tex
+ more related work

@@
 \section{Related Works}
-Robustness analyses: \cite{DBLP:conf/hybrid/WangGRJF16}
+Robustness analyses of closed-loop systems: \cite{DBLP:conf/hybrid/WangGRJF16}.
+The approach relies on an invariant computation
+on the discrete system dynamics.
 
@@
 domain using Lyapunov-based quadratic invariants.
+
+Synthesis of switching
+controllers for stabilizing continuous-time plants: \cite{DBLP:conf/cdc/RavanbakhshS15}
+
 \section{Conclusions}

### 2016-08-31 paper/paper.tex
+ more related work

--- 2016-08-31 paper/paper.tex
@@
 \section{Related Works}
+
+\paragraph{Robustness analyses of closed-loop systems} The analysis in 
+\cite{DBLP:conf/hybrid/WangGRJF16}
+relies on an invariant computation
+on the discrete system dynamics.
+
+\paragraph{Stability analyses of closed loop systems} 
+In \cite{DBLP:conf/hybrid/RouxJG15}, the authors
+perform the analysis in the state space
+domain using Lyapunov-based quadratic invariants.
+In \cite{DBLP:journals/corr/PakmehrWJVF13}, Pakmehr et al. 
+design a control software verification framework for gas turbine engines.
+
+\paragraph{Uses of CEGIS for control sysnthesis} 
+In \cite{DBLP:conf/cdc/RavanbakhshS15}, Ravanbakhsh and Sankaranarayanan use
+CEGIS for the synthesis of switching
+controllers for stabilizing continuous-time plants.
+
 \section{Conclusions}

### 2016-08-31 paper/paper.tex
typo

@@
 
-We are interested in the stability of closed loop systems, i.e., controllers along with a
+We are interested in the stability of closed-loop systems, i.e., controllers along with a
 model of their physical environment, the plant, as shown in Fig.~\ref{fig:closed-system}.
@@
 }
- \caption{Closed Loop System. \label{fig:closed-system}}
+ \caption{Closed-Loop System. \label{fig:closed-system}}
 \end{figure*}
@@
 
-\paragraph{Stability analyses of closed loop systems} 
+\paragraph{Stability analyses of closed-loop systems} 
 In \cite{DBLP:conf/hybrid/RouxJG15}, the authors

### 2016-08-31 paper/paper.tex
removed some comments

@@
 %
-% ---------------------------------------------------------------------------------------------------------------
-% This .tex source is an example which *does* use
-% the .bib file (from which the .bbl file % is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission, you *NEED* to 'insert'
-% your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% ================= IF YOU HAVE QUESTIONS =======================
-% Questions regarding the SIGS styles, SIGS policies and
-% procedures, Conferences etc. should be sent to
-% Adrienne Griscti (griscti@acm.org)
-%
-% Technical questions _only_ to
-% Gerald Murray (murray@hq.acm.org)
-% ===============================================================
-%
-% For tracking purposes - this is V2.0 - May 2012
+% -------------------------------------------------------------------------------------------------% For tracking purposes - this is V2.0 - May 2012
 
@@
 \usepackage{pifont}
-%\usepackage{cite}
-\usepackage{pdflscape} % Experiments table is landscape
 \usepackage{longtable}
@@
 \setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
 
@@
 \isbn{}
-
-%Conference
-%\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}
-
-%\acmPrice{\$15.00}
 
@@
 %
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below. 
-%
-%% \begin{CCSXML}
-%% <ccs2012>
-%%  <concept>
-%%   <concept_id>10010520.10010553.10010562</concept_id>
-%%   <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-%%   <concept_significance>500</concept_significance>
-%%  </concept>
-%%  <concept>
-%%   <concept_id>10010520.10010575.10010755</concept_id>
-%%   <concept_desc>Computer systems organization~Redundancy</concept_desc>
-%%   <concept_significance>300</concept_significance>
-%%  </concept>
-%%  <concept>
-%%   <concept_id>10010520.10010553.10010554</concept_id>
-%%   <concept_desc>Computer systems organization~Robotics</concept_desc>
-%%   <concept_significance>100</concept_significance>
-%%  </concept>
-%%  <concept>
-%%   <concept_id>10003033.10003083.10003095</concept_id>
-%%   <concept_desc>Networks~Network reliability</concept_desc>
-%%   <concept_significance>100</concept_significance>
-%%  </concept>
-%% </ccs2012>  
-%% \end{CCSXML}
-
-%% \ccsdesc[500]{Computer systems organization~Embedded systems}
-%% \ccsdesc[300]{Computer systems organization~Redundancy}
-%% \ccsdesc{Computer systems organization~Robotics}
-%% \ccsdesc[100]{Networks~Network reliability}
-
-%
-% End generated code
-%
-
-%
 %  Use this command to print the description
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
 
-We are interested in the stability of closed-loop systems, i.e., controllers along with a
-model of their physical environment, the plant, as shown in Fig.~\ref{fig:closed-system}.
+We are interested in the stability of closed-loop systems, i.e.,
+controllers along with a model of their physical environment, the
+plant, as shown in Fig.~\ref{fig:closed-system}.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Overview}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Running Example}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Program Synthesis}
 
-We use CounterExample-Guided Inductive Synthesis (CEGIS), as illustrated in Fig~\ref{fig:CEGIS}.
+We use CounterExample-Guided Inductive Synthesis (CEGIS), as
+illustrated in Fig~\ref{fig:CEGIS}.
 
@@
 \end{figure*}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Experiments}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Related Works}
 
-\paragraph{Robustness analyses of closed-loop systems} The analysis in 
-\cite{DBLP:conf/hybrid/WangGRJF16}
-relies on an invariant computation
-on the discrete system dynamics.
+\paragraph{Robustness analyses of closed-loop systems}
+
+The analysis in \cite{DBLP:conf/hybrid/WangGRJF16} relies on an
+invariant computation on the discrete system dynamics.
 
 \paragraph{Stability analyses of closed-loop systems}
-In \cite{DBLP:conf/hybrid/RouxJG15}, the authors
-perform the analysis in the state space
-domain using Lyapunov-based quadratic invariants.
-In \cite{DBLP:journals/corr/PakmehrWJVF13}, Pakmehr et al. 
-design a control software verification framework for gas turbine engines.
+
+In \cite{DBLP:conf/hybrid/RouxJG15}, the authors perform the analysis
+in the state space domain using Lyapunov-based quadratic invariants.
+In \cite{DBLP:journals/corr/PakmehrWJVF13}, Pakmehr et al.  design a
+control software verification framework for gas turbine engines.
 
 \paragraph{Uses of CEGIS for control sysnthesis}
-In \cite{DBLP:conf/cdc/RavanbakhshS15}, Ravanbakhsh and Sankaranarayanan use
-CEGIS for the synthesis of switching
-controllers for stabilizing continuous-time plants.
 
+In \cite{DBLP:conf/cdc/RavanbakhshS15}, Ravanbakhsh and
+Sankaranarayanan use CEGIS for the synthesis of switching controllers
+for stabilizing continuous-time plants.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions}
 
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
 \bibliographystyle{abbrv}
-\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
-%
-% ACM needs 'a single self-contained file'!
-%
+\bibliography{paper}
+
 %APPENDICES are optional

### 2016-09-08 paper/paper.tex
First draft of related work

@@
 
-\paragraph{Robustness analyses of closed-loop systems}
+\paragraph{Robust synthesis of Linear Systems}
 
-The analysis in \cite{DBLP:conf/hybrid/WangGRJF16} relies on an
-invariant computation on the discrete system dynamics.
+The problem of parametric control synthesis based on stability measures for continous Linear Time Invariant (LTI) Single Input-Single Output (SISO) systems has been researched for several decades.
+On a theoretical level it is a solved problem\cite{wonham1967pole} for which researches continuously seek better results based on a number of properties in addition to stability.
+A vast range of pole placement techniques such as Moore's algorithm for eigenstructure assignment \cite{klein1977eigenvalue} or the more recent Linear Quadratic Regulator (LQR) \cite{bemporad2002explicit} have been used in several papers with increasing degrees of succes to ensure stability.
+The latter approach highlights the importance of conserving energy during the control process, which results amongst other things in lower running costs.
+Since real systems are subject to tolerance and noise as well as the need for economy, more recent works focus on the problems of achieving robust stability with minimum gain \cite{schmid2014unified,konigorski2012pole}.
+However, when extending the problem to digital controller synthesis, many of these techniques lack the ability to produce sound or stable results because they disregard the effects of quantization and rounding.
+Modern papers on implementations/synthesis of LTI digital controllers \cite{das2013lqr,ghosh2013fpga} focus on time discretization, failing to account for these error-inducing effects and can therefore result in digitally unstable systems that have been proven to be robustly stable in a continuous space.
+This situation demands the inclusion of formal methods to verify the effects of space discretization on the implementation of the controller.
 
-\paragraph{Stability analyses of closed-loop systems}
+\paragraph{Formal Verification of Linear Digital Controllers}
 
-In \cite{DBLP:conf/hybrid/RouxJG15}, the authors perform the analysis
-in the state space domain using Lyapunov-based quadratic invariants.
-In \cite{DBLP:journals/corr/PakmehrWJVF13}, Pakmehr et al.  design a
-control software verification framework for gas turbine engines.
+Researchers in formal verification methods of control systems have studied various effects of discretising the dynamics, including delayed response \cite{Duggirala2015}, and Finite Word Length (FWL) constraints with the objective to either verify (eg.
+\cite{daes20161}) or optimise (eg.
+\cite{oudjida2014design}) implementations.
+There are in fact two different problems arising from FWL effects.
+The first corresponds to the error in the dynamics caused by the inability of the hardware to represent the exact dynamics of the system whilst the second relates to rounding errors during computation.
+In \cite{fialho1994stability} a stability measure based on the error of the digital dynamics ensures that the FWL errors do not make the digital system unstable.
+A more recent approach \cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to directly model the digital controller so that the selected parameters are stable by design.
+Most papers following this line of verification focus on finding a correct implementation of a known desired controller, looking for optimal parameter representations using FWL but ignoring the effects of rounding errors due to issues of mathematical tractability.
+The analyses in \cite{DBLP:conf/hybrid/WangGRJF16,DBLP:conf/hybrid/RouxJG15} rely on an invariant computation on the discrete system dynamics using Semi-Definite Pogramming (SDP).
+Whilst the former uses BIBO properties to determine stability, the latter uses Lyapunov-based quadratic invariants.
+In both cases the SDP solver uses floating point arithmetic and soundness is checked by upper bounding the error.
 
-\paragraph{Uses of CEGIS for control sysnthesis}
+\paragraph{Robust Synthesis of FWL Digital Controllers}
 
-In \cite{DBLP:conf/cdc/RavanbakhshS15}, Ravanbakhsh and
-Sankaranarayanan use CEGIS for the synthesis of switching controllers
-for stabilizing continuous-time plants.
+To the authors' knowledge, there is no existing work on the automatic synthesis of digital controllers considering FWL effects.
+Parameter synthesis tools such as \cite{cimatti2013parameter} use bounded model checking and fixed point computations to find parameters based on user defined specifications, but they often operate in the continuous domain and are ill-suited for robust analysis since they have no direct means of evaluating robustness.
+Other tools such as \cite{economakos2016automated} are directly aimed at robust stability problems but fail to explore the effects of FWL in their implementation.
+In order to provide a correct by design controller, \cite{alur2016compositional} requires a user-defined finite state abstraction to synthesise a digital controller based on high level specifications.
+Whilst this approach directly overcomes the challenges presented by the FWL problem, it still requires error-prone user intervention.
+A different solution that looks at the other end of the scale is an approach that synthesises word lengths for know problems as developed in \cite{jha2013swati}, however this provides neither an optimal word synthesis nor a comprehensive solution for the problem.
+It is from this vacuum that we seek to explore a CEGIS approach to FWL controller synthesis.
+
+\paragraph{CEGIS}
+
+In recent years the development of program synthesis has found many ways to obtain correct by design programs from high level specifiactions.
+One such approach \cite{itzhaky2010simple} looks to inductively synthesise invariants to generate the desired programs.
+Since these digital programs are already constrained by designed to factors such as FWL, these approaches are ideal for the synthesis of parametric controllers.
+In \cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS for the synthesis of switching controllers for stabilizing continuous-time plants with polynomial dynamics.
+The work extends to its application on affine systems, finding its major challenge in the hardness of solving linear arithmetic on present SMT solvers.
+Since this approach uses switching states instead of linear dynamics in the digital controller, it entirely circumvents the FWL problem.
+It is also not suitable for the kind of control we seek to synthesise.
+What is needed in this regard is the combination of a synthesis engine with a control verification tool that addresses the challenges presented here in the form of FWL effects and stability measures for LTI SISO controllers.
+We take the former from \cite{} and the latter from \cite{daes20161} whilst enhancing the procedure by evaluating the quantaization effects of the Hardware interfaces (ADC/DAC) to obtain an accurate discrete time FWL representation of the continuous dynamics.
+
+%In \cite{DBLP:journals/corr/PakmehrWJVF13}, Pakmehr et al.  design a control software verification framework for gas turbine engines.
 

### 2016-09-09 paper/paper.tex
write running example

@@
 \usepackage{amsfonts}
-\usepackage{amsmath}
 \usepackage{multicol}
@@
 \section{Running Example}
+
+A classical cruise control example is extracted from the literature~\cite{Astrom08}, where the discrete plant model (with time step of $0.2$s) is represented by the following z-expression:
+
+\begin{equation}
+\label{Eq:running-example-plant}
+P\left(z\right) := \frac{0.0264}{z-0.9998}.
+\end{equation}
+
+Using an optimization tool, Wang {\it et al.}~\cite{DBLP:conf/hybrid/WangGRJF16} design a high-performance controller, which is characterized by the following z-expression:
+
+\begin{equation}
+\label{Eq:running-example-controller}
+C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
+\end{equation}
+
+The authors claim that this controller $C(z)$ is extremely stable for the discrete plant model $P(z)$.
+However, if implementation aspects are considered during verification, this controller becomes unstable.
+To properly implement $C(z)$, there is a function $FWL[\cdot]:\mathbb{R}^{k+l+2}\rightarrow Q[\mathbb{R}^{k+l+2}]$, which applies FWL effects to the controller $C(z)$, where $Q[\mathbb{R}]$ represents the quantized set of representable real numbers in the chosen implementation format $<k,l>$ ($k$ is the number of bits of the integer part and $l$ is the number of bits of the fractional part).
+
+For this particular example, the actual implementation of $C(z)$ using $<3,16>$ implementation format can be represented by the following z-expression:
+
+\begin{equation}
+\label{Eq:running-example-controller-quantized}
+C_{q}\left(z\right) := \frac{2.7199859619140625z^2 - 4.1529998779296875z + 1.89599609375}{z^2 - 1.843994140625z + 0.8495941162109375},
+\end{equation}
+
+\noindent which makes the system unstable in closed-loop using series loop configuration.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-09-09 paper/paper.tex
resized equation 3
+ macros

@@
 \usepackage{calc}
+\usepackage[dvipsnames]{xcolor}
 
@@
 \usepackage{wasysym}
+
+\include{macros}
 
@@
 However, if implementation aspects are considered during verification, this controller becomes unstable.
-To properly implement $C(z)$, there is a function $FWL[\cdot]:\mathbb{R}^{k+l+2}\rightarrow Q[\mathbb{R}^{k+l+2}]$, which applies FWL effects to the controller $C(z)$, where $Q[\mathbb{R}]$ represents the quantized set of representable real numbers in the chosen implementation format $<k,l>$ ($k$ is the number of bits of the integer part and $l$ is the number of bits of the fractional part).
+To properly implement $C(z)$, there is a function $FWL[\cdot]:\mathbb{R}^{k+l+2}\rightarrow Q[\mathbb{R}^{k+l+2}]$, which applies FWL effects to the controller $C(z)$, where $Q[\mathbb{R}]$ represents the quantized set of representable real numbers in the chosen implementation format
+\param{k}{l} ($k$ is the number of bits of the integer part and $l$ is the number of bits of the fractional part).
 
-For this particular example, the actual implementation of $C(z)$ using $<3,16>$ implementation format can be represented by the following z-expression:
+For this particular example, the actual implementation of $C(z)$ using \param{3}{16} implementation format can be represented by the following z-expression:
 
@@
 \label{Eq:running-example-controller-quantized}
-C_{q}\left(z\right) := \frac{2.7199859619140625z^2 - 4.1529998779296875z + 1.89599609375}{z^2 - 1.843994140625z + 0.8495941162109375},
+\resizebox{0.5\textwidth}{!}{
+$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2 - 4.1529998779296875z + 1.89599609375}{z^2 - 1.843994140625z + 0.8495941162109375},$
+}
 \end{equation}

### 2016-09-12 paper/paper.tex
include the experimental evaluation section

@@
 
-\noindent which makes the system unstable in closed-loop using series loop configuration.
+\noindent which makes the system unstable in closed-loop using the typical series loop configuration.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Experiments}
+\section{Experimental Evaluation}
+
+This section is split into three parts.
+Section~\ref{experimental-objectives} describes the experimental objectives, while Section~\ref{experimental-setup} discusses the experimental setup and the employed benchmarks.
+Section~\ref{experimental-results} describes the experimental results related to the application of CEGIS to standard control system benchmarks extracted from the literature.
+
+%---------------------------------
+\subsection{Objectives}
+\label{experimental-objectives}
+%---------------------------------
+
+%---------------------------------
+\subsection{Setup}
+\label{experimental-setup}
+%---------------------------------
+
+%---------------------------------
+\subsection{Results}
+\label{experimental-results}
+%---------------------------------
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Related Works}
+\section{Related Work}
 

### 2016-09-19 paper/paper.tex
add preliminaries

@@
 
-\title{TBD}
+\title{Synthesising and Verifying Closed-loop Digital Control Systems}
 %\subtitle{[Extended Abstract]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Overview}
+\section{Preliminaries}
+
+%------------------------------------
+\subsection{Verifying Closed-loop Control Systems}
+\label{verifying-closed-loop-control-systems}
+%------------------------------------
+
+In this study, the methodology used for verifying closed-loop digital control system is based on the Digital-System Verifier (DSVerifier)~\cite{IsmailBCFF15}, which checks the stability of control systems considering finite-word length (FWL) effects in the digital controller and uncertainty parameters in the plant model (plant intervals)~\cite{Bessa16}.
+Let $C(z)$ be a digital controller and $P(z)$ be a plant model given as
+
+\begin{align}
+\small
+\label{controller_plant_tf}
+C(z)&=\frac{\beta_{0}+\beta_{1}z^{-1}+...+\beta_{M_C}z^{-M_C}}{\alpha_{0}+\alpha_{1}z^{-1}+...+\alpha_{N_C}z^{-N_C}}, \\
+%\label{plant_tf}
+P(z)&=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
+\end{align}
+
+\noindent where $\beta$ and $\alpha$ are the controller's coefficients, $b$ and $a$ are the plant's coefficients, and $N$ and $M$ are the number of bits of the integer and fractional part, respectively.
+Note that $P(z)$ is a discrete model of a real (and continuous) plant, {\it i.e.}, a continuous model of the plant must be discretized to obtain the discrete equivalent coefficients $b$ and $a$~\cite{Astrom08}.
+Although there are several discretization methods available in the literature~\cite{Franklin15}, the zero-order hold (ZOH) discretization is more suitable for representing the sampling processes that are typically employed by hybrid systems~\cite{istepanian2012digital}.
+
+Let $C(z)$ and $P(z)$ transfer functions be arranged in vectors $c_0$ and $p_0$, respectively.
+For each $C(z)$ implementation, there is a function $FWL[\cdot]:\mathbb{R}^{N_C+M_C}\rightarrow Q[\mathbb{R}^{N_C+M_C}]$, which applies FWL effects to the controller $C(z)$, where $Q[\mathbb{R}]$ represents the quantized set of representable real numbers in the chosen implementation format \param{N_C}{_C}.
+The quantized controller parameters vector ($c$) is generated via $FWL[c_0]$.
+The uncertain plant parameters ($p$) can be expressed as
+
+\begin{equation}
+p = p_0 + \Delta{p} = \left [
+				\begin{tabular}{c}
+				$b_{0}+\Delta{b_{0}} ~ b_{1}+\Delta{b_{1}} ~ ... ~ b_{M_G}+\Delta{b_{M_G}}$ \\%~ 
+				$a_{0}+\Delta{a_{0}} ~ a_{1}+\Delta{a_{1}} ~ ... ~ a_{N_G}+\Delta{a_{N_G}}$
+				\end{tabular}
+				\right ],
+\end{equation}
+
+\vspace{1 mm} 
+\noindent where $\Delta{p}$ represents the plant uncertainties coefficients. The polynomial set of possible values of $p$ is denoted by $\mathfrak{P}$.
+
+%------------------------------------
+\subsection{DSVerifier Verification Flow}
+\label{verification-flow}
+%------------------------------------
+
+DSVerifier verification flow is shown in Fig.~\ref{DSVerifier_process}.
+Steps from $1$ to $5$ are performed by users and Steps A to D are automatically performed by DSVerifier, which accepts the digital controller transfer functions together with the plant model.
+For any digital controller, implementation details should be provided ({\it e.g.}, number of bits, realization, and sample time).
+
+\begin{figure*}[t]
+\centering
+\includegraphics[width=\textwidth]{figures/verification-flow.pdf}
+\caption{DSVerifier Verification Flow.}
+\label{DSVerifier_process}
+\end{figure*}
+
+In Step $1$, the user provides inputs $p_0$ and $\Delta{p}\%$ ({\it i.e.}, percentage form of $\Delta{p}$), which contain the plant model and the interval, respectively.
+In Step $2$, a digital controller must be designed with any preferred method, where $c_0$ is obtained.
+The controller numerical representation and realization form are chosen in Steps $3$ and $4$, respectively.
+In Step $5$, the user finally configures the verification parameters ({\it e.g.}, verification time, properties, and BMC tool).
+After that, DSVerifier verification engine performs an (automatic) verification of the desired property $\phi$ ({\it i.e.}, stability).
+The user steps described in Steps $1$-$5$ results in an ANSI-C code that should be used as an input for DSVerifier.
+
+In Step A, DSVerifier constructs a non-deterministic model to represent the plant family $\mathfrak{P}$ using $p_0$ and $\Delta{p}\%$, which are provided in Step $1$.
+DSVerifier then formulates $FWL[\cdot]$ in Step B using implementation details provided from Steps $2$ and $3$, and then computes $FWL[c_0]$ in Step C.
+Thus, DSVerifier builds an intermediate ANSI-C code for the digital system implementation, which is used as input for the model-checker, as pointed in Step D.
+
+This intermediate ANSI-C code model has three main modules: digital controller code to be embedded into the microprocessor; plant model code, which simulates the plant model dynamics considering uncertainties; and ``assert'' and ``assume'' statements, which control the verification flow.
+For the digital controller code, transfer functions coefficients are quantized and deterministic, and all operations use fixed-point arithmetic.
+In the plant model code, transfer function coefficients are not quantized, but represented with maximum precision based on double data-type variables; they are treated as non-deterministic variables to support model uncertainties.
+The directive ``assume'' bounds non-deterministic variables, {\it i.e.}, inputs and plant uncertain coefficients.
+
+Finally in the Step D, the translation of ANSI-C code into SAT/SMT formulae is done by a back-end model-checking tool ({\it e.g.}, CBMC~\cite{ClarkeKL04} or ESBMC~\cite{CordeiroFM12}).
+Here, DSVerifier symbolically checks a given property $\phi$ with respect to closed-loop systems, which are composed by $FWL[c_0]$ and every $p$ in $\mathfrak{P}$.
+If any property violation is found, then DSVerifier reports a counterexample, which contains system inputs or parametric deviations $\Delta{p}\%$ that lead the system to a failure.
+A successful verification result is reported if the system is safe with respect to $\phi$.
+In particular, the stability verification is complete and sound, since it does not depend on system outputs and inputs.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 However, if implementation aspects are considered during verification, this controller becomes unstable.
-To properly implement $C(z)$, there is a function $FWL[\cdot]:\mathbb{R}^{k+l+2}\rightarrow Q[\mathbb{R}^{k+l+2}]$, which applies FWL effects to the controller $C(z)$, where $Q[\mathbb{R}]$ represents the quantized set of representable real numbers in the chosen implementation format
-\param{k}{l} ($k$ is the number of bits of the integer part and $l$ is the number of bits of the fractional part).
 

### 2016-09-21 paper/paper.tex
+ general structure of the sec on program synthesis

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Running Example}
+\section{Running Example} \label{sec:running-ex}
 
@@
 
-We use CounterExample-Guided Inductive Synthesis (CEGIS), as
-illustrated in Fig~\ref{fig:CEGIS}.
+% We use CounterExample-Guided Inductive Synthesis (CEGIS), as
+% illustrated in Fig~\ref{fig:CEGIS}.
+
+In order to synthesise closed-loop digital control systems, we use a
+program synthesis engine.  Nowadays, such engines are used
+increasingly often in program verification
+\cite{DBLP:conf/cav/0001A14,DBLP:conf/lpar/DavidKL15}.  Our program
+synthesiser makes use of Counter-Example Guided Inductive Synthesis
+(CEGIS) \cite{sketch}.  We start by presenting its general
+architecture followed by describing the parts specific to control
+systems.
+
+%specialised it for stream refactoring.  
+% adding JST for stream refactoring
+
+\paragraph{General architecture of the program synthesiser}
+%
+The design of our synthesiser is given in
+Fig.~\ref{fig:CEGIS} and consists of two phases, {\sc
+Synthesise} and {\sc Verify}.
+
+\paragraph{Elements specific to control systems}
+
+\paragraph{Running example synthesis}
+We will illustrate our synthesis approach on the running example 
+in Sec.~\ref{sec:running-ex}.
+Our goal is to synthesise ...
+\cdsay{Finish this once the example is working.}
 

### 2016-09-21 paper/paper.tex
general description of the synthesiser

@@
 Fig.~\ref{fig:CEGIS} and consists of two phases, {\sc
-Synthesise} and {\sc Verify}.
+Synthesise} and {\sc Verify}, which interact via a finite set of test vectors {\sc inputs}.
+The {\sc synth} procedure tries to find an existential witness $P$
+that satisfies the specification $\sigma(x, P)$ for all $x$:
+%
+$\exists P . \forall x \in \text{\sc inputs} . \sigma(x, P)$
+
+If {\sc synthesise} succeeds in finding a witness $P$, this witness is a
+candidate solution to the full synthesis formula.  We pass this candidate
+solution to {\sc verify} which determines whether it does satisfy
+the specification on all inputs by checking satisfiability of the
+verification formula:
+%
+$\exists x . \lnot \sigma(x, P)$
+
+If this formula is unsatisfiable, the candidate solution is in fact a
+solution to the synthesis formula and so the algorithm terminates. 
+Otherwise, the witness $x$ is an input on which the candidate solution fails
+to meet the specification.  This witness $x$ is added to the {\sc inputs}
+set and the loop iterates again.  It is worth noting that each iteration of the
+loop adds a new input to the set of inputs being used for synthesis.  If
+the full set of inputs is finite, this means that the refinement loop
+can only iterate a finite number of times.
 
 \paragraph{Elements specific to control systems}
+\cdsay{discussion on the noise introduced by the plant modelling?}
 

### 2016-09-23 paper/paper.tex
error bound verification
add Iury's text related to UNCERTAINTY MODEL FOR QUANTIZATION ERROR

@@
 \usepackage{wasysym}
+
+\newtheorem{myassumption}{Assumption}
+\newtheorem{mylemma}{Lemma}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{A Uncertainty Model for Quantization Error} 
+\label{sec:uncertainty-model-quantization-error}
+
+In this study, an uncertain plant model $\hat{G}(z)$ is split into two terms:
+%
+\begin{equation}
+\label{eq:uncertainplant}
+\hat{G}(z)=G(z)+\Delta{G(z)},
+\end{equation}
+
+\noindent where $G(z)$ is the discretized nominal plant model and $\Delta{G(z)}$ is the additive uncertainty, which is related to parametric uncertainties~\cite{Bessa16}.
+Here, an uncertainty model to accommodate the quantization noise effects on $\hat{G}(z)$ is proposed.
+As a result, Eq.~\eqref{eq:uncertainplant} is rewritten as
+%
+\begin{equation}
+\label{eq:uncertainFWLplant}
+\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}+\Delta{G_{P}(z)},
+\end{equation}
+
+\noindent where $\Delta{G_{Q}(z)}$ represents the quantization uncertainty model and $\Delta{G_{P}(z)}$ describes the parametric uncertainty model.
+Thus, a model for $\Delta{G_{Q}(z)}$ that can represent the quantization noise effect in the plant output, and consequently the closed-loop system output, is proposed.
+For convenience, the parametric uncertainties will be despised here.
+
+Consider the closed-loop sampled system in Figure~\ref{fig:sampledsystem}, where $C(z)$ is the digital controller model, whose control output signal is quantized ($Q2$) and interpolated via a ZOH using digital-to-analog converter (DAC).
+$G(s)$ is the continuous-time model of the plant, from which output samples are taken and quantized ($Q1$) by means of an analog-to-digital converter (ADC) synchronized with the DAC.
+Each quantizer ($Q1$ and $Q2$) will present some contribution for the total quantization noise.
+%
+\begin{figure}[ht]
+\centering
+\includegraphics[width=\columnwidth]{figures/hsystembd.pdf}
+\caption{Sampled system.}
+\label{fig:sampledsystem}
+\end{figure}
+
+First, some assumptions have to be established to obtain a model for $\Delta{G_{Q}(z)}$.
+%
+\begin{myassumption}
+\label{whitenoise}
+The quantization noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the $Q2$) are white noises with zero mean.
+\end{myassumption}
+
+\begin{myassumption}
+The quantization noises $\nu_{1}$ and $\nu_{2}$ are uncorrelated with each other.
+\end{myassumption}
+
+\begin{myassumption}
+The DAC and ADC are synchronized, {\it i.e.}, there is no delay between sampling the plant output at ADC and updating the DAC accordingly.
+\end{myassumption}
+
+\begin{myassumption}
+The controller and plant are linear. In particular, the digital controller does not contain nonlinearities such as overflows, saturation, and limit-cycle oscillations.
+\end{myassumption}
+
+\begin{myassumption}
+The DAC interpolator is an ideal ZOH; it takes the discrete value of control signal $u(k)$ at instant $k$ and produces a rectangular pulse of height $u(k)$ and width equal to the sample time $T$.
+\end{myassumption}
+
+Given those assumptions, the present approach is further based on the following lemmas.
+%
+\begin{mylemma}
+\cite{widrow1956} The second moment (variance) of the PDF of quantization noise is given by \textcolor{red}{expand the acronym PDF}
+\begin{equation}
+\label{eq:variancelemma}
+\sigma_{Q}^{2}=\frac{q^{2}}{12},
+\end{equation}
+\end{mylemma}
+
+\noindent where $q$ is the step size of quantizer.
+
+\begin{mylemma} \cite{astrom1997computer}
+The pulse transfer function $G(z)$ is equivalent at the sample times to the continuous transfer function $G(s)$ driven by ZOH. This pulse transfer function can be computed as
+\begin{equation}
+\label{eq:pulsetf}
+G(z)=(1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
+\end{equation}
+\end{mylemma}
+
+Considering the quantization noise $\nu(k)$ as an output error in the discrete plant model, {\it i.e.}, it does not affect the plant dynamics, but its output samples, it is easy to prove that $\Delta{G_{Q}(z)}$ can be obtained from
+%
+\begin{equation}
+\label{eq:quantization_tf}
+\Delta{G_{Q}(z)}=\frac{\nu(z)}{U(z)},
+\end{equation}
+
+\noindent where $\nu(z)$ is the z-transform of the random process $\nu(k)$, which can be calculated through the power spectral density of $\nu(k)$~\cite{poularikas2000transforms}.
+Thus, the $\Delta{G_{Q}(z)}$ can expressed as
+%
+\begin{equation}
+\label{eq:deltag_var}
+\Delta{G_{Q}(z)}=\frac{\sigma_{Q}^{2}}{U(z)},
+\end{equation}
+
+\noindent where $\sigma_{Q}^{2}$ is the variance of quantization noise and $U(z)$ is the z-transform of control signal ({\it i.e.}, the z-transform of the signal from the digital controller), which is provided to the plant by means of ZOH.
+%
+\begin{proof}
+Suppose that the plant discrete model in Figure~\ref{fig:sampledsystem} can be represented by the following pulse transfer function (without quantization noise effect): 
+\begin{equation}
+\label{eq:tfwithout}
+G(z)=\frac{Y(z)}{U(z)}=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M}z^{-M}}{1+a_{1}z^{-1}+a_{2}z^{-2}+\cdots+a_{N}z^{-N}},
+\end{equation}
+\noindent where $Y(z)$ is the z-transform of the plant output signal without noise $y(k)$, $U(z)$ is the z-transform of the control signal, which is provided to the plant, $A(z)$ and $B(z)$ are the plant pulse transfer function numerator and denominator, respectively.
+
+Considering the quantization noise $\nu(k)$ as an output error in the discrete plant model, an additive noise in the plant output $y(k)$ resulting in the noisy output $\hat{y}(k)$ can be represented as
+%
+\begin{equation}
+\hat{y}(k)=y(k)+\nu(k).
+\end{equation}
+
+Note that the model in Eq.~\eqref{eq:tfwithout} is equivalent to the following difference equation:
+%
+\begin{equation}
+\begin{split}
+y(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
++b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M),
+\end{split}
+\end{equation}
+
+\noindent and consequently $\hat{y}(k)$ can be represented by the following difference equation:
+%
+\begin{equation}
+\label{eq:differencewithnoise}
+\begin{split}
+\hat{y}(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
++b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M)+\nu(k).
+\end{split}
+\end{equation}
+
+The z-transform of Eq.~\eqref{eq:differencewithnoise} is
+%
+\begin{equation}
+\begin{split}
+\hat{Y}(z)=(-a_{1}z^{-1}-a_{2}z^{-2}-\cdots-a_{N}z^{-N})Y(z)\\
++(b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M}z^{-M})U(z)+\nu(z),
+\end{split}
+\end{equation}
+dividing both sides by $U(z)$, it is equivalent to:
+\begin{equation}
+\frac{\hat{Y}(z)}{U(z)}=\hat{G}(z)=[1-A(z)]G(z)+U(z)B(z)+\frac{\nu(z)}{U(z)}.
+\end{equation}
+
+Considering $\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}$ and Eq.~\eqref{eq:tfwithout}, the intended expression can be obtained as
+%
+\begin{equation}
+\Delta{G_{Q}(z)}=\frac{\nu(z)}{U(z)} 
+\end{equation}
+\end{proof}
+
+Eq.~\eqref{eq:deltag_var} indicates that the modeling of quantization noise effect on the plant transfer function demands an estimation of the variance of quantization noise $\sigma_{Q}^{2}$.
+To obtain such estimation, the methodology presented by Widrow and Koll\'ar~\cite{widrow2008quantization} is used.
+The authors provide an algorithm for computing the mean square of the output noise due to $Q1$ and $Q2$.
+Considering that each quantizer contribution can be represented by a white noise with zero mean (Assumption~\ref{whitenoise}), the mean square can be considered as the variance of noise ($\sigma_{Q}^{2}$), which can be calculated as
+%
+\begin{equation}
+\sigma_{Q}^{2}=\frac{\lambda_{1}^{2}\cdot \sum {h_{Q1}^{2}}+\lambda_{2}^{2}\cdot \sum {h_{Q2}^{2}}}{12},
+\end{equation}
+
+\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factor for the quantization $Q1$ and $Q2$, respectively; and $\sum {h_{Q1}^{2}}$ and $\sum {h_{Q2}^{2}}$ are the squares sums of the impulse response obtained by means of a transfer function from $Q1$ and $Q2$ to the plant output, respectively.
+
+The transfer functions $H_{Q1}(z)$ and $H_{Q2}(z)$, from which the squares sums of the impulse response are needed, can be obtained through the analysis of the system in Figure~\ref{fig:sampledsystem}.
+Considering that the quantizer $Q1$ is the source of a white noise with zero mean $\nu_{1}$ and $Q2$ is the source of a white noise with zero mean $\nu_{2}$, the following equation can be written for the system in Figure~\ref{fig:sampledsystem}
+%
+\begin{equation}
+\resizebox{0.48\textwidth}{!}{
+$\hat{Y}(z)=\nu_{1}(z)C(z)G(z)+\nu_{2}(z)G(z)+R(z)C(z)G(z)-\hat{Y}(z)C(z)G(z),$
+}
+\end{equation}
+
+\noindent which can be rewritten as
+%
+\begin{equation}
+\label{eq:outputfunctions}
+\resizebox{0.48\textwidth}{!}{
+$\hat{Y}(z)=\frac{C(z)G(z)}{1+C(z)G(z)}R(z)+\frac{C(z)G(z)}{1+C(z)G(z)}\nu_{1}(z) \\
++\frac{G(z)}{1+C(z)G(z)}\nu_{2}(z).$
+}
+\end{equation}
+
+Thus, $H_{Q1}(z)$ and $H_{Q2}(z)$ can be extracted from Eq.~\eqref{eq:outputfunctions}:
+\begin{equation}
+H_{Q1}(z)=\frac{C(z)G(z)}{1+C(z)G(z)},
+\end{equation}
+and
+\begin{equation}
+H_{Q2}(z)=\frac{G(z)}{1+C(z)G(z)}.
+\end{equation}
+
+These equations are sufficient for computing $\sigma_{Q}^{2}$.
+However, there is still a gap for a complete model for $\Delta{G_{Q}(z)}$ in Eq.~\eqref{eq:deltag_var}, {\it i.e.}, the z-transform of control action $U(z)$.
+This indicates that the quantization noise effect on a discrete plant model mainly depends on three main factors:
+%
+\begin{itemize}
+\item \textbf{Sample time:} the sample time effect is reflected over pulse transfer function that covers the effects of DAC ant its interpolator (ZOH);
+\item \textbf{ADC and DAC step: } these are the main component of quantization noise power, but an $8$-bits converter already reduces the effect of quantization noises in the output for negligible values.
+\item \textbf{Signal-to-noise ratio (SNR): } the dependence on the value of $U(z)$ shows the importance of the SNR for handling quantization noise; for a high SNR of the digital controller, the quantization effect is negligible.
+This happens during the transient of the system, when high control actions are employed.
+However, it can be relevant during the steady state.
+A digital controller with integral action might be sufficient for eliminating such influence on the steady state.
+\end{itemize}
+
+An alternative expression for $\Delta{G_{Q}(z)}$ can be obtained from Eq.~\eqref{eq:deltag_var}, transforming it into a function of the reference $R(z)$.
+Once $U(z)$ is the control signal obtained via digital controller $C(z)$ and error signal, {\it i.e.},
+%
+\begin{equation}
+U(z)=C(z)\cdot[R(z)-Y(z)],
+\end{equation}
+
+\noindent where $Y(z)$ is the first term of Eq.~\eqref{eq:outputfunctions}, thus:
+\begin{equation}
+\label{eq:controlsignal}
+\resizebox{0.48\textwidth}{!}{
+$U(z)=C(z)\cdot \left[R(z)-\frac{C(z)G(z)}{1+C(z)G(z)}R(z)\right]=\frac{C(z)}{1+C(z)G(z)}R(z).$
+}
+\end{equation}
+
+Substituting Eq.~\eqref{eq:controlsignal} in Eq.~\eqref{eq:deltag_var}, a model for $\Delta{G_{Q}(z)}$ depending on $R(z)$ can be obtained:
+%
+\begin{equation}
+\Delta{G_{Q}(z)}=\sigma^{2}_{Q}\cdot \frac{1+C(z)G(z)}{C(z)} \cdot \frac{1}{R(z)},
+\end{equation}
+
+\noindent where $R(z)$ can be considered as a step signal (for stabilization purpose) with height equal to $r$, which can be rewritten as
+\begin{equation}
+\Delta{G_{Q}(z)}=\frac{\sigma^{2}_{Q}}{r}\cdot \frac{1+C(z)G(z)}{C(z)} \cdot \frac{z-1}{z}.
+\end{equation}
+
+A more confident description of $\Delta{G_{Q}(z)}$ can be obtained considering FWL effects on digital controller coefficients, as described in Bessa {\it et al.}~\cite{Bessa16}, {\it i.e.}, using $FWL[C(z)]$ instead of the nominal $C(z)$:
+%
+\begin{equation}
+\label{eq:deltaG_final}
+\Delta{G_{Q}(z)}=\frac{\sigma^{2}_{Q}}{r}\cdot \frac{1+FWL[C(z)]G(z)}{FWL[C(z)]} \cdot \frac{z-1}{z}.
+\end{equation}
+
+Finally, Eq.~\eqref{eq:deltaG_final} is a suitable frequency domain model for quantization noise effects on closed-loop systems.
+This model depends on the plant pulse transfer function ($G(z)$), which is described by Eq.~\eqref{eq:pulsetf}, the height of step reference signal $r$, and the digital controller model.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Running Example} \label{sec:running-ex}
@@
 \noindent which makes the system unstable in closed-loop using the typical series loop configuration.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section{Error Bound Verification}
+
+%As described in the literature, computation using FWL leads to rounding and truncation errors~\cite{Oppenheim1999}.
+In the present work, impairments present on a closed-loop  system output, due to coefficient rounding and arithmetic-operation results, are considered.
+Let $x$ be a real number and $x^*$ be a floating-point representation of $x$.
+The absolute error $\epsilon$, due to the rounding of $x$ represented in floating-point as $x^*$, is
+%
+%\begin{equation} \label{absolute-error}
+%x^* = x + \epsilon,
+%\end{equation}
+
+%\noindent and the relative error $\delta$ by
+%
+%\begin{equation} \label{relative-error}
+%x^* = x\left(1+\delta\right).
+%\end{equation}
+
+%The verification of output error bound is proposed, where the output of a closed-loop system, implemented with reduced-word-length floating-point representation, is compared with a reference output of the same structures, implemented using real variables.
+
+%Thus, considering that the number of precision bits $l_{d}$ in reference models is higher than in designed models, the quantization error $E_{r}$ is given by
+%\begin{equation} \label{errorfixlimits}
+%-2^{-l-1} + 2^{-l_{d}-1} \leq E_{r} \leq 2^{-l-1} - 2^{-l_{d}-1}.
+%\end{equation}
+
+%The expression above shows that the error, computed with the proposed method, is affected by the precision of the reference model.
+
+%For the reduced floating-point models, the computed values are saturated to the maximum representable number on overflow, or to the minimum on underflow; the same input is applied to both models.
+The input vector uses non-deterministic values from $\{ 2^{k-1}-2^{-l}, 2^{-l}, 0, -2^{-l}, 2^{k-1} \}$, that is, values for maximum and minimum amplitudes of the input signal.
+So, errors due to quantization and saturation are explored.
+
+%During closed-loop operation unrolling, the cumulative error can increase beyond the quantization-error interval.
+The following literal is then generated, in order to check whether the output error is in accordance with an acceptable margin:
+%\begin{equation} \label{errorcheck}
+%	l_{no\_error} \Leftrightarrow \arrowvert y - y_{d} \arrowvert \leq M \cdot 2^{-l-1},
+%\end{equation}
+
+%\noindent where $y$ is the output of the designed system, $y_{d}$ is the output of the double precision system, and $M~2^{-l-1}$ is the tolerance margin.
+The verification process searches for the negation of this literal.
+When such a counterexample is found, it indicates that the output error is higher than expected for that controller realization.
 

### 2016-09-23 paper/paper.tex
replace "p" by "g" to describe the physical plant

@@
 In this study, the methodology used for verifying closed-loop digital control system is based on the Digital-System Verifier (DSVerifier)~\cite{IsmailBCFF15}, which checks the stability of control systems considering finite-word length (FWL) effects in the digital controller and uncertainty parameters in the plant model (plant intervals)~\cite{Bessa16}.
-Let $C(z)$ be a digital controller and $P(z)$ be a plant model given as
+Let $C(z)$ be a digital controller and $G(z)$ be a plant model given as
 
@@
 %\label{plant_tf}
-P(z)&=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
+G(z)&=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
 \end{align}
@@
 \noindent where $\beta$ and $\alpha$ are the controller's coefficients, $b$ and $a$ are the plant's coefficients, and $N$ and $M$ are the number of bits of the integer and fractional part, respectively.
-Note that $P(z)$ is a discrete model of a real (and continuous) plant, {\it i.e.}, a continuous model of the plant must be discretized to obtain the discrete equivalent coefficients $b$ and $a$~\cite{Astrom08}.
+Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it i.e.}, a continuous model of the plant must be discretized to obtain the discrete equivalent coefficients $b$ and $a$~\cite{Astrom08}.
 Although there are several discretization methods available in the literature~\cite{Franklin15}, the zero-order hold (ZOH) discretization is more suitable for representing the sampling processes that are typically employed by hybrid systems~\cite{istepanian2012digital}.
 
-Let $C(z)$ and $P(z)$ transfer functions be arranged in vectors $c_0$ and $p_0$, respectively.
-For each $C(z)$ implementation, there is a function $FWL[\cdot]:\mathbb{R}^{N_C+M_C}\rightarrow Q[\mathbb{R}^{N_C+M_C}]$, which applies FWL effects to the controller $C(z)$, where $Q[\mathbb{R}]$ represents the quantized set of representable real numbers in the chosen implementation format \param{N_C}{_C}.
+Let $C(z)$ and $G(z)$ transfer functions be arranged in vectors $c_0$ and $g_0$, respectively.
+For each $C(z)$ implementation, there is a function $FWL[\cdot]:\mathbb{R}^{N_C+M_C}\rightarrow Q[\mathbb{R}^{N_C+M_C}]$, which applies FWL effects to the controller $C(z)$, where $Q[\mathbb{R}]$ represents the quantized set of representable real numbers in the chosen implementation format \param{N_C}{M_C}.
 The quantized controller parameters vector ($c$) is generated via $FWL[c_0]$.
-The uncertain plant parameters ($p$) can be expressed as
+The uncertain plant parameters ($g$) can be expressed as
 
 \begin{equation}
-p = p_0 + \Delta{p} = \left [
+g = g_0 + \Delta{g} = \left [
 				\begin{tabular}{c}
@@
 \vspace{1 mm} 
-\noindent where $\Delta{p}$ represents the plant uncertainties coefficients. The polynomial set of possible values of $p$ is denoted by $\mathfrak{P}$.
+\noindent where $\Delta{g}$ represents the plant uncertainties coefficients. The polynomial set of possible values of $g$ is denoted by $\mathfrak{G}$.
 
@@
 
-In Step $1$, the user provides inputs $p_0$ and $\Delta{p}\%$ ({\it i.e.}, percentage form of $\Delta{p}$), which contain the plant model and the interval, respectively.
+In Step $1$, the user provides inputs $g_0$ and $\Delta{g}\%$ ({\it i.e.}, percentage form of $\Delta{g}$), which contain the plant model and the interval, respectively.
 In Step $2$, a digital controller must be designed with any preferred method, where $c_0$ is obtained.
@@
 
-In Step A, DSVerifier constructs a non-deterministic model to represent the plant family $\mathfrak{P}$ using $p_0$ and $\Delta{p}\%$, which are provided in Step $1$.
+In Step A, DSVerifier constructs a non-deterministic model to represent the plant family $\mathfrak{G}$ using $g_0$ and $\Delta{g}\%$, which are provided in Step $1$.
 DSVerifier then formulates $FWL[\cdot]$ in Step B using implementation details provided from Steps $2$ and $3$, and then computes $FWL[c_0]$ in Step C.
@@
 For the digital controller code, transfer functions coefficients are quantized and deterministic, and all operations use fixed-point arithmetic.
-In the plant model code, transfer function coefficients are not quantized, but represented with maximum precision based on double data-type variables; they are treated as non-deterministic variables to support model uncertainties.
+\textcolor{red}{In the plant model code, transfer function coefficients are not quantized, but represented with maximum precision based on float data-type variables}; they are treated as non-deterministic variables to support model uncertainties.
 The directive ``assume'' bounds non-deterministic variables, {\it i.e.}, inputs and plant uncertain coefficients.
@@
 Finally in the Step D, the translation of ANSI-C code into SAT/SMT formulae is done by a back-end model-checking tool ({\it e.g.}, CBMC~\cite{ClarkeKL04} or ESBMC~\cite{CordeiroFM12}).
-Here, DSVerifier symbolically checks a given property $\phi$ with respect to closed-loop systems, which are composed by $FWL[c_0]$ and every $p$ in $\mathfrak{P}$.
-If any property violation is found, then DSVerifier reports a counterexample, which contains system inputs or parametric deviations $\Delta{p}\%$ that lead the system to a failure.
+Here, DSVerifier symbolically checks a given property $\phi$ with respect to closed-loop systems, which are composed by $FWL[c_0]$ and every $g$ in $\mathfrak{G}$.
+If any property violation is found, then DSVerifier reports a counterexample, which contains system inputs or parametric deviations $\Delta{g}\%$ that lead the system to a failure.
 A successful verification result is reported if the system is safe with respect to $\phi$.

### 2016-09-23 paper/paper.tex
cleanout
crlf -> lf
line breaks

@@
-% This is "sig-alternate.tex" V2.1 April 2013
-% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
-%
-% This example file demonstrates the use of the 'sig-alternate.cls'
-% V2.5 LaTeX2e document class file. It is for those submitting
-% articles to ACM Conference Proceedings WHO DO NOT WISH TO
-% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
-% The 'sig-alternate.cls' file will produce a similar-looking,
-% albeit, 'tighter' paper resulting in, invariably, fewer pages.
-%
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V2.5) produces:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) NO page numbers
-%
-% as against the acm_proc_article-sp.cls file which
-% DOES NOT produce 1) thru' 3) above.
-%
-% Using 'sig-alternate.cls' you have control, however, from within
-% the source .tex file, over both the CopyrightYear
-% (defaulted to 200X) and the ACM Copyright Data
-% (defaulted to X-XXXXX-XX-X/XX/XX).
-% e.g.
-% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
-% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
-%
-% -------------------------------------------------------------------------------------------------% For tracking purposes - this is V2.0 - May 2012
-
 \documentclass{sig-alternate-05-2015}
@@
 
-In this study, the methodology used for verifying closed-loop digital control system is based on the Digital-System Verifier (DSVerifier)~\cite{IsmailBCFF15}, which checks the stability of control systems considering finite-word length (FWL) effects in the digital controller and uncertainty parameters in the plant model (plant intervals)~\cite{Bessa16}.
-Let $C(z)$ be a digital controller and $G(z)$ be a plant model given as
+In this study, the methodology used for verifying closed-loop digital
+control system is based on the Digital-System Verifier
+(DSVerifier)~\cite{IsmailBCFF15}, which checks the stability of control
+systems considering finite-word length (FWL) effects in the digital
+controller and uncertainty parameters in the plant model (plant
+intervals)~\cite{Bessa16}.  Let $C(z)$ be a digital controller and $G(z)$ be
+a plant model given as
 
@@
 DSVerifier verification flow is shown in Fig.~\ref{DSVerifier_process}. 
-Steps from $1$ to $5$ are performed by users and Steps A to D are automatically performed by DSVerifier, which accepts the digital controller transfer functions together with the plant model.
-For any digital controller, implementation details should be provided ({\it e.g.}, number of bits, realization, and sample time).
+Steps from $1$ to $5$ are performed by users and Steps A to D are
+automatically performed by DSVerifier, which accepts the digital controller
+transfer functions together with the plant model.  For any digital
+controller, implementation details should be provided ({\it e.g.}, number of
+bits, realization, and sample time).
 
@@
 
-In Step $1$, the user provides inputs $g_0$ and $\Delta{g}\%$ ({\it i.e.}, percentage form of $\Delta{g}$), which contain the plant model and the interval, respectively.
-In Step $2$, a digital controller must be designed with any preferred method, where $c_0$ is obtained.
-The controller numerical representation and realization form are chosen in Steps $3$ and $4$, respectively.
-In Step $5$, the user finally configures the verification parameters ({\it e.g.}, verification time, properties, and BMC tool).
-After that, DSVerifier verification engine performs an (automatic) verification of the desired property $\phi$ ({\it i.e.}, stability).
-The user steps described in Steps $1$-$5$ results in an ANSI-C code that should be used as an input for DSVerifier.
+In Step $1$, the user provides inputs $g_0$ and $\Delta{g}\%$ ({\it i.e.},
+percentage form of $\Delta{g}$), which contain the plant model and the
+interval, respectively.  In Step $2$, a digital controller must be designed
+with any preferred method, where $c_0$ is obtained.  The controller
+numerical representation and realization form are chosen in Steps $3$ and
+$4$, respectively.  In Step $5$, the user finally configures the
+verification parameters ({\it e.g.}, verification time, properties, and BMC
+tool).  After that, DSVerifier verification engine performs an (automatic)
+verification of the desired property $\phi$ ({\it i.e.}, stability).  The
+user steps described in Steps $1$-$5$ results in an ANSI-C code that should
+be used as an input for DSVerifier.
 
-In Step A, DSVerifier constructs a non-deterministic model to represent the plant family $\mathfrak{G}$ using $g_0$ and $\Delta{g}\%$, which are provided in Step $1$.
-DSVerifier then formulates $FWL[\cdot]$ in Step B using implementation details provided from Steps $2$ and $3$, and then computes $FWL[c_0]$ in Step C.
-Thus, DSVerifier builds an intermediate ANSI-C code for the digital system implementation, which is used as input for the model-checker, as pointed in Step D.
+In Step A, DSVerifier constructs a non-deterministic model to represent the
+plant family $\mathfrak{G}$ using $g_0$ and $\Delta{g}\%$, which are
+provided in Step $1$.  DSVerifier then formulates $FWL[\cdot]$ in Step B
+using implementation details provided from Steps $2$ and $3$, and then
+computes $FWL[c_0]$ in Step C.  Thus, DSVerifier builds an intermediate
+ANSI-C code for the digital system implementation, which is used as input
+for the model-checker, as pointed in Step D.
 
-This intermediate ANSI-C code model has three main modules: digital controller code to be embedded into the microprocessor; plant model code, which simulates the plant model dynamics considering uncertainties; and ``assert'' and ``assume'' statements, which control the verification flow.
-For the digital controller code, transfer functions coefficients are quantized and deterministic, and all operations use fixed-point arithmetic.
-\textcolor{red}{In the plant model code, transfer function coefficients are not quantized, but represented with maximum precision based on float data-type variables}; they are treated as non-deterministic variables to support model uncertainties.
-The directive ``assume'' bounds non-deterministic variables, {\it i.e.}, inputs and plant uncertain coefficients.
+This intermediate ANSI-C code model has three main modules: digital
+controller code to be embedded into the microprocessor; plant model code,
+which simulates the plant model dynamics considering uncertainties; and
+``assert'' and ``assume'' statements, which control the verification flow. 
+For the digital controller code, transfer functions coefficients are
+quantized and deterministic, and all operations use fixed-point arithmetic. 
+\textcolor{red}{In the plant model code, transfer function coefficients are
+not quantized, but represented with maximum precision based on float
+data-type variables}; they are treated as non-deterministic variables to
+support model uncertainties.  The directive ``assume'' bounds
+non-deterministic variables, {\it i.e.}, inputs and plant uncertain
+coefficients.
 
-Finally in the Step D, the translation of ANSI-C code into SAT/SMT formulae is done by a back-end model-checking tool ({\it e.g.}, CBMC~\cite{ClarkeKL04} or ESBMC~\cite{CordeiroFM12}).
-Here, DSVerifier symbolically checks a given property $\phi$ with respect to closed-loop systems, which are composed by $FWL[c_0]$ and every $g$ in $\mathfrak{G}$.
-If any property violation is found, then DSVerifier reports a counterexample, which contains system inputs or parametric deviations $\Delta{g}\%$ that lead the system to a failure.
-A successful verification result is reported if the system is safe with respect to $\phi$.
-In particular, the stability verification is complete and sound, since it does not depend on system outputs and inputs.
+Finally in the Step D, the translation of ANSI-C code into SAT/SMT formulae
+is done by a back-end model-checking tool ({\it e.g.},
+CBMC~\cite{ClarkeKL04} or ESBMC~\cite{CordeiroFM12}).  Here, DSVerifier
+symbolically checks a given property $\phi$ with respect to closed-loop
+systems, which are composed by $FWL[c_0]$ and every $g$ in $\mathfrak{G}$. 
+If any property violation is found, then DSVerifier reports a
+counterexample, which contains system inputs or parametric deviations
+$\Delta{g}\%$ that lead the system to a failure.  A successful verification
+result is reported if the system is safe with respect to $\phi$.  In
+particular, the stability verification is complete and sound, since it does
+not depend on system outputs and inputs.
 
@@
 
-\noindent where $G(z)$ is the discretized nominal plant model and $\Delta{G(z)}$ is the additive uncertainty, which is related to parametric uncertainties~\cite{Bessa16}.
-Here, an uncertainty model to accommodate the quantization noise effects on $\hat{G}(z)$ is proposed.
-As a result, Eq.~\eqref{eq:uncertainplant} is rewritten as
+\noindent where $G(z)$ is the discretized nominal plant model and
+$\Delta{G(z)}$ is the additive uncertainty, which is related to parametric
+uncertainties~\cite{Bessa16}.  Here, an uncertainty model to accommodate the
+quantization noise effects on $\hat{G}(z)$ is proposed.  As a result,
+Eq.~\eqref{eq:uncertainplant} is rewritten as
 %
@@
 
-\noindent where $\Delta{G_{Q}(z)}$ represents the quantization uncertainty model and $\Delta{G_{P}(z)}$ describes the parametric uncertainty model.
-Thus, a model for $\Delta{G_{Q}(z)}$ that can represent the quantization noise effect in the plant output, and consequently the closed-loop system output, is proposed.
-For convenience, the parametric uncertainties will be despised here.
+\noindent where $\Delta{G_{Q}(z)}$ represents the quantization uncertainty
+model and $\Delta{G_{P}(z)}$ describes the parametric uncertainty model. 
+Thus, a model for $\Delta{G_{Q}(z)}$ that can represent the quantization
+noise effect in the plant output, and consequently the closed-loop system
+output, is proposed.  For convenience, the parametric uncertainties will be
+despised here.
 
-Consider the closed-loop sampled system in Figure~\ref{fig:sampledsystem}, where $C(z)$ is the digital controller model, whose control output signal is quantized ($Q2$) and interpolated via a ZOH using digital-to-analog converter (DAC).
-$G(s)$ is the continuous-time model of the plant, from which output samples are taken and quantized ($Q1$) by means of an analog-to-digital converter (ADC) synchronized with the DAC.
-Each quantizer ($Q1$ and $Q2$) will present some contribution for the total quantization noise.
+Consider the closed-loop sampled system in Figure~\ref{fig:sampledsystem},
+where $C(z)$ is the digital controller model, whose control output signal is
+quantized ($Q2$) and interpolated via a ZOH using digital-to-analog
+converter (DAC).  $G(s)$ is the continuous-time model of the plant, from
+which output samples are taken and quantized ($Q1$) by means of an
+analog-to-digital converter (ADC) synchronized with the DAC.  Each quantizer
+($Q1$ and $Q2$) will present some contribution for the total quantization
+noise.
 %
@@
 
-First, some assumptions have to be established to obtain a model for $\Delta{G_{Q}(z)}$.
+First, some assumptions have to be established to obtain a model for
+$\Delta{G_{Q}(z)}$.
 %
@@
 \label{whitenoise}
-The quantization noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the $Q2$) are white noises with zero mean.
+%
+The quantization noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
+$Q2$) are white noises with zero mean.
+%
 \end{myassumption}
@@
 \begin{myassumption}
-The DAC and ADC are synchronized, {\it i.e.}, there is no delay between sampling the plant output at ADC and updating the DAC accordingly.
+%
+The DAC and ADC are synchronized, {\it i.e.}, there is no delay between
+sampling the plant output at ADC and updating the DAC accordingly.
+%
 \end{myassumption}
@@
 \begin{myassumption}
-The controller and plant are linear. In particular, the digital controller does not contain nonlinearities such as overflows, saturation, and limit-cycle oscillations.
+%
+The controller and plant are linear.  In particular, the digital controller
+does not contain nonlinearities such as overflows, saturation, and
+limit-cycle oscillations.
+%
 \end{myassumption}
@@
 \begin{myassumption}
-The DAC interpolator is an ideal ZOH; it takes the discrete value of control signal $u(k)$ at instant $k$ and produces a rectangular pulse of height $u(k)$ and width equal to the sample time $T$.
+%
+The DAC interpolator is an ideal ZOH; it takes the discrete value of control
+signal $u(k)$ at instant $k$ and produces a rectangular pulse of height
+$u(k)$ and width equal to the sample time $T$.
+%
 \end{myassumption}
@@
 \begin{mylemma}
-\cite{widrow1956} The second moment (variance) of the PDF of quantization noise is given by \textcolor{red}{expand the acronym PDF}
+%
+\cite{widrow1956} The second moment (variance) of the PDF of quantization
+noise is given by \textcolor{red}{expand the acronym PDF}
+%
 \begin{equation}
@@
 \begin{mylemma} \cite{astrom1997computer}
-The pulse transfer function $G(z)$ is equivalent at the sample times to the continuous transfer function $G(s)$ driven by ZOH. This pulse transfer function can be computed as
+%
+The pulse transfer function $G(z)$ is equivalent at the sample times to the
+continuous transfer function $G(s)$ driven by ZOH.  This pulse transfer
+function can be computed as
+%
 \begin{equation}
@@
 
-Considering the quantization noise $\nu(k)$ as an output error in the discrete plant model, {\it i.e.}, it does not affect the plant dynamics, but its output samples, it is easy to prove that $\Delta{G_{Q}(z)}$ can be obtained from
+Considering the quantization noise $\nu(k)$ as an output error in the
+discrete plant model, {\it i.e.}, it does not affect the plant dynamics, but
+its output samples, it is easy to prove that $\Delta{G_{Q}(z)}$ can be
+obtained from
 %
@@
 
-\noindent where $\nu(z)$ is the z-transform of the random process $\nu(k)$, which can be calculated through the power spectral density of $\nu(k)$~\cite{poularikas2000transforms}.
-Thus, the $\Delta{G_{Q}(z)}$ can expressed as
+\noindent where $\nu(z)$ is the z-transform of the random process $\nu(k)$,
+which can be calculated through the power spectral density of
+$\nu(k)$~\cite{poularikas2000transforms}.  Thus, the $\Delta{G_{Q}(z)}$ can
+expressed as
 %
@@
 
-\noindent where $\sigma_{Q}^{2}$ is the variance of quantization noise and $U(z)$ is the z-transform of control signal ({\it i.e.}, the z-transform of the signal from the digital controller), which is provided to the plant by means of ZOH.
+\noindent where $\sigma_{Q}^{2}$ is the variance of quantization noise and
+$U(z)$ is the z-transform of control signal ({\it i.e.}, the z-transform of
+the signal from the digital controller), which is provided to the plant by
+means of ZOH.
 %
 \begin{proof}
-Suppose that the plant discrete model in Figure~\ref{fig:sampledsystem} can be represented by the following pulse transfer function (without quantization noise effect): 
+%
+Suppose that the plant discrete model in Figure~\ref{fig:sampledsystem} can
+be represented by the following pulse transfer function (without
+quantization noise effect):
+%
 \begin{equation}
@@
 \end{equation}
-\noindent where $Y(z)$ is the z-transform of the plant output signal without noise $y(k)$, $U(z)$ is the z-transform of the control signal, which is provided to the plant, $A(z)$ and $B(z)$ are the plant pulse transfer function numerator and denominator, respectively.
+%
+\noindent where $Y(z)$ is the z-transform of the plant output signal without
+noise $y(k)$, $U(z)$ is the z-transform of the control signal, which is
+provided to the plant, $A(z)$ and $B(z)$ are the plant pulse transfer
+function numerator and denominator, respectively.
 
-Considering the quantization noise $\nu(k)$ as an output error in the discrete plant model, an additive noise in the plant output $y(k)$ resulting in the noisy output $\hat{y}(k)$ can be represented as
+Considering the quantization noise $\nu(k)$ as an output error in the
+discrete plant model, an additive noise in the plant output $y(k)$ resulting
+in the noisy output $\hat{y}(k)$ can be represented as
 %
@@
 
-Note that the model in Eq.~\eqref{eq:tfwithout} is equivalent to the following difference equation:
+Note that the model in Eq.~\eqref{eq:tfwithout} is equivalent to the
+following difference equation:
 %
@@
 
-\noindent and consequently $\hat{y}(k)$ can be represented by the following difference equation:
+\noindent and consequently $\hat{y}(k)$ can be represented by the following
+difference equation:
 %
@@
 
-Considering $\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}$ and Eq.~\eqref{eq:tfwithout}, the intended expression can be obtained as
+Considering $\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}$ and Eq.~\eqref{eq:tfwithout},
+the intended expression can be obtained as
 %
@@
 
-Eq.~\eqref{eq:deltag_var} indicates that the modeling of quantization noise effect on the plant transfer function demands an estimation of the variance of quantization noise $\sigma_{Q}^{2}$.
-To obtain such estimation, the methodology presented by Widrow and Koll\'ar~\cite{widrow2008quantization} is used.
-The authors provide an algorithm for computing the mean square of the output noise due to $Q1$ and $Q2$.
-Considering that each quantizer contribution can be represented by a white noise with zero mean (Assumption~\ref{whitenoise}), the mean square can be considered as the variance of noise ($\sigma_{Q}^{2}$), which can be calculated as
+Eq.~\eqref{eq:deltag_var} indicates that the modeling of quantization noise
+effect on the plant transfer function demands an estimation of the variance
+of quantization noise $\sigma_{Q}^{2}$.  To obtain such estimation, the
+methodology presented by Widrow and Koll\'ar~\cite{widrow2008quantization}
+is used.  The authors provide an algorithm for computing the mean square of
+the output noise due to $Q1$ and $Q2$.  Considering that each quantizer
+contribution can be represented by a white noise with zero mean
+(Assumption~\ref{whitenoise}), the mean square can be considered as the
+variance of noise ($\sigma_{Q}^{2}$), which can be calculated as
 %
@@
 \end{equation}
+%
+\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factor for the
+quantization $Q1$ and $Q2$, respectively; and $\sum {h_{Q1}^{2}}$ and $\sum
+{h_{Q2}^{2}}$ are the squares sums of the impulse response obtained by means
+of a transfer function from $Q1$ and $Q2$ to the plant output, respectively.
 
-\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factor for the quantization $Q1$ and $Q2$, respectively; and $\sum {h_{Q1}^{2}}$ and $\sum {h_{Q2}^{2}}$ are the squares sums of the impulse response obtained by means of a transfer function from $Q1$ and $Q2$ to the plant output, respectively.
-
-The transfer functions $H_{Q1}(z)$ and $H_{Q2}(z)$, from which the squares sums of the impulse response are needed, can be obtained through the analysis of the system in Figure~\ref{fig:sampledsystem}.
-Considering that the quantizer $Q1$ is the source of a white noise with zero mean $\nu_{1}$ and $Q2$ is the source of a white noise with zero mean $\nu_{2}$, the following equation can be written for the system in Figure~\ref{fig:sampledsystem}
+The transfer functions $H_{Q1}(z)$ and $H_{Q2}(z)$, from which the squares
+sums of the impulse response are needed, can be obtained through the
+analysis of the system in Figure~\ref{fig:sampledsystem}.  Considering that
+the quantizer $Q1$ is the source of a white noise with zero mean $\nu_{1}$
+and $Q2$ is the source of a white noise with zero mean $\nu_{2}$, the
+following equation can be written for the system in
+Figure~\ref{fig:sampledsystem}
 %
@@
 
-These equations are sufficient for computing $\sigma_{Q}^{2}$.
-However, there is still a gap for a complete model for $\Delta{G_{Q}(z)}$ in Eq.~\eqref{eq:deltag_var}, {\it i.e.}, the z-transform of control action $U(z)$.
-This indicates that the quantization noise effect on a discrete plant model mainly depends on three main factors:
+These equations are sufficient for computing $\sigma_{Q}^{2}$.  However,
+there is still a gap for a complete model for $\Delta{G_{Q}(z)}$ in
+Eq.~\eqref{eq:deltag_var}, {\it i.e.}, the z-transform of control action
+$U(z)$.  This indicates that the quantization noise effect on a discrete
+plant model mainly depends on three main factors:
 %
 \begin{itemize}
+%
 \item \textbf{Sample time:} the sample time effect is reflected over pulse transfer function that covers the effects of DAC ant its interpolator (ZOH);
+%
 \item \textbf{ADC and DAC step: } these are the main component of quantization noise power, but an $8$-bits converter already reduces the effect of quantization noises in the output for negligible values.
+%
 \item \textbf{Signal-to-noise ratio (SNR): } the dependence on the value of $U(z)$ shows the importance of the SNR for handling quantization noise; for a high SNR of the digital controller, the quantization effect is negligible.
@@
 A digital controller with integral action might be sufficient for eliminating such influence on the steady state.
+%
 \end{itemize}
 
-An alternative expression for $\Delta{G_{Q}(z)}$ can be obtained from Eq.~\eqref{eq:deltag_var}, transforming it into a function of the reference $R(z)$.
-Once $U(z)$ is the control signal obtained via digital controller $C(z)$ and error signal, {\it i.e.},
+An alternative expression for $\Delta{G_{Q}(z)}$ can be obtained from
+Eq.~\eqref{eq:deltag_var}, transforming it into a function of the reference
+$R(z)$.  Once $U(z)$ is the control signal obtained via digital controller
+$C(z)$ and error signal, {\it i.e.},
 %
@@
 
-Substituting Eq.~\eqref{eq:controlsignal} in Eq.~\eqref{eq:deltag_var}, a model for $\Delta{G_{Q}(z)}$ depending on $R(z)$ can be obtained:
+Substituting Eq.~\eqref{eq:controlsignal} in Eq.~\eqref{eq:deltag_var}, a
+model for $\Delta{G_{Q}(z)}$ depending on $R(z)$ can be obtained:
 %
@@
 
-\noindent where $R(z)$ can be considered as a step signal (for stabilization purpose) with height equal to $r$, which can be rewritten as
+\noindent where $R(z)$ can be considered as a step signal (for stabilization
+purpose) with height equal to $r$, which can be rewritten as
+%
 \begin{equation}
@@
 
-A more confident description of $\Delta{G_{Q}(z)}$ can be obtained considering FWL effects on digital controller coefficients, as described in Bessa {\it et al.}~\cite{Bessa16}, {\it i.e.}, using $FWL[C(z)]$ instead of the nominal $C(z)$:
+A more confident description of $\Delta{G_{Q}(z)}$ can be obtained
+considering FWL effects on digital controller coefficients, as described in
+Bessa {\it et al.}~\cite{Bessa16}, {\it i.e.}, using $FWL[C(z)]$ instead of
+the nominal $C(z)$:
 %
@@
 
-Finally, Eq.~\eqref{eq:deltaG_final} is a suitable frequency domain model for quantization noise effects on closed-loop systems.
-This model depends on the plant pulse transfer function ($G(z)$), which is described by Eq.~\eqref{eq:pulsetf}, the height of step reference signal $r$, and the digital controller model.
+Finally, Eq.~\eqref{eq:deltaG_final} is a suitable frequency domain model
+for quantization noise effects on closed-loop systems.  This model depends
+on the plant pulse transfer function ($G(z)$), which is described by
+Eq.~\eqref{eq:pulsetf}, the height of step reference signal $r$, and the
+digital controller model.
 
@@
 
-A classical cruise control example is extracted from the literature~\cite{Astrom08}, where the discrete plant model (with time step of $0.2$s) is represented by the following z-expression:
+A classical cruise control example is extracted from the
+literature~\cite{Astrom08}, where the discrete plant model (with time step
+of $0.2$s) is represented by the following z-expression:
 
@@
 
-Using an optimization tool, Wang {\it et al.}~\cite{DBLP:conf/hybrid/WangGRJF16} design a high-performance controller, which is characterized by the following z-expression:
+Using an optimization tool, Wang {\it et
+al.}~\cite{DBLP:conf/hybrid/WangGRJF16} design a high-performance
+controller, which is characterized by the following z-expression:
 
@@
 
-The authors claim that this controller $C(z)$ is extremely stable for the discrete plant model $P(z)$.
-However, if implementation aspects are considered during verification, this controller becomes unstable.
+The authors claim that this controller $C(z)$ is extremely stable for the
+discrete plant model $P(z)$.  However, if implementation aspects are
+considered during verification, this controller becomes unstable.
 
-For this particular example, the actual implementation of $C(z)$ using \param{3}{16} implementation format can be represented by the following z-expression:
+For this particular example, the actual implementation of $C(z)$ using
+\param{3}{16} implementation format can be represented by the following
+z-expression:
 
@@
 
-The problem of parametric control synthesis based on stability measures for continous Linear Time Invariant (LTI) Single Input-Single Output (SISO) systems has been researched for several decades.
-On a theoretical level it is a solved problem\cite{wonham1967pole} for which researches continuously seek better results based on a number of properties in addition to stability.
-A vast range of pole placement techniques such as Moore's algorithm for eigenstructure assignment \cite{klein1977eigenvalue} or the more recent Linear Quadratic Regulator (LQR) \cite{bemporad2002explicit} have been used in several papers with increasing degrees of succes to ensure stability.
-The latter approach highlights the importance of conserving energy during the control process, which results amongst other things in lower running costs.
-Since real systems are subject to tolerance and noise as well as the need for economy, more recent works focus on the problems of achieving robust stability with minimum gain \cite{schmid2014unified,konigorski2012pole}.
-However, when extending the problem to digital controller synthesis, many of these techniques lack the ability to produce sound or stable results because they disregard the effects of quantization and rounding.
-Modern papers on implementations/synthesis of LTI digital controllers \cite{das2013lqr,ghosh2013fpga} focus on time discretization, failing to account for these error-inducing effects and can therefore result in digitally unstable systems that have been proven to be robustly stable in a continuous space.
-This situation demands the inclusion of formal methods to verify the effects of space discretization on the implementation of the controller.
+The problem of parametric control synthesis based on stability measures for
+continous Linear Time Invariant (LTI) Single Input-Single Output (SISO)
+systems has been researched for several decades.  On a theoretical level it
+is a solved problem~\cite{wonham1967pole} for which researches continuously
+seek better results based on a number of properties in addition to
+stability.  A vast range of pole placement techniques such as Moore's
+algorithm for eigenstructure assignment~\cite{klein1977eigenvalue} or the
+more recent Linear Quadratic Regulator (LQR)~\cite{bemporad2002explicit}
+have been used in several papers with increasing degrees of succes to ensure
+stability.  The latter approach highlights the importance of conserving
+energy during the control process, which results amongst other things in
+lower running costs.  Since real systems are subject to tolerance and noise
+as well as the need for economy, more recent works focus on the problems of
+achieving robust stability with minimum
+gain~\cite{schmid2014unified,konigorski2012pole}.  However, when extending
+the problem to digital controller synthesis, many of these techniques lack
+the ability to produce sound or stable results because they disregard the
+effects of quantization and rounding.  Modern papers on
+implementations/synthesis of LTI digital
+controllers~\cite{das2013lqr,ghosh2013fpga} focus on time discretization,
+failing to account for these error-inducing effects and can therefore result
+in digitally unstable systems that have been proven to be robustly stable in
+a continuous space.  This situation demands the inclusion of formal methods
+to verify the effects of space discretization on the implementation of the
+controller.
 
@@
 
-Researchers in formal verification methods of control systems have studied various effects of discretising the dynamics, including delayed response \cite{Duggirala2015}, and Finite Word Length (FWL) constraints with the objective to either verify (eg.
-\cite{daes20161}) or optimise (eg.
-\cite{oudjida2014design}) implementations.
-There are in fact two different problems arising from FWL effects.
-The first corresponds to the error in the dynamics caused by the inability of the hardware to represent the exact dynamics of the system whilst the second relates to rounding errors during computation.
-In \cite{fialho1994stability} a stability measure based on the error of the digital dynamics ensures that the FWL errors do not make the digital system unstable.
-A more recent approach \cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to directly model the digital controller so that the selected parameters are stable by design.
-Most papers following this line of verification focus on finding a correct implementation of a known desired controller, looking for optimal parameter representations using FWL but ignoring the effects of rounding errors due to issues of mathematical tractability.
-The analyses in \cite{DBLP:conf/hybrid/WangGRJF16,DBLP:conf/hybrid/RouxJG15} rely on an invariant computation on the discrete system dynamics using Semi-Definite Pogramming (SDP).
-Whilst the former uses BIBO properties to determine stability, the latter uses Lyapunov-based quadratic invariants.
-In both cases the SDP solver uses floating point arithmetic and soundness is checked by upper bounding the error.
+Researchers in formal verification methods of control systems have studied
+various effects of discretising the dynamics, including delayed
+response~\cite{Duggirala2015}, and Finite Word Length (FWL) constraints with
+the objective to either verify (eg.  \cite{daes20161}) or optimise
+(eg.~\cite{oudjida2014design}) implementations.  There are in fact two
+different problems arising from FWL effects.  The first corresponds to the
+error in the dynamics caused by the inability of the hardware to represent
+the exact dynamics of the system whilst the second relates to rounding
+errors during computation.  In \cite{fialho1994stability} a stability
+measure based on the error of the digital dynamics ensures that the FWL
+errors do not make the digital system unstable.  A more recent
+approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
+directly model the digital controller so that the selected parameters are
+stable by design.  Most papers following this line of verification focus on
+finding a correct implementation of a known desired controller, looking for
+optimal parameter representations using FWL but ignoring the effects of
+rounding errors due to issues of mathematical tractability.  The analyses
+in~\cite{DBLP:conf/hybrid/WangGRJF16,DBLP:conf/hybrid/RouxJG15} rely on an
+invariant computation on the discrete system dynamics using Semi-Definite
+Pogramming (SDP).  Whilst the former uses BIBO properties to determine
+stability, the latter uses Lyapunov-based quadratic invariants.  In both
+cases the SDP solver uses floating point arithmetic and soundness is checked
+by upper bounding the error.
 
@@
 
-To the authors' knowledge, there is no existing work on the automatic synthesis of digital controllers considering FWL effects.
-Parameter synthesis tools such as \cite{cimatti2013parameter} use bounded model checking and fixed point computations to find parameters based on user defined specifications, but they often operate in the continuous domain and are ill-suited for robust analysis since they have no direct means of evaluating robustness.
-Other tools such as \cite{economakos2016automated} are directly aimed at robust stability problems but fail to explore the effects of FWL in their implementation.
-In order to provide a correct by design controller, \cite{alur2016compositional} requires a user-defined finite state abstraction to synthesise a digital controller based on high level specifications.
-Whilst this approach directly overcomes the challenges presented by the FWL problem, it still requires error-prone user intervention.
-A different solution that looks at the other end of the scale is an approach that synthesises word lengths for know problems as developed in \cite{jha2013swati}, however this provides neither an optimal word synthesis nor a comprehensive solution for the problem.
-It is from this vacuum that we seek to explore a CEGIS approach to FWL controller synthesis.
+To the authors' knowledge, there is no existing work on the automatic
+synthesis of digital controllers considering FWL effects.  Parameter
+synthesis tools such as~\cite{cimatti2013parameter} use bounded model
+checking and fixed point computations to find parameters based on user
+defined specifications, but they often operate in the continuous domain and
+are ill-suited for robust analysis since they have no direct means of
+evaluating robustness.  Other tools such as~\cite{economakos2016automated}
+are directly aimed at robust stability problems but fail to explore the
+effects of FWL in their implementation.  In order to provide a correct by
+design controller, \cite{alur2016compositional} requires a user-defined
+finite state abstraction to synthesise a digital controller based on high
+level specifications.  Whilst this approach directly overcomes the
+challenges presented by the FWL problem, it still requires error-prone user
+intervention.  A different solution that looks at the other end of the scale
+is an approach that synthesises word lengths for know problems as developed
+in \cite{jha2013swati}, however this provides neither an optimal word
+synthesis nor a comprehensive solution for the problem.  It is from this
+vacuum that we seek to explore a CEGIS approach to FWL controller synthesis.
 
@@
 
-In recent years the development of program synthesis has found many ways to obtain correct by design programs from high level specifiactions.
-One such approach \cite{itzhaky2010simple} looks to inductively synthesise invariants to generate the desired programs.
-Since these digital programs are already constrained by designed to factors such as FWL, these approaches are ideal for the synthesis of parametric controllers.
-In \cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS for the synthesis of switching controllers for stabilizing continuous-time plants with polynomial dynamics.
-The work extends to its application on affine systems, finding its major challenge in the hardness of solving linear arithmetic on present SMT solvers.
-Since this approach uses switching states instead of linear dynamics in the digital controller, it entirely circumvents the FWL problem.
-It is also not suitable for the kind of control we seek to synthesise.
-What is needed in this regard is the combination of a synthesis engine with a control verification tool that addresses the challenges presented here in the form of FWL effects and stability measures for LTI SISO controllers.
-We take the former from \cite{} and the latter from \cite{daes20161} whilst enhancing the procedure by evaluating the quantaization effects of the Hardware interfaces (ADC/DAC) to obtain an accurate discrete time FWL representation of the continuous dynamics.
+In recent years the development of program synthesis has found many ways to
+obtain correct by design programs from high level specifiactions.  One such
+approach~\cite{itzhaky2010simple} looks to inductively synthesise invariants
+to generate the desired programs.  Since these digital programs are already
+constrained by designed to factors such as FWL, these approaches are ideal
+for the synthesis of parametric controllers. 
+In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS for the
+synthesis of switching controllers for stabilizing continuous-time plants
+with polynomial dynamics.  The work extends to its application on affine
+systems, finding its major challenge in the hardness of solving linear
+arithmetic on present SMT solvers.  Since this approach uses switching
+states instead of linear dynamics in the digital controller, it entirely
+circumvents the FWL problem.  It is also not suitable for the kind of
+control we seek to synthesise.  What is needed in this regard is the
+combination of a synthesis engine with a control verification tool that
+addresses the challenges presented here in the form of FWL effects and
+stability measures for LTI SISO controllers.  We take the former
+from~\cite{} and the latter from \cite{daes20161} whilst enhancing the
+procedure by evaluating the quantaization effects of the Hardware interfaces
+(ADC/DAC) to obtain an accurate discrete time FWL representation of the
+continuous dynamics.
 

### 2016-09-23 paper/paper.tex
title
nudges

@@
 
-\title{Synthesising and Verifying Closed-loop Digital Control Systems}
+\title{Counterexample-guided Synthesis \\
+of Closed-loop Digital Control Systems}
 %\subtitle{[Extended Abstract]
@@
 %% }
+
+\author{Author names omitted for review}
 
@@
 a plant model given as
-
+%
 \begin{align}
@@
 \end{align}
+%
+\noindent where $\beta$ and $\alpha$ are the controller's coefficients, $b$
+and $a$ are the plant's coefficients, and $N$ and $M$ are the number of bits
+of the integer and fractional part, respectively.  Note that $G(z)$ is a
+discrete model of a real (and continuous) plant, {\it i.e.}, a continuous
+model of the plant must be discretized to obtain the discrete equivalent
+coefficients $b$ and $a$~\cite{Astrom08}.  Although there are several
+discretization methods available in the literature~\cite{Franklin15}, the
+zero-order hold (ZOH) discretization is more suitable for representing the
+sampling processes that are typically employed by hybrid
+systems~\cite{istepanian2012digital}.
 
-\noindent where $\beta$ and $\alpha$ are the controller's coefficients, $b$ and $a$ are the plant's coefficients, and $N$ and $M$ are the number of bits of the integer and fractional part, respectively.
-Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it i.e.}, a continuous model of the plant must be discretized to obtain the discrete equivalent coefficients $b$ and $a$~\cite{Astrom08}.
-Although there are several discretization methods available in the literature~\cite{Franklin15}, the zero-order hold (ZOH) discretization is more suitable for representing the sampling processes that are typically employed by hybrid systems~\cite{istepanian2012digital}.
-
-Let $C(z)$ and $G(z)$ transfer functions be arranged in vectors $c_0$ and $g_0$, respectively.
-For each $C(z)$ implementation, there is a function $FWL[\cdot]:\mathbb{R}^{N_C+M_C}\rightarrow Q[\mathbb{R}^{N_C+M_C}]$, which applies FWL effects to the controller $C(z)$, where $Q[\mathbb{R}]$ represents the quantized set of representable real numbers in the chosen implementation format \param{N_C}{M_C}.
-The quantized controller parameters vector ($c$) is generated via $FWL[c_0]$.
-The uncertain plant parameters ($g$) can be expressed as
-
+Let $C(z)$ and $G(z)$ transfer functions be arranged in vectors $c_0$ and
+$g_0$, respectively.  For each $C(z)$ implementation, there is a function
+$\mathit{FWL}[\cdot]:\mathbb{R}^{N_C+M_C}\rightarrow
+Q[\mathbb{R}^{N_C+M_C}]$, which applies FWL effects to the controller
+$C(z)$, where $Q[\mathbb{R}]$ represents the quantized set of representable
+real numbers in the chosen implementation format \param{N_C}{M_C}.  The
+quantized controller parameters vector ($c$) is generated via
+$\mathit{FWL}[c_0]$.  The uncertain plant parameters ($g$) can be expressed
+as
+%
 \begin{equation}
@@
 
-DSVerifier verification flow is shown in Fig.~\ref{DSVerifier_process}. 
-Steps from $1$ to $5$ are performed by users and Steps A to D are
-automatically performed by DSVerifier, which accepts the digital controller
-transfer functions together with the plant model.  For any digital
-controller, implementation details should be provided ({\it e.g.}, number of
-bits, realization, and sample time).
+The DSVerifier verification flow is illustrated in
+Fig.~\ref{DSVerifier_process}.  Steps $1$ to $5$ are performed by users and
+Steps A to D are automatically performed by DSVerifier, which accepts the
+digital controller transfer functions together with the plant model.  For
+any digital controller, implementation details should be provided ({\it
+e.g.}, number of bits, realization, and sample time).
 
@@
 verification of the desired property $\phi$ ({\it i.e.}, stability).  The
-user steps described in Steps $1$-$5$ results in an ANSI-C code that should
+user steps described in Steps $1$--$5$ result in an ANSI-C code that should
 be used as an input for DSVerifier.
@@
 plant family $\mathfrak{G}$ using $g_0$ and $\Delta{g}\%$, which are
-provided in Step $1$.  DSVerifier then formulates $FWL[\cdot]$ in Step B
-using implementation details provided from Steps $2$ and $3$, and then
-computes $FWL[c_0]$ in Step C.  Thus, DSVerifier builds an intermediate
-ANSI-C code for the digital system implementation, which is used as input
-for the model-checker, as pointed in Step D.
+provided in Step $1$.  DSVerifier then formulates $\mathit{FWL}[\cdot]$ in
+Step B using implementation details provided from Steps $2$ and $3$, and
+then computes $\mathit{FWL}[c_0]$ in Step C.  Thus, DSVerifier builds an
+intermediate ANSI-C code for the digital system implementation, which is
+used as input for the model-checker, as pointed in Step D.
 

### 2016-09-24 paper/paper.tex
add figure about sampled system

@@
 \label{Eq:running-example-plant}
-P\left(z\right) := \frac{0.0264}{z-0.9998}.
+G\left(z\right) := \frac{0.0264}{z-0.9998}.
 \end{equation}
@@
 The authors claim that this controller $C(z)$ is extremely stable for the
-discrete plant model $P(z)$.  However, if implementation aspects are
+discrete plant model $G(z)$.  However, if implementation aspects are
 considered during verification, this controller becomes unstable.
@@
 %---------------------------------
-\subsection{Setup}
+\subsection{Description of Benchmarks}
 \label{experimental-setup}
 %---------------------------------
+
+%
+\begin{equation}
+\label{cruise-control-g1}
+G_{1}(z)=\frac{1.51z-1.3586}{z-1}.
+\end{equation} 
+%
+\begin{equation}
+\label{cruise-control-c1}
+C_{1}(z)=\frac{0.0264}{z-0.998}.
+\end{equation}
+
+All experiments were conducted on an otherwise idle Intel Core i$7$-$4790$ 
+CPU $3$.$60$ GHz, $16$ GB of RAM, and Linux OS.  All times given are wall 
+clock time in seconds as measured by the UNIX time command.
 

### 2016-09-24 paper/paper.tex
add cruise control model

@@
 
+The discrete plant of a cruise control model with time step
+of 0.2s for the car accounting for rolling friction, aerodynamic drag, 
+and gravitational disturbance force is considered~\cite{Astrom08} 
+as follows
+%
+\begin{equation}
+\label{cruise-control-c1}
+G(z)=\frac{0.0264}{z-0.998}. \nonumber
+\end{equation}
+
+Two proportional-integral (PI) controllers are designed by Wang {\it et al.} 
+for the cruise control plant $G(z)$ \cite{DBLP:conf/hybrid/WangGRJF16}, 
+which has the following mathematical model
 %
@@
 \label{cruise-control-g1}
-G_{1}(z)=\frac{1.51z-1.3586}{z-1}.
+C_{1}(z)=\frac{1.51z-1.3586}{z-1}, \nonumber
 \end{equation} 
@@
 \begin{equation}
-\label{cruise-control-c1}
-C_{1}(z)=\frac{0.0264}{z-0.998}.
+\label{cruise-control-g2}
+C_{2}(z)=\frac{2.72z^2 - 4.153z + 1.896}{1.0z^2 - 1.844z + 0.8496}. \nonumber
 \end{equation}

### 2016-09-24 paper/paper.tex
add spring-mass damper

--- 2016-09-24 paper/paper.tex
@@
 
+The first set of benchmarks considers the discrete plant of a cruise 
+control model for the car accounting for rolling friction, aerodynamic drag, 
+and gravitational disturbance force~\cite{Astrom08} as follows
+%
+\begin{equation}
+\label{cruise-control-c1}
+G_1(z)=\frac{0.0264}{z-0.998}. \nonumber
+\end{equation}
+
+Two proportional-integral (PI) controllers are designed by Wang {\it et al.} 
+for the cruise control plant $G(z)$~\cite{DBLP:conf/hybrid/WangGRJF16}, 
+which has the following mathematical model
 %
@@
 \begin{equation}
-\label{cruise-control-c1}
-C_{1}(z)=\frac{0.0264}{z-0.998}.
+\label{cruise-control-g2}
+C_{2}(z)=\frac{2.72z^2 - 4.153z + 1.896}{1.0z^2 - 1.844z + 0.8496}. \nonumber
+\end{equation}
+
+The second set of benchmarks considers a simple spring-mass 
+damper~\cite{DBLP:conf/hybrid/WangGRJF16}, where both discrete 
+plant dynamics and controller are represented by the following 
+z-expression, resp.
+%
+\begin{equation}
+\label{spring-mass-damper-g}
+G_2(z)=\frac{5\times{10^{-5}}z + 5\times{10^{-5}}}{z^2 - 2z + 1.0001}, \nonumber
+\end{equation} 
+%
+\begin{equation}
+\label{spring-mass-damper-c}
+C_3(z)=\frac{1.28\times{10^{3}}z^2 - 1.354240\times{10^{3}}z + 0.074879\times{10^{3}}}{z^2 - 1.4990z + 0.4995}. \nonumber
 \end{equation}

### 2016-09-27 paper/paper.tex
Initial draft for abstract and Intro

@@
 \begin{abstract}
-
+Modern control systems are by and large implemented in digital microcontrollers.
+This poses a new dimension to the problem of correct by design controllers which do not only need to look at the dynamics involved, but also at the effects of digitalization.
+This is particularly true in small size implementations where the effects of word length are significant with respect to the dynamics.
+This work focuses on the synthesis of digital controllers for Linear Time Invariant SISO systems.
+We explore the effects of digitalization of the continuous signals and Fixed Word Length (FWL) in the controller dynamics.
+To this end we propose a CEGIS solution that uses inductive invariant synthesis in conjunction with a digital stability verification algorithm from a well known tool to find a parametric solution for a digital controller given a model specification.
+The algorithm factors in quantization errors, sample and hold behaviour, and parameter representation round-offs.
+The results show...
 \end{abstract}
@@
 
-\keywords{}
+\keywords{Control Synthesis, CEGIS, FWL}
 
@@
 
-We are interested in the stability of closed-loop systems, i.e.,
-controllers along with a model of their physical environment, the
-plant, as shown in Fig.~\ref{fig:closed-system}.
+Modern implementations of embedded control have proliferated with the availability of low cost devices that can perform simple tasks for linear control, spanning many areas such as environmental control and robotic manipulations.
+The downside to this approach is that in order to achieve low prices, devices are often limited in their capabilities, be it a low number of gates in an FPGA or short word lengths for microcontrollers.
+The ubiquity of these devices requires that they have a robust design that ensures the correct behaviour in a number of environments.
+For this reason it is necessary to provide design tools that formally verify the correctness of the digital controller and in particular we explore the automatic synthesis of these controllers which reduces the deveopment cost and design time for a number of models.
+
+We are interested in the stability of hybrid closed-loop systems, i.e.,
+embedded controllers along with a model of their physical environment, the
+plant, as shown in Fig.~\ref{fig:closed-system}. Due to the complexity of such systems, we focus on linear models with known configurations to perform parametric synthesis of the controller dynamics.
+
+Since the digital control synthesis is performed over a hybrid model, where the plant display a continuous behaviour and the controller operates in both discrete time and state-space, we initially translate the problem into a single domain which represents a bi-simulation of the original dynamics.
+Given or primary interest in evaluating digital effects in addition to stability, we have modeled a digital equivalent of the plant by evaluating the effects of the quantisers (A/D and D/A converters) as time discretisation elements with quantisation noise.
+The resulting closed loop system is a program loop working over bit-vectors of fixed point arithmetic with fixed word length.
+The effect of the FWL is included in the model as a parametric uncertainty which must be taken into account for the correct synthesis of the controller.
 

### 2016-09-28 paper/paper.tex
Added new reference

@@
 The downside to this approach is that in order to achieve low prices, devices are often limited in their capabilities, be it a low number of gates in an FPGA or short word lengths for microcontrollers.
+In most cases a floating point implementation is not feasible and the system can benefit from the added resolution of a fixed point representation.
 The ubiquity of these devices requires that they have a robust design that ensures the correct behaviour in a number of environments.
@@
 To the authors' knowledge, there is no existing work on the automatic
-synthesis of digital controllers considering FWL effects.  Parameter
+synthesis of fixed point digital controllers considering FWL effects.  Parameter
 synthesis tools such as~\cite{cimatti2013parameter} use bounded model
@@
 stability measures for LTI SISO controllers.  We take the former
-from~\cite{} and the latter from \cite{daes20161} whilst enhancing the
+from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from \cite{daes20161} whilst enhancing the
 procedure by evaluating the quantaization effects of the Hardware interfaces

### 2016-09-29 paper/paper.tex
bib reference for park

@@
 by upper bounding the error.
+An alternative approach is taken by \cite{park2016scalable}, where the verification of existing
+code is performed against a known model by extracting an LTI model of the
+code through symbolic execution. In order to account for rounding errors, an
+upper bound is introduced in the verification phase. If the error of the implementation
+is lower than this tolerance level, then the verification is successful.
 

### 2016-09-29 paper/paper.tex
converted Fig 3 to tikz

--- 2016-09-27 paper/paper.tex
@@
 \usepackage{wasysym}
+%\usetikzlibrary{decorations}
+%\usetikzlibrary{decorations.pathmorphing}
 
@@
 \begin{abstract}
-Modern control systems are by and large implemented in digital microcontrollers.
-This poses a new dimension to the problem of correct by design controllers which do not only need to look at the dynamics involved, but also at the effects of digitalization.
-This is particularly true in small size implementations where the effects of word length are significant with respect to the dynamics.
-This work focuses on the synthesis of digital controllers for Linear Time Invariant SISO systems.
-We explore the effects of digitalization of the continuous signals and Fixed Word Length (FWL) in the controller dynamics.
-To this end we propose a CEGIS solution that uses inductive invariant synthesis in conjunction with a digital stability verification algorithm from a well known tool to find a parametric solution for a digital controller given a model specification.
-The algorithm factors in quantization errors, sample and hold behaviour, and parameter representation round-offs.
-The results show...
+
 \end{abstract}
@@
 
-\keywords{Control Synthesis, CEGIS, FWL}
+\keywords{}
 
@@
 
-Modern implementations of embedded control have proliferated with the availability of low cost devices that can perform simple tasks for linear control, spanning many areas such as environmental control and robotic manipulations.
-The downside to this approach is that in order to achieve low prices, devices are often limited in their capabilities, be it a low number of gates in an FPGA or short word lengths for microcontrollers.
-The ubiquity of these devices requires that they have a robust design that ensures the correct behaviour in a number of environments.
-For this reason it is necessary to provide design tools that formally verify the correctness of the digital controller and in particular we explore the automatic synthesis of these controllers which reduces the deveopment cost and design time for a number of models.
-
-We are interested in the stability of hybrid closed-loop systems, i.e.,
-embedded controllers along with a model of their physical environment, the
-plant, as shown in Fig.~\ref{fig:closed-system}. Due to the complexity of such systems, we focus on linear models with known configurations to perform parametric synthesis of the controller dynamics.
-
-Since the digital control synthesis is performed over a hybrid model, where the plant display a continuous behaviour and the controller operates in both discrete time and state-space, we initially translate the problem into a single domain which represents a bi-simulation of the original dynamics.
-Given or primary interest in evaluating digital effects in addition to stability, we have modeled a digital equivalent of the plant by evaluating the effects of the quantisers (A/D and D/A converters) as time discretisation elements with quantisation noise.
-The resulting closed loop system is a program loop working over bit-vectors of fixed point arithmetic with fixed word length.
-The effect of the FWL is included in the model as a parametric uncertainty which must be taken into account for the correct synthesis of the controller.
+We are interested in the stability of closed-loop systems, i.e.,
+controllers along with a model of their physical environment, the
+plant, as shown in Fig.~\ref{fig:closed-system}.
 
@@
   \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=1cm, column sep=1cm] {
-   \coordinate (aux0);
+    \node[draw=none] (r) {r};
+%   \& \coordinate (aux0);
    \& \node[circle] (circle) {};
-   \& \node[fill=yellow!20] (da) {{\sc D/A}}; 
-   \& \node[fill=yellow!20] (p) {{\sc P}};
-   \& \node[fill=yellow!20] (ad) {{\sc A/D}}; 
-   \& \coordinate (aux1);\\
+   \& complexnode/.pic={ 
+     \node[rectangle,draw,
+	minimum width=4cm,
+	minimum height=1cm,
+	label=\textbf{ADC},] (adc) {};
+   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
+   \coordinate (switch1) at ([xshift=-1cm]adc.center);
+   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
+   \node[fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {{\sc Q1}};} 
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Controller}] (cz) {{\sc C(z)}};
+   \& complexnode/.pic={ 
+      \node[rectangle,draw,
+	minimum width=3cm,
+	minimum height=1cm,
+	label=\textbf{DAC},] (dac) {};
+     \node[fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {{\sc Q2}};
+     \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Plant}] (gs) {{\sc G(s)}};
+   \& \coordinate (aux1);
+   \& \node[draw=none] (y) {y};\\
    \& \coordinate (aux3); 
@@
    \&
-   \node[fill=yellow!20] (c) {C};
+   \& 
    \& 
@@
 
-  \path[->] (aux0) edge (circle.west);
+  \path[->] (r) edge (circle.west);
+  \path[->] (aux1) edge (y);
   \path  
-   (circle.east) edge (da.west)
-   (da.east) edge (p.west)
-   (p.east) edge (ad.west)
-   (ad.east) edge (aux1.west)
+   (circle.east) edge (switch1)
+   (switch2) edge (q1.west)
+   (q1.east) edge (cz.west)
+   (cz.east) edge (q2.west)
+   (q2.east) edge (zoh.west)
+   (zoh.east) edge (gs.west)
+   (gs.east) edge (aux1.west)
    (aux1.south) edge (aux2.north)
-   (aux2.west) edge (c.east)
-   (c.west) edge (aux3.east); 
+   (aux2.west) edge (aux3.east); 
   \path[->]  (aux3.north) edge (circle.south);
@@
 \centering
-\includegraphics[width=\columnwidth]{figures/hsystembd.pdf}
-\caption{Sampled system.}
-\label{fig:sampledsystem}
+\resizebox{.5\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
+     semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.5cm, column sep=.5cm] {
+    \node[draw=none] (r) {r};
+%   \& \coordinate (aux0);
+   \& \node[circle] (circle) {};
+   \& complexnode/.pic={ 
+     \node[rectangle,draw,
+	minimum width=4cm,
+	minimum height=1cm,
+	label=\textbf{ADC},] (adc) {};
+   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
+   \coordinate (switch1) at ([xshift=-1cm]adc.center);
+   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
+   \node[fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {{\sc Q1}};} 
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Controller}] (cz) {{\sc C(z)}};
+   \& complexnode/.pic={ 
+      \node[rectangle,draw,
+	minimum width=3cm,
+	minimum height=1cm,
+	label=\textbf{DAC},] (dac) {};
+     \node[fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {{\sc Q2}};
+     \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Plant}] (gs) {{\sc G(s)}};
+   \& \coordinate (aux1);
+   \& \node[draw=none] (y) {y};\\
+   \& \coordinate (aux3); 
+   \&
+   \&
+   \& 
+   \& 
+   \& \coordinate (aux2);\\
+  };
+
+  \path[->] (r) edge (circle.west);
+  \path[->] (aux1) edge (y);
+  \path  
+   (circle.east) edge (switch1)
+   (switch2) edge (q1.west)
+   (q1.east) edge (cz.west)
+   (cz.east) edge (q2.west)
+   (q2.east) edge (zoh.west)
+   (zoh.east) edge (gs.west)
+   (gs.east) edge (aux1.west)
+   (aux1.south) edge (aux2.north)
+   (aux2.west) edge (aux3.east); 
+  \path[->]  (aux3.north) edge (circle.south);
+ \end{tikzpicture}
+}
+ \caption{Sampled System. \label{fig:sampledsystem}}
 \end{figure}
+
+%% \begin{figure}[ht]
+%% \centering
+%% \includegraphics[width=\columnwidth]{figures/hsystembd.pdf}
+%% \caption{Sampled system.}
+%% \label{fig:sampledsystem}
+%% \end{figure}
 

### 2016-10-03 paper/paper.tex
resize fig 1
+ todo
Added counterexample tuples for cruise control in comments.
line breaks + typos + comments

@@
 
-Modern implementations of embedded control have proliferated with the availability of low cost devices that can perform simple tasks for linear control, spanning many areas such as environmental control and robotic manipulations.
-The downside to this approach is that in order to achieve low prices, devices are often limited in their capabilities, be it a low number of gates in an FPGA or short word lengths for microcontrollers.
-In most cases a floating point implementation is not feasible and the system can benefit from the added resolution of a fixed point representation.
-The ubiquity of these devices requires that they have a robust design that ensures the correct behaviour in a number of environments.
-For this reason it is necessary to provide design tools that formally verify the correctness of the digital controller and in particular we explore the automatic synthesis of these controllers which reduces the deveopment cost and design time for a number of models.
-
-We are interested in the stability of hybrid closed-loop systems, i.e.,
-embedded controllers along with a model of their physical environment, the
-plant, as shown in Fig.~\ref{fig:closed-system}. Due to the complexity of such systems, we focus on linear models with known configurations to perform parametric synthesis of the controller dynamics.
-
-Since the digital control synthesis is performed over a hybrid model, where the plant display a continuous behaviour and the controller operates in both discrete time and state-space, we initially translate the problem into a single domain which represents a bi-simulation of the original dynamics.
-Given or primary interest in evaluating digital effects in addition to stability, we have modeled a digital equivalent of the plant by evaluating the effects of the quantisers (A/D and D/A converters) as time discretisation elements with quantisation noise.
-The resulting closed loop system is a program loop working over bit-vectors of fixed point arithmetic with fixed word length.
-The effect of the FWL is included in the model as a parametric uncertainty which must be taken into account for the correct synthesis of the controller.
-
-\begin{figure*}
+Modern implementations of embedded control have proliferated with the
+availability of low cost devices that can perform simple tasks for
+linear control, spanning many areas such as environmental control and
+robotic manipulations. The downside to this approach is that in order
+to achieve low prices, devices are often limited in their
+capabilities, be it a low number of gates in an FPGA or short word
+lengths for microcontrollers. In most cases a floating point
+implementation is not feasible and the system can benefit from the
+added resolution of a fixed point representation. The ubiquity of
+these devices requires that they have a robust design that ensures the
+correct behaviour in a number of environments.  For this reason it is
+necessary to provide design tools that formally verify the correctness
+of the digital controller and in particular we explore the automatic
+synthesis of these controllers which reduces the deveopment cost and
+design time for a number of models.  \cdsay{the last sentence
+  is misleading given that synthesis is not a special case of
+  verification, but taking it one step forward.}
+
+We are interested in the stability of hybrid closed-loop systems,
+i.e., embedded controllers along with a model of their physical
+environment, the plant, as shown in Fig.~\ref{fig:closed-system}.
+\cdsay{in the next paragraph we say that our primary interest is
+  evaluating digital effects in addition to stability, which
+  contradicts the previous sentence, where we only mention stability.}
+Due to the complexity of such systems, we focus on linear models with
+known configurations to perform parametric synthesis of the controller
+dynamics.
+
+Since the digital control synthesis is performed over a hybrid model,
+where the plant displays a continuous behaviour and the controller
+operates in both discrete time and state-space, we initially translate
+the problem into a single domain which represents a bi-simulation of
+the original dynamics. Given our primary interest in evaluating digital
+effects in addition to stability, we have modeled a digital equivalent
+of the plant by evaluating the effects of the quantisers (A/D and D/A
+converters) as time discretisation elements with quantisation noise.
+The resulting closed loop system is a program loop working over
+bit-vectors of fixed point arithmetic with fixed word length. The
+effect of the FWL is included in the model as a parametric uncertainty
+which must be taken into account for the correct synthesis of the
+controller.
+
+\begin{figure}
 \centering
-\resizebox{.5\textwidth}{!}{
+\resizebox{.35\textwidth}{!}{
  \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
@@
 
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=1cm, column sep=1cm] {
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.5cm, column sep=.5cm] {
    \coordinate (aux0);
@@
  \caption{Closed-Loop System. \label{fig:closed-system}}
-\end{figure*}
+\end{figure}
 
@@
 \cdsay{discussion on the noise introduced by the plant modelling?}
+For stability, there are only two counterexamples, which are known. 
+Thus, we can just enumerate them..
+%\cdsay{Then, do we actually need program synthesis?}
 
@@
 Our goal is to synthesise ...
-\cdsay{Finish this once the example is working.}
+% Counterexample from first cruisecontrol02.c benchmark with uncertainty and
+% nondeterminism:
+% 1) { (0.02634525299072265625, 0.9979267120361328125, -0.99768829345703125) }
+% 2) { (0.02644824981689453125, 1.00053310394287109375, -1.0014629364013671875) }
 

### 2016-10-03 paper/paper.tex
hscc17
Signed-off-by: Alessandro Abate <aabate@Alessandros-MacBook-Pro.local>

@@
 
+\newcommand{\blue}[1]{{\color{blue}#1}}
+\newcommand{\red}[1]{{\color{red}#1}}
+
 \newtheorem{myassumption}{Assumption}
@@
 
-\title{Counterexample-guided Synthesis \\
-of Closed-loop Digital Control Systems}
+\title{
+Sound and Automated Synthesis of Digital Controllers for Physical Plants 
+%Counterexample-guided Synthesis of Closed-loop Digital Control Systems
+}
 %\subtitle{[Extended Abstract]
@@
 \section{Preliminaries}
+
+\blue{Please insert a figure clearly distinguishing between continuous and discretised/quantised plant - a template is in a picture sent out by Lucas late last week. 
+We should have 
+\begin{itemize}
+\item 
+$G(s) = \frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}$ -- this is the physical plant, which is focus of interest and to which we refer our specifications/properties
+\item 
+$G(z, T) = \frac{\bar b_{0}+\bar b_{1}z^{-1}+...+\bar b_{M_G}z^{-M_G}}{\bar a_{0}+\bar a_{1}z^{-1}+...+\bar a_{N_G}z^{-N_G}}$ -- this is the time-discretised plant (notice the notation encompasses explicitly the sample time $T$; please write out explicitly the relationship between the $a_i$ and the $\bar a_i$ and likewise for the numerator's coefficients
+\item
+
+\end{itemize}
+}
 
@@
 means of ZOH.
+
+\red{[Please write out a formal statement for the proof below:]}
 %

### 2016-10-03 paper/paper.tex
hscc17
Signed-off-by: Alessandro Abate <aabate@Alessandros-MacBook-Pro.local>

@@
 $G(z, T) = \frac{\bar b_{0}+\bar b_{1}z^{-1}+...+\bar b_{M_G}z^{-M_G}}{\bar a_{0}+\bar a_{1}z^{-1}+...+\bar a_{N_G}z^{-N_G}}$ -- this is the time-discretised plant (notice the notation encompasses explicitly the sample time $T$; please write out explicitly the relationship between the $a_i$ and the $\bar a_i$ and likewise for the numerator's coefficients
+(in particular, are the orders $M_G, N_G$ the same? 
 \item 
-
+we have $Y(z) = G(z,T) U(z)$; then, we introduce $\hat Y(z) \doteq Y(z) + \nu (z)$, so that 
+$$
+\frac{\hat Y(z)}{U(z)} = G(z,T) + \frac{\nu (z)}{U(z)} = G(z,T) + \Delta G_Q(z) \doteq \hat G(z) ,  
+$$ 
+where $\Delta G_Q(z)$ is an error term accounting for the quantisation effects 
+\item 
+finally, we encompass the errors resulting from employing finite parameters representation, 
+which we encompass in a term $\Delta G_P(z)$: is this error additive, so that we would get to a 
+$$
+\tilde G(z) \doteq \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z)?  
+$$ 
+Dario, can you write it out explicitly? In other words, if 
+$$
+\hat G(z) = G(z,T) + \Delta G_Q(z) = \frac{\hat b_{0}+\hat b_{1}z^{-1}+...+\hat b_{M_G}z^{-M_G}}{\hat a_{0}+\hat a_{1}z^{-1}+...+\hat a_{N_G}z^{-N_G}},  
+$$ 
+then what is the explicit expression of 
+$$
+\tilde G(z) = \frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}?
+$$
+(Notice that the orders $M_G, N_G$ need to be properly taken care of.)
 \end{itemize}

### 2016-10-03 paper/paper.tex
hscc17
Signed-off-by: Alessandro Abate <aabate@Alessandros-MacBook-Pro.local>

@@
 \item 
-$G(s) = \frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}$ -- this is the physical plant, which is focus of interest and to which we refer our specifications/properties
+$G(s) = \frac{s^{M_G}b_{0}+s^{M_G-1}b_{1}+...+b_{M_G}}{s^{N_G}a_{0}+s^{N_G-1}a_{1}+...+a_{N_G}}$ -- this is the physical plant, which is focus of interest and to which we refer our specifications/properties
 \item 
@@
 (Notice that the orders $M_G, N_G$ need to be properly taken care of.)
+\item 
+Now, it's over the transfer function $\tilde G(z)$ that we want to synthesise the parameters of a template $C(z)$. 
+This controller's transfer function will be subject to the same quantisation and precision limits as the plant's: 
+we need to argue that the way we do synthesis affects manipulation of quantities that relate to specific errors and be explicit about these. 
+\item[]
+\item 
+An additional source of error can be related to the fact that a plant transfer function, 
+per se a physical entity, is actually represented in a program imprecisely: 
+this would mean that $G(s)$ is actually 
+$$
+G^\ast (s) \doteq \frac{s^{M_G^\ast}b_{0}+s^{M_G^\ast-1}b_{1}+...+b_{M_G}}{s^{N_G^\ast}a_{0}+s^{N_G^\ast-1}a_{1}+...+a_{N_G}}, 
+$$ 
+which perhaps can indeed be re-written as $G^\ast (s) = G(s) + \Delta G_P(s)$? (This proof should come from that above.) 
+We should argue that this error is encompassed by the one derived above (or isn't it?). 
 \end{itemize}

### 2016-10-03 paper/paper.tex
hscc17
Signed-off-by: Alessandro Abate <aabate@Alessandros-MacBook-Pro.local>

@@
 \blue{Please insert a figure clearly distinguishing between continuous and discretised/quantised plant - a template is in a picture sent out by Lucas late last week.
+Please introduced signals on the plot.
+
+Let us straighten the notations next. 
 We should have 
@@
 
+\red{[This section and the next should be merged into a crisp section with the background on DSVerifier, if not included in previous work? 
+Please stick to the introduced notations. Please clarify what the function FWL does, compared to the general approximations introduced above.]}
+
 In this study, the methodology used for verifying closed-loop digital
@@
 model of the plant must be discretized to obtain the discrete equivalent
-coefficients $b$ and $a$~\cite{Astrom08}.  Although there are several
+coefficients $b$ and $a$~\cite{Astrom08} \red{[pls say how]}.  
+Although there are several
 discretization methods available in the literature~\cite{Franklin15}, the
@@
 sampling processes that are typically employed by hybrid
-systems~\cite{istepanian2012digital}.
+systems~\cite{istepanian2012digital} 
+\red{[but the ZOH is for the DAC, not for the ADC?]}.
 
@@
 $C(z)$, where $Q[\mathbb{R}]$ represents the quantized set of representable
-real numbers in the chosen implementation format \param{N_C}{M_C}.  The
+real numbers in the chosen implementation format \param{N_C}{M_C} \red{[clarify this notation]}.  The
 quantized controller parameters vector ($c$) is generated via
@@
 %------------------------------------
+
+\red{[The following description can be made shorter, crisper?]}
 
@@
 output, is proposed.  For convenience, the parametric uncertainties will be
-despised here.
+described here.
 
@@
 
-First, some assumptions have to be established to obtain a model for
-$\Delta{G_{Q}(z)}$.
+First, some assumptions have to be established to obtain a model for $\Delta{G_{Q}(z)}$. 
+\blue{[Here we need to be careful: we first argue that quantisation (spelled with an s, so that ER II is happy) effects can be represented as an additive noise (great), which however is a stochastic signal.
+But we handle the noise deterministically.
+How so?
+Where is the catch?
+]}
 %
@@
 The quantization noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
-$Q2$) are white noises with zero mean.
+$Q2$) \red{[do we need the second? See my further comments below.]} are white noises with zero mean.
 %
@@
 does not contain nonlinearities such as overflows, saturation, and
-limit-cycle oscillations.
+limit-cycle oscillations. \red{[explain difference btw overflows and saturations. Also, do we care about limit cycles? I'd quite happily disregard them.]}
 %
@@
 $u(k)$ and width equal to the sample time $T$.
+\red{[Right: so under this assumption, we really only focus on the quantisation effects introduced by the ADC, correct?
+Let us not mix up the role and the influence of the two blocks.]}
 %
@@
 Given those assumptions, the present approach is further based on the following lemmas. 
+\red{[So we have introduced two quantisation errors, properly indexed. Next we discuss a non-indexed entity - pls clarify or comment.]}
 %
@@
 %
-The pulse transfer function $G(z)$ is equivalent at the sample times to the
+The pulse transfer function \red{[define PTF]} $G(z)$ is equivalent at the sample times to the
 continuous transfer function $G(s)$ driven by ZOH.  This pulse transfer
@@
 \end{mylemma}
+\red{[Here the dependence on the sampling time T needs to appear somewhere.]}
 
@@
 
-\noindent where $\sigma_{Q}^{2}$ is the variance of quantization noise and
+\noindent where $\sigma_{Q}^{2}$ is the variance of the quantization noise and
 $U(z)$ is the z-transform of control signal ({\it i.e.}, the z-transform of
@@
 
-Eq.~\eqref{eq:deltag_var} indicates that the modeling of quantization noise
+Eq.~\eqref{eq:deltag_var} indicates that the modelling of the quantization noise
 effect on the plant transfer function demands an estimation of the variance
 of quantization noise $\sigma_{Q}^{2}$.  To obtain such estimation, the
-methodology presented by Widrow and Koll\'ar~\cite{widrow2008quantization}
+methodology presented by~\cite{widrow2008quantization}
 is used.  The authors provide an algorithm for computing the mean square of
@@
 %
-\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factor for the
+\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factors \red{[define scale factors]} for the
 quantization $Q1$ and $Q2$, respectively; and $\sum {h_{Q1}^{2}}$ and $\sum
@@
 %
-\item \textbf{Sample time:} the sample time effect is reflected over pulse transfer function that covers the effects of DAC ant its interpolator (ZOH);
-%
-\item \textbf{ADC and DAC step: } these are the main component of quantization noise power, but an $8$-bits converter already reduces the effect of quantization noises in the output for negligible values.
-%
-\item \textbf{Signal-to-noise ratio (SNR): } the dependence on the value of $U(z)$ shows the importance of the SNR for handling quantization noise; for a high SNR of the digital controller, the quantization effect is negligible.
+\item \textbf{Sample time:} the sample time effect is reflected over pulse transfer function that covers the effects of DAC ant its interpolator (ZOH) \red{[clarify/revise based on the comments made above.]};
+%
+\item \textbf{ADC and DAC step:} \red{[again, do we need both?]} these are the main component of quantization noise power, but an $8$-bits converter already reduces the effect of quantization noises in the output for negligible values.
+%
+\item \textbf{Signal-to-noise ratio (SNR): } the dependence on the value of $U(z)$ \red{[notice that now we have reduced the problem to depend on the effect of the reference signal transform R(z) - pls revise.]} shows the importance of the SNR for handling quantization noise; for a high SNR of the digital controller, the quantization effect is negligible.
 This happens during the transient of the system, when high control actions are employed.
 However, it can be relevant during the steady state.
-A digital controller with integral action might be sufficient for eliminating such influence on the steady state.
+A digital controller with integral action might be sufficient for eliminating such influence at steady state.
 %
@@
 
-A more confident description of $\Delta{G_{Q}(z)}$ can be obtained
-considering FWL effects on digital controller coefficients, as described in
+A more precise description of $\Delta{G_{Q}(z)}$ can be obtained
+considering FWL \red{[clarify what you mean with FWL, introduce FWL function explicitly and precisely]} effects on digital controller coefficients, as described in
 Bessa {\it et al.}~\cite{Bessa16}, {\it i.e.}, using $FWL[C(z)]$ instead of

### 2016-10-04 paper/paper.tex
Solving comments

@@
 \newcommand{\red}[1]{{\color{red}#1}}
+\newcommand{\green}[1]{{\color{green}#1}}
 
@@
 model of the plant must be discretized to obtain the discrete equivalent
-coefficients $b$ and $a$~\cite{Astrom08} \red{[pls say how]}.  
-Although there are several
-discretization methods available in the literature~\cite{Franklin15}, the
+coefficients $b$ and $a$~\cite{Astrom08} via ZOH discretization %\red{[pls say how]}
+. Although there are several discretization methods available in the literature~\cite{Franklin15}, the
 zero-order hold (ZOH) discretization is more suitable for representing the
@@
 The quantization noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
-$Q2$) \red{[do we need the second? See my further comments below.]} are white noises with zero mean.
+$Q2$) \red{[do we need the second? See my further comments below.]} \green{There was a typo in \eqref{eq:deltaG_final}. It was missing $q_{1}$ and $q_{1}$, both effects are considered here. }
+are white noises.
 %
@@
 %
-The controller and plant are linear.  In particular, the digital controller
-does not contain nonlinearities such as overflows, saturation, and
-limit-cycle oscillations. \red{[explain difference btw overflows and saturations. Also, do we care about limit cycles? I'd quite happily disregard them.]}
+The controller and plant are linear, {\it i.e.} any source of nonlinearity ({\it e.g.} overflows) may be disregard.
+%\red{[explain difference btw overflows and saturations.
+Also, do we care about limit cycles?
+I'd quite happily disregard them.]}
 %
@@
 %
-\cite{widrow1956} The second moment (variance) of the PDF of quantization
-noise is given by \textcolor{red}{expand the acronym PDF}
+\cite{widrow1956} The second moment (variance) of the probability probability density function of quantization
+noise is given by %\textcolor{red}{expand the acronym PDF}
 %
@@
 %
-The pulse transfer function \red{[define PTF]} $G(z)$ is equivalent at the sample times to the
-continuous transfer function $G(s)$ driven by ZOH.  This pulse transfer
+The pulse transfer function $G(z)$ is a z-domain model that relates the output sampled by a ADC and the digital input provided by ZOH.
+It is equivalent at the sample times ({\it i.e.} $kT$ to the continuous transfer function $G(s)$ driven by ZOH.
+This pulse transfer
 function can be computed as
@@
 \end{mylemma}
-\red{[Here the dependence on the sampling time T needs to appear somewhere.]}
+\red{[Here the dependence on the sampling time T needs to appear somewhere.]} \green{It appears,  $kT$ is the time $t$ used after the inverse Laplace transform}
 
@@
 \begin{equation}
-\sigma_{Q}^{2}=\frac{\lambda_{1}^{2}\cdot \sum {h_{Q1}^{2}}+\lambda_{2}^{2}\cdot \sum {h_{Q2}^{2}}}{12},
+\sigma_{Q}^{2}=\frac{\lambda_{1}^{2}\cdot \sum {h_{Q1}^{2}} \cdot q_{1}+\lambda_{2}^{2}\cdot \sum {h_{Q2}^{2}} \cdot q_{2}}{12},
 \end{equation}
@@
 \noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factors \red{[define scale factors]} for the
-quantization $Q1$ and $Q2$, respectively; and $\sum {h_{Q1}^{2}}$ and $\sum
+quantization $Q1$ and $Q2$, respectively; $q_{1}$ and $q_{2}$ are the quantization step for $Q1$ and $Q2$, respectively, and $\sum {h_{Q1}^{2}}$ and $\sum
 {h_{Q2}^{2}}$ are the squares sums of the impulse response obtained by means

### 2016-10-04 paper/paper.tex
+details on the synthesis spec

@@
 \paragraph{Running example synthesis}
+
+There are two different algorithms in DSVerifier that can be used for
+stability verification, one based on Schur's decomposition and another
+one based on Jury's criteria \cite{DBLP:journals/dafes/BessaICF16};
+here, the Jury's method is chosen due to its efficiency.
+
+Jury's algorithm is used to check the stability in the $z$-domain
+for a given characteristic polynomial of the form:
+%
+$$
+S(z) = a_0Z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N=0, a_0\neq0
+$$
+%
+For the stability test procedure, the following Jury matrix
+$M = [m_{ij}]_{(2N−2)\times N}$ is built from $S(z)$ coefficients:
+%
+$$
+M=\left( 
+\begin{array}{c}
+V^{(0)}\\
+V^{(1)}\\
+\vdots\\
+V^{(N-2)}
+\end{array}
+\right)
+$$
+%
+where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ such that:
+%
+$$
+v_{ij}^{(0)}=\left\{
+\begin{array}{ll}
+a_{j-1}, & \texttt{if}~i=1\\
+v_{(1)(N-j+1)}^{0},&\texttt{if}~i=2
+\end{array}
+\right.
+$$
+%
+$$
+v_{ij}^{(k)}=\left\{
+\begin{array}{ll}
+0,&\texttt{if}~j>n-k\\
+v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \texttt{if}~j\leq n-k ~\texttt{and}~i=1\\
+v_{(1)(N-j+1)}^{k},& \texttt{if}~j\leq n-k ~\texttt{and}~i=2\\
+\end{array}
+\right.
+$$
+%
+where $k \in \mathbb{Z}$, such that $0 < k < N − 2$. 
+$S(z)$ is the
+characteristic polynomial of a stable system if and only if
+the following four propositions hold:
+\begin{itemize}
+\item $R_1: S(1) > 0$;
+\item $R_2: (−1)^N S(−1) > 0$;
+\item $R_3: |a_0| < a_N$;
+\item $R_4: m_{11} > 0 \equiv m_{31} \wedge m_{51} \wedge \cdots \wedge m_{(2N−3)(1)}$.
+\end{itemize}
+
+The stability property is then encoded by creating a
+constraint of the form:
+$$\phi_{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4)$$
+\cdsay{figure out what is existentially quantified for the final $\sigma$.}
+
 We will illustrate our synthesis approach on the running example 

### 2016-10-04 paper/paper.tex
+ todo

@@
 \paragraph{Elements specific to control systems}
-\cdsay{discussion on the noise introduced by the plant modelling?}
-For stability, there are only two counterexamples, which are known. 
-Thus, we can just enumerate them..
-%\cdsay{Then, do we actually need program synthesis?}
-
-\paragraph{Running example synthesis}
-
 There are two different algorithms in DSVerifier that can be used for
@@
 
+\paragraph{Running example synthesis}
 We will illustrate our synthesis approach on the running example 
 in Sec.~\ref{sec:running-ex}.
-Our goal is to synthesise ...
+\cdsay{Pascal, I also need the candidate solutions here}
 % Counterexample from first cruisecontrol02.c benchmark with uncertainty and

### 2016-10-05 paper/paper.tex
+ TODO
edit sec 5

@@
 
-Jury's algorithm is used to check the stability in the $z$-domain
-for a given characteristic polynomial of the form:
+Essentially, we use this method to check the stability in the $z$-domain
+for the characteristic polynomial $S(z)$ of 
+the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$.
+We consider the following form for $S(z)$:
 %
@@
 %
-For the stability test procedure, the following Jury matrix
+%\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?}
+
+Next, the following Jury matrix
 $M = [m_{ij}]_{(2N−2)\times N}$ is built from $S(z)$ coefficients:
@@
 % 1) { (0.02634525299072265625, 0.9979267120361328125, -0.99768829345703125) }
+
 % 2) { (0.02644824981689453125, 1.00053310394287109375, -1.0014629364013671875) }

### 2016-10-05 paper/paper.tex
edit sec 5
Added solution for running example.
revised sec 5 (elements specific to control)

@@
 \paragraph{Elements specific to control systems}
+Next, we describe the specific property that we pass to the 
+program synthesiser as the specification $\sigma$.
 There are two different algorithms in DSVerifier that can be used for
 stability verification, one based on Schur's decomposition and another
-one based on Jury's criteria \cite{DBLP:journals/dafes/BessaICF16};
-here, the Jury's method is chosen due to its efficiency.
+one based on Jury's criteria \cite{DBLP:journals/dafes/BessaICF16}.
+Here, we choose Jury's method due to its efficiency.
 
@@
 \item $R_3: |a_0| < a_N$;
-\item $R_4: m_{11} > 0 \equiv m_{31} \wedge m_{51} \wedge \cdots \wedge m_{(2N−3)(1)}$.
+\item $R_4: m_{11} > 0 \wedge m_{31}>0 \wedge m_{51}>0 \wedge \cdots \wedge m_{(2N{-}3)(1)}>0$.
 \end{itemize}
@@
 $$\phi_{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4)$$
-\cdsay{figure out what is existentially quantified for the final $\sigma$.}
+%\cdsay{figure out what is existentially quantified for the final $\sigma$.}
+
+In the {\sc verify} phase, if the system is unstable for the current candidate solution,
+i.e. if $\neg \phi_{stability}$ is satisfiable for $S(z)$, 
+then we obtain a counterexample denoted by 
+values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$,
+which make the closed-loop system unstable. This uncertainty is added to 
+the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
+we obtain a candidate solution consisting 
+of a controller $D_C$ and $N_C$, which makes the closed-loop 
+system stable for all the uncertainties accumulated in {\sc inputs}.
 

### 2016-10-05 paper/paper.tex
review abstract by Abate

--- 2016-10-05 paper/paper.tex
@@
 \begin{abstract}
-Modern control systems are by and large implemented in digital microcontrollers.
-This poses a new dimension to the problem of correct by design controllers which do not only need to look at the dynamics involved, but also at the effects of digitalization.
-This is particularly true in small size implementations where the effects of word length are significant with respect to the dynamics.
-This work focuses on the synthesis of digital controllers for Linear Time Invariant SISO systems.
-We explore the effects of digitalization of the continuous signals and Fixed Word Length (FWL) in the controller dynamics.
-To this end we propose a CEGIS solution that uses inductive invariant synthesis in conjunction with a digital stability verification algorithm from a well known tool to find a parametric solution for a digital controller given a model specification.
-The algorithm factors in quantization errors, sample and hold behaviour, and parameter representation round-offs.
-The results show...
+Modern control systems are by and large implemented via digital microcontrollers, 
+which are designed to work in an embedded environment, 
+within a dynamical plant that can present physical components. 
+%
+This poses a new dimension to the problem of controllers synthesis,   
+which is classically studied in digital control literature. 
+%
+In this study, we plan to provide a principled approach to extend this literature in a number of directions: 
+we are interested in quantitative tasks;  
+we focus on automated correct-by-design synthesis algorithms, as opposed to verification objectives; 
+and we encompass the compete range of approximations, related to time discretisation, quantisation effects, 
+and finite-precision representations (with related rounding errors). To this end, 
+we propose a CEGIS-based solution that uses inductive invariant synthesis in conjunction with a digital verification algorithm 
+to find a parametric solution for a digital controller given a continuous plant specification. 
 \end{abstract}
@@
 
-\keywords{Control Synthesis, CEGIS, FWL}
+\keywords{Control synthesis, CEGIS, finite word length, time sampling, quantisation, interval analysis}
 
@@
 $$\phi_{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4)$$
-\cdsay{figure out what is existentially quantified for the final $\sigma$.}
+%\cdsay{figure out what is existentially quantified for the final $\sigma$.}
+If the system is unstable,
+i.e. if $\neg \phi_{stability}$ is satisfiable for $S(z)$, then the {\sc verify}
+phase will provide values for each coefficients of $\hat{N_{G}(z)}$ and $\hat{D_{G}(z)}$,
+which make the closed-loop system unstable.
 
@@
 % 2) { (0.02644824981689453125, 1.00053310394287109375, -1.0014629364013671875) }
+
+% <a>
+% <item>7.515781402587890625</item>
+% <item>-4.385616302490234375</item>
+% <item>4.142093658447265625</item>
+% </a>
+% <a_size>3</a_size>
+% <b>
+% <item>-3.52398681640625</item>
+% <item>-1.530254364013671875</item>
+% <item>7.58094024658203125</item>
+% </b>
+% <b_size>3</b_size>
 

### 2016-10-05 paper/paper.tex

@@
 %\cdsay{figure out what is existentially quantified for the final $\sigma$.}
-If the system is unstable,
-i.e. if $\neg \phi_{stability}$ is satisfiable for $S(z)$, then the {\sc verify}
-phase will provide values for each coefficients of $\hat{N_{G}(z)}$ and $\hat{D_{G}(z)}$,
-which make the closed-loop system unstable.
+
+In the {\sc verify} phase, if the system is unstable for the current candidate solution,
+i.e. if $\neg \phi_{stability}$ is satisfiable for $S(z)$, 
+then we obtain a counterexample denoted by 
+values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$,
+which make the closed-loop system unstable. This uncertainty is added to 
+the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
+we obtain a candidate solution consisting 
+of a controller $D_C$ and $N_C$, which makes the closed-loop 
+system stable for all the uncertainties accumulated in {\sc inputs}.
 

### 2016-10-05 paper/paper.tex
+ applying the synthesiser on the running example

--- 2016-10-05 paper/paper.tex
@@
 %
-where $k \in \mathbb{Z}$, such that $0 < k < N − 2$. 
+where $k \in \mathbb{Z}$, such that $0 < k < N - 2$. 
 $S(z)$ is the
@@
 
-\paragraph{Running example synthesis}
+\paragraph{Using the program synthesiser for the running example}
 We will illustrate our synthesis approach on the running example 
 in Sec.~\ref{sec:running-ex}.
-\cdsay{Pascal, I also need the candidate solutions here}
+We start with a candidate solution that has all coefficients 0.
+In the first {\sc verify} phase we obtain the following counterexample:
+$$
+\begin{array}{ll}
+\Delta N_G(z) = 0.02634525299072265625\\
+\Delta D_G(z) = 0.9979267120361328125z-0.99768829345703125
+\end{array}
+$$
+
+We add this counterexample to {\sc inputs} and initiate the {\sc
+  synthesise} phase, where we get the following candidate solution:
+
+$$
+\begin{array}{ll}
+N_C(z) {=} 4.00888156890869140625z^2{-}0.00041961669921875z\\
+\qquad\qquad -0.000213623046875\\
+D_C(z) {=} -0.003753662109375z^2{+}7.37355804443359375z \\
+\qquad\qquad -7.2847900390625\\
+\end{array}
+$$
+
+In the second {\sc verify} phase, we check whether the current candidate
+solution above is the final solution. It is not and we get a new counterexample:
+$$
+\begin{array}{ll}
+\Delta N_G(z) = 0.02644824981689453125\\
+\Delta D_G(z) {=} 1.00053310394287109375z{-}1.0014629364013671875
+\end{array}
+$$
+
+After adding this new counterexample to the set of {\sc inputs}, in the 
+next {\sc synthesise} phase, we get a new candidate solution that holds
+for both uncertainties in {\sc Inputs}:
+
+$$
+\begin{array}{ll}
+N_C(z) {=} 7.515781402587890625z^2{-}4.385616302490234375z\\
+\qquad\qquad +4.142093658447265625\\
+D_C(z) {=} -3.52398681640625z^2{-}1.530254364013671875z \\
+\qquad\qquad +7.58094024658203125\\
+\end{array}
+$$
+
+This candidate solution is validated as the final solution by the next 
+{\sc verify} phase, which fails to find a new counterexample (i.e. returns UNSAT).
+
 % Counterexample from first cruisecontrol02.c benchmark with uncertainty and

### 2016-10-05 paper/paper.tex
fix running example solution
fix running example
revised intro

@@
 these devices requires that they have a robust design that ensures the
-correct behaviour in a number of environments.  For this reason it is
-necessary to provide design tools that formally verify the correctness
-of the digital controller and in particular we explore the automatic
-synthesis of these controllers which reduces the deveopment cost and
-design time for a number of models.  \cdsay{the last sentence
-  is misleading given that synthesis is not a special case of
-  verification, but taking it one step forward.}
-
-We are interested in the stability of hybrid closed-loop systems,
-i.e., embedded controllers along with a model of their physical
-environment, the plant, as shown in Fig.~\ref{fig:closed-system}.
-\cdsay{in the next paragraph we say that our primary interest is
-  evaluating digital effects in addition to stability, which
-  contradicts the previous sentence, where we only mention stability.}
-Due to the complexity of such systems, we focus on linear models with
-known configurations to perform parametric synthesis of the controller
-dynamics.
+correct behaviour in a number of environments.  % For this reason it is
+% necessary to provide design tools that formally verify the correctness
+% of the digital controller.
+
+\cdsay{Mention that the resulting systems are also expected to have certain properties, 
+e.g. stability, which makes it even more difficult to synthesise them?}
+
+In this paper, we explore the automatic synthesis of 
+{\em correct-by-construction} controllers, which 
+reduces the deveopment cost and design time for a number of models.  
+In particular, we are interested in synthesising controllers 
+for {\em hybrid closed-loop systems}, i.e., embedded controllers along with a model of their
+physical environment, the plant, as shown in
+Fig.~\ref{fig:closed-system}, that are {\em stable}.  Due to the complexity
+of such systems, we focus on linear models with known configurations
+to perform parametric synthesis of the controller dynamics.
 
@@
 For this particular example, the actual implementation of $C(z)$ using
-\param{3}{16} implementation format can be represented by the following
+\param{20}{20} implementation format can be represented by the following
 z-expression:
@@
 \resizebox{0.5\textwidth}{!}{
-$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2 - 4.1529998779296875z + 1.89599609375}{z^2 - 1.843994140625z + 0.8495941162109375},$
+$C_{q}\left(z\right) {:=} \frac{4.00888156890869140625z^2{-}0.00041961669921875z
+-0.000213623046875}{-0.003753662109375z^2{+}7.37355804443359375z-7.2847900390625},$
 }

### 2016-10-06 paper/paper.tex
comment

@@
 \cdsay{Mention that the resulting systems are also expected to have certain properties, 
-e.g. stability, which makes it even more difficult to synthesise them?}
+e.g. stability, which makes it even more difficult to synthesise the controllers?}
 

### 2016-10-06 paper/paper.tex
review introduction

@@
 linear control, spanning many areas such as environmental control and
-robotic manipulations. The downside to this approach is that in order
+robotic manipulations \textcolor{red}{Dario: could you please insert a citation here?}. 
+The downside to this approach is that in order
 to achieve low prices, devices are often limited in their
 capabilities, be it a low number of gates in an FPGA or short word
-lengths for microcontrollers. In most cases a floating point
+lengths for microcontrollers. In most cases a floating-point
 implementation is not feasible and the system can benefit from the
-added resolution of a fixed point representation. The ubiquity of
+added resolution of a fixed-point representation. The ubiquity of
 these devices requires that they have a robust design that ensures the
-correct behaviour in a number of environments.  % For this reason it is
+correct behaviour in a number of different environments.  % For this reason it is
 % necessary to provide design tools that formally verify the correctness
@@
 
-\cdsay{Mention that the resulting systems are also expected to have certain properties, 
-e.g. stability, which makes it even more difficult to synthesise the controllers?}
-
-In this paper, we explore the automatic synthesis of 
+There has been previous work to formally verify uncertain linear systems stability 
+in digital controllers with considerations to the implementation aspects~\cite{Bessa16}.
+In particular, Bessa {\it et al.} considers finite-word length
+(FWL) effects over controllers and also parameter uncertainties
+in the context of verifying the (so-called) robust non-fragile stability.
+However, the authors do not consider the compete range of approximations, 
+related to time discretisation, and quantisation effects. Additionally, they do not find 
+a parametric solution for a digital controller given a continuous plant specification, 
+in order to synthesize the controller implementation.
+
+In this paper, however, we explore the automatic synthesis of 
 {\em correct-by-construction} controllers, which 

### 2016-10-06 paper/paper.tex
add new reference

@@
 (FWL) effects over controllers and also parameter uncertainties
-in the context of verifying the (so-called) robust non-fragile stability.
+in the context of verifying the (so-called) robust non-fragile stability~\cite{bhattacharyya97}.
 However, the authors do not consider the compete range of approximations, 
-related to time discretisation, and quantisation effects. Additionally, they do not find 
-a parametric solution for a digital controller given a continuous plant specification, 
-in order to synthesize the controller implementation.
+related to time discretisation, and quantisation effects. As a result,
+the stability verification method proposed by Bessa {\it et al.} is incomplete, 
+given that false alarms can be produced due to the quantisation effects. 
+Additionally, the authors do not find a parametric solution for a digital controller 
+given a continuous plant specification, in order to synthesize the controller implementation.
 
@@
 The resulting closed loop system is a program loop working over
-bit-vectors of fixed point arithmetic with fixed word length. The
+bit-vectors of fixed-point arithmetic with fixed word length. The
 effect of the FWL is included in the model as a parametric uncertainty

### 2016-10-06 paper/paper.tex
fix running example
hscc17

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{A Uncertainty Model for Quantization Error} 
-\label{sec:uncertainty-model-quantization-error}
-
-In this study, an uncertain plant model $\hat{G}(z)$ is split into two terms:
+\section{Modelling Errors}
+
+In this section, we show how to embed discretisation errors on the plant model, as follows: 
+%$\hat{G}(z)$ is split into two terms:
 %
@@
 \label{eq:uncertainplant}
-\hat{G}(z)=G(z)+\Delta{G(z)},
-\end{equation}
+%\hat{G}(z)=G(z)+\Delta{G(z)},
+\tilde G(z) = \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z),   
+\end{equation}
+where $G(z,T)$ is the time discretisation of the nominal physical plant $G(s)$,
 
@@
 $\Delta{G(z)}$ is the additive uncertainty, which is related to parametric
-uncertainties~\cite{Bessa16}.  Here, an uncertainty model to accommodate the
+uncertainties~\cite{Bessa16}.
+
+\subsection{A Uncertainty Model for Quantization Error} 
+\label{sec:uncertainty-model-quantization-error}
+
+Here, an uncertainty model to accommodate the
 quantization noise effects on $\hat{G}(z)$ is proposed.  As a result,
@@
 }
- \caption{Sampled System. \label{fig:sampledsystem}}
+ \caption{Sampled System. \label{fig:sampledsystem} \red{[Please update this figure: reference enters downstream of control block. Clarify signals over lines in plot.]}}
 \end{figure}
@@
 For this particular example, the actual implementation of $C(z)$ using
-\param{20}{20} implementation format can be represented by the following
+\param{4}{16} implementation format can be represented by the following
 z-expression:
@@
 \resizebox{0.5\textwidth}{!}{
-$C_{q}\left(z\right) {:=} \frac{4.00888156890869140625z^2{-}0.00041961669921875z
--0.000213623046875}{-0.003753662109375z^2{+}7.37355804443359375z-7.2847900390625},$
+$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
+{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375},$
 }

### 2016-10-06 paper/paper.tex
hscc17

@@
 where $G(z,T)$ is the time discretisation of the nominal physical plant $G(s)$, 
-
-\noindent where $G(z)$ is the discretized nominal plant model and
-$\Delta{G(z)}$ is the additive uncertainty, which is related to parametric
-uncertainties~\cite{Bessa16}.
-
-\subsection{A Uncertainty Model for Quantization Error} 
+$\Delta{G_{Q}(z)}$ represents the quantisation uncertainty model, 
+and $\Delta{G_{P}(z)}$ describes the parametric uncertainty model.
+
+%\noindent where $G(z)$ is the discretized nominal plant model and
+%$\Delta{G(z)}$ is the additive uncertainty, which is related to parametric
+%uncertainties~\cite{Bessa16}.
+
+\subsection{An Uncertainty Model for the Quantization Error} 
 \label{sec:uncertainty-model-quantization-error}
 
-Here, an uncertainty model to accommodate the
-quantization noise effects on $\hat{G}(z)$ is proposed.  As a result,
-Eq.~\eqref{eq:uncertainplant} is rewritten as
-%
-\begin{equation}
-\label{eq:uncertainFWLplant}
-\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}+\Delta{G_{P}(z)},
-\end{equation}
-
-\noindent where $\Delta{G_{Q}(z)}$ represents the quantization uncertainty
-model and $\Delta{G_{P}(z)}$ describes the parametric uncertainty model. 
-Thus, a model for $\Delta{G_{Q}(z)}$ that can represent the quantization
+%Here, an uncertainty model to accommodate the
+%quantization noise effects on $\hat{G}(z)$ is proposed.  
+%As a result, Eq.~\eqref{eq:uncertainplant} is rewritten as
+%
+%\begin{equation}
+%\label{eq:uncertainFWLplant}
+%\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}+\Delta{G_{P}(z)},
+%\end{equation}
+
+A model for $\Delta{G_{Q}(z)}$ that can represent the quantization
 noise effect in the plant output, and consequently the closed-loop system
-output, is proposed.  For convenience, the parametric uncertainties will be
-described here.
+output, is proposed.  
+\red{[eliminate next:] 
+For convenience, the parametric uncertainties will be described here.}
 
@@
 
+\subsection{Modelling Error on Parameters Representation} 
+%\label{sec:}
+
+\red{[TO BE COMPLETED.]}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-10-06 paper/paper.tex
hscc17

@@
 \usepackage[dvipsnames]{xcolor}
+\usepackage{amssymb,amsmath,amsfonts} 
+\usepackage{mathtools}
 
@@
 \newtheorem{mylemma}{Lemma}
+\newtheorem{myprop}{Proposition}
 
@@
 
-Consider the closed-loop sampled system in Figure~\ref{fig:sampledsystem},
+Consider the closed-loop sampled system in Figure~\ref{fig:sampledsystem} \red{[requires updating]},
 where $C(z)$ is the digital controller model, whose control output signal is
 quantized ($Q2$) and interpolated via a ZOH using digital-to-analog
-converter (DAC).  $G(s)$ is the continuous-time model of the plant, from
+converter (DAC).  
+\red{[do we really need to regard the quantisation effects of the ZOH in the DAC? Elaborate next:]}
+$G(s)$ is the continuous-time model of the plant, from
 which output samples are taken and quantized ($Q1$) by means of an
@@
 The quantization noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
-$Q2$) \red{[do we need the second? See my further comments below.]} \green{There was a typo in \eqref{eq:deltaG_final}. It was missing $q_{1}$ and $q_{1}$, both effects are considered here. }
+$Q2$) \red{[do we need the second?
+See my further comments below.]} \green{There was a typo in \eqref{eq:deltaG_final}.
+It was missing $q_{1}$ and $q_{1}$, both effects are considered here.
+} \red{[why are both needed?
+I'm still unconvinced.]}
 are white noises.
@@
 %
-The controller and plant are linear, {\it i.e.} any source of nonlinearity ({\it e.g.} overflows) may be disregard.
+The controller and the plant are linear, {\it i.e.} any source of nonlinearity ({\it e.g.} overflows) may be disregard.
 %\red{[explain difference btw overflows and saturations.
@@
 \end{mylemma}
-
-\noindent where $q$ is the step size of quantizer.
+where $q$ is the step size of quantizer. \blue{[can you add a comment on this assumption? Why the factor 12?]}
 
@@
 \label{eq:pulsetf}
-G(z)=(1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
+G(z) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
 \end{equation}
 \end{mylemma}
-\red{[Here the dependence on the sampling time T needs to appear somewhere.]} \green{It appears,  $kT$ is the time $t$ used after the inverse Laplace transform}
-
-Considering the quantization noise $\nu(k)$ as an output error in the
-discrete plant model, {\it i.e.}, it does not affect the plant dynamics, but
-its output samples, it is easy to prove that $\Delta{G_{Q}(z)}$ can be
-obtained from
+\red{[Here the dependence on the sampling time T needs to appear somewhere.]} 
+\green{It appears,  $kT$ is the time $t$ used after the inverse Laplace transform}
+\red{[ok, then let's call it $G(z,T)$ as I suggested earlier.]}
+
+\begin{myprop}
+Considering the quantisation noise $\nu(k)$ as an output error in the
+discrete plant model, 
+%{\it i.e.}, it does not affect the plant dynamics, but its output samples, 
+$\Delta{G_{Q}(z)}$ can be obtained from
 %
@@
 \end{equation}
-
-\noindent where $\nu(z)$ is the z-transform of the random process $\nu(k)$,
+where $\nu(z)$ is the z-transform of the random process $\nu(k)$,
 which can be calculated through the power spectral density of
-$\nu(k)$~\cite{poularikas2000transforms}.  Thus, the $\Delta{G_{Q}(z)}$ can
-expressed as
+$\nu(k)$~\cite{poularikas2000transforms}.  
+Thus, the $\Delta{G_{Q}(z)}$ can expressed as
 %
@@
 \end{equation}
-
-\noindent where $\sigma_{Q}^{2}$ is the variance of the quantization noise and
+where $\sigma_{Q}^{2}$ is the variance of the quantization noise and
 $U(z)$ is the z-transform of control signal ({\it i.e.}, the z-transform of
@@
 means of ZOH.
-
-\red{[Please write out a formal statement for the proof below:]}
+\end{myprop}
+
 %

### 2016-10-06 paper/paper.tex
hscc17

@@
 
+\blue{[Perhaps we should anticipate this example, partly showing potential repercussions of our formal approach. 
+Indeed, this example does not show the full potential, since it does not start with the physical plant $G(s)$. ]}
+
 A classical cruise control example is extracted from the
@@
 
-Using an optimization tool, Wang {\it et
-al.}~\cite{DBLP:conf/hybrid/WangGRJF16} design a high-performance
-controller, which is characterized by the following z-expression:
-
+Using an optimisation tool, 
+the work in~\cite{DBLP:conf/hybrid/WangGRJF16} has designed a high-performance controller that is characterised by the following z-domain transfer function:
 \begin{equation}
@@
 \end{equation}
-
-The authors claim that this controller $C(z)$ is extremely stable for the
-discrete plant model $G(z)$.  However, if implementation aspects are
-considered during verification, this controller becomes unstable.
-
-For this particular example, the actual implementation of $C(z)$ using
-\param{4}{16} implementation format can be represented by the following
-z-expression:
-
+The authors claim that this controller $C(z)$ is extremely stable for the discrete plant model $G(z)$.  
+However, if \red{[which ones? quantisation?] implementation aspects} are considered during verification, 
+this controller becomes unstable.
+%
+Indeed, the actual implementation of $C(z)$ using \param{4}{16} \red{[clarify this notation]} 
+implementation format can be represented by the following expression: 
 \begin{equation}
@@
 \end{equation} 
-
-\noindent which makes the system unstable in closed-loop using the typical series loop configuration.
+which makes the system unstable in closed-loop \red{using the typical series loop configuration [meaning?]}.
 

### 2016-10-06 paper/paper.tex
hscc17

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Program Synthesis}
+\section{\red{Automated} Program Synthesis for \red{for Controllers}}
 
@@
 %
+\red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
+(Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
+% 
 The design of our synthesiser is given in
 Fig.~\ref{fig:CEGIS} and consists of two phases, {\sc
-Synthesise} and {\sc Verify}, which interact via a finite set of test vectors {\sc inputs}.
+Synthesise} and {\sc Verify}, which interact via a finite set of test vectors {\sc inputs} \blue{that is updated incrementally}.
 The {\sc synth} procedure tries to find an existential witness $P$
-that satisfies the specification $\sigma(x, P)$ for all $x$:
+that satisfies the specification $\sigma(x, P)$ for all $x$, namely:
 %
@@
 candidate solution to the full synthesis formula.  We pass this candidate
-solution to {\sc verify} which determines whether it does satisfy
-the specification on all inputs by checking satisfiability of the
+solution to {\sc verify}, which determines whether it does satisfy
+the specification on all inputs by checking satisfiability of the following 
 verification formula:
@@
 to meet the specification.  This witness $x$ is added to the {\sc inputs}
-set and the loop iterates again.  It is worth noting that each iteration of the
-loop adds a new input to the set of inputs being used for synthesis.  If
-the full set of inputs is finite, this means that the refinement loop
+set, and the loop iterates again.  It is worth noting that each iteration of the
+loop adds a new input to the \red{finite} set $\text{\sc inputs}$  being used for synthesis.  If
+the full set of inputs \blue{[which by now should have a name, as suggested to be introduced above]} is finite, this means that the refinement loop
 can only iterate a finite number of times.
 
-\paragraph{Elements specific to control systems}
+\paragraph{Synthesis elements specific to control systems}
 Next, we describe the specific property that we pass to the 
@@
 stability verification, one based on Schur's decomposition and another
-one based on Jury's criteria \cite{DBLP:journals/dafes/BessaICF16}.
-Here, we choose Jury's method due to its efficiency.
-
-Essentially, we use this method to check the stability in the $z$-domain
-for the characteristic polynomial $S(z)$ of 
-the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$.
+one based on Jury's criteria \cite{DBLP:journals/dafes/BessaICF16} \red{[Jury here is our friend, I wouldn't use his first name ... ]}.
+Here, we choose Jury's method, due to its efficiency.
+
+We use this method to check the stability in the $z$-domain for the characteristic polynomial $S(z)$ of 
+the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$ \red{[unclear: what matrix?
+We need to clarify the relationship between the char.
+poly.
+$S(z)$ and the later quantities $\Delta N_{G}(z), \Delta D_{G}(z)$ and corresponding controller's structure.]}.
 We consider the following form for $S(z)$:
@@
 \end{array}
-\right)
+\right), 
 $$
@@
 $S(z)$ is the
-characteristic polynomial of a stable system if and only if
-the following four propositions hold:
+characteristic polynomial of a stable system if and only if the following four conditions hold:
 \begin{itemize}
@@
 constraint of the form:
-$$\phi_{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4)$$
+$$
+\phi_{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
+$$
 %\cdsay{figure out what is existentially quantified for the final $\sigma$.} 
+\red{[Yes, intuitively all clear, however for the sake of clarity I would like to see the explicit mapping between the above formula and the previously used specification 
+$\sigma(x, P)$, with clear elucidation of the relationship between the domain of $z$ and that of $x$.]}
 
@@
 then we obtain a counterexample denoted by 
-values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$,
+values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$ \red{[see my comment above - these quantities pop up too abruptly.]},
 which make the closed-loop system unstable. This uncertainty is added to 
@@
 
-\paragraph{Using the program synthesiser for the running example}
+\paragraph{Program synthesis for the running example}
 We will illustrate our synthesis approach on the running example 
 in Sec.~\ref{sec:running-ex}.
-We start with a candidate solution that has all coefficients 0.
+We start with a candidate solution that has all coefficients 0 \red{[Be more explicit, write out spurious candidate solution with zero coefficients.
+KISS - you don't want to lose the control audience here.]}.
 In the first {\sc verify} phase we obtain the following counterexample:
@@
 
-We add this counterexample to {\sc inputs} and initiate the {\sc
-  synthesise} phase, where we get the following candidate solution:
-
+We add this counterexample to {\sc inputs} and initiate the {\sc synthesise} phase, where we get the following candidate solution: 
+\red{[ How is the order of the candidate solution chosen here?]}
 $$
@@
 $$
-
+\blue{[Nice, now I'm in the groove. Next unfolds well.] }
 After adding this new counterexample to the set of {\sc inputs}, in the 
@@
     ([yshift=2em]synth.east) edge node {Candidate solution} ([yshift=2em]verif.west)
-    ([yshift=-2em]verif.west) edge node {Counter-ex} ([yshift=-2em]synth.east)
+    ([yshift=-2em]verif.west) edge node {Counterexample} ([yshift=-2em]synth.east)
     ([xshift=5em]verif.south) edge node {Candidate $P$} ([xshift=5em]bmc.north)
@@
 }
- \caption{Counterexample-Guided Inductive Synthesis. \label{fig:CEGIS}}
+ \caption{Counterexample-Guided Inductive Synthesis of Programs (CEGIS paradigm). \label{fig:CEGIS}}
 \end{figure*}
@@
 %---------------------------------
+
+\red{[All very interesting, however we never start from a $G(s)$ plant, we never really display the whole capabilities of the technique! Or am I missing something?]}
 

### 2016-10-06 paper/paper.tex
Working on comments

@@
 zero-order hold (ZOH) discretization is more suitable for representing the
-sampling processes that are typically employed by hybrid
-systems~\cite{istepanian2012digital} 
-\red{[but the ZOH is for the DAC, not for the ADC?]}.
+sampling and holding processes that are typically employed by hybrid
+systems~\cite{istepanian2012digital}, i.e.
+the ZOH discretization models the exact effect of sampling and DAC interpolation over the plant.% {\item \red{[but the ZOH is for the DAC, not for the ADC?]}.
 
@@
 output, is proposed.  
-\red{[eliminate next:] 
-For convenience, the parametric uncertainties will be described here.}
+%\red{[eliminate next:] 
+%For convenience, the parametric uncertainties will be described here.}
 
@@
 \label{eq:pulsetf}
-G(z) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
-\end{equation}
+G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
+\end{equation}
+
+For convenience, we will use only the notation $G(z)$ for represent the pulse transfer function.
 \end{mylemma}
-\red{[Here the dependence on the sampling time T needs to appear somewhere.]} 
-\green{It appears,  $kT$ is the time $t$ used after the inverse Laplace transform}
-\red{[ok, then let's call it $G(z,T)$ as I suggested earlier.]}
+%\red{[Here the dependence on the sampling time T needs to appear somewhere.]} 
+%\green{It appears,  $kT$ is the time $t$ used after the inverse Laplace transform}
+%\red{[ok, then let's call it $G(z,T)$ as I suggested earlier.]}
 
@@
 %
-\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factors \red{[define scale factors]} for the
-quantization $Q1$ and $Q2$, respectively; $q_{1}$ and $q_{2}$ are the quantization step for $Q1$ and $Q2$, respectively, and $\sum {h_{Q1}^{2}}$ and $\sum
+\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factors, {\it i.e.} constant gains usually employed before the ADC and after the DAC in order to avoid the overload of converters  %\red{[define scale factors]}
+for the quantization $Q1$ and $Q2$, respectively; $q_{1}$ and $q_{2}$ are the quantization step for $Q1$ and $Q2$, respectively, and $\sum {h_{Q1}^{2}}$ and $\sum
 {h_{Q2}^{2}}$ are the squares sums of the impulse response obtained by means

### 2016-10-07 paper/paper.tex
Improvement of figure 3 (still need to agree on the reference signal entry location (should be after the ADC) Monor fixes

@@
 we focus on automated correct-by-design synthesis algorithms, as opposed to verification objectives; 
-and we encompass the compete range of approximations, related to time discretisation, quantisation effects, 
+and we encompass the complete range of approximations, related to time discretisation, quantisation effects, 
 and finite-precision representations (with related rounding errors). To this end, 
@@
 quantized ($Q2$) and interpolated via a ZOH using digital-to-analog
-converter (DAC).  
-\red{[do we really need to regard the quantisation effects of the ZOH in the DAC? Elaborate next:]}
+converter (DAC). The quantization occurs because the DAC resolution may be different from the fixed point representation of the controller.  
 $G(s)$ is the continuous-time model of the plant, from
@@
 \centering
+
+\tikzset{add/.style n args={4}{
+    minimum width=6mm,
+    path picture={
+        \draw[circle] 
+            (path picture bounding box.south east) -- (path picture bounding box.north west)
+            (path picture bounding box.south west) -- (path picture bounding box.north east);
+        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+        }
+    }
+ }
+
 \resizebox{.5\textwidth}{!}{
@@
 %   \& \coordinate (aux0);
-   \& \node[circle] (circle) {};
+   \& \node[circle,add={-}{+}{}{}] (circle) {};
    \& complexnode/.pic={ 
@@
 	minimum width=4cm,
-	minimum height=1cm,
+	minimum height=1.6cm,
 	label=\textbf{ADC},] (adc) {};
@@
    \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
-   \node[fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {{\sc Q1}};} 
+   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
+     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
+   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu1$};
    \& \node[rectangle,draw,
@@
         label=\textbf{Controller}] (cz) {{\sc C(z)}};
+   \node[draw=none] (u) at ([xshift=1cm,yshift=.1cm]cz)  {u};
+
    \& complexnode/.pic={ 
@@
 	minimum width=3cm,
-	minimum height=1cm,
+	minimum height=1.6cm,
 	label=\textbf{DAC},] (dac) {};
-     \node[fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {{\sc Q2}};
+     \node[circle,add={}{+}{+}{},fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {};
+     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
+     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu2$};
      \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}
@@
 
+  \path[->] (v1) edge (q1.north);
+  \path[->] (v2) edge (q2.north);
   \path[->] (r) edge (circle.west);
@@
 The quantization noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
-$Q2$) \red{[do we need the second?
-See my further comments below.]} \green{There was a typo in \eqref{eq:deltaG_final}.
-It was missing $q_{1}$ and $q_{1}$, both effects are considered here.
-} \red{[why are both needed?
-I'm still unconvinced.]}
-are white noises.
+$Q2$) are white noises.
 %
@@
 %
-The controller and the plant are linear, {\it i.e.} any source of nonlinearity ({\it e.g.} overflows) may be disregard.
-%\red{[explain difference btw overflows and saturations.
-Also, do we care about limit cycles?
-I'd quite happily disregard them.]}
+The controller and the plant are linear, {\it i.e.} any source of nonlinearity ({\it e.g.} overflows, ADC/DAC nonlinearities) will be disregarded.
+\red{should we explicitly state we want a controller that does not saturate?}
 %

### 2016-10-07 paper/paper.tex
Initial approximation at Alessandro's request for clear nomenclature (still some work to be done on G(s) and the propagation of errors during synthesis)

@@
 \noindent where $\beta$ and $\alpha$ are the controller's coefficients, $b$
-and $a$ are the plant's coefficients, and $N$ and $M$ are the number of bits
-of the integer and fractional part, respectively.  Note that $G(z)$ is a
+and $a$ are the plant's coefficients, and $N$ and $M$ are the number of poles and zeros for the corresponding block.
+
+Note that $G(z)$ is a
 discrete model of a real (and continuous) plant, {\it i.e.}, a continuous
@@
 sampling and holding processes that are typically employed by hybrid
-systems~\cite{istepanian2012digital}, i.e.
-the ZOH discretization models the exact effect of sampling and DAC interpolation over the plant.% {\item \red{[but the ZOH is for the DAC, not for the ADC?]}.
-
-Let $C(z)$ and $G(z)$ transfer functions be arranged in vectors $c_0$ and
-$g_0$, respectively.  For each $C(z)$ implementation, there is a function
-$\mathit{FWL}[\cdot]:\mathbb{R}^{N_C+M_C}\rightarrow
-Q[\mathbb{R}^{N_C+M_C}]$, which applies FWL effects to the controller
-$C(z)$, where $Q[\mathbb{R}]$ represents the quantized set of representable
-real numbers in the chosen implementation format \param{N_C}{M_C} \red{[clarify this notation]}.  The
-quantized controller parameters vector ($c$) is generated via
-$\mathit{FWL}[c_0]$.  The uncertain plant parameters ($g$) can be expressed
-as
-%
-\begin{equation}
-g = g_0 + \Delta{g} = \left [
-				\begin{tabular}{c}
-				$b_{0}+\Delta{b_{0}} ~ b_{1}+\Delta{b_{1}} ~ ... ~ b_{M_G}+\Delta{b_{M_G}}$ \\%~ 
-				$a_{0}+\Delta{a_{0}} ~ a_{1}+\Delta{a_{1}} ~ ... ~ a_{N_G}+\Delta{a_{N_G}}$
-				\end{tabular}
-				\right ],
-\end{equation}
+systems~\cite{istepanian2012digital}, i.e. the ZOH discretization models the exact effect of sampling and DAC interpolation over the plant.
+
+Since $G(z)$ is an approximation of $G(s)$ calculated via a discrete z transform using a selected sampling time, we denote the error in the approximation as $\Delta{G}_P$
+\begin{align}
+\small
+\label{parametric_plant_tf}
+\hat{G}(z)&=\frac{(b_{0}+\Delta_p b_{0}) +...+(b_{M_G}+\Delta_p b_{M_G})z^{-M_G}}{(a_{0}+\Delta_p a_{0})+...+(a_{N_G}+\Delta_p a_{N_G})z^{-N_G}} \nonumber \\
+&=G(z,T)+\Delta{G}_P(z,T).
+\end{align}
+Note that $\Delta{G}_P$ is undefined and upperbound by a user defined percentage which relates to the nature of the z transform and the sampling time.
+For simplicity we will use $G(z)$ to represent $G(z,T)$.
+
+Let $\tilde C(z)$ and $\tilde G(z)$ be the same transfer functions represented using a Fixed Point Finite Word Length with integer size $I$ and fractional size $F$.
+We shall denote this domain as $\mathbb{R}\langle I,F \rangle$
+\begin{align}
+\small
+\label{digital_controller_plant_tf}
+\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
+%\label{plant_tf}
+\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
+\end{align}
+
+Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ domain, 
+ $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
+However, since the plant was originally in the real domain,
+\begin{align}
+\small
+\label{digital_plant_tf}
+&\exists f (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I,F \rangle : \nonumber \\
+\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_q \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_q \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_q \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_q \hat{a}_{N_G})z^{-N_G}} \nonumber \\
+&=G(z)+\Delta{G}_P(z)+\Delta{G}_Q(z).
+\end{align}
 
 \vspace{1 mm} 
-\noindent where $\Delta{g}$ represents the plant uncertainties coefficients. The polynomial set of possible values of $g$ is denoted by $\mathfrak{G}$.
+\noindent where $\Delta{G}_Q(z)$ represents the plant uncertainty caused by the rounding off effect.
+We may encompass all the uncertainty as $\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_Q(z)$.
+Since this value is nondeterministic, the polynomial set of possible values of $\tilde G(z)$ is denoted by $\mathfrak{G}$.
 
@@
 The DAC interpolator is an ideal ZOH; it takes the discrete value of control
-signal $u(k)$ at instant $k$ and produces a rectangular pulse of height
+signal $u_d(k)$ at instant $k$ and produces a rectangular pulse of height
 $u(k)$ and width equal to the sample time $T$.

### 2016-10-08 paper/paper.tex
move running example section
review RUNNING EXAMPLE

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Running Example} \label{sec:running-ex}
+
+To exploit the present approach full potential, a dynamical plant that can present 
+physical components must be considered. However, a discrete plant model can also demonstrate 
+some benefits of the present approach, which considers FWL effects in the digital 
+controller implementation. In particular, a classical cruise control example 
+is extracted from the literature~\cite{Astrom08}, where the discrete plant model (with time step
+of $0.2$s) is represented by the following z-expression:
+%
+\begin{equation}
+\label{Eq:running-example-plant}
+G\left(z\right) := \frac{0.0264}{z-0.9998}.
+\end{equation}
+
+Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16} has designed 
+a high-performance controller, which is characterised by the following z-domain transfer function:
+\begin{equation}
+\label{Eq:running-example-controller}
+C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
+\end{equation}
+The authors claim that this controller $C(z)$ is extremely stable for the discrete plant model $G(z)$.  
+However, if implementation aspects are considered during verification ({\it e.g.}, fixed-point arithmetic 
+and word-length), then this controller becomes unstable.
+%
+Indeed, the actual implementation of $C(z)$ using \param{4}{16} implementation format 
+({\it i.e.}, $4$ bits for the integer part and $16$ bits for the fractional part)
+can be represented by the following expression: 
+\begin{equation}
+\label{Eq:running-example-controller-quantized}
+\resizebox{0.5\textwidth}{!}{
+$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
+{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375},$
+}
+\end{equation} 
+which makes the system unstable in closed-loop using fixed-point arithmetic and 
+the typical series loop configuration, where $C_{q}\left(z\right)$ and $G\left(z\right)$ 
+are in the forward path.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Modelling Errors}
@@
 \red{[TO BE COMPLETED.]}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Running Example} \label{sec:running-ex}
-
-\blue{[Perhaps we should anticipate this example, partly showing potential repercussions of our formal approach. 
-Indeed, this example does not show the full potential, since it does not start with the physical plant $G(s)$. ]}
-
-A classical cruise control example is extracted from the
-literature~\cite{Astrom08}, where the discrete plant model (with time step
-of $0.2$s) is represented by the following z-expression:
-
-\begin{equation}
-\label{Eq:running-example-plant}
-G\left(z\right) := \frac{0.0264}{z-0.9998}.
-\end{equation}
-
-Using an optimisation tool, 
-the work in~\cite{DBLP:conf/hybrid/WangGRJF16} has designed a high-performance controller that is characterised by the following z-domain transfer function:
-\begin{equation}
-\label{Eq:running-example-controller}
-C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
-\end{equation}
-The authors claim that this controller $C(z)$ is extremely stable for the discrete plant model $G(z)$.  
-However, if \red{[which ones? quantisation?] implementation aspects} are considered during verification, 
-this controller becomes unstable.
-%
-Indeed, the actual implementation of $C(z)$ using \param{4}{16} \red{[clarify this notation]} 
-implementation format can be represented by the following expression: 
-\begin{equation}
-\label{Eq:running-example-controller-quantized}
-\resizebox{0.5\textwidth}{!}{
-$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
-{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375},$
-}
-\end{equation} 
-which makes the system unstable in closed-loop \red{using the typical series loop configuration [meaning?]}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Error Bound Verification}
-
-%As described in the literature, computation using FWL leads to rounding and truncation errors~\cite{Oppenheim1999}.
-In the present work, impairments present on a closed-loop  system output, due to coefficient rounding and arithmetic-operation results, are considered.
-Let $x$ be a real number and $x^*$ be a floating-point representation of $x$.
-The absolute error $\epsilon$, due to the rounding of $x$ represented in floating-point as $x^*$, is
-%
-%\begin{equation} \label{absolute-error}
-%x^* = x + \epsilon,
-%\end{equation}
-
-%\noindent and the relative error $\delta$ by
-%
-%\begin{equation} \label{relative-error}
-%x^* = x\left(1+\delta\right).
-%\end{equation}
-
-%The verification of output error bound is proposed, where the output of a closed-loop system, implemented with reduced-word-length floating-point representation, is compared with a reference output of the same structures, implemented using real variables.
-
-%Thus, considering that the number of precision bits $l_{d}$ in reference models is higher than in designed models, the quantization error $E_{r}$ is given by
-%\begin{equation} \label{errorfixlimits}
-%-2^{-l-1} + 2^{-l_{d}-1} \leq E_{r} \leq 2^{-l-1} - 2^{-l_{d}-1}.
-%\end{equation}
-
-%The expression above shows that the error, computed with the proposed method, is affected by the precision of the reference model.
-
-%For the reduced floating-point models, the computed values are saturated to the maximum representable number on overflow, or to the minimum on underflow; the same input is applied to both models.
-The input vector uses non-deterministic values from $\{ 2^{k-1}-2^{-l}, 2^{-l}, 0, -2^{-l}, 2^{k-1} \}$, that is, values for maximum and minimum amplitudes of the input signal.
-So, errors due to quantization and saturation are explored.
-
-%During closed-loop operation unrolling, the cumulative error can increase beyond the quantization-error interval.
-The following literal is then generated, in order to check whether the output error is in accordance with an acceptable margin:
-%\begin{equation} \label{errorcheck}
-%	l_{no\_error} \Leftrightarrow \arrowvert y - y_{d} \arrowvert \leq M \cdot 2^{-l-1},
-%\end{equation}
-
-%\noindent where $y$ is the output of the designed system, $y_{d}$ is the output of the double precision system, and $M~2^{-l-1}$ is the tolerance margin.
-The verification process searches for the negation of this literal.
-When such a counterexample is found, it indicates that the output error is higher than expected for that controller realization.
 

### 2016-10-08 paper/paper.tex
improve running example section

@@
 \end{equation}
-The authors claim that this controller $C(z)$ is extremely stable for the discrete plant model $G(z)$.  
+The authors claim that this controller $C(z)$ stabilizes the closed-loop system for the discrete plant model $G(z)$.  
 However, if implementation aspects are considered during verification ({\it e.g.}, fixed-point arithmetic 
-and word-length), then this controller becomes unstable.
+and word-length), then this closed-loop system becomes unstable.
 %

### 2016-10-08 paper/paper.tex
add satellite applications

@@
 
-\red{[All very interesting, however we never start from a $G(s)$ plant, we never really display the whole capabilities of the technique! Or am I missing something?]}
-
 The first set of benchmarks considers the discrete plant of a cruise 
@@
 C_3(z)=\frac{1.28\times{10^{3}}z^2 - 1.354240\times{10^{3}}z + 0.074879\times{10^{3}}}{z^2 - 1.4990z + 0.4995}. \nonumber
+\end{equation}
+
+A third set of benchmarks that consists of digital controllers for satellite applications
+is considered~\cite{Franklin15}, in order to evaluate the present approach full capabilities.
+In particular, satellites often require attitude (pose) control for proper orientation 
+of antennas and sensors w.r.t. earth. The satellite attitude control is typically used 
+for three-axis attitude tracking, but here only one axis at a time is considered. 
+The motion equation for the one-axis system, despising disturbance torques, is given by:
+%
+\begin{equation}
+\label{eq:satelliteode}
+I\cdot \ddot{\theta} = \tau_{C},
+\end{equation}
+
+\noindent where $I$ is the inertia moment of satellite about its mass center, $\tau_{C}$ is the control 
+torque applied by thusters, and $\theta$ is the controlled attitude angle. 
+Normalizing Eq.~\eqref{eq:satelliteode} by defining the control signal $u=\frac{\tau_{C}}{I}$ and 
+taking Laplace transform, the following $s$-domain transfer function $G(s)$ is obtained:
+%
+\begin{equation}
+\label{eq:satellitetf}
+G_{3}(s)=\frac{\theta(s)}{u(s)}=\frac{1}{s^2},
+\end{equation}
+
+\noindent using the ZOH discretisation defined in Eq.~\eqref{eq:pulsetf}, the following $z$-domain model is obtained:
+\begin{equation}
+G_{3}(z)= \frac{T^{2}}{2} \frac{z+1}{(z+1)^{2}}.
 \end{equation}

### 2016-10-08 paper/paper.tex
add controller c_4 for the experimental evaluation
improve Description of Benchmarks
cite in ascending order

@@
 increasingly often in program verification
-\cite{DBLP:conf/cav/0001A14,DBLP:conf/lpar/DavidKL15}.  Our program
+\cite{DBLP:conf/lpar/DavidKL15,DBLP:conf/cav/0001A14}.  Our program
 synthesiser makes use of Counter-Example Guided Inductive Synthesis
 (CEGIS) \cite{sketch}.  We start by presenting its general
-architecture followed by describing the parts specific to control
+architecture followed by describing the parts specific to closed-loop control
 systems.
@@
 
-\noindent using the ZOH discretisation defined in Eq.~\eqref{eq:pulsetf}, the following $z$-domain model is obtained:
+\noindent using the ZOH discretisation defined in Eq.~\eqref{eq:pulsetf}, 
+the following $z$-domain model is obtained:
 \begin{equation}
 G_{3}(z)= \frac{T^{2}}{2} \frac{z+1}{(z+1)^{2}}.
+\end{equation}
+
+The discrete controllers $C_{4}$ and $C_{5}$ for the satellite plant $G_{3}$ 
+are represented by the following z-expression:
+%
+\begin{equation}
+\label{satellite-b2}
+C_{4}(z)=\frac{2.88z^2 - 4.896z + 2.074}{1.0z^2 - 0.42z - 0.3465 - 0.03915}. \nonumber
+\end{equation} 
+%
+\begin{equation}
+\label{satellite-c2}
+C_{5}(z)=\frac{0.43z^2 - 0.2408z - 0.1316}{1.0z^2 + 1.5z + 0.97 + 0.183}. \nonumber
 \end{equation}

### 2016-10-08 paper/paper.tex
review Synthesis elements specific to control systems

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{\red{Automated} Program Synthesis for \red{for Controllers}}
+\section{Automated Program Synthesis \\ for Digital Controllers}
 
@@
 There are two different algorithms in DSVerifier that can be used for
-stability verification, one based on Schur's decomposition and another
-one based on Jury's criteria \cite{DBLP:journals/dafes/BessaICF16} \red{[Jury here is our friend, I wouldn't use his first name ... ]}.
-Here, we choose Jury's method, due to its efficiency.
+stability verification~\cite{DBLP:journals/dafes/BessaICF16}, 
+one based on Schur's decomposition and another one based on 
+Jury's criteria~\cite{astrom1997computer}.
+Here, we choose Jury's method~\cite{astrom1997computer}, due to its efficiency.
 

### 2016-10-08 paper/paper.tex
update Figure 4

@@
 In the {\sc verify} phase, if the system is unstable for the current candidate solution,
-i.e. if $\neg \phi_{stability}$ is satisfiable for $S(z)$, 
+{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$, 
 then we obtain a counterexample denoted by 
@@
    \& \\
-   \node (gp) {~~~~~~~~~~~~~~Program Search~~~~~~~~~~~~~~~};
+   \node (gp) {~~~~~~~~~~~~~~Closed-loop System Search~~~~~~~~~~~~~~~};
    \&
@@
 }
- \caption{Counterexample-Guided Inductive Synthesis of Programs (CEGIS paradigm). \label{fig:CEGIS}}
+ \caption{Counterexample-Guided Inductive Synthesis of Closed-loop System (CEGIS paradigm). \label{fig:CEGIS}}
 \end{figure*}

### 2016-10-08 paper/paper.tex
review introduction

@@
 linear control, spanning many areas such as environmental control and
-robotic manipulations \textcolor{red}{Dario: could you please insert a citation here?}. 
+robotic manipulations~\cite{astrom1997computer,Franklin15}. 
 The downside to this approach is that in order
@@
 There has been previous work to formally verify uncertain linear systems stability 
-in digital controllers with considerations to the implementation aspects~\cite{Bessa16}.
+in digital controllers with considerations to the implementation aspects 
+({\it i.e.}, fixed-point arithmetic and word-length)~\cite{Bessa16}.
 In particular, Bessa {\it et al.} considers finite-word length
-(FWL) effects over controllers and also parameter uncertainties
+(FWL) effects over digital controllers and also parameter uncertainties
 in the context of verifying the (so-called) robust non-fragile stability~\cite{bhattacharyya97}.
@@
 Additionally, the authors do not find a parametric solution for a digital controller 
-given a continuous plant specification, in order to synthesize the controller implementation.
+given as a continuous plant specification, in order to synthesize the controller implementation.
 
 In this paper, however, we explore the automatic synthesis of 
-{\em correct-by-construction} controllers, which 
+{\em correct-by-construction} dgital controllers, which 
 reduces the deveopment cost and design time for a number of models.  
 In particular, we are interested in synthesising controllers 
-for {\em hybrid closed-loop systems}, i.e., embedded controllers along with a model of their
+for {\em hybrid closed-loop systems}, {\it i.e.}, embedded controllers along with a model of their
 physical environment, the plant, as shown in

### 2016-10-08 paper/paper.tex
we explicitly state we want a controller that does not saturate

@@
 %
-The controller and the plant are linear, {\it i.e.} any source of nonlinearity ({\it e.g.} overflows, ADC/DAC nonlinearities) will be disregarded.
-\red{should we explicitly state we want a controller that does not saturate?}
+The controller and the plant are linear, {\it i.e.}, any source of nonlinearity ({\it e.g.}, saturation, overflow, ADC/DAC nonlinearities) will be disregarded.
 %

### 2016-10-08 paper/paper.tex
Shorter crisp section 2 with ammended notations

@@
 
-Let us straighten the notations next. 
-We should have 
-\begin{itemize}
-\item 
-$G(s) = \frac{s^{M_G}b_{0}+s^{M_G-1}b_{1}+...+b_{M_G}}{s^{N_G}a_{0}+s^{N_G-1}a_{1}+...+a_{N_G}}$ -- this is the physical plant, which is focus of interest and to which we refer our specifications/properties
-\item 
-$G(z, T) = \frac{\bar b_{0}+\bar b_{1}z^{-1}+...+\bar b_{M_G}z^{-M_G}}{\bar a_{0}+\bar a_{1}z^{-1}+...+\bar a_{N_G}z^{-N_G}}$ -- this is the time-discretised plant (notice the notation encompasses explicitly the sample time $T$; please write out explicitly the relationship between the $a_i$ and the $\bar a_i$ and likewise for the numerator's coefficients
-(in particular, are the orders $M_G, N_G$ the same? 
-\item 
-we have $Y(z) = G(z,T) U(z)$; then, we introduce $\hat Y(z) \doteq Y(z) + \nu (z)$, so that 
-$$
-\frac{\hat Y(z)}{U(z)} = G(z,T) + \frac{\nu (z)}{U(z)} = G(z,T) + \Delta G_Q(z) \doteq \hat G(z) ,  
-$$ 
-where $\Delta G_Q(z)$ is an error term accounting for the quantisation effects 
-\item 
-finally, we encompass the errors resulting from employing finite parameters representation, 
-which we encompass in a term $\Delta G_P(z)$: is this error additive, so that we would get to a 
-$$
-\tilde G(z) \doteq \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z)?  
-$$ 
-Dario, can you write it out explicitly? In other words, if 
-$$
-\hat G(z) = G(z,T) + \Delta G_Q(z) = \frac{\hat b_{0}+\hat b_{1}z^{-1}+...+\hat b_{M_G}z^{-M_G}}{\hat a_{0}+\hat a_{1}z^{-1}+...+\hat a_{N_G}z^{-N_G}},  
-$$ 
-then what is the explicit expression of 
-$$
-\tilde G(z) = \frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}?
-$$
-(Notice that the orders $M_G, N_G$ need to be properly taken care of.)
-\item 
-Now, it's over the transfer function $\tilde G(z)$ that we want to synthesise the parameters of a template $C(z)$. 
-This controller's transfer function will be subject to the same quantisation and precision limits as the plant's: 
-we need to argue that the way we do synthesis affects manipulation of quantities that relate to specific errors and be explicit about these. 
-\item[]
-\item 
-An additional source of error can be related to the fact that a plant transfer function, 
-per se a physical entity, is actually represented in a program imprecisely: 
-this would mean that $G(s)$ is actually 
-$$
-G^\ast (s) \doteq \frac{s^{M_G^\ast}b_{0}+s^{M_G^\ast-1}b_{1}+...+b_{M_G}}{s^{N_G^\ast}a_{0}+s^{N_G^\ast-1}a_{1}+...+a_{N_G}}, 
-$$ 
-which perhaps can indeed be re-written as $G^\ast (s) = G(s) + \Delta G_P(s)$? (This proof should come from that above.) 
-We should argue that this error is encompassed by the one derived above (or isn't it?). 
-\end{itemize}
+%Let us straighten the notations next. 
+%We should have 
+%\begin{itemize}
+%\item 
+%$G(s) = \frac{s^{M_G}b_{0}+s^{M_G-1}b_{1}+...+b_{M_G}}{s^{N_G}a_{0}+s^{N_G-1}a_{1}+...+a_{N_G}}$ -- this is the physical plant, which is focus of interest and to which we refer our specifications/properties
+%\item 
+%$G(z, T) = \frac{\bar b_{0}+\bar b_{1}z^{-1}+...+\bar b_{M_G}z^{-M_G}}{\bar a_{0}+\bar a_{1}z^{-1}+...+\bar a_{N_G}z^{-N_G}}$ -- this is the time-discretised plant (notice the notation encompasses explicitly the sample time $T$; please write out explicitly the relationship between the $a_i$ and the $\bar a_i$ and likewise for the numerator's coefficients
+%(in particular, are the orders $M_G, N_G$ the same? 
+%\item 
+%we have $Y(z) = G(z,T) U(z)$; then, we introduce $\hat Y(z) \doteq Y(z) + \nu (z)$, so that 
+%$$
+%\frac{\hat Y(z)}{U(z)} = G(z,T) + \frac{\nu (z)}{U(z)} = G(z,T) + \Delta G_Q(z) \doteq \hat G(z) ,  
+%$$ 
+%where $\Delta G_Q(z)$ is an error term accounting for the quantisation effects 
+%\item 
+%finally, we encompass the errors resulting from employing finite parameters representation, 
+%which we encompass in a term $\Delta G_P(z)$: is this error additive, so that we would get to a 
+%$$
+%\tilde G(z) \doteq \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z)?  
+%$$ 
+%Dario, can you write it out explicitly? In other words, if 
+%$$
+%\hat G(z) = G(z,T) + \Delta G_Q(z) = \frac{\hat b_{0}+\hat b_{1}z^{-1}+...+\hat b_{M_G}z^{-M_G}}{\hat a_{0}+\hat a_{1}z^{-1}+...+\hat a_{N_G}z^{-N_G}},  
+%$$ 
+%then what is the explicit expression of 
+%$$
+%\tilde G(z) = \frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}?
+%$$
+%(Notice that the orders $M_G, N_G$ need to be properly taken care of.)
+%\item 
+%Now, it's over the transfer function $\tilde G(z)$ that we want to synthesise the parameters of a template $C(z)$. 
+%This controller's transfer function will be subject to the same quantisation and precision limits as the plant's: 
+%we need to argue that the way we do synthesis affects manipulation of quantities that relate to specific errors and be explicit about these. 
+%\item[]
+%\item 
+%An additional source of error can be related to the fact that a plant transfer function, 
+%per se a physical entity, is actually represented in a program imprecisely: 
+%this would mean that $G(s)$ is actually 
+%$$
+%G^\ast (s) \doteq \frac{s^{M_G^\ast}b_{0}+s^{M_G^\ast-1}b_{1}+...+b_{M_G}}{s^{N_G^\ast}a_{0}+s^{N_G^\ast-1}a_{1}+...+a_{N_G}}, 
+%$$ 
+%which perhaps can indeed be re-written as $G^\ast (s) = G(s) + \Delta G_P(s)$? (This proof should come from that above.) 
+%We should argue that this error is encompassed by the one derived above (or isn't it?). 
+%\end{itemize}
 }
@@
 
-\red{[This section and the next should be merged into a crisp section with the background on DSVerifier, if not included in previous work? 
-Please stick to the introduced notations. Please clarify what the function FWL does, compared to the general approximations introduced above.]}
+%\red{[This section and the next should be merged into a crisp section with the background on DSVerifier, if not included in previous work? 
+%Please stick to the introduced notations. Please clarify what the function FWL does, compared to the general approximations introduced above.]}
+\red{Alessandro, I've made the changes as requested. Please let me know if this is good enough or if I made it too short}
 
@@
 
-Since $G(z)$ is an approximation of $G(s)$ calculated via a discrete z transform using a selected sampling time, we denote the error in the approximation as $\Delta{G}_P$
+\begin{mylemma} \cite{astrom1997computer}
+%
+The pulse transfer function $G(z)$ is a z-domain model that relates the output sampled by a ADC and the digital input provided by ZOH.
+It is equivalent at the sample times ({\it i.e.} $kT$ to the continuous transfer function $G(s)$ driven by ZOH.
+This pulse transfer
+function can be computed as
+%
+\begin{equation}
+\label{eq:pulsetf}
+G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
+\end{equation}
+
+For convenience, we will use only the notation $G(z)$ to represent the pulse transfer function.
+\end{mylemma}
+
+Since $G(z)$ is an approximation of $G(s)$ we denote the error in the approximation for time $t \neq kT$ as $\Delta{G}_P$
 \begin{align}
@@
 \hat{G}(z)&=\frac{(b_{0}+\Delta_p b_{0}) +...+(b_{M_G}+\Delta_p b_{M_G})z^{-M_G}}{(a_{0}+\Delta_p a_{0})+...+(a_{N_G}+\Delta_p a_{N_G})z^{-N_G}} \nonumber \\
-&=G(z,T)+\Delta{G}_P(z,T).
+&=G(z)+\Delta{G}_P(z).
 \end{align}
-Note that $\Delta{G}_P$ is undefined and upperbound by a user defined percentage which relates to the nature of the z transform and the sampling time.
-For simplicity we will use $G(z)$ to represent $G(z,T)$.
-
-Let $\tilde C(z)$ and $\tilde G(z)$ be the same transfer functions represented using a Fixed Point Finite Word Length with integer size $I$ and fractional size $F$.
+Note that $\Delta{G}_P$ is undefined and upperbound by a user defined percentage such that $\hat{G}(z)$ corresponds to the polynomial set of possible values of $G(z, T): \forall T \in \mathbb{R}$
+
+Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented using a Fixed Point Finite Word Length with integer size $I$ and fractional size $F$.
 We shall denote this domain as $\mathbb{R}\langle I,F \rangle$
@@
  $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
-However, since the plant was originally in the real domain,
+However, given a real plant and real controller $\hat{G}(z), \hat{C}(z)$,
 \begin{align}
 \small
+\label{FWL_tf}
+&\exists f (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I,F \rangle : \\
+\label{digital_controller_tf}
+\tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
+&= C(z) =\hat{C}(z) + \Delta{C}(z)\\
 \label{digital_plant_tf}
-&\exists f (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I,F \rangle : \nonumber \\
 \tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_q \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_q \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_q \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_q \hat{a}_{N_G})z^{-N_G}} \nonumber \\
@@
 We may encompass all the uncertainty as $\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_Q(z)$.
-Since this value is nondeterministic, the polynomial set of possible values of $\tilde G(z)$ is denoted by $\mathfrak{G}$.
+Since this value is nondeterministic, the polynomial set of possible values of $\tilde G(z)$ is denoted by $\mathfrak{G}(z)$.
 
@@
 
-\red{[The following description can be made shorter, crisper?]}
-
-The DSVerifier verification flow is illustrated in
-Fig.~\ref{DSVerifier_process}.  Steps $1$ to $5$ are performed by users and
-Steps A to D are automatically performed by DSVerifier, which accepts the
-digital controller transfer functions together with the plant model.  For
-any digital controller, implementation details should be provided ({\it
-e.g.}, number of bits, realization, and sample time).
+%\red{[The following description can be made shorter, crisper?]}
+
+The DSVerifier verification flow is illustrated in Fig.~\ref{DSVerifier_process}.
+Steps $1$ to $5$ are performed by the user/synthesiser and
+Steps A to D are automatically performed by DSVerifier
+%, which accepts the
+%digital controller transfer functions together with the plant model.  For
+%any digital controller, implementation details should be provided ({\it
+%e.g.}, number of bits, realization, and sample time).
 
@@
 
-In Step $1$, the user provides inputs $g_0$ and $\Delta{g}\%$ ({\it i.e.},
-percentage form of $\Delta{g}$), which contain the plant model and the
-interval, respectively.  In Step $2$, a digital controller must be designed
-with any preferred method, where $c_0$ is obtained.  The controller
-numerical representation and realization form are chosen in Steps $3$ and
-$4$, respectively.  In Step $5$, the user finally configures the
-verification parameters ({\it e.g.}, verification time, properties, and BMC
-tool).  After that, DSVerifier verification engine performs an (automatic)
-verification of the desired property $\phi$ ({\it i.e.}, stability).  The
-user steps described in Steps $1$--$5$ result in an ANSI-C code that should
-be used as an input for DSVerifier.
-
-In Step A, DSVerifier constructs a non-deterministic model to represent the
-plant family $\mathfrak{G}$ using $g_0$ and $\Delta{g}\%$, which are
-provided in Step $1$.  DSVerifier then formulates $\mathit{FWL}[\cdot]$ in
-Step B using implementation details provided from Steps $2$ and $3$, and
-then computes $\mathit{FWL}[c_0]$ in Step C.  Thus, DSVerifier builds an
-intermediate ANSI-C code for the digital system implementation, which is
-used as input for the model-checker, as pointed in Step D.
-
-This intermediate ANSI-C code model has three main modules: digital
-controller code to be embedded into the microprocessor; plant model code,
-which simulates the plant model dynamics considering uncertainties; and
-``assert'' and ``assume'' statements, which control the verification flow. 
-For the digital controller code, transfer functions coefficients are
-quantized and deterministic, and all operations use fixed-point arithmetic. 
-\textcolor{red}{In the plant model code, transfer function coefficients are
-not quantized, but represented with maximum precision based on float
-data-type variables}; they are treated as non-deterministic variables to
-support model uncertainties.  The directive ``assume'' bounds
-non-deterministic variables, {\it i.e.}, inputs and plant uncertain
-coefficients.
-
-Finally in the Step D, the translation of ANSI-C code into SAT/SMT formulae
-is done by a back-end model-checking tool ({\it e.g.},
-CBMC~\cite{ClarkeKL04} or ESBMC~\cite{CordeiroFM12}).  Here, DSVerifier
-symbolically checks a given property $\phi$ with respect to closed-loop
-systems, which are composed by $FWL[c_0]$ and every $g$ in $\mathfrak{G}$. 
-If any property violation is found, then DSVerifier reports a
+%In Step $1$, the user provides inputs $G(z)$ and $\Delta{G}(z)$
+%%$\%$ ({\it i.e.}, $\Delta{G}(z)$ as a percentage of $G(z)$)
+%, which contain the plant model and the
+%interval, respectively.  In Step $2$, a digital controller must be designed
+%with any preferred method, where $C(z)$ is obtained.  The controller
+%numerical representation and realization form are chosen in Steps $3$ and
+%$4$, respectively.  In Step $5$, the user finally configures the
+%verification parameters ({\it e.g.}, verification time, properties, and BMC
+%tool).  After that, DSVerifier verification engine performs an (automatic)
+%verification of the desired property $\phi$ ({\it i.e.}, stability).  The
+%user steps described in Steps $1$--$5$ result in an ANSI-C code that should
+%be used as an input for DSVerifier.
+
+Given a model $(\hat{C}(z),\hat{G}(z), \mathbb{R}\langle I,F \rangle)$, provided
+in an ANSI-C code input file (Steps 1-5),
+DSVerifier constructs a non-deterministic model to represent the plant family
+$\mathfrak{G}(z)$ (Step A), and a transfer function $f$ [eq. \ref{FWL_tf}]
+(step B) to calulate the implementation $f(\hat{C}(z)) \rightarrow \tilde C(z)$
+of the controller (step C).
+Finally DSVerifier builds an intermediate ANSI-C code for the digital system
+implementation, which is used as input for the model-checker (Step D).
+
+This intermediate ANSI-C code model $(\tilde C(z),\mathfrak{G}(z),\phi)$
+containing a specification $\phi$ for the verification properties ({\it i.e.} stability)
+is translated into SAT/SMT formulae by a back-end model-checking tool ({\it e.g.},
+CBMC~\cite{ClarkeKL04} or ESBMC~\cite{CordeiroFM12}).
+If any property violation is found, DSVerifier reports a
 counterexample, which contains system inputs or parametric deviations
-$\Delta{g}\%$ that lead the system to a failure.  A successful verification
+$\Delta{G}$ that lead the system to a failure.  A successful verification
 result is reported if the system is safe with respect to $\phi$.  In
 particular, the stability verification is complete and sound, since it does
-not depend on system outputs and inputs.
+not depend on system inputs and outputs.
+In the case of stability, the specification $\phi$ consists in a number of assumptions
+on the polynomial coefficients following Jury's Criteria, as well as the restrictions
+set in the representation of these coefficients by the function $f$ [eq. \ref{FWL_tf}].
+
+%In Step A, DSVerifier constructs a non-deterministic model to represent the
+%plant family $\mathfrak{G}$ using $g_0$ and $\Delta{g}\%$, which are
+%provided in Step $1$.  DSVerifier then formulates $\mathit{FWL}[\cdot]$ in
+%Step B using implementation details provided from Steps $2$ and $3$, and
+%then computes $\mathit{FWL}[c_0]$ in Step C.  Thus, DSVerifier builds an
+%intermediate ANSI-C code for the digital system implementation, which is
+%used as input for the model-checker, as pointed in Step D.
+
+%This intermediate ANSI-C code model has three main modules: digital
+%controller code to be embedded into the microprocessor; plant model code,
+%which simulates the plant model dynamics considering uncertainties; and
+%``assert'' and ``assume'' statements, which control the verification flow. 
+%For the digital controller code, transfer functions coefficients are
+%quantized and deterministic, and all operations use fixed-point arithmetic. 
+%\textcolor{red}{In the plant model code, transfer function coefficients are
+%not quantized, but represented with maximum precision based on float
+%data-type variables}; they are treated as non-deterministic variables to
+%support model uncertainties.  The directive ``assume'' bounds
+%non-deterministic variables, {\it i.e.}, inputs and plant uncertain
+%coefficients.
+%
+%The translation of ANSI-C code into SAT/SMT formulae
+%is done by a back-end model-checking tool ({\it e.g.},
+%CBMC~\cite{ClarkeKL04} or ESBMC~\cite{CordeiroFM12}).  Here, DSVerifier
+%symbolically checks a given property $\phi$ with respect to closed-loop
+%systems, which are composed by $f(c_i)$ and every $G$ in $\mathfrak{G}$. 
+%If any property violation is found, then DSVerifier reports a
+%counterexample, which contains system inputs or parametric deviations
+%$\Delta{G}$ that lead the system to a failure.  A successful verification
+%result is reported if the system is safe with respect to $\phi$.  In
+%particular, the stability verification is complete and sound, since it does
+%not depend on system outputs and inputs.
 
@@
         label=\textbf{Controller}] (cz) {{\sc C(z)}};
-   \node[draw=none] (u) at ([xshift=1cm,yshift=.1cm]cz)  {u};
+   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$\tilde u(z)$};
 
@@
         label=\textbf{Plant}] (gs) {{\sc G(s)}};
+   \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]gs)  {$u(s)$};
    \& \coordinate (aux1);
@@
 The DAC interpolator is an ideal ZOH; it takes the discrete value of control
-signal $u_d(k)$ at instant $k$ and produces a rectangular pulse of height
+signal $\tilde u(k)$ at instant $k$ and produces a rectangular pulse of height
 $u(k)$ and width equal to the sample time $T$.
@@
 where $q$ is the step size of quantizer. \blue{[can you add a comment on this assumption? Why the factor 12?]}
-
-\begin{mylemma} \cite{astrom1997computer}
-%
-The pulse transfer function $G(z)$ is a z-domain model that relates the output sampled by a ADC and the digital input provided by ZOH.
-It is equivalent at the sample times ({\it i.e.} $kT$ to the continuous transfer function $G(s)$ driven by ZOH.
-This pulse transfer
-function can be computed as
-%
-\begin{equation}
-\label{eq:pulsetf}
-G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
-\end{equation}
-
-For convenience, we will use only the notation $G(z)$ for represent the pulse transfer function.
-\end{mylemma}
-%\red{[Here the dependence on the sampling time T needs to appear somewhere.]} 
-%\green{It appears,  $kT$ is the time $t$ used after the inverse Laplace transform}
-%\red{[ok, then let's call it $G(z,T)$ as I suggested earlier.]}
 

### 2016-10-08 paper/paper.tex
review Robust synthesis of Linear Systems

--- 2016-10-08 paper/paper.tex
@@
 more recent Linear Quadratic Regulator (LQR)~\cite{bemporad2002explicit}
-have been used in several papers with increasing degrees of succes to ensure
+have been used in several studies with increasing degrees of succes to ensure
 stability.  The latter approach highlights the importance of conserving
-energy during the control process, which results amongst other things in
-lower running costs.  Since real systems are subject to tolerance and noise
-as well as the need for economy, more recent works focus on the problems of
+energy during the control process, which results in lower running costs.  
+Since real systems are subject to tolerance and noise
+as well as the need for economy, more recent studies focus on the problems of
 achieving robust stability with minimum
@@
 the ability to produce sound or stable results because they disregard the
-effects of quantization and rounding.  Modern papers on
+effects of quantization and rounding. Recent papers on
 implementations/synthesis of LTI digital

### 2016-10-08 paper/paper.tex
review Formal Verification of Linear Digital Controllers

@@
 
-Researchers in formal verification methods of control systems have studied
+Researchers in formal verification of control systems have studied
 various effects of discretising the dynamics, including delayed
 response~\cite{Duggirala2015}, and Finite Word Length (FWL) constraints with
-the objective to either verify (eg.  \cite{daes20161}) or optimise
-(eg.~\cite{oudjida2014design}) implementations.  There are in fact two
+the goal to either verify ({\it e.g.},  \cite{daes20161}) or optimise
+({\it e.g.},~\cite{oudjida2014design}) implementations.  There are in fact two
 different problems arising from FWL effects.  The first corresponds to the
@@
 directly model the digital controller so that the selected parameters are
-stable by design.  Most papers following this line of verification focus on
+stable by design.  Most studies following this verification research field focus on
 finding a correct implementation of a known desired controller, looking for
-optimal parameter representations using FWL but ignoring the effects of
+optimal parameter representations using FWL, but ignoring the effects of
 rounding errors due to issues of mathematical tractability.  The analyses
@@
 stability, the latter uses Lyapunov-based quadratic invariants.  In both
-cases the SDP solver uses floating point arithmetic and soundness is checked
+cases, the SDP solver uses floating-point arithmetic and soundness is checked
 by upper bounding the error.

### 2016-10-08 paper/paper.tex
review Robust Synthesis of FWL Digital Controllers

@@
 
-To the authors' knowledge, there is no existing work on the automatic
-synthesis of fixed point digital controllers considering FWL effects.  Parameter
-synthesis tools such as~\cite{cimatti2013parameter} use bounded model
-checking and fixed point computations to find parameters based on user
+Given the current knowledge in control system's synthesis, there is no other 
+existing study on the automatic synthesis of fixed-point digital controllers 
+considering FWL effects.  Parameter synthesis tools such as~\cite{cimatti2013parameter} 
+use bounded model checking and fixed-point computations to find parameters based on user
 defined specifications, but they often operate in the continuous domain and
@@
 evaluating robustness.  Other tools such as~\cite{economakos2016automated}
-are directly aimed at robust stability problems but fail to explore the
+are directly aimed at robust stability problems, but they fail to explore the
 effects of FWL in their implementation.  In order to provide a correct by
-design controller, \cite{alur2016compositional} requires a user-defined
+design digital controller, \cite{alur2016compositional} requires a user-defined
 finite state abstraction to synthesise a digital controller based on high
@@
 intervention.  A different solution that looks at the other end of the scale
-is an approach that synthesises word lengths for know problems as developed
-in \cite{jha2013swati}, however this provides neither an optimal word
+is an approach that synthesises word lengths for known problems as developed
+in \cite{jha2013swati}; however, this provides neither an optimal word
 synthesis nor a comprehensive solution for the problem.  It is from this

### 2016-10-08 paper/paper.tex
review CEGIS
review Verifying Closed-loop Control Systems

@@
 model of the plant must be discretized to obtain the discrete equivalent
-coefficients $b$ and $a$~\cite{Astrom08} via ZOH discretization %\red{[pls say how]}
-. Although there are several discretization methods available in the literature~\cite{Franklin15}, the
+coefficients $b$ and $a$~\cite{Astrom08} via ZOH discretization.
+Although there are several discretization methods available in the literature~\cite{Franklin15}, the
 zero-order hold (ZOH) discretization is more suitable for representing the
 sampling and holding processes that are typically employed by hybrid
-systems~\cite{istepanian2012digital}, i.e. the ZOH discretization models the exact effect of sampling and DAC interpolation over the plant.
+systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretization models 
+the exact effect of sampling and DAC interpolation over the plant.
 
@@
 The pulse transfer function $G(z)$ is a z-domain model that relates the output sampled by a ADC and the digital input provided by ZOH.
-It is equivalent at the sample times ({\it i.e.} $kT$ to the continuous transfer function $G(s)$ driven by ZOH.
+It is equivalent at the sample times ({\it i.e.}, $kT$ to the continuous transfer function $G(s)$ driven by ZOH).
 This pulse transfer
@@
 In recent years the development of program synthesis has found many ways to
-obtain correct by design programs from high level specifiactions.  One such
+obtain correct by design programs from high-level specifications.  One such
 approach~\cite{itzhaky2010simple} looks to inductively synthesise invariants

### 2016-10-08 paper/paper.tex
review DSVerifier Verification Flow

@@
 
-The DSVerifier verification flow is illustrated in Fig.~\ref{DSVerifier_process}.
+The DSVerifier verification flow is illustrated in Fig.~\ref{DSVerifier_process};
+a detailed description of DSVerifier tool can be found in~\cite{IsmailBCFF15}.
 Steps $1$ to $5$ are performed by the user/synthesiser and
-Steps A to D are automatically performed by DSVerifier
+Steps A to D are automatically performed by DSVerifier.
 %, which accepts the
@@
 This intermediate ANSI-C code model $(\tilde C(z),\mathfrak{G}(z),\phi)$
-containing a specification $\phi$ for the verification properties ({\it i.e.} stability)
+containing a specification $\phi$ for the verification properties ({\it i.e.}, robust stability)
 is translated into SAT/SMT formulae by a back-end model-checking tool ({\it e.g.},
 CBMC~\cite{ClarkeKL04} or ESBMC~\cite{CordeiroFM12}).
-If any property violation is found, DSVerifier reports a
+If any property violation is found, then DSVerifier reports a
 counterexample, which contains system inputs or parametric deviations
@@
 In the case of stability, the specification $\phi$ consists in a number of assumptions
-on the polynomial coefficients following Jury's Criteria, as well as the restrictions
-set in the representation of these coefficients by the function $f$ [eq. \ref{FWL_tf}].
+on the polynomial coefficients, following Jury's Criteria, as well as the restrictions
+set in the representation of these coefficients by the function $f$ (Eq. \ref{FWL_tf}).
 

### 2016-10-08 paper/paper.tex
describe the objectives of the experimental evaluation

@@
 
-This section is split into three parts.
-Section~\ref{experimental-objectives} describes the experimental objectives, while Section~\ref{experimental-setup} discusses the experimental setup and the employed benchmarks.
-Section~\ref{experimental-results} describes the experimental results related to the application of CEGIS to standard control system benchmarks extracted from the literature.
-
-%---------------------------------
-\subsection{Objectives}
-\label{experimental-objectives}
-%---------------------------------
+This section is split into three parts. Section~\ref{experimental-setup} discusses 
+the experimental setup and the employed benchmarks, while Section~\ref{experimental-objectives} 
+describes the experimental objectives. Section~\ref{experimental-results} describes the experimental 
+results related to the application of CEGIS to the standard closed-loop control system benchmarks 
+described in Section~\ref{experimental-setup}.
 
@@
 clock time in seconds as measured by the UNIX time command.
+
+%---------------------------------
+\subsection{Objectives}
+\label{experimental-objectives}
+%---------------------------------
+
+Using the closed-loop control system benchmarks described in Section~\ref{experimental-setup}, 
+the experimental evaluation of the present approach aims to answer two research questions:
+%
+\begin{enumerate}
+	\item RQ1 \textbf{(sanity check)} which results does our CEGIS approach to FWL controller synthesis 
+	obtain upon synthesizing/verifying benchmarks that compose the specified suite?
+  \item RQ2 \textbf{(performance)} does the CEGIS approach provide a feasible solution in reasonable time
+	considering robust stability of FWL digital controllers?	
+\end{enumerate}
 

### 2016-10-08 paper/paper.tex
nudged the title
Review of quantization error chapter

@@
 \title{
-Sound and Automated Synthesis of Digital Controllers for Physical Plants 
+Sound Automated Synthesis of Digital Controllers
 %Counterexample-guided Synthesis of Closed-loop Digital Control Systems
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Modelling Errors}
-
-In this section, we show how to embed discretisation errors on the plant model, as follows: 
-%$\hat{G}(z)$ is split into two terms:
-%
-\begin{equation}
-\label{eq:uncertainplant}
-%\hat{G}(z)=G(z)+\Delta{G(z)},
-\tilde G(z) = \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z),   
-\end{equation}
-where $G(z,T)$ is the time discretisation of the nominal physical plant $G(s)$, 
-$\Delta{G_{Q}(z)}$ represents the quantisation uncertainty model, 
-and $\Delta{G_{P}(z)}$ describes the parametric uncertainty model.
+%\section{Modelling Errors}
+
+%In this section, we show how to embed discretisation errors on the plant model, as follows: 
+%%$\hat{G}(z)$ is split into two terms:
+%%
+%\begin{equation}
+%\label{eq:uncertainplant}
+%%\hat{G}(z)=G(z)+\Delta{G(z)},
+%\tilde G(z) = \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z),   
+%\end{equation}
+%where $G(z,T)$ is the time discretisation of the nominal physical plant $G(s)$, 
+%$\Delta{G_{Q}(z)}$ represents the quantisation uncertainty model, 
+%and $\Delta{G_{P}(z)}$ describes the parametric uncertainty model.
 
@@
 
-\subsection{An Uncertainty Model for the Quantization Error} 
+\section{An Uncertainty Model for the Quantization Error} 
 \label{sec:uncertainty-model-quantization-error}
@@
 
-Consider the closed-loop sampled system in Figure~\ref{fig:sampledsystem} \red{[requires updating]},
+Consider the closed-loop sampled system in Figure~\ref{fig:sampledsystem},
 where $C(z)$ is the digital controller model, whose control output signal is
@@
 
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.5cm, column sep=.5cm] {
-    \node[draw=none] (r) {r};
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
+    \node[draw=none] (r) {r(z)};
 %   \& \coordinate (aux0);
    \& \node[circle,add={-}{+}{}{}] (circle) {};
-   \& complexnode/.pic={ 
-     \node[rectangle,draw,
-	minimum width=4cm,
-	minimum height=1.6cm,
-	label=\textbf{ADC},] (adc) {};
-   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
-   \coordinate (switch1) at ([xshift=-1cm]adc.center);
-   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
-   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
-     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
-   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu1$};
+   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$\tilde e(z)$};
    \& \node[rectangle,draw,
@@
    \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]gs)  {$u(s)$};
+   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$y(s)$};
+   \& complexnode/.pic={ 
+     \node[rectangle,draw,
+	minimum width=4cm,
+	minimum height=1.6cm,
+	label=\textbf{ADC},] (adc) {};
+   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
+   \coordinate (switch1) at ([xshift=-1cm]adc.center);
+   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
+   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
+     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
+   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu1$};
    \& \coordinate (aux1);
-   \& \node[draw=none] (y) {y};\\
+   \& \node[draw=none] (yz) {$\tilde y(z)$};\\
    \& \coordinate (aux3); 
@@
   \path[->] (r) edge (circle.west);
-  \path[->] (aux1) edge (y);
+  \path[->] (aux1) edge (yz);
   \path  
-   (circle.east) edge (switch1)
-   (switch2) edge (q1.west)
-   (q1.east) edge (cz.west)
+   (circle.east) edge (cz)
    (cz.east) edge (q2.west)
@@
    (zoh.east) edge (gs.west)
-   (gs.east) edge (aux1.west)
+   (switch2) edge (q1.west)
+   (q1.east) edge (aux1.west)
+   (gs.east) edge (switch1.west)
    (aux1.south) edge (aux2.north)
@@
 }
- \caption{Sampled System. \label{fig:sampledsystem} \red{[Please update this figure: reference enters downstream of control block. Clarify signals over lines in plot.]}}
+ \caption{Sampled System. \label{fig:sampledsystem}}
 \end{figure}
@@
 
-First, some assumptions have to be established to obtain a model for $\Delta{G_{Q}(z)}$. 
-\blue{[Here we need to be careful: we first argue that quantisation (spelled with an s, so that ER II is happy) effects can be represented as an additive noise (great), which however is a stochastic signal.
-But we handle the noise deterministically.
-How so?
-Where is the catch?
-]}
+First, some assumptions have to be established to obtain a model for the quantization effects (seen as noise) on the closed loop system. 
 %
@@
 The quantization noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
-$Q2$) are white noises.
-%
-\end{myassumption}
-
-\begin{myassumption}
-The quantization noises $\nu_{1}$ and $\nu_{2}$ are uncorrelated with each other.
+$Q2$) are energy bounded uncorrelated white noises.
+
+In \cite{widrow1956}, Widrow models the quantization noise as a gaussian model in which
+the second moment (variance) of the probability density function (pdf) of the quantization
+noise is given by
+%
+\begin{equation}
+\label{eq:variancelemma}
+\sigma_{Q}^{2}=\frac{q^{2}}{12},
+\end{equation}
+where $q$ is the step size of quantizer, thus supporting this assumption.
 \end{myassumption}
@@
 $u(k)$ and width equal to the sample time $T$.
-\red{[Right: so under this assumption, we really only focus on the quantisation effects introduced by the ADC, correct?
-Let us not mix up the role and the influence of the two blocks.]}
 %
@@
 
-Given those assumptions, the present approach is further based on the following lemmas. 
-\red{[So we have introduced two quantisation errors, properly indexed. Next we discuss a non-indexed entity - pls clarify or comment.]}
-%
-\begin{mylemma}
-%
-\cite{widrow1956} The second moment (variance) of the probability probability density function of quantization
-noise is given by %\textcolor{red}{expand the acronym PDF}
-%
-\begin{equation}
-\label{eq:variancelemma}
-\sigma_{Q}^{2}=\frac{q^{2}}{12},
-\end{equation}
-\end{mylemma}
-where $q$ is the step size of quantizer. \blue{[can you add a comment on this assumption? Why the factor 12?]}
-
-\begin{myprop}
-Considering the quantisation noise $\nu(k)$ as an output error in the
-discrete plant model, 
-%{\it i.e.}, it does not affect the plant dynamics, but its output samples, 
-$\Delta{G_{Q}(z)}$ can be obtained from
-%
-\begin{equation}
-\label{eq:quantization_tf}
-\Delta{G_{Q}(z)}=\frac{\nu(z)}{U(z)},
-\end{equation}
-where $\nu(z)$ is the z-transform of the random process $\nu(k)$,
-which can be calculated through the power spectral density of
-$\nu(k)$~\cite{poularikas2000transforms}.  
-Thus, the $\Delta{G_{Q}(z)}$ can expressed as
-%
-\begin{equation}
-\label{eq:deltag_var}
-\Delta{G_{Q}(z)}=\frac{\sigma_{Q}^{2}}{U(z)},
-\end{equation}
-where $\sigma_{Q}^{2}$ is the variance of the quantization noise and
-$U(z)$ is the z-transform of control signal ({\it i.e.}, the z-transform of
-the signal from the digital controller), which is provided to the plant by
-means of ZOH.
-\end{myprop}
-
-%
-\begin{proof}
-%
-Suppose that the plant discrete model in Figure~\ref{fig:sampledsystem} can
-be represented by the following pulse transfer function (without
-quantization noise effect):
-%
-\begin{equation}
-\label{eq:tfwithout}
-G(z)=\frac{Y(z)}{U(z)}=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M}z^{-M}}{1+a_{1}z^{-1}+a_{2}z^{-2}+\cdots+a_{N}z^{-N}},
-\end{equation}
-%
-\noindent where $Y(z)$ is the z-transform of the plant output signal without
-noise $y(k)$, $U(z)$ is the z-transform of the control signal, which is
-provided to the plant, $A(z)$ and $B(z)$ are the plant pulse transfer
-function numerator and denominator, respectively.
-
-Considering the quantization noise $\nu(k)$ as an output error in the
-discrete plant model, an additive noise in the plant output $y(k)$ resulting
-in the noisy output $\hat{y}(k)$ can be represented as
-%
-\begin{equation}
-\hat{y}(k)=y(k)+\nu(k).
-\end{equation}
-
-Note that the model in Eq.~\eqref{eq:tfwithout} is equivalent to the
-following difference equation:
-%
-\begin{equation}
-\begin{split}
-y(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
-+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M),
-\end{split}
-\end{equation}
-
-\noindent and consequently $\hat{y}(k)$ can be represented by the following
-difference equation:
-%
-\begin{equation}
-\label{eq:differencewithnoise}
-\begin{split}
-\hat{y}(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
-+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M)+\nu(k).
-\end{split}
-\end{equation}
-
-The z-transform of Eq.~\eqref{eq:differencewithnoise} is
-%
-\begin{equation}
-\begin{split}
-\hat{Y}(z)=(-a_{1}z^{-1}-a_{2}z^{-2}-\cdots-a_{N}z^{-N})Y(z)\\
-+(b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M}z^{-M})U(z)+\nu(z),
-\end{split}
-\end{equation}
-dividing both sides by $U(z)$, it is equivalent to:
-\begin{equation}
-\frac{\hat{Y}(z)}{U(z)}=\hat{G}(z)=[1-A(z)]G(z)+U(z)B(z)+\frac{\nu(z)}{U(z)}.
-\end{equation}
-
-Considering $\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}$ and Eq.~\eqref{eq:tfwithout},
-the intended expression can be obtained as
-%
-\begin{equation}
-\Delta{G_{Q}(z)}=\frac{\nu(z)}{U(z)} 
-\end{equation}
-\end{proof}
-
-Eq.~\eqref{eq:deltag_var} indicates that the modelling of the quantization noise
-effect on the plant transfer function demands an estimation of the variance
-of quantization noise $\sigma_{Q}^{2}$.  To obtain such estimation, the
-methodology presented by~\cite{widrow2008quantization}
-is used.  The authors provide an algorithm for computing the mean square of
-the output noise due to $Q1$ and $Q2$.  Considering that each quantizer
-contribution can be represented by a white noise with zero mean
-(Assumption~\ref{whitenoise}), the mean square can be considered as the
-variance of noise ($\sigma_{Q}^{2}$), which can be calculated as
-%
-\begin{equation}
-\sigma_{Q}^{2}=\frac{\lambda_{1}^{2}\cdot \sum {h_{Q1}^{2}} \cdot q_{1}+\lambda_{2}^{2}\cdot \sum {h_{Q2}^{2}} \cdot q_{2}}{12},
-\end{equation}
-%
-\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factors, {\it i.e.} constant gains usually employed before the ADC and after the DAC in order to avoid the overload of converters  %\red{[define scale factors]}
-for the quantization $Q1$ and $Q2$, respectively; $q_{1}$ and $q_{2}$ are the quantization step for $Q1$ and $Q2$, respectively, and $\sum {h_{Q1}^{2}}$ and $\sum
-{h_{Q2}^{2}}$ are the squares sums of the impulse response obtained by means
-of a transfer function from $Q1$ and $Q2$ to the plant output, respectively.
-
-The transfer functions $H_{Q1}(z)$ and $H_{Q2}(z)$, from which the squares
-sums of the impulse response are needed, can be obtained through the
-analysis of the system in Figure~\ref{fig:sampledsystem}.  Considering that
+%\begin{myprop}
+%Considering the quantisation noise $\nu(k)$ as an output error in the
+%discrete plant model, 
+%%{\it i.e.}, it does not affect the plant dynamics, but its output samples, 
+%$\Delta{G_{Q}(z)}$ can be obtained from
+%%
+%\begin{equation}
+%\label{eq:quantization_tf}
+%\Delta{G_{Q}(z)}=\frac{\nu(z)}{U(z)},
+%\end{equation}
+%where $\nu(z)$ is the z-transform of the random process $\nu(k)$,
+%which can be calculated through the power spectral density of
+%$\nu(k)$~\cite{poularikas2000transforms}.  
+%Thus, the $\Delta{G_{Q}(z)}$ can expressed as
+%%
+%\begin{equation}
+%\label{eq:deltag_var}
+%\Delta{G_{Q}(z)}=\frac{\sigma_{Q}^{2}}{U(z)},
+%\end{equation}
+%where $\sigma_{Q}^{2}$ is the variance of the quantization noise and
+%$U(z)$ is the z-transform of control signal ({\it i.e.}, the z-transform of
+%the signal from the digital controller), which is provided to the plant by
+%means of ZOH.
+%\end{myprop}
+%
+%%
+%\begin{proof}
+%%
+%Suppose that the plant discrete model in Figure~\ref{fig:sampledsystem} can
+%be represented by the following pulse transfer function (without
+%quantization noise effect):
+%%
+%\begin{equation}
+%\label{eq:tfwithout}
+%G(z)=\frac{Y(z)}{U(z)}=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M}z^{-M}}{1+a_{1}z^{-1}+a_{2}z^{-2}+\cdots+a_{N}z^{-N}},
+%\end{equation}
+%%
+%\noindent where $Y(z)$ is the z-transform of the plant output signal without
+%noise $y(k)$, $U(z)$ is the z-transform of the control signal, which is
+%provided to the plant, $A(z)$ and $B(z)$ are the plant pulse transfer
+%function numerator and denominator, respectively.
+%
+%Considering the quantization noise $\nu(k)$ as an output error in the
+%discrete plant model, an additive noise in the plant output $y(k)$ resulting
+%in the noisy output $\hat{y}(k)$ can be represented as
+%%
+%\begin{equation}
+%\hat{y}(k)=y(k)+\nu(k).
+%\end{equation}
+%
+%Note that the model in Eq.~\eqref{eq:tfwithout} is equivalent to the
+%following difference equation:
+%%
+%\begin{equation}
+%\begin{split}
+%y(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
+%+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M),
+%\end{split}
+%\end{equation}
+%
+%\noindent and consequently $\hat{y}(k)$ can be represented by the following
+%difference equation:
+%%
+%\begin{equation}
+%\label{eq:differencewithnoise}
+%\begin{split}
+%\hat{y}(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
+%+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M)+\nu(k).
+%\end{split}
+%\end{equation}
+%
+%The z-transform of Eq.~\eqref{eq:differencewithnoise} is
+%%
+%\begin{equation}
+%\begin{split}
+%\hat{Y}(z)=(-a_{1}z^{-1}-a_{2}z^{-2}-\cdots-a_{N}z^{-N})Y(z)\\
+%+(b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M}z^{-M})U(z)+\nu(z),
+%\end{split}
+%\end{equation}
+%dividing both sides by $U(z)$, it is equivalent to:
+%\begin{equation}
+%\frac{\hat{Y}(z)}{U(z)}=\hat{G}(z)=[1-A(z)]G(z)+U(z)B(z)+\frac{\nu(z)}{U(z)}.
+%\end{equation}
+%
+%Considering $\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}$ and Eq.~\eqref{eq:tfwithout},
+%the intended expression can be obtained as
+%%
+%\begin{equation}
+%\Delta{G_{Q}(z)}=\frac{\nu(z)}{U(z)} 
+%\end{equation}
+%\end{proof}
+
+%Eq.~\eqref{eq:deltag_var} indicates that the modelling of the quantization noise
+%effect on the plant transfer function demands an estimation of the variance
+%of quantization noise $\sigma_{Q}^{2}$.  To obtain such estimation, the
+%methodology presented by~\cite{widrow2008quantization}
+%is used.  The authors provide an algorithm for computing the mean square of
+%the output noise due to $Q1$ and $Q2$.  Considering that each quantizer
+%contribution can be represented by a white noise with zero mean
+%(Assumption~\ref{whitenoise}), the mean square can be considered as the
+%variance of noise ($\sigma_{Q}^{2}$), which can be calculated as
+%%
+%\begin{equation}
+%\sigma_{Q}^{2}=\frac{\lambda_{1}^{2}\cdot \sum {h_{Q1}^{2}} \cdot q_{1}+\lambda_{2}^{2}\cdot \sum {h_{Q2}^{2}} \cdot q_{2}}{12},
+%\end{equation}
+%%
+%\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factors, {\it i.e.} constant gains usually employed before the ADC and after the DAC in order to avoid the overload of converters  %\red{[define scale factors]}
+%for the quantization $Q1$ and $Q2$, respectively; $q_{1}$ and $q_{2}$ are the quantization step for $Q1$ and $Q2$, respectively, and $\sum {h_{Q1}^{2}}$ and $\sum
+%{h_{Q2}^{2}}$ are the squares sums of the impulse response obtained by means
+%of a transfer function from $Q1$ and $Q2$ to the plant output, respectively.
+%
+%The transfer functions $H_{Q1}(z)$ and $H_{Q2}(z)$, from which the squares
+%sums of the impulse response are needed, can be obtained through the
+%analysis of the system in Figure~\ref{fig:sampledsystem}. 
+Considering that
 the quantizer $Q1$ is the source of a white noise with zero mean $\nu_{1}$
@@
 \label{eq:outputfunctions}
-\resizebox{0.48\textwidth}{!}{
-$\hat{Y}(z)=\frac{C(z)G(z)}{1+C(z)G(z)}R(z)+\frac{C(z)G(z)}{1+C(z)G(z)}\nu_{1}(z) \\
-+\frac{G(z)}{1+C(z)G(z)}\nu_{2}(z).$
-}
-\end{equation}
-
-Thus, $H_{Q1}(z)$ and $H_{Q2}(z)$ can be extracted from Eq.~\eqref{eq:outputfunctions}:
-\begin{equation}
-H_{Q1}(z)=\frac{C(z)G(z)}{1+C(z)G(z)},
-\end{equation}
-and
-\begin{equation}
-H_{Q2}(z)=\frac{G(z)}{1+C(z)G(z)}.
-\end{equation}
-
-These equations are sufficient for computing $\sigma_{Q}^{2}$.  However,
-there is still a gap for a complete model for $\Delta{G_{Q}(z)}$ in
-Eq.~\eqref{eq:deltag_var}, {\it i.e.}, the z-transform of control action
-$U(z)$.  This indicates that the quantization noise effect on a discrete
-plant model mainly depends on three main factors:
-%
-\begin{itemize}
-%
-\item \textbf{Sample time:} the sample time effect is reflected over pulse transfer function that covers the effects of DAC ant its interpolator (ZOH) \red{[clarify/revise based on the comments made above.]};
-%
-\item \textbf{ADC and DAC step:} \red{[again, do we need both?]} these are the main component of quantization noise power, but an $8$-bits converter already reduces the effect of quantization noises in the output for negligible values.
-%
-\item \textbf{Signal-to-noise ratio (SNR): } the dependence on the value of $U(z)$ \red{[notice that now we have reduced the problem to depend on the effect of the reference signal transform R(z) - pls revise.]} shows the importance of the SNR for handling quantization noise; for a high SNR of the digital controller, the quantization effect is negligible.
+\hat{Y}(z)=H_{1}(z)\left(R(z)+\nu_{1}(z)\right)+H_{2}(z)\nu_{2}(z)
+\end{equation}
+$$H_{1}(z)=\frac{C(z)G(z)}{1+C(z)G(z)}$$
+$$H_{2}(z)=\frac{G(z)}{1+C(z)G(z)}$$
+
+In the case of stability properties we need to verify the stability of both $H_{1}(z)$ and $H_{2}(z)$ to validate the stability of the whole system.
+%These equations are sufficient for computing $\sigma_{Q}^{2}$.  However,
+%there is still a gap for a complete model for $\Delta{G_{Q}(z)}$ in
+%Eq.~\eqref{eq:deltag_var}, {\it i.e.}, the z-transform of control action
+%$U(z)$.  This indicates that the quantization noise effect on a discrete
+%plant model mainly depends on three main factors:
+%%
+%\begin{itemize}
+%%
+%\item \textbf{Sample time:} the sample time effect is reflected over pulse transfer function that covers the effects of DAC ant its interpolator (ZOH) \red{[clarify/revise based on the comments made above.]};
+%%
+%\item \textbf{ADC and DAC step:} \red{[again, do we need both?]} these are the main component of quantization noise power, but an $8$-bits converter already reduces the effect of quantization noises in the output for negligible values.
+%%
+%\item \textbf{Signal-to-noise ratio (SNR): } the dependence on the value of $U(z)$ \red{[notice that now we have reduced the problem to depend on the effect of the reference signal transform R(z) - pls revise.]} shows the importance of the SNR for handling quantization noise; for a high SNR of the digital controller, the quantization effect is negligible.
 This happens during the transient of the system, when high control actions are employed.
@@
 A digital controller with integral action might be sufficient for eliminating such influence at steady state.
-%
-\end{itemize}
-
-An alternative expression for $\Delta{G_{Q}(z)}$ can be obtained from
-Eq.~\eqref{eq:deltag_var}, transforming it into a function of the reference
-$R(z)$.  Once $U(z)$ is the control signal obtained via digital controller
-$C(z)$ and error signal, {\it i.e.},
-%
-\begin{equation}
-U(z)=C(z)\cdot[R(z)-Y(z)],
-\end{equation}
-
-\noindent where $Y(z)$ is the first term of Eq.~\eqref{eq:outputfunctions}, thus:
-\begin{equation}
-\label{eq:controlsignal}
-\resizebox{0.48\textwidth}{!}{
-$U(z)=C(z)\cdot \left[R(z)-\frac{C(z)G(z)}{1+C(z)G(z)}R(z)\right]=\frac{C(z)}{1+C(z)G(z)}R(z).$
-}
-\end{equation}
-
-Substituting Eq.~\eqref{eq:controlsignal} in Eq.~\eqref{eq:deltag_var}, a
-model for $\Delta{G_{Q}(z)}$ depending on $R(z)$ can be obtained:
-%
-\begin{equation}
-\Delta{G_{Q}(z)}=\sigma^{2}_{Q}\cdot \frac{1+C(z)G(z)}{C(z)} \cdot \frac{1}{R(z)},
-\end{equation}
-
-\noindent where $R(z)$ can be considered as a step signal (for stabilization
-purpose) with height equal to $r$, which can be rewritten as
-%
-\begin{equation}
-\Delta{G_{Q}(z)}=\frac{\sigma^{2}_{Q}}{r}\cdot \frac{1+C(z)G(z)}{C(z)} \cdot \frac{z-1}{z}.
-\end{equation}
-
-A more precise description of $\Delta{G_{Q}(z)}$ can be obtained
-considering FWL \red{[clarify what you mean with FWL, introduce FWL function explicitly and precisely]} effects on digital controller coefficients, as described in
-Bessa {\it et al.}~\cite{Bessa16}, {\it i.e.}, using $FWL[C(z)]$ instead of
-the nominal $C(z)$:
-%
-\begin{equation}
-\label{eq:deltaG_final}
-\Delta{G_{Q}(z)}=\frac{\sigma^{2}_{Q}}{r}\cdot \frac{1+FWL[C(z)]G(z)}{FWL[C(z)]} \cdot \frac{z-1}{z}.
-\end{equation}
-
-Finally, Eq.~\eqref{eq:deltaG_final} is a suitable frequency domain model
-for quantization noise effects on closed-loop systems.  This model depends
-on the plant pulse transfer function ($G(z)$), which is described by
-Eq.~\eqref{eq:pulsetf}, the height of step reference signal $r$, and the
-digital controller model.
+%%
+%\end{itemize}
+%
+%An alternative expression for $\Delta{G_{Q}(z)}$ can be obtained from
+%Eq.~\eqref{eq:deltag_var}, transforming it into a function of the reference
+%$R(z)$.  Once $U(z)$ is the control signal obtained via digital controller
+%$C(z)$ and error signal, {\it i.e.},
+%%
+%\begin{equation}
+%U(z)=C(z)\cdot[R(z)-Y(z)],
+%\end{equation} 
+%
+%\noindent where $Y(z)$ is the first term of Eq.~\eqref{eq:outputfunctions}, thus:
+%\begin{equation}
+%\label{eq:controlsignal}
+%\resizebox{0.48\textwidth}{!}{
+%$U(z)=C(z)\cdot \left[R(z)-\frac{C(z)G(z)}{1+C(z)G(z)}R(z)\right]=\frac{C(z)}{1+C(z)G(z)}R(z).$
+%}
+%\end{equation} 
+%
+%Substituting Eq.~\eqref{eq:controlsignal} in Eq.~\eqref{eq:deltag_var}, a
+%model for $\Delta{G_{Q}(z)}$ depending on $R(z)$ can be obtained:
+%%
+%\begin{equation}
+%\Delta{G_{Q}(z)}=\sigma^{2}_{Q}\cdot \frac{1+C(z)G(z)}{C(z)} \cdot \frac{1}{R(z)},
+%\end{equation}
+%
+%\noindent where $R(z)$ can be considered as a step signal (for stabilization
+%purpose) with height equal to $r$, which can be rewritten as
+%%
+%\begin{equation}
+%\Delta{G_{Q}(z)}=\frac{\sigma^{2}_{Q}}{r}\cdot \frac{1+C(z)G(z)}{C(z)} \cdot \frac{z-1}{z}.
+%\end{equation}
+%
+%A more precise description of $\Delta{G_{Q}(z)}$ can be obtained
+%considering FWL \red{[clarify what you mean with FWL, introduce FWL function explicitly and precisely]} effects on digital controller coefficients, as described in
+%Bessa {\it et al.}~\cite{Bessa16}, {\it i.e.}, using $FWL[C(z)]$ instead of
+%the nominal $C(z)$:
+%%
+%\begin{equation}
+%\label{eq:deltaG_final}
+%\Delta{G_{Q}(z)}=\frac{\sigma^{2}_{Q}}{r}\cdot \frac{1+FWL[C(z)]G(z)}{FWL[C(z)]} \cdot \frac{z-1}{z}.
+%\end{equation}
+%
+%Finally, Eq.~\eqref{eq:deltaG_final} is a suitable frequency domain model
+%for quantization noise effects on closed-loop systems.  This model depends
+%on the plant pulse transfer function ($G(z)$), which is described by
+%Eq.~\eqref{eq:pulsetf}, the height of step reference signal $r$, and the
+%digital controller model.
 

### 2016-10-08 paper/paper.tex
nomenclature

@@
   \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
-    \node[draw=none] (r) {r(z)};
+    \node[draw=none] (r) {$\tilde R(z)$};
 %   \& \coordinate (aux0);
@@
         label=\textbf{Controller}] (cz) {{\sc C(z)}};
-   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$\tilde u(z)$};
+   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$\tilde U(z)$};
 
@@
      \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
-     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu2$};
+     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
      \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}
@@
         label=\textbf{Plant}] (gs) {{\sc G(s)}};
-   \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]gs)  {$u(s)$};
-   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$y(s)$};
+   \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]gs)  {$U(s)$};
+   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(s)$};
    \& complexnode/.pic={ 
@@
      \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
-   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu1$};
+   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
    \& \coordinate (aux1);
-   \& \node[draw=none] (yz) {$\tilde y(z)$};\\
+   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
    \& \coordinate (aux3); 
@@
 
-\subsection{Modelling Error on Parameters Representation} 
+%\subsection{Modelling Error on Parameters Representation} 
 %\label{sec:}
 
-\red{[TO BE COMPLETED.]}
+%\red{[TO BE COMPLETED.]}
 

### 2016-10-08 paper/paper.tex
remove Figure 1

@@
 for {\em hybrid closed-loop systems}, {\it i.e.}, embedded controllers along with a model of their
-physical environment, the plant, as shown in
-Fig.~\ref{fig:closed-system}, that are {\em stable}.  Due to the complexity
+physical environment (the plant), which are {\em stable}.  Due to the complexity
 of such systems, we focus on linear models with known configurations
@@
 
-\begin{figure}
-\centering
-\resizebox{.35\textwidth}{!}{
- \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
-     semithick, initial text=, ampersand replacement=\&,]
-
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.5cm, column sep=.5cm] {
-   \coordinate (aux0);
-   \& \node[circle] (circle) {}; 
-   \& \node[fill=yellow!20] (da) {{\sc D/A}}; 
-   \& \node[fill=yellow!20] (p) {{\sc P}};
-   \& \node[fill=yellow!20] (ad) {{\sc A/D}}; 
-   \& \coordinate (aux1);\\
-   \& \coordinate (aux3); 
-   \&
-   \&
-   \node[fill=yellow!20] (c) {C};
-   \& 
-   \& \coordinate (aux2);\\
-  };
-
-  \path[->] (aux0) edge (circle.west);
-  \path  
-   (circle.east) edge (da.west)
-   (da.east) edge (p.west)
-   (p.east) edge (ad.west)
-   (ad.east) edge (aux1.west)
-   (aux1.south) edge (aux2.north)
-   (aux2.west) edge (c.east)
-   (c.west) edge (aux3.east); 
-  \path[->]  (aux3.north) edge (circle.south);
- \end{tikzpicture}
-}
- \caption{Closed-Loop System. \label{fig:closed-system}}
-\end{figure}
+%\begin{figure}
+%\centering
+%\resizebox{.35\textwidth}{!}{
+% \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
+%     semithick, initial text=, ampersand replacement=\&,]
+
+%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.5cm, column sep=.5cm] {
+%   \coordinate (aux0);
+%   \& \node[circle] (circle) {}; 
+%   \& \node[fill=yellow!20] (da) {{\sc D/A}}; 
+%   \& \node[fill=yellow!20] (p) {{\sc P}};
+%   \& \node[fill=yellow!20] (ad) {{\sc A/D}}; 
+%   \& \coordinate (aux1);\\
+%   \& \coordinate (aux3); 
+%   \&
+%   \&
+%   \node[fill=yellow!20] (c) {C};
+%   \& 
+%   \& \coordinate (aux2);\\
+%  };
+
+%  \path[->] (aux0) edge (circle.west);
+%  \path  
+%   (circle.east) edge (da.west)
+%   (da.east) edge (p.west)
+%   (p.east) edge (ad.west)
+%   (ad.east) edge (aux1.west)
+%   (aux1.south) edge (aux2.north)
+%   (aux2.west) edge (c.east)
+%   (c.west) edge (aux3.east); 
+%  \path[->]  (aux3.north) edge (circle.south);
+% \end{tikzpicture}
+%}
+% \caption{Closed-Loop System. \label{fig:closed-system}}
+%\end{figure}
 
@@
 on the polynomial coefficients, following Jury's Criteria, as well as the restrictions
-set in the representation of these coefficients by the function $f$ (Eq. \ref{FWL_tf}).
+set in the representation of these coefficients by the function $f$ (cf. Eq. \eqref{FWL_tf}).
 

### 2016-10-08 paper/paper.tex
implemented a part of the prog synthesis comments

--- 2016-10-08 paper/paper.tex
@@
 \title{
-Sound Automated Synthesis of Digital Controllers
+Sound and Automated Synthesis of Digital Controllers for Physical Plants 
 %Counterexample-guided Synthesis of Closed-loop Digital Control Systems
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Modelling Errors}
-
-%In this section, we show how to embed discretisation errors on the plant model, as follows: 
-%%$\hat{G}(z)$ is split into two terms:
-%%
-%\begin{equation}
-%\label{eq:uncertainplant}
-%%\hat{G}(z)=G(z)+\Delta{G(z)},
-%\tilde G(z) = \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z),   
-%\end{equation}
-%where $G(z,T)$ is the time discretisation of the nominal physical plant $G(s)$, 
-%$\Delta{G_{Q}(z)}$ represents the quantisation uncertainty model, 
-%and $\Delta{G_{P}(z)}$ describes the parametric uncertainty model.
+\section{Modelling Errors}
+
+In this section, we show how to embed discretisation errors on the plant model, as follows: 
+%$\hat{G}(z)$ is split into two terms:
+%
+\begin{equation}
+\label{eq:uncertainplant}
+%\hat{G}(z)=G(z)+\Delta{G(z)},
+\tilde G(z) = \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z),   
+\end{equation}
+where $G(z,T)$ is the time discretisation of the nominal physical plant $G(s)$, 
+$\Delta{G_{Q}(z)}$ represents the quantisation uncertainty model, 
+and $\Delta{G_{P}(z)}$ describes the parametric uncertainty model.
 
@@
 
-\section{An Uncertainty Model for the Quantization Error} 
+\subsection{An Uncertainty Model for the Quantization Error} 
 \label{sec:uncertainty-model-quantization-error}
@@
 
-Consider the closed-loop sampled system in Figure~\ref{fig:sampledsystem},
+Consider the closed-loop sampled system in Figure~\ref{fig:sampledsystem} \red{[requires updating]},
 where $C(z)$ is the digital controller model, whose control output signal is
@@
 
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
-    \node[draw=none] (r) {r(z)};
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.5cm, column sep=.5cm] {
+    \node[draw=none] (r) {r};
 %   \& \coordinate (aux0);
    \& \node[circle,add={-}{+}{}{}] (circle) {};
-   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$\tilde e(z)$};
+   \& complexnode/.pic={ 
+     \node[rectangle,draw,
+	minimum width=4cm,
+	minimum height=1.6cm,
+	label=\textbf{ADC},] (adc) {};
+   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
+   \coordinate (switch1) at ([xshift=-1cm]adc.center);
+   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
+   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
+     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
+   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu1$};
    \& \node[rectangle,draw,
@@
    \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]gs)  {$u(s)$};
-   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$y(s)$};
-   \& complexnode/.pic={ 
-     \node[rectangle,draw,
-	minimum width=4cm,
-	minimum height=1.6cm,
-	label=\textbf{ADC},] (adc) {};
-   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
-   \coordinate (switch1) at ([xshift=-1cm]adc.center);
-   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
-   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
-     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
-   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu1$};
    \& \coordinate (aux1);
-   \& \node[draw=none] (yz) {$\tilde y(z)$};\\
+   \& \node[draw=none] (y) {y};\\
    \& \coordinate (aux3); 
@@
   \path[->] (r) edge (circle.west);
-  \path[->] (aux1) edge (yz);
+  \path[->] (aux1) edge (y);
   \path  
-   (circle.east) edge (cz)
+   (circle.east) edge (switch1)
+   (switch2) edge (q1.west)
+   (q1.east) edge (cz.west)
    (cz.east) edge (q2.west)
@@
    (zoh.east) edge (gs.west)
-   (switch2) edge (q1.west)
-   (q1.east) edge (aux1.west)
-   (gs.east) edge (switch1.west)
+   (gs.east) edge (aux1.west)
    (aux1.south) edge (aux2.north)
@@
 
-First, some assumptions have to be established to obtain a model for the quantization effects (seen as noise) on the closed loop system. 
+First, some assumptions have to be established to obtain a model for $\Delta{G_{Q}(z)}$. 
+\blue{[Here we need to be careful: we first argue that quantisation (spelled with an s, so that ER II is happy) effects can be represented as an additive noise (great), which however is a stochastic signal.
+But we handle the noise deterministically.
+How so?
+Where is the catch?
+]}
 %
@@
 The quantization noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
-$Q2$) are energy bounded uncorrelated white noises.
-
-In \cite{widrow1956}, Widrow models the quantization noise as a gaussian model in which
-the second moment (variance) of the probability density function (pdf) of the quantization
-noise is given by
-%
-\begin{equation}
-\label{eq:variancelemma}
-\sigma_{Q}^{2}=\frac{q^{2}}{12},
-\end{equation}
-where $q$ is the step size of quantizer, thus supporting this assumption.
+$Q2$) are white noises.
+%
+\end{myassumption}
+
+\begin{myassumption}
+The quantization noises $\nu_{1}$ and $\nu_{2}$ are uncorrelated with each other.
 \end{myassumption}
@@
 
-%\begin{myprop}
-%Considering the quantisation noise $\nu(k)$ as an output error in the
-%discrete plant model, 
-%%{\it i.e.}, it does not affect the plant dynamics, but its output samples, 
-%$\Delta{G_{Q}(z)}$ can be obtained from
-%%
-%\begin{equation}
-%\label{eq:quantization_tf}
-%\Delta{G_{Q}(z)}=\frac{\nu(z)}{U(z)},
-%\end{equation}
-%where $\nu(z)$ is the z-transform of the random process $\nu(k)$,
-%which can be calculated through the power spectral density of
-%$\nu(k)$~\cite{poularikas2000transforms}.  
-%Thus, the $\Delta{G_{Q}(z)}$ can expressed as
-%%
-%\begin{equation}
-%\label{eq:deltag_var}
-%\Delta{G_{Q}(z)}=\frac{\sigma_{Q}^{2}}{U(z)},
-%\end{equation}
-%where $\sigma_{Q}^{2}$ is the variance of the quantization noise and
-%$U(z)$ is the z-transform of control signal ({\it i.e.}, the z-transform of
-%the signal from the digital controller), which is provided to the plant by
-%means of ZOH.
-%\end{myprop}
-%
-%%
-%\begin{proof}
-%%
-%Suppose that the plant discrete model in Figure~\ref{fig:sampledsystem} can
-%be represented by the following pulse transfer function (without
-%quantization noise effect):
-%%
-%\begin{equation}
-%\label{eq:tfwithout}
-%G(z)=\frac{Y(z)}{U(z)}=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M}z^{-M}}{1+a_{1}z^{-1}+a_{2}z^{-2}+\cdots+a_{N}z^{-N}},
-%\end{equation}
-%%
-%\noindent where $Y(z)$ is the z-transform of the plant output signal without
-%noise $y(k)$, $U(z)$ is the z-transform of the control signal, which is
-%provided to the plant, $A(z)$ and $B(z)$ are the plant pulse transfer
-%function numerator and denominator, respectively.
-%
-%Considering the quantization noise $\nu(k)$ as an output error in the
-%discrete plant model, an additive noise in the plant output $y(k)$ resulting
-%in the noisy output $\hat{y}(k)$ can be represented as
-%%
-%\begin{equation}
-%\hat{y}(k)=y(k)+\nu(k).
-%\end{equation}
-%
-%Note that the model in Eq.~\eqref{eq:tfwithout} is equivalent to the
-%following difference equation:
-%%
-%\begin{equation}
-%\begin{split}
-%y(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
-%+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M),
-%\end{split}
-%\end{equation}
-%
-%\noindent and consequently $\hat{y}(k)$ can be represented by the following
-%difference equation:
-%%
-%\begin{equation}
-%\label{eq:differencewithnoise}
-%\begin{split}
-%\hat{y}(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
-%+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M)+\nu(k).
-%\end{split}
-%\end{equation}
-%
-%The z-transform of Eq.~\eqref{eq:differencewithnoise} is
-%%
-%\begin{equation}
-%\begin{split}
-%\hat{Y}(z)=(-a_{1}z^{-1}-a_{2}z^{-2}-\cdots-a_{N}z^{-N})Y(z)\\
-%+(b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M}z^{-M})U(z)+\nu(z),
-%\end{split}
-%\end{equation}
-%dividing both sides by $U(z)$, it is equivalent to:
-%\begin{equation}
-%\frac{\hat{Y}(z)}{U(z)}=\hat{G}(z)=[1-A(z)]G(z)+U(z)B(z)+\frac{\nu(z)}{U(z)}.
-%\end{equation}
-%
-%Considering $\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}$ and Eq.~\eqref{eq:tfwithout},
-%the intended expression can be obtained as
-%%
-%\begin{equation}
-%\Delta{G_{Q}(z)}=\frac{\nu(z)}{U(z)} 
-%\end{equation}
-%\end{proof}
-
-%Eq.~\eqref{eq:deltag_var} indicates that the modelling of the quantization noise
-%effect on the plant transfer function demands an estimation of the variance
-%of quantization noise $\sigma_{Q}^{2}$.  To obtain such estimation, the
-%methodology presented by~\cite{widrow2008quantization}
-%is used.  The authors provide an algorithm for computing the mean square of
-%the output noise due to $Q1$ and $Q2$.  Considering that each quantizer
-%contribution can be represented by a white noise with zero mean
-%(Assumption~\ref{whitenoise}), the mean square can be considered as the
-%variance of noise ($\sigma_{Q}^{2}$), which can be calculated as
-%%
-%\begin{equation}
-%\sigma_{Q}^{2}=\frac{\lambda_{1}^{2}\cdot \sum {h_{Q1}^{2}} \cdot q_{1}+\lambda_{2}^{2}\cdot \sum {h_{Q2}^{2}} \cdot q_{2}}{12},
-%\end{equation}
-%%
-%\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factors, {\it i.e.} constant gains usually employed before the ADC and after the DAC in order to avoid the overload of converters  %\red{[define scale factors]}
-%for the quantization $Q1$ and $Q2$, respectively; $q_{1}$ and $q_{2}$ are the quantization step for $Q1$ and $Q2$, respectively, and $\sum {h_{Q1}^{2}}$ and $\sum
-%{h_{Q2}^{2}}$ are the squares sums of the impulse response obtained by means
-%of a transfer function from $Q1$ and $Q2$ to the plant output, respectively.
-%
-%The transfer functions $H_{Q1}(z)$ and $H_{Q2}(z)$, from which the squares
-%sums of the impulse response are needed, can be obtained through the
-%analysis of the system in Figure~\ref{fig:sampledsystem}. 
-Considering that
+Given those assumptions, the present approach is further based on the following lemmas. 
+\red{[So we have introduced two quantisation errors, properly indexed. Next we discuss a non-indexed entity - pls clarify or comment.]}
+%
+\begin{mylemma}
+%
+\cite{widrow1956} The second moment (variance) of the probability probability density function of quantization
+noise is given by %\textcolor{red}{expand the acronym PDF}
+%
+\begin{equation}
+\label{eq:variancelemma}
+\sigma_{Q}^{2}=\frac{q^{2}}{12},
+\end{equation}
+\end{mylemma}
+where $q$ is the step size of quantizer. \blue{[can you add a comment on this assumption? Why the factor 12?]}
+
+\begin{myprop}
+Considering the quantisation noise $\nu(k)$ as an output error in the
+discrete plant model, 
+%{\it i.e.}, it does not affect the plant dynamics, but its output samples, 
+$\Delta{G_{Q}(z)}$ can be obtained from
+%
+\begin{equation}
+\label{eq:quantization_tf}
+\Delta{G_{Q}(z)}=\frac{\nu(z)}{U(z)},
+\end{equation}
+where $\nu(z)$ is the z-transform of the random process $\nu(k)$,
+which can be calculated through the power spectral density of
+$\nu(k)$~\cite{poularikas2000transforms}.  
+Thus, the $\Delta{G_{Q}(z)}$ can expressed as
+%
+\begin{equation}
+\label{eq:deltag_var}
+\Delta{G_{Q}(z)}=\frac{\sigma_{Q}^{2}}{U(z)},
+\end{equation}
+where $\sigma_{Q}^{2}$ is the variance of the quantization noise and
+$U(z)$ is the z-transform of control signal ({\it i.e.}, the z-transform of
+the signal from the digital controller), which is provided to the plant by
+means of ZOH.
+\end{myprop}
+
+%
+\begin{proof}
+%
+Suppose that the plant discrete model in Figure~\ref{fig:sampledsystem} can
+be represented by the following pulse transfer function (without
+quantization noise effect):
+%
+\begin{equation}
+\label{eq:tfwithout}
+G(z)=\frac{Y(z)}{U(z)}=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M}z^{-M}}{1+a_{1}z^{-1}+a_{2}z^{-2}+\cdots+a_{N}z^{-N}},
+\end{equation}
+%
+\noindent where $Y(z)$ is the z-transform of the plant output signal without
+noise $y(k)$, $U(z)$ is the z-transform of the control signal, which is
+provided to the plant, $A(z)$ and $B(z)$ are the plant pulse transfer
+function numerator and denominator, respectively.
+
+Considering the quantization noise $\nu(k)$ as an output error in the
+discrete plant model, an additive noise in the plant output $y(k)$ resulting
+in the noisy output $\hat{y}(k)$ can be represented as
+%
+\begin{equation}
+\hat{y}(k)=y(k)+\nu(k).
+\end{equation}
+
+Note that the model in Eq.~\eqref{eq:tfwithout} is equivalent to the
+following difference equation:
+%
+\begin{equation}
+\begin{split}
+y(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
++b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M),
+\end{split}
+\end{equation}
+
+\noindent and consequently $\hat{y}(k)$ can be represented by the following
+difference equation:
+%
+\begin{equation}
+\label{eq:differencewithnoise}
+\begin{split}
+\hat{y}(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
++b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M)+\nu(k).
+\end{split}
+\end{equation}
+
+The z-transform of Eq.~\eqref{eq:differencewithnoise} is
+%
+\begin{equation}
+\begin{split}
+\hat{Y}(z)=(-a_{1}z^{-1}-a_{2}z^{-2}-\cdots-a_{N}z^{-N})Y(z)\\
++(b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M}z^{-M})U(z)+\nu(z),
+\end{split}
+\end{equation}
+dividing both sides by $U(z)$, it is equivalent to:
+\begin{equation}
+\frac{\hat{Y}(z)}{U(z)}=\hat{G}(z)=[1-A(z)]G(z)+U(z)B(z)+\frac{\nu(z)}{U(z)}.
+\end{equation}
+
+Considering $\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}$ and Eq.~\eqref{eq:tfwithout},
+the intended expression can be obtained as
+%
+\begin{equation}
+\Delta{G_{Q}(z)}=\frac{\nu(z)}{U(z)} 
+\end{equation}
+\end{proof}
+
+Eq.~\eqref{eq:deltag_var} indicates that the modelling of the quantization noise
+effect on the plant transfer function demands an estimation of the variance
+of quantization noise $\sigma_{Q}^{2}$.  To obtain such estimation, the
+methodology presented by~\cite{widrow2008quantization}
+is used.  The authors provide an algorithm for computing the mean square of
+the output noise due to $Q1$ and $Q2$.  Considering that each quantizer
+contribution can be represented by a white noise with zero mean
+(Assumption~\ref{whitenoise}), the mean square can be considered as the
+variance of noise ($\sigma_{Q}^{2}$), which can be calculated as
+%
+\begin{equation}
+\sigma_{Q}^{2}=\frac{\lambda_{1}^{2}\cdot \sum {h_{Q1}^{2}} \cdot q_{1}+\lambda_{2}^{2}\cdot \sum {h_{Q2}^{2}} \cdot q_{2}}{12},
+\end{equation}
+%
+\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factors, {\it i.e.} constant gains usually employed before the ADC and after the DAC in order to avoid the overload of converters  %\red{[define scale factors]}
+for the quantization $Q1$ and $Q2$, respectively; $q_{1}$ and $q_{2}$ are the quantization step for $Q1$ and $Q2$, respectively, and $\sum {h_{Q1}^{2}}$ and $\sum
+{h_{Q2}^{2}}$ are the squares sums of the impulse response obtained by means
+of a transfer function from $Q1$ and $Q2$ to the plant output, respectively.
+
+The transfer functions $H_{Q1}(z)$ and $H_{Q2}(z)$, from which the squares
+sums of the impulse response are needed, can be obtained through the
+analysis of the system in Figure~\ref{fig:sampledsystem}.  Considering that
 the quantizer $Q1$ is the source of a white noise with zero mean $\nu_{1}$
@@
 \label{eq:outputfunctions}
-\hat{Y}(z)=H_{1}(z)\left(R(z)+\nu_{1}(z)\right)+H_{2}(z)\nu_{2}(z)
-\end{equation}
-$$H_{1}(z)=\frac{C(z)G(z)}{1+C(z)G(z)}$$
-$$H_{2}(z)=\frac{G(z)}{1+C(z)G(z)}$$
-
-In the case of stability properties we need to verify the stability of both $H_{1}(z)$ and $H_{2}(z)$ to validate the stability of the whole system.
-%These equations are sufficient for computing $\sigma_{Q}^{2}$.  However,
-%there is still a gap for a complete model for $\Delta{G_{Q}(z)}$ in
-%Eq.~\eqref{eq:deltag_var}, {\it i.e.}, the z-transform of control action
-%$U(z)$.  This indicates that the quantization noise effect on a discrete
-%plant model mainly depends on three main factors:
-%%
-%\begin{itemize}
-%%
-%\item \textbf{Sample time:} the sample time effect is reflected over pulse transfer function that covers the effects of DAC ant its interpolator (ZOH) \red{[clarify/revise based on the comments made above.]};
-%%
-%\item \textbf{ADC and DAC step:} \red{[again, do we need both?]} these are the main component of quantization noise power, but an $8$-bits converter already reduces the effect of quantization noises in the output for negligible values.
-%%
-%\item \textbf{Signal-to-noise ratio (SNR): } the dependence on the value of $U(z)$ \red{[notice that now we have reduced the problem to depend on the effect of the reference signal transform R(z) - pls revise.]} shows the importance of the SNR for handling quantization noise; for a high SNR of the digital controller, the quantization effect is negligible.
+\resizebox{0.48\textwidth}{!}{
+$\hat{Y}(z)=\frac{C(z)G(z)}{1+C(z)G(z)}R(z)+\frac{C(z)G(z)}{1+C(z)G(z)}\nu_{1}(z) \\
++\frac{G(z)}{1+C(z)G(z)}\nu_{2}(z).$
+}
+\end{equation}
+
+Thus, $H_{Q1}(z)$ and $H_{Q2}(z)$ can be extracted from Eq.~\eqref{eq:outputfunctions}:
+\begin{equation}
+H_{Q1}(z)=\frac{C(z)G(z)}{1+C(z)G(z)},
+\end{equation}
+and
+\begin{equation}
+H_{Q2}(z)=\frac{G(z)}{1+C(z)G(z)}.
+\end{equation}
+
+These equations are sufficient for computing $\sigma_{Q}^{2}$.  However,
+there is still a gap for a complete model for $\Delta{G_{Q}(z)}$ in
+Eq.~\eqref{eq:deltag_var}, {\it i.e.}, the z-transform of control action
+$U(z)$.  This indicates that the quantization noise effect on a discrete
+plant model mainly depends on three main factors:
+%
+\begin{itemize}
+%
+\item \textbf{Sample time:} the sample time effect is reflected over pulse transfer function that covers the effects of DAC ant its interpolator (ZOH) \red{[clarify/revise based on the comments made above.]};
+%
+\item \textbf{ADC and DAC step:} \red{[again, do we need both?]} these are the main component of quantization noise power, but an $8$-bits converter already reduces the effect of quantization noises in the output for negligible values.
+%
+\item \textbf{Signal-to-noise ratio (SNR): } the dependence on the value of $U(z)$ \red{[notice that now we have reduced the problem to depend on the effect of the reference signal transform R(z) - pls revise.]} shows the importance of the SNR for handling quantization noise; for a high SNR of the digital controller, the quantization effect is negligible.
 This happens during the transient of the system, when high control actions are employed.
@@
 A digital controller with integral action might be sufficient for eliminating such influence at steady state.
-%%
-%\end{itemize}
-%
-%An alternative expression for $\Delta{G_{Q}(z)}$ can be obtained from
-%Eq.~\eqref{eq:deltag_var}, transforming it into a function of the reference
-%$R(z)$.  Once $U(z)$ is the control signal obtained via digital controller
-%$C(z)$ and error signal, {\it i.e.},
-%%
-%\begin{equation}
-%U(z)=C(z)\cdot[R(z)-Y(z)],
-%\end{equation} 
-%
-%\noindent where $Y(z)$ is the first term of Eq.~\eqref{eq:outputfunctions}, thus:
-%\begin{equation}
-%\label{eq:controlsignal}
-%\resizebox{0.48\textwidth}{!}{
-%$U(z)=C(z)\cdot \left[R(z)-\frac{C(z)G(z)}{1+C(z)G(z)}R(z)\right]=\frac{C(z)}{1+C(z)G(z)}R(z).$
-%}
-%\end{equation} 
-%
-%Substituting Eq.~\eqref{eq:controlsignal} in Eq.~\eqref{eq:deltag_var}, a
-%model for $\Delta{G_{Q}(z)}$ depending on $R(z)$ can be obtained:
-%%
-%\begin{equation}
-%\Delta{G_{Q}(z)}=\sigma^{2}_{Q}\cdot \frac{1+C(z)G(z)}{C(z)} \cdot \frac{1}{R(z)},
-%\end{equation}
-%
-%\noindent where $R(z)$ can be considered as a step signal (for stabilization
-%purpose) with height equal to $r$, which can be rewritten as
-%%
-%\begin{equation}
-%\Delta{G_{Q}(z)}=\frac{\sigma^{2}_{Q}}{r}\cdot \frac{1+C(z)G(z)}{C(z)} \cdot \frac{z-1}{z}.
-%\end{equation}
-%
-%A more precise description of $\Delta{G_{Q}(z)}$ can be obtained
-%considering FWL \red{[clarify what you mean with FWL, introduce FWL function explicitly and precisely]} effects on digital controller coefficients, as described in
-%Bessa {\it et al.}~\cite{Bessa16}, {\it i.e.}, using $FWL[C(z)]$ instead of
-%the nominal $C(z)$:
-%%
-%\begin{equation}
-%\label{eq:deltaG_final}
-%\Delta{G_{Q}(z)}=\frac{\sigma^{2}_{Q}}{r}\cdot \frac{1+FWL[C(z)]G(z)}{FWL[C(z)]} \cdot \frac{z-1}{z}.
-%\end{equation}
-%
-%Finally, Eq.~\eqref{eq:deltaG_final} is a suitable frequency domain model
-%for quantization noise effects on closed-loop systems.  This model depends
-%on the plant pulse transfer function ($G(z)$), which is described by
-%Eq.~\eqref{eq:pulsetf}, the height of step reference signal $r$, and the
-%digital controller model.
+%
+\end{itemize}
+
+An alternative expression for $\Delta{G_{Q}(z)}$ can be obtained from
+Eq.~\eqref{eq:deltag_var}, transforming it into a function of the reference
+$R(z)$.  Once $U(z)$ is the control signal obtained via digital controller
+$C(z)$ and error signal, {\it i.e.},
+%
+\begin{equation}
+U(z)=C(z)\cdot[R(z)-Y(z)],
+\end{equation}
+
+\noindent where $Y(z)$ is the first term of Eq.~\eqref{eq:outputfunctions}, thus:
+\begin{equation}
+\label{eq:controlsignal}
+\resizebox{0.48\textwidth}{!}{
+$U(z)=C(z)\cdot \left[R(z)-\frac{C(z)G(z)}{1+C(z)G(z)}R(z)\right]=\frac{C(z)}{1+C(z)G(z)}R(z).$
+}
+\end{equation}
+
+Substituting Eq.~\eqref{eq:controlsignal} in Eq.~\eqref{eq:deltag_var}, a
+model for $\Delta{G_{Q}(z)}$ depending on $R(z)$ can be obtained:
+%
+\begin{equation}
+\Delta{G_{Q}(z)}=\sigma^{2}_{Q}\cdot \frac{1+C(z)G(z)}{C(z)} \cdot \frac{1}{R(z)},
+\end{equation}
+
+\noindent where $R(z)$ can be considered as a step signal (for stabilization
+purpose) with height equal to $r$, which can be rewritten as
+%
+\begin{equation}
+\Delta{G_{Q}(z)}=\frac{\sigma^{2}_{Q}}{r}\cdot \frac{1+C(z)G(z)}{C(z)} \cdot \frac{z-1}{z}.
+\end{equation}
+
+A more precise description of $\Delta{G_{Q}(z)}$ can be obtained
+considering FWL \red{[clarify what you mean with FWL, introduce FWL function explicitly and precisely]} effects on digital controller coefficients, as described in
+Bessa {\it et al.}~\cite{Bessa16}, {\it i.e.}, using $FWL[C(z)]$ instead of
+the nominal $C(z)$:
+%
+\begin{equation}
+\label{eq:deltaG_final}
+\Delta{G_{Q}(z)}=\frac{\sigma^{2}_{Q}}{r}\cdot \frac{1+FWL[C(z)]G(z)}{FWL[C(z)]} \cdot \frac{z-1}{z}.
+\end{equation}
+
+Finally, Eq.~\eqref{eq:deltaG_final} is a suitable frequency domain model
+for quantization noise effects on closed-loop systems.  This model depends
+on the plant pulse transfer function ($G(z)$), which is described by
+Eq.~\eqref{eq:pulsetf}, the height of step reference signal $r$, and the
+digital controller model.
 
@@
 Fig.~\ref{fig:CEGIS} and consists of two phases, {\sc
-Synthesise} and {\sc Verify}, which interact via a finite set of test vectors {\sc inputs} \blue{that is updated incrementally}.
-The {\sc synth} procedure tries to find an existential witness $P$
+Synthesise} and {\sc Verify}, which interact via a finite set of test vectors {\sc inputs} 
+that is updated incrementally.
+Given a specification $\sigma$ over variables $x$
+and $P$, the {\sc synth} procedure tries to find an existential witness $P$
 that satisfies the specification $\sigma(x, P)$ for all $x$, namely:
@@
 set, and the loop iterates again.  It is worth noting that each iteration of the
-loop adds a new input to the \red{finite} set $\text{\sc inputs}$  being used for synthesis.  If
+loop adds a new input to the finite set $\text{\sc inputs}$  being used for synthesis.  If
 the full set of inputs \blue{[which by now should have a name, as suggested to be introduced above]} is finite, this means that the refinement loop
@@
 We use this method to check the stability in the $z$-domain for the characteristic polynomial $S(z)$ of 
-the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$ \red{[unclear: what matrix?
+the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$, where $Y(z)$ is the 
+closed-loop system output and U(z) is the controller output. 
+%% \red{[unclear: what matrix?
 We need to clarify the relationship between the char.
@@
 $S(z)$ and the later quantities $\Delta N_{G}(z), \Delta D_{G}(z)$ and corresponding controller's structure.]}.
+%
 We consider the following form for $S(z)$:
@@
 %\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?}
+
+Assuming that $\hat{G}(z) = \frac{\hat{N_G}(z)}{\hat{D_G}(z)}$
+and $\hat{C}(z) = \frac{\hat{N_C}(z)}{\hat{D_C}(z)}$, then:
+$$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$
 
@@
 then we obtain a counterexample denoted by 
-values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$ \red{[see my comment above - these quantities pop up too abruptly.]},
-which make the closed-loop system unstable. This uncertainty is added to 
+values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
+%\red{[see my comment above - these quantities pop up too abruptly.]},
+which make the closed-loop system unstable. 
+Note that, similar to the rest of the paper, we use the notation 
+$\hat{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
+$\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
+This uncertainty is added to 
 the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
@@
 in Sec.~\ref{sec:running-ex}.
-We start with a candidate solution that has all coefficients 0 \red{[Be more explicit, write out spurious candidate solution with zero coefficients.
-KISS - you don't want to lose the control audience here.]}.
+We start with a candidate solution that has all coefficients 0:
+%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
+
+$$
+\begin{array}{ll}
+N_C(z) {=} 0z^2{+}0z{+}0\\
+D_C(z) {=} 0z^2{+}0z{+}0\\
+\end{array}
+$$
+
 In the first {\sc verify} phase we obtain the following counterexample:

### 2016-10-08 paper/paper.tex
expand Figure 2
line breaks

@@
 \maketitle
+
 \begin{abstract}
-Modern control systems are by and large implemented via digital microcontrollers, 
-which are designed to work in an embedded environment, 
+%
+Modern control systems are by and large implemented via digital
+microcontrollers, which are designed to work in an embedded environment,
 within a dynamical plant that can present physical components.
 %
-This poses a new dimension to the problem of controllers synthesis,   
-which is classically studied in digital control literature. 
-%
-In this study, we plan to provide a principled approach to extend this literature in a number of directions: 
-we are interested in quantitative tasks;  
-we focus on automated correct-by-design synthesis algorithms, as opposed to verification objectives; 
-and we encompass the complete range of approximations, related to time discretisation, quantisation effects, 
-and finite-precision representations (with related rounding errors). To this end, 
-we propose a CEGIS-based solution that uses inductive invariant synthesis in conjunction with a digital verification algorithm 
-to find a parametric solution for a digital controller given a continuous plant specification. 
+This poses a new dimension to the problem of controllers synthesis, which is
+classically studied in digital control literature.
+%
+In this study, we plan to provide a principled approach to extend this
+literature in a number of directions: we are interested in quantitative
+tasks; we focus on automated correct-by-design synthesis algorithms, as
+opposed to verification objectives; and we encompass the complete range of
+approximations, related to time discretisation, quantisation effects, and
+finite-precision representations (with related rounding errors).  To this
+end, we propose a CEGIS-based solution that uses inductive invariant
+synthesis in conjunction with a digital verification algorithm to find a
+parametric solution for a digital controller given a continuous plant
+specification.
+%
 \end{abstract}
@@
 Modern implementations of embedded control have proliferated with the
-availability of low cost devices that can perform simple tasks for
-linear control, spanning many areas such as environmental control and
-robotic manipulations~\cite{astrom1997computer,Franklin15}. 
-The downside to this approach is that in order
-to achieve low prices, devices are often limited in their
-capabilities, be it a low number of gates in an FPGA or short word
-lengths for microcontrollers. In most cases a floating-point
-implementation is not feasible and the system can benefit from the
-added resolution of a fixed-point representation. The ubiquity of
-these devices requires that they have a robust design that ensures the
-correct behaviour in a number of different environments.  % For this reason it is
+availability of low cost devices that can perform simple tasks for linear
+control, spanning many areas such as environmental control and robotic
+manipulations~\cite{astrom1997computer,Franklin15}.  The downside to this
+approach is that in order to achieve low prices, devices are often limited
+in their capabilities, be it a low number of gates in an FPGA or short word
+lengths for microcontrollers.  In most cases a floating-point implementation
+is not feasible and the system can benefit from the added resolution of a
+fixed-point representation.  The ubiquity of these devices requires that
+they have a robust design that ensures the correct behaviour in a number of
+different environments.
+%
+% For this reason it is
 % necessary to provide design tools that formally verify the correctness
@@
 
-There has been previous work to formally verify uncertain linear systems stability 
-in digital controllers with considerations to the implementation aspects 
-({\it i.e.}, fixed-point arithmetic and word-length)~\cite{Bessa16}.
-In particular, Bessa {\it et al.} considers finite-word length
-(FWL) effects over digital controllers and also parameter uncertainties
-in the context of verifying the (so-called) robust non-fragile stability~\cite{bhattacharyya97}.
-However, the authors do not consider the compete range of approximations, 
-related to time discretisation, and quantisation effects. As a result,
-the stability verification method proposed by Bessa {\it et al.} is incomplete, 
-given that false alarms can be produced due to the quantisation effects. 
-Additionally, the authors do not find a parametric solution for a digital controller 
-given as a continuous plant specification, in order to synthesize the controller implementation.
-
-In this paper, however, we explore the automatic synthesis of 
-{\em correct-by-construction} dgital controllers, which 
-reduces the deveopment cost and design time for a number of models.  
-In particular, we are interested in synthesising controllers 
-for {\em hybrid closed-loop systems}, {\it i.e.}, embedded controllers along with a model of their
-physical environment (the plant), which are {\em stable}.  Due to the complexity
-of such systems, we focus on linear models with known configurations
-to perform parametric synthesis of the controller dynamics.
-
-Since the digital control synthesis is performed over a hybrid model,
-where the plant displays a continuous behaviour and the controller
-operates in both discrete time and state-space, we initially translate
-the problem into a single domain which represents a bi-simulation of
-the original dynamics. Given our primary interest in evaluating digital
-effects in addition to stability, we have modeled a digital equivalent
-of the plant by evaluating the effects of the quantisers (A/D and D/A
-converters) as time discretisation elements with quantisation noise.
-The resulting closed loop system is a program loop working over
-bit-vectors of fixed-point arithmetic with fixed word length. The
-effect of the FWL is included in the model as a parametric uncertainty
-which must be taken into account for the correct synthesis of the
-controller.
+There has been previous work to formally verify uncertain linear systems
+stability in digital controllers with considerations to the implementation
+aspects ({\it i.e.}, fixed-point arithmetic and word-length)~\cite{Bessa16}. 
+In particular, Bessa {\it et al.} considers finite-word length (FWL) effects
+over digital controllers and also parameter uncertainties in the context of
+verifying the (so-called) robust non-fragile
+stability~\cite{bhattacharyya97}.  However, the authors do not consider the
+compete range of approximations, related to time discretisation, and
+quantisation effects.  As a result, the stability verification method
+proposed by Bessa {\it et al.} is incomplete, given that false alarms can be
+produced due to the quantisation effects.  Additionally, the authors do not
+find a parametric solution for a digital controller given as a continuous
+plant specification, in order to synthesize the controller implementation.
+
+In this paper, however, we explore the automatic synthesis of {\em
+correct-by-construction} dgital controllers, which reduces the deveopment
+cost and design time for a number of models.  In particular, we are
+interested in synthesising controllers for {\em hybrid closed-loop systems},
+{\it i.e.}, embedded controllers along with a model of their physical
+environment (the plant), which are {\em stable}.  Due to the complexity of
+such systems, we focus on linear models with known configurations to perform
+parametric synthesis of the controller dynamics.
+
+Since the digital control synthesis is performed over a hybrid model, where
+the plant displays a continuous behaviour and the controller operates in
+both discrete time and state-space, we initially translate the problem into
+a single domain which represents a bi-simulation of the original dynamics. 
+Given our primary interest in evaluating digital effects in addition to
+stability, we have modeled a digital equivalent of the plant by evaluating
+the effects of the quantisers (A/D and D/A converters) as time
+discretisation elements with quantisation noise.  The resulting closed loop
+system is a program loop working over bit-vectors of fixed-point arithmetic
+with fixed word length.  The effect of the FWL is included in the model as a
+parametric uncertainty which must be taken into account for the correct
+synthesis of the controller.
 
@@
 %Please stick to the introduced notations. Please clarify what the function FWL does, compared to the general approximations introduced above.]}
+
 \red{Alessandro, I've made the changes as requested. Please let me know if this is good enough or if I made it too short}
@@
 \noindent where $\beta$ and $\alpha$ are the controller's coefficients, $b$
-and $a$ are the plant's coefficients, and $N$ and $M$ are the number of poles and zeros for the corresponding block.
-
-Note that $G(z)$ is a
-discrete model of a real (and continuous) plant, {\it i.e.}, a continuous
-model of the plant must be discretized to obtain the discrete equivalent
-coefficients $b$ and $a$~\cite{Astrom08} via ZOH discretization.
-Although there are several discretization methods available in the literature~\cite{Franklin15}, the
-zero-order hold (ZOH) discretization is more suitable for representing the
-sampling and holding processes that are typically employed by hybrid
-systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretization models 
-the exact effect of sampling and DAC interpolation over the plant.
-
-\begin{mylemma} \cite{astrom1997computer}
-%
-The pulse transfer function $G(z)$ is a z-domain model that relates the output sampled by a ADC and the digital input provided by ZOH.
-It is equivalent at the sample times ({\it i.e.}, $kT$ to the continuous transfer function $G(s)$ driven by ZOH).
-This pulse transfer
-function can be computed as
+and $a$ are the plant's coefficients, and $N$ and $M$ are the number of
+poles and zeros for the corresponding block.
+
+Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it
+i.e.}, a continuous model of the plant must be discretized to obtain the
+discrete equivalent coefficients $b$ and $a$~\cite{Astrom08} via ZOH
+discretization.  Although there are several discretization methods available
+in the literature~\cite{Franklin15}, the zero-order hold (ZOH)
+discretization is more suitable for representing the sampling and holding
+processes that are typically employed by hybrid
+systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretization
+models the exact effect of sampling and DAC interpolation over the plant.
+
+\begin{mylemma}\cite{astrom1997computer}
+%
+The pulse transfer function $G(z)$ is a z-domain model that relates the
+output sampled by a ADC and the digital input provided by ZOH.  It is
+equivalent at the sample times ({\it i.e.}, $kT$ to the continuous transfer
+function $G(s)$ driven by ZOH).  This pulse transfer function can be
+computed as
 %
@@
 \end{equation}
-
-For convenience, we will use only the notation $G(z)$ to represent the pulse transfer function.
+%
+For convenience, we will use only the notation $G(z)$ to represent the pulse
+transfer function.
+%
 \end{mylemma}
 
-Since $G(z)$ is an approximation of $G(s)$ we denote the error in the approximation for time $t \neq kT$ as $\Delta{G}_P$
+Since $G(z)$ is an approximation of $G(s)$ we denote the error in the
+approximation for time $t \neq kT$ as $\Delta{G}_P$
+%
 \begin{align}
@@
 \end{align}
-Note that $\Delta{G}_P$ is undefined and upperbound by a user defined percentage such that $\hat{G}(z)$ corresponds to the polynomial set of possible values of $G(z, T): \forall T \in \mathbb{R}$
-
-Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented using a Fixed Point Finite Word Length with integer size $I$ and fractional size $F$.
-We shall denote this domain as $\mathbb{R}\langle I,F \rangle$
+%
+Note that $\Delta{G}_P$ is undefined and upperbound by a user defined
+percentage such that $\hat{G}(z)$ corresponds to the polynomial set of
+possible values of $G(z, T): \forall T \in \mathbb{R}$
+
+Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
+using a Fixed Point Finite Word Length with integer size $I$ and fractional
+size $F$.  We shall denote this domain as $\mathbb{R}\langle I,F \rangle$
+%
 \begin{align}
@@
 
-Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ domain, 
+Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$
+domain,
+%
  $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
+%
 However, given a real plant and real controller $\hat{G}(z), \hat{C}(z)$,
+%
 \begin{align}
@@
 \vspace{1 mm} 
-\noindent where $\Delta{G}_Q(z)$ represents the plant uncertainty caused by the rounding off effect.
-We may encompass all the uncertainty as $\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_Q(z)$.
-Since this value is nondeterministic, the polynomial set of possible values of $\tilde G(z)$ is denoted by $\mathfrak{G}(z)$.
+\noindent where $\Delta{G}_Q(z)$ represents the plant uncertainty caused by
+the rounding off effect.  We may encompass all the uncertainty as
+$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_Q(z)$.  Since this value is
+nondeterministic, the polynomial set of possible values of $\tilde G(z)$ is
+denoted by $\mathfrak{G}(z)$.
 
@@
 
-Given a model $(\hat{C}(z),\hat{G}(z), \mathbb{R}\langle I,F \rangle)$, provided
-in an ANSI-C code input file (Steps 1-5),
-DSVerifier constructs a non-deterministic model to represent the plant family
-$\mathfrak{G}(z)$ (Step A), and a transfer function $f$ [eq. \ref{FWL_tf}]
-(step B) to calulate the implementation $f(\hat{C}(z)) \rightarrow \tilde C(z)$
-of the controller (step C).
-Finally DSVerifier builds an intermediate ANSI-C code for the digital system
-implementation, which is used as input for the model-checker (Step D).
+Given a model $(\hat{C}(z),\hat{G}(z), \mathbb{R}\langle I,F \rangle)$,
+provided in an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
+non-deterministic model to represent the plant family $\mathfrak{G}(z)$
+(Step A), and a transfer function $f$ [eq.  \ref{FWL_tf}] (step B) to
+calulate the implementation $f(\hat{C}(z)) \rightarrow \tilde C(z)$ of the
+controller (step C).  Finally DSVerifier builds an intermediate ANSI-C code
+for the digital system implementation, which is used as input for the
+model-checker (Step D).
 
 This intermediate ANSI-C code model $(\tilde C(z),\mathfrak{G}(z),\phi)$
-containing a specification $\phi$ for the verification properties ({\it i.e.}, robust stability)
-is translated into SAT/SMT formulae by a back-end model-checking tool ({\it e.g.},
-CBMC~\cite{ClarkeKL04} or ESBMC~\cite{CordeiroFM12}).
-If any property violation is found, then DSVerifier reports a
-counterexample, which contains system inputs or parametric deviations
-$\Delta{G}$ that lead the system to a failure.  A successful verification
-result is reported if the system is safe with respect to $\phi$.  In
-particular, the stability verification is complete and sound, since it does
-not depend on system inputs and outputs.
-In the case of stability, the specification $\phi$ consists in a number of assumptions
-on the polynomial coefficients, following Jury's Criteria, as well as the restrictions
-set in the representation of these coefficients by the function $f$ (cf. Eq. \eqref{FWL_tf}).
+containing a specification $\phi$ for the verification properties ({\it
+i.e.}, robust stability) is translated into SAT/SMT formulae by a back-end
+model-checking tool ({\it e.g.}, CBMC~\cite{ClarkeKL04} or
+ESBMC~\cite{CordeiroFM12}).  If any property violation is found, then
+DSVerifier reports a counterexample, which contains system inputs or
+parametric deviations $\Delta{G}$ that lead the system to a failure.  A
+successful verification result is reported if the system is safe with
+respect to $\phi$.  In particular, the stability verification is complete
+and sound, since it does not depend on system inputs and outputs.  In the
+case of stability, the specification $\phi$ consists in a number of
+assumptions on the polynomial coefficients, following Jury's Criteria, as
+well as the restrictions set in the representation of these coefficients by
+the function $f$ (cf.~Eq.~\eqref{FWL_tf}).
 
@@
 
-To exploit the present approach full potential, a dynamical plant that can present 
-physical components must be considered. However, a discrete plant model can also demonstrate 
-some benefits of the present approach, which considers FWL effects in the digital 
-controller implementation. In particular, a classical cruise control example 
-is extracted from the literature~\cite{Astrom08}, where the discrete plant model (with time step
+To exploit the present approach full potential, a dynamical plant that can
+present physical components must be considered.  However, a discrete plant
+model can also demonstrate some benefits of the present approach, which
+considers FWL effects in the digital controller implementation.  In
+particular, a classical cruise control example is extracted from the
+literature~\cite{Astrom08}, where the discrete plant model (with time step
 of $0.2$s) is represented by the following z-expression:
@@
 
-Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16} has designed 
-a high-performance controller, which is characterised by the following z-domain transfer function:
+Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16}
+has designed a high-performance controller, which is characterised by the
+following z-domain transfer function:
+%
 \begin{equation}
@@
 \end{equation}
-The authors claim that this controller $C(z)$ stabilizes the closed-loop system for the discrete plant model $G(z)$.  
-However, if implementation aspects are considered during verification ({\it e.g.}, fixed-point arithmetic 
-and word-length), then this closed-loop system becomes unstable.
-%
-Indeed, the actual implementation of $C(z)$ using \param{4}{16} implementation format 
-({\it i.e.}, $4$ bits for the integer part and $16$ bits for the fractional part)
-can be represented by the following expression: 
+%
+The authors claim that this controller $C(z)$ stabilizes the closed-loop
+system for the discrete plant model $G(z)$.  However, if implementation
+aspects are considered during verification ({\it e.g.}, fixed-point
+arithmetic and word-length), then this closed-loop system becomes unstable.
+%
+Indeed, the actual implementation of $C(z)$ using \param{4}{16}
+implementation format ({\it i.e.}, $4$ bits for the integer part and $16$
+bits for the fractional part) can be represented by the following
+expression:
+%
 \begin{equation}
@@
 \end{equation} 
-which makes the system unstable in closed-loop using fixed-point arithmetic and 
-the typical series loop configuration, where $C_{q}\left(z\right)$ and $G\left(z\right)$ 
-are in the forward path.
+%
+which makes the system unstable in closed-loop using fixed-point arithmetic
+and the typical series loop configuration, where $C_{q}\left(z\right)$ and
+$G\left(z\right)$ are in the forward path.
 
@@
 quantized ($Q2$) and interpolated via a ZOH using digital-to-analog
-converter (DAC). The quantization occurs because the DAC resolution may be different from the fixed point representation of the controller.  
-$G(s)$ is the continuous-time model of the plant, from
-which output samples are taken and quantized ($Q1$) by means of an
-analog-to-digital converter (ADC) synchronized with the DAC.  Each quantizer
-($Q1$ and $Q2$) will present some contribution for the total quantization
-noise.
+converter (DAC).  The quantization occurs because the DAC resolution may be
+different from the fixed point representation of the controller.  $G(s)$ is
+the continuous-time model of the plant, from which output samples are taken
+and quantized ($Q1$) by means of an analog-to-digital converter (ADC)
+synchronized with the DAC.  Each quantizer ($Q1$ and $Q2$) will present some
+contribution for the total quantization noise.
 %    
@@
 
-First, some assumptions have to be established to obtain a model for the quantization effects (seen as noise) on the closed loop system. 
+First, some assumptions have to be established to obtain a model for the
+quantization effects (seen as noise) on the closed loop system.
 %
@@
 
-In \cite{widrow1956}, Widrow models the quantization noise as a gaussian model in which
-the second moment (variance) of the probability density function (pdf) of the quantization
-noise is given by
+In~\cite{widrow1956}, Widrow models the quantization noise as a gaussian
+model in which the second moment (variance) of the probability density
+function (pdf) of the quantization noise is given by
 %
@@
 %
-The controller and the plant are linear, {\it i.e.}, any source of nonlinearity ({\it e.g.}, saturation, overflow, ADC/DAC nonlinearities) will be disregarded.
+The controller and the plant are linear, {\it i.e.}, any source of
+nonlinearity ({\it e.g.}, saturation, overflow, ADC/DAC nonlinearities) will
+be disregarded.
 %
@@
 
-In order to synthesise closed-loop digital control systems, we use a
-program synthesis engine.  Nowadays, such engines are used
-increasingly often in program verification
-\cite{DBLP:conf/lpar/DavidKL15,DBLP:conf/cav/0001A14}.  Our program
-synthesiser makes use of Counter-Example Guided Inductive Synthesis
-(CEGIS) \cite{sketch}.  We start by presenting its general
-architecture followed by describing the parts specific to closed-loop control
-systems.
+In order to synthesise closed-loop digital control systems, we use a program
+synthesis engine.  Nowadays, such engines are used increasingly often in
+program verification~\cite{DBLP:conf/lpar/DavidKL15,DBLP:conf/cav/0001A14}. 
+Our program synthesiser makes use of Counter-Example Guided Inductive
+Synthesis (CEGIS) \cite{sketch}.  We start by presenting its general
+architecture followed by describing the parts specific to closed-loop
+control systems.
 
@@
 % 
-The design of our synthesiser is given in
-Fig.~\ref{fig:CEGIS} and consists of two phases, {\sc
-Synthesise} and {\sc Verify}, which interact via a finite set of test vectors {\sc inputs} 
-that is updated incrementally.
-Given a specification $\sigma$ over variables $x$
-and $P$, the {\sc synth} procedure tries to find an existential witness $P$
-that satisfies the specification $\sigma(x, P)$ for all $x$, namely:
+The design of our synthesiser is given in Fig.~\ref{fig:CEGIS} and consists
+of two phases, {\sc Synthesise} and {\sc Verify}, which interact via a
+finite set of test vectors {\sc inputs} that is updated incrementally. 
+Given a specification $\sigma$ over variables $x$ and $P$, the {\sc synth}
+procedure tries to find an existential witness $P$ that satisfies the
+specification $\sigma(x, P)$ for all $x$, namely:
 %
@@
 to meet the specification.  This witness $x$ is added to the {\sc inputs}
-set, and the loop iterates again.  It is worth noting that each iteration of the
-loop adds a new input to the finite set $\text{\sc inputs}$  being used for synthesis.  If
-the full set of inputs \blue{[which by now should have a name, as suggested to be introduced above]} is finite, this means that the refinement loop
-can only iterate a finite number of times.
+set, and the loop iterates again.  It is worth noting that each iteration of
+the loop adds a new input to the finite set $\text{\sc inputs}$ being used
+for synthesis.  If the full set of inputs \blue{[which by now should have a
+name, as suggested to be introduced above]} is finite, this means that the
+refinement loop can only iterate a finite number of times.
 
 \paragraph{Synthesis elements specific to control systems}
-Next, we describe the specific property that we pass to the 
-program synthesiser as the specification $\sigma$.
-There are two different algorithms in DSVerifier that can be used for
-stability verification~\cite{DBLP:journals/dafes/BessaICF16}, 
-one based on Schur's decomposition and another one based on 
-Jury's criteria~\cite{astrom1997computer}.
-Here, we choose Jury's method~\cite{astrom1997computer}, due to its efficiency.
+
+Next, we describe the specific property that we pass to the program
+synthesiser as the specification $\sigma$.  There are two different
+algorithms in DSVerifier that can be used for stability
+verification~\cite{DBLP:journals/dafes/BessaICF16}, one based on Schur's
+decomposition and another one based on Jury's
+criteria~\cite{astrom1997computer}.  Here, we choose Jury's
+method~\cite{astrom1997computer}, due to its efficiency.
 
@@
 
-This section is split into three parts. Section~\ref{experimental-setup} discusses 
-the experimental setup and the employed benchmarks, while Section~\ref{experimental-objectives} 
-describes the experimental objectives. Section~\ref{experimental-results} describes the experimental 
-results related to the application of CEGIS to the standard closed-loop control system benchmarks 
-described in Section~\ref{experimental-setup}.
+This section is split into three parts. Section~\ref{experimental-setup}
+discusses the experimental setup and the employed benchmarks, while
+Section~\ref{experimental-objectives} describes the experimental objectives. 
+Section~\ref{experimental-results} describes the experimental results
+related to the application of CEGIS to the standard closed-loop control
+system benchmarks described in Section~\ref{experimental-setup}.
 
@@
 
-A third set of benchmarks that consists of digital controllers for satellite applications
-is considered~\cite{Franklin15}, in order to evaluate the present approach full capabilities.
-In particular, satellites often require attitude (pose) control for proper orientation 
-of antennas and sensors w.r.t. earth. The satellite attitude control is typically used 
-for three-axis attitude tracking, but here only one axis at a time is considered. 
-The motion equation for the one-axis system, despising disturbance torques, is given by:
+A third set of benchmarks that consists of digital controllers for satellite
+applications is considered~\cite{Franklin15}, in order to evaluate the
+present approach full capabilities.  In particular, satellites often require
+attitude (pose) control for proper orientation of antennas and sensors
+w.r.t.  earth.  The satellite attitude control is typically used for
+three-axis attitude tracking, but here only one axis at a time is
+considered.  The motion equation for the one-axis system, despising
+disturbance torques, is given by:
 %
@@
 more recent Linear Quadratic Regulator (LQR)~\cite{bemporad2002explicit}
-have been used in several studies with increasing degrees of succes to ensure
-stability.  The latter approach highlights the importance of conserving
-energy during the control process, which results in lower running costs.  
-Since real systems are subject to tolerance and noise
-as well as the need for economy, more recent studies focus on the problems of
-achieving robust stability with minimum
+have been used in several studies with increasing degrees of succes to
+ensure stability.  The latter approach highlights the importance of
+conserving energy during the control process, which results in lower running
+costs.  Since real systems are subject to tolerance and noise as well as the
+need for economy, more recent studies focus on the problems of achieving
+robust stability with minimum
 gain~\cite{schmid2014unified,konigorski2012pole}.  However, when extending
@@
 
-Researchers in formal verification of control systems have studied
-various effects of discretising the dynamics, including delayed
+Researchers in formal verification of control systems have studied various
+effects of discretising the dynamics, including delayed
 response~\cite{Duggirala2015}, and Finite Word Length (FWL) constraints with
-the goal to either verify ({\it e.g.},  \cite{daes20161}) or optimise
-({\it e.g.},~\cite{oudjida2014design}) implementations.  There are in fact two
+the goal to either verify ({\it e.g.}, \cite{daes20161}) or optimise ({\it
+e.g.},~\cite{oudjida2014design}) implementations.  There are in fact two
 different problems arising from FWL effects.  The first corresponds to the
@@
 directly model the digital controller so that the selected parameters are
-stable by design.  Most studies following this verification research field focus on
-finding a correct implementation of a known desired controller, looking for
-optimal parameter representations using FWL, but ignoring the effects of
-rounding errors due to issues of mathematical tractability.  The analyses
-in~\cite{DBLP:conf/hybrid/WangGRJF16,DBLP:conf/hybrid/RouxJG15} rely on an
-invariant computation on the discrete system dynamics using Semi-Definite
-Pogramming (SDP).  Whilst the former uses BIBO properties to determine
-stability, the latter uses Lyapunov-based quadratic invariants.  In both
-cases, the SDP solver uses floating-point arithmetic and soundness is checked
-by upper bounding the error.
-An alternative approach is taken by \cite{park2016scalable}, where the verification of existing
-code is performed against a known model by extracting an LTI model of the
-code through symbolic execution. In order to account for rounding errors, an
-upper bound is introduced in the verification phase. If the error of the implementation
-is lower than this tolerance level, then the verification is successful.
+stable by design.  Most studies following this verification research field
+focus on finding a correct implementation of a known desired controller,
+looking for optimal parameter representations using FWL, but ignoring the
+effects of rounding errors due to issues of mathematical tractability.  The
+analyses in~\cite{DBLP:conf/hybrid/WangGRJF16,DBLP:conf/hybrid/RouxJG15}
+rely on an invariant computation on the discrete system dynamics using
+Semi-Definite Pogramming (SDP).  Whilst the former uses BIBO properties to
+determine stability, the latter uses Lyapunov-based quadratic invariants. 
+In both cases, the SDP solver uses floating-point arithmetic and soundness
+is checked by upper bounding the error.  An alternative approach is taken by
+\cite{park2016scalable}, where the verification of existing code is
+performed against a known model by extracting an LTI model of the code
+through symbolic execution.  In order to account for rounding errors, an
+upper bound is introduced in the verification phase.  If the error of the
+implementation is lower than this tolerance level, then the verification is
+successful.
 
@@
 existing study on the automatic synthesis of fixed-point digital controllers
-considering FWL effects.  Parameter synthesis tools such as~\cite{cimatti2013parameter} 
-use bounded model checking and fixed-point computations to find parameters based on user
-defined specifications, but they often operate in the continuous domain and
-are ill-suited for robust analysis since they have no direct means of
-evaluating robustness.  Other tools such as~\cite{economakos2016automated}
-are directly aimed at robust stability problems, but they fail to explore the
-effects of FWL in their implementation.  In order to provide a correct by
-design digital controller, \cite{alur2016compositional} requires a user-defined
-finite state abstraction to synthesise a digital controller based on high
-level specifications.  Whilst this approach directly overcomes the
-challenges presented by the FWL problem, it still requires error-prone user
+considering FWL effects.  Parameter synthesis tools such
+as~\cite{cimatti2013parameter} use bounded model checking and fixed-point
+computations to find parameters based on user defined specifications, but
+they often operate in the continuous domain and are ill-suited for robust
+analysis since they have no direct means of evaluating robustness.  Other
+tools such as~\cite{economakos2016automated} are directly aimed at robust
+stability problems, but they fail to explore the effects of FWL in their
+implementation.  In order to provide a correct by design digital controller,
+\cite{alur2016compositional} requires a user-defined finite state
+abstraction to synthesise a digital controller based on high level
+specifications.  Whilst this approach directly overcomes the challenges
+presented by the FWL problem, it still requires error-prone user
 intervention.  A different solution that looks at the other end of the scale
@@
 stability measures for LTI SISO controllers.  We take the former
-from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from \cite{daes20161} whilst enhancing the
-procedure by evaluating the quantaization effects of the Hardware interfaces
-(ADC/DAC) to obtain an accurate discrete time FWL representation of the
-continuous dynamics.
+from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from~\cite{daes20161}
+whilst enhancing the procedure by evaluating the quantaization effects of
+the Hardware interfaces (ADC/DAC) to obtain an accurate discrete time FWL
+representation of the continuous dynamics.
 

### 2016-10-08 paper/paper.tex
more prog synthesis comments implemented

--- 2016-10-08 paper/paper.tex
@@
 %
-\red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
-(Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
-% 
+%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
+%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
+% 
+The input specification provided to the program synthesiser is of the form
+$\exists \vec{P} . \forall \vec{x} \in \text{\sc inputs} . \sigma(\vec{x}, \vec{P})$
+where $\vec{P}$ ranges over functions, $\vec{x}$ ranges over
+ground terms and $\sigma$ is a quantifier-free formula.
+We interpret the gound terms over some finite domain $\mathcal{D}$.
+
 The design of our synthesiser is given in
@@
 that is updated incrementally.
-Given a specification $\sigma$ over variables $x$
-and $P$, the {\sc synth} procedure tries to find an existential witness $P$
-that satisfies the specification $\sigma(x, P)$ for all $x$, namely:
-%
-$\exists P . \forall x \in \text{\sc inputs} . \sigma(x, P)$
-
+Given the aforementioned specification $\sigma$, the {\sc synth} procedure 
+tries to find an existential witness $P$
+that satisfies the specification $\sigma(x, P)$ for all $x$.
+%
 If {\sc synthesise} succeeds in finding a witness $P$, this witness is a
@@
 set, and the loop iterates again.  It is worth noting that each iteration of the
-loop adds a new input to the finite set $\text{\sc inputs}$  being used for synthesis.  If
-the full set of inputs \blue{[which by now should have a name, as suggested to be introduced above]} is finite, this means that the refinement loop
+loop adds a new input to the finite set $\text{\sc inputs}$  being used for synthesis.  
+Given that the full set of inputs $\mathcal{D}$ 
+%\blue{[which by now should have a name, as suggested to be introduced above]} 
+is finite, this means that the refinement loop
 can only iterate a finite number of times.
@@
 $$
-\blue{[Nice, now I'm in the groove. Next unfolds well.] }
+%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
 After adding this new counterexample to the set of {\sc inputs}, in the 

### 2016-10-08 paper/paper.tex
fix manual merge

--- 2016-10-08 paper/paper.tex
@@
 %    
-\begin{figure}[ht]
+\begin{figure*}[ht]
 \centering
@@
 
-\resizebox{.5\textwidth}{!}{
- \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
+\resizebox{.8\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
      semithick, initial text=, ampersand replacement=\&,]
@@
  \caption{Sampled System. \label{fig:sampledsystem}}
-\end{figure}
+\end{figure*}
 
@@
 %
-\red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
-(Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
-% 
-The design of our synthesiser is given in Fig.~\ref{fig:CEGIS} and consists
-of two phases, {\sc Synthesise} and {\sc Verify}, which interact via a
-finite set of test vectors {\sc inputs} that is updated incrementally. 
-Given a specification $\sigma$ over variables $x$ and $P$, the {\sc synth}
-procedure tries to find an existential witness $P$ that satisfies the
-specification $\sigma(x, P)$ for all $x$, namely:
-%
-$\exists P . \forall x \in \text{\sc inputs} . \sigma(x, P)$
-
+%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
+%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
+% 
+The input specification provided to the program synthesiser is of the form
+$\exists \vec{P} . \forall \vec{x} \in \text{\sc inputs} . \sigma(\vec{x}, \vec{P})$
+where $\vec{P}$ ranges over functions, $\vec{x}$ ranges over
+ground terms and $\sigma$ is a quantifier-free formula.
+We interpret the gound terms over some finite domain $\mathcal{D}$.
+
+The design of our synthesiser is given in
+Fig.~\ref{fig:CEGIS} and consists of two phases, {\sc
+Synthesise} and {\sc Verify}, which interact via a finite set of test vectors {\sc inputs} 
+that is updated incrementally.
+Given the aforementioned specification $\sigma$, the {\sc synth} procedure 
+tries to find an existential witness $P$
+that satisfies the specification $\sigma(x, P)$ for all $x$.
+%
 If {\sc synthesise} succeeds in finding a witness $P$, this witness is a
@@
 to meet the specification.  This witness $x$ is added to the {\sc inputs}
-set, and the loop iterates again.  It is worth noting that each iteration of
-the loop adds a new input to the finite set $\text{\sc inputs}$ being used
-for synthesis.  If the full set of inputs \blue{[which by now should have a
-name, as suggested to be introduced above]} is finite, this means that the
-refinement loop can only iterate a finite number of times.
+set, and the loop iterates again.  It is worth noting that each iteration of the
+loop adds a new input to the finite set $\text{\sc inputs}$  being used for synthesis.  
+Given that the full set of inputs $\mathcal{D}$ 
+%\blue{[which by now should have a name, as suggested to be introduced above]} 
+is finite, this means that the refinement loop
+can only iterate a finite number of times.
 

### 2016-10-08 paper/paper.tex
New figures

--- 2016-10-08 paper/paper.tex
@@
 for {\em hybrid closed-loop systems}, {\it i.e.}, embedded controllers along with a model of their
-physical environment (the plant), which are {\em stable}.  Due to the complexity
+physical environment, the plant, as shown in
+Fig.~\ref{fig:closed-system}, that are {\em stable}.  Due to the complexity
 of such systems, we focus on linear models with known configurations
@@
 
-%\begin{figure}
-%\centering
-%\resizebox{.35\textwidth}{!}{
-% \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
-%     semithick, initial text=, ampersand replacement=\&,]
-
-%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.5cm, column sep=.5cm] {
-%   \coordinate (aux0);
-%   \& \node[circle] (circle) {}; 
-%   \& \node[fill=yellow!20] (da) {{\sc D/A}}; 
-%   \& \node[fill=yellow!20] (p) {{\sc P}};
-%   \& \node[fill=yellow!20] (ad) {{\sc A/D}}; 
-%   \& \coordinate (aux1);\\
-%   \& \coordinate (aux3); 
-%   \&
-%   \&
-%   \node[fill=yellow!20] (c) {C};
-%   \& 
-%   \& \coordinate (aux2);\\
-%  };
-
-%  \path[->] (aux0) edge (circle.west);
-%  \path  
-%   (circle.east) edge (da.west)
-%   (da.east) edge (p.west)
-%   (p.east) edge (ad.west)
-%   (ad.east) edge (aux1.west)
-%   (aux1.south) edge (aux2.north)
-%   (aux2.west) edge (c.east)
-%   (c.west) edge (aux3.east); 
-%  \path[->]  (aux3.north) edge (circle.south);
-% \end{tikzpicture}
-%}
-% \caption{Closed-Loop System. \label{fig:closed-system}}
-%\end{figure}
+\begin{figure}
+\centering
+\resizebox{.35\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
+     semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.5cm, column sep=.5cm] {
+   \coordinate (aux0);
+   \& \node[circle] (circle) {}; 
+   \& \node[fill=yellow!20] (da) {{\sc D/A}}; 
+   \& \node[fill=yellow!20] (p) {{\sc P}};
+   \& \node[fill=yellow!20] (ad) {{\sc A/D}}; 
+   \& \coordinate (aux1);\\
+   \& \coordinate (aux3); 
+   \&
+   \&
+   \node[fill=yellow!20] (c) {C};
+   \& 
+   \& \coordinate (aux2);\\
+  };
+
+  \path[->] (aux0) edge (circle.west);
+  \path  
+   (circle.east) edge (da.west)
+   (da.east) edge (p.west)
+   (p.east) edge (ad.west)
+   (ad.east) edge (aux1.west)
+   (aux1.south) edge (aux2.north)
+   (aux2.west) edge (c.east)
+   (c.west) edge (aux3.east); 
+  \path[->]  (aux3.north) edge (circle.south);
+ \end{tikzpicture}
+}
+ \caption{Closed-Loop System. \label{fig:closed-system}}
+\end{figure}
 
@@
 on the polynomial coefficients, following Jury's Criteria, as well as the restrictions
-set in the representation of these coefficients by the function $f$ (cf. Eq. \eqref{FWL_tf}).
+set in the representation of these coefficients by the function $f$ (Eq. \ref{FWL_tf}).
 
@@
 
+\begin{figure}[ht]
+\centering
+
+\tikzset{add/.style n args={4}{
+    minimum width=6mm,
+    path picture={
+        \draw[circle] 
+            (path picture bounding box.south east) -- (path picture bounding box.north west)
+            (path picture bounding box.south west) -- (path picture bounding box.north east);
+        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+        }
+    }
+ }
+
+\resizebox{.5\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
+     semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
+    \node[draw=none] (r) {$R(z)$};
+%   \& \coordinate (aux0);
+   \& \node[circle,add={-}{+}{}{}] (circle) {};
+   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Controller}] (cz) {{\sc C(z)}};
+   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Plant}] (gs) {{\sc G(z)}};
+   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
+
+   \& \node[circle,add={}{+}{+}{}] (circle2) {};
+%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
+   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
+   \& \coordinate (aux1);
+   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
+   \& \coordinate (aux3); 
+   \&
+   \& 
+   \& 
+   \& \coordinate (aux2);\\
+  };
+
+%  \path[->] (v1) edge (q1.north);
+%  \path[->] (v2) edge (q2.north);
+  \path[->] (r) edge (circle.west);
+  \path[->] (nu) edge (circle2.north);
+  \path[->] (aux1) edge (yz);
+  \path  
+   (circle.east) edge (cz)
+   (cz.east) edge (gs.west)
+   (gs.east) edge (circle2.west)
+   (circle2.east) edge (aux1.west)
+   (aux1.south) edge (aux2.north)
+   (aux2.west) edge (aux3.east); 
+  \path[->]  (aux3.north) edge (circle.south);
+ \end{tikzpicture}
+}
+ \caption{Sampled System. \label{fig:sampledsystem}}
+\end{figure}
+
+%
+%
+
+\begin{figure}[ht]
+\centering
+
+\tikzset{add/.style n args={4}{
+    minimum width=6mm,
+    path picture={
+        \draw[circle] 
+            (path picture bounding box.south east) -- (path picture bounding box.north west)
+            (path picture bounding box.south west) -- (path picture bounding box.north east);
+        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+        }
+    }
+ }
+
+\resizebox{.5\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
+     semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
+    \node[draw=none] (r) {$R(z)$};
+%   \& \coordinate (aux0);
+   \& \node[circle,add={-}{+}{}{}] (circle) {};
+   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
+   \& \coordinate (aux4);
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Controller}] (cz) {{\sc C(z)}};
+   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Plant}] (gs) {{\sc G(z)}};
+   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
+   \& \node[circle,add={+}{+}{}{}] (circle2) {};
+%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
+%   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
+   \& \coordinate (aux1);
+   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
+   \& 
+   \& \coordinate (aux5); 
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm] (deltag) {{\sc $\Delta G(z)$}};
+   \&
+   \& \coordinate (aux6);\\
+   \& \coordinate (aux3); 
+   \&
+   \& 
+   \& 
+   \&
+   \& \coordinate (aux2);\\
+  };
+
+%  \path[->] (v1) edge (q1.north);
+%  \path[->] (v2) edge (q2.north);
+  \path[->] (r) edge (circle.west);
+%  \path[->] (nu) edge (circle2.north);
+  \path[->] (aux1) edge (yz);
+  \path  
+   (aux4.north) edge (aux5.south)
+   (aux5.east) edge (deltag.west)
+   (deltag.east) edge (aux6.west)
+   (aux6.south) edge (circle2.south)
+   (circle.east) edge (cz)
+   (cz.east) edge (gs.west)
+   (gs.east) edge (circle2.west)
+   (circle2.east) edge (aux1.west)
+   (aux1.south) edge (aux2.north)
+   (aux2.west) edge (aux3.east); 
+  \path[->]  (aux3.north) edge (circle.south);
+ \end{tikzpicture}
+}
+ \caption{Sampled System. \label{fig:sampledsystem}}
+\end{figure}
+
 First, some assumptions have to be established to obtain a model for the quantization effects (seen as noise) on the closed loop system. 
@@
 %
-%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
-%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
-% 
-The input specification provided to the program synthesiser is of the form
-$\exists \vec{P} . \forall \vec{x} \in \text{\sc inputs} . \sigma(\vec{x}, \vec{P})$
-where $\vec{P}$ ranges over functions, $\vec{x}$ ranges over
-ground terms and $\sigma$ is a quantifier-free formula.
-We interpret the gound terms over some finite domain $\mathcal{D}$.
-
+\red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
+(Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
+% 
 The design of our synthesiser is given in
 Fig.~\ref{fig:CEGIS} and consists of two phases, {\sc
-Synthesise} and {\sc Verify}, which interact via a finite set of test vectors {\sc inputs} 
-that is updated incrementally.
-Given the aforementioned specification $\sigma$, the {\sc synth} procedure 
-tries to find an existential witness $P$
-that satisfies the specification $\sigma(x, P)$ for all $x$.
-%
+Synthesise} and {\sc Verify}, which interact via a finite set of test vectors {\sc inputs} \blue{that is updated incrementally}.
+The {\sc synth} procedure tries to find an existential witness $P$
+that satisfies the specification $\sigma(x, P)$ for all $x$, namely:
+%
+$\exists P . \forall x \in \text{\sc inputs} . \sigma(x, P)$
+
 If {\sc synthesise} succeeds in finding a witness $P$, this witness is a
@@
 set, and the loop iterates again.  It is worth noting that each iteration of the
-loop adds a new input to the finite set $\text{\sc inputs}$  being used for synthesis.  
-Given that the full set of inputs $\mathcal{D}$ 
-%\blue{[which by now should have a name, as suggested to be introduced above]} 
-is finite, this means that the refinement loop
+loop adds a new input to the \red{finite} set $\text{\sc inputs}$  being used for synthesis.  If
+the full set of inputs \blue{[which by now should have a name, as suggested to be introduced above]} is finite, this means that the refinement loop
 can only iterate a finite number of times.
@@
 We use this method to check the stability in the $z$-domain for the characteristic polynomial $S(z)$ of 
-the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$, where $Y(z)$ is the 
-closed-loop system output and U(z) is the controller output. 
-%% \red{[unclear: what matrix?
+the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$ \red{[unclear: what matrix?
 We need to clarify the relationship between the char.
@@
 $S(z)$ and the later quantities $\Delta N_{G}(z), \Delta D_{G}(z)$ and corresponding controller's structure.]}.
-%
 We consider the following form for $S(z)$:
@@
 %\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?}
-
-Assuming that $\hat{G}(z) = \frac{\hat{N_G}(z)}{\hat{D_G}(z)}$
-and $\hat{C}(z) = \frac{\hat{N_C}(z)}{\hat{D_C}(z)}$, then:
-$$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$
 
@@
 then we obtain a counterexample denoted by 
-values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
-%\red{[see my comment above - these quantities pop up too abruptly.]},
-which make the closed-loop system unstable. 
-Note that, similar to the rest of the paper, we use the notation 
-$\hat{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
-$\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
-This uncertainty is added to 
+values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$ \red{[see my comment above - these quantities pop up too abruptly.]},
+which make the closed-loop system unstable. This uncertainty is added to 
 the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
@@
 in Sec.~\ref{sec:running-ex}.
-We start with a candidate solution that has all coefficients 0:
-%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
-
-$$
-\begin{array}{ll}
-N_C(z) {=} 0z^2{+}0z{+}0\\
-D_C(z) {=} 0z^2{+}0z{+}0\\
-\end{array}
-$$
-
+We start with a candidate solution that has all coefficients 0 \red{[Be more explicit, write out spurious candidate solution with zero coefficients.
+KISS - you don't want to lose the control audience here.]}.
 In the first {\sc verify} phase we obtain the following counterexample:
@@
 $$
-%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
+\blue{[Nice, now I'm in the groove. Next unfolds well.] }
 After adding this new counterexample to the set of {\sc inputs}, in the 

### 2016-10-08 paper/paper.tex
use vectors for vars in sigma

--- 2016-10-08 paper/paper.tex
@@
 
-In order to synthesise closed-loop digital control systems, we use a program
-synthesis engine.  Nowadays, such engines are used increasingly often in
-program verification~\cite{DBLP:conf/lpar/DavidKL15,DBLP:conf/cav/0001A14}. 
+In order to synthesise closed-loop digital control systems, we use a
+program synthesis engine.  Nowadays, such engines are used
+increasingly often in program
+verification~\cite{DBLP:conf/lpar/DavidKL15,DBLP:conf/cav/0001A14}.
 Our program synthesiser makes use of Counter-Example Guided Inductive
@@
 % 
-The input specification provided to the program synthesiser is of the form
-$\exists \vec{P} . \forall \vec{x} \in \text{\sc inputs} . \sigma(\vec{x}, \vec{P})$
-where $\vec{P}$ ranges over functions, $\vec{x}$ ranges over
-ground terms and $\sigma$ is a quantifier-free formula.
-We interpret the gound terms over some finite domain $\mathcal{D}$.
-
-The design of our synthesiser is given in
-Fig.~\ref{fig:CEGIS} and consists of two phases, {\sc
-Synthesise} and {\sc Verify}, which interact via a finite set of test vectors {\sc inputs} 
-that is updated incrementally.
-Given the aforementioned specification $\sigma$, the {\sc synth} procedure 
-tries to find an existential witness $P$
-that satisfies the specification $\sigma(x, P)$ for all $x$.
-%
-If {\sc synthesise} succeeds in finding a witness $P$, this witness is a
-candidate solution to the full synthesis formula.  We pass this candidate
-solution to {\sc verify}, which determines whether it does satisfy
-the specification on all inputs by checking satisfiability of the following 
-verification formula:
-%
-$\exists x . \lnot \sigma(x, P)$
+The input specification provided to the program synthesiser is of the
+form $\exists \vec{P} . \forall \vec{x} \in \text{\sc inputs}
+. \sigma(\vec{x}, \vec{P})$ where $\vec{P}$ ranges over functions,
+$\vec{x}$ ranges over ground terms and $\sigma$ is a quantifier-free
+formula.  We interpret the gound terms over some finite domain
+$\mathcal{D}$.
+
+The design of our synthesiser is given in Fig.~\ref{fig:CEGIS} and
+consists of two phases, {\sc Synthesise} and {\sc Verify}, which
+interact via a finite set of test vectors {\sc inputs} that is updated
+incrementally.  Given the aforementioned specification $\sigma$, the
+{\sc synth} procedure tries to find an existential witness $\vec{P}$
+satisfying the specification $\sigma(\vec{x}, \vec{P})$ for all
+$\vec{x}$.
+%
+If {\sc synthesise} succeeds in finding an witness $\vec{P}$, this
+witness is a candidate solution to the full synthesis formula.  We
+pass this candidate solution to {\sc verify}, which determines whether
+it does satisfy the specification on all inputs by checking
+satisfiability of the following verification formula:
+%
+$\exists \vec{x} . \lnot \sigma(\vec{x}, \vec{P})$
 
@@
 solution to the synthesis formula and so the algorithm terminates.
-Otherwise, the witness $x$ is an input on which the candidate solution fails
-to meet the specification.  This witness $x$ is added to the {\sc inputs}
-set, and the loop iterates again.  It is worth noting that each iteration of the
-loop adds a new input to the finite set $\text{\sc inputs}$  being used for synthesis.  
-Given that the full set of inputs $\mathcal{D}$ 
+Otherwise, the witness $\vec{x}$ denote an input on which the
+candidate solution fails to meet the specification.  Thus, $\vec{x}$ is
+added to the {\sc inputs} set, and the loop iterates again.  It is
+worth noting that each iteration of the loop adds a new input to the
+finite set $\text{\sc inputs}$ being used for synthesis.  Given that
+the full set of inputs $\mathcal{D}$
 %\blue{[which by now should have a name, as suggested to be introduced above]} 
@@
 algorithms in DSVerifier that can be used for stability
-verification~\cite{DBLP:journals/dafes/BessaICF16}, one based on Schur's
-decomposition and another one based on Jury's
+verification~\cite{DBLP:journals/dafes/BessaICF16}, one based on
+Schur's decomposition and another one based on Jury's
 criteria~\cite{astrom1997computer}.  Here, we choose Jury's
@@
 closed-loop system output and U(z) is the controller output. 
-%% \red{[unclear: what matrix?
-We need to clarify the relationship between the char.
-poly.
-$S(z)$ and the later quantities $\Delta N_{G}(z), \Delta D_{G}(z)$ and corresponding controller's structure.]}.
+%% \red{[unclear: what matrix? We need to clarify the relationship
+%% between the char. poly. $S(z)$ and the later quantities $\Delta
+%% N_{G}(z), \Delta D_{G}(z)$ and corresponding controller's
+%% structure.]}.
 %

### 2016-10-08 paper/paper.tex
minor changes

@@
 
+\begin{figure}[ht]
+\centering
+
+\tikzset{add/.style n args={4}{
+    minimum width=6mm,
+    path picture={
+        \draw[circle] 
+            (path picture bounding box.south east) -- (path picture bounding box.north west)
+            (path picture bounding box.south west) -- (path picture bounding box.north east);
+        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+        }
+    }
+ }
+
+\resizebox{.5\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
+     semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
+    \node[draw=none] (r) {$R(z)$};
+%   \& \coordinate (aux0);
+   \& \node[circle,add={-}{+}{}{}] (circle) {};
+   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Controller}] (cz) {{\sc C(z)}};
+   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Plant}] (gs) {{\sc G(z)}};
+   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
+
+   \& \node[circle,add={}{+}{+}{}] (circle2) {};
+%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
+   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
+   \& \coordinate (aux1);
+   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
+   \& \coordinate (aux3); 
+   \&
+   \& 
+   \& 
+   \& \coordinate (aux2);\\
+  };
+
+%  \path[->] (v1) edge (q1.north);
+%  \path[->] (v2) edge (q2.north);
+  \path[->] (r) edge (circle.west);
+  \path[->] (nu) edge (circle2.north);
+  \path[->] (aux1) edge (yz);
+  \path  
+   (circle.east) edge (cz)
+   (cz.east) edge (gs.west)
+   (gs.east) edge (circle2.west)
+   (circle2.east) edge (aux1.west)
+   (aux1.south) edge (aux2.north)
+   (aux2.west) edge (aux3.east); 
+  \path[->]  (aux3.north) edge (circle.south);
+ \end{tikzpicture}
+}
+ \caption{Sampled System. \label{fig:sampledsystem}}
+\end{figure}
+
+%
+%
+
+\begin{figure}[ht]
+\centering
+
+\tikzset{add/.style n args={4}{
+    minimum width=6mm,
+    path picture={
+        \draw[circle] 
+            (path picture bounding box.south east) -- (path picture bounding box.north west)
+            (path picture bounding box.south west) -- (path picture bounding box.north east);
+        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+        }
+    }
+ }
+
+\resizebox{.5\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
+     semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
+    \node[draw=none] (r) {$R(z)$};
+%   \& \coordinate (aux0);
+   \& \node[circle,add={-}{+}{}{}] (circle) {};
+   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
+   \& \coordinate (aux4);
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Controller}] (cz) {{\sc C(z)}};
+   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Plant}] (gs) {{\sc G(z)}};
+   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
+   \& \node[circle,add={+}{+}{}{}] (circle2) {};
+%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
+%   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
+   \& \coordinate (aux1);
+   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
+   \& 
+   \& \coordinate (aux5); 
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm] (deltag) {{\sc $\Delta G(z)$}};
+   \&
+   \& \coordinate (aux6);\\
+   \& \coordinate (aux3); 
+   \&
+   \& 
+   \& 
+   \&
+   \& \coordinate (aux2);\\
+  };
+
+%  \path[->] (v1) edge (q1.north);
+%  \path[->] (v2) edge (q2.north);
+  \path[->] (r) edge (circle.west);
+%  \path[->] (nu) edge (circle2.north);
+  \path[->] (aux1) edge (yz);
+  \path  
+   (aux4.north) edge (aux5.south)
+   (aux5.east) edge (deltag.west)
+   (deltag.east) edge (aux6.west)
+   (aux6.south) edge (circle2.south)
+   (circle.east) edge (cz)
+   (cz.east) edge (gs.west)
+   (gs.east) edge (circle2.west)
+   (circle2.east) edge (aux1.west)
+   (aux1.south) edge (aux2.north)
+   (aux2.west) edge (aux3.east); 
+  \path[->]  (aux3.north) edge (circle.south);
+ \end{tikzpicture}
+}
+ \caption{Sampled System. \label{fig:sampledsystem}}
+\end{figure}
+
 First, some assumptions have to be established to obtain a model for the

### 2016-10-08 paper/paper.tex
citation for the design of the digital controller candidate solution + typo

@@
 in Sec.~\ref{sec:running-ex}.
-We start with a candidate solution that has all coefficients 0:
+We start with the candidate solution given below, which has all coefficients 0.
+Note that the digital controller is designed with typical control system
+techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
 %\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
@@
 We add this counterexample to {\sc inputs} and initiate the {\sc synthesise} phase, where we get the following candidate solution: 
-\red{[ How is the order of the candidate solution chosen here?]}
+%\red{[ How is the order of the candidate solution chosen here?]}
 $$

### 2016-10-08 paper/paper.tex
mapping between the stability property and the general spec sigma

@@
 %\cdsay{figure out what is existentially quantified for the final $\sigma$.} 
-\red{[Yes, intuitively all clear, however for the sake of clarity I would like to see the explicit mapping between the above formula and the previously used specification 
-$\sigma(x, P)$, with clear elucidation of the relationship between the domain of $z$ and that of $x$.]}
+%% \red{[Yes, intuitively all clear, however for the sake of clarity I would like to see the explicit mapping between the above formula and the previously used specification 
+%% $\sigma(x, P)$, with clear elucidation of the relationship between the domain of $z$ and that of $x$.]}
+
+Essentially, the synthesis problem we are trying to solve is the following:
+find a digital controller denoted by  $N_c$ and $D_c$ that
+makes the closed-loop system stable 
+for all possible uncertainties $(\Delta N_G, \Delta D_G)$. 
+When mapping back to the notation used for describing the general architecture 
+of the program synthesiser, the controller $(N_c,D_c)$ denotes $P$ and 
+the uncertainty $(\Delta N_G, \Delta D_G)$ represents $x$.
+
+\red{[clear elucidation of the domain]}
 

### 2016-10-08 paper/paper.tex
small fix
fix + TODO

@@
 for all possible uncertainties $(\Delta N_G, \Delta D_G)$. 
-When mapping back to the notation used for describing the general architecture 
-of the program synthesiser, the controller $(N_c,D_c)$ denotes $P$ and 
-the uncertainty $(\Delta N_G, \Delta D_G)$ represents $x$.
-
-\red{[clear elucidation of the domain]}
+Note that, similar to the rest of the paper, we use the notation 
+$\hat{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
+$\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
+%% When mapping back to the notation used for describing the general architecture 
+%% of the program synthesiser, the controller $(N_c,D_c)$ denotes $P$ and 
+%% $z$ represents $x$.
+
+\red{[clear elucidation here of the mapping between this and the notation used 
+for the general description of the synthesiser]}
 
@@
 which make the closed-loop system unstable. 
-Note that, similar to the rest of the paper, we use the notation 
-$\hat{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
-$\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
 This uncertainty is added to 

### 2016-10-08 paper/paper.tex
fix
adjusted todo

--- 2016-10-08 paper/paper.tex
@@
 for all possible uncertainties $(\Delta N_G, \Delta D_G)$. 
+Note that, similar to the rest of the paper, we use the notation 
+$\hat{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
+$\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
 When mapping back to the notation used for describing the general architecture 
 of the program synthesiser, the controller $(N_c,D_c)$ denotes $P$ and 
-the uncertainty $(\Delta N_G, \Delta D_G)$ represents $x$.
-
-\red{[clear elucidation of the domain]}
+$(\Delta N_G, \Delta D_G)$ represents $x$.
+
+\red{[clear elucidation of the mapping between this and the domains used 
+in the general description of the synthesiser]}
 

### 2016-10-08 paper/paper.tex
hscc17

@@
 
-\red{Alessandro, I've made the changes as requested. Please let me know if this is good enough or if I made it too short}
+%\red{Alessandro, I've made the changes as requested. Please let me know if this is good enough or if I made it too short}
 
@@
 %
-\noindent where $\beta$ and $\alpha$ are the controller's coefficients, $b$
-and $a$ are the plant's coefficients, and $N$ and $M$ are the number of
-poles and zeros for the corresponding block.
+\noindent where $\beta$ and $\alpha$ are vectors containing the controller's coefficients;  
+similarly $b$ and $a$ encompas the plant's coefficients;  
+and $N_{(\cdot)}$ and $M_{(\cdot)}$ denote the number of poles and zeros for the corresponding block.
 
@@
 discretization is more suitable for representing the sampling and holding
-processes that are typically employed by hybrid
-systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretization
+processes that are typically employed in complex systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretization
 models the exact effect of sampling and DAC interpolation over the plant.
@@
 %
-For convenience, we will use only the notation $G(z)$ to represent the pulse
-transfer function.
+For the sake of brevity, 
+we will use only the notation $G(z)$ to represent the pulse transfer function.
 %

### 2016-10-08 paper/paper.tex
hscc17

@@
 
-Since $G(z)$ is an approximation of $G(s)$ we denote the error in the
+Since $G(z)$ is an approximation of $G(s)$ \red{we denote [AA: why `denote'? Shouldn't we prove that we go from the $G(s)$ TF to the $G(z,T)$ form above?]} the error in the
 approximation for time $t \neq kT$ as $\Delta{G}_P$
@@
 percentage such that $\hat{G}(z)$ corresponds to the polynomial set of
-possible values of $G(z, T): \forall T \in \mathbb{R}$
+possible values of $G(z, T): \forall T \in \mathbb{R}$. 
+\red{[The previous statement is confusing and I must disagree here: I want hard error bounds on a specific value of T.]}
 
 Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
-using a Fixed Point Finite Word Length with integer size $I$ and fractional
-size $F$.  We shall denote this domain as $\mathbb{R}\langle I,F \rangle$
+using a Fixed-Point Finite Word Length with integer size $I$ and fractional
+size $F$.  We shall denote this domain as $\mathbb{R}\langle I,F \rangle$ and obtain 
 %
@@
 However, given a real plant and real controller $\hat{G}(z), \hat{C}(z)$, 
+\red{[the first line is not clear, there is in particular a function that is left undefined.]}
 %
@@
 \end{align}
-
-\vspace{1 mm} 
-\noindent where $\Delta{G}_Q(z)$ represents the plant uncertainty caused by
+\red{[please, how can you claim that the error enters as written? Can you show the derivation? Can you show a reference that has derived this form?]}
+where $\Delta{G}_Q(z)$ represents the plant uncertainty caused by
 the rounding off effect.  We may encompass all the uncertainty as
 $\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_Q(z)$.  Since this value is
-nondeterministic, the polynomial set of possible values of $\tilde G(z)$ is
+nondeterministic, the polynomial \red{[why polynomial?]} set of possible values of $\tilde G(z)$ is
 denoted by $\mathfrak{G}(z)$.
@@
 $Q2$) are energy bounded uncorrelated white noises.
-
-In~\cite{widrow1956}, Widrow models the quantization noise as a gaussian
+% 
+In particular, \cite{widrow1956} models the quantization noise as a gaussian
 model in which the second moment (variance) of the probability density
@@
 \end{equation}
-where $q$ is the step size of quantizer, thus supporting this assumption.
+where $q$ is the step size of quantizer. 
+%, thus supporting this assumption.
 \end{myassumption}
@@
 %analysis of the system in Figure~\ref{fig:sampledsystem}.
+
+\red{[The following text needs to be completed. (Notice typos, reference to wrong signal $R$, and to wrong TF $C,G$.]}
+
 Considering that
@@
 $\vec{x}$ ranges over ground terms and $\sigma$ is a quantifier-free
-formula.  We interpret the gound terms over some finite domain
+formula.  We interpret the ground terms over some finite domain
 $\mathcal{D}$.

### 2016-10-09 paper/paper.tex
Some fixes on Alessandro's comments

@@
 \end{mylemma}
-
-Since $G(z)$ is an approximation of $G(s)$ \red{we denote [AA: why `denote'? Shouldn't we prove that we go from the $G(s)$ TF to the $G(z,T)$ form above?]} the error in the
-approximation for time $t \neq kT$ as $\Delta{G}_P$
+Since $G(z)$ is an approximation of $G(s)$ we introduce an error term caused during its calculation as $\Delta{G}_P$
+
 %
@@
 Note that $\Delta{G}_P$ is undefined and upperbound by a user defined
-percentage such that $\hat{G}(z)$ corresponds to the polynomial set of
-possible values of $G(z, T): \forall T \in \mathbb{R}$. 
+value such that $\hat{G}(z)$ corresponds to the set of
+possible polynomial forms of $G(z, T)$ that overapproximate $G(s)$.
+This calculation is performed outside of the scope of this work since it depends on the nature of the tool used to obtain the $\mathcal{Z}$ form.
+The error comes from the bounded horizon and mathematical precision used to calculate the $\mathcal{Z}$ transform, which will be tool and user dependent.
 \red{[The previous statement is confusing and I must disagree here: I want hard error bounds on a specific value of T.]}
+\green{[You are correct.
+It was absolutely wrong.
+Hopefully this explanation is clear.
+We use MATLAB, but still don't know the details of their implementation, so I don't have hard data on how this error is calculated.}
 
@@
 %
-However, given a real plant and real controller $\hat{G}(z), \hat{C}(z)$, 
-\red{[the first line is not clear, there is in particular a function that is left undefined.]}
-%
+However, given a real plant and real controller $\hat{G}(z), \hat{C}(z)$, and a discretizing function
 \begin{align}
@@
 \label{FWL_tf}
-&\exists f (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I,F \rangle : \\
+&f (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I,F \rangle \triangleq \tilde x = x-(x\mod\tilde x)
+\end{align}
+we calculate $\tilde C(z)=f(\hat{C}(z))$ and $\tilde G(z)=f(\hat{G}(z))$
+\begin{align}
 \label{digital_controller_tf}
@@
 \end{align}
+where $\Delta_q\hat{c}_i=\hat{c}_i\mod \tilde{c}_i$
 \red{[please, how can you claim that the error enters as written? Can you show the derivation? Can you show a reference that has derived this form?]}
-where $\Delta{G}_Q(z)$ represents the plant uncertainty caused by
+\green{[the definition of f (now included) should explain it clearly]}
+and $\Delta{G}_Q(z)$ represents the plant uncertainty caused by
 the rounding off effect.  We may encompass all the uncertainty as
 $\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_Q(z)$.  Since this value is
-nondeterministic, the polynomial \red{[why polynomial?]} set of possible values of $\tilde G(z)$ is
+nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
 denoted by $\mathfrak{G}(z)$.
@@
 \resizebox{0.48\textwidth}{!}{
-$\hat{Y}(z)=\nu_{1}(z)C(z)G(z)+\nu_{2}(z)G(z)+R(z)C(z)G(z)-\hat{Y}(z)C(z)G(z),$
+$\tilde{Y}(z)=\tilde R(z)C(z)G(z)-\tilde{Y}(z)C(z)G(z)+\nu_{1}(z)+\nu_{2}(z)G(z),$
 }
@@
 \label{eq:outputfunctions}
-\hat{Y}(z)=H_{1}(z)\left(R(z)+\nu_{1}(z)\right)+H_{2}(z)\nu_{2}(z)
+\tilde{Y}(z)=C(z)G(z)H(z)R(z)+H(z)\nu_{1}(z)+G(z)H(z)\nu_{2}(z)
 \end{equation}
-$$H_{1}(z)=\frac{C(z)G(z)}{1+C(z)G(z)}$$
-$$H_{2}(z)=\frac{G(z)}{1+C(z)G(z)}$$
-
-In the case of stability properties we need to verify the stability of both $H_{1}(z)$ and $H_{2}(z)$ to validate the stability of the whole system.
+$$H(z)=\frac{1}{1+C(z)G(z)}$$
+
+Note that $H(z)$ cancels the poles of both $G(z)$ and $C(z)$, thus we need only verify the stability of $H(z)$
+to validate the stability of the whole system.
 %These equations are sufficient for computing $\sigma_{Q}^{2}$.  However,

### 2016-10-09 paper/paper.tex
Changes in Section 2

@@
 
+\textcolor{blue}{[IB: I'm proposing some changes in this section based on Alessandro's comments and trying to obtain a simpler and uniform notation.]}
+
 In this study, the methodology used for verifying closed-loop digital
@@
 \end{mylemma}
+
+\textcolor{blue}{
+Although the pulse transfer function $G(z)$ represents adequately $G(s)$ domain, the model $G(z)$ may not be accurate and some uncertainties may not be covered by that model.
+These uncertainties may be parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
+\begin{equation}
+\hat{G}(z)=G(z)+\Delta G(z),
+\end{equation}
+that may be represented by the following transfer function:
+\begin{equation}
+\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}}.
+\end{equation}}
+
+\textcolor{blue}{
+The vector of parametric uncertainties  $\Delta{p}$ for $G(z)$ is defined by:
+\begin{equation}
+\Delta{p}=\begin{bmatrix}
+\hat{b_{0}} - b_{0}\\
+\hat{b_{1}} - b_{1}\\
+\vdots \\
+\hat{b}_{M_G} - b_{M_{G}}\\
+\hat{a_{0}} - a_{0}\\
+\hat{a_{1}} - a_{1}\\
+\vdots\\
+\hat{a}_{N_G} - a_{N_{G}}\\
+\end{bmatrix}.
+\end{equation}}
+
+\textcolor{blue}{
+A typical hybrid system is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$, $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.}
+
+\begin{figure*}[htb]
+\centering
+
+\tikzset{add/.style n args={4}{
+    minimum width=6mm,
+    path picture={
+        \draw[circle] 
+            (path picture bounding box.south east) -- (path picture bounding box.north west)
+            (path picture bounding box.south west) -- (path picture bounding box.north east);
+        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+        }
+    }
+ }
+
+\resizebox{.8\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
+     semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
+    \node[draw=none] (r) {$R(z)$};
+%   \& \coordinate (aux0);
+   \& \node[circle,add={-}{+}{}{}] (circle) {};
+   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Controller}] (cz) {{\sc C(z)}};
+   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
+
+   \& complexnode/.pic={ 
+      \node[rectangle,draw,
+	minimum width=3cm,
+	minimum height=1.6cm,
+	label=\textbf{DAC},] (dac) {};
+     \node[circle,add={}{+}{+}{},fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {};
+     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
+     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
+     \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Plant}] (gs) {{\sc $G(s) + \Delta G(s)$}};
+   \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]gs)  {$U(s)$};
+   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(s)$};
+   \& complexnode/.pic={ 
+     \node[rectangle,draw,
+	minimum width=4cm,
+	minimum height=1.6cm,
+	label=\textbf{ADC},] (adc) {};
+   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
+   \coordinate (switch1) at ([xshift=-1cm]adc.center);
+   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
+   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
+     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
+   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
+   \& \coordinate (aux1);
+   \& \node[draw=none] (yz) {$\hat{Y}(z)$};\\
+   \& \coordinate (aux3); 
+   \&
+   \&
+   \& 
+   \& 
+   \& \coordinate (aux2);\\
+  };
+
+  \path[->] (v1) edge (q1.north);
+  \path[->] (v2) edge (q2.north);
+  \path[->] (r) edge (circle.west);
+  \path[->] (aux1) edge (yz);
+  \path  
+   (circle.east) edge (cz)
+   (cz.east) edge (q2.west)
+   (q2.east) edge (zoh.west)
+   (zoh.east) edge (gs.west)
+   (switch2) edge (q1.west)
+   (q1.east) edge (aux1.west)
+   (gs.east) edge (switch1.west)
+   (aux1.south) edge (aux2.north)
+   (aux2.west) edge (aux3.east); 
+  \path[->]  (aux3.north) edge (circle.south);
+ \end{tikzpicture}
+}
+ \caption{Sampled System. \label{fig:sampledsystem}}
+\end{figure*}
+
+\textcolor{blue}{
+The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta G_{P}(z)$ and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is represented as an additive measurement noise $\nu(z)$.}
+
+\begin{figure}[ht]
+\centering
+
+\tikzset{add/.style n args={4}{
+    minimum width=6mm,
+    path picture={
+        \draw[circle] 
+            (path picture bounding box.south east) -- (path picture bounding box.north west)
+            (path picture bounding box.south west) -- (path picture bounding box.north east);
+        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+        }
+    }
+ }
+
+\resizebox{.5\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
+     semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
+    \node[draw=none] (r) {$R(z)$};
+%   \& \coordinate (aux0);
+   \& \node[circle,add={-}{+}{}{}] (circle) {};
+   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Controller}] (cz) {{\sc C(z)}};
+   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Plant}] (gs) {{\sc $G(z) + \Delta G_{P}(z)$}};
+   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
+
+   \& \node[circle,add={}{+}{+}{}] (circle2) {};
+%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
+   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
+   \& \coordinate (aux1);
+   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
+   \& \coordinate (aux3); 
+   \&
+   \& 
+   \& 
+   \& \coordinate (aux2);\\
+  };
+
+%  \path[->] (v1) edge (q1.north);
+%  \path[->] (v2) edge (q2.north);
+  \path[->] (r) edge (circle.west);
+  \path[->] (nu) edge (circle2.north);
+  \path[->] (aux1) edge (yz);
+  \path  
+   (circle.east) edge (cz)
+   (cz.east) edge (gs.west)
+   (gs.east) edge (circle2.west)
+   (circle2.east) edge (aux1.west)
+   (aux1.south) edge (aux2.north)
+   (aux2.west) edge (aux3.east); 
+  \path[->]  (aux3.north) edge (circle.south);
+ \end{tikzpicture}
+}
+ \caption{Digital system equivalent to ~\ref{fig:sampledsystem}. \label{fig:digsystem1}}
+\end{figure}
+
+%
+\textcolor{blue}{
+In figure~\ref{fig:digsystem1}, two sources of uncertainties are considered: parametric uncertainties related to modeling errors, and uncertainties introduced by quantisations in sampling and holding process, {\it i.e.} ADC and DAC conversions.
+Assuming linearity and independence between these sources, the uncertain model may be rewritten as follows:
+\begin{equation}
+\hat{G}(z)=G(z)+\Delta G_{P}(z)+\Delta G_{Q}(z),
+\end{equation}
+where $\Delta G_{P}(z)$ is the term that corresponds to the parametric uncertainties and $\Delta G_{Q}(z)$ is the term that reflects the quantisation effects on the plant model.
+Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.}
+
+\begin{figure}[ht]
+\centering
+
+\tikzset{add/.style n args={4}{
+    minimum width=6mm,
+    path picture={
+        \draw[circle] 
+            (path picture bounding box.south east) -- (path picture bounding box.north west)
+            (path picture bounding box.south west) -- (path picture bounding box.north east);
+        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+        }
+    }
+ }
+
+\resizebox{.5\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
+     semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
+  %
+	\& 
+	\&
+	\& \coordinate (aux7); 
+	\& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm] (deltag2) {{\sc $\Delta G_{Q}(z)$}};
+	\& \coordinate (aux8);\\
+    \node[draw=none] (r) {$R(z)$};
+%   \& \coordinate (aux0);
+   \& \node[circle,add={-}{+}{}{}] (circle) {};
+   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Controller}] (cz) {{\sc C(z)}};
+   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
+   \& \coordinate (aux4);
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Plant}] (gs) {{\sc G(z)}};
+   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
+   \& \node[circle,add={+}{+}{+}{}] (circle2) {};
+%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
+%   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
+   \& \coordinate (aux1);
+   \& \node[draw=none] (yz) {$\hat{Y}(z)$};\\
+   \& 
+   \&
+   \& \coordinate (aux5); 
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm] (deltag) {{\sc $\Delta G_{P}(z)$}};
+   \& \coordinate (aux6);\\
+   \& \coordinate (aux3); 
+   \&
+   \& 
+   \& 
+   \&
+   \& \coordinate (aux2);\\
+  };
+
+%  \path[->] (v1) edge (q1.north);
+%  \path[->] (v2) edge (q2.north);
+  \path[->] (r) edge (circle.west);
+%  \path[->] (nu) edge (circle2.north);
+  \path[->] (aux1) edge (yz);
+  \path  
+   (aux4.north) edge (aux5.south)
+   (aux4.north) edge (aux7.south)
+   (aux5.east) edge (deltag.west)
+   (aux7.east) edge (deltag2.west)
+   (deltag.east) edge (aux6.west)
+   (deltag2.east) edge (aux8.west)
+   (circle.east) edge (cz)
+   (cz.east) edge (gs.west)
+   (circle2.east) edge (aux1.west)
+   (aux1.south) edge (aux2.north)
+   (aux2.west) edge (aux3.east); 
+  \path[->] (aux8.south) edge (circle2.north); 
+  \path[->] (aux6.south) edge (circle2.south);
+  \path[->] (gs.east) edge (circle2.west);
+  \path[->] (aux3.north) edge (circle.south);
+ \end{tikzpicture}
+}
+ \caption{Digital system with additive uncertainties $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$. \label{fig:digsystem2}}
+\end{figure}
+
+\textcolor{blue}{[IB: I propose to exchange the following paragraphs by the previous blue]}
+
 Since $G(z)$ is an approximation of $G(s)$ we introduce an error term caused during its calculation as $\Delta{G}_P$
@@
 %    
-\begin{figure*}[ht]
-\centering
-
-\tikzset{add/.style n args={4}{
-    minimum width=6mm,
-    path picture={
-        \draw[circle] 
-            (path picture bounding box.south east) -- (path picture bounding box.north west)
-            (path picture bounding box.south west) -- (path picture bounding box.north east);
-        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
-        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
-        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
-        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
-        }
-    }
- }
-
-\resizebox{.8\textwidth}{!}{
- \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
-     semithick, initial text=, ampersand replacement=\&,]
-
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
-    \node[draw=none] (r) {$\tilde R(z)$};
-%   \& \coordinate (aux0);
-   \& \node[circle,add={-}{+}{}{}] (circle) {};
-   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$\tilde e(z)$};
-   \& \node[rectangle,draw,
-	minimum width=1cm,
-	minimum height=1cm,
-        label=\textbf{Controller}] (cz) {{\sc C(z)}};
-   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$\tilde U(z)$};
-
-   \& complexnode/.pic={ 
-      \node[rectangle,draw,
-	minimum width=3cm,
-	minimum height=1.6cm,
-	label=\textbf{DAC},] (dac) {};
-     \node[circle,add={}{+}{+}{},fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {};
-     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
-     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
-     \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}
-   \& \node[rectangle,draw,
-	minimum width=1cm,
-	minimum height=1cm,
-        label=\textbf{Plant}] (gs) {{\sc G(s)}};
-   \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]gs)  {$U(s)$};
-   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(s)$};
-   \& complexnode/.pic={ 
-     \node[rectangle,draw,
-	minimum width=4cm,
-	minimum height=1.6cm,
-	label=\textbf{ADC},] (adc) {};
-   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
-   \coordinate (switch1) at ([xshift=-1cm]adc.center);
-   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
-   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
-     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
-   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
-   \& \coordinate (aux1);
-   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
-   \& \coordinate (aux3); 
-   \&
-   \&
-   \& 
-   \& 
-   \& \coordinate (aux2);\\
-  };
-
-  \path[->] (v1) edge (q1.north);
-  \path[->] (v2) edge (q2.north);
-  \path[->] (r) edge (circle.west);
-  \path[->] (aux1) edge (yz);
-  \path  
-   (circle.east) edge (cz)
-   (cz.east) edge (q2.west)
-   (q2.east) edge (zoh.west)
-   (zoh.east) edge (gs.west)
-   (switch2) edge (q1.west)
-   (q1.east) edge (aux1.west)
-   (gs.east) edge (switch1.west)
-   (aux1.south) edge (aux2.north)
-   (aux2.west) edge (aux3.east); 
-  \path[->]  (aux3.north) edge (circle.south);
- \end{tikzpicture}
-}
- \caption{Sampled System. \label{fig:sampledsystem}}
-\end{figure*}
-
-%% \begin{figure}[ht]
-%% \centering
-%% \includegraphics[width=\columnwidth]{figures/hsystembd.pdf}
-%% \caption{Sampled system.}
-%% \label{fig:sampledsystem}
-%% \end{figure}
-
-\begin{figure}[ht]
-\centering
-
-\tikzset{add/.style n args={4}{
-    minimum width=6mm,
-    path picture={
-        \draw[circle] 
-            (path picture bounding box.south east) -- (path picture bounding box.north west)
-            (path picture bounding box.south west) -- (path picture bounding box.north east);
-        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
-        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
-        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
-        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
-        }
-    }
- }
-
-\resizebox{.5\textwidth}{!}{
- \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
-     semithick, initial text=, ampersand replacement=\&,]
-
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
-    \node[draw=none] (r) {$R(z)$};
-%   \& \coordinate (aux0);
-   \& \node[circle,add={-}{+}{}{}] (circle) {};
-   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
-   \& \node[rectangle,draw,
-	minimum width=1cm,
-	minimum height=1cm,
-        label=\textbf{Controller}] (cz) {{\sc C(z)}};
-   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
-   \& \node[rectangle,draw,
-	minimum width=1cm,
-	minimum height=1cm,
-        label=\textbf{Plant}] (gs) {{\sc G(z)}};
-   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
-
-   \& \node[circle,add={}{+}{+}{}] (circle2) {};
-%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
-   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
-   \& \coordinate (aux1);
-   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
-   \& \coordinate (aux3); 
-   \&
-   \& 
-   \& 
-   \& \coordinate (aux2);\\
-  };
-
+%\begin{figure*}[ht]
+%\centering
+%
+%\tikzset{add/.style n args={4}{
+%    minimum width=6mm,
+%    path picture={
+%        \draw[circle] 
+%            (path picture bounding box.south east) -- (path picture bounding box.north west)
+%            (path picture bounding box.south west) -- (path picture bounding box.north east);
+%        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+%        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+%        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+%        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+%        }
+%    }
+% }
+%
+%\resizebox{.8\textwidth}{!}{
+% \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
+%     semithick, initial text=, ampersand replacement=\&,]
+%
+%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
+%    \node[draw=none] (r) {$\tilde R(z)$};
+%%   \& \coordinate (aux0);
+%   \& \node[circle,add={-}{+}{}{}] (circle) {};
+%   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$\tilde e(z)$};
+%   \& \node[rectangle,draw,
+%	minimum width=1cm,
+%	minimum height=1cm,
+%        label=\textbf{Controller}] (cz) {{\sc C(z)}};
+%   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$\tilde U(z)$};
+%     
+%   \& complexnode/.pic={ 
+%      \node[rectangle,draw,
+%	minimum width=3cm,
+%	minimum height=1.6cm,
+%	label=\textbf{DAC},] (dac) {};
+%     \node[circle,add={}{+}{+}{},fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {};
+%     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
+%     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
+%     \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}
+%   \& \node[rectangle,draw,
+%	minimum width=1cm,
+%	minimum height=1cm,
+%        label=\textbf{Plant}] (gs) {{\sc G(s)}};
+%   \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]gs)  {$U(s)$};
+%   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(s)$};
+%   \& complexnode/.pic={ 
+%     \node[rectangle,draw,
+%	minimum width=4cm,
+%	minimum height=1.6cm,
+%	label=\textbf{ADC},] (adc) {};
+%   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
+%   \coordinate (switch1) at ([xshift=-1cm]adc.center);
+%   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
+%   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
+%     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
+%   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
+%   \& \coordinate (aux1);
+%   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
+%   \& \coordinate (aux3); 
+%   \&
+%   \&
+%   \& 
+%   \& 
+%   \& \coordinate (aux2);\\
+%  };
+%
+%
 %  \path[->] (v1) edge (q1.north);
 %  \path[->] (v2) edge (q2.north);
-  \path[->] (r) edge (circle.west);
-  \path[->] (nu) edge (circle2.north);
-  \path[->] (aux1) edge (yz);
-  \path  
-   (circle.east) edge (cz)
-   (cz.east) edge (gs.west)
-   (gs.east) edge (circle2.west)
-   (circle2.east) edge (aux1.west)
-   (aux1.south) edge (aux2.north)
-   (aux2.west) edge (aux3.east); 
-  \path[->]  (aux3.north) edge (circle.south);
- \end{tikzpicture}
-}
- \caption{Sampled System. \label{fig:sampledsystem}}
-\end{figure}
-
-%
-%
-
-\begin{figure}[ht]
-\centering
-
-\tikzset{add/.style n args={4}{
-    minimum width=6mm,
-    path picture={
-        \draw[circle] 
-            (path picture bounding box.south east) -- (path picture bounding box.north west)
-            (path picture bounding box.south west) -- (path picture bounding box.north east);
-        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
-        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
-        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
-        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
-        }
-    }
- }
-
-\resizebox{.5\textwidth}{!}{
- \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
-     semithick, initial text=, ampersand replacement=\&,]
-
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
-    \node[draw=none] (r) {$R(z)$};
-%   \& \coordinate (aux0);
-   \& \node[circle,add={-}{+}{}{}] (circle) {};
-   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
-   \& \coordinate (aux4);
-   \& \node[rectangle,draw,
-	minimum width=1cm,
-	minimum height=1cm,
-        label=\textbf{Controller}] (cz) {{\sc C(z)}};
-   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
-   \& \node[rectangle,draw,
-	minimum width=1cm,
-	minimum height=1cm,
-        label=\textbf{Plant}] (gs) {{\sc G(z)}};
-   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
-   \& \node[circle,add={+}{+}{}{}] (circle2) {};
-%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
+%  \path[->] (r) edge (circle.west);
+%  \path[->] (aux1) edge (yz);
+%  \path  
+%   (circle.east) edge (cz)
+%   (cz.east) edge (q2.west)
+%   (q2.east) edge (zoh.west)
+%   (zoh.east) edge (gs.west)
+%   (switch2) edge (q1.west)
+%   (q1.east) edge (aux1.west)
+%   (gs.east) edge (switch1.west)
+%   (aux1.south) edge (aux2.north)
+%   (aux2.west) edge (aux3.east); 
+%  \path[->]  (aux3.north) edge (circle.south);
+% \end{tikzpicture}
+%}
+% \caption{Sampled System. \label{fig:sampledsystem}}
+%\end{figure*}
+%
+%%% \begin{figure}[ht]
+%%% \centering
+%%% \includegraphics[width=\columnwidth]{figures/hsystembd.pdf}
+%%% \caption{Sampled system.}
+%%% \label{fig:sampledsystem}
+%%% \end{figure}
+%
+%
+%\begin{figure}[ht]
+%\centering
+%
+%\tikzset{add/.style n args={4}{
+%    minimum width=6mm,
+%    path picture={
+%        \draw[circle] 
+%            (path picture bounding box.south east) -- (path picture bounding box.north west)
+%            (path picture bounding box.south west) -- (path picture bounding box.north east);
+%        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+%        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+%        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+%        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+%        }
+%    }
+% }
+%
+%\resizebox{.5\textwidth}{!}{
+% \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
+%     semithick, initial text=, ampersand replacement=\&,]
+%
+%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
+%    \node[draw=none] (r) {$R(z)$};
+%%   \& \coordinate (aux0);
+%   \& \node[circle,add={-}{+}{}{}] (circle) {};
+%   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
+%   \& \node[rectangle,draw,
+%	minimum width=1cm,
+%	minimum height=1cm,
+%        label=\textbf{Controller}] (cz) {{\sc C(z)}};
+%   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
+%   \& \node[rectangle,draw,
+%	minimum width=1cm,
+%	minimum height=1cm,
+%        label=\textbf{Plant}] (gs) {{\sc G(z)}};
+%   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
+%
+%   \& \node[circle,add={}{+}{+}{}] (circle2) {};
+%%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
 %   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
-   \& \coordinate (aux1);
-   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
-   \& 
-   \& \coordinate (aux5); 
-   \& \node[rectangle,draw,
-	minimum width=1cm,
-	minimum height=1cm] (deltag) {{\sc $\Delta G(z)$}};
-   \&
-   \& \coordinate (aux6);\\
-   \& \coordinate (aux3); 
-   \&
-   \& 
-   \& 
-   \&
-   \& \coordinate (aux2);\\
-  };
-
-%  \path[->] (v1) edge (q1.north);
-%  \path[->] (v2) edge (q2.north);
-  \path[->] (r) edge (circle.west);
+%   \& \coordinate (aux1);
+%   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
+%   \& \coordinate (aux3); 
+%   \&
+%   \& 
+%   \& 
+%   \& \coordinate (aux2);\\
+%  };
+%
+%
+%%  \path[->] (v1) edge (q1.north);
+%%  \path[->] (v2) edge (q2.north);
+%  \path[->] (r) edge (circle.west);
 %  \path[->] (nu) edge (circle2.north);
-  \path[->] (aux1) edge (yz);
-  \path  
-   (aux4.north) edge (aux5.south)
-   (aux5.east) edge (deltag.west)
-   (deltag.east) edge (aux6.west)
-   (aux6.south) edge (circle2.south)
-   (circle.east) edge (cz)
-   (cz.east) edge (gs.west)
-   (gs.east) edge (circle2.west)
-   (circle2.east) edge (aux1.west)
-   (aux1.south) edge (aux2.north)
-   (aux2.west) edge (aux3.east); 
-  \path[->]  (aux3.north) edge (circle.south);
- \end{tikzpicture}
-}
- \caption{Sampled System. \label{fig:sampledsystem}}
-\end{figure}
+%  \path[->] (aux1) edge (yz);
+%  \path  
+%   (circle.east) edge (cz)
+%   (cz.east) edge (gs.west)
+%   (gs.east) edge (circle2.west)
+%   (circle2.east) edge (aux1.west)
+%   (aux1.south) edge (aux2.north)
+%   (aux2.west) edge (aux3.east); 
+%  \path[->]  (aux3.north) edge (circle.south);
+% \end{tikzpicture}
+%}
+% \caption{Sampled System. \label{fig:sampledsystem}}
+%\end{figure}
+%
+%%
+%%
+%
+%\begin{figure}[ht]
+%\centering
+%
+%\tikzset{add/.style n args={4}{
+%    minimum width=6mm,
+%    path picture={
+%        \draw[circle] 
+%            (path picture bounding box.south east) -- (path picture bounding box.north west)
+%            (path picture bounding box.south west) -- (path picture bounding box.north east);
+%        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+%        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+%        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+%        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+%        }
+%    }
+% }
+%
+%\resizebox{.5\textwidth}{!}{
+% \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
+%     semithick, initial text=, ampersand replacement=\&,]
+%
+%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
+%    \node[draw=none] (r) {$R(z)$};
+%%   \& \coordinate (aux0);
+%   \& \node[circle,add={-}{+}{}{}] (circle) {};
+%   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
+%   \& \coordinate (aux4);
+%   \& \node[rectangle,draw,
+%	minimum width=1cm,
+%	minimum height=1cm,
+%        label=\textbf{Controller}] (cz) {{\sc C(z)}};
+%   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
+%   \& \node[rectangle,draw,
+%	minimum width=1cm,
+%	minimum height=1cm,
+%        label=\textbf{Plant}] (gs) {{\sc G(z)}};
+%   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
+%   \& \node[circle,add={+}{+}{}{}] (circle2) {};
+%%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
+%%   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
+%   \& \coordinate (aux1);
+%   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
+%   \& 
+%   \& \coordinate (aux5); 
+%   \& \node[rectangle,draw,
+%	minimum width=1cm,
+%	minimum height=1cm] (deltag) {{\sc $\Delta G(z)$}};
+%   \&
+%   \& \coordinate (aux6);\\
+%   \& \coordinate (aux3); 
+%   \&
+%   \& 
+%   \& 
+%   \&
+%   \& \coordinate (aux2);\\
+%  };
+%
+%
+%%  \path[->] (v1) edge (q1.north);
+%%  \path[->] (v2) edge (q2.north);
+%  \path[->] (r) edge (circle.west);
+%%  \path[->] (nu) edge (circle2.north);
+%  \path[->] (aux1) edge (yz);
+%  \path  
+%   (aux4.north) edge (aux5.south)
+%   (aux5.east) edge (deltag.west)
+%   (deltag.east) edge (aux6.west)
+%   (aux6.south) edge (circle2.south)
+%   (circle.east) edge (cz)
+%   (cz.east) edge (gs.west)
+%   (gs.east) edge (circle2.west)
+%   (circle2.east) edge (aux1.west)
+%   (aux1.south) edge (aux2.north)
+%   (aux2.west) edge (aux3.east); 
+%  \path[->]  (aux3.north) edge (circle.south);
+% \end{tikzpicture}
+%}
+% \caption{Sampled System. \label{fig:sampledsystem}}
+%\end{figure}
 

### 2016-10-09 paper/paper.tex
Changes in Section 2

@@
 
-\blue{Please insert a figure clearly distinguishing between continuous and discretised/quantised plant - a template is in a picture sent out by Lucas late last week.
+%\blue{Please insert a figure clearly distinguishing between continuous and discretised/quantised plant - a template is in a picture sent out by Lucas late last week.
 Please introduced signals on the plot.
@@
 %\end{itemize}
-}
+%}
 
@@
 
+\textcolor{blue}{The digital controller $C(z)$ also suffers disturbances from the FWL effects, with roundoffs in coefficients that may change the closed-loop poles and zeros position, and consequently affect its stability, as shown in~\cite{Bessa16}.}
+
+\textcolor{blue}{Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
+domain, {\it i.e.} a Fixed-Point Finite Word Length with integer size $I$ and fractional
+size $F$, we shall denote this domain as $\mathbb{R}\langle I,F \rangle$ and assume that there exists a function $FWL[\cdot]:\mathbb{R}^{n}\rightarrow \mathbb{R}^{n}\langle I,F \rangle$, which applies the FWL effects to a polynomial.
+Thus the perturbed controller model $\hat{C}(z)$ may be computed from the original model $C(z)=\frac{N_{C}(z)}{D_{C}(z)}$ using the following expression:
+\begin{equation}
+\hat{C}(z)=\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}
+\end{equation}}
+
+\textcolor{blue}{[IB: And I propose to exchange the remaining paragraphs by the previous blue]}
+
 Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$

### 2016-10-09 paper/paper.tex
created new section on fixed point manipulation

@@
 
+\textcolor{green}{DC: I believe Alessandro wanted to be more specific about the nature of the modelling error which is why I was trying to explain it.
+In this case I believe there are also two separate sources for $\Delta{G}_p(z)$.
+The first is $\Delta{G}_p(s)$ (which is basically a known tolerance that may come from G(t)), whilst the second is the error introduced by the calculations in the $\mathcal{Z}$ transform.
+Alessandro, do you want to address this second term (possibly as explained below) or just leave the blue section as is?}
+
 Since $G(z)$ is an approximation of $G(s)$ we introduce an error term caused during its calculation as $\Delta{G}_P$
@@
 
+\textcolor{blue}{Since the controller is implemented using a FWL, $C(z)$ also suffers disturbances from the FWL effects, with roundoffs in coefficients that may change the closed-loop poles and zeros position, and consequently affect its stability, as shown in~\cite{Bessa16}.}
+
+\textcolor{blue}{
+Let $\hat{C}(z)$ be the transfer function of the digital controller represented using this FWL with integer size $I$ and fractional
+size $F$.  We shall denote this domain as $\mathbb{R}\langle I,F \rangle$
+%Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
+%domain, {\it i.e.} a Fixed-Point Finite Word Length with integer size $I$ and fractional
+%size $F$, we shall denote this domain as $\mathbb{R}\langle I,F \rangle$ 
+and assume that there exists a function $FWL[\cdot]:\mathbb{R}^{n}\rightarrow \mathbb{R}^{n}\langle I,F \rangle$, which applies the FWL effects to a polynomial.
+Thus the perturbed controller model $\hat{C}(z)$ may be computed from the original model $C(z)=\frac{N_{C}(z)}{D_{C}(z)}$ using the following expression:
+\begin{equation}
+\hat{C}(z)=\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}
+\end{equation}}
+
+\textcolor{blue}{[IB: And I propose to exchange the remaining paragraphs by the previous blue]}
+
+\textcolor{green}{[DC: I changed it to a separate section to differentiate the effects, so we should keep both]}
+
+%------------------------------------
+\subsection{Using Fixed Point Arithmetic for verification}
+\label{fixedpoint_verification}
+%------------------------------------
+
 Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
-using a Fixed-Point Finite Word Length with integer size $I$ and fractional
-size $F$.  We shall denote this domain as $\mathbb{R}\langle I,F \rangle$ and obtain 
+using Fixed-Point bit vectors with integer size $I_b$ and fractional
+size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
 %
@@
 
-\textcolor{blue}{The digital controller $C(z)$ also suffers disturbances from the FWL effects, with roundoffs in coefficients that may change the closed-loop poles and zeros position, and consequently affect its stability, as shown in~\cite{Bessa16}.}
-
-\textcolor{blue}{Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
-domain, {\it i.e.} a Fixed-Point Finite Word Length with integer size $I$ and fractional
-size $F$, we shall denote this domain as $\mathbb{R}\langle I,F \rangle$ and assume that there exists a function $FWL[\cdot]:\mathbb{R}^{n}\rightarrow \mathbb{R}^{n}\langle I,F \rangle$, which applies the FWL effects to a polynomial.
-Thus the perturbed controller model $\hat{C}(z)$ may be computed from the original model $C(z)=\frac{N_{C}(z)}{D_{C}(z)}$ using the following expression:
-\begin{equation}
-\hat{C}(z)=\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}
-\end{equation}}
-
-\textcolor{blue}{[IB: And I propose to exchange the remaining paragraphs by the previous blue]}
-
-Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$
+Since the controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
 domain,
@@
 \label{FWL_tf}
-&f (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I,F \rangle \triangleq \tilde x = x-(x\mod\tilde x)
+&f_b (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = x-(x\mod\tilde x)
 \end{align}
@@
 \tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
-&= C(z) =\hat{C}(z) + \Delta{C}(z)\\
+&= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
 \label{digital_plant_tf}
 \tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_q \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_q \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_q \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_q \hat{a}_{N_G})z^{-N_G}} \nonumber \\
-&=G(z)+\Delta{G}_P(z)+\Delta{G}_Q(z).
+&=G(z)+\Delta{G}_P(z)+\Delta{G}_b(z).
 \end{align}
-where $\Delta_q\hat{c}_i=\hat{c}_i\mod \tilde{c}_i$
-\red{[please, how can you claim that the error enters as written? Can you show the derivation? Can you show a reference that has derived this form?]}
-\green{[the definition of f (now included) should explain it clearly]}
-and $\Delta{G}_Q(z)$ represents the plant uncertainty caused by
+where $\Delta_b\hat{c}_i=\hat{c}_i\mod \tilde{c}_i$
+and $\Delta{G}_b(z)$ represents the plant uncertainty caused by
 the rounding off effect.  We may encompass all the uncertainty as
-$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_Q(z)$.  Since this value is
+$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_b(z)$.  Since this value is
 nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
@@
 
+Two approaches have been taken to synthesise a stabe controller based on this model.
+The first uses a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is upper bound at the source by selecting a conservative $\Delta{G}_b(z)$ that encompasses its propagation over a number of operations.
+The verification phase produces a counterexample if some instance of $\mathfrak{G}(z)$ does not verify the properties and the CEGIS loop iteratively looks for a new controller that verifies the supplied counterexamples.
+Although it is fast, the conservative error calculation can be restrictive to a small number of benchmarks.
+
+The second approch uses interval arithmetic, representing the coefficients $[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\ {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
+and rounding operations outwards during the process. This results in a tighter calculation of the error at the cost of performance.
 %------------------------------------

### 2016-10-10 paper/paper.tex
Minor changes on 2.1.

@@
 %
-\noindent where $\beta$ and $\alpha$ are vectors containing the controller's coefficients;  
-similarly $b$ and $a$ encompas the plant's coefficients;  
+\noindent where $\vec{\beta}$ and $\vec{\alpha}$ are vectors containing the controller's coefficients;  
+similarly $\vec{b}$ and $\vec{a}$ encompas the plant's coefficients;  
 and $N_{(\cdot)}$ and $M_{(\cdot)}$ denote the number of poles and zeros for the corresponding block.
@@
 The pulse transfer function $G(z)$ is a z-domain model that relates the
-output sampled by a ADC and the digital input provided by ZOH.  It is
-equivalent at the sample times ({\it i.e.}, $kT$ to the continuous transfer
-function $G(s)$ driven by ZOH).  This pulse transfer function can be
+output sampled by a ADC and the digital input provided by ZOH.  It is sufficiently
+equivalent at the sample times ({\it i.e.}, $t=kT$) to the continuous transfer
+function $G(s)$ driven by ZOH.  This pulse transfer function can be
 computed as
@@
 
-\textcolor{blue}{
 Although the pulse transfer function $G(z)$ represents adequately $G(s)$ domain, the model $G(z)$ may not be accurate and some uncertainties may not be covered by that model.
@@
 \hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}}.
-\end{equation}}
-
-\textcolor{blue}{
+\end{equation}
+
 The vector of parametric uncertainties  $\Delta{p}$ for $G(z)$ is defined by:
@@
 \hat{a}_{N_G} - a_{N_{G}}\\
-\end{bmatrix}.
-\end{equation}}
+\end{bmatrix}=\begin{bmatrix}
+\vec{\hat{b}}\\
+\vec{\hat{a}}
+\end{bmatrix}-\begin{bmatrix}
+\vec{b}\\
+\vec{a}
+\end{bmatrix}
+\end{equation}
 

### 2016-10-10 paper/paper.tex
Changes on 2.1.

@@
 
-\textcolor{blue}{[IB: I'm proposing some changes in this section based on Alessandro's comments and trying to obtain a simpler and uniform notation.]}
+%\textcolor{blue}{[IB: I'm proposing some changes in this section based on Alessandro's comments and trying to obtain a simpler and uniform notation.]}
 
@@
 The pulse transfer function $G(z)$ is a z-domain model that relates the
-output sampled by a ADC and the digital input provided by ZOH.  It is sufficiently
-equivalent at the sample times ({\it i.e.}, $t=kT$) to the continuous transfer
+output sampled by a ADC and the digital input provided by ZOH.  It is equivalent at the sample times ({\it i.e.}, $t=kT$) to the continuous transfer
 function $G(s)$ driven by ZOH.  This pulse transfer function can be
@@
 \end{mylemma}
+
+\begin{myassumption}
+%
+The controller and the plant are linear time-invariant (LTI) systems, {\it i.e.}, any source of
+nonlinearity ({\it e.g.}, saturation, overflow, ADC/DAC nonlinearities) will
+be disregarded.
+Additionally, the pulse transfer function obtained via \eqref{eq:pulsetf} using an appropriate sample rate ({\it i.e.}, obeying the Nyquist sampling conditions)  may be considered a sufficient discrete-time representation of $G(s)$.
+%
+\end{myassumption}
 
@@
 %
-The controller and the plant are linear, {\it i.e.}, any source of
-nonlinearity ({\it e.g.}, saturation, overflow, ADC/DAC nonlinearities) will
-be disregarded.
-%
-\end{myassumption}
-
-\begin{myassumption}
-%
 The DAC interpolator is an ideal ZOH; it takes the discrete value of control

### 2016-10-10 paper/paper.tex
Changes on 2.1.

@@
 
-\textcolor{blue}{
-A typical hybrid system is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$, $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.}
+A typical hybrid system is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$, $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.
 
@@
 
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
     \node[draw=none] (r) {$R(z)$};
@@
         label=\textbf{Plant}] (gs) {{\sc $G(s) + \Delta G(s)$}};
-   \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]gs)  {$U(s)$};
-   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(s)$};
+   \node[draw=none] (ud) at ([xshift=-2cm,yshift=.15cm]gs)  {$U(s)$};
+   \node[draw=none] (y) at ([xshift=2cm,yshift=.15cm]gs)  {$Y(s)$};
    \& complexnode/.pic={ 
@@
 
-\textcolor{blue}{
-The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta G_{P}(z)$ and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is represented as an additive measurement noise $\nu(z)$.}
+The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta G_{P}(z)=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$ and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is represented as an additive measurement noise $\nu(z)$.
 
@@
         label=\textbf{Plant}] (gs) {{\sc $G(z) + \Delta G_{P}(z)$}};
-   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
+   \node[draw=none] (y) at ([xshift=2cm,yshift=.15cm]gs)  {$Y(z)$};
 
@@
 %
-\textcolor{blue}{
 In figure~\ref{fig:digsystem1}, two sources of uncertainties are considered: parametric uncertainties related to modeling errors, and uncertainties introduced by quantisations in sampling and holding process, {\it i.e.} ADC and DAC conversions.
@@
 where $\Delta G_{P}(z)$ is the term that corresponds to the parametric uncertainties and $\Delta G_{Q}(z)$ is the term that reflects the quantisation effects on the plant model.
-Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.}
+Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.
 
@@
 
-\textcolor{blue}{[IB: I propose to exchange the following paragraphs by the previous blue]}
-
-\textcolor{green}{DC: I believe Alessandro wanted to be more specific about the nature of the modelling error which is why I was trying to explain it.
+%\textcolor{blue}{[IB: I propose to exchange the following paragraphs by the previous blue]}
+
+%\textcolor{green}{DC: I believe Alessandro wanted to be more specific about the nature of the modelling error which is why I was trying to explain it.
 In this case I believe there are also two separate sources for $\Delta{G}_p(z)$.
@@
 
-Since $G(z)$ is an approximation of $G(s)$ we introduce an error term caused during its calculation as $\Delta{G}_P$
-
-%
-\begin{align}
-\small
-\label{parametric_plant_tf}
-\hat{G}(z)&=\frac{(b_{0}+\Delta_p b_{0}) +...+(b_{M_G}+\Delta_p b_{M_G})z^{-M_G}}{(a_{0}+\Delta_p a_{0})+...+(a_{N_G}+\Delta_p a_{N_G})z^{-N_G}} \nonumber \\
-&=G(z)+\Delta{G}_P(z).
-\end{align}
-%
-Note that $\Delta{G}_P$ is undefined and upperbound by a user defined
-value such that $\hat{G}(z)$ corresponds to the set of
-possible polynomial forms of $G(z, T)$ that overapproximate $G(s)$.
-This calculation is performed outside of the scope of this work since it depends on the nature of the tool used to obtain the $\mathcal{Z}$ form.
+%Since $G(z)$ is an approximation of $G(s)$ we introduce an error term caused during its calculation as $\Delta{G}_P$
+%
+%%
+%\begin{align}
+%\small
+%\label{parametric_plant_tf}
+%\hat{G}(z)&=\frac{(b_{0}+\Delta_p b_{0}) +...+(b_{M_G}+\Delta_p b_{M_G})z^{-M_G}}{(a_{0}+\Delta_p a_{0})+...+(a_{N_G}+\Delta_p a_{N_G})z^{-N_G}} \nonumber \\
+%&=G(z)+\Delta{G}_P(z).
+%\end{align}
+%%
+%Note that $\Delta{G}_P$ is undefined and upperbound by a user defined
+%value such that $\hat{G}(z)$ corresponds to the set of
+%possible polynomial forms of $G(z, T)$ that overapproximate $G(s)$.
+%This calculation is performed outside of the scope of this work since it depends on the nature of the tool used to obtain the $\mathcal{Z}$ form.
 The error comes from the bounded horizon and mathematical precision used to calculate the $\mathcal{Z}$ transform, which will be tool and user dependent.
-\red{[The previous statement is confusing and I must disagree here: I want hard error bounds on a specific value of T.]}
-\green{[You are correct.
+%\red{[The previous statement is confusing and I must disagree here: I want hard error bounds on a specific value of T.]}
+%\green{[You are correct.
 It was absolutely wrong.
@@
 
-\textcolor{blue}{Since the controller is implemented using a FWL, $C(z)$ also suffers disturbances from the FWL effects, with roundoffs in coefficients that may change the closed-loop poles and zeros position, and consequently affect its stability, as shown in~\cite{Bessa16}.}
-
-\textcolor{blue}{
+Since the controller is implemented using a FWL, $C(z)$ also suffers disturbances from the FWL effects, with roundoffs in coefficients that may change the closed-loop poles and zeros position, and consequently affect its stability, as shown in~\cite{Bessa16}.
+
 Let $\hat{C}(z)$ be the transfer function of the digital controller represented using this FWL with integer size $I$ and fractional
@@
 \begin{equation}
-\hat{C}(z)=\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}
-\end{equation}}
-
-\textcolor{blue}{[IB: And I propose to exchange the remaining paragraphs by the previous blue]}
-
-\textcolor{green}{[DC: I changed it to a separate section to differentiate the effects, so we should keep both]}
+\hat{C}(z)=\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}.
+\end{equation}
+
+%\textcolor{blue}{[IB: And I propose to exchange the remaining paragraphs by the previous blue]}
+%
+%\textcolor{green}{[DC: I changed it to a separate section to differentiate the effects, so we should keep both]}
 

### 2016-10-10 paper/paper.tex
Changes on section 2

@@
 %
+\label{assumption:cont_and_plant}
 The controller and the plant are linear time-invariant (LTI) systems, {\it i.e.}, any source of
@@
 %------------------------------------
+\subsection{On the stability considering effects of implementation issues and quantization noises}
+\label{sec:stability}
+%------------------------------------
+
+In order to obtain a sound synthesis of digital controller, the effect of FWL implementation in controller and quantization noises in closed loop system have to be considered.
+Considering that the quantizer $Q1$ is the source of a white noise with zero mean $\nu_{1}$ and $Q2$ is the source of a white noise with zero mean $\nu_{2}$, the following equation may written for the system in figure~\ref{fig:sampledsystem} considering the parametric uncertainties $\Delta G(z)$ and the FWL effects on controller  ($\hat{C}(z)$):
+\begin{equation}
+\hat{Y}(z)=\hat{C}(z)\hat{G}(z)[R(z)+\nu_{1}(z)]+\nu_{2}(z)\hat{G}(z)-\hat{Y}(z)\hat{C}(z)\hat{G}(z),
+\end{equation}
+that can be rewritten as follows:
+\begin{equation}
+\label{eq:outputfunctions}
+\hat{Y}(z)=H_{1}[R(z)+\nu_{1}(z)]+H_{2}(z)\nu_{2}(z),
+\end{equation}
+where
+\begin{equation}
+H_{1}=\frac{\hat{C}(z)\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
+\end{equation}
+and
+\begin{equation}
+H_{2}=\frac{\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
+\end{equation}
+
+A discrete-time linear system is said to be Bounded-Input and Bounded-Output (BIBO) stable if and only if every pole of its transfer function lies inside the unit circle.
+Analyzing the~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for stability of closed-loop system in figure~\ref{fig:sampledsystem}.
+
+\begin{mylemma}{\cite{Bessa16,fadali}}
+\label{internal_stab_lemma}
+A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with transfer functions $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and $\hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is internally stable if and only if:
+\begin{itemize}
+\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
+\begin{equation}
+\label{eq_int_stab}
+S(z)=FWL[N_{C}(z)]\hat{N}_{G}(z)+FWL[D_{C}(z)]\hat{D}_{G}(z);
+\end{equation}
+\item the direct loop product $\frac{NFWL[_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle;
+\item the controller $\hat{C}(z)$ is a minimum-phase system. 
+\end{itemize}
+\end{mylemma}
+
+%------------------------------------
 \subsection{Using Fixed Point Arithmetic for verification}
@@
 
-Since the controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
+Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
 domain,

### 2016-10-10 paper/paper.tex
Changes on section 2

@@
 %
+The DAC and ADC are synchronized, {\it i.e.}, there is no delay between
+sampling the plant output at ADC and updating the DAC accordingly.
+%
+\end{myassumption}
+
+\begin{myassumption}
+%
+The DAC interpolator is an ideal ZOH; it takes the discrete value of control
+signal $\tilde u(k)$ at instant $k$ and produces a rectangular pulse of height
+$u(k)$ and width equal to the sample time $T$.
+%
+\end{myassumption}
+
+\begin{myassumption}
+%
 \label{assumption:cont_and_plant}
@@
 A discrete-time linear system is said to be Bounded-Input and Bounded-Output (BIBO) stable if and only if every pole of its transfer function lies inside the unit circle.
-Analyzing the~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for stability of closed-loop system in figure~\ref{fig:sampledsystem}.
+Analyzing the~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for stability of closed-loop system in figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$ are bounded.
 
@@
 \begin{equation}
-\label{eq_int_stab}
+\label{lemma:eq_int_stab}
 S(z)=FWL[N_{C}(z)]\hat{N}_{G}(z)+FWL[D_{C}(z)]\hat{D}_{G}(z);
 \end{equation}
-\item the direct loop product $\frac{NFWL[_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle;
+\item the direct loop product $\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle;
 \item the controller $\hat{C}(z)$ is a minimum-phase system. 
@@
 \end{mylemma}
+
+The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for synthesis of digital controllers able to stabilize closed loop system, considering plant parametric uncertainties ($\Delta G_{P}(z)$), quantization noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital controllers.
+Based on it, the model for plant uncertainty due quantization noise ($\Delta G(z)$ may be disregarded if the conditions on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantization noise is bounded.
 
@@
 
-\begin{myassumption}
-%
-The DAC and ADC are synchronized, {\it i.e.}, there is no delay between
-sampling the plant output at ADC and updating the DAC accordingly.
-%
-\end{myassumption}
-
-\begin{myassumption}
-%
-The DAC interpolator is an ideal ZOH; it takes the discrete value of control
-signal $\tilde u(k)$ at instant $k$ and produces a rectangular pulse of height
-$u(k)$ and width equal to the sample time $T$.
-%
-\end{myassumption}
-
 %\begin{myprop}

### 2016-10-10 paper/paper.tex
Changes on Section 2

@@
 %------------------------------------
-\subsection{On the stability considering effects of implementation issues and quantization noises}
+\subsection{On the stability considering effects of implementation issues and quantisation noises}
 \label{sec:stability}
@@
 
-In order to obtain a sound synthesis of digital controller, the effect of FWL implementation in controller and quantization noises in closed loop system have to be considered.
+In order to obtain a sound synthesis of digital controller, the effect of FWL implementation in controller and quantisation noises in closed loop system have to be considered.
 Considering that the quantizer $Q1$ is the source of a white noise with zero mean $\nu_{1}$ and $Q2$ is the source of a white noise with zero mean $\nu_{2}$, the following equation may written for the system in figure~\ref{fig:sampledsystem} considering the parametric uncertainties $\Delta G(z)$ and the FWL effects on controller  ($\hat{C}(z)$):
@@
 
-The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for synthesis of digital controllers able to stabilize closed loop system, considering plant parametric uncertainties ($\Delta G_{P}(z)$), quantization noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital controllers.
-Based on it, the model for plant uncertainty due quantization noise ($\Delta G(z)$ may be disregarded if the conditions on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantization noise is bounded.
+The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for synthesis of digital controllers able to stabilize closed loop system, considering plant parametric uncertainties ($\Delta G_{P}(z)$), quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital controllers.
+Based on it, the model for plant uncertainty due quantisation noise ($\Delta G(z)$ may be disregarded if the conditions on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise is bounded.
+
+The quantisation noise is indeed bounded, since assumption~\ref{whitenoise} and the Lemmas~\ref{lemma:variance} and~\ref{lemma:boundednoise} are true.
+
+%
+\begin{myassumption}
+\label{whitenoise}
+%
+The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
+$Q2$) are energy bounded uncorrelated white noises.
+% 
+\end{myassumption}
+
+\begin{mylemma}
+\label{lemma:variance}
+In particular, \cite{widrow1956} models the quantisation noise as a gaussian
+model in which the second moment (variance) of the probability density
+function (PDF) of the quantisation noise is given by
+%
+\begin{equation}
+\label{eq:variancelemma}
+\sigma_{Q}^{2}=\frac{q^{2}}{12},
+\end{equation}
+where $q$ is the step size of quantizer. (Proof is on \cite{widrow1956})
+\end{mylemma}
+
+\begin{mylemma}
+\label{lemma:boundednoise}
+The z-transform of the quantisation noise $\nu(z)=\mathcal{Z}\left\lbrace\nu(k)\right\rbrace$ in figure~\ref{fig:digsystem1} may be calculated through the power spectral density of $\nu(k)$, thus:
+\begin{equation}
+\nu(z)= \sigma_{Q}^{2}.
+\end{equation}
+\end{mylemma}
+
+\begin{proof}
+Considering $\nu(k)$ a random process, where $\nu(k)$ is independent from $\nu(k+i)$ for every  integer $k\neq 0$.
+The autocorrelation function of $\nu(k)$, {\it i.e.} $R_{\nu\nu}(\tau)$ may be computed as follows:
+\begin{equation}
+R_{\nu\nu}(\tau)=E[\nu(t+\tau)\nu]=\sigma_{Q}^{2}\cdot \delta(\tau),
+\end{equation}
+where $\delta(\tau)$ is the Dirac delta function at delay time $\tau$.
+
+By definition~\cite{poularikas2000transforms}, the power spectral density of  $nu(k)$ is the z-transform of $R_{\nu\nu}(\tau)$, thus
+\begin{equation}
+\nu(z)=  \sum\limits_{k=-\infty}^{\infty}{R_{\nu\nu}(k)z^{-k}} = \sigma_{Q}^{2}.
+\end{equation}
+\end{proof}
+
+%, thus supporting this assumption.
 
@@
 
-\section{An Uncertainty Model for the Quantization Error} 
-\label{sec:uncertainty-model-quantization-error}
-
-%Here, an uncertainty model to accommodate the
-%quantization noise effects on $\hat{G}(z)$ is proposed.  
-%As a result, Eq.~\eqref{eq:uncertainplant} is rewritten as
-%
-%\begin{equation}
-%\label{eq:uncertainFWLplant}
-%\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}+\Delta{G_{P}(z)},
-%\end{equation}
-
-A model for $\Delta{G_{Q}(z)}$ that can represent the quantization
-noise effect in the plant output, and consequently the closed-loop system
-output, is proposed.  
-%\red{[eliminate next:] 
-%For convenience, the parametric uncertainties will be described here.}
-
-Consider the closed-loop sampled system in Figure~\ref{fig:sampledsystem},
-where $C(z)$ is the digital controller model, whose control output signal is
-quantized ($Q2$) and interpolated via a ZOH using digital-to-analog
-converter (DAC).  The quantization occurs because the DAC resolution may be
-different from the fixed point representation of the controller.  $G(s)$ is
-the continuous-time model of the plant, from which output samples are taken
-and quantized ($Q1$) by means of an analog-to-digital converter (ADC)
-synchronized with the DAC.  Each quantizer ($Q1$ and $Q2$) will present some
-contribution for the total quantization noise.
+%\section{An Uncertainty Model for the quantisation Error} 
+%\label{sec:uncertainty-model-quantisation-error}
+%
+%%Here, an uncertainty model to accommodate the
+%%quantisation noise effects on $\hat{G}(z)$ is proposed.  
+%%As a result, Eq.~\eqref{eq:uncertainplant} is rewritten as
+%%
+%%\begin{equation}
+%%\label{eq:uncertainFWLplant}
+%%\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}+\Delta{G_{P}(z)},
+%%\end{equation}
+%
+%A model for $\Delta{G_{Q}(z)}$ that can represent the quantisation
+%noise effect in the plant output, and consequently the closed-loop system
+%output, is proposed.  
+%%\red{[eliminate next:] 
+%%For convenience, the parametric uncertainties will be described here.}
+%
+%Consider the closed-loop sampled system in Figure~\ref{fig:sampledsystem},
+%where $C(z)$ is the digital controller model, whose control output signal is
+%quantized ($Q2$) and interpolated via a ZOH using digital-to-analog
+%converter (DAC).  The quantisation occurs because the DAC resolution may be
+%different from the fixed point representation of the controller.  $G(s)$ is
+%the continuous-time model of the plant, from which output samples are taken
+%and quantized ($Q1$) by means of an analog-to-digital converter (ADC)
+%synchronized with the DAC.  Each quantizer ($Q1$ and $Q2$) will present some
+%contribution for the total quantisation noise.
 %    
@@
 
-First, some assumptions have to be established to obtain a model for the
-quantization effects (seen as noise) on the closed loop system.
-%
-\begin{myassumption}
-\label{whitenoise}
-%
-The quantization noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
-$Q2$) are energy bounded uncorrelated white noises.
-% 
-In particular, \cite{widrow1956} models the quantization noise as a gaussian
-model in which the second moment (variance) of the probability density
-function (pdf) of the quantization noise is given by
-%
-\begin{equation}
-\label{eq:variancelemma}
-\sigma_{Q}^{2}=\frac{q^{2}}{12},
-\end{equation}
-where $q$ is the step size of quantizer. 
-%, thus supporting this assumption.
-\end{myassumption}
-
 %\begin{myprop}
@@
 %\begin{equation}
-%\label{eq:quantization_tf}
+%\label{eq:quantisation_tf}
 %\Delta{G_{Q}(z)}=\frac{\nu(z)}{U(z)},
@@
 %\end{equation}
-%where $\sigma_{Q}^{2}$ is the variance of the quantization noise and
+%where $\sigma_{Q}^{2}$ is the variance of the quantisation noise and
 %$U(z)$ is the z-transform of control signal ({\it i.e.}, the z-transform of
@@
 %be represented by the following pulse transfer function (without
-%quantization noise effect):
+%quantisation noise effect):
 %%
@@
 %
-%Considering the quantization noise $\nu(k)$ as an output error in the
+%Considering the quantisation noise $\nu(k)$ as an output error in the
 %discrete plant model, an additive noise in the plant output $y(k)$ resulting
@@
 
-%Eq.~\eqref{eq:deltag_var} indicates that the modelling of the quantization noise
+%Eq.~\eqref{eq:deltag_var} indicates that the modelling of the quantisation noise
 %effect on the plant transfer function demands an estimation of the variance
-%of quantization noise $\sigma_{Q}^{2}$.  To obtain such estimation, the
-%methodology presented by~\cite{widrow2008quantization}
+%of quantisation noise $\sigma_{Q}^{2}$.  To obtain such estimation, the
+%methodology presented by~\cite{widrow2008quantisation}
 %is used.  The authors provide an algorithm for computing the mean square of
@@
 %\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factors, {\it i.e.} constant gains usually employed before the ADC and after the DAC in order to avoid the overload of converters  %\red{[define scale factors]}
-%for the quantization $Q1$ and $Q2$, respectively; $q_{1}$ and $q_{2}$ are the quantization step for $Q1$ and $Q2$, respectively, and $\sum {h_{Q1}^{2}}$ and $\sum
+%for the quantisation $Q1$ and $Q2$, respectively; $q_{1}$ and $q_{2}$ are the quantisation step for $Q1$ and $Q2$, respectively, and $\sum {h_{Q1}^{2}}$ and $\sum
 %{h_{Q2}^{2}}$ are the squares sums of the impulse response obtained by means
@@
 
-\red{[The following text needs to be completed. (Notice typos, reference to wrong signal $R$, and to wrong TF $C,G$.]}
-
-Considering that
-the quantizer $Q1$ is the source of a white noise with zero mean $\nu_{1}$
-and $Q2$ is the source of a white noise with zero mean $\nu_{2}$, the
-following equation can be written for the system in
-Figure~\ref{fig:sampledsystem}
-%
-\begin{equation}
-\resizebox{0.48\textwidth}{!}{
-$\tilde{Y}(z)=\tilde R(z)C(z)G(z)-\tilde{Y}(z)C(z)G(z)+\nu_{1}(z)+\nu_{2}(z)G(z),$
-}
-\end{equation}
-
-\noindent which can be rewritten as
-%
-\begin{equation}
-\label{eq:outputfunctions}
-\tilde{Y}(z)=C(z)G(z)H(z)R(z)+H(z)\nu_{1}(z)+G(z)H(z)\nu_{2}(z)
-\end{equation}
-$$H(z)=\frac{1}{1+C(z)G(z)}$$
-
-Note that $H(z)$ cancels the poles of both $G(z)$ and $C(z)$, thus we need only verify the stability of $H(z)$
-to validate the stability of the whole system.
+%\red{[The following text needs to be completed. (Notice typos, reference to wrong signal $R$, and to wrong TF $C,G$.]}
+%
+%Considering that
+%the quantizer $Q1$ is the source of a white noise with zero mean $\nu_{1}$
+%and $Q2$ is the source of a white noise with zero mean $\nu_{2}$, the
+%following equation can be written for the system in
+%Figure~\ref{fig:sampledsystem}
+%%
+%\begin{equation}
+%\resizebox{0.48\textwidth}{!}{
+%$\tilde{Y}(z)=\tilde R(z)C(z)G(z)-\tilde{Y}(z)C(z)G(z)+\nu_{1}(z)+\nu_{2}(z)G(z),$
+%}
+%\end{equation}
+%
+%\noindent which can be rewritten as
+%%
+%\begin{equation}
+%\label{eq:outputfunctions}
+%\tilde{Y}(z)=C(z)G(z)H(z)R(z)+H(z)\nu_{1}(z)+G(z)H(z)\nu_{2}(z)
+%\end{equation}
+%$$H(z)=\frac{1}{1+C(z)G(z)}$$
+%
+%Note that $H(z)$ cancels the poles of both $G(z)$ and $C(z)$, thus we need only verify the stability of $H(z)$
+%to validate the stability of the whole system.
 %These equations are sufficient for computing $\sigma_{Q}^{2}$.  However,
@@
 %Eq.~\eqref{eq:deltag_var}, {\it i.e.}, the z-transform of control action
-%$U(z)$.  This indicates that the quantization noise effect on a discrete
+%$U(z)$.  This indicates that the quantisation noise effect on a discrete
 %plant model mainly depends on three main factors:
@@
 %%
-%\item \textbf{ADC and DAC step:} \red{[again, do we need both?]} these are the main component of quantization noise power, but an $8$-bits converter already reduces the effect of quantization noises in the output for negligible values.
-%%
-%\item \textbf{Signal-to-noise ratio (SNR): } the dependence on the value of $U(z)$ \red{[notice that now we have reduced the problem to depend on the effect of the reference signal transform R(z) - pls revise.]} shows the importance of the SNR for handling quantization noise; for a high SNR of the digital controller, the quantization effect is negligible.
+%\item \textbf{ADC and DAC step:} \red{[again, do we need both?]} these are the main component of quantisation noise power, but an $8$-bits converter already reduces the effect of quantisation noises in the output for negligible values.
+%%
+%\item \textbf{Signal-to-noise ratio (SNR): } the dependence on the value of $U(z)$ \red{[notice that now we have reduced the problem to depend on the effect of the reference signal transform R(z) - pls revise.]} shows the importance of the SNR for handling quantisation noise; for a high SNR of the digital controller, the quantisation effect is negligible.
 This happens during the transient of the system, when high control actions are employed.
@@
 %Finally, Eq.~\eqref{eq:deltaG_final} is a suitable frequency domain model
-%for quantization noise effects on closed-loop systems.  This model depends
+%for quantisation noise effects on closed-loop systems.  This model depends
 %on the plant pulse transfer function ($G(z)$), which is described by
@@
 the ability to produce sound or stable results because they disregard the
-effects of quantization and rounding.  Recent papers on
+effects of quantisation and rounding.  Recent papers on
 implementations/synthesis of LTI digital

### 2016-10-10 paper/paper.tex
Minor changes

@@
 \begin{mylemma}{\cite{Bessa16,fadali}}
-\label{internal_stab_lemma}
+\label{lemma:eq_int_stab}
 A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with transfer functions $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and $\hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is internally stable if and only if:
@@
 \begin{equation}
-\label{lemma:eq_int_stab}
+\label{eq:internal_stab_lemma}
 S(z)=FWL[N_{C}(z)]\hat{N}_{G}(z)+FWL[D_{C}(z)]\hat{D}_{G}(z);
@@
 
-We use this method to check the stability in the $z$-domain for the characteristic polynomial $S(z)$ of 
-the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$, where $Y(z)$ is the 
-closed-loop system output and U(z) is the controller output. 
+We use this method to check the stability in the $z$-domain for the characteristic polynomial $S(z)$ defined in~\eqref{eq:internal_stab_lemma}.
+
+% of the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$, where $Y(z)$ is the closed-loop system output and U(z) is the controller output. 
 %% \red{[unclear: what matrix? We need to clarify the relationship
@@
 $$
-S(z) = a_0Z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N=0, a_0\neq0
+S(z) = a_0z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N=0, a_0\neq0
 $$

### 2016-10-10 paper/paper.tex
Call it a day

@@
 
-The discrete controllers $C_{4}$ and $C_{5}$ for the satellite plant $G_{3}$ 
+The discrete controllers $C_{4}$ and $C_{5}$ for the satellite plant $G_{3}$,discretized with sample time equal to $1 s$ and $2 s$ respectively, 
 are represented by the following z-expression:

### 2016-10-11 paper/paper.tex
Minor changes

@@
 system is a program loop working over bit-vectors of fixed-point arithmetic
-with fixed word length.  The effect of the FWL is included in the model as a
-parametric uncertainty which must be taken into account for the correct
-synthesis of the controller.
+with fixed word length.  \blue{The deterministic effect of the FWL is considered
+and quantization errors are included in the model as a additive uncertainty 
+which must be taken into account for the correct synthesis of the robust controller
+for linear systems with parametric uncertainties.}
 
@@
 
-Although the pulse transfer function $G(z)$ represents adequately $G(s)$ domain, the model $G(z)$ may not be accurate and some uncertainties may not be covered by that model.
+Although the pulse transfer function $G(z)$ represents adequately $G(s)$ in z-domain, the model $G(z)$ may not be accurate and some uncertainties may not be covered by that model.
 These uncertainties may be parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
@@
 
-The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta G_{P}(z)=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$ and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is represented as an additive measurement noise $\nu(z)$.
+The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta G_{P}(z)=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$ and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is represented as an additive (output) measurement noise $\nu(z)$.
 

### 2016-10-11 paper/paper.tex
Minor changes

@@
 \begin{equation}
+\label{eq:complete_unc_model}
 \hat{G}(z)=G(z)+\Delta G_{P}(z)+\Delta G_{Q}(z),
@@
 In order to obtain a sound synthesis of digital controller, the effect of FWL implementation in controller and quantisation noises in closed loop system have to be considered.
-Considering that the quantizer $Q1$ is the source of a white noise with zero mean $\nu_{1}$ and $Q2$ is the source of a white noise with zero mean $\nu_{2}$, the following equation may written for the system in figure~\ref{fig:sampledsystem} considering the parametric uncertainties $\Delta G(z)$ and the FWL effects on controller  ($\hat{C}(z)$):
+Considering that the quantizer $Q1$ is the source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise $\nu_{2}$, the following equation may be written for the system in figure~\ref{fig:sampledsystem} considering the parametric uncertainties $\Delta G(z)$ and the FWL effects on controller  ($\hat{C}(z)$):
 \begin{equation}
@@
 A discrete-time linear system is said to be Bounded-Input and Bounded-Output (BIBO) stable if and only if every pole of its transfer function lies inside the unit circle.
-Analyzing the~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for stability of closed-loop system in figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$ are bounded.
+Analyzing the~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for BIBO stability of closed-loop system in figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$ are bounded.
 
@@
 \label{lemma:eq_int_stab}
-A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with transfer functions $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and $\hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is internally stable if and only if:
+A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with a FWL implementation of the digital controller $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete-model of the plant $\hat{G}(z)=G(z)+\Delta G_{P}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and only if:
 \begin{itemize}

### 2016-10-11 benchmark-runner/simplified_noise.c
fp error bound (semi-sound)

@@ -11,6 +11,7 @@
 #define __OPENLOOP_DEN_SIZE (__CONTROLLER_DEN_SIZE+__PLANT_DEN_SIZE-1)
 #define __OPENLOOP_NUM_SIZE (__CONTROLLER_NUM_SIZE+__PLANT_NUM_SIZE-1)
 
+#define __NORMALIZED
 #ifdef __CPROVER
 #ifndef _FIXEDBV
   #ifndef _EXPONENT_WIDTH
@@ -20,6 +21,7 @@
   #define _FRACTION_WIDTH 11
   #endif
   typedef __CPROVER_floatbv[_EXPONENT_WIDTH][_FRACTION_WIDTH] control_floatt;
+  control_floatt _imp_max=(((1 <<(_EXPONENT_WIDTH-1))-1)<<1)+1;
 #else
   #ifndef _CONTROL_FLOAT_WIDTH
     #define _CONTROL_FLOAT_WIDTH 16
@@ -28,6 +30,7 @@
     #define _CONTORL_RADIX_WIDTH _CONTROL_FLOAT_WIDTH / 2
   #endif
   typedef __CPROVER_fixedbv[_CONTROL_FLOAT_WIDTH][_CONTORL_RADIX_WIDTH] control_floatt;
+  control_floatt _imp_max=(((1 <<_(_CONTROL_FLOAT_WIDTH-1))-1)<<1)+1;
 #endif
   typedef unsigned char cnttype;
 #else
@@ -59,6 +62,9 @@ signed long int _fxp_max;
 signed long int _fxp_min;
 signed long int _fxp_one;
 control_floatt _dbl_lsb;
+control_floatt _poly_error;
+control_floatt _sum_error;
+control_floatt _plant_norm;
 
 struct anonymous0 impl={ .int_bits=_CONTROLER_INT_BITS, .frac_bits=_CONTROLER_FRAC_BITS};
 
@@ -95,6 +101,13 @@ void __DSVERIFIER_assert(_Bool expression)
 void initialization()
 {
   __DSVERIFIER_assert(impl.int_bits+impl.frac_bits < 32);
+#ifdef __NORMALIZED
+  _fxp_one = 1 << (impl.frac_bits + impl.int_bits);
+  _dbl_lsb=1.0/(1 << impl.frac_bits + impl.int_bits);
+  _fxp_min = -(1 << (impl.frac_bits + impl.int_bits -1));
[…]

### 2016-10-11 paper/paper.tex
Minor changes

@@
 
-The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for synthesis of digital controllers able to stabilize closed loop system, considering plant parametric uncertainties ($\Delta G_{P}(z)$), quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital controllers.
-Based on it, the model for plant uncertainty due quantisation noise ($\Delta G(z)$ may be disregarded if the conditions on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise is bounded.
-
-The quantisation noise is indeed bounded, since assumption~\ref{whitenoise} and the Lemmas~\ref{lemma:variance} and~\ref{lemma:boundednoise} are true.
+The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for synthesis of digital controllers able to stabilize closed loop system, considering plant parametric uncertainties ({\it i.e.}, $\Delta G_{P}(z)$), quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital controllers.
+Based on it, the model for plant uncertainty due quantisation noise ({\it i.e.}, $\Delta G_{Q}(z)$) may be disregarded if the conditions on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise is bounded.
+
+The quantisation noise is indeed bounded, since the following assumption~\ref{whitenoise} and the Lemmas~\ref{lemma:variance} and~\ref{lemma:boundednoise} are true.
 

### 2016-10-11 paper/paper.tex
Minor changes

@@
 \label{lemma:variance}
-In particular, \cite{widrow1956} models the quantisation noise as a gaussian
+In particular, Widrow \cite{widrow1956} models the quantisation noise as a gaussian
 model in which the second moment (variance) of the probability density
@@
 \label{lemma:boundednoise}
-The z-transform of the quantisation noise $\nu(z)=\mathcal{Z}\left\lbrace\nu(k)\right\rbrace$ in figure~\ref{fig:digsystem1} may be calculated through the power spectral density of $\nu(k)$, thus:
-\begin{equation}
-\nu(z)= \sigma_{Q}^{2}.
+The power spectral density of the quantisation noise (supposed white) $S_{\nu}(z)$ is bounded and may be computed through the z-transform of autocorrelation function of $\nu(k)$, thus:
+\begin{equation}
+S_{\nu}(z)= \sigma_{Q}^{2}=\frac{q^{2}}{12}.
 \end{equation}
@@
 \begin{equation}
-\nu(z)=  \sum\limits_{k=-\infty}^{\infty}{R_{\nu\nu}(k)z^{-k}} = \sigma_{Q}^{2}.
+\nu(z)=  \sum\limits_{k=-\infty}^{\infty}{R_{\nu\nu}(k)z^{-k}} = \sigma_{Q}^{2},
+\end{equation}
+considering the Lemma~\ref{lemma:variance}:
+\begin{equation}
+\nu(z)=  \frac{q^{2}}{12}.
 \end{equation}
 \end{proof}
+
+Finally, the quantisation noise may be considered a energy-bounded signal (Lemma~\ref{lemma:boundednoise}) and thus $\hat{Y}(z)$ will be bounded and the closed-loop system stable if the conditions in Lemma~\ref{lemma:eq_int_stab} are followed.
 

### 2016-10-12 paper/paper.tex
typos

@@
 in the literature~\cite{Franklin15}, the zero-order hold (ZOH)
-discretization is more suitable for representing the sampling and holding
+discretization is more suitable for representing the sample and hold
 processes that are typically employed in complex systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretization
@@
 The pulse transfer function $G(z)$ is a z-domain model that relates the
-output sampled by a ADC and the digital input provided by ZOH.  It is equivalent at the sample times ({\it i.e.}, $t=kT$) to the continuous transfer
+output sampled by an ADC and the digital input provided by the ZOH.  It is equivalent at the sample times ({\it i.e.}, $t=kT$) to the continuous transfer
 function $G(s)$ driven by ZOH.  This pulse transfer function can be
@@
 For the sake of brevity, 
-we will use only the notation $G(z)$ to represent the pulse transfer function.
+we will use the notation $G(z)$ to represent the pulse transfer function.
 %
@@
 be disregarded.
-Additionally, the pulse transfer function obtained via \eqref{eq:pulsetf} using an appropriate sample rate ({\it i.e.}, obeying the Nyquist sampling conditions)  may be considered a sufficient discrete-time representation of $G(s)$.
+Additionally, the pulse transfer function obtained via \eqref{eq:pulsetf} using an appropriate sample rate ({\it i.e.}, obeying the Nyquist sampling conditions)  is a precise discrete-time representation of $G(s)$.
 %
@@
 
-Although the pulse transfer function $G(z)$ represents adequately $G(s)$ in z-domain, the model $G(z)$ may not be accurate and some uncertainties may not be covered by that model.
+Although the pulse transfer function $G(z)$ represents adequately $G(s)$ in the z-domain, the model $G(z)$ may not be accurate and some uncertainties may not be covered by that model.
 These uncertainties may be parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:

### 2016-10-12 paper/paper.tex
more fixes

@@
 \end{equation}
+In the case of a synthesised controller, because the synthesis is performed using FWL, $\hat{C}(z) \equiv C(z)$.
 
@@
 \end{equation}
-\item the direct loop product $\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle;
-\item the controller $\hat{C}(z)$ is a minimum-phase system. 
+\item the direct loop product $\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle.
 \end{itemize}
@@
 \begin{equation}
-R_{\nu\nu}(\tau)=E[\nu(t+\tau)\nu]=\sigma_{Q}^{2}\cdot \delta(\tau),
+R_{\nu\nu}(\tau)=E[\nu(t+\tau)\nu(t)]=\sigma_{Q}^{2}\cdot \delta(\tau),
 \end{equation}

### 2016-10-12 paper/paper.tex
hscc17

@@
 discrete equivalent coefficients $b$ and $a$~\cite{Astrom08} via ZOH
-discretization.  Although there are several discretization methods available
+discretization.
+
+\red{[why do we discuss the ZOH at this point?]}
+
+Although there are several discretization methods available
 in the literature~\cite{Franklin15}, the zero-order hold (ZOH)
@@
 output sampled by an ADC and the digital input provided by the ZOH.  It is equivalent at the sample times ({\it i.e.}, $t=kT$) to the continuous transfer
-function $G(s)$ driven by ZOH.  This pulse transfer function can be
-computed as
+function $G(s)$ driven by ZOH.  
+\red{[what does it mean that it is continuous ``at the sample times''?
+We're working in frequency.
+Are you matching poles?
+There is still no clear relationship between continuous and samples transfer functions, it is not formal in my opinion.]}
+This pulse transfer function can be computed as
 %
@@
 The DAC interpolator is an ideal ZOH; it takes the discrete value of control
-signal $\tilde u(k)$ at instant $k$ and produces a rectangular pulse of height
+signal $\tilde u(k)$ \red{[is this a new notation over the time domain?
+It does not reflect the signals used in the plot -- utterly confusing!]} at instant $k$ and produces a rectangular pulse of height
 $u(k)$ and width equal to the sample time $T$.

### 2016-10-12 paper/paper.tex
hscc17

@@
 \label{assumption:cont_and_plant}
-The controller and the plant are linear time-invariant (LTI) systems, {\it i.e.}, any source of
+The controller and the plant are linear time-invariant (LTI) systems, {\it i.e.}, 
+\red{[!! of course, we're working with transfer functions!!]}
+any source of
 nonlinearity ({\it e.g.}, saturation, overflow, ADC/DAC nonlinearities) will
-be disregarded.
-Additionally, the pulse transfer function obtained via \eqref{eq:pulsetf} using an appropriate sample rate ({\it i.e.}, obeying the Nyquist sampling conditions)  is a precise discrete-time representation of $G(s)$.
+be disregarded \red{[how is this related to ADC/DAC? very confusing.]}
+.
+Additionally, the pulse transfer function is obtained via \eqref{eq:pulsetf} using an appropriate sample rate ({\it i.e.}, obeying the Nyquist sampling conditions)  is a precise discrete-time representation of $G(s)$.
+\red{[clarify this: this cannot be an assumption, since it is hinging on a specific numerical scheme.
+Assumptions deal with structural properties for example, or choices of certain parameters ...
+]}
 %
@@
 
-Although the pulse transfer function $G(z)$ represents adequately $G(s)$ in the z-domain, the model $G(z)$ may not be accurate and some uncertainties may not be covered by that model.
-These uncertainties may be parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
+Although the pulse transfer function $G(z)$ represents adequately \red{[clarify adverb]} $G(s)$ in the z-domain, 
+the model $G(z)$ may not be accurate and some uncertainties may not be covered by that model. 
+These uncertainties may be \red{[clarify use of conditional tense]} parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
 \begin{equation}
@@
 \end{equation}
-that may be represented by the following transfer function:
+that may be \red{[\ldots]} represented by the following transfer function:
 \begin{equation}
@@
 \end{equation}
+\red{[same order?]}
 
@@
 
-A typical hybrid system is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$, $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.
+A typical hybrid system \red{[clarify the adjective ``hybrid'']} is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$
+\red{[this Delta term now refers to the continuous plant? this is not what has been discussed before, nor what is in some of the plots.]} 
+, $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.
 
@@
 where $\Delta G_{P}(z)$ is the term that corresponds to the parametric uncertainties and $\Delta G_{Q}(z)$ is the term that reflects the quantisation effects on the plant model.
-Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.
+\red{[next figure is a bit unnecessary, does not ad much to the previous one.]} Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.
 
@@
 %size $F$, we shall denote this domain as $\mathbb{R}\langle I,F \rangle$ 
-and assume that there exists a function $FWL[\cdot]:\mathbb{R}^{n}\rightarrow \mathbb{R}^{n}\langle I,F \rangle$, which applies the FWL effects to a polynomial.
+and assume that there exists a function $FWL[\cdot]:\mathbb{R}^{n}\rightarrow \mathbb{R}^{n}\langle I,F \rangle$, which applies the FWL effects to a polynomial \red{[explain index n!
+why do you need to work on a Euclidean domain?]}.
 Thus the perturbed controller model $\hat{C}(z)$ may be computed from the original model $C(z)=\frac{N_{C}(z)}{D_{C}(z)}$ using the following expression:
@@
 In the case of a synthesised controller, because the synthesis is performed using FWL, $\hat{C}(z) \equiv C(z)$.
+
+\red{[what is the relationship between FWL effects over C, and the parametric uncertainty Delta Gp over the plant?]}
 
@@
 \label{lemma:eq_int_stab} 
-A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with a FWL implementation of the digital controller $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete-model of the plant $\hat{G}(z)=G(z)+\Delta G_{P}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and only if:
+A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with a FWL implementation of the digital controller $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete model of the plant $\hat{G}(z)=G(z)+\Delta G_{P}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and only if:
+\red{[this statement does not seem to encompass the quantisation effects on the plant?]} 
 \begin{itemize}
@@
 The quantisation noise is indeed bounded, since the following assumption~\ref{whitenoise} and the Lemmas~\ref{lemma:variance} and~\ref{lemma:boundednoise} are true.
+
+\red{[first: lemmae precede theorems. \\
+second: bounded is not energy bounded. ]}
 

### 2016-10-12 benchmarks/CruiseControl/CruiseControl02_unc01.c

@@ -1,0 +1,5312 @@
+// tag-#anon#ST[ARR100{F64}$F64$'a'|S32'a_size'|U32'$pad0'|ARR100{F64}$F64$'b'|S32'b_size'|U32'$pad1'|F64'sample_time'|ARR100{F64}$F64$'a_uncertainty'|ARR100{F64}$F64$'b_uncertainty']
+// file /home/lucascordeiro/dsverifier/bmc/core/definitions.h line 144
+struct anonymous$0;
+
+// tag-#anon#ST[ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'A'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'B'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'C'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'D'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'states'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'outputs'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'inputs'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'K'|U32'nStates'|U32'nInputs'|U32'nOutputs'|U32'$pad0']
+// file /home/lucascordeiro/dsverifier/bmc/core/definitions.h line 156
+struct anonymous$1;
+
+// tag-#anon#ST[S32'int_bits'|S32'frac_bits'|F64'max'|F64'min'|S32'default_realization'|U32'$pad0'|F64'delta'|S32'scale'|U32'$pad1'|F64'max_error']
+// file /home/lucascordeiro/dsverifier/bmc/core/definitions.h line 171
+struct anonymous$3;
+
+// tag-#anon#ST[S32'push'|S32'in'|S32'sbiw'|S32'cli'|S32'out'|S32'std'|S32'ldd'|S32'subi'|S32'sbci'|S32'lsl'|S32'rol'|S32'add'|S32'adc'|S32'adiw'|S32'rjmp'|S32'mov'|S32'sbc'|S32'ld'|S32'rcall'|S32'cp'|S32'cpc'|S32'ldi'|S32'brge'|S32'pop'|S32'ret'|S32'st'|S32'brlt'|S32'cpi']
[…]

### 2016-10-12 benchmarks/Satellite/SatelliteB2unc01.c

@@ -1,0 +1,5311 @@
+// tag-#anon#ST[ARR100{F64}$F64$'a'|S32'a_size'|U32'$pad0'|ARR100{F64}$F64$'b'|S32'b_size'|U32'$pad1'|F64'sample_time'|ARR100{F64}$F64$'a_uncertainty'|ARR100{F64}$F64$'b_uncertainty']
+// file /home/lucascordeiro/dsverifier/bmc/core/definitions.h line 144
+struct anonymous$0;
+
+// tag-#anon#ST[ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'A'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'B'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'C'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'D'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'states'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'outputs'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'inputs'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'K'|U32'nStates'|U32'nInputs'|U32'nOutputs'|U32'$pad0']
+// file /home/lucascordeiro/dsverifier/bmc/core/definitions.h line 156
+struct anonymous$1;
+
+// tag-#anon#ST[S32'int_bits'|S32'frac_bits'|F64'max'|F64'min'|S32'default_realization'|U32'$pad0'|F64'delta'|S32'scale'|U32'$pad1'|F64'max_error']
+// file /home/lucascordeiro/dsverifier/bmc/core/definitions.h line 171
+struct anonymous$3;
+
+// tag-#anon#ST[S32'push'|S32'in'|S32'sbiw'|S32'cli'|S32'out'|S32'std'|S32'ldd'|S32'subi'|S32'sbci'|S32'lsl'|S32'rol'|S32'add'|S32'adc'|S32'adiw'|S32'rjmp'|S32'mov'|S32'sbc'|S32'ld'|S32'rcall'|S32'cp'|S32'cpc'|S32'ldi'|S32'brge'|S32'pop'|S32'ret'|S32'st'|S32'brlt'|S32'cpi']
[…]

### 2016-10-12 benchmarks/SpringMassDamper/SpringMassDamper_unc01.c

@@ -1,0 +1,5311 @@
+// tag-#anon#ST[ARR100{F64}$F64$'a'|S32'a_size'|U32'$pad0'|ARR100{F64}$F64$'b'|S32'b_size'|U32'$pad1'|F64'sample_time'|ARR100{F64}$F64$'a_uncertainty'|ARR100{F64}$F64$'b_uncertainty']
+// file /home/lucascordeiro/dsverifier/bmc/core/definitions.h line 144
+struct anonymous$0;
+
+// tag-#anon#ST[ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'A'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'B'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'C'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'D'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'states'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'outputs'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'inputs'|ARR20{ARR20{F64}$F64$}$ARR20{F64}$F64$$'K'|U32'nStates'|U32'nInputs'|U32'nOutputs'|U32'$pad0']
+// file /home/lucascordeiro/dsverifier/bmc/core/definitions.h line 156
+struct anonymous$1;
+
+// tag-#anon#ST[S32'int_bits'|S32'frac_bits'|F64'max'|F64'min'|S32'default_realization'|U32'$pad0'|F64'delta'|S32'scale'|U32'$pad1'|F64'max_error']
+// file /home/lucascordeiro/dsverifier/bmc/core/definitions.h line 171
+struct anonymous$2;
+
+// tag-#anon#ST[S32'push'|S32'in'|S32'sbiw'|S32'cli'|S32'out'|S32'std'|S32'ldd'|S32'subi'|S32'sbci'|S32'lsl'|S32'rol'|S32'add'|S32'adc'|S32'adiw'|S32'rjmp'|S32'mov'|S32'sbc'|S32'ld'|S32'rcall'|S32'cp'|S32'cpc'|S32'ldi'|S32'brge'|S32'pop'|S32'ret'|S32'st'|S32'brlt'|S32'cpi']
[…]

### 2016-10-12 paper/paper.tex
review introduction

--- 2016-10-12 paper/paper.tex
@@
 in their capabilities, be it a low number of gates in an FPGA or short word
-lengths for microcontrollers.  In most cases a floating-point implementation
+lengths for microcontrollers.  In most cases, a floating-point implementation
 is not feasible and the system can benefit from the added resolution of a
@@
 aspects ({\it i.e.}, fixed-point arithmetic and word-length)~\cite{Bessa16}. 
-In particular, Bessa {\it et al.} considers finite-word length (FWL) effects
+In particular, Bessa {\it et al.} consider finite-word length (FWL) effects
 over digital controllers and also parameter uncertainties in the context of
@@
 proposed by Bessa {\it et al.} is incomplete, given that false alarms can be
-produced due to the quantisation effects.  Additionally, the authors do not
+produced due to quantisation effects.  Additionally, the authors do not
 find a parametric solution for a digital controller given as a continuous
@@
 
-In this paper, however, we explore the automatic synthesis of {\em
-correct-by-construction} dgital controllers, which reduces the deveopment
+Our work makes two major contributions. First, we explore the automatic synthesis 
+of {\em correct-by-construction} digital controllers, which reduces the development
 cost and design time for a number of models.  In particular, we are
@@
 
-Since the digital control synthesis is performed over a hybrid model, where
-the plant displays a continuous behaviour and the controller operates in
+Second, since the digital control synthesis is performed over a hybrid model, 
+where the plant displays a continuous behaviour and the controller operates in
 both discrete time and state-space, we initially translate the problem into
-a single domain which represents a bi-simulation of the original dynamics. 
+a single domain, which represents a bi-simulation of the original dynamics. 
 Given our primary interest in evaluating digital effects in addition to
@@
 system is a program loop working over bit-vectors of fixed-point arithmetic
-with fixed word length.  \blue{The deterministic effect of the FWL is considered
-and quantization errors are included in the model as a additive uncertainty 
+with fixed word length.  The deterministic effect of the FWL is considered
+and quantization errors are included in the model as an additive uncertainty, 
 which must be taken into account for the correct synthesis of the robust controller
-for linear systems with parametric uncertainties.}
+for linear systems with parametric uncertainties.
 

### 2016-10-12 paper/paper.tex
soundness on FP operations

@@
 
-Two approaches have been taken to synthesise a stabe controller based on this model.
-The first uses a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is upper bound at the source by selecting a conservative $\Delta{G}_b(z)$ that encompasses its propagation over a number of operations.
-The verification phase produces a counterexample if some instance of $\mathfrak{G}(z)$ does not verify the properties and the CEGIS loop iteratively looks for a new controller that verifies the supplied counterexamples.
-Although it is fast, the conservative error calculation can be restrictive to a small number of benchmarks.
-
-The second approch uses interval arithmetic, representing the coefficients $[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\ {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
+Two approaches have been taken to synthesise a stable controller based on this model.
+The first uses interval arithmetic, representing the coefficients $[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\ {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
 and rounding operations outwards during the process. This results in a tighter calculation of the error at the cost of performance.
+
+The second approach uses a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is assumed to be within the expected bounds and verified after synthesis using the interval version of the program.
+The first verification phase produces a counterexample if some instance of $\mathfrak{G}(z)$ does not verify the properties and the CEGIS loop iteratively looks for a new controller that verifies the supplied counterexamples.
+The second phase verifies the propagation of the error in the fixed point calculations.
+If the second phase fails verification, we increase the precision of the analyser and feed the CEGIS loop again to find a sound solution.
+The resulting increase in speed of this approach over the former, which is of several orders of magnitude, vouches for the use of CEGIS in most of our benchmarks.
 %------------------------------------

### 2016-10-12 paper/paper.tex
hscc17

--- 2016-10-12 paper/paper.tex
@@
 in their capabilities, be it a low number of gates in an FPGA or short word
-lengths for microcontrollers.  In most cases, a floating-point implementation
+lengths for microcontrollers.  In most cases a floating-point implementation
 is not feasible and the system can benefit from the added resolution of a
@@
 aspects ({\it i.e.}, fixed-point arithmetic and word-length)~\cite{Bessa16}. 
-In particular, Bessa {\it et al.} consider finite-word length (FWL) effects
+In particular, Bessa {\it et al.} considers finite-word length (FWL) effects
 over digital controllers and also parameter uncertainties in the context of
@@
 proposed by Bessa {\it et al.} is incomplete, given that false alarms can be
-produced due to quantisation effects.  Additionally, the authors do not
+produced due to the quantisation effects.  Additionally, the authors do not
 find a parametric solution for a digital controller given as a continuous
@@
 
-Our work makes two major contributions. First, we explore the automatic synthesis 
-of {\em correct-by-construction} digital controllers, which reduces the development
+In this paper, however, we explore the automatic synthesis of {\em
+correct-by-construction} dgital controllers, which reduces the deveopment
 cost and design time for a number of models.  In particular, we are
@@
 
-Second, since the digital control synthesis is performed over a hybrid model, 
-where the plant displays a continuous behaviour and the controller operates in
+Since the digital control synthesis is performed over a hybrid model, where
+the plant displays a continuous behaviour and the controller operates in
 both discrete time and state-space, we initially translate the problem into
-a single domain, which represents a bi-simulation of the original dynamics. 
+a single domain which represents a bi-simulation of the original dynamics. 
 Given our primary interest in evaluating digital effects in addition to
@@
 system is a program loop working over bit-vectors of fixed-point arithmetic
-with fixed word length.  The deterministic effect of the FWL is considered
-and quantization errors are included in the model as an additive uncertainty, 
+with fixed word length.  \blue{The deterministic effect of the FWL is considered
+and quantization errors are included in the model as a additive uncertainty 
 which must be taken into account for the correct synthesis of the robust controller
-for linear systems with parametric uncertainties.
+for linear systems with parametric uncertainties.}
 
@@
 \end{equation}
+\red{[where is this new variable used later?]}
 
@@
 
+\red{[relate this discussion with the FWL one (and related notations) above.]}
+
 Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
@@
 Two approaches have been taken to synthesise a stabe controller based on this model.
-The first uses a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is upper bound at the source by selecting a conservative $\Delta{G}_b(z)$ that encompasses its propagation over a number of operations.
+The first uses a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is upper bound at the source by selecting a conservative $\Delta{G}_b(z)$ that encompasses \red{[how?
+is this always possible?]} its propagation over a number of operations.
 The verification phase produces a counterexample if some instance of $\mathfrak{G}(z)$ does not verify the properties and the CEGIS loop iteratively looks for a new controller that verifies the supplied counterexamples.

### 2016-10-12 paper/paper.tex
some fixes on AAs comments

--- 2016-10-12 paper/paper.tex
@@
 \label{lemma:eq_int_stab} 
-A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with a FWL implementation of the digital controller $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete model of the plant $\hat{G}(z)=G(z)+\Delta G_{P}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and only if:
-\red{[this statement does not seem to encompass the quantisation effects on the plant?]} 
+A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with a FWL implementation of the digital controller $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete model of the plant $\hat{G}(z)=G(z)+\Delta G_{P}(z)+\Delta G_{Q}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and only if:
 \begin{itemize}
@@
 
-\red{[first: lemmae precede theorems. \\
-second: bounded is not energy bounded. ]}
+\red{[first: lemmae precede theorems. ]}
 
@@
 The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
-$Q2$) are energy bounded uncorrelated white noises.
+$Q2$) are bounded uncorrelated white noises.
 % 

### 2016-10-12 paper/paper.tex
Fixes on AA comments

@@
 
+\begin{myassumption}
+%
+The Sample and Hold of the ADC and the ZOH of the DAC are synchronized, {\it i.e.}, there is no delay between
+sampling the plant output at ADC and updating the DAC accordingly. The DAC interpolator is an ideal ZOH.
+%
+\end{myassumption}
+
 \begin{mylemma}\cite{astrom1997computer}
 %
-The pulse transfer function $G(z)$ is a z-domain model that relates the
-output sampled by an ADC and the digital input provided by the ZOH.  It is equivalent at the sample times ({\it i.e.}, $t=kT$) to the continuous transfer
-function $G(s)$ driven by ZOH.  
-\red{[what does it mean that it is continuous ``at the sample times''?
-We're working in frequency.
-Are you matching poles?
-There is still no clear relationship between continuous and samples transfer functions, it is not formal in my opinion.]}
-This pulse transfer function can be computed as
+Given a synchronized ZOH input and sample and hold output on the plant with a sample time $T$ satisfying Nyquist's sampling criteria, the discrete pulse transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$ which can be computed using the following formula:
 %
@@
 %
-For the sake of brevity, 
-we will use the notation $G(z)$ to represent the pulse transfer function.
+For the sake of brevity, we will use the notation $G(z)$ to represent the pulse transfer function.
 %
@@
 
-\begin{myassumption}
-%
-The DAC and ADC are synchronized, {\it i.e.}, there is no delay between
-sampling the plant output at ADC and updating the DAC accordingly.
-%
-\end{myassumption}
-
-\begin{myassumption}
-%
-The DAC interpolator is an ideal ZOH; it takes the discrete value of control
-signal $\tilde u(k)$ \red{[is this a new notation over the time domain?
-It does not reflect the signals used in the plot -- utterly confusing!]} at instant $k$ and produces a rectangular pulse of height
-$u(k)$ and width equal to the sample time $T$.
-%
-\end{myassumption}
-
-\begin{myassumption}
-%
-\label{assumption:cont_and_plant}
-The controller and the plant are linear time-invariant (LTI) systems, {\it i.e.}, 
-\red{[!! of course, we're working with transfer functions!!]}
-any source of
-nonlinearity ({\it e.g.}, saturation, overflow, ADC/DAC nonlinearities) will
-be disregarded \red{[how is this related to ADC/DAC? very confusing.]}
-.
-Additionally, the pulse transfer function is obtained via \eqref{eq:pulsetf} using an appropriate sample rate ({\it i.e.}, obeying the Nyquist sampling conditions)  is a precise discrete-time representation of $G(s)$.
-\red{[clarify this: this cannot be an assumption, since it is hinging on a specific numerical scheme.
-Assumptions deal with structural properties for example, or choices of certain parameters ...
-]}
-%
-\end{myassumption}
-
-Although the pulse transfer function $G(z)$ represents adequately \red{[clarify adverb]} $G(s)$ in the z-domain, 
-the model $G(z)$ may not be accurate and some uncertainties may not be covered by that model. 
-These uncertainties may be \red{[clarify use of conditional tense]} parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
+Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (\emph{ie} $\Delta{G}_p(s)$), errors in the numeric calculations, or roundoffs in the quantization.
+These uncertainties may be parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
 \begin{equation}
@@
 \end{equation}
-that may be \red{[\ldots]} represented by the following transfer function:
-\begin{equation}
-\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}}.
+which will be represented by the following transfer function:
+\begin{equation}
+\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}} : N_G \geq M_G .
 \end{equation}
@@
 
-A typical hybrid system \red{[clarify the adjective ``hybrid'']} is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$
-\red{[this Delta term now refers to the continuous plant? this is not what has been discussed before, nor what is in some of the plots.]} 
+A typical hybrid system, with a continuous plant and discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$
 , $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.
@@
 	minimum height=1cm,
-        label=\textbf{Plant}] (gs) {{\sc $G(s) + \Delta G(s)$}};
+        label=\textbf{Plant}] (gs) {{\sc $G(s) + \Delta G_p(s)$}};
    \node[draw=none] (ud) at ([xshift=-2cm,yshift=.15cm]gs)  {$U(s)$};

### 2016-10-12 paper/paper.tex
Updated running example.

@@
 \label{Eq:running-example-controller-quantized}
-\resizebox{0.5\textwidth}{!}{
-$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
-{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375},$
-}
+C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
+{+}1.895996}{z^2{-}1.843994z+0.849594},
 \end{equation} 
@@
 in Sec.~\ref{sec:running-ex}.
-We start with the candidate solution given below, which has all coefficients 0.
+We start with the candidate solution given below at $I_b=16,F_b=24$,
+which has all coefficients 0.
 Note that the digital controller is designed with typical control system
@@
 \begin{array}{ll}
-\Delta N_G(z) = 0.02634525299072265625\\
-\Delta D_G(z) = 0.9979267120361328125z-0.99768829345703125
+\Delta N_G(z) = 0.026506\\
+\Delta D_G(z) = 1.000610z+1.002838
 \end{array}
@@
 \begin{array}{ll}
-N_C(z) {=} 4.00888156890869140625z^2{-}0.00041961669921875z\\
-\qquad\qquad -0.000213623046875\\
-D_C(z) {=} -0.003753662109375z^2{+}7.37355804443359375z \\
-\qquad\qquad -7.2847900390625\\
+N_C(z) {=} 12.402664z^2{-}11.439667z{+}0.596756\\
+D_C(z) {=} 4.003906z^2{-}0.287949z{+}0.015625\\
 \end{array}
@@
 In the second {\sc verify} phase, we check whether the current candidate
-solution above is the final solution. It is not and we get a new counterexample:
+solution above is the final solution. It is not and the verifier signals
+that it is due to lack of precision. We thus increase our precision to
+$I_b=20,F_b=28$.
+%
+We stay in the {\sc verify} phase and receive a new counterexample at
+higher precision:
+%
 $$
 \begin{array}{ll}
-\Delta N_G(z) = 0.02644824981689453125\\
-\Delta D_G(z) {=} 1.00053310394287109375z{-}1.0014629364013671875
+\Delta N_G(z) {=} 0.026314\\
+\Delta D_G(z) {=} 0.999024z{-}1.004785
 \end{array}
@@
 %\blue{[Nice, now I'm in the groove. Next unfolds well.] }
-After adding this new counterexample to the set of {\sc inputs}, in the 
-next {\sc synthesise} phase, we get a new candidate solution that holds
-for both uncertainties in {\sc Inputs}:
+Since previous counterexamples were attained at lower precision, we 
+remove them from the counterexample set. In the next {\sc synthesise}
+phase, we get a new candidate solution that holds for the newly
+inserted counterexample:
 
@@
 \begin{array}{ll}
-N_C(z) {=} 7.515781402587890625z^2{-}4.385616302490234375z\\
-\qquad\qquad +4.142093658447265625\\
-D_C(z) {=} -3.52398681640625z^2{-}1.530254364013671875z \\
-\qquad\qquad +7.58094024658203125\\
+N_C(z) {=} 11.035202z^2{+}5.846100z{+}4.901855\\
+D_C(z) {=} 1.097901z^2{+}0.063110z{+}0.128357\\
 \end{array}

### 2016-10-12 paper/paper.tex
Added result table draft.
Changes on section 2

@@
 %------------------------------------
+\subsection{Sampling and Holding in Hybrid Systems}
+\label{ssec:SandH}
+%------------------------------------
+
+The digital controllers synthesized in this paper are typically used in closed loops with continuous (and physical) plants.
+Thus, the proposed approach have to consider dynamics of continuous parts of system ({\it e.g.}, plant) and discrete parts ({\it e.g.}, digital controller), {\it i.e.} the synthesized controller have to consider the issues related to the hybrid systems studies.
+
+For this purpose, the design procedure is based on a discretized model for a continuous plant.
+For transfer function models, we are interested in a $z$-domain transfer function that considers all the aspects about the continuous plant ($G(s)$) and the sampling and hold process.
+
+Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it
+i.e.}, a continuous model of the plant must be discretized to obtain the
+discrete equivalent coefficients $b$ and $a$~\cite{Astrom08} via ZOH
+discretization.
+
+\red{[why do we discuss the ZOH at this point?]}
+
+Although there are several discretization methods available
+in the literature~\cite{Franklin15}, the zero-order hold (ZOH)
+discretization is more suitable for representing the sample and hold
+processes that are typically employed in complex systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretization
+models the exact effect of sampling and DAC interpolation over the plant.
+
+\begin{myassumption}
+%
+The Sample and Hold of the ADC and the ZOH of the DAC are synchronized, {\it i.e.}, there is no delay between
+sampling the plant output at ADC and updating the DAC accordingly. The DAC interpolator is an ideal ZOH.
+%
+\end{myassumption}
+
+\begin{mylemma}\cite{astrom1997computer}
+%
+Given a synchronized ZOH input and sample and hold output on the plant with a sample time $T$ satisfying Nyquist's sampling criteria, the discrete pulse transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$ which can be computed using the following formula:
+%
+\begin{equation}
+\label{eq:pulsetf}
+G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
+\end{equation}
+%
+For the sake of brevity, we will use the notation $G(z)$ to represent the pulse transfer function.
+%
+\end{mylemma}
+
+%------------------------------------
 \subsection{Verifying Closed-loop Control Systems}
@@
 and $N_{(\cdot)}$ and $M_{(\cdot)}$ denote the number of poles and zeros for the corresponding block.
-
-Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it
-i.e.}, a continuous model of the plant must be discretized to obtain the
-discrete equivalent coefficients $b$ and $a$~\cite{Astrom08} via ZOH
-discretization.
-
-\red{[why do we discuss the ZOH at this point?]}
-
-Although there are several discretization methods available
-in the literature~\cite{Franklin15}, the zero-order hold (ZOH)
-discretization is more suitable for representing the sample and hold
-processes that are typically employed in complex systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretization
-models the exact effect of sampling and DAC interpolation over the plant.
-
-\begin{myassumption}
-%
-The Sample and Hold of the ADC and the ZOH of the DAC are synchronized, {\it i.e.}, there is no delay between
-sampling the plant output at ADC and updating the DAC accordingly. The DAC interpolator is an ideal ZOH.
-%
-\end{myassumption}
-
-\begin{mylemma}\cite{astrom1997computer}
-%
-Given a synchronized ZOH input and sample and hold output on the plant with a sample time $T$ satisfying Nyquist's sampling criteria, the discrete pulse transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$ which can be computed using the following formula:
-%
-\begin{equation}
-\label{eq:pulsetf}
-G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
-\end{equation}
-%
-For the sake of brevity, we will use the notation $G(z)$ to represent the pulse transfer function.
-%
-\end{mylemma}
 

### 2016-10-12 paper/paper.tex
Updated experiments table data.
Extended experimental discussion.

@@
 \label{experimental-results}
+We outline the runtimes required to synthesise a stable controller for each
+benchmark in Table~\ref{tab:results}. For most benchmarks the conjecture explained
+in section~\ref{fixedpoint_verification} holds and the inductive back-end is able
+to find a stable solution in less than one minute. This is possible if the inductive
+solutions need to be refined with few counterexamples and fixed point precision
+increases. However, some of our benchmarks did not meet these criteria. In these
+cases the interval arithmetic back-end was able to complement the inductive approach
+and synthesise a solution instead, albeit with significantly larger runtimes.
+
+\begin{figure}[H]
+\centering
+\begin{tabular}{l | r l r l}
+Benchmark              & Base     &         & Unc     & \\\cline{1-4}
+CruiseControl02        & 17\,s    &         & 46\,s   & \\
+SatelliteB2            & 7\,s     &         & 6601\,s & \tbmark\\
+SatelliteC2            & 369\,s   & \tbmark & 76\,s   & \tbmark\\
+SpringMassDamper       &          &         &         & 
+\end{tabular}
+
+\vspace{0.5em}
+\scriptsize{* = solved with interval back-end}
+\vspace{0.5em}
+
+\caption{Experimental results. \label{tab:results}}
+\end{figure}
 %---------------------------------
+
+We conclude from these results that the inductive back-end provides excellent performance
+for synthesising stable controllers in the majority of the benchmarks, and can be
+complemented using the interval arithmetic back-end where the inductive conjectures fail
+too frequently. Both back-ends enabled controller synthesis for all benchmarks within
+reasonable time frames.
 

### 2016-10-12 paper/paper.tex
Changes on section 2

--- 2016-10-12 paper/paper.tex
@@
 For this purpose, the design procedure is based on a discretized model for a continuous plant.
-For transfer function models, we are interested in a $z$-domain transfer function that considers all the aspects about the continuous plant ($G(s)$) and the sampling and hold process.
+Considering only transfer function models, we are interested in a $z$-domain transfer function that considers all the aspects about the continuous plant ($G(s)$) and the sampling and hold process.
 
@@
 i.e.}, a continuous model of the plant must be discretized to obtain the
-discrete equivalent coefficients $b$ and $a$~\cite{Astrom08} via ZOH
+discrete equivalent coefficients via ZOH
 discretization.
 
-\red{[why do we discuss the ZOH at this point?]}
+%\red{[why do we discuss the ZOH at this point?]}
 
@@
 
-Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (\emph{ie} $\Delta{G}_p(s)$), errors in the numeric calculations, or roundoffs in the quantization.
+Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (\emph{i.e.} $\Delta{G}_p(s)$), errors in the numeric calculations, or roundoffs in the quantization.
 These uncertainties may be parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
@@
 where $\Delta G_{P}(z)$ is the term that corresponds to the parametric uncertainties and $\Delta G_{Q}(z)$ is the term that reflects the quantisation effects on the plant model.
-\red{[next figure is a bit unnecessary, does not ad much to the previous one.]} Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.
-
-\begin{figure}[ht]
-\centering
-
-\tikzset{add/.style n args={4}{
-    minimum width=6mm,
-    path picture={
-        \draw[circle] 
-            (path picture bounding box.south east) -- (path picture bounding box.north west)
-            (path picture bounding box.south west) -- (path picture bounding box.north east);
-        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
-        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
-        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
-        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
-        }
-    }
- }
-
-\resizebox{.5\textwidth}{!}{
- \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
-     semithick, initial text=, ampersand replacement=\&,]
-
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
-  %
-	\& 
-	\&
-	\& \coordinate (aux7); 
-	\& \node[rectangle,draw,
-	minimum width=1cm,
-	minimum height=1cm] (deltag2) {{\sc $\Delta G_{Q}(z)$}};
-	\& \coordinate (aux8);\\
-    \node[draw=none] (r) {$R(z)$};
-%   \& \coordinate (aux0);
-   \& \node[circle,add={-}{+}{}{}] (circle) {};
-   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
-   \& \node[rectangle,draw,
-	minimum width=1cm,
-	minimum height=1cm,
-        label=\textbf{Controller}] (cz) {{\sc C(z)}};
-   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
-   \& \coordinate (aux4);
-   \& \node[rectangle,draw,
-	minimum width=1cm,
-	minimum height=1cm,
-        label=\textbf{Plant}] (gs) {{\sc G(z)}};
-   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
-   \& \node[circle,add={+}{+}{+}{}] (circle2) {};
-%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
-%   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
-   \& \coordinate (aux1);
-   \& \node[draw=none] (yz) {$\hat{Y}(z)$};\\
-   \& 
-   \&
-   \& \coordinate (aux5); 
-   \& \node[rectangle,draw,
-	minimum width=1cm,
-	minimum height=1cm] (deltag) {{\sc $\Delta G_{P}(z)$}};
-   \& \coordinate (aux6);\\
-   \& \coordinate (aux3); 
-   \&
-   \& 
-   \& 
-   \&
-   \& \coordinate (aux2);\\
-  };
-
-%  \path[->] (v1) edge (q1.north);
-%  \path[->] (v2) edge (q2.north);
-  \path[->] (r) edge (circle.west);
-%  \path[->] (nu) edge (circle2.north);
-  \path[->] (aux1) edge (yz);
-  \path  
-   (aux4.north) edge (aux5.south)
-   (aux4.north) edge (aux7.south)
-   (aux5.east) edge (deltag.west)
-   (aux7.east) edge (deltag2.west)
-   (deltag.east) edge (aux6.west)
-   (deltag2.east) edge (aux8.west)
-   (circle.east) edge (cz)
-   (cz.east) edge (gs.west)
-   (circle2.east) edge (aux1.west)
-   (aux1.south) edge (aux2.north)
-   (aux2.west) edge (aux3.east); 
-  \path[->] (aux8.south) edge (circle2.north); 
-  \path[->] (aux6.south) edge (circle2.south);
-  \path[->] (gs.east) edge (circle2.west);
-  \path[->] (aux3.north) edge (circle.south);
- \end{tikzpicture}
-}
- \caption{Digital system with additive uncertainties $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$. \label{fig:digsystem2}}
-\end{figure}
+%\red{[next figure is a bit unnecessary, does not ad much to the previous one.]} Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.
+
+%\begin{figure}[ht]
+%\centering
+%
+%\tikzset{add/.style n args={4}{
+%    minimum width=6mm,
+%    path picture={
+%        \draw[circle] 
+%            (path picture bounding box.south east) -- (path picture bounding box.north west)
+%            (path picture bounding box.south west) -- (path picture bounding box.north east);
+%        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+%        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+%        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+%        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+%        }
+%    }
+% }
+%
+%\resizebox{.5\textwidth}{!}{
+% \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
+%     semithick, initial text=, ampersand replacement=\&,]
+%
+%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
+%  %
+%	\& 
+%	\&
+%	\& \coordinate (aux7); 
+%	\& \node[rectangle,draw,
+%	minimum width=1cm,
+%	minimum height=1cm] (deltag2) {{\sc $\Delta G_{Q}(z)$}};
+%	\& \coordinate (aux8);\\
+%    \node[draw=none] (r) {$R(z)$};
+%%   \& \coordinate (aux0);
+%   \& \node[circle,add={-}{+}{}{}] (circle) {};
+%   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
+%   \& \node[rectangle,draw,
+%	minimum width=1cm,
+%	minimum height=1cm,
+%        label=\textbf{Controller}] (cz) {{\sc C(z)}};
+%   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
+%   \& \coordinate (aux4);
+%   \& \node[rectangle,draw,
+%	minimum width=1cm,
+%	minimum height=1cm,
+%        label=\textbf{Plant}] (gs) {{\sc G(z)}};
+%   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
+%   \& \node[circle,add={+}{+}{+}{}] (circle2) {};
+%%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
+%%   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
+%   \& \coordinate (aux1);
+%   \& \node[draw=none] (yz) {$\hat{Y}(z)$};\\
+%   \& 
+%   \&
+%   \& \coordinate (aux5); 
+%   \& \node[rectangle,draw,
+%	minimum width=1cm,
+%	minimum height=1cm] (deltag) {{\sc $\Delta G_{P}(z)$}};
+%   \& \coordinate (aux6);\\
+%   \& \coordinate (aux3); 
+%   \&
+%   \& 
+%   \& 
+%   \&
+%   \& \coordinate (aux2);\\
+%  };
+%
+%
+%%  \path[->] (v1) edge (q1.north);
+%%  \path[->] (v2) edge (q2.north);
+%  \path[->] (r) edge (circle.west);
+%%  \path[->] (nu) edge (circle2.north);
+%  \path[->] (aux1) edge (yz);
+%  \path  
+%   (aux4.north) edge (aux5.south)
+%   (aux4.north) edge (aux7.south)
+%   (aux5.east) edge (deltag.west)
+%   (aux7.east) edge (deltag2.west)
+%   (deltag.east) edge (aux6.west)
+%   (deltag2.east) edge (aux8.west)
+%   (circle.east) edge (cz)
+%   (cz.east) edge (gs.west)
+%   (circle2.east) edge (aux1.west)
+%   (aux1.south) edge (aux2.north)
+%   (aux2.west) edge (aux3.east); 
+%  \path[->] (aux8.south) edge (circle2.north); 
+%  \path[->] (aux6.south) edge (circle2.south);
+%  \path[->] (gs.east) edge (circle2.west);
+%  \path[->] (aux3.north) edge (circle.south);
+% \end{tikzpicture}
+%}
+% \caption{Digital system with additive uncertainties $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$. \label{fig:digsystem2}}
+%\end{figure}
 
@@
 \label{experimental-results}
+
+\begin{figure}[H]
+\centering
+\begin{tabular}{l | r l r l}
+Benchmark              & Base     &         & Unc     & \\\cline{1-4}
+CruiseControl02        & 17\,s    &         & 46\,s   & \\
+SatelliteB2            & 7\,s     &         & 6601\,s & \tbmark\\
+SatelliteC2            & 369\,s   & \tbmark & 76\,s   & \tbmark\\
+SpringMassDamper       &          &         &         & 
+\end{tabular}
+
+\vspace{0.5em}
+\scriptsize{* = solved with interval backend}
+\vspace{0.5em}
+
+\caption{Experimental results. \label{tab:results}}
+\end{figure}
 %---------------------------------

### 2016-10-12 paper/paper.tex

@@
 \label{experimental-results}
+We outline the runtimes required to synthesise a stable controller for each
+benchmark in Table~\ref{tab:results}. For most benchmarks the conjecture explained
+in section~\ref{fixedpoint_verification} holds and the inductive back-end is able
+to find a stable solution in less than one minute. This is possible if the inductive
+solutions need to be refined with few counterexamples and fixed point precision
+increases. However, some of our benchmarks did not meet these criteria. In these
+cases the interval arithmetic back-end was able to complement the inductive approach
+and synthesise a solution instead, albeit with significantly larger runtimes.
 
@@
 \vspace{0.5em}
-\scriptsize{* = solved with interval backend}
+\scriptsize{* = solved with interval back-end}
 \vspace{0.5em}
@@
 %---------------------------------
+
+We conclude from these results that the inductive back-end provides excellent performance
+for synthesising stable controllers in the majority of the benchmarks, and can be
+complemented using the interval arithmetic back-end where the inductive conjectures fail
+too frequently. Both back-ends enabled controller synthesis for all benchmarks within
+reasonable time frames.
 

### 2016-10-12 paper/paper.tex
Changes on Sec 2

@@
 Let $\hat{C}(z)$ be the transfer function of the digital controller represented using this FWL with integer size $I$ and fractional
-size $F$.  We shall denote this domain as $\mathbb{R}\langle I,F \rangle$
+size $F$.  We shall denote the FWL domain of coefficients as $\mathbb{R}\langle I,F \rangle$
 %Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
@@
 %size $F$, we shall denote this domain as $\mathbb{R}\langle I,F \rangle$ 
-and assume that there exists a function $FWL[\cdot]:\mathbb{R}^{n}\rightarrow \mathbb{R}^{n}\langle I,F \rangle$, which applies the FWL effects to a polynomial \red{[explain index n!
-why do you need to work on a Euclidean domain?]}.
+and assume that there exists a function $FWL[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$, which applies the FWL effects to a polynomial.
+$\mathcal{P}^{n}$ is the space of polynomials of $n$-th order and $\mathcal{P}^{n}\langle I,F \rangle$ is is the space of polynomials with coefficients in $\mathbb{R}\langle I,F \rangle$.
+%, \red{[explain index n! why do you need to work on a Euclidean domain?]}. 
 Thus the perturbed controller model $\hat{C}(z)$ may be computed from the original model $C(z)=\frac{N_{C}(z)}{D_{C}(z)}$ using the following expression:
@@
 \red{[what is the relationship between FWL effects over C, and the parametric uncertainty Delta Gp over the plant?]} 
+\blue{[IB: There is no relationship. We must separate that content in another section?]}
 
@@
 Analyzing the~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for BIBO stability of closed-loop system in figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$ are bounded.
+
+\begin{myassumption}
+\label{whitenoise}
+%
+The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
+$Q2$) are bounded uncorrelated white noises.
+% 
+\end{myassumption}
+
+\begin{mylemma}
+\label{lemma:variance}
+In particular, Widrow \cite{widrow1956} models the quantisation noise as a gaussian
+model in which the second moment (variance) of the probability density
+function (PDF) of the quantisation noise is given by
+%
+\begin{equation}
+\label{eq:variancelemma}
+\sigma_{Q}^{2}=\frac{q^{2}}{12},
+\end{equation}
+where $q$ is the step size of quantizer. (Proof is on \cite{widrow1956})
+\end{mylemma}
+
+\begin{mylemma}
+\label{lemma:boundednoise}
+The power spectral density of the quantisation noise (supposed white) $S_{\nu}(z)$ is bounded and may be computed through the z-transform of autocorrelation function of $\nu(k)$, thus:
+\begin{equation}
+S_{\nu}(z)= \sigma_{Q}^{2}=\frac{q^{2}}{12}.
+\end{equation}
+\end{mylemma}
+
+\begin{proof}
+Considering $\nu(k)$ a random process, where $\nu(k)$ is independent from $\nu(k+i)$ for every  integer $k\neq 0$.
+The autocorrelation function of $\nu(k)$, {\it i.e.} $R_{\nu\nu}(\tau)$ may be computed as follows:
+\begin{equation}
+R_{\nu\nu}(\tau)=E[\nu(t+\tau)\nu(t)]=\sigma_{Q}^{2}\cdot \delta(\tau),
+\end{equation}
+where $\delta(\tau)$ is the Dirac delta function at delay time $\tau$.
+
+By definition~\cite{poularikas2000transforms}, the power spectral density of  $\nu(k)$ is the z-transform of $R_{\nu\nu}(\tau)$, thus
+\begin{equation}
+S_{\nu}(z)=  \sum\limits_{k=-\infty}^{\infty}{R_{\nu\nu}(k)z^{-k}} = \sigma_{Q}^{2},
+\end{equation}
+considering the Lemma~\ref{lemma:variance}:
+\begin{equation}
+S_{\nu}(z)=  \frac{q^{2}}{12}.
+\end{equation}
+\end{proof}
+
+Finally, the quantisation noise may be considered a energy-bounded signal (Lemma~\ref{lemma:boundednoise}) and thus $\hat{Y}(z)$ will be bounded and the closed-loop system stable if the conditions in Lemma~\ref{lemma:eq_int_stab} are followed.
 
@@
 Based on it, the model for plant uncertainty due quantisation noise ({\it i.e.}, $\Delta G_{Q}(z)$) may be disregarded if the conditions on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise is bounded.
-
 The quantisation noise is indeed bounded, since the following assumption~\ref{whitenoise} and the Lemmas~\ref{lemma:variance} and~\ref{lemma:boundednoise} are true.
 
-\red{[first: lemmae precede theorems. ]}
-
-%
-\begin{myassumption}
-\label{whitenoise}
-%
-The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
-$Q2$) are bounded uncorrelated white noises.
-% 
-\end{myassumption}
-
-\begin{mylemma}
-\label{lemma:variance}
-In particular, Widrow \cite{widrow1956} models the quantisation noise as a gaussian
-model in which the second moment (variance) of the probability density
-function (PDF) of the quantisation noise is given by
-%
-\begin{equation}
-\label{eq:variancelemma}
-\sigma_{Q}^{2}=\frac{q^{2}}{12},
-\end{equation}
-where $q$ is the step size of quantizer. (Proof is on \cite{widrow1956})
-\end{mylemma}
-
-\begin{mylemma}
-\label{lemma:boundednoise}
-The power spectral density of the quantisation noise (supposed white) $S_{\nu}(z)$ is bounded and may be computed through the z-transform of autocorrelation function of $\nu(k)$, thus:
-\begin{equation}
-S_{\nu}(z)= \sigma_{Q}^{2}=\frac{q^{2}}{12}.
-\end{equation}
-\end{mylemma}
-
-\begin{proof}
-Considering $\nu(k)$ a random process, where $\nu(k)$ is independent from $\nu(k+i)$ for every  integer $k\neq 0$.
-The autocorrelation function of $\nu(k)$, {\it i.e.} $R_{\nu\nu}(\tau)$ may be computed as follows:
-\begin{equation}
-R_{\nu\nu}(\tau)=E[\nu(t+\tau)\nu(t)]=\sigma_{Q}^{2}\cdot \delta(\tau),
-\end{equation}
-where $\delta(\tau)$ is the Dirac delta function at delay time $\tau$.
-
-By definition~\cite{poularikas2000transforms}, the power spectral density of  $nu(k)$ is the z-transform of $R_{\nu\nu}(\tau)$, thus
-\begin{equation}
-\nu(z)=  \sum\limits_{k=-\infty}^{\infty}{R_{\nu\nu}(k)z^{-k}} = \sigma_{Q}^{2},
-\end{equation}
-considering the Lemma~\ref{lemma:variance}:
-\begin{equation}
-\nu(z)=  \frac{q^{2}}{12}.
-\end{equation}
-\end{proof}
-
-Finally, the quantisation noise may be considered a energy-bounded signal (Lemma~\ref{lemma:boundednoise}) and thus $\hat{Y}(z)$ will be bounded and the closed-loop system stable if the conditions in Lemma~\ref{lemma:eq_int_stab} are followed.
+%\red{[first: lemmae precede theorems. ]}
+
+%
 

### 2016-10-12 paper/paper.tex
chenged the CEGIS figure to support the two verifiers

--- 2016-10-12 paper/paper.tex
@@
 For this purpose, the design procedure is based on a discretized model for a continuous plant.
-Considering only transfer function models, we are interested in a $z$-domain transfer function that considers all the aspects about the continuous plant ($G(s)$) and the sampling and hold process.
+For transfer function models, we are interested in a $z$-domain transfer function that considers all the aspects about the continuous plant ($G(s)$) and the sampling and hold process.
 
@@
 i.e.}, a continuous model of the plant must be discretized to obtain the
-discrete equivalent coefficients via ZOH
+discrete equivalent coefficients $b$ and $a$~\cite{Astrom08} via ZOH
 discretization.
 
-%\red{[why do we discuss the ZOH at this point?]}
+\red{[why do we discuss the ZOH at this point?]}
 
@@
 
-Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (\emph{i.e.} $\Delta{G}_p(s)$), errors in the numeric calculations, or roundoffs in the quantization.
+Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (\emph{ie} $\Delta{G}_p(s)$), errors in the numeric calculations, or roundoffs in the quantization.
 These uncertainties may be parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
@@
 where $\Delta G_{P}(z)$ is the term that corresponds to the parametric uncertainties and $\Delta G_{Q}(z)$ is the term that reflects the quantisation effects on the plant model.
-%\red{[next figure is a bit unnecessary, does not ad much to the previous one.]} Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.
-
-%\begin{figure}[ht]
-%\centering
-%
-%\tikzset{add/.style n args={4}{
-%    minimum width=6mm,
-%    path picture={
-%        \draw[circle] 
-%            (path picture bounding box.south east) -- (path picture bounding box.north west)
-%            (path picture bounding box.south west) -- (path picture bounding box.north east);
-%        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
-%        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
-%        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
-%        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
-%        }
-%    }
-% }
-%
-%\resizebox{.5\textwidth}{!}{
-% \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
-%     semithick, initial text=, ampersand replacement=\&,]
-%
-%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
-%  %
-%	\& 
-%	\&
-%	\& \coordinate (aux7); 
-%	\& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm] (deltag2) {{\sc $\Delta G_{Q}(z)$}};
-%	\& \coordinate (aux8);\\
-%    \node[draw=none] (r) {$R(z)$};
-%%   \& \coordinate (aux0);
-%   \& \node[circle,add={-}{+}{}{}] (circle) {};
-%   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
-%   \& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm,
-%        label=\textbf{Controller}] (cz) {{\sc C(z)}};
-%   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
-%   \& \coordinate (aux4);
-%   \& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm,
-%        label=\textbf{Plant}] (gs) {{\sc G(z)}};
-%   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
-%   \& \node[circle,add={+}{+}{+}{}] (circle2) {};
-%%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
-%%   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
-%   \& \coordinate (aux1);
-%   \& \node[draw=none] (yz) {$\hat{Y}(z)$};\\
-%   \& 
-%   \&
-%   \& \coordinate (aux5); 
-%   \& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm] (deltag) {{\sc $\Delta G_{P}(z)$}};
-%   \& \coordinate (aux6);\\
-%   \& \coordinate (aux3); 
-%   \&
-%   \& 
-%   \& 
-%   \&
-%   \& \coordinate (aux2);\\
-%  };
-%
-%
-%%  \path[->] (v1) edge (q1.north);
-%%  \path[->] (v2) edge (q2.north);
-%  \path[->] (r) edge (circle.west);
-%%  \path[->] (nu) edge (circle2.north);
-%  \path[->] (aux1) edge (yz);
-%  \path  
-%   (aux4.north) edge (aux5.south)
-%   (aux4.north) edge (aux7.south)
-%   (aux5.east) edge (deltag.west)
-%   (aux7.east) edge (deltag2.west)
-%   (deltag.east) edge (aux6.west)
-%   (deltag2.east) edge (aux8.west)
-%   (circle.east) edge (cz)
-%   (cz.east) edge (gs.west)
-%   (circle2.east) edge (aux1.west)
-%   (aux1.south) edge (aux2.north)
-%   (aux2.west) edge (aux3.east); 
-%  \path[->] (aux8.south) edge (circle2.north); 
-%  \path[->] (aux6.south) edge (circle2.south);
-%  \path[->] (gs.east) edge (circle2.west);
-%  \path[->] (aux3.north) edge (circle.south);
-% \end{tikzpicture}
-%}
-% \caption{Digital system with additive uncertainties $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$. \label{fig:digsystem2}}
-%\end{figure}
+\red{[next figure is a bit unnecessary, does not ad much to the previous one.]} Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.
+
+\begin{figure}[ht]
+\centering
+
+\tikzset{add/.style n args={4}{
+    minimum width=6mm,
+    path picture={
+        \draw[circle] 
+            (path picture bounding box.south east) -- (path picture bounding box.north west)
+            (path picture bounding box.south west) -- (path picture bounding box.north east);
+        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+        }
+    }
+ }
+
+\resizebox{.5\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
+     semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
+  %
+	\& 
+	\&
+	\& \coordinate (aux7); 
+	\& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm] (deltag2) {{\sc $\Delta G_{Q}(z)$}};
+	\& \coordinate (aux8);\\
+    \node[draw=none] (r) {$R(z)$};
+%   \& \coordinate (aux0);
+   \& \node[circle,add={-}{+}{}{}] (circle) {};
+   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Controller}] (cz) {{\sc C(z)}};
+   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
+   \& \coordinate (aux4);
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Plant}] (gs) {{\sc G(z)}};
+   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
+   \& \node[circle,add={+}{+}{+}{}] (circle2) {};
+%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
+%   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
+   \& \coordinate (aux1);
+   \& \node[draw=none] (yz) {$\hat{Y}(z)$};\\
+   \& 
+   \&
+   \& \coordinate (aux5); 
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm] (deltag) {{\sc $\Delta G_{P}(z)$}};
+   \& \coordinate (aux6);\\
+   \& \coordinate (aux3); 
+   \&
+   \& 
+   \& 
+   \&
+   \& \coordinate (aux2);\\
+  };
+
+%  \path[->] (v1) edge (q1.north);
+%  \path[->] (v2) edge (q2.north);
+  \path[->] (r) edge (circle.west);
+%  \path[->] (nu) edge (circle2.north);
+  \path[->] (aux1) edge (yz);
+  \path  
+   (aux4.north) edge (aux5.south)
+   (aux4.north) edge (aux7.south)
+   (aux5.east) edge (deltag.west)
+   (aux7.east) edge (deltag2.west)
+   (deltag.east) edge (aux6.west)
+   (deltag2.east) edge (aux8.west)
+   (circle.east) edge (cz)
+   (cz.east) edge (gs.west)
+   (circle2.east) edge (aux1.west)
+   (aux1.south) edge (aux2.north)
+   (aux2.west) edge (aux3.east); 
+  \path[->] (aux8.south) edge (circle2.north); 
+  \path[->] (aux6.south) edge (circle2.south);
+  \path[->] (gs.east) edge (circle2.west);
+  \path[->] (aux3.north) edge (circle.south);
+ \end{tikzpicture}
+}
+ \caption{Digital system with additive uncertainties $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$. \label{fig:digsystem2}}
+\end{figure}
 
@@
 },
-          row sep=1cm, column sep=1cm] {
-   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}}; \\
+          row sep=1cm, column sep=1.5cm] {
+   \coordinate (aux1);
+   \& \coordinate (aux2);
+   \&;\\
    \node[fill=yellow!20] (synth) {{\sc Synthesise}};
    \&
-   \node[fill=yellow!20] (verif) {{\sc Verify}}; \\
-
+   complexnode/.pic={ 
+     \node[rectangle,draw,dashed,
+	minimum width=7cm,
+	minimum height=1.6cm,
+	label={\sc Verify},] (verif) {};
+   \node[fill=yellow!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc Uncertainty}};
+   \node[fill=yellow!20] (verif2) at ([xshift=2cm]verif.center) {{\sc Precision}};
+   } 
+   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
+   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
+   %% \&
+   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
    \& \\
    \& \\
-   \node (gp) {~~~~~~~~~~~~~~Closed-loop System Search~~~~~~~~~~~~~~~};
+   \node (gp) {Closed-loop System Search};
    \&
-   \node (bmc) {~~~~~~~~~~~~~~~BMC-based Verifier~~~~~~~~~~~~~~~};
-
+   complexnode/.pic={ 
+     \coordinate (aux);
+   \node (bmc) at ([xshift=-2cm]aux.center) {BMC-based Verifier};
+   \node (fp)  at ([xshift=2cm]aux.center) {Fixed-point \\Arithmetic Verifier};
+   }   
     \\
@@
    \path
-    ([yshift=2em]synth.east) edge node {Candidate solution} ([yshift=2em]verif.west)
-    ([yshift=-2em]verif.west) edge node {Counterexample} ([yshift=-2em]synth.east)
-    ([xshift=5em]verif.south) edge node {Candidate $P$} ([xshift=5em]bmc.north)
-    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif.south)
-    (verif) edge node {} (done)
+    ([yshift=2em]synth.east) edge node {Candidate solution} ([yshift=2em]verif1.west)
+    ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east)
+    ([xshift=5em]verif1.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]bmc.north)
+    ([xshift=5em]verif2.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]fp.north)
+    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
+    ([xshift=-5em]fp.north) edge node[align=center]  {True/\\False} ([xshift=-5em]verif2.south)
+    (verif2) edge node {} (done)
     ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
-    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south);
+    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south)
+    (aux1) edge (synth.north);
+   \path[-]
+   (verif2.north) edge node[align=center] {} ([xshift=6.7cm]aux2)
+   ([xshift=6.7cm]aux2) edge node[align=center] {Reset} (aux1);
+
  \end{tikzpicture}

### 2016-10-12 paper/paper.tex
small adjusting of fig 5

@@
 	label={\sc Verify},] (verif) {};
-   \node[fill=yellow!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc Uncertainty}};
-   \node[fill=yellow!20] (verif2) at ([xshift=2cm]verif.center) {{\sc Precision}};
+   \node[fill=yellow!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc ~~Uncertainty~~~~}};
+   \node[fill=yellow!20] (verif2) at ([xshift=2cm]verif.center) {{\sc ~~~~~Precision~~~}};
    } 

### 2016-10-12 paper/paper.tex
revised general CEGIS description to go with the new figure

@@
 The input specification provided to the program synthesiser is of the
-form $\exists \vec{P} . \forall \vec{x} \in \text{\sc inputs}
-. \sigma(\vec{x}, \vec{P})$ where $\vec{P}$ ranges over functions,
+form $\exists \vec{P} . \forall \vec{x}. \sigma(\vec{x}, \vec{P})$ where $\vec{P}$ ranges over functions,
 $\vec{x}$ ranges over ground terms and $\sigma$ is a quantifier-free
-formula.  We interpret the ground terms over some finite domain
+formula.  We interpret the ground terms over some domain
 $\mathcal{D}$.
@@
 satisfying the specification $\sigma(\vec{x}, \vec{P})$ for all
-$\vec{x}$.
+$\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
 %
 If {\sc synthesise} succeeds in finding an witness $\vec{P}$, this
-witness is a candidate solution to the full synthesis formula.  We
-pass this candidate solution to {\sc verify}, which determines whether
-it does satisfy the specification on all inputs by checking
-satisfiability of the following verification formula:
-%
-$\exists \vec{x} . \lnot \sigma(\vec{x}, \vec{P})$
-
-If this formula is unsatisfiable, the candidate solution is in fact a
-solution to the synthesis formula and so the algorithm terminates.
-Otherwise, the witness $\vec{x}$ denote an input on which the
-candidate solution fails to meet the specification.  Thus, $\vec{x}$ is
-added to the {\sc inputs} set, and the loop iterates again.  It is
-worth noting that each iteration of the loop adds a new input to the
-finite set $\text{\sc inputs}$ being used for synthesis.  Given that
-the full set of inputs $\mathcal{D}$
-%\blue{[which by now should have a name, as suggested to be introduced above]} 
-is finite, this means that the refinement loop
-can only iterate a finite number of times.
+witness is a candidate solution to the full synthesis formula. 
+We pass this candidate solution to {\sc verify}, which 
+checks whether it is a full solution.
+%determines whether
+%it does satisfy the specification on all inputs by checking
+%satisfiability of the following verification formula:
+%
+%$\exists \vec{x} . \lnot \sigma(\vec{x}, \vec{P})$
+%If this formula is unsatisfiable, 
+%% the candidate solution is in fact a 
+%% full solution.
+If this is the case, then
+the algorithm terminates.
+Otherwise, additional information is provided to the {\sc synthesise}
+phase (e.g. a new counterexample that is added to the {\sc inputs} set)
+and the loop iterates again.
+
+%% the witness $\vec{x}$ denote an input on which the
+%% candidate solution fails to meet the specification.  Thus, $\vec{x}$ is
+%% added to the {\sc inputs} set, and the loop iterates again.
+
+%% It is
+%% worth noting that each iteration of the loop adds a new input to the
+%% finite set $\text{\sc inputs}$ being used for synthesis.  Given that
+%% the full set of inputs $\mathcal{D}$
+%% %\blue{[which by now should have a name, as suggested to be introduced above]} 
+%% is finite, this means that the refinement loop
+%% can only iterate a finite number of times.
 

### 2016-10-12 paper/paper.tex
adjusted fig 5

@@
 	minimum width=7cm,
-	minimum height=1.6cm,
+	minimum height=.8cm,
 	label={\sc Verify},] (verif) {};
-   \node[fill=yellow!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc ~~Uncertainty~~~~}};
+   \node[fill=yellow!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc ~Uncertainty~~~~}};
    \node[fill=yellow!20] (verif2) at ([xshift=2cm]verif.center) {{\sc ~~~~~Precision~~~}};

### 2016-10-12 paper/paper.tex
revised sec 4 (synthesis elements specific to control)

@@
 
-\paragraph{General architecture of the program synthesiser}
+\subsection{General architecture of the program synthesiser}
 %
@@
 $\vec{x}$ ranges over ground terms and $\sigma$ is a quantifier-free
-formula.  We interpret the ground terms over some domain
+formula.  We interpret the ground terms over some finite domain
 $\mathcal{D}$.
@@
 
-\paragraph{Synthesis elements specific to control systems}
-
+\subsection{Synthesis elements specific to control systems}
+
+\paragraph{Property specification}
 Next, we describe the specific property that we pass to the program
@@
 
-We use this method to check the stability in the $z$-domain for the characteristic polynomial $S(z)$ defined in~\eqref{eq:internal_stab_lemma}.
+We use this method to check the stability in the $z$-domain for the
+characteristic polynomial $S(z)$ defined
+in~\eqref{eq:internal_stab_lemma}.
 
@@
 
-\red{[clear elucidation of the mapping between this and the domains used 
-in the general description of the synthesiser]}
-
-In the {\sc verify} phase, if the system is unstable for the current candidate solution,
-{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$, 
-then we obtain a counterexample denoted by 
+%% \red{[clear elucidation of the mapping between this and the domains used 
+%% in the general description of the synthesiser]}
+
+\paragraph{The {\sc Synthesise} and {\sc Verify} phases}
+The {\sc synthesise} phase uses a BMC-based verifier to 
+compute a solution ($N_c$,$D_C$). An important remark is that this 
+controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
+domain.  
+\cdsay{integrate sec 2.4 with Dario}
+
+In the {\sc verify} phase, we have a two-step process. 
+First, in the {\sc Uncertainty} sub-phase, assuming the 
+current precision \param{I_b}{F_b},
+we check whether 
+the system is unstable for the current candidate solution,
+{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$.
+If this is the case, then we obtain a counterexample denoted by 
 values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
@@
 
-\paragraph{Program synthesis for the running example}
+If the result of the {\sc Uncertainty} verification is that
+$\neg \phi_{stability}$ is unsatisfiable for $S(z)$, then we pass 
+the current candidate solution to the {\sc Precision} verification sub-phase, 
+which checks the propagation of the error in the fixed-point 
+calculations. If this check returns $false$, then we 
+increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise} phase
+with an empty {\sc inputs} set.
+
+\subsection{Program synthesis for the running example}
 We will illustrate our synthesis approach on the running example 
@@
    (verif2.north) edge node[align=center] {} ([xshift=6.7cm]aux2)
-   ([xshift=6.7cm]aux2) edge node[align=center] {Reset} (aux1);
+   ([xshift=6.7cm]aux2) edge node[align=center] {Increase Precision} (aux1);
 

### 2016-10-12 paper/paper.tex
editing sec 4.3

@@
 If the result of the {\sc Uncertainty} verification is that
-$\neg \phi_{stability}$ is unsatisfiable for $S(z)$, then we pass 
-the current candidate solution to the {\sc Precision} verification sub-phase, 
+the system is stable for the current candidate solution,
+then we pass this solution to the {\sc Precision} verification sub-phase, 
 which checks the propagation of the error in the fixed-point 
@@
 with an empty {\sc inputs} set.
+Otherwise, we found a full solution for our synthesis problem
+and we are done.
 
@@
 higher precision:
+\cdsay{Pascal, this sounds confusing. if you want to increase precision on-the-fly, 
+then this illustration doesn't follow the general diagram in Fig.5. 
+We need to decide which direction we keep.}
 %

### 2016-10-12 paper/paper.tex
small changes to abstract

@@
 literature in a number of directions: we are interested in quantitative
-tasks; we focus on automated correct-by-design synthesis algorithms, as
+tasks; we focus on automated correct-by-construction synthesis algorithms, as
 opposed to verification objectives; and we encompass the complete range of
@@
 finite-precision representations (with related rounding errors).  To this
-end, we propose a CEGIS-based solution that uses inductive invariant
+end, we propose a CEGIS-based solution that uses inductive 
 synthesis in conjunction with a digital verification algorithm to find a
@@
 higher precision:
-\cdsay{Pascal, this sounds confusing. if you want to increase precision on-the-fly, 
+\cdsay{Pascal, this sounds confusing. if you want to increase precision on-the-fly, i.e. 
+not going back to the synthesise phase, 
 then this illustration doesn't follow the general diagram in Fig.5. 

### 2016-10-12 paper/paper.tex
moved sec 2.4 inside the synthesis sec

@@
 %------------------------------------
-\subsection{Using Fixed Point Arithmetic for verification}
-\label{fixedpoint_verification}
+%\subsection{Using Fixed Point Arithmetic for verification}
+%\label{fixedpoint_verification}
 %------------------------------------
 
-Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
-using Fixed-Point bit vectors with integer size $I_b$ and fractional
-size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
-%
-\begin{align}
-\small
-\label{digital_controller_plant_tf}
-\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
-%\label{plant_tf}
-\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
-\end{align}
-
-Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
-domain,
-%
- $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
-%
-However, given a real plant and real controller $\hat{G}(z), \hat{C}(z)$, and a discretizing function
-\begin{align}
-\small
-\label{FWL_tf}
-&f_b (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = x-(x\mod\tilde x)
-\end{align}
-we calculate $\tilde C(z)=f(\hat{C}(z))$ and $\tilde G(z)=f(\hat{G}(z))$
-\begin{align}
-\label{digital_controller_tf}
-\tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
-&= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
-\label{digital_plant_tf}
-\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_q \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_q \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_q \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_q \hat{a}_{N_G})z^{-N_G}} \nonumber \\
-&=G(z)+\Delta{G}_P(z)+\Delta{G}_b(z).
-\end{align}
-where $\Delta_b\hat{c}_i=\hat{c}_i\mod \tilde{c}_i$
-and $\Delta{G}_b(z)$ represents the plant uncertainty caused by
-the rounding off effect.  We may encompass all the uncertainty as
-$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_b(z)$.  Since this value is
-nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
-denoted by $\mathfrak{G}(z)$.
-
-Two approaches have been taken to synthesise a stable controller based on this model.
-The first uses interval arithmetic, representing the coefficients $[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\ {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
-and rounding operations outwards during the process. This results in a tighter calculation of the error at the cost of performance.
-
-The second approach uses a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is assumed to be within the expected bounds and verified after synthesis using the interval version of the program.
-The first verification phase produces a counterexample if some instance of $\mathfrak{G}(z)$ does not verify the properties and the CEGIS loop iteratively looks for a new controller that verifies the supplied counterexamples.
-The second phase verifies the propagation of the error in the fixed point calculations.
-If the second phase fails verification, we increase the precision of the analyser and feed the CEGIS loop again to find a sound solution.
-The resulting increase in speed of this approach over the former, which is of several orders of magnitude, vouches for the use of CEGIS in most of our benchmarks.
 %------------------------------------
@@
 domain.  
-\cdsay{integrate sec 2.4 with Dario}
+\cdsay{integrate the following with Dario}
+Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
+using Fixed-Point bit vectors with integer size $I_b$ and fractional
+size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
+%
+\begin{align}
+\small
+\label{digital_controller_plant_tf}
+\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
+%\label{plant_tf}
+\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
+\end{align}
+
+Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
+domain,
+%
+ $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
+%
+However, given a real plant and real controller $\hat{G}(z), \hat{C}(z)$, and a discretizing function
+\begin{align}
+\small
+\label{FWL_tf}
+&f_b (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = x-(x\mod\tilde x)
+\end{align}
+we calculate $\tilde C(z)=f(\hat{C}(z))$ and $\tilde G(z)=f(\hat{G}(z))$
+\begin{align}
+\label{digital_controller_tf}
+\tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
+&= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
+\label{digital_plant_tf}
+\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_q \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_q \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_q \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_q \hat{a}_{N_G})z^{-N_G}} \nonumber \\
+&=G(z)+\Delta{G}_P(z)+\Delta{G}_b(z).
+\end{align}
+where $\Delta_b\hat{c}_i=\hat{c}_i\mod \tilde{c}_i$
+and $\Delta{G}_b(z)$ represents the plant uncertainty caused by
+the rounding off effect.  We may encompass all the uncertainty as
+$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_b(z)$.  Since this value is
+nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
+denoted by $\mathfrak{G}(z)$.
+
+Two approaches have been taken to synthesise a stable controller based on this model.
+The first uses interval arithmetic, representing the coefficients $[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\ {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
+and rounding operations outwards during the process. This results in a tighter calculation of the error at the cost of performance.
+
+The second approach uses a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is assumed to be within the expected bounds and verified after synthesis using the interval version of the program.
+The first verification phase produces a counterexample if some instance of $\mathfrak{G}(z)$ does not verify the properties and the CEGIS loop iteratively looks for a new controller that verifies the supplied counterexamples.
+The second phase verifies the propagation of the error in the fixed point calculations.
+If the second phase fails verification, we increase the precision of the analyser and feed the CEGIS loop again to find a sound solution.
+The resulting increase in speed of this approach over the former, which is of several orders of magnitude, vouches for the use of CEGIS in most of our benchmarks.
+\cdsay{end of integration}
 

### 2016-10-12 paper/paper.tex
Updated experiments table data.

@@
 \centering
-\begin{tabular}{l | r l r l}
-Benchmark              & Base     &         & Unc     & \\\cline{1-4}
-CruiseControl02        & 17\,s    &         & 46\,s   & \\
-SatelliteB2            & 7\,s     &         & 6601\,s & \tbmark\\
-SatelliteC2            & 369\,s   & \tbmark & 76\,s   & \tbmark\\
-SpringMassDamper       &          &         &         & 
+\begin{tabular}{l | r r l}
+Benchmark              & Base     & Unc     & \\\cline{1-4}
+CruiseControl02        & 17\,s    & 46\,s   & \\
+SatelliteB2            & 7\,s     & 6601\,s & \tbmark\\
+SatelliteC2            & 2\,s     & 76\,s   & \tbmark\\
+SpringMassDamper       & 28\,s    & \xmark  &
 \end{tabular}
@@
 \vspace{0.5em}
-\scriptsize{* = solved with interval back-end}
+\scriptsize{* = solved with interval back-end, \xmark = uncontrollable}
 \vspace{0.5em}

### 2016-10-13 paper/paper.tex

--- 2016-10-12 paper/paper.tex
@@
 literature in a number of directions: we are interested in quantitative
-tasks; we focus on automated correct-by-construction synthesis algorithms, as
+tasks; we focus on automated correct-by-design synthesis algorithms, as
 opposed to verification objectives; and we encompass the complete range of
@@
 finite-precision representations (with related rounding errors).  To this
-end, we propose a CEGIS-based solution that uses inductive 
+end, we propose a CEGIS-based solution that uses inductive invariant
 synthesis in conjunction with a digital verification algorithm to find a
@@
 %------------------------------------
-\subsection{Sampling and Holding in Hybrid Systems}
-\label{ssec:SandH}
-%------------------------------------
-
-The digital controllers synthesized in this paper are typically used in closed loops with continuous (and physical) plants.
-Thus, the proposed approach have to consider dynamics of continuous parts of system ({\it e.g.}, plant) and discrete parts ({\it e.g.}, digital controller), {\it i.e.} the synthesized controller have to consider the issues related to the hybrid systems studies.
-
-For this purpose, the design procedure is based on a discretized model for a continuous plant.
-Considering only transfer function models, we are interested in a $z$-domain transfer function that considers all the aspects about the continuous plant ($G(s)$) and the sampling and hold process.
-
-Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it
-i.e.}, a continuous model of the plant must be discretized to obtain the
-discrete equivalent coefficients via ZOH
-discretization.
-
-%\red{[why do we discuss the ZOH at this point?]}
-
-Although there are several discretization methods available
-in the literature~\cite{Franklin15}, the zero-order hold (ZOH)
-discretization is more suitable for representing the sample and hold
-processes that are typically employed in complex systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretization
-models the exact effect of sampling and DAC interpolation over the plant.
-
-\begin{myassumption}
-%
-The Sample and Hold of the ADC and the ZOH of the DAC are synchronized, {\it i.e.}, there is no delay between
-sampling the plant output at ADC and updating the DAC accordingly. The DAC interpolator is an ideal ZOH.
-%
-\end{myassumption}
-
-\begin{mylemma}\cite{astrom1997computer}
-%
-Given a synchronized ZOH input and sample and hold output on the plant with a sample time $T$ satisfying Nyquist's sampling criteria, the discrete pulse transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$ which can be computed using the following formula:
-%
-\begin{equation}
-\label{eq:pulsetf}
-G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
-\end{equation}
-%
-For the sake of brevity, we will use the notation $G(z)$ to represent the pulse transfer function.
-%
-\end{mylemma}
-
-%------------------------------------
 \subsection{Verifying Closed-loop Control Systems}
@@
 
-Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (\emph{i.e.} $\Delta{G}_p(s)$), errors in the numeric calculations, or roundoffs in the quantization.
-These uncertainties may be parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
+Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it
+i.e.}, a continuous model of the plant must be discretized to obtain the
+discrete equivalent coefficients $b$ and $a$~\cite{Astrom08} via ZOH
+discretization.
+
+\red{[why do we discuss the ZOH at this point?]}
+
+Although there are several discretization methods available
+in the literature~\cite{Franklin15}, the zero-order hold (ZOH)
+discretization is more suitable for representing the sample and hold
+processes that are typically employed in complex systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretization
+models the exact effect of sampling and DAC interpolation over the plant.
+
+\begin{mylemma}\cite{astrom1997computer}
+%
+The pulse transfer function $G(z)$ is a z-domain model that relates the
+output sampled by an ADC and the digital input provided by the ZOH.  It is equivalent at the sample times ({\it i.e.}, $t=kT$) to the continuous transfer
+function $G(s)$ driven by ZOH.  
+\red{[what does it mean that it is continuous ``at the sample times''?
+We're working in frequency.
+Are you matching poles?
+There is still no clear relationship between continuous and samples transfer functions, it is not formal in my opinion.]}
+This pulse transfer function can be computed as
+%
+\begin{equation}
+\label{eq:pulsetf}
+G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
+\end{equation}
+%
+For the sake of brevity, 
+we will use the notation $G(z)$ to represent the pulse transfer function.
+%
+\end{mylemma}
+
+\begin{myassumption}
+%
+The DAC and ADC are synchronized, {\it i.e.}, there is no delay between
+sampling the plant output at ADC and updating the DAC accordingly.
+%
+\end{myassumption}
+
+\begin{myassumption}
+%
+The DAC interpolator is an ideal ZOH; it takes the discrete value of control
+signal $\tilde u(k)$ \red{[is this a new notation over the time domain?
+It does not reflect the signals used in the plot -- utterly confusing!]} at instant $k$ and produces a rectangular pulse of height
+$u(k)$ and width equal to the sample time $T$.
+%
+\end{myassumption}
+
+\begin{myassumption}
+%
+\label{assumption:cont_and_plant}
+The controller and the plant are linear time-invariant (LTI) systems, {\it i.e.}, 
+\red{[!! of course, we're working with transfer functions!!]}
+any source of
+nonlinearity ({\it e.g.}, saturation, overflow, ADC/DAC nonlinearities) will
+be disregarded \red{[how is this related to ADC/DAC? very confusing.]}
+.
+Additionally, the pulse transfer function is obtained via \eqref{eq:pulsetf} using an appropriate sample rate ({\it i.e.}, obeying the Nyquist sampling conditions)  is a precise discrete-time representation of $G(s)$.
+\red{[clarify this: this cannot be an assumption, since it is hinging on a specific numerical scheme.
+Assumptions deal with structural properties for example, or choices of certain parameters ...
+]}
+%
+\end{myassumption}
+
+Although the pulse transfer function $G(z)$ represents adequately \red{[clarify adverb]} $G(s)$ in the z-domain, 
+the model $G(z)$ may not be accurate and some uncertainties may not be covered by that model. 
+These uncertainties may be \red{[clarify use of conditional tense]} parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
 \begin{equation}
@@
 \end{equation}
-which will be represented by the following transfer function:
-\begin{equation}
-\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}} : N_G \geq M_G .
+that may be \red{[\ldots]} represented by the following transfer function:
+\begin{equation}
+\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}}.
 \end{equation}
@@
 \end{equation}
-
-A typical hybrid system, with a continuous plant and discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$
+\red{[where is this new variable used later?]}
+
+A typical hybrid system \red{[clarify the adjective ``hybrid'']} is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$
+\red{[this Delta term now refers to the continuous plant? this is not what has been discussed before, nor what is in some of the plots.]} 
 , $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.
@@
 	minimum height=1cm,
-        label=\textbf{Plant}] (gs) {{\sc $G(s) + \Delta G_p(s)$}};
+        label=\textbf{Plant}] (gs) {{\sc $G(s) + \Delta G(s)$}};
    \node[draw=none] (ud) at ([xshift=-2cm,yshift=.15cm]gs)  {$U(s)$};
@@
 Let $\hat{C}(z)$ be the transfer function of the digital controller represented using this FWL with integer size $I$ and fractional
-size $F$.  We shall denote the FWL domain of coefficients as $\mathbb{R}\langle I,F \rangle$
+size $F$.  We shall denote this domain as $\mathbb{R}\langle I,F \rangle$
 %Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
@@
 %size $F$, we shall denote this domain as $\mathbb{R}\langle I,F \rangle$ 
-and assume that there exists a function $FWL[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$, which applies the FWL effects to a polynomial.
-$\mathcal{P}^{n}$ is the space of polynomials of $n$-th order and $\mathcal{P}^{n}\langle I,F \rangle$ is is the space of polynomials with coefficients in $\mathbb{R}\langle I,F \rangle$.
-%, \red{[explain index n! why do you need to work on a Euclidean domain?]}. 
+and assume that there exists a function $FWL[\cdot]:\mathbb{R}^{n}\rightarrow \mathbb{R}^{n}\langle I,F \rangle$, which applies the FWL effects to a polynomial \red{[explain index n!
+why do you need to work on a Euclidean domain?]}.
 Thus the perturbed controller model $\hat{C}(z)$ may be computed from the original model $C(z)=\frac{N_{C}(z)}{D_{C}(z)}$ using the following expression:
@@
 \red{[what is the relationship between FWL effects over C, and the parametric uncertainty Delta Gp over the plant?]}
-\blue{[IB: There is no relationship. We must separate that content in another section?]}
 
@@
 
+\begin{mylemma}{\cite{Bessa16,fadali}}
+\label{lemma:eq_int_stab} 
+A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with a FWL implementation of the digital controller $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete model of the plant $\hat{G}(z)=G(z)+\Delta G_{P}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and only if:
+\red{[this statement does not seem to encompass the quantisation effects on the plant?]} 
+\begin{itemize}
+\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
+\begin{equation}
+\label{eq:internal_stab_lemma}
+S(z)=FWL[N_{C}(z)]\hat{N}_{G}(z)+FWL[D_{C}(z)]\hat{D}_{G}(z);
+\end{equation}
+\item the direct loop product $\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle.
+\end{itemize}
+\end{mylemma}
+
+The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for synthesis of digital controllers able to stabilize closed loop system, considering plant parametric uncertainties ({\it i.e.}, $\Delta G_{P}(z)$), quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital controllers.
+Based on it, the model for plant uncertainty due quantisation noise ({\it i.e.}, $\Delta G_{Q}(z)$) may be disregarded if the conditions on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise is bounded.
+
+The quantisation noise is indeed bounded, since the following assumption~\ref{whitenoise} and the Lemmas~\ref{lemma:variance} and~\ref{lemma:boundednoise} are true.
+
+\red{[first: lemmae precede theorems. \\
+second: bounded is not energy bounded. ]}
+
+%
 \begin{myassumption}
@@
 The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
-$Q2$) are bounded uncorrelated white noises.
+$Q2$) are energy bounded uncorrelated white noises.
 % 
@@
 
-By definition~\cite{poularikas2000transforms}, the power spectral density of  $\nu(k)$ is the z-transform of $R_{\nu\nu}(\tau)$, thus
-\begin{equation}
-S_{\nu}(z)=  \sum\limits_{k=-\infty}^{\infty}{R_{\nu\nu}(k)z^{-k}} = \sigma_{Q}^{2},
+By definition~\cite{poularikas2000transforms}, the power spectral density of  $nu(k)$ is the z-transform of $R_{\nu\nu}(\tau)$, thus
+\begin{equation}
+\nu(z)=  \sum\limits_{k=-\infty}^{\infty}{R_{\nu\nu}(k)z^{-k}} = \sigma_{Q}^{2},
 \end{equation}
@@
 \begin{equation}
-S_{\nu}(z)=  \frac{q^{2}}{12}.
+\nu(z)=  \frac{q^{2}}{12}.
 \end{equation}
@@
 Finally, the quantisation noise may be considered a energy-bounded signal (Lemma~\ref{lemma:boundednoise}) and thus $\hat{Y}(z)$ will be bounded and the closed-loop system stable if the conditions in Lemma~\ref{lemma:eq_int_stab} are followed.
-
-\begin{mylemma}{\cite{Bessa16,fadali}}
-\label{lemma:eq_int_stab} 
-A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with a FWL implementation of the digital controller $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete model of the plant $\hat{G}(z)=G(z)+\Delta G_{P}(z)+\Delta G_{Q}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and only if:
-\begin{itemize}
-\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
-\begin{equation}
-\label{eq:internal_stab_lemma}
-S(z)=FWL[N_{C}(z)]\hat{N}_{G}(z)+FWL[D_{C}(z)]\hat{D}_{G}(z);
-\end{equation}
-\item the direct loop product $\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle.
-\end{itemize}
-\end{mylemma}
-
-The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for synthesis of digital controllers able to stabilize closed loop system, considering plant parametric uncertainties ({\it i.e.}, $\Delta G_{P}(z)$), quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital controllers.
-Based on it, the model for plant uncertainty due quantisation noise ({\it i.e.}, $\Delta G_{Q}(z)$) may be disregarded if the conditions on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise is bounded.
-The quantisation noise is indeed bounded, since the following assumption~\ref{whitenoise} and the Lemmas~\ref{lemma:variance} and~\ref{lemma:boundednoise} are true.
-
-%\red{[first: lemmae precede theorems. ]}
-
-%
 
@@
 %------------------------------------
+
+\red{[relate this discussion with the FWL one (and related notations) above.]}
 
@@
 \label{Eq:running-example-controller-quantized}
-C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
-{+}1.895996}{z^2{-}1.843994z+0.849594},
+\resizebox{0.5\textwidth}{!}{
+$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
+{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375},$
+}
 \end{equation} 
@@
 
-\subsection{General architecture of the program synthesiser}
+\paragraph{General architecture of the program synthesiser}
 %
@@
 The input specification provided to the program synthesiser is of the
-form $\exists \vec{P} . \forall \vec{x}. \sigma(\vec{x}, \vec{P})$ where $\vec{P}$ ranges over functions,
+form $\exists \vec{P} . \forall \vec{x} \in \text{\sc inputs}
+. \sigma(\vec{x}, \vec{P})$ where $\vec{P}$ ranges over functions,
 $\vec{x}$ ranges over ground terms and $\sigma$ is a quantifier-free
@@
 satisfying the specification $\sigma(\vec{x}, \vec{P})$ for all
-$\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
+$\vec{x}$.
 %
 If {\sc synthesise} succeeds in finding an witness $\vec{P}$, this
-witness is a candidate solution to the full synthesis formula. 
-We pass this candidate solution to {\sc verify}, which 
-checks whether it is a full solution.
-%determines whether
-%it does satisfy the specification on all inputs by checking
-%satisfiability of the following verification formula:
-%
-%$\exists \vec{x} . \lnot \sigma(\vec{x}, \vec{P})$
-%If this formula is unsatisfiable, 
-%% the candidate solution is in fact a 
-%% full solution.
-If this is the case, then
-the algorithm terminates.
-Otherwise, additional information is provided to the {\sc synthesise}
-phase (e.g. a new counterexample that is added to the {\sc inputs} set)
-and the loop iterates again.
-
-%% the witness $\vec{x}$ denote an input on which the
-%% candidate solution fails to meet the specification.  Thus, $\vec{x}$ is
-%% added to the {\sc inputs} set, and the loop iterates again.
-
-%% It is
-%% worth noting that each iteration of the loop adds a new input to the
-%% finite set $\text{\sc inputs}$ being used for synthesis.  Given that
-%% the full set of inputs $\mathcal{D}$
-%% %\blue{[which by now should have a name, as suggested to be introduced above]} 
-%% is finite, this means that the refinement loop
-%% can only iterate a finite number of times.
-
-\subsection{Synthesis elements specific to control systems}
-
-\paragraph{Property specification}
+witness is a candidate solution to the full synthesis formula.  We
+pass this candidate solution to {\sc verify}, which determines whether
+it does satisfy the specification on all inputs by checking
+satisfiability of the following verification formula:
+%
+$\exists \vec{x} . \lnot \sigma(\vec{x}, \vec{P})$
+
+If this formula is unsatisfiable, the candidate solution is in fact a
+solution to the synthesis formula and so the algorithm terminates.
+Otherwise, the witness $\vec{x}$ denote an input on which the
+candidate solution fails to meet the specification.  Thus, $\vec{x}$ is
+added to the {\sc inputs} set, and the loop iterates again.  It is
+worth noting that each iteration of the loop adds a new input to the
+finite set $\text{\sc inputs}$ being used for synthesis.  Given that
+the full set of inputs $\mathcal{D}$
+%\blue{[which by now should have a name, as suggested to be introduced above]} 
+is finite, this means that the refinement loop
+can only iterate a finite number of times.
+
+\paragraph{Synthesis elements specific to control systems}
+
 Next, we describe the specific property that we pass to the program
@@
 
-We use this method to check the stability in the $z$-domain for the
-characteristic polynomial $S(z)$ defined
-in~\eqref{eq:internal_stab_lemma}.
+We use this method to check the stability in the $z$-domain for the characteristic polynomial $S(z)$ defined in~\eqref{eq:internal_stab_lemma}.
 
@@
 
-%% \red{[clear elucidation of the mapping between this and the domains used 
-%% in the general description of the synthesiser]}
-
-\paragraph{The {\sc Synthesise} and {\sc Verify} phases}
-The {\sc synthesise} phase uses a BMC-based verifier to 
-compute a solution ($N_c$,$D_C$). An important remark is that this 
-controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
-domain.  
-\cdsay{integrate sec 2.4 with Dario}
-
-In the {\sc verify} phase, we have a two-step process. 
-First, in the {\sc Uncertainty} sub-phase, assuming the 
-current precision \param{I_b}{F_b},
-we check whether 
-the system is unstable for the current candidate solution,
-{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$.
-If this is the case, then we obtain a counterexample denoted by 
+\red{[clear elucidation of the mapping between this and the domains used 
+in the general description of the synthesiser]}
+
+In the {\sc verify} phase, if the system is unstable for the current candidate solution,
+{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$, 
+then we obtain a counterexample denoted by 
 values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
@@
 
-If the result of the {\sc Uncertainty} verification is that
-the system is stable for the current candidate solution,
-then we pass this solution to the {\sc Precision} verification sub-phase, 
-which checks the propagation of the error in the fixed-point 
-calculations. If this check returns $false$, then we 
-increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise} phase
-with an empty {\sc inputs} set.
-Otherwise, we found a full solution for our synthesis problem
-and we are done.
-
-\subsection{Program synthesis for the running example}
+\paragraph{Program synthesis for the running example}
 We will illustrate our synthesis approach on the running example 
 in Sec.~\ref{sec:running-ex}.
-We start with the candidate solution given below at $I_b=16,F_b=24$,
-which has all coefficients 0.
+We start with the candidate solution given below, which has all coefficients 0.
 Note that the digital controller is designed with typical control system
@@
 \begin{array}{ll}
-\Delta N_G(z) = 0.026506\\
-\Delta D_G(z) = 1.000610z+1.002838
+\Delta N_G(z) = 0.02634525299072265625\\
+\Delta D_G(z) = 0.9979267120361328125z-0.99768829345703125
 \end{array}
@@
 \begin{array}{ll}
-N_C(z) {=} 12.402664z^2{-}11.439667z{+}0.596756\\
-D_C(z) {=} 4.003906z^2{-}0.287949z{+}0.015625\\
+N_C(z) {=} 4.00888156890869140625z^2{-}0.00041961669921875z\\
+\qquad\qquad -0.000213623046875\\
+D_C(z) {=} -0.003753662109375z^2{+}7.37355804443359375z \\
+\qquad\qquad -7.2847900390625\\
 \end{array}
@@
 In the second {\sc verify} phase, we check whether the current candidate
-solution above is the final solution. It is not and the verifier signals
-that it is due to lack of precision. We thus increase our precision to
-$I_b=20,F_b=28$.
-%
-We stay in the {\sc verify} phase and receive a new counterexample at
-higher precision:
-\cdsay{Pascal, this sounds confusing. if you want to increase precision on-the-fly, i.e. 
-not going back to the synthesise phase, 
-then this illustration doesn't follow the general diagram in Fig.5. 
-We need to decide which direction we keep.}
-%
+solution above is the final solution. It is not and we get a new counterexample:
 $$
 \begin{array}{ll}
-\Delta N_G(z) {=} 0.026314\\
-\Delta D_G(z) {=} 0.999024z{-}1.004785
+\Delta N_G(z) = 0.02644824981689453125\\
+\Delta D_G(z) {=} 1.00053310394287109375z{-}1.0014629364013671875
 \end{array}
@@
 %\blue{[Nice, now I'm in the groove. Next unfolds well.] }
-Since previous counterexamples were attained at lower precision, we 
-remove them from the counterexample set. In the next {\sc synthesise}
-phase, we get a new candidate solution that holds for the newly
-inserted counterexample:
+After adding this new counterexample to the set of {\sc inputs}, in the 
+next {\sc synthesise} phase, we get a new candidate solution that holds
+for both uncertainties in {\sc Inputs}:
 
@@
 \begin{array}{ll}
-N_C(z) {=} 11.035202z^2{+}5.846100z{+}4.901855\\
-D_C(z) {=} 1.097901z^2{+}0.063110z{+}0.128357\\
+N_C(z) {=} 7.515781402587890625z^2{-}4.385616302490234375z\\
+\qquad\qquad +4.142093658447265625\\
+D_C(z) {=} -3.52398681640625z^2{-}1.530254364013671875z \\
+\qquad\qquad +7.58094024658203125\\
 \end{array}
@@
 },
-          row sep=1cm, column sep=1.5cm] {
-   \coordinate (aux1);
-   \& \coordinate (aux2);
-   \&;\\
+          row sep=1cm, column sep=1cm] {
+   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}}; \\
    \node[fill=yellow!20] (synth) {{\sc Synthesise}};
    \&
-   complexnode/.pic={ 
-     \node[rectangle,draw,dashed,
-	minimum width=7cm,
-	minimum height=.8cm,
-	label={\sc Verify},] (verif) {};
-   \node[fill=yellow!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc ~Uncertainty~~~~}};
-   \node[fill=yellow!20] (verif2) at ([xshift=2cm]verif.center) {{\sc ~~~~~Precision~~~}};
-   } 
-   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
-   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
-   %% \&
-   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
+   \node[fill=yellow!20] (verif) {{\sc Verify}}; \\
+
    \& \\
    \& \\
-   \node (gp) {Closed-loop System Search};
+   \node (gp) {~~~~~~~~~~~~~~Closed-loop System Search~~~~~~~~~~~~~~~};
    \&
-   complexnode/.pic={ 
-     \coordinate (aux);
-   \node (bmc) at ([xshift=-2cm]aux.center) {BMC-based Verifier};
-   \node (fp)  at ([xshift=2cm]aux.center) {Fixed-point \\Arithmetic Verifier};
-   }   
+   \node (bmc) {~~~~~~~~~~~~~~~BMC-based Verifier~~~~~~~~~~~~~~~};
+
     \\
@@
    \path
-    ([yshift=2em]synth.east) edge node {Candidate solution} ([yshift=2em]verif1.west)
-    ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east)
-    ([xshift=5em]verif1.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]bmc.north)
-    ([xshift=5em]verif2.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]fp.north)
-    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
-    ([xshift=-5em]fp.north) edge node[align=center]  {True/\\False} ([xshift=-5em]verif2.south)
-    (verif2) edge node {} (done)
+    ([yshift=2em]synth.east) edge node {Candidate solution} ([yshift=2em]verif.west)
+    ([yshift=-2em]verif.west) edge node {Counterexample} ([yshift=-2em]synth.east)
+    ([xshift=5em]verif.south) edge node {Candidate $P$} ([xshift=5em]bmc.north)
+    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif.south)
+    (verif) edge node {} (done)
     ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
-    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south)
-    (aux1) edge (synth.north);
-   \path[-]
-   (verif2.north) edge node[align=center] {} ([xshift=6.7cm]aux2)
-   ([xshift=6.7cm]aux2) edge node[align=center] {Increase Precision} (aux1);
-
+    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south);
  \end{tikzpicture}
@@
 \label{experimental-results}
-We outline the runtimes required to synthesise a stable controller for each
-benchmark in Table~\ref{tab:results}. For most benchmarks the conjecture explained
-in section~\ref{fixedpoint_verification} holds and the inductive back-end is able
-to find a stable solution in less than one minute. This is possible if the inductive
-solutions need to be refined with few counterexamples and fixed point precision
-increases. However, some of our benchmarks did not meet these criteria. In these
-cases the interval arithmetic back-end was able to complement the inductive approach
-and synthesise a solution instead, albeit with significantly larger runtimes.
-
-\begin{figure}[H]
-\centering
-\begin{tabular}{l | r l r l}
-Benchmark              & Base     &         & Unc     & \\\cline{1-4}
-CruiseControl02        & 17\,s    &         & 46\,s   & \\
-SatelliteB2            & 7\,s     &         & 6601\,s & \tbmark\\
-SatelliteC2            & 369\,s   & \tbmark & 76\,s   & \tbmark\\
-SpringMassDamper       &          &         &         & 
-\end{tabular}
-
-\vspace{0.5em}
-\scriptsize{* = solved with interval back-end}
-\vspace{0.5em}
-
-\caption{Experimental results. \label{tab:results}}
-\end{figure}
 %---------------------------------
-
-We conclude from these results that the inductive back-end provides excellent performance
-for synthesising stable controllers in the majority of the benchmarks, and can be
-complemented using the interval arithmetic back-end where the inductive conjectures fail
-too frequently. Both back-ends enabled controller synthesis for all benchmarks within
-reasonable time frames.
 

### 2016-10-13 paper/paper.tex

--- 2016-10-12 paper/paper.tex
@@
 
-A typical hybrid system, with a continuous plant and discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$
+\red{[where is this new variable used later?]}
+
+A typical hybrid system \red{[clarify the adjective ``hybrid'']} is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$
+\red{[this Delta term now refers to the continuous plant? this is not what has been discussed before, nor what is in some of the plots.]} 
 , $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.
@@
 
-%
+Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
+using Fixed-Point bit vectors with integer size $I_b$ and fractional
+size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
+%
+\begin{align}
+\small
+\label{digital_controller_plant_tf}
+\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
+%\label{plant_tf}
+\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
+\end{align}
+
+Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
+domain,
+%
+ $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
+
+Two approaches have been taken to synthesise a stable controller based on this model.
+The first uses interval arithmetic, representing the coefficients $[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\ {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$  
+and rounding operations outwards during the process. This results in a tighter calculation of the error at the cost of performance.
 
@@
 %------------------------------------
+>>>>>>> 37d4cc3c530b25bf97f1052f7c187af06f832aea
 

### 2016-10-13 paper/paper.tex
review experimental results

--- 2016-10-12 paper/paper.tex
@@
 \label{experimental-results}
+
+\textcolor{red}{How did you obtain the results from Table~\ref{tab:results}? 
+Can you provide the command-line? The reviewers should be able to reproduce our experiments.}
 We outline the runtimes required to synthesise a stable controller for each
-benchmark in Table~\ref{tab:results}. For most benchmarks the conjecture explained
-in section~\ref{fixedpoint_verification} holds and the inductive back-end is able
-to find a stable solution in less than one minute. This is possible if the inductive
-solutions need to be refined with few counterexamples and fixed point precision
-increases. However, some of our benchmarks did not meet these criteria. In these
-cases the interval arithmetic back-end was able to complement the inductive approach
-and synthesise a solution instead, albeit with significantly larger runtimes.
+benchmark in Table~\ref{tab:results}. \textcolor{red}{Which section do you refer??
+For most benchmarks the conjecture explained in section~\ref{fixedpoint_verification} 
+holds and the inductive back-end is able to find a stable solution in less than one minute}. 
+This is possible if the inductive solutions need to be refined with few counterexamples 
+and fixed point precision increases. However, some of our benchmarks did not meet these criteria. 
+\textcolor{red}{Which cases? Can you refer to Table~\ref{tab:results} In these cases, 
+the interval arithmetic back-end is able to complement the inductive approach
+and synthesise a solution instead, albeit with significantly larger runtimes}.
 
@@
 
+\textcolor{red}{Can you provide the synthesised controllers? Iury could then check the solution using the bode diagram.}
 We conclude from these results that the inductive back-end provides excellent performance
-for synthesising stable controllers in the majority of the benchmarks, and can be
-complemented using the interval arithmetic back-end where the inductive conjectures fail
+for synthesising stable controllers in the majority of the benchmarks \textcolor{red}{can you be more specific? which benchmarks?}, and can be
+complemented using the interval arithmetic back-end, where the inductive conjectures fail
 too frequently. Both back-ends enabled controller synthesis for all benchmarks within

### 2016-10-13 paper/paper.tex
remove 37d4cc3c530b25bf97f1052f7c187af06f832aea
Describing the parametric uncertainties results

--- 2016-10-13 paper/paper.tex
@@
 
-\red{[where is this new variable used later?]}
-
-A typical hybrid system \red{[clarify the adjective ``hybrid'']} is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$
-\red{[this Delta term now refers to the continuous plant? this is not what has been discussed before, nor what is in some of the plots.]} 
+A typical hybrid system, with a continuous plant and discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$
 , $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.
@@
 
+%
+
+%, thus supporting this assumption.
+
+%------------------------------------
+\subsection{Using Fixed Point Arithmetic for verification}
+\label{fixedpoint_verification}
+%------------------------------------
+
 Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
@@
  $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
+%
+However, given a real plant and real controller $\hat{G}(z), \hat{C}(z)$, and a discretizing function
+\begin{align}
+\small
+\label{FWL_tf}
+&f_b (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = x-(x\mod\tilde x)
+\end{align}
+we calculate $\tilde C(z)=f(\hat{C}(z))$ and $\tilde G(z)=f(\hat{G}(z))$
+\begin{align}
+\label{digital_controller_tf}
+\tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
+&= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
+\label{digital_plant_tf}
+\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_q \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_q \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_q \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_q \hat{a}_{N_G})z^{-N_G}} \nonumber \\
+&=G(z)+\Delta{G}_P(z)+\Delta{G}_b(z).
+\end{align}
+where $\Delta_b\hat{c}_i=\hat{c}_i\mod \tilde{c}_i$
+and $\Delta{G}_b(z)$ represents the plant uncertainty caused by
+the rounding off effect.  We may encompass all the uncertainty as
+$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_b(z)$.  Since this value is
+nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
+denoted by $\mathfrak{G}(z)$.
 
@@
 
-%, thus supporting this assumption.
-
-%------------------------------------
-%\subsection{Using Fixed Point Arithmetic for verification}
-%\label{fixedpoint_verification}
-%------------------------------------
->>>>>>> 37d4cc3c530b25bf97f1052f7c187af06f832aea
-
+The second approach uses a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is assumed to be within the expected bounds and verified after synthesis using the interval version of the program.
+The first verification phase produces a counterexample if some instance of $\mathfrak{G}(z)$ does not verify the properties and the CEGIS loop iteratively looks for a new controller that verifies the supplied counterexamples.
+The second phase verifies the propagation of the error in the fixed point calculations.
+If the second phase fails verification, we increase the precision of the analyser and feed the CEGIS loop again to find a sound solution.
+The resulting increase in speed of this approach over the former, which is of several orders of magnitude, vouches for the use of CEGIS in most of our benchmarks.
 %------------------------------------
@@
 
-%% \red{[clear elucidation of the mapping between this and the domains used 
-%% in the general description of the synthesiser]}
-
-\paragraph{The {\sc Synthesise} and {\sc Verify} phases}
-The {\sc synthesise} phase uses a BMC-based verifier to 
-compute a solution ($N_c$,$D_C$). An important remark is that this 
-controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
-domain.  
-\cdsay{integrate the following with Dario}
-Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
-using Fixed-Point bit vectors with integer size $I_b$ and fractional
-size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
-%
-\begin{align}
-\small
-\label{digital_controller_plant_tf}
-\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
-%\label{plant_tf}
-\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
-\end{align}
-
-Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
-domain,
-%
- $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
-%
-However, given a real plant and real controller $\hat{G}(z), \hat{C}(z)$, and a discretizing function
-\begin{align}
-\small
-\label{FWL_tf}
-&f_b (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = x-(x\mod\tilde x)
-\end{align}
-we calculate $\tilde C(z)=f(\hat{C}(z))$ and $\tilde G(z)=f(\hat{G}(z))$
-\begin{align}
-\label{digital_controller_tf}
-\tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
-&= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
-\label{digital_plant_tf}
-\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_q \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_q \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_q \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_q \hat{a}_{N_G})z^{-N_G}} \nonumber \\
-&=G(z)+\Delta{G}_P(z)+\Delta{G}_b(z).
-\end{align}
-where $\Delta_b\hat{c}_i=\hat{c}_i\mod \tilde{c}_i$
-and $\Delta{G}_b(z)$ represents the plant uncertainty caused by
-the rounding off effect.  We may encompass all the uncertainty as
-$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_b(z)$.  Since this value is
-nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
-denoted by $\mathfrak{G}(z)$.
-
-Two approaches have been taken to synthesise a stable controller based on this model.
-The first uses interval arithmetic, representing the coefficients $[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\ {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
-and rounding operations outwards during the process. This results in a tighter calculation of the error at the cost of performance.
-
-The second approach uses a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is assumed to be within the expected bounds and verified after synthesis using the interval version of the program.
-The first verification phase produces a counterexample if some instance of $\mathfrak{G}(z)$ does not verify the properties and the CEGIS loop iteratively looks for a new controller that verifies the supplied counterexamples.
-The second phase verifies the propagation of the error in the fixed point calculations.
-If the second phase fails verification, we increase the precision of the analyser and feed the CEGIS loop again to find a sound solution.
-The resulting increase in speed of this approach over the former, which is of several orders of magnitude, vouches for the use of CEGIS in most of our benchmarks.
-\cdsay{end of integration}
-
-In the {\sc verify} phase, we have a two-step process. 
-First, in the {\sc Uncertainty} sub-phase, assuming the 
-current precision \param{I_b}{F_b},
-we check whether 
-the system is unstable for the current candidate solution,
-{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$.
-If this is the case, then we obtain a counterexample denoted by 
+\red{[clear elucidation of the mapping between this and the domains used 
+in the general description of the synthesiser]}
+
+In the {\sc verify} phase, if the system is unstable for the current candidate solution,
+{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$, 
+then we obtain a counterexample denoted by 
 values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
@@
 
-If the result of the {\sc Uncertainty} verification is that
-the system is stable for the current candidate solution,
-then we pass this solution to the {\sc Precision} verification sub-phase, 
-which checks the propagation of the error in the fixed-point 
-calculations. If this check returns $false$, then we 
-increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise} phase
-with an empty {\sc inputs} set.
-Otherwise, we found a full solution for our synthesis problem
-and we are done.
-
-\subsection{Program synthesis for the running example}
+\paragraph{Program synthesis for the running example}
 We will illustrate our synthesis approach on the running example 
@@
 higher precision:
-\cdsay{Pascal, this sounds confusing. if you want to increase precision on-the-fly, i.e. 
-not going back to the synthesise phase, 
-then this illustration doesn't follow the general diagram in Fig.5. 
-We need to decide which direction we keep.}
 %
@@
 {\sc verify} phase, which fails to find a new counterexample (i.e. returns UNSAT).
+
+\blue{
+For the same cruise control system, the synthesis may be done considering that the plant model have parametric uncertainties ($\Delta G_{P}(z)$).
+Thus, the synthesised controller must to stabilize for any parametric variation $\Delta p$ inside of a given region.
+Specially, in this example, was assumed that each coefficient of $G(z)$ may vary $\pm 0.5\%$.
+}
+
+\blue{Initially, the controller denominator and numerator  ($D_{C}(z)$ and $N_{C}(z)$) are started with zero coefficients, as in previous example.
+Thus,  in the first {\sc verify} phase a counterexample is presented, that is added to {\sc inputs}, whis is usede in the first  {\sc synthesise} phase.
+The resulting controller is
+}
 
@@
 \centering
-\begin{tabular}{l | r r l}
-Benchmark              & Base     & Unc     & \\\cline{1-4}
-CruiseControl02        & 17\,s    & 46\,s   & \\
-SatelliteB2            & 7\,s     & 6601\,s & \tbmark\\
-SatelliteC2            & 2\,s     & 76\,s   & \tbmark\\
-SpringMassDamper       & 28\,s    & \xmark  &
+\begin{tabular}{l | r l r l}
+Benchmark              & Base     &         & Unc     & \\\cline{1-4}
+CruiseControl02        & 17\,s    &         & 46\,s   & \\
+SatelliteB2            & 7\,s     &         & 6601\,s & \tbmark\\
+SatelliteC2            & 369\,s   & \tbmark & 76\,s   & \tbmark\\
+SpringMassDamper       &          &         &         & 
 \end{tabular}
@@
 \vspace{0.5em}
-\scriptsize{* = solved with interval back-end, \xmark = uncontrollable}
+\scriptsize{* = solved with interval back-end}
 \vspace{0.5em}

### 2016-10-13 paper/paper.tex

--- 2016-10-13 paper/paper.tex
@@
 %------------------------------------
->>>>>>> 37d4cc3c530b25bf97f1052f7c187af06f832aea
 

### 2016-10-13 paper/paper.tex
fix typos

--- 2016-10-13 paper/paper.tex
@@
 synthesis in conjunction with a digital verification algorithm to find a
-parametric solution for a digital controller given a continuous plant
-specification.
+parametric solution for a digital controller given a continuous 
+plant specification.
 %
@@
 The digital controllers synthesized in this paper are typically used in closed loops with continuous (and physical) plants.
-Thus, the proposed approach have to consider dynamics of continuous parts of system ({\it e.g.}, plant) and discrete parts ({\it e.g.}, digital controller), {\it i.e.} the synthesized controller have to consider the issues related to the hybrid systems studies.
+Thus, the proposed approach has to consider dynamics of continuous parts of system ({\it e.g.}, plant) and discrete parts ({\it e.g.}, digital controller), {\it i.e.} the synthesized controller has to consider the issues related to the hybrid systems studies.
 

### 2016-10-13 paper/paper.tex
intro to FP

@@
 
-The vector of parametric uncertainties  $\Delta{p}$ for $G(z)$ is defined by:
+The vector of parametric coefficient uncertainties $\Delta{p}$ of $\Delta{G}_p(z)$ is defined by:
 \begin{equation}
@@
 
-\red{[where is this new variable used later?]}
-
-A typical hybrid system \red{[clarify the adjective ``hybrid'']} is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$
+A typical hybrid system, with a continuous plant and a discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$
 \red{[this Delta term now refers to the continuous plant? this is not what has been discussed before, nor what is in some of the plots.]} 
@@
 domain.
+A second remark is that the synthesis and verification engines use fixed/floating point arithmetic,
+therefore we also need to examine the effect of discretization during these operations.
 \cdsay{integrate the following with Dario}

### 2016-10-13 paper/paper.tex
review Results
minor changes
Unc example
review conclusions

@@
 
+\textcolor{red}{Can you relate the benchmarks in Table~\ref{tab:results} in terms of 
+$C$ and $G$ as described in section~\ref{experimental-setup}. You could add an additional column to that table.}
+
 \begin{figure}[H]
@@
 
-\caption{Experimental results. \label{tab:results}}
+\caption{Experimental results. \textcolor{red}{It should be a table and not a figure.} \label{tab:results}}
 \end{figure}
@@
 
+In this study, we have investigated a CEGIS-based approach that uses inductive synthesis 
+in conjunction with a robust closed-loop stability verification algorithm to find a parametric 
+solution for a digital controller given a continuous (or discrete) plant specification.
+In particular, we have exploited the automatic synthesis of correct-by-construction 
+digital controllers along with a model of their physical environment.
+We have also modeled a digital equivalent of the physical plant by evaluating the 
+effects of the quantisers (A/D and D/A converters) as time discretisation elements 
+with quantisation noise. Experimental results show that the inductive back-end of our
+CEGIS-based approach is able to synthesise stable controllers in most benchmarks and can be 
+complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
+Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
+Further studies include the extension of this CEGIS-based approach for different classes of systems
+({\it e.g.}, state-space) and also consider performance requirements while synthesising 
+the digital controller.
+
 \bibliographystyle{abbrv}

### 2016-10-13 paper/paper.tex
review DSVerifier Verification Flow

@@
 non-deterministic model to represent the plant family $\mathfrak{G}(z)$
-(Step A), and a transfer function $f$ [eq.  \ref{FWL_tf}] (step B) to
-calulate the implementation $f(\hat{C}(z)) \rightarrow \tilde C(z)$ of the
-controller (step C).  Finally DSVerifier builds an intermediate ANSI-C code
+(Step A), and a transfer function $f$ represented by Eq.~\eqref{FWL_tf} 
+(step B) to calulate the implementation $f(\hat{C}(z)) \rightarrow \tilde C(z)$ 
+of the controller (step C).  Finally DSVerifier builds an intermediate ANSI-C code
 for the digital system implementation, which is used as input for the

### 2016-10-13 paper/paper.tex
Unc example
Updated experiments result table.

@@
 
-$$
-\begin{array}{ll}
-N_C(z) {=} 0z^2{+}0z{+}0\\
-D_C(z) {=} 0z^2{+}0z{+}0\\
-\end{array}
+%$$
+%\begin{array}{ll}
+%N_C(z) {=} 0z^2{+}0z{+}0\\
+%D_C(z) {=} 0z^2{+}0z{+}0\\
+%\end{array}
+%$$
+$$
+\blue{
+C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}
+}
 $$
@@
 $$
-\begin{array}{ll}
-N_C(z) {=} 12.402664z^2{-}11.439667z{+}0.596756\\
-D_C(z) {=} 4.003906z^2{-}0.287949z{+}0.015625\\
-\end{array}
+\blue{
+C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}
+}
 $$
@@
 $$
-\begin{array}{ll}
-N_C(z) {=} 11.035202z^2{+}5.846100z{+}4.901855\\
-D_C(z) {=} 1.097901z^2{+}0.063110z{+}0.128357\\
-\end{array}
-$$
+\blue{
+C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}
+}
+$$
+%
+%$$
+%\begin{array}{ll}
+%N_C(z) {=} \\
+%D_C(z) {=} \\
+%\end{array}
+%$$
 
@@
 Thus,  in the first {\sc verify} phase a counterexample is presented, that is added to {\sc inputs}, whis is usede in the first  {\sc synthesise} phase.
-The resulting controller is
+The resulting controller is:
 }
+$$
+{
+\blue{
+C(z)=\frac{0.77516z^2{+}-0.71497z{+}0.03729}{0.25024z^2{-}0.01799z{+}0.00097}
+}}
+$$
+
+\blue{In the second {\sc verify} phase, the controller failed to stabilize the system for all the range of uncertainties, another counterexample was provided, and the following candidate controller is presented in another {\sc synthesise} phase:}
+$$
+{
+\blue{
+C(z)=\frac{0.68970z^2{+}0.36538z{+}0.30637}{0.06862z^2{+}0.00394z{+}0.00802}
+}}
+$$
 
@@
 
-\begin{figure}[H]
+\begin{table}[H]
 \centering
-\begin{tabular}{l | r r l}
-Benchmark              & Base     & Unc     & \\\cline{1-4}
-CruiseControl02        & 17\,s    & 46\,s   & \\
-SatelliteB2            & 7\,s     & 6601\,s & \tbmark\\
-SatelliteC2            & 2\,s     & 76\,s   & \tbmark\\
-SpringMassDamper       & 28\,s    & \xmark  &
+\begin{tabular}{l | r l}
+Benchmark                 & Base    & \\\cline{1-2}
+CruiseControl02           & 17\,s   & \\
+CruiseControl02$^\dagger$ & 46\,s   & \\
+SatelliteB2               & 7\,s    & \\
+SatelliteB2$^\dagger$     & 6601\,s & \tbmark\\
+SatelliteC2               & 2\,s    & \\
+SatelliteC2$^\dagger$     & 76\,s   & \tbmark\\
+SpringMassDamper          & 28\,s   & \\
+a\_PL1\_SCH2\_IMPL1       & 2704\,s & \\
+a\_PL1\_SCH2\_IMPL2       & 538\,s  & \\
+a\_PL1\_SCH2\_IMPL3       & 12\,s   & \\
+a\_PL1\_SCH3\_IMPL1       & 318\,s  & \\
+a\_PL1\_SCH3\_IMPL2       & 967\,s  & \\
+a\_PL1\_SCH3\_IMPL3       & 9798\,s & \\
+a\_PL1\_SCH4\_IMPL1       & 6304\,s & \\
 \end{tabular}
@@
 \vspace{0.5em}
-\scriptsize{* = solved with interval back-end, \xmark = uncontrollable}
+\scriptsize{* = solved with interval back-end, $\dagger$ = with uncertainty}
 \vspace{0.5em}
 
-\caption{Experimental results. \textcolor{red}{It should be a table and not a figure.} \label{tab:results}}
-\end{figure}
+\caption{Experimental results. \label{tab:results}}
+\end{table}
 %---------------------------------

### 2016-10-13 paper/paper.tex
Updated experimental section text.

@@
 This is possible if the inductive solutions need to be refined with few counterexamples 
-and fixed point precision increases. However, some of our benchmarks did not meet these criteria. 
-\textcolor{red}{Which cases? Can you refer to Table~\ref{tab:results} In these cases, 
+and fixed point precision increases. However, two benchmarks in our set did not meet these
+criteria (marked with $^*$ in Table~\ref{tab:results}). In these cases, 
 the interval arithmetic back-end is able to complement the inductive approach
-and synthesise a solution instead, albeit with significantly larger runtimes}.
+and synthesise a solution instead, albeit with significantly larger runtimes.
 
@@
 We conclude from these results that the inductive back-end provides excellent performance
-for synthesising stable controllers in the majority of the benchmarks \textcolor{red}{can you be more specific? which benchmarks?}, and can be
-complemented using the interval arithmetic back-end, where the inductive conjectures fail
-too frequently. Both back-ends enabled controller synthesis for all benchmarks within
-reasonable time frames.
+for synthesising stable controllers in the 12 out of 14 benchmarks, and can be
+complemented using the interval arithmetic back-end for the remaining 2 benchmarks,
+where the inductive conjectures fail too frequently. Both back-ends together enabled controller
+synthesis for all benchmarks within reasonable time frames.
 

### 2016-10-13 paper/paper.tex
Unc example

--- 2016-10-13 paper/paper.tex
@@
 \begin{equation}
-\Delta{p}=\begin{bmatrix}
+\Delta{\vec{p}}=\begin{bmatrix}
 \hat{b_{0}} - b_{0}\\
@@
 non-deterministic model to represent the plant family $\mathfrak{G}(z)$
-(Step A), and a transfer function $f$ represented by Eq.~\eqref{FWL_tf} 
-(step B) to calulate the implementation $f(\hat{C}(z)) \rightarrow \tilde C(z)$ 
-of the controller (step C).  Finally DSVerifier builds an intermediate ANSI-C code
+(Step A), and a transfer function $f$ [eq.  \ref{FWL_tf}] (step B) to
+calulate the implementation $f(\hat{C}(z)) \rightarrow \tilde C(z)$ of the
+controller (step C).  Finally DSVerifier builds an intermediate ANSI-C code
 for the digital system implementation, which is used as input for the
@@
 In the first {\sc verify} phase we obtain the following counterexample:
-$$
-\begin{array}{ll}
-\Delta N_G(z) = 0.026506\\
-\Delta D_G(z) = 1.000610z+1.002838
-\end{array}
-$$
+
+$$
+\blue{
+\Delta{\vec{p}} = [0.026506~ 1.000610~ 1.002838]^T
+}
+$$
+
+%$$
+%\begin{array}{ll}
+%\Delta N_G(z) = 0.026506\\
+%\Delta D_G(z) = 1.000610z+1.002838
+%\end{array}
+%$$
 
@@
 %
-$$
-\begin{array}{ll}
-\Delta N_G(z) {=} 0.026314\\
-\Delta D_G(z) {=} 0.999024z{-}1.004785
-\end{array}
-$$
+%$$
+%\begin{array}{ll}
+%\Delta N_G(z) {=} 0.026314\\
+%\Delta D_G(z) {=} 0.999024z{-}1.004785
+%\end{array}
+%$$
+$$
+\blue{
+\Delta{\vec{p}} = [0.026314~ 0.999024~ {-}1.004785]^T
+}
+$$
+
 %\blue{[Nice, now I'm in the groove. Next unfolds well.] }
@@
 $$
+
+\blue{
+This candidate solution is validated as the final solution by the next 
+{\sc verify} phase.
+}
 
@@
 
-\begin{table}[H]
+\begin{figure}[H]
 \centering
-\begin{tabular}{l | r l}
-Benchmark                 & Base    & \\\cline{1-2}
-CruiseControl02           & 17\,s   & \\
-CruiseControl02$^\dagger$ & 46\,s   & \\
-SatelliteB2               & 7\,s    & \\
-SatelliteB2$^\dagger$     & 6601\,s & \tbmark\\
-SatelliteC2               & 2\,s    & \\
-SatelliteC2$^\dagger$     & 76\,s   & \tbmark\\
-SpringMassDamper          & 28\,s   & \\
-a\_PL1\_SCH2\_IMPL1       & 2704\,s & \\
-a\_PL1\_SCH2\_IMPL2       & 538\,s  & \\
-a\_PL1\_SCH2\_IMPL3       & 12\,s   & \\
-a\_PL1\_SCH3\_IMPL1       & 318\,s  & \\
-a\_PL1\_SCH3\_IMPL2       & 967\,s  & \\
-a\_PL1\_SCH3\_IMPL3       & 9798\,s & \\
-a\_PL1\_SCH4\_IMPL1       & 6304\,s & \\
+\begin{tabular}{l | r r l}
+Benchmark              & Base     & Unc     & \\\cline{1-4}
+CruiseControl02        & 17\,s    & 46\,s   & \\
+SatelliteB2            & 7\,s     & 6601\,s & \tbmark\\
+SatelliteC2            & 2\,s     & 76\,s   & \tbmark\\
+SpringMassDamper       & 28\,s    & \xmark  &
 \end{tabular}
@@
 \vspace{0.5em}
-\scriptsize{* = solved with interval back-end, $\dagger$ = with uncertainty}
+\scriptsize{* = solved with interval back-end, \xmark = uncontrollable}
 \vspace{0.5em}
 
-\caption{Experimental results. \label{tab:results}}
-\end{table}
+\caption{Experimental results. \textcolor{red}{It should be a table and not a figure.} \label{tab:results}}
+\end{figure}
 %---------------------------------

### 2016-10-13 paper/paper.tex
hscc17

@@
 synthesis in conjunction with a digital verification algorithm to find a
-parametric solution for a digital controller given a continuous 
-plant specification.
+parametric solution for a digital controller given a continuous plant
+specification.
 %
@@
 The digital controllers synthesized in this paper are typically used in closed loops with continuous (and physical) plants.
-Thus, the proposed approach has to consider dynamics of continuous parts of system ({\it e.g.}, plant) and discrete parts ({\it e.g.}, digital controller), {\it i.e.} the synthesized controller has to consider the issues related to the hybrid systems studies.
+Thus, the proposed approach have to consider dynamics of continuous parts of system ({\it e.g.}, plant) and discrete parts ({\it e.g.}, digital controller), {\it i.e.} the synthesized controller have to consider the issues related to the hybrid systems studies.
 
@@
 
-The vector of parametric coefficient uncertainties $\Delta{p}$ of $\Delta{G}_p(z)$ is defined by:
-\begin{equation}
-\Delta{\vec{p}}=\begin{bmatrix}
+The vector of parametric uncertainties  $\Delta{p}$ for $G(z)$ is defined by:
+\begin{equation}
+\Delta{p}=\begin{bmatrix}
 \hat{b_{0}} - b_{0}\\
@@
 
-A typical hybrid system, with a continuous plant and a discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$
+\red{[where is this new variable used later?]}
+
+A typical hybrid system \red{[clarify the adjective ``hybrid'']} is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$
 \red{[this Delta term now refers to the continuous plant? this is not what has been discussed before, nor what is in some of the plots.]} 
@@
 domain.  
-A second remark is that the synthesis and verification engines use fixed/floating point arithmetic,
-therefore we also need to examine the effect of discretization during these operations.
 \cdsay{integrate the following with Dario}
@@
 
-%$$
-%\begin{array}{ll}
-%N_C(z) {=} 0z^2{+}0z{+}0\\
-%D_C(z) {=} 0z^2{+}0z{+}0\\
-%\end{array}
-%$$
 $$
-\blue{
-C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}
-}
+\begin{array}{ll}
+N_C(z) {=} 0z^2{+}0z{+}0\\
+D_C(z) {=} 0z^2{+}0z{+}0\\
+\end{array}
 $$
@@
 In the first {\sc verify} phase we obtain the following counterexample:
-
 $$
-\blue{
-\Delta{\vec{p}} = [0.026506~ 1.000610~ 1.002838]^T
-}
+\begin{array}{ll}
+\Delta N_G(z) = 0.026506\\
+\Delta D_G(z) = 1.000610z+1.002838
+\end{array}
 $$
-
-%$$
-%\begin{array}{ll}
-%\Delta N_G(z) = 0.026506\\
-%\Delta D_G(z) = 1.000610z+1.002838
-%\end{array}
-%$$
 
@@
 $$
-\blue{
-C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}
-}
+\begin{array}{ll}
+N_C(z) {=} 12.402664z^2{-}11.439667z{+}0.596756\\
+D_C(z) {=} 4.003906z^2{-}0.287949z{+}0.015625\\
+\end{array}
 $$
@@
 %
-%$$
-%\begin{array}{ll}
-%\Delta N_G(z) {=} 0.026314\\
-%\Delta D_G(z) {=} 0.999024z{-}1.004785
-%\end{array}
-%$$
 $$
-\blue{
-\Delta{\vec{p}} = [0.026314~ 0.999024~ {-}1.004785]^T
-}
+\begin{array}{ll}
+\Delta N_G(z) {=} 0.026314\\
+\Delta D_G(z) {=} 0.999024z{-}1.004785
+\end{array}
 $$
-
 %\blue{[Nice, now I'm in the groove. Next unfolds well.] }
@@
 $$
-\blue{
-C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}
-}
+\begin{array}{ll}
+N_C(z) {=} 11.035202z^2{+}5.846100z{+}4.901855\\
+D_C(z) {=} 1.097901z^2{+}0.063110z{+}0.128357\\
+\end{array}
 $$
-%
-%$$
-%\begin{array}{ll}
-%N_C(z) {=} \\
-%D_C(z) {=} \\
-%\end{array}
-%$$
 
@@
 {\sc verify} phase, which fails to find a new counterexample (i.e. returns UNSAT).
-
-\blue{
-For the same cruise control system, the synthesis may be done considering that the plant model have parametric uncertainties ($\Delta G_{P}(z)$).
-Thus, the synthesised controller must to stabilize for any parametric variation $\Delta p$ inside of a given region.
-Specially, in this example, was assumed that each coefficient of $G(z)$ may vary $\pm 0.5\%$.
-}
-
-\blue{Initially, the controller denominator and numerator  ($D_{C}(z)$ and $N_{C}(z)$) are started with zero coefficients, as in previous example.
-Thus,  in the first {\sc verify} phase a counterexample is presented, that is added to {\sc inputs}, whis is usede in the first  {\sc synthesise} phase.
-The resulting controller is:
-}
-$$
-{
-\blue{
-C(z)=\frac{0.77516z^2{+}-0.71497z{+}0.03729}{0.25024z^2{-}0.01799z{+}0.00097}
-}}
-$$
-
-\blue{In the second {\sc verify} phase, the controller failed to stabilize the system for all the range of uncertainties, another counterexample was provided, and the following candidate controller is presented in another {\sc synthesise} phase:}
-$$
-{
-\blue{
-C(z)=\frac{0.68970z^2{+}0.36538z{+}0.30637}{0.06862z^2{+}0.00394z{+}0.00802}
-}}
-$$
-
-\blue{
-This candidate solution is validated as the final solution by the next 
-{\sc verify} phase.
-}
 
@@
 \label{experimental-results}
-
-\textcolor{red}{How did you obtain the results from Table~\ref{tab:results}? 
-Can you provide the command-line? The reviewers should be able to reproduce our experiments.}
 We outline the runtimes required to synthesise a stable controller for each
-benchmark in Table~\ref{tab:results}. \textcolor{red}{Which section do you refer??
-For most benchmarks the conjecture explained in section~\ref{fixedpoint_verification} 
-holds and the inductive back-end is able to find a stable solution in less than one minute}. 
-This is possible if the inductive solutions need to be refined with few counterexamples 
-and fixed point precision increases. However, some of our benchmarks did not meet these criteria. 
-\textcolor{red}{Which cases? Can you refer to Table~\ref{tab:results} In these cases, 
-the interval arithmetic back-end is able to complement the inductive approach
-and synthesise a solution instead, albeit with significantly larger runtimes}.
-
-\textcolor{red}{Can you relate the benchmarks in Table~\ref{tab:results} in terms of 
-$C$ and $G$ as described in section~\ref{experimental-setup}. You could add an additional column to that table.}
+benchmark in Table~\ref{tab:results}. For most benchmarks the conjecture explained
+in section~\ref{fixedpoint_verification} holds and the inductive back-end is able
+to find a stable solution in less than one minute. This is possible if the inductive
+solutions need to be refined with few counterexamples and fixed point precision
+increases. However, some of our benchmarks did not meet these criteria. In these
+cases the interval arithmetic back-end was able to complement the inductive approach
+and synthesise a solution instead, albeit with significantly larger runtimes.
 
@@
 
-\caption{Experimental results. \textcolor{red}{It should be a table and not a figure.} \label{tab:results}}
+\caption{Experimental results. \label{tab:results}}
 \end{figure}
@@
 
-\textcolor{red}{Can you provide the synthesised controllers? Iury could then check the solution using the bode diagram.}
 We conclude from these results that the inductive back-end provides excellent performance
-for synthesising stable controllers in the majority of the benchmarks \textcolor{red}{can you be more specific? which benchmarks?}, and can be
-complemented using the interval arithmetic back-end, where the inductive conjectures fail
+for synthesising stable controllers in the majority of the benchmarks, and can be
+complemented using the interval arithmetic back-end where the inductive conjectures fail
 too frequently. Both back-ends enabled controller synthesis for all benchmarks within
@@
 
-In this study, we have investigated a CEGIS-based approach that uses inductive synthesis 
-in conjunction with a robust closed-loop stability verification algorithm to find a parametric 
-solution for a digital controller given a continuous (or discrete) plant specification.
-In particular, we have exploited the automatic synthesis of correct-by-construction 
-digital controllers along with a model of their physical environment.
-We have also modeled a digital equivalent of the physical plant by evaluating the 
-effects of the quantisers (A/D and D/A converters) as time discretisation elements 
-with quantisation noise. Experimental results show that the inductive back-end of our
-CEGIS-based approach is able to synthesise stable controllers in most benchmarks and can be 
-complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
-Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
-Further studies include the extension of this CEGIS-based approach for different classes of systems
-({\it e.g.}, state-space) and also consider performance requirements while synthesising 
-the digital controller.
-
 \bibliographystyle{abbrv}

### 2016-10-13 paper/paper.tex
integration of the section on the use of fixed point computation into the prog synthesis section

--- 2016-10-13 paper/paper.tex
@@
 \begin{equation}
-\Delta{\vec{p}}=\begin{bmatrix}
+\Delta{p}=\begin{bmatrix}
 \hat{b_{0}} - b_{0}\\
@@
 
-\paragraph{The {\sc Synthesise} and {\sc Verify} phases}
-The {\sc synthesise} phase uses a BMC-based verifier to 
-compute a solution ($N_c$,$D_C$). An important remark is that this 
-controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
-domain.
-A second remark is that the synthesis and verification engines use fixed/floating point arithmetic,
-therefore we also need to examine the effect of discretization during these operations.
-\cdsay{integrate the following with Dario}
+\paragraph{Use of Fixed Point Computation in the Synthesis and Verification Engines}
+The program synthesis engine uses fixed-point arithmetic,
+therefore we need to examine the effect of discretization during these operations.
 Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
@@
 %
-However, given a real plant and real controller $\hat{G}(z), \hat{C}(z)$, and a discretizing function
+However, given a real plant $\hat{G}(z)$, and a discretizing function
 \begin{align}
@@
 \end{align}
-we calculate $\tilde C(z)=f(\hat{C}(z))$ and $\tilde G(z)=f(\hat{G}(z))$
+we calculate $\tilde G(z)=f(\hat{G}(z))$
 \begin{align}
-\label{digital_controller_tf}
-\tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
-&= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
+% \label{digital_controller_tf}
+% \tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
+% &= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
 \label{digital_plant_tf}
-\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_q \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_q \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_q \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_q \hat{a}_{N_G})z^{-N_G}} \nonumber \\
+\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_b \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_b \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_b \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_b \hat{a}_{N_G})z^{-N_G}} \nonumber \\
 &=G(z)+\Delta{G}_P(z)+\Delta{G}_b(z).
@@
 
-Two approaches have been taken to synthesise a stable controller based on this model.
-The first uses interval arithmetic, representing the coefficients $[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\ {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
-and rounding operations outwards during the process. This results in a tighter calculation of the error at the cost of performance.
-
-The second approach uses a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is assumed to be within the expected bounds and verified after synthesis using the interval version of the program.
-The first verification phase produces a counterexample if some instance of $\mathfrak{G}(z)$ does not verify the properties and the CEGIS loop iteratively looks for a new controller that verifies the supplied counterexamples.
-The second phase verifies the propagation of the error in the fixed point calculations.
-If the second phase fails verification, we increase the precision of the analyser and feed the CEGIS loop again to find a sound solution.
-The resulting increase in speed of this approach over the former, which is of several orders of magnitude, vouches for the use of CEGIS in most of our benchmarks.
-\cdsay{end of integration}
-
-In the {\sc verify} phase, we have a two-step process. 
+\paragraph{The {\sc Synthesise} and {\sc Verify} phases}
+The {\sc synthesise} phase uses BMC to 
+compute a solution ($N_c$,$D_C$). % An important remark is that this 
+% controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
+% domain.
+
+There are two approaches for the {\sc verify} phase based on the
+described model.  The first uses interval arithmetic, representing the
+coefficients
+$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\
+{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$
+and rounding operations outwards during the process. 
+% This results in a
+% tighter calculation of the error at the cost of
+% performance.
+Synthesised controllers using this verifier will always
+be correct and only generate counterexamples when the precision of the
+engine is insuficient.  Given the high computational cost of this
+approach, we also designed a second approach, which we describe below.
+In our experimental section Sec.~\ref{sec:experiments}, we 
+show that the increase in speed of the second approach 
+over the first one is in most cases of several orders of magnitude.
+
+In Fig.~\ref{fig:CEGIS}, we illustrate the second approach, which 
+uses a two-stage verification. 
 First, in the {\sc Uncertainty} sub-phase, assuming the 
@@
 which checks the propagation of the error in the fixed-point 
-calculations. If this check returns $false$, then we 
+calculations using a Fixed-point Arithmetic Verifier based on 
+interval arithmetic. 
+%
+% To achieve this, we use a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is assumed to be within the expected bounds and verified after synthesis using the interval version of the program.
+%
+% The first verification phase produces a counterexample if some instance of $\mathfrak{G}(z)$ does not verify the properties and the CEGIS loop iteratively looks for a new controller that verifies the supplied counterexamples.
+The second phase verifies the propagation of the error in the fixed point calculations.
+% If the second phase fails verification, we increase the precision of the analyser and feed the CEGIS loop again to find a sound solution. 
+% vouches for the use of CEGIS in most of our benchmarks.
+% \cdsay{end of integration}
+
+If this check returns $false$, then we 
 increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise} phase
@@
 Thus,  in the first {\sc verify} phase a counterexample is presented, that is added to {\sc inputs}, whis is usede in the first  {\sc synthesise} phase.
-The resulting controller is:
-}
-$$
-{
-\blue{
-C(z)=\frac{0.77516z^2{+}-0.71497z{+}0.03729}{0.25024z^2{-}0.01799z{+}0.00097}
-}}
-$$
-
-\blue{In the second {\sc verify} phase, the controller failed to stabilize the system for all the range of uncertainties, another counterexample was provided, and the following candidate controller is presented in another {\sc synthesise} phase:}
-$$
-{
-\blue{
-C(z)=\frac{0.68970z^2{+}0.36538z{+}0.30637}{0.06862z^2{+}0.00394z{+}0.00802}
-}}
-$$
-
-\blue{
-This candidate solution is validated as the final solution by the next 
-{\sc verify} phase.
+The resulting controller is
 }
@@
 }
- \caption{Counterexample-Guided Inductive Synthesis of Closed-loop System (CEGIS paradigm). \label{fig:CEGIS}}
+ \caption{Counterexample-Guided Inductive Synthesis of Closed-loop System (CEGIS paradigm). 
+\label{fig:CEGIS}}
 \end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Experimental Evaluation}
+\section{Experimental Evaluation} \label{sec:experiments}
 
@@
 
-\textcolor{red}{Can you relate the benchmarks in Table~\ref{tab:results} in terms of 
-$C$ and $G$ as described in section~\ref{experimental-setup}. You could add an additional column to that table.}
-
 \begin{figure}[H]

### 2016-10-13 paper/paper.tex

@@
 Thus,  in the first {\sc verify} phase a counterexample is presented, that is added to {\sc inputs}, whis is usede in the first  {\sc synthesise} phase.
-The resulting controller is
+The resulting controller is:
+}
+$$
+{
+\blue{
+C(z)=\frac{0.77516z^2{+}-0.71497z{+}0.03729}{0.25024z^2{-}0.01799z{+}0.00097}
+}}
+$$
+
+\blue{In the second {\sc verify} phase, the controller failed to stabilize the system for all the range of uncertainties, another counterexample was provided, and the following candidate controller is presented in another {\sc synthesise} phase:}
+$$
+{
+\blue{
+C(z)=\frac{0.68970z^2{+}0.36538z{+}0.30637}{0.06862z^2{+}0.00394z{+}0.00802}
+}}
+$$
+
+\blue{
+This candidate solution is validated as the final solution by the next 
+{\sc verify} phase.
 }
@@
 This is possible if the inductive solutions need to be refined with few counterexamples 
-and fixed point precision increases. However, some of our benchmarks did not meet these criteria. 
-\textcolor{red}{Which cases? Can you refer to Table~\ref{tab:results} In these cases, 
+and fixed point precision increases. However, two benchmarks in our set did not meet these
+criteria (marked with $^*$ in Table~\ref{tab:results}). In these cases, 
 the interval arithmetic back-end is able to complement the inductive approach
-and synthesise a solution instead, albeit with significantly larger runtimes}.
-
-\begin{figure}[H]
+and synthesise a solution instead, albeit with significantly larger runtimes.
+
+\textcolor{red}{Can you relate the benchmarks in Table~\ref{tab:results} in terms of 
+$C$ and $G$ as described in section~\ref{experimental-setup}. You could add an additional column to that table.}
+
+\begin{table}[H]
 \centering
-\begin{tabular}{l | r r l}
-Benchmark              & Base     & Unc     & \\\cline{1-4}
-CruiseControl02        & 17\,s    & 46\,s   & \\
-SatelliteB2            & 7\,s     & 6601\,s & \tbmark\\
-SatelliteC2            & 2\,s     & 76\,s   & \tbmark\\
-SpringMassDamper       & 28\,s    & \xmark  &
+\begin{tabular}{l | r l}
+Benchmark                 & Base    & \\\cline{1-2}
+CruiseControl02           & 17\,s   & \\
+CruiseControl02$^\dagger$ & 46\,s   & \\
+SatelliteB2               & 7\,s    & \\
+SatelliteB2$^\dagger$     & 6601\,s & \tbmark\\
+SatelliteC2               & 2\,s    & \\
+SatelliteC2$^\dagger$     & 76\,s   & \tbmark\\
+SpringMassDamper          & 28\,s   & \\
+a\_PL1\_SCH2\_IMPL1       & 2704\,s & \\
+a\_PL1\_SCH2\_IMPL2       & 538\,s  & \\
+a\_PL1\_SCH2\_IMPL3       & 12\,s   & \\
+a\_PL1\_SCH3\_IMPL1       & 318\,s  & \\
+a\_PL1\_SCH3\_IMPL2       & 967\,s  & \\
+a\_PL1\_SCH3\_IMPL3       & 9798\,s & \\
+a\_PL1\_SCH4\_IMPL1       & 6304\,s & \\
 \end{tabular}
@@
 \vspace{0.5em}
-\scriptsize{* = solved with interval back-end, \xmark = uncontrollable}
+\scriptsize{* = solved with interval back-end, $\dagger$ = with uncertainty}
 \vspace{0.5em}
@@
 \caption{Experimental results. \label{tab:results}}
-\end{figure}
+\end{table}
 %---------------------------------

### 2016-10-13 paper/paper.tex
lower case in paragraph name

@@
 
-\paragraph{Use of Fixed Point Computation in the Synthesis and Verification Engines}
+\paragraph{Use of fixed-point computation in the program synthesis engine}
 The program synthesis engine uses fixed-point arithmetic,

### 2016-10-13 paper/paper.tex
Addressed all TODOs in experimental section.

@@
 \subsection{Synthesis elements specific to control systems}
+\label{synthesis-elements}
 
@@
 
-\textcolor{red}{How did you obtain the results from Table~\ref{tab:results}? 
-Can you provide the command-line? The reviewers should be able to reproduce our experiments.}
 We outline the runtimes required to synthesise a stable controller for each
-benchmark in Table~\ref{tab:results}. \textcolor{red}{Which section do you refer??
-For most benchmarks the conjecture explained in section~\ref{fixedpoint_verification} 
-holds and the inductive back-end is able to find a stable solution in less than one minute}. 
-This is possible if the inductive solutions need to be refined with few counterexamples 
-and fixed point precision increases. However, two benchmarks in our set did not meet these
-criteria (marked with $^*$ in Table~\ref{tab:results}). In these cases, 
+benchmark in Table~\ref{tab:results}. For the majority of our benchmarks the conjecture explained
+in section~\ref{synthesis-elements}  holds and the inductive back-end is able to find a stable
+solution in less than one minute.  This is possible if the inductive solutions need to be refined
+with few counterexamples  and fixed point precision increases. However, two benchmarks in our set
+did not meet these criteria (marked with $^*$ in Table~\ref{tab:results}). In these cases, 
 the interval arithmetic back-end is able to complement the inductive approach
@@
 
-\textcolor{red}{Can you relate the benchmarks in Table~\ref{tab:results} in terms of 
-$C$ and $G$ as described in section~\ref{experimental-setup}. You could add an additional column to that table.}
-
 \begin{table}[H]
 \centering
-\begin{tabular}{l | r l}
-Benchmark                 & Base    & \\\cline{1-2}
-CruiseControl02           & 17\,s   & \\
-CruiseControl02$^\dagger$ & 46\,s   & \\
-SatelliteB2               & 7\,s    & \\
-SatelliteB2$^\dagger$     & 6601\,s & \tbmark\\
-SatelliteC2               & 2\,s    & \\
-SatelliteC2$^\dagger$     & 76\,s   & \tbmark\\
-SpringMassDamper          & 28\,s   & \\
-a\_PL1\_SCH2\_IMPL1       & 2704\,s & \\
-a\_PL1\_SCH2\_IMPL2       & 538\,s  & \\
-a\_PL1\_SCH2\_IMPL3       & 12\,s   & \\
-a\_PL1\_SCH3\_IMPL1       & 318\,s  & \\
-a\_PL1\_SCH3\_IMPL2       & 967\,s  & \\
-a\_PL1\_SCH3\_IMPL3       & 9798\,s & \\
-a\_PL1\_SCH4\_IMPL1       & 6304\,s & \\
+\begin{tabular}{c l | r l}
+      & Benchmark                  & Base    & \\\cline{1-2}
+$G_1$ & CruiseControl02            & 17\,s   & \\
+$G_1$ & CruiseControl02$^\dagger$  & 46\,s   & \\
+$G_2$ & SpringMassDamper           & 28\,s   & \\
+$G_2$ & SpringMassDamper$^\dagger$ & \xmark  & \\
+$G_2$ & SatelliteB2                & 7\,s    & \\
+$G_2$ & SatelliteB2$^\dagger$      & 6601\,s & \tbmark\\
+$G_2$ & SatelliteC2                & 2\,s    & \\
+$G_2$ & SatelliteC2$^\dagger$      & 76\,s   & \tbmark\\
+      & a\_PL1\_SCH2\_IMPL1        & 2704\,s & \\
+      & a\_PL1\_SCH2\_IMPL2        & 538\,s  & \\
+      & a\_PL1\_SCH2\_IMPL3        & 12\,s   & \\
+      & a\_PL1\_SCH3\_IMPL1        & 318\,s  & \\
+      & a\_PL1\_SCH3\_IMPL2        & 967\,s  & \\
+      & a\_PL1\_SCH3\_IMPL3        & 9798\,s & \\
+      & a\_PL1\_SCH4\_IMPL1        & 6304\,s & \\
 \end{tabular}
@@
 \end{table}
+\pksay{TODO: @Lucas: Please complete $G_x$ in table.}
 %---------------------------------
 
-\textcolor{red}{Can you provide the synthesised controllers? Iury could then check the solution using the bode diagram.}
 We conclude from these results that the inductive back-end provides excellent performance
-for synthesising stable controllers in the 12 out of 14 benchmarks, and can be
-complemented using the interval arithmetic back-end for the remaining 2 benchmarks,
+for synthesising stable controllers in the 12 out of 15 benchmarks, and can be
+complemented using the interval arithmetic back-end for 2 additional benchmarks,
 where the inductive conjectures fail too frequently. Both back-ends together enabled controller
-synthesis for all benchmarks within reasonable time frames.
+synthesis for 14 out of 15 benchmarks within reasonable time frames. \pksay{TODO: Upload full
+experiments environment including README and result log files to anonymous Google Drive and
+provide link here.}
 

### 2016-10-13 paper/paper.tex
+ comment on the domains of controller/uncertainty
Updated running example in CEGIS.

@@
 $(\Delta N_G, \Delta D_G)$ represents $x$. 
-
-%% \red{[clear elucidation of the mapping between this and the domains used 
-%% in the general description of the synthesiser]}
+We compute the controller $(N_c,D_c)$ in the domain 
+$\mathbb{R}\langle I,F \rangle$ and 
+the uncertainty in $\mathbb{R}\langle I_b,F_b \rangle$.
+
+% \red{[clear elucidation of the mapping between this and the domains used 
+% in the general description of the synthesiser]}
 
@@
 %
-We stay in the {\sc verify} phase and receive a new counterexample at
-higher precision:
-\cdsay{Pascal, this sounds confusing. if you want to increase precision on-the-fly, i.e. 
-not going back to the synthesise phase, 
-then this illustration doesn't follow the general diagram in Fig.5. 
-We need to decide which direction we keep.}
+Since previous counterexamples were attained at lower precision, we 
+remove them from the counterexample set. Back in the {\sc synthesise}
+phase, we thus retrieve a candidate solution with all coefficients 0.
+The {\sc verify} phase now provides the first counterexample at higher
+precision:
 %
@@
 %\blue{[Nice, now I'm in the groove. Next unfolds well.] }
-Since previous counterexamples were attained at lower precision, we 
-remove them from the counterexample set. In the next {\sc synthesise}
-phase, we get a new candidate solution that holds for the newly
-inserted counterexample:
+In the next {\sc synthesise} phase, we get a new candidate solution that holds for
+the new, higher precision counterexample:
 

### 2016-10-13 paper/paper.tex
update Figure 3

--- 2016-10-13 paper/paper.tex
@@
 \centering
-\includegraphics[width=\textwidth]{figures/verification-flow.pdf}
+\includegraphics[width=\textwidth]{figures/verification-flow.png}
+\vspace{1ex}
 \caption{DSVerifier Verification Flow.}
@@
 the function $f$ (cf.~Eq.~\eqref{FWL_tf}).
+
+\textcolor{red}{Pascal: can you please update this section to include the CEGIS step?}
 
@@
 
-\paragraph{Use of fixed-point computation in the program synthesis engine}
-The program synthesis engine uses fixed-point arithmetic,
-therefore we need to examine the effect of discretization during these operations.
+\paragraph{The {\sc Synthesise} and {\sc Verify} phases}
+The {\sc synthesise} phase uses a BMC-based verifier to 
+compute a solution ($N_c$,$D_C$). An important remark is that this 
+controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
+domain.
+A second remark is that the synthesis and verification engines use fixed/floating point arithmetic,
+therefore we also need to examine the effect of discretization during these operations.
+\cdsay{integrate the following with Dario}
 Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
@@
 %
-However, given a real plant $\hat{G}(z)$, and a discretizing function
+However, given a real plant and real controller $\hat{G}(z), \hat{C}(z)$, and a discretizing function
 \begin{align}
@@
 \end{align}
-we calculate $\tilde G(z)=f(\hat{G}(z))$
+we calculate $\tilde C(z)=f(\hat{C}(z))$ and $\tilde G(z)=f(\hat{G}(z))$
 \begin{align}
-% \label{digital_controller_tf}
-% \tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
-% &= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
+\label{digital_controller_tf}
+\tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
+&= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
 \label{digital_plant_tf}
-\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_b \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_b \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_b \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_b \hat{a}_{N_G})z^{-N_G}} \nonumber \\
+\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_q \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_q \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_q \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_q \hat{a}_{N_G})z^{-N_G}} \nonumber \\
 &=G(z)+\Delta{G}_P(z)+\Delta{G}_b(z).
@@
 
-\paragraph{The {\sc Synthesise} and {\sc Verify} phases}
-The {\sc synthesise} phase uses BMC to 
-compute a solution ($N_c$,$D_C$). % An important remark is that this 
-% controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
-% domain.
-
-There are two approaches for the {\sc verify} phase based on the
-described model.  The first uses interval arithmetic, representing the
-coefficients
-$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\
-{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$
-and rounding operations outwards during the process. 
-% This results in a
-% tighter calculation of the error at the cost of
-% performance.
-Synthesised controllers using this verifier will always
-be correct and only generate counterexamples when the precision of the
-engine is insuficient.  Given the high computational cost of this
-approach, we also designed a second approach, which we describe below.
-In our experimental section Sec.~\ref{sec:experiments}, we 
-show that the increase in speed of the second approach 
-over the first one is in most cases of several orders of magnitude.
-
-In Fig.~\ref{fig:CEGIS}, we illustrate the second approach, which 
-uses a two-stage verification. 
+Two approaches have been taken to synthesise a stable controller based on this model.
+The first uses interval arithmetic, representing the coefficients $[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\ {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
+and rounding operations outwards during the process. This results in a tighter calculation of the error at the cost of performance.
+
+The second approach uses a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is assumed to be within the expected bounds and verified after synthesis using the interval version of the program.
+The first verification phase produces a counterexample if some instance of $\mathfrak{G}(z)$ does not verify the properties and the CEGIS loop iteratively looks for a new controller that verifies the supplied counterexamples.
+The second phase verifies the propagation of the error in the fixed point calculations.
+If the second phase fails verification, we increase the precision of the analyser and feed the CEGIS loop again to find a sound solution.
+The resulting increase in speed of this approach over the former, which is of several orders of magnitude, vouches for the use of CEGIS in most of our benchmarks.
+\cdsay{end of integration}
+
+In the {\sc verify} phase, we have a two-step process. 
 First, in the {\sc Uncertainty} sub-phase, assuming the 
@@
 which checks the propagation of the error in the fixed-point 
-calculations using a Fixed-point Arithmetic Verifier based on 
-interval arithmetic. 
-%
-% To achieve this, we use a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is assumed to be within the expected bounds and verified after synthesis using the interval version of the program.
-%
-% The first verification phase produces a counterexample if some instance of $\mathfrak{G}(z)$ does not verify the properties and the CEGIS loop iteratively looks for a new controller that verifies the supplied counterexamples.
-The second phase verifies the propagation of the error in the fixed point calculations.
-% If the second phase fails verification, we increase the precision of the analyser and feed the CEGIS loop again to find a sound solution. 
-% vouches for the use of CEGIS in most of our benchmarks.
-% \cdsay{end of integration}
-
-If this check returns $false$, then we 
+calculations. If this check returns $false$, then we 
 increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise} phase
@@
 }
- \caption{Counterexample-Guided Inductive Synthesis of Closed-loop System (CEGIS paradigm). 
-\label{fig:CEGIS}}
+ \caption{Counterexample-Guided Inductive Synthesis of Closed-loop System (CEGIS paradigm). \label{fig:CEGIS}}
 \end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Experimental Evaluation} \label{sec:experiments}
+\section{Experimental Evaluation}
 

### 2016-10-13 paper/paper.tex
removed duplicated paragraph + todo
Fixed cline in experiments table.

--- 2016-10-13 paper/paper.tex
@@
 
-Let $\hat{C}(z)$ be the transfer function of the digital controller represented using this FWL with integer size $I$ and fractional
-size $F$.  We shall denote the FWL domain of coefficients as $\mathbb{R}\langle I,F \rangle$
+Let $\hat{C}(z)$ be the transfer function of the digital controller represented using this FWL with integer size $I$ and fractional size $F$.
+We shall denote the FWL domain of coefficients as $\mathbb{R}\langle I,F \rangle$
 %Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
@@
 
-Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
-using Fixed-Point bit vectors with integer size $I_b$ and fractional
-size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
-%
-\begin{align}
-\small
-\label{digital_controller_plant_tf}
-\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
-%\label{plant_tf}
-\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
-\end{align}
-
-Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
-domain,
-%
- $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
-
-Two approaches have been taken to synthesise a stable controller based on this model.
-The first uses interval arithmetic, representing the coefficients $[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\ {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$  
-and rounding operations outwards during the process. This results in a tighter calculation of the error at the cost of performance.
+% Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
+% using Fixed-Point bit vectors with integer size $I_b$ and fractional
+% size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
+% %
+% \begin{align}
+% \small
+% \label{digital_controller_plant_tf}
+% \tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
+% %\label{plant_tf}
+% \tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
+% \end{align}
+
+% Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
+% domain,
+% %
+%  $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
+
+% Two approaches have been taken to synthesise a stable controller based on this model.
+% The first uses interval arithmetic, representing the coefficients $[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\ {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$
+
+% \cdsay{Dario, what coefficients are these?}
+
+% and rounding operations outwards during the process. This results in a tighter calculation of the error at the cost of performance.
 
@@
 and rounding operations outwards during the process. 
+\cdsay{dario, what coefficients are these?}
 % This results in a
@@
 $$
-\blue{
 C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}
-}
 $$
@@
 \begin{tabular}{c l | r l}
-      & Benchmark                  & Base    & \\\cline{1-2}
+Plant & Benchmark                  & Time    & \\\cline{1-3}
 $G_1$ & CruiseControl02            & 17\,s   & \\

### 2016-10-13 paper/paper.tex
fix Satellite plant

--- 2016-10-13 paper/paper.tex
@@
 \begin{tabular}{c l | r l}
-      & Benchmark                  & Base    & \\\cline{1-2}
+Plant & Benchmark                  & Base    & \\\cline{1-2}
 $G_1$ & CruiseControl02            & 17\,s   & \\
@@
 $G_2$ & SpringMassDamper$^\dagger$ & \xmark  & \\
-$G_2$ & SatelliteB2                & 7\,s    & \\
-$G_2$ & SatelliteB2$^\dagger$      & 6601\,s & \tbmark\\
-$G_2$ & SatelliteC2                & 2\,s    & \\
-$G_2$ & SatelliteC2$^\dagger$      & 76\,s   & \tbmark\\
+$G_3$ & SatelliteB2                & 7\,s    & \\
+$G_3$ & SatelliteB2$^\dagger$      & 6601\,s & \tbmark\\
+$G_3$ & SatelliteC2                & 2\,s    & \\
+$G_3$ & SatelliteC2$^\dagger$      & 76\,s   & \tbmark\\
       & a\_PL1\_SCH2\_IMPL1        & 2704\,s & \\

### 2016-10-13 paper/paper.tex
include plant G_4

@@
 
-The discrete controllers $C_{4}$ and $C_{5}$ for the satellite plant $G_{3}$,discretized with sample time equal to $1 s$ and $2 s$ respectively, 
+The discrete controllers $C_{4}$ and $C_{5}$ for the satellite plant $G_{3}$, discretized with sample time $1s$ and $2s$ respectively, 
 are represented by the following z-expression:
@@
 \centering
-\begin{tabular}{c l | r l}
+\begin{tabular}{c | l | r l}
 Plant & Benchmark                  & Time    & \\\cline{1-3}
@@
 $G_3$ & SatelliteC2$^\dagger$      & 76\,s   & \tbmark\\
-      & a\_PL1\_SCH2\_IMPL1        & 2704\,s & \\
-      & a\_PL1\_SCH2\_IMPL2        & 538\,s  & \\
-      & a\_PL1\_SCH2\_IMPL3        & 12\,s   & \\
-      & a\_PL1\_SCH3\_IMPL1        & 318\,s  & \\
-      & a\_PL1\_SCH3\_IMPL2        & 967\,s  & \\
-      & a\_PL1\_SCH3\_IMPL3        & 9798\,s & \\
-      & a\_PL1\_SCH4\_IMPL1        & 6304\,s & \\
+$G_4$ & a\_PL1\_SCH2\_IMPL1        & 2704\,s & \\
+$G_4$ & a\_PL1\_SCH2\_IMPL2        & 538\,s  & \\
+$G_4$ & a\_PL1\_SCH2\_IMPL3        & 12\,s   & \\
+$G_4$ & a\_PL1\_SCH3\_IMPL1        & 318\,s  & \\
+$G_4$ & a\_PL1\_SCH3\_IMPL2        & 967\,s  & \\
+$G_4$ & a\_PL1\_SCH3\_IMPL3        & 9798\,s & \\
+$G_4$ & a\_PL1\_SCH4\_IMPL1        & 6304\,s & \\
 \end{tabular}

### 2016-10-13 paper/paper.tex
revised sec 4.1

--- 2016-10-13 paper/paper.tex
@@
 We pass this candidate solution to {\sc verify}, which 
-checks whether it is a full solution.
+checks whether it is a full solution ({\it i.e.}, $\vec{P}$
+satisfies the specification $\sigma(\vec{x}, \vec{P})$ for all
+$\vec{x}\in\mathcal{D}$).
 %determines whether
@@
 %% full solution.
-If this is the case, then
-the algorithm terminates.
+If this is the case, then the algorithm terminates.
 Otherwise, additional information is provided to the {\sc synthesise}
-phase (e.g. a new counterexample that is added to the {\sc inputs} set)
-and the loop iterates again.
+phase in the form of a new counterexample that is added to the {\sc inputs} set
+and the loop iterates again (note that, for now, we ignore the 
+second feedback signal ``Increase Precision'' provided by the {\sc Verify}
+phase in Fig.~\ref{fig:CEGIS} as it is specific to control synthesis and will 
+be described in the next section).
 
@@
 
-%% It is
-%% worth noting that each iteration of the loop adds a new input to the
-%% finite set $\text{\sc inputs}$ being used for synthesis.  Given that
-%% the full set of inputs $\mathcal{D}$
-%% %\blue{[which by now should have a name, as suggested to be introduced above]} 
-%% is finite, this means that the refinement loop
-%% can only iterate a finite number of times.
+It is
+worth noting that each iteration of the loop adds a new input to the
+finite set $\text{\sc inputs}$ being used for synthesis.  Given that
+the full set of inputs $\mathcal{D}$
+%\blue{[which by now should have a name, as suggested to be introduced above]} 
+is finite, this means that the refinement loop
+can only iterate a finite number of times.
 
@@
 \begin{tabular}{c l | r l}
-Plant & Benchmark                  & Time    & \\\cline{1-3}
+      & Benchmark                  & Base    & \\\cline{1-2}
 $G_1$ & CruiseControl02            & 17\,s   & \\
@@
 $G_2$ & SpringMassDamper$^\dagger$ & \xmark  & \\
-$G_3$ & SatelliteB2                & 7\,s    & \\
-$G_3$ & SatelliteB2$^\dagger$      & 6601\,s & \tbmark\\
-$G_3$ & SatelliteC2                & 2\,s    & \\
-$G_3$ & SatelliteC2$^\dagger$      & 76\,s   & \tbmark\\
+$G_2$ & SatelliteB2                & 7\,s    & \\
+$G_2$ & SatelliteB2$^\dagger$      & 6601\,s & \tbmark\\
+$G_2$ & SatelliteC2                & 2\,s    & \\
+$G_2$ & SatelliteC2$^\dagger$      & 76\,s   & \tbmark\\
       & a\_PL1\_SCH2\_IMPL1        & 2704\,s & \\

### 2016-10-13 paper/paper.tex
add description of G4

--- 2016-10-13 paper/paper.tex
@@
 
+The fourth (and last) set of benchmarks considers the following description for the plant 
+$G_{4}(s)$ extracted from Keel and Bhattacharyya~\cite{bhattacharyya97,keel_Bhattacharyya_examples}.
+%
+\begin{equation}
+\label{exampleA}
+G_{4}(s)=\frac{s-1}{s^{2}-s-2}
+\end{equation}
+%
+\noindent where $G_{4}(z)$ is obtained using the ZOH discretisation defined 
+in Eq.~\eqref{eq:pulsetf} with $3$ different sample times ($0.1$, $0.05$, and $0.03$ 
+seconds); and the controllers are synthesised using $4$, $8$, and $12$-bits.
+
 All experiments were conducted on an otherwise idle Intel Core i$7$-$4790$ 

### 2016-10-13 paper/paper.tex
remove the description of the controllers

--- 2016-10-13 paper/paper.tex
@@
 
-Two proportional-integral (PI) controllers are designed by Wang {\it et al.} 
-for the cruise control plant $G(z)$~\cite{DBLP:conf/hybrid/WangGRJF16}, 
-which has the following mathematical model
-%
-\begin{equation}
-\label{cruise-control-g1}
-C_{1}(z)=\frac{1.51z-1.3586}{z-1}, \nonumber
-\end{equation} 
-%
-\begin{equation}
-\label{cruise-control-g2}
-C_{2}(z)=\frac{2.72z^2 - 4.153z + 1.896}{1.0z^2 - 1.844z + 0.8496}. \nonumber
-\end{equation}
+%Two proportional-integral (PI) controllers are designed by Wang {\it et al.} 
+%for the cruise control plant $G(z)$~\cite{DBLP:conf/hybrid/WangGRJF16}, 
+%which has the following mathematical model
+%
+%\begin{equation}
+%\label{cruise-control-g1}
+%C_{1}(z)=\frac{1.51z-1.3586}{z-1}, \nonumber
+%\end{equation} 
+%
+%\begin{equation}
+%\label{cruise-control-g2}
+%C_{2}(z)=\frac{2.72z^2 - 4.153z + 1.896}{1.0z^2 - 1.844z + 0.8496}. \nonumber
+%\end{equation}
 
 The second set of benchmarks considers a simple spring-mass 
-damper~\cite{DBLP:conf/hybrid/WangGRJF16}, where both discrete 
-plant dynamics and controller are represented by the following 
-z-expression, resp.
+damper~\cite{DBLP:conf/hybrid/WangGRJF16}, where the discrete 
+plant dynamics is represented by the following z-expression
+%
+%where both discrete 
+%plant dynamics and controller are represented by the following 
+%z-expression, resp.
 %
@@
 \label{spring-mass-damper-g}
-G_2(z)=\frac{5\times{10^{-5}}z + 5\times{10^{-5}}}{z^2 - 2z + 1.0001}, \nonumber
-\end{equation} 
-%
-\begin{equation}
-\label{spring-mass-damper-c}
-C_3(z)=\frac{1.28\times{10^{3}}z^2 - 1.354240\times{10^{3}}z + 0.074879\times{10^{3}}}{z^2 - 1.4990z + 0.4995}. \nonumber
-\end{equation}
-
-A third set of benchmarks that consists of digital controllers for satellite
+G_2(z)=\frac{5\times{10^{-5}}z + 5\times{10^{-5}}}{z^2 - 2z + 1.0001}. \nonumber
+\end{equation} 
+%
+%\begin{equation}
+%\label{spring-mass-damper-c}
+%C_3(z)=\frac{1.28\times{10^{3}}z^2 - 1.354240\times{10^{3}}z + 0.074879\times{10^{3}}}{z^2 - 1.4990z + 0.4995}. \nonumber
+%\end{equation}
+
+A third set of benchmarks that consists of a physical plant for satellite
 applications is considered~\cite{Franklin15}, in order to evaluate the
@@
 considered.  The motion equation for the one-axis system, despising
-disturbance torques, is given by:
+disturbance torques, is given by
 %
@@
 Normalizing Eq.~\eqref{eq:satelliteode} by defining the control signal $u=\frac{\tau_{C}}{I}$ and 
-taking Laplace transform, the following $s$-domain transfer function $G(s)$ is obtained:
+taking Laplace transform, the following $s$-domain transfer function $G(s)$ is obtained
 %
@@
 \noindent using the ZOH discretisation defined in Eq.~\eqref{eq:pulsetf}, 
-the following $z$-domain model is obtained:
+the following $z$-domain model is obtained
+%
 \begin{equation}
@@
 
-The discrete controllers $C_{4}$ and $C_{5}$ for the satellite plant $G_{3}$, discretized with sample time $1s$ and $2s$ respectively, 
-are represented by the following z-expression:
-%
-\begin{equation}
-\label{satellite-b2}
-C_{4}(z)=\frac{2.88z^2 - 4.896z + 2.074}{1.0z^2 - 0.42z - 0.3465 - 0.03915}. \nonumber
-\end{equation} 
-%
-\begin{equation}
-\label{satellite-c2}
-C_{5}(z)=\frac{0.43z^2 - 0.2408z - 0.1316}{1.0z^2 + 1.5z + 0.97 + 0.183}. \nonumber
-\end{equation}
-
+%The discrete controllers $C_{4}$ and $C_{5}$ for the satellite plant $G_{3}$, discretized with sample time $1s$ and $2s$ respectively, 
+%are represented by the following z-expression:
+%
+%\begin{equation}
+%\label{satellite-b2}
+%C_{4}(z)=\frac{2.88z^2 - 4.896z + 2.074}{1.0z^2 - 0.42z - 0.3465 - 0.03915}. \nonumber
+%\end{equation} 
+%
+%\begin{equation}
+%\label{satellite-c2}
+%C_{5}(z)=\frac{0.43z^2 - 0.2408z - 0.1316}{1.0z^2 + 1.5z + 0.97 + 0.183}. \nonumber
+%\end{equation}
+
+The fourth (and last) set of benchmarks considers the following description for the plant 
+$G_{4}(s)$, which is typically used for evaluating stability margins~\cite{bhattacharyya97,keel_Bhattacharyya_examples}
+%
+\begin{equation}
+\label{exampleA}
+G_{4}(s)=\frac{s-1}{s^{2}-s-2}
+\end{equation}
+%
+\noindent where $G_{4}(z)$ is obtained using the ZOH discretisation defined 
+in Eq.~\eqref{eq:pulsetf} with $3$ different sample times ($0.1$, $0.05$, and $0.03$ 
+seconds).
+
+\textcolor{red}{Pascal: Can you please check whether this configuration is correct?}
 All experiments were conducted on an otherwise idle Intel Core i$7$-$4790$ 
@@
 \end{table}
-\pksay{TODO: @Lucas: Please complete $G_x$ in table.}
 %---------------------------------

### 2016-10-13 paper/paper.tex
add comments
review results

@@
 \label{experimental-results}
+%---------------------------------
 
@@
 solution in less than one minute.  This is possible if the inductive solutions need to be refined
-with few counterexamples  and fixed point precision increases. However, two benchmarks in our set
-did not meet these criteria (marked with $^*$ in Table~\ref{tab:results}). In these cases, 
-the interval arithmetic back-end is able to complement the inductive approach
-and synthesise a solution instead, albeit with significantly larger runtimes.
+with few counterexamples and fixed-point precision increases. However, two benchmarks in our set
+did not meet these criteria (marked with $^*$ in Table~\ref{tab:results}) \textcolor{red}{Pascal: Why they did not meet the criteria?}. 
+In these cases, the interval arithmetic back-end is able to complement the inductive approach
+and synthesise a solution instead, albeit with significantly larger runtimes \textcolor{red}{Pascal: Why is it slower?}.
+
+\textcolor{red}{Pascal: Can you please add FWL for each synthesized controller using the following format <I,F>, where I represents the number of bits in the integer part and F represents the number of bits in the fractional part?}
 
@@
 
-We conclude from these results that the inductive back-end provides excellent performance
-for synthesising stable controllers in the 12 out of 15 benchmarks, and can be
-complemented using the interval arithmetic back-end for 2 additional benchmarks,
-where the inductive conjectures fail too frequently. Both back-ends together enabled controller
-synthesis for 14 out of 15 benchmarks within reasonable time frames. \pksay{TODO: Upload full
-experiments environment including README and result log files to anonymous Google Drive and
+We conclude from these results that the inductive back-end is able to synthesise 
+stable controllers in the $12$ out of $15$ benchmarks, and can be complemented using 
+the interval arithmetic back-end for $2$ additional benchmarks, where the inductive 
+conjectures fail. Both back-ends together enabled controller synthesis for $14$ 
+out of $15$ benchmarks within reasonable time frames. \textcolor{red}{Why do we fail to synthesise 1 controller?} 
+\pksay{TODO: Upload full experiments environment including README and result log files to anonymous Google Drive and
 provide link here.}

### 2016-10-13 paper/paper.tex
revised sec 4.2

--- 2016-10-13 paper/paper.tex
@@
 \end{bmatrix}
+\label{eq:uncertainty}
 \end{equation}
@@
 
-Assuming that $\hat{G}(z) = \frac{\hat{N_G}(z)}{\hat{D_G}(z)}$
-and $\hat{C}(z) = \frac{\hat{N_C}(z)}{\hat{D_C}(z)}$, then:
-$$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$
+% Assuming that $\hat{G}(z) = \frac{\hat{N_G}(z)}{\hat{D_G}(z)}$
+% and $\hat{C}(z) = \frac{\hat{N_C}(z)}{\hat{D_C}(z)}$, then:
+% $$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$
 
@@
 makes the closed-loop system stable 
-for all possible uncertainties $(\Delta N_G, \Delta D_G)$. 
-Note that, similar to the rest of the paper, we use the notation 
-$\hat{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
-$\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
+for all possible uncertainties $\Delta{\vec{p}}$ (\ref{eq:uncertainty}).
+%$(\Delta N_G, \Delta D_G)$. 
+% Note that, similar to the rest of the paper, we use the notation 
+% $\hat{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
+% $\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
 When mapping back to the notation used for describing the general architecture 
 of the program synthesiser, the controller $(N_c,D_c)$ denotes $P$ and 
-$(\Delta N_G, \Delta D_G)$ represents $x$. 
-We compute the controller $(N_c,D_c)$ in the domain 
-$\mathbb{R}\langle I,F \rangle$ and 
-the uncertainty in $\mathbb{R}\langle I_b,F_b \rangle$.
+$\Delta{\vec{p}}$ represents $x$.
 
@@
 \paragraph{Use of fixed-point computation in the program synthesis engine}
-The program synthesis engine uses fixed-point arithmetic,
-therefore we need to examine the effect of discretization during these operations.
+The program synthesis engine uses fixed-point arithmetic.
+Thus, we compute the coefficients for $N_c$ and $D_c$ in the domains 
+$\mathbb{R}^{n_C}\param{I}{F}$ and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, where 
+$n_C$ and $m_C$ denote the order of the corresponding polynomials
+and $I$ and $F$ denote the integer and fractional size, respectively.
+Regarding the uncertainty, this is synthesised over the 
+domain $\mathbb{R}^{n_G+m_G}\param{I_b}{F_b}$, where $n_G$ and $m_G$ 
+denote the order of the polynomials representing the 
+numerator and denominator of the plant's transfer function, respectively. 
+Again, $I_b$ and $F_b$ denote the integer and fractional size, respectively, with
+$\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
+
+Given the use of fixed-point arithmetic, 
+we need to examine the effect of discretization during these operations.
 Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
-using Fixed-Point bit vectors with integer size $I_b$ and fractional
-size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
+using fixed-point bit vectors.%  with integer size $I_b$ and fractional
+% size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
 %
@@
 the rounding off effect.  We may encompass all the uncertainty as
-$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_b(z)$.  Since this value is
-nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
-denoted by $\mathfrak{G}(z)$.
+$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_b(z)$.  % Since this value is
+% nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
+% denoted by $\mathfrak{G}(z)$.
 
@@
 and rounding operations outwards during the process. 
-\cdsay{dario, what coefficients are these?}
+%\cdsay{dario, what coefficients are these?}
 % This results in a
@@
 approach, we also designed a second approach, which we describe below.
-In our experimental section Sec.~\ref{sec:experiments}, we 
-show that the increase in speed of the second approach 
-over the first one is in most cases of several orders of magnitude.
+In our implementation described in Sec.~\ref{sec:experiments}, we 
+try both approaches and provide the time for the fastest. 
+% show that the increase in speed of the second approach 
+% over the first one is in most cases of several orders of magnitude.
 
@@
 uses a two-stage verification. 
-First, in the {\sc Uncertainty} sub-phase, assuming the 
-current precision \param{I_b}{F_b},
-we check whether 
-the system is unstable for the current candidate solution,
+In the first stage, denoted by {\sc Uncertainty} in Fig.~\ref{fig:CEGIS}, 
+assuming a certain precision \param{I_b}{F_b} for the uncertainty,
+\cdsay{how about the controller?}
+we check whether the system is unstable for the current candidate solution,
 {\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$.
-If this is the case, then we obtain a counterexample denoted by 
-values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
+If this is the case, then we obtain a counterexample 
+$\Delta \vec{p}$, 
+%denoted by values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
 %\red{[see my comment above - these quantities pop up too abruptly.]},
-which make the closed-loop system unstable. 
+which makes the closed-loop system unstable. 
 This uncertainty is added to 
@@
 
-If the result of the {\sc Uncertainty} verification is that
+If the {\sc Uncertainty} verification stage concludes that
 the system is stable for the current candidate solution,
-then we pass this solution to the {\sc Precision} verification sub-phase, 
+then we pass this solution to the second verification stage, {\sc Precision}, 
 which checks the propagation of the error in the fixed-point 
@@
 
-If this check returns $false$, then we 
+If the {\sc precision} verification returns $false$, then we 
 increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise} phase
@@
 
-The fourth (and last) set of benchmarks considers the following description for the plant 
-$G_{4}(s)$ extracted from Keel and Bhattacharyya~\cite{bhattacharyya97,keel_Bhattacharyya_examples}.
-%
-\begin{equation}
-\label{exampleA}
-G_{4}(s)=\frac{s-1}{s^{2}-s-2}
-\end{equation}
-%
-\noindent where $G_{4}(z)$ is obtained using the ZOH discretisation defined 
-in Eq.~\eqref{eq:pulsetf} with $3$ different sample times ($0.1$, $0.05$, and $0.03$ 
-seconds); and the controllers are synthesised using $4$, $8$, and $12$-bits.
-
 All experiments were conducted on an otherwise idle Intel Core i$7$-$4790$ 

### 2016-10-13 paper/paper.tex
partially revised sec 4.3

@@
 in Sec.~\ref{sec:running-ex}.
-We start with the candidate solution given below at $I_b=16,F_b=24$,
-which has all coefficients 0.
+We start with the candidate solution with all coefficients zero 
+given below at $I_b=16,F_b=24$.
 Note that the digital controller is designed with typical control system
@@
 
-In the first {\sc verify} phase we obtain the following counterexample:
+In the first {\sc verify} stage, the {\sc uncertainty} 
+check finds the following counterexample:
 
 $$
-\blue{
 \Delta{\vec{p}} = [0.026506~ 1.000610~ 1.002838]^T
-}
 $$
@@
 $$
-\blue{
 C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}
-}
 $$
 
-In the second {\sc verify} phase, we check whether the current candidate
-solution above is the final solution. It is not and the verifier signals
-that it is due to lack of precision. We thus increase our precision to
-$I_b=20,F_b=28$.
-%
-Since previous counterexamples were attained at lower precision, we 
+This time the {\sc uncertainty} check doesn't find any more counterexamples 
+and we pass the current candidate solution to the {\sc precision} verification stage.
+% In the second {\sc verify} phase, we check whether the current candidate
+% solution above is the final solution. It is not and the verifier signals
+% that it is due to lack of precision.
+We obtain the result $false$, meaning that the current precision is insuficient.
+Consequently, we increase our precision to $I_b=20,F_b=28$.
+%
+Since the previous counterexamples were attained at lower precision, we 
 remove them from the counterexample set. Back in the {\sc synthesise}
-phase, we thus retrieve a candidate solution with all coefficients 0.
-The {\sc verify} phase now provides the first counterexample at higher
+phase, we re-start the process with a candidate solution with all coefficients 0.
+Next, the {\sc uncertainty} verification stage provides the first counterexample at higher
 precision:
@@
 $$
-\blue{
 \Delta{\vec{p}} = [0.026314~ 0.999024~ {-}1.004785]^T
-}
 $$
@@
 $$
-\blue{
 C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}
-}
 $$
@@
 
-This candidate solution is validated as the final solution by the next 
-{\sc verify} phase, which fails to find a new counterexample (i.e. returns UNSAT).
+This candidate solution is validated as the final solution by both stages 
+{\sc uncertainty} and {\sc precision} in the
+{\sc verify} phase. %, which fails to find a new counterexample (i.e. returns UNSAT).
 

### 2016-10-13 paper/paper.tex
fix reference

--- 2016-10-13 paper/paper.tex
@@
 \end{bmatrix}
-\label{eq:uncertainty}
 \end{equation}
@@
 algorithms in DSVerifier that can be used for stability
-verification~\cite{DBLP:journals/dafes/BessaICF16}, one based on
+verification~\cite{daes20161,Bessa16}, one based on
 Schur's decomposition and another one based on Jury's
@@
 
-% Assuming that $\hat{G}(z) = \frac{\hat{N_G}(z)}{\hat{D_G}(z)}$
-% and $\hat{C}(z) = \frac{\hat{N_C}(z)}{\hat{D_C}(z)}$, then:
-% $$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$
+Assuming that $\hat{G}(z) = \frac{\hat{N_G}(z)}{\hat{D_G}(z)}$
+and $\hat{C}(z) = \frac{\hat{N_C}(z)}{\hat{D_C}(z)}$, then:
+$$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$
 
@@
 makes the closed-loop system stable 
-for all possible uncertainties $\Delta{\vec{p}}$ (\ref{eq:uncertainty}).
-%$(\Delta N_G, \Delta D_G)$. 
-% Note that, similar to the rest of the paper, we use the notation 
-% $\hat{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
-% $\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
+for all possible uncertainties $(\Delta N_G, \Delta D_G)$. 
+Note that, similar to the rest of the paper, we use the notation 
+$\hat{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
+$\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
 When mapping back to the notation used for describing the general architecture 
 of the program synthesiser, the controller $(N_c,D_c)$ denotes $P$ and 
-$\Delta{\vec{p}}$ represents $x$.
+$(\Delta N_G, \Delta D_G)$ represents $x$. 
+We compute the controller $(N_c,D_c)$ in the domain 
+$\mathbb{R}\langle I,F \rangle$ and 
+the uncertainty in $\mathbb{R}\langle I_b,F_b \rangle$.
 
@@
 \paragraph{Use of fixed-point computation in the program synthesis engine}
-The program synthesis engine uses fixed-point arithmetic.
-Thus, we compute the coefficients for $N_c$ and $D_c$ in the domains 
-$\mathbb{R}^{n_C}\param{I}{F}$ and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, where 
-$n_C$ and $m_C$ denote the order of the corresponding polynomials
-and $I$ and $F$ denote the integer and fractional size, respectively.
-Regarding the uncertainty, this is synthesised over the 
-domain $\mathbb{R}^{n_G+m_G}\param{I_b}{F_b}$, where $n_G$ and $m_G$ 
-denote the order of the polynomials representing the 
-numerator and denominator of the plant's transfer function, respectively. 
-Again, $I_b$ and $F_b$ denote the integer and fractional size, respectively, with
-$\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
-
-Given the use of fixed-point arithmetic, 
-we need to examine the effect of discretization during these operations.
+The program synthesis engine uses fixed-point arithmetic,
+therefore we need to examine the effect of discretization during these operations.
 Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
-using fixed-point bit vectors.%  with integer size $I_b$ and fractional
-% size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
+using Fixed-Point bit vectors with integer size $I_b$ and fractional
+size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
 %
@@
 the rounding off effect.  We may encompass all the uncertainty as
-$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_b(z)$.  % Since this value is
-% nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
-% denoted by $\mathfrak{G}(z)$.
+$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_b(z)$.  Since this value is
+nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
+denoted by $\mathfrak{G}(z)$.
 
@@
 and rounding operations outwards during the process. 
-%\cdsay{dario, what coefficients are these?}
+\cdsay{dario, what coefficients are these?}
 % This results in a
@@
 approach, we also designed a second approach, which we describe below.
-In our implementation described in Sec.~\ref{sec:experiments}, we 
-try both approaches and provide the time for the fastest. 
-% show that the increase in speed of the second approach 
-% over the first one is in most cases of several orders of magnitude.
+In our experimental section Sec.~\ref{sec:experiments}, we 
+show that the increase in speed of the second approach 
+over the first one is in most cases of several orders of magnitude.
 
@@
 uses a two-stage verification. 
-In the first stage, denoted by {\sc Uncertainty} in Fig.~\ref{fig:CEGIS}, 
-assuming a certain precision \param{I_b}{F_b} for the uncertainty,
-\cdsay{how about the controller?}
-we check whether the system is unstable for the current candidate solution,
+First, in the {\sc Uncertainty} sub-phase, assuming the 
+current precision \param{I_b}{F_b},
+we check whether 
+the system is unstable for the current candidate solution,
 {\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$.
-If this is the case, then we obtain a counterexample 
-$\Delta \vec{p}$, 
-%denoted by values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
+If this is the case, then we obtain a counterexample denoted by 
+values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
 %\red{[see my comment above - these quantities pop up too abruptly.]},
-which makes the closed-loop system unstable. 
+which make the closed-loop system unstable. 
 This uncertainty is added to 
@@
 
-If the {\sc Uncertainty} verification stage concludes that
+If the result of the {\sc Uncertainty} verification is that
 the system is stable for the current candidate solution,
-then we pass this solution to the second verification stage, {\sc Precision}, 
+then we pass this solution to the {\sc Precision} verification sub-phase, 
 which checks the propagation of the error in the fixed-point 
@@
 
-If the {\sc precision} verification returns $false$, then we 
+If this check returns $false$, then we 
 increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise} phase

### 2016-10-13 paper/paper.tex
Updated synthesis process overview.

--- 2016-10-13 paper/paper.tex
@@
 %------------------------------------
-\subsection{DSVerifier Verification Flow}
+\subsection{Synthesis Process using DSVerifier}
 \label{verification-flow}
@@
 
-The DSVerifier verification flow is illustrated in Fig.~\ref{DSVerifier_process};
+The full synthesis process is illustrated in Fig.~\ref{DSVerifier_process};
 a detailed description of DSVerifier tool can be found in~\cite{IsmailBCFF15}.
@@
 containing a specification $\phi$ for the verification properties ({\it
-i.e.}, robust stability) is translated into SAT/SMT formulae by a back-end
-model-checking tool ({\it e.g.}, CBMC~\cite{ClarkeKL04} or
-ESBMC~\cite{CordeiroFM12}).  If any property violation is found, then
-DSVerifier reports a counterexample, which contains system inputs or
-parametric deviations $\Delta{G}$ that lead the system to a failure.  A
-successful verification result is reported if the system is safe with
+i.e.}, robust stability) is provided to CBMC's~\cite{ClarkeKL04} integrated
+CEGIS synthesis module, where $\tilde C(z)$ is marked as input variable to
+synthesise.  If any property violation is found, then
+a counterexample is reported, which contains system inputs or
+parametric deviations $\Delta{G}$ that lead the system to a failure.  
+This information allows the CEGIS module to refine its search for a stable
+controller, which we explain in detail in section~\ref{synthesiser-general}.
+A successful verification result is reported if the system is safe with
 respect to $\phi$.  In particular, the stability verification is complete
@@
 the function $f$ (cf.~Eq.~\eqref{FWL_tf}).
-
-\textcolor{red}{Pascal: can you please update this section to include the CEGIS step?}
 
@@
 \subsection{General architecture of the program synthesiser}
+\label{synthesiser-general}
 %

### 2016-10-13 paper/paper.tex
Updated server CPU/RAM.

@@
 
-\textcolor{red}{Pascal: Can you please check whether this configuration is correct?}
-All experiments were conducted on an otherwise idle Intel Core i$7$-$4790$ 
-CPU $3$.$60$ GHz, $16$ GB of RAM, and Linux OS.  All times given are wall 
-clock time in seconds as measured by the UNIX time command.
+All experiments were conducted on a 12-core 2.40\,GHz Intel Xeon E5-2440 with 96\,GB
+of RAM, and Linux OS.  All times given are wall clock time in seconds as measured
+by the UNIX date command.
 

### 2016-10-13 paper/paper.tex
Added I/F to experimental results.

@@
 
-\textcolor{red}{Pascal: Can you please add FWL for each synthesized controller using the following format <I,F>, where I represents the number of bits in the integer part and F represents the number of bits in the fractional part?}
-
 \begin{table}[H]
 \centering
-\begin{tabular}{c | l | r l}
-Plant & Benchmark                  & Time    & \\\cline{1-3}
-$G_1$ & CruiseControl02            & 17\,s   & \\
-$G_1$ & CruiseControl02$^\dagger$  & 46\,s   & \\
-$G_2$ & SpringMassDamper           & 28\,s   & \\
-$G_2$ & SpringMassDamper$^\dagger$ & \xmark  & \\
-$G_3$ & SatelliteB2                & 7\,s    & \\
-$G_3$ & SatelliteB2$^\dagger$      & 6601\,s & \tbmark\\
-$G_3$ & SatelliteC2                & 2\,s    & \\
-$G_3$ & SatelliteC2$^\dagger$      & 76\,s   & \tbmark\\
-$G_4$ & a\_PL1\_SCH2\_IMPL1        & 2704\,s & \\
-$G_4$ & a\_PL1\_SCH2\_IMPL2        & 538\,s  & \\
-$G_4$ & a\_PL1\_SCH2\_IMPL3        & 12\,s   & \\
-$G_4$ & a\_PL1\_SCH3\_IMPL1        & 318\,s  & \\
-$G_4$ & a\_PL1\_SCH3\_IMPL2        & 967\,s  & \\
-$G_4$ & a\_PL1\_SCH3\_IMPL3        & 9798\,s & \\
-$G_4$ & a\_PL1\_SCH4\_IMPL1        & 6304\,s & \\
+\begin{tabular}{c | l r r | r l}
+Plant & Benchmark                  & $I$ & $F$ & Time    & \\\cline{1-5}
+$G_1$ & CruiseControl02            &   4 &  16 & 17\,s   & \\
+$G_1$ & CruiseControl02$^\dagger$  &   4 &  16 & 46\,s   & \\
+$G_2$ & SpringMassDamper           &  15 &  16 & 28\,s   & \\
+$G_2$ & SpringMassDamper$^\dagger$ &  15 &  16 & \xmark  & \\
+$G_3$ & SatelliteB2                &   3 &   7 & 7\,s    & \\
+$G_3$ & SatelliteB2$^\dagger$      &   3 &   7 & 6601\,s & \tbmark\\
+$G_3$ & SatelliteC2                &   3 &   5 & 2\,s    & \\
+$G_3$ & SatelliteC2$^\dagger$      &   3 &   5 & 76\,s   & \tbmark\\
+$G_4$ & a\_PL1\_SCH2\_IMPL1        &  16 &   4 & 2704\,s & \\
+$G_4$ & a\_PL1\_SCH2\_IMPL2        &  16 &   8 & 538\,s  & \\
+$G_4$ & a\_PL1\_SCH2\_IMPL3        &  16 &  12 & 12\,s   & \\
+$G_4$ & a\_PL1\_SCH3\_IMPL1        &  16 &   4 & 318\,s  & \\
+$G_4$ & a\_PL1\_SCH3\_IMPL2        &  16 &   8 & 967\,s  & \\
+$G_4$ & a\_PL1\_SCH3\_IMPL3        &  16 &  12 & 9798\,s & \\
+$G_4$ & a\_PL1\_SCH4\_IMPL1        &  16 &   4 & 6304\,s & \\
 \end{tabular}

### 2016-10-13 paper/paper.tex
fix typo

--- 2016-10-13 paper/paper.tex
@@
 
-In order to obtain a sound synthesis of digital controller, the effect of FWL implementation in controller and quantisation noises in closed loop system have to be considered.
-Considering that the quantizer $Q1$ is the source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise $\nu_{2}$, the following equation may be written for the system in figure~\ref{fig:sampledsystem} considering the parametric uncertainties $\Delta G(z)$ and the FWL effects on controller  ($\hat{C}(z)$):
+In order to obtain a sound synthesis of the digital controller, the effect of FWL implementation in controller and quantisation noises in closed loop system have to be considered.
+Considering that the quantizer $Q1$ is the source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise $\nu_{2}$, the following equation is written for the system in Figure~\ref{fig:sampledsystem}, considering the parametric uncertainties $\Delta G(z)$ and the FWL effects on controller ($\hat{C}(z)$):
 \begin{equation}
@@
 A discrete-time linear system is said to be Bounded-Input and Bounded-Output (BIBO) stable if and only if every pole of its transfer function lies inside the unit circle.
-Analyzing the~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for BIBO stability of closed-loop system in figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$ are bounded.
+\textcolor{red}{Analyzing Eq.~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for BIBO stability of closed-loop system in Figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$ are bounded.}
 

### 2016-10-13 paper/paper.tex
review Synthesis Process using DSVerifier

@@
 non-deterministic model to represent the plant family $\mathfrak{G}(z)$
-(Step A), and a transfer function $f$ [eq.  \ref{FWL_tf}] (step B) to
-calulate the implementation $f(\hat{C}(z)) \rightarrow \tilde C(z)$ of the
+(Step A), and a transfer function $f$ represented by Eq.~\ref{FWL_tf} (step B) to
+calculate the implementation $f(\hat{C}(z)) \rightarrow \tilde C(z)$ of the
 controller (step C).  Finally DSVerifier builds an intermediate ANSI-C code
@@
 
-To exploit the present approach full potential, a dynamical plant that can
+In order to exploit the present approach full potential, a dynamical plant that can
 present physical components must be considered.  However, a discrete plant

### 2016-10-13 paper/paper.tex
fixed notation and domains in 4.3

--- 2016-10-13 paper/paper.tex
@@
 
-In order to obtain a sound synthesis of the digital controller, the effect of FWL implementation in controller and quantisation noises in closed loop system have to be considered.
-Considering that the quantizer $Q1$ is the source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise $\nu_{2}$, the following equation is written for the system in Figure~\ref{fig:sampledsystem}, considering the parametric uncertainties $\Delta G(z)$ and the FWL effects on controller ($\hat{C}(z)$):
+In order to obtain a sound synthesis of digital controller, the effect of FWL implementation in controller and quantisation noises in closed loop system have to be considered.
+Considering that the quantizer $Q1$ is the source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise $\nu_{2}$, the following equation may be written for the system in figure~\ref{fig:sampledsystem} considering the parametric uncertainties $\Delta G(z)$ and the FWL effects on controller  ($\hat{C}(z)$):
 \begin{equation}
@@
 A discrete-time linear system is said to be Bounded-Input and Bounded-Output (BIBO) stable if and only if every pole of its transfer function lies inside the unit circle.
-\textcolor{red}{Analyzing Eq.~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for BIBO stability of closed-loop system in Figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$ are bounded.}
+Analyzing the~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for BIBO stability of closed-loop system in figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$ are bounded.
 
@@
 %------------------------------------
-\subsection{Synthesis Process using DSVerifier}
+\subsection{DSVerifier Verification Flow}
 \label{verification-flow}
@@
 
-The full synthesis process is illustrated in Fig.~\ref{DSVerifier_process};
+The DSVerifier verification flow is illustrated in Fig.~\ref{DSVerifier_process};
 a detailed description of DSVerifier tool can be found in~\cite{IsmailBCFF15}.
@@
 containing a specification $\phi$ for the verification properties ({\it
-i.e.}, robust stability) is provided to CBMC's~\cite{ClarkeKL04} integrated
-CEGIS synthesis module, where $\tilde C(z)$ is marked as input variable to
-synthesise.  If any property violation is found, then
-a counterexample is reported, which contains system inputs or
-parametric deviations $\Delta{G}$ that lead the system to a failure.  
-This information allows the CEGIS module to refine its search for a stable
-controller, which we explain in detail in section~\ref{synthesiser-general}.
-A successful verification result is reported if the system is safe with
+i.e.}, robust stability) is translated into SAT/SMT formulae by a back-end
+model-checking tool ({\it e.g.}, CBMC~\cite{ClarkeKL04} or
+ESBMC~\cite{CordeiroFM12}).  If any property violation is found, then
+DSVerifier reports a counterexample, which contains system inputs or
+parametric deviations $\Delta{G}$ that lead the system to a failure.  A
+successful verification result is reported if the system is safe with
 respect to $\phi$.  In particular, the stability verification is complete
@@
 \subsection{General architecture of the program synthesiser}
-\label{synthesiser-general}
 %
@@
 algorithms in DSVerifier that can be used for stability
-verification~\cite{daes20161,Bessa16}, one based on
+verification~\cite{DBLP:journals/dafes/BessaICF16}, one based on
 Schur's decomposition and another one based on Jury's
@@
 
-Essentially, the synthesis problem we are trying to solve is the following:
-find a digital controller denoted by  $N_c$ and $D_c$ that
-makes the closed-loop system stable 
-for all possible uncertainties $\Delta{\vec{p}}$ (\ref{eq:uncertainty}).
-%$(\Delta N_G, \Delta D_G)$. 
-% Note that, similar to the rest of the paper, we use the notation 
-% $\hat{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
-% $\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
-When mapping back to the notation used for describing the general architecture 
-of the program synthesiser, the controller $(N_c,D_c)$ denotes $P$ and 
-$\Delta{\vec{p}}$ represents $x$.
-
 % \red{[clear elucidation of the mapping between this and the domains used 
@@
 The program synthesis engine uses fixed-point arithmetic.
-Thus, we compute the coefficients for $N_c$ and $D_c$ in the domains 
-$\mathbb{R}^{n_C}\param{I}{F}$ and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, where 
-$n_C$ and $m_C$ denote the order of the corresponding polynomials
-and $I$ and $F$ denote the integer and fractional size, respectively.
-Regarding the uncertainty, this is synthesised over the 
-domain $\mathbb{R}^{n_G+m_G}\param{I_b}{F_b}$, where $n_G$ and $m_G$ 
-denote the order of the polynomials representing the 
-numerator and denominator of the plant's transfer function, respectively. 
-Again, $I_b$ and $F_b$ denote the integer and fractional size, respectively, with
+Namely, we use the domain $\mathbb{R}\param{I}{F}$
+for the controller's coefficients and the domain 
+$\mathbb{R}\param{I_b}{F_b}$ for the plant's coefficients.
+Note that $I$ and $F$, as well as $I_b$ and $F_b$, 
+denote the integer and fractional size, respectively, with
 $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
+%the coefficients for $C(z)$ 
+%$N_c$ and $D_c$ 
+%in the domain $\mathbb{R}\param{I}{F}$, 
+%and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, 
+%where $n_C$ and $m_C$ denote the order of the corresponding polynomials
+%where $I$ and $F$ denote the integer and fractional size, respectively.
+%Regarding the plant, its coefficients are this is synthesised over the 
+%domain $\mathbb{R}^{n_G+m_G}\param{I_b}{F_b}$, where $n_G$ and $m_G$ 
+%denote the order of the polynomials representing the 
+%numerator and denominator of the plant's transfer function, respectively. 
+%Again, $I_b$ and $F_b$ denote the integer and fractional size, respectively, with
+%$\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
 
@@
 % denoted by $\mathfrak{G}(z)$.
+
+\paragraph{Our synthesis problem}
+The synthesis problem we are trying to solve is the following:
+find a digital controller $C(z)$ %denoted by  $N_c$ and $D_c$ 
+that makes the closed-loop system stable 
+for all possible uncertainties 
+%$\Delta{\vec{p}}$ (\ref{eq:uncertainty}).
+$\tilde G(z)$ (\ref{digital_plant_tf}).
+%, where we precisely describe 
+%$(\Delta N_G, \Delta D_G)$. 
+% Note that, similar to the rest of the paper, we use the notation 
+% $\tilda{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
+% $\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
+When mapping back to the notation used for describing the general architecture 
+of the program synthesiser, the controller $C(z)$ denotes $P$ and 
+$\tilde G(z)$ represents $x$.
+
+As mentioned above, we compute the coefficients for $C(z)$ 
+%$N_c$ and $D_c$ 
+in the domain $\mathbb{R}\param{I}{F}$, 
+%and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, 
+%where $n_C$ and $m_C$ denote the order of the corresponding polynomials
+and those for $\tilde G(z)$ in the domain
+$\mathbb{R}\langle I_b,F_b \rangle$.
 

### 2016-10-13 paper/paper.tex
FWL for f_b
fixed sec 4.3

@@
 $$
-\Delta{\vec{p}} = [0.026506~ 1.000610~ 1.002838]^T
+\tilde G(z) = \frac{0.026506}{1.000610z+1.002838}
 $$
@@
 $$
-\Delta{\vec{p}} = [0.026314~ 0.999024~ {-}1.004785]^T
+\tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785}
 $$
@@
 
-\blue{
-For the same cruise control system, the synthesis may be done considering that the plant model have parametric uncertainties ($\Delta G_{P}(z)$).
+% \blue{
+% For the same cruise control system, the synthesis may be done considering that the plant model have parametric uncertainties ($\Delta G_{P}(z)$).
 Thus, the synthesised controller must to stabilize for any parametric variation $\Delta p$ inside of a given region.
 Specially, in this example, was assumed that each coefficient of $G(z)$ may vary $\pm 0.5\%$.
-}
-
-\blue{Initially, the controller denominator and numerator  ($D_{C}(z)$ and $N_{C}(z)$) are started with zero coefficients, as in previous example.
+% }
+
+% \blue{Initially, the controller denominator and numerator  ($D_{C}(z)$ and $N_{C}(z)$) are started with zero coefficients, as in previous example.
 Thus,  in the first {\sc verify} phase a counterexample is presented, that is added to {\sc inputs}, whis is usede in the first  {\sc synthesise} phase.
 The resulting controller is:
-}
-$$
-{
-\blue{
-C(z)=\frac{0.77516z^2{+}-0.71497z{+}0.03729}{0.25024z^2{-}0.01799z{+}0.00097}
-}}
-$$
-
-\blue{In the second {\sc verify} phase, the controller failed to stabilize the system for all the range of uncertainties, another counterexample was provided, and the following candidate controller is presented in another {\sc synthesise} phase:}
-$$
-{
-\blue{
-C(z)=\frac{0.68970z^2{+}0.36538z{+}0.30637}{0.06862z^2{+}0.00394z{+}0.00802}
-}}
-$$
-
-\blue{
-This candidate solution is validated as the final solution by the next 
-{\sc verify} phase.
-}
-
-% Counterexample from first cruisecontrol02.c benchmark with uncertainty and
-% nondeterminism:
-% 1) { (0.02634525299072265625, 0.9979267120361328125, -0.99768829345703125) }
-
-% 2) { (0.02644824981689453125, 1.00053310394287109375, -1.0014629364013671875) }
-
-% <a>
-% <item>7.515781402587890625</item>
-% <item>-4.385616302490234375</item>
-% <item>4.142093658447265625</item>
-% </a>
-% <a_size>3</a_size>
-% <b>
-% <item>-3.52398681640625</item>
-% <item>-1.530254364013671875</item>
-% <item>7.58094024658203125</item>
-% </b>
-% <b_size>3</b_size>
+% }
+% $$
+% {
+% \blue{
+% C(z)=\frac{0.77516z^2{+}-0.71497z{+}0.03729}{0.25024z^2{-}0.01799z{+}0.00097}
+% }}
+% $$
+
+% \blue{In the second {\sc verify} phase, the controller failed to stabilize the system for all the range of uncertainties, another counterexample was provided, and the following candidate controller is presented in another {\sc synthesise} phase:}
+% $$
+% {
+% \blue{
+% C(z)=\frac{0.68970z^2{+}0.36538z{+}0.30637}{0.06862z^2{+}0.00394z{+}0.00802}
+% }}
+% $$
+
+% \blue{
+% This candidate solution is validated as the final solution by the next 
+% {\sc verify} phase.
+% }
 

### 2016-10-13 paper/paper.tex
Extended results discussion.

@@
 \label{FWL_tf}
-&f_b (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = x-(x\mod\tilde x)
+&f_b (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = x-(x\mod\tilde x) \\
+&FWL_b[P \in \mathcal{P}] = \tilde P \in \mathcal{P}^{n}\langle I_b,F_b \rangle : c_i \in P \wedge \tilde c_i \in \tilde P=f_b(c_i)  \nonumber
 \end{align}
-we calculate $\tilde G(z)=f(\hat{G}(z))$
+we calculate $\tilde G(z)=FWL_b(\hat{G}(z))$
 \begin{align}
@@
 \tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_b \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_b \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_b \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_b \hat{a}_{N_G})z^{-N_G}} \nonumber \\
-&=G(z)+\Delta{G}_P(z)+\Delta{G}_b(z).
+&=\hat{G}(z)+\Delta{G}_b(z)=G(z)+\Delta{G}_P(z)+\Delta{G}_b(z).
 \end{align}
@@
 of RAM, and Linux OS.  All times given are wall clock time in seconds as measured
-by the UNIX date command.
+by the UNIX date command.  For the inductive back-end we apply a timeout of 8 hours
+per benchmark, and 24 hours for the interval arithmetic back-end.
 
@@
 In these cases, the interval arithmetic back-end is able to complement the inductive approach
-and synthesise a solution instead, albeit with significantly larger runtimes \textcolor{red}{Pascal: Why is it slower?}.
+and synthesise a solution instead, albeit with significantly larger runtimes.  This performance
+difference is due to  the fact that the interval back-end does not take advantage of the inductive
+conjecture inherent to CEGIS, but instead fully explores the counterexample space.  The result is
+a performance difference of at least two orders of magnitude in our experiments, leading to the
+interval back-end timing out on the majority of our benchmarks.  Table~\ref{tab:results} only
+lists the faster of the two back-ends for each benchmark, which in 12 out of 14 cases is the inductive
+back-end.
 
@@
 conjectures fail. Both back-ends together enabled controller synthesis for $14$ 
-out of $15$ benchmarks within reasonable time frames. \textcolor{red}{Why do we fail to synthesise 1 controller?} 
+out of $15$ benchmarks within reasonable time frames.  For the 1 remaining benchmark
+our approach failed to synthesise a stable controller in the requested time limits.
+This can be addressed by either increasing the fixed point word widths considered or
+using floating point arithmetic instead. 
 \pksay{TODO: Upload full experiments environment including README and result log files to anonymous Google Drive and

### 2016-10-13 paper/paper.tex
review Table 1

--- 2016-10-13 paper/paper.tex
@@
 
+Essentially, the synthesis problem we are trying to solve is the following:
+find a digital controller denoted by  $N_c$ and $D_c$ that
+makes the closed-loop system stable 
+for all possible uncertainties $\Delta{\vec{p}}$ (\ref{eq:uncertainty}).
+%$(\Delta N_G, \Delta D_G)$. 
+% Note that, similar to the rest of the paper, we use the notation 
+% $\hat{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
+% $\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
+When mapping back to the notation used for describing the general architecture 
+of the program synthesiser, the controller $(N_c,D_c)$ denotes $P$ and 
+$\Delta{\vec{p}}$ represents $x$.
+
 % \red{[clear elucidation of the mapping between this and the domains used 
@@
 The program synthesis engine uses fixed-point arithmetic.
-Namely, we use the domain $\mathbb{R}\param{I}{F}$
-for the controller's coefficients and the domain 
-$\mathbb{R}\param{I_b}{F_b}$ for the plant's coefficients.
-Note that $I$ and $F$, as well as $I_b$ and $F_b$, 
-denote the integer and fractional size, respectively, with
+Thus, we compute the coefficients for $N_c$ and $D_c$ in the domains 
+$\mathbb{R}^{n_C}\param{I}{F}$ and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, where 
+$n_C$ and $m_C$ denote the order of the corresponding polynomials
+and $I$ and $F$ denote the integer and fractional size, respectively.
+Regarding the uncertainty, this is synthesised over the 
+domain $\mathbb{R}^{n_G+m_G}\param{I_b}{F_b}$, where $n_G$ and $m_G$ 
+denote the order of the polynomials representing the 
+numerator and denominator of the plant's transfer function, respectively. 
+Again, $I_b$ and $F_b$ denote the integer and fractional size, respectively, with
 $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
-%the coefficients for $C(z)$ 
-%$N_c$ and $D_c$ 
-%in the domain $\mathbb{R}\param{I}{F}$, 
-%and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, 
-%where $n_C$ and $m_C$ denote the order of the corresponding polynomials
-%where $I$ and $F$ denote the integer and fractional size, respectively.
-%Regarding the plant, its coefficients are this is synthesised over the 
-%domain $\mathbb{R}^{n_G+m_G}\param{I_b}{F_b}$, where $n_G$ and $m_G$ 
-%denote the order of the polynomials representing the 
-%numerator and denominator of the plant's transfer function, respectively. 
-%Again, $I_b$ and $F_b$ denote the integer and fractional size, respectively, with
-%$\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
 
@@
 % denoted by $\mathfrak{G}(z)$.
-
-\paragraph{Our synthesis problem}
-The synthesis problem we are trying to solve is the following:
-find a digital controller $C(z)$ %denoted by  $N_c$ and $D_c$ 
-that makes the closed-loop system stable 
-for all possible uncertainties 
-%$\Delta{\vec{p}}$ (\ref{eq:uncertainty}).
-$\tilde G(z)$ (\ref{digital_plant_tf}).
-%, where we precisely describe 
-%$(\Delta N_G, \Delta D_G)$. 
-% Note that, similar to the rest of the paper, we use the notation 
-% $\tilda{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
-% $\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
-When mapping back to the notation used for describing the general architecture 
-of the program synthesiser, the controller $C(z)$ denotes $P$ and 
-$\tilde G(z)$ represents $x$.
-
-As mentioned above, we compute the coefficients for $C(z)$ 
-%$N_c$ and $D_c$ 
-in the domain $\mathbb{R}\param{I}{F}$, 
-%and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, 
-%where $n_C$ and $m_C$ denote the order of the corresponding polynomials
-and those for $\tilde G(z)$ in the domain
-$\mathbb{R}\langle I_b,F_b \rangle$.
 
@@
 $G_3$ & SatelliteC2$^\dagger$      &   3 &   5 & 76\,s   & \tbmark\\
-$G_4$ & a\_PL1\_SCH2\_IMPL1        &  16 &   4 & 2704\,s & \\
-$G_4$ & a\_PL1\_SCH2\_IMPL2        &  16 &   8 & 538\,s  & \\
-$G_4$ & a\_PL1\_SCH2\_IMPL3        &  16 &  12 & 12\,s   & \\
-$G_4$ & a\_PL1\_SCH3\_IMPL1        &  16 &   4 & 318\,s  & \\
-$G_4$ & a\_PL1\_SCH3\_IMPL2        &  16 &   8 & 967\,s  & \\
-$G_4$ & a\_PL1\_SCH3\_IMPL3        &  16 &  12 & 9798\,s & \\
-$G_4$ & a\_PL1\_SCH4\_IMPL1        &  16 &   4 & 6304\,s & \\
+$G_4$ & a\_ST1\_IMPL1        			 &  16 &   4 & 2704\,s & \\
+$G_4$ & a\_ST1\_IMPL2              &  16 &   8 & 538\,s  & \\
+$G_4$ & a\_ST1\_IMPL3              &  16 &  12 & 12\,s   & \\
+$G_4$ & a\_ST2\_IMPL1              &  16 &   4 & 318\,s  & \\
+$G_4$ & a\_ST2\_IMPL2              &  16 &   8 & 967\,s  & \\
+$G_4$ & a\_ST2\_IMPL3              &  16 &  12 & 9798\,s & \\
+$G_4$ & a\_ST3\_IMPL1              &  16 &   4 & 6304\,s & \\
 \end{tabular}

### 2016-10-13 paper/paper.tex
polynomial orders

@@
 \end{equation}
-\red{[same order?]}
+Due to the nature of the methods used for stability check in this paper, we require that  the parametric errors in the plant have the same polynomial order as the plant itself (other errors are ensured to fulfill this property in our implementation).
 
@@
 
-A typical hybrid system, with a continuous plant and a discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$
-\red{[this Delta term now refers to the continuous plant? this is not what has been discussed before, nor what is in some of the plots.]} 
-, $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.
+A typical hybrid system, with a continuous plant and a discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$ , $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.
 

### 2016-10-13 paper/paper.tex
revised conclusions

--- 2016-10-13 paper/paper.tex
@@
 of RAM, and Linux OS.  All times given are wall clock time in seconds as measured
-by the UNIX date command.  For the inductive back-end we apply a timeout of 8 hours
-per benchmark, and 24 hours for the interval arithmetic back-end.
+by the UNIX date command.
 
@@
 In these cases, the interval arithmetic back-end is able to complement the inductive approach
-and synthesise a solution instead, albeit with significantly larger runtimes.  This performance
-difference is due to  the fact that the interval back-end does not take advantage of the inductive
-conjecture inherent to CEGIS, but instead fully explores the counterexample space.  The result is
-a performance difference of at least two orders of magnitude in our experiments, leading to the
-interval back-end timing out on the majority of our benchmarks.  Table~\ref{tab:results} only
-lists the faster of the two back-ends for each benchmark, which in 12 out of 14 cases is the inductive
-back-end.
+and synthesise a solution instead, albeit with significantly larger runtimes \textcolor{red}{Pascal: Why is it slower?}.
 
@@
 $G_3$ & SatelliteC2$^\dagger$      &   3 &   5 & 76\,s   & \tbmark\\
-$G_4$ & a\_ST1\_IMPL1        			 &  16 &   4 & 2704\,s & \\
-$G_4$ & a\_ST1\_IMPL2              &  16 &   8 & 538\,s  & \\
-$G_4$ & a\_ST1\_IMPL3              &  16 &  12 & 12\,s   & \\
-$G_4$ & a\_ST2\_IMPL1              &  16 &   4 & 318\,s  & \\
-$G_4$ & a\_ST2\_IMPL2              &  16 &   8 & 967\,s  & \\
-$G_4$ & a\_ST2\_IMPL3              &  16 &  12 & 9798\,s & \\
-$G_4$ & a\_ST3\_IMPL1              &  16 &   4 & 6304\,s & \\
+$G_4$ & a\_PL1\_SCH2\_IMPL1        &  16 &   4 & 2704\,s & \\
+$G_4$ & a\_PL1\_SCH2\_IMPL2        &  16 &   8 & 538\,s  & \\
+$G_4$ & a\_PL1\_SCH2\_IMPL3        &  16 &  12 & 12\,s   & \\
+$G_4$ & a\_PL1\_SCH3\_IMPL1        &  16 &   4 & 318\,s  & \\
+$G_4$ & a\_PL1\_SCH3\_IMPL2        &  16 &   8 & 967\,s  & \\
+$G_4$ & a\_PL1\_SCH3\_IMPL3        &  16 &  12 & 9798\,s & \\
+$G_4$ & a\_PL1\_SCH4\_IMPL1        &  16 &   4 & 6304\,s & \\
 \end{tabular}
@@
 conjectures fail. Both back-ends together enabled controller synthesis for $14$ 
-out of $15$ benchmarks within reasonable time frames.  For the 1 remaining benchmark
-our approach failed to synthesise a stable controller in the requested time limits.
-This can be addressed by either increasing the fixed point word widths considered or
-using floating point arithmetic instead. 
+out of $15$ benchmarks within reasonable time frames. \textcolor{red}{Why do we fail to synthesise 1 controller?} 
 \pksay{TODO: Upload full experiments environment including README and result log files to anonymous Google Drive and
@@
 effects of the quantisers (A/D and D/A converters) as time discretisation elements 
-with quantisation noise. Experimental results show that the inductive back-end of our
-CEGIS-based approach is able to synthesise stable controllers in most benchmarks and can be 
-complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
-Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
+with quantisation noise. Experimental results show that our
+CEGIS-based approach is able to synthesise stable controllers in most benchmarks
+within reasonable time frames.
+% and can be 
+%complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
+%Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
 Further studies include the extension of this CEGIS-based approach for different classes of systems

### 2016-10-13 paper/paper.tex
revised sec 4.2

@@
 There are two approaches for the {\sc verify} phase based on the
-described model.  The first uses interval arithmetic, representing the
+described model.  The first uses interval arithmetic 
+\cdsay{Dario, can you please add a reference here?} to represent the
 coefficients
@@
 {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
-and rounding operations outwards during the process. 
+and the rounding operations outwards during the process. 
 %\cdsay{dario, what coefficients are these?}
@@
 approach, we also designed a second approach, which we describe below.
-In our implementation described in Sec.~\ref{sec:experiments}, we 
-try both approaches and provide the time for the fastest. 
-% show that the increase in speed of the second approach 
-% over the first one is in most cases of several orders of magnitude.
+Our experimental results described in Sec.~\ref{sec:experiments},  
+%try both approaches and provide the time for the fastest. 
+show that the increase in speed of the second approach 
+over the first one is in most cases of several orders of magnitude.
 
 In Fig.~\ref{fig:CEGIS}, we illustrate the second approach, which 
-uses a two-stage verification. 
-In the first stage, denoted by {\sc Uncertainty} in Fig.~\ref{fig:CEGIS}, 
-assuming a certain precision \param{I_b}{F_b} for the uncertainty,
+uses a two-stage verification such that in the first stage we 
+assume a certain precision for the uncertainty
+followed by a second stage, where we check the soundness of our assumption.
+
+Essentially, in the first stage, denoted by {\sc Uncertainty} in Fig.~\ref{fig:CEGIS}, 
+assuming a certain precision \param{I_b}{F_b} 
 \cdsay{how about the controller?}

### 2016-10-13 paper/paper.tex
minor changes
Interval arithmetic reference

@@
 There are two approaches for the {\sc verify} phase based on the
-described model.  The first uses interval arithmetic 
-\cdsay{Dario, can you please add a reference here?} to represent the
-coefficients
+described model.  The first uses interval arithmetic \cite{moore1966interval}
+to represent the coefficients
 $[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\
 {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
-and the rounding operations outwards during the process. 
+and rounds operations outwards during calculations. 
 %\cdsay{dario, what coefficients are these?}
@@
 of RAM, and Linux OS.  All times given are wall clock time in seconds as measured
-by the UNIX date command.  For the inductive back-end we apply a timeout of 8 hours
+by the UNIX date command.  For the inductive back-end, we apply a timeout of 8 hours
 per benchmark, and 24 hours for the interval arithmetic back-end.

### 2016-10-13 paper/paper.tex
revised sec 4.3

--- 2016-10-13 paper/paper.tex
@@
 $\mathbb{R}\langle I_b,F_b \rangle$.
+While the controller's precision $\param{I}{F}$ is given, 
+we can vary $\param{I_b}{F_b}$ such that 
+$\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
 
@@
 be correct and only generate counterexamples when the precision of the
-engine is insuficient.  Given the high computational cost of this
+engine is insufficient. Given the high computational cost of this
 approach, we also designed a second approach, which we describe below.
@@
 uses a two-stage verification such that in the first stage we 
-assume a certain precision for the uncertainty
-followed by a second stage, where we check the soundness of our assumption.
+assume a certain precision \param{I_b}{F_b}  
+followed by checking the soundness of our assumption
+in a second verification stage.
 
 Essentially, in the first stage, denoted by {\sc Uncertainty} in Fig.~\ref{fig:CEGIS}, 
-assuming a certain precision \param{I_b}{F_b} 
-\cdsay{how about the controller?}
+assuming a precision \param{I_b}{F_b} 
 we check whether the system is unstable for the current candidate solution,
@@
 If this is the case, then we obtain a counterexample 
-$\Delta \vec{p}$, 
+$\tilde G(z)$, 
 %denoted by values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
@@
 we obtain a candidate solution consisting 
-of a controller $D_C$ and $N_C$, which makes the closed-loop 
+of a controller $C(z)$, which makes the closed-loop 
 system stable for all the uncertainties accumulated in {\sc inputs}.
@@
 % that it is due to lack of precision.
-We obtain the result $false$, meaning that the current precision is insuficient.
+We obtain the result $false$, meaning that the current precision is insufficient.
 Consequently, we increase our precision to $I_b=20,F_b=28$.

### 2016-10-13 paper/paper.tex
Noise formalisation

@@
 
-The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta G_{P}(z)=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$ and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is represented as an additive (output) measurement noise $\nu(z)$.
+The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta G_{P}(z)=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$ and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is represented as an additive (output) measurement noise $\nu(z)$, thus $\hat{Y}(z)=Y(z)+\nu(z)$.
+The measurement noise $\nu(k)$ is enough for represent both quantization noises ($\nu_{1}$ and $\nu_{2}$) what can be obtained reorganizing the equations~\ref{eq:outputfunctions}:
+\begin{equation}
+\label{eq:outputfunctions2}
+\hat{Y}(z)=H_{1}R(z)+H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z),
+\end{equation}
+where $H_{1}R(z)$ is exactly equal to $Y(z)$ without quantization noise effects, thus:
+\begin{equation}
+\nu(z)=H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z).
+\end{equation}
+
+%The system in equation~\ref{controller_plant_tf} (disregarding the $\Delta{G}_{P}(z)$ may be represented by the following difference equation model:
+%\begin{equation}
+%\begin{split}
+%y(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
+%+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M),
+%\end{split}
+%\end{equation}
+%and consequently $\hat{y}(k)$ may be represented by the following difference equation:
+%\begin{equation}
+%\label{eq:differencewithnoise}
+%\begin{split}
+%\hat{y}(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N_{G}}y(k-N_{G})\\
+%+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M_{G}}u(k-M_{G})+\nu(k).
+%\end{split}
+%\end{equation}
+%
+%The z-transform of~\eqref{eq:differencewithnoise} is:
+%\begin{equation}
+%\begin{split}
+%\hat{Y}(z)=(-a_{1}z^{-1}-a_{2}z^{-2}-\cdots-a_{N_{G}}z^{-N_{G}})Y(z)\\
+%+(b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M_{G}}z^{-M_{G}})U(z)+\nu(z),
+%\end{split}
+%\end{equation}
+%dividing both sides by $U(z)$, it is equivalent to:
+%\begin{equation}
+%\frac{\hat{Y}(z)}{U(z)}=[1-D_{G}(z)]G(z)+U(z)D_{G}(z)+\frac{\nu(z)}{U(z)}=G(z)+\Delta{G}_{Q}(z),
+%\end{equation}
+
+%Considering the quantization noise $\nu(k)$ as an output error in discrete plant model, we may represent it as an additive noise in the plant output $y(k)$ resulting in the noisy output $\hat{y}(k)$:
+%\begin{equation}
+%
+%\end{equation}
+
+This noise $\nu(z)$ may represent exactly the same effects that $\nu_{1}(z)$ and $\nu_{2}(z)$ represents together.
 
@@
 
-Let $\hat{C}(z)$ be the transfer function of the digital controller represented using this FWL with integer size $I$ and fractional size $F$.
-We shall denote the FWL domain of coefficients as $\mathbb{R}\langle I,F \rangle$
+Let $\hat{C}(z)$ be the transfer function of the digital controller represented using this FWL with integer size $I$ and fractional
+size $F$.  We shall denote the FWL domain of coefficients as $\mathbb{R}\langle I,F \rangle$
 %Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
@@
 
-Finally, the quantisation noise may be considered a energy-bounded signal (Lemma~\ref{lemma:boundednoise}) and thus $\hat{Y}(z)$ will be bounded and the closed-loop system stable if the conditions in Lemma~\ref{lemma:eq_int_stab} are followed.
+Finally, the quantisation noise spectrum may be considered a energy-bounded (Lemma~\ref{lemma:boundednoise}), and consequently the Parseval's theorem ensures that the quantisation noise is also energy-bounded in time-domain.
+Thus $\hat{Y}(z)$ will be bounded and the closed-loop system stable if the conditions in Lemma~\ref{lemma:eq_int_stab} are followed.
 

### 2016-10-13 paper/paper.tex
Addressed RQ1 and RQ2.

@@
 with few counterexamples and fixed-point precision increases. However, two benchmarks in our set
-did not meet these criteria (marked with $^*$ in Table~\ref{tab:results}) \textcolor{red}{Pascal: Why they did not meet the criteria?}. 
+required too many counterexamples to refine their solution (marked with $^*$ in Table~\ref{tab:results}). 
 In these cases, the interval arithmetic back-end is able to complement the inductive approach
@@
 
-We conclude from these results that the inductive back-end is able to synthesise 
+The median runtime for our benchmark set is 318\,s, implying that half of the controllers
+can be synthesised in 5 minutes or less using our approach. Overall the average synthesis
+time amounts to approximately 30 minutes. With respect to RQ2 we consider
+these times short enough to be of practical use to control engineers.
+Regarding RQ1 we further conclude that the inductive back-end is able to synthesise 
 stable controllers in the $12$ out of $15$ benchmarks, and can be complemented using 
@@
 conjectures fail. Both back-ends together enabled controller synthesis for $14$ 
-out of $15$ benchmarks within reasonable time frames.  For the 1 remaining benchmark
-our approach failed to synthesise a stable controller in the requested time limits.
-This can be addressed by either increasing the fixed point word widths considered or
-using floating point arithmetic instead. 
+out of $15$ benchmarks.  For the 1 remaining benchmark our approach failed to synthesise
+a stable controller in the requested time limits. This can be addressed by either increasing
+the fixed point word widths considered or using floating point arithmetic instead. 
 \pksay{TODO: Upload full experiments environment including README and result log files to anonymous Google Drive and

### 2016-10-13 paper/paper.tex
spell-checking

--- 2016-10-13 paper/paper.tex
@@
 Given our primary interest in evaluating digital effects in addition to
-stability, we have modeled a digital equivalent of the plant by evaluating
+stability, we have modelled a digital equivalent of the plant by evaluating
 the effects of the quantisers (A/D and D/A converters) as time
@@
 \noindent where $\vec{\beta}$ and $\vec{\alpha}$ are vectors containing the controller's coefficients;  
-similarly $\vec{b}$ and $\vec{a}$ encompas the plant's coefficients;  
+similarly $\vec{b}$ and $\vec{a}$ encompass the plant's coefficients;  
 and $N_{(\cdot)}$ and $M_{(\cdot)}$ denote the number of poles and zeros for the corresponding block.
@@
 \end{equation}
-Due to the nature of the methods used for stability check in this paper, we require that  the parametric errors in the plant have the same polynomial order as the plant itself (other errors are ensured to fulfill this property in our implementation).
+Due to the nature of the methods used for stability check in this paper, we require that  the parametric errors in the plant have the same polynomial order as the plant itself (other errors are ensured to fulfil this property in our implementation).
 
@@
 %
-In figure~\ref{fig:digsystem1}, two sources of uncertainties are considered: parametric uncertainties related to modeling errors, and uncertainties introduced by quantisations in sampling and holding process, {\it i.e.} ADC and DAC conversions.
+In figure~\ref{fig:digsystem1}, two sources of uncertainties are considered: parametric uncertainties related to modelling errors, and uncertainties introduced by quantisations in sampling and holding process, {\it i.e.} ADC and DAC conversions.
 Assuming linearity and independence between these sources, the uncertain model may be rewritten as follows:
@@
 The problem of parametric control synthesis based on stability measures for
-continous Linear Time Invariant (LTI) Single Input-Single Output (SISO)
+continuous Linear Time Invariant (LTI) Single Input-Single Output (SISO)
 systems has been researched for several decades.  On a theoretical level it
@@
 more recent Linear Quadratic Regulator (LQR)~\cite{bemporad2002explicit}
-have been used in several studies with increasing degrees of succes to
+have been used in several studies with increasing degrees of success to
 ensure stability.  The latter approach highlights the importance of
@@
 rely on an invariant computation on the discrete system dynamics using
-Semi-Definite Pogramming (SDP).  Whilst the former uses BIBO properties to
+Semi-Definite Programming (SDP).  Whilst the former uses BIBO properties to
 determine stability, the latter uses Lyapunov-based quadratic invariants. 
@@
 from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from~\cite{daes20161}
-whilst enhancing the procedure by evaluating the quantaization effects of
+whilst enhancing the procedure by evaluating the quantization effects of
 the Hardware interfaces (ADC/DAC) to obtain an accurate discrete time FWL
@@
 digital controllers along with a model of their physical environment.
-We have also modeled a digital equivalent of the physical plant by evaluating the 
+We have also modelled a digital equivalent of the physical plant by evaluating the 
 effects of the quantisers (A/D and D/A converters) as time discretisation elements 

### 2016-10-13 paper/paper.tex
Fixed overlay in CEGIS figure.

@@
 \centering
-\resizebox{.7\textwidth}{!}{
+\resizebox{.8\textwidth}{!}{
  \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
@@
    \&;\\
-   \node[fill=yellow!20] (synth) {{\sc Synthesise}};
+   \node[fill=gray!20] (synth) {{\sc Synthesise}};
    \&
@@
 	label={\sc Verify},] (verif) {};
-   \node[fill=yellow!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc ~Uncertainty~~~~}};
-   \node[fill=yellow!20] (verif2) at ([xshift=2cm]verif.center) {{\sc ~~~~~Precision~~~}};
+   \node[fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc ~Uncertainty~~~~}};
+   \node[fill=gray!20] (verif2) at ([xshift=2cm]verif.center) {{\sc ~~~~~Precision~~~}};
    } 
-   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
+   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
    %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
@@
    \path
-    ([yshift=2em]synth.east) edge node {Candidate solution} ([yshift=2em]verif1.west)
+    ([yshift=2em]synth.east) edge node[xshift=-0.5em] {Candidate solution} ([yshift=2em]verif1.west)
     ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east)

### 2016-10-13 paper/paper.tex
discretization -> discretisation uniformly

--- 2016-10-13 paper/paper.tex
@@
 
-For this purpose, the design procedure is based on a discretized model for a continuous plant.
+For this purpose, the design procedure is based on a discretised model for a continuous plant.
 Considering only transfer function models, we are interested in a $z$-domain transfer function that considers all the aspects about the continuous plant ($G(s)$) and the sampling and hold process.
@@
 Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it
-i.e.}, a continuous model of the plant must be discretized to obtain the
+i.e.}, a continuous model of the plant must be discretised to obtain the
 discrete equivalent coefficients via ZOH
-discretization.
+discretisation.
 
@@
 
-Although there are several discretization methods available
+Although there are several discretisation methods available
 in the literature~\cite{Franklin15}, the zero-order hold (ZOH)
-discretization is more suitable for representing the sample and hold
-processes that are typically employed in complex systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretization
+discretisation is more suitable for representing the sample and hold
+processes that are typically employed in complex systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretisation
 models the exact effect of sampling and DAC interpolation over the plant.
@@
 
-%\noindent where $G(z)$ is the discretized nominal plant model and
+%\noindent where $G(z)$ is the discretised nominal plant model and
 %$\Delta{G(z)}$ is the additive uncertainty, which is related to parametric
@@
 Given the use of fixed-point arithmetic, 
-we need to examine the effect of discretization during these operations.
+we need to examine the effect of discretisation during these operations.
 Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
@@
 %
-However, given a real plant $\hat{G}(z)$, and a discretizing function
+However, given a real plant $\hat{G}(z)$, and a discretising function
 \begin{align}
@@
 implementations/synthesis of LTI digital
-controllers~\cite{das2013lqr,ghosh2013fpga} focus on time discretization,
+controllers~\cite{das2013lqr,ghosh2013fpga} focus on time discretisation,
 failing to account for these error-inducing effects and can therefore result
@@
 a continuous space.  This situation demands the inclusion of formal methods
-to verify the effects of space discretization on the implementation of the
+to verify the effects of space discretisation on the implementation of the
 controller.

### 2016-10-13 paper/paper.tex
synthesize -> synthesise

@@
 find a parametric solution for a digital controller given as a continuous
-plant specification, in order to synthesize the controller implementation.
+plant specification, in order to synthesise the controller implementation.
 
@@
 
-The digital controllers synthesized in this paper are typically used in closed loops with continuous (and physical) plants.
-Thus, the proposed approach has to consider dynamics of continuous parts of system ({\it e.g.}, plant) and discrete parts ({\it e.g.}, digital controller), {\it i.e.} the synthesized controller has to consider the issues related to the hybrid systems studies.
+The digital controllers synthesised in this paper are typically used in closed loops with continuous (and physical) plants.
+Thus, the proposed approach has to consider dynamics of continuous parts of system ({\it e.g.}, plant) and discrete parts ({\it e.g.}, digital controller), {\it i.e.} the synthesised controller has to consider the issues related to the hybrid systems studies.
 
@@
 
-Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
+Since the controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
 domain,
@@
 	\item RQ1 \textbf{(sanity check)} which results does our CEGIS approach to FWL controller synthesis 
-	obtain upon synthesizing/verifying benchmarks that compose the specified suite?
+	obtain upon synthesising/verifying benchmarks that compose the specified suite?
   \item RQ2 \textbf{(performance)} does the CEGIS approach provide a feasible solution in reasonable time

### 2016-10-13 paper/paper.tex
hscc17

--- 2016-10-13 paper/paper.tex
@@
 \title{
-Sound Automated Synthesis of Digital Controllers
+Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants
 %Counterexample-guided Synthesis of Closed-loop Digital Control Systems
@@
 
-For this purpose, the design procedure is based on a discretised model for a continuous plant.
+For this purpose, the design procedure is based on a discretized model for a continuous plant.
 Considering only transfer function models, we are interested in a $z$-domain transfer function that considers all the aspects about the continuous plant ($G(s)$) and the sampling and hold process.
@@
 Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it
-i.e.}, a continuous model of the plant must be discretised to obtain the
+i.e.}, a continuous model of the plant must be discretized to obtain the
 discrete equivalent coefficients via ZOH
-discretisation.
+discretization.
 
@@
 
-Although there are several discretisation methods available
+Although there are several discretization methods available
 in the literature~\cite{Franklin15}, the zero-order hold (ZOH)
-discretisation is more suitable for representing the sample and hold
-processes that are typically employed in complex systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretisation
+discretization is more suitable for representing the sample and hold
+processes that are typically employed in complex systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretization
 models the exact effect of sampling and DAC interpolation over the plant.
@@
 
+\red{[Add remark on bound (q/2) for signal. We need a bounded signal to be able to leverage BIBO stability results. ]}
+
 \begin{mylemma}{\cite{Bessa16,fadali}}
@@
 
-%\noindent where $G(z)$ is the discretised nominal plant model and
+%\noindent where $G(z)$ is the discretized nominal plant model and
 %$\Delta{G(z)}$ is the additive uncertainty, which is related to parametric
@@
 Given the use of fixed-point arithmetic, 
-we need to examine the effect of discretisation during these operations.
+we need to examine the effect of discretization during these operations. 
 Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
@@
 %
-However, given a real plant $\hat{G}(z)$, and a discretising function
+However, given a real plant $\hat{G}(z)$, and a discretizing function
 \begin{align}
@@
 implementations/synthesis of LTI digital
-controllers~\cite{das2013lqr,ghosh2013fpga} focus on time discretisation,
+controllers~\cite{das2013lqr,ghosh2013fpga} focus on time discretization,
 failing to account for these error-inducing effects and can therefore result
@@
 a continuous space.  This situation demands the inclusion of formal methods
-to verify the effects of space discretisation on the implementation of the
+to verify the effects of space discretization on the implementation of the
 controller.

### 2016-10-13 paper/paper.tex
describe each column of Table 1

--- 2016-10-13 paper/paper.tex
@@
 We outline the runtimes required to synthesise a stable controller for each
-benchmark in Table~\ref{tab:results}. For the majority of our benchmarks the conjecture explained
+benchmark in Table~\ref{tab:results}. Here, \textit{Plant} is the discrete or 
+continuous plant model, \textit{Benchmark} is the name of the employed benchmark,
+\textit{I} and \textit{F} represent the number of integer and fractional bits of the 
+stable controller, respectively, while \textit{Time} represents the total time 
+(in seconds) to synthesise a stable controller for the given plant.
+
+For the majority of our benchmarks the conjecture explained
 in section~\ref{synthesis-elements}  holds and the inductive back-end is able to find a stable

### 2016-10-13 paper/paper.tex
Rephrased generic description of experimental process.

@@
 \vspace{1ex}
-\caption{DSVerifier Verification Flow.}
+\caption{Synthesis process using DSVerifier and the CBMC CEGIS module.}
 \label{DSVerifier_process}
@@
 
-Given a model $(\hat{C}(z),\hat{G}(z), \mathbb{R}\langle I,F \rangle)$,
+Given a model for a plant for which to synthesize a controller,
 provided in an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
-non-deterministic model to represent the plant family $\mathfrak{G}(z)$
-(Step A), and a transfer function $f$ represented by Eq.~\ref{FWL_tf} (step B) to
-calculate the implementation $f(\hat{C}(z)) \rightarrow \tilde C(z)$ of the
-controller (step C).  Finally DSVerifier builds an intermediate ANSI-C code
-for the digital system implementation, which is used as input for the
-model-checker (Step D).
-
-This intermediate ANSI-C code model $(\tilde C(z),\mathfrak{G}(z),\phi)$
-containing a specification $\phi$ for the verification properties ({\it
-i.e.}, robust stability) is provided to CBMC's~\cite{ClarkeKL04} integrated
-CEGIS synthesis module, where $\tilde C(z)$ is marked as input variable to
-synthesise.  If any property violation is found, then
-a counterexample is reported, which contains system inputs or
-parametric deviations $\Delta{G}$ that lead the system to a failure.  
-This information allows the CEGIS module to refine its search for a stable
-controller, which we explain in detail in section~\ref{synthesiser-general}.
-A successful verification result is reported if the system is safe with
-respect to $\phi$.  In particular, the stability verification is complete
-and sound, since it does not depend on system inputs and outputs.  In the
-case of stability, the specification $\phi$ consists in a number of
-assumptions on the polynomial coefficients, following Jury's Criteria, as
-well as the restrictions set in the representation of these coefficients by
-the function $f$ (cf.~Eq.~\eqref{FWL_tf}).
+non-deterministic model to represent the plant family (Step A), and a transfer
+function $f$ represented by Eq.~\ref{FWL_tf} (step B) to calculate the parameters
+of the controller to be synthesized (step C).  Finally DSVerifier builds an
+intermediate ANSI-C code for the digital system implementation, which is used as
+input for the controller synthesiser (Step D).
+
+This intermediate ANSI-C code model contains a specification $\phi$ for the
+verification properties ({\it i.e.}, robust stability) and is provided to
+CBMC's~\cite{ClarkeKL04} integrated Counterexample-Guided Inductive Synthesis
+(CEGIS) module, where the controller is marked as input variable to synthesize.
+The properties specified in the ANSI-C code model can only be satisfied if CEGIS
+synthesizes controller coefficients satisfying $\phi$. CEGIS employs an iterative,
+counterexample-guided refinement process which is explained in detail in
+section~\ref{synthesiser-general}. A successful synthesis result is reported if
+CEGIS generates a controller which is safe with respect to $\phi$.  In particular,
+the ANSI-C code model guarantees that a synthesized solution is complete
+and sound with respect to stability property $\phi$, since it does not depend on
+system inputs and outputs.  In the case of stability, the specification $\phi$
+consists in a number of assumptions on the polynomial coefficients, following
+Jury's Criteria, as well as the restrictions set in the representation of these
+coefficients by the function $f$ (cf.~Eq.~\eqref{FWL_tf}).
 

### 2016-10-13 paper/paper.tex
minor changes

--- 2016-10-13 paper/paper.tex
@@
 
-For the majority of our benchmarks the conjecture explained
+For the majority of our benchmarks, the conjecture explained
 in section~\ref{synthesis-elements}  holds and the inductive back-end is able to find a stable
 solution in less than one minute.  This is possible if the inductive solutions need to be refined
-with few counterexamples and fixed-point precision increases. However, two benchmarks in our set
+with few counterexamples and fixed-point precision increases. However, $2$ benchmarks in our set
 required too many counterexamples to refine their solution (marked with $^*$ in Table~\ref{tab:results}). 
@@
 interval back-end timing out on the majority of our benchmarks.  Table~\ref{tab:results} only
-lists the faster of the two back-ends for each benchmark, which in 12 out of 14 cases is the inductive
+lists the faster of the two back-ends for each benchmark, which in $12$ out of $14$ cases is the inductive
 back-end.

### 2016-10-13 paper/paper.tex
move running example section

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Running Example} \label{sec:running-ex}
-
-In order to exploit the present approach full potential, a dynamical plant that can
-present physical components must be considered.  However, a discrete plant
-model can also demonstrate some benefits of the present approach, which
-considers FWL effects in the digital controller implementation.  In
-particular, a classical cruise control example is extracted from the
-literature~\cite{Astrom08}, where the discrete plant model (with time step
-of $0.2$s) is represented by the following z-expression:
-%
-\begin{equation}
-\label{Eq:running-example-plant}
-G\left(z\right) := \frac{0.0264}{z-0.9998}.
-\end{equation}
-
-Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16}
-has designed a high-performance controller, which is characterised by the
-following z-domain transfer function:
-%
-\begin{equation}
-\label{Eq:running-example-controller}
-C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
-\end{equation}
-%
-The authors claim that this controller $C(z)$ stabilizes the closed-loop
-system for the discrete plant model $G(z)$.  However, if implementation
-aspects are considered during verification ({\it e.g.}, fixed-point
-arithmetic and word-length), then this closed-loop system becomes unstable.
-%
-Indeed, the actual implementation of $C(z)$ using \param{4}{16}
-implementation format ({\it i.e.}, $4$ bits for the integer part and $16$
-bits for the fractional part) can be represented by the following
-expression:
-%
-\begin{equation}
-\label{Eq:running-example-controller-quantized}
-C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
-{+}1.895996}{z^2{-}1.843994z+0.849594},
-\end{equation} 
-%
-which makes the system unstable in closed-loop using fixed-point arithmetic
-and the typical series loop configuration, where $C_{q}\left(z\right)$ and
-$G\left(z\right)$ are in the forward path.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %\section{Modelling Errors}
@@
 
-\subsection{Program synthesis for the running example}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Illustrative Example} \label{sec:running-ex}
+
+In order to exploit the present approach full potential, a dynamical plant that can
+present physical components must be considered.  However, a discrete plant
+model can also demonstrate some benefits of the present approach, which
+considers FWL effects in the digital controller implementation.  In
+particular, a classical cruise control example is extracted from the
+literature~\cite{Astrom08}, where the discrete plant model (with time step
+of $0.2$s) is represented by the following z-expression:
+%
+\begin{equation}
+\label{Eq:running-example-plant}
+G\left(z\right) := \frac{0.0264}{z-0.9998}.
+\end{equation}
+
+Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16}
+has designed a high-performance controller, which is characterised by the
+following z-domain transfer function:
+%
+\begin{equation}
+\label{Eq:running-example-controller}
+C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
+\end{equation}
+%
+The authors claim that this controller $C(z)$ (Eq.~\eqref{Eq:running-example-plant}) 
+stabilizes the closed-loop system for the discrete plant model $G(z)$ (Eq.~\ref{Eq:running-example-controller}).  
+However, if implementation aspects are considered during verification ({\it e.g.}, fixed-point
+arithmetic and word-length), then this closed-loop system becomes unstable.
+%
+Indeed, the actual implementation of $C(z)$ using \param{4}{16}
+implementation format ({\it i.e.}, $4$ bits for the integer part and $16$
+bits for the fractional part) can be represented by the following
+expression:
+%
+\begin{equation}
+\label{Eq:running-example-controller-quantized}
+C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
+{+}1.895996}{z^2{-}1.843994z+0.849594},
+\end{equation} 
+%
+which makes the system unstable in closed-loop using fixed-point arithmetic
+and the typical series loop configuration, where $C_{q}\left(z\right)$ and
+$G\left(z\right)$ are in the forward path.
+
+\subsubsection{Program synthesis for the illustrative example}
 We will illustrate our synthesis approach on the running example 

### 2016-10-13 paper/paper.tex
review Overview of the Synthesis Process using DSVerifier

@@
 %------------------------------------
-\subsection{Synthesis Process using DSVerifier}
+\subsection{Overview of the Synthesis Process using DSVerifier}
 \label{verification-flow}
@@
 
-The full synthesis process is illustrated in Fig.~\ref{DSVerifier_process};
+An overview of the synthesis process is illustrated in Fig.~\ref{DSVerifier_process};
 a detailed description of DSVerifier tool can be found in~\cite{IsmailBCFF15}.
@@
 provided in an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
-non-deterministic model to represent the plant family (Step A), and a transfer
-function $f$ represented by Eq.~\ref{FWL_tf} (step B) to calculate the parameters
-of the controller to be synthesized (step C).  Finally DSVerifier builds an
-intermediate ANSI-C code for the digital system implementation, which is used as
-input for the controller synthesiser (Step D).
+non-deterministic model to represent the plant family (Step A), and formulates a 
+function (step B) using implementation details provided from Steps $2$ and $3$ 
+to calculate the parameters of the controller to be synthesized (step C).  
+Finally DSVerifier builds an intermediate ANSI-C code for the digital system 
+implementation, which is used as input for the controller synthesiser (Step D).
 
@@
 Jury's Criteria, as well as the restrictions set in the representation of these
-coefficients by the function $f$ (cf.~Eq.~\eqref{FWL_tf}).
-
+coefficients.
+
+% by the function $f$ (cf.~Eq.~\eqref{FWL_tf})
 %In Step A, DSVerifier constructs a non-deterministic model to represent the

### 2016-10-13 paper/paper.tex
review results

@@
 interval back-end timing out on the majority of our benchmarks.  Table~\ref{tab:results} only
-lists the faster of the two back-ends for each benchmark, which in $12$ out of $14$ cases is the inductive
+lists the faster of the two back-ends for each benchmark, which in $12$ out of $15$ benchmarks is the inductive
 back-end.
@@
 \centering
-\begin{tabular}{c | l r r | r l}
-Plant & Benchmark                  & $I$ & $F$ & Time    & \\\cline{1-5}
-$G_1$ & CruiseControl02            &   4 &  16 & 17\,s   & \\
-$G_1$ & CruiseControl02$^\dagger$  &   4 &  16 & 46\,s   & \\
-$G_2$ & SpringMassDamper           &  15 &  16 & 28\,s   & \\
-$G_2$ & SpringMassDamper$^\dagger$ &  15 &  16 & \xmark  & \\
-$G_3$ & SatelliteB2                &   3 &   7 & 7\,s    & \\
-$G_3$ & SatelliteB2$^\dagger$      &   3 &   7 & 6601\,s & \tbmark\\
-$G_3$ & SatelliteC2                &   3 &   5 & 2\,s    & \\
-$G_3$ & SatelliteC2$^\dagger$      &   3 &   5 & 76\,s   & \tbmark\\
-$G_4$ & a\_ST1\_IMPL1              &  16 &   4 & 2704\,s & \\
-$G_4$ & a\_ST1\_IMPL2              &  16 &   8 & 538\,s  & \\
-$G_4$ & a\_ST1\_IMPL3              &  16 &  12 & 12\,s   & \\
-$G_4$ & a\_ST2\_IMPL1              &  16 &   4 & 318\,s  & \\
-$G_4$ & a\_ST2\_IMPL2              &  16 &   8 & 967\,s  & \\
-$G_4$ & a\_ST2\_IMPL3              &  16 &  12 & 9798\,s & \\
-$G_4$ & a\_ST3\_IMPL1              &  16 &   4 & 6304\,s & \\
+\begin{tabular}{c | c | l | r r | r l}
+\# & Plant & Benchmark                  & $I$ & $F$ & Time    & \\\cline{1-6}
+1  & $G_1$ & CruiseControl02            &   4 &  16 & 17\,s   & \\
+2  & $G_1$ & CruiseControl02$^\dagger$  &   4 &  16 & 46\,s   & \\
+3  & $G_2$ & SpringMassDamper           &  15 &  16 & 28\,s   & \\
+4  & $G_2$ & SpringMassDamper$^\dagger$ &  15 &  16 & \xmark  & \\
+5  & $G_3$ & SatelliteB2                &   3 &   7 & 7\,s    & \\
+6  & $G_3$ & SatelliteB2$^\dagger$      &   3 &   7 & 6601\,s & \tbmark\\
+7  & $G_3$ & SatelliteC2                &   3 &   5 & 2\,s    & \\
+8  & $G_3$ & SatelliteC2$^\dagger$      &   3 &   5 & 76\,s   & \tbmark\\
+9  & $G_4$ & a\_ST1\_IMPL1              &  16 &   4 & 2704\,s & \\
+10 & $G_4$ & a\_ST1\_IMPL2              &  16 &   8 & 538\,s  & \\
+11 & $G_4$ & a\_ST1\_IMPL3              &  16 &  12 & 12\,s   & \\
+12 & $G_4$ & a\_ST2\_IMPL1              &  16 &   4 & 318\,s  & \\
+13 & $G_4$ & a\_ST2\_IMPL2              &  16 &   8 & 967\,s  & \\
+14 & $G_4$ & a\_ST2\_IMPL3              &  16 &  12 & 9798\,s & \\
+15 & $G_4$ & a\_ST3\_IMPL1              &  16 &   4 & 6304\,s & \\
 \end{tabular}
@@
 
-The median runtime for our benchmark set is 318\,s, implying that half of the controllers
-can be synthesised in 5 minutes or less using our approach. Overall the average synthesis
-time amounts to approximately 30 minutes. With respect to RQ2 we consider
+The median runtime for our benchmark set is $318$\,s, implying that half of the controllers
+can be synthesised in $5$ minutes or less using our present approach. Overall the average synthesis
+time amounts to approximately $30$ minutes. With respect to RQ2 we consider
 these times short enough to be of practical use to control engineers.
@@
 conjectures fail. Both back-ends together enabled controller synthesis for $14$ 
-out of $15$ benchmarks.  For the 1 remaining benchmark our approach failed to synthesise
+out of $15$ benchmarks.  For the $1$ remaining benchmark our approach failed to synthesise
 a stable controller in the requested time limits. This can be addressed by either increasing

### 2016-10-13 paper/paper.tex
review comment
coefficient representation (first half)

--- 2016-10-13 paper/paper.tex
@@
 \label{controller_plant_tf}
-C(z)&=\frac{\beta_{0}+\beta_{1}z^{-1}+...+\beta_{M_C}z^{-M_C}}{\alpha_{0}+\alpha_{1}z^{-1}+...+\alpha_{N_C}z^{-N_C}}, \\
+C(z)&=\frac{C_n(z)}{C_d{z}}=\frac{\beta_{0}+\beta_{1}z^{-1}+...+\beta_{M_C}z^{-M_C}}{\alpha_{0}+\alpha_{1}z^{-1}+...+\alpha_{N_C}z^{-N_C}}, \\
 %\label{plant_tf}
-G(z)&=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
+G(z)&=\frac{G_n(z)}{G_d{z}}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
 \end{align}
@@
 
-Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (\emph{i.e.} $\Delta{G}_p(s)$), errors in the numeric calculations, or roundoffs in the quantization.
-These uncertainties may be parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
-\begin{equation}
-\hat{G}(z)=G(z)+\Delta G(z),
+Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$), errors in the numeric calculations, or roundoffs in the quantization.
+These uncertainties may be parametrically expressed by additive terms, resulting in a uncertain model $\hat{G}(z)$, such that:
+\begin{equation}
+\hat{G}(z)=\frac{G_n(z)+\Delta G_n(z)}{G_d(z)+\Delta G_d(z)},
 \end{equation}
@@
 
-The vector of parametric coefficient uncertainties $\Delta{p}$ of $\Delta{G}_p(z)$ is defined by:
-\begin{equation}
-\Delta{\vec{p}}=\begin{bmatrix}
-\hat{b_{0}} - b_{0}\\
-\hat{b_{1}} - b_{1}\\
-\vdots \\
-\hat{b}_{M_G} - b_{M_{G}}\\
-\hat{a_{0}} - a_{0}\\
-\hat{a_{1}} - a_{1}\\
-\vdots\\
-\hat{a}_{N_G} - a_{N_{G}}\\
-\end{bmatrix}=\begin{bmatrix}
-\vec{\hat{b}}\\
-\vec{\hat{a}}
-\end{bmatrix}-\begin{bmatrix}
-\vec{b}\\
-\vec{a}
-\end{bmatrix}
-\label{eq:uncertainty}
-\end{equation}
-
-A typical hybrid system, with a continuous plant and a discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$ , $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.
+In order to simplify the notations in this paper, we will use a notation based on the coefficients of the polynomials.
+Let $\mathcal{P}^{N}$ be a polynomial domain of order $N$
+Let $P \in \mathcal{P}^{M,N}$ be a rational polynomial $\frac{P_n}{P_d} : P_n \in \mathcal{P}^{M} \wedge P_d \in \mathcal{P}^{N}$. There is a vector of coefficients 
+\begin{equation}
+\vec{P} \in \mathbb{R}^{N+M+2}=[n_{0}\ n_{1}\ \hdots \ n_{M}\ d_{0}\ d_{1}\ \hdots\ d_{N}\ ]^T
+\label{eq:coefficients}
+\end{equation}
+with uncertainty
+\begin{equation}
+\Delta{\vec{P}}=[\Delta{n}_{0}\ \Delta{n}_{1}\ \hdots \ \Delta{n}_{M}\ \Delta{d}_{0}\ \Delta{d}_{1}\ \hdots\ \Delta{d}_{N}\ ]^T
+\label{eq:coefficients}
+\end{equation}
+Then $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$.
+In the following we may use either notation to represent the functions $G(z)$, $C(z)$, and their respective uncertainties.\\
+
+%\begin{equation}
+%\Delta{\vec{p}}=\begin{bmatrix}
+%\hat{b_{0}} - b_{0}\\
+%\hat{b_{1}} - b_{1}\\
+%\vdots \\
+%\hat{b}_{M_G} - b_{M_{G}}\\
+%\hat{a_{0}} - a_{0}\\
+%\hat{a_{1}} - a_{1}\\
+%\vdots\\
+%\hat{a}_{N_G} - a_{N_{G}}\\
+%\end{bmatrix}=\begin{bmatrix}
+%\vec{\hat{b}}\\
+%\vec{\hat{a}}
+%\end{bmatrix}-\begin{bmatrix}
+%\vec{b}\\
+%\vec{a}
+%\end{bmatrix}
+%\label{eq:uncertainty}
+%\end{equation}
+
+A typical hybrid system, with a continuous plant and a discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta \vec{G}_{P}^s$ , $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.
 
@@
 
-The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta G_{P}(z)=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$ and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is represented as an additive (output) measurement noise $\nu(z)$, thus $\hat{Y}(z)=Y(z)+\nu(z)$.
+The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta \vec{G}_{P}$
+%=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$
+and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is represented as an additive (output) measurement noise $\nu(z)$, thus $\hat{Y}(z)=Y(z)+\nu(z)$.
 The measurement noise $\nu(k)$ is enough for represent both quantization noises ($\nu_{1}$ and $\nu_{2}$) what can be obtained reorganizing the equations~\ref{eq:outputfunctions}:
@@
 \label{eq:complete_unc_model}
-\hat{G}(z)=G(z)+\Delta G_{P}(z)+\Delta G_{Q}(z),
-\end{equation}
-where $\Delta G_{P}(z)$ is the term that corresponds to the parametric uncertainties and $\Delta G_{Q}(z)$ is the term that reflects the quantisation effects on the plant model.
+\vec{\hat{G}}=\vec{G}+\Delta \vec{G}_{P}+\Delta \vec{G}_{Q},
+\end{equation}
+where $\Delta \vec{G}_{P}$ is the term that corresponds to the parametric uncertainties and $\Delta \vec{G}_{Q}$ is the term that reflects the quantisation effects on the plant model.
 %\red{[next figure is a bit unnecessary, does not ad much to the previous one.]} Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.
@@
 In order to obtain a sound synthesis of the digital controller, the effect of FWL implementation in controller and quantisation noises in closed loop system have to be considered.
-Considering that the quantizer $Q1$ is the source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise $\nu_{2}$, the following equation is written for the system in Figure~\ref{fig:sampledsystem}, considering the parametric uncertainties $\Delta G(z)$ and the FWL effects on controller ($\hat{C}(z)$):
+Considering that the quantizer $Q1$ is the source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise $\nu_{2}$, the following equation is written for the system in Figure~\ref{fig:sampledsystem}, considering the parametric uncertainties $\Delta \vec{G}(z)$ and the FWL effects on controller ($\hat{C}(z)$):
 \begin{equation}
@@
 \label{lemma:eq_int_stab} 
-A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with a FWL implementation of the digital controller $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete model of the plant $\hat{G}(z)=G(z)+\Delta G_{P}(z)+\Delta G_{Q}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and only if:
+A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with a FWL implementation of the digital controller $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete model of the plant $\vec{\hat{G}}=\vec{G}+\Delta \vec{G}_{P}+\Delta \vec{G}_{Q}\Rightarrow \hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and only if:
 \begin{itemize}
@@
 \vspace{1ex}
-\caption{Synthesis process using DSVerifier and the CBMC CEGIS module.}
+\caption{DSVerifier Verification Flow.}
 \label{DSVerifier_process}
@@
 
-Given a model for a plant for which to synthesize a controller,
+Given a model $(\hat{C}(z),\hat{G}(z), \mathbb{R}\langle I,F \rangle)$,
 provided in an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
-non-deterministic model to represent the plant family (Step A), and a transfer
-function $f$ represented by Eq.~\ref{FWL_tf} (step B) to calculate the parameters
-of the controller to be synthesized (step C).  Finally DSVerifier builds an
-intermediate ANSI-C code for the digital system implementation, which is used as
-input for the controller synthesiser (Step D).
-
-This intermediate ANSI-C code model contains a specification $\phi$ for the
-verification properties ({\it i.e.}, robust stability) and is provided to
-CBMC's~\cite{ClarkeKL04} integrated Counterexample-Guided Inductive Synthesis
-(CEGIS) module, where the controller is marked as input variable to synthesize.
-The properties specified in the ANSI-C code model can only be satisfied if CEGIS
-synthesizes controller coefficients satisfying $\phi$. CEGIS employs an iterative,
-counterexample-guided refinement process which is explained in detail in
-section~\ref{synthesiser-general}. A successful synthesis result is reported if
-CEGIS generates a controller which is safe with respect to $\phi$.  In particular,
-the ANSI-C code model guarantees that a synthesized solution is complete
-and sound with respect to stability property $\phi$, since it does not depend on
-system inputs and outputs.  In the case of stability, the specification $\phi$
-consists in a number of assumptions on the polynomial coefficients, following
-Jury's Criteria, as well as the restrictions set in the representation of these
-coefficients by the function $f$ (cf.~Eq.~\eqref{FWL_tf}).
+non-deterministic model to represent the plant family $\mathfrak{G}(z)$
+(Step A), and a transfer function $FWL$ represented by Eq.~\ref{FWL_tf} (step B) to
+calculate the implementation $FWL(\hat{C}(z)) \rightarrow \tilde C(z)$ of the
+controller (step C).  Finally DSVerifier builds an intermediate ANSI-C code
+for the digital system implementation, which is used as input for the
+model-checker (Step D).
+
+This intermediate ANSI-C code model $(\tilde C(z),\mathfrak{G}(z),\phi)$
+containing a specification $\phi$ for the verification properties ({\it
+i.e.}, robust stability) is provided to CBMC's~\cite{ClarkeKL04} integrated
+CEGIS synthesis module, where $\tilde C(z)$ is marked as input variable to
+synthesise.  If any property violation is found, then
+a counterexample is reported, which contains system inputs or
+parametric deviations $\Delta{\vec{G}}$ that lead the system to a failure.  
+This information allows the CEGIS module to refine its search for a stable
+controller, which we explain in detail in section~\ref{synthesiser-general}.
+A successful verification result is reported if the system is safe with
+respect to $\phi$.  In particular, the stability verification is complete
+and sound, since it does not depend on system inputs and outputs.  In the
+case of stability, the specification $\phi$ consists in a number of
+assumptions on the polynomial coefficients, following Jury's Criteria, as
+well as the restrictions set in the representation of these coefficients by
+the function $f$ (cf.~Eq.~\eqref{FWL_tf}).
 
@@
 %not depend on system outputs and inputs.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Running Example} \label{sec:running-ex}
+
+In order to exploit the present approach full potential, a dynamical plant that can
+present physical components must be considered.  However, a discrete plant
+model can also demonstrate some benefits of the present approach, which
+considers FWL effects in the digital controller implementation.  In
+particular, a classical cruise control example is extracted from the
+literature~\cite{Astrom08}, where the discrete plant model (with time step
+of $0.2$s) is represented by the following z-expression:
+%
+\begin{equation}
+\label{Eq:running-example-plant}
+G\left(z\right) := \frac{0.0264}{z-0.9998}.
+\end{equation}
+
+Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16}
+has designed a high-performance controller, which is characterised by the
+following z-domain transfer function:
+%
+\begin{equation}
+\label{Eq:running-example-controller}
+C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
+\end{equation}
+%
+The authors claim that this controller $C(z)$ stabilizes the closed-loop
+system for the discrete plant model $G(z)$.  However, if implementation
+aspects are considered during verification ({\it e.g.}, fixed-point
+arithmetic and word-length), then this closed-loop system becomes unstable.
+%
+Indeed, the actual implementation of $C(z)$ using \param{4}{16}
+implementation format ({\it i.e.}, $4$ bits for the integer part and $16$
+bits for the fractional part) can be represented by the following
+expression:
+%
+\begin{equation}
+\label{Eq:running-example-controller-quantized}
+C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
+{+}1.895996}{z^2{-}1.843994z+0.849594},
+\end{equation} 
+%
+which makes the system unstable in closed-loop using fixed-point arithmetic
+and the typical series loop configuration, where $C_{q}\left(z\right)$ and
+$G\left(z\right)$ are in the forward path.
 
@@
 \tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_b \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_b \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_b \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_b \hat{a}_{N_G})z^{-N_G}} \nonumber \\
-&=\hat{G}(z)+\Delta{G}_b(z)=G(z)+\Delta{G}_P(z)+\Delta{G}_b(z).
+&\Rightarrow \vec{\tilde G} =\vec{\hat{G}}+\Delta_b{\vec{G}}=\vec{G}+\Delta_P{\vec{G}}+\Delta_b{\vec{G}}.
 \end{align}
@@
 the rounding off effect.  We may encompass all the uncertainty as
-$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_b(z)$.  % Since this value is
+$\Delta{\vec{G}}=\Delta_P{\vec{G}}+\Delta_b{\vec{G}}$.  % Since this value is
 % nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Illustrative Example} \label{sec:running-ex}
-
-In order to exploit the present approach full potential, a dynamical plant that can
-present physical components must be considered.  However, a discrete plant
-model can also demonstrate some benefits of the present approach, which
-considers FWL effects in the digital controller implementation.  In
-particular, a classical cruise control example is extracted from the
-literature~\cite{Astrom08}, where the discrete plant model (with time step
-of $0.2$s) is represented by the following z-expression:
-%
-\begin{equation}
-\label{Eq:running-example-plant}
-G\left(z\right) := \frac{0.0264}{z-0.9998}.
-\end{equation}
-
-Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16}
-has designed a high-performance controller, which is characterised by the
-following z-domain transfer function:
-%
-\begin{equation}
-\label{Eq:running-example-controller}
-C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
-\end{equation}
-%
-The authors claim that this controller $C(z)$ (Eq.~\eqref{Eq:running-example-plant}) 
-stabilizes the closed-loop system for the discrete plant model $G(z)$ (Eq.~\ref{Eq:running-example-controller}).  
-However, if implementation aspects are considered during verification ({\it e.g.}, fixed-point
-arithmetic and word-length), then this closed-loop system becomes unstable.
-%
-Indeed, the actual implementation of $C(z)$ using \param{4}{16}
-implementation format ({\it i.e.}, $4$ bits for the integer part and $16$
-bits for the fractional part) can be represented by the following
-expression:
-%
-\begin{equation}
-\label{Eq:running-example-controller-quantized}
-C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
-{+}1.895996}{z^2{-}1.843994z+0.849594},
-\end{equation} 
-%
-which makes the system unstable in closed-loop using fixed-point arithmetic
-and the typical series loop configuration, where $C_{q}\left(z\right)$ and
-$G\left(z\right)$ are in the forward path.
-
-\subsubsection{Program synthesis for the illustrative example}
+\subsection{Program synthesis for the running example}
 We will illustrate our synthesis approach on the running example 
@@
 We outline the runtimes required to synthesise a stable controller for each
-benchmark in Table~\ref{tab:results}. Here, \textit{Plant} is the discrete or 
-continuous plant model, \textit{Benchmark} is the name of the employed benchmark,
-\textit{I} and \textit{F} represent the number of integer and fractional bits of the 
-stable controller, respectively, while \textit{Time} represents the total time 
-(in seconds) to synthesise a stable controller for the given plant.
-
-For the majority of our benchmarks, the conjecture explained
+benchmark in Table~\ref{tab:results}. For the majority of our benchmarks the conjecture explained
 in section~\ref{synthesis-elements}  holds and the inductive back-end is able to find a stable
 solution in less than one minute.  This is possible if the inductive solutions need to be refined
-with few counterexamples and fixed-point precision increases. However, $2$ benchmarks in our set
+with few counterexamples and fixed-point precision increases. However, two benchmarks in our set
 required too many counterexamples to refine their solution (marked with $^*$ in Table~\ref{tab:results}). 
@@
 interval back-end timing out on the majority of our benchmarks.  Table~\ref{tab:results} only
-lists the faster of the two back-ends for each benchmark, which in $12$ out of $14$ cases is the inductive
+lists the faster of the two back-ends for each benchmark, which in 12 out of 14 cases is the inductive
 back-end.

### 2016-10-13 paper/paper.tex

--- 2016-10-13 paper/paper.tex
@@
 
-\red{[what is the relationship between FWL effects over C, and the parametric uncertainty Delta Gp over the plant?]} 
-\blue{[IB: There is no relationship. We must separate that content in another section?]}
-
 %\textcolor{blue}{[IB: And I propose to exchange the remaining paragraphs by the previous blue]}

### 2016-10-13 paper/paper.tex
Added Google Drive link to experiments.

--- 2016-10-13 paper/paper.tex
@@
 a stable controller in the requested time limits. This can be addressed by either increasing
-the fixed point word widths considered or using floating point arithmetic instead. 
-\pksay{TODO: Upload full experiments environment including README and result log files to anonymous Google Drive and
-provide link here.}
+the fixed point word widths considered or using floating point arithmetic instead. A link
+to the full experimental environment, including scripts to reproduce the experiment, all
+benchmarks and the CEGIS tool is provided in the footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}
 

### 2016-10-13 paper/paper.tex
small fix sec 4.2

@@
 The {\sc synthesise} phase uses BMC to 
-compute a solution ($N_c$,$D_C$). % An important remark is that this 
+compute a solution $C(z)$. % An important remark is that this 
 % controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
@@
 a stable controller in the requested time limits. This can be addressed by either increasing
-the fixed point word widths considered or using floating point arithmetic instead. A link
-to the full experimental environment, including scripts to reproduce the experiment, all
-benchmarks and the CEGIS tool is provided in the footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}
+the fixed point word widths considered or using floating point arithmetic instead. 
+\pksay{TODO: Upload full experiments environment including README and result log files to anonymous Google Drive and
+provide link here.}
 

### 2016-10-13 paper/paper.tex
more coefficient notation

--- 2016-10-13 paper/paper.tex
@@
 
-A typical hybrid system, with a continuous plant and a discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta \vec{G}_{P}^s$ , $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.
+A typical hybrid system, with a continuous plant and a discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta_p \vec{G}_s$ , $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.
 
@@
 	minimum height=1cm,
-        label=\textbf{Plant}] (gs) {{\sc $G(s) + \Delta G_p(s)$}};
+        label=\textbf{Plant}] (gs) {{\sc $G(s) + \Delta_p G_s$}};
    \node[draw=none] (ud) at ([xshift=-2cm,yshift=.15cm]gs)  {$U(s)$};
@@
 
-The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta \vec{G}_{P}$
+The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta_p \vec{G}$
 %=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$
@@
 	minimum height=1cm,
-        label=\textbf{Plant}] (gs) {{\sc $G(z) + \Delta G_{P}(z)$}};
+        label=\textbf{Plant}] (gs) {{\sc $G(z) + \Delta_p \vec{G}$}};
    \node[draw=none] (y) at ([xshift=2cm,yshift=.15cm]gs)  {$Y(z)$};
@@
 \label{eq:complete_unc_model}
-\vec{\hat{G}}=\vec{G}+\Delta \vec{G}_{P}+\Delta \vec{G}_{Q},
-\end{equation}
-where $\Delta \vec{G}_{P}$ is the term that corresponds to the parametric uncertainties and $\Delta \vec{G}_{Q}$ is the term that reflects the quantisation effects on the plant model.
+\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q \vec{G},
+\end{equation}
+where $\Delta_p \vec{G}$ is the term that corresponds to the parametric uncertainties and $\Delta_q \vec{G}$ is the term that reflects the quantisation effects on the plant model.
 %\red{[next figure is a bit unnecessary, does not ad much to the previous one.]} Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.
@@
 In order to obtain a sound synthesis of the digital controller, the effect of FWL implementation in controller and quantisation noises in closed loop system have to be considered.
-Considering that the quantizer $Q1$ is the source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise $\nu_{2}$, the following equation is written for the system in Figure~\ref{fig:sampledsystem}, considering the parametric uncertainties $\Delta \vec{G}(z)$ and the FWL effects on controller ($\hat{C}(z)$):
+Considering that the quantizer $Q1$ is the source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise $\nu_{2}$, the following equation is written for the system in Figure~\ref{fig:sampledsystem}, considering the parametric uncertainties $\Delta \vec{G}$ and the FWL effects on controller ($\hat{C}(z)$):
 \begin{equation}
@@
 \label{lemma:eq_int_stab} 
-A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with a FWL implementation of the digital controller $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete model of the plant $\vec{\hat{G}}=\vec{G}+\Delta \vec{G}_{P}+\Delta \vec{G}_{Q}\Rightarrow \hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and only if:
+A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with a FWL implementation of the digital controller $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete model of the plant $\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q \vec{G} \Rightarrow \hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and only if:
 \begin{itemize}
@@
 
-The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for synthesis of digital controllers able to stabilize closed loop system, considering plant parametric uncertainties ({\it i.e.}, $\Delta G_{P}(z)$), quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital controllers.
-Based on it, the model for plant uncertainty due quantisation noise ({\it i.e.}, $\Delta G_{Q}(z)$) may be disregarded if the conditions on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise is bounded.
+The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for synthesis of digital controllers able to stabilize closed loop system, considering plant parametric uncertainties ({\it i.e.}, $\Delta_p \vec{G}$), quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital controllers.
+Based on it, the model for plant uncertainty due quantisation noise ({\it i.e.}, $\Delta_q \vec{G}$) may be disregarded if the conditions on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise is bounded.
 The quantisation noise is indeed bounded, since the following assumption~\ref{whitenoise} and the Lemmas~\ref{lemma:variance} and~\ref{lemma:boundednoise} are true.
@@
 &f_b (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = x-(x\mod\tilde x) \\
-&FWL_b[P \in \mathcal{P}] = \tilde P \in \mathcal{P}^{n}\langle I_b,F_b \rangle : c_i \in P \wedge \tilde c_i \in \tilde P=f_b(c_i)  \nonumber
+&FWL_b[P \in \mathcal{P}] = \tilde P \in \mathcal{P}^{n}\langle I_b,F_b \rangle : c_i \in \vec{P} \wedge \tilde c_i \in \tilde \vec{P}=f_b(c_i)  \nonumber
 \end{align}
@@
 % \label{digital_controller_tf}
-% \tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
+% \tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_b \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
 % &= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
@@
 \tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_b \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_b \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_b \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_b \hat{a}_{N_G})z^{-N_G}} \nonumber \\
-&\Rightarrow \vec{\tilde G} =\vec{\hat{G}}+\Delta_b{\vec{G}}=\vec{G}+\Delta_P{\vec{G}}+\Delta_b{\vec{G}}.
+&\Rightarrow \vec{\tilde G} =\vec{\hat{G}}+\Delta_b{\vec{G}}=\vec{G}+\Delta_p{\vec{G}}+\Delta_b{\vec{G}}.
 \end{align}
 where $\Delta_b\hat{c}_i=\hat{c}_i\mod \tilde{c}_i$
-and $\Delta{G}_b(z)$ represents the plant uncertainty caused by
+and $\Delta_b{G}$ represents the plant uncertainty caused by
 the rounding off effect.  We may encompass all the uncertainty as
-$\Delta{\vec{G}}=\Delta_P{\vec{G}}+\Delta_b{\vec{G}}$.  % Since this value is
+$\Delta{\vec{G}}=\Delta_p{\vec{G}}+\Delta_b{\vec{G}}$.  % Since this value is
 % nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is

### 2016-10-13 paper/paper.tex
small fix sec 4.2

--- 2016-10-13 paper/paper.tex
@@
 
-There are two approaches for the {\sc verify} phase based on the
-described model.  The first uses interval arithmetic \cite{moore1966interval}
+There are two approaches for the {\sc verify} phase.
+% based on the described model.  
+The first uses interval arithmetic \cite{moore1966interval}
 to represent the coefficients

### 2016-10-13 paper/paper.tex
small fix sec 4.2

@@
 
-In Fig.~\ref{fig:CEGIS}, we illustrate the second approach, which 
+The second approach is illustrated in Fig.~\ref{fig:CEGIS} and 
 uses a two-stage verification such that in the first stage we 

### 2016-10-13 paper/paper.tex
editing sec 4.2

--- 2016-10-13 paper/paper.tex
@@
 % based on the described model.  
-The first uses interval arithmetic \cite{moore1966interval}
+The first approach uses interval arithmetic \cite{moore1966interval}
 to represent the coefficients
@@
 The second approach is illustrated in Fig.~\ref{fig:CEGIS} and 
-uses a two-stage verification such that in the first stage we 
-assume a certain precision \param{I_b}{F_b}  
-followed by checking the soundness of our assumption
-in a second verification stage.
+uses a two-stage verification such that in the first stage it 
+assumes a certain precision \param{I_b}{F_b}, whose 
+soundness is checked in the second verification stage.
 

### 2016-10-13 paper/paper.tex
conclusion

@@
 
-In this study, we have investigated a CEGIS-based approach that uses inductive synthesis 
-in conjunction with a robust closed-loop stability verification algorithm to find a parametric 
-solution for a digital controller given a continuous (or discrete) plant specification.
-In particular, we have exploited the automatic synthesis of correct-by-construction 
-digital controllers along with a model of their physical environment.
-We have also modelled a digital equivalent of the physical plant by evaluating the 
-effects of the quantisers (A/D and D/A converters) as time discretisation elements 
-with quantisation noise. Experimental results show that our
-CEGIS-based approach is able to synthesise stable controllers in most benchmarks
-within reasonable time frames.
+We have presented a CEGIS-based approach that uses inductive synthesis in
+conjunction with a robust algorithm for verifying closed-loop stability to
+compute a parametric solution for a digital controller given a continuous
+(or discrete) plant specification.  This enables us to automatically
+synthesize correct-by-construction digital controllers for a given model of
+their physical environment.  Our approach addresses the effects of the
+quantisers (A/D and D/A converters) as time discretisation elements with
+quantisation noise.  Our experimental results show that our CEGIS-based
+approach is able to synthesise stable controllers in most benchmarks within
+reasonable time frames fully automatically.
+%
 % and can be 
@@
 %Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
-Further studies include the extension of this CEGIS-based approach for different classes of systems
-({\it e.g.}, state-space) and also consider performance requirements while synthesising 
-the digital controller.
+%
+Future work will be the extension of this CEGIS-based approach for different
+classes of systems (e.g., state-space).  We will also consider performance
+requirements while synthesising the digital controller.
 
@@
 %Appendix A
+
 \end{document}

### 2016-10-13 paper/paper.tex
conclusion
Changed median.

--- 2016-10-13 paper/paper.tex
@@
 
-The median runtime for our benchmark set is $318$\,s, implying that half of the controllers
-can be synthesised in $5$ minutes or less using our present approach. Overall the average synthesis
+The median runtime for our benchmark set is $197$\,s, implying that half of the controllers
+can be synthesised in less than $5$ minutes using our present approach. Overall the average synthesis
 time amounts to approximately $30$ minutes. With respect to RQ2 we consider

### 2016-10-13 paper/paper.tex
re-wrote the intro

--- 2016-10-13 paper/paper.tex
@@
 Modern implementations of embedded control have proliferated with the
-availability of low cost devices that can perform simple tasks for linear
-control, spanning many areas such as environmental control and robotic
-manipulations~\cite{astrom1997computer,Franklin15}.  The downside to this
-approach is that in order to achieve low prices, devices are often limited
-in their capabilities, be it a low number of gates in an FPGA or short word
-lengths for microcontrollers.  In most cases, a floating-point implementation
-is not feasible and the system can benefit from the added resolution of a
-fixed-point representation.  The ubiquity of these devices requires that
-they have a robust design that ensures the correct behaviour in a number of
-different environments.
-%
-% For this reason it is
-% necessary to provide design tools that formally verify the correctness
-% of the digital controller.
-
-There has been previous work to formally verify uncertain linear systems
-stability in digital controllers with considerations to the implementation
-aspects ({\it i.e.}, fixed-point arithmetic and word-length)~\cite{Bessa16}. 
-In particular, Bessa {\it et al.} consider finite-word length (FWL) effects
-over digital controllers and also parameter uncertainties in the context of
-verifying the (so-called) robust non-fragile
-stability~\cite{bhattacharyya97}.  However, the authors do not consider the
-compete range of approximations, related to time discretisation, and
-quantisation effects.  As a result, the stability verification method
-proposed by Bessa {\it et al.} is incomplete, given that false alarms can be
-produced due to quantisation effects.  Additionally, the authors do not
-find a parametric solution for a digital controller given as a continuous
-plant specification, in order to synthesise the controller implementation.
-
-Our work makes two major contributions. First, we explore the automatic synthesis 
-of {\em correct-by-construction} digital controllers, which reduces the development
-cost and design time for a number of models.  In particular, we are
-interested in synthesising controllers for {\em hybrid closed-loop systems},
-{\it i.e.}, embedded controllers along with a model of their physical
-environment (the plant), which are {\em stable}.  Due to the complexity of
-such systems, we focus on linear models with known configurations to perform
-parametric synthesis of the controller dynamics.
-
-Second, since the digital control synthesis is performed over a hybrid model, 
-where the plant displays a continuous behaviour and the controller operates in
-both discrete time and state-space, we initially translate the problem into
-a single domain, which represents a bi-simulation of the original dynamics. 
-Given our primary interest in evaluating digital effects in addition to
-stability, we have modelled a digital equivalent of the plant by evaluating
-the effects of the quantisers (A/D and D/A converters) as time
-discretisation elements with quantisation noise.  The resulting closed loop
-system is a program loop working over bit-vectors of fixed-point arithmetic
-with fixed word length.  The deterministic effect of the FWL is considered
-and quantization errors are included in the model as an additive uncertainty, 
-which must be taken into account for the correct synthesis of the robust controller
-for linear systems with parametric uncertainties.
+availability of low-cost devices that can perform highly non-trivial control
+tasks, with impact in numerous application areas such as environmental
+control and robotics~\cite{astrom1997computer, Franklin15}.
+
+Correct control is non-trivial, however. The problem is exacerbated by
+artefacts specific to digital control such as the effects of
+finite-precision arithmetic, time discretisation, and quantisation noise
+introduced by A/D and D/A conversion.  Thus, the programming is a key
+barrier to broad adoption of digital control, and requires considerable
+expertise.
+
+There has been plenty of previous work that aims at \emph{verifying} a given
+controller designed by the engineer.  Recent work can show the stability
+digital controllers with considerations to implementation aspects, i.e.,
+fixed-point arithmetic and the word length used~\cite{Bessa16}.  This work
+exploits advances in bit-accurate verification of C programs to obtain a
+verifier for software-implemented digital control.
+
+By contrast, we propose to leverage very recent step-change in \emph{program
+synthesis}.  Program synthesis engines use a program specification as the
+starting point, and subsequently generate a sequence of candidate programs. 
+The candidate programs are iteratively refined to match the specification
+more closely.  Program synthesisers that implement Counter-Example Guided
+Inductive Synthesis (CEGIS)~\cite{sketch} are now able to generate programs
+for highly non-trivial specifications with a very high degree of automation. 
+Modern CEGIS engines implement combinations of automated testing, genetic
+algorithms and SMT-based automated reasoning~\cite{DBLP:conf/lpar/DavidKL15,
+DBLP:conf/cav/0001A14}.
+
+By applying a state-of-the-art CEGIS engine we are now able to present a
+tool that automatically \emph{generates} digital controllers for a given
+plant model that are correct by construction.  This approach promises to
+reduce the cost and time of development of digital control dramatically, and
+requires considerably less expertise than methodologies driven by
+verification.  Specifically, we synthesise controllers for hybrid
+closed-loop systems, i.e., software-implemented embedded controllers along
+with a model of their physical environment (the plant), that are
+\emph{stable}.  Due to the complexity of such systems, we focus on linear
+models with known configurations to perform parametric synthesis of the
+controller dynamics.
+
+Our work addresses particularly challenging aspects of the control synthesis
+problem.  We perform digital control synthesis over a hybrid model, where
+the plant exhibits continuous behaviour and the controller operates in both
+discrete time and state-space.  The key insight of our approach is that the
+problem can be translated into a \emph{single, joint domain}, which
+represents a bi-simulation of the original, hybrid dynamics.  Given our
+primary interest in stability despite digitisation effects, we have modelled
+a digital equivalent of the plant by evaluating the effects of the
+quantisers (A/D and D/A converters) as time discretisation elements with
+quantisation noise.  The resulting closed-loop system is a program loop that
+operates on bit-vectors encoded using fixed-point arithmetic with fixed word
+length (FWL).  We calculate the deterministic effect of the FWL and
+quantization errors are included in the model as an additive uncertainty,
+which is taken into account during the synthesis of the controller.
+
+In summary, this paper makes the following original contributions.
+%
+\begin{itemize}
+
+\item TODO 1
+
+\item TODO 2
+
+\end{itemize}
 
@@
 %
-Future work will be the extension of this CEGIS-based approach for different
-classes of systems (e.g., state-space).  We will also consider performance
-requirements while synthesising the digital controller.
+Future work will be the extension of this CEGIS-based approach to further
+classes of systems.  We will also consider performance requirements while
+synthesising the digital controller.
 

### 2016-10-13 paper/paper.tex
line breaks

@@
 
-The digital controllers synthesised in this paper are typically used in closed loops with continuous (and physical) plants.
-Thus, the proposed approach has to consider dynamics of continuous parts of system ({\it e.g.}, plant) and discrete parts ({\it e.g.}, digital controller), {\it i.e.} the synthesised controller has to consider the issues related to the hybrid systems studies.
-
-For this purpose, the design procedure is based on a discretised model for a continuous plant.
-Considering only transfer function models, we are interested in a $z$-domain transfer function that considers all the aspects about the continuous plant ($G(s)$) and the sampling and hold process.
-
-Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it
-i.e.}, a continuous model of the plant must be discretised to obtain the
-discrete equivalent coefficients via ZOH
-discretisation.
+The digital controllers synthesised in this paper are typically used in
+closed loops with continuous (and physical) plants.  Thus, the proposed
+approach has to consider dynamics of continuous parts of system ({\it e.g.},
+plant) and discrete parts ({\it e.g.}, digital controller), {\it i.e.} the
+synthesised controller has to consider the issues related to the hybrid
+systems studies.
+
+For this purpose, the design procedure is based on a discretised model for a
+continuous plant.  Considering only transfer function models, we are
+interested in a $z$-domain transfer function that considers all the aspects
+about the continuous plant ($G(s)$) and the sampling and hold process.
+
+Note that $G(z)$ is a discrete model of a real (and continuous) plant, i.e.,
+a continuous model of the plant must be discretised to obtain the discrete
+equivalent coefficients via ZOH discretisation.
 
@@
 
-Although there are several discretisation methods available
-in the literature~\cite{Franklin15}, the zero-order hold (ZOH)
-discretisation is more suitable for representing the sample and hold
-processes that are typically employed in complex systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretisation
-models the exact effect of sampling and DAC interpolation over the plant.
+Although there are several discretisation methods available in the
+literature~\cite{Franklin15}, the zero-order hold (ZOH) discretisation is
+more suitable for representing the sample and hold processes that are
+typically employed in complex systems~\cite{istepanian2012digital}, {\it
+i.e.}, the ZOH discretisation models the exact effect of sampling and DAC
+interpolation over the plant.
 
@@
 %
-The Sample and Hold of the ADC and the ZOH of the DAC are synchronized, {\it i.e.}, there is no delay between
-sampling the plant output at ADC and updating the DAC accordingly. The DAC interpolator is an ideal ZOH.
+The Sample and Hold of the ADC and the ZOH of the DAC are synchronized, {\it
+i.e.}, there is no delay between sampling the plant output at ADC and
+updating the DAC accordingly.  The DAC interpolator is an ideal ZOH.
 %
@@
 %
-Given a synchronized ZOH input and sample and hold output on the plant with a sample time $T$ satisfying Nyquist's sampling criteria, the discrete pulse transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$ which can be computed using the following formula:
+Given a synchronized ZOH input and sample and hold output on the plant with
+a sample time $T$ satisfying Nyquist's sampling criteria, the discrete pulse
+transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$
+which can be computed using the following formula:
 %
@@
 %
-For the sake of brevity, we will use the notation $G(z)$ to represent the pulse transfer function.
+For the sake of brevity, we will use the notation $G(z)$ to represent the
+pulse transfer function.
 %
@@
 %
-\noindent where $\vec{\beta}$ and $\vec{\alpha}$ are vectors containing the controller's coefficients;  
-similarly $\vec{b}$ and $\vec{a}$ encompass the plant's coefficients;  
-and $N_{(\cdot)}$ and $M_{(\cdot)}$ denote the number of poles and zeros for the corresponding block.
-
-Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$), errors in the numeric calculations, or roundoffs in the quantization.
-These uncertainties may be parametrically expressed by additive terms, resulting in a uncertain model $\hat{G}(z)$, such that:
+\noindent where $\vec{\beta}$ and $\vec{\alpha}$ are vectors containing the
+controller's coefficients; similarly $\vec{b}$ and $\vec{a}$ encompass the
+plant's coefficients; and $N_{(\cdot)}$ and $M_{(\cdot)}$ denote the number
+of poles and zeros for the corresponding block.
+
+Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$
+(\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$), errors in the numeric
+calculations, or roundoffs in the quantization.  These uncertainties may be
+parametrically expressed by additive terms, resulting in a uncertain model
+$\hat{G}(z)$, such that:
+%
 \begin{equation}
@@
 \end{equation}
+%
 which will be represented by the following transfer function:
+%
 \begin{equation}
@@
 \end{equation}
-Due to the nature of the methods used for stability check in this paper, we require that  the parametric errors in the plant have the same polynomial order as the plant itself (other errors are ensured to fulfil this property in our implementation).
-
-In order to simplify the notations in this paper, we will use a notation based on the coefficients of the polynomials.
-Let $\mathcal{P}^{N}$ be a polynomial domain of order $N$
-Let $P \in \mathcal{P}^{M,N}$ be a rational polynomial $\frac{P_n}{P_d} : P_n \in \mathcal{P}^{M} \wedge P_d \in \mathcal{P}^{N}$. There is a vector of coefficients 
+%
+Due to the nature of the methods used for stability check in this paper, we
+require that the parametric errors in the plant have the same polynomial
+order as the plant itself (other errors are ensured to fulfil this property
+in our implementation).
+
+In order to simplify the notations in this paper, we will use a notation
+based on the coefficients of the polynomials.  Let $\mathcal{P}^{N}$ be a
+polynomial domain of order $N$ Let $P \in \mathcal{P}^{M,N}$ be a rational
+polynomial $\frac{P_n}{P_d} : P_n \in \mathcal{P}^{M} \wedge P_d \in
+\mathcal{P}^{N}$.  There is a vector of coefficients
+%
 \begin{equation}
@@
 \end{equation}
+%
 with uncertainty
+%
 \begin{equation}
@@
 \end{equation}
-Then $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$.
-In the following we may use either notation to represent the functions $G(z)$, $C(z)$, and their respective uncertainties.\\
+%
+Then $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$.  In the following we may use
+either notation to represent the functions $G(z)$, $C(z)$, and their
+respective uncertainties.\\
 
@@
 
-A typical hybrid system, with a continuous plant and a discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta_p \vec{G}_s$ , $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.
+A typical hybrid system, with a continuous plant and a discrete controller,
+is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters
+introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the
+continuous-time plant model with parametric additive uncertainty $\Delta_p
+\vec{G}_s$ , $R(z)$ is the reference signal, $U(z)$ is the control signal,
+and $\hat{Y}(z)$ is the output signal affected by the noises and
+uncertainties in the closed-loop system.
 
@@
 
-The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta_p \vec{G}$
+The ADC and DAC may be abstracted changing the hybrid system in
+figure~\ref{fig:sampledsystem} to the digital system in
+figure~\ref{fig:digsystem1} where the parametric uncertainties are
+represented by $\Delta_p \vec{G}$
+%
 %=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$
-and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is represented as an additive (output) measurement noise $\nu(z)$, thus $\hat{Y}(z)=Y(z)+\nu(z)$.
-The measurement noise $\nu(k)$ is enough for represent both quantization noises ($\nu_{1}$ and $\nu_{2}$) what can be obtained reorganizing the equations~\ref{eq:outputfunctions}:
+%
+and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is
+represented as an additive (output) measurement noise $\nu(z)$, thus
+$\hat{Y}(z)=Y(z)+\nu(z)$.  The measurement noise $\nu(k)$ is enough for
+represent both quantization noises ($\nu_{1}$ and $\nu_{2}$) what can be
+obtained reorganizing the equations~\ref{eq:outputfunctions}:
+%
 \begin{equation}
@@
 \end{equation}
+%
 where $H_{1}R(z)$ is exactly equal to $Y(z)$ without quantization noise effects, thus:
+%
 \begin{equation}
@@
 
-This noise $\nu(z)$ may represent exactly the same effects that $\nu_{1}(z)$ and $\nu_{2}(z)$ represents together.
+This noise $\nu(z)$ may represent exactly the same effects that $\nu_{1}(z)$
+and $\nu_{2}(z)$ represents together.
 
@@
 \end{equation}
+%
 where $\Delta_p \vec{G}$ is the term that corresponds to the parametric uncertainties and $\Delta_q \vec{G}$ is the term that reflects the quantisation effects on the plant model.

### 2016-10-13 paper/paper.tex
line breaks

@@
 %
-where $\Delta_p \vec{G}$ is the term that corresponds to the parametric uncertainties and $\Delta_q \vec{G}$ is the term that reflects the quantisation effects on the plant model.
+where $\Delta_p \vec{G}$ is the term that corresponds to the parametric
+uncertainties and $\Delta_q \vec{G}$ is the term that reflects the
+quantisation effects on the plant model.
+
 %\red{[next figure is a bit unnecessary, does not ad much to the previous one.]} Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.
@@
 
-Since the controller is implemented using a FWL, $C(z)$ also suffers disturbances from the FWL effects, with roundoffs in coefficients that may change the closed-loop poles and zeros position, and consequently affect its stability, as shown in~\cite{Bessa16}.
-
-Let $\hat{C}(z)$ be the transfer function of the digital controller represented using this FWL with integer size $I$ and fractional
-size $F$.  We shall denote the FWL domain of coefficients as $\mathbb{R}\langle I,F \rangle$
+Since the controller is implemented using a FWL, $C(z)$ also suffers
+disturbances from the FWL effects, with roundoffs in coefficients that may
+change the closed-loop poles and zeros position, and consequently affect its
+stability, as shown in~\cite{Bessa16}.
+
+Let $\hat{C}(z)$ be the transfer function of the digital controller
+represented using this FWL with integer size $I$ and fractional size $F$. 
+We shall denote the FWL domain of coefficients as $\mathbb{R}\langle I,F
+\rangle$
+%
 %Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
@@
 %, \red{[explain index n! why do you need to work on a Euclidean domain?]}. 
-Thus the perturbed controller model $\hat{C}(z)$ may be computed from the original model $C(z)=\frac{N_{C}(z)}{D_{C}(z)}$ using the following expression:
+%
+Thus the perturbed controller model $\hat{C}(z)$ may be computed from the
+original model $C(z)=\frac{N_{C}(z)}{D_{C}(z)}$ using the following
+expression:
+%
 \begin{equation}
@@
 \end{equation}
-In the case of a synthesised controller, because the synthesis is performed using FWL, $\hat{C}(z) \equiv C(z)$.
+%
+In the case of a synthesised controller, because the synthesis is performed
+using FWL, $\hat{C}(z) \equiv C(z)$.
 
@@
 
-In order to obtain a sound synthesis of the digital controller, the effect of FWL implementation in controller and quantisation noises in closed loop system have to be considered.
-Considering that the quantizer $Q1$ is the source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise $\nu_{2}$, the following equation is written for the system in Figure~\ref{fig:sampledsystem}, considering the parametric uncertainties $\Delta \vec{G}$ and the FWL effects on controller ($\hat{C}(z)$):
+In order to obtain a sound synthesis of the digital controller, the effect
+of FWL implementation in controller and quantisation noises in closed loop
+system have to be considered.  Considering that the quantizer $Q1$ is the
+source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise
+$\nu_{2}$, the following equation is written for the system in
+Figure~\ref{fig:sampledsystem}, considering the parametric uncertainties
+$\Delta \vec{G}$ and the FWL effects on controller ($\hat{C}(z)$):
+%
 \begin{equation}
@@
 \end{equation}
+%
 that can be rewritten as follows:
+%
 \begin{equation}
@@
 \end{equation}
+%
 where
+%
 \begin{equation}
@@
 \end{equation}
+%
 and
+%
 \begin{equation}
@@
 
-A discrete-time linear system is said to be Bounded-Input and Bounded-Output (BIBO) stable if and only if every pole of its transfer function lies inside the unit circle.
-\textcolor{red}{Analyzing Eq.~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for BIBO stability of closed-loop system in Figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$ are bounded.}
+A discrete-time linear system is said to be Bounded-Input and Bounded-Output
+(BIBO) stable if and only if every pole of its transfer function lies inside
+the unit circle.  \textcolor{red}{Analyzing Eq.~\eqref{eq:outputfunctions}
+and based on assumption~\ref{assumption:cont_and_plant}, the following lemma
+states necessary conditions for BIBO stability of closed-loop system in
+Figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$,
+$\nu_{1}$, and $\nu_{2}$ are bounded.}
 
@@
 \label{lemma:variance}
-In particular, Widrow \cite{widrow1956} models the quantisation noise as a gaussian
-model in which the second moment (variance) of the probability density
-function (PDF) of the quantisation noise is given by
+%
+In particular, Widrow \cite{widrow1956} models the quantisation noise as a
+gaussian model in which the second moment (variance) of the probability
+density function (PDF) of the quantisation noise is given by
 %
@@
 \label{lemma:boundednoise}
-The power spectral density of the quantisation noise (supposed white) $S_{\nu}(z)$ is bounded and may be computed through the z-transform of autocorrelation function of $\nu(k)$, thus:
+%
+The power spectral density of the quantisation noise (supposed white)
+$S_{\nu}(z)$ is bounded and may be computed through the z-transform of
+autocorrelation function of $\nu(k)$, thus:
+%
 \begin{equation}
@@
 \begin{proof}
-Considering $\nu(k)$ a random process, where $\nu(k)$ is independent from $\nu(k+i)$ for every  integer $k\neq 0$.
-The autocorrelation function of $\nu(k)$, {\it i.e.} $R_{\nu\nu}(\tau)$ may be computed as follows:
+%
+Considering $\nu(k)$ a random process, where $\nu(k)$ is independent from
+$\nu(k+i)$ for every integer $k\neq 0$.  The autocorrelation function of
+$\nu(k)$, {\it i.e.} $R_{\nu\nu}(\tau)$ may be computed as follows:
+%
 \begin{equation}
@@
 \end{equation}
+%
 where $\delta(\tau)$ is the Dirac delta function at delay time $\tau$.
 
-By definition~\cite{poularikas2000transforms}, the power spectral density of  $\nu(k)$ is the z-transform of $R_{\nu\nu}(\tau)$, thus
+By definition~\cite{poularikas2000transforms}, the power spectral density of
+$\nu(k)$ is the z-transform of $R_{\nu\nu}(\tau)$, thus
+%
 \begin{equation}
@@
 
-Finally, the quantisation noise spectrum may be considered a energy-bounded (Lemma~\ref{lemma:boundednoise}), and consequently the Parseval's theorem ensures that the quantisation noise is also energy-bounded in time-domain.
-Thus $\hat{Y}(z)$ will be bounded and the closed-loop system stable if the conditions in Lemma~\ref{lemma:eq_int_stab} are followed.
+Finally, the quantisation noise spectrum may be considered a energy-bounded
+(Lemma~\ref{lemma:boundednoise}), and consequently the Parseval's theorem
+ensures that the quantisation noise is also energy-bounded in time-domain. 
+Thus $\hat{Y}(z)$ will be bounded and the closed-loop system stable if the
+conditions in Lemma~\ref{lemma:eq_int_stab} are followed.
 
@@
 \label{lemma:eq_int_stab} 
-A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with a FWL implementation of the digital controller $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete model of the plant $\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q \vec{G} \Rightarrow \hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and only if:
+%
+A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem},
+with a FWL implementation of the digital controller $\hat{C}(z) =
+\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete model of the
+plant $\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q \vec{G} \Rightarrow
+\hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and
+only if:
+%
 \begin{itemize}
@@
 
-The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for synthesis of digital controllers able to stabilize closed loop system, considering plant parametric uncertainties ({\it i.e.}, $\Delta_p \vec{G}$), quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital controllers.
-Based on it, the model for plant uncertainty due quantisation noise ({\it i.e.}, $\Delta_q \vec{G}$) may be disregarded if the conditions on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise is bounded.
-The quantisation noise is indeed bounded, since the following assumption~\ref{whitenoise} and the Lemmas~\ref{lemma:variance} and~\ref{lemma:boundednoise} are true.
+The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for
+synthesis of digital controllers able to stabilize closed loop system,
+considering plant parametric uncertainties ({\it i.e.}, $\Delta_p \vec{G}$),
+quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital
+controllers.  Based on it, the model for plant uncertainty due quantisation
+noise ({\it i.e.}, $\Delta_q \vec{G}$) may be disregarded if the conditions
+on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise
+is bounded.  The quantisation noise is indeed bounded, since the following
+assumption~\ref{whitenoise} and the Lemmas~\ref{lemma:variance}
+and~\ref{lemma:boundednoise} are true.
 
@@
 
-An overview of the synthesis process is illustrated in Fig.~\ref{DSVerifier_process};
-a detailed description of DSVerifier tool can be found in~\cite{IsmailBCFF15}.
-Steps $1$ to $5$ are performed by the user/synthesiser and
-Steps A to D are automatically performed by DSVerifier.
+An overview of the synthesis process is illustrated in
+Fig.~\ref{DSVerifier_process}; a detailed description of DSVerifier tool can
+be found in~\cite{IsmailBCFF15}.  Steps $1$ to $5$ are performed by the
+user/synthesiser and Steps A to D are automatically performed by DSVerifier.
+%
 %, which accepts the
@@
 
-Given a model for a plant for which to synthesize a controller,
-provided in an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
-non-deterministic model to represent the plant family (Step A), and formulates a 
-function (step B) using implementation details provided from Steps $2$ and $3$ 
-to calculate the parameters of the controller to be synthesized (step C).  
-Finally DSVerifier builds an intermediate ANSI-C code for the digital system 
-implementation, which is used as input for the controller synthesiser (Step D).
+Given a model for a plant for which to synthesize a controller, provided in
+an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
+non-deterministic model to represent the plant family (Step A), and
+formulates a function (step B) using implementation details provided from
+Steps $2$ and $3$ to calculate the parameters of the controller to be
+synthesized (step C).  Finally DSVerifier builds an intermediate ANSI-C code
+for the digital system implementation, which is used as input for the
+controller synthesiser (Step D).
 
@@
 verification properties ({\it i.e.}, robust stability) and is provided to
-CBMC's~\cite{ClarkeKL04} integrated Counterexample-Guided Inductive Synthesis
-(CEGIS) module, where the controller is marked as input variable to synthesize.
-The properties specified in the ANSI-C code model can only be satisfied if CEGIS
-synthesizes controller coefficients satisfying $\phi$. CEGIS employs an iterative,
-counterexample-guided refinement process which is explained in detail in
-section~\ref{synthesiser-general}. A successful synthesis result is reported if
-CEGIS generates a controller which is safe with respect to $\phi$.  In particular,
-the ANSI-C code model guarantees that a synthesized solution is complete
-and sound with respect to stability property $\phi$, since it does not depend on
-system inputs and outputs.  In the case of stability, the specification $\phi$
-consists in a number of assumptions on the polynomial coefficients, following
-Jury's Criteria, as well as the restrictions set in the representation of these
-coefficients.
+CBMC's~\cite{ClarkeKL04} integrated Counterexample-Guided Inductive
+Synthesis (CEGIS) module, where the controller is marked as input variable
+to synthesize.  The properties specified in the ANSI-C code model can only
+be satisfied if CEGIS synthesizes controller coefficients satisfying $\phi$. 
+CEGIS employs an iterative, counterexample-guided refinement process which
+is explained in detail in section~\ref{synthesiser-general}.  A successful
+synthesis result is reported if CEGIS generates a controller which is safe
+with respect to $\phi$.  In particular, the ANSI-C code model guarantees
+that a synthesized solution is complete and sound with respect to stability
+property $\phi$, since it does not depend on system inputs and outputs.  In
+the case of stability, the specification $\phi$ consists in a number of
+assumptions on the polynomial coefficients, following Jury's Criteria, as
+well as the restrictions set in the representation of these coefficients.
 
@@
 
-In order to synthesise closed-loop digital control systems, we use a
-program synthesis engine.  Nowadays, such engines are used
-increasingly often in program
-verification~\cite{DBLP:conf/lpar/DavidKL15,DBLP:conf/cav/0001A14}.
+In order to synthesise closed-loop digital control systems, we use a program
+synthesis engine.  Nowadays, such engines are used increasingly often in
+program verification~\cite{DBLP:conf/lpar/DavidKL15, DBLP:conf/cav/0001A14}. 
 Our program synthesiser makes use of Counter-Example Guided Inductive
@@
 % 
-The input specification provided to the program synthesiser is of the
-form $\exists \vec{P} . \forall \vec{x}. \sigma(\vec{x}, \vec{P})$ where $\vec{P}$ ranges over functions,
-$\vec{x}$ ranges over ground terms and $\sigma$ is a quantifier-free
-formula.  We interpret the ground terms over some finite domain
-$\mathcal{D}$.
-
-The design of our synthesiser is given in Fig.~\ref{fig:CEGIS} and
-consists of two phases, {\sc Synthesise} and {\sc Verify}, which
-interact via a finite set of test vectors {\sc inputs} that is updated
-incrementally.  Given the aforementioned specification $\sigma$, the
-{\sc synth} procedure tries to find an existential witness $\vec{P}$
-satisfying the specification $\sigma(\vec{x}, \vec{P})$ for all
-$\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
-%
-If {\sc synthesise} succeeds in finding an witness $\vec{P}$, this
-witness is a candidate solution to the full synthesis formula. 
-We pass this candidate solution to {\sc verify}, which 
-checks whether it is a full solution ({\it i.e.}, $\vec{P}$
-satisfies the specification $\sigma(\vec{x}, \vec{P})$ for all
-$\vec{x}\in\mathcal{D}$).
+The input specification provided to the program synthesiser is of the form
+$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
+$\vec{P}$ ranges over functions, $\vec{x}$ ranges over ground terms and
+$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
+some finite domain $\mathcal{D}$.
+
+The design of our synthesiser is given in Fig.~\ref{fig:CEGIS} and consists
+of two phases, {\sc Synthesise} and {\sc Verify}, which interact via a
+finite set of test vectors {\sc inputs} that is updated incrementally. 
+Given the aforementioned specification $\sigma$, the {\sc synth} procedure
+tries to find an existential witness $\vec{P}$ satisfying the specification
+$\sigma(\vec{x}, \vec{P})$ for all $\vec{x}$ in {\sc inputs} (as opposed to
+all $\vec{x} \in \mathcal{D}$).
+%
+If {\sc synthesise} succeeds in finding an witness $\vec{P}$, this witness
+is a candidate solution to the full synthesis formula.  We pass this
+candidate solution to {\sc verify}, which checks whether it is a full
+solution ({\it i.e.}, $\vec{P}$ satisfies the specification $\sigma(\vec{x},
+\vec{P})$ for all $\vec{x}\in\mathcal{D}$).
+%
 %determines whether
@@
 %% full solution.
-If this is the case, then the algorithm terminates.
-Otherwise, additional information is provided to the {\sc synthesise}
-phase in the form of a new counterexample that is added to the {\sc inputs} set
-and the loop iterates again (note that, for now, we ignore the 
-second feedback signal ``Increase Precision'' provided by the {\sc Verify}
-phase in Fig.~\ref{fig:CEGIS} as it is specific to control synthesis and will 
-be described in the next section).
+%
+If this is the case, then the algorithm terminates.  Otherwise, additional
+information is provided to the {\sc synthesise} phase in the form of a new
+counterexample that is added to the {\sc inputs} set and the loop iterates
+again (note that, for now, we ignore the second feedback signal ``Increase
+Precision'' provided by the {\sc Verify} phase in Fig.~\ref{fig:CEGIS} as it
+is specific to control synthesis and will be described in the next section).
 
@@
 However, given a real plant $\hat{G}(z)$, and a discretising function
+%
 \begin{align}
@@
 \end{align}
+%
 we calculate $\tilde G(z)=FWL_b(\hat{G}(z))$
+%
 \begin{align}
@@
 remove them from the counterexample set.  Back in the {\sc synthesise}
-phase, we re-start the process with a candidate solution with all coefficients 0.
-Next, the {\sc uncertainty} verification stage provides the first counterexample at higher
-precision:
+phase, we re-start the process with a candidate solution with all
+coefficients $0$.  Next, the {\sc uncertainty} verification stage provides
+the first counterexample at higher precision:
 %
@@
 attitude (pose) control for proper orientation of antennas and sensors
-w.r.t.  earth.  The satellite attitude control is typically used for
+w.r.t.~earth.  The satellite attitude control is typically used for
 three-axis attitude tracking, but here only one axis at a time is
@@
 
-\noindent where $I$ is the inertia moment of satellite about its mass center, $\tau_{C}$ is the control 
-torque applied by thusters, and $\theta$ is the controlled attitude angle. 
-Normalizing Eq.~\eqref{eq:satelliteode} by defining the control signal $u=\frac{\tau_{C}}{I}$ and 
-taking Laplace transform, the following $s$-domain transfer function $G(s)$ is obtained
+\noindent where $I$ is the inertia moment of satellite about its mass
+center, $\tau_{C}$ is the control torque applied by thusters, and $\theta$
+is the controlled attitude angle.  Normalizing Eq.~\eqref{eq:satelliteode}
+by defining the control signal $u=\frac{\tau_{C}}{I}$ and taking Laplace
+transform, the following $s$-domain transfer function $G(s)$ is obtained
 %
@@
 
-The fourth (and last) set of benchmarks considers the following description for the plant 
-$G_{4}(s)$, which is typically used for evaluating stability margins~\cite{bhattacharyya97,keel_Bhattacharyya_examples}
+The fourth (and last) set of benchmarks considers the following description
+for the plant $G_{4}(s)$, which is typically used for evaluating stability
+margins~\cite{bhattacharyya97, keel_Bhattacharyya_examples}
 %
@@
 We outline the runtimes required to synthesise a stable controller for each
-benchmark in Table~\ref{tab:results}. Here, \textit{Plant} is the discrete or 
-continuous plant model, \textit{Benchmark} is the name of the employed benchmark,
-\textit{I} and \textit{F} represent the number of integer and fractional bits of the 
-stable controller, respectively, while \textit{Time} represents the total time 
-(in seconds) to synthesise a stable controller for the given plant.
-
-For the majority of our benchmarks, the conjecture explained
-in section~\ref{synthesis-elements}  holds and the inductive back-end is able to find a stable
-solution in less than one minute.  This is possible if the inductive solutions need to be refined
-with few counterexamples and fixed-point precision increases. However, $2$ benchmarks in our set
-required too many counterexamples to refine their solution (marked with $^*$ in Table~\ref{tab:results}). 
-In these cases, the interval arithmetic back-end is able to complement the inductive approach
-and synthesise a solution instead, albeit with significantly larger runtimes.  This performance
-difference is due to  the fact that the interval back-end does not take advantage of the inductive
-conjecture inherent to CEGIS, but instead fully explores the counterexample space.  The result is
-a performance difference of at least two orders of magnitude in our experiments, leading to the
-interval back-end timing out on the majority of our benchmarks.  Table~\ref{tab:results} only
-lists the faster of the two back-ends for each benchmark, which in $12$ out of $15$ benchmarks is the inductive
-back-end.
+benchmark in Table~\ref{tab:results}.  Here, \textit{Plant} is the discrete
+or continuous plant model, \textit{Benchmark} is the name of the employed
+benchmark, \textit{I} and \textit{F} represent the number of integer and
+fractional bits of the stable controller, respectively, while \textit{Time}
+represents the total time (in seconds) to synthesise a stable controller for
+the given plant.
+
+For the majority of our benchmarks, the conjecture explained in
+section~\ref{synthesis-elements} holds and the inductive back-end is able to
+find a stable solution in less than one minute.  This is possible if the
+inductive solutions need to be refined with few counterexamples and
+fixed-point precision increases.  However, $2$ benchmarks in our set
+required too many counterexamples to refine their solution (marked with $^*$
+in Table~\ref{tab:results}).  In these cases, the interval arithmetic
+back-end is able to complement the inductive approach and synthesise a
+solution instead, albeit with significantly larger runtimes.  This
+performance difference is due to the fact that the interval back-end does
+not take advantage of the inductive conjecture inherent to CEGIS, but
+instead fully explores the counterexample space.  The result is a
+performance difference of at least two orders of magnitude in our
+experiments, leading to the interval back-end timing out on the majority of
+our benchmarks.  Table~\ref{tab:results} only lists the faster of the two
+back-ends for each benchmark, which in $12$ out of $15$ benchmarks is the
+inductive back-end.
 
@@
 
-The median runtime for our benchmark set is $197$\,s, implying that half of the controllers
-can be synthesised in less than $5$ minutes using our present approach. Overall the average synthesis
-time amounts to approximately $30$ minutes. With respect to RQ2 we consider
-these times short enough to be of practical use to control engineers.
-Regarding RQ1 we further conclude that the inductive back-end is able to synthesise 
-stable controllers in the $12$ out of $15$ benchmarks, and can be complemented using 
-the interval arithmetic back-end for $2$ additional benchmarks, where the inductive 
-conjectures fail. Both back-ends together enabled controller synthesis for $14$ 
-out of $15$ benchmarks.  For the $1$ remaining benchmark our approach failed to synthesise
-a stable controller in the requested time limits. This can be addressed by either increasing
-the fixed point word widths considered or using floating point arithmetic instead. A link
-to the full experimental environment, including scripts to reproduce the experiment, all
-benchmarks and the CEGIS tool is provided in the footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}
+The median runtime for our benchmark set is $197$\,s, implying that half of
+the controllers can be synthesised in less than $5$ minutes using our
+present approach.  Overall the average synthesis time amounts to
+approximately $30$ minutes.  With respect to RQ2 we consider these times
+short enough to be of practical use to control engineers.  Regarding RQ1 we
+further conclude that the inductive back-end is able to synthesise stable
+controllers in the $12$ out of $15$ benchmarks, and can be complemented
+using the interval arithmetic back-end for $2$ additional benchmarks, where
+the inductive conjectures fail.  Both back-ends together enabled controller
+synthesis for $14$ out of $15$ benchmarks.  For the $1$ remaining benchmark
+our approach failed to synthesise a stable controller in the requested time
+limits.  This can be addressed by either increasing the fixed point word
+widths considered or using floating point arithmetic instead.  A link to the
+full experimental environment, including scripts to reproduce the
+experiment, all benchmarks and the CEGIS tool is provided in the
+footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}
 
@@
 need for economy, more recent studies focus on the problems of achieving
-robust stability with minimum
-gain~\cite{schmid2014unified,konigorski2012pole}.  However, when extending
-the problem to digital controller synthesis, many of these techniques lack
-the ability to produce sound or stable results because they disregard the
-effects of quantisation and rounding.  Recent papers on
-implementations/synthesis of LTI digital
+robust stability with minimum gain~\cite{schmid2014unified,
+konigorski2012pole}.  However, when extending the problem to digital
+controller synthesis, many of these techniques lack the ability to produce
+sound or stable results because they disregard the effects of quantisation
+and rounding.  Recent papers on implementations/synthesis of LTI digital
 controllers~\cite{das2013lqr,ghosh2013fpga} focus on time discretisation,

### 2016-10-13 paper/paper.tex
wordings intro

@@
 availability of low-cost devices that can perform highly non-trivial control
-tasks, with impact in numerous application areas such as environmental
-control and robotics~\cite{astrom1997computer, Franklin15}.
+tasks, with significant impact in numerous application areas such as
+environmental control and robotics~\cite{astrom1997computer, Franklin15}.
 
@@
 
-By contrast, we propose to leverage very recent step-change in \emph{program
-synthesis}.  Program synthesis engines use a program specification as the
-starting point, and subsequently generate a sequence of candidate programs. 
-The candidate programs are iteratively refined to match the specification
-more closely.  Program synthesisers that implement Counter-Example Guided
-Inductive Synthesis (CEGIS)~\cite{sketch} are now able to generate programs
-for highly non-trivial specifications with a very high degree of automation. 
-Modern CEGIS engines implement combinations of automated testing, genetic
-algorithms and SMT-based automated reasoning~\cite{DBLP:conf/lpar/DavidKL15,
-DBLP:conf/cav/0001A14}.
+By contrast, we leverage very recent step-change in the scalability of
+\emph{program synthesis}.  Program synthesis engines use a program
+specification as the starting point, and subsequently generate a sequence of
+candidate programs.  The candidate programs are iteratively refined to match
+the specification more closely.  Program synthesisers that implement
+Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} are now
+able to generate programs for highly non-trivial specifications with a very
+high degree of automation.  Modern CEGIS engines implement combinations of
+automated testing, genetic algorithms and SMT-based automated
+reasoning~\cite{DBLP:conf/lpar/DavidKL15, DBLP:conf/cav/0001A14}.
 
@@
 the plant exhibits continuous behaviour and the controller operates in both
-discrete time and state-space.  The key insight of our approach is that the
-problem can be translated into a \emph{single, joint domain}, which
+discrete time and discrete state space.  The key insight of our approach is
+that the problem can be translated into a \emph{single, joint domain}, which
 represents a bi-simulation of the original, hybrid dynamics.  Given our
@@
 quantization errors are included in the model as an additive uncertainty,
-which is taken into account during the synthesis of the controller.
+which is taken into account during the CEGIS-based synthesis of the
+control software for the plant.
 

### 2016-10-13 paper/paper.tex
wordings intro

@@
 length (FWL).  We calculate the deterministic effect of the FWL and
-quantization errors are included in the model as an additive uncertainty,
-which is taken into account during the CEGIS-based synthesis of the
-control software for the plant.
+quantization errors are incorporated into the model as an additive
+uncertainty, which is taken into account during the CEGIS-based synthesis of
+the control software for the plant.
 

### 2016-10-13 paper/paper.tex
Minor changes

--- 2016-10-13 paper/paper.tex
@@
 %------------------------------------
-\subsection{Sampling and Holding in Hybrid Systems}
+\subsection{Sampling and Holding in Closed-loop Systems}
 \label{ssec:SandH}
@@
 approach has to consider dynamics of continuous parts of system ({\it e.g.},
-plant) and discrete parts ({\it e.g.}, digital controller), {\it i.e.} the
-synthesised controller has to consider the issues related to the hybrid
-systems studies.
+plant) and discrete parts ({\it e.g.}, digital controller).
 
@@
 \label{eq:pulsetf}
-G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
+G(z,T) = \mathcal{ZOH}\left\lbrace{G(s)}\right\rbrace =(1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
 \end{equation}
@@
 %\label{plant_tf}
-G(z)&=\frac{G_n(z)}{G_d{z}}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
+G(z)&=\frac{G_n(z)}{G_d(z)}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
 \end{align}
@@
 
-A typical hybrid system, with a continuous plant and a discrete controller,
+A typical digital control system system, with a continuous plant and a discrete controller,
 is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters
@@
 represented as an additive (output) measurement noise $\nu(z)$, thus
-$\hat{Y}(z)=Y(z)+\nu(z)$.  The measurement noise $\nu(k)$ is enough for
-represent both quantization noises ($\nu_{1}$ and $\nu_{2}$) what can be
-obtained reorganizing the equations~\ref{eq:outputfunctions}:
-%
-\begin{equation}
-\label{eq:outputfunctions2}
-\hat{Y}(z)=H_{1}R(z)+H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z),
-\end{equation}
-%
-where $H_{1}R(z)$ is exactly equal to $Y(z)$ without quantization noise effects, thus:
-%
-\begin{equation}
-\nu(z)=H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z).
-\end{equation}
+%$\hat{Y}(z)=Y(z)+\nu(z)$.  The measurement noise $\nu(k)$ is enough for
+%represent both quantization noises ($\nu_{1}$ and $\nu_{2}$) what can be
+%obtained reorganizing the equations~\ref{eq:outputfunctions}:
+%%
+%\begin{equation}
+%\label{eq:outputfunctions2}
+%\hat{Y}(z)=H_{1}R(z)+H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z),
+%\end{equation}
+%%
+%where $H_{1}R(z)$ is exactly equal to $Y(z)$ without quantization noise effects, thus:
+%%
+%\begin{equation}
+%\nu(z)=H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z).
+%\end{equation}
 
@@
 %\end{equation}
-
-This noise $\nu(z)$ may represent exactly the same effects that $\nu_{1}(z)$
-and $\nu_{2}(z)$ represents together.
 

### 2016-10-13 paper/paper.tex
minor changes

@@
 
-A discrete-time linear system is said to be Bounded-Input and Bounded-Output
-(BIBO) stable if and only if every pole of its transfer function lies inside
-the unit circle.  \textcolor{red}{Analyzing Eq.~\eqref{eq:outputfunctions}
-and based on assumption~\ref{assumption:cont_and_plant}, the following lemma
-states necessary conditions for BIBO stability of closed-loop system in
-Figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$,
-$\nu_{1}$, and $\nu_{2}$ are bounded.}
-
 \begin{myassumption}
@@
 
-\red{[Add remark on bound (q/2) for signal. We need a bounded signal to be able to leverage BIBO stability results. ]}
+%\red{[Add remark on bound (q/2) for signal. We need a bounded signal to be able to leverage BIBO stability results. ]}
+
+A discrete-time linear system is said to be Bounded-Input and Bounded-Output
+(BIBO) stable if and only if every pole of its transfer function lies inside
+the unit circle.  \textcolor{red}{Analyzing Eq.~\eqref{eq:outputfunctions}, the following lemma
+states necessary conditions for BIBO stability of closed-loop system in
+Figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$,
+$\nu_{1}$, and $\nu_{2}$ are bounded.}
 

### 2016-10-13 paper/paper.tex
Minor changes

@@
 The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
-$Q2$) are bounded uncorrelated white noises.
+$Q2$) are uncorrelated white noises and their amplitudes are always bounded by the half of quantization step, {\it i.e.} $\vert \nu_{1} \vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$, where $q_{1}$ and $q_{2}$ are respectively the quantization step of  ADC and DAC.
 % 

### 2016-10-13 paper/paper.tex
small editing sec 4.2

--- 2016-10-13 paper/paper.tex
@@
 
-Essentially, in the first stage, denoted by {\sc Uncertainty} in Fig.~\ref{fig:CEGIS}, 
+In more detail, in the first stage, denoted by {\sc Uncertainty} in Fig.~\ref{fig:CEGIS}, 
 assuming a precision \param{I_b}{F_b} 

### 2016-10-13 paper/paper.tex
minor changes

--- 2016-10-13 paper/paper.tex
@@
 length (FWL).  We calculate the deterministic effect of the FWL and
-quantization errors are included in the model as an additive uncertainty,
+quantisation errors are included in the model as an additive uncertainty,
 which is taken into account during the synthesis of the controller.
@@
 \label{eq:pulsetf}
-G(z,T) = \mathcal{ZOH}\left\lbrace{G(s)}\right\rbrace =(1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
+G(z,T) = %\mathcal{ZOH}\left\lbrace{G(s)}\right\rbrace =
+(1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
 \end{equation}
@@
 \end{mylemma}
+
+The lemma \ref{eq:pulsetf} is ensures the poles and zeros matching with $\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$ operations and includes the ZOH dynamics in the $(1-z^{-1})$ term, that is sufficient for the stability studies over $G(s)$
 
@@
 (\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$), errors in the numeric
-calculations, or roundoffs in the quantization.  These uncertainties may be
+calculations, or roundoffs in the quantisation.  These uncertainties may be
 parametrically expressed by additive terms, resulting in a uncertain model
@@
 %$\hat{Y}(z)=Y(z)+\nu(z)$.  The measurement noise $\nu(k)$ is enough for
-%represent both quantization noises ($\nu_{1}$ and $\nu_{2}$) what can be
+%represent both quantisation noises ($\nu_{1}$ and $\nu_{2}$) what can be
 %obtained reorganizing the equations~\ref{eq:outputfunctions}:
@@
 %%
-%where $H_{1}R(z)$ is exactly equal to $Y(z)$ without quantization noise effects, thus:
+%where $H_{1}R(z)$ is exactly equal to $Y(z)$ without quantisation noise effects, thus:
 %%
@@
 
-%Considering the quantization noise $\nu(k)$ as an output error in discrete plant model, we may represent it as an additive noise in the plant output $y(k)$ resulting in the noisy output $\hat{y}(k)$:
+%Considering the quantisation noise $\nu(k)$ as an output error in discrete plant model, we may represent it as an additive noise in the plant output $y(k)$ resulting in the noisy output $\hat{y}(k)$:
 %\begin{equation}
@@
 of FWL implementation in controller and quantisation noises in closed loop
-system have to be considered.  Considering that the quantizer $Q1$ is the
+system have to be considered.  Considering that the quantiser $Q1$ is the
 source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise
@@
 The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
-$Q2$) are bounded uncorrelated white noises.
+$Q2$) are uncorrelated white noises and their amplitudes are always bounded by the half of quantisation step \cite{astrom1997computer}, {\it i.e.} $\vert \nu_{1} \vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$, where $q_{1}$ and $q_{2}$ are respectively the quantisation step of  ADC and DAC.
 % 
@@
 
-\begin{mylemma}
-\label{lemma:variance}
-%
-In particular, Widrow \cite{widrow1956} models the quantisation noise as a
-gaussian model in which the second moment (variance) of the probability
-density function (PDF) of the quantisation noise is given by
-%
-\begin{equation}
-\label{eq:variancelemma}
-\sigma_{Q}^{2}=\frac{q^{2}}{12},
-\end{equation}
-where $q$ is the step size of quantizer. (Proof is on \cite{widrow1956})
-\end{mylemma}
-
-\begin{mylemma}
-\label{lemma:boundednoise}
-%
-The power spectral density of the quantisation noise (supposed white)
-$S_{\nu}(z)$ is bounded and may be computed through the z-transform of
-autocorrelation function of $\nu(k)$, thus:
-%
-\begin{equation}
-S_{\nu}(z)= \sigma_{Q}^{2}=\frac{q^{2}}{12}.
-\end{equation}
-\end{mylemma}
-
-\begin{proof}
-%
-Considering $\nu(k)$ a random process, where $\nu(k)$ is independent from
-$\nu(k+i)$ for every integer $k\neq 0$.  The autocorrelation function of
-$\nu(k)$, {\it i.e.} $R_{\nu\nu}(\tau)$ may be computed as follows:
-%
-\begin{equation}
-R_{\nu\nu}(\tau)=E[\nu(t+\tau)\nu(t)]=\sigma_{Q}^{2}\cdot \delta(\tau),
-\end{equation}
-%
-where $\delta(\tau)$ is the Dirac delta function at delay time $\tau$.
-
-By definition~\cite{poularikas2000transforms}, the power spectral density of
-$\nu(k)$ is the z-transform of $R_{\nu\nu}(\tau)$, thus
-%
-\begin{equation}
-S_{\nu}(z)=  \sum\limits_{k=-\infty}^{\infty}{R_{\nu\nu}(k)z^{-k}} = \sigma_{Q}^{2},
-\end{equation}
-considering the Lemma~\ref{lemma:variance}:
-\begin{equation}
-S_{\nu}(z)=  \frac{q^{2}}{12}.
-\end{equation}
-\end{proof}
-
-Finally, the quantisation noise spectrum may be considered a energy-bounded
-(Lemma~\ref{lemma:boundednoise}), and consequently the Parseval's theorem
-ensures that the quantisation noise is also energy-bounded in time-domain. 
-Thus $\hat{Y}(z)$ will be bounded and the closed-loop system stable if the
-conditions in Lemma~\ref{lemma:eq_int_stab} are followed.
+%\begin{mylemma}
+%\label{lemma:variance}
+%%
+%In particular, Widrow \cite{widrow1956} models the quantisation noise as a
+%gaussian model in which the second moment (variance) of the probability
+%density function (PDF) of the quantisation noise is given by
+%%
+%\begin{equation}
+%\label{eq:variancelemma}
+%\sigma_{Q}^{2}=\frac{q^{2}}{12},
+%\end{equation}
+%where $q$ is the step size of quantiser. (Proof is on \cite{widrow1956})
+%\end{mylemma}
+%
+%\begin{mylemma}
+%\label{lemma:boundednoise}
+%%
+%The power spectral density of the quantisation noise (supposed white)
+%$S_{\nu}(z)$ is bounded and may be computed through the z-transform of
+%autocorrelation function of $\nu(k)$, thus:
+%%
+%\begin{equation}
+%S_{\nu}(z)= \sigma_{Q}^{2}=\frac{q^{2}}{12}.
+%\end{equation}
+%\end{mylemma}
+%
+%\begin{proof}
+%%
+%Considering $\nu(k)$ a random process, where $\nu(k)$ is independent from
+%$\nu(k+i)$ for every integer $k\neq 0$.  The autocorrelation function of
+%$\nu(k)$, {\it i.e.} $R_{\nu\nu}(\tau)$ may be computed as follows:
+%%
+%\begin{equation}
+%R_{\nu\nu}(\tau)=E[\nu(t+\tau)\nu(t)]=\sigma_{Q}^{2}\cdot \delta(\tau),
+%\end{equation}
+%%
+%where $\delta(\tau)$ is the Dirac delta function at delay time $\tau$.
+%
+%By definition~\cite{poularikas2000transforms}, the power spectral density of
+%$\nu(k)$ is the z-transform of $R_{\nu\nu}(\tau)$, thus
+%%
+%\begin{equation}
+%S_{\nu}(z)=  \sum\limits_{k=-\infty}^{\infty}{R_{\nu\nu}(k)z^{-k}} = \sigma_{Q}^{2},
+%\end{equation}
+%considering the Lemma~\ref{lemma:variance}:
+%\begin{equation}
+%S_{\nu}(z)=  \frac{q^{2}}{12}.
+%\end{equation}
+%\end{proof}
+%
+%Finally, the quantisation noise spectrum may be considered a energy-bounded
+%(Lemma~\ref{lemma:boundednoise}), and consequently the Parseval's theorem
+%ensures that the quantisation noise is also energy-bounded in time-domain. 
+%Thus $\hat{Y}(z)$ will be bounded and the closed-loop system stable if the
+%conditions in Lemma~\ref{lemma:eq_int_stab} are followed.
 
@@
 %For the digital controller code, transfer functions coefficients are
-%quantized and deterministic, and all operations use fixed-point arithmetic. 
+%quantised and deterministic, and all operations use fixed-point arithmetic. 
 %\textcolor{red}{In the plant model code, transfer function coefficients are
-%not quantized, but represented with maximum precision based on float
+%not quantised, but represented with maximum precision based on float
 %data-type variables}; they are treated as non-deterministic variables to
@@
 %where $C(z)$ is the digital controller model, whose control output signal is
-%quantized ($Q2$) and interpolated via a ZOH using digital-to-analog
+%quantised ($Q2$) and interpolated via a ZOH using digital-to-analog
 %converter (DAC).  The quantisation occurs because the DAC resolution may be
@@
 %the continuous-time model of the plant, from which output samples are taken
-%and quantized ($Q1$) by means of an analog-to-digital converter (ADC)
-%synchronized with the DAC.  Each quantizer ($Q1$ and $Q2$) will present some
+%and quantised ($Q1$) by means of an analog-to-digital converter (ADC)
+%synchronized with the DAC.  Each quantiser ($Q1$ and $Q2$) will present some
 %contribution for the total quantisation noise.
@@
 %is used.  The authors provide an algorithm for computing the mean square of
-%the output noise due to $Q1$ and $Q2$.  Considering that each quantizer
+%the output noise due to $Q1$ and $Q2$.  Considering that each quantiser
 %contribution can be represented by a white noise with zero mean
@@
 %Considering that
-%the quantizer $Q1$ is the source of a white noise with zero mean $\nu_{1}$
+%the quantiser $Q1$ is the source of a white noise with zero mean $\nu_{1}$
 %and $Q2$ is the source of a white noise with zero mean $\nu_{2}$, the
@@
 \begin{equation}
-\label{Eq:running-example-controller-quantized}
+\label{Eq:running-example-controller-quantised}
 C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
@@
 from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from~\cite{daes20161}
-whilst enhancing the procedure by evaluating the quantization effects of
+whilst enhancing the procedure by evaluating the quantisation effects of
 the Hardware interfaces (ADC/DAC) to obtain an accurate discrete time FWL

### 2016-10-13 paper/paper.tex
minor changes

@@
 (BIBO) stable if and only if every pole of its transfer function lies inside
-the unit circle.  \textcolor{red}{Analyzing Eq.~\eqref{eq:outputfunctions}, the following lemma
+the unit circle.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following lemma
 states necessary conditions for BIBO stability of closed-loop system in
 Figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$,
-$\nu_{1}$, and $\nu_{2}$ are bounded.}
+$\nu_{1}$, and $\nu_{2}$ are bounded.
 
@@
 is bounded.  The quantisation noise is indeed bounded, since the following
-assumption~\ref{whitenoise} and the Lemmas~\ref{lemma:variance}
-and~\ref{lemma:boundednoise} are true.
+assumption~\ref{whitenoise}.
 

### 2016-10-13 paper/paper.tex
add contributions

--- 2016-10-13 paper/paper.tex
@@
 
-\item TODO 1
-
-\item TODO 2
+\item We exploit a CEGIS-based approach, that uses inductive synthesis
+in conjunction with a formal verification algorithm, for synthesising 
+correct-by-design robust digital controllers for non-fragile closed-loop 
+stability.
+
+\item Experiments obtained with our synthesiser show that the combination 
+of interval arithmetic to represent the controller coefficients and a two-stage 
+verification approach to continuously refine precision, we are able to compute 
+a parametric sound solution for $14$ out of $15$ digital stabilizing controllers 
+given a set of continuous and discrete plant with parametric uncertainties.
 
@@
 The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
-$Q2$) are uncorrelated white noises and their amplitudes are always bounded by the half of quantization step, {\it i.e.} $\vert \nu_{1} \vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$, where $q_{1}$ and $q_{2}$ are respectively the quantization step of  ADC and DAC.
+$Q2$) are bounded uncorrelated white noises.
 % 
@@
 
-In more detail, in the first stage, denoted by {\sc Uncertainty} in Fig.~\ref{fig:CEGIS}, 
+Essentially, in the first stage, denoted by {\sc Uncertainty} in Fig.~\ref{fig:CEGIS}, 
 assuming a precision \param{I_b}{F_b} 
@@
 We have presented a CEGIS-based approach that uses inductive synthesis in
-conjunction with a robust algorithm for verifying closed-loop stability to
-compute a parametric solution for a digital controller given a continuous
-(or discrete) plant specification.  This enables us to automatically
+conjunction with an algorithm for verifying robust closed-loop stability, 
+in order to compute a parametric solution for a digital controller given 
+a continuous (or discrete) plant specification.  This enables us to automatically
 synthesize correct-by-construction digital controllers for a given model of

### 2016-10-13 paper/paper.tex

@@
 length (FWL).  We calculate the deterministic effect of the FWL and
-quantisation errors are included in the model as an additive uncertainty,
-which is taken into account during the synthesis of the controller.
+quantisation errors are incorporated into the model as an additive
+uncertainty, which is taken into account during the CEGIS-based synthesis of
+the control software for the plant.
 

### 2016-10-13 paper/paper.tex
contributions

--- 2016-10-13 paper/paper.tex
@@
 
-\item We exploit a CEGIS-based approach, that uses inductive synthesis
-in conjunction with a formal verification algorithm, for synthesising 
-correct-by-design robust digital controllers for non-fragile closed-loop 
-stability.
-
-\item Experiments obtained with our synthesiser show that the combination 
-of interval arithmetic to represent the controller coefficients and a two-stage 
-verification approach to continuously refine precision, we are able to compute 
-a parametric sound solution for $14$ out of $15$ digital stabilizing controllers 
-given a set of continuous and discrete plant with parametric uncertainties.
-
+\item We designed and implemented an automatic approach for 
+generating {\em corect-by-construction} digital controllers that is 
+based on state-of-the-art inductive synthesis techniques.
+Our application of program synthesis is not trivial 
+and requires addressing challenges specific to
+control systems such as handling the effects of quantisers 
+and FWL.
+
+\item We provide experimental results showing that
+our fully automatic CEGIS-based approach is able to synthesise 
+stable controllers for a set of intricate benchmarks taken from 
+the literature in a reasonable amount of time 
+(the median runtime for our benchmark set is 197s, 
+implying that half of the controllers can be synthesised in less
+than 5 minutes). 
 \end{itemize}
@@
 We have presented a CEGIS-based approach that uses inductive synthesis in
-conjunction with an algorithm for verifying robust closed-loop stability, 
-in order to compute a parametric solution for a digital controller given 
-a continuous (or discrete) plant specification.  This enables us to automatically
+conjunction with a robust algorithm for verifying closed-loop stability to
+compute a parametric solution for a digital controller given a continuous
+(or discrete) plant specification.  This enables us to automatically
 synthesize correct-by-construction digital controllers for a given model of

### 2016-10-13 paper/paper.tex
nudge

--- 2016-10-13 paper/paper.tex
@@
 
-\item We exploit a CEGIS-based approach, that uses inductive synthesis
-in conjunction with a formal verification algorithm, for synthesising 
+\item We exploit a CEGIS-based approach that uses inductive synthesis
+together with a bit-precise formal verification algorithm for synthesising
 correct-by-design robust digital controllers for non-fragile closed-loop
@@
 
-\item Experiments obtained with our synthesiser show that the combination 
-of interval arithmetic to represent the controller coefficients and a two-stage 
-verification approach to continuously refine precision, we are able to compute 
-a parametric sound solution for $14$ out of $15$ digital stabilizing controllers 
-given a set of continuous and discrete plant with parametric uncertainties.
+\item Experiments obtained with our synthesiser show that the combination of
+interval arithmetic to represent the controller coefficients and a two-stage
+verification approach to continuously refine precision enables us to compute
+a parametric, sound solution for $14$ out of $15$ digital stabilizing
+controllers for a set of continuous and discrete plants with parametric
+uncertainties.
 

### 2016-10-13 paper/paper.tex
nudge

@@
 
-\item Experiments obtained with our synthesiser show that the combination of
-interval arithmetic to represent the controller coefficients and a two-stage
-verification approach to continuously refine precision enables us to compute
-a parametric, sound solution for $14$ out of $15$ digital stabilizing
-controllers for a set of continuous and discrete plants with parametric
-uncertainties.
+\item Experimental results obtained with our synthesiser show that the
+combination of interval arithmetic to represent the controller coefficients
+and a two-stage verification approach to continuously refine precision
+enables us to compute a parametric, sound solution for $14$ out of $15$
+digital stabilizing controllers for a set of continuous and discrete plants
+with parametric uncertainties.
 

### 2016-10-13 paper/paper.tex
minor corrections

--- 2016-10-13 paper/paper.tex
@@
 There has been plenty of previous work that aims at \emph{verifying} a given
-controller designed by the engineer.  Recent work can show the stability
+controller designed by the engineer.  Recent work can show the of stability
 digital controllers with considerations to implementation aspects, i.e.,
@@
 interested in a $z$-domain transfer function that considers all the aspects
-about the continuous plant ($G(s)$) and the sampling and hold process.
+about the continuous plant (with a Laplace domain transfer function $G(s)$) and the sampling and hold process.
 

### 2016-10-13 paper/paper.tex
nudge

--- 2016-10-13 paper/paper.tex
@@
 
-\item Experiments obtained with our synthesiser show that the combination of
-interval arithmetic to represent the controller coefficients and a two-stage
-verification approach to continuously refine precision enables us to compute
-a parametric, sound solution for $14$ out of $15$ digital stabilizing
-controllers for a set of continuous and discrete plants with parametric
-uncertainties.
+\item Experimental results with our synthesiser show that the
+combination of interval arithmetic to represent the controller coefficients
+and a two-stage verification approach to continuously refine precision
+enables us to compute a parametric, sound solution for $14$ out of $15$
+digital stabilizing controllers for a set of continuous and discrete plants
+with parametric uncertainties.
 

### 2016-10-13 paper/paper.tex
wordings

@@
 
-The digital controllers synthesised in this paper are typically used in
-closed loops with continuous (and physical) plants.  Thus, the proposed
-approach has to consider dynamics of continuous parts of system ({\it e.g.},
-plant) and discrete parts ({\it e.g.}, digital controller).
-
-For this purpose, the design procedure is based on a discretised model for a
-continuous plant.  Considering only transfer function models, we are
-interested in a $z$-domain transfer function that considers all the aspects
-about the continuous plant (with a Laplace domain transfer function $G(s)$) and the sampling and hold process.
-
-Note that $G(z)$ is a discrete model of a real (and continuous) plant, i.e.,
-a continuous model of the plant must be discretised to obtain the discrete
-equivalent coefficients via ZOH discretisation.
+The digital controllers synthesised using the algorithm we present in this
+paper are typically used in closed loops with continuous (and physical)
+plants.  Thus, the proposed approach has to consider dynamics of continuous
+parts of the system (i.e., the plant) and the discrete parts (i.e., the
+digital controller).  To obtain a joint model, the discretise the continuous
+plant.  We only consider transfer function models, and require a $z$-domain
+transfer function that captures all aspects of the continuous plant (with a
+Laplace domain transfer function $G(s)$) and the sampling and hold process.
+
+Note that $G(z)$ is a discrete model of a real-domain (and continuous)
+plant, i.e., the continuous model of the plant must be discretised to obtain
+the discrete equivalent coefficients via ZOH discretisation.
 
@@
 more suitable for representing the sample and hold processes that are
-typically employed in complex systems~\cite{istepanian2012digital}, {\it
-i.e.}, the ZOH discretisation models the exact effect of sampling and DAC
+typically employed in complex systems~\cite{istepanian2012digital}, i.e.,
+the ZOH discretisation models the exact effect of sampling and DAC
 interpolation over the plant.
@@
 %
-The Sample and Hold of the ADC and the ZOH of the DAC are synchronized, {\it
-i.e.}, there is no delay between sampling the plant output at ADC and
+The Sample and Hold of the ADC and the ZOH of the DAC are synchronized,
+i.e., there is no delay between sampling the plant output at ADC and
 updating the DAC accordingly.  The DAC interpolator is an ideal ZOH.
@@
 
-The lemma \ref{eq:pulsetf} is ensures the poles and zeros matching with $\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$ operations and includes the ZOH dynamics in the $(1-z^{-1})$ term, that is sufficient for the stability studies over $G(s)$
+Lemma~\ref{eq:pulsetf} ensures the poles and zeros matching with
+$\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$
+operations and includes the ZOH dynamics in the $(1-z^{-1})$ term, that is
+sufficient for the stability studies over $G(s)$.
 

### 2016-10-13 paper/paper.tex
wordings

@@
 %------------------------------------
-\subsection{Sampling and Holding in Closed-loop Systems}
+\subsection{Discretising the Plant}
 \label{ssec:SandH}
@@
 digital controller).  To obtain a joint model, the discretise the continuous
-plant.  We only consider transfer function models, and require a $z$-domain
+plant. We briefly recall the standard foundations of this step.
+
+We only consider transfer function models, and require a $z$-domain
 transfer function that captures all aspects of the continuous plant (with a
 Laplace domain transfer function $G(s)$) and the sampling and hold process.
-
 Note that $G(z)$ is a discrete model of a real-domain (and continuous)
@@
 
-In this study, the methodology used for verifying closed-loop digital
-control system is based on the Digital-System Verifier
-(DSVerifier)~\cite{IsmailBCFF15}, which checks the stability of control
-systems considering finite-word length (FWL) effects in the digital
-controller and uncertainty parameters in the plant model (plant
-intervals)~\cite{Bessa16}.  Let $C(z)$ be a digital controller and $G(z)$ be
-a plant model given as
+CEGIS-based control synthesis requires a formal verifier to check whether a
+candidate controller meets the requirements when combined with the plant. 
+We use the Digital-System Verifier (DSVerifier)~\cite{IsmailBCFF15} for this
+purpose.  It checks the stability of closed-loop control systems and
+considers finite-word length (FWL) effects in the digital controller and
+uncertainty parameters in the plant model (plant intervals)~\cite{Bessa16}. 
+Let $C(z)$ be a digital controller and $G(z)$ be a plant model given as
 %
@@
 %
-Due to the nature of the methods used for stability check in this paper, we
-require that the parametric errors in the plant have the same polynomial
-order as the plant itself (other errors are ensured to fulfil this property
-in our implementation).
-
-In order to simplify the notations in this paper, we will use a notation
-based on the coefficients of the polynomials.  Let $\mathcal{P}^{N}$ be a
-polynomial domain of order $N$ Let $P \in \mathcal{P}^{M,N}$ be a rational
-polynomial $\frac{P_n}{P_d} : P_n \in \mathcal{P}^{M} \wedge P_d \in
-\mathcal{P}^{N}$.  There is a vector of coefficients
+Due to the nature of the methods we use for the stability check, we require
+that the parametric errors in the plant have the same polynomial order as
+the plant itself (other errors are ensured to fulfil this property in our
+implementation).
+
+In order to simplify presentation, we will use notation based on the
+coefficients of the polynomials.  Let $\mathcal{P}^{N}$ be a polynomial
+domain of order $N$ Let $P \in \mathcal{P}^{M,N}$ be a rational polynomial
+$\frac{P_n}{P_d} : P_n \in \mathcal{P}^{M} \wedge P_d \in \mathcal{P}^{N}$. 
+There is a vector of coefficients
 %
@@
 \begin{equation}
-\Delta{\vec{P}}=[\Delta{n}_{0}\ \Delta{n}_{1}\ \hdots \ \Delta{n}_{M}\ \Delta{d}_{0}\ \Delta{d}_{1}\ \hdots\ \Delta{d}_{N}\ ]^T
+\Delta{\vec{P}}=[\Delta{n}_{0}\ \Delta{n}_{1}\ \hdots \ \Delta{n}_{M}\ \Delta{d}_{0}\ \Delta{d}_{1}\ \hdots\ \Delta{d}_{N}\ ]^T \;.
 \label{eq:coefficients}
@@
 
-A typical digital control system system, with a continuous plant and a discrete controller,
-is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters
-introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the
-continuous-time plant model with parametric additive uncertainty $\Delta_p
-\vec{G}_s$ , $R(z)$ is the reference signal, $U(z)$ is the control signal,
-and $\hat{Y}(z)$ is the output signal affected by the noises and
-uncertainties in the closed-loop system.
+A typical digital control system system with continuous plant and discrete
+controller is illustrated in Figure~\ref{fig:sampledsystem}.  The DAC and
+ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$,
+$G(s)$ is the continuous-time plant model with parametric additive
+uncertainty $\Delta_p \vec{G}_s$, $R(z)$ is the reference signal, $U(z)$ is
+the control signal, and $\hat{Y}(z)$ is the output signal affected by the
+noises and uncertainties in the closed-loop system.
 
@@
 
-The ADC and DAC may be abstracted changing the hybrid system in
-figure~\ref{fig:sampledsystem} to the digital system in
-figure~\ref{fig:digsystem1} where the parametric uncertainties are
-represented by $\Delta_p \vec{G}$
+The ADC and DAC may be abstracted by transforming the hybrid system in
+Figure~\ref{fig:sampledsystem} into the digital system in
+Figure~\ref{fig:digsystem1}, where the parametric uncertainties are
+represented by~$\Delta_p \vec{G}$
 %
@@
 and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is
-represented as an additive (output) measurement noise $\nu(z)$, thus
+represented as an additive (output) measurement noise $\nu(z)$.
+%, thus
 %$\hat{Y}(z)=Y(z)+\nu(z)$.  The measurement noise $\nu(k)$ is enough for
@@
 %
-In figure~\ref{fig:digsystem1}, two sources of uncertainties are considered: parametric uncertainties related to modelling errors, and uncertainties introduced by quantisations in sampling and holding process, {\it i.e.} ADC and DAC conversions.
-Assuming linearity and independence between these sources, the uncertain model may be rewritten as follows:
+In Figure~\ref{fig:digsystem1}, two sources of uncertainties are
+illustrated: parametric uncertainties related to modelling errors, and
+uncertainties introduced by quantisations in sampling and holding process,
+i.e., ADC and DAC conversions.  Assuming linearity and independence between
+these sources, the uncertain model may be rewritten as
+%
 \begin{equation}
@@
 change the closed-loop poles and zeros position, and consequently affect its
-stability, as shown in~\cite{Bessa16}.
+stability, as argued in~\cite{Bessa16}.
 
 Let $\hat{C}(z)$ be the transfer function of the digital controller
-represented using this FWL with integer size $I$ and fractional size $F$. 
+represented using this FWL with integer size $I$ and fractional size~$F$. 
 We shall denote the FWL domain of coefficients as $\mathbb{R}\langle I,F
@@
 %size $F$, we shall denote this domain as $\mathbb{R}\langle I,F \rangle$ 
-and assume that there exists a function $FWL[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$, which applies the FWL effects to a polynomial.
-$\mathcal{P}^{n}$ is the space of polynomials of $n$-th order and $\mathcal{P}^{n}\langle I,F \rangle$ is is the space of polynomials with coefficients in $\mathbb{R}\langle I,F \rangle$.
+%
+and assume that there exists a function
+$FWL[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$,
+which applies the FWL effects to a polynomial.  $\mathcal{P}^{n}$ is the
+space of polynomials of $n$-th order and $\mathcal{P}^{n}\langle I,F
+\rangle$ is is the space of polynomials with coefficients in
+$\mathbb{R}\langle I,F \rangle$.
+%
 %, \red{[explain index n! why do you need to work on a Euclidean domain?]}. 
 %
-Thus the perturbed controller model $\hat{C}(z)$ may be computed from the
+Thus, the perturbed controller model $\hat{C}(z)$ may be obtained from the
 original model $C(z)=\frac{N_{C}(z)}{D_{C}(z)}$ using the following

### 2016-10-13 paper/paper.tex
wordings
font

@@
 and assume that there exists a function
-$FWL[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$,
+$\mathit{FWL}[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$,
 which applies the FWL effects to a polynomial.  $\mathcal{P}^{n}$ is the
@@
 Thus, the perturbed controller model $\hat{C}(z)$ may be obtained from the
-original model $C(z)=\frac{N_{C}(z)}{D_{C}(z)}$ using the following
-expression:
+original model $C(z)=\frac{N_{C}(z)}{D_{C}(z)}$ as follows:
 %
 \begin{equation}
-\hat{C}(z)=\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}.
+\hat{C}(z)=\frac{\mathit{FWL}[N_{C}(z)]}{\mathit{FWL}[D_{C}(z)]}.
 \end{equation}
@@
 with a FWL implementation of the digital controller $\hat{C}(z) =
-\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete model of the
-plant $\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q \vec{G} \Rightarrow
-\hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and
-only if:
+\frac{\mathit{FWL}[N_{C}(z)]}{\mathit{FWL}[D_{C}(z)]}$ and uncertain
+discrete model of the plant $\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q
+\vec{G} \Rightarrow \hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is
+BIBO-stable if and only if:
 %
@@
 \label{eq:internal_stab_lemma}
-S(z)=FWL[N_{C}(z)]\hat{N}_{G}(z)+FWL[D_{C}(z)]\hat{D}_{G}(z);
+S(z)=\mathit{FWL}[N_{C}(z)]\hat{N}_{G}(z)+\mathit{FWL}[D_{C}(z)]\hat{D}_{G}(z);
 \end{equation}
-\item the direct loop product $\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle.
+\item the direct loop product $\frac{\mathit{FWL}[N_{C}(z)]}{\mathit{FWL}[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle.
 \end{itemize}

### 2016-10-13 paper/paper.tex

--- 2016-10-13 paper/paper.tex
@@
 There has been plenty of previous work that aims at \emph{verifying} a given
-controller designed by the engineer.  Recent work can show the of stability
+controller designed by the engineer.  Recent work can show the stability
 digital controllers with considerations to implementation aspects, i.e.,
@@
 
-\item We exploit a CEGIS-based approach that uses inductive synthesis
-together with a bit-precise formal verification algorithm for synthesising
-correct-by-design robust digital controllers for non-fragile closed-loop
-stability.
-
-\item Experimental results with our synthesiser show that the
-combination of interval arithmetic to represent the controller coefficients
-and a two-stage verification approach to continuously refine precision
-enables us to compute a parametric, sound solution for $14$ out of $15$
-digital stabilizing controllers for a set of continuous and discrete plants
-with parametric uncertainties.
+\item We designed and implemented an automatic approach for 
+generating {\em corect-by-construction} digital controllers that is 
+based on state-of-the-art inductive synthesis techniques.
+Our application of program synthesis is not trivial 
+and requires addressing challenges specific to
+control systems such as the effects of quantisers 
+and FWL. In particular, we found that a two-stage 
+verification engine that continuously refines the precision
+of the fixed-point representation is key to the performance of our approach.
+
+\item We provide experimental results showing that
+our fully automatic program synthesis based approach is able to synthesise 
+stable controllers
+%sound parametric solutions for digital stabilizing controllers
+for a set of intricate benchmarks taken from 
+the literature in a reasonable amount of time 
+(the median runtime for our benchmark set is 197s, 
+implying that half of the controllers can be synthesised in less
+than 5 minutes).
+
+%% \item We exploit a CEGIS-based approach, that uses inductive synthesis
+%% in conjunction with a formal verification algorithm, for synthesising 
+%% correct-by-design robust digital controllers for non-fragile closed-loop 
+%% stability.
+
+%% \item Experiments obtained with our synthesiser show that the combination 
+%% of interval arithmetic to represent the controller coefficients and a two-stage 
+%% verification approach to continuously refine precision, we are able to compute 
+%% a parametric sound solution for $14$ out of $15$ digital stabilizing controllers 
+%% given a set of continuous and discrete plant with parametric uncertainties.
 
@@
 
-The digital controllers synthesised using the algorithm we present in this
-paper are typically used in closed loops with continuous (and physical)
-plants.  Thus, the proposed approach has to consider dynamics of continuous
-parts of the system (i.e., the plant) and the discrete parts (i.e., the
-digital controller).  To obtain a joint model, the discretise the continuous
-plant.  We only consider transfer function models, and require a $z$-domain
-transfer function that captures all aspects of the continuous plant (with a
-Laplace domain transfer function $G(s)$) and the sampling and hold process.
-
-Note that $G(z)$ is a discrete model of a real-domain (and continuous)
-plant, i.e., the continuous model of the plant must be discretised to obtain
-the discrete equivalent coefficients via ZOH discretisation.
+The digital controllers synthesised in this paper are typically used in
+closed loops with continuous (and physical) plants.  Thus, the proposed
+approach has to consider dynamics of continuous parts of system ({\it e.g.},
+plant) and discrete parts ({\it e.g.}, digital controller).
+
+For this purpose, the design procedure is based on a discretised model for a
+continuous plant.  Considering only transfer function models, we are
+interested in a $z$-domain transfer function that considers all the aspects
+about the continuous plant ($G(s)$) and the sampling and hold process.
+
+Note that $G(z)$ is a discrete model of a real (and continuous) plant, i.e.,
+a continuous model of the plant must be discretised to obtain the discrete
+equivalent coefficients via ZOH discretisation.
 
@@
 more suitable for representing the sample and hold processes that are
-typically employed in complex systems~\cite{istepanian2012digital}, i.e.,
-the ZOH discretisation models the exact effect of sampling and DAC
+typically employed in complex systems~\cite{istepanian2012digital}, {\it
+i.e.}, the ZOH discretisation models the exact effect of sampling and DAC
 interpolation over the plant.
@@
 %
-The Sample and Hold of the ADC and the ZOH of the DAC are synchronized,
-i.e., there is no delay between sampling the plant output at ADC and
+The Sample and Hold of the ADC and the ZOH of the DAC are synchronized, {\it
+i.e.}, there is no delay between sampling the plant output at ADC and
 updating the DAC accordingly.  The DAC interpolator is an ideal ZOH.
@@
 
-Lemma~\ref{eq:pulsetf} ensures the poles and zeros matching with
-$\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$
-operations and includes the ZOH dynamics in the $(1-z^{-1})$ term, that is
-sufficient for the stability studies over $G(s)$.
+The lemma \ref{eq:pulsetf} is ensures the poles and zeros matching with $\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$ operations and includes the ZOH dynamics in the $(1-z^{-1})$ term, that is sufficient for the stability studies over $G(s)$
 

### 2016-10-13 paper/paper.tex
wordings

--- 2016-10-13 paper/paper.tex
@@
 %------------------------------------
-\subsection{On the stability considering effects of implementation issues and quantisation noises}
+\subsection{Stability under FWL and Noise}
 \label{sec:stability}
@@
 
-In order to obtain a sound synthesis of the digital controller, the effect
-of FWL implementation in controller and quantisation noises in closed loop
-system have to be considered.  Considering that the quantiser $Q1$ is the
-source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise
-$\nu_{2}$, the following equation is written for the system in
-Figure~\ref{fig:sampledsystem}, considering the parametric uncertainties
-$\Delta \vec{G}$ and the FWL effects on controller ($\hat{C}(z)$):
+Correct synthesis of the digital controller requires consideration of the
+effect of FWL in controller and quantisation noises in the closed loop
+system.  Let the quantiser $Q1$ be the source of a white noise $\nu_{1}$ and
+$Q2$ be the source of a white noise $\nu_{2}$.  The following equation
+models the system in Figure~\ref{fig:sampledsystem}, encompassing the
+parametric uncertainties $\Delta \vec{G}$ and the FWL effects on
+the controller ($\hat{C}(z)$):
 %
@@
 %
-that can be rewritten as follows:
+The above can be rewritten as follows:
 %
@@
 \begin{equation}
-H_{2}=\frac{\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
+H_{2}=\frac{\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)}.
 \end{equation}
@@
 %
-The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
-$Q2$) are uncorrelated white noises and their amplitudes are always bounded by the half of quantisation step \cite{astrom1997computer}, {\it i.e.} $\vert \nu_{1} \vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$, where $q_{1}$ and $q_{2}$ are respectively the quantisation step of  ADC and DAC.
+The quantisation noises $\nu_{1}$ (from $Q1$) and $\nu_{2}$ (from $Q2$) are
+uncorrelated white noises and their amplitudes are always bounded by the
+half of quantisation step~\cite{astrom1997computer}, i.e., $\vert \nu_{1}
+\vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$,
+where $q_{1}$ and $q_{2}$, respectively, are the quantisation steps of ADC
+and DAC.
 % 
@@
 (BIBO) stable if and only if every pole of its transfer function lies inside
-the unit circle.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following lemma
-states necessary conditions for BIBO stability of closed-loop system in
-Figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$,
+the unit circle.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following
+lemma states necessary conditions for BIBO stability of closed-loop system
+in Figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$,
 $\nu_{1}$, and $\nu_{2}$ are bounded.
@@
 
-The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for
-synthesis of digital controllers able to stabilize closed loop system,
-considering plant parametric uncertainties ({\it i.e.}, $\Delta_p \vec{G}$),
-quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital
-controllers.  Based on it, the model for plant uncertainty due quantisation
-noise ({\it i.e.}, $\Delta_q \vec{G}$) may be disregarded if the conditions
-on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise
-is bounded.  The quantisation noise is indeed bounded, since the following
+Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for the
+ability of a digital controller to stabilize the closed loop system,
+considering plant parametric uncertainties (i.e., $\Delta_p \vec{G}$),
+quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in the control
+software.  Based on it, the model for plant uncertainty due quantisation
+noise (i.e., $\Delta_q \vec{G}$) may be disregarded if the conditions on
+Lemma~\ref{lemma:eq_int_stab} are satisfied and if the quantisation noise is
+bounded.  The boundedness of the quantisation noise is
 assumption~\ref{whitenoise}.

### 2016-10-13 paper/paper.tex
wordings

@@
 %------------------------------------
-\subsection{Overview of the Synthesis Process using DSVerifier}
+\subsection{Overview of the Synthesis Process}
 \label{verification-flow}
@@
 
-An overview of the synthesis process is illustrated in
-Fig.~\ref{DSVerifier_process}; a detailed description of DSVerifier tool can
-be found in~\cite{IsmailBCFF15}.  Steps $1$ to $5$ are performed by the
-user/synthesiser and Steps A to D are automatically performed by DSVerifier.
+The synthesis process is illustrated in Fig.~\ref{DSVerifier_process}. 
+A~detailed description of DSVerifier tool can be found
+in~\cite{IsmailBCFF15}.  Steps $1$ to $5$ are performed by the
+user/synthesiser and Steps~A to D are automatically performed by DSVerifier.
 %
@@
 \vspace{1ex}
-\caption{Synthesis process using DSVerifier and the CBMC CEGIS module.}
-\label{DSVerifier_process}
+\caption{Overview of the synthesis process\label{DSVerifier_process}}
 \end{figure*}

### 2016-10-13 paper/paper.tex

--- 2016-10-13 paper/paper.tex
@@
 
-\item We exploit a CEGIS-based approach that uses inductive synthesis
-together with a bit-precise formal verification algorithm for synthesising
-correct-by-design robust digital controllers for non-fragile closed-loop
-stability.
-
-\item Experimental results with our synthesiser show that the
-combination of interval arithmetic to represent the controller coefficients
-and a two-stage verification approach to continuously refine precision
-enables us to compute a parametric, sound solution for $14$ out of $15$
-digital stabilizing controllers for a set of continuous and discrete plants
-with parametric uncertainties.
+\item We designed and implemented an automatic approach for 
+generating {\em corect-by-construction} digital controllers that is 
+based on state-of-the-art inductive synthesis techniques.
+Our application of program synthesis is non-trivial 
+and requires addressing challenges specific to
+control systems such as the effects of quantisers 
+and FWL. In particular, we found that a two-stage 
+verification engine that continuously refines the precision
+of the fixed-point representation is key to the performance of our approach
+(the increase in speed over a conventional one-stage verification 
+approach is in most cases of several orders of magnitude).
+
+\item We provide experimental results showing that
+our fully automatic program synthesis based approach is able to synthesise 
+stable controllers
+%sound parametric solutions for digital stabilizing controllers
+for a set of intricate benchmarks taken from 
+the literature in a reasonable amount of time 
+(the median runtime for our benchmark set is 197s, 
+implying that half of the controllers can be synthesised in less
+than 5 minutes).
+
+%% \item We exploit a CEGIS-based approach that uses inductive synthesis
+%% together with a bit-precise formal verification algorithm for synthesising
+%% correct-by-design robust digital controllers for non-fragile closed-loop
+%% stability.
+
+%% \item Experimental results with our synthesiser show that the
+%% combination of interval arithmetic to represent the controller coefficients
+%% and a two-stage verification approach to continuously refine precision
+%% enables us to compute a parametric, sound solution for $14$ out of $15$
+%% digital stabilizing controllers for a set of continuous and discrete plants
+%% with parametric uncertainties.
 
@@
 %------------------------------------
-\subsection{Stability under FWL and Noise}
+\subsection{On the stability considering effects of implementation issues and quantisation noises}
 \label{sec:stability}
@@
 
-Correct synthesis of the digital controller requires consideration of the
-effect of FWL in controller and quantisation noises in the closed loop
-system.  Let the quantiser $Q1$ be the source of a white noise $\nu_{1}$ and
-$Q2$ be the source of a white noise $\nu_{2}$.  The following equation
-models the system in Figure~\ref{fig:sampledsystem}, encompassing the
-parametric uncertainties $\Delta \vec{G}$ and the FWL effects on
-the controller ($\hat{C}(z)$):
+In order to obtain a sound synthesis of the digital controller, the effect
+of FWL implementation in controller and quantisation noises in closed loop
+system have to be considered.  Considering that the quantiser $Q1$ is the
+source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise
+$\nu_{2}$, the following equation is written for the system in
+Figure~\ref{fig:sampledsystem}, considering the parametric uncertainties
+$\Delta \vec{G}$ and the FWL effects on controller ($\hat{C}(z)$):
 %
@@
 %
-The above can be rewritten as follows:
+that can be rewritten as follows:
 %
@@
 \begin{equation}
-H_{2}=\frac{\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)}.
+H_{2}=\frac{\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
 \end{equation}
@@
 %
-The quantisation noises $\nu_{1}$ (from $Q1$) and $\nu_{2}$ (from $Q2$) are
-uncorrelated white noises and their amplitudes are always bounded by the
-half of quantisation step~\cite{astrom1997computer}, i.e., $\vert \nu_{1}
-\vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$,
-where $q_{1}$ and $q_{2}$, respectively, are the quantisation steps of ADC
-and DAC.
+The quantisation noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
+$Q2$) are uncorrelated white noises and their amplitudes are always bounded by the half of quantisation step \cite{astrom1997computer}, {\it i.e.} $\vert \nu_{1} \vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$, where $q_{1}$ and $q_{2}$ are respectively the quantisation step of  ADC and DAC.
 % 
@@
 (BIBO) stable if and only if every pole of its transfer function lies inside
-the unit circle.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following
-lemma states necessary conditions for BIBO stability of closed-loop system
-in Figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$,
+the unit circle.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following lemma
+states necessary conditions for BIBO stability of closed-loop system in
+Figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$,
 $\nu_{1}$, and $\nu_{2}$ are bounded.
@@
 
-Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for the
-ability of a digital controller to stabilize the closed loop system,
-considering plant parametric uncertainties (i.e., $\Delta_p \vec{G}$),
-quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in the control
-software.  Based on it, the model for plant uncertainty due quantisation
-noise (i.e., $\Delta_q \vec{G}$) may be disregarded if the conditions on
-Lemma~\ref{lemma:eq_int_stab} are satisfied and if the quantisation noise is
-bounded.  The boundedness of the quantisation noise is
+The Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for
+synthesis of digital controllers able to stabilize closed loop system,
+considering plant parametric uncertainties ({\it i.e.}, $\Delta_p \vec{G}$),
+quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in digital
+controllers.  Based on it, the model for plant uncertainty due quantisation
+noise ({\it i.e.}, $\Delta_q \vec{G}$) may be disregarded if the conditions
+on Lemma~\ref{lemma:eq_int_stab} are attended and if the quantisation noise
+is bounded.  The quantisation noise is indeed bounded, since the following
 assumption~\ref{whitenoise}.

### 2016-10-13 paper/paper.tex
revised contributions

@@
 of the fixed-point representation is key to the performance of our approach 
-(the increase in speed over a conventional one-stage verification 
-approach is in most cases of several orders of magnitude).
+yielding, in most cases,  a speed-up  
+of several orders of magnitude over 
+a conventional one-stage verification 
+approach.
 

### 2016-10-13 paper/paper.tex
nudges

@@
 
-\item We designed and implemented an automatic approach for 
-generating {\em corect-by-construction} digital controllers that is 
-based on state-of-the-art inductive synthesis techniques.
-Our application of program synthesis is non-trivial 
-and requires addressing challenges specific to
-control systems such as the effects of quantisers 
-and FWL. In particular, we found that a two-stage 
-verification engine that continuously refines the precision
-of the fixed-point representation is key to the performance of our approach 
-yielding, in most cases,  a speed-up  
-of several orders of magnitude over 
-a conventional one-stage verification 
-approach.
-
-\item We provide experimental results showing that
-our fully automatic program synthesis based approach is able to synthesise 
-stable controllers
-%sound parametric solutions for digital stabilizing controllers
-for a set of intricate benchmarks taken from 
-the literature in a reasonable amount of time 
-(the median runtime for our benchmark set is 197s, 
-implying that half of the controllers can be synthesised in less
-than 5 minutes).
-
-%% \item We exploit a CEGIS-based approach that uses inductive synthesis
-%% together with a bit-precise formal verification algorithm for synthesising
-%% correct-by-design robust digital controllers for non-fragile closed-loop
-%% stability.
-
-%% \item Experimental results with our synthesiser show that the
-%% combination of interval arithmetic to represent the controller coefficients
-%% and a two-stage verification approach to continuously refine precision
-%% enables us to compute a parametric, sound solution for $14$ out of $15$
-%% digital stabilizing controllers for a set of continuous and discrete plants
-%% with parametric uncertainties.
+\item We exploit a CEGIS-based approach that uses inductive synthesis
+together with a bit-precise formal verification algorithm for synthesising
+correct-by-design robust digital controllers for non-fragile closed-loop
+stability.
+
+\item Experimental results with our synthesiser show that the
+combination of interval arithmetic to represent the controller coefficients
+and a two-stage verification approach to continuously refine precision
+enables us to compute a parametric, sound solution for $14$ out of $15$
+digital stabilizing controllers for a set of continuous and discrete plants
+with parametric uncertainties.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Automated Program Synthesis \\ for Digital Controllers}
+\section{Automated Program Synthesis \\ for Digital Control}
 
@@
 
-\subsection{General architecture of the program synthesiser}
+\subsection{Architecture of the program synthesiser}
 \label{synthesiser-general}
@@
 
-\subsection{Synthesis elements specific to control systems}
+\subsection{Synthesis for to control}
 \label{synthesis-elements}

### 2016-10-13 paper/paper.tex
hscc17

--- 2016-10-13 paper/paper.tex
@@
 \title{
-Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants
+Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants
 %Counterexample-guided Synthesis of Closed-loop Digital Control Systems
@@
 This poses a new dimension to the problem of controllers synthesis, which is
-classically studied in digital control literature.
+classically studied in the digital control literature.
 %
 In this study, we plan to provide a principled approach to extend this
-literature in a number of directions: we are interested in quantitative
-tasks; we focus on automated correct-by-construction synthesis algorithms, as
-opposed to verification objectives; and we encompass the complete range of
+literature in a number of directions: 
+%we are interested in quantitative tasks; 
+we focus on automated correct-by-construction synthesis algorithms, as
+opposed to verification (or validation) objectives over a designed architecture; 
+and we encompass the complete range of
 approximations, related to time discretisation, quantisation effects, and
@@
 of the fixed-point representation is key to the performance of our approach
-yielding, in most cases,  a speed-up  
-of several orders of magnitude over 
-a conventional one-stage verification 
-approach.
+(the increase in speed over a conventional one-stage verification 
+approach is in most cases of several orders of magnitude).
 

### 2016-10-13 paper/paper.tex
moved sec 2.4 into sec 3
wordings

@@
 
-\item We provide experimental results showing that
-our fully automatic program synthesis based approach is able to synthesise 
-stable controllers
-%sound parametric solutions for digital stabilizing controllers
-for a set of intricate benchmarks taken from 
-the literature in a reasonable amount of time 
-(the median runtime for our benchmark set is 197s, 
-implying that half of the controllers can be synthesised in less
-than 5 minutes).
+\item We provide experimental results showing that our fully automatic
+program synthesis based approach is able to synthesise stable controllers
+for a set of intricate benchmarks taken from the literature efficiently: the
+median runtime for our benchmark set is $197$s, i.e., half of the
+controllers can be synthesised in less than five minutes.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Automated Program Synthesis \\ for Digital Control}
+
 %------------------------------------
@@
 %\red{[TO BE COMPLETED.]}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Automated Program Synthesis \\ for Digital Control}
-
 % We use CounterExample-Guided Inductive Synthesis (CEGIS), as

### 2016-10-13 paper/paper.tex
wordings

@@
 
-\item We provide experimental results showing that our fully automatic
-program synthesis based approach is able to synthesise stable controllers
-for a set of intricate benchmarks taken from the literature efficiently: the
-median runtime for our benchmark set is $197$s, i.e., half of the
-controllers can be synthesised in less than five minutes.
+\item We provide experimental results showing that our tool is able to
+synthesise stable controllers for a set of intricate benchmarks taken from
+the literature efficiently: the median runtime for our benchmark set is
+$197$s, i.e., half of the controllers can be synthesised in less than five
+minutes.
 

### 2016-10-13 paper/paper.tex
small edit contributions

--- 2016-10-13 paper/paper.tex
@@
 \title{
-Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants
+Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants
 %Counterexample-guided Synthesis of Closed-loop Digital Control Systems
@@
 This poses a new dimension to the problem of controllers synthesis, which is
-classically studied in the digital control literature.
+classically studied in digital control literature.
 %
 In this study, we plan to provide a principled approach to extend this
-literature in a number of directions: 
-%we are interested in quantitative tasks; 
-we focus on automated correct-by-construction synthesis algorithms, as
-opposed to verification (or validation) objectives over a designed architecture; 
-and we encompass the complete range of
+literature in a number of directions: we are interested in quantitative
+tasks; we focus on automated correct-by-construction synthesis algorithms, as
+opposed to verification objectives; and we encompass the complete range of
 approximations, related to time discretisation, quantisation effects, and
@@
 a conventional one-stage verification 
-approach.
+engine.
 
@@
 %------------------------------------
-\subsection{Overview of the Synthesis Process}
+\subsection{Overview of the Synthesis Process using DSVerifier}
 \label{verification-flow}
@@
 
-The synthesis process is illustrated in Fig.~\ref{DSVerifier_process}. 
-A~detailed description of DSVerifier tool can be found
-in~\cite{IsmailBCFF15}.  Steps $1$ to $5$ are performed by the
-user/synthesiser and Steps~A to D are automatically performed by DSVerifier.
+An overview of the synthesis process is illustrated in
+Fig.~\ref{DSVerifier_process}; a detailed description of DSVerifier tool can
+be found in~\cite{IsmailBCFF15}.  Steps $1$ to $5$ are performed by the
+user/synthesiser and Steps A to D are automatically performed by DSVerifier.
 %
@@
 \vspace{1ex}
-\caption{Overview of the synthesis process\label{DSVerifier_process}}
+\caption{Synthesis process using DSVerifier and the CBMC CEGIS module.}
+\label{DSVerifier_process}
 \end{figure*}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Automated Program Synthesis \\ for Digital Control}
+\section{Automated Program Synthesis \\ for Digital Controllers}
 
@@
 
-\subsection{Architecture of the program synthesiser}
+\subsection{General architecture of the program synthesiser}
 \label{synthesiser-general}
@@
 
-\subsection{Synthesis for to control}
+\subsection{Synthesis elements specific to control systems}
 \label{synthesis-elements}

### 2016-10-13 paper/paper.tex
captions
modify figure 3

--- 2016-10-13 paper/paper.tex
@@
 }
- \caption{Sampled System. \label{fig:sampledsystem}}
+ \caption{Closed-loop digital control system\label{fig:sampledsystem}}
 \end{figure*}
@@
 }
- \caption{Digital system equivalent to ~\ref{fig:sampledsystem}. \label{fig:digsystem1}}
+\caption{System equivalent to the system in Figure~\ref{fig:sampledsystem}\label{fig:digsystem1}}
 \end{figure}
@@
 A~detailed description of DSVerifier tool can be found
-in~\cite{IsmailBCFF15}.  Steps $1$ to $5$ are performed by the
+in~\cite{IsmailBCFF15}.  Steps $1$ to $3$ are performed by the
 user/synthesiser and Steps~A to D are automatically performed by DSVerifier.
@@
 Given a model for a plant for which to synthesize a controller, provided in
-an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
+an ANSI-C code input file (Steps 1-3), DSVerifier constructs a
 non-deterministic model to represent the plant family (Step A), and
 formulates a function (step B) using implementation details provided from
-Steps $2$ and $3$ to calculate the parameters of the controller to be
+Step $2$ and $3$ to calculate the parameters of the controller to be
 synthesized (step C).  Finally DSVerifier builds an intermediate ANSI-C code

### 2016-10-13 paper/paper.tex
use a unified notation for the two verification engines in sec 3 and 4

--- 2016-10-13 paper/paper.tex
@@
 
+In the rest of the paper, we will refer to the two approaches 
+for the {\sc verify} phase as one-stage and two-stage, respectively.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 For the majority of our benchmarks, the conjecture explained in
-section~\ref{synthesis-elements} holds and the inductive back-end is able to
-find a stable solution in less than one minute.  This is possible if the
+Section~\ref{synthesis-elements} holds and the two-stage verification 
+engine %inductive back-end 
+is able to find a stable solution in less than one minute.  This is possible if the
 inductive solutions need to be refined with few counterexamples and
@@
 required too many counterexamples to refine their solution (marked with $^*$
-in Table~\ref{tab:results}).  In these cases, the interval arithmetic
-back-end is able to complement the inductive approach and synthesise a
+in Table~\ref{tab:results}).  In these cases, the one-stage engine 
+%interval arithmetic back-end 
+is able to complement the two-stage approach and synthesise a
 solution instead, albeit with significantly larger runtimes.  This
-performance difference is due to the fact that the interval back-end does
+performance difference is due to the fact that the one-stage verification engine does
 not take advantage of the inductive conjecture inherent to CEGIS, but
@@
 performance difference of at least two orders of magnitude in our
-experiments, leading to the interval back-end timing out on the majority of
+experiments, leading to the one-stage engine timing out on the majority of
 our benchmarks.  Table~\ref{tab:results} only lists the faster of the two
-back-ends for each benchmark, which in $12$ out of $15$ benchmarks is the
-inductive back-end.
+verification engines for each benchmark, which in $12$ out of $15$ benchmarks is the
+two-stage one.
 
@@
 short enough to be of practical use to control engineers.  Regarding RQ1 we
-further conclude that the inductive back-end is able to synthesise stable
+further conclude that the two-stage verification engine is able to synthesise stable
 controllers in the $12$ out of $15$ benchmarks, and can be complemented
-using the interval arithmetic back-end for $2$ additional benchmarks, where
-the inductive conjectures fail.  Both back-ends together enabled controller
+using the one-stage engine for $2$ additional benchmarks, where
+the inductive conjectures fail.  Both verification engines together enabled controller
 synthesis for $14$ out of $15$ benchmarks.  For the $1$ remaining benchmark

### 2016-10-13 paper/paper.tex
fix typo
small edit

@@
 short enough to be of practical use to control engineers.  Regarding RQ1 we
-further conclude that the two-stage verification engine is able to synthesise stable
+further conclude that the approach using a 
+two-stage verification engine is able to synthesise stable
 controllers in the $12$ out of $15$ benchmarks, and can be complemented

### 2016-10-13 paper/paper.tex
revised contibutions to match experiments

@@
 
-\item We designed and implemented an automatic approach for 
-generating {\em corect-by-construction} digital controllers that is 
-based on state-of-the-art inductive synthesis techniques.
-Our application of program synthesis is non-trivial 
-and requires addressing challenges specific to
-control systems such as the effects of quantisers 
-and FWL. In particular, we found that a two-stage 
-verification engine that continuously refines the precision
-of the fixed-point representation is key to the performance of our approach 
-yielding, in most cases,  a speed-up  
-of several orders of magnitude over 
-a conventional one-stage verification 
-engine.
+\item We designed and implemented an automatic approach for generating
+  {\em corect-by-construction} digital controllers that is based on
+  state-of-the-art inductive synthesis techniques.  Our application of
+  program synthesis is non-trivial and requires addressing challenges
+  specific to control systems such as the effects of quantisers and
+  FWL. In particular, we found that a two-stage verification engine
+  that continuously refines the precision of the fixed-point
+  representation is key to the performance of our approach yielding,
+  in most cases, a speed-up of at least two orders of magnitude over a
+  conventional one-stage verification engine.
 
@@
 
-\subsection{Synthesis for to control}
+\subsection{Synthesis for control}
 \label{synthesis-elements}

### 2016-10-13 paper/paper.tex
change color from yellow to gray in figure 1

--- 2016-10-13 paper/paper.tex
@@
 	label=\textbf{DAC},] (dac) {};
-     \node[circle,add={}{+}{+}{},fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {};
+     \node[circle,add={}{+}{+}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
      \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
      \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
-     \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}   
+     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}   
    \& \node[rectangle,draw,
@@
    \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
-   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
+   \node[circle,add={}{+}{+}{},fill=gray!20] (q1) at ([xshift=1cm]adc.center) {};} 
      \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};

### 2016-10-13 paper/paper.tex
editing

@@
 of RAM, and Linux OS.  All times given are wall clock time in seconds as measured
-by the UNIX date command.  For the inductive back-end, we apply a timeout of 8 hours
-per benchmark, and 24 hours for the interval arithmetic back-end.
+by the UNIX date command.  For the approach using a two-stage verification engine
+we apply a timeout of 8 hours
+per benchmark, and 24 hours for the approach using a one-stage engine.
 
@@
 \vspace{0.5em}
-\scriptsize{* = solved with interval back-end, $\dagger$ = with uncertainty}
+\scriptsize{* = solved with the one-stage engine, $\dagger$ = with uncertainty}
 \vspace{0.5em}

### 2016-10-13 paper/paper.tex
minor corrections in contributions

@@
   program synthesis is non-trivial and requires addressing challenges
-  specific to control systems such as the effects of quantisers and
+  specific to embedded control systems such as the effects of quantisers and
   FWL. In particular, we found that a two-stage verification engine
@@
   representation is key to the performance of our approach yielding,
-  in most cases, a speed-up of at least two orders of magnitude over a
+  in most cases, to a speed-up of at least two orders of magnitude over a
   conventional one-stage verification engine.

### 2016-10-13 paper/paper.tex
izing vs ising explanation of first approach

@@
 We only consider transfer function models, and require a $z$-domain
-transfer function that captures all aspects of the continuous plant (with a
+transfer function $G(z)$ that captures all aspects of the continuous plant (with a
 Laplace domain transfer function $G(s)$) and the sampling and hold process.
-Note that $G(z)$ is a discrete model of a real-domain (and continuous)
+Note that $G(z)$ is a discrete model of a physical, continuous
 plant, i.e., the continuous model of the plant must be discretised to obtain
@@
 %
-The Sample and Hold of the ADC and the ZOH of the DAC are synchronized,
+The Sample and Hold of the ADC and the ZOH of the DAC are synchronised,
 i.e., there is no delay between sampling the plant output at ADC and
@@
 %
-Given a synchronized ZOH input and sample and hold output on the plant with
+Given a synchronised ZOH input and sample and hold output on the plant with
 a sample time $T$ satisfying Nyquist's sampling criteria, the discrete pulse
@@
 
-Given a model for a plant for which to synthesize a controller, provided in
+Given a model for a plant for which to synthesise a controller, provided in
 an ANSI-C code input file (Steps 1-3), DSVerifier constructs a
@@
 Step $2$ and $3$ to calculate the parameters of the controller to be
-synthesized (step C).  Finally DSVerifier builds an intermediate ANSI-C code
+synthesised (step C).  Finally DSVerifier builds an intermediate ANSI-C code
 for the digital system implementation, which is used as input for the
@@
 Synthesis (CEGIS) module, where the controller is marked as input variable
-to synthesize.  The properties specified in the ANSI-C code model can only
-be satisfied if CEGIS synthesizes controller coefficients satisfying $\phi$. 
+to synthesise.  The properties specified in the ANSI-C code model can only
+be satisfied if CEGIS synthesises controller coefficients satisfying $\phi$. 
 CEGIS employs an iterative, counterexample-guided refinement process which
@@
 with respect to $\phi$.  In particular, the ANSI-C code model guarantees
-that a synthesized solution is complete and sound with respect to stability
+that a synthesised solution is complete and sound with respect to stability
 property $\phi$, since it does not depend on system inputs and outputs.  In
@@
 {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
-and rounds operations outwards during calculations. 
-%\cdsay{dario, what coefficients are these?}
-% This results in a
-% tighter calculation of the error at the cost of
-% performance.
+and rounds operations outwards during calculations. This effectively allows
+us to simultaneously evaluate the whole collection of plants $\mathfrak{G}$
+plus the effects of numeric calculations in the engine.
 Synthesised controllers using this verifier will always
-be correct and only generate counterexamples when the precision of the
-engine is insufficient. Given the high computational cost of this
+be stable for all plants in the family and only generate counterexamples when the precision of the
+engine is insufficient (\emph{ie} no stable plant could be found). Given the high computational cost of this
 approach, we also designed a second approach, which we describe below.
@@
 a continuous (or discrete) plant specification.  This enables us to automatically
-synthesize correct-by-construction digital controllers for a given model of
+synthesise correct-by-construction digital controllers for a given model of
 their physical environment.  Our approach addresses the effects of the

### 2016-10-13 paper/paper.tex
second stage soundness restoration

@@
 The second approach is illustrated in Fig.~\ref{fig:CEGIS} and 
-uses a two-stage verification such that in the first stage it 
-assumes a certain precision \param{I_b}{F_b}, whose 
-soundness is checked in the second verification stage.
+uses a two-stage verification with a first stage that performs unsound fixed point operations given the precision \param{I_b}{F_b}, and a second stage that restores soundness by validating these operations using interval arithmetic on the synthesised plant.
 

### 2016-10-13 paper/paper.tex
revised the description of the one-stage engine

@@
 Synthesised controllers using this verifier will always
-be stable for all plants in the family and only generate counterexamples when the precision of the
-engine is insufficient (\emph{ie} no stable plant could be found). Given the high computational cost of this
-approach, we also designed a second approach, which we describe below.
+be stable for all plants in the family.
+% and only generate counterexamples when the precision of the
+%engine is insufficient (\emph{ie} no stable plant could be found). 
+Our preliminary experiments showed that a synthesis approach
+using this verification engine has poor performance and we
+%Given the high computational cost of this
+%approach, 
+therefore designed a second approach, which we describe below.
 Our experimental results described in Sec.~\ref{sec:experiments}, 
 %try both approaches and provide the time for the fastest. 
-show that the increase in speed of the second approach 
-over the first one is in most cases of several orders of magnitude.
+show that the speedup yielded by the second approach 
+is in most cases of several orders of magnitude.
 

### 2016-10-13 paper/paper.tex
revised description of two-stage verifier

@@
 
-The second approach is illustrated in Fig.~\ref{fig:CEGIS} and 
-uses a two-stage verification with a first stage that performs unsound fixed point operations given the precision \param{I_b}{F_b}, and a second stage that restores soundness by validating these operations using interval arithmetic on the synthesised plant.
+The second approach is illustrated in Fig.~\ref{fig:CEGIS} and uses a
+two-stage verification: the first stage performs potentially unsound
+fixed-point operations assuming a precision \param{I_b}{F_b}, and the
+second stage restores soundness by validating these operations
+using interval arithmetic on the synthesised controller.
 

### 2016-10-13 paper/paper.tex
typo

@@
 
-In order to exploit the present approach full potential, a dynamical plant that can
-present physical components must be considered.  However, a discrete plant
-model can also demonstrate some benefits of the present approach, which
-considers FWL effects in the digital controller implementation.  In
-particular, a classical cruise control example is extracted from the
-literature~\cite{Astrom08}, where the discrete plant model (with time step
-of $0.2$s) is represented by the following z-expression:
+In order to exploit the full potential of the present approach, a
+dynamical plant that can present physical components must be
+considered.  However, a discrete plant model can also demonstrate some
+benefits of the present approach, which considers FWL effects in the
+digital controller implementation.  In particular, a classical cruise
+control example is extracted from the literature~\cite{Astrom08},
+where the discrete plant model (with time step of $0.2$s) is
+represented by the following z-expression:
 %
@@
 We will illustrate our synthesis approach on the running example
-in Sec.~\ref{sec:running-ex}.
+described in the previous section. 
+%in Sec.~\ref{sec:running-ex}.
 We start with the candidate solution with all coefficients zero 

### 2016-10-14 paper/paper.tex
typos

@@
 plants.  Thus, the proposed approach has to consider dynamics of continuous
-parts of the system (i.e., the plant) and the discrete parts (i.e., the
-digital controller).  To obtain a joint model, the discretise the continuous
+parts of the system (i.e., the plant) and the discreted parts (i.e., the
+digital controller).  To obtain a joint model, we discretise the continuous
 plant. We briefly recall the standard foundations of this step.

### 2016-10-14 paper/paper.tex
typo intro

@@
 operates on bit-vectors encoded using fixed-point arithmetic with fixed word
-length (FWL).  We calculate the deterministic effect of the FWL and
+length (FWL).  The deterministic effects of the FWL and
 quantisation errors are incorporated into the model as an additive

### 2016-10-14 paper/paper.tex
fix right column in page 2

--- 2016-10-13 paper/paper.tex
@@
 
-Lemma~\ref{eq:pulsetf} ensures the poles and zeros matching with
+Here, Lemma~\ref{eq:pulsetf} ensures the poles and zeros matching with
 $\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$

### 2016-10-14 paper/paper.tex
undo a typo fix by Cristina

--- 2016-10-14 paper/paper.tex
@@
 plants.  Thus, the proposed approach has to consider dynamics of continuous
-parts of the system (i.e., the plant) and the discreted parts (i.e., the
+parts of the system (i.e., the plant) and the discrete parts (i.e., the
 digital controller).  To obtain a joint model, we discretise the continuous

### 2016-10-14 paper/paper.tex
resized gif 1

--- 2016-10-14 paper/paper.tex
@@
 plants.  Thus, the proposed approach has to consider dynamics of continuous
-parts of the system (i.e., the plant) and the discrete parts (i.e., the
+parts of the system (i.e., the plant) and the discreted parts (i.e., the
 digital controller).  To obtain a joint model, we discretise the continuous
@@
 
-\resizebox{.8\textwidth}{!}{
+\resizebox{.9\textwidth}{!}{
  \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,

### 2016-10-14 paper/paper.tex
nudges

--- 2016-10-14 paper/paper.tex
@@
 
-We outline the runtimes required to synthesise a stable controller for each
+We give the runtimes required to synthesise a stable controller for each
 benchmark in Table~\ref{tab:results}.  Here, \textit{Plant} is the discrete
@@
 fractional bits of the stable controller, respectively, while \textit{Time}
-represents the total time (in seconds) to synthesise a stable controller for
-the given plant.
+is the total time (in seconds) required to synthesise a stable controller
+for the given plant.
 
@@
 inductive solutions need to be refined with few counterexamples and
-fixed-point precision increases.  However, $2$ benchmarks in our set
+fixed-point precision increases.  However, two benchmarks in our set
 required too many counterexamples to refine their solution (marked with $^*$
@@
 %interval arithmetic back-end 
-is able to complement the two-stage approach and synthesise a
-solution instead, albeit with significantly larger runtimes.  This
-performance difference is due to the fact that the one-stage verification engine does
+is able to complement the two-stage approach and synthesise a solution
+instead, albeit with significantly larger runtimes.  This performance
+difference is due to the fact that the one-stage verification engine does
 not take advantage of the inductive conjecture inherent to CEGIS, but
@@
 our benchmarks.  Table~\ref{tab:results} only lists the faster of the two
-verification engines for each benchmark, which in $12$ out of $15$ benchmarks is the
-two-stage one.
+verification engines for each benchmark, which in $12$ out of $15$
+benchmarks is the two-stage one.
 
@@
 the controllers can be synthesised in less than $5$ minutes using our
-present approach.  Overall the average synthesis time amounts to
+present approach.  Overall, the average synthesis time amounts to
 approximately $30$ minutes.  With respect to RQ2 we consider these times
 short enough to be of practical use to control engineers.  Regarding RQ1 we
-further conclude that the approach using a 
-two-stage verification engine is able to synthesise stable
-controllers in the $12$ out of $15$ benchmarks, and can be complemented
-using the one-stage engine for $2$ additional benchmarks, where
-the inductive conjectures fail.  Both verification engines together enabled controller
-synthesis for $14$ out of $15$ benchmarks.  For the $1$ remaining benchmark
-our approach failed to synthesise a stable controller in the requested time
-limits.  This can be addressed by either increasing the fixed point word
-widths considered or using floating point arithmetic instead.  A link to the
-full experimental environment, including scripts to reproduce the
-experiment, all benchmarks and the CEGIS tool is provided in the
+further conclude that the approach using a two-stage verification engine is
+able to synthesise stable controllers in the $12$ out of $15$ benchmarks,
+and can be complemented using the one-stage engine for $2$ additional
+benchmarks, where the inductive conjectures fail.  Both verification engines
+together enabled controller synthesis for $14$ out of $15$ benchmarks.  For
+the $1$ remaining benchmark our approach failed to synthesise a stable
+controller in the requested time limits.  This can be addressed by either
+increasing the fixed point word widths considered or using floating point
+arithmetic instead.  A link to the full experimental environment, including
+scripts to reproduce the experiment, all benchmarks and the CEGIS tool is
+provided in the
 footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}
@@
 response~\cite{Duggirala2015}, and Finite Word Length (FWL) constraints with
-the goal to either verify ({\it e.g.}, \cite{daes20161}) or optimise ({\it
-e.g.},~\cite{oudjida2014design}) implementations.  There are in fact two
+the goal to either verify (e.g.~\cite{daes20161}) or optimise
+(e.g.~\cite{oudjida2014design}) implementations.  There are in fact two
 different problems arising from FWL effects.  The first corresponds to the
@@
 the exact dynamics of the system whilst the second relates to rounding
-errors during computation.  In \cite{fialho1994stability} a stability
+errors during computation.  In~\cite{fialho1994stability} a stability
 measure based on the error of the digital dynamics ensures that the FWL
@@
 effects of rounding errors due to issues of mathematical tractability.  The
-analyses in~\cite{DBLP:conf/hybrid/WangGRJF16,DBLP:conf/hybrid/RouxJG15}
+analyses in~\cite{DBLP:conf/hybrid/WangGRJF16, DBLP:conf/hybrid/RouxJG15}
 rely on an invariant computation on the discrete system dynamics using
@@
 In both cases, the SDP solver uses floating-point arithmetic and soundness
-is checked by upper bounding the error.  An alternative approach is taken by
-\cite{park2016scalable}, where the verification of existing code is
+is checked by upper bounding the error.  An alternative approach is taken
+by~\cite{park2016scalable}, where the verification of existing code is
 performed against a known model by extracting an LTI model of the code
@@
 is an approach that synthesises word lengths for known problems as developed
-in \cite{jha2013swati}; however, this provides neither an optimal word
+in~\cite{jha2013swati}; however, this provides neither an optimal word
 synthesis nor a comprehensive solution for the problem.  It is from this

### 2016-10-14 paper/paper.tex
add plants g_4a, g_4b, and g_4c

--- 2016-10-14 paper/paper.tex
@@
 \begin{equation}
-G_{3}(z)= \frac{T^{2}}{2} \frac{z+1}{(z+1)^{2}}.
+G_{3}(z)= \frac{T^{2}}{2} \frac{z+1}{(z+1)^{2}}. \nonumber
 \end{equation}
@@
 in Eq.~\eqref{eq:pulsetf} with $3$ different sample times ($0.1$, $0.05$, and $0.03$ 
-seconds).
+seconds) respectively, as follows
+%
+\begin{equation}
+\label{exampleA-sampletime1}
+G_{4a}(s)=\frac{0.100342181002722z - 0.110876810062963}{1.0z^{2} - 2.12624017619613z + 1.10517091807565}, \nonumber
+\end{equation}
+%
+%
+\begin{equation}
+\label{exampleA-sampletime2}
+G_{4b}(s)=\frac{0.0500422033454653z - 0.0526068264456340}{1.0^{2} - 2.05640034257636z + 1.05127109637602}, \nonumber
+\end{equation}
+%
+%
+\begin{equation}
+\label{exampleA-sampletime3}
+G_{4c}(s)=\frac{0.0300090687252212z - 0.0309228417953966}{1.0^{2} - 2.03228208009387z + 1.03045453395352}. \nonumber
+\end{equation}
 
@@
 8  & $G_3$  & SatelliteC2$^\dagger$      &   3 &   5 & 76\,s   & \tbmark\\
-9  & $G_4$ & a\_ST1\_IMPL1              &  16 &   4 & 2704\,s & \\
-10 & $G_4$ & a\_ST1\_IMPL2              &  16 &   8 & 538\,s  & \\
-11 & $G_4$ & a\_ST1\_IMPL3              &  16 &  12 & 12\,s   & \\
-12 & $G_4$ & a\_ST2\_IMPL1              &  16 &   4 & 318\,s  & \\
-13 & $G_4$ & a\_ST2\_IMPL2              &  16 &   8 & 967\,s  & \\
-14 & $G_4$ & a\_ST2\_IMPL3              &  16 &  12 & 9798\,s & \\
-15 & $G_4$ & a\_ST3\_IMPL1              &  16 &   4 & 6304\,s & \\
+9  & $G_4a$ & a\_ST1\_IMPL1              &  16 &   4 & 2704\,s & \\
+10 & $G_4a$ & a\_ST1\_IMPL2              &  16 &   8 & 538\,s  & \\
+11 & $G_4a$ & a\_ST1\_IMPL3              &  16 &  12 & 12\,s   & \\
+12 & $G_4b$ & a\_ST2\_IMPL1              &  16 &   4 & 318\,s  & \\
+13 & $G_4b$ & a\_ST2\_IMPL2              &  16 &   8 & 967\,s  & \\
+14 & $G_4b$ & a\_ST2\_IMPL3              &  16 &  12 & 9798\,s & \\
+15 & $G_4c$ & a\_ST3\_IMPL1              &  16 &   4 & 6304\,s & \\
 \end{tabular}

### 2016-10-14 paper/paper.tex
replace s by z in g4
nudges

--- 2016-10-14 paper/paper.tex
@@
 control example is extracted from the literature~\cite{Astrom08},
-where the discrete plant model (with time step of $0.2$s) is
-represented by the following z-expression:
+where the discrete plant model (with a time step of $0.2$s) is
+represented by the following $z$-expression:
 %
@@
 has designed a high-performance controller, which is characterised by the
-following z-domain transfer function:
+following $z$-domain transfer function:
 %
@@
 %
-The authors claim that this controller $C(z)$ (Eq.~\eqref{Eq:running-example-plant}) 
-stabilizes the closed-loop system for the discrete plant model $G(z)$ (Eq.~\ref{Eq:running-example-controller}).  
-However, if implementation aspects are considered during verification ({\it e.g.}, fixed-point
-arithmetic and word-length), then this closed-loop system becomes unstable.
-%
-Indeed, the actual implementation of $C(z)$ using \param{4}{16}
-implementation format ({\it i.e.}, $4$ bits for the integer part and $16$
-bits for the fractional part) can be represented by the following
-expression:
+The authors claim that this controller $C(z)$
+(Eq.~\eqref{Eq:running-example-plant}) stabilizes the closed-loop system for
+the discrete plant model $G(z)$ (Eq.~\ref{Eq:running-example-controller}). 
+However, if implementation aspects are considered during verification (e.g.,
+fixed-point arithmetic and word-length), then this closed-loop system
+becomes unstable.
+%
+For instance, an implementation of $C(z)$ using \param{4}{16} fixed-point
+numbers (i.e., $4$ bits for the integer part and $16$ bits for the
+fractional part) can be modeled as follows:
 %
@@
 C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
-{+}1.895996}{z^2{-}1.843994z+0.849594},
+{+}1.895996}{z^2{-}1.843994z+0.849594} \;.
 \end{equation} 
 %
-which makes the system unstable in closed-loop using fixed-point arithmetic
-and the typical series loop configuration, where $C_{q}\left(z\right)$ and
-$G\left(z\right)$ are in the forward path.
-
-\subsubsection{Program synthesis for the illustrative example}
+The resulting system using the typical series loop configuration, where
+$C_{q}\left(z\right)$ and $G\left(z\right)$ are in the forward path, is
+unstable.
+
+\subsection{Program synthesis for the example}
+
 We will illustrate our synthesis approach on the running example
@@
 techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
+%
 %\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
-
+%
 %$$
@@
 check finds the following counterexample:
-
+%
 $$
@@
 
-We add this counterexample to {\sc inputs} and initiate the {\sc synthesise} phase, where we get the following candidate solution: 
+We add this counterexample to {\sc inputs} and initiate the {\sc synthesise}
+phase, where we get the following candidate solution:
+%
 %\red{[ How is the order of the candidate solution chosen here?]}
@@
 
-This time the {\sc uncertainty} check doesn't find any more counterexamples 
-and we pass the current candidate solution to the {\sc precision} verification stage.
+This time, the {\sc uncertainty} check does not find any more
+counterexamples and we pass the current candidate solution to the {\sc
+precision} verification stage.
+%
 % In the second {\sc verify} phase, we check whether the current candidate
@@
 % that it is due to lack of precision.
-We obtain the result $false$, meaning that the current precision is insufficient.
-Consequently, we increase our precision to $I_b=20,F_b=28$.
-%
-Since the previous counterexamples were attained at lower precision, we
+%
+We obtain the result $\mathit{false}$, meaning that the current precision is
+insufficient.  Consequently, we increase our precision to $I_b=20$, $F_b=28$.
+%
+Since the previous counterexamples were obtained at lower precision, we
 remove them from the counterexample set.  Back in the {\sc synthesise}
@@
 
-%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
-In the next {\sc synthesise} phase, we get a new candidate solution that holds for
-the new, higher precision counterexample:
-
+In the next {\sc synthesise} phase, we get a new candidate solution that
+eliminates the new, higher precision counterexample:
+%
 $$

### 2016-10-14 paper/paper.tex

@@
 in Eq.~\eqref{eq:pulsetf} with $3$ different sample times ($0.1$, $0.05$, and $0.03$ 
-seconds).
+seconds) respectively, as follows
+%
+\begin{equation}
+\label{exampleA-sampletime1}
+G_{4a}(z)=\frac{0.100342181002722z - 0.110876810062963}{1.0z^{2} - 2.12624017619613z + 1.10517091807565}, \nonumber
+\end{equation}
+%
+%
+\begin{equation}
+\label{exampleA-sampletime2}
+G_{4b}(z)=\frac{0.0500422033454653z - 0.0526068264456340}{1.0^{2} - 2.05640034257636z + 1.05127109637602}, \nonumber
+\end{equation}
+%
+%
+\begin{equation}
+\label{exampleA-sampletime3}
+G_{4c}(z)=\frac{0.0300090687252212z - 0.0309228417953966}{1.0^{2} - 2.03228208009387z + 1.03045453395352}. \nonumber
+\end{equation}
 

### 2016-10-14 paper/paper.tex
nudges

@@
 \noindent where $G_{4}(z)$ is obtained using the ZOH discretisation defined
-in Eq.~\eqref{eq:pulsetf} with $3$ different sample times ($0.1$, $0.05$, and $0.03$ 
-seconds) respectively, as follows
+in Eq.~\eqref{eq:pulsetf} with three different sample times ($0.1$, $0.05$,
+and $0.03$ seconds), respectively, as follows:
 %
@@
 
-All experiments were conducted on a 12-core 2.40\,GHz Intel Xeon E5-2440 with 96\,GB
-of RAM, and Linux OS.  All times given are wall clock time in seconds as measured
-by the UNIX date command.  For the approach using a two-stage verification engine
-we apply a timeout of 8 hours
-per benchmark, and 24 hours for the approach using a one-stage engine.
+All experiments were conducted on a 12-core 2.40\,GHz Intel Xeon E5-2440
+with 96\,GB of RAM, and Linux OS.  All times given are wall clock time in
+seconds as measured by the UNIX date command.  For the approach using a
+two-stage verification engine we apply a timeout of 8 hours per benchmark,
+and 24 hours for the approach using a one-stage engine.
 

### 2016-10-14 paper/paper.tex
nudges

@@
 
-%\red{[The following description can be made shorter, crisper?]}
-
-The synthesis process is illustrated in Fig.~\ref{DSVerifier_process}. 
-A~detailed description of DSVerifier tool can be found
-in~\cite{IsmailBCFF15}.  Steps $1$ to $3$ are performed by the
-user/synthesiser and Steps~A to D are automatically performed by DSVerifier.
+In order to synthesise closed-loop digital control systems, we use a program
+synthesis engine.  Our program synthesiser implements Counter-Example Guided
+Inductive Synthesis (CEGIS)~\cite{sketch}.  We start by presenting its
+general architecture followed by describing the parts specific to
+closed-loop control systems.  A high-level view of the synthesis process is
+given in Fig.~\ref{DSSynth_process}.  Steps $1$ to $3$ are performed by
+the user and Steps~A to D are automatically performed by our tool for
+Digital Systems Synthsis, named DSSynth.
 %
@@
 \vspace{1ex}
-\caption{Overview of the synthesis process\label{DSVerifier_process}}
+\caption{Overview of the synthesis process\label{DSSynth_process}}
 \end{figure*}
@@
 Given a model for a plant for which to synthesise a controller, provided in
-an ANSI-C code input file (Steps 1-3), DSVerifier constructs a
-non-deterministic model to represent the plant family (Step A), and
-formulates a function (step B) using implementation details provided from
-Step $2$ and $3$ to calculate the parameters of the controller to be
-synthesised (step C).  Finally DSVerifier builds an intermediate ANSI-C code
-for the digital system implementation, which is used as input for the
-controller synthesiser (Step D).
+an ANSI-C input file (Steps 1--3), DSSynth constructs a non-deterministic
+model to represent the plant family (Step~A), and formulates a function
+(step~B) using implementation details provided in Steps~$2$ and $3$ to
+calculate the parameters of the controller to be synthesised (Step~C). 
+Finally, DSSynth builds an intermediate ANSI-C code for the digital system
+implementation, which is used as input for the CEGIS engine (Step~D).
 
 This intermediate ANSI-C code model contains a specification $\phi$ for the
-verification properties ({\it i.e.}, robust stability) and is provided to
+property of interst (i.e., robust stability) and is passed to
 CBMC's~\cite{ClarkeKL04} integrated Counterexample-Guided Inductive
@@
 to synthesise.  The properties specified in the ANSI-C code model can only
-be satisfied if CEGIS synthesises controller coefficients satisfying $\phi$. 
-CEGIS employs an iterative, counterexample-guided refinement process which
-is explained in detail in section~\ref{synthesiser-general}.  A successful
-synthesis result is reported if CEGIS generates a controller which is safe
-with respect to $\phi$.  In particular, the ANSI-C code model guarantees
-that a synthesised solution is complete and sound with respect to stability
-property $\phi$, since it does not depend on system inputs and outputs.  In
-the case of stability, the specification $\phi$ consists in a number of
-assumptions on the polynomial coefficients, following Jury's Criteria, as
-well as the restrictions set in the representation of these coefficients.
+be satisfied if CEGIS synthesises controller coefficients that
+satisfy~$\phi$.  CEGIS employs an iterative, counterexample-guided
+refinement process which is explained in detail in
+section~\ref{synthesiser-general}.  A successful synthesis result is
+reported if CEGIS generates a controllerthat is safe with respect to~$\phi$. 
+In particular, the ANSI-C code model guarantees that a synthesised solution
+is complete and sound with respect to stability property~$\phi$, since it
+does not depend on system inputs and outputs.  In the case of stability, the
+specification~$\phi$ consists in a number of assumptions on the polynomial
+coefficients, following Jury's Criteria, as well as the restrictions set in
+the representation of these coefficients.
 
@@
 
-In order to synthesise closed-loop digital control systems, we use a program
-synthesis engine.  Nowadays, such engines are used increasingly often in
-program verification~\cite{DBLP:conf/lpar/DavidKL15, DBLP:conf/cav/0001A14}. 
-Our program synthesiser makes use of Counter-Example Guided Inductive
-Synthesis (CEGIS) \cite{sketch}.  We start by presenting its general
-architecture followed by describing the parts specific to closed-loop
-control systems.
-
 %specialised it for stream refactoring.  

### 2016-10-14 paper/paper.tex
nudges

@@
 
-\paragraph{Property specification}
+\paragraph{Specification of the stability property}
+
 Next, we describe the specific property that we pass to the program
@@
 
-\paragraph{Use of fixed-point computation in the program synthesis engine}
-The program synthesis engine uses fixed-point arithmetic.
-Namely, we use the domain $\mathbb{R}\param{I}{F}$
-for the controller's coefficients and the domain 
-$\mathbb{R}\param{I_b}{F_b}$ for the plant's coefficients.
-Note that $I$ and $F$, as well as $I_b$ and $F_b$, 
-denote the integer and fractional size, respectively, with
-$\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
+\paragraph{Fixed-point computation in program synthesis}
+
+The program synthesis engine uses fixed-point arithmetic.  Namely, we use
+the domain $\mathbb{R}\param{I}{F}$ for the controller's coefficients and
+the domain $\mathbb{R}\param{I_b}{F_b}$ for the plant's coefficients.  Note
+that $I$ and $F$, as well as $I_b$ and $F_b$, denote the integer and
+fractional size, respectively, with $\mathbb{R}\langle I_b,F_b \rangle
+\supseteq \mathbb{R}\langle I,F \rangle$.
+%
 %the coefficients for $C(z)$ 
@@
 }
- \caption{Counterexample-Guided Inductive Synthesis of Closed-loop System (CEGIS paradigm). 
+ \caption{Counterexample-Guided Inductive Synthesis of Closed-loop System (Step~D)
 \label{fig:CEGIS}}

### 2016-10-14 paper/paper.tex
outline

@@
 
+We cover preliminaries on plant discretisation, the verification of
+closed-loop control systems, and stability in
+Section~\ref{sec:preliminaries}.  Our core contribution is in
+Section~\ref{sec:synthesis}: we present our CEGIS-based algorithm for
+generating stable controllers for a given plant model.  Our experimental
+setup and experimental results are given in Section~\ref{sec:experiments},
+and we discuss how we extend the state-of-the-art beyond the existing
+literature in Section~\ref{sec:related}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Preliminaries}
+\section{Preliminaries}\label{sec:preliminaries}
 
@@
 \Delta{\vec{P}}=[\Delta{n}_{0}\ \Delta{n}_{1}\ \hdots \ \Delta{n}_{M}\ \Delta{d}_{0}\ \Delta{d}_{1}\ \hdots\ \Delta{d}_{N}\ ]^T \;.
-\label{eq:coefficients}
 \end{equation}
@@
 %
-A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem},
+A feedback hybrid control system as given in Fig.~\ref{fig:sampledsystem},
 with a FWL implementation of the digital controller $\hat{C}(z) =
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Automated Program Synthesis \\ for Digital Control}
+\section{Automated Program Synthesis \\ for Digital
+Control}\label{sec:synthesis}
 
@@
 \end{figure*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Experimental Evaluation} \label{sec:experiments}
+\section{Experimental Evaluation}\label{sec:experiments}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Related Work}
+\section{Related Work}\label{sec:related}
 

### 2016-10-14 paper/paper.tex
hscc17

--- 2016-10-14 paper/paper.tex
@@
 
-Modern implementations of embedded control have proliferated with the
+Modern implementations of embedded control systems have proliferated with the
 availability of low-cost devices that can perform highly non-trivial control
@@
 
-Correct control is non-trivial, however. The problem is exacerbated by
-artefacts specific to digital control such as the effects of
+Correct and sound control is non-trivial, however. The problem is exacerbated by
+artefacts specific to digital control, such as the effects of
 finite-precision arithmetic, time discretisation, and quantisation noise
@@
 
-There has been plenty of previous work that aims at \emph{verifying} a given
-controller designed by the engineer.  Recent work can show the of stability
+Beyond classical a-posteriori validation procedures in digital control, 
+there has been plenty of previous work aiming at \emph{verifying} a given
+controller designed by the engineer.  Recent work can show the stability of 
 digital controllers with considerations to implementation aspects, i.e.,

### 2016-10-14 paper/paper.tex
nudge

--- 2016-10-14 paper/paper.tex
@@
 model to represent the plant family (Step~A), and formulates a function
-(step~B) using implementation details provided in Steps~$2$ and $3$ to
+(Step~B) using implementation details provided in Steps~$2$ and $3$ to
 calculate the parameters of the controller to be synthesised (Step~C). 
@@
 This intermediate ANSI-C code model contains a specification $\phi$ for the
-property of interst (i.e., robust stability) and is passed to
-CBMC's~\cite{ClarkeKL04} integrated Counterexample-Guided Inductive
-Synthesis (CEGIS) module, where the controller is marked as input variable
+property of interst (i.e., robust stability) and is passed to the
+Counterexample-Guided Inductive Synthesis (CEGIS) module of
+CBMC~\cite{ClarkeKL04}, where the controller is marked as the input variable
 to synthesise.  The properties specified in the ANSI-C code model can only
@@
 refinement process which is explained in detail in
-section~\ref{synthesiser-general}.  A successful synthesis result is
+section~\ref{synthesiser-general}.  A~successful synthesis result is
 reported if CEGIS generates a controllerthat is safe with respect to~$\phi$. 

### 2016-10-14 paper/paper.tex
hscc17

--- 2016-10-14 paper/paper.tex
@@
 tool that automatically \emph{generates} digital controllers for a given
-plant model that are correct by construction.  This approach promises to
+continuous plant model that are correct by construction.  This approach promises to
 reduce the cost and time of development of digital control dramatically, and
@@
 with a model of their physical environment (the plant), that are
-\emph{stable}.  Due to the complexity of such systems, we focus on linear
-models with known configurations to perform parametric synthesis of the
-controller dynamics.
+\emph{stable}.  Due to the complexity of such systems, in this work we focus on linear
+models with known configurations and perform parametric synthesis of stabilising digital controllers.
 
@@
 problem.  We perform digital control synthesis over a hybrid model, where
-the plant exhibits continuous behaviour and the controller operates in both
-discrete time and discrete state space.  The key insight of our approach is
-that the problem can be translated into a \emph{single, joint domain}, which
-represents a bi-simulation of the original, hybrid dynamics.  Given our
-primary interest in stability despite digitisation effects, we have modelled
+the plant exhibits continuous behaviour whereas the controller operates in 
+discrete time and over a quantised domain.  Our approach translates the problem into a single digital domain.  
+Given our primary interest in stability despite digitisation effects, we have modelled
 a digital equivalent of the plant by evaluating the effects of the
@@
 
-\item We designed and implemented an automatic approach for generating
+\item We design and implement an automatic approach for generating
   {\em corect-by-construction} digital controllers that is based on
@@
   program synthesis is non-trivial and requires addressing challenges
-  specific to embedded control systems such as the effects of quantisers and
-  FWL. In particular, we found that a two-stage verification engine
+  specific to embedded control systems, such as the effects of quantisers and
+  FWL. In particular, we have found that a two-stage verification engine
   that continuously refines the precision of the fixed-point

### 2016-10-14 paper/paper.tex
hscc17

--- 2016-10-14 paper/paper.tex
@@
 the plant exhibits continuous behaviour whereas the controller operates in 
-discrete time and over a quantised domain.  Our approach translates the problem into a single digital domain.  
+discrete time and over a quantised domain.  
+Inspired by a classical approach \cite{astrom1997computer}, 
+we translate the problem into a single digital domain.  
 Given our primary interest in stability despite digitisation effects, we have modelled
@@
 The digital controllers synthesised using the algorithm we present in this
-paper are typically used in closed loops with continuous (and physical)
+paper are typically used in closed loops with continuous (physical)
 plants.  Thus, the proposed approach has to consider dynamics of continuous
 parts of the system (i.e., the plant) and the discrete parts (i.e., the
-digital controller).  To obtain a joint model, we discretise the continuous
+digital controller).  To obtain a joint model, we fully discretise the continuous
 plant. We briefly recall the standard foundations of this step.

### 2016-10-14 paper/paper.tex
Fig. -> Figure for uniformity

--- 2016-10-14 paper/paper.tex
@@
 tool that automatically \emph{generates} digital controllers for a given
-continuous plant model that are correct by construction.  This approach promises to
+plant model that are correct by construction.  This approach promises to
 reduce the cost and time of development of digital control dramatically, and
@@
 with a model of their physical environment (the plant), that are
-\emph{stable}.  Due to the complexity of such systems, in this work we focus on linear
-models with known configurations and perform parametric synthesis of stabilising digital controllers.
+\emph{stable}.  Due to the complexity of such systems, we focus on linear
+models with known configurations to perform parametric synthesis of the
+controller dynamics.
 
@@
 problem.  We perform digital control synthesis over a hybrid model, where
-the plant exhibits continuous behaviour whereas the controller operates in 
-discrete time and over a quantised domain.  
-Inspired by a classical approach \cite{astrom1997computer}, 
-we translate the problem into a single digital domain.  
-Given our primary interest in stability despite digitisation effects, we have modelled
+the plant exhibits continuous behaviour and the controller operates in both
+discrete time and discrete state space.  The key insight of our approach is
+that the problem can be translated into a \emph{single, joint domain}, which
+represents a bi-simulation of the original, hybrid dynamics.  Given our
+primary interest in stability despite digitisation effects, we have modelled
 a digital equivalent of the plant by evaluating the effects of the
@@
 
-\item We design and implement an automatic approach for generating
+\item We designed and implemented an automatic approach for generating
   {\em corect-by-construction} digital controllers that is based on
@@
   program synthesis is non-trivial and requires addressing challenges
-  specific to embedded control systems, such as the effects of quantisers and
-  FWL. In particular, we have found that a two-stage verification engine
+  specific to embedded control systems such as the effects of quantisers and
+  FWL. In particular, we found that a two-stage verification engine
   that continuously refines the precision of the fixed-point
@@
 The digital controllers synthesised using the algorithm we present in this
-paper are typically used in closed loops with continuous (physical)
+paper are typically used in closed loops with continuous (and physical)
 plants.  Thus, the proposed approach has to consider dynamics of continuous
 parts of the system (i.e., the plant) and the discrete parts (i.e., the
-digital controller).  To obtain a joint model, we fully discretise the continuous
+digital controller).  To obtain a joint model, we discretise the continuous
 plant. We briefly recall the standard foundations of this step.
@@
 %
-A feedback hybrid control system as given in Fig.~\ref{fig:sampledsystem},
+A feedback hybrid control system as given in Figure~\ref{fig:sampledsystem},
 with a FWL implementation of the digital controller $\hat{C}(z) =
@@
 closed-loop control systems.  A high-level view of the synthesis process is
-given in Fig.~\ref{DSSynth_process}.  Steps $1$ to $3$ are performed by
+given in Figure~\ref{DSSynth_process}.  Steps $1$ to $3$ are performed by
 the user and Steps~A to D are automatically performed by our tool for
@@
 
-The design of our synthesiser is given in Fig.~\ref{fig:CEGIS} and consists
+The design of our synthesiser is given in Figure~\ref{fig:CEGIS} and consists
 of two phases, {\sc Synthesise} and {\sc Verify}, which interact via a
@@
 again (note that, for now, we ignore the second feedback signal ``Increase
-Precision'' provided by the {\sc Verify} phase in Fig.~\ref{fig:CEGIS} as it
+Precision'' provided by the {\sc Verify} phase in Figure~\ref{fig:CEGIS} as it
 is specific to control synthesis and will be described in the next section).
@@
 
-The second approach is illustrated in Fig.~\ref{fig:CEGIS} and uses a
+The second approach is illustrated in Figure~\ref{fig:CEGIS} and uses a
 two-stage verification: the first stage performs potentially unsound
@@
 
-In more detail, in the first stage, denoted by {\sc Uncertainty} in Fig.~\ref{fig:CEGIS}, 
+In more detail, in the first stage, denoted by {\sc Uncertainty} in Figure~\ref{fig:CEGIS}, 
 assuming a precision \param{I_b}{F_b} 

### 2016-10-14 paper/paper.tex
nudge

--- 2016-10-14 paper/paper.tex
@@
 the plant exhibits continuous behaviour whereas the controller operates in 
-discrete time and over a quantised domain.  
-Inspired by a classical approach \cite{astrom1997computer}, 
-we translate the problem into a single digital domain.  
+discrete time and over a quantised domain.  Our approach translates the problem into a single digital domain.  
 Given our primary interest in stability despite digitisation effects, we have modelled
@@
 
-\resizebox{.9\textwidth}{!}{
+\resizebox{1.0\textwidth}{!}{
  \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
@@
 
-\begin{figure}[ht]
+\begin{figure*}[ht]
 \centering
@@
 
-\resizebox{.5\textwidth}{!}{
+\resizebox{.6\textwidth}{!}{
  \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
@@
 \caption{System equivalent to the system in Figure~\ref{fig:sampledsystem}\label{fig:digsystem1}}
-\end{figure}
+\end{figure*}
 
@@
 \begin{enumerate}
-	\item RQ1 \textbf{(sanity check)} which results does our CEGIS approach to FWL controller synthesis 
-	obtain upon synthesising/verifying benchmarks that compose the specified suite?
-  \item RQ2 \textbf{(performance)} does the CEGIS approach provide a feasible solution in reasonable time
-	considering robust stability of FWL digital controllers?	
+
+\item RQ1 \textbf{(sanity check)} which results does our CEGIS approach to
+FWL controller synthesis obtain upon synthesising/verifying benchmarks that
+compose the specified suite?
+
+\item RQ2 \textbf{(performance)} does the CEGIS approach provide a feasible
+solution in reasonable time considering robust stability of FWL digital
+controllers?
+
 \end{enumerate}
@@
 
-\begin{table}[H]
+\begin{table}
 \centering
@@
 
-\caption{Experimental results. \label{tab:results}}
+\caption{Experimental results\label{tab:results}}
 \end{table}

### 2016-10-14 paper/paper.tex
typo
hscc17

@@
 Laplace domain transfer function $G(s)$) and the sampling and hold process.
-Note that $G(z)$ is a discrete model of a physical, continuous
-plant, i.e., the continuous model of the plant must be discretised to obtain
-the discrete equivalent coefficients via ZOH discretisation.
+%Note that $G(z)$ is a discrete model of a physical, continuous
+%plant, i.e., 
+The continuous model of the plant must be discretised to obtain the corresponding 
+%discrete equivalent 
+coefficients of $G(z)$.
+%via ZOH discretisation.
 
@@
 
-Although there are several discretisation methods available in the
+Amongst the several discretisation methods available in the
 literature~\cite{Franklin15}, the zero-order hold (ZOH) discretisation is
-more suitable for representing the sample and hold processes that are
-typically employed in complex systems~\cite{istepanian2012digital}, i.e.,
-the ZOH discretisation models the exact effect of sampling and DAC
-interpolation over the plant.
+considered to be suitable for representing the sample and hold processes that are
+typically employed in complex systems~\cite{istepanian2012digital}. 
+The ZOH discretisation models the exact effect of sampling and DAC interpolation over the plant.
 
@@
 %
-The Sample and Hold of the ADC and the ZOH of the DAC are synchronised,
+The sample and hold effects of the ADC and the ZOH of the DAC are synchronised,
 i.e., there is no delay between sampling the plant output at ADC and
@@
 
-\resizebox{1.0\textwidth}{!}{
+\resizebox{.9\textwidth}{!}{
  \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
@@
 
-\begin{figure*}[ht]
+\begin{figure}[ht]
 \centering
@@
 
-\resizebox{.6\textwidth}{!}{
+\resizebox{.5\textwidth}{!}{
  \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
@@
 \caption{System equivalent to the system in Figure~\ref{fig:sampledsystem}\label{fig:digsystem1}}
-\end{figure*}
+\end{figure}
 
@@
 \begin{enumerate}
-
-\item RQ1 \textbf{(sanity check)} which results does our CEGIS approach to
-FWL controller synthesis obtain upon synthesising/verifying benchmarks that
-compose the specified suite?
-
-\item RQ2 \textbf{(performance)} does the CEGIS approach provide a feasible
-solution in reasonable time considering robust stability of FWL digital
-controllers?
-
+	\item RQ1 \textbf{(sanity check)} which results does our CEGIS approach to FWL controller synthesis 
+	obtain upon synthesising/verifying benchmarks that compose the specified suite?
+  \item RQ2 \textbf{(performance)} does the CEGIS approach provide a feasible solution in reasonable time
+	considering robust stability of FWL digital controllers?	
 \end{enumerate}
@@
 
-\begin{table}
+\begin{table}[H]
 \centering
@@
 
-\caption{Experimental results\label{tab:results}}
+\caption{Experimental results. \label{tab:results}}
 \end{table}

### 2016-10-14 paper/paper.tex

--- 2016-10-14 paper/paper.tex
@@
 section~\ref{synthesiser-general}.  A~successful synthesis result is
-reported if CEGIS generates a controllerthat is safe with respect to~$\phi$. 
+reported if CEGIS generates a controller that is safe with respect to~$\phi$. 
 In particular, the ANSI-C code model guarantees that a synthesised solution

### 2016-10-14 paper/paper.tex
small edit

@@
 Laplace domain transfer function $G(s)$) and the sampling and hold process.
-%Note that $G(z)$ is a discrete model of a physical, continuous
-%plant, i.e., 
-The continuous model of the plant must be discretised to obtain the corresponding 
-%discrete equivalent 
-coefficients of $G(z)$.
-%via ZOH discretisation.
+Note that $G(z)$ is a discrete model of a physical, continuous
+plant, i.e., the continuous model of the plant must be discretised to obtain
+the discrete equivalent coefficients via ZOH discretisation.
 
@@
 
-Amongst the several discretisation methods available in the
+Although there are several discretisation methods available in the
 literature~\cite{Franklin15}, the zero-order hold (ZOH) discretisation is
-considered to be suitable for representing the sample and hold processes that are
-typically employed in complex systems~\cite{istepanian2012digital}. 
-The ZOH discretisation models the exact effect of sampling and DAC interpolation over the plant.
+more suitable for representing the sample and hold processes that are
+typically employed in complex systems~\cite{istepanian2012digital}, i.e.,
+the ZOH discretisation models the exact effect of sampling and DAC
+interpolation over the plant.
 
@@
 %
-The sample and hold effects of the ADC and the ZOH of the DAC are synchronised,
+The Sample and Hold of the ADC and the ZOH of the DAC are synchronised,
 i.e., there is no delay between sampling the plant output at ADC and
@@
 In particular, the ANSI-C code model guarantees that a synthesised solution
-is complete and sound with respect to stability property~$\phi$, since it
+is complete and sound with respect to the stability property~$\phi$, since it
 does not depend on system inputs and outputs.  In the case of stability, the
@@
 coefficients, following Jury's Criteria, as well as the restrictions set in
-the representation of these coefficients.
+the representation of these coefficients as discussed in more detail in 
+Section~\ref{synthesis-elements}.
 

### 2016-10-14 paper/paper.tex
Sec. -> Section for uniformity
add comma
hscc17

--- 2016-10-14 paper/paper.tex
@@
 quantisation noise.  The resulting closed-loop system is a program loop that
-operates on bit-vectors encoded using fixed-point arithmetic with fixed word
-length (FWL). The deterministic effects of the FWL and
+operates on bit-vectors encoded using fixed-point arithmetic with fixed-word
+length (FWL). 
+\red{[acronym later defined as finite-word length - please unify use]} 
+The deterministic effects of the FWL and
 quantisation errors are incorporated into the model as an additive
@@
 Given a synchronised ZOH input and sample and hold output on the plant with
-a sample time $T$ satisfying Nyquist's sampling criteria, the discrete pulse
+a sample time $T$ satisfying Nyquist criterion, the discrete pulse
 transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$ 
-which can be computed using the following formula:
+that can be computed using the following formula:
 %
@@
 
-Here, Lemma~\ref{eq:pulsetf} ensures the poles and zeros matching with
+Lemma~\ref{eq:pulsetf} ensures the poles and zeros matching under the 
 $\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$
-operations and includes the ZOH dynamics in the $(1-z^{-1})$ term, that is
-sufficient for the stability studies over $G(s)$.
+operations, 
+and it includes the ZOH dynamics in the $(1-z^{-1})$ term, 
+which is sufficient for stability studies over $G(s)$.
 
@@
 Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$
-(\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$), errors in the numeric
-calculations, or roundoffs in the quantisation.  These uncertainties may be
+(\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$ \red{, as defined later}), errors in the numeric
+calculations, or roundoffs in the quantisation.  These uncertainties \red{may be [can be?, are?]} 
 parametrically expressed by additive terms, resulting in a uncertain model
@@
 that the parametric errors in the plant have the same polynomial order as
-the plant itself (other errors are ensured to fulfil this property in our
+the plant itself (\red{other errors [which precisely? all others?]} are ensured to fulfil this property in our
 implementation).
 
-In order to simplify presentation, we will use notation based on the
+In order to simplify the presentation, we employ a notation based on the
 coefficients of the polynomials.  Let $\mathcal{P}^{N}$ be a polynomial
-domain of order $N$ Let $P \in \mathcal{P}^{M,N}$ be a rational polynomial
-$\frac{P_n}{P_d} : P_n \in \mathcal{P}^{M} \wedge P_d \in \mathcal{P}^{N}$. 
-There is a vector of coefficients
+domain of order $N$. Let $P \in \mathcal{P}^{M,N}$ be a rational polynomial
+$\frac{P_n}{P_d}$, where $P_n \in \mathcal{P}^{M}$ and $P_d \in \mathcal{P}^{N}$.  
+For a vector of coefficients
 %
@@
 \begin{equation}
-\Delta{\vec{P}}=[\Delta{n}_{0}\ \Delta{n}_{1}\ \hdots \ \Delta{n}_{M}\ \Delta{d}_{0}\ \Delta{d}_{1}\ \hdots\ \Delta{d}_{N}\ ]^T \;.
+\Delta{\vec{P}}=[\Delta{n}_{0}\ \Delta{n}_{1}\ \hdots \ \Delta{n}_{M}\ \Delta{d}_{0}\ \Delta{d}_{1}\ \hdots\ \Delta{d}_{N}\ ]^T \; 
 \end{equation}
 %
-Then $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$.  In the following we may use
-either notation to represent the functions $G(z)$, $C(z)$, and their
-respective uncertainties.\\
+we have $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$ \red{[uh, now the TF are vectors - confusing]}.  
+In the following we will either represent the functions $G(z)$, $C(z)$, 
+or work over their respective coefficients in vector form.
 

### 2016-10-14 paper/paper.tex

@@
 therefore designed a second approach, which we describe below.
-Our experimental results described in Sec.~\ref{sec:experiments}, 
+Our experimental results described in Section~\ref{sec:experiments}, 
 %try both approaches and provide the time for the fastest. 

### 2016-10-14 paper/paper.tex
typo

@@
 the unit circle.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following
-lemma states necessary conditions for BIBO stability of closed-loop system
+lemma states necessary conditions for BIBO stability of the closed-loop system
 in Figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$,
@@
 \label{exampleA}
-G_{4}(s)=\frac{s-1}{s^{2}-s-2}
+G_{4}(s)=\frac{s-1}{s^{2}-s-2},
 \end{equation}

### 2016-10-14 paper/paper.tex
typo

@@
 lemma states necessary conditions for BIBO stability of the closed-loop system
-in Figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$,
+in Figure~\ref{fig:sampledsystem}, since the exogenous signals $R(z)$,
 $\nu_{1}$, and $\nu_{2}$ are bounded.

### 2016-10-14 paper/paper.tex
line break
replace CEGIS tool by DDSynth tool

--- 2016-10-14 paper/paper.tex
@@
 arithmetic instead.  A link to the full experimental environment, including
-scripts to reproduce the experiment, all benchmarks and the CEGIS tool is
+scripts to reproduce the experiment, all benchmarks and the DDSynth tool is
 provided in the

### 2016-10-14 paper/paper.tex

--- 2016-10-14 paper/paper.tex
@@
 and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is
-represented as an additive (output) measurement noise $\nu(z)$.
+represented as an additive (output) measurement noise~$\nu(z)$.
 %, thus

### 2016-10-14 paper/paper.tex
hscc17

--- 2016-10-14 paper/paper.tex
@@
 Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$
-(\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$ \red{, as defined later}), errors in the numeric
+(\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$ \red{, as defined later?}), errors in the numeric
 calculations, or roundoffs in the quantisation.  These uncertainties \red{may be [can be?, are?]} 
@@
 %
-with uncertainty
+and an uncertainty vector 
 %
@@
 %
-we have $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$ \red{[uh, now the TF are vectors - confusing]}.  
+we write $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$.   
 In the following we will either represent the functions $G(z)$, $C(z)$, 
-or work over their respective coefficients in vector form.
+or work over their respective coefficients $\vec{G}, \vec{C}$ in vector form.
+
+\red{[I've tried to clean the notations above. BUT: you cannot later add a transfer function with a vector of coefficients! Heresy!]}
 
@@
 controller is illustrated in Figure~\ref{fig:sampledsystem}.  The DAC and
-ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$,
+ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$ \red{[this is an assumption and as such must be stated.]},
 $G(s)$ is the continuous-time plant model with parametric additive
-uncertainty $\Delta_p \vec{G}_s$, $R(z)$ is the reference signal, $U(z)$ is
+uncertainty $\Delta_p \vec{G}_s$ \red{[above you used n, d subscripts, here s?]}, $R(z)$ is the reference signal, $U(z)$ is
 the control signal, and $\hat{Y}(z)$ is the output signal affected by the
@@
 \label{exampleA}
-G_{4}(s)=\frac{s-1}{s^{2}-s-2},
+G_{4}(s)=\frac{s-1}{s^{2}-s-2}
 \end{equation}
@@
 arithmetic instead.  A link to the full experimental environment, including
-scripts to reproduce the experiment, all benchmarks and the DDSynth tool is
+scripts to reproduce the experiment, all benchmarks and the CEGIS tool is
 provided in the

### 2016-10-14 paper/paper.tex

@@
 the unit circle.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following
-lemma states necessary conditions for BIBO stability of closed-loop system
-in Figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$,
+lemma states necessary conditions for BIBO stability of the closed-loop system
+in Figure~\ref{fig:sampledsystem}, since the exogenous signals $R(z)$,
 $\nu_{1}$, and $\nu_{2}$ are bounded.

### 2016-10-14 paper/paper.tex
comma

@@
 arithmetic instead.  A link to the full experimental environment, including
-scripts to reproduce the experiment, all benchmarks and the DDSynth tool is
+scripts to reproduce the results, all benchmarks and the DDSynth tool, is
 provided in the

### 2016-10-14 paper/paper.tex
small edit

--- 2016-10-14 paper/paper.tex
@@
 Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$
-(\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$ \red{, as defined later?}), errors in the numeric
+(\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$ \red{, as defined later}), errors in the numeric
 calculations, or roundoffs in the quantisation.  These uncertainties \red{may be [can be?, are?]} 
@@
 %
-and an uncertainty vector 
+with uncertainty
 %
@@
 %
-we write $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$.   
+we have $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$ \red{[uh, now the TF are vectors - confusing]}.  
 In the following we will either represent the functions $G(z)$, $C(z)$, 
-or work over their respective coefficients $\vec{G}, \vec{C}$ in vector form.
-
-\red{[I've tried to clean the notations above. BUT: you cannot later add a transfer function with a vector of coefficients! Heresy!]}
+or work over their respective coefficients in vector form.
 
@@
 controller is illustrated in Figure~\ref{fig:sampledsystem}.  The DAC and
-ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$ \red{[this is an assumption and as such must be stated.]},
+ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$,
 $G(s)$ is the continuous-time plant model with parametric additive
-uncertainty $\Delta_p \vec{G}_s$ \red{[above you used n, d subscripts, here s?]}, $R(z)$ is the reference signal, $U(z)$ is
+uncertainty $\Delta_p \vec{G}_s$, $R(z)$ is the reference signal, $U(z)$ is
 the control signal, and $\hat{Y}(z)$ is the output signal affected by the
@@
 the domain $\mathbb{R}\param{I}{F}$ for the controller's coefficients and
-the domain $\mathbb{R}\param{I_b}{F_b}$ for the plant's coefficients.  Note
-that $I$ and $F$, as well as $I_b$ and $F_b$, denote the integer and
-fractional size, respectively, with $\mathbb{R}\langle I_b,F_b \rangle
+the domain $\mathbb{R}\param{I_b}{F_b}$ for the plant's coefficients, 
+where $I$ and $F$, as well as $I_b$ and $F_b$, denote the integer and
+fractional size, respectively, and $\mathbb{R}\langle I_b,F_b \rangle
 \supseteq \mathbb{R}\langle I,F \rangle$.

### 2016-10-14 paper/paper.tex
font

--- 2016-10-14 paper/paper.tex
@@
 
-If the {\sc precision} verification returns $false$, then we 
-increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise} phase
-with an empty {\sc inputs} set.
-Otherwise, we found a full solution for our synthesis problem
-and we are done.
+If the {\sc precision} verification returns $\mathit{false}$, then we
+increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise}
+phase with an empty {\sc inputs} set.  Otherwise, we found a full solution
+for our synthesis problem and we are done.
 

### 2016-10-14 paper/paper.tex
font

--- 2016-10-14 paper/paper.tex
@@
 $$
-\phi_{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
+\phi_\mathit{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
 $$
@@
 we check whether the system is unstable for the current candidate solution,
-{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$.
+{\it i.e.}, if $\neg \phi_\mathit{stability}$ is satisfiable for $S(z)$.
 If this is the case, then we obtain a counterexample 

### 2016-10-14 paper/paper.tex
hscc17

--- 2016-10-14 paper/paper.tex
@@
 
-The ADC and DAC may be abstracted by transforming the hybrid system in
+The ADC and DAC may be abstracted by transforming the closed-loop system in
 Figure~\ref{fig:sampledsystem} into the digital system in 
@@
 and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is
-represented as an additive (output) measurement noise~$\nu(z)$.
+represented as an additive output noise~$\nu(z)$. 
 %, thus
@@
 these sources, the uncertain model may be rewritten as 
+\red{[unclear whether this is over the s or z domain. further there is lack of proper subscripts (n,d,s), as per the notations introduced above.]}
 %
@@
 $\mathit{FWL}[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$,
-which applies the FWL effects to a polynomial.  $\mathcal{P}^{n}$ is the
+which applies the FWL effects to a polynomial.  
+\red{above $\mathcal{P}$ was defined as a single polynomial, now it is a space of polynomials.
+actually space of polynomials form specific algebraic structures, called diods -- we should have used those ...
+}
+$\mathcal{P}^{n}$ is the
 space of polynomials of $n$-th order and $\mathcal{P}^{n}\langle I,F
@@
 %
+\red{[above you introduced a notation for poly ratios, which now you do not use?]}
 Thus, the perturbed controller model $\hat{C}(z)$ may be obtained from the
@@
 the domain $\mathbb{R}\param{I}{F}$ for the controller's coefficients and
-the domain $\mathbb{R}\param{I_b}{F_b}$ for the plant's coefficients, 
-where $I$ and $F$, as well as $I_b$ and $F_b$, denote the integer and
-fractional size, respectively, and $\mathbb{R}\langle I_b,F_b \rangle
+the domain $\mathbb{R}\param{I_b}{F_b}$ for the plant's coefficients.  Note
+that $I$ and $F$, as well as $I_b$ and $F_b$, denote the integer and
+fractional size, respectively, with $\mathbb{R}\langle I_b,F_b \rangle
 \supseteq \mathbb{R}\langle I,F \rangle$.
@@
 arithmetic instead.  A link to the full experimental environment, including
-scripts to reproduce the results, all benchmarks and the DDSynth tool, is
+scripts to reproduce the experiment, all benchmarks and the DDSynth tool is
 provided in the

### 2016-10-14 paper/paper.tex
add a label for conclusions

--- 2016-10-14 paper/paper.tex
@@
 and we discuss how we extend the state-of-the-art beyond the existing
-literature in Section~\ref{sec:related}.
+literature in Section~\ref{sec:related}. We conclude and describe future
+work in Section~\ref{sec:conclusions}
 
@@
 
-The ADC and DAC may be abstracted by transforming the closed-loop system in
+The ADC and DAC may be abstracted by transforming the hybrid system in
 Figure~\ref{fig:sampledsystem} into the digital system in
@@
 and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is
-represented as an additive output noise~$\nu(z)$. 
+represented as an additive (output) measurement noise~$\nu(z)$.
 %, thus
@@
 these sources, the uncertain model may be rewritten as
-\red{[unclear whether this is over the s or z domain. further there is lack of proper subscripts (n,d,s), as per the notations introduced above.]}
 %
@@
 $\mathit{FWL}[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$,
-which applies the FWL effects to a polynomial.  
-\red{above $\mathcal{P}$ was defined as a single polynomial, now it is a space of polynomials.
-actually space of polynomials form specific algebraic structures, called diods -- we should have used those ...
-}
-$\mathcal{P}^{n}$ is the
+which applies the FWL effects to a polynomial.  $\mathcal{P}^{n}$ is the
 space of polynomials of $n$-th order and $\mathcal{P}^{n}\langle I,F
@@
 %
-\red{[above you introduced a notation for poly ratios, which now you do not use?]}
 Thus, the perturbed controller model $\hat{C}(z)$ may be obtained from the
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
+\section{Conclusions} \label{sec:conclusions}
 

### 2016-10-14 paper/paper.tex
wordings

--- 2016-10-14 paper/paper.tex
@@
 
-In order to exploit the full potential of the present approach, a
-dynamical plant that can present physical components must be
-considered.  However, a discrete plant model can also demonstrate some
-benefits of the present approach, which considers FWL effects in the
-digital controller implementation.  In particular, a classical cruise
-control example is extracted from the literature~\cite{Astrom08},
-where the discrete plant model (with a time step of $0.2$s) is
-represented by the following $z$-expression:
+We will illustrate our approach with a classical cruise control example,
+extracted from the literature~\cite{Astrom08}.  The example will allow us to
+highlight the challenges that arise when using finite precision arithmetic
+in digital control.  We are given a discrete plant model (with a time step
+of $0.2$s), which is represented by the following $z$-expression:
 %
@@
 
-Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16}
-has designed a high-performance controller, which is characterised by the
-following $z$-domain transfer function:
+Using an optimisation tool, the authors
+of~\cite{DBLP:conf/hybrid/WangGRJF16} have designed a high-performance
+controller for this plant, which is characterised by the following
+$z$-domain transfer function:
 %
@@
 The authors claim that this controller $C(z)$
-(Eq.~\eqref{Eq:running-example-plant}) stabilizes the closed-loop system for
-the discrete plant model $G(z)$ (Eq.~\ref{Eq:running-example-controller}). 
-However, if implementation aspects are considered during verification (e.g.,
-fixed-point arithmetic and word-length), then this closed-loop system
-becomes unstable.
+(Eq.~\eqref{Eq:running-example-controller}) stabilizes the closed-loop
+system for the discrete plant model $G(z)$
+(Eq.~\ref{Eq:running-example-plant}).  However, if the effects of finite
+precision arithmetic are considered during verification (e.g., fixed-point
+arithmetic and word-length), then this closed-loop system becomes unstable.
 %

### 2016-10-14 paper/paper.tex
small edit

--- 2016-10-14 paper/paper.tex
@@
 $$
-\phi_\mathit{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
+\phi_{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
 $$
@@
 we check whether the system is unstable for the current candidate solution,
-{\it i.e.}, if $\neg \phi_\mathit{stability}$ is satisfiable for $S(z)$.
+{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$.
 If this is the case, then we obtain a counterexample 
@@
 
-If the {\sc precision} verification returns $\mathit{false}$, then we
-increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise}
-phase with an empty {\sc inputs} set.  Otherwise, we found a full solution
-for our synthesis problem and we are done.
+If the {\sc precision} verification returns $false$, then we 
+increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise} phase
+with an empty {\sc inputs} set.
+Otherwise, we found a full sound solution for our synthesis problem
+and we are done.
 
@@
 
-We will illustrate our approach with a classical cruise control example,
-extracted from the literature~\cite{Astrom08}.  The example will allow us to
-highlight the challenges that arise when using finite precision arithmetic
-in digital control.  We are given a discrete plant model (with a time step
-of $0.2$s), which is represented by the following $z$-expression:
+In order to exploit the full potential of the present approach, a
+dynamical plant that can present physical components must be
+considered.  However, a discrete plant model can also demonstrate some
+benefits of the present approach, which considers FWL effects in the
+digital controller implementation.  In particular, a classical cruise
+control example is extracted from the literature~\cite{Astrom08},
+where the discrete plant model (with a time step of $0.2$s) is
+represented by the following $z$-expression:
 %
@@
 
-Using an optimisation tool, the authors
-of~\cite{DBLP:conf/hybrid/WangGRJF16} have designed a high-performance
-controller for this plant, which is characterised by the following
-$z$-domain transfer function:
+Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16}
+has designed a high-performance controller, which is characterised by the
+following $z$-domain transfer function:
 %
@@
 The authors claim that this controller $C(z)$
-(Eq.~\eqref{Eq:running-example-controller}) stabilizes the closed-loop
-system for the discrete plant model $G(z)$
-(Eq.~\ref{Eq:running-example-plant}).  However, if the effects of finite
-precision arithmetic are considered during verification (e.g., fixed-point
-arithmetic and word-length), then this closed-loop system becomes unstable.
+(Eq.~\eqref{Eq:running-example-plant}) stabilizes the closed-loop system for
+the discrete plant model $G(z)$ (Eq.~\ref{Eq:running-example-controller}). 
+However, if implementation aspects are considered during verification (e.g.,
+fixed-point arithmetic and word-length), then this closed-loop system
+becomes unstable.
 %

### 2016-10-14 paper/paper.tex
hscc17

--- 2016-10-14 paper/paper.tex
@@
 
-A discrete-time linear system is said to be Bounded-Input and Bounded-Output
+It is known that a discrete-time linear system is said to be Bounded-Input and Bounded-Output
 (BIBO) stable if and only if every pole of its transfer function lies inside
-the unit circle.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following
-lemma states necessary conditions for BIBO stability of the closed-loop system
+the unit circle \cite{Astrom08}.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following
+proposition states necessary conditions for BIBO stability of the closed-loop system
 in Figure~\ref{fig:sampledsystem}, since the exogenous signals $R(z)$,
@@
 
+\red{[it's not a lemma, since it is not later used to prove a theorem. state it as a proposition (theorem would be a bit of an over-statement)]}
+
 \begin{mylemma}{\cite{Bessa16,fadali}}
@@
 %
-A feedback hybrid control system as given in Figure~\ref{fig:sampledsystem},
+A feedback closed-loop control system as given in Figure~\ref{fig:sampledsystem},
 with a FWL implementation of the digital controller $\hat{C}(z) =
@@
 discrete model of the plant $\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q
-\vec{G} \Rightarrow \hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is
+\vec{G}$, namely \red{[utter confusion between transfer functions and coefficients - you're next taking the ratio between two vectors of coefficient, which magically now are also a function of the z variable!
+WTF!
+\ldots]} $\hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is
 BIBO-stable if and only if:

### 2016-10-14 paper/paper.tex

@@
 
-It is known that a discrete-time linear system is said to be Bounded-Input and Bounded-Output
+A discrete-time linear system is said to be Bounded-Input and Bounded-Output
 (BIBO) stable if and only if every pole of its transfer function lies inside
-the unit circle \cite{Astrom08}.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following
-proposition states necessary conditions for BIBO stability of the closed-loop system
+the unit circle.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following
+lemma states necessary conditions for BIBO stability of the closed-loop system
 in Figure~\ref{fig:sampledsystem}, since the exogenous signals $R(z)$,
@@
 
-\red{[it's not a lemma, since it is not later used to prove a theorem. state it as a proposition (theorem would be a bit of an over-statement)]}
-
 \begin{mylemma}{\cite{Bessa16,fadali}}
@@
 %
-A feedback closed-loop control system as given in Figure~\ref{fig:sampledsystem},
+A feedback hybrid control system as given in Figure~\ref{fig:sampledsystem},
 with a FWL implementation of the digital controller $\hat{C}(z) =
@@
 discrete model of the plant $\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q
-\vec{G}$, namely \red{[utter confusion between transfer functions and coefficients - you're next taking the ratio between two vectors of coefficient, which magically now are also a function of the z variable!
-WTF!
-\ldots]} $\hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is
+\vec{G} \Rightarrow \hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is
 BIBO-stable if and only if:
@@
 If the {\sc precision} verification returns $\mathit{false}$, then we
-increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise}
-phase with an empty {\sc inputs} set.  Otherwise, we found a full solution
-for our synthesis problem and we are done.
+increase the precision of \param{I_b}{F_b} and re-start the {\sc
+  synthesise} phase with an empty {\sc inputs} set.  Otherwise, we
+found a full sound solution for our synthesis problem and we are done.
 

### 2016-10-14 paper/paper.tex
wordings

@@
 If the {\sc precision} verification returns $\mathit{false}$, then we
-increase the precision of \param{I_b}{F_b} and re-start the {\sc
-  synthesise} phase with an empty {\sc inputs} set.  Otherwise, we
-found a full sound solution for our synthesis problem and we are done.
+increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise}
+phase with an empty {\sc inputs} set.  Otherwise, we found a full solution
+for our synthesis problem and we are done.
 
@@
 %
-The authors claim that this controller $C(z)$
-(Eq.~\eqref{Eq:running-example-controller}) stabilizes the closed-loop
-system for the discrete plant model $G(z)$
+The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that this controller
+$C(z)$ (Eq.~\eqref{Eq:running-example-controller}) stabilizes the
+closed-loop system for the discrete plant model $G(z)$
 (Eq.~\ref{Eq:running-example-plant}).  However, if the effects of finite
@@
 
-We will illustrate our synthesis approach on the running example
-described in the previous section. 
-%in Sec.~\ref{sec:running-ex}.
-We start with the candidate solution with all coefficients zero 
-given below at $I_b=16,F_b=24$.
-Note that the digital controller is designed with typical control system
-techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
+We now demonstrate how our approach solves the synthesis problem for the
+example given in the previous section.  We start with the candidate solution
+with all coefficients zero, as given below, and a precision of $I_b=16$,
+$F_b=24$.  The digital controller is designed with standard techniques for
+control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}.
 %
@@
 %$$
-$$
-C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}
-$$
+$$ C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0} $$
 
@@
 %
-$$
-\tilde G(z) = \frac{0.026506}{1.000610z+1.002838}
-$$
+$$ \tilde G(z) = \frac{0.026506}{1.000610z+1.002838} $$
 
@@
 We add this counterexample to {\sc inputs} and initiate the {\sc synthesise}
-phase, where we get the following candidate solution:
+phase, where we obtain the following candidate solution:
 %
@@
 
-This time, the {\sc uncertainty} check does not find any more
-counterexamples and we pass the current candidate solution to the {\sc
+This time, the {\sc uncertainty} check does not find any
+counterexample and we pass the current candidate solution to the {\sc
 precision} verification stage.
@@
 Since the previous counterexamples were obtained at lower precision, we
-remove them from the counterexample set.  Back in the {\sc synthesise}
+remove them from the set of counterexamples.  Back in the {\sc synthesise}
 phase, we re-start the process with a candidate solution with all
@@
 %$$
-$$
-\tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785}
-$$
+$$ \tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785} $$
 
@@
 %
-$$
-C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}
-$$
+$$ C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357} $$
 %
@@
 This candidate solution is validated as the final solution by both stages
-{\sc uncertainty} and {\sc precision} in the
-{\sc verify} phase. %, which fails to find a new counterexample (i.e. returns UNSAT).
+{\sc uncertainty} and {\sc precision} in the {\sc verify} phase.
+
+%, which fails to find a new counterexample (i.e. returns UNSAT).
 

### 2016-10-14 paper/paper.tex
replace fixed-word length by finite-word length, which is typically used in the control and DSP community

--- 2016-10-14 paper/paper.tex
@@
 quantisation noise.  The resulting closed-loop system is a program loop that
-operates on bit-vectors encoded using fixed-point arithmetic with fixed-word
-length (FWL). 
-\red{[acronym later defined as finite-word length - please unify use]} 
-The deterministic effects of the FWL and
+operates on bit-vectors encoded using fixed-point arithmetic with finite-word
+length (FWL). The deterministic effects of the FWL and
 quantisation errors are incorporated into the model as an additive

### 2016-10-14 paper/paper.tex
tool name macro and abstract

@@
 
+\newcommand\tool{{\sf DSSynth}\xspace}
+
 \maketitle
@@
 %
-Modern control systems are by and large implemented via digital
-microcontrollers, which are designed to work in an embedded environment,
-within a dynamical plant that can present physical components.
-%
-This poses a new dimension to the problem of controllers synthesis, which is
-classically studied in the digital control literature.
-%
-In this study, we plan to provide a principled approach to extend this
-literature in a number of directions: 
-%we are interested in quantitative tasks; 
-we focus on automated correct-by-construction synthesis algorithms, as
-opposed to verification (or validation) objectives over a designed architecture; 
-and we encompass the complete range of
-approximations, related to time discretisation, quantisation effects, and
-finite-precision representations (with related rounding errors).  To this
-end, we propose a CEGIS-based solution that uses inductive 
-synthesis in conjunction with a digital verification algorithm to find a
-parametric solution for a digital controller given a continuous 
-plant specification.
+Modern control is implemented using digital microcontrollers, which are
+designed to work in an embedded environment, within a dynamical plant that
+can present physical components.
+%
+We present a new algorithm based on Counter-Example Guided Inductive
+Synthesis that automates the design of digital controllers that are
+correct-by-construction.  The synthesis result is sound with respect to the
+complete range of approximations, including time discretisation,
+quantisation effects, and finite-precision arithmetic and their related
+rounding errors.
+%
+We have implemented our new algorithm in a tool called \tool, and are able
+to automatically generate stable controllers for a set of intricate plant
+models taken from the literature within minutes.
 %
@@
 the user and Steps~A to D are automatically performed by our tool for
-Digital Systems Synthsis, named DSSynth.
+Digital Systems Synthsis, named \tool.
 %
@@
 Given a model for a plant for which to synthesise a controller, provided in
-an ANSI-C input file (Steps 1--3), DSSynth constructs a non-deterministic
+an ANSI-C input file (Steps 1--3), \tool constructs a non-deterministic
 model to represent the plant family (Step~A), and formulates a function
@@
 calculate the parameters of the controller to be synthesised (Step~C). 
-Finally, DSSynth builds an intermediate ANSI-C code for the digital system
+Finally, \tool builds an intermediate ANSI-C code for the digital system
 implementation, which is used as input for the CEGIS engine (Step~D).
@@
 
-The first set of benchmarks considers the discrete plant of a cruise 
-control model for the car accounting for rolling friction, aerodynamic drag, 
-and gravitational disturbance force~\cite{Astrom08} as follows
+The first set of benchmarks uses the discrete plant of a cruise control
+model for the car accounting for rolling friction, aerodynamic drag, and
+gravitational disturbance force~\cite{Astrom08} as follows
 %
@@
 damper~\cite{DBLP:conf/hybrid/WangGRJF16}, where the discrete 
-plant dynamics is represented by the following z-expression
+plant dynamics is represented by the following $z$-expression
 %

### 2016-10-14 paper/paper.tex
nudge

@@
 
-Using the closed-loop control system benchmarks described in Section~\ref{experimental-setup}, 
-the experimental evaluation of the present approach aims to answer two research questions:
+Using the closed-loop control system benchmarks described in
+Section~\ref{experimental-setup}, our experimental evaluation aims to answer
+two research questions:
 %
@@
 
-\caption{Experimental results\label{tab:results}}
+\caption{Experimental results obtained with \tool\label{tab:results}}
 \end{table}
@@
 
-The median runtime for our benchmark set is $197$\,s, implying that half of
-the controllers can be synthesised in less than $5$ minutes using our
-present approach.  Overall, the average synthesis time amounts to
-approximately $30$ minutes.  With respect to RQ2 we consider these times
-short enough to be of practical use to control engineers.  Regarding RQ1 we
-further conclude that the approach using a two-stage verification engine is
-able to synthesise stable controllers in the $12$ out of $15$ benchmarks,
-and can be complemented using the one-stage engine for $2$ additional
-benchmarks, where the inductive conjectures fail.  Both verification engines
-together enabled controller synthesis for $14$ out of $15$ benchmarks.  For
-the $1$ remaining benchmark our approach failed to synthesise a stable
-controller in the requested time limits.  This can be addressed by either
-increasing the fixed point word widths considered or using floating point
-arithmetic instead.  A link to the full experimental environment, including
-scripts to reproduce the results, all benchmarks and the DDSynth tool, is
-provided in the
+The median runtime for our benchmark set is $197$\,s, implying that \tool
+can synthesise half of the controllers in less than $5$ minutes.  Overall,
+the average synthesis time amounts to approximately $30$ minutes.  With
+respect to RQ2 we consider these times short enough to be of practical use
+to control engineers.  Regarding RQ1 we further conclude that the approach
+using a two-stage verification engine is able to synthesise stable
+controllers in the $12$ out of $15$ benchmarks, and can be complemented
+using the one-stage engine for $2$ additional benchmarks, where the
+inductive conjectures fail.  Both verification engines together enabled
+controller synthesis for $14$ out of $15$ benchmarks.  For the $1$ remaining
+benchmark our approach failed to synthesise a stable controller in the
+requested time limits.  This can be addressed by either increasing the fixed
+point word widths considered or using floating point arithmetic instead. 
+A~link to the full experimental environment, including scripts to reproduce
+the results, all benchmarks and the \tool tool, is provided in the
 footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}

### 2016-10-14 paper/paper.tex
abstract

@@
 designed to work in an embedded environment, within a dynamical plant that
-can present physical components.
-%
-We present a new algorithm based on Counter-Example Guided Inductive
-Synthesis that automates the design of digital controllers that are
-correct-by-construction.  The synthesis result is sound with respect to the
+represents physical components.
+%
+We present a new algorithm based on counterexample guided inductive
+synthesis that automates the design of digital controllers that are
+correct by construction.  The synthesis result is sound with respect to the
 complete range of approximations, including time discretisation,

### 2016-10-14 paper/paper.tex
comma
Minor orthography changes.

@@
 All experiments were conducted on a 12-core 2.40\,GHz Intel Xeon E5-2440
-with 96\,GB of RAM, and Linux OS.  All times given are wall clock time in
+with 96\,GB of RAM and Linux OS.  All times given are wall clock time in
 seconds as measured by the UNIX date command.  For the approach using a
@@
 engine %inductive back-end 
-is able to find a stable solution in less than one minute.  This is possible if the
+is able to find a stable solution in less than five minutes.  This is possible if the
 inductive solutions need to be refined with few counterexamples and
@@
 using a two-stage verification engine is able to synthesise stable
-controllers in the $12$ out of $15$ benchmarks, and can be complemented
+controllers in $12$ out of the $15$ benchmarks, and can be complemented
 using the one-stage engine for $2$ additional benchmarks, where the
@@
 whilst enhancing the procedure by evaluating the quantisation effects of
-the Hardware interfaces (ADC/DAC) to obtain an accurate discrete time FWL
+the Hardware interfaces (ADC/DAC) to obtain an accurate discrete-time FWL
 representation of the continuous dynamics.

### 2016-10-14 paper/paper.tex
nudge
hscc17

--- 2016-10-14 paper/paper.tex
@@
 
-\newcommand\tool{{\sf DSSynth}\xspace}
-
 \maketitle
@@
 %
-Modern control is implemented using digital microcontrollers, which are
-designed to work in an embedded environment, within a dynamical plant that
-represents physical components.
-%
-We present a new algorithm based on counterexample guided inductive
-synthesis that automates the design of digital controllers that are
-correct by construction.  The synthesis result is sound with respect to the
-complete range of approximations, including time discretisation,
-quantisation effects, and finite-precision arithmetic and their related
-rounding errors.
-%
-We have implemented our new algorithm in a tool called \tool, and are able
-to automatically generate stable controllers for a set of intricate plant
-models taken from the literature within minutes.
+Modern control systems are by and large implemented via digital
+microcontrollers, which are designed to work in an embedded environment,
+within a dynamical plant that can present physical components.
+%
+This poses a new dimension to the problem of controllers synthesis, which is
+classically studied in the digital control literature.
+%
+In this study, we plan to provide a principled approach to extend this
+literature in a number of directions: 
+%we are interested in quantitative tasks; 
+we focus on automated correct-by-construction synthesis algorithms, as
+opposed to verification (or validation) objectives over a designed architecture; 
+and we encompass the complete range of
+approximations, related to time discretisation, quantisation effects, and
+finite-precision representations (with related rounding errors).  To this
+end, we propose a CEGIS-based solution that uses inductive 
+synthesis in conjunction with a digital verification algorithm to find a
+parametric solution for a digital controller given a continuous 
+plant specification.
 %
@@
 quantisation noise.  The resulting closed-loop system is a program loop that
-operates on bit-vectors encoded using fixed-point arithmetic with finite-word
-length (FWL). The deterministic effects of the FWL and
+operates on bit-vectors encoded using fixed-point arithmetic with fixed-word
+length (FWL). 
+\red{[acronym later defined as finite-word length - please unify use]} 
+The deterministic effects of the FWL and
 quantisation errors are incorporated into the model as an additive
@@
 }
-\caption{System equivalent to the system in Figure~\ref{fig:sampledsystem}\label{fig:digsystem1}}
+\caption{System equivalent to the system in Figure~\ref{fig:sampledsystem} \red{please do not add a vector and a transfer function! what does that even mean?}\label{fig:digsystem1}}
 \end{figure*}
@@
 
-Lemma~\ref{lemma:eq_int_stab} provides the necessary conditions for the
-ability of a digital controller to stabilize the closed loop system,
+Lemma~\ref{lemma:eq_int_stab} \red{not a lemma} provides the necessary conditions for the digital controller to stabilize the closed loop system, 
 considering plant parametric uncertainties (i.e., $\Delta_p \vec{G}$),
 quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in the control
-software.  Based on it, the model for plant uncertainty due quantisation
-noise (i.e., $\Delta_q \vec{G}$) may be disregarded if the conditions on
-Lemma~\ref{lemma:eq_int_stab} are satisfied and if the quantisation noise is
-bounded.  The boundedness of the quantisation noise is
-assumption~\ref{whitenoise}.
+software.  
+Notice that the model for plant uncertainty due to quantisation noise (i.e., $\Delta_q \vec{G}$) may be disregarded if the conditions on
+Lemma~\ref{lemma:eq_int_stab} \red{not a lemma} are satisfied and if the quantisation noise is
+bounded.  The boundedness of the quantisation noise comes from Assumption~\ref{whitenoise}.
 
@@
 the user and Steps~A to D are automatically performed by our tool for
-Digital Systems Synthsis, named \tool.
+Digital Systems Synthsis, named DSSynth.
 %
@@
 Given a model for a plant for which to synthesise a controller, provided in
-an ANSI-C input file (Steps 1--3), \tool constructs a non-deterministic
+an ANSI-C input file (Steps 1--3), DSSynth constructs a non-deterministic
 model to represent the plant family (Step~A), and formulates a function
@@
 calculate the parameters of the controller to be synthesised (Step~C). 
-Finally, \tool builds an intermediate ANSI-C code for the digital system
+Finally, DSSynth builds an intermediate ANSI-C code for the digital system
 implementation, which is used as input for the CEGIS engine (Step~D).
@@
 %
-The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that this controller
-$C(z)$ (Eq.~\eqref{Eq:running-example-controller}) stabilizes the
-closed-loop system for the discrete plant model $G(z)$
+The authors claim that this controller $C(z)$
+(Eq.~\eqref{Eq:running-example-controller}) stabilizes the closed-loop
+system for the discrete plant model $G(z)$
 (Eq.~\ref{Eq:running-example-plant}).  However, if the effects of finite
@@
 
-We now demonstrate how our approach solves the synthesis problem for the
-example given in the previous section.  We start with the candidate solution
-with all coefficients zero, as given below, and a precision of $I_b=16$,
-$F_b=24$.  The digital controller is designed with standard techniques for
-control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}.
+We will illustrate our synthesis approach on the running example
+described in the previous section. 
+%in Sec.~\ref{sec:running-ex}.
+We start with the candidate solution with all coefficients zero 
+given below at $I_b=16,F_b=24$.
+Note that the digital controller is designed with typical control system
+techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
 %
@@
 %$$
-$$ C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0} $$
+$$
+C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}
+$$
 
@@
 %
-$$ \tilde G(z) = \frac{0.026506}{1.000610z+1.002838} $$
+$$
+\tilde G(z) = \frac{0.026506}{1.000610z+1.002838}
+$$
 
@@
 We add this counterexample to {\sc inputs} and initiate the {\sc synthesise}
-phase, where we obtain the following candidate solution:
+phase, where we get the following candidate solution:
 %
@@
 
-This time, the {\sc uncertainty} check does not find any
-counterexample and we pass the current candidate solution to the {\sc
+This time, the {\sc uncertainty} check does not find any more
+counterexamples and we pass the current candidate solution to the {\sc
 precision} verification stage.
@@
 Since the previous counterexamples were obtained at lower precision, we
-remove them from the set of counterexamples.  Back in the {\sc synthesise}
+remove them from the counterexample set.  Back in the {\sc synthesise}
 phase, we re-start the process with a candidate solution with all
@@
 %$$
-$$ \tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785} $$
+$$
+\tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785}
+$$
 
@@
 %
-$$ C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357} $$
+$$
+C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}
+$$
 %
@@
 This candidate solution is validated as the final solution by both stages 
-{\sc uncertainty} and {\sc precision} in the {\sc verify} phase.
-
-%, which fails to find a new counterexample (i.e. returns UNSAT).
+{\sc uncertainty} and {\sc precision} in the
+{\sc verify} phase. %, which fails to find a new counterexample (i.e. returns UNSAT).
 
@@
 
-The first set of benchmarks uses the discrete plant of a cruise control
-model for the car accounting for rolling friction, aerodynamic drag, and
-gravitational disturbance force~\cite{Astrom08} as follows
+The first set of benchmarks considers the discrete plant of a cruise 
+control model for the car accounting for rolling friction, aerodynamic drag, 
+and gravitational disturbance force~\cite{Astrom08} as follows
 %
@@
 damper~\cite{DBLP:conf/hybrid/WangGRJF16}, where the discrete 
-plant dynamics is represented by the following $z$-expression
+plant dynamics is represented by the following z-expression
 %
@@
 
-Using the closed-loop control system benchmarks described in
-Section~\ref{experimental-setup}, our experimental evaluation aims to answer
-two research questions:
+Using the closed-loop control system benchmarks described in Section~\ref{experimental-setup}, 
+the experimental evaluation of the present approach aims to answer two research questions:
 %
@@
 
-\caption{Experimental results obtained with \tool\label{tab:results}}
+\caption{Experimental results\label{tab:results}}
 \end{table}
@@
 
-The median runtime for our benchmark set is $197$\,s, implying that \tool
-can synthesise half of the controllers in less than $5$ minutes.  Overall,
-the average synthesis time amounts to approximately $30$ minutes.  With
-respect to RQ2 we consider these times short enough to be of practical use
-to control engineers.  Regarding RQ1 we further conclude that the approach
-using a two-stage verification engine is able to synthesise stable
-controllers in the $12$ out of $15$ benchmarks, and can be complemented
-using the one-stage engine for $2$ additional benchmarks, where the
-inductive conjectures fail.  Both verification engines together enabled
-controller synthesis for $14$ out of $15$ benchmarks.  For the $1$ remaining
-benchmark our approach failed to synthesise a stable controller in the
-requested time limits.  This can be addressed by either increasing the fixed
-point word widths considered or using floating point arithmetic instead. 
-A~link to the full experimental environment, including scripts to reproduce
-the results, all benchmarks and the \tool tool, is provided in the
+The median runtime for our benchmark set is $197$\,s, implying that half of
+the controllers can be synthesised in less than $5$ minutes using our
+present approach.  Overall, the average synthesis time amounts to
+approximately $30$ minutes.  With respect to RQ2 we consider these times
+short enough to be of practical use to control engineers.  Regarding RQ1 we
+further conclude that the approach using a two-stage verification engine is
+able to synthesise stable controllers in the $12$ out of $15$ benchmarks,
+and can be complemented using the one-stage engine for $2$ additional
+benchmarks, where the inductive conjectures fail.  Both verification engines
+together enabled controller synthesis for $14$ out of $15$ benchmarks.  For
+the $1$ remaining benchmark our approach failed to synthesise a stable
+controller in the requested time limits.  This can be addressed by either
+increasing the fixed point word widths considered or using floating point
+arithmetic instead.  A link to the full experimental environment, including
+scripts to reproduce the results, all benchmarks and the DDSynth tool, is
+provided in the
 footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}

### 2016-10-14 paper/paper.tex

--- 2016-10-14 paper/paper.tex
@@
 %---------------------------------
-\subsection{Description of Benchmarks}
+\subsection{Description of the Benchmarks}
 \label{experimental-setup}

### 2016-10-14 paper/paper.tex
typo

--- 2016-10-14 paper/paper.tex
@@
   representation is key to the performance of our approach yielding,
-  in most cases, to a speed-up of at least two orders of magnitude over a
+  in most cases, a speed-up of at least two orders of magnitude over a
   conventional one-stage verification engine.
@@
 whilst enhancing the procedure by evaluating the quantisation effects of
-the Hardware interfaces (ADC/DAC) to obtain an accurate discrete-time FWL
+the Hardware interfaces (ADC/DAC) to obtain an accurate discrete time FWL
 representation of the continuous dynamics.

### 2016-10-14 paper/paper.tex
small edit
typo

@@
 show that the speedup yielded by the second approach 
-is in most cases of several orders of magnitude.
+is in most cases of at least two orders of magnitude.
 
@@
 applications is considered~\cite{Franklin15}, in order to evaluate the
-present approach full capabilities.  In particular, satellites often require
+full capabilities of the present approach.  In particular, satellites often require
 attitude (pose) control for proper orientation of antennas and sensors

### 2016-10-14 paper/paper.tex
fixes

@@
 	minimum height=1cm,
-        label=\textbf{Plant}] (gs) {{\sc $G(s) + \Delta_p G_s$}};
+        label=\textbf{Plant}] (gs) {{\sc $\hat{G}(s)$}};
    \node[draw=none] (ud) at ([xshift=-2cm,yshift=.15cm]gs)  {$U(s)$};
@@
 	minimum height=1cm,
-        label=\textbf{Plant}] (gs) {{\sc $G(z) + \Delta_p \vec{G}$}};
+        label=\textbf{Plant}] (gs) {{\sc $\hat{G}(z)$}};
    \node[draw=none] (y) at ([xshift=2cm,yshift=.15cm]gs)  {$Y(z)$};
@@
 }
-\caption{System equivalent to the system in Figure~\ref{fig:sampledsystem} \red{please do not add a vector and a transfer function! what does that even mean?}\label{fig:digsystem1}}
+\caption{System equivalent to the system in Figure~\ref{fig:sampledsystem} 
+\label{fig:digsystem1}}
 \end{figure*}
@@
 \label{FWL_tf}
-&f_b (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = x-(x\mod\tilde x) \\
+&f_b : \mathbb{R} \rightarrow  \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = f_b(x) : \tilde x=x-(x\mod\tilde x)\\
 &FWL_b[P \in \mathcal{P}] = \tilde P \in \mathcal{P}^{n}\langle I_b,F_b \rangle : c_i \in \vec{P} \wedge \tilde c_i \in \tilde \vec{P}=f_b(c_i)  \nonumber
@@
 the rounding off effect.  We may encompass all the uncertainty as
-$\Delta{\vec{G}}=\Delta_p{\vec{G}}+\Delta_b{\vec{G}}$.  % Since this value is
-% nondeterministic, the set of possible polynomial coefficients of $\tilde G(z)$ is
-% denoted by $\mathfrak{G}(z)$.
+$\Delta{\vec{G}}=\Delta_p{\vec{G}}+\Delta_b{\vec{G}}$. 
+Since the complexity of SAT solvers is worst case exponential with respect to the number of clauses (which are directly proportional to the size of the bit-vectors), our algorithm tries to solve the problem first for a low $I_b, F_b$ iteratively increasing the precision if it is insuficient.
 

### 2016-10-14 paper/paper.tex
First draft of threats to validity.

@@
 
+\subsection{Threats to validity}
+
+The experimental evaluation in section~\ref{experimental-results} shows
+a very positive evaluation of \tool over a diverse set of real-world
+benchmarks. Nevertheless, the set of benchmarks is limited within the
+scope of this paper and \tool's performance may not generalise to other
+benchmark scenarios.
+
+Furthermore, our algorithm to select suitable FWL word widths to model
+plant behaviour employs a heuristic based on user-provided controller
+word width specifications. Given the encouraging results of our benchmarks,
+this heuristic appears to be strong enough for the current benchmark set,
+but this may not hold in general. Further experiments towards determining
+suitable plant FWL configurations may thus be necessary in future work.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-10-14 paper/paper.tex
typo

--- 2016-10-14 paper/paper.tex
@@
 two-stage verification engine we apply a timeout of 8 hours per benchmark,
-and 24 hours for the approach using a one-stage engine.
+and 24 hours for the approach using an one-stage engine.
 

### 2016-10-14 paper/paper.tex
review conclusions

@@
 show that the speedup yielded by the second approach 
-is in most cases of at least two orders of magnitude.
+is in most cases of several orders of magnitude.
 
@@
 applications is considered~\cite{Franklin15}, in order to evaluate the
-full capabilities of the present approach.  In particular, satellites often require
+present approach full capabilities.  In particular, satellites often require
 attitude (pose) control for proper orientation of antennas and sensors
@@
 two-stage verification engine we apply a timeout of 8 hours per benchmark,
-and 24 hours for the approach using an one-stage engine.
+and 24 hours for the approach using a one-stage engine.
 
@@
 
-We have presented a CEGIS-based approach that uses inductive synthesis in
-conjunction with an algorithm for verifying robust closed-loop stability, 
-in order to compute a parametric solution for a digital controller given 
-a continuous (or discrete) plant specification.  This enables us to automatically
-synthesise correct-by-construction digital controllers for a given model of
-their physical environment.  Our approach addresses the effects of the
-quantisers (A/D and D/A converters) as time discretisation elements with
-quantisation noise.  Our experimental results show that our CEGIS-based
-approach is able to synthesise stable controllers in most benchmarks within
+We have presented a CEGIS-based approach implemented in a tool called \tool, 
+which uses inductive synthesis in conjunction with an algorithm for verifying 
+robust closed-loop stability. In particular, \tool is able to compute a parametric solution 
+for a stabilizing digital controller given a continuous (or discrete) plant 
+specification.  This enables us to automatically synthesise correct-by-construction 
+digital controllers for a given model of their physical environment.  
+Our approach addresses the effects of the quantisers (A/D and D/A converters) 
+as time discretisation elements with quantisation noise.  Our experimental results 
+show that \tool is able to synthesise stable controllers in most benchmarks within
 reasonable time frames fully automatically.
@@
 Future work will be the extension of this CEGIS-based approach to further
-classes of systems.  We will also consider performance requirements while
+classes of systems, including state-space representation.  
+We will also consider performance requirements while
 synthesising the digital controller.

### 2016-10-14 paper/paper.tex
Extended threats to validity.

@@
 
-The experimental evaluation in section~\ref{experimental-results} shows
-a very positive evaluation of \tool over a diverse set of real-world
+The experimental evaluation in section~\ref{experimental-results} outlines
+a very positive assessment of \tool over a diverse set of real-world
 benchmarks. Nevertheless, the set of benchmarks is limited within the
 scope of this paper and \tool's performance may not generalise to other
-benchmark scenarios.
+benchmark scenarios. This can be addressed by expanding the benchmark set
+based on available literature in future experiments.
 
@@
 suitable plant FWL configurations may thus be necessary in future work.
+
+Finally, the experimental results we attained using \tool with
+regard to stability properties may not generalise to other properties
+expressed over the controller to synthesize. The inductive nature of the
+two-stage back-end of \tool increases performance significantly compared to the
+one-stage back-end, but this performance benefit introduced by CEGIS'
+inductive generalisations may not perform equally well for other controller
+properties. Additional experiments are necessary to confirm that the performance
+of our inductive synthesis approach can be leveraged in those scenarios as well.
 

### 2016-10-14 paper/paper.tex
Minor style changes.

--- 2016-10-14 paper/paper.tex
@@
 a very positive assessment of \tool over a diverse set of real-world
-benchmarks. Nevertheless, the set of benchmarks is limited within the
+benchmarks. Nevertheless, this set of benchmarks is limited within the
 scope of this paper and \tool's performance may not generalise to other

### 2016-10-14 paper/paper.tex
wordings

--- 2016-10-14 paper/paper.tex
@@
 
-The experimental evaluation in section~\ref{experimental-results} shows
-a very positive evaluation of \tool over a diverse set of real-world
-benchmarks. Nevertheless, the set of benchmarks is limited within the
-scope of this paper and \tool's performance may not generalise to other
-benchmark scenarios.
-
-Furthermore, our algorithm to select suitable FWL word widths to model
+We report a favourable assessment of \tool over a diverse set of real-world
+benchmarks.  Nevertheless, the set of benchmarks is limited within the scope
+of this paper and \tool's performance may not generalise to other
+application scenarios.  This can be addressed by expanding the benchmark set
+in future experiments.
+
+Furthermore, our algorithm for selecting the fixed-point precision to model
 plant behaviour employs a heuristic based on user-provided controller
-word width specifications. Given the encouraging results of our benchmarks,
+word-width specifications.  Given the encouraging results of our benchmarks,
 this heuristic appears to be strong enough for the current benchmark set,
-but this may not hold in general. Further experiments towards determining
+but this may not generalise.  Further experiments towards determining
 suitable plant FWL configurations may thus be necessary in future work.
+
+Finally, the experimental results we obtained using \tool for stability
+properties may not generalise to other properties.  The inductive nature of
+the two-stage back-end of \tool increases performance significantly compared
+to the one-stage back-end, but this performance benefit introduced by CEGIS'
+inductive generalisations may not be observed for other controller
+properties.  Additional experiments are necessary to confirm that the
+performance of our inductive synthesis approach can be leveraged in those
+scenarios as well.
 

### 2016-10-14 paper/paper.tex

@@
 
-We report a favourable assessment of \tool over a diverse set of real-world
-benchmarks.  Nevertheless, the set of benchmarks is limited within the scope
-of this paper and \tool's performance may not generalise to other
-application scenarios.  This can be addressed by expanding the benchmark set
+We report a faviourable assessment of \tool over a diverse set of real-world
+benchmarks. Nevertheless, this set of benchmarks is limited within the
+scope of this paper and \tool's performance may not generalise to other
+benchmark scenarios. This can be addressed by expanding the benchmark set
 in future experiments.
 
-Furthermore, our algorithm for selecting the fixed-point precision to model
+Furthermore, our algorithm to select suitable FWL word widths to model
 plant behaviour employs a heuristic based on user-provided controller

### 2016-10-14 paper/paper.tex
wording

@@
 $\Delta{\vec{G}}=\Delta_p{\vec{G}}+\Delta_b{\vec{G}}$. 
-Since the complexity of SAT solvers is worst case exponential with respect to the number of clauses (which are directly proportional to the size of the bit-vectors), our algorithm tries to solve the problem first for a low $I_b, F_b$ iteratively increasing the precision if it is insuficient.
+Since the complexity of SAT solvers is worst-case exponential in the size of
+the problem instance, our algorithm tries to solve the problem first for a
+low $I_b$, $F_b$, iteratively increasing the precision if it is insuficient.
 

### 2016-10-14 paper/paper.tex
more corrections

@@
 Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$
-(\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$ \red{, as defined later?}), errors in the numeric
-calculations, or roundoffs in the quantisation.  These uncertainties \red{may be [can be?, are?]} 
+(\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$ which come from tolerances/imprecisions in the original model), errors in the numeric
+calculations, or roundoffs in the quantisation.  These uncertainties are 
 parametrically expressed by additive terms, resulting in a uncertain model
@@
 that the parametric errors in the plant have the same polynomial order as
-the plant itself (\red{other errors [which precisely? all others?]} are ensured to fulfil this property in our
+the plant itself (all other errors described in this paper are ensured to fulfil this property in our
 implementation).
@@
 \Delta{\vec{P}}=[\Delta{n}_{0}\ \Delta{n}_{1}\ \hdots \ \Delta{n}_{M}\ \Delta{d}_{0}\ \Delta{d}_{1}\ \hdots\ \Delta{d}_{N}\ ]^T \; 
+\label{eq:delta_coefficients}
 \end{equation}
@@
 or work over their respective coefficients $\vec{G}, \vec{C}$ in vector form.
-
-\red{[I've tried to clean the notations above. BUT: you cannot later add a transfer function with a vector of coefficients! Heresy!]}
 
@@
 
-A typical digital control system system with continuous plant and discrete
+A typical digital control system system with a continuous plant and a discrete
 controller is illustrated in Figure~\ref{fig:sampledsystem}.  The DAC and
-ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$ \red{[this is an assumption and as such must be stated.]},
+ADC converters introduce quantisation errors which are modeled as noises $\nu_{1}(z)$ and $\nu_{2}(z)$,
 $G(s)$ is the continuous-time plant model with parametric additive
-uncertainty $\Delta_p \vec{G}_s$ \red{[above you used n, d subscripts, here s?]}, $R(z)$ is the reference signal, $U(z)$ is
+uncertainty $\Delta_p{G}_n(s)$ and $\Delta_p{G}_d(s)$, $R(z)$ is the reference signal, $U(z)$ is
 the control signal, and $\hat{Y}(z)$ is the output signal affected by the
@@
 i.e., ADC and DAC conversions.  Assuming linearity and independence between
-these sources, the uncertain model may be rewritten as 
-\red{[unclear whether this is over the s or z domain. further there is lack of proper subscripts (n,d,s), as per the notations introduced above.]}
+these sources, the uncertain model may be rewritten as a vector of coefficients in the z-domain using equations \ref{eq:coefficients} and \ref{eq:delta_coefficients}
 %
@@
 and assume that there exists a function
-$\mathit{FWL}[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$,
-which applies the FWL effects to a polynomial.  
-\red{above $\mathcal{P}$ was defined as a single polynomial, now it is a space of polynomials.
-actually space of polynomials form specific algebraic structures, called diods -- we should have used those ...
-}
+$\mathit{FWL}_n[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$,
+which applies the FWL effects to a polynomial, with an equivalent $\mathit{FWL}_{n,m}[\cdot]:\mathcal{P}^{n,m}\rightarrow \mathcal{P}^{n,m}\langle I,F \rangle$ that apllies the same effect to a ratio of polynomials, where
 $\mathcal{P}^{n}$ is the
-space of polynomials of $n$-th order and $\mathcal{P}^{n}\langle I,F
+space of polynomials of $n$-th order, $\mathcal{P}^{n}\langle I,F
 \rangle$ is is the space of polynomials with coefficients in
-$\mathbb{R}\langle I,F \rangle$.
-%
-%, \red{[explain index n! why do you need to work on a Euclidean domain?]}. 
-%
+$\mathbb{R}\langle I,F \rangle$, and $\mathcal{P}^{n,m}$,  $\mathcal{P}^{n,m}\langle I,F
+\rangle$ are their rational equivalent.
+
 \red{[above you introduced a notation for poly ratios, which now you do not use?]}
 Thus, the perturbed controller model $\hat{C}(z)$ may be obtained from the
-original model $C(z)=\frac{N_{C}(z)}{D_{C}(z)}$ as follows:
+original model $C(z)=\frac{C_{n}(z)}{C_{d}(z)}$ as follows:
 %
 \begin{equation}
-\hat{C}(z)=\frac{\mathit{FWL}[N_{C}(z)]}{\mathit{FWL}[D_{C}(z)]}.
+\hat{C}(z)=\mathit{FWL}_{M_C,N_C}[C(z)]=\frac{\mathit{FWL}_{M_C}[C_n(z)]}{\mathit{FWL}_{N_C}[C_d(z)]}.
 \end{equation}

### 2016-10-14 paper/paper.tex
Switch RQ1/RQ2, rephrased RQ2.

@@
 
-\item RQ1 \textbf{(sanity check)} which results does our CEGIS approach to
-FWL controller synthesis obtain upon synthesising/verifying benchmarks that
-compose the specified suite?
-
-\item RQ2 \textbf{(performance)} does the CEGIS approach provide a feasible
+\item RQ1 \textbf{(performance)} does the CEGIS approach provide a feasible
 solution in reasonable time considering robust stability of FWL digital
 controllers?
+
+\item RQ2 \textbf{(sanity check)} are the synthesised controllers sound
+and can their stability be confirmed outside of our model?
 
@@
 the average synthesis time amounts to approximately $30$ minutes.  With
-respect to RQ2 we consider these times short enough to be of practical use
-to control engineers.  Regarding RQ1 we further conclude that the approach
+respect to RQ1 we consider these times short enough to be of practical use
+to control engineers.  We further conclude that the approach
 using a two-stage verification engine is able to synthesise stable
@@
 point word widths considered or using floating point arithmetic instead. 
+The synthesised controllers were confirmed to be stable outside of our
+model representation using MATLAB, positively answering RQ2.
 A~link to the full experimental environment, including scripts to reproduce

### 2016-10-14 paper/paper.tex
add figures

--- 2016-10-14 paper/paper.tex
@@
 \usepackage{graphicx}
-\usepackage{float,subfig}
+\usepackage{float}
+\usepackage{subcaption}
 \usepackage{xspace,framed}
@@
 $\Delta{\vec{G}}=\Delta_p{\vec{G}}+\Delta_b{\vec{G}}$. 
-Since the complexity of SAT solvers is worst-case exponential in the size of
-the problem instance, our algorithm tries to solve the problem first for a
-low $I_b$, $F_b$, iteratively increasing the precision if it is insuficient.
+Since the complexity of SAT solvers is worst case exponential with respect to the number of clauses (which are directly proportional to the size of the bit-vectors), our algorithm tries to solve the problem first for a low $I_b, F_b$ iteratively increasing the precision if it is insuficient.
 
@@
 
+Figure~\ref{fig:bode} shows the Bode diagram of the closed-loop system from~\cite{DBLP:conf/hybrid/WangGRJF16} 
+(Fig.~\ref{fig:original}) and from our synthesiser (Fig.~\ref{fig:cegiscontroller}). 
+The phase margin in Figure~\ref{fig:original} is negative, which means that the controller 
+from~\cite{DBLP:conf/hybrid/WangGRJF16} is unstable, considering FWL effects. 
+Note that the final solution from \tool is stable since it presents an infinite phase margin 
+and a gain margin of $17.8 dB$.
+%
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{figures/runningexample_bd0.pdf}
+        \caption{Original controller~\cite{DBLP:conf/hybrid/WangGRJF16}.}
+        \label{fig:original}
+    \end{subfigure}
+    ~
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{figures/runningexample_bd2.pdf}
+        \caption{Controller synthesised by \tool.}
+        \label{fig:cegiscontroller}
+    \end{subfigure}
+    \caption{Bode diagram for original~\cite{DBLP:conf/hybrid/WangGRJF16} and synthesised closed-loop systems.}\label{fig:bode}
+\end{figure}
+
+Figure~\ref{fig:step} shows the step responses of the closed-loop system with the original controller~\cite{DBLP:conf/hybrid/WangGRJF16} (Figure~\ref{fig:step0}), the first candidate solution (Figure~\ref{fig:step1}), and the final solution from \tool (Fig.~\ref{fig:step2}).
+The step response in Figure~\ref{fig:step0} confirms that the stability loss if we consider FWL effects.
+However, Figure~\ref{fig:step2} shows that the first candidate controller is able to stabilize the closed-loop system without uncertainties, but it is rejected by \tool since this solution is not considered to be sound.
+Finally, Figure~\ref{fig:step2} shows a stable behavior for the final (sound) solution, which presents a lower settling time.
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{figures/runningexample_step0.pdf}
+        \caption{Orignal controller.}
+        \label{fig:step0}
+    \end{subfigure}
+    ~
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{figures/runningexample_step1.pdf}
+        \caption{First candidate solution.}
+        \label{fig:step1}
+    \end{subfigure}
+    ~
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{figures/runningexample_step2.pdf}
+        \caption{Final solution by \tool.}
+        \label{fig:step2}
+    \end{subfigure}
+    \caption{Step responses for original~\cite{DBLP:conf/hybrid/WangGRJF16} closed-loop system with FWL effects and for each {\sc synthesise} step of \tool.}\label{fig:step}
+\end{figure*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We report a faviourable assessment of \tool over a diverse set of real-world
-benchmarks. Nevertheless, this set of benchmarks is limited within the
+The experimental evaluation in section~\ref{experimental-results} shows
+a very positive evaluation of \tool over a diverse set of real-world
+benchmarks. Nevertheless, the set of benchmarks is limited within the
 scope of this paper and \tool's performance may not generalise to other
-benchmark scenarios. This can be addressed by expanding the benchmark set
-in future experiments.
+benchmark scenarios.
 
@@
 plant behaviour employs a heuristic based on user-provided controller
-word-width specifications.  Given the encouraging results of our benchmarks,
+word width specifications. Given the encouraging results of our benchmarks,
 this heuristic appears to be strong enough for the current benchmark set,
-but this may not generalise.  Further experiments towards determining
+but this may not hold in general. Further experiments towards determining
 suitable plant FWL configurations may thus be necessary in future work.
-
-Finally, the experimental results we obtained using \tool for stability
-properties may not generalise to other properties.  The inductive nature of
-the two-stage back-end of \tool increases performance significantly compared
-to the one-stage back-end, but this performance benefit introduced by CEGIS'
-inductive generalisations may not be observed for other controller
-properties.  Additional experiments are necessary to confirm that the
-performance of our inductive synthesis approach can be leveraged in those
-scenarios as well.
 

### 2016-10-14 paper/paper.tex
improve section 'Program synthesis for the example'

@@
 {\sc uncertainty} and {\sc precision} in the {\sc verify} phase.
+In particular, Figure~\ref{fig:bode} shows the Bode diagram of the closed-loop system from~\cite{DBLP:conf/hybrid/WangGRJF16} 
+(Fig.~\ref{fig:original}) and from our synthesiser (Fig.~\ref{fig:cegiscontroller}).
 
@@
 
-Figure~\ref{fig:bode} shows the Bode diagram of the closed-loop system from~\cite{DBLP:conf/hybrid/WangGRJF16} 
-(Fig.~\ref{fig:original}) and from our synthesiser (Fig.~\ref{fig:cegiscontroller}). 
 The phase margin in Figure~\ref{fig:original} is negative, which means that the controller 

### 2016-10-14 paper/paper.tex
Minor spelling corrections.
fix typos

--- 2016-10-14 paper/paper.tex
@@
 {\sc uncertainty} and {\sc precision} in the {\sc verify} phase.
+In particular, Figure~\ref{fig:bode} shows the Bode diagram of the illustrative example from~\cite{DBLP:conf/hybrid/WangGRJF16} 
+(Fig.~\ref{fig:original}) and from our synthesiser (Fig.~\ref{fig:cegiscontroller}). 
+The phase margin is negative as shown in Figure~\ref{fig:original}, which means that the controller 
+from~\cite{DBLP:conf/hybrid/WangGRJF16} is unstable, considering FWL effects. 
+However, the final solution from \tool is stable since it presents an infinite phase margin 
+and a gain margin of $17.8 dB$.
 
@@
 
-Figure~\ref{fig:bode} shows the Bode diagram of the closed-loop system from~\cite{DBLP:conf/hybrid/WangGRJF16} 
-(Fig.~\ref{fig:original}) and from our synthesiser (Fig.~\ref{fig:cegiscontroller}). 
-The phase margin in Figure~\ref{fig:original} is negative, which means that the controller 
-from~\cite{DBLP:conf/hybrid/WangGRJF16} is unstable, considering FWL effects. 
-Note that the final solution from \tool is stable since it presents an infinite phase margin 
-and a gain margin of $17.8 dB$.
-%
 \begin{figure}
@@
 
-Figure~\ref{fig:step} shows the step responses of the closed-loop system with the original controller~\cite{DBLP:conf/hybrid/WangGRJF16} (Figure~\ref{fig:step0}), the first candidate solution (Figure~\ref{fig:step1}), and the final solution from \tool (Fig.~\ref{fig:step2}).
-The step response in Figure~\ref{fig:step0} confirms that the stability loss if we consider FWL effects.
-However, Figure~\ref{fig:step2} shows that the first candidate controller is able to stabilize the closed-loop system without uncertainties, but it is rejected by \tool since this solution is not considered to be sound.
-Finally, Figure~\ref{fig:step2} shows a stable behavior for the final (sound) solution, which presents a lower settling time.
+Figure~\ref{fig:step} shows the step responses of the closed-loop system 
+with the original controller~\cite{DBLP:conf/hybrid/WangGRJF16} (Figure~\ref{fig:step0}), 
+the first candidate solution (Figure~\ref{fig:step1}), and the final solution from \tool (Fig.~\ref{fig:step2}). 
+The step response in Figure~\ref{fig:step0} confirms the stability loss if we consider FWL effects. 
+However, Figure~\ref{fig:step2} shows that the first candidate controller is able to stabilize 
+the closed-loop system without uncertainties, but it is rejected by \tool since this solution 
+is not considered to be sound. Finally, Figure~\ref{fig:step2} shows a stable behavior 
+for the final (sound) solution, which presents a lower settling time.
 

### 2016-10-14 paper/paper.tex
spell-checking errors

--- 2016-10-14 paper/paper.tex
@@
 \usepackage{graphicx}
-\usepackage{float}
-\usepackage{subcaption}
+\usepackage{float,subfig}
 \usepackage{xspace,framed}
@@
 $\mathit{FWL}_n[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$,
-which applies the FWL effects to a polynomial, with an equivalent $\mathit{FWL}_{n,m}[\cdot]:\mathcal{P}^{n,m}\rightarrow \mathcal{P}^{n,m}\langle I,F \rangle$ that apllies the same effect to a ratio of polynomials, where
+which applies the FWL effects to a polynomial, with an equivalent $\mathit{FWL}_{n,m}[\cdot]:\mathcal{P}^{n,m}\rightarrow \mathcal{P}^{n,m}\langle I,F \rangle$ that applies the same effect to a ratio of polynomials, where
 $\mathcal{P}^{n}$ is the
@@
 the user and Steps~A to D are automatically performed by our tool for
-Digital Systems Synthsis, named \tool.
+Digital Systems Synthesis, named \tool.
 %
@@
 This intermediate ANSI-C code model contains a specification $\phi$ for the
-property of interst (i.e., robust stability) and is passed to the
+property of interest (i.e., robust stability) and is passed to the
 Counterexample-Guided Inductive Synthesis (CEGIS) module of
@@
 the problem instance, our algorithm tries to solve the problem first for a
-low $I_b$, $F_b$, iteratively increasing the precision if it is insuficient.
+low $I_b$, $F_b$, iteratively increasing the precision if it is insufficient.
 
@@
 
-Figure~\ref{fig:bode} shows the Bode diagram of the closed-loop system from~\cite{DBLP:conf/hybrid/WangGRJF16} 
-(Fig.~\ref{fig:original}) and from our synthesiser (Fig.~\ref{fig:cegiscontroller}). 
-The phase margin in Figure~\ref{fig:original} is negative, which means that the controller 
-from~\cite{DBLP:conf/hybrid/WangGRJF16} is unstable, considering FWL effects. 
-Note that the final solution from \tool is stable since it presents an infinite phase margin 
-and a gain margin of $17.8 dB$.
-%
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{figures/runningexample_bd0.pdf}
-        \caption{Original controller~\cite{DBLP:conf/hybrid/WangGRJF16}.}
-        \label{fig:original}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{figures/runningexample_bd2.pdf}
-        \caption{Controller synthesised by \tool.}
-        \label{fig:cegiscontroller}
-    \end{subfigure}
-    \caption{Bode diagram for original~\cite{DBLP:conf/hybrid/WangGRJF16} and synthesised closed-loop systems.}\label{fig:bode}
-\end{figure}
-
-Figure~\ref{fig:step} shows the step responses of the closed-loop system with the original controller~\cite{DBLP:conf/hybrid/WangGRJF16} (Figure~\ref{fig:step0}), the first candidate solution (Figure~\ref{fig:step1}), and the final solution from \tool (Fig.~\ref{fig:step2}).
-The step response in Figure~\ref{fig:step0} confirms that the stability loss if we consider FWL effects.
-However, Figure~\ref{fig:step2} shows that the first candidate controller is able to stabilize the closed-loop system without uncertainties, but it is rejected by \tool since this solution is not considered to be sound.
-Finally, Figure~\ref{fig:step2} shows a stable behavior for the final (sound) solution, which presents a lower settling time.
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/runningexample_step0.pdf}
-        \caption{Orignal controller.}
-        \label{fig:step0}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/runningexample_step1.pdf}
-        \caption{First candidate solution.}
-        \label{fig:step1}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/runningexample_step2.pdf}
-        \caption{Final solution by \tool.}
-        \label{fig:step2}
-    \end{subfigure}
-    \caption{Step responses for original~\cite{DBLP:conf/hybrid/WangGRJF16} closed-loop system with FWL effects and for each {\sc synthesise} step of \tool.}\label{fig:step}
-\end{figure*}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We report a faviourable assessment of \tool over a diverse set of real-world
+We report a favourable assessment of \tool over a diverse set of real-world
 benchmarks. Nevertheless, this set of benchmarks is limited within the

### 2016-10-14 paper/paper.tex

@@
 
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{figures/runningexample_bd0.pdf}
+        \caption{Original controller~\cite{DBLP:conf/hybrid/WangGRJF16}.}
+        \label{fig:original}
+    \end{subfigure}
+    ~
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{figures/runningexample_bd2.pdf}
+        \caption{Controller synthesised by \tool.}
+        \label{fig:cegiscontroller}
+    \end{subfigure}
+    \caption{Bode diagram for original~\cite{DBLP:conf/hybrid/WangGRJF16} and synthesised closed-loop systems.}\label{fig:bode}
+\end{figure}
+
+Figure~\ref{fig:step} shows the step responses of the closed-loop system 
+with the original controller~\cite{DBLP:conf/hybrid/WangGRJF16} (Figure~\ref{fig:step0}), 
+the first candidate solution (Figure~\ref{fig:step1}), and the final solution from \tool (Fig.~\ref{fig:step2}). 
+The step response in Figure~\ref{fig:step0} confirms the stability loss if we consider FWL effects. 
+However, Figure~\ref{fig:step2} shows that the first candidate controller is able to stabilize 
+the closed-loop system without uncertainties, but it is rejected by \tool since this solution 
+is not considered to be sound. Finally, Figure~\ref{fig:step2} shows a stable behavior 
+for the final (sound) solution, which presents a lower settling time.
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{figures/runningexample_step0.pdf}
+        \caption{Orignal controller.}
+        \label{fig:step0}
+    \end{subfigure}
+    ~
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{figures/runningexample_step1.pdf}
+        \caption{First candidate solution.}
+        \label{fig:step1}
+    \end{subfigure}
+    ~
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{figures/runningexample_step2.pdf}
+        \caption{Final solution by \tool.}
+        \label{fig:step2}
+    \end{subfigure}
+    \caption{Step responses for original~\cite{DBLP:conf/hybrid/WangGRJF16} closed-loop system with FWL effects and for each {\sc synthesise} step of \tool.}\label{fig:step}
+\end{figure*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-10-14 paper/paper.tex
more fixes

@@
 
-\red{[above you introduced a notation for poly ratios, which now you do not use?]}
 Thus, the perturbed controller model $\hat{C}(z)$ may be obtained from the
@@
 
-\red{[it's not a lemma, since it is not later used to prove a theorem. state it as a proposition (theorem would be a bit of an over-statement)]}
-
-\begin{mylemma}{\cite{Bessa16,fadali}}
-\label{lemma:eq_int_stab} 
+\begin{myprop}{\cite{Bessa16,fadali}}
+\label{prop:eq_int_stab} 
 %
 A feedback closed-loop control system as given in Figure~\ref{fig:sampledsystem},
-with a FWL implementation of the digital controller $\hat{C}(z) =
-\frac{\mathit{FWL}[N_{C}(z)]}{\mathit{FWL}[D_{C}(z)]}$ and uncertain
-discrete model of the plant $\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q
-\vec{G}$, namely \red{[utter confusion between transfer functions and coefficients - you're next taking the ratio between two vectors of coefficient, which magically now are also a function of the z variable!
-WTF!
-\ldots]} $\hat{G}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is
+with a FWL implementation of the digital controller $\hat{C}(z) =\mathit{FWL}_{M_C,N_C}[C(z)]$ and uncertain
+discrete model of the plant 
+$$\hat{G}(z) =\frac{\hat{G}_n(z)}{\hat{G}_d(z)}: \vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q
+\vec{G} \text{(from  \ref{eq:coefficients},\ref{eq:delta_coefficients})}$$ ,  
+$\hat{G}(z)$, is
 BIBO-stable if and only if:
@@
 \label{eq:internal_stab_lemma}
-S(z)=\mathit{FWL}[N_{C}(z)]\hat{N}_{G}(z)+\mathit{FWL}[D_{C}(z)]\hat{D}_{G}(z);
+S(z)=\mathit{FWL}_{M_C}[C_n(z)]\hat{G}_n(z)+\mathit{FWL}_{N_C}[C_d(z)]\hat{G}_d(z);
 \end{equation}
-\item the direct loop product $\frac{\mathit{FWL}[N_{C}(z)]}{\mathit{FWL}[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle.
+\item the direct loop product $\mathit{FWL}_{M_C,N_C}[C(z)]\cdot G(z)$ has no pole-zero cancellation on or outside the unit circle.
 \end{itemize}
-\end{mylemma}
-
-Lemma~\ref{lemma:eq_int_stab} \red{not a lemma} provides the necessary conditions for the digital controller to stabilize the closed loop system, 
+\end{myprop}
+
+Proposition~\ref{prop:eq_int_stab} provides the necessary conditions for the digital controller to stabilize the closed loop system, 
 considering plant parametric uncertainties (i.e., $\Delta_p \vec{G}$),
@@
 Notice that the model for plant uncertainty due to quantisation noise (i.e., $\Delta_q \vec{G}$) may be disregarded if the conditions on
-Lemma~\ref{lemma:eq_int_stab} \red{not a lemma} are satisfied and if the quantisation noise is
+Proposition~\ref{prop:eq_int_stab} are satisfied and if the quantisation noise is
 bounded.  The boundedness of the quantisation noise comes from Assumption~\ref{whitenoise}.

### 2016-10-14 paper/paper.tex
fix typos

--- 2016-10-14 paper/paper.tex
@@
 $\mathit{FWL}_n[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$,
-which applies the FWL effects to a polynomial, with an equivalent $\mathit{FWL}_{n,m}[\cdot]:\mathcal{P}^{n,m}\rightarrow \mathcal{P}^{n,m}\langle I,F \rangle$ that applies the same effect to a ratio of polynomials, where
+which applies the FWL effects to a polynomial, with an equivalent $\mathit{FWL}_{n,m}[\cdot]:\mathcal{P}^{n,m}\rightarrow \mathcal{P}^{n,m}\langle I,F \rangle$ that apllies the same effect to a ratio of polynomials, where
 $\mathcal{P}^{n}$ is the
@@
 the user and Steps~A to D are automatically performed by our tool for
-Digital Systems Synthesis, named \tool.
+Digital Systems Synthsis, named \tool.
 %
@@
 This intermediate ANSI-C code model contains a specification $\phi$ for the
-property of interest (i.e., robust stability) and is passed to the
+property of interst (i.e., robust stability) and is passed to the
 Counterexample-Guided Inductive Synthesis (CEGIS) module of
@@
 the problem instance, our algorithm tries to solve the problem first for a
-low $I_b$, $F_b$, iteratively increasing the precision if it is insufficient.
+low $I_b$, $F_b$, iteratively increasing the precision if it is insuficient.
 
@@
 {\sc uncertainty} and {\sc precision} in the {\sc verify} phase.
-In particular, Figure~\ref{fig:bode} shows the Bode diagram of the illustrative example from~\cite{DBLP:conf/hybrid/WangGRJF16} 
-(Fig.~\ref{fig:original}) and from our synthesiser (Fig.~\ref{fig:cegiscontroller}). 
-The phase margin is negative as shown in Figure~\ref{fig:original}, which means that the controller 
-from~\cite{DBLP:conf/hybrid/WangGRJF16} is unstable, considering FWL effects. 
-However, the final solution from \tool is stable since it presents an infinite phase margin 
-and a gain margin of $17.8 dB$.
 
@@
 
+In particular, Figure~\ref{fig:bode} shows the Bode diagram of the illustrative example 
+using the digital controller represented by Eq.~\eqref{Eq:running-example-controller} from~\cite{DBLP:conf/hybrid/WangGRJF16} 
+(Fig.~\ref{fig:original}) and the final candidate solution from our synthesiser (Fig.~\ref{fig:cegiscontroller}). 
+The phase margin is negative as shown in Figure~\ref{fig:original}, which means that the controller 
+represented by Eq.~\eqref{Eq:running-example-controller} is unstable, considering FWL effects. 
+However, the final solution from \tool is stable since it presents an infinite phase margin 
+and a gain margin of $17.8 dB$.
+
 \begin{figure}
@@
 Figure~\ref{fig:step} shows the step responses of the closed-loop system 
-with the original controller~\cite{DBLP:conf/hybrid/WangGRJF16} (Figure~\ref{fig:step0}), 
-the first candidate solution (Figure~\ref{fig:step1}), and the final solution from \tool (Fig.~\ref{fig:step2}). 
+with the original controller represented by Eq.~\eqref{Eq:running-example-controller} (Figure~\ref{fig:step0}), 
+the first (Figure~\ref{fig:step1}) and final (Fig.~\ref{fig:step2}) candidate solutions provided by \tool. 
 The step response in Figure~\ref{fig:step0} confirms the stability loss if we consider FWL effects. 
-However, Figure~\ref{fig:step2} shows that the first candidate controller is able to stabilize 
-the closed-loop system without uncertainties, but it is rejected by \tool since this solution 
-is not considered to be sound. Finally, Figure~\ref{fig:step2} shows a stable behavior 
-for the final (sound) solution, which presents a lower settling time.
+However, Figure~\ref{fig:step1} shows that the first candidate controller is able to stabilize 
+the closed-loop system without uncertainties, but it is rejected during the {\sc precision} phase by 
+\tool since this solution is not considered to be sound. Finally, Figure~\ref{fig:step2} 
+shows a stable behavior for the final (sound) solution, which presents a lower settling time.
 

### 2016-10-14 paper/paper.tex
fwl fixes

--- 2016-10-14 paper/paper.tex
@@
 &f_b : \mathbb{R} \rightarrow  \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = f_b(x) : \tilde x=x-(x\mod\tilde x)\\
-&FWL_b[P \in \mathcal{P}] = \tilde P \in \mathcal{P}^{n}\langle I_b,F_b \rangle : c_i \in \vec{P} \wedge \tilde c_i \in \tilde \vec{P}=f_b(c_i)  \nonumber
+&\mathit{FWL}_n^b[P \in \mathcal{P}] = \tilde P \in \mathcal{P}^{n}\langle I_b,F_b \rangle : c_i \in \vec{P} \wedge \tilde c_i \in \tilde \vec{P}=f_b(c_i)  \nonumber
 \end{align}
 %
-we calculate $\tilde G(z)=FWL_b(\hat{G}(z))$
+we calculate $\tilde G(z)=FWL_{M_G,N_G}^b(\hat{G}(z))$
 %

### 2016-10-14 paper/paper.tex
fix figure 5
reduce height of Fig 4
fix figures
changed I_b,F_b to p to represent the plant

@@
 controller's coefficients; similarly $\vec{b}$ and $\vec{a}$ encompass the
-plant's coefficients; and $N_{(\cdot)}$ and $M_{(\cdot)}$ denote the number
-of poles and zeros for the corresponding block.
+plant's coefficients; and $N_{(\cdot)}$ and $M_{(\cdot)}$ indicate the order of the polynomial of the corresponding block.
 
@@
 % Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
-% using Fixed-Point bit vectors with integer size $I_b$ and fractional
-% size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
+% using Fixed-Point bit vectors with integer size $I_p$ and fractional
+% size $F_p$, whose domain is $\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
 % %
@@
 % Two approaches have been taken to synthesise a stable controller based on this model.
-% The first uses interval arithmetic, representing the coefficients $[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\ {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$
+% The first uses interval arithmetic, representing the coefficients $[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\ {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_p})]$
 
@@
 the domain $\mathbb{R}\param{I}{F}$ for the controller's coefficients and
-the domain $\mathbb{R}\param{I_b}{F_b}$ for the plant's coefficients, 
-where $I$ and $F$, as well as $I_b$ and $F_b$, denote the integer and
-fractional size, respectively, and $\mathbb{R}\langle I_b,F_b \rangle
+the domain $\mathbb{R}\param{I_p}{F_p}$ for the plant's coefficients, 
+where $I$ and $F$, as well as $I_p$ and $F_p$, denote the integer and
+fractional size, respectively, and $\mathbb{R}\langle I_p,F_p \rangle
 \supseteq \mathbb{R}\langle I,F \rangle$.
@@
 %Regarding the plant, its coefficients are this is synthesised over the 
-%domain $\mathbb{R}^{n_G+m_G}\param{I_b}{F_b}$, where $n_G$ and $m_G$ 
+%domain $\mathbb{R}^{n_G+m_G}\param{I_p}{F_p}$, where $n_G$ and $m_G$ 
 %denote the order of the polynomials representing the 
 %numerator and denominator of the plant's transfer function, respectively. 
-%Again, $I_b$ and $F_b$ denote the integer and fractional size, respectively, with
-%$\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
+%Again, $I_p$ and $F_p$ denote the integer and fractional size, respectively, with
+%$\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
 
@@
 Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
-using fixed-point bit vectors.%  with integer size $I_b$ and fractional
-% size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
+using fixed-point bit vectors.%  with integer size $I_p$ and fractional
+% size $F_p$, whose domain is $\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
 %
@@
 \label{FWL_tf}
-&f_b : \mathbb{R} \rightarrow  \mathbb{R}\langle I_b,F_b \rangle \triangleq \tilde x = f_b(x) : \tilde x=x-(x\mod\tilde x)\\
-&\mathit{FWL}_n^b[P \in \mathcal{P}] = \tilde P \in \mathcal{P}^{n}\langle I_b,F_b \rangle : c_i \in \vec{P} \wedge \tilde c_i \in \tilde \vec{P}=f_b(c_i)  \nonumber
+&f^p : \mathbb{R} \rightarrow  \mathbb{R}\langle I_p,F_p \rangle \triangleq \tilde x = f^p(x) : \tilde x=x-(x\mod\tilde x)\\
+&\mathit{FWL}_n^p[P \in \mathcal{P}] = \tilde P \in \mathcal{P}^{n}\langle I_p,F_p \rangle : c_i \in \vec{P} \wedge \tilde c_i \in \tilde \vec{P}=f^p(c_i)  \nonumber
 \end{align}
 %
-we calculate $\tilde G(z)=FWL_{M_G,N_G}^b(\hat{G}(z))$
+we calculate $\tilde G(z)=FWL_{M_G,N_G}^p(\hat{G}(z))$
 %
@@
 the problem instance, our algorithm tries to solve the problem first for a
-low $I_b$, $F_b$, iteratively increasing the precision if it is insufficient.
+low $I_p$, $F_p$, iteratively increasing the precision if it is insufficient.
 
@@
 and those for $\tilde G(z)$ in the domain
-$\mathbb{R}\langle I_b,F_b \rangle$.
+$\mathbb{R}\langle I_p,F_p \rangle$.
 While the controller's precision $\param{I}{F}$ is given, 
-we can vary $\param{I_b}{F_b}$ such that 
-$\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
+we can vary $\param{I_p}{F_p}$ such that 
+$\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
 
@@
 $[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\
-{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_b})]$ 
+{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_p})]$ 
 and rounds operations outwards during calculations. This effectively allows
@@
 two-stage verification: the first stage performs potentially unsound
-fixed-point operations assuming a precision \param{I_b}{F_b}, and the
+fixed-point operations assuming a precision \param{I_p}{F_p}, and the
 second stage restores soundness by validating these operations
@@
 In more detail, in the first stage, denoted by {\sc Uncertainty} in Figure~\ref{fig:CEGIS}, 
-assuming a precision \param{I_b}{F_b} 
+assuming a precision \param{I_p}{F_p} 
 we check whether the system is unstable for the current candidate solution,
@@
 If the {\sc precision} verification returns $\mathit{false}$, then we
-increase the precision of \param{I_b}{F_b} and re-start the {\sc
+increase the precision of \param{I_p}{F_p} and re-start the {\sc
   synthesise} phase with an empty {\sc inputs} set.  Otherwise, we
@@
 example given in the previous section.  We start with the candidate solution
-with all coefficients zero, as given below, and a precision of $I_b=16$,
-$F_b=24$.  The digital controller is designed with standard techniques for
+with all coefficients zero, as given below, and a precision of $I_p=16$,
+$F_p=24$.  The digital controller is designed with standard techniques for
 control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}.
@@
 We obtain the result $\mathit{false}$, meaning that the current precision is
-insufficient.  Consequently, we increase our precision to $I_b=20$, $F_b=28$.
+insufficient.  Consequently, we increase our precision to $I_p=20$, $F_p=28$.
 %
@@
 {\sc uncertainty} and {\sc precision} in the {\sc verify} phase.
+In particular, Figure~\ref{fig:bode} shows the Bode diagram of the illustrative example 
+using the digital controller represented by Eq.~\eqref{Eq:running-example-controller} from~\cite{DBLP:conf/hybrid/WangGRJF16} 
+(Fig.~\ref{fig:original}) and the final candidate solution from our synthesiser (Fig.~\ref{fig:cegiscontroller}). 
+The phase margin is negative as shown in Figure~\ref{fig:original}, which means that the controller 
+represented by Eq.~\eqref{Eq:running-example-controller} is unstable, considering FWL effects. 
+However, the final solution from \tool is stable since it presents an infinite phase margin 
+and a gain margin of $17.8 dB$.
 
@@
 },
-          row sep=1cm, column sep=1.5cm] {
+          row sep=.6cm, column sep=1.5cm] {
    \coordinate (aux1);
@@
 \end{figure*}
-
-In particular, Figure~\ref{fig:bode} shows the Bode diagram of the illustrative example 
-using the digital controller represented by Eq.~\eqref{Eq:running-example-controller} from~\cite{DBLP:conf/hybrid/WangGRJF16} 
-(Fig.~\ref{fig:original}) and the final candidate solution from our synthesiser (Fig.~\ref{fig:cegiscontroller}). 
-The phase margin is negative as shown in Figure~\ref{fig:original}, which means that the controller 
-represented by Eq.~\eqref{Eq:running-example-controller} is unstable, considering FWL effects. 
-However, the final solution from \tool is stable since it presents an infinite phase margin 
-and a gain margin of $17.8 dB$.
-
-\begin{figure}
+%
+\begin{figure}[H]
     \centering
-    \begin{subfigure}[b]{0.45\textwidth}
+    \begin{subfigure}[b]{0.4\textwidth}
         \includegraphics[width=\textwidth]{figures/runningexample_bd0.pdf}
@@
     ~
-    \begin{subfigure}[b]{0.45\textwidth}
+    \begin{subfigure}[b]{0.4\textwidth}
         \includegraphics[width=\textwidth]{figures/runningexample_bd2.pdf}
@@
 \end{figure}
-
+%
 Figure~\ref{fig:step} shows the step responses of the closed-loop system 
@@
 shows a stable behavior for the final (sound) solution, which presents a lower settling time.
-
+%
 \begin{figure*}

### 2016-10-14 paper/paper.tex
resize figure 2
Reduced edge length in CEGIS graph.
make space
update figures
minor changes
replace 'ise' by 'ize'

@@
 
+\renewcommand{\baselinestretch}{0.975}
 \include{macros}
@@
 correct by construction.  The synthesis result is sound with respect to the
-complete range of approximations, including time discretisation,
-quantisation effects, and finite-precision arithmetic and their related
+complete range of approximations, including time discretization,
+quantization effects, and finite-precision arithmetic and their related
 rounding errors.
@@
 
-\keywords{Control synthesis, CEGIS, finite word length, time sampling, quantisation, interval analysis}
+\keywords{Control synthesis, CEGIS, finite word length, time sampling, quantization, interval analysis}
 
@@
 artefacts specific to digital control, such as the effects of
-finite-precision arithmetic, time discretisation, and quantisation noise
+finite-precision arithmetic, time discretization, and quantization noise
 introduced by A/D and D/A conversion.  Thus, the programming is a key
@@
 candidate programs.  The candidate programs are iteratively refined to match
-the specification more closely.  Program synthesisers that implement
+the specification more closely.  Program synthesizers that implement
 Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} are now
@@
 requires considerably less expertise than methodologies driven by
-verification.  Specifically, we synthesise controllers for hybrid
+verification.  Specifically, we synthesize controllers for hybrid
 closed-loop systems, i.e., software-implemented embedded controllers along
@@
 problem.  We perform digital control synthesis over a hybrid model, where
-the plant exhibits continuous behaviour whereas the controller operates in 
-discrete time and over a quantised domain.  
+the plant exhibits continuous behavior whereas the controller operates in 
+discrete time and over a quantized domain.  
 Inspired by a classical approach \cite{astrom1997computer}, 
 we translate the problem into a single digital domain.  
-Given our primary interest in stability despite digitisation effects, we have modelled
+Given our primary interest in stability despite digitization effects, we have modelled
 a digital equivalent of the plant by evaluating the effects of the
-quantisers (A/D and D/A converters) as time discretisation elements with
-quantisation noise.  The resulting closed-loop system is a program loop that
+quantizers (A/D and D/A converters) as time discretization elements with
+quantization noise.  The resulting closed-loop system is a program loop that
 operates on bit-vectors encoded using fixed-point arithmetic with finite-word
 length (FWL). The deterministic effects of the FWL and
-quantisation errors are incorporated into the model as an additive
+quantization errors are incorporated into the model as an additive
 uncertainty, which is taken into account during the CEGIS-based synthesis of
@@
   program synthesis is non-trivial and requires addressing challenges
-  specific to embedded control systems, such as the effects of quantisers and
+  specific to embedded control systems, such as the effects of quantizers and
   FWL. In particular, we have found that a two-stage verification engine
@@
 \item We provide experimental results showing that our tool is able to
-synthesise stable controllers for a set of intricate benchmarks taken from
+synthesize stable controllers for a set of intricate benchmarks taken from
 the literature efficiently: the median runtime for our benchmark set is
-$197$s, i.e., half of the controllers can be synthesised in less than five
+$197$s, i.e., half of the controllers can be synthesized in less than five
 minutes.
@@
 
-We cover preliminaries on plant discretisation, the verification of
+We cover preliminaries on plant discretization, the verification of
 closed-loop control systems, and stability in
@@
 %$$ 
-%where $\Delta G_Q(z)$ is an error term accounting for the quantisation effects 
+%where $\Delta G_Q(z)$ is an error term accounting for the quantization effects 
 %\item 
@@
 %Now, it's over the transfer function $\tilde G(z)$ that we want to synthesise the parameters of a template $C(z)$. 
-%This controller's transfer function will be subject to the same quantisation and precision limits as the plant's: 
+%This controller's transfer function will be subject to the same quantization and precision limits as the plant's: 
 %we need to argue that the way we do synthesis affects manipulation of quantities that relate to specific errors and be explicit about these. 
@@
 
-The digital controllers synthesised using the algorithm we present in this
+The digital controllers synthesized using the algorithm we present in this
 paper are typically used in closed loops with continuous (physical)
@@
 parts of the system (i.e., the plant) and the discrete parts (i.e., the
-digital controller).  To obtain a joint model, we fully discretise the continuous
+digital controller).  To obtain a joint model, we fully discretize the continuous
 plant. We briefly recall the standard foundations of this step.
@@
 %plant, i.e., 
-The continuous model of the plant must be discretised to obtain the corresponding 
+The continuous model of the plant must be discretized to obtain the corresponding 
 %discrete equivalent 
 coefficients of $G(z)$.
-%via ZOH discretisation.
+%via ZOH discretization.
 
@@
 
-Amongst the several discretisation methods available in the
-literature~\cite{Franklin15}, the zero-order hold (ZOH) discretisation is
+Amongst the several discretization methods available in the
+literature~\cite{Franklin15}, the zero-order hold (ZOH) discretization is
 considered to be suitable for representing the sample and hold processes that are
 typically employed in complex systems~\cite{istepanian2012digital}. 
-The ZOH discretisation models the exact effect of sampling and DAC interpolation over the plant.
+The ZOH discretization models the exact effect of sampling and DAC interpolation over the plant.
 
@@
 %
-The sample and hold effects of the ADC and the ZOH of the DAC are synchronised,
+The sample and hold effects of the ADC and the ZOH of the DAC are synchronized,
 i.e., there is no delay between sampling the plant output at ADC and
@@
 %
-Given a synchronised ZOH input and sample and hold output on the plant with
+Given a synchronized ZOH input and sample and hold output on the plant with
 a sample time $T$ satisfying Nyquist criterion, the discrete pulse
@@
 (\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$ which come from tolerances/imprecisions in the original model), errors in the numeric
-calculations, or roundoffs in the quantisation.  These uncertainties are 
+calculations, or roundoffs in the quantization.  These uncertainties are 
 parametrically expressed by additive terms, resulting in a uncertain model
@@
 or work over their respective coefficients $\vec{G}, \vec{C}$ in vector form.
-
-%\begin{equation}
-%\Delta{\vec{p}}=\begin{bmatrix}
-%\hat{b_{0}} - b_{0}\\
-%\hat{b_{1}} - b_{1}\\
-%\vdots \\
-%\hat{b}_{M_G} - b_{M_{G}}\\
-%\hat{a_{0}} - a_{0}\\
-%\hat{a_{1}} - a_{1}\\
-%\vdots\\
-%\hat{a}_{N_G} - a_{N_{G}}\\
-%\end{bmatrix}=\begin{bmatrix}
-%\vec{\hat{b}}\\
-%\vec{\hat{a}}
-%\end{bmatrix}-\begin{bmatrix}
-%\vec{b}\\
-%\vec{a}
-%\end{bmatrix}
-%\label{eq:uncertainty}
-%\end{equation}
-
-A typical digital control system system with a continuous plant and a discrete
-controller is illustrated in Figure~\ref{fig:sampledsystem}.  The DAC and
-ADC converters introduce quantisation errors which are modeled as noises $\nu_{1}(z)$ and $\nu_{2}(z)$,
-$G(s)$ is the continuous-time plant model with parametric additive
-uncertainty $\Delta_p{G}_n(s)$ and $\Delta_p{G}_d(s)$, $R(z)$ is the reference signal, $U(z)$ is
-the control signal, and $\hat{Y}(z)$ is the output signal affected by the
-noises and uncertainties in the closed-loop system.
 
@@
 
+%\begin{equation}
+%\Delta{\vec{p}}=\begin{bmatrix}
+%\hat{b_{0}} - b_{0}\\
+%\hat{b_{1}} - b_{1}\\
+%\vdots \\
+%\hat{b}_{M_G} - b_{M_{G}}\\
+%\hat{a_{0}} - a_{0}\\
+%\hat{a_{1}} - a_{1}\\
+%\vdots\\
+%\hat{a}_{N_G} - a_{N_{G}}\\
+%\end{bmatrix}=\begin{bmatrix}
+%\vec{\hat{b}}\\
+%\vec{\hat{a}}
+%\end{bmatrix}-\begin{bmatrix}
+%\vec{b}\\
+%\vec{a}
+%\end{bmatrix}
+%\label{eq:uncertainty}
+%\end{equation}
+
+A typical digital control system system with a continuous plant and a discrete
+controller is illustrated in Figure~\ref{fig:sampledsystem}.  The DAC and
+ADC converters introduce quantization errors which are modeled as noises $\nu_{1}(z)$ and $\nu_{2}(z)$,
+$G(s)$ is the continuous-time plant model with parametric additive
+uncertainty $\Delta_p{G}_n(s)$ and $\Delta_p{G}_d(s)$, $R(z)$ is the reference signal, $U(z)$ is
+the control signal, and $\hat{Y}(z)$ is the output signal affected by the
+noises and uncertainties in the closed-loop system.
+%
+%
+%
 The ADC and DAC may be abstracted by transforming the closed-loop system in
@@
 %$\hat{Y}(z)=Y(z)+\nu(z)$.  The measurement noise $\nu(k)$ is enough for
-%represent both quantisation noises ($\nu_{1}$ and $\nu_{2}$) what can be
+%represent both quantization noises ($\nu_{1}$ and $\nu_{2}$) what can be
 %obtained reorganizing the equations~\ref{eq:outputfunctions}:
@@
 %%
-%where $H_{1}R(z)$ is exactly equal to $Y(z)$ without quantisation noise effects, thus:
+%where $H_{1}R(z)$ is exactly equal to $Y(z)$ without quantization noise effects, thus:
 %%
@@
 
-%Considering the quantisation noise $\nu(k)$ as an output error in discrete plant model, we may represent it as an additive noise in the plant output $y(k)$ resulting in the noisy output $\hat{y}(k)$:
-%\begin{equation}
-%
-%\end{equation}
-
-\begin{figure*}[ht]
+%Considering the quantization noise $\nu(k)$ as an output error in discrete plant model, we may represent it as an additive noise in the plant output $y(k)$ resulting in the noisy output $\hat{y}(k)$:
+%\begin{equation}
+%
+%\end{equation}
+
+\begin{figure}[ht]
 \centering
-
 \tikzset{add/.style n args={4}{
@@
 
-\resizebox{.6\textwidth}{!}{
+\resizebox{.48\textwidth}{!}{
  \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
@@
 \label{fig:digsystem1}}
-\end{figure*}
+\end{figure}
 
@@
 illustrated: parametric uncertainties related to modelling errors, and
-uncertainties introduced by quantisations in sampling and holding process,
+uncertainties introduced by quantizations in sampling and holding process,
 i.e., ADC and DAC conversions.  Assuming linearity and independence between
@@
 uncertainties and $\Delta_q \vec{G}$ is the term that reflects the
-quantisation effects on the plant model.
+quantization effects on the plant model.
 
@@
 %
-In the case of a synthesised controller, because the synthesis is performed
+In the case of a synthesized controller, because the synthesis is performed
 using FWL, $\hat{C}(z) \equiv C(z)$.
@@
 Correct synthesis of the digital controller requires consideration of the
-effect of FWL in controller and quantisation noises in the closed loop
-system.  Let the quantiser $Q1$ be the source of a white noise $\nu_{1}$ and
+effect of FWL in controller and quantization noises in the closed loop
+system.  Let the quantizer $Q1$ be the source of a white noise $\nu_{1}$ and
 $Q2$ be the source of a white noise $\nu_{2}$.  The following equation
@@
 %
-The quantisation noises $\nu_{1}$ (from $Q1$) and $\nu_{2}$ (from $Q2$) are
+The quantization noises $\nu_{1}$ (from $Q1$) and $\nu_{2}$ (from $Q2$) are
 uncorrelated white noises and their amplitudes are always bounded by the
-half of quantisation step~\cite{astrom1997computer}, i.e., $\vert \nu_{1}
+half of quantization step~\cite{astrom1997computer}, i.e., $\vert \nu_{1}
 \vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$,
-where $q_{1}$ and $q_{2}$, respectively, are the quantisation steps of ADC
+where $q_{1}$ and $q_{2}$, respectively, are the quantization steps of ADC
 and DAC.
@@
 %%
-%In particular, Widrow \cite{widrow1956} models the quantisation noise as a
+%In particular, Widrow \cite{widrow1956} models the quantization noise as a
 %gaussian model in which the second moment (variance) of the probability
-%density function (PDF) of the quantisation noise is given by
+%density function (PDF) of the quantization noise is given by
 %%
@@
 %%
-%The power spectral density of the quantisation noise (supposed white)
+%The power spectral density of the quantization noise (supposed white)
 %$S_{\nu}(z)$ is bounded and may be computed through the z-transform of
@@
 %
-%Finally, the quantisation noise spectrum may be considered a energy-bounded
+%Finally, the quantization noise spectrum may be considered a energy-bounded
 %(Lemma~\ref{lemma:boundednoise}), and consequently the Parseval's theorem
-%ensures that the quantisation noise is also energy-bounded in time-domain. 
+%ensures that the quantization noise is also energy-bounded in time-domain. 
 %Thus $\hat{Y}(z)$ will be bounded and the closed-loop system stable if the
@@
 considering plant parametric uncertainties (i.e., $\Delta_p \vec{G}$),
-quantisation noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in the control
+quantization noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in the control
 software.  
-Notice that the model for plant uncertainty due to quantisation noise (i.e., $\Delta_q \vec{G}$) may be disregarded if the conditions on
-Proposition~\ref{prop:eq_int_stab} are satisfied and if the quantisation noise is
-bounded.  The boundedness of the quantisation noise comes from Assumption~\ref{whitenoise}.
+Notice that the model for plant uncertainty due to quantization noise (i.e., $\Delta_q \vec{G}$) may be disregarded if the conditions on
+Proposition~\ref{prop:eq_int_stab} are satisfied and if the quantization noise is
+bounded.  The boundedness of the quantization noise comes from Assumption~\ref{whitenoise}.
 
@@
 
-In order to synthesise closed-loop digital control systems, we use a program
-synthesis engine.  Our program synthesiser implements Counter-Example Guided
+In order to synthesize closed-loop digital control systems, we use a program
+synthesis engine.  Our program synthesizer implements Counter-Example Guided
 Inductive Synthesis (CEGIS)~\cite{sketch}.  We start by presenting its
@@
 
-Given a model for a plant for which to synthesise a controller, provided in
+Given a model for a plant for which to synthesize a controller, provided in
 an ANSI-C input file (Steps 1--3), \tool constructs a non-deterministic
@@
 (Step~B) using implementation details provided in Steps~$2$ and $3$ to
-calculate the parameters of the controller to be synthesised (Step~C). 
+calculate the parameters of the controller to be synthesized (Step~C). 
 Finally, \tool builds an intermediate ANSI-C code for the digital system
@@
 CBMC~\cite{ClarkeKL04}, where the controller is marked as the input variable
-to synthesise.  The properties specified in the ANSI-C code model can only
-be satisfied if CEGIS synthesises controller coefficients that
+to synthesize.  The properties specified in the ANSI-C code model can only
+be satisfied if CEGIS synthesizes controller coefficients that
 satisfy~$\phi$.  CEGIS employs an iterative, counterexample-guided
 refinement process which is explained in detail in
-section~\ref{synthesiser-general}.  A~successful synthesis result is
+section~\ref{synthesizer-general}.  A~successful synthesis result is
 reported if CEGIS generates a controller that is safe with respect to~$\phi$. 
-In particular, the ANSI-C code model guarantees that a synthesised solution
+In particular, the ANSI-C code model guarantees that a synthesized solution
 is complete and sound with respect to the stability property~$\phi$, since it
@@
 
-%In this section, we show how to embed discretisation errors on the plant model, as follows: 
+%In this section, we show how to embed discretization errors on the plant model, as follows: 
 %%$\hat{G}(z)$ is split into two terms:
@@
 %\end{equation}
-%where $G(z,T)$ is the time discretisation of the nominal physical plant $G(s)$, 
-%$\Delta{G_{Q}(z)}$ represents the quantisation uncertainty model, 
+%where $G(z,T)$ is the time discretization of the nominal physical plant $G(s)$, 
+%$\Delta{G_{Q}(z)}$ represents the quantization uncertainty model, 
 %and $\Delta{G_{P}(z)}$ describes the parametric uncertainty model.
@@
 
-%\section{An Uncertainty Model for the quantisation Error} 
-%\label{sec:uncertainty-model-quantisation-error}
+%\section{An Uncertainty Model for the quantization Error} 
+%\label{sec:uncertainty-model-quantization-error}
 %
 %%Here, an uncertainty model to accommodate the
-%%quantisation noise effects on $\hat{G}(z)$ is proposed.  
+%%quantization noise effects on $\hat{G}(z)$ is proposed.  
 %%As a result, Eq.~\eqref{eq:uncertainplant} is rewritten as
@@
 %
-%A model for $\Delta{G_{Q}(z)}$ that can represent the quantisation
+%A model for $\Delta{G_{Q}(z)}$ that can represent the quantization
 %noise effect in the plant output, and consequently the closed-loop system
@@
 %quantised ($Q2$) and interpolated via a ZOH using digital-to-analog
-%converter (DAC).  The quantisation occurs because the DAC resolution may be
+%converter (DAC).  The quantization occurs because the DAC resolution may be
 %different from the fixed point representation of the controller.  $G(s)$ is
@@
 %synchronized with the DAC.  Each quantiser ($Q1$ and $Q2$) will present some
-%contribution for the total quantisation noise.
+%contribution for the total quantization noise.
 %    
@@
 %\begin{myprop}
-%Considering the quantisation noise $\nu(k)$ as an output error in the
+%Considering the quantization noise $\nu(k)$ as an output error in the
 %discrete plant model, 
@@
 %\begin{equation}
-%\label{eq:quantisation_tf}
+%\label{eq:quantization_tf}
 %\Delta{G_{Q}(z)}=\frac{\nu(z)}{U(z)},
@@
 %\end{equation}
-%where $\sigma_{Q}^{2}$ is the variance of the quantisation noise and
+%where $\sigma_{Q}^{2}$ is the variance of the quantization noise and
 %$U(z)$ is the z-transform of control signal ({\it i.e.}, the z-transform of
@@
 %be represented by the following pulse transfer function (without
-%quantisation noise effect):
+%quantization noise effect):
 %%
@@
 %
-%Considering the quantisation noise $\nu(k)$ as an output error in the
+%Considering the quantization noise $\nu(k)$ as an output error in the
 %discrete plant model, an additive noise in the plant output $y(k)$ resulting
@@
 
-%Eq.~\eqref{eq:deltag_var} indicates that the modelling of the quantisation noise
+%Eq.~\eqref{eq:deltag_var} indicates that the modelling of the quantization noise
 %effect on the plant transfer function demands an estimation of the variance
-%of quantisation noise $\sigma_{Q}^{2}$.  To obtain such estimation, the
-%methodology presented by~\cite{widrow2008quantisation}
+%of quantization noise $\sigma_{Q}^{2}$.  To obtain such estimation, the
+%methodology presented by~\cite{widrow2008quantization}
 %is used.  The authors provide an algorithm for computing the mean square of
@@
 %\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factors, {\it i.e.} constant gains usually employed before the ADC and after the DAC in order to avoid the overload of converters  %\red{[define scale factors]}
-%for the quantisation $Q1$ and $Q2$, respectively; $q_{1}$ and $q_{2}$ are the quantisation step for $Q1$ and $Q2$, respectively, and $\sum {h_{Q1}^{2}}$ and $\sum
+%for the quantization $Q1$ and $Q2$, respectively; $q_{1}$ and $q_{2}$ are the quantization step for $Q1$ and $Q2$, respectively, and $\sum {h_{Q1}^{2}}$ and $\sum
 %{h_{Q2}^{2}}$ are the squares sums of the impulse response obtained by means
@@
 %Eq.~\eqref{eq:deltag_var}, {\it i.e.}, the z-transform of control action
-%$U(z)$.  This indicates that the quantisation noise effect on a discrete
+%$U(z)$.  This indicates that the quantization noise effect on a discrete
 %plant model mainly depends on three main factors:
@@
 %%
-%\item \textbf{ADC and DAC step:} \red{[again, do we need both?]} these are the main component of quantisation noise power, but an $8$-bits converter already reduces the effect of quantisation noises in the output for negligible values.
-%%
-%\item \textbf{Signal-to-noise ratio (SNR): } the dependence on the value of $U(z)$ \red{[notice that now we have reduced the problem to depend on the effect of the reference signal transform R(z) - pls revise.]} shows the importance of the SNR for handling quantisation noise; for a high SNR of the digital controller, the quantisation effect is negligible.
+%\item \textbf{ADC and DAC step:} \red{[again, do we need both?]} these are the main component of quantization noise power, but an $8$-bits converter already reduces the effect of quantization noises in the output for negligible values.
+%%
+%\item \textbf{Signal-to-noise ratio (SNR): } the dependence on the value of $U(z)$ \red{[notice that now we have reduced the problem to depend on the effect of the reference signal transform R(z) - pls revise.]} shows the importance of the SNR for handling quantization noise; for a high SNR of the digital controller, the quantization effect is negligible.
 This happens during the transient of the system, when high control actions are employed.
@@
 %Finally, Eq.~\eqref{eq:deltaG_final} is a suitable frequency domain model
-%for quantisation noise effects on closed-loop systems.  This model depends
+%for quantization noise effects on closed-loop systems.  This model depends
 %on the plant pulse transfer function ($G(z)$), which is described by
@@
 
-\subsection{Architecture of the program synthesiser}
-\label{synthesiser-general}
+\subsection{Architecture of the program synthesizer}
+\label{synthesizer-general}
 %
@@
 % 
-The input specification provided to the program synthesiser is of the form
+The input specification provided to the program synthesizer is of the form
 $\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
@@
 
-The design of our synthesiser is given in Figure~\ref{fig:CEGIS} and consists
-of two phases, {\sc Synthesise} and {\sc Verify}, which interact via a
+The design of our synthesizer is given in Figure~\ref{fig:CEGIS} and consists
+of two phases, {\sc Synthesize} and {\sc Verify}, which interact via a
 finite set of test vectors {\sc inputs} that is updated incrementally. 
@@
 %
-If {\sc synthesise} succeeds in finding an witness $\vec{P}$, this witness
+If {\sc synthesize} succeeds in finding an witness $\vec{P}$, this witness
 is a candidate solution to the full synthesis formula.  We pass this
@@
 If this is the case, then the algorithm terminates.  Otherwise, additional
-information is provided to the {\sc synthesise} phase in the form of a new
+information is provided to the {\sc synthesize} phase in the form of a new
 counterexample that is added to the {\sc inputs} set and the loop iterates
@@
 Next, we describe the specific property that we pass to the program
-synthesiser as the specification $\sigma$.  There are two different
+synthesizer as the specification $\sigma$.  There are two different
 algorithms in DSVerifier that can be used for stability
@@
 in~\eqref{eq:internal_stab_lemma}.
-
+%
 % of the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$, where $Y(z)$ is the closed-loop system output and U(z) is the controller output. 
@@
 characteristic polynomial of a stable system if and only if the following four conditions hold:
-\begin{itemize}
-\item $R_1: S(1) > 0$;
-\item $R_2: (−1)^N S(−1) > 0$;
-\item $R_3: |a_0| < a_N$;
-\item $R_4: m_{11} > 0 \wedge m_{31}>0 \wedge m_{51}>0 \wedge \cdots \wedge m_{(2N{-}3)(1)}>0$.
-\end{itemize}
+%\begin{itemize}
+%\item 
+$R_1: S(1) > 0$;
+%\item 
+$R_2: (−1)^N S(−1) > 0$;
+%\item 
+$R_3: |a_0| < a_N$;
+%\item 
+$R_4: m_{11} > 0 \wedge m_{31}>0 \wedge m_{51}>0 \wedge \cdots \wedge m_{(2N{-}3)(1)}>0$.
+%\end{itemize}
 
@@
 constraint of the form:
-$$
+$
 \phi_\mathit{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
-$$
+$
 %\cdsay{figure out what is existentially quantified for the final $\sigma$.} 
@@
 Given the use of fixed-point arithmetic, 
-we need to examine the effect of discretisation during these operations.
+we need to examine the effect of discretization during these operations.
 Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
@@
 When mapping back to the notation used for describing the general architecture 
-of the program synthesiser, the controller $C(z)$ denotes $P$ and 
+of the program synthesizer, the controller $C(z)$ denotes $P$ and 
 $\tilde G(z)$ represents $x$.
@@
 
-\paragraph{The {\sc Synthesise} and {\sc Verify} phases}
-The {\sc synthesise} phase uses BMC to 
+\paragraph{The {\sc Synthesize} and {\sc Verify} phases}
+The {\sc synthesize} phase uses BMC to 
 compute a solution $C(z)$. % An important remark is that this 
@@
 plus the effects of numeric calculations in the engine.
-Synthesised controllers using this verifier will always
+Synthesized controllers using this verifier will always
 be stable for all plants in the family.
@@
 second stage restores soundness by validating these operations
-using interval arithmetic on the synthesised controller.
-
-In more detail, in the first stage, denoted by {\sc Uncertainty} in Figure~\ref{fig:CEGIS}, 
-assuming a precision \param{I_p}{F_p} 
-we check whether the system is unstable for the current candidate solution,
-{\it i.e.}, if $\neg \phi_\mathit{stability}$ is satisfiable for $S(z)$.
-If this is the case, then we obtain a counterexample 
-$\tilde G(z)$, 
-%denoted by values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
-%\red{[see my comment above - these quantities pop up too abruptly.]},
-which makes the closed-loop system unstable. 
-This uncertainty is added to 
-the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
-we obtain a candidate solution consisting 
-of a controller $C(z)$, which makes the closed-loop 
-system stable for all the uncertainties accumulated in {\sc inputs}.
-
-If the {\sc Uncertainty} verification stage concludes that
-the system is stable for the current candidate solution,
-then we pass this solution to the second verification stage, {\sc Precision}, 
-which checks the propagation of the error in the fixed-point 
-calculations using a Fixed-point Arithmetic Verifier based on 
-interval arithmetic. 
-%
-% To achieve this, we use a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is assumed to be within the expected bounds and verified after synthesis using the interval version of the program.
-%
-% The first verification phase produces a counterexample if some instance of $\mathfrak{G}(z)$ does not verify the properties and the CEGIS loop iteratively looks for a new controller that verifies the supplied counterexamples.
-The second phase verifies the propagation of the error in the fixed point calculations.
-% If the second phase fails verification, we increase the precision of the analyser and feed the CEGIS loop again to find a sound solution. 
-% vouches for the use of CEGIS in most of our benchmarks.
-% \cdsay{end of integration}
-
-If the {\sc precision} verification returns $\mathit{false}$, then we
-increase the precision of \param{I_p}{F_p} and re-start the {\sc
-  synthesise} phase with an empty {\sc inputs} set.  Otherwise, we
-found a full sound solution for our synthesis problem and we are done.
-
-In the rest of the paper, we will refer to the two approaches 
-for the {\sc verify} phase as one-stage and two-stage, respectively.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Illustrative Example} \label{sec:running-ex}
-
-We will illustrate our approach with a classical cruise control example,
-extracted from the literature~\cite{Astrom08}.  The example will allow us to
-highlight the challenges that arise when using finite precision arithmetic
-in digital control.  We are given a discrete plant model (with a time step
-of $0.2$s), which is represented by the following $z$-expression:
-%
-\begin{equation}
-\label{Eq:running-example-plant}
-G\left(z\right) := \frac{0.0264}{z-0.9998}.
-\end{equation}
-
-Using an optimisation tool, the authors
-of~\cite{DBLP:conf/hybrid/WangGRJF16} have designed a high-performance
-controller for this plant, which is characterised by the following
-$z$-domain transfer function:
-%
-\begin{equation}
-\label{Eq:running-example-controller}
-C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
-\end{equation}
-%
-The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that this controller
-$C(z)$ (Eq.~\eqref{Eq:running-example-controller}) stabilizes the
-closed-loop system for the discrete plant model $G(z)$
-(Eq.~\ref{Eq:running-example-plant}).  However, if the effects of finite
-precision arithmetic are considered during verification (e.g., fixed-point
-arithmetic and word-length), then this closed-loop system becomes unstable.
-%
-For instance, an implementation of $C(z)$ using \param{4}{16} fixed-point
-numbers (i.e., $4$ bits for the integer part and $16$ bits for the
-fractional part) can be modeled as follows:
-%
-\begin{equation}
-\label{Eq:running-example-controller-quantised}
-C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
-{+}1.895996}{z^2{-}1.843994z+0.849594} \;.
-\end{equation} 
-%
-The resulting system using the typical series loop configuration, where
-$C_{q}\left(z\right)$ and $G\left(z\right)$ are in the forward path, is
-unstable.
-
-\subsection{Program synthesis for the example}
-
-We now demonstrate how our approach solves the synthesis problem for the
-example given in the previous section.  We start with the candidate solution
-with all coefficients zero, as given below, and a precision of $I_p=16$,
-$F_p=24$.  The digital controller is designed with standard techniques for
-control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}.
-%
-%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
-%
-%$$
-%\begin{array}{ll}
-%N_C(z) {=} 0z^2{+}0z{+}0\\
-%D_C(z) {=} 0z^2{+}0z{+}0\\
-%\end{array}
-%$$
-$$ C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0} $$
-
-In the first {\sc verify} stage, the {\sc uncertainty} 
-check finds the following counterexample:
-%
-$$ \tilde G(z) = \frac{0.026506}{1.000610z+1.002838} $$
-
-%$$
-%\begin{array}{ll}
-%\Delta N_G(z) = 0.026506\\
-%\Delta D_G(z) = 1.000610z+1.002838
-%\end{array}
-%$$
-
-We add this counterexample to {\sc inputs} and initiate the {\sc synthesise}
-phase, where we obtain the following candidate solution:
-%
-%\red{[ How is the order of the candidate solution chosen here?]}
-$$
-C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}
-$$
-
-This time, the {\sc uncertainty} check does not find any
-counterexample and we pass the current candidate solution to the {\sc
-precision} verification stage.
-%
-% In the second {\sc verify} phase, we check whether the current candidate
-% solution above is the final solution. It is not and the verifier signals
-% that it is due to lack of precision.
-%
-We obtain the result $\mathit{false}$, meaning that the current precision is
-insufficient.  Consequently, we increase our precision to $I_p=20$, $F_p=28$.
-%
-Since the previous counterexamples were obtained at lower precision, we
-remove them from the set of counterexamples.  Back in the {\sc synthesise}
-phase, we re-start the process with a candidate solution with all
-coefficients $0$.  Next, the {\sc uncertainty} verification stage provides
-the first counterexample at higher precision:
-%
-%$$
-%\begin{array}{ll}
-%\Delta N_G(z) {=} 0.026314\\
-%\Delta D_G(z) {=} 0.999024z{-}1.004785
-%\end{array}
-%$$
-$$ \tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785} $$
-
-In the next {\sc synthesise} phase, we get a new candidate solution that
-eliminates the new, higher precision counterexample:
-%
-$$ C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357} $$
-%
-%$$
-%\begin{array}{ll}
-%N_C(z) {=} \\
-%D_C(z) {=} \\
-%\end{array}
-%$$
-
-This candidate solution is validated as the final solution by both stages
-{\sc uncertainty} and {\sc precision} in the {\sc verify} phase.
-In particular, Figure~\ref{fig:bode} shows the Bode diagram of the illustrative example 
-using the digital controller represented by Eq.~\eqref{Eq:running-example-controller} from~\cite{DBLP:conf/hybrid/WangGRJF16} 
-(Fig.~\ref{fig:original}) and the final candidate solution from our synthesiser (Fig.~\ref{fig:cegiscontroller}). 
-The phase margin is negative as shown in Figure~\ref{fig:original}, which means that the controller 
-represented by Eq.~\eqref{Eq:running-example-controller} is unstable, considering FWL effects. 
-However, the final solution from \tool is stable since it presents an infinite phase margin 
-and a gain margin of $17.8 dB$.
-
-%, which fails to find a new counterexample (i.e. returns UNSAT).
-
-% \blue{
-% For the same cruise control system, the synthesis may be done considering that the plant model have parametric uncertainties ($\Delta G_{P}(z)$).
-Thus, the synthesised controller must to stabilize for any parametric variation $\Delta p$ inside of a given region.
-Specially, in this example, was assumed that each coefficient of $G(z)$ may vary $\pm 0.5\%$.
-% }
-
-% \blue{Initially, the controller denominator and numerator  ($D_{C}(z)$ and $N_{C}(z)$) are started with zero coefficients, as in previous example.
-Thus,  in the first {\sc verify} phase a counterexample is presented, that is added to {\sc inputs}, whis is usede in the first  {\sc synthesise} phase.
-The resulting controller is:
-% }
-% $$
-% {
-% \blue{
-% C(z)=\frac{0.77516z^2{+}-0.71497z{+}0.03729}{0.25024z^2{-}0.01799z{+}0.00097}
-% }}
-% $$
-
-% \blue{In the second {\sc verify} phase, the controller failed to stabilize the system for all the range of uncertainties, another counterexample was provided, and the following candidate controller is presented in another {\sc synthesise} phase:}
-% $$
-% {
-% \blue{
-% C(z)=\frac{0.68970z^2{+}0.36538z{+}0.30637}{0.06862z^2{+}0.00394z{+}0.00802}
-% }}
-% $$
-
-% \blue{
-% This candidate solution is validated as the final solution by the next 
-% {\sc verify} phase.
-% }
-
-\begin{figure*}
+using interval arithmetic on the synthesized controller.
+%
+\begin{figure*}[htb]
 \centering
@@
    \&;\\
-   \node[fill=gray!20] (synth) {{\sc Synthesise}};
+   \node[fill=gray!20] (synth) {{\sc Synthesize}};
    \&
@@
    \& \\
-   \& \\
    \node (gp) {Closed-loop System Search};
@@
 %
-\begin{figure}[H]
+\subsection{Program synthesis for the example}
+%
+In more detail, in the first stage, denoted by {\sc Uncertainty} in Figure~\ref{fig:CEGIS}, 
+assuming a precision \param{I_p}{F_p} 
+we check whether the system is unstable for the current candidate solution,
+{\it i.e.}, if $\neg \phi_\mathit{stability}$ is satisfiable for $S(z)$.
+If this is the case, then we obtain a counterexample 
+$\tilde G(z)$, 
+%denoted by values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
+%\red{[see my comment above - these quantities pop up too abruptly.]},
+which makes the closed-loop system unstable. 
+This uncertainty is added to 
+the set {\sc inputs} such that, in the subsequent {\sc synthesize} phase, 
+we obtain a candidate solution consisting 
+of a controller $C(z)$, which makes the closed-loop 
+system stable for all the uncertainties accumulated in {\sc inputs}.
+
+If the {\sc Uncertainty} verification stage concludes that
+the system is stable for the current candidate solution,
+then we pass this solution to the second verification stage, {\sc Precision}, 
+which checks the propagation of the error in the fixed-point 
+calculations using a Fixed-point Arithmetic Verifier based on 
+interval arithmetic. 
+%
+% To achieve this, we use a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is assumed to be within the expected bounds and verified after synthesis using the interval version of the program.
+%
+% The first verification phase produces a counterexample if some instance of $\mathfrak{G}(z)$ does not verify the properties and the CEGIS loop iteratively looks for a new controller that verifies the supplied counterexamples.
+The second phase verifies the propagation of the error in the fixed point calculations.
+% If the second phase fails verification, we increase the precision of the analyser and feed the CEGIS loop again to find a sound solution. 
+% vouches for the use of CEGIS in most of our benchmarks.
+% \cdsay{end of integration}
+
+If the {\sc precision} verification returns $\mathit{false}$, then we
+increase the precision of \param{I_p}{F_p} and re-start the {\sc
+  synthesize} phase with an empty {\sc inputs} set.  Otherwise, we
+found a full sound solution for our synthesis problem and we are done.
+
+In the rest of the paper, we will refer to the two approaches 
+for the {\sc verify} phase as one-stage and two-stage, respectively.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Illustrative Example} \label{sec:running-ex}
+
+We will illustrate our approach with a classical cruise control example,
+extracted from the literature~\cite{Astrom08}.  The example will allow us to
+highlight the challenges that arise when using finite precision arithmetic
+in digital control.  We are given a discrete plant model (with a time step
+of $0.2$s), which is represented by the following $z$-expression:
+%
+\begin{equation}
+\label{Eq:running-example-plant}
+G\left(z\right) := \frac{0.0264}{z-0.9998}.
+\end{equation}
+
+Using an optimization tool, the authors
+of~\cite{DBLP:conf/hybrid/WangGRJF16} have designed a high-performance
+controller for this plant, which is characterized by the following
+$z$-domain transfer function:
+%
+\begin{equation}
+\label{Eq:running-example-controller}
+C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
+\end{equation}
+%
+The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that this controller
+$C(z)$ (Eq.~\eqref{Eq:running-example-controller}) stabilizes the
+closed-loop system for the discrete plant model $G(z)$
+(Eq.~\ref{Eq:running-example-plant}).  However, if the effects of finite
+precision arithmetic are considered during verification (e.g., fixed-point
+arithmetic and word-length), then this closed-loop system becomes unstable.
+%
+For instance, an implementation of $C(z)$ using \param{4}{16} fixed-point
+numbers (i.e., $4$ bits for the integer part and $16$ bits for the
+fractional part) can be modeled as follows:
+%
+\begin{equation}
+\label{Eq:running-example-controller-quantized}
+C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
+{+}1.895996}{z^2{-}1.843994z+0.849594} \;.
+\end{equation} 
+%
+The resulting system using the typical series loop configuration, where
+$C_{q}\left(z\right)$ and $G\left(z\right)$ are in the forward path, is
+unstable.
+%
+%
+We now demonstrate how our approach solves the synthesis problem for the
+example given in the previous section.  We start with the candidate solution
+with all coefficients zero, as given below, and a precision of $I_p=16$,
+$F_p=24$.  The digital controller is designed with standard techniques for
+control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}.
+%
+%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
+%
+%$$
+%\begin{array}{ll}
+%N_C(z) {=} 0z^2{+}0z{+}0\\
+%D_C(z) {=} 0z^2{+}0z{+}0\\
+%\end{array}
+%$$
+$$ C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0} $$
+
+In the first {\sc verify} stage, the {\sc uncertainty} 
+check finds the following counterexample:
+%
+$$ \tilde G(z) = \frac{0.026506}{1.000610z+1.002838} $$
+
+%$$
+%\begin{array}{ll}
+%\Delta N_G(z) = 0.026506\\
+%\Delta D_G(z) = 1.000610z+1.002838
+%\end{array}
+%$$
+
+We add this counterexample to {\sc inputs} and initiate the {\sc synthesize}
+phase, where we obtain the following candidate solution:
+%
+%\red{[ How is the order of the candidate solution chosen here?]}
+$$
+C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}
+$$
+
+This time, the {\sc uncertainty} check does not find any
+counterexample and we pass the current candidate solution to the {\sc
+precision} verification stage.
+%
+% In the second {\sc verify} phase, we check whether the current candidate
+% solution above is the final solution. It is not and the verifier signals
+% that it is due to lack of precision.
+%
+We obtain the result $\mathit{false}$, meaning that the current precision is
+insufficient.  Consequently, we increase our precision to $I_p=20$, $F_p=28$.
+%
+Since the previous counterexamples were obtained at lower precision, we
+remove them from the set of counterexamples.  Back in the {\sc synthesize}
+phase, we re-start the process with a candidate solution with all
+coefficients $0$.  Next, the {\sc uncertainty} verification stage provides
+the first counterexample at higher precision:
+%
+%$$
+%\begin{array}{ll}
+%\Delta N_G(z) {=} 0.026314\\
+%\Delta D_G(z) {=} 0.999024z{-}1.004785
+%\end{array}
+%$$
+$$ \tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785} $$
+
+In the next {\sc synthesize} phase, we get a new candidate solution that
+eliminates the new, higher precision counterexample:
+%
+$$ C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357} $$
+%
+%$$
+%\begin{array}{ll}
+%N_C(z) {=} \\
+%D_C(z) {=} \\
+%\end{array}
+%$$
+
+This candidate solution is validated as the final solution by both stages
+{\sc uncertainty} and {\sc precision} in the {\sc verify} phase.
+In particular, Figure~\ref{fig:bode} shows the Bode diagram of the illustrative example 
+using the digital controller represented by Eq.~\eqref{Eq:running-example-controller} from~\cite{DBLP:conf/hybrid/WangGRJF16} 
+(Fig.~\ref{fig:original}) and the final candidate solution from our synthesizer (Fig.~\ref{fig:cegiscontroller}). 
+The phase margin is negative as shown in Figure~\ref{fig:original}, which means that the controller 
+represented by Eq.~\eqref{Eq:running-example-controller} is unstable, considering FWL effects. 
+However, the final solution from \tool is stable since it presents an infinite phase margin 
+and a gain margin of $17.8 dB$.
+
+%, which fails to find a new counterexample (i.e. returns UNSAT).
+
+% \blue{
+% For the same cruise control system, the synthesis may be done considering that the plant model have parametric uncertainties ($\Delta G_{P}(z)$).
+Thus, the synthesised controller must to stabilize for any parametric variation $\Delta p$ inside of a given region.
+Specially, in this example, was assumed that each coefficient of $G(z)$ may vary $\pm 0.5\%$.
+% }
+
+% \blue{Initially, the controller denominator and numerator  ($D_{C}(z)$ and $N_{C}(z)$) are started with zero coefficients, as in previous example.
+Thus,  in the first {\sc verify} phase a counterexample is presented, that is added to {\sc inputs}, whis is usede in the first  {\sc synthesise} phase.
+The resulting controller is:
+% }
+% $$
+% {
+% \blue{
+% C(z)=\frac{0.77516z^2{+}-0.71497z{+}0.03729}{0.25024z^2{-}0.01799z{+}0.00097}
+% }}
+% $$
+
+% \blue{In the second {\sc verify} phase, the controller failed to stabilize the system for all the range of uncertainties, another counterexample was provided, and the following candidate controller is presented in another {\sc synthesise} phase:}
+% $$
+% {
+% \blue{
+% C(z)=\frac{0.68970z^2{+}0.36538z{+}0.30637}{0.06862z^2{+}0.00394z{+}0.00802}
+% }}
+% $$
+
+% \blue{
+% This candidate solution is validated as the final solution by the next 
+% {\sc verify} phase.
+% }
+%
+\begin{figure}[htb]
     \centering
@@
         \includegraphics[width=\textwidth]{figures/runningexample_bd2.pdf}
-        \caption{Controller synthesised by \tool.}
+        \caption{Controller synthesized by \tool.}
         \label{fig:cegiscontroller}
     \end{subfigure}
-    \caption{Bode diagram for original~\cite{DBLP:conf/hybrid/WangGRJF16} and synthesised closed-loop systems.}\label{fig:bode}
+    \caption{Bode diagram for original~\cite{DBLP:conf/hybrid/WangGRJF16} and synthesized closed-loop systems.}\label{fig:bode}
 \end{figure}
@@
     \end{subfigure}
-    \caption{Step responses for original~\cite{DBLP:conf/hybrid/WangGRJF16} closed-loop system with FWL effects and for each {\sc synthesise} step of \tool.}\label{fig:step}
+    \caption{Step responses for original~\cite{DBLP:conf/hybrid/WangGRJF16} closed-loop system with FWL effects and for each {\sc synthesize} step of \tool.}\label{fig:step}
 \end{figure*}
@@
 
-\noindent using the ZOH discretisation defined in Eq.~\eqref{eq:pulsetf}, 
+\noindent using the ZOH discretization defined in Eq.~\eqref{eq:pulsetf}, 
 the following $z$-domain model is obtained
@@
 %
-\noindent where $G_{4}(z)$ is obtained using the ZOH discretisation defined
+\noindent where $G_{4}(z)$ is obtained using the ZOH discretization defined
 in Eq.~\eqref{eq:pulsetf} with three different sample times ($0.1$, $0.05$,
@@
 
-\item RQ2 \textbf{(sanity check)} are the synthesised controllers sound
+\item RQ2 \textbf{(sanity check)} are the synthesized controllers sound
 and can their stability be confirmed outside of our model?
@@
 
-We give the runtimes required to synthesise a stable controller for each
+We give the runtimes required to synthesize a stable controller for each
 benchmark in Table~\ref{tab:results}.  Here, \textit{Plant} is the discrete
@@
 fractional bits of the stable controller, respectively, while \textit{Time}
-is the total time (in seconds) required to synthesise a stable controller
+is the total time (in seconds) required to synthesize a stable controller
 for the given plant.
@@
 %interval arithmetic back-end 
-is able to complement the two-stage approach and synthesise a solution
+is able to complement the two-stage approach and synthesize a solution
 instead, albeit with significantly larger runtimes.  This performance
@@
 The median runtime for our benchmark set is $197$\,s, implying that \tool
-can synthesise half of the controllers in less than $5$ minutes.  Overall,
+can synthesize half of the controllers in less than $5$ minutes.  Overall,
 the average synthesis time amounts to approximately $30$ minutes.  With
@@
 to control engineers.  We further conclude that the approach
-using a two-stage verification engine is able to synthesise stable
+using a two-stage verification engine is able to synthesize stable
 controllers in $12$ out of the $15$ benchmarks, and can be complemented
@@
 controller synthesis for $14$ out of $15$ benchmarks.  For the $1$ remaining
-benchmark our approach failed to synthesise a stable controller in the
+benchmark our approach failed to synthesize a stable controller in the
 requested time limits.  This can be addressed by either increasing the fixed
 point word widths considered or using floating point arithmetic instead. 
-The synthesised controllers were confirmed to be stable outside of our
+The synthesized controllers were confirmed to be stable outside of our
 model representation using MATLAB, positively answering RQ2.
@@
 benchmarks. Nevertheless, this set of benchmarks is limited within the
-scope of this paper and \tool's performance may not generalise to other
+scope of this paper and \tool's performance may not generalize to other
 benchmark scenarios. This can be addressed by expanding the benchmark set
@@
 Furthermore, our algorithm to select suitable FWL word widths to model
-plant behaviour employs a heuristic based on user-provided controller
+plant behavior employs a heuristic based on user-provided controller
 word-width specifications.  Given the encouraging results of our benchmarks,
 this heuristic appears to be strong enough for the current benchmark set,
-but this may not generalise.  Further experiments towards determining
+but this may not generalize.  Further experiments towards determining
 suitable plant FWL configurations may thus be necessary in future work.
@@
 Finally, the experimental results we obtained using \tool for stability
-properties may not generalise to other properties.  The inductive nature of
+properties may not generalize to other properties.  The inductive nature of
 the two-stage back-end of \tool increases performance significantly compared
 to the one-stage back-end, but this performance benefit introduced by CEGIS'
-inductive generalisations may not be observed for other controller
+inductive generalizations may not be observed for other controller
 properties.  Additional experiments are necessary to confirm that the
@@
 controller synthesis, many of these techniques lack the ability to produce
-sound or stable results because they disregard the effects of quantisation
+sound or stable results because they disregard the effects of quantization
 and rounding.  Recent papers on implementations/synthesis of LTI digital
-controllers~\cite{das2013lqr,ghosh2013fpga} focus on time discretisation,
+controllers~\cite{das2013lqr,ghosh2013fpga} focus on time discretization,
 failing to account for these error-inducing effects and can therefore result
@@
 response~\cite{Duggirala2015}, and Finite Word Length (FWL) constraints with
-the goal to either verify (e.g.~\cite{daes20161}) or optimise
+the goal to either verify (e.g.~\cite{daes20161}) or optimize
 (e.g.~\cite{oudjida2014design}) implementations.  There are in fact two
@@
 \cite{alur2016compositional} requires a user-defined finite state
-abstraction to synthesise a digital controller based on high level
+abstraction to synthesize a digital controller based on high level
 specifications.  Whilst this approach directly overcomes the challenges
@@
 intervention.  A different solution that looks at the other end of the scale
-is an approach that synthesises word lengths for known problems as developed
+is an approach that synthesizes word lengths for known problems as developed
 in~\cite{jha2013swati}; however, this provides neither an optimal word
@@
 obtain correct by design programs from high-level specifications.  One such
-approach~\cite{itzhaky2010simple} looks to inductively synthesise invariants
+approach~\cite{itzhaky2010simple} looks to inductively synthesize invariants
 to generate the desired programs.  Since these digital programs are already
@@
 circumvents the FWL problem.  It is also not suitable for the kind of
-control we seek to synthesise.  What is needed in this regard is the
+control we seek to synthesize.  What is needed in this regard is the
 combination of a synthesis engine with a control verification tool that
@@
 from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from~\cite{daes20161}
-whilst enhancing the procedure by evaluating the quantisation effects of
+whilst enhancing the procedure by evaluating the quantization effects of
 the Hardware interfaces (ADC/DAC) to obtain an accurate discrete-time FWL
@@
 for a stabilizing digital controller given a continuous (or discrete) plant 
-specification.  This enables us to automatically synthesise correct-by-construction 
+specification.  This enables us to automatically synthesize correct-by-construction 
 digital controllers for a given model of their physical environment.  
-Our approach addresses the effects of the quantisers (A/D and D/A converters) 
-as time discretisation elements with quantisation noise.  Our experimental results 
-show that \tool is able to synthesise stable controllers in most benchmarks within
+Our approach addresses the effects of the quantizers (A/D and D/A converters) 
+as time discretization elements with quantization noise.  Our experimental results 
+show that \tool is able to synthesize stable controllers in most benchmarks within
 reasonable time frames fully automatically.

### 2016-10-14 paper/paper.tex
replace 'ising' by 'izing'

@@
 \emph{stable}.  Due to the complexity of such systems, in this work we focus on linear
-models with known configurations and perform parametric synthesis of stabilising digital controllers.
+models with known configurations and perform parametric synthesis of stabilizing digital controllers.
 
@@
 %------------------------------------
-\subsection{Discretising the Plant}
+\subsection{Discretizing the Plant}
 \label{ssec:SandH}
@@
 Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$
-(\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$ which come from tolerances/imprecisions in the original model), errors in the numeric
+(\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$ which come from tolerances/imprecision in the original model), errors in the numeric
 calculations, or roundoffs in the quantization.  These uncertainties are 
@@
 that the parametric errors in the plant have the same polynomial order as
-the plant itself (all other errors described in this paper are ensured to fulfil this property in our
+the plant itself (all other errors described in this paper are ensured to fulfill this property in our
 implementation).
@@
 In Figure~\ref{fig:digsystem1}, two sources of uncertainties are
-illustrated: parametric uncertainties related to modelling errors, and
+illustrated: parametric uncertainties related to modeling errors, and
 uncertainties introduced by quantizations in sampling and holding process,
@@
 %
-However, given a real plant $\hat{G}(z)$, and a discretising function
+However, given a real plant $\hat{G}(z)$, and a discretizing function
 %
@@
 three-axis attitude tracking, but here only one axis at a time is
-considered.  The motion equation for the one-axis system, despising
+considered.  The motion equation for the one-axis system, disregarding
 disturbance torques, is given by
@@
 Researchers in formal verification of control systems have studied various
-effects of discretising the dynamics, including delayed
+effects of discretizing the dynamics, including delayed
 response~\cite{Duggirala2015}, and Finite Word Length (FWL) constraints with
@@
 We will also consider performance requirements while
-synthesising the digital controller.
+synthesizing the digital controller.
 

### 2016-10-14 paper/paper.tex
Minor spelling errors.

@@
 \noindent where $I$ is the inertia moment of satellite about its mass
-center, $\tau_{C}$ is the control torque applied by thusters, and $\theta$
+center, $\tau_{C}$ is the control torque applied by thrusters, and $\theta$
 is the controlled attitude angle.  Normalizing Eq.~\eqref{eq:satelliteode}

### 2016-10-14 paper/paper.tex
move back header of sec --Program synthesis for the example--
improve introduction

--- 2016-10-14 paper/paper.tex
@@
 
-\item We design and implement an automatic approach for generating
-  {\em corect-by-construction} digital controllers that is based on
+\item We design and implement an automatic approach in a tool called \tool  
+  for generating {\em corect-by-construction} digital controllers that is based on
   state-of-the-art inductive synthesis techniques.  Our application of
@@
 
-\item We provide experimental results showing that our tool is able to
-synthesize stable controllers for a set of intricate benchmarks taken from
-the literature efficiently: the median runtime for our benchmark set is
-$197$s, i.e., half of the controllers can be synthesized in less than five
-minutes.
+\item We provide experimental results showing that \tool
+is able to synthesize stable controllers for a set of intricate benchmarks 
+taken from the literature efficiently: the median runtime for our benchmark 
+set is $197$s, i.e., half of the controllers can be synthesized in less than 
+five minutes.
 

### 2016-10-14 paper/paper.tex

@@
 %
-\subsection{Program synthesis for the example}
 %
@@
 %
+\subsection{Program synthesis for the example}
 %

### 2016-10-14 paper/paper.tex
formatting

--- 2016-10-14 paper/paper.tex
@@
 %
-A feedback closed-loop control system as given in Figure~\ref{fig:sampledsystem},
-with a FWL implementation of the digital controller $\hat{C}(z) =\mathit{FWL}_{M_C,N_C}[C(z)]$ and uncertain
-discrete model of the plant 
+Consider a feedback closed-loop control system as given in
+Figure~\ref{fig:sampledsystem} with a FWL implementation of the digital
+controller $\hat{C}(z) =\mathit{FWL}_{M_C,N_C}[C(z)]$ and uncertain discrete
+model of the plant
+%
 $$\hat{G}(z) =\frac{\hat{G}_n(z)}{\hat{G}_d(z)}: \vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q
-\vec{G} \text{(from  \ref{eq:coefficients},\ref{eq:delta_coefficients})}$$ ,  
-$\hat{G}(z)$, is
-BIBO-stable if and only if:
+\vec{G} \text{\quad(from~\ref{eq:coefficients},\ref{eq:delta_coefficients})}$$
+%
+Then $\hat{G}(z)$ is BIBO-stable if and only if:
 %

### 2016-10-14 paper/paper.tex

@@
 
-By contrast, we leverage very recent step-change in the scalability of
+By contrast, we leverage a very recent step-change in the scalability of
 \emph{program synthesis}.  Program synthesis engines use a program
@@
 we translate the problem into a single digital domain.  
-Given our primary interest in stability despite digitization effects, we have modelled
+Given our primary interest in stability despite digitization effects, we have modeled
 a digital equivalent of the plant by evaluating the effects of the
@@
   that continuously refines the precision of the fixed-point
-  representation is key to the performance of our approach yielding,
+  representation of the plant is key to the performance of our approach yielding,
   in most cases, a speed-up of at least two orders of magnitude over a
@@
 \item We provide experimental results showing that \tool
-is able to synthesize stable controllers for a set of intricate benchmarks 
-taken from the literature efficiently: the median runtime for our benchmark 
+is able to efficiently synthesize stable controllers for a set of intricate benchmarks 
+taken from the literature: the median runtime for our benchmark 
 set is $197$s, i.e., half of the controllers can be synthesized in less than 
@@
 
-Lemma~\ref{eq:pulsetf} ensures the poles and zeros matching under the 
+Lemma~\ref{eq:pulsetf} ensures that the poles and zeros match under the 
 $\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$
@@
 %
-In Figure~\ref{fig:digsystem1}, two sources of uncertainties are
+In Figure~\ref{fig:digsystem1}, two sources of uncertainty are
 illustrated: parametric uncertainties related to modeling errors, and
@@
 Correct synthesis of the digital controller requires consideration of the
-effect of FWL in controller and quantization noises in the closed loop
+effect of FWL on the controller and quantization noises in the closed loop
 system.  Let the quantizer $Q1$ be the source of a white noise $\nu_{1}$ and

### 2016-10-14 paper/paper.tex
final fixes

@@
 &f^p : \mathbb{R} \rightarrow  \mathbb{R}\langle I_p,F_p \rangle \triangleq \tilde x = f^p(x) : \tilde x=x-(x\mod\tilde x)\\
-&\mathit{FWL}_n^p[P \in \mathcal{P}] = \tilde P \in \mathcal{P}^{n}\langle I_p,F_p \rangle : c_i \in \vec{P} \wedge \tilde c_i \in \tilde \vec{P}=f^p(c_i)  \nonumber
+&\mathit{FWL}_n^p[P \in \mathcal{P}] = \tilde P \in \mathcal{P}^{n}\langle I_p,F_p \rangle : c_i \in \vec{P} \wedge \tilde c_i \in \vec{\tilde{P}}=f^p(c_i)  \nonumber
 \end{align}
@@
 two-stage verification: the first stage performs potentially unsound
-fixed-point operations assuming a precision \param{I_p}{F_p}, and the
+fixed-point operations assuming a plant precision \param{I_p}{F_p}, and the
 second stage restores soundness by validating these operations
@@
 \label{Eq:running-example-plant}
-G\left(z\right) := \frac{0.0264}{z-0.9998}.
+G\left(z\right) = \frac{0.0264}{z-0.9998}.
 \end{equation}
@@
 \label{Eq:running-example-controller}
-C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
+C\left(z\right) = \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
 \end{equation}
@@
 using the digital controller represented by Eq.~\eqref{Eq:running-example-controller} from~\cite{DBLP:conf/hybrid/WangGRJF16} 
-(Fig.~\ref{fig:original}) and the final candidate solution from our synthesizer (Fig.~\ref{fig:cegiscontroller}). 
+(Figure~\ref{fig:original}) and the final candidate solution from our synthesizer (Figure~\ref{fig:cegiscontroller}). 
 The phase margin is negative as shown in Figure~\ref{fig:original}, which means that the controller 
@@
 with the original controller represented by Eq.~\eqref{Eq:running-example-controller} (Figure~\ref{fig:step0}), 
-the first (Figure~\ref{fig:step1}) and final (Fig.~\ref{fig:step2}) candidate solutions provided by \tool. 
+the first (Figure~\ref{fig:step1}) and final (Figure~\ref{fig:step2}) candidate solutions provided by \tool. 
 The step response in Figure~\ref{fig:step0} confirms the stability loss if we consider FWL effects. 
@@
 w.r.t.~earth.  The satellite attitude control is typically used for
-three-axis attitude tracking, but here only one axis at a time is
-considered.  The motion equation for the one-axis system, disregarding
+three-axis attitude tracking, but here we consider one axis at a time.
+The motion equation for the one-axis system, disregarding
 disturbance torques, is given by
@@
 
-\noindent where $I$ is the inertia moment of satellite about its mass
+\noindent where $I$ is the inertia moment of the satellite about its mass
 center, $\tau_{C}$ is the control torque applied by thrusters, and $\theta$
 is the controlled attitude angle.  Normalizing Eq.~\eqref{eq:satelliteode}
-by defining the control signal $u=\frac{\tau_{C}}{I}$ and taking Laplace
+by defining the control signal $u=\frac{\tau_{C}}{I}$ and taking the Laplace
 transform, the following $s$-domain transfer function $G(s)$ is obtained

### 2016-10-15 paper/paper.tex
update es 21
minor changes
Added higher precision to C_q.
dot missing
use a PDF instead of a PNG for Fig 3
nudge

@@
 literature in Section~\ref{sec:related}. We conclude and describe future
-work in Section~\ref{sec:conclusions}
+work in Section~\ref{sec:conclusions}.
 
@@
 \centering
-\includegraphics[width=\textwidth]{figures/verification-flow.png}
+\includegraphics[width=\textwidth]{figures/verification-flow.pdf}
 \vspace{1ex}
@@
 \label{Eq:running-example-controller-quantized}
-C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
-{+}1.895996}{z^2{-}1.843994z+0.849594} \;.
+\resizebox{.47\textwidth}{!}{
+$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
+{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$
+}
 \end{equation} 
@@
         \includegraphics[width=\textwidth]{figures/runningexample_step0.pdf}
-        \caption{Orignal controller.}
+        \caption{Orignal controller}
         \label{fig:step0}
@@
         \includegraphics[width=\textwidth]{figures/runningexample_step1.pdf}
-        \caption{First candidate solution.}
+        \caption{First solution by \tool}
         \label{fig:step1}
@@
         \includegraphics[width=\textwidth]{figures/runningexample_step2.pdf}
-        \caption{Final solution by \tool.}
+        \caption{Final solution by \tool}
         \label{fig:step2}
     \end{subfigure}
-    \caption{Step responses for original~\cite{DBLP:conf/hybrid/WangGRJF16} closed-loop system with FWL effects and for each {\sc synthesize} step of \tool.}\label{fig:step}
+    \caption{Step responses for original~\cite{DBLP:conf/hybrid/WangGRJF16}
+             closed-loop system with FWL effects and for each
+             {\sc synthesize} iteration of \tool}\label{fig:step}
 \end{figure*}

### 2016-10-15 paper/paper.tex
nudge
minor typesetting

@@
 \label{FWL_tf}
-&f^p : \mathbb{R} \rightarrow  \mathbb{R}\langle I_p,F_p \rangle \triangleq \tilde x = f^p(x) : \tilde x=x-(x\mod\tilde x)\\
+&f^p : \mathbb{R} \rightarrow  \mathbb{R}\langle I_p,F_p \rangle \triangleq \tilde x = f^p(x) : \tilde x=x-(x\bmod\tilde x)\\
 &\mathit{FWL}_n^p[P \in \mathcal{P}] = \tilde P \in \mathcal{P}^{n}\langle I_p,F_p \rangle : c_i \in \vec{P} \wedge \tilde c_i \in \vec{\tilde{P}}=f^p(c_i)  \nonumber
@@
 %
-we calculate $\tilde G(z)=FWL_{M_G,N_G}^p(\hat{G}(z))$
+we calculate $\tilde G(z)=\mathit{FWL}_{M_G,N_G}^p(\hat{G}(z))$
 %
@@
 % &= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
+%
 \label{digital_plant_tf}
@@
 \end{align}
-where $\Delta_b\hat{c}_i=\hat{c}_i\mod \tilde{c}_i$
+%
+where $\Delta_b\hat{c}_i=\hat{c}_i\bmod \tilde{c}_i$
 and $\Delta_b{G}$ represents the plant uncertainty caused by
@@
 
-Finally, the experimental results we obtained using \tool for stability
+Finally, the experimental results obtained using \tool for stability
 properties may not generalize to other properties.  The inductive nature of

### 2016-10-15 paper/paper.tex
caps
minor typesetting

@@
 refinement process which is explained in detail in
-section~\ref{synthesizer-general}.  A~successful synthesis result is
+Section~\ref{synthesizer-general}.  A~successful synthesis result is
 reported if CEGIS generates a controller that is safe with respect to~$\phi$. 
@@
 in digital control.  We are given a discrete plant model (with a time step
-of $0.2$s), which is represented by the following $z$-expression:
+of $0.2$\,s), which is represented by the following $z$-expression:
 %
@@
 \label{Eq:running-example-plant}
-G\left(z\right) = \frac{0.0264}{z-0.9998}.
+G(z) = \frac{0.0264}{z-0.9998}.
 \end{equation}
@@
 \label{Eq:running-example-controller}
-C\left(z\right) = \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
+C(z) = \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
 \end{equation}
@@
 \resizebox{.47\textwidth}{!}{
-$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
+$C_{q}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
 {+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$
@@
 The resulting system using the typical series loop configuration, where
-$C_{q}\left(z\right)$ and $G\left(z\right)$ are in the forward path, is
+$C_{q}(z)$ and $G(z)$ are in the forward path, is
 unstable.

### 2016-10-15 paper/paper.tex
minor typesetting

@@
 model for the car accounting for rolling friction, aerodynamic drag, and
-gravitational disturbance force~\cite{Astrom08} as follows
+gravitational disturbance force~\cite{Astrom08} as follows:
 %

### 2016-10-15 paper/paper.tex
minor typesetting

@@
 \label{cruise-control-c1}
-G_1(z)=\frac{0.0264}{z-0.998}. \nonumber
+G_1(z)=\frac{0.0264}{z-0.998} \nonumber
 \end{equation}
@@
 damper~\cite{DBLP:conf/hybrid/WangGRJF16}, where the discrete 
-plant dynamics is represented by the following $z$-expression
+plant dynamics is represented by the following $z$-expression:
 %
@@
 A third set of benchmarks that consists of a physical plant for satellite
-applications is considered~\cite{Franklin15}, in order to evaluate the
-full capabilities of the present approach.  In particular, satellites often require
-attitude (pose) control for proper orientation of antennas and sensors
-w.r.t.~earth.  The satellite attitude control is typically used for
-three-axis attitude tracking, but here we consider one axis at a time.
-The motion equation for the one-axis system, disregarding
-disturbance torques, is given by
+applications is considered~\cite{Franklin15}, in order to evaluate the full
+capabilities of the present approach.  In particular, satellites often
+require attitude (pose) control for proper orientation of antennas and
+sensors w.r.t.~earth.  The satellite attitude control is typically used for
+three-axis attitude tracking, but here we consider one axis at a time.  The
+motion equation for the one-axis system, disregarding disturbance torques,
+is given by
 %
@@
 \end{equation}
-
+%
 \noindent where $I$ is the inertia moment of the satellite about its mass

### 2016-10-15 paper/paper.tex
typesetting units
add authors and affiliations
use addaddr

@@
 
-\author{Author names omitted for review}
+\author{Alessandro Abate$^{1}$, Iury Bessa$^{2}$, Dario Cattaruzza$^{1}$, Lucas Cordeiro$^{1,2}$, \\ 
+Cristina David$^{1}$, Pascal Kesseli$^{1}$ and Daniel Kroening$^{1}$
+\and
+$^{1}$\affaddr{University of Oxford, Oxford, United Kingdom} \\
+$^{2}$\affaddr{Federal University of Amazonas, Manaus, Brazil}
+}
 

### 2016-10-15 paper/paper.tex
nudges

@@
 %
-Modern control is implemented using digital microcontrollers, which are
+Modern control is implemented with digital microcontrollers, which are
 designed to work in an embedded environment, within a dynamical plant that
@@
 %
-We present a new algorithm based on counterexample guided inductive
+We present a new algorithm based on counter\-example guided inductive
 synthesis that automates the design of digital controllers that are
@@
 controller designed by the engineer.  Recent work can show the stability of
-digital controllers with considerations to implementation aspects, i.e.,
-fixed-point arithmetic and the word length used~\cite{Bessa16}.  This work
-exploits advances in bit-accurate verification of C programs to obtain a
-verifier for software-implemented digital control.
+digital controllers with consideration of implementation aspects, i.e.,
+fixed-point arithmetic and the word length used~\cite{Bessa16}.  The authors
+of~\cite{Bessa16} exploit advances in bit-accurate verification of C
+programs to obtain a verifier for software-implemented digital control.
 
@@
 able to generate programs for highly non-trivial specifications with a very
-high degree of automation.  Modern CEGIS engines implement combinations of
-automated testing, genetic algorithms and SMT-based automated
+high degree of automation.  Modern CEGIS engines combine automated testing,
+genetic algorithms and SMT-based automated
 reasoning~\cite{DBLP:conf/lpar/DavidKL15, DBLP:conf/cav/0001A14}.
@@
 tool that automatically \emph{generates} digital controllers for a given
-continuous plant model that are correct by construction.  This approach promises to
-reduce the cost and time of development of digital control dramatically, and
-requires considerably less expertise than methodologies driven by
-verification.  Specifically, we synthesize controllers for hybrid
+continuous plant model that are correct by construction.  This approach
+promises to reduce the cost and time of development of digital control
+dramatically, and requires considerably less expertise than methodologies
+driven by verification.  Specifically, we synthesize controllers for hybrid
 closed-loop systems, i.e., software-implemented embedded controllers along
 with a model of their physical environment (the plant), that are
-\emph{stable}.  Due to the complexity of such systems, in this work we focus on linear
-models with known configurations and perform parametric synthesis of stabilizing digital controllers.
+\emph{stable}.  Due to the complexity of such systems, in this work we focus
+on linear models with known configurations and perform parametric synthesis
+of stabilizing digital controllers.
 
@@
 the plant exhibits continuous behavior whereas the controller operates in
-discrete time and over a quantized domain.  
-Inspired by a classical approach \cite{astrom1997computer}, 
-we translate the problem into a single digital domain.  
-Given our primary interest in stability despite digitization effects, we have modeled
-a digital equivalent of the plant by evaluating the effects of the
-quantizers (A/D and D/A converters) as time discretization elements with
-quantization noise.  The resulting closed-loop system is a program loop that
-operates on bit-vectors encoded using fixed-point arithmetic with finite-word
-length (FWL). The deterministic effects of the FWL and
-quantization errors are incorporated into the model as an additive
+discrete time and over a quantized domain.  Inspired by a classical approach
+\cite{astrom1997computer}, we translate the problem into a single digital
+domain.  Given our primary interest in stability despite digitization
+effects, we have modeled a digital equivalent of the plant by evaluating the
+effects of the quantizers (A/D and D/A converters) as time discretization
+elements with quantization noise.  The resulting closed-loop system is a
+program loop that operates on bit-vectors encoded using fixed-point
+arithmetic with finite word length (FWL).  The deterministic effects of the
+FWL and quantization errors are incorporated into the model as an additive
 uncertainty, which is taken into account during the CEGIS-based synthesis of
@@
 \item We design and implement an automatic approach in a tool called \tool  
-  for generating {\em corect-by-construction} digital controllers that is based on
-  state-of-the-art inductive synthesis techniques.  Our application of
-  program synthesis is non-trivial and requires addressing challenges
-  specific to embedded control systems, such as the effects of quantizers and
-  FWL. In particular, we have found that a two-stage verification engine
-  that continuously refines the precision of the fixed-point
-  representation of the plant is key to the performance of our approach yielding,
-  in most cases, a speed-up of at least two orders of magnitude over a
-  conventional one-stage verification engine.
-
-\item We provide experimental results showing that \tool
-is able to efficiently synthesize stable controllers for a set of intricate benchmarks 
-taken from the literature: the median runtime for our benchmark 
-set is $197$s, i.e., half of the controllers can be synthesized in less than 
-five minutes.
+  for generating {\em correct-by-construction} digital controllers that is
+  based on state-of-the-art inductive synthesis techniques.  Our application
+  of program synthesis is non-trivial and requires addressing challenges
+  specific to embedded control systems, such as the effects of quantizers
+  and FWL.  In particular, we have found that a two-stage verification
+  engine that continuously refines the precision of the fixed-point
+  representation of the plant is key to the performance of our approach
+  yielding, in most cases, a speed-up of at least two orders of magnitude
+  over a conventional one-stage verification engine.
+
+\item We provide experimental results showing that \tool is able to
+  efficiently synthesize stable controllers for a set of intricate
+  benchmarks taken from the literature: the median runtime for our benchmark
+  set is $197$s, i.e., half of the controllers can be synthesized in less
+  than five minutes.
 
 %% \item We exploit a CEGIS-based approach that uses inductive synthesis
-%% together with a bit-precise formal verification algorithm for synthesising
+%% together with a bit-precise formal verification algorithm for synthesizing
 %% correct-by-design robust digital controllers for non-fragile closed-loop
@@
 
-%% \item Experimental results with our synthesiser show that the
+%% \item Experimental results with our synthesizer show that the
 %% combination of interval arithmetic to represent the controller coefficients
@@
 In this case I believe there are also two separate sources for $\Delta{G}_p(z)$.
-The first is $\Delta{G}_p(s)$ (which is basically a known tolerance that may come from G(t)), whilst the second is the error introduced by the calculations in the $\mathcal{Z}$ transform.
+The first is $\Delta{G}_p(s)$ (which is basically a known tolerance that may come from G(t)), while the second is the error introduced by the calculations in the $\mathcal{Z}$ transform.
 Alessandro, do you want to address this second term (possibly as explained below) or just leave the blue section as is?}
@@
 %%
-%Note that $\Delta{G}_P$ is undefined and upperbound by a user defined
+%Note that $\Delta{G}_P$ is undefined and upper bound by a user defined
 %value such that $\hat{G}(z)$ corresponds to the set of
@@
 %In particular, Widrow \cite{widrow1956} models the quantization noise as a
-%gaussian model in which the second moment (variance) of the probability
+%Gaussian model in which the second moment (variance) of the probability
 %density function (PDF) of the quantization noise is given by
@@
 % \blue{Initially, the controller denominator and numerator  ($D_{C}(z)$ and $N_{C}(z)$) are started with zero coefficients, as in previous example.
-Thus,  in the first {\sc verify} phase a counterexample is presented, that is added to {\sc inputs}, whis is usede in the first  {\sc synthesise} phase.
+Thus,  in the first {\sc verify} phase a counterexample is presented, that is added to {\sc inputs}, whis is used in the first  {\sc synthesise} phase.
 The resulting controller is:
@@
         \includegraphics[width=\textwidth]{figures/runningexample_step0.pdf}
-        \caption{Orignal controller}
+        \caption{Original controller}
         \label{fig:step0}
@@
 error in the dynamics caused by the inability of the hardware to represent
-the exact dynamics of the system whilst the second relates to rounding
+the exact dynamics of the system while the second relates to rounding
 errors during computation.  In~\cite{fialho1994stability} a stability
@@
 rely on an invariant computation on the discrete system dynamics using
-Semi-Definite Programming (SDP).  Whilst the former uses BIBO properties to
+Semi-Definite Programming (SDP).  While the former uses BIBO properties to
 determine stability, the latter uses Lyapunov-based quadratic invariants. 
@@
 abstraction to synthesize a digital controller based on high level
-specifications.  Whilst this approach directly overcomes the challenges
+specifications.  While this approach directly overcomes the challenges
 presented by the FWL problem, it still requires error-prone user
@@
 from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from~\cite{daes20161}
-whilst enhancing the procedure by evaluating the quantization effects of
+while enhancing the procedure by evaluating the quantization effects of
 the Hardware interfaces (ADC/DAC) to obtain an accurate discrete-time FWL

### 2016-10-15 paper/paper.tex
nudges

@@
 
-\item We design and implement an automatic approach in a tool called \tool  
+\item We design and implement an automatic approach in our tool \tool  
   for generating {\em correct-by-construction} digital controllers that is

### 2016-10-15 paper/paper.tex
nudges

@@
 
-In recent years the development of program synthesis has found many ways to
-obtain correct by design programs from high-level specifications.  One such
-approach~\cite{itzhaky2010simple} looks to inductively synthesize invariants
-to generate the desired programs.  Since these digital programs are already
-constrained by designed to factors such as FWL, these approaches are ideal
-for the synthesis of parametric controllers. 
-In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS for the
-synthesis of switching controllers for stabilizing continuous-time plants
-with polynomial dynamics.  The work extends to its application on affine
-systems, finding its major challenge in the hardness of solving linear
-arithmetic on present SMT solvers.  Since this approach uses switching
-states instead of linear dynamics in the digital controller, it entirely
-circumvents the FWL problem.  It is also not suitable for the kind of
-control we seek to synthesize.  What is needed in this regard is the
+Program synthesis is the problem of computing correct-by-design programs
+from high-level specifications, and algorithms for this problem have made
+substantial progress in recent years.  One such
+approach~\cite{itzhaky2010simple} inductively synthesizes invariants to
+generate the desired programs.
+
+Program synthesisers are an ideal fit for synthesis of parametric
+controllers since the semantics of programs capture effects such as FWL
+precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
+for the synthesis of switching controllers for stabilizing continuous-time
+plants with polynomial dynamics.  The work extends to its application on
+affine systems, finding its major challenge in the hardness of solving
+linear arithmetic with the state-of-the-art SMT solvers.  Since this
+approach uses switching states instead of linear dynamics in the digital
+controller, it entirely circumvents the FWL problem.  It is also not
+suitable for the kind of control we seek to synthesize.  We require a
 combination of a synthesis engine with a control verification tool that
@@
 from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from~\cite{daes20161}
-while enhancing the procedure by evaluating the quantization effects of
-the Hardware interfaces (ADC/DAC) to obtain an accurate discrete-time FWL
+while enhancing the procedure by evaluating the quantization effects of the
+Hardware interfaces (ADC/DAC) to obtain an accurate discrete-time FWL
 representation of the continuous dynamics.
@@
 We have presented a CEGIS-based approach implemented in a tool called \tool,
-which uses inductive synthesis in conjunction with an algorithm for verifying 
-robust closed-loop stability. In particular, \tool is able to compute a parametric solution 
-for a stabilizing digital controller given a continuous (or discrete) plant 
-specification.  This enables us to automatically synthesize correct-by-construction 
-digital controllers for a given model of their physical environment.  
-Our approach addresses the effects of the quantizers (A/D and D/A converters) 
-as time discretization elements with quantization noise.  Our experimental results 
-show that \tool is able to synthesize stable controllers in most benchmarks within
-reasonable time frames fully automatically.
+which uses inductive synthesis in conjunction with an algorithm for
+verifying robust closed-loop stability.  In particular, \tool is able to
+compute a parametric solution for a stabilizing digital controller given a
+continuous (or discrete) plant specification.  This enables us to
+automatically synthesize correct-by-construction digital controllers for a
+given model of their physical environment.  Our approach addresses the
+effects of the quantizers (A/D and D/A converters) as time discretization
+elements with quantization noise.  Our experimental results show that \tool
+is able to synthesize stable controllers in most benchmarks within
+a reasonable amount of time fully automatically.
 %
@@
 %Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
-%
+
 Future work will be the extension of this CEGIS-based approach to further
-classes of systems, including state-space representation.  
-We will also consider performance requirements while
-synthesizing the digital controller.
+classes of systems, including state-space representation.  We will also
+consider performance requirements while synthesizing the digital controller.
 

### 2016-10-16 paper/paper.tex
wordings

@@
 However, the final solution from \tool is stable since it presents an infinite phase margin 
-and a gain margin of $17.8 dB$.
+and a gain margin of $17.8$\,dB.
 
@@
 systems has been researched for several decades.  On a theoretical level it
-is a solved problem~\cite{wonham1967pole} for which researches continuously
-seek better results based on a number of properties in addition to
+is a solved problem~\cite{wonham1967pole}, for which researchers
+continuously seek better results for a number of aspects in addition to
 stability.  A vast range of pole placement techniques such as Moore's
@@
 costs.  Since real systems are subject to tolerance and noise as well as the
-need for economy, more recent studies focus on the problems of achieving
+need for economy, more recent studies focus on the problem of achieving
 robust stability with minimum gain~\cite{schmid2014unified,
-konigorski2012pole}.  However, when extending the problem to digital
-controller synthesis, many of these techniques lack the ability to produce
+konigorski2012pole}.  However, when applied with the aim of synthesising a
+digital controller, many of these techniques lack the ability to produce
 sound or stable results because they disregard the effects of quantization
 and rounding.  Recent papers on implementations/synthesis of LTI digital
-controllers~\cite{das2013lqr,ghosh2013fpga} focus on time discretization,
+controllers~\cite{das2013lqr, ghosh2013fpga} focus on time discretization,
 failing to account for these error-inducing effects and can therefore result
-in digitally unstable systems that have been proven to be robustly stable in
-a continuous space.  This situation demands the inclusion of formal methods
-to verify the effects of space discretization on the implementation of the
-controller.
+in digital systems that are unstable even though they have been proven to be
+robustly stable in a continuous space.
 
@@
 effects of discretizing the dynamics, including delayed
-response~\cite{Duggirala2015}, and Finite Word Length (FWL) constraints with
+response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics with
 the goal to either verify (e.g.~\cite{daes20161}) or optimize
-(e.g.~\cite{oudjida2014design}) implementations.  There are in fact two
-different problems arising from FWL effects.  The first corresponds to the
-error in the dynamics caused by the inability of the hardware to represent
-the exact dynamics of the system while the second relates to rounding
-errors during computation.  In~\cite{fialho1994stability} a stability
-measure based on the error of the digital dynamics ensures that the FWL
-errors do not make the digital system unstable.  A more recent
+(e.g.~\cite{oudjida2014design}) given implementations.
+
+There are two different problems that arise from FWL semantics.  The first
+is the error in the dynamics caused by the inability to represent the exact
+state of the physical system while the second relates to rounding errors
+during computation.  In~\cite{fialho1994stability}, a stability measure
+based on the error of the digital dynamics ensures that the deviation
+introduced by FWL does not make the digital system unstable.  A more recent
 approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
 directly model the digital controller so that the selected parameters are
-stable by design.  Most studies following this verification research field
-focus on finding a correct implementation of a known desired controller,
-looking for optimal parameter representations using FWL, but ignoring the
-effects of rounding errors due to issues of mathematical tractability.  The
-analyses in~\cite{DBLP:conf/hybrid/WangGRJF16, DBLP:conf/hybrid/RouxJG15}
-rely on an invariant computation on the discrete system dynamics using
-Semi-Definite Programming (SDP).  While the former uses BIBO properties to
-determine stability, the latter uses Lyapunov-based quadratic invariants. 
-In both cases, the SDP solver uses floating-point arithmetic and soundness
-is checked by upper bounding the error.  An alternative approach is taken
+stable by design.  Most work in verification focusses on finding a correct
+variant of a known controller, e.g., by looking for optimal parameter
+representations using FWL, but ignore the effects of rounding errors due to
+issues of mathematical tractability.  The analyses
+in~\cite{DBLP:conf/hybrid/WangGRJF16, DBLP:conf/hybrid/RouxJG15} rely on an
+invariant computation on the discrete system dynamics using Semi-Definite
+Programming (SDP).  While the former uses BIBO properties to determine
+stability, the latter uses Lyapunov-based quadratic invariants.  In both
+cases, the SDP solver uses floating-point arithmetic and soundness is
+checked by bounding the error.  An alternative approach is taken
 by~\cite{park2016scalable}, where the verification of existing code is
@@
 
-Given the current knowledge in control system's synthesis, there is no other
-existing study on the automatic synthesis of fixed-point digital controllers
-considering FWL effects.  Parameter synthesis tools such
-as~\cite{cimatti2013parameter} use bounded model checking and fixed-point
-computations to find parameters based on user defined specifications, but
-they often operate in the continuous domain and are ill-suited for robust
-analysis since they have no direct means of evaluating robustness.  Other
-tools such as~\cite{economakos2016automated} are directly aimed at robust
-stability problems, but they fail to explore the effects of FWL in their
-implementation.  In order to provide a correct by design digital controller,
-\cite{alur2016compositional} requires a user-defined finite state
-abstraction to synthesize a digital controller based on high level
-specifications.  While this approach directly overcomes the challenges
-presented by the FWL problem, it still requires error-prone user
-intervention.  A different solution that looks at the other end of the scale
-is an approach that synthesizes word lengths for known problems as developed
-in~\cite{jha2013swati}; however, this provides neither an optimal word
-synthesis nor a comprehensive solution for the problem.  It is from this
-vacuum that we seek to explore a CEGIS approach to FWL controller synthesis.
+There is no technique in the existing literature for automatic synthesis of
+fixed-point digital controllers that considers FWL effects.  Parameter
+synthesis tools such as~\cite{cimatti2013parameter} use bounded model
+checking and fixed-point computations to compute parameters based on
+user-defined specifications, but they often operate in the continuous domain
+and have no direct means of evaluating robustness.
+
+Other tools such as~\cite{economakos2016automated} are directly aimed at
+robust stability problems, but they fail to take the effects of FWL into
+account.  In order to provide a correct-by-design digital controller,
+\cite{alur2016compositional} requires a user-defined finite-state
+abstraction to synthesize a digital controller based on high-level
+specifications.  While this approach overcomes the challenges presented by
+the FWL problem, it still requires error-prone user intervention. 
+A~different solution that uses FWL as the starting point is an approach that
+synthesizes word lengths for known control problems~\cite{jha2013swati};
+however, this provides neither an optimal result nor a comprehensive
+solution for the problem.
 

### 2016-10-16 paper/paper.tex
wordings

@@
 The first set of benchmarks uses the discrete plant of a cruise control
-model for the car accounting for rolling friction, aerodynamic drag, and
-gravitational disturbance force~\cite{Astrom08} as follows:
+model for a car, and accounts for rolling friction, aerodynamic drag, and
+the gravitational disturbance force~\cite{Astrom08}. The plant model is
+given as follows:
 %
@@
 
-A third set of benchmarks that consists of a physical plant for satellite
-applications is considered~\cite{Franklin15}, in order to evaluate the full
-capabilities of the present approach.  In particular, satellites often
-require attitude (pose) control for proper orientation of antennas and
-sensors w.r.t.~earth.  The satellite attitude control is typically used for
-three-axis attitude tracking, but here we consider one axis at a time.  The
-motion equation for the one-axis system, disregarding disturbance torques,
-is given by
+A third set of benchmarks uses a physical plant for satellite
+applications~\cite{Franklin15}.  Satellites often require attitude (pose)
+control for proper orientation of antennas and sensors w.r.t.~earth.  The
+satellite attitude control is typically used for three-axis attitude
+tracking, but here we consider only one axis at a time.  The motion equation
+for the one-axis system, disregarding disturbance torques, is given by
 %
@@
 \noindent where $I$ is the inertia moment of the satellite about its mass
-center, $\tau_{C}$ is the control torque applied by thrusters, and $\theta$
-is the controlled attitude angle.  Normalizing Eq.~\eqref{eq:satelliteode}
-by defining the control signal $u=\frac{\tau_{C}}{I}$ and taking the Laplace
-transform, the following $s$-domain transfer function $G(s)$ is obtained
+center, $\tau_{C}$ is the control torque applied by the thrusters, and
+$\theta$ is the controlled attitude angle.  Normalizing
+Eq.~\eqref{eq:satelliteode} by defining the control signal
+$u=\frac{\tau_{C}}{I}$ and taking the Laplace transform, the following
+$s$-domain transfer function $G(s)$ is obtained:
 %
@@
 \end{equation}
-
-\noindent using the ZOH discretization defined in Eq.~\eqref{eq:pulsetf}, 
-the following $z$-domain model is obtained
+%
+\noindent Using the ZOH discretization defined in Eq.~\eqref{eq:pulsetf}, 
+we get the following $z$-domain model:
 %
@@
 for the plant $G_{4}(s)$, which is typically used for evaluating stability
-margins~\cite{bhattacharyya97, keel_Bhattacharyya_examples}
+margins~\cite{bhattacharyya97, keel_Bhattacharyya_examples}:
 %
@@
 %
-\noindent where $G_{4}(z)$ is obtained using the ZOH discretization defined
+\noindent We can obtain $G_{4}(z)$ using the ZOH discretization defined
 in Eq.~\eqref{eq:pulsetf} with three different sample times ($0.1$, $0.05$,
@@
 
-\item RQ1 \textbf{(performance)} does the CEGIS approach provide a feasible
-solution in reasonable time considering robust stability of FWL digital
-controllers?
+\item RQ1 \textbf{(performance)} does the CEGIS approach generate a 
+FWL digital controller in a reasonable amount of time?
 
@@
 inductive solutions need to be refined with few counterexamples and
-fixed-point precision increases.  However, two benchmarks in our set
+increases of the fixed-point precision.  However, two benchmarks in our set
 required too many counterexamples to refine their solution (marked with $^*$
@@
 can synthesize half of the controllers in less than $5$ minutes.  Overall,
-the average synthesis time amounts to approximately $30$ minutes.  With
-respect to RQ1 we consider these times short enough to be of practical use
-to control engineers.  We further conclude that the approach
-using a two-stage verification engine is able to synthesize stable
-controllers in $12$ out of the $15$ benchmarks, and can be complemented
-using the one-stage engine for $2$ additional benchmarks, where the
-inductive conjectures fail.  Both verification engines together enabled
-controller synthesis for $14$ out of $15$ benchmarks.  For the $1$ remaining
-benchmark our approach failed to synthesize a stable controller in the
-requested time limits.  This can be addressed by either increasing the fixed
-point word widths considered or using floating point arithmetic instead. 
-The synthesized controllers were confirmed to be stable outside of our
-model representation using MATLAB, positively answering RQ2.
-A~link to the full experimental environment, including scripts to reproduce
-the results, all benchmarks and the \tool tool, is provided in the
+the average synthesis time amounts to approximately $30$ minutes.  We
+consider these times short enough to be of practical use to control
+engineers, and thus affirm RQ1.  We further observe that the approach using
+the two-stage verification engine is able to synthesize stable controllers
+in $12$ out of the $15$ benchmarks, and can be complemented using the
+one-stage engine for two additional benchmarks, where the inductive
+conjectures fail.  Both verification engines together enable controller
+synthesis for $14$ out of $15$ benchmarks.  For the one remaining benchmark
+our approach failed to synthesize a stable controller within the time
+limits.  This can be addressed by either increasing the fixed-point word
+widths considered or using floating-point arithmetic instead.  The
+synthesized controllers were confirmed to be stable outside of our model
+representation using MATLAB, positively answering RQ2.  A~link to the full
+experimental environment, including scripts to reproduce the results, all
+benchmarks and the \tool tool, is provided in the
 footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}

### 2016-10-16 paper/paper.tex
wordings

@@
 The resulting system using the typical series loop configuration, where
-$C_{q}(z)$ and $G(z)$ are in the forward path, is
-unstable.
-%
+$C_{q}(z)$ and $G(z)$ are in the forward path, is unstable. 
+Figure~\ref{fig:original} gives the Bode diagram for the digital controller
+represented by Eq.~\eqref{Eq:running-example-controller}.  The phase margin
+is negative, which means that the controller represented by
+Eq.~\eqref{Eq:running-example-controller} is unstable, considering FWL
+effects.
+
 \subsection{Program synthesis for the example}
@@
 {\sc uncertainty} and {\sc precision} in the {\sc verify} phase. 
-In particular, Figure~\ref{fig:bode} shows the Bode diagram of the illustrative example 
-using the digital controller represented by Eq.~\eqref{Eq:running-example-controller} from~\cite{DBLP:conf/hybrid/WangGRJF16} 
-(Figure~\ref{fig:original}) and the final candidate solution from our synthesizer (Figure~\ref{fig:cegiscontroller}). 
-The phase margin is negative as shown in Figure~\ref{fig:original}, which means that the controller 
-represented by Eq.~\eqref{Eq:running-example-controller} is unstable, considering FWL effects. 
-However, the final solution from \tool is stable since it presents an infinite phase margin 
-and a gain margin of $17.8$\,dB.
+Figure~\ref{fig:bode} compares the Bode diagram of the illustrative example
+using the digital controller represented by
+Eq.~\eqref{Eq:running-example-controller}
+from~\cite{DBLP:conf/hybrid/WangGRJF16} (Figure~\ref{fig:original}) and the
+final candidate solution from our synthesizer
+(Figure~\ref{fig:cegiscontroller}).  The final solution from \tool is stable
+since it presents an infinite phase margin and a gain margin of $17.8$\,dB.
 
@@
 \end{figure}
-%
-Figure~\ref{fig:step} shows the step responses of the closed-loop system 
-with the original controller represented by Eq.~\eqref{Eq:running-example-controller} (Figure~\ref{fig:step0}), 
-the first (Figure~\ref{fig:step1}) and final (Figure~\ref{fig:step2}) candidate solutions provided by \tool. 
-The step response in Figure~\ref{fig:step0} confirms the stability loss if we consider FWL effects. 
-However, Figure~\ref{fig:step1} shows that the first candidate controller is able to stabilize 
-the closed-loop system without uncertainties, but it is rejected during the {\sc precision} phase by 
-\tool since this solution is not considered to be sound. Finally, Figure~\ref{fig:step2} 
-shows a stable behavior for the final (sound) solution, which presents a lower settling time.
-%
+
+Figure~\ref{fig:step} illustrates the step responses of the closed-loop
+system with the original controller represented by
+Eq.~\eqref{Eq:running-example-controller} (Figure~\ref{fig:step0}), the
+first (Figure~\ref{fig:step1}) and final (Figure~\ref{fig:step2}) candidate
+solutions provided by \tool.  The step response in Figure~\ref{fig:step0}
+confirms the stability loss if we consider FWL effects.  However,
+Figure~\ref{fig:step1} shows that the first candidate controller is able to
+stabilize the closed-loop system without uncertainties, but it is rejected
+during the {\sc precision} phase by \tool since this solution is not
+considered to be sound.  Finally, Figure~\ref{fig:step2} shows a stable
+behavior for the final (sound) solution, which presents a lower settling
+time.
+
 \begin{figure*}

### 2016-10-16 paper/paper.tex
wordings
nudge Fig 4

@@
 \usepackage{wasysym}
+\usepackage[scaled]{helvet}
+
 %\usetikzlibrary{decorations}
@@
 \centering
-\resizebox{.8\textwidth}{!}{
+\resizebox{.9\textwidth}{!}{
  \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
@@
 },
-          row sep=.6cm, column sep=1.5cm] {
+          row sep=.6cm, column sep=2cm] {
    \coordinate (aux1);
@@
    \&;\\
-   \node[fill=gray!20] (synth) {{\sc Synthesize}};
+   \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
    \&
@@
 	minimum width=7cm,
-	minimum height=.8cm,
+	minimum height=1cm,
 	label={\sc Verify},] (verif) {};
-   \node[fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc ~Uncertainty~~~~}};
-   \node[fill=gray!20] (verif2) at ([xshift=2cm]verif.center) {{\sc ~~~~~Precision~~~}};
+     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc Uncertainty}};
+     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=2cm]verif.center) {{\sc Precision}};
    } 
@@
    \& \\
-   \node (gp) {Closed-loop System Search};
+   \node (gp) {\sf Closed-loop System Search};
    \&
@@
      \coordinate (aux);
-   \node (bmc) at ([xshift=-2cm]aux.center) {BMC-based Verifier};
-   \node (fp)  at ([xshift=2cm]aux.center) {Fixed-point \\Arithmetic Verifier};
+   \node (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based Verifier};
+   \node (fp)  at ([xshift=2cm]aux.center) {\sf Fixed-point \\\sf Arithmetic Verifier};
    }   
@@
 A third set of benchmarks uses a physical plant for satellite
-applications~\cite{Franklin15}.  Satellites often require attitude (pose)
-control for proper orientation of antennas and sensors w.r.t.~earth.  The
-satellite attitude control is typically used for three-axis attitude
-tracking, but here we consider only one axis at a time.  The motion equation
-for the one-axis system, disregarding disturbance torques, is given by
+applications~\cite{Franklin15}.  Satellites require attitude (pose) control
+for orientation of antennas and sensors w.r.t.~earth.  The satellite
+attitude control is typically used for three-axis attitude tracking, but
+here we consider only one axis at a time.  The motion equation for the
+one-axis system, disregarding disturbance torques, is given by
 %

### 2016-10-16 paper/paper.tex
nudge Fig 4

@@
 \usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
+\usetikzlibrary{patterns}
 \usepackage[justification=centering]{caption}
@@
    complexnode/.pic={ 
-     \node[rectangle,draw,dashed,
+     \node[rectangle,draw,dotted,
 	minimum width=7cm,
 	minimum height=1cm,
+        pattern=north west lines, pattern color=gray!20,
 	label={\sc Verify},] (verif) {};
@@
 }
- \caption{Counterexample-Guided Inductive Synthesis of Closed-loop System (Step~D)
+\caption{Counterexample-Guided Inductive Synthesis of Closed-loop Systems (Step~D)
 \label{fig:CEGIS}}

### 2016-10-16 paper/paper.tex
nudge Fig 4

@@
 \centering
-\resizebox{.9\textwidth}{!}{
+%\resizebox{1\textwidth}{!}
+{
  \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
@@
    \& \\
-   \node (gp) {\sf Closed-loop System Search};
+   \node[minimum height=0.5cm] (gp) {\sf Closed-loop System Search};
    \&
@@
      \coordinate (aux);
-   \node (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based Verifier};
-   \node (fp)  at ([xshift=2cm]aux.center) {\sf Fixed-point \\\sf Arithmetic Verifier};
+   \node[minimum height=0.5cm] (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based Verifier};
+   \node[minimum height=0.5cm] (fp)  at ([xshift=2cm]aux.center) {\sf Fixed-point Arithmetic Verifier};
    }   

### 2016-10-16 paper/paper.tex
nudge wording

@@
 %
-If {\sc synthesize} succeeds in finding an witness $\vec{P}$, this witness
+If {\sc synthesize} succeeds in finding a witness~$\vec{P}$, this witness
 is a candidate solution to the full synthesis formula.  We pass this
 candidate solution to {\sc verify}, which checks whether it is a full
-solution ({\it i.e.}, $\vec{P}$ satisfies the specification $\sigma(\vec{x},
+solution (i.e., $\vec{P}$ satisfies the specification $\sigma(\vec{x},
 \vec{P})$ for all $\vec{x}\in\mathcal{D}$).
@@
 worth noting that each iteration of the loop adds a new input to the
-finite set $\text{\sc inputs}$ being used for synthesis.  Given that
+finite set $\text{\sc inputs}$ that is used for synthesis.  Given that
 the full set of inputs $\mathcal{D}$

### 2016-10-16 paper/paper.tex
nudge wording

@@
 algorithms in DSVerifier that can be used for stability
-verification~\cite{daes20161,Bessa16}, one based on
-Schur's decomposition and another one based on Jury's
-criteria~\cite{astrom1997computer}.  Here, we choose Jury's
-method~\cite{astrom1997computer}, due to its efficiency.
-
-We use this method to check the stability in the $z$-domain for the
-characteristic polynomial $S(z)$ defined
-in~\eqref{eq:internal_stab_lemma}.
+verification~\cite{daes20161, Bessa16}, one based on Schur's decomposition
+and another one based on Jury's criteria~\cite{astrom1997computer}.  Here,
+we choose Jury's method~\cite{astrom1997computer}, due to its efficiency,
+and we use this method to check the stability in the $z$-domain for the
+characteristic polynomial $S(z)$ defined in~\eqref{eq:internal_stab_lemma}.
 %
@@
 %
-We consider the following form for $S(z)$:
+We~consider the following form for $S(z)$:
 %
@@
 
-\paragraph{The {\sc Synthesize} and {\sc Verify} phases}
+\subsection{The {\sc Synthesize} and {\sc Verify} phases}
+
 The {\sc synthesize} phase uses BMC to 

### 2016-10-16 paper/paper.tex
nudge wordings

@@
 The digital controllers synthesized using the algorithm we present in this
-paper are typically used in closed loops with continuous (physical)
-plants.  Thus, the proposed approach has to consider dynamics of continuous
-parts of the system (i.e., the plant) and the discrete parts (i.e., the
-digital controller).  To obtain a joint model, we fully discretize the continuous
+paper are typically used in closed loops with continuous (physical) plants. 
+Thus, the proposed approach has to consider dynamics of continuous parts of
+the system (i.e., the plant) and of discrete parts (i.e., the digital
+controller).  To obtain a joint model, we fully discretize the continuous
 plant.  We briefly recall the standard foundations of this step.
@@
 
-Amongst the several discretization methods available in the
+Among the discretization methods available in the
 literature~\cite{Franklin15}, the zero-order hold (ZOH) discretization is
-considered to be suitable for representing the sample and hold processes that are
-typically employed in complex systems~\cite{istepanian2012digital}. 
-The ZOH discretization models the exact effect of sampling and DAC interpolation over the plant.
+considered suitable for representing the sample and hold processes that are
+typically employed in complex systems~\cite{istepanian2012digital}.  The ZOH
+discretization models the exact effect of sampling and DAC interpolation
+over the plant.
 
@@
 Given a synchronized ZOH input and sample and hold output on the plant with
-a sample time $T$ satisfying Nyquist criterion, the discrete pulse
+a sample time $T$ satisfying the Nyquist criterion, the discrete pulse
 transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$
@@
 %
+\end{mylemma}
+%
 For the sake of brevity, we will use the notation $G(z)$ to represent the
 pulse transfer function.
-%
-\end{mylemma}
 
@@
 $\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$
-operations, 
-and it includes the ZOH dynamics in the $(1-z^{-1})$ term, 
-which is sufficient for stability studies over $G(s)$.
+operations, and it includes the ZOH dynamics in the $(1-z^{-1})$ term, which
+is sufficient for stability studies over $G(s)$.
 
@@
 \noindent where $\vec{\beta}$ and $\vec{\alpha}$ are vectors containing the
-controller's coefficients; similarly $\vec{b}$ and $\vec{a}$ encompass the
-plant's coefficients; and $N_{(\cdot)}$ and $M_{(\cdot)}$ indicate the order of the polynomial of the corresponding block.
-
-Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$
-(\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$ which come from tolerances/imprecision in the original model), errors in the numeric
-calculations, or roundoffs in the quantization.  These uncertainties are 
-parametrically expressed by additive terms, resulting in a uncertain model
-$\hat{G}(z)$, such that:
+controller's coefficients; similarly, $\vec{b}$ and $\vec{a}$ denote the
+plant's coefficients; and $N_{(\cdot)}$ and $M_{(\cdot)}$ indicate the order
+of the polynomial of the corresponding block.
+
+Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (i.e.,
+$\Delta_p{G}_n(s),\Delta_p{G}_d(s)$, which arise from tolerances/imprecision
+in the original model), errors in the numeric calculations, or roundoffs in
+the quantization.  These uncertainties are parametrically expressed by
+additive terms, resulting in an uncertain model $\hat{G}(z)$, such that:
 %
@@
 that the parametric errors in the plant have the same polynomial order as
-the plant itself (all other errors described in this paper are ensured to fulfill this property in our
-implementation).
+the plant itself (all other errors described in this paper are ensured to
+fulfill this property in our implementation).
 
@@
 %
-we write $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$.   
-In the following we will either represent the functions $G(z)$, $C(z)$, 
-or work over their respective coefficients $\vec{G}, \vec{C}$ in vector form.
+we write $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$.  In the following we will
+either use the functions $G(z)$, $C(z)$ directly, or work over their
+respective coefficients $\vec{G}$, $\vec{C}$ in vector form.
 
@@
 %
-In Figure~\ref{fig:digsystem1}, two sources of uncertainty are
-illustrated: parametric uncertainties related to modeling errors, and
-uncertainties introduced by quantizations in sampling and holding process,
-i.e., ADC and DAC conversions.  Assuming linearity and independence between
-these sources, the uncertain model may be rewritten as a vector of coefficients in the z-domain using equations \ref{eq:coefficients} and \ref{eq:delta_coefficients}
+In Figure~\ref{fig:digsystem1}, two sources of uncertainty are illustrated:
+parametric uncertainties related to modeling errors, and uncertainties
+introduced by quantizations in sampling and holding process, i.e., ADC and
+DAC conversions.  Assuming linearity and independence between these sources,
+the uncertain model may be rewritten as a vector of coefficients in the
+z-domain using equations (\ref{eq:coefficients}) and
+(\ref{eq:delta_coefficients})
 %
@@
 
-It is known that a discrete-time linear system is said to be Bounded-Input and Bounded-Output
+A discrete-time linear system is said to be Bounded-Input and Bounded-Output
 (BIBO) stable if and only if every pole of its transfer function lies inside
-the unit circle \cite{Astrom08}.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following
-proposition states necessary conditions for BIBO stability of the closed-loop system
-in Figure~\ref{fig:sampledsystem}, since the exogenous signals $R(z)$,
-$\nu_{1}$, and $\nu_{2}$ are bounded.
-
-\begin{myprop}{\cite{Bessa16,fadali}}
+the unit circle \cite{Astrom08}.  Analyzing Eq.~\eqref{eq:outputfunctions},
+the following proposition gives necessary conditions for BIBO stability of
+the closed-loop system in Figure~\ref{fig:sampledsystem}, since the
+exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$ are bounded.
+
+\begin{myprop}{\cite{fadali,Bessa16}}
 \label{prop:eq_int_stab} 
@@
 
-Proposition~\ref{prop:eq_int_stab} provides the necessary conditions for the digital controller to stabilize the closed loop system, 
-considering plant parametric uncertainties (i.e., $\Delta_p \vec{G}$),
-quantization noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in the control
-software.  
-Notice that the model for plant uncertainty due to quantization noise (i.e., $\Delta_q \vec{G}$) may be disregarded if the conditions on
-Proposition~\ref{prop:eq_int_stab} are satisfied and if the quantization noise is
-bounded.  The boundedness of the quantization noise comes from Assumption~\ref{whitenoise}.
+Proposition~\ref{prop:eq_int_stab} provides the necessary conditions for the
+digital controller to stabilize the closed-loop system, considering plant
+parametric uncertainties (i.e., $\Delta_p \vec{G}$), quantization noises
+($\nu_{1}$ and $\nu_{2}$) and FWL effects in the control software.  Notice
+that the model for plant uncertainty due to quantization noise (i.e.,
+$\Delta_q \vec{G}$) may be disregarded if the conditions on
+Proposition~\ref{prop:eq_int_stab} are satisfied and if the quantization
+noise is bounded.  The boundedness of the quantization noise comes from
+Assumption~\ref{whitenoise}.
 
@@
 
-Given a model for a plant for which to synthesize a controller, provided in
-an ANSI-C input file (Steps 1--3), \tool constructs a non-deterministic
-model to represent the plant family (Step~A), and formulates a function
-(Step~B) using implementation details provided in Steps~$2$ and $3$ to
-calculate the parameters of the controller to be synthesized (Step~C). 
-Finally, \tool builds an intermediate ANSI-C code for the digital system
-implementation, which is used as input for the CEGIS engine (Step~D).
+Given a model for a plant in ANSI-C syntax as input (Steps 1--3), \tool
+constructs a non-deterministic model to represent the plant family (Step~A),
+and formulates a function (Step~B) using implementation details provided in
+Steps~$2$ and $3$ to calculate the parameters of the controller to be
+synthesized (Step~C).  Finally, \tool builds an intermediate ANSI-C code for
+the digital system implementation, which is used as input for the CEGIS
+engine (Step~D).
 
@@
 CBMC~\cite{ClarkeKL04}, where the controller is marked as the input variable
-to synthesize.  The properties specified in the ANSI-C code model can only
-be satisfied if CEGIS synthesizes controller coefficients that
-satisfy~$\phi$.  CEGIS employs an iterative, counterexample-guided
-refinement process which is explained in detail in
-Section~\ref{synthesizer-general}.  A~successful synthesis result is
-reported if CEGIS generates a controller that is safe with respect to~$\phi$. 
-In particular, the ANSI-C code model guarantees that a synthesized solution
-is complete and sound with respect to the stability property~$\phi$, since it
-does not depend on system inputs and outputs.  In the case of stability, the
-specification~$\phi$ consists in a number of assumptions on the polynomial
-coefficients, following Jury's Criteria, as well as the restrictions set in
-the representation of these coefficients as discussed in more detail in 
-Section~\ref{synthesis-elements}.
+to synthesize.  CEGIS employs an iterative, counterexample-guided refinement
+process, which is explained in detail in Section~\ref{synthesizer-general}. 
+CEGIS reports a successful synthesis result if it generates a controller
+that is safe with respect to~$\phi$.  In particular, the ANSI-C code model
+guarantees that a synthesized solution is complete and sound with respect to
+the stability property~$\phi$, since it does not depend on system inputs and
+outputs.  In the case of stability, the specification~$\phi$ consists of a
+number of assumptions on the polynomial coefficients, following Jury's
+Criteria, as well as the restrictions on the representation of these
+coefficients as discussed in detail in Section~\ref{synthesis-elements}.
 
@@
 
-The program synthesis engine uses fixed-point arithmetic.  Namely, we use
-the domain $\mathbb{R}\param{I}{F}$ for the controller's coefficients and
-the domain $\mathbb{R}\param{I_p}{F_p}$ for the plant's coefficients, 
-where $I$ and $F$, as well as $I_p$ and $F_p$, denote the integer and
-fractional size, respectively, and $\mathbb{R}\langle I_p,F_p \rangle
-\supseteq \mathbb{R}\langle I,F \rangle$.
+The program synthesis engine uses fixed-point arithmetic.  Specifically, we
+use the domain $\mathbb{R}\param{I}{F}$ for the controller's coefficients
+and the domain $\mathbb{R}\param{I_p}{F_p}$ for the plant's coefficients,
+where $I$ and $F$, as well as $I_p$ and $F_p$, denote the number of bits for
+the integer and fractional parts, respectively, and $\mathbb{R}\langle
+I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
 %
@@
 therefore designed a second approach, which we describe below.
-Our experimental results described in Section~\ref{sec:experiments}, 
+Our experimental results described in Section~\ref{sec:experiments}
 %try both approaches and provide the time for the fastest. 
@@
 fixed-point operations assuming a plant precision \param{I_p}{F_p}, and the
-second stage restores soundness by validating these operations
-using interval arithmetic on the synthesized controller.
+second stage restores soundness by validating these operations using
+interval arithmetic on the synthesized controller.
 %
@@
 %
-In more detail, in the first stage, denoted by {\sc Uncertainty} in Figure~\ref{fig:CEGIS}, 
-assuming a precision \param{I_p}{F_p} 
-we check whether the system is unstable for the current candidate solution,
-{\it i.e.}, if $\neg \phi_\mathit{stability}$ is satisfiable for $S(z)$.
-If this is the case, then we obtain a counterexample 
-$\tilde G(z)$, 
+In more detail, in the first stage, denoted by {\sc Uncertainty} in
+Figure~\ref{fig:CEGIS}, assuming a precision \param{I_p}{F_p} we check
+whether the system is unstable for the current candidate solution, i.e., if
+$\neg \phi_\mathit{stability}$ is satisfiable for $S(z)$.  If this is the
+case, then we obtain a counterexample $\tilde G(z)$,
+%
 %denoted by values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
 %\red{[see my comment above - these quantities pop up too abruptly.]},
-which makes the closed-loop system unstable. 
-This uncertainty is added to 
-the set {\sc inputs} such that, in the subsequent {\sc synthesize} phase, 
-we obtain a candidate solution consisting 
-of a controller $C(z)$, which makes the closed-loop 
-system stable for all the uncertainties accumulated in {\sc inputs}.
+%
+which makes the closed-loop system unstable.  This uncertainty is added to
+the set {\sc inputs} such that, in the subsequent {\sc synthesize} phase, we
+obtain a candidate solution consisting of a controller $C(z)$, which makes
+the closed-loop system stable for all the uncertainties accumulated in {\sc
+inputs}.
 
@@
 
-We will illustrate our approach with a classical cruise control example,
-extracted from the literature~\cite{Astrom08}.  The example will allow us to
-highlight the challenges that arise when using finite precision arithmetic
-in digital control.  We are given a discrete plant model (with a time step
-of $0.2$\,s), which is represented by the following $z$-expression:
+We illustrate our approach with a classical cruise control example,
+extracted from the literature~\cite{Astrom08}.  The example highlights the
+challenges that arise when using finite-precision arithmetic in digital
+control.  We are given a discrete plant model (with a time step of
+$0.2$\,s), which is represented by the following $z$-expression:
 %
@@
 closed-loop system for the discrete plant model $G(z)$
-(Eq.~\ref{Eq:running-example-plant}).  However, if the effects of finite
-precision arithmetic are considered during verification (e.g., fixed-point
-arithmetic and word-length), then this closed-loop system becomes unstable.
+(Eq.~\ref{Eq:running-example-plant}).  However, if the effects of
+finite-precision arithmetic are considered during verification (e.g.,
+fixed-point arithmetic and word-length), then this closed-loop system
+becomes unstable.
 %
@@
 This section is split into three parts. Section~\ref{experimental-setup}
-discusses the experimental setup and the employed benchmarks, while
+discusses the experimental setup and our benchmarks, while
 Section~\ref{experimental-objectives} describes the experimental objectives. 
-Section~\ref{experimental-results} describes the experimental results
-related to the application of CEGIS to the standard closed-loop control
-system benchmarks described in Section~\ref{experimental-setup}.
+Section~\ref{experimental-results} presents the experimental results
+obtained on the benchmarks with our tool \tool.
 
@@
 
-Using the closed-loop control system benchmarks described in
+Using the closed-loop control system benchmarks given in
 Section~\ref{experimental-setup}, our experimental evaluation aims to answer
@@
 
-\item RQ1 \textbf{(performance)} does the CEGIS approach generate a 
+\item[RQ1] \textbf{(performance)} does the CEGIS approach generate a 
 FWL digital controller in a reasonable amount of time?
 
-\item RQ2 \textbf{(sanity check)} are the synthesized controllers sound
+\item[RQ2] \textbf{(sanity check)} are the synthesized controllers sound
 and can their stability be confirmed outside of our model?

### 2016-11-09 cav2017/cav2017.tex
import initial CAV 2017 paper

%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

\usepackage{url}
%\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
%\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
%\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Automated Synthesis of State-Space Digital Controllers}

% a short form should be given in case it is too long for the running head
%\titlerunning{Lecture Notes in Computer Science: Authors' Instructions}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
%\author{Alfred Hofmann%
%\thanks{Please note that the LNCS Editorial assumes that all authors have used
%the western naming convention, with given names preceding surnames. This determines
%the structure of the names in the running heads and the author index.}%
%\and Ursula Barth\and Ingrid Haas\and Frank Holzwarth\and\\
%Anna Kramer\and Leonie Kunz\and Christine Rei\ss\and\\
%Nicole Sator\and Erika Siebert-Cole\and Peter Stra\ss er}
%
%\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
%\institute{Springer-Verlag, Computer Science Editorial,\\
%Tiergartenstr. 17, 69121 Heidelberg, Germany\\
%\mailsa\\
%\mailsb\\
%\mailsc\\
%\url{http://www.springer.com/lncs}}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

%\toctitle{Lecture Notes in Computer Science}
%\tocauthor{Authors' Instructions}
\maketitle

\begin{abstract}
The abstract should summarize the contents of the paper and should
contain at least 70 and at most 150 words. It should be written using the
\emph{abstract} environment.
\keywords{We would like to encourage you to list your keywords within
the abstract section}
\end{abstract}

%-------------------------------
\section{Introduction}
%-------------------------------

\begin{thebibliography}{4}

\bibitem{jour} Smith, T.F., Waterman, M.S.: Identification of Common Molecular
Subsequences. J. Mol. Biol. 147, 195--197 (1981)

\end{thebibliography}

\end{document}

### 2016-11-10 paper/paper.tex
microtype
line break

@@
 \usepackage{mathtools}
+\usepackage{microtype}
 
@@
 the plant exhibits continuous behavior whereas the controller operates in
-discrete time and over a quantized domain.  Inspired by a classical approach
-\cite{astrom1997computer}, we translate the problem into a single digital
-domain.  Given our primary interest in stability despite digitization
-effects, we have modeled a digital equivalent of the plant by evaluating the
-effects of the quantizers (A/D and D/A converters) as time discretization
-elements with quantization noise.  The resulting closed-loop system is a
-program loop that operates on bit-vectors encoded using fixed-point
-arithmetic with finite word length (FWL).  The deterministic effects of the
-FWL and quantization errors are incorporated into the model as an additive
-uncertainty, which is taken into account during the CEGIS-based synthesis of
-the control software for the plant.
+discrete time and over a quantized domain.  Inspired by a classical
+approach~\cite{astrom1997computer}, we translate the problem into a single
+digital domain.  Given our primary interest in stability despite
+digitization effects, we have modeled a digital equivalent of the plant by
+evaluating the effects of the quantizers (A/D and D/A converters) as time
+discretization elements with quantization noise.  The resulting closed-loop
+system is a program loop that operates on bit-vectors encoded using
+fixed-point arithmetic with finite word length (FWL).  The deterministic
+effects of the FWL and quantization errors are incorporated into the model
+as an additive uncertainty, which is taken into account during the
+CEGIS-based synthesis of the control software for the plant.
 
@@
 through symbolic execution.  In order to account for rounding errors, an
-upper bound is introduced in the verification phase.  If the error of the
+upper bound is introduced in the verification phase.  If~the error of the
 implementation is lower than this tolerance level, then the verification is

### 2016-11-16 cav2017/cav2017.tex
generalised CEGIS + related work on CEGIS

@@
 \usepackage{graphicx}
+\usepackage{tikz}
+\usepackage{framed}
+\usepackage{listings}
+
+\usetikzlibrary{positioning, arrows, automata, shapes}
+
+\newcommand{\todo}[1]{{\color{red} TODO: #1}}
 
@@
 
-\begin{thebibliography}{4}
+\section{Counter-Example Guided Inductive Synthesis with solution generalisation}
 
-\bibitem{jour} Smith, T.F., Waterman, M.S.: Identification of Common Molecular
-Subsequences. J. Mol. Biol. 147, 195--197 (1981)
+\begin{figure}
+\centering
+\hspace*{-1cm}
+\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
+},
+          row sep=1cm, column sep=1.5cm] {
+   \coordinate (aux1);
+   \& \coordinate (aux2);
+   \& ;\\
+   \node[fill=yellow!20,align=center] (synth) {{\sc inductive}\\{\sc generalisation}};
+   \&
+   complexnode/.pic={ 
+     \node[rectangle,draw,dashed,
+	minimum width=7cm,
+	minimum height=.8cm,
+	label={\sc Validation oracles},] (verif) {};
+   \node[fill=yellow!20] (verif1) at ([xshift=-2.1cm]verif.center) {{\sc Validate}};
+   \node[fill=yellow!20,align=center] (verif2) at ([xshift=1.9cm]verif.center) {{\sc validate general}};
+   } 
+   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
+   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
+   %% \&
+   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
+   \& \\
+   \& \\
+   \node (gp) {Program Search};
+   \&
+   complexnode/.pic={ 
+     \coordinate (aux);
+   \node (bmc) at ([xshift=-2.1cm]aux.center) {SAT/SMT Solver};
+   \node (fp)  at ([xshift=1.9cm]aux.center) {SAT/SMT Solver};
+   }   
+    \\
+  };
 
-\end{thebibliography}
+   \path
+    ([yshift=2em]synth.east) edge node[xshift=-0.7em] {Candidate} ([yshift=2em]verif1.west)
+    ([yshift=-2em]verif1.west) edge node[xshift=-0.7em] {New input} ([yshift=-2em]synth.east)
+    (verif1) edge node {Generalise} (verif2)
+    ([xshift=5em]verif1.south) edge node[align=center] {Candidate} ([xshift=5em]bmc.north)
+    ([xshift=5em]verif2.south) edge node[align=center] {Candidate} ([xshift=5em]fp.north)
+    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif1.south)
+    ([xshift=-5em]fp.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif2.south)
+    (verif2) edge node {} (done)
+    ([xshift=5em]synth.south) edge node[align=center] {{\sc Inputs}} ([xshift=5em]gp.north)
+    ([xshift=-5em]gp.north) edge node[align=center] {No solution/\\Candidate} ([xshift=-5em]synth.south)
+    (aux1) edge (synth.north);
+   \path[-]
+   (verif2.north) edge node[align=center] {} ([xshift=6.5cm]aux2)
+   ([xshift=6.5cm]aux2) edge node[align=center] {Increase parameters} (aux1);
+
+\end{tikzpicture}
+\caption{The CEGIS loop with solution generalisation\label{fig:CEGIS-multiple-verif}}
+\end{figure}
+
+\section{Related works}
+
+\paragraph{CEGIS}
+
+Program synthesis is the problem of computing correct-by-design programs
+from high-level specifications, and algorithms for this problem have made
+substantial progress in recent years.  One such
+approach~\cite{itzhaky2010simple} inductively synthesizes invariants to
+generate the desired programs.
+
+Program synthesisers are an ideal fit for synthesis of parametric
+controllers since the semantics of programs capture effects such as FWL
+precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
+for the synthesis of switching controllers for stabilizing continuous-time
+plants with polynomial dynamics.  The work extends to its application on
+affine systems, finding its major challenge in the hardness of solving
+linear arithmetic with the state-of-the-art SMT solvers.  Since this
+approach uses switching states instead of linear dynamics in the digital
+controller, it entirely circumvents the FWL problem.  It is also not
+suitable for the kind of control we seek to synthesize.  We require a
+combination of a synthesis engine with a control verification tool that
+addresses the challenges presented here in the form of FWL effects and
+stability measures for LTI SISO controllers.  We take the former
+from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from~\cite{daes20161}
+while enhancing the procedure by evaluating the quantization effects of the
+Hardware interfaces (ADC/DAC) to obtain an accurate discrete-time FWL
+representation of the continuous dynamics.
+
+\bibliographystyle{abbrv}
+\bibliography{paper}  
+%\begin{thebibliography}{4}
+%\end{thebibliography}
 

### 2016-11-16 cav2017/cav2017.tex
more on solution generalisation

@@
 %-------------------------------
+In this paper we formalise the notion of solution generalisation for CEGIS. 
+This technique allows the inductive generalisation engine to look for 
+candidate solutions in a reduced solution space.
 
 \section{Counter-Example Guided Inductive Synthesis with solution generalisation}
+
+This technique relies on parametrising the target language, which
+induces a lattice of progressively more expressive languages.  We
+start by attempting to synthesise a program at the lowest point on
+this lattice and increase the parameters of the language until we
+reach a point at which the synthesis succeeds. As well as giving us an
+automatic search procedure, this parametrisation greatly increases the
+efficiency of our system since languages low down the lattice are very
+easy to decide safety for (i.e. the validation oracle finds an answer
+fast). If a program can be synthesised in a low-complexity language,
+the whole procedure finishes much faster than if synthesis had been
+attempted in a high-complexity language.
 

### 2016-11-17 cav2017/cav2017.tex
G(S) -> G(Z)

@@
 \usepackage{amssymb}
+\usepackage{amsmath}
 \setcounter{tocdepth}{3}
@@
 
+\section{Discretising Continuous Space Dynamics}
+
+A dynamical system is a system in which a function describes the progression of a state over time. 
+In a continuous domain with linear dynamics, it is described by a first order Ordinary Differential Equation (ODE).
+\begin{equation}
+\dot{x}(t)=\vec{A}\vec{x}(t)+\vec{B}\vec{u}(t) +\vec{w}(t)
+\label{eq:dynamical}
+\end{equation}
+
+Where $\vec{w}$  is a continuous zero-mean white noise source with covariance $N ( 0 , Q )$
+Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
+which may restricts the observability of the statespace from the output space.
+\begin{equation}
+\vec{y}(t)=\vec{C}\vec{x}(t)+\vec{D}\vec{u}(t)
+\end{equation}
+
+Discretization of an continuous dynamical system turns the ODE into a difference equation, assuming zero-order hold
+for the input $\vec{u}$ and continuous integration for the noise $\vec{w}$, to
+\begin{align}
+\label{eq:discretization}
+\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d\vec{u}_k + \vec{w}_k\\
+y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k 
+\end{align}
+with covariance for $\vec{w}_k$, $N ( 0 , Q_d )$
+where
+\begin{align}
+\label{eq:discretize}
+\vec{A}_d &= e^{\vec{A} T_s} = \mathcal{L}^{-1} { ( s \vec{I} - \vec{A} )^{-1} }_{t = T_s}\\
+\vec{B}_d &= \int_{t = 0}^{T_s} e^{\vec{A} t} dt\ \vec{B} = \vec{A}^{-1} ( \vec{A}_d - \vec{I} ) \vec{B}\\
+\vec{C}_d &= \vec{C}\\
+\vec{D}_d &= \vec{D} \\
+Q_d &= \int_{t = 0}^{T_s} e^{\vec{A} t} Q e^{\vec{A}^T t} dt
+\end{align}
+and $T_s$ is the sample time. Then
+\begin{align*}
+x(kT)=x_k \wedge y(kT) = y_k, \forall k
+\end{align*}
+Similarly, we can now state that the Z-transform of the discrete-time equation g(k) and the Laplace transform of the continuous time
+equation g(t) are related.
+$$g(t) \rightarrow g(k) \Leftrightarrow G(S)=\mathcal{L}(g(t)) \rightarrow G(Z)=\mathcal{Z}(g(k))$$
+where the poles $\hat{\lambda}_i=e^{-\lambda_iT} : \hat{\lambda}_i \in G(Z) \wedge \lambda_i \in G(S)$ are derived from \eqref{eq:discretize}.
+Two remarks are worth mentioning regarding the above.
+\begin{remark} 
+The above statement is only valid if the sampling frequency is above the Nyquist criteria, since aliasing could cause 'phantom poles' to appear otherwise. 
+\end{remark}
+\begin{remark}
+The witnessed maximum amplitude of the discrete signals $x_k,y_k$ may be smaller to that of $x(t),y(t)$ due to synchronism at fraction-frequency sampling.
+This means that reasoning about the statespace must consider the effects of this possibility as well of the case of maximal inputs from the continuous specification.
+\end{remark}
+Since \eqref{eq:discretization} is a bisimulation of \eqref{eq:dynamical}, we may use the semantics in section \ref{sec:model_semantics} 
+to model continuous dynamical systems.
+
 \section{Related works}

### 2016-11-19 cav2017/cav2017.tex
LTI model
Comments

@@
 \newcommand{\todo}[1]{{\color{red} TODO: #1}}
+\newcommand{\commentib}[1]{{\color{blue} [IB: #1]}}
 
@@
 
-Where $\vec{w}$  is a continuous zero-mean white noise source with covariance $N ( 0 , Q )$
+Where \textcolor{red}{$\vec{w}$  is a continuous zero-mean white noise source with covariance $N ( 0 , Q )$} \commentib{$N(0,Q)$ is the notation for PDF (specifically a normal zero mean PDF with Q variance) and it is not a notation for covariance.
+All the above expression may be rewritten with "$\vec{w} \sim \mathcal{N}(0,Q)$"}.
 Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
@@
 with covariance for $\vec{w}_k$, $N ( 0 , Q_d )$
-where
+where \commentib{Are the second parts of equations (5) and (6) really nedded?}
 \begin{align}
@@
 \vec{A}_d &= e^{\vec{A} T_s} = \mathcal{L}^{-1} { ( s \vec{I} - \vec{A} )^{-1} }_{t = T_s}\\
-\vec{B}_d &= \int_{t = 0}^{T_s} e^{\vec{A} t} dt\ \vec{B} = \vec{A}^{-1} ( \vec{A}_d - \vec{I} ) \vec{B}\\
+\vec{B}_d &= \int_{0}^{T_s} e^{\vec{A} t} dt\ \vec{B} = \vec{A}^{-1} ( \vec{A}_d - \vec{I} ) \vec{B}\\
 \vec{C}_d &= \vec{C}\\
 \vec{D}_d &= \vec{D} \\
-Q_d &= \int_{t = 0}^{T_s} e^{\vec{A} t} Q e^{\vec{A}^T t} dt
+Q_d &= \int_{0}^{T_s} e^{\vec{A} t} Q e^{\vec{A}^T t} dt
 \end{align}
@@
 equation g(t) are related.
-$$g(t) \rightarrow g(k) \Leftrightarrow G(S)=\mathcal{L}(g(t)) \rightarrow G(Z)=\mathcal{Z}(g(k))$$
-where the poles $\hat{\lambda}_i=e^{-\lambda_iT} : \hat{\lambda}_i \in G(Z) \wedge \lambda_i \in G(S)$ are derived from \eqref{eq:discretize}.
+$$g(t) \rightarrow g(k) \Leftrightarrow G(S)=\mathcal{L}(g(t)) \rightarrow G(Z)=\mathcal{Z}(g(k))$$ \commentib{The notation is wrong. There is no implications ($\rightarrow$) between functions.}
+where the poles $\hat{\lambda}_i=e^{-\lambda_iT} : \hat{\lambda}_i \in G(Z) \wedge \lambda_i \in G(S)$ \commentib{This notation is wrong.
+G(s) (lowercase 's' and not S) is a function in the complex frequency domain, it is not a set.
+Consequently, the set membership notation $\in$ cannot be employed.
+} are derived from \eqref{eq:discretize}.
 Two remarks are worth mentioning regarding the above.
@@
 to model continuous dynamical systems.
+
+\section{LTI representations of ARMAX models}
+
+Let us have a discrete time SISO system with an $n^{th},m{^th} : n\geq m$ order armax model
+$$y[k]=\sum_{i=1}^n a_iy[k-i]+\sum_{i=0}^m b_iu[k-i]$$ \commentib{It is not an armax model.
+There is not a moving average noise component.
+It is an ARX, there are only autoregressive and exogenous terms.}
+where $y$ is the output of the system and $u$ its input.
+The equivalent LTI dynamics of such a model are:
+\begin{align}
+\vec{x}_k=&\vec{A}\vec{x}_{k-1}+\vec{B}u_k : \vec{x}_k=[y_{k-n}\ \hdots y_{k-1}\ y_{k}]^T\\
+y_k=&\vec{C}\vec{x}_k + b_0u_k\nonumber\\
+\vec{A}=&\left[
+\begin{array}{ccccc}
+0&1&0&\cdots&0\\
+0&0&1&\cdots&0\\
+\vdots&\vdots&\vdots&\ddots&\vdots\\
+0&0&0&\cdots&1\\
+-a_n&-a_{n-1}&-a_{n-2}&\cdots&-a_1
+\end{array}\right],
+\vec{B}=\left[
+\begin{array}{c}
+0\\0\\ \vdots\\ 0\\ 1
+\end{array}\right]\nonumber\\
+\vec{C}=&[b_n-a_nb_0\ b_{n-1}-a_{n-1}b_0 \cdots b_1-a_1b_0] : b_{i \in (m\ n]}=0\nonumber
+\end{align}
 

### 2016-11-19 cav2017/cav2017.tex
comments

@@
 equation g(t) are related.
-$$g(t) \rightarrow g(k) \Leftrightarrow G(S)=\mathcal{L}(g(t)) \rightarrow G(Z)=\mathcal{Z}(g(k))$$ \commentib{The notation is wrong. There is no implications ($\rightarrow$) between functions.}
+$$g(t) \rightarrow g(k) \Leftrightarrow G(S)=\mathcal{L}(g(t)) \rightarrow G(Z)=\mathcal{Z}(g(k))$$ \commentib{The notation is wrong.
+There is no implications ($\rightarrow$) between functions.
+The discretization process is not a transition system.
+And this symbol is employed for transformation, but in respect to the domain and counterdomain.}
 where the poles $\hat{\lambda}_i=e^{-\lambda_iT} : \hat{\lambda}_i \in G(Z) \wedge \lambda_i \in G(S)$ \commentib{This notation is wrong.
@@
 Consequently, the set membership notation $\in$ cannot be employed.
+It is valid for G(z) too.
 } are derived from \eqref{eq:discretize}.

### 2016-11-20 cav2017/cav2017.tex
Notation clean-up based on Iury's comments

--- 2016-11-17 cav2017/cav2017.tex
@@
 
-Where $\vec{w}$  is a continuous zero-mean white noise source with covariance $N ( 0 , Q )$
+with $\vec{w} \sim \mathcal{N}(0,Q)$\\
 Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
@@
 \end{align}
-with covariance for $\vec{w}_k$, $N ( 0 , Q_d )$
+with covariance for $\vec{w}_k \sim \mathcal{N}(0,Q_d)$
 where
@@
 \end{align*}
-Similarly, we can now state that the Z-transform of the discrete-time equation g(k) and the Laplace transform of the continuous time
-equation g(t) are related.
-$$g(t) \rightarrow g(k) \Leftrightarrow G(S)=\mathcal{L}(g(t)) \rightarrow G(Z)=\mathcal{Z}(g(k))$$
-where the poles $\hat{\lambda}_i=e^{-\lambda_iT} : \hat{\lambda}_i \in G(Z) \wedge \lambda_i \in G(S)$ are derived from \eqref{eq:discretize}.
-Two remarks are worth mentioning regarding the above.
-\begin{remark} 
-The above statement is only valid if the sampling frequency is above the Nyquist criteria, since aliasing could cause 'phantom poles' to appear otherwise. 
-\end{remark}
+Let $g_d(k)=\mathcal{G}(t,g(t),T)$ be a function that performs the discretization described above, where $g(t)$
+represents the continuous dynamics and $g_d(k)$ the corresponding discrete dynamics. 
+Let $G(s)=\mathcal{L}(g(t))$ and $G_d(z)=\mathcal{Z}(g_(k))$ be the corresponding Laplace and Z-transforms
+of $g(t)$ and $g_d(k)$. Given this relation, we have 
+$$G_d(z)=G(z)|_{z=e^{sT}} : g_d(k)=\mathcal{G}(t,g(t),T) \wedge T < \frac{1}{.5f_s}$$
+Where $.5f_s$ is the Nyquist frequency of $g(t)$. This last restriction is introduced to avoid the effects of aliasing
+which could cause 'phantom poles' to appear otherwise. 
+The eigenvalues of $\vec{A}_d$ corresponding to the poles of $G_d(z)$, and those of $\vec{A}$ corresponding to the poles of $G(s)$ are similarly related.
+$\hat{\lambda}_i=e^{-\lambda_iT} : \hat{\lambda}_i \in \sigma(\vec{A}_d) \wedge \lambda_i \in \sigma(\vec{A})$
+where $\sigma{\cdot}$ is the spectrum of a matrix.
+The following remark is worth mentioning regarding the above.
 \begin{remark}
@@
 to model continuous dynamical systems.
+
+\section{LTI representations of ARMA models}
+
+Let us have a discrete time SISO system with an $n^{th},m{^th} : n\geq m$ order armax model
+$$y[k]=\sum_{i=1}^n a_iy[k-i]+\sum_{i=0}^m b_iu[k-i]$$
+where $y$ is the output of the system and $u$ its input.
+The equivalent LTI dynamics of such a model are:
+\begin{align}
+\vec{x}_k=&\vec{A}\vec{x}_{k-1}+\vec{B}u_k : \vec{x}_k=[y_{k-n}\ \hdots y_{k-1}\ y_{k}]^T\\
+y_k=&\vec{C}\vec{x}_k + b_0u_k\nonumber\\
+\vec{A}=&\left[
+\begin{array}{ccccc}
+0&1&0&\cdots&0\\
+0&0&1&\cdots&0\\
+\vdots&\vdots&\vdots&\ddots&\vdots\\
+0&0&0&\cdots&1\\
+-a_n&-a_{n-1}&-a_{n-2}&\cdots&-a_1
+\end{array}\right],
+\vec{B}=\left[
+\begin{array}{c}
+0\\0\\ \vdots\\ 0\\ 1
+\end{array}\right]\nonumber\\
+\vec{C}=&[b_n-a_nb_0\ b_{n-1}-a_{n-1}b_0 \cdots b_1-a_1b_0] : b_{i \in (m\ n]}=0\nonumber
+\end{align}
 

### 2016-11-20 cav2017/cav2017.tex
typos

@@
 represents the continuous dynamics and $g_d(k)$ the corresponding discrete dynamics. 
-Let $G(s)=\mathcal{L}(g(t))$ and $G_d(z)=\mathcal{Z}(g_(k))$ be the corresponding Laplace and Z-transforms
+Let $G(s)=\mathcal{L}(g(t))$ and $G_d(z)=\mathcal{Z}(g_d(k))$ be the corresponding Laplace and Z-transforms
 of $g(t)$ and $g_d(k)$. Given this relation, we have 
@@
 $\hat{\lambda}_i=e^{-\lambda_iT} : \hat{\lambda}_i \in \sigma(\vec{A}_d) \wedge \lambda_i \in \sigma(\vec{A})$
-where $\sigma{\cdot}$ is the spectrum of a matrix.
+where $\sigma(\cdot)$ is the spectrum of a matrix.
 The following remark is worth mentioning regarding the above.

### 2016-11-21 cav2017/cav2017.tex
add comments to Cristina

@@
 
+\textcolor{red}{LC: Cristina, may I ask you to expand further this section by connecting it to our control-synthesis work?}
 \begin{figure}
@@
 
-with $\vec{w} \sim \mathcal{N}(0,Q)$\\
+\noindent with $\vec{w} \sim \mathcal{N}(0,Q)$.\\
 Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
-which may restricts the observability of the statespace from the output space.
+which may restricts the observability of the state-space from the output space.
 \begin{equation}
@@
 The witnessed maximum amplitude of the discrete signals $x_k,y_k$ may be smaller to that of $x(t),y(t)$ due to synchronism at fraction-frequency sampling.
-This means that reasoning about the statespace must consider the effects of this possibility as well of the case of maximal inputs from the continuous specification.
+This means that reasoning about the state-space must consider the effects of this possibility as well of the case of maximal inputs from the continuous specification.
 \end{remark}

### 2016-11-21 cav2017/cav2017.tex
review section 'Discretising Continuous Space Dynamics'

@@
 \end{tikzpicture}
-\caption{The CEGIS loop with solution generalisation\label{fig:CEGIS-multiple-verif}}
+\caption{The CEGIS loop with solution generalisation\label{fig:CEGIS-multiple-verif}.
+\textcolor{red}{LC: Cristina, can you please fix this figure?
+The text ``candidate'' overlaps with the dotted box.}}
 \end{figure}
@@
 \begin{equation}
-\dot{x}(t)=\vec{A}\vec{x}(t)+\vec{B}\vec{u}(t) +\vec{w}(t)
+\dot{x}(t)=\vec{A}\vec{x}(t)+\vec{B}\vec{u}(t) +\vec{w}(t).
 \label{eq:dynamical}
@@
 \begin{equation}
-\vec{y}(t)=\vec{C}\vec{x}(t)+\vec{D}\vec{u}(t)
+\vec{y}(t)=\vec{C}\vec{x}(t)+\vec{D}\vec{u}(t).
 \end{equation}
@@
 \label{eq:discretization}
-\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d\vec{u}_k + \vec{w}_k\\
-y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k 
+\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d\vec{u}_k + \vec{w}_k,\\
+y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k. 
 \end{align}
-with covariance for $\vec{w}_k \sim \mathcal{N}(0,Q_d)$
+with covariance for $\vec{w}_k \sim \mathcal{N}(0,Q_d)$,
 where
@@
 \label{eq:discretize}
-\vec{A}_d &= e^{\vec{A} T_s} = \mathcal{L}^{-1} { ( s \vec{I} - \vec{A} )^{-1} }_{t = T_s}\\
-\vec{B}_d &= \int_{0}^{T_s} e^{\vec{A} t} dt\ \vec{B} = \vec{A}^{-1} ( \vec{A}_d - \vec{I} ) \vec{B}\\
-\vec{C}_d &= \vec{C}\\
-\vec{D}_d &= \vec{D} \\
-Q_d &= \int_{0}^{T_s} e^{\vec{A} t} Q e^{\vec{A}^T t} dt
+\vec{A}_d &= e^{\vec{A} T_s} = \mathcal{L}^{-1} { ( s \vec{I} - \vec{A} )^{-1} }_{t = T_s},\\
+\vec{B}_d &= \int_{0}^{T_s} e^{\vec{A} t} dt\ \vec{B} = \vec{A}^{-1} ( \vec{A}_d - \vec{I} ) \vec{B},\\
+\vec{C}_d &= \vec{C},\\
+\vec{D}_d &= \vec{D},\\
+Q_d &= \int_{0}^{T_s} e^{\vec{A} t} Q e^{\vec{A}^T t} dt.
 \end{align}
@@
 \begin{align*}
-x(kT)=x_k \wedge y(kT) = y_k, \forall k
+x(kT)=x_k \wedge y(kT) = y_k, \forall k.
 \end{align*}
@@
 of $g(t)$ and $g_d(k)$. Given this relation, we have 
-$$G_d(z)=G(z)|_{z=e^{sT}} : g_d(k)=\mathcal{G}(t,g(t),T) \wedge T < \frac{1}{.5f_s}$$
-Where $.5f_s$ is the Nyquist frequency of $g(t)$. This last restriction is introduced to avoid the effects of aliasing
-which could cause 'phantom poles' to appear otherwise. 
+$$G_d(z)=G(z)|_{z=e^{sT}} : g_d(k)=\mathcal{G}(t,g(t),T) \wedge T < \frac{1}{.5f_s},$$
+where $.5f_s$ is the Nyquist frequency of $g(t)$. This last restriction is introduced to avoid the effects of aliasing
+which could cause ``phantom poles'' to appear otherwise. 
 The eigenvalues of $\vec{A}_d$ corresponding to the poles of $G_d(z)$, and those of $\vec{A}$ corresponding to the poles of $G(s)$ are similarly related.
@@
 \end{remark}
-Since \eqref{eq:discretization} is a bisimulation of \eqref{eq:dynamical}, we may use the semantics in section \ref{sec:model_semantics} 
-to model continuous dynamical systems.
+\textcolor{red}{LC: Dario, where is the section you mention?...
+Since \eqref{eq:discretization} is a bisimulation of \eqref{eq:dynamical}, we may use the semantics in section \ref{sec:model_semantics} to model continuous dynamical systems.}
 

### 2016-11-21 cav2017/cav2017.tex
review section LTI representations of ARMA models

@@
 Let us have a discrete time SISO system with an $n^{th},m{^th} : n\geq m$ order armax model
-$$y[k]=\sum_{i=1}^n a_iy[k-i]+\sum_{i=0}^m b_iu[k-i]$$
+$$y[k]=\sum_{i=1}^n a_iy[k-i]+\sum_{i=0}^m b_iu[k-i],$$
 where $y$ is the output of the system and $u$ its input.

### 2016-11-21 cav2017/cav2017.tex
review related work

@@
 % first the title is needed
-\title{Automated Synthesis of State-Space Digital Controllers}
+\title{Automated Synthesis of State-Space Digital Systems}
 
@@
 
-\section{Related works}
+\section{Related Work}
 
@@
 stability measures for LTI SISO controllers.  We take the former
-from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from~\cite{daes20161}
+from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from~\cite{daes20161},
 while enhancing the procedure by evaluating the quantization effects of the
@@
 representation of the continuous dynamics.
+
+\textcolor{red}{LC: Cristina and Dario, should we further expand this section with other initiatives to synthesise control systems?}
 

### 2016-11-28 cav2017/cav2017.tex
add experimental evaluation section
Description of Benchmarks

@@
 %-------------------------------
+
 In this paper we formalise the notion of solution generalisation for CEGIS. 
@@
 
+%-------------------------------
 \section{Counter-Example Guided Inductive Synthesis with solution generalisation}
+%-------------------------------
 
@@
 
+%-------------------------------
 \section{Discretising Continuous Space Dynamics}
+%-------------------------------
 
@@
 
+%-------------------------------
 \section{LTI representations of ARMA models}
+%-------------------------------
 
@@
 
+%-------------------------------
+\section{Experimental Evaluation}
+%-------------------------------
+
+%-------------------------------
+\subsection{Description of the Benchmarks}
+%-------------------------------
+
+A set of state-space models for different classes of systems were extracted from the literature and employed for validating our automated synthesis methodology.
+All the systems are SISO models of the following form:
+\begin{equation}
+\left\lbrace\begin{array}{c}
+\dot{\textbf{x}}(t)=\textbf{A}\textbf{x}(t)+\textbf{B}u(t)\\
+y(t)=\textbf{C}\textbf{x}(t)+\textbf{D}u(t)
+\end{array}\right.
+\end{equation}
+
+The first plant represents a DC motor position model from~\cite{CTMS}.
+It is a third order system and presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
+$$
+\textbf{A}=\left[\begin{array}{ccc}
+0		& 1 		& 0						\\
+0 		& -1.087	& 8587					\\
+0		& -9964		& -1.455\times 10^{6}	\\
+\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
+0 \\ 0 \\ -1.455\times10^{6}
+\end{array}\right]
+$$
+%
+$$
+\textbf{C}=\left[\begin{array}{ccc}
+1 & 0 & 0\\
+\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
+\theta \\ \dot{\theta} \\ i \\
+\end{array}\right],
+$$
+where the states $\theta$, $\dot{\theta}$, and $i$ are respectively the rotor angular position, rotor angular rate and the current of armature. The DC motor is stable in open loop.
+
+The second benchmark is an aircraft pitch dynamics model extracted from~\cite{CTMS}.
+It is a third order system and it presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
+$$
+\textbf{A}=\left[\begin{array}{ccc}
+-0.313	& 56.7 		& 0		\\
+-0.0139	& -0.426	& 0		\\
+0		& 56.7		& 0		\\
+\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
+0.232 \\ 0.0203 \\ 0
+\end{array}\right]
+$$
+%
+$$
+\textbf{C}=\left[\begin{array}{ccc}
+0 & 0 & 1\\
+\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
+\alpha \\ \dot{\theta} \\ \theta \\
+\end{array}\right],
+$$
+where the states $\alpha$, $\dot{\theta}$, and $\theta$ are respectively the aircraft attack angle, pitch rate and the pitch angle.
+The aircraft pitch dynamic is critically stable in open loop, with a pole in origin of $s$-plane.
+
+The third benchmark is an ball magnetic levitation model extracted from~\cite{maglev}.
+It is a third order system presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
+$$
+\textbf{A}=\left[\begin{array}{ccc}
+0		& 1 		& 0		\\
+1752	& 0			& -34.07\\
+0		& 0			& -38.27\\
+\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
+0 \\ 0 \\ 1.923
+\end{array}\right]
+$$
+%
+$$
+\textbf{C}=\left[\begin{array}{ccc}
+1 & 0 & 0\\
+\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
+z \\ \dot{z} \\ i \\
+\end{array}\right],
+$$
+where the states $z$, $\dot{z}$, and $i$ are respectively the vertical displacement of the ball, its rate and the coil current. This system  is unstable in open loop.
+
+The remaining of benchmarks represents classic DC-DC converters: buck, boost, and buck-boost.
+They are SISO second-order systems stable in open-loop, and their state vector is $\textbf{x}=\textbf{x}=\left[\begin{array}{c}
+i_{L} \\ v_{C}\\
+\end{array}\right]$, where $i_{L}$ is the current in the coil and $v_{c}$ is the voltage on the capacitor.
+The matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, and $\textbf{D}$ for the buck converter are:
+$$
+\textbf{A}=\left[\begin{array}{cc}
+0		& -500 \\
+4545	& -1515\\
+\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+125 \\ 0 \\
+\end{array}\right]~
+\textbf{C}=\left[\begin{array}{cc}
+0 & 1\\
+\end{array}\right],~ \textbf{D}= 0.
+$$
+
+The matrices of the boost converter are:
+$$
+\textbf{A}=\left[\begin{array}{cc}
+0		& -375 \\
+3409	& -1515\\
+\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+500 \\ 0 \\
+\end{array}\right]~
+\textbf{C}=\left[\begin{array}{cc}
+0 & 1\\
+\end{array}\right],~ \textbf{D}= 0.
+$$
+
+Finally, the matrices of the buck-boost converter are:
+$$
+\textbf{A}=\left[\begin{array}{cc}
+0		& 375 \\
+-3409	& -1515\\
+\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+125 \\ 0 \\
+\end{array}\right]~
+\textbf{C}=\left[\begin{array}{cc}
+0 & 1\\
+\end{array}\right],~ \textbf{D}= 0.
+$$.
+
+%-------------------------------
+\subsection{Objectives}
+%-------------------------------
+
+%-------------------------------
+\subsection{Results}
+%-------------------------------
+
+%-------------------------------
+\subsection{Threats to validity}
+%-------------------------------
+
+%-------------------------------
 \section{Related Work}
+%-------------------------------
 

### 2016-11-28 paper/reply.tex
add reply letter

\documentclass[11pt]{article}

\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{url}
%\usepackage{mathtools}
\usepackage{enumerate}
\usepackage[nodayofweek]{datetime}

%\mathtoolsset{showonlyrefs}

\usepackage{xcolor}
%\input{rgbcolors}
%\usepackage{color}
\usepackage{natbib}
% \usepackage[style=authoryear-comp,dashed=false]{biblatex}
% \bibliography{piecewise_lyapunov}
\newcommand{\Real}{\mathbb{R}}

%\definecolor{DarkGreen}{rgb}{0.2, 0.4, 0.2}

\textwidth 15cm
\setlength{\textheight}{1.1\textheight}
\newcommand\hi{\hspace*{\parindent}}
\newcommand\vi{\vspace{\baselineskip}}
\newcommand\lac{{\mbox{{\Huge\bf L}\hspace{-0.65em}
\raisebox{-1.2ex}{\Huge\bf A}\hspace{-1.1em}
\raisebox{-0.6ex}{\Huge\bf C~}}}}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{Manuscript Reference Number: HSCC-2017}
\rhead{Page \thepage\ of \pageref{LastPage}}
\lfoot{}
\rfoot{}

%\pagestyle{headings}
\pagenumbering{roman}
\begin{document}
\setcounter{page}{1}
\thispagestyle{empty}

\vspace*{1cm}

\vi
\subsection*{Reviewer \#1 comments followed by the authors' answers:}

\begin{quote}

{\bf Comments to the Authors}

The paper presents an automated approach for synthesizing correct by design linear stabilizing digital controllers with fixed point arithmetics for linear continuous-time plants.

The approach is essentially as follows:

1) Quantization errors of input/output signals are modeled as additive disturbances

2) The plant is discretized in time, then approximated by a model in fixed point arithmetics, a parametric uncertainty is added to account for approximation error.

3) Controller synthesis is handled using a CEGIS approach:
    - Given a finite number of samples of the uncertain plant model, we synthesize a controller stabilizing all these samples. 
    - We try to verify that this controller stabilizes all possible plant models. If successful then we are done, otherwise we obtain a counter-example, which is added to the set of samples. The authors propose two different approaches for the verification phase consisting of one or two stages, respectively.

The approach is tested against several benchmarks, which shows that the approach seems to be effective in practice.

The paper is fairly well written and easy to follow. The technical contribution does not seem so strong to me: it mainly consists in gathering existing results and tools to solve the considered problem. However, the presented approach is potentially useful in applications and of interest to system designers. One limitation for practical applications, is that it currently adresses only stability specifications. Extending the approach to handle performance criteria would certainly be useful as well.

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Cristina).}
\end{quote}

Some specific comments:
1) In (8), $\Delta_{q} G$ accounts for quantization errors, but I thought it was already account for in the additive disturbance $\nu$.

2) Please provide the non-expert reader with characteristics of FWL in particular what are the practical meaning of I and F ?

3) I believe equation (10) does not correspond to the system on Figure 1. Please check. If needed, correct (11), (12) and (13) and the rest of the paper accordingly.

4) Proposition 1, item 2, should it be $\hat G$ ?

5) Section 3.2, you say that the refinement loop terminates since the set INPUTS is finite. Please acknowledge that it is also huge and that we hope it will not be needed to explore all possible values.6) In (18), it is unclear to me how we can compute  $\Delta_b$ ?

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Iury).}
\end{quote}

\end{quote}

%--------------------------------------------------------------------

\newpage

\subsection*{Reviewer \#2 comments followed by the authors' answers:}
\begin{quote}

{\bf Comments to the Authors}

This paper proposes a methodology for synthesizing digital stabilizing controllers for continuous plants. Several implementation effects such as finite-precision arithmetic, time discretization and quantization noise introduced by analog to digital converter and digital to analog converter make the controller synthesis problem complex. This paper leverages counter-example guided inductive synthesis methodology for synthesizing a valid program satisfying the stability specification.

This paper has several assumptions without justifications. For example:

1. The parametric errors in the plant will have the same polynomial order as the plant itself.

2. The sources of uncertainties are linear and independent.
The authors should provide reasonable justifications for these assumptions.

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Iury).}
\end{quote}

Digital controllers are designed to run on specific processors, and the bit width of a processor is generally fixed and multiple of 8. Traditionally, the bit-width assignment problem is solved to decide the length of the fraction part while the overall lengths fixed. The goal is generally to avoid overflow in the integer part and maximize the precision. However, in this paper, the length of the integer part and the fraction part seems to be changed arbitrarily. For example, in Section 3.5 in the example, the precision of $I_p = 16$ and $F_p = 24$ does not make the precision verification step successful. And in the next step, precision is increased to $I_p = 20$ and $F_p = 28$. This increase in precision looks quite arbitrary. Moreover, it is surprising that with $I_p = 16$ the precision verification step does not succeed, in spite of the fact that the constants in C(z) are quite small.

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Dario).}
\end{quote}

In the experimental results section, the authors have not compared their results with any existing work.

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Dario).}
\end{quote}

In the introduction, the authors claim that their approach achieves a speedup of at least two order of magnitude over conventional one stage verification engine. However, their experimental results do not provide any such evidence.

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Pascal).}
\end{quote}

In the experimental results section, the authors have not provided the information on the number of iteration of the CEGIS loop for each benchmark. Moreover, it will be useful if the authors provide the execution time for different components of their toolchain for synthesizing controller for different benchmarks. This will give us an idea on which component of the tool chain is the most computationally demanding and wold motivate us to optimize that component.

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Pscal).}
\end{quote}

The approach presented in this paper did not succeed for one benchmark example. The authors mentioned that increasing the fixed-point word widths will help their tool to succeed for the benchmark. However, as I understood, in the synthesis process, the author have not kept any upper bound on the fixed-point bit width. The authors should revisit the benchmark and examine the reason of the failure carefully.

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Pascal).}
\end{quote}

The authors may consider placing Figure 5 at a more suitable position.

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Lucas).}
\end{quote}

\end{quote}

%-----------------------------------------------------------------

%--------------------------------------------------------------------

\newpage

\subsection*{Reviewer \#2 comments followed by the authors' answers:}
\begin{quote}

{\bf Comments to the Authors}

This work presents a new algorithm for synthesizing digital controllers based on counterexample guided inductive synthesis (CEGIS). In particular, the authors focuses on linear models with known configurations and perform parametric synthesis of stabilizing digital controllers. It first translates the hybrid model into digital domain by zero-order hold (ZOH) discretization, and then performs the synthesis followed by a validation phase. Quantization errors and uncertainties caused by finite-word length (FWL) encoding are addressed. A tool named DSSynth is implemented based on the proposed algorithms and a few experimental results are given.

1) Novelty
Controller synthesis is a popular topic. This work is new in the sense that it addresses FWL uncertainties, utilizes CEGIS in the synthesis phase and proposes a faster two-stage verification phase. It does provide more benefits compared to the current works, though not very significantly.

2) Technical depth and soundness 
I would say the technical depth is mediate considering that this idea is built on currently existing techniques and rather straight forward. The article is well written and easy to follow. The algorithm looks sound.

3) Potential impact and relevance
The benchmark shows that half of the controllers can be synthesized in less than five minutes (although the experiments are performed on a powerful machine), which shows potential for practical usage.

4) Experimental or numerical validation (if applicable) 
The experiments are performed on the benchmarks taken from literature, which consists of 15 fairly simple examples from 4 different sets. They are fairly simple case studies, and I am curious how it works on larger examples. The authors also provided the link to the experimental environment.

5) Literature review
The authors have discussed a number of related works from different aspects and showed the novelty of their approach.

6) Some noticed TYPOS
- Page 2, formula (2), it should be $C_d(z)$ instead of $C_dz$
- Page 2, Line 4 from right bottom, there is one redundant ``system''
- Page 4, in Sect 3.3 the line below formula S(z)=$a_0$ $z^N$ + $...$, the rows and columns of Jury matrix M should be (2N-2)xN instead of (2N2)xN
- Figure 5 is on the next page of Figure 6, which should be switched.

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Lucas).}
\end{quote}

\end{quote}

\label{LastPage}

\end{document}

### 2016-11-29 paper/reply.tex
replace $C_d{z}$ by $C_d(z)$ in Formula (2)

@@
 6) Some noticed TYPOS
+
 - Page 2, formula (2), it should be $C_d(z)$ instead of $C_dz$
+
 - Page 2, Line 4 from right bottom, there is one redundant ``system''
+
 - Page 4, in Sect 3.3 the line below formula S(z)=$a_0$ $z^N$ + $...$, the rows and columns of Jury matrix M should be (2N-2)xN instead of (2N2)xN
+
 - Figure 5 is on the next page of Figure 6, which should be switched.

### 2016-11-29 paper/paper.tex
replace $C_d{z}$ by $C_d(z)$ in Formula (2)
fix typo
replace (2N2)xN by (2N-2)xN

@@
 \label{controller_plant_tf}
-C(z)&=\frac{C_n(z)}{C_d{z}}=\frac{\beta_{0}+\beta_{1}z^{-1}+...+\beta_{M_C}z^{-M_C}}{\alpha_{0}+\alpha_{1}z^{-1}+...+\alpha_{N_C}z^{-N_C}}, \\
+C(z)&=\frac{C_n(z)}{C_d(z)}=\frac{\beta_{0}+\beta_{1}z^{-1}+...+\beta_{M_C}z^{-M_C}}{\alpha_{0}+\alpha_{1}z^{-1}+...+\alpha_{N_C}z^{-N_C}}, \\
 %\label{plant_tf}
@@
 
-A typical digital control system system with a continuous plant and a discrete
+A typical digital control system with a continuous plant and a discrete
 controller is illustrated in Figure~\ref{fig:sampledsystem}.  The DAC and
@@
 Next, the following Jury matrix
-$M = [m_{ij}]_{(2N−2)\times N}$ is built from $S(z)$ coefficients:
+$M = [m_{ij}]_{(2N-2)\times N}$ is built from $S(z)$ coefficients:
 %

### 2016-11-29 paper/reply.tex
reply to reviewer 3

@@
 
-\subsection*{Reviewer \#2 comments followed by the authors' answers:}
+\subsection*{Reviewer \#3 comments followed by the authors' answers:}
 \begin{quote}
@@
 \begin{quote}
-\textcolor{blue}{\textbf{Response:} Authors' response (Lucas).}
+\textcolor{blue}{\textbf{Response:} We have evaluated our approach using standard benchmarks taken from the control literature [3,15,21,22,35].
+Larger benchmarks would strengthen our claims; however, related work on controller synthesis typically considers even smaller benchmarks (cf.
+3.5 and and 4.1).
+As far as we know, the CEGIS approach that addresses FWL uncertainties in digital controllers has not been described or evaluated in the literature.}
 \end{quote}

### 2016-11-29 paper/reply.tex
replace $G(z)$ by $\hat{G}(z)$ in proposition 1, item 2
Reply letter

@@
 
+\begin{quote}
+\textcolor{blue}{\textbf{Response:} $\Delta_{q} G$ is a model that incorporates the effects of $\nu$ in $\vec{\hat{G}}$ to investigate the consequences in the stability of system, once our stability analysis is based on polynomial coefficients and not over signals.}
+\end{quote}
+
 2) Please provide the non-expert reader with characteristics of FWL in particular what are the practical meaning of I and F ?
 
+\begin{quote}
+\textcolor{blue}{\textbf{Response:} This work addresses the synthesis of digital controller to be embedded in fixed-point hardwares.
+The FWL implementation is a function of the number of integer bits $I$ and fractional bits $F$.
+The $I$ affects strongly the representation range and is set in order to avoid overflows, and $F$ affects the precision and the truncation process after the operations.
+These variables are chosen depending on hardware features, in general purpose processors and DSP's $I$ is minimized avoiding overflows and the remaining of bit representation available are employed in $F$.
+Other flexible hardware structures (\textit{e.g.} FPGA's) allow the design of $F$ and $I$, what affects directly the number of logic arrays utilized.}
+\end{quote}
+
 3) I believe equation (10) does not correspond to the system on Figure 1. Please check. If needed, correct (11), (12) and (13) and the rest of the paper accordingly.
+\begin{quote}
+\textcolor{blue}{\textbf{Response:}
+In fact, these equations are wrong.
+They have to be substituted by the following equations (1)-(5).
+This mistake does not affect the results and conclusions because the proposition 1 is still valid for this set of equations.
+%%
+%\begin{equation}
+%\hat{Y}(z)=\nu_{1}(z)+Y(z)
+%\end{equation}
+%%
+%\begin{equation}
+%Y(z)=\hat{G}(z)\cdot(U(z)+\nu_{2}(z))
+%\end{equation}
+%%
+%\begin{equation}
+%U(z)=C(z)\cdot e(z)=C(z)\cdot (R(z)-\hat{Y}(z))
+%\end{equation}
+%%
+%$$
+%\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\cdot [\hat{C}(z)\cdot(R(z)-\hat{Y}(z))+\nu_{2}(z)]
+%$$
+%%
+\begin{equation}
+\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\cdot C(z)\cdot R(z)+\hat{G}(z)\cdot\nu_{2}(z)-\hat{G}(z)\cdot \hat{C}(z)\cdot \hat{Y}(z)
+\end{equation}
+%
+\begin{equation}
+\hat{Y}(z)=H_{1}(z)\nu_{1}(z)+H_{2}(z)\cdot\nu_{2}(z)+H_{3}(z)\cdot R(z)
+\end{equation}
+%
+\begin{equation}
+H_{1}(z)=\frac{1}{1+\hat{G}(z)\cdot \hat{C}(z)}
+\end{equation}
+\begin{equation}
+H_{2}(z)=\frac{\hat{G}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}
+\end{equation}
+\begin{equation}
+H_{3}(z)=\frac{\hat{G}(z)\cdot \hat{C}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}
+\end{equation}
+}
+\end{quote}
 
 4) Proposition 1, item 2, should it be $\hat G$ ?
+\begin{quote}
+\textcolor{blue}{\textbf{Response:} Authors' response (Iury).}
+\end{quote}
 
 5) Section 3.2, you say that the refinement loop terminates since the set INPUTS is finite.
-Please acknowledge that it is also huge and that we hope it will not be needed to explore all possible values.6) In (18), it is unclear to me how we can compute  $\Delta_b$ ?
+Please acknowledge that it is also huge and that we hope it will not be needed to explore all possible values.
+\begin{quote}
+\textcolor{blue}{\textbf{Response:} Authors' response (?).}
+\end{quote}
 
+6) In (18), it is unclear to me how we can compute  $\Delta_b$ ?
 \begin{quote}
-\textcolor{blue}{\textbf{Response:} Authors' response (Iury).}
+\textcolor{blue}{\textbf{Response:} The $\Delta_{b}$ of a coefficient $c$ (represented by $\Delta_{b}c$ represents the error in the fixed-point representation of $c$ that is the remainder of the division between the correct value of coefficient $c$ and its FWL format $\tilde{c}$, {\it i.e.} $\Delta_{b}c=c~ \texttt{mod}~\tilde{c}$.}
 \end{quote}
@@
 
-\begin{quote}
-\textcolor{blue}{\textbf{Response:} Authors' response (Lucas).}
-\end{quote}
-
 \end{quote}

### 2016-11-30 paper/reply.tex
small response editing

@@
 \begin{quote}
-\textcolor{blue}{\textbf{Response:} Authors' response (Cristina).}
+\textcolor{blue}{\textbf{Response:} 
+We consider this extension for future work.}
 \end{quote}
@@
 \begin{quote}
-\textcolor{blue}{\textbf{Response:} Authors' response (Iury).}
+\textcolor{blue}{\textbf{Response:} The typo was rectified.}
 \end{quote}
@@
 \begin{quote}
-\textcolor{blue}{\textbf{Response:} Authors' response (Iury).}
+\textcolor{blue}{\textbf{Response:} The parametric errors have same order as the plant because of limitations of DSSynth, further improvements may be done to make it flexible.
+In fact, we the modeling errors does not depend on sampling, holding and quantization errors, once it already appears in previous continuous time models and are only propagated in the discrete version.
+The reciprocal is true if the quantization noise is considered exogenous signals as proposed in figures 1 and 2.
+Although the parametric uncertainties and the sampling and holding process present nonlinearities, our linear approximation is enough to represent the majority of these effects and is usually employed in control systems literature.}
 \end{quote}

### 2016-11-30 paper/reply.tex
Added missing benchmark/engine comparison response

@@
 \begin{quote}
-\textcolor{blue}{\textbf{Response:} Authors' response (Pascal).}
+\textcolor{blue}{\textbf{Response:} We only state the winning back-end in the
+results table, annotating where the one-stage engine was faster. The two order
+of magnitudes were measured empirically, since the one-stage engine times out
+on the majority of benchmarks.}
 \end{quote}
@@
 \begin{quote}
-\textcolor{blue}{\textbf{Response:} Authors' response (Pascal).}
+\textcolor{blue}{\textbf{Response:} We did include an upper bound for both the
+bit width and execution time. Given an arbitrarily high precision and given
+unlimited execution time, the engine will always succeed.}
 \end{quote}

### 2016-11-30 paper/reply.tex
reloading darios comments

@@
 \begin{quote}
-\textcolor{blue}{\textbf{Response:} Authors' response (Dario).}
+\textcolor{blue}{\textbf{Response:} Authors' response (Dario).
+In section 3.3 we explain that there are two Fixed point domains in the control synthesis problem.
+Whilst the first domain $\mathbb{R}\langle I,F \rangle$, is the actual domain of the controller, whereas $\mathbb{R}\langle I_p,F_p \rangle$ is the bitvector domain of the synthesiser which is used to try and synthesise a real plant.
+In this section we explain the latter is started at a lower resolution for speed and the resolution increased when the rounding errors in the synthesis algorithm do not allow for correct synthesis.
+\textcolor{red}{This is an optimization of the tool and does not relate to the problem statement.} The reason for the 8-bit steps is because the tool uses byte alignment.
+}
 \end{quote}
@@
 \begin{quote}
-\textcolor{blue}{\textbf{Response:} Authors' response (Dario).}
+\textcolor{blue}{\textbf{Response:} Authors' response (Dario).
+The benchmarks used are from existing work on verification.
+There are no FWL synthesis papers that we are aware of that we can compare with (known synthesis tools do not account for the FWL effects), so we make the comparison between the direct (SAT) and CEGIS approach on known benchmarks which is as close as we can get to these comparisons.
+}
 \end{quote}

### 2016-11-30 paper/reply.tex
update reply letter
add [FWL characteristics, #1/#2]

@@
 \vspace*{1cm}
+
+%-----------------------------------------------------------------
+
+\noindent \textbf{[Novelty, \#1/\#2]}
+
+\noindent \textbf{[Assumptions, \#2]}
+
+\noindent The parametric errors have the same order as that of the plant.
+Modeling errors do not depend on sampling, holding, and quantization errors, since they already appear in previous continuous time models and are only propagated in the discrete version.
+The reciprocal is true if the quantization noise is considered exogenous signals as proposed to Figures 1 and 2.
+Although the parametric uncertainties and the sampling/holding process present nonlinearities, our linear approximation is enough to represent most of those effects, which is typically employed in the control systems literature.
+
+\noindent \textbf{[FWL characteristics, \#1/\#2]}
+
+\noindent The FWL implementation is a function of the number of integer bits $I$ and fractional bits $F$; $I$ strongly affects the representation range and is set to avoid overflows, while $F$ affects the precision and the truncation process after the operations.
+These variables are chosen depending on hardware features.
+In general purpose processors and DSP's, $I$ is minimized to avoid overflows and $F$ is employed for the remaining bit representation.
+Other flexible hardware structures (\textit{e.g.}, FPGAs) allow the design of $F$ and $I$, which affects directly the number of logical gates.
+Note that in section 3.3 we explain that there are two fixed-point domains in our control synthesis problem.
+Whilst the first domain $\mathbb{R}\langle I,F \rangle$, is the actual controller domain, whereas $\mathbb{R}\langle I_p,F_p \rangle$ is the bitvector domain of the synthesiser, which is used to try and synthesise a real plant.
+In this section we explain the latter is started at a lower resolution for speed and the resolution increased when the rounding errors in the synthesis algorithm do not allow for correct synthesis.
+This is a tool optimization and does not relate to the problem statement.
+The reason for the $8$-bit steps is because the tool uses byte alignment.
+
+%-----------------------------------------------------------------
+
+%--------------------------------------------------------------------
+
+\newpage
 
@@
 \begin{quote}
-\textcolor{blue}{\textbf{Response:} Authors' response (Dario).
-In section 3.3 we explain that there are two Fixed point domains in the control synthesis problem.
+\textcolor{blue}{\textbf{Response:} In section 3.3 we explain that there are two Fixed point domains in the control synthesis problem.
 Whilst the first domain $\mathbb{R}\langle I,F \rangle$, is the actual domain of the controller, whereas $\mathbb{R}\langle I_p,F_p \rangle$ is the bitvector domain of the synthesiser which is used to try and synthesise a real plant.
 In this section we explain the latter is started at a lower resolution for speed and the resolution increased when the rounding errors in the synthesis algorithm do not allow for correct synthesis.
-\textcolor{red}{This is an optimization of the tool and does not relate to the problem statement.} The reason for the 8-bit steps is because the tool uses byte alignment.
-}
+\textcolor{red}{This is an optimization of the tool and does not relate to the problem statement.} The reason for the 8-bit steps is because the tool uses byte alignment.}
 \end{quote}

### 2016-11-30 paper/reply.tex
add [Experimental evaluation, #1/#2/#3]

@@
 
-\noindent \textbf{[Novelty, \#1/\#2]}
+\noindent \textbf{[Novelty, \#1/\#2/\#3]}
+
+\noindent  As far as we know, the present synthesis approach that addresses FWL uncertainties in digital controllers has not been described or evaluated in the literature.
+This work is the first to address FWL uncertainties based on CEGIS in the digital controller synthesis phase.
 
@@
 The reason for the $8$-bit steps is because the tool uses byte alignment.
+
+\noindent \textbf{[Experimental evaluation, \#1/\#2/\#3]}
+
+\noindent We have evaluated our approach using standard benchmarks taken mostly from the classical control literature [3,15,21,22,35].
+Note that the used benchmarks are typically from existing work on control system verification.
+Larger benchmarks would strengthen our claims; however, related work on controller verification typically considers even smaller benchmarks (cf.
+3.5 and 4.1).
+Additionally, we only state the winning back-end in the results table, annotating where the one-stage engine was faster.
+The two order of magnitudes were measured empirically, since the one-stage engine times out on the majority of benchmarks.
 
@@
 This mistake does not affect the results and conclusions because the proposition 1 is still valid for this set of equations.
-%%
-%\begin{equation}
-%\hat{Y}(z)=\nu_{1}(z)+Y(z)
-%\end{equation}
-%%
-%\begin{equation}
-%Y(z)=\hat{G}(z)\cdot(U(z)+\nu_{2}(z))
-%\end{equation}
-%%
-%\begin{equation}
-%U(z)=C(z)\cdot e(z)=C(z)\cdot (R(z)-\hat{Y}(z))
-%\end{equation}
-%%
-%$$
-%\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\cdot [\hat{C}(z)\cdot(R(z)-\hat{Y}(z))+\nu_{2}(z)]
-%$$
 %%
@@
 \begin{quote}
-\textcolor{blue}{\textbf{Response:} Authors' response (Dario).
-The benchmarks used are from existing work on verification.
+\textcolor{blue}{\textbf{Response:} The benchmarks used are from existing work on verification.
 There are no FWL synthesis papers that we are aware of that we can compare with (known synthesis tools do not account for the FWL effects), so we make the comparison between the direct (SAT) and CEGIS approach on known benchmarks which is as close as we can get to these comparisons.

### 2016-11-30 paper/reply.tex
added [Novelty, #1/#2/#3]

@@
 \noindent  As far as we know, the present synthesis approach that addresses FWL uncertainties in digital controllers has not been described or evaluated in the literature.
-This work is the first to address FWL uncertainties based on CEGIS in the digital controller synthesis phase.
+This work is the first one to address FWL uncertainties based on CEGIS for synthesizing correct-by-design linear stabilizing digital controllers with fixed-point arithmetic for linear
+continuous-time plants.
 
@@
 3.5 and 4.1).
-Additionally, we only state the winning back-end in the results table, annotating where the one-stage engine was faster.
+We only state the winning back-end in the results table, annotating where the one-stage engine was faster.
 The two order of magnitudes were measured empirically, since the one-stage engine times out on the majority of benchmarks.
+Additionally, we did include an upper bound for both the bit width and execution time.
+Given an arbitrarily high precision and given unlimited execution time, the engine will always succeed.
 

### 2016-11-30 paper/reply.tex
update reply letter

--- 2016-11-30 paper/reply.tex
@@
 
-\noindent \textbf{[Novelty, \#1/\#2/\#3]}
+\noindent \textbf{Novelty (R1,R2,R3)}
 
-\noindent  As far as we know, the present synthesis approach that addresses FWL uncertainties in digital controllers has not been described or evaluated in the literature.
-This work is the first to address FWL uncertainties based on CEGIS in the digital controller synthesis phase.
+\noindent As far as we know, the present synthesis approach that addresses FWL
+uncertainties in digital controllers has not been described or
+evaluated in the literature.  Moreover, this work is the first use of
+CEGIS that handles the effects of quantizers and FWL.  Note that doing
+this efficiently required adjusting the traditional CEGIS refinement
+loop to use a two-stage verification engine, where the first stage
+performs fast, but potentially unsound fixed-point operations and the
+second stage restores soundness by validating the operations performed
+by the first stage by using interval arithmetic.  This architecture 
+enabled us to obtain candidate solutions fast, which is key to our 
+performance.
 
-\noindent \textbf{[Assumptions, \#2]}
+\noindent \textbf{Assumptions (R2)}
 
-\noindent The parametric errors have the same order as that of the plant.
-Modeling errors do not depend on sampling, holding, and quantization errors, since they already appear in previous continuous time models and are only propagated in the discrete version.
-The reciprocal is true if the quantization noise is considered exogenous signals as proposed to Figures 1 and 2.
-Although the parametric uncertainties and the sampling/holding process present nonlinearities, our linear approximation is enough to represent most of those effects, which is typically employed in the control systems literature.
+\noindent The parametric errors have the same order as that of the
+plant. Modeling errors do not depend on sampling, holding, and
+quantization errors, since they already appear in previous 
+continuous-time models and are only propagated in the discrete-time version. 
+The reciprocal is true if the quantization noise is considered exogenous
+signals as proposed to Figures 1 and 2. Although the parametric
+uncertainties and the sampling/holding process present nonlinearities,
+our linear approximation is enough to represent most of those effects,
+which is typically employed in the control systems literature.
 
-\noindent \textbf{[FWL characteristics, \#1/\#2]}
+\noindent \textbf{FWL characteristics (R1,R2)}
 
-\noindent The FWL implementation is a function of the number of integer bits $I$ and fractional bits $F$; $I$ strongly affects the representation range and is set to avoid overflows, while $F$ affects the precision and the truncation process after the operations.
-These variables are chosen depending on hardware features.
-In general purpose processors and DSP's, $I$ is minimized to avoid overflows and $F$ is employed for the remaining bit representation.
-Other flexible hardware structures (\textit{e.g.}, FPGAs) allow the design of $F$ and $I$, which affects directly the number of logical gates.
-Note that in section 3.3 we explain that there are two fixed-point domains in our control synthesis problem.
-Whilst the first domain $\mathbb{R}\langle I,F \rangle$, is the actual controller domain, whereas $\mathbb{R}\langle I_p,F_p \rangle$ is the bitvector domain of the synthesiser, which is used to try and synthesise a real plant.
-In this section we explain the latter is started at a lower resolution for speed and the resolution increased when the rounding errors in the synthesis algorithm do not allow for correct synthesis.
-This is a tool optimization and does not relate to the problem statement.
-The reason for the $8$-bit steps is because the tool uses byte alignment.
+\noindent The FWL implementation is a function of the number of integer bits $I$
+and fractional bits $F$; $I$ strongly affects the representation range
+and is set to avoid overflows, while $F$ affects the precision and the
+truncation process after the arithmetic operations. These variables are chosen
+depending on hardware features. In general purpose processors and
+DSP's, $I$ is minimized to avoid overflows and $F$ is employed for the
+remaining bit representation. Other flexible hardware structures
+(e.g., FPGAs) allow the design of $F$ and $I$, which affects directly
+the number of logical gates. Note that in section 3.3 we explain that
+there are two fixed-point domains in our control synthesis
+problem. Whilst the first domain $\mathbb{R}<I,F>$, is the actual
+controller domain, whereas $\mathbb{R}<I_p,F_p>$ is the bitvector
+domain of the synthesiser, which is used to try and synthesise a real
+plant. In this section we explain the latter is started at a lower
+resolution for speed and the resolution increased when the rounding
+errors in the synthesis algorithm do not allow for correct
+synthesis. This is a tool optimization and does not relate to the
+problem statement. The reason for the 8-bit steps is because the tool
+uses byte alignment.
 
-\noindent \textbf{[Experimental evaluation, \#1/\#2/\#3]}
+\noindent \textbf{Experimental evaluation (R1,R2,R3)}
 
-\noindent We have evaluated our approach using standard benchmarks taken mostly from the classical control literature [3,15,21,22,35].
-Note that the used benchmarks are typically from existing work on control system verification.
-Larger benchmarks would strengthen our claims; however, related work on controller verification typically considers even smaller benchmarks (cf.
-3.5 and 4.1).
-Additionally, we only state the winning back-end in the results table, annotating where the one-stage engine was faster.
-The two order of magnitudes were measured empirically, since the one-stage engine times out on the majority of benchmarks.
+\noindent We have evaluated our approach using standard benchmarks taken mostly
+from the classical control literature [3,15,21,22,35]. Note that the
+used benchmarks are typically from existing work on control system
+verification. Larger benchmarks would strengthen our claims; however,
+related work on controller verification typically considers even
+smaller benchmarks (cf. 3.5 and 4.1). We only state the winning
+back-end in the experimental results table, annotating where the one-stage engine
+was faster. The two order of magnitudes were measured empirically,
+since the one-stage engine times out on the majority of
+benchmarks. Additionally, we did include an upper bound for both the
+bit width and execution time. Note that given an arbitrarily high precision and
+given unlimited execution time, the engine will always succeed.
 

### 2016-11-30 paper/reply.tex
added Preliminaries (R1)

@@
 
+\noindent \textbf{Preliminaries (R1)}
+
+\noindent Since our stability analysis is based on polynomial coefficients
+and not over signals, in Equation (8) $\Delta_{q} G$ is a model that incorporates 
+the effects of $\nu$ in $\vec{\hat{G}}$, in order to investigate the system's 
+stability consequences.
+
+\noindent The $\Delta_{b}$ of a coefficient $c$ (represented by $\Delta_{b}c$) models 
+the error in the fixed-point representation of $c$, which is the division remainder 
+between the correct value of coefficient $c$ and its respective FWL format $\tilde{c}$, 
+i.e., $\Delta_{b}c=c~ \texttt{mod}~\tilde{c}$.
+
 %-----------------------------------------------------------------
@@
 Some specific comments:
+
 1) In (8), $\Delta_{q} G$ accounts for quantization errors, but I thought it was already account for in the additive disturbance $\nu$.

### 2016-11-30 paper/reply.tex
improved Preliminaries (R1)

@@
 \noindent Since our stability analysis is based on polynomial coefficients
-and not over signals, in Equation (8) $\Delta_{q} G$ is a model that incorporates 
-the effects of $\nu$ in $\vec{\hat{G}}$, in order to investigate the system's 
-stability consequences.
+and not over signals, Equation (8) incorporates the effects of $\nu$ in $\vec{\hat{G}}$
+(by means of $\Delta_{q} G$), in order to investigate the system's stability consequences.
 

### 2016-11-30 paper/reply.tex
update reply letter

--- 2016-11-30 paper/reply.tex
@@
 
-\noindent \textbf{Novelty (R1,R2,R3)}
-
-\noindent As far as we know, the present synthesis approach that addresses FWL
-uncertainties in digital controllers has not been described or
-evaluated in the literature.  Moreover, this work is the first use of
-CEGIS that handles the effects of quantizers and FWL.  Note that doing
-this efficiently required adjusting the traditional CEGIS refinement
-loop to use a two-stage verification engine, where the first stage
-performs fast, but potentially unsound fixed-point operations and the
-second stage restores soundness by validating the operations performed
-by the first stage by using interval arithmetic.  This architecture 
-enabled us to obtain candidate solutions fast, which is key to our 
-performance.
-
-\noindent \textbf{Assumptions (R2)}
-
-\noindent The parametric errors have the same order as that of the
-plant. Modeling errors do not depend on sampling, holding, and
-quantization errors, since they already appear in previous 
-continuous-time models and are only propagated in the discrete-time version. 
-The reciprocal is true if the quantization noise is considered exogenous
-signals as proposed to Figures 1 and 2. Although the parametric
-uncertainties and the sampling/holding process present nonlinearities,
-our linear approximation is enough to represent most of those effects,
-which is typically employed in the control systems literature.
-
-\noindent \textbf{FWL characteristics (R1,R2)}
-
-\noindent The FWL implementation is a function of the number of integer bits $I$
-and fractional bits $F$; $I$ strongly affects the representation range
-and is set to avoid overflows, while $F$ affects the precision and the
-truncation process after the arithmetic operations. These variables are chosen
-depending on hardware features. In general purpose processors and
-DSP's, $I$ is minimized to avoid overflows and $F$ is employed for the
-remaining bit representation. Other flexible hardware structures
-(e.g., FPGAs) allow the design of $F$ and $I$, which affects directly
-the number of logical gates. Note that in section 3.3 we explain that
-there are two fixed-point domains in our control synthesis
-problem. Whilst the first domain $\mathbb{R}<I,F>$, is the actual
-controller domain, whereas $\mathbb{R}<I_p,F_p>$ is the bitvector
-domain of the synthesiser, which is used to try and synthesise a real
-plant. In this section we explain the latter is started at a lower
-resolution for speed and the resolution increased when the rounding
-errors in the synthesis algorithm do not allow for correct
-synthesis. This is a tool optimization and does not relate to the
-problem statement. The reason for the 8-bit steps is because the tool
-uses byte alignment.
-
-\noindent \textbf{Experimental evaluation (R1,R2,R3)}
-
-\noindent We have evaluated our approach using standard benchmarks taken mostly
-from the classical control literature [3,15,21,22,35]. Note that the
-used benchmarks are typically from existing work on control system
-verification. Larger benchmarks would strengthen our claims; however,
-related work on controller verification typically considers even
-smaller benchmarks (cf. 3.5 and 4.1). We only state the winning
-back-end in the experimental results table, annotating where the one-stage engine
-was faster. The two order of magnitudes were measured empirically,
-since the one-stage engine times out on the majority of
-benchmarks. Additionally, we did include an upper bound for both the
-bit width and execution time. Note that given an arbitrarily high precision and
-given unlimited execution time, the engine will always succeed.
-
-%-----------------------------------------------------------------
-
 %--------------------------------------------------------------------

### 2016-12-02 paper/reply.tex
Benchmarks

@@
 
-%-----------------------------------------------------------------
-
-%--------------------------------------------------------------------
-
-\newpage
-
 \vi
@@
 \begin{quote}
-\textcolor{blue}{\textbf{Response:} 
-We consider this extension for future work.}
+\textcolor{blue}{\textbf{Response:} Authors' response (Cristina).}
 \end{quote}
@@
 Some specific comments:
-
 1) In (8), $\Delta_{q} G$ accounts for quantization errors, but I thought it was already account for in the additive disturbance $\nu$.
@@
 This mistake does not affect the results and conclusions because the proposition 1 is still valid for this set of equations.
+%%
+%\begin{equation}
+%\hat{Y}(z)=\nu_{1}(z)+Y(z)
+%\end{equation}
+%%
+%\begin{equation}
+%Y(z)=\hat{G}(z)\cdot(U(z)+\nu_{2}(z))
+%\end{equation}
+%%
+%\begin{equation}
+%U(z)=C(z)\cdot e(z)=C(z)\cdot (R(z)-\hat{Y}(z))
+%\end{equation}
+%%
+%$$
+%\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\cdot [\hat{C}(z)\cdot(R(z)-\hat{Y}(z))+\nu_{2}(z)]
+%$$
 %%
@@
 \begin{quote}
-\textcolor{blue}{\textbf{Response:} In section 3.3 we explain that there are two Fixed point domains in the control synthesis problem.
-Whilst the first domain $\mathbb{R}\langle I,F \rangle$, is the actual domain of the controller, whereas $\mathbb{R}\langle I_p,F_p \rangle$ is the bitvector domain of the synthesiser which is used to try and synthesise a real plant.
-In this section we explain the latter is started at a lower resolution for speed and the resolution increased when the rounding errors in the synthesis algorithm do not allow for correct synthesis.
-\textcolor{red}{This is an optimization of the tool and does not relate to the problem statement.} The reason for the 8-bit steps is because the tool uses byte alignment.}
+\textcolor{blue}{\textbf{Response:} Authors' response (Dario).}
 \end{quote}
@@
 \begin{quote}
-\textcolor{blue}{\textbf{Response:} The benchmarks used are from existing work on verification.
-There are no FWL synthesis papers that we are aware of that we can compare with (known synthesis tools do not account for the FWL effects), so we make the comparison between the direct (SAT) and CEGIS approach on known benchmarks which is as close as we can get to these comparisons.
-}
+\textcolor{blue}{\textbf{Response:} Authors' response (Dario).}
 \end{quote}
@@
 \begin{quote}
-\textcolor{blue}{\textbf{Response:} We only state the winning back-end in the
-results table, annotating where the one-stage engine was faster. The two order
-of magnitudes were measured empirically, since the one-stage engine times out
-on the majority of benchmarks.}
+\textcolor{blue}{\textbf{Response:} Authors' response (Pascal).}
 \end{quote}
@@
 \begin{quote}
-\textcolor{blue}{\textbf{Response:} We did include an upper bound for both the
-bit width and execution time. Given an arbitrarily high precision and given
-unlimited execution time, the engine will always succeed.}
+\textcolor{blue}{\textbf{Response:} Authors' response (Pascal).}
 \end{quote}

### 2016-12-07 paper/paper.tex
replace $G(z)$ by $\hat{G}(z)$ in proposition 1, item 2
Updated experiment table with both back-ends.

@@
 \end{equation}
-\item the direct loop product $\mathit{FWL}_{M_C,N_C}[C(z)]\cdot G(z)$ has no pole-zero cancellation on or outside the unit circle.
+\item the direct loop product $\mathit{FWL}_{M_C,N_C}[C(z)]\cdot \hat{G}(z)$ has no pole-zero cancellation on or outside the unit circle.
 \end{itemize}
@@
 \centering
-\begin{tabular}{c | c | l | r r | r l}
-\# & Plant  & Benchmark                  & $I$ & $F$ & Time    & \\\cline{1-6}
-1  & $G_1$  & CruiseControl02            &   4 &  16 & 17\,s   & \\
-2  & $G_1$  & CruiseControl02$^\dagger$  &   4 &  16 & 46\,s   & \\
-3  & $G_2$  & SpringMassDamper           &  15 &  16 & 28\,s   & \\
-4  & $G_2$  & SpringMassDamper$^\dagger$ &  15 &  16 & \xmark  & \\
-5  & $G_3$  & SatelliteB2                &   3 &   7 & 7\,s    & \\
-6  & $G_3$  & SatelliteB2$^\dagger$      &   3 &   7 & 6601\,s & \tbmark\\
-7  & $G_3$  & SatelliteC2                &   3 &   5 & 2\,s    & \\
-8  & $G_3$  & SatelliteC2$^\dagger$      &   3 &   5 & 76\,s   & \tbmark\\
-9  & $G_4a$ & a\_ST1\_IMPL1              &  16 &   4 & 2704\,s & \\
-10 & $G_4a$ & a\_ST1\_IMPL2              &  16 &   8 & 538\,s  & \\
-11 & $G_4a$ & a\_ST1\_IMPL3              &  16 &  12 & 12\,s   & \\
-12 & $G_4b$ & a\_ST2\_IMPL1              &  16 &   4 & 318\,s  & \\
-13 & $G_4b$ & a\_ST2\_IMPL2              &  16 &   8 & 967\,s  & \\
-14 & $G_4b$ & a\_ST2\_IMPL3              &  16 &  12 & 9798\,s & \\
-15 & $G_4c$ & a\_ST3\_IMPL1              &  16 &   4 & 6304\,s & \\
+\begin{tabular}{ | c | c | l | r r || r | r | }
+\hline
+\# & Plant  & Benchmark                  & $I$ & $F$
+   & \multicolumn{1}{|c|}{1-step} & \multicolumn{1}{|c|}{2-step}
+    \\\hline\hline
+1  & $G_1$  & CrsControl02
+            &   4 &  16 & 17\,s   & \xmark     \\
+2  & $G_1$  & CrsControl02$^\dagger$
+            &   4 &  16 & 46\,s   & \xmark     \\
+3  & $G_2$  & SpgMsDamper
+            &  15 &  16 & 28\,s   & \xmark     \\
+4  & $G_2$  & SpgMsDamper$^\dagger$
+            &  15 &  16 & \xmark  & \xmark    \\
+5  & $G_3$  & SatelliteB2
+            &   3 &   7 & 7\,s    & \xmark     \\
+6  & $G_3$  & SatelliteB2$^\dagger$
+            &   3 &   7 & \xmark  & 6601\,s  \\
+7  & $G_3$  & SatelliteC2
+            &   3 &   5 & 2\,s    & \xmark    \\
+8  & $G_3$  & SatelliteC2$^\dagger$
+            &   3 &   5 & \xmark  & 76\,s    \\
+9  & $G_4a$ & a\_ST1\_IMPL1
+            &  16 &   4 & 2704\,s & \xmark   \\
+10 & $G_4a$ & a\_ST1\_IMPL2
+            &  16 &   8 & 538\,s  & \xmark   \\
+11 & $G_4a$ & a\_ST1\_IMPL3
+            &  16 &  12 & 12\,s   & \xmark   \\
+12 & $G_4b$ & a\_ST2\_IMPL1
+            &  16 &   4 & 318\,s  & \xmark   \\
+13 & $G_4b$ & a\_ST2\_IMPL2
+            &  16 &   8 & 967\,s  & \xmark    \\
+14 & $G_4b$ & a\_ST2\_IMPL3
+            &  16 &  12 & 9798\,s & \xmark   \\ 
+15 & $G_4c$ & a\_ST3\_IMPL1
+            &  16 &   4 & 6304\,s & \xmark   \\\hline
 \end{tabular}
@@
 \vspace{0.5em}
-\scriptsize{* = solved with the one-stage engine, $\dagger$ = with uncertainty}
+\scriptsize{\xmark = time-out, $\dagger$ = with uncertainty}
 \vspace{0.5em}

### 2016-12-07 cav2017/cav2017.tex
Benchmarks
figure fix

@@
      \node[rectangle,draw,dashed,
-	minimum width=7cm,
+	minimum width=6.7cm,
 	minimum height=.8cm,
@@
    \node[fill=yellow!20] (verif1) at ([xshift=-2.1cm]verif.center) {{\sc Validate}};
-   \node[fill=yellow!20,align=center] (verif2) at ([xshift=1.9cm]verif.center) {{\sc validate general}};
+   \node[fill=yellow!20,align=center] (verif2) at ([xshift=1.7cm]verif.center) {{\sc validate general}};
    } 
@@
     ([xshift=5em]verif1.south) edge node[align=center] {Candidate} ([xshift=5em]bmc.north)
-    ([xshift=5em]verif2.south) edge node[align=center] {Candidate} ([xshift=5em]fp.north)
+    ([xshift=5em]verif2.south) edge node[align=center] {Candidate} ([xshift=3.8em]fp.north)
     ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif1.south)
-    ([xshift=-5em]fp.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif2.south)
+    ([xshift=-6.2em]fp.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif2.south)
     (verif2) edge node {} (done)
@@
    \path[-]
-   (verif2.north) edge node[align=center] {} ([xshift=6.5cm]aux2)
-   ([xshift=6.5cm]aux2) edge node[align=center] {Increase parameters} (aux1);
+   (verif2.north) edge node[align=center] {} ([xshift=5.6cm]aux2)
+   ([xshift=5.6cm]aux2) edge node[align=center] {Increase parameters} (aux1);
 
 \end{tikzpicture}
-\caption{The CEGIS loop with solution generalisation\label{fig:CEGIS-multiple-verif}.
-\textcolor{red}{LC: Cristina, can you please fix this figure?
-The text ``candidate'' overlaps with the dotted box.}}
+\caption{The CEGIS loop with solution generalisation\label{fig:CEGIS-multiple-verif}.}
 \end{figure}
+
+  %% \textcolor{red}{LC: Cristina, can you please fix this figure? The text ``candidate'' overlaps with the dotted box.}
 
@@
 
-The third benchmark is an ball magnetic levitation model extracted from~\cite{maglev}.
+The third benchmark is a ball magnetic levitation model extracted from~\cite{maglev}.
 It is a third order system presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:

### 2016-12-12 cav2017/cav2017.tex

@@
 controller, it entirely circumvents the FWL problem.  It is also not
-suitable for the kind of control we seek to synthesize.  We require a
+suitable for the kind of control we seek to synthesize.
+Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
+use a CEGIS-based approach for synthesizing continuous-time switching
+controllers that guarantee reach while stay properties of a closed
+loop system. The solution is based on synthesizing control Lyapunov
+functions for switched systems, that yield switching controllers with
+a guaranteed minimum dwell time in each mode.
+
+We require a
 combination of a synthesis engine with a control verification tool that

### 2016-12-12 paper/reply.tex

--- 2016-11-30 paper/reply.tex
@@
 \begin{quote}
-\textcolor{blue}{\textbf{Response:} Authors' response (Pscal).}
+\textcolor{blue}{\textbf{Response:} Number of remains within 1-2 per CEGIS step
+for benchmarks in which two-step engine succeeds. However, there are 3-5 plant
+precision increases using our current implementation. Our CEGIS implementation
+spends 95\% of its runtime in the synthesis phase, and only 5\% in the
+verification phase. Improvements in the  precision increase heuristic and the
+synthesis phase will thus benefit the runtime most.}
 \end{quote}
@@
 \begin{quote}
-\textcolor{blue}{\textbf{Response:} We did include an upper bound for both the
-bit width and execution time. Given an arbitrarily high precision and given
-unlimited execution time, the engine will always succeed.}
+\textcolor{blue}{\textbf{Response:} As stated in section 4.3, we did bound the
+runtime per benchmark in our experiment, which was the reason behind the failure
+to synthesise benchmark 4. We also limited our experiment to 64 bits word width,
+but as stated in 4.3 CBMC supports arbitrary precision fixed point types which,
+given sufficient runtime, can be used to synthesise the missing controller.}
 \end{quote}

### 2016-12-12 cav2017/cav2017.tex
add comments to the paper

@@
 
-\textcolor{red}{LC: Cristina, may I ask you to expand further this section by connecting it to our control-synthesis work?}
+\textcolor{red}{LC: Dario and Cristina, may I ask you to expand further this section by connecting it to our control-synthesis work?}
 \begin{figure}
@@
 
+\textcolor{red}{We will have to move this text to the beginning of the paper.}
+
 A set of state-space models for different classes of systems were extracted from the literature and employed for validating our automated synthesis methodology.
@@
 \end{array}\right],~ \textbf{D}= 0.
-$$.
+$$
 

### 2016-12-16 cav2017/cav2017.tex
benchmarks

--- 2016-12-12 cav2017/cav2017.tex
@@
 
-The remaining of benchmarks represents classic DC-DC converters: buck, boost, and buck-boost.
+There are three benchmarks representing classic DC-DC converters: buck, boost, and buck-boost.
 They are SISO second-order systems stable in open-loop, and their state vector is $\textbf{x}=\textbf{x}=\left[\begin{array}{c}
@@
 $$.
+
+Additionally, various dynamic systems model were extracted from~\cite{Franklin15} and incorporated to our test suite. They are: 
+\begin{itemize}
+\item{\textbf{automotive cruise control system:} 
+$$
+\textbf{A}=-0.05,~ \textbf{B} = 0.03125~
+\textbf{C}=0.032,~ \textbf{D}= 0;
+$$
+}
+\item{\textbf{DC motor:} 
+$$
+\textbf{A}=\left[\begin{array}{cc}
+-1000		& -13 \\
+-8			& 0\\
+\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+4 \\ 0 \\
+\end{array}\right]~
+\textbf{C}=\left[\begin{array}{cc}
+0 & 6.25\\
+\end{array}\right],~ \textbf{D}= 0;
+$$
+}
+\item{\textbf{helicopter longitudinal motion:} 
+$$
+\textbf{A}=\left[\begin{array}{ccc}
+-0.42		& 0.0168		& -0.396	\\
+0.5			& 0				& 0			\\
+0			& 0.5 			& 0			
+\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+16 \\ 0 \\ 0
+\end{array}\right]~
+\textbf{C}=\left[\begin{array}{ccc}
+0.6125	& -0.6125	& 15.44 \\
+\end{array}\right],~ \textbf{D}= 0;
+$$
+}
+\item{\textbf{inverted pendulum cart position:} 
+$$
+\textbf{A}=\left[\begin{array}{cccc}
+0		& 1		& 0 	& 0	\\
+1		& 0		& 0		& 0	\\
+0		& 1 	& 0		& 0 \\
+0		& 0		& 1 	& 0 \\	
+\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+1 \\ 0 \\ 0 \\ 0
+\end{array}\right]~
+\textbf{C}=\left[\begin{array}{cccc}
+0	& 0	& 1 & -0.75 \\
+\end{array}\right],~ \textbf{D}= 0;
+$$
+}
+\item{\textbf{inverted pendulum angle:} 
+$$
+\textbf{A}=\left[\begin{array}{cc}
+0		& 1	\\
+1		& 0	\\
+\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+1 \\ 0 \\ 0 \\ 0
+\end{array}\right]~
+\textbf{C}=\left[\begin{array}{cc}
+ 0	& 1 \\
+\end{array}\right],~ \textbf{D}= 0;
+$$
+}
+\item{\textbf{magnetic pointer:} 
+$$
+\textbf{A}=\left[\begin{array}{ccc}
+-0.271		& -0.05336	& 0	\\
+0.03125		& 0			& 0	\\
+0			& 0.01562 	& 0	\\	
+\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+1 \\ 0 \\ 0
+\end{array}\right]~
+\textbf{C}=\left[\begin{array}{ccc}
+0	& -0.5888	& -0.2562 \\
+\end{array}\right],~ \textbf{D}= 0;
+$$
+}
+\item{\textbf{magnetic suspension:} 
+$$
+\textbf{A}=\left[\begin{array}{cc}
+0		& 31.25	\\
+32		& 0		\\	
+\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+8 \\ 0
+\end{array}\right]~
+\textbf{C}=\left[\begin{array}{cc}
+0	& 9.766 	\\
+\end{array}\right],~ \textbf{D}= 0;
+$$
+}
+\item{\textbf{pendulum:} 
+$$
+\textbf{A}=\left[\begin{array}{cc}
+0		& -2.453	\\
+4		& 0			\\	
+\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+4 \\ 0
+\end{array}\right]~
+\textbf{C}=\left[\begin{array}{cc}
+-1.225	& -2.15 	\\
+\end{array}\right],~ \textbf{D}= 9.8;
+$$
+}
+\item{\textbf{1/4 car suspension:} 
+$$
+\textbf{A}=\left[\begin{array}{cccc}
+-516.1	& -222.1& -79.75& -33.06	\\
+256		& 0		& 0		& 0			\\
+0		& 64 	& 0		& 0 \\
+0		& 0		& 32 	& 0 \\	
+\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+8 \\ 0 \\ 0 \\ 0
+\end{array}\right]~
+\textbf{C}=\left[\begin{array}{cccc}
+0	& 0	& 9.969 & 4.133 \\
+\end{array}\right],~ \textbf{D}= 0;
+$$
+}
+\item{\textbf{computer tape driver:} 
+$$
+\textbf{A}=\left[\begin{array}{ccc}
+-1760		& -976.6	& -457.8	\\
+1024		& 0			& 0			\\
+0			& 512 		& 0			\\	
+\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+8 \\ 0 \\ 0
+\end{array}\right]~
+\textbf{C}=\left[\begin{array}{ccc}
+1.5	& 2.051	& 1.144 \\
+\end{array}\right],~ \textbf{D}= 0;
+$$
+}
+\item{\textbf{USCG cutter Tampa heading angle:} 
+$$
+\textbf{A}=\left[\begin{array}{ccc}
+-0.271		& -0.05336	& 0	\\
+0.03125		& 0			& 0			\\
+0			& 0.01562 	& 0			\\	
+\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+1 \\ 0 \\ 0
+\end{array}\right]~
+\textbf{C}=\left[\begin{array}{ccc}
+0	& -0.5888	& -0.2562 \\
+\end{array}\right],~ \textbf{D}= 0;
+$$
+}
+\end{itemize}
 

### 2016-12-19 cav2017/cav2017.tex
Early draft on The state-space model

@@
 
-\usetikzlibrary{positioning, arrows, automata, shapes}
+\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
 
@@
 \newcommand{\commentib}[1]{{\color{blue} [IB: #1]}}
+\newcommand{\mat}[1]{\boldsymbol{#1}}
 
@@
 
-In this paper we formalise the notion of solution generalisation for CEGIS. 
-This technique allows the inductive generalisation engine to look for 
+Linear Time Invariant Control systems represnt a sizeable portion of modern
+embedded software, performing highly non-trivial control
+tasks, with significant impact in numerous application areas such as
+environmental control, navigation and robotics~\cite{astrom1997computer,Franklin15}.
+
+Correct and sound control is non-trivial, however. The problem is exacerbated by
+artefacts specific to digital control, such as the effects of
+finite-precision arithmetic, time discretization, and quantization noise
+introduced by A/D and D/A conversion.  Thus, the programming is a key
+barrier to broad adoption of digital control, and requires considerable
+expertise.
+
+Whilst there is a vast literature in validation of control systems, the subject
+of control synthesis has been somewhat restricted in the properties it explores.
+Traditionally, this focuses mainly on the subject of stability, working typically on
+continuous domains \cite{sadabadi2016static}, or using switched models~\cite{DBLP:conf/emsoft/RavanbakhshS16}.
+Reachability tools are also used when discretizing the state-space for both verification and parametric synthesis\cite{cimatti2013parameter}.
+
+In this paper, we propose the synthesis of control algorithms for cyberphisical
+systems taking into consideration the continuous domain of the plant alongside
+the discrete domain of the controller and the hybrid elements that communicate
+them.
+
+To this end, we formalise the notion of solution generalisation for CEGIS and 
+apply CEGAR on simplified abstractions of the system in order to achieve scalability. 
+The former technique allows the inductive generalisation engine to look for 
 candidate solutions in a reduced solution space. 
+The latter case is a well know technique for abstract interpretation that allows
+simplification of the procedures over a sound abstraction of the verification model.
+
+%-------------------------------
+\section{Preliminaries}
+%-------------------------------
+In this work we will focus on Linear Dynamical Cyberphisical Systems with
+continuous plants described by ODEs in the form
+\begin{align}
+\label{eq:ode}
+\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\\
+\vec{y}(t)&=\mat{C}\vec{x}+\mat{D}\vec{u}\nonumber
+\end{align}
+which are soundly discretized (as shown in the appendix) into 
+\begin{align}
+\label{eq:plant}
+\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
+\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k\nonumber
+\end{align}
+and Digital Controllers in the form
+\begin{equation}
+\vec{u}_k=\mat{K}_d\vec{y}_k
+\end{equation}
+The output of the plant is being sampled by an ADC, and since the full state of the
+plant cannot be witnessed directly, the controller software includes an observer that 
+estimates the state of the plant (see appendix for details on how such an observer
+is constructed).
+
+We further presume that there are small tolerances in the system described in the
+following form
+\begin{align*}
+\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
+\mat{B} \in \mathcal{G}_B
+\end{align*}
+
+Finally, we also require a safety specification $\Psi(\vec{u},\vec{y})$ which is
+given as a set of linear constraints over the inputs and outputs.
 
@@
 
-%-------------------------------
-\section{Discretising Continuous Space Dynamics}
-%-------------------------------
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{Counterexample Guided Abstractly Refined Inductive Synthesis for LTI Cyberphysical Systems}\label{sec:CEGARIS}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 
-A dynamical system is a system in which a function describes the progression of a state over time. 
-In a continuous domain with linear dynamics, it is described by a first order Ordinary Differential Equation (ODE).
-\begin{equation}
-\dot{x}(t)=\vec{A}\vec{x}(t)+\vec{B}\vec{u}(t) +\vec{w}(t).
-\label{eq:dynamical}
-\end{equation}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Verification of a Conrollable Observed System}\label{sec:cof_verification}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 
-\noindent with $\vec{w} \sim \mathcal{N}(0,Q)$.\\
-Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
-which may restricts the observability of the state-space from the output space.
-\begin{equation}
-\vec{y}(t)=\vec{C}\vec{x}(t)+\vec{D}\vec{u}(t).
-\end{equation}
+Let us recall the formulas used for SISO systems in sections \ref{sec:reachable} and \ref{sec:observable}.
+A controllable and observable system will have the following dynamics:
+\begin{align}
+\label{eq:observer_LTI_cf}
+\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_{k+1}
+=&\left [\begin{array}{cc}\mat{A}_{tp}&\mat{B}_{to}\\ \mat{0}&\mat{A}_{to}\end{array}\right]
+\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_k
++\mat{B}_{tp} \vec{r}_k
++\mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]\\
+\vec{y}_k=&\mat{C}_{t}\vec{x}_k + \mat{D}_{d}\vec{u}_k\nonumber
+\end{align}
+\begin{align*}
+\mat{A}_{tp}=&\mat{T}\mat{A}_d\mat{T}^{-1}-\mat{T}\mat{B}_d\mat{K}_d\mat{T}^{-1}&
+\mat{A}_{to}=&\mat{T}\mat{A}_d\mat{T}^{-1}-\mat{L}_d\mat{C}_d\mat{T}&
+\mat{A}_t=&\left [\begin{array}{cc}\mat{A}_{tp}&\mat{B}_{to}\\ \mat{0}&\mat{A}_{to}\end{array}\right]\\
+\mat{B}_{to}=&\mat{T}\mat{B}_d\mat{K}_d\mat{T}^{-1}&
+\mat{B}_{tp}=&\left[\begin{array}{c}\mat{T}\mat{B}_d\mat{k}_r\\\mat{0}\end{array}\right]&
+\mat{B}_{tn}=&\left[\begin{array}{cc}\mat{T}\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{L}_d\end{array}\right]\\
+\mat{T}=&\mat{R}_{cf}\mat{R}^{-1}&
+\mat{L}=&\mat{W}_o^{-1}\mat{W}_{of} \left[ \begin{array}{c}p_1-a_1\\p_2-a_2\\p_n-a_n\end{array}\right]&
+\mat{C}_t=&\mat{C}_d\mat{T}
+\end{align*}
 
-Discretization of an continuous dynamical system turns the ODE into a difference equation, assuming zero-order hold
-for the input $\vec{u}$ and continuous integration for the noise $\vec{w}$, to
-\begin{align}
-\label{eq:discretization}
-\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d\vec{u}_k + \vec{w}_k,\\
-y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k. 
-\end{align}
-with covariance for $\vec{w}_k \sim \mathcal{N}(0,Q_d)$,
-where
-\begin{align}
-\label{eq:discretize}
-\vec{A}_d &= e^{\vec{A} T_s} = \mathcal{L}^{-1} { ( s \vec{I} - \vec{A} )^{-1} }_{t = T_s},\\
-\vec{B}_d &= \int_{0}^{T_s} e^{\vec{A} t} dt\ \vec{B} = \vec{A}^{-1} ( \vec{A}_d - \vec{I} ) \vec{B},\\
-\vec{C}_d &= \vec{C},\\
-\vec{D}_d &= \vec{D},\\
-Q_d &= \int_{0}^{T_s} e^{\vec{A} t} Q e^{\vec{A}^T t} dt.
-\end{align}
-and $T_s$ is the sample time. Then
 \begin{align*}
-x(kT)=x_k \wedge y(kT) = y_k, \forall k.
-\end{align*}
-Let $g_d(k)=\mathcal{G}(t,g(t),T)$ be a function that performs the discretization described above, where $g(t)$
-represents the continuous dynamics and $g_d(k)$ the corresponding discrete dynamics. 
-Let $G(s)=\mathcal{L}(g(t))$ and $G_d(z)=\mathcal{Z}(g_d(k))$ be the corresponding Laplace and Z-transforms
-of $g(t)$ and $g_d(k)$. Given this relation, we have 
-$$G_d(z)=G(z)|_{z=e^{sT}} : g_d(k)=\mathcal{G}(t,g(t),T) \wedge T < \frac{1}{.5f_s},$$
-where $.5f_s$ is the Nyquist frequency of $g(t)$. This last restriction is introduced to avoid the effects of aliasing
-which could cause ``phantom poles'' to appear otherwise. 
-The eigenvalues of $\vec{A}_d$ corresponding to the poles of $G_d(z)$, and those of $\vec{A}$ corresponding to the poles of $G(s)$ are similarly related.
-$\hat{\lambda}_i=e^{-\lambda_iT} : \hat{\lambda}_i \in \sigma(\vec{A}_d) \wedge \lambda_i \in \sigma(\vec{A})$
-where $\sigma(\cdot)$ is the spectrum of a matrix.
-The following remark is worth mentioning regarding the above.
-\begin{remark}
-The witnessed maximum amplitude of the discrete signals $x_k,y_k$ may be smaller to that of $x(t),y(t)$ due to synchronism at fraction-frequency sampling.
-This means that reasoning about the state-space must consider the effects of this possibility as well of the case of maximal inputs from the continuous specification.
-\end{remark}
-\textcolor{red}{LC: Dario, where is the section you mention?...
-Since \eqref{eq:discretization} is a bisimulation of \eqref{eq:dynamical}, we may use the semantics in section \ref{sec:model_semantics} to model continuous dynamical systems.}
-
-%-------------------------------
-\section{LTI representations of ARMA models}
-%-------------------------------
-
-Let us have a discrete time SISO system with an $n^{th},m{^th} : n\geq m$ order armax model
-$$y[k]=\sum_{i=1}^n a_iy[k-i]+\sum_{i=0}^m b_iu[k-i],$$
-where $y$ is the output of the system and $u$ its input.
-The equivalent LTI dynamics of such a model are:
-\begin{align}
-\vec{x}_k=&\vec{A}\vec{x}_{k-1}+\vec{B}u_k : \vec{x}_k=[y_{k-n}\ \hdots y_{k-1}\ y_{k}]^T\\
-y_k=&\vec{C}\vec{x}_k + b_0u_k\nonumber\\
-\vec{A}=&\left[
+\mat{A}_{tp}=&\left[
 \begin{array}{ccccc}
@@
 0&0&0&\cdots&1\\
--a_n&-a_{n-1}&-a_{n-2}&\cdots&-a_1
-\end{array}\right],
-\vec{B}=\left[
-\begin{array}{c}
-0\\0\\ \vdots\\ 0\\ 1
-\end{array}\right]\nonumber\\
-\vec{C}=&[b_n-a_nb_0\ b_{n-1}-a_{n-1}b_0 \cdots b_1-a_1b_0] : b_{i \in (m\ n]}=0\nonumber
+k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
+\end{array}\right]
+\label{eq:cf_SISO_2}
+\end{align*}
+
+Careful examination of these matrices reveals that because the $\mat{A}_t$ is upper block diagonal, the spectrum of $\mat{A}_t$ is equal to the union of the spectrum of $\mat{A}_{tp}$ and $\mat{A}_{to}$ which can be calculated separately.
+Additionally, these correspond to the roots of the polynomials
+\begin{align*}
+\left(z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}\right) \left(z^n+\sum_{i=1}^p{(p_i-a_i)z^{n-i}}\right)
+\end{align*}
+
+For a stabilised closed loop, we need these roots to remain within the unit circle (left hand side of the plane for continuous time).
+Whilst this is not a sufficient condition for verifying safety properties, it is a necessary one, therefore we will review this verification process.
+The direct approach would be to calculate the roots of the polynomials (\emph{ie} the eigenvalues of the matrix), but this ends up being to costly, particularly in the case of synthesis, so we use an indirect method.
+
+Jury's criteria is a mathematical method used to verify whether the roots of the polynomial are within the unit circle by exploring solely the coefficients of the polynomial.
+In order to achieve this, we first create a matrix $\mat{M} \in \mathbb{R}^{(n+1) \times (n+1)}$ with zero-indexed coefficients $m_{i,j} : i,j \in [0,n],k=n-(i-1)$ in the following form:
+
+\begin{equation}
+\left[\begin{array}{ccccc}
+c_0&c_1&\hdots&c_{n-1}&c_n\\
+m_{\scriptscriptstyle 0,0}-m_{\scriptscriptstyle 0,n}^*\frac{m_{0,n}^*}{m_{0,0}}&m_{\scriptscriptstyle 0,1}-m_{\scriptscriptstyle 0,n-1}^*\frac{m_{0,n}^*}{m_{0,0}}&\hdots&m_{\scriptscriptstyle 0,n-1}-m_{\scriptscriptstyle 0,1}^*\frac{m_{0,n}^*}{m_{0,0}}&0\\
+\vdots&\vdots&\vdots&\vdots&\vdots\\
+m_{\scriptscriptstyle i-1,0}-m_{\scriptscriptstyle i-1,k-j}^*\frac{m_{i-1,k}^*}{m_{i-1,0}}&m_{\scriptscriptstyle i-1,1}-m_{\scriptscriptstyle i-1,k-j}^*\frac{m_{i-1,k}^*}{m_{i-1,0}}&\hdots&0&0\\
+m_{\scriptscriptstyle n-1,0}-m_{\scriptscriptstyle n-1,1-j}^*\frac{m_{n-1,1}^*}{m_{n-1,0}}&0&\hdots&0&0\\
+\end{array}\right]
+\end{equation}
+
+The first row corresponds to the coefficients of the original polynomial.
+Notice also that every row has a polynomial one degree lower than the previous.
+The sufficient and necessary conditions for the polynomial in row 0 to have all of its roots inside the unit circle are~\cite{astrom1997computer}:
+\begin{align}
+|c_n|<c_0&&
+\sum_{i=0}^n c_i > 0&&
+(-1)^n\sum_{i=0}^n c_i (-1)^{n-i}> 0&&
+m_{i,0}>0
 \end{align}
+
+Notice that in both our polynomials $c_0=1$ and we only use reals.
+Now that we have established convergence, we may examine the safety specification of the state space.
+In the case of SISO systems, this is given by a range of the input and a range of the output which are considered safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in [\underline{y}\ \ \overline{y}]$).
+Whilst there are other properties we may include in the verification, we will solely focus on these for simplicity of the explanation.
+We will assume that we do not want saturation in our system, hence the control loop has only one mode. We have also identified the quantization noise as a bounded non-deterministic input.
+First we must translate the safety specification into the statespace. Replacing on the second part of equation \eqref{eq:observer_LTI_cf} we obtain
+\begin{equation}
+\Psi := \underline{y}-\overline{\mat{B}\vec{u}}<\mat{C}_t\vec{x}_k<\overline{y}-\underline{\mat{B}\vec{u}}
+\label{eq:of_bounds}
+\end{equation}
+Note that we use the bounds of the input after the transformation by $\mat{B}$ since the matrix may reverse the bounds.
+Equation \eqref{eq:of_bounds} can be solved using linear programming as it describes a polyhedral region in $\mathbb{R}^n$.
+The second step is evaluating the progression of the system over time in order to calculate $\vec{x}_k$ to validte against this specification.
+For this step we require an initial set from which the system progresses.
+Obviously, this set $\vec{x}_0$ must satisfy the specification, otherwise the system will be unsafe to begin with.
+We will accept a specification in the form $\mat{E}\mat{T}\vec{x}_0<\mat{f}$. The presence of $\mat{T}$ is because this will typically be given in the original state-space.
+Accelerating \eqref{eq:observer_LTI_cf}, we obtain:
+\begin{align}
+\label{eq:acc_observer_LTI_cf}
+\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_k
+=&\mat{A}_t^k
+\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_0
++\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tp} \vec{r}_i
++\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right] :
+ \left [\begin{array}{cc}\mat{E}\mat{T}&\mat{0}\end{array}\right] \left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_0<\mat{f}
+\end{align}
+which would still require us to verify the system for every $k$ up to infinity. Instead we will use abstract acceleration~\cite{cattaruzza2015unbounded}, which translates the formula into
+\begin{align}
+\label{eq:aa_observer_LTI_cf}
+\hat{X}^\#
+=&\mathcal{A}_t X_0+\mathcal{B}_{tp} R + \mathcal{B}_{tn} N\\
+X_0 =&\left \{ \left[\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right] :
+ \left [\begin{array}{cc}\mat{E}\mat{T}&\mat{0}\end{array}\right] \left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_0<\mat{f} \right\}\nonumber\\
+ R =&\{r : \mat{E}_r < \vec{f}_r \}\nonumber\\
+ N=&\left \{ \left[\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right] : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \right \}\nonumber
+\end{align}
+where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A}^k, \mathcal{B}_{tp}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tp}, \mathcal{B}_{tn}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tn}$ are abstract matrices for the system in \eqref{eq:observer_LTI_cf}.
+It is worth noting that $r$ is a non-deterministic parametric input (\emph{ie} $\forall k>0, r_{k+1} =r_k$) whereas the set N is composed of non-deterministic variable inputs.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Numeric Representations and Soundness} \label{sec:numeric_rep}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Let $\mathbb{R} \langle I,F \rangle$ be a fixed point domain with $I$ bits representing the integer part and $F$ bits
+representing the decimal part. We will extend this notation to $\mathbb{R} \langle I,F,E \rangle$ to add a number of
+leading or trailing bits when the domain requires prescaling (ie the maximum is smaller than $0.5$ or the minimum
+is greater than $2$)
+Let also $\mathbb{R}_* \langle M,E \rangle$ be a floating point domain with $M$ bits
+mantissa and $E$ bits exponent. This domain corresponds to 
+$$\mathbb{R}_* \langle M,E \rangle = \bigcup_i \mathbb{R} \langle 1,M-1,E_i \rangle : 2^{1-E} \leq E_i  \leq 2^{E-1}$$
+This means that the distance between any two numbers in the domain depends on the
+location of those numbers.
+Since we've shown that a floating point domain is a union of a number of fixed point domains, we will continue our
+reasoning on fixed point only. Our points will apply to the floating point domain by extension.
+The following approximation errors will arise:
+\begin{enumerate}
+\item Truncation\\
+Let $\mathcal{F}\langle I,F \rangle(\cdot) : \mathbb{R} \rightarrow \mathbb{R}\langle I,F \rangle, \tilde x=\mathcal{F}\langle I,F \rangle(x) = x-\delta : \delta=x\ \%_F\  c\tilde x$, where $\%_F$ is the modulus operation performed on the last bit of the representation ($2^{-F}$).\\
+The number $\delta$ corresponds to the truncation error of the representation and it will propagate across operations.
+\item Rounding\\
+Every time an operation is performed on a number in the $\mathbb{R} \langle I,F,E \rangle$ domain, an error may be
+introduced due to truncation of the result.
+Let us define $c\langle i,f,e \rangle \in \mathbb{R}\langle I,F,E\rangle$, where $i \in [-2^{I-1}\ 2^{I-1}],f \in [0 1),e \in [-2^{E-1}\ 2^{E-1}]$ are its assigned values.
+The smallest number that can be represented for any given exponent is $c_{min(e)}=c\langle 0,2^{-F},e\rangle$.
+The following errors appear in simple operations:
+\begin{enumerate}
+\item Addition/Substraction: $c\langle \cdot,e_1\rangle \pm c\langle \cdot,e_2\rangle=c\langle \cdot,max(e_1,e_2)\rangle + \delta_3 : |\delta_3| \leq (e_1==e_2) ? 0 : c_{min(max(e_2,e_1))}$ 
+\item Multiplication: $c\langle \cdot,e_1\rangle * c\langle \cdot,e_2\rangle=c\langle \cdot,e_1+e_2\rangle + \delta_3 : |\delta_3| \leq c_{min(e_2+e_1)}$
+\end{enumerate}
+The bounds obtained for division are left to the reader as it will not be applied in this paper.
+
+At this point it is worth mentioning that not all systems truncate equally. In the definition above $\delta$ may be positive
+or negative, and even this decision can be made dependent on the sign of $x$. Common cases in computer systems are:
+round downwards (\emph{ie} to $-\infty$), round upwards (\emph{ie} to $+\infty$), and round to zero.
+Rounding errors are cumulative which means the overall error will statistically increase with every operation, thus algorithms
+performing fewer operations can be more precise in this respect than iterative ones. 
+\item Overflow\\
+Another source of error introduced by Finite Word Length representations is that of overflow. The finite word length set a
+maximum representable number in the domain ($\pm 2^{I-1}+1-2^{-F}$), which means that any number outside this range
+cannot be accurately represented by the domain (\emph{eg} $\delta=x-2^{I-1}+1-2^{-F}$). In the case of floating point, a special
+case for infinity has been introduced, which addresses some of this issues, but once the error has gone to infinity, the numbers
+become meaningless. It is the responsibility of software designers and tools to account for overflows and either supply saturation
+functions to prevent them or raise alarms in their presence. In the case of verification, the latter is seen as a safety problem.
+\item Null/Zeno behaviour\\
+Whilst this work does not explore the effect of Zeno behaviours, it is worth noting that this effect may also be caused by rounding
+errors in floating point programs. The reason for this is that if an operation contains two numbers which belong to disjoint sub-domains
+(\emph{ie} neither number can be represented in the domain of its counterpart), the resulting operation may become a no-op/skip,
+subsequently destabilizing the program.
+\end{enumerate}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Fixed Word Length Effects on Matrix Multiplications}\label{sec:cof_fwl}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+Thus far we have presented a verification procedure for a digitalized plant in a continuous space (\emph{ie} the
+range of the quatizers is still $\mathbb{R}$. The next step we must reaize is that the controller and the observer
+exist in a digital program, hence their domain is $\mathbb{R}\langle I,F,E\rangle$. This has two separate effects
+on the model. If we recall equation \eqref{eq:to_of}, the matrices of the observer and the controller  are not necessarily those of the plant.
+In fact we have $\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$, $\mat{A}_o,\mat{B}_o,\mat{C}_o, \mat{K}_d, \mat{L}_d \in \mathbb{R}\langle I,F,E\rangle^*$
+Where $*$ represents the appropriate dimension for each matrix.
+Unfortunately this means that although combined matrices such as $\mat{A}_t$ are in the reals, they suffer from
+the fixed word restrictions in their composing matrices.
+The second effect corresponds to the rounding errors in the calculation of $\hat{x}_{k+1}, u_k$.
+These will introduce a new source of quantiztion noise which we may denote $\vec{\nu}_3 \in [-q_3\ \ q_3]$.
+The estimation of $\hat{\vec{x}}$ corresponds to the sum of three matrix-vector multiplications (we assume $\mat{C}_o$ in Objective form).
+Each of these has a coefficient-wise error bound $c_{min(max(e_{j1}+e_{j2}))}$.
+Hence the overall $\overline{\delta}_{\hat{x}}=3nc_{min(max(e_{j1}+e_{j2}))}$.
+The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=nc_{min(max(e_{k1}+e_{k2}))}+\sum_{k=1}^nc_k\overline{\delta}_{\hat{x}})=3n|\mat{K}|_1c_{min(max(e_{j1}+e_{j2}))}+nc_{min(max(e_{k1}+e_{k2}))}$
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Synthesisig the dynamics}\label{sec:cof_synth}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+Now that we have explained the verification process, we may proceed to describe the synthesis procedure, which is illustrated in figure \ref{fig:CEGARIS}.
+\begin{enumerate}
+\item We start by preprocessing the dynamics. This can be computationally intensive and we don't want it to be part of the CEGIS loop.
+\begin{enumerate}
+\item Calculate $\mat{A}_o,\mat{B}_o,\mat{C}_o$ by rounding down the coefficients $*_{oij}=\mathcal{F}\langle I,F,E\rangle (*_{ij}) : *=\{a,b,c\}$
+\item Calculate $\mat{T}$ and $\mat{W}_o^{-1}\mat{W}_{of}$ using equations \eqref{eq:rncf}\eqref{eq:rcf}\eqref{eq:to_cf}\eqref{eq:wnof}\eqref{eq:wof}
+\item Extract the Plant's characteristic polynomial coefficients from the last row of $P_a=\mat{T}\mat{A}\mat{T}^-1$.
+\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors ($\frac{q_1}{2},\frac{q_2}{2},q_3$)
+\end{enumerate}
+\item Next we synthesise a candidate controller and observer. Let $\mathcal{J}\langle I,F,E \rangle (P,\mat{T})$ be a program describing Jury's method.
+\begin{enumerate}
+\item Select a controller $\tilde{\mat{K}} \in \mathbb{R}\langle I,F,E\rangle^n$.
+This is achieved by solving a SAT formula $\mathcal{J}_K=\mathcal{J}\langle I,F,E \rangle (P_{a-k},\mat{T})$ that satisfies Jury's criteria for $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \mat{K}=\tilde{\mat{K}}\mat{T}$.
+\item Select the observer error characteristic polynomial $\tilde{\mat{L}} \in \mathbb{R}\langle I,F,E\rangle^n$. 
+This is achieved by solving a SAT formula $\mathcal{J}_L=\mathcal{J}\langle I,F,E \rangle (P_p,\mat{W}_o^{-1}\mat{W}_{of})$ 
+that satisfies Jury's criteria for 
+$P_p=z^n+\sum_{i=1}^n p_i z^{n-i} : p_i \in \vec{P}= (\mat{W}_o^{-1}\mat{W}_{of})^-1 \tilde{\mat{L}} 
++ [\begin{array}{cccc}a_1&a_2&\hdots&a_n\end{array}]^T$.
+\item If there is no candidate solution we return UNSAT and exit the loop.
+\end{enumerate}
+\item Once we have a candidate solution, we perform a safety verification using abstract acceleration.
+\begin{enumerate}
+\item Calculate the abstract matrices $\mathcal{A}_t, \mathcal{B}_{tp},\mathcal{B}_{tn}$ for the candidate closed loop solution.
+\item Evaluate $\hat{X}^\# \models \Psi$. If the verification holds we have a solution, and exit the loop.
+\end{enumerate} 
+\item If the candidate solution is not valid we refine the abstraction used by the synthesiser
+\begin{enumerate}
+\item Find the constraints that invalidate the property.
+These are the rows of $\mat{E} \in \Psi$ that intersect/segment $\hat{X}^\#$.
+Transforming these rows into the eigenspace of $\mat{A}_t$, and applying backward acceleration to obtain a set of counterexamples for the eigenvalues, which we define as $\Psi_{\lambda}$ .
+\item Transform the soft constraints on the eigenvalues defined in the counterexample into soft constraints on the coefficients of the characteristic polynomial. 
+$z^n+\sum_{i=1}^n[a_i-k_i]z^{n-i}=\prod_{i=1}^n (z-[\lambda_i]) : |[\lambda_i]|<1 \wedge [\lambda_i] \models \Psi_{\lambda}$.
+\item Pass the refined abstraction with the new contraints to the synthesiser and repeat the loop again.
+
+\end{enumerate} 
+\end{enumerate}
+
+\begin{figure}
+\centering
+\hspace*{-1cm}
+\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=.2cm, column sep=.2cm] {
+   \coordinate (aux1);
+   \& \coordinate (aux2);
+   \& ;\\
+   \&\node[fill=yellow!20,align=center] (pre) {{\sc pre-}\\{\sc processing}};
+   \& \node[fill=yellow!20,align=center] (abstract) {\sc abstraction};
+        \node[draw=none] (FIK) at ([xshift=2.5cm,yshift=.3cm]abstract)  {\sc $\Psi (\mat{K})$};
+   \& \node[fill=yellow!20,align=center] (counter) {\sc counterexample};\\
+   \& 
+   \& \node[fill=yellow!20,align=center, minimum width=3cm] (synth) {\sc synthesiser};
+       \node[draw=none] (KL) at ([xshift=2.5cm,yshift=-.25cm]synth)  {\sc $\mat{K},\mat{L}$};
+       \node[draw=none] (NKL) at ([xshift=2cm,yshift=1.2cm]synth)  {\sc $\neg \mat{K}, \mat{L}, \mat{A}$};
+   \& \node[fill=yellow!20,align=center, minimum width=4cm] (verify) {\sc verifier ($\Psi$)};
+       \node[draw=none] (VUNS) at ([xshift=.6cm,yshift=1cm]verify)  {\sc UNSAT};
+       \node[draw=none] (SAT) at ([xshift=2.5cm,yshift=-.3cm]verify)  {\sc SAT};
+   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
+   \&
+   \& complexnode/.pic={
+     \coordinate (auxsynth);
+     \node[draw,rectangle,align=center] (KSAT) at ([xshift=-.8cm]auxsynth.center) {\sc SAT\\Solver};
+     \node[draw,rectangle,align=center] (LSAT) at ([xshift=.8cm]auxsynth.center) {\sc SAT\\Solver};
+     \node[draw=none] (SATK) at ([xshift=-.5cm,yshift=1.5cm]KSAT)  {$\mathcal{J}_K$};
+     \node[draw=none] (K) at ([xshift=.4cm,yshift=1.5cm]KSAT)  {$\tilde{\mat{K}}$};
+     \node[draw=none] (SATL) at ([xshift=-.5cm,yshift=1.5cm]LSAT)  {$\mathcal{J}_L$};
+     \node[draw=none] (L) at ([xshift=.4cm,yshift=1.5cm]LSAT)  {$\tilde{\mat{L}}$};
+    }
+   \& complexnode/.pic={
+     \coordinate (AA);
+     \node[draw,rectangle,align=center] (AAI) at ([xshift=-1.5cm]AA.center) {\sc AI\\Model};
+     \node[draw,rectangle,align=center] (AAV) at ([xshift=1.5cm]AA.center) {\sc AA\\Solver};
+     \node[draw=none] (AB) at ([xshift=.4cm,yshift=1.5cm]AAI.center)  {\sc $\mat{A}_t$ $\mat{B}_{tp}$ $\mat{B}_{tn}$};     
+     \node[draw=none] (MA) at ([yshift=.2cm]AA.center)  {$\mathcal{A}_t$};     
+     \node[draw=none] (MB) at ([yshift=-.3cm]AA.center)  {$\mathcal{B}_{tp},\mathcal{B}_{tn}$}; 
+     \node[draw=none] (AB) at ([xshift=0.3cm,yshift=1.5cm]AAV.center)  {\sl $\hat{X}^\#$};  
+    }\\
+   \&
+   \& complexnode/.pic={
+     \coordinate (UNSAT);
+     \coordinate (KUNSAT)  at ([xshift=-.8cm]UNSAT.center);
+     \coordinate (LUNSAT) at ([xshift=.8cm]UNSAT.center);
+     \node[draw=none] (UNSATB) at ([xshift=1.6cm,yshift=.3cm]UNSAT)  {\sc UNSAT};
+  }
+  \& \& \coordinate (FAIL);\\
+  };
+  \path
+    (pre.east) edge (abstract.west)
+    (abstract.south) edge (synth.north)
+    (synth.east) edge (verify.west)
+    (verify.east) edge (done.west);
+  \path
+    ([xshift=+.6cm]KSAT.north) edge ([xshift=-2.1cm]synth.south) 
+    ([xshift=-3.3cm]synth.south) edge ([xshift=-.6cm]KSAT.north)
+    ([xshift=.6cm]LSAT.north) edge ([xshift=3.3cm]synth.south)
+    ([xshift=+2.1cm]synth.south) edge ([xshift=-.6cm]LSAT.north)
+    ([xshift=-4.9cm]verify.south) edge (AAI.north)
+    (AAI.east) edge (AAV.west)
+    (AAV.north) edge ([xshift=4.9cm]verify.south)
+    (verify.north) edge (counter.south)
+    (counter.west) edge (abstract.east)
+    (counter.south west) edge (synth.north east)
+    (FAIL.north) edge (done.south);
+   \path[-] 
+     (KSAT.south) edge (KUNSAT.north)
+     (LSAT.south) edge (LUNSAT.north)
+     (KUNSAT.east) edge (LUNSAT.west)
+     (LUNSAT.east) edge (FAIL.west);
+\end{tikzpicture}
+\caption{The CEGIS loop with CEGAR\label{fig:CEGARIS}.}
+\end{figure}
 
@@
 
+\paragraph{Discretization Effects}
+
+The classical approach to control synthesis has often disregarded
+quantization as a minimal effect, thus proving unsound in the case of digital control systems.
+Modern techniques focus on different elements of the discretization effect, including delayed
+response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics with
+the goal to either verify (e.g.~\cite{daes20161}) or optimize
+(e.g.~\cite{oudjida2014design}) given implementations.
+
+There are two different problems that arise from FWL semantics.  The first
+is the error in the dynamics caused by the inability to represent the exact
+state of the physical system while the second relates to rounding errors
+during computation.  In~\cite{fialho1994stability}, a stability measure
+based on the error of the digital dynamics ensures that the deviation
+introduced by FWL does not make the digital system unstable.  A more recent
+approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
+directly model the digital controller so that the selected parameters are
+stable by design.  The analyses
+in~\cite{DBLP:conf/hybrid/WangGRJF16,DBLP:conf/hybrid/RouxJG15} rely on an
+invariant computation on the discrete system dynamics using Semi-Definite
+Programming (SDP).  While the former uses BIBO properties to determine
+stability, the latter uses Lyapunov-based quadratic invariants.  In both
+cases, the SDP solver uses floating-point arithmetic and soundness is
+checked by bounding the error.  An alternative approach is taken
+by~\cite{park2016scalable}, where the verification of existing code is
+performed against a known model by extracting an LTI model of the code
+through symbolic execution.  In order to account for rounding errors, an
+upper bound is introduced in the verification phase.
+The work in \cite{picasso2002construction,picasso2003stabilization} introduces
+attractive invariant sets as a mechanism to bound the quantization error effect
+on stabilization as an invariant set that always converges toward the cotrollable
+set. In a similar fashion, \cite{liberzon2003hybrid} evaluates the dynamics of the
+quantization error and binds their trajectory to a known region over a finite
+period of time. This technique works for both linear and non-linear systems.
+This paper uses an approach that projects the maximum effect of the noise over
+an unbounded time and uses it as a `buffer' region for the safety specification.
+
 \textcolor{red}{LC: Cristina and Dario, should we further expand this section with other initiatives to synthesise control systems?}
+
+\newpage
 
@@
 
+\newpage
+\appendix
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{LTI system Transformations and Equivalencies} \label{sec:appendix}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+%-------------------------------
+\subsection{Discretising Continuous Space Dynamics}
+%-------------------------------
+
+A dynamical system is a system in which a function describes the progression of a state over time. 
+In a continuous domain with linear dynamics, it is described by a first order Ordinary Differential Equation (ODE).
+\begin{equation}
+\dot{x}(t)=\vec{A}\vec{x}(t)+\vec{B}\vec{u}(t) +\vec{w}(t).
+\label{eq:dynamical}
+\end{equation}
+
+\noindent with $\vec{w} \sim \mathcal{N}(0,Q)$.\\
+Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
+which may restricts the observability of the state-space from the output space.
+\begin{equation}
+\vec{y}(t)=\vec{C}\vec{x}(t)+\vec{D}\vec{u}(t).
+\end{equation}
+
+Discretization of an continuous dynamical system turns the ODE into a difference equation, assuming zero-order hold
+for the input $\vec{u}$ and continuous integration for the noise $\vec{w}$, to
+\begin{align}
+\label{eq:discretization}
+\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d\vec{u}_k + \vec{w}_k,\\
+y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k. 
+\end{align}
+with covariance for $\vec{w}_k \sim \mathcal{N}(0,Q_d)$,
+where
+\begin{align}
+\label{eq:discretize}
+\vec{A}_d &= e^{\vec{A} T_s} = \mathcal{L}^{-1} { ( s \vec{I} - \vec{A} )^{-1} }_{t = T_s},\\
+\vec{B}_d &= \int_{0}^{T_s} e^{\vec{A} t} dt\ \vec{B} = \vec{A}^{-1} ( \vec{A}_d - \vec{I} ) \vec{B},\\
+\vec{C}_d &= \vec{C},\\
+\vec{D}_d &= \vec{D},\\
+Q_d &= \int_{0}^{T_s} e^{\vec{A} t} Q e^{\vec{A}^T t} dt.
+\end{align}
+and $T_s$ is the sample time. Then
+\begin{align*}
+x(kT)=x_k \wedge y(kT) = y_k, \forall k.
+\end{align*}
+Let $g_d(k)=\mathcal{G}(t,g(t),T)$ be a function that performs the discretization described above, where $g(t)$
+represents the continuous dynamics and $g_d(k)$ the corresponding discrete dynamics. 
+Let $G(s)=\mathcal{L}(g(t))$ and $G_d(z)=\mathcal{Z}(g_d(k))$ be the corresponding Laplace and Z-transforms
+of $g(t)$ and $g_d(k)$. Given this relation, we have 
+$$G_d(z)=G(z)|_{z=e^{sT}} : g_d(k)=\mathcal{G}(t,g(t),T) \wedge T < \frac{1}{.5f_s},$$
+where $.5f_s$ is the Nyquist frequency of $g(t)$. This last restriction is introduced to avoid the effects of aliasing
+which could cause ``phantom poles'' to appear otherwise. 
+The eigenvalues of $\vec{A}_d$ corresponding to the poles of $G_d(z)$, and those of $\vec{A}$ corresponding to the poles of $G(s)$ are similarly related.
+$\hat{\lambda}_i=e^{-\lambda_iT} : \hat{\lambda}_i \in \sigma(\vec{A}_d) \wedge \lambda_i \in \sigma(\vec{A})$
+where $\sigma(\cdot)$ is the spectrum of a matrix.
+The following remark is worth mentioning regarding the above.
+\begin{remark}
+The witnessed maximum amplitude of the discrete signals $x_k,y_k$ may be smaller to that of $x(t),y(t)$ due to synchronism at fraction-frequency sampling.
+This means that reasoning about the state-space must consider the effects of this possibility as well of the case of maximal inputs from the continuous specification.
+\end{remark}
+ Since \eqref{eq:discretization} is a bisimulation of \eqref{eq:ode}, we may use the semantics in section \ref{sec:model_semantics} to model continuous dynamical systems.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Controllable Canonical Form} \label{sec:reachable}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Let us have a discrete time SISO system with an $n^{th},m^{th} : n\geq m$ order armax model
+$$y[k]=\sum_{i=1}^n a_iy[k-i]+\sum_{i=0}^m b_iu[k-i],$$
+where $y$ is the output of the system and $u$ its input.
+The equivalent LTI dynamics of such a model are:
+\begin{align}
+\label{eq:cf_SISO}
+\vec{x}_{k+1}=&\mat{A}_{cf}\vec{x}_k+\mat{B}_{cf}u_k : \vec{x}_k=[y_{k-n}\ \hdots y_{k-1}\ y_{k}]^T\\
+y_k=&\mat{C}_{cf}\vec{x}_k + b_0u_k\nonumber\\
+\mat{A}_{cf}=&\left[
+\begin{array}{ccccc}
+0&1&0&\cdots&0\\
+0&0&1&\cdots&0\\
+\vdots&\vdots&\vdots&\ddots&\vdots\\
+0&0&0&\cdots&1\\
+-a_n&-a_{n-1}&-a_{n-2}&\cdots&-a_1
+\end{array}\right],
+\mat{B}_{cf}=\left[
+\begin{array}{c}
+0\\0\\ \vdots\\ 0\\ 1
+\end{array}\right]\nonumber\\
+\mat{C}_{cf}=&[\begin{array}{ccccc}b_n-a_nb_0&b_{n-1}-a_{n-1}b_0&\cdots&b_1-a_1b_0\end{array}] : b_{i \in (m\ n]}=0\nonumber
+\end{align}
+
+where the coefficients $a_i$ describe the characteristic polynomial of the system. This matrix shape is
+called a Controllable Canonical Form because the dynamics of the feedback are directly related to these
+coefficients. Specifically, given a feedback controller $\mat{K}$ for this system, the closed loop dynamics
+will have the shape
+\begin{align}
+\mat{A}_{cf}+\mat{B}_{cf}\mat{K}_{cf}=&\left[
+\begin{array}{ccccc}
+0&1&0&\cdots&0\\
+0&0&1&\cdots&0\\
+\vdots&\vdots&\vdots&\ddots&\vdots\\
+0&0&0&\cdots&1\\
+k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
+\end{array}\right]
+\label{eq:cf_SISO_fb}
+\end{align}
+which means we can directly modify each coefficient by selecting a controller parameter.
+In the MIMO case, the Controllable Canonical Form has the following shape:
+\begin{align}
+\mat{A}_{cf}=&\left[
+\begin{array}{ccccc}
+0&\mat{I}_{n-1}&0&\cdots&0\\
+0&0&\mat{I}_{n-2}&\cdots&0\\
+\vdots&\vdots&\vdots&\ddots&\vdots\\
+0&0&0&\cdots&1\\
+-\mat{a_n}\mat{M}_n&-\mat{a_{n-1}}\mat{M}_{n-1}&-\mat{a_{n-2}}\mat{M}_{n-2}&\cdots&-\mat{a_1}\mat{M}_{1}
+\end{array}\right],
+\mat{B}_{cf}=\left[
+\begin{array}{c}
+0\\0\\ \vdots\\ 0\\ \mat{M}_0
+\end{array}\right]\nonumber\\
+\mat{C}_{cf}=&[\begin{array}{ccccc}\mat{\eta}_n&\mat{\eta}_{n-1}&\cdots&\mat{\eta}_1\end{array}] :
+\mat{I}_i,\mat{M}_i \in \mathbb{R}^{q_i \times q_i} \wedge \mat{a}_i \in \mathbb{R}^{q \times q_i} \wedge \mat{\eta}_i \in \mathbb{R}^o \wedge  \mat{\eta}_{i \in (m\ n]}=0 \nonumber
+\label{eq:cf_MIMO}
+\end{align}
+where $q$ is the number of inputs, $q_i$ the number of inputs with a transfer function of order of at least $i$, $\mat{I}_i$ an identity matrix, $\mat{M}_i$ an upper triangular matrix with 1s in its diagonal, $\mat{a_i}$ a matrix of coefficients of the $i^th$ order on its diagonal, and $o$ the number of outputs.
+Ideally we aim for $\mat{M}_i=\mat{I}_i, \forall i>0$
+
+Any LTI system can be transformed into a controllable canonical form by a matrix $\mat{T} : \vec{x}=\mat{T}\hat{\vec{x}}$
+Then the dynamics of the controllable form are
+\begin{align}
+\hat{\vec{x}}_{k+1}=&\mat{A}_{cf}\hat{\vec{x}}_k+\mat{B}_{cf}u_k : \mat{A}_{cf}=\mat{T}\mat{A}\mat{T}^{-1} \wedge \mat{B}_{cf}=\mat{T}\mat{B}\\
+y_k=&\mat{C}_{cf}\hat{\vec{x}}_k + b_0u_k : \mat{C}_{cf}=\mat{C}\mat{T}^{-1}\nonumber
+\end{align}
+where $\mat{T}$ can be calculated as follows:
+
+Let 
+\begin{equation}
+\mat{R}=[\begin{array}{ccccc}\mat{B}&\mat{A}\mat{B}&\mat{A}^2\mat{B}&\hdots&\mat{A}^{n-1}\mat{B}\end{array}]
+\label{eq:rncf}
+\end{equation}
+be the reachability matrix of the system, and
+\begin{equation}
+\mat{R}_{cf}=\left[\begin{array}{ccccc}1&a_1&a_2&\hdots&a_{n-1}\\0&1&a_1&\hdots&a_{n-2}\\ \vdots&\ddots&\ddots&\ddots&\ddots\end{array}\right]
+\label{eq:rcf}
+\end{equation}
+the reachability matrix of the canonical form. Then 
+\begin{equation}
+\mat{T}=\mat{R}_{cf}\mat{R}^{-1}
+\label{eq:to_cf}
+\end{equation}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Observable Canonical Form} \label{sec:observable}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+The Controllable Canonical Form is ideal when we have access to the state space. However, in most cyberphisical
+systems, only the outputs of the plant can be observed, hence we require an Observable Canonical Form.
+For SISO systems, this is:
+\begin{align}
+\label{of_SISO}
+\mat{A}_{of}=&\left[
+\begin{array}{ccccc}
+0&0&0&\cdots&-a_n\\
+1&0&0&\cdots&-a_{n-1}\\
+0&1&0&\cdots&-a_{n-2}\\
+\vdots&\ddots&\ddots&\ddots&\vdots\\
+0&0&\cdots&1&-a_1
+\end{array}\right],
+\mat{B}_{of}=\left[
+\begin{array}{c}
+\eta_n\\ \eta_{n-1}\\ \vdots\\ \eta_1
+\end{array}\right]\\
+\mat{C}_{of}=&[\begin{array}{ccccc}0&0&\cdots&0&1\end{array}] \nonumber
+\end{align}
+
+What is important to notice her is that $\mat{A}_{of}=\mat{A}_{cf}^T, \mat{C}_{of}=\mat{B}_{cf}^T$
+and $\mat{B}_{of}=\mat{C}_{cf}^T$, which also applies to the MIMO case.
+
+Let 
+\begin{equation}
+\label{eq:wnof}
+\mat{W}_o=[\begin{array}{ccccc}\mat{C}&\mat{A}\mat{C}&\mat{A}^2\mat{C}&\hdots&\mat{C}^{n-1}\mat{B}\end{array}]^T
+\end{equation}
+be the observability matrix of the system, and
+\begin{equation}
+\label{eq:wof}
+\mat{W}_{of}=\mat{R}_{cf}^{-1}
+\end{equation}
+the observability matrix of the canonical form (see eg~\cite{astrom1997computer}). 
+Then the dynamical system 
+\begin{equation}
+\label{eq:to_of}
+\hat{\vec{x}}_{k+1}=(\mat{A}_o-\mat{L}\mat{C}_o)\hat{\vec{x}}_k+\mat{B}_o\vec{u}+\mat{L}\vec{y} : \mat{L}=\mat{W}_o^{-1}\mat{W}_{of} \left[ \begin{array}{c}p_1-a_1\\p_2-a_2\\p_n-a_n\end{array}\right]
+\end{equation}
+\begin{displaymath}
+\mat{A}_o=\mat{A},\ \mat{B}_o=\mat{B},\ \mat{C}_o=\mat{C}
+\end{displaymath}
+is an observer of the system $\vec{x}_{k+1}=\mat{A}\vec{x}+\mat{B}\vec{u} : \vec{y}=\mat{C}\vec{x}$. $p_i$ are user selected
+values which will affect the error of the observer estimator.
+The differentiation between $\mat{*}_o$ and $\mat{*}$ will be exploited later in this work.
+For the time being we will assume they are the same.
+
+Figure \ref{fig:observersystem} shows an LTI system with a feedback control using an observer.
+Presuming a sampled model of the plant as described in \eqref{eq:discretize}, the closed loop dynamics of this system are given by:
+\begin{equation}
+\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_{k+1}
+=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}_d&\mat{B}_d\mat{K}_d\\ \mat{0}&\mat{A}_d-\mat{L}_d\mat{C}_d\end{array}\right]
+\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_k
++\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
++\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}_d\end{array}\right]\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]
+\label{eq:observer_LTI}
+\end{equation}
+where $\hat{\vec{x}}_e=\vec{x}-\hat{\vec{x}}$ is the observer error.
+Replacing the matrices in \eqref{eq:observer_LTI} with appropriate symbols, we find that it still has a similar structure to \eqref{eq:discretization} which will be helpful in our analysis.
+
+\begin{figure*}[htb]
+\centering
+
+\tikzset{add/.style n args={4}{
+    minimum width=6mm,
+    path picture={
+        \draw[circle] 
+            (path picture bounding box.south east) -- (path picture bounding box.north west)
+            (path picture bounding box.south west) -- (path picture bounding box.north east);
+        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+        }
+    }
+ }
+
+\resizebox{1.0\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
+     semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
+    \node[draw=none] (r) {$r_k$};
+    \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,] (gain)at ([xshift=1.2cm]r) {\sc $k_r$};
+
+   \& \node[circle,add={-}{+}{}{}] (circle) {};
+   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$u_k$};
+   \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Kd) at ([xshift=0,yshift=-5.5cm]circle)  {\sc $\mat{K}_d$};
+   \coordinate (kdsouth) at ([yshift=-3cm]Kd);
+
+   \& complexnode/.pic={ 
+      \node[rectangle,dashed,draw,minimum width=3cm,minimum height=1.6cm,label=\textbf{DAC}] (dac) {};
+     \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
+     \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
+     \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
+     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {\sc ZOH};
+   }
+
+   \& complexnode/.pic={ 
+      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2.5cm,yshift=.5cm]plant.center)  {\sc $\mat{B}$};
+      \node[draw=none] (u) at ([xshift=-1cm,yshift=.15cm]B)  {$u(t)$};
+      \node[circle,add={+}{+}{}{}] (p1) at ([xshift=-1.3cm,yshift=.5cm]plant.center) {};
+      \node[draw=none] (xdot) at ([xshift=.85cm,yshift=.15cm]p1)  {$\dot{\vec{x}}(t)$};   
+      \node[rectangle,draw,minimum width=1cm] (int) at ([xshift=.5cm,yshift=.5cm]plant.center) {\sc $\int$};
+      \coordinate (xsouth) at ([xshift=1cm]int);
+      \node[draw=none] (x) at ([xshift=1cm,yshift=.15cm]int)  {$\vec{x}(t)$};   
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (C) at ([xshift=2.7cm,yshift=.5cm]plant.center)  {\sc $\mat{C}$};
+      \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]C)  {$\vec{y}(t)$};   
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (A) at ([xshift=.5cm,yshift=-1cm]plant.center)  {\sc $\mat{A}$};
+      \coordinate (aeast) at ([xshift=1cm]A);
+      \coordinate (awest) at ([xshift=-1.8cm]A);
+    }
+
+   complexnode/.pic={ 
+      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=5cm,label=\textbf{Observer}] (observer)  at ([yshift=-5cm]plant.center) {};
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Bd) at ([xshift=-2.5cm]observer.center)  {\sc $\mat{B}_d$};
+      \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]Bd)  {$u_k$};
+      \node[circle,add={+}{+}{+}{}] (o1) at ([xshift=-1.3cm]observer.center) {};
+      \node[draw=none] (xd) at ([xshift=.85cm,yshift=.15cm]o1)  {$\hat{\vec{x}}_{k+1}$};   
+      \node[rectangle,draw,minimum width=1cm] (delay) at ([xshift=.5cm]observer.center) {\sc $z^{-1}$};
+      \coordinate (xdsouth) at ([xshift=1.3cm]delay);
+      \coordinate (fbsouth) at ([xshift=1.3cm,yshift=-3cm]delay);
+      \node[draw=none] (xdp) at ([xshift=1cm,yshift=.15cm]delay)  {$\hat{\vec{x}}_k$};   
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Cd) at ([xshift=2.7cm]observer.center)  {\sc $\mat{C}_d$};
+      \node[draw=none] (y) at ([xshift=.4cm,yshift=.8cm]Cd)  {$\hat{\vec{y}}_k$};   
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ad) at ([xshift=.5cm,yshift=-1.5cm]observer.center)  {\sc $\mat{A}_d$};
+      \coordinate (adeast) at ([xshift=1.3cm]Ad);
+      \coordinate (adwest) at ([xshift=-1.8cm]Ad);
+      \node[circle,add={-}{}{}{+}] (o2) at ([xshift=2.7cm,yshift=1.5cm]observer.center) {};
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ld) at ([xshift=.5cm,yshift=1.5cm]observer.center)  {\sc $\mat{L}_d$};
+      \coordinate (ldwest) at ([xshift=-1.8cm]Ld);
+      \coordinate (bdwest) at ([xshift=-5.5cm]Bd);
+      \coordinate (uksouth) at ([xshift=-5.5cm,yshift=5.5cm]Bd);
+      \coordinate (o2east) at ([xshift=6.3cm]o2);
+    }
+
+   \& complexnode/.pic={ 
+     \node[rectangle,dashed,draw,minimum width=3.5cm,minimum height=1.6cm,label=\textbf{ADC},] (adc) {};
+     \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
+     \coordinate (switch1) at ([xshift=-1cm]adc.center);
+     \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
+     \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
+     \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
+     \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
+     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]q1)  {$\vec{y}_k$};       
+     \coordinate (ykeast) at ([xshift=1.9cm]q1);
+   } 
+   \& \coordinate (aux1);
+   \& \\
+  };
+
+  \path[->] (v1) edge (q1.south);
+  \path[->] (v2) edge (q2.south);
+  \path[->] (r) edge (gain.west);
+  \path[->] (gain.east) edge (circle.west);
+  \path[->] (circle.east) edge (q2.west);
+  \path       (q2.east) edge (zoh.west);
+  \path[->] (zoh.east) edge (B.west);
+  \path
+   (B.east) edge (p1.west)
+   (p1.east) edge (int.west)
+   (xsouth) edge (aeast)
+   (aeast) edge (A.east)
+   (A.west) edge (awest)
+   (awest) edge (p1.south)
+   (int.east) edge (C.west)
+   (C.east) edge (switch1.west)
+   (switch2) edge (q1.west);
+  \path
+   (q1.east) edge (ykeast)
+   (ykeast) edge (o2east);
+  \path       (uksouth) edge (bdwest);
+  \path[->] (bdwest) edge (Bd.west);
+  \path
+   (Bd.east) edge (o1.west)
+   (o1.east) edge (delay.west)
+   (xdsouth) edge (adeast)
+   (adeast) edge (Ad.east)
+   (Ad.west) edge (adwest)
+   (adwest) edge (o1.south)
+   (o2.west) edge (Ld.east)
+   (Ld.west) edge (ldwest)
+   (ldwest) edge (o1.north)
+   (delay.east) edge (Cd.west)
+   (Cd.north) edge (o2.south)
+   (o2east) edge (o2.east)
+   (xdsouth) edge (fbsouth)
+   (fbsouth) edge (kdsouth);
+  \path[->]  (kdsouth) edge (Kd.south);
+  \path (Kd.north) edge (circle.south);
+ \end{tikzpicture}
+}
+ \caption{Closed-loop digital control system with observer\label{fig:observersystem}}
+\end{figure*}
+
 \end{document}

### 2016-12-20 cav2017/cav2017.tex
typos + line breaks in introduction

@@
 
-Linear Time Invariant Control systems represnt a sizeable portion of modern
-embedded software, performing highly non-trivial control
-tasks, with significant impact in numerous application areas such as
-environmental control, navigation and robotics~\cite{astrom1997computer,Franklin15}.
-
-Correct and sound control is non-trivial, however. The problem is exacerbated by
-artefacts specific to digital control, such as the effects of
-finite-precision arithmetic, time discretization, and quantization noise
-introduced by A/D and D/A conversion.  Thus, the programming is a key
-barrier to broad adoption of digital control, and requires considerable
-expertise.
-
-Whilst there is a vast literature in validation of control systems, the subject
-of control synthesis has been somewhat restricted in the properties it explores.
-Traditionally, this focuses mainly on the subject of stability, working typically on
-continuous domains \cite{sadabadi2016static}, or using switched models~\cite{DBLP:conf/emsoft/RavanbakhshS16}.
-Reachability tools are also used when discretizing the state-space for both verification and parametric synthesis\cite{cimatti2013parameter}.
-
-In this paper, we propose the synthesis of control algorithms for cyberphisical
-systems taking into consideration the continuous domain of the plant alongside
-the discrete domain of the controller and the hybrid elements that communicate
-them.
-
-To this end, we formalise the notion of solution generalisation for CEGIS and 
-apply CEGAR on simplified abstractions of the system in order to achieve scalability. 
-The former technique allows the inductive generalisation engine to look for 
-candidate solutions in a reduced solution space. 
-The latter case is a well know technique for abstract interpretation that allows
-simplification of the procedures over a sound abstraction of the verification model.
+Linear Time Invariant Control systems represent a sizeable portion of
+modern embedded software, performing highly non-trivial control tasks,
+with significant impact in numerous application areas such as
+environmental control, navigation and
+robotics~\cite{astrom1997computer,Franklin15}.
+
+Correct and sound control is non-trivial, however. The problem is
+exacerbated by artefacts specific to digital control, such as the
+effects of finite-precision arithmetic, time discretization, and
+quantization noise introduced by A/D and D/A conversion.  Thus, the
+programming is a key barrier to broad adoption of digital control, and
+requires considerable expertise.
+
+Whilst there is a vast literature in validation of control systems,
+the subject of control synthesis has been somewhat restricted in the
+properties it explores.  Traditionally, this focuses mainly on the
+subject of stability, working typically on continuous domains
+\cite{sadabadi2016static}, or using switched
+models~\cite{DBLP:conf/emsoft/RavanbakhshS16}.  Reachability tools are
+also used when discretizing the state-space for both verification and
+parametric synthesis\cite{cimatti2013parameter}.
+
+In this paper, we propose the synthesis of control algorithms for
+cyberphysical systems taking into consideration the continuous domain
+of the plant alongside the discrete domain of the controller and the
+hybrid elements that communicate them.
+
+To this end, we formalise the notion of solution generalisation for
+CEGIS and apply CEGAR on simplified abstractions of the system in
+order to achieve scalability.  The former technique allows the
+inductive generalisation engine to look for candidate solutions in a
+reduced solution space.  The latter case is a well know technique for
+abstract interpretation that allows simplification of the procedures
+over a sound abstraction of the verification model.
 

### 2016-12-20 cav2017/cav2017.tex
Revised intro

@@
 To this end, we formalise the notion of solution generalisation for
-CEGIS and apply CEGAR on simplified abstractions of the system in
-order to achieve scalability.  The former technique allows the
-inductive generalisation engine to look for candidate solutions in a
-reduced solution space.  The latter case is a well know technique for
-abstract interpretation that allows simplification of the procedures
-over a sound abstraction of the verification model.
+Counter-Example Guided Inductive Synthesis (CEGIS) which makes use 
+of Counter-Example Guided Abstraction Refinement (CEGAR)
+%on simplified abstractions of the system
+in order to achieve scalability.
+This strategy enables the inductive generalisation engine inside CEGIS
+to look for candidate solutions in a reduced solution space.  %% The
+%% latter case is a well know technique for abstract interpretation that
+%% allows simplification of the procedures over a sound abstraction of
+%% the verification model.
 

### 2016-12-20 cav2017/cav2017.tex
typos

@@
 Careful examination of these matrices reveals that because the $\mat{A}_t$ is upper block diagonal, the spectrum of $\mat{A}_t$ is equal to the union of the spectrum of $\mat{A}_{tp}$ and $\mat{A}_{to}$ which can be calculated separately.
-Additionally, these correspond to the roots of the polynomials
+Additionally, these correspond to the roots of the following polynomials:
 \begin{align*}
@@
 
-For a stabilised closed loop, we need these roots to remain within the unit circle (left hand side of the plane for continuous time).
-Whilst this is not a sufficient condition for verifying safety properties, it is a necessary one, therefore we will review this verification process.
-The direct approach would be to calculate the roots of the polynomials (\emph{ie} the eigenvalues of the matrix), but this ends up being to costly, particularly in the case of synthesis, so we use an indirect method.
+For a stabilised closed loop, we need these roots to remain within the
+unit circle (left hand side of the plane for continuous time).  Whilst
+this is not a sufficient condition for verifying safety properties, it
+is a necessary one, therefore we will review this verification
+process.  The direct approach would be to calculate the roots of the
+polynomials (\emph{ie} the eigenvalues of the matrix), but this ends
+up being too costly, particularly in the case of synthesis, so we use
+an indirect method.
 

### 2016-12-20 cav2017/cav2017.tex
Table

@@
 \end{itemize}
+
+\begin{table}[]
+\centering
+\footnotesize
+\caption{Test suite for space-state synthesis}
+\label{State-space benchmarks}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+%\textbf{ID \#} & 
+\textbf{System}                                                               & \textbf{A} & \textbf{B} & \textbf{C} & \textbf{D} \\ \hline
+%1              & 
+\begin{tabular}[c]{@{}c@{}}DC Motor\\ Position\end{tabular}                   & $\left[\begin{array}{ccc}
+0		& 1 		& 0						\\
+0 		& -1.087	& 8587					\\
+0		& -9964		& -1.455\times 10^{6}	\\
+\end{array}\right]$ & $\left[\begin{array}{c}
+0 \\ 0 \\ -1.455\times10^{6}
+\end{array}\right]$           & $\left[\begin{array}{ccc}
+1 & 0 & 0\\
+\end{array}\right]$ & 0 \\  \hline
+%2              & 
+\begin{tabular}[c]{@{}c@{}}Aircraft \\ Pitch\\ Dynamics\end{tabular} & $\left[\begin{array}{ccc}
+-0.313	& 56.7 		& 0		\\
+-0.0139	& -0.426	& 0		\\
+0		& 56.7		& 0		\\
+\end{array}\right]$ & $\left[\begin{array}{c}
+0.232 \\ 0.0203 \\ 0
+\end{array}\right]$ & $\left[\begin{array}{ccc}
+1 & 0 & 0\\
+\end{array}\right]$ & 0 \\ \hline
+%3            & 
+\begin{tabular}[c]{@{}c@{}}Ball\\ Magnetic\\ Levitation\end{tabular} & $\left[\begin{array}{ccc}
+0		& 1 		& 0		\\
+1752	& 0			& -34.07\\
+0		& 0			& -38.27\\
+\end{array}\right]$ & $\left[\begin{array}{c}
+0 \\ 0 \\ 1.923
+\end{array}\right]$ & $\left[\begin{array}{ccc}
+1 & 0 & 0\\
+\end{array}\right]$ & 0 \\ \hline
+%4              & 
+\begin{tabular}[c]{@{}c@{}}Buck\\ Converter\end{tabular}                      & $\left[\begin{array}{cc}
+0		& -500 \\
+4545	& -1515\\
+\end{array}\right]$ & $\left[\begin{array}{c}
+125 \\ 0 \\
+\end{array}\right]$ & $\left[\begin{array}{cc}
+ 0 & 1\\
+\end{array}\right]$ & 0 \\ \hline
+%5              & 
+\begin{tabular}[c]{@{}c@{}}Boost\\ Converter\end{tabular} & $\left[\begin{array}{cc}
+0		& -375 \\
+3409	& -1515\\
+\end{array}\right]$ & $\left[\begin{array}{c}
+500 \\ 0 \\
+\end{array}\right]$ &  $\left[\begin{array}{cc}
+0 & 1\\
+\end{array}\right]$  & 0        \\ \hline
+%6              & 
+\begin{tabular}[c]{@{}c@{}}Buck-boost\\ Converter\end{tabular} & $\left[\begin{array}{cc}
+0		& 375 \\
+-3409	& -1515\\
+\end{array}\right]$ & $\left[\begin{array}{c}
+125 \\ 0 \\
+\end{array}\right]$ & $\left[\begin{array}{cc}
+0 & 1\\
+\end{array}\right]$ & 0 \\ \hline
+%7              & 
+\begin{tabular}[c]{@{}c@{}}Automotive\\ Cruise\\ System\end{tabular} & -0.05 & 0.03125 & 0.032 & 0 \\ \hline
+%8              & 
+\begin{tabular}[c]{@{}c@{}}DC Motor\\ Rate\end{tabular} & $\left[\begin{array}{cc}
+-1000		& -13 \\
+-8			& 0\\
+\end{array}\right]$ & $\left[\begin{array}{c}
+4 \\ 0 \\
+\end{array}\right]$ & $\left[\begin{array}{cc}
+0 & 6.25\\
+\end{array}\right]$ & 0 \\ \hline
+%9              & 
+\begin{tabular}[c]{@{}c@{}}Helicopter\\ Longitudinal\\ Motion\end{tabular}    & $\left[\begin{array}{ccc}
+-0.42		& 0.0168		& -0.396	\\
+0.5			& 0				& 0			\\
+0			& 0.5 			& 0			
+\end{array}\right]$ & $\left[\begin{array}{c}
+16 \\ 0 \\ 0
+\end{array}\right]$ & $~
+\left[\begin{array}{ccc}
+0.6125	& -0.6125	& 15.44 \\
+\end{array}\right]$ & 0 \\ \hline
+%10             & 
+Pendulum   & $\left[\begin{array}{cc}
+0		& -2.453	\\
+4		& 0			\\	
+\end{array}\right]$ & $\left[\begin{array}{c}
+4 \\ 0
+\end{array}\right]$ & $\left[\begin{array}{cc}
+-1.225	& -2.15 	\\
+\end{array}\right]$           & 9.8           \\ \hline
+%11             & 
+\begin{tabular}[c]{@{}c@{}}Inverted\\ Pendulum\end{tabular} & $\left[\begin{array}{cccc}
+0		& 1		& 0 	& 0	\\
+1		& 0		& 0		& 0	\\
+0		& 1 	& 0		& 0 \\
+0		& 0		& 1 	& 0 \\	
+\end{array}\right]$ & $\left[\begin{array}{c}
+1 \\ 0 \\ 0 \\ 0
+\end{array}\right]$  & $\left[\begin{array}{cccc}
+0	& 0	& 1 & -0.75 \\
+0	& 1	& 0	& 0		
+\end{array}\right]$ & $\left[\begin{array}{c}
+0 \\
+0 \end{array}\right]$ \\ \hline
+%12             & 
+\begin{tabular}[c]{@{}c@{}}Magnetic\\ Suspension\end{tabular} & $\left[\begin{array}{cc}
+0		& 31.25	\\
+32		& 0		\\	
+\end{array}\right]$ & $\left[\begin{array}{c}
+8 \\ 0
+\end{array}\right]$ & $\left[\begin{array}{cc}
+0	& 9.766 	\\
+\end{array}\right]$ & 0 \\ \hline
+%13             & 
+\begin{tabular}[c]{@{}c@{}}Magnetic\\ Pointer \end{tabular} & $\left[\begin{array}{ccc}
+-0.271		& -0.05336	& 0	\\
+0.03125		& 0			& 0	\\
+0			& 0.01562 	& 0	\\	
+\end{array}\right]$ & $\left[\begin{array}{c}
+1 \\ 0 \\ 0
+\end{array}\right]$ & $\left[\begin{array}{ccc}
+0	& -0.5888	& -0.2562 \\
+\end{array}\right]$ & 0           \\ \hline
+%14             & 
+\begin{tabular}[c]{@{}c@{}}1/4 Car\\ Suspension\end{tabular} & $
+\left[\begin{array}{cccc}
+-516.1	& -222.1& -79.75& -33.06	\\
+256		& 0		& 0		& 0			\\
+0		& 64 	& 0		& 0 \\
+0		& 0		& 32 	& 0 \\	
+\end{array}\right]$ & $\left[\begin{array}{c}
+8 \\ 0 \\ 0 \\ 0
+\end{array}\right]$ & $\left[\begin{array}{cccc}
+0	& 0	& 9.969 & 4.133 \\
+\end{array}\right]$ & 0 \\ \hline
+%15             & 
+\begin{tabular}[c]{@{}c@{}}Computer\\ Tape\\ Driver\end{tabular} & $\left[\begin{array}{ccc}
+-1760		& -976.6	& -457.8	\\
+1024		& 0			& 0			\\
+0			& 512 		& 0			\\	
+\end{array}\right]$ & $\left[\begin{array}{c}
+8 \\ 0 \\ 0
+\end{array}\right]$ & $\left[\begin{array}{ccc}
+1.5	& 2.051	& 1.144 \\
+\end{array}\right]$ & 0           \\ \hline
+%16             & 
+\begin{tabular}[c]{@{}c@{}}USCG \\ Cutter\\ Tampa\\ Heading\\ Angle\end{tabular} & $\left[\begin{array}{ccc}
+-0.271		& -0.05336	& 0	\\
+0.03125		& 0			& 0			\\
+0			& 0.01562 	& 0			\\	
+\end{array}\right]$ & , $\left[\begin{array}{c}
+1 \\ 0 \\ 0
+\end{array}\right]$ & $\left[\begin{array}{ccc}
+0	& -0.5888	& -0.2562 \\
+\end{array}\right]$ & 0 \\ \hline
+\end{tabular}
+\end{table}
 

### 2016-12-21 cav2017/cav2017.tex

@@
 
-The first plant represents a DC motor position model from~\cite{CTMS}.
+The table~\ref{table:State-space benchmarks} summarizes the list of benchmarks extracted from literature~\cite{Franklin15,converters,maglev,CTMS} and adopted in our experiments.
+
+%The first plant represents a DC motor position model from~\cite{CTMS}.
 It is a third order system and presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
-$$
-\textbf{A}=\left[\begin{array}{ccc}
-0		& 1 		& 0						\\
-0 		& -1.087	& 8587					\\
-0		& -9964		& -1.455\times 10^{6}	\\
-\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
-0 \\ 0 \\ -1.455\times10^{6}
-\end{array}\right]
-$$
+%$$
+%\textbf{A}=\left[\begin{array}{ccc}
+%0		& 1 		& 0						\\
+%0 		& -1.087	& 8587					\\
+%0		& -9964		& -1.455\times 10^{6}	\\
+%\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
+%0 \\ 0 \\ -1.455\times10^{6}
+%\end{array}\right]
+%$$
+%%
+%$$
+%\textbf{C}=\left[\begin{array}{ccc}
+%1 & 0 & 0\\
+%\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
+%\theta \\ \dot{\theta} \\ i \\
+%\end{array}\right],
+%$$
+%where the states $\theta$, $\dot{\theta}$, and $i$ are respectively the rotor angular position, rotor angular rate and the current of armature. The DC motor is stable in open loop.
 %
-$$
-\textbf{C}=\left[\begin{array}{ccc}
-1 & 0 & 0\\
-\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
-\theta \\ \dot{\theta} \\ i \\
-\end{array}\right],
-$$
-where the states $\theta$, $\dot{\theta}$, and $i$ are respectively the rotor angular position, rotor angular rate and the current of armature. The DC motor is stable in open loop.
-
-The second benchmark is an aircraft pitch dynamics model extracted from~\cite{CTMS}.
+%The second benchmark is an aircraft pitch dynamics model extracted from~\cite{CTMS}.
 It is a third order system and it presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
-$$
-\textbf{A}=\left[\begin{array}{ccc}
--0.313	& 56.7 		& 0		\\
--0.0139	& -0.426	& 0		\\
-0		& 56.7		& 0		\\
-\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
-0.232 \\ 0.0203 \\ 0
-\end{array}\right]
-$$
+%$$
+%\textbf{A}=\left[\begin{array}{ccc}
+%-0.313	& 56.7 		& 0		\\
+%-0.0139	& -0.426	& 0		\\
+%0		& 56.7		& 0		\\
+%\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
+%0.232 \\ 0.0203 \\ 0
+%\end{array}\right]
+%$$
+%%
+%$$
+%\textbf{C}=\left[\begin{array}{ccc}
+%0 & 0 & 1\\
+%\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
+%\alpha \\ \dot{\theta} \\ \theta \\
+%\end{array}\right],
+%$$
+%where the states $\alpha$, $\dot{\theta}$, and $\theta$ are respectively the aircraft attack angle, pitch rate and the pitch angle.
+The aircraft pitch dynamic is critically stable in open loop, with a pole in origin of $s$-plane.
 %
-$$
-\textbf{C}=\left[\begin{array}{ccc}
-0 & 0 & 1\\
-\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
-\alpha \\ \dot{\theta} \\ \theta \\
-\end{array}\right],
-$$
-where the states $\alpha$, $\dot{\theta}$, and $\theta$ are respectively the aircraft attack angle, pitch rate and the pitch angle.
-The aircraft pitch dynamic is critically stable in open loop, with a pole in origin of $s$-plane.
-
-The third benchmark is a ball magnetic levitation model extracted from~\cite{maglev}.
+%The third benchmark is a ball magnetic levitation model extracted from~\cite{maglev}.
 It is a third order system presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
-$$
-\textbf{A}=\left[\begin{array}{ccc}
-0		& 1 		& 0		\\
-1752	& 0			& -34.07\\
-0		& 0			& -38.27\\
-\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
-0 \\ 0 \\ 1.923
-\end{array}\right]
-$$
+%$$
+%\textbf{A}=\left[\begin{array}{ccc}
+%0		& 1 		& 0		\\
+%1752	& 0			& -34.07\\
+%0		& 0			& -38.27\\
+%\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
+%0 \\ 0 \\ 1.923
+%\end{array}\right]
+%$$
+%%
+%$$
+%\textbf{C}=\left[\begin{array}{ccc}
+%1 & 0 & 0\\
+%\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
+%z \\ \dot{z} \\ i \\
+%\end{array}\right],
+%$$
+%where the states $z$, $\dot{z}$, and $i$ are respectively the vertical displacement of the ball, its rate and the coil current. This system  is unstable in open loop.
 %
-$$
-\textbf{C}=\left[\begin{array}{ccc}
-1 & 0 & 0\\
-\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
-z \\ \dot{z} \\ i \\
-\end{array}\right],
-$$
-where the states $z$, $\dot{z}$, and $i$ are respectively the vertical displacement of the ball, its rate and the coil current. This system  is unstable in open loop.
-
-There are three benchmarks representing classic DC-DC converters: buck, boost, and buck-boost.
+%There are three benchmarks representing classic DC-DC converters: buck, boost, and buck-boost.
 They are SISO second-order systems stable in open-loop, and their state vector is $\textbf{x}=\textbf{x}=\left[\begin{array}{c}
-i_{L} \\ v_{C}\\
-\end{array}\right]$, where $i_{L}$ is the current in the coil and $v_{c}$ is the voltage on the capacitor.
+%i_{L} \\ v_{C}\\
+%\end{array}\right]$, where $i_{L}$ is the current in the coil and $v_{c}$ is the voltage on the capacitor.
 The matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, and $\textbf{D}$ for the buck converter are:
-$$
-\textbf{A}=\left[\begin{array}{cc}
-0		& -500 \\
-4545	& -1515\\
-\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-125 \\ 0 \\
-\end{array}\right]~
-\textbf{C}=\left[\begin{array}{cc}
-0 & 1\\
-\end{array}\right],~ \textbf{D}= 0.
-$$
-
-The matrices of the boost converter are:
-$$
-\textbf{A}=\left[\begin{array}{cc}
-0		& -375 \\
-3409	& -1515\\
-\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-500 \\ 0 \\
-\end{array}\right]~
-\textbf{C}=\left[\begin{array}{cc}
-0 & 1\\
-\end{array}\right],~ \textbf{D}= 0.
-$$
-
-Finally, the matrices of the buck-boost converter are:
-$$
-\textbf{A}=\left[\begin{array}{cc}
-0		& 375 \\
--3409	& -1515\\
-\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-125 \\ 0 \\
-\end{array}\right]~
-\textbf{C}=\left[\begin{array}{cc}
-0 & 1\\
-\end{array}\right],~ \textbf{D}= 0.
-$$
-
-Additionally, various dynamic systems model were extracted from~\cite{Franklin15} and incorporated to our test suite. They are: 
-\begin{itemize}
-\item{\textbf{automotive cruise control system:} 
-$$
-\textbf{A}=-0.05,~ \textbf{B} = 0.03125~
-\textbf{C}=0.032,~ \textbf{D}= 0;
-$$
-}
-\item{\textbf{DC motor:} 
-$$
-\textbf{A}=\left[\begin{array}{cc}
--1000		& -13 \\
--8			& 0\\
-\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-4 \\ 0 \\
-\end{array}\right]~
-\textbf{C}=\left[\begin{array}{cc}
-0 & 6.25\\
-\end{array}\right],~ \textbf{D}= 0;
-$$
-}
-\item{\textbf{helicopter longitudinal motion:} 
-$$
-\textbf{A}=\left[\begin{array}{ccc}
--0.42		& 0.0168		& -0.396	\\
-0.5			& 0				& 0			\\
-0			& 0.5 			& 0			
-\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-16 \\ 0 \\ 0
-\end{array}\right]~
-\textbf{C}=\left[\begin{array}{ccc}
-0.6125	& -0.6125	& 15.44 \\
-\end{array}\right],~ \textbf{D}= 0;
-$$
-}
-\item{\textbf{inverted pendulum cart position:} 
-$$
-\textbf{A}=\left[\begin{array}{cccc}
-0		& 1		& 0 	& 0	\\
-1		& 0		& 0		& 0	\\
-0		& 1 	& 0		& 0 \\
-0		& 0		& 1 	& 0 \\	
-\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-1 \\ 0 \\ 0 \\ 0
-\end{array}\right]~
-\textbf{C}=\left[\begin{array}{cccc}
-0	& 0	& 1 & -0.75 \\
-\end{array}\right],~ \textbf{D}= 0;
-$$
-}
-\item{\textbf{inverted pendulum angle:} 
-$$
-\textbf{A}=\left[\begin{array}{cc}
-0		& 1	\\
-1		& 0	\\
-\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-1 \\ 0 \\ 0 \\ 0
-\end{array}\right]~
-\textbf{C}=\left[\begin{array}{cc}
- 0	& 1 \\
-\end{array}\right],~ \textbf{D}= 0;
-$$
-}
-\item{\textbf{magnetic pointer:} 
-$$
-\textbf{A}=\left[\begin{array}{ccc}
--0.271		& -0.05336	& 0	\\
-0.03125		& 0			& 0	\\
-0			& 0.01562 	& 0	\\	
-\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-1 \\ 0 \\ 0
-\end{array}\right]~
-\textbf{C}=\left[\begin{array}{ccc}
-0	& -0.5888	& -0.2562 \\
-\end{array}\right],~ \textbf{D}= 0;
-$$
-}
-\item{\textbf{magnetic suspension:} 
-$$
-\textbf{A}=\left[\begin{array}{cc}
-0		& 31.25	\\
-32		& 0		\\	
-\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-8 \\ 0
-\end{array}\right]~
-\textbf{C}=\left[\begin{array}{cc}
-0	& 9.766 	\\
-\end{array}\right],~ \textbf{D}= 0;
-$$
-}
-\item{\textbf{pendulum:} 
-$$
-\textbf{A}=\left[\begin{array}{cc}
-0		& -2.453	\\
-4		& 0			\\	
-\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-4 \\ 0
-\end{array}\right]~
-\textbf{C}=\left[\begin{array}{cc}
--1.225	& -2.15 	\\
-\end{array}\right],~ \textbf{D}= 9.8;
-$$
-}
-\item{\textbf{1/4 car suspension:} 
-$$
-\textbf{A}=\left[\begin{array}{cccc}
--516.1	& -222.1& -79.75& -33.06	\\
-256		& 0		& 0		& 0			\\
-0		& 64 	& 0		& 0 \\
-0		& 0		& 32 	& 0 \\	
-\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-8 \\ 0 \\ 0 \\ 0
-\end{array}\right]~
-\textbf{C}=\left[\begin{array}{cccc}
-0	& 0	& 9.969 & 4.133 \\
-\end{array}\right],~ \textbf{D}= 0;
-$$
-}
-\item{\textbf{computer tape driver:} 
-$$
-\textbf{A}=\left[\begin{array}{ccc}
--1760		& -976.6	& -457.8	\\
-1024		& 0			& 0			\\
-0			& 512 		& 0			\\	
-\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-8 \\ 0 \\ 0
-\end{array}\right]~
-\textbf{C}=\left[\begin{array}{ccc}
-1.5	& 2.051	& 1.144 \\
-\end{array}\right],~ \textbf{D}= 0;
-$$
-}
-\item{\textbf{USCG cutter Tampa heading angle:} 
-$$
-\textbf{A}=\left[\begin{array}{ccc}
--0.271		& -0.05336	& 0	\\
-0.03125		& 0			& 0			\\
-0			& 0.01562 	& 0			\\	
-\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-1 \\ 0 \\ 0
-\end{array}\right]~
-\textbf{C}=\left[\begin{array}{ccc}
-0	& -0.5888	& -0.2562 \\
-\end{array}\right],~ \textbf{D}= 0;
-$$
-}
-\end{itemize}
-
-\begin{table}[]
+%$$
+%\textbf{A}=\left[\begin{array}{cc}
+%0		& -500 \\
+%4545	& -1515\\
+%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+%125 \\ 0 \\
+%\end{array}\right]~
+%\textbf{C}=\left[\begin{array}{cc}
+%0 & 1\\
+%\end{array}\right],~ \textbf{D}= 0.
+%$$
+%
+%The matrices of the boost converter are:
+%$$
+%\textbf{A}=\left[\begin{array}{cc}
+%0		& -375 \\
+%3409	& -1515\\
+%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+%500 \\ 0 \\
+%\end{array}\right]~
+%\textbf{C}=\left[\begin{array}{cc}
+%0 & 1\\
+%\end{array}\right],~ \textbf{D}= 0.
+%$$
+%
+%Finally, the matrices of the buck-boost converter are:
+%$$
+%\textbf{A}=\left[\begin{array}{cc}
+%0		& 375 \\
+%-3409	& -1515\\
+%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+%125 \\ 0 \\
+%\end{array}\right]~
+%\textbf{C}=\left[\begin{array}{cc}
+%0 & 1\\
+%\end{array}\right],~ \textbf{D}= 0.
+%$$
+%
+%Additionally, various dynamic systems model were extracted from~\cite{Franklin15} and incorporated to our test suite. They are: 
+%\begin{itemize}
+%\item{\textbf{automotive cruise control system:} 
+%$$
+%\textbf{A}=-0.05,~ \textbf{B} = 0.03125~
+%\textbf{C}=0.032,~ \textbf{D}= 0;
+%$$
+%}
+%\item{\textbf{DC motor:} 
+%$$
+%\textbf{A}=\left[\begin{array}{cc}
+%-1000		& -13 \\
+%-8			& 0\\
+%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+%4 \\ 0 \\
+%\end{array}\right]~
+%\textbf{C}=\left[\begin{array}{cc}
+%0 & 6.25\\
+%\end{array}\right],~ \textbf{D}= 0;
+%$$
+%}
+%\item{\textbf{helicopter longitudinal motion:} 
+%$$
+%\textbf{A}=\left[\begin{array}{ccc}
+%-0.42		& 0.0168		& -0.396	\\
+%0.5			& 0				& 0			\\
+%0			& 0.5 			& 0			
+%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+%16 \\ 0 \\ 0
+%\end{array}\right]~
+%\textbf{C}=\left[\begin{array}{ccc}
+%0.6125	& -0.6125	& 15.44 \\
+%\end{array}\right],~ \textbf{D}= 0;
+%$$
+%}
+%\item{\textbf{inverted pendulum cart position:} 
+%$$
+%\textbf{A}=\left[\begin{array}{cccc}
+%0		& 1		& 0 	& 0	\\
+%1		& 0		& 0		& 0	\\
+%0		& 1 	& 0		& 0 \\
+%0		& 0		& 1 	& 0 \\	
+%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+%1 \\ 0 \\ 0 \\ 0
+%\end{array}\right]~
+%\textbf{C}=\left[\begin{array}{cccc}
+%0	& 0	& 1 & -0.75 \\
+%\end{array}\right],~ \textbf{D}= 0;
+%$$
+%}
+%\item{\textbf{inverted pendulum angle:} 
+%$$
+%\textbf{A}=\left[\begin{array}{cc}
+%0		& 1	\\
+%1		& 0	\\
+%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+%1 \\ 0 \\ 0 \\ 0
+%\end{array}\right]~
+%\textbf{C}=\left[\begin{array}{cc}
+% 0	& 1 \\
+%\end{array}\right],~ \textbf{D}= 0;
+%$$
+%}
+%\item{\textbf{magnetic pointer:} 
+%$$
+%\textbf{A}=\left[\begin{array}{ccc}
+%-0.271		& -0.05336	& 0	\\
+%0.03125		& 0			& 0	\\
+%0			& 0.01562 	& 0	\\	
+%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+%1 \\ 0 \\ 0
+%\end{array}\right]~
+%\textbf{C}=\left[\begin{array}{ccc}
+%0	& -0.5888	& -0.2562 \\
+%\end{array}\right],~ \textbf{D}= 0;
+%$$
+%}
+%\item{\textbf{magnetic suspension:} 
+%$$
+%\textbf{A}=\left[\begin{array}{cc}
+%0		& 31.25	\\
+%32		& 0		\\	
+%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+%8 \\ 0
+%\end{array}\right]~
+%\textbf{C}=\left[\begin{array}{cc}
+%0	& 9.766 	\\
+%\end{array}\right],~ \textbf{D}= 0;
+%$$
+%}
+%\item{\textbf{pendulum:} 
+%$$
+%\textbf{A}=\left[\begin{array}{cc}
+%0		& -2.453	\\
+%4		& 0			\\	
+%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+%4 \\ 0
+%\end{array}\right]~
+%\textbf{C}=\left[\begin{array}{cc}
+%-1.225	& -2.15 	\\
+%\end{array}\right],~ \textbf{D}= 9.8;
+%$$
+%}
+%\item{\textbf{1/4 car suspension:} 
+%$$
+%\textbf{A}=\left[\begin{array}{cccc}
+%-516.1	& -222.1& -79.75& -33.06	\\
+%256		& 0		& 0		& 0			\\
+%0		& 64 	& 0		& 0 \\
+%0		& 0		& 32 	& 0 \\	
+%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+%8 \\ 0 \\ 0 \\ 0
+%\end{array}\right]~
+%\textbf{C}=\left[\begin{array}{cccc}
+%0	& 0	& 9.969 & 4.133 \\
+%\end{array}\right],~ \textbf{D}= 0;
+%$$
+%}
+%\item{\textbf{computer tape driver:} 
+%$$
+%\textbf{A}=\left[\begin{array}{ccc}
+%-1760		& -976.6	& -457.8	\\
+%1024		& 0			& 0			\\
+%0			& 512 		& 0			\\	
+%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+%8 \\ 0 \\ 0
+%\end{array}\right]~
+%\textbf{C}=\left[\begin{array}{ccc}
+%1.5	& 2.051	& 1.144 \\
+%\end{array}\right],~ \textbf{D}= 0;
+%$$
+%}
+%\item{\textbf{USCG cutter Tampa heading angle:} 
+%$$
+%\textbf{A}=\left[\begin{array}{ccc}
+%-0.271		& -0.05336	& 0	\\
+%0.03125		& 0			& 0			\\
+%0			& 0.01562 	& 0			\\	
+%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
+%1 \\ 0 \\ 0
+%\end{array}\right]~
+%\textbf{C}=\left[\begin{array}{ccc}
+%0	& -0.5888	& -0.2562 \\
+%\end{array}\right],~ \textbf{D}= 0;
+%$$
+%}
+%\end{itemize}
+
+\begin{table}[HTB]
 \centering
@@
 \caption{Test suite for space-state synthesis}
-\label{State-space benchmarks}
+\label{table:State-space benchmarks}
 \begin{tabular}{|c|c|c|c|c|}

### 2016-12-21 cav2017/cav2017.tex
review introduction

@@
 
-Linear Time Invariant Control systems represent a sizeable portion of
+Linear Time Invariant (LTI) control systems represent a sizeable portion of
 modern embedded software, performing highly non-trivial control tasks,
 with significant impact in numerous application areas such as
-environmental control, navigation and
+environmental control, navigation, and 
 robotics~\cite{astrom1997computer,Franklin15}.
-
-Correct and sound control is non-trivial, however. The problem is
-exacerbated by artefacts specific to digital control, such as the
-effects of finite-precision arithmetic, time discretization, and
-quantization noise introduced by A/D and D/A conversion.  Thus, the
-programming is a key barrier to broad adoption of digital control, and
-requires considerable expertise.
+Correct and sound control system verification is a challenging task. 
+In particular, the verification problem is exacerbated by artifacts specific 
+to digital control, such as the effects of finite-precision arithmetic, 
+time discretization, and quantization noise, which are typically introduced 
+by Analog-to-Digital (A/D) and Digital-to-Analog (D/A) conversion.  
+Thus, the programming is a key barrier to broad adoption of digital control, 
+and requires considerable expertise.
 
@@
 also used when discretizing the state-space for both verification and
-parametric synthesis\cite{cimatti2013parameter}.
-
-In this paper, we propose the synthesis of control algorithms for
+parametric synthesis~\cite{cimatti2013parameter}.
+In this paper, however, we propose the synthesis of control algorithms for
 cyberphysical systems taking into consideration the continuous domain
-of the plant alongside the discrete domain of the controller and the
+of the plant, alongside the discrete domain of the controller and the
 hybrid elements that communicate them.
@@
 To this end, we formalise the notion of solution generalisation for
-Counter-Example Guided Inductive Synthesis (CEGIS) which makes use 
-of Counter-Example Guided Abstraction Refinement (CEGAR)
+Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
+of Counter-Example Guided Abstraction Refinement (CEGAR),
 %on simplified abstractions of the system
@@
 %% the verification model.
+
+\textcolor{red}{Cristina: Can you please further expand the introduction
+by adding more details about our synthesis approach to control systems?}
 

### 2016-12-21 cav2017/cav2017.tex
review Preliminaries

@@
 %-------------------------------
-In this work we will focus on Linear Dynamical Cyberphisical Systems with
-continuous plants described by ODEs in the form
+In this study, we focus on Linear Dynamical Cyber-Physical Systems with
+continuous plants described by Ordinary Differential Equations (ODEs) 
+in the form
+%
 \begin{align}
@@
 \dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\\
-\vec{y}(t)&=\mat{C}\vec{x}+\mat{D}\vec{u}\nonumber
+\vec{y}(t)&=\mat{C}\vec{x}+\mat{D}\vec{u},\nonumber
 \end{align}
@@
 \vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
-\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k\nonumber
+\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k,\nonumber
 \end{align}
-and Digital Controllers in the form
+%
+and digital controllers in the form
+%
 \begin{equation}
-\vec{u}_k=\mat{K}_d\vec{y}_k
+\vec{u}_k=\mat{K}_d\vec{y}_k.
 \end{equation}
+%
 The output of the plant is being sampled by an ADC, and since the full state of the
@@
 estimates the state of the plant (see appendix for details on how such an observer
-is constructed).
-
-We further presume that there are small tolerances in the system described in the
-following form
+is constructed). We further presume that there are small tolerances in the system 
+described in the following form
+%
 \begin{align*}
 \mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
-\mat{B} \in \mathcal{G}_B
+\mat{B} \in \mathcal{G}_B.
 \end{align*}
 
-Finally, we also require a safety specification $\Psi(\vec{u},\vec{y})$ which is
+Finally, we also require a safety specification $\Psi(\vec{u},\vec{y})$, which is
 given as a set of linear constraints over the inputs and outputs.

### 2016-12-21 cav2017/cav2017.tex
Added comments to Preliminaries

@@
 \end{align}
-which are soundly discretized (as shown in the appendix) into 
+\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
+$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, 
+$\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
+a digital system. Eq.~\ref{eq:ode} is soundly discretized 
+(as shown in the appendix) into 
+\textcolor{red}{Dario: Can you please describe all terms used in the equation?}
+%
 \begin{align}
@@
 and digital controllers in the form
+\textcolor{red}{Dario: Can you please describe all terms used in the equation?}
 %
@@
 described in the following form
+\textcolor{red}{Dario: Can you please describe all terms used in the equation?}
 %

### 2016-12-21 cav2017/cav2017.tex
Added comments to Counter-Example Guided Inductive Synthesis with solution generalisation

@@
 This technique relies on parametrising the target language, which
-induces a lattice of progressively more expressive languages.  We
+induces a lattice of progressively more expressive languages 
+\textcolor{red}{Cristina: Citation?}.  We
 start by attempting to synthesise a program at the lowest point on
@@
 
-\textcolor{red}{LC: Dario and Cristina, may I ask you to expand further this section by connecting it to our control-synthesis work?}
+\textcolor{red}{Cristina: How does this section relate to our control-synthesis work? 
+This is text is too generic...}
+
 \begin{figure}
@@
 \end{tikzpicture}
-\caption{The CEGIS loop with solution generalisation\label{fig:CEGIS-multiple-verif}.}
+\caption{The CEGIS loop with solution generalisation\label{fig:CEGIS-multiple-verif}. 
+\textcolor{red}{Cristina: What is the difference of this figure to that in our HSCC paper?}}
 \end{figure}

### 2016-12-21 cav2017/cav2017.tex
review Verification of a Conrollable Observed System

@@
 
-Let us recall the formulas used for SISO systems in sections \ref{sec:reachable} and \ref{sec:observable}.
+Let us recall the formulas used for single-input and single-output (SISO) systems 
+in sections \ref{sec:reachable} and \ref{sec:observable}.
 A controllable and observable system will have the following dynamics:
+\textcolor{red}{Dario: Do we really need to describe all these equations here?
+Should we simply cite them from a given reference?}
+%
 \begin{align}
@@
 
-Careful examination of these matrices reveals that because the $\mat{A}_t$ is upper block diagonal, the spectrum of $\mat{A}_t$ is equal to the union of the spectrum of $\mat{A}_{tp}$ and $\mat{A}_{to}$ which can be calculated separately.
+Careful examination of these matrices reveals that because the $\mat{A}_t$ is 
+upper block diagonal, the spectrum of $\mat{A}_t$ is equal to the union of the 
+spectrum of $\mat{A}_{tp}$ and $\mat{A}_{to}$, which can be calculated separately. 
 Additionally, these correspond to the roots of the following polynomials:
+%
 \begin{align*}
@@
 
-For a stabilised closed loop, we need these roots to remain within the
+For a stabilized closed-loop, we need these roots to remain within the
 unit circle (left hand side of the plane for continuous time).  Whilst
 this is not a sufficient condition for verifying safety properties, it
-is a necessary one, therefore we will review this verification
-process.  The direct approach would be to calculate the roots of the
-polynomials (\emph{ie} the eigenvalues of the matrix), but this ends
+is a necessary one; therefore, we review this verification process.  
+The direct approach would be to calculate the roots of the
+polynomials (\emph{i.e.}, the matrix eigenvalues), but this ends
 up being too costly, particularly in the case of synthesis, so we use
@@
 
-Jury's criteria is a mathematical method used to verify whether the roots of the polynomial are within the unit circle by exploring solely the coefficients of the polynomial.
-In order to achieve this, we first create a matrix $\mat{M} \in \mathbb{R}^{(n+1) \times (n+1)}$ with zero-indexed coefficients $m_{i,j} : i,j \in [0,n],k=n-(i-1)$ in the following form:
-
+Jury's criteria is a mathematical method used to verify whether the roots 
+of the polynomial are within the unit circle by exploring solely the coefficients 
+of the polynomial. In order to achieve this, we first create a matrix 
+$\mat{M} \in \mathbb{R}^{(n+1) \times (n+1)}$ with zero-indexed coefficients 
+$m_{i,j} : i,j \in [0,n],k=n-(i-1)$ in the following form:
+%
 \begin{equation}
@@
 Notice also that every row has a polynomial one degree lower than the previous. 
-The sufficient and necessary conditions for the polynomial in row 0 to have all of its roots inside the unit circle are~\cite{astrom1997computer}:
+The sufficient and necessary conditions for the polynomial in row $0$ 
+to have all of its roots inside the unit circle are~\cite{astrom1997computer}:
+%
 \begin{align}
@@
 Notice that in both our polynomials $c_0=1$ and we only use reals.
-Now that we have established convergence, we may examine the safety specification of the state space.
-In the case of SISO systems, this is given by a range of the input and a range of the output which are considered safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in [\underline{y}\ \ \overline{y}]$).
-Whilst there are other properties we may include in the verification, we will solely focus on these for simplicity of the explanation.
-We will assume that we do not want saturation in our system, hence the control loop has only one mode. We have also identified the quantization noise as a bounded non-deterministic input.
-First we must translate the safety specification into the statespace. Replacing on the second part of equation \eqref{eq:observer_LTI_cf} we obtain
+Now that we have established convergence, we may examine the safety 
+specification of the state space. In the case of SISO systems, 
+this is given by a range of the input and a range of the output, 
+which are considered safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in [\underline{y}\ \ \overline{y}]$). 
+Whilst there are other properties, we may include in the verification, 
+we will solely focus on these for simplicity of the explanation.
+We will assume that we do not want saturation in our system, 
+hence the control loop has only one mode. We have also identified 
+the quantization noise as a bounded non-deterministic input.
+First we must translate the safety specification into the state-space. 
+Replacing on the second part of equation \eqref{eq:observer_LTI_cf} we obtain
+%
 \begin{equation}
@@
 \end{equation}
-Note that we use the bounds of the input after the transformation by $\mat{B}$ since the matrix may reverse the bounds.
-Equation \eqref{eq:of_bounds} can be solved using linear programming as it describes a polyhedral region in $\mathbb{R}^n$.
-The second step is evaluating the progression of the system over time in order to calculate $\vec{x}_k$ to validte against this specification.
-For this step we require an initial set from which the system progresses.
-Obviously, this set $\vec{x}_0$ must satisfy the specification, otherwise the system will be unsafe to begin with.
-We will accept a specification in the form $\mat{E}\mat{T}\vec{x}_0<\mat{f}$. The presence of $\mat{T}$ is because this will typically be given in the original state-space.
-Accelerating \eqref{eq:observer_LTI_cf}, we obtain:
+Note that we use the bounds of the input after the transformation by $\mat{B}$ 
+since the matrix may reverse the bounds. Eq.~\eqref{eq:of_bounds} can be solved 
+using linear programming as it describes a polyhedral region in $\mathbb{R}^n$.
+The second step is evaluating the progression of the system over time to calculate 
+$\vec{x}_k$ to validate against this specification. For this step we require 
+an initial set from which the system progresses. Obviously, this set $\vec{x}_0$ 
+must satisfy the specification; otherwise, the system will be unsafe to begin with.
+We accept a specification in the form $\mat{E}\mat{T}\vec{x}_0<\mat{f}$. 
+The presence of $\mat{T}$ is because this will typically be given in the original 
+state-space. Accelerating \eqref{eq:observer_LTI_cf}, we obtain:
+%
 \begin{align}
@@
 \end{align}
-which would still require us to verify the system for every $k$ up to infinity. Instead we will use abstract acceleration~\cite{cattaruzza2015unbounded}, which translates the formula into
+which would still require us to verify the system for every $k$ up to infinity. 
+Instead we use abstract acceleration~\cite{cattaruzza2015unbounded}, which translates the formula into
+%
 \begin{align}
@@
 \end{align}
+%
 where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A}^k, \mathcal{B}_{tp}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tp}, \mathcal{B}_{tn}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tn}$ are abstract matrices for the system in \eqref{eq:observer_LTI_cf}.

### 2016-12-21 paper/paper.tex
small fixes
table 1 nudges
nudge

@@
 space of polynomials of $n$-th order, $\mathcal{P}^{n}\langle I,F
-\rangle$ is is the space of polynomials with coefficients in
+\rangle$ is the space of polynomials with coefficients in
 $\mathbb{R}\langle I,F \rangle$, and $\mathcal{P}^{n,m}$,  $\mathcal{P}^{n,m}\langle I,F
@@
 \centering
-\begin{tabular}{ | c | c | l | r r || r | r | }
+\begin{tabular}{| r | c | l | r r || r | r |}
 \hline
 \# & Plant  & Benchmark                  & $I$ & $F$
-   & \multicolumn{1}{|c|}{1-step} & \multicolumn{1}{|c|}{2-step}
+   & 1-step & 2-step
     \\\hline\hline
@@
 introduced by FWL does not make the digital system unstable.  A more recent
-approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
+approach~\cite{DBLP:journals/automatica/WuLCC09} uses the $\mu$-calculus to
 directly model the digital controller so that the selected parameters are

### 2016-12-21 cav2017/cav2017.tex
Some fixed based on conversations with Cristina

@@
 \label{eq:ode}
-\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\\
-\vec{y}(t)&=\mat{C}\vec{x}+\mat{D}\vec{u},\nonumber
+\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
+\vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
 \end{align}
 \noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
-$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, 
-$\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
-a digital system. Eq.~\ref{eq:ode} is soundly discretized 
+$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
+a continuous plant. Eq.~\ref{eq:ode} is soundly discretized 
 (as shown in the appendix) into
-\textcolor{red}{Dario: Can you please describe all terms used in the equation?}
 %
@@
 \begin{equation}
-\vec{u}_k=\mat{K}_d\vec{y}_k.
+\vec{u}_k=\mat{K}_d\vec{y}_k\ \ :\ \ \mat{K}_d \in \mathbb{R}^{m \times o}.
 \end{equation}
@@
 \begin{align*}
-\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
+\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J \wedge
 \mat{B} \in \mathcal{G}_B.
@@
 \item Calculate $\mat{T}$ and $\mat{W}_o^{-1}\mat{W}_{of}$ using equations \eqref{eq:rncf}\eqref{eq:rcf}\eqref{eq:to_cf}\eqref{eq:wnof}\eqref{eq:wof}
-\item Extract the Plant's characteristic polynomial coefficients from the last row of $P_a=\mat{T}\mat{A}\mat{T}^-1$.
+\item Extract the Plant's characteristic polynomial coefficients from the last row of $P_a=(\mat{T}\mat{A}\mat{T}^-1)_{n*}$.
 \item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors ($\frac{q_1}{2},\frac{q_2}{2},q_3$)
+\item Produce an initial abstraction which corresponds to an unconstrained solution space.
 \end{enumerate}
@@
 These are the rows of $\mat{E} \in \Psi$ that intersect/segment $\hat{X}^\#$.
-Transforming these rows into the eigenspace of $\mat{A}_t$, and applying backward acceleration to obtain a set of counterexamples for the eigenvalues, which we define as $\Psi_{\lambda}$ .
-\item Transform the soft constraints on the eigenvalues defined in the counterexample into soft constraints on the coefficients of the characteristic polynomial. 
-$z^n+\sum_{i=1}^n[a_i-k_i]z^{n-i}=\prod_{i=1}^n (z-[\lambda_i]) : |[\lambda_i]|<1 \wedge [\lambda_i] \models \Psi_{\lambda}$.
-\item Pass the refined abstraction with the new contraints to the synthesiser and repeat the loop again.
+Transforming these rows into the eigenspace of $\mat{A}_t$, and applying backward acceleration to obtain a set of counterexamples for the eigenvalues, which we define as $\Psi(\Lambda)$.
+This is a constraint in the spectrum (\emph{ie} frequency response transfer function) of the closed loop dynamics.
+\item Transform the soft constraints on the spectrum into soft constraints on the coefficients of the characteristic polynomial. 
+$z^n+\sum_{i=1}^n[a_i-k_i]z^{n-i}=\prod_{i=1}^n (z-[\lambda_i]) : |[\lambda_i]|<1 \wedge [\lambda_i] \models \Psi_{\Lambda}$.
+\item Pass the refined abstraction with the new contraints to the synthesiser, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again.
+We note that the Abstraction refinement is a soft constraint on the proposed model which can increase or decrease the parameter space at any time, whereas the concrete counterexample passed to the synthesiser is monotonically decreasing.
+The first one improves speed of the tool whereas the second ensures convergence.
 
@@
    \& ;\\
-   \&\node[fill=yellow!20,align=center] (pre) {{\sc pre-}\\{\sc processing}};
-   \& \node[fill=yellow!20,align=center] (abstract) {\sc abstraction};
+   \&\node[fill=yellow!20,align=center] (pre) {{\sc 1. pre-}\\{\sc processing}};
+   \& \node[fill=yellow!20,align=center] (abstract) {\sc 4. abstraction};
         \node[draw=none] (FIK) at ([xshift=2.5cm,yshift=.3cm]abstract)  {\sc $\Psi (\mat{K})$};
@@
    \& 
-   \& \node[fill=yellow!20,align=center, minimum width=3cm] (synth) {\sc synthesiser};
+   \& \node[fill=yellow!20,align=center, minimum width=3cm] (synth) {\sc 2. synthesiser};
        \node[draw=none] (KL) at ([xshift=2.5cm,yshift=-.25cm]synth)  {\sc $\mat{K},\mat{L}$};
-       \node[draw=none] (NKL) at ([xshift=2cm,yshift=1.2cm]synth)  {\sc $\neg \mat{K}, \mat{L}, \mat{A}$};
-   \& \node[fill=yellow!20,align=center, minimum width=4cm] (verify) {\sc verifier ($\Psi$)};
+       \node[draw=none] (NKL) at ([xshift=2cm,yshift=1cm]synth)  {\sc $P_a$};
+   \& \node[fill=yellow!20,align=center, minimum width=4cm] (verify) {\sc 3. verifier ($\Psi$)};
        \node[draw=none] (VUNS) at ([xshift=.6cm,yshift=1cm]verify)  {\sc UNSAT};
@@
      \coordinate (auxsynth);
-     \node[draw,rectangle,align=center] (KSAT) at ([xshift=-.8cm]auxsynth.center) {\sc SAT\\Solver};
-     \node[draw,rectangle,align=center] (LSAT) at ([xshift=.8cm]auxsynth.center) {\sc SAT\\Solver};
+     \node[draw,rectangle,align=center] (KSAT) at ([xshift=-.8cm]auxsynth.center) {\sc Prog.\\Search};
+     \node[draw,rectangle,align=center] (LSAT) at ([xshift=.8cm]auxsynth.center) {\sc Prog.\\Search};
      \node[draw=none] (SATK) at ([xshift=-.5cm,yshift=1.5cm]KSAT)  {$\mathcal{J}_K$};
@@
 
-\begin{table}[HTB]
+\begin{table}[htb]
 \centering

### 2016-12-22 hscc2017/paper.tex
prep for final version
line breaks

--- 2016-12-21 paper/paper.tex
@@
-\documentclass{sig-alternate-05-2015}
+\documentclass[final]{sig-alternate-05-2015}
 
@@
 
-\renewcommand{\baselinestretch}{0.975}
+%\renewcommand{\baselinestretch}{0.975}
+\allowdisplaybreaks
 \include{macros}
@@
 controller is illustrated in Figure~\ref{fig:sampledsystem}.  The DAC and
-ADC converters introduce quantization errors which are modeled as noises $\nu_{1}(z)$ and $\nu_{2}(z)$,
-$G(s)$ is the continuous-time plant model with parametric additive
-uncertainty $\Delta_p{G}_n(s)$ and $\Delta_p{G}_d(s)$, $R(z)$ is the reference signal, $U(z)$ is
-the control signal, and $\hat{Y}(z)$ is the output signal affected by the
-noises and uncertainties in the closed-loop system.
+ADC converters introduce quantization errors which are modeled as noises
+$\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model
+with parametric additive uncertainty $\Delta_p{G}_n(s)$ and
+$\Delta_p{G}_d(s)$, $R(z)$ is the reference signal, $U(z)$ is the control
+signal, and $\hat{Y}(z)$ is the output signal affected by the noises and
+uncertainties in the closed-loop system.
 %
@@
 us to simultaneously evaluate the whole collection of plants $\mathfrak{G}$
-plus the effects of numeric calculations in the engine.
-Synthesized controllers using this verifier will always
-be stable for all plants in the family.
+plus the effects of numeric calculations in the engine.  Synthesized
+controllers using this verifier will always be stable for all plants in the
+family.
 % and only generate counterexamples when the precision of the
@@
 whether the system is unstable for the current candidate solution, i.e., if
-$\neg \phi_\mathit{stability}$ is satisfiable for $S(z)$.  If this is the
-case, then we obtain a counterexample $\tilde G(z)$,
+$\neg \phi_\mathit{stability}$ is satisfiable for~$S(z)$.  If this is the
+case, then we obtain a counterexample~$\tilde G(z)$,
 %
@@
 
-If the {\sc Uncertainty} verification stage concludes that
-the system is stable for the current candidate solution,
-then we pass this solution to the second verification stage, {\sc Precision}, 
-which checks the propagation of the error in the fixed-point 
-calculations using a Fixed-point Arithmetic Verifier based on 
-interval arithmetic. 
+If the {\sc Uncertainty} verification stage concludes that the system is
+stable for the current candidate solution, then we pass this solution to the
+second verification stage, {\sc Precision}, which checks the propagation of
+the error in the fixed-point calculations using a Fixed-point Arithmetic
+Verifier based on interval arithmetic.
 %

### 2016-12-26 cav2017/cav2017.tex
Quantization noise

@@
 \usepackage{tikz}
+\usepackage{pgfplots}
 \usepackage{framed}
@@
 
-%-------------------------------
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsection{Discretising Continuous Space Dynamics}
-%-------------------------------
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 
@@
  Since \eqref{eq:discretization} is a bisimulation of \eqref{eq:ode}, we may use the semantics in section \ref{sec:model_semantics} to model continuous dynamical systems.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Modelling Quantization as noise}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathbb{R}\langle I_{adc},F_{adc} \rangle$ value.
+this sampling uses a threshold which is defined by the less significant bit ($q_{adc}=2^{-F_{adc}}$) of the adc and some nonlinearities of the circuitry.
+The overall conversion is
+$$\mathcal{F}\langle I_{adc},F_{adc} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{adc}}{2}\ \ \ \ y(t)+\frac{q_{adc}}{2}\right]$$.
+If we denote the error in the conversion as $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{adc}}{2}\ \ \frac{q_{adc}}{2}]$.
+
+We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (\emph{ie} the quantizer includes any digital gain added in the code).
+The process of quantization in the DAC is similar except that it is going from $\mathbb{R}\langle I_{adc},F_{adc} \rangle \rightarrow \mathbb{R}\langle I_{dac},F_{dac} \rangle$.
+If these domains are the same ($I_{adc}=I_{dac},F_{adc}=F_{dac}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
+From the above equations we can now infer that $\nu_1 \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], \nu_2 \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{adc} \wedge q_2=q_{dac}$.
+Note that these bounds hold irrespective of whether the noise is correlated, hence we may use them to overapproximate the effect of the noise on the state space progression over time.
+The resulting dynamics are:
+\begin{align}
+\label{eq:pre_quantization}
+\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d(\vec{u}_k+{\vec{\nu}_2}_k) + \vec{w}_k,\\
+y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k+{\vec{\nu}_1}_k. 
+\end{align}
+
+Which, when modelled into closed loop dynamics results in:
+
+\begin{align}
+\label{eq:quantization}
+\vec{x}_{k+1} &= (\vec{A}_d-\vec{B}_d\mat{K}_d\mat{C}_d) \vec{x}_k+\vec{B}_d{\vec{\nu}_2}_k + \vec{w}_k,\\
+y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k+{\vec{\nu}_1}_k. 
+\end{align}
 

### 2016-12-26 cav2017/cav2017.tex
Comments on the tolerances

@@
 %
-and digital controllers in the form
-\textcolor{red}{Dario: Can you please describe all terms used in the equation?}
+and digital controllers creating a feedback loop in the form
 %
@@
 \end{equation}
+%
+where $\mat{K}_d$ are the feedback coefficients.
 %
@@
 described in the following form
-\textcolor{red}{Dario: Can you please describe all terms used in the equation?}
 %
 \begin{align*}
-\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J \wedge
-\mat{B} \in \mathcal{G}_B.
+\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
 \end{align*}
+
+Where $\mathcal{G}_J$ is a collection of eigenvalue ranges that define the frequency response of the system.
+We presume that the internal model of the plant is an ARMA model, modified by a
+state transform that has no tolerances. Tolerances in the eigenvectors will manifest themselves
+as tolerances in the canonical forms outside of the row/column of interests and complicate the 
+evaluation. Whilst it is possible to address these with this methodology, we will focus on the case
+above for simplicity.
 

### 2016-12-28 hscc2017/paper.tex
implement comment related to "Fig 3: clarifications #47"

@@
 Given a model for a plant in ANSI-C syntax as input (Steps 1--3), \tool
-constructs a non-deterministic model to represent the plant family (Step~A),
+constructs a non-deterministic model to represent the plant family,
+i.e., it addresses plant variations as interval sets (Step~A),
 and formulates a function (Step~B) using implementation details provided in
 Steps~$2$ and $3$ to calculate the parameters of the controller to be
-synthesized (Step~C).  Finally, \tool builds an intermediate ANSI-C code for
-the digital system implementation, which is used as input for the CEGIS
-engine (Step~D).
+synthesized (Step~C).  Note that \tool synthesizes the controller 
+coefficients for the given implementation aspects, i.e., numerical
+representation and realization form.  Finally, \tool builds an intermediate 
+ANSI-C code for the digital system implementation, which is used as input 
+for the CEGIS engine (Step~D).
 

### 2016-12-28 hscc2017/paper.tex
Implement "Fig 3: arrow heads #46"
implement comment "Please provide the non-expert reader with characteristics of FWL in particular what are the practical meaning of I and F?"

@@
 disturbances from the FWL effects, with roundoffs in coefficients that may
-change the closed-loop poles and zeros position, and consequently affect its
+change closed-loop poles and zeros position, and consequently affect its
 stability, as argued in~\cite{Bessa16}.
 
-Let $\hat{C}(z)$ be the transfer function of the digital controller
-represented using this FWL with integer size $I$ and fractional size~$F$. 
+Let $\hat{C}(z)$ be the digital controller transfer function
+represented using this FWL with integer size $I$ and fractional size~$F$;
+$I$ affects the representation range and is set to avoid overflows, 
+while $F$ affects the precision and the truncation process after the 
+arithmetic operations. These variables are chosen depending on 
+hardware features.  In general-purpose processors and
+DSP's, $I$ is minimized to avoid overflows and $F$ is employed for the
+remaining bit representation. Other flexible hardware structures
+(e.g., FPGAs) allow the design of $F$ and $I$, which affects directly
+the number of logical gates.
+
 We shall denote the FWL domain of coefficients as $\mathbb{R}\langle I,F
@@
 \centering
-\includegraphics[width=\textwidth]{figures/verification-flow.pdf}
+\includegraphics[width=\textwidth]{figures/verification-flow.png}
 \vspace{1ex}

### 2016-12-28 hscc2017/paper.tex
Review conclusions to make the contributions clearer (https://github.com/kroening/control-synthesis/issues/48)

@@
 
-We have presented a CEGIS-based approach implemented in a tool called \tool,
-which uses inductive synthesis in conjunction with an algorithm for
-verifying robust closed-loop stability.  In particular, \tool is able to
-compute a parametric solution for a stabilizing digital controller given a
-continuous (or discrete) plant specification.  This enables us to
-automatically synthesize correct-by-construction digital controllers for a
-given model of their physical environment.  Our approach addresses the
-effects of the quantizers (A/D and D/A converters) as time discretization
-elements with quantization noise.  Our experimental results show that \tool
+We have presented a CEGIS-based approach implemented in a tool 
+called \tool, which uses inductive synthesis in conjunction with 
+an algorithm for verifying robust closed-loop stability that addresses 
+plant variations as interval sets as well as FWL uncertainties in digital 
+controllers. The present approach is novel in the control system 
+literature in that it puts forward a fully automated synthesis approach that 
+is algorithmically and numerically sound. In particular, \tool marks the first 
+use of the CEGIS paradigm, which handles plants with uncertain models and 
+FWL effects over the digital controller.  Note that implementing this architecture 
+efficiently requires adjusting the traditional CEGIS refinement loop to the use 
+of a two-stage verification engine: here the first stage performs fast, but potentially 
+unsound fixed-point operations, whereas the second stage restores soundness 
+by validating the operations performed by the first stage using interval 
+arithmetic. Our experimental results show that \tool
 is able to synthesize stable controllers in most benchmarks within
-a reasonable amount of time fully automatically.
-%
-% and can be 
-%complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
-%Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
-
-Future work will be the extension of this CEGIS-based approach to further
-classes of systems, including state-space representation.  We will also
-consider performance requirements while synthesizing the digital controller.
+a reasonable amount of time fully automatically.  Future work will be the 
+extension of this CEGIS-based approach to further classes of systems, 
+including state-space.  We will also consider performance 
+requirements while synthesizing the digital controller.
 

### 2016-12-28 hscc2017/paper.tex
minor changes

@@
 uncertainties and $\Delta_q \vec{G}$ is the term that reflects the
-quantization effects on the plant model.
+quantization effects on the plant model, {\it i.e.} $\Delta_q \vec{G}$ is 
+a model that incorporates the effects of $\nu$ in $\vec{\hat{G}}$ to 
+investigate the consequences in the stability of system, once our stability 
+analysis is based on polynomial coefficients and not over signals.
 
@@
 \begin{equation}
-\hat{Y}(z)=\hat{C}(z)\hat{G}(z)[R(z)+\nu_{1}(z)]+\nu_{2}(z)\hat{G}(z)-\hat{Y}(z)\hat{C}(z)\hat{G}(z),
+\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\cdot C(z)\cdot R(z)+\hat{G}(z)\cdot\nu_{2}(z)-\hat{G}(z)\cdot \hat{C}(z)\cdot \hat{Y}(z)
 \end{equation}
+%
+%
+%
 %
@@
 \label{eq:outputfunctions}
-\hat{Y}(z)=H_{1}[R(z)+\nu_{1}(z)]+H_{2}(z)\nu_{2}(z),
+\hat{Y}(z)=H_{1}(z)\nu_{1}(z)+H_{2}(z)\cdot\nu_{2}(z)+H_{3}(z)\cdot R(z)
 \end{equation}
@@
 \begin{equation}
-H_{1}=\frac{\hat{C}(z)\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
+H_{1}(z)=\frac{1}{1+\hat{G}(z)\cdot \hat{C}(z)}
 \end{equation}
 %
+\begin{equation}
+H_{2}(z)=\frac{\hat{G}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}
+\end{equation}
+%
 and
@@
 \begin{equation}
-H_{2}=\frac{\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)}.
+H_{3}(z)=\frac{\hat{G}(z)\cdot \hat{C}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}
 \end{equation}

### 2016-12-28 cav2017/cav2017.tex
Fixed Fig 2

@@
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=.2cm, column sep=.2cm] {
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=.8cm, column sep=.2cm] {
    \coordinate (aux1);
@@
    \& \node[fill=yellow!20,align=center] (abstract) {\sc 4. abstraction};
-        \node[draw=none] (FIK) at ([xshift=2.5cm,yshift=.3cm]abstract)  {\sc $\Psi (\mat{K})$};
-   \& \node[fill=yellow!20,align=center] (counter) {\sc counterexample};\\
+       % \node[draw=none] (FIK) at ([xshift=2.5cm,yshift=.3cm]abstract)  {\sc $\Psi (\mat{K})$};
+   \& \coordinate (aux); \\ % \node[fill=yellow!20,align=center] (counter) {\sc counterexample};\\
    \& 
    \& \node[fill=yellow!20,align=center, minimum width=3cm] (synth) {\sc 2. synthesiser};
-       \node[draw=none] (KL) at ([xshift=2.5cm,yshift=-.25cm]synth)  {\sc $\mat{K},\mat{L}$};
-       \node[draw=none] (NKL) at ([xshift=2cm,yshift=1cm]synth)  {\sc $P_a$};
+       %\node[draw=none] (KL) at ([xshift=2.5cm,yshift=-.25cm]synth)  {\sc $\mat{K},\mat{L}$};
+       %\node[draw=none] (NKL) at ([xshift=2cm,yshift=1cm]synth)  {\sc $P_a$};
    \& \node[fill=yellow!20,align=center, minimum width=4cm] (verify) {\sc 3. verifier ($\Psi$)};
-       \node[draw=none] (VUNS) at ([xshift=.6cm,yshift=1cm]verify)  {\sc UNSAT};
-       \node[draw=none] (SAT) at ([xshift=2.5cm,yshift=-.3cm]verify)  {\sc SAT};
+       %\node[draw=none] (VUNS) at ([xshift=.6cm,yshift=1cm]verify)  {\sc SAT};
+       \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc UNSAT};
    \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
@@
     (abstract.south) edge (synth.north)
-    (synth.east) edge (verify.west)
+    %([yshift=2em]synth.east) edge node {Candidate} ([yshift=2em]verif.west)
+    %([yshift=-2em]verif.west) edge node {New input} ([yshift=-2em]synth.east)
+    %([yshift=2em]synth.east) edge node[xshift=-0.7em] {Candidate} ([yshift=2em]verif.west)
+    %([yshift=-2em]verif.west) edge node[xshift=-0.7em] {New input} ([yshift=-2em]synth.east)
+    ([yshift=1em]synth.east) edge node {$\mat{K},\mat{L}$} ([yshift=1em]verify.west)
+    ([yshift=-1em]verify.west) edge node {$P_a$} ([yshift=-1em]synth.east)
+    (aux) edge (abstract.east) 
     (verify.east) edge (done.west);
@@
     (AAV.north) edge ([xshift=4.9cm]verify.south)
-    (verify.north) edge (counter.south)
-    (counter.west) edge (abstract.east)
-    (counter.south west) edge (synth.north east)
+    %(verify.north) edge (counter.south)
+    %(counter.west) edge (abstract.east)
+    %(counter.south west) edge (synth.north east)
     (FAIL.north) edge (done.south);
@@
      (KUNSAT.east) edge (LUNSAT.west)
+     (verify.north) edge node {$\Psi (\mat{K})$} (aux)
      (LUNSAT.east) edge (FAIL.west);
 \end{tikzpicture}
-\caption{The CEGIS loop with CEGAR\label{fig:CEGARIS}.}
+\caption{The CEGIS loop with abstraction refinement\label{fig:CEGARIS}.}
 \end{figure}

### 2016-12-28 cav2017/cav2017.tex
combine the 2 CEGIS sections

@@
 
-%-------------------------------
-\section{Counter-Example Guided Inductive Synthesis with solution generalisation}
-%-------------------------------
-
-This technique relies on parametrising the target language, which
-induces a lattice of progressively more expressive languages 
-\textcolor{red}{Cristina: Citation?}.  We
-start by attempting to synthesise a program at the lowest point on
-this lattice and increase the parameters of the language until we
-reach a point at which the synthesis succeeds. As well as giving us an
-automatic search procedure, this parametrisation greatly increases the
-efficiency of our system since languages low down the lattice are very
-easy to decide safety for (i.e. the validation oracle finds an answer
-fast). If a program can be synthesised in a low-complexity language,
-the whole procedure finishes much faster than if synthesis had been
-attempted in a high-complexity language.
-
-\textcolor{red}{Cristina: How does this section relate to our control-synthesis work? 
-This is text is too generic...}
-
-\begin{figure}
-\centering
-\hspace*{-1cm}
-\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
-},
-          row sep=1cm, column sep=1.5cm] {
-   \coordinate (aux1);
-   \& \coordinate (aux2);
-   \& ;\\
-   \node[fill=yellow!20,align=center] (synth) {{\sc inductive}\\{\sc generalisation}};
-   \&
-   complexnode/.pic={ 
-     \node[rectangle,draw,dashed,
-	minimum width=6.7cm,
-	minimum height=.8cm,
-	label={\sc Validation oracles},] (verif) {};
-   \node[fill=yellow!20] (verif1) at ([xshift=-2.1cm]verif.center) {{\sc Validate}};
-   \node[fill=yellow!20,align=center] (verif2) at ([xshift=1.7cm]verif.center) {{\sc validate general}};
-   } 
-   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
-   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
+%% %-------------------------------
+%% \section{Counter-Example Guided Inductive Synthesis with solution generalisation}
+%% %-------------------------------
+
+%% This technique relies on parametrising the target language, which
+%% induces a lattice of progressively more expressive languages 
+%% \textcolor{red}{Cristina: Citation?}.  We
+%% start by attempting to synthesise a program at the lowest point on
+%% this lattice and increase the parameters of the language until we
+%% reach a point at which the synthesis succeeds. As well as giving us an
+%% automatic search procedure, this parametrisation greatly increases the
+%% efficiency of our system since languages low down the lattice are very
+%% easy to decide safety for (i.e. the validation oracle finds an answer
+%% fast). If a program can be synthesised in a low-complexity language,
+%% the whole procedure finishes much faster than if synthesis had been
+%% attempted in a high-complexity language.
+
+%% \textcolor{red}{Cristina: How does this section relate to our control-synthesis work? 
+%% This is text is too generic...}
+
+%% \begin{figure}
+%% \centering
+%% \hspace*{-1cm}
+%% \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
+%%   \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
+%% },
+%%           row sep=1cm, column sep=1.5cm] {
+%%    \coordinate (aux1);
+%%    \& \coordinate (aux2);
+%%    \& ;\\
+%%    \node[fill=yellow!20,align=center] (synth) {{\sc inductive}\\{\sc generalisation}};
 %%    \&
-   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
-   \& \\
-   \& \\
-   \node (gp) {Program Search};
-   \&
-   complexnode/.pic={ 
-     \coordinate (aux);
-   \node (bmc) at ([xshift=-2.1cm]aux.center) {SAT/SMT Solver};
-   \node (fp)  at ([xshift=1.9cm]aux.center) {SAT/SMT Solver};
-   }   
-    \\
-  };
-
-   \path
-    ([yshift=2em]synth.east) edge node[xshift=-0.7em] {Candidate} ([yshift=2em]verif1.west)
-    ([yshift=-2em]verif1.west) edge node[xshift=-0.7em] {New input} ([yshift=-2em]synth.east)
-    (verif1) edge node {Generalise} (verif2)
-    ([xshift=5em]verif1.south) edge node[align=center] {Candidate} ([xshift=5em]bmc.north)
-    ([xshift=5em]verif2.south) edge node[align=center] {Candidate} ([xshift=3.8em]fp.north)
-    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif1.south)
-    ([xshift=-6.2em]fp.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif2.south)
-    (verif2) edge node {} (done)
-    ([xshift=5em]synth.south) edge node[align=center] {{\sc Inputs}} ([xshift=5em]gp.north)
-    ([xshift=-5em]gp.north) edge node[align=center] {No solution/\\Candidate} ([xshift=-5em]synth.south)
-    (aux1) edge (synth.north);
-   \path[-]
-   (verif2.north) edge node[align=center] {} ([xshift=5.6cm]aux2)
-   ([xshift=5.6cm]aux2) edge node[align=center] {Increase parameters} (aux1);
-
-\end{tikzpicture}
-\caption{The CEGIS loop with solution generalisation\label{fig:CEGIS-multiple-verif}. 
-\textcolor{red}{Cristina: What is the difference of this figure to that in our HSCC paper?}}
-\end{figure}
-
-  %% \textcolor{red}{LC: Cristina, can you please fix this figure? The text ``candidate'' overlaps with the dotted box.}
+%%    complexnode/.pic={ 
+%%      \node[rectangle,draw,dashed,
+%% 	minimum width=6.7cm,
+%% 	minimum height=.8cm,
+%% 	label={\sc Validation oracles},] (verif) {};
+%%    \node[fill=yellow!20] (verif1) at ([xshift=-2.1cm]verif.center) {{\sc Validate}};
+%%    \node[fill=yellow!20,align=center] (verif2) at ([xshift=1.7cm]verif.center) {{\sc validate general}};
+%%    } 
+%%    \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
+%%    %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
+%%    %% \&
+%%    %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
+%%    \& \\
+%%    \& \\
+%%    \node (gp) {Program Search};
+%%    \&
+%%    complexnode/.pic={ 
+%%      \coordinate (aux);
+%%    \node (bmc) at ([xshift=-2.1cm]aux.center) {SAT/SMT Solver};
+%%    \node (fp)  at ([xshift=1.9cm]aux.center) {SAT/SMT Solver};
+%%    }   
+%%     \\
+%%   };
+
+%%    \path
+%%     ([yshift=2em]synth.east) edge node[xshift=-0.7em] {Candidate} ([yshift=2em]verif1.west)
+%%     ([yshift=-2em]verif1.west) edge node[xshift=-0.7em] {New input} ([yshift=-2em]synth.east)
+%%     (verif1) edge node {Generalise} (verif2)
+%%     ([xshift=5em]verif1.south) edge node[align=center] {Candidate} ([xshift=5em]bmc.north)
+%%     ([xshift=5em]verif2.south) edge node[align=center] {Candidate} ([xshift=3.8em]fp.north)
+%%     ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif1.south)
+%%     ([xshift=-6.2em]fp.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif2.south)
+%%     (verif2) edge node {} (done)
+%%     ([xshift=5em]synth.south) edge node[align=center] {{\sc Inputs}} ([xshift=5em]gp.north)
+%%     ([xshift=-5em]gp.north) edge node[align=center] {No solution/\\Candidate} ([xshift=-5em]synth.south)
+%%     (aux1) edge (synth.north);
+%%    \path[-]
+%%    (verif2.north) edge node[align=center] {} ([xshift=5.6cm]aux2)
+%%    ([xshift=5.6cm]aux2) edge node[align=center] {Increase parameters} (aux1);
+
+%% \end{tikzpicture}
+%% \caption{The CEGIS loop with solution generalisation\label{fig:CEGIS-multiple-verif}. 
+%% \textcolor{red}{Cristina: What is the difference of this figure to that in our HSCC paper?}}
+%% \end{figure}
+
+%%   %% \textcolor{red}{LC: Cristina, can you please fix this figure? The text ``candidate'' overlaps with the dotted box.}
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\todo{Integrate this paragraph better (Cristina):}
+Out CEGIS technique with abstraction refinement
+relies on parametrising the target language, which
+induces a lattice of progressively more expressive languages.  We
+start by attempting to synthesise a program at the lowest point on
+this lattice and increase the parameters of the language until we
+reach a point at which the synthesis succeeds. As well as giving us an
+automatic search procedure, this parametrisation greatly increases the
+efficiency of our system since languages low down the lattice are very
+easy to decide safety for (i.e. the validation oracle finds an answer
+fast). If a program can be synthesised in a low-complexity language,
+the whole procedure finishes much faster than if synthesis had been
+attempted in a high-complexity language.
+
 Now that we have explained the verification process, we may proceed to describe the synthesis procedure, which is illustrated in figure \ref{fig:CEGARIS}.

### 2016-12-30 hscc2017/paper.tex
Fig 3
grants
squeeze paragraphs with a single word in the last line

@@
 \title{
-Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants
+Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous
+Plants%
+\thanks{Supported by EPSRC grant EP/J012564/1
+and ERC project 280053 (CPROVER).}
 %Counterexample-guided Synthesis of Closed-loop Digital Control Systems
@@
 environmental control and robotics~\cite{astrom1997computer, Franklin15}.
-
 Correct and sound control is non-trivial, however. The problem is exacerbated by
@@
 
-Our work addresses particularly challenging aspects of the control synthesis
+Our work addresses challenging aspects of the control synthesis
 problem.  We perform digital control synthesis over a hybrid model, where
@@
 digitization effects, we have modeled a digital equivalent of the plant by
-evaluating the effects of the quantizers (A/D and D/A converters) as time
+evaluating the quantizers effects (A/D and D/A converters) as time
 discretization elements with quantization noise.  The resulting closed-loop
@@
 paper are typically used in closed loops with continuous (physical) plants. 
-Thus, the proposed approach has to consider dynamics of continuous parts of
+Thus, the proposed approach considers dynamics of continuous parts of
 the system (i.e., the plant) and of discrete parts (i.e., the digital
@@
 \label{eq:outputfunctions}
-\hat{Y}(z)=H_{1}(z)\nu_{1}(z)+H_{2}(z)\cdot\nu_{2}(z)+H_{3}(z)\cdot R(z)
+\hat{Y}(z)=H_{1}(z)\nu_{1}(z)+H_{2}(z)\cdot\nu_{2}(z)+H_{3}(z)\cdot R(z),
 \end{equation}
@@
 \centering
-\includegraphics[width=\textwidth]{figures/verification-flow.png}
-\vspace{1ex}
+\includegraphics[width=0.9\textwidth]{figures/verification-flow.pdf}
+\vspace{0.1cm}
 \caption{Overview of the synthesis process\label{DSSynth_process}}
@@
 numbers (i.e., $4$ bits for the integer part and $16$ bits for the
-fractional part) can be modeled as follows:
+fractional part) can be modeled as:
 %
@@
 performance of our inductive synthesis approach can be leveraged in those
-scenarios as well.
+scenarios.
 
@@
 controllers~\cite{das2013lqr, ghosh2013fpga} focus on time discretization,
-failing to account for these error-inducing effects and can therefore result
-in digital systems that are unstable even though they have been proven to be
+failing to account for these error-inducing effects and can result in digital 
+systems that are unstable even though they have been proven to be
 robustly stable in a continuous space.
@@
 
-Other tools such as~\cite{economakos2016automated} are directly aimed at
-robust stability problems, but they fail to take the effects of FWL into
+Other tools such as~\cite{economakos2016automated} are aimed at
+robust stability problems, but they fail to take the FWL effects into
 account.  In order to provide a correct-by-design digital controller,

### 2016-12-30 hscc2017/paper.tex
replace verification-flow by synthesis-flow
fix typo

@@
 \centering
-\includegraphics[width=0.9\textwidth]{figures/verification-flow.pdf}
+\includegraphics[width=0.9\textwidth]{figures/synthesis-flow.pdf}
 \vspace{0.1cm}
@@
 directly model the digital controller so that the selected parameters are
-stable by design.  Most work in verification focusses on finding a correct
-variant of a known controller, e.g., by looking for optimal parameter
+stable by design.  Most work in verification focuses on finding a correct
+variant of a known controller, looking for optimal parameter
 representations using FWL, but ignore the effects of rounding errors due to

### 2016-12-30 hscc2017/paper.tex
squeeze paragraphs with a single word in the last line

@@
 
-In order to simplify the presentation, we employ a notation based on the
-coefficients of the polynomials.  Let $\mathcal{P}^{N}$ be a polynomial
+We employ a notation based on the polynomials coefficients to simplify 
+the presentation.  Let $\mathcal{P}^{N}$ be a polynomial
 domain of order $N$. Let $P \in \mathcal{P}^{M,N}$ be a rational polynomial
@@
 the unit circle \cite{Astrom08}.  Analyzing Eq.~\eqref{eq:outputfunctions},
-the following proposition gives necessary conditions for BIBO stability of
-the closed-loop system in Figure~\ref{fig:sampledsystem}, since the
+the following proposition gives necessary conditions for the closed-loop system 
+BIBO stability in Figure~\ref{fig:sampledsystem}, since the
 exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$ are bounded.
@@
 Proposition~\ref{prop:eq_int_stab} provides the necessary conditions for the
-digital controller to stabilize the closed-loop system, considering plant
+controller to stabilize the closed-loop system, considering plant
 parametric uncertainties (i.e., $\Delta_p \vec{G}$), quantization noises
-($\nu_{1}$ and $\nu_{2}$) and FWL effects in the control software.  Notice
+($\nu_{1}$ and $\nu_{2}$) and FWL effects in the control software.  Note
 that the model for plant uncertainty due to quantization noise (i.e.,
@@
 Proposition~\ref{prop:eq_int_stab} are satisfied and if the quantization
-noise is bounded.  The boundedness of the quantization noise comes from
+noise is bounded.  The quantization noise boundedness comes from
 Assumption~\ref{whitenoise}.
@@
 
-Given a model for a plant in ANSI-C syntax as input (Steps 1--3), \tool
+Given a plant model in ANSI-C syntax as input (Steps 1--3), \tool
 constructs a non-deterministic model to represent the plant family,
@@
 and formulates a function (Step~B) using implementation details provided in
-Steps~$2$ and $3$ to calculate the parameters of the controller to be
+Steps~$2$ and $3$ to calculate the controller parameters to be
 synthesized (Step~C).  Note that \tool synthesizes the controller 
@@
 %\end{itemize}
-
+%
 The stability property is then encoded by creating a
@@
 %$\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
-
-Given the use of fixed-point arithmetic, 
-we need to examine the effect of discretization during these operations.
-Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
-using fixed-point bit vectors.%  with integer size $I_p$ and fractional
+%
+Given the use of fixed-point arithmetic, we examine the discretization effect 
+during these operations. Let $\tilde C(z)$ and $\tilde G(z)$ be 
+transfer functions represented using fixed-point bit-vectors.
+%  with integer size $I_p$ and fractional
 % size $F_p$, whose domain is $\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
@@
 where $\Delta_b\hat{c}_i=\hat{c}_i\bmod \tilde{c}_i$
-and $\Delta_b{G}$ represents the plant uncertainty caused by
-the rounding off effect.  We may encompass all the uncertainty as
+and $\Delta_b{G}$ represent the plant uncertainty caused by
+the rounding off effect.  We encompass all the uncertainty as
 $\Delta{\vec{G}}=\Delta_p{\vec{G}}+\Delta_b{\vec{G}}$. 
-Since the complexity of SAT solvers is worst-case exponential in the size of
+Since the SAT solvers complexity is worst-case exponential in the size of
 the problem instance, our algorithm tries to solve the problem first for a
@@
 % domain.
-
 There are two approaches for the {\sc verify} phase.
@@
 
-In the next {\sc synthesize} phase, we get a new candidate solution that
+In the {\sc synthesize} phase, we get a new candidate solution that
 eliminates the new, higher precision counterexample:
@@
 {\sc uncertainty} and {\sc precision} in the {\sc verify} phase. 
-Figure~\ref{fig:bode} compares the Bode diagram of the illustrative example
-using the digital controller represented by
-Eq.~\eqref{Eq:running-example-controller}
+Figure~\ref{fig:bode} compares the Bode diagram using the digital controller 
+represented by Eq.~\eqref{Eq:running-example-controller}
 from~\cite{DBLP:conf/hybrid/WangGRJF16} (Figure~\ref{fig:original}) and the
 final candidate solution from our synthesizer
-(Figure~\ref{fig:cegiscontroller}).  The final solution from \tool is stable
+(Figure~\ref{fig:cegiscontroller}).  The \tool final solution is stable
 since it presents an infinite phase margin and a gain margin of $17.8$\,dB.
@@
 %
-\noindent where $I$ is the inertia moment of the satellite about its mass
+\noindent where $I$ is the satellite inertia moment about its mass
 center, $\tau_{C}$ is the control torque applied by the thrusters, and
@@
 with 96\,GB of RAM and Linux OS.  All times given are wall clock time in
-seconds as measured by the UNIX date command.  For the approach using a
-two-stage verification engine we apply a timeout of 8 hours per benchmark,
-and 24 hours for the approach using a one-stage engine.
+seconds as measured by the UNIX date command.  For the two-stage verification 
+engine we apply a timeout of 8 hours per benchmark, and 24 hours for the approach 
+using a one-stage engine.
 

### 2017-01-02 hscc2017/paper.tex
wording

@@
 $\Delta{\vec{G}}=\Delta_p{\vec{G}}+\Delta_b{\vec{G}}$. 
-Since the SAT solvers complexity is worst-case exponential in the size of
-the problem instance, our algorithm tries to solve the problem first for a
-low $I_p$, $F_p$, iteratively increasing the precision if it is insufficient.
+%
+As the cost of SAT solving increases with in the size of the problem
+instance, our algorithm tries to solve the problem first for a low $I_p$,
+$F_p$, iteratively increasing the precision if it is insufficient.
 

### 2017-01-02 hscc2017/paper.tex
wording

@@
 As the cost of SAT solving increases with in the size of the problem
-instance, our algorithm tries to solve the problem first for a low $I_p$,
+instance, our algorithm tries to solve the problem first for small $I_p$,
 $F_p$, iteratively increasing the precision if it is insufficient.

### 2017-01-09 hscc2017/paper.tex
nudge

@@
 (Eq.~\ref{Eq:running-example-plant}).  However, if the effects of
-finite-precision arithmetic are considered during verification (e.g.,
-fixed-point arithmetic and word-length), then this closed-loop system
-becomes unstable.
+finite-precision arithmetic are considered (e.g., fixed-point arithmetic and
+word-length), then this closed-loop system becomes unstable.
 %
@@
 
-We have presented a CEGIS-based approach implemented in a tool 
-called \tool, which uses inductive synthesis in conjunction with 
-an algorithm for verifying robust closed-loop stability that addresses 
-plant variations as interval sets as well as FWL uncertainties in digital 
-controllers. The present approach is novel in the control system 
-literature in that it puts forward a fully automated synthesis approach that 
-is algorithmically and numerically sound. In particular, \tool marks the first 
-use of the CEGIS paradigm, which handles plants with uncertain models and 
-FWL effects over the digital controller.  Note that implementing this architecture 
-efficiently requires adjusting the traditional CEGIS refinement loop to the use 
-of a two-stage verification engine: here the first stage performs fast, but potentially 
-unsound fixed-point operations, whereas the second stage restores soundness 
-by validating the operations performed by the first stage using interval 
-arithmetic. Our experimental results show that \tool
-is able to synthesize stable controllers in most benchmarks within
-a reasonable amount of time fully automatically.  Future work will be the 
-extension of this CEGIS-based approach to further classes of systems, 
-including state-space.  We will also consider performance 
-requirements while synthesizing the digital controller.
+We have presented a CEGIS-based approach implemented in a tool called \tool,
+which uses inductive synthesis in conjunction with an algorithm for
+verifying robust closed-loop stability that addresses plant variations as
+interval sets as well as FWL uncertainties in digital controllers.  The
+present approach is novel in the control system literature in that it puts
+forward a fully automated synthesis approach that is algorithmically and
+numerically sound.  In particular, \tool marks the first use of the CEGIS
+paradigm, which handles plants with uncertain models and FWL effects over
+the digital controller.  Note that implementing this architecture
+efficiently requires adjusting the traditional CEGIS refinement loop to the
+use of a two-stage verification engine: here the first stage performs fast,
+but potentially unsound fixed-point operations, whereas the second stage
+restores soundness by validating the operations performed by the first stage
+using interval arithmetic.  Our experimental results show that \tool is able
+to synthesize stable controllers in most benchmarks within a reasonable
+amount of time fully automatically.  Future work will be the extension of
+this CEGIS-based approach to further classes of systems, including those
+with state space.  We will also consider performance requirements while
+synthesizing the digital controller.
 

### 2017-01-11 hscc2017/paper.tex
nudge

@@
 Proposition~\ref{prop:eq_int_stab} are satisfied and if the quantization
-noise is bounded.  The quantization noise boundedness comes from
+noise is bounded.  The bound on the quantization noise is given by
 Assumption~\ref{whitenoise}.
@@
 %\item 
-$R_4: m_{11} > 0 \wedge m_{31}>0 \wedge m_{51}>0 \wedge \cdots \wedge m_{(2N{-}3)(1)}>0$.
+$R_4: m_{11} > 0 \wedge\allowbreak
+      m_{31}>0 \wedge\allowbreak
+      m_{51}>0 \wedge \ldots \wedge\allowbreak
+      m_{(2N{-}3)(1)}>0$.
 %\end{itemize}
 %
-The stability property is then encoded by creating a
-constraint of the form:
+The stability property is then encoded by a constraint of the form:
 $
@@
 to represent the coefficients
-$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\
+$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i,\,\allowbreak
 {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_p})]$ 

### 2017-01-16 cav2017/cav2017.tex
minor changes

@@
 \section{Preliminaries}
-%-------------------------------
-In this study, we focus on Linear Dynamical Cyber-Physical Systems with
-continuous plants described by Ordinary Differential Equations (ODEs) 
+\label{sec:preliminaries}
+%-------------------------------
+
+%-------------------------------
+\subsection{State-space representation of dynamical systems}
+\label{ssec:ssrepresentation}
+%-------------------------------
+
+In this study, we focus on Cyber-Physical Systems with continuous 
+dynamical plants described by Ordinary Differential Equations (ODEs) 
 in the form
@@
 $\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
-a continuous plant. Eq.~\ref{eq:ode} is soundly discretized 
+a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
 (as shown in the appendix) into
@@
 \vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
-\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k,\nonumber
+\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
 \end{align}
 %
-and digital controllers creating a feedback loop in the form
+
+%-------------------------------
+\subsection{State feedback control}
+\label{ssec:statefeedbackcontrol}
+%-------------------------------
+
+Feedback control is usually employed to modify and control the properties and behaviors of process and systems, reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance.
+A well-known feedback control technique is the state feedback control where the control action $\vec{u}_k$ is computed by:
 %
 \begin{equation}
-\vec{u}_k=\mat{K}_d\vec{y}_k\ \ :\ \ \mat{K}_d \in \mathbb{R}^{m \times o}.
+\vec{u}_k=\vec{r}_{k}-\mat{K}\vec{x}_k.
 \end{equation}
 %
-where $\mat{K}_d$ are the feedback coefficients.
-%
-The output of the plant is being sampled by an ADC, and since the full state of the
+where $\mat{K} \in \mathbb{R}^{m \times o}$ is the state feedback gain matrix.
+%
+The output and measurable of the plant is being sampled by an ADC, and since the full state of the
 plant cannot be witnessed directly, the controller software includes an observer that 
 estimates the state of the plant (see appendix for details on how such an observer
-is constructed). We further presume that there are small tolerances in the system 
+is constructed).
+In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.
+We further presume that there are small tolerances in the system
 described in the following form
@@
 \end{align*}
+\commentib{What is S?}
 
@@
 above for simplicity.
+
+%-------------------------------
+\subsection{Stability of closed-loop systems}
+\label{ssec:stability}
+%-------------------------------
+
+%-------------------------------
+\subsection{Quantization error in digital controllers of Cyber-Physical Systems}
+\label{ssec:quantizationerror}
+%-------------------------------
+
+%-------------------------------
+\subsection{Safety specifications for Cyber-Physical Systems}
+\label{ssec:safety}
+%-------------------------------
 

### 2017-01-16 cav2017/cav2017.tex
cav

@@
 % first the title is needed
-\title{Automated Synthesis of State-Space Digital Systems}
+\title{Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants}
 
@@
 %-------------------------------
+\subsection{Related Work}
+\label{sec:relw}
+%-------------------------------
+
+\todo{[Move material from \ref{sec:rw} here]}
+
+%-------------------------------
 \section{Preliminaries}
@@
 %-------------------------------
-\subsection{State-space representation of dynamical systems}
+\subsection{State-space representation of physical systems} 
 \label{ssec:ssrepresentation}
@@
 %-------------------------------
-\subsection{State feedback control}
+\subsection{Controller synthesis via state feedback}
 \label{ssec:statefeedbackcontrol}
@@
 above for simplicity.
+
+%-------------------------------
+\subsection{Digital implementation of feedback controller}
+\label{ssec:statefeedbackcontrol}
+%-------------------------------
 
@@
 \section{Related Work}
+\label{sec:rw}
 %-------------------------------

### 2017-01-16 cav2017/cav2017.tex
cav

@@
 
-In this study, we focus on Cyber-Physical Systems with continuous 
-dynamical plants described by Ordinary Differential Equations (ODEs) 
-in the form
+We consider physical models expressed as ordinary differential equations (ODEs) with full state information:  
 %
@@
 \label{eq:ode}
-\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
-\vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
+\dot{x}(t) = Ax(t)+ B u(t)\ \ :\ \ x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}
 \end{align}
-\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
-$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
-a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
-(as shown in the appendix) into
+where $A$ and $B$ are matrices that fully specify the continuous plant. 
+Eq.~\eqref{eq:ode} is soundly discretised (as shown in the Appendix \todo{[there we can present directly the full LTI case with outputs]}) into
 %
@@
 \label{eq:plant}
-\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
-\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
+x_{k+1}&= A_d x_k+ B_d u_k. 
 \end{align}
 %
+The
 
@@
 
-Feedback control is usually employed to modify and control the properties and behaviors of process and systems, reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance.
+Feedback control is usually employed to modify and control the properties and behaviors of process and systems, 
+reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance.
 A well-known feedback control technique is the state feedback control where the control action $\vec{u}_k$ is computed by:
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Counterexample Guided Abstractly Refined Inductive Synthesis for LTI Cyberphysical Systems}\label{sec:CEGARIS}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Verification of a Conrollable Observed System}\label{sec:cof_verification}
+\section{Counterexample-Guided Abstractly-Refined Inductive Synthesis of Controllers for LTI Systems} 
+\label{sec:CEGARIS} 
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Verification of a Controllable Observed System}\label{sec:cof_verification}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 
+%-------------------------------
+\section{Extensions}
+\label{sec:extensions}
+%-------------------------------
+
+%-------------------------------
+\subsection{LTI systems with output} 
+\label{ssec:LTI}
+%-------------------------------
+
+LTI models in the form: 
+%
+\begin{align}
+\label{eq:ode}
+\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
+\vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
+\end{align}
+\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
+$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
+a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
+(as shown in the appendix) into
+%
+\begin{align}
+\label{eq:plant}
+\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
+\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
+\end{align}
+%
+
 \newpage

### 2017-01-16 cav2017/cav2017.tex
cav

@@
 where $A$ and $B$ are matrices that fully specify the continuous plant.  
+\todo{[specify initial conditions? specify input ranges already here? ]} 
 Eq.~\eqref{eq:ode} is soundly discretised (as shown in the Appendix \todo{[there we can present directly the full LTI case with outputs]}) into
@@
 \label{eq:plant}
-x_{k+1}&= A_d x_k+ B_d u_k. 
+x_{k+1} = A_d x_k+ B_d u_k. 
 \end{align}
@@
 
-Feedback control is usually employed to modify and control the properties and behaviors of process and systems, 
-reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance.
-A well-known feedback control technique is the state feedback control where the control action $\vec{u}_k$ is computed by:
+Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
+Feedback can be employed to affect the properties and behaviours of the process. 
+%reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
+The most basec feedback architecture is the state feedback, 
+where the control action $\vec{u}_k$ is computed by: 
 %
 \begin{equation}
-\vec{u}_k=\vec{r}_{k}-\mat{K}\vec{x}_k.
+u_k = r_{k} - K x_k, 
 \end{equation}
 %
-where $\mat{K} \in \mathbb{R}^{m \times o}$ is the state feedback gain matrix.
-%
+where $K \in \mathbb{R}^{m \times n}$ is a feedback gain matrix, 
+and $r_{k}$ is a reference signal.   
+%
+The closed-loop model then takes the form 
+\begin{align}
+x_{k+1} = ( A_d - B_d K ) + B_d r_k. \nonumber
+\end{align}
+The gain matrix $K$ can be set so that the closed-loop dynamics are shaped as desired, 
+according to a desired goal or objective. 
+A standard objective is to obtain stable closed-loop dynamics.
+
+\todo{[Here discuss Jury criterium]}
+
+\bigskip
+
+\todo{[Unclear what the remainder of the section serves for. ]}
 The output and measurable of the plant is being sampled by an ADC, and since the full state of the

### 2017-01-16 cav2017/cav2017.tex
cav

@@
 
+%-------------------------------
+\subsection{Stability of closed-loop systems}
+\label{ssec:stability}
+%-------------------------------
+
 \todo{[Here discuss Jury criterium]}
@@
 \subsection{Digital implementation of feedback controller}
-\label{ssec:statefeedbackcontrol}
-%-------------------------------
-
-%-------------------------------
-\subsection{Stability of closed-loop systems}
-\label{ssec:stability}
-%-------------------------------
-
-%-------------------------------
-\subsection{Quantization error in digital controllers of Cyber-Physical Systems}
 \label{ssec:quantizationerror}
 %-------------------------------
+
+\todo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.}
 
@@
 %-------------------------------
+
+\todo{The safety specification is defined over the state space, not the output. Further, please distinguish the spec from the input constraints. }
 

### 2017-01-16 cav2017/cav2017.tex
cav

@@
 
-\todo{[Here discuss Jury criterium]}
-
-\bigskip
-
-\todo{[Unclear what the remainder of the section serves for. ]}
+\todo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantisation noises yet).]}
+
+%-------------------------------
+\subsection{Digital implementation of feedback controller}
+\label{ssec:quantizationerror}
+%-------------------------------
+
+\todo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.}
+
+\todo{[The remainder of the section needs to be updated. ]}
 The output and measurable of the plant is being sampled by an ADC, and since the full state of the
@@
 estimates the state of the plant (see appendix for details on how such an observer
-is constructed).
-In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.
+is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  
+\todo{[Unclear what the remainder is for: ]}
 We further presume that there are small tolerances in the system 
@@
 above for simplicity.
-
-%-------------------------------
-\subsection{Digital implementation of feedback controller}
-\label{ssec:quantizationerror}
-%-------------------------------
-
-\todo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.}
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Verification of a Controllable Observed System}\label{sec:cof_verification}
+\subsection{Verification of a Controllable Observed System}
+\label{sec:cof_verification}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-01-16 cav2017/cav2017.tex
some revising

--- 2017-01-16 cav2017/cav2017.tex
@@
 % first the title is needed
-\title{Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants}
+\title{Automated Synthesis of State-Space Digital Systems}
 
@@
 properties it explores.  Traditionally, this focuses mainly on the
-subject of stability, working typically on continuous domains
-\cite{sadabadi2016static}, or using switched
-models~\cite{DBLP:conf/emsoft/RavanbakhshS16}.  Reachability tools are
+subject of stability %, working typically on continuous domains
+\cite{sadabadi2016static, DBLP:journals/corr/AbateBCCDKK16}, or using switched
+models~\cite{DBLP:conf/emsoft/RavanbakhshS16}.
+
+Reachability tools are
 also used when discretizing the state-space for both verification and
@@
 
+In this paper, we synthesize controllers for hybrid
+closed-loop systems, i.e., software-implemented embedded controllers along
+with a model of their physical environment (the plant), that are
+\emph{safe}.  Due to the complexity of such systems, in this work we focus
+on linear models with known configurations and perform parametric synthesis
+of safe digital controllers.
 To this end, we formalise the notion of solution generalisation for
 Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
-of Counter-Example Guided Abstraction Refinement (CEGAR),
+of abstraction refinement
 %on simplified abstractions of the system
@@
 %-------------------------------
-\subsection{Related Work}
-\label{sec:relw}
-%-------------------------------
-
-\todo{[Move material from \ref{sec:rw} here]}
-
-%-------------------------------
 \section{Preliminaries}
@@
 %-------------------------------
-\subsection{State-space representation of physical systems} 
+\subsection{State-space representation of dynamical systems}
 \label{ssec:ssrepresentation}
@@
 
-We consider physical models expressed as ordinary differential equations (ODEs) with full state information:  
+In this study, we focus on Cyber-Physical Systems with continuous 
+dynamical plants described by Ordinary Differential Equations (ODEs) 
+in the form
 %
@@
 \label{eq:ode}
-\dot{x}(t) = Ax(t)+ B u(t)\ \ :\ \ x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}
+\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
+\vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
 \end{align}
-where $A$ and $B$ are matrices that fully specify the continuous plant.  
-\todo{[specify initial conditions? specify input ranges already here? ]} 
-Eq.~\eqref{eq:ode} is soundly discretised (as shown in the Appendix \todo{[there we can present directly the full LTI case with outputs]}) into
+\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
+$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
+a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
+(as shown in the appendix) into
 %
@@
 \label{eq:plant}
-x_{k+1} = A_d x_k+ B_d u_k. 
+\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
+\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
 \end{align}
 %
-The
-
-%-------------------------------
-\subsection{Controller synthesis via state feedback}
+
+%-------------------------------
+\subsection{State feedback control}
 \label{ssec:statefeedbackcontrol}
@@
 
-Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
-Feedback can be employed to affect the properties and behaviours of the process. 
-%reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
-The most basec feedback architecture is the state feedback, 
-where the control action $\vec{u}_k$ is computed by: 
+Feedback control is usually employed to modify and control the properties and behaviors of process and systems, reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance.
+A well-known feedback control technique is the state feedback control where the control action $\vec{u}_k$ is computed by:
 %
 \begin{equation}
-u_k = r_{k} - K x_k, 
+\vec{u}_k=\vec{r}_{k}-\mat{K}\vec{x}_k.
 \end{equation}
 %
-where $K \in \mathbb{R}^{m \times n}$ is a feedback gain matrix, 
-and $r_{k}$ is a reference signal.   
-%
-The closed-loop model then takes the form 
-\begin{align}
-x_{k+1} = ( A_d - B_d K ) + B_d r_k. \nonumber
-\end{align}
-The gain matrix $K$ can be set so that the closed-loop dynamics are shaped as desired, 
-according to a desired goal or objective. 
-A standard objective is to obtain stable closed-loop dynamics.
-
-\todo{[Here discuss Jury criterium]}
-
-\bigskip
-
-\todo{[Unclear what the remainder of the section serves for. ]}
+where $\mat{K} \in \mathbb{R}^{m \times o}$ is the state feedback gain matrix.
+%
 The output and measurable of the plant is being sampled by an ADC, and since the full state of the
@@
 above for simplicity.
-
-%-------------------------------
-\subsection{Digital implementation of feedback controller}
-\label{ssec:statefeedbackcontrol}
-%-------------------------------
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Counterexample-Guided Abstractly-Refined Inductive Synthesis of Controllers for LTI Systems} 
-\label{sec:CEGARIS} 
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Verification of a Controllable Observed System}\label{sec:cof_verification}
+\section{Counterexample Guided Abstractly Refined Inductive Synthesis for LTI Cyberphysical Systems}\label{sec:CEGARIS}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+{\bf Assumption:} We consider the reference signal to be 0, whereas the initial states are non-deterministic.
+
+\todo{Explain the implicaitions of this.}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Verification of a Conrollable Observed System}\label{sec:cof_verification}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 \section{Related Work}
-\label{sec:rw}
 %-------------------------------
@@
 \textcolor{red}{LC: Cristina and Dario, should we further expand this section with other initiatives to synthesise control systems?}
-
-%-------------------------------
-\section{Extensions}
-\label{sec:extensions}
-%-------------------------------
-
-%-------------------------------
-\subsection{LTI systems with output} 
-\label{ssec:LTI}
-%-------------------------------
-
-LTI models in the form: 
-%
-\begin{align}
-\label{eq:ode}
-\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
-\vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
-\end{align}
-\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
-$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
-a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
-(as shown in the appendix) into
-%
-\begin{align}
-\label{eq:plant}
-\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
-\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
-\end{align}
-%
 

### 2017-01-16 cav2017/cav2017.tex

--- 2017-01-16 cav2017/cav2017.tex
@@
 above for simplicity.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Numeric Representations and Soundness} 
+\label{sec:numeric_rep}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Let $\mathbb{R} \langle I,F \rangle$ be a fixed point domain with $I$ bits representing the integer part and $F$ bits
+representing the decimal part. We will extend this notation to $\mathbb{R} \langle I,F,E \rangle$ to add a number of
+leading or trailing bits when the domain requires prescaling (ie the maximum is smaller than $0.5$ or the minimum
+is greater than $2$)
+Let also $\mathbb{R}_* \langle M,E \rangle$ be a floating point domain with $M$ bits
+mantissa and $E$ bits exponent. This domain corresponds to 
+$$\mathbb{R}_* \langle M,E \rangle = \bigcup_i \mathbb{R} \langle 1,M-1,E_i \rangle : 2^{1-E} \leq E_i  \leq 2^{E-1}$$
+This means that the distance between any two numbers in the domain depends on the
+location of those numbers.
+Since we've shown that a floating point domain is a union of a number of fixed point domains, we will continue our
+reasoning on fixed point only. Our points will apply to the floating point domain by extension.
+The following approximation errors will arise:
+\begin{enumerate}
+\item Truncation\\
+Let $\mathcal{F}\langle I,F \rangle(\cdot) : \mathbb{R} \rightarrow \mathbb{R}\langle I,F \rangle, \tilde x=\mathcal{F}\langle I,F \rangle(x) = x-\delta : \delta=x\ \%_F\  c\tilde x$, where $\%_F$ is the modulus operation performed on the last bit of the representation ($2^{-F}$).\\
+The number $\delta$ corresponds to the truncation error of the representation and it will propagate across operations.
+\item Rounding\\
+Every time an operation is performed on a number in the $\mathbb{R} \langle I,F,E \rangle$ domain, an error may be
+introduced due to truncation of the result.
+Let us define $c\langle i,f,e \rangle \in \mathbb{R}\langle I,F,E\rangle$, where $i \in [-2^{I-1}\ 2^{I-1}],f \in [0 1),e \in [-2^{E-1}\ 2^{E-1}]$ are its assigned values.
+The smallest number that can be represented for any given exponent is $c_{min(e)}=c\langle 0,2^{-F},e\rangle$.
+The following errors appear in simple operations:
+\begin{enumerate}
+\item Addition/Substraction: $c\langle \cdot,e_1\rangle \pm c\langle \cdot,e_2\rangle=c\langle \cdot,max(e_1,e_2)\rangle + \delta_3 : |\delta_3| \leq (e_1==e_2) ? 0 : c_{min(max(e_2,e_1))}$ 
+\item Multiplication: $c\langle \cdot,e_1\rangle * c\langle \cdot,e_2\rangle=c\langle \cdot,e_1+e_2\rangle + \delta_3 : |\delta_3| \leq c_{min(e_2+e_1)}$
+\end{enumerate}
+The bounds obtained for division are left to the reader as it will not be applied in this paper.
+
+At this point it is worth mentioning that not all systems truncate equally. In the definition above $\delta$ may be positive
+or negative, and even this decision can be made dependent on the sign of $x$. Common cases in computer systems are:
+round downwards (\emph{ie} to $-\infty$), round upwards (\emph{ie} to $+\infty$), and round to zero.
+Rounding errors are cumulative which means the overall error will statistically increase with every operation, thus algorithms
+performing fewer operations can be more precise in this respect than iterative ones. 
+\item Overflow\\
+Another source of error introduced by Finite Word Length representations is that of overflow. The finite word length set a
+maximum representable number in the domain ($\pm 2^{I-1}+1-2^{-F}$), which means that any number outside this range
+cannot be accurately represented by the domain (\emph{eg} $\delta=x-2^{I-1}+1-2^{-F}$). In the case of floating point, a special
+case for infinity has been introduced, which addresses some of this issues, but once the error has gone to infinity, the numbers
+become meaningless. It is the responsibility of software designers and tools to account for overflows and either supply saturation
+functions to prevent them or raise alarms in their presence. In the case of verification, the latter is seen as a safety problem.
+\item Null/Zeno behaviour\\
+Whilst this work does not explore the effect of Zeno behaviours, it is worth noting that this effect may also be caused by rounding
+errors in floating point programs. The reason for this is that if an operation contains two numbers which belong to disjoint sub-domains
+(\emph{ie} neither number can be represented in the domain of its counterpart), the resulting operation may become a no-op/skip,
+subsequently destabilizing the program.
+\end{enumerate}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Fixed Word Length Effects on Matrix Multiplications}
+\label{sec:cof_fwl}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+Thus far we have presented a verification procedure for a digitalized plant in a continuous space (\emph{ie} the
+range of the quatizers is still $\mathbb{R}$. The next step we must reaize is that the controller and the observer
+exist in a digital program, hence their domain is $\mathbb{R}\langle I,F,E\rangle$. This has two separate effects
+on the model. If we recall equation \eqref{eq:to_of}, the matrices of the observer and the controller  are not necessarily those of the plant.
+In fact we have $\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$, $\mat{A}_o,\mat{B}_o,\mat{C}_o, \mat{K}_d, \mat{L}_d \in \mathbb{R}\langle I,F,E\rangle^*$
+Where $*$ represents the appropriate dimension for each matrix.
+Unfortunately this means that although combined matrices such as $\mat{A}_t$ are in the reals, they suffer from
+the fixed word restrictions in their composing matrices.
+The second effect corresponds to the rounding errors in the calculation of $\hat{x}_{k+1}, u_k$.
+These will introduce a new source of quantiztion noise which we may denote $\vec{\nu}_3 \in [-q_3\ \ q_3]$.
+The estimation of $\hat{\vec{x}}$ corresponds to the sum of three matrix-vector multiplications (we assume $\mat{C}_o$ in Objective form).
+Each of these has a coefficient-wise error bound $c_{min(max(e_{j1}+e_{j2}))}$.
+Hence the overall $\overline{\delta}_{\hat{x}}=3nc_{min(max(e_{j1}+e_{j2}))}$.
+The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=nc_{min(max(e_{k1}+e_{k2}))}+\sum_{k=1}^nc_k\overline{\delta}_{\hat{x}})=3n|\mat{K}|_1c_{min(max(e_{j1}+e_{j2}))}+nc_{min(max(e_{k1}+e_{k2}))}$
 
@@
 
+{\bf Assumption:} We consider the reference signal to be 0, whereas the initial states are non-deterministic.
+
+\todo{Explain the implicaitions of this.}
+
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 It is worth noting that $r$ is a non-deterministic parametric input (\emph{ie} $\forall k>0, r_{k+1} =r_k$) whereas the set N is composed of non-deterministic variable inputs.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Numeric Representations and Soundness} \label{sec:numeric_rep}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Let $\mathbb{R} \langle I,F \rangle$ be a fixed point domain with $I$ bits representing the integer part and $F$ bits
-representing the decimal part. We will extend this notation to $\mathbb{R} \langle I,F,E \rangle$ to add a number of
-leading or trailing bits when the domain requires prescaling (ie the maximum is smaller than $0.5$ or the minimum
-is greater than $2$)
-Let also $\mathbb{R}_* \langle M,E \rangle$ be a floating point domain with $M$ bits
-mantissa and $E$ bits exponent. This domain corresponds to 
-$$\mathbb{R}_* \langle M,E \rangle = \bigcup_i \mathbb{R} \langle 1,M-1,E_i \rangle : 2^{1-E} \leq E_i  \leq 2^{E-1}$$
-This means that the distance between any two numbers in the domain depends on the
-location of those numbers.
-Since we've shown that a floating point domain is a union of a number of fixed point domains, we will continue our
-reasoning on fixed point only. Our points will apply to the floating point domain by extension.
-The following approximation errors will arise:
-\begin{enumerate}
-\item Truncation\\
-Let $\mathcal{F}\langle I,F \rangle(\cdot) : \mathbb{R} \rightarrow \mathbb{R}\langle I,F \rangle, \tilde x=\mathcal{F}\langle I,F \rangle(x) = x-\delta : \delta=x\ \%_F\  c\tilde x$, where $\%_F$ is the modulus operation performed on the last bit of the representation ($2^{-F}$).\\
-The number $\delta$ corresponds to the truncation error of the representation and it will propagate across operations.
-\item Rounding\\
-Every time an operation is performed on a number in the $\mathbb{R} \langle I,F,E \rangle$ domain, an error may be
-introduced due to truncation of the result.
-Let us define $c\langle i,f,e \rangle \in \mathbb{R}\langle I,F,E\rangle$, where $i \in [-2^{I-1}\ 2^{I-1}],f \in [0 1),e \in [-2^{E-1}\ 2^{E-1}]$ are its assigned values.
-The smallest number that can be represented for any given exponent is $c_{min(e)}=c\langle 0,2^{-F},e\rangle$.
-The following errors appear in simple operations:
-\begin{enumerate}
-\item Addition/Substraction: $c\langle \cdot,e_1\rangle \pm c\langle \cdot,e_2\rangle=c\langle \cdot,max(e_1,e_2)\rangle + \delta_3 : |\delta_3| \leq (e_1==e_2) ? 0 : c_{min(max(e_2,e_1))}$ 
-\item Multiplication: $c\langle \cdot,e_1\rangle * c\langle \cdot,e_2\rangle=c\langle \cdot,e_1+e_2\rangle + \delta_3 : |\delta_3| \leq c_{min(e_2+e_1)}$
-\end{enumerate}
-The bounds obtained for division are left to the reader as it will not be applied in this paper.
-
-At this point it is worth mentioning that not all systems truncate equally. In the definition above $\delta$ may be positive
-or negative, and even this decision can be made dependent on the sign of $x$. Common cases in computer systems are:
-round downwards (\emph{ie} to $-\infty$), round upwards (\emph{ie} to $+\infty$), and round to zero.
-Rounding errors are cumulative which means the overall error will statistically increase with every operation, thus algorithms
-performing fewer operations can be more precise in this respect than iterative ones. 
-\item Overflow\\
-Another source of error introduced by Finite Word Length representations is that of overflow. The finite word length set a
-maximum representable number in the domain ($\pm 2^{I-1}+1-2^{-F}$), which means that any number outside this range
-cannot be accurately represented by the domain (\emph{eg} $\delta=x-2^{I-1}+1-2^{-F}$). In the case of floating point, a special
-case for infinity has been introduced, which addresses some of this issues, but once the error has gone to infinity, the numbers
-become meaningless. It is the responsibility of software designers and tools to account for overflows and either supply saturation
-functions to prevent them or raise alarms in their presence. In the case of verification, the latter is seen as a safety problem.
-\item Null/Zeno behaviour\\
-Whilst this work does not explore the effect of Zeno behaviours, it is worth noting that this effect may also be caused by rounding
-errors in floating point programs. The reason for this is that if an operation contains two numbers which belong to disjoint sub-domains
-(\emph{ie} neither number can be represented in the domain of its counterpart), the resulting operation may become a no-op/skip,
-subsequently destabilizing the program.
-\end{enumerate}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Fixed Word Length Effects on Matrix Multiplications}\label{sec:cof_fwl}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-Thus far we have presented a verification procedure for a digitalized plant in a continuous space (\emph{ie} the
-range of the quatizers is still $\mathbb{R}$. The next step we must reaize is that the controller and the observer
-exist in a digital program, hence their domain is $\mathbb{R}\langle I,F,E\rangle$. This has two separate effects
-on the model. If we recall equation \eqref{eq:to_of}, the matrices of the observer and the controller  are not necessarily those of the plant.
-In fact we have $\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$, $\mat{A}_o,\mat{B}_o,\mat{C}_o, \mat{K}_d, \mat{L}_d \in \mathbb{R}\langle I,F,E\rangle^*$
-Where $*$ represents the appropriate dimension for each matrix.
-Unfortunately this means that although combined matrices such as $\mat{A}_t$ are in the reals, they suffer from
-the fixed word restrictions in their composing matrices.
-The second effect corresponds to the rounding errors in the calculation of $\hat{x}_{k+1}, u_k$.
-These will introduce a new source of quantiztion noise which we may denote $\vec{\nu}_3 \in [-q_3\ \ q_3]$.
-The estimation of $\hat{\vec{x}}$ corresponds to the sum of three matrix-vector multiplications (we assume $\mat{C}_o$ in Objective form).
-Each of these has a coefficient-wise error bound $c_{min(max(e_{j1}+e_{j2}))}$.
-Hence the overall $\overline{\delta}_{\hat{x}}=3nc_{min(max(e_{j1}+e_{j2}))}$.
-The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=nc_{min(max(e_{k1}+e_{k2}))}+\sum_{k=1}^nc_k\overline{\delta}_{\hat{x}})=3n|\mat{K}|_1c_{min(max(e_{j1}+e_{j2}))}+nc_{min(max(e_{k1}+e_{k2}))}$
 

### 2017-01-16 cav2017/cav2017.tex
removed space in citation
more revision

@@
 subject of stability %, working typically on continuous domains
-\cite{sadabadi2016static, DBLP:journals/corr/AbateBCCDKK16}, or using switched
+\cite{sadabadi2016static,DBLP:journals/corr/AbateBCCDKK16}, or using switched
 models~\cite{DBLP:conf/emsoft/RavanbakhshS16}.
-
 Reachability tools are
@@
 parametric synthesis~\cite{cimatti2013parameter}.
-In this paper, however, we propose the synthesis of control algorithms for
+
+In this paper, we propose the synthesis of \emph{safe} control algorithms for
 cyberphysical systems taking into consideration the continuous domain
@@
 hybrid elements that communicate them.
-
-In this paper, we synthesize controllers for hybrid
-closed-loop systems, i.e., software-implemented embedded controllers along
-with a model of their physical environment (the plant), that are
-\emph{safe}.  Due to the complexity of such systems, in this work we focus
+%
+%% In this paper, we synthesize controllers for hybrid
+%% closed-loop systems, i.e., software-implemented embedded controllers along
+%% with a model of their physical environment (the plant), that are
+%% \emph{safe}.
+Due to the complexity of such systems, in this work we focus
 on linear models with known configurations and perform parametric synthesis
 of safe digital controllers.
+
 To this end, we formalise the notion of solution generalisation for
@@
 
-\textcolor{red}{Cristina: Can you please further expand the introduction
-by adding more details about our synthesis approach to control systems?}
+%% \textcolor{red}{Cristina: Can you please further expand the introduction
+%% by adding more details about our synthesis approach to control systems?}
 
@@
 
-\todo{[Move material from \ref{sec:rw} here]}
+\paragraph{CEGIS}
+
+Program synthesis is the problem of computing correct-by-design programs
+from high-level specifications, and algorithms for this problem have made
+substantial progress in recent years.  One such
+approach~\cite{itzhaky2010simple} inductively synthesizes invariants to
+generate the desired programs.
+
+Program synthesisers are an ideal fit for synthesis of parametric
+controllers since the semantics of programs capture effects such as FWL
+precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
+for the synthesis of switching controllers for stabilizing continuous-time
+plants with polynomial dynamics.  The work extends to its application on
+affine systems, finding its major challenge in the hardness of solving
+linear arithmetic with the state-of-the-art SMT solvers.  Since this
+approach uses switching states instead of linear dynamics in the digital
+controller, it entirely circumvents the FWL problem.  It is also not
+suitable for the kind of control we seek to synthesize.
+Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
+use a CEGIS-based approach for synthesizing continuous-time switching
+controllers that guarantee reach while stay properties of a closed
+loop system. The solution is based on synthesizing control Lyapunov
+functions for switched systems, that yield switching controllers with
+a guaranteed minimum dwell time in each mode.
+
+We require a
+combination of a synthesis engine with a control verification tool that
+addresses the challenges presented here in the form of FWL effects and
+stability measures for LTI SISO controllers.  We take the former
+from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from~\cite{daes20161},
+while enhancing the procedure by evaluating the quantization effects of the
+Hardware interfaces (ADC/DAC) to obtain an accurate discrete-time FWL
+representation of the continuous dynamics.
+
+\paragraph{Discretization Effects}
+
+The classical approach to control synthesis has often disregarded
+quantization as a minimal effect, thus proving unsound in the case of digital control systems.
+Modern techniques focus on different elements of the discretization effect, including delayed
+response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics with
+the goal to either verify (e.g.~\cite{daes20161}) or optimize
+(e.g.~\cite{oudjida2014design}) given implementations.
+
+There are two different problems that arise from FWL semantics.  The first
+is the error in the dynamics caused by the inability to represent the exact
+state of the physical system while the second relates to rounding errors
+during computation.  In~\cite{fialho1994stability}, a stability measure
+based on the error of the digital dynamics ensures that the deviation
+introduced by FWL does not make the digital system unstable.  A more recent
+approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
+directly model the digital controller so that the selected parameters are
+stable by design.  The analyses
+in~\cite{DBLP:conf/hybrid/WangGRJF16,DBLP:conf/hybrid/RouxJG15} rely on an
+invariant computation on the discrete system dynamics using Semi-Definite
+Programming (SDP).  While the former uses BIBO properties to determine
+stability, the latter uses Lyapunov-based quadratic invariants.  In both
+cases, the SDP solver uses floating-point arithmetic and soundness is
+checked by bounding the error.  An alternative approach is taken
+by~\cite{park2016scalable}, where the verification of existing code is
+performed against a known model by extracting an LTI model of the code
+through symbolic execution.  In order to account for rounding errors, an
+upper bound is introduced in the verification phase.
+The work in \cite{picasso2002construction,picasso2003stabilization} introduces
+attractive invariant sets as a mechanism to bound the quantization error effect
+on stabilization as an invariant set that always converges toward the cotrollable
+set. In a similar fashion, \cite{liberzon2003hybrid} evaluates the dynamics of the
+quantization error and binds their trajectory to a known region over a finite
+period of time. This technique works for both linear and non-linear systems.
+This paper uses an approach that projects the maximum effect of the noise over
+an unbounded time and uses it as a `buffer' region for the safety specification.
+
+%\todo{[Move material from \ref{sec:rw} here]}
 
@@
 
-%-------------------------------
-\section{Related Work}
-\label{sec:rw}
-%-------------------------------
-
-\paragraph{CEGIS}
-
-Program synthesis is the problem of computing correct-by-design programs
-from high-level specifications, and algorithms for this problem have made
-substantial progress in recent years.  One such
-approach~\cite{itzhaky2010simple} inductively synthesizes invariants to
-generate the desired programs.
-
-Program synthesisers are an ideal fit for synthesis of parametric
-controllers since the semantics of programs capture effects such as FWL
-precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
-for the synthesis of switching controllers for stabilizing continuous-time
-plants with polynomial dynamics.  The work extends to its application on
-affine systems, finding its major challenge in the hardness of solving
-linear arithmetic with the state-of-the-art SMT solvers.  Since this
-approach uses switching states instead of linear dynamics in the digital
-controller, it entirely circumvents the FWL problem.  It is also not
-suitable for the kind of control we seek to synthesize.
-Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
-use a CEGIS-based approach for synthesizing continuous-time switching
-controllers that guarantee reach while stay properties of a closed
-loop system. The solution is based on synthesizing control Lyapunov
-functions for switched systems, that yield switching controllers with
-a guaranteed minimum dwell time in each mode.
-
-We require a
-combination of a synthesis engine with a control verification tool that
-addresses the challenges presented here in the form of FWL effects and
-stability measures for LTI SISO controllers.  We take the former
-from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from~\cite{daes20161},
-while enhancing the procedure by evaluating the quantization effects of the
-Hardware interfaces (ADC/DAC) to obtain an accurate discrete-time FWL
-representation of the continuous dynamics.
-
-\paragraph{Discretization Effects}
-
-The classical approach to control synthesis has often disregarded
-quantization as a minimal effect, thus proving unsound in the case of digital control systems.
-Modern techniques focus on different elements of the discretization effect, including delayed
-response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics with
-the goal to either verify (e.g.~\cite{daes20161}) or optimize
-(e.g.~\cite{oudjida2014design}) given implementations.
-
-There are two different problems that arise from FWL semantics.  The first
-is the error in the dynamics caused by the inability to represent the exact
-state of the physical system while the second relates to rounding errors
-during computation.  In~\cite{fialho1994stability}, a stability measure
-based on the error of the digital dynamics ensures that the deviation
-introduced by FWL does not make the digital system unstable.  A more recent
-approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
-directly model the digital controller so that the selected parameters are
-stable by design.  The analyses
-in~\cite{DBLP:conf/hybrid/WangGRJF16,DBLP:conf/hybrid/RouxJG15} rely on an
-invariant computation on the discrete system dynamics using Semi-Definite
-Programming (SDP).  While the former uses BIBO properties to determine
-stability, the latter uses Lyapunov-based quadratic invariants.  In both
-cases, the SDP solver uses floating-point arithmetic and soundness is
-checked by bounding the error.  An alternative approach is taken
-by~\cite{park2016scalable}, where the verification of existing code is
-performed against a known model by extracting an LTI model of the code
-through symbolic execution.  In order to account for rounding errors, an
-upper bound is introduced in the verification phase.
-The work in \cite{picasso2002construction,picasso2003stabilization} introduces
-attractive invariant sets as a mechanism to bound the quantization error effect
-on stabilization as an invariant set that always converges toward the cotrollable
-set. In a similar fashion, \cite{liberzon2003hybrid} evaluates the dynamics of the
-quantization error and binds their trajectory to a known region over a finite
-period of time. This technique works for both linear and non-linear systems.
-This paper uses an approach that projects the maximum effect of the noise over
-an unbounded time and uses it as a `buffer' region for the safety specification.
-
-\textcolor{red}{LC: Cristina and Dario, should we further expand this section with other initiatives to synthesise control systems?}
+%% %-------------------------------
+%% \section{Related Work}
+%% \label{sec:rw}
+%% %-------------------------------
 

### 2017-01-16 cav2017/cav2017.tex
+ our HSCC'17 paper in the related work

@@
 
-We require a
-combination of a synthesis engine with a control verification tool that
-addresses the challenges presented here in the form of FWL effects and
-stability measures for LTI SISO controllers.  We take the former
-from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from~\cite{daes20161},
-while enhancing the procedure by evaluating the quantization effects of the
-Hardware interfaces (ADC/DAC) to obtain an accurate discrete-time FWL
-representation of the continuous dynamics.
+In \cite{DBLP:journals/corr/AbateBCCDKK16}, Abate et al.  focus on
+synthesising stabilizing controllers for continuous plants.  While
+they also make use of a CEGIS-based technique, their approach is
+restricted to synthesising controllers for hybrid closed-loop systems
+that are stable and only consider transfer function models.  In contrast,
+in the current paper we consider a state-space
+representation of the physical system and synthesise controllers that
+make the closed-loop system safe.  Moreover, 
+a key aspect of our approach
+is the fact that we integrate abstraction
+refinement inside the CEGIS loop.
+
+We require a combination of a synthesis engine with a control
+verification tool that addresses the challenges presented here in the
+form of FWL effects and stability measures for LTI SISO controllers.
+We take the former from~\cite{DBLP:conf/lpar/DavidKL15} and the latter
+from~\cite{daes20161}, while enhancing the procedure by evaluating the
+quantization effects of the Hardware interfaces (ADC/DAC) to obtain an
+accurate discrete-time FWL representation of the continuous dynamics.
 

### 2017-01-16 cav2017/cav2017.tex
+contributions

@@
 %% by adding more details about our synthesis approach to control systems?}
+
+\todo{Add contributions (Cristina)}
 
@@
 %
-The
 
@@
 %reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
-The most basec feedback architecture is the state feedback, 
+The most basic feedback architecture is the state feedback, 
 where the control action $\vec{u}_k$ is computed by: 
@@
 
-\todo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantisation noises yet).]}
+%\todo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantisation noises yet).]}
+
+Jury's criterion is a mathematical method used to verify whether the roots 
+of a characteristic polynomial are within the unit circle by exploring solely the coefficients 
+of the polynomial. The first step is to create a matrix 
+$\mat{M} \in \mathbb{R}^{(n+1) \times (n+1)}$ with the first row elements 
+$m_{0,j}=c_j$, where $j \in [0,n]$, $k=n-(i-1)$ and 
+$c_j$ are the coefficients of the original polynomial. 
+%
+\begin{equation}
+\left[\begin{array}{ccccc}
+c_0&c_1&\hdots&c_{n-1}&c_n\\
+m_{\scriptscriptstyle 0,0}-m_{\scriptscriptstyle 0,n}^*\frac{m_{0,n}^*}{m_{0,0}}&m_{\scriptscriptstyle 0,1}-m_{\scriptscriptstyle 0,n-1}^*\frac{m_{0,n}^*}{m_{0,0}}&\hdots&m_{\scriptscriptstyle 0,n-1}-m_{\scriptscriptstyle 0,1}^*\frac{m_{0,n}^*}{m_{0,0}}&0\\
+\vdots&\vdots&\vdots&\vdots&\vdots\\
+m_{\scriptscriptstyle i-1,0}-m_{\scriptscriptstyle i-1,k-j}^*\frac{m_{i-1,k}^*}{m_{i-1,0}}&m_{\scriptscriptstyle i-1,1}-m_{\scriptscriptstyle i-1,k-j}^*\frac{m_{i-1,k}^*}{m_{i-1,0}}&\hdots&0&0\\
+m_{\scriptscriptstyle n-1,0}-m_{\scriptscriptstyle n-1,1-j}^*\frac{m_{n-1,1}^*}{m_{n-1,0}}&0&\hdots&0&0\\
+\end{array}\right]
+\end{equation}
+
+Notice that every row has a polynomial one degree lower than the previous. 
+The sufficient and necessary conditions for the polynomial in row $0$ 
+to have all of its roots inside the unit circle are~(\cite{astrom1997computer}):
+%
+\begin{align}
+|c_n|<c_0&&
+\sum_{i=0}^n c_i > 0&&
+(-1)^n\sum_{i=0}^n c_i (-1)^{n-i}> 0&&
+m_{i,0}>0
+\end{align}
 
@@
 an indirect method.
-
-Jury's criteria is a mathematical method used to verify whether the roots 
-of the polynomial are within the unit circle by exploring solely the coefficients 
-of the polynomial. In order to achieve this, we first create a matrix 
-$\mat{M} \in \mathbb{R}^{(n+1) \times (n+1)}$ with zero-indexed coefficients 
-$m_{i,j} : i,j \in [0,n],k=n-(i-1)$ in the following form:
-%
-\begin{equation}
-\left[\begin{array}{ccccc}
-c_0&c_1&\hdots&c_{n-1}&c_n\\
-m_{\scriptscriptstyle 0,0}-m_{\scriptscriptstyle 0,n}^*\frac{m_{0,n}^*}{m_{0,0}}&m_{\scriptscriptstyle 0,1}-m_{\scriptscriptstyle 0,n-1}^*\frac{m_{0,n}^*}{m_{0,0}}&\hdots&m_{\scriptscriptstyle 0,n-1}-m_{\scriptscriptstyle 0,1}^*\frac{m_{0,n}^*}{m_{0,0}}&0\\
-\vdots&\vdots&\vdots&\vdots&\vdots\\
-m_{\scriptscriptstyle i-1,0}-m_{\scriptscriptstyle i-1,k-j}^*\frac{m_{i-1,k}^*}{m_{i-1,0}}&m_{\scriptscriptstyle i-1,1}-m_{\scriptscriptstyle i-1,k-j}^*\frac{m_{i-1,k}^*}{m_{i-1,0}}&\hdots&0&0\\
-m_{\scriptscriptstyle n-1,0}-m_{\scriptscriptstyle n-1,1-j}^*\frac{m_{n-1,1}^*}{m_{n-1,0}}&0&\hdots&0&0\\
-\end{array}\right]
-\end{equation}
-
-The first row corresponds to the coefficients of the original polynomial. 
-Notice also that every row has a polynomial one degree lower than the previous. 
-The sufficient and necessary conditions for the polynomial in row $0$ 
-to have all of its roots inside the unit circle are~\cite{astrom1997computer}:
-%
-\begin{align}
-|c_n|<c_0&&
-\sum_{i=0}^n c_i > 0&&
-(-1)^n\sum_{i=0}^n c_i (-1)^{n-i}> 0&&
-m_{i,0}>0
-\end{align}
 

### 2017-01-18 cav2017/cav2017.tex
ciao
Stability test

@@
 \begin{align}
-x_{k+1} = ( A_d - B_d K ) + B_d r_k. \nonumber
+\label{eq:closedloopss}
+x_{k+1} = ( A_d - B_d K ) + B_d r_k.
 \end{align}
@@
 
-Jury's criterion is a mathematical method used to verify whether the roots 
-of a characteristic polynomial are within the unit circle by exploring solely the coefficients 
-of the polynomial. The first step is to create a matrix 
-$\mat{M} \in \mathbb{R}^{(n+1) \times (n+1)}$ with the first row elements 
-$m_{0,j}=c_j$, where $j \in [0,n]$, $k=n-(i-1)$ and 
-$c_j$ are the coefficients of the original polynomial. 
-%
+A discrete-time system is asymptotically stable if and only if all the roots 
+of the characteristic polynomial ({\it i.e.}, the eigenvalues) are inside of 
+the unity circle, {\it i.e.}, their absolute value are less than 
+one~\cite{astrom1997computer}. For a closed-loop system as~\eqref{eq:closedloopss}, 
+the characteristic polynomial $P(z)$ should be computed as follows:
 \begin{equation}
-\left[\begin{array}{ccccc}
-c_0&c_1&\hdots&c_{n-1}&c_n\\
-m_{\scriptscriptstyle 0,0}-m_{\scriptscriptstyle 0,n}^*\frac{m_{0,n}^*}{m_{0,0}}&m_{\scriptscriptstyle 0,1}-m_{\scriptscriptstyle 0,n-1}^*\frac{m_{0,n}^*}{m_{0,0}}&\hdots&m_{\scriptscriptstyle 0,n-1}-m_{\scriptscriptstyle 0,1}^*\frac{m_{0,n}^*}{m_{0,0}}&0\\
-\vdots&\vdots&\vdots&\vdots&\vdots\\
-m_{\scriptscriptstyle i-1,0}-m_{\scriptscriptstyle i-1,k-j}^*\frac{m_{i-1,k}^*}{m_{i-1,0}}&m_{\scriptscriptstyle i-1,1}-m_{\scriptscriptstyle i-1,k-j}^*\frac{m_{i-1,k}^*}{m_{i-1,0}}&\hdots&0&0\\
-m_{\scriptscriptstyle n-1,0}-m_{\scriptscriptstyle n-1,1-j}^*\frac{m_{n-1,1}^*}{m_{n-1,0}}&0&\hdots&0&0\\
-\end{array}\right]
+P(z)= \det( z I_{n} - A_d + B_d K ),
 \end{equation}
-
-Notice that every row has a polynomial one degree lower than the previous. 
-The sufficient and necessary conditions for the polynomial in row $0$ 
-to have all of its roots inside the unit circle are~(\cite{astrom1997computer}):
-%
-\begin{align}
-|c_n|<c_0&&
-\sum_{i=0}^n c_i > 0&&
-(-1)^n\sum_{i=0}^n c_i (-1)^{n-i}> 0&&
-m_{i,0}>0
-\end{align}
+where $I_{n}$ is the n-th order identity matrix.
+
+Jury's criterion provides necessary and sufficient conditions for the eigenvalues 
+to be within the unit circle and, consequently, the system is stable.  Given a 
+polynomial $P(z)$ of the form
+$$
+P(z) = a_{0}z^{N} + a_{1}z^{N-1} + ... a_{N-1}z + a_{N} = 0, a_{0}\neq 0,
+$$
+Jury's criterion explores solely the coefficients ($a_{0},a_{1},...,a_{N-1}$) 
+of $P(z)$ for checking the validity of the stability property $\phi_{stability}$.
+
+In particular, Jury stability test is already explained in the control system 
+literature ({\it e.g.}~\cite{fadali}). This study, however, limits itself to 
+explain the encoding of Jury's criterion for the formal synthesis purpose. 
+For the stability  test procedure, the following Jury matrix 
+$M=[m_{ij}]_{(2N-2)\times N}$ is built  from $S(z)$ coefficients:
+$$
+M=\left[
+\begin{matrix}
+  V^{(0)} \\
+  V^{(1)} \\
+  \vdots \\
+  V^{(N-2)}
+ \end{matrix}
+\right]\mbox{,}
+$$
+\noindent where $V^{(k)}=[v^{(k)}_{ij}]_{2\times N}$ such that
+$$
+v^{(0)}_{ij}=\begin{cases} 
+a_{j-1}, & \mbox{if } i=1 \\   v^{(0)}_{(1)(N-j+1)}, & \mbox{if } i=2 
+\end{cases}\mbox{, and} 
+$$
+$$
+v^{(k)}_{ij}=\begin{cases} 
+0, & \mbox{if } j>n-k\\
+v^{(k-1)}_{1j}-v^{(k-1)}_{2j}\cdot\frac{v^{(k-1)}_{11}}{v^{(k-1)}_{21}}, & \mbox{if } j\leq n-k  \mbox{ and } i=1 \\
+v^{(k)}_{(1)(N-j+1)}, & \mbox{if } j\leq n-k \mbox{ and } i=2 \\
+\end{cases} \mbox{,}
+$$
+\noindent where $k\in\mathbb{Z}$, such that $0<k<N-2$. $S(z)$ is the 
+characteristic polynomial of a stable system if and only if the following 
+four propositions hold:
+\begin{itemize}
+\item $R_{1}$: $S(1)>0$;
+\item $R_{2}$: $(-1)^{N}S(-1)>0$;
+\item $R_{3}$: $\vert{a_{0}}\vert <a_{N}$;
+\item $R_{4}$: $m_{11}>0\iff m_{31}\wedge m_{51}\wedge \dots \wedge m_{(2N-3)(1)}$.
+\end{itemize}
+
+The stability property $\phi_{stability}$ is then encoded as follows:
+$$
+\phi_{stability}\iff \ (R_{1} \wedge R_{2} \wedge R_{3} \wedge R_{4}).
+$$
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Counterexample-Guided Abstractly-Refined Inductive Synthesis of Controllers for LTI Systems} 
+\section{Counterexample-Guided Abstractly-Refined Inductive Synthesis of Safe Controllers for LTI Systems} 
 \label{sec:CEGARIS} 

### 2017-01-18 cav2017/cav2017.tex
minor changes

@@
 For the stability  test procedure, the following Jury matrix 
-$M=[m_{ij}]_{(2N-2)\times N}$ is built  from $S(z)$ coefficients:
+$M=[m_{ij}]_{(2N-2)\times N}$ is built  from $P(z)$ coefficients:
 $$
@@
 $$
-\noindent where $k\in\mathbb{Z}$, such that $0<k<N-2$. $S(z)$ is the 
+\noindent where $k\in\mathbb{Z}$, such that $0<k<N-2$. $P(z)$ is the 
 characteristic polynomial of a stable system if and only if the following 
@@
 \item $R_{1}$: $S(1)>0$;
-\item $R_{2}$: $(-1)^{N}S(-1)>0$;
+\item $R_{2}$: $(-1)^{N}P(-1)>0$;
 \item $R_{3}$: $\vert{a_{0}}\vert <a_{N}$;
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Synthesisig the dynamics}\label{sec:cof_synth}
+\subsection{Synthesising the dynamics}\label{sec:cof_synth}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-01-18 cav2017/cav2017.tex
review 2.3 Stability of closed-loop systems

@@
 
-A discrete-time system is asymptotically stable if and only if all the roots 
-of the characteristic polynomial ({\it i.e.}, the eigenvalues) are inside of 
-the unity circle, {\it i.e.}, their absolute value are less than 
+A discrete-time system is asymptotically stable if and only if all 
+characteristic polynomial roots (i.e., eigenvalues) are inside of 
+the unity circle, i.e., their absolute value are less than 
 one~\cite{astrom1997computer}. For a closed-loop system as~\eqref{eq:closedloopss}, 
-the characteristic polynomial $P(z)$ should be computed as follows:
+the characteristic polynomial $P(z)$ can be computed as follows:
 \begin{equation}
@@
 Jury's criterion provides necessary and sufficient conditions for the eigenvalues 
-to be within the unit circle and, consequently, the system is stable.  Given a 
+to be within the unit circle and, consequently, for the system to be stable.  Given a 
 polynomial $P(z)$ of the form
@@
 Jury's criterion explores solely the coefficients ($a_{0},a_{1},...,a_{N-1}$) 
-of $P(z)$ for checking the validity of the stability property $\phi_{stability}$.
-
-In particular, Jury stability test is already explained in the control system 
-literature ({\it e.g.}~\cite{fadali}). This study, however, limits itself to 
+of $P(z)$ for checking the validity of the stability property (represented by 
+$\phi_{stability}$).
+
+Jury stability test is already explained in the control system 
+literature~\cite{fadali}. This study, however, limits itself to 
 explain the encoding of Jury's criterion for the formal synthesis purpose. 

### 2017-01-18 cav2017/cav2017.tex
write introduction of section 4

@@
 
+This section is split into four parts. Section~\ref{description-of-the-benchmarks} 
+discusses the experimental setup and our state-space control system benchmarks, 
+while Section~\ref{experimental-objectives} describes the experimental objectives. 
+Section~\ref{experimental-results} presents the experimental results obtained on the 
+benchmarks with our tool DSSynth, while Section~\ref{threats-to-validity} describes
+threats to the validity of our automated synthesis procedure for digital controllers.
+
 %-------------------------------
 \subsection{Description of the Benchmarks}
+\label{description-of-the-benchmarks}
 %-------------------------------
@@
 The table~\ref{table:State-space benchmarks} summarizes the list of benchmarks extracted from literature~\cite{Franklin15,converters,maglev,CTMS} and adopted in our experiments.
-
-%The first plant represents a DC motor position model from~\cite{CTMS}.
-It is a third order system and presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
-%$$
-%\textbf{A}=\left[\begin{array}{ccc}
-%0		& 1 		& 0						\\
-%0 		& -1.087	& 8587					\\
-%0		& -9964		& -1.455\times 10^{6}	\\
-%\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
-%0 \\ 0 \\ -1.455\times10^{6}
-%\end{array}\right]
-%$$
-%%
-%$$
-%\textbf{C}=\left[\begin{array}{ccc}
-%1 & 0 & 0\\
-%\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
-%\theta \\ \dot{\theta} \\ i \\
-%\end{array}\right],
-%$$
-%where the states $\theta$, $\dot{\theta}$, and $i$ are respectively the rotor angular position, rotor angular rate and the current of armature. The DC motor is stable in open loop.
-%
-%The second benchmark is an aircraft pitch dynamics model extracted from~\cite{CTMS}.
-It is a third order system and it presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
-%$$
-%\textbf{A}=\left[\begin{array}{ccc}
-%-0.313	& 56.7 		& 0		\\
-%-0.0139	& -0.426	& 0		\\
-%0		& 56.7		& 0		\\
-%\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
-%0.232 \\ 0.0203 \\ 0
-%\end{array}\right]
-%$$
-%%
-%$$
-%\textbf{C}=\left[\begin{array}{ccc}
-%0 & 0 & 1\\
-%\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
-%\alpha \\ \dot{\theta} \\ \theta \\
-%\end{array}\right],
-%$$
-%where the states $\alpha$, $\dot{\theta}$, and $\theta$ are respectively the aircraft attack angle, pitch rate and the pitch angle.
-The aircraft pitch dynamic is critically stable in open loop, with a pole in origin of $s$-plane.
-%
-%The third benchmark is a ball magnetic levitation model extracted from~\cite{maglev}.
-It is a third order system presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
-%$$
-%\textbf{A}=\left[\begin{array}{ccc}
-%0		& 1 		& 0		\\
-%1752	& 0			& -34.07\\
-%0		& 0			& -38.27\\
-%\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
-%0 \\ 0 \\ 1.923
-%\end{array}\right]
-%$$
-%%
-%$$
-%\textbf{C}=\left[\begin{array}{ccc}
-%1 & 0 & 0\\
-%\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
-%z \\ \dot{z} \\ i \\
-%\end{array}\right],
-%$$
-%where the states $z$, $\dot{z}$, and $i$ are respectively the vertical displacement of the ball, its rate and the coil current. This system  is unstable in open loop.
-%
-%There are three benchmarks representing classic DC-DC converters: buck, boost, and buck-boost.
-They are SISO second-order systems stable in open-loop, and their state vector is $\textbf{x}=\textbf{x}=\left[\begin{array}{c}
-%i_{L} \\ v_{C}\\
-%\end{array}\right]$, where $i_{L}$ is the current in the coil and $v_{c}$ is the voltage on the capacitor.
-The matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, and $\textbf{D}$ for the buck converter are:
-%$$
-%\textbf{A}=\left[\begin{array}{cc}
-%0		& -500 \\
-%4545	& -1515\\
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%125 \\ 0 \\
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{cc}
-%0 & 1\\
-%\end{array}\right],~ \textbf{D}= 0.
-%$$
-%
-%The matrices of the boost converter are:
-%$$
-%\textbf{A}=\left[\begin{array}{cc}
-%0		& -375 \\
-%3409	& -1515\\
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%500 \\ 0 \\
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{cc}
-%0 & 1\\
-%\end{array}\right],~ \textbf{D}= 0.
-%$$
-%
-%Finally, the matrices of the buck-boost converter are:
-%$$
-%\textbf{A}=\left[\begin{array}{cc}
-%0		& 375 \\
-%-3409	& -1515\\
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%125 \\ 0 \\
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{cc}
-%0 & 1\\
-%\end{array}\right],~ \textbf{D}= 0.
-%$$
-%
-%Additionally, various dynamic systems model were extracted from~\cite{Franklin15} and incorporated to our test suite. They are: 
-%\begin{itemize}
-%\item{\textbf{automotive cruise control system:} 
-%$$
-%\textbf{A}=-0.05,~ \textbf{B} = 0.03125~
-%\textbf{C}=0.032,~ \textbf{D}= 0;
-%$$
-%}
-%\item{\textbf{DC motor:} 
-%$$
-%\textbf{A}=\left[\begin{array}{cc}
-%-1000		& -13 \\
-%-8			& 0\\
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%4 \\ 0 \\
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{cc}
-%0 & 6.25\\
-%\end{array}\right],~ \textbf{D}= 0;
-%$$
-%}
-%\item{\textbf{helicopter longitudinal motion:} 
-%$$
-%\textbf{A}=\left[\begin{array}{ccc}
-%-0.42		& 0.0168		& -0.396	\\
-%0.5			& 0				& 0			\\
-%0			& 0.5 			& 0			
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%16 \\ 0 \\ 0
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{ccc}
-%0.6125	& -0.6125	& 15.44 \\
-%\end{array}\right],~ \textbf{D}= 0;
-%$$
-%}
-%\item{\textbf{inverted pendulum cart position:} 
-%$$
-%\textbf{A}=\left[\begin{array}{cccc}
-%0		& 1		& 0 	& 0	\\
-%1		& 0		& 0		& 0	\\
-%0		& 1 	& 0		& 0 \\
-%0		& 0		& 1 	& 0 \\	
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%1 \\ 0 \\ 0 \\ 0
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{cccc}
-%0	& 0	& 1 & -0.75 \\
-%\end{array}\right],~ \textbf{D}= 0;
-%$$
-%}
-%\item{\textbf{inverted pendulum angle:} 
-%$$
-%\textbf{A}=\left[\begin{array}{cc}
-%0		& 1	\\
-%1		& 0	\\
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%1 \\ 0 \\ 0 \\ 0
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{cc}
-% 0	& 1 \\
-%\end{array}\right],~ \textbf{D}= 0;
-%$$
-%}
-%\item{\textbf{magnetic pointer:} 
-%$$
-%\textbf{A}=\left[\begin{array}{ccc}
-%-0.271		& -0.05336	& 0	\\
-%0.03125		& 0			& 0	\\
-%0			& 0.01562 	& 0	\\	
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%1 \\ 0 \\ 0
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{ccc}
-%0	& -0.5888	& -0.2562 \\
-%\end{array}\right],~ \textbf{D}= 0;
-%$$
-%}
-%\item{\textbf{magnetic suspension:} 
-%$$
-%\textbf{A}=\left[\begin{array}{cc}
-%0		& 31.25	\\
-%32		& 0		\\	
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%8 \\ 0
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{cc}
-%0	& 9.766 	\\
-%\end{array}\right],~ \textbf{D}= 0;
-%$$
-%}
-%\item{\textbf{pendulum:} 
-%$$
-%\textbf{A}=\left[\begin{array}{cc}
-%0		& -2.453	\\
-%4		& 0			\\	
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%4 \\ 0
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{cc}
-%-1.225	& -2.15 	\\
-%\end{array}\right],~ \textbf{D}= 9.8;
-%$$
-%}
-%\item{\textbf{1/4 car suspension:} 
-%$$
-%\textbf{A}=\left[\begin{array}{cccc}
-%-516.1	& -222.1& -79.75& -33.06	\\
-%256		& 0		& 0		& 0			\\
-%0		& 64 	& 0		& 0 \\
-%0		& 0		& 32 	& 0 \\	
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%8 \\ 0 \\ 0 \\ 0
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{cccc}
-%0	& 0	& 9.969 & 4.133 \\
-%\end{array}\right],~ \textbf{D}= 0;
-%$$
-%}
-%\item{\textbf{computer tape driver:} 
-%$$
-%\textbf{A}=\left[\begin{array}{ccc}
-%-1760		& -976.6	& -457.8	\\
-%1024		& 0			& 0			\\
-%0			& 512 		& 0			\\	
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%8 \\ 0 \\ 0
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{ccc}
-%1.5	& 2.051	& 1.144 \\
-%\end{array}\right],~ \textbf{D}= 0;
-%$$
-%}
-%\item{\textbf{USCG cutter Tampa heading angle:} 
-%$$
-%\textbf{A}=\left[\begin{array}{ccc}
-%-0.271		& -0.05336	& 0	\\
-%0.03125		& 0			& 0			\\
-%0			& 0.01562 	& 0			\\	
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%1 \\ 0 \\ 0
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{ccc}
-%0	& -0.5888	& -0.2562 \\
-%\end{array}\right],~ \textbf{D}= 0;
-%$$
-%}
-%\end{itemize}
 
@@
 \subsection{Objectives}
+\label{experimental-objectives}
 %-------------------------------
@@
 \subsection{Results}
+\label{experimental-results}
 %-------------------------------
@@
 \subsection{Threats to validity}
+\label{threats-to-validity}
 %-------------------------------

### 2017-01-18 cav2017/cav2017.tex
First version of safety specifications description

@@
 \begin{equation}
+\label{eq:controlaction}
 u_k = r_{k} - K x_k, 
@@
 
-Finally, we also require a safety specification $\Psi(\vec{u},\vec{y})$, which is
-given as a set of linear constraints over the inputs and outputs.
+Finally, we also require that the closed-loop systems meets safety specifications.
+A safety specification establish bounds for the states, such that he controller $K$ must maintain the states within these bounds for any initial state.
+
+The safety property (represented by $\phi_{safety}$) is encoded as follows:
+\begin{equation}
+\label{eq:safetyliteral}
+\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{x_{i}^{-} \leq x_{i,k} \leq x_{i}^{+}},
+\end{equation}
+where $x_{i}^{-}$ and $x_{i}^{+}$ are respectively the lower and upper bound of the $i$-th state $x_{i}$ at the $k$-th instant, i.e., the states will always be within the $n$-dimensional hyperbox defined by the safety specifications (bounds).
+
+The closed-loop state-space system have to be unrolled until a specific depth ($k_{bound}$) to ensure $\phi_{safety}$.
+The limit $k_{bound}$ is the number of iterations sufficient so that the rate of variation (derivative) of the states is negligible ensuring the boundaries will not be violated for any $k>k_{bound}$.
+\commentib{The k-bound estimative must be explained.}
+
+For any $k\leq k_{bound}$ the states must be computed considering the FWL effects in all operations related to the control action~\ref{eq:controlaction} and disregarding it in the state equation ~\eqref{eq:plant}.
+Thus, the states are computed using the following equations:
+\begin{equation}
+\label{eq:ssunroll}
+\left\lbrace
+\begin{array}{l}
+u_{k}=\mathcal{F}_{\langle I,F \rangle}(r_{k}-\mathcal{F}_{\langle I,F \rangle}(\mathcal{F}_{\langle I,F \rangle}(K)\cdot\mathcal{F}_{\langle I,F \rangle}(x_{k})))\\
+x_{k+1}=Ax_{k}+Bu_{k}
+\end{array}\right.
+\end{equation}
 

### 2017-01-18 cav2017/cav2017.tex
minor changes

--- 2017-01-18 cav2017/cav2017.tex
@@
 
-A discrete-time system is asymptotically stable if and only if all 
-characteristic polynomial roots (i.e., eigenvalues) are inside of 
-the unity circle, i.e., their absolute value are less than 
+A discrete-time system is asymptotically stable if and only if all the roots 
+of the characteristic polynomial ({\it i.e.}, the eigenvalues) are inside of 
+the unity circle, {\it i.e.}, their absolute value are less than 
 one~\cite{astrom1997computer}. For a closed-loop system as~\eqref{eq:closedloopss}, 
-the characteristic polynomial $P(z)$ can be computed as follows:
+the characteristic polynomial $P(z)$ should be computed as follows:
 \begin{equation}
@@
 Jury's criterion provides necessary and sufficient conditions for the eigenvalues 
-to be within the unit circle and, consequently, for the system to be stable.  Given a 
+to be within the unit circle and, consequently, the system is stable.  Given a 
 polynomial $P(z)$ of the form
@@
 Jury's criterion explores solely the coefficients ($a_{0},a_{1},...,a_{N-1}$) 
-of $P(z)$ for checking the validity of the stability property (represented by 
-$\phi_{stability}$).
-
-Jury stability test is already explained in the control system 
-literature~\cite{fadali}. This study, however, limits itself to 
+of $P(z)$ for checking the validity of the stability property $\phi_{stability}$.
+
+In particular, Jury stability test is already explained in the control system 
+literature ({\it e.g.}~\cite{fadali}). This study, however, limits itself to 
 explain the encoding of Jury's criterion for the formal synthesis purpose. 
@@
 
-Finally, we also require a safety specification $\Psi(\vec{u},\vec{y})$, which is
-given as a set of linear constraints over the inputs and outputs.
+Finally, we also require that the closed-loop systems meets safety specifications.
+A safety specification establish bounds for the states, such that he controller $K$ must maintain the states within these bounds for any initial state.
+
+The safety property (represented by $\phi_{safety}$) is encoded as follows:
+\begin{equation}
+\label{eq:safetyliteral}
+\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{x_{i}^{-} \leq x_{i,k} \leq x_{i}^{+}},
+\end{equation}
+where $x_{i}^{-}$ and $x_{i}^{+}$ are respectively the lower and upper bound of the $i$-th state $x_{i}$ at the $k$-th instant, i.e., the states will always be within the $n$-dimensional hyperbox defined by the safety specifications (bounds).
+
+The closed-loop state-space system have to be unrolled until a specific depth ($k_{bound}$) to ensure $\phi_{safety}$.
+The limit $k_{bound}$ is the number of iterations sufficient so that the rate of variation (derivative) of the states is negligible ensuring the boundaries will not be violated for any $k>k_{bound}$.
+\commentib{The k-bound estimative must be explained.}
+
+For any $k\leq k_{bound}$ the states must be computed considering the FWL effects in all operations related to the control action~\ref{eq:controlaction} and disregarding it in the state equation ~\eqref{eq:plant}.
+Thus, the states are computed using the following equations:
+\begin{equation}
+\label{eq:ssunroll}
+\left\lbrace
+\begin{array}{l}
+u_{k}=\mathcal{F}_{\langle I,F \rangle}(r_{k}-\mathcal{F}_{\langle I,F \rangle}(\mathcal{F}_{\langle I,F \rangle}(K)\cdot\mathcal{F}_{\langle I,F \rangle}(x_{k})))\\
+x_{k+1}=Ax_{k}+Bu_{k}
+\end{array}\right.
+\end{equation}
+
+The input sequence $u_{k}$ is non-deterministic with known bounds $u^{+}$ and $u^{-}$, such that ${u^{-} \leq u_{k} \leq u^{+}},\forall k\geq 0$.
 

### 2017-01-18 cav2017/cav2017.tex
minor change

@@
 
-For any $k\leq k_{bound}$ the states must be computed considering the FWL effects in all operations related to the control action~\ref{eq:controlaction} and disregarding it in the state equation ~\eqref{eq:plant}.
+For any $k\leq k_{bound}$ the states must be computed considering the FWL effects in all operations related to the control action~\eqref{eq:controlaction} and disregarding it in the state equation ~\eqref{eq:plant}.
 Thus, the states are computed using the following equations:

### 2017-01-19 cav2017/cav2017.tex
ciao

@@
 \begin{abstract}
-The abstract should summarize the contents of the paper and should
-contain at least 70 and at most 150 words. It should be written using the
-\emph{abstract} environment.
-\keywords{We would like to encourage you to list your keywords within
-the abstract section}
+This work presents a sound and automated approach to synthesise digital feedback control architectures for physical plans represented as linear, time invariant models. 
+Models are encompassed by dynamical equations with inputs, evolving over a continuous state space describing the evolution of the physical variables of the system.
+
+\keywords{
+State-space dynamical models of physical systems; 
+Digital controllers; 
+Analogue-to-digital converters; 
+Time sampling; 
+Quantisation; 
+Fixed-point arithmetics; 
+CEGIS; 
+safety requirements. 
+}
 \end{abstract}

### 2017-01-19 cav2017/cav2017.tex
review 2.7 Safety specifications for Cyber-Physical Systems

--- 2017-01-18 cav2017/cav2017.tex
@@
 
-Finally, we also require that the closed-loop systems meets safety specifications.
-A safety specification establish bounds for the states, such that he controller $K$ must maintain the states within these bounds for any initial state.
-
-The safety property (represented by $\phi_{safety}$) is encoded as follows:
+We require that the closed-loop system meets safety specifications. 
+A safety specification establishes bounds for the states, such that 
+the controller $K$ must maintain the states within a given lower and upper 
+bound for any initial state.
+
+The safety property represented by $\phi_{safety}$ is encoded as follows:
+%
 \begin{equation}
@@
 \end{equation}
-where $x_{i}^{-}$ and $x_{i}^{+}$ are respectively the lower and upper bound of the $i$-th state $x_{i}$ at the $k$-th instant, i.e., the states will always be within the $n$-dimensional hyperbox defined by the safety specifications (bounds).
-
-The closed-loop state-space system have to be unrolled until a specific depth ($k_{bound}$) to ensure $\phi_{safety}$.
-The limit $k_{bound}$ is the number of iterations sufficient so that the rate of variation (derivative) of the states is negligible ensuring the boundaries will not be violated for any $k>k_{bound}$.
-\commentib{The k-bound estimative must be explained.}
-
-For any $k\leq k_{bound}$ the states must be computed considering the FWL effects in all operations related to the control action~\ref{eq:controlaction} and disregarding it in the state equation ~\eqref{eq:plant}.
+%
+where $x_{i}^{-}$ and $x_{i}^{+}$ are the lower and upper bound 
+of the $i$-th state $x_{i}$ at the $k$-th instant, respectively.
+This means that the states will always be within the $n$-dimensional 
+hyper-box, which is typically defined by the safety specification.
+
+The closed-loop state-space system has to be unwound up to a given 
+depth $k_{bound}$ to ensure that $\phi_{safety}$ holds. 
+Here, $k_{bound}$ represents the number of iterations 
+to sufficiently unwind the closed-loop state-space system 
+so that the variation rate (derivative) of the states is negligible, 
+ensuring that the boundaries are not be violated for any $k>k_{bound}$. 
+\commentib{The k-bound estimation must be explained.}
+
+For any $k\leq k_{bound}$, the states must be computed considering 
+the FWL effects in all operations related to the control action~\eqref{eq:controlaction} 
+and disregarding it in the state equation~\eqref{eq:plant}. 
 Thus, the states are computed using the following equations:
+%
 \begin{equation}

### 2017-01-19 cav2017/cav2017.tex
ciao

@@
 Models are encompassed by dynamical equations with inputs, evolving over a continuous state space describing the evolution of the physical variables of the system.  
-
+The approach is divided in two main part, brought together by a counter-example guided inductive synthesis (CEGIS) loop, as follows.   
+First, we devise a static feedback controller that stabilises the system;  
+then, we verify its potential safety by means of either of the following approaches: 
+forward reachability analysis via unfolding of the dynamics, or invariance generation;  
+if the above step fails, we loop back and invoke a CEGIS call to seek alternative stabilising feedbacks, 
+benefitting from the obtained counter-examples to safety. 
+[Mention GA and Abstract Acceleration here?] 
+The approach is proven sound by accounting for errors due to \ldots 
+We test the procedure on a gazillion benchmarks, excruciatingly encoded manually by Iury and Lucas. 
 \keywords{

### 2017-01-19 cav2017/cav2017.tex
fix typos

@@
 \begin{abstract}
-This work presents a sound and automated approach to synthesise digital feedback control architectures for physical plans represented as linear, time invariant models. 
+This work presents a sound and automated approach to synthesise digital feedback control architectures for physical plants represented as linear, time invariant models. 
 Models are encompassed by dynamical equations with inputs, evolving over a continuous state space describing the evolution of the physical variables of the system.  

### 2017-01-19 cav2017/cav2017.tex
keep references in ascending order of citation
split the CEGIS section to accommodate both approaches

--- 2017-01-19 cav2017/cav2017.tex
@@
 %
+\todo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
+
 where $x_{i}^{-}$ and $x_{i}^{+}$ are the lower and upper bound 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Counterexample-Guided Abstractly-Refined Inductive Synthesis of Safe Controllers for LTI Systems} 
+\section{CEGIS of Safe Controllers for LTI Systems with Solution Generalisation} 
 \label{sec:CEGARIS} 
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%Abstractly-Refined
 
 {\bf Assumption:} We consider the reference signal to be 0, whereas the initial states are non-deterministic.
-
-\todo{Explain the implicaitions of this.}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Verification of a Controllable Observed System}
+\todo{Explain all the assumptions.}
+
+%\todo{Integrate this paragraph better (Cristina):}
+Our CEGIS technique with generalisation %abstraction refinement
+relies on parametrising the target language, which
+induces a lattice of progressively more expressive languages.  We
+start by attempting to synthesise a program at the lowest point on
+this lattice and increase the parameters of the language until we
+reach a point at which the synthesis succeeds. As well as giving us an
+automatic search procedure, this parametrisation greatly increases the
+efficiency of our system since languages low down the lattice are very
+easy to decide safety for (i.e. the validation oracle finds an answer
+fast). If a program can be synthesised in a low-complexity language,
+the whole procedure finishes much faster than if synthesis had been
+attempted in a high-complexity language.
+
+We investigate two different approaches of integrating solution generalisation 
+into CEGIS:
+\begin{itemize}
+\item[1.] The first approach uses abstract acceleration to compute the set of reachable states, which 
+enables abstraction refinement inside the CEGIS loop. 
+\item[2.] The second approach relies on computing a completeness threshold $k$ for each loop such that it is sufficient to 
+unroll the corresponding loop $k$ times. For this approach the generalisation step is given as an incremental
+increase of precision and sampling rate.
+\end{itemize}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{CEGIS with Abstraction Refinement}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsubsection{Verification of a Controllable Observed System}
 \label{sec:cof_verification}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Synthesising the dynamics}\label{sec:cof_synth}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\todo{Integrate this paragraph better (Cristina):}
-Out CEGIS technique with abstraction refinement
-relies on parametrising the target language, which
-induces a lattice of progressively more expressive languages.  We
-start by attempting to synthesise a program at the lowest point on
-this lattice and increase the parameters of the language until we
-reach a point at which the synthesis succeeds. As well as giving us an
-automatic search procedure, this parametrisation greatly increases the
-efficiency of our system since languages low down the lattice are very
-easy to decide safety for (i.e. the validation oracle finds an answer
-fast). If a program can be synthesised in a low-complexity language,
-the whole procedure finishes much faster than if synthesis had been
-attempted in a high-complexity language.
-
+\subsubsection{Synthesising the dynamics}\label{sec:cof_synth}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 Now that we have explained the verification process, we may proceed to describe the synthesis procedure, which is illustrated in figure \ref{fig:CEGARIS}.
@@
 \end{figure}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{CEGIS with Precision and Sampling Rate Incrementation}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 

### 2017-01-19 cav2017/cav2017.tex

@@
 subject of stability %, working typically on continuous domains
-\cite{sadabadi2016static,DBLP:journals/corr/AbateBCCDKK16}, or using switched
+\cite{DBLP:journals/corr/AbateBCCDKK16,sadabadi2016static}, or using switched
 models~\cite{DBLP:conf/emsoft/RavanbakhshS16}.

### 2017-01-19 cav2017/cav2017.tex
+ general architecture of the synthesiser

@@
 
-\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
+\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows, patterns}
 
@@
 \end{itemize}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Architecture of the program synthesizer}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\label{synthesizer-general}
+%
+%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
+%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
+% 
+The input specification provided to the program synthesizer is of the form
+$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
+$\vec{P}$ ranges over functions, $\vec{x}$ ranges over ground terms and
+$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
+some finite domain $\mathcal{D}$.
+
+The design of our synthesizer 
+%is given in Figure~\ref{fig:CEGIS} and 
+consists of two phases, an inductive synthesis phase and a validation phase,
+%{\sc Synthesize} and {\sc Verify}, 
+which interact via a finite set of test vectors {\sc inputs} that is updated incrementally. 
+Given the aforementioned specification $\sigma$, the inductive synthesis
+procedure
+tries to find an existential witness $\vec{P}$ satisfying the specification
+$\sigma(\vec{x}, \vec{P})$ for all $\vec{x}$ in {\sc inputs} (as opposed to
+all $\vec{x} \in \mathcal{D}$).
+%
+If the synthesis phase succeeds in finding a witness~$\vec{P}$, this witness
+is a candidate solution to the full synthesis formula.  We pass this
+candidate solution to the validation phase, which checks whether it is a full
+solution (i.e., $\vec{P}$ satisfies the specification $\sigma(\vec{x},
+\vec{P})$ for all $\vec{x}\in\mathcal{D}$).
+%
+%determines whether
+%it does satisfy the specification on all inputs by checking
+%satisfiability of the following verification formula:
+%
+%$\exists \vec{x} . \lnot \sigma(\vec{x}, \vec{P})$
+%If this formula is unsatisfiable, 
+%% the candidate solution is in fact a 
+%% full solution.
+%
+If this is the case, then the algorithm terminates.  Otherwise, additional
+information is provided to the inductive synthesis phase in the form of a new
+counterexample that is added to the {\sc inputs} set and the loop iterates
+again.
+%% the witness $\vec{x}$ denote an input on which the
+%% candidate solution fails to meet the specification.  Thus, $\vec{x}$ is
+%% added to the {\sc inputs} set, and the loop iterates again.
+
+It is
+worth noting that each iteration of the loop adds a new input to the
+finite set $\text{\sc inputs}$ that is used for synthesis.  Given that
+the full set of inputs $\mathcal{D}$
+%\blue{[which by now should have a name, as suggested to be introduced above]} 
+is finite, this means that the refinement loop
+can only iterate a finite number of times.
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+% \begin{figure*}[htb]
+% \centering
+% %\resizebox{1\textwidth}{!}
+% {
+%  \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
+%   \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
+% },
+%           row sep=.6cm, column sep=2cm] {
+%    \coordinate (aux1);
+%    \& \coordinate (aux2);
+%    \&;\\
+%    \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
+%    \&
+%    complexnode/.pic={ 
+%      \node[rectangle,draw,dotted,
+% 	minimum width=7cm,
+% 	minimum height=1cm,
+%         pattern=north west lines, pattern color=gray!20,
+% 	label={\sc Verify},] (verif) {};
+%      \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc Uncertainty}};
+%      \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=2cm]verif.center) {{\sc Precision}};
+%    } 
+%    \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
+%    %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
+%    %% \&
+%    %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
+%    \& \\
+%    \node[minimum height=0.5cm] (gp) {\sf Closed-loop System Search};
+%    \&
+%    complexnode/.pic={ 
+%      \coordinate (aux);
+%    \node[minimum height=0.5cm] (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based Verifier};
+%    \node[minimum height=0.5cm] (fp)  at ([xshift=2cm]aux.center) {\sf Fixed-point Arithmetic Verifier};
+%    }   
+%     \\
+%   };
+
+%    \path
+%     ([yshift=2em]synth.east) edge node[xshift=-0.5em] {Candidate solution} ([yshift=2em]verif1.west)
+%     ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east)
+%     ([xshift=5em]verif1.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]bmc.north)
+%     ([xshift=5em]verif2.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]fp.north)
+%     ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
+%     ([xshift=-5em]fp.north) edge node[align=center]  {True/\\False} ([xshift=-5em]verif2.south)
+%     (verif2) edge node {} (done)
+%     ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
+%     ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south)
+%     (aux1) edge (synth.north);
+%    \path[-]
+%    (verif2.north) edge node[align=center] {} ([xshift=6.7cm]aux2)
+%    ([xshift=6.7cm]aux2) edge node[align=center] {Increase Precision} (aux1);
+
+%  \end{tikzpicture}
+% }
+% \caption{The CEGIS loop with precision and sampling rate incrementation}
+% \label{fig:CEGIS}}
+% \end{figure*}
 

### 2017-01-19 cav2017/cav2017.tex
refine general CEGIS architecture
included macro for tool name
review introduction

@@
 \begin{document}
+
+\newcommand\tool{{\sf DSSynth}\xspace}
 
@@
 
-In this paper, we propose the synthesis of \emph{safe} control algorithms for
+In this paper, however, we propose the synthesis of \emph{safe} control algorithms for
 cyberphysical systems taking into consideration the continuous domain
@@
 %% \emph{safe}.
-Due to the complexity of such systems, in this work we focus
+Due to the complexity of such systems, in this particular work we focus
 on linear models with known configurations and perform parametric synthesis
@@
 \todo{Add contributions (Cristina)}
+
+\todo{We should briefly describe both approaches that we have implemented.}
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Architecture of the program synthesizer}
+\subsection{General Architecture of the program synthesizer}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 
+In Sec.~\ref{sec:CEGIS-abstraction-refinement} and 
+Sec.~\ref{sec:CEGIS-precision-incrementation}, we explain how we 
+specialise the general CEGIS approach in order to perform solution generalisation.
+
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsection{CEGIS with Abstraction Refinement}
+\label{sec:CEGIS-abstraction-refinement}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 \subsection{CEGIS with Precision and Sampling Rate Incrementation}
+\label{sec:CEGIS-precision-incrementation}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-01-19 cav2017/cav2017.tex
+ CEGIS figure with precision/sampling incrementation

--- 2017-01-19 cav2017/cav2017.tex
@@
 \usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
+\usetikzlibrary{patterns}
 
@@
 \end{itemize}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{General Architecture of the program synthesizer}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\label{synthesizer-general}
+%
+%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
+%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
+% 
+The input specification provided to the program synthesizer is of the form
+$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
+$\vec{P}$ ranges over functions, $\vec{x}$ ranges over ground terms and
+$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
+some finite domain $\mathcal{D}$.
+
+The design of our synthesizer 
+%is given in Figure~\ref{fig:CEGIS} and 
+consists of two phases, an inductive synthesis phase and a validation phase,
+%{\sc Synthesize} and {\sc Verify}, 
+which interact via a finite set of test vectors {\sc inputs} that is updated incrementally. 
+Given the aforementioned specification $\sigma$, the inductive synthesis
+procedure
+tries to find an existential witness $\vec{P}$ satisfying the specification
+$\sigma(\vec{x}, \vec{P})$ for all $\vec{x}$ in {\sc inputs} (as opposed to
+all $\vec{x} \in \mathcal{D}$).
+%
+If the synthesis phase succeeds in finding a witness~$\vec{P}$, this witness
+is a candidate solution to the full synthesis formula.  We pass this
+candidate solution to the validation phase, which checks whether it is a full
+solution (i.e., $\vec{P}$ satisfies the specification $\sigma(\vec{x},
+\vec{P})$ for all $\vec{x}\in\mathcal{D}$).
+%
+%determines whether
+%it does satisfy the specification on all inputs by checking
+%satisfiability of the following verification formula:
+%
+%$\exists \vec{x} . \lnot \sigma(\vec{x}, \vec{P})$
+%If this formula is unsatisfiable, 
+%% the candidate solution is in fact a 
+%% full solution.
+%
+If this is the case, then the algorithm terminates.  Otherwise, additional
+information is provided to the inductive synthesis phase in the form of a new
+counterexample that is added to the {\sc inputs} set and the loop iterates
+again.
+%% the witness $\vec{x}$ denote an input on which the
+%% candidate solution fails to meet the specification.  Thus, $\vec{x}$ is
+%% added to the {\sc inputs} set, and the loop iterates again.
+
+It is
+worth noting that each iteration of the loop adds a new input to the
+finite set $\text{\sc inputs}$ that is used for synthesis.  Given that
+the full set of inputs $\mathcal{D}$
+%\blue{[which by now should have a name, as suggested to be introduced above]} 
+is finite, this means that the refinement loop
+can only iterate a finite number of times.
+
+In Sec.~\ref{sec:CEGIS-abstraction-refinement} and 
+Sec.~\ref{sec:CEGIS-precision-incrementation}, we explain how we 
+specialise the general CEGIS approach in order to perform solution generalisation.
 
@@
 \subsection{CEGIS with Abstraction Refinement}
+\label{sec:CEGIS-abstraction-refinement}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 \subsection{CEGIS with Precision and Sampling Rate Incrementation}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\label{sec:CEGIS-precision-incrementation}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+\begin{figure}[htb]
+{\scriptsize
+\centering
+%\resizebox{.8\textwidth}{!}
+{
+ \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
+},
+          row sep=.6cm, column sep=.9cm] {
+   \coordinate (aux1);
+   \& \coordinate (aux2);
+   \&;\\
+   \coordinate (aux3);
+   \& \coordinate (aux4);
+   \&;\\
+   \coordinate (aux5);
+   \& \coordinate (aux6);
+   \&;\\
+   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
+   \&
+   complexnode/.pic={ 
+     \node[rectangle,draw,dotted,
+	minimum width=8cm,
+	minimum height=1cm,
+        pattern=north west lines, pattern color=gray!20,
+	label={\sc Verify},] (verif) {};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2.9cm]verif.center) {{\sc Uncertainty}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=-0.8cm]verif.center) {{\sc Precision}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=1.2cm]verif.center) {{\sc Sampling}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc Complete}};
+   } 
+   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
+   \& \\
+   \node[minimum height=0cm] (gp) {\sf Closed-loop \\ System Search};
+   \&
+   complexnode/.pic={ 
+     \coordinate (aux);
+   \node (bmc) at ([xshift=-2.9cm]aux.center) {\sf BMC-based \\Verifier};
+   \node (fp)  at ([xshift=-.8cm]aux.center) {\sf Fixed-point \\ Arithmetic\\Verifier};
+   \node (sv)  at ([xshift=1.2cm]aux.center) {\sf Sampling\\Verifier};
+   \node (cv)  at ([xshift=3.1cm]aux.center) {\sf Completeness\\Verifier};
+   }   
+    \\
+  };
+
+   \path
+    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$P$} ([yshift=2em]verif1.west)
+    ([yshift=-2em]verif1.west) edge node {C-ex} ([yshift=-2em]synth.east)
+    ([xshift=-5em]fp.north) edge node[align=center]  {T/F} ([xshift=-5em]verif2.south)
+    ([xshift=-5em]sv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif3.south)
+    ([xshift=-5em]cv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif4.south)
+    ([xshift=5em]verif1.south) edge node[align=center] {$P$} ([xshift=5em]bmc.north)
+    ([xshift=5em]verif2.south) edge node[align=center] {$P$} ([xshift=5em]fp.north)
+    ([xshift=5em]verif3.south) edge node[align=center] {$P$} ([xshift=5em]sv.north)
+    ([xshift=5em]verif4.south) edge node[align=center] {$P$} ([xshift=5em]cv.north)
+    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
+    (verif) edge node {} (done)
+    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
+    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$P$} ([xshift=-5em]synth.south)
+    (aux1) edge (synth.north);
+   \path[-]
+   (verif2.north) edge node[align=center] {} ([xshift=-2.7cm]aux6)
+   ([xshift=-2.7cm]aux6) edge node[align=center] {Increase Precision} (aux5)
+   (verif3.north) edge node[align=center] {} ([xshift=4cm]aux4)
+   ([xshift=4cm]aux4) edge node[align=center] {Increase Sampling Rate} (aux3)
+   (verif4.north) edge node[align=center] {} ([xshift=10.5cm]aux2)
+   ([xshift=10.5cm]aux2) edge node[align=center] {Increase $k$} (aux1);
+
+ \end{tikzpicture}
+}}
+\caption{The CEGIS loop with precision and sampling rate incrementation}
+\label{fig:CEGIS}
+\end{figure}
 

### 2017-01-19 cav2017/cav2017.tex
small change fig 2

@@
    (verif4.north) edge node[align=center] {} ([xshift=10.5cm]aux2)
-   ([xshift=10.5cm]aux2) edge node[align=center] {Increase $k$} (aux1);
+   ([xshift=10.5cm]aux2) edge node[align=center] {Increase Completeness Threshold} (aux1);
 

### 2017-01-19 cav2017/cav2017.tex
review 1.1 Related Work

--- 2017-01-19 cav2017/cav2017.tex
@@
 
-\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
-\usetikzlibrary{patterns}
+\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows, patterns}
 
@@
 In \cite{DBLP:journals/corr/AbateBCCDKK16}, Abate et al.  focus on
-synthesising stabilizing controllers for continuous plants.  While
-they also make use of a CEGIS-based technique, their approach is
+synthesising stabilizing controllers for continuous plants
+by exploiting advantage in bit-accurate verification of C programs 
+to obtain a verifier for software-implemented digital control~\cite{Bessa16}.  
+While they also make use of a CEGIS-based technique, their approach is
 restricted to synthesising controllers for hybrid closed-loop systems
 that are stable and only consider transfer function models.  In contrast,
-in the current paper we consider a state-space
+in the current paper, we consider a state-space
 representation of the physical system and synthesise controllers that
@@
 stable by design.  The analyses
-in~\cite{DBLP:conf/hybrid/WangGRJF16,DBLP:conf/hybrid/RouxJG15} rely on an
+in~\cite{DBLP:conf/hybrid/RouxJG15,DBLP:conf/hybrid/WangGRJF16} rely on an
 invariant computation on the discrete system dynamics using Semi-Definite
@@
 upper bound is introduced in the verification phase.
-The work in \cite{picasso2002construction,picasso2003stabilization} introduces
+The work in \cite{picasso2003stabilization,picasso2002construction} introduces
 attractive invariant sets as a mechanism to bound the quantization error effect
@@
 
-\begin{figure}[htb]
-{\scriptsize
-\centering
-%\resizebox{.8\textwidth}{!}
-{
- \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
-},
-          row sep=.6cm, column sep=.9cm] {
-   \coordinate (aux1);
-   \& \coordinate (aux2);
-   \&;\\
-   \coordinate (aux3);
-   \& \coordinate (aux4);
-   \&;\\
-   \coordinate (aux5);
-   \& \coordinate (aux6);
-   \&;\\
-   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
-   \&
-   complexnode/.pic={ 
-     \node[rectangle,draw,dotted,
-	minimum width=8cm,
-	minimum height=1cm,
-        pattern=north west lines, pattern color=gray!20,
-	label={\sc Verify},] (verif) {};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2.9cm]verif.center) {{\sc Uncertainty}};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=-0.8cm]verif.center) {{\sc Precision}};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=1.2cm]verif.center) {{\sc Sampling}};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc Complete}};
-   } 
-   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
-   \& \\
-   \node[minimum height=0cm] (gp) {\sf Closed-loop \\ System Search};
-   \&
-   complexnode/.pic={ 
-     \coordinate (aux);
-   \node (bmc) at ([xshift=-2.9cm]aux.center) {\sf BMC-based \\Verifier};
-   \node (fp)  at ([xshift=-.8cm]aux.center) {\sf Fixed-point \\ Arithmetic\\Verifier};
-   \node (sv)  at ([xshift=1.2cm]aux.center) {\sf Sampling\\Verifier};
-   \node (cv)  at ([xshift=3.1cm]aux.center) {\sf Completeness\\Verifier};
-   }   
-    \\
-  };
-
-   \path
-    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$P$} ([yshift=2em]verif1.west)
-    ([yshift=-2em]verif1.west) edge node {C-ex} ([yshift=-2em]synth.east)
-    ([xshift=-5em]fp.north) edge node[align=center]  {T/F} ([xshift=-5em]verif2.south)
-    ([xshift=-5em]sv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif3.south)
-    ([xshift=-5em]cv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif4.south)
-    ([xshift=5em]verif1.south) edge node[align=center] {$P$} ([xshift=5em]bmc.north)
-    ([xshift=5em]verif2.south) edge node[align=center] {$P$} ([xshift=5em]fp.north)
-    ([xshift=5em]verif3.south) edge node[align=center] {$P$} ([xshift=5em]sv.north)
-    ([xshift=5em]verif4.south) edge node[align=center] {$P$} ([xshift=5em]cv.north)
-    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
-    (verif) edge node {} (done)
-    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
-    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$P$} ([xshift=-5em]synth.south)
-    (aux1) edge (synth.north);
-   \path[-]
-   (verif2.north) edge node[align=center] {} ([xshift=-2.7cm]aux6)
-   ([xshift=-2.7cm]aux6) edge node[align=center] {Increase Precision} (aux5)
-   (verif3.north) edge node[align=center] {} ([xshift=4cm]aux4)
-   ([xshift=4cm]aux4) edge node[align=center] {Increase Sampling Rate} (aux3)
-   (verif4.north) edge node[align=center] {} ([xshift=10.5cm]aux2)
-   ([xshift=10.5cm]aux2) edge node[align=center] {Increase $k$} (aux1);
-
- \end{tikzpicture}
-}}
-\caption{The CEGIS loop with precision and sampling rate incrementation}
-\label{fig:CEGIS}
-\end{figure}
+% \begin{figure*}[htb]
+% \centering
+% %\resizebox{1\textwidth}{!}
+% {
+%  \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
+%   \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
+% },
+%           row sep=.6cm, column sep=2cm] {
+%    \coordinate (aux1);
+%    \& \coordinate (aux2);
+%    \&;\\
+%    \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
+%    \&
+%    complexnode/.pic={ 
+%      \node[rectangle,draw,dotted,
+% 	minimum width=7cm,
+% 	minimum height=1cm,
+%         pattern=north west lines, pattern color=gray!20,
+% 	label={\sc Verify},] (verif) {};
+%      \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc Uncertainty}};
+%      \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=2cm]verif.center) {{\sc Precision}};
+%    } 
+%    \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
+%    %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
+%    %% \&
+%    %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
+%    \& \\
+%    \node[minimum height=0.5cm] (gp) {\sf Closed-loop System Search};
+%    \&
+%    complexnode/.pic={ 
+%      \coordinate (aux);
+%    \node[minimum height=0.5cm] (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based Verifier};
+%    \node[minimum height=0.5cm] (fp)  at ([xshift=2cm]aux.center) {\sf Fixed-point Arithmetic Verifier};
+%    }   
+%     \\
+%   };
+
+%    \path
+%     ([yshift=2em]synth.east) edge node[xshift=-0.5em] {Candidate solution} ([yshift=2em]verif1.west)
+%     ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east)
+%     ([xshift=5em]verif1.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]bmc.north)
+%     ([xshift=5em]verif2.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]fp.north)
+%     ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
+%     ([xshift=-5em]fp.north) edge node[align=center]  {True/\\False} ([xshift=-5em]verif2.south)
+%     (verif2) edge node {} (done)
+%     ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
+%     ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south)
+%     (aux1) edge (synth.north);
+%    \path[-]
+%    (verif2.north) edge node[align=center] {} ([xshift=6.7cm]aux2)
+%    ([xshift=6.7cm]aux2) edge node[align=center] {Increase Precision} (aux1);
+
+%  \end{tikzpicture}
+% }
+% \caption{The CEGIS loop with precision and sampling rate incrementation}
+% \label{fig:CEGIS}}
+% \end{figure*}
 

### 2017-01-19 cav2017/cav2017.tex
make fig 1 and fig 2 look alike
subsections don't have all the words in the title capitalized

@@
 %-------------------------------
-\subsection{Related Work}
+\subsection{Related work}
 \label{sec:relw}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Numeric Representations and Soundness} 
+\subsection{Numeric representations and soundness} 
 \label{sec:numeric_rep}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Fixed Word Length Effects on Matrix Multiplications}
+\subsection{Fixed word length effects on matrix multiplications}
 \label{sec:cof_fwl}
@@
 %-------------------------------
-\subsection{Safety specifications for Cyber-Physical Systems}
+\subsection{Safety specifications for cyber-physical systems}
 \label{ssec:safety}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{General Architecture of the program synthesizer}
+\subsection{General architecture of the program synthesizer}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{CEGIS with Abstraction Refinement}
+\subsection{CEGIS with abstraction refinement}
 \label{sec:CEGIS-abstraction-refinement}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Verification of a Controllable Observed System}
+\subsubsection{Verification of a controllable observed system}
 \label{sec:cof_verification}
@@
 \centering
+{\scriptsize
 \hspace*{-1cm}
@@
    \& ;\\
-   \&\node[fill=yellow!20,align=center] (pre) {{\sc 1. pre-}\\{\sc processing}};
-   \& \node[fill=yellow!20,align=center] (abstract) {\sc 4. abstraction};
+   \&\node[fill=gray!20,align=center] (pre) {{\sc 1. pre-}\\{\sc processing}};
+   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstraction};
        % \node[draw=none] (FIK) at ([xshift=2.5cm,yshift=.3cm]abstract)  {\sc $\Psi (\mat{K})$};
@@
    \& 
-   \& \node[fill=yellow!20,align=center, minimum width=3cm] (synth) {\sc 2. synthesiser};
+   \& \node[fill=gray!20,align=center, minimum width=3cm] (synth) {\sc 2. synthesise};
        %\node[draw=none] (KL) at ([xshift=2.5cm,yshift=-.25cm]synth)  {\sc $\mat{K},\mat{L}$};
        %\node[draw=none] (NKL) at ([xshift=2cm,yshift=1cm]synth)  {\sc $P_a$};
-   \& \node[fill=yellow!20,align=center, minimum width=4cm] (verify) {\sc 3. verifier ($\Psi$)};
+   \& \node[fill=gray!20,align=center, minimum width=4cm] (verify) {\sc 3. verify ($\Psi$)};
        %\node[draw=none] (VUNS) at ([xshift=.6cm,yshift=1cm]verify)  {\sc SAT};
        \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc UNSAT};
-   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
+   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
    \&
@@
 \end{tikzpicture}
+}
 \caption{The CEGIS loop with abstraction refinement\label{fig:CEGARIS}.}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{CEGIS with Precision and Sampling Rate Incrementation}
+\subsection{CEGIS with precision and sampling rate incrementation}
 \label{sec:CEGIS-precision-incrementation}
@@
 %-------------------------------
-\subsection{Description of the Benchmarks}
+\subsection{Description of the benchmarks}
 %-------------------------------
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Discretising Continuous Space Dynamics}
+\subsection{Discretising continuous space dynamics}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Modelling Quantization as noise}
+\subsection{Modelling quantization as noise}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Controllable Canonical Form} \label{sec:reachable}
+\subsection{Controllable canonical form} \label{sec:reachable}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Observable Canonical Form} \label{sec:observable}
+\subsection{Observable canonical form} \label{sec:observable}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-01-19 cav2017/cav2017.tex
restructuring

@@
 
-The closed-loop state-space system has to be unwound up to a given 
-depth $k_{bound}$ to ensure that $\phi_{safety}$ holds. 
-Here, $k_{bound}$ represents the number of iterations 
-to sufficiently unwind the closed-loop state-space system 
-so that the variation rate (derivative) of the states is negligible, 
-ensuring that the boundaries are not be violated for any $k>k_{bound}$. 
-\commentib{The k-bound estimation must be explained.}
-
-For any $k\leq k_{bound}$, the states must be computed considering 
+The states must be computed considering 
 the FWL effects in all operations related to the control action~\eqref{eq:controlaction} 
@@
 
+\subsubsection{Computing the set of reachable states}
+\todo{explain the use of abstract acceleration}
+
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Synthesising the dynamics}\label{sec:cof_synth}
+\subsubsection{Controller synthesis}\label{sec:cof_synth}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 \caption{The CEGIS loop with precision and sampling rate incrementation}
-\label{fig:CEGIS}
+\label{fig:CEGIS-precision-increment}
 \end{figure}
+
+\subsubsection{Computing the reachable states}
+
+In order to compute the set of reachable states we find 
+a completeness threshold $k_{bound}$.
+Essentially, $k_{bound}$ represents the number of iterations 
+to sufficiently unwind the closed-loop state-space system 
+so that the variation rate (derivative) of the states is negligible, 
+ensuring that the boundaries are not be violated for any $k>k_{bound}$. 
+The closed-loop state-space system has to be unwound up to a given 
+depth $k_{bound}$ to ensure that $\phi_{safety}$ holds.
+
+\todo{discuss the completeness threshold computation}
+
+\subsubsection{Controller synthesis}
+
+\todo{Describe each step in Fig~\ref{fig:CEGIS-precision-increment}.}
 

### 2017-01-19 cav2017/cav2017.tex
some revision of sec 2.5 (more needed)

@@
 leading or trailing bits when the domain requires prescaling (ie the maximum is smaller than $0.5$ or the minimum
-is greater than $2$)
+is greater than $2$).
 Let also $\mathbb{R}_* \langle M,E \rangle$ be a floating point domain with $M$ bits
@@
 Since we've shown that a floating point domain is a union of a number of fixed point domains, we will continue our
-reasoning on fixed point only. Our points will apply to the floating point domain by extension.
+reasoning on fixed point only. Our reasoning will apply to the floating point domain by extension.
 The following approximation errors will arise:
 \begin{enumerate}
-\item Truncation\\
-Let $\mathcal{F}\langle I,F \rangle(\cdot) : \mathbb{R} \rightarrow \mathbb{R}\langle I,F \rangle, \tilde x=\mathcal{F}\langle I,F \rangle(x) = x-\delta : \delta=x\ \%_F\  c\tilde x$, where $\%_F$ is the modulus operation performed on the last bit of the representation ($2^{-F}$).\\
+\item {\bf Truncation:}
+Let $\mathcal{F}\langle I,F \rangle(\cdot) : \mathbb{R} \rightarrow \mathbb{R}\langle I,F \rangle, \tilde x=\mathcal{F}\langle I,F \rangle(x) = x-\delta : \delta=x\ \%_F\  c\tilde x$, where $\%_F$ is the modulus operation performed on the last bit of the representation ($2^{-F}$).
 The number $\delta$ corresponds to the truncation error of the representation and it will propagate across operations.
-\item Rounding\\
-Every time an operation is performed on a number in the $\mathbb{R} \langle I,F,E \rangle$ domain, an error may be
-introduced due to truncation of the result.
+\item {\bf Rounding:}
+%% Every time an operation is performed on a number in the $\mathbb{R} \langle I,F,E \rangle$ domain, an error may be
+%% introduced due to truncation of the result.
 Let us define $c\langle i,f,e \rangle \in \mathbb{R}\langle I,F,E\rangle$, where $i \in [-2^{I-1}\ 2^{I-1}],f \in [0 1),e \in [-2^{E-1}\ 2^{E-1}]$ are its assigned values.
@@
 performing fewer operations can be more precise in this respect than iterative ones. 
-\item Overflow\\
-Another source of error introduced by Finite Word Length representations is that of overflow. The finite word length set a
+\item {\bf Overflow:}
+  %Another source of error introduced by Finite Word Length representations is that of overflow.
+  The finite word length set a
 maximum representable number in the domain ($\pm 2^{I-1}+1-2^{-F}$), which means that any number outside this range
@@
 functions to prevent them or raise alarms in their presence. In the case of verification, the latter is seen as a safety problem.
-\item Null/Zeno behaviour\\
+\item {\bf Null/Zeno behaviour:}
 Whilst this work does not explore the effect of Zeno behaviours, it is worth noting that this effect may also be caused by rounding

### 2017-01-19 cav2017/cav2017.tex
typo

@@
 Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
-which may restricts the observability of the state-space from the output space.
+which may restrict the observability of the state-space from the output space.
 \begin{equation}

### 2017-01-20 cav2017/cav2017.tex
review abstract

@@
 \begin{abstract}
-This work presents a sound and automated approach to synthesise digital feedback control architectures for physical plants represented as linear, time invariant models. 
-Models are encompassed by dynamical equations with inputs, evolving over a continuous state space describing the evolution of the physical variables of the system.  
-The approach is divided in two main part, brought together by a counter-example guided inductive synthesis (CEGIS) loop, as follows.   
-First, we devise a static feedback controller that stabilises the system;  
-then, we verify its potential safety by means of either of the following approaches: 
-forward reachability analysis via unfolding of the dynamics, or invariance generation;  
-if the above step fails, we loop back and invoke a CEGIS call to seek alternative stabilising feedbacks, 
-benefitting from the obtained counter-examples to safety. 
-[Mention GA and Abstract Acceleration here?] 
-The approach is proven sound by accounting for errors due to \ldots 
-We test the procedure on a gazillion benchmarks, excruciatingly encoded manually by Iury and Lucas. 
+This work presents a sound and automated approach to synthesise 
+digital feedback control architectures for physical plants represented 
+as linear, time invariant models. Models are encompassed by dynamical 
+equations with inputs, evolving over a continuous state space describing 
+the evolution of the physical variables of the system.  The approach is divided 
+in two main parts, brought together by a counter-example guided inductive 
+synthesis (CEGIS) loop, as follows. First, we devise a static feedback controller 
+that stabilises the system; then, we verify its potential safety by means of either 
+of the following approaches: forward reachability analysis via unfolding of the dynamics, 
+or invariance generation;  if the above step fails, we loop back and invoke a CEGIS call 
+to seek alternative stabilising feedbacks, benefitting from the obtained counter-examples 
+to safety. 
+\textcolor{red}{[Mention GA and Abstract Acceleration here?] 
+The approach is proven sound by accounting for errors due to \ldots }
+The proposed synthesis approaches and respective tool are evaluated considering
+a set of intricate physical plant models taken from the digital control literature.
 \keywords{

### 2017-01-20 cav2017/cav2017.tex
+subsection on pb description

--- 2017-01-19 cav2017/cav2017.tex
@@
 leading or trailing bits when the domain requires prescaling (ie the maximum is smaller than $0.5$ or the minimum
-is greater than $2$).
+is greater than $2$)
 Let also $\mathbb{R}_* \langle M,E \rangle$ be a floating point domain with $M$ bits
@@
 Since we've shown that a floating point domain is a union of a number of fixed point domains, we will continue our
-reasoning on fixed point only. Our reasoning will apply to the floating point domain by extension.
+reasoning on fixed point only. Our points will apply to the floating point domain by extension.
 The following approximation errors will arise:
 \begin{enumerate}
-\item {\bf Truncation:}
-Let $\mathcal{F}\langle I,F \rangle(\cdot) : \mathbb{R} \rightarrow \mathbb{R}\langle I,F \rangle, \tilde x=\mathcal{F}\langle I,F \rangle(x) = x-\delta : \delta=x\ \%_F\  c\tilde x$, where $\%_F$ is the modulus operation performed on the last bit of the representation ($2^{-F}$).
+\item Truncation\\
+Let $\mathcal{F}\langle I,F \rangle(\cdot) : \mathbb{R} \rightarrow \mathbb{R}\langle I,F \rangle, \tilde x=\mathcal{F}\langle I,F \rangle(x) = x-\delta : \delta=x\ \%_F\  c\tilde x$, where $\%_F$ is the modulus operation performed on the last bit of the representation ($2^{-F}$).\\
 The number $\delta$ corresponds to the truncation error of the representation and it will propagate across operations.
-\item {\bf Rounding:}
-%% Every time an operation is performed on a number in the $\mathbb{R} \langle I,F,E \rangle$ domain, an error may be
-%% introduced due to truncation of the result.
+\item Rounding\\
+Every time an operation is performed on a number in the $\mathbb{R} \langle I,F,E \rangle$ domain, an error may be
+introduced due to truncation of the result.
 Let us define $c\langle i,f,e \rangle \in \mathbb{R}\langle I,F,E\rangle$, where $i \in [-2^{I-1}\ 2^{I-1}],f \in [0 1),e \in [-2^{E-1}\ 2^{E-1}]$ are its assigned values.
@@
 performing fewer operations can be more precise in this respect than iterative ones. 
-\item {\bf Overflow:}
-  %Another source of error introduced by Finite Word Length representations is that of overflow.
-  The finite word length set a
+\item Overflow\\
+Another source of error introduced by Finite Word Length representations is that of overflow. The finite word length set a
 maximum representable number in the domain ($\pm 2^{I-1}+1-2^{-F}$), which means that any number outside this range
@@
 functions to prevent them or raise alarms in their presence. In the case of verification, the latter is seen as a safety problem.
-\item {\bf Null/Zeno behaviour:}
+\item Null/Zeno behaviour\\
 Whilst this work does not explore the effect of Zeno behaviours, it is worth noting that this effect may also be caused by rounding
@@
 specialise the general CEGIS approach in order to perform solution generalisation.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Our synthesis problem}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+The synthesis problem we are trying to solve is the following:
+find a digital controller $K$ (see Eq.~\ref{eq:controlaction})
+that makes the closed-loop system safe for 
+initial state $x_0$, reference signal $r_k$ and input $u_k$
+as defined in Sec.~\ref{ssec:safety}. Note that, 
+as mentioned at the beginning of the section, 
+we consider the reference signal to be 0.
+When mapping back to the notation used for describing the general architecture 
+of the program synthesizer, the controller $K$ denotes $P$ and 
+$x_0$ and $u_k$ and  represents $x$.
+
+We compute the coefficients for $K$ 
+in the domain $\mathbb{R}<I,F>$.
 

### 2017-01-20 cav2017/cav2017.tex
small change

@@
 we consider the reference signal to be 0.
-When mapping back to the notation used for describing the general architecture 
+Then , when mapping back to the notation used for describing the general architecture 
 of the program synthesizer, the controller $K$ denotes $P$ and 
-$x_0$ and $u_k$ and  represents $x$.
+$(x_0, u_k)$ represents $x$.
 

### 2017-01-20 cav2017/cav2017.tex
typo

@@
 we consider the reference signal to be 0.
-Then , when mapping back to the notation used for describing the general architecture 
+Then, when mapping back to the notation used for describing the general architecture 
 of the program synthesizer, the controller $K$ denotes $P$ and 

### 2017-01-20 cav2017/cav2017.tex
review introduction

@@
 
+We describe and evaluate two approaches for synthesizing digital controllers 
+for state-space physical plants. Both approaches consider a counterexample 
+guided inductive synthesis (CEGIS) loop. In the first approach, 
+we devise a digital controller that stabilizes the system; then, we verify its 
+potential safety by unfolding the dynamics of the system and checking for 
+a completeness threshold. \textcolor{red}{In the second approach,...}
+
+\textcolor{red}{we have to connect both paragraphs...}
+
 To this end, we formalise the notion of solution generalisation for
 Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
-of abstraction refinement
-%on simplified abstractions of the system
-in order to achieve scalability.
+of abstraction refinement in order to achieve scalability.
 This strategy enables the inductive generalisation engine inside CEGIS
-to look for candidate solutions in a reduced solution space.  %% The
-%% latter case is a well know technique for abstract interpretation that
-%% allows simplification of the procedures over a sound abstraction of
-%% the verification model.
-
-%% \textcolor{red}{Cristina: Can you please further expand the introduction
-%% by adding more details about our synthesis approach to control systems?}
+to look for candidate solutions in a reduced solution space.
 
@@
 
-\todo{We should briefly describe both approaches that we have implemented.}
-
-%-------------------------------
-\subsection{Related work}
+%-------------------------------
+\section{Related work}
 \label{sec:relw}
@@
 specialise the general CEGIS approach in order to perform solution generalisation.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Our synthesis problem}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-The synthesis problem we are trying to solve is the following:
-find a digital controller $K$ (see Eq.~\ref{eq:controlaction})
-that makes the closed-loop system safe for 
-initial state $x_0$, reference signal $r_k$ and input $u_k$
-as defined in Sec.~\ref{ssec:safety}. Note that, 
-as mentioned at the beginning of the section, 
-we consider the reference signal to be 0.
-Then, when mapping back to the notation used for describing the general architecture 
-of the program synthesizer, the controller $K$ denotes $P$ and 
-$(x_0, u_k)$ represents $x$.
-
-We compute the coefficients for $K$ 
-in the domain $\mathbb{R}<I,F>$.
 

### 2017-01-20 cav2017/cav2017.tex

@@
 specialise the general CEGIS approach in order to perform solution generalisation.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Our synthesis problem}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+The synthesis problem we are trying to solve is the following:
+find a digital controller $K$ (see Eq.~\ref{eq:controlaction})
+that makes the closed-loop system safe for 
+initial state $x_0$, reference signal $r_k$ and input $u_k$
+as defined in Sec.~\ref{ssec:safety}. Note that, 
+as mentioned at the beginning of the section, 
+we consider the reference signal to be 0.
+Then, when mapping back to the notation used for describing the general architecture 
+of the program synthesizer, the controller $K$ denotes $P$ and 
+$(x_0, u_k)$ represents $x$.
+
+We compute the coefficients for $K$ 
+in the domain $\mathbb{R}<I,F>$.
 

### 2017-01-20 cav2017/cav2017.tex
swap completeness and sampling checks in fig 2

--- 2017-01-20 cav2017/cav2017.tex
@@
      \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=-0.8cm]verif.center) {{\sc Precision}};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=1.2cm]verif.center) {{\sc Sampling}};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc Complete}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=1.2cm]verif.center) {{\sc Complete}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc Sampling}};
    } 
@@
    \node (fp)  at ([xshift=-.8cm]aux.center) {\sf Fixed-point \\ Arithmetic\\Verifier};
-   \node (sv)  at ([xshift=1.2cm]aux.center) {\sf Sampling\\Verifier};
-   \node (cv)  at ([xshift=3.1cm]aux.center) {\sf Completeness\\Verifier};
+   \node (sv)  at ([xshift=1.2cm]aux.center) {\sf Completeness\\Verifier};
+   \node (cv)  at ([xshift=3.1cm]aux.center) {\sf Sampling\\Verifier};
    }   
@@
    (verif3.north) edge node[align=center] {} ([xshift=4cm]aux4)
-   ([xshift=4cm]aux4) edge node[align=center] {Increase Sampling Rate} (aux3)
+   ([xshift=4cm]aux4) edge node[align=center] {Increase Completeness Threshold} (aux3)
    (verif4.north) edge node[align=center] {} ([xshift=10.5cm]aux2)
-   ([xshift=10.5cm]aux2) edge node[align=center] {Increase Completeness Threshold} (aux1);
+   ([xshift=10.5cm]aux2) edge node[align=center] {Increase Sampling Rate} (aux1);
 

### 2017-01-20 cav2017/cav2017.tex
added 5.1 Description of the benchmarks

--- 2017-01-20 cav2017/cav2017.tex
@@
 
-The table~\ref{table:State-space benchmarks} summarizes the list of benchmarks extracted from literature~\cite{Franklin15,converters,maglev,CTMS} and adopted in our experiments.
-
-%The first plant represents a DC motor position model from~\cite{CTMS}.
-It is a third order system and presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
-%$$
-%\textbf{A}=\left[\begin{array}{ccc}
-%0		& 1 		& 0						\\
-%0 		& -1.087	& 8587					\\
-%0		& -9964		& -1.455\times 10^{6}	\\
-%\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
-%0 \\ 0 \\ -1.455\times10^{6}
-%\end{array}\right]
-%$$
-%%
-%$$
-%\textbf{C}=\left[\begin{array}{ccc}
-%1 & 0 & 0\\
-%\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
-%\theta \\ \dot{\theta} \\ i \\
-%\end{array}\right],
-%$$
-%where the states $\theta$, $\dot{\theta}$, and $i$ are respectively the rotor angular position, rotor angular rate and the current of armature. The DC motor is stable in open loop.
-%
-%The second benchmark is an aircraft pitch dynamics model extracted from~\cite{CTMS}.
-It is a third order system and it presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
-%$$
-%\textbf{A}=\left[\begin{array}{ccc}
-%-0.313	& 56.7 		& 0		\\
-%-0.0139	& -0.426	& 0		\\
-%0		& 56.7		& 0		\\
-%\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
-%0.232 \\ 0.0203 \\ 0
-%\end{array}\right]
-%$$
-%%
-%$$
-%\textbf{C}=\left[\begin{array}{ccc}
-%0 & 0 & 1\\
-%\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
-%\alpha \\ \dot{\theta} \\ \theta \\
-%\end{array}\right],
-%$$
-%where the states $\alpha$, $\dot{\theta}$, and $\theta$ are respectively the aircraft attack angle, pitch rate and the pitch angle.
-The aircraft pitch dynamic is critically stable in open loop, with a pole in origin of $s$-plane.
-%
-%The third benchmark is a ball magnetic levitation model extracted from~\cite{maglev}.
-It is a third order system presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
-%$$
-%\textbf{A}=\left[\begin{array}{ccc}
-%0		& 1 		& 0		\\
-%1752	& 0			& -34.07\\
-%0		& 0			& -38.27\\
-%\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
-%0 \\ 0 \\ 1.923
-%\end{array}\right]
-%$$
-%%
-%$$
-%\textbf{C}=\left[\begin{array}{ccc}
-%1 & 0 & 0\\
-%\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
-%z \\ \dot{z} \\ i \\
-%\end{array}\right],
-%$$
-%where the states $z$, $\dot{z}$, and $i$ are respectively the vertical displacement of the ball, its rate and the coil current. This system  is unstable in open loop.
-%
-%There are three benchmarks representing classic DC-DC converters: buck, boost, and buck-boost.
-They are SISO second-order systems stable in open-loop, and their state vector is $\textbf{x}=\textbf{x}=\left[\begin{array}{c}
-%i_{L} \\ v_{C}\\
-%\end{array}\right]$, where $i_{L}$ is the current in the coil and $v_{c}$ is the voltage on the capacitor.
-The matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, and $\textbf{D}$ for the buck converter are:
-%$$
-%\textbf{A}=\left[\begin{array}{cc}
-%0		& -500 \\
-%4545	& -1515\\
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%125 \\ 0 \\
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{cc}
-%0 & 1\\
-%\end{array}\right],~ \textbf{D}= 0.
-%$$
-%
-%The matrices of the boost converter are:
-%$$
-%\textbf{A}=\left[\begin{array}{cc}
-%0		& -375 \\
-%3409	& -1515\\
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%500 \\ 0 \\
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{cc}
-%0 & 1\\
-%\end{array}\right],~ \textbf{D}= 0.
-%$$
-%
-%Finally, the matrices of the buck-boost converter are:
-%$$
-%\textbf{A}=\left[\begin{array}{cc}
-%0		& 375 \\
-%-3409	& -1515\\
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%125 \\ 0 \\
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{cc}
-%0 & 1\\
-%\end{array}\right],~ \textbf{D}= 0.
-%$$
-%
-%Additionally, various dynamic systems model were extracted from~\cite{Franklin15} and incorporated to our test suite. They are: 
-%\begin{itemize}
-%\item{\textbf{automotive cruise control system:} 
-%$$
-%\textbf{A}=-0.05,~ \textbf{B} = 0.03125~
-%\textbf{C}=0.032,~ \textbf{D}= 0;
-%$$
-%}
-%\item{\textbf{DC motor:} 
-%$$
-%\textbf{A}=\left[\begin{array}{cc}
-%-1000		& -13 \\
-%-8			& 0\\
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%4 \\ 0 \\
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{cc}
-%0 & 6.25\\
-%\end{array}\right],~ \textbf{D}= 0;
-%$$
-%}
-%\item{\textbf{helicopter longitudinal motion:} 
-%$$
-%\textbf{A}=\left[\begin{array}{ccc}
-%-0.42		& 0.0168		& -0.396	\\
-%0.5			& 0				& 0			\\
-%0			& 0.5 			& 0			
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%16 \\ 0 \\ 0
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{ccc}
-%0.6125	& -0.6125	& 15.44 \\
-%\end{array}\right],~ \textbf{D}= 0;
-%$$
-%}
-%\item{\textbf{inverted pendulum cart position:} 
-%$$
-%\textbf{A}=\left[\begin{array}{cccc}
-%0		& 1		& 0 	& 0	\\
-%1		& 0		& 0		& 0	\\
-%0		& 1 	& 0		& 0 \\
-%0		& 0		& 1 	& 0 \\	
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%1 \\ 0 \\ 0 \\ 0
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{cccc}
-%0	& 0	& 1 & -0.75 \\
-%\end{array}\right],~ \textbf{D}= 0;
-%$$
-%}
-%\item{\textbf{inverted pendulum angle:} 
-%$$
-%\textbf{A}=\left[\begin{array}{cc}
-%0		& 1	\\
-%1		& 0	\\
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%1 \\ 0 \\ 0 \\ 0
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{cc}
-% 0	& 1 \\
-%\end{array}\right],~ \textbf{D}= 0;
-%$$
-%}
-%\item{\textbf{magnetic pointer:} 
-%$$
-%\textbf{A}=\left[\begin{array}{ccc}
-%-0.271		& -0.05336	& 0	\\
-%0.03125		& 0			& 0	\\
-%0			& 0.01562 	& 0	\\	
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%1 \\ 0 \\ 0
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{ccc}
-%0	& -0.5888	& -0.2562 \\
-%\end{array}\right],~ \textbf{D}= 0;
-%$$
-%}
-%\item{\textbf{magnetic suspension:} 
-%$$
-%\textbf{A}=\left[\begin{array}{cc}
-%0		& 31.25	\\
-%32		& 0		\\	
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%8 \\ 0
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{cc}
-%0	& 9.766 	\\
-%\end{array}\right],~ \textbf{D}= 0;
-%$$
-%}
-%\item{\textbf{pendulum:} 
-%$$
-%\textbf{A}=\left[\begin{array}{cc}
-%0		& -2.453	\\
-%4		& 0			\\	
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%4 \\ 0
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{cc}
-%-1.225	& -2.15 	\\
-%\end{array}\right],~ \textbf{D}= 9.8;
-%$$
-%}
-%\item{\textbf{1/4 car suspension:} 
-%$$
-%\textbf{A}=\left[\begin{array}{cccc}
-%-516.1	& -222.1& -79.75& -33.06	\\
-%256		& 0		& 0		& 0			\\
-%0		& 64 	& 0		& 0 \\
-%0		& 0		& 32 	& 0 \\	
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%8 \\ 0 \\ 0 \\ 0
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{cccc}
-%0	& 0	& 9.969 & 4.133 \\
-%\end{array}\right],~ \textbf{D}= 0;
-%$$
-%}
-%\item{\textbf{computer tape driver:} 
-%$$
-%\textbf{A}=\left[\begin{array}{ccc}
-%-1760		& -976.6	& -457.8	\\
-%1024		& 0			& 0			\\
-%0			& 512 		& 0			\\	
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%8 \\ 0 \\ 0
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{ccc}
-%1.5	& 2.051	& 1.144 \\
-%\end{array}\right],~ \textbf{D}= 0;
-%$$
-%}
-%\item{\textbf{USCG cutter Tampa heading angle:} 
-%$$
-%\textbf{A}=\left[\begin{array}{ccc}
-%-0.271		& -0.05336	& 0	\\
-%0.03125		& 0			& 0			\\
-%0			& 0.01562 	& 0			\\	
-%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
-%1 \\ 0 \\ 0
-%\end{array}\right]~
-%\textbf{C}=\left[\begin{array}{ccc}
-%0	& -0.5888	& -0.2562 \\
-%\end{array}\right],~ \textbf{D}= 0;
-%$$
-%}
-%\end{itemize}
+Table~\ref{table:State-space benchmarks} summarizes the list of benchmarks extracted from the literature~\cite{Franklin15,maglev,converters,CTMS}.
+\textit{DC Motor Position} plant provides the rotary motion that coupled with wheels and cables provides translational motion.
+\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and control based on the pitch dimension only.
+\textit{Ball Magnetic Levitation} plant describes the magnetic field that keeps a metal ball hanged in air.
 

### 2017-01-20 cav2017/cav2017.tex
description of second approach (fig 2)

--- 2017-01-20 cav2017/cav2017.tex
@@
    \& 
-   \& \node[fill=gray!20,align=center, minimum width=3cm] (synth) {\sc 2. synthesise};
+   \& \node[fill=gray!20,align=center, minimum width=3cm] (synth) {\sc 2. synthesize};
        %\node[draw=none] (KL) at ([xshift=2.5cm,yshift=-.25cm]synth)  {\sc $\mat{K},\mat{L}$};
@@
    \&;\\
-   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
+   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc 1.Synthesize}};
    \&
@@
 	label={\sc Verify},] (verif) {};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2.9cm]verif.center) {{\sc Uncertainty}};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=-0.8cm]verif.center) {{\sc Precision}};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=1.2cm]verif.center) {{\sc Complete}};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc Sampling}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2.9cm]verif.center) {{\sc 2.Safety}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=-0.8cm]verif.center) {{\sc 3.Precision}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=1.2cm]verif.center) {{\sc 4.Complete}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc 5.Sampling}};
    } 
@@
 In order to compute the set of reachable states we find 
-a completeness threshold $k_{bound}$.
-Essentially, $k_{bound}$ represents the number of iterations 
+a completeness threshold $\overline{k}$.
+Essentially, $\overline{k}$ represents the number of iterations 
 to sufficiently unwind the closed-loop state-space system 
 so that the variation rate (derivative) of the states is negligible, 
-ensuring that the boundaries are not be violated for any $k>k_{bound}$. 
+ensuring that the boundaries are not be violated for any $k>\overline{k}$. 
 The closed-loop state-space system has to be unwound up to a given 
-depth $k_{bound}$ to ensure that $\phi_{safety}$ holds.
+depth $\overline{k}$ to ensure that $\phi_{safety}$ holds.
 
@@
 
-\todo{Describe each step in Fig~\ref{fig:CEGIS-precision-increment}.}
+The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}
+and consists of five stages, as described below:
+
+1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to 
+compute a candidate solution $K$.
+
+2. The validation phase consists of four stages 
+(blocks 2-5 in Fig.~\ref{fig:CEGIS-precision-increment}), where the first one
+performs potentially unsound
+operations assuming a plant precision $<I_p,F_p>$, 
+current $k$ and sampling rate, whereas the subsequent three stages are used to 
+restore soundness.
+
+3. This stage restores soundness with respect to the plant precision
+by using interval arithmetic \cite{moore1966interval} to validate the 
+operations performed by the previous stage.
+
+4. This stage checks that the current  $k$ 
+is large enough to ensure that the boundaries are not be violated for any $k'>k$.
+In order to verify this, we compute the 
+completeness threshold $\overline{k}$ for the current candidate $K$ 
+and check that $k{\leq}\overline{k}$.
+
+5. The last stage ensures that the current sampling rate is large enough by using an 
+external checker (\todo{add more details here once we have them}).
 

### 2017-01-20 cav2017/cav2017.tex
typo

@@
 performs potentially unsound
-operations assuming a plant precision $<I_p,F_p>$, 
+operations assuming a plant's precision $<I_p,F_p>$, 
 current $k$ and sampling rate, whereas the subsequent three stages are used to 

### 2017-01-20 cav2017/cav2017.tex
revised CEGIS 2nd approach

@@
 We investigate two different approaches of integrating solution generalisation 
-into CEGIS:
+with CEGIS:
 \begin{itemize}
-\item[1.] The first approach uses abstract acceleration to compute the set of reachable states, which 
-enables abstraction refinement inside the CEGIS loop. 
-\item[2.] The second approach relies on computing a completeness threshold $k$ for each loop such that it is sufficient to 
-unroll the corresponding loop $k$ times. For this approach the generalisation step is given as an incremental
-increase of precision and sampling rate.
+\item[1.] The first approach uses abstract acceleration to compute the set of reachable states, which enables it to perform abstraction refinement inside the CEGIS loop (see Sec~\ref{sec:CEGIS-abstraction-refinement}).
+\item[2.] The second approach relies on computing a 
+completeness threshold $k$ for each loop such that it is sufficient to 
+unroll the corresponding loop $k$ times. For this approach the 
+generalisation step is given as an incremental
+increase of precision and sampling rate (see Sec.~\ref{sec:CEGIS-precision-incrementation}).
 \end{itemize}
@@
 $(x_0, u_k)$ represents $x$. 
-
-We compute the coefficients for $K$ 
-in the domain $\mathbb{R}<I,F>$.
+We compute the coefficients for $K$ in the domain $\mathbb{R}<I,F>$.
 
@@
 
-\subsubsection{Computing the reachable states}
-
-In order to compute the set of reachable states we find 
+%\subsubsection{Controller synthesis}
+
+The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
+One important observation is that, for this approach,
+we compute the set of reachable states by finding 
 a completeness threshold $\overline{k}$.
@@
 ensuring that the boundaries are not be violated for any $k>\overline{k}$. 
-The closed-loop state-space system has to be unwound up to a given 
-depth $\overline{k}$ to ensure that $\phi_{safety}$ holds.
-
-\todo{discuss the completeness threshold computation}
-
-\subsubsection{Controller synthesis}
-
-The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}
-and consists of five stages, as described below:
+Then, it is sufficient to unwound the closed-loop state-space system up to  
+$\overline{k}$ in order to ensure that $\phi_{safety}$ holds.
+
+Next, we describe the five stages from Fig.~\ref{fig:CEGIS-precision-increment}:
 
 1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to 
-compute a candidate solution $K$.
+compute a candidate solution $K$. It does this by assuming 
+a $k$ and a sampling rate. The check that this assumptions were sound 
+will be performed later by the {\sc complete} and {\sc sampling} 
+validation stages.
 
@@
 (blocks 2-5 in Fig.~\ref{fig:CEGIS-precision-increment}), where the first one
-performs potentially unsound
-operations assuming a plant's precision $<I_p,F_p>$, 
+performs potentially unsound operations assuming a plant's precision $<I_p,F_p>$, 
 current $k$ and sampling rate, whereas the subsequent three stages are used to 
@@
 and check that $k{\leq}\overline{k}$. 
+\todo{discuss the computation of the completeness threshold}
 

### 2017-01-20 cav2017/cav2017.tex
todos+typo

@@
 
-\subsubsection{Computing the set of reachable states}
-\todo{explain the use of abstract acceleration}
+\todo{Move as much as possible from Sec~\ref{sec:cof_verification}
+to the appendix (e.g. discussion on abstract acceleration). 
+Merge the rest in Sec~\ref{sec:cof_synth}.}
 
@@
 a $k$ and a sampling rate. The check that this assumptions were sound 
-will be performed later by the {\sc complete} and {\sc sampling} 
+is performed later by the {\sc complete} and {\sc sampling} 
 validation stages.

### 2017-01-20 cav2017/cav2017.tex
Descriptions of benchmarks

--- 2017-01-20 cav2017/cav2017.tex
@@
 
-\todo{The safety specification is defined over the state space, not the output. Further, please distinguish the spec from the input constraints. }
+%\todo{The safety specification is defined over the state space, not the output. Further, please distinguish the spec from the input constraints. }
 
@@
 %
-\todo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
-
+%\todo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
 where $x_{i}^{-}$ and $x_{i}^{+}$ are the lower and upper bound 
@@
 \textit{Ball Magnetic Levitation} plant describes the magnetic field that keeps a metal ball hanged in air.
+
+These benchmarks were discretized with different sample times using the approach described in Appendix ~\ref{sec:appendix}.
+All the experiments were performed considering $x_{i}^{-}=-1$ and $x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.
 

### 2017-01-20 cav2017/cav2017.tex
more benchmarks description

--- 2017-01-20 cav2017/cav2017.tex
@@
 
-%\todo{The safety specification is defined over the state space, not the output. Further, please distinguish the spec from the input constraints. }
+\todo{The safety specification is defined over the state space, not the output. Further, please distinguish the spec from the input constraints. }
 
@@
 %
-%\todo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
+\todo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
+
 where $x_{i}^{-}$ and $x_{i}^{+}$ are the lower and upper bound 
@@
    \& 
-   \& \node[fill=gray!20,align=center, minimum width=3cm] (synth) {\sc 2. synthesize};
+   \& \node[fill=gray!20,align=center, minimum width=3cm] (synth) {\sc 2. synthesise};
        %\node[draw=none] (KL) at ([xshift=2.5cm,yshift=-.25cm]synth)  {\sc $\mat{K},\mat{L}$};
@@
    \&;\\
-   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc 1.Synthesize}};
+   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
    \&
@@
 	label={\sc Verify},] (verif) {};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2.9cm]verif.center) {{\sc 2.Safety}};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=-0.8cm]verif.center) {{\sc 3.Precision}};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=1.2cm]verif.center) {{\sc 4.Complete}};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc 5.Sampling}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2.9cm]verif.center) {{\sc Uncertainty}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=-0.8cm]verif.center) {{\sc Precision}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=1.2cm]verif.center) {{\sc Complete}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc Sampling}};
    } 
@@
 In order to compute the set of reachable states we find 
-a completeness threshold $\overline{k}$.
-Essentially, $\overline{k}$ represents the number of iterations 
+a completeness threshold $k_{bound}$.
+Essentially, $k_{bound}$ represents the number of iterations 
 to sufficiently unwind the closed-loop state-space system 
 so that the variation rate (derivative) of the states is negligible, 
-ensuring that the boundaries are not be violated for any $k>\overline{k}$. 
+ensuring that the boundaries are not be violated for any $k>k_{bound}$. 
 The closed-loop state-space system has to be unwound up to a given 
-depth $\overline{k}$ to ensure that $\phi_{safety}$ holds.
+depth $k_{bound}$ to ensure that $\phi_{safety}$ holds.
 
@@
 
-The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}
-and consists of five stages, as described below:
-
-1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to 
-compute a candidate solution $K$.
-
-2. The validation phase consists of four stages 
-(blocks 2-5 in Fig.~\ref{fig:CEGIS-precision-increment}), where the first one
-performs potentially unsound
-operations assuming a plant's precision $<I_p,F_p>$, 
-current $k$ and sampling rate, whereas the subsequent three stages are used to 
-restore soundness.
-
-3. This stage restores soundness with respect to the plant precision
-by using interval arithmetic \cite{moore1966interval} to validate the 
-operations performed by the previous stage.
-
-4. This stage checks that the current  $k$ 
-is large enough to ensure that the boundaries are not be violated for any $k'>k$.
-In order to verify this, we compute the 
-completeness threshold $\overline{k}$ for the current candidate $K$ 
-and check that $k{\leq}\overline{k}$.
-
-5. The last stage ensures that the current sampling rate is large enough by using an 
-external checker (\todo{add more details here once we have them}).
+\todo{Describe each step in Fig~\ref{fig:CEGIS-precision-increment}.}
 
@@
 Table~\ref{table:State-space benchmarks} summarizes the list of benchmarks extracted from the literature~\cite{Franklin15,maglev,converters,CTMS}.
-\textit{DC Motor Position} plant provides the rotary motion that coupled with wheels and cables provides translational motion.
-\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and control based on the pitch dimension only.
-\textit{Ball Magnetic Levitation} plant describes the magnetic field that keeps a metal ball hanged in air.
-
-These benchmarks were discretized with different sample times using the approach described in Appendix ~\ref{sec:appendix}.
-All the experiments were performed considering $x_{i}^{-}=-1$ and $x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.
+\textit{DC Motor Position} plant describes the rotary motion that coupled with wheels and cables provides translational motion.
+\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and control based on the pitch dimension.
+\textit{Ball Magnetic Levitation} plant describes the magnetic field to keep a metal ball hanged in air.
+\textit{Buck Converter} plant represents a power converter that steps down voltage from the supply to the load while stepping up current.
+\textit{Boost Converter} plant also represents a power converter, but here it steps up voltage from the supply to the load while stepping down current.
+\textit{Buck-boost Converter} plant is a particular type of converter that has an output voltage magnitude that is either greater than or less than the input voltage magnitude.
+\textit{Automotive Cruise System} plant describes a system's model that represents the speed of a motor vehicle.
 

### 2017-01-20 cav2017/cav2017.tex

--- 2017-01-20 cav2017/cav2017.tex
@@
 Table~\ref{table:State-space benchmarks} summarizes the list of benchmarks extracted from the literature~\cite{Franklin15,maglev,converters,CTMS}.
-\textit{DC Motor Position} plant provides the rotary motion that coupled with wheels and cables provides translational motion.
-\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and control based on the pitch dimension only.
-\textit{Ball Magnetic Levitation} plant describes the magnetic field that keeps a metal ball hanged in air.
-
-These benchmarks were discretized with different sample times using the approach described in Appendix ~\ref{sec:appendix}.
-All the experiments were performed considering $x_{i}^{-}=-1$ and $x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.
+\textit{DC Motor Position} plant describes the rotary motion that coupled with wheels and cables provides translational motion.
+\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and control based on the pitch dimension.
+\textit{Ball Magnetic Levitation} plant describes the magnetic field to keep a metal ball hanged in air.
+\textit{Buck Converter} plant represents a power converter that steps down voltage from the supply to the load while stepping up current.
+\textit{Boost Converter} plant also represents a power converter, but here it steps up voltage from the supply to the load while stepping down current.
+\textit{Buck-boost Converter} plant is a particular type of converter that has an output voltage magnitude that is either greater than or less than the input voltage magnitude.
+\textit{Automotive Cruise System} plant describes a system's model that represents the speed of a motor vehicle.
+
+These benchmarks were discretized with different sample times using the approach described in the Appendix~\ref{sec:appendix}.
+All experiments were performed considering $x_{i}^{-}=-1$ and $x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.
 

### 2017-01-20 cav2017/cav2017.tex
Sec 3.1

@@
 \end{align}
-where $A$ and $B$ are matrices that fully specify the continuous plant.  
-\todo{[specify initial conditions? specify input ranges already here? ]} 
-Eq.~\eqref{eq:ode} is soundly discretised (as shown in the Appendix \todo{[there we can present directly the full LTI case with outputs]}) into
+where $A$ and $B$ are matrices that fully specify the continuous plant with the initial states $x(0)$. 
+Eq.~\eqref{eq:ode} is soundly discretised (as shown in the Appendix) into
 %
@@
 \label{eq:plant}
-x_{k+1} = A_d x_k+ B_d u_k. 
+x_{k+1} = A_d x_k+ B_d u_k 
+y_{k} = C_d x_k+ D_d u_k,
 \end{align}
+with initial state $x_{0}=x(0)$.
+
 %

### 2017-01-20 cav2017/cav2017.tex
revision intro synth section

@@
 
-%-------------------------------
-\subsection{Digital implementation of feedback controller}
-\label{ssec:quantizationerror}
-%-------------------------------
-
-\todo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.}
-
-\todo{[The remainder of the section needs to be updated. ]}
-The output and measurable of the plant is being sampled by an ADC, and since the full state of the
-plant cannot be witnessed directly, the controller software includes an observer that 
-estimates the state of the plant (see appendix for details on how such an observer
-is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  
-\todo{[Unclear what the remainder is for: ]}
-We further presume that there are small tolerances in the system 
-described in the following form
-%
-\begin{align*}
-\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
-\end{align*}
-\commentib{What is S?}
-
-Where $\mathcal{G}_J$ is a collection of eigenvalue ranges that define the frequency response of the system.
-We presume that the internal model of the plant is an ARMA model, modified by a
-state transform that has no tolerances. Tolerances in the eigenvectors will manifest themselves
-as tolerances in the canonical forms outside of the row/column of interests and complicate the 
-evaluation. Whilst it is possible to address these with this methodology, we will focus on the case
-above for simplicity.
+%%%-------------------------------
+%%\subsection{Digital implementation of feedback controller}
+%%\label{ssec:quantizationerror}
+%%%-------------------------------
+%%
+%%\todo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.} 
+%%
+%%\todo{[The remainder of the section needs to be updated. ]}
+%%The output and measurable of the plant is being sampled by an ADC, and since the full state of the
+%%plant cannot be witnessed directly, the controller software includes an observer that 
+%%estimates the state of the plant (see appendix for details on how such an observer
+%%is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  
+%%\todo{[Unclear what the remainder is for: ]}
+%%We further presume that there are small tolerances in the system 
+%%described in the following form
+%%%
+%%\begin{align*}
+%%\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
+%%\end{align*}
+%%\commentib{What is S?}
+%%
+%%Where $\mathcal{G}_J$ is a collection of eigenvalue ranges that define the frequency response of the system.
+%%We presume that the internal model of the plant is an ARMA model, modified by a
+%%state transform that has no tolerances. Tolerances in the eigenvectors will manifest themselves
+%%as tolerances in the canonical forms outside of the row/column of interests and complicate the 
+%%evaluation. Whilst it is possible to address these with this methodology, we will focus on the case
+%%above for simplicity.
 
@@
 
-{\bf Assumption:} We consider the reference signal to be 0, whereas the initial states are non-deterministic.
-\todo{Explain all the assumptions.}
-
-%\todo{Integrate this paragraph better (Cristina):}
-Our CEGIS technique with generalisation %abstraction refinement
-relies on parametrising the target language, which
-induces a lattice of progressively more expressive languages.  We
-start by attempting to synthesise a program at the lowest point on
-this lattice and increase the parameters of the language until we
-reach a point at which the synthesis succeeds. As well as giving us an
-automatic search procedure, this parametrisation greatly increases the
-efficiency of our system since languages low down the lattice are very
-easy to decide safety for (i.e. the validation oracle finds an answer
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{General architecture of the program synthesizer}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\label{synthesizer-general}
+The input specification provided to the program synthesizer is of the form
+$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
+$\vec{P}$ ranges over functions, $\vec{x}$ ranges over ground terms and
+$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
+some finite domain $\mathcal{D}$.
+
+The design of our synthesizer consists of two phases, an inductive
+synthesis phase and a validation phase, which interact via a finite
+set of test vectors {\sc inputs} that is updated incrementally.  Given
+the aforementioned specification $\sigma$, the inductive synthesis
+procedure tries to find an existential witness $\vec{P}$ satisfying
+the specification $\sigma(\vec{x}, \vec{P})$ for all $\vec{x}$ in {\sc
+  inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
+%
+If the synthesis phase succeeds in finding a witness~$\vec{P}$, this
+witness is a candidate solution to the full synthesis formula.  We
+pass this candidate solution to the validation phase, which checks
+whether it is a full solution (i.e., $\vec{P}$ satisfies the
+specification $\sigma(\vec{x}, \vec{P})$ for all
+$\vec{x}\in\mathcal{D}$).  If this is the case, then the algorithm
+terminates.  Otherwise, additional information is provided to the
+inductive synthesis phase in the form of a new counterexample that is
+added to the {\sc inputs} set and the loop iterates again.
+
+It is worth noting that each iteration of the loop adds a new input to
+the finite set $\text{\sc inputs}$ that is used for synthesis.  Given
+that the full set of inputs $\mathcal{D}$ is finite, this means that
+the refinement loop can only iterate a finite number of times.
+
+\subsection{Solution generalisation} 
+Given the large soloution space to be searched during the inductive
+synthesis phase, we parametrise the target language, which induces a
+lattice of progressively more expressive languages.  This enables us 
+to start by attempting to synthesise a program at the lowest point on this lattice
+and increase the parameters of the language until we reach a point at
+which the synthesis succeeds. Whenever we manage to synthesise
+a candidate solution at some lower point on the lattice, 
+we apply generalisation to obtain a full solution.
+
+As well as giving us an automatic search
+procedure, this parametrisation greatly increases the efficiency of
+our system since languages low down the lattice are very easy to
+decide safety for (i.e. the validation oracle finds an answer
 fast). If a program can be synthesised in a low-complexity language,
@@
 \end{itemize}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{General architecture of the program synthesizer}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\label{synthesizer-general}
-%
-%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
-%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
-% 
-The input specification provided to the program synthesizer is of the form
-$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
-$\vec{P}$ ranges over functions, $\vec{x}$ ranges over ground terms and
-$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
-some finite domain $\mathcal{D}$.
-
-The design of our synthesizer 
-%is given in Figure~\ref{fig:CEGIS} and 
-consists of two phases, an inductive synthesis phase and a validation phase,
-%{\sc Synthesize} and {\sc Verify}, 
-which interact via a finite set of test vectors {\sc inputs} that is updated incrementally. 
-Given the aforementioned specification $\sigma$, the inductive synthesis
-procedure
-tries to find an existential witness $\vec{P}$ satisfying the specification
-$\sigma(\vec{x}, \vec{P})$ for all $\vec{x}$ in {\sc inputs} (as opposed to
-all $\vec{x} \in \mathcal{D}$).
-%
-If the synthesis phase succeeds in finding a witness~$\vec{P}$, this witness
-is a candidate solution to the full synthesis formula.  We pass this
-candidate solution to the validation phase, which checks whether it is a full
-solution (i.e., $\vec{P}$ satisfies the specification $\sigma(\vec{x},
-\vec{P})$ for all $\vec{x}\in\mathcal{D}$).
-%
-%determines whether
-%it does satisfy the specification on all inputs by checking
-%satisfiability of the following verification formula:
-%
-%$\exists \vec{x} . \lnot \sigma(\vec{x}, \vec{P})$
-%If this formula is unsatisfiable, 
-%% the candidate solution is in fact a 
-%% full solution.
-%
-If this is the case, then the algorithm terminates.  Otherwise, additional
-information is provided to the inductive synthesis phase in the form of a new
-counterexample that is added to the {\sc inputs} set and the loop iterates
-again.
-%% the witness $\vec{x}$ denote an input on which the
-%% candidate solution fails to meet the specification.  Thus, $\vec{x}$ is
-%% added to the {\sc inputs} set, and the loop iterates again.
-
-It is
-worth noting that each iteration of the loop adds a new input to the
-finite set $\text{\sc inputs}$ that is used for synthesis.  Given that
-the full set of inputs $\mathcal{D}$
-%\blue{[which by now should have a name, as suggested to be introduced above]} 
-is finite, this means that the refinement loop
-can only iterate a finite number of times.
-
-In Sec.~\ref{sec:CEGIS-abstraction-refinement} and 
-Sec.~\ref{sec:CEGIS-precision-incrementation}, we explain how we 
-specialise the general CEGIS approach in order to perform solution generalisation.
+
+% In Sec.~\ref{sec:CEGIS-abstraction-refinement} and 
+% Sec.~\ref{sec:CEGIS-precision-incrementation}, we explain how we 
+% specialise the general CEGIS approach in order to perform solution generalisation.
 
@@
 as defined in Sec.~\ref{ssec:safety}. Note that, 
-as mentioned at the beginning of the section, 
-we consider the reference signal to be 0.
+we consider the reference signal to be 0 (\todo{refer to wherever this is explained initially}).
 Then, when mapping back to the notation used for describing the general architecture 

### 2017-01-20 cav2017/cav2017.tex
some revision of sec 4.5

--- 2017-01-20 cav2017/cav2017.tex
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{CEGIS with precision and sampling rate incrementation}
+\subsection{CEGIS with incremental precision, completeness threshold and sampling rate}
 \label{sec:CEGIS-precision-incrementation}
@@
 }}
-\caption{The CEGIS loop with precision and sampling rate incrementation}
+\caption{The CEGIS loop with incremental precision, 
+completeness threshold and sampling rate.}
 \label{fig:CEGIS-precision-increment}
@@
 compute a candidate solution $K$. It does this by assuming 
-a $k$ and a sampling rate. The check that this assumptions were sound 
+a plan't precision $<I_p,F_p>$, a $k$ and a sampling rate. 
+The check that these assumptions are sound 
 is performed later by the {\sc complete} and {\sc sampling} 
@@
 (blocks 2-5 in Fig.~\ref{fig:CEGIS-precision-increment}), where the first one
-performs potentially unsound operations assuming a plant's precision $<I_p,F_p>$, 
-current $k$ and sampling rate, whereas the subsequent three stages are used to 
+performs potentially unsound operations considering the currently assumed 
+plant's precision $<I_p,F_p>$, 
+$k$ and sampling rate, whereas the subsequent three stages are used to 
 restore soundness.

### 2017-01-20 cav2017/cav2017.tex
changed name of 2nd cegis approach to multi-staged verification approach

@@
 }
-\caption{The CEGIS loop with abstraction refinement\label{fig:CEGARIS}.}
+\caption{CEGIS with abstraction refinement\label{fig:CEGARIS}.}
 \end{figure}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{CEGIS with incremental precision, completeness threshold and sampling rate}
+\subsection{CEGIS with multi-staged verification phase}
 \label{sec:CEGIS-precision-incrementation}
@@
 }}
-\caption{The CEGIS loop with incremental precision, 
-completeness threshold and sampling rate.}
+\caption{CEGIS with multi-staged verification phase.}
 \label{fig:CEGIS-precision-increment}

### 2017-01-20 cav2017/cav2017.tex
more benchmarks description

--- 2017-01-20 cav2017/cav2017.tex
@@
 
-\textcolor{red}{We will have to move this text to the beginning of the paper.}
-
 A set of state-space models for different classes of systems were extracted from the literature and employed for validating our automated synthesis methodology.
 All the systems are SISO models of the following form:
+%
 \begin{equation}
@@
 \textit{Boost Converter} plant also represents a power converter, but here it steps up voltage from the supply to the load while stepping down current.
-\textit{Buck-boost Converter} plant is a particular type of converter that has an output voltage magnitude that is either greater than or less than the input voltage magnitude.
+\textit{Buck-boost Converter} plant represents the model of a converter that has an output voltage magnitude, which is either greater than or less than the input voltage magnitude.
 \textit{Automotive Cruise System} plant describes a system's model that represents the speed of a motor vehicle.
-
-These benchmarks were discretized with different sample times using the approach described in the Appendix~\ref{sec:appendix}.
+\textcolor{red}{\textit{DC Motor Rate} plant describes...}.
+\textit{Helicopter Longitudinal Motion} plant provides the longitudinal motion model of a helicopter.
+\textit{Inverted Pendulum} plant describes the model of a pendulum with its center of mass above its pivot point.
+\textit{Magnetic Suspension} plant provides the model for which a given object is suspended via a magnetic field.
+
+All benchmarks were discretized with different sample times using the approach described in the Appendix~\ref{sec:appendix}.
 All experiments were performed considering $x_{i}^{-}=-1$ and $x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.

### 2017-01-20 cav2017/cav2017.tex
small
typo

--- 2017-01-20 cav2017/cav2017.tex
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{CEGIS with multi-staged verification phase}
+\subsection{CEGIS with multi-staged verification}
 \label{sec:CEGIS-precision-incrementation}
@@
 }}
-\caption{CEGIS with multi-staged verification phase.}
+\caption{CEGIS with multi-staged verification.}
 \label{fig:CEGIS-precision-increment}
@@
 so that the variation rate (derivative) of the states is negligible, 
-ensuring that the boundaries are not be violated for any $k>\overline{k}$. 
+ensuring that the boundaries are not violated for any $k>\overline{k}$. 
 Then, it is sufficient to unwound the closed-loop state-space system up to  
@@
 4. This stage checks that the current  $k$ 
-is large enough to ensure that the boundaries are not be violated for any $k'>k$.
+is large enough to ensure that the boundaries are not violated for any $k'>k$.
 In order to verify this, we compute the 

### 2017-01-20 cav2017/cav2017.tex
first round of cleanup
Removed observer and floating point from main text

@@
 \label{eq:plant}
-x_{k+1} = A_d x_k+ B_d u_k 
-y_{k} = C_d x_k+ D_d u_k,
+x_{k+1} = A_d x_k+ B_d u_k. 
 \end{align}
@@
 
+\todo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.}
+
+\todo{[The remainder of the section needs to be updated. ]}
+The output and measurable of the plant is being sampled by an ADC, and since the full state of the
+plant cannot be witnessed directly, the controller software includes an observer that 
+estimates the state of the plant (see appendix for details on how such an observer
+is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  
+\todo{[Unclear what the remainder is for: ]}
+
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 Let $\mathbb{R} \langle I,F \rangle$ be a fixed point domain with $I$ bits representing the integer part and $F$ bits
-representing the decimal part. We will extend this notation to $\mathbb{R} \langle I,F,E \rangle$ to add a number of
-leading or trailing bits when the domain requires prescaling (ie the maximum is smaller than $0.5$ or the minimum
-is greater than $2$).
-Let also $\mathbb{R}_* \langle M,E \rangle$ be a floating point domain with $M$ bits
-mantissa and $E$ bits exponent. This domain corresponds to 
-$$\mathbb{R}_* \langle M,E \rangle = \bigcup_i \mathbb{R} \langle 1,M-1,E_i \rangle : 2^{1-E} \leq E_i  \leq 2^{E-1}$$
-This means that the distance between any two numbers in the domain depends on the
-location of those numbers.
-Since we've shown that a floating point domain is a union of a number of fixed point domains, we will continue our
-reasoning on fixed point only. Our reasoning will apply to the floating point domain by extension.
+representing the decimal part. 
 The following approximation errors will arise:
@@
 %% introduced due to truncation of the result.
-Let us define $c\langle i,f,e \rangle \in \mathbb{R}\langle I,F,E\rangle$, where $i \in [-2^{I-1}\ 2^{I-1}],f \in [0 1),e \in [-2^{E-1}\ 2^{E-1}]$ are its assigned values.
-The smallest number that can be represented for any given exponent is $c_{min(e)}=c\langle 0,2^{-F},e\rangle$.
+Let us define $c\langle i,f \rangle \in \mathbb{R}\langle I,F\rangle$, where $i \in [-2^{I-1}\ 2^{I-1}],f \in [0 1)$ are its assigned values.
+The smallest number that can be represented for any given exponent is $c_{min}=2^{-F}$.
 The following errors appear in simple operations:
 \begin{enumerate}
-\item Addition/Substraction: $c\langle \cdot,e_1\rangle \pm c\langle \cdot,e_2\rangle=c\langle \cdot,max(e_1,e_2)\rangle + \delta_3 : |\delta_3| \leq (e_1==e_2) ? 0 : c_{min(max(e_2,e_1))}$ 
-\item Multiplication: $c\langle \cdot,e_1\rangle * c\langle \cdot,e_2\rangle=c\langle \cdot,e_1+e_2\rangle + \delta_3 : |\delta_3| \leq c_{min(e_2+e_1)}$
+\item Addition/Substraction: in the case of fixed point arithmetic of numbers with the same domain, there are no rounding errors, otherwise the maximum error is given by the domain of the result $c\langle \cdot, F_1\rangle \pm c\langle \cdot , F_2\rangle= c\langle \cdot , F_3\rangle + \delta_3 :|\delta_3| \leq 2^{-F_3} \wedge F_3 \leq F_1,F_2$
+\item Multiplication: $c\langle \cdot, F_1\rangle * c\langle \cdot,F_2\rangle=c\langle \cdot,F_3\rangle + \delta_3 : |\delta_3| \leq 2^{-F_3} \wedge F_3 \leq F_1,F_2$ 
 \end{enumerate}
@@
 functions to prevent them or raise alarms in their presence. In the case of verification, the latter is seen as a safety problem.
-\item {\bf Null/Zeno behaviour:}
-Whilst this work does not explore the effect of Zeno behaviours, it is worth noting that this effect may also be caused by rounding
-errors in floating point programs. The reason for this is that if an operation contains two numbers which belong to disjoint sub-domains
-(\emph{ie} neither number can be represented in the domain of its counterpart), the resulting operation may become a no-op/skip,
-subsequently destabilizing the program.
 \end{enumerate}
@@
 range of the quatizers is still $\mathbb{R}$. The next step we must reaize is that the controller and the observer
-exist in a digital program, hence their domain is $\mathbb{R}\langle I,F,E\rangle$. This has two separate effects
+exist in a digital program, hence their domain is $\mathbb{R}\langle I,F\rangle$. This has two separate effects
 on the model. If we recall equation \eqref{eq:to_of}, the matrices of the observer and the controller  are not necessarily those of the plant.
-In fact we have $\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$, $\mat{A}_o,\mat{B}_o,\mat{C}_o, \mat{K}_d, \mat{L}_d \in \mathbb{R}\langle I,F,E\rangle^*$
+In fact we have $\mat{A},\mat{B} \in \mathbb{R}^*$, $\mat{A}_o,\mat{B}_o,\mat{K}_d, \mat{L}_d \in \mathbb{R}\langle I,F\rangle^*$
 Where $*$ represents the appropriate dimension for each matrix.
@@
 These will introduce a new source of quantiztion noise which we may denote $\vec{\nu}_3 \in [-q_3\ \ q_3]$.
-The estimation of $\hat{\vec{x}}$ corresponds to the sum of three matrix-vector multiplications (we assume $\mat{C}_o$ in Objective form).
-Each of these has a coefficient-wise error bound $c_{min(max(e_{j1}+e_{j2}))}$.
-Hence the overall $\overline{\delta}_{\hat{x}}=3nc_{min(max(e_{j1}+e_{j2}))}$.
-The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=nc_{min(max(e_{k1}+e_{k2}))}+\sum_{k=1}^nc_k\overline{\delta}_{\hat{x}})=3n|\mat{K}|_1c_{min(max(e_{j1}+e_{j2}))}+nc_{min(max(e_{k1}+e_{k2}))}$
+The estimation of $\hat{\vec{x}}$ corresponds to the sum of three matrix-vector multiplications.
+Each of these has a coefficient-wise error bound $c_{min}$.
+Hence the overall $\overline{\delta}_{\hat{x}}=3nc_{min}$.
+The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=nc_{min}+\sum_{k=1}^nc_k\overline{\delta}_{\hat{x}}=(3|\mat{K}|_1+1)n2^{-F}$
 
@@
 %-------------------------------
-
-%\todo{The safety specification is defined over the state space, not the output. Further, please distinguish the spec from the input constraints. }
 
@@
 A controllable and observable system will have the following dynamics:
-\textcolor{red}{Dario: Do we really need to describe all these equations here?
-Should we simply cite them from a given reference?}
+
 %
@@
 \label{eq:observer_LTI_cf}
-\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_{k+1}
-=&\left [\begin{array}{cc}\mat{A}_{tp}&\mat{B}_{to}\\ \mat{0}&\mat{A}_{to}\end{array}\right]
-\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_k
-+\mat{B}_{tp} \vec{r}_k
-+\mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]\\
-\vec{y}_k=&\mat{C}_{t}\vec{x}_k + \mat{D}_{d}\vec{u}_k\nonumber
+\vec{x}_{k+1}=&\mat{A}_{t}\vec{x}_k+\mat{B}_{tp} \vec{r}_k+\mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]
 \end{align}
 \begin{align*}
-\mat{A}_{tp}=&\mat{T}\mat{A}_d\mat{T}^{-1}-\mat{T}\mat{B}_d\mat{K}_d\mat{T}^{-1}&
-\mat{A}_{to}=&\mat{T}\mat{A}_d\mat{T}^{-1}-\mat{L}_d\mat{C}_d\mat{T}&
-\mat{A}_t=&\left [\begin{array}{cc}\mat{A}_{tp}&\mat{B}_{to}\\ \mat{0}&\mat{A}_{to}\end{array}\right]\\
-\mat{B}_{to}=&\mat{T}\mat{B}_d\mat{K}_d\mat{T}^{-1}&
-\mat{B}_{tp}=&\left[\begin{array}{c}\mat{T}\mat{B}_d\mat{k}_r\\\mat{0}\end{array}\right]&
-\mat{B}_{tn}=&\left[\begin{array}{cc}\mat{T}\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{L}_d\end{array}\right]\\
+\mat{A}_{t}=&\mat{T}\mat{A}_d\mat{T}^{-1}&
+\mat{B}_{tp}=&\mat{T}\mat{B}_d&
+\mat{B}_{tn}=&\mat{T}\mat{B}_d&
 \mat{T}=&\mat{R}_{cf}\mat{R}^{-1}&
-\mat{L}=&\mat{W}_o^{-1}\mat{W}_{of} \left[ \begin{array}{c}p_1-a_1\\p_2-a_2\\p_n-a_n\end{array}\right]&
-\mat{C}_t=&\mat{C}_d\mat{T}
 \end{align*}
@@
 \begin{align*}
-\left(z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}\right) \left(z^n+\sum_{i=1}^p{(p_i-a_i)z^{n-i}}\right)
+\left(z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}\right)
 \end{align*}
@@
 \label{eq:acc_observer_LTI_cf}
-\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_k
-=&\mat{A}_t^k
-\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_0
+\vec{x}=&\mat{A}_t^k\vec{x}_0
 +\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tp} \vec{r}_i
-+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right] :
- \left [\begin{array}{cc}\mat{E}\mat{T}&\mat{0}\end{array}\right] \left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_0<\mat{f}
++\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right] : \mat{E}\mat{T} \vec{x}_0<\mat{f}
 \end{align}
@@
 =&\mathcal{A}_t X_0+\mathcal{B}_{tp} R + \mathcal{B}_{tn} N\\
-X_0 =&\left \{ \left[\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right] :
- \left [\begin{array}{cc}\mat{E}\mat{T}&\mat{0}\end{array}\right] \left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_0<\mat{f} \right\}\nonumber\\
+X_0 =&\left \{\vec{x} : \mat{E}\mat{T} \vec{x}_0<\mat{f} \right\}\nonumber\\
  R =&\{r : \mat{E}_r < \vec{f}_r \}\nonumber\\
@@
 \end{enumerate}
-\item Next we synthesise a candidate controller and observer. Let $\mathcal{J}\langle I,F,E \rangle (P,\mat{T})$ be a program describing Jury's method.
+\item Next we synthesise a candidate controller and observer. Let $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ be a program describing Jury's method.
 \begin{enumerate}
-\item Select a controller $\tilde{\mat{K}} \in \mathbb{R}\langle I,F,E\rangle^n$.
+\item Select a controller $\tilde{\mat{K}} \in \mathbb{R}\langle I,F\rangle^n$.
 This is achieved by solving a SAT formula $\mathcal{J}_K=\mathcal{J}\langle I,F,E \rangle (P_{a-k},\mat{T})$ that satisfies Jury's criteria for $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \mat{K}=\tilde{\mat{K}}\mat{T}$.
-\item Select the observer error characteristic polynomial $\tilde{\mat{L}} \in \mathbb{R}\langle I,F,E\rangle^n$. 
-This is achieved by solving a SAT formula $\mathcal{J}_L=\mathcal{J}\langle I,F,E \rangle (P_p,\mat{W}_o^{-1}\mat{W}_{of})$ 
-that satisfies Jury's criteria for 
-$P_p=z^n+\sum_{i=1}^n p_i z^{n-i} : p_i \in \vec{P}= (\mat{W}_o^{-1}\mat{W}_{of})^-1 \tilde{\mat{L}} 
-+ [\begin{array}{cccc}a_1&a_2&\hdots&a_n\end{array}]^T$.
 \item If there is no candidate solution we return UNSAT and exit the loop.

### 2017-01-20 cav2017/cav2017.tex
break lines

--- 2017-01-20 cav2017/cav2017.tex
@@
 
-A set of state-space models for different classes of systems were extracted from the literature and employed for validating our automated synthesis methodology.
+A set of state-space models for different classes of 
+systems were extracted from the literature and employed 
+for validating our automated synthesis methodology. 
 All the systems are SISO models of the following form:
@@
 
-Table~\ref{table:State-space benchmarks} summarizes the list of benchmarks extracted from the literature~\cite{Franklin15,maglev,converters,CTMS}.
-\textit{DC Motor Position} plant describes the rotary motion that coupled with wheels and cables provides translational motion.
-\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and control based on the pitch dimension.
-\textit{Ball Magnetic Levitation} plant describes the magnetic field to keep a metal ball hanged in air.
-\textit{Buck Converter} plant represents a power converter that steps down voltage from the supply to the load while stepping up current.
-\textit{Boost Converter} plant also represents a power converter, but here it steps up voltage from the supply to the load while stepping down current.
-\textit{Buck-boost Converter} plant represents the model of a converter that has an output voltage magnitude, which is either greater than or less than the input voltage magnitude.
-\textit{Automotive Cruise System} plant describes a system's model that represents the speed of a motor vehicle.
-\textcolor{red}{\textit{DC Motor Rate} plant describes...}.
-\textit{Helicopter Longitudinal Motion} plant provides the longitudinal motion model of a helicopter.
-\textit{Inverted Pendulum} plant describes the model of a pendulum with its center of mass above its pivot point.
-\textit{Magnetic Suspension} plant provides the model for which a given object is suspended via a magnetic field.
-
-All benchmarks were discretized with different sample times using the approach described in the Appendix~\ref{sec:appendix}.
-All experiments were performed considering $x_{i}^{-}=-1$ and $x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.
-
+Table~\ref{table:State-space benchmarks} summarizes all benchmarks extracted 
+from the control system literature~\cite{Franklin15,maglev,converters,CTMS}. 
+\textit{DC Motor Position and Rate} plants describes the angular position and 
+velocity of a DC Motor, respectively, that coupled with wheels and cables provides 
+translational motion. 
+\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and 
+control based on the pitch dimension. 
+\textit{Ball Magnetic Levitation} plant describes the magnetic field to keep a 
+metal ball hanged in air. 
+\textit{Buck Converter} plant represents a power converter model that steps down 
+voltage from the supply to the load while stepping up current. 
+\textit{Boost Converter} plant also represents a power converter model, but here 
+it steps up voltage from the supply to the load while stepping down current. 
+\textit{Buck-boost Converter} plant represents a converter model that has an output 
+voltage magnitude, which is either greater than or less than the input voltage magnitude. 
+\textit{Automotive Cruise System} plant describes the model that represents 
+the speed of a motor vehicle. 
+\textit{Helicopter Longitudinal Motion} plant provides the 
+longitudinal motion model of a helicopter. 
+\textit{Inverted Pendulum} plant describes the model of a pendulum 
+with its center of mass above its pivot point. 
+\textit{Magnetic Suspension} plant provides the model for which 
+a given object is suspended via a magnetic field. 
+\textit{Magnetized Pointer} plant describes a model rotated through interaction 
+with magnetic fields, which is typically employed in analog gauges and indicators.
+
+All benchmarks were discretized with different sample times using 
+the approach described in the Appendix~\ref{sec:appendix}. 
+All experiments were performed considering $x_{i}^{-}=-1$ and 
+$x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.
+%
 \begin{table}[htb]

### 2017-01-20 cav2017/cav2017.tex
some changes to the synthesis sec

--- 2017-01-20 cav2017/cav2017.tex
@@
 lattice of progressively more expressive languages.  This enables us
-to start by attempting to synthesise a program at the lowest point on this lattice
-and increase the parameters of the language until we reach a point at
-which the synthesis succeeds. Whenever we manage to synthesise
-a candidate solution at some lower point on the lattice, 
-we apply generalisation to obtain a full solution.
-
-As well as giving us an automatic search
-procedure, this parametrisation greatly increases the efficiency of
-our system since languages low down the lattice are very easy to
-decide safety for (i.e. the validation oracle finds an answer
-fast). If a program can be synthesised in a low-complexity language,
-the whole procedure finishes much faster than if synthesis had been
-attempted in a high-complexity language.
+to start by attempting to synthesise a program at the lowest point on
+this lattice and increase the parameters of the language until we
+reach a point at which the synthesis succeeds. Whenever we manage to
+synthesise a candidate solution at some lower point on the lattice, we
+must apply some form of solution generalisation to obtain a full
+solution (i.e. a solution in the original search space).
+
+As well as giving us an automatic search procedure, this
+parametrisation greatly increases the efficiency of our system since
+languages low down the lattice are very easy to decide safety for
+(i.e. the validation oracle finds an answer fast). If a program can be
+synthesised in a low-complexity language, the whole procedure finishes
+much faster than if synthesis had been attempted in a high-complexity
+language.
 
@@
 
-Next, we describe the five stages from Fig.~\ref{fig:CEGIS-precision-increment}:
+Next, we describe the different phases in Fig.~\ref{fig:CEGIS-precision-increment}
+(blocks 1 to 5):
 
 1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
-compute a candidate solution $K$. It does this by assuming 
-a plan't precision $<I_p,F_p>$, a $k$ and a sampling rate. 
-The check that these assumptions are sound 
-is performed later by the {\sc complete} and {\sc sampling} 
-validation stages.
-
-2. The validation phase consists of four stages 
-(blocks 2-5 in Fig.~\ref{fig:CEGIS-precision-increment}), where the first one
-performs potentially unsound operations considering the currently assumed 
-plant's precision $<I_p,F_p>$, 
-$k$ and sampling rate, whereas the subsequent three stages are used to 
-restore soundness.
+compute a candidate solution $K$. It does this by assuming a plan't
+precision $<I_p,F_p>$, a $k$ and a sampling rate.  The checks that
+these assumptions are sound are performed by the subsequent {\sc
+  verify} stages.
+
+2. The validation phase consists of four stages (blocks 2-5 in
+Fig.~\ref{fig:CEGIS-precision-increment}), where the first one
+performs potentially unsound operations considering the currently
+assumed plant's precision $<I_p,F_p>$, $k$ and sampling rate, whereas
+the subsequent three stages are used to restore soundness.
 
@@
 
-A set of state-space models for different classes of 
-systems were extracted from the literature and employed 
-for validating our automated synthesis methodology. 
+\textcolor{red}{We will have to move this text to the beginning of the paper.}
+
+A set of state-space models for different classes of systems were extracted from the literature and employed for validating our automated synthesis methodology.
 All the systems are SISO models of the following form:
-%
 \begin{equation}
@@
 
-Table~\ref{table:State-space benchmarks} summarizes all benchmarks extracted 
-from the control system literature~\cite{Franklin15,maglev,converters,CTMS}. 
-\textit{DC Motor Position and Rate} plants describes the angular position and 
-velocity of a DC Motor, respectively, that coupled with wheels and cables provides 
-translational motion. 
-\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and 
-control based on the pitch dimension. 
-\textit{Ball Magnetic Levitation} plant describes the magnetic field to keep a 
-metal ball hanged in air. 
-\textit{Buck Converter} plant represents a power converter model that steps down 
-voltage from the supply to the load while stepping up current. 
-\textit{Boost Converter} plant also represents a power converter model, but here 
-it steps up voltage from the supply to the load while stepping down current. 
-\textit{Buck-boost Converter} plant represents a converter model that has an output 
-voltage magnitude, which is either greater than or less than the input voltage magnitude. 
-\textit{Automotive Cruise System} plant describes the model that represents 
-the speed of a motor vehicle. 
-\textit{Helicopter Longitudinal Motion} plant provides the 
-longitudinal motion model of a helicopter. 
-\textit{Inverted Pendulum} plant describes the model of a pendulum 
-with its center of mass above its pivot point. 
-\textit{Magnetic Suspension} plant provides the model for which 
-a given object is suspended via a magnetic field. 
-\textit{Magnetized Pointer} plant describes a model rotated through interaction 
-with magnetic fields, which is typically employed in analog gauges and indicators.
-
-All benchmarks were discretized with different sample times using 
-the approach described in the Appendix~\ref{sec:appendix}. 
-All experiments were performed considering $x_{i}^{-}=-1$ and 
-$x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.
-%
+Table~\ref{table:State-space benchmarks} summarizes the list of benchmarks extracted from the literature~\cite{Franklin15,maglev,converters,CTMS}.
+\textit{DC Motor Position} plant describes the rotary motion that coupled with wheels and cables provides translational motion.
+\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and control based on the pitch dimension.
+\textit{Ball Magnetic Levitation} plant describes the magnetic field to keep a metal ball hanged in air.
+\textit{Buck Converter} plant represents a power converter that steps down voltage from the supply to the load while stepping up current.
+\textit{Boost Converter} plant also represents a power converter, but here it steps up voltage from the supply to the load while stepping down current.
+\textit{Buck-boost Converter} plant is a particular type of converter that has an output voltage magnitude that is either greater than or less than the input voltage magnitude.
+\textit{Automotive Cruise System} plant describes a system's model that represents the speed of a motor vehicle.
+
+These benchmarks were discretized with different sample times using the approach described in the Appendix~\ref{sec:appendix}.
+All experiments were performed considering $x_{i}^{-}=-1$ and $x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.
+
 \begin{table}[htb]

### 2017-01-20 cav2017/cav2017.tex
some changes to the synthesis sec

@@
 Essentially, $\overline{k}$ represents the number of iterations 
-to sufficiently unwind the closed-loop state-space system 
-so that the variation rate (derivative) of the states is negligible, 
-ensuring that the boundaries are not violated for any $k>\overline{k}$. 
-Then, it is sufficient to unwound the closed-loop state-space system up to  
-$\overline{k}$ in order to ensure that $\phi_{safety}$ holds.
+required to sufficiently unwind the closed-loop state-space system 
+such that the boundaries are not violated for any $k>\overline{k}$
+(i.e. it's sufficient to unwound the closed-loop state-space system up to  
+$\overline{k}$ in order to ensure that $\phi_{safety}$ holds).
 

### 2017-01-20 cav2017/cav2017.tex
added the description of more benchmarks

--- 2017-01-20 cav2017/cav2017.tex
@@
 lattice of progressively more expressive languages.  This enables us 
-to start by attempting to synthesise a program at the lowest point on
-this lattice and increase the parameters of the language until we
-reach a point at which the synthesis succeeds. Whenever we manage to
-synthesise a candidate solution at some lower point on the lattice, we
-must apply some form of solution generalisation to obtain a full
-solution (i.e. a solution in the original search space).
-
-As well as giving us an automatic search procedure, this
-parametrisation greatly increases the efficiency of our system since
-languages low down the lattice are very easy to decide safety for
-(i.e. the validation oracle finds an answer fast). If a program can be
-synthesised in a low-complexity language, the whole procedure finishes
-much faster than if synthesis had been attempted in a high-complexity
-language.
+to start by attempting to synthesise a program at the lowest point on this lattice
+and increase the parameters of the language until we reach a point at
+which the synthesis succeeds. Whenever we manage to synthesise
+a candidate solution at some lower point on the lattice, 
+we apply generalisation to obtain a full solution.
+
+As well as giving us an automatic search
+procedure, this parametrisation greatly increases the efficiency of
+our system since languages low down the lattice are very easy to
+decide safety for (i.e. the validation oracle finds an answer
+fast). If a program can be synthesised in a low-complexity language,
+the whole procedure finishes much faster than if synthesis had been
+attempted in a high-complexity language.
 
@@
 
-Next, we describe the different phases in Fig.~\ref{fig:CEGIS-precision-increment}
-(blocks 1 to 5):
+Next, we describe the five stages from Fig.~\ref{fig:CEGIS-precision-increment}:
 
 1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to 
-compute a candidate solution $K$. It does this by assuming a plan't
-precision $<I_p,F_p>$, a $k$ and a sampling rate.  The checks that
-these assumptions are sound are performed by the subsequent {\sc
-  verify} stages.
-
-2. The validation phase consists of four stages (blocks 2-5 in
-Fig.~\ref{fig:CEGIS-precision-increment}), where the first one
-performs potentially unsound operations considering the currently
-assumed plant's precision $<I_p,F_p>$, $k$ and sampling rate, whereas
-the subsequent three stages are used to restore soundness.
+compute a candidate solution $K$. It does this by assuming 
+a plan't precision $<I_p,F_p>$, a $k$ and a sampling rate. 
+The check that these assumptions are sound 
+is performed later by the {\sc complete} and {\sc sampling} 
+validation stages.
+
+2. The validation phase consists of four stages 
+(blocks 2-5 in Fig.~\ref{fig:CEGIS-precision-increment}), where the first one
+performs potentially unsound operations considering the currently assumed 
+plant's precision $<I_p,F_p>$, 
+$k$ and sampling rate, whereas the subsequent three stages are used to 
+restore soundness.
 
@@
 control based on the pitch dimension. 
-\textit{Ball Magnetic Levitation} plant describes the magnetic field to keep a 
-metal ball hanged in air. 
+\textit{Ball Magnetic Levitation} plant describes a physical model to keep a 
+metal ball hanged in air via a magnetic field . 
 \textit{Buck Converter} plant represents a power converter model that steps down 
@@
 voltage magnitude, which is either greater than or less than the input voltage magnitude.
-\textit{Automotive Cruise System} plant describes the model that represents 
+
+\textit{Automotive Cruise System} plant describes a physical model that represents 
 the speed of a motor vehicle. 
@@
 longitudinal motion model of a helicopter. 
-\textit{Inverted Pendulum} plant describes the model of a pendulum 
+\textit{Inverted Pendulum} plant describes a pendulum model
 with its center of mass above its pivot point. 
-\textit{Magnetic Suspension} plant provides the model for which 
+\textit{Magnetic Suspension} plant provides the physical model for which 
 a given object is suspended via a magnetic field. 
-\textit{Magnetized Pointer} plant describes a model rotated through interaction 
-with magnetic fields, which is typically employed in analog gauges and indicators.
+\textit{Magnetized Pointer} plant describes a physical model that is rotated through interaction 
+with magnetic fields (typically employed in analog gauges and indicators).
+\textit{1/4 Car Suspension} plant presents a physical model that connects a car to its wheels 
+and allows relative motion between both parts.
+\textit{Computer Tape Driver} plant describes a physical model to read and write data 
+on a storage device in the computer.
+\textit{USCG Cutter Tampa Heading Angle} plant presents a physical model 
+for the yaw angle dynamics of a US warship USCG Cutter Tampa.
 
@@
 \footnotesize
-\caption{Test suite for space-state synthesis}
+\caption{Benchmarks for State-Space Physical Plants.}
 \label{table:State-space benchmarks}

### 2017-01-20 cav2017/cav2017.tex

@@
 Essentially, $\overline{k}$ represents the number of iterations 
-to sufficiently unwind the closed-loop state-space system 
-so that the variation rate (derivative) of the states is negligible, 
-ensuring that the boundaries are not violated for any $k>\overline{k}$. 
-Then, it is sufficient to unwound the closed-loop state-space system up to  
-$\overline{k}$ in order to ensure that $\phi_{safety}$ holds.
-
-Next, we describe the five stages from Fig.~\ref{fig:CEGIS-precision-increment}:
+required to sufficiently unwind the closed-loop state-space system 
+such that the boundaries are not violated for any $k>\overline{k}$
+(i.e. it's sufficient to unwound the closed-loop state-space system up to  
+$\overline{k}$ in order to ensure that $\phi_{safety}$ holds).
+
+Next, we describe the different phases in Fig.~\ref{fig:CEGIS-precision-increment}
+(blocks 1 to 5):
 
 1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
-compute a candidate solution $K$. It does this by assuming 
-a plan't precision $<I_p,F_p>$, a $k$ and a sampling rate. 
-The check that these assumptions are sound 
-is performed later by the {\sc complete} and {\sc sampling} 
-validation stages.
-
-2. The validation phase consists of four stages 
-(blocks 2-5 in Fig.~\ref{fig:CEGIS-precision-increment}), where the first one
-performs potentially unsound operations considering the currently assumed 
-plant's precision $<I_p,F_p>$, 
-$k$ and sampling rate, whereas the subsequent three stages are used to 
-restore soundness.
+compute a candidate solution $K$. It does this by assuming a plan't
+precision $<I_p,F_p>$, a $k$ and a sampling rate.  The checks that
+these assumptions are sound are performed by the subsequent {\sc
+  verify} stages.
+
+2. The validation phase consists of four stages (blocks 2-5 in
+Fig.~\ref{fig:CEGIS-precision-increment}), where the first one
+performs potentially unsound operations considering the currently
+assumed plant's precision $<I_p,F_p>$, $k$ and sampling rate, whereas
+the subsequent three stages are used to restore soundness.
 

### 2017-01-20 cav2017/cav2017.tex
revision sec 4.5

@@
 1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
-compute a candidate solution $K$. It does this by assuming a plan't
-precision $<I_p,F_p>$, a $k$ and a sampling rate.  The checks that
+compute a candidate solution $K$. It does this by assuming some 
+precision $<I_p,F_p>$ for the plant, a $k$ and a sampling rate.  The checks that
 these assumptions are sound are performed by the subsequent {\sc
@@
 
-2. The validation phase consists of four stages (blocks 2-5 in
-Fig.~\ref{fig:CEGIS-precision-increment}), where the first one
-performs potentially unsound operations considering the currently
-assumed plant's precision $<I_p,F_p>$, $k$ and sampling rate, whereas
-the subsequent three stages are used to restore soundness.
-
-3. This stage restores soundness with respect to the plant precision
+2. The first {\sc verify} stage, {\sc safety}, 
+performs potentially unsound operations by considering the currently
+assumed $<I_p,F_p>$, $k$ and sampling rate. % The soundness is to be 
+% restored by the subsequent three validation stages.
+
+3. The second {\sc verify} stage, {\sc precision}, 
+ restores soundness with respect to the plant's precision
 by using interval arithmetic \cite{moore1966interval} to validate the 
@@
 
-4. This stage checks that the current  $k$ 
-is large enough to ensure that the boundaries are not violated for any $k'>k$.
-In order to verify this, we compute the 
+4. The third {\sc verify} stage, {\sc complete}, checks that the
+current $k$ is large enough to ensure that the boundaries are not
+violated for any $k'>k$.  For this purpose, we compute the
 completeness threshold $\overline{k}$ for the current candidate $K$
-and check that $k{\leq}\overline{k}$. 
-\todo{discuss the computation of the completeness threshold}
-
-5. The last stage ensures that the current sampling rate is large enough by using an 
+and check that $k{\leq}\overline{k}$.  \todo{discuss the computation
+  of the completeness threshold}
+
+5. The last {\sc verify} stage, {\sc sampling}, 
+ensures that the current sampling rate is large enough by using an 
 external checker (\todo{add more details here once we have them}).

### 2017-01-20 cav2017/cav2017.tex
PC configuration

--- 2017-01-20 cav2017/cav2017.tex
@@
 $x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.
+
+We have also conducted the experimental evaluation on a 12-core 2.40 GHz
+Intel Xeon E5-2440 with 96 GB of RAM and Linux OS. All times given are wall 
+clock time in seconds as measured by the UNIX date command.
+
+\textcolor{red}{we have to describe the timeout...}
+
 %

### 2017-01-20 cav2017/cav2017.tex
editing safety spec
Diff between controller error and state space error

--- 2017-01-20 cav2017/cav2017.tex
@@
 
+There are two sources of error due to numeric representation; the numeric error introduced by 
+the fixed point numbers used to model our plant, i.e, the plant dynamics $A_d$, $B_d$ and the states; 
+and the numeric error introduced by the digital controller, which uses an analogue-to-digital converter to read
+the states as a fixed-point number. In this section we formally outline the errors introduced by
+fixed point representation of numbers; in further sections we will differentiate between these
+two errors by referring to them as the \emph{plant error} and the \emph{digital controller error}.
+
 Let $\mathbb{R} \langle I,F \rangle$ be a fixed point domain with $I$ bits representing the integer part and $F$ bits
@@
 
-The states must be computed considering 
-the FWL effects in all operations related to the control action~\eqref{eq:controlaction} 
-and disregarding it in the state equation~\eqref{eq:plant}. 
-Thus, the states are computed using the following equations:
-%
-\begin{equation}
-\label{eq:ssunroll}
-\left\lbrace
-\begin{array}{l}
-u_{k}=\mathcal{F}_{\langle I,F \rangle}(r_{k}-\mathcal{F}_{\langle I,F \rangle}(\mathcal{F}_{\langle I,F \rangle}(K)\cdot\mathcal{F}_{\langle I,F \rangle}(x_{k})))\\
-x_{k+1}=Ax_{k}+Bu_{k}
-\end{array}\right.
-\end{equation}
-
-The input sequence $u_{k}$ is non-deterministic with known bounds $u^{+}$ and $u^{-}$, such that ${u^{-} \leq u_{k} \leq u^{+}},\forall k\geq 0$.
+The states values must be computed considering the digital controller error, i.e., the error introduced by the ADC and
+digital controller, and the digital reference signal. In this paper, we consider systems with
+a reference signal equal to zero. 
+%the FWL effects in all operations related to the control action~\eqref{eq:controlaction} 
+%and disregarding it in the state equation~\eqref{eq:plant}.
+Thus, the states are computed using the following equations. We use $\mathcal{F}_{\langle I_c,F_c \rangle}$
+to denote numbers represented with the precision of the digital controller. All other numbers
+are represented with the precision of our plant model:
+%
+\begin{align*}
+u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})) \\
+x_{k+1}&=Ax_{k}+Bu_{k}
+\end{align*}
+%\left\lbrace
+%\begin{array}{l}
+%u_{k}=\mathcal{F}_{\langle I,F \rangle}(r_{k}-\mathcal{F}_{\langle I,F \rangle}(\mathcal{F}_{\langle I,F \rangle}(K)\cdot\mathcal{F}_{\langle I,F \rangle}(x_{k})))\\
+%x_{k+1}=Ax_{k}+Bu_{k}
+%\end{array}\right.
+%\end{equation}
+
+The input sequence $u_{k}$ is non-deterministic with known bounds $u^{+}$ and $u^{-}$, 
+such that ${u^{-} \leq u_{k} \leq u^{+}},\forall k\geq 0$.
 

### 2017-01-20 cav2017/cav2017.tex
non det input
moved the stability spec description to the appendix

@@
 \subsection{Stability of closed-loop systems}
-\label{ssec:stability}
+\label{sec:stability}
 %-------------------------------
@@
 the unity circle, {\it i.e.}, their absolute value are less than 
-one~\cite{astrom1997computer}. For a closed-loop system as~\eqref{eq:closedloopss}, 
-the characteristic polynomial $P(z)$ should be computed as follows:
-\begin{equation}
-P(z)= \det( z I_{n} - A_d + B_d K ),
-\end{equation}
-where $I_{n}$ is the n-th order identity matrix.
-
-Jury's criterion provides necessary and sufficient conditions for the eigenvalues 
-to be within the unit circle and, consequently, the system is stable.  Given a 
-polynomial $P(z)$ of the form
-$$
-P(z) = a_{0}z^{N} + a_{1}z^{N-1} + ... a_{N-1}z + a_{N} = 0, a_{0}\neq 0,
-$$
-Jury's criterion explores solely the coefficients ($a_{0},a_{1},...,a_{N-1}$) 
-of $P(z)$ for checking the validity of the stability property $\phi_{stability}$.
-
-In particular, Jury stability test is already explained in the control system 
-literature ({\it e.g.}~\cite{fadali}). This study, however, limits itself to 
-explain the encoding of Jury's criterion for the formal synthesis purpose. 
-For the stability  test procedure, the following Jury matrix 
-$M=[m_{ij}]_{(2N-2)\times N}$ is built  from $P(z)$ coefficients:
-$$
-M=\left[
-\begin{matrix}
-  V^{(0)} \\
-  V^{(1)} \\
-  \vdots \\
-  V^{(N-2)}
- \end{matrix}
-\right]\mbox{,}
-$$
-\noindent where $V^{(k)}=[v^{(k)}_{ij}]_{2\times N}$ such that
-$$
-v^{(0)}_{ij}=\begin{cases} 
-a_{j-1}, & \mbox{if } i=1 \\   v^{(0)}_{(1)(N-j+1)}, & \mbox{if } i=2 
-\end{cases}\mbox{, and} 
-$$
-$$
-v^{(k)}_{ij}=\begin{cases} 
-0, & \mbox{if } j>n-k\\
-v^{(k-1)}_{1j}-v^{(k-1)}_{2j}\cdot\frac{v^{(k-1)}_{11}}{v^{(k-1)}_{21}}, & \mbox{if } j\leq n-k  \mbox{ and } i=1 \\
-v^{(k)}_{(1)(N-j+1)}, & \mbox{if } j\leq n-k \mbox{ and } i=2 \\
-\end{cases} \mbox{,}
-$$
-\noindent where $k\in\mathbb{Z}$, such that $0<k<N-2$. $P(z)$ is the 
-characteristic polynomial of a stable system if and only if the following 
-four propositions hold:
-\begin{itemize}
-\item $R_{1}$: $S(1)>0$;
-\item $R_{2}$: $(-1)^{N}P(-1)>0$;
-\item $R_{3}$: $\vert{a_{0}}\vert <a_{N}$;
-\item $R_{4}$: $m_{11}>0\iff m_{31}\wedge m_{51}\wedge \dots \wedge m_{(2N-3)(1)}$.
-\end{itemize}
-
-The stability property $\phi_{stability}$ is then encoded as follows:
-$$
-\phi_{stability}\iff \ (R_{1} \wedge R_{2} \wedge R_{3} \wedge R_{4}).
-$$
+one~\cite{astrom1997computer}. In this paper, we express 
+the stability specification $\phi_{stability}$ in terms of  
+Jury's criterion \cite{fadali}. A detailed description of this 
+specification can be found in the Appendix~\ref{sec:appendix-stability}.
 
@@
 
-The input sequence $u_{k}$ is non-deterministic with known bounds $u^{+}$ and $u^{-}$, 
+The input $u_{k}$%is non-deterministic with 
+has known bounds $u^{+}$ and $u^{-}$, 
 such that ${u^{-} \leq u_{k} \leq u^{+}},\forall k\geq 0$.
@@
 \appendix
+%-------------------------------
+\section{Stability of closed-loop systems}
+\label{sec:appendix-stability}
+%-------------------------------
+
+%\todo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantisation noises yet).]}
+
+A discrete-time system is asymptotically stable if and only if all the roots 
+of the characteristic polynomial ({\it i.e.}, the eigenvalues) are inside of 
+the unity circle, {\it i.e.}, their absolute value are less than 
+one~\cite{astrom1997computer}. In this paper, we express 
+the stability specification $\phi_{stability}$ in terms of  
+Jury's criterion \cite{fadali}. A detailed description of this 
+specification can be found in the Appendix~\ref{sec:appendix-stability}.
+
+For a closed-loop system as~\eqref{eq:closedloopss}, 
+the characteristic polynomial $P(z)$ should be computed as follows:
+\begin{equation}
+P(z)= \det( z I_{n} - A_d + B_d K ),
+\end{equation}
+where $I_{n}$ is the n-th order identity matrix.
+
+Jury's criterion provides necessary and sufficient conditions for the eigenvalues 
+to be within the unit circle and, consequently, the system is stable.  Given a 
+polynomial $P(z)$ of the form
+$$
+P(z) = a_{0}z^{N} + a_{1}z^{N-1} + ... a_{N-1}z + a_{N} = 0, a_{0}\neq 0,
+$$
+Jury's criterion explores solely the coefficients ($a_{0},a_{1},...,a_{N-1}$) 
+of $P(z)$ for checking the validity of the stability property $\phi_{stability}$.
+
+In particular, Jury stability test is already explained in the control system 
+literature ({\it e.g.}~\cite{fadali}). This study, however, limits itself to 
+explain the encoding of Jury's criterion for the formal synthesis purpose. 
+For the stability  test procedure, the following Jury matrix 
+$M=[m_{ij}]_{(2N-2)\times N}$ is built  from $P(z)$ coefficients:
+$$
+M=\left[
+\begin{matrix}
+  V^{(0)} \\
+  V^{(1)} \\
+  \vdots \\
+  V^{(N-2)}
+ \end{matrix}
+\right]\mbox{,}
+$$
+\noindent where $V^{(k)}=[v^{(k)}_{ij}]_{2\times N}$ such that
+$$
+v^{(0)}_{ij}=\begin{cases} 
+a_{j-1}, & \mbox{if } i=1 \\   v^{(0)}_{(1)(N-j+1)}, & \mbox{if } i=2 
+\end{cases}\mbox{, and} 
+$$
+$$
+v^{(k)}_{ij}=\begin{cases} 
+0, & \mbox{if } j>n-k\\
+v^{(k-1)}_{1j}-v^{(k-1)}_{2j}\cdot\frac{v^{(k-1)}_{11}}{v^{(k-1)}_{21}}, & \mbox{if } j\leq n-k  \mbox{ and } i=1 \\
+v^{(k)}_{(1)(N-j+1)}, & \mbox{if } j\leq n-k \mbox{ and } i=2 \\
+\end{cases} \mbox{,}
+$$
+\noindent where $k\in\mathbb{Z}$, such that $0<k<N-2$. $P(z)$ is the 
+characteristic polynomial of a stable system if and only if the following 
+four propositions hold:
+\begin{itemize}
+\item $R_{1}$: $S(1)>0$;
+\item $R_{2}$: $(-1)^{N}P(-1)>0$;
+\item $R_{3}$: $\vert{a_{0}}\vert <a_{N}$;
+\item $R_{4}$: $m_{11}>0\iff m_{31}\wedge m_{51}\wedge \dots \wedge m_{(2N-3)(1)}$.
+\end{itemize}
+
+The stability property $\phi_{stability}$ is then encoded as follows:
+$$
+\phi_{stability}\iff \ (R_{1} \wedge R_{2} \wedge R_{3} \wedge R_{4}).
+$$
+
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-01-20 cav2017/cav2017.tex
commented out paragraph about internal observer

@@
 
-\todo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.}
-
-\todo{[The remainder of the section needs to be updated. ]}
-The output and measurable of the plant is being sampled by an ADC, and since the full state of the
-plant cannot be witnessed directly, the controller software includes an observer that 
-estimates the state of the plant (see appendix for details on how such an observer
-is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  
-\todo{[Unclear what the remainder is for: ]}
+% \todo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.}
+
+% \todo{[The remainder of the section needs to be updated. ]}
+% The output and measurable of the plant is being sampled by an ADC, and since the full state of the
+% plant cannot be witnessed directly, the controller software includes an observer that 
+% estimates the state of the plant (see appendix for details on how such an observer
+% is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  
+% \todo{[Unclear what the remainder is for: ]}
 

### 2017-01-20 cav2017/cav2017.tex
mild edit to problem statement
typo

@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-The synthesis problem we are trying to solve is the following:
-find a digital controller $K$ (see Eq.~\ref{eq:controlaction})
-that makes the closed-loop system safe for 
-initial state $x_0$, reference signal $r_k$ and input $u_k$
-as defined in Sec.~\ref{ssec:safety}. Note that, 
-we consider the reference signal to be 0 (\todo{refer to wherever this is explained initially}).
-Then, when mapping back to the notation used for describing the general architecture 
-of the program synthesizer, the controller $K$ denotes $P$ and 
-$(x_0, u_k)$ represents $x$. 
-We compute the coefficients for $K$ in the domain $\mathbb{R}<I,F>$.
+The synthesis problem we are trying to solve is the following: find a
+digital controller $K$ (see Eq.~\ref{eq:controlaction}) that makes the
+closed-loop system safe for initial state $x_0$, reference signal
+$r_k$ and input $u_k$ as defined in Sec.~\ref{ssec:safety}.  We
+consider non-deterministic initial states within a specified range and
+the reference signal to be 0 (\todo{refer to wherever this is
+  explained initially}).  Then, when mapping back to the notation used
+for describing the general architecture of the program synthesizer,
+the controller $K$ denotes $P$ and $(x_0, u_k)$ represents $x$.  We
+compute the coefficients for $K$ in the domain $\mathbb{R}<I,F>$.
 
@@
 
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Observable canonical form} \label{sec:observable}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-The Controllable Canonical Form is ideal when we have access to the state space. However, in most cyberphisical
-systems, only the outputs of the plant can be observed, hence we require an Observable Canonical Form.
-For SISO systems, this is:
-\begin{align}
-\label{of_SISO}
-\mat{A}_{of}=&\left[
-\begin{array}{ccccc}
-0&0&0&\cdots&-a_n\\
-1&0&0&\cdots&-a_{n-1}\\
-0&1&0&\cdots&-a_{n-2}\\
-\vdots&\ddots&\ddots&\ddots&\vdots\\
-0&0&\cdots&1&-a_1
-\end{array}\right],
-\mat{B}_{of}=\left[
-\begin{array}{c}
-\eta_n\\ \eta_{n-1}\\ \vdots\\ \eta_1
-\end{array}\right]\\
-\mat{C}_{of}=&[\begin{array}{ccccc}0&0&\cdots&0&1\end{array}] \nonumber
-\end{align}
-
-What is important to notice her is that $\mat{A}_{of}=\mat{A}_{cf}^T, \mat{C}_{of}=\mat{B}_{cf}^T$
-and $\mat{B}_{of}=\mat{C}_{cf}^T$, which also applies to the MIMO case.
-
-Let 
-\begin{equation}
-\label{eq:wnof}
-\mat{W}_o=[\begin{array}{ccccc}\mat{C}&\mat{A}\mat{C}&\mat{A}^2\mat{C}&\hdots&\mat{C}^{n-1}\mat{B}\end{array}]^T
-\end{equation}
-be the observability matrix of the system, and
-\begin{equation}
-\label{eq:wof}
-\mat{W}_{of}=\mat{R}_{cf}^{-1}
-\end{equation}
-the observability matrix of the canonical form (see eg~\cite{astrom1997computer}). 
-Then the dynamical system 
-\begin{equation}
-\label{eq:to_of}
-\hat{\vec{x}}_{k+1}=(\mat{A}_o-\mat{L}\mat{C}_o)\hat{\vec{x}}_k+\mat{B}_o\vec{u}+\mat{L}\vec{y} : \mat{L}=\mat{W}_o^{-1}\mat{W}_{of} \left[ \begin{array}{c}p_1-a_1\\p_2-a_2\\p_n-a_n\end{array}\right]
-\end{equation}
-\begin{displaymath}
-\mat{A}_o=\mat{A},\ \mat{B}_o=\mat{B},\ \mat{C}_o=\mat{C}
-\end{displaymath}
-is an observer of the system $\vec{x}_{k+1}=\mat{A}\vec{x}+\mat{B}\vec{u} : \vec{y}=\mat{C}\vec{x}$. $p_i$ are user selected
-values which will affect the error of the observer estimator.
-The differentiation between $\mat{*}_o$ and $\mat{*}$ will be exploited later in this work.
-For the time being we will assume they are the same.
-
-Figure \ref{fig:observersystem} shows an LTI system with a feedback control using an observer.
-Presuming a sampled model of the plant as described in \eqref{eq:discretize}, the closed loop dynamics of this system are given by:
-\begin{equation}
-\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_{k+1}
-=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}_d&\mat{B}_d\mat{K}_d\\ \mat{0}&\mat{A}_d-\mat{L}_d\mat{C}_d\end{array}\right]
-\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_k
-+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
-+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}_d\end{array}\right]\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]
-\label{eq:observer_LTI}
-\end{equation}
-where $\hat{\vec{x}}_e=\vec{x}-\hat{\vec{x}}$ is the observer error.
-Replacing the matrices in \eqref{eq:observer_LTI} with appropriate symbols, we find that it still has a similar structure to \eqref{eq:discretization} which will be helpful in our analysis.
-
-\begin{figure*}[htb]
-\centering
-
-\tikzset{add/.style n args={4}{
-    minimum width=6mm,
-    path picture={
-        \draw[circle] 
-            (path picture bounding box.south east) -- (path picture bounding box.north west)
-            (path picture bounding box.south west) -- (path picture bounding box.north east);
-        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
-        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
-        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
-        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
-        }
-    }
- }
-
-\resizebox{1.0\textwidth}{!}{
- \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
-     semithick, initial text=, ampersand replacement=\&,]
-
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
-    \node[draw=none] (r) {$r_k$};
-    \node[rectangle,draw,
-	minimum width=1cm,
-	minimum height=1cm,] (gain)at ([xshift=1.2cm]r) {\sc $k_r$};
-
-   \& \node[circle,add={-}{+}{}{}] (circle) {};
-   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$u_k$};
-   \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Kd) at ([xshift=0,yshift=-5.5cm]circle)  {\sc $\mat{K}_d$};
-   \coordinate (kdsouth) at ([yshift=-3cm]Kd);
-
-   \& complexnode/.pic={ 
-      \node[rectangle,dashed,draw,minimum width=3cm,minimum height=1.6cm,label=\textbf{DAC}] (dac) {};
-     \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
-     \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
-     \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
-     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {\sc ZOH};
-   }
-
-   \& complexnode/.pic={ 
-      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2.5cm,yshift=.5cm]plant.center)  {\sc $\mat{B}$};
-      \node[draw=none] (u) at ([xshift=-1cm,yshift=.15cm]B)  {$u(t)$};
-      \node[circle,add={+}{+}{}{}] (p1) at ([xshift=-1.3cm,yshift=.5cm]plant.center) {};
-      \node[draw=none] (xdot) at ([xshift=.85cm,yshift=.15cm]p1)  {$\dot{\vec{x}}(t)$};   
-      \node[rectangle,draw,minimum width=1cm] (int) at ([xshift=.5cm,yshift=.5cm]plant.center) {\sc $\int$};
-      \coordinate (xsouth) at ([xshift=1cm]int);
-      \node[draw=none] (x) at ([xshift=1cm,yshift=.15cm]int)  {$\vec{x}(t)$};   
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (C) at ([xshift=2.7cm,yshift=.5cm]plant.center)  {\sc $\mat{C}$};
-      \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]C)  {$\vec{y}(t)$};   
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (A) at ([xshift=.5cm,yshift=-1cm]plant.center)  {\sc $\mat{A}$};
-      \coordinate (aeast) at ([xshift=1cm]A);
-      \coordinate (awest) at ([xshift=-1.8cm]A);
-    }
-
-   complexnode/.pic={ 
-      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=5cm,label=\textbf{Observer}] (observer)  at ([yshift=-5cm]plant.center) {};
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Bd) at ([xshift=-2.5cm]observer.center)  {\sc $\mat{B}_d$};
-      \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]Bd)  {$u_k$};
-      \node[circle,add={+}{+}{+}{}] (o1) at ([xshift=-1.3cm]observer.center) {};
-      \node[draw=none] (xd) at ([xshift=.85cm,yshift=.15cm]o1)  {$\hat{\vec{x}}_{k+1}$};   
-      \node[rectangle,draw,minimum width=1cm] (delay) at ([xshift=.5cm]observer.center) {\sc $z^{-1}$};
-      \coordinate (xdsouth) at ([xshift=1.3cm]delay);
-      \coordinate (fbsouth) at ([xshift=1.3cm,yshift=-3cm]delay);
-      \node[draw=none] (xdp) at ([xshift=1cm,yshift=.15cm]delay)  {$\hat{\vec{x}}_k$};   
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Cd) at ([xshift=2.7cm]observer.center)  {\sc $\mat{C}_d$};
-      \node[draw=none] (y) at ([xshift=.4cm,yshift=.8cm]Cd)  {$\hat{\vec{y}}_k$};   
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ad) at ([xshift=.5cm,yshift=-1.5cm]observer.center)  {\sc $\mat{A}_d$};
-      \coordinate (adeast) at ([xshift=1.3cm]Ad);
-      \coordinate (adwest) at ([xshift=-1.8cm]Ad);
-      \node[circle,add={-}{}{}{+}] (o2) at ([xshift=2.7cm,yshift=1.5cm]observer.center) {};
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ld) at ([xshift=.5cm,yshift=1.5cm]observer.center)  {\sc $\mat{L}_d$};
-      \coordinate (ldwest) at ([xshift=-1.8cm]Ld);
-      \coordinate (bdwest) at ([xshift=-5.5cm]Bd);
-      \coordinate (uksouth) at ([xshift=-5.5cm,yshift=5.5cm]Bd);
-      \coordinate (o2east) at ([xshift=6.3cm]o2);
-    }
-
-   \& complexnode/.pic={ 
-     \node[rectangle,dashed,draw,minimum width=3.5cm,minimum height=1.6cm,label=\textbf{ADC},] (adc) {};
-     \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
-     \coordinate (switch1) at ([xshift=-1cm]adc.center);
-     \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
-     \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
-     \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
-     \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
-     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]q1)  {$\vec{y}_k$};       
-     \coordinate (ykeast) at ([xshift=1.9cm]q1);
-   } 
-   \& \coordinate (aux1);
-   \& \\
-  };
-
-  \path[->] (v1) edge (q1.south);
-  \path[->] (v2) edge (q2.south);
-  \path[->] (r) edge (gain.west);
-  \path[->] (gain.east) edge (circle.west);
-  \path[->] (circle.east) edge (q2.west);
-  \path       (q2.east) edge (zoh.west);
-  \path[->] (zoh.east) edge (B.west);
-  \path
-   (B.east) edge (p1.west)
-   (p1.east) edge (int.west)
-   (xsouth) edge (aeast)
-   (aeast) edge (A.east)
-   (A.west) edge (awest)
-   (awest) edge (p1.south)
-   (int.east) edge (C.west)
-   (C.east) edge (switch1.west)
-   (switch2) edge (q1.west);
-  \path
-   (q1.east) edge (ykeast)
-   (ykeast) edge (o2east);
-  \path       (uksouth) edge (bdwest);
-  \path[->] (bdwest) edge (Bd.west);
-  \path
-   (Bd.east) edge (o1.west)
-   (o1.east) edge (delay.west)
-   (xdsouth) edge (adeast)
-   (adeast) edge (Ad.east)
-   (Ad.west) edge (adwest)
-   (adwest) edge (o1.south)
-   (o2.west) edge (Ld.east)
-   (Ld.west) edge (ldwest)
-   (ldwest) edge (o1.north)
-   (delay.east) edge (Cd.west)
-   (Cd.north) edge (o2.south)
-   (o2east) edge (o2.east)
-   (xdsouth) edge (fbsouth)
-   (fbsouth) edge (kdsouth);
-  \path[->]  (kdsouth) edge (Kd.south);
-  \path (Kd.north) edge (circle.south);
- \end{tikzpicture}
-}
- \caption{Closed-loop digital control system with observer\label{fig:observersystem}}
-\end{figure*}
-
 \end{document}

### 2017-01-20 cav2017/appendix4.tex
adding appendix4 in a separate file just in case anyone wants it back

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Observable canonical form} \label{sec:observable}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
The Controllable Canonical Form is ideal when we have access to the state space. However, in most cyberphisical
systems, only the outputs of the plant can be observed, hence we require an Observable Canonical Form.
For SISO systems, this is:
\begin{align}
\label{of_SISO}
\mat{A}_{of}=&\left[
\begin{array}{ccccc}
0&0&0&\cdots&-a_n\\
1&0&0&\cdots&-a_{n-1}\\
0&1&0&\cdots&-a_{n-2}\\
\vdots&\ddots&\ddots&\ddots&\vdots\\
0&0&\cdots&1&-a_1
\end{array}\right],
\mat{B}_{of}=\left[
\begin{array}{c}
\eta_n\\ \eta_{n-1}\\ \vdots\\ \eta_1
\end{array}\right]\\
\mat{C}_{of}=&[\begin{array}{ccccc}0&0&\cdots&0&1\end{array}] \nonumber
\end{align}

What is important to notice her is that $\mat{A}_{of}=\mat{A}_{cf}^T, \mat{C}_{of}=\mat{B}_{cf}^T$
and $\mat{B}_{of}=\mat{C}_{cf}^T$, which also applies to the MIMO case.

Let 
\begin{equation}
\label{eq:wnof}
\mat{W}_o=[\begin{array}{ccccc}\mat{C}&\mat{A}\mat{C}&\mat{A}^2\mat{C}&\hdots&\mat{C}^{n-1}\mat{B}\end{array}]^T
\end{equation}
be the observability matrix of the system, and
\begin{equation}
\label{eq:wof}
\mat{W}_{of}=\mat{R}_{cf}^{-1}
\end{equation}
the observability matrix of the canonical form (see eg~\cite{astrom1997computer}). 
Then the dynamical system 
\begin{equation}
\label{eq:to_of}
\hat{\vec{x}}_{k+1}=(\mat{A}_o-\mat{L}\mat{C}_o)\hat{\vec{x}}_k+\mat{B}_o\vec{u}+\mat{L}\vec{y} : \mat{L}=\mat{W}_o^{-1}\mat{W}_{of} \left[ \begin{array}{c}p_1-a_1\\p_2-a_2\\p_n-a_n\end{array}\right]
\end{equation}
\begin{displaymath}
\mat{A}_o=\mat{A},\ \mat{B}_o=\mat{B},\ \mat{C}_o=\mat{C}
\end{displaymath}
is an observer of the system $\vec{x}_{k+1}=\mat{A}\vec{x}+\mat{B}\vec{u} : \vec{y}=\mat{C}\vec{x}$. $p_i$ are user selected
values which will affect the error of the observer estimator. The differentiation between $\mat{*}_o$ and $\mat{*}$ will be exploited later in this work. For the time being we will assume they are the same.

Figure \ref{fig:observersystem} shows an LTI system with a feedback control using an observer. Presuming a sampled model of the plant as described in \eqref{eq:discretize}, the closed loop dynamics of this system are given by:
\begin{equation}
\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_{k+1}
=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}_d&\mat{B}_d\mat{K}_d\\ \mat{0}&\mat{A}_d-\mat{L}_d\mat{C}_d\end{array}\right]
\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_k
+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}_d\end{array}\right]\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]
\label{eq:observer_LTI}
\end{equation}
where $\hat{\vec{x}}_e=\vec{x}-\hat{\vec{x}}$ is the observer error.
Replacing the matrices in \eqref{eq:observer_LTI} with appropriate symbols, we find that it still has a similar structure to \eqref{eq:discretization} which will be helpful in our analysis.

\begin{figure*}[htb]
\centering

\tikzset{add/.style n args={4}{
    minimum width=6mm,
    path picture={
        \draw[circle] 
            (path picture bounding box.south east) -- (path picture bounding box.north west)
            (path picture bounding box.south west) -- (path picture bounding box.north east);
        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
        }
    }
 }

\resizebox{1.0\textwidth}{!}{
 \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
     semithick, initial text=, ampersand replacement=\&,]

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
    \node[draw=none] (r) {$r_k$};
    \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,] (gain)at ([xshift=1.2cm]r) {\sc $k_r$};

   \& \node[circle,add={-}{+}{}{}] (circle) {};
   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$u_k$};
   \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Kd) at ([xshift=0,yshift=-5.5cm]circle)  {\sc $\mat{K}_d$};
   \coordinate (kdsouth) at ([yshift=-3cm]Kd);

   \& complexnode/.pic={ 
      \node[rectangle,dashed,draw,minimum width=3cm,minimum height=1.6cm,label=\textbf{DAC}] (dac) {};
     \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
     \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
     \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {\sc ZOH};
   }

   \& complexnode/.pic={ 
      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2.5cm,yshift=.5cm]plant.center)  {\sc $\mat{B}$};
      \node[draw=none] (u) at ([xshift=-1cm,yshift=.15cm]B)  {$u(t)$};
      \node[circle,add={+}{+}{}{}] (p1) at ([xshift=-1.3cm,yshift=.5cm]plant.center) {};
      \node[draw=none] (xdot) at ([xshift=.85cm,yshift=.15cm]p1)  {$\dot{\vec{x}}(t)$};   
      \node[rectangle,draw,minimum width=1cm] (int) at ([xshift=.5cm,yshift=.5cm]plant.center) {\sc $\int$};
      \coordinate (xsouth) at ([xshift=1cm]int);
      \node[draw=none] (x) at ([xshift=1cm,yshift=.15cm]int)  {$\vec{x}(t)$};   
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (C) at ([xshift=2.7cm,yshift=.5cm]plant.center)  {\sc $\mat{C}$};
      \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]C)  {$\vec{y}(t)$};   
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (A) at ([xshift=.5cm,yshift=-1cm]plant.center)  {\sc $\mat{A}$};
      \coordinate (aeast) at ([xshift=1cm]A);
      \coordinate (awest) at ([xshift=-1.8cm]A);
    }

   complexnode/.pic={ 
      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=5cm,label=\textbf{Observer}] (observer)  at ([yshift=-5cm]plant.center) {};
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Bd) at ([xshift=-2.5cm]observer.center)  {\sc $\mat{B}_d$};
      \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]Bd)  {$u_k$};
      \node[circle,add={+}{+}{+}{}] (o1) at ([xshift=-1.3cm]observer.center) {};
      \node[draw=none] (xd) at ([xshift=.85cm,yshift=.15cm]o1)  {$\hat{\vec{x}}_{k+1}$};   
      \node[rectangle,draw,minimum width=1cm] (delay) at ([xshift=.5cm]observer.center) {\sc $z^{-1}$};
      \coordinate (xdsouth) at ([xshift=1.3cm]delay);
      \coordinate (fbsouth) at ([xshift=1.3cm,yshift=-3cm]delay);
      \node[draw=none] (xdp) at ([xshift=1cm,yshift=.15cm]delay)  {$\hat{\vec{x}}_k$};   
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Cd) at ([xshift=2.7cm]observer.center)  {\sc $\mat{C}_d$};
      \node[draw=none] (y) at ([xshift=.4cm,yshift=.8cm]Cd)  {$\hat{\vec{y}}_k$};   
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ad) at ([xshift=.5cm,yshift=-1.5cm]observer.center)  {\sc $\mat{A}_d$};
      \coordinate (adeast) at ([xshift=1.3cm]Ad);
      \coordinate (adwest) at ([xshift=-1.8cm]Ad);
      \node[circle,add={-}{}{}{+}] (o2) at ([xshift=2.7cm,yshift=1.5cm]observer.center) {};
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ld) at ([xshift=.5cm,yshift=1.5cm]observer.center)  {\sc $\mat{L}_d$};
      \coordinate (ldwest) at ([xshift=-1.8cm]Ld);
      \coordinate (bdwest) at ([xshift=-5.5cm]Bd);
      \coordinate (uksouth) at ([xshift=-5.5cm,yshift=5.5cm]Bd);
      \coordinate (o2east) at ([xshift=6.3cm]o2);
    }

   \& complexnode/.pic={ 
     \node[rectangle,dashed,draw,minimum width=3.5cm,minimum height=1.6cm,label=\textbf{ADC},] (adc) {};
     \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
     \coordinate (switch1) at ([xshift=-1cm]adc.center);
     \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
     \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
     \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
     \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]q1)  {$\vec{y}_k$};       
     \coordinate (ykeast) at ([xshift=1.9cm]q1);
   } 
   \& \coordinate (aux1);
   \& \\
  };

  \path[->] (v1) edge (q1.south);
  \path[->] (v2) edge (q2.south);
  \path[->] (r) edge (gain.west);
  \path[->] (gain.east) edge (circle.west);
  \path[->] (circle.east) edge (q2.west);
  \path       (q2.east) edge (zoh.west);
  \path[->] (zoh.east) edge (B.west);
  \path
   (B.east) edge (p1.west)
   (p1.east) edge (int.west)
   (xsouth) edge (aeast)
   (aeast) edge (A.east)
   (A.west) edge (awest)
   (awest) edge (p1.south)
   (int.east) edge (C.west)
   (C.east) edge (switch1.west)
   (switch2) edge (q1.west);
  \path
   (q1.east) edge (ykeast)
   (ykeast) edge (o2east);
  \path       (uksouth) edge (bdwest);
  \path[->] (bdwest) edge (Bd.west);
  \path
   (Bd.east) edge (o1.west)
   (o1.east) edge (delay.west)
   (xdsouth) edge (adeast)
   (adeast) edge (Ad.east)
   (Ad.west) edge (adwest)
   (adwest) edge (o1.south)
   (o2.west) edge (Ld.east)
   (Ld.west) edge (ldwest)
   (ldwest) edge (o1.north)
   (delay.east) edge (Cd.west)
   (Cd.north) edge (o2.south)
   (o2east) edge (o2.east)
   (xdsouth) edge (fbsouth)
   (fbsouth) edge (kdsouth);
  \path[->]  (kdsouth) edge (Kd.south);
  \path (Kd.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Closed-loop digital control system with observer\label{fig:observersystem}}
\end{figure*}

### 2017-01-20 cav2017/cav2017.tex
removed appendix about observable systems
wording

@@
 1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
-compute a candidate solution $K$. It does this by assuming some 
-precision $<I_p,F_p>$ for the plant, a $k$ and a sampling rate.  The checks that
-these assumptions are sound are performed by the subsequent {\sc
-  verify} stages.
+compute a candidate solution $K$. For this purpose, it assumes some
+precision $<I_p,F_p>$ for the plant, a $k$ and a sampling rate.  The
+checks that these assumptions are sound are performed by subsequent
+{\sc verify} stages.
 

### 2017-01-20 cav2017/cav2017.tex
unwinding section

--- 2017-01-20 cav2017/cav2017.tex
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-The synthesis problem we are trying to solve is the following: find a
-digital controller $K$ (see Eq.~\ref{eq:controlaction}) that makes the
-closed-loop system safe for initial state $x_0$, reference signal
-$r_k$ and input $u_k$ as defined in Sec.~\ref{ssec:safety}.  We
-consider non-deterministic initial states within a specified range and
-the reference signal to be 0 (\todo{refer to wherever this is
-  explained initially}).  Then, when mapping back to the notation used
-for describing the general architecture of the program synthesizer,
-the controller $K$ denotes $P$ and $(x_0, u_k)$ represents $x$.  We
-compute the coefficients for $K$ in the domain $\mathbb{R}<I,F>$.
+The synthesis problem we are trying to solve is the following:
+find a digital controller $K$ (see Eq.~\ref{eq:controlaction})
+that makes the closed-loop system safe for 
+initial state $x_0$, reference signal $r_k$ and input $u_k$
+as defined in Sec.~\ref{ssec:safety}. 
+We consider non-deterministic initial states within a specified range
+and the reference signal to be 0 (\todo{refer to wherever this is explained initially}).
+Then, when mapping back to the notation used for describing the general architecture 
+of the program synthesizer, the controller $K$ denotes $P$ and 
+$(x_0, u_k)$ represents $x$. 
+We compute the coefficients for $K$ in the domain $\mathbb{R}<I,F>$.
 
@@
 The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
-One important observation is that, for this approach,
-we compute the set of reachable states by finding 
-a completeness threshold $\overline{k}$.
+One important observation is that, for this approach, we verify and synthesise 
+a controller over $k$ time steps. We then compute a completeness threshold, $\overline{k}$,
+for this controller, and verify the controller's correctness to $\overline{k}$ time steps.
 Essentially, $\overline{k}$ represents the number of iterations 
@@
 1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
-compute a candidate solution $K$. It does this by assuming some 
-precision $<I_p,F_p>$ for the plant, a $k$ and a sampling rate.  The checks that
+compute a candidate solution $K$ that satisfies the stability criteria described in 
+\todo{SECTION STABILITY CRITERIA}, i.e., that the eigenvalues of the dynamics fall within 
+the unit circle, and the safety specification described in \todo{SECTION:SAFETY SPEC}, i.e.,
+that the state values do not violate the safe state upper and lower bounds within $k$ steps. 
+It does this by assuming some 
+precision $<I_p,F_p>$ for the plant, a $k$ and a sampling rate.
+
+The checks that
 these assumptions are sound are performed by the subsequent {\sc
@@
 
-2. The first {\sc verify} stage, {\sc safety}, 
-performs potentially unsound operations by considering the currently
-assumed $<I_p,F_p>$, $k$ and sampling rate. % The soundness is to be 
+2. The first {\sc verify} stage, {\sc safety}, checks that the candidate
+solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
+state within $k$ steps. 
+This check is potentially unsound because we considering the currently
+assumed $<I_p,F_p>$, $k$ and sampling rate.
+
+% The soundness is to be 
 % restored by the subsequent three validation stages.
@@
 completeness threshold $\overline{k}$ for the current candidate $K$
-and check that $k{\leq}\overline{k}$.  \todo{discuss the computation
+and check that $k{\leq}\overline{k}$.
+
+A stable control system is known to have converging dynamics, i.e., the
+distance from the reference (in this case the origin) decreases over time.
+
+ \todo{discuss the computation
   of the completeness threshold}

### 2017-01-20 cav2017/cav2017.tex

@@
 1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
-compute a candidate solution $K$ that satisfies the stability criteria described in 
-\todo{SECTION STABILITY CRITERIA}, i.e., that the eigenvalues of the dynamics fall within 
-the unit circle, and the safety specification described in \todo{SECTION:SAFETY SPEC}, i.e.,
-that the state values do not violate the safe state upper and lower bounds within $k$ steps. 
-It does this by assuming some 
-precision $<I_p,F_p>$ for the plant, a $k$ and a sampling rate.
-
-The checks that
-these assumptions are sound are performed by the subsequent {\sc
-  verify} stages.
+compute a candidate solution $K$. For this purpose, it assumes some
+precision $<I_p,F_p>$ for the plant, a $k$ and a sampling rate.  The
+checks that these assumptions are sound are performed by subsequent
+{\sc verify} stages.
 

### 2017-01-20 cav2017/cav2017.tex
remark regarding the controller's precision

@@
 $(x_0, u_k)$ represents $x$. 
-We compute the coefficients for $K$ in the domain $\mathbb{R}<I,F>$.
+While the controller's precision $\langle I,F\rangle$ is given, 
+we can vary the plant's precision $\langle I_p,F_p\rangle$ such that 
+$\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
 
@@
 compute a candidate solution $K$. For this purpose, it assumes some
-precision $<I_p,F_p>$ for the plant, a $k$ and a sampling rate.  The
+precision $\langle I_p,F_p\rangle$ for the plant, a $k$ and a sampling rate.  The
 checks that these assumptions are sound are performed by subsequent
@@
 state within $k$ steps. 
-This check is potentially unsound because we considering the currently
+This check is potentially unsound because we consider the currently
 assumed $<I_p,F_p>$, $k$ and sampling rate.
-
-% The soundness is to be 
-% restored by the subsequent three validation stages.
 

### 2017-01-20 cav2017/cav2017.tex
use underline/overline for lower/upper bounds

@@
 \label{eq:safetyliteral}
-\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{x_{i}^{-} \leq x_{i,k} \leq x_{i}^{+}},
+\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
 \end{equation}
@@
 %\todo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
-where $x_{i}^{-}$ and $x_{i}^{+}$ are the lower and upper bound 
+where $\underline{x_{i}}$ and $\overline{x_{i}}$ are the lower and upper bound 
 of the $i$-th state $x_{i}$ at the $k$-th instant, respectively.
@@
 
-The input $u_{k}$%is non-deterministic with 
-has known bounds $u^{+}$ and $u^{-}$, 
-such that ${u^{-} \leq u_{k} \leq u^{+}},\forall k\geq 0$.
+The input $u_{k}$ %is non-deterministic with 
+has known bounds $\overline{u}$ and $\underline{u}$, 
+such that ${\underline{u} \leq u_{k} \leq \overline{u}},\forall k\geq 0$.
 

### 2017-01-20 cav2017/cav2017.tex
small

@@
 required to sufficiently unwind the closed-loop state-space system 
-such that the boundaries are not violated for any $k>\overline{k}$
+such that the boundaries are not violated for any $k{>}\overline{k}$
 (i.e. it's sufficient to unwound the closed-loop state-space system up to  
@@
 This check is potentially unsound because we consider the currently
-assumed $<I_p,F_p>$, $k$ and sampling rate.
+assumed $\langle I_p,F_p\rangle$, $k$ and sampling rate.
 
@@
 current $k$ is large enough to ensure that the boundaries are not
-violated for any $k'>k$.  For this purpose, we compute the
+violated for any $k'{>}k$.  For this purpose, we compute the
 completeness threshold $\overline{k}$ for the current candidate $K$

### 2017-01-20 cav2017/cav2017.tex
swapped sections

@@
 
-\subsection{Solution generalisation} 
-Given the large soloution space to be searched during the inductive
-synthesis phase, we parametrise the target language, which induces a
-lattice of progressively more expressive languages.  This enables us
-to start by attempting to synthesise a program at the lowest point on
-this lattice and increase the parameters of the language until we
-reach a point at which the synthesis succeeds. Whenever we manage to
-synthesise a candidate solution at some lower point on the lattice, we
-must apply some form of solution generalisation to obtain a full
-solution (i.e. a solution in the original search space).
-
-As well as giving us an automatic search procedure, this
-parametrisation greatly increases the efficiency of our system since
-languages low down the lattice are very easy to decide safety for
-(i.e. the validation oracle finds an answer fast). If a program can be
-synthesised in a low-complexity language, the whole procedure finishes
-much faster than if synthesis had been attempted in a high-complexity
-language.
-
-We investigate two different approaches of integrating solution generalisation 
-with CEGIS:
-\begin{itemize}
-\item[1.] The first approach uses abstract acceleration to compute the set of reachable states, which enables it to perform abstraction refinement inside the CEGIS loop (see Sec~\ref{sec:CEGIS-abstraction-refinement}).
-\item[2.] The second approach relies on computing a 
-completeness threshold $k$ for each loop such that it is sufficient to 
-unroll the corresponding loop $k$ times. For this approach the 
-generalisation step is given as an incremental
-increase of precision and sampling rate (see Sec.~\ref{sec:CEGIS-precision-incrementation}).
-\end{itemize}
-
-% In Sec.~\ref{sec:CEGIS-abstraction-refinement} and 
-% Sec.~\ref{sec:CEGIS-precision-incrementation}, we explain how we 
-% specialise the general CEGIS approach in order to perform solution generalisation.
-
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 $\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Solution generalisation} 
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+Given the large soloution space to be searched during the inductive
+synthesis phase, we parametrise the target language, which induces a
+lattice of progressively more expressive languages.  This enables us
+to start by attempting to synthesise a program at the lowest point on
+this lattice and increase the parameters of the language until we
+reach a point at which the synthesis succeeds. Whenever we manage to
+synthesise a candidate solution at some lower point on the lattice, we
+must apply some form of solution generalisation to obtain a full
+solution (i.e. a solution in the original search space).
+
+As well as giving us an automatic search procedure, this
+parametrisation greatly increases the efficiency of our system since
+languages low down the lattice are very easy to decide safety for
+(i.e. the validation oracle finds an answer fast). If a program can be
+synthesised in a low-complexity language, the whole procedure finishes
+much faster than if synthesis had been attempted in a high-complexity
+language.
+
+We investigate two different approaches of integrating solution generalisation 
+with CEGIS:
+\begin{itemize}
+\item[1.] The first approach uses abstract acceleration to compute the set of reachable states, which enables it to perform abstraction refinement inside the CEGIS loop (see Sec~\ref{sec:CEGIS-abstraction-refinement}).
+\item[2.] The second approach relies on computing a 
+completeness threshold $k$ for each loop such that it is sufficient to 
+unroll the corresponding loop $k$ times. For this approach the 
+generalisation step is given as an incremental
+increase of precision and sampling rate (see Sec.~\ref{sec:CEGIS-precision-incrementation}).
+\end{itemize}
+
+% In Sec.~\ref{sec:CEGIS-abstraction-refinement} and 
+% Sec.~\ref{sec:CEGIS-precision-incrementation}, we explain how we 
+% specialise the general CEGIS approach in order to perform solution generalisation.
 

### 2017-01-20 cav2017/cav2017.tex
removed paragraph in appendix + added todo
more todos

@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+\todo{Dario, can you please shorten this?}
 
@@
 \begin{itemize}
-\item[1.] The first approach uses abstract acceleration to compute the set of reachable states, which enables it to perform abstraction refinement inside the CEGIS loop (see Sec~\ref{sec:CEGIS-abstraction-refinement}).
-\item[2.] The second approach relies on computing a 
-completeness threshold $k$ for each loop such that it is sufficient to 
-unroll the corresponding loop $k$ times. For this approach the 
-generalisation step is given as an incremental
-increase of precision and sampling rate (see Sec.~\ref{sec:CEGIS-precision-incrementation}).
+\item[1.] The first approach uses abstract acceleration to compute the set of reachable states,
+  which enables it to perform abstraction refinement inside the CEGIS loop (see Sec~\ref{sec:CEGIS-abstraction-refinement}). 
+\todo{Dario, can you briefly explain solution generalisation for your approach?}
+\item[2.] The second approach uses a multi-staged validation phase
+  and performes solution generalisation based on
+the plant's precision, the number of loop unrollongs
+and the sampling rate (see Sec.~\ref{sec:CEGIS-precision-incrementation}).
+%%   relies on computing a 
+%% completeness threshold $k$ for each loop such that it is sufficient to 
+%% unroll the corresponding loop $k$ times. For this approach the 
+%% generalisation step is given as an incremental
+%% increase of precision and sampling rate 
 \end{itemize}
+
+\todo{Can we come up with some sort of figure that makes it easier to visualise
+the generalisation step in each approach?}
 
@@
 
-A discrete-time system is asymptotically stable if and only if all the roots 
-of the characteristic polynomial ({\it i.e.}, the eigenvalues) are inside of 
-the unity circle, {\it i.e.}, their absolute value are less than 
-one~\cite{astrom1997computer}. In this paper, we express 
-the stability specification $\phi_{stability}$ in terms of  
-Jury's criterion \cite{fadali}. A detailed description of this 
-specification can be found in the Appendix~\ref{sec:appendix-stability}.
-
 For a closed-loop system as~\eqref{eq:closedloopss}, 

### 2017-01-20 cav2017/cav2017.tex
typo

@@
   and performes solution generalisation based on
-the plant's precision, the number of loop unrollongs
+the plant's precision, the number of loop unrollings
 and the sampling rate (see Sec.~\ref{sec:CEGIS-precision-incrementation}).

### 2017-01-20 cav2017/cav2017.tex
use <I,F> for the controller's precision
switch to <I_c,F_c> for the controller's precision

@@
 %and disregarding it in the state equation~\eqref{eq:plant}.
-Thus, the states are computed using the following equations. We use $\mathcal{F}_{\langle I_c,F_c \rangle}$
+Thus, the states are computed using the following equations. We use $\mathcal{F}_{\langle I_c,F_c \rangle}$ to 
 to denote numbers represented with the precision of the digital controller. All other numbers
@@
 $(x_0, u_k)$ represents $x$. 
-While the controller's precision $\langle I,F\rangle$ is given, 
+While the controller's precision $\langle I_C,F_C\rangle$ is given, 
 we can vary the plant's precision $\langle I_p,F_p\rangle$ such that 
-$\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
+$\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I_c,F_c \rangle$.
 

### 2017-01-20 cav2017/cav2017.tex
Pseudo-description of the generalization Some extra cleanup on the observer and restructuring of aa approach

@@
 \begin{itemize}
-\item[1.] The first approach uses abstract acceleration to compute the set of reachable states,
-  which enables it to perform abstraction refinement inside the CEGIS loop (see Sec~\ref{sec:CEGIS-abstraction-refinement}). 
-\todo{Dario, can you briefly explain solution generalisation for your approach?}
-\item[2.] The second approach uses a multi-staged validation phase
+\item[1.] The first approach uses a multi-staged validation phase
   and performes solution generalisation based on
@@
 and the sampling rate (see Sec.~\ref{sec:CEGIS-precision-incrementation}).
-%%   relies on computing a 
-%% completeness threshold $k$ for each loop such that it is sufficient to 
-%% unroll the corresponding loop $k$ times. For this approach the 
-%% generalisation step is given as an incremental
-%% increase of precision and sampling rate 
+\item[2.] The second approach uses abstract acceleration to compute the set of reachable states,
+  which enables it to perform abstraction refinement inside the CEGIS loop (see Sec~\ref{sec:CEGIS-abstraction-refinement}).
+
+The advantage of the second approcah are that whereas in the first case we use concrete traces from non-deterministic simulations
+and generalize over continuous sets into an unbounded time, 
+the abstract acceleration synthesis analyses the system over a generalized state-space (ie it looks at all the states simultaneously), requiring the CEGIS loop to generalize only over the time horizon of the system.
+
+Hence, aproach one finds a controller for an individual initial state and input with a bounded time horizon and generalizes to all states, inputs and time horizons (with a final verification loop that verifies the continuous system behaviour against the previously verified discrete system bisimulation).
+Approach two finds a controller for a continuous initial state-space and input sets over an abstraction of the continuous dynamics which conforms to witness proofs at specific times k, and generalizes the solution for all times by refining the number of witnesses.
+
 \end{itemize}
@@
 
+The verification of a hybrid continuous/discrete time/space system over an unbounded time, requires the
+non-deterministic simulation of an infinite set of states, which is undecidable. Our initial approach creates an
+abstraction of this system by establishing bounds on the error between such a system and a discrete-time/space model.
+This model is still however, quite complex, hard to verify, and many of the states involved are inconsequential to
+the safety specification.
+Our second model, rather than look at a direct bisimulation in discrete time, explores a much higher abstraction,
+evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specifcation.
+We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a
+single iteration, in addition to a stability specification defined by Jury's criteria, and try to synthesise a controller that meets these specs.
+A second abstraction that encompasses the accelerated continuous reach-tube over an unbounded time is used to verify that the controller meets the full safety specification.
+If this step fails, we find a counterexmple iteration that causes the selected system to fail and create a new constraint to refine our abstraction.
+The advantage of this model is that it starts with a very simple description regardless of the complexity of the overall dynamics, and only expands to more complex models when a solution cannot be found.
+
 \todo{Move as much as possible from Sec~\ref{sec:cof_verification}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Verification of a controllable observed system}
+\subsubsection{Verification of a controllable system}
 \label{sec:cof_verification}
@@
 in sections \ref{sec:reachable} and \ref{sec:observable}.
-A controllable and observable system will have the following dynamics:
+A controllable system with quantization will have the following dynamics:
 
@@
 \begin{align*}
-\mat{A}_{tp}=&\left[
+\mat{A}_{t}=\mat{T}\mat{A}_d\mat{T}^{-1}&\left[
 \begin{array}{ccccc}
@@
 
-Careful examination of these matrices reveals that because the $\mat{A}_t$ is 
-upper block diagonal, the spectrum of $\mat{A}_t$ is equal to the union of the 
-spectrum of $\mat{A}_{tp}$ and $\mat{A}_{to}$, which can be calculated separately. 
-Additionally, these correspond to the roots of the following polynomials:
+The characteristic polynomial of the above matix is:
 %
 \begin{align*}
-\left(z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}\right)
+z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}
 \end{align*}
@@
 \begin{enumerate}
-\item Calculate $\mat{A}_o,\mat{B}_o,\mat{C}_o$ by rounding down the coefficients $*_{oij}=\mathcal{F}\langle I,F,E\rangle (*_{ij}) : *=\{a,b,c\}$
-\item Calculate $\mat{T}$ and $\mat{W}_o^{-1}\mat{W}_{of}$ using equations \eqref{eq:rncf}\eqref{eq:rcf}\eqref{eq:to_cf}\eqref{eq:wnof}\eqref{eq:wof}
+\item Calculate $\mat{T}$ using equations \eqref{eq:rncf}\eqref{eq:rcf}\eqref{eq:to_cf}
 \item Extract the Plant's characteristic polynomial coefficients from the last row of $P_a=(\mat{T}\mat{A}\mat{T}^-1)_{n*}$.
 \item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors ($\frac{q_1}{2},\frac{q_2}{2},q_3$)
-\item Produce an initial abstraction which corresponds to an unconstrained solution space.
+\item Calculate a set of initial bounds on K based on the input constraints. $$\phi_{input} \Leftrightarrow u_k=r-Kx_k : x \in X^\# \wedge u_k \in [\underline{u}\ \ \overline{u}]$$
 \end{enumerate}
-\item Next we synthesise a candidate controller and observer. Let $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ be a program describing Jury's method.
+\item Next we synthesise a candidate controller. Let $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ be a program describing Jury's method.
 \begin{enumerate}
 \item Select a controller $\tilde{\mat{K}} \in \mathbb{R}\langle I,F\rangle^n$.
-This is achieved by solving a SAT formula $\mathcal{J}_K=\mathcal{J}\langle I,F,E \rangle (P_{a-k},\mat{T})$ that satisfies Jury's criteria for $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \mat{K}=\tilde{\mat{K}}\mat{T}$.
+This is achieved by solving a SAT formula $\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{input}$ that satisfies the input constraint and Jury's criteria for $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \mat{K}=\tilde{\mat{K}}\mat{T}$.
 \item If there is no candidate solution we return UNSAT and exit the loop.

### 2017-01-20 cav2017/cav2017.tex
ciao

@@
 of the following approaches: forward reachability analysis via unfolding of the dynamics, 
-or invariance generation;  if the above step fails, we loop back and invoke a CEGIS call 
+or invariant set generation via abstract acceleration;  
+further, if the above step fails, we loop back and invoke a CEGIS call 
 to seek alternative stabilising feedbacks, benefitting from the obtained counter-examples 
 to safety. 
-\textcolor{red}{[Mention GA and Abstract Acceleration here?] 
-The approach is proven sound by accounting for errors due to \ldots }
-The proposed synthesis approaches and respective tool are evaluated considering
+\textcolor{red}{[Mention GA and Abstract Acceleration here?]}  
+The approach is proven sound by accounting for errors due to the digitalisation of signals that are manipulated by the controller block.  
+The proposed synthesis approaches and a developed tool are evaluated considering 
 a set of intricate physical plant models taken from the digital control literature.
@@
 
-Linear Time Invariant (LTI) control systems represent a sizeable portion of
-modern embedded software, performing highly non-trivial control tasks,
+Linear Time Invariant (LTI) control models represent a broad class of dynamical systems
+%modern embedded software, performing highly non-trivial control tasks,
 with significant impact in numerous application areas such as
-environmental control, navigation, and 
-robotics~\cite{astrom1997computer,Franklin15}.
-Correct and sound control system verification is a challenging task. 
-In particular, the verification problem is exacerbated by artifacts specific 
-to digital control, such as the effects of finite-precision arithmetic, 
-time discretization, and quantization noise, which are typically introduced 
+the life sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}.
+Control synthesis for LTI is a broadly investigated, 
+however the presence of digital control architectures is exacerbated by specific artefacts,  
+%specific to digital control, 
+such as the effects of finite-precision arithmetic, time discretisation, and quantisation noise, which are typically introduced 
 by Analog-to-Digital (A/D) and Digital-to-Analog (D/A) conversion.  
-Thus, the programming is a key barrier to broad adoption of digital control, 
-and requires considerable expertise.
+Whilst the research on digital control is well developed [Astrom book on digital control], 
+automated and sound control synthesis is a challenging task. 
+%Thus, the programming is a key barrier to broad adoption of digital control, 
+%and requires considerable expertise.
 
@@
 Reachability tools are
-also used when discretizing the state-space for both verification and
+also used when discretising the state-space for both verification and
 parametric synthesis~\cite{cimatti2013parameter}.
 
-In this paper, however, we propose the synthesis of \emph{safe} control algorithms for
-cyberphysical systems taking into consideration the continuous domain
-of the plant, alongside the discrete domain of the controller and the
-hybrid elements that communicate them.
-%
+In this work, we propose the synthesis of \emph{safe} control algorithms for
+LTI models taking into consideration the continuous domain of the plant, 
+alongside the discrete domain of the controller and the hybrid elements that relate them.  
 %% In this paper, we synthesize controllers for hybrid
@@
 Due to the complexity of such systems, in this particular work we focus
-on linear models with known configurations and perform parametric synthesis
+on linear models \todo{[clarify next] with known configurations} and perform parametric synthesis
 of safe digital controllers.

### 2017-01-20 cav2017/cav2017.tex
+todo

@@
 
-The advantage of the second approcah are that whereas in the first case we use concrete traces from non-deterministic simulations
-and generalize over continuous sets into an unbounded time, 
-the abstract acceleration synthesis analyses the system over a generalized state-space (ie it looks at all the states simultaneously), requiring the CEGIS loop to generalize only over the time horizon of the system.
-
-Hence, aproach one finds a controller for an individual initial state and input with a bounded time horizon and generalizes to all states, inputs and time horizons (with a final verification loop that verifies the continuous system behaviour against the previously verified discrete system bisimulation).
-Approach two finds a controller for a continuous initial state-space and input sets over an abstraction of the continuous dynamics which conforms to witness proofs at specific times k, and generalizes the solution for all times by refining the number of witnesses.
-
 \end{itemize}
+
+\todo{Revise: }
+The first aproach finds a controller for an individual initial state and input with a bounded time horizon and generalizes to all states, inputs and time horizons (with a final verification loop that verifies the continuous system behaviour against the previously verified discrete system bisimulation).
+The second approach finds a controller for a continuous initial state-space and input sets over an abstraction of the continuous dynamics which conforms to witness proofs at specific times k, and generalizes the solution for all times by refining the number of witnesses.
+
+%% The advantage of the second approcah are that whereas in the first case we use concrete traces from non-deterministic simulations
+%% and generalize over continuous sets into an unbounded time, 
+%% the abstract acceleration synthesis analyses the system over a generalized state-space (ie it looks at all the states simultaneously), requiring the CEGIS loop to generalize only over the time horizon of the system.
 

### 2017-01-21 cav2017/cav2017.tex
some reductions

@@
 and the numeric error introduced by the digital controller, which uses an analogue-to-digital converter to read
-the states as a fixed-point number. In this section we formally outline the errors introduced by
+the states as a fixed-point number and performs operations in this domain. In this section we formally outline the errors introduced by
 fixed point representation of numbers; in further sections we will differentiate between these
@@
 \end{enumerate}
-The bounds obtained for division are left to the reader as it will not be applied in this paper.
-
-At this point it is worth mentioning that not all systems truncate equally. In the definition above $\delta$ may be positive
-or negative, and even this decision can be made dependent on the sign of $x$. Common cases in computer systems are:
-round downwards (\emph{ie} to $-\infty$), round upwards (\emph{ie} to $+\infty$), and round to zero.
-Rounding errors are cumulative which means the overall error will statistically increase with every operation, thus algorithms
-performing fewer operations can be more precise in this respect than iterative ones. 
+The bounds obtained for division are left to the reader as they will not be applied in this paper.
+
 \item {\bf Overflow:}
@@
 maximum representable number in the domain ($\pm 2^{I-1}+1-2^{-F}$), which means that any number outside this range
-cannot be accurately represented by the domain (\emph{eg} $\delta=x-2^{I-1}+1-2^{-F}$). In the case of floating point, a special
-case for infinity has been introduced, which addresses some of this issues, but once the error has gone to infinity, the numbers
-become meaningless. It is the responsibility of software designers and tools to account for overflows and either supply saturation
-functions to prevent them or raise alarms in their presence. In the case of verification, the latter is seen as a safety problem.
+cannot be represented by the domain (\emph{eg} $\delta=x-2^{I-1}+1-2^{-F}$). Our tool currently assumes no saturation
+function and verifies that no state overflows.
 \end{enumerate}
@@
 on the model. If we recall equation \eqref{eq:to_of}, the matrices of the observer and the controller  are not necessarily those of the plant.
-In fact we have $\mat{A},\mat{B} \in \mathbb{R}^*$, $\mat{A}_o,\mat{B}_o,\mat{K}_d, \mat{L}_d \in \mathbb{R}\langle I,F\rangle^*$
-Where $*$ represents the appropriate dimension for each matrix.
+In fact we have $\mat{A},\mat{B},\vec{x} \in \mathbb{R}^*$, $\mat{K}_d,\vec{u} \in \mathbb{R}\langle I,F\rangle^*$
+Where $*$ represents the appropriate dimension for each matrix/vector.
 Unfortunately this means that although combined matrices such as $\mat{A}_t$ are in the reals, they suffer from

### 2017-01-21 cav2017/cav2017.tex
More reductions

@@
 
-\todo{Dario, can you please shorten this?}
-
 There are two sources of error due to numeric representation; the numeric error introduced by 
@@
 Let $\mathbb{R} \langle I,F \rangle$ be a fixed point domain with $I$ bits representing the integer part and $F$ bits
-representing the decimal part. 
+representing the decimal part. The smallest number that can be represented in this domain is $c_m=2^{-F}$.
 The following approximation errors will arise:
@@
 \item {\bf Truncation:}
-Let $\mathcal{F}\langle I,F \rangle(\cdot) : \mathbb{R} \rightarrow \mathbb{R}\langle I,F \rangle, \tilde x=\mathcal{F}\langle I,F \rangle(x) = x-\delta : \delta=x\ \%_F\  c\tilde x$, where $\%_F$ is the modulus operation performed on the last bit of the representation ($2^{-F}$).
-The number $\delta$ corresponds to the truncation error of the representation and it will propagate across operations.
+Let $\mathcal{F}\langle I,F \rangle(\cdot) : \mathbb{R} \rightarrow \mathbb{R}\langle I,F \rangle, \tilde x=\mathcal{F}\langle I,F \rangle(x) = x-\delta_T : \delta_T=x\ \%_{c_m}\ \tilde x$, where $\%_{c_m}$ is the modulus operation performed wrt the last bit.
+$\delta_T$ is the truncation error and it will propagate across operations.
 \item {\bf Rounding:}
-%% Every time an operation is performed on a number in the $\mathbb{R} \langle I,F,E \rangle$ domain, an error may be
-%% introduced due to truncation of the result.
-Let us define $c\langle i,f \rangle \in \mathbb{R}\langle I,F\rangle$, where $i \in [-2^{I-1}\ 2^{I-1}],f \in [0 1)$ are its assigned values.
-The smallest number that can be represented for any given exponent is $c_{min}=2^{-F}$.
 The following errors appear in simple operations:
 \begin{enumerate}
-\item Addition/Substraction: in the case of fixed point arithmetic of numbers with the same domain, there are no rounding errors, otherwise the maximum error is given by the domain of the result $c\langle \cdot, F_1\rangle \pm c\langle \cdot , F_2\rangle= c\langle \cdot , F_3\rangle + \delta_3 :|\delta_3| \leq 2^{-F_3} \wedge F_3 \leq F_1,F_2$
-\item Multiplication: $c\langle \cdot, F_1\rangle * c\langle \cdot,F_2\rangle=c\langle \cdot,F_3\rangle + \delta_3 : |\delta_3| \leq 2^{-F_3} \wedge F_3 \leq F_1,F_2$ 
+\item Addition/Substraction: these operations only propagate errors coming from truncation of the operands.
+$c_1\pm c_2= c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$ 
+\item Multiplication: $c_1 * c_2= c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}*c_2| + |\delta_{T2}*c_1| + c_m$ 
+\item Division will not be applied in these implementations.
 \end{enumerate}
-The bounds obtained for division are left to the reader as they will not be applied in this paper.
 
@@
 Thus far we have presented a verification procedure for a digitalized plant in a continuous space (\emph{ie} the
-range of the quatizers is still $\mathbb{R}$. The next step we must reaize is that the controller and the observer
-exist in a digital program, hence their domain is $\mathbb{R}\langle I,F\rangle$. This has two separate effects
-on the model. If we recall equation \eqref{eq:to_of}, the matrices of the observer and the controller  are not necessarily those of the plant.
-In fact we have $\mat{A},\mat{B},\vec{x} \in \mathbb{R}^*$, $\mat{K}_d,\vec{u} \in \mathbb{R}\langle I,F\rangle^*$
+range of the quatizers is still $\mathbb{R}$. The next step we must reaize is that the controller 
+exists in a digital program, hence its domain is $\mathbb{R}\langle I,F\rangle$. We have $\mat{A},\mat{B},\vec{x} \in \mathbb{R}^*$, $\mat{K}_d,\vec{u} \in \mathbb{R}\langle I,F\rangle^*$
 Where $*$ represents the appropriate dimension for each matrix/vector.

### 2017-01-21 cav2017/cav2017.tex
Final reduction on 3.5

@@
   The finite word length set a
-maximum representable number in the domain ($\pm 2^{I-1}+1-2^{-F}$), which means that any number outside this range
-cannot be represented by the domain (\emph{eg} $\delta=x-2^{I-1}+1-2^{-F}$). Our tool currently assumes no saturation
+maximum representable number in the domain ($\pm (2^{I-1}+1-2^{-F})$), which means that any number outside this range
+cannot be represented by the domain. Our tool currently assumes no saturation
 function and verifies that no state overflows.
@@
 range of the quatizers is still $\mathbb{R}$. The next step we must reaize is that the controller 
-exists in a digital program, hence its domain is $\mathbb{R}\langle I,F\rangle$. We have $\mat{A},\mat{B},\vec{x} \in \mathbb{R}^*$, $\mat{K}_d,\vec{u} \in \mathbb{R}\langle I,F\rangle^*$
+exists in a digital program, hence its domain is $\mathbb{R}\langle I,F\rangle$.
+We have $\mat{A},\mat{B},\vec{x} \in \mathbb{R}^*$, $\mat{K}_d,\vec{u},\hat{\vec{x}}=\mathcal{F}\langle I,F \rangle(\vec{x}) \in \mathbb{R}\langle I,F\rangle^*$
 Where $*$ represents the appropriate dimension for each matrix/vector.
-Unfortunately this means that although combined matrices such as $\mat{A}_t$ are in the reals, they suffer from
-the fixed word restrictions in their composing matrices.
-The second effect corresponds to the rounding errors in the calculation of $\hat{x}_{k+1}, u_k$.
-These will introduce a new source of quantiztion noise which we may denote $\vec{\nu}_3 \in [-q_3\ \ q_3]$.
-The estimation of $\hat{\vec{x}}$ corresponds to the sum of three matrix-vector multiplications.
-Each of these has a coefficient-wise error bound $c_{min}$.
-Hence the overall $\overline{\delta}_{\hat{x}}=3nc_{min}$.
-The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=nc_{min}+\sum_{k=1}^nc_k\overline{\delta}_{\hat{x}}=(3|\mat{K}|_1+1)n2^{-F}$
+Unfortunately this means that although the closed loop dynamics are in the reals, they suffer from
+the fixed word restrictions in their composing elements.
+Apart from the quantization errors $q_1,q_2$ there are rounding errors in the calculation of $u_k$.
+These will introduce a new source of quantization noise which we may denote $\vec{\nu}_3 \in [-q_3\ \ q_3]$.
+The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=(|\mat{K}|_1+1)c_m$
 

### 2017-01-21 cav2017/cav2017.tex
Added todo notes package, also moved safety section
(I like todo notes)

@@
 
+\usepackage{todonotes}
 \usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
@@
 
-\newcommand{\todo}[1]{{\color{red} TODO: #1}}
+\newcommand{\addtodo}[1]{{\color{red} TODO: #1}}
 \newcommand{\commentib}[1]{{\color{blue} [IB: #1]}}
@@
 to safety. 
-\textcolor{red}{[Mention GA and Abstract Acceleration here?]}  
+\textcolor{red}{[Mention GA \todo{GA? Genetic Algorithms? We don't use GA?} and Abstract Acceleration here?]}
+
 The approach is proven sound by accounting for errors due to the digitalisation of signals that are manipulated by the controller block.  
@@
 Due to the complexity of such systems, in this particular work we focus
-on linear models \todo{[clarify next] with known configurations} and perform parametric synthesis
+on linear models \addtodo{[clarify next] with known configurations} and perform parametric synthesis
 of safe digital controllers.
@@
 
-\todo{Add contributions (Cristina)}
+\addtodo{Add contributions (Cristina)}
 
@@
 
-%\todo{[Move material from \ref{sec:rw} here]}
+%\addtodo{[Move material from \ref{sec:rw} here]}
 
@@
 %
-
+\missingfigure{state feedback controller block diagram}
 %-------------------------------
@@
 
-%\todo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantisation noises yet).]}
+%\addtodo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantisation noises yet).]}
 
@@
 
+%-------------------------------
+\subsection{Safety specifications for cyber-physical systems}
+\label{ssec:safety}
+%-------------------------------
+
+We also require that the closed-loop system meets safety specifications. 
+A safety specification establishes bounds for the states, such that 
+the controller $K$ must maintain the states within a given lower and upper 
+bound for any initial state. Note that a stable system is not necessarily a
+safe system, the state values may leave the safe states during the stabilization.
+
+The safety property represented by $\phi_{safety}$ is encoded as follows:
+%
+\begin{equation}
+\label{eq:safetyliteral}
+\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
+\end{equation}
+%
+%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
+where $\underline{x_{i}}$ and $\overline{x_{i}}$ are the lower and upper bound 
+of the $i$-th state $x_{i}$ at the $k$-th instant, respectively.
+This means that the states will always be within the $n$-dimensional 
+hyper-box, which is typically defined by the safety specification.
+
+The states values must be computed considering the digital controller error, i.e., the error introduced by the ADC and
+digital controller, and the digital reference signal. In this paper, we consider systems with
+a reference signal equal to zero. 
+%the FWL effects in all operations related to the control action~\eqref{eq:controlaction} 
+%and disregarding it in the state equation~\eqref{eq:plant}.
+Thus, the states are computed using the following equations. We use $\mathcal{F}_{\langle I_c,F_c \rangle}$ to 
+to denote numbers represented with the precision of the digital controller. All other numbers
+are represented with the precision of our plant model:
+%
+\begin{align*}
+u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})) \\
+x_{k+1}&=Ax_{k}+Bu_{k}
+\end{align*}
+%\left\lbrace
+%\begin{array}{l}
+%u_{k}=\mathcal{F}_{\langle I,F \rangle}(r_{k}-\mathcal{F}_{\langle I,F \rangle}(\mathcal{F}_{\langle I,F \rangle}(K)\cdot\mathcal{F}_{\langle I,F \rangle}(x_{k})))\\
+%x_{k+1}=Ax_{k}+Bu_{k}
+%\end{array}\right.
+%\end{equation}
+
+The input $u_{k}$ %is non-deterministic with 
+has known bounds $\overline{u}$ and $\underline{u}$, 
+such that ${\underline{u} \leq u_{k} \leq \overline{u}},\forall k\geq 0$.
+
 %%%-------------------------------
@@
 %%
-%%\todo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.} 
+%%\addtodo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.} 
 %%
-%%\todo{[The remainder of the section needs to be updated. ]}
+%%\addtodo{[The remainder of the section needs to be updated. ]}
 %%The output and measurable of the plant is being sampled by an ADC, and since the full state of the
@@
 %%is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  
-%%\todo{[Unclear what the remainder is for: ]}
+%%\addtodo{[Unclear what the remainder is for: ]}
 %%We further presume that there are small tolerances in the system 
@@
 
-% \todo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.}
-
-% \todo{[The remainder of the section needs to be updated. ]}
+% \addtodo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.}
+
+% \addtodo{[The remainder of the section needs to be updated. ]}
 % The output and measurable of the plant is being sampled by an ADC, and since the full state of the
@@
 % is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  
-% \todo{[Unclear what the remainder is for: ]}
+% \addtodo{[Unclear what the remainder is for: ]}
 
@@
 The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=(|\mat{K}|_1+1)c_m$
-
-%-------------------------------
-\subsection{Safety specifications for cyber-physical systems}
-\label{ssec:safety}
-%-------------------------------
-
-We require that the closed-loop system meets safety specifications. 
-A safety specification establishes bounds for the states, such that 
-the controller $K$ must maintain the states within a given lower and upper 
-bound for any initial state.
-
-The safety property represented by $\phi_{safety}$ is encoded as follows:
-%
-\begin{equation}
-\label{eq:safetyliteral}
-\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
-\end{equation}
-%
-%\todo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
-where $\underline{x_{i}}$ and $\overline{x_{i}}$ are the lower and upper bound 
-of the $i$-th state $x_{i}$ at the $k$-th instant, respectively.
-This means that the states will always be within the $n$-dimensional 
-hyper-box, which is typically defined by the safety specification.
-
-The states values must be computed considering the digital controller error, i.e., the error introduced by the ADC and
-digital controller, and the digital reference signal. In this paper, we consider systems with
-a reference signal equal to zero. 
-%the FWL effects in all operations related to the control action~\eqref{eq:controlaction} 
-%and disregarding it in the state equation~\eqref{eq:plant}.
-Thus, the states are computed using the following equations. We use $\mathcal{F}_{\langle I_c,F_c \rangle}$ to 
-to denote numbers represented with the precision of the digital controller. All other numbers
-are represented with the precision of our plant model:
-%
-\begin{align*}
-u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})) \\
-x_{k+1}&=Ax_{k}+Bu_{k}
-\end{align*}
-%\left\lbrace
-%\begin{array}{l}
-%u_{k}=\mathcal{F}_{\langle I,F \rangle}(r_{k}-\mathcal{F}_{\langle I,F \rangle}(\mathcal{F}_{\langle I,F \rangle}(K)\cdot\mathcal{F}_{\langle I,F \rangle}(x_{k})))\\
-%x_{k+1}=Ax_{k}+Bu_{k}
-%\end{array}\right.
-%\end{equation}
-
-The input $u_{k}$ %is non-deterministic with 
-has known bounds $\overline{u}$ and $\underline{u}$, 
-such that ${\underline{u} \leq u_{k} \leq \overline{u}},\forall k\geq 0$.
 
@@
 We consider non-deterministic initial states within a specified range
-and the reference signal to be 0 (\todo{refer to wherever this is explained initially}).
+and the reference signal to be 0 (\addtodo{refer to wherever this is explained initially}).
 Then, when mapping back to the notation used for describing the general architecture 
@@
 
-\todo{Revise: }
+\addtodo{Revise: }
 The first aproach finds a controller for an individual initial state and input with a bounded time horizon and generalizes to all states, inputs and time horizons (with a final verification loop that verifies the continuous system behaviour against the previously verified discrete system bisimulation).
@@
 
-\todo{Can we come up with some sort of figure that makes it easier to visualise
+\addtodo{Can we come up with some sort of figure that makes it easier to visualise
 the generalisation step in each approach?}
@@
 
-\todo{Move as much as possible from Sec~\ref{sec:cof_verification}
+\addtodo{Move as much as possible from Sec~\ref{sec:cof_verification}
 to the appendix (e.g. discussion on abstract acceleration). 
@@
 
- \todo{discuss the computation
+ \addtodo{discuss the computation
   of the completeness threshold}
@@
 ensures that the current sampling rate is large enough by using an 
-external checker (\todo{add more details here once we have them}).
+external checker (\addtodo{add more details here once we have them}).
 
@@
 \begin{align}
-\label{eq:ode}
 \dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
@@
 \begin{align}
-\label{eq:plant}
 \vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\

### 2017-01-21 cav2017/cav2017.tex
do something about numeric representaiton section

@@
 
-There are two sources of error due to numeric representation; the numeric error introduced by 
+The systems and models we consider have two sources of error due to numeric representation; the numeric error introduced by 
 the fixed point numbers used to model our plant, i.e, the plant dynamics $A_d$, $B_d$ and the states; 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\todo{this section is unclear and probably needs to move somewhere else as it is only relevant for the acceleration back end}
 Thus far we have presented a verification procedure for a digitalized plant in a continuous space (\emph{ie} the
-range of the quatizers is still $\mathbb{R}$. The next step we must reaize is that the controller 
+range of the quantizers is still $\mathbb{R}$. The next step we must realize is that the controller 
 exists in a digital program, hence its domain is $\mathbb{R}\langle I,F\rangle$.

### 2017-01-21 cav2017/cav2017.tex
Swapped the 2 sections on different approaches
This makes it more consistent with rest of paper that refers to “first
approach” being the unwinding of the state space and “second approach”
being the acceleration

@@
 %Abstractly-Refined
-
+In this section we outline the general architecture of the progam synthesizer used 
+in both approaches. We then detail the 2 methods of solution generalisation that we compare.
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{CEGIS with multi-staged verification}
+\label{sec:CEGIS-precision-incrementation}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+\begin{figure}[htb]
+{\scriptsize
+\centering
+%\resizebox{.8\textwidth}{!}
+{
+ \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
+},
+          row sep=.6cm, column sep=.9cm] {
+   \coordinate (aux1);
+   \& \coordinate (aux2);
+   \&;\\
+   \coordinate (aux3);
+   \& \coordinate (aux4);
+   \&;\\
+   \coordinate (aux5);
+   \& \coordinate (aux6);
+   \&;\\
+   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc 1.Synthesize}};
+   \&
+   complexnode/.pic={ 
+     \node[rectangle,draw,dotted,
+	minimum width=8cm,
+	minimum height=1cm,
+        pattern=north west lines, pattern color=gray!20,
+	label={\sc Verify},] (verif) {};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2.9cm]verif.center) {{\sc 2.Safety}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=-0.8cm]verif.center) {{\sc 3.Precision}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=1.2cm]verif.center) {{\sc 4.Complete}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc 5.Sampling}};
+   } 
+   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
+   \& \\
+   \node[minimum height=0cm] (gp) {\sf Closed-loop \\ System Search};
+   \&
+   complexnode/.pic={ 
+     \coordinate (aux);
+   \node (bmc) at ([xshift=-2.9cm]aux.center) {\sf BMC-based \\Verifier};
+   \node (fp)  at ([xshift=-.8cm]aux.center) {\sf Fixed-point \\ Arithmetic\\Verifier};
+   \node (sv)  at ([xshift=1.2cm]aux.center) {\sf Completeness\\Verifier};
+   \node (cv)  at ([xshift=3.1cm]aux.center) {\sf Sampling\\Verifier};
+   }   
+    \\
+  };
+
+   \path
+    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$P$} ([yshift=2em]verif1.west)
+    ([yshift=-2em]verif1.west) edge node {C-ex} ([yshift=-2em]synth.east)
+    ([xshift=-5em]fp.north) edge node[align=center]  {T/F} ([xshift=-5em]verif2.south)
+    ([xshift=-5em]sv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif3.south)
+    ([xshift=-5em]cv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif4.south)
+    ([xshift=5em]verif1.south) edge node[align=center] {$P$} ([xshift=5em]bmc.north)
+    ([xshift=5em]verif2.south) edge node[align=center] {$P$} ([xshift=5em]fp.north)
+    ([xshift=5em]verif3.south) edge node[align=center] {$P$} ([xshift=5em]sv.north)
+    ([xshift=5em]verif4.south) edge node[align=center] {$P$} ([xshift=5em]cv.north)
+    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
+    (verif) edge node {} (done)
+    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
+    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$P$} ([xshift=-5em]synth.south)
+    (aux1) edge (synth.north);
+   \path[-]
+   (verif2.north) edge node[align=center] {} ([xshift=-2.7cm]aux6)
+   ([xshift=-2.7cm]aux6) edge node[align=center] {Increase Precision} (aux5)
+   (verif3.north) edge node[align=center] {} ([xshift=4cm]aux4)
+   ([xshift=4cm]aux4) edge node[align=center] {Increase Completeness Threshold} (aux3)
+   (verif4.north) edge node[align=center] {} ([xshift=10.5cm]aux2)
+   ([xshift=10.5cm]aux2) edge node[align=center] {Increase Sampling Rate} (aux1);
+
+ \end{tikzpicture}
+}}
+\caption{CEGIS with multi-staged verification.}
+\label{fig:CEGIS-precision-increment}
+\end{figure}
+
+%\subsubsection{Controller synthesis}
+
+The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
+One important observation is that, for this approach, we verify and synthesise 
+a controller over $k$ time steps. We then compute a completeness threshold, $\overline{k}$,
+for this controller, and verify the controller's correctness to $\overline{k}$ time steps.
+Essentially, $\overline{k}$ represents the number of iterations 
+required to sufficiently unwind the closed-loop state-space system 
+such that the boundaries are not violated for any $k{>}\overline{k}$
+(i.e. it's sufficient to unwound the closed-loop state-space system up to  
+$\overline{k}$ in order to ensure that $\phi_{safety}$ holds).
+
+Next, we describe the different phases in Fig.~\ref{fig:CEGIS-precision-increment}
+(blocks 1 to 5):
+
+1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
+compute a candidate solution $K$. For this purpose, it assumes some
+precision $\langle I_p,F_p\rangle$ for the plant, a $k$ and a sampling rate.  The
+checks that these assumptions are sound are performed by subsequent
+{\sc verify} stages.
+
+2. The first {\sc verify} stage, {\sc safety}, checks that the candidate
+solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
+state within $k$ steps. 
+This check is potentially unsound because we consider the currently
+assumed $\langle I_p,F_p\rangle$, $k$ and sampling rate.
+
+3. The second {\sc verify} stage, {\sc precision}, 
+ restores soundness with respect to the plant's precision
+by using interval arithmetic \cite{moore1966interval} to validate the 
+operations performed by the previous stage.
+
+4. The third {\sc verify} stage, {\sc complete}, checks that the
+current $k$ is large enough to ensure that the boundaries are not
+violated for any $k'{>}k$.  For this purpose, we compute the
+completeness threshold $\overline{k}$ for the current candidate $K$
+and check that $k{\leq}\overline{k}$.
+
+A stable control system is known to have converging dynamics, i.e., the
+distance from the reference (in this case the origin) decreases over time.
+
+ \addtodo{discuss the computation
+  of the completeness threshold}
+
+5. The last {\sc verify} stage, {\sc sampling}, 
+ensures that the current sampling rate is large enough by using an 
+external checker (\addtodo{add more details here once we have them}).
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsection{CEGIS with abstraction refinement}
@@
 the safety specification.
-Our second model, rather than look at a direct bisimulation in discrete time, explores a much higher abstraction,
+Our second approach, rather than look at a direct bisimulation in discrete time, explores a much higher abstraction,
 evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specifcation.
@@
 \end{figure}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{CEGIS with multi-staged verification}
-\label{sec:CEGIS-precision-incrementation}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-\begin{figure}[htb]
-{\scriptsize
-\centering
-%\resizebox{.8\textwidth}{!}
-{
- \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
-},
-          row sep=.6cm, column sep=.9cm] {
-   \coordinate (aux1);
-   \& \coordinate (aux2);
-   \&;\\
-   \coordinate (aux3);
-   \& \coordinate (aux4);
-   \&;\\
-   \coordinate (aux5);
-   \& \coordinate (aux6);
-   \&;\\
-   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc 1.Synthesize}};
-   \&
-   complexnode/.pic={ 
-     \node[rectangle,draw,dotted,
-	minimum width=8cm,
-	minimum height=1cm,
-        pattern=north west lines, pattern color=gray!20,
-	label={\sc Verify},] (verif) {};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2.9cm]verif.center) {{\sc 2.Safety}};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=-0.8cm]verif.center) {{\sc 3.Precision}};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=1.2cm]verif.center) {{\sc 4.Complete}};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc 5.Sampling}};
-   } 
-   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
-   \& \\
-   \node[minimum height=0cm] (gp) {\sf Closed-loop \\ System Search};
-   \&
-   complexnode/.pic={ 
-     \coordinate (aux);
-   \node (bmc) at ([xshift=-2.9cm]aux.center) {\sf BMC-based \\Verifier};
-   \node (fp)  at ([xshift=-.8cm]aux.center) {\sf Fixed-point \\ Arithmetic\\Verifier};
-   \node (sv)  at ([xshift=1.2cm]aux.center) {\sf Completeness\\Verifier};
-   \node (cv)  at ([xshift=3.1cm]aux.center) {\sf Sampling\\Verifier};
-   }   
-    \\
-  };
-
-   \path
-    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$P$} ([yshift=2em]verif1.west)
-    ([yshift=-2em]verif1.west) edge node {C-ex} ([yshift=-2em]synth.east)
-    ([xshift=-5em]fp.north) edge node[align=center]  {T/F} ([xshift=-5em]verif2.south)
-    ([xshift=-5em]sv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif3.south)
-    ([xshift=-5em]cv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif4.south)
-    ([xshift=5em]verif1.south) edge node[align=center] {$P$} ([xshift=5em]bmc.north)
-    ([xshift=5em]verif2.south) edge node[align=center] {$P$} ([xshift=5em]fp.north)
-    ([xshift=5em]verif3.south) edge node[align=center] {$P$} ([xshift=5em]sv.north)
-    ([xshift=5em]verif4.south) edge node[align=center] {$P$} ([xshift=5em]cv.north)
-    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
-    (verif) edge node {} (done)
-    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
-    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$P$} ([xshift=-5em]synth.south)
-    (aux1) edge (synth.north);
-   \path[-]
-   (verif2.north) edge node[align=center] {} ([xshift=-2.7cm]aux6)
-   ([xshift=-2.7cm]aux6) edge node[align=center] {Increase Precision} (aux5)
-   (verif3.north) edge node[align=center] {} ([xshift=4cm]aux4)
-   ([xshift=4cm]aux4) edge node[align=center] {Increase Completeness Threshold} (aux3)
-   (verif4.north) edge node[align=center] {} ([xshift=10.5cm]aux2)
-   ([xshift=10.5cm]aux2) edge node[align=center] {Increase Sampling Rate} (aux1);
-
- \end{tikzpicture}
-}}
-\caption{CEGIS with multi-staged verification.}
-\label{fig:CEGIS-precision-increment}
-\end{figure}
-
-%\subsubsection{Controller synthesis}
-
-The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
-One important observation is that, for this approach, we verify and synthesise 
-a controller over $k$ time steps. We then compute a completeness threshold, $\overline{k}$,
-for this controller, and verify the controller's correctness to $\overline{k}$ time steps.
-Essentially, $\overline{k}$ represents the number of iterations 
-required to sufficiently unwind the closed-loop state-space system 
-such that the boundaries are not violated for any $k{>}\overline{k}$
-(i.e. it's sufficient to unwound the closed-loop state-space system up to  
-$\overline{k}$ in order to ensure that $\phi_{safety}$ holds).
-
-Next, we describe the different phases in Fig.~\ref{fig:CEGIS-precision-increment}
-(blocks 1 to 5):
-
-1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
-compute a candidate solution $K$. For this purpose, it assumes some
-precision $\langle I_p,F_p\rangle$ for the plant, a $k$ and a sampling rate.  The
-checks that these assumptions are sound are performed by subsequent
-{\sc verify} stages.
-
-2. The first {\sc verify} stage, {\sc safety}, checks that the candidate
-solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
-state within $k$ steps. 
-This check is potentially unsound because we consider the currently
-assumed $\langle I_p,F_p\rangle$, $k$ and sampling rate.
-
-3. The second {\sc verify} stage, {\sc precision}, 
- restores soundness with respect to the plant's precision
-by using interval arithmetic \cite{moore1966interval} to validate the 
-operations performed by the previous stage.
-
-4. The third {\sc verify} stage, {\sc complete}, checks that the
-current $k$ is large enough to ensure that the boundaries are not
-violated for any $k'{>}k$.  For this purpose, we compute the
-completeness threshold $\overline{k}$ for the current candidate $K$
-and check that $k{\leq}\overline{k}$.
-
-A stable control system is known to have converging dynamics, i.e., the
-distance from the reference (in this case the origin) decreases over time.
-
- \addtodo{discuss the computation
-  of the completeness threshold}
-
-5. The last {\sc verify} stage, {\sc sampling}, 
-ensures that the current sampling rate is large enough by using an 
-external checker (\addtodo{add more details here once we have them}).
 

### 2017-01-21 cav2017/cav2017.tex
Fixing spelling mistakes

@@
 further, if the above step fails, we loop back and invoke a CEGIS call 
-to seek alternative stabilising feedbacks, benefitting from the obtained counter-examples 
+to seek alternative stabilising feedbacks, benefiting from the obtained counter-examples 
 to safety. 
@@
 %specific to digital control, 
-such as the effects of finite-precision arithmetic, time discretisation, and quantisation noise, which are typically introduced 
-by Analog-to-Digital (A/D) and Digital-to-Analog (D/A) conversion.  
+such as the effects of finite-precision arithmetic, time discretization, and quantisation noise, which are typically introduced 
+by Analogue-to-Digital (A/D) and Digital-to-Analogue (D/A) conversion.  
 Whilst the research on digital control is well developed [Astrom book on digital control], 
@@
 attractive invariant sets as a mechanism to bound the quantization error effect
-on stabilization as an invariant set that always converges toward the cotrollable
+on stabilization as an invariant set that always converges toward the controllable
 set. In a similar fashion, \cite{liberzon2003hybrid} evaluates the dynamics of the
@@
 where $A$ and $B$ are matrices that fully specify the continuous plant with the initial states $x(0)$. 
-Eq.~\eqref{eq:ode} is soundly discretised (as shown in the Appendix) into
+Eq.~\eqref{eq:ode} is soundly discretized (as shown in the Appendix) into
 %
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-Given the large soloution space to be searched during the inductive
+Given the large solution space to be searched during the inductive
 synthesis phase, we parametrise the target language, which induces a
@@
 \item[1.] The first approach uses a multi-staged validation phase
-  and performes solution generalisation based on
+  and performs solution generalisation based on
 the plant's precision, the number of loop unrollings
@@
 \addtodo{Revise: }
-The first aproach finds a controller for an individual initial state and input with a bounded time horizon and generalizes to all states, inputs and time horizons (with a final verification loop that verifies the continuous system behaviour against the previously verified discrete system bisimulation).
+The first approach finds a controller for an individual initial state and input with a bounded time horizon and generalizes to all states, inputs and time horizons (with a final verification loop that verifies the continuous system behaviour against the previously verified discrete system bi-simulation).
 The second approach finds a controller for a continuous initial state-space and input sets over an abstraction of the continuous dynamics which conforms to witness proofs at specific times k, and generalizes the solution for all times by refining the number of witnesses.
@@
 the safety specification.
-Our second approach, rather than look at a direct bisimulation in discrete time, explores a much higher abstraction,
-evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specifcation.
+Our second approach, rather than look at a direct bi-simulation in discrete time, explores a much higher abstraction,
+evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specification.
 We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a
-single iteration, in addition to a stability specification defined by Jury's criteria, and try to synthesise a controller that meets these specs.
+single iteration, in addition to a stability specification defined by Jury's criteria, and try to synthesise a controller that meets these specifications.
 A second abstraction that encompasses the accelerated continuous reach-tube over an unbounded time is used to verify that the controller meets the full safety specification.
-If this step fails, we find a counterexmple iteration that causes the selected system to fail and create a new constraint to refine our abstraction.
+If this step fails, we find a counterexample iteration that causes the selected system to fail and create a new constraint to refine our abstraction.
 The advantage of this model is that it starts with a very simple description regardless of the complexity of the overall dynamics, and only expands to more complex models when a solution cannot be found.
@@
 
-The characteristic polynomial of the above matix is:
+The characteristic polynomial of the above matrix is:
 %
@@
 \end{remark}
- Since \eqref{eq:discretization} is a bisimulation of \eqref{eq:ode}, we may use the semantics in section \ref{sec:model_semantics} to model continuous dynamical systems.
+ Since \eqref{eq:discretization} is a bi-simulation of \eqref{eq:ode}, we may use the semantics in section \ref{sec:model_semantics} to model continuous dynamical systems.
 
@@
 During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathbb{R}\langle I_{adc},F_{adc} \rangle$ value.
-this sampling uses a threshold which is defined by the less significant bit ($q_{adc}=2^{-F_{adc}}$) of the adc and some nonlinearities of the circuitry.
+this sampling uses a threshold which is defined by the less significant bit ($q_{adc}=2^{-F_{adc}}$) of the ADC and some non-linearities of the circuitry.
 The overall conversion is
@@
 From the above equations we can now infer that $\nu_1 \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], \nu_2 \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{adc} \wedge q_2=q_{dac}$.
-Note that these bounds hold irrespective of whether the noise is correlated, hence we may use them to overapproximate the effect of the noise on the state space progression over time.
+Note that these bounds hold irrespective of whether the noise is correlated, hence we may use them to over-approximate the effect of the noise on the state space progression over time.
 The resulting dynamics are:

### 2017-01-21 cav2017/cav2017.tex
More refinements

@@
 
-The verification of a hybrid continuous/discrete time/space system over an unbounded time, requires the
+The verification of a hybrid continuous/discrete system over an unbounded time, requires the
 non-deterministic simulation of an infinite set of states, which is undecidable. Our initial approach creates an
-abstraction of this system by establishing bounds on the error between such a system and a discrete-time/space model.
+abstraction of this system by establishing bounds on the error between such a system and a discrete-time/continuous-space model.
 This model is still however, quite complex, hard to verify, and many of the states involved are inconsequential to
 the safety specification.
-Our second approach, rather than look at a direct bi-simulation in discrete time, explores a much higher abstraction,
-evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specification.
+Our second model, rather than look at a bisimulation in discrete time, explores a much higher abstraction,
+evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specifcation.
 We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a
-single iteration, in addition to a stability specification defined by Jury's criteria, and try to synthesise a controller that meets these specifications.
+single iteration, in addition to a stability specification defined by Jury's criteria, and try to synthesise a controller that meets these specs.
 A second abstraction that encompasses the accelerated continuous reach-tube over an unbounded time is used to verify that the controller meets the full safety specification.
-If this step fails, we find a counterexample iteration that causes the selected system to fail and create a new constraint to refine our abstraction.
+If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
 The advantage of this model is that it starts with a very simple description regardless of the complexity of the overall dynamics, and only expands to more complex models when a solution cannot be found.
@@
 \label{eq:observer_LTI_cf}
-\vec{x}_{k+1}=&\mat{A}_{t}\vec{x}_k+\mat{B}_{tp} \vec{r}_k+\mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]
+\vec{x}_{k+1}=&\mat{A}_{t}\vec{x}_k+\mat{B}_{tp} \vec{r}_k+\mat{B}_{tn} (\vec{\nu}_1 + \vec{\nu}_2 + \vec{\nu}_3)
 \end{align}
@@
 \begin{align*}
-\mat{A}_{t}=\mat{T}\mat{A}_d\mat{T}^{-1}&\left[
+\mat{A}_{t}=\mat{T}\mat{A}_d\mat{T}^{-1}=&\left[
 \begin{array}{ccccc}
@@
 
-For a stabilized closed-loop, we need these roots to remain within the
-unit circle (left hand side of the plane for continuous time).  Whilst
-this is not a sufficient condition for verifying safety properties, it
-is a necessary one; therefore, we review this verification process.  
-The direct approach would be to calculate the roots of the
-polynomials (\emph{i.e.}, the matrix eigenvalues), but this ends
-up being too costly, particularly in the case of synthesis, so we use
-an indirect method.
-
-Notice that in both our polynomials $c_0=1$ and we only use reals.
-Now that we have established convergence, we may examine the safety 
-specification of the state space. In the case of SISO systems, 
-this is given by a range of the input and a range of the output, 
-which are considered safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in [\underline{y}\ \ \overline{y}]$). 
+For a stabilized closed-loop, which is necessary for our safety property, we need
+these roots to remain within the unit circle, which we verify using Jury's criteria.
+Notice that in our polynomials $c_0=1$ and we only use reals.
+
+Once we have established convergence, we may examine the 
+specification of the state and input spaces ($\phi_{safety} \wedge \phi_{input}$).
 Whilst there are other properties, we may include in the verification, 
 we will solely focus on these for simplicity of the explanation.
-We will assume that we do not want saturation in our system, 
+We assume that we do not want saturation in our system, 
 hence the control loop has only one mode. We have also identified 
 the quantization noise as a bounded non-deterministic input.
-First we must translate the safety specification into the state-space. 
-Replacing on the second part of equation \eqref{eq:observer_LTI_cf} we obtain
-%
+%
+The first step constraints
 \begin{equation}
-\Psi := \underline{y}-\overline{\mat{B}\vec{u}}<\mat{C}_t\vec{x}_k<\overline{y}-\underline{\mat{B}\vec{u}}
+\mat{K} \models \vec{u}_k=-\mat{K}\vec{x}_k : \phi_{safety} \wedge \phi_{input}
 \label{eq:of_bounds}
 \end{equation}
-Note that we use the bounds of the input after the transformation by $\mat{B}$ 
-since the matrix may reverse the bounds. Eq.~\eqref{eq:of_bounds} can be solved 
-using linear programming as it describes a polyhedral region in $\mathbb{R}^n$.
-The second step is evaluating the progression of the system over time to calculate 
-$\vec{x}_k$ to validate against this specification. For this step we require 
+The second step is evaluating the progression of the system over time to evaluate 
+$\vec{x}_{k+1} \models \phi_{safety}$. For this step we require 
 an initial set from which the system progresses. Obviously, this set $\vec{x}_0$ 
@@
 +\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tp} \vec{r}_i
-+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right] : \mat{E}\mat{T} \vec{x}_0<\mat{f}
++\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tn}(\vec{\nu}_1+\vec{\nu}_2+\vec{\nu}_3) : \vec{x}_0 \models \phi_{init}
 \end{align}
@@
 =&\mathcal{A}_t X_0+\mathcal{B}_{tp} R + \mathcal{B}_{tn} N\\
-X_0 =&\left \{\vec{x} : \mat{E}\mat{T} \vec{x}_0<\mat{f} \right\}\nonumber\\
+X_0 =&\left \{\vec{x} : \vec{x} \models \phi_{init} \right\}\nonumber\\
  R =&\{r : \mat{E}_r < \vec{f}_r \}\nonumber\\
- N=&\left \{ \left[\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right] : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \right \}\nonumber
+ N=&\left \{ \vec{\nu}_1+\vec{\nu}_2+ \vec{\nu}_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber
 \end{align}
 %
-where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A}^k, \mathcal{B}_{tp}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tp}, \mathcal{B}_{tn}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tn}$ are abstract matrices for the system in \eqref{eq:observer_LTI_cf}.
-It is worth noting that $r$ is a non-deterministic parametric input (\emph{ie} $\forall k>0, r_{k+1} =r_k$) whereas the set N is composed of non-deterministic variable inputs.
+where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A}^k, \mathcal{B}_{tp}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tp}, \mathcal{B}_{tn}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tn}$ are abstract matrices for the system in \eqref{eq:observer_LTI_cf} and $r$ is a non-deterministic parametric input (\emph{ie} $\forall k>0, r_{k+1} =r_k$) whereas the set N is composed of non-deterministic variable inputs.
 

### 2017-01-21 cav2017/cav2017.tex
adding detail to first approach section

@@
 1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
-compute a candidate solution $K$. For this purpose, it assumes some
+compute a candidate solution $K$.
+
+We compute a candidate $K$, with the required controller precision $\langle I_c,F_c\rangle$, that satisfies both the stability criteria detailed in 
+section \todo{ref stability section}, and the safety specification in section \todo{ref for safety}.
+The stability criteria are satisfied if the characteristic polynomial of $A_d - B_d * K_d$ meets Jury's criteria. This is 
+independent of the initial states. 
+In order to synthesise a controller for satisfaction of the safety specification, we unwind the transition system
+$k$ steps, and pick a controller $K$ and an initial state such that the states at each step do not violate the safety criteria.
+
+We assumes some
 precision $\langle I_p,F_p\rangle$ for the plant, a $k$ and a sampling rate.  The
@@
 state within $k$ steps.
+
+The safety criteria here must be valid for all possible allowed initial states, and so we 
+unwind the transition system $k$ steps, using the previously synthesised $K$, and check that
+the state values at each step do not violate the safety bounds for any initial state.
+
+This is relatively computationally expensive if the bounds on the allowed initial states are large. 
+However, we can show that, if the controller is safe for each of the corner cases of our hypercube of allowed initial states, 
+it is safe for any initial state in the hypercube. Thus we only need to check $2^N$ initial states, where $N$ is the number 
+of states.
+
+\todo[inline]{ALESSANDRO: please write out proof that checking only the corner cases is valid for the safety verification}
+
 This check is potentially unsound because we consider the currently

### 2017-01-21 cav2017/cav2017.tex
Controller diagram

@@
 %
-\missingfigure{state feedback controller block diagram}
+\begin{figure*}[htb]
+\centering
+
+\tikzset{add/.style n args={4}{
+    minimum width=6mm,
+    path picture={
+        \draw[circle] 
+            (path picture bounding box.south east) -- (path picture bounding box.north west)
+            (path picture bounding box.south west) -- (path picture bounding box.north east);
+        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+        }
+    }
+ }
+
+\resizebox{1.0\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
+     semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
+    \node[draw=none] (r) {$r_k$};
+
+   \& \node[circle,add={-}{+}{}{}] (circle) {};
+   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$u_k$};
+   \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Kd) at ([xshift=0,yshift=-1.5cm]circle)  {\sc $\mat{K}_d$};
+   \coordinate (kdsouth) at ([yshift=-2cm]Kd);
+
+   \& complexnode/.pic={ 
+      \node[rectangle,dashed,draw,minimum width=3cm,minimum height=1.6cm,label=\textbf{DAC}] (dac) {};
+     \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
+     \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
+     \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
+     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {\sc ZOH};
+   }
+
+   \& complexnode/.pic={ 
+      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2.5cm,yshift=.5cm]plant.center)  {\sc $\mat{B}$};
+      \node[draw=none] (u) at ([xshift=-1cm,yshift=.15cm]B)  {$u(t)$};
+      \node[circle,add={+}{+}{}{}] (p1) at ([xshift=-1.3cm,yshift=.5cm]plant.center) {};
+      \node[draw=none] (xdot) at ([xshift=.85cm,yshift=.15cm]p1)  {$\dot{\vec{x}}(t)$};   
+      \node[rectangle,draw,minimum width=1cm] (int) at ([xshift=.5cm,yshift=.5cm]plant.center) {\sc $\int$};
+      \coordinate (xsouth) at ([xshift=1cm]int);
+      \node[draw=none] (x) at ([xshift=1cm,yshift=.15cm]int)  {$\vec{x}(t)$};
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (A) at ([xshift=.5cm,yshift=-1cm]plant.center)  {\sc $\mat{A}$};
+      \coordinate (aeast) at ([xshift=1cm]A);
+      \coordinate (awest) at ([xshift=-1.8cm]A);
+    }
+
+   \& complexnode/.pic={ 
+     \node[rectangle,dashed,draw,minimum width=3.5cm,minimum height=1.6cm,label=\textbf{ADC},] (adc) {};
+     \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
+     \coordinate (switch1) at ([xshift=-1cm]adc.center);
+     \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
+     \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
+     \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
+     \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
+     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]q1)  {$\vec{x}_k$};       
+     \coordinate (ykeast) at ([xshift=1.9cm]q1);
+     \coordinate (yksouth) at ([xshift=1.9cm,yshift=-3.5cm]q1);
+   } 
+   \& \coordinate (aux1);
+   \& \\
+  };
+
+  \path[->] (v1) edge (q1.south);
+  \path[->] (v2) edge (q2.south);
+  \path[->] (r) edge (circle.west);
+  \path[->] (circle.east) edge (q2.west);
+  \path       (q2.east) edge (zoh.west);
+  \path[->] (zoh.east) edge (B.west);
+  \path
+   (B.east) edge (p1.west)
+   (p1.east) edge (int.west)
+   (xsouth) edge (aeast)
+   (aeast) edge (A.east)
+   (A.west) edge (awest)
+   (awest) edge (p1.south)
+   (int.east) edge (switch1.west)
+   (switch2) edge (q1.west);
+  \path
+   (q1.east) edge (ykeast)
+   (ykeast) edge (yksouth)
+   (yksouth) edge (kdsouth);
+  \path[->]  (kdsouth) edge (Kd.south);
+  \path (Kd.north) edge (circle.south);
+ \end{tikzpicture}
+}
+ \caption{Closed-loop digital control system \label{fig:digitalsystem}}
+\end{figure*}
 %-------------------------------

### 2017-01-21 cav2017/cav2017.tex
completeness threshold goes here?
adding pseudocode

@@
 \usepackage{listings}
+\usepackage{algorithm,algpseudocode}
 
@@
 $k$ steps, and pick a controller $K$ and an initial state such that the states at each step do not violate the safety criteria. 
+The unwinding calculation includes the conversion from plant precision to the fixed point controller precision.
 
@@
 
+\begin{algorithm}[]
+\begin{algorithmic}[1]
+\Function{$safetyCheck()$}{}
+	\State assert($ \underline{u}  \leq u \leq \overline{u}$)
+	\While{$i=0; i< k; i++$}
+		%\State $u = (\langle I_p,F_p\rangle)((\langle I_c,F_c\rangle)K * (\langle I_c,F_c\rangle) x)$
+		\State $u = (plant\_typet)((controller\_typet)K * (controller\_typet) x)$
+		\State $x = A * x + B * u$
+		\State assert($\underline{x} \leq x \leq \overline{x}$ )
+  	\EndWhile
+  %\State Return $K$
+\EndFunction
+\end{algorithmic}
+\label{alg:safetycheck}
+\end{algorithm}
+
 2. The first {\sc verify} stage, {\sc safety}, checks that the candidate
@@
 
-\todo[inline]{ALESSANDRO: please write out proof that checking only the corner cases is valid for the safety verification}
+\todo[inline]{Alessandro: please write out proof that checking only the corner cases is valid for the safety verification}
 
@@
 
- \addtodo{discuss the computation
-  of the completeness threshold}
+\todo[inline]{Alessandro: please can we have the proof for the completeness threshold here}
+\missingfigure{picture for completeness threshold}
 

### 2017-01-21 cav2017/cav2017.tex
edited first approach

@@
 \subsection{Stability of closed-loop systems}
-\label{sec:stability}
+\label{ssec:stability}
 %-------------------------------
@@
 1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
-compute a candidate solution $K$.
-
-We compute a candidate $K$, with the required controller precision $\langle I_c,F_c\rangle$, that satisfies both the stability criteria detailed in 
-section \todo{ref stability section}, and the safety specification in section \todo{ref for safety}.
-The stability criteria are satisfied if the characteristic polynomial of $A_d - B_d * K_d$ meets Jury's criteria. This is 
-independent of the initial states. 
-In order to synthesise a controller for satisfaction of the safety specification, we unwind the transition system
-$k$ steps, and pick a controller $K$ and an initial state such that the states at each step do not violate the safety criteria. 
-The unwinding calculation includes the conversion from plant precision to the fixed point controller precision.
-
-We assumes some
-precision $\langle I_p,F_p\rangle$ for the plant, a $k$ and a sampling rate.  The
-checks that these assumptions are sound are performed by subsequent
+compute a candidate solution $K$
+that satisfies both the stability criteria detailed in 
+Sec.~\ref{ssec:stability} and the safety specification in Sec.~\ref{ssec:safety}.
+%% The stability criteria are satisfied if the characteristic polynomial of $A_d - B_d * K_d$ meets Jury's criteria. This is 
+%% independent of the initial states. 
+Regarding the latter, we synthesise a safe controller by unwinding the transition system
+$k$ steps and picking a controller $K$ and an initial state such that the states at each step do
+not violate the safety criteria. This is sound if the current $k$ is below the
+completeness threshold, which we assume to be true in the {\sc synthesize} phase.
+We also assume some
+precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  The
+checks that all these assumptions are sound are performed by subsequent
 {\sc verify} stages.
@@
 solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
-state within $k$ steps.
-
-The safety criteria here must be valid for all possible allowed initial states, and so we 
-unwind the transition system $k$ steps, using the previously synthesised $K$, and check that
-the state values at each step do not violate the safety bounds for any initial state.
-
-This is relatively computationally expensive if the bounds on the allowed initial states are large. 
-However, we can show that, if the controller is safe for each of the corner cases of our hypercube of allowed initial states, 
-it is safe for any initial state in the hypercube. Thus we only need to check $2^N$ initial states, where $N$ is the number 
-of states.
+state within $k$ steps where again we assume $k$ to be under the completeness threshold. 
+%The safety criteria here must be valid for all possible allowed initial states, and so we
+After unwinding the transition system corresponding to the previously synthesised controller
+$k$ steps, we check that the safety specification holds for any initial state.
+
+This is relatively computationally expensive if the bounds on the
+allowed initial states are large.  However, we can show that, if the
+controller is safe for each of the corner cases of our hypercube of
+allowed initial states, it is safe for any initial state in the
+hypercube. Thus we only need to check $2^N$ initial states, where $N$
+is the number of states.
 
 \todo[inline]{Alessandro: please write out proof that checking only the corner cases is valid for the safety verification}
-
-This check is potentially unsound because we consider the currently
-assumed $\langle I_p,F_p\rangle$, $k$ and sampling rate.
 

### 2017-01-21 cav2017/cav2017.tex
clearer todo notes

@@
 
-\todo[inline]{Alessandro: please write out proof that checking only the corner cases is valid for the safety verification}
+\todo[inline]{please will Alessandro write out the proof that checking only the corner cases is valid for the safety verification - EP}
 
@@
 
-\todo[inline]{Alessandro: please can we have the proof for the completeness threshold here}
+\todo[inline] {please will Alessandro write the proof for the completeness threshold here - EP}
 \missingfigure{picture for completeness threshold}

### 2017-01-21 cav2017/cav2017.tex
edited sec 4.3 (on solution generalization)

@@
 \begin{itemize}
-\item[1.] The first approach uses a multi-staged validation phase
-  and performs solution generalisation based on
+\item[1.] The first approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
+  uses a multi-staged validation phase and performs solution generalisation based on
 the plant's precision, the number of loop unrollings
-and the sampling rate (see Sec.~\ref{sec:CEGIS-precision-incrementation}).
-\item[2.] The second approach uses abstract acceleration to compute the set of reachable states,
-  which enables it to perform abstraction refinement inside the CEGIS loop (see Sec~\ref{sec:CEGIS-abstraction-refinement}).
-
+and the sampling rate. Essentially, it finds a controller for an individual initial state
+and input with a bounded time horizon and generalizes to all states,
+inputs and time horizons. %% (with a final verification loop that verifies
+%% the continuous system behaviour against the previously verified
+%% discrete system bi-simulation)
+\item[2.] The second approach described in Sec~\ref{sec:CEGIS-abstraction-refinement}
+  %% uses abstract acceleration to compute the set of reachable states,
+  %% which enables it to perform abstraction refinement inside the CEGIS loop.
+  finds a controller for a continuous initial
+state-space and input sets over an abstraction of the continuous
+dynamics which conforms to witness proofs at specific times, and
+generalizes the solution for all times by refining the number of
+witnesses.
 \end{itemize}
-
-\addtodo{Revise: }
-The first approach finds a controller for an individual initial state and input with a bounded time horizon and generalizes to all states, inputs and time horizons (with a final verification loop that verifies the continuous system behaviour against the previously verified discrete system bi-simulation).
-The second approach finds a controller for a continuous initial state-space and input sets over an abstraction of the continuous dynamics which conforms to witness proofs at specific times k, and generalizes the solution for all times by refining the number of witnesses.
 
@@
 
-\addtodo{Can we come up with some sort of figure that makes it easier to visualise
-the generalisation step in each approach?}
+%% \addtodo{Can we come up with some sort of figure that makes it easier to visualise
+%% the generalisation step in each approach?}
 

### 2017-01-21 cav2017/cav2017.tex
use lower case consistently for precision underscript

@@
 $(x_0, u_k)$ represents $x$. 
-While the controller's precision $\langle I_C,F_C\rangle$ is given, 
+While the controller's precision $\langle I_c,F_c\rangle$ is given, 
 we can vary the plant's precision $\langle I_p,F_p\rangle$ such that 

### 2017-01-21 cav2017/cav2017.tex
Built executable

@@
 These are the rows of $\mat{E} \in \Psi$ that intersect/segment $\hat{X}^\#$.
-Transforming these rows into the eigenspace of $\mat{A}_t$, and applying backward acceleration to obtain a set of counterexamples for the eigenvalues, which we define as $\Psi(\Lambda)$.
+Transforming these rows into the eigenspace of $\mat{A}_t$, and applying backward acceleration to obtain a set of counterexamples for the eigenvalues, which we define as $\phi(\Lambda)$.
 This is a constraint in the spectrum (\emph{ie} frequency response transfer function) of the closed loop dynamics.
 \item Transform the soft constraints on the spectrum into soft constraints on the coefficients of the characteristic polynomial. 
-$z^n+\sum_{i=1}^n[a_i-k_i]z^{n-i}=\prod_{i=1}^n (z-[\lambda_i]) : |[\lambda_i]|<1 \wedge [\lambda_i] \models \Psi_{\Lambda}$.
+$z^n+\sum_{i=1}^n[a_i-k_i]z^{n-i}=\prod_{i=1}^n (z-[\lambda_i]) : |[\lambda_i]|<1 \wedge [\lambda_i] \models \phi_{\Lambda}$.
 \item Pass the refined abstraction with the new contraints to the synthesiser, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again.
@@
      \node[draw,rectangle,align=center] (KSAT) at ([xshift=-.8cm]auxsynth.center) {\sc Prog.\\Search};
-     \node[draw,rectangle,align=center] (LSAT) at ([xshift=.8cm]auxsynth.center) {\sc Prog.\\Search};
      \node[draw=none] (SATK) at ([xshift=-.5cm,yshift=1.5cm]KSAT)  {$\mathcal{J}_K$};
      \node[draw=none] (K) at ([xshift=.4cm,yshift=1.5cm]KSAT)  {$\tilde{\mat{K}}$};
-     \node[draw=none] (SATL) at ([xshift=-.5cm,yshift=1.5cm]LSAT)  {$\mathcal{J}_L$};
-     \node[draw=none] (L) at ([xshift=.4cm,yshift=1.5cm]LSAT)  {$\tilde{\mat{L}}$};
     }
@@
      \coordinate (KUNSAT)  at ([xshift=-.8cm]UNSAT.center);
-     \coordinate (LUNSAT) at ([xshift=.8cm]UNSAT.center);
      \node[draw=none] (UNSATB) at ([xshift=1.6cm,yshift=.3cm]UNSAT)  {\sc UNSAT};
@@
     ([xshift=-3.3cm]synth.south) edge ([xshift=-.6cm]KSAT.north)
-    ([xshift=.6cm]LSAT.north) edge ([xshift=3.3cm]synth.south)
-    ([xshift=+2.1cm]synth.south) edge ([xshift=-.6cm]LSAT.north)
     ([xshift=-4.9cm]verify.south) edge (AAI.north)
@@
      (KSAT.south) edge (KUNSAT.north)
-     (LSAT.south) edge (LUNSAT.north)
-     (KUNSAT.east) edge (LUNSAT.west)
-     (verify.north) edge node {$\Psi (\mat{K})$} (aux)
-     (LUNSAT.east) edge (FAIL.west);
+     (KUNSAT.east) edge (FAIL.west)
+     (verify.north) edge node {$\Psi (\mat{K})$} (aux);
 \end{tikzpicture}

### 2017-01-22 cav2017/cav2017.tex
text

@@
 
-We consider physical models expressed as ordinary differential equations (ODEs) with full state information:  
+We consider models of physical plants expressed as ordinary differential equations (ODEs), 
+with full state information (namely where we have access to all the model variables):  
 %
@@
 \label{eq:ode}
-\dot{x}(t) = Ax(t)+ B u(t)\ \ :\ \ x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}
+\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}, 
 \end{align}
-where $A$ and $B$ are matrices that fully specify the continuous plant with the initial states $x(0)$. 
-Eq.~\eqref{eq:ode} is soundly discretized (as shown in the Appendix) into
+where $t \in \mathbb R_0^+$, 
+where $A$ and $B$ are matrices that fully specify the continuous plant, 
+and with initial states set as $x(0)$. 
+Eq.~\eqref{eq:ode} is soundly discretised in time (as shown in the Appendix) into
 %
@@
 \end{align} 
-with initial state $x_{0}=x(0)$.
+where $k \in \mathbb N$, 
+and with initial state $x_{0}=x(0)$.
 
@@
 Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
-Feedback can be employed to affect the properties and behaviours of the process. 
+Feedback architectures can be employed to affect the properties and behaviours of the continuous process (the plant) of interest.   
 %reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
+We are interested in the synthesis of digital feedback, 
+as implemented on modern FPGAs or ICs. 
 The most basic feedback architecture is the state feedback, 
-where the control action $\vec{u}_k$ is computed by: 
+where the control action $u_k$ (notice we work with the discretised signal) is computed by: 
 %
@@
 \label{eq:controlaction}
-u_k = r_{k} - K x_k, 
+u_k = r_{k} - K x_k. 
 \end{equation}
 %
-where $K \in \mathbb{R}^{m \times n}$ is a feedback gain matrix, 
-and $r_{k}$ is a reference signal.   
+Here $K \in \mathbb{R}^{m \times n}$ is a feedback gain matrix, 
+and $r_{k}$ is a reference signal (again digital).   
 %
@@
 \end{align}
-The gain matrix $K$ can be set so that the closed-loop dynamics are shaped as desired, 
-according to a desired goal or objective. 
-A standard objective is to obtain stable closed-loop dynamics.
+The gain matrix $K$ can be set so that the closed-loop digitalised dynamics are shaped as desired, 
+for instance according to a specific stability goal or around a specific dynamical behaviour \cite{astrom1997computer}. 
+As argued later, in this work, we will target more complex objectives, such as quantitative safety requirements that are not typical in the digital control literature.
 

### 2017-01-22 cav2017/cav2017.tex
text

@@
 and with initial state $x_{0}=x(0)$. 
+Later, we will deal with the issue of variable quantisation, as introduced by the ADC and DAC blocks.
 
@@
 
-A discrete-time system is asymptotically stable if and only if all the roots 
-of the characteristic polynomial ({\it i.e.}, the eigenvalues) are inside of 
-the unity circle, {\it i.e.}, their absolute value are less than 
-one~\cite{astrom1997computer}. In this paper, we express 
-the stability specification $\phi_{stability}$ in terms of  
-Jury's criterion \cite{fadali}. A detailed description of this 
-specification can be found in the Appendix~\ref{sec:appendix-stability}.
-
-%-------------------------------
-\subsection{Safety specifications for cyber-physical systems}
+A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable if and only if all the roots 
+of the characteristic polynomial ({\it i.e.}, the eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity circle in the complex plane, 
+{\it i.e.} iff their absolute value are less than one~\cite{astrom1997computer}. 
+In this paper, we express the stability specification $\phi_{stability}$ in terms of a check known as Jury's criterion \cite{fadali}. 
+This condition boils down to an easy algebraic formula to select the entries of matrix $K$, 
+so that the closed-loop dynamics are shaped as desired. 
+A detailed description of this specification can be found in the Appendix~\ref{sec:appendix-stability}.
+
+%-------------------------------
+\subsection{Safety specifications for dynamical systems}
 \label{ssec:safety}
@@
 
-We also require that the closed-loop system meets safety specifications. 
+As mentioned earlier, 
+in this work we are not bound to the synthesis of digital stabilising controllers -- 
+a well known task in the literature on digital control system -- 
+but target safety requirements with an overall approach that is sound and automated. 
+More specifically, 
+we require that the closed-loop system \eqref{eq:closedloopss} meets given safety specifications. 
 A safety specification establishes bounds for the states, such that 

### 2017-01-22 cav2017/cav2017.tex
text

@@
 
+Asymptotic stability boils down to Lyapunov stability and convergence to an equilibrium point \todo{add reference}.  
+Lyapunov stability requires that model trajectories remain in a neighbourhood of the equilibrium point. 
+In the case of closed-loop LTI models as in \eqref{eq:closedloopss}, 
+the equilibrium point is the origin (if the reference is equal to zero), or an offset thereof.
+
 A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable if and only if all the roots 
@@
 we require that the closed-loop system \eqref{eq:closedloopss} meets given safety specifications. 
-A safety specification establishes bounds for the states, such that 
-the controller $K$ must maintain the states within a given lower and upper 
-bound for any initial state. Note that a stable system is not necessarily a
-safe system, the state values may leave the safe states during the stabilization.
-
-The safety property represented by $\phi_{safety}$ is encoded as follows:
+A safety specification raises a requirement on the states of the model, 
+such that the feedback controller (namely the choice of the gains in $K$) 
+must ensure that the states never exist such requirement. 
+Note that a stable, closed-loop system is not necessarily a safe system: 
+indeed, the state values may leave the safe whilst they converge to the equilibrium, 
+which is typical in the case of oscillatory dynamics.
+
+In this work, the safety property represented by $\phi_{safety}$ is encoded as follows: 
 %
@@
 %\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
-where $\underline{x_{i}}$ and $\overline{x_{i}}$ are the lower and upper bound 
-of the $i$-th state $x_{i}$ at the $k$-th instant, respectively.
-This means that the states will always be within the $n$-dimensional 
-hyper-box, which is typically defined by the safety specification.
+where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th instant, respectively. 
+This means that the states will always be within the $n$-dimensional hyper-box. 
+%, which is typically defined by the safety specification.
+
+Furthermore, 
+it is practically relevant to consider constraints on the input signal $u_{k}$, 
+which we assume has given bounds $\overline{u}$ and $\underline{u}$, 
+such that ${\underline{u} \leq u_{k} \leq \overline{u}},\forall k\geq 0$.  
+In practice, 
+this means that the control input saturates in view of physical constraints.
 
@@
 %\end{equation}
-
-The input $u_{k}$ %is non-deterministic with 
-has known bounds $\overline{u}$ and $\underline{u}$, 
-such that ${\underline{u} \leq u_{k} \leq \overline{u}},\forall k\geq 0$.
 

### 2017-01-22 cav2017/cav2017.tex
text

@@
 the equilibrium point is the origin (if the reference is equal to zero), or an offset thereof.  
+In this paper, we consider systems with a reference signal equal to zero.
 
@@
 this means that the control input saturates in view of physical constraints.
-
-The states values must be computed considering the digital controller error, i.e., the error introduced by the ADC and
-digital controller, and the digital reference signal. In this paper, we consider systems with
-a reference signal equal to zero. 
-%the FWL effects in all operations related to the control action~\eqref{eq:controlaction} 
-%and disregarding it in the state equation~\eqref{eq:plant}.
-Thus, the states are computed using the following equations. We use $\mathcal{F}_{\langle I_c,F_c \rangle}$ to 
-to denote numbers represented with the precision of the digital controller. All other numbers
-are represented with the precision of our plant model:
-%
-\begin{align*}
-u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})) \\
-x_{k+1}&=Ax_{k}+Bu_{k}
-\end{align*}
-%\left\lbrace
-%\begin{array}{l}
-%u_{k}=\mathcal{F}_{\langle I,F \rangle}(r_{k}-\mathcal{F}_{\langle I,F \rangle}(\mathcal{F}_{\langle I,F \rangle}(K)\cdot\mathcal{F}_{\langle I,F \rangle}(x_{k})))\\
-%x_{k+1}=Ax_{k}+Bu_{k}
-%\end{array}\right.
-%\end{equation}
 
@@
 
-The systems and models we consider have two sources of error due to numeric representation; the numeric error introduced by 
-the fixed point numbers used to model our plant, i.e, the plant dynamics $A_d$, $B_d$ and the states; 
-and the numeric error introduced by the digital controller, which uses an analogue-to-digital converter to read
-the states as a fixed-point number and performs operations in this domain. In this section we formally outline the errors introduced by
-fixed point representation of numbers; in further sections we will differentiate between these
-two errors by referring to them as the \emph{plant error} and the \emph{digital controller error}.
-
-Let $\mathbb{R} \langle I,F \rangle$ be a fixed point domain with $I$ bits representing the integer part and $F$ bits
+\todo{I've moved the following paragraph to this section, from that on safety specs.}
+The states values must be computed considering the digital controller error, i.e., the error introduced by the ADC and the digital controller. 
+%, and the digital reference signal. 
+%In this paper, we consider systems with a reference signal equal to zero. 
+%the FWL effects in all operations related to the control action~\eqref{eq:controlaction} 
+%and disregarding it in the state equation~\eqref{eq:plant}.
+Thus, the states are computed using the following equations. We use $\mathcal{F}_{\langle I_c,F_c \rangle}$ \todo{explain and clarify notation.}
+to to denote numbers represented with the precision of the digital controller. All other numbers
+are represented with the precision of our plant model:
+%
+\begin{align*}
+u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  
+%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
+\end{align*}
+%\left\lbrace
+%\begin{array}{l}
+%u_{k}=\mathcal{F}_{\langle I,F \rangle}(r_{k}-\mathcal{F}_{\langle I,F \rangle}(\mathcal{F}_{\langle I,F \rangle}(K)\cdot\mathcal{F}_{\langle I,F \rangle}(x_{k})))\\
+%x_{k+1}=Ax_{k}+Bu_{k}
+%\end{array}\right.
+%\end{equation}
+
+\bigskip
+
+The 
+%systems and 
+models we consider have two sources of error due to numeric representation. 
+The first is the numeric error introduced by the fixed-point numbers employed to model the plant, i.e. to represent the plant dynamics $A_d$, $B_d$ and its states. 
+The second is the numeric error introduced by the digital controller, 
+which 
+%uses an analogue-to-digital converter to read the states as a fixed-point number and performs operations in this domain. 
+performs operations in the domain of fixed-point numbers. 
+In this section we formally outline the errors introduced by fixed-point representation of numbers. 
+In further sections we will differentiate between these two errors, 
+by referring to them as the \emph{plant error} and the \emph{digital controller error} respectively.
+
+Let $\mathbb{R} \langle I,F \rangle$ \todo{notice this notation differs from the one used above} be a fixed point domain with $I$ bits representing the integer part and $F$ bits
 representing the decimal part. The smallest number that can be represented in this domain is $c_m=2^{-F}$.

### 2017-01-22 cav2017/cav2017.tex
text

@@
 
-Let $\mathbb{R} \langle I,F \rangle$ \todo{notice this notation differs from the one used above} be a fixed point domain with $I$ bits representing the integer part and $F$ bits
-representing the decimal part. The smallest number that can be represented in this domain is $c_m=2^{-F}$.
+Let $\mathbb{R} \langle I,F \rangle$ \todo{notice this notation differs from the one used above} be a fixed point domain with $I$ bits representing the integer part 
+and $F$ bits representing the decimal part \todo{why R, comment on that.}. The smallest number that can be represented in this domain is $c_m=2^{-F}$.
 The following approximation errors will arise:
@@
 \item {\bf Truncation:}
-Let $\mathcal{F}\langle I,F \rangle(\cdot) : \mathbb{R} \rightarrow \mathbb{R}\langle I,F \rangle, \tilde x=\mathcal{F}\langle I,F \rangle(x) = x-\delta_T : \delta_T=x\ \%_{c_m}\ \tilde x$, where $\%_{c_m}$ is the modulus operation performed wrt the last bit.
-$\delta_T$ is the truncation error and it will propagate across operations.
+Let $\mathcal{F}\langle I,F \rangle(\cdot) : \mathbb{R} \rightarrow \mathbb{R}\langle I,F \rangle, \tilde x=\mathcal{F}\langle I,F \rangle(x) = x-\delta_T : \delta_T=x\ \%_{c_m}\ \tilde x$, where $\%_{c_m}$ is the modulus operation performed on the last bit.
+So $\delta_T$ is the truncation error and it will propagate across operations.
 \item {\bf Rounding:}
@@
 \begin{enumerate}
-\item Addition/Substraction: these operations only propagate errors coming from truncation of the operands.
+\item Addition/Subtraction: these operations only propagate errors coming from truncation of the operands. 
+\todo{the following maths is loose. fix as follows: define terms with their domain. define operation. apply operator $\mathcal{F}$ above. derive bound. }
 $c_1\pm c_2= c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$ 
-\item Multiplication: $c_1 * c_2= c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}*c_2| + |\delta_{T2}*c_1| + c_m$ 
-\item Division will not be applied in these implementations.
+\item Multiplication: $c_1 * c_2= c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}*c_2| + |\delta_{T2}*c_1| + c_m$  \todo{same as above.}
+\item Division will not be applied in these implementations. \todo{why not? comment further.}
 \end{enumerate}
@@
   The finite word length set a
-maximum representable number in the domain ($\pm (2^{I-1}+1-2^{-F})$), which means that any number outside this range
+maximum representable number in the domain \todo{what is next?
+a domain?
+define formally, no back-of-the-envelope mathsy stuff.} ($\pm (2^{I-1}+1-2^{-F})$), which means that any number outside this range
 cannot be represented by the domain. Our tool currently assumes no saturation

### 2017-01-22 cav2017/cav2017.tex
text

@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Fixed word length effects on matrix multiplications}
-\label{sec:cof_fwl}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%\subsection{Fixed word length effects on matrix multiplications}
+%\label{sec:cof_fwl}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
 \todo{this section is unclear and probably needs to move somewhere else as it is only relevant for the acceleration back end} 
-Thus far we have presented a verification procedure for a digitalized plant in a continuous space (\emph{ie} the
-range of the quantizers is still $\mathbb{R}$. The next step we must realize is that the controller 
+\todo{yes, please reformat the discussion below so that it fits the discussion above. }
+
+Thus far we have presented a verification procedure for a digitalised plant in a continuous space (\emph{ie} the
+range of the quantisers is still $\mathbb{R}$. The next step we must realise is that the controller 
 exists in a digital program, hence its domain is $\mathbb{R}\langle I,F\rangle$.
@@
 the fixed word restrictions in their composing elements.
-Apart from the quantization errors $q_1,q_2$ there are rounding errors in the calculation of $u_k$.
-These will introduce a new source of quantization noise which we may denote $\vec{\nu}_3 \in [-q_3\ \ q_3]$.
+Apart from the quantisation errors $q_1,q_2$ there are rounding errors in the calculation of $u_k$. 
+These will introduce a new source of quantisation noise which we may denote $\vec{\nu}_3 \in [-q_3\ \ q_3]$.
 The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=(|\mat{K}|_1+1)c_m$
@@
 $\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
-$\vec{P}$ ranges over functions, $\vec{x}$ ranges over ground terms and
+$\vec{P}$ ranges over functions, $\vec{x}$ \todo{now variables are vectorised, however previously the model variables aren't.
+please align notation.
+I do not like to use vectors unless essential, let's say it's a waste of ink in printouts.
+} ranges over ground terms and
 $\sigma$ is a quantifier-free formula.  We interpret the ground terms over
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Our synthesis problem}
+\subsection{Synthesis problem: statement}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-01-22 cav2017/cav2017.tex
text

@@
 %Abstractly-Refined
-In this section we outline the general architecture of the progam synthesizer used 
-in both approaches. We then detail the 2 methods of solution generalisation that we compare.
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{General architecture of the program synthesizer}
+In this section we outline the general architecture of the program synthesiser used in both approaches\todo{which approaches?}. 
+We then detail the two methods of solution generalisation that we compare.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{General architecture of the program synthesiser}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Synthesis problem: statement}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Synthesis problem: statement (recap) and connection to program synthesis}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+\todo{The following paragraph has been already stated above. Let us clarify this is a useful repetition to recap things?}
+
 The synthesis problem we are trying to solve is the following:
@@
 We consider non-deterministic initial states within a specified range
-and the reference signal to be 0 (\addtodo{refer to wherever this is explained initially}).
-Then, when mapping back to the notation used for describing the general architecture 
-of the program synthesizer, the controller $K$ denotes $P$ and 
+and the reference signal to be set to zero.
+
+When mapping back to the notation used for describing the general architecture 
+of the program synthesiser, the controller $K$ denotes $P$ and 
 $(x_0, u_k)$ represents $x$. 
@@
 \begin{itemize}
-\item[1.] The first approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
-  uses a multi-staged validation phase and performs solution generalisation based on
-the plant's precision, the number of loop unrollings
+\item[1.] The first approach (described in Sec.~\ref{sec:CEGIS-precision-incrementation})
+  uses a multi-staged verification phase and performs solution generalisation based on
+the plant precision, the number of loop unrollings, 
 and the sampling rate. Essentially, it finds a controller for an individual initial state
-and input with a bounded time horizon and generalizes to all states,
-inputs and time horizons. %% (with a final verification loop that verifies
+and input with a bounded time horizon and generalises to all states,
+inputs, and time horizons. %% (with a final verification loop that verifies
 %% the continuous system behaviour against the previously verified
 %% discrete system bi-simulation)
-\item[2.] The second approach described in Sec~\ref{sec:CEGIS-abstraction-refinement}
+\item[2.] The second approach (described in Sec~\ref{sec:CEGIS-abstraction-refinement})
   %% uses abstract acceleration to compute the set of reachable states,
   %% which enables it to perform abstraction refinement inside the CEGIS loop.
-  finds a controller for a continuous initial
-state-space and input sets over an abstraction of the continuous
-dynamics which conforms to witness proofs at specific times, and
-generalizes the solution for all times by refining the number of
-witnesses.
+  finds a controller for a continuous initial set of states and input set, 
+  over an abstraction of the continuous dynamics that conforms to witness proofs at specific times; 
+  it further generalises the solution over all times by refining the number of witnesses. 
 \end{itemize}
@@
 }}
-\caption{CEGIS with multi-staged verification.}
+\caption{CEGIS with multi-staged verification}
 \label{fig:CEGIS-precision-increment}
@@
 a controller over $k$ time steps. We then compute a completeness threshold, $\overline{k}$,
-for this controller, and verify the controller's correctness to $\overline{k}$ time steps.
+for this controller, and verify the controller correctness to $\overline{k}$ time steps.
 Essentially, $\overline{k}$ represents the number of iterations 
@@
 such that the boundaries are not violated for any $k{>}\overline{k}$
-(i.e. it's sufficient to unwound the closed-loop state-space system up to  
+(i.e. it is sufficient to unwind the closed-loop state-space system up to  
 $\overline{k}$ in order to ensure that $\phi_{safety}$ holds).
+
+\medskip
 
@@
 (blocks 1 to 5):
+
+\todo{please eventually itemize next}
 
@@
 
+Proof. 
+Consider the set of initial states, $X_0$, assumed to be convex since it's a box. 
+Name $v_i$ its vertices, where $i=1,\ldots, 2^n$.  
+Thus any point $x \in X_0$ can be expressed by convexity as $x = \sum_{i=1}^{2^n} \alpha_i v_i$, 
+where $\sum_{i=1}^{2^n} \alpha_i =1$. 
+So then if $x_0=x$, then $x_k = (A_d - B_d K)^k x = 
+(A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i = 
+\sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i  = 
+\sum_{i=1}^{2^n} \alpha_i x_k^i$, 
+where I have denoted with $x_k^i$ the trajectories obtained from the single vertices $v_i$.QED
+
 3. The second {\sc verify} stage, {\sc precision}, 
@@
 \missingfigure{picture for completeness threshold}
+
+Proof sketch. 
+Consider spectrum of matrix $(A_d - B_d K)$ and select eigenvalue with smallest (non trivial) imaginary value.  
+call such value $\vartheta$. 
+At every time interval $kT_s, (k+1)T_s$ ($T_s$ being the sampling time), 
+the dynamics projected on the corresponding eigenspace rotate of $\vartheta T_s$ radiants.  
+So surely taking $k$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, after $k$ steps we've completed a rotation. 
+This is the CT.
 

### 2017-01-22 cav2017/cav2017.tex
text

@@
   over an abstraction of the continuous dynamics that conforms to witness proofs at specific times; 
-  it further generalises the solution over all times by refining the number of witnesses. 
+  it further generalises the solution over all times by refining the number of witnesses.  \todo{clarify use of abstract acceleration. add references.}
 \end{itemize}
@@
 the safety specification.
-Our second model, rather than look at a bisimulation in discrete time, explores a much higher abstraction,
-evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specifcation.
+Our second model, rather than look at a bisimulation \todo{specific notion that has not been formally define - do not use} in discrete time, explores a much higher abstraction, 
+evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specification.
 We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a
@@
 A controllable system with quantization will have the following dynamics:
-
+\todo{eliminate vectors}
 %
@@
 }
-\caption{CEGIS with abstraction refinement\label{fig:CEGARIS}.}
+\caption{CEGIS with abstraction refinement}
+\label{fig:CEGARIS} 
 \end{figure}

### 2017-01-22 cav2017/cav2017.tex
one comment

@@
 in the current paper, we consider a state-space
-representation of the physical system and synthesise controllers that
-make the closed-loop system safe.  Moreover, 
-a key aspect of our approach
+representation of the physical system, which allows us to synthesise controllers that
+make the closed-loop system \emph{safe} as well as stable.  Moreover, 
+a key aspect of the second approach we evaluate
 is the fact that we integrate abstraction
@@
 
-We require a combination of a synthesis engine with a control
+We use a combination of a synthesis engine with a control
 verification tool that addresses the challenges presented here in the
@@
 We take the former from~\cite{DBLP:conf/lpar/DavidKL15} and the latter
-from~\cite{daes20161}, while enhancing the procedure by evaluating the
+from~\cite{daes20161}\todo{This paper seems to be for transfer functions, not state space,
+is there a paper that does state space stability and safety?}
+, while enhancing the procedure by evaluating the
 quantization effects of the Hardware interfaces (ADC/DAC) to obtain an

### 2017-01-22 cav2017/cav2017.tex
response to one of A's comments

@@
 %Abstractly-Refined
-In this section we outline the general architecture of the program synthesiser used in both approaches\todo{which approaches?}. 
-We then detail the two methods of solution generalisation that we compare.
+In this section we outline the general architecture of the program synthesiser used in both approaches%\todo{which approaches?}. 
+We then give the details of the two methods of solution generalisation that we compare; the first checking safety by unwinding the transition relation to a completeness threshold; and the second employing abstract acceleration.
 

### 2017-01-22 benchmark-runner/eigcheck/eigs.c

@@ -1,0 +1,227 @@
+#include <stdio.h>
+typedef __CPROVER_fixedbv[32][16] __CPROVER_EIGEN_fixedbvt;
+
+extern const __CPROVER_fixedbv[24][12] __m[2][2];
+
+__CPROVER_EIGEN_fixedbvt __CPROVER_EIGEN_poly[3];
+void __CPROVER_EIGEN_charpoly_2(void) { //m00*m11 - m10*m11 - m00*x - m11*x + x^2
+
+  __CPROVER_EIGEN_poly[2] = __m[0][0]*__m[1][1] - __m[1][0]*__m[1][1];
+
+  __CPROVER_EIGEN_poly[1] = -__m[0][0] - __m[1][1];
+  // s^2
+  __CPROVER_EIGEN_poly[0] = 1.0;
+}
+
+__CPROVER_EIGEN_fixedbvt internal_pow(__CPROVER_EIGEN_fixedbvt a, unsigned int b){
+
+   __CPROVER_EIGEN_fixedbvt acc = 1.0;
+   for (int i=0; i < b; i++){
+    acc = acc*a;
+   }
+   return acc;
+}
+
+__CPROVER_EIGEN_fixedbvt internal_abs(__CPROVER_EIGEN_fixedbvt a){
+   return a < 0 ? -a : a;
+}
+
+
+int check_stability(void){
+
+#define __a __CPROVER_EIGEN_poly
+#define __n 3u
+   int lines = 2 * __n - 1;
+   int columns = __n;
+   __CPROVER_EIGEN_fixedbvt m[lines][__n];
+   int i,j;
+
+   __CPROVER_EIGEN_fixedbvt current_stability[__n];
+   for (i=0; i < __n; i++){
+     current_stability[i] = __a[i];
+   }
+
+   __CPROVER_EIGEN_fixedbvt sum = 0;
+   for (i=0; i < __n; i++){
+     sum += __a[i];
+   }
+   if (sum <= 0){
+  printf("[DEBUG] the first constraint of Jury criteria failed: (F(1) > 0)");
+     return 0;
+   }
+
+   sum = 0;
+   for (i=0; i < __n; i++){
+    sum += __a[i] * internal_pow(-1, __n-1-i);
+   }
+   sum = sum * internal_pow(-1, __n-1);
+   if (sum <= 0){
[…]

### 2017-01-23 cav2017/cav2017.tex
Beginning of proof for AA continuous envelope

@@
    \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstraction};
-       % \node[draw=none] (FIK) at ([xshift=2.5cm,yshift=.3cm]abstract)  {\sc $\Psi (\mat{K})$};
    \& \coordinate (aux); \\ % \node[fill=yellow!20,align=center] (counter) {\sc counterexample};\\
@@
        %\node[draw=none] (NKL) at ([xshift=2cm,yshift=1cm]synth)  {\sc $P_a$};
-   \& \node[fill=gray!20,align=center, minimum width=4cm] (verify) {\sc 3. verify ($\Psi$)};
+   \& \node[fill=gray!20,align=center, minimum width=4cm] (verify) {\sc 3. verify ($\phi$)};
        %\node[draw=none] (VUNS) at ([xshift=.6cm,yshift=1cm]verify)  {\sc SAT};
-       \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc UNSAT};
+       \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc SAT};
    \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
@@
      \coordinate (auxsynth);
-     \node[draw,rectangle,align=center] (KSAT) at ([xshift=-.8cm]auxsynth.center) {\sc Prog.\\Search};
-     \node[draw=none] (SATK) at ([xshift=-.5cm,yshift=1.5cm]KSAT)  {$\mathcal{J}_K$};
+     \node[draw,rectangle,align=center] (KSAT) at ([xshift=0cm]auxsynth.center) {\sc Prog.\\Search};
+     \node[draw=none] (SATK) at ([xshift=-0.5cm,yshift=1.5cm]KSAT)  {$\mathcal{J}_K$};
      \node[draw=none] (K) at ([xshift=.4cm,yshift=1.5cm]KSAT)  {$\tilde{\mat{K}}$};
@@
      \node[draw,rectangle,align=center] (AAI) at ([xshift=-1.5cm]AA.center) {\sc AI\\Model};
+     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm,yshift=1.5cm]AA.center) {\sc CEGAR};
      \node[draw,rectangle,align=center] (AAV) at ([xshift=1.5cm]AA.center) {\sc AA\\Solver};
-     \node[draw=none] (AB) at ([xshift=.4cm,yshift=1.5cm]AAI.center)  {\sc $\mat{A}_t$ $\mat{B}_{tp}$ $\mat{B}_{tn}$};     
+
+     \node[draw=none] (AB) at ([xshift=.4cm,yshift=1.5cm]AAI.center)  {\sc $\mat{A},\mat{B}$\\$\phi$};     
      \node[draw=none] (MA) at ([yshift=.2cm]AA.center)  {$\mathcal{A}_t$};     
      \node[draw=none] (MB) at ([yshift=-.3cm]AA.center)  {$\mathcal{B}_{tp},\mathcal{B}_{tn}$}; 
-     \node[draw=none] (AB) at ([xshift=0.3cm,yshift=1.5cm]AAV.center)  {\sl $\hat{X}^\#$};  
+     \node[draw=none] (XT) at ([xshift=0.3cm,yshift=0.5cm]AAC.center)  {\sl $\hat{X}_r^\#$};  
+     \node[draw=none] (XT2) at ([xshift=0.3cm,yshift=0.8cm]AAV.center)  {\sl $\hat{X}^\#$};  
+     %\draw [->,line width=1pt] ([xshift=-0.1cm,yshift=2cm]AA.center) arc[x radius=0.7cm, y radius =.7cm, start angle=-250, end angle=60];
     }\\
@@
      \coordinate (UNSAT);
-     \coordinate (KUNSAT)  at ([xshift=-.8cm]UNSAT.center);
+     \coordinate (KUNSAT)  at ([xshift=0cm]UNSAT.center);
      \node[draw=none] (UNSATB) at ([xshift=1.6cm,yshift=.3cm]UNSAT)  {\sc UNSAT};
@@
     %([yshift=-2em]verif.west) edge node[xshift=-0.7em] {New input} ([yshift=-2em]synth.east)
-    ([yshift=1em]synth.east) edge node {$\mat{K},\mat{L}$} ([yshift=1em]verify.west)
+    ([yshift=1em]synth.east) edge node {$\mat{K}$} ([yshift=1em]verify.west)
     ([yshift=-1em]verify.west) edge node {$P_a$} ([yshift=-1em]synth.east)
@@
   \path
-    ([xshift=+.6cm]KSAT.north) edge ([xshift=-2.1cm]synth.south) 
-    ([xshift=-3.3cm]synth.south) edge ([xshift=-.6cm]KSAT.north)
+    ([xshift=+.6cm]KSAT.north) edge ([xshift=0.6cm]synth.south) 
+    ([xshift=-.6cm]synth.south) edge ([xshift=-.6cm]KSAT.north)
     ([xshift=-4.9cm]verify.south) edge (AAI.north)
     (AAI.east) edge (AAV.west)
-    (AAV.north) edge ([xshift=4.9cm]verify.south)
+    (AAV.north) edge (AAC.south)
+    (AAC.north) edge ([xshift=4.9cm]verify.south)
+    (AAC.west) edge (AB.west)
     %(verify.north) edge (counter.south)
@@
      (KUNSAT.east) edge (FAIL.west)
-     (verify.north) edge node {$\Psi (\mat{K})$} (aux);
+     (verify.north) edge node {$\phi (\mat{K},k)$} (aux);
 \end{tikzpicture}
@@
 \begin{align*}
-x(kT)=x_k \wedge y(kT) = y_k, \forall k.
+x(kT_s)=x_k \wedge y(kT_s) = y_k, \forall k.
 \end{align*}
@@
  Since \eqref{eq:discretization} is a bi-simulation of \eqref{eq:ode}, we may use the semantics in section \ref{sec:model_semantics} to model continuous dynamical systems.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Overapproximating continuous space dynamics using discrete models}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+Let us recall equation \ref{eq:discretize}. The discrete representation of the system dynamics discretized with sample time $T_1$ is ruled by the formula
+$\vec{A}_1 = e^{\vec{A} T_1}$. From matrix theory, we have 
+\begin{equation}
+\vec{A}_1 = \mat{S}_1\mat{J}_1\mat{S}_1^{-1}= \mat{S}_1e^{\mat{J} T_1}\mat{S}_1^{-1}.
+\end{equation}
+Let $\mat{J}$ be a diagonal matrix, such that ${\lambda_1}_i=e^{\lambda_i T_1}, \forall \lambda \in \mat{J}$.
+Let us now take a different sample rate $T_2$, such that ${\lambda_2}_i=e^{\lambda_i T_2}, \forall \lambda \in \mat{J}$. We can then say that 
+\begin{equation}
+{\lambda_2}_i=e^{\lambda_i T_1 T_2/T_1}={\lambda_1}_i^{T_2/T_1} \Rightarrow A_2=A_1^{\frac{T_2}{T_1}}
+\end{equation}
+We have also shown in the previous section that $x_k=A^nx_0$ is a witness of $x(t): \dot{x}(t)=Ax(t)$ at time $kT_s$.
+Applying this notion to multiple sample times, we can state that $x_{k_i}=A_i^nx_0$ are a set of witnesses at times $kT_i$, and by extension the set $\{x=A_i^nx_0 : \forall n \in \mathbb{R} \}$ witnesses all states visited by the continuous system in time $t \in [0,\infty)$.
+This applies to any arbitrary sample time $T_i$.
 

### 2017-01-23 benchmark-runner/eigcheck/eigs.c
Remove accidentally added files

@@ -1,227 +1,0 @@
-#include <stdio.h>
-typedef __CPROVER_fixedbv[32][16] __CPROVER_EIGEN_fixedbvt;
-
-extern const __CPROVER_fixedbv[24][12] __m[2][2];
-
-__CPROVER_EIGEN_fixedbvt __CPROVER_EIGEN_poly[3];
-void __CPROVER_EIGEN_charpoly_2(void) { //m00*m11 - m10*m11 - m00*x - m11*x + x^2
-
-  __CPROVER_EIGEN_poly[2] = __m[0][0]*__m[1][1] - __m[1][0]*__m[1][1];
-
-  __CPROVER_EIGEN_poly[1] = -__m[0][0] - __m[1][1];
-  // s^2
-  __CPROVER_EIGEN_poly[0] = 1.0;
-}
-
-__CPROVER_EIGEN_fixedbvt internal_pow(__CPROVER_EIGEN_fixedbvt a, unsigned int b){
-
-   __CPROVER_EIGEN_fixedbvt acc = 1.0;
-   for (int i=0; i < b; i++){
-    acc = acc*a;
-   }
-   return acc;
-}
-
-__CPROVER_EIGEN_fixedbvt internal_abs(__CPROVER_EIGEN_fixedbvt a){
-   return a < 0 ? -a : a;
-}
-
-
-int check_stability(void){
-
-#define __a __CPROVER_EIGEN_poly
-#define __n 3u
-   int lines = 2 * __n - 1;
-   int columns = __n;
-   __CPROVER_EIGEN_fixedbvt m[lines][__n];
-   int i,j;
-
-   __CPROVER_EIGEN_fixedbvt current_stability[__n];
-   for (i=0; i < __n; i++){
-     current_stability[i] = __a[i];
-   }
-
-   __CPROVER_EIGEN_fixedbvt sum = 0;
-   for (i=0; i < __n; i++){
-     sum += __a[i];
-   }
-   if (sum <= 0){
-  printf("[DEBUG] the first constraint of Jury criteria failed: (F(1) > 0)");
-     return 0;
-   }
-
-   sum = 0;
-   for (i=0; i < __n; i++){
-    sum += __a[i] * internal_pow(-1, __n-1-i);
-   }
-   sum = sum * internal_pow(-1, __n-1);
-   if (sum <= 0){
[…]

### 2017-01-23 cav2017/cav2017.tex
remove duplicate comment
added references

@@
 by Analogue-to-Digital (A/D) and Digital-to-Analogue (D/A) conversion.  
-Whilst the research on digital control is well developed [Astrom book on digital control], 
+Whilst the research on digital control is well developed~\cite{astrom1997computer}, 
 automated and sound control synthesis is a challenging task. 
@@
 
-\todo{this section is unclear and probably needs to move somewhere else as it is only relevant for the acceleration back end} 
 \todo{yes, please reformat the discussion below so that it fits the discussion above. }

### 2017-01-23 cav2017/cav2017.tex
handle Alessandro's comments
Wording/grammar

@@
 to safety. 
-\textcolor{red}{[Mention GA \todo{GA? Genetic Algorithms? We don't use GA?} and Abstract Acceleration here?]}
+\textcolor{red}{[Mention GA \todo{GA? Genetic Algorithms? We don't use GA?} and Abstract Acceleration here? Alessandro: we are not using GA. We don't think that we should describe it here.]}
 
@@
 the life sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}.
-Control synthesis for LTI is a broadly investigated, 
-however the presence of digital control architectures is exacerbated by specific artefacts,  
-%specific to digital control, 
-such as the effects of finite-precision arithmetic, time discretization, and quantisation noise, which are typically introduced 
+Control synthesis for LTI is broadly investigated, 
+however the use of digital control architectures adds new challenges due to 
+%exacerbated by specific artefacts,  
+the effects of finite-precision arithmetic, time discretization, and quantisation noise, which are typically introduced 
 by Analogue-to-Digital (A/D) and Digital-to-Analogue (D/A) conversion.  
@@
 
-Whilst there is a vast literature in validation of control systems,
+Whilst there is a vast literature on validation of control systems,
 the subject of control synthesis has been somewhat restricted in the
@@
 Reachability tools are
-also used when discretising the state-space for both verification and
+also used when discretizing the state-space for both verification and
 parametric synthesis~\cite{cimatti2013parameter}.
@@
 Due to the complexity of such systems, in this particular work we focus
-on linear models \addtodo{[clarify next] with known configurations} and perform parametric synthesis
+on linear models %\addtodo{[clarify next] with known configurations} 
+and perform parametric synthesis
 of safe digital controllers.

### 2017-01-23 cav2017/cav2017.tex
addressed AA's comments related to known configurations

--- 2017-01-23 cav2017/cav2017.tex
@@
 Due to the complexity of such systems, in this particular work we focus
-on linear models \addtodo{[clarify next] with known configurations} and perform parametric synthesis
-of safe digital controllers.
+on linear models \addtodo{[clarify next] with known configurations (e.g., number of bits, fixed-point
+arithmetic)} and perform parametric synthesis of safe digital controllers.
 

### 2017-01-23 cav2017/cav2017.tex
revised CEGIS with AA figure

--- 2017-01-23 cav2017/cav2017.tex
@@
    \&\node[fill=gray!20,align=center] (pre) {{\sc 1. pre-}\\{\sc processing}};
-   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstraction};
+   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstract};
    \& \coordinate (aux); \\ % \node[fill=yellow!20,align=center] (counter) {\sc counterexample};\\
@@
      \coordinate (AA);
-     \node[draw,rectangle,align=center] (AAI) at ([xshift=-1.5cm]AA.center) {\sc AI\\Model};
-     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm,yshift=1.5cm]AA.center) {\sc CEGAR};
+     \node[draw,rectangle,align=center] (AAI) at ([xshift=-1.5cm]AA.center) {\sc Abstract};
+     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm,yshift=1.5cm]AA.center) {Abstraction \\ Verifier};
      \node[draw,rectangle,align=center] (AAV) at ([xshift=1.5cm]AA.center) {\sc AA\\Solver};
 
-     \node[draw=none] (AB) at ([xshift=.4cm,yshift=1.5cm]AAI.center)  {\sc $\mat{A},\mat{B}$\\$\phi$};     
+     %\node[draw=none] (AB) at ([xshift=.4cm,yshift=1.5cm]AAI.center)  {\sc $\mat{A},\mat{B}$\\$\phi$};     
      \node[draw=none] (MA) at ([yshift=.2cm]AA.center)  {$\mathcal{A}_t$};     
@@
     ([xshift=-.6cm]synth.south) edge ([xshift=-.6cm]KSAT.north)
-    ([xshift=-4.9cm]verify.south) edge (AAI.north)
+    (AAC) edge[bend right] node[align=center] {$k$} (AAI.north)
+    ([xshift=-4.9cm]verify.south) edge node[align=center] {$\mat{A},\mat{B}$\\$\phi$} (AAI.north)
     (AAI.east) edge (AAV.west)
@@
     (AAC.north) edge ([xshift=4.9cm]verify.south)
-    (AAC.west) edge (AB.west)
+    %(AAC.west) edge (AB.west)
     %(verify.north) edge (counter.south)

### 2017-01-23 cav2017/cav2017.tex

--- 2017-01-23 cav2017/cav2017.tex
@@
 Due to the complexity of such systems, in this particular work we focus
-on linear models %\addtodo{[clarify next] with known configurations} 
-and perform parametric synthesis
-of safe digital controllers.
+on linear models with known  implementation features (e.g., number of bits, fixed-point
+arithmetic) %\addtodo{[clarify next] with known configurations} 
+and perform parametric synthesis of safe digital controllers.
 

### 2017-01-23 cav2017/cav2017.tex
review introduction
reviewed related work

@@
 potential safety by unfolding the dynamics of the system and checking for 
-a completeness threshold. \textcolor{red}{In the second approach,...}
+a completeness threshold. \textcolor{red}{Dario: Can you please briefly explain your approach?
+In the second approach,...}
 
@@
 
-\addtodo{Add contributions (Cristina)}
+\addtodo{We have to summarize our main contributions here}
 
@@
 Program synthesis is the problem of computing correct-by-design programs
-from high-level specifications, and algorithms for this problem have made
+from high-level specifications; algorithms for this problem have made
 substantial progress in recent years.  One such
@@
 suitable for the kind of control we seek to synthesize.
+\textcolor{red}{Cristina: can you please revise this sentence:
 Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
@@
 controllers that guarantee reach while stay properties of a closed
-loop system. The solution is based on synthesizing control Lyapunov
+loop system}. The solution is based on synthesizing control Lyapunov
 functions for switched systems, that yield switching controllers with

### 2017-01-23 cav2017/cav2017.tex
typo

@@
 synthesising stabilizing controllers for continuous plants
-by exploiting advantage in bit-accurate verification of C programs 
-to obtain a verifier for software-implemented digital control~\cite{Bessa16}.  
-While they also make use of a CEGIS-based technique, their approach is
-restricted to synthesising controllers for hybrid closed-loop systems
-that are stable and only consider transfer function models.  In contrast,
-in the current paper, we consider a state-space
+by exploiting advantage in bit-accurate verification of software-implemented 
+digital control~\cite{Bessa16}.  While they also make use of a CEGIS-based 
+technique, their approach is restricted to synthesising controllers for hybrid 
+closed-loop systems that are stable and only consider transfer function models.  
+In contrast, in the current paper, we consider a state-space
 representation of the physical system, which allows us to synthesise controllers that
@@
 We take the former from~\cite{DBLP:conf/lpar/DavidKL15} and the latter
-from~\cite{daes20161}\todo{This paper seems to be for transfer functions, not state space,
-is there a paper that does state space stability and safety?}
+from~\cite{Monteiro16}%\todo{This paper seems to be for transfer functions, not state space,
+%is there a paper that does state space stability and safety?}
 , while enhancing the procedure by evaluating the
@@
 of the characteristic polynomial ({\it i.e.}, the eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity circle in the complex plane, 
-{\it i.e.} iff their absolute value are less than one~\cite{astrom1997computer}. 
+{\it i.e.} iff their absolute values are less than one~\cite{astrom1997computer}. 
 In this paper, we express the stability specification $\phi_{stability}$ in terms of a check known as Jury's criterion \cite{fadali}. 

### 2017-01-23 cav2017/cav2017.tex
added reference

@@
 of the characteristic polynomial ({\it i.e.}, the eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity circle in the complex plane, 
-{\it i.e.} iff their absolute values are less than one~\cite{astrom1997computer}. 
+{\it i.e.} iff their absolute value are less than one~\cite{astrom1997computer}. 
 In this paper, we express the stability specification $\phi_{stability}$ in terms of a check known as Jury's criterion \cite{fadali}. 

### 2017-01-23 cav2017/cav2017.tex
redistributed/removed the initial part of sec 4.5 (before Verification of a controllable system)

--- 2017-01-23 cav2017/cav2017.tex
@@
 
-The verification of a hybrid continuous/discrete system over an unbounded time, requires the
-non-deterministic simulation of an infinite set of states, which is undecidable. Our initial approach creates an
-abstraction of this system by establishing bounds on the error between such a system and a discrete-time/continuous-space model.
-This model is still however, quite complex, hard to verify, and many of the states involved are inconsequential to
-the safety specification.
-Our second model, rather than look at a bisimulation \todo{specific notion that has not been formally define - do not use} in discrete time, explores a much higher abstraction, 
-evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specification.
-We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a
-single iteration, in addition to a stability specification defined by Jury's criteria, and try to synthesise a controller that meets these specs.
-A second abstraction that encompasses the accelerated continuous reach-tube over an unbounded time is used to verify that the controller meets the full safety specification.
-If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
-The advantage of this model is that it starts with a very simple description regardless of the complexity of the overall dynamics, and only expands to more complex models when a solution cannot be found.
-
-\addtodo{Move as much as possible from Sec~\ref{sec:cof_verification}
-to the appendix (e.g. discussion on abstract acceleration). 
-Merge the rest in Sec~\ref{sec:cof_synth}.}
+% The verification of a hybrid continuous/discrete system over an unbounded time, requires the
+% non-deterministic simulation of an infinite set of states, which is undecidable. Our initial approach creates an
+% abstraction of this system by establishing bounds on the error between such a system and a discrete-time/continuous-space model.
+% This model is still however, quite complex, hard to verify, and many of the states involved are inconsequential to
+% the safety specification.
+% The advantage of this model is that it starts with a very simple description regardless of the complexity of the overall dynamics, and only expands to more complex models when a solution cannot be found.
+
+% \addtodo{Move as much as possible from Sec~\ref{sec:cof_verification}
+% to the appendix (e.g. discussion on abstract acceleration). 
+% Merge the rest in Sec~\ref{sec:cof_synth}.}
 
@@
 Now that we have explained the verification process, we may proceed to describe the synthesis procedure, which is illustrated in figure \ref{fig:CEGARIS}.
+Our model, rather than look at a bisimulation \todo{specific notion that has not been formally define - do not use} in discrete time, explores a much higher abstraction, 
+evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specification.
+
 \begin{enumerate}
-\item We start by preprocessing the dynamics. This can be computationally intensive and we don't want it to be part of the CEGIS loop.
+\item 
+We start by preprocessing the dynamics. This can be computationally intensive and we don't want it to be part of the CEGIS loop.
 \begin{enumerate}
@@
 \end{enumerate}
-\item Next we synthesise a candidate controller. Let $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ be a program describing Jury's method.
+\item Next we synthesise a candidate controller. 
+We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability specification defined by Jury's criteria.
+%, and try to synthesise a controller that meets these specs.
+
+Let $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ be a program describing Jury's method.
 \begin{enumerate}
@@
 \item Once we have a candidate solution, we perform a safety verification using abstract acceleration.
+For this purpose, we make use of a second abstraction that encompasses the accelerated continuous reach-tube over an unbounded time.
+% If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
+
 \begin{enumerate}

### 2017-01-23 cav2017/cav2017.tex
Some stuff on Pessoa + some removal of extra words

--- 2017-01-23 cav2017/cav2017.tex
@@
 the subject of control synthesis has been somewhat restricted in the
-properties it explores.  Traditionally, this focuses mainly on the
-subject of stability %, working typically on continuous domains
+properties it explores.  Traditionally, this focuses mainly on stability %, working typically on continuous domains
 \cite{DBLP:journals/corr/AbateBCCDKK16,sadabadi2016static}, or using switched
@@
 Reachability tools are
-also used when discretizing the state-space for both verification and
+also used when discretizing the state-space for verification and
 parametric synthesis~\cite{cimatti2013parameter}.
@@
 Due to the complexity of such systems, in this particular work we focus
-on linear models with known  implementation features (e.g., number of bits, fixed-point
-arithmetic) %\addtodo{[clarify next] with known configurations} 
-and perform parametric synthesis of safe digital controllers.
+on linear models %\addtodo{[clarify next] with known configurations} 
+and perform %parametric 
+correct-by-design synthesis of safe digital controllers.
 
@@
 potential safety by unfolding the dynamics of the system and checking for 
-a completeness threshold. \textcolor{red}{Dario: Can you please briefly explain your approach?
-In the second approach,...}
+a completeness threshold. \textcolor{red}{In the second approach,...}
 
@@
 
-\addtodo{We have to summarize our main contributions here}
+\addtodo{Add contributions (Cristina)}
 
@@
 Program synthesis is the problem of computing correct-by-design programs
-from high-level specifications; algorithms for this problem have made
+from high-level specifications, and algorithms for this problem have made
 substantial progress in recent years.  One such
@@
 
-Program synthesisers are an ideal fit for synthesis of parametric
+Program synthesisers are an ideal fit for synthesis of %parametric
 controllers since the semantics of programs capture effects such as FWL
@@
 suitable for the kind of control we seek to synthesize.
-\textcolor{red}{Cristina: can you please revise this sentence:
 Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
@@
 controllers that guarantee reach while stay properties of a closed
-loop system}. The solution is based on synthesizing control Lyapunov
+loop system. The solution is based on synthesizing control Lyapunov
 functions for switched systems, that yield switching controllers with
@@
 synthesising stabilizing controllers for continuous plants
-by exploiting advantage in bit-accurate verification of software-implemented 
-digital control~\cite{Bessa16}.  While they also make use of a CEGIS-based 
-technique, their approach is restricted to synthesising controllers for hybrid 
-closed-loop systems that are stable and only consider transfer function models.  
-In contrast, in the current paper, we consider a state-space
+by exploiting advantage in bit-accurate verification of C programs 
+to obtain a verifier for software-implemented digital control~\cite{Bessa16}.  
+While they also make use of a CEGIS-based technique, their approach is
+restricted to synthesising controllers for hybrid closed-loop systems
+that are stable and only consider transfer function models.  In contrast,
+in the current paper, we consider a state-space
 representation of the physical system, which allows us to synthesise controllers that
@@
 a key aspect of the second approach we evaluate
-is the fact that we integrate abstraction
+is that we integrate abstraction
 refinement inside the CEGIS loop.
+
+The tool Pessoa~\cite{mazo2010pessoa} is a MatLab toolbox that synthesises correct-by-design
+embedded control software. It is based on the principle of describing a physical system
+as an equivalent finite-state machine and computing reachability over the finite-state 
+machine. Pessoa can synthesise safe embedded controller software for a range of properties based on a safety specification over state
+values, as well as specification on characteristic functions of the controller. 
+However, Pessoa does not have native inclusion of the ADC/DAC quantization error needed for
+synthesising a fixed point digital controller.
 
@@
 form of FWL effects and stability measures for LTI SISO controllers.
-We take the former from~\cite{DBLP:conf/lpar/DavidKL15} and the latter
-from~\cite{Monteiro16}%\todo{This paper seems to be for transfer functions, not state space,
-%is there a paper that does state space stability and safety?}
-, while enhancing the procedure by evaluating the
-quantization effects of the Hardware interfaces (ADC/DAC) to obtain an
-accurate discrete-time FWL representation of the continuous dynamics.
+We take the former from~\cite{DBLP:conf/lpar/DavidKL15}. The latter is 
+based on~\cite{daes20161}, but adapted to state-space representation and
+enhanced to include evaluation of quantization effects.
+
+\todo{something about the acceleration verification engine}
+
+% and the latter from~\cite{daes20161}
+%, while enhancing the procedure by evaluating the
+%quantization effects of the Hardware interfaces (ADC/DAC) to obtain an
+%accurate discrete-time FWL representation of the continuous dynamics.
 
@@
    \&\node[fill=gray!20,align=center] (pre) {{\sc 1. pre-}\\{\sc processing}};
-   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstract};
+   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstraction};
    \& \coordinate (aux); \\ % \node[fill=yellow!20,align=center] (counter) {\sc counterexample};\\
@@
      \coordinate (AA);
-     \node[draw,rectangle,align=center] (AAI) at ([xshift=-1.5cm]AA.center) {\sc Abstract};
-     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm,yshift=1.5cm]AA.center) {Abstraction \\ Verifier};
+     \node[draw,rectangle,align=center] (AAI) at ([xshift=-1.5cm]AA.center) {\sc AI\\Model};
+     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm,yshift=1.5cm]AA.center) {\sc CEGAR};
      \node[draw,rectangle,align=center] (AAV) at ([xshift=1.5cm]AA.center) {\sc AA\\Solver};
 
-     %\node[draw=none] (AB) at ([xshift=.4cm,yshift=1.5cm]AAI.center)  {\sc $\mat{A},\mat{B}$\\$\phi$};     
+     \node[draw=none] (AB) at ([xshift=.4cm,yshift=1.5cm]AAI.center)  {\sc $\mat{A},\mat{B}$\\$\phi$};     
      \node[draw=none] (MA) at ([yshift=.2cm]AA.center)  {$\mathcal{A}_t$};     
@@
     ([xshift=-.6cm]synth.south) edge ([xshift=-.6cm]KSAT.north)
-    (AAC) edge[bend right] node[align=center] {$k$} (AAI.north)
-    ([xshift=-4.9cm]verify.south) edge node[align=center] {$\mat{A},\mat{B}$\\$\phi$} (AAI.north)
+    ([xshift=-4.9cm]verify.south) edge (AAI.north)
     (AAI.east) edge (AAV.west)
@@
     (AAC.north) edge ([xshift=4.9cm]verify.south)
-    %(AAC.west) edge (AB.west)
+    (AAC.west) edge (AB.west)
     %(verify.north) edge (counter.south)

### 2017-01-23 cav2017/cav2017.tex
Stability bug fix Continuous time envelope proof

--- 2017-01-23 cav2017/cav2017.tex
@@
 arithmetic) %\addtodo{[clarify next] with known configurations} 
-and perform parametric synthesis of safe digital controllers.
+and perform %parametric 
+synthesis of safe digital controllers.
 
@@
 form of FWL effects and stability measures for LTI SISO controllers.
-We take the former from~\cite{DBLP:conf/lpar/DavidKL15} and the latter
-from~\cite{Monteiro16}%\todo{This paper seems to be for transfer functions, not state space,
-%is there a paper that does state space stability and safety?}
-, while enhancing the procedure by evaluating the
-quantization effects of the Hardware interfaces (ADC/DAC) to obtain an
-accurate discrete-time FWL representation of the continuous dynamics.
+
+We take the former from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
+the first approach we present, is 
+based on~\cite{Monteiro16}, but 
+enhanced to include evaluation of quantization effects and safety properties
+over the state space. In the second approach, we use a verification engine
+based on XXXXXXX
+\todo{something about the acceleration verification engine}
 
@@
 This applies to any arbitrary sample time $T_i$.
-
+Since the controller output is fed to a Zero Order Holder, the progression of the system between times $kT_s$ and $(k+1)T_s$ is $\mat{A}^n\vec{x}_k+\mat{B}\vec{u}_k : n \in (0,1)$.
+We therefore obtain a reach tube for the continuous dynamics of a time sampled system to be contained within the abstract reach tube $\mathcal{A}^1\mathcal{M}X_0+\mathcal{BK}^1\mathcal{M}X_0=\mathcal{M}X_0$
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-01-23 benchmark-runner/AACegar/FWL_LTI_stability.h

@@ -1,3 +1,5 @@
+#define __CHECK_FP
+
 void make_closed_loop()
 {
   cnttype i,j;
@@ -32,7 +34,7 @@ signed int check_stability_closedloop(vectort a)
   control_floatt sum=_one;
   m[0][0]=1;
 #ifndef __CPROVER
-  printf("polynomial %f",m[0][0]);
+  printf("polynomial[%d] %f",n,m[0][0]);
 #endif
   for(i = 0 ; i < _DIMENSION; i++) 
   { 
@@ -50,29 +52,28 @@ signed int check_stability_closedloop(vectort a)
   verify_assume(-m[0][n-1]+_transform_error < m[0][0]);
 #else
   printf("\n");
+  printf("m[0][0]=%f>%f\n",m[0][0],_transform_error);
   if (!(m[0][0] > _transform_error)) 
   {
-    printf("m[0][0]=%f>%f\n",m[0][0],_transform_error);
     return 0;
   }
+  printf("sum=%f>%f\n",sum,_sum_error);
   if (!(sum > _sum_error))
   {
-    printf("sum=%f>%f\n",sum,_sum_error);
     return 0;
   }
+  printf("m[0][%d]=%f<m[0][0]=%f\n",n-1,m[0][n - 1],m[0][0]);
   if (m[0][n - 1]==0)
   {
-    printf("m[0][%d]=0\n",n-1);
     return 0;    
   }  
   if (!(m[0][n - 1]+_transform_error < m[0][0])) 
   {
-    printf("m[0][%d]=%f<m[0][0]=%f\n",n-1,m[0][n - 1],m[0][0]);
     return 0;
   }
+  printf("-m[0][%d]=%f<m[0][0]=%f\n",n-1,m[0][n - 1],m[0][0]);
   if (!(-m[0][n - 1]+_transform_error < m[0][0])) 
   {
-    printf("-m[0][%d]=%f<m[0][0]=%f\n",n-1,m[0][n - 1],m[0][0]);
     return 0;
   }
 #endif
@@ -82,10 +83,11 @@ signed int check_stability_closedloop(vectort a)
     if (((n -i)&1)!=0) sum+=m[0][i];
     else               sum-=m[0][i];
   }
-  if ((n&1)==0) sum=-sum;
+  if ((n&1)!=0) sum=-sum;
 #ifdef __CPROVER
   verify_assume(sum > _sum_error);
 #else
+  printf("sum_o-sum_e=%f>0\n",sum);
[…]

### 2017-01-23 cav2017/cav2017.tex
more revision of the AA based approach

@@
 
-Let us recall the formulas used for single-input and single-output (SISO) systems 
-in sections \ref{sec:reachable} and \ref{sec:observable}.
-A controllable system with quantization will have the following dynamics:
-\todo{eliminate vectors}
-%
-\begin{align}
-\label{eq:observer_LTI_cf}
-\vec{x}_{k+1}=&\mat{A}_{t}\vec{x}_k+\mat{B}_{tp} \vec{r}_k+\mat{B}_{tn} (\vec{\nu}_1 + \vec{\nu}_2 + \vec{\nu}_3)
-\end{align}
-\begin{align*}
-\mat{A}_{t}=&\mat{T}\mat{A}_d\mat{T}^{-1}&
-\mat{B}_{tp}=&\mat{T}\mat{B}_d&
-\mat{B}_{tn}=&\mat{T}\mat{B}_d&
-\mat{T}=&\mat{R}_{cf}\mat{R}^{-1}&
-\end{align*}
-
-\begin{align*}
-\mat{A}_{t}=\mat{T}\mat{A}_d\mat{T}^{-1}=&\left[
-\begin{array}{ccccc}
-0&1&0&\cdots&0\\
-0&0&1&\cdots&0\\
-\vdots&\vdots&\vdots&\ddots&\vdots\\
-0&0&0&\cdots&1\\
-k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
-\end{array}\right]
-\label{eq:cf_SISO_2}
-\end{align*}
-
-The characteristic polynomial of the above matrix is:
-%
-\begin{align*}
-z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}
-\end{align*}
-
-For a stabilized closed-loop, which is necessary for our safety property, we need
-these roots to remain within the unit circle, which we verify using Jury's criteria.
-Notice that in our polynomials $c_0=1$ and we only use reals.
-
+% Let us recall the formulas used for single-input and single-output (SISO) systems 
+% in sections \ref{sec:reachable} and \ref{sec:observable}.
+% A controllable system with quantization will have the following dynamics:
+% \todo{eliminate vectors}
+% %
+% \begin{align}
+% \label{eq:observer_LTI_cf}
+% \vec{x}_{k+1}=&\mat{A}_{t}\vec{x}_k+\mat{B}_{tp} \vec{r}_k+\mat{B}_{tn} (\vec{\nu}_1 + \vec{\nu}_2 + \vec{\nu}_3)
+% \end{align}
+% \begin{align*}
+% \mat{A}_{t}=&\mat{T}\mat{A}_d\mat{T}^{-1}&
+% \mat{B}_{tp}=&\mat{T}\mat{B}_d&
+% \mat{B}_{tn}=&\mat{T}\mat{B}_d&
+% \mat{T}=&\mat{R}_{cf}\mat{R}^{-1}&
+% \end{align*}
+
+% \begin{align*}
+% \mat{A}_{t}=\mat{T}\mat{A}_d\mat{T}^{-1}=&\left[
+% \begin{array}{ccccc}
+% 0&1&0&\cdots&0\\
+% 0&0&1&\cdots&0\\
+% \vdots&\vdots&\vdots&\ddots&\vdots\\
+% 0&0&0&\cdots&1\\
+% k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
+% \end{array}\right]
+% \label{eq:cf_SISO_2}
+% \end{align*}
+
+% The characteristic polynomial of the above matrix is:
+% %
+% \begin{align*}
+% z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}
+% \end{align*}
+
+% For a stabilized closed-loop, which is necessary for our safety property, we need
+% these roots to remain within the unit circle, which we verify using Jury's criteria.
+% Notice that in our polynomials $c_0=1$ and we only use reals.
+\todo{where is $\phi_{input}$ defined?}
 Once we have established convergence, we may examine the 
 specification of the state and input spaces ($\phi_{safety} \wedge \phi_{input}$).
-Whilst there are other properties, we may include in the verification, 
-we will solely focus on these for simplicity of the explanation.
-We assume that we do not want saturation in our system, 
-hence the control loop has only one mode. We have also identified 
+% Whilst there are other properties, we may include in the verification, 
+% we will solely focus on these for simplicity of the explanation.
+% We assume that we do not want saturation in our system, 
+% hence the control loop has only one mode.
+
+We have also identified 
 the quantization noise as a bounded non-deterministic input.

### 2017-01-23 cav2017/cav2017.tex
added comment

@@
 However, Pessoa does not have native inclusion of the ADC/DAC quantization error needed for
-synthesising a fixed point digital controller.
+synthesising a fixed-point digital controller.
 
@@
 and with initial states set as $x(0)$. 
-Eq.~\eqref{eq:ode} is soundly discretised in time (as shown in the Appendix) into
+Eq.~\eqref{eq:ode} is soundly discretised in time (as shown in the Appendix) into \textcolor{red}{What is subscript ``d''?}
 %

### 2017-01-23 cav2017/cav2017.tex
Threats to validity

@@
 %-------------------------------
+We report an assessment of both our approaches over a diverse set of real-world benchmarks.
+Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalize to other benchmarks.
+
+Our algorithm to select suitable FWL word widths to model plant behaviour employs a heuristic based on user-provided controller word-width specifications.
+For the first approach, where we may need to increase the precision of the time discretization, we select the time steps for the discretizations on a similar basis.
+This works sufficiently well for our benchmarks, but performance may suffer in some cases, for example if the completeness threshold is high.
+
+The performance gain from abstract acceleration may not hold for more complex properties than stability, for instance ``eventually always reaches a certain safe set''.
 

### 2017-01-23 cav2017/cav2017.tex
addressed a part of the comments

@@
 I do not like to use vectors unless essential, let's say it's a waste of ink in printouts.
-} ranges over ground terms and
+}
+ ranges over ground terms and
 $\sigma$ is a quantifier-free formula.  We interpret the ground terms over
@@
 
-\todo{The following paragraph has been already stated above. Let us clarify this is a useful repetition to recap things?}
-
-The synthesis problem we are trying to solve is the following:
+% \todo{The following paragraph has been already stated above. Let us clarify this is a useful repetition to recap things?}
+
+At this point, we recap the the synthesis problem that we solve in this work:
 find a digital controller $K$ (see Eq.~\ref{eq:controlaction})
@@
 and the reference signal to be set to zero.  
-
 When mapping back to the notation used for describing the general architecture 
@@
 and input with a bounded time horizon and generalises to all states,
-inputs, and time horizons. %% (with a final verification loop that verifies
+inputs, and time horizons. The safety check is performed in this approach 
+via unfolding of the transition system corresponding to the synthesised controller.
+
+%% (with a final verification loop that verifies
 %% the continuous system behaviour against the previously verified
@@
 \item[2.] The second approach (described in Sec~\ref{sec:CEGIS-abstraction-refinement})
-  %% uses abstract acceleration to compute the set of reachable states,
-  %% which enables it to perform abstraction refinement inside the CEGIS loop.
-  finds a controller for a continuous initial set of states and input set, 
-  over an abstraction of the continuous dynamics that conforms to witness proofs at specific times; 
-  it further generalises the solution over all times by refining the number of witnesses.  \todo{clarify use of abstract acceleration. add references.}
+  finds a controller for a continuous initial set of states and input
+  set, over an abstraction of the continuous dynamics that conforms to
+  witness proofs at specific times; it further generalises the
+  solution over all times by refining the number of witnesses.  
+  In order to perform the safety check, this approach uses abstract acceleration
+  \cite{cattaruzza2015unbounded} to compute the controller's set of states. 
+  %\todo{clarify use of abstract acceleration. add references.}
 \end{itemize}
@@
 
-% Let us recall the formulas used for single-input and single-output (SISO) systems 
-% in sections \ref{sec:reachable} and \ref{sec:observable}.
-% A controllable system with quantization will have the following dynamics:
-% \todo{eliminate vectors}
-% %
-% \begin{align}
-% \label{eq:observer_LTI_cf}
-% \vec{x}_{k+1}=&\mat{A}_{t}\vec{x}_k+\mat{B}_{tp} \vec{r}_k+\mat{B}_{tn} (\vec{\nu}_1 + \vec{\nu}_2 + \vec{\nu}_3)
-% \end{align}
-% \begin{align*}
-% \mat{A}_{t}=&\mat{T}\mat{A}_d\mat{T}^{-1}&
-% \mat{B}_{tp}=&\mat{T}\mat{B}_d&
-% \mat{B}_{tn}=&\mat{T}\mat{B}_d&
-% \mat{T}=&\mat{R}_{cf}\mat{R}^{-1}&
-% \end{align*}
-
-% \begin{align*}
-% \mat{A}_{t}=\mat{T}\mat{A}_d\mat{T}^{-1}=&\left[
-% \begin{array}{ccccc}
-% 0&1&0&\cdots&0\\
-% 0&0&1&\cdots&0\\
-% \vdots&\vdots&\vdots&\ddots&\vdots\\
-% 0&0&0&\cdots&1\\
-% k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
-% \end{array}\right]
-% \label{eq:cf_SISO_2}
-% \end{align*}
-
-% The characteristic polynomial of the above matrix is:
-% %
-% \begin{align*}
-% z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}
-% \end{align*}
-
-% For a stabilized closed-loop, which is necessary for our safety property, we need
-% these roots to remain within the unit circle, which we verify using Jury's criteria.
-% Notice that in our polynomials $c_0=1$ and we only use reals.
-\todo{where is $\phi_{input}$ defined?}
+Let us recall the formulas used for single-input and single-output (SISO) systems 
+in sections \ref{sec:reachable} and \ref{sec:observable}.
+A controllable system with quantization will have the following dynamics:
+\todo{eliminate vectors}
+%
+\begin{align}
+\label{eq:observer_LTI_cf}
+\vec{x}_{k+1}=&\mat{A}_{t}\vec{x}_k+\mat{B}_{tp} \vec{r}_k+\mat{B}_{tn} (\vec{\nu}_1 + \vec{\nu}_2 + \vec{\nu}_3)
+\end{align}
+\begin{align*}
+\mat{A}_{t}=&\mat{T}\mat{A}_d\mat{T}^{-1}&
+\mat{B}_{tp}=&\mat{T}\mat{B}_d&
+\mat{B}_{tn}=&\mat{T}\mat{B}_d&
+\mat{T}=&\mat{R}_{cf}\mat{R}^{-1}&
+\end{align*}
+
+\begin{align*}
+\mat{A}_{t}=\mat{T}\mat{A}_d\mat{T}^{-1}=&\left[
+\begin{array}{ccccc}
+0&1&0&\cdots&0\\
+0&0&1&\cdots&0\\
+\vdots&\vdots&\vdots&\ddots&\vdots\\
+0&0&0&\cdots&1\\
+k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
+\end{array}\right]
+\label{eq:cf_SISO_2}
+\end{align*}
+
+The characteristic polynomial of the above matrix is:
+%
+\begin{align*}
+z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}
+\end{align*}
+
+For a stabilized closed-loop, which is necessary for our safety property, we need
+these roots to remain within the unit circle, which we verify using Jury's criteria.
+Notice that in our polynomials $c_0=1$ and we only use reals.
+\todo{where is $\phi_{input}$ computed?}
 Once we have established convergence, we may examine the 

### 2017-01-23 cav2017/cav2017.tex
define subscript d

@@
 and with initial states set as $x(0)$. 
-Eq.~\eqref{eq:ode} is soundly discretised in time (as shown in the Appendix) into \textcolor{red}{What is subscript ``d''?}
+Eq.~\eqref{eq:ode} is soundly discretised in time (as shown in the Appendix) into %\textcolor{red}{What is subscript ``d''?}
 %
@@
 where $k \in \mathbb N$, 
-and with initial state $x_{0}=x(0)$. 
+and with initial state $x_{0}=x(0)$. $A_d$ and $B_d$ denote the discretized matrices of $A$ and $B$, the plant dynamics. 
 Later, we will deal with the issue of variable quantisation, as introduced by the ADC and DAC blocks.

### 2017-01-23 cav2017/cav2017.tex
discretiZed

@@
 and with initial states set as $x(0)$. 
-Eq.~\eqref{eq:ode} is soundly discretised in time (as shown in the Appendix) into %\textcolor{red}{What is subscript ``d''?}
+Eq.~\eqref{eq:ode} is soundly discretized in time (as shown in the Appendix) into %\textcolor{red}{What is subscript ``d''?}
 %
@@
 The most basic feedback architecture is the state feedback, 
-where the control action $u_k$ (notice we work with the discretised signal) is computed by: 
+where the control action $u_k$ (notice we work with the discretized signal) is computed by: 
 %

### 2017-01-23 cav2017/cav2017.tex
microtype
reordering of fxp section. Adding note about stability

@@
 
-Asymptotic stability boils down to Lyapunov stability and convergence to an equilibrium point \todo{add reference}.  
+Asymptotic stability boils down to Lyapunov stability and convergence to an equilibrium point\cite{Astrom08} %\todo{add reference}.  
 Lyapunov stability requires that model trajectories remain in a neighbourhood of the equilibrium point. 
@@
 
-\todo{I've moved the following paragraph to this section, from that on safety specs.}
-The states values must be computed considering the digital controller error, i.e., the error introduced by the ADC and the digital controller. 
-%, and the digital reference signal. 
-%In this paper, we consider systems with a reference signal equal to zero. 
-%the FWL effects in all operations related to the control action~\eqref{eq:controlaction} 
-%and disregarding it in the state equation~\eqref{eq:plant}.
-Thus, the states are computed using the following equations. We use $\mathcal{F}_{\langle I_c,F_c \rangle}$ \todo{explain and clarify notation.}
-to to denote numbers represented with the precision of the digital controller. All other numbers
-are represented with the precision of our plant model:
-%
-\begin{align*}
-u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  
-%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
-\end{align*}
-%\left\lbrace
-%\begin{array}{l}
-%u_{k}=\mathcal{F}_{\langle I,F \rangle}(r_{k}-\mathcal{F}_{\langle I,F \rangle}(\mathcal{F}_{\langle I,F \rangle}(K)\cdot\mathcal{F}_{\langle I,F \rangle}(x_{k})))\\
-%x_{k+1}=Ax_{k}+Bu_{k}
-%\end{array}\right.
-%\end{equation}
-
-\bigskip
-
 The 
@@
 The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=(|\mat{K}|_1+1)c_m$
+
+\bigskip
+
+\subsubsection{Effect on safety specification and stability}
+The states values must be computed considering the digital controller error, i.e., the error introduced by the ADC and the digital controller. 
+%, and the digital reference signal. 
+%In this paper, we consider systems with a reference signal equal to zero. 
+%the FWL effects in all operations related to the control action~\eqref{eq:controlaction} 
+%and disregarding it in the state equation~\eqref{eq:plant}.
+Thus, the states are computed using the following equations. We use $\mathcal{F}_{\langle I_c,F_c \rangle}$ \todo{explain and clarify notation.}
+to to denote numbers represented with the precision of the digital controller. All other numbers
+are represented with the precision of our plant model:
+%
+\begin{align*}
+u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  
+%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
+\end{align*}
+
+We note that the effect on stability due to the fixed-word-length error is that the system may, instead of converging to the desired equilibrium point, converge to a point that is $\delta$ away from the desired equilibrium point, see Appendix.
+In this paper, we are concerned with \emph{safe} controllers and therefore concerned only that the system converges to a point within the safety specification.
+Hence, it is sufficient to synthesise a stable controller based on infinite precision, and then verify safety.
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Discretising continuous space dynamics}
+\subsection{Discretizing continuous space dynamics}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-01-23 cav2017/cav2017.tex
sp

--- 2017-01-23 cav2017/cav2017.tex
@@
 \usepackage{algorithm,algpseudocode}
+\usepackage{microtype}
 
@@
 guided inductive synthesis (CEGIS) loop. In the first approach, 
-we devise a digital controller that stabilizes the system; then, we verify its 
+we devise a digital controller that stabilises the system; then, we verify its 
 potential safety by unfolding the dynamics of the system and checking for 
@@
 
-\addtodo{We have to summarize our main contributions here}
+\addtodo{We have to summarise our main contributions here}
 
@@
 substantial progress in recent years.  One such
-approach~\cite{itzhaky2010simple} inductively synthesizes invariants to
+approach~\cite{itzhaky2010simple} inductively synthesises invariants to
 generate the desired programs.
 
-Program synthesisers are an ideal fit for synthesis of %parametric
+Program synthesizers are an ideal fit for synthesis of %parametric
 controllers since the semantics of programs capture effects such as FWL
 precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
-for the synthesis of switching controllers for stabilizing continuous-time
+for the synthesis of switching controllers for stabilising continuous-time
 plants with polynomial dynamics.  The work extends to its application on
@@
 controller, it entirely circumvents the FWL problem.  It is also not
-suitable for the kind of control we seek to synthesize.
+suitable for the kind of control we seek to synthesise.
 \textcolor{red}{Cristina: can you please revise this sentence:
 Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
-use a CEGIS-based approach for synthesizing continuous-time switching
+use a CEGIS-based approach for synthesising continuous-time switching
 controllers that guarantee reach while stay properties of a closed
-loop system}. The solution is based on synthesizing control Lyapunov
+loop system}. The solution is based on synthesising control Lyapunov
 functions for switched systems, that yield switching controllers with
@@
 In \cite{DBLP:journals/corr/AbateBCCDKK16}, Abate et al.  focus on
-synthesising stabilizing controllers for continuous plants
+synthesising stabilising controllers for continuous plants
 by exploiting advantage in bit-accurate verification of software-implemented 
@@
 response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics with
-the goal to either verify (e.g.~\cite{daes20161}) or optimize
+the goal to either verify (e.g.~\cite{daes20161}) or optimise
 (e.g.~\cite{oudjida2014design}) given implementations.
@@
 attractive invariant sets as a mechanism to bound the quantization error effect
-on stabilization as an invariant set that always converges toward the controllable
+on stabilisation as an invariant set that always converges toward the controllable
 set. In a similar fashion, \cite{liberzon2003hybrid} evaluates the dynamics of the
@@
 %Abstractly-Refined
-In this section we outline the general architecture of the program synthesiser used in both approaches%\todo{which approaches?}. 
+In this section we outline the general architecture of the program synthesizer used in both approaches%\todo{which approaches?}. 
 We then give the details of the two methods of solution generalisation that we compare; the first checking safety by unwinding the transition relation to a completeness threshold; and the second employing abstract acceleration.
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{General architecture of the program synthesiser}
+\subsection{General architecture of the program synthesizer}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 When mapping back to the notation used for describing the general architecture 
-of the program synthesiser, the controller $K$ denotes $P$ and 
+of the program synthesizer, the controller $K$ denotes $P$ and 
 $(x_0, u_k)$ represents $x$. 
@@
 
-1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
+1. The inductive synthesis phase (i.e. {\sc synthesise}) uses BMC to
 compute a candidate solution $K$
@@
 not violate the safety criteria. This is sound if the current $k$ is below the
-completeness threshold, which we assume to be true in the {\sc synthesize} phase.
+completeness threshold, which we assume to be true in the {\sc synthesise} phase.
 We also assume some
@@
 Consider the set of initial states, $X_0$, assumed to be convex since it's a box. 
-Name $v_i$ its vertices, where $i=1,\ldots, 2^n$.  
+Name $v_i$ its vertexes, where $i=1,\ldots, 2^n$.  
 Thus any point $x \in X_0$ can be expressed by convexity as $x = \sum_{i=1}^{2^n} \alpha_i v_i$, 
@@
 \sum_{i=1}^{2^n} \alpha_i x_k^i$, 
-where I have denoted with $x_k^i$ the trajectories obtained from the single vertices $v_i$.QED
+where I have denoted with $x_k^i$ the trajectories obtained from the single vertexes $v_i$.QED
 
@@
 
-For a stabilized closed-loop, which is necessary for our safety property, we need
+For a stabilised closed-loop, which is necessary for our safety property, we need
 these roots to remain within the unit circle, which we verify using Jury's criteria.
@@
 \end{enumerate} 
-\item If the candidate solution is not valid we refine the abstraction used by the synthesiser
+\item If the candidate solution is not valid we refine the abstraction used by the synthesizer
 \begin{enumerate}
@@
 $z^n+\sum_{i=1}^n[a_i-k_i]z^{n-i}=\prod_{i=1}^n (z-[\lambda_i]) : |[\lambda_i]|<1 \wedge [\lambda_i] \models \phi_{\Lambda}$.
-\item Pass the refined abstraction with the new contraints to the synthesiser, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again.
-We note that the Abstraction refinement is a soft constraint on the proposed model which can increase or decrease the parameter space at any time, whereas the concrete counterexample passed to the synthesiser is monotonically decreasing.
+\item Pass the refined abstraction with the new constraints to the synthesizer, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again.
+We note that the Abstraction refinement is a soft constraint on the proposed model which can increase or decrease the parameter space at any time, whereas the concrete counterexample passed to the synthesizer is monotonically decreasing.
 The first one improves speed of the tool whereas the second ensures convergence.
@@
 
-Table~\ref{table:State-space benchmarks} summarizes all benchmarks extracted 
+Table~\ref{table:State-space benchmarks} summarises all benchmarks extracted 
 from the control system literature~\cite{Franklin15,maglev,converters,CTMS}. 
@@
 \textit{Magnetized Pointer} plant describes a physical model that is rotated through interaction 
-with magnetic fields (typically employed in analog gauges and indicators).
+with magnetic fields (typically employed in analogue gauges and indicators).
 \textit{1/4 Car Suspension} plant presents a physical model that connects a car to its wheels 
@@
 We report an assessment of both our approaches over a diverse set of real-world benchmarks.
-Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalize to other benchmarks.
+Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalise to other benchmarks.
 

### 2017-01-23 cav2017/cav2017.tex
more progress on the AA section (not done though)

@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Let us recall the formulas used for single-input and single-output (SISO) systems 
-in sections \ref{sec:reachable} and \ref{sec:observable}.
-A controllable system with quantization will have the following dynamics:
+Whilst there are other properties, we may include in the verification, 
+% we will solely focus on these for simplicity of the explanation.
+% We assume that we do not want saturation in our system, 
+% hence the control loop has only one mode.
+
+We have also identified 
+the quantization noise as a bounded non-deterministic input.
+%
+The first step constraints
+\begin{equation}
+\mat{K} \models u_k=-\mat{K}x_k : \phi_{safety}
+\label{eq:of_bounds}
+\end{equation}
+The second step is evaluating the progression of the system over time to evaluate 
+$x_{k+1} \models \phi_{safety}$. For this step we require 
+an initial set from which the system progresses. Obviously, this set $x_0$ 
+must satisfy the specification; otherwise, the system will be unsafe to begin with.
+We accept a specification in the form $\mat{E}\mat{T}x_0<\mat{f}$. 
+The presence of $\mat{T}$ is because this will typically be given in the original 
+state-space. Accelerating \eqref{eq:observer_LTI_cf}, we obtain:
+%
+\begin{align}
+\label{eq:acc_observer_LTI_cf}
+x=&\mat{A}_t^kx_0
++\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tp} r_i
++\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tn}(\nu_1+\nu_2+\nu_3) : x_0 \models \phi_{init}
+\end{align}
+which would still require us to verify the system for every $k$ up to infinity. 
+Instead we use abstract acceleration~\cite{cattaruzza2015unbounded}, which translates the formula into
+%
+\begin{align}
+\label{eq:aa_observer_LTI_cf}
+\hat{X}^\#
+=&\mathcal{A}_t X_0+\mathcal{B}_{tp} R + \mathcal{B}_{tn} N\\
+X_0 =&\left \{x : x \models \phi_{init} \right\}\nonumber\\
+ R =&\{r : \mat{E}_r < f_r \}\nonumber\\
+ N=&\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber
+\end{align}
+%
+where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A}^k, \mathcal{B}_{tp}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tp}, \mathcal{B}_{tn}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tn}$ are abstract matrices for the system in \eqref{eq:observer_LTI_cf} and $r$ is a non-deterministic parametric input (\emph{ie} $\forall k>0, r_{k+1} =r_k$) whereas the set N is composed of non-deterministic variable inputs.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsubsection{Controller synthesis}\label{sec:cof_synth}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+The CEGIS loop for this approach is illustrated in \ref{fig:CEGARIS}.
+
+% Now that we have explained the verification process, we may proceed to describe the synthesis procedure, which is illustrated in figure \ref{fig:CEGARIS}.
+% Our model, rather than look at a bisimulation \todo{specific notion that has not been formally define - do not use} in discrete time, explores a much higher abstraction, 
+% evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specification.
+
+\begin{enumerate}
+\item 
+We start by preprocessing the dynamics. This can be computationally intensive and we don't want it to be part of the CEGIS loop.
+% Let us recall the formulas used for single-input and single-output (SISO) systems 
+% in sections \ref{sec:reachable} and \ref{sec:observable}.
+A controllable system with quantization will have the following dynamics 
+(note that we use underscript ``n'' to denote a noise term,
+``cf'' to denote Controllable Canonical Form and $\mat{J}_{n,m}$ to represent a matrix of ones with $n$ rows and $m$ columns):
 \todo{eliminate vectors}
@@
 \label{eq:observer_LTI_cf}
-\vec{x}_{k+1}=&\mat{A}_{t}\vec{x}_k+\mat{B}_{tp} \vec{r}_k+\mat{B}_{tn} (\vec{\nu}_1 + \vec{\nu}_2 + \vec{\nu}_3)
+x_{k+1}=&\mat{A}_{t}x_k+\mat{B}_{t} r_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)
 \end{align}
@@
 \mat{A}_{t}=&\mat{T}\mat{A}_d\mat{T}^{-1}&
-\mat{B}_{tp}=&\mat{T}\mat{B}_d&
-\mat{B}_{tn}=&\mat{T}\mat{B}_d&
+\mat{B}_{t}=&\mat{T}\mat{B}_d&
+\mat{B}_{n}=&\mat{J}_{n,1}&
 \mat{T}=&\mat{R}_{cf}\mat{R}^{-1}&
@@
 
-For a stabilised closed-loop, which is necessary for our safety property, we need
-these roots to remain within the unit circle, which we verify using Jury's criteria.
-Notice that in our polynomials $c_0=1$ and we only use reals.
-\todo{where is $\phi_{input}$ computed?}
-Once we have established convergence, we may examine the 
-specification of the state and input spaces ($\phi_{safety} \wedge \phi_{input}$).
-% Whilst there are other properties, we may include in the verification, 
-% we will solely focus on these for simplicity of the explanation.
-% We assume that we do not want saturation in our system, 
-% hence the control loop has only one mode.
-
-We have also identified 
-the quantization noise as a bounded non-deterministic input.
-%
-The first step constraints
-\begin{equation}
-\mat{K} \models \vec{u}_k=-\mat{K}\vec{x}_k : \phi_{safety} \wedge \phi_{input}
-\label{eq:of_bounds}
-\end{equation}
-The second step is evaluating the progression of the system over time to evaluate 
-$\vec{x}_{k+1} \models \phi_{safety}$. For this step we require 
-an initial set from which the system progresses. Obviously, this set $\vec{x}_0$ 
-must satisfy the specification; otherwise, the system will be unsafe to begin with.
-We accept a specification in the form $\mat{E}\mat{T}\vec{x}_0<\mat{f}$. 
-The presence of $\mat{T}$ is because this will typically be given in the original 
-state-space. Accelerating \eqref{eq:observer_LTI_cf}, we obtain:
-%
-\begin{align}
-\label{eq:acc_observer_LTI_cf}
-\vec{x}=&\mat{A}_t^k\vec{x}_0
-+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tp} \vec{r}_i
-+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tn}(\vec{\nu}_1+\vec{\nu}_2+\vec{\nu}_3) : \vec{x}_0 \models \phi_{init}
-\end{align}
-which would still require us to verify the system for every $k$ up to infinity. 
-Instead we use abstract acceleration~\cite{cattaruzza2015unbounded}, which translates the formula into
-%
-\begin{align}
-\label{eq:aa_observer_LTI_cf}
-\hat{X}^\#
-=&\mathcal{A}_t X_0+\mathcal{B}_{tp} R + \mathcal{B}_{tn} N\\
-X_0 =&\left \{\vec{x} : \vec{x} \models \phi_{init} \right\}\nonumber\\
- R =&\{r : \mat{E}_r < \vec{f}_r \}\nonumber\\
- N=&\left \{ \vec{\nu}_1+\vec{\nu}_2+ \vec{\nu}_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber
-\end{align}
-%
-where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A}^k, \mathcal{B}_{tp}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tp}, \mathcal{B}_{tn}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tn}$ are abstract matrices for the system in \eqref{eq:observer_LTI_cf} and $r$ is a non-deterministic parametric input (\emph{ie} $\forall k>0, r_{k+1} =r_k$) whereas the set N is composed of non-deterministic variable inputs.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Controller synthesis}\label{sec:cof_synth}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-Now that we have explained the verification process, we may proceed to describe the synthesis procedure, which is illustrated in figure \ref{fig:CEGARIS}.
-Our model, rather than look at a bisimulation \todo{specific notion that has not been formally define - do not use} in discrete time, explores a much higher abstraction, 
-evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specification.
-
-\begin{enumerate}
-\item 
-We start by preprocessing the dynamics. This can be computationally intensive and we don't want it to be part of the CEGIS loop.
 \begin{enumerate}
@@
 %, and try to synthesise a controller that meets these specs.
+% For a stabilized closed-loop, which is necessary for our safety property, we need
+% these roots to remain within the unit circle, which we verify using Jury's criteria.
+% Notice that in our polynomials $c_0=1$ and we only use reals.
+% Once we have established convergence, we may examine the 
+% safety specification $\phi_{safety}$.
 

### 2017-01-23 benchmark-runner/universalrunner/safety_stability.c
eigencharpoly4 intervals.

@@ -173,25 +173,77 @@ __CPROVER_EIGEN_poly[0] = one_type;
 #if NSTATES==4
 void __CPROVER_EIGEN_charpoly_4(void) {
 
- __CPROVER_EIGEN_poly[4] = __m[0][0]*__m[1][1]*__m[2][2]*__m[3][3] - __m[0][0]*__m[1][1]*__m[2][3]*__m[3][2] - __m[0][0]*__m[1][2]*__m[2][1]*__m[3][3] + __m[0][0]*__m[1][2]*__m[2][3]*__m[3][1] + __m[0][0]*__m[1][3]*__m[2][1]*__m[3][2] -
-    __m[0][0]*__m[1][3]*__m[2][2]*__m[3][1] - __m[0][1]*__m[1][0]*__m[2][2]*__m[3][3] + __m[0][1]*__m[1][0]*__m[2][3]*__m[3][2] + __m[0][1]*__m[1][2]*__m[2][0]*__m[3][3] - __m[0][1]*__m[1][2]*__m[2][3]*__m[3][0] -
-    __m[0][1]*__m[1][3]*__m[2][0]*__m[3][2] + __m[0][1]*__m[1][3]*__m[2][2]*__m[3][0] + __m[0][2]*__m[1][0]*__m[2][1]*__m[3][3] - __m[0][2]*__m[1][0]*__m[2][3]*__m[3][1] - __m[0][2]*__m[1][1]*__m[2][0]*__m[3][3] +
-    __m[0][2]*__m[1][1]*__m[2][3]*__m[3][0] + __m[0][2]*__m[1][3]*__m[2][0]*__m[3][1] - __m[0][2]*__m[1][3]*__m[2][1]*__m[3][0] - __m[0][3]*__m[1][0]*__m[2][1]*__m[3][2] + __m[0][3]*__m[1][0]*__m[2][2]*__m[3][1] +
-    __m[0][3]*__m[1][1]*__m[2][0]*__m[3][2] - __m[0][3]*__m[1][1]*__m[2][2]*__m[3][0] - __m[0][3]*__m[1][2]*__m[2][0]*__m[3][1] + __m[0][3]*__m[1][2]*__m[2][1]*__m[3][0];
+  __CPROVER_EIGEN_poly[4] = add(sub(sub(add(add(sub(sub(add(add(sub(sub(add(add(sub(sub(add(add(sub(sub(add(add(sub(sub(
[…]

### 2017-01-23 cav2017/cav2017.tex
added experimental objectives

@@
 \subsection{Description of the benchmarks}
+\label{experimental-setup}
 %-------------------------------
@@
 A set of state-space models for different classes of 
-systems were extracted from the literature and employed 
-for validating our automated synthesis methodology. 
-All the systems are SISO models of the following form:
-%
-\begin{equation}
-\left\lbrace\begin{array}{c}
-\dot{\textbf{x}}(t)=\textbf{A}\textbf{x}(t)+\textbf{B}u(t)\\
-y(t)=\textbf{C}\textbf{x}(t)+\textbf{D}u(t)
-\end{array}\right.
-\end{equation}
-
-Table~\ref{table:State-space benchmarks} summarises all benchmarks extracted 
-from the control system literature~\cite{Franklin15,maglev,converters,CTMS}. 
+systems were extracted from the 
+literature~\cite{Franklin15,maglev,converters,CTMS} 
+and employed for validating our methodology. 
+%All systems are SISO models of the following form:
+%
+%\begin{equation}
+%\left\lbrace\begin{array}{c}
+%\dot{\textbf{x}}(t)=\textbf{A}\textbf{x}(t)+\textbf{B}u(t)\\
+%y(t)=\textbf{C}\textbf{x}(t)+\textbf{D}u(t)
+%\end{array}\right.
+%\end{equation}
+%
+Table~\ref{table:State-space benchmarks} summarizes 
+all our benchmarks, which are SISO models (cf. section~\ref{sec:preliminaries}).
+
 \textit{DC Motor Position and Rate} plants describes the angular position and 
-velocity of a DC Motor, respectively, that coupled with wheels and cables provides 
-translational motion. 
+velocity of a DC Motor, respectively. 
 \textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and 
@@
 
-We have also conducted the experimental evaluation on a 12-core 2.40 GHz
+We have conducted the experimental evaluation on a 12-core 2.40 GHz
 Intel Xeon E5-2440 with 96 GB of RAM and Linux OS. All times given are wall 
@@
 
+Using the state-space models given in Section~\ref{experimental-setup}, 
+our experimental evaluation aims to answer two research questions:
+%
+\begin{enumerate}
+
+\item[RQ1] \textbf{(CEGIS)} do the CEGIS with multi-stage 
+verification and abstraction refinement generate a FWL digital 
+controller in a reasonable amount of time?
+
+\item[RQ2] \textbf{(sanity check)} are the synthesized controllers sound
+and can their stability and safety be confirmed outside of our model?
+
+\end{enumerate}
+
 %-------------------------------

### 2017-01-23 cav2017/cav2017.tex
the AA based CEGIS sec has been reduced and compacted -- it still requires simplifications/explanattions

@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Verification of a controllable system}
-\label{sec:cof_verification}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-Whilst there are other properties, we may include in the verification, 
+%\subsubsection{Verification of a controllable system}
+%\label{sec:cof_verification}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%Whilst there are other properties, we may include in the verification, 
 % we will solely focus on these for simplicity of the explanation.
@@
 
-We have also identified 
-the quantization noise as a bounded non-deterministic input.
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%\subsubsection{Controller synthesis}\label{sec:cof_synth}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+The CEGIS loop for this approach is illustrated in \ref{fig:CEGARIS}.
+
+% Now that we have explained the verification process, we may proceed to describe the synthesis procedure, which is illustrated in figure \ref{fig:CEGARIS}.
+% Our model, rather than look at a bisimulation \todo{specific notion that has not been formally define - do not use} in discrete time, explores a much higher abstraction, 
+% evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specification.
+% We have also identified 
+% the quantization noise as a bounded non-deterministic input.
+
+\begin{enumerate}
+\item 
+We start by preprocessing the dynamics. This can be computationally intensive and we don't want it to be part of the CEGIS loop.
+% Let us recall the formulas used for single-input and single-output (SISO) systems 
+% in sections \ref{sec:reachable} and \ref{sec:observable}.
+A controllable system with quantization will have the following dynamics 
+(note that we use underscript ``n'' to denote a noise term and
+``cf'' to denote Controllable Canonical Form):
+\todo{eliminate vectors}
+%
+\begin{align}
+\label{eq:observer_LTI_cf}
+x_{k+1}=&\mat{A}_{t}x_k+\mat{B}_{t} r_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)
+\end{align}
+\begin{align*}
+\mat{A}_{t}=&\mat{T}\mat{A}_d\mat{T}^{-1}&
+\mat{B}_{t}=&\mat{T}\mat{B}_d&
+\mat{B}_{n}=&[1 \cdots 1]^T&
+\mat{T}=&\mat{W}_{cf}\mat{W}^{-1}&
+\end{align*}
+
+\begin{align*}
+\mat{A}_{t}=\mat{T}\mat{A}_d\mat{T}^{-1}=&\left[
+\begin{array}{ccccc}
+0&1&0&\cdots&0\\
+0&0&1&\cdots&0\\
+\vdots&\vdots&\vdots&\ddots&\vdots\\
+0&0&0&\cdots&1\\
+k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
+\end{array}\right]
+\label{eq:cf_SISO_2}
+\end{align*}
+
+The characteristic polynomial of the above matrix is:
+%
+\begin{align*}
+P_a = z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}
+\end{align*}
+
+\begin{enumerate}
+\item Calculate $\mat{T}$ as $\mat{W}_{cf}\mat{W}^{-1}$. %using equations \eqref{eq:rncf}\eqref{eq:rcf}\eqref{eq:to_cf}
+\item Extract the Plant's characteristic polynomial coefficients from $P_a$. %the last row of $P_a=(\mat{T}\mat{A}\mat{T}^-1)_{n*}$.
+\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
+$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] 
+\wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
+\item Calculate a set of initial bounds on K based on the input constraints. $$\phi_{safety} \Leftrightarrow u_k=r-Kx_k : x \in X^\# \wedge u_k \in [\underline{u}\ \ \overline{u}]$$
+\end{enumerate}
+\item Next we synthesise a candidate controller. 
+We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability specification defined by Jury's criteria.
+%, and try to synthesise a controller that meets these specs.
+% For a stabilized closed-loop, which is necessary for our safety property, we need
+% these roots to remain within the unit circle, which we verify using Jury's criteria.
+% Notice that in our polynomials $c_0=1$ and we only use reals.
+% Once we have established convergence, we may examine the 
+% safety specification $\phi_{safety}$.
+
+Let $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ be a program describing Jury's method.
+\begin{enumerate}
+\item Select a controller $\tilde{\mat{K}} \in \mathbb{R}\langle I,F\rangle^n$.
+This is achieved by solving a SAT formula $\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{input}$ that satisfies the input constraint and Jury's criteria for $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \mat{K}=\tilde{\mat{K}}\mat{T}$.
+\item If there is no candidate solution we return UNSAT and exit the loop.
+\end{enumerate}
+\item Once we have a candidate solution, we perform a safety verification using abstract acceleration.
+For this purpose, we make use of a second abstraction that encompasses the accelerated continuous reach-tube over an unbounded time.
+% If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
 %
@@
 x=&\mat{A}_t^kx_0
-+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tp} r_i
-+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tn}(\nu_1+\nu_2+\nu_3) : x_0 \models \phi_{init}
+%+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i
++\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{n}(\nu_1+\nu_2+\nu_3) : x_0 \models \phi_{init}
 \end{align}
@@
 \hat{X}^\#
-=&\mathcal{A}_t X_0+\mathcal{B}_{tp} R + \mathcal{B}_{tn} N\\
+=&\mathcal{A}_t X_0+\mathcal{B}_{t} R + \mathcal{B}_{n} N\\
 X_0 =&\left \{x : x \models \phi_{init} \right\}\nonumber\\
- R =&\{r : \mat{E}_r < f_r \}\nonumber\\
- N=&\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber
+% R =&\{r : \mat{E}_r < f_r \}\nonumber\\
+ %N=&\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber
 \end{align}
 %
-where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A}^k, \mathcal{B}_{tp}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tp}, \mathcal{B}_{tn}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tn}$ are abstract matrices for the system in \eqref{eq:observer_LTI_cf} and $r$ is a non-deterministic parametric input (\emph{ie} $\forall k>0, r_{k+1} =r_k$) whereas the set N is composed of non-deterministic variable inputs.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Controller synthesis}\label{sec:cof_synth}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-The CEGIS loop for this approach is illustrated in \ref{fig:CEGARIS}.
-
-% Now that we have explained the verification process, we may proceed to describe the synthesis procedure, which is illustrated in figure \ref{fig:CEGARIS}.
-% Our model, rather than look at a bisimulation \todo{specific notion that has not been formally define - do not use} in discrete time, explores a much higher abstraction, 
-% evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specification.
+where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A}^k, \mathcal{B}_{t}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{t}, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{n}$ are abstract matrices for the system in \eqref{eq:observer_LTI_cf}
+%and $r$ is a non-deterministic parametric input (\emph{ie} $\forall k>0, r_{k+1} =r_k$) 
+whereas the set N is composed of non-deterministic variable inputs.
 
 \begin{enumerate}
-\item 
-We start by preprocessing the dynamics. This can be computationally intensive and we don't want it to be part of the CEGIS loop.
-% Let us recall the formulas used for single-input and single-output (SISO) systems 
-% in sections \ref{sec:reachable} and \ref{sec:observable}.
-A controllable system with quantization will have the following dynamics 
-(note that we use underscript ``n'' to denote a noise term,
-``cf'' to denote Controllable Canonical Form and $\mat{J}_{n,m}$ to represent a matrix of ones with $n$ rows and $m$ columns):
-\todo{eliminate vectors}
-%
-\begin{align}
-\label{eq:observer_LTI_cf}
-x_{k+1}=&\mat{A}_{t}x_k+\mat{B}_{t} r_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)
-\end{align}
-\begin{align*}
-\mat{A}_{t}=&\mat{T}\mat{A}_d\mat{T}^{-1}&
-\mat{B}_{t}=&\mat{T}\mat{B}_d&
-\mat{B}_{n}=&\mat{J}_{n,1}&
-\mat{T}=&\mat{R}_{cf}\mat{R}^{-1}&
-\end{align*}
-
-\begin{align*}
-\mat{A}_{t}=\mat{T}\mat{A}_d\mat{T}^{-1}=&\left[
-\begin{array}{ccccc}
-0&1&0&\cdots&0\\
-0&0&1&\cdots&0\\
-\vdots&\vdots&\vdots&\ddots&\vdots\\
-0&0&0&\cdots&1\\
-k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
-\end{array}\right]
-\label{eq:cf_SISO_2}
-\end{align*}
-
-The characteristic polynomial of the above matrix is:
-%
-\begin{align*}
-z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}
-\end{align*}
-
-\begin{enumerate}
-\item Calculate $\mat{T}$ using equations \eqref{eq:rncf}\eqref{eq:rcf}\eqref{eq:to_cf}
-\item Extract the Plant's characteristic polynomial coefficients from the last row of $P_a=(\mat{T}\mat{A}\mat{T}^-1)_{n*}$.
-\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors ($\frac{q_1}{2},\frac{q_2}{2},q_3$)
-\item Calculate a set of initial bounds on K based on the input constraints. $$\phi_{input} \Leftrightarrow u_k=r-Kx_k : x \in X^\# \wedge u_k \in [\underline{u}\ \ \overline{u}]$$
-\end{enumerate}
-\item Next we synthesise a candidate controller. 
-We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability specification defined by Jury's criteria.
-%, and try to synthesise a controller that meets these specs.
-% For a stabilized closed-loop, which is necessary for our safety property, we need
-% these roots to remain within the unit circle, which we verify using Jury's criteria.
-% Notice that in our polynomials $c_0=1$ and we only use reals.
-% Once we have established convergence, we may examine the 
-% safety specification $\phi_{safety}$.
-
-Let $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ be a program describing Jury's method.
-\begin{enumerate}
-\item Select a controller $\tilde{\mat{K}} \in \mathbb{R}\langle I,F\rangle^n$.
-This is achieved by solving a SAT formula $\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{input}$ that satisfies the input constraint and Jury's criteria for $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \mat{K}=\tilde{\mat{K}}\mat{T}$.
-\item If there is no candidate solution we return UNSAT and exit the loop.
-\end{enumerate}
-\item Once we have a candidate solution, we perform a safety verification using abstract acceleration.
-For this purpose, we make use of a second abstraction that encompasses the accelerated continuous reach-tube over an unbounded time.
-% If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
-
-\begin{enumerate}
-\item Calculate the abstract matrices $\mathcal{A}_t, \mathcal{B}_{tp},\mathcal{B}_{tn}$ for the candidate closed loop solution.
+\item Calculate the abstract matrices $\mathcal{A}_t, \mathcal{B}_{t},\mathcal{B}_{n}$ for the candidate closed loop solution.
 \item Evaluate $\hat{X}^\# \models \Psi$. If the verification holds we have a solution, and exit the loop.
@@
      \node[draw=none] (MA) at ([yshift=.2cm]AA.center)  {$\mathcal{A}_t$};     
-     \node[draw=none] (MB) at ([yshift=-.3cm]AA.center)  {$\mathcal{B}_{tp},\mathcal{B}_{tn}$}; 
+     \node[draw=none] (MB) at ([yshift=-.3cm]AA.center)  {$\mathcal{B}_{t},\mathcal{B}_{n}$}; 
      \node[draw=none] (XT) at ([xshift=0.3cm,yshift=0.5cm]AAC.center)  {\sl $\hat{X}_r^\#$};  

### 2017-01-23 cav2017/cav2017.tex
spelling correction and removed thing about GA

@@
 to safety.
-\textcolor{red}{[Mention GA \todo{GA? Genetic Algorithms? We don't use GA?} and Abstract Acceleration here? Alessandro: we are not using GA. We don't think that we should describe it here.]}
 
@@
 Quantisation; 
-Fixed-point arithmetics; 
+Fixed-point arithmetic; 
 CEGIS; 

### 2017-01-23 cav2017/cav2017.tex
clarified Reach While Stay properties

@@
 suitable for the kind of control we seek to synthesise.
-\textcolor{red}{Cristina: can you please revise this sentence:
+
+%\textcolor{red}{Cristina: can you please revise this sentence:
 Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
 use a CEGIS-based approach for synthesising continuous-time switching
-controllers that guarantee reach while stay properties of a closed
-loop system}. The solution is based on synthesising control Lyapunov
+controllers that guarantee Reach While Stay properties of closed
+loop systems, i.e., properties that specify a set of goal states and safe states.%}. 
+The solution is based on synthesising control Lyapunov
 functions for switched systems, that yield switching controllers with

### 2017-01-23 cav2017/cav2017.tex
improved description of the benchmarks

--- 2017-01-23 cav2017/cav2017.tex
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%\subsubsection{Verification of a controllable system}
-%\label{sec:cof_verification}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%Whilst there are other properties, we may include in the verification, 
+\subsubsection{Verification of a controllable system}
+\label{sec:cof_verification}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+Whilst there are other properties, we may include in the verification, 
 % we will solely focus on these for simplicity of the explanation.
@@
 
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%\subsubsection{Controller synthesis}\label{sec:cof_synth}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-The CEGIS loop for this approach is illustrated in \ref{fig:CEGARIS}.
-
-% Now that we have explained the verification process, we may proceed to describe the synthesis procedure, which is illustrated in figure \ref{fig:CEGARIS}.
-% Our model, rather than look at a bisimulation \todo{specific notion that has not been formally define - do not use} in discrete time, explores a much higher abstraction, 
-% evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specification.
-% We have also identified 
-% the quantization noise as a bounded non-deterministic input.
-
-\begin{enumerate}
-\item 
-We start by preprocessing the dynamics. This can be computationally intensive and we don't want it to be part of the CEGIS loop.
-% Let us recall the formulas used for single-input and single-output (SISO) systems 
-% in sections \ref{sec:reachable} and \ref{sec:observable}.
-A controllable system with quantization will have the following dynamics 
-(note that we use underscript ``n'' to denote a noise term and
-``cf'' to denote Controllable Canonical Form):
-\todo{eliminate vectors}
-%
-\begin{align}
-\label{eq:observer_LTI_cf}
-x_{k+1}=&\mat{A}_{t}x_k+\mat{B}_{t} r_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)
-\end{align}
-\begin{align*}
-\mat{A}_{t}=&\mat{T}\mat{A}_d\mat{T}^{-1}&
-\mat{B}_{t}=&\mat{T}\mat{B}_d&
-\mat{B}_{n}=&[1 \cdots 1]^T&
-\mat{T}=&\mat{W}_{cf}\mat{W}^{-1}&
-\end{align*}
-
-\begin{align*}
-\mat{A}_{t}=\mat{T}\mat{A}_d\mat{T}^{-1}=&\left[
-\begin{array}{ccccc}
-0&1&0&\cdots&0\\
-0&0&1&\cdots&0\\
-\vdots&\vdots&\vdots&\ddots&\vdots\\
-0&0&0&\cdots&1\\
-k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
-\end{array}\right]
-\label{eq:cf_SISO_2}
-\end{align*}
-
-The characteristic polynomial of the above matrix is:
-%
-\begin{align*}
-P_a = z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}
-\end{align*}
-
-\begin{enumerate}
-\item Calculate $\mat{T}$ as $\mat{W}_{cf}\mat{W}^{-1}$. %using equations \eqref{eq:rncf}\eqref{eq:rcf}\eqref{eq:to_cf}
-\item Extract the Plant's characteristic polynomial coefficients from $P_a$. %the last row of $P_a=(\mat{T}\mat{A}\mat{T}^-1)_{n*}$.
-\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
-$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] 
-\wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
-\item Calculate a set of initial bounds on K based on the input constraints. $$\phi_{safety} \Leftrightarrow u_k=r-Kx_k : x \in X^\# \wedge u_k \in [\underline{u}\ \ \overline{u}]$$
-\end{enumerate}
-\item Next we synthesise a candidate controller. 
-We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability specification defined by Jury's criteria.
-%, and try to synthesise a controller that meets these specs.
-% For a stabilized closed-loop, which is necessary for our safety property, we need
-% these roots to remain within the unit circle, which we verify using Jury's criteria.
-% Notice that in our polynomials $c_0=1$ and we only use reals.
-% Once we have established convergence, we may examine the 
-% safety specification $\phi_{safety}$.
-
-Let $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ be a program describing Jury's method.
-\begin{enumerate}
-\item Select a controller $\tilde{\mat{K}} \in \mathbb{R}\langle I,F\rangle^n$.
-This is achieved by solving a SAT formula $\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{input}$ that satisfies the input constraint and Jury's criteria for $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \mat{K}=\tilde{\mat{K}}\mat{T}$.
-\item If there is no candidate solution we return UNSAT and exit the loop.
-\end{enumerate}
-\item Once we have a candidate solution, we perform a safety verification using abstract acceleration.
-For this purpose, we make use of a second abstraction that encompasses the accelerated continuous reach-tube over an unbounded time.
-% If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
+We have also identified 
+the quantization noise as a bounded non-deterministic input.
 %
@@
 x=&\mat{A}_t^kx_0
-%+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i
-+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{n}(\nu_1+\nu_2+\nu_3) : x_0 \models \phi_{init}
++\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tp} r_i
++\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tn}(\nu_1+\nu_2+\nu_3) : x_0 \models \phi_{init}
 \end{align}
@@
 \hat{X}^\#
-=&\mathcal{A}_t X_0+\mathcal{B}_{t} R + \mathcal{B}_{n} N\\
+=&\mathcal{A}_t X_0+\mathcal{B}_{tp} R + \mathcal{B}_{tn} N\\
 X_0 =&\left \{x : x \models \phi_{init} \right\}\nonumber\\
-% R =&\{r : \mat{E}_r < f_r \}\nonumber\\
- %N=&\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber
+ R =&\{r : \mat{E}_r < f_r \}\nonumber\\
+ N=&\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber
 \end{align}
 %
-where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A}^k, \mathcal{B}_{t}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{t}, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{n}$ are abstract matrices for the system in \eqref{eq:observer_LTI_cf}
-%and $r$ is a non-deterministic parametric input (\emph{ie} $\forall k>0, r_{k+1} =r_k$) 
-whereas the set N is composed of non-deterministic variable inputs.
+where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A}^k, \mathcal{B}_{tp}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tp}, \mathcal{B}_{tn}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tn}$ are abstract matrices for the system in \eqref{eq:observer_LTI_cf} and $r$ is a non-deterministic parametric input (\emph{ie} $\forall k>0, r_{k+1} =r_k$) whereas the set N is composed of non-deterministic variable inputs.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsubsection{Controller synthesis}\label{sec:cof_synth}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+The CEGIS loop for this approach is illustrated in \ref{fig:CEGARIS}.
+
+% Now that we have explained the verification process, we may proceed to describe the synthesis procedure, which is illustrated in figure \ref{fig:CEGARIS}.
+% Our model, rather than look at a bisimulation \todo{specific notion that has not been formally define - do not use} in discrete time, explores a much higher abstraction, 
+% evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specification.
 
 \begin{enumerate}
-\item Calculate the abstract matrices $\mathcal{A}_t, \mathcal{B}_{t},\mathcal{B}_{n}$ for the candidate closed loop solution.
+\item 
+We start by preprocessing the dynamics. This can be computationally intensive and we don't want it to be part of the CEGIS loop.
+% Let us recall the formulas used for single-input and single-output (SISO) systems 
+% in sections \ref{sec:reachable} and \ref{sec:observable}.
+A controllable system with quantization will have the following dynamics 
+(note that we use underscript ``n'' to denote a noise term,
+``cf'' to denote Controllable Canonical Form and $\mat{J}_{n,m}$ to represent a matrix of ones with $n$ rows and $m$ columns):
+\todo{eliminate vectors}
+%
+\begin{align}
+\label{eq:observer_LTI_cf}
+x_{k+1}=&\mat{A}_{t}x_k+\mat{B}_{t} r_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)
+\end{align}
+\begin{align*}
+\mat{A}_{t}=&\mat{T}\mat{A}_d\mat{T}^{-1}&
+\mat{B}_{t}=&\mat{T}\mat{B}_d&
+\mat{B}_{n}=&\mat{J}_{n,1}&
+\mat{T}=&\mat{R}_{cf}\mat{R}^{-1}&
+\end{align*}
+
+\begin{align*}
+\mat{A}_{t}=\mat{T}\mat{A}_d\mat{T}^{-1}=&\left[
+\begin{array}{ccccc}
+0&1&0&\cdots&0\\
+0&0&1&\cdots&0\\
+\vdots&\vdots&\vdots&\ddots&\vdots\\
+0&0&0&\cdots&1\\
+k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
+\end{array}\right]
+\label{eq:cf_SISO_2}
+\end{align*}
+
+The characteristic polynomial of the above matrix is:
+%
+\begin{align*}
+z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}
+\end{align*}
+
+\begin{enumerate}
+\item Calculate $\mat{T}$ using equations \eqref{eq:rncf}\eqref{eq:rcf}\eqref{eq:to_cf}
+\item Extract the Plant's characteristic polynomial coefficients from the last row of $P_a=(\mat{T}\mat{A}\mat{T}^-1)_{n*}$.
+\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors ($\frac{q_1}{2},\frac{q_2}{2},q_3$)
+\item Calculate a set of initial bounds on K based on the input constraints. $$\phi_{input} \Leftrightarrow u_k=r-Kx_k : x \in X^\# \wedge u_k \in [\underline{u}\ \ \overline{u}]$$
+\end{enumerate}
+\item Next we synthesise a candidate controller. 
+We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability specification defined by Jury's criteria.
+%, and try to synthesise a controller that meets these specs.
+% For a stabilized closed-loop, which is necessary for our safety property, we need
+% these roots to remain within the unit circle, which we verify using Jury's criteria.
+% Notice that in our polynomials $c_0=1$ and we only use reals.
+% Once we have established convergence, we may examine the 
+% safety specification $\phi_{safety}$.
+
+Let $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ be a program describing Jury's method.
+\begin{enumerate}
+\item Select a controller $\tilde{\mat{K}} \in \mathbb{R}\langle I,F\rangle^n$.
+This is achieved by solving a SAT formula $\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{input}$ that satisfies the input constraint and Jury's criteria for $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \mat{K}=\tilde{\mat{K}}\mat{T}$.
+\item If there is no candidate solution we return UNSAT and exit the loop.
+\end{enumerate}
+\item Once we have a candidate solution, we perform a safety verification using abstract acceleration.
+For this purpose, we make use of a second abstraction that encompasses the accelerated continuous reach-tube over an unbounded time.
+% If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
+
+\begin{enumerate}
+\item Calculate the abstract matrices $\mathcal{A}_t, \mathcal{B}_{tp},\mathcal{B}_{tn}$ for the candidate closed loop solution.
 \item Evaluate $\hat{X}^\# \models \Psi$. If the verification holds we have a solution, and exit the loop.
@@
      \node[draw=none] (MA) at ([yshift=.2cm]AA.center)  {$\mathcal{A}_t$};     
-     \node[draw=none] (MB) at ([yshift=-.3cm]AA.center)  {$\mathcal{B}_{t},\mathcal{B}_{n}$}; 
+     \node[draw=none] (MB) at ([yshift=-.3cm]AA.center)  {$\mathcal{B}_{tp},\mathcal{B}_{tn}$}; 
      \node[draw=none] (XT) at ([xshift=0.3cm,yshift=0.5cm]AAC.center)  {\sl $\hat{X}_r^\#$};  
@@
 control based on the pitch dimension. 
-\textit{Ball Magnetic Levitation} plant describes a physical model to keep a 
-metal ball hanged in air via a magnetic field . 
+\textit{Ball Magnetic Levitation} plant describes a physical model that keeps a 
+metal ball hanged in air via a magnetic field. 
 \textit{Buck Converter} plant represents a power converter model that steps down 
@@
 
-\textit{Automotive Cruise System} plant describes a physical model that represents 
-the speed of a motor vehicle. 
-\textit{Helicopter Longitudinal Motion} plant provides the 
-longitudinal motion model of a helicopter. 
+\textit{Automotive Cruise System} plant represents the speed of a motor vehicle. 
+\textit{Helicopter Longitudinal Motion} plant provides the longitudinal motion model 
+of a helicopter. 
 \textit{Inverted Pendulum} plant describes a pendulum model
 with its center of mass above its pivot point. 
-\textit{Magnetic Suspension} plant provides the physical model for which 
-a given object is suspended via a magnetic field. 
+\textit{Magnetic Suspension} plant provides a physical model for which 
+a given object is suspended via magnetic field. 
 \textit{Magnetized Pointer} plant describes a physical model that is rotated through interaction 

### 2017-01-23 cav2017/cav2017.tex
something about the acceleration

--- 2017-01-23 cav2017/cav2017.tex
@@
 We take the former from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
-the first approach we present, is 
+the first approach we present, performs bounded model checking of control properties,
 based on~\cite{Monteiro16}, but 
@@
 over the state space. In the second approach, we use a verification engine
-based on XXXXXXX
-\todo{something about the acceleration verification engine}
+based on abstract acceleration~\cite{cattaruzza2015unbounded} than avoids the explicit 
+unwinding the transition system necessarily for the first approach.
 

### 2017-01-23 cav2017/cav2017.tex
squeeze description of benchmarks

@@
 \textit{Ball Magnetic Levitation} plant describes a physical model that keeps a 
-metal ball hanged in air via a magnetic field. 
+metal ball hanged in air via magnetic field. 
 \textit{Buck Converter} plant represents a power converter model that steps down 
 voltage from the supply to the load while stepping up current. 
-\textit{Boost Converter} plant also represents a power converter model, but here 
+\textit{Boost Converter} plant also represents a power converter model, but
 it steps up voltage from the supply to the load while stepping down current. 
@@
 a given object is suspended via magnetic field. 
-\textit{Magnetized Pointer} plant describes a physical model that is rotated through interaction 
-with magnetic fields (typically employed in analogue gauges and indicators).
+\textit{Magnetized Pointer} plant describes a physical model employed in analogue gauges 
+and indicators that is rotated through interaction with magnetic fields.
 \textit{1/4 Car Suspension} plant presents a physical model that connects a car to its wheels 
@@
 $x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.
-
 We have conducted the experimental evaluation on a 12-core 2.40 GHz

### 2017-01-23 cav2017/cav2017.tex
move extensions to appendix
uurghhg fixed point arithmetic section is a mess

@@
 The first is the numeric error introduced by the fixed-point numbers employed to model the plant, i.e. to represent the plant dynamics $A_d$, $B_d$ and its states. 
-The second is the numeric error introduced by the digital controller, 
+The second is the quantization error introduced by the digital controller, 
 which 
-%uses an analogue-to-digital converter to read the states as a fixed-point number and performs operations in this domain. 
 performs operations in the domain of fixed-point numbers. 
@@
 
-Thus far we have presented a verification procedure for a digitalised plant in a continuous space (\emph{ie} the
+Thus far we have presented a verification procedure for a digitalised plant in a continuous space (\emph{i.e.} the
 range of the quantisers is still $\mathbb{R}$. The next step we must realise is that the controller 
@@
 \subsubsection{Effect on safety specification and stability}
-The states values must be computed considering the digital controller error, i.e., the error introduced by the ADC and the digital controller. 
+First consider the effect of the quantization error on safety; the state values must be computed considering the error introduced by the digital controller caused by performing the multiplication $K*x$ at low digital precision.
 %, and the digital reference signal. 
@@
 %and disregarding it in the state equation~\eqref{eq:plant}.
-Thus, the states are computed using the following equations. We use $\mathcal{F}_{\langle I_c,F_c \rangle}$ \todo{explain and clarify notation.}
-to to denote numbers represented with the precision of the digital controller. All other numbers
-are represented with the precision of our plant model:
+Thus, the states are computed using the following equations. We use $\mathcal{F}_{\langle I_c,F_c \rangle}$ 
+to to denote numbers represented with the precision of the digital controller, where $I_c$ is the number of bits used to represent the integer value in the controller and $F_c$ is the number of bits used to represent the fractional part of numbers in the controller.
 %
@@
 %-------------------------------
-\section{Extensions}
-\label{sec:extensions}
-%-------------------------------
-
-%-------------------------------
-\subsection{LTI systems with output} 
-\label{ssec:LTI}
-%-------------------------------
-
-LTI models in the form: 
-%
-\begin{align}
-\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
-\vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
-\end{align}
-\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
-$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
-a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
-(as shown in the appendix) into
-%
-\begin{align}
-\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
-\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
-\end{align}
-%
+\section{Conclusions}
+%-------------------------------
 
@@
 
+%-------------------------------
+\section{Extensions}
+\label{sec:extensions}
+%-------------------------------
+
+%-------------------------------
+\subsection{LTI systems with output} 
+\label{ssec:LTI}
+%-------------------------------
+
+LTI models in the form: 
+%
+\begin{align}
+\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
+\vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
+\end{align}
+\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
+$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
+a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
+(as shown in the appendix) into
+%
+\begin{align}
+\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
+\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
+\end{align}
+%
 \end{document}

### 2017-01-23 cav2017/cav2017.tex
de-vectorizing

@@
 The input specification provided to the program synthesizer is of the form
-$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
-$\vec{P}$ ranges over functions, $\vec{x}$ \todo{now variables are vectorised, however previously the model variables aren't.
-please align notation.
-I do not like to use vectors unless essential, let's say it's a waste of ink in printouts.
-}
+%$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ 
+$\exists P .  \forall x.  \sigma(x, P)$ 
+where $P$ ranges over functions, $x$ 
  ranges over ground terms and
@@
 the aforementioned specification $\sigma$, the inductive synthesis
-procedure tries to find an existential witness $\vec{P}$ satisfying
-the specification $\sigma(\vec{x}, \vec{P})$ for all $\vec{x}$ in {\sc
-  inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
-%
-If the synthesis phase succeeds in finding a witness~$\vec{P}$, this
+procedure tries to find an existential witness $P$ satisfying
+the specification $\sigma(x, P)$ for all $x$ in {\sc
+  inputs} (as opposed to all $x \in \mathcal{D}$).
+%
+If the synthesis phase succeeds in finding a witness~$P$, this
 witness is a candidate solution to the full synthesis formula.  We
 pass this candidate solution to the validation phase, which checks
-whether it is a full solution (i.e., $\vec{P}$ satisfies the
-specification $\sigma(\vec{x}, \vec{P})$ for all
-$\vec{x}\in\mathcal{D}$).  If this is the case, then the algorithm
+whether it is a full solution (i.e., $P$ satisfies the
+specification $\sigma(x, P)$ for all
+$x\in\mathcal{D}$).  If this is the case, then the algorithm
 terminates.  Otherwise, additional information is provided to the

### 2017-01-23 cav2017/cav2017.tex
quantiZation

@@
 Time sampling; 
-Quantisation; 
+quantization; 
 Fixed-point arithmetic; 
@@
 %exacerbated by specific artefacts,  
-the effects of finite-precision arithmetic, time discretization, and quantisation noise, which are typically introduced 
+the effects of finite-precision arithmetic, time discretization, and quantization noise, which are typically introduced 
 by Analogue-to-Digital (A/D) and Digital-to-Analogue (D/A) conversion.  
@@
 and with initial state $x_{0}=x(0)$. $A_d$ and $B_d$ denote the discretized matrices of $A$ and $B$, the plant dynamics. 
-Later, we will deal with the issue of variable quantisation, as introduced by the ADC and DAC blocks.
+Later, we will deal with the issue of variable quantization, as introduced by the ADC and DAC blocks.
 
@@
 
-%\addtodo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantisation noises yet).]}
+%\addtodo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantization noises yet).]}
 
@@
 Thus far we have presented a verification procedure for a digitalised plant in a continuous space (\emph{i.e.} the
-range of the quantisers is still $\mathbb{R}$. The next step we must realise is that the controller 
+range of the quantizers is still $\mathbb{R}$. The next step we must realise is that the controller 
 exists in a digital program, hence its domain is $\mathbb{R}\langle I,F\rangle$.
@@
 the fixed word restrictions in their composing elements.
-Apart from the quantisation errors $q_1,q_2$ there are rounding errors in the calculation of $u_k$. 
-These will introduce a new source of quantisation noise which we may denote $\vec{\nu}_3 \in [-q_3\ \ q_3]$.
+Apart from the quantization errors $q_1,q_2$ there are rounding errors in the calculation of $u_k$. 
+These will introduce a new source of quantization noise which we may denote $\vec{\nu}_3 \in [-q_3\ \ q_3]$.
 The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=(|\mat{K}|_1+1)c_m$

### 2017-01-23 cav2017/cav2017.tex
itemised as requested

@@
 
-\todo{please eventually itemize next}
-
-1. The inductive synthesis phase (i.e. {\sc synthesise}) uses BMC to
+%\todo{please eventually itemize next}
+\begin{enumerate}
+\item The inductive synthesis phase (i.e. {\sc synthesise}) uses BMC to
 compute a candidate solution $K$
@@
 
-2. The first {\sc verify} stage, {\sc safety}, checks that the candidate
+\item The first {\sc verify} stage, {\sc safety}, checks that the candidate
 solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
@@
 
-3. The second {\sc verify} stage, {\sc precision}, 
+\item The second {\sc verify} stage, {\sc precision}, 
  restores soundness with respect to the plant's precision
@@
 
-4. The third {\sc verify} stage, {\sc complete}, checks that the
+\item The third {\sc verify} stage, {\sc complete}, checks that the
 current $k$ is large enough to ensure that the boundaries are not
@@
 
-5. The last {\sc verify} stage, {\sc sampling}, 
+\item The last {\sc verify} stage, {\sc sampling}, 
 ensures that the current sampling rate is large enough by using an 
@@
 
+\end{enumerate}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-01-23 cav2017/cav2017.tex
more revision of the AA based CEGIS sec

@@
 \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
-\item Calculate a set of initial bounds on K based on the input constraints. $$\phi_{safety} \Leftrightarrow u_k=r-Kx_k : x \in X^\# \wedge u_k \in [\underline{u}\ \ \overline{u}]$$
+\item Calculate a set of initial bounds on K based on the input constraints. Note that these bounds will be used during the 
+synthesis phase to reduce the size of the solution space.
+$$\phi_{safety} \Leftrightarrow u_k=-Kx_k : x_0 \in [\underline{x_0} \ \overline{x_0}] \wedge u_k \in [\underline{u}\ \ \overline{u}]$$
 \end{enumerate}
-\item Next we synthesise a candidate controller. 
-We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability specification defined by Jury's criteria.
-%, and try to synthesise a controller that meets these specs.
+\item In this phase we synthesise a candidate controller
+%We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability 
+% specification defined by Jury's 
+%criteria. %, and try to synthesise a controller that meets these specs.
 % For a stabilized closed-loop, which is necessary for our safety property, we need
@@
 % safety specification $\phi_{safety}$.
-
-Let $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ be a program describing Jury's method.
-\begin{enumerate}
-\item Select a controller $\tilde{\mat{K}} \in \mathbb{R}\langle I,F\rangle^n$.
-This is achieved by solving a SAT formula $\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{input}$ that satisfies the input constraint and Jury's criteria for $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \mat{K}=\tilde{\mat{K}}\mat{T}$.
-\item If there is no candidate solution we return UNSAT and exit the loop.
-\end{enumerate}
-\item Once we have a candidate solution, we perform a safety verification using abstract acceleration.
-For this purpose, we make use of a second abstraction that encompasses the accelerated continuous reach-tube over an unbounded time.
-% If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
-%
-The first step constraints
-\begin{equation}
-\mat{K} \models u_k=-\mat{K}x_k : \phi_{safety}
-\label{eq:of_bounds}
-\end{equation}
-The second step is evaluating the progression of the system over time to evaluate 
-$x_{k+1} \models \phi_{safety}$. For this step we require 
-an initial set from which the system progresses. Obviously, this set $x_0$ 
-must satisfy the specification; otherwise, the system will be unsafe to begin with.
-We accept a specification in the form $\mat{E}\mat{T}x_0<\mat{f}$. 
-The presence of $\mat{T}$ is because this will typically be given in the original 
-state-space. Accelerating \eqref{eq:observer_LTI_cf}, we obtain:
+as a model $\mat{K} \in \mathbb{R}\langle I,F\rangle^n$. We obtain it by solving the SAT formula 
+$$\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{safety}$$ 
+that satisfies the input constraint and Jury's criteria for 
+$P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \tilde{\mat{K}}=\mat{K}\mat{T}$,
+where $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ is a program describing Jury's method.
+If there is no candidate solution we return UNSAT and exit the loop.
+\item Once we have a candidate solution, we perform a safety verification % If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
+%
+consisting of evaluating the progression of the system over time,
+$x_{k+1} \models \phi_{safety}$. For this purpose we require 
+an initial set $\phi_{init}= x_0 \in [\underline{x_0} \ \overline{x_0}]$ 
+from which the system progresses. % Obviously, this set $x_0$ 
+% must satisfy the specification; otherwise, the system will be unsafe to begin with.
+% We accept a specification in the form $\mat{E}\mat{T}x_0<\mat{f}$. 
+% The presence of $\mat{T}$ is because this will typically be given in the original 
+% state-space.
+Next, we use abstract acceleration to get a second abstraction that 
+encompasses the accelerated continuous reach-tube over an unbounded time.
+Accelerating \eqref{eq:observer_LTI_cf}, we obtain:
 %
 \begin{align}
-\label{eq:acc_observer_LTI_cf}
+%\label{eq:acc_observer_LTI_cf}
 x=&\mat{A}_t^kx_0

### 2017-01-23 cav2017/cav2017.tex
removed addressed todo on de-vectorization in sec 4.5
"proof" for stability being independent of FWL error - not sure this is right

@@
 The input specification provided to the program synthesizer is of the form
-%$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ 
+%$\exists P .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ 
 $\exists P .  \forall x.  \sigma(x, P)$ 
@@
 ``cf'' to denote Controllable Canonical Form):
-\todo{eliminate vectors}
+%\todo{eliminate vectors}
 %
@@
 
+%-------------------------------
+\subsection{Stability of closed-loop systems with fixed-point controller error}
+%-------------------------------
+
+The proof above relies on the fact that the relationship between states and next states is defined by
+$x_{k+1} = (A_d  - B_dK)*x_k$, all computed at infinite precision. In fact, when we employ a FWL digital controller, 
+the operation becomes:
+\begin{align*}
+x_{k+1} &= A_d * x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
+x_{k+1} &= (A_d  - B_dK)*x_k + B_dK\delta
+%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
+\end{align*}
+where $\delta$ is the maximum error that can be introduced by the FWL controller in one step, i.e., by reading the states values once and multiplying by $K$ once.
+We derive the closed form expression for $x_n$
+
+\begin{align*}
+x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
+x_{2} &= (A_d  - B_dK)((A_d  - B_dK)x_0 + B_dK\delta ) + B_dK\delta \\
+      &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
+x_{3}  &=(A_d  - B_dK)^3x_0 + (A_d  - B_dK)^2B_dK\delta + (A_d  - B_dK)B_dK\delta + B_dK\delta\\
+x_{k+1} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
+\end{align*}
+
+The definition of asymptotic stability is that the system converges to a reference signal, in this case we use no
+reference signal so an asymptotically stable system will converge to the origin. We know that the original system
+with an infinite precision controller is stable, because we have synthesised it to meet Jury's criteria. Hence
+$(A_d  - B_dK)^n*x_0$ must converge to zero.
+
+Hence, we can show that a fixed point implementation of the same controller will converge to a steady value, as 
+all terms that contain $(A_d  - B_dK)^k$ will eventually converge to zero, and the remaining non-converging term is $B_dK\delta$.
+
+We do not require asymptotic stability to ensure safety, we do require that the controller converges to a steady value 
+in the safe state values.
+
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-01-23 cav2017/cav2017.tex
text

@@
 
-In \cite{DBLP:journals/corr/AbateBCCDKK16}, Abate et al.  focus on
-synthesising stabilising controllers for continuous plants
-by exploiting advantage in bit-accurate verification of software-implemented 
-digital control~\cite{Bessa16}.  While they also make use of a CEGIS-based 
-technique, their approach is restricted to synthesising controllers for hybrid 
-closed-loop systems that are stable and only consider transfer function models.  
-In contrast, in the current paper, we consider a state-space
-representation of the physical system, which allows us to synthesise controllers that
-make the closed-loop system \emph{safe} as well as stable.  Moreover, 
-a key aspect of the second approach we evaluate
-is that we integrate abstraction
-refinement inside the CEGIS loop.
+The work in \cite{DBLP:journals/corr/AbateBCCDKK16} investigates the synthesis of 
+stabilising controllers for continuous plants described as transfer functions, 
+by exploiting bit-accurate verification of software-implemented 
+digital controllers~\cite{Bessa16}.  While this work also make use of a CEGIS-based technique, 
+the approach is restricted to synthesising digital controllers for stable 
+closed-loop systems described via transfer function models.  
+In contrast, in the current paper we consider a state-space representation of the physical system, 
+which is known to be more general \cite{Astrom08} and allows to synthesise controllers that
+make the closed-loop system \emph{safe}.  Moreover, 
+this work  integrates an abstraction/refinement step inside the main CEGIS loop.
 
@@
 \label{eq:closedloopss}
-x_{k+1} = ( A_d - B_d K ) + B_d r_k.
+x_{k+1} = ( A_d - B_d K ) x_k + B_d r_k.
 \end{align}
@@
 
-Asymptotic stability boils down to Lyapunov stability and convergence to an equilibrium point\cite{Astrom08} %\todo{add reference}.  
+Asymptotic stability boils down to Lyapunov stability and convergence to an equilibrium point~\cite{Astrom08}.  %\todo{add reference}.  
 Lyapunov stability requires that model trajectories remain in a neighbourhood of the equilibrium point. 
@@
 0			& 0.01562 	& 0			\\	
-\end{array}\right]$ & , $\left[\begin{array}{c}
+\end{array}\right]$ & $\left[\begin{array}{c}
 1 \\ 0 \\ 0

### 2017-01-23 cav2017/cav2017.tex
convergence of error term

@@
 x_{3}  &=(A_d  - B_dK)^3x_0 + (A_d  - B_dK)^2B_dK\delta + (A_d  - B_dK)B_dK\delta + B_dK\delta\\
-x_{k+1} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
+x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
+  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{i=n-1}(A_d - B_dK)^iB_dk\delta
 \end{align*}
@@
 
-Hence, we can show that a fixed point implementation of the same controller will converge to a steady value, as 
-all terms that contain $(A_d  - B_dK)^k$ will eventually converge to zero, and the remaining non-converging term is $B_dK\delta$.
-
-We do not require asymptotic stability to ensure safety, we do require that the controller converges to a steady value 
-in the safe state values.
+To show that a fixed point implementation of the same controller will converge to a steady value, we need to show that the infinite sum converges.
+
+A known result is that a power series of matrices converges iff the eigenvalues of the matrix are less than 1.
+
+\todo[inline]{complete this, show convergence}
 

### 2017-01-23 cav2017/cav2017.tex
text

@@
 
-Program synthesis is the problem of computing correct-by-design programs
-from high-level specifications; algorithms for this problem have made
-substantial progress in recent years.  One such
-approach~\cite{itzhaky2010simple} inductively synthesises invariants to
+Program synthesis is the problem of computing correct-by-design programs from high-level specifications; 
+algorithms for this problem have made substantial progress in recent years.  
+One such approach~\cite{itzhaky2010simple} inductively synthesises invariants to
 generate the desired programs.
@@
 Program synthesizers are an ideal fit for synthesis of %parametric
-controllers since the semantics of programs capture effects such as FWL
+digital controllers, since the semantics of programs capture effects such as FWL
 precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
 for the synthesis of switching controllers for stabilising continuous-time
-plants with polynomial dynamics.  The work extends to its application on
-affine systems, finding its major challenge in the hardness of solving
-linear arithmetic with the state-of-the-art SMT solvers.  Since this
-approach uses switching states instead of linear dynamics in the digital
-controller, it entirely circumvents the FWL problem.  It is also not
-suitable for the kind of control we seek to synthesise.
+plants with polynomial dynamics.  The work extends to affine systems, 
+finding a major challenge in the hardness of solving linear arithmetic with the state-of-the-art SMT solvers.  
+Since this approach uses switching models instead of linear dynamics for the digital controller, 
+it entirely circumvents the FWL problem, but potentially incurs state-space explosion issues.  
+This approach is not suitable for the kind of control we seek to synthesise.
 
@@
 use a CEGIS-based approach for synthesising continuous-time switching
-controllers that guarantee Reach While Stay properties of closed
-loop systems, i.e., properties that specify a set of goal states and safe states.%}. 
+controllers that guarantee \emph{reach-while-stay} properties of closed-loop systems, 
+i.e., properties that specify a set of goal states and safe states (constrained reachability).%}. 
 The solution is based on synthesising control Lyapunov 
@@
 The tool Pessoa~\cite{mazo2010pessoa} is a MatLab toolbox that synthesises correct-by-design
-embedded control software. It is based on the principle of describing a physical system
-as an equivalent finite-state machine and computing reachability over the finite-state 
-machine. Pessoa can synthesise safe embedded controller software for a range of properties based on a safety specification over state
-values, as well as specification on characteristic functions of the controller. 
-However, Pessoa does not have native inclusion of the ADC/DAC quantization error needed for
-synthesising a fixed-point digital controller.
+embedded control software. It is based on the description of a physical system
+as an equivalent finite-state machine and on the computation of reachability properties over the finite-state 
+machine. 
+Based on this safety specification over state values, 
+Pessoa can synthesise embedded controller software for a range of properties.  
+%based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
+However, Pessoa does not have native inclusion of the ADC/DAC quantisation error needed for
+synthesising fixed-point digital controllers.
 
 We use a combination of a synthesis engine with a control
-verification tool that addresses the challenges presented here in the
-form of FWL effects and stability measures for LTI SISO controllers.
-
-We take the former from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
+verification tool that addresses the challenges presented in the
+form of FWL effects and stability measures over digital controllers for LTI models.
+
+We take the synthesis engine from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
 the first approach we present, performs bounded model checking of control properties,
-based on~\cite{Monteiro16}, but 
-enhanced to include evaluation of quantization effects and safety properties
-over the state space. In the second approach, we use a verification engine
-based on abstract acceleration~\cite{cattaruzza2015unbounded} than avoids the explicit 
-unwinding the transition system necessarily for the first approach.
+based on~\cite{Monteiro16}, but enhanced to include evaluation of quantisation effects and safety properties
+over the state space. In an alternative approach, we use a verification engine based on abstract acceleration~\cite{cattaruzza2015unbounded}, 
+which avoids the explicit unwinding the transition system necessarily for the first approach.
 

### 2017-01-23 cav2017/cav2017.tex
text

@@
 
-The classical approach to control synthesis has often disregarded
-quantization as a minimal effect, thus proving unsound in the case of digital control systems.
-Modern techniques focus on different elements of the discretization effect, including delayed
-response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics with
-the goal to either verify (e.g.~\cite{daes20161}) or optimise
+The classical approach to control synthesis has often disregarded quantization, 
+thus resulting in general to unsound digital controllers. 
+Modern techniques focus on different elements of discretization effects, including delayed
+response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics, 
+with the goal either to verify (e.g.~\cite{daes20161}) or to optimise
 (e.g.~\cite{oudjida2014design}) given implementations.
@@
 is the error in the dynamics caused by the inability to represent the exact
-state of the physical system while the second relates to rounding errors
+state of the physical system, while the second relates to rounding errors
 during computation.  In~\cite{fialho1994stability}, a stability measure
@@
 checked by bounding the error.  An alternative approach is taken
-by~\cite{park2016scalable}, where the verification of existing code is
+by~\cite{park2016scalable}, where the verification of given control code is
 performed against a known model by extracting an LTI model of the code
@@
 set. In a similar fashion, \cite{liberzon2003hybrid} evaluates the dynamics of the
-quantization error and binds their trajectory to a known region over a finite
+quantization error and bounds its trajectory to a known region over a finite
 period of time. This technique works for both linear and non-linear systems.
 This paper uses an approach that projects the maximum effect of the noise over
-an unbounded time and uses it as a `buffer' region for the safety specification.
+an unbounded time and uses it as a buffer region for the safety specification.
 

### 2017-01-23 cav2017/cav2017.tex
text

@@
 \subsubsection{Effect on safety specification and stability}
-First consider the effect of the quantization error on safety; the state values must be computed considering the error introduced by the digital controller caused by performing the multiplication $K*x$ at low digital precision.
+First consider the effect of the quantization error on safety; the state values must be computed considering the error introduced by the digital controller caused by performing the vector multiplication $Kx$ at low digital precision.
 %, and the digital reference signal. 
@@
 %and disregarding it in the state equation~\eqref{eq:plant}.
-Thus, the states are computed using the following equations. We use $\mathcal{F}_{\langle I_c,F_c \rangle}$ 
-to to denote numbers represented with the precision of the digital controller, where $I_c$ is the number of bits used to represent the integer value in the controller and $F_c$ is the number of bits used to represent the fractional part of numbers in the controller.
+Thus, the states are computed using the following equations. We use $\mathcal{F}_{\langle I_c,F_c \rangle}$ \todo{These notations are different from those above.}
+to to denote numbers represented with the precision of the digital controller, where $I_c$ is the number of bits used to represent the integer value in the controller and $F_c$ is the number of bits used to represent the fractional part of the numbers manipulated within the controller.
 %
@@
 
-We note that the effect on stability due to the fixed-word-length error is that the system may, instead of converging to the desired equilibrium point, converge to a point that is $\delta$ away from the desired equilibrium point, see Appendix.
+We note that the effect on stability due to the fixed-word-length error is that the system may, instead of converging to the desired equilibrium point, converge to a point that is bounded away from the desired equilibrium point (see Appendix for details).
 In this paper, we are concerned with \emph{safe} controllers and therefore concerned only that the system converges to a point within the safety specification.

### 2017-01-24 cav2017/cav2017.tex
added running example for the multi-staged verif approach

@@
 \end{enumerate}
+
+\subsubsection{Illustrative Example} \label{sec:running-ex}
+
+We illustrate our approach with \todo{what example is this?} example,
+extracted from the literature~\cite{?}.
+%% Next, we demonstrate how our approach solves the synthesis problem for this
+%% example.
+
+We start with a candidate solution with all coefficients zero, $K=[0
+  \ 0 \ 0]^T$, and a precision of $I_p=13$, $F_p=3$.  In the first
+{\sc verify} stage, the {\sc safety} check finds the counterexample
+%
+$ x_0 = [-0.5 \ 0.5 \ 0.5] $.
+%
+After adding the new counterexample to its sets of {\sc inputs}, {\sc
+  synthesize} finds the candidate solution $K=[0 \ 0
+  \ 0.00048828125]^T$, which prompts the {\sc safety} verifier to
+return $x_0=[-0.5 -0.5 -0.5]$ as the new counterexample.
+
+In the subsequent iteration, the synthesiser can't find any more
+candidates and returns UNSAT, meaning that the current precision is
+insufficient.  Consequently, we increase the precision to $I_p=17$,
+$F_p=7$.
+%
+Since the previous counterexamples were obtained at lower precision,
+we remove them from the set of counterexamples.  Back in the {\sc
+  synthesize} phase, we re-start the process with a candidate solution
+with all coefficients $0$.  Next, the {\sc safety} verification stage
+provides the first counterexample at higher precision, $x_0=[-0.5
+  \ 0.5 \ 0.5]$ and {\sc synthesize} finds $K=[0 \ 0.01171875
+  \ 0.015625]^T$ as a candidate that eliminates this counterexample.
+However, this candidate triggers the counterexample
+$x_0=[0.5\ -0.5\ -0.5]$ found again by the {\sc safety} verification
+stage.  In the next iteration, we get the candidate $K=[0 \ 0
+  \ -0.015625]$, followed by the counterexample $x_0 = [0.5 \ 0.5
+  \ 0.5]$. Finally, {\sc synthesize} find the candidate $K=[0.01171875
+  \ -0.013671875 \ -0.013671875]$, which is validated as a final
+solution by all the verification stages.
+
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-01-24 cav2017/cav2017.tex
added figure about completeness threshold
reviewed Illustrative Example for CT

@@
 
-\todo[inline] {please will Alessandro write the proof for the completeness threshold here - EP}
-\missingfigure{picture for completeness threshold}
+%\todo[inline] {please will Alessandro write the proof for the completeness threshold here - EP}
+%\missingfigure{picture for completeness threshold}
+
+\begin{figure*}[t]
+\centering
+\includegraphics[width=0.7\textwidth]{ct.eps}
+\vspace{0.1cm}
+\caption{Completeness threshold}
+\end{figure*}
 
@@
 We illustrate our approach with \todo{what example is this?} example,
-extracted from the literature~\cite{?}.
+extracted from the literature~\cite{Franklin15}.
 %% Next, we demonstrate how our approach solves the synthesis problem for this
@@
 
-In the subsequent iteration, the synthesiser can't find any more
-candidates and returns UNSAT, meaning that the current precision is
+In the subsequent iteration, the synthesiser is unable to find further 
+suitbale candidates and it returns UNSAT, meaning that the current precision is
 insufficient.  Consequently, we increase the precision to $I_p=17$,
@@
   \ -0.015625]$, followed by the counterexample $x_0 = [0.5 \ 0.5
-  \ 0.5]$. Finally, {\sc synthesize} find the candidate $K=[0.01171875
+  \ 0.5]$. Finally, {\sc synthesize} finds the candidate $K=[0.01171875
   \ -0.013671875 \ -0.013671875]$, which is validated as a final
-solution by all the verification stages.
+solution by all verification stages.
 

### 2017-01-24 cav2017/cav2017.tex

@@
 
-A known result is that a power series of matrices converges iff the eigenvalues of the matrix are less than 1.
-
-\todo[inline]{complete this, show convergence}
+A known result is that a power series of matrices converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less than 1, to the following:
+\begin{align*}
+\sum_{i=0}^{\inf}T^i  &= (I - T)^-1
+\end{align*}
+Where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge
+
+\begin{align*}
+x_{\inf} &= 0 + (I - A_d + B_dK)^-1\B_dk\delta
+\end{align*}
+
+Hence, provided $(I - A_d + B_dK)^-1\B_dk\delta$ is within the safe space, our fixed point controller system is stable, in that it converges to a finite value, although not asymptomatically stable because it doesn't converge to the origin.
 

### 2017-01-24 cav2017/cav2017.tex
infty
fix undefined

@@
 \begin{align*}
-\sum_{i=0}^{\inf}T^i  &= (I - T)^-1
+\sum_{i=0}^{\infty}T^i  &= (I - T)^-1
 \end{align*}
@@
 \begin{align*}
-x_{\inf} &= 0 + (I - A_d + B_dK)^-1\B_dk\delta
+x_{\infty} &= 0 + (I - A_d + B_dK)^{-1}B_dk\delta
 \end{align*}
 
-Hence, provided $(I - A_d + B_dK)^-1\B_dk\delta$ is within the safe space, our fixed point controller system is stable, in that it converges to a finite value, although not asymptomatically stable because it doesn't converge to the origin.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{LTI system Transformations and Equivalencies} \label{sec:appendix}
+Hence, provided $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the safe space, our fixed point controller system is stable, in that it converges to a finite value, although not asymptomatically stable because it doesn't converge to the origin.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{LTI system Transformations and Equivalences} \label{sec:appendix}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-01-24 cav2017/cav2017.tex
fixed point representations

@@
 
-The 
-%systems and 
-models we consider have two sources of error due to numeric representation. 
+The models we consider have two sources of error due to numeric representation. 
 The first is the numeric error introduced by the fixed-point numbers employed to model the plant, i.e. to represent the plant dynamics $A_d$, $B_d$ and its states. 
@@
 In this section we formally outline the errors introduced by fixed-point representation of numbers.
-In further sections we will differentiate between these two errors, 
-by referring to them as the \emph{plant error} and the \emph{digital controller error} respectively.
-
-Let $\mathbb{R} \langle I,F \rangle$ \todo{notice this notation differs from the one used above} be a fixed point domain with $I$ bits representing the integer part 
-and $F$ bits representing the decimal part \todo{why R, comment on that.}. The smallest number that can be represented in this domain is $c_m=2^{-F}$.
+
+Let $\mathcal{F}\langle I,F \rangle(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part.
+The smallest number that can be represented in this domain is $c_m=2^{-F}$.
+
+%Let $\mathbb{R} \langle I,F \rangle$ \todo{notice this notation differs from the one used above} be a fixed point domain with $I$ bits representing the integer part 
+%and $F$ bits representing the decimal part \todo{why R, comment on that.}. The smallest number that can be represented in this domain is $c_m=2^{-F}$.
 The following approximation errors will arise:
@@
 \item {\bf Truncation:}
-Let $\mathcal{F}\langle I,F \rangle(\cdot) : \mathbb{R} \rightarrow \mathbb{R}\langle I,F \rangle, \tilde x=\mathcal{F}\langle I,F \rangle(x) = x-\delta_T : \delta_T=x\ \%_{c_m}\ \tilde x$, where $\%_{c_m}$ is the modulus operation performed on the last bit.
+Let $x$ be a real number, and $\mathcal{F}\langle I,F \rangle(x)$ be the same number represented in a fixed point domain as above.
+$\mathcal{F}\langle I,F \rangle(x) = x-\delta_T : \delta_T=x\ \%_{c_m}\ \tilde x$, where $\%_{c_m}$ is the modulus operation performed on the last bit.
+%Let $\mathcal{F}\langle I,F \rangle(\cdot) : \mathbb{R} \rightarrow \mathbb{R}\langle I,F \rangle, \tilde x=\mathcal{F}\langle I,F \rangle(x) = x-\delta_T : \delta_T=x\ \%_{c_m}\ \tilde x$, where $\%_{c_m}$ is the modulus operation performed on the last bit.
 So $\delta_T$ is the truncation error and it will propagate across operations.
 \item {\bf Rounding:}
-The following errors appear in simple operations:
+The following errors appear in simple operations.
+Let $c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be the truncation errors caused by representing $c_1$ and $c_2$ in the fixed-point domain as above.
 \begin{enumerate}
 \item Addition/Subtraction: these operations only propagate errors coming from truncation of the operands. 
-\todo{the following maths is loose. fix as follows: define terms with their domain. define operation. apply operator $\mathcal{F}$ above. derive bound. }
-$c_1\pm c_2= c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$ 
-\item Multiplication: $c_1 * c_2= c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}*c_2| + |\delta_{T2}*c_1| + c_m$  \todo{same as above.}
-\item Division will not be applied in these implementations. \todo{why not? comment further.}
+$\mathcal{F}\langle I,F \rangle(c_1) \pm \mathcal{F}\langle I,F \rangle(c_2) = c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
+
+%$c_1\pm c_2= c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$ 
+\item Multiplication: $\mathcal{F}\langle I,F \rangle(c_1) * \mathcal{F}\langle I,F \rangle(c_2) =  c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}*\mathcal{F}\langle I,F \rangle(c_2)| + |\delta_{T2}*\mathcal{F}\langle I,F \rangle(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
+\item Division is only needed for positive numbers in this implementation (where it is needed for checking stability). 
 \end{enumerate}
@@
   %Another source of error introduced by Finite Word Length representations is that of overflow.
-  The finite word length set a
-maximum representable number in the domain \todo{what is next?
+The maximum size of a real number $x$ that can be represented in a fixed point domain as $\mathcal{F}\langle I,F \rangle(x)$ is $\pm (2^{I-1}+1-2^{-F})$.
+Numbers outside this range cannot be represented by the domain.
+We assume no saturation (where any overflow is represented as the largest or smallest possible number), and check that overflow does not occur.
+
+%The finite word length set a
+%maximum representable number in the domain \todo{what is next?
 a domain?
 define formally, no back-of-the-envelope mathsy stuff.} ($\pm (2^{I-1}+1-2^{-F})$), which means that any number outside this range
-cannot be represented by the domain. Our tool currently assumes no saturation
-function and verifies that no state overflows.
+%cannot be represented by the domain. Our tool currently assumes no saturation
+%function and verifies that no state overflows.
 \end{enumerate}
@@
 
-\todo{yes, please reformat the discussion below so that it fits the discussion above. }
-
-Thus far we have presented a verification procedure for a digitalised plant in a continuous space (\emph{i.e.} the
-range of the quantizers is still $\mathbb{R}$. The next step we must realise is that the controller 
-exists in a digital program, hence its domain is $\mathbb{R}\langle I,F\rangle$.
+We will use $\mathcal{F}\langle I_c,F_c \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}\langle I_p,F_p \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model.
+Thus any mathematical operations occurring in the digital controller will occur in the domain $\mathcal{F}\langle I_c,F_c \rangle$, and all other calculations will be carried out in the domain $\mathcal{F}\langle I_p,F_p \rangle$.
+
+%Thus far we have presented a verification procedure for a digitalised plant in a continuous space (\emph{i.e.} the
+%range of the quantizers is still $\mathbb{R}$. The next step we must realise is that the controller 
+%exists in a digital program, hence its domain is $\mathbb{R}\langle I,F\rangle$.
 We have $\mat{A},\mat{B},\vec{x} \in \mathbb{R}^*$, $\mat{K}_d,\vec{u},\hat{\vec{x}}=\mathcal{F}\langle I,F \rangle(\vec{x}) \in \mathbb{R}\langle I,F\rangle^*$
-Where $*$ represents the appropriate dimension for each matrix/vector.
-Unfortunately this means that although the closed loop dynamics are in the reals, they suffer from
-the fixed word restrictions in their composing elements.
-Apart from the quantization errors $q_1,q_2$ there are rounding errors in the calculation of $u_k$. 
-These will introduce a new source of quantization noise which we may denote $\vec{\nu}_3 \in [-q_3\ \ q_3]$.
-The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=(|\mat{K}|_1+1)c_m$
-
-\bigskip
+%Where $*$ represents the appropriate dimension for each matrix/vector.
+%Unfortunately this means that although the closed loop dynamics are in the reals, they suffer from
+%the fixed word restrictions in their composing elements.
+%Apart from the quantization errors $q_1,q_2$ there are rounding errors in the calculation of $u_k$. 
+%These will introduce a new source of quantization noise which we may denote $\vec{\nu}_3 \in [-q_3\ \ q_3]$.
+%The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=(|\mat{K}|_1+1)c_m$
 
 \subsubsection{Effect on safety specification and stability}
-First consider the effect of the quantization error on safety; the state values must be computed considering the error introduced by the digital controller caused by performing the vector multiplication $Kx$ at low digital precision.
-%, and the digital reference signal. 
-%In this paper, we consider systems with a reference signal equal to zero. 
-%the FWL effects in all operations related to the control action~\eqref{eq:controlaction} 
-%and disregarding it in the state equation~\eqref{eq:plant}.
-Thus, the states are computed using the following equations. We use $\mathcal{F}_{\langle I_c,F_c \rangle}$ \todo{These notations are different from those above.}
-to to denote numbers represented with the precision of the digital controller, where $I_c$ is the number of bits used to represent the integer value in the controller and $F_c$ is the number of bits used to represent the fractional part of the numbers manipulated within the controller.
-%
+Thus we can consider the effect of these errors on our safety and stability verification.
+
+First consider the effect of the quantization errors on safety; the state values must be computed considering the error introduced by the digital controller caused by performing the vector multiplication $Kx$ at low digital precision.
+
+The states are computed using the following equations. 
 \begin{align*}
 u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  
-%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
+% x_{k+1}&=A_d x_{k} + B_du_{k}
 \end{align*}
+
+This will induce two types of the error detailed above, first the truncation errors due to representing $x_k$ as ${\langle I_c,F_c \rangle}(x_{k})$, and second the rounding error introduce by multiplying $x_k$ and $K$.
+We represent these errors as non-deterministic noise.
+
+A further error is caused by the representation of the plant dynamics.
+\begin{align*}
+\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k})&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
+\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k})(x_{k+1}) &=\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k})(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(u_{k})(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(u_{k})(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k})(u_{k})
+\end{align*}
+
+We address these errors by use of a final verification check that uses interval arithmetic~\cite{moore1966interval}.
 

### 2017-01-24 cav2017/cav2017.tex
add pseudocode for stability, some formatting to Alessandro's proofs

@@
 Sec.~\ref{ssec:stability} and the safety specification in Sec.~\ref{ssec:safety}.
+To synthesise a controller that satisfies the stability criteria, we require that
+a computed characteristic polynomial satisifies Jury's criteria. The details of this
+calculation can be found in the Appendix.
+
 %% The stability criteria are satisfied if the characteristic polynomial of $A_d - B_d * K_d$ meets Jury's criteria. This is 
@@
 \begin{algorithmic}[1]
+\Function{$stabilityCheck()$}{}
+  \State computecharPoly($A_d - B_dK$)
+  \State assert(Jury's criteria hold)
+  %\State Return $K$
+\EndFunction
+\end{algorithmic}
+\label{alg:stabilitycheck}
+\end{algorithm}
+
+\begin{algorithm}[]
+\begin{algorithmic}[1]
 \Function{$safetyCheck()$}{}
 	\State assert($ \underline{u}  \leq u \leq \overline{u}$)
+  \State assert($ \underline{x_0}  \leq x_0 \leq \overline{x_0}$)
 	\While{$i=0; i< k; i++$}
@@
 
-\todo[inline]{please will Alessandro write out the proof that checking only the corner cases is valid for the safety verification - EP}
-
-Proof. 
-Consider the set of initial states, $X_0$, assumed to be convex since it's a box. 
+\begin{proof} 
+Consider the set of initial states, $X_0$, assumed to be convex since it's a hypercube. 
 Name $v_i$ its vertexes, where $i=1,\ldots, 2^n$.  
 Thus any point $x \in X_0$ can be expressed by convexity as $x = \sum_{i=1}^{2^n} \alpha_i v_i$, 
-where $\sum_{i=1}^{2^n} \alpha_i =1$. 
-So then if $x_0=x$, then $x_k = (A_d - B_d K)^k x = 
-(A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i = 
-\sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i  = 
-\sum_{i=1}^{2^n} \alpha_i x_k^i$, 
-where I have denoted with $x_k^i$ the trajectories obtained from the single vertexes $v_i$.QED
+where $\sum_{i=1}^{2^n} \alpha_i =1$. \\
+So then if $x_0=x$, then 
+\begin{align*}
+x_k   &= (A_d - B_d K)^k x \\
+      &= (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i \\
+      &= \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i \\
+      &= \sum_{i=1}^{2^n} \alpha_i x_k^i
+ \end{align*}     
+where $x_k^i$ denotes the trajectories obtained from the single vertexes $v_i$. 
+\end{proof}
 
@@
 
-Proof sketch. 
+\begin{proof}
 Consider spectrum of matrix $(A_d - B_d K)$ and select eigenvalue with smallest (non trivial) imaginary value.  
@@
 So surely taking $k$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, after $k$ steps we've completed a rotation. 
-This is the CT.
-
+This is the completeness threshold. 
+\end{proof}
 \item The last {\sc verify} stage, {\sc sampling}, 

### 2017-01-24 cav2017/cav2017.tex
added contributions

--- 2017-01-24 cav2017/cav2017.tex
@@
 to seek alternative stabilising feedbacks, benefiting from the obtained counter-examples 
-to safety.
-
-The approach is proven sound by accounting for errors due to the digitalisation of signals that are manipulated by the controller block.  
+to safety. The approach is proven sound by accounting for errors due to the digitalisation 
+of signals that are manipulated by the controller block.  
 The proposed synthesis approaches and a developed tool are evaluated considering 
@@
 potential safety by unfolding the dynamics of the system and checking for 
-a completeness threshold. \textcolor{red}{Dario: Can you please briefly explain your approach?
-In the second approach,...}
-
-\textcolor{red}{we have to connect both paragraphs...}
-
-To this end, we formalise the notion of solution generalisation for
-Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
-of abstraction refinement in order to achieve scalability.
-This strategy enables the inductive generalisation engine inside CEGIS
-to look for candidate solutions in a reduced solution space.
-
-\addtodo{We have to summarise our main contributions here}
+a completeness threshold. In the second approach, we employ abstract acceleration
+to accelerate the dynamics forward instead of symbolically unwinding the 
+transition relation~\cite{cattaruzza2015unbounded}.
+
+%\textcolor{red}{we have to connect both paragraphs...}
+
+%To this end, we formalise the notion of solution generalisation for
+%Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
+%of abstraction refinement in order to achieve scalability.
+%This strategy enables the inductive generalisation engine inside CEGIS
+%to look for candidate solutions in a reduced solution space.
+
+In summary, this paper makes the following original contributions.
+%
+\begin{itemize}
+
+\item We design and implement two approaches to synthesize 
+  digital feedback control architectures for physical plants, 
+	considering dynamical equations with inputs that evolves over 
+	a continuous state space. In both approaches, we apply CEGIS to 
+	devise a digital controller that stabilizes the system and we then
+	we verify safety by means of either forward reachability analysis 
+	via dynamics unfolding or invariant set generation via 
+	abstract acceleration.
+
+\item We provide experimental results showing that our approaches
+  are able to efficiently synthesize stable and safe controllers 
+	for a set of intricate physical plant models taken from the digital 
+	control literature: the median runtime for our benchmark
+  set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
+  than \textcolor{red}{$XXX$} seconds.
+
+\end{itemize}
 

### 2017-01-24 cav2017/cav2017.tex
squeeze abstract

@@
 \begin{abstract}
-This work presents a sound and automated approach to synthesise 
+This work presents a sound and automated approach to synthesize 
 digital feedback control architectures for physical plants represented 
 as linear, time invariant models. Models are encompassed by dynamical 
-equations with inputs, evolving over a continuous state space describing 
-the evolution of the physical variables of the system.  The approach is divided 
-in two main parts, brought together by a counter-example guided inductive 
-synthesis (CEGIS) loop, as follows. First, we devise a static feedback controller 
-that stabilises the system; then, we verify its potential safety by means of either 
-of the following approaches: forward reachability analysis via unfolding of the dynamics, 
-or invariant set generation via abstract acceleration;  
-further, if the above step fails, we loop back and invoke a CEGIS call 
-to seek alternative stabilising feedbacks, benefiting from the obtained counter-examples 
-to safety. The approach is proven sound by accounting for errors due to the digitalisation 
-of signals that are manipulated by the controller block.  
-The proposed synthesis approaches and a developed tool are evaluated considering 
-a set of intricate physical plant models taken from the digital control literature.
+equations with inputs, evolving over a continuous state space and accounting 
+for errors due to the digitalization of signals that are manipulated by the 
+controller block. The approach is divided in two main parts, brought together 
+by a counter-example guided inductive synthesis (CEGIS) loop, as follows. 
+First, we devise a static feedback controller that stabilizes the system; 
+then, we verify its potential safety by means of either of the following 
+approaches: forward reachability analysis via unfolding of the dynamics, 
+or invariant set generation via abstract acceleration;  further, if the 
+above step fails, we loop back and invoke a CEGIS call to seek alternative 
+stabilizing feedback, benefiting from the obtained counterexamples 
+to safety. Both approaches are able to efficiently synthesize stable and 
+safe controllers considering a set of intricate physical plant models taken 
+from the digital control literature.
 \keywords{

### 2017-01-24 cav2017/cav2017.tex
updated introduction

@@
 to accelerate the dynamics forward instead of symbolically unwinding the 
-transition relation~\cite{cattaruzza2015unbounded}.
+transition relation~\cite{cattaruzza2015unbounded}. We provide experimental results 
+showing that both approaches are able to efficiently synthesize stable and safe controllers 
+for a set of intricate physical plant models taken from the digital 
+control literature: the median runtime for our benchmark
+set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
+than \textcolor{red}{$XXX$} seconds.
 
@@
 
-In summary, this paper makes the following original contributions.
-%
-\begin{itemize}
-
-\item We design and implement two approaches to synthesize 
-  digital feedback control architectures for physical plants, 
-	considering dynamical equations with inputs that evolves over 
-	a continuous state space. In both approaches, we apply CEGIS to 
-	devise a digital controller that stabilizes the system and we then
-	we verify safety by means of either forward reachability analysis 
-	via dynamics unfolding or invariant set generation via 
-	abstract acceleration.
-
-\item We provide experimental results showing that our approaches
-  are able to efficiently synthesize stable and safe controllers 
-	for a set of intricate physical plant models taken from the digital 
-	control literature: the median runtime for our benchmark
-  set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
-  than \textcolor{red}{$XXX$} seconds.
-
-\end{itemize}
+%In summary, this paper makes the following original contributions.
+%
+%\begin{itemize}
+
+%\item We design and implement two approaches to synthesize 
+%  digital feedback control architectures for physical plants, 
+%	considering dynamical equations with inputs that evolves over 
+%	a continuous state space. In both approaches, we apply CEGIS to 
+%	devise a digital controller that stabilizes the system and we then
+%	we verify safety by means of either forward reachability analysis 
+%	via dynamics unfolding or invariant set generation via 
+%	abstract acceleration.
+
+%\item We provide experimental results showing that our approaches
+%  are able to efficiently synthesize stable and safe controllers 
+%	for a set of intricate physical plant models taken from the digital 
+%	control literature: the median runtime for our benchmark
+%  set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
+%  than \textcolor{red}{$XXX$} seconds.
+
+%\end{itemize}
 

### 2017-01-24 cav2017/cav2017.tex
replace "ising" by "izing"

@@
 precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
-for the synthesis of switching controllers for stabilising continuous-time
+for the synthesis of switching controllers for stabilizing continuous-time
 plants with polynomial dynamics.  The work extends to affine systems, 
@@
 Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
-use a CEGIS-based approach for synthesising continuous-time switching
+use a CEGIS-based approach for synthesizing continuous-time switching
 controllers that guarantee \emph{reach-while-stay} properties of closed-loop systems, 
 i.e., properties that specify a set of goal states and safe states (constrained reachability).%}. 
-The solution is based on synthesising control Lyapunov 
+The solution is based on synthesizing control Lyapunov 
 functions for switched systems, that yield switching controllers with
@@
 The work in \cite{DBLP:journals/corr/AbateBCCDKK16} investigates the synthesis of 
-stabilising controllers for continuous plants described as transfer functions, 
+stabilizing controllers for continuous plants described as transfer functions, 
 by exploiting bit-accurate verification of software-implemented 
 digital controllers~\cite{Bessa16}.  While this work also make use of a CEGIS-based technique, 
-the approach is restricted to synthesising digital controllers for stable 
+the approach is restricted to synthesizing digital controllers for stable 
 closed-loop systems described via transfer function models.  
@@
 However, Pessoa does not have native inclusion of the ADC/DAC quantisation error needed for
-synthesising fixed-point digital controllers.
+synthesizing fixed-point digital controllers.
 
@@
 As mentioned earlier, 
-in this work we are not bound to the synthesis of digital stabilising controllers -- 
+in this work we are not bound to the synthesis of digital stabilizing controllers -- 
 a well known task in the literature on digital control system -- 
@@
 
-%% This technique relies on parametrising the target language, which
+%% This technique relies on parametrizing the target language, which
 %% induces a lattice of progressively more expressive languages 

### 2017-01-24 cav2017/cav2017.tex
replaced "ise" by "ize"

@@
 guided inductive synthesis (CEGIS) loop. In the first approach, 
-we devise a digital controller that stabilises the system; then, we verify its 
+we devise a digital controller that stabilizes the system; then, we verify its 
 potential safety by unfolding the dynamics of the system and checking for 
@@
 algorithms for this problem have made substantial progress in recent years.  
-One such approach~\cite{itzhaky2010simple} inductively synthesises invariants to
+One such approach~\cite{itzhaky2010simple} inductively synthesizes invariants to
 generate the desired programs.
@@
 it entirely circumvents the FWL problem, but potentially incurs state-space explosion issues.  
-This approach is not suitable for the kind of control we seek to synthesise.
+This approach is not suitable for the kind of control we seek to synthesize.
 
@@
 In contrast, in the current paper we consider a state-space representation of the physical system, 
-which is known to be more general \cite{Astrom08} and allows to synthesise controllers that
+which is known to be more general \cite{Astrom08} and allows to synthesize controllers that
 make the closed-loop system \emph{safe}.  Moreover, 
@@
 
-The tool Pessoa~\cite{mazo2010pessoa} is a MatLab toolbox that synthesises correct-by-design
+The tool Pessoa~\cite{mazo2010pessoa} is a MatLab toolbox that synthesizes correct-by-design
 embedded control software. It is based on the description of a physical system
@@
 Based on this safety specification over state values, 
-Pessoa can synthesise embedded controller software for a range of properties.  
+Pessoa can synthesize embedded controller software for a range of properties.  
 %based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
@@
 response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics, 
-with the goal either to verify (e.g.~\cite{daes20161}) or to optimise
+with the goal either to verify (e.g.~\cite{daes20161}) or to optimize
 (e.g.~\cite{oudjida2014design}) given implementations.
@@
 \end{align}
-The gain matrix $K$ can be set so that the closed-loop digitalised dynamics are shaped as desired, 
+The gain matrix $K$ can be set so that the closed-loop digitalized dynamics are shaped as desired, 
 for instance according to a specific stability goal or around a specific dynamical behaviour \cite{astrom1997computer}. 
@@
 In this paper, we are concerned with \emph{safe} controllers and therefore concerned only that the system converges to a point within the safety specification.
-Hence, it is sufficient to synthesise a stable controller based on infinite precision, and then verify safety.
+Hence, it is sufficient to synthesize a stable controller based on infinite precision, and then verify safety.
 
@@
 Given the large solution space to be searched during the inductive
-synthesis phase, we parametrise the target language, which induces a
+synthesis phase, we parametrize the target language, which induces a
 lattice of progressively more expressive languages.  This enables us
-to start by attempting to synthesise a program at the lowest point on
+to start by attempting to synthesize a program at the lowest point on
 this lattice and increase the parameters of the language until we
 reach a point at which the synthesis succeeds. Whenever we manage to
-synthesise a candidate solution at some lower point on the lattice, we
+synthesize a candidate solution at some lower point on the lattice, we
 must apply some form of solution generalisation to obtain a full
@@
 (i.e. the validation oracle finds an answer fast). If a program can be
-synthesised in a low-complexity language, the whole procedure finishes
+synthesized in a low-complexity language, the whole procedure finishes
 much faster than if synthesis had been attempted in a high-complexity
@@
 and the sampling rate. Essentially, it finds a controller for an individual initial state
-and input with a bounded time horizon and generalises to all states,
+and input with a bounded time horizon and generalizes to all states,
 inputs, and time horizons. The safety check is performed in this approach 
-via unfolding of the transition system corresponding to the synthesised controller.
+via unfolding of the transition system corresponding to the synthesized controller.
 
@@
   set, over an abstraction of the continuous dynamics that conforms to
-  witness proofs at specific times; it further generalises the
+  witness proofs at specific times; it further generalizes the
   solution over all times by refining the number of witnesses.  
@@
 The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
-One important observation is that, for this approach, we verify and synthesise 
+One important observation is that, for this approach, we verify and synthesize 
 a controller over $k$ time steps. We then compute a completeness threshold, $\overline{k}$,
@@
 \begin{enumerate}
-\item The inductive synthesis phase (i.e. {\sc synthesise}) uses BMC to
+\item The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
 compute a candidate solution $K$
@@
 Sec.~\ref{ssec:stability} and the safety specification in Sec.~\ref{ssec:safety}.
-To synthesise a controller that satisfies the stability criteria, we require that
+To synthesize a controller that satisfies the stability criteria, we require that
 a computed characteristic polynomial satisifies Jury's criteria. The details of this
@@
 %% independent of the initial states. 
-Regarding the latter, we synthesise a safe controller by unwinding the transition system
+Regarding the latter, we synthesize a safe controller by unwinding the transition system
 $k$ steps and picking a controller $K$ and an initial state such that the states at each step do
 not violate the safety criteria. This is sound if the current $k$ is below the
-completeness threshold, which we assume to be true in the {\sc synthesise} phase.
+completeness threshold, which we assume to be true in the {\sc synthesize} phase.
 We also assume some
@@
 %The safety criteria here must be valid for all possible allowed initial states, and so we
-After unwinding the transition system corresponding to the previously synthesised controller
+After unwinding the transition system corresponding to the previously synthesized controller
 $k$ steps, we check that the safety specification holds for any initial state.
@@
 
-In the subsequent iteration, the synthesiser is unable to find further 
+In the subsequent iteration, the synthesizer is unable to find further 
 suitbale candidates and it returns UNSAT, meaning that the current precision is
@@
 \end{enumerate}
-\item In this phase we synthesise a candidate controller
+\item In this phase we synthesize a candidate controller
 %We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability 
@@
 We report an assessment of both our approaches over a diverse set of real-world benchmarks.
-Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalise to other benchmarks.
+Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalize to other benchmarks.
 
@@
 reference signal so an asymptotically stable system will converge to the origin. We know that the original system
-with an infinite precision controller is stable, because we have synthesised it to meet Jury's criteria. Hence
+with an infinite precision controller is stable, because we have synthesized it to meet Jury's criteria. Hence
 $(A_d  - B_dK)^n*x_0$ must converge to zero.

### 2017-01-24 cav2017/cav2017.tex
replaced "tisation" by "tization"

@@
 %based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
-However, Pessoa does not have native inclusion of the ADC/DAC quantisation error needed for
+However, Pessoa does not have native inclusion of the ADC/DAC quantization error needed for
 synthesizing fixed-point digital controllers.
@@
 the first approach we present, performs bounded model checking of control properties,
-based on~\cite{Monteiro16}, but enhanced to include evaluation of quantisation effects and safety properties
+based on~\cite{Monteiro16}, but enhanced to include evaluation of quantization effects and safety properties
 over the state space. In an alternative approach, we use a verification engine based on abstract acceleration~\cite{cattaruzza2015unbounded}, 

### 2017-01-24 cav2017/cav2017.tex
a better version of CEGIS with AA (not yet perfect though)

@@
 \item 
-We start by preprocessing the dynamics. This can be computationally intensive and we don't want it to be part of the CEGIS loop.
+  We start by doing some preprocessing:%%  that 
+  %% can be computationally intensive and we don't want it to be part of the CEGIS loop.
 % Let us recall the formulas used for single-input and single-output (SISO) systems 
   % in sections \ref{sec:reachable} and \ref{sec:observable}.
-A controllable system with quantization will have the following dynamics 
-(note that we use underscript ``n'' to denote a noise term and
-``cf'' to denote Controllable Canonical Form):
-%\todo{eliminate vectors}
-%
-\begin{align}
-\label{eq:observer_LTI_cf}
-x_{k+1}=&\mat{A}_{t}x_k+\mat{B}_{t} r_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)
-\end{align}
-\begin{align*}
-\mat{A}_{t}=&\mat{T}\mat{A}_d\mat{T}^{-1}&
-\mat{B}_{t}=&\mat{T}\mat{B}_d&
-\mat{B}_{n}=&[1 \cdots 1]^T&
-\mat{T}=&\mat{W}_{cf}\mat{W}^{-1}&
-\end{align*}
-
-\begin{align*}
-\mat{A}_{t}=\mat{T}\mat{A}_d\mat{T}^{-1}=&\left[
-\begin{array}{ccccc}
-0&1&0&\cdots&0\\
-0&0&1&\cdots&0\\
-\vdots&\vdots&\vdots&\ddots&\vdots\\
-0&0&0&\cdots&1\\
-k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
-\end{array}\right]
-\label{eq:cf_SISO_2}
-\end{align*}
-
-The characteristic polynomial of the above matrix is:
-%
-\begin{align*}
-P_a = z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}
-\end{align*}
-
   \begin{enumerate}
-\item Calculate $\mat{T}$ as $\mat{W}_{cf}\mat{W}^{-1}$. %using equations \eqref{eq:rncf}\eqref{eq:rcf}\eqref{eq:to_cf}
-\item Extract the Plant's characteristic polynomial coefficients from $P_a$. %the last row of $P_a=(\mat{T}\mat{A}\mat{T}^-1)_{n*}$.
+\item Compute the characteristic polynomial of the matrix $(\mat{A_d}-\mat{B_d}\mat{K})$ as 
+$P_a(z) = z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}$.
+%%   A controllable system with quantization will have the following dynamics, where
+%% we use underscript ``n'' to denote a noise term,
+%% ``cf'' to denote Controllable Canonical Form,
+%% $\nu_1$, $\nu_2$ are quantization errors
+%% caused by the ADC and DAC conversions, respectively, 
+%% and $\nu_3$ is the round-off error.
+%% \todo{Why do we use $_t$ here?}
+%% %
+%% \begin{align}
+%% \label{eq:observer_LTI_cf}
+%% x_{k+1}=&\mat{A}_{t}x_k+\mat{B}_{t} r_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)
+%% \end{align}
+%% \begin{align*}
+%% \mat{A}_{t}=&\mat{T}\mat{A}_d\mat{T}^{-1}&
+%% \mat{B}_{t}=&\mat{T}\mat{B}_d&
+%% \mat{B}_{n}=&[1 \cdots 1]^T&
+%% \mat{T}=&\mat{W}_{cf}\mat{W}^{-1}&
+%% \end{align*}
+
+%% \begin{align*}
+%% \mat{A}_{t}=\mat{T}\mat{A}_d\mat{T}^{-1}=&\left[
+%% \begin{array}{ccccc}
+%% 0&1&0&\cdots&0\\
+%% 0&0&1&\cdots&0\\
+%% \vdots&\vdots&\vdots&\ddots&\vdots\\
+%% 0&0&0&\cdots&1\\
+%% k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
+%% \end{array}\right]
+%% \label{eq:cf_SISO_2}
+%% \end{align*}
+
+%% \begin{enumerate}
+%% \item Calculate $\mat{T}$ as $\mat{W}_{cf}\mat{W}^{-1}$. %using equations \eqref{eq:rncf}\eqref{eq:rcf}\eqref{eq:to_cf}
+%% \item Extract the characteristic polynomial of the above matrix:
+%% %
+%\begin{align*}
+%$P_a = z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}$
+%\end{align*}
+
 \item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
@@
 \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
-\item Calculate a set of initial bounds on K based on the input constraints. Note that these bounds will be used during the 
-synthesis phase to reduce the size of the solution space.
-$$\phi_{safety} \Leftrightarrow u_k=-Kx_k : x_0 \in [\underline{x_0} \ \overline{x_0}] \wedge u_k \in [\underline{u}\ \ \overline{u}]$$
+More details on how to model quantization as noise are given in the 
+Appendix~\ref{appendix:quantization-noise}.
+\item Calculate a set of initial bounds on $\mat{K}$, $\phi_{init}^{K}$, based on the input constraints.
+Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
+$$(\phi_{init} \wedge u_k=-\mat{K} x_k) \Rightarrow \phi_{init}^{K}$$
+
 \end{enumerate}
-\item In this phase we synthesize a candidate controller
+\item In the {\sc synthesize} phase, we synthesise a candidate controller
 %We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability 
@@
 % safety specification $\phi_{safety}$.
-as a model $\mat{K} \in \mathbb{R}\langle I,F\rangle^n$. We obtain it by solving the SAT formula 
-$$\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{safety}$$ 
-that satisfies the input constraint and Jury's criteria for 
-$P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \tilde{\mat{K}}=\mat{K}\mat{T}$,
-where $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ is a program describing Jury's method.
+  $\mat{K} \in \mathbb{R}\langle I_c,F_c\rangle^n$ that satisfies
+  $\phi_{stability} \wedge \phi_{safety} \wedge \phi_{init}^{K}$ by invoking a SAT solver.
+%%   We obtain it by solving the SAT formula 
+%% $$\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{safety}$$ 
+%% that satisfies the input constraint and Jury's criteria for 
+%% $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \tilde{\mat{K}}=\mat{K}\mat{T}$,
+%% where $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ is a program describing Jury's method.
 If there is no candidate solution we return UNSAT and exit the loop.
@@
   %
-consisting of evaluating the progression of the system over time,
-$x_{k+1} \models \phi_{safety}$. For this purpose we require 
-an initial set $\phi_{init}= x_0 \in [\underline{x_0} \ \overline{x_0}]$ 
-from which the system progresses. % Obviously, this set $x_0$ 
+  of the 
+  %consisting of evaluating the
+  progression of the system from $\phi_{init}$ over time,
+$x_{k+1} \models \phi_{safety}$. %% For this purpose we require 
+%% an initial set $\phi_{init}= x_0 \in [\underline{x_0} \ \overline{x_0}]$ 
+%% from which the system progresses.
+% Obviously, this set $x_0$ 
 % must satisfy the specification; otherwise, the system will be unsafe to begin with.
@@
 % state-space.
-Next, we use abstract acceleration to get a second abstraction that 
-encompasses the accelerated continuous reach-tube over an unbounded time.
-Accelerating \eqref{eq:observer_LTI_cf}, we obtain:
+%% Next, we use abstract acceleration to get a second abstraction that 
+  %% encompasses the accelerated continuous reach-tube over an unbounded time.
+  In order to compute the progression of point $x_0$ at iteration $k$,
+  we accelerate the dynamics of the closed-loop system and obtain:
+  %we take the
+  %the closed-loop model:
+  %$x_{k+1}=\mat{A}_{t}x_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)$
+  %and accelerate it to:
 %
@@
 %+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i
-+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{n}(\nu_1+\nu_2+\nu_3) : x_0 \models \phi_{init}
++\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{n}(\nu_1+\nu_2+\nu_3) 
 \end{align}
-which would still require us to verify the system for every $k$ up to infinity. 
-Instead we use abstract acceleration~\cite{cattaruzza2015unbounded}, which translates the formula into
-%
+\todo{explain $B_n$ and $A_t$}
+As this still requires us to verify the system for every $k$ up to infinity, 
+we use abstract acceleration again to obtain
+the reach-tube, i.e. the set of all reachable states at all times given an initial set $\phi_{init}$:
 \begin{align}
@@
 \hat{X}^\#
-=&\mathcal{A}_t X_0+\mathcal{B}_{t} R + \mathcal{B}_{n} N\\
-X_0 =&\left \{x : x \models \phi_{init} \right\}\nonumber\\
-% R =&\{r : \mat{E}_r < f_r \}\nonumber\\
- %N=&\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber
+=&\mathcal{A}_t X_0 + \mathcal{B}_{n} N\\
+X_0 =&\left \{x : x \models \phi_{init} \right\}\nonumber
 \end{align}
 %
-where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A}^k, \mathcal{B}_{t}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{t}, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{n}$ are abstract matrices for the system in \eqref{eq:observer_LTI_cf}
+where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A_t}^k, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A_t}^i\mat{B}_{n}$ are abstract matrices for the closed-loop system,
+% in \eqref{eq:observer_LTI_cf} 
 %and $r$ is a non-deterministic parametric input (\emph{ie} $\forall k>0, r_{k+1} =r_k$) 
-whereas the set N is composed of non-deterministic variable inputs.
-
+whereas the set N is non-deterministically chosen.
+
+%\begin{enumerate}
+%% \item Calculate the abstract matrices $\mathcal{A}_t, \mathcal{B}_{t},\mathcal{B}_{n}$ for the candidate closed loop solution.
+We next evaluate $\hat{X}^\# \models \phi_{safety}$. If the verification holds we have a solution, and exit the loop. Otherwise, 
+we find a counterexample iteration $k$ and corresponding initial point $x_0$ for which the property does not hold, which we use to locally refine the abstraction.
+When the abstraction cannot be further refined, and provide them to the {\sc abstract} phase.
+\todo{we should have a better argument here.}
+%\end{enumerate} 
+\item If we reach the {\sc abstract} phase, it means that the candidate solution is not valid,
+  in which case we must refine the abstraction used by the synthesizer.
 \begin{enumerate}
-\item Calculate the abstract matrices $\mathcal{A}_t, \mathcal{B}_{t},\mathcal{B}_{n}$ for the candidate closed loop solution.
-\item Evaluate $\hat{X}^\# \models \Psi$. If the verification holds we have a solution, and exit the loop.
-\end{enumerate} 
-\item If the candidate solution is not valid we refine the abstraction used by the synthesizer
-\begin{enumerate}
-\item Find the constraints that invalidate the property.
-These are the rows of $\mat{E} \in \Psi$ that intersect/segment $\hat{X}^\#$.
-Transforming these rows into the eigenspace of $\mat{A}_t$, and applying backward acceleration to obtain a set of counterexamples for the eigenvalues, which we define as $\phi(\Lambda)$.
-This is a constraint in the spectrum (\emph{ie} frequency response transfer function) of the closed loop dynamics.
-\item Transform the soft constraints on the spectrum into soft constraints on the coefficients of the characteristic polynomial. 
-$z^n+\sum_{i=1}^n[a_i-k_i]z^{n-i}=\prod_{i=1}^n (z-[\lambda_i]) : |[\lambda_i]|<1 \wedge [\lambda_i] \models \phi_{\Lambda}$.
-\item Pass the refined abstraction with the new constraints to the synthesizer, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again.
-We note that the Abstraction refinement is a soft constraint on the proposed model which can increase or decrease the parameter space at any time, whereas the concrete counterexample passed to the synthesizer is monotonically decreasing.
-The first one improves speed of the tool whereas the second ensures convergence.
-
+\item Find the constraints that invalidate the property
+  %% These are the rows of $\mat{E} \in \Psi$ that intersect/segment $\hat{X}^\#$. Transforming these rows into the eigenspace of $\mat{A}_t$, and applying backward acceleration to
+ as a set of counterexamples for the eigenvalues, which we define as $\phi_\Lambda$. This is a constraint in the spectrum (\emph{ie} transfer function) of the closed loop dynamics. 
+\item We use $\phi_\Lambda$ to
+  further constrain the characteristic polynomial  
+$z^n+\sum_{i=1}^n(a_i-k_i)z^{n-i}=\prod_{i=1}^n (z-\lambda_i) : |\lambda_i|<1 \wedge \lambda_i \models \phi_{\Lambda}$.
+These constraints correspond to specific iterations for which the system may be unsafe.
+\item Pass the refined abstraction $\phi(\mat{K})$ with the new constraints and the list of iterations $\vec{k}$ to the {\sc synthesize} phase.
+  %, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again. 
 \end{enumerate} 
 \end{enumerate}
+
+%% Note that the abstraction refinement is a constraint on the proposed model which can increase or decrease the parameter space at any time, whereas the concrete counterexample passed to the synthesizer is monotonically decreasing.
+The former improves the speed of the tool, whereas the second ensures convergence.
 
@@
      \coordinate (auxsynth);
-     \node[draw,rectangle,align=center] (KSAT) at ([xshift=0cm]auxsynth.center) {\sc Prog.\\Search};
-     \node[draw=none] (SATK) at ([xshift=-0.5cm,yshift=1.5cm]KSAT)  {$\mathcal{J}_K$};
-     \node[draw=none] (K) at ([xshift=.4cm,yshift=1.5cm]KSAT)  {$\tilde{\mat{K}}$};
+     \node[draw,rectangle,align=center] (KSAT) at ([xshift=0cm]auxsynth.center) {Prog.\\Search};
+     \node[draw=none] (SATK) at ([xshift=-.7cm,yshift=1.5cm]KSAT)  {{\sc Inputs}};
+     \node[draw=none] (K) at ([xshift=.4cm,yshift=1.5cm]KSAT)  {$\mat{K}$};
     }
@@
      \coordinate (AA);
-     \node[draw,rectangle,align=center] (AAI) at ([xshift=-1.5cm]AA.center) {\sc Abstract};
-     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm,yshift=1.5cm]AA.center) {Abstraction \\ Verifier};
-     \node[draw,rectangle,align=center] (AAV) at ([xshift=1.5cm]AA.center) {\sc AA\\Solver};
+     \node[draw,rectangle,align=center] (AAV) at ([xshift=-1.5cm]AA.center) {Abstract\\Acceleration};
+     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm]AA.center) {Abstraction \\ Verifier};
+     %\node[draw,rectangle,align=center] (AAI) at ([xshift=1.5cm]AA.center) {\sc AA\\Solver};
 
      %\node[draw=none] (AB) at ([xshift=.4cm,yshift=1.5cm]AAI.center)  {\sc $\mat{A},\mat{B}$\\$\phi$};     
-     \node[draw=none] (MA) at ([yshift=.2cm]AA.center)  {$\mathcal{A}_t$};     
-     \node[draw=none] (MB) at ([yshift=-.3cm]AA.center)  {$\mathcal{B}_{t},\mathcal{B}_{n}$}; 
-     \node[draw=none] (XT) at ([xshift=0.3cm,yshift=0.5cm]AAC.center)  {\sl $\hat{X}_r^\#$};  
-     \node[draw=none] (XT2) at ([xshift=0.3cm,yshift=0.8cm]AAV.center)  {\sl $\hat{X}^\#$};  
+     %\node[draw=none] (MA) at ([yshift=.2cm]AA.center)  {$\mathcal{A}_t$};     
+     %\node[draw=none] (MB) at ([yshift=-.3cm]AA.center)  {$\mathcal{B}_{t},\mathcal{B}_{n}$}; 
+     %\node[draw=none] (XT) at ([xshift=0.3cm,yshift=0.5cm]AAC.center)  {\sl $\hat{X}_r^\#$};  
+     %\node[draw=none] (XT2) at ([xshift=0.3cm,yshift=0.8cm]AAV.center)  {\sl $\hat{X}^\#$};  
      %\draw [->,line width=1pt] ([xshift=-0.1cm,yshift=2cm]AA.center) arc[x radius=0.7cm, y radius =.7cm, start angle=-250, end angle=60];
@@
   \path
-    (pre.east) edge (abstract.west)
-    (abstract.south) edge (synth.north)
+    (pre.east) edge node[align=center] {$P_a$, $N$,\\ $\phi_{init}^k$} (abstract.west)
+    (abstract.south) edge node{$(\phi(\mat{K}), \vec{k})$} (synth.north)
     %([yshift=2em]synth.east) edge node {Candidate} ([yshift=2em]verif.west)
@@
     ([yshift=1em]synth.east) edge node {$\mat{K}$} ([yshift=1em]verify.west)
-    ([yshift=-1em]verify.west) edge node {$P_a$} ([yshift=-1em]synth.east)
+    %([yshift=-1em]verify.west) edge node {$P_a$} ([yshift=-1em]synth.east)
     (aux) edge (abstract.east) 
@@
     ([xshift=-.6cm]synth.south) edge ([xshift=-.6cm]KSAT.north)
-    (AAC) edge[bend right] node[align=center] {$k$} (AAI.north)
-    ([xshift=-4.9cm]verify.south) edge node[align=center] {$\mat{A},\mat{B}$\\$\phi$} (AAI.north)
-    (AAI.east) edge (AAV.west)
-    (AAV.north) edge (AAC.south)
-    (AAC.north) edge ([xshift=4.9cm]verify.south)
+    %(AAC) edge[bend right] node[align=center] {$k$} (AAI.north)
+    %([xshift=-4.9cm]verify.south) edge node[align=center] {$\mat{A},\mat{B}$\\$\phi$} (AAI.north)
+    %(AAI.east) edge (AAV.west)
+    ([yshift=.5cm]AAV.east) edge node{\sl $\hat{X}^\#$} ([yshift=.5cm]AAC.west)
+    ([yshift=-.5cm]AAC.west) edge node{$(k,x_0)$} ([yshift=-.5cm]AAV.east)
+    (AAC.north) edge node{\sl $\hat{X}^\#$} ([xshift=4.9cm]verify.south)
     %(AAC.west) edge (AB.west)
@@
     %(counter.south west) edge (synth.north east)
-    (FAIL.north) edge (done.south);
+    (FAIL.north) edge (done.south)
+    ([xshift=-5cm]verify.south) edge node{$\mat{K}$} (AAV.north);
   \path[-] 
@@
      (KUNSAT.east) edge (FAIL.west)
-     (verify.north) edge node {$\phi (\mat{K},k)$} (aux);
+     (verify.north) edge node {$(k,x_0)$} (aux);
 \end{tikzpicture}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Modelling quantization as noise}
+\subsection{Modelling quantization as noise} \label{appendix:quantization-noise}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-01-24 cav2017/cav2017.tex
de-vectorize sec 4.5

@@
   \begin{enumerate}
-\item Compute the characteristic polynomial of the matrix $(\mat{A_d}-\mat{B_d}\mat{K})$ as 
+\item Compute the characteristic polynomial of the matrix $(A_d-B_dK)$ as 
 $P_a(z) = z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}$.
@@
 Appendix~\ref{appendix:quantization-noise}.
-\item Calculate a set of initial bounds on $\mat{K}$, $\phi_{init}^{K}$, based on the input constraints.
+\item Calculate a set of initial bounds on $K$, $\phi_{init}^{K}$, based on the input constraints.
 Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
-$$(\phi_{init} \wedge u_k=-\mat{K} x_k) \Rightarrow \phi_{init}^{K}$$
+$$(\phi_{init} \wedge u_k=-K x_k) \Rightarrow \phi_{init}^{K}$$
 
@@
 % safety specification $\phi_{safety}$.
-  $\mat{K} \in \mathbb{R}\langle I_c,F_c\rangle^n$ that satisfies
+  $K \in \mathbb{R}\langle I_c,F_c\rangle^n$ that satisfies
   $\phi_{stability} \wedge \phi_{safety} \wedge \phi_{init}^{K}$ by invoking a SAT solver.
@@
 %\label{eq:acc_observer_LTI_cf}
-x=&\mat{A}_t^kx_0
+x=&A_t^kx_0
 %+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i
-+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{n}(\nu_1+\nu_2+\nu_3) 
++\sum_{i=0}^{k-1} A_t^i B_{n}(\nu_1+\nu_2+\nu_3) 
 \end{align}
@@
 %
-where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A_t}^k, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A_t}^i\mat{B}_{n}$ are abstract matrices for the closed-loop system,
+where $\mathcal{A}_t=\bigcup_{k=1}^\infty A_t^k, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^kA_t^iB_{n}$ are abstract matrices for the closed-loop system,
 % in \eqref{eq:observer_LTI_cf} 
@@
 These constraints correspond to specific iterations for which the system may be unsafe.
-\item Pass the refined abstraction $\phi(\mat{K})$ with the new constraints and the list of iterations $\vec{k}$ to the {\sc synthesize} phase.
+\item Pass the refined abstraction $\phi(K)$ with the new constraints and the list of iterations $\vec{k}$ to the {\sc synthesize} phase.
   %, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again. 
@@
      \node[draw=none] (SATK) at ([xshift=-.7cm,yshift=1.5cm]KSAT)  {{\sc Inputs}};
-     \node[draw=none] (K) at ([xshift=.4cm,yshift=1.5cm]KSAT)  {$\mat{K}$};
+     \node[draw=none] (K) at ([xshift=.4cm,yshift=1.5cm]KSAT)  {$K$};
     }
@@
     (pre.east) edge node[align=center] {$P_a$, $N$,\\ $\phi_{init}^k$} (abstract.west)
-    (abstract.south) edge node{$(\phi(\mat{K}), \vec{k})$} (synth.north)
+    (abstract.south) edge node{$(\phi(K), \vec{k})$} (synth.north)
     %([yshift=2em]synth.east) edge node {Candidate} ([yshift=2em]verif.west)
@@
     %([yshift=-2em]verif.west) edge node[xshift=-0.7em] {New input} ([yshift=-2em]synth.east)
-    ([yshift=1em]synth.east) edge node {$\mat{K}$} ([yshift=1em]verify.west)
+    ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west)
     %([yshift=-1em]verify.west) edge node {$P_a$} ([yshift=-1em]synth.east)
@@
     (FAIL.north) edge (done.south)
-    ([xshift=-5cm]verify.south) edge node{$\mat{K}$} (AAV.north);
+    ([xshift=-5cm]verify.south) edge node{$K$} (AAV.north);
   \path[-] 

### 2017-01-24 cav2017/cav2017.tex
moved contributions

--- 2017-01-24 cav2017/cav2017.tex
@@
 
+\textit{Contributions}. We use a combination of a synthesis engine with a control
+verification tool that addresses the challenges presented in the
+form of FWL effects and stability measures over digital controllers for LTI models.  
+We take the synthesis engine from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
+the first approach we present, performs bounded model checking of control properties,
+based on~\cite{Monteiro16}, but enhanced to include evaluation of quantization effects and 
+safety properties over the state space. In an alternative approach, we use a verification engine based 
+on abstract acceleration~\cite{cattaruzza2015unbounded}, which avoids the explicit unwinding 
+the transition system necessarily for the first approach.
+
 %\textcolor{red}{we have to connect both paragraphs...}
@@
 it entirely circumvents the FWL problem, but potentially incurs state-space explosion issues.  
-This approach is not suitable for the kind of control we seek to synthesize.
-
-%\textcolor{red}{Cristina: can you please revise this sentence:
 Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
@@
 controllers that guarantee \emph{reach-while-stay} properties of closed-loop systems, 
-i.e., properties that specify a set of goal states and safe states (constrained reachability).%}. 
-The solution is based on synthesizing control Lyapunov 
+i.e., properties that specify a set of goal states and safe states (constrained reachability).
+This solution is based on synthesizing control Lyapunov 
 functions for switched systems, that yield switching controllers with
-a guaranteed minimum dwell time in each mode.
+a guaranteed minimum dwell time in each mode. However, both approaches 
+are not suitable for the kind of control we seek to synthesize.
 
@@
 by exploiting bit-accurate verification of software-implemented 
-digital controllers~\cite{Bessa16}.  While this work also make use of a CEGIS-based technique, 
+digital controllers~\cite{Bessa16}.  While this work also makes use of a CEGIS-based technique, 
 the approach is restricted to synthesizing digital controllers for stable 
@@
 synthesizing fixed-point digital controllers.
-
-We use a combination of a synthesis engine with a control
-verification tool that addresses the challenges presented in the
-form of FWL effects and stability measures over digital controllers for LTI models.
-
-We take the synthesis engine from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
-the first approach we present, performs bounded model checking of control properties,
-based on~\cite{Monteiro16}, but enhanced to include evaluation of quantization effects and safety properties
-over the state space. In an alternative approach, we use a verification engine based on abstract acceleration~\cite{cattaruzza2015unbounded}, 
-which avoids the explicit unwinding the transition system necessarily for the first approach.
 

### 2017-01-24 cav2017/cav2017.tex
typo
eps compile

@@
 \usepackage{microtype}
+\usepackage{epstopdf}
 
@@
 verification tool that addresses the challenges presented in the
-form of FWL effects and stability measures over digital controllers for LTI models.  
+form of FWL effects, safety, and stability measures over digital controllers for LTI models.  
 We take the synthesis engine from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
@@
 on abstract acceleration~\cite{cattaruzza2015unbounded}, which avoids the explicit unwinding 
-the transition system necessarily for the first approach.
+the transition system necessarily for the first approach. In both approaches, we project
+the maximum effect of the noise over an unbounded time and uses it as a buffer region 
+for the safety specification.
 
@@
 period of time. This technique works for both linear and non-linear systems.
-This paper uses an approach that projects the maximum effect of the noise over
-an unbounded time and uses it as a buffer region for the safety specification.
 
@@
 \begin{proof}
-Consider spectrum of matrix $(A_d - B_d K)$ and select eigenvalue with smallest (non trivial) imaginary value.  
+Consider the matrix $(A_d - B_d K)$, which updates the states every time step, and select eigenvalue with smallest (non trivial) imaginary value.  
 call such value $\vartheta$. 
@@
 \end{proof}
-\item The last {\sc verify} stage, {\sc sampling}, 
-ensures that the current sampling rate is large enough by using an 
-external checker (\addtodo{add more details here once we have them}).
 
@@
 we find a counterexample iteration $k$ and corresponding initial point $x_0$ for which the property does not hold, which we use to locally refine the abstraction.
-When the abstraction cannot be further refined, and provide them to the {\sc abstract} phase.
+When the abstraction cannot be further refined, we provide them to the {\sc abstract} phase.
 \todo{we should have a better argument here.}

### 2017-01-24 cav2017/cav2017.tex
added more contributions

@@
 \usepackage{microtype}
-\usepackage{epstopdf}
 
@@
 \begin{proof}
-Consider the matrix $(A_d - B_d K)$, which updates the states every time step, and select eigenvalue with smallest (non trivial) imaginary value.  
+Consider spectrum of matrix $(A_d - B_d K)$ and select eigenvalue with smallest (non trivial) imaginary value.  
 call such value $\vartheta$. 
@@
 \end{proof}
+\item The last {\sc verify} stage, {\sc sampling}, 
+ensures that the current sampling rate is large enough by using an 
+external checker (\addtodo{add more details here once we have them}).
 
@@
 we find a counterexample iteration $k$ and corresponding initial point $x_0$ for which the property does not hold, which we use to locally refine the abstraction.
-When the abstraction cannot be further refined, we provide them to the {\sc abstract} phase.
+When the abstraction cannot be further refined, and provide them to the {\sc abstract} phase.
 \todo{we should have a better argument here.}

### 2017-01-24 cav2017/cav2017.tex
remove final verify stage from list
minor change to A's CT proof
Modification of the abstract

--- 2017-01-24 cav2017/cav2017.tex
@@
 This work presents a sound and automated approach to synthesize 
-digital feedback control architectures for physical plants represented 
-as linear, time invariant models. Models are encompassed by dynamical 
+safe digital feedback controllers for physical plants represented 
+as linear, time invariant models. Models are described as dynamical 
 equations with inputs, evolving over a continuous state space and accounting 
 for errors due to the digitalization of signals that are manipulated by the 
-controller block. The approach is divided in two main parts, brought together 
-by a counter-example guided inductive synthesis (CEGIS) loop, as follows. 
-First, we devise a static feedback controller that stabilizes the system; 
-then, we verify its potential safety by means of either of the following 
-approaches: forward reachability analysis via unfolding of the dynamics, 
-or invariant set generation via abstract acceleration;  further, if the 
-above step fails, we loop back and invoke a CEGIS call to seek alternative 
-stabilizing feedback, benefiting from the obtained counterexamples 
-to safety. Both approaches are able to efficiently synthesize stable and 
-safe controllers considering a set of intricate physical plant models taken 
-from the digital control literature.
+controller block. 
+The approach works in two stages, leveraging the use of counter-example guided
+inductive synthesis (CEGIS) and reachability analysis. The former synthesises a static 
+feedback controller that stabilizes the system under some restrictions given by the safety of
+the reach space. The latter verifies its potential safety by means of either of the following 
+approaches: forward reachability analysis via unfolding of the dynamics or invariant set 
+generation via abstract acceleration; if the 
+verification step fails, we loop back to seek an 
+alternative controller benefiting from the obtained counterexamples 
+to safety using solution generalization and abstraction refinement.
+We are able to efficiently synthesize stable and safe controllers
+considering a set of intricate physical plant models taken from the digital
+control literature.
 \keywords{

### 2017-01-24 cav2017/cav2017.tex
reviewed 3.2 Controller synthesis via state feedback

--- 2017-01-24 cav2017/cav2017.tex
@@
 Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
-Feedback architectures can be employed to affect the properties and behaviours of the continuous process (the plant) of interest.   
+Feedback architectures can be employed to affect the properties and behaviours of the continuous process (the plant).   
 %reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 

### 2017-01-24 cav2017/cav2017.tex
removed sampling from Fig 2 (multi-staged CEGIS)

--- 2017-01-24 cav2017/cav2017.tex
@@
      \node[rectangle,draw,dotted,
-	minimum width=8cm,
+	minimum width=6cm,
 	minimum height=1cm,
         pattern=north west lines, pattern color=gray!20,
-	label={\sc Verify},] (verif) {};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2.9cm]verif.center) {{\sc 2.Safety}};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=-0.8cm]verif.center) {{\sc 3.Precision}};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=1.2cm]verif.center) {{\sc 4.Complete}};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc 5.Sampling}};
+	label={\sc ~~~~~~~~~~~~Verify},] (verif) {};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc 2.Safety}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=0cm]verif.center) {{\sc 3.Precision}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=2cm]verif.center) {{\sc 4.Complete}};
+     %\node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc 5.Sampling}};
    } 
@@
      \coordinate (aux);
-   \node (bmc) at ([xshift=-2.9cm]aux.center) {\sf BMC-based \\Verifier};
-   \node (fp)  at ([xshift=-.8cm]aux.center) {\sf Fixed-point \\ Arithmetic\\Verifier};
-   \node (sv)  at ([xshift=1.2cm]aux.center) {\sf Completeness\\Verifier};
-   \node (cv)  at ([xshift=3.1cm]aux.center) {\sf Sampling\\Verifier};
+   \node (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based \\Verifier};
+   \node (fp)  at ([xshift=0cm]aux.center) {\sf Fixed-point \\ Arithmetic\\Verifier};
+   \node (sv)  at ([xshift=2cm]aux.center) {\sf Completeness\\Verifier};
+   %\node (cv)  at ([xshift=3.1cm]aux.center) {\sf Sampling\\Verifier};
    }   
@@
    \path
-    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$P$} ([yshift=2em]verif1.west)
+    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$K$} ([yshift=2em]verif1.west)
     ([yshift=-2em]verif1.west) edge node {C-ex} ([yshift=-2em]synth.east)
@@
     ([xshift=-5em]sv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif3.south)
-    ([xshift=-5em]cv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif4.south)
-    ([xshift=5em]verif1.south) edge node[align=center] {$P$} ([xshift=5em]bmc.north)
-    ([xshift=5em]verif2.south) edge node[align=center] {$P$} ([xshift=5em]fp.north)
-    ([xshift=5em]verif3.south) edge node[align=center] {$P$} ([xshift=5em]sv.north)
-    ([xshift=5em]verif4.south) edge node[align=center] {$P$} ([xshift=5em]cv.north)
+    %([xshift=-5em]cv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif4.south)
+    ([xshift=5em]verif1.south) edge node[align=center] {$K$} ([xshift=5em]bmc.north)
+    ([xshift=5em]verif2.south) edge node[align=center] {$K$} ([xshift=5em]fp.north)
+    ([xshift=5em]verif3.south) edge node[align=center] {$K$} ([xshift=5em]sv.north)
+    %([xshift=5em]verif4.south) edge node[align=center] {$K$} ([xshift=5em]cv.north)
     ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
@@
     ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
-    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$P$} ([xshift=-5em]synth.south)
-    (aux1) edge (synth.north);
+    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$K$} ([xshift=-5em]synth.south)
+    (aux3) edge (synth.north);
    \path[-]
-   (verif2.north) edge node[align=center] {} ([xshift=-2.7cm]aux6)
-   ([xshift=-2.7cm]aux6) edge node[align=center] {Increase Precision} (aux5)
-   (verif3.north) edge node[align=center] {} ([xshift=4cm]aux4)
-   ([xshift=4cm]aux4) edge node[align=center] {Increase Completeness Threshold} (aux3)
-   (verif4.north) edge node[align=center] {} ([xshift=10.5cm]aux2)
-   ([xshift=10.5cm]aux2) edge node[align=center] {Increase Sampling Rate} (aux1);
+   (verif2.north) edge node[align=center] {} ([xshift=0cm]aux6)
+   ([xshift=0cm]aux6) edge node[align=center] {Increase Precision} (aux5)
+   (verif3.north) edge node[align=center] {} ([xshift=6.7cm]aux4)
+   ([xshift=6.7cm]aux4) edge node[align=center] {Increase Completeness Threshold} (aux3);
+   %(verif4.north) edge node[align=center] {} ([xshift=10.5cm]aux2)
+   %([xshift=10.5cm]aux2) edge node[align=center] {Increase Sampling Rate} (aux1);
 

### 2017-01-24 cav2017/cav2017.tex
safety errors

@@
 {\it i.e.} iff their absolute values are less than one~\cite{astrom1997computer}. 
-In this paper, we express the stability specification $\phi_{stability}$ in terms of a check known as Jury's criterion \cite{fadali}. 
+We express the stability specification $\phi_{stability}$ in terms of a check known as Jury's criterion \cite{fadali}. 
 This condition boils down to an easy algebraic formula to select the entries of matrix $K$, 
@@
 indeed, the state values may leave the safe whilst they converge to the equilibrium, 
-which is typical in the case of oscillatory dynamics.
+which is typical in the case of oscillatory dynamics. However, a safe system will always be stable.
 
@@
 
-%Thus far we have presented a verification procedure for a digitalised plant in a continuous space (\emph{i.e.} the
-%range of the quantizers is still $\mathbb{R}$. The next step we must realise is that the controller 
-%exists in a digital program, hence its domain is $\mathbb{R}\langle I,F\rangle$.
-We have $\mat{A},\mat{B},\vec{x} \in \mathbb{R}^*$, $\mat{K}_d,\vec{u},\hat{\vec{x}}=\mathcal{F}\langle I,F \rangle(\vec{x}) \in \mathbb{R}\langle I,F\rangle^*$
-%Where $*$ represents the appropriate dimension for each matrix/vector.
-%Unfortunately this means that although the closed loop dynamics are in the reals, they suffer from
-%the fixed word restrictions in their composing elements.
-%Apart from the quantization errors $q_1,q_2$ there are rounding errors in the calculation of $u_k$. 
-%These will introduce a new source of quantization noise which we may denote $\vec{\nu}_3 \in [-q_3\ \ q_3]$.
-%The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=(|\mat{K}|_1+1)c_m$
-
 \subsubsection{Effect on safety specification and stability}
@@
 We note that the effect on stability due to the fixed-word-length error is that the system may, instead of converging to the desired equilibrium point, converge to a point that is bounded away from the desired equilibrium point (see Appendix for details).
-In this paper, we are concerned with \emph{safe} controllers and therefore concerned only that the system converges to a point within the safety specification.
-Hence, it is sufficient to synthesize a stable controller based on infinite precision, and then verify safety.
+In this paper, we synthesise a stable controller only as a precursor to synthesising a \emph{safe} controllers and it is therefore sufficient that the system converges to a point within the safe states.
+Hence, it is sufficient to disregard the errors when we synthesize a stable controller, and then verify safety.
 

### 2017-01-24 cav2017/cav2017.tex
removing commented out stuff
If you want it back, get it from a previous commit.

@@
 
-%%%-------------------------------
-%%\subsection{Digital implementation of feedback controller}
-%%\label{ssec:quantizationerror}
-%%%-------------------------------
-%%
-%%\addtodo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.} 
-%%
-%%\addtodo{[The remainder of the section needs to be updated. ]}
-%%The output and measurable of the plant is being sampled by an ADC, and since the full state of the
-%%plant cannot be witnessed directly, the controller software includes an observer that 
-%%estimates the state of the plant (see appendix for details on how such an observer
-%%is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  
-%%\addtodo{[Unclear what the remainder is for: ]}
-%%We further presume that there are small tolerances in the system 
-%%described in the following form
-%%%
-%%\begin{align*}
-%%\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
-%%\end{align*}
-%%\commentib{What is S?}
-%%
-%%Where $\mathcal{G}_J$ is a collection of eigenvalue ranges that define the frequency response of the system.
-%%We presume that the internal model of the plant is an ARMA model, modified by a
-%%state transform that has no tolerances. Tolerances in the eigenvectors will manifest themselves
-%%as tolerances in the canonical forms outside of the row/column of interests and complicate the 
-%%evaluation. Whilst it is possible to address these with this methodology, we will focus on the case
-%%above for simplicity.
-
-% \addtodo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.}
-
-% \addtodo{[The remainder of the section needs to be updated. ]}
-% The output and measurable of the plant is being sampled by an ADC, and since the full state of the
-% plant cannot be witnessed directly, the controller software includes an observer that 
-% estimates the state of the plant (see appendix for details on how such an observer
-% is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  
-% \addtodo{[Unclear what the remainder is for: ]}
-
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 
-%Let $\mathbb{R} \langle I,F \rangle$ \todo{notice this notation differs from the one used above} be a fixed point domain with $I$ bits representing the integer part 
-%and $F$ bits representing the decimal part \todo{why R, comment on that.}. The smallest number that can be represented in this domain is $c_m=2^{-F}$.
 The following approximation errors will arise:
@@
 $\mathcal{F}\langle I,F \rangle(x) = x-\delta_T : \delta_T=x\ \%_{c_m}\ \tilde x$, where $\%_{c_m}$ is the modulus operation performed on the last bit.
-%Let $\mathcal{F}\langle I,F \rangle(\cdot) : \mathbb{R} \rightarrow \mathbb{R}\langle I,F \rangle, \tilde x=\mathcal{F}\langle I,F \rangle(x) = x-\delta_T : \delta_T=x\ \%_{c_m}\ \tilde x$, where $\%_{c_m}$ is the modulus operation performed on the last bit.
+
 So $\delta_T$ is the truncation error and it will propagate across operations.
@@
 
-%$c_1\pm c_2= c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$ 
 \item Multiplication: $\mathcal{F}\langle I,F \rangle(c_1) * \mathcal{F}\langle I,F \rangle(c_2) =  c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}*\mathcal{F}\langle I,F \rangle(c_2)| + |\delta_{T2}*\mathcal{F}\langle I,F \rangle(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
@@
 \item {\bf Overflow:}
-  %Another source of error introduced by Finite Word Length representations is that of overflow.
 The maximum size of a real number $x$ that can be represented in a fixed point domain as $\mathcal{F}\langle I,F \rangle(x)$ is $\pm (2^{I-1}+1-2^{-F})$.
@@
 
-%The finite word length set a
-%maximum representable number in the domain \todo{what is next?
-a domain?
-define formally, no back-of-the-envelope mathsy stuff.} ($\pm (2^{I-1}+1-2^{-F})$), which means that any number outside this range
-%cannot be represented by the domain. Our tool currently assumes no saturation
-%function and verifies that no state overflows.
 \end{enumerate}
@@
 Hence, it is sufficient to disregard the errors when we synthesize a stable controller, and then verify safety.
-
-%% %-------------------------------
-%% \section{Counter-Example Guided Inductive Synthesis with solution generalisation}
-%% %-------------------------------
-
-%% This technique relies on parametrizing the target language, which
-%% induces a lattice of progressively more expressive languages 
-%% \textcolor{red}{Cristina: Citation?}.  We
-%% start by attempting to synthesise a program at the lowest point on
-%% this lattice and increase the parameters of the language until we
-%% reach a point at which the synthesis succeeds. As well as giving us an
-%% automatic search procedure, this parametrisation greatly increases the
-%% efficiency of our system since languages low down the lattice are very
-%% easy to decide safety for (i.e. the validation oracle finds an answer
-%% fast). If a program can be synthesised in a low-complexity language,
-%% the whole procedure finishes much faster than if synthesis had been
-%% attempted in a high-complexity language.
-
-%% \textcolor{red}{Cristina: How does this section relate to our control-synthesis work? 
-%% This is text is too generic...}
-
-%% \begin{figure}
-%% \centering
-%% \hspace*{-1cm}
-%% \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
-%%   \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
-%% },
-%%           row sep=1cm, column sep=1.5cm] {
-%%    \coordinate (aux1);
-%%    \& \coordinate (aux2);
-%%    \& ;\\
-%%    \node[fill=yellow!20,align=center] (synth) {{\sc inductive}\\{\sc generalisation}};
-%%    \&
-%%    complexnode/.pic={ 
-%%      \node[rectangle,draw,dashed,
-%% 	minimum width=6.7cm,
-%% 	minimum height=.8cm,
-%% 	label={\sc Validation oracles},] (verif) {};
-%%    \node[fill=yellow!20] (verif1) at ([xshift=-2.1cm]verif.center) {{\sc Validate}};
-%%    \node[fill=yellow!20,align=center] (verif2) at ([xshift=1.7cm]verif.center) {{\sc validate general}};
-%%    } 
-%%    \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
-%%    %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
-%%    %% \&
-%%    %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
-%%    \& \\
-%%    \& \\
-%%    \node (gp) {Program Search};
-%%    \&
-%%    complexnode/.pic={ 
-%%      \coordinate (aux);
-%%    \node (bmc) at ([xshift=-2.1cm]aux.center) {SAT/SMT Solver};
-%%    \node (fp)  at ([xshift=1.9cm]aux.center) {SAT/SMT Solver};
-%%    }   
-%%     \\
-%%   };
-
-%%    \path
-%%     ([yshift=2em]synth.east) edge node[xshift=-0.7em] {Candidate} ([yshift=2em]verif1.west)
-%%     ([yshift=-2em]verif1.west) edge node[xshift=-0.7em] {New input} ([yshift=-2em]synth.east)
-%%     (verif1) edge node {Generalise} (verif2)
-%%     ([xshift=5em]verif1.south) edge node[align=center] {Candidate} ([xshift=5em]bmc.north)
-%%     ([xshift=5em]verif2.south) edge node[align=center] {Candidate} ([xshift=3.8em]fp.north)
-%%     ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif1.south)
-%%     ([xshift=-6.2em]fp.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif2.south)
-%%     (verif2) edge node {} (done)
-%%     ([xshift=5em]synth.south) edge node[align=center] {{\sc Inputs}} ([xshift=5em]gp.north)
-%%     ([xshift=-5em]gp.north) edge node[align=center] {No solution/\\Candidate} ([xshift=-5em]synth.south)
-%%     (aux1) edge (synth.north);
-%%    \path[-]
-%%    (verif2.north) edge node[align=center] {} ([xshift=5.6cm]aux2)
-%%    ([xshift=5.6cm]aux2) edge node[align=center] {Increase parameters} (aux1);
-
-%% \end{tikzpicture}
-%% \caption{The CEGIS loop with solution generalisation\label{fig:CEGIS-multiple-verif}. 
-%% \textcolor{red}{Cristina: What is the difference of this figure to that in our HSCC paper?}}
-%% \end{figure}
-
-%%   %% \textcolor{red}{LC: Cristina, can you please fix this figure? The text ``candidate'' overlaps with the dotted box.}
 

### 2017-01-24 cav2017/cav2017.tex
reviewed 3.3 Stability of closed-loop systems

--- 2017-01-24 cav2017/cav2017.tex
@@
 
-%\addtodo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantization noises yet).]}
-
-Asymptotic stability boils down to Lyapunov stability and convergence to an equilibrium point~\cite{Astrom08}.  %\todo{add reference}.  
-Lyapunov stability requires that model trajectories remain in a neighbourhood of the equilibrium point. 
+Asymptotic stability boils down to Lyapunov stability 
+and convergence to an equilibrium point~\cite{Astrom08}. 
+Lyapunov stability requires that model trajectories remain i
+n a neighborhood of the equilibrium point. 
 In the case of closed-loop LTI models as in \eqref{eq:closedloopss}, 
-the equilibrium point is the origin (if the reference is equal to zero), or an offset thereof.  
-In this paper, we consider systems with a reference signal equal to zero.
-
-A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable if and only if all the roots 
-of the characteristic polynomial ({\it i.e.}, the eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity circle in the complex plane, 
-{\it i.e.} iff their absolute values are less than one~\cite{astrom1997computer}. 
-In this paper, we express the stability specification $\phi_{stability}$ in terms of a check known as Jury's criterion \cite{fadali}. 
-This condition boils down to an easy algebraic formula to select the entries of matrix $K$, 
-so that the closed-loop dynamics are shaped as desired. 
-A detailed description of this specification can be found in the Appendix~\ref{sec:appendix-stability}.
+the equilibrium point is the origin (if the reference is equal to zero), 
+or an offset thereof. Here, we consider systems with a zero reference signal.
+
+A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable 
+\textit{iff} all the roots of the characteristic polynomial 
+(i.e., the eigenvalues of the closed-loop matrix $A_d - B_d K$) 
+are inside the unity circle in the complex plane, i.e., \textit{iff} their absolute 
+values are less than one~\cite{astrom1997computer}. 
+In this paper, we express the stability specification $\phi_{stability}$ 
+in terms of a check known as Jury's criterion~\cite{fadali}. 
+This condition boils down to an easy algebraic formula to select the entries 
+of matrix $K$, so that the closed-loop dynamics are shaped as desired. 
+A detailed description of this specification can be found in the 
+Appendix~\ref{sec:appendix-stability}.
 

### 2017-01-24 cav2017/cav2017.tex
text

--- 2017-01-24 cav2017/cav2017.tex
@@
 
-%\addtodo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantization noises yet).]}
-
-Asymptotic stability boils down to Lyapunov stability and convergence to an equilibrium point~\cite{Astrom08}.  %\todo{add reference}.  
-Lyapunov stability requires that model trajectories remain in a neighbourhood of the equilibrium point. 
-In the case of closed-loop LTI models as in \eqref{eq:closedloopss}, 
-the equilibrium point is the origin (if the reference is equal to zero), or an offset thereof.  
-In this paper, we consider systems with a reference signal equal to zero.
-
-A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable if and only if all the roots 
-of the characteristic polynomial ({\it i.e.}, the eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity circle in the complex plane, 
-{\it i.e.} iff their absolute values are less than one~\cite{astrom1997computer}. 
-We express the stability specification $\phi_{stability}$ in terms of a check known as Jury's criterion \cite{fadali}. 
-This condition boils down to an easy algebraic formula to select the entries of matrix $K$, 
-so that the closed-loop dynamics are shaped as desired. 
-A detailed description of this specification can be found in the Appendix~\ref{sec:appendix-stability}.
+Asymptotic stability boils down to Lyapunov stability 
+and convergence to an equilibrium point~\cite{Astrom08}. 
+Lyapunov stability requires that model trajectories remain in 
+a neighborhood of the equilibrium point. 
+In the case of closed-loop LTI models as in~\eqref{eq:closedloopss}, 
+the equilibrium point is the origin (if the reference is equal to zero), 
+or an offset thereof. Here, we consider systems with a zero reference signal.
+
+A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable 
+\textit{iff} all the roots of the characteristic polynomial 
+(i.e., the eigenvalues of the closed-loop matrix $A_d - B_d K$) 
+are inside the unity circle in the complex plane, i.e., \textit{iff} their absolute 
+values are less than one~\cite{astrom1997computer}. 
+In this paper, we express the stability specification $\phi_{stability}$ 
+in terms of a check known as Jury's criterion~\cite{fadali}. 
+This condition boils down to an easy algebraic formula to select the entries 
+of matrix $K$, so that the closed-loop dynamics are shaped as desired. 
+A detailed description of this specification can be found in the 
+Appendix~\ref{sec:appendix-stability}.
 

### 2017-01-24 benchmark-runner/matlab_check_safety_stability.m
i really really hate char polys

@@ -1,5 +1,6 @@
 
 %mag suspension
+
 K = [17.4384765625, -0.0537109375];
 A = [558.1114,-1;1,0] 
 B = [32;0] 

### 2017-01-24 benchmark-runner/universalrunner/safety_stability.c

@@ -148,7 +148,7 @@ int check_stability(void){
 #if NSTATES==2
 void __CPROVER_EIGEN_charpoly_2(void) { //m00*m11 - m01*m10 - m00*x - m11*x + x^2
 
-  __CPROVER_EIGEN_poly[2] = sub ( mult(__m[0][0],__m[1][1]), mult(__m[1][0] , __m[1][0]) );
+  __CPROVER_EIGEN_poly[2] = sub ( mult(__m[0][0],__m[1][1]), mult(__m[0][1] , __m[1][0]) );
 
   __CPROVER_EIGEN_poly[1] = sub (zero_type, add (__m[0][0], __m[1][1]) ) ;
   // s^2

### 2017-01-24 cav2017/cav2017.tex
reviewed 3.4 Safety specifications for dynamical systems

@@
 
+\todo{Have we covered all the literature by Feron et al?}
+
 \paragraph{Discretization Effects}
@@
 
-As mentioned earlier, 
-in this work we are not bound to the synthesis of digital stabilizing controllers -- 
+In this study, we are not bound to the synthesis of digital stabilizing controllers -- 
 a well known task in the literature on digital control system -- 
@@
 which is typical in the case of oscillatory dynamics. However, a safe system will always be stable.
-
 In this work, the safety property represented by $\phi_{safety}$ is encoded as follows: 
@@
 such that ${\underline{u} \leq u_{k} \leq \overline{u}},\forall k\geq 0$.  
-In practice, 
-this means that the control input saturates in view of physical constraints.
+This means that the control input saturates in view of physical constraints.
 
@@
 \begin{align*}
-x_k   &= (A_d - B_d K)^k x \\
-      &= (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i \\
-      &= \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i \\
-      &= \sum_{i=1}^{2^n} \alpha_i x_k^i
+x_k   &= (A_d - B_d K)^k x = (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i \\
+      &= \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i = \sum_{i=1}^{2^n} \alpha_i x_k^i, 
  \end{align*}     
@@
 \vspace{0.1cm}
-\caption{Completeness threshold}
+\caption{Completeness threshold for multi-staged verification}
 \end{figure*}

### 2017-01-24 cav2017/cav2017.tex
Introduction nudge more contributions

@@
 
-Whilst there is a vast literature on validation of control systems,
+Although there is a vast literature on validation of control systems,
 the subject of control synthesis has been somewhat restricted in the
@@
 alongside the discrete domain of the controller and the hybrid elements that relate them.  
-%% In this paper, we synthesize controllers for hybrid
-%% closed-loop systems, i.e., software-implemented embedded controllers along
-%% with a model of their physical environment (the plant), that are
-%% \emph{safe}.
 Due to the complexity of such systems, in this particular work we focus
 on linear models with known  implementation features (e.g., number of bits, fixed-point
-arithmetic) %\addtodo{[clarify next] with known configurations} 
-and perform %parametric 
-synthesis of safe digital controllers.
+arithmetic) and perform synthesis of safe digital controllers.
 
@@
 guided inductive synthesis (CEGIS) loop. In the first approach, 
-we devise a digital controller that stabilizes the system; then, we verify its 
+we devise a digital controller that stabilizes the system whilst remaining safe given a 
+pre-selected time horizon; then, we verify its 
 potential safety by unfolding the dynamics of the system and checking for 
@@
 based on~\cite{Monteiro16}, but enhanced to include evaluation of quantization effects and 
-safety properties over the state space. In an alternative approach, we use a verification engine based 
+safety properties over the state space. 
+In an alternative approach, we use a verification engine based 
 on abstract acceleration~\cite{cattaruzza2015unbounded}, which avoids the explicit unwinding 
-the transition system necessarily for the first approach. In both approaches, we project
-the maximum effect of the noise over an unbounded time and uses it as a buffer region 
+of the transition system necessary for the first approach. We introduce a CEGAR loop to this abstraction
+in order to make it less conservative, and develop a CEGIS feedback based on abstraction refinement to
+increase the speed of the synthesis algorithm.
+In both approaches, we project the maximum effect of the noise over an unbounded time and uses it as a buffer region 
 for the safety specification.

### 2017-01-24 cav2017/cav2017.tex
i.e.,

@@
 The models we consider have two sources of error due to numeric representation. 
-The first is the numeric error introduced by the fixed-point numbers employed to model the plant, i.e. to represent the plant dynamics $A_d$, $B_d$ and its states. 
+The first is the numeric error introduced by the fixed-point numbers employed to model the plant, i.e., to represent the plant dynamics $A_d$, $B_d$ and its states. 
 The second is the quantization error introduced by the digital controller, 
@@
 \end{enumerate}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%\subsection{Fixed word length effects on matrix multiplications}
-%\label{sec:cof_fwl}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 
@@
 must apply some form of solution generalisation to obtain a full
-solution (i.e. a solution in the original search space).
+solution (i.e., a solution in the original search space).
 
@@
 languages low down the lattice are very easy to decide safety for
-(i.e. the validation oracle finds an answer fast). If a program can be
+(i.e., the validation oracle finds an answer fast). If a program can be
 synthesized in a low-complexity language, the whole procedure finishes
@@
 \end{itemize}
-
-%% The advantage of the second approcah are that whereas in the first case we use concrete traces from non-deterministic simulations
-%% and generalize over continuous sets into an unbounded time, 
-%% the abstract acceleration synthesis analyses the system over a generalized state-space (ie it looks at all the states simultaneously), requiring the CEGIS loop to generalize only over the time horizon of the system.
-
-%% \addtodo{Can we come up with some sort of figure that makes it easier to visualise
-%% the generalisation step in each approach?}
-
-% In Sec.~\ref{sec:CEGIS-abstraction-refinement} and 
-% Sec.~\ref{sec:CEGIS-precision-incrementation}, we explain how we 
-% specialise the general CEGIS approach in order to perform solution generalisation.
 
@@
 such that the boundaries are not violated for any $k{>}\overline{k}$
-(i.e. it is sufficient to unwind the closed-loop state-space system up to  
+(i.e., it is sufficient to unwind the closed-loop state-space system up to  
 $\overline{k}$ in order to ensure that $\phi_{safety}$ holds).
@@
 \begin{enumerate}
-\item The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
+\item The inductive synthesis phase (i.e., {\sc synthesize}) uses BMC to
 compute a candidate solution $K$
@@
 
-%% The stability criteria are satisfied if the characteristic polynomial of $A_d - B_d * K_d$ meets Jury's criteria. This is 
-%% independent of the initial states. 
 Regarding the latter, we synthesize a safe controller by unwinding the transition system
@@
 state within $k$ steps where again we assume $k$ to be under the completeness threshold. 
-%The safety criteria here must be valid for all possible allowed initial states, and so we
 After unwinding the transition system corresponding to the previously synthesized controller
@@
 distance from the reference (in this case the origin) decreases over time.
-
-%\todo[inline] {please will Alessandro write the proof for the completeness threshold here - EP}
-%\missingfigure{picture for completeness threshold}
 
@@
 we use abstract acceleration again to obtain
-the reach-tube, i.e. the set of all reachable states at all times given an initial set $\phi_{init}$:
+the reach-tube, i.e., the set of all reachable states at all times given an initial set $\phi_{init}$:
 \begin{align}

### 2017-01-24 cav2017/cav2017.tex
reviewed 3.5 Numeric representations and soundness

--- 2017-01-24 cav2017/cav2017.tex
@@
 
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%\subsection{Fixed word length effects on matrix multiplications}
-%\label{sec:cof_fwl}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-We will use $\mathcal{F}\langle I_c,F_c \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}\langle I_p,F_p \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model.
-Thus any mathematical operations occurring in the digital controller will occur in the domain $\mathcal{F}\langle I_c,F_c \rangle$, and all other calculations will be carried out in the domain $\mathcal{F}\langle I_p,F_p \rangle$.
+We use $\mathcal{F}\langle I_c,F_c \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}\langle I_p,F_p \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model.
+Thus all mathematical operations occurring in the digital controller occur in the domain $\mathcal{F}\langle I_c,F_c \rangle$, and all other calculations are carried out in the domain $\mathcal{F}\langle I_p,F_p \rangle$.
 

### 2017-01-24 cav2017/cav2017.tex
i.e.,
added initial constraints on x_0

--- 2017-01-24 cav2017/cav2017.tex
@@
 Furthermore, 
-it is practically relevant to consider constraints on the input signal $u_{k}$, 
-which we assume has given bounds $\overline{u}$ and $\underline{u}$, 
-such that ${\underline{u} \leq u_{k} \leq \overline{u}},\forall k\geq 0$.  
-This means that the control input saturates in view of physical constraints.
+it is practically relevant to consider constraints on the input signal $u_{k}$
+and initial states $x_0$, 
+which we assume have given bounds. %%  $\overline{u}$, $\underline{u}$
+%% and $\overline{x_0}$, $\underline{x_0}$, respectively.
+We refer to these constraints as $\phi_{init}$:
+$$\phi_{init} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} 
+\wedge \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}$$.  
+In practice, 
+this means that the control input saturates in view of physical constraints.
+
+%%%-------------------------------
+%%\subsection{Digital implementation of feedback controller}
+%%\label{ssec:quantizationerror}
+%%%-------------------------------
+%%
+%%\addtodo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.} 
+%%
+%%\addtodo{[The remainder of the section needs to be updated. ]}
+%%The output and measurable of the plant is being sampled by an ADC, and since the full state of the
+%%plant cannot be witnessed directly, the controller software includes an observer that 
+%%estimates the state of the plant (see appendix for details on how such an observer
+%%is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  
+%%\addtodo{[Unclear what the remainder is for: ]}
+%%We further presume that there are small tolerances in the system 
+%%described in the following form
+%%%
+%%\begin{align*}
+%%\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
+%%\end{align*}
+%%\commentib{What is S?}
+%%
+%%Where $\mathcal{G}_J$ is a collection of eigenvalue ranges that define the frequency response of the system.
+%%We presume that the internal model of the plant is an ARMA model, modified by a
+%%state transform that has no tolerances. Tolerances in the eigenvectors will manifest themselves
+%%as tolerances in the canonical forms outside of the row/column of interests and complicate the 
+%%evaluation. Whilst it is possible to address these with this methodology, we will focus on the case
+%%above for simplicity.
+
+% \addtodo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.}
+
+% \addtodo{[The remainder of the section needs to be updated. ]}
+% The output and measurable of the plant is being sampled by an ADC, and since the full state of the
+% plant cannot be witnessed directly, the controller software includes an observer that 
+% estimates the state of the plant (see appendix for details on how such an observer
+% is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  
+% \addtodo{[Unclear what the remainder is for: ]}
+>>>>>>> added initial constraints on x_0
 
@@
 Next, we describe the different phases in Fig.~\ref{fig:CEGIS-precision-increment}
-(blocks 1 to 5):
+(blocks 1 to 4):
 
@@
 % \addtodo{Move as much as possible from Sec~\ref{sec:cof_verification}
-% to the appendix (e.g. discussion on abstract acceleration). 
+% to the appendix (e.g., discussion on abstract acceleration). 
 % Merge the rest in Sec~\ref{sec:cof_synth}.}
@@
   %% These are the rows of $\mat{E} \in \Psi$ that intersect/segment $\hat{X}^\#$. Transforming these rows into the eigenspace of $\mat{A}_t$, and applying backward acceleration to
- as a set of counterexamples for the eigenvalues, which we define as $\phi_\Lambda$. This is a constraint in the spectrum (\emph{ie} transfer function) of the closed loop dynamics. 
+ as a set of counterexamples for the eigenvalues, which we define as $\phi_\Lambda$. This is a constraint in the spectrum i.e., transfer function) of the closed loop dynamics. 
 \item We use $\phi_\Lambda$ to

### 2017-01-24 cav2017/cav2017.tex

--- 2017-01-24 cav2017/cav2017.tex
@@
 
-We will use $\mathcal{F}\langle I_c,F_c \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}\langle I_p,F_p \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model.
-Thus any mathematical operations occurring in the digital controller will occur in the domain $\mathcal{F}\langle I_c,F_c \rangle$, and all other calculations will be carried out in the domain $\mathcal{F}\langle I_p,F_p \rangle$.
+We use $\mathcal{F}\langle I_c,F_c \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}\langle I_p,F_p \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model.
+Thus all mathematical operations occurring in the digital controller occur in the domain $\mathcal{F}\langle I_c,F_c \rangle$, and all other calculations are carried out in the domain $\mathcal{F}\langle I_p,F_p \rangle$.
 

### 2017-01-24 cav2017/cav2017.tex
e.g.,

--- 2017-01-24 cav2017/cav2017.tex
@@
 response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics, 
-with the goal either to verify (e.g.~\cite{daes20161}) or to optimize
-(e.g.~\cite{oudjida2014design}) given implementations.
+with the goal either to verify (e.g.,~ \cite{daes20161}) or to optimize
+(e.g.,~ \cite{oudjida2014design}) given implementations.
 

### 2017-01-24 cav2017/cav2017.tex

@@
 response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics, 
-with the goal either to verify (e.g.,~ \cite{daes20161}) or to optimize
-(e.g.,~ \cite{oudjida2014design}) given implementations.
+with the goal either to verify (e.g.~\cite{daes20161}) or to optimize
+(e.g.~\cite{oudjida2014design}) given implementations.
 

### 2017-01-24 cav2017/cav2017.tex
huh, how did that happen
text

--- 2017-01-24 cav2017/cav2017.tex
@@
 %modern embedded software, performing highly non-trivial control tasks,
-with significant impact in numerous application areas such as
+with significant impact in numerous application areas as in 
 the life sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}.
@@
 the effects of finite-precision arithmetic, time discretization, and quantization noise, which are typically introduced 
-by Analogue-to-Digital (A/D) and Digital-to-Analogue (D/A) conversion.  
+by Analogue-to-Digital (A/D) \todo{later ADC and DAC} and Digital-to-Analogue (D/A) conversion.  
 Whilst the research on digital control is well developed~\cite{astrom1997computer}, 
-automated and sound control synthesis is a challenging task. 
+automated and sound control synthesis is a challenging task,  
 %Thus, the programming is a key barrier to broad adoption of digital control, 
 %and requires considerable expertise.
-
-Although there is a vast literature on validation of control systems,
-the subject of control synthesis has been somewhat restricted in the
-properties it explores.  Traditionally, this focuses mainly on stability %, working typically on continuous domains
-\cite{DBLP:journals/corr/AbateBCCDKK16,sadabadi2016static}, or using switched
-models~\cite{DBLP:conf/emsoft/RavanbakhshS16}.
-Reachability tools are
-also used when discretizing the state-space for verification and
-parametric synthesis~\cite{cimatti2013parameter}.
+%Whilst there is a vast literature on validation of control systems,
+%the subject of control synthesis has been somewhat restricted in the properties it explores.  
+%Traditionally, this focuses mainly on stability %, working typically on continuous domains
+particularly when the synthesis objective goes beyond classical stability or tracking requirements. 
+%\cite{DBLP:journals/corr/AbateBCCDKK16,sadabadi2016static}, or using switched
+%models~\cite{DBLP:conf/emsoft/RavanbakhshS16}. 
+Beyond stability, 
+recently reachability tools have been developed [cite SPACEx, Phaver, and others], 
+however they have not been employed towards control synthesis. 
+\todo{why do we cite this paper \cite{cimatti2013parameter}?what is the relationship with our work? }
+% when discretising the state-space for verification and
+%parameter synthesis~\cite{cimatti2013parameter}.
 
@@
 LTI models taking into consideration the continuous domain of the plant, 
-alongside the discrete domain of the controller and the hybrid elements that relate them.  
-Due to the complexity of such systems, in this particular work we focus
+alongside the discrete domain of the controller, 
+as well as the hybrid elements that relate them.  
+%% In this paper, we synthesize controllers for hybrid
+%% closed-loop systems, i.e., software-implemented embedded controllers along
+%% with a model of their physical environment (the plant), that are
+%% \emph{safe}.
+Due to the complexity of such systems, in this work we focus 
 on linear models with known  implementation features (e.g., number of bits, fixed-point
-arithmetic) and perform synthesis of safe digital controllers.
-
-We describe and evaluate two approaches for synthesizing digital controllers 
+arithmetic), %\addtodo{[clarify next] with known configurations} 
+and perform %parametric 
+synthesis of safe digital controllers - the extension to more general quantitative properties is left to future work.
+
+We describe and evaluate two approaches for synthesising digital controllers 
 for state-space physical plants. Both approaches consider a counterexample 
 guided inductive synthesis (CEGIS) loop. In the first approach, 
-we devise a digital controller that stabilizes the system whilst remaining safe given a 
-pre-selected time horizon; then, we verify its 
+we devise a digital controller that stabilises the system; then, we verify its 
 potential safety by unfolding the dynamics of the system and checking for 
-a completeness threshold. In the second approach, we employ abstract acceleration
-to accelerate the dynamics forward instead of symbolically unwinding the 
-transition relation~\cite{cattaruzza2015unbounded}. We provide experimental results 
-showing that both approaches are able to efficiently synthesize stable and safe controllers 
+a completeness threshold. In the second approach, we substitute the second step by employing abstract acceleration
+to unfold the dynamics forward, instead of symbolically unwinding the 
+transition relation~\cite{cattaruzza2015unbounded}. 
+\todo{We need to mention the CEGIS architecture here. We need to emphasise the derivation of errors for soundness. Can we claim completeness already?}
+We provide experimental results 
+showing that both approaches are able to efficiently synthesise stable and safe controllers 
 for a set of intricate physical plant models taken from the digital 
@@
 based on~\cite{Monteiro16}, but enhanced to include evaluation of quantization effects and 
-safety properties over the state space. 
-In an alternative approach, we use a verification engine based 
+safety properties over the state space. In an alternative approach, we use a verification engine based 
 on abstract acceleration~\cite{cattaruzza2015unbounded}, which avoids the explicit unwinding 
-of the transition system necessary for the first approach. We introduce a CEGAR loop to this abstraction
-in order to make it less conservative, and develop a CEGIS feedback based on abstraction refinement to
-increase the speed of the synthesis algorithm.
-In both approaches, we project the maximum effect of the noise over an unbounded time and uses it as a buffer region 
+the transition system necessarily for the first approach. In both approaches, we project
+the maximum effect of the noise over an unbounded time and uses it as a buffer region 
 for the safety specification.
@@
 
-Asymptotic stability boils down to Lyapunov stability 
-and convergence to an equilibrium point~\cite{Astrom08}. 
-Lyapunov stability requires that model trajectories remain in 
-a neighborhood of the equilibrium point. 
-In the case of closed-loop LTI models as in~\eqref{eq:closedloopss}, 
-the equilibrium point is the origin (if the reference is equal to zero), 
-or an offset thereof. Here, we consider systems with a zero reference signal.
-
-A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable 
-\textit{iff} all the roots of the characteristic polynomial 
-(i.e., the eigenvalues of the closed-loop matrix $A_d - B_d K$) 
-are inside the unity circle in the complex plane, i.e., \textit{iff} their absolute 
-values are less than one~\cite{astrom1997computer}. 
-In this paper, we express the stability specification $\phi_{stability}$ 
-in terms of a check known as Jury's criterion~\cite{fadali}. 
-This condition boils down to an easy algebraic formula to select the entries 
-of matrix $K$, so that the closed-loop dynamics are shaped as desired. 
-A detailed description of this specification can be found in the 
-Appendix~\ref{sec:appendix-stability}.
+%\addtodo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantization noises yet).]}
+
+Asymptotic stability boils down to Lyapunov stability and convergence to an equilibrium point~\cite{Astrom08}.  %\todo{add reference}.  
+Lyapunov stability requires that model trajectories remain in a neighbourhood of the equilibrium point. 
+In the case of closed-loop LTI models as in \eqref{eq:closedloopss}, 
+the equilibrium point is the origin (if the reference is equal to zero), or an offset thereof.  
+In this paper, we consider systems with a reference signal equal to zero.
+
+A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable if and only if all the roots 
+of the characteristic polynomial ({\it i.e.}, the eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity circle in the complex plane, 
+{\it i.e.} iff their absolute values are less than one~\cite{astrom1997computer}. 
+We express the stability specification $\phi_{stability}$ in terms of a check known as Jury's criterion \cite{fadali}. 
+This condition boils down to an easy algebraic formula to select the entries of matrix $K$, 
+so that the closed-loop dynamics are shaped as desired. 
+A detailed description of this specification can be found in the Appendix~\ref{sec:appendix-stability}.
 
@@
 
-In this study, we are not bound to the synthesis of digital stabilizing controllers -- 
+As mentioned earlier, 
+in this work we are not bound to the synthesis of digital stabilizing controllers -- 
 a well known task in the literature on digital control system -- 
@@
 which is typical in the case of oscillatory dynamics. However, a safe system will always be stable.
+
 In this work, the safety property represented by $\phi_{safety}$ is encoded as follows: 
@@
 such that ${\underline{u} \leq u_{k} \leq \overline{u}},\forall k\geq 0$.  
-This means that the control input saturates in view of physical constraints.
+In practice, 
+this means that the control input saturates in view of physical constraints.
 
@@
 The models we consider have two sources of error due to numeric representation. 
-The first is the numeric error introduced by the fixed-point numbers employed to model the plant, i.e., to represent the plant dynamics $A_d$, $B_d$ and its states. 
+The first is the numeric error introduced by the fixed-point numbers employed to model the plant, i.e. to represent the plant dynamics $A_d$, $B_d$ and its states. 
 The second is the quantization error introduced by the digital controller, 
@@
 
-We use $\mathcal{F}\langle I_c,F_c \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}\langle I_p,F_p \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model.
-Thus all mathematical operations occurring in the digital controller occur in the domain $\mathcal{F}\langle I_c,F_c \rangle$, and all other calculations are carried out in the domain $\mathcal{F}\langle I_p,F_p \rangle$.
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%\subsection{Fixed word length effects on matrix multiplications}
+%\label{sec:cof_fwl}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+We will use $\mathcal{F}\langle I_c,F_c \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}\langle I_p,F_p \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model.
+Thus any mathematical operations occurring in the digital controller will occur in the domain $\mathcal{F}\langle I_c,F_c \rangle$, and all other calculations will be carried out in the domain $\mathcal{F}\langle I_p,F_p \rangle$.
 
@@
 must apply some form of solution generalisation to obtain a full
-solution (i.e., a solution in the original search space).
+solution (i.e. a solution in the original search space).
 
@@
 languages low down the lattice are very easy to decide safety for
-(i.e., the validation oracle finds an answer fast). If a program can be
+(i.e. the validation oracle finds an answer fast). If a program can be
 synthesized in a low-complexity language, the whole procedure finishes
@@
 \end{itemize}
+
+%% The advantage of the second approcah are that whereas in the first case we use concrete traces from non-deterministic simulations
+%% and generalize over continuous sets into an unbounded time, 
+%% the abstract acceleration synthesis analyses the system over a generalized state-space (ie it looks at all the states simultaneously), requiring the CEGIS loop to generalize only over the time horizon of the system.
+
+%% \addtodo{Can we come up with some sort of figure that makes it easier to visualise
+%% the generalisation step in each approach?}
+
+% In Sec.~\ref{sec:CEGIS-abstraction-refinement} and 
+% Sec.~\ref{sec:CEGIS-precision-incrementation}, we explain how we 
+% specialise the general CEGIS approach in order to perform solution generalisation.
 
@@
 such that the boundaries are not violated for any $k{>}\overline{k}$
-(i.e., it is sufficient to unwind the closed-loop state-space system up to  
+(i.e. it is sufficient to unwind the closed-loop state-space system up to  
 $\overline{k}$ in order to ensure that $\phi_{safety}$ holds).
@@
 \begin{enumerate}
-\item The inductive synthesis phase (i.e., {\sc synthesize}) uses BMC to
+\item The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
 compute a candidate solution $K$
@@
 
+%% The stability criteria are satisfied if the characteristic polynomial of $A_d - B_d * K_d$ meets Jury's criteria. This is 
+%% independent of the initial states. 
 Regarding the latter, we synthesize a safe controller by unwinding the transition system
@@
 state within $k$ steps where again we assume $k$ to be under the completeness threshold. 
+%The safety criteria here must be valid for all possible allowed initial states, and so we
 After unwinding the transition system corresponding to the previously synthesized controller
@@
 distance from the reference (in this case the origin) decreases over time.
+
+%\todo[inline] {please will Alessandro write the proof for the completeness threshold here - EP}
+%\missingfigure{picture for completeness threshold}
 
@@
 we use abstract acceleration again to obtain
-the reach-tube, i.e., the set of all reachable states at all times given an initial set $\phi_{init}$:
+the reach-tube, i.e. the set of all reachable states at all times given an initial set $\phi_{init}$:
 \begin{align}

### 2017-01-24 cav2017/cav2017.tex
limited, not bound

--- 2017-01-24 cav2017/cav2017.tex
@@
 
-In this study, we are not bound to the synthesis of digital stabilizing controllers -- 
+In this study, we are not limited to the synthesis of digital stabilizing controllers -- 
 a well known task in the literature on digital control system -- 
@@
 % \addtodo{[Unclear what the remainder is for: ]}
->>>>>>> added initial constraints on x_0
+%>>>>>>> added initial constraints on x_0
 

### 2017-01-24 cav2017/cav2017.tex

@@
 LTI models taking into consideration the continuous domain of the plant, 
-alongside the discrete domain of the controller and the hybrid elements that relate them.  
-Due to the complexity of such systems, in this particular work we focus
+alongside the discrete domain of the controller, 
+as well as the hybrid elements that relate them.  
+%% In this paper, we synthesize controllers for hybrid
+%% closed-loop systems, i.e., software-implemented embedded controllers along
+%% with a model of their physical environment (the plant), that are
+%% \emph{safe}.
+Due to the complexity of such systems, in this work we focus 
 on linear models with known  implementation features (e.g., number of bits, fixed-point
-arithmetic) and perform synthesis of safe digital controllers.
-
-We describe and evaluate two approaches for synthesizing digital controllers 
+arithmetic), %\addtodo{[clarify next] with known configurations} 
+and perform %parametric 
+synthesis of safe digital controllers - the extension to more general quantitative properties is left to future work.
+
+We describe and evaluate two approaches for synthesising digital controllers 
 for state-space physical plants. Both approaches consider a counterexample 
@@
 potential safety by unfolding the dynamics of the system and checking for 
-a completeness threshold. In the second approach, we employ abstract acceleration
-to accelerate the dynamics forward instead of symbolically unwinding the 
-transition relation~\cite{cattaruzza2015unbounded}. We provide experimental results 
-showing that both approaches are able to efficiently synthesize stable and safe controllers 
+a completeness threshold. In the second approach, we substitute the second step by employing abstract acceleration
+to unfold the dynamics forward, instead of symbolically unwinding the 
+transition relation~\cite{cattaruzza2015unbounded}. 
+\todo{We need to mention the CEGIS architecture here. We need to emphasise the derivation of errors for soundness. Can we claim completeness already?}
+We provide experimental results 
+showing that both approaches are able to efficiently synthesise stable and safe controllers 
 for a set of intricate physical plant models taken from the digital 
@@
 
-In this study, we are not limited to the synthesis of digital stabilizing controllers -- 
+In this study, we are not bound to the synthesis of digital stabilizing controllers -- 
 a well known task in the literature on digital control system -- 

### 2017-01-24 cav2017/cav2017.tex
reviewed 4.1 General architecture of the program synthesizer

--- 2017-01-24 cav2017/cav2017.tex
@@
 We note that the effect on stability due to the fixed-word-length error is that the system may, instead of converging to the desired equilibrium point, converge to a point that is bounded away from the desired equilibrium point (see Appendix for details).
-In this paper, we synthesise a stable controller only as a precursor to synthesising a \emph{safe} controllers and it is therefore sufficient that the system converges to a point within the safe states.
+In this paper, we synthesize a stable controller only as a precursor to synthesizing a \emph{safe} controllers and it is therefore sufficient that the system converges to a point within the safe states.
 Hence, it is sufficient to disregard the errors when we synthesize a stable controller, and then verify safety.
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{CEGIS of Safe Controllers for LTI Systems with Solution Generalisation} 
+\section{CEGIS of Safe Controllers for LTI Systems with Solution Generalization} 
 \label{sec:CEGARIS} 
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%Abstractly-Refined
-In this section we outline the general architecture of the program synthesizer used in both approaches%\todo{which approaches?}. 
-We then give the details of the two methods of solution generalisation that we compare; the first checking safety by unwinding the transition relation to a completeness threshold; and the second employing abstract acceleration.
+
+Here, we outline the general architecture of the program synthesizer used in both approaches. 
+We then give the details of both methods of solution generalization that we compare; 
+the first checking safety by unwinding the transition relation to a completeness threshold; 
+and the second employing abstract acceleration.
 
@@
 some finite domain $\mathcal{D}$.
-
+%
 The design of our synthesizer consists of two phases, an inductive
@@
 added to the {\sc inputs} set and the loop iterates again.
-
+%
 It is worth noting that each iteration of the loop adds a new input to

### 2017-01-24 cav2017/cav2017.tex
edit of sec 4.1 (general architecture of the synthesiser)

@@
 added to the {\sc inputs} set and the loop iterates again.
-%
-It is worth noting that each iteration of the loop adds a new input to
-the finite set $\text{\sc inputs}$ that is used for synthesis.  Given
-that the full set of inputs $\mathcal{D}$ is finite, this means that
-the refinement loop can only iterate a finite number of times.
+More details about the general architecture of the synthesiser can
+be found in~\cite{DBLP:conf/lpar/DavidKL15}.
+%% It is worth noting that each iteration of the loop adds a new input to
+%% the finite set $\text{\sc inputs}$ that is used for synthesis.  Given
+%% that the full set of inputs $\mathcal{D}$ is finite, this means that
+%% the refinement loop can only iterate a finite number of times.
 

### 2017-01-24 cav2017/cav2017.tex
Alessandro's changes

@@
 
-We describe and evaluate two approaches for synthesising digital controllers 
+We describe and evaluate two approaches for synthesizing digital controllers 
 for state-space physical plants. Both approaches consider a counterexample 
@@
 we devise a digital controller that stabilizes the system whilst remaining safe given a 
-pre-selected time horizon; then, we verify its 
-potential safety by unfolding the dynamics of the system and checking for 
+pre-selected time horizon; then, we verify its potential safety by unfolding the dynamics of the system and checking for 
 a completeness threshold. In the second approach, we substitute the second step by employing abstract acceleration
@@
 We provide experimental results 
-showing that both approaches are able to efficiently synthesise stable and safe controllers 
+showing that both approaches are able to efficiently synthesize stable and safe controllers 
 for a set of intricate physical plant models taken from the digital 

### 2017-01-24 cav2017/cav2017.tex
reviewed 4.3 Solution generalization

--- 2017-01-24 cav2017/cav2017.tex
@@
 added to the {\sc inputs} set and the loop iterates again.
-More details about the general architecture of the synthesiser can
-be found in~\cite{DBLP:conf/lpar/DavidKL15}.
-%% It is worth noting that each iteration of the loop adds a new input to
-%% the finite set $\text{\sc inputs}$ that is used for synthesis.  Given
-%% that the full set of inputs $\mathcal{D}$ is finite, this means that
-%% the refinement loop can only iterate a finite number of times.
+%
+It is worth noting that each iteration of the loop adds a new input to
+the finite set $\text{\sc inputs}$ that is used for synthesis.  Given
+that the full set of inputs $\mathcal{D}$ is finite, this means that
+the refinement loop can only iterate a finite number of times.
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Solution generalisation} 
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Solution generalization} 
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
 Given the large solution space to be searched during the inductive
-synthesis phase, we parametrize the target language, which induces a
+synthesis, we parametrize the target language, which induces a
 lattice of progressively more expressive languages.  This enables us
@@
 reach a point at which the synthesis succeeds. Whenever we manage to
-synthesize a candidate solution at some lower point on the lattice, we
-must apply some form of solution generalisation to obtain a full
+synthesize a solution at some lower point on the lattice, we
+must apply some form of solution generalization to obtain a full
 solution (i.e., a solution in the original search space).
-
-As well as giving us an automatic search procedure, this
-parametrisation greatly increases the efficiency of our system since
-languages low down the lattice are very easy to decide safety for
+This parametrization greatly increases the efficiency of our system since
+languages low down the lattice are easy to decide safety for
 (i.e., the validation oracle finds an answer fast). If a program can be
@@
 much faster than if synthesis had been attempted in a high-complexity
-language.
-
-We investigate two different approaches of integrating solution generalisation 
-with CEGIS:
+language. We investigate two different approaches for integrating solution 
+generalization into CEGIS:
+%
 \begin{itemize}

### 2017-01-24 cav2017/cav2017.tex
reviewed 4.3 Solution generalization

@@
 
-\item The first {\sc verify} stage, {\sc safety}, checks that the candidate
+\item The first {\sc verify} stage, {\sc safety}, checks that candidate
 solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
-state within $k$ steps where again we assume $k$ to be under the completeness threshold. 
+state within $k$ steps where we assume $k$ to be under the completeness threshold. 
 After unwinding the transition system corresponding to the previously synthesized controller

### 2017-01-24 cav2017/cav2017.tex
Notations

@@
 for instance according to a specific stability goal or around a specific dynamical behaviour \cite{astrom1997computer}. 
-As argued later, in this work, we will target more complex objectives, such as quantitative safety requirements that are not typical in the digital control literature.
+As argued later in this work, we will target more complex objectives, such as quantitative safety requirements that are not typical in the digital control literature.
 
@@
 such that the feedback controller (namely the choice of the gains in $K$) 
-must ensure that the states never exist such requirement. 
+must ensure that the states never exit such requirement. 
 Note that a stable, closed-loop system is not necessarily a safe system: 
-indeed, the state values may leave the safe whilst they converge to the equilibrium, 
+indeed, the state values may leave the safe space whilst they converge to the equilibrium, 
 which is typical in the case of oscillatory dynamics. However, a safe system will always be stable.
@@
 This means that the states will always be within the $n$-dimensional hyper-box.
-%, which is typically defined by the safety specification.
 
@@
 
-%%%-------------------------------
-%%\subsection{Digital implementation of feedback controller}
-%%\label{ssec:quantizationerror}
-%%%-------------------------------
-%%
-%%\addtodo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.} 
-%%
-%%\addtodo{[The remainder of the section needs to be updated. ]}
-%%The output and measurable of the plant is being sampled by an ADC, and since the full state of the
-%%plant cannot be witnessed directly, the controller software includes an observer that 
-%%estimates the state of the plant (see appendix for details on how such an observer
-%%is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  
-%%\addtodo{[Unclear what the remainder is for: ]}
-%%We further presume that there are small tolerances in the system 
-%%described in the following form
-%%%
-%%\begin{align*}
-%%\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
-%%\end{align*}
-%%\commentib{What is S?}
-%%
-%%Where $\mathcal{G}_J$ is a collection of eigenvalue ranges that define the frequency response of the system.
-%%We presume that the internal model of the plant is an ARMA model, modified by a
-%%state transform that has no tolerances. Tolerances in the eigenvectors will manifest themselves
-%%as tolerances in the canonical forms outside of the row/column of interests and complicate the 
-%%evaluation. Whilst it is possible to address these with this methodology, we will focus on the case
-%%above for simplicity.
-
-% \addtodo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.}
-
 % \addtodo{[The remainder of the section needs to be updated. ]}
@@
 The second is the quantization error introduced by the digital controller, 
-which 
-performs operations in the domain of fixed-point numbers. 
+which performs operations in the domain of fixed-point numbers. 
 In this section we formally outline the errors introduced by fixed-point representation of numbers.
@@
 
+We will use $\mathcal{F}\langle I_c,F_c \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}\langle I_p,F_p \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model ($I_p \geq I_c \wedge F_p \geq F_c$).
+Thus any mathematical operations occurring in the digital controller will occur in the range of $\mathcal{F}\langle I_c,F_c \rangle$, and all other calculations will be carried out in the range of $\mathcal{F}\langle I_p,F_p \rangle$.
+
 \subsubsection{Effect on safety specification and stability}
-Thus we can consider the effect of these errors on our safety and stability verification.
+%Thus we can consider the effect of these errors on our safety and stability verification.
 
@@
 
-The states are computed using the following equations. 
+The inputs are computed using the following equations. 
 \begin{align*}
 u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})). 
-% x_{k+1}&=A_d x_{k} + B_du_{k}
 \end{align*}
 
-This will induce two types of the error detailed above, first the truncation errors due to representing $x_k$ as ${\langle I_c,F_c \rangle}(x_{k})$, and second the rounding error introduce by multiplying $x_k$ and $K$.
+This will induce two types of the error detailed above, first the truncation errors due to representing $x_k$ as $\mathcal{F}{\langle I_c,F_c \rangle}(x_{k})$, and second the rounding error introduced by the multiplication.
 We represent these errors as non-deterministic noise.
@@
 \begin{align*}
-\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k})&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
-\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k})(x_{k+1}) &=\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k})(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(u_{k})(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(u_{k})(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k})(u_{k})
+x_{k+1} &=\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k})
 \end{align*}
@@
 we can vary the plant's precision $\langle I_p,F_p\rangle$ such that 
-$\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I_c,F_c \rangle$.
+$I_p \geq I_c \wedge F_p \geq F_c$.
 

### 2017-01-24 cav2017/cav2017.tex
reviewed 4.5 CEGIS with abstraction refinement
aligning notation for ADC

@@
 the effects of finite-precision arithmetic, time discretization, and quantization noise, which are typically introduced 
-by Analogue-to-Digital (A/D) \todo{later ADC and DAC} and Digital-to-Analogue (D/A) conversion.  
+by Analogue-to-Digital (ADC) and Digital-to-Analogue (DAC) conversion.  
 Whilst the research on digital control is well developed~\cite{astrom1997computer}, 
@@
 %based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
-However, Pessoa does not have native inclusion of the ADC/DAC quantization error needed for
+However, Pessoa does not have native inclusion of the quantization error introduced by Digital-to-Analogue/Analogue-to-Digital conversion needed for
 synthesizing fixed-point digital controllers.
@@
 and with initial state $x_{0}=x(0)$. $A_d$ and $B_d$ denote the discretized matrices of $A$ and $B$, the plant dynamics. 
-Later, we will deal with the issue of variable quantization, as introduced by the ADC and DAC blocks.
+Later, we will deal with the issue of variable quantization, as introduced by the ADC/DAC conversion blocks.
 
@@
 
-During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathbb{R}\langle I_{adc},F_{adc} \rangle$ value.
+During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathbb{R}\langle I_{c},F_{c} \rangle$ value.
 this sampling uses a threshold which is defined by the less significant bit ($q_{adc}=2^{-F_{adc}}$) of the ADC and some non-linearities of the circuitry.
 The overall conversion is
-$$\mathcal{F}\langle I_{adc},F_{adc} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{adc}}{2}\ \ \ \ y(t)+\frac{q_{adc}}{2}\right]$$.
-If we denote the error in the conversion as $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{adc}}{2}\ \ \frac{q_{adc}}{2}]$.
+$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{adc}}{2}\right]$$.
+If we denote the error in the conversion as $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
 
 We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (\emph{ie} the quantizer includes any digital gain added in the code).
-The process of quantization in the DAC is similar except that it is going from $\mathbb{R}\langle I_{adc},F_{adc} \rangle \rightarrow \mathbb{R}\langle I_{dac},F_{dac} \rangle$.
-If these domains are the same ($I_{adc}=I_{dac},F_{adc}=F_{dac}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
-From the above equations we can now infer that $\nu_1 \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], \nu_2 \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{adc} \wedge q_2=q_{dac}$.
+The process of quantization in the DAC is similar except that it is going from $\mathbb{R}\langle I_{c},F_{c} \rangle \rightarrow \mathbb{R}\langle I_{dac},F_{dac} \rangle$.
+If these domains are the same ($I_{c}=I_{dac},F_{c}=F_{dac}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
+From the above equations we can now infer that $\nu_1 \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], \nu_2 \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{c} \wedge q_2=q_{dac}$.
 Note that these bounds hold irrespective of whether the noise is correlated, hence we may use them to over-approximate the effect of the noise on the state space progression over time.

### 2017-01-24 cav2017/cav2017.tex
removing A comment since we no longer cite this paper
rephrase sentence on division

@@
 however they have not been employed towards control synthesis. 
-\todo{why do we cite this paper \cite{cimatti2013parameter}?what is the relationship with our work? }
+%\todo{why do we cite this paper \cite{cimatti2013parameter}?what is the relationship with our work? }
 % when discretising the state-space for verification and
@@
 }
- \caption{Closed-loop digital control system \label{fig:digitalsystem}}
+ \caption{Closed-loop digital control system. 
+ \label{fig:digitalsystem}}
 \end{figure*}
@@
 $$\phi_{init} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} 
-\wedge \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}$$.  
-In practice, 
-this means that the control input saturates in view of physical constraints.
+\wedge \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$$
+
+This means that the control input saturates in view of physical constraints.
 
@@
 \item Multiplication: $\mathcal{F}\langle I,F \rangle(c_1) * \mathcal{F}\langle I,F \rangle(c_2) =  c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}*\mathcal{F}\langle I,F \rangle(c_2)| + |\delta_{T2}*\mathcal{F}\langle I,F \rangle(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
-\item Division is only needed for positive numbers in this implementation (where it is needed for checking stability). 
+\item In this implementation we only need to divide by positive numbers(where it is needed for checking stability). 
 \end{enumerate}
@@
 \begin{align*}
-x_{k+1} &=\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k})
+x_{k+1} &=\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
 \end{align*}
@@
 }}
-\caption{CEGIS with multi-staged verification}
+\caption{CEGIS with multi-staged verification.}
 \label{fig:CEGIS-precision-increment}
@@
 \vspace{0.1cm}
-\caption{Completeness threshold for multi-staged verification}
+\caption{Completeness threshold for multi-staged verification.}
 \end{figure*}
@@
 extracted from the literature~\cite{Franklin15}.
-%% Next, we demonstrate how our approach solves the synthesis problem for this
-%% example.
-
+%
 We start with a candidate solution with all coefficients zero, $K=[0
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-The CEGIS loop for this approach is illustrated in \ref{fig:CEGARIS}.
+The CEGIS loop for this approach is illustrated in Fig.~\ref{fig:CEGARIS}.
 
@@
 }
-\caption{CEGIS with abstraction refinement}
+\caption{CEGIS with abstraction refinement.}
 \label{fig:CEGARIS} 
@@
 \begin{itemize}
-\item $R_{1}$: $S(1)>0$;
+\item $R_{1}$: $P(1)>0$;
 \item $R_{2}$: $(-1)^{N}P(-1)>0$;
 \item $R_{3}$: $\vert{a_{0}}\vert <a_{N}$;
-\item $R_{4}$: $m_{11}>0\iff m_{31}\wedge m_{51}\wedge \dots \wedge m_{(2N-3)(1)}$.
+\item $R_{4}$: $m_{11}>0\iff (m_{31}>0)\wedge (m_{51}>0)\wedge \dots \wedge (m_{(2N-3)(1)>0)}$.
 \end{itemize}

### 2017-01-24 cav2017/cav2017.tex
Minor changes
updated label of all figures
added comment related to CPU time and timeout

--- 2017-01-24 cav2017/cav2017.tex
@@
 \item Multiplication: $\mathcal{F}\langle I,F \rangle(c_1) * \mathcal{F}\langle I,F \rangle(c_2) =  c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}*\mathcal{F}\langle I,F \rangle(c_2)| + |\delta_{T2}*\mathcal{F}\langle I,F \rangle(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
-\item In this implementation we only need to divide by positive numbers(where it is needed for checking stability). 
+\item Division is only needed for positive numbers in this implementation (where it is needed for checking stability). 
 \end{enumerate}
@@
 We have conducted the experimental evaluation on a 12-core 2.40 GHz
-Intel Xeon E5-2440 with 96 GB of RAM and Linux OS. All times given are wall 
-clock time in seconds as measured by the UNIX date command.
-
-\textcolor{red}{we have to describe the timeout...}
+Intel Xeon E5-2440 with 96 GB of RAM and Linux OS.
+
+\textcolor{red}{Pascal, Can you please describe our we measure time?
+All times given are wall clock time in seconds as measured by the UNIX date command.}
+
+\textcolor{red}{Pascal, can you please describe the timeout?}
 

### 2017-01-24 cav2017/cav2017.tex
Contributions

--- 2017-01-24 cav2017/cav2017.tex
@@
 
-\textit{Contributions}. We use a combination of a synthesis engine with a control
-verification tool that addresses the challenges presented in the
-form of FWL effects, safety, and stability measures over digital controllers for LTI models.  
-We take the synthesis engine from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
-the first approach we present, performs bounded model checking of control properties,
-based on~\cite{Monteiro16}, but enhanced to include evaluation of quantization effects and 
-safety properties over the state space. 
-In an alternative approach, we use a verification engine based 
-on abstract acceleration~\cite{cattaruzza2015unbounded}, which avoids the explicit unwinding 
-of the transition system necessary for the first approach. We introduce a CEGAR loop to this abstraction
-in order to make it less conservative, and develop a CEGIS feedback based on abstraction refinement to
-increase the speed of the synthesis algorithm.
-In both approaches, we project the maximum effect of the noise over an unbounded time and uses it as a buffer region 
-for the safety specification.
+\textit{Contributions}. 
+\begin{enumerate}
+\item In this paper we extend the problem of digital control synthesis from a transfer function representation into a state space representation.
+This entails the verification of safety properties in addition to the already existing stability conditions which is a much harder problem.
+\item To achieve this, we develop two approaches and compare them, the first relying on a non-deterministic simulation of the system and a completeness proof, whilst the second leverages on the concepts of abstraction and acceleration to increase speed whilst retaining soundness.
+\item We develop a solution generalization algorithm for the first approach and an abstraction refinement for the second, both of which improve the performance of the CEGIS loop. 
+\item We develop a model for different sources quantization and their effect on the state space progression, for which we find safe bounds that ensure the safety of our controllers in a hybrid continuous-digital domain.
+\end{enumerate}
+
+%We use a combination of a synthesis engine with a control
+%verification tool that addresses the challenges presented in the
+%form of FWL effects, safety, and stability measures over digital controllers for LTI models.  
+%We take the synthesis engine from~\cite{DBLP:conf/lpar/DavidKL15}. The verification engine, for
+%the first approach we present, performs bounded model checking of control properties,
+%based on~\cite{Monteiro16}, but enhanced to include evaluation of quantization effects and 
+%safety properties over the state space. 
+%In an alternative approach, we use a verification engine based 
+%on abstract acceleration~\cite{cattaruzza2015unbounded}, which avoids the explicit unwinding 
+%of the transition system necessary for the first approach. We introduce a CEGAR loop to this abstraction
+%in order to make it less conservative, and develop a CEGIS feedback based on abstraction refinement to
+%increase the speed of the synthesis algorithm.
+%In both approaches, we project the maximum effect of the noise over an unbounded time and uses it as a buffer region 
+%for the safety specification.
 
@@
 We note that the effect on stability due to the fixed-word-length error is that the system may, instead of converging to the desired equilibrium point, converge to a point that is bounded away from the desired equilibrium point (see Appendix for details).
-In this paper, we synthesize a stable controller only as a precursor to synthesizing a \emph{safe} controllers and it is therefore sufficient that the system converges to a point within the safe states.
-Hence, it is sufficient to disregard the errors when we synthesize a stable controller, and then verify safety.
+In this paper, we require stability ony as a precusros to safety and it is therefore sufficient that the system converges to a point within the safe states.
+Hence, it is sufficient to disregard these errors when we synthesize a stable controller, and then verify safety.
 
@@
 %\label{eq:acc_observer_LTI_cf}
-x=&A_t^kx_0
+x=&(A_d-B_dK)^kx_0
 %+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i
-+\sum_{i=0}^{k-1} A_t^i B_{n}(\nu_1+\nu_2+\nu_3) 
++\sum_{i=0}^{k-1} (A_d-B_dK)^i B_{n}(\nu_1+\nu_2+\nu_3) : B_n= [1\ 1 \cdots \ 1 ]^T
 \end{align}
-\todo{explain $B_n$ and $A_t$}
 As this still requires us to verify the system for every $k$ up to infinity, 
@@
 \hat{X}^\#
-=&\mathcal{A}_t X_0 + \mathcal{B}_{n} N\\
+=&\mathcal{A} X_0 + \mathcal{B}_{n} N\\
 X_0 =&\left \{x : x \models \phi_{init} \right\}\nonumber
@@
 %
-where $\mathcal{A}_t=\bigcup_{k=1}^\infty A_t^k, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^kA_t^iB_{n}$ are abstract matrices for the closed-loop system,
-% in \eqref{eq:observer_LTI_cf} 
-%and $r$ is a non-deterministic parametric input (\emph{ie} $\forall k>0, r_{k+1} =r_k$) 
+where $\mathcal{A}=\bigcup_{k=1}^\infty (A_d-B_dK)t^k, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k(A_d-B_dK)^iB_{n}$ are abstract matrices for the closed-loop system,
 whereas the set N is non-deterministically chosen.
 
-%\begin{enumerate}
-%% \item Calculate the abstract matrices $\mathcal{A}_t, \mathcal{B}_{t},\mathcal{B}_{n}$ for the candidate closed loop solution.
 We next evaluate $\hat{X}^\# \models \phi_{safety}$. If the verification holds we have a solution, and exit the loop. Otherwise, 
@@
 \item Find the constraints that invalidate the property
-  %% These are the rows of $\mat{E} \in \Psi$ that intersect/segment $\hat{X}^\#$. Transforming these rows into the eigenspace of $\mat{A}_t$, and applying backward acceleration to
  as a set of counterexamples for the eigenvalues, which we define as $\phi_\Lambda$. This is a constraint in the spectrum i.e., transfer function) of the closed loop dynamics. 
@@
      \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm]AA.center) {Abstraction \\ Verifier};
-     %\node[draw,rectangle,align=center] (AAI) at ([xshift=1.5cm]AA.center) {\sc AA\\Solver};
-
-     %\node[draw=none] (AB) at ([xshift=.4cm,yshift=1.5cm]AAI.center)  {\sc $\mat{A},\mat{B}$\\$\phi$};     
-     %\node[draw=none] (MA) at ([yshift=.2cm]AA.center)  {$\mathcal{A}_t$};     
-     %\node[draw=none] (MB) at ([yshift=-.3cm]AA.center)  {$\mathcal{B}_{t},\mathcal{B}_{n}$}; 
-     %\node[draw=none] (XT) at ([xshift=0.3cm,yshift=0.5cm]AAC.center)  {\sl $\hat{X}_r^\#$};  
-     %\node[draw=none] (XT2) at ([xshift=0.3cm,yshift=0.8cm]AAV.center)  {\sl $\hat{X}^\#$};  
-     %\draw [->,line width=1pt] ([xshift=-0.1cm,yshift=2cm]AA.center) arc[x radius=0.7cm, y radius =.7cm, start angle=-250, end angle=60];
     }\\

### 2017-01-24 cav2017/cav2017.tex
fixed point notation

@@
 
-Let $\mathcal{F}\langle I,F \rangle(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part.
+Let $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part.
 The smallest number that can be represented in this domain is $c_m=2^{-F}$.
@@
 \item {\bf Truncation:}
-Let $x$ be a real number, and $\mathcal{F}\langle I,F \rangle(x)$ be the same number represented in a fixed point domain as above.
-$\mathcal{F}\langle I,F \rangle(x) = x-\delta_T : \delta_T=x\ \%_{c_m}\ \tilde x$, where $\%_{c_m}$ is the modulus operation performed on the last bit.
+Let $x$ be a real number, and $\mathcal{F}_{\langle I,F \rangle}(x)$ be the same number represented in a fixed point domain as above.
+$\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T : \delta_T=x\ \%_{c_m}\ \tilde x$, where $\%_{c_m}$ is the modulus operation performed on the last bit.
 
@@
 \item Addition/Subtraction: these operations only propagate errors coming from truncation of the operands. 
-$\mathcal{F}\langle I,F \rangle(c_1) \pm \mathcal{F}\langle I,F \rangle(c_2) = c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
-
-\item Multiplication: $\mathcal{F}\langle I,F \rangle(c_1) * \mathcal{F}\langle I,F \rangle(c_2) =  c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}*\mathcal{F}\langle I,F \rangle(c_2)| + |\delta_{T2}*\mathcal{F}\langle I,F \rangle(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
+$\mathcal{F}_{\langle I,F \rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
+
+\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) * \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}*\mathcal{F}_{\langle I,F \rangle}(c_2)| + |\delta_{T2}*\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
 \item In this implementation we only need to divide by positive numbers(where it is needed for checking stability). 
@@
 \item {\bf Overflow:}
-The maximum size of a real number $x$ that can be represented in a fixed point domain as $\mathcal{F}\langle I,F \rangle(x)$ is $\pm (2^{I-1}+1-2^{-F})$.
+The maximum size of a real number $x$ that can be represented in a fixed point domain as $\mathcal{F}_{\langle I,F \rangle}(x)$ is $\pm (2^{I-1}+1-2^{-F})$.
 Numbers outside this range cannot be represented by the domain.
@@
 
-We use $\mathcal{F}\langle I_c,F_c \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}\langle I_p,F_p \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model.
-Thus all mathematical operations occurring in the digital controller occur in the domain $\mathcal{F}\langle I_c,F_c \rangle$, and all other calculations are carried out in the domain $\mathcal{F}\langle I_p,F_p \rangle$.
-
-We will use $\mathcal{F}\langle I_c,F_c \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}\langle I_p,F_p \rangle(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model ($I_p \geq I_c \wedge F_p \geq F_c$).
-Thus any mathematical operations occurring in the digital controller will occur in the range of $\mathcal{F}\langle I_c,F_c \rangle$, and all other calculations will be carried out in the range of $\mathcal{F}\langle I_p,F_p \rangle$.
+We use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model.
+Thus all mathematical operations occurring in the digital controller occur in the domain $\mathcal{F}_{\langle I_c,F_c \rangle}$, and all other calculations are carried out in the domain $\mathcal{F}_{\langle I_p,F_p \rangle}$.
+
+We will use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model ($I_p \geq I_c \wedge F_p \geq F_c$).
+Thus any mathematical operations occurring in the digital controller will occur in the range of $\mathcal{F}_{\langle I_c,F_c \rangle}$, and all other calculations will be carried out in the range of $\mathcal{F}_{\langle I_p,F_p \rangle}$.
 

### 2017-01-24 cav2017/cav2017.tex
minor fix

@@
 
-We describe and evaluate two approaches for synthesizing digital controllers 
+We describe and evaluate two approaches for synthesising digital controllers 
 for state-space physical plants. Both approaches consider a counterexample 
@@
 we devise a digital controller that stabilizes the system whilst remaining safe given a 
-pre-selected time horizon; then, we verify its potential safety by unfolding the dynamics of the system and checking for 
+pre-selected time horizon; then, we verify its 
+potential safety by unfolding the dynamics of the system and checking for 
 a completeness threshold. In the second approach, we substitute the second step by employing abstract acceleration
@@
 We provide experimental results 
-showing that both approaches are able to efficiently synthesize stable and safe controllers 
+showing that both approaches are able to efficiently synthesise stable and safe controllers 
 for a set of intricate physical plant models taken from the digital 
@@
 the approach described in the Appendix~\ref{sec:appendix}. 
-All experiments were performed considering $x_{i}^{-}=-1$ and 
-$x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.
+All experiments were performed considering $\underline{x_{i}}=-1$ and 
+$\overline{x_{i}}=1$ and the inputs $u_{k}=0, \forall k>0$.
 We have conducted the experimental evaluation on a 12-core 2.40 GHz
@@
 \begin{align*}
-\sum_{i=0}^{\infty}T^i  &= (I - T)^-1
+\sum_{i=0}^{\infty}T^i  &= (I - T)^{-1}
 \end{align*}

### 2017-01-24 cav2017/cav2017.tex
text2

@@
 transition relation~\cite{cattaruzza2015unbounded}. 
-\todo{We need to mention the CEGIS architecture here. We need to emphasise the derivation of errors for soundness. Can we claim completeness already?}
+\todo{We need to emphasise the derivation of errors for soundness. Can we claim completeness already?}
 We provide experimental results 
@@
 
-\textit{Contributions}. 
+\subsection*{Contributions}
+
 \begin{enumerate}
@@
 As argued later in this work, we will target more complex objectives, such as quantitative safety requirements that are not typical in the digital control literature. 
+Further, we will encompass the digital nature of the controller, which manipulates quantities with finite precision.
 
@@
 In this paper, we express the stability specification $\phi_{stability}$ 
-in terms of a check known as Jury's criterion~\cite{fadali}. 
-This condition boils down to an easy algebraic formula to select the entries 
-of matrix $K$, so that the closed-loop dynamics are shaped as desired. 
-A detailed description of this specification can be found in the 
-Appendix~\ref{sec:appendix-stability}.
+in terms of a check known as Jury's criterion~\cite{fadali}:  
+this is an easy algebraic formula to select the entries of matrix $K$, 
+so that the closed-loop dynamics are shaped as desired. 
+A detailed description of this specification can be found in Appendix~\ref{sec:appendix-stability}.
 
@@
 it is practically relevant to consider constraints on the input signal $u_{k}$
-and initial states $x_0$, 
+and bounds on the initial states $x_0$, 
 which we assume have given bounds. %%  $\overline{u}$, $\underline{u}$
@@
 \wedge \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$$  
-
-This means that the control input saturates in view of physical constraints.
+In the first case, 
+this means that the control input saturates in view of physical constraints.
 

### 2017-01-24 cav2017/cav2017.tex
text2

@@
 which performs operations in the domain of fixed-point numbers. 
-In this section we formally outline the errors introduced by fixed-point representation of numbers.
-
+In this section we formally outline the errors introduced by the fixed-point representation of numbers. 
+% 
 Let $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part.
@@
 \item {\bf Truncation:}
-Let $x$ be a real number, and $\mathcal{F}_{\langle I,F \rangle}(x)$ be the same number represented in a fixed point domain as above.
-$\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T : \delta_T=x\ \%_{c_m}\ \tilde x$, where $\%_{c_m}$ is the modulus operation performed on the last bit.
+Let $x$ be a real number, and $\mathcal{F}_{\langle I,F \rangle}(x)$ be the same number represented in a fixed-point domain as above. 
+Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T : \delta_T=x\ \%_{c_m}\ \tilde x$, where $\%_{c_m}$ is the modulus operation performed on the last bit.
 
@@
 \begin{enumerate}
-\item Addition/Subtraction: these operations only propagate errors coming from truncation of the operands. 
+\item Addition/Subtraction: these operations only propagate errors coming from truncation of the operands, namely 
 $\mathcal{F}_{\langle I,F \rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
@@
 \item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) * \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}*\mathcal{F}_{\langle I,F \rangle}(c_2)| + |\delta_{T2}*\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
-\item In this implementation we only need to divide by positive numbers(where it is needed for checking stability). 
+\item In this implementation we only need to divide by positive numbers(where it is needed for checking stability) \todo{so: what does that imply? pls clarify explicitly.}. 
 \end{enumerate}
@@
 
-We use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model.
-Thus all mathematical operations occurring in the digital controller occur in the domain $\mathcal{F}_{\langle I_c,F_c \rangle}$, and all other calculations are carried out in the domain $\mathcal{F}_{\langle I_p,F_p \rangle}$.
-
 We will use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model ($I_p \geq I_c \wedge F_p \geq F_c$).
+\todo{Should we include a discussion on the fact that the plant is physical?
+So for example, a reviewer may ask what is the meaning of the model with time derivative, with variables over a Euclidean space.
+}
 Thus any mathematical operations occurring in the digital controller will occur in the range of $\mathcal{F}_{\langle I_c,F_c \rangle}$, and all other calculations will be carried out in the range of $\mathcal{F}_{\langle I_p,F_p \rangle}$.

### 2017-01-24 cav2017/cav2017.tex
text2

@@
 \subsubsection{Effect on safety specification and stability}
-%Thus we can consider the effect of these errors on our safety and stability verification.
-
-First consider the effect of the quantization errors on safety; the state values must be computed considering the error introduced by the digital controller caused by performing the vector multiplication $Kx$ at low digital precision.
-
-The inputs are computed using the following equations. 
+
+Let us first consider the effect of the quantization errors on safety. 
+Within the digital controller block, 
+state values are manipulated at low digital precision, 
+alongside the vector multiplication $Kx$.   
+%computed considering the error introduced by the digital controller caused by performing the vector multiplication $Kx$ at low digital precision.
+As such, the inputs are computed using the following equation: 
 \begin{align*}
@@
 
-This will induce two types of the error detailed above, first the truncation errors due to representing $x_k$ as $\mathcal{F}{\langle I_c,F_c \rangle}(x_{k})$, and second the rounding error introduced by the multiplication.
+This induces two types of the errors detailed above:  
+first, the truncation error due to representing $x_k$ as $\mathcal{F}{\langle I_c,F_c \rangle}(x_{k})$; 
+and second, the rounding error introduced by the multiplication operation. 
 We represent these errors as non-deterministic noise.
 
-A further error is caused by the representation of the plant dynamics.
+An additional error is caused by the representation of the plant dynamics, namely 
 \begin{align*}
@@
 
-We address these errors by use of a final verification check that uses interval arithmetic~\cite{moore1966interval}.
-
-We note that the effect on stability due to the fixed-word-length error is that the system may, instead of converging to the desired equilibrium point, converge to a point that is bounded away from the desired equilibrium point (see Appendix for details).
-In this paper, we require stability ony as a precusros to safety and it is therefore sufficient that the system converges to a point within the safe states.
-Hence, it is sufficient to disregard these errors when we synthesize a stable controller, and then verify safety.
+\todo{You mean the second one, or both? Please clarify.} We address these errors by use of a final verification check that uses interval arithmetic~\cite{moore1966interval}.
+
+We note that the effect on stability due to the fixed-word-length error is that the system may, 
+instead of converging to the desired equilibrium point, 
+converge to a neighbourhood around the desired equilibrium point (see Appendix for details). 
+However, since In this paper we require stability only as a precursor to safety, 
+it is sufficient to check the (perturbed, noisy) model converges to a point within the safe states. 
+In the following, we shall disregard these errors when we synthesise a stable controller, 
+and then verify its safety accounting for the finite-precision errors.
 

### 2017-01-24 benchmark-runner/fixedpointcheck.m
fixed point arithmetic matlab check

@@ -1,0 +1,51 @@
+global FiSettings ;
+global FiSettingsP ;
+
+FiSettings = fimath('ProductMode',...
+                   'SpecifyPrecision',... 
+                   'ProductWordLength',16,... 
+                   'ProductFractionLength',8, ...
+                   'RoundingMethod','Floor',...
+                   'SumMode', 'SpecifyPrecision',...
+                   'SumWordLength',16, ...
+                   'SumFractionLength', 8, ...
+                   'OverflowAction', 'Wrap');
+               
+ FiSettingsP = fimath('ProductMode',...
+                   'SpecifyPrecision',... 
+                   'ProductWordLength',64,... 
+                   'ProductFractionLength',32, ...
+                   'RoundingMethod','Floor',...
+                   'SumMode', 'SpecifyPrecision',...
+                   'SumWordLength',64, ...
+                   'SumFractionLength', 32, ...
+                   'OverflowAction', 'Wrap');              
+               
+               
+fxp=@(v) fi(v,1,16,8,FiSettings);
+fxpP = @(v) fi(v,1,64,32,FiSettingsP);
+
+K = [fxp(46.25), fxp(-16)];
+%K = [fxp(17.4384765625), fxp(-0.0537109375)];
+
+A = [fxpP(2.001),fxpP(-1);fxpP(1),fxpP(0)] ;
+B = [fxpP(0.0625);fxpP(0)] ;
+states = [fxpP(0.5); fxpP(0.5)];
+loops = 100;
+for i=1:loops
+
+    input = -K * fxp(states);
+    tmp_input = double(input);
+    if(input>1000 || input< -1000)
+        msg = 'input too big'
+        return
+    end    
+    states = A * (states) + B * fxpP(input);
+    for idx = 1: numel(states)
+        if(states(idx) > 1 || states(idx) < -1)
+            msg = 'unsafe'
+            i
+            return
+        end  
+    end
+end 

### 2017-01-24 cav2017/cav2017.tex
line breaks

@@
 \usepackage{epstopdf}
+\usepackage{cite}
 
@@
 \begin{abstract}
-This work presents a sound and automated approach to synthesize 
-safe digital feedback controllers for physical plants represented 
-as linear, time invariant models. Models are described as dynamical 
-equations with inputs, evolving over a continuous state space and accounting 
-for errors due to the digitalization of signals that are manipulated by the 
-controller block. 
-The approach works in two stages, leveraging the use of counter-example guided
-inductive synthesis (CEGIS) and reachability analysis. The former synthesises a static 
-feedback controller that stabilizes the system under some restrictions given by the safety of
-the reach space. The latter verifies its potential safety by means of either of the following 
-approaches: forward reachability analysis via unfolding of the dynamics or invariant set 
-generation via abstract acceleration; if the 
-verification step fails, we loop back to seek an 
-alternative controller benefiting from the obtained counterexamples 
-to safety using solution generalization and abstraction refinement.
-We are able to efficiently synthesize stable and safe controllers
-considering a set of intricate physical plant models taken from the digital
-control literature.
+%
+This work presents a sound and automated approach to synthesize safe digital
+feedback controllers for physical plants represented as linear, time
+invariant models.  Models are described as dynamical equations with inputs,
+evolving over a continuous state space and accounting for errors due to the
+digitalization of signals that are manipulated by the controller block.  The
+approach works in two stages, leveraging the use of counter-example guided
+inductive synthesis (CEGIS) and reachability analysis.  The former
+synthesises a static feedback controller that stabilizes the system under
+some restrictions given by the safety of the reach space.  The latter
+verifies its potential safety by means of either of the following
+approaches: forward reachability analysis via unfolding of the dynamics or
+invariant set generation via abstract acceleration; if the verification step
+fails, we loop back to seek an alternative controller benefiting from the
+obtained counterexamples to safety using solution generalization and
+abstraction refinement.  We are able to efficiently synthesize stable and
+safe controllers considering a set of intricate physical plant models taken
+from the digital control literature.
+%
 \keywords{
@@
 for state-space physical plants.  Both approaches consider a counterexample
-guided inductive synthesis (CEGIS) loop. In the first approach, 
-we devise a digital controller that stabilizes the system whilst remaining safe given a 
-pre-selected time horizon; then, we verify its 
-potential safety by unfolding the dynamics of the system and checking for 
-a completeness threshold. In the second approach, we substitute the second step by employing abstract acceleration
-to unfold the dynamics forward, instead of symbolically unwinding the 
-transition relation~\cite{cattaruzza2015unbounded}. 
+guided inductive synthesis (CEGIS) loop.  In the first approach, we devise a
+digital controller that stabilizes the system whilst remaining safe given a
+pre-selected time horizon; then, we verify its potential safety by unfolding
+the dynamics of the system and checking for a completeness threshold.  In
+the second approach, we substitute the second step by employing abstract
+acceleration to unfold the dynamics forward, instead of symbolically
+unwinding the transition relation~\cite{cattaruzza2015unbounded}.
 \todo{We need to emphasise the derivation of errors for soundness. Can we claim completeness already?}
@@
 \begin{enumerate}
+%
 \item In this paper we extend the problem of digital control synthesis from a transfer function representation into a state space representation.
 This entails the verification of safety properties in addition to the already existing stability conditions which is a much harder problem.
+%
 \item To achieve this, we develop two approaches and compare them, the first relying on a non-deterministic simulation of the system and a completeness proof, whilst the second leverages on the concepts of abstraction and acceleration to increase speed whilst retaining soundness.
+%
 \item We develop a solution generalization algorithm for the first approach and an abstraction refinement for the second, both of which improve the performance of the CEGIS loop. 
+%
 \item We develop a model for different sources quantization and their effect on the state space progression, for which we find safe bounds that ensure the safety of our controllers in a hybrid continuous-digital domain.
+%
 \end{enumerate}
@@
 
-Program synthesis is the problem of computing correct-by-design programs from high-level specifications; 
-algorithms for this problem have made substantial progress in recent years.  
-One such approach~\cite{itzhaky2010simple} inductively synthesizes invariants to
+Program synthesis is the problem of computing correct-by-design programs
+from high-level specifications; algorithms for this problem have made
+substantial progress in recent years.  One such
+approach~\cite{itzhaky2010simple} inductively synthesizes invariants to
 generate the desired programs.
@@
 Program synthesizers are an ideal fit for synthesis of %parametric
-digital controllers, since the semantics of programs capture effects such as FWL
-precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
-for the synthesis of switching controllers for stabilizing continuous-time
-plants with polynomial dynamics.  The work extends to affine systems, 
-finding a major challenge in the hardness of solving linear arithmetic with the state-of-the-art SMT solvers.  
-Since this approach uses switching models instead of linear dynamics for the digital controller, 
-it entirely circumvents the FWL problem, but potentially incurs state-space explosion issues.  
-Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
-use a CEGIS-based approach for synthesizing continuous-time switching
-controllers that guarantee \emph{reach-while-stay} properties of closed-loop systems, 
-i.e., properties that specify a set of goal states and safe states (constrained reachability).
-This solution is based on synthesizing control Lyapunov 
-functions for switched systems, that yield switching controllers with
-a guaranteed minimum dwell time in each mode. However, both approaches 
-are not suitable for the kind of control we seek to synthesize.
-
-The work in \cite{DBLP:journals/corr/AbateBCCDKK16} investigates the synthesis of 
-stabilizing controllers for continuous plants described as transfer functions, 
-by exploiting bit-accurate verification of software-implemented 
-digital controllers~\cite{Bessa16}.  While this work also makes use of a CEGIS-based technique, 
-the approach is restricted to synthesizing digital controllers for stable 
-closed-loop systems described via transfer function models.  
-In contrast, in the current paper we consider a state-space representation of the physical system, 
-which is known to be more general \cite{Astrom08} and allows to synthesize controllers that
-make the closed-loop system \emph{safe}.  Moreover, 
-this work  integrates an abstraction/refinement step inside the main CEGIS loop.
-
-The tool Pessoa~\cite{mazo2010pessoa} is a MatLab toolbox that synthesizes correct-by-design
-embedded control software. It is based on the description of a physical system
-as an equivalent finite-state machine and on the computation of reachability properties over the finite-state 
-machine. 
-Based on this safety specification over state values, 
-Pessoa can synthesize embedded controller software for a range of properties.  
+digital controllers, since the semantics of programs capture effects such as
+FWL precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use
+CEGIS for the synthesis of switching controllers for stabilizing
+continuous-time plants with polynomial dynamics.  The work extends to affine
+systems, finding a major challenge in the hardness of solving linear
+arithmetic with the state-of-the-art SMT solvers.  Since this approach uses
+switching models instead of linear dynamics for the digital controller, it
+entirely circumvents the FWL problem, but potentially incurs state-space
+explosion issues.  Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the
+same authors use a CEGIS-based approach for synthesizing continuous-time
+switching controllers that guarantee \emph{reach-while-stay} properties of
+closed-loop systems, i.e., properties that specify a set of goal states and
+safe states (constrained reachability).  This solution is based on
+synthesizing control Lyapunov functions for switched systems, that yield
+switching controllers with a guaranteed minimum dwell time in each mode. 
+However, both approaches are not suitable for the kind of control we seek to
+synthesize.
+
+The work in \cite{DBLP:journals/corr/AbateBCCDKK16} investigates the
+synthesis of stabilizing controllers for continuous plants described as
+transfer functions, by exploiting bit-accurate verification of
+software-implemented digital controllers~\cite{Bessa16}.  While this work
+also makes use of a CEGIS-based technique, the approach is restricted to
+synthesizing digital controllers for stable closed-loop systems described
+via transfer function models.  In contrast, in the current paper we consider
+a state-space representation of the physical system, which is known to be
+more general \cite{Astrom08} and allows to synthesize controllers that make
+the closed-loop system \emph{safe}.  Moreover, this work integrates an
+abstraction/refinement step inside the main CEGIS loop.
+
+The tool Pessoa~\cite{mazo2010pessoa} is a MatLab toolbox that synthesizes
+correct-by-design embedded control software.  It is based on the description
+of a physical system as an equivalent finite-state machine and on the
+computation of reachability properties over the finite-state machine.  Based
+on this safety specification over state values, Pessoa can synthesize
+embedded controller software for a range of properties.
 %based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
-However, Pessoa does not have native inclusion of the quantization error introduced by Digital-to-Analogue/Analogue-to-Digital conversion needed for
+However, Pessoa does not have native inclusion of the quantization error
+introduced by Digital-to-Analogue/Analogue-to-Digital conversion needed for
 synthesizing fixed-point digital controllers.
@@
 
-The classical approach to control synthesis has often disregarded quantization, 
-thus resulting in general to unsound digital controllers. 
-Modern techniques focus on different elements of discretization effects, including delayed
-response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics, 
-with the goal either to verify (e.g.,~ \cite{daes20161}) or to optimize
-(e.g.,~ \cite{oudjida2014design}) given implementations.
+The classical approach to control synthesis has often disregarded
+quantization, thus resulting in general to unsound digital controllers. 
+Modern techniques focus on different elements of discretization effects,
+including delayed response~\cite{Duggirala2015}, and Finite Word Length
+(FWL) semantics, with the goal either to verify (e.g.,~ \cite{daes20161}) or
+to optimize (e.g.,~ \cite{oudjida2014design}) given implementations.
 
@@
 directly model the digital controller so that the selected parameters are
-stable by design.  The analyses
-in~\cite{DBLP:conf/hybrid/RouxJG15,DBLP:conf/hybrid/WangGRJF16} rely on an
-invariant computation on the discrete system dynamics using Semi-Definite
-Programming (SDP).  While the former uses BIBO properties to determine
-stability, the latter uses Lyapunov-based quadratic invariants.  In both
-cases, the SDP solver uses floating-point arithmetic and soundness is
-checked by bounding the error.  An alternative approach is taken
-by~\cite{park2016scalable}, where the verification of given control code is
-performed against a known model by extracting an LTI model of the code
-through symbolic execution.  In order to account for rounding errors, an
-upper bound is introduced in the verification phase.
-The work in \cite{picasso2003stabilization,picasso2002construction} introduces
-attractive invariant sets as a mechanism to bound the quantization error effect
-on stabilisation as an invariant set that always converges toward the controllable
-set. In a similar fashion, \cite{liberzon2003hybrid} evaluates the dynamics of the
-quantization error and bounds its trajectory to a known region over a finite
-period of time. This technique works for both linear and non-linear systems.
+stable by design.  The analyses in~\cite{DBLP:conf/hybrid/RouxJG15,
+DBLP:conf/hybrid/WangGRJF16} rely on an invariant computation on the
+discrete system dynamics using Semi-Definite Programming (SDP).  While the
+former uses BIBO properties to determine stability, the latter uses
+Lyapunov-based quadratic invariants.  In both cases, the SDP solver uses
+floating-point arithmetic and soundness is checked by bounding the error. 
+An alternative approach is taken by~\cite{park2016scalable}, where the
+verification of given control code is performed against a known model by
+extracting an LTI model of the code through symbolic execution.  In order to
+account for rounding errors, an upper bound is introduced in the
+verification phase.  The work in \cite{picasso2003stabilization,
+picasso2002construction} introduces attractive invariant sets as a mechanism
+to bound the quantization error effect on stabilisation as an invariant set
+that always converges toward the controllable set.  In a similar fashion,
+\cite{liberzon2003hybrid} evaluates the dynamics of the quantization error
+and bounds its trajectory to a known region over a finite period of time. 
+This technique works for both linear and non-linear systems.
 

### 2017-01-24 cav2017/cav2017.tex
text2

--- 2017-01-24 cav2017/cav2017.tex
@@
 
-Here, we outline the general architecture of the program synthesizer used in both approaches. 
-We then give the details of both methods of solution generalization that we compare; 
-the first checking safety by unwinding the transition relation to a completeness threshold; 
-and the second employing abstract acceleration.
+We outline the general architecture of the program synthesizer used in both approaches \todo{which approaches - pls recall or clarify}. 
+We then give the details of both methods of solution generalization \todo{define ``solution generalisation''} that we compare.  
+The first checks safety by unwinding the transition relation to a completeness threshold, 
+whereas the second employs abstract acceleration.
 
@@
 %$\exists P .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ 
-$\exists P .  \forall x.  \sigma(x, P)$ 
-where $P$ ranges over functions, $x$ 
- ranges over ground terms and
-$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
-some finite domain $\mathcal{D}$.
+$\exists P .  \forall x.  \sigma(x, P)$, 
+where $P$ ranges over functions, 
+$x$ ranges over ground terms, 
+and $\sigma$ is a quantifier-free formula.  
+We interpret the ground terms over some finite domain $\mathcal{D}$.
 %
@@
 At this point, we recap the the synthesis problem that we solve in this work:
-find a digital controller $K$ (see Eq.~\ref{eq:controlaction})
-that makes the closed-loop system safe for 
+we seek a digital feedback controller $K$ (see Eq.~\ref{eq:controlaction})
+that makes the closed-loop plant model safe for 
 initial state $x_0$, reference signal $r_k$ and input $u_k$
 as defined in Sec.~\ref{ssec:safety}. 
-We consider non-deterministic initial states within a specified range
-and the reference signal to be set to zero.  
-When mapping back to the notation used for describing the general architecture 
-of the program synthesizer, the controller $K$ denotes $P$ and 
-$(x_0, u_k)$ represents $x$. 
-While the controller's precision $\langle I_c,F_c\rangle$ is given, 
-we can vary the plant's precision $\langle I_p,F_p\rangle$ such that 
-$I_p \geq I_c \wedge F_p \geq F_c$.
+We consider non-deterministic initial states within a specified range, 
+the reference signal to be set to zero, 
+saturations on the inputs, 
+and account for digitalisation and quantisation errors introduced by the controller.
+
+When mapping back to the notation used for describing the general architecture of the program synthesizer, 
+the controller $K$ denotes $P$ and $(x_0, u_k)$ represents $x$. 
+While the controller precision \todo{update notations} $\langle I_c,F_c\rangle$ is given and fixed, 
+we can vary the plant precision $\langle I_p,F_p\rangle$ such that $I_p \geq I_c \wedge F_p \geq F_c$.
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+\todo{All good - only the word ``generalisation'' won't be understood by a control person (we might have reviewers from this area?).
+Anticipate the explanation  given below to the introduction section.}
 
@@
 lattice of progressively more expressive languages.  This enables us
-to start by attempting to synthesize a program at the lowest point on
-this lattice and increase the parameters of the language until we
-reach a point at which the synthesis succeeds. Whenever we manage to
+to start by synthesizing a program at the lowest point on
+this lattice, and to increase the parameters of the language until we
+reach a point at which the synthesis succeeds \todo{if at all - completeness?}. Whenever we manage to
 synthesize a solution at some lower point on the lattice, we
@@
 solution (i.e., a solution in the original search space).
-This parametrization greatly increases the efficiency of our system since
-languages low down the lattice are easy to decide safety for
-(i.e., the validation oracle finds an answer fast). If a program can be
-synthesized in a low-complexity language, the whole procedure finishes
+This parametrization greatly increases the efficiency of our system, since
+low-level languages (over the lattice) are easier to decide safety for 
+(i.e., the validation oracle finds an answer faster). In other words, 
+if a program can be synthesized in a low-complexity language, the whole procedure finishes
 much faster than if synthesis had been attempted in a high-complexity
@@
 and the sampling rate. Essentially, it finds a controller for an individual initial state
-and input with a bounded time horizon and generalizes to all states,
+and input with a bounded time horizon and generalizes to all reachable states,
 inputs, and time horizons. The safety check is performed in this approach 
 via unfolding of the transition system corresponding to the synthesized controller.
+\todo{mention issue of completeness threshold here?}
 
@@
 \item[2.] The second approach (described in Sec~\ref{sec:CEGIS-abstraction-refinement})
-  finds a controller for a continuous initial set of states and input
-  set, over an abstraction of the continuous dynamics that conforms to
-  witness proofs at specific times; it further generalizes the
+  finds a controller for a continuous initial set of states and set of inputs, 
+  over an abstraction of the continuous dynamics that conforms to
+  witness proofs at specific times. It further generalizes the
   solution over all times by refining the number of witnesses.  
@@
   \cite{cattaruzza2015unbounded} to compute the controller's set of states. 
-  %\todo{clarify use of abstract acceleration. add references.}
+  \todo{clarify: what is the ``set of states'' of the controller? }
 \end{itemize}

### 2017-01-24 cav2017/cav2017.tex
cut abstract

--- 2017-01-24 cav2017/cav2017.tex
@@
 evolving over a continuous state space and accounting for errors due to the
-digitalization of signals that are manipulated by the controller block.  The
-approach works in two stages, leveraging the use of counter-example guided
-inductive synthesis (CEGIS) and reachability analysis.  The former
-synthesises a static feedback controller that stabilizes the system under
-some restrictions given by the safety of the reach space.  The latter
-verifies its potential safety by means of either of the following
-approaches: forward reachability analysis via unfolding of the dynamics or
-invariant set generation via abstract acceleration; if the verification step
-fails, we loop back to seek an alternative controller benefiting from the
-obtained counterexamples to safety using solution generalization and
-abstraction refinement.  We are able to efficiently synthesize stable and
-safe controllers considering a set of intricate physical plant models taken
-from the digital control literature.
+digitalization of signals by the controller.  The approach works in two
+stages, leveraging counterexample guided inductive synthesis (CEGIS) and
+reachability analysis.  CEGIS synthesises a static feedback controller that
+stabilizes the system under some restrictions given by the safety of the
+reach space.  Safety is verfied iether via BMC or abstract acceleration; if
+the verification step fails, we generate an alternative controller by
+generalizing the counterexample.  We synthesize stable and safe controllers
+for intricate physical plant models from the digital control literature.
 %

### 2017-01-24 cav2017/cav2017.tex
Institute
cut abstract

@@
 %\tocauthor{Authors' Instructions}
+\institute{}
+
 \maketitle
@@
 %
-This work presents a sound and automated approach to synthesize safe digital
+We present a sound and automated approach to synthesize safe digital
 feedback controllers for physical plants represented as linear, time

### 2017-01-24 cav2017/cav2017.tex
nudge intro

@@
 
-Linear Time Invariant (LTI) control models represent a broad class of dynamical systems
+Linear Time Invariant (LTI) models represent a broad class of dynamical systems
 %modern embedded software, performing highly non-trivial control tasks,
@@
 the life sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}.
-Control synthesis for LTI is broadly investigated, 
+Synthesis of controllers for LTI models is broadly investigated, 
 however the use of digital control architectures adds new challenges due to 
-%exacerbated by specific artefacts,  
 the effects of finite-precision arithmetic, time discretization, and quantization noise, which are typically introduced 
 by Analogue-to-Digital (ADC) and Digital-to-Analogue (DAC) conversion.  
-Whilst the research on digital control is well developed~\cite{astrom1997computer}, 
-automated and sound control synthesis is a challenging task,  
+While research on digital control is well developed~\cite{astrom1997computer}, 
+automated and sound control synthesis is challenging, 
 %Thus, the programming is a key barrier to broad adoption of digital control, 
@@
 %models~\cite{DBLP:conf/emsoft/RavanbakhshS16}. 
-Beyond stability, 
-recently reachability tools have been developed [cite SPACEx, Phaver, and others], 
-however they have not been employed towards control synthesis. 
+Beyond stability, recently reachability tools have been developed [cite
+SPACEx, Phaver, and others], however they have not been employed towards
+control synthesis.
 %\todo{why do we cite this paper \cite{cimatti2013parameter}?what is the relationship with our work? }

### 2017-01-24 cav2017/cav2017.tex
nudge

@@
 and perform %parametric 
-synthesis of safe digital controllers - the extension to more general quantitative properties is left to future work.
+synthesis of safe digital controllers -- the extension to more general
+quantitative properties is left to future work.
 
@@
 based on the error of the digital dynamics ensures that the deviation
-introduced by FWL does not make the digital system unstable.  A more recent
+introduced by FWL does not make the digital system unstable.  A~more recent
 approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
@@
 
-Asymptotic stability boils down to Lyapunov stability 
-and convergence to an equilibrium point~\cite{Astrom08}. 
-Lyapunov stability requires that model trajectories remain in 
-a neighborhood of the equilibrium point. 
-In the case of closed-loop LTI models as in~\eqref{eq:closedloopss}, 
-the equilibrium point is the origin (if the reference is equal to zero), 
-or an offset thereof. Here, we consider systems with a zero reference signal.
+Asymptotic stability boils down to Lyapunov stability and convergence to an
+equilibrium point~\cite{Astrom08}.  Lyapunov stability requires that model
+trajectories remain in a neighborhood of the equilibrium point.  In the case
+of closed-loop LTI models as in~\eqref{eq:closedloopss}, the equilibrium
+point is the origin (if the reference is equal to zero), or an offset
+thereof.  Here, we consider systems with a zero reference signal.
 
 A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable
-\textit{iff} all the roots of the characteristic polynomial 
-(i.e., the eigenvalues of the closed-loop matrix $A_d - B_d K$) 
-are inside the unity circle in the complex plane, i.e., \textit{iff} their absolute 
-values are less than one~\cite{astrom1997computer}. 
-In this paper, we express the stability specification $\phi_{stability}$ 
-in terms of a check known as Jury's criterion~\cite{fadali}:  
-this is an easy algebraic formula to select the entries of matrix $K$, 
-so that the closed-loop dynamics are shaped as desired. 
-A detailed description of this specification can be found in Appendix~\ref{sec:appendix-stability}.
+\textit{iff} all the roots of the characteristic polynomial (i.e., the
+eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
+circle in the complex plane, i.e., \textit{iff} their absolute values are
+less than one~\cite{astrom1997computer}.  In this paper, we express the
+stability specification $\phi_{stability}$ in terms of a check known as
+Jury's criterion~\cite{fadali}: this is an easy algebraic formula to select
+the entries of matrix $K$, so that the closed-loop dynamics are shaped as
+desired.  A detailed description of this specification can be found in
+Appendix~\ref{sec:appendix-stability}.
 
@@
 
-In this study, we are not limited to the synthesis of digital stabilizing controllers -- 
-a well known task in the literature on digital control system -- 
-but target safety requirements with an overall approach that is sound and automated. 
-More specifically, 
-we require that the closed-loop system \eqref{eq:closedloopss} meets given safety specifications. 
-A safety specification raises a requirement on the states of the model, 
-such that the feedback controller (namely the choice of the gains in $K$) 
-must ensure that the states never exit such requirement. 
-Note that a stable, closed-loop system is not necessarily a safe system: 
-indeed, the state values may leave the safe space whilst they converge to the equilibrium, 
-which is typical in the case of oscillatory dynamics. However, a safe system will always be stable.
-In this work, the safety property represented by $\phi_{safety}$ is encoded as follows: 
+In this study, we are not limited to the synthesis of digital stabilizing
+controllers -- a well known task in the literature on digital control system
+-- but target safety requirements with an overall approach that is sound and
+automated.  More specifically, we require that the closed-loop system
+\eqref{eq:closedloopss} meets given safety specifications.  A safety
+specification raises a requirement on the states of the model, such that the
+feedback controller (namely the choice of the gains in $K$) must ensure that
+the states never exit such requirement.  Note that a stable, closed-loop
+system is not necessarily a safe system: indeed, the state values may leave
+the safe space whilst they converge to the equilibrium, which is typical in
+the case of oscillatory dynamics.  However, a safe system will always be
+stable.  In~this work, the safety property represented by $\phi_{safety}$ is
+encoded as follows:
 %
@@
 %\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
-where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th instant, respectively. 
-This means that the states will always be within the $n$-dimensional hyper-box.
-
-Furthermore, 
-it is practically relevant to consider constraints on the input signal $u_{k}$
-and bounds on the initial states $x_0$, 
+%
+where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
+for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
+instant, respectively.  This means that the states will always be within the
+$n$-dimensional hyper-box.
+
+Furthermore, it is practically relevant to consider constraints on the input
+signal $u_{k}$ and bounds on the initial states $x_0$,
 which we assume have given bounds. %%  $\overline{u}$, $\underline{u}$
@@
 \wedge \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$$  
-In the first case, 
-this means that the control input saturates in view of physical constraints.
+In the first case, this means that the control input saturates in view of
+physical constraints.
 

### 2017-01-24 cav2017/cav2017.tex
more text

--- 2017-01-24 cav2017/cav2017.tex
@@
 the controller $K$ denotes $P$ and $(x_0, u_k)$ represents $x$. 
-While the controller precision \todo{update notations} $\langle I_c,F_c\rangle$ is given and fixed, 
+While the controller precision \todo{are these notations updated?} $\langle I_c,F_c\rangle$ is given and fixed, 
 we can vary the plant precision $\langle I_p,F_p\rangle$ such that $I_p \geq I_c \wedge F_p \geq F_c$.
@@
 
-Regarding the latter, we synthesize a safe controller by unwinding the transition system
-$k$ steps and picking a controller $K$ and an initial state such that the states at each step do
+ \todo{unclear next: it seems like to select a single initial state here, rather than considering the set thereof - clarify. also, clarify relationship btw k and soundness. }
+Regarding the second requirement, we synthesize a safe controller by unwinding the transition system
+$k$ steps and by picking a controller $K$ and an initial state, such that the states at each step do
 not violate the safety criteria. This is sound if the current $k$ is below the

### 2017-01-24 cav2017/cav2017.tex
more text

@@
 allowed initial states, it is safe for any initial state in the
-hypercube. Thus we only need to check $2^N$ initial states, where $N$
-is the number of states.
-
-\begin{proof} 
-Consider the set of initial states, $X_0$, assumed to be convex since it's a hypercube. 
+hypercube. Thus we only need to check $2^n$ initial states, where $n$
+is the dimension of the state space (number of continuous variables).
+
+To argue for this sufficient check, 
+consider the set of initial states, $X_0$, which we assume to be convex since it's a hypercube. 
 Name $v_i$ its vertexes, where $i=1,\ldots, 2^n$.  
 Thus any point $x \in X_0$ can be expressed by convexity as $x = \sum_{i=1}^{2^n} \alpha_i v_i$, 
-where $\sum_{i=1}^{2^n} \alpha_i =1$. \\
-So then if $x_0=x$, then 
+where $\sum_{i=1}^{2^n} \alpha_i =1$. Then if $x_0=x$, we obtain 
 \begin{align*}
@@
 where $x_k^i$ denotes the trajectories obtained from the single vertexes $v_i$.
-\end{proof}
 
@@
 completeness threshold $\overline{k}$ for the current candidate $K$
-and check that $k{\leq}\overline{k}$.
-
-A stable control system is known to have converging dynamics, i.e., the
-distance from the reference (in this case the origin) decreases over time.
+and check that $k{\leq}\overline{k}$. This is done according to the following argument.
+
+A stable control system is known to have converging dynamics. 
+Assume the closed-loop matrix eigenvalues are not repeated (which is sensible to do, since we select them). 
+The distance of trajectories from the reference point (in this case the origin) decreases over time within subspaces related to real-valued eigenvalues. 
+However, this in general not the case when dealing with complex eigenvalues.  
+Consider the matrix $(A_d - B_d K)$, which updates the states every time step, and select eigenvalue with smallest (non trivial) imaginary value.  
+call such value $\vartheta$. 
+At every time interval $kT_s, (k+1)T_s$ ($T_s$ being the sampling time), 
+the dynamics projected on the corresponding eigenspace rotate of $\vartheta T_s$ radiants.  
+So surely taking $k$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, 
+after $k$ steps we have completed a rotation. 
+This is the completeness threshold.
 
@@
 
-\begin{proof}
-Consider the matrix $(A_d - B_d K)$, which updates the states every time step, and select eigenvalue with smallest (non trivial) imaginary value.  
-call such value $\vartheta$. 
-At every time interval $kT_s, (k+1)T_s$ ($T_s$ being the sampling time), 
-the dynamics projected on the corresponding eigenspace rotate of $\vartheta T_s$ radiants.  
-So surely taking $k$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, after $k$ steps we've completed a rotation. 
-This is the completeness threshold. 
-\end{proof}
-
 \end{enumerate}
@@
 
-We illustrate our approach with \todo{what example is this?} example,
+We illustrate our approach with \todo{what example is this?} an example,
 extracted from the literature~\cite{Franklin15}.

### 2017-01-24 cav2017/cav2017.tex
jaded

@@
 where $\mathcal{A}=\bigcup_{k=1}^\infty (A_d-B_dK)t^k, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k(A_d-B_dK)^iB_{n}$ are abstract matrices for the closed-loop system,
-whereas the set N is non-deterministically chosen.
+whereas the set N is non-deterministically chosen. \todo{add citation to SAS article, readers will be lost. }
 
@@
 all our benchmarks, which are SISO models (cf. section~\ref{sec:preliminaries}). 
+\todo{they are not: we do not have a 1d output map (SO= single output), rather get access to all variables. so the output map (C) is the identity, if you will. 
+this is a good point to clarify this, mention possible extensions to observer-based feedback architectures. }
 

### 2017-01-24 cav2017/cav2017.tex
revised intro to the CEGIS sec + revised some comments

@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{CEGIS of Safe Controllers for LTI Systems with Solution Generalization} 
+\section{CEGIS of Safe Controllers for LTI Systems} 
 \label{sec:CEGARIS} 
@@
 
-We outline the general architecture of the program synthesizer used in both approaches \todo{which approaches - pls recall or clarify}. 
-We then give the details of both methods of solution generalization \todo{define ``solution generalisation''} that we compare.  
-The first checks safety by unwinding the transition relation to a completeness threshold, 
-whereas the second employs abstract acceleration.
+In this section, we describe our technique for synthesizing safe
+digital feedback controllers using CEGIS.  For this purpose, we first
+provide the synthesiser's general architecture, followed by describing
+two approaches that use it to automatically generate safe controllers:
+the first one is a baseline approach which relies on a naive explicit
+unwinding of the transition relation, whereas the second uses an
+abstraction to implicitly evaluate all possible progressions of the
+system simultaneously. % on an infinite time horizon.
+
+%% We outline the general architecture of the program synthesizer used in both approaches \todo{which approaches - pls recall or clarify}. 
+%% We then give the details of both methods of solution generalization \todo{define ``solution generalisation''} that we compare.  
+%% The first checks safety by unwinding the transition relation to a completeness threshold, 
+%% whereas the second employs abstract acceleration.
 
@@
 the controller $K$ denotes $P$ and $(x_0, u_k)$ represents $x$. 
-While the controller precision \todo{are these notations updated?} $\langle I_c,F_c\rangle$ is given and fixed, 
-we can vary the plant precision $\langle I_p,F_p\rangle$ such that $I_p \geq I_c \wedge F_p \geq F_c$.
+%% While the controller precision \todo{update notations} $\langle I_c,F_c\rangle$ is given and fixed, 
+%% we can vary the plant precision $\langle I_p,F_p\rangle$ such that $I_p \geq I_c \wedge F_p \geq F_c$.
 

### 2017-01-24 cav2017/cav2017.tex
restructured and edited sec 4.4 (abstraction-based CEGIS)

@@
 
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Solution generalization} 
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-\todo{All good - only the word ``generalisation'' won't be understood by a control person (we might have reviewers from this area?).
+%% %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%% \subsection{Solution generalization} 
+%% %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+%% \todo{All good - only the word ``generalisation'' won't be understood by a control person (we might have reviewers from this area?).
 Anticipate the explanation  given below to the introduction section.}
 
-Given the large solution space to be searched during the inductive
-synthesis, we parametrize the target language, which induces a
-lattice of progressively more expressive languages.  This enables us
-to start by synthesizing a program at the lowest point on
-this lattice, and to increase the parameters of the language until we
-reach a point at which the synthesis succeeds \todo{if at all - completeness?}. Whenever we manage to
-synthesize a solution at some lower point on the lattice, we
-must apply some form of solution generalization to obtain a full
-solution (i.e., a solution in the original search space).
-This parametrization greatly increases the efficiency of our system, since
-low-level languages (over the lattice) are easier to decide safety for 
-(i.e., the validation oracle finds an answer faster). In other words, 
-if a program can be synthesized in a low-complexity language, the whole procedure finishes
-much faster than if synthesis had been attempted in a high-complexity
-language. We investigate two different approaches for integrating solution 
-generalization into CEGIS:
-%
-\begin{itemize}
-\item[1.] The first approach (described in Sec.~\ref{sec:CEGIS-precision-incrementation})
-  uses a multi-staged verification phase and performs solution generalisation based on
-the plant precision, the number of loop unrollings, 
-and the sampling rate. Essentially, it finds a controller for an individual initial state
-and input with a bounded time horizon and generalizes to all reachable states,
-inputs, and time horizons. The safety check is performed in this approach 
-via unfolding of the transition system corresponding to the synthesized controller.
-\todo{mention issue of completeness threshold here?}
-
-%% (with a final verification loop that verifies
-%% the continuous system behaviour against the previously verified
-%% discrete system bi-simulation)
-\item[2.] The second approach (described in Sec~\ref{sec:CEGIS-abstraction-refinement})
-  finds a controller for a continuous initial set of states and set of inputs, 
-  over an abstraction of the continuous dynamics that conforms to
-  witness proofs at specific times. It further generalizes the
-  solution over all times by refining the number of witnesses.  
-  In order to perform the safety check, this approach uses abstract acceleration
-  \cite{cattaruzza2015unbounded} to compute the controller's set of states. 
-  \todo{clarify: what is the ``set of states'' of the controller? }
-\end{itemize}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{CEGIS with multi-staged verification}
+%% Given the large solution space to be searched during the inductive
+%% synthesis, we parametrize the target language, which induces a
+%% lattice of progressively more expressive languages.  This enables us
+%% to start by synthesizing a program at the lowest point on
+%% this lattice, and to increase the parameters of the language until we
+%% reach a point at which the synthesis succeeds \todo{if at all - completeness?}. Whenever we manage to
+%% synthesize a solution at some lower point on the lattice, we
+%% must apply some form of solution generalization to obtain a full
+%% solution (i.e., a solution in the original search space).
+%% This parametrization greatly increases the efficiency of our system, since
+%% low-level languages (over the lattice) are easier to decide safety for 
+%% (i.e., the validation oracle finds an answer faster). In other words, 
+%% if a program can be synthesized in a low-complexity language, the whole procedure finishes
+%% much faster than if synthesis had been attempted in a high-complexity
+%% language. We investigate two different approaches for integrating solution 
+%% generalization into CEGIS:
+%% %
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Naive approach: CEGIS with multi-staged verification}
 \label{sec:CEGIS-precision-incrementation}
@@
   \ 0.5]$. Finally, {\sc synthesize} finds the candidate $K=[0.01171875
-  \ -0.013671875 \ -0.013671875]$, which is validated as a final
+  \ -0.013671875 \ -0.013671875]^T$, which is validated as a final
 solution by all verification stages.
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{CEGIS with abstraction refinement}
+\subsection{Abstraction-based CEGIS}
 \label{sec:CEGIS-abstraction-refinement}
@@
 
-% The verification of a hybrid continuous/discrete system over an unbounded time, requires the
-% non-deterministic simulation of an infinite set of states, which is undecidable. Our initial approach creates an
-% abstraction of this system by establishing bounds on the error between such a system and a discrete-time/continuous-space model.
-% This model is still however, quite complex, hard to verify, and many of the states involved are inconsequential to
-% the safety specification.
-% The advantage of this model is that it starts with a very simple description regardless of the complexity of the overall dynamics, and only expands to more complex models when a solution cannot be found.
-
-% \addtodo{Move as much as possible from Sec~\ref{sec:cof_verification}
-% to the appendix (e.g., discussion on abstract acceleration). 
-% Merge the rest in Sec~\ref{sec:cof_synth}.}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%\subsubsection{Verification of a controllable system}
-%\label{sec:cof_verification}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%Whilst there are other properties, we may include in the verification, 
-% we will solely focus on these for simplicity of the explanation.
-% We assume that we do not want saturation in our system, 
-% hence the control loop has only one mode.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%\subsubsection{Controller synthesis}\label{sec:cof_synth}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%\begin{itemize}
+%\item[1.]
+
+  The naive approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
+  %uses a multi-staged verification phase and performs solution generalisation based on
+%the plant precision, the number of loop unrollings, 
+  %and the sampling rate. Essentially, it
+  synthesises a controller for an individual initial state
+and input with a bounded time horizon and, subsequently, it generalizes it to all reachable states,
+inputs, and time horizons during the verification phase.
+Essentially, this approach relies on the explicit
+simulation over a bounded time horizon of individual states that form
+part of an uncountable space and tries to generalize it for an
+infinite space over an infinite time horizon.
+
+%% The safety check is performed in this approach 
+%% via unfolding of the transition system corresponding to the synthesized controller
+%% up to a completeness threshold. Due to its 
+%\todo{mention issue of completeness threshold here?}
+
+  %% solution over all times by refining the number of witnesses.  
+  %% In order to perform the safety check, this approach uses abstract acceleration
+  %% \cite{cattaruzza2015unbounded} to compute the controller's set of states. 
+  %% \todo{clarify: what is the ``set of states'' of the controller? }
+%\end{itemize}
+
+%% The verification of a hybrid continuous/discrete system over an
+%% unbounded time, requires the non-deterministic simulation of an
+%% infinite set of states, which is undecidable.
+
+%% Our naive approach
+%% creates an abstraction of the system by establishing bounds on the
+%% error between such a system and a discrete-time/continuous-space
+%% model.  This model is still however, quite complex, hard to verify,
+%% and many of the states involved are inconsequential to the safety
+%% specification.
+
+Conversely, in this section, 
+we  find a controller for a continuous initial set of states and set of inputs, 
+  over an abstraction of the continuous dynamics that conforms to
+  witness proofs at specific times. %% It further generalizes the
+  Moreover, this approach uses abstraction refinement enabling us to 
+  always start with a very simple description regardless of the complexity of the overall
+dynamics, and only expand to more complex models when a solution
+cannot be found.
+
   The CEGIS loop for this approach is illustrated in Fig.~\ref{fig:CEGARIS}.
@@
 }
-\caption{CEGIS with abstraction refinement.}
+\caption{Abstraction-based CEGIS.}
 \label{fig:CEGARIS} 

### 2017-01-25 cav2017/cav2017.tex
Table for res

@@
 
+\begin{table}
+
+\begin{tabular}{| r | c | l | r | r |}
+\hline
+\# & Benchmark  & $\mathcal{F}_{\langle I_c,F_c \rangle}$ & time for approach 1  & time for approach 2 \\\hline
+1 & Ball Maglev & & & \\
+2 & Cruise Control & & & \\
+3 & DC Motor& & & \\
+4 & Helicopter & & & \\
+5 & Inverted Pendulum 1& & & \\
+6 & Inverted Pendulum 2& & & \\
+7 & Magnetic Pointer& & & \\
+8 & Magnetic Suspension& & & \\
+9 & Pendulum& & & \\
+10 & Suspension& & & \\
+11 & Tape Driver & & & \\
+12 & Uscgtamper & & & \\
+13 & Satellite & & & \\\hline
+
+\end{tabular}
+\caption{Experimental results}
+\end{table}
+
 %-------------------------------

### 2017-01-25 cav2017/cav2017.tex
running example (with abstraction refinement) for AA

@@
 \end{enumerate}
+
+\paragraph{Illustrative Example}
+
+Let us take the Helicopter example in Table \ref{table:State-space benchmarks} with discretized dynamics
+$$A_d = \left[\begin{array}{ccc}2.6207&-1.1793&0.65705\\2&0&0\\0&0.5&0\end{array}\right], B_d = \left [\begin{array}{c}8\\0\\0\end{array}\right]$$
+Using an initial state $\bigwedge -.9 \leq x_{0,i} \leq .9$, inputs $-10 \leq u \leq 10$, and a safety specification $\bigwedge -.92 \leq x_i \leq .92$, the {\sc synthesize} phase in Fig.~\ref{fig:CEGARIS} synthesises an initial candidate controller $K=[\begin{array}{ccc}0.24609375&-0.125&0.1484375\end{array}]$.
+Although this candidate is stable, the {\sc verify} phase finds it to be unsafe and returns a list of iterations with an example initial state that fails the safety specification
+$(k,x_0) \in \{ (2, [\begin{array}{ccc}0.9&-0.9&0.9\end{array}]), (3, [\begin{array}{ccc}0.9&-0.9&-0.9\end{array}])\}$.
+This allows the {\sc abstract} phase to create a new safety specification that considers these iterations for these initial states to constrain the solution space.
+This refinement allows {\sc synthesize} to find a controller $K=[\begin{array}{ccc}0.23828125&-0.17578125&0.109375\end{array}]$, which this time passes the verification phase, resulting in a safe system.
 

### 2017-01-25 cav2017/cav2017.tex
some changes to the intro

@@
 on linear models with known  implementation features (e.g., number of bits, fixed-point
-arithmetic), %\addtodo{[clarify next] with known configurations} 
-and perform %parametric 
+arithmetic), and perform 
 synthesis of safe digital controllers -- the extension to more general
@@
 We describe and evaluate two approaches for synthesising digital controllers
-for state-space physical plants.  Both approaches consider a counterexample
-guided inductive synthesis (CEGIS) loop.  In the first approach, we devise a
-digital controller that stabilizes the system whilst remaining safe given a
-pre-selected time horizon; then, we verify its potential safety by unfolding
-the dynamics of the system and checking for a completeness threshold.  In
-the second approach, we substitute the second step by employing abstract
-acceleration to unfold the dynamics forward, instead of symbolically
-unwinding the transition relation~\cite{cattaruzza2015unbounded}.
+for state-space physical plants, both based on a counterexample
+guided inductive synthesis (CEGIS)~\cite{sketch} loop.
+The first approach uses a naive
+technique that starts by devising a digital controller that stabilizes the system
+whilst remaining safe for a 
+pre-selected time horizon and, subsequently, verifies its potential safety by unfolding
+the dynamics of the system and checking for a completeness threshold.
+As it requires explicit unfolding up to a completeness
+threshold, this approach may result in a state space explosion.
+Instead of explicitly unfolding the dynamics, the second approach 
+employs abstract acceleration~\cite{cattaruzza2015unbounded} to implicitly
+evaluate all possible progressions of the system simultaneously.
+Additionally, the second approach uses
+abstraction refinement enabling us to always start with a very simple description
+regardless of the complexity of the overall dynamics, and only expand to more
+complex models when a solution cannot be found.
+
+%% we substitute the second step by employing abstract
+%% acceleration to unfold the dynamics forward, instead of symbolically
+%% unwinding the transition relation~\cite{cattaruzza2015unbounded}.
 \todo{We need to emphasise the derivation of errors for soundness. Can we claim completeness already?}
+
 We provide experimental results 
@@
 infinite space over an infinite time horizon.
-
-%% The safety check is performed in this approach 
-%% via unfolding of the transition system corresponding to the synthesized controller
-%% up to a completeness threshold. Due to its 
-%\todo{mention issue of completeness threshold here?}
 

### 2017-01-25 cav2017/cav2017.tex
small editing intro

@@
 We describe and evaluate two approaches for synthesising digital controllers
-for state-space physical plants, both based on a counterexample
-guided inductive synthesis (CEGIS)~\cite{sketch} loop.
+for state-space physical plants, both based on CounterExample
+Guided Inductive Synthesis (CEGIS)~\cite{sketch}.
 The first approach uses a naive
@@
 whilst remaining safe for a 
-pre-selected time horizon and, subsequently, verifies its potential safety by unfolding
+pre-selected time horizon; then, it verifies its potential safety by unfolding
 the dynamics of the system and checking for a completeness threshold.

### 2017-01-25 cav2017/cav2017.tex
edited contributions

@@
 Guided Inductive Synthesis (CEGIS)~\cite{sketch}.
-The first approach uses a naive
+{\em The first approach} uses a naive
 technique that starts by devising a digital controller that stabilizes the system
@@
 threshold, this approach may result in a state space explosion.
-Instead of explicitly unfolding the dynamics, the second approach 
+Instead of explicitly unfolding the dynamics, {\em the second approach} 
 employs abstract acceleration~\cite{cattaruzza2015unbounded} to implicitly
@@
 %
-\item In this paper we extend the problem of digital control synthesis from a transfer function representation into a state space representation.
-This entails the verification of safety properties in addition to the already existing stability conditions which is a much harder problem.
-%
-\item To achieve this, we develop two approaches and compare them, the first relying on a non-deterministic simulation of the system and a completeness proof, whilst the second leverages on the concepts of abstraction and acceleration to increase speed whilst retaining soundness.
-%
-\item We develop a solution generalization algorithm for the first approach and an abstraction refinement for the second, both of which improve the performance of the CEGIS loop. 
-%
-\item We develop a model for different sources quantization and their effect on the state space progression, for which we find safe bounds that ensure the safety of our controllers in a hybrid continuous-digital domain.
+\item In this paper we extend the problem of digital control synthesis
+  from a transfer function representation into a state space
+  representation.  This entails the verification of safety properties
+  in addition to the already existing stability conditions which is a
+  much harder problem.
+%
+\item We develop two approaches: the first, naive one relies on
+  explicit unfolding of the system's dynamics up to a completeness
+  threshold, whilst the second one is abstraction-based and leverages
+  on the concept of abstraction refinement and acceleration to increase speed whilst retaining
+  soundness.
+%
+\item We develop a model for different sources quantization and their
+  effect on the state space progression, for which we find safe bounds
+  that ensure the safety of our controllers in a hybrid
+  continuous-digital domain.
 %

### 2017-01-25 cav2017/cav2017.tex
Some stuff in the results

@@
 
+We give the run-times required to synthesize a stable controller for each
+benchmark in Table~\ref{tab:results}.  
+Here \textit{Benchmark} is the name of the employed
+benchmark, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used to model the plant, while \textit{Time}
+is the total time (in seconds) required to synthesize a stable controller
+for the given plant, for approach 1 and approach 2. The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is always chosen to be $I_c = 8, F_c = 8$.
+
+For the majority of our benchmarks, the conjecture stands that the Acceleration back-end is faster than the basic multi-staged verification approach.
+However, it does fail to find solutions to XXX benchmarks, where the numbers given in the discretization matrices are really small.
+
+The basic multi-staged verification approach finds X / X benchmarks, albeit in an expected slower time. The solutions that are not found are due to time-out or XXXX
+
 \begin{table}
@@
 \hline
-\# & Benchmark  & $\mathcal{F}_{\langle I_c,F_c \rangle}$ & time for approach 1  & time for approach 2 \\\hline
+\# & Benchmark  & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & time for approach 1  & time for approach 2 \\\hline
 1 & Ball Maglev & & & \\
@@
 \end{tabular}
-\caption{Experimental results}
+\caption{Experimental results \label{tab:results}}
 \end{table}
+
+he median runtime for our benchmark set is XXXX.  Overall,
+the average synthesis time amounts to approximately XXX minutes.  We
+consider these times short enough to be of practical use to control
+engineers, and thus affirm RQ1.
+
+The
+synthesized controllers were confirmed to be stable outside of our model
+representation using MATLAB, positively answering RQ2.  A~link to the full
+experimental environment, including scripts to reproduce the results, all
+benchmarks and the tool, is provided in the
+footnote.\footnote{\url{url.here.}}
 

### 2017-01-25 benchmark-runner/axelerator_matlab_check_12am.m
re-run of axelerator

@@ -3,33 +3,18 @@ K = [fxp(0.5)];
 A = [ 0.998 ];
 B = [ 0.125 ];
 INPUT = [-1,1];
-%run fixedpointcheck.m: SINGLE STATE, manually checked
+%run fixedpointcheck.m %single state = checked manually
 
 msg = 'dcmotor_ss_disc1.ss'
 K = [fxp(0), fxp(-0.96875)];
 A = [ 0.90122,1.3429e-08;7.4506e-09,0 ];
 B = [ 128;0 ];
 INPUT = [-1,1];
-
 run fixedpointcheck.m
+
 msg = 'helicopter_ss_disc1.ss'
 K = [fxp(0.234375), fxp(-0.1484375), fxp(0.078125)];
 A = [ 2.6207,-1.1793,0.65705;2,0,0;0,0.5,0 ];
 B = [ 8;0;0 ];
 INPUT = [-1,1];
-
-run fixedpointcheck.m
-
-msg = 'magsuspension_ss_disc2.ss'
-K = [fxp(40.17578125), fxp(-15.953125)];
-A = [ 2.001,-1;1,0 ];
-B = [ 0.0625;0 ];
-INPUT = [-1000,1000];
-run fixedpointcheck.m
-
-msg = 'invpendulum_pendang_ss_disc1.ss'
-K = [fxp(4.75), fxp(-1)];
-A = [ 2.2553,-1;1,0 ];
-B = [ 0.5;0 ];
-INPUT = [-10,10];
 run fixedpointcheck.m

### 2017-01-25 cav2017/cav2017.tex
more editing intro + contributions

@@
 Guided Inductive Synthesis (CEGIS)~\cite{sketch}.
-{\em The first approach} uses a naive
+
+{\em The first approach} uses a {\em naive}
 technique that starts by devising a digital controller that stabilizes the system
@@
 pre-selected time horizon; then, it verifies its potential safety by unfolding
-the dynamics of the system and checking for a completeness threshold.
-As it requires explicit unfolding up to a completeness
-threshold, this approach may result in a state space explosion.
+the dynamics of the system and checking for a {\em completeness threshold}, i.e.,
+the number of iterations required to sufficiently unwind
+the closed-loop state-space system such
+that the boundaries are not violated for any larger number of iterations.
+As it requires explicit unfolding up to the completeness
+threshold, this approach may result in state space explosion.
+
 Instead of explicitly unfolding the dynamics, {\em the second approach} 
-employs abstract acceleration~\cite{cattaruzza2015unbounded} to implicitly
-evaluate all possible progressions of the system simultaneously.
+employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to implicitly
+evaluate all possible progressions of the system simultaneously and thus avoid
+the state space explosion problem.
 Additionally, the second approach uses
-abstraction refinement enabling us to always start with a very simple description
+{\em abstraction refinement} enabling us to always start with a very simple description
 regardless of the complexity of the overall dynamics, and only expand to more
@@
 %
-\item We develop two approaches: the first, naive one relies on
-  explicit unfolding of the system's dynamics up to a completeness
+\item We develop two approaches: the first, naive, one relies on
+  explicit unfolding of the system's dynamics up to the completeness
   threshold, whilst the second one is abstraction-based and leverages
-  on the concept of abstraction refinement and acceleration to increase speed whilst retaining
+  the concepts of abstraction refinement and acceleration to increase speed whilst retaining
   soundness.

### 2017-01-25 benchmark-runner/accelerator-ss-benchmark-runner.sh
Adapted safety_stability.c to match new matlab script.
Debugged safety_stability.c to now match MatLab reference script logic.

@@ -9,6 +9,7 @@ width_check_file='width_LTI.c'
 script_base_directory=`pwd`
 spec_header_file='spec.h'
 cbmc_log_file='cbmc-tmp.log'
+solution_file='solution.log'
 
 function setup_benchmark_directory {
  mkdir -p "$1" 2>/dev/null
@@ -105,21 +106,22 @@ else
 
  #dkr11
  if [ "$1" == "dkr11" ]; then
-  benchmark_dirs=('/users/pkesseli/documents/control-synthesis/benchmarks/state-space/magsuspension_ss/' '/users/pkesseli/documents/control-synthesis/benchmarks/state-space/invpendulum_pendang_ss/')
+  benchmark_dirs=('/users/pkesseli/documents/control-synthesis/benchmarks/state-space/ballmaglev_ss/' '/users/pkesseli/documents/control-synthesis/benchmarks/state-space/magsuspension_ss/' '/users/pkesseli/documents/control-synthesis/benchmarks/state-space/invpendulum_pendang_ss/')
  fi
 
  #dkr12
  if [ "$1" == "dkr12" ]; then
-  benchmark_dirs=('/users/pkesseli/documents/control-synthesis/benchmarks/state-space/invpendulum_cartpos_ss/' '/users/pkesseli/documents/control-synthesis/benchmarks/state-space/suspension_ss/')
+  benchmark_dirs=('/users/pkesseli/documents/control-synthesis/benchmarks/state-space/magneticpointer_ss/' '/users/pkesseli/documents/control-synthesis/benchmarks/state-space/invpendulum_cartpos_ss/' '/users/pkesseli/documents/control-synthesis/benchmarks/state-space/suspension_ss/')
  fi
 
  #dkr13
  if [ "$1" == "dkr13" ]; then
-  benchmark_dirs=('/users/pkesseli/documents/control-synthesis/benchmarks/state-space/tapedriver_ss/' '/users/pkesseli/documents/control-synthesis/benchmarks/state-space/pendulum_ss/')
+  benchmark_dirs=('/users/pkesseli/documents/control-synthesis/benchmarks/state-space/pendulum_ss/' '/users/pkesseli/documents/control-synthesis/benchmarks/state-space/uscgtampa_ss/')
[…]

### 2017-01-25 benchmark-runner/completeness-threshold-ss-benchmark-runner.sh

@@ -6,6 +6,7 @@ synthesis_file='safety_stability.c'
 script_base_directory=`pwd`
 spec_header_file='benchmark.h'
 source_template_directory=${script_base_directory}/universalrunner
+solution_file='solution.log'
 
 function echo_log {
  echo $1 | tee -a ${log_file}
@@ -45,12 +46,14 @@ function extract_input_upper_bound {
 
 function setup_benchmark_directory {
  mkdir -p "$1" 2>/dev/null
- rm "$1"/* 2>/dev/null
+ #rm "$1"/* 2>/dev/null
  cp ${source_template_directory}/${synthesis_file} ${working_directory}/
  cp ${source_template_directory}/control_types.h ${working_directory}/
  cp ${source_template_directory}/operators.h ${working_directory}/
  cp ${source_template_directory}/intervals.h ${working_directory}/
  cp ${source_template_directory}/mpreal.h ${working_directory}/
+ cp ${source_template_directory}/int_2Inverse.h ${working_directory}/
+ cp ${source_template_directory}/int_3Inverse.h ${working_directory}/
  cp ${source_template_directory}/discrete_step_k_completeness_check.cpp ${working_directory}/
 }
 
@@ -64,8 +67,13 @@ function write_spec_header {
 
  echo "#define NINPUTS ${num_inputs}" >>${header_file}
  echo "#define NOUTPUTS ${num_outputs}" >>${header_file}
+ echo '#ifdef INTERVAL' >>${header_file}
+ echo "#define INPUT_LOWERBOUND (__plant_precisiont)${input_lower_bound}" >>${header_file}
+ echo "#define INPUT_UPPERBOUND (__plant_precisiont)${input_upper_bound}" >>${header_file}
+ echo '#else' >>${header_file}
  echo "#define INPUT_LOWERBOUND (__plant_typet)${input_lower_bound}" >>${header_file}
  echo "#define INPUT_UPPERBOUND (__plant_typet)${input_upper_bound}" >>${header_file}
+ echo '#endif' >>${header_file}
  A_value=$(echo ${A} | sed -r 's/;/ }, { /g')
  A_value=$(echo ${A_value} | sed -r 's/([-0-9]+(\.[0-9e-]+)?)/interval(\1)/g')
  echo "const __plant_typet _controller_A[NSTATES][NSTATES] = { { ${A_value} } };" >>${header_file}
@@ -89,11 +97,11 @@ if [ -z "$1" ]; then
  #dkr10
[…]

### 2017-01-25 benchmark-runner/universalrunner/safety_stability.c

@@ -321,13 +321,11 @@ void inputs_equal_ref_minus_k_times_states(void)
        //{ result_fxp += (K_fxp[k] * (__controller_typet)_controller_states[k]);}
 
         _controller_inputs = sub(zero_type, plant_cast(result_fxp));
-      #ifdef CPROVER
-          #ifdef INTERVAL
-          __CPROVER_assume(_controller_inputs.high<INPUT_UPPERBOUND && _controller_inputs.low >INPUT_LOWERBOUND);
-          #else
-          __CPROVER_assume(_controller_inputs < INPUT_UPPERBOUND && _controller_inputs > INPUT_LOWERBOUND);
-          #endif
-      #endif
+        #ifdef INTERVAL
+        __DSVERIFIER_assert(_controller_inputs.high<INPUT_UPPERBOUND && _controller_inputs.low >INPUT_LOWERBOUND);
+        #else
+        __DSVERIFIER_assert(_controller_inputs < INPUT_UPPERBOUND && _controller_inputs > INPUT_LOWERBOUND);
+        #endif
 
   }
  }
@@ -349,8 +347,8 @@ void states_equals_A_states_plus_B_inputs(void)
      //states_equals_A_states_plus_B_inputs_result[i]=0;
     for(int k=0; k<NSTATES; k++) {
       states_equals_A_states_plus_B_inputs_result[i] = add(states_equals_A_states_plus_B_inputs_result[i] , mult( _controller_A[i][k],_controller_states[k]));
-      states_equals_A_states_plus_B_inputs_result[i] = add(states_equals_A_states_plus_B_inputs_result[i] , mult( _controller_B[i],_controller_inputs));
     }
+    states_equals_A_states_plus_B_inputs_result[i] = add(states_equals_A_states_plus_B_inputs_result[i] , mult( _controller_B[i],_controller_inputs));
    }
 
 #ifndef INTERVAL
@@ -402,7 +400,7 @@ void states_equals_A_states_plus_B_inputs(void)
 int check_safety(void)
 {
 
-  for(int j=0; j<NSTATES; j++)//set initial states and reference
+  /*for(int j=0; j<NSTATES; j++)//set initial states and reference
   {
     #ifdef CPROVER
      __plant_typet __state0 = _controller_states[0];
@@ -417,7 +415,7 @@ int check_safety(void)
[…]

### 2017-01-25 cav2017/cav2017.tex
Fixed some comments

@@
 automated and sound control synthesis is challenging, 
-%Thus, the programming is a key barrier to broad adoption of digital control, 
-%and requires considerable expertise.
-%Whilst there is a vast literature on validation of control systems,
-%the subject of control synthesis has been somewhat restricted in the properties it explores.  
-%Traditionally, this focuses mainly on stability %, working typically on continuous domains
 particularly when the synthesis objective goes beyond classical stability or tracking requirements. 
-%\cite{DBLP:journals/corr/AbateBCCDKK16,sadabadi2016static}, or using switched
-%models~\cite{DBLP:conf/emsoft/RavanbakhshS16}. 
-Beyond stability, recently reachability tools have been developed [cite
-SPACEx, Phaver, and others], however they have not been employed towards
+Beyond stability, recently reachability tools have been developed \cite{FLD+11,Fre05}, however they have not been employed towards
 control synthesis.
-%\todo{why do we cite this paper \cite{cimatti2013parameter}?what is the relationship with our work? }
-% when discretising the state-space for verification and
-%parameter synthesis~\cite{cimatti2013parameter}.
+The problem of safety is an important one, since the synthesis of a stable controller does not ensure
+that the system will not transitively visit an unsafe state which may result in an unrecoverable failure.
 
@@
 $\mathcal{F}_{\langle I,F \rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
-
 \item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) * \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}*\mathcal{F}_{\langle I,F \rangle}(c_2)| + |\delta_{T2}*\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
-\item In this implementation we only need to divide by positive numbers(where it is needed for checking stability) \todo{so: what does that imply? pls clarify explicitly.}. 
+\item Division: the operations performed by our controllers in the FWL domain do not include division, so these bounds are inconsequential to this paper. 
 \end{enumerate}
@@
 We will use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model ($I_p \geq I_c \wedge F_p \geq F_c$).
-\todo{Should we include a discussion on the fact that the plant is physical?
-So for example, a reviewer may ask what is the meaning of the model with time derivative, with variables over a Euclidean space.
-}
 Thus any mathematical operations occurring in the digital controller will occur in the range of $\mathcal{F}_{\langle I_c,F_c \rangle}$, and all other calculations will be carried out in the range of $\mathcal{F}_{\langle I_p,F_p \rangle}$.
+The physical plant operates in the reals, which means our verification phase must account for calculation errors in the model.
 
@@
 
-\todo{You mean the second one, or both? Please clarify.} We address these errors by use of a final verification check that uses interval arithmetic~\cite{moore1966interval}.
+We address this last error by use of interval arithmetic~\cite{moore1966interval} in the verification phase.
 
@@
 %
-where $\mathcal{A}=\bigcup_{k=1}^\infty (A_d-B_dK)t^k, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k(A_d-B_dK)^iB_{n}$ are abstract matrices for the closed-loop system,
-whereas the set N is non-deterministically chosen. \todo{add citation to SAS article, readers will be lost. }
+where $\mathcal{A}=\bigcup_{k=1}^\infty (A_d-B_dK)t^k, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k(A_d-B_dK)^iB_{n}$ are abstract matrices for the closed-loop system \cite{cattaruzza2015unbounded}, whereas the set N is non-deterministically chosen.
 
@@
 
-\paragraph{Illustrative Example}
-
+\subsubsection{Illustrative Example}
+%
 Let us take the Helicopter example in Table \ref{table:State-space benchmarks} with discretized dynamics

### 2017-01-25 cav2017/cav2017.tex
small edit objectives

@@
 \item[RQ1] \textbf{(CEGIS)} do the CEGIS with multi-stage 
-verification and abstraction refinement generate a FWL digital 
+verification and abstraction-based generate a FWL digital 
 controller in a reasonable amount of time?

### 2017-01-25 cav2017/cav2017.tex
some editing intro to sec 4

@@
 provide the synthesiser's general architecture, followed by describing
-two approaches that use it to automatically generate safe controllers:
+our two approaches to synthesizing safe controllers:
 the first one is a baseline approach which relies on a naive explicit

### 2017-01-25 cav2017/cav2017.tex
Ontributions

@@
 \item In this paper we extend the problem of digital control synthesis 
-  from a transfer function representation into a state space
-  representation.  This entails the verification of safety properties
-  in addition to the already existing stability conditions which is a
-  much harder problem.
+from a transfer function representation into a state space representation. 
+Such representation allows to study the  input-to-state dynamics, while 
+transfer functions represents only input-output relations and cannot be 
+enough to ensure deeper properties, e.g. the safety property.
+%
+\item We proposes a synthesis of state feedback controllers that ensures 
+safety properties, that is only  possible in state-space representation. 
+In addition to the already existing stability conditions which is a much 
+harder problem.
 %

### 2017-01-25 cav2017/cav2017.tex
intro

@@
 In this work, we propose the synthesis of \emph{safe} control algorithms for
-LTI models taking into consideration the continuous domain of the plant, 
-alongside the discrete domain of the controller, 
-as well as the hybrid elements that relate them.  
+LTI models taking into consideration the continuous dynamics of the plant, 
+alongside the discrete dynamics of the controller and the effects of its 
+implementation, as well as the hybrid elements that relate them.  
 %% In this paper, we synthesize controllers for hybrid
@@
 on linear models with known  implementation features (e.g., number of bits, fixed-point
-arithmetic), and perform 
-synthesis of safe digital controllers -- the extension to more general
-quantitative properties is left to future work.
+arithmetic), and perform synthesis of safe digital controllers, a property often 
+overlooked in feedback control synthesis, but which plays an important role 
+in real-world systems.
 

### 2017-01-25 cav2017/cav2017.tex
intro

@@
 
-We describe and evaluate two approaches for synthesising digital controllers
+We describe and evaluate two approaches for synthesizing digital controllers
 for state-space physical plants, both based on CounterExample
-Guided Inductive Synthesis (CEGIS)~\cite{sketch}.
+Guided Inductive Synthesis (CEGIS)~\cite{sketch}, performed considering deviations due the computation computations and representations of dynamics, providing sufficient conditions for sound and complete solutions.
 
@@
 %% unwinding the transition relation~\cite{cattaruzza2015unbounded}.
-\todo{We need to emphasise the derivation of errors for soundness. Can we claim completeness already?}
+%\todo{We need to emphasise the derivation of errors for soundness. Can we claim completeness already?}
 
 We provide experimental results 
-showing that both approaches are able to efficiently synthesise stable and safe controllers 
+showing that both approaches are able to efficiently synthesize stable and safe controllers 
 for a set of intricate physical plant models taken from the digital 
@@
   threshold, whilst the second one is abstraction-based and leverages
-  the concepts of abstraction refinement and acceleration to increase speed whilst retaining
-  soundness.
+  the concepts of abstraction refinement and acceleration to increase 
+  speed whilst retaining soundness. Both approaches provide sound and 
+  complete synthesis of state feedback systems considering the various
+  errors sources in the implementation of control algorithm and in the
+  computational modeling of plant dynamics.
 %

### 2017-01-25 cav2017/cav2017.tex
intro

@@
 for state-space physical plants, both based on CounterExample
-Guided Inductive Synthesis (CEGIS)~\cite{sketch}, performed considering deviations due the computation computations and representations of dynamics, providing sufficient conditions for sound and complete solutions.
+Guided Inductive Synthesis (CEGIS)~\cite{sketch}, performed considering deviations due the computation computations and representations of dynamics, providing sufficient conditions for sound and complete safe solutions for the state feedback control problem.
 

### 2017-01-25 cav2017/cav2017.tex
revised contributions

@@
 \item In this paper we extend the problem of digital control synthesis 
-  from a transfer function representation into a state space representation. 
+  from a transfer function representation into a state space one. 
   Such representation allows to study the  input-to-state dynamics, while 
@@
 \item We proposes a synthesis of state feedback controllers that ensures 
-  safety properties, that is only  possible in state-space representation. 
-  In addition to the already existing stability conditions which is a much 
-  harder problem.
+  safety properties in addition to the already existing stability conditions,
+  that is only  possible in state-space representation. 
 %

### 2017-01-25 cav2017/cav2017.tex
related work

--- 2017-01-25 cav2017/cav2017.tex
@@
 via transfer function models.  In contrast, in the current paper we consider
-a state-space representation of the physical system, which is known to be
-more general \cite{Astrom08} and allows to synthesize controllers that make
-the closed-loop system \emph{safe}.  Moreover, this work integrates an
+a state-space representation of the physical system, which is known to present
+various advantages over transfer function representation \cite{Astrom08}: (i) 
+easy to generalize for the multivariate systems (i.e., with multiple inputs 
+and outputs); (ii) shows the state-to-input relationships offering an internal 
+model of the system; and (iii) allows to synthesize control systems that ensures
+properties about the internal dynamics, e.g., to synthesize controllers that make
+the closed-loop system \emph{safe}. This work focuses in the \emph{safety} of 
+internal states, such property is usually overlooked in the previous cited 
+works, but plays an important role in real world systems, where systems states 
+cannot assume any real value. Moreover, this work integrates an
 abstraction/refinement step inside the main CEGIS loop.

### 2017-01-25 cav2017/cav2017.tex
revised contributions

@@
   from a transfer function representation into a state space one. 
-  Such representation allows to study the  input-to-state dynamics, while 
-  transfer functions represents only input-output relations and cannot be 
-  enough to ensure deeper properties, e.g. the safety property.
-%
-\item We proposes a synthesis of state feedback controllers that ensures 
-  safety properties in addition to the already existing stability conditions,
-  that is only  possible in state-space representation. 
+  Such a representation allows to study the  input-to-state dynamics, whereas
+  transfer functions only represent input-output relations and are not sufficient 
+  to ensure deeper properties, e.g. safety.
+%
+\item We proposes a synthesis of state feedback controllers that,
+  in addition to the already existing stability conditions,
+  ensures safety properties,
+  which is only  possible in the state-space representation. 
 %
@@
   the concepts of abstraction refinement and acceleration to increase 
-  speed whilst retaining soundness. Both approaches provide sound and 
-  complete synthesis of state feedback systems considering the various
-  errors sources in the implementation of control algorithm and in the
-  computational modeling of plant dynamics.
+  speed whilst retaining soundness. Both approaches provide sound
+  synthesis of state feedback systems considering the various
+  error sources in the implementation of the control algorithm and in the
+  computational modelling of plant dynamics.
 %

### 2017-01-25 cav2017/cav2017.tex
edits

@@
 As it requires explicit unfolding up to the completeness
-threshold, this approach may result in state space explosion.
+threshold, this approach may suffer from state space explosion.
 
@@
 %
-\item We proposes a synthesis of state feedback controllers that,
+\item We propose a synthesis of state feedback controllers that,
   in addition to the already existing stability conditions,

### 2017-01-25 cav2017/cav2017.tex
preliminaries

--- 2017-01-25 cav2017/cav2017.tex
@@
 \item In this paper we extend the problem of digital control synthesis 
-  from a transfer function representation into a state space one. 
+  from a transfer function representation into a state space representation. 
   Such representation allows to study the  input-to-state dynamics, while 
@@
 \item We proposes a synthesis of state feedback controllers that ensures 
-  safety properties in addition to the already existing stability conditions,
-  that is only  possible in state-space representation. 
+  safety properties, that is only  possible in state-space representation. 
+  In addition to the already existing stability conditions which is a much 
+  harder problem.
 %
@@
 and with initial states set as $x(0)$. 
-Eq.~\eqref{eq:ode} is soundly discretized in time (as shown in the Appendix) into %\textcolor{red}{What is subscript ``d''?}
+Eq.~\eqref{eq:ode} is soundly discretized in time (as shown in the Appendix~\ref{sec:appendix:LTIbackground}) into %\textcolor{red}{What is subscript ``d''?}
 %
@@
 where $k \in \mathbb N$, 
-and with initial state $x_{0}=x(0)$. $A_d$ and $B_d$ denote the discretized matrices of $A$ and $B$, the plant dynamics. 
+and with initial state $x_{0}=x(0)$. $A_d$ and $B_d$ denote the matrices that describes the discretized plant dynamics and $A$ and $B$ the continuous plant dynamics. 
 Later, we will deal with the issue of variable quantization, as introduced by the ADC/DAC conversion blocks.
@@
 Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
-Feedback architectures can be employed to affect the properties and behaviours of the continuous process (the plant).   
+Feedback architectures can be employed to manipulate the properties and behaviors of the continuous process (the plant).   
 %reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{LTI system Transformations and Equivalences} \label{sec:appendix}
+\section{LTI system Transformations and Equivalences} \label{sec:appendix:LTIbackground}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-01-25 cav2017/cav2017.tex
Sec 3.2

@@
 %reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
-We are interested in the synthesis of digital feedback, 
-as implemented on modern FPGAs or ICs. 
+We are interested in the synthesis of digital feedback control algorithm, 
+as implemented on modern FPGAs or DSPs. 
 The most basic feedback architecture is the state feedback, 
@@
 %
-Here $K \in \mathbb{R}^{m \times n}$ is a feedback gain matrix, 
+Here $K \in \mathbb{R}^{m \times n}$ is a state feedback gain matrix, 
 and $r_{k}$ is a reference signal (again digital).   
@@
 \end{align}
-The gain matrix $K$ can be set so that the closed-loop digitalized dynamics are shaped as desired, 
-for instance according to a specific stability goal or around a specific dynamical behaviour \cite{astrom1997computer}. 
+The gain matrix $K$ can be set so that the closed-loop discrete dynamics are shaped as desired, 
+for instance according to a specific stability goal or around a specific dynamical behavior \cite{astrom1997computer}. 
 As argued later in this work, we will target more complex objectives, such as quantitative safety requirements that are not typical in the digital control literature. 
@@
 
-Our algorithm to select suitable FWL word widths to model plant behaviour employs a heuristic based on user-provided controller word-width specifications.
+Our algorithm to select suitable FWL word widths to model plant behavior employs a heuristic based on user-provided controller word-width specifications.
 For the first approach, where we may need to increase the precision of the time discretization, we select the time steps for the discretizations on a similar basis.

### 2017-01-25 cav2017/cav2017.tex
sec 3.3.

@@
 picasso2002construction} introduces attractive invariant sets as a mechanism
-to bound the quantization error effect on stabilisation as an invariant set
+to bound the quantization error effect on stabilization as an invariant set
 that always converges toward the controllable set.  In a similar fashion,
@@
 
-Asymptotic stability boils down to Lyapunov stability and convergence to an
-equilibrium point~\cite{Astrom08}.  Lyapunov stability requires that model
-trajectories remain in a neighborhood of the equilibrium point.  In the case
-of closed-loop LTI models as in~\eqref{eq:closedloopss}, the equilibrium
-point is the origin (if the reference is equal to zero), or an offset
-thereof.  Here, we consider systems with a zero reference signal.
-
-A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable
+Asymptotic stability implies convergence to an equilibrium point from any states in its neighborhood.
+This stability concept is stronger than the Lyapunov and BIBO stability researched by previous works~\cite{DBLP:conf/emsoft/RavanbakhshS16,DBLP:journals/corr/AbateBCCDKK16,DBLP:conf/hybrid/RouxJG15,
+DBLP:conf/hybrid/WangGRJF16}. In the case of linear systems as 
+in~\eqref{eq:closedloopss}, the equilibrium point for zero-input 
+response is always the  origin.  Here, we consider systems with 
+a zero reference signal.
+
+A discrete-time LTI system as \eqref{eq:closedloopss} is asymptotically stable
 \textit{iff} all the roots of the characteristic polynomial (i.e., the

### 2017-01-25 cav2017/cav2017.tex
Effects on stability

@@
 specification raises a requirement on the states of the model, such that the
-feedback controller (namely the choice of the gains in $K$) must ensure that
+feedback controller (namely the choice of the gains matrix $K$) must ensure that
 the states never exit such requirement.  Note that a stable, closed-loop
@@
 Numbers outside this range cannot be represented by the domain.
-We assume no saturation (where any overflow is represented as the largest or smallest possible number), and check that overflow does not occur.
+We check that overflow does not occur.
 
@@
 
-We will use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant model ($I_p \geq I_c \wedge F_p \geq F_c$).
+We will use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant computational model ($I_p \geq I_c \wedge F_p \geq F_c$).
 Thus any mathematical operations occurring in the digital controller will occur in the range of $\mathcal{F}_{\langle I_c,F_c \rangle}$, and all other calculations will be carried out in the range of $\mathcal{F}_{\langle I_p,F_p \rangle}$.
@@
 
-We note that the effect on stability due to the fixed-word-length error is that the system may, 
-instead of converging to the desired equilibrium point, 
-converge to a neighbourhood around the desired equilibrium point (see Appendix for details). 
-However, since In this paper we require stability only as a precursor to safety, 
-it is sufficient to check the (perturbed, noisy) model converges to a point within the safe states. 
-In the following, we shall disregard these errors when we synthesise a stable controller, 
-and then verify its safety accounting for the finite-precision errors.
+Previous studies~\cite{gangli1} show that the FWL affects the poles and 
+zeros positions, degrading the closed-loop dynamics, causing steady-state 
+errors (see the Appendix~\ref{sec:appendix:LTIbackground} for details) 
+and eventually destabilizing  the system~\cite{Bessa16}. However, since 
+in this paper we require stability only as a precursor to safety, it is 
+sufficient to check the (perturbed, noisy) model converges to a point 
+within the safe states.
+
+In the following, we shall disregard these steady-state errors (caused by FWL effects)
+ when the stability is ensured by synthesis, and then verify its safety accounting for the finite-precision errors.
 

### 2017-01-25 cav2017/cav2017.tex
minor change

@@
 $$A_d = \left[\begin{array}{ccc}2.6207&-1.1793&0.65705\\2&0&0\\0&0.5&0\end{array}\right], B_d = \left [\begin{array}{c}8\\0\\0\end{array}\right]$$
-Using an initial state $\bigwedge -.9 \leq x_{0,i} \leq .9$, inputs $-10 \leq u \leq 10$, and a safety specification $\bigwedge -.92 \leq x_i \leq .92$, the {\sc synthesize} phase in Fig.~\ref{fig:CEGARIS} synthesises an initial candidate controller $K=[\begin{array}{ccc}0.24609375&-0.125&0.1484375\end{array}]$.
+Using the initial state bounds $\underline{x_{0}}=-0.9$ and $\overline{x_{0}}=0.9$, the input bounds $\underline{u}=-10$ and $\overline{u}=10$, and safety specifications 
+$\underline{x_{i}}=-0.92$ and $\overline{x_{i}}=0.92$, the {\sc synthesize} phase in Fig.~\ref{fig:CEGARIS} synthesises an initial candidate controller $K=[\begin{array}{ccc}0.24609375&-0.125&0.1484375\end{array}]$.
 Although this candidate is stable, the {\sc verify} phase finds it to be unsafe and returns a list of iterations with an example initial state that fails the safety specification

### 2017-01-25 cav2017/cav2017.tex
Benchmarks description

@@
 Table~\ref{table:State-space benchmarks} summarizes 
-all our benchmarks, which are SISO models (cf. section~\ref{sec:preliminaries}). 
-\todo{they are not: we do not have a 1d output map (SO= single output), rather get access to all variables. so the output map (C) is the identity, if you will. 
-this is a good point to clarify this, mention possible extensions to observer-based feedback architectures. }
+all our benchmarks, which are SISO models (cf.
+section~\ref{sec:preliminaries}).
+In the Table~\ref{table:State-space benchmarks}, the Inverted Pendulum appears to be a two output system but it was treated as two SISO systems during the experiments.
+For the sake of simplicity all the states measurements are assumed available.
+In practice, state estimators should be designed in order to obtain an estimate of the states from the single output.
+Further extensions of this work can include state observers synthesis.
+
+%\todo{they are not: we do not have a 1d output map (SO= single output), rather get access to all variables. so the output map (C) is the identity, if you will. 
+%this is a good point to clarify this, mention possible extensions to observer-based feedback architectures. }
 

### 2017-01-25 cav2017/cav2017.tex
Filled experimental results table.
Added results from both back-ends, as well as precision at which
controller was found.

@@
 \usepackage{cite}
+\usepackage{pifont}
 
@@
 \newcommand{\mat}[1]{\boldsymbol{#1}}
+\newcommand{\xmark}{\ding{55}}
 
@@
 control based on the pitch dimension. 
-\textit{Ball Magnetic Levitation} plant describes a physical model that keeps a 
-metal ball hanged in air via magnetic field. 
 \textit{Buck Converter} plant represents a power converter model that steps down 
@@
 %2              & 
-\begin{tabular}[c]{@{}c@{}}Aircraft \\ Pitch\\ Dynamics\end{tabular} & $\left[\begin{array}{ccc}
--0.313	& 56.7 		& 0		\\
--0.0139	& -0.426	& 0		\\
-0		& 56.7		& 0		\\
-\end{array}\right]$ & $\left[\begin{array}{c}
-0.232 \\ 0.0203 \\ 0
-\end{array}\right]$ & $\left[\begin{array}{ccc}
-1 & 0 & 0\\
-\end{array}\right]$ & 0 \\ \hline
+% \begin{tabular}[c]{@{}c@{}}Aircraft \\ Pitch\\ Dynamics\end{tabular} & $\left[\begin{array}{ccc}
+% -0.313	& 56.7 		& 0		\\
+% -0.0139	& -0.426	& 0		\\
+% 0		& 56.7		& 0		\\
+% \end{array}\right]$ & $\left[\begin{array}{c}
+% 0.232 \\ 0.0203 \\ 0
+% \end{array}\right]$ & $\left[\begin{array}{ccc}
+% 1 & 0 & 0\\
+% \end{array}\right]$ & 0 \\ \hline
 %3            & 
@@
 %4              & 
-\begin{tabular}[c]{@{}c@{}}Buck\\ Converter\end{tabular}                      & $\left[\begin{array}{cc}
-0		& -500 \\
-4545	& -1515\\
-\end{array}\right]$ & $\left[\begin{array}{c}
-125 \\ 0 \\
-\end{array}\right]$ & $\left[\begin{array}{cc}
- 0 & 1\\
-\end{array}\right]$ & 0 \\ \hline
+% \begin{tabular}[c]{@{}c@{}}Buck\\ Converter\end{tabular}                      & $\left[\begin{array}{cc}
+% 0		& -500 \\
+% 4545	& -1515\\
+% \end{array}\right]$ & $\left[\begin{array}{c}
+% 125 \\ 0 \\
+% \end{array}\right]$ & $\left[\begin{array}{cc}
+%  0 & 1\\
+% \end{array}\right]$ & 0 \\ \hline
 %5              & 
-\begin{tabular}[c]{@{}c@{}}Boost\\ Converter\end{tabular} & $\left[\begin{array}{cc}
-0		& -375 \\
-3409	& -1515\\
-\end{array}\right]$ & $\left[\begin{array}{c}
-500 \\ 0 \\
-\end{array}\right]$ &  $\left[\begin{array}{cc}
-0 & 1\\
-\end{array}\right]$  & 0        \\ \hline
+% \begin{tabular}[c]{@{}c@{}}Boost\\ Converter\end{tabular} & $\left[\begin{array}{cc}
+% 0		& -375 \\
+% 3409	& -1515\\
+% \end{array}\right]$ & $\left[\begin{array}{c}
+% 500 \\ 0 \\
+% \end{array}\right]$ &  $\left[\begin{array}{cc}
+% 0 & 1\\
+% \end{array}\right]$  & 0        \\ \hline
 %6              & 
-\begin{tabular}[c]{@{}c@{}}Buck-boost\\ Converter\end{tabular} & $\left[\begin{array}{cc}
-0		& 375 \\
--3409	& -1515\\
-\end{array}\right]$ & $\left[\begin{array}{c}
-125 \\ 0 \\
-\end{array}\right]$ & $\left[\begin{array}{cc}
-0 & 1\\
-\end{array}\right]$ & 0 \\ \hline
+% \begin{tabular}[c]{@{}c@{}}Buck-boost\\ Converter\end{tabular} & $\left[\begin{array}{cc}
+% 0		& 375 \\
+% -3409	& -1515\\
+% \end{array}\right]$ & $\left[\begin{array}{c}
+% 125 \\ 0 \\
+% \end{array}\right]$ & $\left[\begin{array}{cc}
+% 0 & 1\\
+% \end{array}\right]$ & 0 \\ \hline
 %7              & 
@@
 %16             & 
-\begin{tabular}[c]{@{}c@{}}USCG \\ Cutter\\ Tampa\\ Heading\\ Angle\end{tabular} & $\left[\begin{array}{ccc}
--0.271		& -0.05336	& 0	\\
-0.03125		& 0			& 0			\\
-0			& 0.01562 	& 0			\\	
-\end{array}\right]$ & $\left[\begin{array}{c}
-1 \\ 0 \\ 0
-\end{array}\right]$ & $\left[\begin{array}{ccc}
-0	& -0.5888	& -0.2562 \\
-\end{array}\right]$ & 0 \\ \hline
+% \begin{tabular}[c]{@{}c@{}}USCG \\ Cutter\\ Tampa\\ Heading\\ Angle\end{tabular} & $\left[\begin{array}{ccc}
+% -0.271		& -0.05336	& 0	\\
+% 0.03125		& 0			& 0			\\
+% 0			& 0.01562 	& 0			\\	
+% \end{array}\right]$ & $\left[\begin{array}{c}
+% 1 \\ 0 \\ 0
+% \end{array}\right]$ & $\left[\begin{array}{ccc}
+% 0	& -0.5888	& -0.2562 \\
+% \end{array}\right]$ & 0 \\ \hline
 \end{tabular}
@@
 \begin{table}
-
-\begin{tabular}{| r | c | l | r | r |}
+\centering
+\begin{tabular}{| r | c | c | r | c | r |}
 \hline
-\# & Benchmark  & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & time for approach 1  & time for approach 2 \\\hline
-1 & Ball Maglev & & & \\
-2 & Cruise Control & & & \\
-3 & DC Motor& & & \\
-4 & Helicopter & & & \\
-5 & Inverted Pendulum 1& & & \\
-6 & Inverted Pendulum 2& & & \\
-7 & Magnetic Pointer& & & \\
-8 & Magnetic Suspension& & & \\
-9 & Pendulum& & & \\
-10 & Suspension& & & \\
-11 & Tape Driver & & & \\
-12 & Uscgtamper & & & \\
-13 & Satellite & & & \\\hline
+\# & Benchmark  & \multicolumn{2}{|c|}{Multi-stage}                 & \multicolumn{2}{|c|}{Abstraction} \\
+   &            & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Runtime & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Runtime \\\hline
+1  & Cruise Control      & 8,16   & 6875   & 16,16  & 241    \\
+2  & DC Motor            & 8,16   & 8103   & 20,20  & 5376   \\
+3  & Helicopter          & \xmark & \xmark & 16,16  & 2120   \\
+4  & Inverted Pendulum   & 8,16   & 7813   & 16,16  & 387    \\
+5  & Magnetic Pointer    & \xmark & \xmark & 28,28  & 132845 \\
+6  & Magnetic Suspension & 12,20  & 8727   & 32,32  & 7854   \\
+7  & Pendulum            & 8,16   & 9008   & 20,20  & 1150   \\
+8  & Suspension          & 12,20  & 49410  & \xmark & \xmark \\
+9  & Tape Driver         & 8,16   & 9177   & \xmark & \xmark \\
+10 & Satellite           & 8,16   & 8975   & \xmark & \xmark \\\hline
 

### 2017-01-25 cav2017/cav2017.tex
Updated experimental description.
Updated discusison of experimental results, confirming our research
questions.

@@
 We have conducted the experimental evaluation on a 12-core 2.40 GHz
-Intel Xeon E5-2440 with 96 GB of RAM and Linux OS.
-
-\textcolor{red}{Pascal, Can you please describe our we measure time?
-All times given are wall clock time in seconds as measured by the UNIX date command.}
-
-\textcolor{red}{Pascal, can you please describe the timeout?}
-
+Intel Xeon E5-2440 with 96 GB of RAM and Linux OS. We used the Linux \emph{times} command
+to measure CPU time used for each benchmark. The experimental runtime was limited to
+one hour per benchmark.
 %
@@
 Here \textit{Benchmark} is the name of the employed
-benchmark, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used to model the plant, while \textit{Time}
-is the total time (in seconds) required to synthesize a stable controller
-for the given plant, for approach 1 and approach 2. The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is always chosen to be $I_c = 8, F_c = 8$.
-
-For the majority of our benchmarks, the conjecture stands that the Acceleration back-end is faster than the basic multi-staged verification approach.
-However, it does fail to find solutions to XXX benchmarks, where the numbers given in the discretization matrices are really small.
-
-The basic multi-staged verification approach finds X / X benchmarks, albeit in an expected slower time. The solutions that are not found are due to time-out or XXXX
+benchmark, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used
+to model the plant, while \textit{Time}
+is the total time (in milliseconds) required to synthesize a stable controller
+for the given plant, for CEGIS with multi-staged verification as well as
+abstraction-based CEGIS. The precision for the controller,
+$\mathcal{F}_{\langle I_c,F_c \rangle}$, is always chosen to be $I_c = 8, F_c = 8$.
+
+For the majority of our benchmarks, the conjecture stands that the abstraction-based back-end
+is faster than the basic multi-staged verification approach. However, it does fail to
+find solutions to 3 benchmarks, as compared to 2 with the multi-staged back-end, where
+the numbers given in the discretization matrices are too small. In direct comparison the
+abstraction-based is able to find a solution in approximately 35\% of the time required
+using the multi-staged back-end. The two back-ends complement each other well in their
+benchmark coverage and together solve all benchmarks provided in the set.
 
@@
 \hline
-\# & Benchmark  & \multicolumn{2}{|c|}{Multi-stage}                 & \multicolumn{2}{|c|}{Abstraction} \\
-   &            & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Runtime & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Runtime \\\hline
+\# & Benchmark  & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
+   &            & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
 1  & Cruise Control      & 8,16   & 6875   & 16,16  & 241    \\
@@
 \end{tabular}
-\caption{Experimental results \label{tab:results}}
+\caption{Experimental results with runtime in milliseconds \label{tab:results}}
 \end{table}
 
-he median runtime for our benchmark set is XXXX.  Overall,
-the average synthesis time amounts to approximately XXX minutes.  We
+The median runtime for our benchmark set is 7.9\,s.  Overall,
+the average synthesis time amounts to approximately 17.2\,s.  We
 consider these times short enough to be of practical use to control

### 2017-01-25 cav2017/cav2017.tex
Added link to benchmarks on anonymous Google Drive.
Added full benchmark environment, with generated logs, into an archive and
shared on a Google Drive.

@@
 benchmarks and the tool, is provided in the
-footnote.\footnote{\url{url.here.}}
+footnote.\footnote{\url{https://drive.google.com/open?id=0ByIexo3Z5N91eDludEdWdWxfV1E}}
 

### 2017-01-25 cav2017/cav2017.tex
Removed unused benchmarks.
Removed benchmarks which were never discretized or do not have a proven
solution.

@@
 velocity of a DC Motor, respectively. 
-\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and 
-control based on the pitch dimension. 
-\textit{Buck Converter} plant represents a power converter model that steps down 
-voltage from the supply to the load while stepping up current. 
-\textit{Boost Converter} plant also represents a power converter model, but
-it steps up voltage from the supply to the load while stepping down current. 
-\textit{Buck-boost Converter} plant represents a converter model that has an output 
-voltage magnitude, which is either greater than or less than the input voltage magnitude.
-
 \textit{Automotive Cruise System} plant represents the speed of a motor vehicle. 
@@
 on a storage device in the computer.
-\textit{USCG Cutter Tampa Heading Angle} plant presents a physical model 
-for the yaw angle dynamics of a US warship USCG Cutter Tampa.
 

### 2017-01-25 cav2017/cav2017.tex
Address comment about single initial state in synth phase

@@
 
- \todo{unclear next: it seems like to select a single initial state here, rather than considering the set thereof - clarify. also, clarify relationship btw k and soundness. }
+ %\todo{unclear next: it seems like to select a single initial state here, rather than considering the set thereof - clarify. also, clarify relationship btw k and soundness. }
 Regarding the second requirement, we synthesize a safe controller by unwinding the transition system
-$k$ steps and by picking a controller $K$ and an initial state, such that the states at each step do
-not violate the safety criteria. This is sound if the current $k$ is below the
+$k$ steps and by picking a controller $K$ and a single initial state,  such that the states at each step do
+not violate the safety criteria.
+That is, we ask the bounded model checker if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states.
+This is sound if the current $k$ is below the
 completeness threshold, which we assume to be true in the {\sc synthesize} phase.
@@
 \State assert($ \underline{u}  \leq u \leq \overline{u}$)
-  \State assert($ \underline{x_0}  \leq x_0 \leq \overline{x_0}$)
+ \State set $x_0$ to be a vertex state, e.g., $[\underline{x_0},\underline{x_0}]$	
+\While ($c=0; c < 2^{Num_States}; c++$)
+  %\State assert($ \underline{x_0}  \leq x_0 \leq \overline{x_0}$)
 	\While{$i=0; i< k; i++$}
@@
   	\EndWhile
+  	\State set $x_0$ to be a new vertex state
+  	\EndWhile
   %\State Return $K$
@@
 \item The first {\sc verify} stage, {\sc safety}, checks that candidate
-solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
+solution $K$, which we synthesised to be safe for at least one initial state, is safe for \emph{all} possible initial states, i.e., does not reach an unsafe
 state within $k$ steps where we assume $k$ to be under the completeness threshold. 

### 2017-01-25 cav2017/cav2017.tex
Pessoa rewording

@@
 
-The tool Pessoa~\cite{mazo2010pessoa} is a MatLab toolbox that synthesizes
-correct-by-design embedded control software.  It is based on the description
+The tool Pessoa~\cite{mazo2010pessoa} synthesizes
+correct-by-design embedded control software, in a Matlab ToolBox.  It is based on the description
 of a physical system as an equivalent finite-state machine and on the
@@
 embedded controller software for a range of properties.
+The embedded controller software can be more complicated than
+the state feedback control we synthesised, and the properties 
+available cover more detail.
 %based on a safety specification over state values, as well as specification on characteristic functions of the controller. 

### 2017-01-25 cav2017/cav2017.tex
reviewed introduction and related work

@@
 control literature: the median runtime for our benchmark
-set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
-than \textcolor{red}{$XXX$} seconds.
+set is $7.9$s, i.e., most controllers can be synthesized in less
+than $17.2$ seconds.
 
@@
 transfer functions, by exploiting bit-accurate verification of
-software-implemented digital controllers~\cite{Bessa16}.  While this work
+software-implemented digital controllers~\cite{IsmailBCFF15,Bessa16}.  While this work
 also makes use of a CEGIS-based technique, the approach is restricted to

### 2017-01-25 cav2017/cav2017.tex
replaced "e.g." by "e.g.,"

@@
   transfer functions represents only input-output relations and cannot be 
-  enough to ensure deeper properties, e.g. the safety property.
+  enough to ensure deeper properties, e.g., the safety property.
 %
@@
 In particular, Jury stability test is already explained in the control system 
-literature ({\it e.g.}~\cite{fadali}). This study, however, limits itself to 
+literature ({\it e.g.},~\cite{fadali}). This study, however, limits itself to 
 explain the encoding of Jury's criterion for the formal synthesis purpose. 

### 2017-01-25 cav2017/cav2017.tex
typo in abstract

@@
 stabilizes the system under some restrictions given by the safety of the
-reach space.  Safety is verfied iether via BMC or abstract acceleration; if
+reach space.  Safety is verified either via BMC or abstract acceleration; if
 the verification step fails, we generate an alternative controller by

### 2017-01-25 cav2017/cav2017.tex
reword - repetition in into

@@
 on linear models with known  implementation features (e.g., number of bits, fixed-point
-arithmetic), and perform synthesis of safe digital controllers, a property often 
+arithmetic). We specify the safety requirement over the state space. This is a property often 
 overlooked in feedback control synthesis, but which plays an important role 

### 2017-01-25 cav2017/cav2017.tex
paper beautification

--- 2017-01-25 cav2017/cav2017.tex
@@
 %-------------------------------
-\section{Related work}
-\label{sec:relw}
+\subsection*{Related work}
+%\label{sec:relw}
 %-------------------------------
@@
 
-We illustrate our approach with \todo{what example is this?} an example,
+We illustrate our approach with an example,
 extracted from the literature~\cite{Franklin15}.
@@
 In the subsequent iteration, the synthesizer is unable to find further 
-suitbale candidates and it returns UNSAT, meaning that the current precision is
+suitable candidates and it returns UNSAT, meaning that the current precision is
 insufficient.  Consequently, we increase the precision to $I_p=17$,
@@
 \end{tabular}
-\caption{Experimental results with runtime in milliseconds \label{tab:results}}
+\caption{Experimental results with runtime in milliseconds. \label{tab:results}}
 \end{table}

### 2017-01-25 cav2017/cav2017.tex
clarification of this initial state thingy

--- 2017-01-25 cav2017/cav2017.tex
@@
 whilst remaining safe for a 
-pre-selected time horizon; then, it verifies its potential safety by unfolding
-the dynamics of the system and checking for a {\em completeness threshold}, i.e.,
+pre-selected time horizon and a single initial state; then, it verifies its potential safety by unfolding
+the dynamics of the system, considering the full hyper-cube of initial states, and checking for a {\em completeness threshold}, i.e.,
 the number of iterations required to sufficiently unwind

### 2017-01-25 cav2017/cav2017.tex
wordings Pessoa related work

@@
 The tool Pessoa~\cite{mazo2010pessoa} synthesizes
-correct-by-design embedded control software, in a Matlab ToolBox.  It is based on the description
-of a physical system as an equivalent finite-state machine and on the
+correct-by-design embedded control software, in a Matlab ToolBox.  It is based on the abstraction
+of a physical system to an equivalent finite-state machine and on the
 computation of reachability properties over the finite-state machine.  Based

### 2017-01-25 cav2017/cav2017.tex
grammar

@@
 properties about the internal dynamics, e.g., to synthesize controllers that make
-the closed-loop system \emph{safe}. This work focuses in the \emph{safety} of 
+the closed-loop system \emph{safe}. This work focuses on the \emph{safety} of 
 internal states, such property is usually overlooked in the previous cited 

### 2017-01-25 cav2017/cav2017.tex
paper beautification

--- 2017-01-25 cav2017/cav2017.tex
@@
 
-We describe and evaluate two approaches for synthesizing digital controllers
-for state-space physical plants, both based on CounterExample
-Guided Inductive Synthesis (CEGIS)~\cite{sketch}, performed considering deviations due the computation computations and representations of dynamics, providing sufficient conditions for sound and complete safe solutions for the state feedback control problem.
+We describe and evaluate two approaches for synthesizing digital controllers for state-space physical plants, 
+both based on the CounterExample Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use for program synthesis.   
+We provide two alternative automated procedures to synthesise safe digital state-feedback controls, 
+and alongside completeness we prove their soundness by encompassing errors due to digitalisation and quantisation effects that are present in the digital controller interacting with the continuous plant.
+% computations and representations of dynamics, providing sufficient conditions for sound and complete safe solutions for the state feedback control problem.
 

### 2017-01-25 cav2017/cav2017.tex
write initial version of the conclusion

--- 2017-01-25 cav2017/cav2017.tex
@@
 stabilizes the system under some restrictions given by the safety of the
-reach space.  Safety is verified either via BMC or abstract acceleration; if
+reach space.  Safety is verfied iether via BMC or abstract acceleration; if
 the verification step fails, we generate an alternative controller by
@@
 on linear models with known  implementation features (e.g., number of bits, fixed-point
-arithmetic). We specify the safety requirement over the state space. This is a property often 
+arithmetic), and perform synthesis of safe digital controllers, a property often 
 overlooked in feedback control synthesis, but which plays an important role 
@@
 whilst remaining safe for a 
-pre-selected time horizon and a single initial state; then, it verifies its potential safety by unfolding
-the dynamics of the system, considering the full hyper-cube of initial states, and checking for a {\em completeness threshold}, i.e.,
+pre-selected time horizon; then, it verifies its potential safety by unfolding
+the dynamics of the system and checking for a {\em completeness threshold}, i.e.,
 the number of iterations required to sufficiently unwind
@@
 %-------------------------------
-\subsection*{Related work}
-%\label{sec:relw}
+\section{Related work}
+\label{sec:relw}
 %-------------------------------
@@
 The tool Pessoa~\cite{mazo2010pessoa} synthesizes
-correct-by-design embedded control software, in a Matlab ToolBox.  It is based on the abstraction
-of a physical system to an equivalent finite-state machine and on the
+correct-by-design embedded control software, in a Matlab ToolBox.  It is based on the description
+of a physical system as an equivalent finite-state machine and on the
 computation of reachability properties over the finite-state machine.  Based
@@
 
-We illustrate our approach with an example,
+We illustrate our approach with \todo{what example is this?} an example,
 extracted from the literature~\cite{Franklin15}.
@@
 In the subsequent iteration, the synthesizer is unable to find further 
-suitable candidates and it returns UNSAT, meaning that the current precision is
+suitbale candidates and it returns UNSAT, meaning that the current precision is
 insufficient.  Consequently, we increase the precision to $I_p=17$,
@@
 \end{tabular}
-\caption{Experimental results with runtime in milliseconds. \label{tab:results}}
+\caption{Experimental results with runtime in milliseconds \label{tab:results}}
 \end{table}
@@
 %-------------------------------
+
+We have presented two approaches to synthesize state feedback controllers 
+that ensure both stability and safety over the state-space representation.
+The first approach relies on explicit unfolding of the system's dynamics 
+up to the completeness threshold, whilst the second one applies abstraction 
+refinement and acceleration to increase speed whilst retaining soundness.
+Both approaches are novel in the control system literature in that it puts
+forward a fully automated synthesis approach that is algorithmically and
+numerically sound, considering the various error sources in the implementation 
+of the control algorithm and in the computational modeling of plant dynamics.
+Our experimental results show that both approaches are able
+to synthesize stable controllers in most benchmarks within a reasonable
+amount of time fully automatically.  In particular, both approaches
+complement each other in the benchmark coverage and together 
+solve all benchmarks provided in the set.
+Future work will be the extension of these approaches to consider performance 
+requirements while synthesizing digital controllers.
 

### 2017-01-25 cav2017/cav2017.tex

@@
 
+We have presented two approaches to synthesize state feedback controllers 
+that ensure both stability and safety over the state-space representation.
+The first approach relies on explicit unfolding of the system's dynamics 
+up to the completeness threshold, whilst the second one applies abstraction 
+refinement and acceleration to increase speed whilst retaining soundness.
+Both approaches are novel in the control system literature in that it puts
+forward a fully automated synthesis approach that is algorithmically and
+numerically sound, considering the various error sources in the implementation 
+of the control algorithm and in the computational modeling of plant dynamics.
+Our experimental results show that both approaches are able
+to synthesize stable controllers in most benchmarks within a reasonable
+amount of time fully automatically.  In particular, both approaches
+complement each other in the benchmark coverage and together 
+solve all benchmarks provided in the set.
+Future work will be the extension of these approaches to consider performance 
+requirements while synthesizing digital controllers.
+
 \newpage

### 2017-01-25 cav2017/cav2017.tex
Added citation for numeric representation, also clarified DSP

@@
 We are interested in the synthesis of digital feedback control algorithm, 
-as implemented on modern FPGAs or DSPs. 
+as implemented on modern FPGAs or Digital Signal Processorss. 
 The most basic feedback architecture is the state feedback, 
@@
 which performs operations in the domain of fixed-point numbers. 
-In this section we formally outline the errors introduced by the fixed-point representation of numbers. 
+In this section we formally outline the errors introduced by the fixed-point representation of numbers~\cite{DBLP:conf/arith/BrainTRW15}. 
 % 

### 2017-01-25 cav2017/cav2017.tex
reviewed 5 Conclusions
reviewed 4.4 Threats to validity
+todo

@@
 We provide two alternative automated procedures to synthesise safe digital state-feedback controls, 
-and alongside completeness we prove their soundness by encompassing errors due to digitalisation and quantisation effects that are present in the digital controller interacting with the continuous plant.
+and alongside completeness \todo{are we actually complete?
+for instance, abstraction refinement might not be successful (we do TO)} we prove their soundness by encompassing errors due to digitalisation and quantisation effects that are present in the digital controller interacting with the continuous plant.
 % computations and representations of dynamics, providing sufficient conditions for sound and complete safe solutions for the state feedback control problem.
@@
 Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalize to other benchmarks.
-
+%
 Our algorithm to select suitable FWL word widths to model plant behavior employs a heuristic based on user-provided controller word-width specifications.
@@
 This works sufficiently well for our benchmarks, but performance may suffer in some cases, for example if the completeness threshold is high.
-
+%
 The performance gain from abstract acceleration may not hold for more complex properties than stability, for instance ``eventually always reaches a certain safe set''.
@@
 amount of time fully automatically.  In particular, both approaches
-complement each other in the benchmark coverage and together 
-solve all benchmarks provided in the set.
+complement each other and together solve all benchmarks provided in the set.
 Future work will be the extension of these approaches to consider performance 

### 2017-01-25 cav2017/cav2017.tex
paper beautification

--- 2017-01-25 cav2017/cav2017.tex
@@
 in this paper we require stability only as a precursor to safety, it is 
-sufficient to check the (perturbed, noisy) model converges to a point 
-within the safe states.
+sufficient to check that the (perturbed, noisy) model converges to a neighbourhood of the equilibrium within the safe set.
 
@@
 \begin{align*}
-x_k   &= (A_d - B_d K)^k x = (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i \\
-      &= \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i = \sum_{i=1}^{2^n} \alpha_i x_k^i, 
+x_k   &= (A_d - B_d K)^k x = (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i 
+      = \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i = \sum_{i=1}^{2^n} \alpha_i x_k^i, 
  \end{align*}     
-where $x_k^i$ denotes the trajectories obtained from the single vertexes $v_i$.
+where $x_k^i$ denotes the trajectories obtained from the single vertex $v_i$. 
+We conclude that any $k$-step trajectory is encompassed, within a convex set, by those generated from the vertices.
 
@@
 completeness threshold $\overline{k}$ for the current candidate $K$
-and check that $k{\leq}\overline{k}$. This is done according to the following argument.
+and check that $k{\leq}\overline{k}$. This is done according to the following argument, depicted in Fig \ref{fig:ct}.
 
@@
 Assume the closed-loop matrix eigenvalues are not repeated (which is sensible to do, since we select them). 
-The distance of trajectories from the reference point (in this case the origin) decreases over time within subspaces related to real-valued eigenvalues. 
-However, this in general not the case when dealing with complex eigenvalues.  
-Consider the matrix $(A_d - B_d K)$, which updates the states every time step, and select eigenvalue with smallest (non trivial) imaginary value.  
-call such value $\vartheta$. 
-At every time interval $kT_s, (k+1)T_s$ ($T_s$ being the sampling time), 
+The distance of trajectories from the reference point (in this case the origin) decreases over time within subspaces related to real-valued eigenvalues;  
+however, this in general not the case when dealing with complex eigenvalues.  
+Consider the closed-loop matrix, which updates the states every discrete time step, 
+and select the eigenvalue with smallest (non trivial) imaginary value -- call such value $\vartheta$. 
+At every consecutive time steps $kT_s, (k+1)T_s$ ($T_s$ being the sampling time), 
 the dynamics projected on the corresponding eigenspace rotate of $\vartheta T_s$ radiants.  
-So surely taking $k$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, 
-after $k$ steps we have completed a rotation. 
-This is the completeness threshold.
+So taking $k$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, 
+surely after $k$ steps we have completed a full rotation, which results in a point that is closer to the origin. 
+This $k$ is then taken to be the completeness threshold.
 
@@
 \caption{Completeness threshold for multi-staged verification.}
+\label{fig:ct}
 \end{figure*}
@@
 
-We have presented two approaches to synthesize state feedback controllers 
-that ensure both stability and safety over the state-space representation.
-The first approach relies on explicit unfolding of the system's dynamics 
-up to the completeness threshold, whilst the second one applies abstraction 
-refinement and acceleration to increase speed whilst retaining soundness.
-Both approaches are novel in the control system literature in that it puts
-forward a fully automated synthesis approach that is algorithmically and
-numerically sound, considering the various error sources in the implementation 
-of the control algorithm and in the computational modeling of plant dynamics.
-Our experimental results show that both approaches are able
-to synthesize stable controllers in most benchmarks within a reasonable
-amount of time fully automatically.  In particular, both approaches
-complement each other in the benchmark coverage and together 
-solve all benchmarks provided in the set.
-Future work will be the extension of these approaches to consider performance 
-requirements while synthesizing digital controllers.
-
 \newpage

### 2017-01-25 cav2017/cav2017.tex

@@
 %-------------------------------
+
+We have presented two approaches to synthesize state feedback controllers 
+that ensure both stability and safety over the state-space representation.
+The first approach relies on explicit unfolding of the system's dynamics 
+up to the completeness threshold, whilst the second one applies abstraction 
+refinement and acceleration to increase speed whilst retaining soundness.
+Both approaches are novel in the control system literature in that it puts
+forward a fully automated synthesis approach that is algorithmically and
+numerically sound, considering the various error sources in the implementation 
+of the control algorithm and in the computational modeling of plant dynamics.
+Our experimental results show that both approaches are able
+to synthesize stable controllers in most benchmarks within a reasonable
+amount of time fully automatically.  In particular, both approaches
+complement each other and together solve all benchmarks provided in the set.
+Future work will be the extension of these approaches to consider performance 
+requirements while synthesizing digital controllers.
 

### 2017-01-25 cav2017/cav2017.tex
replace : with words in numerical representation

@@
 Let $x$ be a real number, and $\mathcal{F}_{\langle I,F \rangle}(x)$ be the same number represented in a fixed-point domain as above. 
-Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T : \delta_T=x\ \%_{c_m}\ \tilde x$, where $\%_{c_m}$ is the modulus operation performed on the last bit.
+Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the error $ \delta_T=x\ \%_{c_m}\ \tilde x$, and $\%_{c_m}$ is the modulus operation performed on the last bit.
 
@@
 \item Addition/Subtraction: these operations only propagate errors coming from truncation of the operands, namely 
-$\mathcal{F}_{\langle I,F \rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
-\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) * \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}*\mathcal{F}_{\langle I,F \rangle}(c_2)| + |\delta_{T2}*\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
+$\mathcal{F}_{\langle I,F \rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3$ with $|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
+\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) * \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3| \leq |\delta_{T1}*\mathcal{F}_{\langle I,F \rangle}(c_2)| + |\delta_{T2}*\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
 \item Division: the operations performed by our controllers in the FWL domain do not include division, so these bounds are inconsequential to this paper. 

### 2017-01-25 cav2017/cav2017.tex
remove extensions from appendix

@@
 
-%-------------------------------
-\section{Extensions}
-\label{sec:extensions}
-%-------------------------------
-
-%-------------------------------
-\subsection{LTI systems with output} 
-\label{ssec:LTI}
-%-------------------------------
-
-LTI models in the form: 
-%
-\begin{align}
-\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
-\vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
-\end{align}
-\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
-$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
-a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
-(as shown in the appendix) into
-%
-\begin{align}
-\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
-\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
-\end{align}
+% %-------------------------------
+% \section{Extensions}
+% \label{sec:extensions}
+% %-------------------------------
+
+% %-------------------------------
+% \subsection{LTI systems with output} 
+% \label{ssec:LTI}
+% %-------------------------------
+
+% LTI models in the form: 
+% %
+% \begin{align}
+% \dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
+% \vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
+% \end{align}
+% \noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
+% $\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
+% a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
+% (as shown in the appendix) into
+% %
+% \begin{align}
+% \vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
+% \vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
+% \end{align}
 %

### 2017-01-25 cav2017/cav2017.tex
replace "its states" with x

@@
 The models we consider have two sources of error due to numeric representation. 
-The first is the numeric error introduced by the fixed-point numbers employed to model the plant, i.e., to represent the plant dynamics $A_d$, $B_d$ and its states. 
+The first is the numeric error introduced by the fixed-point numbers employed to model the plant, i.e., to represent the plant dynamics $A_d$, $B_d$ and $x_k$. 
 The second is the quantization error introduced by the digital controller, 

### 2017-01-25 cav2017/cav2017.tex
paper beautification

--- 2017-01-25 cav2017/cav2017.tex
@@
 control literature: the median runtime for our benchmark
-set is $7.9$s, i.e., most controllers can be synthesized in less
+set is $7.9$ seconds, and most controllers can be synthesized in less
 than $17.2$ seconds.
@@
 \end{enumerate}
+
+\todo{Have we clarified anywhere the time domain of validity of our claims? CT vs DT? }
 
@@
 %% and $\overline{x_0}$, $\underline{x_0}$, respectively.
-We refer to these constraints as $\phi_{init}$:
+We refer to these constraints as $\phi_{init}$: \todo{input constraints should not be called 'init'}
 $$\phi_{init} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} 
@@
 Let $x$ be a real number, and $\mathcal{F}_{\langle I,F \rangle}(x)$ be the same number represented in a fixed-point domain as above. 
-Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the error $ \delta_T=x\ \%_{c_m}\ \tilde x$, and $\%_{c_m}$ is the modulus operation performed on the last bit.
+Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T : \delta_T=x\ \%_{c_m}\ \tilde x$, where $\%_{c_m}$ is the modulus operation performed on the last bit.
 
@@
 \item Addition/Subtraction: these operations only propagate errors coming from truncation of the operands, namely 
-$\mathcal{F}_{\langle I,F \rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3$ with $|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
-\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) * \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3| \leq |\delta_{T1}*\mathcal{F}_{\langle I,F \rangle}(c_2)| + |\delta_{T2}*\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
+$\mathcal{F}_{\langle I,F \rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
+\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) * \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3 :|\delta_3| \leq |\delta_{T1}*\mathcal{F}_{\langle I,F \rangle}(c_2)| + |\delta_{T2}*\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
 \item Division: the operations performed by our controllers in the FWL domain do not include division, so these bounds are inconsequential to this paper. 

### 2017-01-25 cav2017/cav2017.tex
removed continuous time related stuff from the appendix

@@
 \end{remark}
- Since \eqref{eq:discretization} is a bi-simulation of \eqref{eq:ode}, we may use the semantics in section \ref{sec:model_semantics} to model continuous dynamical systems.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Overapproximating continuous space dynamics using discrete models}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-Let us recall equation \ref{eq:discretize}. The discrete representation of the system dynamics discretized with sample time $T_1$ is ruled by the formula
-$\vec{A}_1 = e^{\vec{A} T_1}$. From matrix theory, we have 
-\begin{equation}
-\vec{A}_1 = \mat{S}_1\mat{J}_1\mat{S}_1^{-1}= \mat{S}_1e^{\mat{J} T_1}\mat{S}_1^{-1}.
-\end{equation}
-Let $\mat{J}$ be a diagonal matrix, such that ${\lambda_1}_i=e^{\lambda_i T_1}, \forall \lambda \in \mat{J}$.
-Let us now take a different sample rate $T_2$, such that ${\lambda_2}_i=e^{\lambda_i T_2}, \forall \lambda \in \mat{J}$. We can then say that 
-\begin{equation}
-{\lambda_2}_i=e^{\lambda_i T_1 T_2/T_1}={\lambda_1}_i^{T_2/T_1} \Rightarrow A_2=A_1^{\frac{T_2}{T_1}}
-\end{equation}
-We have also shown in the previous section that $x_k=A^nx_0$ is a witness of $x(t): \dot{x}(t)=Ax(t)$ at time $kT_s$.
+%  Since \eqref{eq:discretization} is a bi-simulation of \eqref{eq:ode}, we may use the semantics in section \ref{sec:model_semantics} to model continuous dynamical systems.
+
+% %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+% \subsection{Overapproximating continuous space dynamics using discrete models}
+% %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+% Let us recall equation \ref{eq:discretize}. The discrete representation of the system dynamics discretized with sample time $T_1$ is ruled by the formula
+% $\vec{A}_1 = e^{\vec{A} T_1}$. From matrix theory, we have 
+% \begin{equation}
+% \vec{A}_1 = \mat{S}_1\mat{J}_1\mat{S}_1^{-1}= \mat{S}_1e^{\mat{J} T_1}\mat{S}_1^{-1}.
+% \end{equation}
+% Let $\mat{J}$ be a diagonal matrix, such that ${\lambda_1}_i=e^{\lambda_i T_1}, \forall \lambda \in \mat{J}$.
+% Let us now take a different sample rate $T_2$, such that ${\lambda_2}_i=e^{\lambda_i T_2}, \forall \lambda \in \mat{J}$. We can then say that 
+% \begin{equation}
+% {\lambda_2}_i=e^{\lambda_i T_1 T_2/T_1}={\lambda_1}_i^{T_2/T_1} \Rightarrow A_2=A_1^{\frac{T_2}{T_1}}
+% \end{equation}
+% We have also shown in the previous section that $x_k=A^nx_0$ is a witness of $x(t): \dot{x}(t)=Ax(t)$ at time $kT_s$.
 Applying this notion to multiple sample times, we can state that $x_{k_i}=A_i^nx_0$ are a set of witnesses at times $kT_i$, and by extension the set $\{x=A_i^nx_0 : \forall n \in \mathbb{R} \}$ witnesses all states visited by the continuous system in time $t \in [0,\infty)$.
 This applies to any arbitrary sample time $T_i$.
-Since the controller output is fed to a Zero Order Holder, the progression of the system between times $kT_s$ and $(k+1)T_s$ is $\mat{A}^n\vec{x}_k+\mat{B}\vec{u}_k : n \in (0,1)$.
+% Since the controller output is fed to a Zero Order Holder, the progression of the system between times $kT_s$ and $(k+1)T_s$ is $\mat{A}^n\vec{x}_k+\mat{B}\vec{u}_k : n \in (0,1)$.
 We therefore obtain a reach tube for the continuous dynamics of a time sampled system to be contained within the abstract reach tube $\mathcal{A}^1\mathcal{M}X_0+\mathcal{BK}^1\mathcal{M}X_0=\mathcal{M}X_0$

### 2017-01-25 cav2017/cav2017.tex
moved table "Benchmarks for State-Space Physical Plants" to appendix

--- 2017-01-25 cav2017/cav2017.tex
@@
 
+\renewcommand{\baselinestretch}{0.975}
 \newcommand{\addtodo}[1]{{\color{red} TODO: #1}}
@@
 We provide two alternative automated procedures to synthesise safe digital state-feedback controls, 
-and alongside completeness \todo{are we actually complete?
-for instance, abstraction refinement might not be successful (we do TO)} we prove their soundness by encompassing errors due to digitalisation and quantisation effects that are present in the digital controller interacting with the continuous plant.
+and alongside completeness we prove their soundness by encompassing errors due to digitalisation and quantisation effects that are present in the digital controller interacting with the continuous plant.
 % computations and representations of dynamics, providing sufficient conditions for sound and complete safe solutions for the state feedback control problem.
@@
 control literature: the median runtime for our benchmark
-set is $7.9$ seconds, and most controllers can be synthesized in less
+set is $7.9$s, i.e., most controllers can be synthesized in less
 than $17.2$ seconds.
@@
 \end{enumerate}
-
-\todo{Have we clarified anywhere the time domain of validity of our claims? CT vs DT? }
 
@@
 %% and $\overline{x_0}$, $\underline{x_0}$, respectively.
-We refer to these constraints as $\phi_{init}$: \todo{input constraints should not be called 'init'}
+We refer to these constraints as $\phi_{init}$:
 $$\phi_{init} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} 
@@
 in this paper we require stability only as a precursor to safety, it is 
-sufficient to check that the (perturbed, noisy) model converges to a neighbourhood of the equilibrium within the safe set.
+sufficient to check the (perturbed, noisy) model converges to a point 
+within the safe states.
 
@@
 \begin{align*}
-x_k   &= (A_d - B_d K)^k x = (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i 
-      = \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i = \sum_{i=1}^{2^n} \alpha_i x_k^i, 
+x_k   &= (A_d - B_d K)^k x = (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i \\
+      &= \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i = \sum_{i=1}^{2^n} \alpha_i x_k^i, 
  \end{align*}     
-where $x_k^i$ denotes the trajectories obtained from the single vertex $v_i$. 
-We conclude that any $k$-step trajectory is encompassed, within a convex set, by those generated from the vertices.
+where $x_k^i$ denotes the trajectories obtained from the single vertexes $v_i$.
 
@@
 completeness threshold $\overline{k}$ for the current candidate $K$
-and check that $k{\leq}\overline{k}$. This is done according to the following argument, depicted in Fig \ref{fig:ct}.
+and check that $k{\leq}\overline{k}$. This is done according to the following argument.
 
@@
 Assume the closed-loop matrix eigenvalues are not repeated (which is sensible to do, since we select them). 
-The distance of trajectories from the reference point (in this case the origin) decreases over time within subspaces related to real-valued eigenvalues;  
-however, this in general not the case when dealing with complex eigenvalues.  
-Consider the closed-loop matrix, which updates the states every discrete time step, 
-and select the eigenvalue with smallest (non trivial) imaginary value -- call such value $\vartheta$. 
-At every consecutive time steps $kT_s, (k+1)T_s$ ($T_s$ being the sampling time), 
+The distance of trajectories from the reference point (in this case the origin) decreases over time within subspaces related to real-valued eigenvalues. 
+However, this in general not the case when dealing with complex eigenvalues.  
+Consider the matrix $(A_d - B_d K)$, which updates the states every time step, and select eigenvalue with smallest (non trivial) imaginary value.  
+call such value $\vartheta$. 
+At every time interval $kT_s, (k+1)T_s$ ($T_s$ being the sampling time), 
 the dynamics projected on the corresponding eigenspace rotate of $\vartheta T_s$ radiants.  
-So taking $k$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, 
-surely after $k$ steps we have completed a full rotation, which results in a point that is closer to the origin. 
-This $k$ is then taken to be the completeness threshold.
+So surely taking $k$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, 
+after $k$ steps we have completed a rotation. 
+This is the completeness threshold.
 
@@
 \caption{Completeness threshold for multi-staged verification.}
-\label{fig:ct}
 \end{figure*}
@@
 and employed for validating our methodology.
-%All systems are SISO models of the following form:
-%
-%\begin{equation}
-%\left\lbrace\begin{array}{c}
-%\dot{\textbf{x}}(t)=\textbf{A}\textbf{x}(t)+\textbf{B}u(t)\\
-%y(t)=\textbf{C}\textbf{x}(t)+\textbf{D}u(t)
-%\end{array}\right.
-%\end{equation}
-%
-Table~\ref{table:State-space benchmarks} summarizes 
-all our benchmarks, which are SISO models (cf.
-section~\ref{sec:preliminaries}).
-In the Table~\ref{table:State-space benchmarks}, the Inverted Pendulum appears to be a two output system but it was treated as two SISO systems during the experiments.
-For the sake of simplicity all the states measurements are assumed available.
-In practice, state estimators should be designed in order to obtain an estimate of the states from the single output.
-Further extensions of this work can include state observers synthesis.
-
-%\todo{they are not: we do not have a 1d output map (SO= single output), rather get access to all variables. so the output map (C) is the identity, if you will. 
-%this is a good point to clarify this, mention possible extensions to observer-based feedback architectures. }
 
@@
 
+Section~\ref{sec:BenchmarksforStateSpace} in the appendix summarizes 
+all our benchmarks, which are SISO models (cf. section~\ref{sec:preliminaries}). 
+The Inverted Pendulum appears to be a two output system, but it was treated as two 
+SISO systems during the experiments. For the sake of simplicity all the states 
+measurements are assumed available. In practice, state estimators should be designed 
+in order to obtain an estimate of the states from the single output. 
+Further extensions of this work can include 
+state observers synthesis.
+
 All benchmarks were discretized with different sample times using 
-the approach described in the Appendix~\ref{sec:appendix}. 
+the approach described in the Appendix~\ref{sec:appendix:LTIbackground}. 
 All experiments were performed considering $\underline{x_{i}}=-1$ and 
@@
 %
+
+%-------------------------------
+\subsection{Objectives}
+%-------------------------------
+
+Using the state-space models given in Section~\ref{experimental-setup}, 
+our experimental evaluation aims to answer two research questions:
+%
+\begin{enumerate}
+
+\item[RQ1] \textbf{(CEGIS)} do the CEGIS with multi-stage 
+verification and abstraction-based generate a FWL digital 
+controller in a reasonable amount of time?
+
+\item[RQ2] \textbf{(sanity check)} are the synthesized controllers sound
+and can their stability and safety be confirmed outside of our model?
+
+\end{enumerate}
+
+%-------------------------------
+\subsection{Results}
+%-------------------------------
+
+We give the run-times required to synthesize a stable controller for each
+benchmark in Table~\ref{tab:results}.  
+Here \textit{Benchmark} is the name of the employed
+benchmark, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used
+to model the plant, while \textit{Time}
+is the total time (in milliseconds) required to synthesize a stable controller
+for the given plant, for CEGIS with multi-staged verification as well as
+abstraction-based CEGIS. The precision for the controller,
+$\mathcal{F}_{\langle I_c,F_c \rangle}$, is always chosen to be $I_c = 8, F_c = 8$.
+
+For the majority of our benchmarks, the conjecture stands that the abstraction-based back-end
+is faster than the basic multi-staged verification approach. However, it does fail to
+find solutions to 3 benchmarks, as compared to 2 with the multi-staged back-end, where
+the numbers given in the discretization matrices are too small. In direct comparison the
+abstraction-based is able to find a solution in approximately 35\% of the time required
+using the multi-staged back-end. The two back-ends complement each other well in their
+benchmark coverage and together solve all benchmarks provided in the set.
+
+\begin{table}
+\centering
+\begin{tabular}{| r | c | c | r | c | r |}
+\hline
+\# & Benchmark  & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
+   &            & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
+1  & Cruise Control      & 8,16   & 6875   & 16,16  & 241    \\
+2  & DC Motor            & 8,16   & 8103   & 20,20  & 5376   \\
+3  & Helicopter          & \xmark & \xmark & 16,16  & 2120   \\
+4  & Inverted Pendulum   & 8,16   & 7813   & 16,16  & 387    \\
+5  & Magnetic Pointer    & \xmark & \xmark & 28,28  & 132845 \\
+6  & Magnetic Suspension & 12,20  & 8727   & 32,32  & 7854   \\
+7  & Pendulum            & 8,16   & 9008   & 20,20  & 1150   \\
+8  & Suspension          & 12,20  & 49410  & \xmark & \xmark \\
+9  & Tape Driver         & 8,16   & 9177   & \xmark & \xmark \\
+10 & Satellite           & 8,16   & 8975   & \xmark & \xmark \\\hline
+
+\end{tabular}
+\caption{Experimental results with runtime in milliseconds. \label{tab:results}}
+\end{table}
+
+The median runtime for our benchmark set is 7.9\,s.  Overall,
+the average synthesis time amounts to approximately 17.2\,s.  We
+consider these times short enough to be of practical use to control
+engineers, and thus affirm RQ1.
+
+The
+synthesized controllers were confirmed to be stable outside of our model
+representation using MATLAB, positively answering RQ2.  A~link to the full
+experimental environment, including scripts to reproduce the results, all
+benchmarks and the tool, is provided in the
+footnote.\footnote{\url{https://drive.google.com/open?id=0ByIexo3Z5N91eDludEdWdWxfV1E}}
+
+%-------------------------------
+\subsection{Threats to validity}
+%-------------------------------
+We report an assessment of both our approaches over a diverse set of real-world benchmarks.
+Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalize to other benchmarks.
+%
+Our algorithm to select suitable FWL word widths to model plant behavior employs a heuristic based on user-provided controller word-width specifications.
+For the first approach, where we may need to increase the precision of the time discretization, we select the time steps for the discretizations on a similar basis.
+This works sufficiently well for our benchmarks, but performance may suffer in some cases, for example if the completeness threshold is high.
+%
+The performance gain from abstract acceleration may not hold for more complex properties than stability, for instance ``eventually always reaches a certain safe set''.
+
+%% %-------------------------------
+%% \section{Related Work}
+%% \label{sec:rw}
+%% %-------------------------------
+
+%-------------------------------
+\section{Conclusions}
+%-------------------------------
+
+We have presented two approaches to synthesize state feedback controllers 
+that ensure both stability and safety over the state-space representation.
+The first approach relies on explicit unfolding of the system's dynamics 
+up to the completeness threshold, whilst the second one applies abstraction 
+refinement and acceleration to increase speed whilst retaining soundness.
+Both approaches are novel in the control system literature in that it puts
+forward a fully automated synthesis approach that is algorithmically and
+numerically sound, considering the various error sources in the implementation 
+of the control algorithm and in the computational modeling of plant dynamics.
+Our experimental results show that both approaches are able
+to synthesize stable controllers in most benchmarks within a reasonable
+amount of time fully automatically.  In particular, both approaches
+complement each other and together solve all benchmarks provided in the set.
+Future work will be the extension of these approaches to consider performance 
+requirements while synthesizing digital controllers.
+
+\newpage
+
+\bibliographystyle{abbrv}
+\bibliography{paper}  
+%\begin{thebibliography}{4}
+%\end{thebibliography}
+
+\newpage
+\appendix
+%-------------------------------
+\section{Stability of closed-loop systems}
+\label{sec:appendix-stability}
+%-------------------------------
+
+%\addtodo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantization noises yet).]}
+
+For a closed-loop system as~\eqref{eq:closedloopss}, 
+the characteristic polynomial $P(z)$ should be computed as follows:
+\begin{equation}
+P(z)= \det( z I_{n} - A_d + B_d K ),
+\end{equation}
+where $I_{n}$ is the n-th order identity matrix.
+
+Jury's criterion provides necessary and sufficient conditions for the eigenvalues 
+to be within the unit circle and, consequently, the system is stable.  Given a 
+polynomial $P(z)$ of the form
+$$
+P(z) = a_{0}z^{N} + a_{1}z^{N-1} + ... a_{N-1}z + a_{N} = 0, a_{0}\neq 0,
+$$
+Jury's criterion explores solely the coefficients ($a_{0},a_{1},...,a_{N-1}$) 
+of $P(z)$ for checking the validity of the stability property $\phi_{stability}$.
+
+In particular, Jury stability test is already explained in the control system 
+literature ({\it e.g.},~\cite{fadali}). This study, however, limits itself to 
+explain the encoding of Jury's criterion for the formal synthesis purpose. 
+For the stability  test procedure, the following Jury matrix 
+$M=[m_{ij}]_{(2N-2)\times N}$ is built  from $P(z)$ coefficients:
+$$
+M=\left[
+\begin{matrix}
+  V^{(0)} \\
+  V^{(1)} \\
+  \vdots \\
+  V^{(N-2)}
+ \end{matrix}
+\right]\mbox{,}
+$$
+\noindent where $V^{(k)}=[v^{(k)}_{ij}]_{2\times N}$ such that
+$$
+v^{(0)}_{ij}=\begin{cases} 
+a_{j-1}, & \mbox{if } i=1 \\   v^{(0)}_{(1)(N-j+1)}, & \mbox{if } i=2 
+\end{cases}\mbox{, and} 
+$$
+$$
+v^{(k)}_{ij}=\begin{cases} 
+0, & \mbox{if } j>n-k\\
+v^{(k-1)}_{1j}-v^{(k-1)}_{2j}\cdot\frac{v^{(k-1)}_{11}}{v^{(k-1)}_{21}}, & \mbox{if } j\leq n-k  \mbox{ and } i=1 \\
+v^{(k)}_{(1)(N-j+1)}, & \mbox{if } j\leq n-k \mbox{ and } i=2 \\
+\end{cases} \mbox{,}
+$$
+\noindent where $k\in\mathbb{Z}$, such that $0<k<N-2$. $P(z)$ is the 
+characteristic polynomial of a stable system if and only if the following 
+four propositions hold:
+\begin{itemize}
+\item $R_{1}$: $P(1)>0$;
+\item $R_{2}$: $(-1)^{N}P(-1)>0$;
+\item $R_{3}$: $\vert{a_{0}}\vert <a_{N}$;
+\item $R_{4}$: $m_{11}>0\iff (m_{31}>0)\wedge (m_{51}>0)\wedge \dots \wedge (m_{(2N-3)(1)>0)}$.
+\end{itemize}
+
+The stability property $\phi_{stability}$ is then encoded as follows:
+$$
+\phi_{stability}\iff \ (R_{1} \wedge R_{2} \wedge R_{3} \wedge R_{4}).
+$$
+
+%-------------------------------
+\subsection{Stability of closed-loop systems with fixed-point controller error}
+%-------------------------------
+
+The proof above relies on the fact that the relationship between states and next states is defined by
+$x_{k+1} = (A_d  - B_dK)*x_k$, all computed at infinite precision. In fact, when we employ a FWL digital controller, 
+the operation becomes:
+\begin{align*}
+x_{k+1} &= A_d * x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
+x_{k+1} &= (A_d  - B_dK)*x_k + B_dK\delta
+%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
+\end{align*}
+where $\delta$ is the maximum error that can be introduced by the FWL controller in one step, i.e., by reading the states values once and multiplying by $K$ once.
+We derive the closed form expression for $x_n$
+
+\begin{align*}
+x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
+x_{2} &= (A_d  - B_dK)((A_d  - B_dK)x_0 + B_dK\delta ) + B_dK\delta \\
+      &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
+x_{3}  &=(A_d  - B_dK)^3x_0 + (A_d  - B_dK)^2B_dK\delta + (A_d  - B_dK)B_dK\delta + B_dK\delta\\
+x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
+  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{i=n-1}(A_d - B_dK)^iB_dk\delta
+\end{align*}
+
+The definition of asymptotic stability is that the system converges to a reference signal, in this case we use no
+reference signal so an asymptotically stable system will converge to the origin. We know that the original system
+with an infinite precision controller is stable, because we have synthesized it to meet Jury's criteria. Hence
+$(A_d  - B_dK)^n*x_0$ must converge to zero.
+
+To show that a fixed point implementation of the same controller will converge to a steady value, we need to show that the infinite sum converges.
+
+A known result is that a power series of matrices converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less than 1, to the following:
+\begin{align*}
+\sum_{i=0}^{\infty}T^i  &= (I - T)^{-1}
+\end{align*}
+Where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge
+
+\begin{align*}
+x_{\infty} &= 0 + (I - A_d + B_dK)^{-1}B_dk\delta
+\end{align*}
+
+Hence, provided $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the safe space, our fixed point controller system is stable, in that it converges to a finite value, although not asymptomatically stable because it doesn't converge to the origin.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{LTI system Transformations and Equivalences} \label{sec:appendix:LTIbackground}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Discretizing continuous space dynamics}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+A dynamical system is a system in which a function describes the progression of a state over time. 
+In a continuous domain with linear dynamics, it is described by a first order Ordinary Differential Equation (ODE).
+\begin{equation}
+\dot{x}(t)=\vec{A}\vec{x}(t)+\vec{B}\vec{u}(t) +\vec{w}(t).
+\label{eq:dynamical}
+\end{equation}
+
+\noindent with $\vec{w} \sim \mathcal{N}(0,Q)$.\\
+Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
+which may restrict the observability of the state-space from the output space.
+\begin{equation}
+\vec{y}(t)=\vec{C}\vec{x}(t)+\vec{D}\vec{u}(t).
+\end{equation}
+
+Discretization of an continuous dynamical system turns the ODE into a difference equation, assuming zero-order hold
+for the input $\vec{u}$ and continuous integration for the noise $\vec{w}$, to
+\begin{align}
+\label{eq:discretization}
+\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d\vec{u}_k + \vec{w}_k,\\
+y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k. 
+\end{align}
+with covariance for $\vec{w}_k \sim \mathcal{N}(0,Q_d)$,
+where
+\begin{align}
+\label{eq:discretize}
+\vec{A}_d &= e^{\vec{A} T_s} = \mathcal{L}^{-1} { ( s \vec{I} - \vec{A} )^{-1} }_{t = T_s},\\
+\vec{B}_d &= \int_{0}^{T_s} e^{\vec{A} t} dt\ \vec{B} = \vec{A}^{-1} ( \vec{A}_d - \vec{I} ) \vec{B},\\
+\vec{C}_d &= \vec{C},\\
+\vec{D}_d &= \vec{D},\\
+Q_d &= \int_{0}^{T_s} e^{\vec{A} t} Q e^{\vec{A}^T t} dt.
+\end{align}
+and $T_s$ is the sample time. Then
+\begin{align*}
+x(kT_s)=x_k \wedge y(kT_s) = y_k, \forall k.
+\end{align*}
+Let $g_d(k)=\mathcal{G}(t,g(t),T)$ be a function that performs the discretization described above, where $g(t)$
+represents the continuous dynamics and $g_d(k)$ the corresponding discrete dynamics. 
+Let $G(s)=\mathcal{L}(g(t))$ and $G_d(z)=\mathcal{Z}(g_d(k))$ be the corresponding Laplace and Z-transforms
+of $g(t)$ and $g_d(k)$. Given this relation, we have 
+$$G_d(z)=G(z)|_{z=e^{sT}} : g_d(k)=\mathcal{G}(t,g(t),T) \wedge T < \frac{1}{.5f_s},$$
+where $.5f_s$ is the Nyquist frequency of $g(t)$. This last restriction is introduced to avoid the effects of aliasing
+which could cause ``phantom poles'' to appear otherwise. 
+The eigenvalues of $\vec{A}_d$ corresponding to the poles of $G_d(z)$, and those of $\vec{A}$ corresponding to the poles of $G(s)$ are similarly related.
+$\hat{\lambda}_i=e^{-\lambda_iT} : \hat{\lambda}_i \in \sigma(\vec{A}_d) \wedge \lambda_i \in \sigma(\vec{A})$
+where $\sigma(\cdot)$ is the spectrum of a matrix.
+The following remark is worth mentioning regarding the above.
+\begin{remark}
+The witnessed maximum amplitude of the discrete signals $x_k,y_k$ may be smaller to that of $x(t),y(t)$ due to synchronism at fraction-frequency sampling.
+This means that reasoning about the state-space must consider the effects of this possibility as well of the case of maximal inputs from the continuous specification.
+\end{remark}
+ Since \eqref{eq:discretization} is a bi-simulation of \eqref{eq:ode}, we may use the semantics in section \ref{sec:model_semantics} to model continuous dynamical systems.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Overapproximating continuous space dynamics using discrete models}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+Let us recall equation \ref{eq:discretize}. The discrete representation of the system dynamics discretized with sample time $T_1$ is ruled by the formula
+$\vec{A}_1 = e^{\vec{A} T_1}$. From matrix theory, we have 
+\begin{equation}
+\vec{A}_1 = \mat{S}_1\mat{J}_1\mat{S}_1^{-1}= \mat{S}_1e^{\mat{J} T_1}\mat{S}_1^{-1}.
+\end{equation}
+Let $\mat{J}$ be a diagonal matrix, such that ${\lambda_1}_i=e^{\lambda_i T_1}, \forall \lambda \in \mat{J}$.
+Let us now take a different sample rate $T_2$, such that ${\lambda_2}_i=e^{\lambda_i T_2}, \forall \lambda \in \mat{J}$. We can then say that 
+\begin{equation}
+{\lambda_2}_i=e^{\lambda_i T_1 T_2/T_1}={\lambda_1}_i^{T_2/T_1} \Rightarrow A_2=A_1^{\frac{T_2}{T_1}}
+\end{equation}
+We have also shown in the previous section that $x_k=A^nx_0$ is a witness of $x(t): \dot{x}(t)=Ax(t)$ at time $kT_s$.
+Applying this notion to multiple sample times, we can state that $x_{k_i}=A_i^nx_0$ are a set of witnesses at times $kT_i$, and by extension the set $\{x=A_i^nx_0 : \forall n \in \mathbb{R} \}$ witnesses all states visited by the continuous system in time $t \in [0,\infty)$.
+This applies to any arbitrary sample time $T_i$.
+Since the controller output is fed to a Zero Order Holder, the progression of the system between times $kT_s$ and $(k+1)T_s$ is $\mat{A}^n\vec{x}_k+\mat{B}\vec{u}_k : n \in (0,1)$.
+We therefore obtain a reach tube for the continuous dynamics of a time sampled system to be contained within the abstract reach tube $\mathcal{A}^1\mathcal{M}X_0+\mathcal{BK}^1\mathcal{M}X_0=\mathcal{M}X_0$
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Modelling quantization as noise} \label{appendix:quantization-noise}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathbb{R}\langle I_{c},F_{c} \rangle$ value.
+this sampling uses a threshold which is defined by the less significant bit ($q_{adc}=2^{-F_{adc}}$) of the ADC and some non-linearities of the circuitry.
+The overall conversion is
+$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{adc}}{2}\right]$$.
+If we denote the error in the conversion as $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
+
+We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (\emph{ie} the quantizer includes any digital gain added in the code).
+The process of quantization in the DAC is similar except that it is going from $\mathbb{R}\langle I_{c},F_{c} \rangle \rightarrow \mathbb{R}\langle I_{dac},F_{dac} \rangle$.
+If these domains are the same ($I_{c}=I_{dac},F_{c}=F_{dac}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
+From the above equations we can now infer that $\nu_1 \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], \nu_2 \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{c} \wedge q_2=q_{dac}$.
+Note that these bounds hold irrespective of whether the noise is correlated, hence we may use them to over-approximate the effect of the noise on the state space progression over time.
+The resulting dynamics are:
+\begin{align}
+\label{eq:pre_quantization}
+\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d(\vec{u}_k+{\vec{\nu}_2}_k) + \vec{w}_k,\\
+y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k+{\vec{\nu}_1}_k. 
+\end{align}
+
+Which, when modelled into closed loop dynamics results in:
+
+\begin{align}
+\label{eq:quantization}
+\vec{x}_{k+1} &= (\vec{A}_d-\vec{B}_d\mat{K}_d\mat{C}_d) \vec{x}_k+\vec{B}_d{\vec{\nu}_2}_k + \vec{w}_k,\\
+y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k+{\vec{\nu}_1}_k. 
+\end{align}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Controllable canonical form} \label{sec:reachable}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Let us have a discrete time SISO system with an $n^{th},m^{th} : n\geq m$ order armax model
+$$y[k]=\sum_{i=1}^n a_iy[k-i]+\sum_{i=0}^m b_iu[k-i],$$
+where $y$ is the output of the system and $u$ its input.
+The equivalent LTI dynamics of such a model are:
+\begin{align}
+\label{eq:cf_SISO}
+\vec{x}_{k+1}=&\mat{A}_{cf}\vec{x}_k+\mat{B}_{cf}u_k : \vec{x}_k=[y_{k-n}\ \hdots y_{k-1}\ y_{k}]^T\\
+y_k=&\mat{C}_{cf}\vec{x}_k + b_0u_k\nonumber\\
+\mat{A}_{cf}=&\left[
+\begin{array}{ccccc}
+0&1&0&\cdots&0\\
+0&0&1&\cdots&0\\
+\vdots&\vdots&\vdots&\ddots&\vdots\\
+0&0&0&\cdots&1\\
+-a_n&-a_{n-1}&-a_{n-2}&\cdots&-a_1
+\end{array}\right],
+\mat{B}_{cf}=\left[
+\begin{array}{c}
+0\\0\\ \vdots\\ 0\\ 1
+\end{array}\right]\nonumber\\
+\mat{C}_{cf}=&[\begin{array}{ccccc}b_n-a_nb_0&b_{n-1}-a_{n-1}b_0&\cdots&b_1-a_1b_0\end{array}] : b_{i \in (m\ n]}=0\nonumber
+\end{align}
+
+where the coefficients $a_i$ describe the characteristic polynomial of the system. This matrix shape is
+called a Controllable Canonical Form because the dynamics of the feedback are directly related to these
+coefficients. Specifically, given a feedback controller $\mat{K}$ for this system, the closed loop dynamics
+will have the shape
+\begin{align}
+\mat{A}_{cf}+\mat{B}_{cf}\mat{K}_{cf}=&\left[
+\begin{array}{ccccc}
+0&1&0&\cdots&0\\
+0&0&1&\cdots&0\\
+\vdots&\vdots&\vdots&\ddots&\vdots\\
+0&0&0&\cdots&1\\
+k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
+\end{array}\right]
+\label{eq:cf_SISO_fb}
+\end{align}
+which means we can directly modify each coefficient by selecting a controller parameter.
+In the MIMO case, the Controllable Canonical Form has the following shape:
+\begin{align}
+\mat{A}_{cf}=&\left[
+\begin{array}{ccccc}
+0&\mat{I}_{n-1}&0&\cdots&0\\
+0&0&\mat{I}_{n-2}&\cdots&0\\
+\vdots&\vdots&\vdots&\ddots&\vdots\\
+0&0&0&\cdots&1\\
+-\mat{a_n}\mat{M}_n&-\mat{a_{n-1}}\mat{M}_{n-1}&-\mat{a_{n-2}}\mat{M}_{n-2}&\cdots&-\mat{a_1}\mat{M}_{1}
+\end{array}\right],
+\mat{B}_{cf}=\left[
+\begin{array}{c}
+0\\0\\ \vdots\\ 0\\ \mat{M}_0
+\end{array}\right]\nonumber\\
+\mat{C}_{cf}=&[\begin{array}{ccccc}\mat{\eta}_n&\mat{\eta}_{n-1}&\cdots&\mat{\eta}_1\end{array}] :
+\mat{I}_i,\mat{M}_i \in \mathbb{R}^{q_i \times q_i} \wedge \mat{a}_i \in \mathbb{R}^{q \times q_i} \wedge \mat{\eta}_i \in \mathbb{R}^o \wedge  \mat{\eta}_{i \in (m\ n]}=0 \nonumber
+\label{eq:cf_MIMO}
+\end{align}
+where $q$ is the number of inputs, $q_i$ the number of inputs with a transfer function of order of at least $i$, $\mat{I}_i$ an identity matrix, $\mat{M}_i$ an upper triangular matrix with 1s in its diagonal, $\mat{a_i}$ a matrix of coefficients of the $i^th$ order on its diagonal, and $o$ the number of outputs.
+Ideally we aim for $\mat{M}_i=\mat{I}_i, \forall i>0$
+
+Any LTI system can be transformed into a controllable canonical form by a matrix $\mat{T} : \vec{x}=\mat{T}\hat{\vec{x}}$
+Then the dynamics of the controllable form are
+\begin{align}
+\hat{\vec{x}}_{k+1}=&\mat{A}_{cf}\hat{\vec{x}}_k+\mat{B}_{cf}u_k : \mat{A}_{cf}=\mat{T}\mat{A}\mat{T}^{-1} \wedge \mat{B}_{cf}=\mat{T}\mat{B}\\
+y_k=&\mat{C}_{cf}\hat{\vec{x}}_k + b_0u_k : \mat{C}_{cf}=\mat{C}\mat{T}^{-1}\nonumber
+\end{align}
+where $\mat{T}$ can be calculated as follows:
+
+Let 
+\begin{equation}
+\mat{R}=[\begin{array}{ccccc}\mat{B}&\mat{A}\mat{B}&\mat{A}^2\mat{B}&\hdots&\mat{A}^{n-1}\mat{B}\end{array}]
+\label{eq:rncf}
+\end{equation}
+be the reachability matrix of the system, and
+\begin{equation}
+\mat{R}_{cf}=\left[\begin{array}{ccccc}1&a_1&a_2&\hdots&a_{n-1}\\0&1&a_1&\hdots&a_{n-2}\\ \vdots&\ddots&\ddots&\ddots&\ddots\end{array}\right]
+\label{eq:rcf}
+\end{equation}
+the reachability matrix of the canonical form. Then 
+\begin{equation}
+\mat{T}=\mat{R}_{cf}\mat{R}^{-1}
+\label{eq:to_cf}
+\end{equation}
+
+%-------------------------------
+\section{Extensions}
+\label{sec:extensions}
+%-------------------------------
+
+%-------------------------------
+\subsection{LTI systems with output} 
+\label{ssec:LTI}
+%-------------------------------
+
+LTI models in the form: 
+%
+\begin{align}
+\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
+\vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
+\end{align}
+\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
+$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
+a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
+(as shown in the appendix) into
+%
+\begin{align}
+\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
+\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
+\end{align}
+%
+
+%-------------------------------
+\section{Benchmarks for State-Space Physical Plants}
+\label{sec:BenchmarksforStateSpace}
+%-------------------------------
+
 \begin{table}[htb]
@@
 \caption{Benchmarks for State-Space Physical Plants.}
-\label{table:State-space benchmarks}
+\label{table:State-space-benchmarks}
 \begin{tabular}{|c|c|c|c|c|}
@@
 
-%-------------------------------
-\subsection{Objectives}
-%-------------------------------
-
-Using the state-space models given in Section~\ref{experimental-setup}, 
-our experimental evaluation aims to answer two research questions:
-%
-\begin{enumerate}
-
-\item[RQ1] \textbf{(CEGIS)} do the CEGIS with multi-stage 
-verification and abstraction-based generate a FWL digital 
-controller in a reasonable amount of time?
-
-\item[RQ2] \textbf{(sanity check)} are the synthesized controllers sound
-and can their stability and safety be confirmed outside of our model?
-
-\end{enumerate}
-
-%-------------------------------
-\subsection{Results}
-%-------------------------------
-
-We give the run-times required to synthesize a stable controller for each
-benchmark in Table~\ref{tab:results}.  
-Here \textit{Benchmark} is the name of the employed
-benchmark, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used
-to model the plant, while \textit{Time}
-is the total time (in milliseconds) required to synthesize a stable controller
-for the given plant, for CEGIS with multi-staged verification as well as
-abstraction-based CEGIS. The precision for the controller,
-$\mathcal{F}_{\langle I_c,F_c \rangle}$, is always chosen to be $I_c = 8, F_c = 8$.
-
-For the majority of our benchmarks, the conjecture stands that the abstraction-based back-end
-is faster than the basic multi-staged verification approach. However, it does fail to
-find solutions to 3 benchmarks, as compared to 2 with the multi-staged back-end, where
-the numbers given in the discretization matrices are too small. In direct comparison the
-abstraction-based is able to find a solution in approximately 35\% of the time required
-using the multi-staged back-end. The two back-ends complement each other well in their
-benchmark coverage and together solve all benchmarks provided in the set.
-
-\begin{table}
-\centering
-\begin{tabular}{| r | c | c | r | c | r |}
-\hline
-\# & Benchmark  & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
-   &            & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
-1  & Cruise Control      & 8,16   & 6875   & 16,16  & 241    \\
-2  & DC Motor            & 8,16   & 8103   & 20,20  & 5376   \\
-3  & Helicopter          & \xmark & \xmark & 16,16  & 2120   \\
-4  & Inverted Pendulum   & 8,16   & 7813   & 16,16  & 387    \\
-5  & Magnetic Pointer    & \xmark & \xmark & 28,28  & 132845 \\
-6  & Magnetic Suspension & 12,20  & 8727   & 32,32  & 7854   \\
-7  & Pendulum            & 8,16   & 9008   & 20,20  & 1150   \\
-8  & Suspension          & 12,20  & 49410  & \xmark & \xmark \\
-9  & Tape Driver         & 8,16   & 9177   & \xmark & \xmark \\
-10 & Satellite           & 8,16   & 8975   & \xmark & \xmark \\\hline
-
-\end{tabular}
-\caption{Experimental results with runtime in milliseconds. \label{tab:results}}
-\end{table}
-
-The median runtime for our benchmark set is 7.9\,s.  Overall,
-the average synthesis time amounts to approximately 17.2\,s.  We
-consider these times short enough to be of practical use to control
-engineers, and thus affirm RQ1.
-
-The
-synthesized controllers were confirmed to be stable outside of our model
-representation using MATLAB, positively answering RQ2.  A~link to the full
-experimental environment, including scripts to reproduce the results, all
-benchmarks and the tool, is provided in the
-footnote.\footnote{\url{https://drive.google.com/open?id=0ByIexo3Z5N91eDludEdWdWxfV1E}}
-
-%-------------------------------
-\subsection{Threats to validity}
-%-------------------------------
-We report an assessment of both our approaches over a diverse set of real-world benchmarks.
-Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalize to other benchmarks.
-%
-Our algorithm to select suitable FWL word widths to model plant behavior employs a heuristic based on user-provided controller word-width specifications.
-For the first approach, where we may need to increase the precision of the time discretization, we select the time steps for the discretizations on a similar basis.
-This works sufficiently well for our benchmarks, but performance may suffer in some cases, for example if the completeness threshold is high.
-%
-The performance gain from abstract acceleration may not hold for more complex properties than stability, for instance ``eventually always reaches a certain safe set''.
-
-%% %-------------------------------
-%% \section{Related Work}
-%% \label{sec:rw}
-%% %-------------------------------
-
-%-------------------------------
-\section{Conclusions}
-%-------------------------------
-
-We have presented two approaches to synthesize state feedback controllers 
-that ensure both stability and safety over the state-space representation.
-The first approach relies on explicit unfolding of the system's dynamics 
-up to the completeness threshold, whilst the second one applies abstraction 
-refinement and acceleration to increase speed whilst retaining soundness.
-Both approaches are novel in the control system literature in that it puts
-forward a fully automated synthesis approach that is algorithmically and
-numerically sound, considering the various error sources in the implementation 
-of the control algorithm and in the computational modeling of plant dynamics.
-Our experimental results show that both approaches are able
-to synthesize stable controllers in most benchmarks within a reasonable
-amount of time fully automatically.  In particular, both approaches
-complement each other and together solve all benchmarks provided in the set.
-Future work will be the extension of these approaches to consider performance 
-requirements while synthesizing digital controllers.
-
-\newpage
-
-\bibliographystyle{abbrv}
-\bibliography{paper}  
-%\begin{thebibliography}{4}
-%\end{thebibliography}
-
-\newpage
-\appendix
-%-------------------------------
-\section{Stability of closed-loop systems}
-\label{sec:appendix-stability}
-%-------------------------------
-
-%\addtodo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantization noises yet).]}
-
-For a closed-loop system as~\eqref{eq:closedloopss}, 
-the characteristic polynomial $P(z)$ should be computed as follows:
-\begin{equation}
-P(z)= \det( z I_{n} - A_d + B_d K ),
-\end{equation}
-where $I_{n}$ is the n-th order identity matrix.
-
-Jury's criterion provides necessary and sufficient conditions for the eigenvalues 
-to be within the unit circle and, consequently, the system is stable.  Given a 
-polynomial $P(z)$ of the form
-$$
-P(z) = a_{0}z^{N} + a_{1}z^{N-1} + ... a_{N-1}z + a_{N} = 0, a_{0}\neq 0,
-$$
-Jury's criterion explores solely the coefficients ($a_{0},a_{1},...,a_{N-1}$) 
-of $P(z)$ for checking the validity of the stability property $\phi_{stability}$.
-
-In particular, Jury stability test is already explained in the control system 
-literature ({\it e.g.},~\cite{fadali}). This study, however, limits itself to 
-explain the encoding of Jury's criterion for the formal synthesis purpose. 
-For the stability  test procedure, the following Jury matrix 
-$M=[m_{ij}]_{(2N-2)\times N}$ is built  from $P(z)$ coefficients:
-$$
-M=\left[
-\begin{matrix}
-  V^{(0)} \\
-  V^{(1)} \\
-  \vdots \\
-  V^{(N-2)}
- \end{matrix}
-\right]\mbox{,}
-$$
-\noindent where $V^{(k)}=[v^{(k)}_{ij}]_{2\times N}$ such that
-$$
-v^{(0)}_{ij}=\begin{cases} 
-a_{j-1}, & \mbox{if } i=1 \\   v^{(0)}_{(1)(N-j+1)}, & \mbox{if } i=2 
-\end{cases}\mbox{, and} 
-$$
-$$
-v^{(k)}_{ij}=\begin{cases} 
-0, & \mbox{if } j>n-k\\
-v^{(k-1)}_{1j}-v^{(k-1)}_{2j}\cdot\frac{v^{(k-1)}_{11}}{v^{(k-1)}_{21}}, & \mbox{if } j\leq n-k  \mbox{ and } i=1 \\
-v^{(k)}_{(1)(N-j+1)}, & \mbox{if } j\leq n-k \mbox{ and } i=2 \\
-\end{cases} \mbox{,}
-$$
-\noindent where $k\in\mathbb{Z}$, such that $0<k<N-2$. $P(z)$ is the 
-characteristic polynomial of a stable system if and only if the following 
-four propositions hold:
-\begin{itemize}
-\item $R_{1}$: $P(1)>0$;
-\item $R_{2}$: $(-1)^{N}P(-1)>0$;
-\item $R_{3}$: $\vert{a_{0}}\vert <a_{N}$;
-\item $R_{4}$: $m_{11}>0\iff (m_{31}>0)\wedge (m_{51}>0)\wedge \dots \wedge (m_{(2N-3)(1)>0)}$.
-\end{itemize}
-
-The stability property $\phi_{stability}$ is then encoded as follows:
-$$
-\phi_{stability}\iff \ (R_{1} \wedge R_{2} \wedge R_{3} \wedge R_{4}).
-$$
-
-%-------------------------------
-\subsection{Stability of closed-loop systems with fixed-point controller error}
-%-------------------------------
-
-The proof above relies on the fact that the relationship between states and next states is defined by
-$x_{k+1} = (A_d  - B_dK)*x_k$, all computed at infinite precision. In fact, when we employ a FWL digital controller, 
-the operation becomes:
-\begin{align*}
-x_{k+1} &= A_d * x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
-x_{k+1} &= (A_d  - B_dK)*x_k + B_dK\delta
-%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
-\end{align*}
-where $\delta$ is the maximum error that can be introduced by the FWL controller in one step, i.e., by reading the states values once and multiplying by $K$ once.
-We derive the closed form expression for $x_n$
-
-\begin{align*}
-x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
-x_{2} &= (A_d  - B_dK)((A_d  - B_dK)x_0 + B_dK\delta ) + B_dK\delta \\
-      &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
-x_{3}  &=(A_d  - B_dK)^3x_0 + (A_d  - B_dK)^2B_dK\delta + (A_d  - B_dK)B_dK\delta + B_dK\delta\\
-x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
-  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{i=n-1}(A_d - B_dK)^iB_dk\delta
-\end{align*}
-
-The definition of asymptotic stability is that the system converges to a reference signal, in this case we use no
-reference signal so an asymptotically stable system will converge to the origin. We know that the original system
-with an infinite precision controller is stable, because we have synthesized it to meet Jury's criteria. Hence
-$(A_d  - B_dK)^n*x_0$ must converge to zero.
-
-To show that a fixed point implementation of the same controller will converge to a steady value, we need to show that the infinite sum converges.
-
-A known result is that a power series of matrices converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less than 1, to the following:
-\begin{align*}
-\sum_{i=0}^{\infty}T^i  &= (I - T)^{-1}
-\end{align*}
-Where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge
-
-\begin{align*}
-x_{\infty} &= 0 + (I - A_d + B_dK)^{-1}B_dk\delta
-\end{align*}
-
-Hence, provided $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the safe space, our fixed point controller system is stable, in that it converges to a finite value, although not asymptomatically stable because it doesn't converge to the origin.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{LTI system Transformations and Equivalences} \label{sec:appendix:LTIbackground}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Discretizing continuous space dynamics}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-A dynamical system is a system in which a function describes the progression of a state over time. 
-In a continuous domain with linear dynamics, it is described by a first order Ordinary Differential Equation (ODE).
-\begin{equation}
-\dot{x}(t)=\vec{A}\vec{x}(t)+\vec{B}\vec{u}(t) +\vec{w}(t).
-\label{eq:dynamical}
-\end{equation}
-
-\noindent with $\vec{w} \sim \mathcal{N}(0,Q)$.\\
-Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
-which may restrict the observability of the state-space from the output space.
-\begin{equation}
-\vec{y}(t)=\vec{C}\vec{x}(t)+\vec{D}\vec{u}(t).
-\end{equation}
-
-Discretization of an continuous dynamical system turns the ODE into a difference equation, assuming zero-order hold
-for the input $\vec{u}$ and continuous integration for the noise $\vec{w}$, to
-\begin{align}
-\label{eq:discretization}
-\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d\vec{u}_k + \vec{w}_k,\\
-y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k. 
-\end{align}
-with covariance for $\vec{w}_k \sim \mathcal{N}(0,Q_d)$,
-where
-\begin{align}
-\label{eq:discretize}
-\vec{A}_d &= e^{\vec{A} T_s} = \mathcal{L}^{-1} { ( s \vec{I} - \vec{A} )^{-1} }_{t = T_s},\\
-\vec{B}_d &= \int_{0}^{T_s} e^{\vec{A} t} dt\ \vec{B} = \vec{A}^{-1} ( \vec{A}_d - \vec{I} ) \vec{B},\\
-\vec{C}_d &= \vec{C},\\
-\vec{D}_d &= \vec{D},\\
-Q_d &= \int_{0}^{T_s} e^{\vec{A} t} Q e^{\vec{A}^T t} dt.
-\end{align}
-and $T_s$ is the sample time. Then
-\begin{align*}
-x(kT_s)=x_k \wedge y(kT_s) = y_k, \forall k.
-\end{align*}
-Let $g_d(k)=\mathcal{G}(t,g(t),T)$ be a function that performs the discretization described above, where $g(t)$
-represents the continuous dynamics and $g_d(k)$ the corresponding discrete dynamics. 
-Let $G(s)=\mathcal{L}(g(t))$ and $G_d(z)=\mathcal{Z}(g_d(k))$ be the corresponding Laplace and Z-transforms
-of $g(t)$ and $g_d(k)$. Given this relation, we have 
-$$G_d(z)=G(z)|_{z=e^{sT}} : g_d(k)=\mathcal{G}(t,g(t),T) \wedge T < \frac{1}{.5f_s},$$
-where $.5f_s$ is the Nyquist frequency of $g(t)$. This last restriction is introduced to avoid the effects of aliasing
-which could cause ``phantom poles'' to appear otherwise. 
-The eigenvalues of $\vec{A}_d$ corresponding to the poles of $G_d(z)$, and those of $\vec{A}$ corresponding to the poles of $G(s)$ are similarly related.
-$\hat{\lambda}_i=e^{-\lambda_iT} : \hat{\lambda}_i \in \sigma(\vec{A}_d) \wedge \lambda_i \in \sigma(\vec{A})$
-where $\sigma(\cdot)$ is the spectrum of a matrix.
-The following remark is worth mentioning regarding the above.
-\begin{remark}
-The witnessed maximum amplitude of the discrete signals $x_k,y_k$ may be smaller to that of $x(t),y(t)$ due to synchronism at fraction-frequency sampling.
-This means that reasoning about the state-space must consider the effects of this possibility as well of the case of maximal inputs from the continuous specification.
-\end{remark}
- Since \eqref{eq:discretization} is a bi-simulation of \eqref{eq:ode}, we may use the semantics in section \ref{sec:model_semantics} to model continuous dynamical systems.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Overapproximating continuous space dynamics using discrete models}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-Let us recall equation \ref{eq:discretize}. The discrete representation of the system dynamics discretized with sample time $T_1$ is ruled by the formula
-$\vec{A}_1 = e^{\vec{A} T_1}$. From matrix theory, we have 
-\begin{equation}
-\vec{A}_1 = \mat{S}_1\mat{J}_1\mat{S}_1^{-1}= \mat{S}_1e^{\mat{J} T_1}\mat{S}_1^{-1}.
-\end{equation}
-Let $\mat{J}$ be a diagonal matrix, such that ${\lambda_1}_i=e^{\lambda_i T_1}, \forall \lambda \in \mat{J}$.
-Let us now take a different sample rate $T_2$, such that ${\lambda_2}_i=e^{\lambda_i T_2}, \forall \lambda \in \mat{J}$. We can then say that 
-\begin{equation}
-{\lambda_2}_i=e^{\lambda_i T_1 T_2/T_1}={\lambda_1}_i^{T_2/T_1} \Rightarrow A_2=A_1^{\frac{T_2}{T_1}}
-\end{equation}
-We have also shown in the previous section that $x_k=A^nx_0$ is a witness of $x(t): \dot{x}(t)=Ax(t)$ at time $kT_s$.
-Applying this notion to multiple sample times, we can state that $x_{k_i}=A_i^nx_0$ are a set of witnesses at times $kT_i$, and by extension the set $\{x=A_i^nx_0 : \forall n \in \mathbb{R} \}$ witnesses all states visited by the continuous system in time $t \in [0,\infty)$.
-This applies to any arbitrary sample time $T_i$.
-Since the controller output is fed to a Zero Order Holder, the progression of the system between times $kT_s$ and $(k+1)T_s$ is $\mat{A}^n\vec{x}_k+\mat{B}\vec{u}_k : n \in (0,1)$.
-We therefore obtain a reach tube for the continuous dynamics of a time sampled system to be contained within the abstract reach tube $\mathcal{A}^1\mathcal{M}X_0+\mathcal{BK}^1\mathcal{M}X_0=\mathcal{M}X_0$
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Modelling quantization as noise} \label{appendix:quantization-noise}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathbb{R}\langle I_{c},F_{c} \rangle$ value.
-this sampling uses a threshold which is defined by the less significant bit ($q_{adc}=2^{-F_{adc}}$) of the ADC and some non-linearities of the circuitry.
-The overall conversion is
-$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{adc}}{2}\right]$$.
-If we denote the error in the conversion as $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
-
-We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (\emph{ie} the quantizer includes any digital gain added in the code).
-The process of quantization in the DAC is similar except that it is going from $\mathbb{R}\langle I_{c},F_{c} \rangle \rightarrow \mathbb{R}\langle I_{dac},F_{dac} \rangle$.
-If these domains are the same ($I_{c}=I_{dac},F_{c}=F_{dac}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
-From the above equations we can now infer that $\nu_1 \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], \nu_2 \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{c} \wedge q_2=q_{dac}$.
-Note that these bounds hold irrespective of whether the noise is correlated, hence we may use them to over-approximate the effect of the noise on the state space progression over time.
-The resulting dynamics are:
-\begin{align}
-\label{eq:pre_quantization}
-\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d(\vec{u}_k+{\vec{\nu}_2}_k) + \vec{w}_k,\\
-y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k+{\vec{\nu}_1}_k. 
-\end{align}
-
-Which, when modelled into closed loop dynamics results in:
-
-\begin{align}
-\label{eq:quantization}
-\vec{x}_{k+1} &= (\vec{A}_d-\vec{B}_d\mat{K}_d\mat{C}_d) \vec{x}_k+\vec{B}_d{\vec{\nu}_2}_k + \vec{w}_k,\\
-y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k+{\vec{\nu}_1}_k. 
-\end{align}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Controllable canonical form} \label{sec:reachable}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Let us have a discrete time SISO system with an $n^{th},m^{th} : n\geq m$ order armax model
-$$y[k]=\sum_{i=1}^n a_iy[k-i]+\sum_{i=0}^m b_iu[k-i],$$
-where $y$ is the output of the system and $u$ its input.
-The equivalent LTI dynamics of such a model are:
-\begin{align}
-\label{eq:cf_SISO}
-\vec{x}_{k+1}=&\mat{A}_{cf}\vec{x}_k+\mat{B}_{cf}u_k : \vec{x}_k=[y_{k-n}\ \hdots y_{k-1}\ y_{k}]^T\\
-y_k=&\mat{C}_{cf}\vec{x}_k + b_0u_k\nonumber\\
-\mat{A}_{cf}=&\left[
-\begin{array}{ccccc}
-0&1&0&\cdots&0\\
-0&0&1&\cdots&0\\
-\vdots&\vdots&\vdots&\ddots&\vdots\\
-0&0&0&\cdots&1\\
--a_n&-a_{n-1}&-a_{n-2}&\cdots&-a_1
-\end{array}\right],
-\mat{B}_{cf}=\left[
-\begin{array}{c}
-0\\0\\ \vdots\\ 0\\ 1
-\end{array}\right]\nonumber\\
-\mat{C}_{cf}=&[\begin{array}{ccccc}b_n-a_nb_0&b_{n-1}-a_{n-1}b_0&\cdots&b_1-a_1b_0\end{array}] : b_{i \in (m\ n]}=0\nonumber
-\end{align}
-
-where the coefficients $a_i$ describe the characteristic polynomial of the system. This matrix shape is
-called a Controllable Canonical Form because the dynamics of the feedback are directly related to these
-coefficients. Specifically, given a feedback controller $\mat{K}$ for this system, the closed loop dynamics
-will have the shape
-\begin{align}
-\mat{A}_{cf}+\mat{B}_{cf}\mat{K}_{cf}=&\left[
-\begin{array}{ccccc}
-0&1&0&\cdots&0\\
-0&0&1&\cdots&0\\
-\vdots&\vdots&\vdots&\ddots&\vdots\\
-0&0&0&\cdots&1\\
-k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
-\end{array}\right]
-\label{eq:cf_SISO_fb}
-\end{align}
-which means we can directly modify each coefficient by selecting a controller parameter.
-In the MIMO case, the Controllable Canonical Form has the following shape:
-\begin{align}
-\mat{A}_{cf}=&\left[
-\begin{array}{ccccc}
-0&\mat{I}_{n-1}&0&\cdots&0\\
-0&0&\mat{I}_{n-2}&\cdots&0\\
-\vdots&\vdots&\vdots&\ddots&\vdots\\
-0&0&0&\cdots&1\\
--\mat{a_n}\mat{M}_n&-\mat{a_{n-1}}\mat{M}_{n-1}&-\mat{a_{n-2}}\mat{M}_{n-2}&\cdots&-\mat{a_1}\mat{M}_{1}
-\end{array}\right],
-\mat{B}_{cf}=\left[
-\begin{array}{c}
-0\\0\\ \vdots\\ 0\\ \mat{M}_0
-\end{array}\right]\nonumber\\
-\mat{C}_{cf}=&[\begin{array}{ccccc}\mat{\eta}_n&\mat{\eta}_{n-1}&\cdots&\mat{\eta}_1\end{array}] :
-\mat{I}_i,\mat{M}_i \in \mathbb{R}^{q_i \times q_i} \wedge \mat{a}_i \in \mathbb{R}^{q \times q_i} \wedge \mat{\eta}_i \in \mathbb{R}^o \wedge  \mat{\eta}_{i \in (m\ n]}=0 \nonumber
-\label{eq:cf_MIMO}
-\end{align}
-where $q$ is the number of inputs, $q_i$ the number of inputs with a transfer function of order of at least $i$, $\mat{I}_i$ an identity matrix, $\mat{M}_i$ an upper triangular matrix with 1s in its diagonal, $\mat{a_i}$ a matrix of coefficients of the $i^th$ order on its diagonal, and $o$ the number of outputs.
-Ideally we aim for $\mat{M}_i=\mat{I}_i, \forall i>0$
-
-Any LTI system can be transformed into a controllable canonical form by a matrix $\mat{T} : \vec{x}=\mat{T}\hat{\vec{x}}$
-Then the dynamics of the controllable form are
-\begin{align}
-\hat{\vec{x}}_{k+1}=&\mat{A}_{cf}\hat{\vec{x}}_k+\mat{B}_{cf}u_k : \mat{A}_{cf}=\mat{T}\mat{A}\mat{T}^{-1} \wedge \mat{B}_{cf}=\mat{T}\mat{B}\\
-y_k=&\mat{C}_{cf}\hat{\vec{x}}_k + b_0u_k : \mat{C}_{cf}=\mat{C}\mat{T}^{-1}\nonumber
-\end{align}
-where $\mat{T}$ can be calculated as follows:
-
-Let 
-\begin{equation}
-\mat{R}=[\begin{array}{ccccc}\mat{B}&\mat{A}\mat{B}&\mat{A}^2\mat{B}&\hdots&\mat{A}^{n-1}\mat{B}\end{array}]
-\label{eq:rncf}
-\end{equation}
-be the reachability matrix of the system, and
-\begin{equation}
-\mat{R}_{cf}=\left[\begin{array}{ccccc}1&a_1&a_2&\hdots&a_{n-1}\\0&1&a_1&\hdots&a_{n-2}\\ \vdots&\ddots&\ddots&\ddots&\ddots\end{array}\right]
-\label{eq:rcf}
-\end{equation}
-the reachability matrix of the canonical form. Then 
-\begin{equation}
-\mat{T}=\mat{R}_{cf}\mat{R}^{-1}
-\label{eq:to_cf}
-\end{equation}
-
-%-------------------------------
-\section{Extensions}
-\label{sec:extensions}
-%-------------------------------
-
-%-------------------------------
-\subsection{LTI systems with output} 
-\label{ssec:LTI}
-%-------------------------------
-
-LTI models in the form: 
-%
-\begin{align}
-\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
-\vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
-\end{align}
-\noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
-$\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
-a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
-(as shown in the appendix) into
-%
-\begin{align}
-\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
-\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
-\end{align}
-%
 \end{document}

### 2017-01-25 cav2017/cav2017.tex

--- 2017-01-25 cav2017/cav2017.tex
@@
 %
+
+%-------------------------------
+\subsection{Objectives}
+%-------------------------------
+
+Using the state-space models given in Section~\ref{experimental-setup}, 
+our experimental evaluation aims to answer two research questions:
+%
+\begin{enumerate}
+
+\item[RQ1] \textbf{(CEGIS)} do the CEGIS with multi-stage 
+verification and abstraction-based generate a FWL digital 
+controller in a reasonable amount of time?
+
+\item[RQ2] \textbf{(sanity check)} are the synthesized controllers sound
+and can their stability and safety be confirmed outside of our model?
+
+\end{enumerate}
+
+%-------------------------------
+\subsection{Results}
+%-------------------------------
+
+We give the run-times required to synthesize a stable controller for each
+benchmark in Table~\ref{tab:results}.  
+Here \textit{Benchmark} is the name of the employed
+benchmark, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used
+to model the plant, while \textit{Time}
+is the total time (in milliseconds) required to synthesize a stable controller
+for the given plant, for CEGIS with multi-staged verification as well as
+abstraction-based CEGIS. The precision for the controller,
+$\mathcal{F}_{\langle I_c,F_c \rangle}$, is always chosen to be $I_c = 8, F_c = 8$.
+
+For the majority of our benchmarks, the conjecture stands that the abstraction-based back-end
+is faster than the basic multi-staged verification approach. However, it does fail to
+find solutions to 3 benchmarks, as compared to 2 with the multi-staged back-end, where
+the numbers given in the discretization matrices are too small. In direct comparison the
+abstraction-based is able to find a solution in approximately 35\% of the time required
+using the multi-staged back-end. The two back-ends complement each other well in their
+benchmark coverage and together solve all benchmarks provided in the set.
+
+\begin{table}
+\centering
+\begin{tabular}{| r | c | c | r | c | r |}
+\hline
+\# & Benchmark  & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
+   &            & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
+1  & Cruise Control      & 8,16   & 6875   & 16,16  & 241    \\
+2  & DC Motor            & 8,16   & 8103   & 20,20  & 5376   \\
+3  & Helicopter          & \xmark & \xmark & 16,16  & 2120   \\
+4  & Inverted Pendulum   & 8,16   & 7813   & 16,16  & 387    \\
+5  & Magnetic Pointer    & \xmark & \xmark & 28,28  & 132845 \\
+6  & Magnetic Suspension & 12,20  & 8727   & 32,32  & 7854   \\
+7  & Pendulum            & 8,16   & 9008   & 20,20  & 1150   \\
+8  & Suspension          & 12,20  & 49410  & \xmark & \xmark \\
+9  & Tape Driver         & 8,16   & 9177   & \xmark & \xmark \\
+10 & Satellite           & 8,16   & 8975   & \xmark & \xmark \\\hline
+
+\end{tabular}
+\caption{Experimental results with runtime in milliseconds. \label{tab:results}}
+\end{table}
+
+The median runtime for our benchmark set is 7.9\,s.  Overall,
+the average synthesis time amounts to approximately 17.2\,s.  We
+consider these times short enough to be of practical use to control
+engineers, and thus affirm RQ1.
+
+The
+synthesized controllers were confirmed to be stable outside of our model
+representation using MATLAB, positively answering RQ2.  A~link to the full
+experimental environment, including scripts to reproduce the results, all
+benchmarks and the tool, is provided in the
+footnote.\footnote{\url{https://drive.google.com/open?id=0ByIexo3Z5N91eDludEdWdWxfV1E}}
+
+%-------------------------------
+\subsection{Threats to validity}
+%-------------------------------
+We report an assessment of both our approaches over a diverse set of real-world benchmarks.
+Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalize to other benchmarks.
+%
+Our algorithm to select suitable FWL word widths to model plant behavior employs a heuristic based on user-provided controller word-width specifications.
+For the first approach, where we may need to increase the precision of the time discretization, we select the time steps for the discretizations on a similar basis.
+This works sufficiently well for our benchmarks, but performance may suffer in some cases, for example if the completeness threshold is high.
+%
+The performance gain from abstract acceleration may not hold for more complex properties than stability, for instance ``eventually always reaches a certain safe set''.
+
+%% %-------------------------------
+%% \section{Related Work}
+%% \label{sec:rw}
+%% %-------------------------------
+
+%-------------------------------
+\section{Conclusions}
+%-------------------------------
+
+We have presented two approaches to synthesize state feedback controllers 
+that ensure both stability and safety over the state-space representation.
+The first approach relies on explicit unfolding of the system's dynamics 
+up to the completeness threshold, whilst the second one applies abstraction 
+refinement and acceleration to increase speed whilst retaining soundness.
+Both approaches are novel in the control system literature in that it puts
+forward a fully automated synthesis approach that is algorithmically and
+numerically sound, considering the various error sources in the implementation 
+of the control algorithm and in the computational modeling of plant dynamics.
+Our experimental results show that both approaches are able
+to synthesize stable controllers in most benchmarks within a reasonable
+amount of time fully automatically.  In particular, both approaches
+complement each other and together solve all benchmarks provided in the set.
+Future work will be the extension of these approaches to consider performance 
+requirements while synthesizing digital controllers.
+
+\newpage
+
+\bibliographystyle{abbrv}
+\bibliography{paper}  
+%\begin{thebibliography}{4}
+%\end{thebibliography}
+
+\newpage
+\appendix
+%-------------------------------
+\section{Stability of closed-loop systems}
+\label{sec:appendix-stability}
+%-------------------------------
+
+%\addtodo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantization noises yet).]}
+
+For a closed-loop system as~\eqref{eq:closedloopss}, 
+the characteristic polynomial $P(z)$ should be computed as follows:
+\begin{equation}
+P(z)= \det( z I_{n} - A_d + B_d K ),
+\end{equation}
+where $I_{n}$ is the n-th order identity matrix.
+
+Jury's criterion provides necessary and sufficient conditions for the eigenvalues 
+to be within the unit circle and, consequently, the system is stable.  Given a 
+polynomial $P(z)$ of the form
+$$
+P(z) = a_{0}z^{N} + a_{1}z^{N-1} + ... a_{N-1}z + a_{N} = 0, a_{0}\neq 0,
+$$
+Jury's criterion explores solely the coefficients ($a_{0},a_{1},...,a_{N-1}$) 
+of $P(z)$ for checking the validity of the stability property $\phi_{stability}$.
+
+In particular, Jury stability test is already explained in the control system 
+literature ({\it e.g.},~\cite{fadali}). This study, however, limits itself to 
+explain the encoding of Jury's criterion for the formal synthesis purpose. 
+For the stability  test procedure, the following Jury matrix 
+$M=[m_{ij}]_{(2N-2)\times N}$ is built  from $P(z)$ coefficients:
+$$
+M=\left[
+\begin{matrix}
+  V^{(0)} \\
+  V^{(1)} \\
+  \vdots \\
+  V^{(N-2)}
+ \end{matrix}
+\right]\mbox{,}
+$$
+\noindent where $V^{(k)}=[v^{(k)}_{ij}]_{2\times N}$ such that
+$$
+v^{(0)}_{ij}=\begin{cases} 
+a_{j-1}, & \mbox{if } i=1 \\   v^{(0)}_{(1)(N-j+1)}, & \mbox{if } i=2 
+\end{cases}\mbox{, and} 
+$$
+$$
+v^{(k)}_{ij}=\begin{cases} 
+0, & \mbox{if } j>n-k\\
+v^{(k-1)}_{1j}-v^{(k-1)}_{2j}\cdot\frac{v^{(k-1)}_{11}}{v^{(k-1)}_{21}}, & \mbox{if } j\leq n-k  \mbox{ and } i=1 \\
+v^{(k)}_{(1)(N-j+1)}, & \mbox{if } j\leq n-k \mbox{ and } i=2 \\
+\end{cases} \mbox{,}
+$$
+\noindent where $k\in\mathbb{Z}$, such that $0<k<N-2$. $P(z)$ is the 
+characteristic polynomial of a stable system if and only if the following 
+four propositions hold:
+\begin{itemize}
+\item $R_{1}$: $P(1)>0$;
+\item $R_{2}$: $(-1)^{N}P(-1)>0$;
+\item $R_{3}$: $\vert{a_{0}}\vert <a_{N}$;
+\item $R_{4}$: $m_{11}>0\iff (m_{31}>0)\wedge (m_{51}>0)\wedge \dots \wedge (m_{(2N-3)(1)>0)}$.
+\end{itemize}
+
+The stability property $\phi_{stability}$ is then encoded as follows:
+$$
+\phi_{stability}\iff \ (R_{1} \wedge R_{2} \wedge R_{3} \wedge R_{4}).
+$$
+
+%-------------------------------
+\subsection{Stability of closed-loop systems with fixed-point controller error}
+%-------------------------------
+
+The proof above relies on the fact that the relationship between states and next states is defined by
+$x_{k+1} = (A_d  - B_dK)*x_k$, all computed at infinite precision. In fact, when we employ a FWL digital controller, 
+the operation becomes:
+\begin{align*}
+x_{k+1} &= A_d * x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
+x_{k+1} &= (A_d  - B_dK)*x_k + B_dK\delta
+%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
+\end{align*}
+where $\delta$ is the maximum error that can be introduced by the FWL controller in one step, i.e., by reading the states values once and multiplying by $K$ once.
+We derive the closed form expression for $x_n$
+
+\begin{align*}
+x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
+x_{2} &= (A_d  - B_dK)((A_d  - B_dK)x_0 + B_dK\delta ) + B_dK\delta \\
+      &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
+x_{3}  &=(A_d  - B_dK)^3x_0 + (A_d  - B_dK)^2B_dK\delta + (A_d  - B_dK)B_dK\delta + B_dK\delta\\
+x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
+  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{i=n-1}(A_d - B_dK)^iB_dk\delta
+\end{align*}
+
+The definition of asymptotic stability is that the system converges to a reference signal, in this case we use no
+reference signal so an asymptotically stable system will converge to the origin. We know that the original system
+with an infinite precision controller is stable, because we have synthesized it to meet Jury's criteria. Hence
+$(A_d  - B_dK)^n*x_0$ must converge to zero.
+
+To show that a fixed point implementation of the same controller will converge to a steady value, we need to show that the infinite sum converges.
+
+A known result is that a power series of matrices converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less than 1, to the following:
+\begin{align*}
+\sum_{i=0}^{\infty}T^i  &= (I - T)^{-1}
+\end{align*}
+Where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge
+
+\begin{align*}
+x_{\infty} &= 0 + (I - A_d + B_dK)^{-1}B_dk\delta
+\end{align*}
+
+Hence, provided $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the safe space, our fixed point controller system is stable, in that it converges to a finite value, although not asymptomatically stable because it doesn't converge to the origin.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{LTI system Transformations and Equivalences} \label{sec:appendix:LTIbackground}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Discretizing continuous space dynamics}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+A dynamical system is a system in which a function describes the progression of a state over time. 
+In a continuous domain with linear dynamics, it is described by a first order Ordinary Differential Equation (ODE).
+\begin{equation}
+\dot{x}(t)=\vec{A}\vec{x}(t)+\vec{B}\vec{u}(t) +\vec{w}(t).
+\label{eq:dynamical}
+\end{equation}
+
+\noindent with $\vec{w} \sim \mathcal{N}(0,Q)$.\\
+Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
+which may restrict the observability of the state-space from the output space.
+\begin{equation}
+\vec{y}(t)=\vec{C}\vec{x}(t)+\vec{D}\vec{u}(t).
+\end{equation}
+
+Discretization of an continuous dynamical system turns the ODE into a difference equation, assuming zero-order hold
+for the input $\vec{u}$ and continuous integration for the noise $\vec{w}$, to
+\begin{align}
+\label{eq:discretization}
+\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d\vec{u}_k + \vec{w}_k,\\
+y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k. 
+\end{align}
+with covariance for $\vec{w}_k \sim \mathcal{N}(0,Q_d)$,
+where
+\begin{align}
+\label{eq:discretize}
+\vec{A}_d &= e^{\vec{A} T_s} = \mathcal{L}^{-1} { ( s \vec{I} - \vec{A} )^{-1} }_{t = T_s},\\
+\vec{B}_d &= \int_{0}^{T_s} e^{\vec{A} t} dt\ \vec{B} = \vec{A}^{-1} ( \vec{A}_d - \vec{I} ) \vec{B},\\
+\vec{C}_d &= \vec{C},\\
+\vec{D}_d &= \vec{D},\\
+Q_d &= \int_{0}^{T_s} e^{\vec{A} t} Q e^{\vec{A}^T t} dt.
+\end{align}
+and $T_s$ is the sample time. Then
+\begin{align*}
+x(kT_s)=x_k \wedge y(kT_s) = y_k, \forall k.
+\end{align*}
+Let $g_d(k)=\mathcal{G}(t,g(t),T)$ be a function that performs the discretization described above, where $g(t)$
+represents the continuous dynamics and $g_d(k)$ the corresponding discrete dynamics. 
+Let $G(s)=\mathcal{L}(g(t))$ and $G_d(z)=\mathcal{Z}(g_d(k))$ be the corresponding Laplace and Z-transforms
+of $g(t)$ and $g_d(k)$. Given this relation, we have 
+$$G_d(z)=G(z)|_{z=e^{sT}} : g_d(k)=\mathcal{G}(t,g(t),T) \wedge T < \frac{1}{.5f_s},$$
+where $.5f_s$ is the Nyquist frequency of $g(t)$. This last restriction is introduced to avoid the effects of aliasing
+which could cause ``phantom poles'' to appear otherwise. 
+The eigenvalues of $\vec{A}_d$ corresponding to the poles of $G_d(z)$, and those of $\vec{A}$ corresponding to the poles of $G(s)$ are similarly related.
+$\hat{\lambda}_i=e^{-\lambda_iT} : \hat{\lambda}_i \in \sigma(\vec{A}_d) \wedge \lambda_i \in \sigma(\vec{A})$
+where $\sigma(\cdot)$ is the spectrum of a matrix.
+The following remark is worth mentioning regarding the above.
+\begin{remark}
+The witnessed maximum amplitude of the discrete signals $x_k,y_k$ may be smaller to that of $x(t),y(t)$ due to synchronism at fraction-frequency sampling.
+This means that reasoning about the state-space must consider the effects of this possibility as well of the case of maximal inputs from the continuous specification.
+\end{remark}
+%  Since \eqref{eq:discretization} is a bi-simulation of \eqref{eq:ode}, we may use the semantics in section \ref{sec:model_semantics} to model continuous dynamical systems.
+
+% %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+% \subsection{Overapproximating continuous space dynamics using discrete models}
+% %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+% Let us recall equation \ref{eq:discretize}. The discrete representation of the system dynamics discretized with sample time $T_1$ is ruled by the formula
+% $\vec{A}_1 = e^{\vec{A} T_1}$. From matrix theory, we have 
+% \begin{equation}
+% \vec{A}_1 = \mat{S}_1\mat{J}_1\mat{S}_1^{-1}= \mat{S}_1e^{\mat{J} T_1}\mat{S}_1^{-1}.
+% \end{equation}
+% Let $\mat{J}$ be a diagonal matrix, such that ${\lambda_1}_i=e^{\lambda_i T_1}, \forall \lambda \in \mat{J}$.
+% Let us now take a different sample rate $T_2$, such that ${\lambda_2}_i=e^{\lambda_i T_2}, \forall \lambda \in \mat{J}$. We can then say that 
+% \begin{equation}
+% {\lambda_2}_i=e^{\lambda_i T_1 T_2/T_1}={\lambda_1}_i^{T_2/T_1} \Rightarrow A_2=A_1^{\frac{T_2}{T_1}}
+% \end{equation}
+% We have also shown in the previous section that $x_k=A^nx_0$ is a witness of $x(t): \dot{x}(t)=Ax(t)$ at time $kT_s$.
+Applying this notion to multiple sample times, we can state that $x_{k_i}=A_i^nx_0$ are a set of witnesses at times $kT_i$, and by extension the set $\{x=A_i^nx_0 : \forall n \in \mathbb{R} \}$ witnesses all states visited by the continuous system in time $t \in [0,\infty)$.
+This applies to any arbitrary sample time $T_i$.
+% Since the controller output is fed to a Zero Order Holder, the progression of the system between times $kT_s$ and $(k+1)T_s$ is $\mat{A}^n\vec{x}_k+\mat{B}\vec{u}_k : n \in (0,1)$.
+We therefore obtain a reach tube for the continuous dynamics of a time sampled system to be contained within the abstract reach tube $\mathcal{A}^1\mathcal{M}X_0+\mathcal{BK}^1\mathcal{M}X_0=\mathcal{M}X_0$
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Modelling quantization as noise} \label{appendix:quantization-noise}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathbb{R}\langle I_{c},F_{c} \rangle$ value.
+this sampling uses a threshold which is defined by the less significant bit ($q_{adc}=2^{-F_{adc}}$) of the ADC and some non-linearities of the circuitry.
+The overall conversion is
+$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{adc}}{2}\right]$$.
+If we denote the error in the conversion as $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
+
+We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (\emph{ie} the quantizer includes any digital gain added in the code).
+The process of quantization in the DAC is similar except that it is going from $\mathbb{R}\langle I_{c},F_{c} \rangle \rightarrow \mathbb{R}\langle I_{dac},F_{dac} \rangle$.
+If these domains are the same ($I_{c}=I_{dac},F_{c}=F_{dac}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
+From the above equations we can now infer that $\nu_1 \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], \nu_2 \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{c} \wedge q_2=q_{dac}$.
+Note that these bounds hold irrespective of whether the noise is correlated, hence we may use them to over-approximate the effect of the noise on the state space progression over time.
+The resulting dynamics are:
+\begin{align}
+\label{eq:pre_quantization}
+\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d(\vec{u}_k+{\vec{\nu}_2}_k) + \vec{w}_k,\\
+y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k+{\vec{\nu}_1}_k. 
+\end{align}
+
+Which, when modelled into closed loop dynamics results in:
+
+\begin{align}
+\label{eq:quantization}
+\vec{x}_{k+1} &= (\vec{A}_d-\vec{B}_d\mat{K}_d\mat{C}_d) \vec{x}_k+\vec{B}_d{\vec{\nu}_2}_k + \vec{w}_k,\\
+y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k+{\vec{\nu}_1}_k. 
+\end{align}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Controllable canonical form} \label{sec:reachable}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Let us have a discrete time SISO system with an $n^{th},m^{th} : n\geq m$ order armax model
+$$y[k]=\sum_{i=1}^n a_iy[k-i]+\sum_{i=0}^m b_iu[k-i],$$
+where $y$ is the output of the system and $u$ its input.
+The equivalent LTI dynamics of such a model are:
+\begin{align}
+\label{eq:cf_SISO}
+\vec{x}_{k+1}=&\mat{A}_{cf}\vec{x}_k+\mat{B}_{cf}u_k : \vec{x}_k=[y_{k-n}\ \hdots y_{k-1}\ y_{k}]^T\\
+y_k=&\mat{C}_{cf}\vec{x}_k + b_0u_k\nonumber\\
+\mat{A}_{cf}=&\left[
+\begin{array}{ccccc}
+0&1&0&\cdots&0\\
+0&0&1&\cdots&0\\
+\vdots&\vdots&\vdots&\ddots&\vdots\\
+0&0&0&\cdots&1\\
+-a_n&-a_{n-1}&-a_{n-2}&\cdots&-a_1
+\end{array}\right],
+\mat{B}_{cf}=\left[
+\begin{array}{c}
+0\\0\\ \vdots\\ 0\\ 1
+\end{array}\right]\nonumber\\
+\mat{C}_{cf}=&[\begin{array}{ccccc}b_n-a_nb_0&b_{n-1}-a_{n-1}b_0&\cdots&b_1-a_1b_0\end{array}] : b_{i \in (m\ n]}=0\nonumber
+\end{align}
+
+where the coefficients $a_i$ describe the characteristic polynomial of the system. This matrix shape is
+called a Controllable Canonical Form because the dynamics of the feedback are directly related to these
+coefficients. Specifically, given a feedback controller $\mat{K}$ for this system, the closed loop dynamics
+will have the shape
+\begin{align}
+\mat{A}_{cf}+\mat{B}_{cf}\mat{K}_{cf}=&\left[
+\begin{array}{ccccc}
+0&1&0&\cdots&0\\
+0&0&1&\cdots&0\\
+\vdots&\vdots&\vdots&\ddots&\vdots\\
+0&0&0&\cdots&1\\
+k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
+\end{array}\right]
+\label{eq:cf_SISO_fb}
+\end{align}
+which means we can directly modify each coefficient by selecting a controller parameter.
+In the MIMO case, the Controllable Canonical Form has the following shape:
+\begin{align}
+\mat{A}_{cf}=&\left[
+\begin{array}{ccccc}
+0&\mat{I}_{n-1}&0&\cdots&0\\
+0&0&\mat{I}_{n-2}&\cdots&0\\
+\vdots&\vdots&\vdots&\ddots&\vdots\\
+0&0&0&\cdots&1\\
+-\mat{a_n}\mat{M}_n&-\mat{a_{n-1}}\mat{M}_{n-1}&-\mat{a_{n-2}}\mat{M}_{n-2}&\cdots&-\mat{a_1}\mat{M}_{1}
+\end{array}\right],
+\mat{B}_{cf}=\left[
+\begin{array}{c}
+0\\0\\ \vdots\\ 0\\ \mat{M}_0
+\end{array}\right]\nonumber\\
+\mat{C}_{cf}=&[\begin{array}{ccccc}\mat{\eta}_n&\mat{\eta}_{n-1}&\cdots&\mat{\eta}_1\end{array}] :
+\mat{I}_i,\mat{M}_i \in \mathbb{R}^{q_i \times q_i} \wedge \mat{a}_i \in \mathbb{R}^{q \times q_i} \wedge \mat{\eta}_i \in \mathbb{R}^o \wedge  \mat{\eta}_{i \in (m\ n]}=0 \nonumber
+\label{eq:cf_MIMO}
+\end{align}
+where $q$ is the number of inputs, $q_i$ the number of inputs with a transfer function of order of at least $i$, $\mat{I}_i$ an identity matrix, $\mat{M}_i$ an upper triangular matrix with 1s in its diagonal, $\mat{a_i}$ a matrix of coefficients of the $i^th$ order on its diagonal, and $o$ the number of outputs.
+Ideally we aim for $\mat{M}_i=\mat{I}_i, \forall i>0$
+
+Any LTI system can be transformed into a controllable canonical form by a matrix $\mat{T} : \vec{x}=\mat{T}\hat{\vec{x}}$
+Then the dynamics of the controllable form are
+\begin{align}
+\hat{\vec{x}}_{k+1}=&\mat{A}_{cf}\hat{\vec{x}}_k+\mat{B}_{cf}u_k : \mat{A}_{cf}=\mat{T}\mat{A}\mat{T}^{-1} \wedge \mat{B}_{cf}=\mat{T}\mat{B}\\
+y_k=&\mat{C}_{cf}\hat{\vec{x}}_k + b_0u_k : \mat{C}_{cf}=\mat{C}\mat{T}^{-1}\nonumber
+\end{align}
+where $\mat{T}$ can be calculated as follows:
+
+Let 
+\begin{equation}
+\mat{R}=[\begin{array}{ccccc}\mat{B}&\mat{A}\mat{B}&\mat{A}^2\mat{B}&\hdots&\mat{A}^{n-1}\mat{B}\end{array}]
+\label{eq:rncf}
+\end{equation}
+be the reachability matrix of the system, and
+\begin{equation}
+\mat{R}_{cf}=\left[\begin{array}{ccccc}1&a_1&a_2&\hdots&a_{n-1}\\0&1&a_1&\hdots&a_{n-2}\\ \vdots&\ddots&\ddots&\ddots&\ddots\end{array}\right]
+\label{eq:rcf}
+\end{equation}
+the reachability matrix of the canonical form. Then 
+\begin{equation}
+\mat{T}=\mat{R}_{cf}\mat{R}^{-1}
+\label{eq:to_cf}
+\end{equation}
+
+% %-------------------------------
+% \section{Extensions}
+% \label{sec:extensions}
+% %-------------------------------
+
+% %-------------------------------
+% \subsection{LTI systems with output} 
+% \label{ssec:LTI}
+% %-------------------------------
+
+% LTI models in the form: 
+% %
+% \begin{align}
+% \dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
+% \vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
+% \end{align}
+% \noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
+% $\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
+% a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
+% (as shown in the appendix) into
+% %
+% \begin{align}
+% \vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
+% \vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
+% \end{align}
+%
+
+%-------------------------------
+\section{Benchmarks for State-Space Physical Plants}
+\label{sec:BenchmarksforStateSpace}
+%-------------------------------
+
 \begin{table}[htb]
@@
 
-%-------------------------------
-\subsection{Objectives}
-%-------------------------------
-
-Using the state-space models given in Section~\ref{experimental-setup}, 
-our experimental evaluation aims to answer two research questions:
-%
-\begin{enumerate}
-
-\item[RQ1] \textbf{(CEGIS)} do the CEGIS with multi-stage 
-verification and abstraction-based generate a FWL digital 
-controller in a reasonable amount of time?
-
-\item[RQ2] \textbf{(sanity check)} are the synthesized controllers sound
-and can their stability and safety be confirmed outside of our model?
-
-\end{enumerate}
-
-%-------------------------------
-\subsection{Results}
-%-------------------------------
-
-We give the run-times required to synthesize a stable controller for each
-benchmark in Table~\ref{tab:results}.  
-Here \textit{Benchmark} is the name of the employed
-benchmark, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used
-to model the plant, while \textit{Time}
-is the total time (in milliseconds) required to synthesize a stable controller
-for the given plant, for CEGIS with multi-staged verification as well as
-abstraction-based CEGIS. The precision for the controller,
-$\mathcal{F}_{\langle I_c,F_c \rangle}$, is always chosen to be $I_c = 8, F_c = 8$.
-
-For the majority of our benchmarks, the conjecture stands that the abstraction-based back-end
-is faster than the basic multi-staged verification approach. However, it does fail to
-find solutions to 3 benchmarks, as compared to 2 with the multi-staged back-end, where
-the numbers given in the discretization matrices are too small. In direct comparison the
-abstraction-based is able to find a solution in approximately 35\% of the time required
-using the multi-staged back-end. The two back-ends complement each other well in their
-benchmark coverage and together solve all benchmarks provided in the set.
-
-\begin{table}
-\centering
-\begin{tabular}{| r | c | c | r | c | r |}
-\hline
-\# & Benchmark  & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
-   &            & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
-1  & Cruise Control      & 8,16   & 6875   & 16,16  & 241    \\
-2  & DC Motor            & 8,16   & 8103   & 20,20  & 5376   \\
-3  & Helicopter          & \xmark & \xmark & 16,16  & 2120   \\
-4  & Inverted Pendulum   & 8,16   & 7813   & 16,16  & 387    \\
-5  & Magnetic Pointer    & \xmark & \xmark & 28,28  & 132845 \\
-6  & Magnetic Suspension & 12,20  & 8727   & 32,32  & 7854   \\
-7  & Pendulum            & 8,16   & 9008   & 20,20  & 1150   \\
-8  & Suspension          & 12,20  & 49410  & \xmark & \xmark \\
-9  & Tape Driver         & 8,16   & 9177   & \xmark & \xmark \\
-10 & Satellite           & 8,16   & 8975   & \xmark & \xmark \\\hline
-
-\end{tabular}
-\caption{Experimental results with runtime in milliseconds. \label{tab:results}}
-\end{table}
-
-The median runtime for our benchmark set is 7.9\,s.  Overall,
-the average synthesis time amounts to approximately 17.2\,s.  We
-consider these times short enough to be of practical use to control
-engineers, and thus affirm RQ1.
-
-The
-synthesized controllers were confirmed to be stable outside of our model
-representation using MATLAB, positively answering RQ2.  A~link to the full
-experimental environment, including scripts to reproduce the results, all
-benchmarks and the tool, is provided in the
-footnote.\footnote{\url{https://drive.google.com/open?id=0ByIexo3Z5N91eDludEdWdWxfV1E}}
-
-%-------------------------------
-\subsection{Threats to validity}
-%-------------------------------
-We report an assessment of both our approaches over a diverse set of real-world benchmarks.
-Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalize to other benchmarks.
-%
-Our algorithm to select suitable FWL word widths to model plant behavior employs a heuristic based on user-provided controller word-width specifications.
-For the first approach, where we may need to increase the precision of the time discretization, we select the time steps for the discretizations on a similar basis.
-This works sufficiently well for our benchmarks, but performance may suffer in some cases, for example if the completeness threshold is high.
-%
-The performance gain from abstract acceleration may not hold for more complex properties than stability, for instance ``eventually always reaches a certain safe set''.
-
-%% %-------------------------------
-%% \section{Related Work}
-%% \label{sec:rw}
-%% %-------------------------------
-
-%-------------------------------
-\section{Conclusions}
-%-------------------------------
-
-We have presented two approaches to synthesize state feedback controllers 
-that ensure both stability and safety over the state-space representation.
-The first approach relies on explicit unfolding of the system's dynamics 
-up to the completeness threshold, whilst the second one applies abstraction 
-refinement and acceleration to increase speed whilst retaining soundness.
-Both approaches are novel in the control system literature in that it puts
-forward a fully automated synthesis approach that is algorithmically and
-numerically sound, considering the various error sources in the implementation 
-of the control algorithm and in the computational modeling of plant dynamics.
-Our experimental results show that both approaches are able
-to synthesize stable controllers in most benchmarks within a reasonable
-amount of time fully automatically.  In particular, both approaches
-complement each other and together solve all benchmarks provided in the set.
-Future work will be the extension of these approaches to consider performance 
-requirements while synthesizing digital controllers.
-
-\newpage
-
-\bibliographystyle{abbrv}
-\bibliography{paper}  
-%\begin{thebibliography}{4}
-%\end{thebibliography}
-
-\newpage
-\appendix
-%-------------------------------
-\section{Stability of closed-loop systems}
-\label{sec:appendix-stability}
-%-------------------------------
-
-%\addtodo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantization noises yet).]}
-
-For a closed-loop system as~\eqref{eq:closedloopss}, 
-the characteristic polynomial $P(z)$ should be computed as follows:
-\begin{equation}
-P(z)= \det( z I_{n} - A_d + B_d K ),
-\end{equation}
-where $I_{n}$ is the n-th order identity matrix.
-
-Jury's criterion provides necessary and sufficient conditions for the eigenvalues 
-to be within the unit circle and, consequently, the system is stable.  Given a 
-polynomial $P(z)$ of the form
-$$
-P(z) = a_{0}z^{N} + a_{1}z^{N-1} + ... a_{N-1}z + a_{N} = 0, a_{0}\neq 0,
-$$
-Jury's criterion explores solely the coefficients ($a_{0},a_{1},...,a_{N-1}$) 
-of $P(z)$ for checking the validity of the stability property $\phi_{stability}$.
-
-In particular, Jury stability test is already explained in the control system 
-literature ({\it e.g.},~\cite{fadali}). This study, however, limits itself to 
-explain the encoding of Jury's criterion for the formal synthesis purpose. 
-For the stability  test procedure, the following Jury matrix 
-$M=[m_{ij}]_{(2N-2)\times N}$ is built  from $P(z)$ coefficients:
-$$
-M=\left[
-\begin{matrix}
-  V^{(0)} \\
-  V^{(1)} \\
-  \vdots \\
-  V^{(N-2)}
- \end{matrix}
-\right]\mbox{,}
-$$
-\noindent where $V^{(k)}=[v^{(k)}_{ij}]_{2\times N}$ such that
-$$
-v^{(0)}_{ij}=\begin{cases} 
-a_{j-1}, & \mbox{if } i=1 \\   v^{(0)}_{(1)(N-j+1)}, & \mbox{if } i=2 
-\end{cases}\mbox{, and} 
-$$
-$$
-v^{(k)}_{ij}=\begin{cases} 
-0, & \mbox{if } j>n-k\\
-v^{(k-1)}_{1j}-v^{(k-1)}_{2j}\cdot\frac{v^{(k-1)}_{11}}{v^{(k-1)}_{21}}, & \mbox{if } j\leq n-k  \mbox{ and } i=1 \\
-v^{(k)}_{(1)(N-j+1)}, & \mbox{if } j\leq n-k \mbox{ and } i=2 \\
-\end{cases} \mbox{,}
-$$
-\noindent where $k\in\mathbb{Z}$, such that $0<k<N-2$. $P(z)$ is the 
-characteristic polynomial of a stable system if and only if the following 
-four propositions hold:
-\begin{itemize}
-\item $R_{1}$: $P(1)>0$;
-\item $R_{2}$: $(-1)^{N}P(-1)>0$;
-\item $R_{3}$: $\vert{a_{0}}\vert <a_{N}$;
-\item $R_{4}$: $m_{11}>0\iff (m_{31}>0)\wedge (m_{51}>0)\wedge \dots \wedge (m_{(2N-3)(1)>0)}$.
-\end{itemize}
-
-The stability property $\phi_{stability}$ is then encoded as follows:
-$$
-\phi_{stability}\iff \ (R_{1} \wedge R_{2} \wedge R_{3} \wedge R_{4}).
-$$
-
-%-------------------------------
-\subsection{Stability of closed-loop systems with fixed-point controller error}
-%-------------------------------
-
-The proof above relies on the fact that the relationship between states and next states is defined by
-$x_{k+1} = (A_d  - B_dK)*x_k$, all computed at infinite precision. In fact, when we employ a FWL digital controller, 
-the operation becomes:
-\begin{align*}
-x_{k+1} &= A_d * x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
-x_{k+1} &= (A_d  - B_dK)*x_k + B_dK\delta
-%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
-\end{align*}
-where $\delta$ is the maximum error that can be introduced by the FWL controller in one step, i.e., by reading the states values once and multiplying by $K$ once.
-We derive the closed form expression for $x_n$
-
-\begin{align*}
-x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
-x_{2} &= (A_d  - B_dK)((A_d  - B_dK)x_0 + B_dK\delta ) + B_dK\delta \\
-      &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
-x_{3}  &=(A_d  - B_dK)^3x_0 + (A_d  - B_dK)^2B_dK\delta + (A_d  - B_dK)B_dK\delta + B_dK\delta\\
-x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
-  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{i=n-1}(A_d - B_dK)^iB_dk\delta
-\end{align*}
-
-The definition of asymptotic stability is that the system converges to a reference signal, in this case we use no
-reference signal so an asymptotically stable system will converge to the origin. We know that the original system
-with an infinite precision controller is stable, because we have synthesized it to meet Jury's criteria. Hence
-$(A_d  - B_dK)^n*x_0$ must converge to zero.
-
-To show that a fixed point implementation of the same controller will converge to a steady value, we need to show that the infinite sum converges.
-
-A known result is that a power series of matrices converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less than 1, to the following:
-\begin{align*}
-\sum_{i=0}^{\infty}T^i  &= (I - T)^{-1}
-\end{align*}
-Where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge
-
-\begin{align*}
-x_{\infty} &= 0 + (I - A_d + B_dK)^{-1}B_dk\delta
-\end{align*}
-
-Hence, provided $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the safe space, our fixed point controller system is stable, in that it converges to a finite value, although not asymptomatically stable because it doesn't converge to the origin.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{LTI system Transformations and Equivalences} \label{sec:appendix:LTIbackground}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Discretizing continuous space dynamics}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-A dynamical system is a system in which a function describes the progression of a state over time. 
-In a continuous domain with linear dynamics, it is described by a first order Ordinary Differential Equation (ODE).
-\begin{equation}
-\dot{x}(t)=\vec{A}\vec{x}(t)+\vec{B}\vec{u}(t) +\vec{w}(t).
-\label{eq:dynamical}
-\end{equation}
-
-\noindent with $\vec{w} \sim \mathcal{N}(0,Q)$.\\
-Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
-which may restrict the observability of the state-space from the output space.
-\begin{equation}
-\vec{y}(t)=\vec{C}\vec{x}(t)+\vec{D}\vec{u}(t).
-\end{equation}
-
-Discretization of an continuous dynamical system turns the ODE into a difference equation, assuming zero-order hold
-for the input $\vec{u}$ and continuous integration for the noise $\vec{w}$, to
-\begin{align}
-\label{eq:discretization}
-\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d\vec{u}_k + \vec{w}_k,\\
-y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k. 
-\end{align}
-with covariance for $\vec{w}_k \sim \mathcal{N}(0,Q_d)$,
-where
-\begin{align}
-\label{eq:discretize}
-\vec{A}_d &= e^{\vec{A} T_s} = \mathcal{L}^{-1} { ( s \vec{I} - \vec{A} )^{-1} }_{t = T_s},\\
-\vec{B}_d &= \int_{0}^{T_s} e^{\vec{A} t} dt\ \vec{B} = \vec{A}^{-1} ( \vec{A}_d - \vec{I} ) \vec{B},\\
-\vec{C}_d &= \vec{C},\\
-\vec{D}_d &= \vec{D},\\
-Q_d &= \int_{0}^{T_s} e^{\vec{A} t} Q e^{\vec{A}^T t} dt.
-\end{align}
-and $T_s$ is the sample time. Then
-\begin{align*}
-x(kT_s)=x_k \wedge y(kT_s) = y_k, \forall k.
-\end{align*}
-Let $g_d(k)=\mathcal{G}(t,g(t),T)$ be a function that performs the discretization described above, where $g(t)$
-represents the continuous dynamics and $g_d(k)$ the corresponding discrete dynamics. 
-Let $G(s)=\mathcal{L}(g(t))$ and $G_d(z)=\mathcal{Z}(g_d(k))$ be the corresponding Laplace and Z-transforms
-of $g(t)$ and $g_d(k)$. Given this relation, we have 
-$$G_d(z)=G(z)|_{z=e^{sT}} : g_d(k)=\mathcal{G}(t,g(t),T) \wedge T < \frac{1}{.5f_s},$$
-where $.5f_s$ is the Nyquist frequency of $g(t)$. This last restriction is introduced to avoid the effects of aliasing
-which could cause ``phantom poles'' to appear otherwise. 
-The eigenvalues of $\vec{A}_d$ corresponding to the poles of $G_d(z)$, and those of $\vec{A}$ corresponding to the poles of $G(s)$ are similarly related.
-$\hat{\lambda}_i=e^{-\lambda_iT} : \hat{\lambda}_i \in \sigma(\vec{A}_d) \wedge \lambda_i \in \sigma(\vec{A})$
-where $\sigma(\cdot)$ is the spectrum of a matrix.
-The following remark is worth mentioning regarding the above.
-\begin{remark}
-The witnessed maximum amplitude of the discrete signals $x_k,y_k$ may be smaller to that of $x(t),y(t)$ due to synchronism at fraction-frequency sampling.
-This means that reasoning about the state-space must consider the effects of this possibility as well of the case of maximal inputs from the continuous specification.
-\end{remark}
-%  Since \eqref{eq:discretization} is a bi-simulation of \eqref{eq:ode}, we may use the semantics in section \ref{sec:model_semantics} to model continuous dynamical systems.
-
-% %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-% \subsection{Overapproximating continuous space dynamics using discrete models}
-% %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-% Let us recall equation \ref{eq:discretize}. The discrete representation of the system dynamics discretized with sample time $T_1$ is ruled by the formula
-% $\vec{A}_1 = e^{\vec{A} T_1}$. From matrix theory, we have 
-% \begin{equation}
-% \vec{A}_1 = \mat{S}_1\mat{J}_1\mat{S}_1^{-1}= \mat{S}_1e^{\mat{J} T_1}\mat{S}_1^{-1}.
-% \end{equation}
-% Let $\mat{J}$ be a diagonal matrix, such that ${\lambda_1}_i=e^{\lambda_i T_1}, \forall \lambda \in \mat{J}$.
-% Let us now take a different sample rate $T_2$, such that ${\lambda_2}_i=e^{\lambda_i T_2}, \forall \lambda \in \mat{J}$. We can then say that 
-% \begin{equation}
-% {\lambda_2}_i=e^{\lambda_i T_1 T_2/T_1}={\lambda_1}_i^{T_2/T_1} \Rightarrow A_2=A_1^{\frac{T_2}{T_1}}
-% \end{equation}
-% We have also shown in the previous section that $x_k=A^nx_0$ is a witness of $x(t): \dot{x}(t)=Ax(t)$ at time $kT_s$.
-Applying this notion to multiple sample times, we can state that $x_{k_i}=A_i^nx_0$ are a set of witnesses at times $kT_i$, and by extension the set $\{x=A_i^nx_0 : \forall n \in \mathbb{R} \}$ witnesses all states visited by the continuous system in time $t \in [0,\infty)$.
-This applies to any arbitrary sample time $T_i$.
-% Since the controller output is fed to a Zero Order Holder, the progression of the system between times $kT_s$ and $(k+1)T_s$ is $\mat{A}^n\vec{x}_k+\mat{B}\vec{u}_k : n \in (0,1)$.
-We therefore obtain a reach tube for the continuous dynamics of a time sampled system to be contained within the abstract reach tube $\mathcal{A}^1\mathcal{M}X_0+\mathcal{BK}^1\mathcal{M}X_0=\mathcal{M}X_0$
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Modelling quantization as noise} \label{appendix:quantization-noise}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathbb{R}\langle I_{c},F_{c} \rangle$ value.
-this sampling uses a threshold which is defined by the less significant bit ($q_{adc}=2^{-F_{adc}}$) of the ADC and some non-linearities of the circuitry.
-The overall conversion is
-$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{adc}}{2}\right]$$.
-If we denote the error in the conversion as $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
-
-We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (\emph{ie} the quantizer includes any digital gain added in the code).
-The process of quantization in the DAC is similar except that it is going from $\mathbb{R}\langle I_{c},F_{c} \rangle \rightarrow \mathbb{R}\langle I_{dac},F_{dac} \rangle$.
-If these domains are the same ($I_{c}=I_{dac},F_{c}=F_{dac}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
-From the above equations we can now infer that $\nu_1 \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], \nu_2 \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{c} \wedge q_2=q_{dac}$.
-Note that these bounds hold irrespective of whether the noise is correlated, hence we may use them to over-approximate the effect of the noise on the state space progression over time.
-The resulting dynamics are:
-\begin{align}
-\label{eq:pre_quantization}
-\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d(\vec{u}_k+{\vec{\nu}_2}_k) + \vec{w}_k,\\
-y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k+{\vec{\nu}_1}_k. 
-\end{align}
-
-Which, when modelled into closed loop dynamics results in:
-
-\begin{align}
-\label{eq:quantization}
-\vec{x}_{k+1} &= (\vec{A}_d-\vec{B}_d\mat{K}_d\mat{C}_d) \vec{x}_k+\vec{B}_d{\vec{\nu}_2}_k + \vec{w}_k,\\
-y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k+{\vec{\nu}_1}_k. 
-\end{align}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Controllable canonical form} \label{sec:reachable}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Let us have a discrete time SISO system with an $n^{th},m^{th} : n\geq m$ order armax model
-$$y[k]=\sum_{i=1}^n a_iy[k-i]+\sum_{i=0}^m b_iu[k-i],$$
-where $y$ is the output of the system and $u$ its input.
-The equivalent LTI dynamics of such a model are:
-\begin{align}
-\label{eq:cf_SISO}
-\vec{x}_{k+1}=&\mat{A}_{cf}\vec{x}_k+\mat{B}_{cf}u_k : \vec{x}_k=[y_{k-n}\ \hdots y_{k-1}\ y_{k}]^T\\
-y_k=&\mat{C}_{cf}\vec{x}_k + b_0u_k\nonumber\\
-\mat{A}_{cf}=&\left[
-\begin{array}{ccccc}
-0&1&0&\cdots&0\\
-0&0&1&\cdots&0\\
-\vdots&\vdots&\vdots&\ddots&\vdots\\
-0&0&0&\cdots&1\\
--a_n&-a_{n-1}&-a_{n-2}&\cdots&-a_1
-\end{array}\right],
-\mat{B}_{cf}=\left[
-\begin{array}{c}
-0\\0\\ \vdots\\ 0\\ 1
-\end{array}\right]\nonumber\\
-\mat{C}_{cf}=&[\begin{array}{ccccc}b_n-a_nb_0&b_{n-1}-a_{n-1}b_0&\cdots&b_1-a_1b_0\end{array}] : b_{i \in (m\ n]}=0\nonumber
-\end{align}
-
-where the coefficients $a_i$ describe the characteristic polynomial of the system. This matrix shape is
-called a Controllable Canonical Form because the dynamics of the feedback are directly related to these
-coefficients. Specifically, given a feedback controller $\mat{K}$ for this system, the closed loop dynamics
-will have the shape
-\begin{align}
-\mat{A}_{cf}+\mat{B}_{cf}\mat{K}_{cf}=&\left[
-\begin{array}{ccccc}
-0&1&0&\cdots&0\\
-0&0&1&\cdots&0\\
-\vdots&\vdots&\vdots&\ddots&\vdots\\
-0&0&0&\cdots&1\\
-k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
-\end{array}\right]
-\label{eq:cf_SISO_fb}
-\end{align}
-which means we can directly modify each coefficient by selecting a controller parameter.
-In the MIMO case, the Controllable Canonical Form has the following shape:
-\begin{align}
-\mat{A}_{cf}=&\left[
-\begin{array}{ccccc}
-0&\mat{I}_{n-1}&0&\cdots&0\\
-0&0&\mat{I}_{n-2}&\cdots&0\\
-\vdots&\vdots&\vdots&\ddots&\vdots\\
-0&0&0&\cdots&1\\
--\mat{a_n}\mat{M}_n&-\mat{a_{n-1}}\mat{M}_{n-1}&-\mat{a_{n-2}}\mat{M}_{n-2}&\cdots&-\mat{a_1}\mat{M}_{1}
-\end{array}\right],
-\mat{B}_{cf}=\left[
-\begin{array}{c}
-0\\0\\ \vdots\\ 0\\ \mat{M}_0
-\end{array}\right]\nonumber\\
-\mat{C}_{cf}=&[\begin{array}{ccccc}\mat{\eta}_n&\mat{\eta}_{n-1}&\cdots&\mat{\eta}_1\end{array}] :
-\mat{I}_i,\mat{M}_i \in \mathbb{R}^{q_i \times q_i} \wedge \mat{a}_i \in \mathbb{R}^{q \times q_i} \wedge \mat{\eta}_i \in \mathbb{R}^o \wedge  \mat{\eta}_{i \in (m\ n]}=0 \nonumber
-\label{eq:cf_MIMO}
-\end{align}
-where $q$ is the number of inputs, $q_i$ the number of inputs with a transfer function of order of at least $i$, $\mat{I}_i$ an identity matrix, $\mat{M}_i$ an upper triangular matrix with 1s in its diagonal, $\mat{a_i}$ a matrix of coefficients of the $i^th$ order on its diagonal, and $o$ the number of outputs.
-Ideally we aim for $\mat{M}_i=\mat{I}_i, \forall i>0$
-
-Any LTI system can be transformed into a controllable canonical form by a matrix $\mat{T} : \vec{x}=\mat{T}\hat{\vec{x}}$
-Then the dynamics of the controllable form are
-\begin{align}
-\hat{\vec{x}}_{k+1}=&\mat{A}_{cf}\hat{\vec{x}}_k+\mat{B}_{cf}u_k : \mat{A}_{cf}=\mat{T}\mat{A}\mat{T}^{-1} \wedge \mat{B}_{cf}=\mat{T}\mat{B}\\
-y_k=&\mat{C}_{cf}\hat{\vec{x}}_k + b_0u_k : \mat{C}_{cf}=\mat{C}\mat{T}^{-1}\nonumber
-\end{align}
-where $\mat{T}$ can be calculated as follows:
-
-Let 
-\begin{equation}
-\mat{R}=[\begin{array}{ccccc}\mat{B}&\mat{A}\mat{B}&\mat{A}^2\mat{B}&\hdots&\mat{A}^{n-1}\mat{B}\end{array}]
-\label{eq:rncf}
-\end{equation}
-be the reachability matrix of the system, and
-\begin{equation}
-\mat{R}_{cf}=\left[\begin{array}{ccccc}1&a_1&a_2&\hdots&a_{n-1}\\0&1&a_1&\hdots&a_{n-2}\\ \vdots&\ddots&\ddots&\ddots&\ddots\end{array}\right]
-\label{eq:rcf}
-\end{equation}
-the reachability matrix of the canonical form. Then 
-\begin{equation}
-\mat{T}=\mat{R}_{cf}\mat{R}^{-1}
-\label{eq:to_cf}
-\end{equation}
-
-% %-------------------------------
-% \section{Extensions}
-% \label{sec:extensions}
-% %-------------------------------
-
-% %-------------------------------
-% \subsection{LTI systems with output} 
-% \label{ssec:LTI}
-% %-------------------------------
-
-% LTI models in the form: 
-% %
-% \begin{align}
-% \dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\ \ :\ \ \vec{x} \in \mathbb{R}^{n}, \vec{u} \in \mathbb{R}^m, \mat{A} \in \mathbb{R}^{n \times n},\mat{B} \in \mathbb{R}^{n \times m}\\
-% \vec{y}(t)&=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)\ \ :\ \ \vec{y} \in \mathbb{R}^{o}, \mat{C} \in \mathbb{R}^{o \times n}, \mat{D}  \in \mathbb{R}^{o \times m}\nonumber
-% \end{align}
-% \noindent where $\dot{\vec{x}}(t)$ describes the state evolution equation; 
-% $\vec{y}(t)$ represents an instantaneous output equation; and $\mat{A}$, $\mat{B}$, $\mat{C}$, and $\mat{D}$ are matrices that fully specify 
-% a continuous plant. Eq.~\eqref{eq:ode} is soundly discretized 
-% (as shown in the appendix) into
-% %
-% \begin{align}
-% \vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
-% \vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k .\nonumber
-% \end{align}
-%
 \end{document}

### 2017-01-25 cav2017/cav2017.tex
conc

@@
 Future work will be the extension of these approaches to consider performance 
-requirements while synthesizing digital controllers.
+requirements while synthesizing digital controllers and the application of them
+for synthesizing state observers that generally appears in state feedback 
+architecture.
 

### 2017-01-25 cav2017/cav2017.tex
squeeze paragraph

--- 2017-01-25 cav2017/cav2017.tex
@@
 \item The third {\sc verify} stage, {\sc complete}, checks that the
-current $k$ is large enough to ensure that the boundaries are not
-violated for any $k'{>}k$.  For this purpose, we compute the
+current $k$ is large enough to ensure that boundaries are not
+violated for any $k'{>}k$.  Here, we compute the
 completeness threshold $\overline{k}$ for the current candidate $K$
-and check that $k{\leq}\overline{k}$. This is done according to the following argument, depicted in Fig \ref{fig:ct}.
+and check that $k{\leq}\overline{k}$. This is done according to the following argument, 
+shown in Fig~\ref{fig:ct}.
 
 A stable control system is known to have converging dynamics. 
-Assume the closed-loop matrix eigenvalues are not repeated (which is sensible to do, since we select them). 
-The distance of trajectories from the reference point (in this case the origin) decreases over time within subspaces related to real-valued eigenvalues;  
+Assume the closed-loop matrix eigenvalues are not repeated 
+(which is sensible to do, since we select them). 
+The trajectories distance from the reference point (in this case the origin) 
+decreases over time within subspaces related to real-valued eigenvalues;  
 however, this in general not the case when dealing with complex eigenvalues.  
 Consider the closed-loop matrix, which updates the states every discrete time step, 
-and select the eigenvalue with smallest (non trivial) imaginary value -- call such value $\vartheta$. 
+and select the eigenvalue with smallest (non-trivial) imaginary value -- call such value $\vartheta$. 
 At every consecutive time steps $kT_s, (k+1)T_s$ ($T_s$ being the sampling time), 
@@
 So taking $k$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, 
-surely after $k$ steps we have completed a full rotation, which results in a point that is closer to the origin. 
-This $k$ is then taken to be the completeness threshold.
+after $k$ steps we have completed a full rotation, which results in a point that is closer to the origin. 
+This $k$ is taken to be the completeness threshold.
 

### 2017-01-25 cav2017/cav2017.tex
squeeze paragraph
minor change

@@
 \item The third {\sc verify} stage, {\sc complete}, checks that the
-current $k$ is large enough to ensure that boundaries are not
-violated for any $k'{>}k$.  Here, we compute the
+current $k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
 completeness threshold $\overline{k}$ for the current candidate $K$
@@
 
-We give the run-times required to synthesize a stable controller for each
-benchmark in Table~\ref{tab:results}.  
-Here \textit{Benchmark} is the name of the employed
+We give the run-times required to synthesize a stable controller for all our
+benchmarks. Here \textit{Benchmark} is the name of the employed
 benchmark, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used

### 2017-01-25 cav2017/cav2017.tex
sec 4

@@
 (which is sensible to do, since we select them). 
-The trajectories distance from the reference point (in this case the origin) 
+The trajectories distance from the reference point (origin) 
 decreases over time within subspaces related to real-valued eigenvalues;  
@@
 Consider the closed-loop matrix, which updates the states every discrete time step, 
-and select the eigenvalue with smallest (non-trivial) imaginary value -- call such value $\vartheta$. 
-At every consecutive time steps $kT_s, (k+1)T_s$ ($T_s$ being the sampling time), 
+and select the eigenvalue $\vartheta$ with smallest (non-trivial) imaginary value. 
+At every consecutive time steps $kT_s, (k+1)T_s$, 
 the dynamics projected on the corresponding eigenspace rotate of $\vartheta T_s$ radiants.  
-So taking $k$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, 
-after $k$ steps we have completed a full rotation, which results in a point that is closer to the origin. 
-This $k$ is taken to be the completeness threshold.
+So taking $k{\leq}\overline{k}$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, 
+after $k{\leq}\overline{k}$ steps we have completed a full rotation, which results in a point closer to the origin, and it is the completeness threshold.
 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{ct.eps}
+\includegraphics[width=0.6\textwidth]{ct.eps}
 \vspace{0.1cm}
@@
 
-We give the run-times required to synthesize a stable controller for all our
-benchmarks. Here \textit{Benchmark} is the name of the employed
+We give the run-times required to synthesize a stable controller for each
+benchmark in Table~\ref{tab:results}.  
+Here \textit{Benchmark} is the name of the employed
 benchmark, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used

### 2017-01-25 cav2017/cav2017.tex
remove completeness claim from intro

@@
 We describe and evaluate two approaches for synthesizing digital controllers for state-space physical plants, 
-both based on the CounterExample Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use for program synthesis.   
-We provide two alternative automated procedures to synthesise safe digital state-feedback controls, 
-and alongside completeness \todo{are we actually complete?
-for instance, abstraction refinement might not be successful (we do TO)} we prove their soundness by encompassing errors due to digitalisation and quantisation effects that are present in the digital controller interacting with the continuous plant.
+both based on the Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use for program synthesis.   
+We provide two alternative automated procedures to synthesise safe 
+digital state-feedback controls
+and prove their soundness by encompassing errors due to digitalisation and quantisation effects that are present in the digital controller interacting with the continuous plant. 
 % computations and representations of dynamics, providing sufficient conditions for sound and complete safe solutions for the state feedback control problem.
@@
 We provide experimental results 
+showing that both approaches are able to efficiently synthesize stable and safe controllers 
+for a set of intricate physical plant models taken from the digital 
+control literature: the median runtime for our benchmark
+set is $7.9$ seconds, and most controllers can be synthesized in less
+than $17.2$ seconds.
+
+We implemented both our approaches and provide experimental proof 
+that, while the naive approach does manage to synthesize 
+stable and sound controllers for the majority of our benchmarks
+for a set of intricate physical plant models taken from the digital 
+control literature
+
+it is an order of magniture slower than the abstraction-based one.
+
 showing that both approaches are able to efficiently synthesize stable and safe controllers 

### 2017-01-25 cav2017/cav2017.tex
minor change

@@
 the entries of matrix $K$, so that the closed-loop dynamics are shaped as
-desired.  A detailed description of this specification can be found in
-Appendix~\ref{sec:appendix-stability}.
+desired (see Appendix~\ref{sec:appendix-stability} for details.
 

### 2017-01-25 cav2017/cav2017.tex
fixed my intro pb

@@
 We provide experimental results 
-showing that both approaches are able to efficiently synthesize stable and safe controllers 
-for a set of intricate physical plant models taken from the digital 
-control literature: the median runtime for our benchmark
-set is $7.9$ seconds, and most controllers can be synthesized in less
-than $17.2$ seconds.
-
-We implemented both our approaches and provide experimental proof 
-that, while the naive approach does manage to synthesize 
-stable and sound controllers for the majority of our benchmarks
-for a set of intricate physical plant models taken from the digital 
-control literature
-
-it is an order of magniture slower than the abstraction-based one.
-
 showing that both approaches are able to efficiently synthesize stable and safe controllers 

### 2017-01-25 cav2017/cav2017.tex
Stressed time benefit in experimental section
Added head-to-head comparison of median time.

@@
 find solutions to 3 benchmarks, as compared to 2 with the multi-staged back-end, where
-the numbers given in the discretization matrices are too small. In direct comparison the
-abstraction-based is able to find a solution in approximately 35\% of the time required
-using the multi-staged back-end. The two back-ends complement each other well in their
-benchmark coverage and together solve all benchmarks provided in the set.
+the numbers given in the discretization matrices are too small. In direct comparison, the
+abstraction-based approach is on average able to find a solution in approximately 35\% of
+the time required using the multi-staged back-end, and has a median runtime 1.15\,s, which is
+seven times smaller than the multi-staged approach. The two back-ends complement each other
+in benchmark coverage and together solve all benchmarks in the set.
 

### 2017-01-25 cav2017/cav2017.tex
resize tables and algs
paper beautification

--- 2017-01-25 cav2017/cav2017.tex
@@
 the entries of matrix $K$, so that the closed-loop dynamics are shaped as
-desired (see Appendix~\ref{sec:appendix-stability} for details.
+desired.  A detailed description of this specification can be found in
+Appendix~\ref{sec:appendix-stability}.
 
@@
 Jury's criterion provides necessary and sufficient conditions for the eigenvalues 
-to be within the unit circle and, consequently, the system is stable.  Given a 
+to be within the unit circle and, consequently, for the system is stable.  
+It is a known stability test from the control system literature~\cite{fadali}.  
+Given a 
 polynomial $P(z)$ of the form
 $$
-P(z) = a_{0}z^{N} + a_{1}z^{N-1} + ... a_{N-1}z + a_{N} = 0, a_{0}\neq 0,
+P(z) = a_{0}z^{N} + a_{1}z^{N-1} + ... a_{N-1}z + a_{N} = 0, \;\; a_{0}\neq 0,
 $$
 Jury's criterion explores solely the coefficients ($a_{0},a_{1},...,a_{N-1}$) 
-of $P(z)$ for checking the validity of the stability property $\phi_{stability}$.
-
-In particular, Jury stability test is already explained in the control system 
-literature ({\it e.g.},~\cite{fadali}). This study, however, limits itself to 
+of $P(z)$ for checking stability, which we encompass as property $\phi_{stability}$.
+
+This study, however, limits itself to 
 explain the encoding of Jury's criterion for the formal synthesis purpose. 

### 2017-01-25 cav2017/cav2017.tex
q3 explanation

--- 2017-01-25 cav2017/cav2017.tex
@@
 
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+aazZ%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsection{Numeric representations and soundness} 
@@
 \begin{algorithm}[]
+\scriptsize
 \begin{algorithmic}[1]
@@
 \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
+where $q3$ is the maximum truncation and rounding error of $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}
 More details on how to model quantization as noise are given in the 
@@
 \centering
+\scriptsize
 \begin{tabular}{| r | c | c | r | c | r |}

### 2017-01-25 cav2017/cav2017.tex

@@
 
-aazZ%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsection{Numeric representations and soundness} 
@@
 \begin{algorithm}[]
-\scriptsize
 \begin{algorithmic}[1]
@@
 \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
-where $q3$ is the maximum truncation and rounding error of $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}
 More details on how to model quantization as noise are given in the 
@@
 \centering
-\scriptsize
 \begin{tabular}{| r | c | c | r | c | r |}

### 2017-01-25 cav2017/cav2017.tex
paper beautification

@@
 %-------------------------------
-\section{Stability of closed-loop systems}
+\section{Stability of closed-loop models}
 \label{sec:appendix-stability}
@@
 %\addtodo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantization noises yet).]}
+
+%-------------------------------
+\subsection{Encoding of Jury's criterion}
+%-------------------------------
 
@@
 Jury's criterion explores solely the coefficients ($a_{0},a_{1},...,a_{N-1}$) 
-of $P(z)$ for checking stability, which we encompass as property $\phi_{stability}$.
-
-This study, however, limits itself to 
-explain the encoding of Jury's criterion for the formal synthesis purpose. 
-For the stability  test procedure, the following Jury matrix 
+of $P(z)$ for checking stability, which we encompass as property $\phi_{stability}$, as detailed below.
+
+This study limits itself to explain the encoding of Jury's criterion for formal synthesis.  
+For the stability  test procedure, the following matrix 
 $M=[m_{ij}]_{(2N-2)\times N}$ is built  from $P(z)$ coefficients:
@@
 $$
-\noindent where $V^{(k)}=[v^{(k)}_{ij}]_{2\times N}$ such that
+\noindent where $V^{(k)}=[v^{(k)}_{ij}]_{2\times N}$ is such that
 $$
@@
 \end{itemize}
-
-The stability property $\phi_{stability}$ is then encoded as follows:
+In conclusion, the stability property $\phi_{stability}$ is encoded as the following formula:
 $$

### 2017-01-25 cav2017/cav2017.tex
minor change

@@
 which performs operations in the domain of fixed-point numbers. 
-In this section we formally outline the errors introduced by the fixed-point representation of numbers~\cite{DBLP:conf/arith/BrainTRW15}. 
+In this section we formally outline the errors introduced by the fixed-point representation of numbers. 
 % 
@@
 The smallest number that can be represented in this domain is $c_m=2^{-F}$.
-
-The following approximation errors will arise:
-\begin{enumerate}
-\item {\bf Truncation:}
-Let $x$ be a real number, and $\mathcal{F}_{\langle I,F \rangle}(x)$ be the same number represented in a fixed-point domain as above. 
-Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the error $ \delta_T=x\ \%_{c_m}\ \tilde x$, and $\%_{c_m}$ is the modulus operation performed on the last bit.
-
-So $\delta_T$ is the truncation error and it will propagate across operations.
-\item {\bf Rounding:}
-The following errors appear in simple operations.
-Let $c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be the truncation errors caused by representing $c_1$ and $c_2$ in the fixed-point domain as above.
-\begin{enumerate}
-\item Addition/Subtraction: these operations only propagate errors coming from truncation of the operands, namely 
-$\mathcal{F}_{\langle I,F \rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3$ with $|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
-\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) * \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3| \leq |\delta_{T1}*\mathcal{F}_{\langle I,F \rangle}(c_2)| + |\delta_{T2}*\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
-\item Division: the operations performed by our controllers in the FWL domain do not include division, so these bounds are inconsequential to this paper. 
-\end{enumerate}
-
-\item {\bf Overflow:}
-The maximum size of a real number $x$ that can be represented in a fixed point domain as $\mathcal{F}_{\langle I,F \rangle}(x)$ is $\pm (2^{I-1}+1-2^{-F})$.
-Numbers outside this range cannot be represented by the domain.
-We check that overflow does not occur.
-
-\end{enumerate}
+Any mathematical operations performed at the precision $\mathcal{F}_{\langle I,F \rangle}(x)$ will introduce errors, that can be upper bounded~\cite{DBLP:conf/arith/BrainTRW15}.
+Further details are in Appendix~\ref{appendix:numerical_errors}.
 
@@
  when the stability is ensured by synthesis, and then verify its safety accounting for the finite-precision errors. 
-
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 and allows relative motion between both parts.
-\textit{Computer Tape Driver} plant describes a physical model to read and write data 
+\textit{Computer Tape Driver} plant describes a system to read and write data 
 on a storage device in the computer.
@@
 in order to obtain an estimate of the states from the single output. 
-Further extensions of this work can include 
+Further work can include 
 state observers synthesis.
@@
 \end{remark}
+
+\subsection{Errors due to numerical representation} \label{appendix:numerical_errors}
+
+Let $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part.
+The smallest number that can be represented in this domain is $c_m=2^{-F}$.
+The following approximation errors will arise in mathematical operations and representation:
+\begin{enumerate}
+\item {\bf Truncation:}
+Let $x$ be a real number, and $\mathcal{F}_{\langle I,F \rangle}(x)$ be the same number represented in a fixed-point domain as above. 
+Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the error $ \delta_T=x\ \%_{c_m}\ \tilde x$, and $\%_{c_m}$ is the modulus operation performed on the last bit.
+
+So $\delta_T$ is the truncation error and it will propagate across operations.
+\item {\bf Rounding:}
+The following errors appear in simple operations.
+Let $c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be the truncation errors caused by representing $c_1$ and $c_2$ in the fixed-point domain as above.
+\begin{enumerate}
+\item Addition/Subtraction: these operations only propagate errors coming from truncation of the operands, namely 
+$\mathcal{F}_{\langle I,F \rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3$ with $|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
+\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) * \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3| \leq |\delta_{T1}*\mathcal{F}_{\langle I,F \rangle}(c_2)| + |\delta_{T2}*\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
+\item Division: the operations performed by our controllers in the FWL domain do not include division.
+However, we do use division in computations at the precision of the plant.
+$\mathcal{F}_{\langle I,F \rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3| \leq $, where $c_m=2^{-F}$ as above.
+\end{enumerate}
+
+\item {\bf Overflow:}
+The maximum size of a real number $x$ that can be represented in a fixed point domain as $\mathcal{F}_{\langle I,F \rangle}(x)$ is $\pm (2^{I-1}+1-2^{-F})$.
+Numbers outside this range cannot be represented by the domain.
+We check that overflow does not occur.
+
+\end{enumerate}
+
 %  Since \eqref{eq:discretization} is a bi-simulation of \eqref{eq:ode}, we may use the semantics in section \ref{sec:model_semantics} to model continuous dynamical systems.

### 2017-01-25 cav2017/cav2017.tex
shuffle num rep to appendix

@@
 and allows relative motion between both parts.
-\textit{Computer Tape Driver} plant describes a system to read and write data 
+\textit{Computer Tape Driver} plant describes a physical model to read and write data 
 on a storage device in the computer.
@@
 in order to obtain an estimate of the states from the single output. 
-Further work can include 
+Further extensions of this work can include 
 state observers synthesis.

### 2017-01-25 cav2017/cav2017.tex
split init contraints into init and input

--- 2017-01-25 cav2017/cav2017.tex
@@
 
-Furthermore, it is practically relevant to consider constraints on the input
-signal $u_{k}$ and bounds on the initial states $x_0$,
-which we assume have given bounds. %%  $\overline{u}$, $\underline{u}$
-%% and $\overline{x_0}$, $\underline{x_0}$, respectively.
-We refer to these constraints as $\phi_{init}$: \todo{input constraints should not be called 'init'}
-$$\phi_{init} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} 
-\wedge \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$$  
+Furthermore, it is practically relevant to consider the 
+constraints $\phi_{init}$ on the input
+signal $u_{k}$ and $\phi_{input}$ on the initial states $x_0$,
+which we assume have given bounds:
+$\phi_{init} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
+$\phi_{input} = \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$
 In the first case, this means that the control input saturates in view of

### 2017-01-25 cav2017/cav2017.tex
updated benchmarks' table

--- 2017-01-25 cav2017/cav2017.tex
@@
 The smallest number that can be represented in this domain is $c_m=2^{-F}$.
-Any mathematical operations performed at the precision $\mathcal{F}_{\langle I,F \rangle}(x)$ will introduce errors, that can be upper bounded~\cite{DBLP:conf/arith/BrainTRW15}.
-Further details are in Appendix~\ref{appendix:numerical_errors}.
+
+The following approximation errors will arise:
+\begin{enumerate}
+\item {\bf Truncation:}
+Let $x$ be a real number, and $\mathcal{F}_{\langle I,F \rangle}(x)$ be the same number represented in a fixed-point domain as above. 
+Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the error $ \delta_T=x\ \%_{c_m}\ \tilde x$, and $\%_{c_m}$ is the modulus operation performed on the last bit.
+
+So $\delta_T$ is the truncation error and it will propagate across operations.
+\item {\bf Rounding:}
+The following errors appear in simple operations.
+Let $c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be the truncation errors caused by representing $c_1$ and $c_2$ in the fixed-point domain as above.
+\begin{enumerate}
+\item Addition/Subtraction: these operations only propagate errors coming from truncation of the operands, namely 
+$\mathcal{F}_{\langle I,F \rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3$ with $|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
+\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) * \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3| \leq |\delta_{T1}*\mathcal{F}_{\langle I,F \rangle}(c_2)| + |\delta_{T2}*\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
+\item Division: the operations performed by our controllers in the FWL domain do not include division, so these bounds are inconsequential to this paper. 
+\end{enumerate}
+
+\item {\bf Overflow:}
+The maximum size of a real number $x$ that can be represented in a fixed point domain as $\mathcal{F}_{\langle I,F \rangle}(x)$ is $\pm (2^{I-1}+1-2^{-F})$.
+Numbers outside this range cannot be represented by the domain.
+We check that overflow does not occur.
+
+\end{enumerate}
 
@@
  when the stability is ensured by synthesis, and then verify its safety accounting for the finite-precision errors.
+
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 %-------------------------------
-\section{Stability of closed-loop models}
+\section{Stability of closed-loop systems}
 \label{sec:appendix-stability}
@@
 %\addtodo{[Here discuss Jury criterium for DISCRETE-TIME models - a simplified version of the first part of what is now in Section \ref{sec:cof_verification} (with no quantization noises yet).]}
-
-%-------------------------------
-\subsection{Encoding of Jury's criterion}
-%-------------------------------
 
@@
 Jury's criterion explores solely the coefficients ($a_{0},a_{1},...,a_{N-1}$) 
-of $P(z)$ for checking stability, which we encompass as property $\phi_{stability}$, as detailed below.
-
-This study limits itself to explain the encoding of Jury's criterion for formal synthesis.  
-For the stability  test procedure, the following matrix 
+of $P(z)$ for checking stability, which we encompass as property $\phi_{stability}$.
+
+This study, however, limits itself to 
+explain the encoding of Jury's criterion for the formal synthesis purpose. 
+For the stability  test procedure, the following Jury matrix 
 $M=[m_{ij}]_{(2N-2)\times N}$ is built  from $P(z)$ coefficients:
@@
 $$
-\noindent where $V^{(k)}=[v^{(k)}_{ij}]_{2\times N}$ is such that
+\noindent where $V^{(k)}=[v^{(k)}_{ij}]_{2\times N}$ such that
 $$
@@
 \end{itemize}
-In conclusion, the stability property $\phi_{stability}$ is encoded as the following formula:
+
+The stability property $\phi_{stability}$ is then encoded as follows:
 $$
@@
 \end{remark}
-
-\subsection{Errors due to numerical representation} \label{appendix:numerical_errors}
-
-Let $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part.
-The smallest number that can be represented in this domain is $c_m=2^{-F}$.
-The following approximation errors will arise in mathematical operations and representation:
-\begin{enumerate}
-\item {\bf Truncation:}
-Let $x$ be a real number, and $\mathcal{F}_{\langle I,F \rangle}(x)$ be the same number represented in a fixed-point domain as above. 
-Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the error $ \delta_T=x\ \%_{c_m}\ \tilde x$, and $\%_{c_m}$ is the modulus operation performed on the last bit.
-
-So $\delta_T$ is the truncation error and it will propagate across operations.
-\item {\bf Rounding:}
-The following errors appear in simple operations.
-Let $c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be the truncation errors caused by representing $c_1$ and $c_2$ in the fixed-point domain as above.
-\begin{enumerate}
-\item Addition/Subtraction: these operations only propagate errors coming from truncation of the operands, namely 
-$\mathcal{F}_{\langle I,F \rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3$ with $|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
-\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) * \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3| \leq |\delta_{T1}*\mathcal{F}_{\langle I,F \rangle}(c_2)| + |\delta_{T2}*\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
-\item Division: the operations performed by our controllers in the FWL domain do not include division.
-However, we do use division in computations at the precision of the plant.
-$\mathcal{F}_{\langle I,F \rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3| \leq $, where $c_m=2^{-F}$ as above.
-\end{enumerate}
-
-\item {\bf Overflow:}
-The maximum size of a real number $x$ that can be represented in a fixed point domain as $\mathcal{F}_{\langle I,F \rangle}(x)$ is $\pm (2^{I-1}+1-2^{-F})$.
-Numbers outside this range cannot be represented by the domain.
-We check that overflow does not occur.
-
-\end{enumerate}
-
 %  Since \eqref{eq:discretization} is a bi-simulation of \eqref{eq:ode}, we may use the semantics in section \ref{sec:model_semantics} to model continuous dynamical systems.
@@
 %3            & 
-\begin{tabular}[c]{@{}c@{}}Ball\\ Magnetic\\ Levitation\end{tabular} & $\left[\begin{array}{ccc}
-0		& 1 		& 0		\\
-1752	& 0			& -34.07\\
-0		& 0			& -38.27\\
-\end{array}\right]$ & $\left[\begin{array}{c}
-0 \\ 0 \\ 1.923
-\end{array}\right]$ & $\left[\begin{array}{ccc}
-1 & 0 & 0\\
-\end{array}\right]$ & 0 \\ \hline
+%\begin{tabular}[c]{@{}c@{}}Ball\\ Magnetic\\ Levitation\end{tabular} & $\left[\begin{array}{ccc}
+%0		& 1 		& 0		\\
+%1752	& 0			& -34.07\\
+%0		& 0			& -38.27\\
+%\end{array}\right]$ & $\left[\begin{array}{c}
+%0 \\ 0 \\ 1.923
+%\end{array}\right]$ & $\left[\begin{array}{ccc}
+%1 & 0 & 0\\
+%\end{array}\right]$ & 0 \\ \hline
 %4              & 

### 2017-01-25 cav2017/cav2017.tex
remove stability check alg
fixed typo

--- 2017-01-25 cav2017/cav2017.tex
@@
 
-\begin{algorithm}[]
-\scriptsize
-\begin{algorithmic}[1]
-\Function{$stabilityCheck()$}{}
-  \State computecharPoly($A_d - B_dK$)
-  \State assert(Jury's criteria hold)
+%\begin{algorithm}[]
+%\scriptsize
+%\begin{algorithmic}[1]
+%\Function{$stabilityCheck()$}{}
+%  \State computecharPoly($A_d - B_dK$)
+%  \State assert(Jury's criteria hold)
   %\State Return $K$
-\EndFunction
-\end{algorithmic}
-\label{alg:stabilitycheck}
-\end{algorithm}
+%\EndFunction
+%\end{algorithmic}
+%\label{alg:stabilitycheck}
+%\end{algorithm}
 
@@
 
-\textit{DC Motor Position and Rate} plants describes the angular position and 
+\textit{DC Motor Position and Rate} plants describe the angular position and 
 velocity of a DC Motor, respectively. 

### 2017-01-25 cav2017/cav2017.tex
paper beautification

--- 2017-01-25 cav2017/cav2017.tex
@@
 where $\delta$ is the maximum error that can be introduced by the FWL controller in one step, i.e., by reading the states values once and multiplying by $K$ once. 
-We derive the closed form expression for $x_n$
-
+We derive the closed form expression for $x_n$ as follows: 
 \begin{align*}
@@
 reference signal so an asymptotically stable system will converge to the origin. We know that the original system
-with an infinite precision controller is stable, because we have synthesized it to meet Jury's criteria. Hence
+with an infinite-precision controller is stable, because we have synthesized it to meet Jury's criterion. Hence, 
 $(A_d  - B_dK)^n*x_0$ must converge to zero.
 
-To show that a fixed point implementation of the same controller will converge to a steady value, we need to show that the infinite sum converges.
-
-A known result is that a power series of matrices converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less than 1, to the following:
+To show that a fixed-point implementation of the same controller will converge to a finite value, 
+we need to show that the infinite sum converges.
+A known result is that a power series of matrices converges~\cite{horn1990matrix}, iff the eigenvalues of the matrix are less than 1, as follows:
+%\begin{align*}
+$\sum_{i=0}^{\infty}T^i  = (I - T)^{-1}$, 
+%\end{align*}
+where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge to the value 
 \begin{align*}
-\sum_{i=0}^{\infty}T^i  &= (I - T)^{-1}
+0 + (I - A_d + B_dK)^{-1}B_dk\delta. 
 \end{align*}
-Where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge
-
-\begin{align*}
-x_{\infty} &= 0 + (I - A_d + B_dK)^{-1}B_dk\delta
-\end{align*}
-
-Hence, provided $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the safe space, our fixed point controller system is stable, in that it converges to a finite value, although not asymptomatically stable because it doesn't converge to the origin.
+As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the safe space, then the synthesized fixed-point controller results in a safe closed-loop model. 
+The convergence to a finite value, however, will not make it asymptomatically stable.
 
@@
 %3            & 
-%\begin{tabular}[c]{@{}c@{}}Ball\\ Magnetic\\ Levitation\end{tabular} & $\left[\begin{array}{ccc}
-%0		& 1 		& 0		\\
-%1752	& 0			& -34.07\\
-%0		& 0			& -38.27\\
-%\end{array}\right]$ & $\left[\begin{array}{c}
-%0 \\ 0 \\ 1.923
-%\end{array}\right]$ & $\left[\begin{array}{ccc}
-%1 & 0 & 0\\
-%\end{array}\right]$ & 0 \\ \hline
+\begin{tabular}[c]{@{}c@{}}Ball\\ Magnetic\\ Levitation\end{tabular} & $\left[\begin{array}{ccc}
+0		& 1 		& 0		\\
+1752	& 0			& -34.07\\
+0		& 0			& -38.27\\
+\end{array}\right]$ & $\left[\begin{array}{c}
+0 \\ 0 \\ 1.923
+\end{array}\right]$ & $\left[\begin{array}{ccc}
+1 & 0 & 0\\
+\end{array}\right]$ & 0 \\ \hline
 %4              & 

### 2017-01-25 cav2017/cav2017.tex
Added median runtime improvement to introduction.
Added median runtime improvement introduced by the abstraction to the
introduction.
completeness

@@
 set is $7.9$ seconds, and most controllers can be synthesized in less
-than $17.2$ seconds.
+than $17.2$ seconds. We further show that, in a direct comparison, the abstraction-based
+approach lowers the median runtime of our benchmarks by a factor of seven over the
+multi-staged approach.
 
@@
 \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
-where $q3$ is the maximum truncation and rounding error of $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}
+where $q3$ is the maximum truncation and rounding error of $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}.
 More details on how to model quantization as noise are given in the 
@@
 engineers, and thus affirm RQ1.  
-
-The
-synthesized controllers were confirmed to be stable outside of our model
+There are several cases for which the system may fail to find a controller. In the naive approach,
+there is the risk of the completeness threshold being too large, thus causing a timeout.
+In the abstraction case, there is the risk of requiring a very precise abstraction, resulting in too many refinements which may timeout.
+Other sources for incompleness are the inability of the {\sc synthesize} phase to use a large enough precision for the plant model in a given problem.
+
+The synthesized controllers were confirmed to be stable outside of our model
 representation using MATLAB, positively answering RQ2.  A~link to the full

### 2017-01-25 cav2017/cav2017.tex
described work by Feron

--- 2017-01-25 cav2017/cav2017.tex
@@
 
-\todo{Have we covered all the literature by Feron et al?}
+%\todo{Have we covered all the literature by Feron et al?}
 
@@
 discrete system dynamics using Semi-Definite Programming (SDP).  While the
-former uses BIBO properties to determine stability, the latter uses
-Lyapunov-based quadratic invariants.  In both cases, the SDP solver uses
+former uses bounded-input and bounded-output (BIBO) properties to determine stability, 
+the latter uses Lyapunov-based quadratic invariants.  In both cases, the SDP solver uses
 floating-point arithmetic and soundness is checked by bounding the error. 
@@
 where $\delta$ is the maximum error that can be introduced by the FWL controller in one step, i.e., by reading the states values once and multiplying by $K$ once.
-We derive the closed form expression for $x_n$ as follows: 
+We derive the closed form expression for $x_n$
+
 \begin{align*}
@@
 reference signal so an asymptotically stable system will converge to the origin. We know that the original system
-with an infinite-precision controller is stable, because we have synthesized it to meet Jury's criterion. Hence, 
+with an infinite precision controller is stable, because we have synthesized it to meet Jury's criteria. Hence
 $(A_d  - B_dK)^n*x_0$ must converge to zero.
 
-To show that a fixed-point implementation of the same controller will converge to a finite value, 
-we need to show that the infinite sum converges.
-A known result is that a power series of matrices converges~\cite{horn1990matrix}, iff the eigenvalues of the matrix are less than 1, as follows:
-%\begin{align*}
-$\sum_{i=0}^{\infty}T^i  = (I - T)^{-1}$, 
-%\end{align*}
-where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge to the value 
+To show that a fixed point implementation of the same controller will converge to a steady value, we need to show that the infinite sum converges.
+
+A known result is that a power series of matrices converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less than 1, to the following:
 \begin{align*}
-0 + (I - A_d + B_dK)^{-1}B_dk\delta. 
+\sum_{i=0}^{\infty}T^i  &= (I - T)^{-1}
 \end{align*}
-As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the safe space, then the synthesized fixed-point controller results in a safe closed-loop model. 
-The convergence to a finite value, however, will not make it asymptomatically stable.
+Where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge
+
+\begin{align*}
+x_{\infty} &= 0 + (I - A_d + B_dK)^{-1}B_dk\delta
+\end{align*}
+
+Hence, provided $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the safe space, our fixed point controller system is stable, in that it converges to a finite value, although not asymptomatically stable because it doesn't converge to the origin.
 

### 2017-01-25 cav2017/cav2017.tex
fixing benchmarks
added phi input to the CEGIS with AA section
replaced "isation" by "ization"

@@
 digital state-feedback controls
-and prove their soundness by encompassing errors due to digitalisation and quantisation effects that are present in the digital controller interacting with the continuous plant. 
+and prove their soundness by encompassing errors due to digitalization and quantization effects that are present in the digital controller interacting with the continuous plant. 
 % computations and representations of dynamics, providing sufficient conditions for sound and complete safe solutions for the state feedback control problem.
@@
 
-%To this end, we formalise the notion of solution generalisation for
+%To this end, we formalise the notion of solution generalization for
 %Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
 %of abstraction refinement in order to achieve scalability.
-%This strategy enables the inductive generalisation engine inside CEGIS
+%This strategy enables the inductive generalization engine inside CEGIS
 %to look for candidate solutions in a reduced solution space.
@@
 %% We outline the general architecture of the program synthesizer used in both approaches \todo{which approaches - pls recall or clarify}. 
-%% We then give the details of both methods of solution generalization \todo{define ``solution generalisation''} that we compare.  
+%% We then give the details of both methods of solution generalization \todo{define ``solution generalization''} that we compare.  
 %% The first checks safety by unwinding the transition relation to a completeness threshold, 
@@
 saturations on the inputs, 
-and account for digitalisation and quantisation errors introduced by the controller.
+and account for digitalization and quantization errors introduced by the controller.
 
@@
 
-%% \todo{All good - only the word ``generalisation'' won't be understood by a control person (we might have reviewers from this area?).
+%% \todo{All good - only the word ``generalization'' won't be understood by a control person (we might have reviewers from this area?).
 Anticipate the explanation  given below to the introduction section.}
@@
   The naive approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
-  %uses a multi-staged verification phase and performs solution generalisation based on
+  %uses a multi-staged verification phase and performs solution generalization based on
 %the plant precision, the number of loop unrollings, 

### 2017-01-25 cav2017/cav2017.tex
paper beautification

--- 2017-01-25 cav2017/cav2017.tex
@@
 set is $7.9$ seconds, and most controllers can be synthesized in less
-than $17.2$ seconds. We further show that, in a direct comparison, the abstraction-based
-approach lowers the median runtime of our benchmarks by a factor of seven over the
-multi-staged approach.
+than $17.2$ seconds.
 
@@
 
-%\todo{Have we covered all the literature by Feron et al?}
+\todo{Have we covered all the literature by Feron et al?}
 
@@
 discrete system dynamics using Semi-Definite Programming (SDP).  While the
-former uses bounded-input and bounded-output (BIBO) properties to determine stability, 
-the latter uses Lyapunov-based quadratic invariants.  In both cases, the SDP solver uses
+former uses BIBO properties to determine stability, the latter uses
+Lyapunov-based quadratic invariants.  In both cases, the SDP solver uses
 floating-point arithmetic and soundness is checked by bounding the error. 
@@
 \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
-where $q3$ is the maximum truncation and rounding error of $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}.
+where $q3$ is the maximum truncation and rounding error of $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}
 More details on how to model quantization as noise are given in the 
@@
 engineers, and thus affirm RQ1.
-There are several cases for which the system may fail to find a controller. In the naive approach,
-there is the risk of the completeness threshold being too large, thus causing a timeout.
-In the abstraction case, there is the risk of requiring a very precise abstraction, resulting in too many refinements which may timeout.
-Other sources for incompleness are the inability of the {\sc synthesize} phase to use a large enough precision for the plant model in a given problem.
-
-The synthesized controllers were confirmed to be stable outside of our model
+
+The
+synthesized controllers were confirmed to be stable outside of our model
 representation using MATLAB, positively answering RQ2.  A~link to the full
@@
 
-We have presented two approaches to synthesize state feedback controllers 
+We have presented two automated approaches to synthesize digital state-feedback controllers 
 that ensure both stability and safety over the state-space representation.
-The first approach relies on explicit unfolding of the system's dynamics 
-up to the completeness threshold, whilst the second one applies abstraction 
+The first approach relies on explicit unfolding of the closed-loop model dynamics 
+up to a completeness threshold, whilst the second one applies abstraction 
 refinement and acceleration to increase speed whilst retaining soundness.
-Both approaches are novel in the control system literature in that it puts
+%
+Both approaches are novel within the control literature: they put 
 forward a fully automated synthesis approach that is algorithmically and
-numerically sound, considering the various error sources in the implementation 
-of the control algorithm and in the computational modeling of plant dynamics.
+numerically sound, considering various error sources in the implementation 
+of the digital control algorithm and in the computational modeling of plant dynamics. 
+%
 Our experimental results show that both approaches are able
-to synthesize stable controllers in most benchmarks within a reasonable
-amount of time fully automatically.  In particular, both approaches
-complement each other and together solve all benchmarks provided in the set.
-Future work will be the extension of these approaches to consider performance 
-requirements while synthesizing digital controllers and the application of them
-for synthesizing state observers that generally appears in state feedback 
-architecture.
+to synthesize stable controllers in most benchmarks within a small 
+amount of time automatically.  In particular, both approaches 
+complement each other and together solve all benchmarks, which have been derived from the control literature.
+
+Future work will focus the extension of these approaches to output-based control architectures (hinging on the use of observers), 
+and to considering performance requirements (alongside safety) in the synthesis of digital controllers.
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Discretizing continuous space dynamics}
+\subsection{Time discretization of continuous-space dynamics}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-01-25 cav2017/cav2017.tex

@@
 Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
-$$(\phi_{init} \wedge u_k=-K x_k) \Rightarrow \phi_{init}^{K}$$
+$$(\phi_{init} \wedge \phi_{input} \wedge u_k=-K x_k) \Rightarrow \phi_{init}^{K}$$
 
@@
 When the abstraction cannot be further refined, we provide them to the {\sc abstract} phase.
-\todo{we should have a better argument here.}
+%\todo{we should have a better argument here.}
 %\end{enumerate} 
@@
 %1              & 
-\begin{tabular}[c]{@{}c@{}}DC Motor\\ Position\end{tabular}                   & $\left[\begin{array}{ccc}
-0		& 1 		& 0						\\
-0 		& -1.087	& 8587					\\
-0		& -9964		& -1.455\times 10^{6}	\\
-\end{array}\right]$ & $\left[\begin{array}{c}
-0 \\ 0 \\ -1.455\times10^{6}
-\end{array}\right]$           & $\left[\begin{array}{ccc}
-1 & 0 & 0\\
-\end{array}\right]$ & 0 \\  \hline
+%\begin{tabular}[c]{@{}c@{}}DC Motor\\ Position\end{tabular}                   & $\left[\begin{array}{ccc}
+%0		& 1 		& 0						\\
+%0 		& -1.087	& 8587					\\
+%0		& -9964		& -1.455\times 10^{6}	\\
+%\end{array}\right]$ & $\left[\begin{array}{c}
+%0 \\ 0 \\ -1.455\times10^{6}
+%\end{array}\right]$           & $\left[\begin{array}{ccc}
+%1 & 0 & 0\\
+%\end{array}\right]$ & 0 \\  \hline
 %2              & 
@@
 \begin{tabular}[c]{@{}c@{}}DC Motor\\ Rate\end{tabular} & $\left[\begin{array}{cc}
--1000		& -13 \\
--8			& 0\\
+-1000		& -104 \\
+1			& 0\\
 \end{array}\right]$ & $\left[\begin{array}{c}
-4 \\ 0 \\
+1 \\ 0 \\
 \end{array}\right]$ & $\left[\begin{array}{cc}
-0 & 6.25\\
+0 & 200\\
 \end{array}\right]$ & 0 \\ \hline

### 2017-01-25 cav2017/cav2017.tex
Rephrased RQ 1
Rephares RQ 1 to improve flow.

@@
 
-\textit{DC Motor Position and Rate} plants describe the angular position and 
-velocity of a DC Motor, respectively. 
+\textit{DC Motor Rate} plants describes the angular velocity of a DC Motor, respectively. 
 \textit{Automotive Cruise System} plant represents the speed of a motor vehicle. 
@@
 
-\item[RQ1] \textbf{(CEGIS)} do the CEGIS with multi-stage 
-verification and abstraction-based generate a FWL digital 
-controller in a reasonable amount of time?
+\item[RQ1] \textbf{(CEGIS)} do the multi-staged verification and abstraction-based
+CEGIS generate a FWL digital controller in a reasonable amount of time?
 

### 2017-01-25 cav2017/cav2017.tex

@@
 
-\textit{DC Motor Rate} plants describes the angular velocity of a DC Motor, respectively. 
+\textit{DC Motor Position and Rate} plants describe the angular position and 
+velocity of a DC Motor, respectively. 
 \textit{Automotive Cruise System} plant represents the speed of a motor vehicle. 
@@
 
-\item[RQ1] \textbf{(CEGIS)} do the multi-staged verification and abstraction-based
-CEGIS generate a FWL digital controller in a reasonable amount of time?
+\item[RQ1] \textbf{(CEGIS)} do the CEGIS with multi-stage 
+verification and abstraction-based generate a FWL digital 
+controller in a reasonable amount of time?
 

### 2017-01-25 cav2017/cav2017.tex
various items

--- 2017-01-25 cav2017/cav2017.tex
@@
 stages, leveraging counterexample guided inductive synthesis (CEGIS) and
-reachability analysis.  CEGIS synthesises a static feedback controller that
+reachability analysis.  CEGIS synthesizes a static feedback controller that
 stabilizes the system under some restrictions given by the safety of the
@@
 both based on the Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use for program synthesis.   
-We provide two alternative automated procedures to synthesise safe 
+We provide two alternative automated procedures to synthesize safe 
 digital state-feedback controls
@@
 
-%% we substitute the second step by employing abstract
-%% acceleration to unfold the dynamics forward, instead of symbolically
-%% unwinding the transition relation~\cite{cattaruzza2015unbounded}.
-%\todo{We need to emphasise the derivation of errors for soundness. Can we claim completeness already?}
+Both models synthesise sound safe controllers given a discrete-time model of the closed-loop system.
 
@@
 
-%To this end, we formalise the notion of solution generalization for
+%To this end, we formalize the notion of solution generalization for
 %Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
@@
 The embedded controller software can be more complicated than
-the state feedback control we synthesised, and the properties 
+the state feedback control we synthesized, and the properties 
 available cover more detail.
@@
 digital feedback controllers using CEGIS.  For this purpose, we first
-provide the synthesiser's general architecture, followed by describing
+provide the synthesizer's general architecture, followed by describing
 our two approaches to synthesizing safe controllers:
@@
 added to the {\sc inputs} set and the loop iterates again.
-More details about the general architecture of the synthesiser can
+More details about the general architecture of the synthesizer can
 be found in~\cite{DBLP:conf/lpar/DavidKL15}.
@@
 \item The first {\sc verify} stage, {\sc safety}, checks that candidate
-solution $K$, which we synthesised to be safe for at least one initial state, is safe for \emph{all} possible initial states, i.e., does not reach an unsafe
+solution $K$, which we synthesized to be safe for at least one initial state, is safe for \emph{all} possible initial states, i.e., does not reach an unsafe
 state within $k$ steps where we assume $k$ to be under the completeness threshold. 
@@
   %and the sampling rate. Essentially, it
-  synthesises a controller for an individual initial state
+  synthesizes a controller for an individual initial state
 and input with a bounded time horizon and, subsequently, it generalizes it to all reachable states,
@@
 \end{enumerate}
-\item In the {\sc synthesize} phase, we synthesise a candidate controller
+\item In the {\sc synthesize} phase, we synthesize a candidate controller
 %We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability 
@@
 Using the initial state bounds $\underline{x_{0}}=-0.9$ and $\overline{x_{0}}=0.9$, the input bounds $\underline{u}=-10$ and $\overline{u}=10$, and safety specifications 
-$\underline{x_{i}}=-0.92$ and $\overline{x_{i}}=0.92$, the {\sc synthesize} phase in Fig.~\ref{fig:CEGARIS} synthesises an initial candidate controller $K=[\begin{array}{ccc}0.24609375&-0.125&0.1484375\end{array}]$.
+$\underline{x_{i}}=-0.92$ and $\overline{x_{i}}=0.92$, the {\sc synthesize} phase in Fig.~\ref{fig:CEGARIS} synthesizes an initial candidate controller $K=[\begin{array}{ccc}0.24609375&-0.125&0.1484375\end{array}]$.
 Although this candidate is stable, the {\sc verify} phase finds it to be unsafe and returns a list of iterations with an example initial state that fails the safety specification
@@
 engineers, and thus affirm RQ1.
-There are several cases for which the system may fail to find a controller. In the naive approach,
-there is the risk of the completeness threshold being too large, thus causing a timeout.
-In the abstraction case, there is the risk of requiring a very precise abstraction, resulting in too many refinements which may timeout.
-Other sources for incompleness are the inability of the {\sc synthesize} phase to use a large enough precision for the plant model in a given problem.
+
+There are several cases for which the system
+may fail to find a controller. For the naive approach, 
+the completeness threshold may be too large, thus causing a
+timeout.  On the other hand, the abstraction-based approach may
+require a very precise abstraction, resulting in too many refinements
+and, consequently, a timeout.  Yet another source of incompleness is the inability
+of the {\sc synthesize} phase to use a large enough precision for the
+plant model in a given problem.
 
@@
 Our experimental results show that both approaches are able
-to synthesize stable controllers in most benchmarks within a small 
-amount of time automatically.  In particular, both approaches 
-complement each other and together solve all benchmarks, which have been derived from the control literature.
-
-Future work will focus the extension of these approaches to output-based control architectures (hinging on the use of observers), 
+to synthesize stable controllers in most benchmarks within a reasonable
+amount of time fully automatically.  In particular, both approaches
+complement each other and together solve all benchmarks , which have been derived from the control literature.
+
+Future work will focus the extension of these approaches to the continuous time case with output-based control architectures (hinging on the use of observers), 
 and to considering performance requirements (alongside safety) in the synthesis of digital controllers.

### 2017-01-25 cav2017/cav2017.tex
replaced "ise" by "ize"

@@
 
-Both models synthesise sound safe controllers given a discrete-time model of the closed-loop system.
+%% we substitute the second step by employing abstract
+%% acceleration to unfold the dynamics forward, instead of symbolically
+%% unwinding the transition relation~\cite{cattaruzza2015unbounded}.
+%\todo{We need to emphasize the derivation of errors for soundness. Can we claim completeness already?}
 
@@
 engineers, and thus affirm RQ1.  
-
-There are several cases for which the system
-may fail to find a controller. For the naive approach, 
-the completeness threshold may be too large, thus causing a
-timeout.  On the other hand, the abstraction-based approach may
-require a very precise abstraction, resulting in too many refinements
-and, consequently, a timeout.  Yet another source of incompleness is the inability
-of the {\sc synthesize} phase to use a large enough precision for the
-plant model in a given problem.
+There are several cases for which the system may fail to find a controller. In the naive approach,
+there is the risk of the completeness threshold being too large, thus causing a timeout.
+In the abstraction case, there is the risk of requiring a very precise abstraction, resulting in too many refinements which may timeout.
+Other sources for incompleness are the inability of the {\sc synthesize} phase to use a large enough precision for the plant model in a given problem.
 
@@
 Our experimental results show that both approaches are able
-to synthesize stable controllers in most benchmarks within a reasonable
-amount of time fully automatically.  In particular, both approaches
-complement each other and together solve all benchmarks , which have been derived from the control literature.
-
-Future work will focus the extension of these approaches to the continuous time case with output-based control architectures (hinging on the use of observers), 
+to synthesize stable controllers in most benchmarks within a small 
+amount of time automatically.  In particular, both approaches 
+complement each other and together solve all benchmarks, which have been derived from the control literature.
+
+Future work will focus the extension of these approaches to output-based control architectures (hinging on the use of observers), 
 and to considering performance requirements (alongside safety) in the synthesis of digital controllers.

### 2017-01-25 cav2017/cav2017.tex
Reviewed experimental section.
Fixed typos, unified notation.

@@
 
-\renewcommand{\baselinestretch}{0.975}
 \newcommand{\addtodo}[1]{{\color{red} TODO: #1}}
@@
 
-%% we substitute the second step by employing abstract
-%% acceleration to unfold the dynamics forward, instead of symbolically
-%% unwinding the transition relation~\cite{cattaruzza2015unbounded}.
-%\todo{We need to emphasize the derivation of errors for soundness. Can we claim completeness already?}
+Both models synthesise sound safe controllers given a discrete-time model of the closed-loop system.
 
@@
 We are interested in the synthesis of digital feedback control algorithm, 
-as implemented on modern FPGAs or Digital Signal Processorss. 
+as implemented on modern Field-Programmable Gate Arrays or Digital Signal Processors. 
 The most basic feedback architecture is the state feedback, 
@@
 \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
-where $q3$ is the maximum truncation and rounding error of $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}.
-More details on how to model quantization as noise are given in the 
-Appendix~\ref{appendix:quantization-noise}.
+where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is the error introduced by the DAC and $q3$ is the maximum truncation and rounding error of $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}.
+We consider the error introduced by the DAC to be equal to zero, since the domain of the plant is at a higher precision than the controller.
+%More details on how to model quantization as noise are given in the 
+%Appendix~\ref{appendix:quantization-noise}.
 \item Calculate a set of initial bounds on $K$, $\phi_{init}^{K}$, based on the input constraints.
@@
 %
-Let us take the Helicopter example in Table \ref{table:State-space benchmarks} with discretized dynamics
+Let us take the Helicopter example in Table \ref{table:State-space-benchmarks} with discretized dynamics
 $$A_d = \left[\begin{array}{ccc}2.6207&-1.1793&0.65705\\2&0&0\\0&0.5&0\end{array}\right], B_d = \left [\begin{array}{c}8\\0\\0\end{array}\right]$$
@@
 
-We give the run-times required to synthesize a stable controller for each
+We give the runtimes required to synthesize a stable controller for each
 benchmark in Table~\ref{tab:results}.  
-Here \textit{Benchmark} is the name of the employed
+Here \textit{Benchmark} is the name of the respective
 benchmark, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used
@@
 \scriptsize
-\begin{tabular}{| r | c | c | r | c | r |}
+\begin{tabular}{| c | l | c | r | c | r |}
 \hline
-\# & Benchmark  & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
+\# & \multicolumn{1}{|c|}{Benchmark}  & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
    &                                  & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
@@
 %
-Our algorithm to select suitable FWL word widths to model plant behavior employs a heuristic based on user-provided controller word-width specifications.
+Our algorithm to select suitable FWL word widths to model the plant behavior employs a heuristic based on user-provided controller word-width specifications.
 For the first approach, where we may need to increase the precision of the time discretization, we select the time steps for the discretizations on a similar basis.
@@
 \begin{equation}
-\dot{x}(t)=\vec{A}\vec{x}(t)+\vec{B}\vec{u}(t) +\vec{w}(t).
+\dot{x}(t)=Ax(t)+Bu(t).
 \label{eq:dynamical}
 \end{equation}
-
-\noindent with $\vec{w} \sim \mathcal{N}(0,Q)$.\\
-Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
-which may restrict the observability of the state-space from the output space.
-\begin{equation}
-\vec{y}(t)=\vec{C}\vec{x}(t)+\vec{D}\vec{u}(t).
-\end{equation}
+%Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
+%which may restrict the observability of the state-space from the output space.
+%\begin{equation}
+%\vec{y}(t)=\vec{C}\vec{x}(t)+\vec{D}\vec{u}(t).
+%\end{equation}
 
 Discretization of an continuous dynamical system turns the ODE into a difference equation, assuming zero-order hold
-for the input $\vec{u}$ and continuous integration for the noise $\vec{w}$, to
+for the input $u$, 
+%and continuous integration for the noise $\vec{w}$, 
+to
 \begin{align}
 \label{eq:discretization}
-\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d\vec{u}_k + \vec{w}_k,\\
-y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k. 
+x_{k+1} &= A_d x_k+B_d u_k,
+%\\y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k. 
 \end{align}
-with covariance for $\vec{w}_k \sim \mathcal{N}(0,Q_d)$,
+%with covariance for $\vec{w}_k \sim \mathcal{N}(0,Q_d)$,
 where
@@
 \label{eq:discretize}
-\vec{A}_d &= e^{\vec{A} T_s} = \mathcal{L}^{-1} { ( s \vec{I} - \vec{A} )^{-1} }_{t = T_s},\\
-\vec{B}_d &= \int_{0}^{T_s} e^{\vec{A} t} dt\ \vec{B} = \vec{A}^{-1} ( \vec{A}_d - \vec{I} ) \vec{B},\\
-\vec{C}_d &= \vec{C},\\
-\vec{D}_d &= \vec{D},\\
-Q_d &= \int_{0}^{T_s} e^{\vec{A} t} Q e^{\vec{A}^T t} dt.
+A_d &= e^{A T_s} = \mathcal{L}^{-1} { ( s I - A )^{-1} }_{t = T_s},\\
+B_d &= \int_{0}^{T_s} e^{A t} dt\ B = A^{-1} ( A_d - I ) B,
+%\\
+%\vec{C}_d &= \vec{C},\\
+%\vec{D}_d &= \vec{D},\\
+%Q_d &= \int_{0}^{T_s} e^{\vec{A} t} Q e^{\vec{A}^T t} dt.
 \end{align}
 and $T_s$ is the sample time. Then
-\begin{align*}
-x(kT_s)=x_k \wedge y(kT_s) = y_k, \forall k.
-\end{align*}
-Let $g_d(k)=\mathcal{G}(t,g(t),T)$ be a function that performs the discretization described above, where $g(t)$
-represents the continuous dynamics and $g_d(k)$ the corresponding discrete dynamics. 
-Let $G(s)=\mathcal{L}(g(t))$ and $G_d(z)=\mathcal{Z}(g_d(k))$ be the corresponding Laplace and Z-transforms
-of $g(t)$ and $g_d(k)$. Given this relation, we have 
-$$G_d(z)=G(z)|_{z=e^{sT}} : g_d(k)=\mathcal{G}(t,g(t),T) \wedge T < \frac{1}{.5f_s},$$
-where $.5f_s$ is the Nyquist frequency of $g(t)$. This last restriction is introduced to avoid the effects of aliasing
-which could cause ``phantom poles'' to appear otherwise. 
-The eigenvalues of $\vec{A}_d$ corresponding to the poles of $G_d(z)$, and those of $\vec{A}$ corresponding to the poles of $G(s)$ are similarly related.
-$\hat{\lambda}_i=e^{-\lambda_iT} : \hat{\lambda}_i \in \sigma(\vec{A}_d) \wedge \lambda_i \in \sigma(\vec{A})$
+$x(kT_s)=x_k 
+%\wedge y(kT_s) = y_k, 
+\forall k \in \mathbb N$.
+%\end{align*}
+%Let $g_d(k)=\mathcal{G}(t,g(t),T)$ be a function that performs the discretization described above, where $g(t)$
+%represents the continuous dynamics and $g_d(k)$ the corresponding discrete dynamics. 
+%Let $G(s)=\mathcal{L}(g(t))$ and $G_d(z)=\mathcal{Z}(g_d(k))$ be the corresponding Laplace and Z-transforms
+%of $g(t)$ and $g_d(k)$. Given this relation, we have 
+%$$G_d(z)=G(z)|_{z=e^{sT}} : g_d(k)=\mathcal{G}(t,g(t),T) \wedge T < \frac{1}{.5f_s},$$
+%where $.5f_s$ is the Nyquist frequency of $g(t)$. This last restriction is introduced to avoid the effects of aliasing
+%which could cause ``phantom poles'' to appear otherwise. 
+The eigenvalues of $A_d$ 
+%corresponding to the poles of $G_d(z)$, 
+are related to those of $A$:  
+% corresponding to the poles of $G(s)$ are similarly related.
+$\hat{\lambda}_i=e^{-\lambda_iT_s}$, where $\hat{\lambda}_i \in \sigma(A_d) \wedge \lambda_i \in \sigma(A)$
 where $\sigma(\cdot)$ is the spectrum of a matrix.
-The following remark is worth mentioning regarding the above.
-\begin{remark}
-The witnessed maximum amplitude of the discrete signals $x_k,y_k$ may be smaller to that of $x(t),y(t)$ due to synchronism at fraction-frequency sampling.
-This means that reasoning about the state-space must consider the effects of this possibility as well of the case of maximal inputs from the continuous specification.
-\end{remark}
+
+%The following remark is worth mentioning regarding the above.
+%\begin{remark}
+%The witnessed maximum amplitude of the discrete signals $x_k,y_k$ may be smaller to that of $x(t),y(t)$ due to synchronism at fraction-frequency sampling.
+%This means that reasoning about the state-space must consider the effects of this possibility as well of the case of maximal inputs from the continuous specification.
+%\end{remark}
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Modelling quantization as noise} \label{appendix:quantization-noise}
+%\subsection{Modelling quantization as noise} \label{appendix:quantization-noise}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 
-During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathbb{R}\langle I_{c},F_{c} \rangle$ value.
-this sampling uses a threshold which is defined by the less significant bit ($q_{adc}=2^{-F_{adc}}$) of the ADC and some non-linearities of the circuitry.
+%During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathcal{F}_{\langle I_c,F_c \rangle}$ value.
+This sampling uses a threshold which is defined by the less significant bit of the ADC.
+We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (\emph{ie} the quantizer includes any digital gain added in the code), and so we will denote this error $q_{c}=2^{-F_{c}}$).
+We omit the effect of non-linearities of the circuitry.
 The overall conversion is
-$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{adc}}{2}\right]$$.
-If we denote the error in the conversion as $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
-
-We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (\emph{ie} the quantizer includes any digital gain added in the code).
-The process of quantization in the DAC is similar except that it is going from $\mathbb{R}\langle I_{c},F_{c} \rangle \rightarrow \mathbb{R}\langle I_{dac},F_{dac} \rangle$.
-If these domains are the same ($I_{c}=I_{dac},F_{c}=F_{dac}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
-From the above equations we can now infer that $\nu_1 \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], \nu_2 \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{c} \wedge q_2=q_{dac}$.
-Note that these bounds hold irrespective of whether the noise is correlated, hence we may use them to over-approximate the effect of the noise on the state space progression over time.
-The resulting dynamics are:
-\begin{align}
-\label{eq:pre_quantization}
-\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d(\vec{u}_k+{\vec{\nu}_2}_k) + \vec{w}_k,\\
-y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k+{\vec{\nu}_1}_k. 
-\end{align}
-
-Which, when modelled into closed loop dynamics results in:
-
-\begin{align}
-\label{eq:quantization}
-\vec{x}_{k+1} &= (\vec{A}_d-\vec{B}_d\mat{K}_d\mat{C}_d) \vec{x}_k+\vec{B}_d{\vec{\nu}_2}_k + \vec{w}_k,\\
-y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k+{\vec{\nu}_1}_k. 
-\end{align}
+%$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right]$$.
+%If we denote the error in the conversion as noise $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
+
+%The process of quantization in the DAC is similar except that it is going from $\mathcal{F}_{\langle I_c,F_c \rangle}  \rightarrow \mathcal{F}_{\langle I_p,F_p \rangle}$.
+If these domains are the same ($I_{p}=I_{c},F_{p}=F_{c}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
+%From the above equations we can now infer that $\nu_1 \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], \nu_2 \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{c} \wedge q_2=q_{dac}$.
+%Note that these bounds hold irrespective of whether the noise is correlated, hence we may use them to over-approximate the effect of the noise on the state space progression over time.
+%The resulting dynamics are:
+%\begin{align}
+%\label{eq:pre_quantization}
+%\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d(\vec{u}_k+{\vec{\nu}_2}_k) + \vec{w}_k,\\
+%y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k+{\vec{\nu}_1}_k. 
+%\end{align}
+
+%Which, when modelled into closed loop dynamics results in:
+
+%\begin{align}
+%\label{eq:quantization}
+%\vec{x}_{k+1} &= (\vec{A}_d-\vec{B}_d\mat{K}_d\mat{C}_d) \vec{x}_k+\vec{B}_d{\vec{\nu}_2}_k + \vec{w}_k,\\
+%y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k+{\vec{\nu}_1}_k. 
+%\end{align}
 

### 2017-01-25 cav2017/cav2017.tex
changes to noise

--- 2017-01-25 cav2017/cav2017.tex
@@
 
-During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathbb{R}\langle I_{c},F_{c} \rangle$ value.
-this sampling uses a threshold which is defined by the less significant bit ($q_{adc}=2^{-F_{adc}}$) of the ADC and some non-linearities of the circuitry.
+During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathcal{F}_{\langle I_c,F_c \rangle}$ value.
+This sampling uses a threshold which is defined by the less significant bit of the ADC.
+We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (\emph{ie} the quantizer includes any digital gain added in the code), and so we will denote this error $q_{c}=2^{-F_{c}}$).
+We omit the effect of non-linearities of the circuitry.
 The overall conversion is
-$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{adc}}{2}\right]$$.
-If we denote the error in the conversion as $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
-
-We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (\emph{ie} the quantizer includes any digital gain added in the code).
-The process of quantization in the DAC is similar except that it is going from $\mathbb{R}\langle I_{c},F_{c} \rangle \rightarrow \mathbb{R}\langle I_{dac},F_{dac} \rangle$.
-If these domains are the same ($I_{c}=I_{dac},F_{c}=F_{dac}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
+$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right]$$.
+If we denote the error in the conversion as noise $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
+
+The process of quantization in the DAC is similar except that it is going from $\mathcal{F}_{\langle I_c,F_c \rangle}  \rightarrow \mathcal{F}_{\langle I_p,F_p \rangle}$.
+If these domains are the same ($I_{p}=I_{c},F_{p}=F_{c}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
 From the above equations we can now infer that $\nu_1 \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], \nu_2 \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{c} \wedge q_2=q_{dac}$.

### 2017-01-25 cav2017/cav2017.tex
removed section unless i can fix maths before deadline

@@
 where $q3$ is the maximum truncation and rounding error of $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}.
-More details on how to model quantization as noise are given in the 
-Appendix~\ref{appendix:quantization-noise}.
+%More details on how to model quantization as noise are given in the 
+%Appendix~\ref{appendix:quantization-noise}.
 \item Calculate a set of initial bounds on $K$, $\phi_{init}^{K}$, based on the input constraints.
@@
 
-During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathcal{F}_{\langle I_c,F_c \rangle}$ value.
+%During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathcal{F}_{\langle I_c,F_c \rangle}$ value.
 This sampling uses a threshold which is defined by the less significant bit of the ADC.
@@
 The overall conversion is
-$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right]$$.
-If we denote the error in the conversion as noise $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
-
-The process of quantization in the DAC is similar except that it is going from $\mathcal{F}_{\langle I_c,F_c \rangle}  \rightarrow \mathcal{F}_{\langle I_p,F_p \rangle}$.
+%$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right]$$.
+%If we denote the error in the conversion as noise $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
+
+%The process of quantization in the DAC is similar except that it is going from $\mathcal{F}_{\langle I_c,F_c \rangle}  \rightarrow \mathcal{F}_{\langle I_p,F_p \rangle}$.
 If these domains are the same ($I_{p}=I_{c},F_{p}=F_{c}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
-From the above equations we can now infer that $\nu_1 \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], \nu_2 \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{c} \wedge q_2=q_{dac}$.
-Note that these bounds hold irrespective of whether the noise is correlated, hence we may use them to over-approximate the effect of the noise on the state space progression over time.
-The resulting dynamics are:
-\begin{align}
-\label{eq:pre_quantization}
-\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d(\vec{u}_k+{\vec{\nu}_2}_k) + \vec{w}_k,\\
-y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k+{\vec{\nu}_1}_k. 
-\end{align}
-
-Which, when modelled into closed loop dynamics results in:
-
-\begin{align}
-\label{eq:quantization}
-\vec{x}_{k+1} &= (\vec{A}_d-\vec{B}_d\mat{K}_d\mat{C}_d) \vec{x}_k+\vec{B}_d{\vec{\nu}_2}_k + \vec{w}_k,\\
-y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k+{\vec{\nu}_1}_k. 
-\end{align}
+%From the above equations we can now infer that $\nu_1 \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], \nu_2 \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{c} \wedge q_2=q_{dac}$.
+%Note that these bounds hold irrespective of whether the noise is correlated, hence we may use them to over-approximate the effect of the noise on the state space progression over time.
+%The resulting dynamics are:
+%\begin{align}
+%\label{eq:pre_quantization}
+%\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d(\vec{u}_k+{\vec{\nu}_2}_k) + \vec{w}_k,\\
+%y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k+{\vec{\nu}_1}_k. 
+%\end{align}
+
+%Which, when modelled into closed loop dynamics results in:
+
+%\begin{align}
+%\label{eq:quantization}
+%\vec{x}_{k+1} &= (\vec{A}_d-\vec{B}_d\mat{K}_d\mat{C}_d) \vec{x}_k+\vec{B}_d{\vec{\nu}_2}_k + \vec{w}_k,\\
+%y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k+{\vec{\nu}_1}_k. 
+%\end{align}
 

### 2017-01-25 cav2017/cav2017.tex
expanded FPGA and fixed typo

--- 2017-01-25 cav2017/cav2017.tex
@@
 
-During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathcal{F}_{\langle I_c,F_c \rangle}$ value.
-This sampling uses a threshold which is defined by the less significant bit of the ADC.
-We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (\emph{ie} the quantizer includes any digital gain added in the code), and so we will denote this error $q_{c}=2^{-F_{c}}$).
-We omit the effect of non-linearities of the circuitry.
+During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathbb{R}\langle I_{c},F_{c} \rangle$ value.
+this sampling uses a threshold which is defined by the less significant bit ($q_{adc}=2^{-F_{adc}}$) of the ADC and some non-linearities of the circuitry.
 The overall conversion is
-$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right]$$.
-If we denote the error in the conversion as noise $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
-
-The process of quantization in the DAC is similar except that it is going from $\mathcal{F}_{\langle I_c,F_c \rangle}  \rightarrow \mathcal{F}_{\langle I_p,F_p \rangle}$.
-If these domains are the same ($I_{p}=I_{c},F_{p}=F_{c}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
+$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{adc}}{2}\right]$$.
+If we denote the error in the conversion as $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
+
+We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (\emph{ie} the quantizer includes any digital gain added in the code).
+The process of quantization in the DAC is similar except that it is going from $\mathbb{R}\langle I_{c},F_{c} \rangle \rightarrow \mathbb{R}\langle I_{dac},F_{dac} \rangle$.
+If these domains are the same ($I_{c}=I_{dac},F_{c}=F_{dac}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
 From the above equations we can now infer that $\nu_1 \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], \nu_2 \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{c} \wedge q_2=q_{dac}$.

### 2017-01-25 cav2017/cav2017.tex
paper beautification

@@
 stages, leveraging counterexample guided inductive synthesis (CEGIS) and
-reachability analysis.  CEGIS synthesizes a static feedback controller that
+reachability analysis.  CEGIS synthesises a static feedback controller that
 stabilizes the system under some restrictions given by the safety of the
@@
 both based on the Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use for program synthesis.   
-We provide two alternative automated procedures to synthesize safe 
+We provide two alternative automated procedures to synthesise safe 
 digital state-feedback controls
@@
 %% unwinding the transition relation~\cite{cattaruzza2015unbounded}.
-%\todo{We need to emphasize the derivation of errors for soundness. Can we claim completeness already?}
+%\todo{We need to emphasise the derivation of errors for soundness. Can we claim completeness already?}
 
@@
 
-%To this end, we formalize the notion of solution generalization for
+%To this end, we formalise the notion of solution generalization for
 %Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
@@
 The embedded controller software can be more complicated than
-the state feedback control we synthesized, and the properties 
+the state feedback control we synthesised, and the properties 
 available cover more detail.
@@
 We are interested in the synthesis of digital feedback control algorithm, 
-as implemented on modern Field-Programmable Gate Arrays or Digital Signal Processors. 
+as implemented on modern FPGAs or Digital Signal Processorss. 
 The most basic feedback architecture is the state feedback, 
@@
 digital feedback controllers using CEGIS.  For this purpose, we first
-provide the synthesizer's general architecture, followed by describing
+provide the synthesiser's general architecture, followed by describing
 our two approaches to synthesizing safe controllers:
@@
 added to the {\sc inputs} set and the loop iterates again.
-More details about the general architecture of the synthesizer can
+More details about the general architecture of the synthesiser can
 be found in~\cite{DBLP:conf/lpar/DavidKL15}.
@@
 \item The first {\sc verify} stage, {\sc safety}, checks that candidate
-solution $K$, which we synthesized to be safe for at least one initial state, is safe for \emph{all} possible initial states, i.e., does not reach an unsafe
+solution $K$, which we synthesised to be safe for at least one initial state, is safe for \emph{all} possible initial states, i.e., does not reach an unsafe
 state within $k$ steps where we assume $k$ to be under the completeness threshold. 
@@
   %and the sampling rate. Essentially, it
-  synthesizes a controller for an individual initial state
+  synthesises a controller for an individual initial state
 and input with a bounded time horizon and, subsequently, it generalizes it to all reachable states,
@@
 \end{enumerate}
-\item In the {\sc synthesize} phase, we synthesize a candidate controller
+\item In the {\sc synthesize} phase, we synthesise a candidate controller
 %We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability 
@@
 Using the initial state bounds $\underline{x_{0}}=-0.9$ and $\overline{x_{0}}=0.9$, the input bounds $\underline{u}=-10$ and $\overline{u}=10$, and safety specifications 
-$\underline{x_{i}}=-0.92$ and $\overline{x_{i}}=0.92$, the {\sc synthesize} phase in Fig.~\ref{fig:CEGARIS} synthesizes an initial candidate controller $K=[\begin{array}{ccc}0.24609375&-0.125&0.1484375\end{array}]$.
+$\underline{x_{i}}=-0.92$ and $\overline{x_{i}}=0.92$, the {\sc synthesize} phase in Fig.~\ref{fig:CEGARIS} synthesises an initial candidate controller $K=[\begin{array}{ccc}0.24609375&-0.125&0.1484375\end{array}]$.
 Although this candidate is stable, the {\sc verify} phase finds it to be unsafe and returns a list of iterations with an example initial state that fails the safety specification

### 2017-01-25 cav2017/cav2017.tex
removed maths

--- 2017-01-25 cav2017/cav2017.tex
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Modelling quantization as noise} \label{appendix:quantization-noise}
+%\subsection{Modelling quantization as noise} \label{appendix:quantization-noise}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-01-25 cav2017/cav2017.tex
noise notes

@@
 \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
-where $q3$ is the maximum truncation and rounding error of $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}.
+where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is the error introduced by the DAC and $q3$ is the maximum truncation and rounding error of $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}.
+We consider the error introduced by the DAC to be equal to zero, since the domain of the plant is at a higher precision than the controller.
 %More details on how to model quantization as noise are given in the 

### 2017-01-25 cav2017/cav2017.tex
minor fix

@@
  \State set $x_0$ to be a vertex state, e.g., $[\underline{x_0},\underline{x_0}]$	
-\While ($c=0; c < 2^{Num_States}; c++$)
+\For ($c=0; c < 2^{Num_States}; c++$)
   %\State assert($ \underline{x_0}  \leq x_0 \leq \overline{x_0}$)
@@
   	\State set $x_0$ to be a new vertex state
-  	\EndWhile
+  	\EndFor
   %\State Return $K$
@@
 \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
-where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is the error introduced by the DAC and $q3$ is the maximum truncation and rounding error of $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}.
+where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is the error introduced by the DAC and $q3$ is the maximum truncation and rounding error of the mathematical operation $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}.
 We consider the error introduced by the DAC to be equal to zero, since the domain of the plant is at a higher precision than the controller.

### 2017-01-25 cav2017/cav2017.tex
minor change
minor fix

@@
 the entries of matrix $K$, so that the closed-loop dynamics are shaped as
-desired (see Appendix~\ref{sec:appendix-stability} for details.
+desired (see Appendix~\ref{sec:appendix-stability} for details).
 

### 2017-01-25 cav2017/cav2017.tex
removed controller canonical form

@@
 %\end{align}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Controllable canonical form} \label{sec:reachable}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Let us have a discrete time SISO system with an $n^{th},m^{th} : n\geq m$ order armax model
-$$y[k]=\sum_{i=1}^n a_iy[k-i]+\sum_{i=0}^m b_iu[k-i],$$
-where $y$ is the output of the system and $u$ its input.
-The equivalent LTI dynamics of such a model are:
-\begin{align}
-\label{eq:cf_SISO}
-\vec{x}_{k+1}=&\mat{A}_{cf}\vec{x}_k+\mat{B}_{cf}u_k : \vec{x}_k=[y_{k-n}\ \hdots y_{k-1}\ y_{k}]^T\\
-y_k=&\mat{C}_{cf}\vec{x}_k + b_0u_k\nonumber\\
-\mat{A}_{cf}=&\left[
-\begin{array}{ccccc}
-0&1&0&\cdots&0\\
-0&0&1&\cdots&0\\
-\vdots&\vdots&\vdots&\ddots&\vdots\\
-0&0&0&\cdots&1\\
--a_n&-a_{n-1}&-a_{n-2}&\cdots&-a_1
-\end{array}\right],
-\mat{B}_{cf}=\left[
-\begin{array}{c}
-0\\0\\ \vdots\\ 0\\ 1
-\end{array}\right]\nonumber\\
-\mat{C}_{cf}=&[\begin{array}{ccccc}b_n-a_nb_0&b_{n-1}-a_{n-1}b_0&\cdots&b_1-a_1b_0\end{array}] : b_{i \in (m\ n]}=0\nonumber
-\end{align}
-
-where the coefficients $a_i$ describe the characteristic polynomial of the system. This matrix shape is
-called a Controllable Canonical Form because the dynamics of the feedback are directly related to these
-coefficients. Specifically, given a feedback controller $\mat{K}$ for this system, the closed loop dynamics
-will have the shape
-\begin{align}
-\mat{A}_{cf}+\mat{B}_{cf}\mat{K}_{cf}=&\left[
-\begin{array}{ccccc}
-0&1&0&\cdots&0\\
-0&0&1&\cdots&0\\
-\vdots&\vdots&\vdots&\ddots&\vdots\\
-0&0&0&\cdots&1\\
-k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
-\end{array}\right]
-\label{eq:cf_SISO_fb}
-\end{align}
-which means we can directly modify each coefficient by selecting a controller parameter.
-In the MIMO case, the Controllable Canonical Form has the following shape:
-\begin{align}
-\mat{A}_{cf}=&\left[
-\begin{array}{ccccc}
-0&\mat{I}_{n-1}&0&\cdots&0\\
-0&0&\mat{I}_{n-2}&\cdots&0\\
-\vdots&\vdots&\vdots&\ddots&\vdots\\
-0&0&0&\cdots&1\\
--\mat{a_n}\mat{M}_n&-\mat{a_{n-1}}\mat{M}_{n-1}&-\mat{a_{n-2}}\mat{M}_{n-2}&\cdots&-\mat{a_1}\mat{M}_{1}
-\end{array}\right],
-\mat{B}_{cf}=\left[
-\begin{array}{c}
-0\\0\\ \vdots\\ 0\\ \mat{M}_0
-\end{array}\right]\nonumber\\
-\mat{C}_{cf}=&[\begin{array}{ccccc}\mat{\eta}_n&\mat{\eta}_{n-1}&\cdots&\mat{\eta}_1\end{array}] :
-\mat{I}_i,\mat{M}_i \in \mathbb{R}^{q_i \times q_i} \wedge \mat{a}_i \in \mathbb{R}^{q \times q_i} \wedge \mat{\eta}_i \in \mathbb{R}^o \wedge  \mat{\eta}_{i \in (m\ n]}=0 \nonumber
-\label{eq:cf_MIMO}
-\end{align}
-where $q$ is the number of inputs, $q_i$ the number of inputs with a transfer function of order of at least $i$, $\mat{I}_i$ an identity matrix, $\mat{M}_i$ an upper triangular matrix with 1s in its diagonal, $\mat{a_i}$ a matrix of coefficients of the $i^th$ order on its diagonal, and $o$ the number of outputs.
-Ideally we aim for $\mat{M}_i=\mat{I}_i, \forall i>0$
-
-Any LTI system can be transformed into a controllable canonical form by a matrix $\mat{T} : \vec{x}=\mat{T}\hat{\vec{x}}$
-Then the dynamics of the controllable form are
-\begin{align}
-\hat{\vec{x}}_{k+1}=&\mat{A}_{cf}\hat{\vec{x}}_k+\mat{B}_{cf}u_k : \mat{A}_{cf}=\mat{T}\mat{A}\mat{T}^{-1} \wedge \mat{B}_{cf}=\mat{T}\mat{B}\\
-y_k=&\mat{C}_{cf}\hat{\vec{x}}_k + b_0u_k : \mat{C}_{cf}=\mat{C}\mat{T}^{-1}\nonumber
-\end{align}
-where $\mat{T}$ can be calculated as follows:
-
-Let 
-\begin{equation}
-\mat{R}=[\begin{array}{ccccc}\mat{B}&\mat{A}\mat{B}&\mat{A}^2\mat{B}&\hdots&\mat{A}^{n-1}\mat{B}\end{array}]
-\label{eq:rncf}
-\end{equation}
-be the reachability matrix of the system, and
-\begin{equation}
-\mat{R}_{cf}=\left[\begin{array}{ccccc}1&a_1&a_2&\hdots&a_{n-1}\\0&1&a_1&\hdots&a_{n-2}\\ \vdots&\ddots&\ddots&\ddots&\ddots\end{array}\right]
-\label{eq:rcf}
-\end{equation}
-the reachability matrix of the canonical form. Then 
-\begin{equation}
-\mat{T}=\mat{R}_{cf}\mat{R}^{-1}
-\label{eq:to_cf}
-\end{equation}
 

### 2017-01-25 cav2017/cav2017.tex
paper beautification

@@
 the entries of matrix $K$, so that the closed-loop dynamics are shaped as
-desired (see Appendix~\ref{sec:appendix-stability} for details).
+desired (see Appendix~\ref{sec:appendix-stability} for details.
 
@@
  \State set $x_0$ to be a vertex state, e.g., $[\underline{x_0},\underline{x_0}]$	
-\For ($c=0; c < 2^{Num_States}; c++$)
+\While ($c=0; c < 2^{Num_States}; c++$)
   %\State assert($ \underline{x_0}  \leq x_0 \leq \overline{x_0}$)
@@
   	\State set $x_0$ to be a new vertex state
-  	\EndFor
+  	\EndWhile
   %\State Return $K$
@@
 \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
-where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is the error introduced by the DAC and $q3$ is the maximum truncation and rounding error of the mathematical operation $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}.
-We consider the error introduced by the DAC to be equal to zero, since the domain of the plant is at a higher precision than the controller.
+where $q3$ is the maximum truncation and rounding error of $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}.
 %More details on how to model quantization as noise are given in the 
@@
 %
-Let us take the Helicopter example in Table \ref{table:State-space-benchmarks} with discretized dynamics
+Let us take the Helicopter example in Table \ref{table:State-space benchmarks} with discretized dynamics
 $$A_d = \left[\begin{array}{ccc}2.6207&-1.1793&0.65705\\2&0&0\\0&0.5&0\end{array}\right], B_d = \left [\begin{array}{c}8\\0\\0\end{array}\right]$$
@@
 
-We give the runtimes required to synthesize a stable controller for each
+We give the run-times required to synthesize a stable controller for each
 benchmark in Table~\ref{tab:results}.  
-Here \textit{Benchmark} is the name of the respective
+Here \textit{Benchmark} is the name of the employed
 benchmark, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used
@@
 \scriptsize
-\begin{tabular}{| c | l | c | r | c | r |}
+\begin{tabular}{| r | c | c | r | c | r |}
 \hline
-\# & \multicolumn{1}{|c|}{Benchmark}  & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
+\# & Benchmark  & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
    &            & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
@@
 %
-Our algorithm to select suitable FWL word widths to model the plant behavior employs a heuristic based on user-provided controller word-width specifications.
+Our algorithm to select suitable FWL word widths to model plant behavior employs a heuristic based on user-provided controller word-width specifications.
 For the first approach, where we may need to increase the precision of the time discretization, we select the time steps for the discretizations on a similar basis.
@@
 
+%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%\subsection{Controllable canonical form} \label{sec:reachable}
+%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%
+%Let us have a discrete time SISO system with an $n^{th},m^{th} : n\geq m$ order armax model
+%$$y[k]=\sum_{i=1}^n a_iy[k-i]+\sum_{i=0}^m b_iu[k-i],$$
+%where $y$ is the output of the system and $u$ its input.
+%The equivalent LTI dynamics of such a model are:
+%\begin{align}
+%\label{eq:cf_SISO}
+%\vec{x}_{k+1}=&\mat{A}_{cf}\vec{x}_k+\mat{B}_{cf}u_k : \vec{x}_k=[y_{k-n}\ \hdots y_{k-1}\ y_{k}]^T\\
+%y_k=&\mat{C}_{cf}\vec{x}_k + b_0u_k\nonumber\\
+%\mat{A}_{cf}=&\left[
+%\begin{array}{ccccc}
+%0&1&0&\cdots&0\\
+%0&0&1&\cdots&0\\
+%\vdots&\vdots&\vdots&\ddots&\vdots\\
+%0&0&0&\cdots&1\\
+%-a_n&-a_{n-1}&-a_{n-2}&\cdots&-a_1
+%\end{array}\right],
+%\mat{B}_{cf}=\left[
+%\begin{array}{c}
+%0\\0\\ \vdots\\ 0\\ 1
+%\end{array}\right]\nonumber\\
+%\mat{C}_{cf}=&[\begin{array}{ccccc}b_n-a_nb_0&b_{n-1}-a_{n-1}b_0&\cdots&b_1-a_1b_0\end{array}] : b_{i \in (m\ n]}=0\nonumber
+%\end{align}
+%
+%where the coefficients $a_i$ describe the characteristic polynomial of the system. This matrix shape is
+%called a Controllable Canonical Form because the dynamics of the feedback are directly related to these
+%coefficients. Specifically, given a feedback controller $\mat{K}$ for this system, the closed loop dynamics
+%will have the shape
+%\begin{align}
+%\mat{A}_{cf}+\mat{B}_{cf}\mat{K}_{cf}=&\left[
+%\begin{array}{ccccc}
+%0&1&0&\cdots&0\\
+%0&0&1&\cdots&0\\
+%\vdots&\vdots&\vdots&\ddots&\vdots\\
+%0&0&0&\cdots&1\\
+%k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
+%\end{array}\right]
+%\label{eq:cf_SISO_fb}
+%\end{align}
+%which means we can directly modify each coefficient by selecting a controller parameter.
+%In the MIMO case, the Controllable Canonical Form has the following shape:
+%\begin{align}
+%\mat{A}_{cf}=&\left[
+%\begin{array}{ccccc}
+%0&\mat{I}_{n-1}&0&\cdots&0\\
+%0&0&\mat{I}_{n-2}&\cdots&0\\
+%\vdots&\vdots&\vdots&\ddots&\vdots\\
+%0&0&0&\cdots&1\\
+%-\mat{a_n}\mat{M}_n&-\mat{a_{n-1}}\mat{M}_{n-1}&-\mat{a_{n-2}}\mat{M}_{n-2}&\cdots&-\mat{a_1}\mat{M}_{1}
+%\end{array}\right],
+%\mat{B}_{cf}=\left[
+%\begin{array}{c}
+%0\\0\\ \vdots\\ 0\\ \mat{M}_0
+%\end{array}\right]\nonumber\\
+%\mat{C}_{cf}=&[\begin{array}{ccccc}\mat{\eta}_n&\mat{\eta}_{n-1}&\cdots&\mat{\eta}_1\end{array}] :
+%\mat{I}_i,\mat{M}_i \in \mathbb{R}^{q_i \times q_i} \wedge \mat{a}_i \in \mathbb{R}^{q \times q_i} \wedge \mat{\eta}_i \in \mathbb{R}^o \wedge  \mat{\eta}_{i \in (m\ n]}=0 \nonumber
+%\label{eq:cf_MIMO}
+%\end{align}
+%where $q$ is the number of inputs, $q_i$ the number of inputs with a transfer function of order of at least $i$, $\mat{I}_i$ an identity matrix, $\mat{M}_i$ an upper triangular matrix with 1s in its diagonal, $\mat{a_i}$ a matrix of coefficients of the $i^th$ order on its diagonal, and $o$ the number of outputs.
+Ideally we aim for $\mat{M}_i=\mat{I}_i, \forall i>0$
+%
+%Any LTI system can be transformed into a controllable canonical form by a matrix $\mat{T} : \vec{x}=\mat{T}\hat{\vec{x}}$
+%Then the dynamics of the controllable form are
+%\begin{align}
+%\hat{\vec{x}}_{k+1}=&\mat{A}_{cf}\hat{\vec{x}}_k+\mat{B}_{cf}u_k : \mat{A}_{cf}=\mat{T}\mat{A}\mat{T}^{-1} \wedge \mat{B}_{cf}=\mat{T}\mat{B}\\
+%y_k=&\mat{C}_{cf}\hat{\vec{x}}_k + b_0u_k : \mat{C}_{cf}=\mat{C}\mat{T}^{-1}\nonumber
+%\end{align}
+%where $\mat{T}$ can be calculated as follows:
+%
+%Let 
+%\begin{equation}
+%\mat{R}=[\begin{array}{ccccc}\mat{B}&\mat{A}\mat{B}&\mat{A}^2\mat{B}&\hdots&\mat{A}^{n-1}\mat{B}\end{array}]
+%\label{eq:rncf}
+%\end{equation}
+%be the reachability matrix of the system, and
+%\begin{equation}
+%\mat{R}_{cf}=\left[\begin{array}{ccccc}1&a_1&a_2&\hdots&a_{n-1}\\0&1&a_1&\hdots&a_{n-2}\\ \vdots&\ddots&\ddots&\ddots&\ddots\end{array}\right]
+%\label{eq:rcf}
+%\end{equation}
+%the reachability matrix of the canonical form. Then 
+%\begin{equation}
+%\mat{T}=\mat{R}_{cf}\mat{R}^{-1}
+%\label{eq:to_cf}
+%\end{equation}
+%
+
 % %-------------------------------
@@
 
+\newpage
+
 %-------------------------------
@@
 %-------------------------------
+
+We have derived a number of benchmarks from the control literature, which we report below. 
+As discussed, in this paper, we disregard the presence of output signals, that is the effect of matrices $\textbf{C}, \textbf{D}$. 
+%
 

### 2017-01-25 cav2017/cav2017.tex
american

--- 2017-01-25 cav2017/cav2017.tex
@@
 
-Both models synthesise sound safe controllers given a discrete-time model of the closed-loop system.
+Both models synthesize sound safe controllers given a discrete-time model of the closed-loop system.
 

### 2017-01-25 cav2017/cav2017.tex
num changes rep

@@
 which performs operations in the domain of fixed-point numbers. 
-In this section we formally outline the errors introduced by the fixed-point representation of numbers. 
-% 
+In this section we outline the notation for the fixed-point representation of numbers, and briefly describe the errors introduced. A formal outline is in Appendix~\ref{appendix:numerical_errors}.
+
 Let $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part.
@@
 Any mathematical operations performed at the precision $\mathcal{F}_{\langle I,F \rangle}(x)$ will introduce errors, that can be upper bounded~\cite{DBLP:conf/arith/BrainTRW15}.
-Further details are in Appendix~\ref{appendix:numerical_errors}.
 
@@
 
-Let $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part.
+We have  used $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part.
 The smallest number that can be represented in this domain is $c_m=2^{-F}$.

### 2017-01-25 cav2017/cav2017.tex
Added paragraphs in threats to validty.
Added paragraphs to differentiate different threats more clearly.

@@
 %-------------------------------
-We report an assessment of both our approaches over a diverse set of real-world benchmarks.
-Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalize to other benchmarks.
-%
-Our algorithm to select suitable FWL word widths to model the plant behavior employs a heuristic based on user-provided controller word-width specifications.
+\textit{Benchmark selection:} We report an assessment of both our approaches over a diverse set of real-world benchmarks.
+Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalize to other benchmarks.\\
+%
+\textit{Plant precision and discretization heuristic:} Our algorithm to select suitable FWL word widths to model the plant behavior employs a heuristic based on user-provided controller word-width specifications.
 For the first approach, where we may need to increase the precision of the time discretization, we select the time steps for the discretizations on a similar basis.
-This works sufficiently well for our benchmarks, but performance may suffer in some cases, for example if the completeness threshold is high.
-%
-The performance gain from abstract acceleration may not hold for more complex properties than stability, for instance ``eventually always reaches a certain safe set''.
+This works sufficiently well for our benchmarks, but performance may suffer in some cases, for example if the completeness threshold is high.\\
+%
+\textit{Abstraction on other properties:} The performance gain from abstract acceleration may not hold for more complex properties than stability, for instance ``eventually always reaches a certain safe set''.
 

### 2017-01-25 cav2017/cav2017.tex
minor change

@@
 digital state-feedback controls
-and prove their soundness by encompassing errors due to digitalization and quantization effects that are present in the digital controller interacting with the continuous plant. 
-% computations and representations of dynamics, providing sufficient conditions for sound and complete safe solutions for the state feedback control problem.
+and prove their soundness by encompassing errors due to digitalization and quantization 
+effects that are present in the digital controller interacting with the continuous plant. 
+Both models synthesize sound safe controllers given a discrete-time model of the closed-loop system.
 
@@
 
-Both models synthesize sound safe controllers given a discrete-time model of the closed-loop system.
-
 We provide experimental results 
@@
 for a set of intricate physical plant models taken from the digital 
-control literature: the median runtime for our benchmark
+control literature: the median run-time for our benchmark
 set is $7.9$ seconds, and most controllers can be synthesized in less
 than $17.2$ seconds. We further show that, in a direct comparison, the abstraction-based
-approach lowers the median runtime of our benchmarks by a factor of seven over the
+approach lowers the median run-time of our benchmarks by a factor of seven over the
 multi-staged approach.
@@
   error sources in the implementation of the control algorithm and in the
-  computational modelling of plant dynamics.
+  computational modeling of plant dynamics.
 %
@@
 directly model the digital controller so that the selected parameters are
-stable by design.  The analyses in~\cite{DBLP:conf/hybrid/RouxJG15,
+stable by design.  The analysis in~\cite{DBLP:conf/hybrid/RouxJG15,
 DBLP:conf/hybrid/WangGRJF16} rely on an invariant computation on the
@@
 in this paper we require stability only as a precursor to safety, it is 
-sufficient to check that the (perturbed, noisy) model converges to a neighbourhood of the equilibrium within the safe set.
+sufficient to check that the (perturbed, noisy) model converges to a neighborhood of the equilibrium within the safe set.
 
@@
 the reference signal to be set to zero, 
-saturations on the inputs, 
+saturation on the inputs, 
 and account for digitalization and quantization errors introduced by the controller.
@@
 To synthesize a controller that satisfies the stability criteria, we require that
-a computed characteristic polynomial satisifies Jury's criteria. The details of this
+a computed characteristic polynomial satisfies Jury's criteria. The details of this
 calculation can be found in the Appendix.
@@
  \State set $x_0$ to be a vertex state, e.g., $[\underline{x_0},\underline{x_0}]$	
-\For ($c=0; c < 2^{Num_States}; c++$)
+\For {($c=0; c < 2^{Num_States}; c++$)}
   %\State assert($ \underline{x_0}  \leq x_0 \leq \overline{x_0}$)
@@
 Although this candidate is stable, the {\sc verify} phase finds it to be unsafe and returns a list of iterations with an example initial state that fails the safety specification
-$(k,x_0) \in \{ (2, [\begin{array}{ccc}0.9&-0.9&0.9\end{array}]), (3, [\begin{array}{ccc}0.9&-0.9&-0.9\end{array}])\}$.
+{\footnotesize $(k,x_0) {\in} \{ (2, [\begin{array}{ccc}0.9&-0.9&0.9\end{array}]), (3, [\begin{array}{ccc}0.9&-0.9&-0.9\end{array}])\}$}.
 This allows the {\sc abstract} phase to create a new safety specification that considers these iterations for these initial states to constrain the solution space.
-This refinement allows {\sc synthesize} to find a controller $K=[\begin{array}{ccc}0.23828125&-0.17578125&0.109375\end{array}]$, which this time passes the verification phase, resulting in a safe system.
+This refinement allows {\sc synthesize} to find a controller {\footnotesize $K=[\begin{array}{ccc}0.23828125&-0.17578125&0.109375\end{array}]$}, which this time passes the verification phase, resulting in a safe system.
 
@@
 
-We give the runtimes required to synthesize a stable controller for each
+We give the run-times required to synthesize a stable controller for each
 benchmark in Table~\ref{tab:results}.  
@@
 abstraction-based approach is on average able to find a solution in approximately 35\% of
-the time required using the multi-staged back-end, and has a median runtime 1.15\,s, which is
+the time required using the multi-staged back-end, and has a median run-time 1.15\,s, which is
 seven times smaller than the multi-staged approach. The two back-ends complement each other
@@
 
-The median runtime for our benchmark set is 7.9\,s.  Overall,
+The median run-time for our benchmark set is 7.9\,s.  Overall,
 the average synthesis time amounts to approximately 17.2\,s.  We
@@
 require a very precise abstraction, resulting in too many refinements
-and, consequently, a timeout.  Yet another source of incompleness is the inability
+and, consequently, a timeout.  Yet another source of incompleteness is the inability
 of the {\sc synthesize} phase to use a large enough precision for the
@@
 We have derived a number of benchmarks from the control literature, which we report below. 
-As discussed, in this paper, we disregard the presence of output signals, that is the effect of matrices $\textbf{C}, \textbf{D}$. 
+As discussed, in this paper, we disregard the presence of output signals, that is the effect of matrices $\textbf{C}, \textbf{D}$, and use
+direct state-feedback. 
 %

### 2017-01-25 cav2017/cav2017.tex
updated intro

--- 2017-01-25 cav2017/cav2017.tex
@@
 which performs operations in the domain of fixed-point numbers. 
-In this section we outline the notation for the fixed-point representation of numbers, and briefly describe the errors introduced. A formal outline is in Appendix~\ref{appendix:numerical_errors}.
-
+In this section we formally outline the errors introduced by the fixed-point representation of numbers. 
+% 
 Let $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part.
@@
 Any mathematical operations performed at the precision $\mathcal{F}_{\langle I,F \rangle}(x)$ will introduce errors, that can be upper bounded~\cite{DBLP:conf/arith/BrainTRW15}.
+Further details are in Appendix~\ref{appendix:numerical_errors}.
 
@@
 
-We have  used $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part.
+Let $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part.
 The smallest number that can be represented in this domain is $c_m=2^{-F}$.
@@
 
-%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%\subsection{Controllable canonical form} \label{sec:reachable}
-%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%
-%Let us have a discrete time SISO system with an $n^{th},m^{th} : n\geq m$ order armax model
-%$$y[k]=\sum_{i=1}^n a_iy[k-i]+\sum_{i=0}^m b_iu[k-i],$$
-%where $y$ is the output of the system and $u$ its input.
-%The equivalent LTI dynamics of such a model are:
-%\begin{align}
-%\label{eq:cf_SISO}
-%\vec{x}_{k+1}=&\mat{A}_{cf}\vec{x}_k+\mat{B}_{cf}u_k : \vec{x}_k=[y_{k-n}\ \hdots y_{k-1}\ y_{k}]^T\\
-%y_k=&\mat{C}_{cf}\vec{x}_k + b_0u_k\nonumber\\
-%\mat{A}_{cf}=&\left[
-%\begin{array}{ccccc}
-%0&1&0&\cdots&0\\
-%0&0&1&\cdots&0\\
-%\vdots&\vdots&\vdots&\ddots&\vdots\\
-%0&0&0&\cdots&1\\
-%-a_n&-a_{n-1}&-a_{n-2}&\cdots&-a_1
-%\end{array}\right],
-%\mat{B}_{cf}=\left[
-%\begin{array}{c}
-%0\\0\\ \vdots\\ 0\\ 1
-%\end{array}\right]\nonumber\\
-%\mat{C}_{cf}=&[\begin{array}{ccccc}b_n-a_nb_0&b_{n-1}-a_{n-1}b_0&\cdots&b_1-a_1b_0\end{array}] : b_{i \in (m\ n]}=0\nonumber
-%\end{align}
-%
-%where the coefficients $a_i$ describe the characteristic polynomial of the system. This matrix shape is
-%called a Controllable Canonical Form because the dynamics of the feedback are directly related to these
-%coefficients. Specifically, given a feedback controller $\mat{K}$ for this system, the closed loop dynamics
-%will have the shape
-%\begin{align}
-%\mat{A}_{cf}+\mat{B}_{cf}\mat{K}_{cf}=&\left[
-%\begin{array}{ccccc}
-%0&1&0&\cdots&0\\
-%0&0&1&\cdots&0\\
-%\vdots&\vdots&\vdots&\ddots&\vdots\\
-%0&0&0&\cdots&1\\
-%k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
-%\end{array}\right]
-%\label{eq:cf_SISO_fb}
-%\end{align}
-%which means we can directly modify each coefficient by selecting a controller parameter.
-%In the MIMO case, the Controllable Canonical Form has the following shape:
-%\begin{align}
-%\mat{A}_{cf}=&\left[
-%\begin{array}{ccccc}
-%0&\mat{I}_{n-1}&0&\cdots&0\\
-%0&0&\mat{I}_{n-2}&\cdots&0\\
-%\vdots&\vdots&\vdots&\ddots&\vdots\\
-%0&0&0&\cdots&1\\
-%-\mat{a_n}\mat{M}_n&-\mat{a_{n-1}}\mat{M}_{n-1}&-\mat{a_{n-2}}\mat{M}_{n-2}&\cdots&-\mat{a_1}\mat{M}_{1}
-%\end{array}\right],
-%\mat{B}_{cf}=\left[
-%\begin{array}{c}
-%0\\0\\ \vdots\\ 0\\ \mat{M}_0
-%\end{array}\right]\nonumber\\
-%\mat{C}_{cf}=&[\begin{array}{ccccc}\mat{\eta}_n&\mat{\eta}_{n-1}&\cdots&\mat{\eta}_1\end{array}] :
-%\mat{I}_i,\mat{M}_i \in \mathbb{R}^{q_i \times q_i} \wedge \mat{a}_i \in \mathbb{R}^{q \times q_i} \wedge \mat{\eta}_i \in \mathbb{R}^o \wedge  \mat{\eta}_{i \in (m\ n]}=0 \nonumber
-%\label{eq:cf_MIMO}
-%\end{align}
-%where $q$ is the number of inputs, $q_i$ the number of inputs with a transfer function of order of at least $i$, $\mat{I}_i$ an identity matrix, $\mat{M}_i$ an upper triangular matrix with 1s in its diagonal, $\mat{a_i}$ a matrix of coefficients of the $i^th$ order on its diagonal, and $o$ the number of outputs.
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Controllable canonical form} \label{sec:reachable}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Let us have a discrete time SISO system with an $n^{th},m^{th} : n\geq m$ order armax model
+$$y[k]=\sum_{i=1}^n a_iy[k-i]+\sum_{i=0}^m b_iu[k-i],$$
+where $y$ is the output of the system and $u$ its input.
+The equivalent LTI dynamics of such a model are:
+\begin{align}
+\label{eq:cf_SISO}
+\vec{x}_{k+1}=&\mat{A}_{cf}\vec{x}_k+\mat{B}_{cf}u_k : \vec{x}_k=[y_{k-n}\ \hdots y_{k-1}\ y_{k}]^T\\
+y_k=&\mat{C}_{cf}\vec{x}_k + b_0u_k\nonumber\\
+\mat{A}_{cf}=&\left[
+\begin{array}{ccccc}
+0&1&0&\cdots&0\\
+0&0&1&\cdots&0\\
+\vdots&\vdots&\vdots&\ddots&\vdots\\
+0&0&0&\cdots&1\\
+-a_n&-a_{n-1}&-a_{n-2}&\cdots&-a_1
+\end{array}\right],
+\mat{B}_{cf}=\left[
+\begin{array}{c}
+0\\0\\ \vdots\\ 0\\ 1
+\end{array}\right]\nonumber\\
+\mat{C}_{cf}=&[\begin{array}{ccccc}b_n-a_nb_0&b_{n-1}-a_{n-1}b_0&\cdots&b_1-a_1b_0\end{array}] : b_{i \in (m\ n]}=0\nonumber
+\end{align}
+
+where the coefficients $a_i$ describe the characteristic polynomial of the system. This matrix shape is
+called a Controllable Canonical Form because the dynamics of the feedback are directly related to these
+coefficients. Specifically, given a feedback controller $\mat{K}$ for this system, the closed loop dynamics
+will have the shape
+\begin{align}
+\mat{A}_{cf}+\mat{B}_{cf}\mat{K}_{cf}=&\left[
+\begin{array}{ccccc}
+0&1&0&\cdots&0\\
+0&0&1&\cdots&0\\
+\vdots&\vdots&\vdots&\ddots&\vdots\\
+0&0&0&\cdots&1\\
+k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
+\end{array}\right]
+\label{eq:cf_SISO_fb}
+\end{align}
+which means we can directly modify each coefficient by selecting a controller parameter.
+In the MIMO case, the Controllable Canonical Form has the following shape:
+\begin{align}
+\mat{A}_{cf}=&\left[
+\begin{array}{ccccc}
+0&\mat{I}_{n-1}&0&\cdots&0\\
+0&0&\mat{I}_{n-2}&\cdots&0\\
+\vdots&\vdots&\vdots&\ddots&\vdots\\
+0&0&0&\cdots&1\\
+-\mat{a_n}\mat{M}_n&-\mat{a_{n-1}}\mat{M}_{n-1}&-\mat{a_{n-2}}\mat{M}_{n-2}&\cdots&-\mat{a_1}\mat{M}_{1}
+\end{array}\right],
+\mat{B}_{cf}=\left[
+\begin{array}{c}
+0\\0\\ \vdots\\ 0\\ \mat{M}_0
+\end{array}\right]\nonumber\\
+\mat{C}_{cf}=&[\begin{array}{ccccc}\mat{\eta}_n&\mat{\eta}_{n-1}&\cdots&\mat{\eta}_1\end{array}] :
+\mat{I}_i,\mat{M}_i \in \mathbb{R}^{q_i \times q_i} \wedge \mat{a}_i \in \mathbb{R}^{q \times q_i} \wedge \mat{\eta}_i \in \mathbb{R}^o \wedge  \mat{\eta}_{i \in (m\ n]}=0 \nonumber
+\label{eq:cf_MIMO}
+\end{align}
+where $q$ is the number of inputs, $q_i$ the number of inputs with a transfer function of order of at least $i$, $\mat{I}_i$ an identity matrix, $\mat{M}_i$ an upper triangular matrix with 1s in its diagonal, $\mat{a_i}$ a matrix of coefficients of the $i^th$ order on its diagonal, and $o$ the number of outputs.
 Ideally we aim for $\mat{M}_i=\mat{I}_i, \forall i>0$
-%
-%Any LTI system can be transformed into a controllable canonical form by a matrix $\mat{T} : \vec{x}=\mat{T}\hat{\vec{x}}$
-%Then the dynamics of the controllable form are
-%\begin{align}
-%\hat{\vec{x}}_{k+1}=&\mat{A}_{cf}\hat{\vec{x}}_k+\mat{B}_{cf}u_k : \mat{A}_{cf}=\mat{T}\mat{A}\mat{T}^{-1} \wedge \mat{B}_{cf}=\mat{T}\mat{B}\\
-%y_k=&\mat{C}_{cf}\hat{\vec{x}}_k + b_0u_k : \mat{C}_{cf}=\mat{C}\mat{T}^{-1}\nonumber
-%\end{align}
-%where $\mat{T}$ can be calculated as follows:
-%
-%Let 
-%\begin{equation}
-%\mat{R}=[\begin{array}{ccccc}\mat{B}&\mat{A}\mat{B}&\mat{A}^2\mat{B}&\hdots&\mat{A}^{n-1}\mat{B}\end{array}]
-%\label{eq:rncf}
-%\end{equation}
-%be the reachability matrix of the system, and
-%\begin{equation}
-%\mat{R}_{cf}=\left[\begin{array}{ccccc}1&a_1&a_2&\hdots&a_{n-1}\\0&1&a_1&\hdots&a_{n-2}\\ \vdots&\ddots&\ddots&\ddots&\ddots\end{array}\right]
-%\label{eq:rcf}
-%\end{equation}
-%the reachability matrix of the canonical form. Then 
-%\begin{equation}
-%\mat{T}=\mat{R}_{cf}\mat{R}^{-1}
-%\label{eq:to_cf}
-%\end{equation}
-%
+
+Any LTI system can be transformed into a controllable canonical form by a matrix $\mat{T} : \vec{x}=\mat{T}\hat{\vec{x}}$
+Then the dynamics of the controllable form are
+\begin{align}
+\hat{\vec{x}}_{k+1}=&\mat{A}_{cf}\hat{\vec{x}}_k+\mat{B}_{cf}u_k : \mat{A}_{cf}=\mat{T}\mat{A}\mat{T}^{-1} \wedge \mat{B}_{cf}=\mat{T}\mat{B}\\
+y_k=&\mat{C}_{cf}\hat{\vec{x}}_k + b_0u_k : \mat{C}_{cf}=\mat{C}\mat{T}^{-1}\nonumber
+\end{align}
+where $\mat{T}$ can be calculated as follows:
+
+Let 
+\begin{equation}
+\mat{R}=[\begin{array}{ccccc}\mat{B}&\mat{A}\mat{B}&\mat{A}^2\mat{B}&\hdots&\mat{A}^{n-1}\mat{B}\end{array}]
+\label{eq:rncf}
+\end{equation}
+be the reachability matrix of the system, and
+\begin{equation}
+\mat{R}_{cf}=\left[\begin{array}{ccccc}1&a_1&a_2&\hdots&a_{n-1}\\0&1&a_1&\hdots&a_{n-2}\\ \vdots&\ddots&\ddots&\ddots&\ddots\end{array}\right]
+\label{eq:rcf}
+\end{equation}
+the reachability matrix of the canonical form. Then 
+\begin{equation}
+\mat{T}=\mat{R}_{cf}\mat{R}^{-1}
+\label{eq:to_cf}
+\end{equation}
 
@@
 
-\newpage
-
 %-------------------------------
@@
 %-------------------------------
-
-We have derived a number of benchmarks from the control literature, which we report below. 
-As discussed, in this paper, we disregard the presence of output signals, that is the effect of matrices $\textbf{C}, \textbf{D}$. 
-%
 

### 2017-01-25 cav2017/cav2017.tex
division in fixed point

@@
 However, we do use division in computations at the precision of the plant.
-$\mathcal{F}_{\langle I,F \rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3| \leq $, where $c_m=2^{-F}$ as above.
+Here the error depends on whether the divisor is greater or smaller than the dividend.
+$\mathcal{F}_{\langle I,F \rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) =  (c_1 - \delta_{T1})/ (c_2 + \delta_{T2}) + c_m $, where $c_m=2^{-F}$ as above.
 \end{enumerate}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%\subsection{Modelling quantization as noise} \label{appendix:quantization-noise}
+\subsection{Modelling quantization as noise} \label{appendix:quantization-noise}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 
-%During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathcal{F}_{\langle I_c,F_c \rangle}$ value.
+During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathcal{F}_{\langle I_c,F_c \rangle}$ value.
 This sampling uses a threshold which is defined by the less significant bit of the ADC.
-We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (\emph{ie} the quantizer includes any digital gain added in the code), and so we will denote this error $q_{c}=2^{-F_{c}}$).
+We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (i.e., the quantizer includes any digital gain added in the code), and so we will denote this error $q_{c}=2^{-F_{c}}$).
 We omit the effect of non-linearities of the circuitry.

### 2017-01-25 cav2017/cav2017.tex
paper beautification

--- 2017-01-25 cav2017/cav2017.tex
@@
 
-{\em The first approach} uses a {\em naive}
+{\em The first approach} uses a {\em na\"ive}
 technique that starts by devising a digital controller that stabilizes the system
@@
 than $17.2$ seconds. We further show that, in a direct comparison, the abstraction-based
-approach lowers the median run-time of our benchmarks by a factor of seven over the
-multi-staged approach.
+approach (second) lowers the median run-time of our benchmarks by a factor of seven over the
+first approach based on the unfolding of the dynamics.
 
@@
   error sources in the implementation of the control algorithm and in the
-  computational modeling of plant dynamics.
+  computational modelling of plant dynamics.
 %
@@
 directly model the digital controller so that the selected parameters are
-stable by design.  The analysis in~\cite{DBLP:conf/hybrid/RouxJG15,
+stable by design.  The analyses in~\cite{DBLP:conf/hybrid/RouxJG15,
 DBLP:conf/hybrid/WangGRJF16} rely on an invariant computation on the
@@
 We consider models of physical plants expressed as ordinary differential equations (ODEs), 
-with full state information (namely where we have access to all the model variables):  
+which we assume to be controllable and under full state information (namely where we have access to all the model variables):  
 %
@@
 and with initial states set as $x(0)$. 
-Eq.~\eqref{eq:ode} is soundly discretized in time (as shown in the Appendix~\ref{sec:appendix:LTIbackground}) into %\textcolor{red}{What is subscript ``d''?}
+Whilst we ideally would like to work on the continuous-time plant, 
+in this work Eq.~\eqref{eq:ode} is soundly discretized in time (as shown in the Appendix~\ref{sec:appendix:LTIbackground}) into %\textcolor{red}{What is subscript ``d''?}
 %
@@
 in this paper we require stability only as a precursor to safety, it is 
-sufficient to check that the (perturbed, noisy) model converges to a neighborhood of the equilibrium within the safe set.
+sufficient to check that the (perturbed, noisy) model converges to a neighbourhood of the equilibrium within the safe set.
 
@@
 the reference signal to be set to zero, 
-saturation on the inputs, 
+saturations on the inputs, 
 and account for digitalization and quantization errors introduced by the controller.
@@
 To synthesize a controller that satisfies the stability criteria, we require that
-a computed characteristic polynomial satisfies Jury's criteria. The details of this
+a computed characteristic polynomial satisifies Jury's criteria. The details of this
 calculation can be found in the Appendix.
@@
 
-We give the run-times required to synthesize a stable controller for each
+We give the runtimes required to synthesize a stable controller for each
 benchmark in Table~\ref{tab:results}.  
@@
 abstraction-based approach is on average able to find a solution in approximately 35\% of
-the time required using the multi-staged back-end, and has a median run-time 1.15\,s, which is
+the time required using the multi-staged back-end, and has a median runtime 1.15\,s, which is
 seven times smaller than the multi-staged approach. The two back-ends complement each other
@@
 
-The median run-time for our benchmark set is 7.9\,s.  Overall,
+The median runtime for our benchmark set is 7.9\,s.  Overall,
 the average synthesis time amounts to approximately 17.2\,s.  We
@@
 require a very precise abstraction, resulting in too many refinements
-and, consequently, a timeout.  Yet another source of incompleteness is the inability
+and, consequently, a timeout.  Yet another source of incompleness is the inability
 of the {\sc synthesize} phase to use a large enough precision for the
@@
 
-Future work will focus the extension of these approaches to the continuous time case with output-based control architectures (hinging on the use of observers), 
+Future work will focus the extension of these approaches to the continuous time case, 
+to models with output-based control architectures (hinging on the use of observers), 
 and to considering performance requirements (alongside safety) in the synthesis of digital controllers.

### 2017-01-25 cav2017/cav2017.tex
quantization noise

@@
 Here the error depends on whether the divisor is greater or smaller than the dividend.
-$\mathcal{F}_{\langle I,F \rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) =  (c_1 - \delta_{T1})/ (c_2 + \delta_{T2}) + c_m $, where $c_m=2^{-F}$ as above.
+$\mathcal{F}_{\langle I,F \rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_{T3}$ where $\delta_{T3}$ is $(\delta_{T2}*c_1 - \delta_{T1}*c_2)/(\delta_{T2}^2 - \delta_{T2} c_2)$,
+%$\mathcal{F}_{\langle I,F \rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) =  (c_1 - \delta_{T1})/ (c_2 + \delta_{T2}) + c_m $, where $c_m=2^{-F}$ as above.
 \end{enumerate}
@@
 
-During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathcal{F}_{\langle I_c,F_c \rangle}$ value.
+During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed by $\mathcal{F}\langle I_{c},F_{c} \rangle (x)$.
+this sampling uses a threshold which is defined by the less significant bit ($q_{adc}=2^{-F_{adc}}$) of the ADC and some non-linearities of the circuitry.
+The overall conversion is
+$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{adc}}{2}\right]$$
+If we denote the error in the conversion as $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
+
+We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (\emph{ie} the quantizer includes any digital gain added in the code).
+The process of quantization in the DAC is similar except that it is calculating $\mathcal{F}\langle I_{dac},F_{dac} \rangle (\mathcal{F}\langle I_{c},F_{c} \rangle (x)) $.
+If these domains are the same ($I_{c}=I_{dac},F_{c}=F_{dac}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
+From the above equations we can now infer that $\nu_1 \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], \nu_2 \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{c} \wedge q_2=q_{dac}$.
+Note that these bounds hold irrespective of whether the noise is correlated, hence we may use them to over-approximate the effect of the noise on the state space progression over time.
+The resulting dynamics are:
+\begin{align}
+\label{eq:pre_quantization}
+\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d(\vec{u}_k+{\vec{\nu}_2}_k),\\
+u_k&=-K\vec{x}_{k}+{\vec{\nu}_1}_k. 
+\end{align}
+
+%During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathcal{F}_{\langle I_c,F_c \rangle}$ value.
 This sampling uses a threshold which is defined by the less significant bit of the ADC.
@@
 %If we denote the error in the conversion as noise $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
+
+which give the closed loop dynamics:
+\begin{align}
+\label{eq:quantization}
+\vec{x}_{k+1} &= (\vec{A}_d-\vec{B}_d\mat{K}_d) \vec{x}_k+\vec{B}_d{\vec{\nu}_2}_k +{\vec{\nu}_1}_k. 
+\end{align}
 

### 2017-01-25 cav2017/cav2017.tex
undoing an unintentional change

--- 2017-01-25 cav2017/cav2017.tex
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Modelling quantization as noise} \label{appendix:quantization-noise}
+%\subsection{Modelling quantization as noise} \label{appendix:quantization-noise}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 
-During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathcal{F}_{\langle I_c,F_c \rangle}$ value.
+%During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathcal{F}_{\langle I_c,F_c \rangle}$ value.
 This sampling uses a threshold which is defined by the less significant bit of the ADC.

### 2017-01-25 cav2017/cav2017.tex
final div formula
one word change

--- 2017-01-25 cav2017/cav2017.tex
@@
 %
-\textit{Abstraction on other properties:} The performance gain from abstract acceleration may not hold for more complex properties than stability, for instance ``eventually always reaches a certain safe set''.
+\textit{Abstraction on other properties:} The performance gain from abstract acceleration may not hold for more complex properties than safety, for instance ``eventually always reaches a certain safe set''.
 

### 2017-01-25 cav2017/cav2017.tex
running title
dashes

@@
 \title{Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants} 
+\titlerunning{Automated Formal Synthesis of Digital Controllers}
 
@@
 As it requires explicit unfolding up to the completeness
-threshold, this approach may suffer from state space explosion.
+threshold, this approach may suffer from state-space explosion.
 
@@
 evaluate all possible progressions of the system simultaneously and thus avoid
-the state space explosion problem.
+the state-space explosion problem.
 Additionally, the second approach uses
@@
 \item In this paper we extend the problem of digital control synthesis 
-  from a transfer function representation into a state space representation. 
+  from a transfer function representation into a state-space representation. 
   Such representation allows to study the  input-to-state dynamics, while 
@@
 %
-\item We proposes a synthesis of state feedback controllers that ensures 
+\item We proposes a synthesis of state-feedback controllers that ensures 
   safety properties, that is only  possible in state-space representation. 
@@
   speed whilst retaining soundness. Both approaches provide sound
-  synthesis of state feedback systems considering the various
+  synthesis of state-feedback systems considering the various
   error sources in the implementation of the control algorithm and in the
@@
 \item We develop a model for different sources quantization and their
-  effect on the state space progression, for which we find safe bounds
+  effect on the state-space progression, for which we find safe bounds
   that ensure the safety of our controllers in a hybrid
@@
 The embedded controller software can be more complicated than
-the state feedback control we synthesized, and the properties 
+the state-feedback control we synthesized, and the properties 
 available cover more detail.
@@
 %
-Here $K \in \mathbb{R}^{m \times n}$ is a state feedback gain matrix, 
+Here $K \in \mathbb{R}^{m \times n}$ is a state-feedback gain matrix, 
 and $r_{k}$ is a reference signal (again digital).   

### 2017-01-25 cav2017/cav2017.tex
remove hyphen

@@
 We describe and evaluate two approaches for synthesizing digital controllers for state-space physical plants, 
-both based on the Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use for program synthesis.   
+both based on the CounterExample Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use for program synthesis.   
 We provide two alternative automated procedures to synthesize safe 

### 2017-01-25 cav2017/cav2017.tex
edits

--- 2017-01-25 cav2017/cav2017.tex
@@
 %
-\item We proposes a synthesis of state-feedback controllers that ensures 
+\item We proposes a synthesis of state-feedback controllers that guarantees 
   safety properties, that is only  possible in state-space representation. 
@@
 safe states (constrained reachability).  This solution is based on
-synthesizing control Lyapunov functions for switched systems, that yield
+synthesizing control Lyapunov functions for switched systems that yield
 switching controllers with a guaranteed minimum dwell time in each mode. 
@@
 
-The work in \cite{DBLP:journals/corr/AbateBCCDKK16} investigates the
+The work in~\cite{DBLP:journals/corr/AbateBCCDKK16} investigates the
 synthesis of stabilizing controllers for continuous plants described as
@@
 synthesizing digital controllers for stable closed-loop systems described
-via transfer function models.  In contrast, in the current paper we consider
+via transfer function models.  By contrast, in the current paper we consider
 a state-space representation of the physical system, which is known to present
-various advantages over transfer function representation \cite{Astrom08}: (i) 
-easy to generalize for the multivariate systems (i.e., with multiple inputs 
-and outputs); (ii) shows the state-to-input relationships offering an internal 
-model of the system; and (iii) allows to synthesize control systems that ensures
-properties about the internal dynamics, e.g., to synthesize controllers that make
+various advantages over transfer function representation \cite{Astrom08}:
+(i)~easy to generalize for the multivariate systems (i.e., with multiple inputs 
+and outputs); (ii)~shows the state-to-input relationships offering an internal 
+model of the system; and (iii)~allows to synthesize control systems with
+guarantees about the internal dynamics, e.g., to synthesize controllers that make
 the closed-loop system \emph{safe}. This work focuses on the \emph{safety} of 
 internal states, such property is usually overlooked in the previous cited 
-works, but plays an important role in real world systems, where systems states 
-cannot assume any real value. Moreover, this work integrates an
+works, but plays an important role in real world systems, where system
+variables cannot assume arbitrary real values. Moreover, our work integrates an
 abstraction/refinement step inside the main CEGIS loop.
@@
 The tool Pessoa~\cite{mazo2010pessoa} synthesizes
-correct-by-design embedded control software, in a Matlab ToolBox.  It is based on the abstraction
+correct-by-design embedded control software, in a Matlab toolbox.  It is based on the abstraction
 of a physical system to an equivalent finite-state machine and on the
 computation of reachability properties over the finite-state machine.  Based
-on this safety specification over state values, Pessoa can synthesize
+on this safety specification, Pessoa can synthesize
 embedded controller software for a range of properties.
@@
 including delayed response~\cite{Duggirala2015}, and Finite Word Length
-(FWL) semantics, with the goal either to verify (e.g.,~ \cite{daes20161}) or
-to optimize (e.g.,~ \cite{oudjida2014design}) given implementations.
+(FWL) semantics, with the goal either to verify (e.g.,~\cite{daes20161}) or
+to optimize (e.g.,~\cite{oudjida2014design}) given implementations.
 
@@
 introduced by FWL does not make the digital system unstable.  A~more recent
-approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
+approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$-calculus to
 directly model the digital controller so that the selected parameters are
@@
 Whilst we ideally would like to work on the continuous-time plant, 
-in this work Eq.~\eqref{eq:ode} is soundly discretized in time (as shown in the Appendix~\ref{sec:appendix:LTIbackground}) into %\textcolor{red}{What is subscript ``d''?}
+in this work Eq.~\eqref{eq:ode} is soundly discretized in time (as shown in Appendix~\ref{sec:appendix:LTIbackground}) into %\textcolor{red}{What is subscript ``d''?}
 %
@@
 the case of oscillatory dynamics.  However, a safe system will always be
-stable.  In~this work, the safety property represented by $\phi_{safety}$ is
+stable.  In~this work, the safety property represented by $\phi_\mathit{safety}$ is
 encoded as follows:
@@
 \label{eq:safetyliteral}
-\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
+\phi_\mathit{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
 \end{equation}
@@
 Furthermore, it is practically relevant to consider the 
-constraints $\phi_{init}$ on the input
-signal $u_{k}$ and $\phi_{input}$ on the initial states $x_0$,
+constraints $\phi_\mathit{init}$ on the input
+signal $u_{k}$ and $\phi_\mathit{input}$ on the initial states $x_0$,
 which we assume have given bounds:
-$\phi_{init} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
-$\phi_{input} = \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$
+$\phi_\mathit{init} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
+$\phi_\mathit{input} = \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$
 In the first case, this means that the control input saturates in view of
@@
 %Appendix~\ref{appendix:quantization-noise}.
-\item Calculate a set of initial bounds on $K$, $\phi_{init}^{K}$, based on the input constraints.
+\item Calculate a set of initial bounds on $K$, $\phi_\mathit{init}^{K}$, based on the input constraints.
 Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
-$$(\phi_{init} \wedge \phi_{input} \wedge u_k=-K x_k) \Rightarrow \phi_{init}^{K}$$
+$$(\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-K x_k) \Rightarrow \phi_\mathit{init}^{K}$$
 
@@
   $K \in \mathbb{R}\langle I_c,F_c\rangle^n$ that satisfies
-  $\phi_{stability} \wedge \phi_{safety} \wedge \phi_{init}^{K}$ by invoking a SAT solver.
+  $\phi_\mathit{stability} \wedge \phi_\mathit{safety} \wedge \phi_\mathit{init}^{K}$ by invoking a SAT solver.
 %%   We obtain it by solving the SAT formula 
@@
   %consisting of evaluating the
-  progression of the system from $\phi_{init}$ over time,
-$x_{k+1} \models \phi_{safety}$. %% For this purpose we require 
+  progression of the system from $\phi_\mathit{init}$ over time,
+$x_{k+1} \models \phi_\mathit{safety}$. %% For this purpose we require 
 %% an initial set $\phi_{init}= x_0 \in [\underline{x_0} \ \overline{x_0}]$ 
@@
 we use abstract acceleration again to obtain
-the reach-tube, i.e., the set of all reachable states at all times given an initial set $\phi_{init}$:
+the reach-tube, i.e., the set of all reachable states at all times given an initial set $\phi_\mathit{init}$:
 \begin{align}
@@
 =&\mathcal{A} X_0 + \mathcal{B}_{n} N\\
-X_0 =&\left \{x : x \models \phi_{init} \right\}\nonumber
+X_0 =&\left \{x : x \models \phi_\mathit{init} \right\}\nonumber
 \end{align}
@@
   \path
-    (pre.east) edge node[align=center] {$P_a$, $N$,\\ $\phi_{init}^k$} (abstract.west)
+    (pre.east) edge node[align=center] {$P_a$, $N$,\\ $\phi_\mathit{init}^k$} (abstract.west)
     (abstract.south) edge node{$(\phi(K), \vec{k})$} (synth.north)

### 2017-01-25 cav2017/cav2017.tex
edits

@@
 The second is the quantization error introduced by the digital controller, 
-which performs operations in the domain of fixed-point numbers. 
+which performs operations on fixed-point numbers. 
 In this section we outline the notation for the fixed-point representation of numbers, and briefly describe the errors introduced. A formal outline is in Appendix~\ref{appendix:numerical_errors}.
@@
 Let us first consider the effect of the quantization errors on safety. 
-Within the digital controller block, 
-state values are manipulated at low digital precision, 
+Within the controller, 
+state values are manipulated at low precision, 
 alongside the vector multiplication $Kx$.   
 %computed considering the error introduced by the digital controller caused by performing the vector multiplication $Kx$ at low digital precision.
-As such, the inputs are computed using the following equation: 
+The inputs are computed using the following equation: 
+%
 \begin{align*}
@@
 An additional error is caused by the representation of the plant dynamics, namely 
+%
 \begin{align*}
@@
 $\overline{x_{i}}=1$ and the inputs $u_{k}=0, \forall k>0$.
-We have conducted the experimental evaluation on a 12-core 2.40 GHz
-Intel Xeon E5-2440 with 96 GB of RAM and Linux OS. We used the Linux \emph{times} command
+We have conducted the experimental evaluation on a 12-core 2.40\,GHz
+Intel Xeon E5-2440 with 96\,GB of RAM and Linux OS. We used the Linux \emph{times} command
 to measure CPU time used for each benchmark. The experimental runtime was limited to
@@
 \item {\bf Rounding:}
-The following errors appear in simple operations.
+The following errors appear in basic operations.
 Let $c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be the truncation errors caused by representing $c_1$ and $c_2$ in the fixed-point domain as above.

### 2017-01-25 cav2017/cav2017.tex
edits
abstract

@@
 %\tocauthor{Authors' Instructions}
+\author{Anonymous}
 \institute{}
@@
 feedback controllers for physical plants represented as linear, time
-invariant models.  Models are described as dynamical equations with inputs,
+invariant models.  Models are given as dynamical equations with inputs,
 evolving over a continuous state space and accounting for errors due to the
-digitalization of signals by the controller.  The approach works in two
-stages, leveraging counterexample guided inductive synthesis (CEGIS) and
+digitalization of signals by the controller.  Our approach has two stages,
+leveraging counterexample guided inductive synthesis (CEGIS) and
 reachability analysis.  CEGIS synthesizes a static feedback controller that
-stabilizes the system under some restrictions given by the safety of the
-reach space.  Safety is verified either via BMC or abstract acceleration; if
-the verification step fails, we generate an alternative controller by
-generalizing the counterexample.  We synthesize stable and safe controllers
-for intricate physical plant models from the digital control literature.
+stabilizes the system under restrictions given by the safety of the reach
+space.  Safety is verified either via BMC or abstract acceleration; if the
+verification step fails, we refine the controller by generalizing the
+counterexample.  We synthesize stable and safe controllers for intricate
+physical plant models from the digital control literature.
 %
@@
 All benchmarks were discretized with different sample times using 
-the approach described in the Appendix~\ref{sec:appendix:LTIbackground}. 
+the approach described in Appendix~\ref{sec:appendix:LTIbackground}. 
 All experiments were performed considering $\underline{x_{i}}=-1$ and 

### 2017-01-25 cav2017/cav2017.tex
form

@@
 
-Linear Time Invariant (LTI) models represent a broad class of dynamical systems
-%modern embedded software, performing highly non-trivial control tasks,
-with significant impact in numerous application areas as in 
-the life sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}.
-Synthesis of controllers for LTI models is broadly investigated, 
-however the use of digital control architectures adds new challenges due to 
-the effects of finite-precision arithmetic, time discretization, and quantization noise, which are typically introduced 
-by Analogue-to-Digital (ADC) and Digital-to-Analogue (DAC) conversion.  
-While research on digital control is well developed~\cite{astrom1997computer}, 
-automated and sound control synthesis is challenging, 
-particularly when the synthesis objective goes beyond classical stability or tracking requirements. 
-Beyond stability, recently reachability tools have been developed \cite{FLD+11,Fre05}, however they have not been employed towards
-control synthesis.
-The problem of safety is an important one, since the synthesis of a stable controller does not ensure
-that the system will not transitively visit an unsafe state which may result in an unrecoverable failure.
+Linear Time Invariant (LTI) models represent a broad class of dynamical
+systems with significant impact in numerous application areas as in the life
+sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}. 
+Synthesis of controllers for LTI models is broadly investigated, however the
+use of digital control architectures adds new challenges due to the effects
+of finite-precision arithmetic, time discretization, and quantization noise,
+which are typically introduced by Analogue-to-Digital (ADC) and
+Digital-to-Analogue (DAC) conversion.  While research on digital control is
+well developed~\cite{astrom1997computer}, automated and sound control
+synthesis is challenging, particularly when the synthesis objective goes
+beyond classical stability or tracking requirements.  Beyond stability,
+recently reachability tools have been developed~\cite{FLD+11,Fre05}, however
+they have not been employed towards control synthesis.  The problem of
+safety is an important one, since the synthesis of a stable controller does
+not ensure that the system will not transitively visit an unsafe state which
+may result in an unrecoverable failure.
 

### 2017-01-25 cav2017/cav2017.tex
form

@@
 
-We describe and evaluate two approaches for synthesizing digital controllers for state-space physical plants, 
-both based on the CounterExample Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use for program synthesis.   
-We provide two alternative automated procedures to synthesize safe 
-digital state-feedback controls
-and prove their soundness by encompassing errors due to digitalization and quantization 
-effects that are present in the digital controller interacting with the continuous plant. 
-Both models synthesize sound safe controllers given a discrete-time model of the closed-loop system.
-
-{\em The first approach} uses a {\em na\"ive}
-technique that starts by devising a digital controller that stabilizes the system
-whilst remaining safe for a 
-pre-selected time horizon and a single initial state; then, it verifies its potential safety by unfolding
-the dynamics of the system, considering the full hyper-cube of initial states, and checking for a {\em completeness threshold}, i.e.,
-the number of iterations required to sufficiently unwind
-the closed-loop state-space system such
-that the boundaries are not violated for any larger number of iterations.
-As it requires explicit unfolding up to the completeness
-threshold, this approach may suffer from state-space explosion.
+We describe and evaluate two approaches for synthesizing digital controllers
+for state-space physical plants, both based on the CounterExample Guided
+Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use
+for program synthesis.  We provide two alternative automated procedures to
+synthesize safe digital state-feedback controls and prove their soundness by
+encompassing errors due to digitalization and quantization effects that are
+present in the digital controller interacting with the continuous plant. 
+Both models synthesize sound safe controllers given a discrete-time model of
+the closed-loop system.
+
+{\em The first approach} uses a {\em na\"ive} technique that starts by
+devising a digital controller that stabilizes the system whilst remaining
+safe for a pre-selected time horizon and a single initial state; then, it
+verifies its potential safety by unfolding the dynamics of the system,
+considering the full hyper-cube of initial states, and checking for a {\em
+completeness threshold}, i.e., the number of iterations required to
+sufficiently unwind the closed-loop state-space system such that the
+boundaries are not violated for any larger number of iterations.  As it
+requires explicit unfolding up to the completeness threshold, this approach
+may suffer from state-space explosion.
 
 Instead of explicitly unfolding the dynamics, {\em the second approach}
-employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to implicitly
-evaluate all possible progressions of the system simultaneously and thus avoid
-the state-space explosion problem.
-Additionally, the second approach uses
-{\em abstraction refinement} enabling us to always start with a very simple description
-regardless of the complexity of the overall dynamics, and only expand to more
-complex models when a solution cannot be found.
-
-We provide experimental results 
-showing that both approaches are able to efficiently synthesize stable and safe controllers 
-for a set of intricate physical plant models taken from the digital 
-control literature: the median run-time for our benchmark
-set is $7.9$ seconds, and most controllers can be synthesized in less
-than $17.2$ seconds. We further show that, in a direct comparison, the abstraction-based
-approach (second) lowers the median run-time of our benchmarks by a factor of seven over the
-first approach based on the unfolding of the dynamics.
+employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to
+implicitly evaluate all possible progressions of the system simultaneously
+and thus avoid the state-space explosion problem.  Additionally, the second
+approach uses {\em abstraction refinement} enabling us to always start with
+a very simple description regardless of the complexity of the overall
+dynamics, and only expand to more complex models when a solution cannot be
+found.
+
+We provide experimental results showing that both approaches are able to
+efficiently synthesize stable and safe controllers for a set of intricate
+physical plant models taken from the digital control literature: the median
+run-time for our benchmark set is $7.9$ seconds, and most controllers can be
+synthesized in less than $17.2$ seconds.  We further show that, in a direct
+comparison, the abstraction-based approach (second) lowers the median
+run-time of our benchmarks by a factor of seven over the first approach
+based on the unfolding of the dynamics.
 
@@
 
-Program synthesizers are an ideal fit for synthesis of %parametric
-digital controllers, since the semantics of programs capture effects such as
-FWL precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use
-CEGIS for the synthesis of switching controllers for stabilizing
-continuous-time plants with polynomial dynamics.  The work extends to affine
-systems, finding a major challenge in the hardness of solving linear
-arithmetic with the state-of-the-art SMT solvers.  Since this approach uses
-switching models instead of linear dynamics for the digital controller, it
-entirely circumvents the FWL problem, but potentially incurs state-space
-explosion issues.  Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the
-same authors use a CEGIS-based approach for synthesizing continuous-time
+Program synthesizers are an ideal fit for synthesis of %parametric digital
+controllers, since the semantics of programs capture effects such as FWL
+precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
+for the synthesis of switching controllers for stabilizing continuous-time
+plants with polynomial dynamics.  The work extends to affine systems,
+finding a major challenge in the hardness of solving linear arithmetic with
+the state-of-the-art SMT solvers.  Since this approach uses switching models
+instead of linear dynamics for the digital controller, it entirely
+circumvents the FWL problem, but potentially incurs state-space explosion
+issues.  Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same
+authors use a CEGIS-based approach for synthesizing continuous-time
 switching controllers that guarantee \emph{reach-while-stay} properties of
@@
 transfer functions, by exploiting bit-accurate verification of
-software-implemented digital controllers~\cite{IsmailBCFF15,Bessa16}.  While this work
-also makes use of a CEGIS-based technique, the approach is restricted to
-synthesizing digital controllers for stable closed-loop systems described
-via transfer function models.  By contrast, in the current paper we consider
-a state-space representation of the physical system, which is known to present
-various advantages over transfer function representation \cite{Astrom08}:
-(i)~easy to generalize for the multivariate systems (i.e., with multiple inputs 
-and outputs); (ii)~shows the state-to-input relationships offering an internal 
-model of the system; and (iii)~allows to synthesize control systems with
-guarantees about the internal dynamics, e.g., to synthesize controllers that make
-the closed-loop system \emph{safe}. This work focuses on the \emph{safety} of 
-internal states, such property is usually overlooked in the previous cited 
-works, but plays an important role in real world systems, where system
-variables cannot assume arbitrary real values. Moreover, our work integrates an
+software-implemented digital controllers~\cite{IsmailBCFF15,Bessa16}.  While
+this work also makes use of a CEGIS-based technique, the approach is
+restricted to synthesizing digital controllers for stable closed-loop
+systems described via transfer function models.  By contrast, in the current
+paper we consider a state-space representation of the physical system, which
+is known to present various advantages over transfer function
+representation~\cite{Astrom08}: (i)~easy to generalize for the multivariate
+systems (i.e., with multiple inputs and outputs); (ii)~shows the
+state-to-input relationships offering an internal model of the system; and
+(iii)~allows to synthesize control systems with guarantees about the
+internal dynamics, e.g., to synthesize controllers that make the closed-loop
+system \emph{safe}.  This work focuses on the \emph{safety} of internal
+states, such property is usually overlooked in the previous cited works, but
+plays an important role in real world systems, where system variables cannot
+assume arbitrary real values.  Moreover, our work integrates an
 abstraction/refinement step inside the main CEGIS loop.
 
-The tool Pessoa~\cite{mazo2010pessoa} synthesizes
-correct-by-design embedded control software, in a Matlab toolbox.  It is based on the abstraction
-of a physical system to an equivalent finite-state machine and on the
-computation of reachability properties over the finite-state machine.  Based
-on this safety specification, Pessoa can synthesize
-embedded controller software for a range of properties.
-The embedded controller software can be more complicated than
-the state-feedback control we synthesized, and the properties 
-available cover more detail.
+The tool Pessoa~\cite{mazo2010pessoa} synthesizes correct-by-design embedded
+control software, in a Matlab toolbox.  It is based on the abstraction of a
+physical system to an equivalent finite-state machine and on the computation
+of reachability properties over the finite-state machine.  Based on this
+safety specification, Pessoa can synthesize embedded controller software for
+a range of properties.  The embedded controller software can be more
+complicated than the state-feedback control we synthesized, and the
+properties available cover more detail.
+%
 %based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
@@
 discrete system dynamics using Semi-Definite Programming (SDP).  While the
-former uses bounded-input and bounded-output (BIBO) properties to determine stability, 
-the latter uses Lyapunov-based quadratic invariants.  In both cases, the SDP solver uses
-floating-point arithmetic and soundness is checked by bounding the error. 
-An alternative approach is taken by~\cite{park2016scalable}, where the
-verification of given control code is performed against a known model by
-extracting an LTI model of the code through symbolic execution.  In order to
-account for rounding errors, an upper bound is introduced in the
-verification phase.  The work in \cite{picasso2003stabilization,
-picasso2002construction} introduces attractive invariant sets as a mechanism
-to bound the quantization error effect on stabilization as an invariant set
-that always converges toward the controllable set.  In a similar fashion,
-\cite{liberzon2003hybrid} evaluates the dynamics of the quantization error
-and bounds its trajectory to a known region over a finite period of time. 
-This technique works for both linear and non-linear systems.
+former uses bounded-input and bounded-output (BIBO) properties to determine
+stability, the latter uses Lyapunov-based quadratic invariants.  In both
+cases, the SDP solver uses floating-point arithmetic and soundness is
+checked by bounding the error.  An alternative approach is taken
+by~\cite{park2016scalable}, where the verification of given control code is
+performed against a known model by extracting an LTI model of the code
+through symbolic execution.  In order to account for rounding errors, an
+upper bound is introduced in the verification phase.  The work in
+\cite{picasso2003stabilization, picasso2002construction} introduces
+attractive invariant sets as a mechanism to bound the quantization error
+effect on stabilization as an invariant set that always converges toward the
+controllable set.  In a similar fashion, \cite{liberzon2003hybrid} evaluates
+the dynamics of the quantization error and bounds its trajectory to a known
+region over a finite period of time.  This technique works for both linear
+and non-linear systems.
 

### 2017-01-25 cav2017/cav2017.tex
wordings

@@
 synthesis is challenging, particularly when the synthesis objective goes
-beyond classical stability or tracking requirements.  Beyond stability,
-recently reachability tools have been developed~\cite{FLD+11,Fre05}, however
-they have not been employed towards control synthesis.  The problem of
-safety is an important one, since the synthesis of a stable controller does
-not ensure that the system will not transitively visit an unsafe state which
-may result in an unrecoverable failure.
-
-In this work, we propose the synthesis of \emph{safe} control algorithms for
-LTI models taking into consideration the continuous dynamics of the plant, 
-alongside the discrete dynamics of the controller and the effects of its 
-implementation, as well as the hybrid elements that relate them.  
+beyond classical stability.  There are recent methods for verifying more
+general reachability properties of a given controller~\cite{FLD+11,Fre05}. 
+However, these methods have not been generalized to control synthesis. 
+We~remark that a synthesis algorithm that guarantees satability does not
+ensure safety: the system might transitively visit an unsafe state that
+results in an unrecoverable failure.
+
+We propose a novel algorithm for the synthesis of control algorithms for LTI
+models that are guaranteed to be both stable and safe, considering both the
+continuous dynamics of the plant and the finite-precision discrete dynamics
+of the controller, as well as the hybrid elements that connect them.
+%
 %% In this paper, we synthesize controllers for hybrid
@@
 %% \emph{safe}.
-Due to the complexity of such systems, in this work we focus 
-on linear models with known  implementation features (e.g., number of bits, fixed-point
-arithmetic). We specify the safety requirement over the state space. This is a property often 
-overlooked in feedback control synthesis, but which plays an important role 
-in real-world systems.
+%
+Due to the complexity of such systems, we focus on linear models with known
+implementation features (e.g., number of bits, fixed-point arithmetic). 
+We~expect a safety requirement given as a reachability property.  Safety
+requirements are frequently overlooked in conventional feedback control
+synthesis, but play an important role in systems engineering.
 

### 2017-01-25 cav2017/cav2017.tex
Quantization noise appendix fixes

@@
 
-During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed by $\mathcal{F}\langle I_{c},F_{c} \rangle (x)$.
-this sampling uses a threshold which is defined by the less significant bit ($q_{adc}=2^{-F_{adc}}$) of the ADC and some non-linearities of the circuitry.
+During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed by $\mathcal{F}\langle I_{c},F_{c} \rangle (x)$ (assuming the ADC discretization is the same as the digital implementation).
+this sampling uses a threshold which is defined by the less significant bit ($q_{c}=2^{-F_c}$) of the ADC and some non-linearities of the circuitry.
 The overall conversion is
-$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{adc}}{2}\right]$$
+$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right]$$
 If we denote the error in the conversion as $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
@@
 If these domains are the same ($I_{c}=I_{dac},F_{c}=F_{dac}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
-From the above equations we can now infer that $\nu_1 \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], \nu_2 \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{c} \wedge q_2=q_{dac}$.
+From the above equations we can now define the ADC and DAC quantization noises, ${\nu_1}_k \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], {\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{c} \wedge q_2=q_{dac}$.
+Where $Q_1$ is the quantizer of the ADC and $Q_2$ the quantizer for the DAC (see fig.
+\ref{ssec:statefeedbackcontrol}).
 Note that these bounds hold irrespective of whether the noise is correlated, hence we may use them to over-approximate the effect of the noise on the state space progression over time.

### 2017-01-25 cav2017/cav2017.tex
rephrasing and removed some vectors that A doesn't like for some reason

@@
 During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed by $\mathcal{F}\langle I_{c},F_{c} \rangle (x)$ (assuming the ADC discretization is the same as the digital implementation).
-this sampling uses a threshold which is defined by the less significant bit ($q_{c}=2^{-F_c}$) of the ADC and some non-linearities of the circuitry.
+This sampling uses a threshold which is defined by the less significant bit ($q_{c}=2^{-F_c}$) of the ADC and some non-linearities of the circuitry.
 The overall conversion is
@@
 If these domains are the same ($I_{c}=I_{dac},F_{c}=F_{dac}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
-From the above equations we can now define the ADC and DAC quantization noises, ${\nu_1}_k \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], {\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{c} \wedge q_2=q_{dac}$.
-Where $Q_1$ is the quantizer of the ADC and $Q_2$ the quantizer for the DAC (see fig.
-\ref{ssec:statefeedbackcontrol}).
-Note that these bounds hold irrespective of whether the noise is correlated, hence we may use them to over-approximate the effect of the noise on the state space progression over time.
+From the above equations we can now define the ADC and DAC quantization noises, ${\nu_1}_k \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], {\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}]$ where $q_1=q_{c} \wedge q_2=q_{dac}$.
+Note that this is shown in fig.
+\ref{ssec:statefeedbackcontrol} where $Q_1$ is the quantizer of the ADC and $Q_2$ the quantizer for the DAC.
+These bounds hold irrespective of whether the noise is correlated, hence we may use them to over-approximate the effect of the noise on the state space progression over time.
 The resulting dynamics are:
@@
 \label{eq:pre_quantization}
-\vec{x}_{k+1} &= \vec{A}_d\vec{x}_k+\vec{B}_d(\vec{u}_k+{\vec{\nu}_2}_k),\\
-u_k&=-K\vec{x}_{k}+{\vec{\nu}_1}_k. 
+{x}_{k+1} &= {A}_d{x}_k+{B}_d({u}_k+{{\nu}_2}_k),\\
+u_k&=-K{x}_{k}+{{\nu}_1}_k. 
 \end{align}
-
-%During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed into a $\mathcal{F}_{\langle I_c,F_c \rangle}$ value.
-This sampling uses a threshold which is defined by the less significant bit of the ADC.
-We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (i.e., the quantizer includes any digital gain added in the code), and so we will denote this error $q_{c}=2^{-F_{c}}$).
-We omit the effect of non-linearities of the circuitry.
-The overall conversion is
-%$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right]$$.
-%If we denote the error in the conversion as noise $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
 
@@
 \label{eq:quantization}
-\vec{x}_{k+1} &= (\vec{A}_d-\vec{B}_d\mat{K}_d) \vec{x}_k+\vec{B}_d{\vec{\nu}_2}_k +{\vec{\nu}_1}_k. 
+{x}_{k+1} &= ({A}_d-{B}_d{K}_d) {x}_k+{B}_d{{\nu}_2}_k +{{\nu}_1}_k. 
 \end{align}

### 2017-01-25 cav2017/cav2017.tex
inconsistent i.e.,

@@
 
-We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (\emph{ie} the quantizer includes any digital gain added in the code).
+We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (i.e, the quantizer includes any digital gain added in the code).
 The process of quantization in the DAC is similar except that it is calculating $\mathcal{F}\langle I_{dac},F_{dac} \rangle (\mathcal{F}\langle I_{c},F_{c} \rangle (x)) $.

### 2017-01-25 cav2017/cav2017.tex
wordings

--- 2017-01-25 cav2017/cav2017.tex
@@
 
-We describe and evaluate two approaches for synthesizing digital controllers
-for state-space physical plants, both based on the CounterExample Guided
-Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use
-for program synthesis.  We provide two alternative automated procedures to
-synthesize safe digital state-feedback controls and prove their soundness by
-encompassing errors due to digitalization and quantization effects that are
-present in the digital controller interacting with the continuous plant. 
-Both models synthesize sound safe controllers given a discrete-time model of
-the closed-loop system.
+We give two alternative approaches for synthesizing digital controllers for
+state-space physical plants, both based on CounterExample Guided Inductive
+Synthesis (CEGIS)~\cite{sketch}.  We prove their soundness by quantifying
+errors caused digitalization and quantization effects that arise when
+time/value-discrete digital controller interacts with the continuous plant.
 
 {\em The first approach} uses a {\em na\"ive} technique that starts by
-devising a digital controller that stabilizes the system whilst remaining
+devising a digital controller that stabilizes the system while remaining
 safe for a pre-selected time horizon and a single initial state; then, it
-verifies its potential safety by unfolding the dynamics of the system,
-considering the full hyper-cube of initial states, and checking for a {\em
+verifies unbounded safety by unfolding the dynamics of the system,
+considering the full hyper-cube of initial states, and checking a {\em
 completeness threshold}, i.e., the number of iterations required to
 sufficiently unwind the closed-loop state-space system such that the
-boundaries are not violated for any larger number of iterations.  As it
+boundaries are not violated for any larger number of iterations.  As~it
 requires explicit unfolding up to the completeness threshold, this approach
-may suffer from state-space explosion.
+is computationally expensive.
 
@@
 employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to
-implicitly evaluate all possible progressions of the system simultaneously
-and thus avoid the state-space explosion problem.  Additionally, the second
-approach uses {\em abstraction refinement} enabling us to always start with
-a very simple description regardless of the complexity of the overall
-dynamics, and only expand to more complex models when a solution cannot be
-found.
+implicitly evaluate all possible progressions of the system simultaneously. 
+Additionally, the second approach uses {\em abstraction refinement},
+enabling us to always start with a very simple description regardless of the
+complexity of the overall dynamics, and only expand to more complex models
+when a solution cannot be found.
 
@@
 
-During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed by $\mathcal{F}\langle I_{c},F_{c} \rangle (x)$ (assuming the ADC discretization is the same as the digital implementation).
-this sampling uses a threshold which is defined by the less significant bit ($q_{c}=2^{-F_c}$) of the ADC and some non-linearities of the circuitry.
+During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed by $\mathcal{F}\langle I_{c},F_{c} \rangle (x)$.
+this sampling uses a threshold which is defined by the less significant bit ($q_{adc}=2^{-F_{adc}}$) of the ADC and some non-linearities of the circuitry.
 The overall conversion is
-$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right]$$
+$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{adc}}{2}\right]$$
 If we denote the error in the conversion as $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
@@
 If these domains are the same ($I_{c}=I_{dac},F_{c}=F_{dac}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
-From the above equations we can now define the ADC and DAC quantization noises, ${\nu_1}_k \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], {\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{c} \wedge q_2=q_{dac}$.
-Where $Q_1$ is the quantizer of the ADC and $Q_2$ the quantizer for the DAC (see fig.
-\ref{ssec:statefeedbackcontrol}).
+From the above equations we can now infer that $\nu_1 \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], \nu_2 \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}] : q_1=q_{c} \wedge q_2=q_{dac}$.
 Note that these bounds hold irrespective of whether the noise is correlated, hence we may use them to over-approximate the effect of the noise on the state space progression over time.

### 2017-01-25 cav2017/cav2017.tex
t = nk?

@@
 $$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right]$$
-If we denote the error in the conversion as $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
+If we denote the error in the conversion as $\nu_k=y_k-y(t)$ where $t$ is the non-descretized time $nk$, then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
 

### 2017-01-25 cav2017/cav2017.tex
ref to appendix on noise

--- 2017-01-25 cav2017/cav2017.tex
@@
 where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is the error introduced by the DAC and $q3$ is the maximum truncation and rounding error of the mathematical operation $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}.
-We consider the error introduced by the DAC to be equal to zero, since the domain of the plant is at a higher precision than the controller.
-%More details on how to model quantization as noise are given in the 
-%Appendix~\ref{appendix:quantization-noise}.
+More details on how to model quantization as noise are given in the 
+Appendix~\ref{appendix:quantization-noise}.
 \item Calculate a set of initial bounds on $K$, $\phi_\mathit{init}^{K}$, based on the input constraints.
@@
 $$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right]$$
-If we denote the error in the conversion as $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
+If we denote the error in the conversion as $\nu_k=y_k-y(t)$ where $t = nk$, and $n$ is the sampling time and $k$ the number of steps, then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
 

### 2017-01-25 cav2017/cav2017.tex
wordings

--- 2017-01-25 cav2017/cav2017.tex
@@
 %
-\item In this paper we extend the problem of digital control synthesis 
-  from a transfer function representation into a state-space representation. 
-  Such representation allows to study the  input-to-state dynamics, while 
-  transfer functions represents only input-output relations and cannot be 
-  enough to ensure deeper properties, e.g., the safety property.
-%
-\item We proposes a synthesis of state-feedback controllers that guarantees 
-  safety properties, that is only  possible in state-space representation. 
-  In addition to the already existing stability conditions which is a much 
-  harder problem.
-%
-\item We develop two approaches: the first, naive, one relies on
-  explicit unfolding of the system's dynamics up to the completeness
-  threshold, whilst the second one is abstraction-based and leverages
-  the concepts of abstraction refinement and acceleration to increase 
-  speed whilst retaining soundness. Both approaches provide sound
-  synthesis of state-feedback systems considering the various
-  error sources in the implementation of the control algorithm and in the
-  computational modeling of plant dynamics.
-%
-\item We develop a model for different sources quantization and their
-  effect on the state-space progression, for which we find safe bounds
-  that ensure the safety of our controllers in a hybrid
-  continuous-digital domain.
+\item  We give a novel synthesis algorithm for generating
+  state-feedback controllers that are provably stable and in addition
+  guaranteee a given safety property. Existing methods for controller
+  synthesis rely on transfer function representations, which are
+  insufficient to prove safety requirements.
+%
+\item We give two algorithms: the first, naive one, relies on
+  an unfolding of the system's dynamics up to a completeness threshold,
+  while the second one is abstraction-based and leverages abstraction
+  refinement and acceleration to improve the scalability of the analysis
+  while retaining soundness.  Both approaches provide sound synthesis of
+  state-feedback systems and consider the various sources of imprecision in
+  the implementation of the control algorithm and in the computational
+  modeling of plant dynamics.
+%
+\item We develop a model for different sources of quantization errors and
+  their effect on reachability properties.  We give bounds that ensure the
+  safety of our controllers in a hybrid continuous-digital domain.
 %

### 2017-01-25 cav2017/cav2017.tex
replace q1 with q_1 for consistency

@@
 \item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
-$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] 
+$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q_1}{2}\ \ \frac{q_1}{2}\right] 
 \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$

### 2017-01-25 cav2017/cav2017.tex
make notation consistent for noise

@@
 $$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q_1}{2}\ \ \frac{q_1}{2}\right] 
-\wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
-where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is the error introduced by the DAC and $q3$ is the maximum truncation and rounding error of the mathematical operation $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}.
+\wedge \nu_2 \in \left[-\frac{q_2}{2}\ \ \frac{q_2}{2}\right]  \wedge \nu_3 \in \left[-q_3\ \ q_3\right]  \right \}\nonumber$$
+where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is the error introduced by the DAC and $q_3$ is the maximum truncation and rounding error of the mathematical operation $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}.
 More details on how to model quantization as noise are given in the 

### 2017-01-25 cav2017/cav2017.tex
wordings

--- 2017-01-25 cav2017/cav2017.tex
@@
 
-Program synthesizers are an ideal fit for synthesis of %parametric digital
-controllers, since the semantics of programs capture effects such as FWL
+Program synthesizers are an ideal fit for synthesis of controllers, since
+the semantics of programs capture the effects of finite-precision arithmetic
 precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
 for the synthesis of switching controllers for stabilizing continuous-time
-plants with polynomial dynamics.  The work extends to affine systems,
-finding a major challenge in the hardness of solving linear arithmetic with
-the state-of-the-art SMT solvers.  Since this approach uses switching models
-instead of linear dynamics for the digital controller, it entirely
-circumvents the FWL problem, but potentially incurs state-space explosion
-issues.  Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same
+plants with polynomial dynamics.  The work extends to affine systems, but is
+limited by the capacity of the state-of-the-art SMT solvers for solving
+linear arithmetic.  Since this approach uses switching models instead of
+linear dynamics for the digital controller, it avoids problems related to
+finite precision problem, but potentially suffers from state-space
+explosion.  Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same
 authors use a CEGIS-based approach for synthesizing continuous-time
@@
 
-The work in~\cite{DBLP:journals/corr/AbateBCCDKK16} investigates the
-synthesis of stabilizing controllers for continuous plants described as
-transfer functions, by exploiting bit-accurate verification of
-software-implemented digital controllers~\cite{IsmailBCFF15,Bessa16}.  While
-this work also makes use of a CEGIS-based technique, the approach is
-restricted to synthesizing digital controllers for stable closed-loop
-systems described via transfer function models.  By contrast, in the current
+The work in~\cite{DBLP:journals/corr/AbateBCCDKK16} synthesizes stabilizing
+controllers for continuous plants given as transfer functions by exploiting
+bit-accurate verification of software-implemented digital
+controllers~\cite{IsmailBCFF15, Bessa16}.  While this work also uses CEGIS,
+their approach is restricted to digital controllers for stable closed-loop
+systems given as transfer function models.  By contrast, in the current
 paper we consider a state-space representation of the physical system, which
-is known to present various advantages over transfer function
-representation~\cite{Astrom08}: (i)~easy to generalize for the multivariate
-systems (i.e., with multiple inputs and outputs); (ii)~shows the
-state-to-input relationships offering an internal model of the system; and
-(iii)~allows to synthesize control systems with guarantees about the
-internal dynamics, e.g., to synthesize controllers that make the closed-loop
-system \emph{safe}.  This work focuses on the \emph{safety} of internal
-states, such property is usually overlooked in the previous cited works, but
-plays an important role in real world systems, where system variables cannot
-assume arbitrary real values.  Moreover, our work integrates an
+has known advantages over the transfer function
+representation~\cite{Astrom08}: (i)~it generalizes to multivariate systems
+(i.e., with multiple inputs and outputs); (ii)~gives the state-to-input
+relationships, offering an internal model of the system; and (iii)~allows to
+synthesize control systems with guarantees on the internal dynamics, e.g.,
+to synthesize controllers that make the closed-loop system \emph{safe}.  Our
+work focuses on the \emph{safety} of internal states, which is usually
+overlooked in the literature.  Moreover, our work integrates an
 abstraction/refinement step inside the main CEGIS loop.
@@
 The tool Pessoa~\cite{mazo2010pessoa} synthesizes correct-by-design embedded
-control software, in a Matlab toolbox.  It is based on the abstraction of a
+control software in a Matlab toolbox.  It is based on the abstraction of a
 physical system to an equivalent finite-state machine and on the computation

### 2017-01-25 cav2017/cav2017.tex

@@
 \item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
-$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] 
-\wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
-where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is the error introduced by the DAC and $q3$ is the maximum truncation and rounding error of the mathematical operation $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}.
+$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q_1}{2}\ \ \frac{q_1}{2}\right] 
+\wedge \nu_2 \in \left[-\frac{q_2}{2}\ \ \frac{q_2}{2}\right]  \wedge \nu_3 \in \left[-q_3\ \ q_3\right]  \right \}\nonumber$$
+where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is the error introduced by the DAC and $q_3$ is the maximum truncation and rounding error of the mathematical operation $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}.
 More details on how to model quantization as noise are given in the 

### 2017-01-25 cav2017/cav2017.tex
getting rid of new evolving notation

@@
 \wedge \nu_2 \in \left[-\frac{q_2}{2}\ \ \frac{q_2}{2}\right]  \wedge \nu_3 \in \left[-q_3\ \ q_3\right]  \right \}\nonumber$$
-where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is the error introduced by the DAC and $q_3$ is the maximum truncation and rounding error of the mathematical operation $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}.
+where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is the error introduced by the DAC and $q_3$ is the maximum truncation and rounding error of the mathematical operation $u_k=-K*\mathcal{F}_{\langle I_c,F_c \rangle}(x_k)$ as discussed in section \ref{sec:numeric_rep}.
 More details on how to model quantization as noise are given in the 

### 2017-01-25 cav2017/cav2017.tex
wordings

--- 2017-01-25 cav2017/cav2017.tex
@@
 The classical approach to control synthesis has often disregarded
-quantization, thus resulting in general to unsound digital controllers. 
-Modern techniques focus on different elements of discretization effects,
-including delayed response~\cite{Duggirala2015}, and Finite Word Length
-(FWL) semantics, with the goal either to verify (e.g.,~\cite{daes20161}) or
-to optimize (e.g.,~\cite{oudjida2014design}) given implementations.
+quantization, thus sacrificing soundness.  Modern techniques focus on
+different aspects of discretization, including delayed
+response~\cite{Duggirala2015} and Finite Word Length (FWL) semantics, with
+the goal either to verify (e.g.,~\cite{daes20161}) or to optimize
+(e.g.,~\cite{oudjida2014design}) given implementations.
 
@@
 
-We consider models of physical plants expressed as ordinary differential equations (ODEs), 
-which we assume to be controllable and under full state information (namely where we have access to all the model variables):  
+We consider models of physical plants expressed as ordinary differential
+equations (ODEs), which we assume to be controllable and under full state
+information (i.e., we have access to all the model variables):
 %
@@
 \end{align}
-where $t \in \mathbb R_0^+$, 
-where $A$ and $B$ are matrices that fully specify the continuous plant, 
-and with initial states set as $x(0)$. 
-Whilst we ideally would like to work on the continuous-time plant, 
-in this work Eq.~\eqref{eq:ode} is soundly discretized in time (as shown in Appendix~\ref{sec:appendix:LTIbackground}) into %\textcolor{red}{What is subscript ``d''?}
+%
+where $t \in \mathbb R_0^+$, where $A$ and $B$ are matrices that fully
+specify the continuous plant, and with initial states set as $x(0)$.  While
+we ideally would like to work on the continuous-time plant, in this work
+Eq.~\eqref{eq:ode} is soundly discretized in time (as shown in
+Appendix~\ref{sec:appendix:LTIbackground}) into
+%
+%\textcolor{red}{What is subscript ``d''?}
 %
@@
 \end{align} 
-where $k \in \mathbb N$, 
-and with initial state $x_{0}=x(0)$. $A_d$ and $B_d$ denote the matrices that describes the discretized plant dynamics and $A$ and $B$ the continuous plant dynamics. 
-Later, we will deal with the issue of variable quantization, as introduced by the ADC/DAC conversion blocks.
-
-%
+%
+where $k \in \mathbb N$ and with initial state $x_{0}=x(0)$.  $A_d$ and
+$B_d$ denote the matrices that describe the discretized plant dynamics and
+$A$ and $B$ the continuous plant dynamics.  Later, we will address the
+issue of variable quantization, as introduced by the ADC/DAC conversion
+blocks (Fig.~\ref{fig:digitalsystem}).
+
 \begin{figure*}[htb]
@@
 }
- \caption{Closed-loop digital control system. 
+ \caption{Closed-loop digital control system 
  \label{fig:digitalsystem}}
 \end{figure*}
+
 %-------------------------------
@@
 \end{align}
-The gain matrix $K$ can be set so that the closed-loop discrete dynamics are shaped as desired, 
-for instance according to a specific stability goal or around a specific dynamical behavior \cite{astrom1997computer}. 
-As argued later in this work, we will target more complex objectives, such as quantitative safety requirements that are not typical in the digital control literature. 
-Further, we will encompass the digital nature of the controller, which manipulates quantities with finite precision.
+%
+The gain matrix $K$ can be set so that the closed-loop discrete dynamics are
+shaped as desired, for instance according to a specific stability goal or
+around a specific dynamical behavior \cite{astrom1997computer}.  As argued
+later in this work, we will target more complex objectives, such as
+quantitative safety requirements, which are not typical in the digital
+control literature.  Further, we will embrace the digital nature of the
+controller, which manipulates quantities with finite precision.
 
@@
 
-Asymptotic stability implies convergence to an equilibrium point from any states in its neighborhood.
-This stability concept is stronger than the Lyapunov and BIBO stability researched by previous works~\cite{DBLP:conf/emsoft/RavanbakhshS16,DBLP:journals/corr/AbateBCCDKK16,DBLP:conf/hybrid/RouxJG15,
+Asymptotic stability implies convergence to an equilibrium point from any
+states in its neighborhood.  This stability concept is stronger than the
+Lyapunov and BIBO stability researched by previous
+works~\cite{DBLP:conf/emsoft/RavanbakhshS16,DBLP:journals/corr/AbateBCCDKK16,DBLP:conf/hybrid/RouxJG15,
 DBLP:conf/hybrid/WangGRJF16}.  In the case of linear systems as
-in~\eqref{eq:closedloopss}, the equilibrium point for zero-input 
-response is always the  origin.  Here, we consider systems with 
-a zero reference signal.
+in~\eqref{eq:closedloopss}, the equilibrium point for zero-input response is
+always the origin.  Here, we consider systems with a zero reference signal.
 
@@
 
-In this study, we are not limited to the synthesis of digital stabilizing
-controllers -- a well known task in the literature on digital control system
--- but target safety requirements with an overall approach that is sound and
-automated.  More specifically, we require that the closed-loop system
+We are not limited to the synthesis of digital stabilizing controllers -- a
+well known task in the literature on digital control system -- but target
+safety requirements with an overall approach that is sound and automated. 
+More specifically, we require that the closed-loop system
 \eqref{eq:closedloopss} meets given safety specifications.  A safety
 specification raises a requirement on the states of the model, such that the
-feedback controller (namely the choice of the gains matrix $K$) must ensure that
-the states never exit such requirement.  Note that a stable, closed-loop
-system is not necessarily a safe system: indeed, the state values may leave
-the safe space whilst they converge to the equilibrium, which is typical in
-the case of oscillatory dynamics.  However, a safe system will always be
-stable.  In~this work, the safety property represented by $\phi_\mathit{safety}$ is
-encoded as follows:
+feedback controller (namely the choice of the gains matrix $K$) must ensure
+that the states never exit such requirement.  Note that a stable,
+closed-loop system is not necessarily a safe system: indeed, the state
+values may leave the safe space whilst they converge to the equilibrium,
+which is typical in the case of oscillatory dynamics.  However, a safe
+system will always be stable.  In~this work, the safety property represented
+by $\phi_\mathit{safety}$ is encoded as follows:
 %

### 2017-01-25 cav2017/cav2017.tex
wordings

@@
 specification raises a requirement on the states of the model, such that the
-feedback controller (namely the choice of the gains matrix $K$) must ensure
+feedback controller (namely the choice of the gains matrix~$K$) must ensure
 that the states never exit such requirement.  Note that a stable,
@@
 
-The models we consider have two sources of error due to numeric representation. 
-The first is the numeric error introduced by the fixed-point numbers employed to model the plant, i.e., to represent the plant dynamics $A_d$, $B_d$ and $x_k$. 
-The second is the quantization error introduced by the digital controller, 
-which performs operations on fixed-point numbers. 
-In this section we outline the notation for the fixed-point representation of numbers, and briefly describe the errors introduced. A formal outline is in Appendix~\ref{appendix:numerical_errors}.
-
-Let $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part.
-The smallest number that can be represented in this domain is $c_m=2^{-F}$.
-Any mathematical operations performed at the precision $\mathcal{F}_{\langle I,F \rangle}(x)$ will introduce errors, that can be upper bounded~\cite{DBLP:conf/arith/BrainTRW15}.
-
-We will use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real number $x$ represented in the fixed-point precision level of the controller, and $\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$ represented in the fixed-point precision level of the plant computational model ($I_p \geq I_c \wedge F_p \geq F_c$).
-Thus any mathematical operations occurring in the digital controller will occur in the range of $\mathcal{F}_{\langle I_c,F_c \rangle}$, and all other calculations will be carried out in the range of $\mathcal{F}_{\langle I_p,F_p \rangle}$.
-The physical plant operates in the reals, which means our verification phase must account for calculation errors in the model.
+The models we consider have two sources of error due to numeric
+representation.  The first is the numeric error introduced by the
+fixed-point numbers employed to model the plant, i.e., to represent the
+plant dynamics $A_d$, $B_d$ and $x_k$.  The second is the quantization error
+introduced by the digital controller, which performs operations on
+fixed-point numbers.  In this section we outline the notation for the
+fixed-point representation of numbers, and briefly describe the errors
+introduced.  A formal discussion is in
+Appendix~\ref{appendix:numerical_errors}.
+
+Let $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$
+represented in a fixed point domain, with $I$ bits representing the integer
+part and $F$ bits representing the decimal part.  The smallest number that
+can be represented in this domain is $c_m=2^{-F}$.  Any mathematical
+operations performed at the precision $\mathcal{F}_{\langle I,F \rangle}(x)$
+will introduce errors, that can be upper
+bounded~\cite{DBLP:conf/arith/BrainTRW15}.
+
+We will use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real
+number $x$ represented in the fixed-point precision level of the controller,
+and $\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$
+represented in the fixed-point precision level of the plant computational
+model ($I_p \geq I_c \wedge F_p \geq F_c$).  Thus any mathematical
+operations occurring in the digital controller will occur in the range of
+$\mathcal{F}_{\langle I_c,F_c \rangle}$, and all other calculations will be
+carried out in the range of $\mathcal{F}_{\langle I_p,F_p \rangle}$.  The
+physical plant operates in the reals, which means our verification phase
+must account for calculation errors in the model.
 
@@
 Let us first consider the effect of the quantization errors on safety. 
-Within the controller, 
-state values are manipulated at low precision, 
+Within the controller, state values are manipulated at low precision,
 alongside the vector multiplication $Kx$.
+%
 %computed considering the error introduced by the digital controller caused by performing the vector multiplication $Kx$ at low digital precision.
@@
 
-This induces two types of the errors detailed above:  
-first, the truncation error due to representing $x_k$ as $\mathcal{F}{\langle I_c,F_c \rangle}(x_{k})$; 
-and second, the rounding error introduced by the multiplication operation. 
-We represent these errors as non-deterministic noise.
+This induces two types of the errors detailed above: first, the truncation
+error due to representing $x_k$ as $\mathcal{F}{\langle I_c,F_c
+\rangle}(x_{k})$; and second, the rounding error introduced by the
+multiplication operation.  We represent these errors as non-deterministic
+noise.
 
@@
 
-We address this last error by use of interval arithmetic~\cite{moore1966interval} in the verification phase.
+We address this last error by use of interval
+arithmetic~\cite{moore1966interval} in the verification phase.
 
@@
 zeros positions, degrading the closed-loop dynamics, causing steady-state
-errors (see the Appendix~\ref{sec:appendix:LTIbackground} for details) 
-and eventually destabilizing  the system~\cite{Bessa16}. However, since 
-in this paper we require stability only as a precursor to safety, it is 
-sufficient to check that the (perturbed, noisy) model converges to a neighborhood of the equilibrium within the safe set.
-
-In the following, we shall disregard these steady-state errors (caused by FWL effects)
- when the stability is ensured by synthesis, and then verify its safety accounting for the finite-precision errors. 
+errors (see the Appendix~\ref{sec:appendix:LTIbackground} for details) and
+eventually destabilizing the system~\cite{Bessa16}.  However, since in this
+paper we require stability only as a precursor to safety, it is sufficient
+to check that the (perturbed, noisy) model converges to a neighborhood of
+the equilibrium within the safe set.
+
+In the following, we shall disregard these steady-state errors (caused by
+FWL effects) when the stability is ensured by synthesis, and then verify its
+safety accounting for the finite-precision errors.
+
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-01-25 cav2017/cav2017.tex
wordings

@@
 operations performed at the precision $\mathcal{F}_{\langle I,F \rangle}(x)$
-will introduce errors, that can be upper
-bounded~\cite{DBLP:conf/arith/BrainTRW15}.
+will introduce errors, for which an upper bound can be
+given~\cite{DBLP:conf/arith/BrainTRW15}.
 

### 2017-01-25 cav2017/cav2017.tex
wordings

@@
 zeros positions, degrading the closed-loop dynamics, causing steady-state
-errors (see the Appendix~\ref{sec:appendix:LTIbackground} for details) and
+errors (see Appendix~\ref{sec:appendix:LTIbackground} for details) and
 eventually destabilizing the system~\cite{Bessa16}.  However, since in this
@@
 
-In this section, we describe our technique for synthesizing safe
-digital feedback controllers using CEGIS.  For this purpose, we first
-provide the synthesizer's general architecture, followed by describing
-our two approaches to synthesizing safe controllers:
-the first one is a baseline approach which relies on a naive explicit
-unwinding of the transition relation, whereas the second uses an
-abstraction to implicitly evaluate all possible progressions of the
-system simultaneously. % on an infinite time horizon.
+In this section, we describe our technique for synthesizing safe digital
+feedback controllers using CEGIS.  For this purpose, we first provide the
+synthesizer's general architecture, followed by describing our two
+approaches to synthesizing safe controllers: the first one is a baseline
+approach that relies on a naive explicit unwinding of the transition
+relation, whereas the second uses abstraction to implicitly evaluate all
+possible progressions of the system simultaneously.
+
+% on an infinite time horizon.
 
@@
 and $\sigma$ is a quantifier-free formula.  
-We interpret the ground terms over some finite domain $\mathcal{D}$.
+We interpret the ground terms over some finite domain~$\mathcal{D}$.
 %

### 2017-01-25 cav2017/cav2017.tex
wordings

@@
 
-At this point, we recap the the synthesis problem that we solve in this work:
-we seek a digital feedback controller $K$ (see Eq.~\ref{eq:controlaction})
-that makes the closed-loop plant model safe for 
-initial state $x_0$, reference signal $r_k$ and input $u_k$
-as defined in Sec.~\ref{ssec:safety}. 
-We consider non-deterministic initial states within a specified range, 
-the reference signal to be set to zero, 
-saturation on the inputs, 
-and account for digitalization and quantization errors introduced by the controller.
-
-When mapping back to the notation used for describing the general architecture of the program synthesizer, 
-the controller $K$ denotes $P$ and $(x_0, u_k)$ represents $x$. 
+At this point, we recall the the synthesis problem that we solve in this
+work: we seek a digital feedback controller $K$ (see
+Eq.~\ref{eq:controlaction}) that makes the closed-loop plant model safe for
+initial state $x_0$, reference signal $r_k$ and input $u_k$ as defined in
+Sec.~\ref{ssec:safety}.  We consider non-deterministic initial states within
+a specified range, the reference signal to be set to zero, saturation on the
+inputs, and account for digitalization and quantization errors introduced by
+the controller.
+
+When mapping back to the notation used for describing the general
+architecture of the program synthesizer, the controller $K$ denotes $P$ and
+$(x_0, u_k)$ represents $x$.
+
 %% While the controller precision \todo{update notations} $\langle I_c,F_c\rangle$ is given and fixed, 
@@
 
-The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
-One important observation is that, for this approach, we verify and synthesize 
-a controller over $k$ time steps. We then compute a completeness threshold, $\overline{k}$,
-for this controller, and verify the controller correctness to $\overline{k}$ time steps.
-Essentially, $\overline{k}$ represents the number of iterations 
-required to sufficiently unwind the closed-loop state-space system 
-such that the boundaries are not violated for any $k{>}\overline{k}$
-(i.e., it is sufficient to unwind the closed-loop state-space system up to  
-$\overline{k}$ in order to ensure that $\phi_{safety}$ holds).
+The controller synthesis is described in
+Fig.~\ref{fig:CEGIS-precision-increment}.  One important observation is
+that, for this approach, we verify and synthesize a controller over $k$ time
+steps.  We~then compute a completeness threshold, $\overline{k}$, for this
+controller, and verify the controller correctness to $\overline{k}$ time
+steps.  Essentially, $\overline{k}$ represents the number of iterations
+required to sufficiently unwind the closed-loop state-space system such that
+the boundaries are not violated for any $k{>}\overline{k}$ (i.e., it is
+sufficient to unwind the closed-loop state-space system up to $\overline{k}$
+in order to ensure that $\phi_{safety}$ holds).
 

### 2017-01-26 hscc2017/paper.tex
Nudge on the reviewers comments about uncertainty

@@
 introduced by quantizations in sampling and holding process, i.e., ADC and
-DAC conversions.  Assuming linearity and independence between these sources,
-the uncertain model may be rewritten as a vector of coefficients in the
-z-domain using equations (\ref{eq:coefficients}) and
-(\ref{eq:delta_coefficients})
+DAC conversions.  These sources are assumed to be non-deterministic, 
+which poses no further restriction to our model, thus, the uncertain model
+may be rewritten as a vector of coefficients in the z-domain using equations
+(\ref{eq:coefficients}) and (\ref{eq:delta_coefficients})
 %
@@
 analysis is based on polynomial coefficients and not over signals.
+
+The parametric uncertainties in the plant are assumed to have the same
+order as the plant model, since tolerances of higher order would invalidate
+feedback model (even tiny errors of higher order can move the poles by a
+large amount preventing any single controller from stabilizing such a collection).
+This is a reasonable assumption since most tolerances do not change the 
+architecture of the plant, and models subject to such effects are simply
+inadequate as a proposed solution.
 

### 2017-01-28 hscc2017/paper.tex
copyright
wording

--- 2017-01-11 hscc2017/paper.tex
@@
 analysis is based on polynomial coefficients and not over signals.
+
+The parametric uncertainties in the plant are assumed to have the same
+order as the plant model, since tolerances of higher order would invalidate
+feedback model (even tiny errors of higher order can move the poles by a
+large amount preventing any single controller from stabilizing such a setup).
+This is a reasonable assumption since most tolerances do not change the 
+architecture of the plant, and models subject to such effects are
+inadequate.
 

### 2017-01-28 hscc2017/paper.tex
wording

@@
 
-Let $\hat{C}(z)$ be the digital controller transfer function
-represented using this FWL with integer size $I$ and fractional size~$F$;
-$I$ affects the representation range and is set to avoid overflows, 
-while $F$ affects the precision and the truncation process after the 
-arithmetic operations. These variables are chosen depending on 
-hardware features.  In general-purpose processors and
-DSP's, $I$ is minimized to avoid overflows and $F$ is employed for the
-remaining bit representation. Other flexible hardware structures
-(e.g., FPGAs) allow the design of $F$ and $I$, which affects directly
-the number of logical gates.
-
-We shall denote the FWL domain of coefficients as $\mathbb{R}\langle I,F
+Let $\hat{C}(z)$ be the digital controller transfer function represented
+using this FWL with integer size $I$ and fractional size~$F$; $I$ affects
+the range of the representation and is set to avoid overflows, while $F$
+affects the precision and the truncation after arithmetic operations.
+We shall denote the FWL domain of the coefficients by $\mathbb{R}\langle I,F
 \rangle$

### 2017-01-28 hscc2017/paper.tex
dots

@@
         \includegraphics[width=\textwidth]{figures/runningexample_bd0.pdf}
-        \caption{Original controller~\cite{DBLP:conf/hybrid/WangGRJF16}.}
+        \caption{Original controller~\cite{DBLP:conf/hybrid/WangGRJF16}}
         \label{fig:original}
@@
     \end{subfigure}
-    \caption{Bode diagram for original~\cite{DBLP:conf/hybrid/WangGRJF16} and synthesized closed-loop systems.}\label{fig:bode}
+    \caption{Bode diagram for original~\cite{DBLP:conf/hybrid/WangGRJF16} and synthesized closed-loop systems}\label{fig:bode}
 \end{figure}

### 2017-01-28 hscc2017/paper.tex
dots
nudge number

@@
   benchmarks taken from the literature: the median runtime for our benchmark
-  set is $197$s, i.e., half of the controllers can be synthesized in less
+  set is $197$\,s, i.e., half of the controllers can be synthesized in less
   than five minutes.
@@
         \includegraphics[width=\textwidth]{figures/runningexample_bd2.pdf}
-        \caption{Controller synthesized by \tool.}
+        \caption{Controller synthesized by \tool}
         \label{fig:cegiscontroller}

### 2017-01-28 cav2017/cav2017.tex
edits appendix

@@
 
-The work in~\cite{DBLP:journals/corr/AbateBCCDKK16} synthesizes stabilizing
+The work in~\cite{hscc-paper} synthesizes stabilizing
 controllers for continuous plants given as transfer functions by exploiting
@@
 %-------------------------------
-\subsection{Stability of closed-loop systems}
+\subsection{Stability of Closed-loop Systems}
 \label{ssec:stability}
@@
 Lyapunov and BIBO stability researched by previous
-works~\cite{DBLP:conf/emsoft/RavanbakhshS16,DBLP:journals/corr/AbateBCCDKK16,DBLP:conf/hybrid/RouxJG15,
-DBLP:conf/hybrid/WangGRJF16}.  In the case of linear systems as
-in~\eqref{eq:closedloopss}, the equilibrium point for zero-input response is
-always the origin.  Here, we consider systems with a zero reference signal.
-
-A discrete-time LTI system as \eqref{eq:closedloopss} is asymptotically stable
-\textit{iff} all the roots of the characteristic polynomial (i.e., the
-eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
-circle in the complex plane, i.e., \textit{iff} their absolute values are
-less than one~\cite{astrom1997computer}.  In this paper, we express the
+work~\cite{DBLP:conf/emsoft/RavanbakhshS16, hscc-paper,
+DBLP:conf/hybrid/RouxJG15, DBLP:conf/hybrid/WangGRJF16}.  In the case of
+linear systems as in~\eqref{eq:closedloopss}, the equilibrium point for
+zero-input response is always the origin.  Here, we consider systems with a
+zero reference signal.
+
+A discrete-time LTI system as \eqref{eq:closedloopss} is asymptotically
+stable \textit{iff} all the roots of the characteristic polynomial (i.e.,
+the eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the
+unity circle in the complex plane, i.e., \textit{iff} their absolute values
+are less than one~\cite{astrom1997computer}.  In this paper, we express the
 stability specification $\phi_{stability}$ in terms of a check known as
@@
 
-Jury's criterion provides necessary and sufficient conditions for the eigenvalues 
-to be within the unit circle and, consequently, for the system is stable.  
-It is a known stability test from the control system literature~\cite{fadali}.  
-Given a 
-polynomial $P(z)$ of the form
+Jury's criterion provides necessary and sufficient conditions for the
+eigenvalues to be within the unit circle and, consequently, for the system
+is stable~\cite{fadali}.  Given a polynomial $P(z)$ of the form
+%
 $$
@@
 $$
-Jury's criterion explores solely the coefficients ($a_{0},a_{1},...,a_{N-1}$) 
-of $P(z)$ for checking stability, which we encompass as property $\phi_{stability}$, as detailed below.
-
-This study limits itself to explain the encoding of Jury's criterion for formal synthesis.  
-For the stability  test procedure, the following matrix 
-$M=[m_{ij}]_{(2N-2)\times N}$ is built  from $P(z)$ coefficients:
+%
+Jury's criterion explores solely the coefficients
+$a_{0},a_{1},\ldots,a_{N-1}$ of $P(z)$ for checking stability, which we
+capture as property $\phi_{stability}$, as detailed below.
+
+This study limits itself to explain the encoding of Jury's criterion for
+formal synthesis.  For the stability test procedure, the following matrix
+$M=[m_{ij}]_{(2N-2)\times N}$ is built from the coefficients of $P(z)$:
+%
 $$
@@
 \end{itemize}
-In conclusion, the stability property $\phi_{stability}$ is encoded as the following formula:
+%
+The stability property $\phi_\mathit{stability}$ is encoded as the following formula:
 $$
-\phi_{stability}\iff \ (R_{1} \wedge R_{2} \wedge R_{3} \wedge R_{4}).
+\phi_\mathit{stability}\iff \ (R_{1} \wedge R_{2} \wedge R_{3} \wedge R_{4}).
 $$
@@
 %-------------------------------
-\subsection{Stability of closed-loop systems with fixed-point controller error}
-%-------------------------------
-
-The proof above relies on the fact that the relationship between states and next states is defined by
-$x_{k+1} = (A_d  - B_dK)*x_k$, all computed at infinite precision. In fact, when we employ a FWL digital controller, 
-the operation becomes:
+\subsection{Stability of Closed-loop Systems with Fixed-point Controller Error}
+%-------------------------------
+
+The proof above relies on the fact that the relationship between states and
+next states is defined by $x_{k+1} = (A_d - B_dK) \cdot x_k$, all computed
+at infinite precision.  When we employ a FWL digital controller, the
+operation becomes:
+%
 \begin{align*}
-x_{k+1} &= A_d * x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
-x_{k+1} &= (A_d  - B_dK)*x_k + B_dK\delta
+x_{k+1} &= A_d \cdot x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
+x_{k+1} &= (A_d  - B_dK) \cdot x_k + B_dK\delta
 %\\ x_{k+1}&=A_d x_{k} + B_du_{k}
 \end{align*}
-where $\delta$ is the maximum error that can be introduced by the FWL controller in one step, i.e., by reading the states values once and multiplying by $K$ once. 
-We derive the closed form expression for $x_n$ as follows: 
+%
+where $\delta$ is the maximum error that can be introduced by the FWL
+controller in one step, i.e., by reading the states values once and
+multiplying by $K$ once.  We derive the closed form expression for $x_n$ as
+follows:
+%
 \begin{align*}
@@
 
-The definition of asymptotic stability is that the system converges to a reference signal, in this case we use no
-reference signal so an asymptotically stable system will converge to the origin. We know that the original system
-with an infinite-precision controller is stable, because we have synthesized it to meet Jury's criterion. Hence, 
-$(A_d  - B_dK)^n*x_0$ must converge to zero.
-
-To show that a fixed-point implementation of the same controller will converge to a finite value, 
-we need to show that the infinite sum converges.
-A known result is that a power series of matrices converges~\cite{horn1990matrix}, iff the eigenvalues of the matrix are less than 1, as follows:
+The definition of asymptotic stability is that the system converges to a
+reference signal, in this case we use no reference signal so an
+asymptotically stable system will converge to the origin.  We know that the
+original system with an infinite-precision controller is stable, because we
+have synthesized it to meet Jury's criterion.  Hence, $(A_d - B_dK)^n \cdot
+x_0$ must converge to zero.
+
+To show that a fixed-point implementation of the same controller will
+converge to a finite value, we need to show that the infinite sum converges. 
+A known result is that a power series of matrices
+converges~\cite{horn1990matrix}, iff the eigenvalues of the matrix are less
+than~1, as follows:
+%
 %\begin{align*}
@@
 %\end{align*}
+%
 where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge to the value 
+%
 \begin{align*}
@@
 \end{align*}
-As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the safe space, then the synthesized fixed-point controller results in a safe closed-loop model. 
-The convergence to a finite value, however, will not make it asymptomatically stable.
+%
+As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the
+safe space, then the synthesized fixed-point controller results in a safe
+closed-loop model.  The convergence to a finite value, however, will not
+make it asymptomatically stable.
 
@@
 So $\delta_T$ is the truncation error and it will propagate across operations.
-\item {\bf Rounding:}
-The following errors appear in basic operations.
-Let $c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be the truncation errors caused by representing $c_1$ and $c_2$ in the fixed-point domain as above.
+%
+\item {\bf Rounding:} The following errors appear in basic operations.  Let
+$c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be
+the truncation errors caused by representing $c_1$ and $c_2$ in the
+fixed-point domain as above.
+%
 \begin{enumerate}
-\item Addition/Subtraction: these operations only propagate errors coming from truncation of the operands, namely 
-$\mathcal{F}_{\langle I,F \rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3$ with $|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
-\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) * \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3| \leq |\delta_{T1}*\mathcal{F}_{\langle I,F \rangle}(c_2)| + |\delta_{T2}*\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where $c_m=2^{-F}$ as above.
-\item Division: the operations performed by our controllers in the FWL domain do not include division.
-However, we do use division in computations at the precision of the plant.
-Here the error depends on whether the divisor is greater or smaller than the dividend.
-$\mathcal{F}_{\langle I,F \rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_{T3}$ where $\delta_{T3}$ is $(\delta_{T2}*c_1 - \delta_{T1}*c_2)/(\delta_{T2}^2 - \delta_{T2} c_2)$,
+%
+\item Addition/Subtraction: these operations only propagate errors coming
+from truncation of the operands, namely $\mathcal{F}_{\langle I,F
+\rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3$
+with $|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
+%
+\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) \cdot
+\mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3|
+\leq |\delta_{T1}\cdot\mathcal{F}_{\langle I,F \rangle}(c_2)| +
+|\delta_{T2}\cdot\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where
+$c_m=2^{-F}$ as above.
+%
+\item Division: the operations performed by our controllers in the FWL
+domain do not include division.  However, we do use division in computations
+at the precision of the plant.  Here the error depends on whether the
+divisor is greater or smaller than the dividend.  $\mathcal{F}_{\langle I,F
+\rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_{T3}$
+where $\delta_{T3}$ is $(\delta_{T2}\cdot c_1 - \delta_{T1}\cdot
+c_2)/(\delta_{T2}^2 - \delta_{T2} c_2)$,
+%
 %$\mathcal{F}_{\langle I,F \rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) =  (c_1 - \delta_{T1})/ (c_2 + \delta_{T2}) + c_m $, where $c_m=2^{-F}$ as above.

### 2017-01-28 cav2017/cav2017.tex
math mode table 2
caption table 2
edit appendix

@@
 
-We will assume, for the purposes of this analysis, that the domain of the ADC is that of the digital controller (i.e, the quantizer includes any digital gain added in the code).
-The process of quantization in the DAC is similar except that it is calculating $\mathcal{F}\langle I_{dac},F_{dac} \rangle (\mathcal{F}\langle I_{c},F_{c} \rangle (x)) $.
-If these domains are the same ($I_{c}=I_{dac},F_{c}=F_{dac}$), or if the DAC resolution in higher than the ADCs, then the DAC quantization error is equal to zero.
-From the above equations we can now define the ADC and DAC quantization noises, ${\nu_1}_k \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}], {\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}]$ where $q_1=q_{c} \wedge q_2=q_{dac}$.
-Note that this is shown in fig.
-\ref{ssec:statefeedbackcontrol} where $Q_1$ is the quantizer of the ADC and $Q_2$ the quantizer for the DAC.
-These bounds hold irrespective of whether the noise is correlated, hence we may use them to over-approximate the effect of the noise on the state space progression over time.
-The resulting dynamics are:
+We will assume, for the purposes of this analysis, that the domain of the
+ADC is that of the digital controller (i.e, the quantizer includes any
+digital gain added in the code).  The process of quantization in the DAC is
+similar except that it is calculating $\mathcal{F}\langle I_{dac},F_{dac}
+\rangle (\mathcal{F}\langle I_{c},F_{c} \rangle (x)) $.  If these domains
+are the same ($I_{c}=I_{dac},\allowbreak F_{c}=F_{dac}$), or if the DAC
+resolution in higher than the ADCs, then the DAC quantization error is equal
+to zero.  From the above equations we can now define the ADC and DAC
+quantization noises ${\nu_1}_k \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}]$ and
+${\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}]$ where $q_1=q_{c} \wedge
+q_2=q_\mathit{dac}$.  This is illustrated in
+Fig.~\ref{ssec:statefeedbackcontrol} where $Q_1$ is the quantizer of the ADC
+and $Q_2$ the quantizer for the DAC.  These bounds hold irrespective of
+whether the noise is correlated, hence we may use them to over-approximate
+the effect of the noise on the state space progression over time.  The
+resulting dynamics are:
+%
 \begin{align}
@@
 \footnotesize
-\caption{Benchmarks for State-Space Physical Plants.}
-\label{table:State-space-benchmarks}
 \begin{tabular}{|c|c|c|c|c|}
@@
 %7              & 
-\begin{tabular}[c]{@{}c@{}}Automotive\\ Cruise\\ System\end{tabular} & -0.05 & 0.03125 & 0.032 & 0 \\ \hline
+\begin{tabular}[c]{@{}c@{}}Automotive\\ Cruise\\ System\end{tabular} & $-0.05$ & $0.03125$ & $0.032$ & $0$ \\ \hline
 %8              & 
@@
 \end{tabular}
+\caption{Benchmarks for State-Space Physical Plants}
+\label{table:State-space-benchmarks}
 \end{table}

### 2017-01-28 cav2017/cav2017.tex
edit appendix

@@
 
-During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed by $\mathcal{F}\langle I_{c},F_{c} \rangle (x)$ (assuming the ADC discretization is the same as the digital implementation).
-This sampling uses a threshold which is defined by the less significant bit ($q_{c}=2^{-F_c}$) of the ADC and some non-linearities of the circuitry.
-The overall conversion is
-$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right]$$
-If we denote the error in the conversion as $\nu_k=y_k-y(t)$ where $t = nk$, and $n$ is the sampling time and $k$ the number of steps, then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
+During any given ADC conversion, the continuous signal will be sampled in
+the real domain and transformed by $\mathcal{F}\langle I_{c},F_{c} \rangle
+(x)$ (assuming the ADC discretization is the same as the digital
+implementation).  This sampling uses a threshold which is defined by the
+less significant bit ($q_{c}=2^{-F_c}$) of the ADC and some non-linearities
+of the circuitry.  The overall conversion is
+%
+$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k :
+y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right] \,.$$
+%
+If we denote the error in the conversion by $\nu_k=y_k-y(t)$ where $t = nk$,
+and $n$ is the sampling time and $k$ the number of steps, then we may define
+some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
 
@@
 the effect of the noise on the state space progression over time.  The
-resulting dynamics are:
+resulting dynamics are
 %
@@
 \label{eq:pre_quantization}
-{x}_{k+1} &= {A}_d{x}_k+{B}_d({u}_k+{{\nu}_2}_k),\\
-u_k&=-K{x}_{k}+{{\nu}_1}_k. 
+{x}_{k+1} &= {A}_d{x}_k+{B}_d({u}_k+{{\nu}_2}_k)\\
+u_k&=-K{x}_{k}+{{\nu}_1}_k \,,
 \end{align}
-
-which give the closed loop dynamics:
+%
+which result in the following closed loop dynamics:
+%
 \begin{align}
 \label{eq:quantization}
-{x}_{k+1} &= ({A}_d-{B}_d{K}_d) {x}_k+{B}_d{{\nu}_2}_k +{{\nu}_1}_k. 
+{x}_{k+1} &= ({A}_d-{B}_d{K}_d) {x}_k+{B}_d{{\nu}_2}_k +{{\nu}_1}_k \,. 
 \end{align}

### 2017-01-28 cav2017/cav2017.tex
edit appendix

@@
 \begin{align*}
-0 + (I - A_d + B_dK)^{-1}B_dk\delta. 
+0 + (I - A_d + B_dK)^{-1}B_dk\delta \,. 
 \end{align*}
@@
 
-A dynamical system is a system in which a function describes the progression of a state over time. 
-In a continuous domain with linear dynamics, it is described by a first order Ordinary Differential Equation (ODE).
+A dynamical system is a system in which a function describes the progression
+of a state over time.  In a continuous domain with linear dynamics, it is
+described by a first-order Ordinary Differential Equation (ODE).
+%
 \begin{equation}
-\dot{x}(t)=Ax(t)+Bu(t).
+\dot{x}(t)=Ax(t)+Bu(t) \,.
 \label{eq:dynamical}
@@
 
-Discretization of an continuous dynamical system turns the ODE into a difference equation, assuming zero-order hold
-for the input $u$, 
+Discretization of an continuous dynamical system turns the ODE into a
+difference equation, assuming zero-order hold for the input $u$,
+%
 %and continuous integration for the noise $\vec{w}$, 
@@
 \label{eq:discretization}
-x_{k+1} &= A_d x_k+B_d u_k,
+x_{k+1} &= A_d x_k+B_d u_k \,,
 %\\y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k. 
@@
 \label{eq:discretize}
-A_d &= e^{A T_s} = \mathcal{L}^{-1} { ( s I - A )^{-1} }_{t = T_s},\\
-B_d &= \int_{0}^{T_s} e^{A t} dt\ B = A^{-1} ( A_d - I ) B,
+A_d &= e^{A T_s} = \mathcal{L}^{-1} { ( s I - A )^{-1} }_{t = T_s}\\
+B_d &= \int_{0}^{T_s} e^{A t} dt\ B = A^{-1} ( A_d - I ) B \,,
 %\\
@@
 \end{align}
+%
 and $T_s$ is the sample time. Then
@@
 % corresponding to the poles of $G(s)$ are similarly related.
-$\hat{\lambda}_i=e^{-\lambda_iT_s}$, where $\hat{\lambda}_i \in \sigma(A_d) \wedge \lambda_i \in \sigma(A)$
-where $\sigma(\cdot)$ is the spectrum of a matrix.
+%
+$\hat{\lambda}_i=e^{-\lambda_iT_s}$, where $\hat{\lambda}_i \in \sigma(A_d)
+\wedge \lambda_i \in \sigma(A)$ where $\sigma(\cdot)$ is the spectrum of a
+matrix.
 
@@
 \mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3|
-\leq |\delta_{T1}\cdot\mathcal{F}_{\langle I,F \rangle}(c_2)| +
+\leq |\delta_{T1}\cdot\mathcal{F}_{\langle I,F \rangle}(c_2)|\allowbreak +
 |\delta_{T2}\cdot\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where

### 2017-01-28 cav2017/cav2017.tex
edits Sec 4

@@
 %-------------------------------
-\subsection{Description of the benchmarks}
+\subsection{Description of the Benchmarks}
 \label{experimental-setup}
@@
 
-A set of state-space models for different classes of 
-systems were extracted from the 
-literature~\cite{Franklin15,maglev,converters,CTMS} 
-and employed for validating our methodology.
+A set of state-space models for different classes of systems was extracted
+from the literature~\cite{Franklin15, maglev, converters, CTMS} and employed
+for validating our methodology.
 
 \textit{DC Motor Rate} plants describes the angular velocity of a DC Motor, respectively. 
-\textit{Automotive Cruise System} plant represents the speed of a motor vehicle. 
-\textit{Helicopter Longitudinal Motion} plant provides the longitudinal motion model 
+The \textit{Automotive Cruise System} plant represents the speed of a motor vehicle. 
+The \textit{Helicopter Longitudinal Motion} plant provides the longitudinal motion model 
 of a helicopter. 
-\textit{Inverted Pendulum} plant describes a pendulum model
+The \textit{Inverted Pendulum} plant describes a pendulum model
 with its center of mass above its pivot point. 
-\textit{Magnetic Suspension} plant provides a physical model for which 
+The \textit{Magnetic Suspension} plant provides a physical model for which 
 a given object is suspended via magnetic field. 
-\textit{Magnetized Pointer} plant describes a physical model employed in analogue gauges 
+The \textit{Magnetized Pointer} plant describes a physical model employed in analogue gauges 
 and indicators that is rotated through interaction with magnetic fields.
-\textit{1/4 Car Suspension} plant presents a physical model that connects a car to its wheels 
+The \textit{1/4 Car Suspension} plant presents a physical model that connects a car to its wheels 
 and allows relative motion between both parts.
-\textit{Computer Tape Driver} plant describes a system to read and write data 
+The \textit{Computer Tape Driver} plant describes a system to read and write data 
 on a storage device in the computer.
 
-Section~\ref{sec:BenchmarksforStateSpace} in the appendix summarizes 
-all our benchmarks, which are SISO models (cf. section~\ref{sec:preliminaries}). 
-The Inverted Pendulum appears to be a two output system, but it was treated as two 
-SISO systems during the experiments. For the sake of simplicity all the states 
-measurements are assumed available. In practice, state estimators should be designed 
-in order to obtain an estimate of the states from the single output. 
-Further work can include 
-state observers synthesis.
+Section~\ref{sec:BenchmarksforStateSpace} in the appendix summarizes all our
+benchmarks, which are SISO models (Section~\ref{sec:preliminaries}).  The
+Inverted Pendulum appears to be a two output system, but it was treated as
+two SISO systems during the experiments.  For the sake of simplicity all the
+state measurements are assumed available.  In practice, state estimators
+should be designed in order to obtain an estimate of the states from the
+single output.  Further work can include state observers synthesis.
 
@@
 $\overline{x_{i}}=1$ and the inputs $u_{k}=0, \forall k>0$.
-We have conducted the experimental evaluation on a 12-core 2.40\,GHz
-Intel Xeon E5-2440 with 96\,GB of RAM and Linux OS. We used the Linux \emph{times} command
-to measure CPU time used for each benchmark. The experimental runtime was limited to
-one hour per benchmark.
-%
+We have conducted the experimental evaluation on a 12-core 2.40\,GHz Intel
+Xeon E5-2440 with 96\,GB of RAM and Linux OS.  We used the Linux
+\emph{times} command to measure CPU time used for each benchmark.  The
+runtime was limited to one hour per benchmark.
 
@@
 We give the run-times required to synthesize a stable controller for each
-benchmark in Table~\ref{tab:results}.  
-Here \textit{Benchmark} is the name of the respective
-benchmark, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used
-to model the plant, while \textit{Time}
-is the total time (in milliseconds) required to synthesize a stable controller
-for the given plant, for CEGIS with multi-staged verification as well as
-abstraction-based CEGIS. The precision for the controller,
-$\mathcal{F}_{\langle I_c,F_c \rangle}$, is always chosen to be $I_c = 8, F_c = 8$.
-
-For the majority of our benchmarks, the conjecture stands that the abstraction-based back-end
-is faster than the basic multi-staged verification approach. However, it does fail to
-find solutions to 3 benchmarks, as compared to 2 with the multi-staged back-end, where
-the numbers given in the discretization matrices are too small. In direct comparison, the
-abstraction-based approach is on average able to find a solution in approximately 35\% of
-the time required using the multi-staged back-end, and has a median run-time 1.15\,s, which is
-seven times smaller than the multi-staged approach. The two back-ends complement each other
-in benchmark coverage and together solve all benchmarks in the set.
+benchmark in Table~\ref{tab:results}.  Here \textit{Benchmark} is the name
+of the respective benchmark, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the
+fixed-point precision used to model the plant, while \textit{Time} is the
+total time required to synthesize a stable controller for the given plant,
+for CEGIS with multi-staged verification as well as abstraction-based CEGIS. 
+The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$,
+is always chosen to be $I_c = 8, F_c = 8$.
+
+For the majority of our benchmarks, we observe that the abstraction-based
+back-end is faster than the basic multi-staged verification approach. 
+However, it fails to find solutions to three benchmarks, as compared to two
+with the multi-staged back-end, where the numbers given in the
+discretization matrices are too small.  In direct comparison, the
+abstraction-based approach is on average able to find a solution in
+approximately 35\% of the time required using the multi-staged back-end, and
+has a median run-time 1.15\,s, which is seven times smaller than the
+multi-staged approach.  The two back-ends complement each other in benchmark
+coverage and together solve all benchmarks in the set.
 
@@
 \begin{tabular}{| c | l | c | r | c | r |}
+%
 \hline
@@
    &                                  & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
-1  & Cruise Control      & 8,16   & 6875   & 16,16  & 241    \\
-2  & DC Motor            & 8,16   & 8103   & 20,20  & 5376   \\
+1  & Cruise Control      & 8,16   & 6.88\,s & 16,16  & 241    \\
+2  & DC Motor            & 8,16   & 8.10\,s & 20,20  & 5376   \\
 3  & Helicopter          & \xmark & \xmark  & 16,16  & 2120   \\
-4  & Inverted Pendulum   & 8,16   & 7813   & 16,16  & 387    \\
+4  & Inverted Pendulum   & 8,16   & 7.81\,s & 16,16  & 387    \\
 5  & Magnetic Pointer    & \xmark & \xmark  & 28,28  & 132845 \\
-6  & Magnetic Suspension & 12,20  & 8727   & 32,32  & 7854   \\
-7  & Pendulum            & 8,16   & 9008   & 20,20  & 1150   \\
-8  & Suspension          & 12,20  & 49410  & \xmark & \xmark \\
-9  & Tape Driver         & 8,16   & 9177   & \xmark & \xmark \\
-10 & Satellite           & 8,16   & 8975   & \xmark & \xmark \\\hline
-
+6  & Magnetic Suspension & 12,20  & 8.73\,s & 32,32  & 7854   \\
+7  & Pendulum            & 8,16   & 9.01\,s & 20,20  & 1150   \\
+8  & Suspension          & 12,20  &49.41\,s & \xmark & \xmark \\
+9  & Tape Driver         & 8,16   & 9.18\,s & \xmark & \xmark \\
+10 & Satellite           & 8,16   & 8.98\,s & \xmark & \xmark \\\hline
+%
 \end{tabular}
-\caption{Experimental results with runtime in milliseconds. \label{tab:results}}
+\caption{Experimental results\label{tab:results}}
 \end{table}
 
-The median run-time for our benchmark set is 7.9\,s.  Overall,
-the average synthesis time amounts to approximately 17.2\,s.  We
-consider these times short enough to be of practical use to control
-engineers, and thus affirm RQ1.
-
-There are several cases for which the system
-may fail to find a controller. For the naive approach, 
-the completeness threshold may be too large, thus causing a
-timeout.  On the other hand, the abstraction-based approach may
-require a very precise abstraction, resulting in too many refinements
-and, consequently, a timeout.  Yet another source of incompleteness is the inability
-of the {\sc synthesize} phase to use a large enough precision for the
-plant model in a given problem.
+The median run-time for our benchmark set is 7.9\,s.  Overall, the average
+synthesis time amounts to approximately 17.2\,s.  We consider these times
+short enough to be of practical use to control engineers, and thus affirm
+RQ1.
+
+There are several cases for which the system may fail to find a controller. 
+For the naive approach, the completeness threshold may be too large, thus
+causing a timeout.  On the other hand, the abstraction-based approach may
+require a very precise abstraction, resulting in too many refinements and,
+consequently, a timeout.  Yet another source of incompleteness is the
+inability of the {\sc synthesize} phase to use a large enough precision for
+the plant model in a given problem.
 
@@
 %-------------------------------
-\textit{Benchmark selection:} We report an assessment of both our approaches over a diverse set of real-world benchmarks.
-Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalize to other benchmarks.\\
-%
-\textit{Plant precision and discretization heuristic:} Our algorithm to select suitable FWL word widths to model the plant behavior employs a heuristic based on user-provided controller word-width specifications.
-For the first approach, where we may need to increase the precision of the time discretization, we select the time steps for the discretizations on a similar basis.
-This works sufficiently well for our benchmarks, but performance may suffer in some cases, for example if the completeness threshold is high.\\
-%
-\textit{Abstraction on other properties:} The performance gain from abstract acceleration may not hold for more complex properties than safety, for instance ``eventually always reaches a certain safe set''.
+
+\textit{Benchmark selection:} We report an assessment of both our approaches
+over a diverse set of real-world benchmarks.  Nevertheless, this set of
+benchmarks is limited within the scope of this paper and the performance may
+not generalize to other benchmarks.\\
+%
+\textit{Plant precision and discretization heuristic:} Our algorithm to
+select suitable FWL word widths to model the plant behavior employs a
+heuristic based on user-provided controller word-width specifications.  For
+the first approach, where we may need to increase the precision of the time
+discretization, we select the time steps for the discretizations on a
+similar basis.  This works sufficiently well for our benchmarks, but
+performance may suffer in some cases, for example if the completeness
+threshold is high.\\
+%
+\textit{Abstraction on other properties:} The performance gain from abstract
+acceleration may not hold for more complex properties than safety, for
+instance ``eventually always reaches a certain safe set''.
 

### 2017-01-28 cav2017/cav2017.tex
edits Sec 5

@@
 
-%% %-------------------------------
-%% \section{Related Work}
-%% \label{sec:rw}
-%% %-------------------------------
-
-%-------------------------------
-\section{Conclusions}
-%-------------------------------
-
-We have presented two automated approaches to synthesize digital state-feedback controllers 
-that ensure both stability and safety over the state-space representation.
-The first approach relies on explicit unfolding of the closed-loop model dynamics 
-up to a completeness threshold, whilst the second one applies abstraction 
-refinement and acceleration to increase speed whilst retaining soundness.
-%
-Both approaches are novel within the control literature: they put 
-forward a fully automated synthesis approach that is algorithmically and
-numerically sound, considering various error sources in the implementation 
-of the digital control algorithm and in the computational modeling of plant dynamics. 
-%
-Our experimental results show that both approaches are able
-to synthesize stable controllers in most benchmarks within a reasonable
-amount of time fully automatically.  In particular, both approaches
-complement each other and together solve all benchmarks , which have been derived from the control literature.
-
-Future work will focus the extension of these approaches to the continuous time case, 
-to models with output-based control architectures (hinging on the use of observers), 
-and to considering performance requirements (alongside safety) in the synthesis of digital controllers.
+%-------------------------------
+\section{Conclusion}
+%-------------------------------
+
+We have presented two automated approaches to synthesize digital
+state-feedback controllers that ensure both stability and safety over the
+state-space representation.  The first approach relies on explicit unfolding
+of the closed-loop model dynamics up to a completeness threshold, whilst the
+second one applies abstraction refinement and acceleration to increase speed
+whilst retaining soundness.
+%
+Both approaches are novel within the control literature: they give a fully
+automated synthesis method that is algorithmically and numerically sound,
+considering various error sources in the implementation of the digital
+control algorithm and in the computational modeling of plant dynamics.
+%
+Our experimental results show that both approaches are able to synthesize
+stable controllers for most benchmarks within a reasonable amount of time
+fully automatically.  In particular, both approaches complement each other
+and together solve all benchmarks, which have been derived from the control
+literature.
+
+Future work will focus the extension of these approaches to the
+continuous-time case, to models with output-based control architectures
+(hinging on the use of observers), and to considering performance
+requirements (alongside safety) in the synthesis of digital controllers.
 

### 2017-01-28 cav2017/cav2017.tex
edits Sec. 3

@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Naive approach: CEGIS with multi-staged verification}
+\subsection{Naive Approach: CEGIS with Multi-staged Verification}
 \label{sec:CEGIS-precision-incrementation}
@@
 
-The controller synthesis is described in
+An overview of the controller synthesis is given in
 Fig.~\ref{fig:CEGIS-precision-increment}.  One important observation is
@@
 steps.  We~then compute a completeness threshold, $\overline{k}$, for this
-controller, and verify the controller correctness to $\overline{k}$ time
-steps.  Essentially, $\overline{k}$ represents the number of iterations
-required to sufficiently unwind the closed-loop state-space system such that
-the boundaries are not violated for any $k{>}\overline{k}$ (i.e., it is
+controller, and verify correctness for $\overline{k}$ time steps. 
+Essentially, $\overline{k}$ is the number of iterations required to
+sufficiently unwind the closed-loop state-space system such that the
+boundaries are not violated for any $k{>}\overline{k}$ (i.e., it is
 sufficient to unwind the closed-loop state-space system up to $\overline{k}$
-in order to ensure that $\phi_{safety}$ holds).
+in order to ensure that $\phi_\mathit{safety}$ holds).
 
@@
 Next, we describe the different phases in Fig.~\ref{fig:CEGIS-precision-increment}
-(blocks 1 to 4):
+(blocks 1 to 4) in detail.
 
@@
 \begin{enumerate}
+
 \item The inductive synthesis phase (i.e., {\sc synthesize}) uses BMC to
-compute a candidate solution $K$
-that satisfies both the stability criteria detailed in 
-Sec.~\ref{ssec:stability} and the safety specification in Sec.~\ref{ssec:safety}.
-To synthesize a controller that satisfies the stability criteria, we require that
-a computed characteristic polynomial satisfies Jury's criteria. The details of this
-calculation can be found in the Appendix.
+compute a candidate solution $K$ that satisfies both the stability criteria
+(Sec.~\ref{ssec:stability}) and the safety specification
+(Sec.~\ref{ssec:safety}).  To synthesize a controller that satisfies the
+stability criteria, we require that a computed characteristic polynomial
+satisfies Jury's criteria.  The details of this calculation can be found in
+the Appendix.
 
  %\todo{unclear next: it seems like to select a single initial state here, rather than considering the set thereof - clarify. also, clarify relationship btw k and soundness. }
-Regarding the second requirement, we synthesize a safe controller by unwinding the transition system
-$k$ steps and by picking a controller $K$ and a single initial state,  such that the states at each step do
-not violate the safety criteria.
-That is, we ask the bounded model checker if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states.
-This is sound if the current $k$ is below the
-completeness threshold, which we assume to be true in the {\sc synthesize} phase.
-We also assume some
-precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  The
-checks that all these assumptions are sound are performed by subsequent
-{\sc verify} stages.
+
+Regarding the second requirement, we synthesize a safe controller by
+unwinding the transition system $k$ steps and by picking a controller $K$
+and a single initial state, such that the states at each step do not violate
+the safety criteria.  That is, we ask the bounded model checker if there
+exists a $K$ that is safe for at least one $x_0$ in our set of all possible
+initial states.  This is sound if the current $k$ is below the completeness
+threshold, which we assume to be true in the {\sc synthesize} phase.  We
+also assume some precision $\langle I_p,F_p\rangle$ for the plant and a
+sampling rate.  The checks that these assumptions hold are performed by
+subsequent {\sc verify} stages.
 
@@
 \begin{algorithmic}[1]
-\Function{$safetyCheck()$}{}
+\Function{$\mathit{safetyCheck}()$}{}
 \State assert($ \underline{u}  \leq u \leq \overline{u}$)
  \State set $x_0$ to be a vertex state, e.g., $[\underline{x_0},\underline{x_0}]$	
-\For {($c=0; c < 2^{Num_States}; c++$)}
+\For {($c=0; c < 2^\mathit{Num\_States}; c++$)}
   %\State assert($ \underline{x_0}  \leq x_0 \leq \overline{x_0}$)
@@
  \end{align*}     
-where $x_k^i$ denotes the trajectories obtained from the single vertex $v_i$. 
-We conclude that any $k$-step trajectory is encompassed, within a convex set, by those generated from the vertices.
+%
+where $x_k^i$ denotes the trajectories obtained from the single vertex
+$v_i$.  We~conclude that any $k$-step trajectory is encompassed, within a
+convex set, by those generated from the vertices.
 
@@
 
-\item The third {\sc verify} stage, {\sc complete}, checks that the
-current $k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
-completeness threshold $\overline{k}$ for the current candidate $K$
-and check that $k{\leq}\overline{k}$. This is done according to the following argument, 
-shown in Fig~\ref{fig:ct}.
-
-A stable control system is known to have converging dynamics. 
-Assume the closed-loop matrix eigenvalues are not repeated 
-(which is sensible to do, since we select them). 
-The trajectories distance from the reference point (origin) 
-decreases over time within subspaces related to real-valued eigenvalues;  
-however, this in general not the case when dealing with complex eigenvalues.  
-Consider the closed-loop matrix, which updates the states every discrete time step, 
-and select the eigenvalue $\vartheta$ with smallest (non-trivial) imaginary value. 
-At every consecutive time steps $kT_s, (k+1)T_s$, 
-the dynamics projected on the corresponding eigenspace rotate of $\vartheta T_s$ radiants.  
-So taking $k{\leq}\overline{k}$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, 
-after $k{\leq}\overline{k}$ steps we have completed a full rotation, which results in a point closer to the origin, and it is the completeness threshold.
+\item The third {\sc verify} stage, {\sc complete}, checks that the current
+$k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
+completeness threshold $\overline{k}$ for the current candidate $K$ and
+check that $k{\leq}\overline{k}$.  This is done according to the following
+argument, illustrated in Fig.~\ref{fig:ct}.
+
+A stable control system is known to have converging dynamics.  Assume the
+closed-loop matrix eigenvalues are not repeated (which is sensible to do,
+since we select them).  The distance of the trajectory from the reference
+point (origin) decreases over time within subspaces related to real-valued
+eigenvalues; however, this in general not the case when dealing with complex
+eigenvalues.  Consider the closed-loop matrix, which updates the states
+every discrete time step, and select the eigenvalue $\vartheta$ with
+smallest (non-trivial) imaginary value.  At every consecutive time steps
+$kT_s, (k+1)T_s$, the dynamics projected on the corresponding eigenspace
+rotate of $\vartheta T_s$ radiants.  So taking $k{\leq}\overline{k}$ as the
+ceiling of $\frac{2\pi}{\vartheta T_s}$, after $k{\leq}\overline{k}$ steps
+we have completed a full rotation, which results in a point closer to the
+origin, and it is the completeness threshold.
 
@@
 \vspace{0.1cm}
-\caption{Completeness threshold for multi-staged verification.}
+\caption{Completeness threshold for multi-staged verification}
 \label{fig:ct}

### 2017-01-28 cav2017/cav2017.tex
edits Sec. 3

@@
 \item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
+%
 $$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q_1}{2}\ \ \frac{q_1}{2}\right] 
 \wedge \nu_2 \in \left[-\frac{q_2}{2}\ \ \frac{q_2}{2}\right]  \wedge \nu_3 \in \left[-q_3\ \ q_3\right]  \right \}\nonumber$$
-where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is the error introduced by the DAC and $q_3$ is the maximum truncation and rounding error of the mathematical operation $u_k=-K*\mathcal{F}_{\langle I_c,F_c \rangle}(x_k)$ as discussed in section \ref{sec:numeric_rep}.
-More details on how to model quantization as noise are given in the 
+%
+where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is
+the error introduced by the DAC and $q_3$ is the maximum truncation and
+rounding error in $u_k=-K \cdot \mathcal{F}_{\langle I_c,F_c \rangle}(x_k)$ as
+discussed in Section~\ref{sec:numeric_rep}.  More details on how to model
+quantization as noise are given in
 Appendix~\ref{appendix:quantization-noise}.
-\item Calculate a set of initial bounds on $K$, $\phi_\mathit{init}^{K}$, based on the input constraints.
-Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
-$$(\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-K x_k) \Rightarrow \phi_\mathit{init}^{K}$$
+
+\item Calculate a set of initial bounds on $K$, $\phi_\mathit{init}^{K}$,
+based on the input constraints.  Note that these bounds will be used by the
+{\sc synthesize} phase to reduce the size of the solution space. 
+%
+$$(\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-K x_k)
+\Rightarrow \phi_\mathit{init}^{K}$$
 
@@
 \end{align}
+%
 As this still requires us to verify the system for every $k$ up to infinity,
-we use abstract acceleration again to obtain
-the reach-tube, i.e., the set of all reachable states at all times given an initial set $\phi_\mathit{init}$:
+we use abstract acceleration again to obtain the reach-tube, i.e., the set
+of all reachable states at all times given an initial set
+$\phi_\mathit{init}$:
+%
 \begin{align}
@@
 %
-where $\mathcal{A}=\bigcup_{k=1}^\infty (A_d-B_dK)t^k, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k(A_d-B_dK)^iB_{n}$ are abstract matrices for the closed-loop system \cite{cattaruzza2015unbounded}, whereas the set N is non-deterministically chosen.
-
-We next evaluate $\hat{X}^\# \models \phi_{safety}$. If the verification holds we have a solution, and exit the loop. Otherwise, 
-we find a counterexample iteration $k$ and corresponding initial point $x_0$ for which the property does not hold, which we use to locally refine the abstraction.
-When the abstraction cannot be further refined, we provide them to the {\sc abstract} phase.
+where $\mathcal{A}=\bigcup_{k=1}^\infty (A_d-B_dK)t^k,
+\mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k(A_d-B_dK)^iB_{n}$ are
+abstract matrices for the closed-loop system~\cite{cattaruzza2015unbounded},
+whereas the set $N$ is non-deterministically chosen.
+
+We next evaluate $\hat{X}^\# \models \phi_\mathit{safety}$.  If the
+verification holds we have a solution, and exit the loop.  Otherwise, we
+find a counterexample iteration $k$ and corresponding initial point $x_0$
+for which the property does not hold, which we use to locally refine the
+abstraction.  When the abstraction cannot be further refined, we provide
+them to the {\sc abstract} phase.
+%
 %\todo{we should have a better argument here.}
@@
 %
-Let us take the Helicopter example in Table \ref{table:State-space-benchmarks} with discretized dynamics
-$$A_d = \left[\begin{array}{ccc}2.6207&-1.1793&0.65705\\2&0&0\\0&0.5&0\end{array}\right], B_d = \left [\begin{array}{c}8\\0\\0\end{array}\right]$$
-Using the initial state bounds $\underline{x_{0}}=-0.9$ and $\overline{x_{0}}=0.9$, the input bounds $\underline{u}=-10$ and $\overline{u}=10$, and safety specifications 
-$\underline{x_{i}}=-0.92$ and $\overline{x_{i}}=0.92$, the {\sc synthesize} phase in Fig.~\ref{fig:CEGARIS} synthesizes an initial candidate controller $K=[\begin{array}{ccc}0.24609375&-0.125&0.1484375\end{array}]$.
-Although this candidate is stable, the {\sc verify} phase finds it to be unsafe and returns a list of iterations with an example initial state that fails the safety specification
-{\footnotesize $(k,x_0) {\in} \{ (2, [\begin{array}{ccc}0.9&-0.9&0.9\end{array}]), (3, [\begin{array}{ccc}0.9&-0.9&-0.9\end{array}])\}$}.
-This allows the {\sc abstract} phase to create a new safety specification that considers these iterations for these initial states to constrain the solution space.
-This refinement allows {\sc synthesize} to find a controller {\footnotesize $K=[\begin{array}{ccc}0.23828125&-0.17578125&0.109375\end{array}]$}, which this time passes the verification phase, resulting in a safe system.
+Let us consider the Helicopter example in Table
+\ref{table:State-space-benchmarks} with discretized dynamics
+%
+$$A_d = \left[\begin{array}{ccc}2.6207&-1.1793&0.65705\\2&0&0\\0&0.5&0\end{array}\right],
+\quad B_d = \left [\begin{array}{c}8\\0\\0\end{array}\right]$$
+%
+Using the initial state bounds $\underline{x_{0}}=-0.9$ and
+$\overline{x_{0}}=0.9$, the input bounds $\underline{u}=-10$ and
+$\overline{u}=10$, and safety specifications $\underline{x_{i}}=-0.92$ and
+$\overline{x_{i}}=0.92$, the {\sc synthesize} phase in
+Fig.~\ref{fig:CEGARIS} synthesizes an initial candidate controller
+$K=[\begin{array}{ccc}0.24609375&-0.125&0.1484375\end{array}]$.
+Although this candidate is stable, the {\sc verify} phase finds it to be
+unsafe and returns a list of iterations with an example initial state that
+fails the safety specification {\footnotesize $(k,x_0) {\in}
+\{ (2, [\begin{array}{ccc}0.9&-0.9&0.9\end{array}]),\allowbreak (3,
+[\begin{array}{ccc}0.9&-0.9&-0.9\end{array}])\}$}.  This allows the {\sc
+abstract} phase to create a new safety specification that considers these
+iterations for these initial states to constrain the solution space.  This
+refinement allows {\sc synthesize} to find a controller {\footnotesize
+$K=[\begin{array}{ccc}0.23828125&-0.17578125&0.109375\end{array}]$}, which
+this time passes the verification phase, resulting in a safe system.
 

### 2017-01-28 cav2017/cav2017.tex
edits

@@
 represented in the fixed-point precision level of the plant computational
-model ($I_p \geq I_c \wedge F_p \geq F_c$).  Thus any mathematical
+model ($I_p \geq I_c \wedge\allowbreak F_p \geq F_c$).  Thus any mathematical
 operations occurring in the digital controller will occur in the range of

### 2017-01-28 cav2017/cav2017.tex
font size table
fix

@@
 \centering
-\scriptsize
+%\scriptsize
 \begin{tabular}{| c | l | c | r | c | r |}
@@
 the characteristic polynomial $P(z)$ should be computed as follows:
+%
 \begin{equation}
-P(z)= \det( z I_{n} - A_d + B_d K ),
+P(z)= \det( z I_{n} - A_d + B_d K ) \,,
 \end{equation}
-where $I_{n}$ is the n-th order identity matrix.
+%
+where $I_{n}$ is the $n$-th order identity matrix.
 
@@
 $$
-P(z) = a_{0}z^{N} + a_{1}z^{N-1} + ... a_{N-1}z + a_{N} = 0, \;\; a_{0}\neq 0,
+P(z) = a_{0}z^{N} + a_{1}z^{N-1} + ... a_{N-1}z + a_{N} = 0, \;\; a_{0}\neq 0 \,,
 $$
@@
 $a_{0},a_{1},\ldots,a_{N-1}$ of $P(z)$ for checking stability, which we
-capture as property $\phi_{stability}$, as detailed below.
+capture as property $\phi_\mathit{stability}$, as detailed below.
 
@@
 \item $R_{3}$: $\vert{a_{0}}\vert <a_{N}$;
-\item $R_{4}$: $m_{11}>0\iff (m_{31}>0)\wedge (m_{51}>0)\wedge \dots \wedge (m_{(2N-3)(1)>0)}$.
+\item $R_{4}$: $m_{11}>0\iff (m_{31}>0)\wedge (m_{51}>0)\wedge \ldots \wedge (m_{(2N-3)(1)}>0)$.
 \end{itemize}

### 2017-01-28 cav2017/cav2017.tex
wording

@@
 cases, the SDP solver uses floating-point arithmetic and soundness is
-checked by bounding the error.  An alternative approach is taken
-by~\cite{park2016scalable}, where the verification of given control code is
-performed against a known model by extracting an LTI model of the code
-through symbolic execution.  In order to account for rounding errors, an
-upper bound is introduced in the verification phase.  The work in
-\cite{picasso2003stabilization, picasso2002construction} introduces
-attractive invariant sets as a mechanism to bound the quantization error
-effect on stabilization as an invariant set that always converges toward the
-controllable set.  In a similar fashion, \cite{liberzon2003hybrid} evaluates
-the dynamics of the quantization error and bounds its trajectory to a known
-region over a finite period of time.  This technique works for both linear
-and non-linear systems.
+checked by bounding the error.  An alternative is~\cite{park2016scalable},
+where the verification of given control code is performed against a known
+model by extracting an LTI model of the code by symbolic execution. 
+To~account for rounding errors, an upper bound is introduced in the
+verification phase.  The work in \cite{picasso2003stabilization,
+picasso2002construction} introduces attractive invariant sets as a mechanism
+to bound the quantization error effect on stabilization as an invariant set
+that always converges toward the controllable set.  In a similar fashion,
+\cite{liberzon2003hybrid} evaluates the dynamics of the quantization error
+and bounds its trajectory to a known region over a finite period of time. 
+This technique works for both linear and non-linear systems.
 

### 2017-01-28 cav2017/cav2017.tex
nudge

@@
 A discrete-time LTI system as \eqref{eq:closedloopss} is asymptotically
-stable \textit{iff} all the roots of the characteristic polynomial (i.e.,
-the eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the
-unity circle in the complex plane, i.e., \textit{iff} their absolute values
-are less than one~\cite{astrom1997computer}.  In this paper, we express the
-stability specification $\phi_{stability}$ in terms of a check known as
-Jury's criterion~\cite{fadali}: this is an easy algebraic formula to select
-the entries of matrix $K$, so that the closed-loop dynamics are shaped as
+stable iff all the roots of the characteristic polynomial (i.e., the
+eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
+circle in the complex plane, i.e., iff their absolute values are less than
+one~\cite{astrom1997computer}.  In this paper, we express the stability
+specification $\phi_\mathit{stability}$ in terms of a check known as Jury's
+criterion~\cite{fadali}: this is an easy algebraic formula to select the
+entries of matrix $K$, so that the closed-loop dynamics are shaped as
 desired (see Appendix~\ref{sec:appendix-stability} for details).

### 2017-01-28 cav2017/cav2017.tex
authors
edits

@@
 %\tocauthor{Authors' Instructions}
-\author{Anonymous}
+
+\author{%
+Alessandro Abate \and
+Iury Bessa \and
+Dario Cattaruzza \and
+Lucas Cordeiro \and
+\mbox{Cristina David} \and
+Pascal Kesseli \and
+Daniel Kroening \and
+Elizabeth Polgreen}
+
 \institute{}
@@
 which is typical in the case of oscillatory dynamics.  However, a safe
-system will always be stable.  In~this work, the safety property represented
-by $\phi_\mathit{safety}$ is encoded as follows:
+system will always be stable.  In~this work, the safety property 
+is modeled as follows:
 %
@@
 \label{eq:safetyliteral}
-\phi_\mathit{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
+\phi_\mathit{safety}\iff \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
 \end{equation}
@@
 \item {\bf Overflow:}
-The maximum size of a real number $x$ that can be represented in a fixed point domain as $\mathcal{F}_{\langle I,F \rangle}(x)$ is $\pm (2^{I-1}+1-2^{-F})$.
-Numbers outside this range cannot be represented by the domain.
-We check that overflow does not occur.
+The maximum size of a real number $x$ that can be represented in a fixed
+point domain as $\mathcal{F}_{\langle I,F \rangle}(x)$ is $\pm
+(2^{I-1}+1-2^{-F})$.  Numbers outside this range cannot be represented by
+the domain.  We check that overflow does not occur.
 

### 2017-01-28 cav2017/cav2017.tex
edits

@@
 fixed-point representation of numbers, and briefly describe the errors
-introduced.  A formal discussion is in
+introduced.  A~formal discussion is in
 Appendix~\ref{appendix:numerical_errors}.
@@
 %$\exists P .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ 
-$\exists P .  \forall x.  \sigma(x, P)$, 
+$\exists P .\,  \forall x.\,  \sigma(x, P)$, 
 where $P$ ranges over functions, 
@@
 $kT_s, (k+1)T_s$, the dynamics projected on the corresponding eigenspace
-rotate of $\vartheta T_s$ radiants.  So taking $k{\leq}\overline{k}$ as the
+rotate of $\vartheta T_s$ radiants.  Thus, taking $k{\leq}\overline{k}$ as the
 ceiling of $\frac{2\pi}{\vartheta T_s}$, after $k{\leq}\overline{k}$ steps
@@
 
-We have  used $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$ represented in a fixed point domain, with $I$ bits representing the integer part and $F$ bits representing the decimal part.
-The smallest number that can be represented in this domain is $c_m=2^{-F}$.
-The following approximation errors will arise in mathematical operations and representation:
+We have  used $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number
+$x$ represented in a fixed point domain, with $I$ bits representing the
+integer part and $F$ bits representing the decimal part.  The smallest
+number that can be represented in this domain is $c_m=2^{-F}$.  The
+following approximation errors will arise in mathematical operations and
+representation:
+%
 \begin{enumerate}
-\item {\bf Truncation:}
-Let $x$ be a real number, and $\mathcal{F}_{\langle I,F \rangle}(x)$ be the same number represented in a fixed-point domain as above. 
-Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the error $ \delta_T=x\ \%_{c_m}\ \tilde x$, and $\%_{c_m}$ is the modulus operation performed on the last bit.
-
-So $\delta_T$ is the truncation error and it will propagate across operations.
+
+\item {\bf Truncation:} Let $x$ be a real number, and $\mathcal{F}_{\langle
+I,F \rangle}(x)$ be the same number represented in a fixed-point domain as
+above.  Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the
+error $ \delta_T=x\ \%_{c_m}\ \tilde x$, and $\%_{c_m}$ is the modulus
+operation performed on the last bit.
+
+Thus, $\delta_T$ is the truncation error and it will propagate across
+operations.
 %

### 2017-01-28 cav2017/cav2017.tex
edits

@@
    &                                  & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
-1  & Cruise Control      & 8,16   & 6.88\,s & 16,16  & 241    \\
-2  & DC Motor            & 8,16   & 8.10\,s & 20,20  & 5376   \\
-3  & Helicopter          & \xmark & \xmark  & 16,16  & 2120   \\
-4  & Inverted Pendulum   & 8,16   & 7.81\,s & 16,16  & 387    \\
-5  & Magnetic Pointer    & \xmark & \xmark  & 28,28  & 132845 \\
-6  & Magnetic Suspension & 12,20  & 8.73\,s & 32,32  & 7854   \\
-7  & Pendulum            & 8,16   & 9.01\,s & 20,20  & 1150   \\
+1  & Cruise Control      & 8,16   & 6.88\,s & 16,16  &   0.24 \\
+2  & DC Motor            & 8,16   & 8.10\,s & 20,20  &   5.38 \\
+3  & Helicopter          & \xmark & \xmark  & 16,16  &   2.12 \\
+4  & Inverted Pendulum   & 8,16   & 7.81\,s & 16,16  &   0.39 \\
+5  & Magnetic Pointer    & \xmark & \xmark  & 28,28  & 132.85 \\
+6  & Magnetic Suspension & 12,20  & 8.73\,s & 32,32  &   7.85 \\
+7  & Pendulum            & 8,16   & 9.01\,s & 20,20  &   1.15 \\
 8  & Suspension          & 12,20  &49.41\,s & \xmark & \xmark \\

### 2017-01-28 cav2017/cav2017.tex
edits

@@
    &                                  & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
-1  & Cruise Control      & 8,16   & 6.88\,s & 16,16  &   0.24 \\
-2  & DC Motor            & 8,16   & 8.10\,s & 20,20  &   5.38 \\
-3  & Helicopter          & \xmark & \xmark  & 16,16  &   2.12 \\
-4  & Inverted Pendulum   & 8,16   & 7.81\,s & 16,16  &   0.39 \\
-5  & Magnetic Pointer    & \xmark & \xmark  & 28,28  & 132.85 \\
-6  & Magnetic Suspension & 12,20  & 8.73\,s & 32,32  &   7.85 \\
-7  & Pendulum            & 8,16   & 9.01\,s & 20,20  &   1.15 \\
+1  & Cruise Control      & 8,16   & 6.88\,s & 16,16  &   0.24\,s \\
+2  & DC Motor            & 8,16   & 8.10\,s & 20,20  &   5.38\,s \\
+3  & Helicopter          & \xmark & \xmark  & 16,16  &   2.12\,s \\
+4  & Inverted Pendulum   & 8,16   & 7.81\,s & 16,16  &   0.39\,s \\
+5  & Magnetic Pointer    & \xmark & \xmark  & 28,28  & 132.85\,s \\
+6  & Magnetic Suspension & 12,20  & 8.73\,s & 32,32  &   7.85\,s \\
+7  & Pendulum            & 8,16   & 9.01\,s & 20,20  &   1.15\,s \\
 8  & Suspension          & 12,20  &49.41\,s & \xmark & \xmark \\

### 2017-01-28 cav2017/cav2017.tex
edits

@@
 
-We give the run-times required to synthesize a stable controller for each
-benchmark in Table~\ref{tab:results}.  Here \textit{Benchmark} is the name
-of the respective benchmark, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the
-fixed-point precision used to model the plant, while \textit{Time} is the
-total time required to synthesize a stable controller for the given plant,
-for CEGIS with multi-staged verification as well as abstraction-based CEGIS. 
-The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$,
-is always chosen to be $I_c = 8, F_c = 8$.
+We give the results in Table~\ref{tab:results}.  Here \textit{Benchmark} is
+the name of the respective benchmark, $\mathcal{F}_{\langle I_p,F_p
+\rangle}$ is the fixed-point precision used to model the plant, while
+\textit{Time} is the total time required to synthesize a stable controller
+for the given plant, for CEGIS with multi-staged verification as well as
+abstraction-based CEGIS.  Timeouts are indicated by~\xmark.  The precision
+for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is chosen to be
+$I_c = 8$, $F_c = 8$.
 
@@
 %\scriptsize
-\begin{tabular}{| c | l | c | r | c | r |}
+\begin{tabular}{| r | l | c | r | c | r |}
 %

### 2017-01-28 cav2017/cav2017.tex
edits

@@
 require a very precise abstraction, resulting in too many refinements and,
-consequently, a timeout.  Yet another source of incompleteness is the
+consequently, timeout.  Yet another source of incompleteness is the
 inability of the {\sc synthesize} phase to use a large enough precision for
-the plant model in a given problem.
+the plant model.
 

### 2017-01-28 cav2017/cav2017.tex
wording

@@
 %
-\item  We give a novel synthesis algorithm for generating
-  state-feedback controllers that are provably stable and in addition
-  guaranteee a given safety property. Existing methods for controller
-  synthesis rely on transfer function representations, which are
+\item  We compute state-feedback controllers that are provably stable and in
+  addition guaranteee a given safety property.  Existing methods for
+  controller synthesis rely on transfer function representations, which are
   insufficient to prove safety requirements.
 %
-\item We give two algorithms: the first, naive one, relies on
-  an unfolding of the system's dynamics up to a completeness threshold,
-  while the second one is abstraction-based and leverages abstraction
-  refinement and acceleration to improve the scalability of the analysis
-  while retaining soundness.  Both approaches provide sound synthesis of
-  state-feedback systems and consider the various sources of imprecision in
-  the implementation of the control algorithm and in the computational
-  modeling of plant dynamics.
+\item We give two novel algorithms: the first, naive one, relies on
+  an unfolding of the dynamics up to a completeness threshold, while the
+  second one is abstraction-based and leverages abstraction refinement and
+  acceleration to improve scalability while retaining soundness.  Both
+  approaches provide sound synthesis of state-feedback systems and consider
+  the various sources of imprecision in the implementation of the control
+  algorithm and in the modeling of plant.
 %

### 2017-01-28 cav2017/cav2017.tex
wording

@@
 We will use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real
-number $x$ represented in the fixed-point precision level of the controller,
-and $\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$
-represented in the fixed-point precision level of the plant computational
-model ($I_p \geq I_c \wedge\allowbreak F_p \geq F_c$).  Thus any mathematical
-operations occurring in the digital controller will occur in the range of
-$\mathcal{F}_{\langle I_c,F_c \rangle}$, and all other calculations will be
-carried out in the range of $\mathcal{F}_{\langle I_p,F_p \rangle}$.  The
-physical plant operates in the reals, which means our verification phase
-must account for calculation errors in the model.
+number $x$ represented at the fixed-point precision of the controller, and
+$\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$
+represented at the fixed-point precision of the plant model ($I_p \geq I_c
+\wedge\allowbreak F_p \geq F_c$).  Thus any mathematical operations in the
+digital controller will be in the range of $\mathcal{F}_{\langle I_c,F_c
+\rangle}$, and all other calculations will be carried out in the range of
+$\mathcal{F}_{\langle I_p,F_p \rangle}$.  The physical plant operates in the
+reals, which means our verification phase must account for calculation
+errors in the model.
 

### 2017-01-28 cav2017/cav2017.tex
wording

@@
 %based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
-However, Pessoa does not have native inclusion of the quantization error
-introduced by Digital-to-Analogue/Analogue-to-Digital conversion needed for
-synthesizing fixed-point digital controllers.
+%
+However, Pessoa does not have consider the quantization error introduced by
+Digital-to-Analogue/Analogue-to-Digital conversion needed for synthesizing
+fixed-point digital controllers.
 

### 2017-01-28 cav2017/cav2017.tex
edits

@@
 approaches to synthesizing safe controllers: the first one is a baseline
-approach that relies on a naive explicit unwinding of the transition
+approach that relies on a naive explicit unfolding of the transition
 relation, whereas the second uses abstraction to implicitly evaluate all
@@
    (verif3.north) edge node[align=center] {} ([xshift=6.7cm]aux4)
-   ([xshift=6.7cm]aux4) edge node[align=center] {Increase Completeness Threshold} (aux3);
+   ([xshift=6.7cm]aux4) edge node[align=center] {Increase Unfolding Bound} (aux3);
    %(verif4.north) edge node[align=center] {} ([xshift=10.5cm]aux2)
@@
 Regarding the second requirement, we synthesize a safe controller by
-unwinding the transition system $k$ steps and by picking a controller $K$
+unfolding the transition system $k$ steps and by picking a controller $K$
 and a single initial state, such that the states at each step do not violate
@@
 \item The first {\sc verify} stage, {\sc safety}, checks that candidate
-solution $K$, which we synthesized to be safe for at least one initial state, is safe for \emph{all} possible initial states, i.e., does not reach an unsafe
-state within $k$ steps where we assume $k$ to be under the completeness threshold. 
-After unwinding the transition system corresponding to the previously synthesized controller
-$k$ steps, we check that the safety specification holds for any initial state.
+solution $K$, which we synthesized to be safe for at least one initial
+state, is safe for \emph{all} possible initial states, i.e., does not reach
+an unsafe state within $k$ steps where we assume $k$ to be under the
+completeness threshold.  After unfolding the transition system corresponding
+to the previously synthesized controller $k$ steps, we check that the safety
+specification holds for any initial state.
 

### 2017-01-29 cav2017/cav2017.tex
nuge

@@
    \& 
-   \& \node[fill=gray!20,align=center, minimum width=3cm] (synth) {\sc 2. synthesize};
+   \& \node[fill=gray!20,align=center] (synth) {\sc 2. synthesize};
        %\node[draw=none] (KL) at ([xshift=2.5cm,yshift=-.25cm]synth)  {\sc $\mat{K},\mat{L}$};
@@
        %\node[draw=none] (VUNS) at ([xshift=.6cm,yshift=1cm]verify)  {\sc SAT};
-       \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc SAT};
+       \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc PASS};
    \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
@@
      \coordinate (auxsynth);
-     \node[draw,rectangle,align=center] (KSAT) at ([xshift=0cm]auxsynth.center) {Prog.\\Search};
-     \node[draw=none] (SATK) at ([xshift=-.7cm,yshift=1.5cm]KSAT)  {{\sc Inputs}};
+     \node[draw,rectangle,align=center] (KSAT) at ([xshift=0cm]auxsynth.center) {Program\\Search};
+     \node[draw=none] (SATK) at ([xshift=-.7cm,yshift=1.5cm]KSAT)  {{$\phi(K,k)$}};
      \node[draw=none] (K) at ([xshift=.4cm,yshift=1.5cm]KSAT)  {$K$};
@@
      \coordinate (KUNSAT)  at ([xshift=0cm]UNSAT.center);
-     \node[draw=none] (UNSATB) at ([xshift=1.6cm,yshift=.3cm]UNSAT)  {\sc UNSAT};
+     \node[draw=none] (UNSATB) at ([xshift=1.6cm,yshift=.3cm]UNSAT)  {\sc UNSAT\\ (No Candidate Found)};
   }

### 2017-01-29 hscc2017/paper.tex

@@
 based on the error of the digital dynamics ensures that the deviation
-introduced by FWL does not make the digital system unstable.  A more recent
+introduced by FWL does not make the digital system unstable.  A~recent
 approach~\cite{DBLP:journals/automatica/WuLCC09} uses the $\mu$-calculus to

### 2017-01-30 cav2017/cav2017.tex
fixes for fig 4 (abstraction-based CEGIS)

@@
    \& ;\\
-   \&\node[fill=gray!20,align=center] (pre) {{\sc 1. pre-}\\{\sc processing}};
+   \&\node[fill=gray!20,align=center,xshift=-1.5cm] (pre) {{\sc 1. pre-}\\{\sc processing}};
    \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstract};
-   \& \coordinate (aux); \\ % \node[fill=yellow!20,align=center] (counter) {\sc counterexample};\\
+   \& \coordinate (aux); \\ 
    \&
    \& \node[fill=gray!20,align=center] (synth) {\sc 2. synthesize};
-       %\node[draw=none] (KL) at ([xshift=2.5cm,yshift=-.25cm]synth)  {\sc $\mat{K},\mat{L}$};
-       %\node[draw=none] (NKL) at ([xshift=2cm,yshift=1cm]synth)  {\sc $P_a$};
    \& \node[fill=gray!20,align=center, minimum width=4cm] (verify) {\sc 3. verify ($\phi$)};
-       %\node[draw=none] (VUNS) at ([xshift=.6cm,yshift=1cm]verify)  {\sc SAT};
       \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc PASS};
@@
    \&
-   \& complexnode/.pic={
-     \coordinate (auxsynth);
-     \node[draw,rectangle,align=center] (KSAT) at ([xshift=0cm]auxsynth.center) {Program\\Search};
-     \node[draw=none] (SATK) at ([xshift=-.7cm,yshift=1.5cm]KSAT)  {{$\phi(K,k)$}};
-     \node[draw=none] (K) at ([xshift=.4cm,yshift=1.5cm]KSAT)  {$K$};
-    }
+   \& \node[draw,rectangle,align=center] (KSAT) {Program \\ Search};
    \& complexnode/.pic={
@@
     (abstract.south) edge node{$(\phi(K), \vec{k})$} (synth.north)
-    %([yshift=2em]synth.east) edge node {Candidate} ([yshift=2em]verif.west)
-    %([yshift=-2em]verif.west) edge node {New input} ([yshift=-2em]synth.east)
-    %([yshift=2em]synth.east) edge node[xshift=-0.7em] {Candidate} ([yshift=2em]verif.west)
-    %([yshift=-2em]verif.west) edge node[xshift=-0.7em] {New input} ([yshift=-2em]synth.east)
     ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west)
-    %([yshift=-1em]verify.west) edge node {$P_a$} ([yshift=-1em]synth.east)
     (aux) edge (abstract.east) 
@@
   \path
-    ([xshift=+.6cm]KSAT.north) edge ([xshift=0.6cm]synth.south) 
-    ([xshift=-.6cm]synth.south) edge ([xshift=-.6cm]KSAT.north)
-    %(AAC) edge[bend right] node[align=center] {$k$} (AAI.north)
-    %([xshift=-4.9cm]verify.south) edge node[align=center] {$\mat{A},\mat{B}$\\$\phi$} (AAI.north)
-    %(AAI.east) edge (AAV.west)
+    ([xshift=+.6cm]KSAT.north) edge[left,xshift=-3cm] node {$K$} ([xshift=0.6cm]synth.south) 
+    ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$(\phi(K),\vec{k})$} ([xshift=-.6cm]KSAT.north)
     ([yshift=.5cm]AAV.east) edge node{\sl $\hat{X}^\#$} ([yshift=.5cm]AAC.west)
@@
     (AAC.north) edge node{\sl $\hat{X}^\#$} ([xshift=4.9cm]verify.south)
-    %(AAC.west) edge (AB.west)
-    %(verify.north) edge (counter.south)
-    %(counter.west) edge (abstract.east)
-    %(counter.south west) edge (synth.north east)
     (FAIL.north) edge (done.south)

### 2017-01-30 cav2017/cav2017.tex
make Fig 2 and Fig 4 uniform

@@
    \& \\
-   \node[minimum height=0cm] (gp) {\sf Closed-loop \\ System Search};
+   \node[minimum height=0cm] (gp) {\sf Program Search};
    \&
@@
     ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
-    (verif) edge node {} (done)
+    (verif) edge node {PASS} (done)
     ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)

### 2017-01-30 cav2017/cav2017.tex
de-vectorized k in Fig 4

@@
 These constraints correspond to specific iterations for which the system may be unsafe.
-\item Pass the refined abstraction $\phi(K)$ with the new constraints and the list of iterations $\vec{k}$ to the {\sc synthesize} phase.
+\item Pass the refined abstraction $\phi(K)$ with the new constraints and the list of iterations $k$ to the {\sc synthesize} phase.
   %, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again. 
@@
     (pre.east) edge node[align=center] {$P_a$, $N$,\\ $\phi_\mathit{init}^k$} (abstract.west)
-    (abstract.south) edge node{$(\phi(K), \vec{k})$} (synth.north)
+    (abstract.south) edge node{$(\phi(K), k)$} (synth.north)
     ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west)
@@
     ([xshift=+.6cm]KSAT.north) edge[left,xshift=-3cm] node {$K$} ([xshift=0.6cm]synth.south) 
-    ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$(\phi(K),\vec{k})$} ([xshift=-.6cm]KSAT.north)
+    ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$(\phi(K),k)$} ([xshift=-.6cm]KSAT.north)
     ([yshift=.5cm]AAV.east) edge node{\sl $\hat{X}^\#$} ([yshift=.5cm]AAC.west)

### 2017-01-30 cav2017/cav2017.tex
dot
fixed broken edges and removed UNSAT from Fig 4

@@
 {\scriptsize
-\hspace*{-1cm}
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
@@
     }\\
-   \&
-   \& complexnode/.pic={
-     \coordinate (UNSAT);
-     \coordinate (KUNSAT)  at ([xshift=0cm]UNSAT.center);
-     \node[draw=none] (UNSATB) at ([xshift=1.6cm,yshift=.3cm]UNSAT)  {\sc UNSAT\\ (No Candidate Found)};
-  }
-  \& \& \coordinate (FAIL);\\
   };
@@
   \path
-    ([xshift=+.6cm]KSAT.north) edge[left,xshift=-3cm] node {$K$} ([xshift=0.6cm]synth.south) 
+    ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {$K$} ([xshift=0.6cm]synth.south) 
     ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$(\phi(K),k)$} ([xshift=-.6cm]KSAT.north)
@@
     (AAC.north) edge node{\sl $\hat{X}^\#$} ([xshift=4.9cm]verify.south)
-    (FAIL.north) edge (done.south)
     ([xshift=-5cm]verify.south) edge node{$K$} (AAV.north);
   \path[-] 
-     (KSAT.south) edge (KUNSAT.north)
-     (KUNSAT.east) edge (FAIL.west)
      (verify.north) edge node {$(k,x_0)$} (aux);
@@
 }
-\caption{Abstraction-based CEGIS.}
+\caption{Abstraction-based CEGIS}
 \label{fig:CEGARIS} 

### 2017-01-30 hscc2017/paper.tex
address comment regarding the fact that the CEGIS solution space is finite but potentially very large

@@
 
-%\renewcommand{\baselinestretch}{0.975}
+\renewcommand{\baselinestretch}{0.99}
 \allowdisplaybreaks
@@
 
-% Copyright
+\CopyrightYear{2017}
 \setcopyright{acmcopyright}
-
-% DOI
-\doi{}
-
-% ISBN
-\isbn{}
-
-%
-% --- Author Metadata here ---
-%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
-%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
-%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
-% --- End of Author Metadata ---
+\conferenceinfo{HSCC '17,}{April 18--20, 2017, Pittsburgh, PA, USA.}
+\isbn{978-1-4503-4590-3/17/04}\acmPrice{\$15.00.}
+\doi{TDB.}
 
@@
 \thanks{Supported by EPSRC grant EP/J012564/1
-and ERC project 280053 (CPROVER).}
-%Counterexample-guided Synthesis of Closed-loop Digital Control Systems
-}
+and ERC project 280053 (CPROVER).}}
+
 %\subtitle{[Extended Abstract]
@@
 
-It is
-worth noting that each iteration of the loop adds a new input to the
-finite set $\text{\sc inputs}$ that is used for synthesis.  Given that
-the full set of inputs $\mathcal{D}$
-%\blue{[which by now should have a name, as suggested to be introduced above]} 
-is finite, this means that the refinement loop
-can only iterate a finite number of times.
+It is worth noting that each iteration of the loop adds a new input to
+the finite set $\text{\sc inputs}$ that is used for synthesis.  Given
+that the full set of inputs $\mathcal{D}$ is finite, this means that
+the refinement loop can only iterate a potentially very large, but
+finite number of times.
 

### 2017-01-30 cav2017/cav2017.tex
nudge

@@
 Elizabeth Polgreen}
+
+\authorrunning{Abate et al.}
 
@@
 $\overline{x_{i}}=0.92$, the {\sc synthesize} phase in
-Fig.~\ref{fig:CEGARIS} synthesizes an initial candidate controller
+Fig.~\ref{fig:CEGARIS} generates an initial candidate controller
 $K=[\begin{array}{ccc}0.24609375&-0.125&0.1484375\end{array}]$.
-Although this candidate is stable, the {\sc verify} phase finds it to be
-unsafe and returns a list of iterations with an example initial state that
+This candidate is stable, but the {\sc verify} phase finds it to be
+unsafe and returns a list of iterations with an initial state that
 fails the safety specification {\footnotesize $(k,x_0) {\in}
@@
 iterations for these initial states to constrain the solution space.  This
-refinement allows {\sc synthesize} to find a controller {\footnotesize
+refinement allows {\sc synthesize} to find a new controller {\footnotesize
 $K=[\begin{array}{ccc}0.23828125&-0.17578125&0.109375\end{array}]$}, which

### 2017-01-31 cav2017/cav2017.tex
nudge
extract lemmas from section 4.3

@@
 sufficiently unwind the closed-loop state-space system such that the
-boundaries are not violated for any $k{>}\overline{k}$ (i.e., it is
+boundaries are not violated for any $k{>}\overline{k}$.
+
+\begin{lemma} There exists a $\overline{k}$ such that it is
 sufficient to unwind the closed-loop state-space system up to $\overline{k}$
-in order to ensure that $\phi_\mathit{safety}$ holds).
+in order to ensure that $\phi_\mathit{safety}$ holds. 
+\end{lemma}
+
+\begin{proof}
+A stable control system is known to have converging dynamics.  Assume the
+closed-loop matrix eigenvalues are not repeated (which is sensible to do,
+since we select them).  The distance of the trajectory from the reference
+point (origin) decreases over time within subspaces related to real-valued
+eigenvalues; however, this in general not the case when dealing with complex
+eigenvalues.  Consider the closed-loop matrix, which updates the states
+every discrete time step, and select the eigenvalue $\vartheta$ with
+smallest (non-trivial) imaginary value.  At every consecutive time steps
+$kT_s, (k+1)T_s$, the dynamics projected on the corresponding eigenspace
+rotate of $\vartheta T_s$ radiants.  Thus, taking $k{\leq}\overline{k}$ as the
+ceiling of $\frac{2\pi}{\vartheta T_s}$, after $k{\leq}\overline{k}$ steps
+we have completed a full rotation, which results in a point closer to the
+origin, and it is the completeness threshold.
+\end{proof}
 
@@
 the Appendix.
-
- %\todo{unclear next: it seems like to select a single initial state here, rather than considering the set thereof - clarify. also, clarify relationship btw k and soundness. }
 
@@
 
-This is relatively computationally expensive if the bounds on the
-allowed initial states are large.  However, we can show that, if the
-controller is safe for each of the corner cases of our hypercube of
+\item The second {\sc verify} stage, {\sc precision}, 
+ restores soundness with respect to the plant's precision
+by using interval arithmetic \cite{moore1966interval} to validate the 
+operations performed by the previous stage.
+
+\item The third {\sc verify} stage, {\sc complete}, checks that the current
+$k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
+completeness threshold $\overline{k}$ for the current candidate $K$ and
+check that $k{\leq}\overline{k}$.  This is done according to the argument given above
+and illustrated in Fig.~\ref{fig:ct}.
+
+\begin{figure*}[t]
+\centering
+\includegraphics[width=0.6\textwidth]{ct.eps}
+\vspace{0.1cm}
+\caption{Completeness threshold for multi-staged verification}
+\label{fig:ct}
+\end{figure*}
+
+\end{enumerate}
+
+Checking that the safety specification holds for any initial state can be 
+computationally expensive if the bounds on the
+allowed initial states are large.
+
+\begin{lemma} 
+If a controller is safe for each of the corner cases of our hypercube of
 allowed initial states, it is safe for any initial state in the
-hypercube. Thus we only need to check $2^n$ initial states, where $n$
+hypercube. 
+\end{lemma}
+
+Thus we only need to check $2^n$ initial states, where $n$
 is the dimension of the state space (number of continuous variables). 
-
-To argue for this sufficient check, 
-consider the set of initial states, $X_0$, which we assume to be convex since it's a hypercube. 
+\begin{proof}
+Consider the set of initial states, $X_0$, which we assume to be convex since it's a hypercube. 
 Name $v_i$ its vertexes, where $i=1,\ldots, 2^n$.  
@@
 convex set, by those generated from the vertices.
-
-\item The second {\sc verify} stage, {\sc precision}, 
- restores soundness with respect to the plant's precision
-by using interval arithmetic \cite{moore1966interval} to validate the 
-operations performed by the previous stage.
-
-\item The third {\sc verify} stage, {\sc complete}, checks that the current
-$k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
-completeness threshold $\overline{k}$ for the current candidate $K$ and
-check that $k{\leq}\overline{k}$.  This is done according to the following
-argument, illustrated in Fig.~\ref{fig:ct}.
-
-A stable control system is known to have converging dynamics.  Assume the
-closed-loop matrix eigenvalues are not repeated (which is sensible to do,
-since we select them).  The distance of the trajectory from the reference
-point (origin) decreases over time within subspaces related to real-valued
-eigenvalues; however, this in general not the case when dealing with complex
-eigenvalues.  Consider the closed-loop matrix, which updates the states
-every discrete time step, and select the eigenvalue $\vartheta$ with
-smallest (non-trivial) imaginary value.  At every consecutive time steps
-$kT_s, (k+1)T_s$, the dynamics projected on the corresponding eigenspace
-rotate of $\vartheta T_s$ radiants.  Thus, taking $k{\leq}\overline{k}$ as the
-ceiling of $\frac{2\pi}{\vartheta T_s}$, after $k{\leq}\overline{k}$ steps
-we have completed a full rotation, which results in a point closer to the
-origin, and it is the completeness threshold.
-
-\begin{figure*}[t]
-\centering
-\includegraphics[width=0.6\textwidth]{ct.eps}
-\vspace{0.1cm}
-\caption{Completeness threshold for multi-staged verification}
-\label{fig:ct}
-\end{figure*}
-
-\end{enumerate}
+\end{proof}
 

### 2017-01-31 hscc2017/paper.tex
updated description of benchmarks for HSCC 2017 paper

@@
 
-The first set of benchmarks uses the discrete plant of a cruise control
+The first set of benchmarks uses the discrete plant $G_1(z)$ of a cruise control
 model for a car, and accounts for rolling friction, aerodynamic drag, and
-the gravitational disturbance force~\cite{Astrom08}. The plant model is
-given as follows:
-%
-\begin{equation}
-\label{cruise-control-c1}
-G_1(z)=\frac{0.0264}{z-0.998} \nonumber
-\end{equation}
-
-%Two proportional-integral (PI) controllers are designed by Wang {\it et al.} 
-%for the cruise control plant $G(z)$~\cite{DBLP:conf/hybrid/WangGRJF16}, 
-%which has the following mathematical model
-%
-%\begin{equation}
-%\label{cruise-control-g1}
-%C_{1}(z)=\frac{1.51z-1.3586}{z-1}, \nonumber
-%\end{equation} 
-%
-%\begin{equation}
-%\label{cruise-control-g2}
-%C_{2}(z)=\frac{2.72z^2 - 4.153z + 1.896}{1.0z^2 - 1.844z + 0.8496}. \nonumber
-%\end{equation}
-
-The second set of benchmarks considers a simple spring-mass 
-damper~\cite{DBLP:conf/hybrid/WangGRJF16}, where the discrete 
-plant dynamics is represented by the following $z$-expression:
-%
-%where both discrete 
-%plant dynamics and controller are represented by the following 
-%z-expression, resp.
-%
-\begin{equation}
-\label{spring-mass-damper-g}
-G_2(z)=\frac{5\times{10^{-5}}z + 5\times{10^{-5}}}{z^2 - 2z + 1.0001}. \nonumber
-\end{equation} 
-%
-%\begin{equation}
-%\label{spring-mass-damper-c}
-%C_3(z)=\frac{1.28\times{10^{3}}z^2 - 1.354240\times{10^{3}}z + 0.074879\times{10^{3}}}{z^2 - 1.4990z + 0.4995}. \nonumber
-%\end{equation}
-
-A third set of benchmarks uses a physical plant for satellite
+the gravitational disturbance force~\cite{Astrom08}. 
+%The plant model is given as follows:
+%
+%\begin{equation}
+%\label{cruise-control-c1}
+%G_1(z)=\frac{0.0264}{z-0.998} \nonumber
+%\end{equation} 
+%
+The second set of benchmarks considers the discrete plant $G_2(z)$ 
+of a simple spring-mass damper~\cite{DBLP:conf/hybrid/WangGRJF16}. 
+%where the discrete 
+%plant dynamics is represented by the following $z$-expression:
+%
+%\begin{equation}
+%\label{spring-mass-damper-g}
+%G_2(z)=\frac{5\times{10^{-5}}z + 5\times{10^{-5}}}{z^2 - 2z + 1.0001}. \nonumber
+%\end{equation} 
+%
+A third set of benchmarks uses the discrete plant $G_{3}(z)$ for satellite
 applications~\cite{Franklin15}.  Satellites require attitude (pose) control
@@
 attitude control is typically used for three-axis attitude tracking, but
-here we consider only one axis at a time.  The motion equation for the
-one-axis system, disregarding disturbance torques, is given by
-%
-\begin{equation}
-\label{eq:satelliteode}
-I\cdot \ddot{\theta} = \tau_{C}, 
-\end{equation}
-%
-\noindent where $I$ is the satellite inertia moment about its mass
-center, $\tau_{C}$ is the control torque applied by the thrusters, and
-$\theta$ is the controlled attitude angle.  Normalizing
-Eq.~\eqref{eq:satelliteode} by defining the control signal
-$u=\frac{\tau_{C}}{I}$ and taking the Laplace transform, the following
-$s$-domain transfer function $G(s)$ is obtained:
-%
-\begin{equation}
-\label{eq:satellitetf}
-G_{3}(s)=\frac{\theta(s)}{u(s)}=\frac{1}{s^2},
-\end{equation}
-%
-\noindent Using the ZOH discretization defined in Eq.~\eqref{eq:pulsetf}, 
-we get the following $z$-domain model:
-%
-\begin{equation}
-G_{3}(z)= \frac{T^{2}}{2} \frac{z+1}{(z+1)^{2}}. \nonumber
-\end{equation}
-
-%The discrete controllers $C_{4}$ and $C_{5}$ for the satellite plant $G_{3}$, discretized with sample time $1s$ and $2s$ respectively, 
-%are represented by the following z-expression:
-%
-%\begin{equation}
-%\label{satellite-b2}
-%C_{4}(z)=\frac{2.88z^2 - 4.896z + 2.074}{1.0z^2 - 0.42z - 0.3465 - 0.03915}. \nonumber
-%\end{equation} 
-%
-%\begin{equation}
-%\label{satellite-c2}
-%C_{5}(z)=\frac{0.43z^2 - 0.2408z - 0.1316}{1.0z^2 + 1.5z + 0.97 + 0.183}. \nonumber
-%\end{equation}
-
-The fourth (and last) set of benchmarks considers the following description
-for the plant $G_{4}(s)$, which is typically used for evaluating stability
-margins~\cite{bhattacharyya97, keel_Bhattacharyya_examples}:
-%
-\begin{equation}
-\label{exampleA}
-G_{4}(s)=\frac{s-1}{s^{2}-s-2},
-\end{equation}
-%
-\noindent We can obtain $G_{4}(z)$ using the ZOH discretization defined
-in Eq.~\eqref{eq:pulsetf} with three different sample times ($0.1$, $0.05$,
-and $0.03$ seconds), respectively, as follows:
-%
-\begin{equation}
-\label{exampleA-sampletime1}
-G_{4a}(z)=\frac{0.100342181002722z - 0.110876810062963}{1.0z^{2} - 2.12624017619613z + 1.10517091807565}, \nonumber
-\end{equation}
-%
-%
-\begin{equation}
-\label{exampleA-sampletime2}
-G_{4b}(z)=\frac{0.0500422033454653z - 0.0526068264456340}{1.0^{2} - 2.05640034257636z + 1.05127109637602}, \nonumber
-\end{equation}
-%
-%
-\begin{equation}
-\label{exampleA-sampletime3}
-G_{4c}(z)=\frac{0.0300090687252212z - 0.0309228417953966}{1.0^{2} - 2.03228208009387z + 1.03045453395352}. \nonumber
-\end{equation}
+here we consider only one axis at a time.  
+%The motion equation for the
+%one-axis system, disregarding disturbance torques, is given by
+%
+%\begin{equation}
+%\label{eq:satelliteode}
+%I\cdot \ddot{\theta} = \tau_{C}, 
+%\end{equation}
+%
+%\noindent where $I$ is the satellite inertia moment about its mass
+%center, $\tau_{C}$ is the control torque applied by the thrusters, and
+%$\theta$ is the controlled attitude angle.  Normalizing
+%Eq.~\eqref{eq:satelliteode} by defining the control signal
+%$u=\frac{\tau_{C}}{I}$ and taking the Laplace transform, the following
+%$s$-domain transfer function $G(s)$ is obtained:
+%
+%\begin{equation}
+%\label{eq:satellitetf}
+%G_{3}(s)=\frac{\theta(s)}{u(s)}=\frac{1}{s^2},
+%\end{equation}
+%
+%\noindent Using the ZOH discretization defined in Eq.~\eqref{eq:pulsetf}, 
+%we get the following $z$-domain model:
+%
+%\begin{equation}
+%G_{3}(z)= \frac{T^{2}}{2} \frac{z+1}{(z+1)^{2}}. \nonumber
+%\end{equation}
+%
+The fourth set of benchmarks considers the discrete plant $G_{4}(z)$
+that is typically used for evaluating stability
+margins~\cite{bhattacharyya97, keel_Bhattacharyya_examples}.
+%
+%\begin{equation}
+%\label{exampleA}
+%G_{4}(s)=\frac{s-1}{s^{2}-s-2},
+%\end{equation}
+%
+%\noindent We can obtain $G_{4}(z)$ using the ZOH discretization defined
+%in Eq.~\eqref{eq:pulsetf} with three different sample times ($0.1$, $0.05$,
+%and $0.03$ seconds), respectively, as follows:
+%
+%\begin{equation}
+%\label{exampleA-sampletime1}
+%G_{4a}(z)=\frac{0.100342181002722z - 0.110876810062963}{1.0z^{2} - 2.12624017619613z + 1.10517091807565}, \nonumber
+%\end{equation}
+%
+%
+%\begin{equation}
+%\label{exampleA-sampletime2}
+%G_{4b}(z)=\frac{0.0500422033454653z - 0.0526068264456340}{1.0^{2} - 2.05640034257636z + 1.05127109637602}, \nonumber
+%\end{equation}
+%
+%\begin{equation}
+%\label{exampleA-sampletime3}
+%G_{4c}(z)=\frac{0.0300090687252212z - 0.0309228417953966}{1.0^{2} - 2.03228208009387z + 1.03045453395352}. \nonumber
+%\end{equation}
+
+The fifth set of benchmarks contains the \textit{DC Motor Rate} discrete plant $G_{5}(z)$, which 
+describes the angular velocity of a DC Motor~\cite{Franklin15}. 
+%
+%\begin{equation}
+%\label{DC-Motor-Rate}
+%G_{5}(z)=\frac{ 0.1898z + 1.8027\times{10^{-4}}}{1.0z^{2} -0.9012z -1.0006\times{10^{-16}}}. \nonumber
+%\end{equation}
+%
+The sixth set of benchmarks contains the \textit{Helicopter Longitudinal Motion} discrete plant $G_{6}(z)$,
+which provides the longitudinal motion model of a helicopter~\cite{Franklin15}. 
+%
+%\begin{equation}
+%\label{Helicopter-Longitudinal-Motion}
+%G_{6}(z)=\frac{15.1315z^{2} + 17.8600z + 17.4549}{z^{3} -2.6207z^{2} + 2.3586z -0.6570}. \nonumber
+%\end{equation}
+%
+The seventh set of benchmarks contains the \textit{Inverted Pendulum} discrete plant $G_{7}(z)$, which 
+describes a pendulum model with its center of mass above its pivot point~\cite{Franklin15}. 
+%
+%\begin{equation}
+%\label{Inverted-Pendulum}
+%G_{7}(z)=\frac{0.0263z^{2} + 0.0143z -0.0383}{z^{4} -4.2553z^{3} + 6.5105z^{2} -4.2553z + 1}. \nonumber
+%\end{equation}
+%
+The eighth set of benchmarks contains the \textit{Magnetic Suspension} discrete plant $G_{8}(z)$,
+which provides a model for which a given object is suspended via magnetic field~\cite{Franklin15}. 
+%
+%\begin{equation}
+%\label{Magnetic-Suspension}
+%G_{8}(z)=\frac{6.769\times{10^{13}}z + 6.784\times{10^{13}}}{z^{2} -5.415\times{10^{13}}z + 4.23\times{10^{11}}}. \nonumber
+%\end{equation}
+
+The ninth set of benchmarks contains the \textit{1/4 Car Suspension} discrete plant $G_{9}(z)$,
+which presents a model that connects a car to its wheels and allows relative motion between both parts~\cite{Franklin15}.
+%
+%\begin{equation}
+%\label{Car-Suspension}
+%G_{8}(z)=\frac{0.25z^{3} + 0.5z^{3} + 0.25z -5.7065\times{10^{-10}}}{z^{3} + 6.8455\times{10^{-9}}z^{2} + 3.3925\times{10^{-17}}z - 3.4667\times%{10^{-94}}}. \nonumber
+%\end{equation}
+%
+The tenth set of benchmarks contains the \textit{Computer Tape Driver} discrete plant $G_{10}(z)$, which 
+describes a system to read and write data on a storage device in the computer~\cite{Franklin15}.
+%
+%\begin{equation}
+%\label{Computer-Tape-Driver}
+%G_{10}(z)=\frac{0.0200z -3.8303\times{10^{-176}}}{1.0z -4.6764\times{10^{-166}}}. \nonumber
+%\end{equation}
+The last two set of benchmarks describe discrete plants $G_{11}(z)$ and $G_{12}(z)$ 
+for a DC servo motor application (e.g., velocity control)~\cite{exampleCAD,Tan01}.
 

### 2017-01-31 hscc2017/paper.tex
minor changes on benchmarks description

@@
 
-The first set of benchmarks uses the discrete plant $G_1(z)$ of a cruise control
-model for a car, and accounts for rolling friction, aerodynamic drag, and
+The first set of benchmarks uses the discrete model $G_1(z)$ of a cruise control
+system for a car, and accounts for rolling friction, aerodynamic drag, and
 the gravitational disturbance force~\cite{Astrom08}. 
@@
 %
-The second set of benchmarks considers the discrete plant $G_2(z)$ 
-of a simple spring-mass damper~\cite{DBLP:conf/hybrid/WangGRJF16}. 
+The second set of benchmarks considers the discrete model $G_2(z)$ 
+of a simple spring-mass damper plant~\cite{DBLP:conf/hybrid/WangGRJF16}. 
 %where the discrete 
@@
 %
-A third set of benchmarks uses the discrete plant $G_{3}(z)$ for satellite
-applications~\cite{Franklin15}.  Satellites require attitude (pose) control
+A third set of benchmarks uses the discrete model $G_{3}(z)$ for satellite attitude 
+dynamics~\cite{Franklin15}.  Satellites require attitude (pose) control
 for orientation of antennas and sensors w.r.t.~earth.  The satellite
@@
 %
-The fourth set of benchmarks considers the discrete plant $G_{4}(z)$
+The fourth set of benchmarks considers the discrete model $G_{4}(z)$
 that is typically used for evaluating stability
-margins~\cite{bhattacharyya97, keel_Bhattacharyya_examples}.
+margins and controller fragility~\cite{bhattacharyya97, keel_Bhattacharyya_examples}.
 %
@@
 
-The fifth set of benchmarks contains the \textit{DC Motor Rate} discrete plant $G_{5}(z)$, which 
-describes the angular velocity of a DC Motor~\cite{Franklin15}. 
+The fifth set of benchmarks contains the \textit{DC Motor Rate} discrete model $G_{5}(z)$, which 
+describes the angular velocity of a DC Motor plant~\cite{Franklin15}. 
 %
@@
 %
-The sixth set of benchmarks contains the \textit{Helicopter Longitudinal Motion} discrete plant $G_{6}(z)$,
-which provides the longitudinal motion model of a helicopter~\cite{Franklin15}. 
+The sixth set of benchmarks contains the \textit{Helicopter Longitudinal Motion} discrete model $G_{6}(z)$,
+which provides the longitudinal motion dynamics of a helicopter plant~\cite{Franklin15}. 
 %
@@
 %
-The seventh set of benchmarks contains the \textit{Inverted Pendulum} discrete plant $G_{7}(z)$, which 
-describes a pendulum model with its center of mass above its pivot point~\cite{Franklin15}. 
+The seventh set of benchmarks contains the \textit{Inverted Pendulum} discrete model $G_{7}(z)$, which 
+describes a pendulum dynamics with its center of mass above its pivot point~\cite{Franklin15}. 
 %
@@
 %
-The eighth set of benchmarks contains the \textit{Magnetic Suspension} discrete plant $G_{8}(z)$,
-which provides a model for which a given object is suspended via magnetic field~\cite{Franklin15}. 
+The eighth set of benchmarks contains the \textit{Magnetic Suspension} discrete model $G_{8}(z)$, which describes the dynamics of a mass that levitates with support only of a magnetic field~\cite{Franklin15}.
 %
@@
 
-The ninth set of benchmarks contains the \textit{1/4 Car Suspension} discrete plant $G_{9}(z)$,
-which presents a model that connects a car to its wheels and allows relative motion between both parts~\cite{Franklin15}.
+The ninth set of benchmarks contains the \textit{1/4 Car Suspension} discrete model $G_{9}(z)$,
+which represents the dynamics of a single wheel suspension plant, {\it i.e.}, a system that connects a car to a wheel and allows relative motion between both parts~\cite{Franklin15}.
 %
@@
 %
-The tenth set of benchmarks contains the \textit{Computer Tape Driver} discrete plant $G_{10}(z)$, which 
+The tenth set of benchmarks contains the \textit{Computer Tape Driver} discrete model $G_{10}(z)$, which 
 describes a system to read and write data on a storage device in the computer~\cite{Franklin15}.
@@
 %\end{equation}
-The last two set of benchmarks describe discrete plants $G_{11}(z)$ and $G_{12}(z)$ 
-for a DC servo motor application (e.g., velocity control)~\cite{exampleCAD,Tan01}.
+The eleventh benchmark describe the discrete model of a DC servo motor velocity dynamics~\cite{exampleCAD,Tan01}.
+
+The last benchmark contains the discrete well-studied non-minimal phase model $G_{12}(z)$.
+Non-minimal phase model offers additional difficulties for the controller design~\cite{Doyle:1991:FCT:574259}.
 

### 2017-02-01 hscc2017/paper.tex
Updated benchmark results
Reran benchmarks for artifact evaluation with updated CBMC version.

@@
 1  & $G_1$  & CrsControl02
-            &   4 &  16 & 17\,s   & \xmark     \\
+            &   4 &  16 & 12\,s   & 67\,s     \\
 2  & $G_1$  & CrsControl02$^\dagger$
-            &   4 &  16 & 46\,s   & \xmark     \\
+            &   4 &  16 & 14600\,s   & 52\,s     \\
 3  & $G_2$  & SpgMsDamper
-            &  15 &  16 & 28\,s   & \xmark     \\
+            &  15 &  16 & 52\,s   & 318\,s     \\
 4  & $G_2$  & SpgMsDamper$^\dagger$
@@
 5  & $G_3$  & SatelliteB2
-            &   3 &   7 & 7\,s    & \xmark     \\
+            &   3 &   7 & 36,s    & \xmark     \\
 6  & $G_3$  & SatelliteB2$^\dagger$
-            &   3 &   7 & \xmark  & 6601\,s  \\
+            &   3 &   7 & \xmark  & 4111\,s  \\
 7  & $G_3$  & SatelliteC2
-            &   3 &   5 & 2\,s    & \xmark    \\
+            &   3 &   5 & 3\,s    & 205\,s    \\
 8  & $G_3$  & SatelliteC2$^\dagger$
-            &   3 &   5 & \xmark  & 76\,s    \\
-9  & $G_4a$ & a\_ST1\_IMPL1
-            &  16 &   4 & 2704\,s & \xmark   \\
-10 & $G_4a$ & a\_ST1\_IMPL2
-            &  16 &   8 & 538\,s  & \xmark   \\
-11 & $G_4a$ & a\_ST1\_IMPL3
-            &  16 &  12 & 12\,s   & \xmark   \\
-12 & $G_4b$ & a\_ST2\_IMPL1
-            &  16 &   4 & 318\,s  & \xmark   \\
-13 & $G_4b$ & a\_ST2\_IMPL2
-            &  16 &   8 & 967\,s  & \xmark    \\
-14 & $G_4b$ & a\_ST2\_IMPL3
-            &  16 &  12 & 9798\,s & \xmark   \\ 
-15 & $G_4c$ & a\_ST3\_IMPL1
-            &  16 &   4 & 6304\,s & \xmark   \\\hline
+            &   3 &   5 & 50\,s  & 1315\,s    \\
+9  & $G_3$  & Cruise
+            &   3 &   7 & 1\,s  & 1\,s    \\
+10 & $G_3$  & DC Motor
+            &   3 &   7 & 1\,s  & 10\,s    \\
+11 & $G_3$  & DC servomotor
+            &   4 &  11 & 46\,s  & \xmark    \\
+12 & $G_3$  & Doyleetal
+            &   4 &  11 & 8769\,s  & \xmark    \\
+13 & $G_3$  & Helicopter
+            &   3 &   7 & 44\,s  & \xmark    \\
+14 & $G_3$  & Pendulum
+            &   3 &   7 & 1\,s  & 14826\,s    \\
+15 & $G_3$  & Suspension
+            &   3 &   7 & 1\,s  & 5\,s    \\
+16 & $G_4a$ & a\_ST1\_IMPL1
+            &  16 &   4 & 11748\,s & \xmark   \\
+17 & $G_4a$ & a\_ST1\_IMPL2
+            &  16 &   8 & 351\,s  & \xmark   \\
+18 & $G_4a$ & a\_ST1\_IMPL3
+            &  16 &  12 & 8772\,s   & \xmark   \\
+19 & $G_4b$ & a\_ST2\_IMPL1
+            &  16 &   4 & 1128\,s  & \xmark   \\
+20 & $G_4b$ & a\_ST2\_IMPL2
+            &  16 &   8 & \xmark  & \xmark    \\
+21 & $G_4b$ & a\_ST2\_IMPL3
+            &  16 &  12 & 15183\,s & \xmark   \\ 
+22 & $G_4c$ & a\_ST3\_IMPL1
+            &  16 &   4 & \xmark & \xmark   \\\hline
 \end{tabular}
@@
 
-The median runtime for our benchmark set is $197$\,s, implying that \tool
-can synthesize half of the controllers in less than $5$ minutes.  Overall,
-the average synthesis time amounts to approximately $30$ minutes.  We
+The median runtime for our benchmark set is $50$\,s, implying that \tool
+can synthesize half of the controllers in less than one minute.  Overall,
+the average synthesis time amounts to approximately $45$ minutes.  We
 consider these times short enough to be of practical use to control
@@
 the two-stage verification engine is able to synthesize stable controllers
-in $12$ out of the $15$ benchmarks, and can be complemented using the
-one-stage engine for two additional benchmarks, where the inductive
+in $18$ out of the $22$ benchmarks, and can be complemented using the
+one-stage engine for additional benchmarks, where the inductive
 conjectures fail.  Both verification engines together enable controller
-synthesis for $14$ out of $15$ benchmarks.  For the one remaining benchmark
+synthesis for $19$ out of $22$ benchmarks.  For the remaining benchmarks
 our approach failed to synthesize a stable controller within the time
-limits.  This can be addressed by either increasing the fixed-point word
-widths considered or using floating-point arithmetic instead.  The
-synthesized controllers were confirmed to be stable outside of our model
-representation using MATLAB, positively answering RQ2.  A~link to the full
-experimental environment, including scripts to reproduce the results, all
-benchmarks and the \tool tool, is provided in the
+limits.  This can be addressed by either increasing either the time limit
+or the fixed-point word widths considered, or by using floating-point
+arithmetic instead.  The synthesized controllers were confirmed to be stable
+outside of our model representation using MATLAB, positively answering RQ2.
+A~link to the full experimental environment, including scripts to reproduce
+the results, all benchmarks and the \tool tool, is provided in the
 footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}

### 2017-02-01 hscc2017/paper.tex
work on text

--- 2017-01-31 hscc2017/paper.tex
@@
 %
-Given a synchronized ZOH input and sample and hold output on the plant with
+Given a synchronized ZOH input and sample-and-hold output on the plant with
 a sample time $T$ satisfying the Nyquist criterion, the discrete pulse
@@
 For the sake of brevity, we will use the notation $G(z)$ to represent the
-pulse transfer function.
+pulse transfer function $G(z,T)$.
 
@@
 operations, and it includes the ZOH dynamics in the $(1-z^{-1})$ term, which
-is sufficient for stability studies over $G(s)$.
+is sufficient for stability studies over $G(s)$ \red{[we need to clarify the last sentence - why is it sufficient, where is this fact stated?]}.
 
@@
 purpose.  It checks the stability of closed-loop control systems and
-considers finite-word length (FWL) effects in the digital controller and
+considers finite-word length (FWL) effects in the digital controller, and
 uncertainty parameters in the plant model (plant intervals)~\cite{Bessa16}. 
@@
 plant's coefficients; and $N_{(\cdot)}$ and $M_{(\cdot)}$ indicate the order
-of the polynomial of the corresponding block.
+of the polynomials. 
+% of the corresponding block.
 
@@
 %
+\red{[why is this condition on the order of the polynomials raised only now? how is it used later?]}
 Due to the nature of the methods we use for the stability check, we require
 that the parametric errors in the plant have the same polynomial order as
-the plant itself (all other errors described in this paper are ensured to
-fulfill this property in our implementation).
+the plant itself (\blue{all other errors described in this paper are ensured to
+fulfil this property in our implementation}\red{[have we later argued that this is indeed the case?]}) 
+\blue{and that enter the plant linearly}.
 
 We employ a notation based on the polynomials coefficients to simplify 
-the presentation.  Let $\mathcal{P}^{N}$ be a polynomial
-domain of order $N$. Let $P \in \mathcal{P}^{M,N}$ be a rational polynomial
+the presentation.  Let $\mathcal{P}^{N}$ be the space of polynomials of order $N$. 
+Let $P \in \mathcal{P}^{M,N}$ be a rational polynomial 
 $\frac{P_n}{P_d}$, where $P_n \in \mathcal{P}^{M}$ and $P_d \in \mathcal{P}^{N}$.  
@@
 %
-we write $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$.  In the following we will
+we write $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$.  
+\red{[confusing: we mix notations on abstract polynomials with those used for the plant above - the orders of the two are different ($N$ vs $N_G$) - please use the latter.]}
+In the following we will
 either use the functions $G(z)$, $C(z)$ directly, or work over their
@@
 represented as an additive output noise~$\nu(z)$.  
+\red{[We have recast the model as in Figure 2, but never defined $\nu$ and never use it later - retain the two separate noise contributions as in Figure 1.]}
 %, thus
@@
 }
-\caption{System equivalent to the system in Figure~\ref{fig:sampledsystem} 
+\caption{Digital equivalent to the system in Figure~\ref{fig:sampledsystem} 
 \label{fig:digsystem1}}
@@
 
+\red{[why is the output in Figure 2 tilde, whereas that in  figure 1 hat?]}
 %

### 2017-02-01 hscc2017/paper.tex
Added CBMC commit
Added exact CBMC commit download url.

@@
 the results, all benchmarks and the \tool tool, is provided in the
-footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}
+footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}\footnote{CBMC version: \url{https://github.com/diffblue/cbmc/archive/7a6cec1dd0eb8843559591105235f1f2c4678801.zip}}
 

### 2017-02-01 hscc2017/paper.tex
work on text

--- 2017-02-01 hscc2017/paper.tex
@@
 %
+\red{[what is the relationship between the deltas in this formula, and those in the previous paragraph? please clarify and hopefully simplify formulae. ]}
 which will be represented by the following transfer function:
@@
 controller is illustrated in Figure~\ref{fig:sampledsystem}.  The DAC and
-ADC converters introduce quantization errors which are modeled as noises
+ADC converters introduce quantization errors 
+\red{[why is the DAC introducing a quantisation error again?]}
+which are modeled as noises
 $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model
@@
 introduced by quantizations in sampling and holding process, i.e., ADC and
-DAC conversions.  These sources are assumed to be non-deterministic, 
+DAC conversions \red{[but the sample-and-hold happens only in the DAC, not in the ADC - right?]}.  These sources are assumed to be non-deterministic, 
 which poses no further restriction to our model, thus, the uncertain model
@@
 quantization effects on the plant model, {\it i.e.} $\Delta_q \vec{G}$ is 
-a model that incorporates the effects of $\nu$ in $\vec{\hat{G}}$ to 
+a model that incorporates the effects of $\nu$ \red{[undefined, see above]} in $\vec{\hat{G}}$ to 
 investigate the consequences in the stability of system, once our stability 
@@
 
-Since the controller is implemented using a FWL, $C(z)$ also suffers
+\smallskip
+
+Since the controller is implemented using finite representation, $C(z)$ also suffers
 disturbances from the FWL effects, with roundoffs in coefficients that may
@@
 affects the precision and the truncation after arithmetic operations. 
+\red{[we ought to align the following notations with those use in the CAV submission.]}
 We shall denote the FWL domain of the coefficients by $\mathbb{R}\langle I,F
@@
 %------------------------------------
-\subsection{Stability under FWL and Noise}
+\subsection{Stability under Finite Representation and Quantisation Noise}
 \label{sec:stability}
@@
 parametric uncertainties $\Delta \vec{G}$ and the FWL effects on
-the controller ($\hat{C}(z)$):
+the controller $\hat{C}(z)$:
 %
@@
 %
-\begin{equation}
+\begin{equation*}
 H_{1}(z)=\frac{1}{1+\hat{G}(z)\cdot \hat{C}(z)}
-\end{equation}
-%
-\begin{equation}
+\end{equation*}
+%
+\begin{equation*}
 H_{2}(z)=\frac{\hat{G}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}
-\end{equation}
+\end{equation*}
 %
@@
 %
-\begin{equation}
+\begin{equation*}
 H_{3}(z)=\frac{\hat{G}(z)\cdot \hat{C}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}
-\end{equation}
+\end{equation*}
 
@@
 \vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$,
-where $q_{1}$ and $q_{2}$, respectively, are the quantization steps of ADC
-and DAC.
+where $q_{1}$ and $q_{2}$ are the quantization steps of ADC and DAC, respectively.
 % 
@@
 the following proposition gives necessary conditions for the closed-loop system 
-BIBO stability in Figure~\ref{fig:sampledsystem}, since the
-exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$ are bounded.
-
-\begin{myprop}{\cite{fadali,Bessa16}}
+BIBO stability in Figure~\ref{fig:sampledsystem}, with regards to the 
+exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$, which are bounded.
+
+\begin{myprop}{\cite{Bessa16,fadali}}
 \label{prop:eq_int_stab} 
@@
 %
-$$\hat{G}(z) =\frac{\hat{G}_n(z)}{\hat{G}_d(z)}: \vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q
-\vec{G} \text{\quad(from~\ref{eq:coefficients},\ref{eq:delta_coefficients})}$$
+$$
+\hat{G}(z) =\frac{\hat{G}_n(z)}{\hat{G}_d(z)}: \vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q 
+\vec{G} \text{\quad(from~\ref{eq:coefficients},\ref{eq:delta_coefficients})}.
+$$
 %
@@
 
-Proposition~\ref{prop:eq_int_stab} provides the necessary conditions for the
+Proposition~\ref{prop:eq_int_stab} provides necessary (and sufficient) conditions for the
 controller to stabilize the closed-loop system, considering plant

### 2017-02-01 hscc2017/paper.tex
Added missing benchmark
Added missing tapedriver benchmark.

@@
             &   3 &   5 & 50\,s  & 1315\,s    \\
-9  & $G_3$  & Cruise
+9  & $G_4$  & Cruise
             &   3 &   7 & 1\,s  & 1\,s    \\
-10 & $G_3$  & DC Motor
+10 & $G_5$  & DC Motor
             &   3 &   7 & 1\,s  & 10\,s    \\
-11 & $G_3$  & DC servomotor
+11 & $G_6$  & DC servomotor
             &   4 &  11 & 46\,s  & \xmark    \\
-12 & $G_3$  & Doyleetal
+12 & $G_7$  & Doyleetal
             &   4 &  11 & 8769\,s  & \xmark    \\
-13 & $G_3$  & Helicopter
+13 & $G_8$  & Helicopter
             &   3 &   7 & 44\,s  & \xmark    \\
-14 & $G_3$  & Pendulum
+14 & $G_9$  & Pendulum
             &   3 &   7 & 1\,s  & 14826\,s    \\
-15 & $G_3$  & Suspension
+15 & $G_10$  & Suspension
             &   3 &   7 & 1\,s  & 5\,s    \\
-16 & $G_4a$ & a\_ST1\_IMPL1
+16 & $G_11$  & Tapedriver
+            &   3 &   7 & 1\,s  & 1\,s    \\
+17 & $G_12a$ & a\_ST1\_IMPL1
             &  16 &   4 & 11748\,s & \xmark   \\
-17 & $G_4a$ & a\_ST1\_IMPL2
+18 & $G_12a$ & a\_ST1\_IMPL2
             &  16 &   8 & 351\,s  & \xmark   \\
-18 & $G_4a$ & a\_ST1\_IMPL3
+19 & $G_12a$ & a\_ST1\_IMPL3
             &  16 &  12 & 8772\,s   & \xmark   \\
-19 & $G_4b$ & a\_ST2\_IMPL1
+20 & $G_12b$ & a\_ST2\_IMPL1
             &  16 &   4 & 1128\,s  & \xmark   \\
-20 & $G_4b$ & a\_ST2\_IMPL2
+21 & $G_12b$ & a\_ST2\_IMPL2
             &  16 &   8 & \xmark  & \xmark    \\
-21 & $G_4b$ & a\_ST2\_IMPL3
+22 & $G_12b$ & a\_ST2\_IMPL3
             &  16 &  12 & 15183\,s & \xmark   \\ 
-22 & $G_4c$ & a\_ST3\_IMPL1
+23 & $G_12c$ & a\_ST3\_IMPL1
             &  16 &   4 & \xmark & \xmark   \\\hline
@@
 
-The median runtime for our benchmark set is $50$\,s, implying that \tool
+The median runtime for our benchmark set is $48$\,s, implying that \tool
 can synthesize half of the controllers in less than one minute.  Overall,
-the average synthesis time amounts to approximately $45$ minutes.  We
+the average synthesis time amounts to approximately $42$ minutes.  We
 consider these times short enough to be of practical use to control
@@
 the two-stage verification engine is able to synthesize stable controllers
-in $18$ out of the $22$ benchmarks, and can be complemented using the
+in $19$ out of the $23$ benchmarks, and can be complemented using the
 one-stage engine for additional benchmarks, where the inductive
 conjectures fail.  Both verification engines together enable controller
-synthesis for $19$ out of $22$ benchmarks.  For the remaining benchmarks
+synthesis for $20$ out of $23$ benchmarks.  For the remaining benchmarks
 our approach failed to synthesize a stable controller within the time

### 2017-02-01 hscc2017/paper.tex
fix plant IDs

@@
             &   3 &   7 & 1\,s  & 14826\,s    \\
-15 & $G_10$  & Suspension
+15 &$G_{10}$& Suspension
             &   3 &   7 & 1\,s  & 5\,s    \\
-16 & $G_11$  & Tapedriver
+16 &$G_{11}$& Tapedriver
             &   3 &   7 & 1\,s  & 1\,s    \\
-17 & $G_12a$ & a\_ST1\_IMPL1
+17 &$G_{12a}$& a\_ST1\_IMPL1
             &  16 &   4 & 11748\,s & \xmark   \\
-18 & $G_12a$ & a\_ST1\_IMPL2
+18 &$G_{12a}$& a\_ST1\_IMPL2
             &  16 &   8 & 351\,s  & \xmark   \\
-19 & $G_12a$ & a\_ST1\_IMPL3
+19 &$G_{12a}$& a\_ST1\_IMPL3
             &  16 &  12 & 8772\,s   & \xmark   \\
-20 & $G_12b$ & a\_ST2\_IMPL1
+20 &$G_{12b}$& a\_ST2\_IMPL1
             &  16 &   4 & 1128\,s  & \xmark   \\
-21 & $G_12b$ & a\_ST2\_IMPL2
+21 &$G_{12b}$& a\_ST2\_IMPL2
             &  16 &   8 & \xmark  & \xmark    \\
-22 & $G_12b$ & a\_ST2\_IMPL3
+22 &$G_{12b}$& a\_ST2\_IMPL3
             &  16 &  12 & 15183\,s & \xmark   \\ 
-23 & $G_12c$ & a\_ST3\_IMPL1
+23 &$G_{12c}$& a\_ST3\_IMPL1
             &  16 &   4 & \xmark & \xmark   \\\hline

### 2017-02-01 hscc2017/paper.tex
wording

@@
 The sixth set of benchmarks contains the \textit{Helicopter Longitudinal Motion} discrete model $G_{6}(z)$,
-which provides the longitudinal motion dynamics of a helicopter plant~\cite{Franklin15}. 
+which provides the longitudinal motion dynamics of a helicopter~\cite{Franklin15}. 
 %
@@
 The tenth set of benchmarks contains the \textit{Computer Tape Driver} discrete model $G_{10}(z)$, which 
-describes a system to read and write data on a storage device in the computer~\cite{Franklin15}.
+describes a system to read and write data on a storage device~\cite{Franklin15}.
 %

### 2017-02-01 hscc2017/paper.tex
Draft section on soundness

@@
 controller is illustrated in Figure~\ref{fig:sampledsystem}.  The DAC and
-ADC converters introduce quantization errors 
-\red{[why is the DAC introducing a quantisation error again?]}
+ADC converters introduce quantization errors (notice that each of them
+may have a different FWL than the controller),
+%\red{[why is the DAC introducing a quantisation error again?]}
 which are modeled as noises
@@
 for the {\sc verify} phase as one-stage and two-stage, respectively.
+
+\subsection{Soundness}
+The soundness of the model is ensured by the {\sc verify} phase.
+The {\sc synthesise} phase is only concerned with providing a candidate solution that is not ensured to work for any of the plant models.
+However, it is increasingly likely to be correct as the system loops through counterexamples.
+The overall result is that if a candidate solution is validated by the verifier, it is necessarily sound, otherwise we may simply not find a valid solution in the given time.
+The {\sc verify} phase looks at two separate elements for soundness.
+The first corresponds to the fitness of the controller for all plant models.
+This phase ensures that there exists no counterexample plant that would create a closed loop with unstable poles.
+The fixed word length of the controller is not relevant at this point since the parameters have already been chosen to fit this criteria (\emph{ie} the candidate solution is FWL).
+The model is verified using the SAT solver backend in cbmc, which looks for the satisfiability of a plant with an unstable closed loop.
+If no counterexample is found, then the controller is necessarily stable for all plants in the collection.
+The limitation of this approach is the data type used by the verifier to perform the evaluation.
+Since the actual plant works in the reals, whereas we use fixed/floating point arithmetic to evaluate it, we need to ensure that the rounding errors in the caculations do not cause the solution to be unsound.
+For this reason the second verification phase uses interval arithmetic with outward rounding to ensure that these errors do not exceed critical bounds that could make some (or all) plant(s) unstable.
+This means that whilst the solution may not be complete, it is sound for evaluating any collection of real plants with a defined FWL controller for all of them.
+The need for two verification phases is because whereas this second phase can ensure the stability of all plants in the collection, it is unable to provide a counterexample.
 

### 2017-02-02 hscc2017/paper.tex
Addressed some of Alessandro's comments

@@
    \& \coordinate (aux1);
-   \& \node[draw=none] (yz) {$\hat{Y}(z)$};\\
+   \& \node[draw=none] (yz) {$\tilde {Y}(z)$};\\
    \& \coordinate (aux3); 
@@
 
-\red{[why is the output in Figure 2 tilde, whereas that in  figure 1 hat?]}
+%\red{[why is the output in Figure 2 tilde, whereas that in  figure 1 hat?]}
 %
@@
 introduced by quantizations in sampling and holding process, i.e., ADC and
-DAC conversions \red{[but the sample-and-hold happens only in the DAC, not in the ADC - right?]}.  These sources are assumed to be non-deterministic, 
+DAC conversions \red{[but the sample-and-hold happens only in the DAC, not in the ADC - right?]}\blue{[the sample-and-hold is on the ADC, the DAC is ZOH.
+I would just put `quantizations in the ADC and DAC conversions']}.
+These sources are assumed to be non-deterministic,
 which poses no further restriction to our model, thus, the uncertain model
@@
 quantization effects on the plant model, {\it i.e.} $\Delta_q \vec{G}$ is 
-a model that incorporates the effects of $\nu$ \red{[undefined, see above]} in $\vec{\hat{G}}$ to 
+a model that incorporates the effects of $\nu_1,\nu_2$ in $\vec{\hat{G}}$ to 
 investigate the consequences in the stability of system, once our stability 

### 2017-02-02 hscc2017/paper.tex
scale down table
cuts to wordings

@@
 \newcommand{\green}[1]{{\color{green}#1}}
+%\newcommand{\blue}[1]{}
+%\newcommand{\red}[1]{}
+%\newcommand{\green}[1]{}
 
@@
 
-\item We design and implement an automatic approach in our tool \tool  
-  for generating {\em correct-by-construction} digital controllers that is
-  based on state-of-the-art inductive synthesis techniques.  Our application
-  of program synthesis is non-trivial and requires addressing challenges
-  specific to embedded control systems, such as the effects of quantizers
-  and FWL.  In particular, we have found that a two-stage verification
-  engine that continuously refines the precision of the fixed-point
-  representation of the plant is key to the performance of our approach
-  yielding, in most cases, a speed-up of at least two orders of magnitude
-  over a conventional one-stage verification engine.
-
-\item We provide experimental results showing that \tool is able to
-  efficiently synthesize stable controllers for a set of intricate
-  benchmarks taken from the literature: the median runtime for our benchmark
-  set is $197$\,s, i.e., half of the controllers can be synthesized in less
-  than five minutes.
+\item We automatically generate {\em correct-by-construction} digital
+  controllers using inductive synthesis.  Our application of program
+  synthesis is non-trivial and addresses challenges specific to control
+  systems, such as the effects of quantizers and FWL.  In particular, we
+  have found that a two-stage verification engine that continuously refines
+  the precision of the fixed-point representation of the plant yields a
+  speed-up of two orders of magnitude over a conventional one-stage
+  verification engine.
+
+\item Experimental results show that \tool is able to efficiently synthesize
+  stable controllers for a set of intricate benchmarks taken from the
+  literature: the median runtime for our benchmark set is $197$\,s, i.e.,
+  half of the controllers can be synthesized in less than five minutes.
 
@@
 and we discuss how we extend the state-of-the-art beyond the existing
-literature in Section~\ref{sec:related}. We conclude and describe future
-work in Section~\ref{sec:conclusions}.
+literature in Section~\ref{sec:related}.
 
@@
 paper are typically used in closed loops with continuous (physical) plants. 
-Thus, the proposed approach considers dynamics of continuous parts of
-the system (i.e., the plant) and of discrete parts (i.e., the digital
-controller).  To obtain a joint model, we fully discretize the continuous
-plant.  We briefly recall the standard foundations of this step.
-
-We only consider transfer function models, and require a $z$-domain
-transfer function $G(z)$ that captures all aspects of the continuous plant (with a
-Laplace domain transfer function $G(s)$) and the sampling and hold process.
-%Note that $G(z)$ is a discrete model of a physical, continuous
-%plant, i.e., 
-The continuous model of the plant must be discretized to obtain the corresponding 
-%discrete equivalent 
-coefficients of $G(z)$.
-%via ZOH discretization.
+Thus, we consider continuous dynamics (the plant) and discrete parts (the
+digital controller).  To obtain a joint model, we fully discretize the
+continuous plant.  We briefly recall the standard foundations of this step.
+
+We only consider transfer function models, and require a $z$-domain transfer
+function $G(z)$ that captures all aspects of the continuous plant with a
+Laplace domain transfer function $G(s)$ and the sampling and hold process. 
+The continuous model of the plant must be discretized to obtain the
+corresponding coefficients of $G(z)$.
 
@@
 
-Among the discretization methods available in the
-literature~\cite{Franklin15}, the zero-order hold (ZOH) discretization is
-considered suitable for representing the sample and hold processes that are
-typically employed in complex systems~\cite{istepanian2012digital}.  The ZOH
+Among the discretization methods in the literature~\cite{Franklin15}, the
+zero-order hold (ZOH) discretization is suitable for representing the sample
+and hold processes in complex systems~\cite{istepanian2012digital}.  The ZOH
 discretization models the exact effect of sampling and DAC interpolation
@@
 \centering
+\scalebox{0.8}{
 \begin{tabular}{| r | c | l | r r || r | r |}
@@
             &  16 &   4 & \xmark & \xmark   \\\hline
-\end{tabular}
-
-\vspace{0.5em}
-\scriptsize{\xmark = time-out, $\dagger$ = with uncertainty}
-\vspace{0.5em}
-
-\caption{Experimental results obtained with \tool\label{tab:results}}
+\end{tabular}}\\[0.2ex]
+\caption{\tool results ({\xmark} = time-out, $\dagger$ = 
+uncertainty)
+\label{tab:results}}
 \end{table}

### 2017-02-02 hscc2017/paper.tex
line breaks
reviewed 3.5 Soundness

@@
 
+%-----------------------------
 \subsection{Soundness}
+%-----------------------------
+
 The soundness of the model is ensured by the {\sc verify} phase.
@@
 However, it is increasingly likely to be correct as the system loops through counterexamples.
-The overall result is that if a candidate solution is validated by the verifier, it is necessarily sound, otherwise we may simply not find a valid solution in the given time.
+The overall result is that if a candidate solution is validated by the verifier, it is necessarily sound; otherwise, we may simply not find a valid solution in the given time.
 The {\sc verify} phase looks at two separate elements for soundness.
 The first corresponds to the fitness of the controller for all plant models.
-This phase ensures that there exists no counterexample plant that would create a closed loop with unstable poles.
-The fixed word length of the controller is not relevant at this point since the parameters have already been chosen to fit this criteria (\emph{ie} the candidate solution is FWL).
-The model is verified using the SAT solver backend in cbmc, which looks for the satisfiability of a plant with an unstable closed loop.
+This phase ensures that there exists no counterexample plant that would create a closed-loop with unstable poles.
+The fixed word length of the controller is not relevant at this point since the parameters have already been chosen to fit this criteria (i.e., the candidate solution is FWL).
+The model is verified using the SAT solver backend in CBMC, which looks for the satisfiability of a plant with an unstable closed loop.
 If no counterexample is found, then the controller is necessarily stable for all plants in the collection.

### 2017-02-02 hscc2017/paper.tex
minor changes to 3.5 Soundness

@@
 The soundness of the model is ensured by the {\sc verify} phase. 
-The {\sc synthesise} phase is only concerned with providing a candidate solution that is not ensured to work for any of the plant models.
-However, it is increasingly likely to be correct as the system loops through counterexamples.
-The overall result is that if a candidate solution is validated by the verifier, it is necessarily sound; otherwise, we may simply not find a valid solution in the given time.
-The {\sc verify} phase looks at two separate elements for soundness.
-The first corresponds to the fitness of the controller for all plant models.
-This phase ensures that there exists no counterexample plant that would create a closed-loop with unstable poles.
-The fixed word length of the controller is not relevant at this point since the parameters have already been chosen to fit this criteria (i.e., the candidate solution is FWL).
-The model is verified using the SAT solver backend in CBMC, which looks for the satisfiability of a plant with an unstable closed loop.
-If no counterexample is found, then the controller is necessarily stable for all plants in the collection.
-The limitation of this approach is the data type used by the verifier to perform the evaluation.
-Since the actual plant works in the reals, whereas we use fixed/floating point arithmetic to evaluate it, we need to ensure that the rounding errors in the caculations do not cause the solution to be unsound.
-For this reason the second verification phase uses interval arithmetic with outward rounding to ensure that these errors do not exceed critical bounds that could make some (or all) plant(s) unstable.
-This means that whilst the solution may not be complete, it is sound for evaluating any collection of real plants with a defined FWL controller for all of them.
-The need for two verification phases is because whereas this second phase can ensure the stability of all plants in the collection, it is unable to provide a counterexample.
+The {\sc synthesise} phase is only concerned with providing a candidate 
+solution that is not ensured to work for any of the plant models. 
+However, it is increasingly likely to be correct as the system loops 
+through counterexamples. The overall result is that if a candidate solution 
+is validated by the verifier, it is necessarily sound; otherwise, we may simply 
+not find a valid solution in the given time. The {\sc verify} phase looks at 
+two separate elements for soundness. The first corresponds to the controller fitness 
+for all plant models. This phase ensures that there exists no counterexample plant 
+that would create a closed-loop with unstable poles. The controller fixed word length 
+is not relevant at this point since the parameters have already been chosen to fit 
+this criteria (i.e., the candidate solution is FWL). The model is verified using 
+the SAT solver backend in CBMC, which looks for the satisfiability of a plant 
+with an unstable closed-loop. If no counterexample is found, then the controller 
+is necessarily stable for all plants in the collection. The limitation of this approach 
+is the data type used by the verifier to perform the evaluation. Since the actual plant 
+works in the reals, whereas we use fixed/floating point arithmetic to evaluate it, 
+we need to ensure that the rounding errors in the calculations do not cause the solution 
+to be unsound. For this reason the second verification phase uses interval arithmetic 
+with outward rounding to ensure that these errors do not exceed critical bounds that 
+could make some (or all) plant(s) unstable. This means that whilst the solution may not be complete, 
+it is sound for evaluating any collection of real plants with a defined FWL controller for all of them. 
+The need for two verification phases is because whereas this second phase can ensure 
+the stability of all plants in the collection, it is unable to provide a counterexample.
 

### 2017-02-02 hscc2017/paper.tex
reviewed 4.3 Results

@@
 A third set of benchmarks uses the discrete model $G_{3}(z)$ for satellite attitude 
-dynamics~\cite{Franklin15}.  Satellites require attitude (pose) control
-for orientation of antennas and sensors w.r.t.~earth.  The satellite
-attitude control is typically used for three-axis attitude tracking, but
-here we consider only one axis at a time.  
+dynamics~\cite{Franklin15}, which require attitude (pose) control
+for orientation of antennas and sensors w.r.t.~earth.  
+%The satellite
+%attitude control is typically used for three-axis attitude tracking, but
+%here we consider only one axis at a time.  
 %The motion equation for the
@@
 %
-The fourth set of benchmarks considers the discrete model $G_{4}(z)$
-that is typically used for evaluating stability
-margins and controller fragility~\cite{bhattacharyya97, keel_Bhattacharyya_examples}.
 %
@@
 
-The fifth set of benchmarks contains the \textit{DC Motor Rate} discrete model $G_{5}(z)$, which 
-describes the angular velocity of a DC Motor plant~\cite{Franklin15}. 
+The fifth and sixth set of benchmarks describe the discrete model 
+of a DC servo motor velocity dynamics~\cite{exampleCAD,Tan01}.
+
+The seventh set of benchmarks contains the discrete well-studied 
+non-minimal phase model $G_{7}(z)$. Non-minimal phase model offers 
+additional difficulties for the controller design~\cite{Doyle:1991:FCT:574259}.
+
+%The fifth set of benchmarks contains the \textit{DC Motor Rate} discrete model $G_{5}(z)$, which 
+%describes the angular velocity of a DC Motor plant~\cite{Franklin15}. 
 %
@@
 %
-The sixth set of benchmarks contains the \textit{Helicopter Longitudinal Motion} discrete model $G_{6}(z)$,
+The eighth set of benchmarks contains the \textit{Helicopter Longitudinal Motion} discrete model $G_{8}(z)$,
 which provides the longitudinal motion dynamics of a helicopter~\cite{Franklin15}. 
@@
 %
-The seventh set of benchmarks contains the \textit{Inverted Pendulum} discrete model $G_{7}(z)$, which 
+The ninth  set of benchmarks contains the \textit{Inverted Pendulum} discrete model $G_{9}(z)$, which 
 describes a pendulum dynamics with its center of mass above its pivot point~\cite{Franklin15}. 
@@
 %
-The eighth set of benchmarks contains the \textit{Magnetic Suspension} discrete model $G_{8}(z)$, which describes the dynamics of a mass that levitates with support only of a magnetic field~\cite{Franklin15}.
+The tenth set of benchmarks contains the \textit{Magnetic Suspension} discrete model $G_{10}(z)$, which describes the dynamics of a mass that levitates with support only of a magnetic field~\cite{Franklin15}.
 %
@@
 
-The ninth set of benchmarks contains the \textit{1/4 Car Suspension} discrete model $G_{9}(z)$,
-which represents the dynamics of a single wheel suspension plant, {\it i.e.}, a system that connects a car to a wheel and allows relative motion between both parts~\cite{Franklin15}.
+%The ninth set of benchmarks contains the \textit{1/4 Car Suspension} discrete model $G_{9}(z)$,
+%which represents the dynamics of a single wheel suspension plant, {\it i.e.}, a system that connects a car to a wheel and allows relative motion between both %parts~\cite{Franklin15}.
 %
@@
 %
-The tenth set of benchmarks contains the \textit{Computer Tape Driver} discrete model $G_{10}(z)$, which 
+The eleventh set of benchmarks contains the \textit{Computer Tape Driver} discrete model $G_{11}(z)$, which 
 describes a system to read and write data on a storage device~\cite{Franklin15}.
@@
 %\end{equation}
-The eleventh benchmark describe the discrete model of a DC servo motor velocity dynamics~\cite{exampleCAD,Tan01}.
-
-The last benchmark contains the discrete well-studied non-minimal phase model $G_{12}(z)$.
-Non-minimal phase model offers additional difficulties for the controller design~\cite{Doyle:1991:FCT:574259}.
+%
+The last set of benchmarks considers the discrete model $G_{12}(z)$
+that is typically used for evaluating stability
+margins and controller fragility~\cite{bhattacharyya97, keel_Bhattacharyya_examples}.
 
@@
 seconds as measured by the UNIX date command.  For the two-stage verification 
-engine we apply a timeout of 8 hours per benchmark, and 24 hours for the approach 
+engine we apply a timeout of $8$ hours per benchmark, and $24$ hours for the approach 
 using a one-stage engine.

### 2017-02-02 hscc2017/paper.tex
reviewed 4.1 Description of the Benchmarks
reviewed 4.3 Results

@@
 for orientation of antennas and sensors w.r.t.~earth.
+The fourth set of benchmarks presents an alternative discrete model $G_4(z)$ 
+of a cruise control system~\cite{DBLP:conf/hybrid/WangGRJF16}. 
 %The satellite
@@
 %\end{equation}
-
+%
 The fifth and sixth set of benchmarks describe the discrete model 
@@
 additional difficulties for the controller design~\cite{Doyle:1991:FCT:574259}.
-
+%
 %The fifth set of benchmarks contains the \textit{DC Motor Rate} discrete model $G_{5}(z)$, which 
@@
 
-We give the runtimes required to synthesize a stable controller for each
+We give the run-times required to synthesize a stable controller for each
 benchmark in Table~\ref{tab:results}.  Here, \textit{Plant} is the discrete
@@
 increases of the fixed-point precision.  However, two benchmarks in our set
-required too many counterexamples to refine their solution (marked with $^*$
-in Table~\ref{tab:results}).  In these cases, the one-stage engine 
-%interval arithmetic back-end 
-is able to complement the two-stage approach and synthesize a solution
-instead, albeit with significantly larger runtimes.  This performance
-difference is due to the fact that the one-stage verification engine does
+required too many counterexamples to refine their solution \textcolor{red}{
+(marked with $^*$ in Table~\ref{tab:results})}.  
+In these cases, the one-stage engine is able to complement the two-stage 
+approach and synthesize a solution instead, albeit with significantly larger run-times.  
+This performance difference is due to the fact that the one-stage verification engine does
 not take advantage of the inductive conjecture inherent to CEGIS, but
@@
 experiments, leading to the one-stage engine timing out on the majority of
-our benchmarks.  Table~\ref{tab:results} only lists the faster of the two
+our benchmarks. \textcolor{red}{Table~\ref{tab:results} only lists the faster of the two
 verification engines for each benchmark, which in $12$ out of $15$
-benchmarks is the two-stage one.
+benchmarks is the two-stage one}.
 
@@
 
-The median runtime for our benchmark set is $48$\,s, implying that \tool
+The median run-time for our benchmark set is $48$\,s, implying that \tool
 can synthesize half of the controllers in less than one minute.  Overall,
@@
 
+%--------------------------------------
 \subsection{Threats to validity}
+%--------------------------------------
 

### 2017-02-02 hscc2017/paper.tex
some revision of the soundness discussion

@@
 
-The soundness of the model is ensured by the {\sc verify} phase. 
-The {\sc synthesise} phase is only concerned with providing a candidate 
-solution that is not ensured to work for any of the plant models. 
-However, it is increasingly likely to be correct as the system loops 
-through counterexamples. The overall result is that if a candidate solution 
-is validated by the verifier, it is necessarily sound; otherwise, we may simply 
-not find a valid solution in the given time. The {\sc verify} phase looks at 
-two separate elements for soundness. The first corresponds to the controller fitness 
-for all plant models. This phase ensures that there exists no counterexample plant 
-that would create a closed-loop with unstable poles. The controller fixed word length 
-is not relevant at this point since the parameters have already been chosen to fit 
-this criteria (i.e., the candidate solution is FWL). The model is verified using 
-the SAT solver backend in CBMC, which looks for the satisfiability of a plant 
-with an unstable closed-loop. If no counterexample is found, then the controller 
-is necessarily stable for all plants in the collection. The limitation of this approach 
-is the data type used by the verifier to perform the evaluation. Since the actual plant 
-works in the reals, whereas we use fixed/floating point arithmetic to evaluate it, 
-we need to ensure that the rounding errors in the calculations do not cause the solution 
-to be unsound. For this reason the second verification phase uses interval arithmetic 
-with outward rounding to ensure that these errors do not exceed critical bounds that 
-could make some (or all) plant(s) unstable. This means that whilst the solution may not be complete, 
-it is sound for evaluating any collection of real plants with a defined FWL controller for all of them. 
-The need for two verification phases is because whereas this second phase can ensure 
-the stability of all plants in the collection, it is unable to provide a counterexample.
+While the {\sc synthesise} phase searches for potentially unsound 
+candidate solutions, the soundness of the model is ensured by the {\sc verify} phase.  
+If a candidate solution is validated by the verifier, it is necessarily
+sound.
+
+Through its two stages, the {\sc verify} phase looks at two separate elements for
+soundness.
+% The first ensures that there exists no
+% counterexample plant that would create a closed-loop with unstable
+% poles. The fixed word length of the controller is not relevant at this
+% point since the parameters have already been chosen to fit this
+% criteria (i.e., the candidate solution is FWL).
+The first stage ensures that no counterexample
+plant with an unstable closed loop exists with % If no such
+% system exists, then the controller is stable for all
+% plants in the collection with
+the limitations given by the data
+type used by the verifier. Since the actual
+plant works in the reals, whereas we use fixed/floating point
+arithmetic to evaluate it, we need to ensure that the rounding errors
+in the caculations do not cause the solution to be unsound.
+
+For this reason the second verification stage uses interval arithmetic with
+outward rounding to ensure that these errors do not exceed critical
+bounds that could make some (or all) plant(s) unstable. This means
+that whilst the solution may not be complete, it is sound for
+evaluating any collection of real plants with a defined FWL controller
+for all of them. We require two verification stages because,
+while the second phase can ensure the stability of all plants in
+the collection, it is unable to provide a counterexample.
 

### 2017-02-02 hscc2017/paper.tex
reviewed 4.3 Results

--- 2017-02-02 hscc2017/paper.tex
@@
 Section~\ref{synthesis-elements} holds and the two-stage verification 
-engine %inductive back-end 
-is able to find a stable solution in less than five minutes.  This is possible if the
-inductive solutions need to be refined with few counterexamples and
-increases of the fixed-point precision.  However, two benchmarks in our set
-required too many counterexamples to refine their solution \textcolor{red}{
-(marked with $^*$ in Table~\ref{tab:results})}.  
+engine is able to find a stable solution in less than one minute for half
+of the benchmarks. This is possible if the inductive solutions need to be 
+refined with few counterexamples and increases of the fixed-point precision.  
+\textcolor{red}{However, two benchmarks in our set required too many counterexamples 
+to refine their solution (marked with $^*$ in Table~\ref{tab:results}).  
 In these cases, the one-stage engine is able to complement the two-stage 
@@
 experiments, leading to the one-stage engine timing out on the majority of
-our benchmarks. \textcolor{red}{Table~\ref{tab:results} only lists the faster of the two
+our benchmarks. Table~\ref{tab:results} only lists the faster of the two
 verification engines for each benchmark, which in $12$ out of $15$
@@
 5  & $G_3$  & SatelliteB2
-            &   3 &   7 & 36,s    & \xmark     \\
+            &   3 &   7 & 36\,s    & \xmark     \\
 6  & $G_3$  & SatelliteB2$^\dagger$
@@
             &  16 &   4 & 1128\,s  & \xmark   \\
-21 &$G_{12b}$& a\_ST2\_IMPL2
+21 &$G_{12b}$& a\_ST2\_IMPL2$^{*}$
             &  16 &   8 & \xmark  & \xmark    \\
@@
             &  16 &  12 & 15183\,s & \xmark   \\ 
-23 &$G_{12c}$& a\_ST3\_IMPL1
+23 &$G_{12c}$& a\_ST3\_IMPL1$^{*}$
             &  16 &   4 & \xmark & \xmark   \\\hline

### 2017-02-02 hscc2017/paper.tex
Adapted engine results discussion
Discussion section referred to benchmarks which no longer time out.

@@
 refined with few counterexamples and increases of the fixed-point precision.  
-\textcolor{red}{However, two benchmarks in our set required too many counterexamples 
-to refine their solution (marked with $^*$ in Table~\ref{tab:results}).  
-In these cases, the one-stage engine is able to complement the two-stage 
-approach and synthesize a solution instead, albeit with significantly larger run-times.  
-This performance difference is due to the fact that the one-stage verification engine does
-not take advantage of the inductive conjecture inherent to CEGIS, but
-instead fully explores the counterexample space.  The result is a
-performance difference of at least two orders of magnitude in our
-experiments, leading to the one-stage engine timing out on the majority of
-our benchmarks. Table~\ref{tab:results} only lists the faster of the two
-verification engines for each benchmark, which in $12$ out of $15$
-benchmarks is the two-stage one}.
+However, the benchmark \emph{SatelliteB2} with uncertainty
+required too many counterexamples to refine its solution.  
+For this particular case, the one-stage engine is able to complement the
+two-stage approach and synthesize a solution instead.  It is important to
+reiterate that the one-stage verification engine does not take advantage of
+the inductive conjecture inherent to CEGIS, but instead fully explores the
+counterexample space in one SAT instance.  As expected, this approach is
+significantly slower on average and is only useful for benchmarks where
+the CEGIS approach requires too many counterexample refinement iterations
+such that exploring all counterexamples in a single SAT instance performs better.
+Our results suggest an average performance difference of at least two orders
+of magnitude between the two engines, leading to the one-stage engine timing
+out on the majority of our benchmarks.  Table~\ref{tab:results}
+lists the results for both engines independently, where in $16$ out of $23$
+benchmarks the two-stage engine is faster.
 
@@
 \# & Plant  & Benchmark                  & $I$ & $F$
-   & 1-step & 2-step
+   & 2-step & 1-step
     \\\hline\hline

### 2017-02-02 hscc2017/paper.tex
Updated experiment.tar.gz URL
Moved experiment environment to cprover.org.

@@
 the results, all benchmarks and the \tool tool, is provided in the
-footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}\footnote{CBMC version: \url{https://github.com/diffblue/cbmc/archive/7a6cec1dd0eb8843559591105235f1f2c4678801.zip}}
+footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}}\footnote{CBMC version: 7a6cec1dd0eb8843559591105235f1f2c4678801}
 

### 2017-02-02 hscc2017/paper.tex
replaced "2-step" and "1-step" by "2-stage" and "1-stage"

@@
 
-This section is split into three parts. Section~\ref{experimental-setup}
-discusses the experimental setup and our benchmarks, while
-Section~\ref{experimental-objectives} describes the experimental objectives. 
-Section~\ref{experimental-results} presents the experimental results
-obtained on the benchmarks with our tool \tool.
+%This section is split into three parts. Section~\ref{experimental-setup}
+%discusses the experimental setup and our benchmarks, while
+%Section~\ref{experimental-objectives} describes the experimental objectives. 
+%Section~\ref{experimental-results} presents the experimental results
+%obtained on the benchmarks with our tool \tool.
 
@@
 \# & Plant  & Benchmark                  & $I$ & $F$
-   & 2-step & 1-step
+   & 2-stage & 1-stage
     \\\hline\hline

### 2017-02-02 hscc2017/paper.tex
added unique ID for each plant

@@
     \\\hline\hline
-1  & $G_1$  & CrsControl02
+1  & $G_{1a}$  & CrsControl02
             &   4 &  16 & 12\,s   & 67\,s     \\
-2  & $G_1$  & CrsControl02$^\dagger$
+2  & $G_{1b}$  & CrsControl02$^\dagger$
             &   4 &  16 & 14600\,s   & 52\,s     \\
-3  & $G_2$  & SpgMsDamper
+3  & $G_{2a}$  & SpgMsDamper
             &  15 &  16 & 52\,s   & 318\,s     \\
-4  & $G_2$  & SpgMsDamper$^\dagger$
+4  & $G_{2b}$  & SpgMsDamper$^\dagger$
             &  15 &  16 & \xmark  & \xmark    \\
-5  & $G_3$  & SatelliteB2
+5  & $G_{3a}$  & SatelliteB2
             &   3 &   7 & 36\,s    & \xmark     \\
-6  & $G_3$  & SatelliteB2$^\dagger$
+6  & $G_{3b}$  & SatelliteB2$^\dagger$
             &   3 &   7 & \xmark  & 4111\,s  \\
-7  & $G_3$  & SatelliteC2
+7  & $G_{3c}$  & SatelliteC2
             &   3 &   5 & 3\,s    & 205\,s    \\
-8  & $G_3$  & SatelliteC2$^\dagger$
+8  & $G_{3d}$  & SatelliteC2$^\dagger$
             &   3 &   5 & 50\,s  & 1315\,s    \\

### 2017-02-02 hscc2017/paper.tex
explicitly stated the benchmark
updated median time for 2-stage verification engine

@@
   stable controllers for a set of intricate benchmarks taken from the
-  literature: the median runtime for our benchmark set is $197$\,s, i.e.,
+  literature: the median runtime for our benchmark set with the two-stage 
+  verification engine is $52$\,s, i.e.,
   half of the controllers can be synthesized in less than five minutes.
@@
 refined with few counterexamples and increases of the fixed-point precision.  
-However, the benchmark \emph{SatelliteB2} with uncertainty
-required too many counterexamples to refine its solution.  
+However, the benchmark \emph{SatelliteB2} with uncertainty (represented by $G_{3b}$
+in Table~\ref{tab:results}) required too many counterexamples to refine its solution.  
 For this particular case, the one-stage engine is able to complement the
@@
 
-The median run-time for our benchmark set is $48$\,s, implying that \tool
+The median run-time for our benchmark set with the two-stage verification engine is 
+$52$\,s, implying that \tool
 can synthesize half of the controllers in less than one minute. Overall,

### 2017-02-02 hscc2017/paper.tex
keep the same standard about capital letters for the subsection heading
marked the faster engine for each benchmark as bold in Table 1

@@
 \isbn{978-1-4503-4590-3/17/04}\acmPrice{\$15.00.}
-\doi{TDB.}
+\doi{TBD.}
 
@@
 
-\subsection{Architecture of the program synthesizer}
+\subsection{Architecture of the Program Synthesizer}
 \label{synthesizer-general}
@@
 
-\subsection{Synthesis for control}
+\subsection{Synthesis for Control}
 \label{synthesis-elements}
@@
 
-\subsection{Program synthesis for the example}
+\subsection{Program Synthesis for the Example}
 %
@@
 1  & $G_{1a}$  & CrsControl02
-            &   4 &  16 & 12\,s   & 67\,s     \\
+            &   4 &  16 & \textbf{12\,s}   & 67\,s     \\
 2  & $G_{1b}$  & CrsControl02$^\dagger$
-            &   4 &  16 & 14600\,s   & 52\,s     \\
+            &   4 &  16 & 14600\,s   & \textbf{52\,s}     \\
 3  & $G_{2a}$  & SpgMsDamper
-            &  15 &  16 & 52\,s   & 318\,s     \\
+            &  15 &  16 & \textbf{52\,s}   & 318\,s     \\
 4  & $G_{2b}$  & SpgMsDamper$^\dagger$
@@
 5  & $G_{3a}$  & SatelliteB2
-            &   3 &   7 & 36\,s    & \xmark     \\
+            &   3 &   7 & \textbf{36\,s}    & \xmark     \\
 6  & $G_{3b}$  & SatelliteB2$^\dagger$
-            &   3 &   7 & \xmark  & 4111\,s  \\
+            &   3 &   7 & \xmark  & \textbf{4111\,s}  \\
 7  & $G_{3c}$  & SatelliteC2
-            &   3 &   5 & 3\,s    & 205\,s    \\
+            &   3 &   5 & \textbf{3\,s}    & 205\,s    \\
 8  & $G_{3d}$  & SatelliteC2$^\dagger$
-            &   3 &   5 & 50\,s  & 1315\,s    \\
+            &   3 &   5 & \textbf{50\,s}  & 1315\,s    \\
 9  & $G_4$  & Cruise
@@
 10 & $G_5$  & DC Motor
-            &   3 &   7 & 1\,s  & 10\,s    \\
+            &   3 &   7 & \textbf{1\,s}  & 10\,s    \\
 11 & $G_6$  & DC servomotor
-            &   4 &  11 & 46\,s  & \xmark    \\
+            &   4 &  11 & \textbf{46\,s}  & \xmark    \\
 12 & $G_7$  & Doyleetal
-            &   4 &  11 & 8769\,s  & \xmark    \\
+            &   4 &  11 & \textbf{8769\,s}  & \xmark    \\
 13 & $G_8$  & Helicopter
-            &   3 &   7 & 44\,s  & \xmark    \\
+            &   3 &   7 & \textbf{44\,s}  & \xmark    \\
 14 & $G_9$  & Pendulum
-            &   3 &   7 & 1\,s  & 14826\,s    \\
+            &   3 &   7 & \textbf{1\,s}  & 14826\,s    \\
 15 &$G_{10}$& Suspension
-            &   3 &   7 & 1\,s  & 5\,s    \\
+            &   3 &   7 & \textbf{1\,s}  & 5\,s    \\
 16 &$G_{11}$& Tapedriver
@@
 17 &$G_{12a}$& a\_ST1\_IMPL1
-            &  16 &   4 & 11748\,s & \xmark   \\
+            &  16 &   4 & \textbf{11748\,s} & \xmark   \\
 18 &$G_{12a}$& a\_ST1\_IMPL2
-            &  16 &   8 & 351\,s  & \xmark   \\
+            &  16 &   8 & \textbf{351\,s}  & \xmark   \\
 19 &$G_{12a}$& a\_ST1\_IMPL3
-            &  16 &  12 & 8772\,s   & \xmark   \\
+            &  16 &  12 & \textbf{8772\,s}   & \xmark   \\
 20 &$G_{12b}$& a\_ST2\_IMPL1
-            &  16 &   4 & 1128\,s  & \xmark   \\
+            &  16 &   4 & \textbf{1128\,s}  & \xmark   \\
 21 &$G_{12b}$& a\_ST2\_IMPL2$^{*}$
@@
 22 &$G_{12b}$& a\_ST2\_IMPL3
-            &  16 &  12 & 15183\,s & \xmark   \\ 
+            &  16 &  12 & \textbf{15183\,s} & \xmark   \\ 
 23 &$G_{12c}$& a\_ST3\_IMPL1$^{*}$
@@
 
-The median run-time for our benchmark set with the two-stage verification engine is 
-$52$\,s, implying that \tool
-can synthesize half of the controllers in less than one minute. Overall,
-the average synthesis time amounts to approximately $42$ minutes.  We
+Considering the faster engine for each benchmark (marked as bold in Table~\ref{tab:results}), 
+the median run-time amounts to $48$\,s, implying that \tool can synthesize half of the controllers 
+in less than one minute. Overall, the average fastest synthesis time considering
+both engines is approximately $42$ minutes.  We
 consider these times short enough to be of practical use to control
@@
 %--------------------------------------
-\subsection{Threats to validity}
+\subsection{Threats to Validity}
 %--------------------------------------

### 2017-02-02 hscc2017/paper.tex
updated experimental results

@@
 refined with few counterexamples and increases of the fixed-point precision.  
-However, the benchmark \emph{SatelliteB2} with uncertainty (represented by $G_{3b}$
-in Table~\ref{tab:results}) required too many counterexamples to refine its solution.  
+However, the benchmark \emph{SatelliteB2} with uncertainty ($G_{3b}$)
+required too many counterexamples to refine its solution.  
 For this particular case, the one-stage engine is able to complement the
@@
     \\\hline\hline
-1  & $G_{1a}$  & CrsControl02
+1  & $G_{1a}$  & CruiseControl02
             &   4 &  16 & \textbf{12\,s}   & 67\,s     \\
-2  & $G_{1b}$  & CrsControl02$^\dagger$
+2  & $G_{1b}$  & CruiseControl02$^\dagger$
             &   4 &  16 & 14600\,s   & \textbf{52\,s}     \\
@@
             &   3 &   7 & 1\,s  & 1\,s    \\
-10 & $G_5$  & DC Motor
+10 & $G_5$  & DCMotor
             &   3 &   7 & \textbf{1\,s}  & 10\,s    \\
-11 & $G_6$  & DC servomotor
+11 & $G_6$  & DCServomotor
             &   4 &  11 & \textbf{46\,s}  & \xmark    \\
@@
             &  16 &   4 & \textbf{1128\,s}  & \xmark   \\
-21 &$G_{12b}$& a\_ST2\_IMPL2$^{*}$
+21 &$G_{12b}$& a\_ST2\_IMPL2
             &  16 &   8 & \xmark  & \xmark    \\
@@
             &  16 &  12 & \textbf{15183\,s} & \xmark   \\ 
-23 &$G_{12c}$& a\_ST3\_IMPL1$^{*}$
+23 &$G_{12c}$& a\_ST3\_IMPL1
             &  16 &   4 & \xmark & \xmark   \\\hline
@@
 in $19$ out of the $23$ benchmarks, and can be complemented using the
-one-stage engine for additional benchmarks, where the inductive
+one-stage engine, which is faster for two benchmarks where the inductive
 conjectures fail.  Both verification engines together enable controller

### 2017-02-03 hscc2017/paper.tex

@@
   stable controllers for a set of intricate benchmarks taken from the
-  literature: the median runtime for our benchmark set with the two-stage 
-  verification engine is $52$\,s, i.e.,
-  half of the controllers can be synthesized in less than five minutes.
+  literature: the median runtime for our benchmark set considering the faster 
+	engine is $48$\,s, i.e., half of the controllers can be synthesized in less than one minute.
 
@@
 %
-\red{[what is the relationship between the deltas in this formula, and those in the previous paragraph? please clarify and hopefully simplify formulae. ]}
+%\red{[what is the relationship between the deltas in this formula, and those in the previous paragraph? please clarify and hopefully simplify formulae. ]}
 which will be represented by the following transfer function:
@@
 %
-\red{[why is this condition on the order of the polynomials raised only now? how is it used later?]}
+%\red{[why is this condition on the order of the polynomials raised only now? how is it used later?]}
 Due to the nature of the methods we use for the stability check, we require
@@
 the plant itself (\blue{all other errors described in this paper are ensured to
-fulfil this property in our implementation}\red{[have we later argued that this is indeed the case?]}) 
-\blue{and that enter the plant linearly}.
+fulfil this property in our implementation}
+%\red{[have we later argued that this is indeed the case?]}) 
+%\blue{and that enter the plant linearly}.
 

### 2017-02-03 hscc2017/paper.tex
cut

@@
 out on the majority of our benchmarks.  Table~\ref{tab:results}
-lists the results for both engines independently, where in $16$ out of $23$
+lists the results for both engines, where in $16$ out of $23$
 benchmarks the two-stage engine is faster.
@@
 There is no technique in the existing literature for automatic synthesis of
-fixed-point digital controllers that considers FWL effects.  Parameter
-synthesis tools such as~\cite{cimatti2013parameter} use bounded model
-checking and fixed-point computations to compute parameters based on
-user-defined specifications, but they often operate in the continuous domain
-and have no direct means of evaluating robustness.
+fixed-point digital controllers that considers FWL effects.
+%  Parameter
+%synthesis tools such as~\cite{cimatti2013parameter} use bounded model
+%checking and fixed-point computations to compute parameters based on
+%user-defined specifications, but they often operate in the continuous domain
+%and have no direct means of evaluating robustness.
 

### 2017-02-07 hscc2017/paper.tex
SC^2
nudges

@@
 Plants%
-\thanks{Supported by EPSRC grant EP/J012564/1
-and ERC project 280053 (CPROVER).}}
+\thanks{Supported by EPSRC grant EP/J012564/1,
+ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}}
 
@@
 %
-Modern control is implemented with digital microcontrollers, which are
-designed to work in an embedded environment, within a dynamical plant that
-represents physical components.
+Modern control is implemented with digital microcontrollers, embedded within
+a dynamical plant that represents physical components.
 %
@@
 complete range of approximations, including time discretization,
-quantization effects, and finite-precision arithmetic and their related
+quantization effects, and finite-precision arithmetic and its
 rounding errors.
@@
 
-\keywords{Control synthesis, CEGIS, finite word length, time sampling, quantization, interval analysis}
+\keywords{Control synthesis, CEGIS, finite word length, time sampling, quantization}
 
@@
 environmental control and robotics~\cite{astrom1997computer, Franklin15}.
-Correct and sound control is non-trivial, however. The problem is exacerbated by
+Correct control is non-trivial, however. The problem is exacerbated by
 artefacts specific to digital control, such as the effects of
@@
 able to generate programs for highly non-trivial specifications with a very
-high degree of automation.  Modern CEGIS engines combine automated testing,
-genetic algorithms and SMT-based automated
-reasoning~\cite{DBLP:conf/lpar/DavidKL15, DBLP:conf/cav/0001A14}.
-
-By applying a state-of-the-art CEGIS engine we are now able to present a
+high degree of automation.  Modern synthesis engines combine automated
+testing, genetic algorithms and SMT-based automated
+reasoning~\cite{DBLP:conf/lpar/DavidKL15, DBLP:journals/corr/AlurFSS16a}.
+
+By applying a state-of-the-art synthesis engine we are now able to present a
 tool that automatically \emph{generates} digital controllers for a given

### 2017-02-07 hscc2017/paper.tex
wording

@@
 
-Our work addresses challenging aspects of the control synthesis
-problem.  We perform digital control synthesis over a hybrid model, where
-the plant exhibits continuous behavior whereas the controller operates in
-discrete time and over a quantized domain.  Inspired by a classical
+Our work addresses challenging aspects of the control synthesis problem.  We
+perform digital control synthesis over a hybrid model, where the plant
+exhibits continuous behavior whereas the controller operates in discrete
+time and over a quantized domain.  Inspired by a classical
 approach~\cite{astrom1997computer}, we translate the problem into a single
@@
 digitization effects, we have modeled a digital equivalent of the plant by
-evaluating the quantizers effects (A/D and D/A converters) as time
+evaluating the effects of the quantizers (A/D and D/A converters) as time
 discretization elements with quantization noise.  The resulting closed-loop

### 2017-02-08 hscc2017/paper.tex
Clarification of vector rep

@@
 \begin{equation}
-\Delta{\vec{P}}=[\Delta{n}_{0}\ \Delta{n}_{1}\ \hdots \ \Delta{n}_{M}\ \Delta{d}_{0}\ \Delta{d}_{1}\ \hdots\ \Delta{d}_{N}\ ]^T \; 
+\Delta{\vec{P}}\in \mathbb{R}^{N+M+2}=[\Delta{n}_{0}\ \hdots \ \Delta{n}_{M}\ \Delta{d}_{0}\ \hdots\ \Delta{d}_{N}\ ]^T \; 
 \label{eq:delta_coefficients}
@@
 %
-we write $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$.  
-\red{[confusing: we mix notations on abstract polynomials with those used for the plant above - the orders of the two are different ($N$ vs $N_G$) - please use the latter.]}
+we write $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$, with
+\begin{align*}
+\vec{G} \in \mathbb{R}^{N_G+M_G+2}&=[b_{0}\ \hdots \ b_{M_G}\ a_{0}\ \hdots\ a_{N_G}\ ]^T\\
+\Delta{\vec{G}}\in \mathbb{R}^{N_G+M_G+2}&=[\Delta{b}_{0}\ \hdots \ \Delta{b}_{M_G}\ \Delta{a}_{0}\ \hdots\ \Delta{a}_{N_G}\ ]^T 
+\end{align*}
 In the following we will

### 2017-02-08 hscc2017/paper.tex
removed delta_qG

@@
 %
-we write $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$, with
-\begin{align*}
-\vec{G} \in \mathbb{R}^{N_G+M_G+2}&=[b_{0}\ \hdots \ b_{M_G}\ a_{0}\ \hdots\ a_{N_G}\ ]^T\\
-\Delta{\vec{G}}\in \mathbb{R}^{N_G+M_G+2}&=[\Delta{b}_{0}\ \hdots \ \Delta{b}_{M_G}\ \Delta{a}_{0}\ \hdots\ \Delta{a}_{N_G}\ ]^T 
-\end{align*}
+we write
+\begin{align}
+\label{eq:hatgvector}
+\vec{\hat{G}}&=\vec{G}+\Delta{\vec{G}}\\
+\vec{G} \in \mathbb{R}^{N_G+M_G+2}&=[b_{0}\ \hdots \ b_{M_G}\ a_{0}\ \hdots\ a_{N_G}\ ]^T\nonumber \\
+\Delta{\vec{G}}\in \mathbb{R}^{N_G+M_G+2}&=[\Delta{b}_{0}\ \hdots \ \Delta{b}_{M_G}\ \Delta{a}_{0}\ \hdots\ \Delta{a}_{N_G}\ ]^T\nonumber
+\end{align}
 In the following we will
@@
 represented by~$\Delta_p \vec{G}$
-%
-%=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$
-%
-and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is
-represented as an additive output noise~$\nu(z)$.  
-\red{[We have recast the model as in Figure 2, but never defined $\nu$ and never use it later - retain the two separate noise contributions as in Figure 1.]}
-%, thus
-%$\hat{Y}(z)=Y(z)+\nu(z)$.  The measurement noise $\nu(k)$ is enough for
-%represent both quantization noises ($\nu_{1}$ and $\nu_{2}$) what can be
-%obtained reorganizing the equations~\ref{eq:outputfunctions}:
-%%
-%\begin{equation}
-%\label{eq:outputfunctions2}
-%\hat{Y}(z)=H_{1}R(z)+H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z),
-%\end{equation}
-%%
-%where $H_{1}R(z)$ is exactly equal to $Y(z)$ without quantization noise effects, thus:
-%%
-%\begin{equation}
-%\nu(z)=H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z).
-%\end{equation}
+and the effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is
+seen as additive noise.
 
@@
    \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
+   \& \node[circle,add={}{+}{+}{}] (circle2) {};
+   \node[draw=none] (nu2) at ([yshift=1cm]circle2)  {$\nu_2(z)$};
    \& \node[rectangle,draw,
@@
 
-   \& \node[circle,add={}{+}{+}{}] (circle2) {};
-%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
-   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
+   \& \node[circle,add={}{+}{+}{}] (circle3) {};
+   \node[draw=none] (nu1) at ([yshift=1cm]circle3)  {$\nu_1(z)$};
    \& \coordinate (aux1);
@@
    \& 
+   \&
    \& \coordinate (aux2);\\
@@
   \path[->] (r) edge (circle.west);
-  \path[->] (nu) edge (circle2.north);
+  \path[->] (nu2) edge (circle2.north);
+  \path[->] (nu1) edge (circle3.north);
   \path[->] (aux1) edge (yz);
@@
    (circle.east) edge (cz)
-   (cz.east) edge (gs.west)
-   (gs.east) edge (circle2.west)
-   (circle2.east) edge (aux1.west)
+   (cz.east) edge (circle2.west)
+   (circle2.east) edge (gs.west)
+   (gs.east) edge (circle3.west)
+   (circle3.east) edge (aux1.west)
    (aux1.south) edge (aux2.north)
@@
 parametric uncertainties related to modeling errors, and uncertainties
-introduced by quantizations in sampling and holding process, i.e., ADC and
-DAC conversions \red{[but the sample-and-hold happens only in the DAC, not in the ADC - right?]}\blue{[the sample-and-hold is on the ADC, the DAC is ZOH.
-I would just put `quantizations in the ADC and DAC conversions']}.
-These sources are assumed to be non-deterministic,
+introduced by quantizations in the ADC and
+DAC conversions.  These sources are assumed to be non-deterministic, 
 which poses no further restriction to our model, thus, the uncertain model
-may be rewritten as a vector of coefficients in the z-domain using equations
-(\ref{eq:coefficients}) and (\ref{eq:delta_coefficients})
+may be rewritten as a vector of coefficients in the z-domain using equation
+(\ref{eq:hatgvector})
 %
@@
 \label{eq:complete_unc_model}
-\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q \vec{G},
+\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G},
 \end{equation}
@@
 where $\Delta_p \vec{G}$ is the term that corresponds to the parametric
-uncertainties and $\Delta_q \vec{G}$ is the term that reflects the
-quantization effects on the plant model, {\it i.e.} $\Delta_q \vec{G}$ is 
-a model that incorporates the effects of $\nu_1,\nu_2$ in $\vec{\hat{G}}$ to 
-investigate the consequences in the stability of system, once our stability 
-analysis is based on polynomial coefficients and not over signals.
+uncertainties. Notice that the quantization noise is additive, which means
+it does not affect the transfer function. Instead, we prove that the system
+is stable given these non-deterministic noise inputs.
 
@@
 $$
-\hat{G}(z) =\frac{\hat{G}_n(z)}{\hat{G}_d(z)}: \vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q 
-\vec{G} \text{\quad(from~\ref{eq:coefficients},\ref{eq:delta_coefficients})}.
+\hat{G}(z) =\frac{\hat{G}_n(z)}{\hat{G}_d(z)}: \vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}
+\text{\quad(from~\ref{eq:coefficients},\ref{eq:delta_coefficients})}.
 $$
@@
 ($\nu_{1}$ and $\nu_{2}$) and FWL effects in the control software.  Note
-that the model for plant uncertainty due to quantization noise (i.e.,
-$\Delta_q \vec{G}$) may be disregarded if the conditions on
+that the model for quantization noise enters as a signal to be stabilized (i.e.,
+the noise may be disregarded if the conditions on
 Proposition~\ref{prop:eq_int_stab} are satisfied and if the quantization

### 2017-02-08 hscc2017/paper.tex
Nudge to align CAV FWL notation

@@
 and assume that there exists a function
-$\mathit{FWL}_n[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$,
-which applies the FWL effects to a polynomial, with an equivalent $\mathit{FWL}_{n,m}[\cdot]:\mathcal{P}^{n,m}\rightarrow \mathcal{P}^{n,m}\langle I,F \rangle$ that applies the same effect to a ratio of polynomials, where
+$\mathcal{F}_n\langle I,F \rangle(\cdot):\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$,
+which applies the FWL effects to a polynomial, with an equivalent $\mathcal{F}_{n,m}\langle I,F \rangle(\cdot):\mathcal{P}^{n,m}\rightarrow \mathcal{P}^{n,m}\langle I,F \rangle$ that applies the same effect to a ratio of polynomials, where
 $\mathcal{P}^{n}$ is the
@@
 \begin{equation}
-\hat{C}(z)=\mathit{FWL}_{M_C,N_C}[C(z)]=\frac{\mathit{FWL}_{M_C}[C_n(z)]}{\mathit{FWL}_{N_C}[C_d(z)]}.
+\hat{C}(z)=\mathcal{F}_{M_C,N_C}\langle I,F \rangle(C(z))=\frac{\mathcal{F}_{M_C}\langle I,F \rangle(C_n(z))}{\mathcal{F}_{N_C}\langle I,F \rangle(C_d(z))}.
 \end{equation}
@@
 Figure~\ref{fig:sampledsystem} with a FWL implementation of the digital
-controller $\hat{C}(z) =\mathit{FWL}_{M_C,N_C}[C(z)]$ and uncertain discrete
+controller $\hat{C}(z) =\mathcal{F}_{M_C,N_C}\langle I,F \rangle(C(z))$ and uncertain discrete
 model of the plant
@@
 \label{eq:internal_stab_lemma}
-S(z)=\mathit{FWL}_{M_C}[C_n(z)]\hat{G}_n(z)+\mathit{FWL}_{N_C}[C_d(z)]\hat{G}_d(z);
+S(z)=\mathcal{F}_{M_C}\langle I,F \rangle(C_n(z))\hat{G}_n(z)+\mathcal{F}_{N_C}\langle I,F \rangle(C_d(z))\hat{G}_d(z);
 \end{equation}
-\item the direct loop product $\mathit{FWL}_{M_C,N_C}[C(z)]\cdot \hat{G}(z)$ has no pole-zero cancellation on or outside the unit circle.
+\item the direct loop product $\mathcal{F}_{M_C,N_C}\langle I,F \rangle(C(z))\cdot \hat{G}(z)$ has no pole-zero cancellation on or outside the unit circle.
 \end{itemize}
@@
 %plant family $\mathfrak{G}$ using $g_0$ and $\Delta{g}\%$, which are
-%provided in Step $1$.  DSVerifier then formulates $\mathit{FWL}[\cdot]$ in
+%provided in Step $1$.  DSVerifier then formulates $\mathcal{F}\langle I,F \rangle(\cdot)$ in
 %Step B using implementation details provided from Steps $2$ and $3$, and
-%then computes $\mathit{FWL}[c_0]$ in Step C.  Thus, DSVerifier builds an
+%then computes $\mathcal{F}\langle I,F \rangle(c_0)$ in Step C.  Thus, DSVerifier builds an
 %intermediate ANSI-C code for the digital system implementation, which is
@@
 \label{FWL_tf}
-&f^p : \mathbb{R} \rightarrow  \mathbb{R}\langle I_p,F_p \rangle \triangleq \tilde x = f^p(x) : \tilde x=x-(x\bmod\tilde x)\\
-&\mathit{FWL}_n^p[P \in \mathcal{P}] = \tilde P \in \mathcal{P}^{n}\langle I_p,F_p \rangle : c_i \in \vec{P} \wedge \tilde c_i \in \vec{\tilde{P}}=f^p(c_i)  \nonumber
+\mathcal{F}&\langle I_p,F_p \rangle : \mathbb{R} \rightarrow  \mathbb{R}\langle I_p,F_p \rangle\\
+&\triangleq \tilde x = \mathcal{F}\langle I_p,F_p \rangle(x) : \tilde x=x-(x\bmod\tilde x)\nonumber\\
+\mathcal{F}_n&\langle I_p,F_p \rangle(P \in \mathcal{P}) \\
+&=\tilde P \in \mathcal{P}^{n}\langle I_p,F_p \rangle : c_i \in \vec{P} \wedge \tilde c_i \in \vec{\tilde{P}}=\mathcal{F}\langle I_p,F_p \rangle(c_i)  \nonumber
 \end{align}
 %
-we calculate $\tilde G(z)=\mathit{FWL}_{M_G,N_G}^p(\hat{G}(z))$
+we calculate $\tilde G(z)=\mathcal{F}_{M_G,N_G}\langle I_p,F_p \rangle(\hat{G}(z))$
 %

### 2017-02-08 hscc2017/paper.tex
conclusion

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions} \label{sec:conclusions}
+\section{Conclusions}\label{sec:conclusions}
 
@@
 interval sets as well as FWL uncertainties in digital controllers.  The
-present approach is novel in the control system literature in that it puts
-forward a fully automated synthesis approach that is algorithmically and
-numerically sound.  In particular, \tool marks the first use of the CEGIS
-paradigm, which handles plants with uncertain models and FWL effects over
-the digital controller.  Note that implementing this architecture
-efficiently requires adjusting the traditional CEGIS refinement loop to the
-use of a two-stage verification engine: here the first stage performs fast,
-but potentially unsound fixed-point operations, whereas the second stage
-restores soundness by validating the operations performed by the first stage
-using interval arithmetic.  Our experimental results show that \tool is able
-to synthesize stable controllers in most benchmarks within a reasonable
-amount of time fully automatically.  Future work will be the extension of
-this CEGIS-based approach to further classes of systems, including those
-with state space.  We will also consider performance requirements while
-synthesizing the digital controller.
+novelty in our approach is that it is fully automated and algorithmically
+and numerically sound.  In particular, \tool marks the first use of the
+CEGIS that handles plants with uncertain models and FWL effects over the
+digital controller.  Implementing this architecture efficiently requires
+adjusting the traditional CEGIS refinement loop to the use of a two-stage
+verification engine: here, the first stage performs fast, but potentially
+unsound fixed-point operations, whereas the second stage restores soundness
+by validating the operations performed by the first stage using interval
+arithmetic.  Our experimental results show that \tool is able to synthesize
+stable controllers in most benchmarks within a reasonable amount of time
+fully automatically.  Future work will be the extension of this CEGIS-based
+approach to further classes of systems, including those with state space. 
+We will also consider performance requirements while synthesizing the
+digital controller.
 

### 2017-02-08 hscc2017/paper.tex
PTF comment

@@
 operations, and it includes the ZOH dynamics in the $(1-z^{-1})$ term, which
-is sufficient for stability studies over $G(s)$ \red{[we need to clarify the last sentence - why is it sufficient, where is this fact stated?]}.
+is sufficient for stability studies over $G(s)$~\cite{fadali}, {\it i.e.}, if there is any unstable pole domain ($\Re\{s\}\geq 0$), the pulse transfer function~\ref{eq:pulsetf} will also present the same number of unstable poles ($|z|<1$)~\cite{Franklin15}.
 

### 2017-02-10 hscc2017/poster.tex
poster early draft

--- 2017-02-08 hscc2017/paper.tex
@@
 
-%\usetikzlibrary{decorations}
-%\usetikzlibrary{decorations.pathmorphing}
-
 \newcommand{\blue}[1]{{\color{blue}#1}}
@@
 \newcommand{\green}[1]{{\color{green}#1}}
-%\newcommand{\blue}[1]{}
-%\newcommand{\red}[1]{}
-%\newcommand{\green}[1]{}
 
@@
 
-%\subtitle{[Extended Abstract]
-%\titlenote{A full version of this paper is available as
-%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
-%\LaTeX$2_\epsilon$\ and BibTeX} at
-%\texttt{www.acm.org/eaddress.htm}}}
-%
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
-
-%\numberofauthors{8} %  in this sample file, there are a *total*
-% of EIGHT authors. SIX appear on the 'first-page' (for formatting
-% reasons) and the remaining two appear in the \additionalauthors section.
-%
-%% \author{
-%% % You can go ahead and credit any number of authors here,
-%% % e.g. one 'row of three' or two rows (consisting of one row of three
-%% % and a second row of one, two or three).
-%% %
-%% % The command \alignauthor (no curly braces needed) should
-%% % precede each author name, affiliation/snail-mail address and
-%% % e-mail address. Additionally, tag each line of
-%% % affiliation/address with \affaddr, and tag the
-%% % e-mail address with \email.
-%% %
-%% % 1st. author
-%% \alignauthor
-%% Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
-%%        \affaddr{Institute for Clarity in Documentation}\\
-%%        \affaddr{1932 Wallamaloo Lane}\\
-%%        \affaddr{Wallamaloo, New Zealand}\\
-%%        \email{trovato@corporation.com}
-%% % 2nd. author
-%% \alignauthor
-%% G.K.M. Tobin\titlenote{The secretary disavows
-%% any knowledge of this author's actions.}\\
-%%        \affaddr{Institute for Clarity in Documentation}\\
-%%        \affaddr{P.O. Box 1212}\\
-%%        \affaddr{Dublin, Ohio 43017-6221}\\
-%%        \email{webmaster@marysville-ohio.com}
-%% }
-
 \author{Alessandro Abate$^{1}$, Iury Bessa$^{2}$, Dario Cattaruzza$^{1}$, Lucas Cordeiro$^{1,2}$, \\ 
@@
 Modern control is implemented with digital microcontrollers, embedded within
-a dynamical plant that represents physical components.
-%
-We present a new algorithm based on counter\-example guided inductive
-synthesis that automates the design of digital controllers that are
-correct by construction.  The synthesis result is sound with respect to the
-complete range of approximations, including time discretization,
-quantization effects, and finite-precision arithmetic and its
-rounding errors.
-%
-We have implemented our new algorithm in a tool called \tool, and are able
-to automatically generate stable controllers for a set of intricate plant
-models taken from the literature within minutes.
-%
-\end{abstract}
-
-%
-%  Use this command to print the description
-%
-\printccsdesc
-
-% We no longer use \terms command
-%\terms{Theory}
-
-\keywords{Control synthesis, CEGIS, finite word length, time sampling, quantization}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-
-Modern implementations of embedded control systems have proliferated with the
-availability of low-cost devices that can perform highly non-trivial control
-tasks, with significant impact in numerous application areas such as
-environmental control and robotics~\cite{astrom1997computer, Franklin15}.
-Correct control is non-trivial, however. The problem is exacerbated by
-artefacts specific to digital control, such as the effects of
-finite-precision arithmetic, time discretization, and quantization noise
-introduced by A/D and D/A conversion.  Thus, the programming is a key
-barrier to broad adoption of digital control, and requires considerable
-expertise.
-
-Beyond classical a-posteriori validation procedures in digital control,
-there has been plenty of previous work aiming at \emph{verifying} a given
-controller designed by the engineer.  Recent work can show the stability of
-digital controllers with consideration of implementation aspects, i.e.,
-fixed-point arithmetic and the word length used~\cite{Bessa16}.  The authors
-of~\cite{Bessa16} exploit advances in bit-accurate verification of C
-programs to obtain a verifier for software-implemented digital control.
-
-By contrast, we leverage a very recent step-change in the scalability of
-\emph{program synthesis}.  Program synthesis engines use a program
-specification as the starting point, and subsequently generate a sequence of
-candidate programs.  The candidate programs are iteratively refined to match
-the specification more closely.  Program synthesizers that implement
-Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} are now
-able to generate programs for highly non-trivial specifications with a very
-high degree of automation.  Modern synthesis engines combine automated
-testing, genetic algorithms and SMT-based automated
-reasoning~\cite{DBLP:conf/lpar/DavidKL15, DBLP:journals/corr/AlurFSS16a}.
-
-By applying a state-of-the-art synthesis engine we are now able to present a
-tool that automatically \emph{generates} digital controllers for a given
+a dynamical plant that represents physical components. Correct control is
+non-trivial, however. The problem is exacerbated by artefacts specific to digital
+control, such as the effects of finite-precision arithmetic, time discretization,
+and quantization noise introduced by A/D and D/A conversion.  Thus, the
+programming is a key barrier to broad adoption of digital control, and requires
+considerable expertise.
+%
+We present a new algorithm based on Counter-Example Guided Inductive
+Synthesis (CEGIS) that automates the design of digital controllers for a given
 continuous plant model that are correct by construction. This approach
@@
 dramatically, and requires considerably less expertise than methodologies
-driven by verification.  Specifically, we synthesize controllers for hybrid
-closed-loop systems, i.e., software-implemented embedded controllers along
-with a model of their physical environment (the plant), that are
-\emph{stable}.  Due to the complexity of such systems, in this work we focus
-on linear models with known configurations and perform parametric synthesis
-of stabilizing digital controllers.
-
-Our work addresses challenging aspects of the control synthesis problem.  We
-perform digital control synthesis over a hybrid model, where the plant
-exhibits continuous behavior whereas the controller operates in discrete
-time and over a quantized domain.  Inspired by a classical
-approach~\cite{astrom1997computer}, we translate the problem into a single
-digital domain.  Given our primary interest in stability despite
-digitization effects, we have modeled a digital equivalent of the plant by
-evaluating the effects of the quantizers (A/D and D/A converters) as time
-discretization elements with quantization noise.  The resulting closed-loop
+driven by verification. Specifically, we soundly
+synthesize controllers for hybrid closed-loop systems, i.e., software-implemented
+embedded controllers along with a model of their physical environment (the plant),
+that are \emph{stable}, taking into consideration the effects of time-discretization
+(sampling), quantization (A/D and D/A converters), and the use of finite-precision arithmetic.
+
+\paragraph{Problem Statement}
+We only consider linear transfer function models, and require a $z$-domain transfer
+function $G(z)$ that captures all aspects of the continuous plant with a
+Laplace domain transfer function $G(s)$ and the sampling and hold process. 
+The continuous model of the plant must be discretized to obtain the
+corresponding coefficients of $G(z)$.
+
+Given a synchronized ZOH input and sample-and-hold output on the plant with
+a sample time $T$ satisfying the Nyquist criterion, the discrete pulse
+transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$
+that can be computed using the following formula:
+%
+\begin{equation}
+\label{eq:pulsetf}
+G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
+\end{equation}
+%
+For the sake of brevity, we will use the notation $G(z)$ to represent $G(z,T)$.
+
+We further consider parametric errors (tolerances) in the plant model such that
+\begin{equation}
+\label{eq:tolerancetf}
+\hat{G}(z) = G(z)+\Delta_pG(z).
+\end{equation}
+Due to the nature of the methods we use for the stability check, we require
+that the parametric errors in the plant have the same polynomial order as
+the plant itself, since tolerances of higher order would invalidate
+feedback model.
+
+Finally we consider the discretization effect of modelling the plant using Fixed Precision arithmetic
+\begin{equation}
+\label{eq:fwltf}
+\tilde{G}(z) = \mathcal{F}\langle I,F\rangle(\hat{G}(z))
+\end{equation}
+
+Where $\mathcal{F}\langle I,F\rangle(\cdot)$ is a discretizing function that truncates the coefficients of $\hat{G}(z)$ using $I$ integer bits and $F$ fractional bits.
+This last effect does not exist in the actual implementation, but it is caused by the use of fixed precision arithmetic in the synthesis and verification tools.
+The controller model has no tolerances and is already aligned with the Fixed Precision arithmetic, thus $\tilde{C}(z)=\hat{C}(z)=C(z)$.
+Notice that this is a condition on the synthesiser, which must ensure these equalities are met.
+The effects of the A/D, D/A quantizations are introduced as bounded additive uncertainties ($\nu_1(z),\nu_2(z)$) that need to be stabilized along with the plant.
+These sources are assumed to be non-deterministic,
+which poses no further restriction to our model. Notice that the quantization noise is additive, which means
+it does not affect the transfer function.
+
+The overall closed loop equation describing the system in figure \ref{fig:sampledsystem} becomes.
+\begin{equation}
+\tilde{Y}(z)=\nu_{1}(z)+\tilde{G}(z) \tilde{C}(z) R(z)+\tilde{G}(z)\nu_{2}(z)-\tilde{G}(z) \tilde{C}(z) \tilde{Y}(z)
+\end{equation}
+which will be stable if the poles in $\frac{1}{1+\hat{G}(z)\hat{C}(z)}$ remain within the unit circle.
+We use Jury's Criterion~\cite{astrom1997computer} to ensure this, thus avoiding the calculation of polynomial roots.
+The resulting closed-loop
 system is a program loop that operates on bit-vectors encoded using
@@
 
-In summary, this paper makes the following original contributions.
-%
-\begin{itemize}
-
-\item We automatically generate {\em correct-by-construction} digital
-  controllers using inductive synthesis.  Our application of program
-  synthesis is non-trivial and addresses challenges specific to control
-  systems, such as the effects of quantizers and FWL.  In particular, we
-  have found that a two-stage verification engine that continuously refines
-  the precision of the fixed-point representation of the plant yields a
-  speed-up of two orders of magnitude over a conventional one-stage
-  verification engine.
-
-\item Experimental results show that \tool is able to efficiently synthesize
-  stable controllers for a set of intricate benchmarks taken from the
-  literature: the median runtime for our benchmark set considering the faster 
-	engine is $48$\,s, i.e., half of the controllers can be synthesized in less than one minute.
-
-%% \item We exploit a CEGIS-based approach that uses inductive synthesis
-%% together with a bit-precise formal verification algorithm for synthesizing
-%% correct-by-design robust digital controllers for non-fragile closed-loop
-%% stability.
-
-%% \item Experimental results with our synthesizer show that the
-%% combination of interval arithmetic to represent the controller coefficients
-%% and a two-stage verification approach to continuously refine precision
-%% enables us to compute a parametric, sound solution for $14$ out of $15$
-%% digital stabilizing controllers for a set of continuous and discrete plants
-%% with parametric uncertainties.
-
-\end{itemize}
-
-%\begin{figure}
-%\centering
-%\resizebox{.35\textwidth}{!}{
-% \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
-%     semithick, initial text=, ampersand replacement=\&,]
-
-%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.5cm, column sep=.5cm] {
-%   \coordinate (aux0);
-%   \& \node[circle] (circle) {}; 
-%   \& \node[fill=yellow!20] (da) {{\sc D/A}}; 
-%   \& \node[fill=yellow!20] (p) {{\sc P}};
-%   \& \node[fill=yellow!20] (ad) {{\sc A/D}}; 
-%   \& \coordinate (aux1);\\
-%   \& \coordinate (aux3); 
-%   \&
-%   \&
-%   \node[fill=yellow!20] (c) {C};
-%   \& 
-%   \& \coordinate (aux2);\\
-%  };
-
-%  \path[->] (aux0) edge (circle.west);
-%  \path  
-%   (circle.east) edge (da.west)
-%   (da.east) edge (p.west)
-%   (p.east) edge (ad.west)
-%   (ad.east) edge (aux1.west)
-%   (aux1.south) edge (aux2.north)
-%   (aux2.west) edge (c.east)
-%   (c.west) edge (aux3.east); 
-%  \path[->]  (aux3.north) edge (circle.south);
-% \end{tikzpicture}
-%}
-% \caption{Closed-Loop System. \label{fig:closed-system}}
-%\end{figure}
-
-We cover preliminaries on plant discretization, the verification of
-closed-loop control systems, and stability in
-Section~\ref{sec:preliminaries}.  Our core contribution is in
-Section~\ref{sec:synthesis}: we present our CEGIS-based algorithm for
-generating stable controllers for a given plant model.  Our experimental
-setup and experimental results are given in Section~\ref{sec:experiments},
-and we discuss how we extend the state-of-the-art beyond the existing
-literature in Section~\ref{sec:related}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Preliminaries}\label{sec:preliminaries}
-
-%\blue{Please insert a figure clearly distinguishing between continuous and discretised/quantised plant - a template is in a picture sent out by Lucas late last week.
-Please introduced signals on the plot.
-
-%Let us straighten the notations next. 
-%We should have 
-%\begin{itemize}
-%\item 
-%$G(s) = \frac{s^{M_G}b_{0}+s^{M_G-1}b_{1}+...+b_{M_G}}{s^{N_G}a_{0}+s^{N_G-1}a_{1}+...+a_{N_G}}$ -- this is the physical plant, which is focus of interest and to which we refer our specifications/properties
-%\item 
-%$G(z, T) = \frac{\bar b_{0}+\bar b_{1}z^{-1}+...+\bar b_{M_G}z^{-M_G}}{\bar a_{0}+\bar a_{1}z^{-1}+...+\bar a_{N_G}z^{-N_G}}$ -- this is the time-discretised plant (notice the notation encompasses explicitly the sample time $T$; please write out explicitly the relationship between the $a_i$ and the $\bar a_i$ and likewise for the numerator's coefficients
-%(in particular, are the orders $M_G, N_G$ the same? 
-%\item 
-%we have $Y(z) = G(z,T) U(z)$; then, we introduce $\hat Y(z) \doteq Y(z) + \nu (z)$, so that 
-%$$
-%\frac{\hat Y(z)}{U(z)} = G(z,T) + \frac{\nu (z)}{U(z)} = G(z,T) + \Delta G_Q(z) \doteq \hat G(z) ,  
-%$$ 
-%where $\Delta G_Q(z)$ is an error term accounting for the quantization effects 
-%\item 
-%finally, we encompass the errors resulting from employing finite parameters representation, 
-%which we encompass in a term $\Delta G_P(z)$: is this error additive, so that we would get to a 
-%$$
-%\tilde G(z) \doteq \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z)?  
-%$$ 
-%Dario, can you write it out explicitly? In other words, if 
-%$$
-%\hat G(z) = G(z,T) + \Delta G_Q(z) = \frac{\hat b_{0}+\hat b_{1}z^{-1}+...+\hat b_{M_G}z^{-M_G}}{\hat a_{0}+\hat a_{1}z^{-1}+...+\hat a_{N_G}z^{-N_G}},  
-%$$ 
-%then what is the explicit expression of 
-%$$
-%\tilde G(z) = \frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}?
-%$$
-%(Notice that the orders $M_G, N_G$ need to be properly taken care of.)
-%\item 
-%Now, it's over the transfer function $\tilde G(z)$ that we want to synthesise the parameters of a template $C(z)$. 
-%This controller's transfer function will be subject to the same quantization and precision limits as the plant's: 
-%we need to argue that the way we do synthesis affects manipulation of quantities that relate to specific errors and be explicit about these. 
-%\item[]
-%\item 
-%An additional source of error can be related to the fact that a plant transfer function, 
-%per se a physical entity, is actually represented in a program imprecisely: 
-%this would mean that $G(s)$ is actually 
-%$$
-%G^\ast (s) \doteq \frac{s^{M_G^\ast}b_{0}+s^{M_G^\ast-1}b_{1}+...+b_{M_G}}{s^{N_G^\ast}a_{0}+s^{N_G^\ast-1}a_{1}+...+a_{N_G}}, 
-%$$ 
-%which perhaps can indeed be re-written as $G^\ast (s) = G(s) + \Delta G_P(s)$? (This proof should come from that above.) 
-%We should argue that this error is encompassed by the one derived above (or isn't it?). 
-%\end{itemize}
-%}
-
-%------------------------------------
-\subsection{Discretizing the Plant}
-\label{ssec:SandH}
-%------------------------------------
-
-The digital controllers synthesized using the algorithm we present in this
-paper are typically used in closed loops with continuous (physical) plants. 
-Thus, we consider continuous dynamics (the plant) and discrete parts (the
-digital controller).  To obtain a joint model, we fully discretize the
-continuous plant.  We briefly recall the standard foundations of this step.
-
-We only consider transfer function models, and require a $z$-domain transfer
-function $G(z)$ that captures all aspects of the continuous plant with a
-Laplace domain transfer function $G(s)$ and the sampling and hold process. 
-The continuous model of the plant must be discretized to obtain the
-corresponding coefficients of $G(z)$.
-
-%\red{[why do we discuss the ZOH at this point?]}
-
-Among the discretization methods in the literature~\cite{Franklin15}, the
-zero-order hold (ZOH) discretization is suitable for representing the sample
-and hold processes in complex systems~\cite{istepanian2012digital}.  The ZOH
-discretization models the exact effect of sampling and DAC interpolation
-over the plant.
-
-\begin{myassumption}
-%
-The sample and hold effects of the ADC and the ZOH of the DAC are synchronized,
-i.e., there is no delay between sampling the plant output at ADC and
-updating the DAC accordingly.  The DAC interpolator is an ideal ZOH. 
-%
-\end{myassumption}
-
-\begin{mylemma}\cite{astrom1997computer}
-%
-Given a synchronized ZOH input and sample-and-hold output on the plant with
-a sample time $T$ satisfying the Nyquist criterion, the discrete pulse
-transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$
-that can be computed using the following formula:
-%
-\begin{equation}
-\label{eq:pulsetf}
-G(z,T) = %\mathcal{ZOH}\left\lbrace{G(s)}\right\rbrace =
-(1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
-\end{equation}
-%
-\end{mylemma}
-%
-For the sake of brevity, we will use the notation $G(z)$ to represent the
-pulse transfer function $G(z,T)$.
-
-Lemma~\ref{eq:pulsetf} ensures that the poles and zeros match under the
-$\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$
-operations, and it includes the ZOH dynamics in the $(1-z^{-1})$ term, which
-is sufficient for stability studies over $G(s)$ \red{[we need to clarify the last sentence - why is it sufficient, where is this fact stated?]}.
-
-%------------------------------------
-\subsection{Verifying Closed-loop Control Systems}
-\label{verifying-closed-loop-control-systems}
-%------------------------------------
-
-%\red{[This section and the next should be merged into a crisp section with the background on DSVerifier, if not included in previous work? 
-%Please stick to the introduced notations. Please clarify what the function FWL does, compared to the general approximations introduced above.]}
-
-%\red{Alessandro, I've made the changes as requested. Please let me know if this is good enough or if I made it too short}
-
-%\textcolor{blue}{[IB: I'm proposing some changes in this section based on Alessandro's comments and trying to obtain a simpler and uniform notation.]}
-
-CEGIS-based control synthesis requires a formal verifier to check whether a
-candidate controller meets the requirements when combined with the plant. 
-We use the Digital-System Verifier (DSVerifier)~\cite{IsmailBCFF15} for this
-purpose.  It checks the stability of closed-loop control systems and
-considers finite-word length (FWL) effects in the digital controller, and
-uncertainty parameters in the plant model (plant intervals)~\cite{Bessa16}. 
-Let $C(z)$ be a digital controller and $G(z)$ be a plant model given as
-%
-\begin{align}
-\small
-\label{controller_plant_tf}
-C(z)&=\frac{C_n(z)}{C_d(z)}=\frac{\beta_{0}+\beta_{1}z^{-1}+...+\beta_{M_C}z^{-M_C}}{\alpha_{0}+\alpha_{1}z^{-1}+...+\alpha_{N_C}z^{-N_C}}, \\
-%\label{plant_tf}
-G(z)&=\frac{G_n(z)}{G_d(z)}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
-\end{align}
-%
-\noindent where $\vec{\beta}$ and $\vec{\alpha}$ are vectors containing the
-controller's coefficients; similarly, $\vec{b}$ and $\vec{a}$ denote the
-plant's coefficients; and $N_{(\cdot)}$ and $M_{(\cdot)}$ indicate the order
-of the polynomials. 
-% of the corresponding block.
-
-Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (i.e.,
-$\Delta_p{G}_n(s),\Delta_p{G}_d(s)$, which arise from tolerances/imprecision
-in the original model), errors in the numeric calculations, or roundoffs in
-the quantization.  These uncertainties are parametrically expressed by
-additive terms, resulting in an uncertain model $\hat{G}(z)$, such that:
-%
-\begin{equation}
-\hat{G}(z)=\frac{G_n(z)+\Delta G_n(z)}{G_d(z)+\Delta G_d(z)},
-\end{equation}
-%
-%\red{[what is the relationship between the deltas in this formula, and those in the previous paragraph? please clarify and hopefully simplify formulae. ]}
-which will be represented by the following transfer function:
-%
-\begin{equation}
-\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}} : N_G \geq M_G .
-\end{equation}
-%
-%\red{[why is this condition on the order of the polynomials raised only now? how is it used later?]}
-Due to the nature of the methods we use for the stability check, we require
-that the parametric errors in the plant have the same polynomial order as
-the plant itself (\blue{all other errors described in this paper are ensured to
-fulfil this property in our implementation}
-%\red{[have we later argued that this is indeed the case?]}) 
-%\blue{and that enter the plant linearly}.
-
-We employ a notation based on the polynomials coefficients to simplify 
-the presentation.  Let $\mathcal{P}^{N}$ be the space of polynomials of order $N$. 
-Let $P \in \mathcal{P}^{M,N}$ be a rational polynomial 
-$\frac{P_n}{P_d}$, where $P_n \in \mathcal{P}^{M}$ and $P_d \in \mathcal{P}^{N}$.  
-For a vector of coefficients
-%
-\begin{equation}
-\vec{P} \in \mathbb{R}^{N+M+2}=[n_{0}\ n_{1}\ \hdots \ n_{M}\ d_{0}\ d_{1}\ \hdots\ d_{N}\ ]^T
-\label{eq:coefficients}
-\end{equation}
-%
-and an uncertainty vector 
-%
-\begin{equation}
-\Delta{\vec{P}}\in \mathbb{R}^{N+M+2}=[\Delta{n}_{0}\ \hdots \ \Delta{n}_{M}\ \Delta{d}_{0}\ \hdots\ \Delta{d}_{N}\ ]^T \; 
-\label{eq:delta_coefficients}
-\end{equation}
-%
-we write
-\begin{align}
-\label{eq:hatgvector}
-\vec{\hat{G}}&=\vec{G}+\Delta{\vec{G}}\\
-\vec{G} \in \mathbb{R}^{N_G+M_G+2}&=[b_{0}\ \hdots \ b_{M_G}\ a_{0}\ \hdots\ a_{N_G}\ ]^T\nonumber \\
-\Delta{\vec{G}}\in \mathbb{R}^{N_G+M_G+2}&=[\Delta{b}_{0}\ \hdots \ \Delta{b}_{M_G}\ \Delta{a}_{0}\ \hdots\ \Delta{a}_{N_G}\ ]^T\nonumber
-\end{align}
-In the following we will
-either use the functions $G(z)$, $C(z)$ directly, or work over their
-respective coefficients $\vec{G}$, $\vec{C}$ in vector form.
+\paragraph{Our Synthesis Approach}
+We have implemented our new algorithm in a tool called \tool, and are able
+to automatically generate stable controllers for a set of intricate plant
+models taken from the literature within minutes.
+The tool uses a two stage approach. 
+As the cost of SAT solving increases with in the size of the problem
+instance, our algorithm tries to solve the problem first for small word length,
+iteratively increasing the precision if it is insufficient.
+The initial phase uses SAT-solving
+techniques in order to synthesise a candidate solution. This solution is neither sound nor universal.
+The candidate is then fed to a formal verifier, which will prove its universality for the collection of plant models (considering the tolerances).
+If the verifier finds a counterexample, it will be fed back to the synthesiser, which will use it as a guideline for future synthesis, thus slicing away candidate solutions that are not likely to be universal.
+If no counter-example is found by the verifier, it enters a second phase in which it restores soundness by evaluating the result using interval arithmetic.
+If this check fails, the loop returns to the synthesis phase, requiring higher precision in order to minimise rounding errors.
+If the check passes, we have found a sound stabilizing controller.
+%
+\end{abstract}
+
+\printccsdesc
 
@@
 
-%\begin{equation}
-%\Delta{\vec{p}}=\begin{bmatrix}
-%\hat{b_{0}} - b_{0}\\
-%\hat{b_{1}} - b_{1}\\
-%\vdots \\
-%\hat{b}_{M_G} - b_{M_{G}}\\
-%\hat{a_{0}} - a_{0}\\
-%\hat{a_{1}} - a_{1}\\
-%\vdots\\
-%\hat{a}_{N_G} - a_{N_{G}}\\
-%\end{bmatrix}=\begin{bmatrix}
-%\vec{\hat{b}}\\
-%\vec{\hat{a}}
-%\end{bmatrix}-\begin{bmatrix}
-%\vec{b}\\
-%\vec{a}
-%\end{bmatrix}
-%\label{eq:uncertainty}
-%\end{equation}
-
-A typical digital control system with a continuous plant and a discrete
-controller is illustrated in Figure~\ref{fig:sampledsystem}.  The DAC and
-ADC converters introduce quantization errors (notice that each of them
-may have a different FWL than the controller),
-%\red{[why is the DAC introducing a quantisation error again?]}
-which are modeled as noises
-$\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model
-with parametric additive uncertainty $\Delta_p{G}_n(s)$ and
-$\Delta_p{G}_d(s)$, $R(z)$ is the reference signal, $U(z)$ is the control
-signal, and $\hat{Y}(z)$ is the output signal affected by the noises and
-uncertainties in the closed-loop system.
-%
-%
-%
-The ADC and DAC may be abstracted by transforming the closed-loop system in
-Figure~\ref{fig:sampledsystem} into the digital system in 
-Figure~\ref{fig:digsystem1}, where the parametric uncertainties are
-represented by~$\Delta_p \vec{G}$
-and the effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is
-seen as additive noise.
-
-%The system in equation~\ref{controller_plant_tf} (disregarding the $\Delta{G}_{P}(z)$ may be represented by the following difference equation model:
-%\begin{equation}
-%\begin{split}
-%y(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
-%+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M),
-%\end{split}
-%\end{equation}
-%and consequently $\hat{y}(k)$ may be represented by the following difference equation:
-%\begin{equation}
-%\label{eq:differencewithnoise}
-%\begin{split}
-%\hat{y}(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N_{G}}y(k-N_{G})\\
-%+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M_{G}}u(k-M_{G})+\nu(k).
-%\end{split}
-%\end{equation}
-%
-%The z-transform of~\eqref{eq:differencewithnoise} is:
-%\begin{equation}
-%\begin{split}
-%\hat{Y}(z)=(-a_{1}z^{-1}-a_{2}z^{-2}-\cdots-a_{N_{G}}z^{-N_{G}})Y(z)\\
-%+(b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M_{G}}z^{-M_{G}})U(z)+\nu(z),
-%\end{split}
-%\end{equation}
-%dividing both sides by $U(z)$, it is equivalent to:
-%\begin{equation}
-%\frac{\hat{Y}(z)}{U(z)}=[1-D_{G}(z)]G(z)+U(z)D_{G}(z)+\frac{\nu(z)}{U(z)}=G(z)+\Delta{G}_{Q}(z),
-%\end{equation}
-
-%Considering the quantization noise $\nu(k)$ as an output error in discrete plant model, we may represent it as an additive noise in the plant output $y(k)$ resulting in the noisy output $\hat{y}(k)$:
-%\begin{equation}
-%
-%\end{equation}
-
-\begin{figure}[ht]
-\centering
-\tikzset{add/.style n args={4}{
-    minimum width=6mm,
-    path picture={
-        \draw[circle] 
-            (path picture bounding box.south east) -- (path picture bounding box.north west)
-            (path picture bounding box.south west) -- (path picture bounding box.north east);
-        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
-        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
-        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
-        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
-        }
-    }
- }
-
-\resizebox{.48\textwidth}{!}{
- \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
-     semithick, initial text=, ampersand replacement=\&,]
-
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
-    \node[draw=none] (r) {$R(z)$};
-%   \& \coordinate (aux0);
-   \& \node[circle,add={-}{+}{}{}] (circle) {};
-   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
-   \& \node[rectangle,draw,
-	minimum width=1cm,
-	minimum height=1cm,
-        label=\textbf{Controller}] (cz) {{\sc C(z)}};
-   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
-   \& \node[circle,add={}{+}{+}{}] (circle2) {};
-   \node[draw=none] (nu2) at ([yshift=1cm]circle2)  {$\nu_2(z)$};
-   \& \node[rectangle,draw,
-	minimum width=1cm,
-	minimum height=1cm,
-        label=\textbf{Plant}] (gs) {{\sc $\hat{G}(z)$}};
-   \node[draw=none] (y) at ([xshift=2cm,yshift=.15cm]gs)  {$Y(z)$};
-
-   \& \node[circle,add={}{+}{+}{}] (circle3) {};
-   \node[draw=none] (nu1) at ([yshift=1cm]circle3)  {$\nu_1(z)$};
-   \& \coordinate (aux1);
-   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
-   \& \coordinate (aux3); 
-   \&
-   \& 
-   \& 
-   \&
-   \& \coordinate (aux2);\\
-  };
-
-%  \path[->] (v1) edge (q1.north);
-%  \path[->] (v2) edge (q2.north);
-  \path[->] (r) edge (circle.west);
-  \path[->] (nu2) edge (circle2.north);
-  \path[->] (nu1) edge (circle3.north);
-  \path[->] (aux1) edge (yz);
-  \path  
-   (circle.east) edge (cz)
-   (cz.east) edge (circle2.west)
-   (circle2.east) edge (gs.west)
-   (gs.east) edge (circle3.west)
-   (circle3.east) edge (aux1.west)
-   (aux1.south) edge (aux2.north)
-   (aux2.west) edge (aux3.east); 
-  \path[->]  (aux3.north) edge (circle.south);
- \end{tikzpicture}
-}
-\caption{Digital equivalent to the system in Figure~\ref{fig:sampledsystem} 
-\label{fig:digsystem1}}
-\end{figure}
-
-%\red{[why is the output in Figure 2 tilde, whereas that in  figure 1 hat?]}
-%
-In Figure~\ref{fig:digsystem1}, two sources of uncertainty are illustrated:
-parametric uncertainties related to modeling errors, and uncertainties
-introduced by quantizations in the ADC and
-DAC conversions.  These sources are assumed to be non-deterministic, 
-which poses no further restriction to our model, thus, the uncertain model
-may be rewritten as a vector of coefficients in the z-domain using equation
-(\ref{eq:hatgvector})
-%
-\begin{equation}
-\label{eq:complete_unc_model}
-\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G},
-\end{equation}
-%
-where $\Delta_p \vec{G}$ is the term that corresponds to the parametric
-uncertainties. Notice that the quantization noise is additive, which means
-it does not affect the transfer function. Instead, we prove that the system
-is stable given these non-deterministic noise inputs.
-
-The parametric uncertainties in the plant are assumed to have the same
-order as the plant model, since tolerances of higher order would invalidate
-feedback model (even tiny errors of higher order can move the poles by a
-large amount preventing any single controller from stabilizing such a setup).
-This is a reasonable assumption since most tolerances do not change the 
-architecture of the plant, and models subject to such effects are
-inadequate.
-
-%\red{[next figure is a bit unnecessary, does not ad much to the previous one.]} Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.
-
-%\begin{figure}[ht]
-%\centering
-%
-%\tikzset{add/.style n args={4}{
-%    minimum width=6mm,
-%    path picture={
-%        \draw[circle] 
-%            (path picture bounding box.south east) -- (path picture bounding box.north west)
-%            (path picture bounding box.south west) -- (path picture bounding box.north east);
-%        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
-%        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
-%        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
-%        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
-%        }
-%    }
-% }
-%
-%\resizebox{.5\textwidth}{!}{
-% \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
-%     semithick, initial text=, ampersand replacement=\&,]
-%
-%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
-%  %
-%	\& 
-%	\&
-%	\& \coordinate (aux7); 
-%	\& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm] (deltag2) {{\sc $\Delta G_{Q}(z)$}};
-%	\& \coordinate (aux8);\\
-%    \node[draw=none] (r) {$R(z)$};
-%%   \& \coordinate (aux0);
-%   \& \node[circle,add={-}{+}{}{}] (circle) {};
-%   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
-%   \& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm,
-%        label=\textbf{Controller}] (cz) {{\sc C(z)}};
-%   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
-%   \& \coordinate (aux4);
-%   \& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm,
-%        label=\textbf{Plant}] (gs) {{\sc G(z)}};
-%   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
-%   \& \node[circle,add={+}{+}{+}{}] (circle2) {};
-%%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
-%%   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
-%   \& \coordinate (aux1);
-%   \& \node[draw=none] (yz) {$\hat{Y}(z)$};\\
-%   \& 
-%   \&
-%   \& \coordinate (aux5); 
-%   \& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm] (deltag) {{\sc $\Delta G_{P}(z)$}};
-%   \& \coordinate (aux6);\\
-%   \& \coordinate (aux3); 
-%   \&
-%   \& 
-%   \& 
-%   \&
-%   \& \coordinate (aux2);\\
-%  };
-%
-%
-%%  \path[->] (v1) edge (q1.north);
-%%  \path[->] (v2) edge (q2.north);
-%  \path[->] (r) edge (circle.west);
-%%  \path[->] (nu) edge (circle2.north);
-%  \path[->] (aux1) edge (yz);
-%  \path  
-%   (aux4.north) edge (aux5.south)
-%   (aux4.north) edge (aux7.south)
-%   (aux5.east) edge (deltag.west)
-%   (aux7.east) edge (deltag2.west)
-%   (deltag.east) edge (aux6.west)
-%   (deltag2.east) edge (aux8.west)
-%   (circle.east) edge (cz)
-%   (cz.east) edge (gs.west)
-%   (circle2.east) edge (aux1.west)
-%   (aux1.south) edge (aux2.north)
-%   (aux2.west) edge (aux3.east); 
-%  \path[->] (aux8.south) edge (circle2.north); 
-%  \path[->] (aux6.south) edge (circle2.south);
-%  \path[->] (gs.east) edge (circle2.west);
-%  \path[->] (aux3.north) edge (circle.south);
-% \end{tikzpicture}
-%}
-% \caption{Digital system with additive uncertainties $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$. \label{fig:digsystem2}}
-%\end{figure}
-
-%\textcolor{blue}{[IB: I propose to exchange the following paragraphs by the previous blue]}
-
-%\textcolor{green}{DC: I believe Alessandro wanted to be more specific about the nature of the modelling error which is why I was trying to explain it.
-In this case I believe there are also two separate sources for $\Delta{G}_p(z)$.
-The first is $\Delta{G}_p(s)$ (which is basically a known tolerance that may come from G(t)), while the second is the error introduced by the calculations in the $\mathcal{Z}$ transform.
-Alessandro, do you want to address this second term (possibly as explained below) or just leave the blue section as is?}
-
-%Since $G(z)$ is an approximation of $G(s)$ we introduce an error term caused during its calculation as $\Delta{G}_P$
-%
-%%
-%\begin{align}
-%\small
-%\label{parametric_plant_tf}
-%\hat{G}(z)&=\frac{(b_{0}+\Delta_p b_{0}) +...+(b_{M_G}+\Delta_p b_{M_G})z^{-M_G}}{(a_{0}+\Delta_p a_{0})+...+(a_{N_G}+\Delta_p a_{N_G})z^{-N_G}} \nonumber \\
-%&=G(z)+\Delta{G}_P(z).
-%\end{align}
-%%
-%Note that $\Delta{G}_P$ is undefined and upper bound by a user defined
-%value such that $\hat{G}(z)$ corresponds to the set of
-%possible polynomial forms of $G(z, T)$ that overapproximate $G(s)$.
-%This calculation is performed outside of the scope of this work since it depends on the nature of the tool used to obtain the $\mathcal{Z}$ form.
-The error comes from the bounded horizon and mathematical precision used to calculate the $\mathcal{Z}$ transform, which will be tool and user dependent.
-%\red{[The previous statement is confusing and I must disagree here: I want hard error bounds on a specific value of T.]}
-%\green{[You are correct.
-It was absolutely wrong.
-Hopefully this explanation is clear.
-We use MATLAB, but still don't know the details of their implementation, so I don't have hard data on how this error is calculated.}
-
-\smallskip
-
-Since the controller is implemented using finite representation, $C(z)$ also suffers
-disturbances from the FWL effects, with roundoffs in coefficients that may
-change closed-loop poles and zeros position, and consequently affect its
-stability, as argued in~\cite{Bessa16}.
-
-Let $\hat{C}(z)$ be the digital controller transfer function represented
-using this FWL with integer size $I$ and fractional size~$F$; $I$ affects
-the range of the representation and is set to avoid overflows, while $F$
-affects the precision and the truncation after arithmetic operations. 
-\red{[we ought to align the following notations with those use in the CAV submission.]}
-We shall denote the FWL domain of the coefficients by $\mathbb{R}\langle I,F
-\rangle$
-%
-%Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
-%domain, {\it i.e.} a Fixed-Point Finite Word Length with integer size $I$ and fractional
-%size $F$, we shall denote this domain as $\mathbb{R}\langle I,F \rangle$ 
-%
-and assume that there exists a function
-$\mathcal{F}_n\langle I,F \rangle(\cdot):\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$,
-which applies the FWL effects to a polynomial, with an equivalent $\mathcal{F}_{n,m}\langle I,F \rangle(\cdot):\mathcal{P}^{n,m}\rightarrow \mathcal{P}^{n,m}\langle I,F \rangle$ that applies the same effect to a ratio of polynomials, where
-$\mathcal{P}^{n}$ is the
-space of polynomials of $n$-th order, $\mathcal{P}^{n}\langle I,F
-\rangle$ is the space of polynomials with coefficients in
-$\mathbb{R}\langle I,F \rangle$, and $\mathcal{P}^{n,m}$,  $\mathcal{P}^{n,m}\langle I,F
-\rangle$ are their rational equivalent.
-
-Thus, the perturbed controller model $\hat{C}(z)$ may be obtained from the
-original model $C(z)=\frac{C_{n}(z)}{C_{d}(z)}$ as follows:
-%
-\begin{equation}
-\hat{C}(z)=\mathcal{F}_{M_C,N_C}\langle I,F \rangle(C(z))=\frac{\mathcal{F}_{M_C}\langle I,F \rangle(C_n(z))}{\mathcal{F}_{N_C}\langle I,F \rangle(C_d(z))}.
-\end{equation}
-%
-In the case of a synthesized controller, because the synthesis is performed
-using FWL, $\hat{C}(z) \equiv C(z)$.
-
-%\textcolor{blue}{[IB: And I propose to exchange the remaining paragraphs by the previous blue]}
-%
-%\textcolor{green}{[DC: I changed it to a separate section to differentiate the effects, so we should keep both]}
-
-%------------------------------------
-\subsection{Stability under Finite Representation and Quantisation Noise}
-\label{sec:stability}
-%------------------------------------
-
-Correct synthesis of the digital controller requires consideration of the
-effect of FWL on the controller and quantization noises in the closed loop
-system.  Let the quantizer $Q1$ be the source of a white noise $\nu_{1}$ and
-$Q2$ be the source of a white noise $\nu_{2}$.  The following equation
-models the system in Figure~\ref{fig:sampledsystem}, encompassing the
-parametric uncertainties $\Delta \vec{G}$ and the FWL effects on
-the controller $\hat{C}(z)$:
-%
-\begin{equation}
-\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\cdot C(z)\cdot R(z)+\hat{G}(z)\cdot\nu_{2}(z)-\hat{G}(z)\cdot \hat{C}(z)\cdot \hat{Y}(z)
-\end{equation}
-%
-%
-%
-%
-The above can be rewritten as follows:
-%
-\begin{equation}
-\label{eq:outputfunctions}
-\hat{Y}(z)=H_{1}(z)\nu_{1}(z)+H_{2}(z)\cdot\nu_{2}(z)+H_{3}(z)\cdot R(z),
-\end{equation}
-%
-where
-%
-\begin{equation*}
-H_{1}(z)=\frac{1}{1+\hat{G}(z)\cdot \hat{C}(z)}
-\end{equation*}
-%
-\begin{equation*}
-H_{2}(z)=\frac{\hat{G}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}
-\end{equation*}
-%
-and
-%
-\begin{equation*}
-H_{3}(z)=\frac{\hat{G}(z)\cdot \hat{C}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}
-\end{equation*}
-
-\begin{myassumption}
-\label{whitenoise}
-%
-The quantization noises $\nu_{1}$ (from $Q1$) and $\nu_{2}$ (from $Q2$) are
-uncorrelated white noises and their amplitudes are always bounded by the
-half of quantization step~\cite{astrom1997computer}, i.e., $\vert \nu_{1}
-\vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$,
-where $q_{1}$ and $q_{2}$ are the quantization steps of ADC and DAC, respectively.
-% 
-\end{myassumption}
-
-%\begin{mylemma}
-%\label{lemma:variance}
-%%
-%In particular, Widrow \cite{widrow1956} models the quantization noise as a
-%Gaussian model in which the second moment (variance) of the probability
-%density function (PDF) of the quantization noise is given by
-%%
-%\begin{equation}
-%\label{eq:variancelemma}
-%\sigma_{Q}^{2}=\frac{q^{2}}{12},
-%\end{equation}
-%where $q$ is the step size of quantiser. (Proof is on \cite{widrow1956})
-%\end{mylemma}
-%
-%\begin{mylemma}
-%\label{lemma:boundednoise}
-%%
-%The power spectral density of the quantization noise (supposed white)
-%$S_{\nu}(z)$ is bounded and may be computed through the z-transform of
-%autocorrelation function of $\nu(k)$, thus:
-%%
-%\begin{equation}
-%S_{\nu}(z)= \sigma_{Q}^{2}=\frac{q^{2}}{12}.
-%\end{equation}
-%\end{mylemma}
-%
-%\begin{proof}
-%%
-%Considering $\nu(k)$ a random process, where $\nu(k)$ is independent from
-%$\nu(k+i)$ for every integer $k\neq 0$.  The autocorrelation function of
-%$\nu(k)$, {\it i.e.} $R_{\nu\nu}(\tau)$ may be computed as follows:
-%%
-%\begin{equation}
-%R_{\nu\nu}(\tau)=E[\nu(t+\tau)\nu(t)]=\sigma_{Q}^{2}\cdot \delta(\tau),
-%\end{equation}
-%%
-%where $\delta(\tau)$ is the Dirac delta function at delay time $\tau$.
-%
-%By definition~\cite{poularikas2000transforms}, the power spectral density of
-%$\nu(k)$ is the z-transform of $R_{\nu\nu}(\tau)$, thus
-%%
-%\begin{equation}
-%S_{\nu}(z)=  \sum\limits_{k=-\infty}^{\infty}{R_{\nu\nu}(k)z^{-k}} = \sigma_{Q}^{2},
-%\end{equation}
-%considering the Lemma~\ref{lemma:variance}:
-%\begin{equation}
-%S_{\nu}(z)=  \frac{q^{2}}{12}.
-%\end{equation}
-%\end{proof}
-%
-%Finally, the quantization noise spectrum may be considered a energy-bounded
-%(Lemma~\ref{lemma:boundednoise}), and consequently the Parseval's theorem
-%ensures that the quantization noise is also energy-bounded in time-domain. 
-%Thus $\hat{Y}(z)$ will be bounded and the closed-loop system stable if the
-%conditions in Lemma~\ref{lemma:eq_int_stab} are followed.
-
-%\red{[Add remark on bound (q/2) for signal. We need a bounded signal to be able to leverage BIBO stability results. ]}
-
-A discrete-time linear system is said to be Bounded-Input and Bounded-Output
-(BIBO) stable if and only if every pole of its transfer function lies inside
-the unit circle \cite{Astrom08}.  Analyzing Eq.~\eqref{eq:outputfunctions},
-the following proposition gives necessary conditions for the closed-loop system 
-BIBO stability in Figure~\ref{fig:sampledsystem}, with regards to the 
-exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$, which are bounded.
-
-\begin{myprop}{\cite{Bessa16,fadali}}
-\label{prop:eq_int_stab} 
-%
-Consider a feedback closed-loop control system as given in
-Figure~\ref{fig:sampledsystem} with a FWL implementation of the digital
-controller $\hat{C}(z) =\mathcal{F}_{M_C,N_C}\langle I,F \rangle(C(z))$ and uncertain discrete
-model of the plant
-%
-$$
-\hat{G}(z) =\frac{\hat{G}_n(z)}{\hat{G}_d(z)}: \vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}
-\text{\quad(from~\ref{eq:coefficients},\ref{eq:delta_coefficients})}.
-$$
-%
-Then $\hat{G}(z)$ is BIBO-stable if and only if:
-%
-\begin{itemize}
-\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
-\begin{equation}
-\label{eq:internal_stab_lemma}
-S(z)=\mathcal{F}_{M_C}\langle I,F \rangle(C_n(z))\hat{G}_n(z)+\mathcal{F}_{N_C}\langle I,F \rangle(C_d(z))\hat{G}_d(z);
-\end{equation}
-\item the direct loop product $\mathcal{F}_{M_C,N_C}\langle I,F \rangle(C(z))\cdot \hat{G}(z)$ has no pole-zero cancellation on or outside the unit circle.
-\end{itemize}
-\end{myprop}
-
-Proposition~\ref{prop:eq_int_stab} provides necessary (and sufficient) conditions for the
-controller to stabilize the closed-loop system, considering plant
-parametric uncertainties (i.e., $\Delta_p \vec{G}$), quantization noises
-($\nu_{1}$ and $\nu_{2}$) and FWL effects in the control software.  Note
-that the model for quantization noise enters as a signal to be stabilized (i.e.,
-the noise may be disregarded if the conditions on
-Proposition~\ref{prop:eq_int_stab} are satisfied and if the quantization
-noise is bounded.  The bound on the quantization noise is given by
-Assumption~\ref{whitenoise}.
-
-%\red{[first: lemmae precede theorems. ]}
-
-% Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
-% using Fixed-Point bit vectors with integer size $I_p$ and fractional
-% size $F_p$, whose domain is $\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
-% %
-% \begin{align}
-% \small
-% \label{digital_controller_plant_tf}
-% \tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
-% %\label{plant_tf}
-% \tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
-% \end{align}
-
-% Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
-% domain,
-% %
-%  $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
-
-% Two approaches have been taken to synthesise a stable controller based on this model.
-% The first uses interval arithmetic, representing the coefficients $[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\ {c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_p})]$
-
-% \cdsay{Dario, what coefficients are these?}
-
-% and rounding operations outwards during the process. This results in a tighter calculation of the error at the cost of performance.
-
-%, thus supporting this assumption.
-
-%------------------------------------
-%\subsection{Using Fixed Point Arithmetic for verification}
-%\label{fixedpoint_verification}
-%------------------------------------
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Automated Program Synthesis \\ for Digital
-Control}\label{sec:synthesis}
-
-%------------------------------------
-\subsection{Overview of the Synthesis Process}
-\label{verification-flow}
-%------------------------------------
-
-In order to synthesize closed-loop digital control systems, we use a program
-synthesis engine.  Our program synthesizer implements Counter-Example Guided
-Inductive Synthesis (CEGIS)~\cite{sketch}.  We start by presenting its
-general architecture followed by describing the parts specific to
-closed-loop control systems.  A high-level view of the synthesis process is
-given in Figure~\ref{DSSynth_process}.  Steps $1$ to $3$ are performed by
-the user and Steps~A to D are automatically performed by our tool for
-Digital Systems Synthesis, named \tool.
-%
-%, which accepts the
-%digital controller transfer functions together with the plant model.  For
-%any digital controller, implementation details should be provided ({\it
-%e.g.}, number of bits, realization, and sample time).
-
-\begin{figure*}[t]
-\centering
-\includegraphics[width=0.9\textwidth]{figures/synthesis-flow.pdf}
-\vspace{0.1cm}
-\caption{Overview of the synthesis process\label{DSSynth_process}}
-\end{figure*}
-
-%In Step $1$, the user provides inputs $G(z)$ and $\Delta{G}(z)$
-%%$\%$ ({\it i.e.}, $\Delta{G}(z)$ as a percentage of $G(z)$)
-%, which contain the plant model and the
-%interval, respectively.  In Step $2$, a digital controller must be designed
-%with any preferred method, where $C(z)$ is obtained.  The controller
-%numerical representation and realization form are chosen in Steps $3$ and
-%$4$, respectively.  In Step $5$, the user finally configures the
-%verification parameters ({\it e.g.}, verification time, properties, and BMC
-%tool).  After that, DSVerifier verification engine performs an (automatic)
-%verification of the desired property $\phi$ ({\it i.e.}, stability).  The
-%user steps described in Steps $1$--$5$ result in an ANSI-C code that should
-%be used as an input for DSVerifier.
-
-Given a plant model in ANSI-C syntax as input (Steps 1--3), \tool
-constructs a non-deterministic model to represent the plant family,
-i.e., it addresses plant variations as interval sets (Step~A),
-and formulates a function (Step~B) using implementation details provided in
-Steps~$2$ and $3$ to calculate the controller parameters to be
-synthesized (Step~C).  Note that \tool synthesizes the controller 
-coefficients for the given implementation aspects, i.e., numerical
-representation and realization form.  Finally, \tool builds an intermediate 
-ANSI-C code for the digital system implementation, which is used as input 
-for the CEGIS engine (Step~D).
-
-This intermediate ANSI-C code model contains a specification $\phi$ for the
-property of interest (i.e., robust stability) and is passed to the
-Counterexample-Guided Inductive Synthesis (CEGIS) module of
-CBMC~\cite{ClarkeKL04}, where the controller is marked as the input variable
-to synthesize.  CEGIS employs an iterative, counterexample-guided refinement
-process, which is explained in detail in Section~\ref{synthesizer-general}. 
-CEGIS reports a successful synthesis result if it generates a controller
-that is safe with respect to~$\phi$.  In particular, the ANSI-C code model
-guarantees that a synthesized solution is complete and sound with respect to
-the stability property~$\phi$, since it does not depend on system inputs and
-outputs.  In the case of stability, the specification~$\phi$ consists of a
-number of assumptions on the polynomial coefficients, following Jury's
-Criteria, as well as the restrictions on the representation of these
-coefficients as discussed in detail in Section~\ref{synthesis-elements}.
-
-% by the function $f$ (cf.~Eq.~\eqref{FWL_tf})
-%In Step A, DSVerifier constructs a non-deterministic model to represent the
-%plant family $\mathfrak{G}$ using $g_0$ and $\Delta{g}\%$, which are
-%provided in Step $1$.  DSVerifier then formulates $\mathcal{F}\langle I,F \rangle(\cdot)$ in
-%Step B using implementation details provided from Steps $2$ and $3$, and
-%then computes $\mathcal{F}\langle I,F \rangle(c_0)$ in Step C.  Thus, DSVerifier builds an
-%intermediate ANSI-C code for the digital system implementation, which is
-%used as input for the model-checker, as pointed in Step D.
-
-%This intermediate ANSI-C code model has three main modules: digital
-%controller code to be embedded into the microprocessor; plant model code,
-%which simulates the plant model dynamics considering uncertainties; and
-%``assert'' and ``assume'' statements, which control the verification flow. 
-%For the digital controller code, transfer functions coefficients are
-%quantised and deterministic, and all operations use fixed-point arithmetic. 
-%\textcolor{red}{In the plant model code, transfer function coefficients are
-%not quantised, but represented with maximum precision based on float
-%data-type variables}; they are treated as non-deterministic variables to
-%support model uncertainties.  The directive ``assume'' bounds
-%non-deterministic variables, {\it i.e.}, inputs and plant uncertain
-%coefficients.
-%
-%The translation of ANSI-C code into SAT/SMT formulae
-%is done by a back-end model-checking tool ({\it e.g.},
-%CBMC~\cite{ClarkeKL04} or ESBMC~\cite{CordeiroFM12}).  Here, DSVerifier
-%symbolically checks a given property $\phi$ with respect to closed-loop
-%systems, which are composed by $f(c_i)$ and every $G$ in $\mathfrak{G}$. 
-%If any property violation is found, then DSVerifier reports a
-%counterexample, which contains system inputs or parametric deviations
-%$\Delta{G}$ that lead the system to a failure.  A successful verification
-%result is reported if the system is safe with respect to $\phi$.  In
-%particular, the stability verification is complete and sound, since it does
-%not depend on system outputs and inputs.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Modelling Errors}
-
-%In this section, we show how to embed discretization errors on the plant model, as follows: 
-%%$\hat{G}(z)$ is split into two terms:
-%%
-%\begin{equation}
-%\label{eq:uncertainplant}
-%%\hat{G}(z)=G(z)+\Delta{G(z)},
-%\tilde G(z) = \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z),   
-%\end{equation}
-%where $G(z,T)$ is the time discretization of the nominal physical plant $G(s)$, 
-%$\Delta{G_{Q}(z)}$ represents the quantization uncertainty model, 
-%and $\Delta{G_{P}(z)}$ describes the parametric uncertainty model.
-
-%\noindent where $G(z)$ is the discretised nominal plant model and
-%$\Delta{G(z)}$ is the additive uncertainty, which is related to parametric
-%uncertainties~\cite{Bessa16}.
-
-%\section{An Uncertainty Model for the quantization Error} 
-%\label{sec:uncertainty-model-quantization-error}
-%
-%%Here, an uncertainty model to accommodate the
-%%quantization noise effects on $\hat{G}(z)$ is proposed.  
-%%As a result, Eq.~\eqref{eq:uncertainplant} is rewritten as
-%%
-%%\begin{equation}
-%%\label{eq:uncertainFWLplant}
-%%\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}+\Delta{G_{P}(z)},
-%%\end{equation}
-%
-%A model for $\Delta{G_{Q}(z)}$ that can represent the quantization
-%noise effect in the plant output, and consequently the closed-loop system
-%output, is proposed.  
-%%\red{[eliminate next:] 
-%%For convenience, the parametric uncertainties will be described here.}
-%
-%Consider the closed-loop sampled system in Figure~\ref{fig:sampledsystem},
-%where $C(z)$ is the digital controller model, whose control output signal is
-%quantised ($Q2$) and interpolated via a ZOH using digital-to-analog
-%converter (DAC).  The quantization occurs because the DAC resolution may be
-%different from the fixed point representation of the controller.  $G(s)$ is
-%the continuous-time model of the plant, from which output samples are taken
-%and quantised ($Q1$) by means of an analog-to-digital converter (ADC)
-%synchronized with the DAC.  Each quantiser ($Q1$ and $Q2$) will present some
-%contribution for the total quantization noise.
-%    
-%\begin{figure*}[ht]
-%\centering
-%
-%\tikzset{add/.style n args={4}{
-%    minimum width=6mm,
-%    path picture={
-%        \draw[circle] 
-%            (path picture bounding box.south east) -- (path picture bounding box.north west)
-%            (path picture bounding box.south west) -- (path picture bounding box.north east);
-%        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
-%        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
-%        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
-%        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
-%        }
-%    }
-% }
-%
-%\resizebox{.8\textwidth}{!}{
-% \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
-%     semithick, initial text=, ampersand replacement=\&,]
-%
-%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
-%    \node[draw=none] (r) {$\tilde R(z)$};
-%%   \& \coordinate (aux0);
-%   \& \node[circle,add={-}{+}{}{}] (circle) {};
-%   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$\tilde e(z)$};
-%   \& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm,
-%        label=\textbf{Controller}] (cz) {{\sc C(z)}};
-%   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$\tilde U(z)$};
-%     
-%   \& complexnode/.pic={ 
-%      \node[rectangle,draw,
-%	minimum width=3cm,
-%	minimum height=1.6cm,
-%	label=\textbf{DAC},] (dac) {};
-%     \node[circle,add={}{+}{+}{},fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {};
-%     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
-%     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
-%     \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}
-%   \& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm,
-%        label=\textbf{Plant}] (gs) {{\sc G(s)}};
-%   \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]gs)  {$U(s)$};
-%   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(s)$};
-%   \& complexnode/.pic={ 
-%     \node[rectangle,draw,
-%	minimum width=4cm,
-%	minimum height=1.6cm,
-%	label=\textbf{ADC},] (adc) {};
-%   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
-%   \coordinate (switch1) at ([xshift=-1cm]adc.center);
-%   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
-%   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
-%     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
-%   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
-%   \& \coordinate (aux1);
-%   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
-%   \& \coordinate (aux3); 
-%   \&
-%   \&
-%   \& 
-%   \& 
-%   \& \coordinate (aux2);\\
-%  };
-%
-%
-%  \path[->] (v1) edge (q1.north);
-%  \path[->] (v2) edge (q2.north);
-%  \path[->] (r) edge (circle.west);
-%  \path[->] (aux1) edge (yz);
-%  \path  
-%   (circle.east) edge (cz)
-%   (cz.east) edge (q2.west)
-%   (q2.east) edge (zoh.west)
-%   (zoh.east) edge (gs.west)
-%   (switch2) edge (q1.west)
-%   (q1.east) edge (aux1.west)
-%   (gs.east) edge (switch1.west)
-%   (aux1.south) edge (aux2.north)
-%   (aux2.west) edge (aux3.east); 
-%  \path[->]  (aux3.north) edge (circle.south);
-% \end{tikzpicture}
-%}
-% \caption{Sampled System. \label{fig:sampledsystem}}
-%\end{figure*}
-%
-%%% \begin{figure}[ht]
-%%% \centering
-%%% \includegraphics[width=\columnwidth]{figures/hsystembd.pdf}
-%%% \caption{Sampled system.}
-%%% \label{fig:sampledsystem}
-%%% \end{figure}
-%
-%
-%\begin{figure}[ht]
-%\centering
-%
-%\tikzset{add/.style n args={4}{
-%    minimum width=6mm,
-%    path picture={
-%        \draw[circle] 
-%            (path picture bounding box.south east) -- (path picture bounding box.north west)
-%            (path picture bounding box.south west) -- (path picture bounding box.north east);
-%        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
-%        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
-%        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
-%        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
-%        }
-%    }
-% }
-%
-%\resizebox{.5\textwidth}{!}{
-% \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
-%     semithick, initial text=, ampersand replacement=\&,]
-%
-%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
-%    \node[draw=none] (r) {$R(z)$};
-%%   \& \coordinate (aux0);
-%   \& \node[circle,add={-}{+}{}{}] (circle) {};
-%   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
-%   \& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm,
-%        label=\textbf{Controller}] (cz) {{\sc C(z)}};
-%   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
-%   \& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm,
-%        label=\textbf{Plant}] (gs) {{\sc G(z)}};
-%   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
-%
-%   \& \node[circle,add={}{+}{+}{}] (circle2) {};
-%%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
-%   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
-%   \& \coordinate (aux1);
-%   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
-%   \& \coordinate (aux3); 
-%   \&
-%   \& 
-%   \& 
-%   \& \coordinate (aux2);\\
-%  };
-%
-%
-%%  \path[->] (v1) edge (q1.north);
-%%  \path[->] (v2) edge (q2.north);
-%  \path[->] (r) edge (circle.west);
-%  \path[->] (nu) edge (circle2.north);
-%  \path[->] (aux1) edge (yz);
-%  \path  
-%   (circle.east) edge (cz)
-%   (cz.east) edge (gs.west)
-%   (gs.east) edge (circle2.west)
-%   (circle2.east) edge (aux1.west)
-%   (aux1.south) edge (aux2.north)
-%   (aux2.west) edge (aux3.east); 
-%  \path[->]  (aux3.north) edge (circle.south);
-% \end{tikzpicture}
-%}
-% \caption{Sampled System. \label{fig:sampledsystem}}
-%\end{figure}
-%
-%%
-%%
-%
-%\begin{figure}[ht]
-%\centering
-%
-%\tikzset{add/.style n args={4}{
-%    minimum width=6mm,
-%    path picture={
-%        \draw[circle] 
-%            (path picture bounding box.south east) -- (path picture bounding box.north west)
-%            (path picture bounding box.south west) -- (path picture bounding box.north east);
-%        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
-%        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
-%        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
-%        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
-%        }
-%    }
-% }
-%
-%\resizebox{.5\textwidth}{!}{
-% \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
-%     semithick, initial text=, ampersand replacement=\&,]
-%
-%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
-%    \node[draw=none] (r) {$R(z)$};
-%%   \& \coordinate (aux0);
-%   \& \node[circle,add={-}{+}{}{}] (circle) {};
-%   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
-%   \& \coordinate (aux4);
-%   \& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm,
-%        label=\textbf{Controller}] (cz) {{\sc C(z)}};
-%   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
-%   \& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm,
-%        label=\textbf{Plant}] (gs) {{\sc G(z)}};
-%   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
-%   \& \node[circle,add={+}{+}{}{}] (circle2) {};
-%%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
-%%   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
-%   \& \coordinate (aux1);
-%   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
-%   \& 
-%   \& \coordinate (aux5); 
-%   \& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm] (deltag) {{\sc $\Delta G(z)$}};
-%   \&
-%   \& \coordinate (aux6);\\
-%   \& \coordinate (aux3); 
-%   \&
-%   \& 
-%   \& 
-%   \&
-%   \& \coordinate (aux2);\\
-%  };
-%
-%
-%%  \path[->] (v1) edge (q1.north);
-%%  \path[->] (v2) edge (q2.north);
-%  \path[->] (r) edge (circle.west);
-%%  \path[->] (nu) edge (circle2.north);
-%  \path[->] (aux1) edge (yz);
-%  \path  
-%   (aux4.north) edge (aux5.south)
-%   (aux5.east) edge (deltag.west)
-%   (deltag.east) edge (aux6.west)
-%   (aux6.south) edge (circle2.south)
-%   (circle.east) edge (cz)
-%   (cz.east) edge (gs.west)
-%   (gs.east) edge (circle2.west)
-%   (circle2.east) edge (aux1.west)
-%   (aux1.south) edge (aux2.north)
-%   (aux2.west) edge (aux3.east); 
-%  \path[->]  (aux3.north) edge (circle.south);
-% \end{tikzpicture}
-%}
-% \caption{Sampled System. \label{fig:sampledsystem}}
-%\end{figure}
-
-%\begin{myprop}
-%Considering the quantization noise $\nu(k)$ as an output error in the
-%discrete plant model, 
-%%{\it i.e.}, it does not affect the plant dynamics, but its output samples, 
-%$\Delta{G_{Q}(z)}$ can be obtained from
-%%
-%\begin{equation}
-%\label{eq:quantization_tf}
-%\Delta{G_{Q}(z)}=\frac{\nu(z)}{U(z)},
-%\end{equation}
-%where $\nu(z)$ is the z-transform of the random process $\nu(k)$,
-%which can be calculated through the power spectral density of
-%$\nu(k)$~\cite{poularikas2000transforms}.  
-%Thus, the $\Delta{G_{Q}(z)}$ can expressed as
-%%
-%\begin{equation}
-%\label{eq:deltag_var}
-%\Delta{G_{Q}(z)}=\frac{\sigma_{Q}^{2}}{U(z)},
-%\end{equation}
-%where $\sigma_{Q}^{2}$ is the variance of the quantization noise and
-%$U(z)$ is the z-transform of control signal ({\it i.e.}, the z-transform of
-%the signal from the digital controller), which is provided to the plant by
-%means of ZOH.
-%\end{myprop}
-%
-%%
-%\begin{proof}
-%%
-%Suppose that the plant discrete model in Figure~\ref{fig:sampledsystem} can
-%be represented by the following pulse transfer function (without
-%quantization noise effect):
-%%
-%\begin{equation}
-%\label{eq:tfwithout}
-%G(z)=\frac{Y(z)}{U(z)}=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M}z^{-M}}{1+a_{1}z^{-1}+a_{2}z^{-2}+\cdots+a_{N}z^{-N}},
-%\end{equation}
-%%
-%\noindent where $Y(z)$ is the z-transform of the plant output signal without
-%noise $y(k)$, $U(z)$ is the z-transform of the control signal, which is
-%provided to the plant, $A(z)$ and $B(z)$ are the plant pulse transfer
-%function numerator and denominator, respectively.
-%
-%Considering the quantization noise $\nu(k)$ as an output error in the
-%discrete plant model, an additive noise in the plant output $y(k)$ resulting
-%in the noisy output $\hat{y}(k)$ can be represented as
-%%
-%\begin{equation}
-%\hat{y}(k)=y(k)+\nu(k).
-%\end{equation}
-%
-%Note that the model in Eq.~\eqref{eq:tfwithout} is equivalent to the
-%following difference equation:
-%%
-%\begin{equation}
-%\begin{split}
-%y(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
-%+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M),
-%\end{split}
-%\end{equation}
-%
-%\noindent and consequently $\hat{y}(k)$ can be represented by the following
-%difference equation:
-%%
-%\begin{equation}
-%\label{eq:differencewithnoise}
-%\begin{split}
-%\hat{y}(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
-%+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M)+\nu(k).
-%\end{split}
-%\end{equation}
-%
-%The z-transform of Eq.~\eqref{eq:differencewithnoise} is
-%%
-%\begin{equation}
-%\begin{split}
-%\hat{Y}(z)=(-a_{1}z^{-1}-a_{2}z^{-2}-\cdots-a_{N}z^{-N})Y(z)\\
-%+(b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M}z^{-M})U(z)+\nu(z),
-%\end{split}
-%\end{equation}
-%dividing both sides by $U(z)$, it is equivalent to:
-%\begin{equation}
-%\frac{\hat{Y}(z)}{U(z)}=\hat{G}(z)=[1-A(z)]G(z)+U(z)B(z)+\frac{\nu(z)}{U(z)}.
-%\end{equation}
-%
-%Considering $\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}$ and Eq.~\eqref{eq:tfwithout},
-%the intended expression can be obtained as
-%%
-%\begin{equation}
-%\Delta{G_{Q}(z)}=\frac{\nu(z)}{U(z)} 
-%\end{equation}
-%\end{proof}
-
-%Eq.~\eqref{eq:deltag_var} indicates that the modelling of the quantization noise
-%effect on the plant transfer function demands an estimation of the variance
-%of quantization noise $\sigma_{Q}^{2}$.  To obtain such estimation, the
-%methodology presented by~\cite{widrow2008quantization}
-%is used.  The authors provide an algorithm for computing the mean square of
-%the output noise due to $Q1$ and $Q2$.  Considering that each quantiser
-%contribution can be represented by a white noise with zero mean
-%(Assumption~\ref{whitenoise}), the mean square can be considered as the
-%variance of noise ($\sigma_{Q}^{2}$), which can be calculated as
-%%
-%\begin{equation}
-%\sigma_{Q}^{2}=\frac{\lambda_{1}^{2}\cdot \sum {h_{Q1}^{2}} \cdot q_{1}+\lambda_{2}^{2}\cdot \sum {h_{Q2}^{2}} \cdot q_{2}}{12},
-%\end{equation}
-%%
-%\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factors, {\it i.e.} constant gains usually employed before the ADC and after the DAC in order to avoid the overload of converters  %\red{[define scale factors]}
-%for the quantization $Q1$ and $Q2$, respectively; $q_{1}$ and $q_{2}$ are the quantization step for $Q1$ and $Q2$, respectively, and $\sum {h_{Q1}^{2}}$ and $\sum
-%{h_{Q2}^{2}}$ are the squares sums of the impulse response obtained by means
-%of a transfer function from $Q1$ and $Q2$ to the plant output, respectively.
-%
-%The transfer functions $H_{Q1}(z)$ and $H_{Q2}(z)$, from which the squares
-%sums of the impulse response are needed, can be obtained through the
-%analysis of the system in Figure~\ref{fig:sampledsystem}.
-
-%\red{[The following text needs to be completed. (Notice typos, reference to wrong signal $R$, and to wrong TF $C,G$.]}
-%
-%Considering that
-%the quantiser $Q1$ is the source of a white noise with zero mean $\nu_{1}$
-%and $Q2$ is the source of a white noise with zero mean $\nu_{2}$, the
-%following equation can be written for the system in
-%Figure~\ref{fig:sampledsystem}
-%%
-%\begin{equation}
-%\resizebox{0.48\textwidth}{!}{
-%$\tilde{Y}(z)=\tilde R(z)C(z)G(z)-\tilde{Y}(z)C(z)G(z)+\nu_{1}(z)+\nu_{2}(z)G(z),$
-%}
-%\end{equation}
-%
-%\noindent which can be rewritten as
-%%
-%\begin{equation}
-%\label{eq:outputfunctions}
-%\tilde{Y}(z)=C(z)G(z)H(z)R(z)+H(z)\nu_{1}(z)+G(z)H(z)\nu_{2}(z)
-%\end{equation}
-%$$H(z)=\frac{1}{1+C(z)G(z)}$$
-%
-%Note that $H(z)$ cancels the poles of both $G(z)$ and $C(z)$, thus we need only verify the stability of $H(z)$
-%to validate the stability of the whole system.
-%These equations are sufficient for computing $\sigma_{Q}^{2}$.  However,
-%there is still a gap for a complete model for $\Delta{G_{Q}(z)}$ in
-%Eq.~\eqref{eq:deltag_var}, {\it i.e.}, the z-transform of control action
-%$U(z)$.  This indicates that the quantization noise effect on a discrete
-%plant model mainly depends on three main factors:
-%%
-%\begin{itemize}
-%%
-%\item \textbf{Sample time:} the sample time effect is reflected over pulse transfer function that covers the effects of DAC ant its interpolator (ZOH) \red{[clarify/revise based on the comments made above.]};
-%%
-%\item \textbf{ADC and DAC step:} \red{[again, do we need both?]} these are the main component of quantization noise power, but an $8$-bits converter already reduces the effect of quantization noises in the output for negligible values.
-%%
-%\item \textbf{Signal-to-noise ratio (SNR): } the dependence on the value of $U(z)$ \red{[notice that now we have reduced the problem to depend on the effect of the reference signal transform R(z) - pls revise.]} shows the importance of the SNR for handling quantization noise; for a high SNR of the digital controller, the quantization effect is negligible.
-This happens during the transient of the system, when high control actions are employed.
-However, it can be relevant during the steady state.
-A digital controller with integral action might be sufficient for eliminating such influence at steady state.
-%%
-%\end{itemize}
-%
-%An alternative expression for $\Delta{G_{Q}(z)}$ can be obtained from
-%Eq.~\eqref{eq:deltag_var}, transforming it into a function of the reference
-%$R(z)$.  Once $U(z)$ is the control signal obtained via digital controller
-%$C(z)$ and error signal, {\it i.e.},
-%%
-%\begin{equation}
-%U(z)=C(z)\cdot[R(z)-Y(z)],
-%\end{equation} 
-%
-%\noindent where $Y(z)$ is the first term of Eq.~\eqref{eq:outputfunctions}, thus:
-%\begin{equation}
-%\label{eq:controlsignal}
-%\resizebox{0.48\textwidth}{!}{
-%$U(z)=C(z)\cdot \left[R(z)-\frac{C(z)G(z)}{1+C(z)G(z)}R(z)\right]=\frac{C(z)}{1+C(z)G(z)}R(z).$
-%}
-%\end{equation} 
-%
-%Substituting Eq.~\eqref{eq:controlsignal} in Eq.~\eqref{eq:deltag_var}, a
-%model for $\Delta{G_{Q}(z)}$ depending on $R(z)$ can be obtained:
-%%
-%\begin{equation}
-%\Delta{G_{Q}(z)}=\sigma^{2}_{Q}\cdot \frac{1+C(z)G(z)}{C(z)} \cdot \frac{1}{R(z)},
-%\end{equation}
-%
-%\noindent where $R(z)$ can be considered as a step signal (for stabilization
-%purpose) with height equal to $r$, which can be rewritten as
-%%
-%\begin{equation}
-%\Delta{G_{Q}(z)}=\frac{\sigma^{2}_{Q}}{r}\cdot \frac{1+C(z)G(z)}{C(z)} \cdot \frac{z-1}{z}.
-%\end{equation}
-%
-%A more precise description of $\Delta{G_{Q}(z)}$ can be obtained
-%considering FWL \red{[clarify what you mean with FWL, introduce FWL function explicitly and precisely]} effects on digital controller coefficients, as described in
-%Bessa {\it et al.}~\cite{Bessa16}, {\it i.e.}, using $FWL[C(z)]$ instead of
-%the nominal $C(z)$:
-%%
-%\begin{equation}
-%\label{eq:deltaG_final}
-%\Delta{G_{Q}(z)}=\frac{\sigma^{2}_{Q}}{r}\cdot \frac{1+FWL[C(z)]G(z)}{FWL[C(z)]} \cdot \frac{z-1}{z}.
-%\end{equation}
-%
-%Finally, Eq.~\eqref{eq:deltaG_final} is a suitable frequency domain model
-%for quantization noise effects on closed-loop systems.  This model depends
-%on the plant pulse transfer function ($G(z)$), which is described by
-%Eq.~\eqref{eq:pulsetf}, the height of step reference signal $r$, and the
-%digital controller model.
-
-%\subsection{Modelling Error on Parameters Representation} 
-%\label{sec:}
-
-%\red{[TO BE COMPLETED.]}
-% We use CounterExample-Guided Inductive Synthesis (CEGIS), as
-% illustrated in Fig~\ref{fig:CEGIS}.
-
-%specialised it for stream refactoring.  
-% adding JST for stream refactoring
-
-\subsection{Architecture of the Program Synthesizer}
+\paragraph{Architecture of the Program Synthesizer}
 \label{synthesizer-general}
-%
-%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
-%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
 %
@@
 %
-%determines whether
-%it does satisfy the specification on all inputs by checking
-%satisfiability of the following verification formula:
-%
-%$\exists \vec{x} . \lnot \sigma(\vec{x}, \vec{P})$
-%If this formula is unsatisfiable, 
-%% the candidate solution is in fact a 
-%% full solution.
-%
 If this is the case, then the algorithm terminates.  Otherwise, additional
@@
 
-%% the witness $\vec{x}$ denote an input on which the
-%% candidate solution fails to meet the specification.  Thus, $\vec{x}$ is
-%% added to the {\sc inputs} set, and the loop iterates again.
-
 It is worth noting that each iteration of the loop adds a new input to
@@
 
-\subsection{Synthesis for Control}
-\label{synthesis-elements}
-
-\paragraph{Specification of the stability property}
-
-Next, we describe the specific property that we pass to the program
-synthesizer as the specification $\sigma$.  There are two different
-algorithms in DSVerifier that can be used for stability
-verification~\cite{daes20161, Bessa16}, one based on Schur's decomposition
-and another one based on Jury's criteria~\cite{astrom1997computer}.  Here,
-we choose Jury's method~\cite{astrom1997computer}, due to its efficiency,
-and we use this method to check the stability in the $z$-domain for the
-characteristic polynomial $S(z)$ defined in~\eqref{eq:internal_stab_lemma}.
-%
-% of the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$, where $Y(z)$ is the closed-loop system output and U(z) is the controller output. 
-%% \red{[unclear: what matrix? We need to clarify the relationship
-%% between the char. poly. $S(z)$ and the later quantities $\Delta
-%% N_{G}(z), \Delta D_{G}(z)$ and corresponding controller's
-%% structure.]}.
-%
-We~consider the following form for $S(z)$:
-%
-$$
-S(z) = a_0z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N=0, a_0\neq0
-$$
-%
-%\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?}
-
-% Assuming that $\hat{G}(z) = \frac{\hat{N_G}(z)}{\hat{D_G}(z)}$
-% and $\hat{C}(z) = \frac{\hat{N_C}(z)}{\hat{D_C}(z)}$, then:
-% $$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$
-
-Next, the following Jury matrix
-$M = [m_{ij}]_{(2N-2)\times N}$ is built from $S(z)$ coefficients:
-%
-$$
-M=\left( 
-\begin{array}{c}
-V^{(0)}\\
-V^{(1)}\\
-\vdots\\
-V^{(N-2)}
-\end{array}
-\right), 
-$$
-%
-where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ such that:
-%
-$$
-v_{ij}^{(0)}=\left\{
-\begin{array}{ll}
-a_{j-1}, & \texttt{if}~i=1\\
-v_{(1)(N-j+1)}^{0},&\texttt{if}~i=2
-\end{array}
-\right.
-$$
-%
-$$
-v_{ij}^{(k)}=\left\{
-\begin{array}{ll}
-0,&\texttt{if}~j>n-k\\
-v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \texttt{if}~j\leq n-k ~\texttt{and}~i=1\\
-v_{(1)(N-j+1)}^{k},& \texttt{if}~j\leq n-k ~\texttt{and}~i=2\\
-\end{array}
-\right.
-$$
-%
-where $k \in \mathbb{Z}$, such that $0 < k < N - 2$. 
-$S(z)$ is the
-characteristic polynomial of a stable system if and only if the following four conditions hold:
-%\begin{itemize}
-%\item 
-$R_1: S(1) > 0$;
-%\item 
-$R_2: (−1)^N S(−1) > 0$;
-%\item 
-$R_3: |a_0| < a_N$;
-%\item 
-$R_4: m_{11} > 0 \wedge\allowbreak
-      m_{31}>0 \wedge\allowbreak
-      m_{51}>0 \wedge \ldots \wedge\allowbreak
-      m_{(2N{-}3)(1)}>0$.
-%\end{itemize}
-%
-The stability property is then encoded by a constraint of the form:
-$
-\phi_\mathit{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
-$
-%\cdsay{figure out what is existentially quantified for the final $\sigma$.} 
-%% \red{[Yes, intuitively all clear, however for the sake of clarity I would like to see the explicit mapping between the above formula and the previously used specification 
-%% $\sigma(x, P)$, with clear elucidation of the relationship between the domain of $z$ and that of $x$.]}
-
-% \red{[clear elucidation of the mapping between this and the domains used 
-% in the general description of the synthesiser]}
-
-\paragraph{Fixed-point computation in program synthesis}
-
-The program synthesis engine uses fixed-point arithmetic.  Specifically, we
-use the domain $\mathbb{R}\param{I}{F}$ for the controller's coefficients
-and the domain $\mathbb{R}\param{I_p}{F_p}$ for the plant's coefficients,
-where $I$ and $F$, as well as $I_p$ and $F_p$, denote the number of bits for
-the integer and fractional parts, respectively, and $\mathbb{R}\langle
-I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
-%
-%the coefficients for $C(z)$ 
-%$N_c$ and $D_c$ 
-%in the domain $\mathbb{R}\param{I}{F}$, 
-%and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, 
-%where $n_C$ and $m_C$ denote the order of the corresponding polynomials
-%where $I$ and $F$ denote the integer and fractional size, respectively.
-%Regarding the plant, its coefficients are this is synthesised over the 
-%domain $\mathbb{R}^{n_G+m_G}\param{I_p}{F_p}$, where $n_G$ and $m_G$ 
-%denote the order of the polynomials representing the 
-%numerator and denominator of the plant's transfer function, respectively. 
-%Again, $I_p$ and $F_p$ denote the integer and fractional size, respectively, with
-%$\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
-%
-Given the use of fixed-point arithmetic, we examine the discretization effect 
-during these operations. Let $\tilde C(z)$ and $\tilde G(z)$ be 
-transfer functions represented using fixed-point bit-vectors.
-%  with integer size $I_p$ and fractional
-% size $F_p$, whose domain is $\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
-%
-\begin{align}
-\small
-\label{digital_controller_plant_tf}
-\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
-%\label{plant_tf}
-\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
-\end{align}
-
-Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
-domain,
-%
-$$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
-%
-However, given a real plant $\hat{G}(z)$, and a discretizing function
-%
-\begin{align}
-\small
-\label{FWL_tf}
-\mathcal{F}&\langle I_p,F_p \rangle : \mathbb{R} \rightarrow  \mathbb{R}\langle I_p,F_p \rangle\\
-&\triangleq \tilde x = \mathcal{F}\langle I_p,F_p \rangle(x) : \tilde x=x-(x\bmod\tilde x)\nonumber\\
-\mathcal{F}_n&\langle I_p,F_p \rangle(P \in \mathcal{P}) \\
-&=\tilde P \in \mathcal{P}^{n}\langle I_p,F_p \rangle : c_i \in \vec{P} \wedge \tilde c_i \in \vec{\tilde{P}}=\mathcal{F}\langle I_p,F_p \rangle(c_i)  \nonumber
-\end{align}
-%
-we calculate $\tilde G(z)=\mathcal{F}_{M_G,N_G}\langle I_p,F_p \rangle(\hat{G}(z))$
-%
-\begin{align}
-% \label{digital_controller_tf}
-% \tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_b \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
-% &= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
-%
-\label{digital_plant_tf}
-\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_b \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_b \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_b \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_b \hat{a}_{N_G})z^{-N_G}} \nonumber \\
-&\Rightarrow \vec{\tilde G} =\vec{\hat{G}}+\Delta_b{\vec{G}}=\vec{G}+\Delta_p{\vec{G}}+\Delta_b{\vec{G}}.
-\end{align}
-%
-where $\Delta_b\hat{c}_i=\hat{c}_i\bmod \tilde{c}_i$
-and $\Delta_b{G}$ represent the plant uncertainty caused by
-the rounding off effect.  We encompass all the uncertainty as
-$\Delta{\vec{G}}=\Delta_p{\vec{G}}+\Delta_b{\vec{G}}$. 
-%
-As the cost of SAT solving increases with in the size of the problem
-instance, our algorithm tries to solve the problem first for small $I_p$,
-$F_p$, iteratively increasing the precision if it is insufficient.
-
-\paragraph{Our synthesis problem}
-The synthesis problem we are trying to solve is the following:
-find a digital controller $C(z)$ %denoted by  $N_c$ and $D_c$ 
-that makes the closed-loop system stable 
-for all possible uncertainties 
-%$\Delta{\vec{p}}$ (\ref{eq:uncertainty}).
-$\tilde G(z)$ (\ref{digital_plant_tf}).
-%, where we precisely describe 
-%$(\Delta N_G, \Delta D_G)$. 
-% Note that, similar to the rest of the paper, we use the notation 
-% $\tilda{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
-% $\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
-When mapping back to the notation used for describing the general architecture 
-of the program synthesizer, the controller $C(z)$ denotes $P$ and 
-$\tilde G(z)$ represents $x$.
-
-As mentioned above, we compute the coefficients for $C(z)$ 
-%$N_c$ and $D_c$ 
-in the domain $\mathbb{R}\param{I}{F}$, 
-%and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, 
-%where $n_C$ and $m_C$ denote the order of the corresponding polynomials
-and those for $\tilde G(z)$ in the domain
-$\mathbb{R}\langle I_p,F_p \rangle$.
-While the controller's precision $\param{I}{F}$ is given, 
-we can vary $\param{I_p}{F_p}$ such that 
-$\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
-
-\subsection{The {\sc Synthesize} and {\sc Verify} phases}
-
-The {\sc synthesize} phase uses BMC to 
-compute a solution $C(z)$. % An important remark is that this 
-% controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
-% domain.
-There are two approaches for the {\sc verify} phase.
-% based on the described model.  
-The first approach uses interval arithmetic \cite{moore1966interval}
-to represent the coefficients
-$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i,\,\allowbreak
-{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_p})]$ 
-and rounds operations outwards during calculations.  This effectively allows
-us to simultaneously evaluate the whole collection of plants $\mathfrak{G}$
-plus the effects of numeric calculations in the engine.  Synthesized
-controllers using this verifier will always be stable for all plants in the
-family.
-% and only generate counterexamples when the precision of the
-%engine is insufficient (\emph{ie} no stable plant could be found). 
-Our preliminary experiments showed that a synthesis approach
-using this verification engine has poor performance and we
-%Given the high computational cost of this
-%approach, 
-therefore designed a second approach, which we describe below.
-Our experimental results described in Section~\ref{sec:experiments}
-%try both approaches and provide the time for the fastest. 
-show that the speedup yielded by the second approach 
-is in most cases of at least two orders of magnitude.
-
-The second approach is illustrated in Figure~\ref{fig:CEGIS} and uses a
-two-stage verification: the first stage performs potentially unsound
-fixed-point operations assuming a plant precision \param{I_p}{F_p}, and the
-second stage restores soundness by validating these operations using
-interval arithmetic on the synthesized controller.
 %
@@
 }
-\caption{Counterexample-Guided Inductive Synthesis of Closed-loop Systems (Step~D)
+\caption{Counterexample-Guided Inductive Synthesis of Closed-loop Systems
 \label{fig:CEGIS}}
@@
 %
-%
-In more detail, in the first stage, denoted by {\sc Uncertainty} in
-Figure~\ref{fig:CEGIS}, assuming a precision \param{I_p}{F_p} we check
-whether the system is unstable for the current candidate solution, i.e., if
-$\neg \phi_\mathit{stability}$ is satisfiable for~$S(z)$.  If this is the
-case, then we obtain a counterexample~$\tilde G(z)$,
-%
-%denoted by values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
-%\red{[see my comment above - these quantities pop up too abruptly.]},
-%
-which makes the closed-loop system unstable.  This uncertainty is added to
-the set {\sc inputs} such that, in the subsequent {\sc synthesize} phase, we
-obtain a candidate solution consisting of a controller $C(z)$, which makes
-the closed-loop system stable for all the uncertainties accumulated in {\sc
-inputs}.
-
-If the {\sc Uncertainty} verification stage concludes that the system is
-stable for the current candidate solution, then we pass this solution to the
-second verification stage, {\sc Precision}, which checks the propagation of
-the error in the fixed-point calculations using a Fixed-point Arithmetic
-Verifier based on interval arithmetic.
-%
-% To achieve this, we use a nondeterministic plant selected from $\mathfrak{G}(z)$ where the expected error of the bit vector calculations is assumed to be within the expected bounds and verified after synthesis using the interval version of the program.
-%
-% The first verification phase produces a counterexample if some instance of $\mathfrak{G}(z)$ does not verify the properties and the CEGIS loop iteratively looks for a new controller that verifies the supplied counterexamples.
-The second phase verifies the propagation of the error in the fixed point calculations.
-% If the second phase fails verification, we increase the precision of the analyser and feed the CEGIS loop again to find a sound solution. 
-% vouches for the use of CEGIS in most of our benchmarks.
-% \cdsay{end of integration}
-
-If the {\sc precision} verification returns $\mathit{false}$, then we
-increase the precision of \param{I_p}{F_p} and re-start the {\sc
-  synthesize} phase with an empty {\sc inputs} set.  Otherwise, we
-found a full sound solution for our synthesis problem and we are done.
-
-In the rest of the paper, we will refer to the two approaches 
-for the {\sc verify} phase as one-stage and two-stage, respectively.
-
-%-----------------------------
-\subsection{Soundness}
-%-----------------------------
-
-While the {\sc synthesise} phase searches for potentially unsound 
-candidate solutions, the soundness of the model is ensured by the {\sc verify} phase.  
-If a candidate solution is validated by the verifier, it is necessarily
-sound.
-
-Through its two stages, the {\sc verify} phase looks at two separate elements for
-soundness.
-% The first ensures that there exists no
-% counterexample plant that would create a closed-loop with unstable
-% poles. The fixed word length of the controller is not relevant at this
-% point since the parameters have already been chosen to fit this
-% criteria (i.e., the candidate solution is FWL).
-The first stage ensures that no counterexample
-plant with an unstable closed loop exists with % If no such
-% system exists, then the controller is stable for all
-% plants in the collection with
-the limitations given by the data
-type used by the verifier. Since the actual
-plant works in the reals, whereas we use fixed/floating point
-arithmetic to evaluate it, we need to ensure that the rounding errors
-in the caculations do not cause the solution to be unsound.
-
-For this reason the second verification stage uses interval arithmetic with
-outward rounding to ensure that these errors do not exceed critical
-bounds that could make some (or all) plant(s) unstable. This means
-that whilst the solution may not be complete, it is sound for
-evaluating any collection of real plants with a defined FWL controller
-for all of them. We require two verification stages because,
-while the second phase can ensure the stability of all plants in
-the collection, it is unable to provide a counterexample.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Illustrative Example} \label{sec:running-ex}
-
-We illustrate our approach with a classical cruise control example,
-extracted from the literature~\cite{Astrom08}.  The example highlights the
-challenges that arise when using finite-precision arithmetic in digital
-control.  We are given a discrete plant model (with a time step of
-$0.2$\,s), which is represented by the following $z$-expression:
-%
-\begin{equation}
-\label{Eq:running-example-plant}
-G(z) = \frac{0.0264}{z-0.9998}.
-\end{equation}
-
-Using an optimization tool, the authors
-of~\cite{DBLP:conf/hybrid/WangGRJF16} have designed a high-performance
-controller for this plant, which is characterized by the following
-$z$-domain transfer function:
-%
-\begin{equation}
-\label{Eq:running-example-controller}
-C(z) = \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
-\end{equation}
-%
-The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that this controller
-$C(z)$ (Eq.~\eqref{Eq:running-example-controller}) stabilizes the
-closed-loop system for the discrete plant model $G(z)$
-(Eq.~\ref{Eq:running-example-plant}).  However, if the effects of
-finite-precision arithmetic are considered (e.g., fixed-point arithmetic and
-word-length), then this closed-loop system becomes unstable.
-%
-For instance, an implementation of $C(z)$ using \param{4}{16} fixed-point
-numbers (i.e., $4$ bits for the integer part and $16$ bits for the
-fractional part) can be modeled as:
-%
-\begin{equation}
-\label{Eq:running-example-controller-quantized}
-\resizebox{.47\textwidth}{!}{
-$C_{q}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
-{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$
-}
-\end{equation} 
-%
-The resulting system using the typical series loop configuration, where
-$C_{q}(z)$ and $G(z)$ are in the forward path, is unstable. 
-Figure~\ref{fig:original} gives the Bode diagram for the digital controller
-represented by Eq.~\eqref{Eq:running-example-controller}.  The phase margin
-is negative, which means that the controller represented by
-Eq.~\eqref{Eq:running-example-controller} is unstable, considering FWL
-effects.
-
-\subsection{Program Synthesis for the Example}
-%
-We now demonstrate how our approach solves the synthesis problem for the
-example given in the previous section.  We start with the candidate solution
-with all coefficients zero, as given below, and a precision of $I_p=16$,
-$F_p=24$.  The digital controller is designed with standard techniques for
-control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}.
-%
-%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
-%
-%$$
-%\begin{array}{ll}
-%N_C(z) {=} 0z^2{+}0z{+}0\\
-%D_C(z) {=} 0z^2{+}0z{+}0\\
-%\end{array}
-%$$
-$$ C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0} $$
-
-In the first {\sc verify} stage, the {\sc uncertainty} 
-check finds the following counterexample:
-%
-$$ \tilde G(z) = \frac{0.026506}{1.000610z+1.002838} $$
-
-%$$
-%\begin{array}{ll}
-%\Delta N_G(z) = 0.026506\\
-%\Delta D_G(z) = 1.000610z+1.002838
-%\end{array}
-%$$
-
-We add this counterexample to {\sc inputs} and initiate the {\sc synthesize}
-phase, where we obtain the following candidate solution:
-%
-%\red{[ How is the order of the candidate solution chosen here?]}
-$$
-C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}
-$$
-
-This time, the {\sc uncertainty} check does not find any
-counterexample and we pass the current candidate solution to the {\sc
-precision} verification stage.
-%
-% In the second {\sc verify} phase, we check whether the current candidate
-% solution above is the final solution. It is not and the verifier signals
-% that it is due to lack of precision.
-%
-We obtain the result $\mathit{false}$, meaning that the current precision is
-insufficient.  Consequently, we increase our precision to $I_p=20$, $F_p=28$.
-%
-Since the previous counterexamples were obtained at lower precision, we
-remove them from the set of counterexamples.  Back in the {\sc synthesize}
-phase, we re-start the process with a candidate solution with all
-coefficients $0$.  Next, the {\sc uncertainty} verification stage provides
-the first counterexample at higher precision:
-%
-%$$
-%\begin{array}{ll}
-%\Delta N_G(z) {=} 0.026314\\
-%\Delta D_G(z) {=} 0.999024z{-}1.004785
-%\end{array}
-%$$
-$$ \tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785} $$
-
-In the {\sc synthesize} phase, we get a new candidate solution that
-eliminates the new, higher precision counterexample:
-%
-$$ C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357} $$
-%
-%$$
-%\begin{array}{ll}
-%N_C(z) {=} \\
-%D_C(z) {=} \\
-%\end{array}
-%$$
-
-This candidate solution is validated  as the final solution by both stages
-{\sc uncertainty} and {\sc precision} in the {\sc verify} phase. 
-Figure~\ref{fig:bode} compares the Bode diagram using the digital controller 
-represented by Eq.~\eqref{Eq:running-example-controller}
-from~\cite{DBLP:conf/hybrid/WangGRJF16} (Figure~\ref{fig:original}) and the
-final candidate solution from our synthesizer
-(Figure~\ref{fig:cegiscontroller}).  The \tool final solution is stable
-since it presents an infinite phase margin and a gain margin of $17.8$\,dB.
-
-%, which fails to find a new counterexample (i.e. returns UNSAT).
-
-% \blue{
-% For the same cruise control system, the synthesis may be done considering that the plant model have parametric uncertainties ($\Delta G_{P}(z)$).
-Thus, the synthesised controller must to stabilize for any parametric variation $\Delta p$ inside of a given region.
-Specially, in this example, was assumed that each coefficient of $G(z)$ may vary $\pm 0.5\%$.
-% }
-
-% \blue{Initially, the controller denominator and numerator  ($D_{C}(z)$ and $N_{C}(z)$) are started with zero coefficients, as in previous example.
-Thus,  in the first {\sc verify} phase a counterexample is presented, that is added to {\sc inputs}, whis is used in the first  {\sc synthesise} phase.
-The resulting controller is:
-% }
-% $$
-% {
-% \blue{
-% C(z)=\frac{0.77516z^2{+}-0.71497z{+}0.03729}{0.25024z^2{-}0.01799z{+}0.00097}
-% }}
-% $$
-
-% \blue{In the second {\sc verify} phase, the controller failed to stabilize the system for all the range of uncertainties, another counterexample was provided, and the following candidate controller is presented in another {\sc synthesise} phase:}
-% $$
-% {
-% \blue{
-% C(z)=\frac{0.68970z^2{+}0.36538z{+}0.30637}{0.06862z^2{+}0.00394z{+}0.00802}
-% }}
-% $$
-
-% \blue{
-% This candidate solution is validated as the final solution by the next 
-% {\sc verify} phase.
-% }
-%
-\begin{figure}[htb]
-    \centering
-    \begin{subfigure}[b]{0.4\textwidth}
-        \includegraphics[width=\textwidth]{figures/runningexample_bd0.pdf}
-        \caption{Original controller~\cite{DBLP:conf/hybrid/WangGRJF16}}
-        \label{fig:original}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.4\textwidth}
-        \includegraphics[width=\textwidth]{figures/runningexample_bd2.pdf}
-        \caption{Controller synthesized by \tool}
-        \label{fig:cegiscontroller}
-    \end{subfigure}
-    \caption{Bode diagram for original~\cite{DBLP:conf/hybrid/WangGRJF16} and synthesized closed-loop systems}\label{fig:bode}
-\end{figure}
-
-Figure~\ref{fig:step} illustrates the step responses of the closed-loop
-system with the original controller represented by
-Eq.~\eqref{Eq:running-example-controller} (Figure~\ref{fig:step0}), the
-first (Figure~\ref{fig:step1}) and final (Figure~\ref{fig:step2}) candidate
-solutions provided by \tool.  The step response in Figure~\ref{fig:step0}
-confirms the stability loss if we consider FWL effects.  However,
-Figure~\ref{fig:step1} shows that the first candidate controller is able to
-stabilize the closed-loop system without uncertainties, but it is rejected
-during the {\sc precision} phase by \tool since this solution is not
-considered to be sound.  Finally, Figure~\ref{fig:step2} shows a stable
-behavior for the final (sound) solution, which presents a lower settling
-time.
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/runningexample_step0.pdf}
-        \caption{Original controller}
-        \label{fig:step0}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/runningexample_step1.pdf}
-        \caption{First solution by \tool}
-        \label{fig:step1}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/runningexample_step2.pdf}
-        \caption{Final solution by \tool}
-        \label{fig:step2}
-    \end{subfigure}
-    \caption{Step responses for original~\cite{DBLP:conf/hybrid/WangGRJF16}
-             closed-loop system with FWL effects and for each
-             {\sc synthesize} iteration of \tool}\label{fig:step}
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Experimental Evaluation}\label{sec:experiments}
-
-%This section is split into three parts. Section~\ref{experimental-setup}
-%discusses the experimental setup and our benchmarks, while
-%Section~\ref{experimental-objectives} describes the experimental objectives. 
-%Section~\ref{experimental-results} presents the experimental results
-%obtained on the benchmarks with our tool \tool.
-
-%---------------------------------
-\subsection{Description of the Benchmarks}
-\label{experimental-setup}
-%---------------------------------
-
-The first set of benchmarks uses the discrete model $G_1(z)$ of a cruise control
-system for a car, and accounts for rolling friction, aerodynamic drag, and
-the gravitational disturbance force~\cite{Astrom08}. 
-%The plant model is given as follows:
-%
-%\begin{equation}
-%\label{cruise-control-c1}
-%G_1(z)=\frac{0.0264}{z-0.998} \nonumber
-%\end{equation} 
-%
-The second set of benchmarks considers the discrete model $G_2(z)$ 
-of a simple spring-mass damper plant~\cite{DBLP:conf/hybrid/WangGRJF16}. 
-%where the discrete 
-%plant dynamics is represented by the following $z$-expression:
-%
-%\begin{equation}
-%\label{spring-mass-damper-g}
-%G_2(z)=\frac{5\times{10^{-5}}z + 5\times{10^{-5}}}{z^2 - 2z + 1.0001}. \nonumber
-%\end{equation} 
-%
-A third set of benchmarks uses the discrete model $G_{3}(z)$ for satellite attitude 
-dynamics~\cite{Franklin15}, which require attitude (pose) control
-for orientation of antennas and sensors w.r.t.~earth.
-The fourth set of benchmarks presents an alternative discrete model $G_4(z)$ 
-of a cruise control system~\cite{DBLP:conf/hybrid/WangGRJF16}. 
-%The satellite
-%attitude control is typically used for three-axis attitude tracking, but
-%here we consider only one axis at a time.  
-%The motion equation for the
-%one-axis system, disregarding disturbance torques, is given by
-%
-%\begin{equation}
-%\label{eq:satelliteode}
-%I\cdot \ddot{\theta} = \tau_{C}, 
-%\end{equation}
-%
-%\noindent where $I$ is the satellite inertia moment about its mass
-%center, $\tau_{C}$ is the control torque applied by the thrusters, and
-%$\theta$ is the controlled attitude angle.  Normalizing
-%Eq.~\eqref{eq:satelliteode} by defining the control signal
-%$u=\frac{\tau_{C}}{I}$ and taking the Laplace transform, the following
-%$s$-domain transfer function $G(s)$ is obtained:
-%
-%\begin{equation}
-%\label{eq:satellitetf}
-%G_{3}(s)=\frac{\theta(s)}{u(s)}=\frac{1}{s^2},
-%\end{equation}
-%
-%\noindent Using the ZOH discretization defined in Eq.~\eqref{eq:pulsetf}, 
-%we get the following $z$-domain model:
-%
-%\begin{equation}
-%G_{3}(z)= \frac{T^{2}}{2} \frac{z+1}{(z+1)^{2}}. \nonumber
-%\end{equation}
-%
-%
-%\begin{equation}
-%\label{exampleA}
-%G_{4}(s)=\frac{s-1}{s^{2}-s-2},
-%\end{equation}
-%
-%\noindent We can obtain $G_{4}(z)$ using the ZOH discretization defined
-%in Eq.~\eqref{eq:pulsetf} with three different sample times ($0.1$, $0.05$,
-%and $0.03$ seconds), respectively, as follows:
-%
-%\begin{equation}
-%\label{exampleA-sampletime1}
-%G_{4a}(z)=\frac{0.100342181002722z - 0.110876810062963}{1.0z^{2} - 2.12624017619613z + 1.10517091807565}, \nonumber
-%\end{equation}
-%
-%
-%\begin{equation}
-%\label{exampleA-sampletime2}
-%G_{4b}(z)=\frac{0.0500422033454653z - 0.0526068264456340}{1.0^{2} - 2.05640034257636z + 1.05127109637602}, \nonumber
-%\end{equation}
-%
-%\begin{equation}
-%\label{exampleA-sampletime3}
-%G_{4c}(z)=\frac{0.0300090687252212z - 0.0309228417953966}{1.0^{2} - 2.03228208009387z + 1.03045453395352}. \nonumber
-%\end{equation}
-%
-The fifth and sixth set of benchmarks describe the discrete model 
-of a DC servo motor velocity dynamics~\cite{exampleCAD,Tan01}.
-
-The seventh set of benchmarks contains the discrete well-studied 
-non-minimal phase model $G_{7}(z)$. Non-minimal phase model offers 
-additional difficulties for the controller design~\cite{Doyle:1991:FCT:574259}.
-%
-%The fifth set of benchmarks contains the \textit{DC Motor Rate} discrete model $G_{5}(z)$, which 
-%describes the angular velocity of a DC Motor plant~\cite{Franklin15}. 
-%
-%\begin{equation}
-%\label{DC-Motor-Rate}
-%G_{5}(z)=\frac{ 0.1898z + 1.8027\times{10^{-4}}}{1.0z^{2} -0.9012z -1.0006\times{10^{-16}}}. \nonumber
-%\end{equation}
-%
-The eighth set of benchmarks contains the \textit{Helicopter Longitudinal Motion} discrete model $G_{8}(z)$,
-which provides the longitudinal motion dynamics of a helicopter~\cite{Franklin15}. 
-%
-%\begin{equation}
-%\label{Helicopter-Longitudinal-Motion}
-%G_{6}(z)=\frac{15.1315z^{2} + 17.8600z + 17.4549}{z^{3} -2.6207z^{2} + 2.3586z -0.6570}. \nonumber
-%\end{equation}
-%
-The ninth  set of benchmarks contains the \textit{Inverted Pendulum} discrete model $G_{9}(z)$, which 
-describes a pendulum dynamics with its center of mass above its pivot point~\cite{Franklin15}. 
-%
-%\begin{equation}
-%\label{Inverted-Pendulum}
-%G_{7}(z)=\frac{0.0263z^{2} + 0.0143z -0.0383}{z^{4} -4.2553z^{3} + 6.5105z^{2} -4.2553z + 1}. \nonumber
-%\end{equation}
-%
-The tenth set of benchmarks contains the \textit{Magnetic Suspension} discrete model $G_{10}(z)$, which describes the dynamics of a mass that levitates with support only of a magnetic field~\cite{Franklin15}.
-%
-%\begin{equation}
-%\label{Magnetic-Suspension}
-%G_{8}(z)=\frac{6.769\times{10^{13}}z + 6.784\times{10^{13}}}{z^{2} -5.415\times{10^{13}}z + 4.23\times{10^{11}}}. \nonumber
-%\end{equation}
-
-%The ninth set of benchmarks contains the \textit{1/4 Car Suspension} discrete model $G_{9}(z)$,
-%which represents the dynamics of a single wheel suspension plant, {\it i.e.}, a system that connects a car to a wheel and allows relative motion between both %parts~\cite{Franklin15}.
-%
-%\begin{equation}
-%\label{Car-Suspension}
-%G_{8}(z)=\frac{0.25z^{3} + 0.5z^{3} + 0.25z -5.7065\times{10^{-10}}}{z^{3} + 6.8455\times{10^{-9}}z^{2} + 3.3925\times{10^{-17}}z - 3.4667\times%{10^{-94}}}. \nonumber
-%\end{equation}
-%
-The eleventh set of benchmarks contains the \textit{Computer Tape Driver} discrete model $G_{11}(z)$, which 
-describes a system to read and write data on a storage device~\cite{Franklin15}.
-%
-%\begin{equation}
-%\label{Computer-Tape-Driver}
-%G_{10}(z)=\frac{0.0200z -3.8303\times{10^{-176}}}{1.0z -4.6764\times{10^{-166}}}. \nonumber
-%\end{equation}
-%
-The last set of benchmarks considers the discrete model $G_{12}(z)$
-that is typically used for evaluating stability
-margins and controller fragility~\cite{bhattacharyya97, keel_Bhattacharyya_examples}.
-
-All experiments were conducted on a 12-core 2.40\,GHz Intel Xeon E5-2440
-with 96\,GB of RAM and Linux OS.  All times given are wall clock time in
-seconds as measured by the UNIX date command.  For the two-stage verification 
-engine we apply a timeout of $8$ hours per benchmark, and $24$ hours for the approach 
-using a one-stage engine.
-
-%---------------------------------
-\subsection{Objectives}
-\label{experimental-objectives}
-%---------------------------------
-
-Using the closed-loop control system benchmarks given in
-Section~\ref{experimental-setup}, our experimental evaluation aims to answer
-two research questions:
-%
-\begin{enumerate}
-
-\item[RQ1] \textbf{(performance)} does the CEGIS approach generate a 
-FWL digital controller in a reasonable amount of time?
-
-\item[RQ2] \textbf{(sanity check)} are the synthesized controllers sound
-and can their stability be confirmed outside of our model?
-
-\end{enumerate}
-
-%---------------------------------
-\subsection{Results}
-\label{experimental-results}
-%---------------------------------
-
-We give the run-times required to synthesize a stable controller for each
-benchmark in Table~\ref{tab:results}.  Here, \textit{Plant} is the discrete
-or continuous plant model, \textit{Benchmark} is the name of the employed
-benchmark, \textit{I} and \textit{F} represent the number of integer and
-fractional bits of the stable controller, respectively, while \textit{Time}
-is the total time (in seconds) required to synthesize a stable controller
-for the given plant.
-
-For the majority of our benchmarks, the conjecture explained in
-Section~\ref{synthesis-elements} holds and the two-stage verification 
-engine is able to find a stable solution in less than one minute for half
-of the benchmarks. This is possible if the inductive solutions need to be 
-refined with few counterexamples and increases of the fixed-point precision.  
-However, the benchmark \emph{SatelliteB2} with uncertainty ($G_{3b}$)
-required too many counterexamples to refine its solution.  
-For this particular case, the one-stage engine is able to complement the
-two-stage approach and synthesize a solution instead.  It is important to
-reiterate that the one-stage verification engine does not take advantage of
-the inductive conjecture inherent to CEGIS, but instead fully explores the
-counterexample space in one SAT instance.  As expected, this approach is
-significantly slower on average and is only useful for benchmarks where
-the CEGIS approach requires too many counterexample refinement iterations
-such that exploring all counterexamples in a single SAT instance performs better.
-Our results suggest an average performance difference of at least two orders
-of magnitude between the two engines, leading to the one-stage engine timing
-out on the majority of our benchmarks.  Table~\ref{tab:results}
-lists the results for both engines, where in $16$ out of $23$
-benchmarks the two-stage engine is faster.
-
-\begin{table}
-\centering
-\scalebox{0.8}{
-\begin{tabular}{| r | c | l | r r || r | r |}
-\hline
-\# & Plant  & Benchmark                  & $I$ & $F$
-   & 2-stage & 1-stage
-    \\\hline\hline
-1  & $G_{1a}$  & CruiseControl02
-            &   4 &  16 & \textbf{12\,s}   & 67\,s     \\
-2  & $G_{1b}$  & CruiseControl02$^\dagger$
-            &   4 &  16 & 14600\,s   & \textbf{52\,s}     \\
-3  & $G_{2a}$  & SpgMsDamper
-            &  15 &  16 & \textbf{52\,s}   & 318\,s     \\
-4  & $G_{2b}$  & SpgMsDamper$^\dagger$
-            &  15 &  16 & \xmark  & \xmark    \\
-5  & $G_{3a}$  & SatelliteB2
-            &   3 &   7 & \textbf{36\,s}    & \xmark     \\
-6  & $G_{3b}$  & SatelliteB2$^\dagger$
-            &   3 &   7 & \xmark  & \textbf{4111\,s}  \\
-7  & $G_{3c}$  & SatelliteC2
-            &   3 &   5 & \textbf{3\,s}    & 205\,s    \\
-8  & $G_{3d}$  & SatelliteC2$^\dagger$
-            &   3 &   5 & \textbf{50\,s}  & 1315\,s    \\
-9  & $G_4$  & Cruise
-            &   3 &   7 & 1\,s  & 1\,s    \\
-10 & $G_5$  & DCMotor
-            &   3 &   7 & \textbf{1\,s}  & 10\,s    \\
-11 & $G_6$  & DCServomotor
-            &   4 &  11 & \textbf{46\,s}  & \xmark    \\
-12 & $G_7$  & Doyleetal
-            &   4 &  11 & \textbf{8769\,s}  & \xmark    \\
-13 & $G_8$  & Helicopter
-            &   3 &   7 & \textbf{44\,s}  & \xmark    \\
-14 & $G_9$  & Pendulum
-            &   3 &   7 & \textbf{1\,s}  & 14826\,s    \\
-15 &$G_{10}$& Suspension
-            &   3 &   7 & \textbf{1\,s}  & 5\,s    \\
-16 &$G_{11}$& Tapedriver
-            &   3 &   7 & 1\,s  & 1\,s    \\
-17 &$G_{12a}$& a\_ST1\_IMPL1
-            &  16 &   4 & \textbf{11748\,s} & \xmark   \\
-18 &$G_{12a}$& a\_ST1\_IMPL2
-            &  16 &   8 & \textbf{351\,s}  & \xmark   \\
-19 &$G_{12a}$& a\_ST1\_IMPL3
-            &  16 &  12 & \textbf{8772\,s}   & \xmark   \\
-20 &$G_{12b}$& a\_ST2\_IMPL1
-            &  16 &   4 & \textbf{1128\,s}  & \xmark   \\
-21 &$G_{12b}$& a\_ST2\_IMPL2
-            &  16 &   8 & \xmark  & \xmark    \\
-22 &$G_{12b}$& a\_ST2\_IMPL3
-            &  16 &  12 & \textbf{15183\,s} & \xmark   \\ 
-23 &$G_{12c}$& a\_ST3\_IMPL1
-            &  16 &   4 & \xmark & \xmark   \\\hline
-\end{tabular}}\\[0.2ex]
-\caption{\tool results ({\xmark} = time-out, $\dagger$ = 
-uncertainty)
-\label{tab:results}}
-\end{table}
-%---------------------------------
-
-Considering the faster engine for each benchmark (marked as bold in Table~\ref{tab:results}), 
-the median run-time amounts to $48$\,s, implying that \tool can synthesize half of the controllers 
-in less than one minute. Overall, the average fastest synthesis time considering
-both engines is approximately $42$ minutes.  We
-consider these times short enough to be of practical use to control
-engineers, and thus affirm RQ1.  We further observe that the approach using
-the two-stage verification engine is able to synthesize stable controllers
-in $19$ out of the $23$ benchmarks, and can be complemented using the
-one-stage engine, which is faster for two benchmarks where the inductive
-conjectures fail.  Both verification engines together enable controller
-synthesis for $20$ out of $23$ benchmarks.  For the remaining benchmarks
+\paragraph{Experimental Evaluation}\label{sec:experiments}
+
+The median run-time amounts to $48$\,s, implying that \tool can synthesize half of the controllers 
+in less than one minute. We consider these times short enough to be of practical use to control
+engineers.  We further observe that the approach is able to synthesize stable controllers
+in $20$ out of the $23$ benchmarks.  For the remaining benchmarks
 our approach failed to synthesize a stable controller within the time
@@
 arithmetic instead.  The synthesized controllers were confirmed to be stable
-outside of our model representation using MATLAB, positively answering RQ2.
-A~link to the full experimental environment, including scripts to reproduce
-the results, all benchmarks and the \tool tool, is provided in the
-footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}}\footnote{CBMC version: 7a6cec1dd0eb8843559591105235f1f2c4678801}
-
-%--------------------------------------
-\subsection{Threats to Validity}
-%--------------------------------------
-
-We report a favourable assessment of \tool over a diverse set of real-world
-benchmarks. Nevertheless, this set of benchmarks is limited within the
-scope of this paper and \tool's performance may not generalize to other
-benchmark scenarios. This can be addressed by expanding the benchmark set
-in future experiments.
-
-Furthermore, our algorithm to select suitable FWL word widths to model
-plant behavior employs a heuristic based on user-provided controller
-word-width specifications.  Given the encouraging results of our benchmarks,
-this heuristic appears to be strong enough for the current benchmark set,
-but this may not generalize.  Further experiments towards determining
-suitable plant FWL configurations may thus be necessary in future work.
-
-Finally, the experimental results obtained using \tool for stability
-properties may not generalize to other properties.  The inductive nature of
-the two-stage back-end of \tool increases performance significantly compared
-to the one-stage back-end, but this performance benefit introduced by CEGIS'
-inductive generalizations may not be observed for other controller
-properties.  Additional experiments are necessary to confirm that the
-performance of our inductive synthesis approach can be leveraged in those
-scenarios.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Related Work}\label{sec:related}
-
-\paragraph{Robust synthesis of Linear Systems}
-
-The problem of parametric control synthesis based on stability measures for
-continuous Linear Time Invariant (LTI) Single Input-Single Output (SISO)
-systems has been researched for several decades.  On a theoretical level it
-is a solved problem~\cite{wonham1967pole}, for which researchers
-continuously seek better results for a number of aspects in addition to
-stability.  A vast range of pole placement techniques such as Moore's
-algorithm for eigenstructure assignment~\cite{klein1977eigenvalue} or the
-more recent Linear Quadratic Regulator (LQR)~\cite{bemporad2002explicit}
-have been used in several studies with increasing degrees of success to
-ensure stability.  The latter approach highlights the importance of
-conserving energy during the control process, which results in lower running
-costs.  Since real systems are subject to tolerance and noise as well as the
-need for economy, more recent studies focus on the problem of achieving
-robust stability with minimum gain~\cite{schmid2014unified,
-konigorski2012pole}.  However, when applied with the aim of synthesising a
-digital controller, many of these techniques lack the ability to produce
-sound or stable results because they disregard the effects of quantization
-and rounding.  Recent papers on implementations/synthesis of LTI digital
-controllers~\cite{das2013lqr, ghosh2013fpga} focus on time discretization,
-failing to account for these error-inducing effects and can result in digital 
-systems that are unstable even though they have been proven to be
-robustly stable in a continuous space.
-
-\paragraph{Formal Verification of Linear Digital Controllers}
-
-Researchers in formal verification of control systems have studied various
-effects of discretizing the dynamics, including delayed
-response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics with
-the goal to either verify (e.g.~\cite{daes20161}) or optimize
-(e.g.~\cite{oudjida2014design}) given implementations.
-
-There are two different problems that arise from FWL semantics.  The first
-is the error in the dynamics caused by the inability to represent the exact
-state of the physical system while the second relates to rounding errors
-during computation.  In~\cite{fialho1994stability}, a stability measure
-based on the error of the digital dynamics ensures that the deviation
-introduced by FWL does not make the digital system unstable.  A~recent
-approach~\cite{DBLP:journals/automatica/WuLCC09} uses the $\mu$-calculus to
-directly model the digital controller so that the selected parameters are
-stable by design.  Most work in verification focuses on finding a correct
-variant of a known controller, looking for optimal parameter
-representations using FWL, but ignore the effects of rounding errors due to
-issues of mathematical tractability.  The analyses
-in~\cite{DBLP:conf/hybrid/WangGRJF16, DBLP:conf/hybrid/RouxJG15} rely on an
-invariant computation on the discrete system dynamics using Semi-Definite
-Programming (SDP).  While the former uses BIBO properties to determine
-stability, the latter uses Lyapunov-based quadratic invariants.  In both
-cases, the SDP solver uses floating-point arithmetic and soundness is
-checked by bounding the error.  An alternative approach is taken
-by~\cite{park2016scalable}, where the verification of existing code is
-performed against a known model by extracting an LTI model of the code
-through symbolic execution.  In order to account for rounding errors, an
-upper bound is introduced in the verification phase.  If~the error of the
-implementation is lower than this tolerance level, then the verification is
-successful.
-
-\paragraph{Robust Synthesis of FWL Digital Controllers}
-
-There is no technique in the existing literature for automatic synthesis of
-fixed-point digital controllers that considers FWL effects.
-%  Parameter
-%synthesis tools such as~\cite{cimatti2013parameter} use bounded model
-%checking and fixed-point computations to compute parameters based on
-%user-defined specifications, but they often operate in the continuous domain
-%and have no direct means of evaluating robustness.
-
-Other tools such as~\cite{economakos2016automated} are aimed at
-robust stability problems, but they fail to take the FWL effects into
-account.  In order to provide a correct-by-design digital controller,
-\cite{alur2016compositional} requires a user-defined finite-state
-abstraction to synthesize a digital controller based on high-level
-specifications.  While this approach overcomes the challenges presented by
-the FWL problem, it still requires error-prone user intervention. 
-A~different solution that uses FWL as the starting point is an approach that
-synthesizes word lengths for known control problems~\cite{jha2013swati};
-however, this provides neither an optimal result nor a comprehensive
-solution for the problem.
-
-\paragraph{CEGIS}
-
-Program synthesis is the problem of computing correct-by-design programs
-from high-level specifications, and algorithms for this problem have made
-substantial progress in recent years.  One such
-approach~\cite{itzhaky2010simple} inductively synthesizes invariants to
-generate the desired programs.
-
-Program synthesisers are an ideal fit for synthesis of parametric
-controllers since the semantics of programs capture effects such as FWL
-precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
-for the synthesis of switching controllers for stabilizing continuous-time
-plants with polynomial dynamics.  The work extends to its application on
-affine systems, finding its major challenge in the hardness of solving
-linear arithmetic with the state-of-the-art SMT solvers.  Since this
-approach uses switching states instead of linear dynamics in the digital
-controller, it entirely circumvents the FWL problem.  It is also not
-suitable for the kind of control we seek to synthesize.  We require a
-combination of a synthesis engine with a control verification tool that
-addresses the challenges presented here in the form of FWL effects and
-stability measures for LTI SISO controllers.  We take the former
-from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from~\cite{daes20161}
-while enhancing the procedure by evaluating the quantization effects of the
-Hardware interfaces (ADC/DAC) to obtain an accurate discrete-time FWL
-representation of the continuous dynamics.
-
-%In \cite{DBLP:journals/corr/PakmehrWJVF13}, Pakmehr et al.  design a control software verification framework for gas turbine engines.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}\label{sec:conclusions}
-
-We have presented a CEGIS-based approach implemented in a tool called \tool,
-which uses inductive synthesis in conjunction with an algorithm for
-verifying robust closed-loop stability that addresses plant variations as
-interval sets as well as FWL uncertainties in digital controllers.  The
-novelty in our approach is that it is fully automated and algorithmically
-and numerically sound.  In particular, \tool marks the first use of the
-CEGIS that handles plants with uncertain models and FWL effects over the
-digital controller.  Implementing this architecture efficiently requires
-adjusting the traditional CEGIS refinement loop to the use of a two-stage
-verification engine: here, the first stage performs fast, but potentially
-unsound fixed-point operations, whereas the second stage restores soundness
-by validating the operations performed by the first stage using interval
-arithmetic.  Our experimental results show that \tool is able to synthesize
-stable controllers in most benchmarks within a reasonable amount of time
-fully automatically.  Future work will be the extension of this CEGIS-based
-approach to further classes of systems, including those with state space. 
-We will also consider performance requirements while synthesizing the
-digital controller.
+outside of our model representation using MATLAB.
 
 \bibliographystyle{abbrv}
-\bibliography{paper}
-
-%APPENDICES are optional
-%\balancecolumns
-%\appendix
-%Appendix A
+%\bibliography{paper}
 

### 2017-02-10 hscc2017/poster.tex
fixes

@@
 counterexample that is added to the {\sc inputs} set and the loop iterates
-again (note that, for now, we ignore the second feedback signal ``Increase
-Precision'' provided by the {\sc Verify} phase in Figure~\ref{fig:CEGIS} as it
-is specific to control synthesis and will be described in the next section).
-
-It is worth noting that each iteration of the loop adds a new input to
-the finite set $\text{\sc inputs}$ that is used for synthesis.  Given
-that the full set of inputs $\mathcal{D}$ is finite, this means that
-the refinement loop can only iterate a potentially very large, but
-finite number of times.
+again.
 
@@
 \bibliographystyle{abbrv}
-%\bibliography{paper}
+\bibliography{paper}
 

### 2017-02-11 hscc2017/paper.tex
hscc17

@@
 Thus, we consider continuous dynamics (the plant) and discrete parts (the
-digital controller).  To obtain a joint model, we fully discretize the
-continuous plant.  We briefly recall the standard foundations of this step.
-
-We only consider transfer function models, and require a $z$-domain transfer
-function $G(z)$ that captures all aspects of the continuous plant with a
-Laplace domain transfer function $G(s)$ and the sampling and hold process. 
+digital controller). In order to obtain an overall model, we discretize the
+continuous plant and look at the plant dynamics from the perspective of the digital controller. 
+%We briefly recall the standard foundations of this step.
+
+As we only consider transfer function models, and require a $z$-domain transfer
+function $G(z)$ that captures all aspects of the continuous plant, 
+which is naturally described via a Laplace-domain transfer function $G(s)$. 
+% and the sampling and hold process. 
 The continuous model of the plant must be discretized to obtain the
@@
 
-Among the discretization methods in the literature~\cite{Franklin15}, the
-zero-order hold (ZOH) discretization is suitable for representing the sample
-and hold processes in complex systems~\cite{istepanian2012digital}.  The ZOH
-discretization models the exact effect of sampling and DAC interpolation
-over the plant.
+Among the discretization methods in the literature~\cite{Franklin15}, 
+%the zero-order hold (ZOH) discretization is suitable for representing 
+we consider the sample-and-hold processes in complex systems~\cite{istepanian2012digital}.  
+On the other hand, 
+the ZOH discretization models the exact effect of sampling and DAC interpolation over the plant.
 

### 2017-02-11 hscc2017/paper.tex
hscc17

@@
 %------------------------------------
-\subsection{Discretizing the Plant}
+\subsection{Discretization of the Plant}
 \label{ssec:SandH}
@@
 %
-The sample and hold effects of the ADC and the ZOH of the DAC are synchronized,
-i.e., there is no delay between sampling the plant output at ADC and
+The sample-and-hold effects of the ADC and the presence of the ZOH of the DAC are synchronized,
+namely there is no delay between sampling the plant output at the ADC and
 updating the DAC accordingly.  The DAC interpolator is an ideal ZOH. 
@@
 %
-Given a synchronized ZOH input and sample-and-hold output on the plant with
-a sample time $T$ satisfying the Nyquist criterion, the discrete pulse
-transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$
-that can be computed using the following formula:
+Given a synchronized ZOH input and sample-and-hold output on the plant, 
+with a sample time $T$ satisfying the Nyquist criterion, the discrete pulse
+transfer function $G(z,T)$ is an exact z-domain representation of $G(s)$, 
+and can be computed using the following formula:
 %
@@
 pulse transfer function $G(z,T)$.
-
+% 
 Lemma~\ref{eq:pulsetf} ensures that the poles and zeros match under the
 $\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$
-operations, and it includes the ZOH dynamics in the $(1-z^{-1})$ term, which
-is sufficient for stability studies over $G(s)$~\cite{fadali}, {\it i.e.}, if there is any unstable pole domain ($\Re\{s\}\geq 0$), the pulse transfer function~\ref{eq:pulsetf} will also present the same number of unstable poles ($|z|<1$)~\cite{Franklin15}.
+operations, and it includes the ZOH dynamics in the $(1-z^{-1})$ term. 
+This is sufficient for stability studies over $G(s)$~\cite{fadali}, {\it i.e.}, if there is any unstable pole (in the complex domain $\Re\{s\} > 0$), 
+the pulse transfer function~\eqref{eq:pulsetf} will also present the same number of unstable poles ($|z| > 1$)~\cite{Franklin15}.
 
@@
 uncertainty parameters in the plant model (plant intervals)~\cite{Bessa16}. 
-Let $C(z)$ be a digital controller and $G(z)$ be a plant model given as
+Let $C(z)$ be a digital controller and $G(z)$ be a digital representation of the plant, 
+given as
 %
@@
 %
-\noindent where $\vec{\beta}$ and $\vec{\alpha}$ are vectors containing the
+where $\vec{\beta}$ and $\vec{\alpha}$ are vectors containing the
 controller's coefficients; similarly, $\vec{b}$ and $\vec{a}$ denote the
-plant's coefficients; and $N_{(\cdot)}$ and $M_{(\cdot)}$ indicate the order
-of the polynomials. 
-% of the corresponding block.
-
-Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (i.e.,
-$\Delta_p{G}_n(s),\Delta_p{G}_d(s)$, which arise from tolerances/imprecision
-in the original model), errors in the numeric calculations, or roundoffs in
-the quantization.  These uncertainties are parametrically expressed by
-additive terms, resulting in an uncertain model $\hat{G}(z)$, such that:
+plant's coefficients; 
+and finally $N_{(\cdot)}$ and $M_{(\cdot)}$ indicate the order of the polynomials,  
+and we require in particular that $N_G \geq M_G$.
+
+Uncertainties in $G(z)$ may appear due to: 
+1. uncertainties in $G(s)$ (we denote them $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$) arising from tolerances/imprecision in the original model; 
+2. errors in the numerical calculations (\red{denoted \ldots}); 
+and 3. roundoffs in the quantization (\red{denoted \ldots}).  
+These uncertainties are parametrically expressed by additive terms, eventually resulting in an uncertain model $\hat{G}(z)$, such that:
 %
@@
 \begin{equation}
-\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}} : N_G \geq M_G .
+\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}}. 
 \end{equation}
@@
 %\red{[why is this condition on the order of the polynomials raised only now? how is it used later?]}
-Due to the nature of the methods we use for the stability check, we require
+Notice that, due to the nature of the methods we use for the stability check, we require
 that the parametric errors in the plant have the same polynomial order as
-the plant itself (\blue{all other errors described in this paper are ensured to
-fulfil this property in our implementation}
+the plant itself (\blue{indeed, all other errors described in this paper are ensured to
+fulfil this property in our implementation}). 
 %\red{[have we later argued that this is indeed the case?]}) 
@@
 
-We employ a notation based on the polynomials coefficients to simplify 
+We introduce next a notation based on the polynomials coefficients to simplify 
 the presentation.  Let $\mathcal{P}^{N}$ be the space of polynomials of order $N$. 
@@
 \vec{G} \in \mathbb{R}^{N_G+M_G+2}&=[b_{0}\ \hdots \ b_{M_G}\ a_{0}\ \hdots\ a_{N_G}\ ]^T\nonumber \\
-\Delta{\vec{G}}\in \mathbb{R}^{N_G+M_G+2}&=[\Delta{b}_{0}\ \hdots \ \Delta{b}_{M_G}\ \Delta{a}_{0}\ \hdots\ \Delta{a}_{N_G}\ ]^T\nonumber
+\Delta{\vec{G}}\in \mathbb{R}^{N_G+M_G+2}&=[\Delta{b}_{0}\ \hdots \ \Delta{b}_{M_G}\ \Delta{a}_{0}\ \hdots\ \Delta{a}_{N_G}\ ]^T. \nonumber
 \end{align}
-In the following we will
-either use the functions $G(z)$, $C(z)$ directly, or work over their
-respective coefficients $\vec{G}$, $\vec{C}$ in vector form.
+In the following we will either manipulate the transfer functions $G(z)$, $C(z)$ directly, 
+or work over their respective coefficients $\vec{G}$, $\vec{C}$ in vector form.
+
+\medskip
 

### 2017-02-11 hscc2017/paper.tex
hscc17

@@
 %------------------------------------
-\subsection{Verifying Closed-loop Control Systems}
+\subsection{Verifying Closed-loop Control Systems \\ \blue{Effects of Imprecisions, Quantization, and Finite Word Length Representation}}
 \label{verifying-closed-loop-control-systems}
@@
 }
- \caption{Closed-loop digital control system\label{fig:sampledsystem}}
+ \caption{Closed-loop digital control system \red{[has this notation for the plant ever been introduced?]} \label{fig:sampledsystem}}
 \end{figure*}
@@
 ADC converters introduce quantization errors (notice that each of them
-may have a different FWL than the controller),
+may have a different FWL representation than the controller),
 %\red{[why is the DAC introducing a quantisation error again?]}
 which are modeled as noises
-$\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model
-with parametric additive uncertainty $\Delta_p{G}_n(s)$ and
-$\Delta_p{G}_d(s)$, $R(z)$ is the reference signal, $U(z)$ is the control
-signal, and $\hat{Y}(z)$ is the output signal affected by the noises and
-uncertainties in the closed-loop system.
+$\nu_{1}(z)$ and $\nu_{2}(z)$;  
+$G(s)$ is the continuous-time plant model
+with parametric additive uncertainty $\Delta_p{G}_n(s)$ and $\Delta_p{G}_d(s)$ (as mentioned above);  
+$R(z)$ is a given reference signal; 
+$U(z)$ is the control signal; 
+and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system 
+\red{[notice we have tilde outputs in the two figures! these need to be explained here.]}. 
 %
@@
 Figure~\ref{fig:sampledsystem} into the digital system in 
-Figure~\ref{fig:digsystem1}, where the parametric uncertainties are
-represented by~$\Delta_p \vec{G}$
-and the effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is
+Figure~\ref{fig:digsystem1}, 
+where 
+% the parametric uncertainties are represented by~$\Delta_p \vec{G}$ and 
+the effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is
 seen as additive noise.
@@
 }
-\caption{Digital equivalent to the system in Figure~\ref{fig:sampledsystem} 
+\caption{Fully digital equivalent to system in Figure~\ref{fig:sampledsystem} 
 \label{fig:digsystem1}}
@@
 In Figure~\ref{fig:digsystem1}, two sources of uncertainty are illustrated:
-parametric uncertainties related to modeling errors, and uncertainties
-introduced by quantizations in the ADC and
-DAC conversions.  These sources are assumed to be non-deterministic, 
-which poses no further restriction to our model, thus, the uncertain model
-may be rewritten as a vector of coefficients in the z-domain using equation
-(\ref{eq:hatgvector})
+parametric uncertainties related to modeling errors  
+(which are represented by~$\Delta_p \vec{G}$),  
+and uncertainties introduced by quantizations in the ADC and
+DAC conversions \red{[how are these denoted?]}.  
+These sources are assumed to be non-deterministic \blue{[here you mean specifically the quantization effects?]}:  
+%which poses no further restriction to our model, 
+thus, 
+the uncertain model may be rewritten as a vector of coefficients in the z-domain using equation (\ref{eq:hatgvector}) as 
 %
@@
 \label{eq:complete_unc_model}
-\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G},
+\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}. 
 \end{equation}
 %
-where $\Delta_p \vec{G}$ is the term that corresponds to the parametric
-uncertainties. Notice that the quantization noise is additive, which means
-it does not affect the transfer function. Instead, we prove that the system
-is stable given these non-deterministic noise inputs.
+%where $\Delta_p \vec{G}$ is the term that corresponds to the parametric uncertainties. 
+Recall that we discussed how the quantization noise is encompassed as an additive term, 
+which means it does not enter parametrically in the transfer function. 
+Instead, we later show that the system is stable given these non-deterministic noise inputs.
 
@@
 %
+\blue{[not confusing next?]}
 In the case of a synthesized controller, because the synthesis is performed
@@
 %------------------------------------
-\subsection{Stability under Finite Representation and Quantisation Noise}
+\subsection{Stability under FWL Representation and under Quantisation Noise \blue{(and params uncertainties?)}}
 \label{sec:stability}
@@
 
-Correct synthesis of the digital controller requires consideration of the
-effect of FWL on the controller and quantization noises in the closed loop
-system.  Let the quantizer $Q1$ be the source of a white noise $\nu_{1}$ and
-$Q2$ be the source of a white noise $\nu_{2}$.  The following equation
+Sound synthesis of the digital controller requires the consideration of the effect of FWL on the controller, 
+and of quantization noises in the closed-loop system.  
+Let the quantizer $Q1$ \blue{[new notation- needed really?] (DAC)} be the source of a white noise $\nu_{1}$, 
+and $Q2$ \blue{[ditto] (ADC)} be the source of a white noise $\nu_{2}$.  The following equation
 models the system in Figure~\ref{fig:sampledsystem}, encompassing the
@@
 \begin{equation}
-\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\cdot C(z)\cdot R(z)+\hat{G}(z)\cdot\nu_{2}(z)-\hat{G}(z)\cdot \hat{C}(z)\cdot \hat{Y}(z)
+\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\cdot C(z)\cdot R(z)+\hat{G}(z)\cdot\nu_{2}(z)-\hat{G}(z)\cdot \hat{C}(z)\cdot \hat{Y}(z). 
 \end{equation}
-%
-%
-%
 %
@@
 \label{eq:outputfunctions}
-\hat{Y}(z)=H_{1}(z)\nu_{1}(z)+H_{2}(z)\cdot\nu_{2}(z)+H_{3}(z)\cdot R(z),
+\hat{Y}(z)=H_{1}(z)\cdot\nu_{1}(z)+H_{2}(z)\cdot\nu_{2}(z)+H_{3}(z)\cdot R(z),
 \end{equation}
@@
 \begin{equation*}
-H_{1}(z)=\frac{1}{1+\hat{G}(z)\cdot \hat{C}(z)}
+H_{1}(z)=\frac{1}{1+\hat{G}(z)\cdot \hat{C}(z)}, 
 \end{equation*}
@@
 \begin{equation*}
-H_{2}(z)=\frac{\hat{G}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}
+H_{2}(z)=\frac{\hat{G}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}, 
 \end{equation*}
 %
-and
-%
 \begin{equation*}
-H_{3}(z)=\frac{\hat{G}(z)\cdot \hat{C}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}
+H_{3}(z)=\frac{\hat{G}(z)\cdot \hat{C}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}. 
 \end{equation*}
@@
 %
-The quantization noises $\nu_{1}$ (from $Q1$) and $\nu_{2}$ (from $Q2$) are
+The quantization noises $\nu_{1}$ \blue{(from $Q1$)} and $\nu_{2}$ \blue{(from $Q2$)} are
 uncorrelated white noises and their amplitudes are always bounded by the
@@
 
-A discrete-time linear system is said to be Bounded-Input and Bounded-Output
-(BIBO) stable if and only if every pole of its transfer function lies inside
-the unit circle \cite{Astrom08}.  Analyzing Eq.~\eqref{eq:outputfunctions},
-the following proposition gives necessary conditions for the closed-loop system 
-BIBO stability in Figure~\ref{fig:sampledsystem}, with regards to the 
-exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$, which are bounded.
-
+A discrete-time dynamical system is said to be Bounded-Input and Bounded-Output
+(BIBO) stable if bounded inputs necessarily result in bounded outputs. 
+This condition holds true over an LTI model if and only if every pole of its transfer function lies inside the unit circle \cite{Astrom08}.  
+Analyzing Eq.~\eqref{eq:outputfunctions}, 
+the following proposition provides conditions for the BIBO stability of the system in Figure~\ref{fig:sampledsystem}, 
+with regards to the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$, which are all bounded 
+(in particular, the bound on the quantization noise is given by
+Assumption~\ref{whitenoise}). 
+%
 \begin{myprop}{\cite{Bessa16,fadali}}
@@
 controller $\hat{C}(z) =\mathcal{F}_{M_C,N_C}\langle I,F \rangle(C(z))$ and uncertain discrete
-model of the plant
+model of the plant from~\eqref{eq:coefficients},\eqref{eq:delta_coefficients} 
 %
 $$
-\hat{G}(z) =\frac{\hat{G}_n(z)}{\hat{G}_d(z)}: \vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}
-\text{\quad(from~\ref{eq:coefficients},\ref{eq:delta_coefficients})}.
+\hat{G}(z) =\frac{\hat{G}_n(z)}{\hat{G}_d(z)}, \quad \vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}.
 $$
@@
 \label{eq:internal_stab_lemma}
-S(z)=\mathcal{F}_{M_C}\langle I,F \rangle(C_n(z))\hat{G}_n(z)+\mathcal{F}_{N_C}\langle I,F \rangle(C_d(z))\hat{G}_d(z);
+\hspace{-3ex} S(z)=\mathcal{F}_{M_C}\langle I,F \rangle(C_n(z))\hat{G}_n(z)+\mathcal{F}_{N_C}\langle I,F \rangle(C_d(z))\hat{G}_d(z);
 \end{equation}
@@
 parametric uncertainties (i.e., $\Delta_p \vec{G}$), quantization noises
-($\nu_{1}$ and $\nu_{2}$) and FWL effects in the control software.  Note
-that the model for quantization noise enters as a signal to be stabilized (i.e.,
+($\nu_{1}$ and $\nu_{2}$) and FWL effects in the control software.  
+In particular, 
+note that the model for quantization noise enters as a signal to be stabilized: 
+in practice, 
+if the quantization noise is bounded, 
 the noise may be disregarded if the conditions on
-Proposition~\ref{prop:eq_int_stab} are satisfied and if the quantization
-noise is bounded.  The bound on the quantization noise is given by
-Assumption~\ref{whitenoise}.
+Proposition~\ref{prop:eq_int_stab} are satisfied.
 

### 2017-02-11 hscc2017/paper.tex
hscc17

@@
 candidate controller meets the requirements when combined with the plant. 
-We use the Digital-System Verifier (DSVerifier)~\cite{IsmailBCFF15} for this
+We use the Digital-System Verifier (DSVerifier)~\cite{IsmailBCFF15} \red{[unclear difference btw dssynth and dsverifier]} for this
 purpose.  It checks the stability of closed-loop control systems and
@@
 synthesizer as the specification $\sigma$.  There are two different
-algorithms in DSVerifier that can be used for stability
+algorithms in \red{DSVerifier} that can be used for stability
 verification~\cite{daes20161, Bessa16}, one based on Schur's decomposition
-and another one based on Jury's criteria~\cite{astrom1997computer}.  Here,
+and another one based on Jury's criterion~\cite{astrom1997computer}.  Here,
 we choose Jury's method~\cite{astrom1997computer}, due to its efficiency,
@@
 %
-$$
-S(z) = a_0z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N=0, a_0\neq0
-$$
-%
+\begin{equation*}
+S(z) = a_0z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N=0, a_0\neq0. 
+\end{equation*}
 %\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?}
@@
 % $$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$
-
 Next, the following Jury matrix
@@
 %
-$$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
+$$
+\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j}, \text{ that is } \tilde C(z) \equiv C(z). 
+$$
 %
@@
 %
-we calculate $\tilde G(z)=\mathcal{F}_{M_G,N_G}\langle I_p,F_p \rangle(\hat{G}(z))$
+we calculate $\tilde G(z)=\mathcal{F}_{M_G,N_G}\langle I_p,F_p \rangle(\hat{G}(z))$, where 
 %
@@
 \tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_b \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_b \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_b \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_b \hat{a}_{N_G})z^{-N_G}} \nonumber \\
-&\Rightarrow \vec{\tilde G} =\vec{\hat{G}}+\Delta_b{\vec{G}}=\vec{G}+\Delta_p{\vec{G}}+\Delta_b{\vec{G}}.
+&\Rightarrow \vec{\tilde G} =\vec{\hat{G}}+\Delta_b{\vec{G}}=\vec{G}+\Delta_p{\vec{G}}+\Delta_b{\vec{G}}, 
 \end{align}
 %
-where $\Delta_b\hat{c}_i=\hat{c}_i\bmod \tilde{c}_i$
-and $\Delta_b{G}$ represent the plant uncertainty caused by
+where $\Delta_b\hat{c}_i=\hat{c}_i\bmod \tilde{c}_i$, 
+and $\Delta_b{G}$ represents the plant uncertainty caused by
 the rounding off effect.  We encompass all the uncertainty as
@@
 
-\paragraph{Our synthesis problem}
+\paragraph{The synthesis problem}
 The synthesis problem we are trying to solve is the following:
@@
 and rounds operations outwards during calculations.  This effectively allows
-us to simultaneously evaluate the whole collection of plants $\mathfrak{G}$
+us to simultaneously evaluate the whole collection of plants $\mathfrak{G}$ \red{[weird new notation needed? used elsewhere?]}
 plus the effects of numeric calculations in the engine.  Synthesized

### 2017-02-12 hscc2017/paper.tex
addressed some of Alessandro's comments

@@
 %------------------------------------
-\subsection{Verifying Closed-loop Control Systems \\ \blue{Effects of Imprecisions, Quantization, and Finite Word Length Representation}}
+\subsection{Verifying Closed-loop Control Systems \\ \blue{Under the Effect of Imprecisions, Quantization, and Finite Word Length Representation}}
 \label{verifying-closed-loop-control-systems}
@@
 candidate controller meets the requirements when combined with the plant. 
-We use the Digital-System Verifier (DSVerifier)~\cite{IsmailBCFF15} \red{[unclear difference btw dssynth and dsverifier]} for this
-purpose.  It checks the stability of closed-loop control systems and
+We use the Digital-System Verifier (DSVerifier)~\cite{IsmailBCFF15} in the
+verification module for \tool.  It checks the stability of closed-loop control systems and
 considers finite-word length (FWL) effects in the digital controller, and
@@
 1. uncertainties in $G(s)$ (we denote them $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$) arising from tolerances/imprecision in the original model; 
-2. errors in the numerical calculations (\red{denoted \ldots}); 
-and 3. roundoffs in the quantization (\red{denoted \ldots}).  
+2. errors in the numerical calculations (equal to $0$ since we introduce them as external noises $\nu_1$ and $\nu_2$); 
+and 3. roundoffs in the quantization (denoted $\Delta_b{G}_n(s),\Delta_b{G}_d(s)$).  
 These uncertainties are parametrically expressed by additive terms, eventually resulting in an uncertain model $\hat{G}(z)$, such that:
@@
 and uncertainties introduced by quantizations in the ADC and
-DAC conversions \red{[how are these denoted?]}.  
+DAC conversions ($\nu_1$ and $\nu_2$).  
 These sources are assumed to be non-deterministic \blue{[here you mean specifically the quantization effects?]}:  
@@
 affects the precision and the truncation after arithmetic operations. 
-\red{[we ought to align the following notations with those use in the CAV submission.]}
 We shall denote the FWL domain of the coefficients by $\mathbb{R}\langle I,F
@@
 %------------------------------------
-\subsection{Stability under FWL Representation and under Quantisation Noise \blue{(and params uncertainties?)}}
+\subsection{Stability under FWL Representation, Quantisation Noise and Parametric Uncertainties}
 \label{sec:stability}
@@
 and of quantization noises in the closed-loop system.  
-Let the quantizer $Q1$ \blue{[new notation- needed really?] (DAC)} be the source of a white noise $\nu_{1}$, 
-and $Q2$ \blue{[ditto] (ADC)} be the source of a white noise $\nu_{2}$.  The following equation
+Let the quantizer $Q1$ (ADC) be the source of a white noise $\nu_{1}$, 
+and $Q2$ (DAC) be the source of a white noise $\nu_{2}$.  The following equation
 models the system in Figure~\ref{fig:sampledsystem}, encompassing the
@@
 %
-The quantization noises $\nu_{1}$ \blue{(from $Q1$)} and $\nu_{2}$ \blue{(from $Q2$)} are
+The quantization noises $\nu_{1}$ (from $Q1$) and $\nu_{2}$ (from $Q2$) are
 uncorrelated white noises and their amplitudes are always bounded by the
@@
 synthesizer as the specification $\sigma$.  There are two different
-algorithms in \red{DSVerifier} that can be used for stability
-verification~\cite{daes20161, Bessa16}, one based on Schur's decomposition
+algorithms in our verification engine that can be used for stability
+~\cite{daes20161, Bessa16}, one based on Schur's decomposition
 and another one based on Jury's criterion~\cite{astrom1997computer}.  Here,
@@
 and rounds operations outwards during calculations.  This effectively allows
-us to simultaneously evaluate the whole collection of plants $\mathfrak{G}$ \red{[weird new notation needed? used elsewhere?]}
+us to simultaneously evaluate the whole collection of plants $\hat{G}(s)$
 plus the effects of numeric calculations in the engine.  Synthesized

### 2017-02-12 hscc2017/paper.tex
hscc17

@@
 %------------------------------------
-\subsection{Verifying Closed-loop Control Systems \\ \blue{Under the Effect of Imprecisions, Quantization, and Finite Word Length Representation}}
+\subsection{Verifying Closed-loop Control Systems \\ \blue{Model Imprecision, Quantization Effects, and Finite Word Length Representation}}
 \label{verifying-closed-loop-control-systems}
@@
 The parametric uncertainties in the plant are assumed to have the same
-order as the plant model, since tolerances of higher order would invalidate
-feedback model (even tiny errors of higher order can move the poles by a
-large amount preventing any single controller from stabilizing such a setup).
+order as the plant model, since 
+%tolerances of higher order would invalidate the feedback model (even tiny 
+errors of higher order can move the closed-loop poles by large amounts, 
+thus preventing any given controller from stabilizing such a setup. 
 This is a reasonable assumption since most tolerances do not change the 
-architecture of the plant, and models subject to such effects are
-inadequate.
+architecture of the plant. 
+%, and models subject to such effects are inadequate.
 

### 2017-02-12 hscc2017/paper.tex
hscc17

@@
 %
+\textcolor{cyan}{[rearrange next paragraph - param and quant]}
 In Figure~\ref{fig:digsystem1}, two sources of uncertainty are illustrated:
@@
 
+\textcolor{cyan}{[next discussion on fwl]}
+
 Since the controller is implemented using finite representation, $C(z)$ also suffers
@@
 Let $\hat{C}(z)$ be the digital controller transfer function represented
-using this FWL with integer size $I$ and fractional size~$F$; $I$ affects
-the range of the representation and is set to avoid overflows, while $F$
-affects the precision and the truncation after arithmetic operations. 
+using this FWL with integer size $I$ and fractional size~$F$. 
+The term $I$ affects the range of the representation and is set to avoid overflows, 
+while $F$ affects the precision and the truncation after arithmetic operations. 
 We shall denote the FWL domain of the coefficients by $\mathbb{R}\langle I,F
@@
 %
-\blue{[not confusing next?]}
+\blue{[ next statement is potentially quite confusing, especially since you used the hatted variables next. ]}
 In the case of a synthesized controller, because the synthesis is performed

### 2017-02-12 hscc2017/paper.tex
hscc17

@@
 1. uncertainties in $G(s)$ (we denote them $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$) arising from tolerances/imprecision in the original model; 
-2. errors in the numerical calculations (equal to $0$ since we introduce them as external noises $\nu_1$ and $\nu_2$); 
-and 3. roundoffs in the quantization (denoted $\Delta_b{G}_n(s),\Delta_b{G}_d(s)$).  
+2. errors in the numerical calculations (which we model later as as external noises $\nu_1$ and $\nu_2$ \red{[no, these are the quantisation ones!]}); 
+and 3.
+roundoffs in the quantization (denoted $\Delta_b{G}_n(s),\Delta_b{G}_d(s)$ \red{[these are related to FWL - we introduce them as such, but then use other operators in equation 10 - very confusing]}).
 These uncertainties are parametrically expressed by additive terms, eventually resulting in an uncertain model $\hat{G}(z)$, such that:
@@
 }
- \caption{Closed-loop digital control system \red{[has this notation for the plant ever been introduced?]} \label{fig:sampledsystem}}
+ \caption{Closed-loop digital control system \red{[has this hatted notation for the continuous-frequency plant ever been introduced?]} \label{fig:sampledsystem}}
 \end{figure*}

### 2017-02-12 hscc2017/paper.tex
hscc17

@@
 This is sufficient for stability studies over $G(s)$~\cite{fadali}, {\it i.e.}, if there is any unstable pole (in the complex domain $\Re\{s\} > 0$), 
-the pulse transfer function~\eqref{eq:pulsetf} will also present the same number of unstable poles ($|z| > 1$)~\cite{Franklin15}.
+the pulse transfer function in~\eqref{eq:pulsetf} will also present the same number of unstable poles ($|z| > 1$)~\cite{Franklin15}.
 
@@
 uncertainty parameters in the plant model (plant intervals)~\cite{Bessa16}.
+
 Let $C(z)$ be a digital controller and $G(z)$ be a digital representation of the plant, 
@@
 \label{eq:hatgvector}
-\vec{\hat{G}}&=\vec{G}+\Delta{\vec{G}}\\
-\vec{G} \in \mathbb{R}^{N_G+M_G+2}&=[b_{0}\ \hdots \ b_{M_G}\ a_{0}\ \hdots\ a_{N_G}\ ]^T\nonumber \\
+\vec{\hat{G}}&=\vec{G}+\Delta{\vec{G}}, \text{ where} \\
+\vec{G} \in \mathbb{R}^{N_G+M_G+2}&=[b_{0}\ \hdots \ b_{M_G}\ a_{0}\ \hdots\ a_{N_G}\ ]^T, \nonumber \\
 \Delta{\vec{G}}\in \mathbb{R}^{N_G+M_G+2}&=[\Delta{b}_{0}\ \hdots \ \Delta{b}_{M_G}\ \Delta{a}_{0}\ \hdots\ \Delta{a}_{N_G}\ ]^T. \nonumber
@@
 thus, 
-the uncertain model may be rewritten as a vector of coefficients in the z-domain using equation (\ref{eq:hatgvector}) as 
-%
-\begin{equation}
-\label{eq:complete_unc_model}
-\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}. 
-\end{equation}
+the uncertain model may be rewritten as a vector of coefficients in the z-domain using equation \eqref{eq:hatgvector} as  
+%
+%\begin{equation}
+%\label{eq:complete_unc_model}
+$\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}$. 
+%\end{equation}
 %
@@
 using FWL, $\hat{C}(z) \equiv C(z)$.
+\red{[discuss relationship with introduced terms $\Delta_b{G}_n(s),\Delta_b{G}_d(s)$?]}
 
@@
 Next, we describe the specific property that we pass to the program
-synthesizer as the specification $\sigma$.  There are two different
-algorithms in our verification engine that can be used for stability
-~\cite{daes20161, Bessa16}, one based on Schur's decomposition
-and another one based on Jury's criterion~\cite{astrom1997computer}.  Here,
-we choose Jury's method~\cite{astrom1997computer}, due to its efficiency,
-and we use this method to check the stability in the $z$-domain for the
+synthesizer as the specification $\sigma$.  There are a number of 
+algorithms in our verification engine that can be used for stability analysis~\cite{daes20161, Bessa16}.  
+%one based on Schur's decomposition
+%and another one based on Jury's criterion~\cite{astrom1997computer}.  
+Here we choose Jury's criterion~\cite{astrom1997computer} in view of its efficiency: 
+we employ this method to check the stability in the $z$-domain for the
 characteristic polynomial $S(z)$ defined in~\eqref{eq:internal_stab_lemma}.
@@
 % $$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$
-Next, the following Jury matrix
+Next, the following matrix
 $M = [m_{ij}]_{(2N-2)\times N}$ is built from $S(z)$ coefficients:
@@
 %
-where $k \in \mathbb{Z}$, such that $0 < k < N - 2$. 
+and where $k \in \mathbb{Z}$ is such that $0 < k < N - 2$. 
+We have that~\cite{astrom1997computer} 
 $S(z)$ is the
@@
 \tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_b \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_b \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_b \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_b \hat{a}_{N_G})z^{-N_G}} \nonumber \\
-&\Rightarrow \vec{\tilde G} =\vec{\hat{G}}+\Delta_b{\vec{G}}=\vec{G}+\Delta_p{\vec{G}}+\Delta_b{\vec{G}}, 
+\vec{\tilde G} &=\vec{\hat{G}}+\Delta_b{\vec{G}}=\vec{G}+\Delta_p{\vec{G}}+\Delta_b{\vec{G}}, 
 \end{align}
@@
 %$\Delta{\vec{p}}$ (\ref{eq:uncertainty}).
-$\tilde G(z)$ (\ref{digital_plant_tf}).
+$\tilde G(z)$ \eqref{digital_plant_tf}.
 %, where we precisely describe 
@@
 and rounds operations outwards during calculations.  This effectively allows
-us to simultaneously evaluate the whole collection of plants $\hat{G}(s)$
+us to simultaneously evaluate \blue{[unclear:] the whole collection of plants $\hat{G}(s)$}
 plus the effects of numeric calculations in the engine.  Synthesized
@@
 response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics with
-the goal to either verify (e.g.~\cite{daes20161}) or optimize
-(e.g.~\cite{oudjida2014design}) given implementations.
+the goal to either verify~\cite{daes20161} or to optimize~\cite{oudjida2014design} 
+given implementations.
 
@@
 issues of mathematical tractability.  The analyses
-in~\cite{DBLP:conf/hybrid/WangGRJF16, DBLP:conf/hybrid/RouxJG15} rely on an
+in~\cite{DBLP:conf/hybrid/RouxJG15,DBLP:conf/hybrid/WangGRJF16} rely on an
 invariant computation on the discrete system dynamics using Semi-Definite
@@
 
-\paragraph{CEGIS}
+\paragraph{The CEGIS Architecture}
 

### 2017-02-13 hscc2017/paper.tex
hscc17
work on text

@@
 
-\keywords{Control synthesis, CEGIS, finite word length, time sampling, quantization}
+\keywords{Digital control synthesis, CEGIS, finite-word-length representation, time sampling, quantization}
 
@@
 finite-precision arithmetic, time discretization, and quantization noise
-introduced by A/D and D/A conversion.  Thus, the programming is a key
-barrier to broad adoption of digital control, and requires considerable
-expertise.
+introduced by A/D and D/A conversion.  Thus, programming expertise is a key 
+barrier to broad adoption of correct digital controllers, and requires considerable
+knowledge often unusual to the control engineer.
 
@@
 there has been plenty of previous work aiming at \emph{verifying} a given 
-controller designed by the engineer.  Recent work can show the stability of
-digital controllers with consideration of implementation aspects, i.e.,
-fixed-point arithmetic and the word length used~\cite{Bessa16}.  The authors
-of~\cite{Bessa16} exploit advances in bit-accurate verification of C
+designed controller, which however broadly lack automation.  
+Recent work has studied the stability of digital controllers with consideration of their implementation aspects, i.e.,
+fixed-point arithmetic and the word length used: 
+\cite{Bessa16} exploit advances in bit-accurate verification of C
 programs to obtain a verifier for software-implemented digital control.
@@
 specification as the starting point, and subsequently generate a sequence of
-candidate programs.  The candidate programs are iteratively refined to match
-the specification more closely.  Program synthesizers that implement
-Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} are now
+candidate programs from a given template.  
+The candidate programs are iteratively refined to eventually match the desired program specification.   
+Program synthesizers implementing the 
+Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture are now
 able to generate programs for highly non-trivial specifications with a very 
-high degree of automation.  Modern synthesis engines combine automated
-testing, genetic algorithms and SMT-based automated
-reasoning~\cite{DBLP:conf/lpar/DavidKL15, DBLP:journals/corr/AlurFSS16a}.
+high degree of automation.  Modern synthesis engines combine automated testing, 
+genetic algorithms, 
+and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a,DBLP:conf/lpar/DavidKL15}.
 
@@
 domain, 
+\red{[confusing? (related to observation above.)]}
 %
@@
 However, given a real plant $\hat{G}(z)$, and a discretizing function 
+\red{[the function has been defined over a space of polynomials, but it is now applied to a real number x? ]}
 %
@@
 \small
-\label{FWL_tf}
+%\label{FWL_tf}
 \mathcal{F}&\langle I_p,F_p \rangle : \mathbb{R} \rightarrow  \mathbb{R}\langle I_p,F_p \rangle\\
 &\triangleq \tilde x = \mathcal{F}\langle I_p,F_p \rangle(x) : \tilde x=x-(x\bmod\tilde x)\nonumber\\ 
+\red{\text{above: circular definition?}}\\
 \mathcal{F}_n&\langle I_p,F_p \rangle(P \in \mathcal{P}) \\

### 2017-02-13 hscc2017/paper.tex
work on text

@@
 
-By contrast, we leverage a very recent step-change in the scalability of
+By contrast, we leverage a very recent step-change in the automation and scalability of 
 \emph{program synthesis}.  Program synthesis engines use a program
@@
 
-By applying a state-of-the-art synthesis engine we are now able to present a
-tool that automatically \emph{generates} digital controllers for a given
-continuous plant model that are correct by construction.  This approach
-promises to reduce the cost and time of development of digital control
-dramatically, and requires considerably less expertise than methodologies
-driven by verification.  Specifically, we synthesize controllers for hybrid
-closed-loop systems, i.e., software-implemented embedded controllers along
-with a model of their physical environment (the plant), that are
-\emph{stable}.  Due to the complexity of such systems, in this work we focus
-on linear models with known configurations and perform parametric synthesis
-of stabilizing digital controllers.
+By combining and applying state-of-the-art synthesis engines we present a 
+tool that automatically generates digital controllers for a given 
+continuous plant model that are correct by construction.  
+This approach presents a high degree of autonomy, 
+promises to reduce the cost and time of development of digital control dramatically, 
+and requires considerably less expertise than a-posteriori verification methodologies.   
+Specifically, we synthesize stable,  
+%controllers for hybrid closed-loop systems, i.e., 
+software-implemented embedded controllers along with a model of a physical plant. 
+%, that are \emph{stable}.  
+Due to the complexity of such closed-loop systems, in this work we focus
+on linear models with known configurations, and perform parametric synthesis
+of stabilizing digital controllers (further closed-loop requirements are left to future work).
 
@@
 approach~\cite{astrom1997computer}, we translate the problem into a single
-digital domain.  Given our primary interest in stability despite
-digitization effects, we have modeled a digital equivalent of the plant by
-evaluating the effects of the quantizers (A/D and D/A converters) as time
-discretization elements with quantization noise.  The resulting closed-loop
-system is a program loop that operates on bit-vectors encoded using
-fixed-point arithmetic with finite word length (FWL).  The deterministic
-effects of the FWL and quantization errors are incorporated into the model
-as an additive uncertainty, which is taken into account during the
-CEGIS-based synthesis of the control software for the plant.
+digital domain.  
+Towards our goal of closed-loop stability, 
+% despite digitization effects, 
+we have modeled a digital equivalent of the continuous plant by evaluating the effects of the quantizers (A/D and D/A converters) and of time
+discretization. 
+% elements with quantization noise.  
+We further account for uncertainties on the plant models. 
+The resulting closed-loop system is a program loop that operates on bit-vectors encoded using
+fixed-point arithmetic with finite word length (FWL). 
+The effects of the both the FWL and quantization errors are incorporated into the model, 
+%as an additive uncertainty, 
+and are taken into account during the CEGIS-based synthesis of the control software for the plant.
 
@@
 \item We automatically generate {\em correct-by-construction} digital
-  controllers using inductive synthesis.  Our application of program
+  controllers using an inductive synthesis approach.  Our application of program
   synthesis is non-trivial and addresses challenges specific to control
@@
 
+\textcolor{cyan}{[if space is needed, the next paragraph can be cut. ]}
 We cover preliminaries on plant discretization, the verification of

### 2017-02-13 hscc2017/paper.tex
work on text

@@
 fixed-point arithmetic with finite word length (FWL). 
-The effects of the both the FWL and quantization errors are incorporated into the model, 
+\blue{[match list ordering with later one.]}
+The three effects of 1. uncertaities, 2. FWL representation, and 3. quantization errors are incorporated into the model, 
 %as an additive uncertainty, 
@@
 }
-\caption{Counterexample-Guided Inductive Synthesis of Closed-loop Systems (Step~D)
+\caption{Counterexample-Guided Inductive Synthesis of Closed-loop Systems (Step~D) in Figure~\ref{DSSynth_process}
 \label{fig:CEGIS}}
@@
 
-While the {\sc synthesise} phase searches for potentially unsound 
+Within the scheme in Figure \ref{fig:CEGIS}, 
+while the {\sc synthesise} phase searches for potentially unsound 
 candidate solutions, the soundness of the model is ensured by the {\sc verify} phase.  
-If a candidate solution is validated by the verifier, it is necessarily
-sound.
+If a candidate solution is successfully verified, it is necessarily sound.
 
@@
 in the caculations do not cause the solution to be unsound.
-
+% 
 For this reason the second verification stage uses interval arithmetic with
 outward rounding to ensure that these errors do not exceed critical
-bounds that could make some (or all) plant(s) unstable. This means
-that whilst the solution may not be complete, it is sound for
-evaluating any collection of real plants with a defined FWL controller
-for all of them. We require two verification stages because,
-while the second phase can ensure the stability of all plants in
-the collection, it is unable to provide a counterexample.
+bounds that could make some (or all) plant(s) unstable.
+
+This means that whilst the solution may not be complete, it is sound for
+evaluating any collection of real plants with a defined FWL controller. 
+We require two verification stages because,
+while the second phase can ensure the stability of all plants in the collection, 
+it is unable to provide a counterexample.
 

### 2017-02-13 hscc2017/paper.tex
work on text

@@
 The second approach is illustrated in Figure~\ref{fig:CEGIS} and uses a
-two-stage verification: the first stage performs potentially unsound
+two-stage verification approach: the first stage performs potentially unsound
 fixed-point operations assuming a plant precision \param{I_p}{F_p}, and the
@@
 %
-The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that this controller
-$C(z)$ (Eq.~\eqref{Eq:running-example-controller}) stabilizes the
-closed-loop system for the discrete plant model $G(z)$
-(Eq.~\ref{Eq:running-example-plant}).  However, if the effects of
-finite-precision arithmetic are considered (e.g., fixed-point arithmetic and
+The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that the controller
+$C(z)$ in~\eqref{Eq:running-example-controller} stabilizes the
+closed-loop system for the discrete plant model $G(z)$ in~\ref{Eq:running-example-plant}.  
+However, if the effects of finite-precision arithmetic are considered (e.g., fixed-point arithmetic and
 word-length), then this closed-loop system becomes unstable.
 %
-For instance, an implementation of $C(z)$ using \param{4}{16} fixed-point
+For instance, an implementation of $C(z)$ using \blue{[align with notation introduced earlier]} \param{4}{16} fixed-point
 numbers (i.e., $4$ bits for the integer part and $16$ bits for the
@@
 %
+\red{[new notation for controller with FWL?]}
 \begin{equation}
@@
 $C_{q}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
-{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$
+{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$. 
 }
@@
 Figure~\ref{fig:original} gives the Bode diagram for the digital controller
-represented by Eq.~\eqref{Eq:running-example-controller}.  The phase margin
-is negative, which means that the controller represented by
-Eq.~\eqref{Eq:running-example-controller} is unstable, considering FWL
-effects.
+represented in~\eqref{Eq:running-example-controller}: 
+as the phase margin is negative, 
+the controller is unstable when considering the above FWL effects.
 
@@
 control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}. 
+\red{[Add comment on the next candidate solution - generated automatically, or selected manually?]}
 %
@@
 %$$
-$$ C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0} $$
-
+$$ 
+C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}. 
+$$
 In the first {\sc verify} stage, the {\sc uncertainty} 
@@
 %
-$$ \tilde G(z) = \frac{0.026506}{1.000610z+1.002838} $$
+$$ 
+\tilde G(z) = \frac{0.026506}{1.000610z+1.002838}. 
+$$
 
@@
 $$
-C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}
+C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}. 
 $$ 
-
 This time, the {\sc uncertainty} check does not find any
@@
 phase, we re-start the process with a candidate solution with all
-coefficients $0$.  Next, the {\sc uncertainty} verification stage provides
+coefficients $0$, as above.  Next, the {\sc uncertainty} verification stage provides
 the first counterexample at higher precision:
@@
     \end{subfigure}
-    \caption{Bode diagram for original~\cite{DBLP:conf/hybrid/WangGRJF16} and synthesized closed-loop systems}\label{fig:bode}
+    \caption{Bode diagram for original controller in~\cite{DBLP:conf/hybrid/WangGRJF16}, 
+    and for newly synthesized closed-loop system}\label{fig:bode}
 \end{figure}

### 2017-02-13 hscc2017/paper.tex
work on text

@@
 $$
-
 %$$
@@
 %$$ 
-
 We add this counterexample to {\sc inputs} and initiate the {\sc synthesize}
@@
 %$$
-$$ \tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785} $$
-
+$$ 
+\tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785}. 
+$$
 In the {\sc synthesize} phase, we get a new candidate solution that
@@
 %
-$$ C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357} $$
+$$ 
+C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}. 
+$$
 %
@@
 solutions provided by \tool.  The step response in Figure~\ref{fig:step0}
-confirms the stability loss if we consider FWL effects.  However,
+confirms the stability loss if we consider FWL effects.  
 Figure~\ref{fig:step1} shows that the first candidate controller is able to
@@
 time. 
+\blue{[explain why 6b is continuous, but not 6c.]}
 
@@
 A third set of benchmarks uses the discrete model $G_{3}(z)$ for satellite attitude 
-dynamics~\cite{Franklin15}, which require attitude (pose) control
-for orientation of antennas and sensors w.r.t.~earth.
+dynamics~\cite{Franklin15}, which require attitude control
+for orientation of antennas and sensors w.r.t.~Earth.
 The fourth set of benchmarks presents an alternative discrete model $G_4(z)$ 
@@
 of a DC servo motor velocity dynamics~\cite{exampleCAD,Tan01}. 
-
-The seventh set of benchmarks contains the discrete well-studied 
-non-minimal phase model $G_{7}(z)$. Non-minimal phase model offers 
-additional difficulties for the controller design~\cite{Doyle:1991:FCT:574259}.
+%
+The seventh set of benchmarks contains a well-studied discrete  
+non-minimal phase model $G_{7}(z)$. As known, non-minimal phase model offers 
+additional difficulties for the design of stable controllers~\cite{Doyle:1991:FCT:574259}. 
 %
@@
 %
-The eighth set of benchmarks contains the \textit{Helicopter Longitudinal Motion} discrete model $G_{8}(z)$,
+The eighth set of benchmarks describes the discrete model $G_{8}(z)$ for the \textit{Helicopter Longitudinal Motion},
 which provides the longitudinal motion dynamics of a helicopter~\cite{Franklin15}. 
@@
 %
-The ninth  set of benchmarks contains the \textit{Inverted Pendulum} discrete model $G_{9}(z)$, which 
+The ninth  set of benchmarks contains the discrete model $G_{9}(z)$ for the known \textit{Inverted Pendulum}, which 
 describes a pendulum dynamics with its center of mass above its pivot point~\cite{Franklin15}. 
@@
 %\end{equation}
-
 %The ninth set of benchmarks contains the \textit{1/4 Car Suspension} discrete model $G_{9}(z)$,
@@
 %
-The last set of benchmarks considers the discrete model $G_{12}(z)$
+The last set of benchmarks considers a discrete model $G_{12}(z)$ 
 that is typically used for evaluating stability
@@
 
-All experiments were conducted on a 12-core 2.40\,GHz Intel Xeon E5-2440
-with 96\,GB of RAM and Linux OS.  All times given are wall clock time in
-seconds as measured by the UNIX date command.  For the two-stage verification 
-engine we apply a timeout of $8$ hours per benchmark, and $24$ hours for the approach 
-using a one-stage engine.
+All experiments have been conducted on a 12-core 2.40\,GHz Intel Xeon E5-2440
+with 96\,GB of RAM and Linux OS.  All times given are wall clock times in
+seconds, as measured by the UNIX date command.  For the two-stage verification 
+engine in Figure~\ref{fig:CEGIS} we have applied a timeout of $8$ hours per benchmark, 
+whereas $24$ hours have been set for the approach using a one-stage engine.
 
@@
 benchmark, \textit{I} and \textit{F} represent the number of integer and
-fractional bits of the stable controller, respectively, while \textit{Time}
-is the total time (in seconds) required to synthesize a stable controller
+fractional bits of the stable controller, respectively, 
+while the two right columns display the total time (in seconds) required to synthesize a stable controller
 for the given plant.
 
-For the majority of our benchmarks, the conjecture explained in
+For the majority of the benchmarks, the conjecture explained in
 Section~\ref{synthesis-elements} holds and the two-stage verification 
@@
 of the benchmarks. This is possible if the inductive solutions need to be 
-refined with few counterexamples and increases of the fixed-point precision.  
-However, the benchmark \emph{SatelliteB2} with uncertainty ($G_{3b}$)
+refined with few counterexamples and increments of the fixed-point precision.  
+However, the benchmark \emph{SatelliteB2} with uncertainty ($G_{3b}$) has 
 required too many counterexamples to refine its solution.  
@@
 
+\blue{[The presence of uncertainty is not explained in this description and should be clearly elaborated and commented over the results in the Table.]}
+
 Considering the faster engine for each benchmark (marked as bold in Table~\ref{tab:results}), 
@@
 or the fixed-point word widths considered, or by using floating-point
-arithmetic instead.  The synthesized controllers were confirmed to be stable
+arithmetic instead.  The synthesized controllers have been confirmed to be stable
 outside of our model representation using MATLAB, positively answering RQ2. 
@@
 the results, all benchmarks and the \tool tool, is provided in the
-footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}}\footnote{CBMC version: 7a6cec1dd0eb8843559591105235f1f2c4678801}
+footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}\\ \red{[what does this alpha-numerical code mean?]}CBMC version: 7a6cec1dd0eb8843559591105235f1f2c4678801}
 

### 2017-02-13 hscc2017/paper.tex
work on text

@@
 %--------------------------------------
-\subsection{Threats to Validity}
+\subsection{Threats to Validity and Generalizations}
 %--------------------------------------
 
-We report a favourable assessment of \tool over a diverse set of real-world
+We have reported a favourable assessment of \tool over a diverse set of real-world
 benchmarks. Nevertheless, this set of benchmarks is limited within the
-scope of this paper and \tool's performance may not generalize to other
-benchmark scenarios. This can be addressed by expanding the benchmark set
+scope of this paper and \tool's performance 
+%may not generalize to other benchmark scenarios. This can 
+needs to be addressed by expanding the benchmarks set
 in future experiments.
 
-Furthermore, our algorithm to select suitable FWL word widths to model
+Furthermore, our approach to select suitable FWL word widths to model
 plant behavior employs a heuristic based on user-provided controller
@@
 the two-stage back-end of \tool increases performance significantly compared
-to the one-stage back-end, but this performance benefit introduced by CEGIS'
+to the one-stage back-end, but this performance benefit introduced by CEGIS 
 inductive generalizations may not be observed for other controller 
@@
 
-\paragraph{Robust synthesis of Linear Systems}
+\paragraph{Robust Synthesis of Linear Systems}
 

### 2017-02-13 hscc2017/paper.tex
More on Alessandro's comments

@@
 
+\newcommand{\aabatecmt}[1]{}%{{\color{blue}#1}}
 \newcommand{\blue}[1]{{\color{blue}#1}}
@@
 fixed-point arithmetic with finite word length (FWL). 
-\blue{[match list ordering with later one.]}
+\aabatecmt{[match list ordering with later one.]}
 The three effects of 1. uncertaities, 2. FWL representation, and 3. quantization errors are incorporated into the model, 
@@
 1. uncertainties in $G(s)$ (we denote them $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$) arising from tolerances/imprecision in the original model; 
-2. errors in the numerical calculations (which we model later as as external noises $\nu_1$ and $\nu_2$ \red{[no, these are the quantisation ones!]}); 
-and 3.
-roundoffs in the quantization (denoted $\Delta_b{G}_n(s),\Delta_b{G}_d(s)$ \red{[these are related to FWL - we introduce them as such, but then use other operators in equation 10 - very confusing]}).
+2. errors in the numerical calculations including FWL effects (denoted $\Delta_b{G}_n(s),\Delta_b{G}_d(s)$)
+\aabatecmt{[these are related to FWL - we introduce them as such, but then use other operators in equation 10 - very confusing]}.  
+and 
+3. errors caused by quantization (which we model later as as external noises $\nu_1$ and $\nu_2$);
+\aabatecmt{[no, these are the quantisation ones!]}
 These uncertainties are parametrically expressed by additive terms, eventually resulting in an uncertain model $\hat{G}(z)$, such that:
@@
    \node[draw=none] (ud) at ([xshift=-2cm,yshift=.15cm]gs)  {$U(s)$};
-   \node[draw=none] (y) at ([xshift=2cm,yshift=.15cm]gs)  {$Y(s)$};
+   \node[draw=none] (y) at ([xshift=2cm,yshift=.15cm]gs)  {$\hat{Y}(s)$};
    \& complexnode/.pic={ 
@@
 }
- \caption{Closed-loop digital control system \red{[has this hatted notation for the continuous-frequency plant ever been introduced?]} \label{fig:sampledsystem}}
+ \caption{Closed-loop digital control system \aabatecmt{[has this hatted notation for the continuous-frequency plant ever been introduced?]} \label{fig:sampledsystem}}
 \end{figure*}
@@
 and uncertainties introduced by quantizations in the ADC and
-DAC conversions ($\nu_1$ and $\nu_2$).  
-These sources are assumed to be non-deterministic \blue{[here you mean specifically the quantization effects?]}:  
+DAC conversions ($\nu_1$ and $\nu_2$) which are assumed to be non-deterministic.
+% \blue{[here you mean specifically the quantization effects?]}:  
 %which poses no further restriction to our model, 
-thus, 
-the uncertain model may be rewritten as a vector of coefficients in the z-domain using equation \eqref{eq:hatgvector} as  
+Thus, the uncertain model may be rewritten as a vector of coefficients in the 
+z-domain using equation \eqref{eq:hatgvector} as  
 %
@@
 %
-\blue{[ next statement is potentially quite confusing, especially since you used the hatted variables next. ]}
+\aabatecmt{[ next statement is potentially quite confusing, especially since you used the hatted variables next. ]}
 In the case of a synthesized controller, because the synthesis is performed
-using FWL, $\hat{C}(z) \equiv C(z)$.
-\red{[discuss relationship with introduced terms $\Delta_b{G}_n(s),\Delta_b{G}_d(s)$?]}
+using FWL, $\hat{C}(z) \equiv C(z)$ (\emph{ie} we synthesise a controller that is already in the domain $\mathbb{R} \langle I,F \rangle$ and has therefore no uncertanties.
+$\Delta_pC_n(z)=\Delta_pC_d(z)=\Delta_bC_n(z)=\Delta_bC_d(z)=0$).
+\aabatecmt{[discuss relationship with introduced terms $\Delta_b{G}_n(s),\Delta_b{G}_d(s)$?]}
 
@@
 and rounds operations outwards during calculations.  This effectively allows
-us to simultaneously evaluate \blue{[unclear:] the whole collection of plants $\hat{G}(s)$}
+us to simultaneously evaluate the whole collection of plants $\hat{G}(s)$ (\emph{ie} all concrete plants $G(s)$ in the range $G(s) \pm \Delta_pG(s)$)
+\aabatecmt{[unclear:] }
 plus the effects of numeric calculations in the engine.  Synthesized
@@
 %
-For instance, an implementation of $C(z)$ using \blue{[align with notation introduced earlier]} \param{4}{16} fixed-point
+For instance, an implementation of $C(z)$ using
+\aabatecmt{[align with notation introduced earlier]} 
+\param{4}{16} fixed-point
 numbers (i.e., $4$ bits for the integer part and $16$ bits for the
@@
 %
-\red{[new notation for controller with FWL?]}
+\aabatecmt{[new notation for controller with FWL?]}
 \begin{equation}
@@
 \resizebox{.47\textwidth}{!}{
-$C_{q}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
+$\hat{C}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
 {+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$. 
@@
 We now demonstrate how our approach solves the synthesis problem for the
-example given in the previous section.  We start with the candidate solution
+example given in the previous section.  We start with an a priori candidate solution
 with all coefficients zero, as given below, and a precision of $I_p=16$,
@@
 control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}. 
-\red{[Add comment on the next candidate solution - generated automatically, or selected manually?]}
+\aabatecmt{[Add comment on the next candidate solution - generated automatically, or selected manually?]}
 %

### 2017-02-13 hscc2017/paper.tex
included SHA-1 hash

--- 2017-02-13 hscc2017/paper.tex
@@
 the results, all benchmarks and the \tool tool, is provided in the
-footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}\\ \red{[what does this alpha-numerical code mean?]}CBMC version: 7a6cec1dd0eb8843559591105235f1f2c4678801}
+footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}\\ 
+CBMC (SHA-1 hash) version: 7a6cec1dd0eb8843559591105235f1f2c4678801}
 

### 2017-02-13 hscc2017/paper.tex
explained the presence of uncertainty in the experimental evaluation

@@
 lists the results for both engines, where in $16$ out of $23$
-benchmarks the two-stage engine is faster.
+benchmarks, the two-stage engine is faster.
 
@@
 
-\blue{[The presence of uncertainty is not explained in this description and should be clearly elaborated and commented over the results in the Table.]}
-
-Considering the faster engine for each benchmark (marked as bold in Table~\ref{tab:results}), 
-the median run-time amounts to $48$\,s, implying that \tool can synthesize half of the controllers 
-in less than one minute. Overall, the average fastest synthesis time considering
-both engines is approximately $42$ minutes.  We
+The presence of uncertainty in some particular benchmarks ($2$, $4$, $6$, and $8$) 
+leads to harder verification conditions to be checked 
+by the {\sc verify} phase, which thus influences the overall synthesis time. 
+However, considering the faster engine for each benchmark (marked as bold in Table~\ref{tab:results}), 
+the median run-time amounts to $48$\,s, implying that \tool can synthesize 
+half of the controllers in less than one minute. Overall, the average fastest synthesis 
+time considering both engines is approximately $42$ minutes.  We
 consider these times short enough to be of practical use to control

### 2017-02-13 hscc2017/paper.tex
work on text

--- 2017-02-13 hscc2017/paper.tex
@@
 
-\newcommand{\aabatecmt}[1]{}%{{\color{blue}#1}}
+\newcommand{\aabatecmt}[1]{{\color{blue}#1}}
 \newcommand{\blue}[1]{{\color{blue}#1}}
@@
 %------------------------------------
-\subsection{Verifying Closed-loop Control Systems \\ \blue{Model Imprecision, Quantization Effects, and Finite Word Length Representation}}
+\subsection{Model Imprecision, Finite Word Length Representation, and Quantization Effects}
 \label{verifying-closed-loop-control-systems}
@@
 1. uncertainties in $G(s)$ (we denote them $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$) arising from tolerances/imprecision in the original model; 
-2. errors in the numerical calculations including FWL effects (denoted $\Delta_b{G}_n(s),\Delta_b{G}_d(s)$)
-\aabatecmt{[these are related to FWL - we introduce them as such, but then use other operators in equation 10 - very confusing]}.  
+2. errors in the numerical calculations due to FWL effects (e.g., coefficient truncation and round-off, which will be denoted as $\Delta_b{G}_n(s),\Delta_b{G}_d(s)$);    
 and 
-3. errors caused by quantization (which we model later as as external noises $\nu_1$ and $\nu_2$);
-\aabatecmt{[no, these are the quantisation ones!]}
+3. errors caused by quantization (which we model later as as external noises $\nu_1$ and $\nu_2$). 
 These uncertainties are parametrically expressed by additive terms, eventually resulting in an uncertain model $\hat{G}(z)$, such that:
@@
 that the parametric errors in the plant have the same polynomial order as
-the plant itself (\blue{indeed, all other errors described in this paper are ensured to
-fulfil this property in our implementation}). 
+the plant itself (indeed, all other errors described in this paper are ensured to
+fulfil this property in our implementation). 
 %\red{[have we later argued that this is indeed the case?]}) 
@@
 the results, all benchmarks and the \tool tool, is provided in the
-footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}\\ 
-CBMC (SHA-1 hash) version: 7a6cec1dd0eb8843559591105235f1f2c4678801}
+footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}\\ \red{[what does this alpha-numerical code mean?]}CBMC version: 7a6cec1dd0eb8843559591105235f1f2c4678801}
 

### 2017-02-13 hscc2017/paper.tex
work on text

@@
 domain, 
-\red{[confusing? (related to observation above.)]}
 %
@@
 $C(z)$ in~\eqref{Eq:running-example-controller} stabilizes the
-closed-loop system for the discrete plant model $G(z)$ in~\ref{Eq:running-example-plant}.  
+closed-loop system for the discrete plant model $G(z)$ in~\eqref{Eq:running-example-plant}.  
 However, if the effects of finite-precision arithmetic are considered (e.g., fixed-point arithmetic and
@@
 For instance, an implementation of $C(z)$ using 
-\aabatecmt{[align with notation introduced earlier]} 
-\param{4}{16} fixed-point
+$\mathbb R \langle 4, 16 \rangle$ fixed-point
 numbers (i.e., $4$ bits for the integer part and $16$ bits for the

### 2017-02-13 hscc2017/paper.tex
Moved Fixed arithmetic section up

@@
 
-\newcommand{\aabatecmt}[1]{{\color{blue}#1}}
+\newcommand{\aabatecmt}[1]{}%{{\color{blue}#1}}
 \newcommand{\blue}[1]{{\color{blue}#1}}
@@
 fulfil this property in our implementation). 
-%\red{[have we later argued that this is indeed the case?]}) 
-%\blue{and that enter the plant linearly}.
+We also note that due to the digital implementation, there are no parametric errors in the controller($\Delta_pC_n(z)=\Delta_pC_d(z)$). Thus $\hat{C}(z) \equiv C(z)$.
 
@@
 
-%\begin{equation}
-%\Delta{\vec{p}}=\begin{bmatrix}
-%\hat{b_{0}} - b_{0}\\
-%\hat{b_{1}} - b_{1}\\
-%\vdots \\
-%\hat{b}_{M_G} - b_{M_{G}}\\
-%\hat{a_{0}} - a_{0}\\
-%\hat{a_{1}} - a_{1}\\
-%\vdots\\
-%\hat{a}_{N_G} - a_{N_{G}}\\
-%\end{bmatrix}=\begin{bmatrix}
-%\vec{\hat{b}}\\
-%\vec{\hat{a}}
-%\end{bmatrix}-\begin{bmatrix}
-%\vec{b}\\
-%\vec{a}
-%\end{bmatrix}
-%\label{eq:uncertainty}
-%\end{equation}
-
 A typical digital control system with a continuous plant and a discrete
@@
 seen as additive noise.
-
-%The system in equation~\ref{controller_plant_tf} (disregarding the $\Delta{G}_{P}(z)$ may be represented by the following difference equation model:
-%\begin{equation}
-%\begin{split}
-%y(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
-%+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M),
-%\end{split}
-%\end{equation}
-%and consequently $\hat{y}(k)$ may be represented by the following difference equation:
-%\begin{equation}
-%\label{eq:differencewithnoise}
-%\begin{split}
-%\hat{y}(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N_{G}}y(k-N_{G})\\
-%+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M_{G}}u(k-M_{G})+\nu(k).
-%\end{split}
-%\end{equation}
-%
-%The z-transform of~\eqref{eq:differencewithnoise} is:
-%\begin{equation}
-%\begin{split}
-%\hat{Y}(z)=(-a_{1}z^{-1}-a_{2}z^{-2}-\cdots-a_{N_{G}}z^{-N_{G}})Y(z)\\
-%+(b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M_{G}}z^{-M_{G}})U(z)+\nu(z),
-%\end{split}
-%\end{equation}
-%dividing both sides by $U(z)$, it is equivalent to:
-%\begin{equation}
-%\frac{\hat{Y}(z)}{U(z)}=[1-D_{G}(z)]G(z)+U(z)D_{G}(z)+\frac{\nu(z)}{U(z)}=G(z)+\Delta{G}_{Q}(z),
-%\end{equation}
-
-%Considering the quantization noise $\nu(k)$ as an output error in discrete plant model, we may represent it as an additive noise in the plant output $y(k)$ resulting in the noisy output $\hat{y}(k)$:
-%\begin{equation}
-%
-%\end{equation}
 
@@
 
-%\red{[why is the output in Figure 2 tilde, whereas that in  figure 1 hat?]}
-%
-\textcolor{cyan}{[rearrange next paragraph - param and quant]}
 In Figure~\ref{fig:digsystem1}, two sources of uncertainty are illustrated:
@@
 DAC conversions ($\nu_1$ and $\nu_2$) which are assumed to be non-deterministic. 
-% \blue{[here you mean specifically the quantization effects?]}:  
-%which poses no further restriction to our model, 
-Thus, the uncertain model may be rewritten as a vector of coefficients in the 
-z-domain using equation \eqref{eq:hatgvector} as  
-%
-%\begin{equation}
-%\label{eq:complete_unc_model}
-$\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}$. 
-%\end{equation}
-%
-%where $\Delta_p \vec{G}$ is the term that corresponds to the parametric uncertainties. 
 Recall that we discussed how the quantization noise is encompassed as an additive term, 
@@
 
+The uncertain model may be rewritten as a vector of coefficients in the 
+z-domain using equation \eqref{eq:hatgvector} as  
+$\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}$.
 The parametric uncertainties in the plant are assumed to have the same
 order as the plant model, since 
-%tolerances of higher order would invalidate the feedback model (even tiny 
 errors of higher order can move the closed-loop poles by large amounts, 
@@
 architecture of the plant.
-%, and models subject to such effects are inadequate.
-
-%\red{[next figure is a bit unnecessary, does not ad much to the previous one.]} Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.
-
-%\begin{figure}[ht]
-%\centering
-%
-%\tikzset{add/.style n args={4}{
-%    minimum width=6mm,
-%    path picture={
-%        \draw[circle] 
-%            (path picture bounding box.south east) -- (path picture bounding box.north west)
-%            (path picture bounding box.south west) -- (path picture bounding box.north east);
-%        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
-%        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
-%        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
-%        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
-%        }
-%    }
-% }
-%
-%\resizebox{.5\textwidth}{!}{
-% \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
-%     semithick, initial text=, ampersand replacement=\&,]
-%
-%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
-%  %
-%	\& 
-%	\&
-%	\& \coordinate (aux7); 
-%	\& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm] (deltag2) {{\sc $\Delta G_{Q}(z)$}};
-%	\& \coordinate (aux8);\\
-%    \node[draw=none] (r) {$R(z)$};
-%%   \& \coordinate (aux0);
-%   \& \node[circle,add={-}{+}{}{}] (circle) {};
-%   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
-%   \& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm,
-%        label=\textbf{Controller}] (cz) {{\sc C(z)}};
-%   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
-%   \& \coordinate (aux4);
-%   \& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm,
-%        label=\textbf{Plant}] (gs) {{\sc G(z)}};
-%   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$Y(z)$};
-%   \& \node[circle,add={+}{+}{+}{}] (circle2) {};
-%%   \node[draw=none] (tyz) at ([xshift=-1cm,yshift=.15cm]circle2)  {$Y(z)$};
-%%   \node[draw=none] (nu) at ([yshift=1cm]circle2)  {$\nu(z)$};
-%   \& \coordinate (aux1);
-%   \& \node[draw=none] (yz) {$\hat{Y}(z)$};\\
-%   \& 
-%   \&
-%   \& \coordinate (aux5); 
-%   \& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm] (deltag) {{\sc $\Delta G_{P}(z)$}};
-%   \& \coordinate (aux6);\\
-%   \& \coordinate (aux3); 
-%   \&
-%   \& 
-%   \& 
-%   \&
-%   \& \coordinate (aux2);\\
-%  };
-%
-%
-%%  \path[->] (v1) edge (q1.north);
-%%  \path[->] (v2) edge (q2.north);
-%  \path[->] (r) edge (circle.west);
-%%  \path[->] (nu) edge (circle2.north);
-%  \path[->] (aux1) edge (yz);
-%  \path  
-%   (aux4.north) edge (aux5.south)
-%   (aux4.north) edge (aux7.south)
-%   (aux5.east) edge (deltag.west)
-%   (aux7.east) edge (deltag2.west)
-%   (deltag.east) edge (aux6.west)
-%   (deltag2.east) edge (aux8.west)
-%   (circle.east) edge (cz)
-%   (cz.east) edge (gs.west)
-%   (circle2.east) edge (aux1.west)
-%   (aux1.south) edge (aux2.north)
-%   (aux2.west) edge (aux3.east); 
-%  \path[->] (aux8.south) edge (circle2.north); 
-%  \path[->] (aux6.south) edge (circle2.south);
-%  \path[->] (gs.east) edge (circle2.west);
-%  \path[->] (aux3.north) edge (circle.south);
-% \end{tikzpicture}
-%}
-% \caption{Digital system with additive uncertainties $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$. \label{fig:digsystem2}}
-%\end{figure}
-
-%\textcolor{blue}{[IB: I propose to exchange the following paragraphs by the previous blue]}
-
-%\textcolor{green}{DC: I believe Alessandro wanted to be more specific about the nature of the modelling error which is why I was trying to explain it.
-In this case I believe there are also two separate sources for $\Delta{G}_p(z)$.
-The first is $\Delta{G}_p(s)$ (which is basically a known tolerance that may come from G(t)), while the second is the error introduced by the calculations in the $\mathcal{Z}$ transform.
-Alessandro, do you want to address this second term (possibly as explained below) or just leave the blue section as is?}
-
-%Since $G(z)$ is an approximation of $G(s)$ we introduce an error term caused during its calculation as $\Delta{G}_P$
-%
-%%
-%\begin{align}
-%\small
-%\label{parametric_plant_tf}
-%\hat{G}(z)&=\frac{(b_{0}+\Delta_p b_{0}) +...+(b_{M_G}+\Delta_p b_{M_G})z^{-M_G}}{(a_{0}+\Delta_p a_{0})+...+(a_{N_G}+\Delta_p a_{N_G})z^{-N_G}} \nonumber \\
-%&=G(z)+\Delta{G}_P(z).
-%\end{align}
-%%
-%Note that $\Delta{G}_P$ is undefined and upper bound by a user defined
-%value such that $\hat{G}(z)$ corresponds to the set of
-%possible polynomial forms of $G(z, T)$ that overapproximate $G(s)$.
-%This calculation is performed outside of the scope of this work since it depends on the nature of the tool used to obtain the $\mathcal{Z}$ form.
-The error comes from the bounded horizon and mathematical precision used to calculate the $\mathcal{Z}$ transform, which will be tool and user dependent.
-%\red{[The previous statement is confusing and I must disagree here: I want hard error bounds on a specific value of T.]}
-%\green{[You are correct.
-It was absolutely wrong.
-Hopefully this explanation is clear.
-We use MATLAB, but still don't know the details of their implementation, so I don't have hard data on how this error is calculated.}
 
@@
 
-\textcolor{cyan}{[next discussion on fwl]}
+\paragraph{Using a Fixed-point Controller}
 
@@
 We shall denote the FWL domain of the coefficients by $\mathbb{R}\langle I,F
-\rangle$
-%
-%Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
-%domain, {\it i.e.} a Fixed-Point Finite Word Length with integer size $I$ and fractional
-%size $F$, we shall denote this domain as $\mathbb{R}\langle I,F \rangle$ 
-%
-and assume that there exists a function
-$\mathcal{F}_n\langle I,F \rangle(\cdot):\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$,
-which applies the FWL effects to a polynomial, with an equivalent $\mathcal{F}_{n,m}\langle I,F \rangle(\cdot):\mathcal{P}^{n,m}\rightarrow \mathcal{P}^{n,m}\langle I,F \rangle$ that applies the same effect to a ratio of polynomials, where
-$\mathcal{P}^{n}$ is the
-space of polynomials of $n$-th order, $\mathcal{P}^{n}\langle I,F
-\rangle$ is the space of polynomials with coefficients in
-$\mathbb{R}\langle I,F \rangle$, and $\mathcal{P}^{n,m}$,  $\mathcal{P}^{n,m}\langle I,F
-\rangle$ are their rational equivalent.
-
-Thus, the perturbed controller model $\hat{C}(z)$ may be obtained from the
+\rangle$ and define a function
+\begin{align}
+\small
+%\label{FWL_tf}
+\mathcal{F}_n&\param{I}{F}(P \in \mathcal{P}):\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\param{I}{F} \\
+&\triangleq \tilde P \in \mathcal{P}^{n}\param{I}{F} : c_i \in \vec{P} \wedge \tilde c_i \in \vec{\tilde{P}}=\mathcal{F}_0\param{I}{F}(c_i)  \nonumber
+\end{align}
+where $\mathcal{P}^{n}$ is the space of polynomials of $n$-th order,
+$\mathcal{P}^{n}\param{I}{F}$ is the space of polynomials with coefficients in
+$\mathbb{R}\param{I}{F}$ and $\mathcal{F}_0\param{I}{F}(x)$ returns the
+element $\tilde{x} \in \mathbb{R}\param{I}{F}$ that is closest to $x$.
+
+Similarly, $\mathcal{F}_{n,m}\langle I,F \rangle(\cdot):\mathcal{P}^{n,m}\rightarrow \mathcal{P}^{n,m}\langle I,F \rangle$ applies the same effect to a ratio of polynomials, where $\mathcal{P}^{n,m}$,  $\mathcal{P}^{n,m}\langle I,F
+\rangle$ are rational polynomial domains.
+
+Thus, the perturbed controller model $\tilde{C}(z)$ may be obtained from the
 original model $C(z)=\frac{C_{n}(z)}{C_{d}(z)}$ as follows:
@@
 \begin{equation}
-\hat{C}(z)=\mathcal{F}_{M_C,N_C}\langle I,F \rangle(C(z))=\frac{\mathcal{F}_{M_C}\langle I,F \rangle(C_n(z))}{\mathcal{F}_{N_C}\langle I,F \rangle(C_d(z))}.
+\tilde{C}(z)=\mathcal{F}_{M_C,N_C}\param{I}{F}(C(z))=\frac{\mathcal{F}_{M_C}\param{I}{F} (\hat{C}_n(z))}{\mathcal{F}_{N_C}\param{I}{F}(\hat{C}_d(z))}.
 \end{equation}
 %
-\aabatecmt{[ next statement is potentially quite confusing, especially since you used the hatted variables next. ]}
 In the case of a synthesized controller, because the synthesis is performed
-using FWL, $\hat{C}(z) \equiv C(z)$ (\emph{ie} we synthesise a controller that is already in the domain $\mathbb{R} \langle I,F \rangle$ and has therefore no uncertanties.
-$\Delta_pC_n(z)=\Delta_pC_d(z)=\Delta_bC_n(z)=\Delta_bC_d(z)=0$).
-\aabatecmt{[discuss relationship with introduced terms $\Delta_b{G}_n(s),\Delta_b{G}_d(s)$?]}
-
-%\textcolor{blue}{[IB: And I propose to exchange the remaining paragraphs by the previous blue]}
-%
-%\textcolor{green}{[DC: I changed it to a separate section to differentiate the effects, so we should keep both]}
+using FWL, $\tilde{C}(z) \equiv \hat{C}(z) \equiv C(z)$ (\emph{ie} we synthesise a controller that is already in the domain $\mathbb{R} \param{I}{F}$ and has therefore no uncertanties.
+$\Delta_bC_n(z)=\Delta_bC_d(z)=0$).
+
+\paragraph{Fixed-point computation in program synthesis}
+
+The program synthesis engine uses fixed-point arithmetic.  Specifically, we
+use the domain $\mathbb{R}\param{I}{F}$ for the controller's coefficients
+and the domain $\mathbb{R}\param{I_p}{F_p}$ for the plant's coefficients,
+where $I$ and $F$, as well as $I_p$ and $F_p$, denote the number of bits for
+the integer and fractional parts, respectively, and $\mathbb{R}\param{
+I_p}{F_p} \supseteq \mathbb{R}\param{I}{F}$.
+
+Given the use of fixed-point arithmetic, we examine the discretization effect 
+during these operations. Let $\tilde C(z)$ and $\tilde G(z)$ be 
+transfer functions represented using fixed-point bit-vectors.
+%
+\begin{align}
+\small
+\label{digital_controller_plant_tf}
+\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
+%\label{plant_tf}
+\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
+\end{align}
+
+Since the controller is synthesized in the $\mathbb{R}\param {I}{F}$
+domain, $\tilde{C}(z) \equiv \hat{C}(z) \equiv C(z)$
+
+However, given a real plant collection $\hat{G}(z)$,
+%
+we calculate $\tilde G(z)=\mathcal{F}_{M_G,N_G}\param {I_p}{F_p}(\hat{G}(z))$, where 
+%
+\begin{align}
+\label{digital_plant_tf}
+\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_b \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_b \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_b \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_b \hat{a}_{N_G})z^{-N_G}} \nonumber \\
+\vec{\tilde G} &=\vec{\hat{G}}+\Delta_b{\vec{G}}=\vec{G}+\Delta_p{\vec{G}}+\Delta_b{\vec{G}}, 
+\end{align}
+%
+where $\Delta_bc_i=\tilde{c}_i-\hat{c}_i$, 
+and $\Delta_b{G}$ represents the plant uncertainty caused by
+the rounding off effect.  We encompass all the uncertainty as
+$\Delta{\vec{G}}=\Delta_p{\vec{G}}+\Delta_b{\vec{G}}$.
+
+As the cost of SAT solving increases with in the size of the problem
+instance, our algorithm tries to solve the problem first for small $I_p$,
+$F_p$, iteratively increasing the precision if it is insufficient.
 
@@
 \end{myassumption}
-
-%\begin{mylemma}
-%\label{lemma:variance}
-%%
-%In particular, Widrow \cite{widrow1956} models the quantization noise as a
-%Gaussian model in which the second moment (variance) of the probability
-%density function (PDF) of the quantization noise is given by
-%%
-%\begin{equation}
-%\label{eq:variancelemma}
-%\sigma_{Q}^{2}=\frac{q^{2}}{12},
-%\end{equation}
-%where $q$ is the step size of quantiser. (Proof is on \cite{widrow1956})
-%\end{mylemma}
-%
-%\begin{mylemma}
-%\label{lemma:boundednoise}
-%%
-%The power spectral density of the quantization noise (supposed white)
-%$S_{\nu}(z)$ is bounded and may be computed through the z-transform of
-%autocorrelation function of $\nu(k)$, thus:
-%%
-%\begin{equation}
-%S_{\nu}(z)= \sigma_{Q}^{2}=\frac{q^{2}}{12}.
-%\end{equation}
-%\end{mylemma}
-%
-%\begin{proof}
-%%
-%Considering $\nu(k)$ a random process, where $\nu(k)$ is independent from
-%$\nu(k+i)$ for every integer $k\neq 0$.  The autocorrelation function of
-%$\nu(k)$, {\it i.e.} $R_{\nu\nu}(\tau)$ may be computed as follows:
-%%
-%\begin{equation}
-%R_{\nu\nu}(\tau)=E[\nu(t+\tau)\nu(t)]=\sigma_{Q}^{2}\cdot \delta(\tau),
-%\end{equation}
-%%
-%where $\delta(\tau)$ is the Dirac delta function at delay time $\tau$.
-%
-%By definition~\cite{poularikas2000transforms}, the power spectral density of
-%$\nu(k)$ is the z-transform of $R_{\nu\nu}(\tau)$, thus
-%%
-%\begin{equation}
-%S_{\nu}(z)=  \sum\limits_{k=-\infty}^{\infty}{R_{\nu\nu}(k)z^{-k}} = \sigma_{Q}^{2},
-%\end{equation}
-%considering the Lemma~\ref{lemma:variance}:
-%\begin{equation}
-%S_{\nu}(z)=  \frac{q^{2}}{12}.
-%\end{equation}
-%\end{proof}
-%
-%Finally, the quantization noise spectrum may be considered a energy-bounded
-%(Lemma~\ref{lemma:boundednoise}), and consequently the Parseval's theorem
-%ensures that the quantization noise is also energy-bounded in time-domain. 
-%Thus $\hat{Y}(z)$ will be bounded and the closed-loop system stable if the
-%conditions in Lemma~\ref{lemma:eq_int_stab} are followed.
-
-%\red{[Add remark on bound (q/2) for signal. We need a bounded signal to be able to leverage BIBO stability results. ]}
 
@@
 % in the general description of the synthesiser]}
-
-\paragraph{Fixed-point computation in program synthesis}
-
-The program synthesis engine uses fixed-point arithmetic.  Specifically, we
-use the domain $\mathbb{R}\param{I}{F}$ for the controller's coefficients
-and the domain $\mathbb{R}\param{I_p}{F_p}$ for the plant's coefficients,
-where $I$ and $F$, as well as $I_p$ and $F_p$, denote the number of bits for
-the integer and fractional parts, respectively, and $\mathbb{R}\langle
-I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
-%
-%the coefficients for $C(z)$ 
-%$N_c$ and $D_c$ 
-%in the domain $\mathbb{R}\param{I}{F}$, 
-%and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, 
-%where $n_C$ and $m_C$ denote the order of the corresponding polynomials
-%where $I$ and $F$ denote the integer and fractional size, respectively.
-%Regarding the plant, its coefficients are this is synthesised over the 
-%domain $\mathbb{R}^{n_G+m_G}\param{I_p}{F_p}$, where $n_G$ and $m_G$ 
-%denote the order of the polynomials representing the 
-%numerator and denominator of the plant's transfer function, respectively. 
-%Again, $I_p$ and $F_p$ denote the integer and fractional size, respectively, with
-%$\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
-%
-Given the use of fixed-point arithmetic, we examine the discretization effect 
-during these operations. Let $\tilde C(z)$ and $\tilde G(z)$ be 
-transfer functions represented using fixed-point bit-vectors.
-%  with integer size $I_p$ and fractional
-% size $F_p$, whose domain is $\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
-%
-\begin{align}
-\small
-\label{digital_controller_plant_tf}
-\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
-%\label{plant_tf}
-\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
-\end{align}
-
-Since the controller is synthesized in the $\mathbb{R}\langle I,F \rangle$
-domain, 
-%
-$$
-\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j}, \text{ that is } \tilde C(z) \equiv C(z). 
-$$
-%
-However, given a real plant $\hat{G}(z)$, and a discretizing function 
-\red{[the function has been defined over a space of polynomials, but it is now applied to a real number x? ]}
-%
-\begin{align}
-\small
-%\label{FWL_tf}
-\mathcal{F}&\langle I_p,F_p \rangle : \mathbb{R} \rightarrow  \mathbb{R}\langle I_p,F_p \rangle\\
-&\triangleq \tilde x = \mathcal{F}\langle I_p,F_p \rangle(x) : \tilde x=x-(x\bmod\tilde x)\nonumber\\ 
-\red{\text{above: circular definition?}}\\
-\mathcal{F}_n&\langle I_p,F_p \rangle(P \in \mathcal{P}) \\
-&=\tilde P \in \mathcal{P}^{n}\langle I_p,F_p \rangle : c_i \in \vec{P} \wedge \tilde c_i \in \vec{\tilde{P}}=\mathcal{F}\langle I_p,F_p \rangle(c_i)  \nonumber
-\end{align}
-%
-we calculate $\tilde G(z)=\mathcal{F}_{M_G,N_G}\langle I_p,F_p \rangle(\hat{G}(z))$, where 
-%
-\begin{align}
-% \label{digital_controller_tf}
-% \tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_b \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
-% &= C(z) =\hat{C}(z) + \Delta{C}_b(z)\\
-%
-\label{digital_plant_tf}
-\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_b \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_b \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_b \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_b \hat{a}_{N_G})z^{-N_G}} \nonumber \\
-\vec{\tilde G} &=\vec{\hat{G}}+\Delta_b{\vec{G}}=\vec{G}+\Delta_p{\vec{G}}+\Delta_b{\vec{G}}, 
-\end{align}
-%
-where $\Delta_b\hat{c}_i=\hat{c}_i\bmod \tilde{c}_i$, 
-and $\Delta_b{G}$ represents the plant uncertainty caused by
-the rounding off effect.  We encompass all the uncertainty as
-$\Delta{\vec{G}}=\Delta_p{\vec{G}}+\Delta_b{\vec{G}}$. 
-%
-As the cost of SAT solving increases with in the size of the problem
-instance, our algorithm tries to solve the problem first for small $I_p$,
-$F_p$, iteratively increasing the precision if it is insufficient.
 

### 2017-02-13 hscc2017/paper.tex
More comments

@@
 
-\textcolor{cyan}{[if space is needed, the next paragraph can be cut. ]}
-We cover preliminaries on plant discretization, the verification of
-closed-loop control systems, and stability in
-Section~\ref{sec:preliminaries}.  Our core contribution is in
-Section~\ref{sec:synthesis}: we present our CEGIS-based algorithm for
-generating stable controllers for a given plant model.  Our experimental
-setup and experimental results are given in Section~\ref{sec:experiments},
-and we discuss how we extend the state-of-the-art beyond the existing
-literature in Section~\ref{sec:related}.
+%\textcolor{cyan}{[if space is needed, the next paragraph can be cut. ]}
+%We cover preliminaries on plant discretization, the verification of
+%closed-loop control systems, and stability in
+%Section~\ref{sec:preliminaries}.  Our core contribution is in
+%Section~\ref{sec:synthesis}: we present our CEGIS-based algorithm for
+%generating stable controllers for a given plant model.  Our experimental
+%setup and experimental results are given in Section~\ref{sec:experiments},
+%and we discuss how we extend the state-of-the-art beyond the existing
+%literature in Section~\ref{sec:related}.
 
@@
 \section{Preliminaries}\label{sec:preliminaries}
-
-%\blue{Please insert a figure clearly distinguishing between continuous and discretised/quantised plant - a template is in a picture sent out by Lucas late last week.
-Please introduced signals on the plot.
-
-%Let us straighten the notations next. 
-%We should have 
-%\begin{itemize}
-%\item 
-%$G(s) = \frac{s^{M_G}b_{0}+s^{M_G-1}b_{1}+...+b_{M_G}}{s^{N_G}a_{0}+s^{N_G-1}a_{1}+...+a_{N_G}}$ -- this is the physical plant, which is focus of interest and to which we refer our specifications/properties
-%\item 
-%$G(z, T) = \frac{\bar b_{0}+\bar b_{1}z^{-1}+...+\bar b_{M_G}z^{-M_G}}{\bar a_{0}+\bar a_{1}z^{-1}+...+\bar a_{N_G}z^{-N_G}}$ -- this is the time-discretised plant (notice the notation encompasses explicitly the sample time $T$; please write out explicitly the relationship between the $a_i$ and the $\bar a_i$ and likewise for the numerator's coefficients
-%(in particular, are the orders $M_G, N_G$ the same? 
-%\item 
-%we have $Y(z) = G(z,T) U(z)$; then, we introduce $\hat Y(z) \doteq Y(z) + \nu (z)$, so that 
-%$$
-%\frac{\hat Y(z)}{U(z)} = G(z,T) + \frac{\nu (z)}{U(z)} = G(z,T) + \Delta G_Q(z) \doteq \hat G(z) ,  
-%$$ 
-%where $\Delta G_Q(z)$ is an error term accounting for the quantization effects 
-%\item 
-%finally, we encompass the errors resulting from employing finite parameters representation, 
-%which we encompass in a term $\Delta G_P(z)$: is this error additive, so that we would get to a 
-%$$
-%\tilde G(z) \doteq \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z)?  
-%$$ 
-%Dario, can you write it out explicitly? In other words, if 
-%$$
-%\hat G(z) = G(z,T) + \Delta G_Q(z) = \frac{\hat b_{0}+\hat b_{1}z^{-1}+...+\hat b_{M_G}z^{-M_G}}{\hat a_{0}+\hat a_{1}z^{-1}+...+\hat a_{N_G}z^{-N_G}},  
-%$$ 
-%then what is the explicit expression of 
-%$$
-%\tilde G(z) = \frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}?
-%$$
-%(Notice that the orders $M_G, N_G$ need to be properly taken care of.)
-%\item 
-%Now, it's over the transfer function $\tilde G(z)$ that we want to synthesise the parameters of a template $C(z)$. 
-%This controller's transfer function will be subject to the same quantization and precision limits as the plant's: 
-%we need to argue that the way we do synthesis affects manipulation of quantities that relate to specific errors and be explicit about these. 
-%\item[]
-%\item 
-%An additional source of error can be related to the fact that a plant transfer function, 
-%per se a physical entity, is actually represented in a program imprecisely: 
-%this would mean that $G(s)$ is actually 
-%$$
-%G^\ast (s) \doteq \frac{s^{M_G^\ast}b_{0}+s^{M_G^\ast-1}b_{1}+...+b_{M_G}}{s^{N_G^\ast}a_{0}+s^{N_G^\ast-1}a_{1}+...+a_{N_G}}, 
-%$$ 
-%which perhaps can indeed be re-written as $G^\ast (s) = G(s) + \Delta G_P(s)$? (This proof should come from that above.) 
-%We should argue that this error is encompassed by the one derived above (or isn't it?). 
-%\end{itemize}
-%}
 
@@
 continuous plant and look at the plant dynamics from the perspective of the digital controller.
-%We briefly recall the standard foundations of this step.
 
@@
 which is naturally described via a Laplace-domain transfer function $G(s)$. 
-% and the sampling and hold process. 
 The continuous model of the plant must be discretized to obtain the
@@
 
-%\red{[why do we discuss the ZOH at this point?]}
-
 Among the discretization methods in the literature~\cite{Franklin15}, 
-%the zero-order hold (ZOH) discretization is suitable for representing 
 we consider the sample-and-hold processes in complex systems~\cite{istepanian2012digital}.  
@@
 %------------------------------------
-
-%\red{[This section and the next should be merged into a crisp section with the background on DSVerifier, if not included in previous work? 
-%Please stick to the introduced notations. Please clarify what the function FWL does, compared to the general approximations introduced above.]}
-
-%\red{Alessandro, I've made the changes as requested. Please let me know if this is good enough or if I made it too short}
-
-%\textcolor{blue}{[IB: I'm proposing some changes in this section based on Alessandro's comments and trying to obtain a simpler and uniform notation.]}
 
@@
 
-Let $C(z)$ be a digital controller and $G(z)$ be a digital representation of the plant, 
+Let $C(z)$ be a digital controller and $G(z)$ be a discrete-time representation of the plant, 
 given as
@@
 Uncertainties in $G(z)$ may appear due to: 
-1. uncertainties in $G(s)$ (we denote them $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$) arising from tolerances/imprecision in the original model; 
+1. uncertainties in $G(s)$ (we denote $\hat{G}(s)=\frac{G_n(s)+\Delta_p{G}_n(s)}{G_d(s)+\Delta_p{G}_d(s)}$) arising from tolerances/imprecision in the original model; 
 2. errors in the numerical calculations due to FWL effects (e.g., coefficient truncation and round-off, which will be denoted as $\Delta_b{G}_n(s),\Delta_b{G}_d(s)$);    
@@
 	minimum height=1cm,
-        label=\textbf{Controller}] (cz) {{\sc C(z)}};
+        label=\textbf{Controller}] (cz) {\sc $\hat{C}(z)$};
    \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
@@
    \& \coordinate (aux1);
-   \& \node[draw=none] (yz) {$\tilde {Y}(z)$};\\
+   \& \node[draw=none] (yz) {$\hat {Y}(z)$};\\
    \& \coordinate (aux3); 
@@
 may have a different FWL representation than the controller),
-%\red{[why is the DAC introducing a quantisation error again?]}
 which are modeled as noises
@@
 and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system 
-\red{[notice we have tilde outputs in the two figures! these need to be explained here.]}. 
 %
@@
         label=\textbf{Plant}] (gs) {{\sc $\hat{G}(z)$}};
-   \node[draw=none] (y) at ([xshift=2cm,yshift=.15cm]gs)  {$Y(z)$};
+%   \node[draw=none] (y) at ([xshift=2cm,yshift=.15cm]gs)  {$Y(z)$};
 
@@
    \& \coordinate (aux1);
-   \& \node[draw=none] (yz) {$\tilde Y(z)$};\\
+   \& \node[draw=none] (yz) {$\hat Y(z)$};\\
    \& \coordinate (aux3); 
@@
 The synthesis problem we are trying to solve is the following:
-find a digital controller $C(z)$ %denoted by  $N_c$ and $D_c$ 
+find a digital controller $\tilde C(z)$ %denoted by  $N_c$ and $D_c$ 
 that makes the closed-loop system stable 
@@
 When mapping back to the notation used for describing the general architecture 
-of the program synthesizer, the controller $C(z)$ denotes $P$ and 
+of the program synthesizer, the controller $\tilde C(z)$ denotes $P$ and 
 $\tilde G(z)$ represents $x$.
 
-As mentioned above, we compute the coefficients for $C(z)$ 
+As mentioned above, we compute the coefficients for $\tilde C(z)$ 
 %$N_c$ and $D_c$ 
@@
 The {\sc synthesize} phase uses BMC to 
-compute a solution $C(z)$. % An important remark is that this 
-% controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
-% domain.
+compute a solution $\tilde C(z)$.
 There are two approaches for the {\sc verify} phase.
-% based on the described model.  
 The first approach uses interval arithmetic \cite{moore1966interval}
@@
 us to simultaneously evaluate the whole collection of plants $\hat{G}(s)$ (\emph{ie} all concrete plants $G(s)$ in the range $G(s) \pm \Delta_pG(s)$)
-\aabatecmt{[unclear:] }
 plus the effects of numeric calculations in the engine.  Synthesized
@@
 The resulting system using the typical series loop configuration, where
-$C_{q}(z)$ and $G(z)$ are in the forward path, is unstable. 
+$\hat{C}(z)$ and $G(z)$ are in the forward path, is unstable. 
 Figure~\ref{fig:original} gives the Bode diagram for the digital controller

### 2017-02-14 hscc2017/paper.tex
hscc17

@@
 \and
-$^{1}$\affaddr{University of Oxford, Oxford, United Kingdom} \\
+$^{1}$\affaddr{University of Oxford, Oxford, United Kingdom} \quad
 $^{2}$\affaddr{Federal University of Amazonas, Manaus, Brazil}
@@
 fixed-point arithmetic with finite word length (FWL).  
-\aabatecmt{[match list ordering with later one.]}
 The three effects of 1. uncertaities, 2. FWL representation, and 3. quantization errors are incorporated into the model, 
@@
 
+\red{[This part should be removed, or moved to a later place - it does not have anything to do with the material discussed in this section.]
 CEGIS-based control synthesis requires a formal verifier to check whether a
@@
 uncertainty parameters in the plant model (plant intervals)~\cite{Bessa16}.   
+}
 
@@
 Uncertainties in $G(z)$ may appear due to: 
-1. uncertainties in $G(s)$ (we denote $\hat{G}(s)=\frac{G_n(s)+\Delta_p{G}_n(s)}{G_d(s)+\Delta_p{G}_d(s)}$) arising from tolerances/imprecision in the original model; 
+1.
+uncertainties in $G(s)$ (we denote the uncertain continuous plant by $\hat{G}(s)=\frac{G_n(s)+\Delta_p{G}_n(s)}{G_d(s)+\Delta_p{G}_d(s)}$) arising from tolerances/imprecision in the original model;
 2. errors in the numerical calculations due to FWL effects (e.g., coefficient truncation and round-off, which will be denoted as $\Delta_b{G}_n(s),\Delta_b{G}_d(s)$);    
@@
 }
- \caption{Closed-loop digital control system \aabatecmt{[has this hatted notation for the continuous-frequency plant ever been introduced?]} \label{fig:sampledsystem}}
+ \caption{Closed-loop digital control system \label{fig:sampledsystem}}
 \end{figure*}
@@
 
-\paragraph{Using a Fixed-point Controller}
+\paragraph{Use of a fixed-point controller}
 
@@
 
+\red{[This part should be removed, or moved to a later place - it does not have anything to do with the material discussed in this section.]
 As the cost of SAT solving increases with in the size of the problem
@@
 $F_p$, iteratively increasing the precision if it is insufficient.
+}
 
 %------------------------------------
-\subsection{Stability under FWL Representation, Quantisation Noise and Parametric Uncertainties}
+\subsection{Closed-Loop Stability Verification under Parametric Uncertainties FWL Representation, and Quantisation Noise}
 \label{sec:stability}
@@
 
-\paragraph{Specification of the stability property}
+\paragraph{Formal specification of the stability property}
 

### 2017-02-14 hscc2017/paper.tex
small edits sec 3.5 (soundness)

@@
 outward rounding to ensure that these errors do not exceed critical
-bounds that could make some (or all) plant(s) unstable.
+bounds that could make some plant unstable.
 
@@
 We require two verification stages because,
-while the second phase can ensure the stability of all plants in the collection, 
+while the second one can ensure the stability of all plants in the collection, 
 it is unable to provide a counterexample.

### 2017-02-14 hscc2017/paper.tex
hscc17

--- 2017-02-14 hscc2017/paper.tex
@@
 1.
-uncertainties in $G(s)$ (we denote the uncertain continuous plant by $\hat{G}(s)=\frac{G_n(s)+\Delta_p{G}_n(s)}{G_d(s)+\Delta_p{G}_d(s)}$) arising from tolerances/imprecision in the original model;
+uncertainties in $G(s)$ (we denote the uncertain continuous plant by $\hat{G}(s)=\frac{G_n(s)+\Delta_p{G}_n(s)}{G_d(s)+\Delta_p{G}_d(s)}$ to explicitly encompass the effects of the uncertainty terms $\Delta_p{G}_{(\cdot)}(s)$) arising from tolerances/imprecision in the original model;
 2. errors in the numerical calculations due to FWL effects (e.g., coefficient truncation and round-off, which will be denoted as $\Delta_b{G}_n(s),\Delta_b{G}_d(s)$);    
@@
 fulfil this property in our implementation). 
-We also note that due to the digital implementation, there are no parametric errors in the controller($\Delta_pC_n(z)=\Delta_pC_d(z)$). Thus $\hat{C}(z) \equiv C(z)$.
+We also remark that, due to its native digital implementation, 
+there are no parametric errors ($\Delta_pC_n(z), \Delta_pC_d(z)$) entering in the controller. 
+Thus $\hat{C}(z) \equiv C(z)$.
 

### 2017-02-14 hscc2017/paper.tex
fix on comments

--- 2017-02-14 hscc2017/paper.tex
@@
 
-\newcommand{\aabatecmt}[1]{{\color{blue}#1}}
 \newcommand{\blue}[1]{{\color{blue}#1}}
@@
 %------------------------------------
-
-\red{[This part should be removed, or moved to a later place - it does not have anything to do with the material discussed in this section.]
-CEGIS-based control synthesis requires a formal verifier to check whether a
-candidate controller meets the requirements when combined with the plant. 
-We use the Digital-System Verifier (DSVerifier)~\cite{IsmailBCFF15} in the
-verification module for \tool.  It checks the stability of closed-loop control systems and
-considers finite-word length (FWL) effects in the digital controller, and
-uncertainty parameters in the plant model (plant intervals)~\cite{Bessa16}.   
-}
 
@@
 
-\red{[This part should be removed, or moved to a later place - it does not have anything to do with the material discussed in this section.]
-As the cost of SAT solving increases with in the size of the problem
-instance, our algorithm tries to solve the problem first for small $I_p$,
-$F_p$, iteratively increasing the precision if it is insufficient.
-}
-
 %------------------------------------
@@
 Digital Systems Synthesis, named \tool.
+
+CEGIS-based control synthesis requires a formal verifier to check whether a
+candidate controller meets the requirements when combined with the plant. 
+We use the Digital-System Verifier (DSVerifier)~\cite{IsmailBCFF15} in the
+verification module for \tool.  It checks the stability of closed-loop control systems and
+considers finite-word length (FWL) effects in the digital controller, and
+uncertainty parameters in the plant model (plant intervals)~\cite{Bessa16}.
+
 %
@@
 $\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
+
+As the cost of SAT solving increases with in the size of the problem
+instance, our algorithm tries to solve the problem first for small $I_p$,
+$F_p$, iteratively increasing the precision if it is insufficient.
 
@@
 For instance, an implementation of $C(z)$ using 
-$\mathbb R \langle 4, 16 \rangle$ fixed-point
+$\mathbb R \param {4}{16}$ fixed-point
 numbers (i.e., $4$ bits for the integer part and $16$ bits for the
@@
 %
-\aabatecmt{[new notation for controller with FWL?]}
 \begin{equation}
@@
 control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}.
-\aabatecmt{[Add comment on the next candidate solution - generated automatically, or selected manually?]}
 %

### 2017-02-14 hscc2017/paper.tex
hscc17

@@
 }
- \caption{Closed-loop digital control system \label{fig:sampledsystem}}
+ \caption{Closed-loop digital control system (cf. Section \ref{verifying-closed-loop-control-systems} for notations) \label{fig:sampledsystem}}
 \end{figure*}
@@
 footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}\\ 
-CBMC (SHA-1 hash) version: 7a6cec1dd0eb8843559591105235f1f2c4678801}
+CBMC (SHA-1 hash) version: \\ 
+7a6cec1dd0eb8843559591105235f1f2c4678801}
 

### 2017-02-14 hscc2017/paper.tex
added Alessandro's comments back

--- 2017-02-14 hscc2017/paper.tex
@@
 
-The presence of uncertainty in some particular benchmarks ($2$, $4$, $6$, and $8$) 
+\blue{[The presence of uncertainty is not explained in this description and should be clearly elaborated and commented over the results in the Table.]}
+
+\textcolor{green}{The presence of uncertainty in some particular benchmarks ($2$, $4$, $6$, and $8$) 
 leads to harder verification conditions to be checked 
-by the {\sc verify} phase, which thus influences the overall synthesis time. 
+by the {\sc verify} phase, which thus influences the overall synthesis time}. 
 However, considering the faster engine for each benchmark (marked as bold in Table~\ref{tab:results}), 
@@
 footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}\\ 
-CBMC (SHA-1 hash) version: 7a6cec1dd0eb8843559591105235f1f2c4678801}
+\red{[what does this alpha-numerical code mean?]}
+\textcolor{green}{CBMC (SHA-1 hash) version:} 7a6cec1dd0eb8843559591105235f1f2c4678801}
 

### 2017-02-14 hscc2017/paper.tex
hscc17

--- 2017-02-14 hscc2017/paper.tex
@@
 \mathcal{F}_n&\param{I}{F}(P \in \mathcal{P}):\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\param{I}{F} \\
-&\triangleq \tilde P \in \mathcal{P}^{n}\param{I}{F} : c_i \in \vec{P} \wedge \tilde c_i \in \vec{\tilde{P}}=\mathcal{F}_0\param{I}{F}(c_i)  \nonumber
+&\triangleq \tilde P \in \mathcal{P}^{n}\param{I}{F} : c_i \in \vec{P} \wedge \tilde c_i \in \vec{\tilde{P}}=\mathcal{F}_0\param{I}{F}(c_i),  \nonumber
 \end{align}
 where $\mathcal{P}^{n}$ is the space of polynomials of $n$-th order,
-$\mathcal{P}^{n}\param{I}{F}$ is the space of polynomials with coefficients in
-$\mathbb{R}\param{I}{F}$ and $\mathcal{F}_0\param{I}{F}(x)$ returns the
-element $\tilde{x} \in \mathbb{R}\param{I}{F}$ that is closest to $x$.
+$\mathcal{P}^{n}\param{I}{F}$ is the space of polynomials with coefficients in $\mathbb{R}\param{I}{F}$, 
+and (as a special case) $\mathcal{F}_0\param{I}{F}(x)$ returns the element $\tilde{x} \in \mathbb{R}\param{I}{F}$ that is closest to the real parameter $x$.
 
@@
 Thus, the perturbed controller model $\tilde{C}(z)$ may be obtained from the
-original model $C(z)=\frac{C_{n}(z)}{C_{d}(z)}$ as follows:
+original model $\hat{C}(z) = C(z) = \frac{C_{n}(z)}{C_{d}(z)}$ as follows:
 %
@@
 %
-In the case of a synthesized controller, because the synthesis is performed
-using FWL, $\tilde{C}(z) \equiv \hat{C}(z) \equiv C(z)$ (\emph{ie} we synthesise a controller that is already in the domain $\mathbb{R} \param{I}{F}$ and has therefore no uncertanties.
-$\Delta_bC_n(z)=\Delta_bC_d(z)=0$).
+In the case of a digitally synthesized controller (as it is the case in this work), 
+because the synthesis is performed directly using FWL representation, 
+$\tilde{C}(z) \equiv \hat{C}(z) \equiv C(z)$ 
+(in other words, 
+we synthesise a controller that is already in the domain $\mathbb{R} \param{I}{F}$ and has therefore no uncertainties entering because of FWL representations, 
+that is $\Delta_bC_n(z)=\Delta_bC_d(z)=0$).
 

### 2017-02-14 hscc2017/paper.tex

@@
 footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}\\ 
-CBMC (SHA-1 hash) version: \\ 
-7a6cec1dd0eb8843559591105235f1f2c4678801}
+\red{[what does this alpha-numerical code mean?]}
+\textcolor{green}{CBMC (SHA-1 hash) version:} 7a6cec1dd0eb8843559591105235f1f2c4678801}
 

### 2017-02-14 hscc2017/paper.tex
hscc17

--- 2017-02-14 hscc2017/paper.tex
@@
 
-\paragraph{Use of a fixed-point controller}
+\paragraph{Direct use of controllers in fixed-point representation}
 
@@
 where $I$ and $F$, as well as $I_p$ and $F_p$, denote the number of bits for
-the integer and fractional parts, respectively, and $\mathbb{R}\param{
+the integer and fractional parts, respectively, and where it is practically motivated to consider $\mathbb{R}\param{
 I_p}{F_p} \supseteq \mathbb{R}\param{I}{F}$.
@@
 
-Since the controller is synthesized in the $\mathbb{R}\param {I}{F}$
-domain, $\tilde{C}(z) \equiv \hat{C}(z) \equiv C(z)$
-
-However, given a real plant collection $\hat{G}(z)$,
-%
-we calculate $\tilde G(z)=\mathcal{F}_{M_G,N_G}\param {I_p}{F_p}(\hat{G}(z))$, where 
+Recall that since the controller is synthesized in the $\mathbb{R}\param {I}{F}$
+domain, $\tilde{C}(z) \equiv \hat{C}(z) \equiv C(z)$. 
+However, given a real plant $\hat{G}(z)$, 
+we need to introduce $\tilde G(z)=\mathcal{F}_{M_G,N_G}\param {I_p}{F_p}(\hat{G}(z))$, where 
 %
@@
 and $\Delta_b{G}$ represents the plant uncertainty caused by
-the rounding off effect.  We encompass all the uncertainty as
+the rounding off effect.  We encompass the global uncertainty as
 $\Delta{\vec{G}}=\Delta_p{\vec{G}}+\Delta_b{\vec{G}}$.

### 2017-02-14 hscc2017/paper.tex
hscc17

@@
 
+\red{[Dario: please go through this section again, and clarify what sources of imprecision we consider where, distinguishing between plant and controller.
+also comment on why we operate on hat G rather than on tilde G - as we discussed yesterday.
+]}
+
 Sound synthesis of the digital controller requires the consideration of the effect of FWL on the controller, 
@@
 %and another one based on Jury's criterion~\cite{astrom1997computer}.  
-Here we choose Jury's criterion~\cite{astrom1997computer} in view of its efficiency: 
+Here we choose Jury's criterion~\cite{astrom1997computer} in view of its efficiency \blue{[check correctness] and ease of integration within \tool}: 
 we employ this method to check the stability in the $z$-domain for the
@@
 $\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
-
+%
 As the cost of SAT solving increases with in the size of the problem
@@
 However, if the effects of finite-precision arithmetic are considered (e.g., fixed-point arithmetic and
-word-length), then this closed-loop system becomes unstable.
+FWL), then this closed-loop system becomes unstable.
 %
@@
 fractional part) can be modeled as: 
+\red{[wait I'm confused: the next should be a tilde!!]}
 %
@@
 $\hat{C}(z)$ and $G(z)$ are in the forward path, is unstable. 
+\red{[hang in there - did we not consider FWL on $G(z)$? why not?]}
 Figure~\ref{fig:original} gives the Bode diagram for the digital controller

### 2017-02-14 hscc2017/paper.tex
more comments and alignment (removed bib pages to fit page-count)

@@
 and 
-3. errors caused by quantization (which we model later as as external noises $\nu_1$ and $\nu_2$). 
+3. errors caused by quantization (which we model later as as external disturbances $\nu_1$ and $\nu_2$). 
 These uncertainties are parametrically expressed by additive terms, eventually resulting in an uncertain model $\hat{G}(z)$, such that:
@@
 may have a different FWL representation than the controller),
-which are modeled as noises
+which are modeled as disturbances 
 $\nu_{1}(z)$ and $\nu_{2}(z)$;  
@@
 $U(z)$ is the control signal; 
-and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system 
+and $\hat{Y}(z)$ is the output signal affected by the disturbances and uncertainties in the closed-loop system 
 %
@@
 which means it does not enter parametrically in the transfer function. 
-Instead, we later show that the system is stable given these non-deterministic noise inputs.
+Instead, we later show that the system is stable given these non-deterministic disturbance inputs.
 
@@
 Sound synthesis of the digital controller requires the consideration of the effect of FWL on the controller, 
-and of quantization noises in the closed-loop system.  
+and of quantization disturbances in the closed-loop system.  
 Let the quantizer $Q1$ (ADC) be the source of a white noise $\nu_{1}$, 
@@
 \begin{equation}
-\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\cdot C(z)\cdot R(z)+\hat{G}(z)\cdot\nu_{2}(z)-\hat{G}(z)\cdot \hat{C}(z)\cdot \hat{Y}(z). 
+\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)C(z)R(z)+\hat{G}(z)\nu_{2}(z)-\hat{G}(z)\hat{C}(z)\hat{Y}(z). 
 \end{equation}
@@
 \label{eq:outputfunctions}
-\hat{Y}(z)=H_{1}(z)\cdot\nu_{1}(z)+H_{2}(z)\cdot\nu_{2}(z)+H_{3}(z)\cdot R(z),
+\hat{Y}(z)=H_{1}(z)\nu_{1}(z)+H_{2}(z)\nu_{2}(z)+H_{3}(z) R(z),
 \end{equation}
@@
 \begin{equation*}
-H_{1}(z)=\frac{1}{1+\hat{G}(z)\cdot \hat{C}(z)}, 
+H_{1}(z)=\frac{1}{1+\hat{G}(z) \hat{C}(z)}, 
 \end{equation*}
@@
 \begin{equation*}
-H_{2}(z)=\frac{\hat{G}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}, 
+H_{2}(z)=\frac{\hat{G}(z)}{1+\hat{G}(z) \hat{C}(z)}, 
 \end{equation*}
@@
 \begin{equation*}
-H_{3}(z)=\frac{\hat{G}(z)\cdot \hat{C}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}. 
+H_{3}(z)=\frac{\hat{G}(z) \hat{C}(z)}{1+\hat{G}(z) \hat{C}(z)}. 
 \end{equation*}
@@
 Figure~\ref{fig:sampledsystem} with a FWL implementation of the digital
-controller $\hat{C}(z) =\mathcal{F}_{M_C,N_C}\langle I,F \rangle(C(z))$ and uncertain discrete
+controller $\tilde{C}(z) =\mathcal{F}_{M_C,N_C}\param {I}{F}(C(z))$ and uncertain discrete
 model of the plant from~\eqref{eq:coefficients},\eqref{eq:delta_coefficients} 
@@
 \label{eq:internal_stab_lemma}
-\hspace{-3ex} S(z)=\mathcal{F}_{M_C}\langle I,F \rangle(C_n(z))\hat{G}_n(z)+\mathcal{F}_{N_C}\langle I,F \rangle(C_d(z))\hat{G}_d(z);
+\hspace{-3ex} S(z)=\tilde{C}_n(z)\hat{G}_n(z)+\tilde{C}_d(z)\hat{G}_d(z);
 \end{equation}
-\item the direct loop product $\mathcal{F}_{M_C,N_C}\langle I,F \rangle(C(z))\cdot \hat{G}(z)$ has no pole-zero cancellation on or outside the unit circle.
+\item the direct loop product $\tilde{C}(z) \hat{G}(z)$ has no pole-zero cancellation on or outside the unit circle.
 \end{itemize}
@@
 fractional part) can be modeled as: 
-\red{[wait I'm confused: the next should be a tilde!!]}
+\red{[wait I'm confused: to be precise, the next should be a tilde in view of the preceding comments on FWL!!] notice we are indeed approximating a C, so the equality comments from above do not apply!
+correct?}
 %
@@
 \resizebox{.47\textwidth}{!}{
-$\hat{C}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
+$\tilde{C}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
 {+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$. 
@@
 The resulting system using the typical series loop configuration, where
-$\hat{C}(z)$ and $G(z)$ are in the forward path, is unstable. 
+$\tilde{C}(z)$ and $G(z)$ are in the forward path, is unstable. 
 \red{[hang in there - did we not consider FWL on $G(z)$? why not?]}
@@
 We now demonstrate how our approach solves the synthesis problem for the
-example given in the previous section.  We start with an a priori candidate solution
-with all coefficients zero, as given below, and a precision of $I_p=16$,
-$F_p=24$.  The digital controller is designed with standard techniques for
+example given in the previous section.  
+Assuming a precision of $I_p=16$, $F_p=24$,  
+\blue{[so you mean we're not using Jury's criterion? pllease clarify.] the digital controller is designed with standard techniques for
 control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}. 
+}
+We start with an a-priori candidate solution with all coefficients zero: 
 %
@@
 $$ 
-C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}. 
+\tilde{C}(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}. 
 $$
+\blue{[here recall that indeed this C equates to the tilde version, because \ldots ]}
 In the first {\sc verify} stage, the {\sc uncertainty} 
@@
 $$
-C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}. 
+\tilde{C}(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}. 
 $$ 
@@
 $$ 
-C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}. 
+\tilde{C}(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}. 
 $$
@@
 behavior for the final (sound) solution, which presents a lower settling
-time. 
-\blue{[explain why 6b is continuous, but not 6c.]}
+time (hence the noticeable digitazion effect).
 
@@
 
-\blue{[The presence of uncertainty is not explained in this description and should be clearly elaborated and commented over the results in the Table.]}
-
-\textcolor{green}{The presence of uncertainty in some particular benchmarks ($2$, $4$, $6$, and $8$) 
+The presence of uncertainty in some particular benchmarks ($2$, $4$, $6$, and $8$) 
 leads to harder verification conditions to be checked 
-by the {\sc verify} phase, which thus influences the overall synthesis time}. 
+by the {\sc verify} phase, which thus influences the overall synthesis time.  
+\blue{[great, all good: how much uncertainty have you introduced? where precisely? in the coefficients or as an exogenous disturbance? ]}
 However, considering the faster engine for each benchmark (marked as bold in Table~\ref{tab:results}), 
@@
 footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}\\ 
-\red{[what does this alpha-numerical code mean?]}
-\textcolor{green}{CBMC (SHA-1 hash) version:} 7a6cec1dd0eb8843559591105235f1f2c4678801}
+CBMC (SHA-1 hash) version: \\ 
+7a6cec1dd0eb8843559591105235f1f2c4678801}
 

### 2017-02-14 hscc2017/paper.tex
hscc17

--- 2017-02-14 hscc2017/paper.tex
@@
 $$
+
 In the first {\sc verify} stage, the {\sc uncertainty} 

### 2017-02-14 hscc2017/paper.tex
hscc17

@@
 $$
-
+\blue{[here recall that indeed this C equates to the tilde version, because \ldots ]}
 In the first {\sc verify} stage, the {\sc uncertainty} 

### 2017-02-14 hscc2017/paper.tex
new comments

@@
 %\usetikzlibrary{decorations.pathmorphing}
+
+\newcommand{\aabatecmt}[1]{}%{{\color{red}#1}}
+\newcommand{\dariocmt}[1]{}%{{\color{blue}#1}}
 
@@
 
-\red{[Dario: please go through this section again, and clarify what sources of imprecision we consider where, distinguishing between plant and controller.
+\aabatecmt{[Dario: please go through this section again, and clarify what sources of imprecision we consider where, distinguishing between plant and controller.
 also comment on why we operate on hat G rather than on tilde G - as we discussed yesterday.
@@
 parametric uncertainties $\Delta \vec{G}$ and the FWL effects on
-the controller $\hat{C}(z)$:
+the controller $\tilde{C}(z)$:
 %
 \begin{equation}
-\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\cdot C(z)\cdot R(z)+\hat{G}(z)\cdot\nu_{2}(z)-\hat{G}(z)\cdot \hat{C}(z)\cdot \hat{Y}(z). 
+\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\tilde{C}(z)R(z)+\hat{G}(z)\nu_{2}(z)-\hat{G}(z)\tilde{C}(z)\hat{Y}(z). 
 \end{equation}
@@
 \begin{equation*}
-H_{1}(z)=\frac{1}{1+\hat{G}(z)\cdot \hat{C}(z)}, 
+H_{1}(z)=\frac{1}{1+\hat{G}(z) \tilde{C}(z)}, 
 \end{equation*}
@@
 \begin{equation*}
-H_{2}(z)=\frac{\hat{G}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}, 
+H_{2}(z)=\frac{\hat{G}(z)}{1+\hat{G}(z) \tilde{C}(z)}, 
 \end{equation*}
@@
 \begin{equation*}
-H_{3}(z)=\frac{\hat{G}(z)\cdot \hat{C}(z)}{1+\hat{G}(z)\cdot \hat{C}(z)}. 
+H_{3}(z)=\frac{\hat{G}(z) \tilde{C}(z)}{1+\hat{G}(z) \tilde{C}(z)}. 
 \end{equation*}
@@
 note that the model for quantization noise enters as a signal to be stabilized: 
-in practice, 
-if the quantization noise is bounded, 
+in practice, if the quantization noise is bounded, 
 the noise may be disregarded if the conditions on
 Proposition~\ref{prop:eq_int_stab} are satisfied.
+
+If the verification is performed using FWL arithmetic, 
+we note that the above equations must use $\tilde{G}(z)$ instead of $\hat{G}(z)$. 
+The former will provide sufficient conditions for the latter to be stabilized.
 
@@
 fractional part) can be modeled as: 
-\red{[wait I'm confused: to be precise, the next should be a tilde in view of the preceding comments on FWL!!] notice we are indeed approximating a C, so the equality comments from above do not apply!
+\aabatecmt{[wait I'm confused: to be precise, the next should be a tilde in view of the preceding comments on FWL!!] notice we are indeed approximating a C, so the equality comments from above do not apply!
 correct?}
@@
 The resulting system using the typical series loop configuration, where
-$\hat{C}(z)$ and $G(z)$ are in the forward path, is unstable. 
-\red{[hang in there - did we not consider FWL on $G(z)$? why not?]}
+$\tilde{C}(z)$ and $G(z)$ are in the forward path, is unstable. 
+\aabatecmt{[hang in there - did we not consider FWL on $G(z)$? why not?]}
+\dariocmt{we are explaining the case where a real plant (no FWL) is not correctly stabilized by $\tilde{C}$, so although our analysis might evaluate $\tilde{G}(z)$, the problem statement is over $G(z)$}
 Figure~\ref{fig:original} gives the Bode diagram for the digital controller
@@
 %
-%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
-%
-%$$
-%\begin{array}{ll}
-%N_C(z) {=} 0z^2{+}0z{+}0\\
-%D_C(z) {=} 0z^2{+}0z{+}0\\
-%\end{array}
-%$$
 $$ 
-C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}. 
+\tilde{C}(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}. 
 $$

### 2017-02-14 hscc2017/poster.tex
Cosmetic changes to poster submission
new comments

@@
 
-\begin{abstract}
 %
@@
 (sampling), quantization (A/D and D/A converters), and the use of finite-precision arithmetic.
+
+This work has been accepted at HSCC 2017 \cite{DBLP:journals/corr/AbateBCCDKK16}.
 
@@
 
-\paragraph{Our Synthesis Approach}
-We have implemented our new algorithm in a tool called \tool, and are able
-to automatically generate stable controllers for a set of intricate plant
-models taken from the literature within minutes.
-The tool uses a two stage approach. 
-As the cost of SAT solving increases with in the size of the problem
-instance, our algorithm tries to solve the problem first for small word length,
-iteratively increasing the precision if it is insufficient.
-The initial phase uses SAT-solving
-techniques in order to synthesise a candidate solution. This solution is neither sound nor universal.
-The candidate is then fed to a formal verifier, which will prove its universality for the collection of plant models (considering the tolerances).
-If the verifier finds a counterexample, it will be fed back to the synthesiser, which will use it as a guideline for future synthesis, thus slicing away candidate solutions that are not likely to be universal.
-If no counter-example is found by the verifier, it enters a second phase in which it restores soundness by evaluating the result using interval arithmetic.
-If this check fails, the loop returns to the synthesis phase, requiring higher precision in order to minimise rounding errors.
-If the check passes, we have found a sound stabilizing controller.
-%
-\end{abstract}
-
 \printccsdesc
 
-\begin{figure*}[htb]
+\begin{figure*}[h!tb]
 \centering
-
 \tikzset{add/.style n args={4}{
@@
 
-\resizebox{1.0\textwidth}{!}{
+\resizebox{0.62\textwidth}{!}{
  \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
@@
 
-\paragraph{Architecture of the Program Synthesizer}
-\label{synthesizer-general}
 %
-The input specification provided to the program synthesizer is of the form
-$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
-$\vec{P}$ ranges over functions, $\vec{x}$ ranges over ground terms and
-$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
-some finite domain $\mathcal{D}$.
-
-The design of our synthesizer is given in Figure~\ref{fig:CEGIS} and consists
-of two phases, {\sc Synthesize} and {\sc Verify}, which interact via a
-finite set of test vectors {\sc inputs} that is updated incrementally. 
-Given the aforementioned specification $\sigma$, the {\sc synth} procedure
-tries to find an existential witness $\vec{P}$ satisfying the specification
-$\sigma(\vec{x}, \vec{P})$ for all $\vec{x}$ in {\sc inputs} (as opposed to
-all $\vec{x} \in \mathcal{D}$).
-%
-If {\sc synthesize} succeeds in finding a witness~$\vec{P}$, this witness
-is a candidate solution to the full synthesis formula.  We pass this
-candidate solution to {\sc verify}, which checks whether it is a full
-solution (i.e., $\vec{P}$ satisfies the specification $\sigma(\vec{x},
-\vec{P})$ for all $\vec{x}\in\mathcal{D}$).
-%
-If this is the case, then the algorithm terminates.  Otherwise, additional
-information is provided to the {\sc synthesize} phase in the form of a new
-counterexample that is added to the {\sc inputs} set and the loop iterates
-again.
-
-%
-\begin{figure*}[htb]
+\begin{figure*}[h!tb]
 \centering
-%\resizebox{1\textwidth}{!}
+\resizebox{0.55\textwidth}{!}
 {
@@
 
+\paragraph{Our Synthesis Approach}
+We have implemented our new algorithm in a tool called \tool, and are able
+to automatically generate stable controllers for a set of intricate plant
+models taken from the literature within minutes.
+The tool uses a two stage approach. 
+As the cost of SAT solving increases with in the size of the problem
+instance, our algorithm tries to solve the problem first for small word length,
+iteratively increasing the precision if it is insufficient.
+The initial phase uses SAT-solving
+techniques in order to synthesise a candidate solution. This solution is neither sound nor universal.
+The candidate is then fed to a formal verifier, which will prove its universality for the collection of plant models (considering the tolerances).
+If the verifier finds a counterexample, it will be fed back to the synthesiser, which will use it as a guideline for future synthesis, thus slicing away candidate solutions that are not likely to be universal.
+If no counter-example is found by the verifier, it enters a second phase in which it restores soundness by evaluating the result using interval arithmetic.
+If this check fails, the loop returns to the synthesis phase, requiring higher precision in order to minimise rounding errors.
+If the check passes, we have found a sound stabilizing controller.
+%
+
+%\paragraph{Architecture of the Program Synthesizer}
+%\label{synthesizer-general}
+%%
+%The input specification provided to the program synthesizer is of the form
+%$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
+%$\vec{P}$ ranges over functions, $\vec{x}$ ranges over ground terms and
+%$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
+%some finite domain $\mathcal{D}$.
+%
+%The design of our synthesizer is given in Figure~\ref{fig:CEGIS} and consists
+%of two phases, {\sc Synthesize} and {\sc Verify}, which interact via a
+%finite set of test vectors {\sc inputs} that is updated incrementally. 
+%Given the aforementioned specification $\sigma$, the {\sc synth} procedure
+%tries to find an existential witness $\vec{P}$ satisfying the specification
+%$\sigma(\vec{x}, \vec{P})$ for all $\vec{x}$ in {\sc inputs} (as opposed to
+%all $\vec{x} \in \mathcal{D}$).
+%%
+%If {\sc synthesize} succeeds in finding a witness~$\vec{P}$, this witness
+%is a candidate solution to the full synthesis formula.  We pass this
+%candidate solution to {\sc verify}, which checks whether it is a full
+%solution (i.e., $\vec{P}$ satisfies the specification $\sigma(\vec{x},
+%\vec{P})$ for all $\vec{x}\in\mathcal{D}$).
+%%
+%If this is the case, then the algorithm terminates.  Otherwise, additional
+%information is provided to the {\sc synthesize} phase in the form of a new
+%counterexample that is added to the {\sc inputs} set and the loop iterates
+%again.
+
+\paragraph{Case Study} \label{sec:running-ex}
+
+We illustrate our approach with a classical cruise control example,
+extracted from the literature~\cite{Astrom08}.  The example highlights the
+challenges that arise when using finite-precision arithmetic in digital
+control.  Given a discrete plant model:
+%
+\begin{equation}
+\label{Eq:running-example-plant}
+\resizebox{.15\textwidth}{!}{
+$G(z) = \frac{0.0264}{z-0.9998}$.
+}
+\end{equation}
+
+classic techniques produce a stabilizing controller:
+%
+\begin{equation}
+\label{Eq:running-example-controller}
+\resizebox{.25\textwidth}{!}{
+$C(z) = \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}$.
+}
+\end{equation}
+%
+However, given an implementation of this controller using 20bit fixed-point arithmetic 
+($I=4$,$F=16$) the coefficients change, giving us:
+%
+\begin{equation}
+\label{Eq:running-example-controller-quantized}
+\resizebox{.47\textwidth}{!}{
+$\tilde{C}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
+{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$. 
+}
+\end{equation} 
+%
+The resulting system using the typical series loop configuration, where
+$\tilde{C}(z)$ and $G(z)$ are in the forward path, is unstable.
+
+We now demonstrate how our approach solves the synthesis problem for this
+example.  We start with an a priori candidate solution
+with all coefficients zero, and a precision for the verifier of 40bits ($I_p=16$,$F_p=24$).
+In the first {\sc verify} stage, the {\sc uncertainty} 
+check finds the following counterexample:
+%
+$$ 
+\resizebox{.2\textwidth}{!}{
+$\tilde G(z) = \frac{0.026506}{1.000610z+1.002838}$. 
+}
+$$
+We add this counterexample to {\sc inputs} and initiate the {\sc synthesize}
+phase, where we obtain the following candidate solution:
+%
+$$
+\resizebox{.3\textwidth}{!}{
+$\tilde{C}(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}.$
+}
+$$ 
+This time, the {\sc uncertainty} check does not find any
+counterexample and we pass the current candidate solution to the {\sc
+precision} verification stage.
+
+We obtain the result $\mathit{false}$, meaning that the current precision is
+insufficient.  Consequently, we increase our precision to 48bits ($I_p=20$,$F_p=28$).
+%
+Since the previous counterexamples were obtained at lower precision, we
+remove them from the set of counterexamples.  Back in the {\sc synthesize}
+phase, we re-start the process with a candidate solution with all
+coefficients $0$, as above.  Next, the {\sc uncertainty} verification stage provides
+the first counterexample at higher precision:
+$$ 
+\resizebox{.2\textwidth}{!}{
+$\tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785}$. 
+}$$
+In the {\sc synthesize} phase, we get a new candidate solution that
+eliminates the new, higher precision counterexample:
+%
+$$ 
+\resizebox{.3\textwidth}{!}{
+$\tilde{C}(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}$. 
+}$$
+
+This candidate solution is validated  as the final solution by both stages
+{\sc uncertainty} and {\sc precision} in the {\sc verify} phase.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 engineers.  We further observe that the approach is able to synthesize stable controllers
-in $20$ out of the $23$ benchmarks.  For the remaining benchmarks
-our approach failed to synthesize a stable controller within the time
-limits.  This can be addressed by either increasing either the time limit
-or the fixed-point word widths considered, or by using floating-point
-arithmetic instead.  The synthesized controllers were confirmed to be stable
+in $20$ out of the $23$ benchmarks.  The synthesized controllers were confirmed to be stable
 outside of our model representation using MATLAB.
@@
 \bibliographystyle{abbrv}
-\bibliography{paper}
+\bibliography{poster}
 

### 2017-02-14 hscc2017/paper.tex
More comments There is a switch on alessandros and my comments to remove them

@@
 
-\newcommand{\aabatecmt}[1]{}%{{\color{red}#1}}
-\newcommand{\dariocmt}[1]{}%{{\color{blue}#1}}
+\newcommand{\aabatecmt}[1]{{\color{red}#1}}
+\newcommand{\dariocmt}[1]{{\color{blue}#1}}
 
@@
 ]}
-
+\dariocmt{I added a paragraph at the end of the section that should clarify.}
 Sound synthesis of the digital controller requires the consideration of the effect of FWL on the controller, 
@@
 correct?}
+\dariocmt{yes, I changed all C(z) below for tildes}
 %
@@
 Assuming a precision of $I_p=16$, $F_p=24$,  
-\blue{[so you mean we're not using Jury's criterion? pllease clarify.] the digital controller is designed with standard techniques for
-control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}. 
+\aabatecmt{[so you mean we're not using Jury's criterion? pllease clarify.] 
+%the digital controller is designed with standard techniques for 
+%control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}. 
 }
-We start with an a-priori candidate solution with all coefficients zero: 
+\dariocmt{I'm just removing this. Not even sure what it means}
+we start with an a-priori candidate solution with all coefficients zero (note that the controller is in the FWL domain, hence we use $\tilde{C}(z)$): 
 %
@@
 $$
-\blue{[here recall that indeed this C equates to the tilde version, because \ldots ]}
+\aabatecmt{[here recall that indeed this C equates to the tilde version, because \ldots ]}
+\dariocmt{addressed above}
 In the first {\sc verify} stage, the {\sc uncertainty} 

### 2017-02-14 hscc2017/paper.tex
nudge

@@
 there has been plenty of previous work aiming at \emph{verifying} a given
-designed controller, which however broadly lack automation.  
-Recent work has studied the stability of digital controllers with consideration of their implementation aspects, i.e.,
-fixed-point arithmetic and the word length used: 
-\cite{Bessa16} exploit advances in bit-accurate verification of C
-programs to obtain a verifier for software-implemented digital control.
-
-By contrast, we leverage a very recent step-change in the automation and scalability of 
-\emph{program synthesis}.  Program synthesis engines use a program
+designed controller, which however broadly lack automation.  Recent work has
+studied the stability of digital controllers considering implementation
+aspects, i.e., fixed-point arithmetic and the word length~\cite{Bessa16}. 
+They exploit advances in bit-accurate verification of C programs to obtain a
+verifier for software-implemented digital control.
+
+By contrast, we leverage a very recent step-change in the automation and
+scalability of \emph{program synthesis}.  Program synthesis engines use a
 specification as the starting point, and subsequently generate a sequence of
-candidate programs from a given template.  
-The candidate programs are iteratively refined to eventually match the desired program specification.   
-Program synthesizers implementing the 
-Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture are now
-able to generate programs for highly non-trivial specifications with a very 
-high degree of automation.  Modern synthesis engines combine automated testing, 
-genetic algorithms, 
-and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a,DBLP:conf/lpar/DavidKL15}.
+candidate programs from a given template.  The candidate programs are
+iteratively refined to eventually satisfy the specification.  Program
+synthesizers implementing Counter-Example Guided Inductive Synthesis
+(CEGIS)~\cite{sketch} are now able to generate programs for highly
+non-trivial specifications with a very high degree of automation.  Modern
+synthesis engines combine automated testing, genetic algorithms, and
+SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a,
+DBLP:conf/lpar/DavidKL15}.
 
@@
 % elements with quantization noise.  
-We further account for uncertainties on the plant models. 
-The resulting closed-loop system is a program loop that operates on bit-vectors encoded using
-fixed-point arithmetic with finite word length (FWL).  
-The three effects of 1. uncertaities, 2. FWL representation, and 3. quantization errors are incorporated into the model, 
+%
+We further account for uncertainties on the plant models.  The resulting
+closed-loop system is a program loop that operates on bit-vectors encoded
+using fixed-point arithmetic with finite word length (FWL).  The three
+effects of 1.~uncertaities, 2.~FWL representation and 3.~quantization
+errors are incorporated into the model,
+%
 %as an additive uncertainty, 

### 2017-02-14 hscc2017/paper.tex
comma
plant unc comment

@@
 margins and controller fragility~\cite{bhattacharyya97, keel_Bhattacharyya_examples}.
+
+\textcolor{green}{
+Additional benchmarks were created for the \textit{Cruise Control System}, \textit{Springer-mass damper}, and \textit{Satellite} considering parametric additive in the nominal plant model (represented by $\Delta_{p}\vec{G}$ in Eq.~\eqref{digital_plant_tf}).
+These uncertain models are respectively represented by $G_{1b}(z)$, $G_{2b}(z)$, $G_{3b}(z)$, and $G_{3d}(z)$.
+}
 
@@
 by the {\sc verify} phase, which thus influences the overall synthesis time.  
-\blue{[great, all good: how much uncertainty have you introduced? where precisely? in the coefficients or as an exogenous disturbance? ]}
+\blue{[great, all good: how much uncertainty have you introduced?
+where precisely?
+in the coefficients or as an exogenous disturbance?
+\textcolor{green}{It is addressed in Sec \ref{experimental-setup}}]}
 However, considering the faster engine for each benchmark (marked as bold in Table~\ref{tab:results}), 

### 2017-02-14 hscc2017/paper.tex
minor change
hscc17

--- 2017-02-14 hscc2017/paper.tex
@@
 fractional part) can be modeled as: 
-\aabatecmt{[wait I'm confused: to be precise, the next should be a tilde in view of the preceding comments on FWL!!] notice we are indeed approximating a C, so the equality comments from above do not apply!
-correct?}
-\dariocmt{yes, I changed all C(z) below for tildes}
 %
@@
 Assuming a precision of $I_p=16$, $F_p=24$,  
-\aabatecmt{[so you mean we're not using Jury's criterion? pllease clarify.] 
-%the digital controller is designed with standard techniques for 
-%control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}. 
-}
-\dariocmt{I'm just removing this. Not even sure what it means}
 we start with an a-priori candidate solution with all coefficients zero (note that the controller is in the FWL domain, hence we use $\tilde{C}(z)$): 
@@
 $$
-\aabatecmt{[here recall that indeed this C equates to the tilde version, because \ldots ]}
-\dariocmt{addressed above}
 In the first {\sc verify} stage, the {\sc uncertainty} 
@@
 behavior for the final (sound) solution, which presents a lower settling
-time (hence the noticeable digitazion effect).
+time (hence the noticeable digitazion effects).
 
@@
 margins and controller fragility~\cite{bhattacharyya97, keel_Bhattacharyya_examples}.
+
+Additional benchmarks were created for the \textit{Cruise Control System}, \textit{Springer-mass damper}, and \textit{Satellite} considering parametric additive in the nominal plant model  (represented by $\Delta_{p}\vec{G}$ in Eq.~\eqref{digital_plant_tf}).
+The uncertainties are deviations bounded to a maximum magnitude of $0.5$ in each coefficient.
+These uncertain models are respectively represented by $G_{1b}(z)$, $G_{2b}(z)$, $G_{3b}(z)$, and $G_{3d}(z)$.
 
@@
 by the {\sc verify} phase, which thus influences the overall synthesis time.   
-\blue{[great, all good: how much uncertainty have you introduced? where precisely? in the coefficients or as an exogenous disturbance? ]}
 However, considering the faster engine for each benchmark (marked as bold in Table~\ref{tab:results}), 
@@
 effects of discretizing the dynamics, including delayed
-response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics with
-the goal to either verify~\cite{daes20161} or to optimize~\cite{oudjida2014design} 
+response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics \cite{Anta:2010:AVC:1879021.1879024} 
+with the goal to either verify~\cite{daes20161} or to optimize~\cite{oudjida2014design} 
 given implementations.

### 2017-02-15 hscc2017/paper.tex
comma

@@
 %------------------------------------
-\subsection{Model Imprecision, Finite Word Length Representation, and Quantization Effects}
+\subsection{Model Imprecision, Finite Word Length Representation and Quantization Effects}
 \label{verifying-closed-loop-control-systems}
@@
     \end{subfigure}
-    \caption{Bode diagram for original controller in~\cite{DBLP:conf/hybrid/WangGRJF16}, 
+    \caption{Bode diagram for original controller in~\cite{DBLP:conf/hybrid/WangGRJF16} 
     and for newly synthesized closed-loop system}\label{fig:bode}

### 2017-02-15 hscc2017/paper.tex
line breaks

@@
 
-Modern implementations of embedded control systems have proliferated with the
-availability of low-cost devices that can perform highly non-trivial control
-tasks, with significant impact in numerous application areas such as
+Modern implementations of embedded control systems have proliferated with
+the availability of low-cost devices that can perform highly non-trivial
+control tasks, with significant impact in numerous application areas such as
 environmental control and robotics~\cite{astrom1997computer, Franklin15}. 
@@
 introduced by A/D and D/A conversion.  Thus, programming expertise is a key
-barrier to broad adoption of correct digital controllers, and requires considerable
-knowledge often unusual to the control engineer.
+barrier to broad adoption of correct digital controllers, and requires
+considerable knowledge often unusual to the control engineer.
 
@@
 By combining and applying state-of-the-art synthesis engines we present a
-tool that automatically generates digital controllers for a given 
-continuous plant model that are correct by construction.  
-This approach presents a high degree of autonomy, 
-promises to reduce the cost and time of development of digital control dramatically, 
-and requires considerably less expertise than a-posteriori verification methodologies.   
-Specifically, we synthesize stable,  
-%controllers for hybrid closed-loop systems, i.e., 
-software-implemented embedded controllers along with a model of a physical plant. 
-%, that are \emph{stable}.  
-Due to the complexity of such closed-loop systems, in this work we focus
-on linear models with known configurations, and perform parametric synthesis
-of stabilizing digital controllers (further closed-loop requirements are left to future work).
+tool that automatically generates digital controllers for a given continuous
+plant model that are correct by construction.  This approach presents a high
+degree of autonomy, promises to reduce the cost and time of development of
+digital control dramatically, and requires considerably less expertise than
+a-posteriori verification methodologies.  Specifically, we synthesize
+stable, software-implemented embedded controllers along with a model of a
+physical plant.  Due to the complexity of such closed-loop systems, in this
+work we focus on linear models with known configurations, and perform
+parametric synthesis of stabilizing digital controllers (further closed-loop
+requirements are left to future work).
 
@@
 approach~\cite{astrom1997computer}, we translate the problem into a single
-digital domain.  
-Towards our goal of closed-loop stability, 
-% despite digitization effects, 
-we have modeled a digital equivalent of the continuous plant by evaluating the effects of the quantizers (A/D and D/A converters) and of time
-discretization. 
-% elements with quantization noise.  
-%
-We further account for uncertainties on the plant models.  The resulting
+digital domain.  Towards our goal of closed-loop stability, we have modeled
+a digital equivalent of the continuous plant by evaluating the effects of
+the quantizers (A/D and D/A converters) and of time discretization.  We
+further account for uncertainties on the plant models.  The resulting
 closed-loop system is a program loop that operates on bit-vectors encoded
 using fixed-point arithmetic with finite word length (FWL).  The three
-effects of 1.~uncertaities, 2.~FWL representation and 3.~quantization
-errors are incorporated into the model,
-%
-%as an additive uncertainty, 
-and are taken into account during the CEGIS-based synthesis of the control software for the plant.
+effects of 1.~uncertaities, 2.~FWL representation and 3.~quantization errors
+are incorporated into the model, and are taken into account during the
+CEGIS-based synthesis of the control software for the plant.
 
@@
   stable controllers for a set of intricate benchmarks taken from the
-  literature: the median runtime for our benchmark set considering the faster 
-	engine is $48$\,s, i.e., half of the controllers can be synthesized in less than one minute.
+  literature: the median runtime for our benchmark set considering the
+  faster engine is $48$\,s, i.e., half of the controllers can be synthesized
+  in less than one minute.
 
@@
 }
- \caption{Closed-loop digital control system (cf. Section \ref{verifying-closed-loop-control-systems} for notations) \label{fig:sampledsystem}}
+ \caption{Closed-loop digital control system (cf.~Section \ref{verifying-closed-loop-control-systems} for notation) \label{fig:sampledsystem}}
 \end{figure*}

### 2017-02-15 hscc2017/paper.tex
wording

@@
 barrier to broad adoption of correct digital controllers, and requires
-considerable knowledge often unusual to the control engineer.
-
-Beyond classical a-posteriori validation procedures in digital control,
-there has been plenty of previous work aiming at \emph{verifying} a given
-designed controller, which however broadly lack automation.  Recent work has
-studied the stability of digital controllers considering implementation
-aspects, i.e., fixed-point arithmetic and the word length~\cite{Bessa16}. 
-They exploit advances in bit-accurate verification of C programs to obtain a
+considerable knowledge outside of the expertise of many control engineers.
+
+Beyond classical a-posteriori validation in digital control, there has been
+plenty of previous work aiming at \emph{verifying} a given designed
+controller, which however broadly lack automation.  Recent work has studied
+the stability of digital controllers considering implementation aspects,
+i.e., fixed-point arithmetic and the word length~\cite{Bessa16}.  They
+exploit advances in bit-accurate verification of C programs to obtain a
 verifier for software-implemented digital control.

### 2017-02-15 hscc2017/paper.tex
wording

@@
 tool that automatically generates digital controllers for a given continuous
-plant model that are correct by construction.  This approach presents a high
-degree of autonomy, promises to reduce the cost and time of development of
+plant model that are correct by construction.  This approach delivers a high
+degree of automation, promises to reduce the cost and time of development of
 digital control dramatically, and requires considerably less expertise than
-a-posteriori verification methodologies.  Specifically, we synthesize
-stable, software-implemented embedded controllers along with a model of a
-physical plant.  Due to the complexity of such closed-loop systems, in this
-work we focus on linear models with known configurations, and perform
-parametric synthesis of stabilizing digital controllers (further closed-loop
+a-posteriori verification.  Specifically, we synthesize stable,
+software-implemented embedded controllers along with a model of a physical
+plant.  Due to the complexity of such closed-loop systems, in this work we
+focus on linear models with known configurations, and perform parametric
+synthesis of stabilizing digital controllers (further closed-loop
 requirements are left to future work).
@@
 approach~\cite{astrom1997computer}, we translate the problem into a single
-digital domain.  Towards our goal of closed-loop stability, we have modeled
-a digital equivalent of the continuous plant by evaluating the effects of
-the quantizers (A/D and D/A converters) and of time discretization.  We
-further account for uncertainties on the plant models.  The resulting
-closed-loop system is a program loop that operates on bit-vectors encoded
-using fixed-point arithmetic with finite word length (FWL).  The three
-effects of 1.~uncertaities, 2.~FWL representation and 3.~quantization errors
-are incorporated into the model, and are taken into account during the
-CEGIS-based synthesis of the control software for the plant.
+digital domain, i.e., we model a digital equivalent of the continuous plant
+by evaluating the effects of the quantizers (A/D and D/A converters) and of
+time discretization.  We further account for uncertainties in the plant
+model.  The resulting closed-loop system is a program with a loop that
+operates on bit-vectors encoded using fixed-point arithmetic with finite
+word length (FWL).  The three effects of 1.~uncertaities, 2.~FWL
+representation and 3.~quantization errors are incorporated into the model,
+and are taken into account during the CEGIS-based synthesis of the control
+software for the plant.
 
@@
 $\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\cdot}\right\rbrace_{t=kT}}\right\rbrace$
-operations, and it includes the ZOH dynamics in the $(1-z^{-1})$ term. 
-This is sufficient for stability studies over $G(s)$~\cite{fadali}, {\it i.e.}, if there is any unstable pole (in the complex domain $\Re\{s\} > 0$), 
-the pulse transfer function in~\eqref{eq:pulsetf} will also present the same number of unstable poles ($|z| > 1$)~\cite{Franklin15}.
+operations, and it includes the ZOH dynamics in the $(1-z^{-1})$ term.  This
+is sufficient for stability studies over $G(s)$~\cite{fadali}, i.e., if
+there is any unstable pole (in the complex domain $\Re\{s\} > 0$), the pulse
+transfer function in~\eqref{eq:pulsetf} will also present the same number of
+unstable poles ($|z| > 1$)~\cite{Franklin15}.
 

### 2017-02-15 hscc2017/paper.tex
wording

@@
 
-Uncertainties in $G(z)$ may appear due to: 
-1.
-uncertainties in $G(s)$ (we denote the uncertain continuous plant by $\hat{G}(s)=\frac{G_n(s)+\Delta_p{G}_n(s)}{G_d(s)+\Delta_p{G}_d(s)}$ to explicitly encompass the effects of the uncertainty terms $\Delta_p{G}_{(\cdot)}(s)$) arising from tolerances/imprecision in the original model;
-2. errors in the numerical calculations due to FWL effects (e.g., coefficient truncation and round-off, which will be denoted as $\Delta_b{G}_n(s),\Delta_b{G}_d(s)$);    
-and 
-3. errors caused by quantization (which we model later as as external disturbances $\nu_1$ and $\nu_2$). 
-These uncertainties are parametrically expressed by additive terms, eventually resulting in an uncertain model $\hat{G}(z)$, such that:
+Uncertainties in $G(z)$ may appear owing to: 1.~uncertainties in $G(s)$ (we
+denote the uncertain continuous plant by
+$\hat{G}(s)=\frac{G_n(s)+\Delta_p{G}_n(s)}{G_d(s)+\Delta_p{G}_d(s)}$ to
+explicitly encompass the effects of the uncertainty terms
+$\Delta_p{G}_{(\cdot)}(s)$) arising from tolerances/imprecision in the
+original model; 2.~errors in the numerical calculations due to FWL effects
+(e.g., coefficient truncation and round-off, which will be denoted as
+$\Delta_b{G}_n(s),\Delta_b{G}_d(s)$); and 3.~errors caused by quantization
+(which we model later as as external disturbances $\nu_1$ and $\nu_2$). 
+These uncertainties are parametrically expressed by additive terms,
+eventually resulting in an uncertain model $\hat{G}(z)$, such that:
 %
@@
 %
-%\red{[why is this condition on the order of the polynomials raised only now? how is it used later?]}
-Notice that, due to the nature of the methods we use for the stability check, we require
-that the parametric errors in the plant have the same polynomial order as
-the plant itself (indeed, all other errors described in this paper are ensured to
-fulfil this property in our implementation). 
-We also remark that, due to its native digital implementation, 
-there are no parametric errors ($\Delta_pC_n(z), \Delta_pC_d(z)$) entering in the controller. 
-Thus $\hat{C}(z) \equiv C(z)$.
+%\red{[why is this condition on the order of the polynomials raised only
+now?  how is it used later?]} Notice that, due to the nature of the methods
+we use for the stability check, we require that the parametric errors in the
+plant have the same polynomial order as the plant itself (indeed, all other
+errors described in this paper fulfil this property).  We
+also remark that, due to its native digital implementation, there are no
+parametric errors ($\Delta_pC_n(z), \Delta_pC_d(z)$) entering in the
+controller.  Thus $\hat{C}(z) \equiv C(z)$.
 

### 2017-02-15 hscc2017/paper.tex
wording

@@
 %
-%\red{[why is this condition on the order of the polynomials raised only
-now?  how is it used later?]} Notice that, due to the nature of the methods
-we use for the stability check, we require that the parametric errors in the
-plant have the same polynomial order as the plant itself (indeed, all other
-errors described in this paper fulfil this property).  We
-also remark that, due to its native digital implementation, there are no
-parametric errors ($\Delta_pC_n(z), \Delta_pC_d(z)$) entering in the
-controller.  Thus $\hat{C}(z) \equiv C(z)$.
+Notice that, due to the nature of the methods we use for the stability
+check, we require that the parametric errors in the plant have the same
+polynomial order as the plant itself (indeed, all other errors described in
+this paper fulfil this property).  We~also remark that, due to its native
+digital implementation, there are no parametric errors ($\Delta_pC_n(z),
+\Delta_pC_d(z)$) in the controller.  Thus $\hat{C}(z) \equiv C(z)$.
 

### 2017-02-15 hscc2017/paper.tex
wording

@@
 
-We introduce next a notation based on the polynomials coefficients to simplify 
-the presentation.  Let $\mathcal{P}^{N}$ be the space of polynomials of order $N$. 
-Let $P \in \mathcal{P}^{M,N}$ be a rational polynomial 
-$\frac{P_n}{P_d}$, where $P_n \in \mathcal{P}^{M}$ and $P_d \in \mathcal{P}^{N}$.  
-For a vector of coefficients
+We introduce next a notation based on the coefficients of the polynomial to
+simplify the presentation.  Let $\mathcal{P}^{N}$ be the space of
+polynomials of order $N$.  Let $P \in \mathcal{P}^{M,N}$ be a rational
+polynomial $\frac{P_n}{P_d}$, where $P_n \in \mathcal{P}^{M}$ and $P_d \in
+\mathcal{P}^{N}$.  For a vector of coefficients
 %
@@
 the effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is
-seen as additive noise.
+additive noise.
 
@@
 In Figure~\ref{fig:digsystem1}, two sources of uncertainty are illustrated:
-parametric uncertainties related to modeling errors  
-(which are represented by~$\Delta_p \vec{G}$),  
-and uncertainties introduced by quantizations in the ADC and
-DAC conversions ($\nu_1$ and $\nu_2$) which are assumed to be non-deterministic. 
-Recall that we discussed how the quantization noise is encompassed as an additive term, 
-which means it does not enter parametrically in the transfer function. 
-Instead, we later show that the system is stable given these non-deterministic disturbance inputs.
+parametric uncertainties model the errors (which are represented
+by~$\Delta_p \vec{G}$), and uncertainties for the quantizations in the ADC
+and DAC conversions ($\nu_1$ and $\nu_2$), which are assumed to be
+non-deterministic.  Recall that we discussed how the quantization noise is
+an additive term, which means it does not enter parametrically in the
+transfer function.  Instead, we later show that the system is stable given
+these non-deterministic disturbance.
 
@@
 z-domain using equation \eqref{eq:hatgvector} as
-$\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}$.
-The parametric uncertainties in the plant are assumed to have the same
-order as the plant model, since 
-errors of higher order can move the closed-loop poles by large amounts, 
-thus preventing any given controller from stabilizing such a setup. 
-This is a reasonable assumption since most tolerances do not change the 
-architecture of the plant.
+$\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}$.  The parametric uncertainties in
+the plant are assumed to have the same order as the plant model, since
+errors of higher order can move the closed-loop poles by large amounts, thus
+preventing any given controller from stabilizing such a setup.  This is a
+reasonable assumption since most tolerances do not change the architecture
+of the plant.
 
@@
 
-Since the controller is implemented using finite representation, $C(z)$ also suffers
-disturbances from the FWL effects, with roundoffs in coefficients that may
-change closed-loop poles and zeros position, and consequently affect its
-stability, as argued in~\cite{Bessa16}.
+Since the controller is implemented using finite representation, $C(z)$ also
+suffers disturbances from the FWL effects, with roundoffs in coefficients
+that may change closed-loop poles and zeros position, and consequently
+affect its stability, as argued in~\cite{Bessa16}.
 
@@
 \end{align}
+%
 where $\mathcal{P}^{n}$ is the space of polynomials of $n$-th order,
-$\mathcal{P}^{n}\param{I}{F}$ is the space of polynomials with coefficients in $\mathbb{R}\param{I}{F}$, 
-and (as a special case) $\mathcal{F}_0\param{I}{F}(x)$ returns the element $\tilde{x} \in \mathbb{R}\param{I}{F}$ that is closest to the real parameter $x$.
+$\mathcal{P}^{n}\param{I}{F}$ is the space of polynomials with coefficients
+in $\mathbb{R}\param{I}{F}$, and (as a special case)
+$\mathcal{F}_0\param{I}{F}(x)$ returns the element $\tilde{x} \in
+\mathbb{R}\param{I}{F}$ that is closest to the real parameter $x$.
 
@@
 %
-In the case of a digitally synthesized controller (as it is the case in this work), 
-because the synthesis is performed directly using FWL representation, 
-$\tilde{C}(z) \equiv \hat{C}(z) \equiv C(z)$ 
-(in other words, 
-we synthesise a controller that is already in the domain $\mathbb{R} \param{I}{F}$ and has therefore no uncertainties entering because of FWL representations, 
-that is $\Delta_bC_n(z)=\Delta_bC_d(z)=0$).
+In the case of a digitally synthesized controller (as it is the case in this
+work), $\tilde{C}(z) \equiv \hat{C}(z) \equiv C(z)$ because the synthesis is
+performed directly using FWL representation.  In other words, we synthesise
+a controller that is already in the domain $\mathbb{R} \param{I}{F}$ and has
+therefore no uncertainties entering because of FWL representations, that is,
+$\Delta_bC_n(z)=\Delta_bC_d(z)=0$.
 
@@
 where $I$ and $F$, as well as $I_p$ and $F_p$, denote the number of bits for
-the integer and fractional parts, respectively, and where it is practically motivated to consider $\mathbb{R}\param{
-I_p}{F_p} \supseteq \mathbb{R}\param{I}{F}$.
+the integer and fractional parts, respectively, and where it is practically
+motivated to consider $\mathbb{R}\param{ I_p}{F_p} \supseteq
+\mathbb{R}\param{I}{F}$.
 

### 2017-02-15 hscc2017/paper.tex
wording

@@
 %
-where $\Delta_bc_i=\tilde{c}_i-\hat{c}_i$, 
-and $\Delta_b{G}$ represents the plant uncertainty caused by
-the rounding off effect.  We encompass the global uncertainty as
-$\Delta{\vec{G}}=\Delta_p{\vec{G}}+\Delta_b{\vec{G}}$.
+where $\Delta_bc_i=\tilde{c}_i-\hat{c}_i$, and $\Delta_b{G}$ represents the
+plant uncertainty caused by the rounding off effect.  We capture the global
+uncertainty as $\Delta{\vec{G}}=\Delta_p{\vec{G}}+\Delta_b{\vec{G}}$.
 
 %------------------------------------
-\subsection{Closed-Loop Stability Verification under Parametric Uncertainties FWL Representation, and Quantisation Noise}
+\subsection{Closed-Loop Stability Verification under Parametric
+Uncertainties, FWL Representation and Quantisation Noise}
 \label{sec:stability}
@@
 \dariocmt{I added a paragraph at the end of the section that should clarify.}
-Sound synthesis of the digital controller requires the consideration of the effect of FWL on the controller, 
-and of quantization disturbances in the closed-loop system.  
-Let the quantizer $Q1$ (ADC) be the source of a white noise $\nu_{1}$, 
-and $Q2$ (DAC) be the source of a white noise $\nu_{2}$.  The following equation
-models the system in Figure~\ref{fig:sampledsystem}, encompassing the
-parametric uncertainties $\Delta \vec{G}$ and the FWL effects on
-the controller $\tilde{C}(z)$:
+%
+Sound synthesis of the digital controller requires the consideration of the
+effect of FWL on the controller, and of quantization disturbances in the
+closed-loop system.  Let the quantizer $Q1$ (ADC) be the source of a white
+noise $\nu_{1}$, and $Q2$ (DAC) be the source of a white noise~$\nu_{2}$. 
+The following equation models the system in Figure~\ref{fig:sampledsystem},
+including the parametric uncertainties $\Delta \vec{G}$ and the FWL
+effects on the controller $\tilde{C}(z)$:
 %
@@
 
-A discrete-time dynamical system is said to be Bounded-Input and Bounded-Output
-(BIBO) stable if bounded inputs necessarily result in bounded outputs. 
-This condition holds true over an LTI model if and only if every pole of its transfer function lies inside the unit circle \cite{Astrom08}.  
-Analyzing Eq.~\eqref{eq:outputfunctions}, 
-the following proposition provides conditions for the BIBO stability of the system in Figure~\ref{fig:sampledsystem}, 
-with regards to the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$, which are all bounded 
-(in particular, the bound on the quantization noise is given by
-Assumption~\ref{whitenoise}). 
+A discrete-time dynamical system is said to be Bounded-Input and
+Bounded-Output (BIBO) stable if bounded inputs necessarily result in bounded
+outputs.  This condition holds true over an LTI model if and only if every
+pole of its transfer function lies inside the unit circle \cite{Astrom08}. 
+Analyzing Eq.~\eqref{eq:outputfunctions}, the following proposition provides
+conditions for the BIBO stability of the system in
+Figure~\ref{fig:sampledsystem}, with regards to the exogenous signals
+$R(z)$, $\nu_{1}$, and $\nu_{2}$, which are all bounded (in particular, the
+bound on the quantization noise is given by Assumption~\ref{whitenoise}).
 %
@@
 Figure~\ref{fig:sampledsystem} with a FWL implementation of the digital
-controller $\tilde{C}(z) =\mathcal{F}_{M_C,N_C}\param {I}{F}(C(z))$ and uncertain discrete
-model of the plant from~\eqref{eq:coefficients},\eqref{eq:delta_coefficients} 
+controller $\tilde{C}(z) =\mathcal{F}_{M_C,N_C}\param {I}{F}(C(z))$ and
+uncertain discrete model of the plant
+from~\eqref{eq:coefficients}, \eqref{eq:delta_coefficients}
 %
@@
 
-Proposition~\ref{prop:eq_int_stab} provides necessary (and sufficient) conditions for the
-controller to stabilize the closed-loop system, considering plant
-parametric uncertainties (i.e., $\Delta_p \vec{G}$), quantization noises
-($\nu_{1}$ and $\nu_{2}$) and FWL effects in the control software.  
-In particular, 
-note that the model for quantization noise enters as a signal to be stabilized: 
-in practice, if the quantization noise is bounded, 
-the noise may be disregarded if the conditions on
+Proposition~\ref{prop:eq_int_stab} provides necessary (and sufficient)
+conditions for the controller to stabilize the closed-loop system,
+considering plant parametric uncertainties (i.e., $\Delta_p \vec{G}$),
+quantization noises ($\nu_{1}$ and $\nu_{2}$) and FWL effects in the control
+software.  In particular, note that the model for quantization noise enters
+as a signal to be stabilized: in practice, if the quantization noise is
+bounded, the noise may be disregarded if the conditions on
 Proposition~\ref{prop:eq_int_stab} are satisfied.
 
-If the verification is performed using FWL arithmetic, 
-we note that the above equations must use $\tilde{G}(z)$ instead of $\hat{G}(z)$. 
-The former will provide sufficient conditions for the latter to be stabilized.
+If the verification is performed using FWL arithmetic,  the above equations
+must use $\tilde{G}(z)$ instead of $\hat{G}(z)$.  The former will provide
+sufficient conditions for the latter to be stabilized.
 

### 2017-02-15 hscc2017/paper.tex
wording

@@
 
-Among the discretization methods in the literature~\cite{Franklin15}, 
-we consider the sample-and-hold processes in complex systems~\cite{istepanian2012digital}.  
-On the other hand, 
-the ZOH discretization models the exact effect of sampling and DAC interpolation over the plant.
+Among the discretization methods in the literature~\cite{Franklin15}, we
+consider the sample-and-hold processes in complex
+systems~\cite{istepanian2012digital}.  On the other hand, the ZOH
+discretization models the exact effect of sampling and DAC interpolation
+over the plant.
 
@@
 
-Given a plant model in ANSI-C syntax as input (Steps 1--3), \tool
-constructs a non-deterministic model to represent the plant family,
-i.e., it addresses plant variations as interval sets (Step~A),
-and formulates a function (Step~B) using implementation details provided in
-Steps~$2$ and $3$ to calculate the controller parameters to be
-synthesized (Step~C).  Note that \tool synthesizes the controller 
-coefficients for the given implementation aspects, i.e., numerical
-representation and realization form.  Finally, \tool builds an intermediate 
-ANSI-C code for the digital system implementation, which is used as input 
-for the CEGIS engine (Step~D).
+Given a plant model in ANSI-C syntax as input (Steps 1--3), \tool constructs
+a non-deterministic model to represent the plant family, i.e., it addresses
+plant variations as interval sets (Step~A), and formulates a function
+(Step~B) using implementation details provided in Steps~$2$ and $3$ to
+calculate the controller parameters to be synthesized (Step~C).  Note that
+\tool synthesizes the controller for the desired numerical representation
+and realization form.  Finally, \tool builds an intermediate ANSI-C code for
+the digital system implementation, which is used as input for the CEGIS
+engine (Step~D).
 
@@
 counterexample that is added to the {\sc inputs} set and the loop iterates
-again (note that, for now, we ignore the second feedback signal ``Increase
-Precision'' provided by the {\sc Verify} phase in Figure~\ref{fig:CEGIS} as it
-is specific to control synthesis and will be described in the next section).
+again (the second feedback signal ``Increase Precision'' provided by the
+{\sc Verify} phase in Figure~\ref{fig:CEGIS} is specific to control
+synthesis and will be described in the next section).
 
@@
 
-It is worth noting that each iteration of the loop adds a new input to
-the finite set $\text{\sc inputs}$ that is used for synthesis.  Given
-that the full set of inputs $\mathcal{D}$ is finite, this means that
-the refinement loop can only iterate a potentially very large, but
-finite number of times.
+Each iteration of the loop adds a new input to the finite set $\text{\sc
+inputs}$ that is used for synthesis.  Given that the full set of inputs
+$\mathcal{D}$ is finite, this means that the refinement loop can only
+iterate a potentially very large, but finite number of times.
 
@@
 %
-As the cost of SAT solving increases with in the size of the problem
+As~the cost of SAT solving increases with in the size of the problem
 instance, our algorithm tries to solve the problem first for small $I_p$,
@@
 
-The {\sc synthesize} phase uses BMC to 
-compute a solution $\tilde C(z)$.
-There are two approaches for the {\sc verify} phase.
-The first approach uses interval arithmetic \cite{moore1966interval}
-to represent the coefficients
-$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i,\,\allowbreak
-{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_p})]$ 
-and rounds operations outwards during calculations.  This effectively allows
-us to simultaneously evaluate the whole collection of plants $\hat{G}(s)$ (\emph{ie} all concrete plants $G(s)$ in the range $G(s) \pm \Delta_pG(s)$)
-plus the effects of numeric calculations in the engine.  Synthesized
-controllers using this verifier will always be stable for all plants in the
-family.
-% and only generate counterexamples when the precision of the
-%engine is insufficient (\emph{ie} no stable plant could be found). 
-Our preliminary experiments showed that a synthesis approach
-using this verification engine has poor performance and we
-%Given the high computational cost of this
-%approach, 
-therefore designed a second approach, which we describe below.
-Our experimental results described in Section~\ref{sec:experiments}
-%try both approaches and provide the time for the fastest. 
-show that the speedup yielded by the second approach 
-is in most cases of at least two orders of magnitude.
+The {\sc synthesize} phase uses BMC to compute a solution $\tilde C(z)$. 
+There are two alternatives for the {\sc verify} phase.  The first approach
+uses interval arithmetic \cite{moore1966interval} to represent the
+coefficients $[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i,\,\allowbreak
+{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_p})]$ and rounds outwards.  This0
+allows us to simultaneously evaluate the full collection of plants
+$\hat{G}(s)$ (i.e., all concrete plants $G(s)$ in the range $G(s) \pm
+\Delta_pG(s)$) plus the effects of numeric calculations.  Synthesized
+controllers are stable for all plants in the family.  Preliminary
+experiments show that a synthesis approach using this verification engine
+has poor performance and we therefore designed a second approach.  Our
+experimental results in Section~\ref{sec:experiments} show that the speedup
+yielded by the second approach is in most cases of at least two orders of
+magnitude.
 
 The second approach is illustrated in Figure~\ref{fig:CEGIS} and uses a
-two-stage verification approach: the first stage performs potentially unsound
-fixed-point operations assuming a plant precision \param{I_p}{F_p}, and the
-second stage restores soundness by validating these operations using
+two-stage verification approach: the first stage performs potentially
+unsound fixed-point operations assuming a plant precision \param{I_p}{F_p},
+and the second stage restores soundness by validating these operations using
 interval arithmetic on the synthesized controller.

### 2017-02-16 hscc2017/paper.tex
hscc17

@@
 %
-The resulting system using the typical series loop configuration, where
-$\tilde{C}(z)$ and $G(z)$ are in the forward path, is unstable. 
-\aabatecmt{[hang in there - did we not consider FWL on $G(z)$? why not?]}
-\dariocmt{we are explaining the case where a real plant (no FWL) is not correctly stabilized by $\tilde{C}$, so although our analysis might evaluate $\tilde{G}(z)$, the problem statement is over $G(z)$}
+The resulting system, 
+%using the typical series loop configuration, 
+where $\tilde{C}(z)$ and $G(z)$ are in the forward path, is unstable. 
+\blue{[check correctness](Notice that this is disregarding further approximation effects on the plant, not accounted for in the reference study.)}   
+%\aabatecmt{[hang in there - did we not consider FWL on $G(z)$? why not?]}
+%\dariocmt{we are explaining the case where a real plant (no FWL) is not correctly stabilized by $\tilde{C}$, so although our analysis might evaluate $\tilde{G}(z)$, the problem statement is over $G(z)$}
 Figure~\ref{fig:original} gives the Bode diagram for the digital controller

### 2017-02-16 hscc2017/paper.tex
nudge
cut

@@
 
-\renewcommand{\baselinestretch}{0.99}
+\renewcommand{\baselinestretch}{0.98}
 \allowdisplaybreaks
@@
 
-We have presented a CEGIS-based approach implemented in a tool called \tool,
-which uses inductive synthesis in conjunction with an algorithm for
-verifying robust closed-loop stability that addresses plant variations as
-interval sets as well as FWL uncertainties in digital controllers.  The
-novelty in our approach is that it is fully automated and algorithmically
-and numerically sound.  In particular, \tool marks the first use of the
-CEGIS that handles plants with uncertain models and FWL effects over the
-digital controller.  Implementing this architecture efficiently requires
-adjusting the traditional CEGIS refinement loop to the use of a two-stage
-verification engine: here, the first stage performs fast, but potentially
-unsound fixed-point operations, whereas the second stage restores soundness
-by validating the operations performed by the first stage using interval
-arithmetic.  Our experimental results show that \tool is able to synthesize
-stable controllers in most benchmarks within a reasonable amount of time
-fully automatically.  Future work will be the extension of this CEGIS-based
-approach to further classes of systems, including those with state space. 
-We will also consider performance requirements while synthesizing the
-digital controller.
+We have presented a method for synthesizing stable controllers and an
+implementation in a tool called \tool.  The novelty in our approach is that
+it is fully automated and algorithmically and numerically sound.  In
+particular, \tool marks the first use of the CEGIS that handles plants with
+uncertain models and FWL effects over the digital controller.  Implementing
+this architecture requires transforming the traditional CEGIS refinement
+loop into a two-stage engine: here, the first stage performs fast, but
+potentially unsound fixed-point operations, whereas the second stage
+restores soundness by validating the operations performed by the first stage
+using interval arithmetic.  Our experimental results show that \tool is able
+to synthesize stable controllers for most benchmarks within a reasonable
+amount of time fully automatically.  Future work will be the extension of
+this CEGIS-based approach to further classes of systems, including those
+with state space.  We will also consider performance requirements while
+synthesizing the digital controller.
 
@@
 
-%APPENDICES are optional
-%\balancecolumns
-%\appendix
-%Appendix A
-
 \end{document}

### 2017-02-16 hscc2017/paper.tex
wording

@@
 
-Within the scheme in Figure \ref{fig:CEGIS}, 
-while the {\sc synthesise} phase searches for potentially unsound 
-candidate solutions, the soundness of the model is ensured by the {\sc verify} phase.  
-If a candidate solution is successfully verified, it is necessarily sound.
-
-Through its two stages, the {\sc verify} phase looks at two separate elements for
-soundness.
-% The first ensures that there exists no
-% counterexample plant that would create a closed-loop with unstable
-% poles. The fixed word length of the controller is not relevant at this
-% point since the parameters have already been chosen to fit this
-% criteria (i.e., the candidate solution is FWL).
-The first stage ensures that no counterexample
-plant with an unstable closed loop exists with % If no such
-% system exists, then the controller is stable for all
-% plants in the collection with
-the limitations given by the data
-type used by the verifier. Since the actual
-plant works in the reals, whereas we use fixed/floating point
-arithmetic to evaluate it, we need to ensure that the rounding errors
-in the caculations do not cause the solution to be unsound.
-% 
-For this reason the second verification stage uses interval arithmetic with
-outward rounding to ensure that these errors do not exceed critical
-bounds that could make some plant unstable.
-
-This means that whilst the solution may not be complete, it is sound for
-evaluating any collection of real plants with a defined FWL controller. 
-We require two verification stages because,
-while the second one can ensure the stability of all plants in the collection, 
-it is unable to provide a counterexample.
+The {\sc synthesise} phase generates potentially unsound candidate
+solutions.  The soundness of the model is ensured by the {\sc verify} phase. 
+If a candidate solution passes verification, it is necessarily sound.
+
+The {\sc verify} phase considers two aspects of soundness.  The first stage
+ensures that no counterexample plant with an unstable closed loop exists
+over finite-precision arithmetic.  Since the actual plant uses reals, we
+need to ensure we do not miss a counterexample because of rounding errors. 
+For this reason, the second verification stage uses an overapproximation
+with interval arithmetic with outward rounding. Thus, the first verification
+stage underapproximates and is used to generate counterexamples, and the
+second stage overapproximates and provides proof that no counterexample
+exists.
 

### 2017-02-16 hscc2017/paper.tex
spelling

@@
 Correct control is non-trivial, however.  The problem is exacerbated by
-artefacts specific to digital control, such as the effects of
+artifacts specific to digital control, such as the effects of
 finite-precision arithmetic, time discretization, and quantization noise
@@
 operates on bit-vectors encoded using fixed-point arithmetic with finite
-word length (FWL).  The three effects of 1.~uncertaities, 2.~FWL
+word length (FWL).  The three effects of 1.~uncertainties, 2.~FWL
 representation and 3.~quantization errors are incorporated into the model,
@@
 polynomial order as the plant itself (indeed, all other errors described in
-this paper fulfil this property).  We~also remark that, due to its native
+this paper fulfill this property).  We~also remark that, due to its native
 digital implementation, there are no parametric errors ($\Delta_pC_n(z),
@@
 work), $\tilde{C}(z) \equiv \hat{C}(z) \equiv C(z)$ because the synthesis is
-performed directly using FWL representation.  In other words, we synthesise
+performed directly using FWL representation.  In other words, we synthesize
 a controller that is already in the domain $\mathbb{R} \param{I}{F}$ and has
@@
 \subsection{Closed-Loop Stability Verification under Parametric
-Uncertainties, FWL Representation and Quantisation Noise}
+Uncertainties, FWL Representation and Quantization Noise}
 \label{sec:stability}
@@
 behavior for the final (sound) solution, which presents a lower settling
-time (hence the noticeable digitazion effects).
+time (hence the noticeable digitization effects).
 
@@
 
-We have reported a favourable assessment of \tool over a diverse set of real-world
+We have reported a favorable assessment of \tool over a diverse set of real-world
 benchmarks. Nevertheless, this set of benchmarks is limited within the
@@
 robust stability with minimum gain~\cite{schmid2014unified,
-konigorski2012pole}.  However, when applied with the aim of synthesising a
+konigorski2012pole}.  However, when applied with the aim of synthesizing a
 digital controller, many of these techniques lack the ability to produce
@@
 
-Program synthesisers are an ideal fit for synthesis of parametric
+Program synthesizers are an ideal fit for synthesis of parametric
 controllers since the semantics of programs capture effects such as FWL

### 2017-02-16 hscc2017/paper.tex
another comment

@@
 
-\newcommand{\aabatecmt}[1]{{\color{red}#1}}
-\newcommand{\dariocmt}[1]{{\color{blue}#1}}
+\newcommand{\aabatecmt}[1]{}%{{\color{red}#1}}
+\newcommand{\dariocmt}[1]{}%{{\color{blue}#1}}
 
@@
 %and another one based on Jury's criterion~\cite{astrom1997computer}.  
-Here we choose Jury's criterion~\cite{astrom1997computer} in view of its efficiency \blue{[check correctness] and ease of integration within \tool}: 
+Here we choose Jury's criterion~\cite{astrom1997computer} in view of its efficiency 
+\aabatecmt{[check correctness]} 
+and ease of integration within \tool: 
 we employ this method to check the stability in the $z$-domain for the

### 2017-02-16 hscc2017/paper.tex
spacing
wording
cleanup

@@
 \usepackage[scaled]{helvet}
+\usepackage{mdwlist}
 
@@
 ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}}
-
-%\subtitle{[Extended Abstract]
-%\titlenote{A full version of this paper is available as
-%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
-%\LaTeX$2_\epsilon$\ and BibTeX} at
-%\texttt{www.acm.org/eaddress.htm}}}
-%
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
-
-%\numberofauthors{8} %  in this sample file, there are a *total*
-% of EIGHT authors. SIX appear on the 'first-page' (for formatting
-% reasons) and the remaining two appear in the \additionalauthors section.
-%
-%% \author{
-%% % You can go ahead and credit any number of authors here,
-%% % e.g. one 'row of three' or two rows (consisting of one row of three
-%% % and a second row of one, two or three).
-%% %
-%% % The command \alignauthor (no curly braces needed) should
-%% % precede each author name, affiliation/snail-mail address and
-%% % e-mail address. Additionally, tag each line of
-%% % affiliation/address with \affaddr, and tag the
-%% % e-mail address with \email.
-%% %
-%% % 1st. author
-%% \alignauthor
-%% Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
-%%        \affaddr{Institute for Clarity in Documentation}\\
-%%        \affaddr{1932 Wallamaloo Lane}\\
-%%        \affaddr{Wallamaloo, New Zealand}\\
-%%        \email{trovato@corporation.com}
-%% % 2nd. author
-%% \alignauthor
-%% G.K.M. Tobin\titlenote{The secretary disavows
-%% any knowledge of this author's actions.}\\
-%%        \affaddr{Institute for Clarity in Documentation}\\
-%%        \affaddr{P.O. Box 1212}\\
-%%        \affaddr{Dublin, Ohio 43017-6221}\\
-%%        \email{webmaster@marysville-ohio.com}
-%% }
 
@@
 \printccsdesc
-
-% We no longer use \terms command
-%\terms{Theory}
 
@@
 %
-\begin{itemize}
+\begin{itemize*}
 
@@
 
-\end{itemize}
+\end{itemize*}
 
@@
 %
-\begin{itemize}
+\begin{itemize*}
 \item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
@@
 \item the direct loop product $\tilde{C}(z) \hat{G}(z)$ has no pole-zero cancellation on or outside the unit circle.
-\end{itemize}
+\end{itemize*}
 \end{myprop}
@@
 
-The {\sc verify} phase considers two aspects of soundness.  The first stage
-ensures that no counterexample plant with an unstable closed loop exists
-over finite-precision arithmetic.  Since the actual plant uses reals, we
-need to ensure we do not miss a counterexample because of rounding errors. 
-For this reason, the second verification stage uses an overapproximation
-with interval arithmetic with outward rounding. Thus, the first verification
+The {\sc verify} phase has two stages.  The first stage ensures that no
+counterexample plant with an unstable closed loop exists over
+finite-precision arithmetic.  Since the actual plant uses reals, we need to
+ensure we do not miss a counterexample because of rounding errors.  For this
+reason, the second verification stage uses an overapproximation with
+interval arithmetic with outward rounding.  Thus, the first verification
 stage underapproximates and is used to generate counterexamples, and the
@@
 
-Researchers in formal verification of control systems have studied various
-effects of discretizing the dynamics, including delayed
-response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics \cite{Anta:2010:AVC:1879021.1879024} 
-with the goal to either verify~\cite{daes20161} or to optimize~\cite{oudjida2014design} 
-given implementations.
+Various effects of discretizing dynamics, including delayed
+response~\cite{Duggirala2015} and Finite Word Length (FWL)
+semantics~\cite{Anta:2010:AVC:1879021.1879024} have been studied, with the
+goal to either verify~\cite{daes20161} or to
+optimize~\cite{oudjida2014design} given implementations.
 
@@
 stable by design.  Most work in verification focuses on finding a correct
-variant of a known controller, looking for optimal parameter
-representations using FWL, but ignore the effects of rounding errors due to
-issues of mathematical tractability.  The analyses
-in~\cite{DBLP:conf/hybrid/RouxJG15,DBLP:conf/hybrid/WangGRJF16} rely on an
-invariant computation on the discrete system dynamics using Semi-Definite
-Programming (SDP).  While the former uses BIBO properties to determine
-stability, the latter uses Lyapunov-based quadratic invariants.  In both
-cases, the SDP solver uses floating-point arithmetic and soundness is
-checked by bounding the error.  An alternative approach is taken
-by~\cite{park2016scalable}, where the verification of existing code is
-performed against a known model by extracting an LTI model of the code
-through symbolic execution.  In order to account for rounding errors, an
-upper bound is introduced in the verification phase.  If~the error of the
-implementation is lower than this tolerance level, then the verification is
-successful.
+variant of a known controller, looking for optimal parameter representations
+using FWL, but ignore the effects of rounding errors due to issues of
+mathematical tractability.  The analyses in~\cite{DBLP:conf/hybrid/RouxJG15,
+DBLP:conf/hybrid/WangGRJF16} rely on an invariant computation on the
+discrete system dynamics using Semi-Definite Programming (SDP).  While the
+former uses BIBO properties to determine stability, the latter uses
+Lyapunov-based quadratic invariants.  In both cases, the SDP solver uses
+floating-point arithmetic and soundness is checked by bounding the error. 
+An alternative approach is taken by~\cite{park2016scalable}, where the
+verification of existing code is performed against a known model by
+extracting an LTI model of the code through symbolic execution.  In order to
+account for rounding errors, an upper bound is introduced in the
+verification phase.  If~the error of the implementation is lower than this
+tolerance level, then the verification is successful.
 
@@
 
-%In \cite{DBLP:journals/corr/PakmehrWJVF13}, Pakmehr et al.  design a control software verification framework for gas turbine engines.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-02-16 hscc2017/paper.tex
move section 2.2 to the beginning of the next column
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
added Alessandro's comment related to the illustrative example
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
nudge
keep the standard throughout the text about i.e.
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
space
move title of section 2.2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\renewcommand{\baselinestretch}{0.98}
+\renewcommand{\baselinestretch}{0.99}
 \allowdisplaybreaks
@@
 focus on linear models with known configurations, and perform parametric
-synthesis of stabilizing digital controllers (further closed-loop
+synthesis of stabilizing digital controllers (further closed-loop performance
 requirements are left to future work).
@@
 Thus, we consider continuous dynamics (the plant) and discrete parts (the
-digital controller). In order to obtain an overall model, we discretize the
-continuous plant and look at the plant dynamics from the perspective of the digital controller.
+digital controller). In order to obtain an overall model for the synthesis, 
+we discretize the continuous plant and particularly look at the plant dynamics 
+from the perspective of the digital controller.
 
@@
 %
-For the sake of brevity, we will use the notation $G(z)$ to represent the
+In this study, for the sake of brevity, we will use the notation $G(z)$ to represent the
 pulse transfer function $G(z,T)$.
@@
 where $\tilde{C}(z)$ and $G(z)$ are in the forward path, is unstable. 
-\blue{[check correctness](Notice that this is disregarding further approximation effects on the plant, not accounted for in the reference study.)}   
+Notice that this is disregarding further approximation effects on the plant caused by quantization in the verifier (i.e., $\tilde{G}(z)$).
 %\aabatecmt{[hang in there - did we not consider FWL on $G(z)$? why not?]}

### 2017-02-16 hscc2017/paper.tex
added DOI and reduce space
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
typo

@@
 \CopyrightYear{2017}
-\setcopyright{acmcopyright}
+\setcopyright{rightsretained}
 \conferenceinfo{HSCC '17,}{April 18--20, 2017, Pittsburgh, PA, USA.}
-\isbn{978-1-4503-4590-3/17/04}\acmPrice{\$15.00.}
-\doi{TBD.}
+\isbn{978-1-4503-4590-3/17/04}%\acmPrice{\$15.00.}
+\doi{http://dx.doi.org/10.1145/3049797.3049802}
 
@@
 
-Additional benchmarks were created for the \textit{Cruise Control System}, \textit{Springer-mass damper}, and \textit{Satellite} considering parametric additive in the nominal plant model  (represented by $\Delta_{p}\vec{G}$ in Eq.~\eqref{digital_plant_tf}).
+Additional benchmarks were created for the \textit{Cruise Control System}, \textit{Spring-mass damper}, and \textit{Satellite} considering parametric additive in the nominal plant model  (represented by $\Delta_{p}\vec{G}$ in Eq.~\eqref{digital_plant_tf}).
 The uncertainties are deviations bounded to a maximum magnitude of $0.5$ in each coefficient.

### 2017-02-16 hscc2017/paper.tex
magic number
wording

@@
 
-\renewcommand{\baselinestretch}{0.98}
+\renewcommand{\baselinestretch}{0.9857}
 \allowdisplaybreaks
@@
 
-We illustrate our approach with a classical cruise control example,
-extracted from the literature~\cite{Astrom08}.  The example highlights the
-challenges that arise when using finite-precision arithmetic in digital
-control.  We are given a discrete plant model (with a time step of
-$0.2$\,s), which is represented by the following $z$-expression:
+We illustrate our approach with a classical cruise control example from the
+literature~\cite{Astrom08}.  It highlights the challenges that
+arise when using finite-precision arithmetic in digital control.  We are
+given a discrete plant model (with a time step of $0.2$\,s), 
+represented by the following $z$-expression:
 %
@@
 The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that the controller
-$C(z)$ in~\eqref{Eq:running-example-controller} stabilizes the
-closed-loop system for the discrete plant model $G(z)$ in~\eqref{Eq:running-example-plant}.  
-However, if the effects of finite-precision arithmetic are considered (e.g., fixed-point arithmetic and
-FWL), then this closed-loop system becomes unstable.
+$C(z)$ in~\eqref{Eq:running-example-controller} stabilizes the closed-loop
+system for the discrete plant model $G(z)$
+in~\eqref{Eq:running-example-plant}.  However, if the effects of
+finite-precision arithmetic are considered, then this closed-loop system
+becomes unstable.
 %
@@
 as the phase margin is negative, 
-the controller is unstable when considering the above FWL effects.
+the controller is unstable when considering the FWL effects.
 

### 2017-02-16 hscc2017/paper.tex
wording

@@
 We now demonstrate how our approach solves the synthesis problem for the
-example given in the previous section.  
-Assuming a precision of $I_p=16$, $F_p=24$,  
-we start with an a-priori candidate solution with all coefficients zero (note that the controller is in the FWL domain, hence we use $\tilde{C}(z)$): 
+example given in the previous section.  Assuming a precision of $I_p=16$,
+$F_p=24$, we start with an a-priori candidate solution with all coefficients
+zero (the controller performs FWL arithmetic, hence we use
+$\tilde{C}(z)$):
 %
@@
 
-The first set of benchmarks uses the discrete model $G_1(z)$ of a cruise control
+The first set of benchmarks uses the discrete model $G_1$ of a cruise control
 system for a car, and accounts for rolling friction, aerodynamic drag, and
@@
 %
-The second set of benchmarks considers the discrete model $G_2(z)$ 
+The second set of benchmarks considers the discrete model $G_2$ 
 of a simple spring-mass damper plant~\cite{DBLP:conf/hybrid/WangGRJF16}. 
@@
 %
-A third set of benchmarks uses the discrete model $G_{3}(z)$ for satellite attitude 
+A third set of benchmarks uses the discrete model $G_{3}$ for satellite attitude 
 dynamics~\cite{Franklin15}, which require attitude control
 for orientation of antennas and sensors w.r.t.~Earth.
-The fourth set of benchmarks presents an alternative discrete model $G_4(z)$ 
+The fourth set of benchmarks presents an alternative discrete model $G_4$ 
 of a cruise control system~\cite{DBLP:conf/hybrid/WangGRJF16}. 
@@
 %
-%\noindent We can obtain $G_{4}(z)$ using the ZOH discretization defined
+%\noindent We can obtain $G_{4}$ using the ZOH discretization defined
 %in Eq.~\eqref{eq:pulsetf} with three different sample times ($0.1$, $0.05$,
@@
 %
-The seventh set of benchmarks contains a well-studied discrete  
-non-minimal phase model $G_{7}(z)$. As known, non-minimal phase model offers 
-additional difficulties for the design of stable controllers~\cite{Doyle:1991:FCT:574259}. 
+The seventh set of benchmarks contains a well-studied discrete non-minimal
+phase model $G_{7}$.  Non-minimal phase models cause additional
+difficulties for the design of stable
+controllers~\cite{Doyle:1991:FCT:574259}.
 %
@@
 %
-The eighth set of benchmarks describes the discrete model $G_{8}(z)$ for the \textit{Helicopter Longitudinal Motion},
-which provides the longitudinal motion dynamics of a helicopter~\cite{Franklin15}. 
+The eighth set of benchmarks describes the discrete model $G_{8}$ for the
+\textit{Helicopter Longitudinal Motion}, which provides the longitudinal
+motion dynamics of a helicopter~\cite{Franklin15}.
 %
@@
 %
-The ninth  set of benchmarks contains the discrete model $G_{9}(z)$ for the known \textit{Inverted Pendulum}, which 
-describes a pendulum dynamics with its center of mass above its pivot point~\cite{Franklin15}. 
+The ninth set of benchmarks contains the discrete model $G_{9}$ for the
+known \textit{Inverted Pendulum}, which describes a pendulum dynamics with
+its center of mass above its pivot point~\cite{Franklin15}.
 %
@@
 %
-The tenth set of benchmarks contains the \textit{Magnetic Suspension} discrete model $G_{10}(z)$, which describes the dynamics of a mass that levitates with support only of a magnetic field~\cite{Franklin15}.
+The tenth set of benchmarks contains the \textit{Magnetic Suspension}
+discrete model $G_{10}$, which describes the dynamics of a mass that
+levitates with support only of a magnetic field~\cite{Franklin15}.
 %
@@
 %
-The eleventh set of benchmarks contains the \textit{Computer Tape Driver} discrete model $G_{11}(z)$, which 
-describes a system to read and write data on a storage device~\cite{Franklin15}.
+The eleventh set of benchmarks contains the \textit{Computer Tape Driver}
+discrete model $G_{11}$, which describes a system to read and write data
+on a storage device~\cite{Franklin15}.
 %
@@
 %
-The last set of benchmarks considers a discrete model $G_{12}(z)$ 
-that is typically used for evaluating stability
-margins and controller fragility~\cite{bhattacharyya97, keel_Bhattacharyya_examples}.
-
-Additional benchmarks were created for the \textit{Cruise Control System}, \textit{Spring-mass damper}, and \textit{Satellite} considering parametric additive in the nominal plant model  (represented by $\Delta_{p}\vec{G}$ in Eq.~\eqref{digital_plant_tf}).
-The uncertainties are deviations bounded to a maximum magnitude of $0.5$ in each coefficient.
-These uncertain models are respectively represented by $G_{1b}(z)$, $G_{2b}(z)$, $G_{3b}(z)$, and $G_{3d}(z)$.
-
-All experiments have been conducted on a 12-core 2.40\,GHz Intel Xeon E5-2440
-with 96\,GB of RAM and Linux OS.  All times given are wall clock times in
-seconds, as measured by the UNIX date command.  For the two-stage verification 
-engine in Figure~\ref{fig:CEGIS} we have applied a timeout of $8$ hours per benchmark, 
-whereas $24$ hours have been set for the approach using a one-stage engine.
+The last set of benchmarks considers a discrete model $G_{12}$ that is
+typically used for evaluating stability margins and controller
+fragility~\cite{bhattacharyya97, keel_Bhattacharyya_examples}.
+
+Additional benchmarks were created for the \textit{Cruise Control System},
+\textit{Spring-mass damper}, and \textit{Satellite} considering parametric
+additive in the nominal plant model  (represented by $\Delta_{p}\vec{G}$ in
+Eq.~\eqref{digital_plant_tf}).  The uncertainties are deviations bounded to
+a maximum magnitude of $0.5$ in each coefficient.  These uncertain models
+are respectively represented by $G_{1b}$, $G_{2b}$, $G_{3b}$ and
+$G_{3d}$.
+
+All experiments have been conducted on a 12-core 2.40\,GHz Intel Xeon
+E5-2440 with 96\,GB of RAM and Linux OS.  All times given are wall clock
+times in seconds, as measured by the UNIX date command.  For the two-stage
+verification engine in Figure~\ref{fig:CEGIS} we have applied a timeout of
+$8$ hours per benchmark, whereas $24$ hours have been set for the approach
+using a one-stage engine.
 

### 2017-02-16 hscc2017/paper.tex
wording

@@
 For the majority of the benchmarks, the conjecture explained in
-Section~\ref{synthesis-elements} holds and the two-stage verification 
-engine is able to find a stable solution in less than one minute for half
-of the benchmarks. This is possible if the inductive solutions need to be 
-refined with few counterexamples and increments of the fixed-point precision.  
+Section~\ref{synthesis-elements} holds and the two-stage verification engine
+is able to find a stable solution in less than one minute for half of the
+benchmarks.  This is possible if the inductive solutions need to be refined
+with few counterexamples and increments of the fixed-point precision. 
 However, the benchmark \emph{SatelliteB2} with uncertainty ($G_{3b}$) has
-required too many counterexamples to refine its solution.  
-For this particular case, the one-stage engine is able to complement the
-two-stage approach and synthesize a solution instead.  It is important to
-reiterate that the one-stage verification engine does not take advantage of
-the inductive conjecture inherent to CEGIS, but instead fully explores the
-counterexample space in one SAT instance.  As expected, this approach is 
-significantly slower on average and is only useful for benchmarks where 
-the CEGIS approach requires too many counterexample refinement iterations
-such that exploring all counterexamples in a single SAT instance performs better.
-Our results suggest an average performance difference of at least two orders
-of magnitude between the two engines, leading to the one-stage engine timing
-out on the majority of our benchmarks.  Table~\ref{tab:results}
-lists the results for both engines, where in $16$ out of $23$
-benchmarks, the two-stage engine is faster.
+required too many counterexamples to refine its solution.  For this
+particular case, the one-stage engine is able to complement the two-stage
+approach and synthesizes a solution.  It is important to reiterate that the
+one-stage verification engine does not take advantage of the inductive
+conjecture inherent to CEGIS, but instead fully explores the counterexample
+space in a single SAT instance.  As expected, this approach is significantly
+slower on average and is only useful for benchmarks where the CEGIS approach
+requires too many refinement iterations such that exploring all
+counterexamples in a single SAT instance performs better.  Our results
+suggest an average performance difference of at least two orders of
+magnitude, leading to the one-stage engine timing out on the majority of our
+benchmarks.  Table~\ref{tab:results} lists the results for both engines,
+where in $16$ out of $23$ benchmarks, the two-stage engine is faster.
 

### 2017-02-16 hscc2017/paper.tex
wording

@@
 
-The presence of uncertainty in some particular benchmarks ($2$, $4$, $6$, and $8$)  
-leads to harder verification conditions to be checked 
-by the {\sc verify} phase, which thus influences the overall synthesis time.   
-However, considering the faster engine for each benchmark (marked as bold in Table~\ref{tab:results}), 
-the median run-time amounts to $48$\,s, implying that \tool can synthesize 
-half of the controllers in less than one minute. Overall, the average fastest synthesis 
-time considering both engines is approximately $42$ minutes.  We
-consider these times short enough to be of practical use to control
-engineers, and thus affirm RQ1.  We further observe that the approach using
-the two-stage verification engine is able to synthesize stable controllers
-in $19$ out of the $23$ benchmarks, and can be complemented using the
-one-stage engine, which is faster for two benchmarks where the inductive
-conjectures fail.  Both verification engines together enable controller
-synthesis for $20$ out of $23$ benchmarks.  For the remaining benchmarks
-our approach failed to synthesize a stable controller within the time
-limits.  This can be addressed by either increasing either the time limit
-or the fixed-point word widths considered, or by using floating-point
-arithmetic instead.  The synthesized controllers have been confirmed to be stable
-outside of our model representation using MATLAB, positively answering RQ2. 
-A~link to the full experimental environment, including scripts to reproduce
-the results, all benchmarks and the \tool tool, is provided in the
+The presence of uncertainty in some particular benchmarks ($2$, $4$, $6$,
+and $8$) leads to harder verification conditions to be checked by the {\sc
+verify} phase, which impacts the overall synthesis time.  However,
+considering the faster engine for each benchmark (marked in bold in
+Table~\ref{tab:results}), the median run-time is $48$\,s, implying that
+\tool can synthesize half of the controllers in less than one minute. 
+Overall, the average fastest synthesis time considering both engines is
+approximately $42$ minutes.  We consider these times short enough to be of
+practical use to control engineers, and thus affirm RQ1.  We further observe
+that the two-stage verification engine is able to synthesize stable
+controllers for $19$ out of the $23$ benchmarks, and can be complemented
+using the one-stage engine, which is faster for two benchmarks where the
+inductive conjectures fail.  Both verification engines together enable
+controller synthesis for $20$ out of $23$ benchmarks.  For the remaining
+benchmarks our approach failed to synthesize a stable controller within the
+time limits.  This can be addressed by either increasing either the time
+limit or the fixed-point word widths considered, or by using floating-point
+arithmetic instead.  The synthesized controllers have been confirmed to be
+stable outside of our model representation using MATLAB, positively
+answering RQ2.  A~link to the full experimental environment, including
+scripts to reproduce the results, all benchmarks and the \tool tool, is
+provided in the
 footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}\\
-CBMC (SHA-1 hash) version: \\ 
-7a6cec1dd0eb8843559591105235f1f2c4678801}
+CBMC (SHA-1 hash) version: \\ 7a6cec1dd0eb8843559591105235f1f2c4678801}
 
 %--------------------------------------
-\subsection{Threats to Validity and Generalizations}
+\subsection{Threats to Validity}
 %--------------------------------------
 
-We have reported a favorable assessment of \tool over a diverse set of real-world
-benchmarks. Nevertheless, this set of benchmarks is limited within the
-scope of this paper and \tool's performance 
-%may not generalize to other benchmark scenarios. This can 
-needs to be addressed by expanding the benchmarks set
-in future experiments.
+We have reported a favorable assessment of \tool over a diverse set of
+real-world benchmarks.  Nevertheless, this set of benchmarks is limited
+within the scope of this paper and \tool's performance needs to be assessed
+on a larger benchmark set in future work.
 

### 2017-02-16 hscc2017/paper.tex
wording

@@
 more recent Linear Quadratic Regulator (LQR)~\cite{bemporad2002explicit}
-have been used in several studies with increasing degrees of success to
-ensure stability.  The latter approach highlights the importance of
-conserving energy during the control process, which results in lower running
-costs.  Since real systems are subject to tolerance and noise as well as the
-need for economy, more recent studies focus on the problem of achieving
-robust stability with minimum gain~\cite{schmid2014unified,
-konigorski2012pole}.  However, when applied with the aim of synthesizing a
-digital controller, many of these techniques lack the ability to produce
-sound or stable results because they disregard the effects of quantization
-and rounding.  Recent papers on implementations/synthesis of LTI digital
-controllers~\cite{das2013lqr, ghosh2013fpga} focus on time discretization,
-failing to account for these error-inducing effects and can result in digital 
-systems that are unstable even though they have been proven to be
-robustly stable in a continuous space.
+have been used with increasing degrees of success.  The latter approach
+highlights the importance of conserving energy during the control process,
+which results in lower running costs.  Since real systems are subject to
+tolerance and noise as well as the need for economy, more recent studies
+focus on the problem of achieving robust stability with minimum
+gain~\cite{schmid2014unified, konigorski2012pole}.  However, when applied
+with the aim of synthesizing a digital controller, many of these techniques
+lack the ability to produce sound or stable results because they disregard
+the effects of quantization and rounding.  Recent papers on
+implementations/synthesis of LTI digital controllers~\cite{das2013lqr,
+ghosh2013fpga} focus on time discretization, failing to account for these
+error-inducing effects and can result in digital systems that are unstable
+even though they have been proven to be robustly stable in a continuous
+space.
 

### 2017-02-16 hscc2017/paper.tex
wording

@@
 
-\renewcommand{\baselinestretch}{0.9857}
+\renewcommand{\baselinestretch}{0.992}
 \allowdisplaybreaks
@@
 controller is illustrated in Figure~\ref{fig:sampledsystem}.  The DAC and
-ADC converters introduce quantization errors (notice that each of them
-may have a different FWL representation than the controller),
-which are modeled as disturbances 
-$\nu_{1}(z)$ and $\nu_{2}(z)$;  
-$G(s)$ is the continuous-time plant model
-with parametric additive uncertainty $\Delta_p{G}_n(s)$ and $\Delta_p{G}_d(s)$ (as mentioned above);  
-$R(z)$ is a given reference signal; 
-$U(z)$ is the control signal; 
-and $\hat{Y}(z)$ is the output signal affected by the disturbances and uncertainties in the closed-loop system 
+ADC converters introduce quantization errors (notice that each of them may
+have a different FWL representation than the controller), which are modeled
+as disturbances $\nu_{1}(z)$ and $\nu_{2}(z)$; $G(s)$ is the continuous-time
+plant model with parametric additive uncertainty $\Delta_p{G}_n(s)$ and
+$\Delta_p{G}_d(s)$ (as mentioned above); $R(z)$ is a given reference signal;
+$U(z)$ is the control signal; and $\hat{Y}(z)$ is the output signal affected
+by the disturbances and uncertainties in the closed-loop system
 %
@@
 during the {\sc precision} phase by \tool since this solution is not
-considered to be sound.  Finally, Figure~\ref{fig:step2} shows a stable
+sound.  Finally, Figure~\ref{fig:step2} shows a stable
 behavior for the final (sound) solution, which presents a lower settling
-time (hence the noticeable digitization effects).
+time (hence the digitization effects).
 

### 2017-02-19 hscc2017/paper.tex
nudge
various superflous commas

@@
 artifacts specific to digital control, such as the effects of
-finite-precision arithmetic, time discretization, and quantization noise
+finite-precision arithmetic, time discretization and quantization noise
 introduced by A/D and D/A conversion.  Thus, programming expertise is a key
@@
 
-As we only consider transfer function models, and require a $z$-domain transfer
+As we only consider transfer function models and require a $z$-domain transfer
 function $G(z)$ that captures all aspects of the continuous plant, 
@@
 %
-where $\Delta_bc_i=\tilde{c}_i-\hat{c}_i$, and $\Delta_b{G}$ represents the
+where $\Delta_bc_i=\tilde{c}_i-\hat{c}_i$ and $\Delta_b{G}$ represents the
 plant uncertainty caused by the rounding off effect.  We capture the global
@@
 Sound synthesis of the digital controller requires the consideration of the
-effect of FWL on the controller, and of quantization disturbances in the
+effect of FWL on the controller and of quantization disturbances in the
 closed-loop system.  Let the quantizer $Q1$ (ADC) be the source of a white
-noise $\nu_{1}$, and $Q2$ (DAC) be the source of a white noise~$\nu_{2}$. 
+noise $\nu_{1}$ and $Q2$ (DAC) be the source of a white noise~$\nu_{2}$. 
 The following equation models the system in Figure~\ref{fig:sampledsystem},
@@
 Figure~\ref{fig:sampledsystem}, with regards to the exogenous signals
-$R(z)$, $\nu_{1}$, and $\nu_{2}$, which are all bounded (in particular, the
+$R(z)$, $\nu_{1}$ and $\nu_{2}$, which are all bounded (in particular, the
 bound on the quantization noise is given by Assumption~\ref{whitenoise}).
@@
 verification module for \tool.  It checks the stability of closed-loop control systems and
-considers finite-word length (FWL) effects in the digital controller, and
+considers finite-word length (FWL) effects in the digital controller and
 uncertainty parameters in the plant model (plant intervals)~\cite{Bessa16}.
@@
 }
-\caption{Counterexample-Guided Inductive Synthesis of Closed-loop Systems (Step~D) in Figure~\ref{DSSynth_process}
+\caption{Counterexample-Guided Inductive Synthesis of Closed-loop Systems (Step~D)
 \label{fig:CEGIS}}
@@
 %
-\begin{figure}[htb]
+\begin{figure}[tb]
     \centering
-    \begin{subfigure}[b]{0.4\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
         \includegraphics[width=\textwidth]{figures/runningexample_bd0.pdf}
@@
     ~
-    \begin{subfigure}[b]{0.4\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
         \includegraphics[width=\textwidth]{figures/runningexample_bd2.pdf}
@@
 Additional benchmarks were created for the \textit{Cruise Control System},
-\textit{Spring-mass damper}, and \textit{Satellite} considering parametric
+\textit{Spring-mass damper} and \textit{Satellite} considering parametric
 additive in the nominal plant model (represented by $\Delta_{p}\vec{G}$ in
@@
 
-The presence of uncertainty in some particular benchmarks ($2$, $4$, $6$,
+The presence of uncertainty in some particular benchmarks ($2$, $4$, $6$
 and $8$) leads to harder verification conditions to be checked by the {\sc
@@
 Program synthesis is the problem of computing correct-by-design programs
-from high-level specifications, and algorithms for this problem have made
+from high-level specifications. Algorithms for this problem have made
 substantial progress in recent years.  One such

### 2017-02-19 hscc2017/paper.tex
font
comma

@@
 $\mathcal{D}$ is finite, this means that the refinement loop can only
-iterate a potentially very large, but finite number of times.
+iterate a potentially very large but finite number of times.
 
@@
 \begin{array}{ll}
-a_{j-1}, & \texttt{if}~i=1\\
-v_{(1)(N-j+1)}^{0},&\texttt{if}~i=2
+a_{j-1}, & \mbox{if}~i=1\\
+v_{(1)(N-j+1)}^{0},&\mbox{if}~i=2
 \end{array}
@@
 \begin{array}{ll}
-0,&\texttt{if}~j>n-k\\
-v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \texttt{if}~j\leq n-k ~\texttt{and}~i=1\\
-v_{(1)(N-j+1)}^{k},& \texttt{if}~j\leq n-k ~\texttt{and}~i=2\\
+0,&\mbox{if}~j>n-k\\
+v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \mbox{if}~j\leq n-k ~\mbox{and}~i=1\\
+v_{(1)(N-j+1)}^{k},& \mbox{if}~j\leq n-k ~\mbox{and}~i=2\\
 \end{array}

### 2017-03-01 hscc2017/paper.tex
RE badge
cite ASPLOS 2006 paper

@@
 
-\renewcommand{\baselinestretch}{0.992}
+\renewcommand{\baselinestretch}{0.99}
 \allowdisplaybreaks
@@
 \title{
-Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous
-Plants%
+Sound and Automated Synthesis of Digital\\
+Stabilizing Controllers for Continuous Plants%
 \thanks{Supported by EPSRC grant EP/J012564/1,
@@
 
+% RE badge
+\begin{tikzpicture}[remember picture,overlay]
+  \node[anchor=north east,inner sep=0pt] at ($(current page.south west)+(8.1in,10.6in)$) {
+     \includegraphics[scale=0.3]{hscc-badge2}
+  };
+\end{tikzpicture}%
+%
 Modern implementations of embedded control systems have proliferated with
@@
 synthesizers implementing Counter-Example Guided Inductive Synthesis
-(CEGIS)~\cite{sketch} are now able to generate programs for highly
-non-trivial specifications with a very high degree of automation.  Modern
-synthesis engines combine automated testing, genetic algorithms, and
-SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a,
-DBLP:conf/lpar/DavidKL15}.
+(CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} are now able to generate
+programs for highly non-trivial specifications with a very high degree of
+automation.  Modern synthesis engines combine automated testing, genetic
+algorithms, and SMT-based automated
+reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}.
 
@@
 synthesis engine.  Our program synthesizer implements Counter-Example Guided
-Inductive Synthesis (CEGIS)~\cite{sketch}.  We start by presenting its
-general architecture followed by describing the parts specific to
-closed-loop control systems.  A high-level view of the synthesis process is
-given in Figure~\ref{DSSynth_process}.  Steps $1$ to $3$ are performed by
-the user and Steps~A to D are automatically performed by our tool for
-Digital Systems Synthesis, named \tool.
+Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}.  We
+start by presenting its general architecture followed by describing the
+parts specific to closed-loop control systems.  A high-level view of the
+synthesis process is given in Figure~\ref{DSSynth_process}.  Steps $1$ to
+$3$ are performed by the user and Steps~A to D are automatically performed
+by our tool for Digital Systems Synthesis, named \tool.
 
@@
 
-We have presented a method for synthesizing stable controllers and an
-implementation in a tool called \tool.  The novelty in our approach is that
-it is fully automated and algorithmically and numerically sound.  In
-particular, \tool marks the first use of the CEGIS that handles plants with
-uncertain models and FWL effects over the digital controller.  Implementing
-this architecture requires transforming the traditional CEGIS refinement
-loop into a two-stage engine: here, the first stage performs fast, but
-potentially unsound fixed-point operations, whereas the second stage
-restores soundness by validating the operations performed by the first stage
-using interval arithmetic.  Our experimental results show that \tool is able
-to synthesize stable controllers for most benchmarks within a reasonable
-amount of time fully automatically.  Future work will be the extension of
-this CEGIS-based approach to further classes of systems, including those
-with state space.  We will also consider performance requirements while
-synthesizing the digital controller.
+We have presented a method for synthesizing stable controllers, implemented
+in a tool called \tool.  Our approach is it is fully automated and
+algorithmically and numerically sound.  \tool marks the first use of the
+CEGIS that handles plants with uncertain models and FWL effects over the
+digital controller.  We transform the traditional CEGIS refinement loop into
+a two-stage engine: here, the first stage performs fast, but potentially
+unsound fixed-point operations, whereas the second stage restores soundness
+by validating the operations performed by the first stage using interval
+arithmetic.  Our experimental results show that \tool is able to synthesize
+stable controllers for most benchmarks within a reasonable amount of time
+fully automatically.  Future work will be the extension of this CEGIS-based
+approach to further classes of systems, including those with state space. 
+We will also consider performance requirements while synthesizing the
+digital controller.
 

### 2017-03-03 hscc2017/paper.tex
nudge

@@
 
-\renewcommand{\baselinestretch}{0.99}
+\renewcommand{\baselinestretch}{0.991}
 \allowdisplaybreaks
@@
 
-By combining and applying state-of-the-art synthesis engines we present a
-tool that automatically generates digital controllers for a given continuous
-plant model that are correct by construction.  This approach delivers a high
+By combining state-of-the-art synthesis engines we present a tool that
+automatically generates digital controllers for a given continuous plant
+model that are correct by construction.  This approach delivers a high
 degree of automation, promises to reduce the cost and time of development of
@@
 focus on linear models with known configurations, and perform parametric
-synthesis of stabilizing digital controllers (further closed-loop performance
-requirements are left to future work).
+synthesis of stabilizing digital controllers (further closed-loop
+performance requirements are left to future work).
 
@@
   synthesis is non-trivial and addresses challenges specific to control
-  systems, such as the effects of quantizers and FWL.  In particular, we
+  systems, such as quantizers and FWL.  In particular, we
   have found that a two-stage verification engine that continuously refines
@@
 
+\newpage
 \bibliographystyle{abbrv}

### 2017-03-03 hscc2017/paper.tex
page breaks
SWATI paper

@@
 %------------------------------------
+\newpage
 \subsection{Model Imprecision, Finite Word Length Representation and Quantization Effects}
@@
 A~different solution that uses FWL as the starting point is an approach that
-synthesizes word lengths for known control problems~\cite{jha2013swati};
+synthesizes word lengths for known control problems~\cite{jha-nsv13};
 however, this provides neither an optimal result nor a comprehensive
@@
 approach to further classes of systems, including those with state space.
-We will also consider performance requirements while synthesizing the
-digital controller.
-
-\newpage
+
+%Finally, we will consider performance requirements.
+
+%\newpage
 \bibliographystyle{abbrv}

### 2017-03-08 slides/presentation.tex
HSCC Presentation first draft

\documentclass{beamer}

\usepackage{url}           % format URLs
\usepackage{listings}      % format code
\lstset{
  mathescape, 
  language={C},
  basicstyle=\small
}
\usepackage{enumitem}      % adjust spacing in enums
%\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage{xspace,framed}
\usepackage{colortbl}
\usepackage{calc}
%\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb,amsmath,amsfonts} 
\usepackage{mathtools}
\usepackage{microtype}

\usepackage{algorithm}
\usepackage{amsfonts}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usetikzlibrary{patterns}
\usepackage[justification=centering]{caption}
\usepackage{stmaryrd}
\usepackage{hhline}
\usepackage{pifont}
\usepackage{pgfplots}
\usepackage{longtable}
\usepackage{afterpage}
\usepackage{wasysym}
\usepackage[scaled]{helvet}
\usepackage{mdwlist}

\newtheorem{myassumption}{Assumption}
\newtheorem{mylemma}{Lemma}
\newtheorem{myprop}{Proposition}

\renewcommand{\baselinestretch}{0.991}
\allowdisplaybreaks
\newcommand\tool{{\sf DSSynth}\xspace}
\newcommand{\xmark}{\ding{55}}

\begin{document}

\title {Sound and Automated Synthesis of Digital
Stabilizing Controllers for Continuous Plants}

\author{\textbf{Alessandro Abate}, Iury Bessa, Dario Cattaruzza, Lucas Cordeiro, Cristina David, Pascal Kesseli and Daniel Kroening}

\frame{\maketitle}

\begin{frame}{\tool}
%
Modern control is implemented with digital microcontrollers, embedded within
a dynamical plant that represents physical components.
\begin{figure}
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/step1_figureB.png}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/step1_figureC.png}
    \end{subfigure}
     ~
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/step1_figureD.png}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.15\textwidth}
        \includegraphics[width=\textwidth]{figures/step1_figureA.png}
    \end{subfigure}
\end{figure}

\tool uses counter\-example guided inductive
synthesis to automate the design of digital controllers that are
correct by construction.
%
\end{frame}

\begin{frame}[fragile]{Hybrid Dynamical System}{Continuous Plant and Digital Controller}

\begin{figure}[htb]
\centering

\tikzset{add/.style n args={4}{
    minimum width=6mm,
    path picture={
        \draw[circle] 
            (path picture bounding box.south east) -- (path picture bounding box.north west)
            (path picture bounding box.south west) -- (path picture bounding box.north east);
        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
        }
    }
 }

\resizebox{1.0\textwidth}{!}{
 \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
     semithick, initial text=, ampersand replacement=\&,]

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.2cm] {
    \node[draw=none] (r) {$R(z)$};
%   \& \coordinate (aux0);
   \& \node[circle,add={-}{+}{}{}] (circle) {};
   \node[draw=none] (ez) at ([xshift=.9cm,yshift=.2cm]circle)  {$e(z)$};
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Controller}] (cz) at ([xshift=.5cm,yshift=0cm]circle) {\sc $\hat{C}(z)$};
   \node[draw=none] (ud) at ([xshift=1cm,yshift=.2cm]cz)  {$U(z)$};

   \& complexnode/.pic={ 
      \node[rectangle,draw,
	minimum width=3cm,
	minimum height=1.6cm,
	label=\textbf{DAC},] (dac) {};
     \node[circle,add={}{+}{+}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}   
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc $\hat{G}(s)$}};
   \node[draw=none] (ud) at ([xshift=-1cm,yshift=.2cm]gs)  {$U(s)$};
   \node[draw=none] (y) at ([xshift=1cm,yshift=.2cm]gs)  {$\hat{Y}(s)$};
   \& complexnode/.pic={ 
     \node[rectangle,draw,
	minimum width=4cm,
	minimum height=1.6cm,
	label=\textbf{ADC},] (adc) {};
   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
   \coordinate (switch1) at ([xshift=-1cm]adc.center);
   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
   \node[circle,add={}{+}{+}{},fill=gray!20] (q1) at ([xshift=1cm]adc.center) {};} 
     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
   \& \coordinate (aux1);
   \& \node[draw=none] (yz) {$\hat {Y}(z)$};\\
   \& \coordinate (aux3);
   \&
   \&
   \& 
   \& 
   \& \coordinate (aux2);\\
  };

  \path[->] (v1) edge (q1.north);
  \path[->] (v2) edge (q2.north);
  \path[->] (r) edge (circle.west);
  \path[->] (aux1) edge (yz);
  \path  
   (circle.east) edge (cz)
   (cz.east) edge (q2.west)
   (q2.east) edge (zoh.west)
   (zoh.east) edge (gs.west)
   (switch2) edge (q1.west)
   (q1.east) edge (aux1.west)
   (gs.east) edge (switch1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
% \caption{Closed-loop digital control system \label{fig:sampledsystem}}
\end{figure}

%\end{frame}

%\begin{frame}[fragile]{Discrete Time Model}

\uncover<2->
{
\begin{figure}[ht]
\centering
\tikzset{add/.style n args={4}{
    minimum width=6mm,
    path picture={
        \draw[circle] 
            (path picture bounding box.south east) -- (path picture bounding box.north west)
            (path picture bounding box.south west) -- (path picture bounding box.north east);
        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
        }
    }
 }

\resizebox{1.0\textwidth}{!}{
 \begin{tikzpicture}[scale=0.3,-,>=stealth',shorten >=.2pt,auto,
     semithick, initial text=, ampersand replacement=\&,]

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
    \node[draw=none] (r) {$R(z)$};
%   \& \coordinate (aux0);
   \& \node[circle,add={-}{+}{}{}] (circle) {};
   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Controller}] (cz) {\sc $\hat{C}(z)$};
   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
   \& \node[circle,add={}{+}{+}{}] (circle2) {};
   \node[draw=none] (nu2) at ([yshift=1cm]circle2)  {$\nu_2(z)$};
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc $\hat{G}(z)$}};

   \& \node[circle,add={}{+}{+}{}] (circle3) {};
   \node[draw=none] (nu1) at ([yshift=1cm]circle3)  {$\nu_1(z)$};
   \& \coordinate (aux1);
   \& \node[draw=none] (yz) {$\hat Y(z)$};\\
   \& \coordinate (aux3); 
   \&
   \& 
   \& 
   \&
   \& \coordinate (aux2);\\
  };

  \path[->] (r) edge (circle.west);
  \path[->] (nu2) edge (circle2.north);
  \path[->] (nu1) edge (circle3.north);
  \path[->] (aux1) edge (yz);
  \path  
   (circle.east) edge (cz)
   (cz.east) edge (circle2.west)
   (circle2.east) edge (gs.west)
   (gs.east) edge (circle3.west)
   (circle3.east) edge (aux1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
%\caption{Fully digital equivalent to system in Figure~\ref{fig:sampledsystem} 
%\label{fig:digsystem1}}
\end{figure}
}

\only<2>{
\begin{displaymath}
\label{eq:pulsetf}
\hat{G}(z) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{\hat{G}(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace
\end{displaymath}
}

%\only<2-3>{
%\begin{displaymath}
%\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\tilde{C}(z)R(z)+\hat{G}(z)\nu_{2}(z)-\hat{G}(z)\tilde{C}(z)\hat{Y}(z)
%\end{displaymath}
%}

\only<3>{
\begin{equation*}
\label{eq:outputfunctions}
\hat{Y}(z)=\frac{\nu_{1}(z)}{1+\hat{G}(z) \tilde{C}(z)}+\frac{\nu_{2}(z)\hat{G}(z)}{1+\hat{G}(z) \tilde{C}(z)}+\frac{R(z)\hat{G}(z) \tilde{C}(z)}{1+\hat{G}(z) \tilde{C}(z)}
\end{equation*}
}

\uncover<4>{
Common denominator:
$$\hat{G}_n(z) \tilde{C}_n(z)+\hat{G}_d(z) \tilde{C}_d(z)$$
}

\end{frame}

\begin{frame}{Jury's Criterion}
\begin{equation*}
S(z) = \hat{G}_n(z) \tilde{C}_n(z)+\hat{G}_d(z) \tilde{C}_d(z) = \sum_{i=0}^{N_S} c_iz^{N_s-i}, c_0\neq0. 
\end{equation*}

$$
M=\left( 
\begin{array}{ccc}
v^{(0)}_{1} &\cdots & v^{(0)}_{N_S}\\
v^{(1)}_{1} &\cdots&  v^{(1)}_{N_S}\\
\vdots&\vdots&\vdots\\
v^{(N_S-1)}_{1} &\cdots&  v^{(N_S-1)}_{N_S}\\
\end{array}
\right), $$
%
$$
v_{j}^{(k)}=\left\{
\begin{array}{ll}
c_{j-1}, & k=0\\
0,&k>0 \wedge \mbox{if}~j>N_S-k\\
v_{1}^{(k-1)}-v_{N_S-j}^{(k-1)} . \frac{v_{1}^{(k-1)}}{v_{N_S-k}^{(k-1)}}, &k>0 \wedge  \mbox{if}~j\leq N_S-k\\
\end{array}
\right.
$$
%
$S(z)$ is stable iif:
$$\phi_\mathit{stability} \equiv \textcolor{blue}{S(1) > 0}\ \uncover<2->{\wedge\ \textcolor{blue}{(-1)^{N_S} S(-1) > 0}}\ \uncover<3->{\wedge\ \textcolor{blue}{|c_0| < c_{N_S}}}\ \uncover<4>{\wedge\ \textcolor{blue}{\forall k, v_1^{(k)} > 0}}$$
\end{frame}

\begin{frame}{Transfer Functions and Uncertainty}
\begin{align*}
\small
\label{controller_plant_tf}
\hat{C}(z)&=\frac{\hat{C}_n(z)}{\hat{C}_d(z)}=\frac{\sum_{i=0}^{M_C}(\beta_{i}+\Delta\beta_{i}) z^{-i}}{\sum_{i=0}^{N_C}(\alpha_{i}+\Delta \alpha_{i}) z^{-i}}, \\
\\%\label{plant_tf}
\hat{G}(z)&=\frac{\hat{G}_n(z)}{\hat{G}_d(z)}=\frac{\sum_{i=0}^{M_G}(b_{i}+\Delta b_i) z^{-i}}{\sum_{i=0}^{N_G}(a_{i}+\Delta a_{i}) z^{-i}}.
\end{align*}
%
where $\vec{\beta}$ and $\vec{\alpha}$ are vectors containing the
controller's coefficients and $\vec{b}$ and $\vec{a}$ denote the
plant's coefficients.

\end{frame}

\begin{frame}{Sources of Uncertainty}
\setbeamertemplate{itemize items}[square]
\begin{itemize}
\item<1-> Model Parametric Errors (Affect $\Delta G(z)$)
\item<2-> Quantization Errors in the ADC, DAC, and controller arithmetic. 
(Modelled as external noise. Do not affect the transfer functions)
\item<3-> Roundoff Errors in the verification process (Affect $\Delta S(z)$)
\item<4-> Discretization Errors  (Affect $\Delta G(z)$ and $\Delta C(z)$)
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Pole Placement}

\pgfplotsset{grid style={dotted,gray}}
\pgfplotsset{minor grid style={dotted,gray}}
\pgfplotsset{major grid style={dotted,gray}}

\begin{figure}
\centering
\begin{tikzpicture}[scale=1]
\begin{axis}[xmin=-2.5,xmax=2.5,ymin=-2,ymax=2]
\draw[dashed,color=red] (axis cs:0cm,0cm) circle[radius=100];
\node at (axis cs:.7,-.7) [pin={-10:{stable region}},inner sep=0pt] {};
\draw[color=blue] (axis cs:0.5,0.7) ellipse[x radius=5, y radius=15];
\node at (axis cs:.5,.7) [pin={+10:poles},inner sep=0pt] {};
\end{axis}
\end{tikzpicture}
\end{figure}
\end{frame}

%\begin{frame}[fragile]
%\begin{figure}
%\centering
%\begin{tikzpicture}[scale=1]
%\begin{axis}[xmin=-2.5,xmax=2.5,ymin=-2,ymax=2, minor xtick={-2,-1.75, ..., 2}, minor ytick={-2,-1.75, ..., 2}, grid=both]
%\draw[dashed,color=red] (axis cs:0cm,0cm) circle[radius=100];
%\node at (axis cs:.7,-.7) [pin={-10:stable},inner sep=0pt] {};
%\only<1>{
%\draw[color=blue] (axis cs:0.5,0.7)  ellipse[x radius=5, y radius=15];
%\node at (axis cs:.5,.7) [pin={+10:poles},inner sep=0pt] {};
%}
%\only<2>{
%\draw[color=orange] (axis cs:0.5,0.75) ellipse[x radius=5, y radius=15];
%\node at (axis cs:.5,.75) [pin={+10:poles},inner sep=0pt] {};
%}
%\end{axis}
%\end{tikzpicture}
%\end{figure}
%\end{frame}

\begin{frame}[fragile]{Pole Placement}
\begin{figure}
\centering
\begin{tikzpicture}[scale=1]
\begin{axis}[xmin=0,xmax=1.5,ymin=0,ymax=1]
\draw[dashed,color=red] (axis cs:0cm,0cm) circle[radius=100];
\node at (axis cs:.7,-.7) [pin={-10:stable},inner sep=0pt] {};
\draw[color=blue] (axis cs:0.5,0.7) ellipse[x radius=5, y radius=15];
\node at (axis cs:.5,.7) [pin={+10:poles},inner sep=0pt] {};
\end{axis}
\end{tikzpicture}
\end{figure}
\end{frame}

\begin{frame}[fragile]{Pole Placement in a Discretized Domain}

\pgfplotsset{grid style={dotted,gray}}
\pgfplotsset{minor grid style={dotted,gray}}
\pgfplotsset{major grid style={dotted,gray}}

\begin{figure}
\centering
\begin{tikzpicture}[scale=1]
\begin{axis}[xmin=0,xmax=1.25,ymin=0,ymax=1, xtick={0,0.25, ..., 1.25}, ytick={0,0.25, ..., 1.25}, grid=both]
\draw[dashed,color=red] (axis cs:0cm,0cm) circle[radius=100];
\node at (axis cs:.7,-.7) [pin={-10:stable},inner sep=0pt] {};
\only<1>{
\draw[color=blue] (axis cs:0.5,0.7)  ellipse[x radius=5, y radius=15];
\node at (axis cs:.5,.7) [pin={+10:poles},inner sep=0pt] {};
}
\only<2>{
\draw[color=orange] (axis cs:0.5,0.75) ellipse[x radius=5, y radius=15];
\node at (axis cs:.5,.75) [pin={+10:poles},inner sep=0pt] {};
}
\end{axis}
\end{tikzpicture}
\end{figure}
\end{frame}

%
\begin{frame}{Our Objective}
We seek to synthesise a controller where $\Delta \vec{\beta}=0$ and $\Delta \vec{\alpha}=0$ and which stabilizes all plants within a given range of $\Delta \vec{b}$ and $\Delta \vec{a}$.
\end{frame}

\begin{frame}[fragile]{Our CEGIS Model}
\begin{figure}[htb]
\centering
\resizebox{1.0\textwidth}{!}
{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=7cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc Verify},] (verif) {};
     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc Uncertainty}};
     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=2cm]verif.center) {{\sc Precision}};
   } 
   \only<1,22>{\& \node[ellipse, fill=gray!20] (done) {{\sc Done}};}\\
   \& \\
   \node[minimum height=0.5cm] (gp) {\sf Closed-loop System Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node[minimum height=0.5cm] (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based\\Verifier};
   \node[minimum height=0.5cm] (fp)  at ([xshift=2cm]aux.center) {\sf Interval Arithmetic\\Verifier};
   }   
    \\
  };

   \only<1,22>{\path (verif2) edge node {} (done);}
   \only<1>{\path ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north);}
   \only<2-7,16-17>{\path ([xshift=5em]synth.south) edge node[align=center] {$\textcolor{blue}{\frac{0.0264}{z-0.9998}}$} ([xshift=5em]gp.north);}
   \only<1-2,8,16,18>{\path ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south);}
   \only<3-7,17>{\path ([xshift=-5em]gp.north) edge node[align=center] {$\textcolor{blue}{\frac{0z^2+0z+0}{0z^2+0z+0}}$} ([xshift=-5em]synth.south);}
   \only<1-3,8-9,16,18>{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {Candidate solution} ([yshift=2em]verif1.west);}
   \only<4-7,17>{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {$\textcolor{blue}{\frac{0z^2+0z+0}{0z^2+0z+0}}$} ([yshift=2em]verif1.west);}
   \only<1-4,8-10,16,18-19>{\path  ([xshift=5em]verif1.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]bmc.north);}
   \only<5-7,17>{\path  ([xshift=5em]verif1.south) edge node[align=center] {$\textcolor{blue}{\frac{0z^2+0z+0}{0z^2+0z+0}}$} ([xshift=5em]bmc.north);}
   \only<1-5,8-11,16,18-19>{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south);}
   \only<6-7>{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([xshift=-5em]verif1.south);}
   \only<1-6,8-12,16,18>{\path ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east);}
   \only<7>{\path ([yshift=-2em]verif1.west) edge node {$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([yshift=-2em]synth.east);}
   \only<8-15>{\path ([xshift=5em]synth.south) edge node[align=center] {$\textcolor{blue}{\frac{0.0264}{z-0.9998}}$\\$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([xshift=5em]gp.north);}
   \only<9-15,19->{\path ([xshift=-5em]gp.north) edge node[align=center] {$\textcolor{blue}{\tilde C(z)}$} ([xshift=-5em]synth.south);}
   \only<10-15>{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {$\textcolor{blue}{\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}}$} ([yshift=2em]verif1.west);}
   \only<11-15,20->{\path  ([xshift=5em]verif1.south) edge node[align=center] {$\textcolor{blue}{\tilde C(z)}$} ([xshift=5em]bmc.north);}
   \only<12-15,20->{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {\textcolor{blue}{UNSAT}\\\textcolor{blue}{Pass}} ([xshift=-5em]verif1.south);}
   \only<1-12,16-20>{\path ([xshift=5em]verif2.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]fp.north);}
   \only<13-15,21->{\path ([xshift=5em]verif2.south) edge node[align=center] {$\textcolor{blue}{\tilde C(z)}$} ([xshift=5em]fp.north);}
   \only<1-13,16-20>{\path  ([xshift=-5em]fp.north) edge node[align=center]  {True/\\False} ([xshift=-5em]verif2.south);}
   \only<14-15>{\path  ([xshift=-5em]fp.north) edge node[align=center]  {\textcolor{blue}{False}} ([xshift=-5em]verif2.south);}
   \only<15>{\path ([yshift=-2em]verif1.west) edge node {\textcolor{blue}{precision}} ([yshift=-2em]synth.east);}
   \only<17>{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {$\textcolor{blue}{\frac{0.026314}{0.999024z{-}1.004785}}$} ([xshift=-5em]verif1.south);}
   \only<17>{\path ([yshift=-2em]verif1.west) edge node {$\textcolor{blue}{\frac{0.026314}{0.999024z{-}1.004785}}$} ([yshift=-2em]synth.east);}
   \only<18->{\path ([xshift=5em]synth.south) edge node[align=center] {$\textcolor{blue}{\frac{0.0264}{z-0.9998}}$\\$\textcolor{blue}{\frac{0.026314}{0.999024z{-}1.004785}}$} ([xshift=5em]gp.north);}
   \only<19->{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {$\textcolor{blue}{\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}}$} ([yshift=2em]verif1.west);}
   \only<21->{\path  ([xshift=-5em]fp.north) edge node[align=center]  {\textcolor{blue}{True}} ([xshift=-5em]verif2.south);}

   \path (aux1) edge (synth.north);
   \path[-]
   (verif2.north) edge node[align=center] {} ([xshift=6.7cm]aux2)
   ([xshift=6.7cm]aux2) edge node[align=center] {Increase Precision} (aux1);

 \end{tikzpicture}
}
\end{figure}
\end{frame}

%\begin{frame}
%
%\begin{itemize*}
%
%\item We automatically generate {\em correct-by-construction} digital
%  controllers using an inductive synthesis approach.  Our application of program
%  synthesis is non-trivial and addresses challenges specific to control
%  systems, such as quantizers and FWL.  In particular, we
%  have found that a two-stage verification engine that continuously refines
%  the precision of the fixed-point representation of the plant yields a
%  speed-up of two orders of magnitude over a conventional one-stage
%  verification engine.
%
%\item Experimental results show that \tool is able to efficiently synthesize
%  stable controllers for a set of intricate benchmarks taken from the
%  literature: the median runtime for our benchmark set considering the
%  faster engine is $48$\,s, i.e., half of the controllers can be synthesized
%  in less than one minute.
%
%\end{itemize*}
%\end{frame}

%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Illustrative Example} \label{sec:running-ex}
%
%We illustrate our approach with a classical cruise control example from the
%literature~\cite{Astrom08}.  It highlights the challenges that
%arise when using finite-precision arithmetic in digital control.  We are
%given a discrete plant model (with a time step of $0.2$\,s), 
%represented by the following $z$-expression:
%%
%\begin{equation}
%\label{Eq:running-example-plant}
%G(z) = \frac{0.0264}{z-0.9998}.
%\end{equation}
%
%Using an optimization tool, the authors
%of~\cite{DBLP:conf/hybrid/WangGRJF16} have designed a high-performance
%controller for this plant, which is characterized by the following
%$z$-domain transfer function:
%%
%\begin{equation}
%\label{Eq:running-example-controller}
%C(z) = \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
%\end{equation}
%%
%The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that the controller
%$C(z)$ in~\eqref{Eq:running-example-controller} stabilizes the closed-loop
%system for the discrete plant model $G(z)$
%in~\eqref{Eq:running-example-plant}.  However, if the effects of
%finite-precision arithmetic are considered, then this closed-loop system
%becomes unstable.
%%
%For instance, an implementation of $C(z)$ using 
%$\mathbb R \param {4}{16}$ fixed-point
%numbers (i.e., $4$ bits for the integer part and $16$ bits for the
%fractional part) can be modeled as: 
%%
%\begin{equation}
%\label{Eq:running-example-controller-quantized}
%\resizebox{.47\textwidth}{!}{
%$\tilde{C}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
%{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$. 
%}
%\end{equation} 
%%
%The resulting system, 
%%using the typical series loop configuration, 
%where $\tilde{C}(z)$ and $G(z)$ are in the forward path, is unstable. 
%Notice that this is disregarding further approximation effects on the plant caused by quantization in the verifier (i.e., $\tilde{G}(z)$).
%%\aabatecmt{[hang in there - did we not consider FWL on $G(z)$? why not?]}
%%\dariocmt{we are explaining the case where a real plant (no FWL) is not correctly stabilized by $\tilde{C}$, so although our analysis might evaluate $\tilde{G}(z)$, the problem statement is over $G(z)$}
%Figure~\ref{fig:original} gives the Bode diagram for the digital controller
%represented in~\eqref{Eq:running-example-controller}: 
%as the phase margin is negative, 
%the controller is unstable when considering the FWL effects.
%
%
\begin{frame}[fragile]{Step Response for the Candidate Solutions}
\begin{figure}
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_step0.pdf}
        \caption{Original controller}
        \label{fig:step0}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_step1.pdf}
        \caption{First solution by \tool}
        \label{fig:step1}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/runningexample_step2.pdf}
        \caption{Final solution by \tool}
        \label{fig:step2}
    \end{subfigure}
\end{figure}
The Original Controller was synthesised ignoring FWL effects and as can be seen, it becomes unstable over time.
\end{frame}
%
\begin{frame}[fragile]{Synthesised Results}
\begin{figure}
 \begin{tikzpicture}
\begin{axis}[ylabel=order,xlabel=time,xmode=log
]
\addplot[scatter,only marks,mark=*] table{./results.dat};
\end{axis}
\end{tikzpicture}
\end{figure}
\end{frame}

\begin{frame}[fragile]{Synthesised Results}

\begin{table}
\centering
\scalebox{0.6}{
\begin{tabular}{| r | c | l | r r || r | r |}
\hline
\# & Plant  & Benchmark                  & $I$ & $F$
   & 2-stage & 1-stage
    \\\hline\hline
1  & $G_{1a}$  & CruiseControl02
            &   4 &  16 & \textbf{12\,s}   & 67\,s     \\
2  & $G_{1b}$  & CruiseControl02$^\dagger$
            &   4 &  16 & 14600\,s   & \textbf{52\,s}     \\
3  & $G_{2a}$  & SpgMsDamper
            &  15 &  16 & \textbf{52\,s}   & 318\,s     \\
4  & $G_{2b}$  & SpgMsDamper$^\dagger$
            &  15 &  16 & \xmark  & \xmark    \\
5  & $G_{3a}$  & SatelliteB2
            &   3 &   7 & \textbf{36\,s}    & \xmark     \\
6  & $G_{3b}$  & SatelliteB2$^\dagger$
            &   3 &   7 & \xmark  & \textbf{4111\,s}  \\
7  & $G_{3c}$  & SatelliteC2
            &   3 &   5 & \textbf{3\,s}    & 205\,s    \\
8  & $G_{3d}$  & SatelliteC2$^\dagger$
            &   3 &   5 & \textbf{50\,s}  & 1315\,s    \\
9  & $G_4$  & Cruise
            &   3 &   7 & 1\,s  & 1\,s    \\
10 & $G_5$  & DCMotor
            &   3 &   7 & \textbf{1\,s}  & 10\,s    \\
11 & $G_6$  & DCServomotor
            &   4 &  11 & \textbf{46\,s}  & \xmark    \\
12 & $G_7$  & Doyleetal
            &   4 &  11 & \textbf{8769\,s}  & \xmark    \\
13 & $G_8$  & Helicopter
            &   3 &   7 & \textbf{44\,s}  & \xmark    \\
14 & $G_9$  & Pendulum
            &   3 &   7 & \textbf{1\,s}  & 14826\,s    \\
15 &$G_{10}$& Suspension
            &   3 &   7 & \textbf{1\,s}  & 5\,s    \\
16 &$G_{11}$& Tapedriver
            &   3 &   7 & 1\,s  & 1\,s    \\
17 &$G_{12a}$& a\_ST1\_IMPL1
            &  16 &   4 & \textbf{11748\,s} & \xmark   \\
18 &$G_{12a}$& a\_ST1\_IMPL2
            &  16 &   8 & \textbf{351\,s}  & \xmark   \\
19 &$G_{12a}$& a\_ST1\_IMPL3
            &  16 &  12 & \textbf{8772\,s}   & \xmark   \\
20 &$G_{12b}$& a\_ST2\_IMPL1
            &  16 &   4 & \textbf{1128\,s}  & \xmark   \\
21 &$G_{12b}$& a\_ST2\_IMPL2
            &  16 &   8 & \xmark  & \xmark    \\
22 &$G_{12b}$& a\_ST2\_IMPL3
            &  16 &  12 & \textbf{15183\,s} & \xmark   \\ 
23 &$G_{12c}$& a\_ST3\_IMPL1
            &  16 &   4 & \xmark & \xmark   \\\hline
\end{tabular}}\\[0.2ex]
\caption{\tool results ({\xmark} = time-out, $\dagger$ = 
uncertainty)
\label{tab:results}}
\end{table}
\end{frame}

\begin{frame}{Conclusions}
\begin{itemize}
\item We have presented a method for automatically synthesizing stable and sound controllers, implemented
in a tool called \tool.
\item \tool marks the first use of the
CEGIS that handles plants with uncertain models and FWL effects over the
digital controller.  
\item Our experimental results show that \tool is able to synthesize
stable controllers for most benchmarks within a reasonable amount of time.  
\item Future work will extend this CEGIS-based
approach to LTI systems with state space safety specifications. 
\end{itemize}
\end{frame}
\end{document}

### 2017-03-10 slides/presentation.tex
presentation improvements

@@
 
-\begin{frame}[fragile]{Hybrid Dynamical System}{Continuous Plant and Digital Controller}
+\begin{frame}[fragile]{Cyberphysical System}{Continuous Plant and Digital Controller}
 
@@
 
+ \only<1>{
+ \& \node[rectangle,draw,minimum width=3cm,
+	minimum height=1.6cm,] (bbdac) {\sc DAC};
+ }
+ \only<2->{
    \& complexnode/.pic={ 
       \node[rectangle,draw,
-	minimum width=3cm,
+	minimum width=4cm,
 	minimum height=1.6cm,
@@
      \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};} 
+     }
    \& \node[rectangle,draw,
@@
    \node[draw=none] (y) at ([xshift=1cm,yshift=.2cm]gs)  {$\hat{Y}(s)$};
+ \only<1>{
+ \& \node[rectangle,draw,minimum width=4cm,
+	minimum height=1.6cm,] (bbadc) {\sc ADC};
+ }   
+ \only<2->{
    \& complexnode/.pic={ 
@@
    \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
+   }
    \& \coordinate (aux1);
@@
 
-  \path[->] (v1) edge (q1.north);
-  \path[->] (v2) edge (q2.north);
   \path[->] (r) edge (circle.west);
   \path[->] (aux1) edge (yz);
+  \path (circle.east) edge (cz);
+  \only<1> {
    \path
-   (circle.east) edge (cz)
+     (cz.east) edge (bbdac.west)
+     (bbdac.east) edge (gs.west);
+   \path
+      (gs.east) edge (bbadc.west)
+      (bbadc.east) edge (aux1.west);
+  }
+   \only<2->{
+  \path[->] (v2) edge (q2.north);
+  \path  
    (cz.east) edge (q2.west)
    (q2.east) edge (zoh.west)
-   (zoh.east) edge (gs.west)
+   (zoh.east) edge (gs.west);
+  \path[->] (v1) edge (q1.north);
+  \path
+   (gs.east) edge (switch1.west)
    (switch2) edge (q1.west)
-   (q1.east) edge (aux1.west)
-   (gs.east) edge (switch1.west)
+   (q1.east) edge (aux1.west);
+  }
+  \path
    (aux1.south) edge (aux2.north)
@@
 
-\uncover<2->
+\uncover<3->
 {
@@
 
-\only<2>{
+\only<4>{
 \begin{displaymath}
@@
 
-\only<3>{
+\only<5>{
 \begin{equation*}
@@
 
-\uncover<4>{
+\uncover<6>{
 Common denominator:
@@
    \& \\
-   \node[minimum height=0.5cm] (gp) {\sf Closed-loop System Search};
+   \node[minimum height=0.5cm] (gp) {\sf Closed-loop System Search\\ \only<2-15>{$\textcolor{blue}{FP=\mathbb{R}\langle16,24\rangle}$}\only<16->{$\textcolor{blue}{FP=\mathbb{R}\langle20,28\rangle}$}};
    \&

### 2017-03-13 slides/presentation.tex
pres

@@
 
-\title {Sound and Automated Synthesis of Digital
-Stabilizing Controllers for Continuous Plants}
+\title {Sound and Automated Synthesis of Digital Controllers for Continuous Plants}
 
@@
 
+\date{March 2017}
+
 \frame{\maketitle}
 
-\begin{frame}{\tool}
+\begin{frame}{Cyber-Physical Systems}
 %
-Modern control is implemented with digital microcontrollers, embedded within
-a dynamical plant that represents physical components.
+\begin{itemize}
+\item 
+modern controls are implemented with digital microcontrollers, 
+embedded within dynamical plants representing physical components 
+\end{itemize}
+
 \begin{figure}
@@
     \end{subfigure}
+%     ~
+%    \begin{subfigure}[b]{0.3\textwidth}
+%        \includegraphics[width=\textwidth]{figures/step1_figureD.png}
+%    \end{subfigure}
     ~
     \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{figures/step1_figureD.png}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.15\textwidth}
         \includegraphics[width=\textwidth]{figures/step1_figureA.png}

### 2017-03-13 slides/presentation.tex
pres

@@
 
-\begin{frame}{Cyber-Physical Systems}
-%
+\begin{frame}{Cyber-Physical Systems (CPS)}
+
 \begin{itemize}
@@
 embedded within dynamical plants representing physical components 
+\item 
+digital control literature: success and limitations 
 \end{itemize}
@@
 
-\tool uses counter\-example guided inductive
-synthesis to automate the design of digital controllers that are
-correct by construction.
-%
+\pause
+
+\begin{itemize}
+\item 
+use of counter\-example guided inductive synthesis (CEGIS)\\ 
+to automate design of sound digital controllers 
+\end{itemize}
+
 \end{frame}
 
-\begin{frame}[fragile]{Cyberphysical System}{Continuous Plant and Digital Controller}
+\begin{frame}[fragile]{CPS Setup: Continuous Plant and Digital Controller}
 
@@
 \begin{displaymath}
-\label{eq:pulsetf}
 \hat{G}(z) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{\hat{G}(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace
@@
 \begin{equation*}
-\label{eq:outputfunctions}
-\hat{Y}(z)=\frac{\nu_{1}(z)}{1+\hat{G}(z) \tilde{C}(z)}+\frac{\nu_{2}(z)\hat{G}(z)}{1+\hat{G}(z) \tilde{C}(z)}+\frac{R(z)\hat{G}(z) \tilde{C}(z)}{1+\hat{G}(z) \tilde{C}(z)}
+\hat{Y}(z) = 
+\frac{\hat{G}(z) \tilde{C}(z)}{1+\hat{G}(z) \tilde{C}(z)}R(z) + 
+\frac{1}{1+\hat{G}(z) \tilde{C}(z)} \nu_{1}(z) + 
+\frac{\hat{G}(z)}{1+\hat{G}(z) \tilde{C}(z)} \nu_{2}(z) 
 \end{equation*}
@@
 $$\hat{G}_n(z) \tilde{C}_n(z)+\hat{G}_d(z) \tilde{C}_d(z)$$ 
+\textcolor{red}{clarify use of tilde C and of hat C }
 }

### 2017-03-13 slides/presentation.tex
pres

@@
 
-\begin{frame}{Jury's Criterion}
+\begin{frame}{Stability Analysis via Jury's Criterion}
+
 \begin{equation*}
-S(z) = \hat{G}_n(z) \tilde{C}_n(z)+\hat{G}_d(z) \tilde{C}_d(z) = \sum_{i=0}^{N_S} c_iz^{N_s-i}, c_0\neq0. 
+S(z) = \hat{G}_n(z) \tilde{C}_n(z)+\hat{G}_d(z) \tilde{C}_d(z) = \sum_{i=0}^{N_S} c_iz^{N_s-i}, c_0 \neq 0 
 \end{equation*}
@@
 %
-$S(z)$ is stable iif:
-$$\phi_\mathit{stability} \equiv \textcolor{blue}{S(1) > 0}\ \uncover<2->{\wedge\ \textcolor{blue}{(-1)^{N_S} S(-1) > 0}}\ \uncover<3->{\wedge\ \textcolor{blue}{|c_0| < c_{N_S}}}\ \uncover<4>{\wedge\ \textcolor{blue}{\forall k, v_1^{(k)} > 0}}$$
+$S(z)$ is stable $\Leftrightarrow$
+$$
+%\phi_\mathit{stability} \equiv 
+\textcolor{blue}{S(1) > 0}\ \uncover<2->{\wedge\ \textcolor{blue}{(-1)^{N_S} S(-1) > 0}}\ \uncover<3->{\wedge\ \textcolor{blue}{|c_0| < c_{N_S}}}\ \uncover<4>{\wedge\ \textcolor{blue}{\forall k, v_1^{(k)} > 0}}
+$$
+
 \end{frame}
@@
 \begin{frame}{Transfer Functions and Uncertainty}
+
 \begin{align*}
 \small
-\label{controller_plant_tf}
 \hat{C}(z)&=\frac{\hat{C}_n(z)}{\hat{C}_d(z)}=\frac{\sum_{i=0}^{M_C}(\beta_{i}+\Delta\beta_{i}) z^{-i}}{\sum_{i=0}^{N_C}(\alpha_{i}+\Delta \alpha_{i}) z^{-i}}, \\
@@
 %
-where $\vec{\beta}$ and $\vec{\alpha}$ are vectors containing the
-controller's coefficients and $\vec{b}$ and $\vec{a}$ denote the
-plant's coefficients.
+\begin{itemize}
+\item 
+$\vec{\beta}$ and $\vec{\alpha}$ -- vectors containing controller coefficients 
+\item 
+$\vec{b}$ and $\vec{a}$ -- plant coefficients 
+\end{itemize}
 
@@
 \setbeamertemplate{itemize items}[square]
+
 \begin{itemize}
-\item<1-> Model Parametric Errors (Affect $\Delta G(z)$)
-\item<2-> Quantization Errors in the ADC, DAC, and controller arithmetic. 
-(Modelled as external noise. Do not affect the transfer functions)
-\item<3-> Roundoff Errors in the verification process (Affect $\Delta S(z)$)
-\item<4-> Discretization Errors  (Affect $\Delta G(z)$ and $\Delta C(z)$)
+\item<1->[1.] Model Parametric Errors (affect $\Delta G(z)$)
+\item<2->[2.] Quantisation errors in the ADC, DAC, and controller arithmetics  
+(modelled as external noise, do not affect transfer functions)
+\item<3->[3.] Roundoff errors in verification process (affect $\Delta S(z)$)
+\item<4->[4.] Discretisation errors (affect $\Delta G(z)$ and $\Delta C(z)$) 
 \end{itemize}
@@
 \begin{frame}{Our Objective}
+
 We seek to synthesise a controller where $\Delta \vec{\beta}=0$ and $\Delta \vec{\alpha}=0$ and which stabilizes all plants within a given range of $\Delta \vec{b}$ and $\Delta \vec{a}$.
+
 \end{frame}
 
-\begin{frame}[fragile]{Our CEGIS Model}
+\begin{frame}[fragile]{CEGIS Architecture}
 \begin{figure}[htb]

### 2017-03-13 slides/presentation.tex
pres

@@
 %
-$S(z)$ is stable $\Leftrightarrow$
-$$
+\begin{eqnarray*}
+&S(z) \text{ is stable } \Leftrightarrow& \\ 
 %\phi_\mathit{stability} \equiv 
-\textcolor{blue}{S(1) > 0}\ \uncover<2->{\wedge\ \textcolor{blue}{(-1)^{N_S} S(-1) > 0}}\ \uncover<3->{\wedge\ \textcolor{blue}{|c_0| < c_{N_S}}}\ \uncover<4>{\wedge\ \textcolor{blue}{\forall k, v_1^{(k)} > 0}}
-$$
+&\textcolor{blue}{S(1) > 0}\ \uncover<2->{\wedge\ \textcolor{blue}{(-1)^{N_S} S(-1) > 0}}\ \uncover<3->{\wedge\ \textcolor{blue}{|c_0| < c_{N_S}}}\ \uncover<4>{\wedge\ \textcolor{blue}{\forall k, v_1^{(k)} > 0}}&
+\end{eqnarray*}
 
@@
 %
-\begin{frame}{Our Objective}
+\begin{frame}{Objective}
 
 We seek to synthesise a controller where $\Delta \vec{\beta}=0$ and $\Delta \vec{\alpha}=0$ and which stabilizes all plants within a given range of $\Delta \vec{b}$ and $\Delta \vec{a}$.
+
+\textcolor{red}{Copy here CEGIS architecture scheme.}
+
+\end{frame}
+
+\begin{frame}{Case Study}
+
+\textcolor{red}{Introduce details of case study. }
 
@@
 %the controller is unstable when considering the FWL effects.
-%
-%
-\begin{frame}[fragile]{Step Response for the Candidate Solutions}
+
+\begin{frame}[fragile]{Outcomes: Step Response}
 \begin{figure}
@@
         \includegraphics[width=\textwidth]{figures/runningexample_step0.pdf}
-        \caption{Original controller}
+        \caption{Original\\ controller}
         \label{fig:step0}
@@
         \includegraphics[width=\textwidth]{figures/runningexample_step1.pdf}
-        \caption{First solution by \tool}
+        \caption{Controller (first step)}
         \label{fig:step1}
@@
         \includegraphics[width=\textwidth]{figures/runningexample_step2.pdf}
-        \caption{Final solution by \tool}
+        \caption{Controller (final step)}
         \label{fig:step2}
@@
 \end{figure}
-The Original Controller was synthesised ignoring FWL effects and as can be seen, it becomes unstable over time.
+
+\begin{itemize} 
+\item 
+original controller was synthesised ignoring FWL effects (becomes unstable over time) 
+\end{itemize}
+
 \end{frame}
-%
-\begin{frame}[fragile]{Synthesised Results}
+
+\begin{frame}[fragile]{Outcomes: Controller Order}
 \begin{figure}
@@
 
-\begin{frame}[fragile]{Synthesised Results}
+\begin{frame}[fragile]{Outcomes: Benchmark}
 

### 2017-03-14 slides/presentation.tex
fixes to slides

@@
 \newcommand{\xmark}{\ding{55}}
+\newcommand{\mat}[1]{\boldsymbol{#1}}
+\newcommand{\cavslides}[1]{#1}
 
@@
 %\begin{displaymath}
-%\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\tilde{C}(z)R(z)+\hat{G}(z)\nu_{2}(z)-\hat{G}(z)\tilde{C}(z)\hat{Y}(z)
+%\hat{Y}(z)=\nu_{1}(z)+\hat{G}(z)\hat{C}(z)R(z)+\hat{G}(z)\nu_{2}(z)-\hat{G}(z)\hat{C}(z)\hat{Y}(z)
 %\end{displaymath}
@@
 \hat{Y}(z) = 
-\frac{\hat{G}(z) \tilde{C}(z)}{1+\hat{G}(z) \tilde{C}(z)}R(z) + 
-\frac{1}{1+\hat{G}(z) \tilde{C}(z)} \nu_{1}(z) + 
-\frac{\hat{G}(z)}{1+\hat{G}(z) \tilde{C}(z)} \nu_{2}(z) 
+\frac{\hat{G}(z) \hat{C}(z)}{1+\hat{G}(z) \hat{C}(z)}R(z) + 
+\frac{1}{1+\hat{G}(z) \hat{C}(z)} \nu_{1}(z) + 
+\frac{\hat{G}(z)}{1+\hat{G}(z) \hat{C}(z)} \nu_{2}(z) 
 \end{equation*}
@@
 Common denominator:
-$$\hat{G}_n(z) \tilde{C}_n(z)+\hat{G}_d(z) \tilde{C}_d(z)$$ 
-\textcolor{red}{clarify use of tilde C and of hat C }
+$$\hat{G}_n(z) \hat{C}_n(z)+\hat{G}_d(z) \hat{C}_d(z)$$ 
 }
@@
 \begin{equation*}
-S(z) = \hat{G}_n(z) \tilde{C}_n(z)+\hat{G}_d(z) \tilde{C}_d(z) = \sum_{i=0}^{N_S} c_iz^{N_s-i}, c_0 \neq 0 
+S(z) = \hat{G}_n(z) \hat{C}_n(z)+\hat{G}_d(z) \hat{C}_d(z) = \sum_{i=0}^{N_S} c_iz^{N_s-i}, c_0 \neq 0 
 \end{equation*}
@@
 
-\textcolor{red}{Introduce details of case study. }
+Take a classical cruise control example from the literature. 
+%
+\begin{equation*}
+G(z) = \frac{0.0264}{z-0.9998}.
+\end{equation*}
+
+Using an optimization tool, the following stable high-performance
+controller was designed:
+%
+\begin{equation*}
+C(z) = \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
+\end{equation*}
+%
+However, if we implement the controller in $\mathbb{R} \langle 4,16\rangle$.
+%
+\begin{equation*}
+\resizebox{.9\textwidth}{!}{
+$\tilde{C}(z) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
+{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375}$. 
+}
+\end{equation*} 
+%
+where $\tilde{C}(z)$ is the controller adjusted to the FWL. The resulting system is unstable.
 
@@
    \only<6-7>{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([xshift=-5em]verif1.south);}
-   \only<1-6,8-12,16,18>{\path ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east);}
+   \only<1-6,8-12,16,18-19>{\path ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east);}
    \only<7>{\path ([yshift=-2em]verif1.west) edge node {$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([yshift=-2em]synth.east);}
    \only<8-15>{\path ([xshift=5em]synth.south) edge node[align=center] {$\textcolor{blue}{\frac{0.0264}{z-0.9998}}$\\$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([xshift=5em]gp.north);}
-   \only<9-15,19->{\path ([xshift=-5em]gp.north) edge node[align=center] {$\textcolor{blue}{\tilde C(z)}$} ([xshift=-5em]synth.south);}
+   \only<9-15,19->{\path ([xshift=-5em]gp.north) edge node[align=center] {$\textcolor{blue}{\hat{C}(z)}$} ([xshift=-5em]synth.south);}
    \only<10-15>{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {$\textcolor{blue}{\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}}$} ([yshift=2em]verif1.west);}
-   \only<11-15,20->{\path  ([xshift=5em]verif1.south) edge node[align=center] {$\textcolor{blue}{\tilde C(z)}$} ([xshift=5em]bmc.north);}
+   \only<11-15,20->{\path  ([xshift=5em]verif1.south) edge node[align=center] {$\textcolor{blue}{\hat{C}(z)}$} ([xshift=5em]bmc.north);}
    \only<12-15,20->{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {\textcolor{blue}{UNSAT}\\\textcolor{blue}{Pass}} ([xshift=-5em]verif1.south);}
    \only<1-12,16-20>{\path ([xshift=5em]verif2.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]fp.north);}
-   \only<13-15,21->{\path ([xshift=5em]verif2.south) edge node[align=center] {$\textcolor{blue}{\tilde C(z)}$} ([xshift=5em]fp.north);}
+   \only<13-15,21->{\path ([xshift=5em]verif2.south) edge node[align=center] {$\textcolor{blue}{\hat{C}(z)}$} ([xshift=5em]fp.north);}
    \only<1-13,16-20>{\path  ([xshift=-5em]fp.north) edge node[align=center]  {True/\\False} ([xshift=-5em]verif2.south);}
    \only<14-15>{\path  ([xshift=-5em]fp.north) edge node[align=center]  {\textcolor{blue}{False}} ([xshift=-5em]verif2.south);}
-   \only<15>{\path ([yshift=-2em]verif1.west) edge node {\textcolor{blue}{precision}} ([yshift=-2em]synth.east);}
+   %\only<15>{\path ([yshift=-2em]verif1.west) edge node {\textcolor{blue}{precision}} ([yshift=-2em]synth.east);}
    \only<17>{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {$\textcolor{blue}{\frac{0.026314}{0.999024z{-}1.004785}}$} ([xshift=-5em]verif1.south);}
@@
    \path (aux1) edge (synth.north);
-   \path[-]
-   (verif2.north) edge node[align=center] {} ([xshift=6.7cm]aux2)
-   ([xshift=6.7cm]aux2) edge node[align=center] {Increase Precision} (aux1);
-
+   \path[-] (verif2.north) edge node[align=center] {} ([xshift=6.7cm]aux2);
+   \only<1-14,16-> {\path[-] ([xshift=6.7cm]aux2) edge node[align=center] {Increase Precision} (aux1);}
+   \only<15> {\path[-] ([xshift=6.7cm]aux2) edge node[align=center] {\textcolor{blue}{Increase Precision}} (aux1);}
  \end{tikzpicture}
@@
 \end{frame}
+
+\begin{frame}[fragile]{LTI Closed Loop System}
+\begin{figure}[htb]
+\centering
+
+\tikzset{add/.style n args={4}{
+    minimum width=6mm,
+    path picture={
+        \draw[circle] 
+            (path picture bounding box.south east) -- (path picture bounding box.north west)
+            (path picture bounding box.south west) -- (path picture bounding box.north east);
+        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+        }
+    }
+ }
+
+\resizebox{1.0\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
+     semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
+    \node[draw=none] (r) {$r_k$};
+
+   \& \node[circle,add={-}{+}{\only<3>{+}}{}] (circle) {};
+   \only<3>{\node[draw=none] (v12) at ([xshift=0cm,yshift=1cm]circle)  {$\nu_2-\mat{K}_d\nu_1+\nu_3$};}
+   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$u_k$};
+   \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Kd) at ([xshift=0,yshift=-1.5cm]circle)  {\sc $\mat{K}_d$};
+   \coordinate (kdsouth) at ([yshift=-2cm]Kd);
+
+\only<1>{
+ \& \node[rectangle,draw,minimum width=3cm,
+	minimum height=1.6cm,] (bbdac) {\sc DAC};
+ }
+
+\only<2>{   
+   \& complexnode/.pic={ 
+     \node[rectangle,dashed,draw,minimum width=3cm,minimum height=1.6cm,label=\textbf{DAC}] (dac) {};
+     \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
+     \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
+     \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
+     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {\sc ZOH};
+   }   
+}
+
+   \& complexnode/.pic={ 
+      \only<1-2>{\node[rectangle,dashed,draw,minimum width=6.5cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};}
+      \only<3>{\node[rectangle,dashed,draw,minimum width=6.5cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.75cm]dac.center) {};}
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2cm,yshift=.5cm]plant.center)  {\sc \only<1-2>{$\mat{B}$}\only<3>{$\mat{B}_d$}};
+      \node[draw=none] (u) at ([xshift=-.8cm,yshift=.15cm]B)  {\only<1-2>{$u(t)$}};
+      \node[circle,add={+}{+}{}{}] (p1) at ([xshift=-0.6cm,yshift=.5cm]plant.center) {};
+      \node[draw=none] (xdot) at ([xshift=.9cm,yshift=.2cm]p1)  {\only<1-2>{$\dot{\mat{x}}(t)$}\only<3>{$\mat{x}_{k+1}$}};   
+      \node[rectangle,draw,minimum width=1cm] (int) at ([xshift=1.2cm,yshift=.5cm]plant.center) {\sc \only<1-2>{$\int$}\only<3>{$Z^{-1}$}};
+      \coordinate (xsouth) at ([xshift=1cm]int);
+      \node[draw=none] (x) at ([xshift=1.2cm,yshift=.15cm]int)  {\only<1-2>{$\mat{x}(t)$}\only<3>{$\mat{x}_k$}};
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (A) at ([xshift=1.2cm,yshift=-1cm]plant.center)  {\sc \only<1-2>{$\mat{A}$}\only<3>{$\mat{A}_d$}};
+      \coordinate (aeast) at ([xshift=1cm]A);
+      \coordinate (awest) at ([xshift=-1.8cm]A);
+    }
+
+\only<1>{
+ \& \node[rectangle,draw,minimum width=3cm,
+	minimum height=1.6cm,] (bbadc) {\sc ADC};
+     \coordinate (ykeast) at ([xshift=1.9cm]bbadc);
+     \coordinate (yksouth) at ([xshift=1.9cm,yshift=-3.5cm]bbadc);
+ }
+\only<2>{
+   \& complexnode/.pic={ 
+     \node[rectangle,dashed,draw,minimum width=3.5cm,minimum height=1.6cm,label=\textbf{ADC},] (adc) {};
+     \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
+     \coordinate (switch1) at ([xshift=-1cm]adc.center);
+     \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
+     \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
+     \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
+     \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
+     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]q1)  {$\mat{x}_k$};} 
+     \coordinate (ykeast) at ([xshift=1.9cm]q1);
+     \coordinate (yksouth) at ([xshift=1.9cm,yshift=-3.5cm]q1);
+   }
+   \& \coordinate (aux1);
+   \& \\
+  };
+\only<3>{
+   \coordinate (ykeast) at ([xshift=4.5cm]int);
+   \coordinate (yksouth) at ([xshift=4.5cm,yshift=-5.8cm]int);
+}
+  \path[->] (r) edge (circle.west);
+  \only<1>{
+  \path
+    (circle.east) edge (bbdac.west)
+    (bbdac.east) edge (B.west);
+  }
+  \only<2>{
+    \path[->] (v2) edge (q2.south);
+    \path[->] (circle.east) edge (q2.west);
+    \path       (q2.east) edge (zoh.west);
+    \path[->] (zoh.east) edge (B.west);
+  }
+  \only<3>{
+    \path[->] (v12) edge (circle.north);
+    \path[->] (circle.east) edge (B.west);
+  }
+  \path
+   (B.east) edge (p1.west)
+   (p1.east) edge (int.west)
+   (xsouth) edge (aeast)
+   (aeast) edge (A.east)
+   (A.west) edge (awest)
+   (awest) edge (p1.south);
+   \only<2>{
+   \path[->] (v1) edge (q1.south);
+   \path   
+   (int.east) edge (switch1.west)
+   (switch2) edge (q1.west);
+   }
+\only<1>{ 
+  \path 
+    (int.east) edge (bbadc.west)
+    (bbadc.east) edge (ykeast);
+}   
+\only<2>{ \path (q1.east) edge (ykeast);}
+\only<3>{ \path (int.east) edge (ykeast);}
+  \path
+   (ykeast) edge (yksouth)
+   (yksouth) edge (kdsouth);
+  \path[->]  (kdsouth) edge (Kd.south);
+  \path (Kd.north) edge (circle.south);
+ \end{tikzpicture}
+}
+\end{figure}
+\uncover<3>{
+\begin{align*}
+A_d &= e^{A T_s} = \mathcal{L}^{-1} { ( s I - A )^{-1} }_{t = T_s}\\
+B_d &= \int_{0}^{T_s} e^{A t} dt\ B = A^{-1} ( A_d - I ) B
+\end{align*}}
+\end{frame}
+
+\begin{frame}[fragile]{Multi-stage Verification CEGIS}
+\begin{figure}[htb]
+{\scriptsize
+\centering
+{
+ \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
+},
+          row sep=.6cm, column sep=.9cm] {
+   \coordinate (aux1);
+   \& \coordinate (aux2);
+   \&;\\
+   \coordinate (aux3);
+   \& \coordinate (aux4);
+   \&;\\
+   \coordinate (aux5);
+   \& \coordinate (aux6);
+   \&;\\
+   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc 1.Synthesize}};
+   \&
+   complexnode/.pic={ 
+     \node[rectangle,draw,dotted,
+	minimum width=6cm,
+	minimum height=1cm,
+        pattern=north west lines, pattern color=gray!20,
+	label={\sc ~~~~~~~~~~~~Verify},] (verif) {};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc 2.Safety}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=0cm]verif.center) {{\sc 3.Precision}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=2cm]verif.center) {{\sc 4.Complete}};
+   } 
+   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
+   \& \\
+   \node[minimum height=0cm] (gp) {\sf Program Search};
+   \&
+   complexnode/.pic={ 
+     \coordinate (aux);
+   \node (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based \\Verifier};
+   \node (fp)  at ([xshift=0cm]aux.center) {\sf Fixed-point \\ Arithmetic\\Verifier};
+   \node (sv)  at ([xshift=2cm]aux.center) {\sf Completeness\\Verifier};
+   }   
+    \\
+  };
+
+   \path
+    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$K$} ([yshift=2em]verif1.west)
+    ([yshift=-2em]verif1.west) edge node {C-ex} ([yshift=-2em]synth.east)
+    ([xshift=-5em]fp.north) edge node[align=center]  {T/F} ([xshift=-5em]verif2.south)
+    ([xshift=-5em]sv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif3.south)
+    ([xshift=5em]verif1.south) edge node[align=center] {$K$} ([xshift=5em]bmc.north)
+    ([xshift=5em]verif2.south) edge node[align=center] {$K$} ([xshift=5em]fp.north)
+    ([xshift=5em]verif3.south) edge node[align=center] {$K$} ([xshift=5em]sv.north)
+    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
+    (verif) edge node {PASS} (done)
+    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
+    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$K$} ([xshift=-5em]synth.south)
+    (aux3) edge (synth.north);
+   \path[-]
+   (verif2.north) edge node[align=center] {} ([xshift=0cm]aux6)
+   ([xshift=0cm]aux6) edge node[align=center] {Increase Precision} (aux5)
+   (verif3.north) edge node[align=center] {} ([xshift=6.7cm]aux4)
+   ([xshift=6.7cm]aux4) edge node[align=center] {Increase Unfolding Bound} (aux3);
+
+ \end{tikzpicture}
+}}
+\end{figure}
+\end{frame}
+
+\begin{frame}[fragile]{Completeness Bound}
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.6\textwidth]{ct.eps}
+\vspace{0.1cm}
+\label{fig:ct}
+\end{figure}
+\end{frame}
+
+%\begin{frame}{Illustrative Example}
+%We illustrate our approach with an example,
+%extracted from the literature~\cite{Franklin15}.
+%%
+%We start with a candidate solution with all coefficients zero, $K=[0
+%  \ 0 \ 0]^T$, and a precision of $I_p=13$, $F_p=3$.  In the first
+%{\sc verify} stage, the {\sc safety} check finds the counterexample
+%%
+%$ x_0 = [-0.5 \ 0.5 \ 0.5] $.
+%%
+%After adding the new counterexample to its sets of {\sc inputs}, {\sc
+%  synthesize} finds the candidate solution $K=[0 \ 0
+%  \ 0.00048828125]^T$, which prompts the {\sc safety} verifier to
+%return $x_0=[-0.5 -0.5 -0.5]$ as the new counterexample.
+%
+%In the subsequent iteration, the synthesizer is unable to find further 
+%suitable candidates and it returns UNSAT, meaning that the current precision is
+%insufficient.  Consequently, we increase the precision to $I_p=17$,
+%$F_p=7$.
+%%
+%Since the previous counterexamples were obtained at lower precision,
+%we remove them from the set of counterexamples.  Back in the {\sc
+%  synthesize} phase, we re-start the process with a candidate solution
+%with all coefficients $0$.  Next, the {\sc safety} verification stage
+%provides the first counterexample at higher precision, $x_0=[-0.5
+%  \ 0.5 \ 0.5]$ and {\sc synthesize} finds $K=[0 \ 0.01171875
+%  \ 0.015625]^T$ as a candidate that eliminates this counterexample.
+%However, this candidate triggers the counterexample
+%$x_0=[0.5\ -0.5\ -0.5]$ found again by the {\sc safety} verification
+%stage.  In the next iteration, we get the candidate $K=[0 \ 0
+%  \ -0.015625]$, followed by the counterexample $x_0 = [0.5 \ 0.5
+%  \ 0.5]$. Finally, {\sc synthesize} finds the candidate $K=[0.01171875
+%  \ -0.013671875 \ -0.013671875]^T$, which is validated as a final
+%solution by all verification stages.
+%end{frame}
+
+\begin{frame}[fragile]{Abstraction-based CEGIS}
+\begin{figure}
+\centering
+{\scriptsize
+\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=.8cm, column sep=.2cm] {
+   \coordinate (aux1);
+   \& \coordinate (aux2);
+   \& ;\\
+   \&\node[fill=gray!20,align=center,xshift=-1.5cm] (pre) {{\sc 1. pre-}\\{\sc processing}};
+   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstract};
+   \& \coordinate (aux); \\ 
+   \&
+   \& \node[fill=gray!20,align=center] (synth) {\sc 2. synthesize};
+   \& \node[fill=gray!20,align=center, minimum width=3.5cm] (verify) {\sc 3. verify ($\phi$)};
+      \node[draw=none] (SAT) at ([xshift=2.2cm,yshift=-.3cm]verify)  {\sc PASS};
+   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
+   \&
+   \& \node[draw,rectangle,align=center] (KSAT) {Program \\ Search};
+   \& complexnode/.pic={
+     \coordinate (AA);
+     \node[draw,rectangle,align=center] (AAV) at ([xshift=-1.5cm]AA.center) {Abstract\\Acceleration};
+     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm]AA.center) {Abstraction \\ Verifier};
+    }\\
+  };
+  \path
+    (pre.east) edge node[align=center] {$P_a$, $N$,\\ $\phi_\mathit{init}^k$} (abstract.west)
+    (abstract.south) edge node{$(\phi(K), k)$} (synth.north)
+    ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west)
+    (aux) edge (abstract.east) 
+    (verify.east) edge (done.west);
+  \path
+    ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {$(\phi(K),k)$} ([xshift=0.6cm]synth.south) 
+    ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$K$} ([xshift=-.6cm]KSAT.north)
+    ([yshift=.5cm]AAV.east) edge node{\sl $\hat{X}^\#$} ([yshift=.5cm]AAC.west)
+    ([yshift=-.5cm]AAC.west) edge node{$(k,x_0)$} ([yshift=-.5cm]AAV.east)
+    (AAC.north) edge node{\sl $\hat{X}^\#$} ([xshift=4.9cm]verify.south)
+    ([xshift=-5cm]verify.south) edge node{$K$} (AAV.north);
+  \path[-] 
+     (verify.north) edge node {$(k,x_0)$} (aux);
+\end{tikzpicture}
+}
+\end{figure}
+\end{frame}
+
+\begin{frame}[fragile]{Abstraction-based CEGIS}
+\begin{itemize}
+\uncover<1->{ \item Calculate $\mat{T}$ such that $P_a = z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}$ is the first line of $\mat{T}\mat{A}_b\mat{T}^{-1}$}
+\uncover<2->{\item Calculate $N= \left \{ \nu_1+\nu_2+ \nu_3 \right \}$ from the quantizer resolutions and estimated round-off errors:
+
+\begin{align*}
+\nu_1 \in \left[-\frac{q_1}{2}\ \ \frac{q_1}{2}\right] \wedge \nu_2 \in \left[-\frac{q_2}{2}\ \ \frac{q_2}{2}\right]  \wedge \nu_3 \in \left[-q_3\ \ q_3\right]\nonumber
+\end{align*}
+
+where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is
+the error introduced by the DAC and $q_3$ is the maximum truncation and
+rounding error in $u_k=-K \cdot \mathcal{F}_{\langle I_c,F_c \rangle}(x_k)$}
+
+\uncover<3->{
+\item Calculate $\phi_\mathit{init}^K := -K x_0 \in \phi_{input} : x_0 \in \phi_{\mathit{init}}$}
+
+\end{itemize}
+\end{frame}
+
+%
+%\item In the {\sc synthesize} phase, we synthesize a candidate controller
+
+%% Once we have established convergence, we may examine the 
+%% safety specification $\phi_{safety}$.
+%  $K \in \mathbb{R}\langle I_c,F_c\rangle^n$ that satisfies
+%  $\phi_\mathit{stability} \wedge \phi_\mathit{safety} \wedge \phi_\mathit{init}^{K}$ by invoking a SAT solver.
+%%%   We obtain it by solving the SAT formula 
+%%% $$\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{safety}$$ 
+%%% that satisfies the input constraint and Jury's criteria for 
+%%% $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \tilde{\mat{K}}=\mat{K}\mat{T}$,
+%%% where $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ is a program describing Jury's method.
+%If there is no candidate solution we return UNSAT and exit the loop.
+%\item Once we have a candidate solution, we perform a safety verification % If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
+%  %
+%  of the 
+%  %consisting of evaluating the
+%  progression of the system from $\phi_\mathit{init}$ over time,
+%$x_{k+1} \models \phi_\mathit{safety}$. %% For this purpose we require 
+%%% an initial set $\phi_{init}= x_0 \in [\underline{x_0} \ \overline{x_0}]$ 
+%%% from which the system progresses.
+%% Obviously, this set $x_0$ 
+%% must satisfy the specification; otherwise, the system will be unsafe to begin with.
+%% We accept a specification in the form $\mat{E}\mat{T}x_0<\mat{f}$. 
+%% The presence of $\mat{T}$ is because this will typically be given in the original 
+%% state-space.
+%%% Next, we use abstract acceleration to get a second abstraction that 
+%  %% encompasses the accelerated continuous reach-tube over an unbounded time.
+%  In order to compute the progression of point $x_0$ at iteration $k$,
+%  we accelerate the dynamics of the closed-loop system and obtain:
+%  %we take the
+%  %the closed-loop model:
+%  %$x_{k+1}=\mat{A}_{t}x_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)$
+%  %and accelerate it to:
+%%
+%\begin{align}
+%%\label{eq:acc_observer_LTI_cf}
+%x=&(A_d-B_dK)^kx_0
+%%+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i
+%+\sum_{i=0}^{k-1} (A_d-B_dK)^i B_{n}(\nu_1+\nu_2+\nu_3) : B_n= [1\ 1 \cdots \ 1 ]^T
+%\end{align}
+%%
+%As this still requires us to verify the system for every $k$ up to infinity,
+%we use abstract acceleration again to obtain the reach-tube, i.e., the set
+%of all reachable states at all times given an initial set
+%$\phi_\mathit{init}$:
+%%
+%\begin{align}
+%\label{eq:aa_observer_LTI_cf}
+%\hat{X}^\#
+%=&\mathcal{A} X_0 + \mathcal{B}_{n} N\\
+%X_0 =&\left \{x : x \models \phi_\mathit{init} \right\}\nonumber
+%\end{align}
+%%
+%where $\mathcal{A}=\bigcup_{k=1}^\infty (A_d-B_dK)t^k,
+%\mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k(A_d-B_dK)^iB_{n}$ are
+%abstract matrices for the closed-loop system~\cite{cattaruzza2015unbounded},
+%whereas the set $N$ is non-deterministically chosen.
+%
+%We next evaluate $\hat{X}^\# \models \phi_\mathit{safety}$.  If the
+%verification holds we have a solution, and exit the loop.  Otherwise, we
+%find a counterexample iteration $k$ and corresponding initial point $x_0$
+%for which the property does not hold, which we use to locally refine the
+%abstraction.  When the abstraction cannot be further refined, we provide
+%them to the {\sc abstract} phase.
+%%
+%%\todo{we should have a better argument here.}
+%%\end{enumerate} 
+%\item If we reach the {\sc abstract} phase, it means that the candidate solution is not valid,
+%  in which case we must refine the abstraction used by the synthesizer.
+%\begin{enumerate}
+%\item Find the constraints that invalidate the property
+% as a set of counterexamples for the eigenvalues, which we define as $\phi_\Lambda$. This is a constraint in the spectrum i.e., transfer function) of the closed loop dynamics. 
+%\item We use $\phi_\Lambda$ to
+%  further constrain the characteristic polynomial  
+%$z^n+\sum_{i=1}^n(a_i-k_i)z^{n-i}=\prod_{i=1}^n (z-\lambda_i) : |\lambda_i|<1 \wedge \lambda_i \models \phi_{\Lambda}$.
+These constraints correspond to specific iterations for which the system may be unsafe.
+%\item Pass the refined abstraction $\phi(K)$ with the new constraints and the list of iterations $k$ to the {\sc synthesize} phase.
+%  %, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again. 
+%\end{enumerate}
+
+\begin{frame}{Case Study}
+Consider the sampled helicopter example:
+\begin{align*}
+A_d &= \left[\begin{array}{ccc}2.6207&-1.1793&0.65705\\2&0&0\\0&0.5&0\end{array}\right] &
+B_d &= \left [\begin{array}{c}8\\0\\0\end{array}\right]\\
+x_0 &\in [-.9\ \ .9] \wedge u \in [-10\ \ 10] \wedge x_k \in [-.92\ \ .92]\\
+\mathbb{R}&\langle I,F \rangle=\mathbb{R}\langle 8,8 \rangle
+\end{align*}
+With pre-processed characteristic polynomial, transform matrix, noise and initial constraints
+\begin{align*}
+P_a(z) &=z^3 + 2.6207z^2 -2.3586 z + 0.65705\\
+T &= \left[\begin{array}{ccc}8&0&0\\0&16&0\\0&0&8\end{array}\right]\\
+N &\in [-.00595\ \ .00595]\\
+\phi_{init}&=(|K_1|+|K_2|+|K_3|<10.87)
+\end{align*}
+\end{frame}
+
+\begin{frame}[fragile]{Case Study}
+\begin{figure}
+\centering
+{\scriptsize
+\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=1.5cm, column sep=2cm] {
+   \coordinate (aux1);
+   \& \coordinate (aux2);
+   \& ;\\
+   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstract};
+   \& \coordinate (aux); \\ 
+   \& \node[fill=gray!20,align=center] (synth) {\sc 2. synthesize};
+   \& \node[fill=gray!20,align=center, minimum width=3.5cm] (verify) {\sc 3. verify ($\phi$)};
+         \node[draw=none] (SAT) at ([xshift=2.2cm,yshift=-.3cm]verify)  {\sc \textcolor{blue}{PASS}};
+
+   \\
+   \& \node[draw,rectangle,align=center] (KSAT) {Program \\ Search};
+   \& complexnode/.pic={
+     \coordinate (AA);
+     \node[draw,rectangle,align=center] (AAV) at ([xshift=-1.5cm]AA.center) {Abstract\\Acceleration};
+     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm]AA.center) {Abstraction \\ Verifier};
+    }\\
+  };
+  \only<1-3>{\path (abstract.south) edge node{$\textcolor{blue}{\begin{array}{c}\phi_{init}^K\\P_a(z)\\k=0\end{array}}$} (synth.north);}
+  \only<4->{\path (abstract.south) edge node{$\textcolor{blue}{\begin{array}{c}\phi_{k,x_0}^K\\P_a(z)\\k=0,1,2\end{array}}$} (synth.north);}
+    \only<1,4>{\path ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west);}
+    \only<2-3,5->{\path ([yshift=1em]synth.east) edge node {$\textcolor{blue}{K}$} ([yshift=1em]verify.west);}
+    \path (aux) edge (abstract.east);
+  \only<1-3>{\path ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {$\textcolor{blue}{\begin{array}{c}\phi_{init}^K\\P_a(z)\end{array}}$} ([xshift=0.6cm]synth.south);}
+  \only<4->{\path ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {$\textcolor{blue}{\begin{array}{c}\phi_{k,x_0}^K\\P_a(z)\\k=0,1,2\end{array}}$} ([xshift=0.6cm]synth.south);}
+    \only<1>{\path ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$K$} ([xshift=-.6cm]KSAT.north);}
+    \only<2-3>{\path ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$\textcolor{blue}{\left[\begin{array}{c}0.24609375\\-0.125\\0.1484375\end{array}\right]^T}$} ([xshift=-.6cm]KSAT.north);}
+    \only<4>{\path ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$K$} ([xshift=-.6cm]KSAT.north);}
+    \only<5->{\path ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$\textcolor{blue}{\left[\begin{array}{c}0.23828125\\-0.17578125\\0.109375\end{array}\right]^T}$} ([xshift=-.6cm]KSAT.north);}
+    \only<1-2,4>{
+    \path ([yshift=.5cm]AAV.east) edge node{\sl $\hat{X}^\#$} ([yshift=.5cm]AAC.west);
+    \path ([yshift=-.5cm]AAC.west) edge node{$(k,x_0)$} ([yshift=-.5cm]AAV.east);
+    \path (AAC.north) edge node{\sl $\hat{X}^\#$} ([xshift=4.9cm]verify.south);
+    \path ([xshift=-5cm]verify.south) edge node{$K$} (AAV.north);
+    }
+    \only<3,5->{
+    \path ([yshift=.5cm]AAV.east) edge node{\sl $\textcolor{blue}{\hat{X}^\#}$} ([yshift=.5cm]AAC.west);
+    \path ([yshift=-.5cm]AAC.west) edge node{$\textcolor{blue}{(k,x_0)}$} ([yshift=-.5cm]AAV.east);
+    \path (AAC.north) edge node{\sl $\textcolor{blue}{\hat{X}^\#}$} ([xshift=4.9cm]verify.south);
+    \path ([xshift=-5cm]verify.south) edge node{$\textcolor{blue}{K}$} (AAV.north);
+    }
+
+  \only<1-2,5->{\path[-] (verify.north) edge node {$(k,x_0)$} (aux);}
+  \only<3-4>{\path[-] (verify.north) edge node {$\tiny \textcolor{blue}{\left(\begin{array}{cc}2,&[\begin{array}{ccc}.9&-.9&.9\end{array}]\\3,&[\begin{array}{ccc}.9&-.9&-.9\end{array}]\end{array}\right)}$} (aux);}
+\end{tikzpicture}
+}
+\end{figure}
+\end{frame}
+
 \end{document}

### 2017-03-17 slides/presentation.tex
bug fixes

@@
 \draw[dashed,color=red] (axis cs:0cm,0cm) circle[radius=100];
-\node at (axis cs:.7,-.7) [pin={-10:{stable region}},inner sep=0pt] {};
+\node at (axis cs:.5,-.866) [pin={-80:{stable region}},inner sep=0pt] {};
 \draw[color=blue] (axis cs:0.5,0.7) ellipse[x radius=5, y radius=15];
@@
 
-\textcolor{red}{Copy here CEGIS architecture scheme.}
+\begin{figure}[htb]
+\centering
+\resizebox{1.0\textwidth}{!}
+{
+ \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
+},
+          row sep=1cm, column sep=2cm] {
+   \coordinate (aux1);
+   \& \coordinate (aux2);
+   \&;\\
+   \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
+   \&
+   complexnode/.pic={ 
+     \node[rectangle,draw,dotted,
+	minimum width=7cm,
+	minimum height=1cm,
+        pattern=north west lines, pattern color=gray!20,
+	label={\sc Verify},] (verif) {};
+     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc Uncertainty}};
+     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=2cm]verif.center) {{\sc Precision}};
+   } 
+   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
+   \& \\
+   \node[minimum height=0.5cm] (gp) {\sf Closed-loop System Search};
+   \&
+   complexnode/.pic={ 
+     \coordinate (aux);
+   \node[minimum height=0.5cm] (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based\\Verifier};
+   \node[minimum height=0.5cm] (fp)  at ([xshift=2cm]aux.center) {\sf Interval Arithmetic\\Verifier};
+   }   
+    \\
+  };
+
+   \path (verif2) edge node {} (done);
+   \path ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north);
+   \path ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south);
+   \path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {Candidate solution} ([yshift=2em]verif1.west);
+   \path  ([xshift=5em]verif1.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]bmc.north);
+   \path  ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south);
+   \path ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east);
+   \path ([xshift=5em]verif2.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]fp.north);
+   \path  ([xshift=-5em]fp.north) edge node[align=center]  {True/\\False} ([xshift=-5em]verif2.south);
+   \path (aux1) edge (synth.north);
+   \path[-] (verif2.north) edge node[align=center] {} ([xshift=6.7cm]aux2);
+   \path[-] ([xshift=6.7cm]aux2) edge node[align=center] {Increase Precision} (aux1);
+ \end{tikzpicture}
+}
+\end{figure}
 
@@
    \& complexnode/.pic={ 
-      \only<1-2>{\node[rectangle,dashed,draw,minimum width=6.5cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};}
+      \only<1>{\node[rectangle,dashed,draw,minimum width=6.5cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.4cm]dac.center) {};}
+      \only<2>{\node[rectangle,dashed,draw,minimum width=6.5cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};}
       \only<3>{\node[rectangle,dashed,draw,minimum width=6.5cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.75cm]dac.center) {};}

### 2017-03-19 slides/presentation.tex
pres
counterexample fix
fixes to Abstraction CEGIS

@@
 }
-\usepackage{enumitem}      % adjust spacing in enums
+%\usepackage{enumitem}      % adjust spacing in enums
 %\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   
@@
    \only<6-7>{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([xshift=-5em]verif1.south);}
-   \only<1-6,8-12,16,18-19>{\path ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east);}
+   \only<1-6,8-16,18->{\path ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east);}
    \only<7>{\path ([yshift=-2em]verif1.west) edge node {$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([yshift=-2em]synth.east);}
@@
 
-\begin{frame}[fragile]{Completeness Bound}
+\begin{frame}[fragile]{Completeness Bound/Threshold}
 \begin{figure}[t]
 \centering
-\includegraphics[width=0.6\textwidth]{ct.eps}
+\includegraphics[width=0.6\textwidth]{./figures/ct.pdf}
 \vspace{0.1cm}
@@
    \& \node[fill=gray!20,align=center, minimum width=3.5cm] (verify) {\sc 3. verify ($\phi$)};
-         \node[draw=none] (SAT) at ([xshift=2.2cm,yshift=-.3cm]verify)  {\sc \textcolor{blue}{PASS}};
+        \uncover<9>{ \node[draw=none] (SAT) at ([xshift=2.2cm,yshift=-.3cm]verify)  {\sc \textcolor{blue}{PASS}};}
 
@@
   };
-  \only<1-3>{\path (abstract.south) edge node{$\textcolor{blue}{\begin{array}{c}\phi_{init}^K\\P_a(z)\\k=0\end{array}}$} (synth.north);}
-  \only<4->{\path (abstract.south) edge node{$\textcolor{blue}{\begin{array}{c}\phi_{k,x_0}^K\\P_a(z)\\k=0,1,2\end{array}}$} (synth.north);}
-    \only<1,4>{\path ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west);}
-    \only<2-3,5->{\path ([yshift=1em]synth.east) edge node {$\textcolor{blue}{K}$} ([yshift=1em]verify.west);}
+  \only<1-5>{\path (abstract.south) edge node{$\textcolor{blue}{\begin{array}{c}\phi_{init}^K\\P_a(z)\\k=0\end{array}}$} (synth.north);}
+  \only<6->{\path (abstract.south) edge node{$\textcolor{blue}{\begin{array}{c}\phi_{k,x_0}^K\\P_a(z)\\k=0,1,2\end{array}}$} (synth.north);}
+    \only<1-2,6>{\path ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west);}
+    \only<3-5,7->{\path ([yshift=1em]synth.east) edge node {$\textcolor{blue}{K}$} ([yshift=1em]verify.west);}
     \path (aux) edge (abstract.east);
-  \only<1-3>{\path ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {$\textcolor{blue}{\begin{array}{c}\phi_{init}^K\\P_a(z)\end{array}}$} ([xshift=0.6cm]synth.south);}
-  \only<4->{\path ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {$\textcolor{blue}{\begin{array}{c}\phi_{k,x_0}^K\\P_a(z)\\k=0,1,2\end{array}}$} ([xshift=0.6cm]synth.south);}
-    \only<1>{\path ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$K$} ([xshift=-.6cm]KSAT.north);}
-    \only<2-3>{\path ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$\textcolor{blue}{\left[\begin{array}{c}0.24609375\\-0.125\\0.1484375\end{array}\right]^T}$} ([xshift=-.6cm]KSAT.north);}
-    \only<4>{\path ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$K$} ([xshift=-.6cm]KSAT.north);}
-    \only<5->{\path ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$\textcolor{blue}{\left[\begin{array}{c}0.23828125\\-0.17578125\\0.109375\end{array}\right]^T}$} ([xshift=-.6cm]KSAT.north);}
-    \only<1-2,4>{
+
+  \only<1,6>{\path ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {$(\phi(K),k)$} ([xshift=0.6cm]synth.south);}
+  \only<2-5>{\path ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {$\textcolor{blue}{\begin{array}{c}\phi_{init}^K\\P_a(z)\end{array}}$} ([xshift=0.6cm]synth.south);}
+  \only<7->{\path ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {$\textcolor{blue}{\begin{array}{c}\phi_{k,x_0}^K\\P_a(z)\\k=0,1,2\end{array}}$} ([xshift=0.6cm]synth.south);}
+    \only<1-2,6>{\path ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$K$} ([xshift=-.6cm]KSAT.north);}
+    \only<3-5>{\path ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$\textcolor{blue}{\left[\begin{array}{c}0.24609375\\-0.125\\0.1484375\end{array}\right]^T}$} ([xshift=-.6cm]KSAT.north);}
+    \only<7->{\path ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$\textcolor{blue}{\left[\begin{array}{c}0.23828125\\-0.17578125\\0.109375\end{array}\right]^T}$} ([xshift=-.6cm]KSAT.north);}
+    \only<1-3,6-7>{
     \path ([yshift=.5cm]AAV.east) edge node{\sl $\hat{X}^\#$} ([yshift=.5cm]AAC.west);
@@
     }
-    \only<3,5->{
+    \only<4-5,8->{
     \path ([yshift=.5cm]AAV.east) edge node{\sl $\textcolor{blue}{\hat{X}^\#}$} ([yshift=.5cm]AAC.west);
@@
 
-  \only<1-2,5->{\path[-] (verify.north) edge node {$(k,x_0)$} (aux);}
-  \only<3-4>{\path[-] (verify.north) edge node {$\tiny \textcolor{blue}{\left(\begin{array}{cc}2,&[\begin{array}{ccc}.9&-.9&.9\end{array}]\\3,&[\begin{array}{ccc}.9&-.9&-.9\end{array}]\end{array}\right)}$} (aux);}
+  \only<1-4,7->{\path[-] (verify.north) edge node {$(k,x_0)$} (aux);}
+  \only<5-6>{\path[-] (verify.north) edge node {$\tiny \textcolor{blue}{\left(\begin{array}{cc}2,&[\begin{array}{ccc}.9&-.9&.9\end{array}]\\3,&[\begin{array}{ccc}.9&-.9&-.9\end{array}]\end{array}\right)}$} (aux);}
 \end{tikzpicture}

### 2017-04-13 cav2017/reviews-after-rebuttal.txt
added CAV reviews after the rebuttal phase
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

===========================================================================
                            CAV'17 Review #160A
---------------------------------------------------------------------------
Paper #160: Automated Formal Synthesis of Digital Controllers for
            State-Space Physical Plants
---------------------------------------------------------------------------

                      Overall merit: 3. Weak accept

                         ===== Paper summary =====

The paper describes two methods for synthesizing controllers represented as linear time invariant models. The first is based on the use of a bounded model checker, using unwinding. The second is based on the use of abstraction refinement. The paper shows that the second method can be faster, although in an empirical evaluation both methods were found to encounter models for which synthesis failed.

                      ===== Comments for author =====

The paper claims two improvements over earlier or related work. One is the establishment of safety guarantees, formalized as reachability regions. The second is treatment of quantization errors and their possible effect on controller stability and/or safety.
It would be good to more clearly describe on those two points how your methods differ in the results that are produced, and in the cost of producing those results. E.g., if both additional factors are removed, does your method perform identical to earlier methods? As each factor is added, how much does it impact feasibility and cost of finding a solution?

===========================================================================
                            CAV'17 Review #160B
                     Updated 6 Apr 2017 8:52:09am CEST
---------------------------------------------------------------------------
Paper #160: Automated Formal Synthesis of Digital Controllers for
            State-Space Physical Plants
---------------------------------------------------------------------------

                      Overall merit: 3. Weak accept

                         ===== Paper summary =====

The paper entitled "Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants" presents a fully automated method for the synthesis of provably sound digital state-feedback controllers ensuring safety and stability of the controlled system.

                      ===== Comments for author =====

The authors emphasize the following main features of their synthesis approach:
- They consider the true continuous dynamics of the plant as the starting point of the design.
- They account for errors introduced by fixed-point arithmetics arising from a digital implementation of the controller.
- They can ensure safety with respect to a safe set of states (containing the set of initial conditions) additionally to stability.
- They get a fully automated synthesis methodology taking a continuous LTI plant model and a safety specification as an input and returning a digital controller s.t. the resulting closed loop system is safe and stable.

Given these motivating points, there is actually a large body of work in the context of abstraction based controller synthesis for cyber-physical systems (CPS) which is not cited by the authors tackling these challenges. Furthermore, most of the work in this community can actually handle a lot more powerful specifications (beyond safety) and plant models (up to non-linear models without stability assumptions or stochastic models) by providing a fully automated design scheme as envisioned by the authors. Here is a short list of some related works that I have at the top of my head, but there are many more:

- textbook on the topic:
* Paulo Tabuada, Verification and Control of Hybrid Systems - A Symbolic Approach,  2009
(http://www.springer.com/de/book/9781441902238)

- work especially on safety specifications:
* Antoine Girard, Controller synthesis for safety and reachability via approximate bisimulation, 2012 (http://www.sciencedirect.com/science/article/pii/S000510981200088X)

- work especially on LTI systems:
* Paulo Tabuada, Symbolic models for linear control systems with disturbances, 2007 (http://ieeexplore.ieee.org/abstract/document/4434957/)

- some recent works that talk explicitly about how errors form digital controller implementations are handled by the framework:
* Jun Liu and Necmiye Ozay, Abstraction, Discretization, and Robustness in Temporal Logic Control of Dynamical Systems, 2014 (http://web.eecs.umich.edu/~necmiye/pubs/LiuO_hscc14.pdf)
* Gunther Reissig, Alexander Weber, and Matthias Rungger, Feedback Refinement Relations for the Synthesis of Symbolic Controllers 2016 (http://ieeexplore.ieee.org/abstract/document/7519063/)
* Mahmoud Khaled, Matthias Rungger, and Majid Zamani, Symbolic Models of Networked Control Systems: A Feedback Refinement Relation Approach, 2016 (https://www.researchgate.net/profile/Majid_Zamani/publication/306017464_Symbolic_Models_of_Networked_Control_Systems_A_Feedback_Refinement_Relation_Approach/links/5857b7db08ae544d8863bef1.pdf)

Given the fact that the authors do not compare their work to the literature mentioned above, in which I think the proposed problem is already solved, I suggest to reject the paper.

Added after the rebuttal
----------------------------

I think my subreviewer discounted the difficulty of taking into account implementation effects in controller design. Based on the rebuttal, I am increasing my score to 3. I think this is an interesting direction and scalable tools are lacking.

===========================================================================
                            CAV'17 Review #160C
---------------------------------------------------------------------------
Paper #160: Automated Formal Synthesis of Digital Controllers for
            State-Space Physical Plants
---------------------------------------------------------------------------

                      Overall merit: 3. Weak accept

                         ===== Paper summary =====

The paper presents a novel approach to synthesise controllers for LTI
models based on the CEGIS framework. The authors suggest two
approaches:

(a) The naive approach works by unfolding system behaviour for k steps
    and calling an SMT solver to instantiate a gain matrix K. This
    step is followed by a validation step where (1) precision and (3)
    completeness are checked. Stability is encoded as a constraint
    using Jury's criterion.

(b) An advanced method uses a concept of abstraction to boost the
    performance of the synthesis routine. The abstraction seems to
    reason in terms of eigenvalues of some matrix with refinement
    algorithm adding further constraints on the eigen value
    structure. The completeness step from (a) is replaced by abstract
    acceleration.

                      ===== Comments for author =====

The paper is generally well-written, although some parts require some
more clarification (see the question section). In addition, the
experimental section misses some details which would be helpful to get
a better insight into the algorithm behaviour.

I am not sure method (a) will scale due to exponential number of
checks in the verification phase. Generally, I am missing a break down
of the performance into phases (synthesis + verification). In
particular, I am wondering which phase dominates the whole run-time.

For the abstraction-based method, I am missing one of the main
indicators relevant for abstraction-based methods and namely number of
refinements for each experiment.

Some more questions:

* On the naive algorithm:

- I am confused about the completeness argument: The statement by the
  authors that a stable converges towards an origin seems to be
  correct, which is relevant for *stability*. Yet, I am not sure how
  the authors can derive their guarantees in case of *safety*. Could
  you please clarify?

* On the abstraction-based algorithm:

- How do you use characteristic polynomial in the algorithm? In other
  words, I could not find any references to P_a(x) from step 1(a) in
  any further steps.

- It is not clear how you derive constraints on the eigen value
  structure based on a counter-example. Please clarify.

### 2017-04-20 cav2017/cav2017.tex
added \institute

@@
 \author{%
-Alessandro Abate \and
-Iury Bessa \and
-Dario Cattaruzza \and
-Lucas Cordeiro \and
-\mbox{Cristina David} \and
-Pascal Kesseli \and
-Daniel Kroening \and
-Elizabeth Polgreen}
+Alessandro Abate\inst{1} \and
+Iury Bessa\inst{2} \and
+Dario Cattaruzza\inst{1} \and
+Lucas Cordeiro\inst{1} \and
+\mbox{Cristina David}\inst{1} \and
+Pascal Kesseli\inst{1} \and
+Daniel Kroening\inst{1} \and
+Elizabeth Polgreen\inst{1}}
 
@@
 
-\institute{}
+\institute{University of Oxford, UK
+\and
+Federal University of Amazonas, Manaus, Brazil}
 
@@
 %
-which result in the following closed loop dynamics:
+which result in the following closed-loop dynamics:
 %

### 2017-04-20 cav2017/cav2017.tex
grants
line break

@@
 
-% first the title is needed
-\title{Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants} 
+\title{Automated Formal Synthesis of Digital Controllers for State-Space
+Physical Plants\thanks{Supported by EPSRC grant EP/J012564/1, ERC project
+280053 (CPROVER) and the H2020 FET OPEN 712689 SC$^2$.}}
+
 \titlerunning{Automated Formal Synthesis of Digital Controllers}
@@
 of reachability properties over the finite-state machine.  Based on this
-safety specification, Pessoa can synthesize embedded controller software for
-a range of properties.  The embedded controller software can be more
-complicated than the state-feedback control we synthesized, and the
+safety specification, \mbox{Pessoa} can synthesize embedded controller
+software for a range of properties.  The embedded controller software can be
+more complicated than the state-feedback control we synthesized, and the
 properties available cover more detail.

### 2017-04-27 cav2017/cav2017.tex
x --> a in the description of the synthesis architecture

@@
 The input specification provided to the program synthesizer is of the form
-%$\exists P .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ 
-$\exists P .\,  \forall x.\,  \sigma(x, P)$, 
+%$\exists P .  \forall \vec{a}.  \sigma(\vec{a}, \vec{P})$ 
+$\exists P .\,  \forall a.\,  \sigma(a, P)$, 
 where $P$ ranges over functions, 
-$x$ ranges over ground terms, 
+$a$ ranges over ground terms, 
 and $\sigma$ is a quantifier-free formula.  
@@
 procedure tries to find an existential witness $P$ satisfying
-the specification $\sigma(x, P)$ for all $x$ in {\sc
+the specification $\sigma(a, P)$ for all $a$ in {\sc
   inputs} (as opposed to all $x \in \mathcal{D}$).
@@
 whether it is a full solution (i.e., $P$ satisfies the
-specification $\sigma(x, P)$ for all
+specification $\sigma(a, P)$ for all
 $x\in\mathcal{D}$).  If this is the case, then the algorithm
@@
 architecture of the program synthesizer, the controller $K$ denotes $P$ and
-$(x_0, u_k)$ represents $x$.
+$(x_0, u_k)$ represents $a$.
 
@@
 For the majority of our benchmarks, we observe that the abstraction-based
-back-end is faster than the basic multi-staged verification approach. 
-However, it fails to find solutions to three benchmarks, as compared to two
-with the multi-staged back-end, where the numbers given in the
-discretization matrices are too small.  In direct comparison, the
+back-end is faster than the basic multi-staged verification approach, and
+finds one solution more (9) than the multi-staged back-end (8).
+In direct comparison, the
 abstraction-based approach is on average able to find a solution in
-approximately 35\% of the time required using the multi-staged back-end, and
-has a median run-time 1.15\,s, which is seven times smaller than the
+approximately 70\% of the time required using the multi-staged back-end, and
+has a median run-time 1.4\,s, which is seven times smaller than the
 multi-staged approach.  The two back-ends complement each other in benchmark
@@
    &                                  & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
-1  & Cruise Control      & 8,16   & 6.88\,s & 16,16  &   0.24\,s \\
-2  & DC Motor            & 8,16   & 8.10\,s & 20,20  &   5.38\,s \\
-3  & Helicopter          & \xmark & \xmark  & 16,16  &   2.12\,s \\
-4  & Inverted Pendulum   & 8,16   & 7.81\,s & 16,16  &   0.39\,s \\
-5  & Magnetic Pointer    & \xmark & \xmark  & 28,28  & 132.85\,s \\
-6  & Magnetic Suspension & 12,20  & 8.73\,s & 32,32  &   7.85\,s \\
-7  & Pendulum            & 8,16   & 9.01\,s & 20,20  &   1.15\,s \\
-8  & Suspension          & 12,20  &49.41\,s & \xmark & \xmark \\
-9  & Tape Driver         & 8,16   & 9.18\,s & \xmark & \xmark \\
-10 & Satellite           & 8,16   & 8.98\,s & \xmark & \xmark \\\hline
+1  & Cruise Control      & 8,16   & 8.40\,s & 16,16  &   2.17\,s \\
+2  & DC Motor            & 8,16   & 9.45\,s & 20,20  &   2.06\,s \\
+3  & Helicopter          & \xmark & \xmark  & 16,16  &   1.37\,s \\
+4  & Inverted Pendulum   & 8,16   & 9.65\,s & 16,16  &   0.56\,s \\
+5  & Magnetic Pointer    & \xmark & \xmark  & 28,28  &  44.14\,s \\
+6  & Magnetic Suspension & 12,20  &10.41\,s & 16,16  &   0.61\,s \\
+7  & Pendulum            & 8,16   &14.02\,s & 16,16  &   0.60\,s \\
+8  & Suspension          & 12,20  &73.66\,s & \xmark &    \xmark \\
+9  & Tape Driver         & 8,16   &10.10\,s & 16,16  &  68.24\,s \\
+10 & Satellite           & 8,16   & 9.43\,s & 16,16  &   0.67\,s \\\hline
 %
@@
 
-The median run-time for our benchmark set is 7.9\,s.  Overall, the average
-synthesis time amounts to approximately 17.2\,s.  We consider these times
+The median run-time for our benchmark set is 9.4\,s.  Overall, the average
+synthesis time amounts to approximately 15.6\,s.  We consider these times
 short enough to be of practical use to control engineers, and thus affirm
@@
 benchmarks and the tool, is provided in the
-footnote.\footnote{\url{https://drive.google.com/open?id=0ByIexo3Z5N91eDludEdWdWxfV1E}}
+footnote as an Open Virtual Appliance
+(OVA).\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}
 

### 2017-04-27 cav2017/cav2017.tex

@@
 The input specification provided to the program synthesizer is of the form
-%$\exists P .  \forall \vec{a}.  \sigma(\vec{a}, \vec{P})$ 
-$\exists P .\,  \forall a.\,  \sigma(a, P)$, 
+%$\exists P .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ 
+$\exists P .\,  \forall x.\,  \sigma(x, P)$, 
 where $P$ ranges over functions, 
-$a$ ranges over ground terms, 
+$x$ ranges over ground terms, 
 and $\sigma$ is a quantifier-free formula.  
@@
 procedure tries to find an existential witness $P$ satisfying
-the specification $\sigma(a, P)$ for all $a$ in {\sc
+the specification $\sigma(x, P)$ for all $x$ in {\sc
   inputs} (as opposed to all $x \in \mathcal{D}$).
@@
 whether it is a full solution (i.e., $P$ satisfies the
-specification $\sigma(a, P)$ for all
+specification $\sigma(x, P)$ for all
 $x\in\mathcal{D}$).  If this is the case, then the algorithm
@@
 architecture of the program synthesizer, the controller $K$ denotes $P$ and
-$(x_0, u_k)$ represents $a$.
+$(x_0, u_k)$ represents $x$.
 

### 2017-04-27 cav2017/cav2017.tex

--- 2017-04-27 cav2017/cav2017.tex
@@
 the specification $\sigma(a, P)$ for all $a$ in {\sc
-  inputs} (as opposed to all $x \in \mathcal{D}$).
+  inputs} (as opposed to all $a \in \mathcal{D}$).
 %
@@
 specification $\sigma(a, P)$ for all
-$x\in\mathcal{D}$).  If this is the case, then the algorithm
+$a\in\mathcal{D}$).  If this is the case, then the algorithm
 terminates.  Otherwise, additional information is provided to the

### 2017-04-27 cav2017/cav2017.tex
+TODOs

@@
 based on the unfolding of the dynamics.
+
+\todo{Clarify challenges: FWL (rounding, truncation), quantisation (ADC, DAC).}
+
+\todo{Discuss numerical (HSCC'17) vs. algorithmical soundness (CAV'17).}
 
@@
 
+\todo{Refer to the SAS paper in this section.}
+
 %\begin{itemize}
@@
 %
+
+\todo{Remove RQ2 and only discuss the sanity check in 5.3?}
+
 \begin{enumerate}
@@
 
+\todo{Add the percentage of the total time taken by verification and synthesis.}
+
+\todo{Discuss the number of abstraction refinements (inner loop, not the outer one)
+  for the 2nd approach?
+  Although, if it's always one, I'm not sure how interesting it is.. }
+
 The median run-time for our benchmark set is 9.4\,s.  Overall, the average
@@
 \appendix
+
+\todo{Integrate Appendix in the actual paper.}
+
 %-------------------------------

### 2017-04-27 cav2017/cav2017.tex
swap phi init and phi input

@@
 Furthermore, it is practically relevant to consider the 
-constraints $\phi_\mathit{init}$ on the input
-signal $u_{k}$ and $\phi_\mathit{input}$ on the initial states $x_0$,
+constraints $\phi_\mathit{input}$ on the input
+signal $u_{k}$ and $\phi_\mathit{init}$ on the initial states $x_0$,
 which we assume have given bounds:
-$\phi_\mathit{init} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
-$\phi_\mathit{input} = \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$
-In the first case, this means that the control input saturates in view of
+$\phi_\mathit{input} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
+$\phi_\mathit{init} = \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$
+For the former, this means that the control input saturates in view of
 physical constraints.

### 2017-04-27 cav2017/cav2017.tex
+ specification for synthesis

@@
 When mapping back to the notation used for describing the general
-architecture of the program synthesizer, the controller $K$ denotes $P$ and
-$(x_0, u_k)$ represents $a$.
+architecture of the program synthesizer, the controller $K$ denotes $P$,
+$(x_0, u_k)$ represents $a$ and $\phi_{input} \wedge \phi_{init} \wedge \phi_{safety}$
+denotes the specification $\sigma$.
 

### 2017-04-27 cav2017/cav2017.tex
+ stability for the synthesis specification

--- 2017-04-27 cav2017/cav2017.tex
@@
 When mapping back to the notation used for describing the general
-architecture of the program synthesizer, the controller $K$ denotes $P$ and
-$(x_0, u_k)$ represents $a$.
+architecture of the program synthesizer, the controller $K$ denotes $P$,
+$(x_0, u_k)$ represents $a$ and $\phi_{stability} \wedge \phi_{input} \wedge \phi_{init} \wedge \phi_{safety}$
+denotes the specification $\sigma$.
 

### 2017-04-28 cav2017/cav2017.tex
editing

@@
 However, these methods have not been generalized to control synthesis. 
-We~remark that a synthesis algorithm that guarantees satability does not
+We~remark that a synthesis algorithm that guarantees stability does not
 ensure safety: the system might transitively visit an unsafe state that
@@
 Synthesis (CEGIS)~\cite{sketch}.  We prove their soundness by quantifying
-errors caused digitalization and quantization effects that arise when
+errors caused by digitalization and quantization effects that arise when
 time/value-discrete digital controller interacts with the continuous plant.
@@
 synthesized in less than $17.2$ seconds.  We further show that, in a direct
-comparison, the abstraction-based approach (second) lowers the median
+comparison, the abstraction-based approach (i.e., second approach) lowers the median
 run-time of our benchmarks by a factor of seven over the first approach
@@
   the various sources of imprecision in the implementation of the control
-  algorithm and in the modeling of plant.
+  algorithm and in the modeling of the plant.
 %
@@
 %
-where $k \in \mathbb N$ and with initial state $x_{0}=x(0)$.  $A_d$ and
-$B_d$ denote the matrices that describe the discretized plant dynamics and
+where $k \in \mathbb N$ and $x_{0}=x(0)$ is the initial state.  $A_d$ and
+$B_d$ denote the matrices that describe the discretized plant dynamics, whereas
 $A$ and $B$ the continuous plant dynamics.  Later, we will address the
@@
 
-Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
+Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t)$ and  $u_k$, respectively. 
 Feedback architectures can be employed to manipulate the properties and behaviors of the continuous process (the plant).   
 %reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
-We are interested in the synthesis of digital feedback control algorithm, 
+We are interested in the synthesis of digital feedback control algorithms, 
 as implemented on modern Field-Programmable Gate Arrays or Digital Signal Processors. 

### 2017-04-29 cav2017/cav2017.tex
missing article

@@
 synthesized in less than $17.2$ seconds.  We further show that, in a direct
-comparison, the abstraction-based approach (i.e., second approach) lowers the median
+comparison, the abstraction-based approach (i.e., the second approach) lowers the median
 run-time of our benchmarks by a factor of seven over the first approach

### 2017-04-29 cav2017/cav2017.tex
math font

@@
 architecture of the program synthesizer, the controller $K$ denotes $P$,
-$(x_0, u_k)$ represents $a$ and $\phi_{stability} \wedge \phi_{input} \wedge \phi_{init} \wedge \phi_{safety}$
+$(x_0, u_k)$ represents $a$ and
+$\phi_\mathit{stability} \wedge \phi_\mathit{input} \wedge
+\phi_\mathit{init} \wedge \phi_\mathit{safety}$
 denotes the specification $\sigma$.
@@
 % Once we have established convergence, we may examine the 
-% safety specification $\phi_{safety}$.
+% safety specification $\phi_\mathit{safety}$.
   $K \in \mathbb{R}\langle I_c,F_c\rangle^n$ that satisfies
@@
 %%   We obtain it by solving the SAT formula 
-%% $$\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{safety}$$ 
+%% $$\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_\mathit{safety}$$ 
 %% that satisfies the input constraint and Jury's criteria for 
@@
 $x_{k+1} \models \phi_\mathit{safety}$. %% For this purpose we require 
-%% an initial set $\phi_{init}= x_0 \in [\underline{x_0} \ \overline{x_0}]$ 
+%% an initial set $\phi_\mathit{init}= x_0 \in [\underline{x_0} \ \overline{x_0}]$ 
 %% from which the system progresses.

### 2017-05-01 cav2017/cav2017.tex
caps on keywords

--- 2017-04-28 cav2017/cav2017.tex
@@
 State-space dynamical models of physical systems; 
-Digital controllers; 
-Analogue-to-digital converters; 
-Time sampling; 
+digital controllers; 
+analogue-to-digital converters; 
+time sampling; 
 quantization; 
-Fixed-point arithmetic; 
+fixed-point arithmetic; 
 CEGIS; 
@@
 However, these methods have not been generalized to control synthesis. 
-We~remark that a synthesis algorithm that guarantees stability does not
+We~remark that a synthesis algorithm that guarantees satability does not
 ensure safety: the system might transitively visit an unsafe state that
@@
 Synthesis (CEGIS)~\cite{sketch}.  We prove their soundness by quantifying
-errors caused by digitalization and quantization effects that arise when
+errors caused digitalization and quantization effects that arise when
 time/value-discrete digital controller interacts with the continuous plant.
@@
 synthesized in less than $17.2$ seconds.  We further show that, in a direct
-comparison, the abstraction-based approach (i.e., second approach) lowers the median
+comparison, the abstraction-based approach (second) lowers the median
 run-time of our benchmarks by a factor of seven over the first approach
@@
   the various sources of imprecision in the implementation of the control
-  algorithm and in the modeling of the plant.
+  algorithm and in the modeling of plant.
 %
@@
 %
-where $k \in \mathbb N$ and $x_{0}=x(0)$ is the initial state.  $A_d$ and
-$B_d$ denote the matrices that describe the discretized plant dynamics, whereas
+where $k \in \mathbb N$ and with initial state $x_{0}=x(0)$.  $A_d$ and
+$B_d$ denote the matrices that describe the discretized plant dynamics and
 $A$ and $B$ the continuous plant dynamics.  Later, we will address the
@@
 
-Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t)$ and  $u_k$, respectively. 
+Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
 Feedback architectures can be employed to manipulate the properties and behaviors of the continuous process (the plant).   
 %reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
-We are interested in the synthesis of digital feedback control algorithms, 
+We are interested in the synthesis of digital feedback control algorithm, 
 as implemented on modern Field-Programmable Gate Arrays or Digital Signal Processors. 

### 2017-05-01 cav2017/cav2017.tex
wording

@@
 Linear Time Invariant (LTI) models represent a broad class of dynamical
-systems with significant impact in numerous application areas as in the life
+systems with significant impact in numerous application areas such as in life
 sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}. 

### 2017-05-01 cav2017/cav2017.tex
uniform spelling of naive

@@
 sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}. 
-Synthesis of controllers for LTI models is broadly investigated, however the
+The synthesis of controllers for LTI models is well understood, however the
 use of digital control architectures adds new challenges due to the effects
@@
 synthesis is challenging, particularly when the synthesis objective goes
-beyond classical stability.  There are recent methods for verifying more
-general reachability properties of a given controller~\cite{FLD+11,Fre05}. 
+beyond classical stability.  There are recent methods for verifying
+reachability properties of a given controller~\cite{FLD+11,Fre05}. 
 However, these methods have not been generalized to control synthesis. 
@@
 
-{\em The first approach} uses a {\em na\"ive} technique that starts by
+{\em The first approach} uses a na\"ive technique that starts by
 devising a digital controller that stabilizes the system while remaining
@@
 boundaries are not violated for any larger number of iterations.  As~it
-requires explicit unfolding up to the completeness threshold, this approach
+requires unfolding up to the completeness threshold, this approach
 is computationally expensive.
 
-Instead of explicitly unfolding the dynamics, {\em the second approach}
+Instead of unfolding the dynamics, {\em the second approach}
 employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to
-implicitly evaluate all possible progressions of the system simultaneously. 
+evaluate all possible progressions of the system simultaneously. 
 Additionally, the second approach uses {\em abstraction refinement},
@@
 %
-\item We give two novel algorithms: the first, naive one, relies on
+\item We give two novel algorithms: the first, na\"ive one, relies on
   an unfolding of the dynamics up to a completeness threshold, while the
@@
 approaches to synthesizing safe controllers: the first one is a baseline
-approach that relies on a naive explicit unfolding of the transition
+approach that relies on a na\"ive explicit unfolding of the transition
 relation, whereas the second uses abstraction to implicitly evaluate all
@@
 
-  The naive approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
+  The na\"ive approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
   %uses a multi-staged verification phase and performs solution generalization based on
@@
 
-%% Our naive approach
+%% Our na\"ive approach
 %% creates an abstraction of the system by establishing bounds on the
@@
 There are several cases for which the system may fail to find a controller. 
-For the naive approach, the completeness threshold may be too large, thus
+For the na\"ive approach, the completeness threshold may be too large, thus
 causing a timeout.  On the other hand, the abstraction-based approach may

### 2017-05-01 cav2017/cav2017.tex

@@
 synthesized in less than $17.2$ seconds.  We further show that, in a direct
-comparison, the abstraction-based approach (second) lowers the median
+comparison, the abstraction-based approach (i.e., the second approach) lowers the median
 run-time of our benchmarks by a factor of seven over the first approach

### 2017-05-01 cav2017/cav2017.tex
wordings

@@
 %In an alternative approach, we use a verification engine based 
-%on abstract acceleration~\cite{cattaruzza2015unbounded}, which avoids the explicit unwinding 
+%on abstract acceleration~\cite{cattaruzza2015unbounded}, which avoids the unwinding 
 %of the transition system necessary for the first approach. We introduce a CEGAR loop to this abstraction
@@
 linear dynamics for the digital controller, it avoids problems related to
-finite precision problem, but potentially suffers from state-space
+finite precision arithmetic, but potentially suffers from state-space
 explosion.  Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same
@@
 \label{eq:plant}
-x_{k+1} = A_d x_k+ B_d u_k. 
+x_{k+1} = A_d x_k+ B_d u_k
 \end{align} 
@@
 where $k \in \mathbb N$ and $x_{0}=x(0)$ is the initial state.  $A_d$ and
-$B_d$ denote the matrices that describe the discretized plant dynamics, whereas
-$A$ and $B$ the continuous plant dynamics.  Later, we will address the
-issue of variable quantization, as introduced by the ADC/DAC conversion
-blocks (Fig.~\ref{fig:digitalsystem}).
+$B_d$ denote the matrices that describe the discretized plant dynamics,
+whereas $A$ and $B$ give the continuous plant dynamics.  Later, we will
+address the issue of variable quantization, as introduced by the ADC/DAC
+conversion blocks (Fig.~\ref{fig:digitalsystem}).
 
@@
 %
-Here $K \in \mathbb{R}^{m \times n}$ is a state-feedback gain matrix, 
+Here, $K \in \mathbb{R}^{m \times n}$ is a state-feedback gain matrix, 
 and $r_{k}$ is a reference signal (again digital).   
@@
 one~\cite{astrom1997computer}.  In this paper, we express the stability
-specification $\phi_\mathit{stability}$ in terms of a check known as Jury's
-criterion~\cite{fadali}: this is an easy algebraic formula to select the
-entries of matrix $K$, so that the closed-loop dynamics are shaped as
-desired (see Appendix~\ref{sec:appendix-stability} for details).
+specification $\phi_\mathit{stability}$ in terms of a check known as
+\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic formula to
+select the entries of matrix $K$ so that the closed-loop dynamics are shaped
+as desired (see Appendix~\ref{sec:appendix-stability} for details).
 
@@
 \eqref{eq:closedloopss} meets given safety specifications.  A safety
-specification raises a requirement on the states of the model, such that the
-feedback controller (namely the choice of the gains matrix~$K$) must ensure
-that the states never exit such requirement.  Note that a stable,
-closed-loop system is not necessarily a safe system: indeed, the state
-values may leave the safe space whilst they converge to the equilibrium,
-which is typical in the case of oscillatory dynamics.  However, a safe
-system will always be stable.  In~this work, the safety property 
-is modeled as follows:
+specification gives raise to a requirement on the states of the model, such
+that the feedback controller (namely the choice of the gains matrix~$K$)
+must ensure that the state never violates the requirement.  Note that a
+stable, closed-loop system is not necessarily a safe system: indeed, the
+state values may leave the safe part of the state space while they converge
+to the equilibrium, which is typical in the case of oscillatory dynamics. 
+However, a safe system will always be stable.  In~this work, the safety
+property is modeled as follows:
 %
@@
 approaches to synthesizing safe controllers: the first one is a baseline
-approach that relies on a na\"ive explicit unfolding of the transition
-relation, whereas the second uses abstraction to implicitly evaluate all
-possible progressions of the system simultaneously.
+approach that relies on a na\"ive unfolding of the transition relation,
+whereas the second uses abstraction to evaluate all possible progressions of
+the system.
 
@@
 \label{synthesizer-general}
+
 The input specification provided to the program synthesizer is of the form
-%$\exists P .  \forall \vec{a}.  \sigma(\vec{a}, \vec{P})$ 
-$\exists P .\,  \forall a.\,  \sigma(a, P)$, 
-where $P$ ranges over functions, 
-$a$ ranges over ground terms, 
-and $\sigma$ is a quantifier-free formula.  
-We interpret the ground terms over some finite domain~$\mathcal{D}$.
-%
-The design of our synthesizer consists of two phases, an inductive
-synthesis phase and a validation phase, which interact via a finite
-set of test vectors {\sc inputs} that is updated incrementally.  Given
-the aforementioned specification $\sigma$, the inductive synthesis
-procedure tries to find an existential witness $P$ satisfying
-the specification $\sigma(a, P)$ for all $a$ in {\sc
-  inputs} (as opposed to all $a \in \mathcal{D}$).
-%
-If the synthesis phase succeeds in finding a witness~$P$, this
-witness is a candidate solution to the full synthesis formula.  We
-pass this candidate solution to the validation phase, which checks
-whether it is a full solution (i.e., $P$ satisfies the
-specification $\sigma(a, P)$ for all
-$a\in\mathcal{D}$).  If this is the case, then the algorithm
-terminates.  Otherwise, additional information is provided to the
-inductive synthesis phase in the form of a new counterexample that is
-added to the {\sc inputs} set and the loop iterates again.
-More details about the general architecture of the synthesizer can
-be found in~\cite{DBLP:conf/lpar/DavidKL15}.
+$\exists P .\, \forall a.\, \sigma(a, P)$, where $P$ ranges over functions,
+$a$ ranges over ground terms, and $\sigma$ is a quantifier-free formula. 
+We~interpret the ground terms over some finite domain~$\mathcal{D}$.
+%
+The design of our synthesizer consists of two phases, an inductive synthesis
+phase and a validation phase, which interact via a finite set of test
+vectors {\sc inputs} that is updated incrementally.  Given the
+aforementioned specification $\sigma$, the inductive synthesis procedure
+tries to find an existential witness $P$ satisfying the specification
+$\sigma(a, P)$ for all $a$ in {\sc inputs} (as opposed to all $a \in
+\mathcal{D}$).
+%
+If the synthesis phase succeeds in finding a witness~$P$, this witness is a
+candidate solution to the full synthesis formula.  We pass this candidate
+solution to the validation phase, which checks whether it is a full solution
+(i.e., $P$ satisfies the specification $\sigma(a, P)$ for all
+$a\in\mathcal{D}$).  If this is the case, then the algorithm terminates. 
+Otherwise, additional information is provided to the inductive synthesis
+phase in the form of a new counterexample that is added to the {\sc inputs}
+set and the loop iterates again.  More details about the general
+architecture of the synthesizer can be found
+in~\cite{DBLP:conf/lpar/DavidKL15}.
+%
 %% It is worth noting that each iteration of the loop adds a new input to
@@
      \coordinate (aux);
-   \node (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based \\Verifier};
-   \node (fp)  at ([xshift=0cm]aux.center) {\sf Fixed-point \\ Arithmetic\\Verifier};
-   \node (sv)  at ([xshift=2cm]aux.center) {\sf Completeness\\Verifier};
+   \node (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based \\ \sf Verifier};
+   \node (fp)  at ([xshift=0cm]aux.center) {\sf Fixed-point \\ \sf Arithmetic\\ \sf Verifier};
+   \node (sv)  at ([xshift=2cm]aux.center) {\sf Completeness\\ \sf Verifier};
    %\node (cv)  at ([xshift=3.1cm]aux.center) {\sf Sampling\\Verifier};
@@
 
-An overview of the controller synthesis is given in
-Fig.~\ref{fig:CEGIS-precision-increment}.  One important observation is
-that, for this approach, we verify and synthesize a controller over $k$ time
-steps.  We~then compute a completeness threshold, $\overline{k}$, for this
-controller, and verify correctness for $\overline{k}$ time steps. 
-Essentially, $\overline{k}$ is the number of iterations required to
-sufficiently unwind the closed-loop state-space system such that the
-boundaries are not violated for any $k{>}\overline{k}$.
+An overview of the algorithm for controller synthesis is given in
+Fig.~\ref{fig:CEGIS-precision-increment}.  One important observation is that
+we verify and synthesize a controller over $k$ time steps.  We~then compute
+a completeness threshold, $\overline{k}$, for this controller, and verify
+correctness for $\overline{k}$ time steps.  Essentially, $\overline{k}$ is
+the number of iterations required to sufficiently unwind the closed-loop
+state-space system such that the boundaries are not violated for any
+$k{>}\overline{k}$.
 
@@
 \begin{proof}
+%
 A stable control system is known to have converging dynamics.  Assume the
@@
 point (origin) decreases over time within subspaces related to real-valued
-eigenvalues; however, this in general not the case when dealing with complex
-eigenvalues.  Consider the closed-loop matrix, which updates the states
-every discrete time step, and select the eigenvalue $\vartheta$ with
-smallest (non-trivial) imaginary value.  At every consecutive time steps
-$kT_s, (k+1)T_s$, the dynamics projected on the corresponding eigenspace
-rotate of $\vartheta T_s$ radiants.  Thus, taking $k{\leq}\overline{k}$ as the
-ceiling of $\frac{2\pi}{\vartheta T_s}$, after $k{\leq}\overline{k}$ steps
-we have completed a full rotation, which results in a point closer to the
-origin, and it is the completeness threshold.
+eigenvalues; however, this is not the case in general when dealing with
+complex eigenvalues.  Consider the closed-loop matrix that updates the
+states in every discrete time step, and select the eigenvalue $\vartheta$
+with the smallest (non-trivial) imaginary value.  At every consecutive time
+step $kT_s, (k+1)T_s$, the dynamics projected on the corresponding
+eigenspace rotate $\vartheta T_s$ radiants.  Thus, taking
+$k{\leq}\overline{k}$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, after
+$k{\leq}\overline{k}$ steps we have completed a full rotation, which results
+in a point closer to the origin. This is the completeness threshold. 
+%
 \end{proof}
@@
 state-feedback controllers that ensure both stability and safety over the
-state-space representation.  The first approach relies on explicit unfolding
-of the closed-loop model dynamics up to a completeness threshold, whilst the
-second one applies abstraction refinement and acceleration to increase speed
-whilst retaining soundness.
+state-space representation.  The first approach relies on unfolding of the
+closed-loop model dynamics up to a completeness threshold, whilst the second
+one applies abstraction refinement and acceleration to increase speed whilst
+retaining soundness.
 %

### 2017-05-01 cav2017/cav2017.tex
cite for completeness threshold

@@
 
-{\em The first approach} uses a na\"ive technique that starts by
-devising a digital controller that stabilizes the system while remaining
-safe for a pre-selected time horizon and a single initial state; then, it
-verifies unbounded safety by unfolding the dynamics of the system,
-considering the full hyper-cube of initial states, and checking a {\em
-completeness threshold}, i.e., the number of iterations required to
-sufficiently unwind the closed-loop state-space system such that the
-boundaries are not violated for any larger number of iterations.  As~it
-requires unfolding up to the completeness threshold, this approach
-is computationally expensive.
+{\em The first approach} uses a na\"ive technique that starts by devising a
+digital controller that stabilizes the system while remaining safe for a
+pre-selected time horizon and a single initial state; then, it verifies
+unbounded safety by unfolding the dynamics of the system, considering the
+full hyper-cube of initial states, and checking a {\em completeness
+threshold}~\cite{DBLP:conf/vmcai/KroeningS03}, i.e., the number of
+iterations required to sufficiently unwind the closed-loop state-space
+system such that the boundaries are not violated for any larger number of
+iterations.  As~it requires unfolding up to the completeness threshold, this
+approach is computationally expensive.
 
@@
 we verify and synthesize a controller over $k$ time steps.  We~then compute
-a completeness threshold, $\overline{k}$, for this controller, and verify
-correctness for $\overline{k}$ time steps.  Essentially, $\overline{k}$ is
-the number of iterations required to sufficiently unwind the closed-loop
-state-space system such that the boundaries are not violated for any
-$k{>}\overline{k}$.
+a completeness threshold~\cite{DBLP:conf/vmcai/KroeningS03}, $\overline{k}$,
+for this controller, and verify correctness for $\overline{k}$ time steps. 
+Essentially, $\overline{k}$ is the number of iterations required to
+sufficiently unwind the closed-loop state-space system such that the
+boundaries are not violated for any $k{>}\overline{k}$.
 
@@
 completeness threshold $\overline{k}$ for the current candidate $K$ and
-check that $k{\leq}\overline{k}$.  This is done according to the argument given above
-and illustrated in Fig.~\ref{fig:ct}.
+check that $k{\leq}\overline{k}$.  This is done according to the argument
+given above and illustrated in Fig.~\ref{fig:ct}.
 
@@
 state-space representation.  The first approach relies on unfolding of the
-closed-loop model dynamics up to a completeness threshold, whilst the second
+closed-loop model dynamics up to a completeness threshold, while the second
 one applies abstraction refinement and acceleration to increase speed whilst

### 2017-05-01 cav2017/cav2017.tex
nudge

@@
 
-\item The inductive synthesis phase (i.e., {\sc synthesize}) uses BMC to
+\item The inductive synthesis phase ({\sc synthesize}) uses BMC to
 compute a candidate solution $K$ that satisfies both the stability criteria
@@
 exists a $K$ that is safe for at least one $x_0$ in our set of all possible
-initial states.  This is sound if the current $k$ is below the completeness
-threshold, which we assume to be true in the {\sc synthesize} phase.  We
-also assume some precision $\langle I_p,F_p\rangle$ for the plant and a
-sampling rate.  The checks that these assumptions hold are performed by
-subsequent {\sc verify} stages.
+initial states.  This is sound if the current $k$ exceeds the completeness
+threshold.  We~also assume some precision $\langle I_p,F_p\rangle$ for the
+plant and a sampling rate.  The checks that these assumptions hold are
+performed by subsequent {\sc verify} stages.
 
@@
 \begin{algorithm}[]
-\scriptsize
+%\scriptsize
 \begin{algorithmic}[1]

### 2017-05-01 cav2017/cav2017.tex
fix for Alg 1
wording

@@
 states in every discrete time step, and select the eigenvalue $\vartheta$
-with the smallest (non-trivial) imaginary value.  At every consecutive time
-step $kT_s, (k+1)T_s$, the dynamics projected on the corresponding
-eigenspace rotate $\vartheta T_s$ radiants.  Thus, taking
+with the smallest (non-trivial) imaginary value.  Between every pair of
+consecutive time steps $k\,T_s$ and $(k+1)\,T_s$, the dynamics projected on
+the corresponding eigenspace rotate $\vartheta T_s$ radiants.  Thus, taking
 $k{\leq}\overline{k}$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, after
@@
 exists a $K$ that is safe for at least one $x_0$ in our set of all possible
-initial states.  This is sound if the current $k$ exceeds the completeness
+initial states.  This is sound if the current $k$ is below the completeness
 threshold.  We~also assume some precision $\langle I_p,F_p\rangle$ for the
@@
  \State set $x_0$ to be a vertex state, e.g., $[\underline{x_0},\underline{x_0}]$	
-\For {($c=0; c < 2^\mathit{Num\_States}; c++$)}
+\For {($c=0;~c < 2^\mathit{Num\_States};~c\mbox{++}$)}
   %\State assert($ \underline{x_0}  \leq x_0 \leq \overline{x_0}$)
-	\While{$i=0; i< k; i++$}
+	\For{($i=0;~i< k;~i\mbox{++}$)}
 		%\State $u = (\langle I_p,F_p\rangle)((\langle I_c,F_c\rangle)K * (\langle I_c,F_c\rangle) x)$
@@
 		\State assert($\underline{x} \leq x \leq \overline{x}$ )
-  	\EndWhile
+  	\EndFor
   	\State set $x_0$ to be a new vertex state
@@
 \end{algorithmic}
-\label{alg:safetycheck}
+\caption{Safety check\label{alg:safetycheck}}
 \end{algorithm}

### 2017-05-02 cav2017/cav2017.tex
TODOs
wording

--- 2017-05-01 cav2017/cav2017.tex
@@
 State-space dynamical models of physical systems; 
-digital controllers; 
-analogue-to-digital converters; 
-time sampling; 
+Digital controllers; 
+Analogue-to-digital converters; 
+Time sampling; 
 quantization; 
-fixed-point arithmetic; 
+Fixed-point arithmetic; 
 CEGIS; 
@@
 Linear Time Invariant (LTI) models represent a broad class of dynamical
-systems with significant impact in numerous application areas such as in life
+systems with significant impact in numerous application areas as in the life
 sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}. 
-The synthesis of controllers for LTI models is well understood, however the
+Synthesis of controllers for LTI models is broadly investigated, however the
 use of digital control architectures adds new challenges due to the effects
@@
 synthesis is challenging, particularly when the synthesis objective goes
-beyond classical stability.  There are recent methods for verifying
-reachability properties of a given controller~\cite{FLD+11,Fre05}. 
+beyond classical stability.  There are recent methods for verifying more
+general reachability properties of a given controller~\cite{FLD+11,Fre05}. 
 However, these methods have not been generalized to control synthesis. 
@@
 
-{\em The first approach} uses a na\"ive technique that starts by devising a
-digital controller that stabilizes the system while remaining safe for a
-pre-selected time horizon and a single initial state; then, it verifies
-unbounded safety by unfolding the dynamics of the system, considering the
-full hyper-cube of initial states, and checking a {\em completeness
-threshold}~\cite{DBLP:conf/vmcai/KroeningS03}, i.e., the number of
-iterations required to sufficiently unwind the closed-loop state-space
-system such that the boundaries are not violated for any larger number of
-iterations.  As~it requires unfolding up to the completeness threshold, this
-approach is computationally expensive.
-
-Instead of unfolding the dynamics, {\em the second approach}
+{\em The first approach} uses a {\em na\"ive} technique that starts by
+devising a digital controller that stabilizes the system while remaining
+safe for a pre-selected time horizon and a single initial state; then, it
+verifies unbounded safety by unfolding the dynamics of the system,
+considering the full hyper-cube of initial states, and checking a {\em
+completeness threshold}, i.e., the number of iterations required to
+sufficiently unwind the closed-loop state-space system such that the
+boundaries are not violated for any larger number of iterations.  As~it
+requires explicit unfolding up to the completeness threshold, this approach
+is computationally expensive.
+
+Instead of explicitly unfolding the dynamics, {\em the second approach}
 employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to
-evaluate all possible progressions of the system simultaneously. 
+implicitly evaluate all possible progressions of the system simultaneously. 
 Additionally, the second approach uses {\em abstraction refinement},
@@
 %
-\item We give two novel algorithms: the first, na\"ive one, relies on
+\item We give two novel algorithms: the first, naive one, relies on
   an unfolding of the dynamics up to a completeness threshold, while the
@@
 %In an alternative approach, we use a verification engine based 
-%on abstract acceleration~\cite{cattaruzza2015unbounded}, which avoids the unwinding 
+%on abstract acceleration~\cite{cattaruzza2015unbounded}, which avoids the explicit unwinding 
 %of the transition system necessary for the first approach. We introduce a CEGAR loop to this abstraction
@@
 linear dynamics for the digital controller, it avoids problems related to
-finite precision arithmetic, but potentially suffers from state-space
+finite precision problem, but potentially suffers from state-space
 explosion.  Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same
@@
 \label{eq:plant}
-x_{k+1} = A_d x_k+ B_d u_k
+x_{k+1} = A_d x_k+ B_d u_k. 
 \end{align} 
@@
 where $k \in \mathbb N$ and $x_{0}=x(0)$ is the initial state.  $A_d$ and
-$B_d$ denote the matrices that describe the discretized plant dynamics,
-whereas $A$ and $B$ give the continuous plant dynamics.  Later, we will
-address the issue of variable quantization, as introduced by the ADC/DAC
-conversion blocks (Fig.~\ref{fig:digitalsystem}).
+$B_d$ denote the matrices that describe the discretized plant dynamics, whereas
+$A$ and $B$ denote the continuous plant dynamics.  Later, we will address the
+issue of variable quantization, as introduced by the ADC/DAC conversion
+blocks (Fig.~\ref{fig:digitalsystem}).
 
@@
 %
-Here, $K \in \mathbb{R}^{m \times n}$ is a state-feedback gain matrix, 
+Here $K \in \mathbb{R}^{m \times n}$ is a state-feedback gain matrix, 
 and $r_{k}$ is a reference signal (again digital).   
@@
 one~\cite{astrom1997computer}.  In this paper, we express the stability
-specification $\phi_\mathit{stability}$ in terms of a check known as
-\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic formula to
-select the entries of matrix $K$ so that the closed-loop dynamics are shaped
-as desired (see Appendix~\ref{sec:appendix-stability} for details).
+specification $\phi_\mathit{stability}$ in terms of a check known as Jury's
+criterion~\cite{fadali}: this is an easy algebraic formula to select the
+entries of matrix $K$, so that the closed-loop dynamics are shaped as
+desired (see Appendix~\ref{sec:appendix-stability} for details).
 
@@
 \eqref{eq:closedloopss} meets given safety specifications.  A safety
-specification gives raise to a requirement on the states of the model, such
-that the feedback controller (namely the choice of the gains matrix~$K$)
-must ensure that the state never violates the requirement.  Note that a
-stable, closed-loop system is not necessarily a safe system: indeed, the
-state values may leave the safe part of the state space while they converge
-to the equilibrium, which is typical in the case of oscillatory dynamics. 
-However, a safe system will always be stable.  In~this work, the safety
-property is modeled as follows:
+specification raises a requirement on the states of the model, such that the
+feedback controller (namely the choice of the gains matrix~$K$) must ensure
+that the states never exit such requirement.  Note that a stable,
+closed-loop system is not necessarily a safe system: indeed, the state
+values may leave the safe space whilst they converge to the equilibrium,
+which is typical in the case of oscillatory dynamics.  However, a safe
+system will always be stable.  In~this work, the safety property 
+is modeled as follows:
 %
@@
 approaches to synthesizing safe controllers: the first one is a baseline
-approach that relies on a na\"ive unfolding of the transition relation,
-whereas the second uses abstraction to evaluate all possible progressions of
-the system.
+approach that relies on a naive explicit unfolding of the transition
+relation, whereas the second uses abstraction to implicitly evaluate all
+possible progressions of the system simultaneously.
 
@@
 \label{synthesizer-general}
-
 The input specification provided to the program synthesizer is of the form
-$\exists P .\, \forall a.\, \sigma(a, P)$, where $P$ ranges over functions,
-$a$ ranges over ground terms, and $\sigma$ is a quantifier-free formula. 
-We~interpret the ground terms over some finite domain~$\mathcal{D}$.
-%
-The design of our synthesizer consists of two phases, an inductive synthesis
-phase and a validation phase, which interact via a finite set of test
-vectors {\sc inputs} that is updated incrementally.  Given the
-aforementioned specification $\sigma$, the inductive synthesis procedure
-tries to find an existential witness $P$ satisfying the specification
-$\sigma(a, P)$ for all $a$ in {\sc inputs} (as opposed to all $a \in
-\mathcal{D}$).
-%
-If the synthesis phase succeeds in finding a witness~$P$, this witness is a
-candidate solution to the full synthesis formula.  We pass this candidate
-solution to the validation phase, which checks whether it is a full solution
-(i.e., $P$ satisfies the specification $\sigma(a, P)$ for all
-$a\in\mathcal{D}$).  If this is the case, then the algorithm terminates. 
-Otherwise, additional information is provided to the inductive synthesis
-phase in the form of a new counterexample that is added to the {\sc inputs}
-set and the loop iterates again.  More details about the general
-architecture of the synthesizer can be found
-in~\cite{DBLP:conf/lpar/DavidKL15}.
-%
+%$\exists P .  \forall \vec{a}.  \sigma(\vec{a}, \vec{P})$ 
+$\exists P .\,  \forall a.\,  \sigma(a, P)$, 
+where $P$ ranges over functions, 
+$a$ ranges over ground terms, 
+and $\sigma$ is a quantifier-free formula.  
+We interpret the ground terms over some finite domain~$\mathcal{D}$.
+%
+The design of our synthesizer consists of two phases, an inductive
+synthesis phase and a validation phase, which interact via a finite
+set of test vectors {\sc inputs} that is updated incrementally.  Given
+the aforementioned specification $\sigma$, the inductive synthesis
+procedure tries to find an existential witness $P$ satisfying
+the specification $\sigma(a, P)$ for all $a$ in {\sc
+  inputs} (as opposed to all $a \in \mathcal{D}$).
+%
+If the synthesis phase succeeds in finding a witness~$P$, this
+witness is a candidate solution to the full synthesis formula.  We
+pass this candidate solution to the validation phase, which checks
+whether it is a full solution (i.e., $P$ satisfies the
+specification $\sigma(a, P)$ for all
+$a\in\mathcal{D}$).  If this is the case, then the algorithm
+terminates.  Otherwise, additional information is provided to the
+inductive synthesis phase in the form of a new counterexample that is
+added to the {\sc inputs} set and the loop iterates again.
+More details about the general architecture of the synthesizer can
+be found in~\cite{DBLP:conf/lpar/DavidKL15}.
 %% It is worth noting that each iteration of the loop adds a new input to
@@
      \coordinate (aux);
-   \node (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based \\ \sf Verifier};
-   \node (fp)  at ([xshift=0cm]aux.center) {\sf Fixed-point \\ \sf Arithmetic\\ \sf Verifier};
-   \node (sv)  at ([xshift=2cm]aux.center) {\sf Completeness\\ \sf Verifier};
+   \node (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based \\Verifier};
+   \node (fp)  at ([xshift=0cm]aux.center) {\sf Fixed-point \\ Arithmetic\\Verifier};
+   \node (sv)  at ([xshift=2cm]aux.center) {\sf Completeness\\Verifier};
    %\node (cv)  at ([xshift=3.1cm]aux.center) {\sf Sampling\\Verifier};
@@
 
-An overview of the algorithm for controller synthesis is given in
-Fig.~\ref{fig:CEGIS-precision-increment}.  One important observation is that
-we verify and synthesize a controller over $k$ time steps.  We~then compute
-a completeness threshold~\cite{DBLP:conf/vmcai/KroeningS03}, $\overline{k}$,
-for this controller, and verify correctness for $\overline{k}$ time steps. 
+An overview of the controller synthesis is given in
+Fig.~\ref{fig:CEGIS-precision-increment}.  One important observation is
+that, for this approach, we verify and synthesize a controller over $k$ time
+steps.  We~then compute a completeness threshold, $\overline{k}$, for this
+controller, and verify correctness for $\overline{k}$ time steps. 
 Essentially, $\overline{k}$ is the number of iterations required to
@@
 \begin{proof}
-%
 A stable control system is known to have converging dynamics.  Assume the
@@
 point (origin) decreases over time within subspaces related to real-valued
-eigenvalues; however, this is not the case in general when dealing with
-complex eigenvalues.  Consider the closed-loop matrix that updates the
-states in every discrete time step, and select the eigenvalue $\vartheta$
-with the smallest (non-trivial) imaginary value.  At every consecutive time
-step $kT_s, (k+1)T_s$, the dynamics projected on the corresponding
-eigenspace rotate $\vartheta T_s$ radiants.  Thus, taking
-$k{\leq}\overline{k}$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, after
-$k{\leq}\overline{k}$ steps we have completed a full rotation, which results
-in a point closer to the origin. This is the completeness threshold. 
-%
+eigenvalues; however, this in general not the case when dealing with complex
+eigenvalues.  Consider the closed-loop matrix, which updates the states
+every discrete time step, and select the eigenvalue $\vartheta$ with
+smallest (non-trivial) imaginary value.  At every consecutive time steps
+$kT_s, (k+1)T_s$, the dynamics projected on the corresponding eigenspace
+rotate of $\vartheta T_s$ radiants.  Thus, taking $k{\leq}\overline{k}$ as the
+ceiling of $\frac{2\pi}{\vartheta T_s}$, after $k{\leq}\overline{k}$ steps
+we have completed a full rotation, which results in a point closer to the
+origin, and it is the completeness threshold.
 \end{proof}
@@
 completeness threshold $\overline{k}$ for the current candidate $K$ and
-check that $k{\leq}\overline{k}$.  This is done according to the argument
-given above and illustrated in Fig.~\ref{fig:ct}.
+check that $k{\leq}\overline{k}$.  This is done according to the argument given above
+and illustrated in Fig.~\ref{fig:ct}.
 
@@
 
-  The na\"ive approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
+  The naive approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
   %uses a multi-staged verification phase and performs solution generalization based on
@@
 
-%% Our na\"ive approach
+%% Our naive approach
 %% creates an abstraction of the system by establishing bounds on the
@@
 There are several cases for which the system may fail to find a controller. 
-For the na\"ive approach, the completeness threshold may be too large, thus
+For the naive approach, the completeness threshold may be too large, thus
 causing a timeout.  On the other hand, the abstraction-based approach may
@@
 state-feedback controllers that ensure both stability and safety over the
-state-space representation.  The first approach relies on unfolding of the
-closed-loop model dynamics up to a completeness threshold, while the second
-one applies abstraction refinement and acceleration to increase speed whilst
-retaining soundness.
+state-space representation.  The first approach relies on explicit unfolding
+of the closed-loop model dynamics up to a completeness threshold, whilst the
+second one applies abstraction refinement and acceleration to increase speed
+whilst retaining soundness.
 %

### 2017-05-02 cav2017/cav2017.tex

--- 2017-05-01 cav2017/cav2017.tex
@@
 
+\todo{There is no reference to Alg.~\ref{alg:safetycheck}}
+
 \item The second {\sc verify} stage, {\sc precision}, 
@@
 given above and illustrated in Fig.~\ref{fig:ct}.
+
+\end{enumerate}
+
+\todo{check whether the above/below CT story is right}
 
@@
 \end{figure*}
-
-\end{enumerate}
 

### 2017-05-02 cav2017/cav2017.tex
fix CT

@@
 consecutive time steps $k\,T_s$ and $(k+1)\,T_s$, the dynamics projected on
-the corresponding eigenspace rotate $\vartheta T_s$ radiants.  Thus, taking
-$k{\leq}\overline{k}$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, after
-$k{\leq}\overline{k}$ steps we have completed a full rotation, which results
+the corresponding eigenspace rotate $\vartheta T_s$ radians.  Thus, taking
+$\overline{k}$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, after
+$k{\geq}\overline{k}$ steps we have completed a full rotation, which results
 in a point closer to the origin.  This is the completeness threshold.
+
 %
@@
 exists a $K$ that is safe for at least one $x_0$ in our set of all possible
-initial states.  This is sound if the current $k$ is below the completeness
+initial states.  This is sound if the current $k$ is greater than the completeness
 threshold.  We~also assume some precision $\langle I_p,F_p\rangle$ for the
@@
 to the previously synthesized controller $k$ steps, we check that the safety
-specification holds for any initial state.
-
-\todo{There is no reference to Alg.~\ref{alg:safetycheck}}
+specification holds for any initial state. This is shown in Alg.~~\ref{alg:safetycheck}.
 
@@
 completeness threshold $\overline{k}$ for the current candidate $K$ and
-check that $k{\leq}\overline{k}$.  This is done according to the argument
+check that $k{\geq}\overline{k}$.  This is done according to the argument
 given above and illustrated in Fig.~\ref{fig:ct}.
@@
 
-\todo{check whether the above/below CT story is right}
+\todo{EP: I've changed $\leq$ to $\geq$. Also changed: 
+"take $k{\leq}\overline{k}$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$" to 
+"take $\overline{k}$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$"; is this right ?
+\textcolor{gray}{check whether the above/below CT story is right. }}
 

### 2017-05-02 cav2017/cav2017.tex
aa citation

@@
 
-\todo{Refer to the SAS paper in this section.}
+%\todo{Refer to the SAS paper in this section.}
 
@@
 we  find a controller for a continuous initial set of states and set of inputs, 
-  over an abstraction of the continuous dynamics that conforms to
+  over an abstraction of the continuous dynamics (taken from \cite{cattaruzza2015unbounded}) that conforms to
   witness proofs at specific times. %% It further generalizes the

### 2017-05-02 cav2017/cav2017.tex
trimming to size

@@
 %
-\keywords{
-State-space dynamical models of physical systems; 
-digital controllers; 
-analogue-to-digital converters; 
-time sampling; 
-quantization; 
-fixed-point arithmetic; 
-CEGIS; 
-safety requirements. 
-}
+%\keywords{
+%State-space dynamical models of physical systems; 
+%digital controllers; 
+%analogue-to-digital converters; 
+%time sampling; 
+%quantization; 
+%fixed-point arithmetic; 
+%CEGIS; 
+%safety requirements. 
+%}
 \end{abstract}
@@
 \todo{Clarify challenges: FWL (rounding, truncation), quantisation (ADC, DAC).}
-
+%
 \todo{Discuss numerical (HSCC'17) vs. algorithmical soundness (CAV'17).}
@@
 we ideally would like to work on the continuous-time plant, in this work
-Eq.~\eqref{eq:ode} is soundly discretized in time (as shown in
-Appendix~\ref{sec:appendix:LTIbackground}) into
+Eq.~\eqref{eq:ode} is soundly discretized in time~\cite{fadali} into
 %
@@
 select the entries of matrix $K$ so that the closed-loop dynamics are shaped
-as desired (see Appendix~\ref{sec:appendix-stability} for details).
+as desired.
 
@@
 
-\todo{EP: I've changed $\leq$ to $\geq$. Also changed: 
-"take $k{\leq}\overline{k}$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$" to 
-"take $\overline{k}$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$"; is this right ?
-\textcolor{gray}{check whether the above/below CT story is right. }}
-
 \begin{figure*}[t]
@@
 
-%\todo{Refer to the SAS paper in this section.}
+\todo{Refer to the SAS paper in this section.}
 
@@
 %
-Let us consider the Helicopter example in Table
-\ref{table:State-space-benchmarks} with discretized dynamics
+Let us consider the following example with discretized dynamics
 %
@@
 
-Section~\ref{sec:BenchmarksforStateSpace} in the appendix summarizes all our
-benchmarks, which are SISO models (Section~\ref{sec:preliminaries}).  The
+%Section~\ref{sec:BenchmarksforStateSpace} in the appendix summarizes all our
+Our benchmarks are SISO models (Section~\ref{sec:preliminaries}).  The
 Inverted Pendulum appears to be a two output system, but it was treated as
@@
 
-All benchmarks were discretized with different sample times using 
-the approach described in Appendix~\ref{sec:appendix:LTIbackground}. 
+All benchmarks were discretized with different sample times~\cite{fadali}. 
 All experiments were performed considering $\underline{x_{i}}=-1$ and 
@@
   Although, if it's always one, I'm not sure how interesting it is.. }
-
+\vskip -0.5cm
 The median run-time for our benchmark set is 9.4\,s.  Overall, the average
@@
 
-\newpage
+%\newpage
 
@@
 
-\newpage
 \appendix
-
-\todo{Integrate Appendix in the actual paper.}
 
@@
 %-------------------------------
-\subsection{Encoding of Jury's criterion}
-%-------------------------------
-
-For a closed-loop system as~\eqref{eq:closedloopss}, 
-the characteristic polynomial $P(z)$ should be computed as follows:
-%
-\begin{equation}
-P(z)= \det( z I_{n} - A_d + B_d K ) \,,
-\end{equation}
-%
-where $I_{n}$ is the $n$-th order identity matrix.
-
-Jury's criterion provides necessary and sufficient conditions for the
-eigenvalues to be within the unit circle and, consequently, for the system
-is stable~\cite{fadali}.  Given a polynomial $P(z)$ of the form
-%
-$$
-P(z) = a_{0}z^{N} + a_{1}z^{N-1} + ... a_{N-1}z + a_{N} = 0, \;\; a_{0}\neq 0 \,,
-$$
-%
-Jury's criterion explores solely the coefficients
-$a_{0},a_{1},\ldots,a_{N-1}$ of $P(z)$ for checking stability, which we
-capture as property $\phi_\mathit{stability}$, as detailed below.
-
-This study limits itself to explain the encoding of Jury's criterion for
-formal synthesis.  For the stability test procedure, the following matrix
-$M=[m_{ij}]_{(2N-2)\times N}$ is built from the coefficients of $P(z)$:
-%
-$$
-M=\left[
-\begin{matrix}
-  V^{(0)} \\
-  V^{(1)} \\
-  \vdots \\
-  V^{(N-2)}
- \end{matrix}
-\right]\mbox{,}
-$$
-\noindent where $V^{(k)}=[v^{(k)}_{ij}]_{2\times N}$ is such that
-$$
-v^{(0)}_{ij}=\begin{cases} 
-a_{j-1}, & \mbox{if } i=1 \\   v^{(0)}_{(1)(N-j+1)}, & \mbox{if } i=2 
-\end{cases}\mbox{, and} 
-$$
-$$
-v^{(k)}_{ij}=\begin{cases} 
-0, & \mbox{if } j>n-k\\
-v^{(k-1)}_{1j}-v^{(k-1)}_{2j}\cdot\frac{v^{(k-1)}_{11}}{v^{(k-1)}_{21}}, & \mbox{if } j\leq n-k  \mbox{ and } i=1 \\
-v^{(k)}_{(1)(N-j+1)}, & \mbox{if } j\leq n-k \mbox{ and } i=2 \\
-\end{cases} \mbox{,}
-$$
-\noindent where $k\in\mathbb{Z}$, such that $0<k<N-2$. $P(z)$ is the 
-characteristic polynomial of a stable system if and only if the following 
-four propositions hold:
-\begin{itemize}
-\item $R_{1}$: $P(1)>0$;
-\item $R_{2}$: $(-1)^{N}P(-1)>0$;
-\item $R_{3}$: $\vert{a_{0}}\vert <a_{N}$;
-\item $R_{4}$: $m_{11}>0\iff (m_{31}>0)\wedge (m_{51}>0)\wedge \ldots \wedge (m_{(2N-3)(1)}>0)$.
-\end{itemize}
-%
-The stability property $\phi_\mathit{stability}$ is encoded as the following formula:
-$$
-\phi_\mathit{stability}\iff \ (R_{1} \wedge R_{2} \wedge R_{3} \wedge R_{4}).
-$$
+%\subsection{Encoding of Jury's criterion}
+%-------------------------------
+
+%For a closed-loop system as~\eqref{eq:closedloopss}, 
+%the characteristic polynomial $P(z)$ should be computed as follows:
+%
+%\begin{equation}
+%P(z)= \det( z I_{n} - A_d + B_d K ) \,,
+%\end{equation}
+%
+%where $I_{n}$ is the $n$-th order identity matrix.
+
+%Jury's criterion provides necessary and sufficient conditions for the
+%eigenvalues to be within the unit circle and, consequently, for the system
+%is stable~\cite{fadali}.  Given a polynomial $P(z)$ of the form
+%
+%$$
+%P(z) = a_{0}z^{N} + a_{1}z^{N-1} + ... a_{N-1}z + a_{N} = 0, \;\; a_{0}\neq 0 \,,
+%$$
+%
+%Jury's criterion explores solely the coefficients
+%$a_{0},a_{1},\ldots,a_{N-1}$ of $P(z)$ for checking stability, which we
+%capture as property $\phi_\mathit{stability}$, as detailed below.
+
+%This study limits itself to explain the encoding of Jury's criterion for
+%formal synthesis.  For the stability test procedure, the following matrix
+%$M=[m_{ij}]_{(2N-2)\times N}$ is built from the coefficients of $P(z)$:
+%
+%$$
+%M=\left[
+%\begin{matrix}
+%  V^{(0)} \\
+%  V^{(1)} \\
+%  \vdots \\
+%  V^{(N-2)}
+% \end{matrix}
+%\right]\mbox{,}
+%$$
+%\noindent where $V^{(k)}=[v^{(k)}_{ij}]_{2\times N}$ is such that
+%$$
+%v^{(0)}_{ij}=\begin{cases} 
+%a_{j-1}, & \mbox{if } i=1 \\   v^{(0)}_{(1)(N-j+1)}, & \mbox{if } i=2 
+%\end{cases}\mbox{, and} 
+%$$
+%$$
+%v^{(k)}_{ij}=\begin{cases} 
+%0, & \mbox{if } j>n-k\\
+%v^{(k-1)}_{1j}-v^{(k-1)}_{2j}\cdot\frac{v^{(k-1)}_{11}}{v^{(k-1)}_{21}}, & \mbox{if } j\leq n-k  \mbox{ and } i=1 \\
+%v^{(k)}_{(1)(N-j+1)}, & \mbox{if } j\leq n-k \mbox{ and } i=2 \\
+%\end{cases} \mbox{,}
+%$$
+%\noindent where $k\in\mathbb{Z}$, such that $0<k<N-2$. $P(z)$ is the 
+%characteristic polynomial of a stable system if and only if the following 
+%four propositions hold:
+%\begin{itemize}
+%\item $R_{1}$: $P(1)>0$;
+%\item $R_{2}$: $(-1)^{N}P(-1)>0$;
+%\item $R_{3}$: $\vert{a_{0}}\vert <a_{N}$;
+%\item $R_{4}$: $m_{11}>0\iff (m_{31}>0)\wedge (m_{51}>0)\wedge \ldots \wedge (m_{(2N-3)(1)}>0)$.
+%\end{itemize}
+%
+%The stability property $\phi_\mathit{stability}$ is encoded as the following formula:
+%$$
+%\phi_\mathit{stability}\iff \ (R_{1} \wedge R_{2} \wedge R_{3} \wedge R_{4}).
+%$$
 
@@
 
-The proof above relies on the fact that the relationship between states and
+The proof for Jury's criteria~\cite{fadali} relies on the fact that the relationship between states and
 next states is defined by $x_{k+1} = (A_d - B_dK) \cdot x_k$, all computed
@@
       &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
-x_{3}  &=(A_d  - B_dK)^3x_0 + (A_d  - B_dK)^2B_dK\delta + (A_d  - B_dK)B_dK\delta + B_dK\delta\\
+%x_{3}  &=(A_d  - B_dK)^3x_0 + (A_d  - B_dK)^2B_dK\delta + (A_d  - B_dK)B_dK\delta + B_dK\delta\\
 x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Time discretization of continuous-space dynamics}
+%\subsection{Time discretization of continuous-space dynamics}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-A dynamical system is a system in which a function describes the progression
-of a state over time.  In a continuous domain with linear dynamics, it is
-described by a first-order Ordinary Differential Equation (ODE).
-%
-\begin{equation}
-\dot{x}(t)=Ax(t)+Bu(t) \,.
-\label{eq:dynamical}
-\end{equation}
+%
+%A dynamical system is a system in which a function describes the progression
+%of a state over time.  In a continuous domain with linear dynamics, it is
+%described by a first-order Ordinary Differential Equation (ODE).
+%
+%\begin{equation}
+%\dot{x}(t)=Ax(t)+Bu(t) \,.
+%\label{eq:dynamical}
+%\end{equation}
 %Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
@@
 %\end{equation}
-
-Discretization of an continuous dynamical system turns the ODE into a
-difference equation, assuming zero-order hold for the input $u$,
+%
+%Discretization of an continuous dynamical system turns the ODE into a
+%difference equation, assuming zero-order hold for the input $u$,
 %
 %and continuous integration for the noise $\vec{w}$, 
-to
-\begin{align}
-\label{eq:discretization}
-x_{k+1} &= A_d x_k+B_d u_k \,,
+%to
+%\begin{align}
+%\label{eq:discretization}
+%x_{k+1} &= A_d x_k+B_d u_k \,,
 %\\y_k &= \vec{C}_d \vec{x}_ k + \vec{D}_d \vec{u}_ k. 
-\end{align}
+%\end{align}
 %with covariance for $\vec{w}_k \sim \mathcal{N}(0,Q_d)$,
-where
-\begin{align}
-\label{eq:discretize}
-A_d &= e^{A T_s} = \mathcal{L}^{-1} { ( s I - A )^{-1} }_{t = T_s}\\
-B_d &= \int_{0}^{T_s} e^{A t} dt\ B = A^{-1} ( A_d - I ) B \,,
+%where
+%\begin{align}
+%\label{eq:discretize}
+%A_d &= e^{A T_s} = \mathcal{L}^{-1} { ( s I - A )^{-1} }_{t = T_s}\\
+%B_d &= \int_{0}^{T_s} e^{A t} dt\ B = A^{-1} ( A_d - I ) B \,,
 %\\
@@
 %Q_d &= \int_{0}^{T_s} e^{\vec{A} t} Q e^{\vec{A}^T t} dt.
-\end{align}
-%
-and $T_s$ is the sample time. Then
-$x(kT_s)=x_k 
+%\end{align}
+%
+%and $T_s$ is the sample time. Then
+%$x(kT_s)=x_k 
 %\wedge y(kT_s) = y_k, 
-\forall k \in \mathbb N$.
+%\forall k \in \mathbb N$.
 %\end{align*}
@@
 %which could cause ``phantom poles'' to appear otherwise. 
-The eigenvalues of $A_d$ 
+%The eigenvalues of $A_d$ 
 %corresponding to the poles of $G_d(z)$, 
-are related to those of $A$:  
-% corresponding to the poles of $G(s)$ are similarly related.
-%
-$\hat{\lambda}_i=e^{-\lambda_iT_s}$, where $\hat{\lambda}_i \in \sigma(A_d)
-\wedge \lambda_i \in \sigma(A)$ where $\sigma(\cdot)$ is the spectrum of a
-matrix.
-
+%are related to those of $A$:  
+%corresponding to the poles of $G(s)$ are similarly related.
+%
+%$\hat{\lambda}_i=e^{-\lambda_iT_s}$, where $\hat{\lambda}_i \in \sigma(A_d)
+%\wedge \lambda_i \in \sigma(A)$ where $\sigma(\cdot)$ is the spectrum of a
+%matrix.
+%
 %The following remark is worth mentioning regarding the above.
@@
 %
+
 which result in the following closed-loop dynamics:
@@
 
-\newpage
-
-%-------------------------------
-\section{Benchmarks for State-Space Physical Plants}
-\label{sec:BenchmarksforStateSpace}
-%-------------------------------
-
-We have derived a number of benchmarks from the control literature, which we report below. 
-As discussed, in this paper, we disregard the presence of output signals, that is the effect of matrices $\textbf{C}, \textbf{D}$, and use
-direct state-feedback. 
-%
-
-\begin{table}[htb]
-\centering
-\footnotesize
-\begin{tabular}{|c|c|c|c|c|}
-\hline
+%-------------------------------
+%\section{Benchmarks for State-Space Physical Plants}
+%\label{sec:BenchmarksforStateSpace}
+%-------------------------------
+%
+%We have derived a number of benchmarks from the control literature, which we report below. 
+%As discussed, in this paper, we disregard the presence of output signals, that is the effect of matrices $\textbf{C}, \textbf{D}$, and use
+%direct state-feedback. 
+%
+%
+%\begin{table}[htb]
+%\centering
+%\footnotesize
+%\begin{tabular}{|c|c|c|c|c|}
+%\hline
 %\textbf{ID \#} & 
-\textbf{System}                                                               & \textbf{A} & \textbf{B} & \textbf{C} & \textbf{D} \\ \hline
+%\textbf{System}                                                               & \textbf{A} & \textbf{B} & \textbf{C} & \textbf{D} \\ \hline
 %1              & 
@@
 %2              & 
-% \begin{tabular}[c]{@{}c@{}}Aircraft \\ Pitch\\ Dynamics\end{tabular} & $\left[\begin{array}{ccc}
-% -0.313	& 56.7 		& 0		\\
-% -0.0139	& -0.426	& 0		\\
-% 0		& 56.7		& 0		\\
-% \end{array}\right]$ & $\left[\begin{array}{c}
-% 0.232 \\ 0.0203 \\ 0
-% \end{array}\right]$ & $\left[\begin{array}{ccc}
-% 1 & 0 & 0\\
-% \end{array}\right]$ & 0 \\ \hline
+%\begin{tabular}[c]{@{}c@{}}Aircraft \\ Pitch\\ Dynamics\end{tabular} & $\left[\begin{array}{ccc}
+%-0.313	& 56.7 		& 0		\\
+%-0.0139	& -0.426	& 0		\\
+%0		& 56.7		& 0		\\
+%\end{array}\right]$ & $\left[\begin{array}{c}
+%0.232 \\ 0.0203 \\ 0
+%\end{array}\right]$ & $\left[\begin{array}{ccc}
+%1 & 0 & 0\\
+%\end{array}\right]$ & 0 \\ \hline
 %3            & 
@@
 %4              & 
-% \begin{tabular}[c]{@{}c@{}}Buck\\ Converter\end{tabular}                      & $\left[\begin{array}{cc}
-% 0		& -500 \\
-% 4545	& -1515\\
-% \end{array}\right]$ & $\left[\begin{array}{c}
-% 125 \\ 0 \\
-% \end{array}\right]$ & $\left[\begin{array}{cc}
+%\begin{tabular}[c]{@{}c@{}}Buck\\ Converter\end{tabular}                      & $\left[\begin{array}{cc}
+%0		& -500 \\
+%4545	& -1515\\
+%\end{array}\right]$ & $\left[\begin{array}{c}
+%125 \\ 0 \\
+%\end{array}\right]$ & $\left[\begin{array}{cc}
 % 0 & 1\\
-% \end{array}\right]$ & 0 \\ \hline
+%\end{array}\right]$ & 0 \\ \hline
 %5              & 
-% \begin{tabular}[c]{@{}c@{}}Boost\\ Converter\end{tabular} & $\left[\begin{array}{cc}
-% 0		& -375 \\
-% 3409	& -1515\\
-% \end{array}\right]$ & $\left[\begin{array}{c}
-% 500 \\ 0 \\
-% \end{array}\right]$ &  $\left[\begin{array}{cc}
-% 0 & 1\\
-% \end{array}\right]$  & 0        \\ \hline
+%\begin{tabular}[c]{@{}c@{}}Boost\\ Converter\end{tabular} & $\left[\begin{array}{cc}
+%0		& -375 \\
+%3409	& -1515\\
+%\end{array}\right]$ & $\left[\begin{array}{c}
+%500 \\ 0 \\
+%\end{array}\right]$ &  $\left[\begin{array}{cc}
+%0 & 1\\
+%\end{array}\right]$  & 0        \\ \hline
 %6              & 
-% \begin{tabular}[c]{@{}c@{}}Buck-boost\\ Converter\end{tabular} & $\left[\begin{array}{cc}
-% 0		& 375 \\
-% -3409	& -1515\\
-% \end{array}\right]$ & $\left[\begin{array}{c}
-% 125 \\ 0 \\
-% \end{array}\right]$ & $\left[\begin{array}{cc}
-% 0 & 1\\
-% \end{array}\right]$ & 0 \\ \hline
+%\begin{tabular}[c]{@{}c@{}}Buck-boost\\ Converter\end{tabular} & $\left[\begin{array}{cc}
+%0		& 375 \\
+%-3409	& -1515\\
+%\end{array}\right]$ & $\left[\begin{array}{c}
+%125 \\ 0 \\
+%\end{array}\right]$ & $\left[\begin{array}{cc}
+%0 & 1\\
+%\end{array}\right]$ & 0 \\ \hline
 %7              & 
-\begin{tabular}[c]{@{}c@{}}Automotive\\ Cruise\\ System\end{tabular} & $-0.05$ & $0.03125$ & $0.032$ & $0$ \\ \hline
+%\begin{tabular}[c]{@{}c@{}}Automotive\\ Cruise\\ System\end{tabular} & $-0.05$ & $0.03125$ & $0.032$ & $0$ \\ \hline
 %8              & 
-\begin{tabular}[c]{@{}c@{}}DC Motor\\ Rate\end{tabular} & $\left[\begin{array}{cc}
--1000		& -104 \\
-1			& 0\\
-\end{array}\right]$ & $\left[\begin{array}{c}
-1 \\ 0 \\
-\end{array}\right]$ & $\left[\begin{array}{cc}
-0 & 200\\
-\end{array}\right]$ & 0 \\ \hline
+%\begin{tabular}[c]{@{}c@{}}DC Motor\\ Rate\end{tabular} & $\left[\begin{array}{cc}
+%-1000		& -104 \\
+%1			& 0\\
+%\end{array}\right]$ & $\left[\begin{array}{c}
+%1 \\ 0 \\
+%\end{array}\right]$ & $\left[\begin{array}{cc}
+%0 & 200\\
+%\end{array}\right]$ & 0 \\ \hline
 %9              & 
-\begin{tabular}[c]{@{}c@{}}Helicopter\\ Longitudinal\\ Motion\end{tabular}    & $\left[\begin{array}{ccc}
--0.42		& 0.0168		& -0.396	\\
-0.5			& 0				& 0			\\
-0			& 0.5 			& 0			
-\end{array}\right]$ & $\left[\begin{array}{c}
-16 \\ 0 \\ 0
-\end{array}\right]$ & $~
-\left[\begin{array}{ccc}
-0.6125	& -0.6125	& 15.44 \\
-\end{array}\right]$ & 0 \\ \hline
+%\begin{tabular}[c]{@{}c@{}}Helicopter\\ Longitudinal\\ Motion\end{tabular}    & $\left[\begin{array}{ccc}
+%-0.42		& 0.0168		& -0.396	\\
+%0.5			& 0				& 0			\\
+%0			& 0.5 			& 0			
+%\end{array}\right]$ & $\left[\begin{array}{c}
+%16 \\ 0 \\ 0
+%\end{array}\right]$ & $~
+%\left[\begin{array}{ccc}
+%0.6125	& -0.6125	& 15.44 \\
+%\end{array}\right]$ & 0 \\ \hline
 %10             & 
-Pendulum   & $\left[\begin{array}{cc}
-0		& -2.453	\\
-4		& 0			\\	
-\end{array}\right]$ & $\left[\begin{array}{c}
-4 \\ 0
-\end{array}\right]$ & $\left[\begin{array}{cc}
--1.225	& -2.15 	\\
-\end{array}\right]$           & 9.8           \\ \hline
+%Pendulum   & $\left[\begin{array}{cc}
+%0		& -2.453	\\
+%4		& 0			\\	
+%\end{array}\right]$ & $\left[\begin{array}{c}
+%4 \\ 0
+%\end{array}\right]$ & $\left[\begin{array}{cc}
+%-1.225	& -2.15 	\\
+%\end{array}\right]$           & 9.8           \\ \hline
 %11             & 
-\begin{tabular}[c]{@{}c@{}}Inverted\\ Pendulum\end{tabular} & $\left[\begin{array}{cccc}
-0		& 1		& 0 	& 0	\\
-1		& 0		& 0		& 0	\\
-0		& 1 	& 0		& 0 \\
-0		& 0		& 1 	& 0 \\	
-\end{array}\right]$ & $\left[\begin{array}{c}
-1 \\ 0 \\ 0 \\ 0
-\end{array}\right]$  & $\left[\begin{array}{cccc}
-0	& 0	& 1 & -0.75 \\
-0	& 1	& 0	& 0		
-\end{array}\right]$ & $\left[\begin{array}{c}
-0 \\
-0 \end{array}\right]$ \\ \hline
+%\begin{tabular}[c]{@{}c@{}}Inverted\\ Pendulum\end{tabular} & $\left[\begin{array}{cccc}
+%0		& 1		& 0 	& 0	\\
+%1		& 0		& 0		& 0	\\
+%0		& 1 	& 0		& 0 \\
+%0		& 0		& 1 	& 0 \\	
+%\end{array}\right]$ & $\left[\begin{array}{c}
+%1 \\ 0 \\ 0 \\ 0
+%\end{array}\right]$  & $\left[\begin{array}{cccc}
+%0	& 0	& 1 & -0.75 \\
+%0	& 1	& 0	& 0		
+%\end{array}\right]$ & $\left[\begin{array}{c}
+%0 \\
+%0 \end{array}\right]$ \\ \hline
 %12             & 
-\begin{tabular}[c]{@{}c@{}}Magnetic\\ Suspension\end{tabular} & $\left[\begin{array}{cc}
-0		& 31.25	\\
-32		& 0		\\	
-\end{array}\right]$ & $\left[\begin{array}{c}
-8 \\ 0
-\end{array}\right]$ & $\left[\begin{array}{cc}
-0	& 9.766 	\\
-\end{array}\right]$ & 0 \\ \hline
+%\begin{tabular}[c]{@{}c@{}}Magnetic\\ Suspension\end{tabular} & $\left[\begin{array}{cc}
+%0		& 31.25	\\
+%32		& 0		\\	
+%\end{array}\right]$ & $\left[\begin{array}{c}
+%8 \\ 0
+%\end{array}\right]$ & $\left[\begin{array}{cc}
+%0	& 9.766 	\\
+%\end{array}\right]$ & 0 \\ \hline
 %13             & 
-\begin{tabular}[c]{@{}c@{}}Magnetic\\ Pointer \end{tabular} & $\left[\begin{array}{ccc}
--0.271		& -0.05336	& 0	\\
-0.03125		& 0			& 0	\\
-0			& 0.01562 	& 0	\\	
-\end{array}\right]$ & $\left[\begin{array}{c}
-1 \\ 0 \\ 0
-\end{array}\right]$ & $\left[\begin{array}{ccc}
-0	& -0.5888	& -0.2562 \\
-\end{array}\right]$ & 0           \\ \hline
+%\begin{tabular}[c]{@{}c@{}}Magnetic\\ Pointer \end{tabular} & $\left[\begin{array}{ccc}
+%-0.271		& -0.05336	& 0	\\
+%0.03125		& 0			& 0	\\
+%0			& 0.01562 	& 0	\\	
+%\end{array}\right]$ & $\left[\begin{array}{c}
+%1 \\ 0 \\ 0
+%\end{array}\right]$ & $\left[\begin{array}{ccc}
+%0	& -0.5888	& -0.2562 \\
+%\end{array}\right]$ & 0           \\ \hline
 %14             & 
-\begin{tabular}[c]{@{}c@{}}1/4 Car\\ Suspension\end{tabular} & $
-\left[\begin{array}{cccc}
--516.1	& -222.1& -79.75& -33.06	\\
-256		& 0		& 0		& 0			\\
-0		& 64 	& 0		& 0 \\
-0		& 0		& 32 	& 0 \\	
-\end{array}\right]$ & $\left[\begin{array}{c}
-8 \\ 0 \\ 0 \\ 0
-\end{array}\right]$ & $\left[\begin{array}{cccc}
-0	& 0	& 9.969 & 4.133 \\
-\end{array}\right]$ & 0 \\ \hline
+%\begin{tabular}[c]{@{}c@{}}1/4 Car\\ Suspension\end{tabular} & $
+%\left[\begin{array}{cccc}
+%-516.1	& -222.1& -79.75& -33.06	\\
+%256		& 0		& 0		& 0			\\
+%0		& 64 	& 0		& 0 \\
+%0		& 0		& 32 	& 0 \\	
+%\end{array}\right]$ & $\left[\begin{array}{c}
+%8 \\ 0 \\ 0 \\ 0
+%\end{array}\right]$ & $\left[\begin{array}{cccc}
+%0	& 0	& 9.969 & 4.133 \\
+%\end{array}\right]$ & 0 \\ \hline
 %15             & 
-\begin{tabular}[c]{@{}c@{}}Computer\\ Tape\\ Driver\end{tabular} & $\left[\begin{array}{ccc}
--1760		& -976.6	& -457.8	\\
-1024		& 0			& 0			\\
-0			& 512 		& 0			\\	
-\end{array}\right]$ & $\left[\begin{array}{c}
-8 \\ 0 \\ 0
-\end{array}\right]$ & $\left[\begin{array}{ccc}
-1.5	& 2.051	& 1.144 \\
-\end{array}\right]$ & 0           \\ \hline
+%\begin{tabular}[c]{@{}c@{}}Computer\\ Tape\\ Driver\end{tabular} & $\left[\begin{array}{ccc}
+%-1760		& -976.6	& -457.8	\\
+%1024		& 0			& 0			\\
+%0			& 512 		& 0			\\	
+%\end{array}\right]$ & $\left[\begin{array}{c}
+%8 \\ 0 \\ 0
+%\end{array}\right]$ & $\left[\begin{array}{ccc}
+%1.5	& 2.051	& 1.144 \\
+%\end{array}\right]$ & 0           \\ \hline
 %16             & 
-% \begin{tabular}[c]{@{}c@{}}USCG \\ Cutter\\ Tampa\\ Heading\\ Angle\end{tabular} & $\left[\begin{array}{ccc}
-% -0.271		& -0.05336	& 0	\\
-% 0.03125		& 0			& 0			\\
-% 0			& 0.01562 	& 0			\\	
-% \end{array}\right]$ & $\left[\begin{array}{c}
-% 1 \\ 0 \\ 0
-% \end{array}\right]$ & $\left[\begin{array}{ccc}
-% 0	& -0.5888	& -0.2562 \\
-% \end{array}\right]$ & 0 \\ \hline
-\end{tabular}
-\caption{Benchmarks for State-Space Physical Plants}
-\label{table:State-space-benchmarks}
-\end{table}
-
+%\begin{tabular}[c]{@{}c@{}}USCG \\ Cutter\\ Tampa\\ Heading\\ Angle\end{tabular} & $\left[\begin{array}{ccc}
+%-0.271		& -0.05336	& 0	\\
+%0.03125		& 0			& 0			\\
+%0			& 0.01562 	& 0			\\	
+%\end{array}\right]$ & $\left[\begin{array}{c}
+%1 \\ 0 \\ 0
+%\end{array}\right]$ & $\left[\begin{array}{ccc}
+%0	& -0.5888	& -0.2562 \\
+%\end{array}\right]$ & 0 \\ \hline
+%\end{tabular}
+%\caption{Benchmarks for State-Space Physical Plants}
+%\label{table:State-space-benchmarks}
+%\end{table}
+%
 \end{document}

### 2017-05-02 cav2017/cav2017.tex
stable?

@@
 \newcommand{\xmark}{\ding{55}}
+\newcommand{\blue}[1]{{\color{blue}#1}}
 
@@
 verification step fails, we refine the controller by generalizing the
-counterexample.  We synthesize stable and safe controllers for intricate
+counterexample.  We synthesize \blue{stable} and safe controllers for intricate
 physical plant models from the digital control literature.
@@
 We propose a novel algorithm for the synthesis of control algorithms for LTI
-models that are guaranteed to be both stable and safe, considering both the
+models that are guaranteed to be both \blue{stable} and safe, considering both the
 continuous dynamics of the plant and the finite-precision discrete dynamics
@@
 We provide experimental results showing that both approaches are able to
-efficiently synthesize stable and safe controllers for a set of intricate
+efficiently synthesize \blue{stable} and safe controllers for a set of intricate
 physical plant models taken from the digital control literature: the median
@@
 %
-\item  We compute state-feedback controllers that are provably stable and in
+\item  We compute state-feedback controllers that are provably \blue{stable} and in
   addition guaranteee a given safety property.  Existing methods for
@@
 %-------------------------------
-
+\todo{this section sort of implies we are synthesising stable controllers?}
 Asymptotic stability implies convergence to an equilibrium point from any
@@
 %
-A stable control system is known to have converging dynamics.  Assume the
+A \blue{stable} control system is known to have converging dynamics.  Assume the
 closed-loop matrix eigenvalues are not repeated (which is sensible to do,
@@
 $K=[\begin{array}{ccc}0.24609375&-0.125&0.1484375\end{array}]$.
-This candidate is stable, but the {\sc verify} phase finds it to be
+This candidate is \blue{stable}, but the {\sc verify} phase finds it to be
 unsafe and returns a list of iterations with an initial state that
@@
 \rangle}$ is the fixed-point precision used to model the plant, while
-\textit{Time} is the total time required to synthesize a stable controller
+\textit{Time} is the total time required to synthesize a \blue{stable} controller
 for the given plant, for CEGIS with multi-staged verification as well as
@@
 
-The synthesized controllers were confirmed to be stable outside of our model
+The synthesized controllers were confirmed to be safe outside of our model
 representation using MATLAB, positively answering RQ2.  A~link to the full
@@
 Our experimental results show that both approaches are able to synthesize
-stable controllers for most benchmarks within a reasonable amount of time
+safe controllers for most benchmarks within a reasonable amount of time
 fully automatically.  In particular, both approaches complement each other

### 2017-05-02 cav2017/cav2017.tex
correct cite for CEGIS

@@
 state-space physical plants, both based on CounterExample Guided Inductive
-Synthesis (CEGIS)~\cite{sketch}.  We prove their soundness by quantifying
-errors caused by digitalization and quantization effects that arise when
-time/value-discrete digital controller interacts with the continuous plant.
+Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}.  We prove
+their soundness by quantifying errors caused by digitalization and
+quantization effects that arise when time/value-discrete digital controller
+interacts with the continuous plant.
 

### 2017-05-03 cav2017/cav2017.tex
hyphen

@@
 We present a sound and automated approach to synthesize safe digital
-feedback controllers for physical plants represented as linear, time
-invariant models.  Models are given as dynamical equations with inputs,
+feedback controllers for physical plants represented as linear,
+time-invariant models.  Models are given as dynamical equations with inputs,
 evolving over a continuous state space and accounting for errors due to the

### 2017-05-03 cav2017/cav2017.tex
wording
spacing

@@
 specify the continuous plant, and with initial states set as $x(0)$.  While
-we ideally would like to work on the continuous-time plant, in this work
+ideally we would like to work on the continuous-time plant, in this work
 Eq.~\eqref{eq:ode} is soundly discretized in time~\cite{fadali} into
@@
 After adding the new counterexample to its sets of {\sc inputs}, {\sc
-  synthesize} finds the candidate solution $K=[0 \ 0
-  \ 0.00048828125]^T$, which prompts the {\sc safety} verifier to
-return $x_0=[-0.5 -0.5 -0.5]$ as the new counterexample.
+  synthesize} finds the candidate solution $K=[0\,0
+  \,0.00048828125]^T$, which prompts the {\sc safety} verifier to
+return $x_0=[-0.5\,-0.5\,-0.5]$ as the new counterexample.
 

### 2017-05-03 cav2017/cav2017.tex
added Order column to the experimental results table
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 We give the results in Table~\ref{tab:results}.  Here \textit{Benchmark} is
-the name of the respective benchmark, $\mathcal{F}_{\langle I_p,F_p
-\rangle}$ is the fixed-point precision used to model the plant, while
+the name of the respective benchmark, \textit{order} is the number of states, 
+$\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used to model the plant, while
 \textit{Time} is the total time required to synthesize a \blue{stable} controller
@@
 %\scriptsize
-\begin{tabular}{| r | l | c | r | c | r |}
+\begin{tabular}{| r | l | c | c | r | c | r |}
 %
 \hline
-\# & \multicolumn{1}{|c|}{Benchmark}  & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
-   &                                  & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
-1  & Cruise Control      & 8,16   & 8.40\,s & 16,16  &   2.17\,s \\
-2  & DC Motor            & 8,16   & 9.45\,s & 20,20  &   2.06\,s \\
-3  & Helicopter          & \xmark & \xmark  & 16,16  &   1.37\,s \\
-4  & Inverted Pendulum   & 8,16   & 9.65\,s & 16,16  &   0.56\,s \\
-5  & Magnetic Pointer    & \xmark & \xmark  & 28,28  &  44.14\,s \\
-6  & Magnetic Suspension & 12,20  &10.41\,s & 16,16  &   0.61\,s \\
-7  & Pendulum            & 8,16   &14.02\,s & 16,16  &   0.60\,s \\
-8  & Suspension          & 12,20  &73.66\,s & \xmark &    \xmark \\
-9  & Tape Driver         & 8,16   &10.10\,s & 16,16  &  68.24\,s \\
-10 & Satellite           & 8,16   & 9.43\,s & 16,16  &   0.67\,s \\\hline
+\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
+   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
+1  & Cruise Control  & 1 & 8,16   & 8.40\,s & 16,16  &   2.17\,s \\
+2  & DC Motor          & 2 & 8,16   & 9.45\,s & 20,20  &   2.06\,s \\
+3  & Helicopter        & 3 & \xmark & \xmark  & 16,16  &   1.37\,s \\
+4  & Inverted Pendulum & 4 & 8,16   & 9.65\,s & 16,16  &   0.56\,s \\
+5  & Magnetic Pointer  & 2 & \xmark & \xmark  & 28,28  &  44.14\,s \\
+6  & Magnetic Suspension & 2 & 12,20  &10.41\,s & 16,16  &   0.61\,s \\
+7  & Pendulum          & 2 & 8,16   &14.02\,s & 16,16  &   0.60\,s \\
+8  & Suspension        & 2 & 12,20  &73.66\,s & \xmark &    \xmark \\
+9  & Tape Driver       & 3 & 8,16   &10.10\,s & 16,16  &  68.24\,s \\
+10 & Satellite          & 2 & 8,16   & 9.43\,s & 16,16  &   0.67\,s \\\hline
 %

### 2017-05-04 cav2017/cav2017.tex
intro

@@
 verification step fails, we refine the controller by generalizing the
-counterexample.  We synthesize \blue{stable} and safe controllers for intricate
+counterexample.  We display the practical value of this approach by automatically synthesizing safe controllers for intricate
 physical plant models from the digital control literature. 
@@
 We propose a novel algorithm for the synthesis of control algorithms for LTI
-models that are guaranteed to be both \blue{stable} and safe, considering both the
-continuous dynamics of the plant and the finite-precision discrete dynamics
+models that are guaranteed to be 
+%both \blue{stable} and 
+safe, considering both the continuous dynamics of the plant and the finite-precision discrete dynamics
 of the controller, as well as the hybrid elements that connect them.

### 2017-05-04 cav2017/cav2017.tex
intro

@@
 However, these methods have not been generalized to control synthesis.  
-We~remark that a synthesis algorithm that guarantees stability does not
-ensure safety: the system might transitively visit an unsafe state that
-results in an unrecoverable failure.
+Notice that a synthesis algorithm that guarantees stability does not
+ensure safety: the system might transitively visit an unsafe state resulting in unrecoverable failure.
 
@@
 We provide experimental results showing that both approaches are able to
-efficiently synthesize \blue{stable} and safe controllers for a set of intricate
+efficiently synthesize 
+%\blue{stable} and 
+safe controllers for a set of intricate
 physical plant models taken from the digital control literature: the median
@@
 %
-\item  We compute state-feedback controllers that are provably \blue{stable} and in
-  addition guaranteee a given safety property.  Existing methods for
+\item  We compute state-feedback controllers that 
+%are provably \blue{stable} and in addition 
+  guarantee a given safety property.  Existing methods for
   controller synthesis rely on transfer function representations, which are
-  insufficient to prove safety requirements.
-%
-\item We give two novel algorithms: the first, na\"ive one, relies on
+  inadequate to prove safety requirements.
+%
+\item We provide two novel algorithms: the first, na\"ive one, relies on
   an unfolding of the dynamics up to a completeness threshold, while the
@@
 
-\paragraph{CEGIS}
+\paragraph{CEGIS -}
 
@@
 controllers~\cite{IsmailBCFF15, Bessa16}.  While this work also uses CEGIS,
-their approach is restricted to digital controllers for stable closed-loop
-systems given as transfer function models.  By contrast, in the current
-paper we consider a state-space representation of the physical system, which
-has known advantages over the transfer function
-representation~\cite{Astrom08}: (i)~it generalizes to multivariate systems
+the approach is restricted to digital controllers for stable closed-loop
+systems given as transfer function models: 
+this results in  a static check on their coefficients.  
+By contrast, in the current paper we consider a state-space representation of the physical system, 
+which requires ensuring the specification over actual traces of the model, 
+alongside the numerical soundness required by the effects of discretisation and imprecision errors.   
+A state-space model has known advantages over the transfer function
+representation~\cite{Astrom08}: (i)~it naturally generalizes to multivariate systems
 (i.e., with multiple inputs and outputs); (ii)~gives the state-to-input
@@
 
-\paragraph{Discretization Effects}
+\paragraph{Discretization Effects -}
 
@@
 %
-where $k \in \mathbb N$ and $x_{0}=x(0)$ is the initial state.  $A_d$ and
-$B_d$ denote the matrices that describe the discretized plant dynamics, whereas
-$A$ and $B$ denote the continuous plant dynamics.  Later, we will address the
-issue of variable quantization, as introduced by the ADC/DAC conversion
-blocks (Fig.~\ref{fig:digitalsystem}).
+where $k \in \mathbb N$ and $x_{0}=x(0)$ is the initial state. 
+$A_d$ and $B_d$ denote the matrices that describe the discretized plant dynamics, whereas
+$A$ and $B$ denote the continuous plant dynamics.  
+We synthesize for requirements over this discrete-time domain. 
+Later, we will address the issue of variable quantization, 
+as introduced by the ADC/DAC conversion blocks (Fig.~\ref{fig:digitalsystem}).
 
@@
 as implemented on modern Field-Programmable Gate Arrays or Digital Signal Processors. 
-The most basic feedback architecture is the state feedback, 
+The most basic feedback architecture is the state feedback one, 
 where the control action $u_k$ (notice we work with the discretized signal) is computed by: 
@@
 control literature.  Further, we will embrace the digital nature of the
-controller, which manipulates quantities with finite precision.
-
-%-------------------------------
-\subsection{Stability of Closed-loop Systems}
+controller, which manipulates quantized signals as discrete quantities represented with finite precision.
+
+%-------------------------------
+\subsection{Stability of closed-loop Systems}
 \label{ssec:stability}
 %-------------------------------
-\todo{this section sort of implies we are synthesising stable controllers?}
+\todo{this section sort of implies we are synthesising stable controllers? I argue we use this objective to guess reasonable controllers in the synthesis loop. }
+
 Asymptotic stability implies convergence to an equilibrium point from any
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Numeric representations and soundness} 
+\subsection{Numerical representation and soundness} 
 \label{sec:numeric_rep}
@@
 The models we consider have two sources of error due to numeric
-representation.  The first is the numeric error introduced by the
+representation.  The first is the numerical error introduced by the
 fixed-point numbers employed to model the plant, i.e., to represent the

### 2017-05-04 cav2017/cav2017.tex
+ some brief explanation on fct representation in the CEGIS sec

@@
 The input specification provided to the program synthesizer is of the form
-$\exists P .\, \forall a.\, \sigma(a, P)$, where $P$ ranges over functions,
+$\exists P .\, \forall a.\, \sigma(a, P)$, where $P$ ranges over functions
+(where a function is represented by the program computing it),
 $a$ ranges over ground terms, and $\sigma$ is a quantifier-free formula. 

### 2017-05-04 cav2017/cav2017.tex
research question --> experimental goal

@@
 Using the state-space models given in Section~\ref{experimental-setup}, 
-our experimental evaluation aims to answer two research questions:
-%
-
-\todo{Remove RQ2 and only discuss the sanity check in 5.3?}
+our evaluation has the following two experimental goals:
+%aims to answer two research questions:
+%
+
+%\todo{Remove RQ2 and only discuss the sanity check in 5.3?}
 
@@
 
-\item[RQ1] \textbf{(CEGIS)} do the multi-staged verification and abstraction-based
-CEGIS generate a FWL digital controller in a reasonable amount of time?
-
-\item[RQ2] \textbf{(sanity check)} are the synthesized controllers sound
-and can their stability and safety be confirmed outside of our model?
+\item[EG1] \textbf{(CEGIS)} Show that multi-staged verification and abstraction-based
+CEGIS are able to generate FWL digital controllers in a reasonable amount of time.
+
+\item[EG2] \textbf{(sanity check)} Confirm the
+stability and safety of the synthesized controllers outside of our model.
 
@@
 short enough to be of practical use to control engineers, and thus affirm
-RQ1.
+EG1.
 
@@
 The synthesized controllers were confirmed to be safe outside of our model
-representation using MATLAB, positively answering RQ2.  A~link to the full
+representation using MATLAB, achieving EG2.  A~link to the full
 experimental environment, including scripts to reproduce the results, all

### 2017-05-04 cav2017/cav2017.tex
sec 2

--- 2017-05-04 cav2017/cav2017.tex
@@
 %-------------------------------
-\subsection{Stability of closed-loop Systems}
+\subsection{Stability of closed-loop systems}
 \label{ssec:stability}
@@
 
+In this work we employ asymptotic stability in the CEGIS loop,  
+as an objective for guessing controllers that are later proven sound over safety requirements.  
 Asymptotic stability implies convergence to an equilibrium point from any
-states in its neighborhood.  This stability concept is stronger than the
-Lyapunov and BIBO stability researched by previous
-work~\cite{DBLP:conf/emsoft/RavanbakhshS16, hscc-paper,
-DBLP:conf/hybrid/RouxJG15, DBLP:conf/hybrid/WangGRJF16}.  In the case of
-linear systems as in~\eqref{eq:closedloopss}, the equilibrium point for
-zero-input response is always the origin.  Here, we consider systems with a
-zero reference signal.
+states in a neighborhood.  
+%This stability concept is stronger than the
+%Lyapunov and BIBO stability researched by previous
+%work~\cite{DBLP:conf/emsoft/RavanbakhshS16, hscc-paper,
+%DBLP:conf/hybrid/RouxJG15, DBLP:conf/hybrid/WangGRJF16}.  
+In the case of linear systems as in~\eqref{eq:closedloopss}, 
+considered with a zero reference signal, 
+the equilibrium point of interest is the origin.
 
 A discrete-time LTI system as \eqref{eq:closedloopss} is asymptotically
-stable iff all the roots of the characteristic polynomial (i.e., the
+stable if all the roots of its characteristic polynomial (i.e., the
 eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
-circle in the complex plane, i.e., iff their absolute values are less than
-one~\cite{astrom1997computer}.  In this paper, we express the stability
-specification $\phi_\mathit{stability}$ in terms of a check known as
+circle of the complex plane, i.e., if their absolute values are strictly less than
+one~\cite{astrom1997computer} (this simple sufficient condition can be generalised, 
+however this is not necessary in our work).  
+In this paper, we express this stability specification $\phi_\mathit{stability}$ in terms of a check known as
 \emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic formula to
@@
 We are not limited to the synthesis of digital stabilizing controllers -- a
-well known task in the literature on digital control system -- but target
+well known task in the literature on digital control systems -- but target
 safety requirements with an overall approach that is sound and automated. 

### 2017-05-04 cav2017/cav2017.tex
sec 2

@@
 %-------------------------------
-\section{Related work}
+\section{Related Work}
 \label{sec:relw}
@@
 to the equilibrium, which is typical in the case of oscillatory dynamics. 
-However, a safe system will always be stable.  In~this work, the safety
-property is modeled as follows:
+%However, a safe system will always be stable.  
+In~this work, the safety property is expressed as follows:
 %
@@
 for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
-instant, respectively.  This means that the states will always be within the
-$n$-dimensional hyper-box.
+instant, respectively.  This means that the states will always be within an $n$-dimensional hyper-box.
 
@@
 $\phi_\mathit{init} = \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$
-For the former, this means that the control input saturates in view of
+For the former, this means that the control input might saturates in view of
 physical constraints.
@@
 
-The models we consider have two sources of error due to numeric
+The models we consider have two sources of error that are due to numerical  
 representation.  The first is the numerical error introduced by the
@@
 $\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$
-represented at the fixed-point precision of the plant model ($I_p \geq I_c
-\wedge\allowbreak F_p \geq F_c$).  Thus any mathematical operations in the
+represented at the fixed-point precision of the plant model (\blue{[justify this assumption:]} $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$).  Thus any mathematical operations in the
 digital controller will be in the range of $\mathcal{F}_{\langle I_c,F_c
 \rangle}$, and all other calculations will be carried out in the range of
-$\mathcal{F}_{\langle I_p,F_p \rangle}$.  The physical plant operates in the
+$\mathcal{F}_{\langle I_p,F_p \rangle}$.  
+\blue{[this statement is potentially confusing: are we referring to quantisation effects, or to the uncertainty errors that we have handled in our HSCC17 work?]
+The physical plant operates in the
 reals, which means our verification phase must account for calculation
 errors in the model. 
+}
 
@@
 multiplication operation.  We represent these errors as non-deterministic
-noise.
+additive noise, which might de-stabilize the closed-loop model.
 
@@
 errors (see Appendix~\ref{sec:appendix:LTIbackground} for details) and
-eventually destabilizing the system~\cite{Bessa16}.  However, since in this
+eventually de-stabilizing the system~\cite{Bessa16}.  However, since in this
 paper we require stability only as a precursor to safety, it is sufficient
@@
 approach that relies on a na\"ive unfolding of the transition relation,
-whereas the second uses abstraction to evaluate all possible progressions of
+whereas the second uses abstraction to evaluate all possible executions of
 the system.
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Naive Approach: CEGIS with Multi-staged Verification}
+\subsection{Na\"ive Approach: CEGIS with multi-staged verification}
 \label{sec:CEGIS-precision-incrementation}
@@
 we verify and synthesize a controller over $k$ time steps.  We~then compute
-a completeness threshold~\cite{DBLP:conf/vmcai/KroeningS03}, $\overline{k}$,
+a completeness threshold $\overline{k}$~\cite{DBLP:conf/vmcai/KroeningS03}
 for this controller, and verify correctness for $\overline{k}$ time steps. 
 Essentially, $\overline{k}$ is the number of iterations required to
-sufficiently unwind the closed-loop state-space system such that the
-boundaries are not violated for any $k{>}\overline{k}$.
-
-\begin{lemma} There exists a $\overline{k}$ such that it is
+sufficiently unwind the closed-loop state-space system, 
+which ensures that the boundaries are not violated for any other $k{>}\overline{k}$.
+
+\begin{theorem} There exists a finite $\overline{k}$ such that it is
 sufficient to unwind the closed-loop state-space system up to $\overline{k}$
 in order to ensure that $\phi_\mathit{safety}$ holds. 
-\end{lemma}
+\end{theorem}
 
@@
 %
-A \blue{stable} control system is known to have converging dynamics.  Assume the
+A stable control system is known to have converging dynamics.  Assume the
 closed-loop matrix eigenvalues are not repeated (which is sensible to do,
@@
 $k{\geq}\overline{k}$ steps we have completed a full rotation, which results
-in a point closer to the origin.  This is the completeness threshold.
-
+in a point closer to the origin.  The synthesized $\overline{k}$ is the completeness threshold.
+\qed 
 %
@@
 (Sec.~\ref{ssec:safety}).  To synthesize a controller that satisfies the
-stability criteria, we require that a computed characteristic polynomial
-satisfies Jury's criteria.  The details of this calculation can be found in
+stability criteria, we require that a computed polynomial
+satisfies Jury's criterion~\cite{fadali}.  The details of this calculation can be found in
 the Appendix.
@@
 
-\item The first {\sc verify} stage, {\sc safety}, checks that candidate
+\item The first {\sc verify} stage, {\sc safety}, checks that the candidate
 solution $K$, which we synthesized to be safe for at least one initial
@@
 
-\begin{lemma} 
+\begin{theorem} 
 If a controller is safe for each of the corner cases of our hypercube of
-allowed initial states, it is safe for any initial state in the
-hypercube. 
-\end{lemma}
+allowed initial states, it is safe for any initial state in the hypercube. 
+\end{theorem}
 
@@
 convex set, by those generated from the vertices. 
+\qed
 \end{proof}
@@
 %-------------------------------
-\subsection{Description of the Benchmarks}
+\subsection{Description of the benchmarks}
 \label{experimental-setup}
@@
 \end{tabular}
+\vspace{0.05in}
 \caption{Experimental results\label{tab:results}}
@@
 %-------------------------------
-\section{Stability of closed-loop models}
+\section{Stability of Closed-loop Models}
 \label{sec:appendix-stability}
@@
 %-------------------------------
-\subsection{Stability of Closed-loop Systems with Fixed-point Controller Error}
+\subsection{Stability of closed-loop models with fixed-point controller error}
 %-------------------------------
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{LTI system Transformations and Equivalences} \label{sec:appendix:LTIbackground}
+\section{Errors in LTI models} \label{sec:appendix:LTIbackground}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-05-04 cav2017/cav2017.tex
order

--- 2017-05-04 cav2017/cav2017.tex
@@
 We give the results in Table~\ref{tab:results}.  Here \textit{Benchmark} is
-the name of the respective benchmark, \textit{order} is the number of states, 
-$\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used to model the plant, while
-\textit{Time} is the total time required to synthesize a \blue{stable} controller
-for the given plant, for CEGIS with multi-staged verification as well as
-abstraction-based CEGIS.  Timeouts are indicated by~\xmark.  The precision
-for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is chosen to be
-$I_c = 8$, $F_c = 8$.
+the name of the respective benchmark, \textit{order} is the number of
+continuous variables, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the
+fixed-point precision used to model the plant, while \textit{Time} is the
+total time required to synthesize a \blue{stable} controller for the given
+plant with the given method.  Timeouts are indicated by~\xmark.  The
+precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
+chosen to be $I_c = 8$, $F_c = 8$.
 
@@
 back-end is faster than the basic multi-staged verification approach, and
-finds one solution more (9) than the multi-staged back-end (8).
-In direct comparison, the
-abstraction-based approach is on average able to find a solution in
-approximately 70\% of the time required using the multi-staged back-end, and
-has a median run-time 1.4\,s, which is seven times smaller than the
-multi-staged approach.  The two back-ends complement each other in benchmark
-coverage and together solve all benchmarks in the set.
+finds one solution more (9) than the multi-staged back-end (8).  In direct
+comparison, the abstraction-based approach is on average able to find a
+solution in approximately 70\% of the time required using the multi-staged
+back-end, and has a median run-time 1.4\,s, which is seven times smaller
+than the multi-staged approach.  The two back-ends complement each other in
+benchmark coverage and together solve all benchmarks in the set.
 

### 2017-05-04 cav2017/cav2017.tex
numerical representations

@@
 $\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$
-represented at the fixed-point precision of the plant model (\blue{[justify this assumption:]} $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$).  Thus any mathematical operations in the
+represented at the fixed-point precision of the plant model ($I_c$ and $F_c$ are determined by the controller.
+We pick $I_p$ and $F_p$ for our synthesis such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$).
+Thus any mathematical operations in our modelled
 digital controller will be in the range of $\mathcal{F}_{\langle I_c,F_c
-\rangle}$, and all other calculations will be carried out in the range of
+\rangle}$, and all other calculations in our model will be carried out in the range of
 $\mathcal{F}_{\langle I_p,F_p \rangle}$.  
-\blue{[this statement is potentially confusing: are we referring to quantisation effects, or to the uncertainty errors that we have handled in our HSCC17 work?]
 The physical plant operates in the
-reals, which means our verification phase must account for calculation
-errors in the model. 
-}
+reals, which means our verification phase must also account for the numerical error and quantization errors caused by representing the physical plant at the finite precision $\mathcal{F}_{\langle I_p,F_p \rangle}$.
 

### 2017-05-04 cav2017/cav2017.tex
edit sec 5.2

--- 2017-05-04 cav2017/cav2017.tex
@@
 %-------------------------------
-\subsection{Stability of closed-loop systems}
+\subsection{Stability of closed-loop Systems}
 \label{ssec:stability}
@@
 
-In this work we employ asymptotic stability in the CEGIS loop,  
-as an objective for guessing controllers that are later proven sound over safety requirements.  
 Asymptotic stability implies convergence to an equilibrium point from any
-states in a neighborhood.  
-%This stability concept is stronger than the
-%Lyapunov and BIBO stability researched by previous
-%work~\cite{DBLP:conf/emsoft/RavanbakhshS16, hscc-paper,
-%DBLP:conf/hybrid/RouxJG15, DBLP:conf/hybrid/WangGRJF16}.  
-In the case of linear systems as in~\eqref{eq:closedloopss}, 
-considered with a zero reference signal, 
-the equilibrium point of interest is the origin.
+states in its neighborhood.  This stability concept is stronger than the
+Lyapunov and BIBO stability researched by previous
+work~\cite{DBLP:conf/emsoft/RavanbakhshS16, hscc-paper,
+DBLP:conf/hybrid/RouxJG15, DBLP:conf/hybrid/WangGRJF16}.  In the case of
+linear systems as in~\eqref{eq:closedloopss}, the equilibrium point for
+zero-input response is always the origin.  Here, we consider systems with a
+zero reference signal.
 
 A discrete-time LTI system as \eqref{eq:closedloopss} is asymptotically
-stable if all the roots of its characteristic polynomial (i.e., the
+stable iff all the roots of the characteristic polynomial (i.e., the
 eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
-circle of the complex plane, i.e., if their absolute values are strictly less than
-one~\cite{astrom1997computer} (this simple sufficient condition can be generalised, 
-however this is not necessary in our work).  
-In this paper, we express this stability specification $\phi_\mathit{stability}$ in terms of a check known as
+circle in the complex plane, i.e., iff their absolute values are less than
+one~\cite{astrom1997computer}.  In this paper, we express the stability
+specification $\phi_\mathit{stability}$ in terms of a check known as
 \emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic formula to
@@
 We are not limited to the synthesis of digital stabilizing controllers -- a
-well known task in the literature on digital control systems -- but target
+well known task in the literature on digital control system -- but target
 safety requirements with an overall approach that is sound and automated. 
@@
 
-\item[EG1] \textbf{(CEGIS)} Show that multi-staged verification and abstraction-based
-CEGIS are able to generate FWL digital controllers in a reasonable amount of time.
+\item[EG1] \textbf{(CEGIS)} Show that both the multi-staged and the abstraction-based
+CEGIS approaches are able to generate FWL digital controllers in a reasonable amount of time.
 
@@
 We give the results in Table~\ref{tab:results}.  Here \textit{Benchmark} is
-the name of the respective benchmark, \textit{order} is the number of
-continuous variables, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the
-fixed-point precision used to model the plant, while \textit{Time} is the
-total time required to synthesize a \blue{stable} controller for the given
-plant with the given method.  Timeouts are indicated by~\xmark.  The
-precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
-chosen to be $I_c = 8$, $F_c = 8$.
+the name of the respective benchmark, \textit{order} is the number of states, 
+$\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used to model the plant, while
+\textit{Time} is the total time required to synthesize a \blue{stable} controller
+for the given plant, for CEGIS with multi-staged verification as well as
+abstraction-based CEGIS.  Timeouts are indicated by~\xmark.  The precision
+for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is chosen to be
+$I_c = 8$, $F_c = 8$.
 
@@
 back-end is faster than the basic multi-staged verification approach, and
-finds one solution more (9) than the multi-staged back-end (8).  In direct
-comparison, the abstraction-based approach is on average able to find a
-solution in approximately 70\% of the time required using the multi-staged
-back-end, and has a median run-time 1.4\,s, which is seven times smaller
-than the multi-staged approach.  The two back-ends complement each other in
-benchmark coverage and together solve all benchmarks in the set.
+finds one solution more (9) than the multi-staged back-end (8).
+In direct comparison, the
+abstraction-based approach is on average able to find a solution in
+approximately 70\% of the time required using the multi-staged back-end, and
+has a median run-time 1.4\,s, which is seven times smaller than the
+multi-staged approach.  The two back-ends complement each other in benchmark
+coverage and together solve all benchmarks in the set.
 

### 2017-05-04 cav2017/cav2017.tex
intro

@@
 %
+We account for the presence of errors originating from a number of sources: 
+quantisation errors in ADC and DAC, 
+representation errors (from the discretisation introduced by finite-precision arithmetics), 
+and roundoff and saturation errors in the verification process 
+(from finite-precision operations).  
+%
 Due to the complexity of such systems, we focus on linear models with known
@@
 
-\todo{Clarify challenges: FWL (rounding, truncation), quantisation (ADC, DAC).}
-%
-\todo{Discuss numerical (HSCC'17) vs. algorithmical soundness (CAV'17).}
+%\todo{Clarify challenges: FWL (rounding, truncation), quantisation (ADC, DAC).}
+%
+%\todo{Discuss numerical (HSCC'17) vs. algorithmical soundness (CAV'17).}
 

### 2017-05-04 cav2017/cav2017.tex
intro

@@
 different aspects of discretization, including delayed
-response~\cite{Duggirala2015} and Finite Word Length (FWL) semantics, with
-the goal either to verify (e.g.,~\cite{daes20161}) or to optimize
+response~\cite{Duggirala2015} and finite word length (FWL) semantics, 
+with the goal either to verify (e.g.,~\cite{daes20161}) or to optimize
 (e.g.,~\cite{oudjida2014design}) given implementations.
@@
 %-------------------------------
-\todo{this section sort of implies we are synthesising stable controllers? I argue we use this objective to guess reasonable controllers in the synthesis loop. }
+%\todo{this section sort of implies we are synthesising stable controllers? I argue we use this objective to guess reasonable controllers in the synthesis loop. }
 
@@
 as an objective for guessing controllers that are later proven sound over safety requirements.  
-Asymptotic stability implies convergence to an equilibrium point from any
-states in a neighborhood.  
+Asymptotic stability is a property that amounts to convergence of the model executions to an equilibrium point, 
+starting from any states in a neighborhood of the point (see Figure~\ref{fig:ct} for the portrait of a stable execution, converging to the origin).  
 %This stability concept is stronger than the
@@
 
-An additional error is caused by the representation of the plant dynamics, namely 
+An additional error is due to the representation of the plant dynamics, namely 
 %
@@
 \end{align*}
-
-We address this last error by use of interval
+We address this error by use of interval
 arithmetic~\cite{moore1966interval} in the verification phase.
@@
 $k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
-completeness threshold $\overline{k}$ for the current candidate $K$ and
+completeness threshold $\overline{k}$ for the current candidate controller $K$ and
 check that $k{\geq}\overline{k}$.  This is done according to the argument
@@
 \vspace{0.1cm}
-\caption{Completeness threshold for multi-staged verification}
+\caption{Completeness threshold for multi-staged verification \blue{[Explain meaning of Ts, which I don't think is introduced anywhere in the current draft.]}}
 \label{fig:ct}
@@
 We start with a candidate solution with all coefficients zero, $K=[0
-  \ 0 \ 0]^T$, and a precision of $I_p=13$, $F_p=3$.  In the first
+  \ 0 \ 0]^T$ \blue{[an attempted explanation of this first guess is due.]}, and a precision of $I_p=13$, $F_p=3$.  In the first
 {\sc verify} stage, the {\sc safety} check finds the counterexample
@@
 insufficient.  Consequently, we increase the precision to $I_p=17$,
-$F_p=7$.
+$F_p=7$. \blue{[ Explain how precision is increased, byte-congruent.]}
 %
@@
 inputs, and time horizons during the verification phase.
-Essentially, this approach relies on the explicit
-simulation over a bounded time horizon of individual states that form
+Essentially, this approach relies on the \blue{[qualitative term, please elaborate:] explicit
+simulation} over a bounded time horizon of individual states that form
 part of an uncountable space and tries to generalize it for an
@@
 we  find a controller for a continuous initial set of states and set of inputs, 
-  over an abstraction of the continuous dynamics (taken from \cite{cattaruzza2015unbounded}) that conforms to
+  over an abstraction of the continuous dynamics \cite{cattaruzza2015unbounded} that conforms to
   witness proofs at specific times. %% It further generalizes the
@@
 $P_a(z) = z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}$. 
+\blue{[shouldn't there be a b term in the polynomial's coefficients here?]}
 %%   A controllable system with quantization will have the following dynamics, where
@@
 \item Calculate a set of initial bounds on $K$, $\phi_\mathit{init}^{K}$,
-based on the input constraints.  Note that these bounds will be used by the
-{\sc synthesize} phase to reduce the size of the solution space. 
+based on the input constraints \blue{[how is this practically done?]}.  
+Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space. 
 %
@@
   progression of the system from $\phi_\mathit{init}$ over time,
-$x_{k+1} \models \phi_\mathit{safety}$. %% For this purpose we require 
+$x_{k+1} \models \phi_\mathit{safety}$ \blue{why $k+1$ here?}. %% For this purpose we require 
 %% an initial set $\phi_\mathit{init}= x_0 \in [\underline{x_0} \ \overline{x_0}]$ 
@@
 %\label{eq:acc_observer_LTI_cf}
-x=&(A_d-B_dK)^kx_0
+\!\! x=&(A_d-B_dK)^kx_0
 %+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i
-+\sum_{i=0}^{k-1} (A_d-B_dK)^i B_{n}(\nu_1+\nu_2+\nu_3) : B_n= [1\ 1 \cdots \ 1 ]^T
++\sum_{i=0}^{k-1} (A_d-B_dK)^i B_{n}(\nu_1+\nu_2+\nu_3) : B_n= [1 \cdots 1]^T
 \end{align}
@@
 \hat{X}^\#
-=&\mathcal{A} X_0 + \mathcal{B}_{n} N\\
-X_0 =&\left \{x : x \models \phi_\mathit{init} \right\}\nonumber
+=\mathcal{A} X_0 + \mathcal{B}_{n} N, \quad
+X_0 =\left \{x : x \models \phi_\mathit{init} \right\}, 
 \end{align}
 %
-where $\mathcal{A}=\bigcup_{k=1}^\infty (A_d-B_dK)t^k,
+where \blue{[what is $t$ in $t^k$?]} $\mathcal{A}=\bigcup_{k=1}^\infty (A_d-B_dK)t^k,
 \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k(A_d-B_dK)^iB_{n}$ are

### 2017-05-04 cav2017/cav2017.tex
intro

@@
 \item We use $\phi_\Lambda$ to
-  further constrain the characteristic polynomial  
+  further constrain the characteristic polynomial \blue{[again, check the coefficients of the characteristic polynomial.]} 
 $z^n+\sum_{i=1}^n(a_i-k_i)z^{n-i}=\prod_{i=1}^n (z-\lambda_i) : |\lambda_i|<1 \wedge \lambda_i \models \phi_{\Lambda}$.
@@
 $K=[\begin{array}{ccc}0.24609375&-0.125&0.1484375\end{array}]$.
-This candidate is \blue{stable}, but the {\sc verify} phase finds it to be
+This candidate is chosen for its closed-loop stable dynamics, but the {\sc verify} phase finds it to be
 unsafe and returns a list of iterations with an initial state that

### 2017-05-04 cav2017/cav2017.tex
intro

@@
 %\label{eq:acc_observer_LTI_cf}
-\!\! x=&(A_d-B_dK)^kx_0
+\hspace{-0.1in} x=&(A_d-B_dK)^kx_0
 %+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i
@@
 
-A set of state-space models for different classes of systems was extracted
+A set of state-space models for different classes of systems has been taken 
 from the literature~\cite{Franklin15, maglev, converters, CTMS} and employed
@@
 The \textit{Magnetic Suspension} plant provides a physical model for which 
-a given object is suspended via magnetic field. 
+a given object is suspended via a magnetic field. 
 The \textit{Magnetized Pointer} plant describes a physical model employed in analogue gauges 
@@
 The \textit{1/4 Car Suspension} plant presents a physical model that connects a car to its wheels 
-and allows relative motion between both parts.
+and allows relative motion between the two parts.
 The \textit{Computer Tape Driver} plant describes a system to read and write data 
-on a storage device in the computer.
+on a storage device in a computer.
 
@@
 Our benchmarks are SISO models (Section~\ref{sec:preliminaries}).  The
-Inverted Pendulum appears to be a two output system, but it was treated as
-two SISO systems during the experiments.  For the sake of simplicity all the
-state measurements are assumed available.  In practice, state estimators
-should be designed in order to obtain an estimate of the states from the
-single output.  Further work can include state observers synthesis.
-
-All benchmarks were discretized with different sample times~\cite{fadali}. 
-All experiments were performed considering $\underline{x_{i}}=-1$ and 
-$\overline{x_{i}}=1$ and the inputs $u_{k}=0, \forall k>0$.
-We have conducted the experimental evaluation on a 12-core 2.40\,GHz Intel
-Xeon E5-2440 with 96\,GB of RAM and Linux OS.  We used the Linux
+Inverted Pendulum appears to be a two-output system, but it is treated as
+two SISO models during the experiments.  For the sake of simplicity all the
+state measurements are assumed to be available.  
+%In practice, state estimators should be designed in order to obtain an estimate of the states from the single output.  
+(Current work targets the extension of our framework to observer-based synthesis.)
+
+All benchmarks are discretized with different sample times~\cite{fadali}. 
+All experiments are performed considering $\underline{x_{i}}=-1$ and 
+$\overline{x_{i}}=1$ \blue{[what does this mean:] and the inputs $u_{k}=0, \forall k>0$}.
+We conduct the experimental evaluation on a 12-core 2.40\,GHz Intel
+Xeon E5-2440 with 96\,GB of RAM and Linux OS.  We use the Linux
 \emph{times} command to measure CPU time used for each benchmark.  The
-runtime was limited to one hour per benchmark.
+runtime is limited to one hour per benchmark.
 
@@
 
-We give the results in Table~\ref{tab:results}.  Here \textit{Benchmark} is
-the name of the respective benchmark, \textit{order} is the number of
+We provide the results in Table~\ref{tab:results}.  Here \textit{Benchmark} is
+the name of the respective benchmark, \textit{Order} is the number of
 continuous variables, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the
 fixed-point precision used to model the plant, while \textit{Time} is the
-total time required to synthesize a \blue{stable} controller for the given
-plant with the given method.  Timeouts are indicated by~\xmark.  The
+total time required to synthesize a controller for the given
+plant with one of the two methods.  Timeouts are indicated by~\xmark.  The
 precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
@@
 
-There are several cases for which the system may fail to find a controller. 
+There are a few instances for which the system fails to find a controller. 
 For the na\"ive approach, the completeness threshold may be too large, thus
@@
 require a very precise abstraction, resulting in too many refinements and,
-consequently, timeout.  Yet another source of incompleteness is the
+consequently, in a timeout.  Yet another source of incompleteness is the
 inability of the {\sc synthesize} phase to use a large enough precision for
@@
 
-The synthesized controllers were confirmed to be safe outside of our model
+The synthesized controllers are confirmed to be safe outside of our model
 representation using MATLAB, achieving EG2.  A~link to the full
@@
 select suitable FWL word widths to model the plant behavior employs a
-heuristic based on user-provided controller word-width specifications.  For
+heuristic based on user-provided controller word-width specifications \blue{[explain how precision is increased as number of bits?]}.  For
 the first approach, where we may need to increase the precision of the time

### 2017-05-04 cav2017/cav2017.tex
intro

@@
 acceleration may not hold for more complex properties than safety, for
-instance ``eventually always reaches a certain safe set''.
+instance ``eventually reach and always remain in a given safe set''.
 
@@
 continuous-time case, to models with output-based control architectures
-(hinging on the use of observers), and to considering performance
-requirements (alongside safety) in the synthesis of digital controllers.
+(with the use of observers), and to the consideration of more complex specifications 
+and of additional performance requirements in the synthesis of digital controllers.
 
@@
 
-The proof for Jury's criteria~\cite{fadali} relies on the fact that the relationship between states and
-next states is defined by $x_{k+1} = (A_d - B_dK) \cdot x_k$, all computed
+The proof of Jury's criterion~\cite{fadali} relies on the fact that the relationship between states and
+next states is defined by $x_{k+1} = (A_d - B_dK) x_k$, all computed
 at infinite precision.  When we employ a FWL digital controller, the
@@
 x_{k+1} &= A_d \cdot x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
-x_{k+1} &= (A_d  - B_dK) \cdot x_k + B_dK\delta
+x_{k+1} &= (A_d  - B_dK) \cdot x_k + B_dK\delta, 
 %\\ x_{k+1}&=A_d x_{k} + B_du_{k}
@@
 operation performed on the last bit. 
-
 Thus, $\delta_T$ is the truncation error and it will propagate across
@@
 at the precision of the plant.  Here the error depends on whether the
-divisor is greater or smaller than the dividend.  $\mathcal{F}_{\langle I,F
+divisor is greater or smaller than the dividend:  $\mathcal{F}_{\langle I,F
 \rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_{T3}$
@@
 implementation).  This sampling uses a threshold which is defined by the
-less significant bit ($q_{c}=2^{-F_c}$) of the ADC and some non-linearities
+less significant bit \blue{[this quantity was named $c_m$ above and in other parts of the paper - please uniformise notations]} ($q_{c}=2^{-F_c}$) of the ADC and some non-linearities
 of the circuitry.  The overall conversion is
@@
 quantization noises ${\nu_1}_k \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}]$ and
-${\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}]$ where $q_1=q_{c} \wedge
-q_2=q_\mathit{dac}$.  This is illustrated in
+${\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}]$, where $q_1=q_{c}$ and 
+$q_2=q_\mathit{dac}$.  This is illustrated in
 Fig.~\ref{ssec:statefeedbackcontrol} where $Q_1$ is the quantizer of the ADC
@@
 %
-\begin{align}
-\label{eq:pre_quantization}
+\begin{align*}
+%\label{eq:pre_quantization}
 {x}_{k+1} &= {A}_d{x}_k+{B}_d({u}_k+{{\nu}_2}_k)\\
 u_k&=-K{x}_{k}+{{\nu}_1}_k \,,
-\end{align}
-%
-
+\end{align*}
+%
 which result in the following closed-loop dynamics:
 %
-\begin{align}
-\label{eq:quantization}
+\begin{align*}
+%\label{eq:quantization}
 {x}_{k+1} &= ({A}_d-{B}_d{K}_d) {x}_k+{B}_d{{\nu}_2}_k +{{\nu}_1}_k \,. 
-\end{align}
+\end{align*}
 

### 2017-05-04 cav2017/cav2017.tex
intro
Updated experimental section based on rebuttal
Added % for verification/synthesis time. Described bit width increase.
Removed obsolete comments.

@@
 than the multi-staged approach.  The two back-ends complement each other in
-benchmark coverage and together solve all benchmarks in the set.
+benchmark coverage and together solve all benchmarks in the set.  On average
+our engine spent 52\% in the synthesis and 48\% in the verification phase.
 
@@
 
-\todo{Add the percentage of the total time taken by verification and synthesis.}
-
-\todo{Discuss the number of abstraction refinements (inner loop, not the outer one)
-  for the 2nd approach?
-  Although, if it's always one, I'm not sure how interesting it is.. }
-\vskip -0.5cm
 The median run-time for our benchmark set is 9.4\,s.  Overall, the average
@@
 (OVA).\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}
+The provided experimental environment runs multiple discretisations for each
+benchmark, but only lists the fastest as the result synthesis time.
 
@@
 select suitable FWL word widths to model the plant behavior employs a
-heuristic based on user-provided controller word-width specifications \blue{[explain how precision is increased as number of bits?]}.  For
-the first approach, where we may need to increase the precision of the time
+heuristic based on user-provided controller word-width specifications.
+In order to be compliant with the CBMC type API, we increase the precision
+by 8 bits at each step.
+For the first approach, where we may need to increase the precision of the time
 discretization, we select the time steps for the discretizations on a
@@
 x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
-  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{i=n-1}(A_d - B_dK)^iB_dk\delta
+  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{i=n-1}(A_d - B_dK)^iB_dk\delta. 
 \end{align*}
@@
 original system with an infinite-precision controller is stable, because we
-have synthesized it to meet Jury's criterion.  Hence, $(A_d - B_dK)^n \cdot
-x_0$ must converge to zero.
+have synthesized it to meet Jury's criterion.  Hence, $(A_d - B_dK)^n x_0$ 
+must converge to zero.
 

### 2017-05-05 cav2017/cav2017.tex
Some fixes

@@
 \item Compute the characteristic polynomial of the matrix $(A_d-B_dK)$ as 
-$P_a(z) = z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}$. 
-\blue{[shouldn't there be a b term in the polynomial's coefficients here?]}
+$P_a(z) = z^n+\sum_{i=1}^n{(a_i-k_i)z^{n-i}}$. 
+%\blue{[shouldn't there be a b term in the polynomial's coefficients here? No. the polynomial only evaluates the poles]}
 %%   A controllable system with quantization will have the following dynamics, where
@@
 %
-where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is
+where  $q_1$ is the error introduced by the truncation in the ADC, $q_2$ is
 the error introduced by the DAC and $q_3$ is the maximum truncation and
@@
 \item Calculate a set of initial bounds on $K$, $\phi_\mathit{init}^{K}$,
-based on the input constraints \blue{[how is this practically done?]}.  
-Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space. 
+based on the input constraints %\blue{[how is this practically done?With the equation below]}.  
 %
@@
 \Rightarrow \phi_\mathit{init}^{K}$$
+Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
 
@@
   progression of the system from $\phi_\mathit{init}$ over time,
-$x_{k+1} \models \phi_\mathit{safety}$ \blue{why $k+1$ here?}. %% For this purpose we require 
+$x_{k} \models \phi_\mathit{safety}$. %\blue{why $k+1$ here?}. %% For this purpose we require 
 %% an initial set $\phi_\mathit{init}= x_0 \in [\underline{x_0} \ \overline{x_0}]$ 
@@
 %
-where \blue{[what is $t$ in $t^k$?]} $\mathcal{A}=\bigcup_{k=1}^\infty (A_d-B_dK)t^k,
+where $\mathcal{A}=\bigcup_{k=1}^\infty (A_d-B_dK)^k,
 \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k(A_d-B_dK)^iB_{n}$ are
@@
 \item We use $\phi_\Lambda$ to
-  further constrain the characteristic polynomial \blue{[again, check the coefficients of the characteristic polynomial.]} 
+  further constrain the characteristic polynomial %\blue{[again, check the coefficients of the characteristic polynomial.]I don't find any error} 
 $z^n+\sum_{i=1}^n(a_i-k_i)z^{n-i}=\prod_{i=1}^n (z-\lambda_i) : |\lambda_i|<1 \wedge \lambda_i \models \phi_{\Lambda}$.
@@
 All experiments are performed considering $\underline{x_{i}}=-1$ and 
-$\overline{x_{i}}=1$ \blue{[what does this mean:] and the inputs $u_{k}=0, \forall k>0$}.
+$\overline{x_{i}}=1$ and the reference inputs $r_{k}=0, \forall k>0$.
 We conduct the experimental evaluation on a 12-core 2.40\,GHz Intel
@@
 implementation).  This sampling uses a threshold which is defined by the
-less significant bit \blue{[this quantity was named $c_m$ above and in other parts of the paper - please uniformise notations]} ($q_{c}=2^{-F_c}$) of the ADC and some non-linearities
-of the circuitry.  The overall conversion is
+less significant bit ($q_{c}=c_{m_c}=2^{-F_c}$) 
+%\blue{[this quantity was named $c_m$ above and in other parts of the paper - please uniformise notations]}
+of the ADC and some non-linearities of the circuitry.  The overall conversion is
 %

### 2017-05-05 cav2017/cav2017.tex
minor typo

@@
 eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
-circle of the complex plane, i.e., if their absolute values are strictly less than
+circle of the complex plane, i.e., their absolute values are strictly less than
 one~\cite{astrom1997computer} (this simple sufficient condition can be generalised, 

### 2017-05-05 cav2017/cav2017.tex
define Ts
tidying

@@
 \vspace{0.1cm}
-\caption{Completeness threshold for multi-staged verification \blue{[Explain meaning of Ts, which I don't think is introduced anywhere in the current draft.]}}
+\caption{Completeness threshold for multi-staged verification. $T_s$ is the time step for the time discretization of the control matrices.}
 \label{fig:ct}
@@
 suitable candidates and it returns UNSAT, meaning that the current precision is
-insufficient.  Consequently, we increase the precision to $I_p=17$,
-$F_p=7$. \blue{[ Explain how precision is increased, byte-congruent.]}
+insufficient.  Consequently, we increase the precision the plant is modelled with to $I_p=17$,
+$F_p=7$. We increase the precision by 8 bits each step in order to be compliant with the CBMC type API.
 %
@@
 x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
-x_{2} &= (A_d  - B_dK)((A_d  - B_dK)x_0 + B_dK\delta ) + B_dK\delta \\
+x_{2} %&= (A_d  - B_dK)((A_d  - B_dK)x_0 + B_dK\delta ) + B_dK\delta \\
  &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
@@
 
-To show that a fixed-point implementation of the same controller will
-converge to a finite value, we need to show that the infinite sum converges. 
-A known result is that a power series of matrices
-converges~\cite{horn1990matrix}, iff the eigenvalues of the matrix are less
-than~1, as follows:
+%T%o show that a fixed-point implementation of the same controller will
+%converge to a finite value, we need to show that the infinite sum converges. 
+The power series of matrices
+converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less
+than~1 as follows:
 %

### 2017-05-05 cav2017/cav2017.tex
ref appendix

@@
 to check that the (perturbed, noisy) model converges to a neighborhood of
-the equilibrium within the safe set.
+the equilibrium within the safe set (see Appendix~\ref{sec:stab_FWL}.
 
@@
 %-------------------------------
-
+\label{sec:stab_FWL}
 The proof of Jury's criterion~\cite{fadali} relies on the fact that the relationship between states and

### 2017-05-05 cav2017/cav2017.tex
typo

@@
 to check that the (perturbed, noisy) model converges to a neighborhood of
-the equilibrium within the safe set (see Appendix~\ref{sec:stab_FWL}.
+the equilibrium within the safe set (see Appendix~\ref{sec:stab_FWL}).
 

### 2017-05-05 cav2017/cav2017.tex
spelling, grammar

@@
 evolving over a continuous state space and accounting for errors due to the
-digitalization of signals by the controller.  Our approach has two stages,
+digitization of signals by the controller.  Our approach has two stages,
 leveraging counterexample guided inductive synthesis (CEGIS) and
@@
 verification step fails, we refine the controller by generalizing the
-counterexample.  We display the practical value of this approach by automatically synthesizing safe controllers for intricate
+counterexample.  We demonstrate the practical value of this approach by automatically synthesizing safe controllers for intricate
 physical plant models from the digital control literature. 
@@
 Linear Time Invariant (LTI) models represent a broad class of dynamical
-systems with significant impact in numerous application areas such as in life
+systems with significant impact in numerous application areas such as life
 sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}. 
@@
 of finite-precision arithmetic, time discretization, and quantization noise,
-which are typically introduced by Analogue-to-Digital (ADC) and
+which is typically introduced by Analogue-to-Digital (ADC) and
 Digital-to-Analogue (DAC) conversion.  While research on digital control is
@@
 However, these methods have not been generalized to control synthesis.  
-Notice that a synthesis algorithm that guarantees stability does not
+Note that a synthesis algorithm that guarantees stability does not
 ensure safety: the system might transitively visit an unsafe state resulting in unrecoverable failure.
@@
 quantisation errors in ADC and DAC, 
-representation errors (from the discretisation introduced by finite-precision arithmetics), 
+representation errors (from the discretization introduced by finite-precision arithmetic), 
 and roundoff and saturation errors in the verification process 
@@
 Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}.  We prove
-their soundness by quantifying errors caused by digitalization and
-quantization effects that arise when time/value-discrete digital controller
+their soundness by quantifying errors caused by digitization and
+quantization effects that arise when %time/value-discrete 
+the digital controller
 interacts with the continuous plant.
@@
 a specified range, the reference signal to be set to zero, saturation on the
-inputs, and account for digitalization and quantization errors introduced by
+inputs, and account for digitization and quantization errors introduced by
 the controller.

### 2017-05-05 cav2017/cav2017.tex
spelling/grammar

@@
 switching controllers with a guaranteed minimum dwell time in each mode. 
-However, both approaches are not suitable for the kind of control we seek to
+However, both approaches are unsuitable for the kind of control we seek to
 synthesize.
@@
 which requires ensuring the specification over actual traces of the model, 
-alongside the numerical soundness required by the effects of discretisation and imprecision errors.   
+alongside the numerical soundness required by the effects of discretization and imprecision errors.   
 A state-space model has known advantages over the transfer function
@@
 (i.e., with multiple inputs and outputs); (ii)~gives the state-to-input
-relationships, offering an internal model of the system; and (iii)~allows to
-synthesize control systems with guarantees on the internal dynamics, e.g.,
+relationships, offering an internal model of the system; and (iii)~allows the
+synthesis of control systems with guarantees on the internal dynamics, e.g.,
 to synthesize controllers that make the closed-loop system \emph{safe}.  Our
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Modelling quantization as noise} \label{appendix:quantization-noise}
+\subsection{Modeling quantization as noise} \label{appendix:quantization-noise}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-05-05 cav2017/cav2017.tex
weird sentence
literature and refs

--- 2017-05-05 cav2017/cav2017.tex
@@
 beyond classical stability.  There are recent methods for verifying
-reachability properties of a given controller~\cite{FLD+11,Fre05}. 
+reachability properties of a given controller~\cite{FLD+11}. 
 However, these methods have not been generalized to control synthesis.  
@@
 Program synthesis is the problem of computing correct-by-design programs
-from high-level specifications; algorithms for this problem have made
-substantial progress in recent years.  One such
-approach~\cite{itzhaky2010simple} inductively synthesizes invariants to
-generate the desired programs.
-
-Program synthesizers are an ideal fit for synthesis of controllers, since
+from high-level specifications. Algorithms for this problem have made
+substantial progress in recent years, for instance~\cite{itzhaky2010simple} to inductively synthesize invariants for the 
+generation of desired programs.
+
+Program synthesizers are an ideal fit for the synthesis of digital controllers, since
 the semantics of programs capture the effects of finite-precision arithmetic
@@
 bit-accurate verification of software-implemented digital
-controllers~\cite{IsmailBCFF15, Bessa16}.  While this work also uses CEGIS,
+controllers~\cite{%IsmailBCFF15, 
+Bessa16}.  While this work also uses CEGIS,
 the approach is restricted to digital controllers for stable closed-loop
@@
 which requires ensuring the specification over actual traces of the model, 
-alongside the numerical soundness required by the effects of discretisation and imprecision errors.   
+alongside the numerical soundness required by the effects of discretisation and finite-precision errors.   
 A state-space model has known advantages over the transfer function
-representation~\cite{Astrom08}: (i)~it naturally generalizes to multivariate systems
-(i.e., with multiple inputs and outputs); (ii)~gives the state-to-input
-relationships, offering an internal model of the system; and (iii)~allows to
-synthesize control systems with guarantees on the internal dynamics, e.g.,
+representation~\cite{Franklin15}: it naturally generalizes to multivariate systems
+(i.e., with multiple inputs and outputs); 
+%(ii)~gives the state-to-input relationships, offering an internal model of the system;  
+and it allows to synthesize control systems with guarantees on the internal dynamics, e.g.,
 to synthesize controllers that make the closed-loop system \emph{safe}.  Our
@@
 overlooked in the literature.  Moreover, our work integrates an
-abstraction/refinement step inside the main CEGIS loop.
+abstraction/refinement (CEGAR) step inside the main CEGIS loop.
 
@@
 physical system to an equivalent finite-state machine and on the computation
-of reachability properties over the finite-state machine.  Based on this
-safety specification, \mbox{Pessoa} can synthesize embedded controller
+of reachability properties thereon. 
+%over the finite-state machine.  
+Based on this safety specification, \mbox{Pessoa} can synthesize embedded controller
 software for a range of properties.  The embedded controller software can be
-more complicated than the state-feedback control we synthesized, and the
+more complicated than the state-feedback control we synthesize, and the
 properties available cover more detail. 
@@
 %
-However, Pessoa does not have consider the quantization error introduced by
-Digital-to-Analogue/Analogue-to-Digital conversion needed for synthesizing
-fixed-point digital controllers.
+However, relying on state-space discretization \mbox{Pessoa} is likely to incur in scalability limitations. 
+Along this research line, \cite{Anta2010,liu16} studies the synthesis of digital controllers for continuous dynamics, 
+and \cite{zamani2014} extends the approach to the recent setup of Network Control Systems.
 
@@
 
-The classical approach to control synthesis has often disregarded
-quantization, thus sacrificing soundness.  Modern techniques focus on
+The classical approach to control synthesis has often disregarded digitalization effects, 
+%thus sacrificing soundness. 
+whereas more recently modern techniques have focused on
 different aspects of discretization, including delayed
@@
 is the error in the dynamics caused by the inability to represent the exact
-state of the physical system, while the second relates to rounding errors
+state of the physical system, while the second relates to rounding and saturation errors
 during computation.  In~\cite{fialho1994stability}, a stability measure
@@
 where the verification of given control code is performed against a known
-model by extracting an LTI model of the code by symbolic execution. 
-To~account for rounding errors, an upper bound is introduced in the
-verification phase.  The work in \cite{picasso2003stabilization,
-picasso2002construction} introduces attractive invariant sets as a mechanism
+model by extracting an LTI model of the code by symbolic execution:  
+to account for rounding errors, an upper bound is introduced in the
+verification phase.  The work in \cite{picasso2003stabilization}
+%picasso2002construction} 
+introduces attractive invariant sets as a mechanism
 to bound the quantization error effect on stabilization as an invariant set
@@
 to check that the (perturbed, noisy) model converges to a neighborhood of
-the equilibrium within the safe set (see Appendix~\ref{sec:stab_FWL}).
+the equilibrium within the safe set.
 
 In the following, we shall disregard these steady-state errors (caused by
-FWL effects) when the stability is ensured by synthesis, and then verify its
+FWL effects) when stability is ensured by synthesis, and then verify its
 safety accounting for the finite-precision errors.
@@
 suitable candidates and it returns UNSAT, meaning that the current precision is
-insufficient.  Consequently, we increase the precision the plant is modelled with to $I_p=17$,
-$F_p=7$. We increase the precision by 8 bits each step in order to be compliant with the CBMC type API.
+insufficient.  Consequently, we increase the precision to $I_p=17$,
+$F_p=7$. \blue{[ Explain how precision is increased, byte-congruent.]}
 %
@@
 %-------------------------------
-\label{sec:stab_FWL}
+
 The proof of Jury's criterion~\cite{fadali} relies on the fact that the relationship between states and
@@
 
-%T%o show that a fixed-point implementation of the same controller will
-%converge to a finite value, we need to show that the infinite sum converges. 
-The power series of matrices
-converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less
-than~1 as follows:
+To show that a fixed-point implementation of the same controller will
+converge to a finite value, we need to show that the infinite sum converges. 
+A known result is that a power series of matrices
+converges~\cite{horn1990matrix}, iff the eigenvalues of the matrix are less
+than~1, as follows:
 %
@@
 %\label{eq:pre_quantization}
-{x}_{k+1} &= {A}_d{x}_k+{B}_d({u}_k+{{\nu}_2}_k)\\
-u_k&=-K{x}_{k}+{{\nu}_1}_k \,,
+{x}_{k+1} = {A}_d{x}_k+{B}_d({u}_k+{{\nu}_2}_k), \quad u_k = -K{x}_{k}+{{\nu}_1}_k, 
 \end{align*}

### 2017-05-05 cav2017/cav2017.tex
solve conflict in related work

@@
 which requires ensuring the specification over actual traces of the model, 
+%<<<<<<< HEAD
 alongside the numerical soundness required by the effects of discretisation and finite-precision errors.   
@@
 and it allows to synthesize control systems with guarantees on the internal dynamics, e.g.,
+%=======
+%% alongside the numerical soundness required by the effects of discretization and imprecision errors.   
+%% A state-space model has known advantages over the transfer function
+%% representation~\cite{Astrom08}: (i)~it naturally generalizes to multivariate systems
+%% (i.e., with multiple inputs and outputs); (ii)~gives the state-to-input
+%% relationships, offering an internal model of the system; and (iii)~allows the
+%% synthesis of control systems with guarantees on the internal dynamics, e.g.,
+%% >>>>>>> 14b2cf34a87b12f077cef9a8fca94e2213ab9364
 to synthesize controllers that make the closed-loop system \emph{safe}.  Our
@@
 multiplication operation.  We represent these errors as non-deterministic
-additive noise, which might de-stabilize the closed-loop model.
+additive noise.%, which might de-stabilize the closed-loop model.
 
@@
 to check that the (perturbed, noisy) model converges to a neighborhood of
-the equilibrium within the safe set.
+the equilibrium within the safe set (see Appendix~\ref{sec:stab_FWL}).
 

### 2017-05-05 cav2017/cav2017.tex
nudge

--- 2017-05-05 cav2017/cav2017.tex
@@
 evolving over a continuous state space and accounting for errors due to the
-digitization of signals by the controller.  Our approach has two stages,
+digitalization of signals by the controller.  Our approach has two stages,
 leveraging counterexample guided inductive synthesis (CEGIS) and
@@
 verification step fails, we refine the controller by generalizing the
-counterexample.  We demonstrate the practical value of this approach by automatically synthesizing safe controllers for intricate
+counterexample.  We display the practical value of this approach by automatically synthesizing safe controllers for intricate
 physical plant models from the digital control literature. 
@@
 Linear Time Invariant (LTI) models represent a broad class of dynamical
-systems with significant impact in numerous application areas such as life
+systems with significant impact in numerous application areas such as in life
 sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}. 
@@
 of finite-precision arithmetic, time discretization, and quantization noise,
-which is typically introduced by Analogue-to-Digital (ADC) and
+which are typically introduced by Analogue-to-Digital (ADC) and
 Digital-to-Analogue (DAC) conversion.  While research on digital control is
@@
 However, these methods have not been generalized to control synthesis.  
-Note that a synthesis algorithm that guarantees stability does not
+Notice that a synthesis algorithm that guarantees stability does not
 ensure safety: the system might transitively visit an unsafe state resulting in unrecoverable failure.
@@
 quantisation errors in ADC and DAC, 
-representation errors (from the discretization introduced by finite-precision arithmetic), 
+representation errors (from the discretisation introduced by finite-precision arithmetics), 
 and roundoff and saturation errors in the verification process 
@@
 Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}.  We prove
-their soundness by quantifying errors caused by digitization and
-quantization effects that arise when %time/value-discrete 
-the digital controller
+their soundness by quantifying errors caused by digitalization and
+quantization effects that arise when time/value-discrete digital controller
 interacts with the continuous plant.
@@
 switching controllers with a guaranteed minimum dwell time in each mode. 
-However, both approaches are unsuitable for the kind of control we seek to
+However, both approaches are not suitable for the kind of control we seek to
 synthesize.
@@
 which requires ensuring the specification over actual traces of the model, 
-alongside the numerical soundness required by the effects of discretization and imprecision errors.   
+alongside the numerical soundness required by the effects of discretisation and imprecision errors.   
 A state-space model has known advantages over the transfer function
@@
 (i.e., with multiple inputs and outputs); (ii)~gives the state-to-input
-relationships, offering an internal model of the system; and (iii)~allows the
-synthesis of control systems with guarantees on the internal dynamics, e.g.,
+relationships, offering an internal model of the system; and (iii)~allows to
+synthesize control systems with guarantees on the internal dynamics, e.g.,
 to synthesize controllers that make the closed-loop system \emph{safe}.  Our
@@
 eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
-circle of the complex plane, i.e., their absolute values are strictly less than
+circle of the complex plane, i.e., if their absolute values are strictly less than
 one~\cite{astrom1997computer} (this simple sufficient condition can be generalised, 
@@
 to check that the (perturbed, noisy) model converges to a neighborhood of
-the equilibrium within the safe set (see Appendix~\ref{sec:stab_FWL}).
+the equilibrium within the safe set.
 
@@
 a specified range, the reference signal to be set to zero, saturation on the
-inputs, and account for digitization and quantization errors introduced by
+inputs, and account for digitalization and quantization errors introduced by
 the controller.
@@
 \vspace{0.1cm}
-\caption{Completeness threshold for multi-staged verification. $T_s$ is the time step for the time discretization of the control matrices.}
+\caption{Completeness threshold for multi-staged verification \blue{[Explain meaning of Ts, which I don't think is introduced anywhere in the current draft.]}}
 \label{fig:ct}
@@
 inputs, and time horizons during the verification phase.
-Essentially, this approach relies on the \blue{[qualitative term, please elaborate:] explicit
-simulation} over a bounded time horizon of individual states that form
+Essentially, this approach relies on the symbolic
+simulation over a bounded time horizon of individual initial states and inputs that form
 part of an uncountable space and tries to generalize it for an
@@
 x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
-x_{2} %&= (A_d  - B_dK)((A_d  - B_dK)x_0 + B_dK\delta ) + B_dK\delta \\
+x_{2} &= (A_d  - B_dK)((A_d  - B_dK)x_0 + B_dK\delta ) + B_dK\delta \\
       &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Modeling quantization as noise} \label{appendix:quantization-noise}
+\subsection{Modelling quantization as noise} \label{appendix:quantization-noise}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-05-05 cav2017/cav2017.tex
grammar
edited threats to validity

--- 2017-05-05 cav2017/cav2017.tex
@@
 %
-\textit{Plant precision and discretization heuristic:} Our algorithm to
-select suitable FWL word widths to model the plant behavior employs a
-heuristic based on user-provided controller word-width specifications.
-In order to be compliant with the CBMC type API, we increase the precision
-by 8 bits at each step.
-For the first approach, where we may need to increase the precision of the time
-discretization, we select the time steps for the discretizations on a
-similar basis.  This works sufficiently well for our benchmarks, but
+\textit{Plant precision and discretization heuristics:} Our algorithm to
+select suitable FWL word widths to model the plant behavior %% employs a
+%% heuristic based on user-provided controller word-width specifications.
+increases the precision by 8 bits at each step 
+in order to be compliant with the CBMC type API. %% , we increase the precision
+%% by 8 bits at each step.
+Similarly, for discretization, we run multiple discretisations for each
+benchmark and retain the fastest run.
+%% where we may need to increase the precision of the time
+%% discretization,
+%% we select the time steps for the discretizations on a
+%% similar basis.
+This works sufficiently well for our benchmarks, but
 performance may suffer in some cases, for example if the completeness

### 2017-05-05 cav2017/cav2017.tex

@@
 %(ii)~gives the state-to-input relationships, offering an internal model of the system;  
-and it allows to synthesize control systems with guarantees on the internal dynamics, e.g.,
+and it allows synthesis of control systems with guarantees on the internal dynamics, e.g.,
 %=======

### 2017-05-05 cav2017/cav2017.tex
small rephrasing

@@
 The provided experimental environment runs multiple discretisations for each
-benchmark, but only lists the fastest as the result synthesis time.
+benchmark, and lists the fastest as the result synthesis time.
 

### 2017-05-05 cav2017/cav2017.tex
Small spelling correction
Used American English instead of British.
Added AE badge
Added the AE .pdf and command.

@@
 \usepackage{pifont}
+
+\usepackage[firstpage]{draftwatermark}\SetWatermarkText{\hspace*{5.2in}\raisebox{5in}{\includegraphics[scale=0.1]{aec-badge-cav}}}\SetWatermarkAngle{0}
 
@@
 %% by 8 bits at each step.
-Similarly, for discretization, we run multiple discretisations for each
+Similarly, for discretization, we run multiple discretizations for each
 benchmark and retain the fastest run.

### 2017-05-05 cav2017/cav2017.tex
Added explanation for K=[0,0,0]
Explained zero controller choice with lack of knwoledge about the system
and ease of reproduction.
abstract suggested changes

@@
 evolving over a continuous state space and accounting for errors due to the
-digitization of signals by the controller.  Our approach has two stages,
-leveraging counterexample guided inductive synthesis (CEGIS) and
-reachability analysis.  CEGIS synthesizes a static feedback controller that
-stabilizes the system under restrictions given by the safety of the reach
-space.  Safety is verified either via BMC or abstract acceleration; if the
-verification step fails, we refine the controller by generalizing the
-counterexample.  We demonstrate the practical value of this approach by automatically synthesizing safe controllers for intricate
+digitization of signals by the controller.  
+Our counterexample guided inductive synthesis (CEGIS) approach has two phases: We synthesize a static feedback controller that stabilizes the system but that may not be safe for all initial conditions.
+Safety is then verified either via BMC or abstract acceleration; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until a safe controller is obtained.
+%Our approach has two stages,
+%leveraging counterexample guided inductive synthesis (CEGIS) and
+%reachability analysis.  CEGIS synthesizes a static feedback controller that
+%stabilizes the system under restrictions given by the safety of the reach
+%space.  Safety is verified either via BMC or abstract acceleration; if the
+%verification step fails, we refine the controller by generalizing the
+%counterexample.  
+We demonstrate the practical value of this approach by automatically synthesizing safe controllers for intricate
 physical plant models from the digital control literature. 
@@
 %
-We start with a candidate solution with all coefficients zero, $K=[0
-  \ 0 \ 0]^T$ \blue{[an attempted explanation of this first guess is due.]}, and a precision of $I_p=13$, $F_p=3$.  In the first
+Since we have not learned any information about the system yet,
+we pick an arbitrary candidate solution (we always choose $K=[0
+  \ 0 \ 0]^T$ in our experiments to simplify reproduction), and a
+precision of $I_p=13$, $F_p=3$.  In the first
 {\sc verify} stage, the {\sc safety} check finds the counterexample

### 2017-05-23 automatica/automatica.tex
automatica template

% autosam.tex
% Annotated sample file for the preparation of LaTeX files
% for the final versions of papers submitted to or accepted for 
% publication in AUTOMATICA.

% See also the Information for Authors.

% Make sure that the zip file that you send contains all the 
% files, including the files for the figures and the bib file.

% Output produced with the elsart style file does not imitate the
% AUTOMATICA style. The style file is generic for all Elsevier
% journals and the output is laid out for easy copy editing. The
% final document is produced from the source file in the
% AUTOMATICA style at Elsevier.

% You may use the style file autart.cls to obtain a two-column 
% document (see below) that more or less imitates the printed 
% Automatica style. This may helpful to improve the formatting 
% of the equations, tables and figures, and also serves to check 
% whether the paper satisfies the length requirements.

% Please note: Authors must not create their own macros.

% For further information regarding the preparation of LaTeX files 
% for Elsevier, please refer to the "Full Instructions to Authors" 
% from Elsevier's anonymous ftp server on ftp.elsevier.nl in the
% directory pub/styles, or from the internet (CTAN sites) on
% ftp.shsu.edu, ftp.dante.de and ftp.tex.ac.uk in the directory
% tex-archive/macros/latex/contrib/supported/elsevier.

%\documentclass{elsart}               % The use of LaTeX2e is preferred.

\documentclass[twocolumn]{autart}    % Enable this line and disable the 
                                     % preceding line to obtain a two-column 
                                     % document whose style resembles the
                                     % printed Automatica style.

\usepackage{graphicx}          % Include this line if your 
                               % document contains figures,
%\usepackage[dvips]{epsfig}    % or this line, depending on which
                               % you prefer.

\begin{document}

\begin{frontmatter}
%\runtitle{Insert a suggested running title}  % Running title for regular 
                                              % papers but only if the title  
                                              % is over 5 words. Running title 
                                              % is not shown in output.

\title{In Catilinam IV\thanksref{footnoteinfo}} % Title, preferably not more 
                                                % than 10 words.

\thanks[footnoteinfo]{This paper was not presented at any IFAC 
meeting. Corresponding author M.~T.~Cicero. Tel. +XXXIX-VI-mmmxxi. 
Fax +XXXIX-VI-mmmxxv.}

\author[Paestum]{Marcus Tullius Cicero}\ead{cicero@senate.ir},    % Add the 
\author[Rome]{Julius Caesar}\ead{julius@caesar.ir},               % e-mail address 
\author[Baiae]{Publius Maro Vergilius}\ead{vergilius@culture.ir}  % (ead) as shown

\address[Paestum]{Buckingham Palace, Paestum}  % Please supply                                              
\address[Rome]{Senate House, Rome}             % full addresses
\address[Baiae]{The White House, Baiae}        % here.

\begin{keyword}                           % Five to ten keywords,  
Cicero; Catiline; orations.               % chosen from the IFAC 
\end{keyword}                             % keyword list or with the 
                                          % help of the Automatica 
                                          % keyword wizard

\begin{abstract}                          % Abstract of not more than 200 words.
Cum M.~Cicero consul Nonis Decembribus senatum in aede Iovis 
Statoris consuleret, quid de iis coniurationis Catilinae sociis 
fieri placeret, qui in custodiam traditi essent, factum est, ut 
duae potissimum sententiae proponerentur, una D.~Silani consulis 
designati, qui morte multandos illos censebat, altera C.~Caesaris, 
qui illos publicatis bonis per municipia Italiae distribuendos 
ac vinculis sempiternis tenendos existimabat.
\end{abstract}

\end{frontmatter}

\section{Introduction}
Video, patres conscripti, in me omnium vestrum ora atque oculos esse 
conversos, video vos non solunn de vestro ac rei publicae, verum 
etiam, si id depulsum sit, de meo periculo esse sollicitos. Est mihi 
iucunda in malis et grata in dolore vestra erga me voluntas, sed eam, 
per deos inmortales, deponite atque obliti salutis meae de vobis ac 
de vestris liberis cogitate. Mihi si haec condicio consulatus data 
est, ut omnis acerbitates, onunis dolores cruciatusque perferrem, 
feram non solum fortiter, verum etiam lubenter, dum modo meis 
laboribus vobis populoque Romano dignitas salusque pariatur.

%\begin{figure}
%\begin{center}
%\includegraphics[height=4cm]{jcaesar.eps}    % The printed column  
%\caption{Gaius Julius Caesar, 100--44 B.C.}  % width is 8.4 cm.
%\label{fig1}                                 % Size the figures 
%\end{center}                                 % accordingly.
%\end{figure}

% OR

%\begin{figure}
%\begin{center}
%\epsfig{file=jcaesar,width=7cm}
%\caption{Gaius Julius Caesar, 100--44 B.C.}
%\label{fig1}
%\end{center}
%\end{figure}

\subsection{A subsection}
Marcus Tullius Cicero, 106--43 B.C. was a Roman statesman, orator, 
and philosopher.  A major figure in the last years of the Republic, 
he is best known for his orations against Catiline\footnote{
This footnote should be very brief.}
and for his mastery of Latin prose \cite{Heritage:92}. He was a 
contemporary of Julius Caesar (Fig.~\ref{fig1}).

\section{The argument}
Some words might be appropriate describing equation~(\ref{e1}), if 
we had but time and space enough.
\begin{equation} \label{e1}
{{\partial F}\over {\partial t}} =
D{{\partial^2 F}\over {\partial x^2}}.
\end{equation}
See \cite{Abl:56}, \cite{AbTaRu:54}, \cite{Keo:58} and 
\cite{Pow:85}.
This equation goes far beyond the celebrated theorem ascribed to the great
Pythagoras by his followers.
\begin{thm}
The square of the length of the hypotenuse of a right triangle equals the sum of the squares 
of the lengths of the other two sides.
\end{thm}
\section{Epilogue}
A word or two to conclude, and this even includes some inline 
maths:  $R(x,t)\sim t^{-\beta}g(x/t^\alpha)\exp(-|x|/t^\alpha)$.

\begin{ack}                               % Place acknowledgements
Partially supported by the Roman Senate.  % here.
\end{ack}

\bibliographystyle{plain}        % Include this if you use bibtex 
\bibliography{paper}           % and a bib file to produce the 
                                 % bibliography (preferred). The
                                 % correct style is generated by
                                 % Elsevier at the time of printing.

%\begin{thebibliography}{99}     % Otherwise use the  
                                 % thebibliography environment.
                                 % Insert the full references here.
                                 % See a recent issue of Automatica 
                                 % for the style.
%  \bibitem[Heritage, 1992]{Heritage:92}
%     (1992) {\it The American Heritage. 
%     Dictionary of the American Language.}
%     Houghton Mifflin Company.
%  \bibitem[Able, 1956]{Abl:56}
%     B.~C.~Able (1956). Nucleic acid content of macroscope. 
%     {\it Nature 2}, 7--9. 
%  \bibitem[Able {\em et al.}, 1954]{AbTaRu:54}   
%     B.~C. Able, R.~A. Tagg, and M.~Rush (1954).
%     Enzyme-catalyzed cellular transanimations.
%     In A.~F.~Round, editor, 
%     {\it Advances in Enzymology Vol. 2} (125--247). 
%     New York, Academic Press.
%  \bibitem[R.~Keohane, 1958]{Keo:58}
%     R.~Keohane (1958).
%     {\it Power and Interdependence: 
%     World Politics in Transition.}
%     Boston, Little, Brown \& Co.
%  \bibitem[Powers, 1985]{Pow:85}
%     T.~Powers (1985).
%     Is there a way out?
%     {\it Harpers, June 1985}, 35--47.

%\end{thebibliography}

\appendix
\section{A summary of Latin grammar}    % Each appendix must have a short title.
\section{Some Latin vocabulary}         % Sections and subsections are supported  
                                        % in the appendices.
\end{document}

### 2017-05-24 automatica/automatica.tex
added paper title
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
added authors and affiliations
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\title{In Catilinam IV\thanksref{footnoteinfo}} % Title, preferably not more 
+%\thanksref{footnoteinfo}
+
+\title{Safe and Robust Formal  Synthesis of Digital Controllers for Continuous Plants with Transient Performance Specifications} % Title, preferably not more 
                                                 % than 10 words.
 
-\thanks[footnoteinfo]{This paper was not presented at any IFAC 
-meeting. Corresponding author M.~T.~Cicero. Tel. +XXXIX-VI-mmmxxi. 
-Fax +XXXIX-VI-mmmxxv.}
+%\thanks[footnoteinfo]{This paper was not presented at any IFAC 
+%meeting. Corresponding author M.~T.~Cicero. Tel. +XXXIX-VI-mmmxxi. 
+%Fax +XXXIX-VI-mmmxxv.}
 
-\author[Paestum]{Marcus Tullius Cicero}\ead{cicero@senate.ir},    % Add the 
-\author[Rome]{Julius Caesar}\ead{julius@caesar.ir},               % e-mail address 
-\author[Baiae]{Publius Maro Vergilius}\ead{vergilius@culture.ir}  % (ead) as shown
+\author[abate]{Alessandro Abate}\ead{alessandro.abate@cs.ox.ac.uk},
+\author[bessa]{Iury Bessa}\ead{iurybessa@ufam.edu.br},
+\author[cattaruzza]{Dario Cattaruzza}\ead{dario.cattaruzza@cs.ox.ac.uk},
+\author[cordeiro]{Lucas Cordeiro}\ead{lucas.cordeiro@cs.ox.ac.uk},
+\author[david]{Cristina David}\ead{cristina.david@cs.ox.ac.uk},
+\author[kesseli]{Pascal Kessel}\ead{pascal.kesseli@stx.ox.ac.uk},
+\author[kroening]{Daniel Kroening}\ead{kroening@cs.ox.ac.uk},
+\author[polgreen]{Elizabeth Polgreen}\ead{elizabeth.polgreen@linacre.ox.ac.uk}
 
-\address[Paestum]{Buckingham Palace, Paestum}  % Please supply                                              
-\address[Rome]{Senate House, Rome}             % full addresses
-\address[Baiae]{The White House, Baiae}        % here.
+\address[abate]{University of Oxford, UK}
+\address[bessa]{Federal University of Amazonas, Brazil}
+\address[cattaruzza]{University of Oxford, UK}
+\address[cordeiro]{University of Oxford, UK}
+\address[david]{University of Oxford, UK}
+\address[kesseli]{University of Oxford, UK}
+\address[kroening]{University of Oxford, UK}
+\address[polgreen]{University of Oxford, UK}
+
+%\author[Paestum]{Marcus Tullius Cicero}\ead{cicero@senate.ir},    % Add the 
+%\author[Rome]{Julius Caesar}\ead{julius@caesar.ir},               % e-mail address 
+%\author[Baiae]{Publius Maro Vergilius}\ead{vergilius@culture.ir}  % (ead) as shown
+
+%\address[Paestum]{Buckingham Palace, Paestum}  % Please supply                                              
+%\address[Rome]{Senate House, Rome}             % full addresses
+%\address[Baiae]{The White House, Baiae}        % here.
 

### 2017-05-24 automatica/automatica.tex
we should write a new abstract and introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
                                % you prefer.
+\usepackage{color}
 
@@
 \begin{abstract}                          % Abstract of not more than 200 words.
-Cum M.~Cicero consul Nonis Decembribus senatum in aede Iovis 
-Statoris consuleret, quid de iis coniurationis Catilinae sociis 
-fieri placeret, qui in custodiam traditi essent, factum est, ut 
-duae potissimum sententiae proponerentur, una D.~Silani consulis 
-designati, qui morte multandos illos censebat, altera C.~Caesaris, 
-qui illos publicatis bonis per municipia Italiae distribuendos 
-ac vinculis sempiternis tenendos existimabat.
+\textcolor{red}{We have to write a new abstract.}
 \end{abstract}
@@
 \section{Introduction}
-Video, patres conscripti, in me omnium vestrum ora atque oculos esse 
-conversos, video vos non solunn de vestro ac rei publicae, verum 
-etiam, si id depulsum sit, de meo periculo esse sollicitos. Est mihi 
-iucunda in malis et grata in dolore vestra erga me voluntas, sed eam, 
-per deos inmortales, deponite atque obliti salutis meae de vobis ac 
-de vestris liberis cogitate. Mihi si haec condicio consulatus data 
-est, ut omnis acerbitates, onunis dolores cruciatusque perferrem, 
-feram non solum fortiter, verum etiam lubenter, dum modo meis 
-laboribus vobis populoque Romano dignitas salusque pariatur.
+\textcolor{red}{We have to write a new introduction as well.}
 

### 2017-05-24 automatica/automatica.tex
fixed affiliations
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\author[abate]{Alessandro Abate}\ead{alessandro.abate@cs.ox.ac.uk},
-\author[bessa]{Iury Bessa}\ead{iurybessa@ufam.edu.br},
-\author[cattaruzza]{Dario Cattaruzza}\ead{dario.cattaruzza@cs.ox.ac.uk},
-\author[cordeiro]{Lucas Cordeiro}\ead{lucas.cordeiro@cs.ox.ac.uk},
-\author[david]{Cristina David}\ead{cristina.david@cs.ox.ac.uk},
-\author[kesseli]{Pascal Kessel}\ead{pascal.kesseli@stx.ox.ac.uk},
-\author[kroening]{Daniel Kroening}\ead{kroening@cs.ox.ac.uk},
-\author[polgreen]{Elizabeth Polgreen}\ead{elizabeth.polgreen@linacre.ox.ac.uk}
+\author[oxford]{Alessandro Abate}\ead{alessandro.abate@cs.ox.ac.uk},
+\author[manaus]{Iury Bessa}\ead{iurybessa@ufam.edu.br},
+\author[oxford]{Dario Cattaruzza}\ead{dario.cattaruzza@cs.ox.ac.uk},
+\author[oxford,manaus]{Lucas Cordeiro}\ead{lucas.cordeiro@cs.ox.ac.uk},
+\author[oxford]{Cristina David}\ead{cristina.david@cs.ox.ac.uk},
+\author[oxford]{Pascal Kessel}\ead{pascal.kesseli@stx.ox.ac.uk},
+\author[oxford]{Daniel Kroening}\ead{kroening@cs.ox.ac.uk},
+\author[oxford]{Elizabeth Polgreen}\ead{elizabeth.polgreen@linacre.ox.ac.uk}
 
-\address[abate]{University of Oxford, UK}
-\address[bessa]{Federal University of Amazonas, Brazil}
-\address[cattaruzza]{University of Oxford, UK}
-\address[cordeiro]{University of Oxford, UK}
-\address[david]{University of Oxford, UK}
-\address[kesseli]{University of Oxford, UK}
-\address[kroening]{University of Oxford, UK}
-\address[polgreen]{University of Oxford, UK}
+\address[oxford]{University of Oxford, UK}
+\address[manaus]{Federal University of Amazonas, Brazil}
 

### 2017-05-24 automatica/automatica.tex
added related work section
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\subsection{A subsection}
-Marcus Tullius Cicero, 106--43 B.C. was a Roman statesman, orator, 
-and philosopher.  A major figure in the last years of the Republic, 
-he is best known for his orations against Catiline\footnote{
-This footnote should be very brief.}
-and for his mastery of Latin prose \cite{Heritage:92}. He was a 
-contemporary of Julius Caesar (Fig.~\ref{fig1}).
+%\subsection{A subsection}
+%Marcus Tullius Cicero, 106--43 B.C. was a Roman statesman, orator, 
+%and philosopher.  A major figure in the last years of the Republic, 
+%he is best known for his orations against Catiline\footnote{
+%This footnote should be very brief.}
+%and for his mastery of Latin prose \cite{Heritage:92}. He was a 
+%contemporary of Julius Caesar (Fig.~\ref{fig1}).
 
-\section{The argument}
-Some words might be appropriate describing equation~(\ref{e1}), if 
-we had but time and space enough.
-\begin{equation} \label{e1}
-{{\partial F}\over {\partial t}} =
-D{{\partial^2 F}\over {\partial x^2}}.
-\end{equation}
-See \cite{Abl:56}, \cite{AbTaRu:54}, \cite{Keo:58} and 
-\cite{Pow:85}.
-This equation goes far beyond the celebrated theorem ascribed to the great
-Pythagoras by his followers.
-\begin{thm}
-The square of the length of the hypotenuse of a right triangle equals the sum of the squares 
-of the lengths of the other two sides.
-\end{thm}
-\section{Epilogue}
-A word or two to conclude, and this even includes some inline 
-maths:  $R(x,t)\sim t^{-\beta}g(x/t^\alpha)\exp(-|x|/t^\alpha)$.
+%-------------------------------
+\section{Related Work}
+\label{sec:relw}
+%-------------------------------
 
-\begin{ack}                               % Place acknowledgements
-Partially supported by the Roman Senate.  % here.
-\end{ack}
+\textbf{CEGIS -}
+Program synthesis is the problem of computing correct-by-design programs
+from high-level specifications. Algorithms for this problem have made
+substantial progress in recent years, for instance~\cite{itzhaky2010simple} 
+to inductively synthesize invariants for the generation of desired programs.
+
+Program synthesizers are an ideal fit for the synthesis of digital controllers, since
+the semantics of programs capture the effects of finite-precision arithmetic
+precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
+for the synthesis of switching controllers for stabilizing continuous-time
+plants with polynomial dynamics.  The work extends to affine systems, but is
+limited by the capacity of the state-of-the-art SMT solvers for solving
+linear arithmetic.  Since this approach uses switching models instead of
+linear dynamics for the digital controller, it avoids problems related to
+finite precision arithmetic, but potentially suffers from state-space
+explosion.  Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same
+authors use a CEGIS-based approach for synthesizing continuous-time
+switching controllers that guarantee \emph{reach-while-stay} properties of
+closed-loop systems, i.e., properties that specify a set of goal states and
+safe states (constrained reachability).  This solution is based on
+synthesizing control Lyapunov functions for switched systems that yield
+switching controllers with a guaranteed minimum dwell time in each mode. 
+However, both approaches are unsuitable for the kind of control we seek to
+synthesize.
+
+The work in~\cite{hscc-paper} synthesizes stabilizing
+controllers for continuous plants given as transfer functions by exploiting
+bit-accurate verification of software-implemented digital
+controllers~\cite{Bessa16}.  While this work also uses CEGIS,
+the approach is restricted to digital controllers for stable closed-loop
+systems given as transfer function models: 
+this results in  a static check on their coefficients.  
+By contrast, in the current paper we consider a state-space representation of the physical system, 
+which requires ensuring the specification over actual traces of the model, 
+alongside the numerical soundness required by the effects of discretisation and finite-precision errors.   
+A state-space model has known advantages over the transfer function
+representation~\cite{Franklin15}: it naturally generalizes to multivariate systems
+(i.e., with multiple inputs and outputs); 
+and it allows synthesis of control systems with guarantees on the internal dynamics, e.g.,
+to synthesize controllers that make the closed-loop system \emph{safe}.  Our
+work focuses on the \emph{safety} of internal states, which is usually
+overlooked in the literature.  Moreover, our work integrates an
+abstraction/refinement (CEGAR) step inside the main CEGIS loop.
+
+The tool Pessoa~\cite{mazo2010pessoa} synthesizes correct-by-design embedded
+control software in a Matlab toolbox.  It is based on the abstraction of a
+physical system to an equivalent finite-state machine and on the computation
+of reachability properties thereon. 
+Based on this safety specification, \mbox{Pessoa} can synthesize embedded controller
+software for a range of properties.  The embedded controller software can be
+more complicated than the state-feedback control we synthesize, and the
+properties available cover more detail. 
+However, relying on state-space discretization \mbox{Pessoa} is likely to incur in scalability limitations. 
+Along this research line, \cite{Anta2010,liu16} studies the synthesis of digital controllers for continuous dynamics, 
+and \cite{zamani2014} extends the approach to the recent setup of Network Control Systems.
+
+\textbf{Discretization Effects -}
+The classical approach to control synthesis has often disregarded digitalization effects, 
+whereas more recently modern techniques have focused on
+different aspects of discretization, including delayed
+response~\cite{Duggirala2015} and finite word length (FWL) semantics, 
+with the goal either to verify (e.g.,~\cite{daes20161}) or to optimize
+(e.g.,~\cite{oudjida2014design}) given implementations.
+
+There are two different problems that arise from FWL semantics.  The first
+is the error in the dynamics caused by the inability to represent the exact
+state of the physical system, while the second relates to rounding and saturation errors
+during computation.  In~\cite{fialho1994stability}, a stability measure
+based on the error of the digital dynamics ensures that the deviation
+introduced by FWL does not make the digital system unstable.  A~more recent
+approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$-calculus to
+directly model the digital controller so that the selected parameters are
+stable by design.  The analyses in~\cite{DBLP:conf/hybrid/RouxJG15,
+DBLP:conf/hybrid/WangGRJF16} rely on an invariant computation on the
+discrete system dynamics using Semi-Definite Programming (SDP).  While the
+former uses bounded-input and bounded-output (BIBO) properties to determine
+stability, the latter uses Lyapunov-based quadratic invariants.  In both
+cases, the SDP solver uses floating-point arithmetic and soundness is
+checked by bounding the error.  An alternative is~\cite{park2016scalable},
+where the verification of given control code is performed against a known
+model by extracting an LTI model of the code by symbolic execution:  
+to account for rounding errors, an upper bound is introduced in the
+verification phase.  The work in \cite{picasso2003stabilization}
+introduces invariant sets as a mechanism
+to bound the quantization error effect on stabilization as an invariant set
+that always converges toward the controllable set.  Similarly,
+\cite{liberzon2003hybrid} evaluates the quantization error dynamics
+and bounds its trajectory to a known region over a finite time period. 
+This technique works for both linear and non-linear systems.
+
+%\addtodo{[Move material from \ref{sec:rw} here]}
+
+%\begin{ack}                               % Place acknowledgements
+%Partially supported by the Roman Senate.  % here.
+%\end{ack}
 

### 2017-05-24 automatica/automatica.tex
added keywords
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
removed appendix
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{keyword}                           % Five to ten keywords,  
-Cicero; Catiline; orations.               % chosen from the IFAC 
+Digital Control; A/D converters; Control System Synthesis; Transient Analysis; Safety Analysis; Quantization Errors; Sampling.               % chosen from the IFAC 
 \end{keyword}                             % keyword list or with the 
@@
                                           % keyword wizard
+
+%\keywords{
+%State-space dynamical models of physical systems; 
+%digital controllers; 
+%analogue-to-digital converters; 
+%time sampling; 
+%quantization; 
+%fixed-point arithmetic; 
+%CEGIS; 
+%safety requirements. 
+%}
 
@@
 
-\appendix
-\section{A summary of Latin grammar}    % Each appendix must have a short title.
-\section{Some Latin vocabulary}         % Sections and subsections are supported  
+%\appendix
+%\section{A summary of Latin grammar}    % Each appendix must have a short title.
+%\section{Some Latin vocabulary}         % Sections and subsections are supported  
                                         % in the appendices.

### 2017-05-24 automatica/automatica.tex
added experimental evaluation section
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
added preliminaries section
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \usepackage{color}
+\usepackage{amssymb}
+\usepackage{amsmath}
+\setcounter{tocdepth}{3}
+\usepackage{graphicx}
+\usepackage{tikz}
+\usepackage{pgfplots}
+\usepackage{framed}
+\usepackage{listings}
+\usepackage{algorithm,algpseudocode}
+\usepackage{epstopdf}
+\usepackage{cite}
+\usepackage{pifont}
+\usepackage{todonotes}
+\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
+\usetikzlibrary{patterns}
+\usepackage{url}
 
@@
 
+%-------------------------------
+\section{Preliminaries}
+\label{sec:preliminaries}
+%-------------------------------
+
+%-------------------------------
+\subsection{State-space representation of physical systems} 
+\label{ssec:ssrepresentation}
+%-------------------------------
+
+We consider models of physical plants expressed as ordinary differential
+equations (ODEs), which we assume to be controllable and under full state
+information (i.e., we have access to all the model variables):
+%
+\begin{align}
+\label{eq:ode}
+\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, \\ \nonumber A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}, 
+\end{align}
+%
+where $t \in \mathbb R_0^+$, where $A$ and $B$ are matrices that fully
+specify the continuous plant, and with initial states set as $x(0)$.  While
+ideally we intend to work on the continuous-time plant, in this work
+Eq.~\eqref{eq:ode} is soundly discretized in time~\cite{fadali} into
+%
+\begin{align}
+\label{eq:plant}
+x_{k+1} = A_d x_k+ B_d u_k
+\end{align} 
+%
+where $k \in \mathbb N$ and $x_{0}=x(0)$ is the initial state. 
+$A_d$ and $B_d$ denote the matrices that describe the discretized plant dynamics, whereas
+$A$ and $B$ denote the continuous plant dynamics.  
+We synthesize for requirements over this discrete-time domain. 
+Later, we will address the issue of variable quantization, 
+as introduced by the ADC/DAC conversion blocks 
+(\textcolor{red}{we should include a figure that describes the control system model that we tackle}).
+
+%-------------------------------
+\subsection{Controller synthesis via state feedback}
+\label{ssec:statefeedbackcontrol}
+%-------------------------------
+
+Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t)$ and  $u_k$, respectively. 
+Feedback architectures can be employed to manipulate the properties and behaviors of the continuous process (the plant).   
+We are interested in the synthesis of digital feedback control algorithms, 
+as implemented on Field-Programmable Gate Arrays or Digital Signal Processors. 
+The most basic feedback architecture is the state feedback one, 
+where the control action $u_k$ (notice we work with the discretized signal) is computed by: 
+%
+\begin{equation}
+\label{eq:controlaction}
+u_k = r_{k} - K x_k. 
+\end{equation}
+%
+Here, $K \in \mathbb{R}^{m \times n}$ is a state-feedback gain matrix, 
+and $r_{k}$ is a reference signal (again digital).   
+%
+The closed-loop model then takes the form 
+\begin{align}
+\label{eq:closedloopss}
+x_{k+1} = ( A_d - B_d K ) x_k + B_d r_k.
+\end{align}
+%
+The gain matrix $K$ can be set so that the closed-loop discrete dynamics are
+shaped as desired, for instance according to a specific stability goal or
+around a specific dynamical behavior \cite{astrom1997computer}.  As argued
+later in this work, we will target more complex objectives, such as
+quantitative safety requirements, which are not typical in the digital
+control literature.  Further, we will embrace the digital nature of the
+controller, which manipulates quantized signals as discrete quantities represented with finite precision.
+
+%-------------------------------
+\subsection{Stability of closed-loop systems}
+\label{ssec:stability}
+%-------------------------------
+
+In this work we employ asymptotic stability in the CEGIS loop,  
+as an objective for guessing controllers that are later proven sound over safety requirements.  
+Asymptotic stability is a property that amounts to convergence of the model executions to an equilibrium point, 
+starting from any states in a neighborhood of the point (see Figure~\ref{fig:ct} for the portrait of a stable execution, converging to the origin).  
+In the case of linear systems as in~\eqref{eq:closedloopss}, 
+considered with a zero reference signal, 
+the equilibrium point of interest is the origin.
+
+A discrete-time LTI system as \eqref{eq:closedloopss} is asymptotically
+stable if all the roots of its characteristic polynomial (i.e., the
+eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
+circle of the complex plane, i.e., their absolute values are strictly less than
+one~\cite{astrom1997computer} (this simple sufficient condition can be generalised, 
+however this is not necessary in our work).  
+In this paper, we express this stability specification $\phi_\mathit{stability}$ in terms of a check known as
+\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic formula to
+select the entries of matrix $K$ so that the closed-loop dynamics are shaped
+as desired.
+
+%-------------------------------
+\subsection{Safety specifications for dynamical systems}
+\label{ssec:safety}
+%-------------------------------
+
+We are not limited to the synthesis of digital stabilizing controllers -- a
+well known task in the literature on digital control systems -- but target
+safety requirements with an overall approach that is sound and automated. 
+More specifically, we require that the closed-loop system
+\eqref{eq:closedloopss} meets given safety specifications.  A safety
+specification gives raise to a requirement on the states of the model, such
+that the feedback controller (namely the choice of the gains matrix~$K$)
+must ensure that the state never violates the requirement.  Note that a
+stable, closed-loop system is not necessarily a safe system: indeed, the
+state values may leave the safe part of the state space while they converge
+to the equilibrium, which is typical in the case of oscillatory dynamics. 
+In~this work, the safety property is expressed as:
+%
+\begin{equation}
+\label{eq:safetyliteral}
+\phi_\mathit{safety}\iff \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
+\end{equation}
+where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
+for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
+instant, respectively.  This means that the states will always be within an $n$-dimensional hyper-box.
+
+Furthermore, it is practically relevant to consider the 
+constraints $\phi_\mathit{input}$ on the input
+signal $u_{k}$ and $\phi_\mathit{init}$ on the initial states $x_0$,
+which we assume have given bounds:
+$\phi_\mathit{input} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
+$\phi_\mathit{init} = \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$
+For the former, this means that the control input might saturates in view of
+physical constraints.
+
+%-------------------------------
+\subsection{Performance specifications for dynamical systems}
+\label{ssec:performance}
+%-------------------------------
+
+\textcolor{red}{we should describe here about the performance specifications for dynamical systems.}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Numerical representation and soundness} 
+\label{sec:numeric_rep}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+\textcolor{red}{this section needs to be updated to describe about floating-point arithmetic.}
+
+The models we consider have two sources of error that are due to numerical  
+representation.  The first is the numerical error introduced by the
+fixed-point numbers employed to model the plant, i.e., to represent the
+plant dynamics $A_d$, $B_d$ and $x_k$.  The second is the quantization error
+introduced by the digital controller, which performs operations on
+fixed-point numbers.  In this section we outline the notation for the
+fixed-point representation of numbers, and briefly describe the errors
+introduced.  A~formal discussion is in
+%Appendix~\ref{appendix:numerical_errors}.
+
+Let $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$
+represented in a fixed point domain, with $I$ bits representing the integer
+part and $F$ bits representing the decimal part.  The smallest number that
+can be represented in this domain is $c_m=2^{-F}$.  Any mathematical
+operations performed at the precision $\mathcal{F}_{\langle I,F \rangle}(x)$
+will introduce errors, for which an upper bound can be
+given~\cite{DBLP:conf/arith/BrainTRW15}.
+
+We will use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real
+number $x$ represented at the fixed-point precision of the controller, and
+$\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$
+represented at the fixed-point precision of the plant model ($I_c$ and $F_c$ are determined by the controller.
+We pick $I_p$ and $F_p$ for our synthesis such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$).
+Thus any mathematical operations in our modelled
+digital controller will be in the range of $\mathcal{F}_{\langle I_c,F_c
+\rangle}$, and all other calculations in our model will be carried out in the range of
+$\mathcal{F}_{\langle I_p,F_p \rangle}$.  
+The physical plant operates in the
+reals, which means our verification phase must also account for the numerical error and quantization errors caused by representing the physical plant at the finite precision $\mathcal{F}_{\langle I_p,F_p \rangle}$.
+
+\subsubsection{Effect on safety specification and stability}
+
+Let us first consider the effect of the quantization errors on safety. 
+Within the controller, state values are manipulated at low precision,
+alongside the vector multiplication $Kx$.
+The inputs are computed using the following equation: 
+%
+\begin{align*}
+u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})). 
+\end{align*}
+
+This induces two types of the errors detailed above: first, the truncation
+error due to representing $x_k$ as $\mathcal{F}{\langle I_c,F_c
+\rangle}(x_{k})$; and second, the rounding error introduced by the
+multiplication operation.  We represent these errors as non-deterministic
+additive noise.
+
+An additional error is due to the representation of the plant dynamics, namely 
+%
+\begin{align*}
+x_{k+1} &=\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
+\end{align*}
+We address this error by use of interval
+arithmetic~\cite{moore1966interval} in the verification phase.
+
+Previous studies~\cite{gangli1} show that the FWL affects the poles and
+zeros positions, degrading the closed-loop dynamics, causing steady-state
+errors (see Appendix~\ref{sec:appendix:LTIbackground} for details) and
+eventually de-stabilizing the system~\cite{Bessa16}.  However, since in this
+paper we require stability only as a precursor to safety, it is sufficient
+to check that the (perturbed, noisy) model converges to a neighborhood of
+the equilibrium within the safe set (see Appendix~\ref{sec:stab_FWL}).
+
+In the following, we shall disregard these steady-state errors (caused by
+FWL effects) when stability is ensured by synthesis, and then verify its
+safety accounting for the finite-precision errors.
+
+%-------------------------------
+\section{Experimental Evaluation}
+\label{exp:evaluation}
+%-------------------------------
+
+%-------------------------------
+\subsection{Description of the benchmarks}
+\label{exp:benchmarks}
+%-------------------------------
+
+%-------------------------------
+\subsection{Objectives}
+\label{exp:objectives}
+%-------------------------------
+
+%-------------------------------
+\subsection{Results}
+\label{exp:results}
+%-------------------------------
+
+%-------------------------------
+\subsection{Threats to validity}
+\label{exp:threats-to-validity}
+%-------------------------------
+
+%-------------------------------
+\section{Conclusions}
+\label{sec:conclusions}
+%-------------------------------
+
+\textcolor{red}{We need to write a new conclusions about this work.}
+
 %\addtodo{[Move material from \ref{sec:rw} here]}

### 2017-05-24 automatica/automatica.tex
added relevant appendix
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-%\appendix
+\appendix
+
+%-------------------------------
+\section{Stability of Closed-loop Models}
+\label{sec:appendix-stability}
+%-------------------------------
+
+%-------------------------------
+\subsection{Stability of closed-loop models with fixed-point controller error}
+\label{sec:stab_FWL}
+%-------------------------------
+
+The proof of Jury's criterion~\cite{fadali} relies on the fact that the relationship between states and
+next states is defined by $x_{k+1} = (A_d - B_dK) x_k$, all computed
+at infinite precision.  When we employ a FWL digital controller, the
+operation becomes:
+%
+\begin{align*}
+x_{k+1} &= A_d \cdot x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
+x_{k+1} &= (A_d  - B_dK) \cdot x_k + B_dK\delta, 
+\end{align*}
+%
+where $\delta$ is the maximum error that can be introduced by the FWL
+controller in one step, i.e., by reading the states values once and
+multiplying by $K$ once.  We derive the closed form expression for $x_n$ as
+follows:
+%
+\begin{align*}
+x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
+x_{2} 
+ &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
+x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... \\  \nonumber & + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
+  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{i=n-1}(A_d - B_dK)^iB_dk\delta. 
+\end{align*}
+
+The definition of asymptotic stability is that the system converges to a
+reference signal, in this case we use no reference signal so an
+asymptotically stable system will converge to the origin.  We know that the
+original system with an infinite-precision controller is stable, because we
+have synthesized it to meet Jury's criterion.  Hence, $(A_d - B_dK)^n x_0$ 
+must converge to zero.
+
+The power series of matrices
+converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less
+than~1 as follows:
+%
+%\begin{align*}
+$\sum_{i=0}^{\infty}T^i  = (I - T)^{-1}$, 
+%\end{align*}
+%
+where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge to the value 
+%
+\begin{align*}
+0 + (I - A_d + B_dK)^{-1}B_dk\delta \,. 
+\end{align*}
+%
+As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the
+safe space, then the synthesized fixed-point controller results in a safe
+closed-loop model.  The convergence to a finite value, however, will not
+make it asymptomatically stable.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{Errors in LTI models} \label{sec:appendix:LTIbackground}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+\subsection{Errors due to numerical representation} \label{appendix:numerical_errors}
+
+We have  used $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number
+$x$ represented in a fixed point domain, with $I$ bits representing the
+integer part and $F$ bits representing the decimal part.  The smallest
+number that can be represented in this domain is $c_m=2^{-F}$.  The
+following approximation errors will arise in mathematical operations and
+representation:
+%
+\begin{enumerate}
+
+\item {\bf Truncation:} Let $x$ be a real number, and $\mathcal{F}_{\langle
+I,F \rangle}(x)$ be the same number represented in a fixed-point domain as
+above.  Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the
+error $ \delta_T=x\ \%_{c_m}\ \tilde x$, and $\%_{c_m}$ is the modulus
+operation performed on the last bit. 
+Thus, $\delta_T$ is the truncation error and it will propagate across
+operations.
+%
+\item {\bf Rounding:} The following errors appear in basic operations.  Let
+$c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be
+the truncation errors caused by representing $c_1$ and $c_2$ in the
+fixed-point domain as above.
+%
+\begin{enumerate}
+%
+\item Addition/Subtraction: these operations only propagate errors coming
+from truncation of the operands, namely $\mathcal{F}_{\langle I,F
+\rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3$
+with $|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
+%
+\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) \cdot
+\mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3|
+\leq |\delta_{T1}\cdot\mathcal{F}_{\langle I,F \rangle}(c_2)|\allowbreak +
+|\delta_{T2}\cdot\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where
+$c_m=2^{-F}$ as above.
+%
+\item Division: the operations performed by our controllers in the FWL
+domain do not include division.  However, we do use division in computations
+at the precision of the plant.  Here the error depends on whether the
+divisor is greater or smaller than the dividend:  $\mathcal{F}_{\langle I,F
+\rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_{T3}$
+where $\delta_{T3}$ is $(\delta_{T2}\cdot c_1 - \delta_{T1}\cdot
+c_2)/(\delta_{T2}^2 - \delta_{T2} c_2)$,
+\end{enumerate}
+
+\item {\bf Overflow:}
+The maximum size of a real number $x$ that can be represented in a fixed
+point domain as $\mathcal{F}_{\langle I,F \rangle}(x)$ is $\pm
+(2^{I-1}+1-2^{-F})$.  Numbers outside this range cannot be represented by
+the domain.  We check that overflow does not occur.
+
+\end{enumerate}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Modeling quantization as noise} \label{appendix:quantization-noise}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+During any given ADC conversion, the continuous signal will be sampled in
+the real domain and transformed by $\mathcal{F}\langle I_{c},F_{c} \rangle
+(x)$ (assuming the ADC discretization is the same as the digital
+implementation).  This sampling uses a threshold which is defined by the
+less significant bit ($q_{c}=c_{m_c}=2^{-F_c}$) 
+of the ADC and some non-linearities of the circuitry.  The overall conversion is
+%
+$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k :
+y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right] \,.$$
+%
+If we denote the error in the conversion by $\nu_k=y_k-y(t)$ where $t = nk$,
+and $n$ is the sampling time and $k$ the number of steps, then we may define
+some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
+
+We will assume, for the purposes of this analysis, that the domain of the
+ADC is that of the digital controller (i.e, the quantizer includes any
+digital gain added in the code).  The process of quantization in the DAC is
+similar except that it is calculating $\mathcal{F}\langle I_{dac},F_{dac}
+\rangle (\mathcal{F}\langle I_{c},F_{c} \rangle (x)) $.  If these domains
+are the same ($I_{c}=I_{dac},\allowbreak F_{c}=F_{dac}$), or if the DAC
+resolution in higher than the ADCs, then the DAC quantization error is equal
+to zero.  From the above equations we can now define the ADC and DAC
+quantization noises ${\nu_1}_k \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}]$ and
+${\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}]$, where $q_1=q_{c}$ and 
+$q_2=q_\mathit{dac}$.  This is illustrated in
+Fig.~\ref{ssec:statefeedbackcontrol} where $Q_1$ is the quantizer of the ADC
+and $Q_2$ the quantizer for the DAC.  These bounds hold irrespective of
+whether the noise is correlated, hence we may use them to over-approximate
+the noise effect on the state space progression over time.  The
+resulting dynamics are
+%
+\begin{align*}
+%\label{eq:pre_quantization}
+{x}_{k+1} = {A}_d{x}_k+{B}_d({u}_k+{{\nu}_2}_k), \quad u_k = -K{x}_{k}+{{\nu}_1}_k, 
+\end{align*}
+%
+which result in the following closed-loop dynamics:
+%
+\begin{align*}
+%\label{eq:quantization}
+{x}_{k+1} &= ({A}_d-{B}_d{K}_d) {x}_k+{B}_d{{\nu}_2}_k +{{\nu}_1}_k \,. 
+\end{align*}
+
 %\section{A summary of Latin grammar}    % Each appendix must have a short title.

### 2017-05-25 automatica/automatica.tex
automatica structure

@@
 
+{\color{blue}[IB:] In my opinion, the subsections \ref{ssec:statefeedbackcontrol}, \ref{ssec:ssrepresentation}, are \ref{ssec:stability} are useless for the Automatica audience.
+In addition, i guess that all the subsections~\ref{ssec:ssrepresentation}-\ref{ssec:performance} should be erased and a new section about formal specification of transient and stability specifications can be created.}
+
+%-------------------------------
+\subsection{Notation} 
+\label{ssec:notation}
+%-------------------------------
+
+%-------------------------------
+\subsection{Counterexample Guided Inductive Synthesis} 
+\label{ssec:cegis}
+%-------------------------------
+
+%-------------------------------
+\subsubsection{CEGIS of digital controllers} 
+\label{sssec:cegisdig}
+%-------------------------------
+
+%-------------------------------
+\subsubsection{Naive approach} 
+\label{sssec:naive}
+%-------------------------------
+
+%-------------------------------
+\subsubsection{Abstraction-based CEGIS} 
+\label{sssec:abstraction}
+%-------------------------------
+
 %-------------------------------
@@
 safety accounting for the finite-precision errors.
+
+%-------------------------------
+\section{Formal specification of control systems properties} 
+\label{sec:specification}
+%-------------------------------
+
+%-------------------------------
+\subsection{Formal specification of stability} 
+\label{ssec:stabspecification}
+%-------------------------------
+
+%-------------------------------
+\subsection{Formal specification of safety} 
+\label{ssec:safespecification}
+%-------------------------------
+
+%-------------------------------
+\subsection{Formal specification of transient response} 
+\label{ssec:transientspecification}
+%-------------------------------
+
+%-------------------------------
+\section{CEGIS of digital control system with transient specifications}
+\label{sec:method}
+%-------------------------------
+
+%-------------------------------
+\subsection{Synthesis in frequency domain}
+\label{ssec:frequencycegis}
+%-------------------------------
+
+%-------------------------------
+\subsection{Synthesis of state feedback controllers}
+\label{ssec:sscegis}
+%-------------------------------
+
+%-------------------------------
+\subsection{Synthesis of state observers}
+\label{ssec:sobsvcegis}
+%-------------------------------
 

### 2017-05-25 automatica/automatica.tex
update automatica

@@
 \usepackage{url}
-
+%\newcommand{\tool}{{\sf DSSynth}\xspace}
 \begin{document}
-
+\newcommand\tool{{\sf DSSynth}}
 \begin{frontmatter}
@@
 
+In order to synthesize closed-loop digital control systems, we use a program
+synthesis engine.  Our program synthesizer implements Counter-Example Guided
+Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}.  We
+start by presenting its general architecture followed by describing the
+parts specific to closed-loop control systems.  A high-level view of the
+synthesis process is given in Figure~\ref{DSSynth_process}.  Steps $1$ to
+$3$ are performed by the user and Steps~A to D are automatically performed
+by our tool for Digital Systems Synthesis, named \tool.
+
+CEGIS-based control synthesis requires a formal verifier to check whether a
+candidate controller meets the requirements when combined with the plant. 
+We use the Digital-System Verifier (DSVerifier)~\cite{IsmailBCFF15} in the
+verification module for \tool.  It checks the stability of closed-loop control systems and
+considers finite-word length (FWL) effects in the digital controller and
+uncertainty parameters in the plant model (plant intervals)~\cite{Bessa16}.
+
+%
+%, which accepts the
+%digital controller transfer functions together with the plant model.  For
+%any digital controller, implementation details should be provided ({\it
+%e.g.}, number of bits, realization, and sample time).
+
+\begin{figure*}[t]
+\centering
+\includegraphics[width=0.9\textwidth]{figures/synthesis-flow.pdf}
+\vspace{0.1cm}
+\caption{Overview of the synthesis process\label{DSSynth_process}}
+\end{figure*}
+
+%In Step $1$, the user provides inputs $G(z)$ and $\Delta{G}(z)$
+%%$\%$ ({\it i.e.}, $\Delta{G}(z)$ as a percentage of $G(z)$)
+%, which contain the plant model and the
+%interval, respectively.  In Step $2$, a digital controller must be designed
+%with any preferred method, where $C(z)$ is obtained.  The controller
+%numerical representation and realization form are chosen in Steps $3$ and
+%$4$, respectively.  In Step $5$, the user finally configures the
+%verification parameters ({\it e.g.}, verification time, properties, and BMC
+%tool).  After that, DSVerifier verification engine performs an (automatic)
+%verification of the desired property $\phi$ ({\it i.e.}, stability).  The
+%user steps described in Steps $1$--$5$ result in an ANSI-C code that should
+%be used as an input for DSVerifier.
+
+Given a plant model in ANSI-C syntax as input (Steps 1--3), \tool constructs
+a non-deterministic model to represent the plant family, i.e., it addresses
+plant variations as interval sets (Step~A), and formulates a function
+(Step~B) using implementation details provided in Steps~$2$ and $3$ to
+calculate the controller parameters to be synthesized (Step~C).  Note that
+\tool synthesizes the controller for the desired numerical representation
+and realization form.  Finally, \tool builds an intermediate ANSI-C code for
+the digital system implementation, which is used as input for the CEGIS
+engine (Step~D).
+
+This intermediate ANSI-C code model contains a specification $\phi$ for the
+property of interest (i.e., robust stability) and is passed to the
+Counterexample-Guided Inductive Synthesis (CEGIS) module of
+CBMC~\cite{ClarkeKL04}, where the controller is marked as the input variable
+to synthesize.  CEGIS employs an iterative, counterexample-guided refinement
+process, which is explained in detail in Section~\ref{synthesizer-general}. 
+CEGIS reports a successful synthesis result if it generates a controller
+that is safe with respect to~$\phi$.  In particular, the ANSI-C code model
+guarantees that a synthesized solution is complete and sound with respect to
+the stability property~$\phi$, since it does not depend on system inputs and
+outputs.  In the case of stability, the specification~$\phi$ consists of a
+number of assumptions on the polynomial coefficients, following Jury's
+Criteria, as well as the restrictions on the representation of these
+coefficients as discussed in detail in Section~\ref{synthesis-elements}.
+
 %-------------------------------
@@
 
+\begin{figure}[htb]
+{\scriptsize
+\centering
+%\resizebox{.8\textwidth}{!}
+{
+ \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
+},
+          row sep=.6cm, column sep=.9cm] {
+   \coordinate (aux1);
+   \& \coordinate (aux2);
+   \&;\\
+   \coordinate (aux3);
+   \& \coordinate (aux4);
+   \&;\\
+   \coordinate (aux5);
+   \& \coordinate (aux6);
+   \&;\\
+   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc 1.Synthesize}};
+   \&
+   complexnode/.pic={ 
+     \node[rectangle,draw,dotted,
+	minimum width=6cm,
+	minimum height=1cm,
+        pattern=north west lines, pattern color=gray!20,
+	label={\sc ~~~~~~~~~~~~Verify},] (verif) {};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc 2.Safety}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=0cm]verif.center) {{\sc 3.Precision}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=2cm]verif.center) {{\sc 4.Complete}};
+     %\node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc 5.Sampling}};
+   } 
+   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
+   \& \\
+   \node[minimum height=0cm] (gp) {\sf Program Search};
+   \&
+   complexnode/.pic={ 
+     \coordinate (aux);
+   \node (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based \\ \sf Verifier};
+   \node (fp)  at ([xshift=0cm]aux.center) {\sf Fixed-point \\ \sf Arithmetic\\ \sf Verifier};
+   \node (sv)  at ([xshift=2cm]aux.center) {\sf Completeness\\ \sf Verifier};
+   %\node (cv)  at ([xshift=3.1cm]aux.center) {\sf Sampling\\Verifier};
+   }   
+    \\
+  };
+
+   \path
+    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$K$} ([yshift=2em]verif1.west)
+    ([yshift=-2em]verif1.west) edge node {C-ex} ([yshift=-2em]synth.east)
+    ([xshift=-5em]fp.north) edge node[align=center]  {T/F} ([xshift=-5em]verif2.south)
+    ([xshift=-5em]sv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif3.south)
+    %([xshift=-5em]cv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif4.south)
+    ([xshift=5em]verif1.south) edge node[align=center] {$K$} ([xshift=5em]bmc.north)
+    ([xshift=5em]verif2.south) edge node[align=center] {$K$} ([xshift=5em]fp.north)
+    ([xshift=5em]verif3.south) edge node[align=center] {$K$} ([xshift=5em]sv.north)
+    %([xshift=5em]verif4.south) edge node[align=center] {$K$} ([xshift=5em]cv.north)
+    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
+    (verif) edge node {PASS} (done)
+    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
+    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$K$} ([xshift=-5em]synth.south)
+    (aux3) edge (synth.north);
+   \path[-]
+   (verif2.north) edge node[align=center] {} ([xshift=0cm]aux6)
+   ([xshift=0cm]aux6) edge node[align=center] {Increase Precision} (aux5)
+   (verif3.north) edge node[align=center] {} ([xshift=6.7cm]aux4)
+   ([xshift=6.7cm]aux4) edge node[align=center] {Increase Unfolding Bound} (aux3);
+   %(verif4.north) edge node[align=center] {} ([xshift=10.5cm]aux2)
+   %([xshift=10.5cm]aux2) edge node[align=center] {Increase Sampling Rate} (aux1);
+
+ \end{tikzpicture}
+}}
+\caption{CEGIS with multi-staged verification}
+\label{fig:CEGIS-precision-increment}
+\end{figure}
+
+%\subsubsection{Controller synthesis}
+
+An overview of the algorithm for controller synthesis is given in
+Fig.~\ref{fig:CEGIS-precision-increment}.  One important observation is that
+we verify and synthesize a controller over $k$ time steps.  We~then compute
+a completeness threshold $\overline{k}$~\cite{DBLP:conf/vmcai/KroeningS03}
+for this controller, and verify correctness for $\overline{k}$ time steps. 
+Essentially, $\overline{k}$ is the number of iterations required to
+sufficiently unwind the closed-loop state-space system, 
+which ensures that the boundaries are not violated for any other $k{>}\overline{k}$.
+
+%\begin{theorem} There exists a finite $\overline{k}$ such that it is
+%sufficient to unwind the closed-loop state-space system up to $\overline{k}$
+%in order to ensure that $\phi_\mathit{safety}$ holds. 
+%\end{theorem}
+%
+%\begin{proof}
+%%
+%A stable control system is known to have converging dynamics.  Assume the
+%closed-loop matrix eigenvalues are not repeated (which is sensible to do,
+%since we select them).  The distance of the trajectory from the reference
+%point (origin) decreases over time within subspaces related to real-valued
+%eigenvalues; however, this is not the case in general when dealing with
+%complex eigenvalues.  Consider the closed-loop matrix that updates the
+%states in every discrete time step, and select the eigenvalue $\vartheta$
+%with the smallest (non-trivial) imaginary value.  Between every pair of
+%consecutive time steps $k\,T_s$ and $(k+1)\,T_s$, the dynamics projected on
+%the corresponding eigenspace rotate $\vartheta T_s$ radians.  Thus, taking
+%$\overline{k}$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, after
+%$k{\geq}\overline{k}$ steps we have completed a full rotation, which results
+%in a point closer to the origin.  The synthesized $\overline{k}$ is the completeness threshold.
+%\qed 
+%%
+%\end{proof}
+%
+%\medskip
+
+Next, we describe the different phases in Fig.~\ref{fig:CEGIS-precision-increment}
+(blocks 1 to 4) in detail.
+
+%\todo{please eventually itemize next}
+\begin{enumerate}
+
+\item The inductive synthesis phase ({\sc synthesize}) uses BMC to
+compute a candidate solution $K$ that satisfies both the stability criteria
+(Sec.~\ref{ssec:stability}) and the safety specification
+(Sec.~\ref{ssec:safety}).  To synthesize a controller that satisfies the
+stability criteria, we require that a computed polynomial
+satisfies Jury's criterion~\cite{fadali}.  The details of this calculation can be found in
+the Appendix.
+
+Regarding the second requirement, we synthesize a safe controller by
+unfolding the transition system $k$ steps and by picking a controller $K$
+and a single initial state, such that the states at each step do not violate
+the safety criteria.  That is, we ask the bounded model checker if there
+exists a $K$ that is safe for at least one $x_0$ in our set of all possible
+initial states.  This is sound if the current $k$ is greater than the completeness
+threshold.  We~also assume some precision $\langle I_p,F_p\rangle$ for the
+plant and a sampling rate.  The checks that these assumptions hold are
+performed by subsequent {\sc verify} stages.
+
+%\begin{algorithm}[]
+%\scriptsize
+%\begin{algorithmic}[1]
+%\Function{$stabilityCheck()$}{}
+%  \State computecharPoly($A_d - B_dK$)
+%  \State assert(Jury's criteria hold)
+  %\State Return $K$
+%\EndFunction
+%\end{algorithmic}
+%\label{alg:stabilitycheck}
+%\end{algorithm}
+
+\begin{algorithm}[]
+%\scriptsize
+\begin{algorithmic}[1]
+\Function{$\mathit{safetyCheck}()$}{}
+\State assert($ \underline{u}  \leq u \leq \overline{u}$)
+ \State set $x_0$ to be a vertex state, e.g., $[\underline{x_0},\underline{x_0}]$	
+\For {($c=0;~c < 2^\mathit{Num\_States};~c\mbox{++}$)}
+  %\State assert($ \underline{x_0}  \leq x_0 \leq \overline{x_0}$)
+	\For{($i=0;~i< k;~i\mbox{++}$)}
+		%\State $u = (\langle I_p,F_p\rangle)((\langle I_c,F_c\rangle)K * (\langle I_c,F_c\rangle) x)$
+		\State $u = (plant\_typet)((controller\_typet)K * (controller\_typet) x)$
+		\State $x = A * x + B * u$
+		\State assert($\underline{x} \leq x \leq \overline{x}$ )
+  	\EndFor
+  	\State set $x_0$ to be a new vertex state
+  	\EndFor
+  %\State Return $K$
+\EndFunction
+\end{algorithmic}
+\caption{Safety check\label{alg:safetycheck}}
+\end{algorithm}
+
+\item The first {\sc verify} stage, {\sc safety}, checks that the candidate
+solution $K$, which we synthesized to be safe for at least one initial
+state, is safe for \emph{all} possible initial states, i.e., does not reach
+an unsafe state within $k$ steps where we assume $k$ to be under the
+completeness threshold.  After unfolding the transition system corresponding
+to the previously synthesized controller $k$ steps, we check that the safety
+specification holds for any initial state. This is shown in Alg.~~\ref{alg:safetycheck}.
+
+\item The second {\sc verify} stage, {\sc precision}, 
+ restores soundness with respect to the plant's precision
+by using interval arithmetic \cite{moore1966interval} to validate the 
+operations performed by the previous stage.
+
+\item The third {\sc verify} stage, {\sc complete}, checks that the current
+$k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
+completeness threshold $\overline{k}$ for the current candidate controller $K$ and
+check that $k{\geq}\overline{k}$.  This is done according to the argument
+given above and illustrated in Fig.~\ref{fig:ct}.
+
+\end{enumerate}
+
+\begin{figure*}[t]
+\centering
+\includegraphics[width=0.6\textwidth]{figures/ct.eps}
+\vspace{0.1cm}
+\caption{Completeness threshold for multi-staged verification. $T_s$ is the time step for the time discretization of the control matrices.}
+\label{fig:ct}
+\end{figure*}
+
+Checking that the safety specification holds for any initial state can be 
+computationally expensive if the bounds on the
+allowed initial states are large.
+
 %-------------------------------
@@
 
-%-------------------------------
-\subsection{State-space representation of physical systems} 
-\label{ssec:ssrepresentation}
-%-------------------------------
-
-We consider models of physical plants expressed as ordinary differential
-equations (ODEs), which we assume to be controllable and under full state
-information (i.e., we have access to all the model variables):
+  The na\"ive approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
+  %uses a multi-staged verification phase and performs solution generalization based on
+%the plant precision, the number of loop unrollings, 
+  %and the sampling rate. Essentially, it
+  synthesizes a controller for an individual initial state
+and input with a bounded time horizon and, subsequently, it generalizes it to all reachable states,
+inputs, and time horizons during the verification phase.
+Essentially, this approach relies on the symbolic
+simulation over a bounded time horizon of individual initial states and inputs that form
+part of an uncountable space and tries to generalize it for an
+infinite space over an infinite time horizon.
+
+  %% solution over all times by refining the number of witnesses.  
+  %% In order to perform the safety check, this approach uses abstract acceleration
+  %% \cite{cattaruzza2015unbounded} to compute the controller's set of states. 
+  %% \todo{clarify: what is the ``set of states'' of the controller? }
+%\end{itemize}
+
+%% The verification of a hybrid continuous/discrete system over an
+%% unbounded time, requires the non-deterministic simulation of an
+%% infinite set of states, which is undecidable.
+
+%% Our na\"ive approach
+%% creates an abstraction of the system by establishing bounds on the
+%% error between such a system and a discrete-time/continuous-space
+%% model.  This model is still however, quite complex, hard to verify,
+%% and many of the states involved are inconsequential to the safety
+%% specification.
+
+Conversely, in this section, 
+we  find a controller for a continuous initial set of states and set of inputs, 
+  over an abstraction of the continuous dynamics \cite{cattaruzza2015unbounded} that conforms to
+  witness proofs at specific times. %% It further generalizes the
+  Moreover, this approach uses abstraction refinement enabling us to 
+  always start with a very simple description regardless of the complexity of the overall
+dynamics, and only expand to more complex models when a solution
+cannot be found.
+
+  The CEGIS loop for this approach is illustrated in Fig.~\ref{fig:CEGARIS}.
+
+% Now that we have explained the verification process, we may proceed to describe the synthesis procedure, which is illustrated in figure \ref{fig:CEGARIS}.
+% Our model, rather than look at a bisimulation \todo{specific notion that has not been formally define - do not use} in discrete time, explores a much higher abstraction, 
+% evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specification.
+% We have also identified 
+% the quantization noise as a bounded non-deterministic input.
+
+\begin{enumerate}
+\item 
+  We start by doing some preprocessing:%%  that 
+  %% can be computationally intensive and we don't want it to be part of the CEGIS loop.
+% Let us recall the formulas used for single-input and single-output (SISO) systems 
+  % in sections \ref{sec:reachable} and \ref{sec:observable}.
+  \begin{enumerate}
+\item Compute the characteristic polynomial of the matrix $(A_d-B_dK)$ as 
+$P_a(z) = z^n+\sum_{i=1}^n{(a_i-k_i)z^{n-i}}$. 
+%\blue{[shouldn't there be a b term in the polynomial's coefficients here? No. the polynomial only evaluates the poles]}
+%%   A controllable system with quantization will have the following dynamics, where
+%% we use underscript ``n'' to denote a noise term,
+%% ``cf'' to denote Controllable Canonical Form,
+%% $\nu_1$, $\nu_2$ are quantization errors
+%% caused by the ADC and DAC conversions, respectively, 
+%% and $\nu_3$ is the round-off error.
+%% \todo{Why do we use $_t$ here?}
+%% %
+%% \begin{align}
+%% \label{eq:observer_LTI_cf}
+%% x_{k+1}=&\mat{A}_{t}x_k+\mat{B}_{t} r_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)
+%% \end{align}
+%% \begin{align*}
+%% \mat{A}_{t}=&\mat{T}\mat{A}_d\mat{T}^{-1}&
+%% \mat{B}_{t}=&\mat{T}\mat{B}_d&
+%% \mat{B}_{n}=&[1 \cdots 1]^T&
+%% \mat{T}=&\mat{W}_{cf}\mat{W}^{-1}&
+%% \end{align*}
+
+%% \begin{align*}
+%% \mat{A}_{t}=\mat{T}\mat{A}_d\mat{T}^{-1}=&\left[
+%% \begin{array}{ccccc}
+%% 0&1&0&\cdots&0\\
+%% 0&0&1&\cdots&0\\
+%% \vdots&\vdots&\vdots&\ddots&\vdots\\
+%% 0&0&0&\cdots&1\\
+%% k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
+%% \end{array}\right]
+%% \label{eq:cf_SISO_2}
+%% \end{align*}
+
+%% \begin{enumerate}
+%% \item Calculate $\mat{T}$ as $\mat{W}_{cf}\mat{W}^{-1}$. %using equations \eqref{eq:rncf}\eqref{eq:rcf}\eqref{eq:to_cf}
+%% \item Extract the characteristic polynomial of the above matrix:
+%% %
+%\begin{align*}
+%$P_a = z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}$
+%\end{align*}
+
+\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
+%
+$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q_1}{2}\ \ \frac{q_1}{2}\right] 
+\wedge \nu_2 \in \left[-\frac{q_2}{2}\ \ \frac{q_2}{2}\right]  \wedge \nu_3 \in \left[-q_3\ \ q_3\right]  \right \}\nonumber$$
+%
+where  $q_1$ is the error introduced by the truncation in the ADC, $q_2$ is
+the error introduced by the DAC and $q_3$ is the maximum truncation and
+rounding error in $u_k=-K \cdot \mathcal{F}_{\langle I_c,F_c \rangle}(x_k)$ as
+discussed in Section~\ref{sec:numeric_rep}.  More details on how to model
+quantization as noise are given in
+Appendix~\ref{appendix:quantization-noise}.
+
+\item Calculate a set of initial bounds on $K$, $\phi_\mathit{init}^{K}$,
+based on the input constraints %\blue{[how is this practically done?With the equation below]}.  
+%
+$$(\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-K x_k)
+\Rightarrow \phi_\mathit{init}^{K}$$
+Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
+
+\end{enumerate}
+\item In the {\sc synthesize} phase, we synthesize a candidate controller
+%We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability 
+% specification defined by Jury's 
+%criteria. %, and try to synthesise a controller that meets these specs.
+% For a stabilized closed-loop, which is necessary for our safety property, we need
+% these roots to remain within the unit circle, which we verify using Jury's criteria.
+% Notice that in our polynomials $c_0=1$ and we only use reals.
+% Once we have established convergence, we may examine the 
+% safety specification $\phi_\mathit{safety}$.
+  $K \in \mathbb{R}\langle I_c,F_c\rangle^n$ that satisfies
+  $\phi_\mathit{stability} \wedge \phi_\mathit{safety} \wedge \phi_\mathit{init}^{K}$ by invoking a SAT solver.
+%%   We obtain it by solving the SAT formula 
+%% $$\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_\mathit{safety}$$ 
+%% that satisfies the input constraint and Jury's criteria for 
+%% $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \tilde{\mat{K}}=\mat{K}\mat{T}$,
+%% where $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ is a program describing Jury's method.
+If there is no candidate solution we return UNSAT and exit the loop.
+\item Once we have a candidate solution, we perform a safety verification % If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
+  %
+  of the 
+  %consisting of evaluating the
+  progression of the system from $\phi_\mathit{init}$ over time,
+$x_{k} \models \phi_\mathit{safety}$. %\blue{why $k+1$ here?}. %% For this purpose we require 
+%% an initial set $\phi_\mathit{init}= x_0 \in [\underline{x_0} \ \overline{x_0}]$ 
+%% from which the system progresses.
+% Obviously, this set $x_0$ 
+% must satisfy the specification; otherwise, the system will be unsafe to begin with.
+% We accept a specification in the form $\mat{E}\mat{T}x_0<\mat{f}$. 
+% The presence of $\mat{T}$ is because this will typically be given in the original 
+% state-space.
+%% Next, we use abstract acceleration to get a second abstraction that 
+  %% encompasses the accelerated continuous reach-tube over an unbounded time.
+  In order to compute the progression of point $x_0$ at iteration $k$,
+  we accelerate the dynamics of the closed-loop system and obtain:
+  %we take the
+  %the closed-loop model:
+  %$x_{k+1}=\mat{A}_{t}x_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)$
+  %and accelerate it to:
 %
 \begin{align}
-\label{eq:ode}
-\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, \\ \nonumber A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}, 
+%\label{eq:acc_observer_LTI_cf}
+\hspace{-0.1in} x=&(A_d-B_dK)^kx_0
+%+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i
++\sum_{i=0}^{k-1} (A_d-B_dK)^i B_{n}(\nu_1+\nu_2+\nu_3) : B_n= [1 \cdots 1]^T
 \end{align}
 %
-where $t \in \mathbb R_0^+$, where $A$ and $B$ are matrices that fully
-specify the continuous plant, and with initial states set as $x(0)$.  While
-ideally we intend to work on the continuous-time plant, in this work
-Eq.~\eqref{eq:ode} is soundly discretized in time~\cite{fadali} into
+As this still requires us to verify the system for every $k$ up to infinity,
+we use abstract acceleration again to obtain the reach-tube, i.e., the set
+of all reachable states at all times given an initial set
+$\phi_\mathit{init}$:
 %
 \begin{align}
-\label{eq:plant}
-x_{k+1} = A_d x_k+ B_d u_k
+\label{eq:aa_observer_LTI_cf}
+\hat{X}^\#
+=\mathcal{A} X_0 + \mathcal{B}_{n} N, \quad
+X_0 =\left \{x : x \models \phi_\mathit{init} \right\}, 
 \end{align}
 %
-where $k \in \mathbb N$ and $x_{0}=x(0)$ is the initial state. 
-$A_d$ and $B_d$ denote the matrices that describe the discretized plant dynamics, whereas
-$A$ and $B$ denote the continuous plant dynamics.  
-We synthesize for requirements over this discrete-time domain. 
-Later, we will address the issue of variable quantization, 
-as introduced by the ADC/DAC conversion blocks 
-(\textcolor{red}{we should include a figure that describes the control system model that we tackle}).
-
-%-------------------------------
-\subsection{Controller synthesis via state feedback}
-\label{ssec:statefeedbackcontrol}
-%-------------------------------
-
-Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t)$ and  $u_k$, respectively. 
-Feedback architectures can be employed to manipulate the properties and behaviors of the continuous process (the plant).   
-We are interested in the synthesis of digital feedback control algorithms, 
-as implemented on Field-Programmable Gate Arrays or Digital Signal Processors. 
-The most basic feedback architecture is the state feedback one, 
-where the control action $u_k$ (notice we work with the discretized signal) is computed by: 
-%
-\begin{equation}
-\label{eq:controlaction}
-u_k = r_{k} - K x_k. 
-\end{equation}
-%
-Here, $K \in \mathbb{R}^{m \times n}$ is a state-feedback gain matrix, 
-and $r_{k}$ is a reference signal (again digital).   
-%
-The closed-loop model then takes the form 
-\begin{align}
-\label{eq:closedloopss}
-x_{k+1} = ( A_d - B_d K ) x_k + B_d r_k.
-\end{align}
-%
-The gain matrix $K$ can be set so that the closed-loop discrete dynamics are
-shaped as desired, for instance according to a specific stability goal or
-around a specific dynamical behavior \cite{astrom1997computer}.  As argued
-later in this work, we will target more complex objectives, such as
-quantitative safety requirements, which are not typical in the digital
-control literature.  Further, we will embrace the digital nature of the
-controller, which manipulates quantized signals as discrete quantities represented with finite precision.
-
-%-------------------------------
-\subsection{Stability of closed-loop systems}
-\label{ssec:stability}
-%-------------------------------
-
-In this work we employ asymptotic stability in the CEGIS loop,  
-as an objective for guessing controllers that are later proven sound over safety requirements.  
-Asymptotic stability is a property that amounts to convergence of the model executions to an equilibrium point, 
-starting from any states in a neighborhood of the point (see Figure~\ref{fig:ct} for the portrait of a stable execution, converging to the origin).  
-In the case of linear systems as in~\eqref{eq:closedloopss}, 
-considered with a zero reference signal, 
-the equilibrium point of interest is the origin.
-
-A discrete-time LTI system as \eqref{eq:closedloopss} is asymptotically
-stable if all the roots of its characteristic polynomial (i.e., the
-eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
-circle of the complex plane, i.e., their absolute values are strictly less than
-one~\cite{astrom1997computer} (this simple sufficient condition can be generalised, 
-however this is not necessary in our work).  
-In this paper, we express this stability specification $\phi_\mathit{stability}$ in terms of a check known as
-\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic formula to
-select the entries of matrix $K$ so that the closed-loop dynamics are shaped
-as desired.
-
-%-------------------------------
-\subsection{Safety specifications for dynamical systems}
-\label{ssec:safety}
+where $\mathcal{A}=\bigcup_{k=1}^\infty (A_d-B_dK)^k,
+\mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k(A_d-B_dK)^iB_{n}$ are
+abstract matrices for the closed-loop system~\cite{cattaruzza2015unbounded},
+whereas the set $N$ is non-deterministically chosen.
+
+We next evaluate $\hat{X}^\# \models \phi_\mathit{safety}$.  If the
+verification holds we have a solution, and exit the loop.  Otherwise, we
+find a counterexample iteration $k$ and corresponding initial point $x_0$
+for which the property does not hold, which we use to locally refine the
+abstraction.  When the abstraction cannot be further refined, we provide
+them to the {\sc abstract} phase.
+%
+%\todo{we should have a better argument here.}
+%\end{enumerate} 
+\item If we reach the {\sc abstract} phase, it means that the candidate solution is not valid,
+  in which case we must refine the abstraction used by the synthesizer.
+\begin{enumerate}
+\item Find the constraints that invalidate the property
+ as a set of counterexamples for the eigenvalues, which we define as $\phi_\Lambda$. This is a constraint in the spectrum i.e., transfer function) of the closed loop dynamics. 
+\item We use $\phi_\Lambda$ to
+  further constrain the characteristic polynomial %\blue{[again, check the coefficients of the characteristic polynomial.]I don't find any error} 
+$z^n+\sum_{i=1}^n(a_i-k_i)z^{n-i}=\prod_{i=1}^n (z-\lambda_i) : |\lambda_i|<1 \wedge \lambda_i \models \phi_{\Lambda}$.
+These constraints correspond to specific iterations for which the system may be unsafe.
+\item Pass the refined abstraction $\phi(K)$ with the new constraints and the list of iterations $k$ to the {\sc synthesize} phase.
+  %, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again. 
+\end{enumerate} 
+\end{enumerate}
+
+%%-------------------------------
+%\subsection{State-space representation of physical systems} 
+%\label{ssec:ssrepresentation}
+%%-------------------------------
+%
+%We consider models of physical plants expressed as ordinary differential
+%equations (ODEs), which we assume to be controllable and under full state
+%information (i.e., we have access to all the model variables):
+%%
+%\begin{align}
+%\label{eq:ode}
+%\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, \\ \nonumber A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}, 
+%\end{align}
+%%
+%where $t \in \mathbb R_0^+$, where $A$ and $B$ are matrices that fully
+%specify the continuous plant, and with initial states set as $x(0)$.  While
+%ideally we intend to work on the continuous-time plant, in this work
+%Eq.~\eqref{eq:ode} is soundly discretized in time~\cite{fadali} into
+%%
+%\begin{align}
+%\label{eq:plant}
+%x_{k+1} = A_d x_k+ B_d u_k
+%\end{align} 
+%%
+%where $k \in \mathbb N$ and $x_{0}=x(0)$ is the initial state. 
+%$A_d$ and $B_d$ denote the matrices that describe the discretized plant dynamics, whereas
+%$A$ and $B$ denote the continuous plant dynamics.  
+%We synthesize for requirements over this discrete-time domain. 
+%Later, we will address the issue of variable quantization, 
+%as introduced by the ADC/DAC conversion blocks 
+%(\textcolor{red}{we should include a figure that describes the control system model that we tackle}).
+%
+%
+%
+%%-------------------------------
+%\subsection{Controller synthesis via state feedback}
+%\label{ssec:statefeedbackcontrol}
+%%-------------------------------
+%
+%Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t)$ and  $u_k$, respectively. 
+%Feedback architectures can be employed to manipulate the properties and behaviors of the continuous process (the plant).   
+%We are interested in the synthesis of digital feedback control algorithms, 
+%as implemented on Field-Programmable Gate Arrays or Digital Signal Processors. 
+%The most basic feedback architecture is the state feedback one, 
+%where the control action $u_k$ (notice we work with the discretized signal) is computed by: 
+%%
+%\begin{equation}
+%\label{eq:controlaction}
+%u_k = r_{k} - K x_k. 
+%\end{equation}
+%%
+%Here, $K \in \mathbb{R}^{m \times n}$ is a state-feedback gain matrix, 
+%and $r_{k}$ is a reference signal (again digital).   
+%%
+%The closed-loop model then takes the form 
+%\begin{align}
+%\label{eq:closedloopss}
+%x_{k+1} = ( A_d - B_d K ) x_k + B_d r_k.
+%\end{align}
+%%
+%The gain matrix $K$ can be set so that the closed-loop discrete dynamics are
+%shaped as desired, for instance according to a specific stability goal or
+%around a specific dynamical behavior \cite{astrom1997computer}.  As argued
+%later in this work, we will target more complex objectives, such as
+%quantitative safety requirements, which are not typical in the digital
+%control literature.  Further, we will embrace the digital nature of the
+%controller, which manipulates quantized signals as discrete quantities represented with finite precision. 
+%
+%%-------------------------------
+%\subsection{Stability of closed-loop systems}
+%\label{ssec:stability}
+%%-------------------------------
+%
+%In this work we employ asymptotic stability in the CEGIS loop,  
+%as an objective for guessing controllers that are later proven sound over safety requirements.  
+%Asymptotic stability is a property that amounts to convergence of the model executions to an equilibrium point, 
+%starting from any states in a neighborhood of the point (see Figure~\ref{fig:ct} for the portrait of a stable execution, converging to the origin).  
+%In the case of linear systems as in~\eqref{eq:closedloopss}, 
+%considered with a zero reference signal, 
+%the equilibrium point of interest is the origin. 
+%
+%A discrete-time LTI system as \eqref{eq:closedloopss} is asymptotically
+%stable if all the roots of its characteristic polynomial (i.e., the
+%eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
+%circle of the complex plane, i.e., their absolute values are strictly less than
+%one~\cite{astrom1997computer} (this simple sufficient condition can be generalised, 
+%however this is not necessary in our work).  
+%In this paper, we express this stability specification $\phi_\mathit{stability}$ in terms of a check known as
+%\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic formula to
+%select the entries of matrix $K$ so that the closed-loop dynamics are shaped
+%as desired.
+%
+%%-------------------------------
+%\subsection{Safety specifications for dynamical systems}
+%\label{ssec:safety}
+%%-------------------------------
+%
+%We are not limited to the synthesis of digital stabilizing controllers -- a
+%well known task in the literature on digital control systems -- but target
+%safety requirements with an overall approach that is sound and automated. 
+%More specifically, we require that the closed-loop system
+%\eqref{eq:closedloopss} meets given safety specifications.  A safety
+%specification gives raise to a requirement on the states of the model, such
+%that the feedback controller (namely the choice of the gains matrix~$K$)
+%must ensure that the state never violates the requirement.  Note that a
+%stable, closed-loop system is not necessarily a safe system: indeed, the
+%state values may leave the safe part of the state space while they converge
+%to the equilibrium, which is typical in the case of oscillatory dynamics. 
+%In~this work, the safety property is expressed as:
+%%
+%\begin{equation}
+%\label{eq:safetyliteral}
+%\phi_\mathit{safety}\iff \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
+%\end{equation}
+%where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
+%for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
+%instant, respectively.  This means that the states will always be within an $n$-dimensional hyper-box.
+%
+%Furthermore, it is practically relevant to consider the 
+%constraints $\phi_\mathit{input}$ on the input
+%signal $u_{k}$ and $\phi_\mathit{init}$ on the initial states $x_0$,
+%which we assume have given bounds:
+%$\phi_\mathit{input} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
+%$\phi_\mathit{init} = \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$
+%For the former, this means that the control input might saturates in view of
+%physical constraints.
+%
+%%-------------------------------
+%\subsection{Performance specifications for dynamical systems}
+%\label{ssec:performance}
+%%-------------------------------
+%
+%\textcolor{red}{we should describe here about the performance specifications for dynamical systems.}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Numerical representation and soundness} 
+\label{sec:numeric_rep}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+\textcolor{red}{this section needs to be updated to describe about floating-point arithmetic.}
+
+The models we consider have two sources of error that are due to numerical  
+representation.  The first is the numerical error introduced by the
+fixed-point numbers employed to model the plant, i.e., to represent the
+plant dynamics $A_d$, $B_d$ and $x_k$.  The second is the quantization error
+introduced by the digital controller, which performs operations on
+fixed-point numbers.  In this section we outline the notation for the
+fixed-point representation of numbers, and briefly describe the errors
+introduced.  A~formal discussion is in
+%Appendix~\ref{appendix:numerical_errors}.
+
+Let $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$
+represented in a fixed point domain, with $I$ bits representing the integer
+part and $F$ bits representing the decimal part.  The smallest number that
+can be represented in this domain is $c_m=2^{-F}$.  Any mathematical
+operations performed at the precision $\mathcal{F}_{\langle I,F \rangle}(x)$
+will introduce errors, for which an upper bound can be
+given~\cite{DBLP:conf/arith/BrainTRW15}.
+
+We will use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real
+number $x$ represented at the fixed-point precision of the controller, and
+$\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$
+represented at the fixed-point precision of the plant model ($I_c$ and $F_c$ are determined by the controller.
+We pick $I_p$ and $F_p$ for our synthesis such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$).
+Thus any mathematical operations in our modelled
+digital controller will be in the range of $\mathcal{F}_{\langle I_c,F_c
+\rangle}$, and all other calculations in our model will be carried out in the range of
+$\mathcal{F}_{\langle I_p,F_p \rangle}$.  
+The physical plant operates in the
+reals, which means our verification phase must also account for the numerical error and quantization errors caused by representing the physical plant at the finite precision $\mathcal{F}_{\langle I_p,F_p \rangle}$.
+
+\subsubsection{Effect on safety specification and stability}
+
+Let us first consider the effect of the quantization errors on safety. 
+Within the controller, state values are manipulated at low precision,
+alongside the vector multiplication $Kx$.
+The inputs are computed using the following equation: 
+%
+\begin{align*}
+u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})). 
+\end{align*}
+
+This induces two types of the errors detailed above: first, the truncation
+error due to representing $x_k$ as $\mathcal{F}{\langle I_c,F_c
+\rangle}(x_{k})$; and second, the rounding error introduced by the
+multiplication operation.  We represent these errors as non-deterministic
+additive noise.
+
+An additional error is due to the representation of the plant dynamics, namely 
+%
+\begin{align*}
+x_{k+1} &=\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
+\end{align*}
+We address this error by use of interval
+arithmetic~\cite{moore1966interval} in the verification phase.
+
+Previous studies~\cite{gangli1} show that the FWL affects the poles and
+zeros positions, degrading the closed-loop dynamics, causing steady-state
+errors (see Appendix~\ref{sec:appendix:LTIbackground} for details) and
+eventually de-stabilizing the system~\cite{Bessa16}.  However, since in this
+paper we require stability only as a precursor to safety, it is sufficient
+to check that the (perturbed, noisy) model converges to a neighborhood of
+the equilibrium within the safe set (see Appendix~\ref{sec:stab_FWL}).
+
+In the following, we shall disregard these steady-state errors (caused by
+FWL effects) when stability is ensured by synthesis, and then verify its
+safety accounting for the finite-precision errors.
+
+%-------------------------------
+\section{Formal specification of control systems properties} 
+\label{sec:specification}
+%-------------------------------
+
+%-------------------------------
+\subsection{Formal specification of stability} 
+\label{ssec:stabspecification}
+%-------------------------------
+
+Next, we describe the specific property that we pass to the program
+synthesizer as the specification $\sigma$.  There are a number of 
+algorithms in our verification engine that can be used for stability analysis~\cite{daes20161, Bessa16}.  
+%one based on Schur's decomposition
+%and another one based on Jury's criterion~\cite{astrom1997computer}.  
+Here we choose Jury's criterion~\cite{astrom1997computer} in view of its efficiency 
+and ease of integration within \tool: 
+we employ this method to check the stability in the $z$-domain for the
+characteristic polynomial $S(z)$ defined in~\eqref{eq:internal_stab_lemma}.
+%
+% of the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$, where $Y(z)$ is the closed-loop system output and U(z) is the controller output. 
+%% \red{[unclear: what matrix? We need to clarify the relationship
+%% between the char. poly. $S(z)$ and the later quantities $\Delta
+%% N_{G}(z), \Delta D_{G}(z)$ and corresponding controller's
+%% structure.]}.
+%
+We~consider the following form for $S(z)$:
+%
+\begin{equation*}
+S(z) = a_0z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N=0, a_0\neq0. 
+\end{equation*}
+%\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?}
+
+% Assuming that $\hat{G}(z) = \frac{\hat{N_G}(z)}{\hat{D_G}(z)}$
+% and $\hat{C}(z) = \frac{\hat{N_C}(z)}{\hat{D_C}(z)}$, then:
+% $$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$
+Next, the following matrix
+$M = [m_{ij}]_{(2N-2)\times N}$ is built from $S(z)$ coefficients:
+%
+$$
+M=\left( 
+\begin{array}{c}
+V^{(0)}\\
+V^{(1)}\\
+\vdots\\
+V^{(N-2)}
+\end{array}
+\right), 
+$$
+%
+where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ such that:
+%
+$$
+v_{ij}^{(0)}=\left\{
+\begin{array}{ll}
+a_{j-1}, & \mbox{if}~i=1\\
+v_{(1)(N-j+1)}^{0},&\mbox{if}~i=2
+\end{array}
+\right.
+$$
+%
+$$
+v_{ij}^{(k)}=\left\{
+\begin{array}{ll}
+0,&\mbox{if}~j>n-k\\
+v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \mbox{if}~j\leq n-k ~\mbox{and}~i=1\\
+v_{(1)(N-j+1)}^{k},& \mbox{if}~j\leq n-k ~\mbox{and}~i=2\\
+\end{array}
+\right.
+$$
+%
+and where $k \in \mathbb{Z}$ is such that $0 < k < N - 2$. 
+We have that~\cite{astrom1997computer} 
+$S(z)$ is the
+characteristic polynomial of a stable system if and only if the following four conditions hold:
+%\begin{itemize}
+%\item 
+$R_1: S(1) > 0$;
+%\item 
+$R_2: (−1)^N S(−1) > 0$;
+%\item 
+$R_3: |a_0| < a_N$;
+%\item 
+$R_4: m_{11} > 0 \wedge\allowbreak
+      m_{31}>0 \wedge\allowbreak
+      m_{51}>0 \wedge \ldots \wedge\allowbreak
+      m_{(2N{-}3)(1)}>0$.
+%\end{itemize}
+%
+The stability property is then encoded by a constraint of the form:
+$
+\phi_\mathit{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
+$
+
+%-------------------------------
+\subsection{Formal specification of safety} 
+\label{ssec:safespecification}
 %-------------------------------
@@
 to the equilibrium, which is typical in the case of oscillatory dynamics. 
+%However, a safe system will always be stable.  
 In~this work, the safety property is expressed as:
@@
 \end{equation}
+%
+%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
+%
 where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
@@
 %-------------------------------
-\subsection{Performance specifications for dynamical systems}
-\label{ssec:performance}
-%-------------------------------
-
-\textcolor{red}{we should describe here about the performance specifications for dynamical systems.}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Numerical representation and soundness} 
-\label{sec:numeric_rep}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-\textcolor{red}{this section needs to be updated to describe about floating-point arithmetic.}
-
-The models we consider have two sources of error that are due to numerical  
-representation.  The first is the numerical error introduced by the
-fixed-point numbers employed to model the plant, i.e., to represent the
-plant dynamics $A_d$, $B_d$ and $x_k$.  The second is the quantization error
-introduced by the digital controller, which performs operations on
-fixed-point numbers.  In this section we outline the notation for the
-fixed-point representation of numbers, and briefly describe the errors
-introduced.  A~formal discussion is in
-%Appendix~\ref{appendix:numerical_errors}.
-
-Let $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$
-represented in a fixed point domain, with $I$ bits representing the integer
-part and $F$ bits representing the decimal part.  The smallest number that
-can be represented in this domain is $c_m=2^{-F}$.  Any mathematical
-operations performed at the precision $\mathcal{F}_{\langle I,F \rangle}(x)$
-will introduce errors, for which an upper bound can be
-given~\cite{DBLP:conf/arith/BrainTRW15}.
-
-We will use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real
-number $x$ represented at the fixed-point precision of the controller, and
-$\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$
-represented at the fixed-point precision of the plant model ($I_c$ and $F_c$ are determined by the controller.
-We pick $I_p$ and $F_p$ for our synthesis such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$).
-Thus any mathematical operations in our modelled
-digital controller will be in the range of $\mathcal{F}_{\langle I_c,F_c
-\rangle}$, and all other calculations in our model will be carried out in the range of
-$\mathcal{F}_{\langle I_p,F_p \rangle}$.  
-The physical plant operates in the
-reals, which means our verification phase must also account for the numerical error and quantization errors caused by representing the physical plant at the finite precision $\mathcal{F}_{\langle I_p,F_p \rangle}$.
-
-\subsubsection{Effect on safety specification and stability}
-
-Let us first consider the effect of the quantization errors on safety. 
-Within the controller, state values are manipulated at low precision,
-alongside the vector multiplication $Kx$.
-The inputs are computed using the following equation: 
-%
-\begin{align*}
-u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})). 
-\end{align*}
-
-This induces two types of the errors detailed above: first, the truncation
-error due to representing $x_k$ as $\mathcal{F}{\langle I_c,F_c
-\rangle}(x_{k})$; and second, the rounding error introduced by the
-multiplication operation.  We represent these errors as non-deterministic
-additive noise.
-
-An additional error is due to the representation of the plant dynamics, namely 
-%
-\begin{align*}
-x_{k+1} &=\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
-\end{align*}
-We address this error by use of interval
-arithmetic~\cite{moore1966interval} in the verification phase.
-
-Previous studies~\cite{gangli1} show that the FWL affects the poles and
-zeros positions, degrading the closed-loop dynamics, causing steady-state
-errors (see Appendix~\ref{sec:appendix:LTIbackground} for details) and
-eventually de-stabilizing the system~\cite{Bessa16}.  However, since in this
-paper we require stability only as a precursor to safety, it is sufficient
-to check that the (perturbed, noisy) model converges to a neighborhood of
-the equilibrium within the safe set (see Appendix~\ref{sec:stab_FWL}).
-
-In the following, we shall disregard these steady-state errors (caused by
-FWL effects) when stability is ensured by synthesis, and then verify its
-safety accounting for the finite-precision errors.
-
-%-------------------------------
-\section{Formal specification of control systems properties} 
-\label{sec:specification}
-%-------------------------------
-
-%-------------------------------
-\subsection{Formal specification of stability} 
-\label{ssec:stabspecification}
-%-------------------------------
-
-%-------------------------------
-\subsection{Formal specification of safety} 
-\label{ssec:safespecification}
-%-------------------------------
-
-%-------------------------------
 \subsection{Formal specification of transient response} 
@@
 %-------------------------------
+
+{\color{red} It must be carefully described: it will be an important contribution}
 

### 2017-05-25 automatica/automatica.tex
Fixes

@@
 
-{\color{blue}[IB:] In my opinion, the subsections \ref{ssec:statefeedbackcontrol}, \ref{ssec:ssrepresentation}, are \ref{ssec:stability} are useless for the Automatica audience.
-In addition, i guess that all the subsections~\ref{ssec:ssrepresentation}-\ref{ssec:performance} should be erased and a new section about formal specification of transient and stability specifications can be created.}
-
 %-------------------------------
@@
 
-\begin{figure*}[t]
+\begin{figure}[t]
 \centering
-\includegraphics[width=0.9\textwidth]{figures/synthesis-flow.pdf}
+\includegraphics[width=\columnwidth]{figures/synthesis-flow.pdf}
 \vspace{0.1cm}
 \caption{Overview of the synthesis process\label{DSSynth_process}}
-\end{figure*}
+\end{figure}
 
@@
 \centering
-%\resizebox{.8\textwidth}{!}
+\resizebox{\columnwidth}{!}
 {
@@
 
-\begin{figure*}[t]
+\begin{figure}[t]
 \centering
-\includegraphics[width=0.6\textwidth]{figures/ct.eps}
-\vspace{0.1cm}
+\includegraphics[width=0.9\columnwidth]{figures/ct.eps}
+%\vspace{0.1cm}
 \caption{Completeness threshold for multi-staged verification. $T_s$ is the time step for the time discretization of the control matrices.}
 \label{fig:ct}
-\end{figure*}
+\end{figure}
 
@@
 %
-$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q_1}{2}\ \ \frac{q_1}{2}\right] 
-\wedge \nu_2 \in \left[-\frac{q_2}{2}\ \ \frac{q_2}{2}\right]  \wedge \nu_3 \in \left[-q_3\ \ q_3\right]  \right \}\nonumber$$
+\begin{equation}
+\nonumber
+\begin{split}
+N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q_1}{2}\ \ \frac{q_1}{2}\right] 
+\wedge \right. \\ \left. \nu_2 \in \left[-\frac{q_2}{2}\ \ \frac{q_2}{2}\right]  \wedge  \nu_3 \in \left[-q_3\ \ q_3\right]  \right \}
+\end{split}
+\end{equation}
 %
@@
 %
-\begin{align}
+{
+\scriptsize
+\begin{equation}
+%\begin{split}
+x=(A_d-B_dK)^kx_0+ \sum_{i=0}^{k-1} (A_d-B_dK)^i B_{n}(\nu_1+\nu_2+\nu_3)% 
+%\end{split}
+\end{equation}
+\begin{equation}
+B_n= [1 \cdots 1]^T
+\end{equation}
+}
 %\label{eq:acc_observer_LTI_cf}
-\hspace{-0.1in} x=&(A_d-B_dK)^kx_0
 %+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i
-+\sum_{i=0}^{k-1} (A_d-B_dK)^i B_{n}(\nu_1+\nu_2+\nu_3) : B_n= [1 \cdots 1]^T
-\end{align}
+
 %
@@
 \end{enumerate}
+
+\begin{figure}
+\centering
+\resizebox{\columnwidth}{!}
+{\scriptsize
+\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=.8cm, column sep=.2cm] {
+   \coordinate (aux1);
+   \& \coordinate (aux2);
+   \& ;\\
+   \&\node[fill=gray!20,align=center,xshift=-1.5cm] (pre) {{\sc 1. pre-}\\{\sc processing}};
+   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstract};
+   \& \coordinate (aux); \\ 
+   \&
+   \& \node[fill=gray!20,align=center] (synth) {\sc 2. synthesize};
+   \& \node[fill=gray!20,align=center, minimum width=4cm] (verify) {\sc 3. verify ($\phi$)};
+      \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc PASS};
+   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
+   \&
+   \& \node[draw,rectangle,align=center] (KSAT) {Program \\ Search};
+   \& complexnode/.pic={
+     \coordinate (AA);
+     \node[draw,rectangle,align=center] (AAV) at ([xshift=-1.5cm]AA.center) {Abstract\\Acceleration};
+     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm]AA.center) {Abstraction \\ Verifier};
+    }\\
+  };
+  \path
+    (pre.east) edge node[align=center] {$P_a$, $N$,\\ $\phi_\mathit{init}^k$} (abstract.west)
+    (abstract.south) edge node{$(\phi(K), k)$} (synth.north)
+    ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west)
+    (aux) edge (abstract.east) 
+    (verify.east) edge (done.west);
+  \path
+    ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {$K$} ([xshift=0.6cm]synth.south) 
+    ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$(\phi(K),k)$} ([xshift=-.6cm]KSAT.north)
+    ([yshift=.5cm]AAV.east) edge node{\sl $\hat{X}^\#$} ([yshift=.5cm]AAC.west)
+    ([yshift=-.5cm]AAC.west) edge node{$(k,x_0)$} ([yshift=-.5cm]AAV.east)
+    (AAC.north) edge node{\sl $\hat{X}^\#$} ([xshift=4.9cm]verify.south)
+    ([xshift=-5cm]verify.south) edge node{$K$} (AAV.north);
+  \path[-] 
+     (verify.north) edge node {$(k,x_0)$} (aux);
+\end{tikzpicture}
+}
+\caption{Abstraction-based CEGIS}
+\label{fig:CEGARIS} 
+\end{figure}
 

### 2017-05-25 automatica/automatica.tex
fixes

@@
 to synthesize.  CEGIS employs an iterative, counterexample-guided refinement
-process, which is explained in detail in Section~\ref{synthesizer-general}. 
+process.%, which is explained in detail in Section~\ref{synthesizer-general}. 
 CEGIS reports a successful synthesis result if it generates a controller
@@
 Criteria, as well as the restrictions on the representation of these
-coefficients as discussed in detail in Section~\ref{synthesis-elements}.
+coefficients.% as discussed in detail in Section~\ref{synthesis-elements}.
 
@@
 compute a candidate solution $K$ that satisfies both the stability criteria
-(Sec.~\ref{ssec:stability}) and the safety specification
-(Sec.~\ref{ssec:safety}).  To synthesize a controller that satisfies the
+ and the safety specification.  To synthesize a controller that satisfies the
 stability criteria, we require that a computed polynomial
@@
 
-  The na\"ive approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
+%  The na\"ive approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
   %uses a multi-staged verification phase and performs solution generalization based on
@@
   %and the sampling rate. Essentially, it
-  synthesizes a controller for an individual initial state
-and input with a bounded time horizon and, subsequently, it generalizes it to all reachable states,
-inputs, and time horizons during the verification phase.
+%  synthesizes a controller for an individual initial state
+%and input with a bounded time horizon and, subsequently, it generalizes it to all reachable states,
+%inputs, and time horizons during the verification phase.
 Essentially, this approach relies on the symbolic
@@
 \end{equation}
+
 %
@@
 we employ this method to check the stability in the $z$-domain for the
-characteristic polynomial $S(z)$ defined in~\eqref{eq:internal_stab_lemma}.
+characteristic polynomial $S(z)$.
 %
@@
 
-%-------------------------------
-\section{Stability of Closed-loop Models}
-\label{sec:appendix-stability}
-%-------------------------------
-
-%-------------------------------
-\subsection{Stability of closed-loop models with fixed-point controller error}
-\label{sec:stab_FWL}
-%-------------------------------
-
-The proof of Jury's criterion~\cite{fadali} relies on the fact that the relationship between states and
-next states is defined by $x_{k+1} = (A_d - B_dK) x_k$, all computed
-at infinite precision.  When we employ a FWL digital controller, the
-operation becomes:
-%
-\begin{align*}
-x_{k+1} &= A_d \cdot x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
-x_{k+1} &= (A_d  - B_dK) \cdot x_k + B_dK\delta, 
-\end{align*}
-%
-where $\delta$ is the maximum error that can be introduced by the FWL
-controller in one step, i.e., by reading the states values once and
-multiplying by $K$ once.  We derive the closed form expression for $x_n$ as
-follows:
-%
-\begin{align*}
-x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
-x_{2} 
- &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
-x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... \\  \nonumber & + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
-  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{i=n-1}(A_d - B_dK)^iB_dk\delta. 
-\end{align*}
-
-The definition of asymptotic stability is that the system converges to a
-reference signal, in this case we use no reference signal so an
-asymptotically stable system will converge to the origin.  We know that the
-original system with an infinite-precision controller is stable, because we
-have synthesized it to meet Jury's criterion.  Hence, $(A_d - B_dK)^n x_0$ 
-must converge to zero.
-
-The power series of matrices
-converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less
-than~1 as follows:
-%
+%%-------------------------------
+%\section{Stability of Closed-loop Models}
+%\label{sec:appendix-stability}
+%%-------------------------------
+%
+%%-------------------------------
+%\subsection{Stability of closed-loop models with fixed-point controller error}
+%\label{sec:stab_FWL}
+%%-------------------------------
+%
+%The proof of Jury's criterion~\cite{fadali} relies on the fact that the relationship between states and
+%next states is defined by $x_{k+1} = (A_d - B_dK) x_k$, all computed
+%at infinite precision.  When we employ a FWL digital controller, the
+%operation becomes:
+%%
 %\begin{align*}
-$\sum_{i=0}^{\infty}T^i  = (I - T)^{-1}$, 
+%x_{k+1} &= A_d \cdot x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
+%x_{k+1} &= (A_d  - B_dK) \cdot x_k + B_dK\delta, 
 %\end{align*}
-%
-where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge to the value 
-%
-\begin{align*}
-0 + (I - A_d + B_dK)^{-1}B_dk\delta \,. 
-\end{align*}
-%
-As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the
-safe space, then the synthesized fixed-point controller results in a safe
-closed-loop model.  The convergence to a finite value, however, will not
-make it asymptomatically stable.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Errors in LTI models} \label{sec:appendix:LTIbackground}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-\subsection{Errors due to numerical representation} \label{appendix:numerical_errors}
-
-We have  used $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number
-$x$ represented in a fixed point domain, with $I$ bits representing the
-integer part and $F$ bits representing the decimal part.  The smallest
-number that can be represented in this domain is $c_m=2^{-F}$.  The
-following approximation errors will arise in mathematical operations and
-representation:
-%
-\begin{enumerate}
-
-\item {\bf Truncation:} Let $x$ be a real number, and $\mathcal{F}_{\langle
-I,F \rangle}(x)$ be the same number represented in a fixed-point domain as
-above.  Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the
-error $ \delta_T=x\ \%_{c_m}\ \tilde x$, and $\%_{c_m}$ is the modulus
-operation performed on the last bit. 
-Thus, $\delta_T$ is the truncation error and it will propagate across
-operations.
-%
-\item {\bf Rounding:} The following errors appear in basic operations.  Let
-$c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be
-the truncation errors caused by representing $c_1$ and $c_2$ in the
-fixed-point domain as above.
-%
-\begin{enumerate}
-%
-\item Addition/Subtraction: these operations only propagate errors coming
-from truncation of the operands, namely $\mathcal{F}_{\langle I,F
-\rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3$
-with $|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
-%
-\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) \cdot
-\mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3|
-\leq |\delta_{T1}\cdot\mathcal{F}_{\langle I,F \rangle}(c_2)|\allowbreak +
-|\delta_{T2}\cdot\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where
-$c_m=2^{-F}$ as above.
-%
-\item Division: the operations performed by our controllers in the FWL
-domain do not include division.  However, we do use division in computations
-at the precision of the plant.  Here the error depends on whether the
-divisor is greater or smaller than the dividend:  $\mathcal{F}_{\langle I,F
-\rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_{T3}$
-where $\delta_{T3}$ is $(\delta_{T2}\cdot c_1 - \delta_{T1}\cdot
-c_2)/(\delta_{T2}^2 - \delta_{T2} c_2)$,
-\end{enumerate}
-
-\item {\bf Overflow:}
-The maximum size of a real number $x$ that can be represented in a fixed
-point domain as $\mathcal{F}_{\langle I,F \rangle}(x)$ is $\pm
-(2^{I-1}+1-2^{-F})$.  Numbers outside this range cannot be represented by
-the domain.  We check that overflow does not occur.
-
-\end{enumerate}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Modeling quantization as noise} \label{appendix:quantization-noise}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-During any given ADC conversion, the continuous signal will be sampled in
-the real domain and transformed by $\mathcal{F}\langle I_{c},F_{c} \rangle
-(x)$ (assuming the ADC discretization is the same as the digital
-implementation).  This sampling uses a threshold which is defined by the
-less significant bit ($q_{c}=c_{m_c}=2^{-F_c}$) 
-of the ADC and some non-linearities of the circuitry.  The overall conversion is
-%
-$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k :
-y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right] \,.$$
-%
-If we denote the error in the conversion by $\nu_k=y_k-y(t)$ where $t = nk$,
-and $n$ is the sampling time and $k$ the number of steps, then we may define
-some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
-
-We will assume, for the purposes of this analysis, that the domain of the
-ADC is that of the digital controller (i.e, the quantizer includes any
-digital gain added in the code).  The process of quantization in the DAC is
-similar except that it is calculating $\mathcal{F}\langle I_{dac},F_{dac}
-\rangle (\mathcal{F}\langle I_{c},F_{c} \rangle (x)) $.  If these domains
-are the same ($I_{c}=I_{dac},\allowbreak F_{c}=F_{dac}$), or if the DAC
-resolution in higher than the ADCs, then the DAC quantization error is equal
-to zero.  From the above equations we can now define the ADC and DAC
-quantization noises ${\nu_1}_k \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}]$ and
-${\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}]$, where $q_1=q_{c}$ and 
-$q_2=q_\mathit{dac}$.  This is illustrated in
-Fig.~\ref{ssec:statefeedbackcontrol} where $Q_1$ is the quantizer of the ADC
-and $Q_2$ the quantizer for the DAC.  These bounds hold irrespective of
-whether the noise is correlated, hence we may use them to over-approximate
-the noise effect on the state space progression over time.  The
-resulting dynamics are
-%
-\begin{align*}
-%\label{eq:pre_quantization}
-{x}_{k+1} = {A}_d{x}_k+{B}_d({u}_k+{{\nu}_2}_k), \quad u_k = -K{x}_{k}+{{\nu}_1}_k, 
-\end{align*}
-%
-which result in the following closed-loop dynamics:
-%
-\begin{align*}
-%\label{eq:quantization}
-{x}_{k+1} &= ({A}_d-{B}_d{K}_d) {x}_k+{B}_d{{\nu}_2}_k +{{\nu}_1}_k \,. 
-\end{align*}
+%%
+%where $\delta$ is the maximum error that can be introduced by the FWL
+%controller in one step, i.e., by reading the states values once and
+%multiplying by $K$ once.  We derive the closed form expression for $x_n$ as
+%follows:
+%%
+%\begin{align*}
+%x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
+%x_{2} 
+% &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
+%x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... \\  \nonumber & + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
+%  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{i=n-1}(A_d - B_dK)^iB_dk\delta. 
+%\end{align*}
+%
+%The definition of asymptotic stability is that the system converges to a
+%reference signal, in this case we use no reference signal so an
+%asymptotically stable system will converge to the origin.  We know that the
+%original system with an infinite-precision controller is stable, because we
+%have synthesized it to meet Jury's criterion.  Hence, $(A_d - B_dK)^n x_0$ 
+%must converge to zero.
+%
+%The power series of matrices
+%converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less
+%than~1 as follows:
+%%
+%%\begin{align*}
+%$\sum_{i=0}^{\infty}T^i  = (I - T)^{-1}$, 
+%%\end{align*}
+%%
+%where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge to the value 
+%%
+%\begin{align*}
+%0 + (I - A_d + B_dK)^{-1}B_dk\delta \,. 
+%\end{align*}
+%%
+%As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the
+%safe space, then the synthesized fixed-point controller results in a safe
+%closed-loop model.  The convergence to a finite value, however, will not
+%make it asymptomatically stable.
+%
+%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%\section{Errors in LTI models} \label{sec:appendix:LTIbackground}
+%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%
+%\subsection{Errors due to numerical representation} \label{appendix:numerical_errors}
+%
+%We have  used $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number
+%$x$ represented in a fixed point domain, with $I$ bits representing the
+%integer part and $F$ bits representing the decimal part.  The smallest
+%number that can be represented in this domain is $c_m=2^{-F}$.  The
+%following approximation errors will arise in mathematical operations and
+%representation:
+%%
+%\begin{enumerate}
+%
+%\item {\bf Truncation:} Let $x$ be a real number, and $\mathcal{F}_{\langle
+%I,F \rangle}(x)$ be the same number represented in a fixed-point domain as
+%above.  Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the
+%error $ \delta_T=x\ \%_{c_m}\ \tilde x$, and $\%_{c_m}$ is the modulus
+%operation performed on the last bit. 
+%Thus, $\delta_T$ is the truncation error and it will propagate across
+%operations.
+%%
+%\item {\bf Rounding:} The following errors appear in basic operations.  Let
+%$c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be
+%the truncation errors caused by representing $c_1$ and $c_2$ in the
+%fixed-point domain as above.
+%%
+%\begin{enumerate}
+%%
+%\item Addition/Subtraction: these operations only propagate errors coming
+%from truncation of the operands, namely $\mathcal{F}_{\langle I,F
+%\rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3$
+%with $|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
+%%
+%\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) \cdot
+%\mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3|
+%\leq |\delta_{T1}\cdot\mathcal{F}_{\langle I,F \rangle}(c_2)|\allowbreak +
+%|\delta_{T2}\cdot\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where
+%$c_m=2^{-F}$ as above.
+%%
+%\item Division: the operations performed by our controllers in the FWL
+%domain do not include division.  However, we do use division in computations
+%at the precision of the plant.  Here the error depends on whether the
+%divisor is greater or smaller than the dividend:  $\mathcal{F}_{\langle I,F
+%\rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_{T3}$
+%where $\delta_{T3}$ is $(\delta_{T2}\cdot c_1 - \delta_{T1}\cdot
+%c_2)/(\delta_{T2}^2 - \delta_{T2} c_2)$,
+%\end{enumerate}
+%
+%\item {\bf Overflow:}
+%The maximum size of a real number $x$ that can be represented in a fixed
+%point domain as $\mathcal{F}_{\langle I,F \rangle}(x)$ is $\pm
+%(2^{I-1}+1-2^{-F})$.  Numbers outside this range cannot be represented by
+%the domain.  We check that overflow does not occur.
+%
+%\end{enumerate}
+%
+%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%\subsection{Modeling quantization as noise} \label{appendix:quantization-noise}
+%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%
+%During any given ADC conversion, the continuous signal will be sampled in
+%the real domain and transformed by $\mathcal{F}\langle I_{c},F_{c} \rangle
+%(x)$ (assuming the ADC discretization is the same as the digital
+%implementation).  This sampling uses a threshold which is defined by the
+%less significant bit ($q_{c}=c_{m_c}=2^{-F_c}$) 
+%of the ADC and some non-linearities of the circuitry.  The overall conversion is
+%%
+%$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k :
+%y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right] \,.$$
+%%
+%If we denote the error in the conversion by $\nu_k=y_k-y(t)$ where $t = nk$,
+%and $n$ is the sampling time and $k$ the number of steps, then we may define
+%some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
+%
+%We will assume, for the purposes of this analysis, that the domain of the
+%ADC is that of the digital controller (i.e, the quantizer includes any
+%digital gain added in the code).  The process of quantization in the DAC is
+%similar except that it is calculating $\mathcal{F}\langle I_{dac},F_{dac}
+%\rangle (\mathcal{F}\langle I_{c},F_{c} \rangle (x)) $.  If these domains
+%are the same ($I_{c}=I_{dac},\allowbreak F_{c}=F_{dac}$), or if the DAC
+%resolution in higher than the ADCs, then the DAC quantization error is equal
+%to zero.  From the above equations we can now define the ADC and DAC
+%quantization noises ${\nu_1}_k \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}]$ and
+%${\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}]$, where $q_1=q_{c}$ and 
+%$q_2=q_\mathit{dac}$.  This is illustrated in
+%Fig.~\ref{ssec:statefeedbackcontrol} where $Q_1$ is the quantizer of the ADC
+%and $Q_2$ the quantizer for the DAC.  These bounds hold irrespective of
+%whether the noise is correlated, hence we may use them to over-approximate
+%the noise effect on the state space progression over time.  The
+%resulting dynamics are
+%%
+%\begin{align*}
+%%\label{eq:pre_quantization}
+%{x}_{k+1} = {A}_d{x}_k+{B}_d({u}_k+{{\nu}_2}_k), \quad u_k = -K{x}_{k}+{{\nu}_1}_k, 
+%\end{align*}
+%%
+%which result in the following closed-loop dynamics:
+%%
+%\begin{align*}
+%%\label{eq:quantization}
+%{x}_{k+1} &= ({A}_d-{B}_d{K}_d) {x}_k+{B}_d{{\nu}_2}_k +{{\nu}_1}_k \,. 
+%\end{align*}
 

### 2017-05-25 automatica/automatica.tex
cleanup

--- 2017-05-25 automatica/automatica.tex
@@
 
-\usepackage{graphicx}          % Include this line if your 
-                               % document contains figures,
-%\usepackage[dvips]{epsfig}    % or this line, depending on which
-                               % you prefer.
+\usepackage{graphicx}
 \usepackage{color}
@@
 \usepackage{url}
+
 %\newcommand{\tool}{{\sf DSSynth}\xspace}
+
 \begin{document}
@@
 \begin{frontmatter}
+
 %\runtitle{Insert a suggested running title}  % Running title for regular 
@@
 
-\title{Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants with Transient Performance Specifications} % Title, preferably not more 
+\title{Safe and Robust Formal Synthesis of Digital Controllers
+       for Continuous Plants with Transient Performance Specifications}
+% Title, preferably not more
 % than 10 words.

### 2017-05-25 automatica/automatica.tex
fixes

@@
 rounding error in $u_k=-K \cdot \mathcal{F}_{\langle I_c,F_c \rangle}(x_k)$ as
-discussed in Section~\ref{sec:numeric_rep}.  More details on how to model
-quantization as noise are given in
-Appendix~\ref{appendix:quantization-noise}.
+discussed in Section~\ref{sec:numeric_rep}. % More details on how to model
+%quantization as noise are given in
+%Appendix~\ref{appendix:quantization-noise}.
 
@@
 %
-\begin{align*}
-x_{k+1} &=\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
-\end{align*}
+{\scriptsize
+\begin{equation}
+x_{k+1} =\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
+\end{equation}
+}
 We address this error by use of interval
@@
 zeros positions, degrading the closed-loop dynamics, causing steady-state
-errors (see Appendix~\ref{sec:appendix:LTIbackground} for details) and
+errors  and
 eventually de-stabilizing the system~\cite{Bessa16}.  However, since in this
@@
 More specifically, we require that the closed-loop system
-\eqref{eq:closedloopss} meets given safety specifications.  A safety
+ meets given safety specifications.  A safety
 specification gives raise to a requirement on the states of the model, such
@@
 
-\appendix
+%\appendix
 

### 2017-05-25 automatica/automatica.tex
assigned sections to collaborators
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{abstract}                          % Abstract of not more than 200 words.
-\textcolor{red}{We have to write a new abstract.}
+\textcolor{red}{Lucas: We have to write a new abstract.}
 \end{abstract}
@@
 \section{Introduction}
-\textcolor{red}{We have to write a new introduction as well.}
+\textcolor{red}{Cristina: We have to write a new introduction as well.}
 
@@
 %-------------------------------
+
+\textcolor{red}{Elizabeth: we need to define the notation used throughout the paper.}
 
@@
 
-\textcolor{red}{this section needs to be updated to describe about floating-point arithmetic.}
+\textcolor{red}{Elizabeth: this section needs to be updated to describe about floating-point arithmetic.}
 
@@
 
-{\color{red} It must be carefully described: it will be an important contribution}
+{\color{red} Dario: this section must be carefully described: it will be an important contribution}
 
@@
 
+\textcolor{red}{Iury: can you please describe the benchmarks?}
+
 %-------------------------------
@@
 
+\textcolor{red}{Lucas: describe here the experimental objectives.}
+
 %-------------------------------
@@
 
+\textcolor{red}{Pascal: can you please describe here the experimental results?}
+
 %-------------------------------
@@
 
+\textcolor{red}{Pascal: can you please describe here the threats to validity?}
+
 %-------------------------------
@@
 
-\textcolor{red}{We need to write a new conclusions about this work.}
+\textcolor{red}{Lucas: We need to write a new conclusions about this work.}
 

### 2017-05-28 automatica/automatica.tex
Settling time proof

@@
 %\newcommand{\tool}{{\sf DSSynth}\xspace}
+\newcommand{\mat}[1]{\boldsymbol{#1}}
+\renewcommand{\vec}[1]{\boldsymbol{#1}}
+\newtheorem{theorem}{Theorem}
+\newtheorem{proof}{Proof}
 
@@
 
-{\color{red} Dario: this section must be carefully described: it will be an important contribution}
-
+In a SISO system, there are 2 values that typically define the response-time of the system (using a step response).
+\begin{enumerate}
+\item The \emph{rise time} is defined as the time it takes the output to reach a percentage (eg $90\%$) of the target value given a step chnage in the input.
+\item The \emph{settling time} is defined as the time it takes the output to stabilize within a margin of the target value (eg $10\%$).
+\end{enumerate} 
+In the case of first and second order systems (with ), the decay is governed by the equations 
+\begin{align*}
+&y_{decay}=
+&\left\{
+\begin{array}{cc}
+e^{-|\omega| t}& 1^{st} order\\
+e^{\zeta |\omega| t}\left(\frac{\sin\left(|\omega| t\sqrt{1-\zeta^2}+\sin^{-1}\sqrt{1-\zeta^2}\right)}{\sqrt{1-\zeta^2}} \right)&\zeta<1\\
+e^{-|\omega| t}-|\omega| t e^{-|\omega| t}&\zeta=1\\
+\frac{|\omega| e^{-|\omega_2| t}-|\omega_2| e^{-|\omega| t}}{|\omega|-|\omega_2|}&\zeta>1\end{array}\right.
+\end{align*}
+where $|\omega|$ and $|\omega_2|$ are the magnitudes of the eigenvalues (roots) of the system and  $\zeta=-\cos(\theta)$ where $\theta$ is the polar angle of the conjugate pair if it exists ($\zeta \geq 1$ if it doesn't).
+These equations become increasingly complicated for higher order systems.
+However, we note their strong dependency on the magnitude of the eigenvalues, and use this property to define an upperbound on the decay function.
+All of the above equations will decay faster than $e^{-|\omega| t}$ given $|\omega| < |\omega_2|$, hence we may use this function as our upper bound.
+\begin{theorem}
+Given a set of eigenvalues for a discrete time modle of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1\ n]$, the settling time of the system is upperbounded by
+\begin{equation}
+t_s<-log_{|\overline{\lambda}|}({p_s}) : |\overline{\lambda}| =\max(|\lambda_i|) \wedge |\overline{\lambda}|<1,\ \forall i \in [1\ n]
+\label{eq:set_time}
+\end{equation}
+where $0\leq p_s \leq 1$ is the desired percentage of the target within to remain after $t_s$.
+\end{theorem} 
+\begin{proof}
+Given a closed loop single output LTI system of order $n$ with dynamics
+\begin{equation}
+\left\{\begin{array}{c}\vec{x}_k=\mat{A}\vec{x}_{k-1}\\ \vec{y}_k=\mat{C}\vec{x}_k\end{array}\right.
+\Rightarrow \left\{ \begin{array}{c}\vec{x}_k'=\mat{J}\vec{x}_{k-1}'\\ \vec{y}_k=\mat{C}\mat{S}\vec{x}_k'\end{array}\right.
+: \left\{ \begin{array}{c}\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \\ \vec{x}_k'=\mat{S}^{-1}\vec{x}_k\end{array}\right.
+\end{equation}
+the output decay is a linear combination of the decay of eigenvalues or eigenvalue pairs.
+Hence the overall decay of the system is always smaller than $p=e^{-|\overline{\omega}| t}$ where $0\leq p\leq 1$ is the remaining percentage of the decay expressed.
+reversing we have $t=-\frac{ln(p)}{|\overline{\omega}|}=-\frac{ln(p)}{ln(|\overline{\lambda}|)}$.
+replacing for $p_s$ , $t_s$, and $\overline{\lambda}$ we get equation \eqref{eq:set_time}
+\qed
+\end{proof}
+We may now use this limit to express a constraint in terms of the coefficients for our synthesis process.
+Let 
+\begin{equation}
+P=\prod_{i=0}^n (s-\lambda_i)=\sum_{j=0}^n c_js^j.
+\end{equation}
+We use Jury's criterion to limit $|\lambda_i| \leq 1$.
+Let us now define a transformation $\lambda_i'=\frac{\lambda_i}{\overline{\lambda}}$.
+We want to ensure $\lambda_i' \leq 1$ which can be done by applying Jury's criterion to $P'=\prod_{i=0}^n (s-\lambda_i')=\sum_{j=0}^n c_j's^j$ where $c_j'$ are unknown.
+However, if we replace for $\lambda_i$, we obtain
+\begin{equation}
+P'=\prod_{i=0}^n (s-\lambda_i')=\prod_{i=0}^n (s-\lambda_i\overline{\lambda})=\sum_{j=0}^n c_j\overline{\lambda}^{n-j}s^j
+\end{equation}
+where all members are known, we may now synthesise coefficients that ensure the eigenvalues are smaller than a desired magnitue, thus ensuring that the settling time is too.
 %-------------------------------

### 2017-05-28 emsoft2017/emsoft-paper.tex

\documentclass[sigconf]{acmart}

\usepackage{xspace,framed}

\setcopyright{acmcopyright}
\acmDOI{10.475/123_4}
\acmISBN{123-4567-24-567/08/06}
\acmConference[EMSOFT '17]{The ACM SIGBED International Conference on Embedded Software }{October 15--20, 2017}{Seoul, South Korea}
\acmYear{2017}
\copyrightyear{2017}
\acmPrice{15.00}

\newcommand\tool{{DSSynth Toolbox}\xspace}

\begin{document}

\title{DSSynth Toolbox: Automated Synthesis of Digital Controllers \\ for Physical Plants via MATLAB Toolbox}

\begin{abstract}
We present an automated approach implemented as a MATLAB Toolbox to synthesize stable and safe digital-control systems for physical plants represented as linear and time invariant models. The tool developed in the current paper is named as DSSynth (Digital-Systems Synthesis), which is a MATLAB Toolbox that synthesizes digital controllers w.r.t. the stability specification, considering finite word-length (FWL) effects for physical plants represented by transfer-function or state-space equations. DSSynth considers fixed-point numerical representation for the digital controller and dynamic input ranges for the closed-loop control system. Currently, there are two versions of the DSSynth toolbox: command-line and MATLAB application.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010520.10010570</concept_id>
<concept_desc>Computer systems organization~Real-time systems</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010520.10010553.10010562</concept_id>
<concept_desc>Computer systems organization~Embedded systems</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10011007.10010940.10010992.10010998.10003791</concept_id>
<concept_desc>Software and its engineering~Model checking</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10010940.10010992.10010998</concept_id>
<concept_desc>Software and its engineering~Formal methods</concept_desc>
<concept_significance>100</concept_significance>
</concept>
<concept>
<concept_id>10003752.10003790.10011192</concept_id>
<concept_desc>Theory of computation~Verification by model checking</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Real-time systems}
\ccsdesc[300]{Computer systems organization~Embedded systems}
\ccsdesc[500]{Software and its engineering~Model checking}
\ccsdesc[100]{Software and its engineering~Formal methods}
\ccsdesc[300]{Theory of computation~Verification by model checking}

\keywords{Formal Synthesis, Digital Controllers, MATLAB Toolbox, Fixed-point Arithmetic, Transfer-Function, State-Space, Digital Control Synthesis}

\maketitle

\input{paper-body}

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}

### 2017-05-28 emsoft2017/paper-body.tex

%---------------------------------------------------
\section{Introduction}
%---------------------------------------------------

%There are many application of embedded systems with low-cost devices that can perform non-trival tasks, such as UAV (Unmanned Aerial Vehicles) approach that could be used in various application (civil and millitary) that requires a reliable operation in order to avoid crashes and malfunctioning~\cite{williams2006human}. Synthesis of controllers for LTI (Linear Time Invariant) systems is broadly investigated, however the use of digital control architectures adds new challenges due to the effects of finite-precision arithmetic, time discretization, and quantization noise, which are typically introduced by Analogue-to-Digital (ADC) and Digital-to-Analogue (DAC) conversion~\cite{astrom1997computer}.

%In addition, embedded systems present a lot of advantages, if compared with analog ones, such as more flexibility, scalability, adaptability, and lower implementation cost. However, embedded systems are expressed as digital-control systems which are vulnerable to finite word-length (FWL) effects~\cite{Guang2013, Istepanian2001}, that can cause several quantization problems, such as truncation or round-off errors.

Linear Time Invariant (LTI) systems are concepts that are used in many applications in order to support non-trivial tasks when applied in embedded systems. In addition, synthesis of controllers for LTI systems is richly studied by different researchers, however there are many challenges when digital-control systems theory is used due to the effects of finite-word length (FWL)~\cite{Guang2013, Istepanian2001}, time discretization, and quantization noise, which are typically introduced by Analogue-to-Digital (ADC) and Digital-to-Analogue (DAC) conversion, that can cause several quantization problems, such as truncation or round-off errors.~\cite{astrom1997computer}.

Digital-control systems are computations that manipulate digital signals, in order to influence the behavior of a system~\cite{Ogata2001}; it can be mathematically expressed as difference equations, transfer functions, or state-space equations. In this particular work, the focus is on transfer-function and state-space representation. The following expression presents the general form of a digital-control system in transfer function format:
%
\begin{equation}
\small
\label{eq:transferfunction}
H(z)=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M}z^{-M}}{1+a_{1}z^{-1}+...+a_{N}z^{-N}},
\end{equation}
%
where $z^{-1}$ is called backward-shift operator, $A(z)$ and $B(z)$ are the denominator and numerator polynomials, respectively.

In state-space format, the digital-control system represents the behavior of a system through a state evolution equation $\dot{x}(n+1)$ and an instantaneous output equation $y(n)$, as follows:

\begin{equation}
\begin{split}
\dot{x}(n+1) &= A x(n) + B u(n)
\\
y(n) &= C x(n) + D u(n), 
\end{split}\label{eq:ss-example}
\end{equation}

%Recently, Bessa {\it et al.}~\cite{daes20161} has studied the stability of digital controllers considering implementation aspects, i.e., fixed-point arithmetic and the word length wich performs a model checking procedure based on satisfiability modulo theories (SMT) named as Digital-System Verifier (DSVerifier)~\cite{dsverifier}. While research on digital controller is well developed~\cite{astrom1997computer}, automated and sound control synthesis is challenging, particularly when the synthesis objective goes beyond classical stability.

Recently, a new methodology to synthesize digital-control systems was designed, named as DSSynth (Digital-System Synthesizer)~\cite{abate2017, abatecav2017}, which is based on Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} that are able to generate programs for highly non-trivial specifications with a very high degree of automation. Program synthesis engines use a specification as the starting point, and subsequently generate a sequence of candidate programs from a given template. The candidate programs are iteratively refined to eventually satisfy the specification. Modern synthesis engines combine automated testing, genetic algorithms, and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. Currently, Abate {\it et al.}~\cite{abate2017} synthesizes stable, software-implemented embedded controllers along with a model of a physical plant for transfer-function~\cite{abate2017}, and recently, also supports for state-space representation~\cite{abatecav2017}.

Notably, there are toolboxes in MATLAB with functions and scripts to facilitate the digital system design and implementation~\cite{matlab-toolbox}. In fact, there is a MATLAB Toolbox named as DSVerifier Toolbox~\cite{issta2017} that automatically detect specific errors related to digital system design ({\it e.g.}, stability) using symbolic model checking based on SAT and SMT solvers given the physical plant and the digital controller. However, there is no toolbox in MATLAB to perform the digital control synthesis based on Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} considering FWL effects.

The present paper addresses this problem and presents a MATLAB toolbox for DSSynth~\cite{abate2017, abatecav2017} in the MATLAB's environment named as \tool. The main advantage regarding the use of a MATLAB toolbox lies on designing physical plants in MATLAB and then promptly synthesizes a stable digital controller. Additionally, when using the \tool, an engineer is able to design a digital system with MATLAB, through transfer-function or state-space representations, consider low-level systems parameters (implementation features and numerical format), and then gets a stable synthesized digital-controller.

%---------------------------------------------------
\section{Synthesizing Digital Controller with \tool}
%---------------------------------------------------

The proposed synthesization methodology for closed-loop digital systems is based on DSSynth~\cite{abate2017, abatecav2017} and it can be split into two main stages as follows: manual (user) and automated (DSSynth) procedures, as shown in Fig.~\ref{fig:synthesis-flow}.

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{synthesis-flow.pdf}
\caption{Digital-Control Synthesis Methodology.}
\label{fig:synthesis-flow}
\end{figure}

In step $1$, the digital-control representation is determined, and it could be in transfer-function or state-space equations. In step $2$, the physical plant with the coefficients must be designed according to equations (\ref{eq:transferfunction}) and (\ref{eq:ss-example}). And finally, in step $3$, the numerical representation with the digital-control implementation must be defined, {\it i.e.}, the FWL format that includes the number of bits in the integer and fractional parts and the dynamic range inputs. The result from the manual procedure is a digital-system implementation for the given physical plant in MATLAB.

The synthesis process starts in step $A$, when the \tool gets the digital-system in MATLAB, and then translate it in a ANSI-C program, and then in step $B$, the DSSynth Tool is invoked. Finally, in step $C$, the digital controller is synthesized based on (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. The output generated in MATLAB is the digital controller synthesized, and it could be represented in transfer-function or state-space format. The synthesis is \emph{successful} when a digital controller is synthesized correctly, and the synthesis has status \emph{failed} when any parameter is defined incorrectly in previous steps, or there is no solution for the digital-system designed.

%---------------------------------------------------
\subsection{\tool Procedures}
%---------------------------------------------------

The \tool performs the following automated procedures in order to synthesize a digital controller:

\begin{enumerate}
\item \textbf{Setup}: obtain the plant, fixed-point format and dynamic input ranges, and translate them to a struct in MATLAB;
\item \textbf{Parse}: obtain the digital plant implementation, and then translate it to an ANSI-C file;
\item \textbf{Execute}: obtain the ANSI-C file from the previous step, call CBMC-CEGIS as back-end program synthesis tool, and then perform the automated synthesis;
\item \textbf{Extract}: obtain the .log that is generated after the synthesis phase and then check the synthesized digital-controller.
\item \textbf{Report}: obtain the digital-controller, translate it to a MATLAB system, and then show the result to the user.
\end{enumerate}

%---------------------------------------------------
\subsection{\tool Features}
%-----------------------------------------------

The \tool's features can be described as follows:

\begin{itemize}
\item \textbf{Representation}: the synthesis could be performed for digital-systems in transfer-function or state-space equations;
\item \textbf{Fixed-Point Arithmetic}: the digital controller is synthesized considering FWL effects, in fixed-point numeric representation;
\item \textbf{Interface}: the synthesis could be executed using the command-line version, and a GUI Application version. In addition, in the GUI Application, the user is able to plot the step response in order to reproduce the stability of the digital controller synthesized;
\end{itemize}
%---------------------------------------------------
\subsection{\tool Usage}
%---------------------------------------------------

%---------------------------------------------------
\subsubsection{Command Line Version}
%---------------------------------------------------

Users must provide a digital system described as a MATLAB system  using a \texttt{``tf''} (for transfer-function) or an \texttt{``ss''} (for state-space) command (cf. step $1$ of Fig.~\ref{fig:synthesis-flow}).

\tool is called via command line in MATLAB as \texttt{synthesize(plant, intBits, fracBits, maxRange, minRange)}, where \texttt{plant} is the physical plant in state-space or transfer-function representation, \texttt{intBits} is the integer part, \texttt{fracBits} is the fractional part, \texttt{maxRange} and \texttt{minRange} are the maximum and minimum dynamic range, respectively.

After executing \texttt{synthesize} command in MATLAB, the output prints the synthesized digital controller according to the digital system representation, {\it i.e.}, transfer-function or state-space equations.

%---------------------------------------------------
\subsubsection{MATLAB Application Version} 
%---------------------------------------------------

A graphical user interface application was developed (Fig.~\ref{fig:gui-for-tf}), in order to favor digital-control systems synthesis in MATLAB, besides improving usability and, consequently, attracting more digital-system engineers. Users can provide all required parameters for digital-system synthesization: physical plant specification, fixed-point implementation and dynamic inputs. 
%
\begin{figure}
  \includegraphics[width=0.5\textwidth]{screens_dssynth.png}
  \caption{GUI Application for Transfer-Function Synthesis.}
  \label{fig:gui-for-tf}
\end{figure}

\section{Conclusions}

\tool is able to synthesize dynamic physical plants designed in MATLAB, through transfer-function and state-space representations based on Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}.

Given the current literature in formal synthesis, there is no other MATLAB toolbox for synthesize stable digital systems, while taking into account implementation aspects (fixed-point arithmetic).

As future work, \tool will perform synthesis to generate stable digital controllers and be combined with DSVerifier Toolbox~\cite{issta2017} to verify the stability of the digital controller synthesized, and also, with DSValidator Toolbox~\cite{dsvalidator}, in order to reproduce and validate the stability property.

### 2017-05-28 emsoft2017/emsoft-paper.tex
moved paper-body to emsoft-paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\input{paper-body}
+%---------------------------------------------------
+\section{Introduction}
+%---------------------------------------------------
+
+%There are many application of embedded systems with low-cost devices that can perform non-trival tasks, such as UAV (Unmanned Aerial Vehicles) approach that could be used in various application (civil and millitary) that requires a reliable operation in order to avoid crashes and malfunctioning~\cite{williams2006human}.
+Synthesis of controllers for LTI (Linear Time Invariant) systems is broadly investigated, however the use of digital control architectures adds new challenges due to the effects of finite-precision arithmetic, time discretization, and quantization noise, which are typically introduced by Analogue-to-Digital (ADC) and Digital-to-Analogue (DAC) conversion~\cite{astrom1997computer}.
+
+%In addition, embedded systems present a lot of advantages, if compared with analog ones, such as more flexibility, scalability, adaptability, and lower implementation cost.
+However, embedded systems are expressed as digital-control systems which are vulnerable to finite word-length (FWL) effects~\cite{Guang2013, Istepanian2001}, that can cause several quantization problems, such as truncation or round-off errors.
+
+Linear Time Invariant (LTI) systems are concepts that are used in many applications in order to support non-trivial tasks when applied in embedded systems.
+In addition, synthesis of controllers for LTI systems is richly studied by different researchers, however there are many challenges when digital-control systems theory is used due to the effects of finite-word length (FWL)~\cite{Guang2013, Istepanian2001}, time discretization, and quantization noise, which are typically introduced by Analogue-to-Digital (ADC) and Digital-to-Analogue (DAC) conversion, that can cause several quantization problems, such as truncation or round-off errors.~\cite{astrom1997computer}.
+
+Digital-control systems are computations that manipulate digital signals, in order to influence the behavior of a system~\cite{Ogata2001}; it can be mathematically expressed as difference equations, transfer functions, or state-space equations.
+In this particular work, the focus is on transfer-function and state-space representation.
+The following expression presents the general form of a digital-control system in transfer function format:
+%
+\begin{equation}
+\small
+\label{eq:transferfunction}
+H(z)=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M}z^{-M}}{1+a_{1}z^{-1}+...+a_{N}z^{-N}},
+\end{equation}
+%
+where $z^{-1}$ is called backward-shift operator, $A(z)$ and $B(z)$ are the denominator and numerator polynomials, respectively.
+
+In state-space format, the digital-control system represents the behavior of a system through a state evolution equation $\dot{x}(n+1)$ and an instantaneous output equation $y(n)$, as follows:
+
+\begin{equation}
+\begin{split}
+\dot{x}(n+1) &= A x(n) + B u(n)
+\\
+y(n) &= C x(n) + D u(n), 
+\end{split}\label{eq:ss-example}
+\end{equation}
+
+%Recently, Bessa {\it et al.}~\cite{daes20161} has studied the stability of digital controllers considering implementation aspects, i.e., fixed-point arithmetic and the word length wich performs a model checking procedure based on satisfiability modulo theories (SMT) named as Digital-System Verifier (DSVerifier)~\cite{dsverifier}.
+While research on digital controller is well developed~\cite{astrom1997computer}, automated and sound control synthesis is challenging, particularly when the synthesis objective goes beyond classical stability.
+
+Recently, a new methodology to synthesize digital-control systems was designed, named as DSSynth (Digital-System Synthesizer)~\cite{abate2017, abatecav2017}, which is based on Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} that are able to generate programs for highly non-trivial specifications with a very high degree of automation.
+Program synthesis engines use a specification as the starting point, and subsequently generate a sequence of candidate programs from a given template.
+The candidate programs are iteratively refined to eventually satisfy the specification.
+Modern synthesis engines combine automated testing, genetic algorithms, and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}.
+Currently, Abate {\it et al.}~\cite{abate2017} synthesizes stable, software-implemented embedded controllers along with a model of a physical plant for transfer-function~\cite{abate2017}, and recently, also supports for state-space representation~\cite{abatecav2017}.
+
+Notably, there are toolboxes in MATLAB with functions and scripts to facilitate the digital system design and implementation~\cite{matlab-toolbox}.
+In fact, there is a MATLAB Toolbox named as DSVerifier Toolbox~\cite{issta2017} that automatically detect specific errors related to digital system design ({\it e.g.}, stability) using symbolic model checking based on SAT and SMT solvers given the physical plant and the digital controller.
+However, there is no toolbox in MATLAB to perform the digital control synthesis based on Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} considering FWL effects.
+
+The present paper addresses this problem and presents a MATLAB toolbox for DSSynth~\cite{abate2017, abatecav2017} in the MATLAB's environment named as \tool.
+The main advantage regarding the use of a MATLAB toolbox lies on designing physical plants in MATLAB and then promptly synthesizes a stable digital controller.
+Additionally, when using the \tool, an engineer is able to design a digital system with MATLAB, through transfer-function or state-space representations, consider low-level systems parameters (implementation features and numerical format), and then gets a stable synthesized digital-controller.
+
+%---------------------------------------------------
+\section{Synthesizing Digital Controller with \tool}
+%---------------------------------------------------
+
+%---------------------------------------------------
+\subsection{\tool Architecture}
+%---------------------------------------------------
+
+The proposed synthesization methodology for closed-loop digital systems is based on DSSynth~\cite{abate2017, abatecav2017} and it can be split into two main stages as follows: manual (user) and automated (DSSynth) procedures, as shown in Fig.~\ref{fig:synthesis-flow}.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.5\textwidth]{synthesis-flow.pdf}
+\caption{Digital-Control Synthesis Methodology.}
+\label{fig:synthesis-flow}
+\end{figure}
+
+In step $1$, the digital-control representation is determined, and it could be in transfer-function or state-space equations.
+In step $2$, the physical plant with the coefficients must be designed according to equations (\ref{eq:transferfunction}) and (\ref{eq:ss-example}).
+And finally, in step $3$, the numerical representation with the digital-control implementation must be defined, {\it i.e.}, the FWL format that includes the number of bits in the integer and fractional parts and the dynamic range inputs.
+The result from the manual procedure is a digital-system implementation for the given physical plant in MATLAB.
+
+The synthesis process starts in step $A$, when the \tool gets the digital-system in MATLAB, and then translate it in a ANSI-C program, and then in step $B$, the DSSynth Tool is invoked.
+Finally, in step $C$, the digital controller is synthesized based on (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}.
+The output generated in MATLAB is the digital controller synthesized, and it could be represented in transfer-function or state-space format.
+The synthesis is \emph{successful} when a digital controller is synthesized correctly, and the synthesis has status \emph{failed} when any parameter is defined incorrectly in previous steps, or there is no solution for the digital-system designed.
+
+%---------------------------------------------------
+\subsection{\tool Procedures}
+%---------------------------------------------------
+
+The \tool performs the following automated procedures in order to synthesize a digital controller:
+
+\begin{enumerate}
+\item \textbf{Setup}: obtain the plant, fixed-point format and dynamic input ranges, and translate them to a struct in MATLAB;
+\item \textbf{Parse}: obtain the digital plant implementation, and then translate it to an ANSI-C file;
+\item \textbf{Execute}: obtain the ANSI-C file from the previous step, call CBMC-CEGIS as back-end program synthesis tool, and then perform the automated synthesis;
+\item \textbf{Extract}: obtain the .log that is generated after the synthesis phase and then check the synthesized digital-controller.
+\item \textbf{Report}: obtain the digital-controller, translate it to a MATLAB system, and then show the result to the user.
+\end{enumerate}
+
+%---------------------------------------------------
+\subsection{\tool Features}
+%-----------------------------------------------
+
+The \tool's features can be described as follows:
+
+\begin{itemize}
+\item \textbf{Representation}: the synthesis could be performed for digital-systems in transfer-function or state-space equations;
+\item \textbf{Fixed-Point Arithmetic}: the digital controller is synthesized considering FWL effects, in fixed-point numeric representation;
+\item \textbf{Interface}: the synthesis could be executed using the command-line version, and a GUI Application version.
+In addition, in the GUI Application, the user is able to plot the step response in order to reproduce the stability of the digital controller synthesized;
+\end{itemize}
+%---------------------------------------------------
+\subsection{\tool Usage}
+%---------------------------------------------------
+
+%---------------------------------------------------
+\subsubsection{Command Line Version}
+%---------------------------------------------------
+
+Users must provide a digital system described as a MATLAB system  using a \texttt{``tf''} (for transfer-function) or an \texttt{``ss''} (for state-space) command (cf.
+step $1$ of Fig.~\ref{fig:synthesis-flow}).
+
+\tool is called via command line in MATLAB as \texttt{synthesize(plant, intBits, fracBits, maxRange, minRange)}, where \texttt{plant} is the physical plant in state-space or transfer-function representation, \texttt{intBits} is the integer part, \texttt{fracBits} is the fractional part, \texttt{maxRange} and \texttt{minRange} are the maximum and minimum dynamic range, respectively.
+
+After executing \texttt{synthesize} command in MATLAB, the output prints the synthesized digital controller according to the digital system representation, {\it i.e.}, transfer-function or state-space equations.
+
+%---------------------------------------------------
+\subsubsection{MATLAB Application Version} 
+%---------------------------------------------------
+
+A graphical user interface application was developed (Fig.~\ref{fig:gui-for-tf}), in order to favor digital-control systems synthesis in MATLAB, besides improving usability and, consequently, attracting more digital-system engineers.
+Users can provide all required parameters for digital-system synthesization: physical plant specification, fixed-point implementation and dynamic inputs.
+%
+\begin{figure}
+  \includegraphics[width=0.5\textwidth]{screens_dssynth.png}
+  \caption{GUI Application for Transfer-Function Synthesis.}
+  \label{fig:gui-for-tf}
+\end{figure}
+
+%---------------------------------------------------
+\subsection{Illustrative Example}
+%---------------------------------------------------
+
+\textcolor{red}{Lennon, can you please describe an illustrative example here?}
+
+\section{Conclusions}
+
+\tool is able to synthesize dynamic physical plants designed in MATLAB, through transfer-function and state-space representations based on Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}.
+
+Given the current literature in formal synthesis, there is no other MATLAB toolbox for synthesize stable digital systems, while taking into account implementation aspects (fixed-point arithmetic).
+
+As future work, \tool will perform synthesis to generate stable digital controllers and be combined with DSVerifier Toolbox~\cite{issta2017} to verify the stability of the digital controller synthesized, and also, with DSValidator Toolbox~\cite{dsvalidator}, in order to reproduce and validate the stability property.
 

### 2017-05-29 automatica/automatica.tex
Continuous time proofs

@@
 \newtheorem{theorem}{Theorem}
+\newtheorem{corollary}{Corollary}
 \newtheorem{proof}{Proof}
@@
 \textcolor{red}{Elizabeth: we need to define the notation used throughout the paper.}
+
+%-------------------------------
+\subsection{Abstract Acceleration} 
+\label{ssec:aa}
+%-------------------------------
+For abstraction based synthesis, we will use Abstract Acceleration~\cite{JSS14,cattaruzza2015unbounded}.
+Given an iterative program with dynamics
+\begin{equation}
+\vec{x}_{k+1}=\mat{A}\vec{x}_k : \vec{x}_k \in \mathbb{R}^n \wedge \mat{A} \in \mathbb{R}^{n \times n} \wedge k \in [0\ \ \infty),
+\end{equation}
+we want to find all possible states visited over an infinite time horizon starting at an initial set $X_0$. We call this set the \emph{reach tube} of the model:
+\begin{equation}
+\hat{X} = \{ \vec{x}_k : k \in [0\ \infty) \wedge \vec{x}_0 \in X_0 \wedge \vec{x}_{k+1}=\mat{A}\vec{x}_k\}.
+\end{equation}
+It is easy to see that the infinite number of iterations would result in an unbounded cumulative rounding error, but using Abstract Acceleration we transform this problem into a one-step solution.
+We first change the problem statement by means of acceleration into 
+\begin{equation}
+\hat{X} = \{ \vec{x}_k=\mat{A}^k\vec{x}_0 : k \in [0\ \infty) \wedge \vec{x}_0 \in X_0 \}, 
+\end{equation}
+and further define new model semantics and corresponding set: 
+\begin{equation}\label{eq:aa_reachtube}
+\hat{X} \subseteq \hat{X}^\sharp = \mathcal{A}X_0, \text{ such that } \bigcup_{k \in [0\ \infty)} \mat{A}^k \subseteq \mathcal{A}, 
+\end{equation}
+where the newly introduced \emph{abstract reach tube} $\hat{X}^\sharp$ is an over-approximation of the reach tube of the model \cite{JSS14}.
+All we need to do is define the nature of $\mathcal{A}X_0$.
+
+Let $\mat{S}\mat{J}\mat{S}^{-1}=\mat{A}$ be the eigen-decomposition of
+$\mat{A}$, where $\mat{S}$ is the set of generalised eigenvectors of
+$\mat{A}$ and $\mat{J}$ is the Jordan Form containing the eigenvalues of
+$\mat{A}$ in its main diagonal.  We correspondingly define
+$\mathcal{J}=\mat{S}^{-1}\mathcal{A}\mat{S}$, which is such that $\mathcal{J} \supseteq \bigcup_{k \in [0\
+\infty)} \mat{J}^k$.
+
+Introduce set $X=\{ \vec{x} : \mat{C}\vec{x} \leq \vec{d}\}$. 
+The linear transformation $\vec{x}'=\mat{S}^{-1}\vec{x}$ leads to set 
+\begin{equation}
+X'= \mat{S}^{-1}X = \{\vec{x}' : \mat{C}\mat{S}\vec{x}'\leq \vec{d}\}.  
+\label{eq:eigenInit}
+\end{equation}
+Analogously, 
+let $X_0'=\mat{S}^{-1}X_0$ and ${\hat{X}'^\sharp}=\mat{S}^{-1}{\hat{X}^\sharp}$ be the initial set and the abstract reach tube mapped onto the eigenspace of matrix $\mat{A}$. 
+We may transform equation \eqref{eq:aa_reachtube} into:
+\begin{equation}
+\hat{X}' \subseteq {\hat{X}'^\sharp} = \mathcal{J}X_0', \text{ such that } \bigcup_{k \in [0\ \ \infty)}\mat{J}^k \subseteq \mathcal{J}, 
+\end{equation}
+where $\hat{X}'=\mat{S}^{-1}\hat{X}$ and $\mathcal{J}$ is a convex polyhedron representing restrictions on the eigenvalues of $\mat{A}$.
+$\hat{X}'^\sharp$ is calculated by applying a simplex algorithm with a tableau defined by $\mathcal{J}$ and objective functions derived from each vertex of $X_0'$ (step \eqref{alg:getReachTube} in Algorithm \ref{alg:findReachTube} below).
+We note, however, that if we wish to use numerical analysis in the decomposition of $\mat{A}$, 
+the Tableau in $\mathcal{J}$ contains small intervals given by the errors, which cannot be processed efficiently by a regular simplex and require a new procedure.
+
+The calculation of the abstract reach tube via abstract acceleration is encompassed in Algorithm \ref{alg:findReachTube}, 
+which can be summarised as follows (its steps are denoted in parentheses):
+%
+\begin{enumerate}
+\item We perform unsound eigen-decomposition using an existing algebra package (lines \ref{alg:calcEigenvalues}-\ref{alg:calcEigenvectors}).
+\item Then we restore soundness to the results using the methods described in Section \ref{sec:eigensolver} (lines \ref{alg:soundEigenvalues}-\ref{alg:soundEigenvectors}). 
+\item The inverse of the matrix of eigenvectors is calculated after soundness is restored, using interval arithmetic in order to ensure its soundness (line \ref{alg:inverse}).
+\item The abstract dynamics are obtained by evaluating the convex hull of all powers of eigenvalues up to the desired number of iterations as described in \cite{cattaruzza2015unbounded} (line \ref{alg:aa}).
+\item Using Equation \eqref{eq:eigenInit}, transform the initial state into the eigenspace (line \ref{alg:eigeninit}).
+\item Extract the vertices of the eigen-polyhedron $X_0'$ using the sound over-approximation of the double description algorithm \cite{fukuda1996double} from Section \ref{sec:dd} (line \ref{alg:getVertices}).
+It is worth noting that this algorithm uses a simplex to seed it: we will first discuss the simplex algorithm, which is also needed at the next step, and then the vertex enumeration algorithm used at this stage.
+\item Calculate the mapped \emph{abstract reach tube} ${\hat{X}'^\sharp}$ that over-approximates the image of the reach tube in the eigenspace (line \ref{alg:getReachTube}).
+This is achieved by evaluating a set of objective functions using the abstract dynamics as a simplex Tableau,
+and via a sound simplex described in Section \ref{sec:simplex}. 
+The objective functions are defined by the vertices of $X'_0$, 
+denote as $V_0$, 
+and by the desired template directions, 
+such that 
+\begin{equation*}
+\vec{w}_{ij}= \vec{v}_i \circ \vec{t}_j : \vec{v}_i \in V_0 \wedge \vec{t}_j \in T,
+\end{equation*}
+where $T$ is the set of template directions, and $\circ$ denotes a component-wise multiplication yielding a vector. 
+\item Using Equation \eqref{eq:eigenInit}, find the reach tube $\hat{X}^\sharp=\mat{S}{\hat{X}'^\sharp}$ (line \ref{alg:getNormReachTube}).
+\end{enumerate}
+
+\begin{algorithm}[]
+\small
+\begin{algorithmic}[1]
+\Function{$\mathit{findAbstractReachTube}()$}{}
+\State $\hat{\mat{J}}=$ calculateEigenvalues($ \mat{A}$)
+\label{alg:calcEigenvalues}
+\State $\hat{\mat{S}}=$ calculateEigenvectors($ \mat{A}$)
+\label{alg:calcEigenvectors}
+\State $[\mat{J}]=$ soundifyEigenvalues($\mat{A},\mat{J},\mat{S}$)
+\label{alg:soundEigenvalues}
+\State $[\mat{S}]=$ soundifyEigenvectors($\mat{A},[\mat{J}],\mat{S}$)
+\label{alg:soundEigenvectors}
+\State $[\mat{S}]^{-1}=$ calculateInverse($[\mat{S}]$)
+\label{alg:inverse}
+\State $\mathcal{J}=getAbstractDynamics([\mat{J}])$
+\label{alg:aa}
+\State $[X_0']=$ transformInitialSpace($X_0,\mat{S}$)
+\label{alg:eigeninit}
+\State $[V_0]=$ getVertices($[X_0']$)
+\label{alg:getVertices}
+\State ${\hat{X}'^\sharp}=$ getReachTube($\mathcal{J},[V_0]$)
+\label{alg:getReachTube}
+\State ${\hat{X}^\sharp}=$ transformReachTube(${\hat{X}'^\sharp},[\mat{S}]^{-1}$)
+\label{alg:getNormReachTube}
+\EndFunction
+\end{algorithmic}
+\caption{Calculation of Abstract Reach Tube Using Abstract Acceleration}
+\label{alg:findReachTube}
+\end{algorithm}
+
+%-------------------------------
+ \subsection{Overapproximating continuous time dynamics using discrete models}
+ \label{sec:cont_aa}
+%-------------------------------
+Thus far we wave discussed the Abstract Accelertion of Discrete Time systems. However, our plant models derive
+from the discretization of continuous time systems. We therefore seek to establish a sound
+overapproximation which does not only encompass the selected discretization, but any chosen discretization in the 
+time domain.
+
+%-------------------------------
+ \subsubsection{A discrete time model using reals}
+ \label{sec:real_aa}
+%-------------------------------
+
+ \begin{theorem}
+ The expression
+ \begin{align}
+ \vec{x}_k&=\vec{x}(t=k)=\mat{A}_k\vec{x}_0 : \dot{\vec{x}}=\mat{A}\vec{x} \wedge \mat{A}=\mat{S}\mat{J}\mat{S}^{-1}\\
+ \mat{A}_k&= \mat{S}
+ \left [ \begin{array}{cccc}
+ e^{k\lambda_i}  & s_i\frac{k^{j-i}e^{k\lambda_i}}{(j-i)!} & \hdots  & s_i\frac{k^{p-i}e^{k\lambda_i}}{(p-i)!} \\
+0 & e^{k\lambda_i}  & s_i\frac{k^{j-i}e^{k\lambda_i}}{(j-i)!} & \vdots \\
+\vdots & & \ddots & \vdots \\
+0 & \cdots & 0  &e^{k\lambda_i} \\
+\end{array} \right ]
+ \mat{S}^{-1}: s_i=\left\{\begin{array}{cc}1&gm(\lambda_i)>1\\0&gm(\lambda_i)=1\end{array}\right.
+ \label{eq:continuous_tube_dyn}
+ \end{align}
+ where $\lambda_i \in \mat{J}$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$ is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}$ at time t=k.
+ \end{theorem}
+ \begin{corollary}
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x} : k \in (0,\infty)$ is a witness of the system at time $t=kT_d$.
+ \end{corollary}
+ \begin{proof}
+ Let us recall equation \ref{eq:discretize}. The discrete representation of the system dynamics discretized with sample time $T_1$ is ruled by the formula
+ $\mat{A}_1 = e^{\mat{A} T_1}$. From matrix theory, we have 
+\begin{align}
+ e^{\mat{A}}&=\sum_{k=0}^\infty \frac{1}{k!}\mat{A}^k
+\end{align} 
+\begin{align} 
+ e^{\mat{S}\mat{J}\mat{S}^{-1}}&=\sum_{k=0}^\infty \frac{1}{k!}(\mat{S}\mat{J}\mat{S}^{-1})^k
+ =\mat{S} \left (\sum_{k=0}^\infty \frac{1}{k!}\mat{J}^k\right) \mat{S}^{-1}
+ =\mat{S}e^{\mat{J}}\mat{S}^{-1}
+\end{align} 
+\begin{equation}
+\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \Rightarrow \vec{A}_1 = \mat{S}\mat{J}_1\mat{S}^{-1}= \mat{S}e^{\mat{J} T_1}\mat{S}^{-1}.
+ \end{equation}
+
+ Let $\mat{J}$ be a diagonal matrix, such that 
+ $${\lambda_1}_i=e^{\lambda_i T_1}, \forall \lambda_i \in \mat{J}.$$
+ Let us now take a different sample rate $T_2$, such that 
+ $${\lambda_2}_i=e^{\lambda_i T_2}, \forall \lambda_i \in \mat{J}.$$
+ We can then say that 
+ \begin{equation}
+ {\lambda_2}_i=e^{\lambda_i T_1 \frac{T_2}{T_1}}={\lambda_1}_i^{\frac{T_2}{T_1}} \Rightarrow A_2=A_1^{\frac{T_2}{T_1}}.
+ \end{equation}
+ This proves the theorem for $gm(\lambda_i)=1$.
+ We now note that given an exponentiated Jordan form with geometric multiplicity, the upper diagonal terms can be
+ referenced to the original eigenvalues modified by the sampling rate.
+  Let $\mat{J}\in \mathbb{R}^{p \times p}$ be a Jordan Canonical matrix. Then
+\begin{align}
+\tiny
+ \mat{J}_1=&\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{J}T_1\right)^k\nonumber\\
+\tiny
+=&\sum_{k=0}^\infty \frac{1}{k!} \left [ \begin{array}{cccc}
+ \lambda_i^k  & \binom{k}{1}  \lambda^{k-1} & \hdots  & \binom{k}{p-1} \lambda_i^{k-p+1} \\
+& \lambda_i^k  & \binom{k}{1}  \lambda_i^{k-1} & \vdots \\
+\vdots & \ddots & \ddots & \vdots \\
+& &  &\lambda_i^k \\
+\end{array} \right ] T_1^k
+\end{align}
+The eigenvalues remain the same as in the diagonal case, but the upper triangular terms are of the form:
+\begin{align}
+\forall j>i, c_{ij}&=\sum_{k=j-i}^\infty \frac{1}{k!}\binom{k}{j-i} \lambda_i^{k-(j-i)}T_1^k\\
+&=\frac{1}{(j-i)!}\sum_{k=j-i}^\infty \frac{1}{(k-(j-i))!} \lambda_i^{k-(j-i)}T_1^k\nonumber\\
+&=\frac{T_1^{j-i}e^{\lambda_i T_1}}{(j-i)!}\nonumber
+\end{align}
+which completes the proof for $gm(\lambda_i)>1$.
+\end{proof}
+
+%-------------------------------
+ \subsubsection{Finding Abstract Supports for Continuous Dynamics}
+ \label{sec:cont_aasup}
+%-------------------------------
+
+In the case of Discrete dynamics, support functions can be found by evaluating hyperplanes of consecutive exponents of the eigenvalues using differences.
+In the case of continuous time, this translates to calculating derivatives. Once again, when the sets are known to be convex,
+we may calculate the normal vector to this derivative and evaluate its support function on the selected iteration.
+The direction of the vector is determined by evaluating the support function of another point in the curve, which is known to be smaller than that of the selected point.
+The corresponding derivatives are:
+\begin{enumerate}
+\item for real eigenvalues: we first calculate the slope of the tangent between the two progressions: $\frac{d f(k)}{d g(k)}=\frac{f'(k)}{g'(k)}$.
+Hence $\frac{d \lambda_1^k}{d \lambda_2^k}=\frac{log(\lambda_1) \lambda_1^k}{log(\lambda_2) \lambda_2^k}$.
+From this we know that the polar angle of the support vector is $\psi = \tan^{-1}(\frac{log(\lambda_1) \lambda_1^k}{log(\lambda_2) \lambda_2^k})+\frac{\pi}{2}$
+\item for conjugate eigenvalue pairs: the pair forms a logarithmic spiral.
+The tangent of a spiral with polar equation $r=a e^{b\theta}$ will have a derivative $\frac{d r}{d \theta}=b a e^{b\theta}=b r$, hence the angle of the vector normal to the curve is $\tan^{-1}(\frac{r}{\frac{d r}{d \theta}})+\frac{\pi}{2}=\tan^{-1}(\frac{1}{b})+\frac{\pi}{2}$
+\item for Jordan blocks with $gm>1$: in the case of real eigenvalues, we follow the same procedure as in the real case, but considering that the equation for each eigenvalue is $\frac{k^j}{j!}e^{\lambda k}$ where $j$ is the index of the term within the Jordan block (note that when $j=0$ the term is the same as for real eigenvalues above).
+The derivatives f'(k),g'(k) are in the form $(j+k*log(\lambda))\frac{k^{j-1}}{j!}e^{\lambda k}$.
+\item for any combination of complex eigenvalues we use the above equations using the envelope of their magnitude (ie $|\lambda|$).
+\end{enumerate}
 
@@
 where all members are known, we may now synthesise coefficients that ensure the eigenvalues are smaller than a desired magnitue, thus ensuring that the settling time is too.
-%-------------------------------
+%---------------janus----------------
 \section{CEGIS of digital control system with transient specifications}

### 2017-05-29 emsoft2017/emsoft-paper.tex
added illustrative example

@@
 \usepackage{xspace,framed}
+\usepackage{listings}
 
@@
 
-\title{DSSynth Toolbox: Automated Synthesis of Digital Controllers \\ for Physical Plants via MATLAB Toolbox}
+\title{DSSynth: An Automated Synthesis Tool of Digital Controllers \\ for Physical Plants via MATLAB Toolbox}
 
@@
 
-\textcolor{red}{Lennon, can you please describe an illustrative example here?}
+To illustrate the \tool's usage, Fig.~\ref{toolbox-usage} shows the synthesis for a physical plant defined in Eq.(~\ref{equation_plant}) using the transfer-function representation, where ``num'' and ``den'' represent the numerator $A(z)$ and denominator $B(z)$, respectively.
+%
+\begin{equation}
+\label{equation_plant}
+H(z)=\frac{B(z)}{A(z)}=\frac{-0.06875z^{2}}{z^2-1.696z+0.7089},
+\end{equation}
+%
+\begin{figure}[ht]
+\scriptsize
+\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
+>> num = [-0.06875 0 0];
+>> den = [1.0000 -1.696 0.7089];
+>> system = tf(num,den,0.002);
+>> y = synthesize(system,8,8,1,-1);
+>> SYNTHESIS SUCCESSFUL
+>> y = (-0.9983z^2 + 0.09587z + 0.1926)/(z^2+0.5665+0.75);
+\end{lstlisting}
+\vspace{-0.2cm}
+\caption{Synthesis of a Digital Controller for the physical plant defined in Eq.(~\ref{equation_plant}) in MATLAB, with a fixed-point format  $\left\langle 8,8\right\rangle$.}
+\label{toolbox-usage}
+\end{figure}
+%
+In the Fig.~\ref{toolbox-usage}, the value returned in $y$ represents the digital controller synthesized and stable.
+In order to validate and reproduce the stability in the digital system composed by the physical plant defined in Eq.(~\ref{equation_plant}) and the digital controller represented by $y$, the user can invoke the step response using the command \texttt{dstep}, and then observe that the graph plotted shows a stable digital system, as can be seen in Fig.~\ref{step-response}.
+%
+\begin{figure}[ht]
+  \includegraphics[width=0.5\textwidth]{step-response.eps}
+  \caption{Step response for the Eq.~\eqref{equation_plant} describing a stable system.}
+  \label{step-response}
+\end{figure}
 

### 2017-05-29 emsoft2017/plot_step_response.m

@@ -1,0 +1,12 @@
+num = [-0.06875 0 0];
+den = [1.0000 -1.696 0.7089];
+plant = tf(num,den,0.002);
+controller = tf([-0.9983 0.09587 0.1926], [1 0.5665 0.75], 0.002);
+
+syscl = feedback(series(plant,controller),1);
+
+num_cl = cell2mat(syscl.Numerator);
+den_cl = cell2mat(syscl.Denominator);
+
+dstep(num_cl,den_cl)
+set(findall(gcf,'-property','FontSize'),'FontSize',30)

### 2017-05-30 automatica/automatica.tex
nudge to continuous time proof

@@
  \begin{align}
- \vec{x}_k&=\vec{x}(t=k)=\mat{A}_k\vec{x}_0 : \dot{\vec{x}}=\mat{A}\vec{x} \wedge \mat{A}=\mat{S}\mat{J}\mat{S}^{-1}\\
- \mat{A}_k&= \mat{S}
+ \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x}_0 : \dot{\vec{x}}=\mat{A}\vec{x} \wedge \mat{A}=\mat{S}\mat{J}\mat{S}^{-1}\nonumber\\
+ \mat{A}_{T}&= \mat{S}
  \left [ \begin{array}{cccc}
- e^{k\lambda_i}  & s_i\frac{k^{j-i}e^{k\lambda_i}}{(j-i)!} & \hdots  & s_i\frac{k^{p-i}e^{k\lambda_i}}{(p-i)!} \\
-0 & e^{k\lambda_i}  & s_i\frac{k^{j-i}e^{k\lambda_i}}{(j-i)!} & \vdots \\
+ e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \hdots  & s_i\frac{T^{p-i}e^{T\lambda_i}}{(p-i)!} \\
+0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
 \vdots & & \ddots & \vdots \\
-0 & \cdots & 0  &e^{k\lambda_i} \\
+0 & \cdots & 0  &e^{T\lambda_i} \\
 \end{array} \right ]
- \mat{S}^{-1}: s_i=\left\{\begin{array}{cc}1&gm(\lambda_i)>1\\0&gm(\lambda_i)=1\end{array}\right.
+ \mat{S}^{-1}\nonumber\\
+ s_i&=\left\{\begin{array}{cc}1&gm(\lambda_i)>1\\0&gm(\lambda_i)=1\end{array}\right.
  \label{eq:continuous_tube_dyn}
  \end{align}
- where $\lambda_i \in \mat{J}$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$ is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}$ at time t=k.
+ where $\lambda_i \in \mat{J}$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$ is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}$ at time t=T.
  \end{theorem}
@@
  referenced to the original eigenvalues modified by the sampling rate.
-  Let $\mat{J}\in \mathbb{R}^{p \times p}$ be a Jordan Canonical matrix. Then
+  Let $\mat{J}\in \mathbb{R}^{p \times p}$ be a Jordan Canonical matrix whose powers are described in Equation \eqref{jord:pow}
+ Then
 \begin{align}
-\tiny
- \mat{J}_1=&\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{J}T_1\right)^k\nonumber\\
-\tiny
-=&\sum_{k=0}^\infty \frac{1}{k!} \left [ \begin{array}{cccc}
+ \mat{J}_1=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{J}T_1\right)^k=
+&\sum_{k=0}^\infty \frac{1}{k!} \left [ \begin{array}{cccc}
  \lambda_i^k  & \binom{k}{1}  \lambda^{k-1} & \hdots  & \binom{k}{p-1} \lambda_i^{k-p+1} \\

### 2017-05-31 emsoft2017/emsoft-paper.tex
updated EMSOFT'17 title
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
reviewed abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\title{DSSynth: An Automated Synthesis Tool of Digital Controllers \\ for Physical Plants via MATLAB Toolbox}
+\title{DSSynth: An Automated Synthesis Tool for Physical Plants \\ Digital Controllers via MATLAB Toolbox}
 
 \begin{abstract}
-We present an automated approach implemented as a MATLAB Toolbox to synthesize stable and safe digital-control systems for physical plants represented as linear and time invariant models.
-The tool developed in the current paper is named as DSSynth (Digital-Systems Synthesis), which is a MATLAB Toolbox that synthesizes digital controllers w.r.t.
-the stability specification, considering finite word-length (FWL) effects for physical plants represented by transfer-function or state-space equations.
-DSSynth considers fixed-point numerical representation for the digital controller and dynamic input ranges for the closed-loop control system.
-Currently, there are two versions of the DSSynth toolbox: command-line and MATLAB application.
+We present an automated MATLAB Toolbox, named as DSSynth 
+(Digital System Synthesis), to synthesize stable and safe digital-control 
+systems for physical plants represented as linear time-invariant
+systems with single-input and single-output. DSSynth synthesizes digital 
+controllers w.r.t. the stability and safety specifications, considering finite word-length 
+effects for physical plants represented by transfer-function or state-space 
+equations. DSSynth considers fixed-point numerical representation for the 
+digital controller and dynamic input ranges for the closed-loop control system. 
+Currently, there are two DSSynth toolbox versions: command-line and 
+MATLAB application. The resulting toolbox enables application of synthesis to 
+real-world systems by control engineers.
 \end{abstract}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{synthesis-flow.pdf}
+\includegraphics[width=0.45\textwidth]{synthesis-flow.pdf}
 \caption{Digital-Control Synthesis Methodology.}

### 2017-05-31 emsoft2017/emsoft-paper.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-%There are many application of embedded systems with low-cost devices that can perform non-trival tasks, such as UAV (Unmanned Aerial Vehicles) approach that could be used in various application (civil and millitary) that requires a reliable operation in order to avoid crashes and malfunctioning~\cite{williams2006human}.
-Synthesis of controllers for LTI (Linear Time Invariant) systems is broadly investigated, however the use of digital control architectures adds new challenges due to the effects of finite-precision arithmetic, time discretization, and quantization noise, which are typically introduced by Analogue-to-Digital (ADC) and Digital-to-Analogue (DAC) conversion~\cite{astrom1997computer}.
+Linear-Time Invariant (LTI) systems are used in several applications
+to support non-trivial tasks when applied to embedded systems 
+(e.g., robot manipulator, power plants and guidance system). 
+In addition, controllers synthesis for LTI systems is richly studied 
+by different researchers; however, there are many challenges when 
+digital-control systems theory is used due to the effects of finite-word 
+length (FWL)~\cite{Guang2013, Istepanian2001}, time discretization 
+and quantization noise, which are typically introduced by Analogue-to-Digital 
+(ADC) and Digital-to-Analogue (DAC) conversion, which can lead to several 
+quantization problems, such as truncation or round-off errors~\cite{astrom1997computer}.
 
-%In addition, embedded systems present a lot of advantages, if compared with analog ones, such as more flexibility, scalability, adaptability, and lower implementation cost.
-However, embedded systems are expressed as digital-control systems which are vulnerable to finite word-length (FWL) effects~\cite{Guang2013, Istepanian2001}, that can cause several quantization problems, such as truncation or round-off errors.
-
-Linear Time Invariant (LTI) systems are concepts that are used in many applications in order to support non-trivial tasks when applied in embedded systems.
-In addition, synthesis of controllers for LTI systems is richly studied by different researchers, however there are many challenges when digital-control systems theory is used due to the effects of finite-word length (FWL)~\cite{Guang2013, Istepanian2001}, time discretization, and quantization noise, which are typically introduced by Analogue-to-Digital (ADC) and Digital-to-Analogue (DAC) conversion, that can cause several quantization problems, such as truncation or round-off errors.~\cite{astrom1997computer}.
-
-Digital-control systems are computations that manipulate digital signals, in order to influence the behavior of a system~\cite{Ogata2001}; it can be mathematically expressed as difference equations, transfer functions, or state-space equations.
-In this particular work, the focus is on transfer-function and state-space representation.
-The following expression presents the general form of a digital-control system in transfer function format:
+Embedded digital control systems perform computations over digital signals 
+to influence the system behavior~\cite{Ogata2001}; it can be mathematically 
+expressed as difference equations, transfer functions or state-space equations. 
+Here, the focus is on transfer-function and state-space representations. 
+The following expression presents the general form of a digital control system 
+using the transfer function representation:
 %
@@
 %
-where $z^{-1}$ is called backward-shift operator, $A(z)$ and $B(z)$ are the denominator and numerator polynomials, respectively.
+\noindent where $z^{-1}$ is called backward-shift operator, $A(z)$ and $B(z)$ are 
+the denominator and numerator polynomials, respectively.
 
-In state-space format, the digital-control system represents the behavior of a system through a state evolution equation $\dot{x}(n+1)$ and an instantaneous output equation $y(n)$, as follows:
-
+In state-space format, the digital control system represents the behavior 
+of a system via a state evolution equation $\dot{x}(n+1)$ and an instantaneous 
+output equation $y(n)$, as follows:
+%
 \begin{equation}
@@
 
-%Recently, Bessa {\it et al.}~\cite{daes20161} has studied the stability of digital controllers considering implementation aspects, i.e., fixed-point arithmetic and the word length wich performs a model checking procedure based on satisfiability modulo theories (SMT) named as Digital-System Verifier (DSVerifier)~\cite{dsverifier}.
-While research on digital controller is well developed~\cite{astrom1997computer}, automated and sound control synthesis is challenging, particularly when the synthesis objective goes beyond classical stability.
+\noindent where A, B, C and D are matrices that fully specify a digital system.
 
-Recently, a new methodology to synthesize digital-control systems was designed, named as DSSynth (Digital-System Synthesizer)~\cite{abate2017, abatecav2017}, which is based on Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} that are able to generate programs for highly non-trivial specifications with a very high degree of automation.
-Program synthesis engines use a specification as the starting point, and subsequently generate a sequence of candidate programs from a given template.
-The candidate programs are iteratively refined to eventually satisfy the specification.
-Modern synthesis engines combine automated testing, genetic algorithms, and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}.
-Currently, Abate {\it et al.}~\cite{abate2017} synthesizes stable, software-implemented embedded controllers along with a model of a physical plant for transfer-function~\cite{abate2017}, and recently, also supports for state-space representation~\cite{abatecav2017}.
+Recently, a new methodology to synthesize digital-control systems was proposed, 
+named as DSSynth (Digital System Synthesis)~\cite{abate2017, abatecav2017}, 
+which is based on Counter-Example Guided Inductive Synthesis 
+(CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} able to produce programs 
+for highly non-trivial specifications with a very high degree of automation. 
+Program synthesis engines use a specification as the starting point, and subsequently 
+produce a sequence of candidate programs from a given template. The candidate programs 
+are iteratively refined to eventually satisfy the specification. Modern synthesis engines combine 
+automated testing, genetic algorithms and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
+Currently, Abate {\it et al.}~\cite{abate2017} synthesize stable, software-implemented 
+embedded controllers along with a model of a physical plant for transfer-function~\cite{abate2017}, 
+and recently, they also support state-space representation~\cite{abatecav2017}.
 
-Notably, there are toolboxes in MATLAB with functions and scripts to facilitate the digital system design and implementation~\cite{matlab-toolbox}.
-In fact, there is a MATLAB Toolbox named as DSVerifier Toolbox~\cite{issta2017} that automatically detect specific errors related to digital system design ({\it e.g.}, stability) using symbolic model checking based on SAT and SMT solvers given the physical plant and the digital controller.
-However, there is no toolbox in MATLAB to perform the digital control synthesis based on Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} considering FWL effects.
+Notably, there are toolboxes in MATLAB with functions and scripts to facilitate the 
+digital system design and implementation~\cite{matlab-toolbox}. In fact, there is a MATLAB 
+Toolbox named as DSVerifier Toolbox~\cite{issta2017}, which automatically detects 
+specific errors related to digital system design ({\it e.g.}, stability, limit cycle and overflow) 
+using symbolic model checking techniques based on Boolean Satisfiability (SAT) and 
+Satisfiability Modulo Theories (SMT) solvers, given the physical plant and the digital controller. 
+However, there is no toolbox in MATLAB to perform digital control synthesis; in particular, based on 
+CEGIS considering FWL effects.
 
-The present paper addresses this problem and presents a MATLAB toolbox for DSSynth~\cite{abate2017, abatecav2017} in the MATLAB's environment named as \tool.
-The main advantage regarding the use of a MATLAB toolbox lies on designing physical plants in MATLAB and then promptly synthesizes a stable digital controller.
-Additionally, when using the \tool, an engineer is able to design a digital system with MATLAB, through transfer-function or state-space representations, consider low-level systems parameters (implementation features and numerical format), and then gets a stable synthesized digital-controller.
+The present paper addresses this problem and describes a MATLAB toolbox for DSSynth~\cite{abate2017, abatecav2017} 
+in MATLAB's environment named as \tool. The main advantage regarding the use of a MATLAB toolbox 
+lies on designing physical plants in MATLAB and then promptly synthesizing a stable digital controller. 
+Additionally, when using the \tool, an engineer is able to design a digital system with MATLAB, 
+through transfer-function or state-space representations, consider low-level systems parameters 
+(implementation features and numerical format), and then gets a stable synthesized digital-controller.
 

### 2017-05-31 emsoft2017/emsoft-paper.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 In addition, controllers synthesis for LTI systems is richly studied 
-by different researchers; however, there are many challenges when 
-digital-control systems theory is used due to the effects of finite-word 
-length (FWL)~\cite{Guang2013, Istepanian2001}, time discretization 
+by different researchers~\cite{mazo2010pessoa,DBLP:conf/emsoft/RavanbakhshS16,economakos2016automated}; 
+however, there are many challenges when 
+digital-control systems theory is used due to the finite-word 
+length (FWL) effects~\cite{Guang2013, Istepanian2001}, time discretization 
 and quantization noise, which are typically introduced by Analogue-to-Digital 
-(ADC) and Digital-to-Analogue (DAC) conversion, which can lead to several 
-quantization problems, such as truncation or round-off errors~\cite{astrom1997computer}.
+(ADC) and Digital-to-Analogue (DAC) conversion, leading to truncation 
+or round-off errors~\cite{astrom1997computer}.
 
@@
 the denominator and numerator polynomials, respectively.
-
+%
 In state-space format, the digital control system represents the behavior 
@@
 
-\noindent where A, B, C and D are matrices that fully specify a digital system.
+\noindent where $A$, $B$, $C$ and $D$ are matrices that fully specify a digital system.
 
@@
 named as DSSynth (Digital System Synthesis)~\cite{abate2017, abatecav2017}, 
-which is based on Counter-Example Guided Inductive Synthesis 
-(CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} able to produce programs 
-for highly non-trivial specifications with a very high degree of automation. 
-Program synthesis engines use a specification as the starting point, and subsequently 
+which is based on the Counter-Example Guided Inductive Synthesis 
+(CEGIS) approach~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. Here, CEGIS is used
+as a program synthesis engine able to produce controllers for highly non-trivial 
+specifications with a very high degree of automation. Program synthesis engines 
+as CEGIS use a specification as the starting point, and subsequently 
 produce a sequence of candidate programs from a given template. The candidate programs 
@@
 Currently, Abate {\it et al.}~\cite{abate2017} synthesize stable, software-implemented 
-embedded controllers along with a model of a physical plant for transfer-function~\cite{abate2017}, 
-and recently, they also support state-space representation~\cite{abatecav2017}.
+embedded controllers, along with a physical plant model represented by transfer functions 
+or state-space equations~\cite{abate2017,abatecav2017} using a CEGIS-based approach.
 

### 2017-05-31 emsoft2017/emsoft-paper.tex
reviewed section 2.1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\keywords{Formal Synthesis, Digital Controllers, MATLAB Toolbox, Fixed-point Arithmetic, Transfer-Function, State-Space, Digital Control Synthesis}
+\keywords{Formal Synthesis; Digital Control Systems; MATLAB Toolbox; Finite-Word Length; Verification}
 
@@
 %---------------------------------------------------
-\section{Synthesizing Digital Controller with \tool}
+\section{Synthesizing Digital Controllers with \tool}
 %---------------------------------------------------
@@
 
-The proposed synthesization methodology for closed-loop digital systems is based on DSSynth~\cite{abate2017, abatecav2017} and it can be split into two main stages as follows: manual (user) and automated (DSSynth) procedures, as shown in Fig.~\ref{fig:synthesis-flow}.
-
+The proposed synthesis methodology for closed-loop digital control
+systems is based on the DSSynth tool~\cite{abate2017, abatecav2017}; 
+it can be split into two main stages as follows: manual (user) and 
+automated (DSSynth) procedures, as illustrated in Fig.~\ref{fig:synthesis-flow}. 
+%
 \begin{figure}[ht!]
@@
 \includegraphics[width=0.45\textwidth]{synthesis-flow.pdf}
-\caption{Digital-Control Synthesis Methodology.}
+\caption{Digital Controller Synthesis Methodology.}
 \label{fig:synthesis-flow}
@@
 
-In step $1$, the digital-control representation is determined, and it could be in transfer-function or state-space equations.
-In step $2$, the physical plant with the coefficients must be designed according to equations (\ref{eq:transferfunction}) and (\ref{eq:ss-example}).
-And finally, in step $3$, the numerical representation with the digital-control implementation must be defined, {\it i.e.}, the FWL format that includes the number of bits in the integer and fractional parts and the dynamic range inputs.
-The result from the manual procedure is a digital-system implementation for the given physical plant in MATLAB.
+In step $1$, the digital-control representation is define, which can be in 
+transfer-function or state-space equations. In step $2$, the physical plant 
+with the respective coefficients must be designed, according to equations 
+(\ref{eq:transferfunction}) and (\ref{eq:ss-example}). And finally, in step $3$, 
+the numerical representation for the digital controller implementation must be 
+defined, {\it i.e.}, the FWL format that includes the number of bits for the integer 
+and fractional parts and the dynamic range inputs. The results from the manual 
+procedure is a digital-system implementation for the given physical plant in MATLAB.
 
-The synthesis process starts in step $A$, when the \tool gets the digital-system in MATLAB, and then translate it in a ANSI-C program, and then in step $B$, the DSSynth Tool is invoked.
-Finally, in step $C$, the digital controller is synthesized based on (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}.
-The output generated in MATLAB is the digital controller synthesized, and it could be represented in transfer-function or state-space format.
-The synthesis is \emph{successful} when a digital controller is synthesized correctly, and the synthesis has status \emph{failed} when any parameter is defined incorrectly in previous steps, or there is no solution for the digital-system designed.
+The synthesis process starts in step $A$, when the \tool gets the digital-system in MATLAB, 
+and then translates it into a ANSI-C program; then in step $B$, the DSSynth Tool is invoked. 
+Finally, in step $C$, the digital controller is synthesized based on CEGIS. The output generated 
+in MATLAB is the synthesized digital controller, which can be represented in transfer-function 
+or state-space format. The synthesis is \emph{successful} if a digital controller is correctly synthesized;
+otherwise the synthesis has status \emph{failed} if any parameter is defined incorrectly 
+in previous steps, or there is no solution for the designed digital controller.
 

### 2017-05-31 emsoft2017/emsoft-paper.tex
reviewed section 2.1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 The proposed synthesis methodology for closed-loop digital control
-systems is based on the DSSynth tool~\cite{abate2017, abatecav2017}; 
-it can be split into two main stages as follows: manual (user) and 
+systems is based on the DSSynth tool~\cite{abate2017, abatecav2017}, 
+which can be split into two main stages as follows: manual (user) and 
 automated (DSSynth) procedures, as illustrated in Fig.~\ref{fig:synthesis-flow}. 
@@
 
-In step $1$, the digital-control representation is define, which can be in 
-transfer-function or state-space equations. In step $2$, the physical plant 
-with the respective coefficients must be designed, according to equations 
-(\ref{eq:transferfunction}) and (\ref{eq:ss-example}). And finally, in step $3$, 
+In step $1$, the user has to define the digital controller representation, 
+which can be transfer-function or state-space equations. 
+In step $2$, the physical plant (represented by Equations (\ref{eq:transferfunction}) 
+and (\ref{eq:ss-example})) must be designed, using the preferred method 
+from the control literature~\cite{astrom1997computer}. Finally, in step $3$, 
 the numerical representation for the digital controller implementation must be 
-defined, {\it i.e.}, the FWL format that includes the number of bits for the integer 
-and fractional parts and the dynamic range inputs. The results from the manual 
-procedure is a digital-system implementation for the given physical plant in MATLAB.
+defined by the user, {\it i.e.}, the FWL format that includes the number of bits for the integer 
+and fractional parts as well as the dynamic range inputs. The result of the manual 
+procedure performed by the user is a digital system specification for the given 
+physical plant in MATLAB.
 
-The synthesis process starts in step $A$, when the \tool gets the digital-system in MATLAB, 
-and then translates it into a ANSI-C program; then in step $B$, the DSSynth Tool is invoked. 
-Finally, in step $C$, the digital controller is synthesized based on CEGIS. The output generated 
-in MATLAB is the synthesized digital controller, which can be represented in transfer-function 
-or state-space format. The synthesis is \emph{successful} if a digital controller is correctly synthesized;
-otherwise the synthesis has status \emph{failed} if any parameter is defined incorrectly 
-in previous steps, or there is no solution for the designed digital controller.
+After that, the synthesis process starts in step $A$, when \tool obtains the digital system 
+specification in MATLAB, and then translates it into an ANSI-C program. 
+In step $B$, our CEGIS engine is invoked to synthesize the digital controller w.r.t. the digital system
+specification. Finally, in step $C$, the synthesized digital controller considering FWL effects is produced. 
+The output generated by \tool is the synthesized digital controller represented either in transfer-function 
+or state-space format. The synthesis is considered to be \emph{successful} if a digital controller is correctly 
+synthesized w.r.t. FWL effects; otherwise the synthesis is considered to be \emph{failed}, if any parameter is 
+incorrectly defined in previous steps, or if there is no solution (digital controller) for the respective physical plant
+ given the digital controller word-length.
 

### 2017-05-31 emsoft2017/emsoft-paper.tex
reviewed section 2.2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-The \tool performs the following automated procedures in order to synthesize a digital controller:
+The \tool performs the following automated procedures to synthesize a given digital controller:
 
 \begin{enumerate}
-\item \textbf{Setup}: obtain the plant, fixed-point format and dynamic input ranges, and translate them to a struct in MATLAB;
-\item \textbf{Parse}: obtain the digital plant implementation, and then translate it to an ANSI-C file;
-\item \textbf{Execute}: obtain the ANSI-C file from the previous step, call CBMC-CEGIS as back-end program synthesis tool, and then perform the automated synthesis;
-\item \textbf{Extract}: obtain the .log that is generated after the synthesis phase and then check the synthesized digital-controller.
-\item \textbf{Report}: obtain the digital-controller, translate it to a MATLAB system, and then show the result to the user.
+\item \textbf{Setup}: obtains the physical plant, fixed-point format and dynamic input ranges, and translates them to a specific structure in MATLAB;
+\item \textbf{Parse}: obtains the digital system specification and translates it into an ANSI-C program;
+\item \textbf{Execution}: obtains the ANSI-C program from the previous step and calls our CEGIS engine as back-end program synthesis tool to perform the automated synthesis;
+\item \textbf{Extraction}: obtains the ``.log'' file that is generated after the synthesis phase and then checks the synthesized digital-controller;
+\item \textbf{Report}: obtains the digital controller from the previous step and translates it into the MATLAB structures to show the respective result to the user.
 \end{enumerate}

### 2017-05-31 emsoft2017/emsoft-paper.tex
reviewed section 2.3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{itemize}
-\item \textbf{Representation}: the synthesis could be performed for digital-systems in transfer-function or state-space equations;
+\item \textbf{Representation}: the synthesis can be performed for digital systems specified as transfer-function or state-space equations;
 \item \textbf{Fixed-Point Arithmetic}: the digital controller is synthesized considering FWL effects, in fixed-point numeric representation;
-\item \textbf{Interface}: the synthesis could be executed using the command-line version, and a GUI Application version.
-In addition, in the GUI Application, the user is able to plot the step response in order to reproduce the stability of the digital controller synthesized;
+\item \textbf{Interface}: the synthesis can be executed via command-line or graphical-user interface (GUI).
+For the GUI application, the user can plot the step response to reproduce the stability in closed-loop of the synthesized digital controller;
 \end{itemize}

### 2017-05-31 emsoft2017/emsoft-paper.tex
reviewed section 2.4.1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-The \tool performs the following automated procedures to synthesize a given digital controller:
+The \tool performs the following automated procedures 
+to synthesize a given digital controller:
 
 \begin{enumerate}
-\item \textbf{Setup}: obtains the physical plant, fixed-point format and dynamic input ranges, and translates them to a specific structure in MATLAB;
-\item \textbf{Parse}: obtains the digital system specification and translates it into an ANSI-C program;
-\item \textbf{Execution}: obtains the ANSI-C program from the previous step and calls our CEGIS engine as back-end program synthesis tool to perform the automated synthesis;
-\item \textbf{Extraction}: obtains the ``.log'' file that is generated after the synthesis phase and then checks the synthesized digital-controller;
-\item \textbf{Report}: obtains the digital controller from the previous step and translates it into the MATLAB structures to show the respective result to the user.
+\item \textbf{Setup}: obtains the physical plant, fixed-point format 
+and dynamic input ranges, and translates them to a specific structure in MATLAB;
+\item \textbf{Parse}: obtains the digital system specification and translates 
+it into an ANSI-C program;
+\item \textbf{Execution}: obtains the ANSI-C program from the previous step 
+and calls our CEGIS engine as back-end program synthesis tool to perform the automated synthesis;
+\item \textbf{Extraction}: obtains the ``.log'' file that is generated 
+after the synthesis phase and then checks the synthesized digital-controller;
+\item \textbf{Report}: obtains the digital controller from the previous step 
+and translates it into the MATLAB structures to show the respective result to the user.
 \end{enumerate}
@@
 \begin{itemize}
-\item \textbf{Representation}: the synthesis can be performed for digital systems specified as transfer-function or state-space equations;
-\item \textbf{Fixed-Point Arithmetic}: the digital controller is synthesized considering FWL effects, in fixed-point numeric representation;
-\item \textbf{Interface}: the synthesis can be executed via command-line or graphical-user interface (GUI).
-For the GUI application, the user can plot the step response to reproduce the stability in closed-loop of the synthesized digital controller;
+\item \textbf{Representation}: the synthesis can be 
+performed for digital systems specified as 
+transfer-function or state-space equations;
+\item \textbf{Fixed-Point Arithmetic}: the digital 
+controller is synthesized considering FWL effects, 
+in fixed-point numeric representation;
+\item \textbf{Interface}: the synthesis can be executed 
+via command-line or graphical-user interface (GUI). 
+For the GUI application, the user can plot the step response 
+to reproduce the stability in closed-loop of the synthesized digital controller;
 \end{itemize}
+
 %---------------------------------------------------
@@
 
-Users must provide a digital system described as a MATLAB system  using a \texttt{``tf''} (for transfer-function) or an \texttt{``ss''} (for state-space) command (cf.
-step $1$ of Fig.~\ref{fig:synthesis-flow}).
+Users must provide a digital system described as a MATLAB system 
+using a \texttt{tf} (for transfer-function) or an \texttt{ss} (for state-space) 
+command (cf. step $1$ of Fig.~\ref{fig:synthesis-flow}).
+\tool is called via command line in MATLAB as
 
-\tool is called via command line in MATLAB as \texttt{synthesize(plant, intBits, fracBits, maxRange, minRange)}, where \texttt{plant} is the physical plant in state-space or transfer-function representation, \texttt{intBits} is the integer part, \texttt{fracBits} is the fractional part, \texttt{maxRange} and \texttt{minRange} are the maximum and minimum dynamic range, respectively.
+\begin{verbatim}  synthesize(plant, intBits, fracBits, maxR, minR) \end{verbatim}
 
-After executing \texttt{synthesize} command in MATLAB, the output prints the synthesized digital controller according to the digital system representation, {\it i.e.}, transfer-function or state-space equations.
+\noindent where \texttt{plant} is the physical plant in state-space or transfer-function representation, 
+\texttt{intBits} is the integer part, \texttt{fracBits} is the fractional part, \texttt{maxR} and \texttt{minR} 
+are the maximum and minimum dynamic range, respectively (cf. steps $2$ and $3$ of Fig.~\ref{fig:synthesis-flow}).
+%
+After executing the \texttt{synthesize} command in MATLAB, 
+\tool provides the synthesized digital controller, according to 
+the digital system representation, {\it i.e.}, transfer-function or 
+state-space equations.
 

### 2017-05-31 emsoft2017/emsoft-paper.tex
reviewed section 2.4.2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-A graphical user interface application was developed (Fig.~\ref{fig:gui-for-tf}), in order to favor digital-control systems synthesis in MATLAB, besides improving usability and, consequently, attracting more digital-system engineers.
-Users can provide all required parameters for digital-system synthesization: physical plant specification, fixed-point implementation and dynamic inputs.
+A graphical user interface application was developed (Fig.~\ref{fig:gui-for-tf}) 
+to favor digital controller synthesis in MATLAB, besides improving usability and, 
+consequently, attracting more digital dynamical system engineers. Users can provide all 
+required parameters for digital controller synthesis: physical plant specification, 
+fixed-point representation and dynamic inputs. 
 %

### 2017-05-31 emsoft2017/emsoft-paper.tex
reviewed section 2.5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-To illustrate the \tool's usage, Fig.~\ref{toolbox-usage} shows the synthesis for a physical plant defined in Eq.(~\ref{equation_plant}) using the transfer-function representation, where ``num'' and ``den'' represent the numerator $A(z)$ and denominator $B(z)$, respectively.
+To illustrate the \tool's usage, Fig.~\ref{toolbox-usage} shows the 
+synthesis for a physical plant defined in Eq.(~\ref{equation_plant}) 
+using the transfer-function representation, where ``num'' and ``den'' 
+represent the numerator $A(z)$ and denominator $B(z)$, respectively.
 %
@@
 \label{equation_plant}
-H(z)=\frac{B(z)}{A(z)}=\frac{-0.06875z^{2}}{z^2-1.696z+0.7089},
+H(z)=\frac{B(z)}{A(z)}=\frac{-0.06875z^{2}}{z^2-1.696z+0.7089}.
 \end{equation}
@@
 \vspace{-0.2cm}
-\caption{Synthesis of a Digital Controller for the physical plant defined in Eq.(~\ref{equation_plant}) in MATLAB, with a fixed-point format  $\left\langle 8,8\right\rangle$.}
+\caption{Synthesis of a digital controller for the physical plant defined in Eq.(~\ref{equation_plant}) in MATLAB, with a fixed-point format  $\left\langle 8,8\right\rangle$.}
 \label{toolbox-usage}
@@
 %
-In the Fig.~\ref{toolbox-usage}, the value returned in $y$ represents the digital controller synthesized and stable.
-In order to validate and reproduce the stability in the digital system composed by the physical plant defined in Eq.(~\ref{equation_plant}) and the digital controller represented by $y$, the user can invoke the step response using the command \texttt{dstep}, and then observe that the graph plotted shows a stable digital system, as can be seen in Fig.~\ref{step-response}.
+In Fig.~\ref{toolbox-usage}, the value returned in variable $y$ represents 
+the synthesized stable digital controller. In order to validate and reproduce 
+the stability of the digital system composed by the physical plant defined in Eq.(~\ref{equation_plant}) 
+and the digital controller represented by $y$, the user can invoke the step response using the 
+command \texttt{dstep}, and then observe that the plotted graph shows a stable digital system, 
+as shown in Fig.~\ref{step-response}.
 %

### 2017-05-31 emsoft2017/emsoft-paper.tex
reviewed section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
+%--------------------------------------
 \section{Conclusions}
+%--------------------------------------
 
-\tool is able to synthesize dynamic physical plants designed in MATLAB, through transfer-function and state-space representations based on Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}.
-
-Given the current literature in formal synthesis, there is no other MATLAB toolbox for synthesize stable digital systems, while taking into account implementation aspects (fixed-point arithmetic).
-
-As future work, \tool will perform synthesis to generate stable digital controllers and be combined with DSVerifier Toolbox~\cite{issta2017} to verify the stability of the digital controller synthesized, and also, with DSValidator Toolbox~\cite{dsvalidator}, in order to reproduce and validate the stability property.
+\tool can synthesize digital controllers for dynamic physical plants 
+w.r.t. stability and safety, designed in MATLAB through transfer-function 
+and state-space representations using the CEGIS approach.
+%
+Given the current literature in controller synthesis, there is no other MATLAB toolbox 
+for synthesizing stable digital controllers for physical plants, while taking into account implementation 
+aspects (fixed-point arithmetic). 
+%
+As future work, \tool will perform synthesis of other types of specifications (e.g., performance) 
+and be combined with DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to verify/validate
+ other controller properties (e.g., limit cycle).
 

### 2017-06-01 automatica/automatica.tex
Proof for continuous systems with inputs

@@
 time domain.
+
+A dynamical system is a system in which a function describes the progression of a state over time. 
+In a continuous domain with linear dynamics, it is described by a first order Ordinary Differential Equation (ODE).
+\begin{equation}
+\dot{x}(t)=\mat{A}_o\vec{x}(t)+\mat{B}_o\vec{u}(t) +\vec{w}(t)
+\label{eq:dynamical}
+\end{equation}
+where $\vec{w}$  is a continuous zero-mean white noise source with covariance $N ( 0 , Q )$
+Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
+which may restricts the observability of the statespace from the output space.
+\begin{equation}
+\vec{y}(t)=\mat{C}_o\vec{x}(t)+\mat{D}_o\vec{u}(t)
+\end{equation}
+Discretization of a continuous dynamical system turns the ODE into a difference equation, assuming zero-order hold
+for the input $\vec{u}$ and continuous integration for the noise $\vec{w}$, to
+\begin{align}
+\label{eq:discretization}
+\vec{x}_{k+1} &= \mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k + \vec{w}_k\\
+y_k &= \mat{C}_d \vec{x}_ k + \mat{D}_d \vec{u}_ k 
+\end{align}
+with covariance for $\vec{w}_k$, $N ( 0 , Q_d )$
+where
+\begin{align}
+\label{eq:discretize}
+\mat{A}_d &= e^{\mat{A}_o T_s} = \mathcal{L}^{-1} { ( s \mat{I} - \mat{A}_o )^{-1} }_{t = T_s}\\
+\mat{B}_d &= \int_{t = 0}^{T_s} e^{\mat{A}_o t} dt\ \mat{B}_o = \mat{A}_o^{-1} ( \mat{A}_d - \mat{I} ) \mat{B}_o\\
+\mat{C}_d &= \mat{C}_o\\
+\mat{D}_d &= \mat{D}_o \\
+Q_d &= \int_{t = 0}^{T_s} e^{\mat{A}_o t} Q e^{\mat{A}_o^T t} dt
+\end{align}
+and $T_s$ is the sample time. Then
+\begin{align*}
+x(kT)=x_k \wedge y(kT) = y_k, \forall k
+\end{align*}
 
@@
  referenced to the original eigenvalues modified by the sampling rate.
-  Let $\mat{J}\in \mathbb{R}^{p \times p}$ be a Jordan Canonical matrix whose powers are described in Equation \eqref{jord:pow}
- Then
+  Let $\mat{J}\in \mathbb{R}^{p \times p}$ be a Jordan Canonical matrix. Then
 \begin{align}
- \mat{J}_1=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{J}T_1\right)^k=
-&\sum_{k=0}^\infty \frac{1}{k!} \left [ \begin{array}{cccc}
+ \mat{J}_1=&\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{J}T_1\right)^k\nonumber\\
+ =&\sum_{k=0}^\infty \frac{1}{k!} \left [ \begin{array}{cccc}
  \lambda_i^k  & \binom{k}{1}  \lambda^{k-1} & \hdots  & \binom{k}{p-1} \lambda_i^{k-p+1} \\
@@
 which completes the proof for $gm(\lambda_i)>1$.
+\end{proof}
+
+\begin{theorem}
+The expression
+ \begin{align}
+ \vec{x}_T&=\vec{x}(t=T)=\mat{A}^{-1}\vec{x}_T'\nonumber\\
+\vec{x}_T'&=\mat{A}\mat{A}_T\vec{x}_0 + (\mat{I}-\mat{A}_T)\mat{B}\vec{u} : \forall t \leq T,\ \vec{u}(t)=\vec{u} 
+ \end{align}
+ with $\mat{A}_T$ as per \eqref{eq:continuous_tube_dyn} is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$.
+ \end{theorem}
+ \begin{corollary}
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}+(\mat{I}-\mat{A}_d^k\mat{B}\vec{u}) : k \in (0,\infty)$ is a witness of the system at time $kT_d$.
+ \end{corollary}
+ \begin{proof}
+ We begin by expanding the equation
+ \begin{align}
+ \vec{x}_T&=\mat{A}^{-1}\vec{x}_T'\\
+ \vec{x}_T'&=\mat{A}_T\vec{x}_0 + \mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}\vec{u} = \mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u}\nonumber
+ \end{align}
+ where $\mat{A}_T=e^{\mat{A}T}$ and $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$ correspond to $\mat{A}_d$ and $\mat{B}_d$ in equation \eqref{eq:discretize}
+ \end{proof}
+ \begin{theorem}
+Let $\mat{A}_b$ be a spherical overapproximation of $\mat{A}$ and $U_b$ a spherical overapproximation of $U$ centered at $\vec{u}_c$
+\begin{align}
+\mat{A}_b&=\mat{S} \mat{J}_b \mat{S}^{-1}\\
+\mat{J}_{bs}&=\lambda_{bs}\mat{I} \wedge \lambda_{bs}=|| \mat{J}_s ||=
+\max_{\vec{u} \subseteq U_b'} \frac{|| \mat{J}_s\vec{u}_s ||}{||
+  \vec{u}_s ||}\nonumber
+\label{eq:induced}
+\end{align}
+where $|| \mat{J}_s ||$ is the induced matrix norm, $s$ indicates the index of each Jordan block, and $\vec{u}_s$ is the corresponding subvector of $\vec{u}$ (\emph{ie} the subspace of $\vec{u}$ on which $\mat{J}_s$ operates).
+Directly from the definition of the matrix norm, we have 
+\begin{equation}
+||\mat{J}_s\vec{u}_s|| \leq ||\mat{J}_s||\,||\vec{u}_s||, 
+\label{eq:overinduced}
+\end{equation}
+and $\mat{J}_{b} U_b$ is the smallest ball that over-approximates $\mat{J}  U_d$.
+
+The expression
+ \begin{align}
+X_T^\sharp &=\mat{A}^{-1}X_T'\supseteq X_T\\
+X_T'&=\mat{A}\mat{A}_TX_0 \oplus (\mat{I}-\mat{A}_{bT})\mat{B}U_b \oplus (\mat{I}-\mat{A}_T)\mat{B}\vec{u}_c\nonumber
+ \end{align}
+ is an overapproximation of the reach set  at time $t=T$ of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t) + \mat{B}\vec{u}(t)$ given $\vec{x}(0) \in X_0$ and $\vec{u}(t) \in U$.
+ \end{theorem}
+\begin{corollary}
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then 
+ \begin{equation}
+ \tiny
+ X_k=A_d^kX_0 \oplus (\mat{I}-\mat{A}_{bd}^k)(\mat{I}-\mat{A}_{bd})^{-1}\mat{B}U_b \oplus (\mat{I}-\mat{A}_d^k)(\mat{I}-\mat{A}_d)^{-1}\mat{B}\vec{u}_c\nonumber\\
+ k \in (0,\infty)
+ \end{equation}
+  is a witness of the system at time $kT_d$, where $\mat{A}_{bd}$ is a spherical overapproximation of $\mat{A}_d$
+\end{corollary}
+ \begin{proof}
+Let $U'=\mat{B}U$, with $\vec{u}'$ its geometrical centre and $U_b'$ the smallest sphere centered at $\vec{u}'$ containing all points in $U'$.
+Then $U'\subseteq U_b' \oplus \vec{u}_c' \Rightarrow (\mat{I}-\mat{A}_T)U' \subseteq (\mat{I}-\mat{A}_T)U_b' \oplus (\mat{I}-\mat{A}_T)\vec{u}_c'$.
+Since $ (\mat{I}-\mat{A}_{bT})U_b'\supseteq  (\mat{I}-\mat{A}_T)U_b'$, then $(\mat{I}-\mat{A}_T)U' \subseteq (\mat{I}-\mat{A}_{bT})U_b' \oplus (\mat{I}-\mat{A}_T)\vec{u}_c'$ thus proving the theorem.
+
 \end{proof}

### 2017-06-01 ase2017/paper.tex
added section about CEGIS for control
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
described about the tool architecture
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2017-05-31 emsoft2017/emsoft-paper.tex
@@
 
-\setcopyright{acmcopyright}
-\acmDOI{10.475/123_4}
-\acmISBN{123-4567-24-567/08/06}
-\acmConference[EMSOFT '17]{The ACM SIGBED International Conference on Embedded Software }{October 15--20, 2017}{Seoul, South Korea}
-\acmYear{2017}
-\copyrightyear{2017}
-\acmPrice{15.00}
+%\setcopyright{acmcopyright}
+%\acmDOI{10.475/123_4}
+%\acmISBN{123-4567-24-567/08/06}
+%\acmConference[ASE '17]{The ACM SIGBED International Conference on Embedded Software }{October 15--20, 2017}{Seoul, South Korea}
+%\acmYear{2017}
+%\copyrightyear{2017}
+%\acmPrice{15.00}
 
@@
 %---------------------------------------------------
+\section{Counterexample-Guided Inductive Synthesis for Control Systems}
+%---------------------------------------------------
+
+\textcolor{red}{Cristina: can you please generalize our CEGIS implementation for control here?}
+
+\textcolor{red}{We have to talk about the naive and AA back-ends, which are based on our CEGIS framework}
+
+%---------------------------------------------------
 \section{Synthesizing Digital Controllers with \tool}
@@
  given the digital controller word-length.
+
+\textcolor{blue}{The main development challenge related to \tool is the representation of the
+closed-loop control system models, considering FWL effects, time discretization 
+and quantization noise.  In particular, our implementation consists of $400$
+lines of code related to MATLAB scripts, $585$ and $800$ lines of C code related to the
+naive and abstract accelerator backends. In addition, there are $4000$ lines of C code
+related to utility functions (e.g., interval and fixed-point arithmetic), $50$ lines
+of code to parse MATLAB functions and there are approximately $20$
+control system benchmarks to ensure the \tool's regression.  All those artifacts together
+with documentation and videos are available in a public github repository,
+which is located at \url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}.
 

### 2017-06-01 ase2017/paper.tex
added more comments related to the tool paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\title{DSSynth: An Automated Synthesis Tool for Physical Plants \\ Digital Controllers via MATLAB Toolbox}
+\title{DSSynth: An Automated Synthesis Tool of Digital Controllers \\ for Physical Plants via MATLAB Toolbox}
 
@@
 
+\textcolor{red}{Pascal, can you please review this paragraph?}
+
 \textcolor{blue}{The main development challenge related to \tool is the representation of the
@@
 
+\textcolor{red}{Lennon, can you please use an illustrative example related to UAV?}
+
 To illustrate the \tool's usage, Fig.~\ref{toolbox-usage} shows the 
@@
 
+%---------------------------------------------------
+\section{\tool Experimental Evaluation}
+%---------------------------------------------------
+
+%---------------------------------------------------
+\subsection{Benchmarks Description}
+%---------------------------------------------------
+
+%---------------------------------------------------
+\subsection{Objectives}
+%---------------------------------------------------
+
+%---------------------------------------------------
+\subsection{Results}
+%---------------------------------------------------
+
 %--------------------------------------

### 2017-06-01 ase2017/paper.tex
explained a typical closed-loop control system
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \usepackage{listings}
+\usepackage{graphicx}
+\usepackage{subfigure}
 
@@
 
-Linear-Time Invariant (LTI) systems are used in several applications
-to support non-trivial tasks when applied to embedded systems 
-(e.g., robot manipulator, power plants and guidance system). 
-In addition, controllers synthesis for LTI systems is richly studied 
-by different researchers~\cite{mazo2010pessoa,DBLP:conf/emsoft/RavanbakhshS16,economakos2016automated}; 
-however, there are many challenges when 
-digital-control systems theory is used due to the finite-word 
-length (FWL) effects~\cite{Guang2013, Istepanian2001}, time discretization 
-and quantization noise, which are typically introduced by Analogue-to-Digital 
-(ADC) and Digital-to-Analogue (DAC) conversion, leading to truncation 
-or round-off errors~\cite{astrom1997computer}.
+Control theory achieves the construction of reliable systems by 
+offering mathematical guarantees about the stability and the desired 
+performance of closed-loop systems, where plant states or outputs 
+are fed back and compared to a reference signal to which a (designed) 
+controller should maintain a set of control objectives~\cite{astrom1997computer}. 
+Fig.~\ref{fig:typical-control-system} shows a typical closed-loop digital control system.
 
-Embedded digital control systems perform computations over digital signals 
-to influence the system behavior~\cite{Ogata2001}; it can be mathematically 
-expressed as difference equations, transfer functions or state-space equations. 
-Here, the focus is on transfer-function and state-space representations. 
-The following expression presents the general form of a digital control system 
-using the transfer function representation:
+\textcolor{red}{Cristina, can you please draw this figure in tikz?}
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=0.35\textwidth]{closedloopseries.pdf}
+\caption{Typical Closed-loop Control System.}
+\label{fig:typical-control-system}
+\end{figure}
+
+%Embedded digital control systems perform computations over digital signals 
+%to influence the system behavior~\cite{Ogata2001}; it can be mathematically 
+%expressed as difference equations, transfer functions or state-space equations. 
+%Here, the focus is on transfer-function and state-space representations.
+
+There are various mathematical representations for digital control
+systems,  e.g.,  difference  equations,  state-space,  and
+transfer functions. Here, linear time-invariant (LTI) systems 
+with single-input and single-output (SISO) are considered and 
+represented by transfer function and state space. LTI systems 
+are used in several applications to support non-trivial tasks when 
+applied to embedded systems (e.g., robot manipulator, power plants 
+and guidance system). The following expression presents the general form 
+of a digital control system using the transfer function representation:
 %
@@
 
-Recently, a new methodology to synthesize digital-control systems was proposed, 
+Controllers synthesis for LTI systems is richly studied 
+by different researchers~\cite{mazo2010pessoa,DBLP:conf/emsoft/RavanbakhshS16,economakos2016automated}; 
+however, there are many challenges when 
+digital control system theory is used, mainly due to the finite-word 
+length (FWL) effects~\cite{Guang2013, Istepanian2001}, time discretization 
+and quantization noise, which are typically introduced by Analogue-to-Digital 
+(ADC) and Digital-to-Analogue (DAC) conversion, leading to truncation 
+or round-off errors~\cite{astrom1997computer}.
+
+Recently, a new methodology to synthesize digital control systems was proposed, 
 named as DSSynth (Digital System Synthesis)~\cite{abate2017, abatecav2017}, 
 which is based on the Counter-Example Guided Inductive Synthesis 
-(CEGIS) approach~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. Here, CEGIS is used
-as a program synthesis engine able to produce controllers for highly non-trivial 
-specifications with a very high degree of automation. Program synthesis engines 
-as CEGIS use a specification as the starting point, and subsequently 
-produce a sequence of candidate programs from a given template. The candidate programs 
-are iteratively refined to eventually satisfy the specification. Modern synthesis engines combine 
-automated testing, genetic algorithms and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
-Currently, Abate {\it et al.}~\cite{abate2017} synthesize stable, software-implemented 
-embedded controllers, along with a physical plant model represented by transfer functions 
-or state-space equations~\cite{abate2017,abatecav2017} using a CEGIS-based approach.
+(CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. Here, CEGIS is used
+as a program synthesis engine that is able to produce controllers for highly non-trivial 
+control system specifications with a very high degree of automation. Program synthesis engines 
+use a specification as the starting point, and subsequently produce a sequence of candidate 
+programs from a given template. The candidate programs are iteratively refined to eventually 
+satisfy the specification. Modern synthesis engines combine automated testing, genetic algorithms 
+and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
+DSSynth synthesizes stable digtal controllers using that CEGIS-based approach,
+for a given physical plant represented by transfer function or state-space equations~\cite{abate2017,abatecav2017}.
 
 Notably, there are toolboxes in MATLAB with functions and scripts to facilitate the 
-digital system design and implementation~\cite{matlab-toolbox}. In fact, there is a MATLAB 
+digital system design and implementation~\cite{matlab-toolbox}. Indeed, there is a MATLAB 
 Toolbox named as DSVerifier Toolbox~\cite{issta2017}, which automatically detects 
@@
 Satisfiability Modulo Theories (SMT) solvers, given the physical plant and the digital controller. 
-However, there is no toolbox in MATLAB to perform digital control synthesis; in particular, based on 
+However, there is no toolbox in MATLAB to perform digital controller synthesis; in particular, based on 
 CEGIS considering FWL effects.
@@
 through transfer-function or state-space representations, consider low-level systems parameters 
-(implementation features and numerical format), and then gets a stable synthesized digital-controller.
+(implementation features and numerical format), and then obtains a stable synthesized digital-controller.
 

### 2017-06-01 ase2017/paper.tex
Updated to IEEE Style

@@
-\documentclass[sigconf]{acmart}
+\documentclass[10pt,conference]{IEEEtran}
 
@@
 \usepackage{subfigure} 
+\usepackage{xcolor,colortbl}
+\usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage{hyperref}
+\usepackage{cite}
 
@@
 \title{DSSynth: An Automated Synthesis Tool of Digital Controllers \\ for Physical Plants via MATLAB Toolbox}
+
+\maketitle
 
@@
 %
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10010520.10010570</concept_id>
-<concept_desc>Computer systems organization~Real-time systems</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-<concept>
-<concept_id>10010520.10010553.10010562</concept_id>
-<concept_desc>Computer systems organization~Embedded systems</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10011007.10010940.10010992.10010998.10003791</concept_id>
-<concept_desc>Software and its engineering~Model checking</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-<concept>
-<concept_id>10011007.10010940.10010992.10010998</concept_id>
-<concept_desc>Software and its engineering~Formal methods</concept_desc>
-<concept_significance>100</concept_significance>
-</concept>
-<concept>
-<concept_id>10003752.10003790.10011192</concept_id>
-<concept_desc>Theory of computation~Verification by model checking</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Computer systems organization~Real-time systems}
-\ccsdesc[300]{Computer systems organization~Embedded systems}
-\ccsdesc[500]{Software and its engineering~Model checking}
-\ccsdesc[100]{Software and its engineering~Formal methods}
-\ccsdesc[300]{Theory of computation~Verification by model checking}
-
-\keywords{Formal Synthesis; Digital Control Systems; MATLAB Toolbox; Finite-Word Length; Verification}
-
-\maketitle
+\begin{IEEEkeywords}
+Formal Synthesis; Digital Control Systems; MATLAB Toolbox; Finite-Word Length; Verification
+\end{IEEEkeywords}
 
@@
 
-\bibliographystyle{ACM-Reference-Format}
+\bibliographystyle{IEEEtran}
 \bibliography{references}

### 2017-06-04 ase2017/paper.tex
added UAV illustrative example

@@
 
-\title{DSSynth: An Automated Synthesis Tool of Digital Controllers \\ for Physical Plants via MATLAB Toolbox}
+\title{DSSynth: An Automated Synthesis Tool of Digital \\ Controllers for Physical Plants via MATLAB Toolbox}
 
@@
 
-\textcolor{red}{Lennon, can you please use an illustrative example related to UAV?}
-
 To illustrate the \tool's usage, Fig.~\ref{toolbox-usage} shows the 
-synthesis for a physical plant defined in Eq.(~\ref{equation_plant}) 
-using the transfer-function representation, where ``num'' and ``den'' 
+synthesis for a physical plant defined in Eq.(~\ref{equation_plant}),
+which represents a UAV a quadcopter system, whose model was described by Bouabdallah {\it et al.}~\cite{bouabdallah}.
+The physical plant in Eq.(~\ref{equation_plant}) is represented using the transfer-function format, where ``num'' and ``den''
 represent the numerator $A(z)$ and denominator $B(z)$, respectively.

### 2017-06-04 ase2017/paper.tex
updated illustrative example

@@
 \usepackage{cite}	
+\usepackage{mathtools}
 
@@
 \newcommand\tool{{DSSynth Toolbox}\xspace}
+\newcommand{\fwl}[1]{\mathcal{FWL}[#1]}
 
@@
 
-\begin{verbatim} synthesize(plant, intBits, fracBits, maxR, minR) \end{verbatim}
+\begin{center} 
+\texttt{synthesize(plant, intBits, fracBits, maxR, minR)}
+\end{center}
 
@@
 \label{equation_plant}
-H(z)=\frac{B(z)}{A(z)}=\frac{-0.06875z^{2}}{z^2-1.696z+0.7089}.
+G(z)=\frac{B(z)}{A(z)}=\frac{-0.06875z^{2}}{z^2-1.696z+0.7089}.
 \end{equation}
@@
 >> SYNTHESIS SUCCESSFUL
->> y = (-0.9983z^2 + 0.09587z + 0.1926)/(z^2+0.5665+0.75);
+>> y = 
+>>  -0.9983 z^2 + 0.09587 z + 0.1926
+>>  --------------------------------
+>>       z^2 + 0.5665 z + 0.75
 \end{lstlisting}
 \vspace{-0.2cm}
-\caption{Synthesis of a digital controller for the physical plant defined in Eq.(~\ref{equation_plant}) in MATLAB, with a fixed-point format  $\left\langle 8,8\right\rangle$.}
+\caption{Synthesis of a digital controller for the physical plant defined in Eq.(\ref{equation_plant}) in MATLAB, with a fixed-point format  $\left\langle 8,8\right\rangle$.}
 \label{toolbox-usage}
@@
 In Fig.~\ref{toolbox-usage}, the value returned in variable $y$ represents 
-the synthesized stable digital controller. In order to validate and reproduce 
-the stability of the digital system composed by the physical plant defined in Eq.(~\ref{equation_plant}) 
-and the digital controller represented by $y$, the user can invoke the step response using the 
+the synthesized stable digital controller, which could be expressed in Eq.(\ref{equation_controller}).
+
+\begin{equation}
+\label{equation_controller}
+H(z)=\frac{-0.9983^{2}+0.09587z+0.1926}{z^2+0.5665z+0.75}.
+\end{equation}
+
+In addition, a digital system is stable \textit{iff} all of its poles are inside the $z$-plane unitary circle; poles must have the modulus less than one.
+In order to compute the poles from the digital system represented by the physical plant and the controller defined in Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}), respectively, the user can use \texttt{feedback} and \texttt{series} commands in MATLAB~\cite{matlab} to achieve a general equation regarding the transfer-function representation.
+The general equation that represents the combination between Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}) is represented by Eq.~(\ref{equation_general}):
+%
+\begin{equation}
+\small
+\label{equation_general}
+\frac{N(z)}{D(z)}=\frac{0.06863z^{4} - 0.006591z^{3} - 0.01324z^{2}}{1.069z^{4} - 1.136z^{3} + 0.4849z^{2} -0.8704z + 0.5317}.
+\end{equation}
+
+Applying the FWL effects in the $D(z)$ in order to compute the roots for stability reproduction, then if any root has modulus equal or greater than one, then the system is unstable; otherwise, it is stable.
+In fact, the roots computed by the function \texttt{roots} in MATLAB resulted in $-0.2909 + 0.8065i$, $-0.2909 - 0.8065i$, $0.8553$ and $0.7924$, which means that DSSynth returned a stable digital controller.
+
+Simulating the digital system represented by Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}), in order to validate and reproduce the stability, the user can invoke the step response using the
 command \texttt{dstep}, and then observe that the plotted graph shows a stable digital system, 

### 2017-06-04 ase2017/paper.tex
minor change

@@
 In addition, a digital system is stable \textit{iff} all of its poles are inside the $z$-plane unitary circle; poles must have the modulus less than one.
-In order to compute the poles from the digital system represented by the physical plant and the controller defined in Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}), respectively, the user can use \texttt{feedback} and \texttt{series} commands in MATLAB~\cite{matlab} to achieve a general equation regarding the transfer-function representation.
+In order to compute the poles from the digital system represented by the physical plant and the controller defined in Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}), respectively, the user can use \texttt{feedback} and \texttt{series} commands in MATLAB~\cite{matlab-toolbox} to achieve a general equation regarding the transfer-function representation.
 The general equation that represents the combination between Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}) is represented by Eq.~(\ref{equation_general}):
@@
 Applying the FWL effects in the $D(z)$ in order to compute the roots for stability reproduction, then if any root has modulus equal or greater than one, then the system is unstable; otherwise, it is stable.
-In fact, the roots computed by the function \texttt{roots} in MATLAB resulted in $-0.2909 + 0.8065i$, $-0.2909 - 0.8065i$, $0.8553$ and $0.7924$, which means that DSSynth returned a stable digital controller.
+In fact, the roots computed by the function \texttt{roots} in MATLAB~\cite{matlab-toolbox} resulted in $-0.2909 + 0.8065i$, $-0.2909 - 0.8065i$, $0.8553$ and $0.7924$, which means that DSSynth returned a stable digital controller.
 

### 2017-06-05 ase2017/paper.tex
updated figure

--- 2017-06-04 ase2017/paper.tex
@@
 \usepackage{graphicx}
-\usepackage{subfigure} 
+\usepackage{subfig} 
 \usepackage{xcolor,colortbl}
@@
 
-\title{DSSynth: An Automated Synthesis Tool of Digital \\ Controllers for Physical Plants via MATLAB Toolbox}
+\title{DSSynth: An Automated Controller Synthesis Tool \\ for Physical Plants via MATLAB Toolbox}
 
@@
 %
-\begin{figure}
-  \includegraphics[width=0.5\textwidth]{screens_dssynth.png}
-  \caption{GUI Application for Transfer-Function Synthesis.}
+
+\begin{figure}[ht]
+    \centering
+    \subfloat[Define representation and the physical plant.]{
+		\includegraphics[width=0.35\textwidth]{step1.png}
+		\label{step1}}
+		\hfil
+    \subfloat[Determine the implementation and the dynamic range.]{
+	\includegraphics[width=0.35\textwidth]{step2.png}
+		\label{step2}}
+		\hfil
+    \subfloat[Digital controler synthesized.]{
+	\includegraphics[width=0.35\textwidth]{step3.png}
+		\label{step2}}
+		\hfil
+    \subfloat[Step Response for the stable digital controller synthesized]{
+	\includegraphics[width=0.35\textwidth]{step4.png}
+		\label{step3}}
+		\hfil
+    \caption{GUI application for the digital synthesis based on the transfer function representation.}
     \label{fig:gui-for-tf}
@@
 
-To illustrate the \tool's usage, Fig.~\ref{toolbox-usage} shows the 
-synthesis for a physical plant defined in Eq.(~\ref{equation_plant}),
-which represents a UAV a quadcopter system, whose model was described by Bouabdallah {\it et al.}~\cite{bouabdallah}.
-The physical plant in Eq.(~\ref{equation_plant}) is represented using the transfer-function format, where ``num'' and ``den''
-represent the numerator $A(z)$ and denominator $B(z)$, respectively.
+To illustrate the \tool's usage, Fig.~\ref{toolbox-usage} shows each step of the 
+synthesis process for a physical plant described in Eq.~\eqref{equation_plant},
+which represents a real unmanned aerial vehicle (UAV) quadcopter system~\cite{bouabdallah}. 
+This physical plant is expressed by a transfer function, where 
+$B(z)$ and $A(z)$ represent the numerator and denominator, respectively, as
 %
@@
 \end{equation}
-%
+
 \begin{figure}[ht]
@@
 \end{figure}
+
+In Fig.~\ref{toolbox-usage}, ``num'' represents $A(z)$ and ``den'' represent $B(z)$, while 
+$y$ represents the synthesized stable digital controller, which is defined by Eq.(\ref{equation_controller}).
 %
-In Fig.~\ref{toolbox-usage}, the value returned in variable $y$ represents 
-the synthesized stable digital controller, which could be expressed in Eq.(\ref{equation_controller}).
-
 \begin{equation}
 \label{equation_controller}
-H(z)=\frac{-0.9983^{2}+0.09587z+0.1926}{z^2+0.5665z+0.75}.
+C(z)=\frac{-0.9983^{2}+0.09587z+0.1926}{z^2+0.5665z+0.75}.
 \end{equation}
 
-In addition, a digital system is stable \textit{iff} all of its poles are inside the $z$-plane unitary circle; poles must have the modulus less than one.
-In order to compute the poles from the digital system represented by the physical plant and the controller defined in Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}), respectively, the user can use \texttt{feedback} and \texttt{series} commands in MATLAB~\cite{matlab} to achieve a general equation regarding the transfer-function representation.
-The general equation that represents the combination between Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}) is represented by Eq.~(\ref{equation_general}):
+A digital system is stable \textit{iff} all of its poles are inside the $z$-plane unitary circle; 
+poles must have the modulus less than one. In order to compute the poles for the digital 
+system represented by Equations~\eqref{equation_plant} and \eqref{equation_controller}, 
+the user can invoke the \texttt{feedback} and \texttt{series} commands in MATLAB~\cite{matlab-toolbox} 
+to achieve a general equation regarding the transfer function representation. 
+The general equation that represents the combination between Equations~\eqref{equation_plant}
+and~\eqref{equation_controller} is
 %
@@
 
-Applying the FWL effects in the $D(z)$ in order to compute the roots for stability reproduction, then if any root has modulus equal or greater than one, then the system is unstable; otherwise, it is stable.
-In fact, the roots computed by the function \texttt{roots} in MATLAB resulted in $-0.2909 + 0.8065i$, $-0.2909 - 0.8065i$, $0.8553$ and $0.7924$, which means that DSSynth returned a stable digital controller.
+For the stability check, if any root has modulus equal or greater than one, then the system is unstable; 
+otherwise, it is stable. Indeed, the roots computed by the function \texttt{roots} 
+in MATLAB~\cite{matlab-toolbox} result in the following poles: 
+$-0.2909 + 0.8065i$, $-0.2909 - 0.8065i$, $0.8553$ and $0.7924$, 
+which means that DSSynth has synthesized a stable digital controller.
 
-Simulating the digital system represented by Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}), in order to validate and reproduce the stability, the user can invoke the step response using the
-command \texttt{dstep}, and then observe that the plotted graph shows a stable digital system, 
+Simulating the digital system represented by Equations \eqref{equation_plant} and \eqref{equation_controller} 
+to validate and reproduce the system stability, the user can invoke the step response using the 
+command \texttt{dstep} in MATLAB, and then observe that the plotted graph shows a stable digital system, 
 as shown in Fig.~\ref{step-response}.
@@
   \includegraphics[width=0.5\textwidth]{step-response.eps}
-  \caption{Step response for the Eq.~\eqref{equation_plant} describing a stable system.}
+  \caption{Step response for the Eq.~\eqref{equation_plant} describing a stable system for the UAV quadcopter system.}
   \label{step-response}
@@
 %---------------------------------------------------
+
+Our experimental evaluation consist of a set of control system benchmarks,
+which include physical plants for UAV, cruise control, spring-mass damper,
+satellite, direct current (DC) servo motor, helicopter, inverted pendulum,
+magnetic suspension, computer tape driver, robot manipulator, flexible beam,
+guidance system, and an antenna control system~\cite{abate2017, abatecav2017}.
 

### 2017-06-05 ase2017/paper.tex
minor change
reviewed illustrative example
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2017-06-04 ase2017/paper.tex
@@
 synthesis for a physical plant defined in Eq.(~\ref{equation_plant}),
-which represents a UAV a quadcopter system, whose model was described by Bouabdallah {\it et al.}~\cite{bouabdallah}.
-The physical plant in Eq.(~\ref{equation_plant}) is represented using the transfer-function format, where ``num'' and ``den''
+which represents a UAV a quadcopter system, described by 
+Bouabdallah {\it et al.}~\cite{bouabdallah}. The physical plant in Eq.(~\ref{equation_plant}) 
+is represented using the transfer-function format, where ``num'' and ``den'' 
 represent the numerator $A(z)$ and denominator $B(z)$, respectively.
@@
 In Fig.~\ref{toolbox-usage}, the value returned in variable $y$ represents 
-the synthesized stable digital controller, which could be expressed in Eq.(\ref{equation_controller}).
+the synthesized stable digital controller, which can be expressed in Eq.(\ref{equation_controller}).
 
@@
 
-In addition, a digital system is stable \textit{iff} all of its poles are inside the $z$-plane unitary circle; poles must have the modulus less than one.
-In order to compute the poles from the digital system represented by the physical plant and the controller defined in Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}), respectively, the user can use \texttt{feedback} and \texttt{series} commands in MATLAB~\cite{matlab-toolbox} to achieve a general equation regarding the transfer-function representation.
-The general equation that represents the combination between Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}) is represented by Eq.~(\ref{equation_general}):
+A digital system is stable \textit{iff} all of its poles are inside the $z$-plane unitary circle; 
+poles must have the modulus less than one. In order to compute the poles from the digital 
+system represented by the physical plant and the controller defined in Eq.~(\ref{equation_plant}) 
+and Eq.~(\ref{equation_controller}), respectively, the user can use \texttt{feedback} and \texttt{series} 
+commands in MATLAB~\cite{matlab-toolbox} to achieve a general equation regarding the 
+transfer-function representation. The general equation that represents the combination 
+between Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}) is represented by Eq.~(\ref{equation_general}):
 %
@@
 
-Applying the FWL effects in the $D(z)$ in order to compute the roots for stability reproduction, then if any root has modulus equal or greater than one, then the system is unstable; otherwise, it is stable.
-In fact, the roots computed by the function \texttt{roots} in MATLAB~\cite{matlab-toolbox} resulted in $-0.2909 + 0.8065i$, $-0.2909 - 0.8065i$, $0.8553$ and $0.7924$, which means that DSSynth returned a stable digital controller.
+After applying FWL effects in $D(z)$ to compute the roots for stability reproduction, 
+if any root has modulus equal or greater than one, then the system is unstable; 
+otherwise, it is stable. Indeed, the roots computed by the function \texttt{roots} 
+in MATLAB~\cite{matlab-toolbox} result in $-0.2909 + 0.8065i$, $-0.2909 - 0.8065i$, $0.8553$ and $0.7924$, 
+which means that DSSynth has synthesized a stable digital controller.
 
-Simulating the digital system represented by Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}), in order to validate and reproduce the stability, the user can invoke the step response using the
+Simulating the digital system represented by Eq.~(\ref{equation_plant}) and Eq.~(\ref{equation_controller}), 
+in order to validate and reproduce the stability, the user can invoke the step response using the 
 command \texttt{dstep}, and then observe that the plotted graph shows a stable digital system, 

### 2017-06-05 ase2017/paper.tex
fixed figure label
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
   \includegraphics[width=0.5\textwidth]{screens_dssynth.png}
-  \caption{GUI Application for Transfer-Function Synthesis.}
+  \caption{GUI application for the digital controller synthesis based on the transfer function representation.}
   \label{fig:gui-for-tf}
@@
 To illustrate the \tool's usage, Fig.~\ref{toolbox-usage} shows the 
-synthesis for a physical plant defined in Eq.(~\ref{equation_plant}),
-which represents a UAV a quadcopter system, described by 
-Bouabdallah {\it et al.}~\cite{bouabdallah}. The physical plant in Eq.(~\ref{equation_plant}) 
-is represented using the transfer-function format, where ``num'' and ``den'' 
-represent the numerator $A(z)$ and denominator $B(z)$, respectively.
+synthesis process for a physical plant described by Eq.(~\ref{equation_plant}),
+which represents a UAV a quadcopter system~\cite{bouabdallah}. 
+The physical plant in Eq.(~\ref{equation_plant}) is represented using 
+the transfer-function format, where ``num'' and ``den'' represent the 
+numerator $A(z)$ and denominator $B(z)$, respectively.
 %

### 2017-06-05 ase2017/paper.tex
improved llustrative Example
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2017-06-05 ase2017/paper.tex
@@
 \usepackage{graphicx}
-\usepackage{subfig} 
+\usepackage{subfigure} 
 \usepackage{xcolor,colortbl}
@@
 
-\title{DSSynth: An Automated Controller Synthesis Tool \\ for Physical Plants via MATLAB Toolbox}
+\title{DSSynth: An Automated Synthesis Tool of Digital \\ Controllers for Physical Plants via MATLAB Toolbox}
 
@@
 %
-
-\begin{figure}[ht]
-    \centering
-    \subfloat[Define representation and the physical plant.]{
-		\includegraphics[width=0.35\textwidth]{step1.png}
-		\label{step1}}
-		\hfil
-    \subfloat[Determine the implementation and the dynamic range.]{
-	\includegraphics[width=0.35\textwidth]{step2.png}
-		\label{step2}}
-		\hfil
-    \subfloat[Digital controler synthesized.]{
-	\includegraphics[width=0.35\textwidth]{step3.png}
-		\label{step2}}
-		\hfil
-    \subfloat[Step Response for the stable digital controller synthesized]{
-	\includegraphics[width=0.35\textwidth]{step4.png}
-		\label{step3}}
-		\hfil
-    \caption{GUI application for the digital synthesis based on the transfer function representation.}
+\begin{figure}
+  \includegraphics[width=0.5\textwidth]{screens_dssynth.png}
+  \caption{GUI application for the digital controller synthesis based on the transfer function representation.}
   \label{fig:gui-for-tf}
@@
 
-Our experimental evaluation consist of a set of control system benchmarks,
-which include physical plants for UAV, cruise control, spring-mass damper,
-satellite, direct current (DC) servo motor, helicopter, inverted pendulum,
-magnetic suspension, computer tape driver, robot manipulator, flexible beam,
-guidance system, and an antenna control system~\cite{abate2017, abatecav2017}.
-
 %---------------------------------------------------

### 2017-06-05 ase2017/paper.tex
changed title of our tool paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
added comments in the tool paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
   \includegraphics[width=0.5\textwidth]{screens_dssynth.png}
-  \caption{GUI application for the digital controller synthesis based on the transfer function representation.}
+  \caption{GUI application for the digital synthesis based on the transfer function representation.
+\textcolor{red}{Lennon, can you please split this figure into 4 subfigures?
+The idea is to assign a label for each subfigure to explain a given step of our synthesis process}
+}
   \label{fig:gui-for-tf}

### 2017-06-05 ase2017/paper.tex
added benchmarks description
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
+Our experimental evaluation consist of a set of control system benchmarks,
+which include physical plants for UAV, cruise control, spring-mass damper,
+satellite, direct current (DC) servo motor, helicopter, inverted pendulum,
+magnetic suspension, computer tape driver, robot manipulator, flexible beam,
+guidance system, and an antenna control system~\cite{abate2017, abatecav2017}.
+
 %---------------------------------------------------

### 2017-06-05 ase2017/paper.tex
Fill in the CEGIS section

@@
 
-\textcolor{red}{Cristina: can you please generalize our CEGIS implementation for control here?}
+%\textcolor{red}{Cristina: can you please generalize our CEGIS implementation for control here?}
 
-\textcolor{red}{We have to talk about the naive and AA back-ends, which are based on our CEGIS framework}
+%% The input specification provided to the program synthesizer is of the form
+%% $\exists P .\, \forall a.\, \sigma(a, P)$, where $P$ ranges over functions
+%% (where a function is represented by the program computing it),
+%% $a$ ranges over ground terms, and $\sigma$ is a quantifier-free formula. 
+%% We~interpret the ground terms over some finite domain~$\mathcal{D}$.
+
+The design of our synthesizer consists of two phases, an inductive
+synthesis phase and a validation phase, which interact via a finite
+set of test vectors that is updated incrementally.  Given a stability
+and safety specification, the inductive synthesis procedure tries to
+find a candidate solution satisfying the specification for the given set of test inputs.
+%
+If the synthesis phase succeeds in finding a witness, this witness is
+a candidate solution to the full synthesis formula.  We pass this
+candidate solution to the validation phase, which checks whether it is
+a full solution (i.e., satisfies the specification for all possible
+inputs).  If this is the case, then the algorithm terminates.
+Otherwise, additional information is provided to the inductive
+synthesis phase in the form of a new counterexample that is added to
+the set of test inputs and the loop iterates again.
+
+We use two different instantiations of the synthesiser
+in order to synthesise stable and safe digital
+controllers. The two approaches differ in
+the manner in which they check the safety specification
+for all reachable states.
+
+The first approach uses a multi-staged verification process. 
+Essentially, it starts by devising a
+digital controller that stabilizes the system while remaining safe for a
+pre-selected time horizon and a single initial state; then, it
+employs a multi-staged verification process:
+(i) The first verification stage checks that the candidate
+solution, which we synthesized to be safe for at least one initial
+state, is safe for \emph{all} possible initial states, i.e., does not reach
+an unsafe state within $k$ steps.
+(ii) The second verification stage 
+ restores soundness with respect to the plant's precision
+by using interval arithmetic \cite{moore1966interval} to validate the 
+operations performed by the previous stage. 
+(iii) The third verification stage checks that the current
+$k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
+completeness threshold $\overline{k}$ for the current candidate controller $K$,
+i.e., the number of
+iterations required to sufficiently unwind the closed-loop state-space
+system such that the boundaries are not violated for any larger number of
+iterations, and
+check that $k{\geq}\overline{k}$.
+
+Instead of unfolding the dynamics, the second approach
+employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to
+evaluate all possible progressions of the system simultaneously. 
+Additionally, the second approach uses abstraction refinement,
+enabling us to always start with a very simple description regardless of the
+dynamics complexity, and only expand to more complex models
+when a solution cannot be found.
+
+\textcolor{red}{add more for the second approach}
+
+%\textcolor{red}{We have to talk about the naive and AA back-ends, which are based on our CEGIS framework}
 

### 2017-06-05 ase2017/paper.tex

@@
 %
-\begin{figure}
-  \includegraphics[width=0.5\textwidth]{screens_dssynth.png}
-  \caption{GUI application for the digital synthesis based on the transfer function representation.
-\textcolor{red}{Lennon, can you please split this figure into 4 subfigures?
-The idea is to assign a label for each subfigure to explain a given step of our synthesis process}
-}
+
+\begin{figure}[ht]
+    \centering
+    \subfloat[Define representation and the physical plant.]{
+		\includegraphics[width=0.2\textwidth]{step1.png}
+		\label{step1}}
+		\hfil
+    \subfloat[Determine the implementation and the dynamic range.]{
+	\includegraphics[width=0.2\textwidth]{step2.png}
+		\label{step2}}
+		\hfil
+    \subfloat[Digital controler synthesized.]{
+	\includegraphics[width=0.2\textwidth]{step3.png}
+		\label{step2}}
+		\hfil
+    \subfloat[Step Response for the stable digital controller synthesized]{
+	\includegraphics[width=0.22\textwidth]{step4.png}
+		\label{step3}}
+		\hfil
+    \caption{GUI application for the digital synthesis based on the transfer function representation.}
     \label{fig:gui-for-tf}

### 2017-06-06 ase2017/paper.tex
improved labels of Figure 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %
-
 \begin{figure}[ht]
     \centering
-    \subfloat[Define representation and the physical plant.]{
+    \subfloat[Define the system representation and the physical plant.]{
 		\includegraphics[width=0.2\textwidth]{step1.png}
@@
 		\hfil
-    \subfloat[Determine the implementation and the dynamic range.]{
+    \subfloat[Define implementation features and dynamic range.]{
 	\includegraphics[width=0.2\textwidth]{step2.png}
@@
 		\hfil
-    \subfloat[Digital controler synthesized.]{
+    \subfloat[Digital controller synthesized by DSSynth.]{
 	\includegraphics[width=0.2\textwidth]{step3.png}
@@
 		\hfil
-    \subfloat[Step Response for the stable digital controller synthesized]{
+    \subfloat[Step Response for the synthesized digital controller]{
 	\includegraphics[width=0.22\textwidth]{step4.png}
@@
 		\hfil
-    \caption{GUI application for the digital synthesis based on the transfer function representation.}
+    \caption{DSSynth GUI application for the controller synthesis based on transfer function representation.}
     \label{fig:gui-for-tf}

### 2017-06-12 ase2017/paper.tex
Added implementation section
Added implementation section with reference to CBMC module, description of
instrumentation and CBMC's role as oracle, and all URLs to CBMC 5.7, OVA
and GitHub.

@@
 
-\textcolor{red}{Pascal, can you please review this paragraph?}
-
-\textcolor{blue}{The main development challenge related to \tool is the representation of the
-closed-loop control system models, considering FWL effects, time discretization 
-and quantization noise.  In particular, our implementation consists of $400$
-lines of code related to MATLAB scripts, $585$ and $800$ lines of C code related to the
-naive and abstract accelerator backends. In addition, there are $4000$ lines of C code
-related to utility functions (e.g., interval and fixed-point arithmetic), $50$ lines
-of code to parse MATLAB functions and there are approximately $20$
-control system benchmarks to ensure the \tool's regression.  All those artifacts together
-with documentation and videos are available in a public github repository,
-which is located at \url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}.
+Our CEGIS engine is implemented as an integrated module within the bounded model checker CBMC~\cite{cbmc}.  CBMC
+transforms an ANSI-C representation of our closed-loop control system models into its internal format called
+\emph{GOTO}.  We instrument this internal \emph{GOTO} program for each synthesis or verification scenario accordingly,
+and use CBMC as an oracle to answer our queries.  CBMC itself relies on an underlying SAT or SMT solver to solve the
+resulting formulae.  We model FWL effects, time discretization and quantization noise explicitly using CBMC's
+nondeterminism API.  Our module was included in CBMC~5.7 and is available for
+download\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}.  We further created a VirtualBox OVA image
+with our tool pre-installed, including our MATLAB-generated benchmarks and benchmark shell script with instructions
+to run all benchmarks and reproduce our
+experiments\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}.  The current development branch
+of our tool is available in a public GitHub
+repository\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}.
 

### 2017-06-13 ase2017/paper.tex
+ CEGIS figures

@@
 \usepackage{mathtools}
+\usepackage{tikz}
+\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
+\usetikzlibrary{patterns}
+\usepackage{pgfplots}
 
@@
 
-The first approach uses a multi-staged verification process. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htb]
+{\scriptsize
+\centering
+\resizebox{.5\textwidth}{!}
+{
+\hspace{-1cm}
+  \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
+},
+          row sep=.6cm, column sep=.9cm] {
+   \coordinate (aux1);
+   \& \coordinate (aux2);
+   \&;\\
+   \coordinate (aux3);
+   \& \coordinate (aux4);
+   \&;\\
+   \coordinate (aux5);
+   \& \coordinate (aux6);
+   \&;\\
+   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc 1.Synthesize}};
+   \&
+   complexnode/.pic={ 
+     \node[rectangle,draw,dotted,
+	minimum width=6cm,
+	minimum height=1cm,
+        pattern=north west lines, pattern color=gray!20,
+	label={\sc ~~~~~~~~~~~~Verify},] (verif) {};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc 2.Safety}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=0cm]verif.center) {{\sc 3.Precision}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=2cm]verif.center) {{\sc 4.Complete}};
+     %\node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc 5.Sampling}};
+   } 
+   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
+   \& \\
+   \node[minimum height=0cm] (gp) {\sf Program Search};
+   \&
+   complexnode/.pic={ 
+     \coordinate (aux);
+   \node (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based \\ \sf Verifier};
+   \node (fp)  at ([xshift=0cm]aux.center) {\sf Fixed-point \\ \sf Arithmetic\\ \sf Verifier};
+   \node (sv)  at ([xshift=2cm]aux.center) {\sf Completeness\\ \sf Verifier};
+   %\node (cv)  at ([xshift=3.1cm]aux.center) {\sf Sampling\\Verifier};
+   }   
+    \\
+  };
+
+   \path
+    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$K$} ([yshift=2em]verif1.west)
+    ([yshift=-2em]verif1.west) edge node {C-ex} ([yshift=-2em]synth.east)
+    ([xshift=-5em]fp.north) edge node[align=center]  {T/F} ([xshift=-5em]verif2.south)
+    ([xshift=-5em]sv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif3.south)
+    %([xshift=-5em]cv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif4.south)
+    ([xshift=5em]verif1.south) edge node[align=center] {$K$} ([xshift=5em]bmc.north)
+    ([xshift=5em]verif2.south) edge node[align=center] {$K$} ([xshift=5em]fp.north)
+    ([xshift=5em]verif3.south) edge node[align=center] {$K$} ([xshift=5em]sv.north)
+    %([xshift=5em]verif4.south) edge node[align=center] {$K$} ([xshift=5em]cv.north)
+    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
+    (verif) edge node {PASS} (done)
+    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
+    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$K$} ([xshift=-5em]synth.south)
+    (aux3) edge (synth.north);
+   \path[-]
+   (verif2.north) edge node[align=center] {} ([xshift=0cm]aux6)
+   ([xshift=0cm]aux6) edge node[align=center] {Increase Precision} (aux5)
+   (verif3.north) edge node[align=center] {} ([xshift=6.7cm]aux4)
+   ([xshift=6.7cm]aux4) edge node[align=center] {Increase Unfolding Bound} (aux3);
+   %(verif4.north) edge node[align=center] {} ([xshift=10.5cm]aux2)
+   %([xshift=10.5cm]aux2) edge node[align=center] {Increase Sampling Rate} (aux1);
+
+ \end{tikzpicture}
+}}
+\caption{CEGIS with multi-staged verification}
+\label{fig:CEGIS-precision-increment}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The first approach presented in Figure~\ref{fig:CEGIS-precision-increment}
+uses a multi-staged verification process. 
 Essentially, it starts by devising a
@@
 
-Instead of unfolding the dynamics, the second approach
+\begin{figure}
+\centering
+{\scriptsize
+  \resizebox{.5\textwidth}{!}
+  {
+\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=.8cm, column sep=.2cm] {
+   \coordinate (aux1);
+   \& \coordinate (aux2);
+   \& ;\\
+   \&\node[fill=gray!20,align=center,xshift=-1.5cm] (pre) {{\sc 1. pre-}\\{\sc processing}};
+   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstract};
+   \& \coordinate (aux); \\ 
+   \&
+   \& \node[fill=gray!20,align=center] (synth) {\sc 2. synthesize};
+   \& \node[fill=gray!20,align=center, minimum width=4cm] (verify) {\sc 3. verify ($\phi$)};
+      \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc PASS};
+   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
+   \&
+   \& \node[draw,rectangle,align=center] (KSAT) {Program \\ Search};
+   \& complexnode/.pic={
+     \coordinate (AA);
+     \node[draw,rectangle,align=center] (AAV) at ([xshift=-1.5cm]AA.center) {Abstract\\Acceleration};
+     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm]AA.center) {Abstraction \\ Verifier};
+    }\\
+  };
+  \path
+    (pre.east) edge node[align=center] {$P_a$, $N$,\\ $\phi_\mathit{init}^k$} (abstract.west)
+    (abstract.south) edge node{$(\phi(K), k)$} (synth.north)
+    ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west)
+    (aux) edge (abstract.east) 
+    (verify.east) edge (done.west);
+  \path
+    ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {$K$} ([xshift=0.6cm]synth.south) 
+    ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$(\phi(K),k)$} ([xshift=-.6cm]KSAT.north)
+    ([yshift=.5cm]AAV.east) edge node{\sl $\hat{X}^\#$} ([yshift=.5cm]AAC.west)
+    ([yshift=-.5cm]AAC.west) edge node{$(k,x_0)$} ([yshift=-.5cm]AAV.east)
+    (AAC.north) edge node{\sl $\hat{X}^\#$} ([xshift=4.9cm]verify.south)
+    ([xshift=-5cm]verify.south) edge node{$K$} (AAV.north);
+  \path[-] 
+     (verify.north) edge node {$(k,x_0)$} (aux);
+\end{tikzpicture}
+}
+}
+\caption{Abstraction-based CEGIS}
+\label{fig:CEGARIS} 
+\end{figure}
+
+Instead of unfolding the dynamics, the second approach shown in Figure~\ref{fig:CEGARIS}
 employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to
@@
 
-\textcolor{red}{add more for the second approach}
+%\textcolor{red}{add more for the second approach}
 

### 2017-06-15 benchmark-runner/AACegar/FWL_LTI.c
floating point synthesiser code for abstraction CEGIS

@@ -4,8 +4,8 @@
 #include "FWL_LTI.h"
 #include "types.h"
 #include "system.h"
-#ifdef defined(__CPROVER) && !defined(_FIXEBV)
-  typedef __CPROVER_floatbv[impl.int_bits][impl.frac_bits] controller_floatt;
+#if defined(__CPROVER) && !defined(_FIXEBV)
+  typedef __CPROVER_floatbv[_EXP_BITS][_FRAC_BITS] controller_floatt;
 #endif
 
 void print_vector(char *name,vectort vector)

### 2017-06-15 benchmark-runner/AACegar/FWL_LTI_FWL.h

@@ -38,11 +38,17 @@ int check_vector_bounds(vectort coeffs)
   cnttype i;
   for( i=0; i < _DIMENSION; i++)
   {
-    const control_floatt value=coeffs[i];
 #ifdef __CPROVER 
+  #ifdef _FIXEDBV
+    const control_floatt value=coeffs[i];
     verify_assume(value <= _dbl_max);
     verify_assume(value >= _dbl_min);
+  #else
+    const controller_floatt value=coeffs[i];
+    coeffs[i]=value;
+  #endif
 #else
+    const control_floatt value=coeffs[i];
     if(value > _dbl_max) return 10;
     if(value < _dbl_min) return 10;
 #endif  
@@ -62,10 +68,10 @@ int check_matrix_bounds(matrixt coeffs)
       const control_floatt value=coeffs[i][j];
       verify_assume(value <= _dbl_max);
       verify_assume(value >= _dbl_min);
-      #else
+  #else
       const controller_floatt value=coeffs[i][j];
       coeffs[i][j]=value;
-      #endif
+  #endif
 #else
       const control_floatt value=coeffs[i][j];
       if(value > _dbl_max) return 10;
@@ -105,22 +111,30 @@ signed long int fxp_control_floatt_to_fxp(control_floatt value)
   return tmp;
 }
 
-void fxp_check(control_floatt *value)
+control_floatt fxp_check(control_floatt value)
 {
 #ifdef __CPROVER
-  control_floatt tmp_value=*value;
-  if (tmp_value < _zero) tmp_value=-tmp_value;
-  verify_assume((~_dbl_max&tmp_value)==0);
+  #ifdef _FIXEDBV
+    control_floatt tmp_value=value;
+    if (tmp_value < _zero) tmp_value=-tmp_value;
+    verify_assume((~_dbl_max&tmp_value)==0);
+    return value;
+  #else
+    const controller_floatt fwl_value=value;
+    verify_assume(fwl_value!=0);
+    return fwl_value;
+  #endif
 #else
-  *value=fxp_control_floatt_to_fxp(*value);
-  *value/=_fxp_one;
+  value=fxp_control_floatt_to_fxp(value);
+  value/=_fxp_one;
+  return value;
 #endif
 }
 
 void fxp_check_coeffs(vectort f)
 {
   cnttype i;
-  for(i=0; i < _DIMENSION; i++) fxp_check(&f[i]);
+  for(i=0; i < _DIMENSION; i++) f[i]=fxp_check(f[i]);
 }
 
 int validation()

### 2017-06-15 automatica/paper.tex

--- 2017-06-01 automatica/automatica.tex
@@
 \section{Introduction}
-\textcolor{red}{Cristina: We have to write a new introduction as well.}
-
-%\begin{figure}
-%\begin{center}
-%\includegraphics[height=4cm]{jcaesar.eps}    % The printed column  
-%\caption{Gaius Julius Caesar, 100--44 B.C.}  % width is 8.4 cm.
-%\label{fig1}                                 % Size the figures 
-%\end{center}                                 % accordingly.
-%\end{figure}
-
-% OR
-
-%\begin{figure}
-%\begin{center}
-%\epsfig{file=jcaesar,width=7cm}
-%\caption{Gaius Julius Caesar, 100--44 B.C.}
-%\label{fig1}
-%\end{center}
-%\end{figure}
-
-%\subsection{A subsection}
-%Marcus Tullius Cicero, 106--43 B.C. was a Roman statesman, orator, 
-%and philosopher.  A major figure in the last years of the Republic, 
-%he is best known for his orations against Catiline\footnote{
-%This footnote should be very brief.}
-%and for his mastery of Latin prose \cite{Heritage:92}. He was a 
-%contemporary of Julius Caesar (Fig.~\ref{fig1}).
+Modern implementations of embedded control systems have proliferated with
+the availability of low-cost devices that can perform highly non-trivial
+control tasks, with significant impact in numerous application areas such as
+life sciences, environmental control and robotics~\cite{astrom1997computer, Franklin15}. 
+Correct synthesis is non-trivial, even in cases with restriceted dynamics.
+We examine the case of Linear Time Invariant (LTI) Models, for which the
+synthesis of controllers is well understood. However, the
+use of digital control architectures adds new challenges caused by artifacts
+specific to digital control, such as the effects of finite-precision arithmetic, time
+discretization and quantization noise introduced by A/D and D/A conversion.
+
+While research on digital control is well developed~\cite{astrom1997computer},
+automated and sound control synthesis is challenging, particularly when the
+synthesis objective goes beyond classical stability.  There are recent methods
+for verifying reachability properties of a given controller~\cite{FLD+11}.
+However, these methods have not been generalized to control synthesis.  
+Note that a synthesis algorithm that guarantees stability does not
+ensure safety: the system might transitively visit an unsafe state resulting
+in unrecoverable failure. Programming expertise is a key
+barrier to broad adoption of correct digital controllers, and requires
+considerable knowledge outside of the expertise of many control engineers.
+
+Beyond classical a-posteriori validation in digital control, there has been
+plenty of previous work aiming at \emph{verifying} a given designed
+controller, which however broadly lack automation.  Recent work has studied
+the stability of digital controllers considering implementation aspects,
+i.e., fixed-point arithmetic and the word length~\cite{Bessa16}.  They
+exploit advances in bit-accurate verification of C programs to obtain a
+verifier for software-implemented digital control.
+
+By contrast, we leverage a very recent step-change in the automation and
+scalability of \emph{program synthesis}.  Program synthesis engines use a
+specification as the starting point, and subsequently generate a sequence of
+candidate programs from a given template.  The candidate programs are
+iteratively refined to eventually satisfy the specification.  Program
+synthesizers implementing Counter-Example Guided Inductive Synthesis
+(CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} are now able to generate
+programs for highly non-trivial specifications with a very high degree of
+automation.  Modern synthesis engines combine automated testing, genetic
+algorithms, and SMT-based automated
+reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}.
+
+By combining state-of-the-art synthesis engines we present a tool that
+automatically generates digital controllers for a given continuous plant
+model that are correct by construction.  This approach delivers a high
+degree of automation, promises to reduce the cost and time of development of
+digital control dramatically, and requires considerably less expertise than
+a-posteriori verification.  Specifically, we synthesize stable,
+software-implemented embedded controllers along with a model of a physical
+plant.  Due to the complexity of such closed-loop systems, in this work we
+focus on linear models with known configurations, and perform parametric
+synthesis of stabilizing digital controllers with a number of properties that
+define their desired behaviour.
+
+Our work addresses challenging aspects of the control synthesis problem.
+We perform digital control synthesis over a hybrid model, where the plant
+exhibits continuous behavior whereas the controller operates in discrete
+time and over a quantized domain. In particular, our model evaluates the
+effects of the quantizers (A/D and D/A converters) and of time discretization,
+as well as representation errors introduced by in modelling artifacts
+such as an observer~\cite{astrom1997computer} in a finite precision domain, 
+while reasoning about high level properties such as stability, robustness, safety,
+and response time, which define the behaviour of the system. In particular,
+safety requirements are frequently overlooked in conventional feedback control
+synthesis, but play an important role in systems engineering.
+
+Using state of the art verifiers, we evaluate these models against automatically 
+synthesised controllers using CEGIS-based synsthesis that incorporate the above
+mentioned artifacts in different models of Single-Input/Single-Output (SISO) systems.
+We offer three modes of operation that address different aspects of the problem.
+
+{\em The first  approach} uses a transfer-function based analysis that solves the
+problem of robust stability for closed loop systems for a collection of unstable plants.
+Inthis case, there is no safety specification since we are working in the frequency domain.
+
+{\em The second approach} uses a na\"ive technique that starts by devising a
+digital controller that stabilizes the system while remaining safe for a
+pre-selected time horizon and a single initial state; then, it verifies
+unbounded safety by unfolding the dynamics of the system, considering the
+full hyper-cube of initial states, and checking a {\em completeness
+threshold}~\cite{DBLP:conf/vmcai/KroeningS03}, i.e., the number of
+iterations required to sufficiently unwind the closed-loop state-space
+system such that the boundaries are not violated for any larger number of
+iterations.  As~it requires unfolding up to the completeness threshold, this
+approach is computationally expensive.
+
+Instead of unfolding the dynamics, {\em the third approach}
+employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to
+evaluate all possible progressions of the system simultaneously. 
+Additionally, this approach uses {\em abstraction refinement},
+enabling us to always start with a very simple description regardless of the
+dynamics complexity, and only expand to more complex models
+when a solution cannot be found.
+
+We provide experimental results showing that all our approaches are able to
+efficiently synthesize safe controllers for a set of intricate
+physical plant models taken from the digital control literature.
+
+In summary, this paper makes the following original contributions.
+%
+\begin{enumerate}
+
+\item We automatically generate {\em correct-by-construction} digital
+  controllers using an inductive synthesis approach.  Our application of program
+  synthesis is non-trivial and addresses challenges specific to control
+  systems, such as quantizers and FWL.  In particular, we
+  have found that a two-stage verification engine that continuously refines
+  the precision of the fixed-point representation of the plant yields a
+  speed-up of two orders of magnitude over a conventional one-stage
+  verification engine.
+
+%
+\item  We compute state-feedback controllers that 
+  guarantee a given safety property alongside stability and response time
+  specifications.  Existing methods for controller synthesis rely on transfer
+  function representations, which are inadequate to prove safety requirements.
+%
+\item We provide three novel algorithms: the first, na\"ive one, relies on
+  an unfolding of the dynamics up to a completeness threshold, while the
+  second one is abstraction-based and leverages abstraction refinement and
+  acceleration to improve scalability while retaining soundness.  A third algorithm
+  evaluates systems using transfer functions where no state-space description is given.
+  All three approaches provide sound synthesis of feedback controllers and consider
+  the various sources of imprecision in the implementation of the control
+  algorithm and in the modeling of the plant.
+%
+\item We develop a model for different sources of quantization error and
+  their effect on reachability properties.  We give bounds that ensure the
+  safety of our controllers in a hybrid continuous-digital domain.
+\end{enumerate}
 

### 2017-06-15 automatica/paper.tex
Observable system

@@
 where all members are known, we may now synthesise coefficients that ensure the eigenvalues are smaller than a desired magnitue, thus ensuring that the settling time is too.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{Verification of a Conrollable Observed System}\label{sec:cof_verification}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+\begin{figure*}[htb]
+\centering
+
+\tikzset{add/.style n args={4}{
+    minimum width=6mm,
+    path picture={
+        \draw[circle] 
+            (path picture bounding box.south east) -- (path picture bounding box.north west)
+            (path picture bounding box.south west) -- (path picture bounding box.north east);
+        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+        }
+    }
+ }
+
+\resizebox{1.0\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
+     semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
+    \node[draw=none] (r) {$r_k$};
+    \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,] (gain)at ([xshift=1.2cm]r) {\sc $k_r$};
+
+   \& \node[circle,add={-}{+}{}{}] (circle) {};
+   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$u_k$};
+   \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Kd) at ([xshift=0,yshift=-5.5cm]circle)  {\sc $\mat{K}_d$};
+   \coordinate (kdsouth) at ([yshift=-3cm]Kd);
+
+   \& complexnode/.pic={ 
+      \node[rectangle,dashed,draw,minimum width=3cm,minimum height=1.6cm,label=\textbf{DAC}] (dac) {};
+     \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
+     \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
+     \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
+     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {\sc ZOH};
+   }
+
+   \& complexnode/.pic={ 
+      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2.5cm,yshift=.5cm]plant.center)  {\sc $\mat{B}$};
+      \node[draw=none] (u) at ([xshift=-1cm,yshift=.15cm]B)  {$u(t)$};
+      \node[circle,add={+}{+}{}{}] (p1) at ([xshift=-1.3cm,yshift=.5cm]plant.center) {};
+      \node[draw=none] (xdot) at ([xshift=.85cm,yshift=.15cm]p1)  {$\dot{\vec{x}}(t)$};   
+      \node[rectangle,draw,minimum width=1cm] (int) at ([xshift=.5cm,yshift=.5cm]plant.center) {\sc $\int$};
+      \coordinate (xsouth) at ([xshift=1cm]int);
+      \node[draw=none] (x) at ([xshift=1cm,yshift=.15cm]int)  {$\vec{x}(t)$};   
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (C) at ([xshift=2.7cm,yshift=.5cm]plant.center)  {\sc $\mat{C}$};
+      \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]C)  {$\vec{y}(t)$};   
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (A) at ([xshift=.5cm,yshift=-1cm]plant.center)  {\sc $\mat{A}$};
+      \coordinate (aeast) at ([xshift=1cm]A);
+      \coordinate (awest) at ([xshift=-1.8cm]A);
+    }
+
+   complexnode/.pic={ 
+      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=5cm,label=\textbf{Observer}] (observer)  at ([yshift=-5cm]plant.center) {};
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Bd) at ([xshift=-2.5cm]observer.center)  {\sc $\mat{B}_o$};
+      \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]Bd)  {$u_k$};
+      \node[circle,add={+}{+}{+}{}] (o1) at ([xshift=-1.3cm]observer.center) {};
+      \node[draw=none] (xd) at ([xshift=.85cm,yshift=.15cm]o1)  {$\hat{\vec{x}}_{k+1}$};   
+      \node[rectangle,draw,minimum width=1cm] (delay) at ([xshift=.5cm]observer.center) {\sc $z^{-1}$};
+      \coordinate (xdsouth) at ([xshift=1.3cm]delay);
+      \coordinate (fbsouth) at ([xshift=1.3cm,yshift=-3cm]delay);
+      \node[draw=none] (xdp) at ([xshift=1cm,yshift=.15cm]delay)  {$\hat{\vec{x}}_k$};   
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Cd) at ([xshift=2.7cm]observer.center)  {\sc $\mat{C}_o$};
+      \node[draw=none] (y) at ([xshift=.4cm,yshift=.8cm]Cd)  {$\hat{\vec{y}}_k$};   
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ad) at ([xshift=.5cm,yshift=-1.5cm]observer.center)  {\sc $\mat{A}_o$};
+      \coordinate (adeast) at ([xshift=1.3cm]Ad);
+      \coordinate (adwest) at ([xshift=-1.8cm]Ad);
+      \node[circle,add={-}{}{}{+}] (o2) at ([xshift=2.7cm,yshift=1.5cm]observer.center) {};
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ld) at ([xshift=.5cm,yshift=1.5cm]observer.center)  {\sc $\mat{L}_d$};
+      \coordinate (ldwest) at ([xshift=-1.8cm]Ld);
+      \coordinate (bdwest) at ([xshift=-5.5cm]Bd);
+      \coordinate (uksouth) at ([xshift=-5.5cm,yshift=5.5cm]Bd);
+      \coordinate (o2east) at ([xshift=6.3cm]o2);
+    }
+
+   \& complexnode/.pic={ 
+     \node[rectangle,dashed,draw,minimum width=3.5cm,minimum height=1.6cm,label=\textbf{ADC},] (adc) {};
+     \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
+     \coordinate (switch1) at ([xshift=-1cm]adc.center);
+     \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
+     \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
+     \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
+     \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
+     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]q1)  {$\vec{y}_k$};       
+     \coordinate (ykeast) at ([xshift=1.9cm]q1);
+   } 
+   \& \coordinate (aux1);
+   \& \\
+  };
+
+  \path[->] (v1) edge (q1.south);
+  \path[->] (v2) edge (q2.south);
+  \path[->] (r) edge (gain.west);
+  \path[->] (gain.east) edge (circle.west);
+  \path[->] (circle.east) edge (q2.west);
+  \path       (q2.east) edge (zoh.west);
+  \path[->] (zoh.east) edge (B.west);
+  \path
+   (B.east) edge (p1.west)
+   (p1.east) edge (int.west)
+   (xsouth) edge (aeast)
+   (aeast) edge (A.east)
+   (A.west) edge (awest)
+   (awest) edge (p1.south)
+   (int.east) edge (C.west)
+   (C.east) edge (switch1.west)
+   (switch2) edge (q1.west);
+  \path
+   (q1.east) edge (ykeast)
+   (ykeast) edge (o2east);
+  \path       (uksouth) edge (bdwest);
+  \path[->] (bdwest) edge (Bd.west);
+  \path
+   (Bd.east) edge (o1.west)
+   (o1.east) edge (delay.west)
+   (xdsouth) edge (adeast)
+   (adeast) edge (Ad.east)
+   (Ad.west) edge (adwest)
+   (adwest) edge (o1.south)
+   (o2.west) edge (Ld.east)
+   (Ld.west) edge (ldwest)
+   (ldwest) edge (o1.north)
+   (delay.east) edge (Cd.west)
+   (Cd.north) edge (o2.south)
+   (o2east) edge (o2.east)
+   (xdsouth) edge (fbsouth)
+   (fbsouth) edge (kdsouth);
+  \path[->]  (kdsouth) edge (Kd.south);
+  \path (Kd.north) edge (circle.south);
+ \end{tikzpicture}
+}
+ \caption{Closed-loop digital control system with observer\label{fig:observersystem}}
+\end{figure*}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Stability of an Observed System}\label{sec:cof_stability}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally $\mat{A}_o=\mat{A}_d$, $\mat{B}_o=\mat{B}_d$ and $\mat{C}_o=\mat{C}_d$ for a given time discretization.
+A controllable and observable system will have the following dynamics:
+\begin{equation}
+\tiny
+\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_{k+1}
+=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}_d&\mat{B}_d\mat{K}_d\\ \mat{0}&\mat{A}_d-\mat{L}_d\mat{C}_d\end{array}\right]
+\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_k
++\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
++\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}_d\end{array}\right]\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]
+\end{equation}
+In order for the system to be in canonical form, we must however perform a transformation. The challenge however is that we want the state space dynamics in
+reachable form and the observer error dynamics in observable form. Let 
+\begin{equation}
+\left[\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e'\end{array}\right]=
+\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right] 
+\left[\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e\end{array}\right]
+\end{equation}
+We can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
+
+\begin{align}
+\label{eq:observer_LTI_cf}
+\left [\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e' \end{array}\right]_{k+1}
+=&\left [\begin{array}{cc}\mat{A}_{tp}&\mat{B}_{to}\\ \mat{0}&\mat{A}_{to}\end{array}\right]
+\left [\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e' \end{array}\right]_k
++\mat{B}_{tp} \vec{r}_k
++\mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]\\
+\vec{y}_k=&\mat{C}_{t}\vec{x}_k + \mat{D}_{d}\vec{u}_k\nonumber
+\end{align}
+\begin{align*}
+\mat{A}_{tp}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_d\right)\mat{T}_c^{-1}&
+\mat{A}_{to}=&\mat{T}_o\left(\mat{A}_d-\mat{L}_d\mat{C}_d\right)\mat{T}_o^{-1}\\
+\mat{A}_t=&\left [\begin{array}{cc}\mat{A}_{tp}&\mat{B}_{to}\\ \mat{0}&\mat{A}_{to}\end{array}\right]&
+\mat{B}_{to}=&\mat{T}_c\mat{B}_d\mat{K}_d\mat{T}_o^{-1}\\
+\mat{B}_{tp}=&\left[\begin{array}{c}\mat{T}_c\mat{B}_d\mat{k}_r\\\mat{0}\end{array}\right]&
+\mat{B}_{tn}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_d\end{array}\right]\\
+\mat{T}_с=&\mat{R}_{cf}\mat{R}^{-1}&
+\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
+\mat{L}_d=& \mat{T}_o^{-1}\left[ \begin{array}{c}p_1\\p_2\\p_n\end{array}\right]&
+\mat{C}_t=&\mat{C}_d\mat{T}_c
+\end{align*}
+
+\begin{align*}
+\mat{A}_{tp}=&\left[
+\begin{array}{ccccc}
+0&1&0&\cdots&0\\
+0&0&1&\cdots&0\\
+\vdots&\vdots&\vdots&\ddots&\vdots\\
+0&0&0&\cdots&1\\
+k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
+\end{array}\right]
+\label{eq:cf_SISO_2}
+\end{align*}
+
+Careful examination of these matrices reveals that because the $\mat{A}_t$ is upper block diagonal, the spectrum of $\mat{A}_t$ is equal to the union of the spectrum of $\mat{A}_{tp}$ and $\mat{A}_{to}$ which can be calculated separately.
+Additionally, these correspond to the roots of the polynomials
+\begin{align*}
+\left(z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}\right) \left(z^n+\sum_{i=1}^p{(p_i-a_i)z^{n-i}}\right)
+\end{align*}
+
+As stated in section \ref{ssec:stabspecification}, we use Jury's Criterion to assert this specification.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Safety of an Observed System}\label{sec:cof_safety}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Now that we have established convergence, we may examine the safety specification of the state space.
+In the case of SISO systems, this is given by a range of the input and a range of the output which are considered safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in [\underline{y}\ \ \overline{y}]$).
+Whilst there are other properties we may include in the verification, we will solely focus on these for simplicity of the explanation.
+We will assume that we do not want saturation in our system, hence the control loop has only one mode. We have also identified the quantization noise as a bounded non-deterministic input.
+First we must translate the safety specification into the statespace. Replacing on the second part of equation \eqref{eq:observer_LTI_cf} we obtain
+\begin{equation}
+\Psi := \underline{y}-\overline{\mat{B}\vec{u}}<\mat{C}_t\vec{x}_k<\overline{y}-\underline{\mat{B}\vec{u}}
+\label{eq:of_bounds}
+\end{equation}
+Note that we use the bounds of the input after the transformation by $\mat{B}$ since the matrix may reverse the bounds.
+Equation \eqref{eq:of_bounds} can be solved using linear programming as it describes a polyhedral region in $\mathbb{R}^n$.
+The second step is evaluating the progression of the system over time in order to calculate $\vec{x}_k$ to validte against this specification.
+For this step we require an initial set from which the system progresses.
+Obviously, this set $\vec{x}_0$ must satisfy the specification, otherwise the system will be unsafe to begin with.
+We will accept a specification in the form $\mat{E}\mat{T}\vec{x}_0<\mat{f}$. The presence of $\mat{T}$ is because this will typically be given in the original state-space.
+Accelerating \eqref{eq:observer_LTI_cf}, we obtain:
+\begin{align}
+\label{eq:acc_observer_LTI_cf}
+\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_k
+=&\mat{A}_t^k
+\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_0
++\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tp} \vec{r}_i
++\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right] \nonumber\\
+:&\left [\begin{array}{cc}\mat{E}\mat{T}&\mat{0}\end{array}\right] \left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_0<\mat{f}
+\end{align}
+which would still require us to verify the system for every $k$ up to infinity. Instead we will use abstract acceleration~\cite{}, which translates the formula into
+\begin{align}
+\label{eq:aa_observer_LTI_cf}
+\hat{X}^\#
+=&\mathcal{A}_t X_0+\mathcal{B}_{tp} R + \mathcal{B}_{tn} N\\
+X_0 =&\left \{ \left[\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right] :
+ \left [\begin{array}{cc}\mat{E}\mat{T}&\mat{0}\end{array}\right] \left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_0<\mat{f} \right\}\nonumber\\
+ R =&\{r : \mat{E}_r < \vec{f}_r \}\nonumber\\
+ N=&\left \{ \left[\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right] : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \right \}\nonumber
+\end{align}
+where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A}^k, \mathcal{B}_{tp}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tp}, \mathcal{B}_{tn}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tn}$ are abstract matrices for the system in \eqref{eq:observer_LTI_cf}.
+It is worth noting that $r$ is a non-deterministic parametric input (\emph{ie} $\forall k>0, r_{k+1} =r_k$) whereas the set N is composed of non-deterministic variable inputs.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Stability of an Digitally Observed System}\label{sec:cof_fwl_stability}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+Thus far we have presented a verification procedure for a continuous plant in discretized time domain (\emph{ie} the
+range of the quatizers is still $\mathbb{R}$. The next step we must reaize is that the controller and the observer
+exist in a digital program, hence their domain is $\mathbb{R}\langle I,F,E\rangle$. This has two separate effects
+on the model. If we recall equation \eqref{eq:to_of}, the matrices of the observer and the controller  are not necessarily those of the plant.
+In fact we have $\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$, $\mat{A}_o,\mat{B}_o,\mat{C}_o, \mat{K}_d, \mat{L}_d \in \mathbb{R}\langle I,F,E\rangle^*$
+Where $*$ represents the appropriate dimension for each matrix.
+Unfortunately this means that although combined matrices such as $\mat{A}_t$ are in the reals, they suffer from
+the fixed word restrictions in their composing matrices.
+
+When our observer is implemented using a finite precision controller, new problems arise due to the FWL effects.
+Let $\mat{A}_o$, $\mat{B}_o$ and $\mat{C}_o$ be the dynamics represented in
+$\mathbb{R} \langle I , F, E \rangle$, and  $\mat{A}_e=\mat{A}_d-\mat{A}_o$, $\mat{B}_e=\mat{B}_d-\mat{B}_o$,
+and $\mat{C}_e=\mat{C}_d-\mat{C}_o$ their corresponding errors.
+Equation \eqref{eq:observer_LTI_cf} will become
+\begin{align}
+\tiny
+\left [\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e' \end{array}\right]_{k+1}
+=&\tiny \left [\begin{array}{cc}\mat{A}_{tp}+\mat{B}_{eo}&\mat{B}_{to}\\ \mat{A}_{eo}&\mat{A}_{to}\end{array}\right]
+\left [\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e' \end{array}\right]_k
++\mat{B}_{tp} \vec{r}_k
++\mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]\nonumber\\
+\tiny\vec{y}_k=&\tiny\mat{C}_{t}\vec{x}_k + \mat{D}_{d}\vec{u}_k
+\label{eq:observer_LTI_FWL_cf}
+\end{align}
+\begin{align*}
+\mat{A}_{tp}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_d\right)\mat{T}_c^{-1}&
+\mat{A}_{to}=&\mat{T}_o\left(\mat{A}_o-\mat{L}_o\mat{C}_o\right)\mat{T}_o^{-1}\\
+\mat{A}_t=&\left [\begin{array}{cc}\mat{A}_{tp}&\mat{B}_{to}\\ \mat{0}&\mat{A}_{to}\end{array}\right]&
+\mat{B}_{to}=&\mat{T}_c\mat{B}_o\mat{K}_d\mat{T}_o^{-1}\\
+\mat{B}_{tp}=&\left[\begin{array}{c}\mat{T}_c\mat{B}_o\mat{k}_r\\\mat{0}\end{array}\right]&
+\mat{B}_{tn}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_o\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_d\end{array}\right]\\
+\mat{T}_с=&\mat{R}_{cf}\mat{R}^{-1}&
+\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
+\mat{L}_d=& \mat{T}_o^{-1}\left[ \begin{array}{c}p_1\\p_2\\p_n\end{array}\right]&
+\mat{A}_{eo}=&\mat{T}_o\left(\mat{A}_e+\mat{L}_o\mat{C}_e\right)\mat{T}_o^{-1}\\
+\mat{B}_{eo}=&\mat{T}_c\mat{B}_e\mat{K}_d\mat{T}_o^{-1}&
+\mat{C}_t=&\mat{C}_d\mat{T}_c
+\end{align*}
+
+The first effect of this new equation is that the matrix is no longer upper diagonal. We must therefore compensate for the errors introduced in order to find a stable solution.
+We can use Gershgoring disks to limit the error in the expected eigenvalues.
+Let $\delta_o=\max(|\mat{A}_{ei*}|_2)$ (\emph{i.e.} the largest row norm in $\mat{A}_e$) be the largest error bound for any eigenvalue in $\mat{A}_e$.
+Then $\forall i \in [1\ n], |\lambda_{oi}-\hat{\lambda}_{oi}|<\delta_o$,where $\lambda_{oi}$ are the true eigenvalues of the observer and $\hat{\lambda}_{oi}$ the eigenvalues of the perturbed observer.
+We note that in the case of stability we only care about the error with respect to the unit circle, which is equivalent to upper bounding the estimation of the largest eigenvalue.
+Hence given a desired upper value $\overline{\lambda}$, we apply Iurys criterion on the polynomial.
+\begin{equation}
+P_o'=\sum_{j=0}^n c_j\overline{\lambda'}^{n-j}s^j : \overline{\lambda'}=(1+\delta_o)\overline{\lambda}
+\end{equation}
+Inthe case of the reachable eigenvalues, the procedure is the same except that we obtain our bound $\delta_c=\max(|\mat{A}_{e*i}+\mat{B}_{e*i}|_2)$ (\emph{i.e.} the largest column norm in $[\mat{A}_e\ \mat{B}_e]^T$) and apply Jury's Criterion over
+\begin{equation}
+P_r'=\sum_{j=0}^n c_j\overline{\lambda'}^{n-j}s^j : \overline{\lambda'}=(1+\delta_c)\overline{\lambda}
+\end{equation}
+
+As a final annotation, we remark that the safety specification must be applied to the model described in this section, accounting for the representation errors of the FWL domain.
+
 %---------------janus----------------

### 2017-06-16 cav2017/paper.tex
rename to paper.tex

--- 2017-05-05 cav2017/cav2017.tex
@@
 Dario Cattaruzza\inst{1} \and
-Lucas Cordeiro\inst{1} \and
+Lucas Cordeiro\inst{1,2} \and
 \mbox{Cristina David}\inst{1} \and
@@
 enabling us to always start with a very simple description regardless of the
-complexity of the overall dynamics, and only expand to more complex models
+dynamics complexity, and only expand to more complex models
 when a solution cannot be found.
@@
 %picasso2002construction} 
-introduces attractive invariant sets as a mechanism
+introduces invariant sets as a mechanism
 to bound the quantization error effect on stabilization as an invariant set
-that always converges toward the controllable set.  In a similar fashion,
-\cite{liberzon2003hybrid} evaluates the dynamics of the quantization error
-and bounds its trajectory to a known region over a finite period of time. 
+that always converges toward the controllable set.  Similarly,
+\cite{liberzon2003hybrid} evaluates the quantization error dynamics
+and bounds its trajectory to a known region over a finite time period. 
 This technique works for both linear and non-linear systems.
@@
 specify the continuous plant, and with initial states set as $x(0)$.  While
-ideally we would like to work on the continuous-time plant, in this work
+ideally we intend to work on the continuous-time plant, in this work
 Eq.~\eqref{eq:ode} is soundly discretized in time~\cite{fadali} into
@@
 We are interested in the synthesis of digital feedback control algorithms, 
-as implemented on modern Field-Programmable Gate Arrays or Digital Signal Processors. 
+as implemented on Field-Programmable Gate Arrays or Digital Signal Processors. 
 The most basic feedback architecture is the state feedback one, 
@@
 %However, a safe system will always be stable.  
-In~this work, the safety property is expressed as follows:
+In~this work, the safety property is expressed as:
 %
@@
 \begin{proof}
-Consider the set of initial states, $X_0$, which we assume to be convex since it's a hypercube. 
+Consider the set of initial states, $X_0$, which we assume to be convex since it is a hypercube. 
 Name $v_i$ its vertexes, where $i=1,\ldots, 2^n$.  
@@
 We illustrate our approach with an example,
-extracted from the literature~\cite{Franklin15}.
+extracted from~\cite{Franklin15}.
 %
@@
 The \textit{Computer Tape Driver} plant describes a system to read and write data 
-on a storage device in a computer.
+on a storage device.
 
@@
 Inverted Pendulum appears to be a two-output system, but it is treated as
-two SISO models during the experiments.  For the sake of simplicity all the
-state measurements are assumed to be available.  
+two SISO models during the experiments.  All the
+state measurements are assumed to be available  
 %In practice, state estimators should be designed in order to obtain an estimate of the states from the single output.  
-(Current work targets the extension of our framework to observer-based synthesis.)
+(current work targets the extension of our framework to observer-based synthesis).
 
@@
 continuous-time case, to models with output-based control architectures
-(with the use of observers), and to the consideration of more complex specifications 
-and of additional performance requirements in the synthesis of digital controllers.
+(with the use of observers), and to the consideration of more complex specifications. 
+%and of additional performance requirements in the synthesis of digital controllers.
 
@@
 whether the noise is correlated, hence we may use them to over-approximate
-the effect of the noise on the state space progression over time.  The
+the noise effect on the state space progression over time.  The
 resulting dynamics are

### 2017-06-16 ase2017/paper.tex
added comments in the tool paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-%\textcolor{red}{add more for the second approach}
+\textcolor{red}{Dario: Can you please expand a bit further the second approach}
 
@@
 repository\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}.
+
+\textcolor{red}{Pascal: May I ask you to briefly mention the modules and also the LOC associated to each module?
+The tool paper reviewers usually like to know about the tool's complexity (i.e., number of modules/components and LOC).}
 

### 2017-06-19 ase2017/paper.tex
improved Figure 1 of our tool paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
reviewed abstract of the tool paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 We present an automated MATLAB Toolbox, named as DSSynth 
-(Digital System Synthesis), to synthesize stable and safe digital-control 
-systems for physical plants represented as linear time-invariant
-systems with single-input and single-output. DSSynth synthesizes digital 
-controllers w.r.t. the stability and safety specifications, considering finite word-length 
-effects for physical plants represented by transfer-function or state-space 
-equations. DSSynth considers fixed-point numerical representation for the 
-digital controller and dynamic input ranges for the closed-loop control system. 
+(Digital-System Synthesizer), to synthesize stable and safe digital controllers 
+for physical plants represented as linear time-invariant
+systems with single-input and single-output. In particular, DSSynth synthesizes digital 
+controllers w.r.t. the stability and safety specifications by taking into account finite word-length 
+effects. DSSynth considers the complete range
+of approximations, including time discretization, quantization effects, 
+and finite-precision arithmetic and its rounding errors. 
 Currently, there are two DSSynth toolbox versions: command-line and 
-MATLAB application. The resulting toolbox enables application of synthesis to 
-real-world systems by control engineers.
+MATLAB application for synthesizing digital controllers for physical plants 
+represented by transfer-function or state-space equations. The resulting toolbox 
+enables application of program synthesis to real-world systems by control engineers.
 \end{abstract}
@@
 Fig.~\ref{fig:typical-control-system} shows a typical closed-loop digital control system.
-
-\textcolor{red}{Cristina, can you please draw this figure in tikz?}
+%
 \begin{figure}[ht!]

### 2017-06-19 ase2017/paper.tex
reviewed introduction of the tool paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 offering mathematical guarantees about the stability and the desired 
-performance of closed-loop systems, where plant states or outputs 
+performance of closed-loop systems, where states or outputs of discrete plant $G(z)$ 
 are fed back and compared to a reference signal to which a (designed) 
-controller should maintain a set of control objectives~\cite{astrom1997computer}. 
+controller $C(z)$ should maintain a set of control objectives~\cite{astrom1997computer}. 
 Fig.~\ref{fig:typical-control-system} shows a typical closed-loop digital control system.
@@
 There are various mathematical representations for digital control
-systems,  e.g.,  difference  equations,  state-space,  and
-transfer functions. Here, linear time-invariant (LTI) systems 
+systems,  e.g.,  difference  equations, transfer functions and state-space
+equations. Here, linear time-invariant (LTI) systems 
 with single-input and single-output (SISO) are considered and 
-represented by transfer function and state space. LTI systems 
-are used in several applications to support non-trivial tasks when 
+represented by transfer functions or state space equations. LTI systems 
+are used in several engineering applications to support non-trivial tasks when 
 applied to embedded systems (e.g., robot manipulator, power plants 
 and guidance system). The following expression presents the general form 
-of a digital control system using the transfer function representation:
+of a discrete plant or a digital controller based on the transfer function representation:
 %
@@
 %
-\noindent where $z^{-1}$ is called backward-shift operator, $A(z)$ and $B(z)$ are 
-the denominator and numerator polynomials, respectively.
+\noindent where $z^{-1}$ is called backward-shift operator; $A(z)$ and $B(z)$ are 
+the denominator and numerator polynomials, respectively; and $N$ and $M$
+represent the denominator and numerator polynomials order, respectively.
 %
@@
 \noindent where $A$, $B$, $C$ and $D$ are matrices that fully specify a digital system. 
-
+%
 Controllers synthesis for LTI systems is richly studied 
-by different researchers~\cite{mazo2010pessoa,DBLP:conf/emsoft/RavanbakhshS16,economakos2016automated}; 
+in the literature~\cite{mazo2010pessoa,DBLP:conf/emsoft/RavanbakhshS16,economakos2016automated}; 
 however, there are many challenges when 
@@
 Recently, a new methodology to synthesize digital control systems was proposed, 
-named as DSSynth (Digital System Synthesis)~\cite{abate2017, abatecav2017}, 
+named as DSSynth (Digital-System Synthesizer)~\cite{abate2017, abatecav2017}, 
 which is based on the Counter-Example Guided Inductive Synthesis 
-(CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. Here, CEGIS is used
-as a program synthesis engine that is able to produce controllers for highly non-trivial 
+(CEGIS) approach~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. Here, CEGIS is used
+as a program synthesis engine that is able to produce digital controllers for highly non-trivial 
 control system specifications with a very high degree of automation. Program synthesis engines 
@@
 programs from a given template. The candidate programs are iteratively refined to eventually 
-satisfy the specification. Modern synthesis engines combine automated testing, genetic algorithms 
+satisfy the specification. Modern synthesis engines as the one used here combine automated testing, genetic algorithms 
 and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
 DSSynth synthesizes stable digtal controllers using that CEGIS-based approach,
-for a given physical plant represented by transfer function or state-space equations~\cite{abate2017,abatecav2017}.
+for a given physical plant represented by either transfer functions or state-space equations~\cite{abate2017,abatecav2017}.
 
@@
 using symbolic model checking techniques based on Boolean Satisfiability (SAT) and 
-Satisfiability Modulo Theories (SMT) solvers, given the physical plant and the digital controller. 
-However, there is no toolbox in MATLAB to perform digital controller synthesis; in particular, based on 
-CEGIS considering FWL effects.
+Satisfiability Modulo Theories (SMT) solvers. Pessoa~\cite{mazo2010pessoa} is another 
+toolbox applied to the synthesis of correct-by-design digital controllers. 
+In particular, Pessoa is based on approximate bisimulation, which allows control engineers to replace differential equations, 
+describing a physical plant, by a respective finite-state machine. However, Pessoa does not take advantage of
+recent advances in bit-accurate verification of programs to synthesize controllers w.r.t. FWL effects.
+As a result, there is no other MATLAB toolbox to perform digital controller synthesis based on 
+program synthesis engines and considering the complete range of approximations, including time discretization, 
+quantization effects, and finite-precision arithmetic and its rounding errors.
 
-The present paper addresses this problem and describes a MATLAB toolbox for DSSynth~\cite{abate2017, abatecav2017} 
+The present paper addresses this problem and describes a toolbox for the DSSynth tool~\cite{abate2017, abatecav2017} 
 in MATLAB's environment named as \tool. The main advantage regarding the use of a MATLAB toolbox 
-lies on designing physical plants in MATLAB and then promptly synthesizing a stable digital controller. 
-Additionally, when using the \tool, an engineer is able to design a digital system with MATLAB, 
-through transfer-function or state-space representations, consider low-level systems parameters 
-(implementation features and numerical format), and then obtains a stable synthesized digital-controller.
+lies on designing physical plants in MATLAB and then promptly synthesizing a stable and safe digital controller,
+considering the complete range of approximations. 
+Additionally, when using the \tool, an engineer is able to model a physical plant with MATLAB, 
+through transfer-function or state-space representations, considering low-level systems parameters 
+(implementation features and numerical format), and then obtain a stable and safe synthesized digital-controller.
 

### 2017-06-19 automatica/paper.tex
nomenclature

@@
 We can use Gershgoring disks to limit the error in the expected eigenvalues.
-Let $\delta_o=\max(|\mat{A}_{ei*}|_2)$ (\emph{i.e.} the largest row norm in $\mat{A}_e$) be the largest error bound for any eigenvalue in $\mat{A}_e$.
+Let $\delta_o=\max(|\mat{A}_{ei*}|_2)$ (\emph{i.e.} the largest row norm in $\mat{A}_e$) be the largest error bound for any eigenvalue in $\mat{A}_t$ that corresponds to the observer.
 Then $\forall i \in [1\ n], |\lambda_{oi}-\hat{\lambda}_{oi}|<\delta_o$,where $\lambda_{oi}$ are the true eigenvalues of the observer and $\hat{\lambda}_{oi}$ the eigenvalues of the perturbed observer.

### 2017-06-19 ase2017/paper.tex

@@
 \usepackage{graphicx}
+\usepackage{epstopdf} %converting to PDF
 \usepackage{subfig} 
@@
 employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to
-evaluate all possible progressions of the system simultaneously. 
-Additionally, the second approach uses abstraction refinement,
-enabling us to always start with a very simple description regardless of the
-dynamics complexity, and only expand to more complex models
-when a solution cannot be found.
-
-\textcolor{red}{Dario: Can you please expand a bit further the second approach}
+evaluate all possible progressions of the system simultaneously. This eliminates the need for
+a completenes threshold since the time horizon is always infinite.
+Since this model is based on abstraction, we initially perform the synthesis over a basic
+model that abstracts away the complexity of the specification and is only refined to a more
+complex model when a counterexample is found. Thus we may only look at the gain of the
+system to synthesise a controller and add further restrictions on specific sections of the reach
+tube when these prove to invalidate the solution. The use of Counter-Example Guided 
+Abstraction Refinement results in much faster synthesis and verification since it is applied to
+both phases,allowing for faster results whilst maintaining soundness for an infinite time horizon.
 

### 2017-06-20 ase2017/paper.tex
reviewed paragraph about AA in the tool paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \centering
-\includegraphics[width=0.35\textwidth]{closedloopseries.pdf}
+\includegraphics[width=0.4\textwidth]{closedloopseries.pdf}
 \caption{Typical Closed-loop Control System.}
@@
 model that abstracts away the complexity of the specification and is only refined to a more
-complex model when a counterexample is found. Thus we may only look at the gain of the
+complex model when a counterexample is found. Thus, we may only look at the gain of the
 system to synthesise a controller and add further restrictions on specific sections of the reach
-tube when these prove to invalidate the solution. The use of Counter-Example Guided 
+tube when these prove to invalidate the solution. The use of Counterexample-Guided 
 Abstraction Refinement results in much faster synthesis and verification since it is applied to
-both phases,allowing for faster results whilst maintaining soundness for an infinite time horizon.
+both phases, allowing for faster results whilst maintaining soundness for an infinite time horizon.
 

### 2017-06-21 cav2017/cav2017.tex
Fixed reference to figure

@@
 $q_2=q_\mathit{dac}$.  This is illustrated in
-Fig.~\ref{ssec:statefeedbackcontrol} where $Q_1$ is the quantizer of the ADC
+Fig.~\ref{fig:digitalsystem} where $Q_1$ is the quantizer of the ADC
 and $Q_2$ the quantizer for the DAC.  These bounds hold irrespective of
 whether the noise is correlated, hence we may use them to over-approximate
-the effect of the noise on the state space progression over time.  The
+the noise effect on the state space progression over time.  The
 resulting dynamics are

### 2017-06-21 benchmark-runner/AACegar/FWL_LTI.c
Observer files

@@ -32,8 +32,8 @@ void print_matrix(char *name,matrixt matrix)
 #endif
 }
 
-vectort plant_cbmc,controller_cbmc;
-matrixt transform_cbmc;
+vectort plant_cbmc,controller_cbmc,observer_cbmc;
+matrixt transform_cbmc,observer_transform_cbmc;
 matrixt loop_cbmc;
 
 #include "FWL_LTI_FWL.h"
@@ -78,7 +78,14 @@ int main()
 #ifndef __CPROVER
   print_matrix("dynamics",dynamics);
   print_matrix("loop",loop_cbmc);
-#endif  
+#endif
+  vectort polynomial;
+  control_floatt speed_factor;
+  for (i=0;i<_DIMENSION;i++)
+  {
+    polynomial[i]=plant_cbmc[i];
+    for (j=0;j<=i;j++) polynomial[i]*=speed_factor;
+  }
   result=check_stability_closedloop(plant_cbmc);
 #ifndef __CPROVER
   printf("stability=%d\n",result);

### 2017-06-21 benchmark-runner/AACegar/FWL_LTI.h

@@ -3,10 +3,10 @@
 #ifdef __CPROVER
 #ifndef _FIXEDBV
   #ifndef _EXPONENT_WIDTH
-    #define _EXPONENT_WIDTH 8
+    #define _EXPONENT_WIDTH 16
   #endif
   #ifndef _FRACTION_WIDTH
-  #define _FRACTION_WIDTH 24
+  #define _FRACTION_WIDTH 11
   #endif
   typedef __CPROVER_floatbv[_EXPONENT_WIDTH][_FRACTION_WIDTH] control_floatt;
   control_floatt _imp_max=(((1 <<(_EXPONENT_WIDTH-1))-1)<<1)+1;

### 2017-06-21 benchmark-runner/AACegar/FWL_LTI_iters.h

@@ -64,7 +64,7 @@ void accelerateInputs()
   }
   
 }
-./axelerator -u -p -ii -mpi 256 -synth CEGIS -params "p=2,q=1,f=1,m=256:16:8" -dynamics "[0.90122,1.3429e-08;7.4506e-09,0]" -init "[cube<.5]" -isense "[128;0]" -inputs "[1>-1;1<1]" -sguard "[cube<1]" -control "[0]"
+
 #ifdef _NUM_ITERATIONS
 
 void checkIteration(vectort point,matrixt transform,int input_index)

### 2017-06-21 benchmark-runner/AACegar/FWL_LTI_nondet.h

@@ -22,7 +22,7 @@ void make_nondet_coeffs(vectort src,vectort uncertainty,vectort dst)
 {
   cnttype i=0;
   for(i = 0; i < _DIMENSION; i++)
-#ifdef __CPROVER
+#ifdef __CPROVER 
     if(uncertainty[i] > _zero)
     {
       control_floatt min=src[i] -uncertainty[i];

### 2017-06-21 benchmark-runner/AACegar/FWL_LTI_stability.h

@@ -21,6 +21,18 @@ void make_closed_loop()
 #endif
   for (i = 0;i<_DIMENSION;i++) plant_cbmc[i]-=controller_cbmc[i];
   
+#ifdef _OBSERVER
+  make_nondet_transform(observer_transform.coeffs,observer_transform.uncertainty,observer_transform_cbmc);
+  fxp_check_coeffs(observer);
+  for (i = 0;i<_DIMENSION;i++)
+  {
+    observer_cbmc[i]=0;
+    for (j = 0;j<_DIMENSION;j++)
+    {
+      observer_cbmc[i]+=observer_transform_cbmc[j][i]*observer[j];
+    }
+  }
+#endif
 }
 
 signed int check_stability_closedloop(vectort a)

### 2017-06-21 automatica/paper.tex
Formatting changes

--- 2017-06-15 automatica/paper.tex
@@
 \section{Introduction}
+
 Modern implementations of embedded control systems have proliferated with
@@
 control tasks, with significant impact in numerous application areas such as
-life sciences, environmental control and robotics~\cite{astrom1997computer, Franklin15}. 
-Correct synthesis is non-trivial, even in cases with restriceted dynamics.
-We examine the case of Linear Time Invariant (LTI) Models, for which the
-synthesis of controllers is well understood. However, the
-use of digital control architectures adds new challenges caused by artifacts
-specific to digital control, such as the effects of finite-precision arithmetic, time
-discretization and quantization noise introduced by A/D and D/A conversion.
+life sciences, environmental control and robotics~\cite{astrom1997computer,
+Franklin15}.  Correct synthesis is non-trivial, even in cases with
+restriceted dynamics.  We examine the case of Linear Time Invariant (LTI)
+Models, for which the synthesis of controllers is well understood.  However,
+the use of digital control architectures adds new challenges caused by
+artifacts specific to digital control, such as the effects of
+finite-precision arithmetic, time discretization and quantization noise
+introduced by A/D and D/A conversion.
 
@@
 
-Our work addresses challenging aspects of the control synthesis problem.
-We perform digital control synthesis over a hybrid model, where the plant
+Our work addresses challenging aspects of the control synthesis problem.  We
+perform digital control synthesis over a hybrid model, where the plant
 exhibits continuous behavior whereas the controller operates in discrete
 time and over a quantized domain.  In particular, our model evaluates the
-effects of the quantizers (A/D and D/A converters) and of time discretization,
-as well as representation errors introduced by in modelling artifacts
-such as an observer~\cite{astrom1997computer} in a finite precision domain, 
-while reasoning about high level properties such as stability, robustness, safety,
-and response time, which define the behaviour of the system. In particular,
-safety requirements are frequently overlooked in conventional feedback control
-synthesis, but play an important role in systems engineering.
-
-Using state of the art verifiers, we evaluate these models against automatically 
-synthesised controllers using CEGIS-based synsthesis that incorporate the above
-mentioned artifacts in different models of Single-Input/Single-Output (SISO) systems.
-We offer three modes of operation that address different aspects of the problem.
-
-{\em The first  approach} uses a transfer-function based analysis that solves the
-problem of robust stability for closed loop systems for a collection of unstable plants.
-Inthis case, there is no safety specification since we are working in the frequency domain.
+effects of the quantizers (A/D and D/A converters) and of time
+discretization, as well as representation errors introduced by in modelling
+artifacts such as an observer~\cite{astrom1997computer} in a finite
+precision domain, while reasoning about high level properties such as
+stability, robustness, safety, and response time, which define the behaviour
+of the system.  In particular, safety requirements are frequently overlooked
+in conventional feedback control synthesis, but play an important role in
+systems engineering.
+
+Using state of the art verifiers, we evaluate these models against
+automatically synthesised controllers using CEGIS-based synsthesis that
+incorporate the above mentioned artifacts in different models of
+Single-Input/Single-Output (SISO) systems.  We offer three modes of
+operation that address different aspects of the problem.
+
+{\em The first  approach} uses a transfer-function based analysis that
+solves the problem of robust stability for closed loop systems for a
+collection of unstable plants.  Inthis case, there is no safety
+specification since we are working in the frequency domain.
 
@@
 We provide experimental results showing that all our approaches are able to
-efficiently synthesize safe controllers for a set of intricate
-physical plant models taken from the digital control literature.
+efficiently synthesize safe controllers for a set of intricate physical
+plant models taken from the digital control literature.
 
@@
   verification engine.
-
 %
@@
   second one is abstraction-based and leverages abstraction refinement and
-  acceleration to improve scalability while retaining soundness.  A third algorithm
-  evaluates systems using transfer functions where no state-space description is given.
-  All three approaches provide sound synthesis of feedback controllers and consider
-  the various sources of imprecision in the implementation of the control
-  algorithm and in the modeling of the plant.
+  acceleration to improve scalability while retaining soundness.  A third
+  algorithm evaluates systems using transfer functions where no state-space
+  description is given.  All three approaches provide sound synthesis of
+  feedback controllers and consider the various sources of imprecision in
+  the implementation of the control algorithm and in the modeling of the
+  plant.
 %
@@
 
-The work in~\cite{hscc-paper} synthesizes stabilizing
-controllers for continuous plants given as transfer functions by exploiting
-bit-accurate verification of software-implemented digital
-controllers~\cite{Bessa16}.  While this work also uses CEGIS,
-the approach is restricted to digital controllers for stable closed-loop
-systems given as transfer function models: 
-this results in  a static check on their coefficients.  
-By contrast, in the current paper we consider a state-space representation of the physical system, 
-which requires ensuring the specification over actual traces of the model, 
-alongside the numerical soundness required by the effects of discretisation and finite-precision errors.   
-A state-space model has known advantages over the transfer function
-representation~\cite{Franklin15}: it naturally generalizes to multivariate systems
-(i.e., with multiple inputs and outputs); 
-and it allows synthesis of control systems with guarantees on the internal dynamics, e.g.,
-to synthesize controllers that make the closed-loop system \emph{safe}.  Our
+The work in~\cite{hscc-paper} synthesizes stabilizing controllers for
+continuous plants given as transfer functions by exploiting bit-accurate
+verification of software-implemented digital controllers~\cite{Bessa16}. 
+While this work also uses CEGIS, the approach is restricted to digital
+controllers for stable closed-loop systems given as transfer function
+models: this results in a static check on their coefficients.  By contrast,
+in the current paper we consider a state-space representation of the
+physical system, which requires ensuring the specification over actual
+traces of the model, alongside the numerical soundness required by the
+effects of discretisation and finite-precision errors.  A state-space model
+has known advantages over the transfer function
+representation~\cite{Franklin15}: it naturally generalizes to multivariate
+systems (i.e., with multiple inputs and outputs); and it allows synthesis of
+control systems with guarantees on the internal dynamics, e.g., to
+synthesize controllers that make the closed-loop system \emph{safe}.  Our
 work focuses on the \emph{safety} of internal states, which is usually
@@
 physical system to an equivalent finite-state machine and on the computation
-of reachability properties thereon. 
-Based on this safety specification, \mbox{Pessoa} can synthesize embedded controller
-software for a range of properties.  The embedded controller software can be
-more complicated than the state-feedback control we synthesize, and the
-properties available cover more detail. 
-However, relying on state-space discretization \mbox{Pessoa} is likely to incur in scalability limitations. 
-Along this research line, \cite{Anta2010,liu16} studies the synthesis of digital controllers for continuous dynamics, 
-and \cite{zamani2014} extends the approach to the recent setup of Network Control Systems.
+of reachability properties thereon.  Based on this safety specification,
+\mbox{Pessoa} can synthesize embedded controller software for a range of
+properties.  The embedded controller software can be more complicated than
+the state-feedback control we synthesize, and the properties available cover
+more detail.  However, relying on state-space discretization \mbox{Pessoa}
+is likely to incur in scalability limitations.  Along this research line,
+\cite{Anta2010,liu16} studies the synthesis of digital controllers for
+continuous dynamics, and \cite{zamani2014} extends the approach to the
+recent setup of Network Control Systems.
 
 \textbf{Discretization Effects -}
-The classical approach to control synthesis has often disregarded digitalization effects, 
-whereas more recently modern techniques have focused on
-different aspects of discretization, including delayed
-response~\cite{Duggirala2015} and finite word length (FWL) semantics, 
-with the goal either to verify (e.g.,~\cite{daes20161}) or to optimize
+The classical approach to control synthesis has often disregarded
+digitalization effects, whereas more recently modern techniques have focused
+on different aspects of discretization, including delayed
+response~\cite{Duggirala2015} and finite word length (FWL) semantics, with
+the goal either to verify (e.g.,~\cite{daes20161}) or to optimize
 (e.g.,~\cite{oudjida2014design}) given implementations.
@@
 is the error in the dynamics caused by the inability to represent the exact
-state of the physical system, while the second relates to rounding and saturation errors
-during computation.  In~\cite{fialho1994stability}, a stability measure
-based on the error of the digital dynamics ensures that the deviation
-introduced by FWL does not make the digital system unstable.  A~more recent
-approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$-calculus to
-directly model the digital controller so that the selected parameters are
-stable by design.  The analyses in~\cite{DBLP:conf/hybrid/RouxJG15,
-DBLP:conf/hybrid/WangGRJF16} rely on an invariant computation on the
-discrete system dynamics using Semi-Definite Programming (SDP).  While the
-former uses bounded-input and bounded-output (BIBO) properties to determine
-stability, the latter uses Lyapunov-based quadratic invariants.  In both
-cases, the SDP solver uses floating-point arithmetic and soundness is
-checked by bounding the error.  An alternative is~\cite{park2016scalable},
-where the verification of given control code is performed against a known
-model by extracting an LTI model of the code by symbolic execution:  
-to account for rounding errors, an upper bound is introduced in the
-verification phase.  The work in \cite{picasso2003stabilization}
-introduces invariant sets as a mechanism
-to bound the quantization error effect on stabilization as an invariant set
+state of the physical system, while the second relates to rounding and
+saturation errors during computation.  In~\cite{fialho1994stability}, a
+stability measure based on the error of the digital dynamics ensures that
+the deviation introduced by FWL does not make the digital system unstable. 
+A~more recent approach~\cite{DBLP:journals/automatica/WuLCC09} uses
+$\mu$-calculus to directly model the digital controller so that the selected
+parameters are stable by design.  The analyses
+in~\cite{DBLP:conf/hybrid/RouxJG15, DBLP:conf/hybrid/WangGRJF16} rely on an
+invariant computation on the discrete system dynamics using Semi-Definite
+Programming (SDP).  While the former uses bounded-input and bounded-output
+(BIBO) properties to determine stability, the latter uses Lyapunov-based
+quadratic invariants.  In both cases, the SDP solver uses floating-point
+arithmetic and soundness is checked by bounding the error.  An alternative
+is~\cite{park2016scalable}, where the verification of given control code is
+performed against a known model by extracting an LTI model of the code by
+symbolic execution: to account for rounding errors, an upper bound is
+introduced in the verification phase.  The work in
+\cite{picasso2003stabilization} introduces invariant sets as a mechanism to
+bound the quantization error effect on stabilization as an invariant set
 that always converges toward the controllable set.  Similarly,
-\cite{liberzon2003hybrid} evaluates the quantization error dynamics
-and bounds its trajectory to a known region over a finite time period. 
-This technique works for both linear and non-linear systems.
+\cite{liberzon2003hybrid} evaluates the quantization error dynamics and
+bounds its trajectory to a known region over a finite time period.  This
+technique works for both linear and non-linear systems.
 
@@
 %-------------------------------
-For abstraction based synthesis, we will use Abstract Acceleration~\cite{JSS14,cattaruzza2015unbounded}.
-Given an iterative program with dynamics
+
+For abstraction based synthesis, we will use Abstract
+Acceleration~\cite{JSS14,cattaruzza2015unbounded}.  Given an iterative
+program with dynamics
+%
 \begin{equation}
@@
 \end{equation}
-we want to find all possible states visited over an infinite time horizon starting at an initial set $X_0$. We call this set the \emph{reach tube} of the model:
+%
+we want to find all possible states visited over an infinite time horizon
+starting at an initial set $X_0$.  We call this set the \emph{reach tube} of
+the model:
+%
 \begin{equation}
@@
 \end{equation}
-It is easy to see that the infinite number of iterations would result in an unbounded cumulative rounding error, but using Abstract Acceleration we transform this problem into a one-step solution.
-We first change the problem statement by means of acceleration into 
+%
+It is easy to see that the infinite number of iterations would result in an
+unbounded cumulative rounding error, but using Abstract Acceleration we
+transform this problem into a one-step solution.  We first change the
+problem statement by means of acceleration into
+%
 \begin{equation}
@@
 \end{equation}
+%
 and further define new model semantics and corresponding set: 
+%
 \begin{equation}\label{eq:aa_reachtube}
@@
 \end{equation}
-where the newly introduced \emph{abstract reach tube} $\hat{X}^\sharp$ is an over-approximation of the reach tube of the model \cite{JSS14}.
-All we need to do is define the nature of $\mathcal{A}X_0$.
+%
+where the newly introduced \emph{abstract reach tube} $\hat{X}^\sharp$ is an
+over-approximation of the reach tube of the model \cite{JSS14}.  All we need
+to do is define the nature of $\mathcal{A}X_0$.
 
@@
 $\mat{A}$ in its main diagonal.  We correspondingly define
-$\mathcal{J}=\mat{S}^{-1}\mathcal{A}\mat{S}$, which is such that $\mathcal{J} \supseteq \bigcup_{k \in [0\
-\infty)} \mat{J}^k$.
+$\mathcal{J}=\mat{S}^{-1}\mathcal{A}\mat{S}$, which is such that
+$\mathcal{J} \supseteq \bigcup_{k \in [0\ \infty)} \mat{J}^k$.
 
@@
 The linear transformation $\vec{x}'=\mat{S}^{-1}\vec{x}$ leads to set 
+%
 \begin{equation}
@@
 \end{equation}
-Analogously, 
-let $X_0'=\mat{S}^{-1}X_0$ and ${\hat{X}'^\sharp}=\mat{S}^{-1}{\hat{X}^\sharp}$ be the initial set and the abstract reach tube mapped onto the eigenspace of matrix $\mat{A}$. 
-We may transform equation \eqref{eq:aa_reachtube} into:
+%
+Analogously, let $X_0'=\mat{S}^{-1}X_0$ and
+${\hat{X}'^\sharp}=\mat{S}^{-1}{\hat{X}^\sharp}$ be the initial set and the
+abstract reach tube mapped onto the eigenspace of matrix $\mat{A}$.  We may
+transform equation \eqref{eq:aa_reachtube} into:
+%
 \begin{equation}
@@
 \end{equation}
-where $\hat{X}'=\mat{S}^{-1}\hat{X}$ and $\mathcal{J}$ is a convex polyhedron representing restrictions on the eigenvalues of $\mat{A}$.
-$\hat{X}'^\sharp$ is calculated by applying a simplex algorithm with a tableau defined by $\mathcal{J}$ and objective functions derived from each vertex of $X_0'$ (step \eqref{alg:getReachTube} in Algorithm \ref{alg:findReachTube} below).
-We note, however, that if we wish to use numerical analysis in the decomposition of $\mat{A}$, 
-the Tableau in $\mathcal{J}$ contains small intervals given by the errors, which cannot be processed efficiently by a regular simplex and require a new procedure.
-
-The calculation of the abstract reach tube via abstract acceleration is encompassed in Algorithm \ref{alg:findReachTube}, 
-which can be summarised as follows (its steps are denoted in parentheses):
+%
+where $\hat{X}'=\mat{S}^{-1}\hat{X}$ and $\mathcal{J}$ is a convex
+polyhedron representing restrictions on the eigenvalues of $\mat{A}$. 
+$\hat{X}'^\sharp$ is calculated by applying a simplex algorithm with a
+tableau defined by $\mathcal{J}$ and objective functions derived from each
+vertex of $X_0'$ (step \eqref{alg:getReachTube} in Algorithm
+\ref{alg:findReachTube} below).  We note, however, that if we wish to use
+numerical analysis in the decomposition of $\mat{A}$, the Tableau in
+$\mathcal{J}$ contains small intervals given by the errors, which cannot be
+processed efficiently by a regular simplex and require a new procedure.
+
+The calculation of the abstract reach tube via abstract acceleration is
+encompassed in Algorithm~\ref{alg:findReachTube}, which can be summarised as
+follows (its steps are denoted in parentheses):
 %
 \begin{enumerate}
+%
 \item We perform unsound eigen-decomposition using an existing algebra package (lines \ref{alg:calcEigenvalues}-\ref{alg:calcEigenvectors}).
+%
 \item Then we restore soundness to the results using the methods described in Section \ref{sec:eigensolver} (lines \ref{alg:soundEigenvalues}-\ref{alg:soundEigenvectors}). 
+%
 \item The inverse of the matrix of eigenvectors is calculated after soundness is restored, using interval arithmetic in order to ensure its soundness (line \ref{alg:inverse}).
+%
 \item The abstract dynamics are obtained by evaluating the convex hull of all powers of eigenvalues up to the desired number of iterations as described in \cite{cattaruzza2015unbounded} (line \ref{alg:aa}).
+%
 \item Using Equation \eqref{eq:eigenInit}, transform the initial state into the eigenspace (line \ref{alg:eigeninit}).
+%
 \item Extract the vertices of the eigen-polyhedron $X_0'$ using the sound over-approximation of the double description algorithm \cite{fukuda1996double} from Section \ref{sec:dd} (line \ref{alg:getVertices}).
 It is worth noting that this algorithm uses a simplex to seed it: we will first discuss the simplex algorithm, which is also needed at the next step, and then the vertex enumeration algorithm used at this stage.
-\item Calculate the mapped \emph{abstract reach tube} ${\hat{X}'^\sharp}$ that over-approximates the image of the reach tube in the eigenspace (line \ref{alg:getReachTube}).
-This is achieved by evaluating a set of objective functions using the abstract dynamics as a simplex Tableau,
-and via a sound simplex described in Section \ref{sec:simplex}. 
-The objective functions are defined by the vertices of $X'_0$, 
-denote as $V_0$, 
-and by the desired template directions, 
-such that 
+%
+\item Calculate the mapped \emph{abstract reach tube} ${\hat{X}'^\sharp}$
+that over-approximates the image of the reach tube in the eigenspace (line
+\ref{alg:getReachTube}).  This is achieved by evaluating a set of objective
+functions using the abstract dynamics as a simplex Tableau, and via a sound
+simplex described in Section \ref{sec:simplex}.  The objective functions are
+defined by the vertices of $X'_0$, denote as $V_0$, and by the desired
+template directions, such that
+%
 \begin{equation*}
@@
 \end{equation*}
-where $T$ is the set of template directions, and $\circ$ denotes a component-wise multiplication yielding a vector. 
-\item Using Equation \eqref{eq:eigenInit}, find the reach tube $\hat{X}^\sharp=\mat{S}{\hat{X}'^\sharp}$ (line \ref{alg:getNormReachTube}).
+%
+where $T$ is the set of template directions, and $\circ$ denotes a
+component-wise multiplication yielding a vector.
+%
+\item Using Equation~\eqref{eq:eigenInit}, find the reach tube
+$\hat{X}^\sharp=\mat{S}{\hat{X}'^\sharp}$ (line \ref{alg:getNormReachTube}).
+%
 \end{enumerate}
@@
 %-------------------------------
-Thus far we wave discussed the Abstract Accelertion of Discrete Time systems. However, our plant models derive
-from the discretization of continuous time systems. We therefore seek to establish a sound
-overapproximation which does not only encompass the selected discretization, but any chosen discretization in the 
-time domain.
-
-A dynamical system is a system in which a function describes the progression of a state over time. 
-In a continuous domain with linear dynamics, it is described by a first order Ordinary Differential Equation (ODE).
+
+Thus far we wave discussed the Abstract Accelertion of Discrete Time
+systems.  However, our plant models derive from the discretization of
+continuous time systems.  We therefore seek to establish a sound
+overapproximation which does not only encompass the selected discretization,
+but any chosen discretization in the time domain.
+
+A dynamical system is a system in which a function describes the progression
+of a state over time.  In a continuous domain with linear dynamics, it is
+described by a first order Ordinary Differential Equation (ODE).
+%
 \begin{equation}
@@
 \end{equation}
-where $\vec{w}$  is a continuous zero-mean white noise source with covariance $N ( 0 , Q )$
-Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
-which may restricts the observability of the statespace from the output space.
+%
+where $\vec{w}$  is a continuous zero-mean white noise source with
+covariance $N ( 0 , Q )$ Furthermore, a control system may have a derived
+output that is a linear combination of its states and inputs, which may
+restricts the observability of the statespace from the output space.
+%
 \begin{equation}
@@
 \end{equation}
-Discretization of a continuous dynamical system turns the ODE into a difference equation, assuming zero-order hold
-for the input $\vec{u}$ and continuous integration for the noise $\vec{w}$, to
+%
+Discretization of a continuous dynamical system turns the ODE into a
+difference equation, assuming zero-order hold for the input $\vec{u}$ and
+continuous integration for the noise $\vec{w}$, to
+%
 \begin{align}
@@
 \end{align}
+%
 The eigenvalues remain the same as in the diagonal case, but the upper triangular terms are of the form:
+%
 \begin{align}
@@
 
-In the case of Discrete dynamics, support functions can be found by evaluating hyperplanes of consecutive exponents of the eigenvalues using differences.
-In the case of continuous time, this translates to calculating derivatives. Once again, when the sets are known to be convex,
-we may calculate the normal vector to this derivative and evaluate its support function on the selected iteration.
-The direction of the vector is determined by evaluating the support function of another point in the curve, which is known to be smaller than that of the selected point.
-The corresponding derivatives are:
+In the case of Discrete dynamics, support functions can be found by
+evaluating hyperplanes of consecutive exponents of the eigenvalues using
+differences.  In the case of continuous time, this translates to calculating
+derivatives.  Once again, when the sets are known to be convex, we may
+calculate the normal vector to this derivative and evaluate its support
+function on the selected iteration.  The direction of the vector is
+determined by evaluating the support function of another point in the curve,
+which is known to be smaller than that of the selected point.  The
+corresponding derivatives are:
+%
 \begin{enumerate}
-\item for real eigenvalues: we first calculate the slope of the tangent between the two progressions: $\frac{d f(k)}{d g(k)}=\frac{f'(k)}{g'(k)}$.
-Hence $\frac{d \lambda_1^k}{d \lambda_2^k}=\frac{log(\lambda_1) \lambda_1^k}{log(\lambda_2) \lambda_2^k}$.
-From this we know that the polar angle of the support vector is $\psi = \tan^{-1}(\frac{log(\lambda_1) \lambda_1^k}{log(\lambda_2) \lambda_2^k})+\frac{\pi}{2}$
+%
+\item for real eigenvalues: we first calculate the slope of the tangent
+between the two progressions: $\frac{d f(k)}{d g(k)}=\frac{f'(k)}{g'(k)}$. 
+Hence $\frac{d \lambda_1^k}{d \lambda_2^k}=\frac{log(\lambda_1)
+\lambda_1^k}{log(\lambda_2) \lambda_2^k}$.  From this we know that the polar
+angle of the support vector is $\psi = \tan^{-1}(\frac{log(\lambda_1)
+\lambda_1^k}{log(\lambda_2) \lambda_2^k})+\frac{\pi}{2}$
+%
 \item for conjugate eigenvalue pairs: the pair forms a logarithmic spiral. 
-The tangent of a spiral with polar equation $r=a e^{b\theta}$ will have a derivative $\frac{d r}{d \theta}=b a e^{b\theta}=b r$, hence the angle of the vector normal to the curve is $\tan^{-1}(\frac{r}{\frac{d r}{d \theta}})+\frac{\pi}{2}=\tan^{-1}(\frac{1}{b})+\frac{\pi}{2}$
-\item for Jordan blocks with $gm>1$: in the case of real eigenvalues, we follow the same procedure as in the real case, but considering that the equation for each eigenvalue is $\frac{k^j}{j!}e^{\lambda k}$ where $j$ is the index of the term within the Jordan block (note that when $j=0$ the term is the same as for real eigenvalues above).
-The derivatives f'(k),g'(k) are in the form $(j+k*log(\lambda))\frac{k^{j-1}}{j!}e^{\lambda k}$.
-\item for any combination of complex eigenvalues we use the above equations using the envelope of their magnitude (ie $|\lambda|$).
+The tangent of a spiral with polar equation $r=a e^{b\theta}$ will have a
+derivative $\frac{d r}{d \theta}=b a e^{b\theta}=b r$, hence the angle of
+the vector normal to the curve is $\tan^{-1}(\frac{r}{\frac{d r}{d
+\theta}})+\frac{\pi}{2}=\tan^{-1}(\frac{1}{b})+\frac{\pi}{2}$
+%
+\item for Jordan blocks with $gm>1$: in the case of real eigenvalues, we
+follow the same procedure as in the real case, but considering that the
+equation for each eigenvalue is $\frac{k^j}{j!}e^{\lambda k}$ where $j$ is
+the index of the term within the Jordan block (note that when $j=0$ the term
+is the same as for real eigenvalues above).  The derivatives f'(k),g'(k) are
+in the form $(j+k*log(\lambda))\frac{k^{j-1}}{j!}e^{\lambda k}$.
+%
+\item for any combination of complex eigenvalues we use the above equations
+using the envelope of their magnitude (ie $|\lambda|$).
+%
 \end{enumerate}
@@
 
-\item The inductive synthesis phase ({\sc synthesize}) uses BMC to
-compute a candidate solution $K$ that satisfies both the stability criteria
- and the safety specification.  To synthesize a controller that satisfies the
-stability criteria, we require that a computed polynomial
-satisfies Jury's criterion~\cite{fadali}.  The details of this calculation can be found in
+\item The inductive synthesis phase ({\sc synthesize}) uses BMC to compute a
+candidate solution $K$ that satisfies both the stability criteria and the
+safety specification.  To synthesize a controller that satisfies the
+stability criteria, we require that a computed polynomial satisfies Jury's
+criterion~\cite{fadali}.  The details of this calculation can be found in
 the Appendix.
@@
 Checking that the safety specification holds for any initial state can be
-computationally expensive if the bounds on the
-allowed initial states are large.
+computationally expensive if the bounds on the allowed initial states are
+large.
 
@@
 %inputs, and time horizons during the verification phase.
-Essentially, this approach relies on the symbolic
-simulation over a bounded time horizon of individual initial states and inputs that form
-part of an uncountable space and tries to generalize it for an
-infinite space over an infinite time horizon.
+
+Essentially, this approach relies on the symbolic simulation over a bounded
+time horizon of individual initial states and inputs that form part of an
+uncountable space and tries to generalize it for an infinite space over an
+infinite time horizon.
 
@@
 
-Conversely, in this section, 
-we  find a controller for a continuous initial set of states and set of inputs, 
-  over an abstraction of the continuous dynamics \cite{cattaruzza2015unbounded} that conforms to
-  witness proofs at specific times. %% It further generalizes the
-  Moreover, this approach uses abstraction refinement enabling us to 
-  always start with a very simple description regardless of the complexity of the overall
-dynamics, and only expand to more complex models when a solution
+Conversely, in this section, we find a controller for a continuous initial
+set of states and set of inputs, over an abstraction of the continuous
+dynamics \cite{cattaruzza2015unbounded} that conforms to witness proofs at
+specific times.  %% It further generalizes the
+Moreover, this approach uses abstraction refinement enabling us to always
+start with a very simple description regardless of the complexity of the
+overall dynamics, and only expand to more complex models when a solution
 cannot be found.
@@
 $\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$
-represented at the fixed-point precision of the plant model ($I_c$ and $F_c$ are determined by the controller.
-We pick $I_p$ and $F_p$ for our synthesis such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$).
-Thus any mathematical operations in our modelled
-digital controller will be in the range of $\mathcal{F}_{\langle I_c,F_c
-\rangle}$, and all other calculations in our model will be carried out in the range of
-$\mathcal{F}_{\langle I_p,F_p \rangle}$.  
-The physical plant operates in the
-reals, which means our verification phase must also account for the numerical error and quantization errors caused by representing the physical plant at the finite precision $\mathcal{F}_{\langle I_p,F_p \rangle}$.
+represented at the fixed-point precision of the plant model ($I_c$ and $F_c$
+are determined by the controller.  We pick $I_p$ and $F_p$ for our synthesis
+such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$).  Thus any
+mathematical operations in our modelled digital controller will be in the
+range of $\mathcal{F}_{\langle I_c,F_c \rangle}$, and all other calculations
+in our model will be carried out in the range of $\mathcal{F}_{\langle
+I_p,F_p \rangle}$.  The physical plant operates in the reals, which means
+our verification phase must also account for the numerical error and
+quantization errors caused by representing the physical plant at the finite
+precision $\mathcal{F}_{\langle I_p,F_p \rangle}$.
 
@@
 zeros positions, degrading the closed-loop dynamics, causing steady-state
-errors  and
-eventually de-stabilizing the system~\cite{Bessa16}.  However, since in this
-paper we require stability only as a precursor to safety, it is sufficient
-to check that the (perturbed, noisy) model converges to a neighborhood of
-the equilibrium within the safe set.
+errors and eventually de-stabilizing the system~\cite{Bessa16}.  However,
+since in this paper we require stability only as a precursor to safety, it
+is sufficient to check that the (perturbed, noisy) model converges to a
+neighborhood of the equilibrium within the safe set.
 
@@
 \end{equation}
-the output decay is a linear combination of the decay of eigenvalues or eigenvalue pairs.
-Hence the overall decay of the system is always smaller than $p=e^{-|\overline{\omega}| t}$ where $0\leq p\leq 1$ is the remaining percentage of the decay expressed.
-reversing we have $t=-\frac{ln(p)}{|\overline{\omega}|}=-\frac{ln(p)}{ln(|\overline{\lambda}|)}$.
-replacing for $p_s$ , $t_s$, and $\overline{\lambda}$ we get equation \eqref{eq:set_time}
+%
+the output decay is a linear combination of the decay of eigenvalues or
+eigenvalue pairs.  Hence the overall decay of the system is always smaller
+than $p=e^{-|\overline{\omega}| t}$ where $0\leq p\leq 1$ is the remaining
+percentage of the decay expressed.  reversing we have
+$t=-\frac{ln(p)}{|\overline{\omega}|}=-\frac{ln(p)}{ln(|\overline{\lambda}|)}$. 
+replacing for $p_s$ , $t_s$, and $\overline{\lambda}$ we get equation
+\eqref{eq:set_time}
+%
 \qed
 \end{proof}
-We may now use this limit to express a constraint in terms of the coefficients for our synthesis process.
-Let 
+%
+We may now use this limit to express a constraint in terms of the
+coefficients for our synthesis process.  Let
+%
 \begin{equation}
@@
 \end{equation}
-We use Jury's criterion to limit $|\lambda_i| \leq 1$.
-Let us now define a transformation $\lambda_i'=\frac{\lambda_i}{\overline{\lambda}}$.
-We want to ensure $\lambda_i' \leq 1$ which can be done by applying Jury's criterion to $P'=\prod_{i=0}^n (s-\lambda_i')=\sum_{j=0}^n c_j's^j$ where $c_j'$ are unknown.
-However, if we replace for $\lambda_i$, we obtain
+%
+We use Jury's criterion to limit $|\lambda_i| \leq 1$.  Let us now define a
+transformation $\lambda_i'=\frac{\lambda_i}{\overline{\lambda}}$.  We want
+to ensure $\lambda_i' \leq 1$ which can be done by applying Jury's criterion
+to $P'=\prod_{i=0}^n (s-\lambda_i')=\sum_{j=0}^n c_j's^j$ where $c_j'$ are
+unknown.  However, if we replace for $\lambda_i$, we obtain
+%
 \begin{equation}
@@
 \end{equation}
-where all members are known, we may now synthesise coefficients that ensure the eigenvalues are smaller than a desired magnitue, thus ensuring that the settling time is too.
+%
+where all members are known, we may now synthesise coefficients that ensure
+the eigenvalues are smaller than a desired magnitue, thus ensuring that the
+settling time is too.
 
@@
 
-As stated in section \ref{ssec:stabspecification}, we use Jury's Criterion to assert this specification.
+As stated in Section~\ref{ssec:stabspecification}, we use Jury's Criterion
+to assert this specification.
 
@@
 
-Now that we have established convergence, we may examine the safety specification of the state space.
-In the case of SISO systems, this is given by a range of the input and a range of the output which are considered safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in [\underline{y}\ \ \overline{y}]$).
-Whilst there are other properties we may include in the verification, we will solely focus on these for simplicity of the explanation.
-We will assume that we do not want saturation in our system, hence the control loop has only one mode. We have also identified the quantization noise as a bounded non-deterministic input.
-First we must translate the safety specification into the statespace. Replacing on the second part of equation \eqref{eq:observer_LTI_cf} we obtain
+Now that we have established convergence, we may examine the safety
+specification of the state space.  In the case of SISO systems, this is
+given by a range of the input and a range of the output which are considered
+safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in
+[\underline{y}\ \ \overline{y}]$).  Whilst there are other properties we may
+include in the verification, we will solely focus on these for simplicity of
+the explanation.  We will assume that we do not want saturation in our
+system, hence the control loop has only one mode.  We have also identified
+the quantization noise as a bounded non-deterministic input.  First we must
+translate the safety specification into the statespace.  Replacing on the
+second part of equation \eqref{eq:observer_LTI_cf} we obtain
+%
 \begin{equation}
@@
 \end{align}
-where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A}^k, \mathcal{B}_{tp}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tp}, \mathcal{B}_{tn}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tn}$ are abstract matrices for the system in \eqref{eq:observer_LTI_cf}.
-It is worth noting that $r$ is a non-deterministic parametric input (\emph{ie} $\forall k>0, r_{k+1} =r_k$) whereas the set N is composed of non-deterministic variable inputs.
+%
+where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A}^k,
+\mathcal{B}_{tp}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tp},
+\mathcal{B}_{tn}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tn}$ are
+abstract matrices for the system in \eqref{eq:observer_LTI_cf}.  It is worth
+noting that $r$ is a non-deterministic parametric input (\emph{ie} $\forall
+k>0, r_{k+1} =r_k$) whereas the set N is composed of non-deterministic
+variable inputs.
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-Thus far we have presented a verification procedure for a continuous plant in discretized time domain (\emph{ie} the
-range of the quatizers is still $\mathbb{R}$. The next step we must reaize is that the controller and the observer
-exist in a digital program, hence their domain is $\mathbb{R}\langle I,F,E\rangle$. This has two separate effects
-on the model. If we recall equation \eqref{eq:to_of}, the matrices of the observer and the controller  are not necessarily those of the plant.
-In fact we have $\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$, $\mat{A}_o,\mat{B}_o,\mat{C}_o, \mat{K}_d, \mat{L}_d \in \mathbb{R}\langle I,F,E\rangle^*$
-Where $*$ represents the appropriate dimension for each matrix.
-Unfortunately this means that although combined matrices such as $\mat{A}_t$ are in the reals, they suffer from
-the fixed word restrictions in their composing matrices.
-
-When our observer is implemented using a finite precision controller, new problems arise due to the FWL effects.
-Let $\mat{A}_o$, $\mat{B}_o$ and $\mat{C}_o$ be the dynamics represented in
-$\mathbb{R} \langle I , F, E \rangle$, and  $\mat{A}_e=\mat{A}_d-\mat{A}_o$, $\mat{B}_e=\mat{B}_d-\mat{B}_o$,
-and $\mat{C}_e=\mat{C}_d-\mat{C}_o$ their corresponding errors.
-Equation \eqref{eq:observer_LTI_cf} will become
+
+Thus far we have presented a verification procedure for a continuous plant
+in discretized time domain (\emph{ie} the range of the quatizers is still
+$\mathbb{R}$.  The next step we must reaize is that the controller and the
+observer exist in a digital program, hence their domain is
+$\mathbb{R}\langle I,F,E\rangle$.  This has two separate effects on the
+model.  If we recall equation \eqref{eq:to_of}, the matrices of the observer
+and the controller are not necessarily those of the plant.  In fact we have
+$\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$, $\mat{A}_o,\mat{B}_o,\mat{C}_o,
+\mat{K}_d, \mat{L}_d \in \mathbb{R}\langle I,F,E\rangle^*$ Where $*$
+represents the appropriate dimension for each matrix.  Unfortunately this
+means that although combined matrices such as $\mat{A}_t$ are in the reals,
+they suffer from the fixed word restrictions in their composing matrices.
+
+When our observer is implemented using a finite precision controller, new
+problems arise due to the FWL effects.  Let $\mat{A}_o$, $\mat{B}_o$ and
+$\mat{C}_o$ be the dynamics represented in $\mathbb{R} \langle I , F, E
+\rangle$, and $\mat{A}_e=\mat{A}_d-\mat{A}_o$,
+$\mat{B}_e=\mat{B}_d-\mat{B}_o$, and $\mat{C}_e=\mat{C}_d-\mat{C}_o$ their
+corresponding errors.  Equation \eqref{eq:observer_LTI_cf} will become
+%
 \begin{align}
@@
 
-The first effect of this new equation is that the matrix is no longer upper diagonal. We must therefore compensate for the errors introduced in order to find a stable solution.
-We can use Gershgoring disks to limit the error in the expected eigenvalues.
-Let $\delta_o=\max(|\mat{A}_{ei*}|_2)$ (\emph{i.e.} the largest row norm in $\mat{A}_e$) be the largest error bound for any eigenvalue in $\mat{A}_e$.
-Then $\forall i \in [1\ n], |\lambda_{oi}-\hat{\lambda}_{oi}|<\delta_o$,where $\lambda_{oi}$ are the true eigenvalues of the observer and $\hat{\lambda}_{oi}$ the eigenvalues of the perturbed observer.
-We note that in the case of stability we only care about the error with respect to the unit circle, which is equivalent to upper bounding the estimation of the largest eigenvalue.
-Hence given a desired upper value $\overline{\lambda}$, we apply Iurys criterion on the polynomial.
+The first effect of this new equation is that the matrix is no longer upper
+diagonal.  We must therefore compensate for the errors introduced in order
+to find a stable solution.  We can use Gershgoring disks to limit the error
+in the expected eigenvalues.  Let $\delta_o=\max(|\mat{A}_{ei*}|_2)$
+(\emph{i.e.} the largest row norm in $\mat{A}_e$) be the largest error bound
+for any eigenvalue in $\mat{A}_e$.  Then $\forall i \in [1\ n],
+|\lambda_{oi}-\hat{\lambda}_{oi}|<\delta_o$,where $\lambda_{oi}$ are the
+true eigenvalues of the observer and $\hat{\lambda}_{oi}$ the eigenvalues of
+the perturbed observer.  We note that in the case of stability we only care
+about the error with respect to the unit circle, which is equivalent to
+upper bounding the estimation of the largest eigenvalue.  Hence given a
+desired upper value $\overline{\lambda}$, we apply Iurys criterion on the
+polynomial.
+%
 \begin{equation}
@@
 \end{equation}
-Inthe case of the reachable eigenvalues, the procedure is the same except that we obtain our bound $\delta_c=\max(|\mat{A}_{e*i}+\mat{B}_{e*i}|_2)$ (\emph{i.e.} the largest column norm in $[\mat{A}_e\ \mat{B}_e]^T$) and apply Jury's Criterion over
+%
+In the case of the reachable eigenvalues, the procedure is the same except
+that we obtain our bound $\delta_c=\max(|\mat{A}_{e*i}+\mat{B}_{e*i}|_2)$
+(\emph{i.e.} the largest column norm in $[\mat{A}_e\ \mat{B}_e]^T$) and
+apply Jury's Criterion over
+%
 \begin{equation}
@@
 
-As a final annotation, we remark that the safety specification must be applied to the model described in this section, accounting for the representation errors of the FWL domain.
+As a final annotation, we remark that the safety specification must be
+applied to the model described in this section, accounting for the
+representation errors of the FWL domain.
 

### 2017-06-21 automatica/paper.tex
Continuous proof for input integral

@@
  \begin{align}
+ \label{eq:contu_reachset}
 X_T^\sharp &=\mat{A}^{-1}X_T'\supseteq X_T\\
@@
 Then $U'\subseteq U_b' \oplus \vec{u}_c' \Rightarrow (\mat{I}-\mat{A}_T)U' \subseteq (\mat{I}-\mat{A}_T)U_b' \oplus (\mat{I}-\mat{A}_T)\vec{u}_c'$.
-Since $ (\mat{I}-\mat{A}_{bT})U_b'\supseteq  (\mat{I}-\mat{A}_T)U_b'$, then $(\mat{I}-\mat{A}_T)U' \subseteq (\mat{I}-\mat{A}_{bT})U_b' \oplus (\mat{I}-\mat{A}_T)\vec{u}_c'$ thus proving the theorem.
-
+Since $ (\mat{I}-\mat{A}_{bT})U_b'\supseteq  (\mat{I}-\mat{A}_T)U_b'$, then $(\mat{I}-\mat{A}_T)U' \subseteq (\mat{I}-\mat{A}_{bT})U_b' \oplus (\mat{I}-\mat{A}_T)\vec{u}_c'$ thus proving the theorem for $\vec{u}(t)=\vec{u}_0 : t \in [0\ T]$.
+
+For the continuous time interval, let us look at the solution for the differential equation at time $T$ with a non-deterministic input $\vec{u}$.
+\begin{equation*}
+\vec{x}_T=e^AT\vec{x}_0+\int_{t = 0}^{T_s} e^{\mat{A} t} \mat{B} \vec{u}(t) dt
+\end{equation*}
+We will first divide this equation into 
+\begin{align*}
+\vec{x}_T&=e^AT\vec{x}_0+\int_{t = 0}^{T} e^{\mat{A} t} \mat{B} \vec{u}_c dt +\int_{t = 0}^{T_s} e^{\mat{A} t} \mat{B} (\vec{u}(t)-\vec{u}_c) dt\\
+&=A_T\vec{x}_0+B_T\vec{u}_c+\int_{t = 0}^{T} \mat{S}e^{\mat{J} t} \mat{S}^{-1}\mat{B} (\vec{u}(t)-\vec{u}_c) dt\\
+&=A_T\vec{x}_0+B_T\vec{u}_c+\mat{S}\int_{t = 0}^{T} e^{\mat{J} t} \vec{u}_{j}'(t) dt\\
+&=A_T\vec{x}_0+B_T\vec{u}_c+\mat{S}\int_{t = 0}^{T} \sum_{k=0}^\infty \frac{1}{k!} \mat{J}^k t^k \vec{u}_{j}'(t) dt\\
+&=A_T\vec{x}_0+B_T\vec{u}_c+\mat{S}\sum_{k=0}^\infty \frac{1}{k!} \int_{t = 0}^{T} t^k \mat{J}^k \vec{u}_{j}'(t) dt
+\end{align*}
+It follows from equation \eqref{eq:overinduced} that $\mat{J}^k \vec{u}_{j}'(t) \subseteq \mat{J}_b^k U_{bj}'$ (where $U_{bj}'=\mat{S}^{-1}U_b'$), hence
+\begin{align*}
+&X_T \subseteq A_TX_0+B_T\vec{u}_c+\mat{S}\sum_{k=0}^\infty \frac{1}{k!} \int_{t = 0}^{T} t^k \mat{J}_b^k U_{bj}' dt\\
+\Rightarrow &X_T \subseteq A_TX_0+B_T\vec{u}_c+\mat{S} \int_{t = 0}^{T} \sum_{k=0}^\infty \frac{1}{k!}\mat{J}_b^k t^k U_{bj}' dt\\
+\Rightarrow &X_T \subseteq A_TX_0+B_T\vec{u}_c+\int_{t = 0}^{T_s} e^{\mat{A}_b t} U_b' dt\\
+\Rightarrow &X_T \subseteq A_TX_0+B_T\vec{u}_c+ \mat{A}^{-1}(\mat{I}-\mat{A}_{bT}) \mat{B} U_b
+\end{align*}
+Multiplying by $\mat{A}$ we get $X_T'$ as in \eqref{eq:contu_reachset}, thus proving the theorem.
 \end{proof}

### 2017-06-23 automatica/paper.tex
Description of benchmarks

--- 2017-06-21 automatica/paper.tex
@@
 
-\textcolor{red}{Iury: can you please describe the benchmarks?}
+%\textcolor{red}{Iury: can you please describe the benchmarks?}
+
+The benchmark suite employed to evaluate the proposed technique is 
+composed by 18 MIMO models extracted from the literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS} and discretized with different sample time
+resulting in 167 benchmarks.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph*{DC Motor}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+DC Motor benchmark describes the velocity dynamics of a basic 
+brushed direct current electrical machine.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph*{Automotive Cruise System}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+An automotive cruise control system is used to keep constant the speed 
+of an automobile  tracking a desired speed reference, compensating 
+disturbances and uncertainties related to relief and terrain.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph*{Pendulum}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+A pendulum is system composed by a swinging point mass suspended from 
+a frictionless pivot through a negligible mass rod.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph*{Inverted Pendulum}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+An inverted pendulum is a system similar to the pendulum but the point 
+mass must be equilibrated above the pivot point that is mounted on an 
+one degree of freedom cart that moves over a track through a DC motor.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph*{Magnetic Suspension}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Magnetic suspension benchmark corresponds to the discrete model of a 
+simple eletromagnet-ball system where a steel ball is levitated in air 
+by the action of an electromagnetic force generated by an electromagnet.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph*{Magnetic Pointer}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Magnetic pointer is a pointer, that is usually employed in analogue 
+gauges and indicators, whose angular position dynamics is controlled 
+by a magnetic field.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph*{1/4 Car Suspension}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The 1/4 Car Suspension benchmark corresponds to the model of a single 
+wheel suspension system of a car, {\it i.e.} the relative motion dynamics 
+of a mass springer damp model that connects the car to one of its wheels.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph*{Computer Tape Driver}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Computer Tape Drive is a computer storage device used to read and write 
+data on magnetic tapes.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph*{Acrobot - Robot Manipulator}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The Acrobot benchmark corresponds to the model of an two-link 
+underactuated robot manipulator, named Acrobot, linearized by partial 
+feedback linearization~\cite{acrobot}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph*{High-order Systems from Chen et. al.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+These benchmarks corresponds to a series of high-order system model 
+generally used as example for order reduction techniques~\cite{CHEN1979389}.
+ In this work, these benchmarks are used for evaluate the proposed control
+ synthesis technique under critical conditions, {\it i.e.} with a greater 
+ number of parameters to be considered.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph*{Continuous Stirred Tank Reactor}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+This benchmark describes a linear model for PH dynamics of a PH 
+neutralization process of an aqueous solution of sodium acetate with 
+hydrochloric acid in a continuous flow stirred-tank reactor.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph*{Flexible Beam}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+A Flexible Beam is a plant usually employed in vibration studies. It is 
+composed by a flexible metallic structure with piezoceramic actuators 
+and sensors.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph*{Helicopter Longitudinal Motion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The Helicopter Longitudinal Motion benchmark describes the dynamics of 
+transitional motion with respect to a longitudinal plane and the 
+rotational motion around the longitudinal axis.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph*{USCG cutter Tampa Heading Angle}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The USCG cutter Tampa Heading Angle describes the heading angle 
+dynamics of a Coast Guard cutter.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph*{Voltage regulator}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The voltage regulator benchmark~\cite{KOKOTOVIC198023} consists 
+in a linear model of a synchronous machine connected to an 
+infinite bus.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph*{Guidance Control System}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The Guidance Control System benchmark is another high-order system 
+model used by Chen et al.~\cite{CHEN1979389}  in order reduction 
+techniques. Guidance systems are used to determine the path of an 
+autonomous vehicle movement.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph*{Satellite Attitude Control System}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+This benchmark describes the dynamics of a satellite attitude, 
+{\it i.e.} the orientation angles. An attitude control system must 
+maintain the desired orientation of satellite with respect to an 
+inertial frame during all the excursion.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph*{Springer-mass damper}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The springer-mass damper systems are classic models for a lot of 
+mechanical systems dynamics. This benchmark describes a mass that is 
+fixed to a node through a springer and moves under the action of a 
+input force, damping, and elastic force.
 

### 2017-06-26 ase2017/paper.tex
ase paper

@@
 offering mathematical guarantees about the stability and the desired 
-performance of closed-loop systems, where states or outputs of discrete plant $G(z)$ 
+performance of closed-loop dynamical systems, where states or outputs of discrete plant $G(z)$ 
 are fed back and compared to a reference signal to which a (designed) 
@@
 In state-space format, the digital control system represents the behavior 
-of a system via a state evolution equation $\dot{x}(n+1)$ and an instantaneous 
+of a system via a state evolution equation $x(n+1)$ and an instantaneous 
 output equation $y(n)$, as follows:
@@
 \begin{split}
-\dot{x}(n+1) &= A x(n) + B u(n)
+x(n+1) &= A x(n) + B u(n)
 \\
@@
 describing a physical plant, by a respective finite-state machine. However, Pessoa does not take advantage of
-recent advances in bit-accurate verification of programs to synthesize controllers w.r.t. FWL effects.
+recent advances in bit-accurate verification of programs to synthesize controllers w.r.t.
+FWL effects.
+MATLAB already offers a toll (Control System Tuner~\cite{autotuner}) for automatically designing controllers based on optimization solvers or graphical analysis.
+However, the Control System Tuner is unable to consider FWL effects during the design process.
 As a result, there is no other MATLAB toolbox to perform digital controller synthesis based on 

### 2017-06-26 ase2017/paper.tex
Added LOC to implementation
Added description of LOC in the various modules of our implementation.

--- 2017-06-20 ase2017/paper.tex
@@
 
-\textcolor{red}{Pascal: May I ask you to briefly mention the modules and also the LOC associated to each module?
-The tool paper reviewers usually like to know about the tool's complexity (i.e., number of modules/components and LOC).}
+The entire implementation consists of $400$ lines of MATLAB scripts for the UI
+module, $585$ and $800$ lines of C code in the naive and abstract accelerator
+model respectively.  $4000$ lines of C code for utility functions such as
+interval and fixed-point arithmetic, as well as $1000$ lines of C++ code in the
+control synthesis module in CEGIS CBMC.  We evaluate \tool using $20$ regression
+test cases.
 

### 2017-06-26 ase2017/paper.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 FWL effects.
-MATLAB already offers a toll (Control System Tuner~\cite{autotuner}) for automatically designing controllers based on optimization solvers or graphical analysis.
+MATLAB already offers a tool (Control System Tuner~\cite{autotuner}) for automatically designing controllers based on optimization solvers or graphical analysis.
 However, the Control System Tuner is unable to consider FWL effects during the design process.

### 2017-06-26 ase2017/paper.tex
improved sentence
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 describing a physical plant, by a respective finite-state machine. However, Pessoa does not take advantage of
-recent advances in bit-accurate verification of programs to synthesize controllers w.r.t.
-FWL effects.
-MATLAB already offers a tool (Control System Tuner~\cite{autotuner}) for automatically designing controllers based on optimization solvers or graphical analysis.
-However, the Control System Tuner is unable to consider FWL effects during the design process.
+recent advances in bit-accurate verification of programs to synthesize controllers w.r.t. FWL effects. MATLAB already offers a tool 
+named as Control System Tuner~\cite{autotuner} for automatically designing controllers based on optimization solvers or graphical analysis. 
+However, the Control System Tuner is unable to consider FWL effects during the controller synthesis process.
 As a result, there is no other MATLAB toolbox to perform digital controller synthesis based on 

### 2017-06-26 ase2017/paper.tex
added experimental setup.

@@
 
+%-----------------------------------
+\subsection{Experimental Setup}
+\label{experimental-setup}
+%-----------------------------------
+
+For all evaluated benchmarks, the signal input range lies between $-1$ and $1$, and the implementation used for the integer part is $8$ bits, and for fractional part is also $8$ bits.
+%
+All experiments with \tool v$1$.$0$.$0$  were conducted on an otherwise idle Intel Core i$7-2600$ 
+$3.40$ GHz processor, with $24$ GB of RAM, running Ubuntu $64$-bits.
+
 %---------------------------------------------------

### 2017-06-26 automatica/paper.tex
make figures readable
Further proof for the settling time limit

--- 2017-06-21 automatica/paper.tex
@@
 \begin{theorem}
-Given a set of eigenvalues for a discrete time modle of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1\ n]$, the settling time of the system is upperbounded by
+Given a set of eigenvalues for a discrete time model of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1\ n]$, the settling time of the system is upperbounded by
 \begin{equation}
@@
 : \left\{ \begin{array}{c}\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \\ \vec{x}_k'=\mat{S}^{-1}\vec{x}_k\end{array}\right.
+\label{eq:eigendynamics}
 \end{equation}
@@
 the output decay is a linear combination of the decay of eigenvalues or
-eigenvalue pairs.  Hence the overall decay of the system is always smaller
+eigenvalue pairs.  
+Let $\mat{C}'\in \mathbb{R}^{1 \times n}=\mat{C}\mat{S}$.
+Since $\mat{C}'$ is constant, the output $y_k$ is a linear combination of the states $\vec{x}'_k$.
+We accelerate equation \eqref{eq:eigendynamics} to obtain
+\begin{align}
+%\vec{x}_k'&=\mat{J}^k\vec{x}_0' \\
+y_k&=\mat{C}'\mat{J}^k\vec{x}_0 = \sum_{i=0}^n \left( c_i \lambda_i^k + c_{il}\binom{k}{l} \lambda_i^{k-l}\right)\\
+|y_k|&\leq \sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right||\lambda_i^k|
+\end{align}
+where the second  part of the equation corresponds to the upper diagonal terms of the Jordan blocks. We also have $|\lambda_i^k|\leq |\overline{\omega}^k|$,hence
+\begin{align}
+|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right|
+\end{align}
+Since we are synthesising the eigenvalues, rather than solve this formula for complex Jordan Shapes, we will restrict our synthesiser to provide solutions with distinct eigenvalues (which is by far the most common case).
+Therefore the right hand terms dissappear and we end up with
+\begin{align}
+|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n |c_i|
+\end{align}
+
+Hence the overall decay of the system is always smaller
 than $p=e^{-|\overline{\omega}| t}$ where $0\leq p\leq 1$ is the remaining
@@
 \begin{equation}
-P'=\prod_{i=0}^n (s-\lambda_i')=\prod_{i=0}^n (s-\lambda_i\overline{\lambda})=\sum_{j=0}^n c_j\overline{\lambda}^{n-j}s^j
+P'=\prod_{i=0}^n (s-\lambda_i')=\prod_{i=0}^n \left(s-\frac{\lambda_i}{\overline{\lambda}}\right)=\sum_{j=0}^n \frac{c_j}{\overline{\lambda}^{n-j}}s^j
 \end{equation}
@@
 A controllable and observable system will have the following dynamics:
-\begin{equation}
+\begin{align}
 \tiny
 \left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_{k+1}
-=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}_d&\mat{B}_d\mat{K}_d\\ \mat{0}&\mat{A}_d-\mat{L}_d\mat{C}_d\end{array}\right]
-\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_k
-+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
+&\tiny=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}_d&\mat{B}_d\mat{K}_d\\ \mat{0}&\mat{A}_d-\mat{L}_d\mat{C}_d\end{array}\right]
+\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_k\nonumber\\
+&\tiny+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
 +\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}_d\end{array}\right]\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]
-\end{equation}
+\label{eq:observer_LTI}
+\end{align}
 In order for the system to be in canonical form, we must however perform a transformation. The challenge however is that we want the state space dynamics in
@@
 \begin{align}
-\label{eq:observer_LTI_cf}
 \left [\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e' \end{array}\right]_{k+1}
@@
 +\mat{B}_{tp} \vec{r}_k
-+\mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]\\
-\vec{y}_k=&\mat{C}_{t}\vec{x}_k + \mat{D}_{d}\vec{u}_k\nonumber
++\mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]\nonumber\\
+\vec{y}_k=&\mat{C}_{t}\vec{x}_k + \mat{D}_{d}\vec{u}_k
+\label{eq:observer_LTI_cf}
 \end{align}
@@
 \mat{B}_{tp}=&\left[\begin{array}{c}\mat{T}_c\mat{B}_o\mat{k}_r\\\mat{0}\end{array}\right]&
-\mat{B}_{tn}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_o\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_d\end{array}\right]\\
+\mat{B}_{tn}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_o&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_d\end{array}\right]\\
 \mat{T}_с=&\mat{R}_{cf}\mat{R}^{-1}&
@@
 \mat{L}_d=& \mat{T}_o^{-1}\left[ \begin{array}{c}p_1\\p_2\\p_n\end{array}\right]&
-\mat{A}_{eo}=&\mat{T}_o\left(\mat{A}_e+\mat{L}_o\mat{C}_e\right)\mat{T}_o^{-1}\\
+\mat{A}_{eo}=&\mat{T}_o\left(\mat{A}_e-\mat{L}_o\mat{C}_e\right)\mat{T}_o^{-1}\\
 \mat{B}_{eo}=&\mat{T}_c\mat{B}_e\mat{K}_d\mat{T}_o^{-1}&

### 2017-06-26 automatica/paper.tex

@@
 
-\begin{figure}[t]
+\begin{figure*}[t]
 \centering
-\includegraphics[width=\columnwidth]{figures/synthesis-flow.pdf}
+\includegraphics[width=\textwidth]{figures/synthesis-flow.pdf}
 \vspace{0.1cm}
 \caption{Overview of the synthesis process\label{DSSynth_process}}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}[htb]
-{\scriptsize
-\centering
-\resizebox{\columnwidth}{!}
-{
+\begin{figure*}[htb]
+\scriptsize\centering
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
-},
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},
           row sep=.6cm, column sep=.9cm] {
@@
    %([xshift=10.5cm]aux2) edge node[align=center] {Increase Sampling Rate} (aux1);
-
 \end{tikzpicture}
-}}
 \caption{CEGIS with multi-staged verification}
 \label{fig:CEGIS-precision-increment}
-\end{figure}
+\end{figure*}
 
@@
 \centering
-\includegraphics[width=0.9\columnwidth]{figures/ct.eps}
+\includegraphics[width=\columnwidth]{figures/ct.eps}
 %\vspace{0.1cm}
@@
 
-\begin{figure}
-\centering
-\resizebox{\columnwidth}{!}
-{\scriptsize
+\begin{figure*}
+\centering\scriptsize
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
@@
 \end{tikzpicture}
-}
 \caption{Abstraction-based CEGIS}
 \label{fig:CEGARIS} 
-\end{figure}
+\end{figure*}
 

### 2017-06-27 ase2017/paper.tex
typo

@@
 and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
-DSSynth synthesizes stable digtal controllers using that CEGIS-based approach,
+DSSynth synthesizes stable digital controllers using that CEGIS-based approach,
 for a given physical plant represented by either transfer functions or state-space equations~\cite{abate2017,abatecav2017}.

### 2017-06-29 ase2017/paper.tex
added benchmarks description

@@
 
-Our experimental evaluation consist of a set of control system benchmarks,
-which include physical plants for UAV, cruise control, spring-mass damper,
-satellite, direct current (DC) servo motor, helicopter, inverted pendulum,
-magnetic suspension, computer tape driver, robot manipulator, flexible beam,
-guidance system, and an antenna control system~\cite{abate2017, abatecav2017}.
+Our experimental evaluation consist of a set of control system benchmarks and  is  composed by 18 MIMO models extracted from the literature~\cite{bouabdallah, acrobot,cstr,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS},
+which include physical plants for UAV (unammed aerial vehicle), cruise control system, spring-mass damper, satellite, direct current (DC) servo motor, helicopter, inverted pendulum, pendulum, magnetic suspension, magnitezed pointer, 1/4 car suspension, computer tape driver, flexible beam, guidance system, USCG cutter tampa, continuous stirred tank reactor, voltage regulator, and an acrobot control system~\cite{abate2017, abatecav2017}.
+
+The first set of benchmarks uses the discrete model of a cruise control system for a car, and accounts for rolling friction, aerodynamic drag, and the gravitational disturbance force. %cruise-control
+The second set of benchmarks considers the discrete model of a simple spring-mass damper plant. %spring-mass damper
+A third set of benchmarks uses the discrete model for satellite attitude dynamics, which require attitude control for orientation of antennas and sensors w.r.t. Earth. %satellite
+The fourth and fifth set of benchmarks describe the discrete model of a DC servo motor velocity dynamics. %servor-motor
+The fifth set of benchcmarks corresponds an USCG cutter Tampa Heading Angle that describes the heading angle  dynamics of a Coast Guard cutter.
+The sixth set of benchmarks contain a flexible beam system that is a plant usually employed in vibration studies.
+It is  composed by a flexible metallic structure with piezoceramic actuators and sensors.%flexible beam
+The seventh set of benchmarks describes the discrete model for the Helicopter Longitudinal Motion, which provides the longitudinal motion dynamics of a helicopter. %helicopter
+The eighth set of benchmarks contains the discrete model for the known Inverted Pendulum, which describes a pendulum dynamics with its center of mass above its pivot point. %inverted pendulum
+The ninth set of benchmarks contains the Magnetic Suspension discrete model, which describes the dynamics of a mass that levitates with support only of a magnetic field. %magnetic suspension
+The tenth set of benchmarks contains the Computer Tape Driver discrete model, which describes a system to read and write data on a storage device. %tape driver
+The eleventh set of benchmarks contains the unmanned aerial vehicle (UAV) discret model, in particular, a quadrotor attitude system. %uav
+The twelfth set of benchmarks contains the 1/4 Car Suspension plant presents a physical model that connects a car to its wheels and allows relative motion between both parts. %1/4 car suspension
+The thirteenth set of benchmarks contains the Magnetized Pointer plant describes a physical model employed in analogue gauges and indicators that is rotated through interaction with magnetic fields.
+%magnitezed pointer
+The fourteenth set of benchmarks contains the pendulum which is system composed by a swinging point mass suspended from  a frictionless pivot through a negligible mass rod. %pendulum
+The fifteenth set of benchmarks  contains the Acrobot benchmark corresponds to the model of an two-link  underactuated robot manipulator, named Acrobot, linearized by partial  feedback linearization~\cite{acrobot}.
+%acrobot
+The sixteenth set of benchmarks contains a voltage regulator benchmark~\cite{KOKOTOVIC198023} that consists in a linear model of a synchronous machine connected to an  infinite bus.
+The seventeenth set of benchmarks contais a continuous stirred tank reactor which describes a linear model for PH dynamics of a PH  neutralization process of an aqueous solution of sodium acetate with  hydrochloric acid in a continuous flow stirred-tank reactor.%cstr
+And finally, the last set of benchmarks contaians the Guidance Control System benchmark which is another high-order system  model used by Chen et al.~\cite{CHEN1979389}  in order reduction  techniques.
+Guidance systems are used to determine the path of an autonomous vehicle movement.
 

### 2017-06-29 automatica/paper.tex
removed useless comment for Elizabeth
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
Proof for feedback model with continuous plant and discrete controller

@@
 Multiplying by $\mat{A}$ we get $X_T'$ as in \eqref{eq:contu_reachset}, thus proving the theorem.
+\end{proof}
+
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ \subsubsection{Discrete dynamics using reals for systems with discrete time feedback inputs}\label{sec:real_discrete_feedback_inputs}
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+The final case we analyse here is that of hybrid time systems, where the plant dynamics evolve in continuous time
+while the feedback dynamics evolve in discrete time.
+
+\begin{theorem}
+The expression
+ \begin{align}
+ \vec{x}_{t} &= (\mat{A}_{t-kT_s}-\mat{B}_{t-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
+ \end{align}
+ with $\mat{A}_t, \mat{B}_t$ as per \eqref{eq:continuous_tube_dyn} and $\mat{A}_d, \mat{B}_d$ as per equation \eqref{eq:discretize} is a witness of the system
+ \begin{align}
+ \dot{\vec{x}}_{t} &= \mat{A}\vec{x}+\mat{B}\vec{u}_t\nonumber\\
+ \vec{u}_t=\mat{K}\vec{x}_k  : kT_s \leq t < (k+1)T_s
+ \end{align}
+ \end{theorem}
+
+\begin{proof}
+Let $\mat{K}$ be a feedback controller such that $\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$. Let the output of
+the feedback system be a zero order holder such that $\vec{u}(t+kT_s)=\vec{u}(kT_s) : 0 \leq t < T_s$.
+The closed loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
+\begin{equation}
+\vec{x}_{k,t}=\mat{A}_t\vec{x}_k-\mat{B}_t\mat{K}\vec{x}_k = (\mat{A}_t-\mat{B}_t\mat{K})\vec{x}_k : 0 \leq t < T_s
+\end{equation}
+We further explore the dynamics across discrete time boundaries. Let $\mat{A}_d=\mat{A}_{T_s}$ and $\mat{B}_d=\mat{B}_{T_s}$
+\begin{align}
+\vec{x}_{k}&=\vec{x}_{k-1,T_s}= (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}\\
+\vec{x}_{k,T_s} &= (\mat{A}_d-\mat{B}_d\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}
+\end{align}
+which accelerating results becomes
+\begin{align}
+\vec{x}_{k} &= (\mat{A}_d-\mat{B}_d\mat{K}) ^k\vec{x}_0\\
+\vec{x}_{t} &= (\mat{A}_{t-kT_s}-\mat{B}_{t-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
+\end{align}
 \end{proof}

### 2017-06-29 ase2017/paper.tex

@@
 \subsection{Benchmarks Description}
+\label{benchmarks-description}
 %---------------------------------------------------
@@
 
+The main purpose of our experiments for set of the benchmarks described in Section~\ref{benchmarks-description} is (1) evaluate the performance of the \tool to produce stable controllers, and also (2) confirm the
+stability of the synthesized controllers outside of our model in state-space and transfer-function formats.
+
 %---------------------------------------------------

### 2017-06-29 ase2017/paper.tex
updated benchmarks

--- 2017-06-27 ase2017/paper.tex
@@
 \subsection{Benchmarks Description}
+\label{benchmarks-description}
 %---------------------------------------------------
 
-Our experimental evaluation consist of a set of control system benchmarks,
-which include physical plants for UAV, cruise control, spring-mass damper,
-satellite, direct current (DC) servo motor, helicopter, inverted pendulum,
-magnetic suspension, computer tape driver, robot manipulator, flexible beam,
-guidance system, and an antenna control system~\cite{abate2017, abatecav2017}.
+Our experimental evaluation consist of a set of control system benchmarks and  is  composed by 18 MIMO models extracted from the literature~\cite{bouabdallah, acrobot,cstr,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS},
+which include physical plants for UAV (unammed aerial vehicle), cruise control system, spring-mass damper, satellite, direct current (DC) servo motor, helicopter, inverted pendulum, pendulum, magnetic suspension, magnitezed pointer, 1/4 car suspension, computer tape driver, flexible beam, guidance system, USCG cutter tampa, continuous stirred tank reactor, voltage regulator, and an acrobot control system~\cite{abate2017, abatecav2017}.
+
+%The first set of benchmarks uses the discrete model of a cruise control system for a car, and accounts for rolling friction, aerodynamic drag, and the gravitational disturbance force. %cruise-control
+%The second set of benchmarks considers the discrete model of a simple spring-mass damper plant. %spring-mass damper
+%A third set of benchmarks uses the discrete model for satellite attitude dynamics, which require attitude control for orientation of antennas and sensors w.r.t. Earth. %satellite
+%The fourth and fifth set of benchmarks describe the discrete model of a DC servo motor velocity dynamics. %servor-motor
+%The fifth set of benchcmarks corresponds an USCG cutter Tampa Heading Angle that describes the heading angle  dynamics of a Coast Guard cutter.
+%The sixth set of benchmarks contain a flexible beam system that is a plant usually employed in vibration studies.
+It is  composed by a flexible metallic structure with piezoceramic actuators and sensors.%flexible beam
+%The seventh set of benchmarks describes the discrete model for the Helicopter Longitudinal Motion, which provides the longitudinal motion dynamics of a helicopter. %helicopter
+%The eighth set of benchmarks contains the discrete model for the known Inverted Pendulum, which describes a pendulum dynamics with its center of mass above its pivot point. %inverted pendulum
+%The ninth set of benchmarks contains the Magnetic Suspension discrete model, which describes the dynamics of a mass that levitates with support only of a magnetic field. %magnetic suspension
+%The tenth set of benchmarks contains the Computer Tape Driver discrete model, which describes a system to read and write data on a storage device. %tape driver
+%The eleventh set of benchmarks contains the unmanned aerial vehicle (UAV) discret model, in particular, a quadrotor attitude system. %uav
+%The twelfth set of benchmarks contains the 1/4 Car Suspension plant presents a physical model that connects a car to its wheels and allows relative motion between both parts. %1/4 car suspension
+%The thirteenth set of benchmarks contains the Magnetized Pointer plant describes a physical model employed in analogue gauges and indicators that is rotated through interaction with magnetic fields.
+%magnitezed pointer
+%The fourteenth set of benchmarks contains the pendulum which is system composed by a swinging point mass suspended from  a frictionless pivot through a negligible mass rod. %pendulum
+%The fifteenth set of benchmarks  contains the Acrobot benchmark corresponds to the model of an two-link  underactuated robot manipulator, named Acrobot, linearized by partial  feedback linearization~\cite{acrobot}.
+%acrobot
+%The sixteenth set of benchmarks contains a voltage regulator benchmark~\cite{KOKOTOVIC198023} that consists in a linear model of a synchronous machine connected to an  infinite bus.
+%The seventeenth set of benchmarks contais a continuous stirred tank reactor which describes a linear model for PH dynamics of a PH  neutralization process of an aqueous solution of sodium acetate with  hydrochloric acid in a continuous flow stirred-tank reactor.%cstr
+%And finally, the last set of benchmarks contaians the Guidance Control System benchmark which is another high-order system  model used by Chen et al.~\cite{CHEN1979389}  in order reduction  techniques.
+Guidance systems are used to determine the path of an autonomous vehicle movement.
 
@@
 %---------------------------------------------------
+
+The main purpose of our experiments for set of the benchmarks described in Section~\ref{benchmarks-description} is (1) evaluate the performance of the \tool to produce stable controllers, and also (2) confirm the
+stability of the synthesized controllers outside of our model in state-space and transfer-function formats.
 

### 2017-06-29 ase2017/paper.tex
ase
Signed-off-by: aabate <aabate@cs.ox.ac.uk>

@@
 
-\title{DSSynth: An Automated Controller Synthesis Tool \\ for Physical Plants via MATLAB Toolbox}
+\title{DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants} 
+% via MATLAB Toolbox}
 
@@
 We present an automated MATLAB Toolbox, named as DSSynth 
-(Digital-System Synthesizer), to synthesize stable and safe digital controllers 
-for physical plants represented as linear time-invariant
-systems with single-input and single-output. In particular, DSSynth synthesizes digital 
-controllers w.r.t. the stability and safety specifications by taking into account finite word-length 
-effects. DSSynth considers the complete range
+(Digital-System Synthesizer), to synthesize sound digital controllers 
+for physical plants that are represented as linear time-invariant
+systems with single input and output. In particular, DSSynth synthesizes digital 
+controllers that are sound w.r.t. stability and safety specifications by taking into account finite word-length 
+effects in their representation. DSSynth considers the complete range
 of approximations, including time discretization, quantization effects, 
-and finite-precision arithmetic and its rounding errors. 
-Currently, there are two DSSynth toolbox versions: command-line and 
-MATLAB application for synthesizing digital controllers for physical plants 
-represented by transfer-function or state-space equations. The resulting toolbox 
-enables application of program synthesis to real-world systems by control engineers.
+and finite-precision arithmetic (and its rounding errors). 
+Currently, there are two DSSynth versions for synthesizing digital controllers for physical plants 
+represented by transfer-function or state-space equations: a command-line and 
+a MATLAB application. The resulting toolbox 
+enables application of program synthesis to real-world control engineering systems.
 \end{abstract}
@@
 
-Control theory achieves the construction of reliable systems by 
-offering mathematical guarantees about the stability and the desired 
-performance of closed-loop dynamical systems, where states or outputs of discrete plant $G(z)$ 
+Control theory targets the construction of reliable systems by providing mathematical guarantees about the stability and the desired 
+performance of closed-loop dynamics, where outputs of discrete plant $G(z)$ 
 are fed back and compared to a reference signal to which a (designed) 
-controller $C(z)$ should maintain a set of control objectives~\cite{astrom1997computer}. 
+controller $C(z)$ should steer~\cite{astrom1997computer}. 
 Fig.~\ref{fig:typical-control-system} shows a typical closed-loop digital control system.
@@
 
-There are various mathematical representations for digital control
-systems,  e.g.,  difference  equations, transfer functions and state-space
-equations. Here, linear time-invariant (LTI) systems 
-with single-input and single-output (SISO) are considered and 
-represented by transfer functions or state space equations. LTI systems 
+There are various mathematical representations for control 
+systems,  e.g.,  transfer functions and state-space equations (difference or differential equations). 
+Here, 
+systems with a single input and a single output (SISO) are considered and 
+represented by transfer functions or state-space LTI models. LTI models 
 are used in several engineering applications to support non-trivial tasks when 
@@
 }}
-\caption{CEGIS with multi-staged verification}
+\caption{CEGIS with multi-staged verification \textcolor{red}{[make this fit the column]}}
 \label{fig:CEGIS-precision-increment}
@@
 
-\tool can synthesize digital controllers for dynamic physical plants 
-w.r.t. stability and safety, designed in MATLAB through transfer-function 
-and state-space representations using the CEGIS approach.
+\tool can synthesize digital controllers for dynamic physical plants, 
+represented in MATLAB through transfer-function and state-space,  
+w.r.t. stability and safety, using the CEGIS approach. 
 %
 Given the current literature in controller synthesis, there is no other MATLAB toolbox 
-for synthesizing stable digital controllers for physical plants, while taking into account implementation 
-aspects (fixed-point arithmetic). 
+for synthesizing stable digital controllers for physical plants, while taking into account all aspects of its digital implementation (fixed-point arithmetic). 
 %
@@
 and be combined with DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to verify/validate 
- other controller properties (e.g., limit cycle).
+other controller properties (e.g., presence of limit cycles).
+
+\textcolor{red}{[Pls update CAV reference with details from proof of article just received from Springer. ]}
 

### 2017-06-29 ase2017/paper.tex
ase
Signed-off-by: aabate <aabate@cs.ox.ac.uk>

@@
 %
-\noindent where $z^{-1}$ is called backward-shift operator; $A(z)$ and $B(z)$ are 
-the denominator and numerator polynomials, respectively; and $N$ and $M$
+\noindent where $z^{-1}$ is called the backward-shift operator; $A(z)$ and $B(z)$ are 
+the denominator and numerator polynomials; and $N$ and $M$
 represent the denominator and numerator polynomials order, respectively.
 %
-In state-space format, the digital control system represents the behavior 
-of a system via a state evolution equation $x(n+1)$ and an instantaneous 
+In a state-space form, 
+the behavior of a system is represented via a state evolution equation $x(n+1)$ and an instantaneous 
 output equation $y(n)$, as follows:
@@
 
-\noindent where $A$, $B$, $C$ and $D$ are matrices that fully specify a digital system. 
+\noindent where $A$, $B$, $C$ and $D$ are matrices that fully specify the model. 
 %
@@
 digital control system theory is used, mainly due to the finite-word 
-length (FWL) effects~\cite{Guang2013, Istepanian2001}, time discretization 
+length (FWL) effects leading to truncation 
+or round-off errors~\cite{Guang2013, Istepanian2001}, time discretization 
 and quantization noise, which are typically introduced by Analogue-to-Digital 
-(ADC) and Digital-to-Analogue (DAC) conversion, leading to truncation 
-or round-off errors~\cite{astrom1997computer}.
+(ADC) and Digital-to-Analogue (DAC) conversion~\cite{astrom1997computer}.
 
-Recently, a new methodology to synthesize digital control systems was proposed, 
-named as DSSynth (Digital-System Synthesizer)~\cite{abate2017, abatecav2017}, 
+Recently, a new methodology to synthesize digital control systems has been proposed, 
+named DSSynth (Digital-System Synthesizer)~\cite{abate2017, abatecav2017}, 
 which is based on the Counter-Example Guided Inductive Synthesis 
 (CEGIS) approach~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. Here, CEGIS is used
-as a program synthesis engine that is able to produce digital controllers for highly non-trivial 
+as a program synthesis engine that is able to generate sound digital controllers for highly non-trivial 
 control system specifications with a very high degree of automation. Program synthesis engines 
@@
 programs from a given template. The candidate programs are iteratively refined to eventually 
-satisfy the specification. Modern synthesis engines as the one used here combine automated testing, genetic algorithms 
+satisfy the specification. Modern synthesis engines such as the one used here combine automated testing, genetic algorithms 
 and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
-DSSynth synthesizes stable digital controllers using that CEGIS-based approach,
+DSSynth synthesizes stable digital controllers using the CEGIS-based approach,
 for a given physical plant represented by either transfer functions or state-space equations~\cite{abate2017,abatecav2017}.
@@
 recent advances in bit-accurate verification of programs to synthesize controllers w.r.t. FWL effects. MATLAB already offers a tool 
-named as Control System Tuner~\cite{autotuner} for automatically designing controllers based on optimization solvers or graphical analysis. 
+named as Control System Tuner~\cite{autotuner} \textcolor{red}{[fix ref]} for automatically designing controllers based on optimization solvers or graphical analysis. 
 However, the Control System Tuner is unable to consider FWL effects during the controller synthesis process.
@@
 
-The present paper addresses this problem and describes a toolbox for the DSSynth tool~\cite{abate2017, abatecav2017} 
-in MATLAB's environment named as \tool. The main advantage regarding the use of a MATLAB toolbox 
+The present paper addresses this limitation and describes a toolbox for the DSSynth tool~\cite{abate2017, abatecav2017} 
+in a MATLAB environment, named \tool. The main advantage for the use of a MATLAB toolbox 
 lies on designing physical plants in MATLAB and then promptly synthesizing a stable and safe digital controller,
@@
 through transfer-function or state-space representations, considering low-level systems parameters 
-(implementation features and numerical format), and then obtain a stable and safe synthesized digital-controller.
+(implementation features and numerical format), and then to synthesize a stable and safe digital controller.
 
@@
 synthesis phase in the form of a new counterexample that is added to
-the set of test inputs and the loop iterates again.
+the set of test inputs, and the loop iterates again.
 
 We use two different instantiations of the synthesiser
-in order to synthesise stable and safe digital
+in order to find stable and safe digital
 controllers. The two approaches differ in
@@
 
-The first approach presented in Figure~\ref{fig:CEGIS-precision-increment}
+The first approach, presented in Figure~\ref{fig:CEGIS-precision-increment}, 
 uses a multi-staged verification process. 
-Essentially, it starts by devising a
-digital controller that stabilizes the system while remaining safe for a
-pre-selected time horizon and a single initial state; then, it
-employs a multi-staged verification process:
+It starts by devising a digital controller that stabilizes the model while remaining safe for a
+pre-selected time horizon ($k$) and a single initial state; then, it
+employs a multi-staged verification process as follows:
 (i) The first verification stage checks that the candidate
@@
 (ii) The second verification stage 
- restores soundness with respect to the plant's precision
+ restores soundness with respect to the plant precision
 by using interval arithmetic \cite{moore1966interval} to validate the 
@@
 iterations required to sufficiently unwind the closed-loop state-space
-system such that the boundaries are not violated for any larger number of
+model such that the boundaries are not violated for any larger number of
 iterations, and
@@
 
-Instead of unfolding the dynamics, the second approach shown in Figure~\ref{fig:CEGARIS}
+Instead of unfolding the dynamics, the second approach (shown in Figure~\ref{fig:CEGARIS}) 
 employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to 
-evaluate all possible progressions of the system simultaneously. This eliminates the need for
-a completenes threshold since the time horizon is always infinite.
+simultaneously evaluate all possible progressions of the model. This eliminates the need for
+a completeness threshold, since the time horizon considered in abstract acceleration is infinite.
 Since this model is based on abstraction, we initially perform the synthesis over a basic
@@
 complex model when a counterexample is found. Thus, we may only look at the gain of the
-system to synthesise a controller and add further restrictions on specific sections of the reach
-tube when these prove to invalidate the solution. The use of Counterexample-Guided 
-Abstraction Refinement results in much faster synthesis and verification since it is applied to
+model to synthesise a controller and to add further restrictions on specific sections of the reach
+tube when these prove to invalidate the solution. The use of this Counterexample-Guided 
+Abstraction-Refinement (CEGAR) results in much faster synthesis and verification since it is applied to
 both phases, allowing for faster results whilst maintaining soundness for an infinite time horizon.
@@
 In step $1$, the user has to define the digital controller representation, 
-which can be transfer-function or state-space equations. 
+which can be a transfer function or a state-space model. 
 In step $2$, the physical plant (represented by Equations (\ref{eq:transferfunction}) 
-and (\ref{eq:ss-example})) must be designed, using the preferred method 
+and (\ref{eq:ss-example})) must be designed, using a method selected 
 from the control literature~\cite{astrom1997computer}. Finally, in step $3$, 
@@
 specification. Finally, in step $C$, the synthesized digital controller considering FWL effects is produced. 
-The output generated by \tool is the synthesized digital controller represented either in transfer-function 
+The output generated by \tool is the synthesized digital controller represented either in transfer function form 
 or state-space format. The synthesis is considered to be \emph{successful} if a digital controller is correctly 
@@
 incorrectly defined in previous steps, or if there is no solution (digital controller) for the respective physical plant 
- given the digital controller word-length.
+given the digital controller word length.
 

### 2017-06-29 ase2017/paper.tex
ase
Signed-off-by: aabate <aabate@cs.ox.ac.uk>

@@
 Our CEGIS engine is implemented as an integrated module within the bounded model checker CBMC~\cite{cbmc}.  CBMC
-transforms an ANSI-C representation of our closed-loop control system models into its internal format called
+transforms an ANSI-C representation of our closed-loop control system model into its internal format called
 \emph{GOTO}.  We instrument this internal \emph{GOTO} program for each synthesis or verification scenario accordingly,
 and use CBMC as an oracle to answer our queries.  CBMC itself relies on an underlying SAT or SMT solver to solve the
-resulting formulae.  We model FWL effects, time discretization and quantization noise explicitly using CBMC's
+resulting formulae.  We model FWL effects, time discretization and the presence of quantization noise explicitly using CBMC's  
 nondeterminism API.  Our module was included in CBMC~5.7 and is available for
@@
 \item \textbf{Execution}: obtains the ANSI-C program from the previous step 
-and calls our CEGIS engine as back-end program synthesis tool to perform the automated synthesis;
+and calls our CEGIS engine as a back-end program synthesis tool to perform the automated synthesis;
 \item \textbf{Extraction}: obtains the ``.log'' file that is generated 
@@
 \item \textbf{Representation}: the synthesis can be 
-performed for digital systems specified as 
-transfer-function or state-space equations;
+performed for digital systems specified via 
+transfer function or as state-space models;
 \item \textbf{Fixed-Point Arithmetic}: the digital 
@@
 
-Users must provide a digital system described as a MATLAB system 
-using a \texttt{tf} (for transfer-function) or an \texttt{ss} (for state-space) 
+Users must provide a digital system described as a MATLAB model 
+using a \texttt{tf} (for transfer function) or an \texttt{ss} (for state-space model) 
 command (cf. step $1$ of Fig.~\ref{fig:synthesis-flow}).
@@
 
-\noindent where \texttt{plant} is the physical plant in state-space or transfer-function representation, 
+\noindent where \texttt{plant} is the physical plant in state-space or transfer function representation, 
 \texttt{intBits} is the integer part, \texttt{fracBits} is the fractional part, \texttt{maxR} and \texttt{minR} 
@@
 After executing the \texttt{synthesize} command in MATLAB, 
-\tool provides the synthesized digital controller, according to 
-the digital system representation, {\it i.e.}, transfer-function or 
-state-space equations.
+\tool provides the synthesized digital controller, according to the digital system representation.
 
@@
 
-A digital system is stable \textit{iff} all of its poles are inside the $z$-plane unitary circle; 
-poles must have the modulus less than one. In order to compute the poles for the digital 
+A digital system is stable \textit{iff} all of its poles are inside the $z$-plane unity circle, 
+namely poles must have the modulus less than one. In order to compute the poles for the digital 
 system represented by Equations~\eqref{equation_plant} and \eqref{equation_controller}, 
@@
 \tool can synthesize digital controllers for dynamic physical plants, 
-represented in MATLAB through transfer-function and state-space,  
+represented in MATLAB as a transfer function or a state-space model,  
 w.r.t. stability and safety, using the CEGIS approach. 

### 2017-06-30 ase2017/paper.tex
reviewed benchmarks description
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-Our experimental evaluation consist of a set of control system benchmarks and  is  composed by 18 MIMO models extracted from the literature~\cite{bouabdallah, acrobot,cstr,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS},
-which include physical plants for UAV (unammed aerial vehicle), cruise control system, spring-mass damper, satellite, direct current (DC) servo motor, helicopter, inverted pendulum, pendulum, magnetic suspension, magnitezed pointer, 1/4 car suspension, computer tape driver, flexible beam, guidance system, USCG cutter tampa, continuous stirred tank reactor, voltage regulator, and an acrobot control system~\cite{abate2017, abatecav2017}.
+Our experimental evaluation consists of $18$ SISO control system benchmarks 
+extracted from the literature~\cite{abate2017, abatecav2017,bouabdallah, acrobot,cstr,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS},
+which include physical plants for unmanned aerial vehicle (UAV), cruise control system, 
+spring-mass damper, satellite, direct current (DC) servo motor, helicopter, 
+inverted pendulum, pendulum, magnetic suspension, magnitezed pointer, 1/4 car suspension, 
+computer tape driver, flexible beam, guidance system, USCG cutter tampa, continuous stirred tank reactor, 
+voltage regulator, and an acrobot control system.
 

### 2017-06-30 ase2017/paper.tex
reviewed experimental setup
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-For all evaluated benchmarks, the signal input range lies between $-1$ and $1$, and the implementation used for the integer part is $8$ bits, and for fractional part is also $8$ bits.
-%
-All experiments with \tool v$1$.$0$.$0$  were conducted on an otherwise idle Intel Core i$7-2600$ 
-$3.40$ GHz processor, with $24$ GB of RAM, running Ubuntu $64$-bits.
+For all evaluated benchmarks, the signal input range related to the control system 
+lies between $-1$ and $1$. The implementation features used for digital controller are:
+$8$-bits for the integer part (including the sign bit) and $8$-bits for the fractional 
+part. All experiments with \tool v$1$.$0$.$0$  were conducted on an otherwise idle 
+Intel Core i$7-2600$ $3.40$ GHz processor, with $24$ GB of RAM, running Ubuntu $64$-bits.
 

### 2017-06-30 ase2017/paper.tex
reviewed experimental objectives
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-The main purpose of our experiments for set of the benchmarks described in Section~\ref{benchmarks-description} is (1) evaluate the performance of the \tool to produce stable controllers, and also (2) confirm the
-stability of the synthesized controllers outside of our model in state-space and transfer-function formats.
+The main objectives of our experimental evaluation is to (1) evaluate the \tool performance 
+to produce stable controllers, and also (2) confirm the stability of the synthesized digital 
+controllers outside of our model, using both the transfer-function and state-space representations.
 

### 2017-06-30 ase2017/paper.tex
fixed references
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
implemented Alessadro's suggestions
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 recent advances in bit-accurate verification of programs to synthesize controllers w.r.t. FWL effects. MATLAB already offers a tool 
-named as Control System Tuner~\cite{autotuner} \textcolor{red}{[fix ref]} for automatically designing controllers based on optimization solvers or graphical analysis. 
+named as Control System Tuner~\cite{autotuner} for automatically designing controllers based on optimization solvers or graphical analysis. 
 However, the Control System Tuner is unable to consider FWL effects during the controller synthesis process.
@@
 
-\textcolor{red}{[Pls update CAV reference with details from proof of article just received from Springer. ]}
-
 \bibliographystyle{IEEEtran}

### 2017-06-30 ase2017/paper.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 are used in several engineering applications to support non-trivial tasks when 
-applied to embedded systems (e.g., robot manipulator, power plants 
-and guidance system). The following expression presents the general form 
+applied to embedded \& cyber-physical systems (e.g., robot manipulator, smart grid, 
+power plants, distributed robotics, and automatic pilot avionics). 
+The following expression presents the general form 
 of a discrete plant or a digital controller based on the transfer function representation:
@@
 Satisfiability Modulo Theories (SMT) solvers. Pessoa~\cite{mazo2010pessoa} is another 
-toolbox applied to the synthesis of correct-by-design digital controllers. 
+toolbox, but applied to the synthesis of correct-by-design digital controllers. 
 In particular, Pessoa is based on approximate bisimulation, which allows control engineers to replace differential equations, 
@@
 
-The present paper addresses this limitation and describes a toolbox for the DSSynth tool~\cite{abate2017, abatecav2017} 
+The present tool paper addresses this limitation and describes a toolbox for the DSSynth tool~\cite{abate2017, abatecav2017} 
 in a MATLAB environment, named \tool. The main advantage for the use of a MATLAB toolbox 

### 2017-06-30 ase2017/paper.tex
reviewed section 2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 $k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
-completeness threshold $\overline{k}$ for the current candidate controller $K$,
-i.e., the number of
+completeness threshold $\overline{k}$ for the current candidate controller 
+$K$~\cite{abatecav2017}, i.e., the number of
 iterations required to sufficiently unwind the closed-loop state-space
@@
 tube when these prove to invalidate the solution. The use of this Counterexample-Guided 
-Abstraction-Refinement (CEGAR) results in much faster synthesis and verification since it is applied to
+Abstraction-Refinement results in much faster synthesis and verification since it is applied to
 both phases, allowing for faster results whilst maintaining soundness for an infinite time horizon.

### 2017-06-30 ase2017/paper.tex
reviewed section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Currently, there are two DSSynth versions for synthesizing digital controllers for physical plants 
-represented by transfer-function or state-space equations: a command-line and 
+represented by transfer function or state-space equations: a command-line and 
 a MATLAB application. The resulting toolbox 
@@
 %expressed as difference equations, transfer functions or state-space equations. 
-%Here, the focus is on transfer-function and state-space representations.
+%Here, the focus is on transfer function and state-space representations.
 
@@
 Additionally, when using the \tool, an engineer is able to model a physical plant with MATLAB, 
-through transfer-function or state-space representations, considering low-level systems parameters 
+through transfer function or state-space representations, considering low-level systems parameters 
 (implementation features and numerical format), and then to synthesize a stable and safe digital controller.
@@
 specification. Finally, in step $C$, the synthesized digital controller considering FWL effects is produced. 
-The output generated by \tool is the synthesized digital controller represented either in transfer function form 
-or state-space format. The synthesis is considered to be \emph{successful} if a digital controller is correctly 
-synthesized w.r.t. FWL effects; otherwise the synthesis is considered to be \emph{failed}, if any parameter is 
-incorrectly defined in previous steps, or if there is no solution (digital controller) for the respective physical plant 
-given the digital controller word length.
+The output generated by \tool is the synthesized digital controller represented either in transfer function 
+or state-space equation. The synthesis is considered to be \emph{successful} if a digital controller is correctly 
+synthesized w.r.t. FWL effects; otherwise, if any parameter is incorrectly defined in previous steps, 
+or if there is no solution (digital controller) for the respective physical plant (given the digital controller
+ implementation aspects), then the synthesis is considered to be \emph{failed}.
 
-Our CEGIS engine is implemented as an integrated module within the bounded model checker CBMC~\cite{cbmc}.  CBMC
+Our CEGIS engine is implemented as an integrated module within the C bounded model checker (CBMC)~\cite{cbmc}.  CBMC
 transforms an ANSI-C representation of our closed-loop control system model into its internal format called
@@
 resulting formulae.  We model FWL effects, time discretization and the presence of quantization noise explicitly using CBMC's  
-nondeterminism API.  Our module was included in CBMC~5.7 and is available for
-download\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}.  We further created a VirtualBox OVA image
+nondeterminism API (e.g., \texttt{nondet}, \texttt{CPROVER\_assume} intrinsic functions).  Our module was included in CBMC~5.7 and is available for
+public download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}  We further created a VirtualBox OVA image
 with our tool pre-installed, including our MATLAB-generated benchmarks and benchmark shell script with instructions
 to run all benchmarks and reproduce our
-experiments\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}.  The current development branch
+experiments\.footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}  The current development branch
 of our tool is available in a public GitHub
-repository\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}.
+repository.\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}
 
@@
 module, $585$ and $800$ lines of C code in the naive and abstract accelerator
-model respectively.  $4000$ lines of C code for utility functions such as
+model, respectively.  $4000$ lines of C code for utility functions such as
 interval and fixed-point arithmetic, as well as $1000$ lines of C++ code in the
-control synthesis module in CEGIS CBMC.  We evaluate \tool using $20$ regression
-test cases.
+control synthesis module in CEGIS CBMC.  We evaluate \tool using about $20$ 
+control system benchmarks.
 
@@
 to produce stable controllers, and also (2) confirm the stability of the synthesized digital 
-controllers outside of our model, using both the transfer-function and state-space representations.
+controllers outside of our model, using both the transfer function and state-space representations.
 

### 2017-06-30 ase2017/paper.tex
reviewed section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \item \textbf{Setup}: obtains the physical plant, fixed-point format 
-and dynamic input ranges, and translates them to a specific structure in MATLAB;
+and dynamic input ranges, and translates them to a specific structure in MATLAB.
 \item \textbf{Parse}: obtains the digital system specification and translates 
-it into an ANSI-C program;
-\item \textbf{Execution}: obtains the ANSI-C program from the previous step 
+it into an ANSI-C program.
+\item \textbf{Execution}: obtains the ANSI-C program from the previous (parse) step 
 and calls our CEGIS engine as a back-end program synthesis tool to perform the automated synthesis;
 \item \textbf{Extraction}: obtains the ``.log'' file that is generated 
-after the synthesis phase and then checks the synthesized digital-controller;
-\item \textbf{Report}: obtains the digital controller from the previous step 
+after the synthesis phase and then checks the synthesized digital-controller.
+\item \textbf{Report}: obtains the digital controller from the previous (extraction) step 
 and translates it into the MATLAB structures to show the respective result to the user.
@@
 performed for digital systems specified via 
-transfer function or as state-space models;
+transfer function or as state-space models.
 \item \textbf{Fixed-Point Arithmetic}: the digital 
 controller is synthesized considering FWL effects, 
-in fixed-point numeric representation;
+using the given fixed-point numerical representation.
 \item \textbf{Interface}: the synthesis can be executed 
@@
 For the GUI application, the user can plot the step response 
-to reproduce the stability in closed-loop of the synthesized digital controller;
+to reproduce the stability in closed-loop of the synthesized digital controller.
 \end{itemize}
@@
 
-A graphical user interface application was developed (Fig.~\ref{fig:gui-for-tf}) 
+A graphical user interface application was developed (as shown in Fig.~\ref{fig:gui-for-tf}) 
 to favor digital controller synthesis in MATLAB, besides improving usability and, 
@@
 		\hfil
-    \subfloat[Define implementation features and dynamic range.]{
+    \subfloat[Define implementation aspects and dynamic range.]{
 	\includegraphics[width=0.2\textwidth]{step2.png}
@@
 		\hfil
-    \subfloat[Digital controller synthesized by DSSynth.]{
+    \subfloat[Resulting digital controller synthesized by DSSynth.]{
 	\includegraphics[width=0.2\textwidth]{step3.png}
@@
 		\hfil
-    \subfloat[Step Response for the synthesized digital controller]{
+    \subfloat[Step response for the synthesized digital controller.]{
 	\includegraphics[width=0.22\textwidth]{step4.png}

### 2017-06-30 ase2017/paper.tex
Adjust Fig 2

--- 2017-06-30 ase2017/paper.tex
@@
 are used in several engineering applications to support non-trivial tasks when 
-applied to embedded \& cyber-physical systems (e.g., robot manipulator, smart grid, 
-power plants, distributed robotics, and automatic pilot avionics). 
-The following expression presents the general form 
+applied to embedded systems (e.g., robot manipulator, power plants 
+and guidance system). The following expression presents the general form 
 of a discrete plant or a digital controller based on the transfer function representation:
@@
 Satisfiability Modulo Theories (SMT) solvers. Pessoa~\cite{mazo2010pessoa} is another 
-toolbox, but applied to the synthesis of correct-by-design digital controllers. 
+toolbox applied to the synthesis of correct-by-design digital controllers. 
 In particular, Pessoa is based on approximate bisimulation, which allows control engineers to replace differential equations, 
@@
 
-The present tool paper addresses this limitation and describes a toolbox for the DSSynth tool~\cite{abate2017, abatecav2017} 
+The present paper addresses this limitation and describes a toolbox for the DSSynth tool~\cite{abate2017, abatecav2017} 
 in a MATLAB environment, named \tool. The main advantage for the use of a MATLAB toolbox 
@@
 \centering
-\resizebox{.5\textwidth}{!}
+\resizebox{.43\textwidth}{!}
 {
-\hspace{-1cm}
   \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
@@
 }}
-\caption{CEGIS with multi-staged verification \textcolor{red}{[make this fit the column]}}
+\caption{CEGIS with multi-staged verification}
 \label{fig:CEGIS-precision-increment}
@@
 $k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
-completeness threshold $\overline{k}$ for the current candidate controller 
-$K$~\cite{abatecav2017}, i.e., the number of
+completeness threshold $\overline{k}$ for the current candidate controller $K$,
+i.e., the number of
 iterations required to sufficiently unwind the closed-loop state-space
@@
 tube when these prove to invalidate the solution. The use of this Counterexample-Guided 
-Abstraction-Refinement results in much faster synthesis and verification since it is applied to
+Abstraction-Refinement (CEGAR) results in much faster synthesis and verification since it is applied to
 both phases, allowing for faster results whilst maintaining soundness for an infinite time horizon.

### 2017-06-30 ase2017/paper.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2017-06-30 ase2017/paper.tex
@@
 
-In Fig.~\ref{toolbox-usage}, ``num'' represents $A(z)$ and ``den'' represent $B(z)$, while 
+In Fig.~\ref{toolbox-usage}, ``num'' represents $B(z)$ and ``den'' represent $A(z)$, while 
 $y$ represents the synthesized stable digital controller, which is defined by Eq.(\ref{equation_controller}).

### 2017-06-30 ase2017/paper.tex
reviewed section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 to achieve a general equation regarding the transfer function representation.
+
 The general equation that represents the combination between Equations~\eqref{equation_plant}
-and~\eqref{equation_controller} is
+and~\eqref{equation_controller} using the \texttt{series} configuration (as shown in Figure~\ref{fig:typical-control-system}) is
 %

### 2017-06-30 ase2017/paper.tex
intro editing

@@
 \label{eq:transferfunction}
-H(z)=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M}z^{-M}}{1+a_{1}z^{-1}+...+a_{N}z^{-N}},
+H(z)=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M}z^{-M}}{a_{0}+a_{1}z^{-1}+...+a_{N}z^{-N}},
 \end{equation}
@@
 as a program synthesis engine that is able to generate sound digital controllers for highly non-trivial 
-control system specifications with a very high degree of automation. Program synthesis engines 
-use a specification as the starting point, and subsequently produce a sequence of candidate 
+control system specifications with a very high degree of automation. The program synthesis engine 
+uses a specification as starting point, and subsequently produces a sequence of candidate 
 programs from a given template. The candidate programs are iteratively refined to eventually 
@@
 and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
-DSSynth synthesizes stable digital controllers using the CEGIS-based approach,
+Using the CEGIS-based approach, DSSynth synthesizes stable digital controllers
 for a given physical plant represented by either transfer functions or state-space equations~\cite{abate2017,abatecav2017}.

### 2017-06-30 ase2017/paper.tex
intro editing

@@
 However, the Control System Tuner is unable to consider FWL effects during the controller synthesis process.
-As a result, there is no other MATLAB toolbox to perform digital controller synthesis based on 
-program synthesis engines and considering the complete range of approximations, including time discretization, 
+To the best of our knowledge, there is no MATLAB toolbox able to perform digital controller synthesis based on 
+program synthesis engines that considers the complete range of approximations, including time discretization, 
 quantization effects, and finite-precision arithmetic and its rounding errors.
@@
 considering the complete range of approximations. 
-Additionally, when using the \tool, an engineer is able to model a physical plant with MATLAB, 
+Notably, when using the \tool, an engineer is able to model a physical plant with MATLAB
 through transfer function or state-space representations, considering low-level systems parameters 
-(implementation features and numerical format), and then to synthesize a stable and safe digital controller.
+(implementation features and numerical format).
 

### 2017-06-30 ase2017/paper.tex
improved illustrative example
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 the user can invoke the \texttt{feedback} and \texttt{series} commands in MATLAB~\cite{matlab-toolbox} 
-to achieve a general equation regarding the transfer function representation.
+to achieve a general equation regarding the transfer function representation as shown in Figure~\ref{combine-controller-plant}.
 
-The general equation that represents the combination between Equations~\eqref{equation_plant}
-and~\eqref{equation_controller} using the \texttt{series} configuration (as shown in Figure~\ref{fig:typical-control-system}) is
+\begin{figure}[ht]
+\scriptsize
+\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
+>> num = [-0.99832 0.09587 0.1926];
+>> den = [1 0.5665 0.75];
+>> controller = tf(num,den,0.002);
+>> num = [-0.06875 0 0];
+>> den = [1.0000 -1.696 0.7089];
+>> plant = tf(num,den,0.002);
+>> sys = series(controller,plant)
+>> sys =
+>> 
+>>      0.06863 z^4 - 0.006591 z^3 - 0.01324 z^2
+>>  ------------------------------------------------
+>>  z^4 - 1.129 z^3 + 0.4981 z^2 - 0.8704 z + 0.5317
+\end{lstlisting}
+\vspace{-0.2cm}
+\caption{General equation for the closed-loop control system using the series configuration (as shown in Figure~\ref{fig:typical-control-system}).}
+\label{combine-controller-plant}
+\end{figure}
+
+The general equation that represents the closed-loop control system using the series 
+configuration is described by Equation~\ref{equation_general} as follows
 %
@@
 \label{equation_general}
-\frac{N(z)}{D(z)}=\frac{0.06863z^{4} - 0.006591z^{3} - 0.01324z^{2}}{1.069z^{4} - 1.136z^{3} + 0.4849z^{2} -0.8704z + 0.5317}.
+\frac{N(z)}{D(z)}=\frac{0.06863z^{4} - 0.006591z^{3} - 0.01324z^{2}}{z^{4} - 1.129z^{3} + 0.4981z^{2} -0.8704z + 0.5317}.
 \end{equation}
 
-For the stability check, if any root has modulus equal or greater than one, then the system is unstable; 
+For the stability check, if any root of the polynomial $D(z)$ in Equation~\ref{equation_general} 
+has modulus equal or greater than one, then the system is unstable; 
 otherwise, it is stable. Indeed, the roots computed by the function \texttt{roots} 
-in MATLAB~\cite{matlab-toolbox} result in the following poles: 
-$-0.2909 + 0.8065i$, $-0.2909 - 0.8065i$, $0.8553$ and $0.7924$, 
+in MATLAB~\cite{matlab-toolbox} result in the following poles as shown in Figure~\ref{roots-of-dz}, 
 which means that DSSynth has synthesized a stable digital controller.
+
+\begin{figure}[ht]
+\scriptsize
+\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
+>> den = [1 -1.129 0.4981 -0.8704 0.5317]
+>> r = roots(den)
+>> r =
+>>  -0.2833 + 0.8185i
+>>  -0.2833 - 0.8185i
+>>   0.9480 + 0.0000i
+>>   0.7476 + 0.0000i
+\end{lstlisting}
+\vspace{-0.2cm}
+\caption{Roots of the polynomial $D(z)$ given by Equation~\ref{equation_general}.}
+\label{roots-of-dz}
+\end{figure}
 

### 2017-06-30 ase2017/paper.tex
Edited Sec 2

@@
 The design of our synthesizer consists of two phases, an inductive
-synthesis phase and a validation phase, which interact via a finite
-set of test vectors that is updated incrementally.  Given a stability
-and safety specification, the inductive synthesis procedure tries to
-find a candidate solution satisfying the specification for the given set of test inputs.
+synthesis phase, {\sc synthesise}, and a validation phase, {\sc verify},
+which interact via a finite set of test vectors that is updated
+incrementally.  Given a stability and safety specification, the
+inductive synthesis procedure tries to find a candidate solution
+satisfying the specification for the given set of test inputs.
 %
@@
    \path
-    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$K$} ([yshift=2em]verif1.west)
+    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {K} ([yshift=2em]verif1.west)
     ([yshift=-2em]verif1.west) edge node {C-ex} ([yshift=-2em]synth.east)
-    ([xshift=-5em]fp.north) edge node[align=center]  {T/F} ([xshift=-5em]verif2.south)
-    ([xshift=-5em]sv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif3.south)
+    ([xshift=-5em]fp.north) edge node[align=center]  {} ([xshift=-5em]verif2.south)
+    ([xshift=-5em]sv.north) edge node[align=center]  {} ([xshift=-5em]verif3.south)
     %([xshift=-5em]cv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif4.south)
-    ([xshift=5em]verif1.south) edge node[align=center] {$K$} ([xshift=5em]bmc.north)
-    ([xshift=5em]verif2.south) edge node[align=center] {$K$} ([xshift=5em]fp.north)
-    ([xshift=5em]verif3.south) edge node[align=center] {$K$} ([xshift=5em]sv.north)
+    ([xshift=5em]verif1.south) edge node[align=center] {} ([xshift=5em]bmc.north)
+    ([xshift=5em]verif2.south) edge node[align=center] {} ([xshift=5em]fp.north)
+    ([xshift=5em]verif3.south) edge node[align=center] {} ([xshift=5em]sv.north)
     %([xshift=5em]verif4.south) edge node[align=center] {$K$} ([xshift=5em]cv.north)
-    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
+    ([xshift=-5em]bmc.north) edge node[align=center]  {} ([xshift=-5em]verif1.south)
     (verif) edge node {PASS} (done)
-    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
-    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$K$} ([xshift=-5em]synth.south)
+    ([xshift=5em]synth.south) edge node[align=center] {} ([xshift=5em]gp.north)
+    ([xshift=-5em]gp.north) edge node[align=center] {} ([xshift=-5em]synth.south)
     (aux3) edge (synth.north);
@@
   \path
-    (pre.east) edge node[align=center] {$P_a$, $N$,\\ $\phi_\mathit{init}^k$} (abstract.west)
-    (abstract.south) edge node{$(\phi(K), k)$} (synth.north)
+    (pre.east) edge node[align=center] {} (abstract.west)
+    (abstract.south) edge node{} (synth.north)
     ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west)
@@
   \path
-    ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {$K$} ([xshift=0.6cm]synth.south) 
-    ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$(\phi(K),k)$} ([xshift=-.6cm]KSAT.north)
-    ([yshift=.5cm]AAV.east) edge node{\sl $\hat{X}^\#$} ([yshift=.5cm]AAC.west)
-    ([yshift=-.5cm]AAC.west) edge node{$(k,x_0)$} ([yshift=-.5cm]AAV.east)
-    (AAC.north) edge node{\sl $\hat{X}^\#$} ([xshift=4.9cm]verify.south)
-    ([xshift=-5cm]verify.south) edge node{$K$} (AAV.north);
+    ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {} ([xshift=0.6cm]synth.south) 
+    ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {} ([xshift=-.6cm]KSAT.north)
+    ([yshift=.5cm]AAV.east) edge node{} ([yshift=.5cm]AAC.west)
+    ([yshift=-.5cm]AAC.west) edge node{} ([yshift=-.5cm]AAV.east)
+    (AAC.north) edge node{} ([xshift=4.9cm]verify.south)
+    ([xshift=-5cm]verify.south) edge node{} (AAV.north);
   \path[-] 
-     (verify.north) edge node {$(k,x_0)$} (aux);
+     (verify.north) edge node {C-ex} (aux);
 \end{tikzpicture}
@@
 a completeness threshold, since the time horizon considered in abstract acceleration is infinite.
+An additional preprocessing phase is used to compute 
+a set of initial bounds on $K$ based on input constraints. 
+Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
+%
 Since this model is based on abstraction, we initially perform the synthesis over a basic
 model that abstracts away the complexity of the specification and is only refined to a more
-complex model when a counterexample is found. Thus, we may only look at the gain of the
-model to synthesise a controller and to add further restrictions on specific sections of the reach
-tube when these prove to invalidate the solution. The use of this Counterexample-Guided 
+complex model when a counterexample is found. 
+% Thus, we may only look at the gain of the
+% model to synthesise a controller and to add further restrictions on specific sections of the reach
+% tube when these prove to invalidate the solution.
+The use of this Counterexample-Guided 
 Abstraction-Refinement results in much faster synthesis and verification since it is applied to

### 2017-06-30 ase2017/paper.tex
replaced Figure by Fig. throughout the paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-The first approach, presented in Figure~\ref{fig:CEGIS-precision-increment}, 
+The first approach, presented in Fig.~\ref{fig:CEGIS-precision-increment}, 
 uses a multi-staged verification process. 
@@
 
-Instead of unfolding the dynamics, the second approach (shown in Figure~\ref{fig:CEGARIS}) 
+Instead of unfolding the dynamics, the second approach (shown in Fig.~\ref{fig:CEGARIS}) 
 employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to 
@@
 the user can invoke the \texttt{feedback} and \texttt{series} commands in MATLAB~\cite{matlab-toolbox} 
-to achieve a general equation regarding the transfer function representation as shown in Figure~\ref{combine-controller-plant}.
+to achieve a general equation regarding the transfer function representation as shown in Fig.~\ref{combine-controller-plant}.
 
@@
 \vspace{-0.2cm}
-\caption{General equation for the closed-loop control system using the series configuration (as shown in Figure~\ref{fig:typical-control-system}).}
+\caption{General equation for the closed-loop control system using the series configuration (as shown in Fig.~\ref{fig:typical-control-system}).}
 \label{combine-controller-plant}
@@
 otherwise, it is stable. Indeed, the roots computed by the function \texttt{roots} 
-in MATLAB~\cite{matlab-toolbox} result in the following poles as shown in Figure~\ref{roots-of-dz}, 
+in MATLAB~\cite{matlab-toolbox} result in the following poles as shown in Fig.~\ref{roots-of-dz}, 
 which means that DSSynth has synthesized a stable digital controller.

### 2017-06-30 ase2017/paper.tex
reviewed CEGIS with multi-staged verification
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-The design of our synthesizer consists of two phases, an inductive
+The design of our synthesizer consists of two main phases, an inductive
 synthesis phase, {\sc synthesise}, and a validation phase, {\sc verify},
@@
 	label={\sc ~~~~~~~~~~~~Verify},] (verif) {};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc 2.Safety}};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=0cm]verif.center) {{\sc 3.Precision}};
-     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=2cm]verif.center) {{\sc 4.Complete}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc 1.Safety}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=0cm]verif.center) {{\sc 2.Precision}};
+     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=2cm]verif.center) {{\sc 3.Complete}};
      %\node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc 5.Sampling}};
@@
 employs a multi-staged verification process as follows:
-(i) The first verification stage checks that the candidate
+(i) The first verification stage ({\sc safety}) checks that the candidate
 solution, which we synthesized to be safe for at least one initial
@@
 an unsafe state within $k$ steps.
-(ii) The second verification stage 
+(ii) The second verification stage ({\sc precision})
  restores soundness with respect to the plant precision
@@
 operations performed by the previous stage. 
-(iii) The third verification stage checks that the current
+(iii) The third verification stage ({\sc complete}) checks that the current
 $k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the

### 2017-06-30 ase2017/paper.tex
improved illustrative example
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 >> y = 
->>  -0.9983 z^2 + 0.09587 z + 0.1926
+>>  -0.9983z^2 + 0.09587z + 0.1926
 >>  --------------------------------
->>       z^2 + 0.5665 z + 0.75
+>>       z^2 + 0.5665z + 0.75
 \end{lstlisting}
@@
 >> plant = tf(num,den,0.002);
->> sys = series(controller,plant)
+>> sys = feedback(series(controller, plant),1)
 >> sys =
->> 
->>      0.06863 z^4 - 0.006591 z^3 - 0.01324 z^2
->>  ------------------------------------------------
->>  z^4 - 1.129 z^3 + 0.4981 z^2 - 0.8704 z + 0.5317
+>>        0.06863z^4 - 0.006591z^3 - 0.01324z^2
+>> ---------------------------------------------------
+>> 1.069z^4 - 1.136z^3 + 0.4849z^2 - 0.8704z + 0.5317
 \end{lstlisting}
 \vspace{-0.2cm}
-\caption{General equation for the closed-loop control system using the series configuration (as shown in Fig.~\ref{fig:typical-control-system}).}
+\caption{General equation for the closed-loop control system.}
 \label{combine-controller-plant}
@@
 
-The general equation that represents the closed-loop control system using the series 
-configuration is described by Equation~\ref{equation_general} as follows
+The general equation that represents the closed-loop control system 
+is described by Equation~\ref{equation_general} as follows
 %
@@
 \label{equation_general}
-\frac{N(z)}{D(z)}=\frac{0.06863z^{4} - 0.006591z^{3} - 0.01324z^{2}}{z^{4} - 1.129z^{3} + 0.4981z^{2} -0.8704z + 0.5317}.
+\frac{N(z)}{D(z)}=\frac{0.06863z^{4} - 0.006591z^{3} - 0.01324z^{2}}{1.069z^{4} - 1.136z^{3} + 0.4849z^{2} -0.8704z + 0.5317}.
 \end{equation}
@@
 \begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
->> den = [1 -1.129 0.4981 -0.8704 0.5317]
+>> den = [1.069 -1.136 0.4849 -0.8704 0.5317]
 >> r = roots(den)
 >> r =
->>  -0.2833 + 0.8185i
->>  -0.2833 - 0.8185i
->>   0.9480 + 0.0000i
->>   0.7476 + 0.0000i
+>>  -0.2912 + 0.8061i
+>>  -0.2912 - 0.8061i
+>>   0.8225 + 0.0219i
+>>   0.8225 - 0.0219i
 \end{lstlisting}

### 2017-06-30 ase2017/paper.tex
improved illustrative example
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 which represents a real unmanned aerial vehicle (UAV) quadcopter system~\cite{bouabdallah}. 
-This physical plant is expressed by a transfer function, where 
+This physical plant is expressed by a transfer function $G(z)$, where 
 $B(z)$ and $A(z)$ represent the numerator and denominator, respectively, as
@@
 A digital system is stable \textit{iff} all of its poles are inside the $z$-plane unity circle, 
-namely poles must have the modulus less than one. In order to compute the poles for the digital 
+namely poles must have the modulus less than one~\cite{astrom1997computer}. In order to compute the poles for the digital 
 system represented by Equations~\eqref{equation_plant} and \eqref{equation_controller}, 
 the user can invoke the \texttt{feedback} and \texttt{series} commands in MATLAB~\cite{matlab-toolbox} 
-to achieve a general equation regarding the transfer function representation as shown in Fig.~\ref{combine-controller-plant}.
+to achieve a general equation regarding the transfer function representation, as illustrated in Fig.~\ref{combine-controller-plant}.
 
@@
 \vspace{-0.2cm}
-\caption{General equation for the closed-loop control system.}
+\caption{General equation for the closed-loop control system using the series configuration as shown in Fig.~\ref{fig:typical-control-system}.}
 \label{combine-controller-plant}
@@
 
-The general equation that represents the closed-loop control system 
+The general equation that represents the closed-loop control system, using the series configuration as shown in Fig.~\ref{fig:typical-control-system},
 is described by Equation~\ref{equation_general} as follows
@@
 
-For the stability check, if any root of the polynomial $D(z)$ in Equation~\ref{equation_general} 
+For the stability check, if any root of the denominator polynomial $D(z)$ in Equation~\ref{equation_general} 
 has modulus equal or greater than one, then the system is unstable; 

### 2017-06-30 ase2017/paper.tex
Editing Sec III

@@
 In step $2$, the physical plant (represented by Equations (\ref{eq:transferfunction}) 
-and (\ref{eq:ss-example})) must be designed, using a method selected 
+or (\ref{eq:ss-example})) must be designed, using a method selected 
 from the control literature~\cite{astrom1997computer}. Finally, in step $3$, 
@@
 or if there is no solution (digital controller) for the respective physical plant (given the digital controller
- implementation aspects), then the synthesis is considered to be \emph{failed}.
+ implementation aspects), then the synthesis is considered to have \emph{failed}.
 
 Our CEGIS engine is implemented as an integrated module within the C bounded model checker (CBMC)~\cite{cbmc}.  CBMC
-transforms an ANSI-C representation of our closed-loop control system model into its internal format called
+transforms the ANSI-C representation of our closed-loop control system model into its internal format called
 \emph{GOTO}.  We instrument this internal \emph{GOTO} program for each synthesis or verification scenario accordingly,

### 2017-06-30 ase2017/paper.tex
Editing Sec III

@@
 A graphical user interface application was developed (as shown in Fig.~\ref{fig:gui-for-tf}) 
-to favor digital controller synthesis in MATLAB, besides improving usability and, 
-consequently, attracting more digital dynamical system engineers. Users can provide all 
+to favor digital controller synthesis in MATLAB. Its aim is to improve usability and, 
+consequently, to attract more digital dynamical system engineers. Users can provide all 
 required parameters for digital controller synthesis: physical plant specification, 

### 2017-06-30 ase2017/paper.tex
provided link to the documentation and videos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \section{Counterexample-Guided Inductive Synthesis for Control Systems}
+\label{sec:CEGIS}
 %---------------------------------------------------
@@
 to run all benchmarks and reproduce our
-experiments\.footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}  The current development branch
-of our tool is available in a public GitHub
+experiments.\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}  The current development branch
+of our toolbox is available in a public GitHub
 repository.\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}
@@
 module, $585$ and $800$ lines of C code in the naive and abstract accelerator
-model, respectively.  $4000$ lines of C code for utility functions such as
+back-ends, respectively (cf.~Section~\ref{sec:CEGIS}).  $4000$ lines of C code for utility functions such as
 interval and fixed-point arithmetic, as well as $1000$ lines of C++ code in the
 control synthesis module in CEGIS CBMC.  We evaluate \tool using about $20$ 
-control system benchmarks.
+control system benchmarks. Additionally, the documentation and videos about \tool are available 
+at \url{http://dsverifier.org/dsverifier/dssynth-toolbox/}.
 

### 2017-06-30 ase2017/paper.tex
added authors to the tool paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 % via MATLAB Toolbox}
+
+\author{\IEEEauthorblockN{Alessandro Abate$^{1}$, Iury Bessa$^{2}$, Dario Cattaruzza$^{1}$, Lennon Chaves$^{2}$, Lucas Cordeiro$^{1,2}$, \\ 
+Cristina David$^{1}$, Pascal Kesseli$^{1}$, Daniel Kroening$^{1}$ and Elizabeth Polgreen$^{1}$}
+\IEEEauthorblockA{$^{1}$University of Oxford, Oxford, United Kingdom \\
+$^{2}$Federal University of Amazonas, Manaus, Brazil}}
+
+%\author{\IEEEauthorblockN{Erickson H. da S. Alves, Lucas C. Cordeiro, Eddie B. de Lima Filho}
+%		\IEEEauthorblockA{Federal University of Amazonas, Brazil\\
+%			E-mails: erickson.alves@indt.org.br, lucascordeiro@ufam.edu.br, eddie@ctpim.org.br}}
 

### 2017-06-30 ase2017/paper.tex
small addition

@@
 Otherwise, additional information is provided to the inductive
-synthesis phase in the form of a new counterexample that is added to
+synthesis phase in the form of a new counterexample, C-ex, that is added to
 the set of test inputs, and the loop iterates again.

### 2017-07-01 ase2017/paper.tex
updated section

@@
 
+For our experiments, we could observe that the \tool finds at least one controller sinthesized for our set of benchmarks in transfer-function and state-space representation.
+
+We employed diverse set of real-world benchmarks.
+However, this set of benchmarks is limited within the scope of this paper, and the performance may not generalize to other bencharks.
+The media runtime for our benchmarks was 124s, and the average synthesis time amounts 35.5s for state-space benchamarks, while for transfer-function benchmark the average was 123.6s.
+
+In particular, we can reproduce the stability property in the synthesized controller for a DC motor plant described in Eq.~\eqref{tf-synth-controller} simulating the step response in MATLAB.
+As can be seen, the Fig.~\ref{tf-step-response} shows that the controller synthesized using the \tool is stable, giving the reliability about the results of our tool.
+
+\begin{equation}
+\label{tf-synth-controller}
+C(z)=\frac{-0.3466796875z+0.015625}{-0.5z^{2}+0.19921875z}.
+\end{equation}
+
+\begin{figure}[ht]
+  \includegraphics[width=0.5\textwidth]{tf-step-response.eps}
+  \caption{Step response for the Eq.~\eqref{tf-synth-controller} describing a stable system for the DC motor plant.}
+  \label{tf-step-response}
+\end{figure}
+
+Regarding the state-space representation, we can check in the plant expressed by Eq.~\eqref{ss-synth-controller} (that describes a system for pendulum) that the feedback matrix (represented by the Eq.~\eqref{ss-synth-feedback}) generated by \tool, when combined with the plant with the state equations described in Eq.~\eqref{ss-synth-controller} is also stable, as can been seen in Fig.~\ref{ss-step-response}.
+
+\begin{equation}
+\label{ss-synth-controller}
+\begin{split}
+x(n+1) &= A x(n) + B u(n)
+\\
+y(n) &= C x(n) + D u(n), 
+\end{split}\
+\end{equation}
+
+Where,
+%
+$$A = \left[\begin{array}{cc}-1.999909737361046&-1.000000000000000\\1&0\end{array}\right],$$
+$$B = \left [\begin{array}{c}4\\0\end{array}\right],$$
+$$C = \left [\begin{array}{cc}-1.756887232846049&-1.7494556607764090\end{array}\right],$$
+$$\quad D = \left [\begin{array}{c}9.8\end{array}\right].$$
+
+\begin{equation}
+\label{ss-synth-feedback}
+\begin{split}
+K &= \left [\begin{array}{cc}-0.5898&-0.1914\end{array}\right]
+\end{split}\
+\end{equation}
+
+\begin{figure}[ht]
+  \includegraphics[width=0.5\textwidth]{ss-step-response.eps}
+  \caption{Step response for the Eq.~\eqref{ss-synth-controller} describing a stable system for the pendulum plant.}
+  \label{ss-step-response}
+\end{figure}
+
+The synthesized controllers are validated to be stable using the MATLAB approach, which means that our results are reliable for control engineers.
+A link to the full experimental environment, including the scripts to reproduce the results, all benchmarks and the tool, is provided in the footnoote on our website\footnote{\url{www.dsverifier.org}}.
+
 %--------------------------------------

### 2017-07-01 ase2017/plot_ss.m

@@ -1,0 +1,19 @@
+A = [-1.999909737361046 -1.000000000000000;1 0];
+B = [4;0], 
+C = [-1.756887232846049 -1.749455660776409];
+D = 9.800000000000000
+K = [-0.5898 -0.1914];
+
+A_ = A-B*K;
+B_ = B;
+C_= C-D*K;
+D_= D;
+
+sys = ss(A,B,C,D, 0.002);
+
+roots = eig(F);
+
+dstep(A_,B_,C_,D_)
+
+set(findall(gcf,'-property','FontSize'),'FontSize',22)
+

### 2017-07-01 ase2017/plot_step_response.m

@@ -9,4 +9,4 @@ num_cl = cell2mat(syscl.Numerator);
 den_cl = cell2mat(syscl.Denominator);
 
 dstep(num_cl,den_cl)
-set(findall(gcf,'-property','FontSize'),'FontSize',30)
+set(findall(gcf,'-property','FontSize'),'FontSize',22)

### 2017-07-01 ase2017/plot_tf.m

@@ -1,0 +1,10 @@
+plant = tf([0.1898 1.8027*10^-4],[1 -0.9012, -1.0006*10^-16],2);
+controller = tf([-0.3466796875 0.015625],[0.5 0.19921875 0],2);
+
+syscl= feedback(series(plant,controller),1);
+
+num_cl = cell2mat(syscl.Numerator);
+den_cl = cell2mat(syscl.Denominator);
+
+dstep(num_cl,den_cl)
+set(findall(gcf,'-property','FontSize'),'FontSize',22)

### 2017-07-01 ase2017/paper.tex
reviewed results
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2017-06-30 ase2017/paper.tex
@@
 
+For our experiments, we observed that the \tool finds at least one controller synthesized 
+for our set of benchmarks represented by transfer function or state-space equations.
+
+We employed a diverse set of real-world benchmarks extracted from the literature. 
+However, this set of benchmarks is still limited within the scope of this paper, and 
+the performance may not be generalized to other benchmarks. The media runtime 
+for our benchmarks is $124$\,s, and the average synthesis time amounts $35.5$\,s 
+for state-space benchmarks, while for transfer function benchmarks, the average is $123.6$\,s.
+
+In particular, we can reproduce the stability property in the synthesized controller 
+for a DC motor plant described in Eq.~\eqref{tf-synth-controller}, simulating the step response 
+in MATLAB. As can be seen, Fig.~\ref{tf-step-response} shows that the synthesized controller 
+using the \tool is stable, giving the reliability about the results of our tool.
+
+\begin{equation}
+\label{tf-synth-controller}
+C(z)=\frac{-0.3466796875z+0.015625}{-0.5z^{2}+0.19921875z}.
+\end{equation}
+
+\begin{figure}[ht]
+  \includegraphics[width=0.5\textwidth]{tf-step-response.eps}
+  \caption{Step response for the Eq.~\eqref{tf-synth-controller} describing a stable system for the DC motor plant.}
+  \label{tf-step-response}
+\end{figure}
+
+Regarding the state-space representation, we can check in the plant expressed by 
+Eq.~\eqref{ss-synth-controller} (that describes a system for pendulum) that the feedback matrix 
+(represented by Eq.~\eqref{ss-synth-feedback}) generated by \tool, when combined with the plant 
+with the state equations described in Eq.~\eqref{ss-synth-controller} is also stable, as can been seen in Fig.~\ref{ss-step-response}.
+%
+\begin{equation}
+\label{ss-synth-controller}
+\begin{split}
+x(n+1) &= A x(n) + B u(n)
+\\
+y(n) &= C x(n) + D u(n), 
+\end{split}\
+\end{equation}
+
+Where,
+%
+$$A = \left[\begin{array}{cc}-1.999909737361046&-1.000000000000000\\1&0\end{array}\right],$$
+$$B = \left [\begin{array}{c}4\\0\end{array}\right],$$
+$$C = \left [\begin{array}{cc}-1.756887232846049&-1.7494556607764090\end{array}\right],$$
+$$\quad D = \left [\begin{array}{c}9.8\end{array}\right].$$
+
+\begin{equation}
+\label{ss-synth-feedback}
+\begin{split}
+K &= \left [\begin{array}{cc}-0.5898&-0.1914\end{array}\right]
+\end{split}\
+\end{equation}
+
+\begin{figure}[ht]
+  \includegraphics[width=0.5\textwidth]{ss-step-response.eps}
+  \caption{Step response for the Eq.~\eqref{ss-synth-controller} describing a stable system for the pendulum plant.}
+  \label{ss-step-response}
+\end{figure}
+
+The synthesized controllers are validated to be stable using the MATLAB approach, 
+which means that our results are reliable for control engineers. A link to the full experimental environment, 
+including the scripts to reproduce the results, all benchmarks and the tool, is provided online in our website\footnote{\url{www.dsverifier.org}}.
+
 %--------------------------------------

### 2017-07-01 ase2017/paper.tex
reviewed experimental evaluation
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2017-06-30 ase2017/paper.tex
@@
 digital system design and implementation~\cite{matlab-toolbox}. Indeed, there is a MATLAB 
-Toolbox named as DSVerifier Toolbox~\cite{issta2017}, which automatically detects 
+Toolbox named as DSVerifier Toolbox~\cite{issta2017,DBLP:journals/tc/BessaIPCF17,DBLP:journals/dafes/BessaICF16}, which automatically detects 
 specific errors related to digital system design ({\it e.g.}, stability, limit cycle and overflow) 
@@
 Our experimental evaluation consists of $18$ SISO control system benchmarks 
-extracted from the literature~\cite{abate2017, abatecav2017,bouabdallah, acrobot,cstr,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS},
+extracted from the literature~\cite{abate2017,abatecav2017,bouabdallah, acrobot,cstr,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS,DBLP:journals/tc/BessaIPCF17,DBLP:journals/dafes/BessaICF16},
 which include physical plants for unmanned aerial vehicle (UAV), cruise control system, 
@@
 
+For our experiments, we observed that the \tool correctly synthesizes stable digital controllers 
+for our set of benchmarks represented by transfer function or state-space equations. 
+We employed a diverse set of real-world benchmarks extracted from the control literature. 
+However, note that this set of benchmarks is still limited within the scope of this paper, and 
+the performance may not be generalized to other benchmarks. 
+The media runtime for our benchmarks set is $124$\,s, and the average synthesis time amounts 
+to $35.5$\,s for closed-loop control systems represented by state-space equations, while 
+for transfer functions, the average synthesis time amounts to $123.6$\,s.
+
+Additionally, we are able to reproduce the stability for all evaluated control system benchmarks.
+As an example, we have reproduced the stability property in the synthesized controller 
+for a DC motor plant described in Eq.~\eqref{tf-synth-controller}, simulating the step response 
+in MATLAB. Fig.~\ref{tf-step-response} shows that the digital controller 
+synthesized by the \tool stabilizes the closed-loop control system using 
+the series connection (as shown in Fig.~\ref{fig:typical-control-system}) for the DC motor plant. 
+We have applied this procedure to all synthesized controllers to confirm the reliability of our experimental results.
+%
+\begin{equation}
+\label{tf-synth-controller}
+C(z)=\frac{-0.3466796875z+0.015625}{-0.5z^{2}+0.19921875z}.
+\end{equation}
+
+\begin{figure}[ht]
+  \includegraphics[width=0.5\textwidth]{tf-step-response.eps}
+  \caption{Step response for the Eq.~\eqref{tf-synth-controller} describing a stable system for the DC motor plant.}
+  \label{tf-step-response}
+\end{figure}
+
+Regarding the state-space representation, we can check the physical plant expressed by 
+Eq.~\eqref{ss-synth-controller} (describing a pendulum control system), that the feedback matrix 
+(represented by Eq.~\eqref{ss-synth-feedback}) generated by \tool, when combined with the physical plant 
+with the state equations described in Eq.~\eqref{ss-synth-controller} is also stable, as can been seen in Fig.~\ref{ss-step-response}.
+%
+\begin{equation}
+\label{ss-synth-controller}
+\begin{split}
+x(n+1) &= A x(n) + B u(n)
+\\
+y(n) &= C x(n) + D u(n), 
+\end{split}\
+\end{equation}
+
+Where,
+%
+$$A = \left[\begin{array}{cc}-1.999909737361046&-1.000000000000000\\1&0\end{array}\right],$$
+$$B = \left [\begin{array}{c}4\\0\end{array}\right],$$
+$$C = \left [\begin{array}{cc}-1.756887232846049&-1.7494556607764090\end{array}\right],$$
+$$\quad D = \left [\begin{array}{c}9.8\end{array}\right].$$
+
+\begin{equation}
+\label{ss-synth-feedback}
+\begin{split}
+K &= \left [\begin{array}{cc}-0.5898&-0.1914\end{array}\right]
+\end{split}\
+\end{equation}
+
+\begin{figure}[ht]
+  \includegraphics[width=0.5\textwidth]{ss-step-response.eps}
+  \caption{Step response for the Eq.~\eqref{ss-synth-controller} describing a stable system for the pendulum plant.}
+  \label{ss-step-response}
+\end{figure}
+
+The synthesized controllers are validated to be stable using the MATLAB step reponse, 
+which means that our results are reliable for control engineers. A link to the full experimental environment, 
+including the scripts to reproduce the results, all benchmarks and the tool, is provided online in our website.\footnote{\url{www.dsverifier.org}}
+
 %--------------------------------------

### 2017-07-01 ase2017/paper.tex
reviewed experimental evaluation
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-Regarding the state-space representation, we can check the physical plant expressed by 
-Eq.~\eqref{ss-synth-controller} (describing a pendulum control system), that the feedback matrix 
-(represented by Eq.~\eqref{ss-synth-feedback}) generated by \tool, when combined with the physical plant 
-with the state equations described in Eq.~\eqref{ss-synth-controller} is also stable, as can been seen in Fig.~\ref{ss-step-response}.
+Regarding the state-space representation, we have reproduced the stability property for 
+the closed-loop control system of a pendulum represented by Eq.~\eqref{ss-synth-controller}. 
 %
@@
 
+For this particular closed-loop control system, the feedback matrix (see Eq.~\eqref{ss-synth-feedback}) generated 
+by the \tool is also stable, as shown in Fig.~\ref{ss-step-response}.
+%
 \begin{equation}
@@
 
-The synthesized controllers are validated to be stable using the MATLAB step reponse, 
-which means that our results are reliable for control engineers. A link to the full experimental environment, 
-including the scripts to reproduce the results, all benchmarks and the tool, is provided online in our website.\footnote{\url{www.dsverifier.org}}
+The digital controllers synthesized by \tool are all stable using the MATLAB step response
+as a validation procedure, which means that our results are reliable for control engineers. 
+A link to the full experimental environment, including the scripts to reproduce the results, 
+all benchmarks, videos, documentation and the tool, is provided online.\footnote{\url{www.dsverifier.org}}
 

### 2017-07-01 ase2017/paper.tex
reviewed conclusions
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\tool can synthesize digital controllers for dynamic physical plants, 
-represented in MATLAB as a transfer function or a state-space model,  
-w.r.t. stability and safety, using the CEGIS approach. 
+\tool can automatically synthesize stable digital controllers for intricate dynamic physical plants, 
+represented in MATLAB as a transfer function or a state-space equation using the CEGIS approach. 
+In particular, the \tool represents the first fully automated synthesis
+tool that is algorithmically and numerically sound, considering various error
+sources in the implementation of the digital control algorithm and in the computational 
+modeling of plant dynamics~\cite{abate2017,abatecav2017}.
 %
-Given the current literature in controller synthesis, there is no other MATLAB toolbox 
-for synthesizing stable digital controllers for physical plants, while taking into account all aspects of its digital implementation (fixed-point arithmetic). 
+Additionally, given the current literature in controller synthesis, there is no other MATLAB toolbox 
+for synthesizing stable digital controllers for physical plants, while taking into account all aspects of its 
+digital implementation. 
 %
-As future work, \tool will perform synthesis of other types of specifications (e.g., performance) 
+As future work, the \tool will perform synthesis of other specifications (e.g., performance) 
 and be combined with DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to verify/validate 

### 2017-07-01 ase2017/paper.tex
reviewed abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 systems with single input and output. In particular, DSSynth synthesizes digital 
-controllers that are sound w.r.t. stability and safety specifications by taking into account finite word-length 
+controllers that are sound w.r.t. the stability specification by taking into account finite word-length 
 effects in their representation. DSSynth considers the complete range
@@
 interval and fixed-point arithmetic, as well as $1000$ lines of C++ code in the
-control synthesis module in CEGIS CBMC.  We evaluate \tool using about $20$ 
+control synthesis module in CEGIS CBMC.  We evaluate \tool using $18$ SISO 
 control system benchmarks. Additionally, the documentation and videos about \tool are available 
@@
 For our experiments, we observed that the \tool correctly synthesizes stable digital controllers 
-for our set of benchmarks represented by transfer function or state-space equations. 
+for our set of benchmarks represented by transfer functions or state-space equations. 
 We employed a diverse set of real-world benchmarks extracted from the control literature. 
@@
 For this particular closed-loop control system, the feedback matrix (see Eq.~\eqref{ss-synth-feedback}) generated 
-by the \tool is also stable, as shown in Fig.~\ref{ss-step-response}.
+by the \tool also leads to a stable system, as shown in Fig.~\ref{ss-step-response}.
 %
@@
 
-\tool can automatically synthesize stable digital controllers for intricate dynamic physical plants, 
+The \tool can automatically synthesize stable digital controllers for intricate dynamic physical plants, 
 represented in MATLAB as a transfer function or a state-space equation using the CEGIS approach. 

### 2017-07-01 ase2017/paper.tex
specified the DSSynth back-end used for the experiments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
typo + question

@@
 
+\renewcommand{\baselinestretch}{0.991}
 \newcommand\tool{{DSSynth Toolbox}\xspace}
@@
 $8$-bits for the integer part (including the sign bit) and $8$-bits for the fractional 
-part. All experiments with \tool v$1$.$0$.$0$  were conducted on an otherwise idle 
+part. We have run the \tool using the CEGIS with multi-staged verification (cf.~Section~\ref{sec:CEGIS}).
+All experiments with \tool v$1$.$0$.$0$  were conducted on an otherwise idle 
 Intel Core i$7-2600$ $3.40$ GHz processor, with $24$ GB of RAM, running Ubuntu $64$-bits.
@@
 
+\textcolor{red}{Why are the experiments only mentioning stable controllers? Up until this point, we discuss stable and safe controllers.}
+
 For our experiments, we observed that the \tool correctly synthesizes stable digital controllers 
@@
 the performance may not be generalized to other benchmarks. 
-The media runtime for our benchmarks set is $124$\,s, and the average synthesis time amounts 
+The median runtime for our benchmarks set is $124$\,s, and the average synthesis time amounts 
 to $35.5$\,s for closed-loop control systems represented by state-space equations, while 

### 2017-07-02 ase2017/paper.tex
minor change

@@
 represented by transfer functions or state-space LTI models. LTI models 
-are used in several engineering applications to support non-trivial tasks when 
+are used to represent dynamics in several engineering applications to support non-trivial tasks when 
 applied to embedded \& cyber-physical systems (e.g., robot manipulator, smart grid, 

### 2017-07-02 ase2017/paper.tex
discussed about safe digital controllers
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\renewcommand{\baselinestretch}{0.991}
+\renewcommand{\baselinestretch}{0.99}
 \newcommand\tool{{DSSynth Toolbox}\xspace}
@@
 systems with single input and output. In particular, DSSynth synthesizes digital 
-controllers that are sound w.r.t. the stability specification by taking into account finite word-length 
+controllers that are sound w.r.t. the stability and safety specifications by taking into account finite word-length 
 effects in their representation. DSSynth considers the complete range
@@
 performance of closed-loop dynamics, where outputs of discrete plant $G(z)$ 
-are fed back and compared to a reference signal to which a (designed) 
+are fed back and compared to a reference signal to which a 
 controller $C(z)$ should steer~\cite{astrom1997computer}. 
@@
 which is based on the Counter-Example Guided Inductive Synthesis 
-(CEGIS) approach~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. Here, CEGIS is used
+(CEGIS) approach~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. CEGIS is used
 as a program synthesis engine that is able to generate sound digital controllers for highly non-trivial 
@@
 satisfy the specification. Modern synthesis engines such as the one used here combine automated testing, genetic algorithms 
-and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
+and SMT-based reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
 Using the CEGIS-based approach, DSSynth synthesizes stable digital controllers
@@
 for all reachable states.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 check that $k{\geq}\overline{k}$.
-
+%
 \begin{figure}
@@
 %
-After executing the \texttt{synthesize} command in MATLAB, 
-\tool provides the synthesized digital controller, according to the digital system representation.
+After executing the \texttt{synthesize} command, 
+\tool provides the synthesized digital controller, according to the implementation aspects.
 
@@
 
-Our experimental evaluation consists of $18$ SISO control system benchmarks 
+Our evaluation consists of $18$ SISO control system benchmarks 
 extracted from the literature~\cite{abate2017,abatecav2017,bouabdallah, acrobot,cstr,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS,DBLP:journals/tc/BessaIPCF17,DBLP:journals/dafes/BessaICF16},
@@
 The main objectives of our experimental evaluation is to (1) evaluate the \tool performance 
-to produce stable controllers, and also (2) confirm the stability of the synthesized digital 
-controllers outside of our model, using both the transfer function and state-space representations.
+to produce stable and safe controllers, and also (2) confirm the stability and safety of the synthesized digital 
+controllers outside of our model using MATLAB. %, using both the transfer function and state-space representations.
 
@@
 
-\textcolor{red}{Why are the experiments only mentioning stable controllers? Up until this point, we discuss stable and safe controllers.}
+%\textcolor{red}{Why are the experiments only mentioning stable controllers? Up until this point, we discuss stable and safe controllers.}
 
-For our experiments, we observed that the \tool correctly synthesizes stable digital controllers 
+For our experiments, we observed that the \tool correctly synthesizes stable and safe digital controllers 
 for our set of benchmarks represented by transfer functions or state-space equations. 
@@
 
-Additionally, we are able to reproduce the stability for all evaluated control system benchmarks.
+Additionally, we are able to reproduce the stability and safety for all evaluated control system benchmarks.
 As an example, we have reproduced the stability property in the synthesized controller 
@@
 
-The digital controllers synthesized by \tool are all stable using the MATLAB step response
-as a validation procedure, which means that our results are reliable for control engineers. 
-A link to the full experimental environment, including the scripts to reproduce the results, 
-all benchmarks, videos, documentation and the tool, is provided online.\footnote{\url{www.dsverifier.org}}
+%The digital controllers synthesized by \tool are all stable using the MATLAB step response
+%as a validation procedure, which means that our results are reliable for control engineers. 
+The synthesized controllers are also confirmed to be safe outside of our model
+representation using MATLAB, which means that our results are reliable for control engineers. 
+In particular, we unfold the system dynamics up to a given depth, 
+compute the system's input and output via the feedback matrix, and then check the states' bounds.
+ A link to the full experimental environment, including the scripts, benchmarks, 
+ videos, documentation and the tool, is provided online.\footnote{\url{www.dsverifier.org}}
 

### 2017-07-02 ase2017/paper.tex
replaced Equation by Eq.
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 The general equation that represents the closed-loop control system, using the series configuration as shown in Fig.~\ref{fig:typical-control-system},
-is described by Equation~\ref{equation_general} as follows
+is described by Eq.~\ref{equation_general} as follows
 %
@@
 
-For the stability check, if any root of the denominator polynomial $D(z)$ in Equation~\ref{equation_general} 
+For the stability check, if any root of the denominator polynomial $D(z)$ in Eq.~\ref{equation_general} 
 has modulus equal or greater than one, then the system is unstable; 
@@
 \vspace{-0.2cm}
-\caption{Roots of the polynomial $D(z)$ given by Equation~\ref{equation_general}.}
+\caption{Roots of the polynomial $D(z)$ given by Eq.~\ref{equation_general}.}
 \label{roots-of-dz}
@@
 In particular, we unfold the system dynamics up to a given depth, 
-compute the system's input and output via the feedback matrix, and then check the states' bounds.
+compute the system input and output via the feedback matrix, and then check the states bounds.
  A link to the full experimental environment, including the scripts, benchmarks, 

### 2017-07-02 ase2017/paper.tex
adding safe in addition to stable for the conclusions

@@
 
-The \tool can automatically synthesize stable digital controllers for intricate dynamic physical plants, 
+The \tool can automatically synthesize stable and safe digital controllers for intricate dynamic physical plants, 
 represented in MATLAB as a transfer function or a state-space equation using the CEGIS approach. 

### 2017-07-02 ase2017/paper.tex
back in 6 pages

--- 2017-07-02 ase2017/paper.tex
@@
 
-The \tool can automatically synthesize stable digital controllers for intricate dynamic physical plants, 
-represented in MATLAB as a transfer function or a state-space equation using the CEGIS approach. 
+The \tool can automatically synthesize stable and safe digital controllers for intricate dynamic physical plants, 
+represented in MATLAB as a transfer function or a state-space equation using CEGIS. 
 In particular, the \tool represents the first fully automated synthesis

### 2017-07-02 ase2017/paper.tex
reviewed conclusions
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Additionally, given the current literature in controller synthesis, there is no other MATLAB toolbox 
-for synthesizing stable digital controllers for physical plants, while taking into account all aspects of its 
+for synthesizing stable and safe digital controllers for physical plants, while taking into account all aspects of its 
 digital implementation. 
@@
 and be combined with DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to verify/validate 
-other controller properties (e.g., presence of limit cycles).
+other controller properties.
 

### 2017-07-02 ase2017/paper.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
microtype
line breaks

@@
 
+\usepackage{microtype}
 \usepackage{xspace,framed}
@@
 \begin{abstract}
-We present an automated MATLAB Toolbox, named as DSSynth 
-(Digital-System Synthesizer), to synthesize sound digital controllers 
-for physical plants that are represented as linear time-invariant
-systems with single input and output. In particular, DSSynth synthesizes digital 
-controllers that are sound w.r.t. the stability and safety specifications by taking into account finite word-length 
-effects in their representation. DSSynth considers the complete range
-of approximations, including time discretization, quantization effects, 
-and finite-precision arithmetic (and its rounding errors). 
-Currently, there are two DSSynth versions for synthesizing digital controllers for physical plants 
-represented by transfer function or state-space equations: a command-line and 
-a MATLAB application. The resulting toolbox 
-enables application of program synthesis to real-world control engineering systems.
+%
+We present an automated MATLAB Toolbox, named as DSSynth (Digital-System
+Synthesizer), to synthesize sound digital controllers for physical plants
+that are represented as linear time-invariant systems with single input and
+output.  In particular, DSSynth synthesizes digital controllers that are
+sound w.r.t.  the stability and safety specifications by taking into account
+finite word-length effects in their representation.  DSSynth considers the
+complete range of approximations, including time discretization,
+quantization effects, and finite-precision arithmetic (and its rounding
+errors).  Currently, there are two DSSynth versions for synthesizing digital
+controllers for physical plants represented by transfer function or
+state-space equations: a command-line and a MATLAB application.  The
+resulting toolbox enables application of program synthesis to real-world
+control engineering systems.
+%
 \end{abstract}
@@
 
-Control theory targets the construction of reliable systems by providing mathematical guarantees about the stability and the desired 
-performance of closed-loop dynamics, where outputs of discrete plant $G(z)$ 
-are fed back and compared to a reference signal to which a 
-controller $C(z)$ should steer~\cite{astrom1997computer}. 
-Fig.~\ref{fig:typical-control-system} shows a typical closed-loop digital control system.
+Control theory targets the construction of reliable systems by providing
+mathematical guarantees about the stability and the desired performance of
+closed-loop dynamics, where outputs of discrete plant $G(z)$ are fed back
+and compared to a reference signal to which a controller $C(z)$ should
+steer~\cite{astrom1997computer}.  Fig.~\ref{fig:typical-control-system}
+shows a typical closed-loop digital control system.
 %
@@
 
-There are various mathematical representations for control 
-systems,  e.g.,  transfer functions and state-space equations (difference or differential equations). 
-Here, 
-systems with a single input and a single output (SISO) are considered and 
-represented by transfer functions or state-space LTI models. LTI models 
-are used to represent dynamics in several engineering applications to support non-trivial tasks when 
-applied to embedded \& cyber-physical systems (e.g., robot manipulator, smart grid, 
-power plants, distributed robotics, and automatic pilot avionics). 
-The following expression presents the general form 
-of a discrete plant or a digital controller based on the transfer function representation:
+There are various mathematical representations for control systems, e.g.,
+transfer functions and state-space equations (difference or differential
+equations).  Here, systems with a single input and a single output (SISO)
+are considered and represented by transfer functions or state-space LTI
+models.  LTI models are used to represent dynamics in several engineering
+applications to support non-trivial tasks when applied to embedded \&
+cyber-physical systems (e.g., robot manipulator, smart grid, power plants,
+distributed robotics, and automatic pilot avionics).  The following
+expression presents the general form of a discrete plant or a digital
+controller based on the transfer function representation:
 %
@@
 %
-Controllers synthesis for LTI systems is richly studied 
-in the literature~\cite{mazo2010pessoa,DBLP:conf/emsoft/RavanbakhshS16,economakos2016automated}; 
-however, there are many challenges when 
-digital control system theory is used, mainly due to the finite-word 
-length (FWL) effects leading to truncation 
-or round-off errors~\cite{Guang2013, Istepanian2001}, time discretization 
-and quantization noise, which are typically introduced by Analogue-to-Digital 
-(ADC) and Digital-to-Analogue (DAC) conversion~\cite{astrom1997computer}.
+Controllers synthesis for LTI systems is richly studied in the
+literature~\cite{mazo2010pessoa,DBLP:conf/emsoft/RavanbakhshS16,economakos2016automated};
+however, there are many challenges when digital control system theory is
+used, mainly due to the finite-word length (FWL) effects leading to
+truncation or round-off errors~\cite{Guang2013, Istepanian2001}, time
+discretization and quantization noise, which are typically introduced by
+Analogue-to-Digital (ADC) and Digital-to-Analogue (DAC)
+conversion~\cite{astrom1997computer}.
 
-Recently, a new methodology to synthesize digital control systems has been proposed, 
-named DSSynth (Digital-System Synthesizer)~\cite{abate2017, abatecav2017}, 
-which is based on the Counter-Example Guided Inductive Synthesis 
-(CEGIS) approach~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. CEGIS is used
-as a program synthesis engine that is able to generate sound digital controllers for highly non-trivial 
-control system specifications with a very high degree of automation. The program synthesis engine 
-uses a specification as starting point, and subsequently produces a sequence of candidate 
-programs from a given template. The candidate programs are iteratively refined to eventually 
-satisfy the specification. Modern synthesis engines such as the one used here combine automated testing, genetic algorithms 
-and SMT-based reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
-Using the CEGIS-based approach, DSSynth synthesizes stable digital controllers
-for a given physical plant represented by either transfer functions or state-space equations~\cite{abate2017,abatecav2017}.
+Recently, a new methodology to synthesize digital control systems has been
+proposed, named DSSynth (Digital-System Synthesizer)~\cite{abate2017,
+abatecav2017}, which is based on the Counter-Example Guided Inductive
+Synthesis (CEGIS) approach~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. 
+CEGIS is used as a program synthesis engine that is able to generate sound
+digital controllers for highly non-trivial control system specifications
+with a very high degree of automation.  The program synthesis engine uses a
+specification as starting point, and subsequently produces a sequence of
+candidate programs from a given template.  The candidate programs are
+iteratively refined to eventually satisfy the specification.  Modern
+synthesis engines such as the one used here combine automated testing,
+genetic algorithms and SMT-based
+reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
+Using the CEGIS-based approach, DSSynth synthesizes stable digital
+controllers for a given physical plant represented by either transfer
+functions or state-space equations~\cite{abate2017,abatecav2017}.
 
-Notably, there are toolboxes in MATLAB with functions and scripts to facilitate the 
-digital system design and implementation~\cite{matlab-toolbox}. Indeed, there is a MATLAB 
-Toolbox named as DSVerifier Toolbox~\cite{issta2017,DBLP:journals/tc/BessaIPCF17,DBLP:journals/dafes/BessaICF16}, which automatically detects 
-specific errors related to digital system design ({\it e.g.}, stability, limit cycle and overflow) 
-using symbolic model checking techniques based on Boolean Satisfiability (SAT) and 
-Satisfiability Modulo Theories (SMT) solvers. Pessoa~\cite{mazo2010pessoa} is another 
-toolbox, but applied to the synthesis of correct-by-design digital controllers. 
-In particular, Pessoa is based on approximate bisimulation, which allows control engineers to replace differential equations, 
-describing a physical plant, by a respective finite-state machine. However, Pessoa does not take advantage of
-recent advances in bit-accurate verification of programs to synthesize controllers w.r.t. FWL effects. MATLAB already offers a tool 
-named as Control System Tuner~\cite{autotuner} for automatically designing controllers based on optimization solvers or graphical analysis. 
-However, the Control System Tuner is unable to consider FWL effects during the controller synthesis process.
-To the best of our knowledge, there is no MATLAB toolbox able to perform digital controller synthesis based on 
-program synthesis engines that considers the complete range of approximations, including time discretization, 
-quantization effects, and finite-precision arithmetic and its rounding errors.
+Notably, there are toolboxes in MATLAB with functions and scripts to
+facilitate the digital system design and
+implementation~\cite{matlab-toolbox}.  Indeed, there is a MATLAB Toolbox
+named as DSVerifier
+Toolbox~\cite{issta2017,DBLP:journals/tc/BessaIPCF17,DBLP:journals/dafes/BessaICF16},
+which automatically detects specific errors related to digital system design
+({\it e.g.}, stability, limit cycle and overflow) using symbolic model
+checking techniques based on Boolean Satisfiability (SAT) and Satisfiability
+Modulo Theories (SMT) solvers.  Pessoa~\cite{mazo2010pessoa} is another
+toolbox, but applied to the synthesis of correct-by-design digital
+controllers.  In particular, Pessoa is based on approximate bisimulation,
+which allows control engineers to replace differential equations, describing
+a physical plant, by a respective finite-state machine.  However, Pessoa
+does not take advantage of recent advances in bit-accurate verification of
+programs to synthesize controllers w.r.t.  FWL effects.  MATLAB already
+offers a tool named as Control System Tuner~\cite{autotuner} for
+automatically designing controllers based on optimization solvers or
+graphical analysis.  However, the Control System Tuner is unable to consider
+FWL effects during the controller synthesis process.  To the best of our
+knowledge, there is no MATLAB toolbox able to perform digital controller
+synthesis based on program synthesis engines that considers the complete
+range of approximations, including time discretization, quantization
+effects, and finite-precision arithmetic and its rounding errors.
 
-The present tool paper addresses this limitation and describes a toolbox for the DSSynth tool~\cite{abate2017, abatecav2017} 
-in a MATLAB environment, named \tool. The main advantage for the use of a MATLAB toolbox 
-lies on designing physical plants in MATLAB and then promptly synthesizing a stable and safe digital controller,
-considering the complete range of approximations. 
-Notably, when using the \tool, an engineer is able to model a physical plant with MATLAB
-through transfer function or state-space representations, considering low-level systems parameters 
-(implementation features and numerical format).
+The present tool paper addresses this limitation and describes a toolbox for
+the DSSynth tool~\cite{abate2017, abatecav2017} in a MATLAB environment,
+named \tool.  The main advantage for the use of a MATLAB toolbox lies on
+designing physical plants in MATLAB and then promptly synthesizing a stable
+and safe digital controller, considering the complete range of
+approximations.  Notably, when using the \tool, an engineer is able to model
+a physical plant with MATLAB through transfer function or state-space
+representations, considering low-level systems parameters (implementation
+features and numerical format).
 
@@
 which interact via a finite set of test vectors that is updated
-incrementally.  Given a stability and safety specification, the
-inductive synthesis procedure tries to find a candidate solution
-satisfying the specification for the given set of test inputs.
+incrementally.  Given a stability and safety specification, the inductive
+synthesis procedure tries to find a candidate solution satisfying the
+specification for the given set of test inputs.
 %
@@
 
-Instead of unfolding the dynamics, the second approach (shown in Fig.~\ref{fig:CEGARIS}) 
-employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to 
-simultaneously evaluate all possible progressions of the model. This eliminates the need for
-a completeness threshold, since the time horizon considered in abstract acceleration is infinite.
-An additional preprocessing phase is used to compute 
-a set of initial bounds on $K$ based on input constraints. 
-Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
+Instead of unfolding the dynamics, the second approach (shown in
+Fig.~\ref{fig:CEGARIS}) employs {\em abstract
+acceleration}~\cite{cattaruzza2015unbounded} to simultaneously evaluate all
+possible progressions of the model.  This eliminates the need for a
+completeness threshold, since the time horizon considered in abstract
+acceleration is infinite.  An additional preprocessing phase is used to
+compute a set of initial bounds on $K$ based on input constraints.  Note
+that these bounds will be used by the {\sc synthesize} phase to reduce the
+size of the solution space.
 %
-Since this model is based on abstraction, we initially perform the synthesis over a basic
-model that abstracts away the complexity of the specification and is only refined to a more
-complex model when a counterexample is found. 
+Since this model is based on abstraction, we initially perform the synthesis
+over a basic model that abstracts away the complexity of the specification
+and is only refined to a more complex model when a counterexample is found.
+%
 % Thus, we may only look at the gain of the
@@
 % tube when these prove to invalidate the solution.
-The use of this Counterexample-Guided 
-Abstraction-Refinement results in much faster synthesis and verification since it is applied to
-both phases, allowing for faster results whilst maintaining soundness for an infinite time horizon.
+%
+The use of this Counterexample-Guided Abstraction-Refinement results in much
+faster synthesis and verification since it is applied to both phases,
+allowing for faster results whilst maintaining soundness for an infinite
+time horizon.
 
@@
 In step $1$, the user has to define the digital controller representation,
-which can be a transfer function or a state-space model. 
-In step $2$, the physical plant (represented by Equations (\ref{eq:transferfunction}) 
-or (\ref{eq:ss-example})) must be designed, using a method selected 
-from the control literature~\cite{astrom1997computer}. Finally, in step $3$, 
-the numerical representation for the digital controller implementation must be 
-defined by the user, {\it i.e.}, the FWL format that includes the number of bits for the integer 
-and fractional parts as well as the dynamic range inputs. The result of the manual 
-procedure performed by the user is a digital system specification for the given 
-physical plant in MATLAB.
+which can be a transfer function or a state-space model.  In step $2$, the
+physical plant (represented by Equations (\ref{eq:transferfunction}) or
+(\ref{eq:ss-example})) must be designed, using a method selected from the
+control literature~\cite{astrom1997computer}.  Finally, in step $3$, the
+numerical representation for the digital controller implementation must be
+defined by the user, {\it i.e.}, the FWL format that includes the number of
+bits for the integer and fractional parts as well as the dynamic range
+inputs.  The result of the manual procedure performed by the user is a
+digital system specification for the given physical plant in MATLAB.
 
-After that, the synthesis process starts in step $A$, when \tool obtains the digital system 
-specification in MATLAB, and then translates it into an ANSI-C program. 
-In step $B$, our CEGIS engine is invoked to synthesize the digital controller w.r.t. the digital system
-specification. Finally, in step $C$, the synthesized digital controller considering FWL effects is produced. 
-The output generated by \tool is the synthesized digital controller represented either in transfer function 
-or state-space equation. The synthesis is considered to be \emph{successful} if a digital controller is correctly 
-synthesized w.r.t. FWL effects; otherwise, if any parameter is incorrectly defined in previous steps, 
-or if there is no solution (digital controller) for the respective physical plant (given the digital controller
- implementation aspects), then the synthesis is considered to have \emph{failed}.
+After that, the synthesis process starts in step $A$, when \tool obtains the
+digital system specification in MATLAB, and then translates it into an
+ANSI-C program.  In step $B$, our CEGIS engine is invoked to synthesize the
+digital controller w.r.t.  the digital system specification.  Finally, in
+step $C$, the synthesized digital controller considering FWL effects is
+produced.  The output generated by \tool is the synthesized digital
+controller represented either in transfer function or state-space equation. 
+The synthesis is considered to be \emph{successful} if a digital controller
+is correctly synthesized w.r.t.  FWL effects; otherwise, if any parameter is
+incorrectly defined in previous steps, or if there is no solution (digital
+controller) for the respective physical plant (given the digital controller
+implementation aspects), then the synthesis is considered to have
+\emph{failed}.
 
-Our CEGIS engine is implemented as an integrated module within the C bounded model checker (CBMC)~\cite{cbmc}.  CBMC
-transforms the ANSI-C representation of our closed-loop control system model into its internal format called
-\emph{GOTO}.  We instrument this internal \emph{GOTO} program for each synthesis or verification scenario accordingly,
-and use CBMC as an oracle to answer our queries.  CBMC itself relies on an underlying SAT or SMT solver to solve the
-resulting formulae.  We model FWL effects, time discretization and the presence of quantization noise explicitly using CBMC's  
-nondeterminism API (e.g., \texttt{nondet}, \texttt{CPROVER\_assume} intrinsic functions).  Our module was included in CBMC~5.7 and is available for
-public download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}  We further created a VirtualBox OVA image
-with our tool pre-installed, including our MATLAB-generated benchmarks and benchmark shell script with instructions
-to run all benchmarks and reproduce our
-experiments.\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}  The current development branch
-of our toolbox is available in a public GitHub
+Our CEGIS engine is implemented as an integrated module within the C bounded
+model checker (CBMC)~\cite{cbmc}.  CBMC transforms the ANSI-C representation
+of our closed-loop control system model into its internal format called
+\emph{GOTO}.  We instrument this internal \emph{GOTO} program for each
+synthesis or verification scenario accordingly, and use CBMC as an oracle to
+answer our queries.  CBMC itself relies on an underlying SAT or SMT solver
+to solve the resulting formulae.  We model FWL effects, time discretization
+and the presence of quantization noise explicitly using CBMC's
+nondeterminism API (e.g., \texttt{nondet}, \texttt{CPROVER\_assume}
+intrinsic functions).  Our module was included in CBMC~5.7 and is available
+for public
+download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}
+We further created a VirtualBox OVA image with our tool pre-installed,
+including our MATLAB-generated benchmarks and benchmark shell script with
+instructions to run all benchmarks and reproduce our
+experiments.\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}
+The current development branch of our toolbox is available in a public
+GitHub
 repository.\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}
 
-The entire implementation consists of $400$ lines of MATLAB scripts for the UI
-module, $585$ and $800$ lines of C code in the naive and abstract accelerator
-back-ends, respectively (cf.~Section~\ref{sec:CEGIS}).  $4000$ lines of C code for utility functions such as
-interval and fixed-point arithmetic, as well as $1000$ lines of C++ code in the
-control synthesis module in CEGIS CBMC.  We evaluate \tool using $18$ SISO 
-control system benchmarks. Additionally, the documentation and videos about \tool are available 
-at \url{http://dsverifier.org/dsverifier/dssynth-toolbox/}.
+The entire implementation consists of $400$ lines of MATLAB scripts for the
+UI module, $585$ and $800$ lines of C code in the naive and abstract
+accelerator back-ends, respectively (cf.~Section~\ref{sec:CEGIS}).  $4000$
+lines of C code for utility functions such as interval and fixed-point
+arithmetic, as well as $1000$ lines of C++ code in the control synthesis
+module in CEGIS CBMC.  We evaluate \tool using $18$ SISO control system
+benchmarks.  Additionally, the documentation and videos about \tool are
+available at \url{http://dsverifier.org/dsverifier/dssynth-toolbox/}.
 
@@
 
-A digital system is stable \textit{iff} all of its poles are inside the $z$-plane unity circle, 
-namely poles must have the modulus less than one~\cite{astrom1997computer}. In order to compute the poles for the digital 
-system represented by Equations~\eqref{equation_plant} and \eqref{equation_controller}, 
-the user can invoke the \texttt{feedback} and \texttt{series} commands in MATLAB~\cite{matlab-toolbox} 
-to achieve a general equation regarding the transfer function representation, as illustrated in Fig.~\ref{combine-controller-plant}.
+A digital system is stable \textit{iff} all of its poles are inside the
+$z$-plane unity circle, namely poles must have the modulus less than
+one~\cite{astrom1997computer}.  In order to compute the poles for the
+digital system represented by Equations~\eqref{equation_plant} and
+\eqref{equation_controller}, the user can invoke the \texttt{feedback} and
+\texttt{series} commands in MATLAB~\cite{matlab-toolbox} to achieve a
+general equation regarding the transfer function representation, as
+illustrated in Fig.~\ref{combine-controller-plant}.
 
@@
 
-For the stability check, if any root of the denominator polynomial $D(z)$ in Eq.~\ref{equation_general} 
-has modulus equal or greater than one, then the system is unstable; 
-otherwise, it is stable. Indeed, the roots computed by the function \texttt{roots} 
-in MATLAB~\cite{matlab-toolbox} result in the following poles as shown in Fig.~\ref{roots-of-dz}, 
-which means that DSSynth has synthesized a stable digital controller.
+For the stability check, if any root of the denominator polynomial $D(z)$ in
+Eq.~\ref{equation_general} has modulus equal or greater than one, then the
+system is unstable; otherwise, it is stable.  Indeed, the roots computed by
+the function \texttt{roots} in MATLAB~\cite{matlab-toolbox} result in the
+following poles as shown in Fig.~\ref{roots-of-dz}, which means that DSSynth
+has synthesized a stable digital controller.
 
@@
 
-Simulating the digital system represented by Equations \eqref{equation_plant} and \eqref{equation_controller} 
-to validate and reproduce the system stability, the user can invoke the step response using the 
-command \texttt{dstep} in MATLAB, and then observe that the plotted graph shows a stable digital system, 
-as shown in Fig.~\ref{step-response}.
+Simulating the digital system represented by Equations
+\eqref{equation_plant} and \eqref{equation_controller} to validate and
+reproduce the system stability, the user can invoke the step response using
+the command \texttt{dstep} in MATLAB, and then observe that the plotted
+graph shows a stable digital system, as shown in Fig.~\ref{step-response}.
 %
@@
 
-Our evaluation consists of $18$ SISO control system benchmarks 
-extracted from the literature~\cite{abate2017,abatecav2017,bouabdallah, acrobot,cstr,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS,DBLP:journals/tc/BessaIPCF17,DBLP:journals/dafes/BessaICF16},
-which include physical plants for unmanned aerial vehicle (UAV), cruise control system, 
-spring-mass damper, satellite, direct current (DC) servo motor, helicopter, 
-inverted pendulum, pendulum, magnetic suspension, magnitezed pointer, 1/4 car suspension, 
-computer tape driver, flexible beam, guidance system, USCG cutter tampa, continuous stirred tank reactor, 
-voltage regulator, and an acrobot control system.
+Our evaluation consists of $18$ SISO control system benchmarks extracted
+from the literature~\cite{abate2017,abatecav2017,bouabdallah,
+acrobot,cstr,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev,
+converters,
+CTMS,DBLP:journals/tc/BessaIPCF17,DBLP:journals/dafes/BessaICF16}, which
+include physical plants for unmanned aerial vehicle (UAV), cruise control
+system, spring-mass damper, satellite, direct current (DC) servo motor,
+helicopter, inverted pendulum, pendulum, magnetic suspension, magnitezed
+pointer, 1/4 car suspension, computer tape driver, flexible beam, guidance
+system, USCG cutter tampa, continuous stirred tank reactor, voltage
+regulator, and an acrobot control system.
 
@@
 
-For all evaluated benchmarks, the signal input range related to the control system 
-lies between $-1$ and $1$. The implementation features used for digital controller are:
-$8$-bits for the integer part (including the sign bit) and $8$-bits for the fractional 
-part. We have run the \tool using the CEGIS with multi-staged verification (cf.~Section~\ref{sec:CEGIS}).
-All experiments with \tool v$1$.$0$.$0$  were conducted on an otherwise idle 
-Intel Core i$7-2600$ $3.40$ GHz processor, with $24$ GB of RAM, running Ubuntu $64$-bits.
+For all evaluated benchmarks, the signal input range related to the control
+system lies between $-1$ and $1$.  The implementation features used for
+digital controller are: $8$-bits for the integer part (including the sign
+bit) and $8$-bits for the fractional part.  We have run the \tool using the
+CEGIS with multi-staged verification (cf.~Section~\ref{sec:CEGIS}).  All
+experiments with \tool v$1$.$0$.$0$ were conducted on an otherwise idle
+Intel Core i$7-2600$ $3.40$ GHz processor, with $24$ GB of RAM, running
+Ubuntu $64$-bits.
 
@@
 
-For our experiments, we observed that the \tool correctly synthesizes stable and safe digital controllers 
-for our set of benchmarks represented by transfer functions or state-space equations. 
-We employed a diverse set of real-world benchmarks extracted from the control literature. 
-However, note that this set of benchmarks is still limited within the scope of this paper, and 
-the performance may not be generalized to other benchmarks. 
-The median runtime for our benchmarks set is $124$\,s, and the average synthesis time amounts 
-to $35.5$\,s for closed-loop control systems represented by state-space equations, while 
-for transfer functions, the average synthesis time amounts to $123.6$\,s.
+For our experiments, we observed that the \tool correctly synthesizes stable
+and safe digital controllers for our set of benchmarks represented by
+transfer functions or state-space equations.  We employed a diverse set of
+real-world benchmarks extracted from the control literature.  However, note
+that this set of benchmarks is still limited within the scope of this paper,
+and the performance may not be generalized to other benchmarks.  The median
+runtime for our benchmarks set is $124$\,s, and the average synthesis time
+amounts to $35.5$\,s for closed-loop control systems represented by
+state-space equations, while for transfer functions, the average synthesis
+time amounts to $123.6$\,s.
 
-Additionally, we are able to reproduce the stability and safety for all evaluated control system benchmarks.
-As an example, we have reproduced the stability property in the synthesized controller 
-for a DC motor plant described in Eq.~\eqref{tf-synth-controller}, simulating the step response 
+Additionally, we are able to reproduce the stability and safety for all
+evaluated control system benchmarks.  As an example, we have reproduced the
+stability property in the synthesized controller for a DC motor plant
+described in Eq.~\eqref{tf-synth-controller}, simulating the step response
 in MATLAB.  Fig.~\ref{tf-step-response} shows that the digital controller
-synthesized by the \tool stabilizes the closed-loop control system using 
-the series connection (as shown in Fig.~\ref{fig:typical-control-system}) for the DC motor plant. 
-We have applied this procedure to all synthesized controllers to confirm the reliability of our experimental results.
+synthesized by the \tool stabilizes the closed-loop control system using the
+series connection (as shown in Fig.~\ref{fig:typical-control-system}) for
+the DC motor plant.  We have applied this procedure to all synthesized
+controllers to confirm the reliability of our experimental results.
 %
@@
 \end{equation}
-
-Where,
+%
+\noindent where,
 %
@@
 
-The \tool can automatically synthesize stable and safe digital controllers for intricate dynamic physical plants, 
-represented in MATLAB as a transfer function or a state-space equation using CEGIS. 
-In particular, the \tool represents the first fully automated synthesis
-tool that is algorithmically and numerically sound, considering various error
-sources in the implementation of the digital control algorithm and in the computational 
+The \tool can automatically synthesize stable and safe digital controllers
+for intricate dynamic physical plants, represented in MATLAB as a transfer
+function or a state-space equation using CEGIS.  In particular, the \tool
+represents the first fully automated synthesis tool that is algorithmically
+and numerically sound, considering various error sources in the
+implementation of the digital control algorithm and in the computational
 modeling of plant dynamics~\cite{abate2017,abatecav2017}.
 %
-Additionally, given the current literature in controller synthesis, there is no other MATLAB toolbox 
-for synthesizing stable and safe digital controllers for physical plants, while taking into account all aspects of its 
-digital implementation. 
+Additionally, given the current literature in controller synthesis, there is
+no other MATLAB toolbox for synthesizing stable and safe digital controllers
+for physical plants, while taking into account all aspects of its digital
+implementation.
 %
-As future work, the \tool will perform synthesis of other specifications (e.g., performance) 
-and be combined with DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to verify/validate 
-other controller properties.
+As future work, the \tool will perform synthesis of other specifications
+(e.g., performance) and be combined with DSVerifier/DSValidator
+Toolboxes~\cite{issta2017,dsvalidator} to verify/validate other controller
+properties.
 

### 2017-07-02 ase2017/paper.tex
Wording abstract

@@
 %
-We present an automated MATLAB Toolbox, named as DSSynth (Digital-System
+We present an automated MATLAB Toolbox, named \emph{DSSynth} (Digital-System
 Synthesizer), to synthesize sound digital controllers for physical plants
 that are represented as linear time-invariant systems with single input and
-output.  In particular, DSSynth synthesizes digital controllers that are
-sound w.r.t.  the stability and safety specifications by taking into account
-finite word-length effects in their representation.  DSSynth considers the
+output.  In~particular, DSSynth synthesizes digital controllers that are
+sound w.r.t.~stability and safety specifications.  DSSynth considers the
 complete range of approximations, including time discretization,
-quantization effects, and finite-precision arithmetic (and its rounding
-errors).  Currently, there are two DSSynth versions for synthesizing digital
-controllers for physical plants represented by transfer function or
-state-space equations: a command-line and a MATLAB application.  The
-resulting toolbox enables application of program synthesis to real-world
-control engineering systems.
+quantization effects and finite-precision arithmetic (and its rounding
+errors).  The resulting toolbox enables the application of program synthesis
+to real-world control engineering problems.
 %

### 2017-07-02 ase2017/paper.tex
wordings

@@
 closed-loop dynamics, where outputs of discrete plant $G(z)$ are fed back
-and compared to a reference signal to which a controller $C(z)$ should
+and compared to a reference signal towards which a controller $C(z)$ should
 steer~\cite{astrom1997computer}.  Fig.~\ref{fig:typical-control-system}
-shows a typical closed-loop digital control system.
-%
+depicts a typical closed-loop digital control system.
+
 \begin{figure}[ht!]
@@
 \includegraphics[width=0.4\textwidth]{closedloopseries.pdf}
-\caption{Typical Closed-loop Control System.}
+\caption{Typical Closed-loop Control System}
 \label{fig:typical-control-system}
@@
 
-There are various mathematical representations for control systems, e.g.,
-transfer functions and state-space equations (difference or differential
-equations).  Here, systems with a single input and a single output (SISO)
-are considered and represented by transfer functions or state-space LTI
-models.  LTI models are used to represent dynamics in several engineering
-applications to support non-trivial tasks when applied to embedded \&
-cyber-physical systems (e.g., robot manipulator, smart grid, power plants,
-distributed robotics, and automatic pilot avionics).  The following
-expression presents the general form of a discrete plant or a digital
-controller based on the transfer function representation:
+There are various ways to model control systems.  Two common ways to
+represent the dynamics of such systems are transfer functions and
+state-space equations (difference or differential equations).  In this
+paper, we consider systems with a single input and a single output (SISO)
+given either as transfer functions or state-space linear time-invariant
+(LTI) models.  LTI models are a common sub-class, and are frequently used in
+cyber-physical systems (e.g., in robotics, smart grids, power plants, and
+avionics).  A discretized plant or a digital controller is, in generally,
+given as follows when using a transfer function representation:
 %
@@
 %
-\noindent where $z^{-1}$ is called the backward-shift operator; $A(z)$ and $B(z)$ are 
-the denominator and numerator polynomials; and $N$ and $M$
-represent the denominator and numerator polynomials order, respectively.
-%
-In a state-space form, 
-the behavior of a system is represented via a state evolution equation $x(n+1)$ and an instantaneous 
-output equation $y(n)$, as follows:
+In this representation, $z^{-1}$ is called the backward-shift operator;
+$A(z)$ and $B(z)$ are the denominator and numerator polynomials; and $N$ and
+$M$ are the order of the denominator and numerator polynomials, respectively.
+
+In a state-space form, the behavior of a system is represented via a state
+evolution equation $x(n+1)$ and an instantaneous output equation $y(n)$, as
+follows:
 %
@@
 \end{equation}
+%
+where $A$, $B$, $C$ and $D$ are matrices that fully specify the model.
 
-\noindent where $A$, $B$, $C$ and $D$ are matrices that fully specify the model. 
-%
 Controllers synthesis for LTI systems is richly studied in the

### 2017-07-02 ase2017/paper.tex
wordings

@@
 
-Controllers synthesis for LTI systems is richly studied in the
-literature~\cite{mazo2010pessoa,DBLP:conf/emsoft/RavanbakhshS16,economakos2016automated};
-however, there are many challenges when digital control system theory is
-used, mainly due to the finite-word length (FWL) effects leading to
-truncation or round-off errors~\cite{Guang2013, Istepanian2001}, time
+There is a rich body of literature on automating the synthesis of
+controllers for LTI systems~\cite{mazo2010pessoa,
+DBLP:conf/emsoft/RavanbakhshS16, economakos2016automated}.  However, there
+are many challenges when digital control is used to implement the
+controller, mainly due to effects of finite-word length (FWL), which leads
+to truncation or round-off errors~\cite{Guang2013, Istepanian2001}, and time
 discretization and quantization noise, which are typically introduced by
@@
 
-Recently, a new methodology to synthesize digital control systems has been
-proposed, named DSSynth (Digital-System Synthesizer)~\cite{abate2017,
-abatecav2017}, which is based on the Counter-Example Guided Inductive
-Synthesis (CEGIS) approach~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. 
-CEGIS is used as a program synthesis engine that is able to generate sound
-digital controllers for highly non-trivial control system specifications
-with a very high degree of automation.  The program synthesis engine uses a
-specification as starting point, and subsequently produces a sequence of
-candidate programs from a given template.  The candidate programs are
-iteratively refined to eventually satisfy the specification.  Modern
-synthesis engines such as the one used here combine automated testing,
-genetic algorithms and SMT-based
+We have recently proposed a new method to synthesize digital control systems
+for LTI systems, which we have named \emph{DSSynth} (Digital-System
+Synthesizer)~\cite{abate2017, abatecav2017}.  The algorithm implements
+Counter-Example Guided Inductive Synthesis
+(CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}.  CEGIS is used to
+realize a program synthesis engine that is able to generate sound digital
+controllers for highly non-trivial system specifications with a very high
+degree of automation.  The program synthesis engine is given a specification
+and subsequently produces a sequence of candidate programs from a template. 
+The candidate programs are iteratively refined to eventually satisfy the
+specification.  Modern synthesis engines such as the one used here combine
+automated testing, genetic algorithms and SMT-based
 reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
@@
 controllers for a given physical plant represented by either transfer
-functions or state-space equations~\cite{abate2017,abatecav2017}.
+functions or state-space equations.
 

### 2017-07-02 ase2017/paper.tex
wording

@@
 
-Notably, there are toolboxes in MATLAB with functions and scripts to
-facilitate the digital system design and
-implementation~\cite{matlab-toolbox}.  Indeed, there is a MATLAB Toolbox
-named as DSVerifier
-Toolbox~\cite{issta2017,DBLP:journals/tc/BessaIPCF17,DBLP:journals/dafes/BessaICF16},
-which automatically detects specific errors related to digital system design
-({\it e.g.}, stability, limit cycle and overflow) using symbolic model
-checking techniques based on Boolean Satisfiability (SAT) and Satisfiability
-Modulo Theories (SMT) solvers.  Pessoa~\cite{mazo2010pessoa} is another
-toolbox, but applied to the synthesis of correct-by-design digital
-controllers.  In particular, Pessoa is based on approximate bisimulation,
-which allows control engineers to replace differential equations, describing
-a physical plant, by a respective finite-state machine.  However, Pessoa
-does not take advantage of recent advances in bit-accurate verification of
-programs to synthesize controllers w.r.t.  FWL effects.  MATLAB already
-offers a tool named as Control System Tuner~\cite{autotuner} for
+There are existing toolboxes for MATLAB that provide functions and scripts
+to support design and implementation of digital
+controllers~\cite{matlab-toolbox}.  In~particular, there is a MATLAB Toolbox
+named \emph{DSVerifier}~\cite{issta2017, DBLP:journals/tc/BessaIPCF17,
+DBLP:journals/dafes/BessaICF16}, which automatically detects specific errors
+in a given digital system design (e.g., errors related to stability, limit
+cycle and overflow) using symbolic model checking based on Boolean
+Satisfiability (SAT) and Satisfiability Modulo Theories (SMT) solvers.  The
+Pessoa~\cite{mazo2010pessoa} toolbox performs synthesis of correct-by-design
+digital controllers.  Pessoa is based on approximate bisimulation, which
+allows control engineers to replace differential equations, describing a
+physical plant, by a respective finite-state machine.  However, Pessoa does
+not take advantage of recent advances in bit-accurate verification of
+programs to synthesize controllers w.r.t.~FWL effects.  MATLAB 
+offers a tool named Control System Tuner~\cite{autotuner} for
 automatically designing controllers based on optimization solvers or

### 2017-07-02 ase2017/paper.tex
wording

@@
 not take advantage of recent advances in bit-accurate verification of
-programs to synthesize controllers w.r.t.~FWL effects.  MATLAB 
-offers a tool named Control System Tuner~\cite{autotuner} for
-automatically designing controllers based on optimization solvers or
-graphical analysis.  However, the Control System Tuner is unable to consider
-FWL effects during the controller synthesis process.  To the best of our
-knowledge, there is no MATLAB toolbox able to perform digital controller
-synthesis based on program synthesis engines that considers the complete
-range of approximations, including time discretization, quantization
-effects, and finite-precision arithmetic and its rounding errors.
+programs to synthesize controllers w.r.t.~FWL effects.  MATLAB offers a tool
+named \emph{Control System Tuner}~\cite{autotuner} for automatically
+designing controllers based on optimization or graphical analysis.  However,
+the Control System Tuner is unable to consider FWL effects during controller
+synthesis.  To the best of our knowledge, there is no MATLAB toolbox able to
+perform digital controller synthesis that considers the complete range of
+approximations, including time discretization, quantization effects, and
+finite-precision arithmetic and its rounding errors.
 
 The present tool paper addresses this limitation and describes a toolbox for
-the DSSynth tool~\cite{abate2017, abatecav2017} in a MATLAB environment,
-named \tool.  The main advantage for the use of a MATLAB toolbox lies on
-designing physical plants in MATLAB and then promptly synthesizing a stable
-and safe digital controller, considering the complete range of
-approximations.  Notably, when using the \tool, an engineer is able to model
-a physical plant with MATLAB through transfer function or state-space
-representations, considering low-level systems parameters (implementation
-features and numerical format).
+DSSynth in MATLAB.  MATLAB is very commonly used for modeling physical
+plants.  Thus, the integration into MATLAB enables rapid synthesis of a
+stable and safe digital controller for such plants without switching the
+environment.
 

### 2017-07-02 ase2017/paper.tex
wording

@@
 
-The design of our synthesizer consists of two main phases, an inductive
-synthesis phase, {\sc synthesise}, and a validation phase, {\sc verify},
-which interact via a finite set of test vectors that is updated
+Our synthesizer iterates between two main phases, an inductive synthesis
+phase, {\sc synthesise}, and a validation phase, {\sc verify}.  The two
+phases interact via a finite set of test vectors, which is updated
 incrementally.  Given a stability and safety specification, the inductive
@@
 %
-If the synthesis phase succeeds in finding a witness, this witness is
-a candidate solution to the full synthesis formula.  We pass this
-candidate solution to the validation phase, which checks whether it is
-a full solution (i.e., satisfies the specification for all possible
-inputs).  If this is the case, then the algorithm terminates.
-Otherwise, additional information is provided to the inductive
-synthesis phase in the form of a new counterexample, C-ex, that is added to
-the set of test inputs, and the loop iterates again.
+If the synthesis phase succeeds in finding a witness, this witness is a
+candidate solution to the full synthesis formula.  We pass this candidate
+solution to the validation phase, which checks whether it is a full solution
+(i.e., satisfies the specification for all possible inputs).  If this is the
+case, then the algorithm terminates.  Otherwise, additional information is
+provided to the inductive synthesis phase in the form of a new
+counterexample, C-ex, that is added to the set of test inputs, and the loop
+iterates again.
 

### 2017-07-02 ase2017/paper.tex
wording

@@
 
-The present tool paper addresses this limitation and describes a toolbox for
-DSSynth in MATLAB.  MATLAB is very commonly used for modeling physical
+The present tool paper addresses this limitation and describes a MATLAB
+toolbox for DSSynth.  MATLAB is very commonly used for modeling physical
 plants.  Thus, the integration into MATLAB enables rapid synthesis of a
@@
 
-Instead of unfolding the dynamics, the second approach (shown in
+Instead of unfolding the dynamics, the second approach (illustrated in
 Fig.~\ref{fig:CEGARIS}) employs {\em abstract
@@
 
-A graphical user interface application was developed (as shown in Fig.~\ref{fig:gui-for-tf}) 
-to favor digital controller synthesis in MATLAB. Its aim is to improve usability and, 
-consequently, to attract more digital dynamical system engineers. Users can provide all 
-required parameters for digital controller synthesis: physical plant specification, 
-fixed-point representation and dynamic inputs. 
+A graphical user interface application was developed (illustrated in
+Fig.~\ref{fig:gui-for-tf}) to favor digital controller synthesis in MATLAB. 
+Its aim is to improve usability and, consequently, to attract more digital
+dynamical system engineers.  Users can provide all required parameters for
+digital controller synthesis: physical plant specification, fixed-point
+representation and dynamic inputs.
 %
@@
 \vspace{-0.2cm}
-\caption{General equation for the closed-loop control system using the series configuration as shown in Fig.~\ref{fig:typical-control-system}.}
+\caption{General equation for the closed-loop control system using the series configuration as
+illustrated in Fig.~\ref{fig:typical-control-system}}
 \label{combine-controller-plant}
@@
 
-The general equation that represents the closed-loop control system, using the series configuration as shown in Fig.~\ref{fig:typical-control-system},
-is described by Eq.~\ref{equation_general} as follows
+The general equation that represents the closed-loop control system, using
+the series configuration as illustrated in
+Fig.~\ref{fig:typical-control-system}, is described by
+Eq.~\ref{equation_general} as follows
 %
@@
 the function \texttt{roots} in MATLAB~\cite{matlab-toolbox} result in the
-following poles as shown in Fig.~\ref{roots-of-dz}, which means that DSSynth
-has synthesized a stable digital controller.
+following poles as illustrated in Fig.~\ref{roots-of-dz}, which means that
+DSSynth has synthesized a stable digital controller.
 
@@
 the command \texttt{dstep} in MATLAB, and then observe that the plotted
-graph shows a stable digital system, as shown in Fig.~\ref{step-response}.
+graph shows a stable digital system, as illustrated in
+Fig.~\ref{step-response}.
 %
@@
 synthesized by the \tool stabilizes the closed-loop control system using the
-series connection (as shown in Fig.~\ref{fig:typical-control-system}) for
+series connection (illustrated in Fig.~\ref{fig:typical-control-system}) for
 the DC motor plant.  We have applied this procedure to all synthesized
@@
 
-For this particular closed-loop control system, the feedback matrix (see Eq.~\eqref{ss-synth-feedback}) generated 
-by the \tool also leads to a stable system, as shown in Fig.~\ref{ss-step-response}.
+For this particular closed-loop control system, the feedback matrix (see
+Eq.~\eqref{ss-synth-feedback}) generated by the \tool also leads to a stable
+system, as sillustrated in Fig.~\ref{ss-step-response}.
 %

### 2017-07-02 ase2017/paper.tex
wording

@@
 for all reachable states.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \centering
-\resizebox{.43\textwidth}{!}
+\resizebox{.5\textwidth}{!}
 {
@@
 systems is based on the DSSynth tool~\cite{abate2017, abatecav2017}, 
-which can be split into two main stages as follows: manual (user) and 
-automated (DSSynth) procedures, as illustrated in Fig.~\ref{fig:synthesis-flow}. 
+which can be split into two main stages as follows: manual and 
+automated steps, as illustrated in Fig.~\ref{fig:synthesis-flow}. 
 %
@@
 
-In step $1$, the user has to define the digital controller representation,
-which can be a transfer function or a state-space model.  In step $2$, the
-physical plant (represented by Equations (\ref{eq:transferfunction}) or
-(\ref{eq:ss-example})) must be designed, using a method selected from the
-control literature~\cite{astrom1997computer}.  Finally, in step $3$, the
-numerical representation for the digital controller implementation must be
-defined by the user, {\it i.e.}, the FWL format that includes the number of
-bits for the integer and fractional parts as well as the dynamic range
-inputs.  The result of the manual procedure performed by the user is a
-digital system specification for the given physical plant in MATLAB.
+In Step~$1$, the user selects the digital controller representation, which
+can be a transfer function or a state-space model.  In Step~$2$, the
+physical plant (in the form of Equation~(\ref{eq:transferfunction}) or
+(\ref{eq:ss-example}), depending on representation) must be
+given~\cite{astrom1997computer}.  Finally, in Step~$3$, the numerical
+representation for the digital controller implementation must be set by the
+user, i.e., the FWL format that defines the number of bits of the integer
+and fractional parts as well as the dynamic range inputs.  The result of the
+input given by the user is a specification of the physical plant.
 
-After that, the synthesis process starts in step $A$, when \tool obtains the
-digital system specification in MATLAB, and then translates it into an
-ANSI-C program.  In step $B$, our CEGIS engine is invoked to synthesize the
-digital controller w.r.t.  the digital system specification.  Finally, in
-step $C$, the synthesized digital controller considering FWL effects is
-produced.  The output generated by \tool is the synthesized digital
-controller represented either in transfer function or state-space equation. 
-The synthesis is considered to be \emph{successful} if a digital controller
-is correctly synthesized w.r.t.  FWL effects; otherwise, if any parameter is
-incorrectly defined in previous steps, or if there is no solution (digital
-controller) for the respective physical plant (given the digital controller
-implementation aspects), then the synthesis is considered to have
-\emph{failed}.
+After that, the automated synthesis process starts with Step~$A$, where the
+\tool translates the digital system specification from the MATLAB format
+into an ANSI-C program.  In Step~$B$, our CEGIS engine is invoked to
+synthesize the digital controller w.r.t.~the digital system specification. 
+Finally, in Step~$C$, the synthesized digital controller is produced.  The
+output generated by the \tool is the synthesized digital controller
+represented either in transfer function or state-space equation.  The
+synthesis is considered to be \emph{successful} if a digital controller is
+correctly synthesized w.r.t.~FWL effects; otherwise, if any parameter is
+incorrectly defined in previous steps, or if there is no solution (no
+controller) for the respective physical plant (given the implementation
+requirements), then the synthesis is considered to have \emph{failed}.
 
@@
 answer our queries.  CBMC itself relies on an underlying SAT or SMT solver
-to solve the resulting formulae.  We model FWL effects, time discretization
+to solve the resulting formulae.  We~model FWL effects, time discretization
 and the presence of quantization noise explicitly using CBMC's
@@
 
-The \tool's features can be described as follows:
+The features of the \tool can be summarized as follows:
 

### 2017-07-02 ase2017/paper.tex
wording

@@
 The \tool can automatically synthesize stable and safe digital controllers
-for intricate dynamic physical plants, represented in MATLAB as a transfer
-function or a state-space equation using CEGIS.  In particular, the \tool
-represents the first fully automated synthesis tool that is algorithmically
-and numerically sound, considering various error sources in the
-implementation of the digital control algorithm and in the computational
-modeling of plant dynamics~\cite{abate2017,abatecav2017}.
+for intricate dynamic physical plants, represented in MATLAB either as a
+transfer function or a state-space equation.  The \tool is the first fully
+automated synthesis tool that is algorithmically and numerically sound,
+considering various error sources in the implementation of the digital
+control algorithm and in the computational modeling of plant
+dynamics~\cite{abate2017, abatecav2017}.
 %
@@
 no other MATLAB toolbox for synthesizing stable and safe digital controllers
-for physical plants, while taking into account all aspects of its digital
+for physical plants that considers all aspects of their digital
 implementation.
 %
-As future work, the \tool will perform synthesis of other specifications
-(e.g., performance) and be combined with DSVerifier/DSValidator
-Toolboxes~\cite{issta2017,dsvalidator} to verify/validate other controller
-properties.
+As future work, the \tool will perform synthesis considering additional
+requirements (e.g., performance) and will be combined with the
+DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to
+verify/validate further controller properties.
 

### 2017-07-02 ase2017/paper.tex
improved abstract and introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 quantization effects and finite-precision arithmetic (and its rounding
-errors).  The resulting toolbox enables the application of program synthesis
+errors).  We demonstrate the practical value of
+this toolbox by automatically synthesizing stable and safe controllers for intricate
+physical plant models from the digital control literature.
+The resulting toolbox enables the application of program synthesis
 to real-world control engineering problems.
@@
 depicts a typical closed-loop digital control system.
-
+%
 \begin{figure}[ht!]
@@
 stable and safe digital controller for such plants without switching the
-environment.
+environment. Experimental results show that \tool is able to efficiently 
+synthesize stable and safe controllers for a set of intricate benchmarks taken 
+from the literature:  the median runtime for our benchmarks set is $124$\,s, 
+and the average synthesis time amounts to $35.5$\,s for closed-loop control 
+systems represented by state-space equations, while for transfer functions, the average synthesis
+time amounts to $123.6$\,s.
 

### 2017-07-08 ase2017/paper.tex

@@
 
-In Step~$1$, the user selects the digital controller representation, which
-can be a transfer function or a state-space model.  In Step~$2$, the
+In Step~1, the user selects the digital controller representation, which
+can be a transfer function or a state-space model.  In Step~2, the
 physical plant (in the form of Equation~(\ref{eq:transferfunction}) or
 (\ref{eq:ss-example}), depending on representation) must be
-given~\cite{astrom1997computer}.  Finally, in Step~$3$, the numerical
+given~\cite{astrom1997computer}.  Finally, in Step~3, the numerical
 representation for the digital controller implementation must be set by the
@@
 
-After that, the automated synthesis process starts with Step~$A$, where the
+After that, the automated synthesis process starts with Step~A, where the
 \tool translates the digital system specification from the MATLAB format
-into an ANSI-C program.  In Step~$B$, our CEGIS engine is invoked to
+into an ANSI-C program.  In Step~B, our CEGIS engine is invoked to
 synthesize the digital controller w.r.t.~the digital system specification. 
-Finally, in Step~$C$, the synthesized digital controller is produced.  The
+Finally, in Step~C, the synthesized digital controller is produced.  The
 output generated by the \tool is the synthesized digital controller
@@
 model checker (CBMC)~\cite{cbmc}.  CBMC transforms the ANSI-C representation
-of our closed-loop control system model into its internal format called
-\emph{GOTO}.  We instrument this internal \emph{GOTO} program for each
-synthesis or verification scenario accordingly, and use CBMC as an oracle to
-answer our queries.  CBMC itself relies on an underlying SAT or SMT solver
-to solve the resulting formulae.  We~model FWL effects, time discretization
-and the presence of quantization noise explicitly using CBMC's
-nondeterminism API (e.g., \texttt{nondet}, \texttt{CPROVER\_assume}
-intrinsic functions).  Our module was included in CBMC~5.7 and is available
-for public
+of our closed-loop control system model into its internal format.  We
+instrument this IR for each synthesis or verification scenario accordingly,
+and use CBMC as an oracle to answer our queries.  CBMC itself relies on an
+underlying SAT or SMT solver to solve verification conditions.  We~model FWL
+effects, time discretization and the presence of quantization noise
+explicitly using CBMC's nondeterminism API (e.g., \texttt{nondet},
+\texttt{CPROVER\_assume} intrinsic functions).  Our module is included in
+CBMC~5.7 and is available for
 download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}
@@
 UI module, $585$ and $800$ lines of C code in the naive and abstract
-accelerator back-ends, respectively (cf.~Section~\ref{sec:CEGIS}).  $4000$
+accelerator back-ends, respectively (cf.~Section~\ref{sec:CEGIS}), $4000$
 lines of C code for utility functions such as interval and fixed-point
@@
 module in CEGIS CBMC.  We evaluate \tool using $18$ SISO control system
-benchmarks.  Additionally, the documentation and videos about \tool are
+benchmarks.  Additionally, documentation and videos about the \tool are
 available at \url{http://dsverifier.org/dsverifier/dssynth-toolbox/}.
@@
 
-The \tool performs the following automated procedures 
+The \tool performs the following automated steps
 to synthesize a given digital controller:
-
+%
 \begin{enumerate}
-\item \textbf{Setup}: obtains the physical plant, fixed-point format 
-and dynamic input ranges, and translates them to a specific structure in MATLAB.
+%
+\item \textbf{Setup}: obtains the physical plant, fixed-point format and
+dynamic input ranges, and translates them to a specific structure in MATLAB.
+%
 \item \textbf{Parse}: obtains the digital system specification and translates 
 it into an ANSI-C program.
-\item \textbf{Execution}: obtains the ANSI-C program from the previous (parse) step 
-and calls our CEGIS engine as a back-end program synthesis tool to perform the automated synthesis;
+%
+\item \textbf{Execution}: obtains the ANSI-C program from the previous
+(parse) step and calls our CEGIS engine as a back-end program synthesis tool
+to perform the automated synthesis;
+%
 \item \textbf{Extraction}: obtains the ``.log'' file that is generated 
 after the synthesis phase and then checks the synthesized digital-controller.
-\item \textbf{Report}: obtains the digital controller from the previous (extraction) step 
-and translates it into the MATLAB structures to show the respective result to the user.
+%
+\item \textbf{Report}: obtains the digital controller from the previous
+(extraction) step and translates it into MATLAB, for presentation to the
+user.
+%
 \end{enumerate}
@@
 The features of the \tool can be summarized as follows:
-
+%
 \begin{itemize}
+%
 \item \textbf{Representation}: the synthesis can be 
@@
 transfer function or as state-space models.
+%
 \item \textbf{Fixed-Point Arithmetic}: the digital 
@@
 using the given fixed-point numerical representation.
-\item \textbf{Interface}: the synthesis can be executed 
-via command-line or graphical-user interface (GUI). 
-For the GUI application, the user can plot the step response 
-to reproduce the stability in closed-loop of the synthesized digital controller.
+%
+\item \textbf{Interface}: the synthesis can be executed via command-line or
+graphical-user interface (GUI).  For the GUI application, the user can plot
+the step response to reproduce the stability in closed-loop of the
+synthesized digital controller.
+%
 \end{itemize}
@@
 
-Users must provide a digital system described as a MATLAB model 
-using a \texttt{tf} (for transfer function) or an \texttt{ss} (for state-space model) 
-command (cf. step $1$ of Fig.~\ref{fig:synthesis-flow}).
-\tool is called via command line in MATLAB as
+Users must provide a digital system described as a MATLAB model using a
+\texttt{tf} (for transfer function) or an \texttt{ss} (for state-space
+model) command (step $1$ of Fig.~\ref{fig:synthesis-flow}).  The \tool is
+called via the command line in MATLAB as
 
@@
 
-\noindent where \texttt{plant} is the physical plant in state-space or transfer function representation, 
-\texttt{intBits} is the integer part, \texttt{fracBits} is the fractional part, \texttt{maxR} and \texttt{minR} 
-are the maximum and minimum dynamic range, respectively (cf. steps $2$ and $3$ of Fig.~\ref{fig:synthesis-flow}).
+\noindent where \texttt{plant} is the physical plant in state-space or
+transfer function representation, \texttt{intBits} is the integer part,
+\texttt{fracBits} is the fractional part, \texttt{maxR} and \texttt{minR}
+are the maximum and minimum dynamic range, respectively (steps $2$ and
+$3$ of Fig.~\ref{fig:synthesis-flow}).
 %
-After executing the \texttt{synthesize} command, 
-\tool provides the synthesized digital controller, according to the implementation aspects.
+After executing the \texttt{synthesize} command, the \tool provides the
+synthesized digital controller.
 
@@
 A graphical user interface application was developed (illustrated in
-Fig.~\ref{fig:gui-for-tf}) to favor digital controller synthesis in MATLAB. 
-Its aim is to improve usability and, consequently, to attract more digital
-dynamical system engineers.  Users can provide all required parameters for
-digital controller synthesis: physical plant specification, fixed-point
-representation and dynamic inputs.
-%
+Fig.~\ref{fig:gui-for-tf}) to support digital controller synthesis in
+MATLAB.  Its aim is to improve usability and, consequently, to attract more
+engineers.  Users provide the following inputs for digital controller
+synthesis within the UI: physical plant specification, fixed-point
+representation and the range of the inputs.
+
 \begin{figure}[ht]
     \centering
-    \subfloat[Define the system representation and the physical plant.]{
+    \subfloat[Definition of the system representation and the physical plant]{
 		\includegraphics[width=0.2\textwidth]{step1.png}
@@
 		\hfil
-    \subfloat[Define implementation aspects and dynamic range.]{
+    \subfloat[Definition of implementation aspects and input ranges]{
 	\includegraphics[width=0.2\textwidth]{step2.png}
@@
 		\hfil
-    \subfloat[Resulting digital controller synthesized by DSSynth.]{
+    \subfloat[Digital controller synthesized by DSSynth]{
 	\includegraphics[width=0.2\textwidth]{step3.png}
@@
 		\hfil
-    \subfloat[Step response for the synthesized digital controller.]{
+    \subfloat[Step response for the synthesized digital controller]{
 	\includegraphics[width=0.22\textwidth]{step4.png}
@@
 		\hfil
-    \caption{DSSynth GUI application for the controller synthesis based on transfer function representation.}
+    \caption{DSSynth GUI for controller synthesis using transfer function representation}
     \label{fig:gui-for-tf}
@@
 
-To illustrate the \tool's usage, Fig.~\ref{toolbox-usage} shows each step of the 
-synthesis process for a physical plant described in Eq.~\eqref{equation_plant},
-which represents a real unmanned aerial vehicle (UAV) quadcopter system~\cite{bouabdallah}. 
-This physical plant is expressed by a transfer function $G(z)$, where 
-$B(z)$ and $A(z)$ represent the numerator and denominator, respectively, as
+To illustrate the usage of the \tool, Fig.~\ref{toolbox-usage} shows each
+step of the synthesis process for a physical plant described in
+Eq.~\eqref{equation_plant}, which represents a unmanned aerial vehicle
+(UAV) quadcopter system~\cite{bouabdallah}.  This physical plant is
+expressed by a transfer function $G(z)$, where $B(z)$ and $A(z)$ represent
+the numerator and denominator, respectively, as
 %
@@
 \vspace{-0.2cm}
-\caption{Synthesis of a digital controller for the physical plant defined in Eq.(\ref{equation_plant}) in MATLAB, with a fixed-point format  $\left\langle 8,8\right\rangle$.}
+\caption{Synthesis of a digital controller for the physical plant defined in Eq.(\ref{equation_plant}) in MATLAB, with a fixed-point format  $\left\langle 8,8\right\rangle$}
 \label{toolbox-usage}
@@
 
-In Fig.~\ref{toolbox-usage}, ``num'' represents $B(z)$ and ``den'' represent $A(z)$, while 
-$y$ represents the synthesized stable digital controller, which is defined by Eq.(\ref{equation_controller}).
+In Fig.~\ref{toolbox-usage}, ``num'' represents $B(z)$ and ``den'' represent
+$A(z)$, while $y$ represents the synthesized stable digital controller,
+which is defined by Eq.(\ref{equation_controller}).
 %
@@
 
-A digital system is stable \textit{iff} all of its poles are inside the
-$z$-plane unity circle, namely poles must have the modulus less than
+A digital system is stable iff all of its poles are inside the
+$z$-plane unity circle, i.e., the poles must have a modulus less than
 one~\cite{astrom1997computer}.  In order to compute the poles for the
@@
 \eqref{equation_controller}, the user can invoke the \texttt{feedback} and
-\texttt{series} commands in MATLAB~\cite{matlab-toolbox} to achieve a
+\texttt{series} commands in MATLAB~\cite{matlab-toolbox} to obtain a
 general equation regarding the transfer function representation, as
@@
 \eqref{equation_plant} and \eqref{equation_controller} to validate and
-reproduce the system stability, the user can invoke the step response using
+reproduce the system stability, the user can obtain the step response using
 the command \texttt{dstep} in MATLAB, and then observe that the plotted
-graph shows a stable digital system, as illustrated in
-Fig.~\ref{step-response}.
-%
+graph indicates a stable digital system (Fig.~\ref{step-response}).
+
 \begin{figure}[ht]
   \includegraphics[width=0.5\textwidth]{step-response.eps}
-  \caption{Step response for the Eq.~\eqref{equation_plant} describing a stable system for the UAV quadcopter system.}
+  \caption{Step response for Eq.~\eqref{equation_plant} describing a stable system for the UAV quadcopter system}
   \label{step-response}
@@
 Our evaluation consists of $18$ SISO control system benchmarks extracted
-from the literature~\cite{abate2017,abatecav2017,bouabdallah,
-acrobot,cstr,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev,
-converters,
-CTMS,DBLP:journals/tc/BessaIPCF17,DBLP:journals/dafes/BessaICF16}, which
-include physical plants for unmanned aerial vehicle (UAV), cruise control
-system, spring-mass damper, satellite, direct current (DC) servo motor,
-helicopter, inverted pendulum, pendulum, magnetic suspension, magnitezed
-pointer, 1/4 car suspension, computer tape driver, flexible beam, guidance
-system, USCG cutter tampa, continuous stirred tank reactor, voltage
-regulator, and an acrobot control system.
+from the literature~\cite{abate2017, abatecav2017, bouabdallah, acrobot,
+cstr, KOKOTOVIC198023, gajic2008optimal, Franklin15, maglev, converters,
+CTMS, DBLP:journals/tc/BessaIPCF17, DBLP:journals/dafes/BessaICF16}, which
+include physical plants for a unmanned aerial vehicle (UAV), a cruise
+control system, a spring-mass damper, a satellite, a direct current (DC)
+servo motor, a helicopter, the inverted pendulum, a pendulum, magnetic
+suspension, a magnitezed pointer, 1/4 car suspension, a computer tape
+driver, a flexible beam, a guidance system, a USCG cutter tampa, a
+continuous stirred tank reactor, a voltage regulator, and an acrobot control
+system.
 
@@
 For all evaluated benchmarks, the signal input range related to the control
-system lies between $-1$ and $1$.  The implementation features used for
-digital controller are: $8$-bits for the integer part (including the sign
-bit) and $8$-bits for the fractional part.  We have run the \tool using the
+system is between $-1$ and $1$.  The implementation features used for
+digital controller are: $8$~bits for the integer part (including the sign
+bit) and $8$~bits for the fractional part.  We have run the \tool using
 CEGIS with multi-staged verification (cf.~Section~\ref{sec:CEGIS}).  All
@@
 
-The main objectives of our experimental evaluation is to (1) evaluate the \tool performance 
-to produce stable and safe controllers, and also (2) confirm the stability and safety of the synthesized digital 
-controllers outside of our model using MATLAB. %, using both the transfer function and state-space representations.
+The main objectives of our experimental evaluation is to (1)~evaluate the
+\tool performance to produce stable and safe controllers, and also
+(2)~confirm the stability and safety of the synthesized digital controllers
+outside of our model using MATLAB.
+
+%, using both the transfer function and state-space representations.
 

### 2017-08-06 ase2017/paper.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
ase2017

@@
 cyber-physical systems (e.g., in robotics, smart grids, power plants, and
-avionics).  A discretized plant or a digital controller is, in generally,
+avionics).  A discretized plant or a digital controller is, in general,
 given as follows when using a transfer function representation:
@@
 representation using MATLAB, which means that our results are reliable for control engineers. 
-In particular, we unfold the system dynamics up to a given depth, 
-compute the system input and output via the feedback matrix, and then check the states bounds.
+In particular, the safety of controllers may be checked in computing the infinity norm of states, {\it i.e.}, the product between $l_{\infty}$ norm of initial states ($\vert\vert{x_{0}}\vert\vert_{\infty}=\max{x_{0}}$) and the $l_{1}$ norm of ($\vert\vert{\bar{A}}\vert\vert_{1}=\max\limits_{j}{\sum\limits_{i=1}^{m} \vert \bar{a}_{ij} \vert}$, where $\bar{A}=A-BK$).
+This is a conservative safety checking that is based in a sufficient condition~\cite{toscano2013structured}.
+An alternative (and less conservative)  is to unfold the system dynamics up to a given depth, with the initial state equal to its maximum value, and compute the system input and output via the feedback matrix, and then check the states bounds.
  A link to the full experimental environment, including the scripts, benchmarks, 

### 2017-08-14 ase2017/paper.tex
minor corrections
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2017-07-08 ase2017/paper.tex
@@
 representation using MATLAB, which means that our results are reliable for control engineers. 
-In particular, we unfold the system dynamics up to a given depth, 
-compute the system input and output via the feedback matrix, and then check the states bounds.
- A link to the full experimental environment, including the scripts, benchmarks, 
+In particular, the controllers safety can be checked by computing the states infinity norm, {\it i.e.}, 
+the product between $l_{\infty}$ norm of initial states ($\vert\vert{x_{0}}\vert\vert_{\infty}=\max{x_{0}}$) 
+and the $l_{1}$ norm of ($\vert\vert{\bar{A}}\vert\vert_{1}=\max\limits_{j}{\sum\limits_{i=1}^{m} \vert \bar{a}_{ij} \vert}$, 
+where $\bar{A}=A-BK$). This is a conservative safety check, which is based on a sufficient condition~\cite{toscano2013structured}. 
+An alternative (and less conservative) approach is to unfold the system dynamics up to a given depth, 
+with the initial state equal to its maximum value, compute the system input and output via the feedback matrix, 
+and then check the states bounds. A link to the full experimental environment, including the scripts, benchmarks, 
  videos, documentation and the tool, is provided online.\footnote{\url{www.dsverifier.org}}

### 2017-08-14 ase2017/paper.tex
added CPROVER link to download DSSynth
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 benchmarks.  Additionally, documentation and videos about the \tool are
-available at \url{http://dsverifier.org/dsverifier/dssynth-toolbox/}.
+available at \url{www.cprover.org/DSSynth/dssynth-toolbox-1.0.0.zip}.
 
@@
 and then check the states bounds. A link to the full experimental environment, including the scripts, benchmarks, 
- videos, documentation and the tool, is provided online.\footnote{\url{www.dsverifier.org}}
+ videos, documentation and the tool, is provided online.\footnote{\url{www.cprover.org/DSSynth/dssynth-toolbox-1.0.0.zip}}
 

### 2017-08-14 ase2017/paper.tex
minor fixes

@@
 representation using MATLAB, which means that our results are reliable for control engineers. 
-In particular, the controllers safety can be checked by computing the states infinity norm, {\it i.e.}, 
+In particular, given that the closed loop dynamics are convergent, the controller's safety can be checked by computing the initial state's infinity norm, {\it i.e.}, 
 the product between $l_{\infty}$ norm of initial states ($\vert\vert{x_{0}}\vert\vert_{\infty}=\max{x_{0}}$) 

### 2017-08-14 ase2017/paper.tex
Added connections to ASE topics
Added brief mention of future work relevant to ASE community.

@@
 %
+The \tool presents a practical application of CEGIS-based program synthesis.
+Tractable program synthesis in control engineering encourages the application
+of this technique in other fields such as program repair or superoptimisation.
+Future work of this group will pursue the application of CEGIS to software
+engineering problems.
+%
 Additionally, given the current literature in controller synthesis, there is

### 2017-08-16 ase2017/paper.tex
reviewed conclusions of the ASE tool paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 with the initial state equal to its maximum value, compute the system input and output via the feedback matrix, 
-and then check the states bounds. A link to the full experimental environment, including the scripts, benchmarks, 
- videos, documentation and the tool, is provided online.\footnote{\url{www.cprover.org/DSSynth/dssynth-toolbox-1.0.0.zip}}
+and then check the states bounds.
+
+%A link to the full experimental environment, including the scripts, benchmarks, 
+%videos, documentation and the tool, is provided online.\footnote{\url{www.cprover.org/DSSynth/dssynth-toolbox-1.0.0.zip}}
 
@@
 of this technique in other fields such as program repair or superoptimisation.
-Future work of this group will pursue the application of CEGIS to software
-engineering problems.
 %
@@
 verify/validate further controller properties.
+We will also pursue the application of CEGIS to software
+engineering problems.
 

### 2017-08-16 ase2017/paper.tex
nudge

@@
 automated steps, as illustrated in Fig.~\ref{fig:synthesis-flow}.
-%
+
 \begin{figure}[ht!]
 \centering
-\includegraphics[width=0.45\textwidth]{synthesis-flow.pdf}
-\caption{Digital Controller Synthesis Methodology.}
+\includegraphics[width=0.47\textwidth]{synthesis-flow.pdf}
+\caption{Phases of the Controller Synthesis}
 \label{fig:synthesis-flow}
@@
 experiments.\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}
-The current development branch of our toolbox is available in a public
-GitHub
-repository.\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}
+Our toolbox is available
+online.\footnote{\url{https://github.com/ssvlab/dsverifier/tree/master/toolbox-dssynth}}
 

### 2017-08-16 ase2017/paper.tex
tt font
eucal
font tweaks

@@
 \usepackage{pgfplots}
+\usepackage{inconsolata} % tt font
+\usepackage{eucal}
 
@@
 \scriptsize
-\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
+\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,basicstyle=\tt]
 >> num = [-0.06875 0 0];
@@
 \end{lstlisting}
-\vspace{-0.2cm}
-\caption{Synthesis of a digital controller for the physical plant defined in Eq.(\ref{equation_plant}) in MATLAB, with a fixed-point format  $\left\langle 8,8\right\rangle$}
+\caption{Synthesis of a digital controller for the physical plant
+defined in Eq.~(\ref{equation_plant}) with 
+fixed-point format $\left\langle 8,8\right\rangle$}
 \label{toolbox-usage}
@@
 \scriptsize
-\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
+\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,basicstyle=\tt]
 >> num = [-0.99832 0.09587 0.1926];
@@
 \scriptsize
-\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
+\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single, basicstyle=\tt]
 >> den = [1.069 -1.136 0.4849 -0.8704 0.5317]
@@
 \vspace{-0.2cm}
-\caption{Roots of the polynomial $D(z)$ given by Eq.~\ref{equation_general}.}
+\caption{Roots of the polynomial $D(z)$ given by Eq.~\ref{equation_general}}
 \label{roots-of-dz}

### 2017-08-16 ase2017/paper.tex
space

@@
 $A(z)$, while $y$ represents the synthesized stable digital controller,
-which is defined by Eq.(\ref{equation_controller}).
+which is defined by Eq.~(\ref{equation_controller}).
 %

### 2017-08-16 ase2017/paper.tex
font consistency

@@
    \&
-   \& \node[draw,rectangle,align=center] (KSAT) {Program \\ Search};
+   \& \node[draw,rectangle,align=center] (KSAT) { \sf Program \\ \sf Search};
    \& complexnode/.pic={
      \coordinate (AA);
-     \node[draw,rectangle,align=center] (AAV) at ([xshift=-1.5cm]AA.center) {Abstract\\Acceleration};
-     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm]AA.center) {Abstraction \\ Verifier};
+     \node[draw,rectangle,align=center] (AAV) at ([xshift=-1.5cm]AA.center) { \sf Abstract\\ \sf Acceleration};
+     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm]AA.center) { \sf Abstraction \\ \sf Verifier};
     }\\

### 2017-08-16 ase2017/paper.tex
fixed typos in the introduction section
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Control theory targets the construction of reliable systems by providing
-mathematical guarantees about the stability and the desired performance of
-closed-loop dynamics, where outputs of discrete plant $G(z)$ are fed back
+mathematical guarantees about the stability and the performance of
+closed-loop dynamics, where outputs of a discrete plant $G(z)$ are fed back
 and compared to a reference signal towards which a controller $C(z)$ should
@@
 state-space equations (difference or differential equations).  In this
-paper, we consider systems with a single input and a single output (SISO)
+paper, we consider systems with a single input and a single output (SISO),
 given either as transfer functions or state-space linear time-invariant
 (LTI) models.  LTI models are a common sub-class, and are frequently used in
-cyber-physical systems (e.g., in robotics, smart grids, power plants, and
+cyber-physical systems (e.g., in robotics, smart grids, power plants and
 avionics).  A discretized plant or a digital controller is, in general,
-given as follows when using a transfer function representation:
+given as follows when using the transfer function representation:
 %
@@
 
-In a state-space form, the behavior of a system is represented via a state
+In state-space form, the behavior of a system is represented via a state
 evolution equation $x(n+1)$ and an instantaneous output equation $y(n)$, as
@@
 There are existing toolboxes for MATLAB that provide functions and scripts
-to support design and implementation of digital
+to support the design and implementation of digital
 controllers~\cite{matlab-toolbox}.  In~particular, there is a MATLAB Toolbox
@@
 digital controllers.  Pessoa is based on approximate bisimulation, which
-allows control engineers to replace differential equations, describing a
-physical plant, by a respective finite-state machine.  However, Pessoa does
+allows control engineers to replace the differential equations (describing the
+physical plant) by a finite-state machine.  However, Pessoa does
 not take advantage of recent advances in bit-accurate verification of
@@
 stable and safe digital controller for such plants without switching the
-environment. Experimental results show that \tool is able to efficiently 
+environment. Experimental results show that the \tool is able to efficiently 
 synthesize stable and safe controllers for a set of intricate benchmarks taken 

### 2017-08-16 ase2017/paper.tex
fixed typos in section II
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 candidate solution to the full synthesis formula.  We pass this candidate
-solution to the validation phase, which checks whether it is a full solution
+solution to the validation phase, which checks whether it is a proper solution
 (i.e., satisfies the specification for all possible inputs).  If this is the
@@
 provided to the inductive synthesis phase in the form of a new
-counterexample, C-ex, that is added to the set of test inputs, and the loop
+counterexample, C-ex, which is added to the set of test inputs, and the loop
 iterates again.
 
-We use two different instantiations of the synthesiser
-in order to find stable and safe digital
-controllers. The two approaches differ in
-the manner in which they check the safety specification
-for all reachable states.
+We use two different instantiations of the synthesiser. 
+The two approaches differ in
+the manner in which they check the safety specification.
 
@@
 The first approach, presented in Fig.~\ref{fig:CEGIS-precision-increment}, 
-uses a multi-staged verification process. 
-It starts by devising a digital controller that stabilizes the model while remaining safe for a
+starts by devising a digital controller that stabilizes the model while remaining safe for a
 pre-selected time horizon ($k$) and a single initial state; then, it
@@
 completeness threshold, since the time horizon considered in abstract
-acceleration is infinite.  An additional preprocessing phase is used to
+acceleration is infinite.  An~additional preprocessing phase is used to
 compute a set of initial bounds on $K$ based on input constraints.  Note

### 2017-08-16 ase2017/paper.tex
fixed typos in section III
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %---------------------------------------------------
-\section{Synthesizing Digital Controllers with \tool}
+\section{Synthesizing Digital Controllers with the \tool}
 %---------------------------------------------------
@@
 
+\begin{figure*}[t]
+\centering
+\includegraphics[width=0.7\textwidth]{synthesis-flow.pdf}
+\caption{Phases of the Controller Synthesis}
+\label{fig:synthesis-flow}
+\end{figure*}
+
 The proposed synthesis methodology for closed-loop digital control
@@
 automated steps, as illustrated in Fig.~\ref{fig:synthesis-flow}.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=0.47\textwidth]{synthesis-flow.pdf}
-\caption{Phases of the Controller Synthesis}
-\label{fig:synthesis-flow}
-\end{figure}
 
@@
 user, i.e., the FWL format that defines the number of bits of the integer
-and fractional parts as well as the dynamic range inputs.  The result of the
-input given by the user is a specification of the physical plant.
+and fractional parts as well as the dynamic range inputs.  The input 
+provided by the user is a specification of the physical plant.
 
@@
 \texttt{CPROVER\_assume} intrinsic functions).  Our module is included in
-CBMC~5.7 and is available for
-download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}
+CBMC~5.8 and is available for
+download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.8.zip}}
 We further created a VirtualBox OVA image with our tool pre-installed,
@@
 The \tool performs the following automated steps
-to synthesize a given digital controller:
+to synthesize a digital controller for the given physical plant:
 %
@@
 (parse) step and calls our CEGIS engine as a back-end program synthesis tool
-to perform the automated synthesis;
+to perform the automated synthesis.
 %
 \item \textbf{Extraction}: obtains the ``.log'' file that is generated 
-after the synthesis phase and then checks the synthesized digital-controller.
+after the synthesis phase and then checks the synthesized digital controller.
 %
@@
 %---------------------------------------------------
-\subsection{\tool Features}
+%\subsection{\tool Features}
 %-----------------------------------------------
 
-The features of the \tool can be summarized as follows:
+%The features of the \tool can be summarized as follows:
 %
-\begin{itemize}
+%\begin{itemize}
 %
-\item \textbf{Representation}: the synthesis can be 
-performed for digital systems specified via 
-transfer function or as state-space models.
+%\item \textbf{Representation}: the synthesis can be 
+%performed for digital systems specified via 
+%transfer function or as state-space models.
 %
-\item \textbf{Fixed-Point Arithmetic}: the digital 
-controller is synthesized considering FWL effects, 
-using the given fixed-point numerical representation.
+%\item \textbf{Fixed-Point Arithmetic}: the digital 
+%controller is synthesized considering FWL effects, 
+%using the given fixed-point numerical representation.
 %
-\item \textbf{Interface}: the synthesis can be executed via command-line or
-graphical-user interface (GUI).  For the GUI application, the user can plot
-the step response to reproduce the stability in closed-loop of the
-synthesized digital controller.
+%\item \textbf{Interface}: the synthesis can be executed via command-line or
+%graphical-user interface (GUI).  For the GUI application, the user can plot
+%the step response to reproduce the stability in closed-loop of the
+%synthesized digital controller.
 %
-\end{itemize}
+%\end{itemize}
 
@@
 \texttt{tf} (for transfer function) or an \texttt{ss} (for state-space
-model) command (step $1$ of Fig.~\ref{fig:synthesis-flow}).  The \tool is
+model) command (Step $1$ of Fig.~\ref{fig:synthesis-flow}).  The \tool is
 called via the command line in MATLAB as
@@
 \texttt{fracBits} is the fractional part, \texttt{maxR} and \texttt{minR}
-are the maximum and minimum dynamic range, respectively (steps $2$ and
+are the maximum and minimum dynamic range, respectively (Steps $2$ and
 $3$ of Fig.~\ref{fig:synthesis-flow}).
@@
 
-To illustrate the usage of the \tool, Fig.~\ref{toolbox-usage} shows each
+Fig.~\ref{toolbox-usage} illustrates each
 step of the synthesis process for a physical plant described in
-Eq.~\eqref{equation_plant}, which represents a unmanned aerial vehicle
+Eq.~\eqref{equation_plant}, which represents an unmanned aerial vehicle
 (UAV) quadcopter system~\cite{bouabdallah}.  This physical plant is
@@
 
-In Fig.~\ref{toolbox-usage}, ``num'' represents $B(z)$ and ``den'' represent
+In Fig.~\ref{toolbox-usage}, ``num'' represents $B(z)$ and ``den'' represents
 $A(z)$, while $y$ represents the synthesized stable digital controller,

### 2017-08-16 ase2017/paper.tex
fixed typos in section IV
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %---------------------------------------------------
-\subsection{Benchmarks Description}
+\subsection{Benchmark Description}
 \label{benchmarks-description}
@@
 CTMS, DBLP:journals/tc/BessaIPCF17, DBLP:journals/dafes/BessaICF16}, which
-include physical plants for a unmanned aerial vehicle (UAV), a cruise
+include physical plants for an unmanned aerial vehicle (UAV), a cruise
 control system, a spring-mass damper, a satellite, a direct current (DC)
@@
 suspension, a magnitezed pointer, 1/4 car suspension, a computer tape
-driver, a flexible beam, a guidance system, a USCG cutter tampa, a
+driver, a flexible beam, a guidance system, a US Coast Guard cutter, a
 continuous stirred tank reactor, a voltage regulator, and an acrobot control
@@
 Intel Core i$7-2600$ $3.40$ GHz processor, with $24$ GB of RAM, running
-Ubuntu $64$-bits.
+Ubuntu $64$-bit.
 
@@
 that this set of benchmarks is still limited within the scope of this paper,
-and the performance may not be generalized to other benchmarks.  The median
-runtime for our benchmarks set is $124$\,s, and the average synthesis time
+and the performance may not generalize to other benchmarks.  The median
+runtime for our benchmarks is $124$\,s, and the average synthesis time
 amounts to $35.5$\,s for closed-loop control systems represented by
@@
 the DC motor plant.  We have applied this procedure to all synthesized
-controllers to confirm the reliability of our experimental results.
+controllers to validate our experimental results.
 %
@@
 %
-\noindent where,
+\noindent where
 %
@@
 Eq.~\eqref{ss-synth-feedback}) generated by the \tool also leads to a stable
-system, as sillustrated in Fig.~\ref{ss-step-response}.
+system, as illustrated in Fig.~\ref{ss-step-response}.
 %
@@
 The synthesized controllers are also confirmed to be safe outside of our model
-representation using MATLAB, which means that our results are reliable for control engineers. 
-In particular, given that the closed loop dynamics are convergent, the controller's safety can be checked by computing the initial state's infinity norm, {\it i.e.}, 
+representation using MATLAB, which means that our results are usable for control engineers. 
+In~particular, given that the closed loop dynamics are convergent, 
+the controller's safety can be checked by computing the initial state's infinity norm, i.e., 
 the product between $l_{\infty}$ norm of initial states ($\vert\vert{x_{0}}\vert\vert_{\infty}=\max{x_{0}}$) 
@@
 where $\bar{A}=A-BK$). This is a conservative safety check, which is based on a sufficient condition~\cite{toscano2013structured}. 
-An alternative (and less conservative) approach is to unfold the system dynamics up to a given depth, 
+An~alternative (but not conservative) approach is to unfold the system dynamics up to a given depth, 
 with the initial state equal to its maximum value, compute the system input and output via the feedback matrix, 
-and then check the states bounds.
+and then check the state bounds.
 

### 2017-08-16 ase2017/paper.tex
fixed typos in section V
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\renewcommand{\baselinestretch}{0.99}
+\renewcommand{\baselinestretch}{0.986}
 \newcommand\tool{{DSSynth Toolbox}\xspace}
@@
 digital controller are: $8$~bits for the integer part (including the sign
-bit) and $8$~bits for the fractional part.  We have run the \tool using
+bit) and $8$~bits for the fractional part.  We~have run the \tool using
 CEGIS with multi-staged verification (cf.~Section~\ref{sec:CEGIS}).  All
@@
 The \tool presents a practical application of CEGIS-based program synthesis.
-Tractable program synthesis in control engineering encourages the application
+Our results in control engineering encourages the application
 of this technique in other fields such as program repair or superoptimisation.
@@
 %
-As future work, the \tool will perform synthesis considering additional
-requirements (e.g., performance) and will be combined with the
+As future work, the \tool will perform synthesis considering performance
+requirements and will be combined with the
 DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to
-verify/validate further controller properties.
-We will also pursue the application of CEGIS to software
+verify/validate other controller properties.
+We will also pursue the application of CEGIS to further software
 engineering problems.

### 2017-08-17 ase2017/paper.tex
typo
tweak line breaks

@@
 The first approach, presented in Fig.~\ref{fig:CEGIS-precision-increment},
-starts by devising a digital controller that stabilizes the model while remaining safe for a
-pre-selected time horizon ($k$) and a single initial state; then, it
-employs a multi-staged verification process as follows:
-(i) The first verification stage ({\sc safety}) checks that the candidate
+starts by devising a digital controller that stabilizes the model while
+remaining safe for a pre-selected time horizon ($k$) and a single initial
+state; then, it employs a multi-staged verification process as follows:
+(i)~The first verification stage ({\sc safety}) checks that the candidate
 solution, which we synthesized to be safe for at least one initial
@@
 an unsafe state within $k$ steps.
-(ii) The second verification stage ({\sc precision})
+(ii)~The second verification stage ({\sc precision})
  restores soundness with respect to the plant precision
-by using interval arithmetic \cite{moore1966interval} to validate the 
+by using interval arithmetic~\cite{moore1966interval} to validate the 
 operations performed by the previous stage. 
-(iii) The third verification stage ({\sc complete}) checks that the current
+(iii)~The third verification stage ({\sc complete}) checks that the current
 $k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
@@
 The \tool presents a practical application of CEGIS-based program synthesis.
-Our results in control engineering encourages the application
+Our results in control engineering encourage the application
 of this technique in other fields such as program repair or superoptimisation.

### 2017-08-18 ase2017/paper.tex
nudge
improved step response graphs
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
-\documentclass[10pt,conference]{IEEEtran}
+\documentclass[conference]{IEEEtran}
 
@@
 \renewcommand{\baselinestretch}{0.986}
+\setlength{\belowcaptionskip}{-2.8 pt} 
 \newcommand\tool{{DSSynth Toolbox}\xspace}
@@
 the manner in which they check the safety specification.
-
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{figure}
-
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%
 The first approach, presented in Fig.~\ref{fig:CEGIS-precision-increment},
@@
 
-Instead of unfolding the dynamics, the second approach (illustrated in
+The second approach (illustrated in
 Fig.~\ref{fig:CEGARIS}) employs {\em abstract
@@
 %---------------------------------------------------
-\subsubsection{Command Line Version}
+\subsubsection{Command Line}
 %---------------------------------------------------
@@
 %---------------------------------------------------
-\subsubsection{MATLAB Application Version} 
+\subsubsection{MATLAB Application} 
 %---------------------------------------------------
@@
 
-For all evaluated benchmarks, the signal input range related to the control
-system is between $-1$ and $1$.  The implementation features used for
+For all evaluated benchmarks, the signal input range is between $-1$ and $1$.  
+The implementation features used for
 digital controller are: $8$~bits for the integer part (including the sign
@@
 \label{ss-synth-controller}
-\begin{split}
-x(n+1) &= A x(n) + B u(n)
-\\
-y(n) &= C x(n) + D u(n), 
-\end{split}\
+\begin{array}{c} 
+A = \left[\begin{array}{cc}-1.999909737361046&-1.000000000000000\\1&0\end{array}\right], \\
+B = \left [\begin{array}{c}4\\0\end{array}\right], \\
+C = \left [\begin{array}{cc}-1.756887232846049&-1.7494556607764090\end{array}\right], \\
+\quad D = \left [\begin{array}{c}9.8\end{array}\right].
+\end{array}
 \end{equation}
-%
-\noindent where
-%
-$$A = \left[\begin{array}{cc}-1.999909737361046&-1.000000000000000\\1&0\end{array}\right],$$
-$$B = \left [\begin{array}{c}4\\0\end{array}\right],$$
-$$C = \left [\begin{array}{cc}-1.756887232846049&-1.7494556607764090\end{array}\right],$$
-$$\quad D = \left [\begin{array}{c}9.8\end{array}\right].$$
 
@@
 \begin{split}
-K &= \left [\begin{array}{cc}-0.5898&-0.1914\end{array}\right]
+K &= \left [\begin{array}{cc}-0.5898&-0.1914\end{array}\right].
 \end{split}\
@@
 representation using MATLAB, which means that our results are usable for control engineers. 
-In~particular, given that the closed loop dynamics are convergent, 
+Given that the closed loop dynamics are convergent, 
 the controller's safety can be checked by computing the initial state's infinity norm, i.e., 
@@
 The \tool can automatically synthesize stable and safe digital controllers
-for intricate dynamic physical plants, represented in MATLAB either as a
+for dynamic physical plants, represented in MATLAB either as a
 transfer function or a state-space equation.  The \tool is the first fully

### 2017-08-18 ase2017/plot_ss.m

@@ -11,9 +11,7 @@ D_= D;
 
 sys = ss(A,B,C,D, 0.002);
 
-roots = eig(F);
-
 dstep(A_,B_,C_,D_)
 
-set(findall(gcf,'-property','FontSize'),'FontSize',22)
+set(findall(gcf,'-property','LineWidth'),'LineWidth',2)
 

### 2017-08-18 ase2017/plot_step_response.m

@@ -9,4 +9,4 @@ num_cl = cell2mat(syscl.Numerator);
 den_cl = cell2mat(syscl.Denominator);
 
 dstep(num_cl,den_cl)
-set(findall(gcf,'-property','FontSize'),'FontSize',22)
+set(findall(gcf,'-property','LineWidth'),'LineWidth',2)

### 2017-08-18 ase2017/plot_tf.m

@@ -7,4 +7,4 @@ num_cl = cell2mat(syscl.Numerator);
 den_cl = cell2mat(syscl.Denominator);
 
 dstep(num_cl,den_cl)
-set(findall(gcf,'-property','FontSize'),'FontSize',22)
+set(findall(gcf,'-property','LineWidth'),'LineWidth',2)

### 2017-08-21 ase2017/paper.tex
captions

@@
 \includegraphics[width=0.4\textwidth]{closedloopseries.pdf}
-\caption{Typical Closed-loop Control System}
+\caption{Typical closed-loop control system}
 \label{fig:typical-control-system}
@@
 \includegraphics[width=0.7\textwidth]{synthesis-flow.pdf}
-\caption{Phases of the Controller Synthesis}
+\caption{Phases of the controller synthesis}
 \label{fig:synthesis-flow}
@@
   \includegraphics[width=0.5\textwidth]{tf-step-response.eps}
-  \caption{Step response for the Eq.~\eqref{tf-synth-controller} describing a stable system for the DC motor plant.}
+  \caption{Step response for the Eq.~\eqref{tf-synth-controller} describing a stable system for the DC motor plant}
   \label{tf-step-response}
@@
   \includegraphics[width=0.5\textwidth]{ss-step-response.eps}
-  \caption{Step response for the Eq.~\eqref{ss-synth-controller} describing a stable system for the pendulum plant.}
+  \caption{Step response for the Eq.~\eqref{ss-synth-controller} describing a stable system for the pendulum plant}
   \label{ss-step-response}

### 2017-08-21 ase2017/paper.tex
nudge

@@
 Fig.~\ref{fig:typical-control-system}, is described by
-Eq.~\ref{equation_general} as follows
+Eq.~\ref{equation_general} as follows:
 %

### 2017-08-21 ase2017/paper.tex
articles

@@
 %as a validation procedure, which means that our results are reliable for control engineers.
-The synthesized controllers are also confirmed to be safe outside of our model
-representation using MATLAB, which means that our results are usable for control engineers. 
-Given that the closed loop dynamics are convergent, 
-the controller's safety can be checked by computing the initial state's infinity norm, i.e., 
-the product between $l_{\infty}$ norm of initial states ($\vert\vert{x_{0}}\vert\vert_{\infty}=\max{x_{0}}$) 
-and the $l_{1}$ norm of ($\vert\vert{\bar{A}}\vert\vert_{1}=\max\limits_{j}{\sum\limits_{i=1}^{m} \vert \bar{a}_{ij} \vert}$, 
-where $\bar{A}=A-BK$). This is a conservative safety check, which is based on a sufficient condition~\cite{toscano2013structured}. 
-An~alternative (but not conservative) approach is to unfold the system dynamics up to a given depth, 
-with the initial state equal to its maximum value, compute the system input and output via the feedback matrix, 
-and then check the state bounds.
+
+The synthesized controllers are also confirmed to be safe outside of our
+model representation using MATLAB, which means that our results are usable
+for control engineers.  Given that the closed loop dynamics are convergent,
+the controller's safety can be checked by computing the initial state's
+infinity norm, i.e., the product between the $l_{\infty}$ norm of the
+initial states ($\vert\vert{x_{0}}\vert\vert_{\infty}=\max{x_{0}}$) and the
+$l_{1}$ norm of
+($\vert\vert{\bar{A}}\vert\vert_{1}=\max\limits_{j}{\sum\limits_{i=1}^{m}
+\vert \bar{a}_{ij} \vert}$, where $\bar{A}=A-BK$).  This is a conservative
+safety check, which is based on a sufficient
+condition~\cite{toscano2013structured}.  An~alternative (but not
+conservative) approach is to unfold the system dynamics up to a given depth,
+with the initial state equal to its maximum value, compute the system input
+and output via the feedback matrix, and then check the state bounds.
 

### 2017-08-23 ase2017/paper.tex
added robust control toolbox

@@
 the Control System Tuner is unable to consider FWL effects during controller
-synthesis.  To the best of our knowledge, there is no MATLAB toolbox able to
+synthesis. In addition, there is another toolbox called 
+\emph{Robust Control Toolbox}~\cite{robusttool}, which computes a  
+stabilizing $H_{2}$ optimal controller $K$ for a partitioned LTI plant $P$. 
+The main output provided by this toolbox is the controller synthesized, and also,
+the closed-loop system that combines the plant and the controller synthesized. 
+However, the FWL effects is not taking account as well.
+To the best of our knowledge, there is no MATLAB toolbox able to
 perform digital controller synthesis that considers the complete range of
@@
 and the average synthesis time amounts to $35.5$\,s for closed-loop control 
-systems represented by state-space equations, while for transfer functions, the average synthesis
-time amounts to $123.6$\,s.
+systems represented by state-space equations, while for transfer functions, 
+the average synthesis time amounts to $123.6$\,s.
 

### 2017-08-30 ase2017/paper.tex
added text about experiments to be evaluated
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2017-08-21 ase2017/paper.tex
@@
 servo motor, a helicopter, the inverted pendulum, a pendulum, magnetic
-suspension, a magnitezed pointer, 1/4 car suspension, a computer tape
+suspension, a magnetized pointer, 1/4 car suspension, a computer tape
 driver, a flexible beam, a guidance system, a US Coast Guard cutter, a

### 2017-10-10 TACAS2018/paper.tex
Tacas2018

%\documentclass[sigconf]{acmart}
\documentclass[sigconf]{llncs}

\usepackage{microtype}
\usepackage{graphicx}
\usepackage{color}
\usepackage{amssymb}
\usepackage{amsmath}
%\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{framed}
\usepackage{listings}
\usepackage{algorithm,algpseudocode}
\usepackage{epstopdf}
\usepackage{pifont}
\usepackage{todonotes}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usetikzlibrary{patterns}
\usepackage{url}

\newcommand{\jrronly}[1]{{}}
\newcommand{\mat}[1]{\boldsymbol{#1}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
%\newtheorem{theorem}{Theorem}
%\newtheorem{corollary}{Corollary}
%\newtheorem{proof}{Proof}

\newcommand\tool{{\sf DSSynth}}

\begin{document}

\title{Formal Synthesis of Digital Controllers for Observable Continuous
Plants with Transient Performance Specifications}

\author{Dario Cattaruzza, Alessandro Abate, Daniel Kroening}%\email{alessandro.abate@cs.ox.ac.uk}
%\email{dario.cattaruzza@cs.ox.ac.uk}
%\author{Cristina David}\email{cristina.david@cs.ox.ac.uk}
%\email{kroening@cs.ox.ac.uk}

%\end{frontmatter}

\maketitle

%\begin{keyword}                   
%Digital Control; A/D converters; Control System Synthesis; Safety Analysis; Quantization Errors; Observer-based Controller. Sampling.
%\end{keyword}

\begin{abstract} 
%
We present a sound and automated approach to synthesize safe, digital
observer-based controllers for physical plants represented as linear,
time-invariant models.  Models are given as dynamical equations with inputs,
evolving over a continuous state space and accounting for errors caused by
the digitization effects of the controller.  We use multi-staged
counterexample-guided inductive synthesis (CEGIS) with four phases: 1)~We
create a modular abstraction of the model and feed it to a two stage synthesiser
to reduce computational cost.  2)~We use the coarsest level of
abstraction to synthesise an approximate observer-based controller using
a Bounded Model Checker(BMC), and then  3)~We feed the imprecise result to
a second synthesiser based on eigendecomposition which uses a more precise
abstraction to refine the result.
The BMC is computationally more expensive, but able to reason
about more complex models, whereas the eigensolver is fast but requires a
reference candidate solution close to the desired result to guide the synthesis.
The intuition is that because our solutions form sets of connected spaces, 
the desired solution lies in the vicinity of a [possibly] unsuitable candidate
found by the first synthesiser.  4)~The refined candidate solution is still
unsound.  Safety and other design properties are then verified using continuous
and discrete-time reachability analysis tools.  If either verification
fails, a counterexample is provided to the modelling phase, which will refine
the abstraction based on the type of counter-example and feed it back to
the synthesisers.  The process iterates until a safe controller is obtained.
We demonstrate the practical value of this approach by automatically
synthesizing safe observer-based controllers for physical plant models from
the digital control literature.
%
\end{abstract}

\section{Introduction}

Modern implementations of embedded control systems have proliferated with
the availability of low-cost devices that can perform highly non-trivial
control tasks, with significant impact in numerous application areas such as
life sciences, environmental control and robotics~\cite{astrom1997computer,Franklin15}.  Correct synthesis is non-trivial, even in cases with
restricted dynamics.  We examine the case of Linear Time Invariant (LTI)
Models, for which the synthesis of controllers is well understood.  However,
the use of digital control architectures adds new challenges caused by
artifacts specific to digital control, such as the effects of
finite-precision arithmetic, time discretization and quantization errors
introduced by A/D and D/A conversion.

While research on digital control is well
developed~\cite{astrom1997computer}, automated and sound control synthesis
is challenging, particularly when the synthesis objective goes beyond
classical stability.  Recent work~\cite{abate2017automated} described a
method for synthesising safe digital stabilizing controllers for fully
observable LTI plants.  This work differs from the vast majority of existing
approaches in that it explores the continuous space of the system to
synthesise correct by construction minimal digital controllers.  Contrary to
LTL models that require thousands of states and elaborate algorithms to
implement, these PID-like controllers are represented by a few parameters
and only require a few lines of code, thus reducing the implementation cost
and execution time while remaining resilient to the effects of digitilazation.
However,~\cite{abate2017automated}~is still restricted to fully observed
systems (i.e. where all the states are known) modelled in discrete time,
and furthemore explores only a limited set of properties that engineers
are interested in.

In this paper we build on the ideas presented in~\cite{abate2017automated}
and develop a new technique that addresses most of these limitations. 
By~combining state-of-the-art synthesis and verification engines we
automatically generate digital observer controllers for a given continuous
plant model that are correct by construction.  This approach delivers a high
degree of automation, promises to reduce the cost and time of development of
digital control dramatically, and requires considerably less expertise than
a-posteriori verification.  Specifically, we synthesize stable,
software-implemented embedded controllers along with a model of a physical
plant (observer).  Due to the complexity of such closed-loop systems, in
this work we focus on linear models with known configurations, and perform
parametric synthesis of controllers meeting a number of properties that
define their desired behaviour.

We perform digital control synthesis over a hybrid model, where the plant
exhibits continuous behavior whereas the controller operates in discrete
time and over a quantized domain.  Our model evaluates the effects of the
quantizers (A/D and D/A converters) and of time discretization, as well as
representation errors introduced by modelling artifacts such as an
observer~\cite{astrom1997computer} in a finite precision domain, while
reasoning about high level properties such as stability, robustness, safety,
and response time, which define the behaviour of the system.  In particular,
safety requirements are frequently overlooked in conventional feedback
control synthesis, but play an important role in systems engineering.

Using state of the art verifiers, we evaluate these models against
automatically synthesised controllers using CEGIS-based synsthesis that
incorporate the above mentioned artifacts in different models of
Single-Input/Single-Output (SISO) systems.  We offer a multi-tiered approach
that exploits different aspects of the problem at each stage.

The coarse synthesiser uses a low resolution discretized model of a 
transformation of the original model. Furthermore, it only looks initially at
static properties  of the system. This largely reduces the complexity of
the problem, enabling the synthesiser to offer fast response times. If any 
of these parameters is inadequate, the refinement loop will supply a better
abstraction to obtain a feasible answer.
Due to either numerical imprecision or overapproximations, the candidate
solution presented by the first synthesiser will likely not meet the spec. A 
second synthesiser, with a much more precise refinement including a 
mapping between the real and transformed spaces will create a candidate
solution that is more adequate to the real model. This second stage uses
perturbation analysis and therefore requires an initial solution to operate.
If the second synthesiser is unable to find a candidate solution, it will cue
the modeller to supply a finer abstraction to the coarse synthesiser which
will in turn provide a better candiate to the second stage.
The combined synthesisers are thus capable of reasoning about complex
models with high computational efficiency due to their modularity.

%The synthesiser uses a discrete time model that relates to the sampling
%time.  It begins with a very simple abstraction of the real system which
%only considers the static properties of the model.  It~also uses a very low
%precision bit vector representation of the real dynamics in order to
%minimise synthesis time.  
A candidate solution is then passed to a set of verifiers which will
evaluate the synthesised controller over an even more precise
abstraction of the concrete domain in both discrete and continuous
space/time.  This stage uses abstraction refinement when needed to ensure
that rejected candidates are not being discarded due to the
over-approximation.  The nature of the counterexamples varies depending on
the following conditions:
%
\begin{enumerate}
%
\item Initially, we look for possible errors caused by the restricted domain
of the synthesisers (e.g., overflows and rounding).  These will typically 
manifest in the static properties of the system. If an error is found, the
modeller is signalled to increase the precision of the synthesisers.
%
\item Next we explore the nature of the discrete-time progression to mark
a counterexample that relates to the progression of the system. If such a
counterexample exists, we indicate its initial conditions and time horizon,
thus instructing the synthesiser to refine its abstraction with respect to the
set of initial states and number of iterations. 
%
\item Continuous time analysis indicates the need for decreasing the
sampling time due to continuous excursions outside the safety region in
between samples.  This changes the problem statement of the synthesiser to a
new discrete-time model.
%
\item A final condition arises when a candidate solution cannot be found,
thus requiring higher precision of the abstraction numerical representation. 
We initially consider the plant representation to be too conservative and
may eventually increase the controller FWL specification when no controller
can be found for a given precision.
%
\end{enumerate}

We provide experimental results showing that our approach is able to
efficiently synthesize safe controllers for a set of physical
plant models taken from the digital control literature.

In summary, this paper makes the following original contributions.
%
\begin{enumerate}

\item We automatically generate \emph{correct-by-construction} digital
  state-feedback observer controllers that guarantee a given safety property
  alongside stability and response time specifications.  We note that
  observers are much more complex and difficult to synthesise than standard
  full-state feedback controllers.
%
\item  Our synthesis addresses challenges created by digitalization errors
 such as quantization, and time discretization as well as delays in the
 sampling and processing times which introduce control errors in real
 implementations.
 \item we present a model for soundly evaluating reachability in a combined 
 continuous-discrete time/space. Sound tools for continuous time reachability 
 are scarce and to the authors' knowledge no tool provides a model that 
 combines both. 
%
\item We develop a model for inductive synthesis that combines CEGIS with
abstraction refinement in order to minimize the synthesis cost. In particular
we explore the idea of a multi-tiered model where different verification, 
synthesis and modelling tools/modules explore different parts of the problem
to deliver an optimal response.
%
\end{enumerate}

%-------------------------------
\section{Related Work}
\label{sec:relw}
%-------------------------------

\textbf{CEGIS --}
Program synthesis is the problem of computing correct-by-design programs
from high-level specifications.  Algorithms for this problem have made
substantial progress in recent years, for instance~\cite{itzhaky2010simple}
to inductively synthesize invariants for the generation of desired programs.

Program synthesizers are an ideal fit for the synthesis of digital
controllers, since the semantics of programs capture the effects of
finite-precision arithmetic precisely. 
In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS for the
synthesis of switching controllers for stabilizing continuous-time plants
with polynomial dynamics.  The work extends to affine systems, but is
limited by the capacity of the state-of-the-art SMT solvers for solving
linear arithmetic.  Since this approach uses switching models instead of
linear dynamics for the digital controller, it avoids problems related to
finite precision arithmetic, but potentially suffers from state-space
explosion.  Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same
authors use a CEGIS-based approach for synthesizing continuous-time
switching controllers that guarantee \emph{reach-while-stay} properties of
closed-loop systems, i.e., properties that specify a set of goal states and
safe states (constrained reachability).  This solution is based on
synthesizing control Lyapunov functions for switched systems that yield
switching controllers with a guaranteed minimum dwell time in each mode. 
However, both approaches are unsuitable for the kind of control we seek to
synthesize.

The work in~\cite{hscc-paper} synthesizes stabilizing controllers for
continuous plants given as transfer functions by exploiting bit-accurate
verification of software-implemented digital controllers~\cite{Bessa16}. 
While this work also uses CEGIS, the approach is restricted to digital
controllers for stable closed-loop systems given as transfer function
models: this results in a static check on their coefficients.  By contrast,
in the current paper we consider a state-space representation of the
physical system, which requires ensuring the specification over actual
traces of the model, alongside the numerical soundness required by the
effects of discretisation and finite-precision errors.  A state-space model
has known advantages over the transfer function
representation~\cite{Franklin15}: it naturally generalizes to multivariate
systems (i.e., with multiple inputs and outputs); and it allows synthesis of
control systems with guarantees on the internal dynamics, e.g., to
synthesize controllers that make the closed-loop system \emph{safe}.  Our
work focuses on the \emph{safety} of internal states, which is usually
overlooked in the literature.  Moreover, our work integrates an
abstraction/refinement (CEGAR) step inside the main CEGIS loop.

The tool Pessoa~\cite{mazo2010pessoa} synthesizes correct-by-design embedded
control software in a Matlab toolbox.  It is based on the abstraction of a
physical system to an equivalent finite-state machine and on the
verification of reachability properties on it.  Based on this safety
specification, \mbox{Pessoa} can synthesize embedded controller software for
a range of properties.  The embedded controller software can be more
complicated than the state-feedback control we synthesize, and the
properties available cover more detail.  However, relying on state-space
discretization \mbox{Pessoa} is likely to incur in scalability limitations. 
Along this research line, \cite{Anta2010,liu16} studies the synthesis of
digital controllers for continuous dynamics, and \cite{zamani2014} extends
the approach to the recent setup of Network Control Systems.

\textbf{Discretization Effects --}
The classical approach to control synthesis has often disregarded
digitalization effects, whereas more recently modern techniques have focused
on different aspects of discretization, including delayed
response~\cite{Duggirala2015} and finite word length (FWL) semantics, with
the goal either to verify (e.g.,~\cite{daes20161}) or to optimize
(e.g.,~\cite{oudjida2014design}) given implementations.

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system, while the second relates to rounding and
saturation errors during computation.  In~\cite{fialho1994stability}, a
stability measure based on the error of the digital dynamics ensures that
the deviation introduced by FWL does not make the digital system unstable. 
A~more recent approach~\cite{DBLP:journals/automatica/WuLCC09} uses
$\mu$-calculus to directly model the digital controller so that the selected
parameters are stable by design.  The analyses
in~\cite{DBLP:conf/hybrid/RouxJG15,DBLP:conf/hybrid/WangGRJF16} rely on an
invariant computation on the discrete system dynamics using Semi-Definite
Programming (SDP).  While the former uses bounded-input and bounded-output
(BIBO) properties to determine stability, the latter uses Lyapunov-based
quadratic invariants.  In both cases, the SDP solver uses floating-point
arithmetic and soundness is checked by bounding the error.  An alternative
is~\cite{park2016scalable}, where the verification of given control code is
performed against a known model by extracting an LTI model of the code by
symbolic execution: to account for rounding errors, an upper bound is
introduced in the verification phase.  The work in
\cite{picasso2003stabilization} introduces invariant sets as a mechanism to
bound the quantization error effect on stabilization as an invariant set
that always converges toward the controllable set.  Similarly,
\cite{liberzon2003hybrid} evaluates the quantization error dynamics and
bounds its trajectory to a known region over a finite time period.  This
technique works for both linear and non-linear systems.

%-------------------------------
\section{Preliminaries}
\label{sec:preliminaries}
%-------------------------------

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Model Semantics}\label{sec:model_semantics}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

The traces of the model starting from an initial set $X_0\subseteq \mathbb{R}^p$, 
with inputs restricted to $U \subseteq \mathbb{R}^q$, are sequences 
$ \vec{x}_0 \xrightarrow{\vec{u}_0} \vec{x}_1 \xrightarrow{\vec{u}_1} \vec{x}_2 \xrightarrow{\vec{u}_2} \ldots $, 
%
where $ \vec{x}_0 \in X_0$ and $\forall k\geq 0, \vec{x}_{k+1} = \tau(\vec{x}_k,\vec{u}_k) $, 
where 
%
\begin{equation}\label{equ:reachtraj}
\tau(\vec{x}_k,\vec{u}_k) = 
\big( \mat{A}\vec{x}_k +
\mat{B}\vec{u}_k \mid \mat{G}\vec{x}_k \leq \vec{h} \wedge \vec{u}_k \in U \big) \;. 
\end{equation}

We extend the notation above to convex sets of initial conditions and inputs ($X_0$ and $U$), 
and write $\tau(X_0,U)$ to denote the set of states $\{\vec{x} \mid \vec{x}_0 \in
X_0 \wedge \vec{u} \in U \wedge \vec{x} = \tau(\vec{x}_0,\vec{u})\}$
reached from $X_0$ by $\tau$ in one step. 
%
We furthermore write $\tau^n(X_0,U)$ to denote the set of states reached from
$X_0$ via $\tau$ in $n$ steps (\emph{$n$-reach set}), i.e.\ for $n\geq 1$
%
\begin{align}\label{equ:reachset}
\tau^n(X_0,U) = \{\vec{x}_n \mid &\vec{x}_0 \in X_0 \wedge \forall k\in [0,n-1]\nonumber\\ 
 &\vec{u}_{k} \in U \wedge \vec{x}_{k+1}=\tau(\vec{x}_{k},\vec{u}_{k}) \} \;. 
\end{align}
%
Since the transformations $\mat{A}$ and $\mat{B}$ are linear and
vector sums preserve convexity, the sets $X_n = \tau^n(X_0,U)$ are also
convex.

We define the \emph{$n$-reach tube} 
\begin{equation}\label{equ:reachtube}
\hat{X}_n=\hat{\tau}^n(X_0,U)=\bigcup_{k\in[0,n]} \tau^k(X_0,U)
\end{equation}
as the union of the reachable sets over $n$ iterations.
%
Moreover, $\hat{X} 
=\bigcup_{n\geq 0} \tau^n(X_0,U)$ 
extends the previous notion over an 
unbounded time horizon.

%-------------------------------
\subsection{Overapproximating continuous time dynamics using discrete models}
\label{sec:cont_aa}
%-------------------------------

Thus far we wave discussed the Abstract Accelertion of Discrete Time
systems.  However, our plant models derive from the discretization of
continuous time systems.  We therefore seek to establish a sound
overapproximation which does not only encompass the selected discretization,
but any chosen discretization in the time domain.

A dynamical system is a system in which a function describes the progression
of a state over time.  In a continuous domain with linear dynamics, it is
described by a first order Ordinary Differential Equation (ODE).
\begin{equation}
\dot{x}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)% +\vec{w}(t)
\label{eq:dynamical}
\end{equation}

%where $\vec{w}$  is a continuous zero-mean white noise source with
%covariance $N ( 0 , Q )$ 
Furthermore, a control system may have a derived
output that is a linear combination of its states and inputs, which may
restricts the observability of the statespace from the output space.
\begin{equation}
\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)
\end{equation}

Discretization of a continuous dynamical system turns the ODE into a
difference equation, assuming zero-order hold for the input $\vec{u}$
%and continuous integration for the noise $\vec{w}$,
to
\begin{align}
\label{eq:discretization}
\vec{x}_{k+1} &= \mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\% + \vec{w}_k\\
y_k &= \mat{C}_d \vec{x}_ k + \mat{D}_d \vec{u}_ k 
\end{align}
%with covariance for $\vec{w}_k$, $N ( 0 , Q_d )$
where
\begin{align}
\label{eq:discretize}
\mat{A}_d &= e^{\mat{A} T_s} = \mathcal{L}^{-1} { ( s \mat{I} - \mat{A} )^{-1} }_{t = T_s}\\
\mat{B}_d &= \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B} = \mat{A}^{-1} ( \mat{A}_d - \mat{I} ) \mat{B}\\
\mat{C}_d &= \mat{C}\\
\mat{D}_d &= \mat{D}
%\\Q_d &= \int_{t = 0}^{T_s} e^{\mat{A} t} Q e^{\mat{A}^T t} dt
\end{align}
and $T_s$ is the sample time. Then
\begin{align*}
x(kT_s)=x_k \text{ and } y(kT_s) = y_k, \forall k
\end{align*}

 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsubsection{Discrete dynamics using reals for systems without inputs}\label{sec:real_discrete_no_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \begin{theorem}
 Given $\dot{\vec{x}}=\mat{A}\vec{x}$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, the expression
 \begin{align}
 \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x}_0\\
 \mat{A}_{T}&= \mat{S}
 \left [ \begin{array}{cccc}
 e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(1)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
\vdots & & \ddots & \vdots \\
0 & \cdots & 0  &e^{T\lambda_i} \\
\end{array} \right ]
 \mat{S}^{-1}
 \label{eq:continuous_tube_dyn}\\
 &\text{where } s_i=\left\{\begin{array}{cc}1&gm(\lambda_i)>1\\0&gm(\lambda_i)=1\end{array}\right.,\nonumber
 \end{align}
$\lambda_i \in \mat{J}$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.  $\vec{x}_T$ is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}$ at time t=T.
 \end{theorem}
 \begin{corollary}
 If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x} : k \in (0,\infty)$ is a witness of the system at time $t=kT_d$.
 \end{corollary}
% \begin{proof}
% Let us recall equation \ref{eq:discretize}. The discrete representation of the system dynamics discretised with sample time $T_1$ is ruled by the formula
% $\mat{A}_1 = e^{\mat{A} T_1}$. From matrix theory, we have 
%\begin{align}
% e^{\mat{A}}&=\sum_{k=0}^\infty \frac{1}{k!}\mat{A}^k
%\end{align} 
%\begin{align} 
% e^{\mat{S}\mat{J}\mat{S}^{-1}}&=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{S}\mat{J}\mat{S}^{-1}\right)^k
% =\mat{S} \left (\sum_{k=0}^\infty \frac{1}{k!}\mat{J}^k\right) \mat{S}^{-1}\nonumber\\
% &=\mat{S}e^{\mat{J}}\mat{S}^{-1}
%\end{align} 
%\begin{equation}
%\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \Rightarrow \vec{A}_1 = \mat{S}\mat{J}_1\mat{S}^{-1}= \mat{S}e^{\mat{J} T_1}\mat{S}^{-1}.
% \end{equation}
% 
% Let $\mat{J}$ be a diagonal matrix, such that 
% $${\lambda_1}_i=e^{\lambda_i T_1}, \forall \lambda_i \in \mat{J}.$$
% Let us now take a different sample rate $T_2$, such that 
% $${\lambda_2}_i=e^{\lambda_i T_2}, \forall \lambda_i \in \mat{J}.$$
% We can then say that 
% \begin{equation}
% {\lambda_2}_i=e^{\lambda_i T_1 \frac{T_2}{T_1}}={\lambda_1}_i^{\frac{T_2}{T_1}} \Rightarrow A_2=A_1^{\frac{T_2}{T_1}}.
% \end{equation}
% This proves the theorem for $gm(\lambda_i)=1$.
% We now note that given an exponentiated Jordan form with geometric multiplicity, the upper diagonal terms can be
% referenced to the original eigenvalues modified by the sampling rate.
%  Let $\mat{J}\in \mathbb{R}^{p \times p}$ be a Jordan Canonical matrix.
% Then
%\begin{align}
% \mat{J}_1&=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{J}T_1\right)^k=\sum_{k=0}^\infty \frac{1}{k!} \left [ \begin{array}{cccc}
% \lambda_i^k  & \binom{k}{1}  \lambda^{k-1} & \hdots  & \binom{k}{p-1} \lambda_i^{k-p+1} \\
%& \lambda_i^k  & \binom{k}{1}  \lambda_i^{k-1} & \vdots \\
%\vdots & \ddots & \ddots & \vdots \\
%& &  &\lambda_i^k \\
%\end{array} \right ] T_1^k
%\end{align}
%The eigenvalues remain the same as in the diagonal case, but the upper triangular terms are of the form:
%\begin{align}
%\forall j>i, c_{ij}&=\sum_{k=j-i}^\infty \frac{1}{k!}\binom{k}{j-i} \lambda_i^{k-(j-i)}T_1^k\\
%&=\frac{1}{(j-i)!}\sum_{k=j-i}^\infty \frac{1}{(k-(j-i))!} \lambda_i^{k-(j-i)}T_1^k\nonumber\\
%&=\frac{T_1^{j-i}e^{\lambda_i T_1}}{(j-i)!}\nonumber
%\end{align}
%which completes the proof for $gm(\lambda_i)>1$.
%\end{proof}

 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsubsection{Discrete dynamics using reals for systems with parametric inputs}\label{sec:real_discrete_param_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\begin{theorem}
The expression
 \begin{align}
 \vec{x}_T&=\vec{x}(t=T)=\mat{A}^{-1}\vec{x}_T'\nonumber\\
\vec{x}_T'&=\mat{A}\mat{A}_T\vec{x}_0 + (\mat{I}-\mat{A}_T)\mat{B}\vec{u} : \forall t \leq T,\ \vec{u}(t)=\vec{u} 
 \end{align}
 with $\mat{A}_T$ as per \eqref{eq:continuous_tube_dyn} is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$.
 \end{theorem}
 \begin{corollary}
 If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}+(\mat{I}-\mat{A}_d^k\mat{B}\vec{u}) : k \in (0,\infty)$ is a witness of the system at time $kT_d$.
 \end{corollary}
% \begin{proof}
% We begin by expanding the equation
% \begin{align}
% \vec{x}_T&=\mat{A}^{-1}\vec{x}_T'\nonumber\\
% &=\mat{A}_T\vec{x}_0 + \mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}\vec{u}\nonumber\\
% &= \mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u}
% \end{align}
% where $\mat{A}_T=e^{\mat{A}T}$ and $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$ correspond to $\mat{A}_d$ and $\mat{B}_d$ in equation \eqref{eq:discretize}
% \end{proof}

 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsubsection{Discrete dynamics using reals for systems with discrete time feedback inputs}\label{sec:real_discrete_feedback_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

The final case we analyse here is that of hybrid time systems, where the
plant dynamics evolve in continuous time while the feedback dynamics evolve
in discrete time.

\begin{theorem}
The expression
 \begin{align}
 \vec{x}_{t} &= (\mat{A}_{t-kT_s}-\mat{B}_{t-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
 \label{eq:cyber_feedback}
 \end{align}
 with $\mat{A}_t, \mat{B}_t$ as per \eqref{eq:continuous_tube_dyn} and $\mat{A}_d, \mat{B}_d$ as per equation \eqref{eq:discretize} is a witness of the system
 \begin{align}
 \dot{\vec{x}}_{t} &= \mat{A}\vec{x}+\mat{B}\vec{u}_t\nonumber\\
 \vec{u}_t&=\mat{K}\vec{x}_k  \mid  kT_s \leq t < (k+1)T_s
 \end{align}
 \end{theorem}

%\begin{proof}
%Let $\mat{K}$ be a feedback controller such that $\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$. Let the output of
%the feedback system be a zero order holder such that $\vec{u}(t+kT_s)=\vec{u}(kT_s) : 0 \leq t < T_s$.
%The closed loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
%\begin{equation}
%\vec{x}_{k,t}=\mat{A}_t\vec{x}_k-\mat{B}_t\mat{K}\vec{x}_k = (\mat{A}_t-\mat{B}_t\mat{K})\vec{x}_k : 0 \leq t < T_s
%\end{equation}
%We further explore the dynamics across discrete time boundaries. Let $\mat{A}_d=\mat{A}_{T_s}$ and $\mat{B}_d=\mat{B}_{T_s}$
%\begin{align}
%\vec{x}_{k}&=\vec{x}_{k-1,T_s}= (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}\\
%\vec{x}_{k,T_s} &= (\mat{A}_d-\mat{B}_d\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}
%\end{align}
%which accelerating results becomes
%\begin{align}
%\label{eq:feedback_sampled_cont}
%\vec{x}_{k} &= (\mat{A}_d-\mat{B}_d\mat{K}) ^k\vec{x}_0\\
%\vec{x}_{t} &= (\mat{A}_{t-kT_s}-\mat{B}_{t-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
%\label{eq:feedback_cont}
%\end{align}
%\end{proof}

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsubsection{Time delay on discrete time feedback systems} \label{sec:delay}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

A common ocurrence in digital systems is that they do not necessarily
satisfy the real-time specifications.  Delays due to processing time,
communication lines, or other mechanisms will cause disturbances in the
control loop.  In our model these delays are all deferred to the ZOH, i.e.,
we presume that everything that happens in the digital world takes place at
the sampling instance $t$ and the output of the result is delayed at the DAC
when it is fed back into the real world.  We~will also presume that this
delay is much smaller than the sampling time.

Let us look at equations \eqref{eq:feedback_sampled_cont} and
\eqref{eq:feedback_cont}.  When we introduce an arbitrary delay $T_d$ where
$t_d=T_d$ and $t_s=T_s-T_d$ we obtain:
%
\begin{align}
\vec{x}_{k} &=\mat{A}_{t_s}(\mat{A}_{t_d}\vec{x}_{k-1}-\mat{B}_{t_d}\mat{K}\vec{x}_{k-2})-\mat{B}\mat{K}\vec{x}_{k-1}\nonumber\\
&=  (\mat{A}_{T_s}-\mat{B}_{t_s}\mat{K})\vec{x}_{k-1}-\mat{A}_{t_s}\mat{B}_{t_d}\mat{K}\vec{x}_{k-2}
\label{eq:delay_cont}
\end{align}
%
Differentiating with the expected progression without delay, we get a delay
error:
%
\begin{align}
{\vec{x}_e}_{k}=&(\mat{B}_{T_s}-\mat{B}_{t_s})\mat{K}\vec{x}_{k-1}-\mat{A}_{t_s}\mat{B}_{t_d}\mat{K}\vec{x}_{k-2}\nonumber\\
=&(\mat{B}_{T_s}-\mat{B}_{t_s})\vec{u}_{k}-\mat{A}_{t_s}\mat{B}_{t_d}\vec{u}_{k-1}
\end{align}
Rather than explicitly calculate this error, we will find an upper bound. Let $|U|_\infty=max(|\vec{u}|_\infty \mid \vec{u} \in U)$ be the maximum infinity norm of a vector set, propagating the error to the output $\vec{y}_k$ we have:
\begin{align}
|{\vec{y}_e}_{k}|_1 \leq q_t=&(|\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})|_1+|\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}|_1)|U|_\infty
\end{align}

We overapproximate the effects of this vector by introducing a noise signal at the output $\nu_t=[-q_t\ q_t]$ and use the dynamics of the system without delay.

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Numerical representation and soundness} 
\label{sec:numeric_rep}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

In embedded software programs interacting and/or simulating physical plants
it is of great importance to understand the effects of the chosen numeric 
representation for the continuous state-space and interacting discrete dynamics. 
\jrronly{
These representations are almost invariably approximations to the original
which are assumed to be precise enough as to not cause any trouble,
but it is precisely this assumption that often results in the most difficult and
dangerous errors.
There are generally speaking two formats for representing numbers in
programs. On one hand we have variable word length types which will
attempt to use as much memory as needed to precisely represent the
original domain (usually the reals). In this case the limitations are caused
by memory and speed, both of which are directly affected by the
increasingly larger word lengths. Multiple precision floating-point arithmetic
and software rationals are good examples of these cases. It is possible for
some of these data types to have memory constraints, at which point they
fall into the second category.
Fixed precision data types are most common in software programs.
}
Whether they be floating point or fixed point
\jrronly{ (of which integers are the special case for 0 decimal places) }
numbers, the problem arises in the misrepresentation of the reals%
\jrronly{ (or equivalent data type being represented) }.
Let $\mathbb{R}_{\langle M,F \rangle}$ be a fixed point domain with $M$ bits
representing the binary word length of the representation and $F$ bits
representing the prescaling $2^{-F}$ (\emph{i.e} the number of bits after
the decimal place).  We note that a negative $F$ denotes an integer
multiplication that adds $-F$ trailing zeros in the number represented by
$M$.  Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point
domain with $M$ bits mantissa and $E$ bits exponent.  This domain
corresponds to $$\mathbb{R}_{\langle M,[E] \rangle} = \bigcup_F
\mathbb{R}_{\langle M,F \rangle} \mid F \in [2^{1-E}, 2^{E-1}]$$ This
definition important because it means that the distance between any two
numbers in the domain depends on the location of those numbers.  Since we
have shown that a floating point domain is a union of a number of fixed
point domains, we will continue our reasoning on fixed point only, which
will apply to the floating point domain by extension.  Operations on these
numbers will incur errors that can be bound
by~\cite{DBLP:conf/arith/BrainTRW15}.  We examine the most relevant ones:
%
\begin{enumerate}
\item Truncation\\
Let $\mathcal{F}_{\langle M,F \rangle}(\cdot) : \mathbb{R} \rightarrow \mathbb{R}_{\langle M,F \rangle}$
\begin{align*}
x_{\langle M,F \rangle}=\mathcal{F}_{\langle M,F \rangle}(x) = x-\delta \mid \delta=mod_F(x,c x_{\langle M,F \rangle})
\end{align*} 
where $mod_F(\cdot)$ is the modulus operation performed on the last bit of the representation ($2^{-F}$).\\
The number $\delta$ corresponds to the truncation error of the representation and it will propagate across operations.
\jrronly{
%
It is worth mentioning that not all systems truncate equally.  In the
definition above $\delta$ may be positive or negative, and even this
decision can be made dependent on the sign of $x$.  Common cases in computer
systems are: round downwards (\emph{ie} to $-\infty$), round upwards
(\emph{ie} to $+\infty$), and round to zero.  Rounding errors are cumulative
which means the overall error will statistically increase with every
operation, thus algorithms performing fewer operations can be more precise
in this respect than iterative ones.
%
}
\item Rounding\\
Every time an operation is performed on a number in the $\mathbb{R}_{\langle M,F \rangle}$ domain, an error may be
introduced due to truncation of the result. 
The following errors appear in simple operations:
\begin{enumerate}
\item Addition/Substraction
\begin{align*}
&x_{\langle M,F_1\rangle} \pm y_{\langle M,F_2\rangle}=z_{\langle M,F\rangle} + \delta,  F=\text{min}(F_1,F_2)\\
&\text{ where } |\delta| \leq 2^{-F} \text{ and } F_1=F_2 \Rightarrow \delta=0.
\end{align*}
\item Multiplication
\begin{align*}
&x_{\langle M,F_1\rangle} * y_{\langle M,F_2\rangle}=z_{\langle M,F\rangle} + \delta, \text{ where } F=F_1+F_2 \text{ and } |\delta| \leq 2^{-F}
\end{align*}
%\item Division\\
%The operations performed by our controllers in the FWL
%domain do not include division.  However, we do use division in computations
%at the precision of the plant.  Here the error depends on whether the
%divisor is greater or smaller than the dividend:  $x_{\langle M,F_1\rangle} / y_{\langle M,F_2 \rangle} = c_3 + \delta_{T3}$
%where $\delta_{T3}$ is $(\delta_{T2}\cdot x - \delta_{T1}\cdot y)/(\delta_{T2}^2 - \delta_{T2} y)$,
\end{enumerate}

\jrronly{
\item Overflow\\
Another source of error introduced by Finite Word Length representations is that of overflow.
The finite word length set a maximum representable number in the domain
$\pm \overline{M} \mid \overline{M}=2^{M-F}-2^{-F}$, which means that any number
outside this range cannot be accurately represented by the domain (\emph{eg} $\delta=x-\overline{M}$).
In the case of floating point, a special cases for infinity has been introduced, which addresses
some of these issues, but once the error has gone to infinity, the numbers become meaningless.
It is the responsibility of software designers and tools to account for overflows and either
supply saturation functions to prevent them or raise alarms in their presence. In the case
of verification, the latter is seen as a safety problem.
\item Null/Zeno behaviour\\
Whilst this work does not explore the effect of Zeno behaviours, it is worth noting that this
effect may also be caused by rounding errors in floating point programs. The reason for this
is that if an operation contains two numbers which belong to disjoint sub-domains
(\emph{ie} neither number can be represented in the domain of its counterpart), the
resulting operation may become a no-op/skip, subsequently destabilizing the program.
}
\end{enumerate}
We will use the domain $\mathbb{R}_{\langle C \rangle} \mid \langle C \rangle = \langle M_c,F_c \rangle$
to represent the fixed point precision of the controller, and 
$\mathbb{R}_{\langle P \rangle} \supseteq \mathbb{R}_{\langle C \rangle}$
to represent the domain of the plant model.
Thus any mathematical operations in our modelled digital controller will be executed in the
domain $\mathbb{R}_{\langle C \rangle}$, and all other calculations
in our model will be carried out in the domain $\mathbb{R}_{\langle
P \rangle}$.  The physical plant operates in the reals, which means
our verification phase must also account for the numerical error caused by representing the
physical plant at the finite precision $\mathbb{R}_{\langle P \rangle}$.

We will use these subindices to represent functions, number, vectors and matrices in their
corresponding domains. We further note that by choosing $\langle C \rangle = \langle M_c,[E_c] \rangle$
we extend the following to floating point reasoning.

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsubsection{Quantization errors} \label{sec:quantization}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

Let us first consider the effect of the quantization errors. 
Within the controller, state values are manipulated at low precision,
alongside the vector multiplication $\mat{K}\vec{x}$. Furthermore, 
the quantizers for the DAC and the ADC introduce truncation errors
which we denote by the effect of the functions $\mathcal{F}_{\langle D \rangle}$
and $\mathcal{F}_{\langle A \rangle}$ respectively. Finally, let us call $\vec{\nu}_e$ the
error caused by the FWL effects on the observer (\emph{i.e} the numerical errors 
in the calculations as opposed to the estimation error).
The inputs are computed using the following equation: 
%
\begin{align}
u_{k}&=\mathcal{F}_{\langle D \rangle}\left(-\mat{K}_{\langle C \rangle}\cdot\left(\mathcal{F}_{\langle C \rangle}\left(\mathcal{F}_{\langle A \rangle}(\vec{x}_{k})\right)\right) +\vec{\nu}_e\right)
\label{eq:uk}
\end{align}

This induces two types of the errors detailed above: first, the truncation
error due to the domain transformations $\mathcal{F}_{\langle *
\rangle}(\cdot)$; and second, the rounding error introduced by the
multiplication operation.  We represent these errors as non-deterministic
additive noise.

Let $q_c=2^{-F_c},q_a=2^{-F_a},q_d=2^{-F_d}$ be the smallest difference
between two numbers in their corresponding domains.  Assuming that our
system truncates numbers to the nearest value, this means thet the error
$\delta$ introduced by the function $\mathcal{F}_{\langle * \rangle}$ is
$\delta_*=\mathcal{F}_{\langle * \rangle}(x)-x \in \left[-\frac{q_*}{2}\
\frac{q_*}{2}\right]$.  We note that in the case of floating point,the
choice of $F$ is taken from the largest multiplication found (e.g.,
$|\mat{A}|_1|\vec{x}|_\infty \mid \vec{x} \models \phi_\mathit{safety}$,
where $\phi_\mathit{safety}$ is defined in \ref{eq:safetyspec}). From these
equations we can define:
%
\begin{align*}
\nu_1 \in \left[-\frac{q_a}{2}\ \frac{q_a}{2}\right] \cap  \left[-\frac{q_c}{2}\ \frac{q_c}{2}\right],
\nu_2 \in \left[-\frac{q_d}{2}\ \frac{q_d}{2}\right]
\end{align*}

We may also bound $\nu_2'$ from \eqref{eq:uk} as follollows:
\begin{align*}
\delta\left(\mat{K}_{\langle C\rangle} \vec{x}_{\langle C\rangle} \right) &\in \left[ -p \frac{q_c}{2}\ \ p \frac{q_c}{2}\right]\\
{\vec{\nu_e}}_i &\in \left[ -(p+2) \frac{q_c}{2}\ \ (p+2) \frac{q_c}{2}\right], i \in [1, p]\\
\Rightarrow \nu_2' &\in \left[  -p(|\mat{K}_{\langle C \rangle}|_1+2) \frac{q_c}{2}\ \ p(|\mat{K}_{\langle C \rangle}|_1+2) \frac{q_c}{2}\right]
\end{align*}
Similarly we also find
\begin{align*}
\nu_1' &\in \left[  -p(|{\mat{C}_d}_{\langle C \rangle}|_1+2) \frac{q_c}{2}\ \ p(|{\mat{C}_d}_{\langle C \rangle}|_1+2) \frac{q_c}{2}\right]
\end{align*}
The proof derives from $|\mat{K}\vec{x}| \leq |\mat{K}|_1|\vec{x}|_\infty$.

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsubsection{Modelling errors}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

Errors incurred by the use of numerical algorithms during synthesis are not
accounted for but rather checked during the verification phase.  If the
counterexample provided corresponds to a pre-existing one, the synthesiser
then increases its precision to reduce this error.

Previous studies~\cite{gangli1} show that the FWL affects the poles and
zeros positions, degrading the closed-loop dynamics, causing steady-state
errors and eventually de-stabilizing the system~\cite{Bessa16}.  However,
since the verifier also checks for the stability of the dynamics as a
precursor to safety, this case is handled inside the loop.  In the
following, we shall disregard these steady-state errors (caused by FWL
effects) when stability is ensured by synthesis, and then verify its safety
accounting for the finite-precision errors.

%-------------------------------
\section{Specification of control systems properties} 
\label{sec:specification}
%-------------------------------

%-------------------------------
\subsection{Stability} 
\label{ssec:stabspecification}
%-------------------------------

There are a number of algorithms that can be
used for stability analysis~\cite{daes20161,Bessa16}.
Since the canonical forms used in this work use the coefficients of the
characteristic polynomial $S(z)$ as opposed to its roots (which are
extremely hard to calculate for a SAT solver), we choose Jury's
criterion~\cite{astrom1997computer} to check the stability in the
$z$-domain in view of its efficiency.

We~consider the following form for $S(z)$:
%
\begin{equation*}
S(z) = z^{p}+a_1z^{p-1}+\cdots+a_{p-1}z+a_p.
\end{equation*}

and build the matrix
$\mat{M} \in \mathbb{R}^{p \times p}$ from its coefficients such that:
%
\begin{align*}
\mat{M}_{1,j}&=a_j\\
\mat{M}_{i+1,j}&=\left\{
\begin{array}{ll}
0,&j>p'\\
\mat{M}_{i,j}-\mat{M}_{i,p'-j+1}\frac{\mat{M}_{i,1}}{\mat{M}_{i,p'}} &j\leq p'
\end{array}
\right.\\
p'&=p-i+1
\end{align*}
%
$S(z)$ is the characteristic polynomial of a stable system if and
only if the following conditions hold~\cite{astrom1997computer}:
\begin{align*}
\phi_\mathit{stability}(S) \equiv
(S(1) > 0) \wedge ((-1)^p S(-1) > 0) \wedge (|a_p| < 1) \wedge \bigwedge\limits_{i=1}^p (\mat{M}_{i,1} > 0).
\end{align*}

%-------------------------------
\subsection{Safety} 
\label{ssec:safespecification}
%-------------------------------

We are not limited to the synthesis of digital stabilizing controllers -- a
well known task in the literature on digital control systems -- but target
safety requirements with an overall approach that is sound and automated. 
More specifically, we require that the closed-loop system meets given safety
specifications.  A safety specification gives raise to a requirement on the
states of the model, such that the feedback controller (namely the choice of
the gains matrix~$K$) must ensure that the state never violates the
requirement.  Note that a stable, closed-loop system is not necessarily a
safe system: indeed, the state values may leave the safe part of the state
space while they converge to the equilibrium, which is typical in the case
of oscillatory dynamics.  In~this work, the safety property is expressed as:
%
\begin{align}
\phi_\mathit{safety}\equiv& \underline{y} \leq y_k \leq \overline{y}
\iff \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
\label{eq:safetyspec}
\end{align}

where $\mat{G}$ is a matrix of template directions taken as row vectors, and $\vec{h}$ is an upper
bound for the set in the corresponding row direction.

Furthermore, we also need to consider the 
constraints 
\begin{align}
\phi_\mathit{input}\equiv \underline{u} \leq u_k \leq \overline{u}
\label{eq:inputspec}
\end{align}
which comes from physical restrictions in the energy of the system, and
\begin{align}
\phi_\mathit{init}\equiv \mat{G}' \vec{x}_0 \leq \vec{h}'
\label{eq:initspec}
\end{align}

%-------------------------------
\subsection{Transient response} 
\label{ssec:transientspecification}
%-------------------------------

\begin{theorem}
Given a set of eigenvalues for a discrete time model of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1\ n]$, the settling time of the system is upperbounded by
\begin{equation}
t_s<-log_{|\overline{\lambda}|}({p_s}) : |\overline{\lambda}| =\max(|\lambda_i|) \wedge |\overline{\lambda}|<1,\ \forall i \in [1\ n]
\label{eq:set_time}
\end{equation}
where $0\leq p_s \leq 1$ is the desired percentage of the target within to remain after $t_s$.
\end{theorem} 
%\begin{proof}
%In a SISO system, there are two values that typically define the
%response-time of the system (using a step response).
%%
%\begin{enumerate}
%\item The \emph{rise time} is defined as the time it takes the output to reach a percentage (eg $90\%$) of the target value given a step chnage in the input.
%\item The \emph{settling time} is defined as the time it takes the output to stabilize within a margin of the target value (eg $10\%$).
%\end{enumerate} 
%%
%In the case of first and second order systems, the decay is governed by the equations 
%%
%\begin{align*}
%&y_{decay}=
%&\left\{
%\begin{array}{cc}
%e^{-|\omega| t}& 1^{st} order\\
%e^{\zeta |\omega| t}\left(\frac{\sin\left(|\omega| t\sqrt{1-\zeta^2}+\sin^{-1}\sqrt{1-\zeta^2}\right)}{\sqrt{1-\zeta^2}} \right)&\zeta<1\\
%e^{-|\omega| t}-|\omega| t e^{-|\omega| t}&\zeta=1\\
%\frac{|\omega| e^{-|\omega_2| t}-|\omega_2| e^{-|\omega| t}}{|\omega|-|\omega_2|}&\zeta>1\end{array}\right.
%\end{align*}
%where $|\omega|$ and $|\omega_2|$ are the magnitudes of the eigenvalues (roots) of the system and  $\zeta=-\cos(\theta)$ where $\theta$ is the polar angle of the conjugate pair if it exists ($\zeta \geq 1$ if it doesn't).
%These equations become increasingly complicated for higher order systems. However, we note their strong dependency on the magnitude of the eigenvalues, and use this property to define an upperbound on the decay function.
%All of the above equations will decay faster than $e^{-|\omega| t}$ given $|\omega| < |\omega_2|$, hence we may use this function as our upper bound.
%
%Given a closed loop single output LTI system of order $n$ with dynamics
%\begin{equation}
%\left\{\begin{array}{c}\vec{x}_k=\mat{A}\vec{x}_{k-1}\\ \vec{y}_k=\mat{C}\vec{x}_k\end{array}\right. \Rightarrow \left\{ \begin{array}{c}\vec{x}_k'=\mat{J}\vec{x}_{k-1}'\\ \vec{y}_k=\mat{C}\mat{S}\vec{x}_k'\end{array}\right. : \left\{ \begin{array}{c}\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \\ \vec{x}_k'=\mat{S}^{-1}\vec{x}_k\end{array}\right.
%\label{eq:eigendynamics}
%\end{equation}
%%
%the output decay is a linear combination of the decay of eigenvalues or
%eigenvalue pairs.  Let $\mat{C}'\in \mathbb{R}^{1 \times n}=\mat{C}\mat{S}$. 
%Since $\mat{C}'$ is constant, the output $y_k$ is a linear combination of
%the states $\vec{x}'_k$.  We accelerate equation \eqref{eq:eigendynamics} to
%obtain
%%
%\begin{align}
%%\vec{x}_k'&=\mat{J}^k\vec{x}_0' \\
%y_k&=\mat{C}'\mat{J}^k\vec{x}_0 = \sum_{i=0}^p \left( c_i \lambda_i^k + c_{il}\binom{k}{l} \lambda_i^{k-l}\right)\\
%|y_k|&\leq \sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right||\lambda_i^k|
%\end{align}
%%
%where the second  part of the equation corresponds to the upper diagonal
%terms of the Jordan blocks.  We also have $|\lambda_i^k|\leq
%|\overline{\omega}^k|$,hence
%%
%\begin{align}
%|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right|
%\end{align}
%%
%Since we are synthesising the eigenvalues, rather than solve this formula
%for complex Jordan Shapes, we will restrict our synthesiser to provide
%solutions with distinct eigenvalues (which is by far the most common case). 
%Therefore the right hand terms dissappear and we obtain
%%
%\begin{align}
%|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n |c_i|
%\end{align}
%
%Hence the overall decay of the system is always smaller
%than $d=e^{-|\overline{\omega}| t}$ where $0\leq d\leq 1$ is the remaining
%percentage of the decay expressed.  Reversing we have
%$t=-\frac{ln(d)}{|\overline{\omega}|}=-\frac{ln(d)}{ln(|\overline{\lambda}|)}$. 
%replacing for $p_s$ , $t_s$, and $\overline{\lambda}$ we get equation
%\eqref{eq:set_time}
%%
%\qed
%\end{proof}
%
We may now use this limit to express a constraint in terms of the
coefficients for our synthesis process.  Let
%
\begin{equation}
P=\prod_{i=0}^p (s-\lambda_i)=\sum_{j=0}^p c_js^j.
\end{equation}
%
We use Jury's criterion to limit $|\lambda_i| \leq 1$.  Let us now define a
transformation $\lambda_i'=\frac{\lambda_i}{\overline{\lambda}}$.  We want
to ensure $\lambda_i' \leq 1$ which can be done by applying Jury's criterion
to $P'=\prod_{i=0}^p (s-\lambda_i')=\sum_{j=0}^p c_j's^j$ where $c_j'$ are
unknown.  However, if we replace for $\lambda_i$, we obtain
%
\begin{equation}
P'=\prod_{i=0}^p (s-\lambda_i')=\prod_{i=0}^p \left(s-\frac{\lambda_i}{\overline{\lambda}}\right)=\sum_{j=0}^p \frac{c_j}{\overline{\lambda}^{p-j}}s^j
\end{equation}
%
where all members are known, we may now synthesise coefficients that ensure
the eigenvalues are smaller than a desired magnitude, thus ensuring that the
settling time is too.

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Verification of a Conrollable Observed System}\label{sec:cof_verification}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\begin{figure*}[htb]
\centering
\tikzset{add/.style n args={4}{
    minimum width=6mm,
    path picture={
        \draw[circle] 
            (path picture bounding box.south east) -- (path picture bounding box.north west)
            (path picture bounding box.south west) -- (path picture bounding box.north east);
        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
        }
    }
 }

\resizebox{1.0\textwidth}{!}{
 \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
     semithick, initial text=, ampersand replacement=\&,]

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
    \node[draw=none] (r) {$r_k$};
    \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,] (gain)at ([xshift=1.2cm]r) {\sc $k_r$};

   \& \node[circle,add={-}{+}{+}{}] (circle) {};
   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$u_k$};
   \node[draw=none] (v2p)  at ([yshift=1.2cm]circle) {$\nu_2'$};
   \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Kd) at ([xshift=0,yshift=-5.5cm]circle)  {\sc $\mat{K}_{\langle C \rangle}$};
   \coordinate (kdsouth) at ([yshift=-3cm]Kd);

   \& complexnode/.pic={ 
      \node[rectangle,dashed,draw,minimum width=3cm,minimum height=1.6cm,label=\textbf{DAC}] (dac) {};
     \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
     \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
     \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {\sc ZOH};
   }

   \& complexnode/.pic={ 
      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2.5cm,yshift=.5cm]plant.center)  {\sc $\mat{B}$};
      \node[draw=none] (u) at ([xshift=-1cm,yshift=.15cm]B)  {$u(t)$};
      \node[circle,add={+}{+}{}{}] (p1) at ([xshift=-1.3cm,yshift=.5cm]plant.center) {};
      \node[draw=none] (xdot) at ([xshift=.85cm,yshift=.15cm]p1)  {$\dot{\vec{x}}(t)$};   
      \node[rectangle,draw,minimum width=1cm] (int) at ([xshift=.5cm,yshift=.5cm]plant.center) {\sc $\int$};
      \coordinate (xsouth) at ([xshift=1cm]int);
      \node[draw=none] (x) at ([xshift=1cm,yshift=.15cm]int)  {$\vec{x}(t)$};   
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (C) at ([xshift=2.7cm,yshift=.5cm]plant.center)  {\sc $\mat{C}$};
      \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]C)  {$\vec{y}(t)$};   
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (A) at ([xshift=.5cm,yshift=-1cm]plant.center)  {\sc $\mat{A}$};
      \coordinate (aeast) at ([xshift=1cm]A);
      \coordinate (awest) at ([xshift=-1.8cm]A);
    }   
    \node[circle,add={+}{+}{}{}]at ([xshift=2cm]C) (lag) {};
    \node[draw=none] (vt)  at ([yshift=-1.5cm]lag) {$\nu_t$};
   complexnode/.pic={ 
      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=5cm,label=\textbf{Observer}] (observer)  at ([yshift=-5cm]plant.center) {};
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Bd) at ([xshift=-2.5cm]observer.center)  {\sc ${\mat{B}_d}_{\langle C \rangle}$};
      \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]Bd)  {$u_k$};
      \node[circle,add={+}{+}{+}{}] (o1) at ([xshift=-1.3cm]observer.center) {};
      \node[draw=none] (xd) at ([xshift=.85cm,yshift=.15cm]o1)  {$\hat{\vec{x}}_{k+1}$};   
      \node[rectangle,draw,minimum width=1cm] (delay) at ([xshift=.5cm]observer.center) {\sc $z^{-1}$};
      \coordinate (xdsouth) at ([xshift=1.3cm]delay);
      \coordinate (fbsouth) at ([xshift=1.3cm,yshift=-3cm]delay);
      \node[draw=none] (xdp) at ([xshift=1cm,yshift=.15cm]delay)  {$\hat{\vec{x}}_k$};   
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Cd) at ([xshift=2.7cm]observer.center)  {\sc ${\mat{C}_d}_{\langle C \rangle}$};
      \node[draw=none] (y) at ([xshift=.4cm,yshift=.8cm]Cd)  {$\hat{\vec{y}}_k$};   
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ad) at ([xshift=.5cm,yshift=-1.5cm]observer.center)  {\sc ${\mat{A}_d}_{\langle C \rangle}$};
      \coordinate (adeast) at ([xshift=1.3cm]Ad);
      \coordinate (adwest) at ([xshift=-1.8cm]Ad);
      \node[circle,add={-}{}{+}{+}] (o2) at ([xshift=2.7cm,yshift=1.5cm]observer.center) {};
      \node[draw=none] (v1p) at ([yshift=1.2cm]o2) {$\nu_1'$};
      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ld) at ([xshift=.5cm,yshift=1.5cm]observer.center)  {\sc $\mat{L}_{\langle C \rangle}$};
      \coordinate (ldwest) at ([xshift=-1.8cm]Ld);
      \coordinate (bdwest) at ([xshift=-5.5cm]Bd);
      \coordinate (uksouth) at ([xshift=-5.5cm,yshift=5.5cm]Bd);
      \coordinate (o2east) at ([xshift=7.17cm]o2);
    }

   \& complexnode/.pic={ 
     \node[rectangle,dashed,draw,minimum width=3.5cm,minimum height=1.6cm,label=\textbf{ADC},] (adc) {};
     \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
     \coordinate (switch1) at ([xshift=-1cm]adc.center);
     \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
     \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
     \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
     \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]q1)  {$\vec{y}_k$};       
     \coordinate (ykeast) at ([xshift=1.9cm]q1);
   } 
   \& \coordinate (aux1);
   \& \\
  };

  \path[->] (v1) edge (q1.south);
  \path[->] (v2) edge (q2.south);
  \path[->] (vt) edge (lag.south);
  \path[->] (v1p) edge (o2.north);
  \path[->] (v2p) edge (circle.north);
  \path[->] (r) edge (gain.west);
  \path[->] (gain.east) edge (circle.west);
  \path[->] (circle.east) edge (q2.west);
  \path       (q2.east) edge (zoh.west);
  \path[->] (zoh.east) edge (B.west);
  \path
   (B.east) edge (p1.west)
   (p1.east) edge (int.west)
   (xsouth) edge (aeast)
   (aeast) edge (A.east)
   (A.west) edge (awest)
   (awest) edge (p1.south)
   (int.east) edge (C.west)
   (C.east) edge (lag.west)
   (lag.east) edge (switch1.west)
   (switch2) edge (q1.west);
  \path
   (q1.east) edge (ykeast)
   (ykeast) edge (o2east);
  \path       (uksouth) edge (bdwest);
  \path[->] (bdwest) edge (Bd.west);
  \path
   (Bd.east) edge (o1.west)
   (o1.east) edge (delay.west)
   (xdsouth) edge (adeast)
   (adeast) edge (Ad.east)
   (Ad.west) edge (adwest)
   (adwest) edge (o1.south)
   (o2.west) edge (Ld.east)
   (Ld.west) edge (ldwest)
   (ldwest) edge (o1.north)
   (delay.east) edge (Cd.west)
   (Cd.north) edge (o2.south)
   (o2east) edge (o2.east)
   (xdsouth) edge (fbsouth)
   (fbsouth) edge (kdsouth);
  \path[->]  (kdsouth) edge (Kd.south);
  \path[->] (Kd.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Closed-loop digital control system with observer\label{fig:observersystem}}
\end{figure*}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Stability of an Observed System}\label{sec:cof_stability}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally ${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$ and ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d$ for a given time discretization. We will initially assume this for the description of the system and then introduce the errors caused  by misrepresentations. For simplicity of the description, we will agregate the noises as follows:
\begin{align*}
\eta_1&=\nu_1+\nu_1'+\nu_t\\
\eta_2&=\nu_2+\nu_2'
\end{align*}
A controllable and observable system will have the following dynamics:
\begin{align}
\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_{k+1}
&=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}_d&\mat{B}_d\mat{K}_d\\ \mat{0}&\mat{A}_d-\mat{L}_d\mat{C}_d\end{array}\right]
\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_k\nonumber\\
&+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}_d\end{array}\right]\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
\label{eq:observer_LTI}
\end{align}
In order for the system to be in canonical form, we must however perform a transformation. The challenge however is that we want the state space dynamics in
reachable form and the observer error dynamics in observable form. Let 
\begin{equation}
\left[\begin{array}{c}\vec{x}'\\ \vec{x}_e'\end{array}\right]=
\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right] 
\left[\begin{array}{c}\vec{x}\\ \vec{x}_e\end{array}\right]
\end{equation}
We can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
\begin{align}
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
=& \left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
+\mat{B}' \vec{r}_k
+\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
\nonumber\\
\vec{y}_k
=& \mat{C}_{t}\vec{x}_k + \mat{D}_{d}\vec{u}_k
\label{eq:observer_LTI_cf}
\end{align}
where
{
\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{0pt}
%\begin{align*}
%
%\mat{A}_{c}=&\left[
%\begin{array}{ccccc}
%0&1&0&\cdots&0\\
%0&0&1&\cdots&0\\
%\vdots&\vdots&\vdots&\ddots&\vdots\\
%0&0&0&\cdots&1\\
%k_n-a_n&\cdots&k_i-a_i&\cdots&k_1-a_1
%\end{array}\right]
%\label{eq:cf_SISO_2}
%\end{align*}
\begin{align*}
\mat{A}_{c}=\left[
\begin{array}{cc}
\mat{0}&\mat{I}\\
k_n-a_n&\begin{array}{cc}\cdots&k_1-a_1\end{array}
\end{array}\right]&&
\mat{A}_{o}=\left[
\begin{array}{ccc}
\mat{0}&&a_n-l_n\\
&&\vdots\\
\mat{I}&&a_1-l_1
\end{array}\right]
\end{align*}
}
{\setlength{\belowdisplayskip}{0pt}
\begin{align*}
\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_d\right)\mat{T}_c^{-1}&
\mat{A}_{o}=&\mat{T}_o\left(\mat{A}_d-\mat{L}_d\mat{C}_d\right)\mat{T}_o^{-1}\\
\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]&
\mat{B}_{o}=&\mat{T}_c\mat{B}_d\mat{K}_d\mat{T}_o^{-1}\\
\mat{B}'=&\left[\begin{array}{c}\mat{T}_c\mat{B}_d\mat{k}_r\\\mat{0}\end{array}\right]&
\mat{B}_{\eta}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_d\end{array}\right]\\
\mat{T}_c=&\mat{R}_{cf}\mat{R}^{-1}&
\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
\mat{C}_t=&\mat{C}_d\mat{T}_c&
\mat{L}_d=& \mat{T}_o^{-1}\left[ \begin{array}{ccc}l_1&\cdots&l_n\end{array}\right]^T
\end{align*}
}

The matrices $\mat{R}$%$\mat{R}=\left[\begin{array}{cccc} \mat{B} & \mat{A}\mat{B} & \cdots & \mat{A}^{p-1}\mat{B} \end{array}\right]$
~and $\mat{R}_{cf}$%$\mat{R}_{cf}=\left[\begin{array}{cccc} mat{B}_c & \mat{A}_c\mat{B}_c & \cdots & \mat{A}_c^{p-1}\mat{B}_c \end{array}\right]$
~are called reachability matrices (of the system and its Reachable Canonical Form respectively),
and $\mat{W}_o$%$\mat{W}_o=\left[\begin{array}{c} mat{C}\\ \mat{C}\mat{A}\\ \vdots \\ \mat{C}\mat{A}^{p-1} \end{array}\right]$
~and $\mat{W}_{of}$%$\mat{W}_{of}=\left[\begin{array}{c} mat{C}_o\\ \mat{C}_o\mat{A}_o\\ \vdots \\ \mat{C}_o\mat{A}_o^{p-1} \end{array}\right]$
~are its observability matrices  (of the system and its Observable Canonical Form respectively)~\cite{astrom1997computer}.

Careful examination of the above matrices reveals that because the $\mat{A}'$ is
upper block diagonal, the spectrum of $\mat{A}'$ is equal to the union of
the spectrum of $\mat{A}_{c}$ and $\mat{A}_{o}$, which can be calculated
separately.  Additionally, these correspond to the roots of the polynomials
%
\begin{align*}
\left(z^p+\sum_{i=1}^p{(a_i-k_i)z^{p-i}}\right) \left(z^p+\sum_{i=1}^p{(l_i-a_i)z^{p-i}}\right)
\end{align*}

As stated in Section~\ref{ssec:stabspecification}, we use Jury's Criterion
to assert this specification.

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Safety of a Digitally Observed System}\label{sec:cof_safety}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

Now that we have established convergence, we may examine the safety
specification of the state space.  In the case of SISO systems, this is
given by a range of the input and a range of the output which are considered
safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in
[\underline{y}\ \ \overline{y}]$).  Whilst there are other properties we may
include in the verification, we will solely focus on these for simplicity of
the explanation.  We will assume that we do not want saturation in our
system, hence the control loop has only one mode.  We have also identified
the quantization noise as a bounded non-deterministic input.  First we must
translate the safety specification into the statespace.  Replacing on the
second part of equation \eqref{eq:observer_LTI_cf} we obtain
%
\begin{equation}
\phi_{safety} := \underline{y}<\mat{C}\vec{x}_k<\overline{y}, \forall k \geq 0
\label{eq:of_bounds}
\end{equation}
%
%Note that we use the bounds of the input after the transformation by $\mat{B}$ since the matrix may reverse the bounds. 
%
Equation~\eqref{eq:of_bounds} can be solved using linear programming as it
describes a polyhedral region in $\mathbb{R}^p$.  The second step is
evaluating the progression of the system over time in order to calculate
$\vec{x}_k$ to validate against this specification.  For this step we require
an initial set from which the system progresses.  Obviously, this set
$\vec{x}_0$ must satisfy the specification, otherwise the system will be
unsafe to begin with.  We will accept a specification in the form
$\mat{E}\mat{T}\vec{x}_0<\mat{f}$.  The presence of $\mat{T}$ is because
this will typically be given in the original state-space.

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Stability of a Digitally Observed System}\label{sec:cof_fwl_stability}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

Thus far we have presented a verification procedure for a continuous plant
in discretized time domain (i.e., the range of the quatizers is still
$\mathbb{R}$).  The next step we must reaize is that the controller and the
observer exist in a digital program, hence their domain is
$\mathbb{R}_{\langle C \rangle}$.  This has two separate effects on the
model.  If we recall Equation~\eqref{eq:observer_LTI}, the matrices of the observer
and the controller are not necessarily those of the plant.  In fact we have
$\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$, ${\mat{A}_d}_{\langle C
\rangle},{\mat{B}_d}_{\langle C \rangle},{\mat{C}_d}_{\langle C \rangle},
\mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \in
\mathbb{R}_{\langle C \rangle}^*$ where $*$ represents the appropriate
dimension for each matrix.  Unfortunately this means that although combined
matrices such as $\mat{A}_t$ are in the reals, they suffer from the fixed
word restrictions in their composing matrices.

When our observer is implemented using a finite precision controller, new
problems arise due to the FWL effects.  Let ${\mat{A}_d}_{\langle C
\rangle}$, ${\mat{B}_d}_{\langle C \rangle}$ and ${\mat{C}_d}_{\langle C
\rangle}$ be the dynamics represented in $\mathbb{R}_{\langle C\rangle}^*$,
%
%and $\mat{A}_e=\mat{A}_d-{\mat{A}_d}_{\langle C \rangle}$, $\mat{B}_e=\mat{B}_d-{\mat{B}_d}_{\langle C \rangle}$,
%and $\mat{C}_e=\mat{C}_d-{\mat{C}_d}_{\langle C \rangle}$ their corresponding errors.  
Equation \eqref{eq:observer_LTI_cf} becomes:
%
\begin{align}
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
=& \left [\begin{array}{cc}\mat{A}_{c}+\mat{B}_{e}&\mat{B}_{o}\\ \mat{A}_{e}&\mat{A}_{o}\end{array}\right]
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
+\mat{B}_{c} \vec{r}_k
+\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
\vec{y}_k=&\mat{C}_{t}\vec{x}_k' + \mat{D}_{d}\vec{u}_k
\label{eq:observer_LTI_FWL_cf}
\end{align}
where
{\setlength{\abovedisplayskip}{2pt}
\setlength{\belowdisplayskip}{2pt}
\begin{align*}
\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_d\right)\mat{T}_c^{-1}&
\mat{A}_{o}=&\mat{T}_o\left({\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}{\mat{C}_d}_{\langle C \rangle}\right)\mat{T}_o^{-1}\\
\mat{B}_{o}=&\mat{T}_c{\mat{B}_d}_{\langle C \rangle}\mat{K}_{\langle C \rangle}\mat{T}_o^{-1}&
\mat{B}_{e}=&\mat{T}_c(\mat{B}_d-{\mat{B}_d}_{\langle C \rangle})\mat{K}_{\langle C \rangle}\mat{T}_o^{-1}\\
\mat{A}_{e}=&\mat{T}_o\left(\mat{A}_d-{\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}\mat{C}_e\right)\mat{T}_o^{-1}&
\mat{C}_{e}=&\mat{C}_d-{\mat{C}_d}_{\langle C \rangle}\\
\mat{T}_c=&\mat{R}_{cf}\mat{R}^{-1}&
\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
\mat{C}_t=&\mat{C}_d\mat{T}_c&
\mat{L}_{\langle C \rangle}=& \mat{T}_o^{-1}\left[ \begin{array}{ccc}l_1&\cdots&l_n\end{array}\right]^T
\end{align*}
}
{\setlength{\abovedisplayskip}{0pt}
\begin{align*}
\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}+\mat{B}_{e}&\mat{B}_{o}\\ \mat{A}_{e}&\mat{A}_{o}\end{array}\right]&
\mat{B}_{c}=&\left[\begin{array}{c}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}\mat{k}_r\\\mat{0}\end{array}\right]&
\mat{B}_{\eta}=&\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]
\end{align*}
}
The first effect of this new equation is that $\mat{A}'$ is no longer upper
diagonal.  We must therefore compensate for the errors introduced in order
to find a stable solution.  We can use Gershgoring disks to limit the error
in the expected eigenvalues.  Let $\delta_o=\max(|{\mat{A}_e}_{i,*}|_2)$
(\emph{i.e.} the largest row norm in $\mat{A}_e$) be the largest error bound
for any eigenvalue in $\mat{A}_e$.  Then $\forall i \in [1, n],
|{\lambda_o}_{i}-\hat{\lambda_o}_{i}|<\delta_o$,where ${\lambda_o}_{i}$ are the
true eigenvalues of the observer and $\hat{\lambda_o}_{i}$ the eigenvalues of
the perturbed observer.  We note that in the case of stability we only care
about the error with respect to the unit circle, which is equivalent to
upper bounding the estimation of the largest eigenvalue.  Hence given a
desired upper value $\overline{\lambda}$, we apply Jury's criterion on the
polynomial.
%
\begin{equation}
P_o'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j : \overline{\lambda'}=(1+\delta_o)\overline{\lambda}
\end{equation}
%
In the case of the reachable eigenvalues, the procedure is the same except
that we obtain our bound $\delta_c=\max(|{\mat{A}_e}_{*,i}+{\mat{B}_e}_{*,i}|_2)$
(\emph{i.e.} the largest column norm in $ \left[\begin{array}{c}\mat{A}_e\\ \mat{B}_e\end{array}\right]$) and
apply Jury's Criterion over
%
\begin{equation}
P_r'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j : \overline{\lambda'}=(1+\delta_c)\overline{\lambda}
\end{equation}

As a final annotation, we remark that the safety specification must be
applied to the model described in this section, accounting for the
representation errors of the FWL domain.

%-------------------------------
\section{Counterexample Guided Inductive Synthesis} 
\label{ssec:cegis}
%-------------------------------

In order to synthesize closed-loop digital control systems, we use a program
synthesis engine.  Our program implements Counter-Example Guided
Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}.  We
start by presenting its general architecture followed by describing the
parts specific to closed-loop control systems.

CEGIS-based control synthesis requires a formal verifier to check whether a
candidate controller meets the requirements when combined with the plant.
We use the tool Axelerator~\cite{} in the verification module.  It checks the
stability of a cyberphysical closed-loop control system and considers finite-word
length (FWL) effects in the digital controller and continuous dynamics in continuous
time progression in the plant.
As part of the counterexample, Axelerator generates an ANSI-C code model
containing information about different transforms of the system as well as other
abstractions relating to quantization and safety which allow us to create models
for the synthesisers. This specification (which we refer to as $\phi$) is passed to
the Bounded Model Checker CBMC~\cite{ClarkeKL04} which uses SAT solving to
generate a valid input for a controller and observer that meet the given specification.
The ANSI-C code model guarantees that a synthesized solution is complete and
sound with respect to the given abstraction since it does not depend on system
inputs and outputs, but further analysis is required to obatin a solution that meets
the original specification. These results are then fed back to a synthesis module in
Axelerator which uses eigendecomposition and other linear transformations to
refine the solution.

%-------------------------------
\subsection{CEGIS of digital controllers} 
\label{sssec:cegisdig}
%-------------------------------

Our approach is illustrated in Fig.~\ref{fig:CEGARIS}. It relies on the
construction of an unsound abstract model that approximates the dynamics
of the cyberphysical system in order to synthesise a candidate controller
and observer and then verify its behaviour against a sound overapproximation
of the concrete dynamics of the system for an infinite space over an infinite
time horizon.
The verifier's abstraction uses a CEGAR loop in order to minimise 
overapproximation errors and provides counterexamples for both
discrete and continuous dynamics to feed a CEGIS loop on the synthesiser
waiting for a new candidate solution.

We find a controller for a continuous initial set of states and set of inputs,
over an abstraction of the continuous dynamics \cite{cattaruzza2015unbounded}
that conforms to witness proofs at specific times.
Moreover, this approach uses abstraction refinement enabling us to always
start with a very simple description regardless of the complexity of the
overall dynamics, and only expand to more complex models when a solution
cannot be found.

The CEGIS loop for this approach

\begin{enumerate}
\item 
The {\sc ABSTRACT} module starts by creating an abstraction from the initial specification,
\begin{enumerate}
\item Select a sample time that minimizes the magnitudes of the matrices used in both the
implementation and the abstraction. This ensures that a small bitvector size is required for
the synthesis process.
\item Build the Observer matrices ${\mat{A}_d}_{\langle C \rangle}$, ${\mat{B}_d}_{\langle C \rangle}$
and ${\mat{C}_d}_{\langle C \rangle}$ using the truncation described in section \ref{sec:numeric_rep}.
\item Transform the system into Canonical form and add nondeterminism for the errors
using the techniques described in section \ref{sec:cof_fwl_stability}. The transformation
matrices will be needed to obtain an FWL compliant controller and observer.
\item Compute the characteristic polynomial of the matrix $(\mat{A}_d-\mat{B}_d\mat{K}_{\langle C \rangle})$
as $P_a(z) = z^p+\sum_{i=1}^p{(a_i-k_i)z^{p-i}}$. 
\item Compute the characteristic polynomial of the matrix $({\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}{\mat{C}_d}_{\langle C \rangle})$
as $P_l(z) = z^p+\sum_{i=1}^p{(l_i-a_i)z^{p-i}}$. 
\item Create a stability specification based on the characteristic polynomials, perturbation
error ($\mat{A}_e$,$\mat{B}_e$), and response time $\phi_{stability}(P_a,P_l,\overline{\lambda})$
as described in section \ref{ssec:transientspecification}.
\item Calculate the noise sets $\eta_1$ and $\eta_2$ from the equations
described in sections \ref{sec:delay} and \ref{sec:quantization}.
\item Calculate a set of initial bounds on $\mat{K}$, $\phi_\mathit{init}^{K}$,
based on the input constraints.  
%
$(\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-\mat{K} x_k)
\Rightarrow \phi_\mathit{init}^{K}$.
These bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space. 
\end{enumerate}
The Abstraction is fed to the synthesiser.
\item In the {\sc synthesize} phase, we synthesize a candidate controller $\mat{K} \in \mathbb{R}_{\langle C\rangle}^p$
and observer $\mat{L} \in \mathbb{R}_{\langle C\rangle}^p$ that satisfy
$\phi_\mathit{stability} \wedge \phi_\mathit{safety} \wedge \phi_\mathit{init}^{K}$ by invoking a SAT solver.
There are two exit conditions:
\begin{enumerate}
\item If there is no candidate solution we return UNSAT and signal the modeller. Based on the current abstraction,
the {\sc  model} phase may choose to increase the precision, decrease the sample time, or return a synthesis failure.
\item If we have a candidate solution we will feed it to the verifier in order to validate it.
\end{enumerate}
\item The verifier works in multiple stages.
\begin{enumerate}
%
\item The {\sc Verify Synthesis} submodule verifies $\phi_{static}$ of  both the
controller and the observer.  If one of these results does not satisfy the tighter
specification, it feeds back to the modeller which uses sensitivity analysis to
synthesise a refined solution. 
Formally speaking, given a violating controller $\{ \mat{K},\mat{L} \} \not \models \phi_{static}$
we look for a variation $\mat{\delta}_K, \mat{\delta}_L$ such that
$\{ \mat{K}', \mat{L}' \}=\{ \mat{K}+\mat{\delta}_K,\mat{L}+\mat{\delta}_L \} \models \phi_{static}$, and similarly for the observer.
%\mat{K}' \in \mathbb{R}_{\langle C \rangle}$. 
If the Modeller cannot synthesise a suitable candidate($\mat{K}' \not
\models \phi_{static}^K$), it returns to the synthesiser with a request for
either higher precision or a lower upper bound $\overline{\lambda}$. Otherwise
the refined candidate solution is given to the second verification stage.
%
\item The {\sc Discrete Time} submodule verifies $\phi_{safety}$ using discrete
time dynamics.  If the verification fails, the verifier reports to the
modeller with a counterexample, including details of initial states and
iterations that failed the specification.  The modeller will then create a
refined abstraction that explores this time horizon for the given initial
state.  If the magnitude of the violation is small, we may choose to try
a synthesis refinement loop before feeding back to the main synthesiser.
%
\item If the Discrete Time verification is successful, the problem is
evaluated by the {\sc Continuous Time} submodule.  This stage verifies that the
transitions between sample times meet the specification $\phi_{safety}$.  If
a counterexample is found, information about the maximum distance of the
violation to the specification boundary is fed back to the modeller.  Once
again, the modeller will refine the abstraction based on this information by
creating constraints on the surrounding points (constraining the safety
abstraction to exclude the violation based on the projection of the discrete
time dynamics onto the continuous ones).
%
\end{enumerate}

\item If we reach the {\sc abstract} phase, it means that the candidate
  solution is not valid, in which case we must refine the abstraction used
  by the synthesizer.
%
\begin{enumerate}
%
\item Find the constraints that invalidate the property
 as a set of counterexamples for the eigenvalues, which we define as
$\phi_\Lambda$.  This is a constraint in the spectrum i.e., transfer
function) of the closed loop dynamics.
%
\item We use $\phi_\Lambda$ to further constrain the characteristic polynomial 
\begin{equation*}
z^p+\sum_{i=1}^p(a_i-k_i)z^{p-i}=\prod_{i=1}^p (z-\lambda_i) \mid |\lambda_i|<1 \wedge \lambda_i \models \phi_{\Lambda}.
\end{equation*} 
These constraints correspond to specific iterations for which the system may be unsafe.

\item Pass the refined abstraction $\phi(K)$ with the new constraints and the list of iterations $k$ to the {\sc synthesize} phase.
  %, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again. 
\end{enumerate} 
\end{enumerate}

\begin{figure*}[htb]
{
 \centering
 \scriptsize
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=1cm] {
  \coordinate (aux1);\&\&
  \coordinate (aux2);
  \coordinate (aux3) at ([xshift=3cm]aux2); \\
  \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (model1) {{\sc 1. Abstract}};
  \&\& complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=8cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc Model~~~~~~~~~~~},] (model) {};
     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (model2) at ([xshift=-3cm]model.center) {{\sc 3. Refine}\\{\sc Synthesis}};
     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (model3) at ([xshift=0cm]model.center) {{\sc 4. Refine}\\{\sc Abstraction}};
     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (model4) at ([xshift=3cm]model.center) {{\sc 5. Sample}};
   } ;\\
   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc 2.Synthesize}};
   \&\&
   complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=8cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc Verify~~~~~~~~~~~},] (verif) {};
     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-3cm]verif.center) {{\sc 5. Verify}\\{\sc Synthesis}};
     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=0cm]verif.center) {{\sc 6. Discrete}\\{\sc Time}};
     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=3cm]verif.center) {{\sc 7. Continuous}\\{\sc Time}};
   } 
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \& \\
   \node[minimum height=0cm] (gp) {{\sf Program}\\{\sf Search}};
   \&\&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-3cm]aux.center) {\sf Eigensolver};
   \node (fp)  at ([xshift=0cm]aux.center) {\sf Reachability \\ \sf Analysis};
   \node (sv)  at ([xshift=3cm]aux.center) {\sf Reachability \\ \sf Analysis};
   }   
    \\
  };
   \path[-]
    (model3.north) edge node[align=center,xshift=0.8cm] {$k$,$X_0'$} (aux2.north)
    (aux2.west) edge (aux1.east)
    (aux3.west) edge (aux2.east)
    (model4.north) edge node[align=center,xshift=0.5cm] {$T_s$} (aux3.north);
   \path
    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$\mat{K}$,$\mat{L}$} ([yshift=2em]verif1.west)
    ([yshift=-2em]verif1.west) edge node {C-ex} ([yshift=-2em]synth.east)
    (verif1.east) edge node {SAT} (verif2.west)
    (verif2.north) edge node[xshift=.8cm] {C-ex} (model3.south)
    (verif2.east) edge node {SAT} (verif3.west)
    (verif3.north) edge node {C-ex} (model4.south)
    (aux1.south) edge node {$\phi$} (model1.north)
    (model3.west) edge node {$\phi_\Lambda$} (model2.east)
    (model4.west) edge node {$\phi_\Lambda$} (model3.east)
    ([xshift=-5em]fp.north) edge node[align=center]  {SAT/\\C-ex} ([xshift=-5em]verif2.south)
    ([xshift=-5em]sv.north) edge node[align=center]  {SAT/\\C-ex} ([xshift=-5em]verif3.south)
    ([xshift=5em]verif1.south) edge node[align=center] {$\mat{A}'$} ([xshift=5em]bmc.north)
    ([xshift=5em]verif2.south) edge node[align=center] {$\mat{A}'$,$\mat{B}'$,$\phi$} ([xshift=5em]fp.north)
    ([xshift=5em]verif3.south) edge node[align=center] {{$\mat{A}$,$\mat{B}$,$\mat{C}$}\\{$\mat{A}'$,$\mat{B}'$,$\phi$}} ([xshift=5em]sv.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {SAT/\\C-ex} ([xshift=-5em]verif1.south)
    (verif) edge node {PASS} (done)
    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$\mat{K}$,$\mat{L}$} ([xshift=-5em]synth.south)
    ([xshift=5em]model1.south) edge node[align=center,xshift=-.65cm] {$\langle P \rangle$} ([xshift=5em]synth.north) node[align=left,yshift=-0.7cm,xshift=1.3cm] {{$\phi_{stability}(P_a,P_l,\overline{\lambda})$}\\{$\phi_{safety}(\eta,k)$}\\ {$\phi_{init}^K$}}
   ([xshift=-5em]synth.north) edge node[align=center] {UNSAT} ([xshift=-5em]model1.south);
   \path[->]
    ([xshift=-5em]verif1.north) edge node[align=center]  {$\mat{K}$,$\mat{L}$} ([xshift=-5em]model2.south)
    ([xshift=5em]model2.south) edge node[align=center]  {$\mat{K}'$,$\mat{L}'$} ([xshift=5em]verif1.north)
    (model2.west) edge node[align=center] {$\overline{\lambda},\langle C \rangle$} (model1.east)
    ([yshift=1em]model1.east) edge node[align=center] {$\phi_{static}$} ([yshift=1em]model2.west);

   %(verif4.north) edge node[align=center] {} ([xshift=10.5cm]aux2)
   %([xshift=10.5cm]aux2) edge node[align=center] {Increase Sampling Rate} (aux1);

 \end{tikzpicture}
}
\caption{CEGIS with Abstraction Refinement}
\label{fig:CEGARIS}
\end{figure*}

%-------------------------------
\section{Experimental Evaluation}
\label{exp:evaluation}
%-------------------------------

\jrronly{
%-------------------------------
\subsection{Description of the benchmarks}
\label{exp:benchmarks}
%-------------------------------
}
%\textcolor{red}{Iury: can you please describe the benchmarks?}

The benchmark suite employed to evaluate the proposed technique is 
composed by 18 MIMO models extracted from the literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15,maglev,converters}

\jrronly{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{DC Motor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

DC Motor benchmark describes the velocity dynamics of a basic 
brushed direct current electrical machine.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Automotive Cruise System}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

An automotive cruise control system is used to keep constant the speed 
of an automobile  tracking a desired speed reference, compensating 
disturbances and uncertainties related to relief and terrain.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Pendulum}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A pendulum is system composed by a swinging point mass suspended from 
a frictionless pivot through a negligible mass rod.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Inverted Pendulum}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

An inverted pendulum is a system similar to the pendulum but the point 
mass must be equilibrated above the pivot point that is mounted on an 
one degree of freedom cart that moves over a track through a DC motor.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Magnetic Suspension}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Magnetic suspension benchmark corresponds to the discrete model of a 
simple eletromagnet-ball system where a steel ball is levitated in air 
by the action of an electromagnetic force generated by an electromagnet.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Magnetic Pointer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Magnetic pointer is a pointer, that is usually employed in analogue 
gauges and indicators, whose angular position dynamics is controlled 
by a magnetic field.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{1/4 Car Suspension}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The 1/4 Car Suspension benchmark corresponds to the model of a single 
wheel suspension system of a car, {\it i.e.} the relative motion dynamics 
of a mass springer damp model that connects the car to one of its wheels.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Computer Tape Driver}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Computer Tape Drive is a computer storage device used to read and write 
data on magnetic tapes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Acrobot - Robot Manipulator}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Acrobot benchmark corresponds to the model of an two-link 
underactuated robot manipulator, linearized by partial 
feedback linearization~\cite{acrobot}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{High-order Systems from Chen et. al.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

These benchmarks corresponds to a series of high-order system model 
generally used as example for order reduction techniques~\cite{CHEN1979389}.
 In this work, these benchmarks are used for evaluate the proposed control
 synthesis technique under critical conditions, {\it i.e.} with a greater 
 number of parameters to be considered.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Continuous Stirred Tank Reactor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This benchmark describes a linear model for PH dynamics of a PH 
neutralization process of an aqueous solution of sodium acetate with 
hydrochloric acid in a continuous flow stirred-tank reactor.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Flexible Beam}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A Flexible Beam is a plant usually employed in vibration studies. It is 
composed by a flexible metallic structure with piezoceramic actuators 
and sensors.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Helicopter Longitudinal Motion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Helicopter Longitudinal Motion benchmark describes the dynamics of 
transitional motion with respect to a longitudinal plane and the 
rotational motion around the longitudinal axis.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{USCG cutter Tampa Heading Angle}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The USCG cutter Tampa Heading Angle describes the heading angle 
dynamics of a Coast Guard cutter.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Voltage regulator}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The voltage regulator benchmark~\cite{KOKOTOVIC198023} consists 
in a linear model of a synchronous machine connected to an 
infinite bus.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Guidance Control System}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Guidance Control System benchmark is another high-order system 
model used by Chen et al.~\cite{CHEN1979389}  in order reduction 
techniques. Guidance systems are used to determine the path of an 
autonomous vehicle movement.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Satellite Attitude Control System}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This benchmark describes the dynamics of a satellite attitude, 
{\it i.e.} the orientation angles. An attitude control system must 
maintain the desired orientation of satellite with respect to an 
inertial frame during all the excursion.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{Springer-mass damper}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The springer-mass damper systems are classic models for a lot of 
mechanical systems dynamics. This benchmark describes a mass that is 
fixed to a node through a springer and moves under the action of a 
input force, damping, and elastic force.

}

%-------------------------------
\subsection{Results}
\label{exp:results}
%-------------------------------
The technique was applied  to the benchmarks and the results can be seen in table \ref{tab:results}
\begin{table}
\centering
%
\begin{tabular}{| r | l | c | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{order}  & \multicolumn{1}{|c|}{$\mat{K}$} & \multicolumn{3}{|c|}{$\mat{K}+\mat{L}+T_s$} \\
   &                                  & & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{Max}\\\hline
1  & DC Motor          & 2 & 2.1\,s& 16,16  &   4.1\,s &   4.1\,s\\
2  & Helicopter        & 3  & 1.4\,s& 24,16  &   18.7\,s &   18.7\,s\\
3  & Inverted Pendulum & 4 &   0.6\,s& 16,24  &  308.4\,s &  308.4\,s\\
4  & Magnetic Pointer  & 2  & 44.1\,s& 24,16  &  7.7\,s &  7.7\,s \\
%5  & Magnetic Suspension & 2 & 0.6\,s& 16,24  &   0\,s &   0\,s\\
5  & Pendulum          & 2 & 14.0\,s& 16,16  &   3.4\,s &   3.4\,s\\
6  & Suspension        & 2 & 73.7\,s& 16,24  &   1316.2\,s &   1316.2\,s\\
7  & Tape Driver       & 3 & 68.3\,s& 16,24  &   57.8\,s &   57.8\,s\\
%9 & Satellite          & 2 &   0.7\,s& - &  - &  -\\ %unobservable
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table}

%%-------------------------------
%\subsection{Threats to validity}
%\label{exp:threats-to-validity}
%%-------------------------------
Since our synthesisers use abstract aproximations of the real dynamics, our solution is not complete.
it is possible to have models where a true solution is not found although it exists.
Soundness is ensured by the verifiers,but once again, since these use over-approximations of the real dynamics, they may also reject valid solutions, hence affecting completeness.

%-------------------------------
\section{Conclusions}
\label{sec:conclusions}
%-------------------------------

\newpage
\bibliographystyle{splncs03}
\bibliography{paper}
\newpage
\appendix
%-------------------------------
\section{Proofs of theorems}
%-------------------------------
\setcounter{theorem}{0}
\setcounter{corollary}{0}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsubsection{Discrete dynamics using reals for systems without inputs}\label{asec:real_discrete_no_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \begin{theorem}
 Given $\dot{\vec{x}}=\mat{A}\vec{x}$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, the expression
 \begin{align}
 \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x}_0\\
 \mat{A}_{T}&= \mat{S}
 \left [ \begin{array}{cccc}
 e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(1)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
\vdots & & \ddots & \vdots \\
0 & \cdots & 0  &e^{T\lambda_i} \\
\end{array} \right ]
 \mat{S}^{-1}
 \label{eq:continuous_tube_dyn}\\
 &\text{where } s_i=\left\{\begin{array}{cc}1&gm(\lambda_i)>1\\0&gm(\lambda_i)=1\end{array}\right.,\nonumber
 \end{align}
$\lambda_i \in \mat{J}$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.  $\vec{x}_T$ is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}$ at time t=T.
 \end{theorem}
 \begin{corollary}
 If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x} : k \in (0,\infty)$ is a witness of the system at time $t=kT_d$.
 \end{corollary}
 \begin{proof}
 Let us recall equation \ref{eq:discretize}. The discrete representation of the system dynamics discretised with sample time $T_1$ is ruled by the formula
 $\mat{A}_1 = e^{\mat{A} T_1}$. From matrix theory, we have 
\begin{align}
 e^{\mat{A}}&=\sum_{k=0}^\infty \frac{1}{k!}\mat{A}^k
\end{align} 
\begin{align} 
 e^{\mat{S}\mat{J}\mat{S}^{-1}}&=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{S}\mat{J}\mat{S}^{-1}\right)^k
 =\mat{S} \left (\sum_{k=0}^\infty \frac{1}{k!}\mat{J}^k\right) \mat{S}^{-1}\nonumber\\
 &=\mat{S}e^{\mat{J}}\mat{S}^{-1}
\end{align} 
\begin{equation}
\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \Rightarrow \vec{A}_1 = \mat{S}\mat{J}_1\mat{S}^{-1}= \mat{S}e^{\mat{J} T_1}\mat{S}^{-1}.
 \end{equation}

 Let $\mat{J}$ be a diagonal matrix, such that 
 $${\lambda_1}_i=e^{\lambda_i T_1}, \forall \lambda_i \in \mat{J}.$$
 Let us now take a different sample rate $T_2$, such that 
 $${\lambda_2}_i=e^{\lambda_i T_2}, \forall \lambda_i \in \mat{J}.$$
 We can then say that 
 \begin{equation}
 {\lambda_2}_i=e^{\lambda_i T_1 \frac{T_2}{T_1}}={\lambda_1}_i^{\frac{T_2}{T_1}} \Rightarrow A_2=A_1^{\frac{T_2}{T_1}}.
 \end{equation}
 This proves the theorem for $gm(\lambda_i)=1$.
 We now note that given an exponentiated Jordan form with geometric multiplicity, the upper diagonal terms can be
 referenced to the original eigenvalues modified by the sampling rate.
  Let $\mat{J}\in \mathbb{R}^{p \times p}$ be a Jordan Canonical matrix.
 Then
\begin{align}
 \mat{J}_1&=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{J}T_1\right)^k=\sum_{k=0}^\infty \frac{1}{k!} \left [ \begin{array}{cccc}
 \lambda_i^k  & \binom{k}{1}  \lambda^{k-1} & \hdots  & \binom{k}{p-1} \lambda_i^{k-p+1} \\
& \lambda_i^k  & \binom{k}{1}  \lambda_i^{k-1} & \vdots \\
\vdots & \ddots & \ddots & \vdots \\
& &  &\lambda_i^k \\
\end{array} \right ] T_1^k
\end{align}
The eigenvalues remain the same as in the diagonal case, but the upper triangular terms are of the form:
\begin{align}
\forall j>i, c_{ij}&=\sum_{k=j-i}^\infty \frac{1}{k!}\binom{k}{j-i} \lambda_i^{k-(j-i)}T_1^k\\
&=\frac{1}{(j-i)!}\sum_{k=j-i}^\infty \frac{1}{(k-(j-i))!} \lambda_i^{k-(j-i)}T_1^k\nonumber\\
&=\frac{T_1^{j-i}e^{\lambda_i T_1}}{(j-i)!}\nonumber
\end{align}
which completes the proof for $gm(\lambda_i)>1$.
\end{proof}

 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsubsection{Discrete dynamics using reals for systems with parametric inputs}\label{asec:real_discrete_param_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\begin{theorem}
The expression
 \begin{align}
 \vec{x}_T&=\vec{x}(t=T)=\mat{A}^{-1}\vec{x}_T'\nonumber\\
\vec{x}_T'&=\mat{A}\mat{A}_T\vec{x}_0 + (\mat{I}-\mat{A}_T)\mat{B}\vec{u} : \forall t \leq T,\ \vec{u}(t)=\vec{u} 
 \end{align}
 with $\mat{A}_T$ as per \eqref{eq:continuous_tube_dyn} is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$.
 \end{theorem}
 \begin{corollary}
 If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}+(\mat{I}-\mat{A}_d^k\mat{B}\vec{u}) : k \in (0,\infty)$ is a witness of the system at time $kT_d$.
 \end{corollary}
 \begin{proof}
 We begin by expanding the equation
 \begin{align}
 \vec{x}_T&=\mat{A}^{-1}\vec{x}_T'\nonumber\\
 &=\mat{A}_T\vec{x}_0 + \mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}\vec{u}\nonumber\\
 &= \mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u}
 \end{align}
 where $\mat{A}_T=e^{\mat{A}T}$ and $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$ correspond to $\mat{A}_d$ and $\mat{B}_d$ in equation \eqref{eq:discretize}
 \end{proof}

 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsubsection{Discrete dynamics using reals for systems with discrete time feedback inputs}\label{asec:real_discrete_feedback_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

The final case we analyse here is that of hybrid time systems, where the
plant dynamics evolve in continuous time while the feedback dynamics evolve
in discrete time.

\begin{theorem}
The expression
 \begin{align}
 \vec{x}_{t} &= (\mat{A}_{t-kT_s}-\mat{B}_{t-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
 \label{eq:cyber_feedback}
 \end{align}
 with $\mat{A}_t, \mat{B}_t$ as per \eqref{eq:continuous_tube_dyn} and $\mat{A}_d, \mat{B}_d$ as per equation \eqref{eq:discretize} is a witness of the system
 \begin{align}
 \dot{\vec{x}}_{t} &= \mat{A}\vec{x}+\mat{B}\vec{u}_t\nonumber\\
 \vec{u}_t&=\mat{K}\vec{x}_k  \mid  kT_s \leq t < (k+1)T_s
 \end{align}
 \end{theorem}

\begin{proof}
Let $\mat{K}$ be a feedback controller such that $\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$. Let the output of
the feedback system be a zero order holder such that $\vec{u}(t+kT_s)=\vec{u}(kT_s) : 0 \leq t < T_s$.
The closed loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
\begin{equation}
\vec{x}_{k,t}=\mat{A}_t\vec{x}_k-\mat{B}_t\mat{K}\vec{x}_k = (\mat{A}_t-\mat{B}_t\mat{K})\vec{x}_k : 0 \leq t < T_s
\end{equation}
We further explore the dynamics across discrete time boundaries. Let $\mat{A}_d=\mat{A}_{T_s}$ and $\mat{B}_d=\mat{B}_{T_s}$
\begin{align}
\vec{x}_{k}&=\vec{x}_{k-1,T_s}= (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}\\
\vec{x}_{k,T_s} &= (\mat{A}_d-\mat{B}_d\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}
\end{align}
which accelerating results becomes
\begin{align}
\label{eq:feedback_sampled_cont}
\vec{x}_{k} &= (\mat{A}_d-\mat{B}_d\mat{K}) ^k\vec{x}_0\\
\vec{x}_{t} &= (\mat{A}_{t-kT_s}-\mat{B}_{t-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
\label{eq:feedback_cont}
\end{align}
\end{proof}

%-------------------------------
\subsection{Transient response} 
\label{asec:transientspecification}
%-------------------------------

\begin{theorem}
Given a set of eigenvalues for a discrete time model of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1\ n]$, the settling time of the system is upperbounded by
\begin{equation}
t_s<-log_{|\overline{\lambda}|}({p_s}) : |\overline{\lambda}| =\max(|\lambda_i|) \wedge |\overline{\lambda}|<1,\ \forall i \in [1\ n]
\label{eq:set_time}
\end{equation}
where $0\leq p_s \leq 1$ is the desired percentage of the target within to remain after $t_s$.
\end{theorem} 
\begin{proof}
In a SISO system, there are two values that typically define the
response-time of the system (using a step response).
%
\begin{enumerate}
\item The \emph{rise time} is defined as the time it takes the output to reach a percentage (eg $90\%$) of the target value given a step chnage in the input.
\item The \emph{settling time} is defined as the time it takes the output to stabilize within a margin of the target value (eg $10\%$).
\end{enumerate} 
%
In the case of first and second order systems, the decay is governed by the equations 
%
\begin{align*}
&y_{decay}=
&\left\{
\begin{array}{cc}
e^{-|\omega| t}& 1^{st} order\\
e^{\zeta |\omega| t}\left(\frac{\sin\left(|\omega| t\sqrt{1-\zeta^2}+\sin^{-1}\sqrt{1-\zeta^2}\right)}{\sqrt{1-\zeta^2}} \right)&\zeta<1\\
e^{-|\omega| t}-|\omega| t e^{-|\omega| t}&\zeta=1\\
\frac{|\omega| e^{-|\omega_2| t}-|\omega_2| e^{-|\omega| t}}{|\omega|-|\omega_2|}&\zeta>1\end{array}\right.
\end{align*}
where $|\omega|$ and $|\omega_2|$ are the magnitudes of the eigenvalues (roots) of the system and  $\zeta=-\cos(\theta)$ where $\theta$ is the polar angle of the conjugate pair if it exists ($\zeta \geq 1$ if it doesn't).
These equations become increasingly complicated for higher order systems. However, we note their strong dependency on the magnitude of the eigenvalues, and use this property to define an upperbound on the decay function.
All of the above equations will decay faster than $e^{-|\omega| t}$ given $|\omega| < |\omega_2|$, hence we may use this function as our upper bound.

Given a closed loop single output LTI system of order $n$ with dynamics
\begin{equation}
\left\{\begin{array}{c}\vec{x}_k=\mat{A}\vec{x}_{k-1}\\ \vec{y}_k=\mat{C}\vec{x}_k\end{array}\right. \Rightarrow \left\{ \begin{array}{c}\vec{x}_k'=\mat{J}\vec{x}_{k-1}'\\ \vec{y}_k=\mat{C}\mat{S}\vec{x}_k'\end{array}\right. : \left\{ \begin{array}{c}\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \\ \vec{x}_k'=\mat{S}^{-1}\vec{x}_k\end{array}\right.
\label{eq:eigendynamics}
\end{equation}
%
the output decay is a linear combination of the decay of eigenvalues or
eigenvalue pairs.  Let $\mat{C}'\in \mathbb{R}^{1 \times n}=\mat{C}\mat{S}$. 
Since $\mat{C}'$ is constant, the output $y_k$ is a linear combination of
the states $\vec{x}'_k$.  We accelerate equation \eqref{eq:eigendynamics} to
obtain
%
\begin{align}
%\vec{x}_k'&=\mat{J}^k\vec{x}_0' \\
y_k&=\mat{C}'\mat{J}^k\vec{x}_0 = \sum_{i=0}^p \left( c_i \lambda_i^k + c_{il}\binom{k}{l} \lambda_i^{k-l}\right)\\
|y_k|&\leq \sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right||\lambda_i^k|
\end{align}
%
where the second  part of the equation corresponds to the upper diagonal
terms of the Jordan blocks.  We also have $|\lambda_i^k|\leq
|\overline{\omega}^k|$,hence
%
\begin{align}
|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right|
\end{align}
%
Since we are synthesising the eigenvalues, rather than solve this formula
for complex Jordan Shapes, we will restrict our synthesiser to provide
solutions with distinct eigenvalues (which is by far the most common case). 
Therefore the right hand terms dissappear and we obtain
%
\begin{align}
|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n |c_i|
\end{align}

Hence the overall decay of the system is always smaller
than $d=e^{-|\overline{\omega}| t}$ where $0\leq d\leq 1$ is the remaining
percentage of the decay expressed.  Reversing we have
$t=-\frac{ln(d)}{|\overline{\omega}|}=-\frac{ln(d)}{ln(|\overline{\lambda}|)}$. 
replacing for $p_s$ , $t_s$, and $\overline{\lambda}$ we get equation
\eqref{eq:set_time}
%
\qed
\end{proof}

%%-------------------------------
%\section{Stability of Closed-loop Models}
%\label{sec:appendix-stability}
%%-------------------------------
%
%%-------------------------------
%\subsection{Stability of closed-loop models with fixed-point controller error}
%\label{sec:stab_FWL}
%%-------------------------------
%
%The proof of Jury's criterion~\cite{fadali} relies on the fact that the relationship between states and
%next states is defined by $x_{k+1} = (A_d - B_dK) x_k$, all computed
%at infinite precision.  When we employ a FWL digital controller, the
%operation becomes:
%%
%\begin{align*}
%x_{k+1} &= A_d \cdot x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
%x_{k+1} &= (A_d  - B_dK) \cdot x_k + B_dK\delta, 
%\end{align*}
%%
%where $\delta$ is the maximum error that can be introduced by the FWL
%controller in one step, i.e., by reading the states values once and
%multiplying by $K$ once.  We derive the closed form expression for $x_n$ as
%follows:
%%
%\begin{align*}
%x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
%x_{2} 
% &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
%x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta + ... \\  \nonumber & + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
%  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{i=n-1}(A_d - B_dK)^iB_dk\delta. 
%\end{align*}
%
%The definition of asymptotic stability is that the system converges to a
%reference signal, in this case we use no reference signal so an
%asymptotically stable system will converge to the origin.  We know that the
%original system with an infinite-precision controller is stable, because we
%have synthesized it to meet Jury's criterion.  Hence, $(A_d - B_dK)^n x_0$ 
%must converge to zero.
%
%The power series of matrices
%converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less
%than~1 as follows:
%%
%%\begin{align*}
%$\sum_{i=0}^{\infty}T^i  = (I - T)^{-1}$, 
%%\end{align*}
%%
%where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge to the value 
%%
%\begin{align*}
%0 + (I - A_d + B_dK)^{-1}B_dk\delta \,. 
%\end{align*}
%%
%As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the
%safe space, then the synthesized fixed-point controller results in a safe
%closed-loop model.  The convergence to a finite value, however, will not
%make it asymptomatically stable.
%

\end{document}

### 2017-10-11 ase2017/paper.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
added a serial comma before 'and' in the list of authors
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \author{\IEEEauthorblockN{Alessandro Abate$^{1}$, Iury Bessa$^{2}$, Dario Cattaruzza$^{1}$, Lennon Chaves$^{2}$, Lucas Cordeiro$^{1,2}$, \\ 
-Cristina David$^{1}$, Pascal Kesseli$^{1}$, Daniel Kroening$^{1}$ and Elizabeth Polgreen$^{1}$}
+Cristina David$^{1}$, Pascal Kesseli$^{1}$, Daniel Kroening$^{1}$, and Elizabeth Polgreen$^{1}$}
 \IEEEauthorblockA{$^{1}$University of Oxford, Oxford, United Kingdom \\
@@
 Our results in control engineering encourage the application
-of this technique in other fields such as program repair or superoptimisation.
+of this technique in other fields such as program repair or superoptimization.
 %

### 2017-10-12 TACAS2018/paper.tex
Some refinement of the abstract

@@
 %
-We present a sound and automated approach to synthesize safe, digital
-observer-based controllers for physical plants represented as linear,
-time-invariant models.  Models are given as dynamical equations with inputs,
-evolving over a continuous state space and accounting for errors caused by
-the digitization effects of the controller.  We use multi-staged
-counterexample-guided inductive synthesis (CEGIS) with four phases: 1)~We
-create a modular abstraction of the model and feed it to a two stage synthesiser
-to reduce computational cost.  2)~We use the coarsest level of
-abstraction to synthesise an approximate observer-based controller using
-a Bounded Model Checker(BMC), and then  3)~We feed the imprecise result to
-a second synthesiser based on eigendecomposition which uses a more precise
-abstraction to refine the result.
-The BMC is computationally more expensive, but able to reason
-about more complex models, whereas the eigensolver is fast but requires a
-reference candidate solution close to the desired result to guide the synthesis.
-The intuition is that because our solutions form sets of connected spaces, 
-the desired solution lies in the vicinity of a [possibly] unsuitable candidate
-found by the first synthesiser.  4)~The refined candidate solution is still
-unsound.  Safety and other design properties are then verified using continuous
-and discrete-time reachability analysis tools.  If either verification
-fails, a counterexample is provided to the modelling phase, which will refine
-the abstraction based on the type of counter-example and feed it back to
-the synthesisers.  The process iterates until a safe controller is obtained.
-We demonstrate the practical value of this approach by automatically
-synthesizing safe observer-based controllers for physical plant models from
-the digital control literature.
+We present a sound and automated approach to synthesizing safe,
+digital observer-based controllers for physical plants represented as
+linear, time-invariant models.  Models are given as dynamical
+equations with inputs, evolving over a continuous state space and
+accounting for errors caused by the digitization effects of the
+controller.  We use a two-stage counterexample-guided inductive
+synthesis (CEGIS) driven by abstraction refinement: (1) The first,
+coarse, synthesis stage uses a low resolution discretized model of the
+original one and, initially, only looks at static properties of the
+system.  (2) The second synthesis stage uses eigendecomposition to
+refine the imprecise result computed by the first stage.  Whenever the
+second stage is unable to find a candidate solution, it triggers an
+abstraction refinement phase, resulting in a finer abstraction being
+fed back to the first stage.  This design resulted in a significant
+speed-up compared to a traditional single stage one.  We demonstrate
+the practical value of this approach by automatically synthesizing
+safe observer-based controllers for physical plant models from the
+digital control literature.
 %
@@
 
+%\todo{reword paragraph?}
 Using state of the art verifiers, we evaluate these models against
@@
 that rejected candidates are not being discarded due to the
-over-approximation.  The nature of the counterexamples varies depending on
+over-approximation.
+
+\todo{remove until end of enumerate}
+The nature of the counterexamples varies depending on
 the following conditions:

### 2017-10-12 TACAS2018/paper.tex
Some refining of the intro

@@
 
-The coarse synthesiser uses a low resolution discretized model of a 
+We make use of a two-stage counterexample-guided inductive
+synthesis (CEGIS) driven by abstraction refinement.
+The first, coarse, synthesis stage uses a low resolution discretized model of a 
 transformation of the original model. Furthermore, it only looks initially at
 static properties  of the system. This largely reduces the complexity of
-the problem, enabling the synthesiser to offer fast response times. If any 
-of these parameters is inadequate, the refinement loop will supply a better
-abstraction to obtain a feasible answer.
-Due to either numerical imprecision or overapproximations, the candidate
-solution presented by the first synthesiser will likely not meet the spec. A 
-second synthesiser, with a much more precise refinement including a 
-mapping between the real and transformed spaces will create a candidate
-solution that is more adequate to the real model. This second stage uses
-perturbation analysis and therefore requires an initial solution to operate.
-If the second synthesiser is unable to find a candidate solution, it will cue
-the modeller to supply a finer abstraction to the coarse synthesiser which
-will in turn provide a better candiate to the second stage.
-The combined synthesisers are thus capable of reasoning about complex
-models with high computational efficiency due to their modularity.
+the problem, enabling the synthesiser to offer fast response times. %% If any 
+%% of these parameters is inadequate, the refinement loop will supply a better
+%% abstraction to obtain a feasible answer.
+Due to either numerical imprecision or overapproximations, the
+candidate solution presented by the first synthesiser will likely not
+meet the spec. A second synthesis stage, with a much more precise
+refinement including a mapping between the real and transformed spaces
+will create a candidate solution that is more adequate to the real
+model. This second stage uses perturbation analysis and therefore
+requires an initial solution to operate.  Whenever the second stage is
+unable to find a candidate solution, it triggers an abstraction
+refinement phase, resulting in a finer abstraction being fed back to
+the first stage.  The combined synthesisers are thus capable of
+reasoning about complex models with high computational efficiency due
+to their modularity.
 
@@
 abstraction of the concrete domain in both discrete and continuous
-space/time.  This stage uses abstraction refinement when needed to ensure
+space/time.  The verification phase uses abstraction refinement when needed to ensure
 that rejected candidates are not being discarded due to the
@@
 
-\todo{remove until end of enumerate}
-The nature of the counterexamples varies depending on
-the following conditions:
-%
-\begin{enumerate}
-%
-\item Initially, we look for possible errors caused by the restricted domain
-of the synthesisers (e.g., overflows and rounding).  These will typically 
-manifest in the static properties of the system. If an error is found, the
-modeller is signalled to increase the precision of the synthesisers.
-%
-\item Next we explore the nature of the discrete-time progression to mark
-a counterexample that relates to the progression of the system. If such a
-counterexample exists, we indicate its initial conditions and time horizon,
-thus instructing the synthesiser to refine its abstraction with respect to the
-set of initial states and number of iterations. 
-%
-\item Continuous time analysis indicates the need for decreasing the
-sampling time due to continuous excursions outside the safety region in
-between samples.  This changes the problem statement of the synthesiser to a
-new discrete-time model.
-%
-\item A final condition arises when a candidate solution cannot be found,
-thus requiring higher precision of the abstraction numerical representation. 
-We initially consider the plant representation to be too conservative and
-may eventually increase the controller FWL specification when no controller
-can be found for a given precision.
-%
-\end{enumerate}
+%% The nature of the counterexamples varies depending on
+%% the following conditions:
+%% %
+%% \begin{enumerate}
+%% %
+%% \item Initially, we look for possible errors caused by the restricted domain
+%% of the synthesisers (e.g., overflows and rounding).  These will typically 
+%% manifest in the static properties of the system. If an error is found, the
+%% modeller is signalled to increase the precision of the synthesisers.
+%% %
+%% \item Next we explore the nature of the discrete-time progression to mark
+%% a counterexample that relates to the progression of the system. If such a
+%% counterexample exists, we indicate its initial conditions and time horizon,
+%% thus instructing the synthesiser to refine its abstraction with respect to the
+%% set of initial states and number of iterations. 
+%% %
+%% \item Continuous time analysis indicates the need for decreasing the
+%% sampling time due to continuous excursions outside the safety region in
+%% between samples.  This changes the problem statement of the synthesiser to a
+%% new discrete-time model.
+%% %
+%% \item A final condition arises when a candidate solution cannot be found,
+%% thus requiring higher precision of the abstraction numerical representation. 
+%% We initially consider the plant representation to be too conservative and
+%% may eventually increase the controller FWL specification when no controller
+%% can be found for a given precision.
+%% %
+%% \end{enumerate}
 

### 2017-10-12 TACAS2018/paper.tex
Some refining of the intro

@@
 
-%\todo{reword paragraph?}
-Using state of the art verifiers, we evaluate these models against
-automatically synthesised controllers using CEGIS-based synsthesis that
-incorporate the above mentioned artifacts in different models of
-Single-Input/Single-Output (SISO) systems.  We offer a multi-tiered approach
-that exploits different aspects of the problem at each stage.
+%% Using state of the art verifiers, we evaluate these models against
+%% automatically synthesised controllers using CEGIS-based synsthesis that
+%% incorporate the above mentioned artifacts in different models of
+%% Single-Input/Single-Output (SISO) systems.  We offer a multi-tiered approach
+%% that exploits different aspects of the problem at each stage.
 

### 2017-10-12 TACAS2018/paper.tex
reworded sec 3.2

@@
 
+\todo{This section should be integrated later, closer to the use of AA}
+
 The traces of the model starting from an initial set $X_0\subseteq \mathbb{R}^p$, 
@@
 %-------------------------------
-\subsection{Overapproximating continuous time dynamics using discrete models}
-\label{sec:cont_aa}
-%-------------------------------
-
-Thus far we wave discussed the Abstract Accelertion of Discrete Time
-systems.  However, our plant models derive from the discretization of
-continuous time systems.  We therefore seek to establish a sound
-overapproximation which does not only encompass the selected discretization,
-but any chosen discretization in the time domain.
-
-A dynamical system is a system in which a function describes the progression
-of a state over time.  In a continuous domain with linear dynamics, it is
-described by a first order Ordinary Differential Equation (ODE).
-\begin{equation}
-\dot{x}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)% +\vec{w}(t)
-\label{eq:dynamical}
-\end{equation}
-
-%where $\vec{w}$  is a continuous zero-mean white noise source with
-%covariance $N ( 0 , Q )$ 
+\subsection{State-space representation of physical systems}
+\label{sec:ssrepresentation}
+%-------------------------------
+
+%% A dynamical system is a system in which a function describes the progression
+%% of a state over time.  In a continuous domain with linear dynamics, it is
+%% described by a first order Ordinary Differential Equation (ODE).
+%% \begin{equation}
+%% \dot{x}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)% +\vec{w}(t)
+%% \label{eq:dynamical}
+%% \end{equation}
+
+We consider models of physical plants expressed as ordinary differential
+equations (ODEs), which we assume to be controllable:
+%
+\begin{align}
+\label{eq:ode1}
+\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}, 
+\end{align}
+%
+where $t \in \mathbb R_0^+$, where $A$ and $B$ are matrices that 
+specify the continuous plant, and with initial states set as $x(0)$.
+
 Furthermore, a control system may have a derived
@@
 \begin{equation}
+\label{eq:ode2}  
 \vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)
@@
 
-Discretization of a continuous dynamical system turns the ODE into a
-difference equation, assuming zero-order hold for the input $\vec{u}$
-%and continuous integration for the noise $\vec{w}$,
-to
-\begin{align}
-\label{eq:discretization}
-\vec{x}_{k+1} &= \mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\% + \vec{w}_k\\
-y_k &= \mat{C}_d \vec{x}_ k + \mat{D}_d \vec{u}_ k 
-\end{align}
-%with covariance for $\vec{w}_k$, $N ( 0 , Q_d )$
-where
-\begin{align}
-\label{eq:discretize}
-\mat{A}_d &= e^{\mat{A} T_s} = \mathcal{L}^{-1} { ( s \mat{I} - \mat{A} )^{-1} }_{t = T_s}\\
-\mat{B}_d &= \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B} = \mat{A}^{-1} ( \mat{A}_d - \mat{I} ) \mat{B}\\
-\mat{C}_d &= \mat{C}\\
-\mat{D}_d &= \mat{D}
-%\\Q_d &= \int_{t = 0}^{T_s} e^{\mat{A} t} Q e^{\mat{A}^T t} dt
-\end{align}
-and $T_s$ is the sample time. Then
-\begin{align*}
-x(kT_s)=x_k \text{ and } y(kT_s) = y_k, \forall k
-\end{align*}
+In this work, equations~\eqref{eq:ode1} and~\eqref{eq:ode2} is soundly discretized in time (see Section~\ref{sec:cont_aa}) \todo{or use another paper as reference and remove sec .1?} into
+\begin{align}
+\label{eq:plant}
+x_{k+1} = A_d x_k+ B_d u_k\\
+y_{k} = C_d x_k + D_d u_k
+\end{align} 
+%
+where $k \in \mathbb N$ and $x_{0}=x(0)$ is the initial state. 
+$A_d$, $B_d$, $C_d$ and $D_d$ denote the matrices that describe the discretized plant dynamics, whereas $A$, $B$, $C$ and $D$ denote the continuous plant dynamics.  
+%% We synthesize for requirements over this discrete-time domain. 
+%% Later, we will address the issue of variable quantization, 
+%% as introduced by the ADC/DAC conversion blocks (Fig.~\ref{fig:digitalsystem}).
 
@@
 \appendix
+
+%-------------------------------
+\subsection{Overapproximating continuous time dynamics using discrete models}
+\label{sec:cont_aa}
+%-------------------------------
+Our plant models derive from the discretization of
+continuous time systems.  We therefore seek to establish a sound
+overapproximation which does not only encompass the selected discretization,
+but any chosen discretization in the time domain.
+
+A dynamical system is a system in which a function describes the progression
+of a state over time.  In a continuous domain with linear dynamics, it is
+described by a first order Ordinary Differential Equation (ODE).
+\begin{equation}
+\dot{x}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)% +\vec{w}(t)
+\label{eq:dynamical}
+\end{equation}
+
+%where $\vec{w}$  is a continuous zero-mean white noise source with
+%covariance $N ( 0 , Q )$ 
+Furthermore, a control system may have a derived
+output that is a linear combination of its states and inputs, which may
+restricts the observability of the statespace from the output space.
+\begin{equation}
+\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)
+\end{equation}
+
+Discretization of a continuous dynamical system turns the ODE into a
+difference equation, assuming zero-order hold for the input $\vec{u}$
+%and continuous integration for the noise $\vec{w}$,
+to
+\begin{align}
+\label{eq:discretization}
+\vec{x}_{k+1} &= \mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\% + \vec{w}_k\\
+y_k &= \mat{C}_d \vec{x}_ k + \mat{D}_d \vec{u}_ k 
+\end{align}
+%with covariance for $\vec{w}_k$, $N ( 0 , Q_d )$
+where
+\begin{align}
+\label{eq:discretize}
+\mat{A}_d &= e^{\mat{A} T_s} = \mathcal{L}^{-1} { ( s \mat{I} - \mat{A} )^{-1} }_{t = T_s}\\
+\mat{B}_d &= \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B} = \mat{A}^{-1} ( \mat{A}_d - \mat{I} ) \mat{B}\\
+\mat{C}_d &= \mat{C}\\
+\mat{D}_d &= \mat{D}
+%\\Q_d &= \int_{t = 0}^{T_s} e^{\mat{A} t} Q e^{\mat{A}^T t} dt
+\end{align}
+and $T_s$ is the sample time. Then
+\begin{align*}
+x(kT_s)=x_k \text{ and } y(kT_s) = y_k, \forall k
+\end{align*}
+
 %-------------------------------

### 2017-10-12 TACAS2018/paper.tex
edited the numerical representation sec

@@
 
-In this work, equations~\eqref{eq:ode1} and~\eqref{eq:ode2} is soundly discretized in time (see Section~\ref{sec:cont_aa}) \todo{or use another paper as reference and remove sec .1?} into
+In this work, equations~\eqref{eq:ode1} and~\eqref{eq:ode2} is soundly discretized in time (see Appendix~\ref{sec:cont_aa}) \todo{or use another paper as reference and remove sec .1?} into
 \begin{align}
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ \todo{these theorems need more wording. what's their goal here?}
  \begin{theorem}
@@
 
-In embedded software programs interacting and/or simulating physical plants
-it is of great importance to understand the effects of the chosen numeric 
-representation for the continuous state-space and interacting discrete dynamics. 
-\jrronly{
-These representations are almost invariably approximations to the original
-which are assumed to be precise enough as to not cause any trouble,
-but it is precisely this assumption that often results in the most difficult and
-dangerous errors.
-There are generally speaking two formats for representing numbers in
-programs. On one hand we have variable word length types which will
-attempt to use as much memory as needed to precisely represent the
-original domain (usually the reals). In this case the limitations are caused
-by memory and speed, both of which are directly affected by the
-increasingly larger word lengths. Multiple precision floating-point arithmetic
-and software rationals are good examples of these cases. It is possible for
-some of these data types to have memory constraints, at which point they
-fall into the second category.
-Fixed precision data types are most common in software programs.
-}
-Whether they be floating point or fixed point
-\jrronly{ (of which integers are the special case for 0 decimal places) }
-numbers, the problem arises in the misrepresentation of the reals%
-\jrronly{ (or equivalent data type being represented) }.
+The models we consider have two sources of error that are due to numerical  
+representation.  The first is the numerical error introduced by the
+fixed-point numbers employed to model the plant, i.e., to represent the
+plant dynamics $A_d$, $B_d$, $C_d$, $D_d$, $x_k$ and $y_k$.
+The second is the quantization error
+introduced by the digital controller, which performs operations on
+fixed-point numbers.  In this section we outline the notation for the
+representation of numbers, and briefly describe the errors
+introduced.  A~formal discussion is in
+Appendix~\ref{sec:numeric_rep}.
+
 Let $\mathbb{R}_{\langle M,F \rangle}$ be a fixed point domain with $M$ bits
@@
 definition important because it means that the distance between any two
-numbers in the domain depends on the location of those numbers.  Since we
-have shown that a floating point domain is a union of a number of fixed
+numbers in the domain depends on the location of those numbers.  Since
+%we have shown that
+a floating point domain is a union of a number of fixed
 point domains, we will continue our reasoning on fixed point only, which
@@
 numbers will incur errors that can be bound
-by~\cite{DBLP:conf/arith/BrainTRW15}.  We examine the most relevant ones:
-%
-\begin{enumerate}
-\item Truncation\\
-Let $\mathcal{F}_{\langle M,F \rangle}(\cdot) : \mathbb{R} \rightarrow \mathbb{R}_{\langle M,F \rangle}$
-\begin{align*}
-x_{\langle M,F \rangle}=\mathcal{F}_{\langle M,F \rangle}(x) = x-\delta \mid \delta=mod_F(x,c x_{\langle M,F \rangle})
-\end{align*} 
-where $mod_F(\cdot)$ is the modulus operation performed on the last bit of the representation ($2^{-F}$).\\
-The number $\delta$ corresponds to the truncation error of the representation and it will propagate across operations.
-\jrronly{
-%
-It is worth mentioning that not all systems truncate equally.  In the
-definition above $\delta$ may be positive or negative, and even this
-decision can be made dependent on the sign of $x$.  Common cases in computer
-systems are: round downwards (\emph{ie} to $-\infty$), round upwards
-(\emph{ie} to $+\infty$), and round to zero.  Rounding errors are cumulative
-which means the overall error will statistically increase with every
-operation, thus algorithms performing fewer operations can be more precise
-in this respect than iterative ones.
-%
-}
-\item Rounding\\
-Every time an operation is performed on a number in the $\mathbb{R}_{\langle M,F \rangle}$ domain, an error may be
-introduced due to truncation of the result. 
-The following errors appear in simple operations:
-\begin{enumerate}
-\item Addition/Substraction
-\begin{align*}
-&x_{\langle M,F_1\rangle} \pm y_{\langle M,F_2\rangle}=z_{\langle M,F\rangle} + \delta,  F=\text{min}(F_1,F_2)\\
-&\text{ where } |\delta| \leq 2^{-F} \text{ and } F_1=F_2 \Rightarrow \delta=0.
-\end{align*}
-\item Multiplication
-\begin{align*}
-&x_{\langle M,F_1\rangle} * y_{\langle M,F_2\rangle}=z_{\langle M,F\rangle} + \delta, \text{ where } F=F_1+F_2 \text{ and } |\delta| \leq 2^{-F}
-\end{align*}
-%\item Division\\
-%The operations performed by our controllers in the FWL
-%domain do not include division.  However, we do use division in computations
-%at the precision of the plant.  Here the error depends on whether the
-%divisor is greater or smaller than the dividend:  $x_{\langle M,F_1\rangle} / y_{\langle M,F_2 \rangle} = c_3 + \delta_{T3}$
-%where $\delta_{T3}$ is $(\delta_{T2}\cdot x - \delta_{T1}\cdot y)/(\delta_{T2}^2 - \delta_{T2} y)$,
-\end{enumerate}
-
-\jrronly{
-\item Overflow\\
-Another source of error introduced by Finite Word Length representations is that of overflow.
-The finite word length set a maximum representable number in the domain
-$\pm \overline{M} \mid \overline{M}=2^{M-F}-2^{-F}$, which means that any number
-outside this range cannot be accurately represented by the domain (\emph{eg} $\delta=x-\overline{M}$).
-In the case of floating point, a special cases for infinity has been introduced, which addresses
-some of these issues, but once the error has gone to infinity, the numbers become meaningless.
-It is the responsibility of software designers and tools to account for overflows and either
-supply saturation functions to prevent them or raise alarms in their presence. In the case
-of verification, the latter is seen as a safety problem.
-\item Null/Zeno behaviour\\
-Whilst this work does not explore the effect of Zeno behaviours, it is worth noting that this
-effect may also be caused by rounding errors in floating point programs. The reason for this
-is that if an operation contains two numbers which belong to disjoint sub-domains
-(\emph{ie} neither number can be represented in the domain of its counterpart), the
-resulting operation may become a no-op/skip, subsequently destabilizing the program.
-}
-\end{enumerate}
+by~\cite{DBLP:conf/arith/BrainTRW15}.
+
 We will use the domain $\mathbb{R}_{\langle C \rangle} \mid \langle C \rangle = \langle M_c,F_c \rangle$
@@
 to represent the domain of the plant model.
-Thus any mathematical operations in our modelled digital controller will be executed in the
+Thus, any mathematical operations in our modelled digital controller will be executed in the
 domain $\mathbb{R}_{\langle C \rangle}$, and all other calculations
 in our model will be carried out in the domain $\mathbb{R}_{\langle
-P \rangle}$.  The physical plant operates in the reals, which means
-our verification phase must also account for the numerical error caused by representing the
-physical plant at the finite precision $\mathbb{R}_{\langle P \rangle}$.
-
-We will use these subindices to represent functions, number, vectors and matrices in their
-corresponding domains. We further note that by choosing $\langle C \rangle = \langle M_c,[E_c] \rangle$
+  P \rangle}$.
+%% The physical plant operates in the reals, which means
+%% our verification phase must also account for the numerical error caused by representing the
+%% physical plant at the finite precision $\mathbb{R}_{\langle P \rangle}$.
+
+%% We will use these subindices to represent functions, number, vectors and matrices in their
+%% corresponding domains.
+
+\todo{unclear}
+We further note that by choosing $\langle C \rangle = \langle M_c,[E_c] \rangle$
 we extend the following to floating point reasoning.
+
+%% \subsubsection{Effect on safety specification and stability}
+
+%% Let us first consider the effect of the quantization errors on safety. 
+%% Within the controller, state values are manipulated at low precision,
+%% alongside the vector multiplication $Kx$.
+%% %
+%% %computed considering the error introduced by the digital controller caused by performing the vector multiplication $Kx$ at low digital precision.
+%% The inputs are computed using the following equation: 
+%% %
+%% \begin{align*}
+%% u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})). 
+%% \end{align*}
+
+%% This induces two types of the errors detailed above: first, the truncation
+%% error due to representing $x_k$ as $\mathcal{F}{\langle I_c,F_c
+%% \rangle}(x_{k})$; and second, the rounding error introduced by the
+%% multiplication operation.  We represent these errors as non-deterministic
+%% additive noise.%, which might de-stabilize the closed-loop model.
+
+%% An additional error is due to the representation of the plant dynamics, namely 
+%% %
+%% \begin{align*}
+%% x_{k+1} &=\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
+%% \end{align*}
+%% We address this error by use of interval
+%% arithmetic~\cite{moore1966interval} in the verification phase.
+
+%% Previous studies~\cite{gangli1} show that the FWL affects the poles and
+%% zeros positions, degrading the closed-loop dynamics, causing steady-state
+%% errors (see Appendix~\ref{sec:appendix:LTIbackground} for details) and
+%% eventually de-stabilizing the system~\cite{Bessa16}.  However, since in this
+%% paper we require stability only as a precursor to safety, it is sufficient
+%% to check that the (perturbed, noisy) model converges to a neighborhood of
+%% the equilibrium within the safe set (see Appendix~\ref{sec:stab_FWL}).
+
+%% In the following, we shall disregard these steady-state errors (caused by
+%% FWL effects) when stability is ensured by synthesis, and then verify its
+%% safety accounting for the finite-precision errors.
 
@@
 multiplication operation.  We represent these errors as non-deterministic
-additive noise.
-
-Let $q_c=2^{-F_c},q_a=2^{-F_a},q_d=2^{-F_d}$ be the smallest difference
-between two numbers in their corresponding domains.  Assuming that our
-system truncates numbers to the nearest value, this means thet the error
-$\delta$ introduced by the function $\mathcal{F}_{\langle * \rangle}$ is
-$\delta_*=\mathcal{F}_{\langle * \rangle}(x)-x \in \left[-\frac{q_*}{2}\
-\frac{q_*}{2}\right]$.  We note that in the case of floating point,the
-choice of $F$ is taken from the largest multiplication found (e.g.,
-$|\mat{A}|_1|\vec{x}|_\infty \mid \vec{x} \models \phi_\mathit{safety}$,
-where $\phi_\mathit{safety}$ is defined in \ref{eq:safetyspec}). From these
-equations we can define:
-%
-\begin{align*}
-\nu_1 \in \left[-\frac{q_a}{2}\ \frac{q_a}{2}\right] \cap  \left[-\frac{q_c}{2}\ \frac{q_c}{2}\right],
-\nu_2 \in \left[-\frac{q_d}{2}\ \frac{q_d}{2}\right]
-\end{align*}
-
-We may also bound $\nu_2'$ from \eqref{eq:uk} as follollows:
-\begin{align*}
-\delta\left(\mat{K}_{\langle C\rangle} \vec{x}_{\langle C\rangle} \right) &\in \left[ -p \frac{q_c}{2}\ \ p \frac{q_c}{2}\right]\\
-{\vec{\nu_e}}_i &\in \left[ -(p+2) \frac{q_c}{2}\ \ (p+2) \frac{q_c}{2}\right], i \in [1, p]\\
-\Rightarrow \nu_2' &\in \left[  -p(|\mat{K}_{\langle C \rangle}|_1+2) \frac{q_c}{2}\ \ p(|\mat{K}_{\langle C \rangle}|_1+2) \frac{q_c}{2}\right]
-\end{align*}
-Similarly we also find
-\begin{align*}
-\nu_1' &\in \left[  -p(|{\mat{C}_d}_{\langle C \rangle}|_1+2) \frac{q_c}{2}\ \ p(|{\mat{C}_d}_{\langle C \rangle}|_1+2) \frac{q_c}{2}\right]
-\end{align*}
-The proof derives from $|\mat{K}\vec{x}| \leq |\mat{K}|_1|\vec{x}|_\infty$.
+additive noise. More details can be found in Appendix~\ref{appendix:quantization}.
 
@@
 
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Numerical representation and soundness} 
+\label{sec:numeric_rep}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+In embedded software programs interacting and/or simulating physical plants
+it is of great importance to understand the effects of the chosen numeric 
+representation for the continuous state-space and interacting discrete dynamics. 
+\jrronly{
+These representations are almost invariably approximations to the original
+which are assumed to be precise enough as to not cause any trouble,
+but it is precisely this assumption that often results in the most difficult and
+dangerous errors.
+There are generally speaking two formats for representing numbers in
+programs. On one hand we have variable word length types which will
+attempt to use as much memory as needed to precisely represent the
+original domain (usually the reals). In this case the limitations are caused
+by memory and speed, both of which are directly affected by the
+increasingly larger word lengths. Multiple precision floating-point arithmetic
+and software rationals are good examples of these cases. It is possible for
+some of these data types to have memory constraints, at which point they
+fall into the second category.
+Fixed precision data types are most common in software programs.
+}
+Whether they be floating point or fixed point
+\jrronly{ (of which integers are the special case for 0 decimal places) }
+numbers, the problem arises in the misrepresentation of the reals%
+\jrronly{ (or equivalent data type being represented) }.
+Let $\mathbb{R}_{\langle M,F \rangle}$ be a fixed point domain with $M$ bits
+representing the binary word length of the representation and $F$ bits
+representing the prescaling $2^{-F}$ (\emph{i.e} the number of bits after
+the decimal place).  We note that a negative $F$ denotes an integer
+multiplication that adds $-F$ trailing zeros in the number represented by
+$M$.  Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point
+domain with $M$ bits mantissa and $E$ bits exponent.  This domain
+corresponds to $$\mathbb{R}_{\langle M,[E] \rangle} = \bigcup_F
+\mathbb{R}_{\langle M,F \rangle} \mid F \in [2^{1-E}, 2^{E-1}]$$ This
+definition important because it means that the distance between any two
+numbers in the domain depends on the location of those numbers.  Since we
+have shown that a floating point domain is a union of a number of fixed
+point domains, we will continue our reasoning on fixed point only, which
+will apply to the floating point domain by extension.  Operations on these
+numbers will incur errors that can be bound
+by~\cite{DBLP:conf/arith/BrainTRW15}.  We examine the most relevant ones:
+%
+\begin{enumerate}
+\item Truncation\\
+Let $\mathcal{F}_{\langle M,F \rangle}(\cdot) : \mathbb{R} \rightarrow \mathbb{R}_{\langle M,F \rangle}$
+\begin{align*}
+x_{\langle M,F \rangle}=\mathcal{F}_{\langle M,F \rangle}(x) = x-\delta \mid \delta=mod_F(x,c x_{\langle M,F \rangle})
+\end{align*} 
+where $mod_F(\cdot)$ is the modulus operation performed on the last bit of the representation ($2^{-F}$).\\
+The number $\delta$ corresponds to the truncation error of the representation and it will propagate across operations.
+\jrronly{
+%
+It is worth mentioning that not all systems truncate equally.  In the
+definition above $\delta$ may be positive or negative, and even this
+decision can be made dependent on the sign of $x$.  Common cases in computer
+systems are: round downwards (\emph{ie} to $-\infty$), round upwards
+(\emph{ie} to $+\infty$), and round to zero.  Rounding errors are cumulative
+which means the overall error will statistically increase with every
+operation, thus algorithms performing fewer operations can be more precise
+in this respect than iterative ones.
+%
+}
+\item Rounding\\
+Every time an operation is performed on a number in the $\mathbb{R}_{\langle M,F \rangle}$ domain, an error may be
+introduced due to truncation of the result. 
+The following errors appear in simple operations:
+\begin{enumerate}
+\item Addition/Substraction
+\begin{align*}
+&x_{\langle M,F_1\rangle} \pm y_{\langle M,F_2\rangle}=z_{\langle M,F\rangle} + \delta,  F=\text{min}(F_1,F_2)\\
+&\text{ where } |\delta| \leq 2^{-F} \text{ and } F_1=F_2 \Rightarrow \delta=0.
+\end{align*}
+\item Multiplication
+\begin{align*}
+&x_{\langle M,F_1\rangle} * y_{\langle M,F_2\rangle}=z_{\langle M,F\rangle} + \delta, \text{ where } F=F_1+F_2 \text{ and } |\delta| \leq 2^{-F}
+\end{align*}
+%\item Division\\
+%The operations performed by our controllers in the FWL
+%domain do not include division.  However, we do use division in computations
+%at the precision of the plant.  Here the error depends on whether the
+%divisor is greater or smaller than the dividend:  $x_{\langle M,F_1\rangle} / y_{\langle M,F_2 \rangle} = c_3 + \delta_{T3}$
+%where $\delta_{T3}$ is $(\delta_{T2}\cdot x - \delta_{T1}\cdot y)/(\delta_{T2}^2 - \delta_{T2} y)$,
+\end{enumerate}
+
+\jrronly{
+\item Overflow\\
+Another source of error introduced by Finite Word Length representations is that of overflow.
+The finite word length set a maximum representable number in the domain
+$\pm \overline{M} \mid \overline{M}=2^{M-F}-2^{-F}$, which means that any number
+outside this range cannot be accurately represented by the domain (\emph{eg} $\delta=x-\overline{M}$).
+In the case of floating point, a special cases for infinity has been introduced, which addresses
+some of these issues, but once the error has gone to infinity, the numbers become meaningless.
+It is the responsibility of software designers and tools to account for overflows and either
+supply saturation functions to prevent them or raise alarms in their presence. In the case
+of verification, the latter is seen as a safety problem.
+\item Null/Zeno behaviour\\
+Whilst this work does not explore the effect of Zeno behaviours, it is worth noting that this
+effect may also be caused by rounding errors in floating point programs. The reason for this
+is that if an operation contains two numbers which belong to disjoint sub-domains
+(\emph{ie} neither number can be represented in the domain of its counterpart), the
+resulting operation may become a no-op/skip, subsequently destabilizing the program.
+}
+\end{enumerate}
+We will use the domain $\mathbb{R}_{\langle C \rangle} \mid \langle C \rangle = \langle M_c,F_c \rangle$
+to represent the fixed point precision of the controller, and 
+$\mathbb{R}_{\langle P \rangle} \supseteq \mathbb{R}_{\langle C \rangle}$
+to represent the domain of the plant model.
+Thus any mathematical operations in our modelled digital controller will be executed in the
+domain $\mathbb{R}_{\langle C \rangle}$, and all other calculations
+in our model will be carried out in the domain $\mathbb{R}_{\langle
+P \rangle}$.  The physical plant operates in the reals, which means
+our verification phase must also account for the numerical error caused by representing the
+physical plant at the finite precision $\mathbb{R}_{\langle P \rangle}$.
+
+We will use these subindices to represent functions, number, vectors and matrices in their
+corresponding domains. We further note that by choosing $\langle C \rangle = \langle M_c,[E_c] \rangle$
+we extend the following to floating point reasoning.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsubsection{Quantization error}
+\label{appendix:quantization}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Let $q_c=2^{-F_c},q_a=2^{-F_a},q_d=2^{-F_d}$ be the smallest difference
+between two numbers in their corresponding domains.  Assuming that our
+system truncates numbers to the nearest value, this means thet the error
+$\delta$ introduced by the function $\mathcal{F}_{\langle * \rangle}$ is
+$\delta_*=\mathcal{F}_{\langle * \rangle}(x)-x \in \left[-\frac{q_*}{2}\
+\frac{q_*}{2}\right]$.  We note that in the case of floating point,the
+choice of $F$ is taken from the largest multiplication found (e.g.,
+$|\mat{A}|_1|\vec{x}|_\infty \mid \vec{x} \models \phi_\mathit{safety}$,
+where $\phi_\mathit{safety}$ is defined in \ref{eq:safetyspec}). From these
+equations we can define:
+%
+\begin{align*}
+\nu_1 \in \left[-\frac{q_a}{2}\ \frac{q_a}{2}\right] \cap  \left[-\frac{q_c}{2}\ \frac{q_c}{2}\right],
+\nu_2 \in \left[-\frac{q_d}{2}\ \frac{q_d}{2}\right]
+\end{align*}
+
+We may also bound $\nu_2'$ from \eqref{eq:uk} as follollows:
+\begin{align*}
+\delta\left(\mat{K}_{\langle C\rangle} \vec{x}_{\langle C\rangle} \right) &\in \left[ -p \frac{q_c}{2}\ \ p \frac{q_c}{2}\right]\\
+{\vec{\nu_e}}_i &\in \left[ -(p+2) \frac{q_c}{2}\ \ (p+2) \frac{q_c}{2}\right], i \in [1, p]\\
+\Rightarrow \nu_2' &\in \left[  -p(|\mat{K}_{\langle C \rangle}|_1+2) \frac{q_c}{2}\ \ p(|\mat{K}_{\langle C \rangle}|_1+2) \frac{q_c}{2}\right]
+\end{align*}
+Similarly we also find
+\begin{align*}
+\nu_1' &\in \left[  -p(|{\mat{C}_d}_{\langle C \rangle}|_1+2) \frac{q_c}{2}\ \ p(|{\mat{C}_d}_{\langle C \rangle}|_1+2) \frac{q_c}{2}\right]
+\end{align*}
+The proof derives from $|\mat{K}\vec{x}| \leq |\mat{K}|_1|\vec{x}|_\infty$.
+
 %-------------------------------

### 2017-10-12 TACAS2018/paper.tex
more on the numerical representation sec

@@
 multiplication that adds $-F$ trailing zeros in the number represented by
-$M$.  Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point
+$M$.
+\todo{why do we need to go into floating point?}
+Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point
 domain with $M$ bits mantissa and $E$ bits exponent.  This domain
@@
 Within the controller, state values are manipulated at low precision,
-alongside the vector multiplication $\mat{K}\vec{x}$. Furthermore, 
+alongside the vector multiplication $\mat{K}\vec{x}$.
+\todo{$\mathcal{F}$ is not clearly defined}
+Furthermore, 
 the quantizers for the DAC and the ADC introduce truncation errors
@@
 
-This induces two types of the errors detailed above: first, the truncation
+This induces two types of the errors: first, the truncation
 error due to the domain transformations $\mathcal{F}_{\langle *
@@
 multiplication that adds $-F$ trailing zeros in the number represented by
-$M$.  Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point
+$M$.
+Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point
 domain with $M$ bits mantissa and $E$ bits exponent.  This domain

### 2017-10-12 TACAS2018/paper.tex
some comments

@@
  \todo{these theorems need more wording. what's their goal here?}
+ \todo{It's not clear to me why you look at all these symtems.}
  \begin{theorem}
@@
 %-------------------------------
+\todo{this needs some explanation before the theorem in order to explain the purpose of this section.}
 
@@
 \end{figure*}
+
+\todo{explain the purpose of this section, challenges etc...}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-10-12 TACAS2018/paper.tex
Addressed Cristina's comments

@@
 %
-where $ \vec{x}_0 \in X_0$ and $\forall k\geq 0, \vec{x}_{k+1} = \tau(\vec{x}_k,\vec{u}_k) $, 
+where $ \vec{x}_0 \in X_0$ and $\forall k\geq 0, \vec{u}_k \in U \text{ and } \vec{x}_{k+1} = \tau(\vec{x}_k,\vec{u}_k) $, 
 where 
@@
 \big( \mat{A}\vec{x}_k +
-\mat{B}\vec{u}_k \mid \mat{G}\vec{x}_k \leq \vec{h} \wedge \vec{u}_k \in U \big) \;. 
+\mat{B}\vec{u}_k \mid \mat{G}\vec{x}_k \leq \vec{h}\big)\;. 
 \end{equation}
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ \subsection{Verification of Continuous time systems}\label{sec:continuous_time_accel}
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+The main problem with the above discretization is that is does not allow us to observe the system at arbitrary points in time, only at integer multiples of the sample time.
+While this is adequate for the controller, it is not sufficient for verification.
+We must therefore establish a new model that allows us to observe the system at a given time $t$.
+We achieve this by using acceleration as described below.
+
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
  \subsubsection{Discrete dynamics using reals for systems without inputs}\label{sec:real_discrete_no_inputs}
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \todo{these theorems need more wording. what's their goal here?}
- \todo{It's not clear to me why you look at all these symtems.}
  \begin{theorem}
@@
 $M$.
-\todo{why do we need to go into floating point?}
-Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point
-domain with $M$ bits mantissa and $E$ bits exponent.  This domain
-corresponds to $$\mathbb{R}_{\langle M,[E] \rangle} = \bigcup_F
-\mathbb{R}_{\langle M,F \rangle} \mid F \in [2^{1-E}, 2^{E-1}]$$ This
-definition important because it means that the distance between any two
-numbers in the domain depends on the location of those numbers.  Since
-%we have shown that
-a floating point domain is a union of a number of fixed
-point domains, we will continue our reasoning on fixed point only, which
-will apply to the floating point domain by extension.  Operations on these
-numbers will incur errors that can be bound
-by~\cite{DBLP:conf/arith/BrainTRW15}.
+%Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point
+%domain with $M$ bits mantissa and $E$ bits exponent.  This domain
+%corresponds to $$\mathbb{R}_{\langle M,[E] \rangle} = \bigcup_F
+%\mathbb{R}_{\langle M,F \rangle} \mid F \in [2^{1-E}, 2^{E-1}]$$ This
+%definition important because it means that the distance between any two
+%numbers in the domain depends on the location of those numbers.  Since
+%a floating point domain is a union of a number of fixed
+%point domains, we will continue our reasoning on fixed point only, which
+%will apply to the floating point domain by extension.  Operations on these
+%numbers will incur errors that can be bound
+%by~\cite{DBLP:conf/arith/BrainTRW15}.
 
@@
 domain $\mathbb{R}_{\langle C \rangle}$, and all other calculations
-in our model will be carried out in the domain $\mathbb{R}_{\langle
-  P \rangle}$.
+in our model will be carried out in the domain $\mathbb{R}_{\langle P \rangle}$.
+Given ${\langle M,F \rangle}$ we use $\mathcal{F}_{\langle M,F \rangle} : \mathbb{R} \rightarrow \mathbb{R}_{\langle M,F \rangle}$ as the truncation function.
+
 %% The physical plant operates in the reals, which means
@@
 
-\todo{unclear}
-We further note that by choosing $\langle C \rangle = \langle M_c,[E_c] \rangle$
-we extend the following to floating point reasoning.
+%\todo{unclear}
+%We further note that by choosing $\langle C \rangle = \langle M_c,[E_c] \rangle$
+%we extend the following to floating point reasoning.
 
@@
 alongside the vector multiplication $\mat{K}\vec{x}$.
-\todo{$\mathcal{F}$ is not clearly defined}
 Furthermore, 
@@
 %-------------------------------
-\todo{this needs some explanation before the theorem in order to explain the purpose of this section.}
+In many cases the speed of the response, i.e. how fast it converges to the set point, is a requirement of great importance. 
+This is given as a settling time for the system to become stable.
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+In most real implementations, the internal state of a plant cannot be directly measured. All we can do is infer its
+value through its effecton the output. A plant model that minimises the difference between the outputs is called
+an observer and it is a well known paradigm in the control literature\cite{astrom1997computer}. Since we are
+interested in synthesising controllers with observer designs, we need to look at the challenges presented by 
+the introduction of the observer.
+
 \begin{figure*}[htb]
@@
 
-\todo{explain the purpose of this section, challenges etc...}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 \begin{align*}
-x(kT_s)=x_k \text{ and } y(kT_s) = y_k, \forall k
+\forall k, x(kT_s)=x_k \text{ and } y(kT_s) = y_k
 \end{align*}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Numerical representation and soundness} 
+\section{Numerical representation and soundness} 
 \label{sec:numeric_rep}
@@
 \item Truncation\\
-Let $\mathcal{F}_{\langle M,F \rangle}(\cdot) : \mathbb{R} \rightarrow \mathbb{R}_{\langle M,F \rangle}$
+Let $\mathcal{F}_{\langle M,F \rangle} : \mathbb{R} \rightarrow \mathbb{R}_{\langle M,F \rangle}$
+be a truncation function, defined as:
 \begin{align*}

### 2017-10-13 TACAS2018/paper.tex
Added Cristina
some comments

@@
 
-\author{Dario Cattaruzza, Alessandro Abate, Daniel Kroening}%\email{alessandro.abate@cs.ox.ac.uk}
+\author{Dario Cattaruzza, Alessandro Abate, Cristina David, Daniel Kroening}%\email{alessandro.abate@cs.ox.ac.uk}
 %\email{dario.cattaruzza@cs.ox.ac.uk}
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ \todo{I find this section header unclear. What is being verified here? Stability and safety only come later on.}
  The main problem with the above discretization is that is does not allow us to observe the system at arbitrary points in time, only at integer multiples of the sample time.
@@
 We must therefore establish a new model that allows us to observe the system at a given time $t$.
-We achieve this by using acceleration as described below.
+ %We achieve this by using acceleration as described below.
+
+ \todo{Again, it's not clear to me what ``not sufficient for verification'' means here.}
+
+ \todo{Are all three cases, i.e. discrete dynamics using reals for systems without inputs,
+   discrete dynamics using reals for systems with parametric inputs, discrete dynamics using reals for systems with discrete time feedback inputs, relevant?
+If they are, then having a sentence describing the progression in this section would be useful.}
 
@@
  \begin{theorem}
- Given $\dot{\vec{x}}=\mat{A}\vec{x}$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, the expression
+ Given $\dot{\vec{x}}=\mat{A}\vec{x}$ \todo{$\dot{\vec{x}}(t)$?}, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, the expression
  \begin{align}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\todo{How does fit in the description at the beginning of sec 3.3?}
 
@@
 
+\todo{equations \eqref{eq:feedback_sampled_cont} and
+  \eqref{eq:feedback_cont} are in the appendix so it's preferable to not
+refer to them so directly.}
 Let us look at equations \eqref{eq:feedback_sampled_cont} and

### 2017-10-13 TACAS2018/paper.tex
comments/edits sec 5

@@
 \end{equation}
-where $0\leq p_s \leq 1$ is the desired percentage of the target within to remain after $t_s$.
+where $0\leq p_s \leq 1$ is the desired percentage of the target within \todo{typo?} to remain after $t_s$.
 \end{theorem}
@@
 
-In most real implementations, the internal state of a plant cannot be directly measured. All we can do is infer its
-value through its effecton the output. A plant model that minimises the difference between the outputs is called
-an observer and it is a well known paradigm in the control literature\cite{astrom1997computer}. Since we are
-interested in synthesising controllers with observer designs, we need to look at the challenges presented by 
-the introduction of the observer.
+In most real implementations, the internal state of a plant cannot be
+directly measured but rather inferred from its
+effect on the output. A plant model that minimises the difference
+between the outputs is called an observer and it is a well known
+paradigm in the control literature~\cite{astrom1997computer}. Since we
+are interested in synthesising controllers with observer designs, in this
+section we will look at checking stability and safety in the presence of an observer.
+
+%the challenges presented by the introduction of the observer.
 
@@
 As stated in Section~\ref{ssec:stabspecification}, we use Jury's Criterion
-to assert this specification.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Safety of a Digitally Observed System}\label{sec:cof_safety}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Now that we have established convergence, we may examine the safety
-specification of the state space.  In the case of SISO systems, this is
-given by a range of the input and a range of the output which are considered
-safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in
-[\underline{y}\ \ \overline{y}]$).  Whilst there are other properties we may
-include in the verification, we will solely focus on these for simplicity of
-the explanation.  We will assume that we do not want saturation in our
-system, hence the control loop has only one mode.  We have also identified
-the quantization noise as a bounded non-deterministic input.  First we must
-translate the safety specification into the statespace.  Replacing on the
-second part of equation \eqref{eq:observer_LTI_cf} we obtain
-%
-\begin{equation}
-\phi_{safety} := \underline{y}<\mat{C}\vec{x}_k<\overline{y}, \forall k \geq 0
-\label{eq:of_bounds}
-\end{equation}
-%
-%Note that we use the bounds of the input after the transformation by $\mat{B}$ since the matrix may reverse the bounds. 
-%
-Equation~\eqref{eq:of_bounds} can be solved using linear programming as it
-describes a polyhedral region in $\mathbb{R}^p$.  The second step is
-evaluating the progression of the system over time in order to calculate
-$\vec{x}_k$ to validate against this specification.  For this step we require
-an initial set from which the system progresses.  Obviously, this set
-$\vec{x}_0$ must satisfy the specification, otherwise the system will be
-unsafe to begin with.  We will accept a specification in the form
-$\mat{E}\mat{T}\vec{x}_0<\mat{f}$.  The presence of $\mat{T}$ is because
-this will typically be given in the original state-space.
+to assert this specification. \todo{Not clear to me what ``this specification'' refers to.}
 
@@
 
-Thus far we have presented a verification procedure for a continuous plant
-in discretized time domain (i.e., the range of the quatizers is still
-$\mathbb{R}$).  The next step we must reaize is that the controller and the
+Thus far we looked at checking stability
+%have presented a verification procedure for
+of a continuous plant in discretized time domain (i.e., the range of the quatizers is still
+$\mathbb{R}$) \todo{do you mean that we only considered time domains discretization until now and
+now we look at value domain discretization as well?}.  The next step we must realize is that the controller and the
 observer exist in a digital program, hence their domain is
@@
 representation errors of the FWL domain.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Safety of a Digitally Observed System}\label{sec:cof_safety}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+%% Now that we have established convergence, we may examine the safety
+%% specification of the state space.
+In the case of SISO systems, the safety specification is
+given by a range of the input and a range of the output which are considered
+safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in
+[\underline{y}\ \ \overline{y}]$)
+\todo{I think the safety specification is generally on the states of the system.}.
+Whilst there are other properties we may
+include in the verification, we will solely focus on these for simplicity of
+the explanation.  We assume that we do not want saturation in our
+system, hence the control loop has only one mode.
+%We have also identified the quantization noise as a bounded non-deterministic input.
+First we must
+translate the safety specification into the statespace.  Replacing on the
+second part of equation \eqref{eq:observer_LTI_cf} we obtain
+%
+\begin{equation}
+\phi_{safety} := \underline{y}<\mat{C}\vec{x}_k<\overline{y}, \forall k \geq 0
+\label{eq:of_bounds}
+\end{equation}
+\todo{what happened to u when going from \eqref{eq:observer_LTI_cf}?}
+%
+%Note that we use the bounds of the input after the transformation by $\mat{B}$ since the matrix may reverse the bounds. 
+%
+\todo{I thought \eqref{eq:of_bounds} was the safety spec. Why is it solved?}
+Equation~\eqref{eq:of_bounds} can be solved using linear programming as it
+describes a polyhedral region in $\mathbb{R}^p$.  The second \todo{second?} step is
+evaluating the progression of the system over time in order to calculate
+$\vec{x}_k$ to validate against this specification.  For this step we require
+an initial set $\vec{x}_0$ from which the system progresses.  Obviously, this set
+%$\vec{x}_0$
+must satisfy the specification, otherwise the system will be
+unsafe to begin with.  We will accept a specification in the form
+$\mat{E}\mat{T}\vec{x}_0<\mat{f}$ \todo{ET? f?}.  The presence of $\mat{T}$ is because
+this will typically be given in the original state-space.
 

### 2017-10-13 TACAS2018/paper.tex
more comments
editing sec 6

@@
 %
+\todo{shouldn't this be over the states of the system?}
 \begin{align}
@@
 
-In order to synthesize closed-loop digital control systems, we use a program
-synthesis engine.  Our program implements Counter-Example Guided
-Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}.  We
-start by presenting its general architecture followed by describing the
-parts specific to closed-loop control systems.
-
-CEGIS-based control synthesis requires a formal verifier to check whether a
-candidate controller meets the requirements when combined with the plant.
-We use the tool Axelerator~\cite{} in the verification module.  It checks the
-stability of a cyberphysical closed-loop control system and considers finite-word
-length (FWL) effects in the digital controller and continuous dynamics in continuous
-time progression in the plant.
-As part of the counterexample, Axelerator generates an ANSI-C code model
-containing information about different transforms of the system as well as other
-abstractions relating to quantization and safety which allow us to create models
-for the synthesisers. This specification (which we refer to as $\phi$) is passed to
-the Bounded Model Checker CBMC~\cite{ClarkeKL04} which uses SAT solving to
-generate a valid input for a controller and observer that meet the given specification.
-The ANSI-C code model guarantees that a synthesized solution is complete and
-sound with respect to the given abstraction since it does not depend on system
-inputs and outputs, but further analysis is required to obatin a solution that meets
-the original specification. These results are then fed back to a synthesis module in
-Axelerator which uses eigendecomposition and other linear transformations to
-refine the solution.
-
-%-------------------------------
-\subsection{CEGIS of digital controllers} 
-\label{sssec:cegisdig}
-%-------------------------------
+In this section, we describe our technique for synthesizing safe
+digital feedback controllers using CEGIS. Broadly speaking, CEGIS
+denotes an iterative technique where each iteration performs inductive
+generalisation based on counterexamples provided by a verification
+engine.
+
+%% In order to synthesize closed-loop digital control systems, we use a program
+%% synthesis engine.  Our program implements Counter-Example Guided
+%% Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}.  We
+%% start by presenting its general architecture followed by describing the
+%% parts specific to closed-loop control systems.
+
+%% CEGIS-based control synthesis requires a formal verifier to check whether a
+%% candidate controller meets the requirements when combined with the plant.
+%% We use the tool Axelerator~\cite{} in the verification module.  It checks the
+%% stability of a cyberphysical closed-loop control system and considers finite-word
+%% length (FWL) effects in the digital controller and continuous dynamics in continuous
+%% time progression in the plant.
+%% As part of the counterexample, Axelerator generates an ANSI-C code model
+%% containing information about different transforms of the system as well as other
+%% abstractions relating to quantization and safety which allow us to create models
+%% for the synthesisers. This specification (which we refer to as $\phi$) is passed to
+%% the Bounded Model Checker CBMC~\cite{ClarkeKL04} which uses SAT solving to
+%% generate a valid input for a controller and observer that meet the given specification.
+%% The ANSI-C code model guarantees that a synthesized solution is complete and
+%% sound with respect to the given abstraction since it does not depend on system
+%% inputs and outputs, but further analysis is required to obatin a solution that meets
+%% the original specification. These results are then fed back to a synthesis module in
+%% Axelerator which uses eigendecomposition and other linear transformations to
+%% refine the solution.
+
+%% %-------------------------------
+%% \subsection{CEGIS of digital controllers} 
+%% \label{sssec:cegisdig}
+%% %-------------------------------
 
@@
 The benchmark suite employed to evaluate the proposed technique is 
-composed by 18 MIMO models extracted from the literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15,maglev,converters}
+composed by 18 MIMO models extracted from the literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15,maglev,converters}.
+
+In the verification module, we use the tool Axelerator~\cite{} .
 

### 2017-10-13 TACAS2018/paper.tex
Moved jury's criterion to the appendix

@@
 
-There are a number of algorithms that can be
-used for stability analysis~\cite{daes20161,Bessa16}.
-Since the canonical forms used in this work use the coefficients of the
-characteristic polynomial $S(z)$ as opposed to its roots (which are
-extremely hard to calculate for a SAT solver), we choose Jury's
-criterion~\cite{astrom1997computer} to check the stability in the
-$z$-domain in view of its efficiency.
-
-We~consider the following form for $S(z)$:
-%
-\begin{equation*}
-S(z) = z^{p}+a_1z^{p-1}+\cdots+a_{p-1}z+a_p.
-\end{equation*}
-
-and build the matrix
-$\mat{M} \in \mathbb{R}^{p \times p}$ from its coefficients such that:
-%
-\begin{align*}
-\mat{M}_{1,j}&=a_j\\
-\mat{M}_{i+1,j}&=\left\{
-\begin{array}{ll}
-0,&j>p'\\
-\mat{M}_{i,j}-\mat{M}_{i,p'-j+1}\frac{\mat{M}_{i,1}}{\mat{M}_{i,p'}} &j\leq p'
-\end{array}
-\right.\\
-p'&=p-i+1
-\end{align*}
-%
-$S(z)$ is the characteristic polynomial of a stable system if and
-only if the following conditions hold~\cite{astrom1997computer}:
-\begin{align*}
-\phi_\mathit{stability}(S) \equiv
-(S(1) > 0) \wedge ((-1)^p S(-1) > 0) \wedge (|a_p| < 1) \wedge \bigwedge\limits_{i=1}^p (\mat{M}_{i,1} > 0).
-\end{align*}
+In this work we are interested in asymptotic stability: asymptotic
+stability is a property that amounts to convergence of the model
+executions to an equilibrium point, starting from any states in a
+neighborhood of the point.
+
+%% There are a number of algorithms that can be
+%% used for stability analysis~\cite{daes20161,Bessa16}.
+
+A discrete-time LTI system is
+asymptotically stable if all the roots of its characteristic
+polynomial (i.e., the eigenvalues of the closed-loop matrix $A_d - B_d
+K$) are inside the unity circle of the complex plane, i.e., their
+absolute values are strictly less than one~\cite{astrom1997computer}
+(this simple sufficient condition can be generalised, however this is
+not necessary in our work).  In this paper, we express this stability
+specification $\phi_\mathit{stability}$ in terms of a check known as
+\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic
+formula to select the entries of matrix $K$ so that the closed-loop
+dynamics are shaped as desired.
 
@@
 
+\todo{this descrition does not mention two synthesis phases, which we should
+focus on more.}
+
 We find a controller for a continuous initial set of states and set of inputs,
@@
 The CEGIS loop for this approach 
+\todo{the description here is incomplete (stops at phase 4).}
 
@@
 %-------------------------------
+\section{Stability} 
+\label{ssec:stabspecification}
+%-------------------------------
+
+There are a number of algorithms that can be
+used for stability analysis~\cite{daes20161,Bessa16}.
+
+A discrete-time LTI system as \eqref{eq:closedloopss} is
+asymptotically stable if all the roots of its characteristic
+polynomial (i.e., the eigenvalues of the closed-loop matrix $A_d - B_d
+K$) are inside the unity circle of the complex plane, i.e., their
+absolute values are strictly less than one~\cite{astrom1997computer}
+(this simple sufficient condition can be generalised, however this is
+not necessary in our work).  In this paper, we express this stability
+specification $\phi_\mathit{stability}$ in terms of a check known as
+\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic
+formula to select the entries of matrix $K$ so that the closed-loop
+dynamics are shaped as desired.
+
+Since the canonical forms used in this work use the coefficients of the
+characteristic polynomial $S(z)$ as opposed to its roots (which are
+extremely hard to calculate for a SAT solver), we choose Jury's
+criterion~\cite{astrom1997computer} to check the stability in the
+$z$-domain in view of its efficiency.
+
+We~consider the following form for $S(z)$:
+%
+\begin{equation*}
+S(z) = z^{p}+a_1z^{p-1}+\cdots+a_{p-1}z+a_p.
+\end{equation*}
+
+and build the matrix
+$\mat{M} \in \mathbb{R}^{p \times p}$ from its coefficients such that:
+%
+\begin{align*}
+\mat{M}_{1,j}&=a_j\\
+\mat{M}_{i+1,j}&=\left\{
+\begin{array}{ll}
+0,&j>p'\\
+\mat{M}_{i,j}-\mat{M}_{i,p'-j+1}\frac{\mat{M}_{i,1}}{\mat{M}_{i,p'}} &j\leq p'
+\end{array}
+\right.\\
+p'&=p-i+1
+\end{align*}
+%
+$S(z)$ is the characteristic polynomial of a stable system if and
+only if the following conditions hold~\cite{astrom1997computer}:
+\begin{align*}
+\phi_\mathit{stability}(S) \equiv
+(S(1) > 0) \wedge ((-1)^p S(-1) > 0) \wedge (|a_p| < 1) \wedge \bigwedge\limits_{i=1}^p (\mat{M}_{i,1} > 0).
+\end{align*}
+
+%-------------------------------
 \section{Proofs of theorems}

### 2017-10-15 TACAS2018/paper.tex
Changes with cristina

@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsection{Verification of Continuous time systems}\label{sec:continuous_time_accel}
+ \section{Acceleration of Continuous time systems}\label{sec:continuous_time_accel}
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsubsection{Discrete dynamics using reals for systems without inputs}\label{sec:real_discrete_no_inputs}
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ \subsection{Accelrated dynamics using reals for systems without inputs}\label{sec:real_discrete_no_inputs}
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ The state $\vec{x}_T$ present at time $T$ can be expressed as a linear function of $\vec{x}_0$ as described below
  \begin{theorem}
- Given $\dot{\vec{x}}=\mat{A}\vec{x}$ \todo{$\dot{\vec{x}}(t)$?}, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, the expression
+ Given $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ \todo{$\dot{\vec{x}}(t)$?}, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, the expression
  \begin{align}
@@
 $\lambda_i \in \mat{J}$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.
-$\vec{x}_T$ is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}$ at time t=T.
+$\vec{x}_T$ is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T.
  \end{theorem}
  \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x} : k \in (0,\infty)$ is a witness of the system at time $t=kT_d$.
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}_0 : k \in (0,\infty)$ is a witness of the system at time $t=kT_d$.
  \end{corollary}
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsubsection{Discrete dynamics using reals for systems with parametric inputs}\label{sec:real_discrete_param_inputs}
+ \subsection{Accelerated dynamics using reals for systems with parametric inputs}\label{sec:real_discrete_param_inputs}
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
  \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}+(\mat{I}-\mat{A}_d^k\mat{B}\vec{u}) : k \in (0,\infty)$ is a witness of the system at time $kT_d$.
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}_0+(\mat{I}-\mat{A}_d^k\mat{B}\vec{u}) : k \in (0,\infty)$ is a witness of the system at time $kT_d$.
  \end{corollary}
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsubsection{Discrete dynamics using reals for systems with discrete time feedback inputs}\label{sec:real_discrete_feedback_inputs}
+ \subsection{Accelerated dynamics using reals for systems with discrete time feedback inputs}\label{sec:real_discrete_feedback_inputs}
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 plant dynamics evolve in continuous time while the feedback dynamics evolve
-in discrete time.
+in discrete time, i.e. a new input value is only produced for every sample interval.
 
@@
  \begin{align}
- \vec{x}_{t} &= (\mat{A}_{t-kT_s}-\mat{B}_{t-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
+ \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
  \label{eq:cyber_feedback}
  \end{align}
- with $\mat{A}_t, \mat{B}_t$ as per \eqref{eq:continuous_tube_dyn} and $\mat{A}_d, \mat{B}_d$ as per equation \eqref{eq:discretize} is a witness of the system
- \begin{align}
- \dot{\vec{x}}_{t} &= \mat{A}\vec{x}+\mat{B}\vec{u}_t\nonumber\\
+ with $\mat{A}_T, \mat{B}_T$ as per \eqref{eq:continuous_tube_dyn} and $\mat{A}_d, \mat{B}_d$ as per equation \eqref{eq:discretize} is a witness of the system
+ \begin{align}
+ \dot{\vec{x}}(t) &= \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\nonumber\\
  \vec{u}_t&=\mat{K}\vec{x}_k  \mid  kT_s \leq t < (k+1)T_s
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Time delay on discrete time feedback systems} \label{sec:delay}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\todo{How does fit in the description at the beginning of sec 3.3?}
-
+\subsection{Time delay on discrete time feedback systems} \label{sec:delay}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 A common ocurrence in digital systems is that they do not necessarily
@@
 
-\todo{equations \eqref{eq:feedback_sampled_cont} and
-  \eqref{eq:feedback_cont} are in the appendix so it's preferable to not
-refer to them so directly.}
-Let us look at equations \eqref{eq:feedback_sampled_cont} and
-\eqref{eq:feedback_cont}.  When we introduce an arbitrary delay $T_d$ where
-$t_d=T_d$ and $t_s=T_s-T_d$ we obtain:
-%
-\begin{align}
-\vec{x}_{k} &=\mat{A}_{t_s}(\mat{A}_{t_d}\vec{x}_{k-1}-\mat{B}_{t_d}\mat{K}\vec{x}_{k-2})-\mat{B}\mat{K}\vec{x}_{k-1}\nonumber\\
-&=  (\mat{A}_{T_s}-\mat{B}_{t_s}\mat{K})\vec{x}_{k-1}-\mat{A}_{t_s}\mat{B}_{t_d}\mat{K}\vec{x}_{k-2}
-\label{eq:delay_cont}
-\end{align}
-%
-Differentiating with the expected progression without delay, we get a delay
-error:
-%
-\begin{align}
-{\vec{x}_e}_{k}=&(\mat{B}_{T_s}-\mat{B}_{t_s})\mat{K}\vec{x}_{k-1}-\mat{A}_{t_s}\mat{B}_{t_d}\mat{K}\vec{x}_{k-2}\nonumber\\
-=&(\mat{B}_{T_s}-\mat{B}_{t_s})\vec{u}_{k}-\mat{A}_{t_s}\mat{B}_{t_d}\vec{u}_{k-1}
-\end{align}
-Rather than explicitly calculate this error, we will find an upper bound.
-Let $|U|_\infty=max(|\vec{u}|_\infty \mid \vec{u} \in U)$ be the maximum infinity norm of a vector set, propagating the error to the output $\vec{y}_k$ we have:
-\begin{align}
-|{\vec{y}_e}_{k}|_1 \leq q_t=&(|\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})|_1+|\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}|_1)|U|_\infty
-\end{align}
-
-We overapproximate the effects of this vector by introducing a noise signal at the output $\nu_t=[-q_t\ q_t]$ and use the dynamics of the system without delay.
+\begin{theorem}
+The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modelled as a non-deterministic noise signal upperbound by 
+\begin{align}
+|{\vec{y}_e}_{k}|_1 \leq q_t, \text{ where } q_t=&(|\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})|_1+|\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}|_1)|U|_\infty
+\end{align}
+\end{theorem}
 
@@
 The models we consider have two sources of error that are due to numerical  
-representation.  The first is the numerical error introduced by the
+representation which we commonly refer to as the FWL effect.
+The first is the numerical error introduced by the
 fixed-point numbers employed to model the plant, i.e., to represent the
@@
 \end{equation}
-where $0\leq p_s \leq 1$ is the desired percentage of the target within \todo{typo?} to remain after $t_s$.
+where $0\leq p_s \leq 1$ is the desired percentage of the target within which the output must remain after $t_s$.
 \end{theorem}
@@
 
-As stated in Section~\ref{ssec:stabspecification}, we use Jury's Criterion
-to assert this specification. \todo{Not clear to me what ``this specification'' refers to.}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Stability of a Digitally Observed System}\label{sec:cof_fwl_stability}
+As stated in Section~\ref{ssec:stabspecification}, we use Jury's Criterion on these polynomials
+to assert the stability specification.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Stability of an Observed System with FWL effects}\label{sec:cof_fwl_stability}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 \end{equation}
-\todo{what happened to u when going from \eqref{eq:observer_LTI_cf}?}
 %
@@
 %
-\todo{I thought \eqref{eq:of_bounds} was the safety spec. Why is it solved?}
-Equation~\eqref{eq:of_bounds} can be solved using linear programming as it
-describes a polyhedral region in $\mathbb{R}^p$.  The second \todo{second?} step is
-evaluating the progression of the system over time in order to calculate
-$\vec{x}_k$ to validate against this specification.  For this step we require
-an initial set $\vec{x}_0$ from which the system progresses.  Obviously, this set
-%$\vec{x}_0$
-must satisfy the specification, otherwise the system will be
-unsafe to begin with.  We will accept a specification in the form
-$\mat{E}\mat{T}\vec{x}_0<\mat{f}$ \todo{ET? f?}.  The presence of $\mat{T}$ is because
-this will typically be given in the original state-space.
+%We evaluate the progression of the system over time by calculating
+%$\vec{x}_k$ to validate against this specification.  For this step we require
+%an initial set $\vec{x}_0$ from which the system progresses.  Obviously, this set
+%must satisfy the specification, otherwise the system will be
+%unsafe to begin with.
+For efficiency purposes, the inequality in \eqref{eq:of_bounds} is transformed into reachable form using $\mat{T}_c, \mat{T}_o$ which reduces the complexity from $\mathcal{O}(p^2)$ to $\mathcal{O}(p)$.
 
@@
 These bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space. 
+\item Select an initial width for the bitvectors representing the controller and the plant $\phi_{\langle C \rangle}, \phi_{\langle P \rangle}$. We will increase either precision as needed.
 \end{enumerate}
-The Abstraction is fed to the synthesiser.
-\item In the {\sc synthesize} phase, we synthesize a candidate controller $\mat{K} \in \mathbb{R}_{\langle C\rangle}^p$
-and observer $\mat{L} \in \mathbb{R}_{\langle C\rangle}^p$ that satisfy
-$\phi_\mathit{stability} \wedge \phi_\mathit{safety} \wedge \phi_\mathit{init}^{K}$ by invoking a SAT solver.
+There are two abstractions created by these specifications: $\phi_{synth}$ which is given to the synthesiser and $\phi_{static}$ which is given to the synthesis refinement loop.
+These abstractions will be refined independently, so we will not detail what each will contain at a given stage.
+We only note that at all times $\phi_{static} \models \phi_{synth}$.
+
+\item In {\sc synthesize}, we synthesize a candidate controller $\mat{K}$
+and observer $\mat{L}$ that satisfy
+$\phi_{synth}$ by invoking a SAT solver.
 There are two exit conditions:
-\begin{enumerate}
-\item If there is no candidate solution we return UNSAT and signal the modeller. Based on the current abstraction,
-the {\sc  model} phase may choose to increase the precision, decrease the sample time, or return a synthesis failure.
-\item If we have a candidate solution we will feed it to the verifier in order to validate it.
-\end{enumerate}
-\item The verifier works in multiple stages.
-\begin{enumerate}
-%
-\item The {\sc Verify Synthesis} submodule verifies $\phi_{static}$ of  both the
+If there is no candidate solution we return FAIL and signal {\sc Abstract}. Based on the current abstraction,
+{\sc  Abstract} may choose to increase the precision, refine the abstraction, or return a synthesis failure.
+If we have a candidate solution we will feed it to the verifier chain in order to validate it.
+%
+\item {\sc Verify Synthesis} verifies $\phi_{static}$ of  both the
 controller and the observer.  If one of these results does not satisfy the tighter
-specification, it feeds back to the modeller which uses sensitivity analysis to
-synthesise a refined solution. 
-Formally speaking, given a violating controller $\{ \mat{K},\mat{L} \} \not \models \phi_{static}$
-we look for a variation $\mat{\delta}_K, \mat{\delta}_L$ such that
-$\{ \mat{K}', \mat{L}' \}=\{ \mat{K}+\mat{\delta}_K,\mat{L}+\mat{\delta}_L \} \models \phi_{static}$, and similarly for the observer.
-%\mat{K}' \in \mathbb{R}_{\langle C \rangle}$. 
-If the Modeller cannot synthesise a suitable candidate($\mat{K}' \not
-\models \phi_{static}^K$), it returns to the synthesiser with a request for
-either higher precision or a lower upper bound $\overline{\lambda}$. Otherwise
-the refined candidate solution is given to the second verification stage.
-%
-\item The {\sc Discrete Time} submodule verifies $\phi_{safety}$ using discrete
-time dynamics.  If the verification fails, the verifier reports to the
-modeller with a counterexample, including details of initial states and
-iterations that failed the specification.  The modeller will then create a
-refined abstraction that explores this time horizon for the given initial
-state.  If the magnitude of the violation is small, we may choose to try
-a synthesis refinement loop before feeding back to the main synthesiser.
-%
-\item If the Discrete Time verification is successful, the problem is
-evaluated by the {\sc Continuous Time} submodule.  This stage verifies that the
-transitions between sample times meet the specification $\phi_{safety}$.  If
+specification, it feeds back to the {\sc Refine Synthesis} phase which uses sensitivity analysis to
+synthesise a refined solution. If the candidate is valid, we feed it to {\sc Discrete Time}. 
+\item {\sc Refine Synthesis} takes $\mat{K},\mat{L} \not \models \phi_{static}$ and synthesises $\mat{K}_{\langle C \rangle} = \mat{K}+\mat{\delta}_K, \mat{L}_{\langle C \rangle}=\mat{L}+\mat{\delta}_L, where \mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \models \phi_{static}$
+If we cannot synthesise a suitable candidate, we signal the {\sc Abstract} phase to refine $\phi_{synth}$ and request {\sc Synthesise} to produce a new candidate.
+Otherwise the refined candidate solution is given back to {\sc Verify Synthesis}.
+%
+\item {\sc Discrete Time} verifies $\phi_{safety}^{\infty}$ using discrete
+time dynamics.  If the verification fails, we report the counterexample to
+{\sc Refine Abstraction} including details of initial states and
+iterations that failed the specification.  
+\item {\sc Refine Abstraction} changes $\phi_{safety}$ to encompass any arising conterexample. 
+This can be done by increasing the time horizon $k$ for the safety specification of the violating initial condition and input.
+It also modifies $\phi_{static}$ to account for the counterexample.
+If the magnitude of the violation is small, {\sc Refine Synthesis} may find a new candidate, otherwise it will feed through to {\sc Abstract}.
+%
+\item {\sc Continuous Time} verifies that the
+transitions between sample times meet the specification $\phi_{safety}^{\infty}$.  If
 a counterexample is found, information about the maximum distance of the
-violation to the specification boundary is fed back to the modeller.  Once
-again, the modeller will refine the abstraction based on this information by
-creating constraints on the surrounding points (constraining the safety
-abstraction to exclude the violation based on the projection of the discrete
-time dynamics onto the continuous ones).
-%
-\end{enumerate}
+violation to the specification boundary is fed to {\sc Sample}. 
+\item {\sc Sample} will select a smaller suitable sample time and modify the abstractions to meet the discretization. 
+It will then feed back to the abstraction refinement loop to look for a suitable action for the updated model.
+%
 
 \item If we reach the {\sc abstract} phase, it means that the candidate
-  solution is not valid, in which case we must refine the abstraction used
-  by the synthesizer.
-%
-\begin{enumerate}
-%
-\item Find the constraints that invalidate the property
- as a set of counterexamples for the eigenvalues, which we define as
-$\phi_\Lambda$.  This is a constraint in the spectrum i.e., transfer
-function) of the closed loop dynamics.
-%
-\item We use $\phi_\Lambda$ to further constrain the characteristic polynomial 
-\begin{equation*}
-z^p+\sum_{i=1}^p(a_i-k_i)z^{p-i}=\prod_{i=1}^p (z-\lambda_i) \mid |\lambda_i|<1 \wedge \lambda_i \models \phi_{\Lambda}.
-\end{equation*} 
-These constraints correspond to specific iterations for which the system may be unsafe.
-
-\item Pass the refined abstraction $\phi(K)$ with the new constraints and the list of iterations $k$ to the {\sc synthesize} phase.
-  %, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again. 
-\end{enumerate} 
+  solution is not valid, in which case we must refine $\phi_{synth}$. If $\phi_{synth}$ cannot be further refined, 
+  then we cannot synthesise a new candidate and return a synthesis failure.
 \end{enumerate}
@@
 	label={\sc Model~~~~~~~~~~~},] (model) {};
-     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (model2) at ([xshift=-3cm]model.center) {{\sc 3. Refine}\\{\sc Synthesis}};
-     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (model3) at ([xshift=0cm]model.center) {{\sc 4. Refine}\\{\sc Abstraction}};
-     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (model4) at ([xshift=3cm]model.center) {{\sc 5. Sample}};
+     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (model2) at ([xshift=-3cm]model.center) {{\sc 4. Refine}\\{\sc Synthesis}};
+     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (model3) at ([xshift=0cm]model.center) {{\sc 6. Refine}\\{\sc Abstraction}};
+     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (model4) at ([xshift=3cm]model.center) {{\sc 8. Sample}};
    } ;\\
@@
 	label={\sc Verify~~~~~~~~~~~},] (verif) {};
-     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-3cm]verif.center) {{\sc 5. Verify}\\{\sc Synthesis}};
-     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=0cm]verif.center) {{\sc 6. Discrete}\\{\sc Time}};
+     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-3cm]verif.center) {{\sc 3. Verify}\\{\sc Synthesis}};
+     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=0cm]verif.center) {{\sc 5. Discrete}\\{\sc Time}};
      \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=3cm]verif.center) {{\sc 7. Continuous}\\{\sc Time}};
@@
   };
-   \path[-]
-    (model3.north) edge node[align=center,xshift=0.8cm] {$k$,$X_0'$} (aux2.north)
-    (aux2.west) edge (aux1.east)
-    (aux3.west) edge (aux2.east)
-    (model4.north) edge node[align=center,xshift=0.5cm] {$T_s$} (aux3.north);
    \path
-    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$\mat{K}$,$\mat{L}$} ([yshift=2em]verif1.west)
-    ([yshift=-2em]verif1.west) edge node {C-ex} ([yshift=-2em]synth.east)
-    (verif1.east) edge node {SAT} (verif2.west)
+    (synth.east) edge node[xshift=-0.5em,align=center] {$\mat{K}$,$\mat{L}$} (verif1.west)
+    (verif1.east) edge node {PASS} (verif2.west)
     (verif2.north) edge node[xshift=.8cm] {C-ex} (model3.south)
-    (verif2.east) edge node {SAT} (verif3.west)
+    (verif2.east) edge node {PASS} (verif3.west)
     (verif3.north) edge node {C-ex} (model4.south)
-    (aux1.south) edge node {$\phi$} (model1.north)
-    (model3.west) edge node {$\phi_\Lambda$} (model2.east)
-    (model4.west) edge node {$\phi_\Lambda$} (model3.east)
-    ([xshift=-5em]fp.north) edge node[align=center]  {SAT/\\C-ex} ([xshift=-5em]verif2.south)
-    ([xshift=-5em]sv.north) edge node[align=center]  {SAT/\\C-ex} ([xshift=-5em]verif3.south)
+    (model3.west) edge node {$k$,$X_0'$} (model2.east)
+    (model4.west) edge node {$T_s$} (model3.east)
+    ([xshift=-5em]fp.north) edge node[align=center]  {PASS/\\C-ex} ([xshift=-5em]verif2.south)
+    ([xshift=-5em]sv.north) edge node[align=center]  {PASS/\\C-ex} ([xshift=-5em]verif3.south)
     ([xshift=5em]verif1.south) edge node[align=center] {$\mat{A}'$} ([xshift=5em]bmc.north)
@@
     ([xshift=5em]verif3.south) edge node[align=center] {{$\mat{A}$,$\mat{B}$,$\mat{C}$}\\{$\mat{A}'$,$\mat{B}'$,$\phi$}} ([xshift=5em]sv.north)
-    ([xshift=-5em]bmc.north) edge node[align=center]  {SAT/\\C-ex} ([xshift=-5em]verif1.south)
+    ([xshift=-5em]bmc.north) edge node[align=center]  {PASS/\\C-ex} ([xshift=-5em]verif1.south)
     (verif) edge node {PASS} (done)
     ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
-    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$\mat{K}$,$\mat{L}$} ([xshift=-5em]synth.south)
-    ([xshift=5em]model1.south) edge node[align=center,xshift=-.65cm] {$\langle P \rangle$} ([xshift=5em]synth.north) node[align=left,yshift=-0.7cm,xshift=1.3cm] {{$\phi_{stability}(P_a,P_l,\overline{\lambda})$}\\{$\phi_{safety}(\eta,k)$}\\ {$\phi_{init}^K$}}
-   ([xshift=-5em]synth.north) edge node[align=center] {UNSAT} ([xshift=-5em]model1.south);
+    ([xshift=-5em]gp.north) edge node[align=center] {FAIL/\\$\mat{K}$,$\mat{L}$} ([xshift=-5em]synth.south)
+    ([xshift=5em]model1.south) edge node[align=center,xshift=-.65cm] {$\langle P \rangle$} ([xshift=5em]synth.north) node[align=left,yshift=-0.7cm,xshift=.8cm] {{$\phi_{stability}$}\\{$\phi_{safety}$}\\ {$\phi_{init}^K$}}
+   ([xshift=-5em]synth.north) edge node[align=center] {FAIL} ([xshift=-5em]model1.south);
    \path[->]
-    ([xshift=-5em]verif1.north) edge node[align=center]  {$\mat{K}$,$\mat{L}$} ([xshift=-5em]model2.south)
+    ([xshift=-5em]verif1.north) edge node[align=center]  {C-ex} ([xshift=-5em]model2.south)
     ([xshift=5em]model2.south) edge node[align=center]  {$\mat{K}'$,$\mat{L}'$} ([xshift=5em]verif1.north)
-    (model2.west) edge node[align=center] {$\overline{\lambda},\langle C \rangle$} (model1.east)
-    ([yshift=1em]model1.east) edge node[align=center] {$\phi_{static}$} ([yshift=1em]model2.west);
+    (model2.west) edge node[align=center] {$\phi$} (model1.east);
 
@@
 \section{Stability} 
-\label{ssec:stabspecification}
+\label{appendix:stabspecification}
 %-------------------------------
@@
 \end{proof}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsubsection{Time delay on discrete time feedback systems} \label{sec:delay}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\begin{theorem}
+The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modelled as a non-deterministic noise signal upperbound by 
+\begin{align}
+|{\vec{y}_e}_{k}|_1 \leq q_t, \text{ where } q_t=&(|\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})|_1+|\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}|_1)|U|_\infty
+\end{align}
+\end{theorem}
+
+\begin{proof}
+Let us look at equations \eqref{eq:feedback_sampled_cont} and
+\eqref{eq:feedback_cont}.  When we introduce an arbitrary delay $T_d$ where
+$t_d=T_d$ and $t_s=T_s-T_d$ we obtain:
+%
+\begin{align}
+\vec{x}_{k} &=\mat{A}_{t_s}(\mat{A}_{t_d}\vec{x}_{k-1}-\mat{B}_{t_d}\mat{K}\vec{x}_{k-2})-\mat{B}\mat{K}\vec{x}_{k-1}\nonumber\\
+&=  (\mat{A}_{T_s}-\mat{B}_{t_s}\mat{K})\vec{x}_{k-1}-\mat{A}_{t_s}\mat{B}_{t_d}\mat{K}\vec{x}_{k-2}
+\label{eq:delay_cont}
+\end{align}
+%
+Differentiating with the expected progression without delay, we get a delay
+error:
+%
+\begin{align}
+{\vec{x}_e}_{k}=&(\mat{B}_{T_s}-\mat{B}_{t_s})\mat{K}\vec{x}_{k-1}-\mat{A}_{t_s}\mat{B}_{t_d}\mat{K}\vec{x}_{k-2}\nonumber\\
+=&(\mat{B}_{T_s}-\mat{B}_{t_s})\vec{u}_{k}-\mat{A}_{t_s}\mat{B}_{t_d}\vec{u}_{k-1}
+\end{align}
+Rather than explicitly calculate this error, we will find an upper bound.
+Let $|U|_\infty=max(|\vec{u}|_\infty \mid \vec{u} \in U)$ be the maximum infinity norm of a vector set, propagating the error to the output $\vec{y}_k$ we have:
+\begin{align}
+|{\vec{y}_e}_{k}|_1 \subseteq &(\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})+\mat{C}\mat{A}_{t_s}\mat{B}_{t_d})U
+\end{align}
+\end{proof}
+We overapproximate the effects of this vector by introducing a noise signal at the output $\nu_t=[-q_t\ q_t]$ and use the dynamics of the system without delay.
 

### 2017-10-16 TACAS2018/paper.tex
introduction edit

@@
 restricted dynamics.  We examine the case of Linear Time Invariant (LTI)
-Models, for which the synthesis of controllers is well understood.  However,
+models, for which the synthesis of controllers is well understood.  However,
 the use of digital control architectures adds new challenges caused by
@@
 synthesise correct by construction minimal digital controllers.  Contrary to
-LTL models that require thousands of states and elaborate algorithms to
+LTL models \todo{citation} that require thousands of states and elaborate algorithms to
 implement, these PID-like controllers are represented by a few parameters
 and only require a few lines of code, thus reducing the implementation cost
-and execution time while remaining resilient to the effects of digitilazation.
-However,~\cite{abate2017automated}~is still restricted to fully observed
-systems (i.e. where all the states are known) modelled in discrete time,
+and execution time while remaining resilient to the effects of digitalization.
+However,~\cite{abate2017automated}~is restricted to fully observed
+systems (i.e., where all the states are known) modelled in discrete time,
 and furthemore explores only a limited set of properties that engineers
-are interested in.
+are interested in. Conversely, 
+in most real implementations, the internal state of a plant cannot be
+directly measured but rather inferred from its
+effect on the output. A plant model that minimises the difference
+between the outputs is called an observer and it is a well known
+paradigm in the control literature~\cite{astrom1997computer}.
 
@@
 automatically generate digital observer controllers for a given continuous
-plant model that are correct by construction.  This approach delivers a high
-degree of automation, promises to reduce the cost and time of development of
-digital control dramatically, and requires considerably less expertise than
-a-posteriori verification.  Specifically, we synthesize stable,
+plant model that are correct by construction.  %% This approach delivers a high
+%% degree of automation, promises to reduce the cost and time of development of
+%% digital control dramatically, and requires considerably less expertise than
+%% a-posteriori verification.
+Specifically, we synthesize stable,
 software-implemented embedded controllers along with a model of a physical
@@
 %minimise synthesis time.  
-A candidate solution is then passed to a set of verifiers which will
-evaluate the synthesised controller over an even more precise
-abstraction of the concrete domain in both discrete and continuous
-space/time.  The verification phase uses abstraction refinement when needed to ensure
-that rejected candidates are not being discarded due to the
-over-approximation.
+%% A candidate solution is then passed to a set of verifiers which will
+%% evaluate the synthesised controller over an even more precise
+%% abstraction of the concrete domain in both discrete and continuous
+%% space/time.  The verification phase uses abstraction refinement when needed to ensure
+%% that rejected candidates are not being discarded due to the
+%% over-approximation.
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Verification of a Conrollable Observed System}\label{sec:cof_verification}
+\section{Verification of a Controllable Observed System}\label{sec:cof_verification}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-10-16 TACAS2018/paper.tex
related work edit

@@
 The work in~\cite{hscc-paper} synthesizes stabilizing controllers for
-continuous plants given as transfer functions by exploiting bit-accurate
-verification of software-implemented digital controllers~\cite{Bessa16}. 
-While this work also uses CEGIS, the approach is restricted to digital
-controllers for stable closed-loop systems given as transfer function
-models: this results in a static check on their coefficients.  By contrast,
-in the current paper we consider a state-space representation of the
-physical system, which requires ensuring the specification over actual
-traces of the model, alongside the numerical soundness required by the
-effects of discretisation and finite-precision errors.  A state-space model
-has known advantages over the transfer function
-representation~\cite{Franklin15}: it naturally generalizes to multivariate
-systems (i.e., with multiple inputs and outputs); and it allows synthesis of
-control systems with guarantees on the internal dynamics, e.g., to
-synthesize controllers that make the closed-loop system \emph{safe}.  Our
-work focuses on the \emph{safety} of internal states, which is usually
-overlooked in the literature.  Moreover, our work integrates an
-abstraction/refinement (CEGAR) step inside the main CEGIS loop.
+continuous plants
+%given as transfer functions
+by exploiting bit-accurate verification of software-implemented
+digital controllers~\cite{Bessa16} but it is restricted to closed-loop
+systems given as transfer function models.
+
+%% While this work also uses CEGIS, the approach is restricted to digital
+%% controllers for stable closed-loop systems given as transfer function
+%% models: this results in a static check on their coefficients.  By contrast,
+%% in the current paper we consider a state-space representation of the
+%% physical system, which requires ensuring the specification over actual
+%% traces of the model, alongside the numerical soundness required by the
+%% effects of discretisation and finite-precision errors.  A state-space model
+%% has known advantages over the transfer function
+%% representation~\cite{Franklin15}: it naturally generalizes to multivariate
+%% systems (i.e., with multiple inputs and outputs); and it allows synthesis of
+%% control systems with guarantees on the internal dynamics, e.g., to
+%% synthesize controllers that make the closed-loop system \emph{safe}.  Our
+%% work focuses on the \emph{safety} of internal states, which is usually
+%% overlooked in the literature.  Moreover, our work integrates an
+%% abstraction/refinement (CEGAR) step inside the main CEGIS loop.
 

### 2017-10-16 TACAS2018/paper.tex
sec 3.1 and 3.2 editing

@@
 
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Model Semantics}\label{sec:model_semantics}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-\todo{This section should be integrated later, closer to the use of AA}
-
-The traces of the model starting from an initial set $X_0\subseteq \mathbb{R}^p$, 
-with inputs restricted to $U \subseteq \mathbb{R}^q$, are sequences 
-$ \vec{x}_0 \xrightarrow{\vec{u}_0} \vec{x}_1 \xrightarrow{\vec{u}_1} \vec{x}_2 \xrightarrow{\vec{u}_2} \ldots $, 
-%
-where $ \vec{x}_0 \in X_0$ and $\forall k\geq 0, \vec{u}_k \in U \text{ and } \vec{x}_{k+1} = \tau(\vec{x}_k,\vec{u}_k) $, 
-where 
-%
-\begin{equation}\label{equ:reachtraj}
-\tau(\vec{x}_k,\vec{u}_k) = 
-\big( \mat{A}\vec{x}_k +
-\mat{B}\vec{u}_k \mid \mat{G}\vec{x}_k \leq \vec{h}\big)\;. 
-\end{equation}
-
-We extend the notation above to convex sets of initial conditions and inputs ($X_0$ and $U$), 
-and write $\tau(X_0,U)$ to denote the set of states $\{\vec{x} \mid \vec{x}_0 \in
-X_0 \wedge \vec{u} \in U \wedge \vec{x} = \tau(\vec{x}_0,\vec{u})\}$
-reached from $X_0$ by $\tau$ in one step. 
-%
-We furthermore write $\tau^n(X_0,U)$ to denote the set of states reached from
-$X_0$ via $\tau$ in $n$ steps (\emph{$n$-reach set}), i.e.\ for $n\geq 1$
-%
-\begin{align}\label{equ:reachset}
-\tau^n(X_0,U) = \{\vec{x}_n \mid &\vec{x}_0 \in X_0 \wedge \forall k\in [0,n-1]\nonumber\\ 
- &\vec{u}_{k} \in U \wedge \vec{x}_{k+1}=\tau(\vec{x}_{k},\vec{u}_{k}) \} \;. 
-\end{align}
-%
-Since the transformations $\mat{A}$ and $\mat{B}$ are linear and
-vector sums preserve convexity, the sets $X_n = \tau^n(X_0,U)$ are also
-convex.
-
-We define the \emph{$n$-reach tube} 
-\begin{equation}\label{equ:reachtube}
-\hat{X}_n=\hat{\tau}^n(X_0,U)=\bigcup_{k\in[0,n]} \tau^k(X_0,U)
-\end{equation}
-as the union of the reachable sets over $n$ iterations.
-%
-Moreover, $\hat{X} 
-=\bigcup_{n\geq 0} \tau^n(X_0,U)$ 
-extends the previous notion over an 
-unbounded time horizon.
-
 %-------------------------------
@@
 output that is a linear combination of its states and inputs, which may
-restricts the observability of the statespace from the output space.
+restrict the observability of the statespace from the output space.
 \begin{equation}
@@
 %% as introduced by the ADC/DAC conversion blocks (Fig.~\ref{fig:digitalsystem}).
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Model semantics of LTI models}\label{sec:model_semantics}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+The traces of the model starting from an initial set $X_0\subseteq \mathbb{R}^p$, 
+with inputs restricted to $U \subseteq \mathbb{R}^q$, are sequences 
+$ \vec{x}_0 \xrightarrow{\vec{u}_0} \vec{x}_1 \xrightarrow{\vec{u}_1} \vec{x}_2 \xrightarrow{\vec{u}_2} \ldots $, 
+%
+where $ \vec{x}_0 \in X_0$ and $\forall k\geq 0, \vec{u}_k \in U \text{ and } \vec{x}_{k+1} = \tau(\vec{x}_k,\vec{u}_k) $, 
+where 
+%
+\begin{equation}\label{equ:reachtraj}
+\tau(\vec{x}_k,\vec{u}_k) = 
+\big( \mat{A}\vec{x}_k +
+\mat{B}\vec{u}_k \mid \mat{G}\vec{x}_k \leq \vec{h}\big)\;. 
+\end{equation}
+
+We extend the notation above to convex sets of initial conditions and inputs ($X_0$ and $U$), 
+and write $\tau(X_0,U)$ to denote the set of states $\{\vec{x} \mid \vec{x}_0 \in
+X_0 \wedge \vec{u} \in U \wedge \vec{x} = \tau(\vec{x}_0,\vec{u})\}$
+reached from $X_0$ by $\tau$ in one step. 
+%
+We furthermore write $\tau^n(X_0,U)$ to denote the set of states reached from
+$X_0$ via $\tau$ in $n$ steps (\emph{$n$-reach set}), i.e.\ for $n\geq 1$
+%
+\begin{align}\label{equ:reachset}
+\tau^n(X_0,U) = \{\vec{x}_n \mid &\vec{x}_0 \in X_0 \wedge \forall k\in [0,n-1]\nonumber\\ 
+ &\vec{u}_{k} \in U \wedge \vec{x}_{k+1}=\tau(\vec{x}_{k},\vec{u}_{k}) \} \;. 
+\end{align}
+%
+Since the transformations $\mat{A}$ and $\mat{B}$ are linear and
+vector sums preserve convexity, the sets $X_n = \tau^n(X_0,U)$ are also
+convex.
+
+We define the \emph{$n$-reach tube} 
+\begin{equation}\label{equ:reachtube}
+\hat{X}_n=\hat{\tau}^n(X_0,U)=\bigcup_{k\in[0,n]} \tau^k(X_0,U)
+\end{equation}
+as the union of the reachable sets over $n$ iterations.
+%
+Moreover, $\hat{X} 
+=\bigcup_{n\geq 0} \tau^n(X_0,U)$ 
+extends the previous notion over an 
+unbounded time horizon.
 
@@
 output that is a linear combination of its states and inputs, which may
-restricts the observability of the statespace from the output space.
+restrict the observability of the state-space from the output space.
 \begin{equation}

### 2017-10-16 TACAS2018/paper.tex
sec 3.2 editing

@@
 
+\todo{$\mathbb{R}^p$?}
 The traces of the model starting from an initial set $X_0\subseteq \mathbb{R}^p$, 
@@
 \end{equation}
+
+\todo{$\mat{G}, \vec{h}$?}
 

### 2017-10-16 TACAS2018/paper.tex
removed addressed comments from sec 4

@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \todo{I find this section header unclear. What is being verified here? Stability and safety only come later on.}
  The main problem with the above discretization is that is does not allow us to observe the system at arbitrary points in time, only at integer multiples of the sample time.
@@
 
- \todo{Again, it's not clear to me what ``not sufficient for verification'' means here.}
-
- \todo{Are all three cases, i.e. discrete dynamics using reals for systems without inputs,
-   discrete dynamics using reals for systems with parametric inputs, discrete dynamics using reals for systems with discrete time feedback inputs, relevant?
-If they are, then having a sentence describing the progression in this section would be useful.}
-
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
  \begin{theorem}
- Given $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ \todo{$\dot{\vec{x}}(t)$?}, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, the expression
+ Given $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, the expression
  \begin{align}

### 2017-10-16 TACAS2018/paper.tex
sec 4 edit (partial)

@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Model semantics of LTI models}\label{sec:model_semantics}
+\subsection{Semantics of LTI models}\label{sec:model_semantics}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \section{Acceleration of Continuous time systems}\label{sec:continuous_time_accel}
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- The main problem with the above discretization is that is does not allow us to observe the system at arbitrary points in time, only at integer multiples of the sample time.
-While this is adequate for the controller, it is not sufficient for verification.
-We must therefore establish a new model that allows us to observe the system at a given time $t$.
+ \section{Acceleration of continuous time systems}\label{sec:continuous_time_accel}
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ Note that the discretization in Sec.~\ref{sec:ssrepresentation} only 
+ allows us to observe the system at integer multiples of the sample time.
+ As we are interested in ensuring that certain properties of the system hold at any given
+ time (not just integer multiples of the sample time),
+ we accelerate the dynamics of the system (according to the model semantics in Sec.~\ref{sec:model_semantics}) in order to compute the state $\vec{x}_T$  at a given time $T$.
+
+ %While this is adequate for the controller, it is not sufficient for verification. We must therefore establish a new model that allows us to observe the system at a given time $t$.
  %We achieve this by using acceleration as described below.
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsection{Accelrated dynamics using reals for systems without inputs}\label{sec:real_discrete_no_inputs}
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- The state $\vec{x}_T$ present at time $T$ can be expressed as a linear function of $\vec{x}_0$ as described below
+ \subsection{Accelerated dynamics for systems without inputs}\label{sec:real_discrete_no_inputs}
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ Given a specific time $T$, the state $\vec{x}_T$ present at $T$ can be expressed as a linear function of $\vec{x}_0$ as described below.
+Note that, as the system has no inputs, its dynamics are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.
+
  \begin{theorem}
- Given $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, the expression
+ Given $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, we have
  \begin{align}
  \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x}_0\\
- \mat{A}_{T}&= \mat{S}
+ \text{where }\mat{A}_{T}&= \mat{S}
  \left [ \begin{array}{cccc}
@@
  \label{eq:continuous_tube_dyn}\\
- &\text{where } s_i=\left\{\begin{array}{cc}1&gm(\lambda_i)>1\\0&gm(\lambda_i)=1\end{array}\right.,\nonumber
+ &\text{and } s_i=\left\{\begin{array}{cc}1&gm(\lambda_i)>1\\0&gm(\lambda_i)=1\end{array}\right.,\nonumber
  \end{align}
 $\lambda_i \in \mat{J}$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.
-$\vec{x}_T$ is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T.
+We call $\vec{x}_T$ a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T.
  \end{theorem}
+ %% We can apply Th.~\ref{eq:continuous_tube_dyn} to discretized systems without inputs in order to
+ %% obtain a witness ..
+
+\todo{Can the corallary be motivated? The general motivation of the section was observing the system at times that are not necessarily integer multiple of the sampling time...} 
  \begin{corollary}
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsection{Accelerated dynamics using reals for systems with parametric inputs}\label{sec:real_discrete_param_inputs}
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ \subsection{Accelerated dynamics for systems with parametric inputs}\label{sec:real_discrete_param_inputs}
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ Next, we are interested in observing systems with parametric
+ inputs, described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$.
+ For such systems, a witness $\vec{x}_T$ is computed next.
 \begin{theorem}
@@
 \end{theorem}
+\todo{\eqref{eq:continuous_tube_dyn} is in the appendix}
  \begin{corollary}
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsection{Accelerated dynamics using reals for systems with discrete time feedback inputs}\label{sec:real_discrete_feedback_inputs}
+ \subsection{Accelerated dynamics for systems with discrete time feedback inputs}\label{sec:real_discrete_feedback_inputs}
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-10-16 TACAS2018/paper.tex
sec 5 edit

@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
+%
 \todo{$\mathbb{R}^p$?}
@@
 \end{equation}
-
+%
 \todo{$\mat{G}, \vec{h}$?}
-
+%
 We extend the notation above to convex sets of initial conditions and inputs ($X_0$ and $U$), 
@@
  %% obtain a witness ..
-
+%
 \todo{Can the corallary be motivated? The general motivation of the section was observing the system at times that are not necessarily integer multiple of the sampling time...} 
@@
 \end{theorem}
-\todo{\eqref{eq:continuous_tube_dyn} is in the appendix}
  \begin{corollary}
@@
 
-The final case we analyse here is that of hybrid time systems, where the
+The final case we analyse is that of hybrid time systems, where the
 plant dynamics evolve in continuous time while the feedback dynamics evolve
@@
  \end{align}
- with $\mat{A}_T, \mat{B}_T$ as per \eqref{eq:continuous_tube_dyn} and $\mat{A}_d, \mat{B}_d$ as per equation \eqref{eq:discretize} is a witness of the system
+ with $\mat{A}_T, \mat{B}_T$ as per \eqref{eq:continuous_tube_dyn} and $\mat{A}_d, \mat{B}_d$ describing the discretized plant dynamics is a witness of the system
  \begin{align}
@@
  \end{theorem}
-
+%
+\todo{\eqref{eq:continuous_tube_dyn} does not define $\mat{B}_T$}
+\todo{$\vec{u}_t$?}
+%
 %\begin{proof}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{Error modelling and soundness}\label{sec:errors}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsection{Time delay on discrete time feedback systems} \label{sec:delay}
@@
 \end{theorem}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Numerical representation and soundness} 
+%
+\todo{${\vec{y}_e}_{k}$ ?, notation $| |_x$ ?}
+\todo{also, now we do have an output $y$, why didn't we consider this case at
+\ref{sec:real_discrete_feedback_inputs}?}
+%
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Errors generated by the numerical representation} 
 \label{sec:numeric_rep}
@@
  \mat{S}^{-1}
- \label{eq:continuous_tube_dyn}\\
+ \label{appendix:continuous_tube_dyn}\\
  &\text{where } s_i=\left\{\begin{array}{cc}1&gm(\lambda_i)>1\\0&gm(\lambda_i)=1\end{array}\right.,\nonumber

### 2017-10-16 TACAS2018/paper.tex
more comments

@@
 Let us first consider the effect of the quantization errors. 
-Within the controller, state values are manipulated at low precision,
-alongside the vector multiplication $\mat{K}\vec{x}$.
-Furthermore, 
-the quantizers for the DAC and the ADC introduce truncation errors
+Within the controller, state values are manipulated at low precision.
+%alongside the vector multiplication $\mat{K}\vec{x}$.
+Furthermore, the quantizers for the DAC and the ADC introduce truncation errors
 which we denote by the effect of the functions $\mathcal{F}_{\langle D \rangle}$
-and $\mathcal{F}_{\langle A \rangle}$ respectively. Finally, let us call $\vec{\nu}_e$ the
-error caused by the FWL effects on the observer (\emph{i.e} the numerical errors 
+and $\mathcal{F}_{\langle A \rangle}$, respectively. Finally, let us call $\vec{\nu}_e$ the
+error caused by the FWL effects on the observer
+\todo{the observer was not defined..}
+(\emph{i.e} the numerical errors 
 in the calculations as opposed to the estimation error).
@@
 %-------------------------------
+\todo{all this section needs to be merged with the next one and only
+discussed for an observed model.}
 
@@
 
-where $\mat{G}$ is a matrix of template directions taken as row vectors, and $\vec{h}$ is an upper
+where $\mat{G}$ is a matrix of template directions taken as row vectors \todo{unclear to me}, and $\vec{h}$ is an upper
 bound for the set in the corresponding row direction.
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\todo{the observer dynamics?}
 
@@
 of a continuous plant in discretized time domain (i.e., the range of the quatizers is still
-$\mathbb{R}$) \todo{do you mean that we only considered time domains discretization until now and
-now we look at value domain discretization as well?}.  The next step we must realize is that the controller and the
+$\mathbb{R}$).  The next step we must realize is that the controller and the
 observer exist in a digital program, hence their domain is
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\todo{FWL effects here?}
 
@@
 [\underline{y}\ \ \overline{y}]$)
-\todo{I think the safety specification is generally on the states of the system.}.
 Whilst there are other properties we may
@@
 \end{equation}
+\todo{Using \eqref{eq:observer_LTI_cf} doesn't result in this.}
+%
+\todo{transient response?}
 %
@@
 
-\todo{this descrition does not mention two synthesis phases, which we should
+\todo{this description does not mention two synthesis phases, which we should
 focus on more.}
@@
 
-The CEGIS loop for this approach 
-\todo{the description here is incomplete (stops at phase 4).}
+The CEGIS loop for this approach is described next.
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Numerical representation and soundness} 
+\section{Numerical representation} 
 \label{sec:numeric_rep}
@@
 
+\todo{preliminaries should also contain the observer model.}
+\todo{why is sec 4 not considering the observer model or a system with output?}
+\todo{sec 6 needs to be merged into 7.}
+\todo{transient response for an observed model?}
+
 \end{document}

### 2017-10-16 TACAS2018/paper.tex
more comments

@@
 
+\todo{we are interested in observable systems so this is the definitely the case...}
 Furthermore, a control system may have a derived
 output that is a linear combination of its states and inputs, which may
-restrict the observability of the statespace from the output space.
+restrict the observability of the state-space from the output space.
 \begin{equation}

### 2017-10-17 TACAS2018/paper.tex
Fixes

@@
 \label{eq:ode1}
-\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}, 
+\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^p, u \in \mathbb{R}^q, A \in \mathbb{R}^{p \times p}, B \in \mathbb{R}^{p \times q}, 
 \end{align}
@@
 \label{eq:plant}
-x_{k+1} = A_d x_k+ B_d u_k\\
-y_{k} = C_d x_k + D_d u_k
+\vec{x}_{k+1} = \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k\\
+\vec{y}_{k} = \mat{C}_d \vec{x}_k + \mat{D}_d \vec{u}_k
 \end{align} 
@@
 where $k \in \mathbb N$ and $x_{0}=x(0)$ is the initial state. 
-$A_d$, $B_d$, $C_d$ and $D_d$ denote the matrices that describe the discretized plant dynamics, whereas $A$, $B$, $C$ and $D$ denote the continuous plant dynamics.  
+$\mat{A}_d$, $\mat{B}_d$, $\mat{C}_d$ and $\mat{D}_d$ denote the matrices that describe the discretized plant dynamics, whereas $\mat{A}$, $\mat{B}$, $\mat{C}$ and $\mat{D}$ denote the continuous plant dynamics.
+In this work we will assume $\mat{D}_d=\mat{D}=\mat{0}$.
+Since $\vec{y}$ can be directly derived from $\vec{x}$, we will omit discussing it in the following unless strictly necessary.
 %% We synthesize for requirements over this discrete-time domain. 
@@
 %
-\todo{$\mathbb{R}^p$?}
 The traces of the model starting from an initial set $X_0\subseteq \mathbb{R}^p$, 
@@
 %
-\todo{$\mat{G}, \vec{h}$?}
+where $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
 %
@@
  \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}_0 : k \in (0,\infty)$ is a witness of the system at time $t=kT_d$.
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}_0 : k \in \mathbb{R}^+$ is a witness of the system at time $t=kT_d$.
  \end{corollary}
@@
  \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}_0+(\mat{I}-\mat{A}_d^k\mat{B}\vec{u}) : k \in (0,\infty)$ is a witness of the system at time $kT_d$.
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}_0+(\mat{I}-\mat{A}_d^k\mat{B}\vec{u}) : k \in \mathbb{R}^+$ is a witness of the system at time $kT_d$.
  \end{corollary}
@@
  \end{align}
- with $\mat{A}_T, \mat{B}_T$ as per \eqref{eq:continuous_tube_dyn} and $\mat{A}_d, \mat{B}_d$ describing the discretized plant dynamics is a witness of the system
+ with $\mat{A}_T$ as per \eqref{eq:continuous_tube_dyn}, 
+ $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$ and 
+ $\mat{A}_d, \mat{B}_d$ describing the discretized plant dynamics is a witness of the system
  \begin{align}
  \dot{\vec{x}}(t) &= \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\nonumber\\
- \vec{u}_t&=\mat{K}\vec{x}_k  \mid  kT_s \leq t < (k+1)T_s
+ \vec{u}(t)&=\mat{K}\vec{x}_k  \mid  kT_s \leq t < (k+1)T_s
  \end{align}
@@
 %
-\todo{\eqref{eq:continuous_tube_dyn} does not define $\mat{B}_T$}
-\todo{$\vec{u}_t$?}
 %
@@
 \begin{align}
-|{\vec{y}_e}_{k}|_1 \leq q_t, \text{ where } q_t=&(|\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})|_1+|\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}|_1)|U|_\infty
-\end{align}
+|\vec{y}_{k}-{\vec{y}_{t_d}}_{k}|_1 \leq q_t, \text{ where } q_t=&(|\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})|_1+|\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}|_1)|U|_\infty
+\end{align}
+where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$.
 \end{theorem}
 %
-\todo{${\vec{y}_e}_{k}$ ?, notation $| |_x$ ?}
-\todo{also, now we do have an output $y$, why didn't we consider this case at
-\ref{sec:real_discrete_feedback_inputs}?}
+\todo{notation $| |_x$ ?}
 %
@@
 %
-\todo{shouldn't this be over the states of the system?}
 \begin{align}
@@
 
-where $\mat{G}$ is a matrix of template directions taken as row vectors \todo{unclear to me}, and $\vec{h}$ is an upper
-bound for the set in the corresponding row direction.
+where $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
 
@@
 \begin{equation}
-t_s<-log_{|\overline{\lambda}|}({p_s}) : |\overline{\lambda}| =\max(|\lambda_i|) \wedge |\overline{\lambda}|<1,\ \forall i \in [1\ n]
+t_s<-log_{\overline{\lambda}}({p_s}) : \overline{\lambda} = \max(|\lambda_i|) \wedge \overline{\lambda}<1,\ \forall i \in [1\ n]
 \label{eq:set_time}
@@
 %percentage of the decay expressed.  Reversing we have
-%$t=-\frac{ln(d)}{|\overline{\omega}|}=-\frac{ln(d)}{ln(|\overline{\lambda}|)}$. 
+%$t=-\frac{ln(d)}{|\overline{\omega}|}=-\frac{ln(d)}{ln(\overline{\lambda})}$. 
 %replacing for $p_s$ , $t_s$, and $\overline{\lambda}$ we get equation
@@
    (adwest) edge (o1.south)
-   (o2.west) edge (Ld.east)
+   (o2.west) edge node {$\vec{y}_e$} (Ld.east)
    (Ld.west) edge (ldwest)
@@
 \end{align*}
+where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations.
 A controllable and observable system will have the following dynamics:
 \begin{align}
+\scriptstyle
 \left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_{k+1}
-&=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}_d&\mat{B}_d\mat{K}_d\\ \mat{0}&\mat{A}_d-\mat{L}_d\mat{C}_d\end{array}\right]
-\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_k\nonumber\\
-&+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
-+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}_d\end{array}\right]\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
+=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}&\mat{B}_d\mat{K}\\ \mat{0}&\mat{A}_d-\mat{L}\mat{C}_d\end{array}\right]
+\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_k
++\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
++\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}\end{array}\right]\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
 \label{eq:observer_LTI}
 \end{align}
+where $\vec{x}_e=\vec{x}-\hat{\vec{x}}$ is the estimation error of the state space by the observer, and $k_r$ is a reference gain required by the model.
+
 In order for the system to be in canonical form, we must however perform a transformation. The challenge however is that we want the state space dynamics in
@@
 \vec{y}_k
-=& \mat{C}_{t}\vec{x}_k + \mat{D}_{d}\vec{u}_k
+=& \mat{C}_{t}\vec{x}_k% + \mat{D}_{d}\vec{u}_k
 \label{eq:observer_LTI_cf}
@@
 \begin{array}{cc}
-\mat{0}&\mat{I}\\
-k_n-a_n&\begin{array}{cc}\cdots&k_1-a_1\end{array}
+k_n-a_n&\begin{array}{cc}\cdots&k_1-a_1\end{array}\\
+\mat{I}&\mat{0}
 \end{array}\right]&&
@@
 \begin{array}{ccc}
-\mat{0}&&a_n-l_n\\
+a_n-l_n&&\mat{I}\\
 &&\vdots\\
-\mat{I}&&a_1-l_1
+a_1-l_1&&\mat{0}
 \end{array}\right]
@@
 \begin{align*}
-\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_d\right)\mat{T}_c^{-1}&
-\mat{A}_{o}=&\mat{T}_o\left(\mat{A}_d-\mat{L}_d\mat{C}_d\right)\mat{T}_o^{-1}\\
+\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
+\mat{A}_{o}=&\mat{T}_o\left(\mat{A}_d-\mat{L}\mat{C}_d\right)\mat{T}_o^{-1}\\
 \mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]&
-\mat{B}_{o}=&\mat{T}_c\mat{B}_d\mat{K}_d\mat{T}_o^{-1}\\
+\mat{B}_{o}=&\mat{T}_c\mat{B}_d\mat{K}\mat{T}_o^{-1}\\
 \mat{B}'=&\left[\begin{array}{c}\mat{T}_c\mat{B}_d\mat{k}_r\\\mat{0}\end{array}\right]&
-\mat{B}_{\eta}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_d\end{array}\right]\\
+\mat{B}_{\eta}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}\end{array}\right]\\
 \mat{T}_c=&\mat{R}_{cf}\mat{R}^{-1}&
@@
 \mat{C}_t=&\mat{C}_d\mat{T}_c&
-\mat{L}_d=& \mat{T}_o^{-1}\left[ \begin{array}{ccc}l_1&\cdots&l_n\end{array}\right]^T
+\mat{L}=& \mat{T}_o^{-1}\left[ \begin{array}{ccc}l_1&\cdots&l_n\end{array}\right]^T
 \end{align*}
@@
 the spectrum of $\mat{A}_{c}$ and $\mat{A}_{o}$, which can be calculated
-separately.  Additionally, these correspond to the roots of the polynomials
+separately.  In other words, the characteristic polynomial of the closed loop is
+equal to the multiplication of the characteristic polynomials of the controller
+and the observer when seen independently.
 %
 \begin{align*}
-\left(z^p+\sum_{i=1}^p{(a_i-k_i)z^{p-i}}\right) \left(z^p+\sum_{i=1}^p{(l_i-a_i)z^{p-i}}\right)
+P(z)=P_K(z)P_L(z)=\left(z^p+\sum_{i=1}^p{(a_i-k_i)z^{p-i}}\right) \left(z^p+\sum_{i=1}^p{(l_i-a_i)z^{p-i}}\right)
 \end{align*}
@@
 +\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
-\vec{y}_k=&\mat{C}_{t}\vec{x}_k' + \mat{D}_{d}\vec{u}_k
+\vec{y}_k=&\mat{C}_{t}\vec{x}_k'% + \mat{D}_{d}\vec{u}_k
 \label{eq:observer_LTI_FWL_cf}
@@
 \begin{align*}
-\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_d\right)\mat{T}_c^{-1}&
+\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
 \mat{A}_{o}=&\mat{T}_o\left({\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}{\mat{C}_d}_{\langle C \rangle}\right)\mat{T}_o^{-1}\\
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\todo{FWL effects here?}
+\todo{FWL effects here? they are implicit from equation \ref{eq:observer_LTI_FWL_cf}}
 
@@
 1  & DC Motor          & 2 & 2.1\,s& 16,16  &   4.1\,s &   4.1\,s\\
-2  & Helicopter        & 3  & 1.4\,s& 24,16  &   18.7\,s &   18.7\,s\\
+2  & Helicopter        & 3  & 1.4\,s& 8.6\,s  &   54.9\,s &   t.o.\\
 3  & Inverted Pendulum & 4 &   0.6\,s& 16,24  &  308.4\,s &  308.4\,s\\
@@
 \begin{equation}
-t_s<-log_{|\overline{\lambda}|}({p_s}) : |\overline{\lambda}| =\max(|\lambda_i|) \wedge |\overline{\lambda}|<1,\ \forall i \in [1\ n]
+t_s<-log_{\overline{\lambda}}({p_s}) : \overline{\lambda} =\max(|\lambda_i|) \wedge \overline{\lambda}<1,\ \forall i \in [1\ n]
 \label{eq:set_time}
@@
 percentage of the decay expressed.  Reversing we have
-$t=-\frac{ln(d)}{|\overline{\omega}|}=-\frac{ln(d)}{ln(|\overline{\lambda}|)}$. 
+$t=-\frac{ln(d)}{|\overline{\omega}|}=-\frac{ln(d)}{ln(\overline{\lambda})}$. 
 replacing for $p_s$ , $t_s$, and $\overline{\lambda}$ we get equation

### 2017-10-17 TACAS2018/paper.tex
sec 3.1 edit

@@
 \label{eq:ode1}
-\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^p, u \in \mathbb{R}^q, A \in \mathbb{R}^{p \times p}, B \in \mathbb{R}^{p \times q}, 
-\end{align}
-%
-where $t \in \mathbb R_0^+$, where $A$ and $B$ are matrices that 
+\dot{x}(t) = \mat{A}x(t)+ \mat{B} u(t), \quad x \in \mathbb{R}^p, u \in \mathbb{R}^q, \mat{A} \in \mathbb{R}^{p \times p}, \mat{B} \in \mathbb{R}^{p \times q},
+\end{align}
+%
+where $t \in \mathbb R_0^+$, where $\mat{A}$ and $\mat{B}$ are matrices that 
 specify the continuous plant, and with initial states set as $x(0)$.
 
-\todo{we are interested in observable systems so this is the definitely the case...}
-Furthermore, a control system may have a derived
-output that is a linear combination of its states and inputs, which may
-restrict the observability of the state-space from the output space.
+Furthermore, we are interested in control systems with a derived
+output $\vec{y}$ that is a linear combination of its states and inputs:
+%, which may restrict the observability of the state-space from the output space.
 \begin{equation}
@@
 
-In this work, equations~\eqref{eq:ode1} and~\eqref{eq:ode2} is soundly discretized in time (see Appendix~\ref{sec:cont_aa}) \todo{or use another paper as reference and remove sec .1?} into
+In this work, equations~\eqref{eq:ode1} and~\eqref{eq:ode2} are soundly discretized in time (see Appendix~\ref{sec:cont_aa}) \todo{or use another paper as reference and remove sec .1?} into
 \begin{align}
@@
 $\mat{A}_d$, $\mat{B}_d$, $\mat{C}_d$ and $\mat{D}_d$ denote the matrices that describe the discretized plant dynamics, whereas $\mat{A}$, $\mat{B}$, $\mat{C}$ and $\mat{D}$ denote the continuous plant dynamics.
-In this work we will assume $\mat{D}_d=\mat{D}=\mat{0}$.
-Since $\vec{y}$ can be directly derived from $\vec{x}$, we will omit discussing it in the following unless strictly necessary.
+In this work we assume $\mat{D}_d=\mat{D}=\mat{0}$.
+Also, since $\vec{y}$ can be directly derived from $\vec{x}$, we will omit discussing it in the following unless strictly necessary.
 %% We synthesize for requirements over this discrete-time domain. 

### 2017-10-17 TACAS2018/paper.tex
added a section on the state observer

@@
 effect on the output. A plant model that minimises the difference
-between the outputs is called an observer and it is a well known
+between its output and the real plant output is called an observer and it is a well known
 paradigm in the control literature~\cite{astrom1997computer}.
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Semantics of LTI models}\label{sec:model_semantics}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%
-The traces of the model starting from an initial set $X_0\subseteq \mathbb{R}^p$, 
-with inputs restricted to $U \subseteq \mathbb{R}^q$, are sequences 
-$ \vec{x}_0 \xrightarrow{\vec{u}_0} \vec{x}_1 \xrightarrow{\vec{u}_1} \vec{x}_2 \xrightarrow{\vec{u}_2} \ldots $, 
-%
-where $ \vec{x}_0 \in X_0$ and $\forall k\geq 0, \vec{u}_k \in U \text{ and } \vec{x}_{k+1} = \tau(\vec{x}_k,\vec{u}_k) $, 
-where 
-%
-\begin{equation}\label{equ:reachtraj}
-\tau(\vec{x}_k,\vec{u}_k) = 
-\big( \mat{A}\vec{x}_k +
-\mat{B}\vec{u}_k \mid \mat{G}\vec{x}_k \leq \vec{h}\big)\;. 
-\end{equation}
-%
-where $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
-%
-We extend the notation above to convex sets of initial conditions and inputs ($X_0$ and $U$), 
-and write $\tau(X_0,U)$ to denote the set of states $\{\vec{x} \mid \vec{x}_0 \in
-X_0 \wedge \vec{u} \in U \wedge \vec{x} = \tau(\vec{x}_0,\vec{u})\}$
-reached from $X_0$ by $\tau$ in one step. 
-%
-We furthermore write $\tau^n(X_0,U)$ to denote the set of states reached from
-$X_0$ via $\tau$ in $n$ steps (\emph{$n$-reach set}), i.e.\ for $n\geq 1$
-%
-\begin{align}\label{equ:reachset}
-\tau^n(X_0,U) = \{\vec{x}_n \mid &\vec{x}_0 \in X_0 \wedge \forall k\in [0,n-1]\nonumber\\ 
- &\vec{u}_{k} \in U \wedge \vec{x}_{k+1}=\tau(\vec{x}_{k},\vec{u}_{k}) \} \;. 
-\end{align}
-%
-Since the transformations $\mat{A}$ and $\mat{B}$ are linear and
-vector sums preserve convexity, the sets $X_n = \tau^n(X_0,U)$ are also
-convex.
-
-We define the \emph{$n$-reach tube} 
-\begin{equation}\label{equ:reachtube}
-\hat{X}_n=\hat{\tau}^n(X_0,U)=\bigcup_{k\in[0,n]} \tau^k(X_0,U)
-\end{equation}
-as the union of the reachable sets over $n$ iterations.
-%
-Moreover, $\hat{X} 
-=\bigcup_{n\geq 0} \tau^n(X_0,U)$ 
-extends the previous notion over an 
-unbounded time horizon.
-
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \section{Acceleration of continuous time systems}\label{sec:continuous_time_accel}
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- Note that the discretization in Sec.~\ref{sec:ssrepresentation} only 
- allows us to observe the system at integer multiples of the sample time.
- As we are interested in ensuring that certain properties of the system hold at any given
- time (not just integer multiples of the sample time),
- we accelerate the dynamics of the system (according to the model semantics in Sec.~\ref{sec:model_semantics}) in order to compute the state $\vec{x}_T$  at a given time $T$.
-
- %While this is adequate for the controller, it is not sufficient for verification. We must therefore establish a new model that allows us to observe the system at a given time $t$.
- %We achieve this by using acceleration as described below.
-
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsection{Accelerated dynamics for systems without inputs}\label{sec:real_discrete_no_inputs}
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- Given a specific time $T$, the state $\vec{x}_T$ present at $T$ can be expressed as a linear function of $\vec{x}_0$ as described below.
-Note that, as the system has no inputs, its dynamics are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.
-
- \begin{theorem}
- Given $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, we have
- \begin{align}
- \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x}_0\\
- \text{where }\mat{A}_{T}&= \mat{S}
- \left [ \begin{array}{cccc}
- e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(1)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
-0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
-\vdots & & \ddots & \vdots \\
-0 & \cdots & 0  &e^{T\lambda_i} \\
-\end{array} \right ]
- \mat{S}^{-1}
- \label{eq:continuous_tube_dyn}\\
- &\text{and } s_i=\left\{\begin{array}{cc}1&gm(\lambda_i)>1\\0&gm(\lambda_i)=1\end{array}\right.,\nonumber
- \end{align}
-$\lambda_i \in \mat{J}$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.
-We call $\vec{x}_T$ a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T.
- \end{theorem}
- %% We can apply Th.~\ref{eq:continuous_tube_dyn} to discretized systems without inputs in order to
- %% obtain a witness ..
-%
-\todo{Can the corallary be motivated? The general motivation of the section was observing the system at times that are not necessarily integer multiple of the sampling time...} 
- \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}_0 : k \in \mathbb{R}^+$ is a witness of the system at time $t=kT_d$.
- \end{corollary}
-% \begin{proof}
-% Let us recall equation \ref{eq:discretize}. The discrete representation of the system dynamics discretised with sample time $T_1$ is ruled by the formula
-% $\mat{A}_1 = e^{\mat{A} T_1}$. From matrix theory, we have 
-%\begin{align}
-% e^{\mat{A}}&=\sum_{k=0}^\infty \frac{1}{k!}\mat{A}^k
-%\end{align} 
-%\begin{align} 
-% e^{\mat{S}\mat{J}\mat{S}^{-1}}&=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{S}\mat{J}\mat{S}^{-1}\right)^k
-% =\mat{S} \left (\sum_{k=0}^\infty \frac{1}{k!}\mat{J}^k\right) \mat{S}^{-1}\nonumber\\
-% &=\mat{S}e^{\mat{J}}\mat{S}^{-1}
-%\end{align} 
-%\begin{equation}
-%\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \Rightarrow \vec{A}_1 = \mat{S}\mat{J}_1\mat{S}^{-1}= \mat{S}e^{\mat{J} T_1}\mat{S}^{-1}.
-% \end{equation}
-% 
-% Let $\mat{J}$ be a diagonal matrix, such that 
-% $${\lambda_1}_i=e^{\lambda_i T_1}, \forall \lambda_i \in \mat{J}.$$
-% Let us now take a different sample rate $T_2$, such that 
-% $${\lambda_2}_i=e^{\lambda_i T_2}, \forall \lambda_i \in \mat{J}.$$
-% We can then say that 
-% \begin{equation}
-% {\lambda_2}_i=e^{\lambda_i T_1 \frac{T_2}{T_1}}={\lambda_1}_i^{\frac{T_2}{T_1}} \Rightarrow A_2=A_1^{\frac{T_2}{T_1}}.
-% \end{equation}
-% This proves the theorem for $gm(\lambda_i)=1$.
-% We now note that given an exponentiated Jordan form with geometric multiplicity, the upper diagonal terms can be
-% referenced to the original eigenvalues modified by the sampling rate.
-%  Let $\mat{J}\in \mathbb{R}^{p \times p}$ be a Jordan Canonical matrix.
-% Then
-%\begin{align}
-% \mat{J}_1&=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{J}T_1\right)^k=\sum_{k=0}^\infty \frac{1}{k!} \left [ \begin{array}{cccc}
-% \lambda_i^k  & \binom{k}{1}  \lambda^{k-1} & \hdots  & \binom{k}{p-1} \lambda_i^{k-p+1} \\
-%& \lambda_i^k  & \binom{k}{1}  \lambda_i^{k-1} & \vdots \\
-%\vdots & \ddots & \ddots & \vdots \\
-%& &  &\lambda_i^k \\
-%\end{array} \right ] T_1^k
-%\end{align}
-%The eigenvalues remain the same as in the diagonal case, but the upper triangular terms are of the form:
-%\begin{align}
-%\forall j>i, c_{ij}&=\sum_{k=j-i}^\infty \frac{1}{k!}\binom{k}{j-i} \lambda_i^{k-(j-i)}T_1^k\\
-%&=\frac{1}{(j-i)!}\sum_{k=j-i}^\infty \frac{1}{(k-(j-i))!} \lambda_i^{k-(j-i)}T_1^k\nonumber\\
-%&=\frac{T_1^{j-i}e^{\lambda_i T_1}}{(j-i)!}\nonumber
-%\end{align}
-%which completes the proof for $gm(\lambda_i)>1$.
-%\end{proof}
-
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsection{Accelerated dynamics for systems with parametric inputs}\label{sec:real_discrete_param_inputs}
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- Next, we are interested in observing systems with parametric
- inputs, described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$.
- For such systems, a witness $\vec{x}_T$ is computed next.
-\begin{theorem}
-The expression
- \begin{align}
- \vec{x}_T&=\vec{x}(t=T)=\mat{A}^{-1}\vec{x}_T'\nonumber\\
-\vec{x}_T'&=\mat{A}\mat{A}_T\vec{x}_0 + (\mat{I}-\mat{A}_T)\mat{B}\vec{u} : \forall t \leq T,\ \vec{u}(t)=\vec{u} 
- \end{align}
- with $\mat{A}_T$ as per \eqref{eq:continuous_tube_dyn} is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$.
-\end{theorem}
- \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}_0+(\mat{I}-\mat{A}_d^k\mat{B}\vec{u}) : k \in \mathbb{R}^+$ is a witness of the system at time $kT_d$.
- \end{corollary}
-% \begin{proof}
-% We begin by expanding the equation
-% \begin{align}
-% \vec{x}_T&=\mat{A}^{-1}\vec{x}_T'\nonumber\\
-% &=\mat{A}_T\vec{x}_0 + \mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}\vec{u}\nonumber\\
-% &= \mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u}
-% \end{align}
-% where $\mat{A}_T=e^{\mat{A}T}$ and $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$ correspond to $\mat{A}_d$ and $\mat{B}_d$ in equation \eqref{eq:discretize}
-% \end{proof}
-
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsection{Accelerated dynamics for systems with discrete time feedback inputs}\label{sec:real_discrete_feedback_inputs}
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-The final case we analyse is that of hybrid time systems, where the
-plant dynamics evolve in continuous time while the feedback dynamics evolve
-in discrete time, i.e. a new input value is only produced for every sample interval.
-
-\begin{theorem}
-The expression
- \begin{align}
- \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
- \label{eq:cyber_feedback}
- \end{align}
- with $\mat{A}_T$ as per \eqref{eq:continuous_tube_dyn}, 
- $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$ and 
- $\mat{A}_d, \mat{B}_d$ describing the discretized plant dynamics is a witness of the system
- \begin{align}
- \dot{\vec{x}}(t) &= \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\nonumber\\
- \vec{u}(t)&=\mat{K}\vec{x}_k  \mid  kT_s \leq t < (k+1)T_s
- \end{align}
- \end{theorem}
-%
-%
-%\begin{proof}
-%Let $\mat{K}$ be a feedback controller such that $\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$. Let the output of
-%the feedback system be a zero order holder such that $\vec{u}(t+kT_s)=\vec{u}(kT_s) : 0 \leq t < T_s$.
-%The closed loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
-%\begin{equation}
-%\vec{x}_{k,t}=\mat{A}_t\vec{x}_k-\mat{B}_t\mat{K}\vec{x}_k = (\mat{A}_t-\mat{B}_t\mat{K})\vec{x}_k : 0 \leq t < T_s
-%\end{equation}
-%We further explore the dynamics across discrete time boundaries. Let $\mat{A}_d=\mat{A}_{T_s}$ and $\mat{B}_d=\mat{B}_{T_s}$
-%\begin{align}
-%\vec{x}_{k}&=\vec{x}_{k-1,T_s}= (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}\\
-%\vec{x}_{k,T_s} &= (\mat{A}_d-\mat{B}_d\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}
-%\end{align}
-%which accelerating results becomes
-%\begin{align}
-%\label{eq:feedback_sampled_cont}
-%\vec{x}_{k} &= (\mat{A}_d-\mat{B}_d\mat{K}) ^k\vec{x}_0\\
-%\vec{x}_{t} &= (\mat{A}_{t-kT_s}-\mat{B}_{t-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
-%\label{eq:feedback_cont}
-%\end{align}
-%\end{proof}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Error modelling and soundness}\label{sec:errors}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Time delay on discrete time feedback systems} \label{sec:delay}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-A common ocurrence in digital systems is that they do not necessarily
-satisfy the real-time specifications.  Delays due to processing time,
-communication lines, or other mechanisms will cause disturbances in the
-control loop.  In our model these delays are all deferred to the ZOH, i.e.,
-we presume that everything that happens in the digital world takes place at
-the sampling instance $t$ and the output of the result is delayed at the DAC
-when it is fed back into the real world.  We~will also presume that this
-delay is much smaller than the sampling time.
-
-\begin{theorem}
-The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modelled as a non-deterministic noise signal upperbound by 
-\begin{align}
-|\vec{y}_{k}-{\vec{y}_{t_d}}_{k}|_1 \leq q_t, \text{ where } q_t=&(|\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})|_1+|\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}|_1)|U|_\infty
-\end{align}
-where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$.
-\end{theorem}
-%
-\todo{notation $| |_x$ ?}
-%
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Errors generated by the numerical representation} 
-\label{sec:numeric_rep}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-The models we consider have two sources of error that are due to numerical  
-representation which we commonly refer to as the FWL effect.
-The first is the numerical error introduced by the
-fixed-point numbers employed to model the plant, i.e., to represent the
-plant dynamics $A_d$, $B_d$, $C_d$, $D_d$, $x_k$ and $y_k$.
-The second is the quantization error
-introduced by the digital controller, which performs operations on
-fixed-point numbers.  In this section we outline the notation for the
-representation of numbers, and briefly describe the errors
-introduced.  A~formal discussion is in
-Appendix~\ref{sec:numeric_rep}.
-
-Let $\mathbb{R}_{\langle M,F \rangle}$ be a fixed point domain with $M$ bits
-representing the binary word length of the representation and $F$ bits
-representing the prescaling $2^{-F}$ (\emph{i.e} the number of bits after
-the decimal place).  We note that a negative $F$ denotes an integer
-multiplication that adds $-F$ trailing zeros in the number represented by
-$M$.
-%Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point
-%domain with $M$ bits mantissa and $E$ bits exponent.  This domain
-%corresponds to $$\mathbb{R}_{\langle M,[E] \rangle} = \bigcup_F
-%\mathbb{R}_{\langle M,F \rangle} \mid F \in [2^{1-E}, 2^{E-1}]$$ This
-%definition important because it means that the distance between any two
-%numbers in the domain depends on the location of those numbers.  Since
-%a floating point domain is a union of a number of fixed
-%point domains, we will continue our reasoning on fixed point only, which
-%will apply to the floating point domain by extension.  Operations on these
-%numbers will incur errors that can be bound
-%by~\cite{DBLP:conf/arith/BrainTRW15}.
-
-We will use the domain $\mathbb{R}_{\langle C \rangle} \mid \langle C \rangle = \langle M_c,F_c \rangle$
-to represent the fixed point precision of the controller, and 
-$\mathbb{R}_{\langle P \rangle} \supseteq \mathbb{R}_{\langle C \rangle}$
-to represent the domain of the plant model.
-Thus, any mathematical operations in our modelled digital controller will be executed in the
-domain $\mathbb{R}_{\langle C \rangle}$, and all other calculations
-in our model will be carried out in the domain $\mathbb{R}_{\langle P \rangle}$.
-Given ${\langle M,F \rangle}$ we use $\mathcal{F}_{\langle M,F \rangle} : \mathbb{R} \rightarrow \mathbb{R}_{\langle M,F \rangle}$ as the truncation function.
-
-%% The physical plant operates in the reals, which means
-%% our verification phase must also account for the numerical error caused by representing the
-%% physical plant at the finite precision $\mathbb{R}_{\langle P \rangle}$.
-
-%% We will use these subindices to represent functions, number, vectors and matrices in their
-%% corresponding domains.
-
-%\todo{unclear}
-%We further note that by choosing $\langle C \rangle = \langle M_c,[E_c] \rangle$
-%we extend the following to floating point reasoning.
-
-%% \subsubsection{Effect on safety specification and stability}
-
-%% Let us first consider the effect of the quantization errors on safety. 
-%% Within the controller, state values are manipulated at low precision,
-%% alongside the vector multiplication $Kx$.
-%% %
-%% %computed considering the error introduced by the digital controller caused by performing the vector multiplication $Kx$ at low digital precision.
-%% The inputs are computed using the following equation: 
-%% %
-%% \begin{align*}
-%% u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})). 
-%% \end{align*}
-
-%% This induces two types of the errors detailed above: first, the truncation
-%% error due to representing $x_k$ as $\mathcal{F}{\langle I_c,F_c
-%% \rangle}(x_{k})$; and second, the rounding error introduced by the
-%% multiplication operation.  We represent these errors as non-deterministic
-%% additive noise.%, which might de-stabilize the closed-loop model.
-
-%% An additional error is due to the representation of the plant dynamics, namely 
-%% %
-%% \begin{align*}
-%% x_{k+1} &=\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
-%% \end{align*}
-%% We address this error by use of interval
-%% arithmetic~\cite{moore1966interval} in the verification phase.
-
-%% Previous studies~\cite{gangli1} show that the FWL affects the poles and
-%% zeros positions, degrading the closed-loop dynamics, causing steady-state
-%% errors (see Appendix~\ref{sec:appendix:LTIbackground} for details) and
-%% eventually de-stabilizing the system~\cite{Bessa16}.  However, since in this
-%% paper we require stability only as a precursor to safety, it is sufficient
-%% to check that the (perturbed, noisy) model converges to a neighborhood of
-%% the equilibrium within the safe set (see Appendix~\ref{sec:stab_FWL}).
-
-%% In the following, we shall disregard these steady-state errors (caused by
-%% FWL effects) when stability is ensured by synthesis, and then verify its
-%% safety accounting for the finite-precision errors.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Quantization errors} \label{sec:quantization}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Let us first consider the effect of the quantization errors. 
-Within the controller, state values are manipulated at low precision.
-%alongside the vector multiplication $\mat{K}\vec{x}$.
-Furthermore, the quantizers for the DAC and the ADC introduce truncation errors
-which we denote by the effect of the functions $\mathcal{F}_{\langle D \rangle}$
-and $\mathcal{F}_{\langle A \rangle}$, respectively. Finally, let us call $\vec{\nu}_e$ the
-error caused by the FWL effects on the observer
-\todo{the observer was not defined..}
-(\emph{i.e} the numerical errors 
-in the calculations as opposed to the estimation error).
-The inputs are computed using the following equation: 
-%
-\begin{align}
-u_{k}&=\mathcal{F}_{\langle D \rangle}\left(-\mat{K}_{\langle C \rangle}\cdot\left(\mathcal{F}_{\langle C \rangle}\left(\mathcal{F}_{\langle A \rangle}(\vec{x}_{k})\right)\right) +\vec{\nu}_e\right)
-\label{eq:uk}
-\end{align}
-
-This induces two types of the errors: first, the truncation
-error due to the domain transformations $\mathcal{F}_{\langle *
-\rangle}(\cdot)$; and second, the rounding error introduced by the
-multiplication operation.  We represent these errors as non-deterministic
-additive noise. More details can be found in Appendix~\ref{appendix:quantization}.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Modelling errors}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Errors incurred by the use of numerical algorithms during synthesis are not
-accounted for but rather checked during the verification phase.  If the
-counterexample provided corresponds to a pre-existing one, the synthesiser
-then increases its precision to reduce this error.
-
-Previous studies~\cite{gangli1} show that the FWL affects the poles and
-zeros positions, degrading the closed-loop dynamics, causing steady-state
-errors and eventually de-stabilizing the system~\cite{Bessa16}.  However,
-since the verifier also checks for the stability of the dynamics as a
-precursor to safety, this case is handled inside the loop.  In the
-following, we shall disregard these steady-state errors (caused by FWL
-effects) when stability is ensured by synthesis, and then verify its safety
-accounting for the finite-precision errors.
-
-%-------------------------------
-\section{Specification of control systems properties} 
-\label{sec:specification}
-%-------------------------------
-\todo{all this section needs to be merged with the next one and only
-discussed for an observed model.}
-
-%-------------------------------
-\subsection{Stability} 
-\label{ssec:stabspecification}
-%-------------------------------
-
-In this work we are interested in asymptotic stability: asymptotic
-stability is a property that amounts to convergence of the model
-executions to an equilibrium point, starting from any states in a
-neighborhood of the point.
-
-%% There are a number of algorithms that can be
-%% used for stability analysis~\cite{daes20161,Bessa16}.
-
-A discrete-time LTI system is
-asymptotically stable if all the roots of its characteristic
-polynomial (i.e., the eigenvalues of the closed-loop matrix $A_d - B_d
-K$) are inside the unity circle of the complex plane, i.e., their
-absolute values are strictly less than one~\cite{astrom1997computer}
-(this simple sufficient condition can be generalised, however this is
-not necessary in our work).  In this paper, we express this stability
-specification $\phi_\mathit{stability}$ in terms of a check known as
-\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic
-formula to select the entries of matrix $K$ so that the closed-loop
-dynamics are shaped as desired.
-
-%-------------------------------
-\subsection{Safety} 
-\label{ssec:safespecification}
-%-------------------------------
-
-We are not limited to the synthesis of digital stabilizing controllers -- a
-well known task in the literature on digital control systems -- but target
-safety requirements with an overall approach that is sound and automated. 
-More specifically, we require that the closed-loop system meets given safety
-specifications.  A safety specification gives raise to a requirement on the
-states of the model, such that the feedback controller (namely the choice of
-the gains matrix~$K$) must ensure that the state never violates the
-requirement.  Note that a stable, closed-loop system is not necessarily a
-safe system: indeed, the state values may leave the safe part of the state
-space while they converge to the equilibrium, which is typical in the case
-of oscillatory dynamics.  In~this work, the safety property is expressed as:
-%
-\begin{align}
-\phi_\mathit{safety}\equiv& \underline{y} \leq y_k \leq \overline{y}
-\iff \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
-\label{eq:safetyspec}
-\end{align}
-
-where $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
-
-Furthermore, we also need to consider the 
-constraints 
-\begin{align}
-\phi_\mathit{input}\equiv \underline{u} \leq u_k \leq \overline{u}
-\label{eq:inputspec}
-\end{align}
-which comes from physical restrictions in the energy of the system, and
-\begin{align}
-\phi_\mathit{init}\equiv \mat{G}' \vec{x}_0 \leq \vec{h}'
-\label{eq:initspec}
-\end{align}
-
-%-------------------------------
-\subsection{Transient response} 
-\label{ssec:transientspecification}
-%-------------------------------
-In many cases the speed of the response, i.e. how fast it converges to the set point, is a requirement of great importance. 
-This is given as a settling time for the system to become stable.
-
-\begin{theorem}
-Given a set of eigenvalues for a discrete time model of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1\ n]$, the settling time of the system is upperbounded by
-\begin{equation}
-t_s<-log_{\overline{\lambda}}({p_s}) : \overline{\lambda} = \max(|\lambda_i|) \wedge \overline{\lambda}<1,\ \forall i \in [1\ n]
-\label{eq:set_time}
-\end{equation}
-where $0\leq p_s \leq 1$ is the desired percentage of the target within which the output must remain after $t_s$.
-\end{theorem}
-%\begin{proof}
-%In a SISO system, there are two values that typically define the
-%response-time of the system (using a step response).
-%%
-%\begin{enumerate}
-%\item The \emph{rise time} is defined as the time it takes the output to reach a percentage (eg $90\%$) of the target value given a step chnage in the input.
-%\item The \emph{settling time} is defined as the time it takes the output to stabilize within a margin of the target value (eg $10\%$).
-%\end{enumerate} 
-%%
-%In the case of first and second order systems, the decay is governed by the equations 
-%%
-%\begin{align*}
-%&y_{decay}=
-%&\left\{
-%\begin{array}{cc}
-%e^{-|\omega| t}& 1^{st} order\\
-%e^{\zeta |\omega| t}\left(\frac{\sin\left(|\omega| t\sqrt{1-\zeta^2}+\sin^{-1}\sqrt{1-\zeta^2}\right)}{\sqrt{1-\zeta^2}} \right)&\zeta<1\\
-%e^{-|\omega| t}-|\omega| t e^{-|\omega| t}&\zeta=1\\
-%\frac{|\omega| e^{-|\omega_2| t}-|\omega_2| e^{-|\omega| t}}{|\omega|-|\omega_2|}&\zeta>1\end{array}\right.
-%\end{align*}
-%where $|\omega|$ and $|\omega_2|$ are the magnitudes of the eigenvalues (roots) of the system and  $\zeta=-\cos(\theta)$ where $\theta$ is the polar angle of the conjugate pair if it exists ($\zeta \geq 1$ if it doesn't).
-%These equations become increasingly complicated for higher order systems.
-However, we note their strong dependency on the magnitude of the eigenvalues, and use this property to define an upperbound on the decay function.
-%All of the above equations will decay faster than $e^{-|\omega| t}$ given $|\omega| < |\omega_2|$, hence we may use this function as our upper bound.
-%
-%Given a closed loop single output LTI system of order $n$ with dynamics
-%\begin{equation}
-%\left\{\begin{array}{c}\vec{x}_k=\mat{A}\vec{x}_{k-1}\\ \vec{y}_k=\mat{C}\vec{x}_k\end{array}\right.
-\Rightarrow \left\{ \begin{array}{c}\vec{x}_k'=\mat{J}\vec{x}_{k-1}'\\ \vec{y}_k=\mat{C}\mat{S}\vec{x}_k'\end{array}\right.
-: \left\{ \begin{array}{c}\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \\ \vec{x}_k'=\mat{S}^{-1}\vec{x}_k\end{array}\right.
-%\label{eq:eigendynamics}
-%\end{equation}
-%%
-%the output decay is a linear combination of the decay of eigenvalues or
-%eigenvalue pairs.  Let $\mat{C}'\in \mathbb{R}^{1 \times n}=\mat{C}\mat{S}$. 
-%Since $\mat{C}'$ is constant, the output $y_k$ is a linear combination of
-%the states $\vec{x}'_k$.  We accelerate equation \eqref{eq:eigendynamics} to
-%obtain
-%%
-%\begin{align}
-%%\vec{x}_k'&=\mat{J}^k\vec{x}_0' \\
-%y_k&=\mat{C}'\mat{J}^k\vec{x}_0 = \sum_{i=0}^p \left( c_i \lambda_i^k + c_{il}\binom{k}{l} \lambda_i^{k-l}\right)\\
-%|y_k|&\leq \sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right||\lambda_i^k|
-%\end{align}
-%%
-%where the second  part of the equation corresponds to the upper diagonal
-%terms of the Jordan blocks.  We also have $|\lambda_i^k|\leq
-%|\overline{\omega}^k|$,hence
-%%
-%\begin{align}
-%|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right|
-%\end{align}
-%%
-%Since we are synthesising the eigenvalues, rather than solve this formula
-%for complex Jordan Shapes, we will restrict our synthesiser to provide
-%solutions with distinct eigenvalues (which is by far the most common case). 
-%Therefore the right hand terms dissappear and we obtain
-%%
-%\begin{align}
-%|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n |c_i|
-%\end{align}
-%
-%Hence the overall decay of the system is always smaller
-%than $d=e^{-|\overline{\omega}| t}$ where $0\leq d\leq 1$ is the remaining
-%percentage of the decay expressed.  Reversing we have
-%$t=-\frac{ln(d)}{|\overline{\omega}|}=-\frac{ln(d)}{ln(\overline{\lambda})}$. 
-%replacing for $p_s$ , $t_s$, and $\overline{\lambda}$ we get equation
-%\eqref{eq:set_time}
-%%
-%\qed
-%\end{proof}
-%
-We may now use this limit to express a constraint in terms of the
-coefficients for our synthesis process.  Let
-%
-\begin{equation}
-P=\prod_{i=0}^p (s-\lambda_i)=\sum_{j=0}^p c_js^j.
-\end{equation}
-%
-We use Jury's criterion to limit $|\lambda_i| \leq 1$.  Let us now define a
-transformation $\lambda_i'=\frac{\lambda_i}{\overline{\lambda}}$.  We want
-to ensure $\lambda_i' \leq 1$ which can be done by applying Jury's criterion
-to $P'=\prod_{i=0}^p (s-\lambda_i')=\sum_{j=0}^p c_j's^j$ where $c_j'$ are
-unknown.  However, if we replace for $\lambda_i$, we obtain
-%
-\begin{equation}
-P'=\prod_{i=0}^p (s-\lambda_i')=\prod_{i=0}^p \left(s-\frac{\lambda_i}{\overline{\lambda}}\right)=\sum_{j=0}^p \frac{c_j}{\overline{\lambda}^{p-j}}s^j
-\end{equation}
-%
-where all members are known, we may now synthesise coefficients that ensure
-the eigenvalues are smaller than a desired magnitude, thus ensuring that the
-settling time is too.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Verification of a Controllable Observed System}\label{sec:cof_verification}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\todo{the observer dynamics?}
-
+\subsection{State observer}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 In most real implementations, the internal state of a plant cannot be
-directly measured but rather inferred from its
-effect on the output. A plant model that minimises the difference
-between the outputs is called an observer and it is a well known
-paradigm in the control literature~\cite{astrom1997computer}. Since we
-are interested in synthesising controllers with observer designs, in this
-section we will look at checking stability and safety in the presence of an observer.
-
-%the challenges presented by the introduction of the observer.
+directly measured but rather inferred from its effect on the output by
+using an observer.  Essentially, a state observer is a system that
+provides an estimate of the internal state of a given real system,
+from measurements of the input and output of the real system.
+
+A closed-loop digital control system with observer is shown in Fig.~\ref{fig:observersystem}.
+Note that the variables of a state observer are denoted by a "$~\hat{}~$" (e.g. {$\hat {\vec{x}}(k)$})
+  to distinguish them from the variables of the actual physical system.
+  Moreover, $\vec{y}_e=\hat{\vec{y}_k}-\vec{y}_k$ is the output estimation error defined
+  as the difference between the real output $\vec{y}_k$ and estimated one $\hat{\vec{y}_k}$, whereas
+  $\mat{L}$ is the error sensitivity matrix, which amplifies the output estimation error.
+  The figure also contains references to $\nu_1$, $\nu_2$, $\nu_1'$, $\nu_2'$ and $\nu_t$, which
+  denote noise and will be explained later in the paper.
+%%   With respect to noises (denoted by $\nu$), 
+%% $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations.
+  Lastly, $k_r$ is a reference gain required by the model.
 
@@
 \end{figure*}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Semantics of LTI models}\label{sec:model_semantics}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%
+The traces of the model starting from an initial set $X_0\subseteq \mathbb{R}^p$, 
+with inputs restricted to $U \subseteq \mathbb{R}^q$, are sequences 
+$ \vec{x}_0 \xrightarrow{\vec{u}_0} \vec{x}_1 \xrightarrow{\vec{u}_1} \vec{x}_2 \xrightarrow{\vec{u}_2} \ldots $, 
+%
+where $ \vec{x}_0 \in X_0$ and $\forall k\geq 0, \vec{u}_k \in U \text{ and } \vec{x}_{k+1} = \tau(\vec{x}_k,\vec{u}_k) $, 
+where 
+%
+\begin{equation}\label{equ:reachtraj}
+\tau(\vec{x}_k,\vec{u}_k) = 
+\big( \mat{A}\vec{x}_k +
+\mat{B}\vec{u}_k \mid \mat{G}\vec{x}_k \leq \vec{h}\big)\;. 
+\end{equation}
+%
+where $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
+%
+We extend the notation above to convex sets of initial conditions and inputs ($X_0$ and $U$), 
+and write $\tau(X_0,U)$ to denote the set of states $\{\vec{x} \mid \vec{x}_0 \in
+X_0 \wedge \vec{u} \in U \wedge \vec{x} = \tau(\vec{x}_0,\vec{u})\}$
+reached from $X_0$ by $\tau$ in one step. 
+%
+We furthermore write $\tau^n(X_0,U)$ to denote the set of states reached from
+$X_0$ via $\tau$ in $n$ steps (\emph{$n$-reach set}), i.e.\ for $n\geq 1$
+%
+\begin{align}\label{equ:reachset}
+\tau^n(X_0,U) = \{\vec{x}_n \mid &\vec{x}_0 \in X_0 \wedge \forall k\in [0,n-1]\nonumber\\ 
+ &\vec{u}_{k} \in U \wedge \vec{x}_{k+1}=\tau(\vec{x}_{k},\vec{u}_{k}) \} \;. 
+\end{align}
+%
+Since the transformations $\mat{A}$ and $\mat{B}$ are linear and
+vector sums preserve convexity, the sets $X_n = \tau^n(X_0,U)$ are also
+convex.
+
+We define the \emph{$n$-reach tube} 
+\begin{equation}\label{equ:reachtube}
+\hat{X}_n=\hat{\tau}^n(X_0,U)=\bigcup_{k\in[0,n]} \tau^k(X_0,U)
+\end{equation}
+as the union of the reachable sets over $n$ iterations.
+%
+Moreover, $\hat{X} 
+=\bigcup_{n\geq 0} \tau^n(X_0,U)$ 
+extends the previous notion over an 
+unbounded time horizon.
+
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ \section{Acceleration of continuous time systems}\label{sec:continuous_time_accel}
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ Note that the discretization in Sec.~\ref{sec:ssrepresentation} only 
+ allows us to observe the system at integer multiples of the sample time.
+ As we are interested in ensuring that certain properties of the system hold at any given
+ time (not just integer multiples of the sample time),
+ we accelerate the dynamics of the system (according to the model semantics in Sec.~\ref{sec:model_semantics}) in order to compute the state $\vec{x}_T$  at a given time $T$.
+
+ %While this is adequate for the controller, it is not sufficient for verification. We must therefore establish a new model that allows us to observe the system at a given time $t$.
+ %We achieve this by using acceleration as described below.
+
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ \subsection{Accelerated dynamics for systems without inputs}\label{sec:real_discrete_no_inputs}
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ Given a specific time $T$, the state $\vec{x}_T$ present at $T$ can be expressed as a linear function of $\vec{x}_0$ as described below.
+Note that, as the system has no inputs, its dynamics are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.
+
+ \begin{theorem}
+ Given $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, we have
+ \begin{align}
+ \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x}_0\\
+ \text{where }\mat{A}_{T}&= \mat{S}
+ \left [ \begin{array}{cccc}
+ e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(1)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
+0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
+\vdots & & \ddots & \vdots \\
+0 & \cdots & 0  &e^{T\lambda_i} \\
+\end{array} \right ]
+ \mat{S}^{-1}
+ \label{eq:continuous_tube_dyn}\\
+ &\text{and } s_i=\left\{\begin{array}{cc}1&gm(\lambda_i)>1\\0&gm(\lambda_i)=1\end{array}\right.,\nonumber
+ \end{align}
+$\lambda_i \in \mat{J}$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.
+We call $\vec{x}_T$ a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T.
+ \end{theorem}
+ %% We can apply Th.~\ref{eq:continuous_tube_dyn} to discretized systems without inputs in order to
+ %% obtain a witness ..
+%
+\todo{Can the corallary be motivated? The general motivation of the section was observing the system at times that are not necessarily integer multiple of the sampling time...} 
+ \begin{corollary}
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}_0 : k \in \mathbb{R}^+$ is a witness of the system at time $t=kT_d$.
+ \end{corollary}
+% \begin{proof}
+% Let us recall equation \ref{eq:discretize}. The discrete representation of the system dynamics discretised with sample time $T_1$ is ruled by the formula
+% $\mat{A}_1 = e^{\mat{A} T_1}$. From matrix theory, we have 
+%\begin{align}
+% e^{\mat{A}}&=\sum_{k=0}^\infty \frac{1}{k!}\mat{A}^k
+%\end{align} 
+%\begin{align} 
+% e^{\mat{S}\mat{J}\mat{S}^{-1}}&=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{S}\mat{J}\mat{S}^{-1}\right)^k
+% =\mat{S} \left (\sum_{k=0}^\infty \frac{1}{k!}\mat{J}^k\right) \mat{S}^{-1}\nonumber\\
+% &=\mat{S}e^{\mat{J}}\mat{S}^{-1}
+%\end{align} 
+%\begin{equation}
+%\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \Rightarrow \vec{A}_1 = \mat{S}\mat{J}_1\mat{S}^{-1}= \mat{S}e^{\mat{J} T_1}\mat{S}^{-1}.
+% \end{equation}
+% 
+% Let $\mat{J}$ be a diagonal matrix, such that 
+% $${\lambda_1}_i=e^{\lambda_i T_1}, \forall \lambda_i \in \mat{J}.$$
+% Let us now take a different sample rate $T_2$, such that 
+% $${\lambda_2}_i=e^{\lambda_i T_2}, \forall \lambda_i \in \mat{J}.$$
+% We can then say that 
+% \begin{equation}
+% {\lambda_2}_i=e^{\lambda_i T_1 \frac{T_2}{T_1}}={\lambda_1}_i^{\frac{T_2}{T_1}} \Rightarrow A_2=A_1^{\frac{T_2}{T_1}}.
+% \end{equation}
+% This proves the theorem for $gm(\lambda_i)=1$.
+% We now note that given an exponentiated Jordan form with geometric multiplicity, the upper diagonal terms can be
+% referenced to the original eigenvalues modified by the sampling rate.
+%  Let $\mat{J}\in \mathbb{R}^{p \times p}$ be a Jordan Canonical matrix.
+% Then
+%\begin{align}
+% \mat{J}_1&=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{J}T_1\right)^k=\sum_{k=0}^\infty \frac{1}{k!} \left [ \begin{array}{cccc}
+% \lambda_i^k  & \binom{k}{1}  \lambda^{k-1} & \hdots  & \binom{k}{p-1} \lambda_i^{k-p+1} \\
+%& \lambda_i^k  & \binom{k}{1}  \lambda_i^{k-1} & \vdots \\
+%\vdots & \ddots & \ddots & \vdots \\
+%& &  &\lambda_i^k \\
+%\end{array} \right ] T_1^k
+%\end{align}
+%The eigenvalues remain the same as in the diagonal case, but the upper triangular terms are of the form:
+%\begin{align}
+%\forall j>i, c_{ij}&=\sum_{k=j-i}^\infty \frac{1}{k!}\binom{k}{j-i} \lambda_i^{k-(j-i)}T_1^k\\
+%&=\frac{1}{(j-i)!}\sum_{k=j-i}^\infty \frac{1}{(k-(j-i))!} \lambda_i^{k-(j-i)}T_1^k\nonumber\\
+%&=\frac{T_1^{j-i}e^{\lambda_i T_1}}{(j-i)!}\nonumber
+%\end{align}
+%which completes the proof for $gm(\lambda_i)>1$.
+%\end{proof}
+
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ \subsection{Accelerated dynamics for systems with parametric inputs}\label{sec:real_discrete_param_inputs}
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ Next, we are interested in observing systems with parametric
+ inputs, described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$.
+ For such systems, a witness $\vec{x}_T$ is computed next.
+\begin{theorem}
+The expression
+ \begin{align}
+ \vec{x}_T&=\vec{x}(t=T)=\mat{A}^{-1}\vec{x}_T'\nonumber\\
+\vec{x}_T'&=\mat{A}\mat{A}_T\vec{x}_0 + (\mat{I}-\mat{A}_T)\mat{B}\vec{u} : \forall t \leq T,\ \vec{u}(t)=\vec{u} 
+ \end{align}
+ with $\mat{A}_T$ as per \eqref{eq:continuous_tube_dyn} is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$.
+\end{theorem}
+ \begin{corollary}
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}_0+(\mat{I}-\mat{A}_d^k\mat{B}\vec{u}) : k \in \mathbb{R}^+$ is a witness of the system at time $kT_d$.
+ \end{corollary}
+% \begin{proof}
+% We begin by expanding the equation
+% \begin{align}
+% \vec{x}_T&=\mat{A}^{-1}\vec{x}_T'\nonumber\\
+% &=\mat{A}_T\vec{x}_0 + \mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}\vec{u}\nonumber\\
+% &= \mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u}
+% \end{align}
+% where $\mat{A}_T=e^{\mat{A}T}$ and $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$ correspond to $\mat{A}_d$ and $\mat{B}_d$ in equation \eqref{eq:discretize}
+% \end{proof}
+
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ \subsection{Accelerated dynamics for systems with discrete time feedback inputs}\label{sec:real_discrete_feedback_inputs}
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+The final case we analyse is that of hybrid time systems, where the
+plant dynamics evolve in continuous time while the feedback dynamics evolve
+in discrete time, i.e. a new input value is only produced for every sample interval.
+
+\begin{theorem}
+The expression
+ \begin{align}
+ \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
+ \label{eq:cyber_feedback}
+ \end{align}
+ with $\mat{A}_T$ as per \eqref{eq:continuous_tube_dyn}, 
+ $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$ and 
+ $\mat{A}_d, \mat{B}_d$ describing the discretized plant dynamics is a witness of the system
+ \begin{align}
+ \dot{\vec{x}}(t) &= \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\nonumber\\
+ \vec{u}(t)&=\mat{K}\vec{x}_k  \mid  kT_s \leq t < (k+1)T_s
+ \end{align}
+ \end{theorem}
+%
+%
+%\begin{proof}
+%Let $\mat{K}$ be a feedback controller such that $\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$. Let the output of
+%the feedback system be a zero order holder such that $\vec{u}(t+kT_s)=\vec{u}(kT_s) : 0 \leq t < T_s$.
+%The closed loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
+%\begin{equation}
+%\vec{x}_{k,t}=\mat{A}_t\vec{x}_k-\mat{B}_t\mat{K}\vec{x}_k = (\mat{A}_t-\mat{B}_t\mat{K})\vec{x}_k : 0 \leq t < T_s
+%\end{equation}
+%We further explore the dynamics across discrete time boundaries. Let $\mat{A}_d=\mat{A}_{T_s}$ and $\mat{B}_d=\mat{B}_{T_s}$
+%\begin{align}
+%\vec{x}_{k}&=\vec{x}_{k-1,T_s}= (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}\\
+%\vec{x}_{k,T_s} &= (\mat{A}_d-\mat{B}_d\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}
+%\end{align}
+%which accelerating results becomes
+%\begin{align}
+%\label{eq:feedback_sampled_cont}
+%\vec{x}_{k} &= (\mat{A}_d-\mat{B}_d\mat{K}) ^k\vec{x}_0\\
+%\vec{x}_{t} &= (\mat{A}_{t-kT_s}-\mat{B}_{t-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
+%\label{eq:feedback_cont}
+%\end{align}
+%\end{proof}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{Error modelling and soundness}\label{sec:errors}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Time delay on discrete time feedback systems} \label{sec:delay}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+A common ocurrence in digital systems is that they do not necessarily
+satisfy the real-time specifications.  Delays due to processing time,
+communication lines, or other mechanisms will cause disturbances in the
+control loop.  In our model these delays are all deferred to the ZOH, i.e.,
+we presume that everything that happens in the digital world takes place at
+the sampling instance $t$ and the output of the result is delayed at the DAC
+when it is fed back into the real world.  We~will also presume that this
+delay is much smaller than the sampling time.
+
+\begin{theorem}
+The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modelled as a non-deterministic noise signal upperbound by 
+\begin{align}
+|\vec{y}_{k}-{\vec{y}_{t_d}}_{k}|_1 \leq q_t, \text{ where } q_t=&(|\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})|_1+|\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}|_1)|U|_\infty
+\end{align}
+where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$.
+\end{theorem}
+%
+\todo{notation $| |_x$ ?}
+%
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Errors generated by the numerical representation} 
+\label{sec:numeric_rep}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+The models we consider have two sources of error that are due to numerical  
+representation which we commonly refer to as the FWL effect.
+The first is the numerical error introduced by the
+fixed-point numbers employed to model the plant, i.e., to represent the
+plant dynamics $A_d$, $B_d$, $C_d$, $D_d$, $x_k$ and $y_k$.
+The second is the quantization error
+introduced by the digital controller, which performs operations on
+fixed-point numbers.  In this section we outline the notation for the
+representation of numbers, and briefly describe the errors
+introduced.  A~formal discussion is in
+Appendix~\ref{sec:numeric_rep}.
+
+Let $\mathbb{R}_{\langle M,F \rangle}$ be a fixed point domain with $M$ bits
+representing the binary word length of the representation and $F$ bits
+representing the prescaling $2^{-F}$ (\emph{i.e} the number of bits after
+the decimal place).  We note that a negative $F$ denotes an integer
+multiplication that adds $-F$ trailing zeros in the number represented by
+$M$.
+%Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point
+%domain with $M$ bits mantissa and $E$ bits exponent.  This domain
+%corresponds to $$\mathbb{R}_{\langle M,[E] \rangle} = \bigcup_F
+%\mathbb{R}_{\langle M,F \rangle} \mid F \in [2^{1-E}, 2^{E-1}]$$ This
+%definition important because it means that the distance between any two
+%numbers in the domain depends on the location of those numbers.  Since
+%a floating point domain is a union of a number of fixed
+%point domains, we will continue our reasoning on fixed point only, which
+%will apply to the floating point domain by extension.  Operations on these
+%numbers will incur errors that can be bound
+%by~\cite{DBLP:conf/arith/BrainTRW15}.
+
+We will use the domain $\mathbb{R}_{\langle C \rangle} \mid \langle C \rangle = \langle M_c,F_c \rangle$
+to represent the fixed point precision of the controller, and 
+$\mathbb{R}_{\langle P \rangle} \supseteq \mathbb{R}_{\langle C \rangle}$
+to represent the domain of the plant model.
+Thus, any mathematical operations in our modelled digital controller will be executed in the
+domain $\mathbb{R}_{\langle C \rangle}$, and all other calculations
+in our model will be carried out in the domain $\mathbb{R}_{\langle P \rangle}$.
+Given ${\langle M,F \rangle}$ we use $\mathcal{F}_{\langle M,F \rangle} : \mathbb{R} \rightarrow \mathbb{R}_{\langle M,F \rangle}$ as the truncation function.
+
+%% The physical plant operates in the reals, which means
+%% our verification phase must also account for the numerical error caused by representing the
+%% physical plant at the finite precision $\mathbb{R}_{\langle P \rangle}$.
+
+%% We will use these subindices to represent functions, number, vectors and matrices in their
+%% corresponding domains.
+
+%\todo{unclear}
+%We further note that by choosing $\langle C \rangle = \langle M_c,[E_c] \rangle$
+%we extend the following to floating point reasoning.
+
+%% \subsubsection{Effect on safety specification and stability}
+
+%% Let us first consider the effect of the quantization errors on safety. 
+%% Within the controller, state values are manipulated at low precision,
+%% alongside the vector multiplication $Kx$.
+%% %
+%% %computed considering the error introduced by the digital controller caused by performing the vector multiplication $Kx$ at low digital precision.
+%% The inputs are computed using the following equation: 
+%% %
+%% \begin{align*}
+%% u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})). 
+%% \end{align*}
+
+%% This induces two types of the errors detailed above: first, the truncation
+%% error due to representing $x_k$ as $\mathcal{F}{\langle I_c,F_c
+%% \rangle}(x_{k})$; and second, the rounding error introduced by the
+%% multiplication operation.  We represent these errors as non-deterministic
+%% additive noise.%, which might de-stabilize the closed-loop model.
+
+%% An additional error is due to the representation of the plant dynamics, namely 
+%% %
+%% \begin{align*}
+%% x_{k+1} &=\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
+%% \end{align*}
+%% We address this error by use of interval
+%% arithmetic~\cite{moore1966interval} in the verification phase.
+
+%% Previous studies~\cite{gangli1} show that the FWL affects the poles and
+%% zeros positions, degrading the closed-loop dynamics, causing steady-state
+%% errors (see Appendix~\ref{sec:appendix:LTIbackground} for details) and
+%% eventually de-stabilizing the system~\cite{Bessa16}.  However, since in this
+%% paper we require stability only as a precursor to safety, it is sufficient
+%% to check that the (perturbed, noisy) model converges to a neighborhood of
+%% the equilibrium within the safe set (see Appendix~\ref{sec:stab_FWL}).
+
+%% In the following, we shall disregard these steady-state errors (caused by
+%% FWL effects) when stability is ensured by synthesis, and then verify its
+%% safety accounting for the finite-precision errors.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsubsection{Quantization errors} \label{sec:quantization}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Let us first consider the effect of the quantization errors. 
+Within the controller, state values are manipulated at low precision.
+%alongside the vector multiplication $\mat{K}\vec{x}$.
+Furthermore, the quantizers for the DAC and the ADC introduce truncation errors
+which we denote by the effect of the functions $\mathcal{F}_{\langle D \rangle}$
+and $\mathcal{F}_{\langle A \rangle}$, respectively. Finally, let us call $\vec{\nu}_e$ the
+error caused by the FWL effects on the observer
+\todo{the observer was not defined..}
+(\emph{i.e} the numerical errors 
+in the calculations as opposed to the estimation error).
+The inputs are computed using the following equation: 
+%
+\begin{align}
+u_{k}&=\mathcal{F}_{\langle D \rangle}\left(-\mat{K}_{\langle C \rangle}\cdot\left(\mathcal{F}_{\langle C \rangle}\left(\mathcal{F}_{\langle A \rangle}(\vec{x}_{k})\right)\right) +\vec{\nu}_e\right)
+\label{eq:uk}
+\end{align}
+
+This induces two types of the errors: first, the truncation
+error due to the domain transformations $\mathcal{F}_{\langle *
+\rangle}(\cdot)$; and second, the rounding error introduced by the
+multiplication operation.  We represent these errors as non-deterministic
+additive noise. More details can be found in Appendix~\ref{appendix:quantization}.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsubsection{Modelling errors}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Errors incurred by the use of numerical algorithms during synthesis are not
+accounted for but rather checked during the verification phase.  If the
+counterexample provided corresponds to a pre-existing one, the synthesiser
+then increases its precision to reduce this error.
+
+Previous studies~\cite{gangli1} show that the FWL affects the poles and
+zeros positions, degrading the closed-loop dynamics, causing steady-state
+errors and eventually de-stabilizing the system~\cite{Bessa16}.  However,
+since the verifier also checks for the stability of the dynamics as a
+precursor to safety, this case is handled inside the loop.  In the
+following, we shall disregard these steady-state errors (caused by FWL
+effects) when stability is ensured by synthesis, and then verify its safety
+accounting for the finite-precision errors.
+
+%-------------------------------
+\section{Specification of control systems properties} 
+\label{sec:specification}
+%-------------------------------
+\todo{all this section needs to be merged with the next one and only
+discussed for an observed model.}
+
+%-------------------------------
+\subsection{Stability} 
+\label{ssec:stabspecification}
+%-------------------------------
+
+In this work we are interested in asymptotic stability: asymptotic
+stability is a property that amounts to convergence of the model
+executions to an equilibrium point, starting from any states in a
+neighborhood of the point.
+
+%% There are a number of algorithms that can be
+%% used for stability analysis~\cite{daes20161,Bessa16}.
+
+A discrete-time LTI system is
+asymptotically stable if all the roots of its characteristic
+polynomial (i.e., the eigenvalues of the closed-loop matrix $A_d - B_d
+K$) are inside the unity circle of the complex plane, i.e., their
+absolute values are strictly less than one~\cite{astrom1997computer}
+(this simple sufficient condition can be generalised, however this is
+not necessary in our work).  In this paper, we express this stability
+specification $\phi_\mathit{stability}$ in terms of a check known as
+\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic
+formula to select the entries of matrix $K$ so that the closed-loop
+dynamics are shaped as desired.
+
+%-------------------------------
+\subsection{Safety} 
+\label{ssec:safespecification}
+%-------------------------------
+
+We are not limited to the synthesis of digital stabilizing controllers -- a
+well known task in the literature on digital control systems -- but target
+safety requirements with an overall approach that is sound and automated. 
+More specifically, we require that the closed-loop system meets given safety
+specifications.  A safety specification gives raise to a requirement on the
+states of the model, such that the feedback controller (namely the choice of
+the gains matrix~$K$) must ensure that the state never violates the
+requirement.  Note that a stable, closed-loop system is not necessarily a
+safe system: indeed, the state values may leave the safe part of the state
+space while they converge to the equilibrium, which is typical in the case
+of oscillatory dynamics.  In~this work, the safety property is expressed as:
+%
+\begin{align}
+\phi_\mathit{safety}\equiv& \underline{y} \leq y_k \leq \overline{y}
+\iff \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
+\label{eq:safetyspec}
+\end{align}
+
+where $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
+
+Furthermore, we also need to consider the 
+constraints 
+\begin{align}
+\phi_\mathit{input}\equiv \underline{u} \leq u_k \leq \overline{u}
+\label{eq:inputspec}
+\end{align}
+which comes from physical restrictions in the energy of the system, and
+\begin{align}
+\phi_\mathit{init}\equiv \mat{G}' \vec{x}_0 \leq \vec{h}'
+\label{eq:initspec}
+\end{align}
+
+%-------------------------------
+\subsection{Transient response} 
+\label{ssec:transientspecification}
+%-------------------------------
+In many cases the speed of the response, i.e. how fast it converges to the set point, is a requirement of great importance. 
+This is given as a settling time for the system to become stable.
+
+\begin{theorem}
+Given a set of eigenvalues for a discrete time model of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1\ n]$, the settling time of the system is upperbounded by
+\begin{equation}
+t_s<-log_{\overline{\lambda}}({p_s}) : \overline{\lambda} = \max(|\lambda_i|) \wedge \overline{\lambda}<1,\ \forall i \in [1\ n]
+\label{eq:set_time}
+\end{equation}
+where $0\leq p_s \leq 1$ is the desired percentage of the target within which the output must remain after $t_s$.
+\end{theorem}
+%\begin{proof}
+%In a SISO system, there are two values that typically define the
+%response-time of the system (using a step response).
+%%
+%\begin{enumerate}
+%\item The \emph{rise time} is defined as the time it takes the output to reach a percentage (eg $90\%$) of the target value given a step chnage in the input.
+%\item The \emph{settling time} is defined as the time it takes the output to stabilize within a margin of the target value (eg $10\%$).
+%\end{enumerate} 
+%%
+%In the case of first and second order systems, the decay is governed by the equations 
+%%
+%\begin{align*}
+%&y_{decay}=
+%&\left\{
+%\begin{array}{cc}
+%e^{-|\omega| t}& 1^{st} order\\
+%e^{\zeta |\omega| t}\left(\frac{\sin\left(|\omega| t\sqrt{1-\zeta^2}+\sin^{-1}\sqrt{1-\zeta^2}\right)}{\sqrt{1-\zeta^2}} \right)&\zeta<1\\
+%e^{-|\omega| t}-|\omega| t e^{-|\omega| t}&\zeta=1\\
+%\frac{|\omega| e^{-|\omega_2| t}-|\omega_2| e^{-|\omega| t}}{|\omega|-|\omega_2|}&\zeta>1\end{array}\right.
+%\end{align*}
+%where $|\omega|$ and $|\omega_2|$ are the magnitudes of the eigenvalues (roots) of the system and  $\zeta=-\cos(\theta)$ where $\theta$ is the polar angle of the conjugate pair if it exists ($\zeta \geq 1$ if it doesn't).
+%These equations become increasingly complicated for higher order systems.
+However, we note their strong dependency on the magnitude of the eigenvalues, and use this property to define an upperbound on the decay function.
+%All of the above equations will decay faster than $e^{-|\omega| t}$ given $|\omega| < |\omega_2|$, hence we may use this function as our upper bound.
+%
+%Given a closed loop single output LTI system of order $n$ with dynamics
+%\begin{equation}
+%\left\{\begin{array}{c}\vec{x}_k=\mat{A}\vec{x}_{k-1}\\ \vec{y}_k=\mat{C}\vec{x}_k\end{array}\right.
+\Rightarrow \left\{ \begin{array}{c}\vec{x}_k'=\mat{J}\vec{x}_{k-1}'\\ \vec{y}_k=\mat{C}\mat{S}\vec{x}_k'\end{array}\right.
+: \left\{ \begin{array}{c}\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \\ \vec{x}_k'=\mat{S}^{-1}\vec{x}_k\end{array}\right.
+%\label{eq:eigendynamics}
+%\end{equation}
+%%
+%the output decay is a linear combination of the decay of eigenvalues or
+%eigenvalue pairs.  Let $\mat{C}'\in \mathbb{R}^{1 \times n}=\mat{C}\mat{S}$. 
+%Since $\mat{C}'$ is constant, the output $y_k$ is a linear combination of
+%the states $\vec{x}'_k$.  We accelerate equation \eqref{eq:eigendynamics} to
+%obtain
+%%
+%\begin{align}
+%%\vec{x}_k'&=\mat{J}^k\vec{x}_0' \\
+%y_k&=\mat{C}'\mat{J}^k\vec{x}_0 = \sum_{i=0}^p \left( c_i \lambda_i^k + c_{il}\binom{k}{l} \lambda_i^{k-l}\right)\\
+%|y_k|&\leq \sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right||\lambda_i^k|
+%\end{align}
+%%
+%where the second  part of the equation corresponds to the upper diagonal
+%terms of the Jordan blocks.  We also have $|\lambda_i^k|\leq
+%|\overline{\omega}^k|$,hence
+%%
+%\begin{align}
+%|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right|
+%\end{align}
+%%
+%Since we are synthesising the eigenvalues, rather than solve this formula
+%for complex Jordan Shapes, we will restrict our synthesiser to provide
+%solutions with distinct eigenvalues (which is by far the most common case). 
+%Therefore the right hand terms dissappear and we obtain
+%%
+%\begin{align}
+%|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n |c_i|
+%\end{align}
+%
+%Hence the overall decay of the system is always smaller
+%than $d=e^{-|\overline{\omega}| t}$ where $0\leq d\leq 1$ is the remaining
+%percentage of the decay expressed.  Reversing we have
+%$t=-\frac{ln(d)}{|\overline{\omega}|}=-\frac{ln(d)}{ln(\overline{\lambda})}$. 
+%replacing for $p_s$ , $t_s$, and $\overline{\lambda}$ we get equation
+%\eqref{eq:set_time}
+%%
+%\qed
+%\end{proof}
+%
+We may now use this limit to express a constraint in terms of the
+coefficients for our synthesis process.  Let
+%
+\begin{equation}
+P=\prod_{i=0}^p (s-\lambda_i)=\sum_{j=0}^p c_js^j.
+\end{equation}
+%
+We use Jury's criterion to limit $|\lambda_i| \leq 1$.  Let us now define a
+transformation $\lambda_i'=\frac{\lambda_i}{\overline{\lambda}}$.  We want
+to ensure $\lambda_i' \leq 1$ which can be done by applying Jury's criterion
+to $P'=\prod_{i=0}^p (s-\lambda_i')=\sum_{j=0}^p c_j's^j$ where $c_j'$ are
+unknown.  However, if we replace for $\lambda_i$, we obtain
+%
+\begin{equation}
+P'=\prod_{i=0}^p (s-\lambda_i')=\prod_{i=0}^p \left(s-\frac{\lambda_i}{\overline{\lambda}}\right)=\sum_{j=0}^p \frac{c_j}{\overline{\lambda}^{p-j}}s^j
+\end{equation}
+%
+where all members are known, we may now synthesise coefficients that ensure
+the eigenvalues are smaller than a desired magnitude, thus ensuring that the
+settling time is too.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{Verification of a Controllable Observed System}\label{sec:cof_verification}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\todo{the observer dynamics?}
+
+In most real implementations, the internal state of a plant cannot be
+directly measured but rather inferred from its
+effect on the output. A plant model that minimises the difference
+between the outputs is called an observer and it is a well known
+paradigm in the control literature~\cite{astrom1997computer}. Since we
+are interested in synthesising controllers with observer designs, in this
+section we will look at checking stability and safety in the presence of an observer.
+
+%the challenges presented by the introduction of the observer.
 

### 2017-10-17 TACAS2018/paper.tex
sec 5 edit

@@
 %-------------------------------
-\subsection{State-space representation of physical systems}
+\subsection{State-space representation of LTI models}
 \label{sec:ssrepresentation}
@@
 %% as introduced by the ADC/DAC conversion blocks (Fig.~\ref{fig:digitalsystem}).
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Semantics of LTI models}\label{sec:model_semantics}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%
+The traces of the model starting from an initial set $X_0\subseteq \mathbb{R}^p$, 
+with inputs restricted to $U \subseteq \mathbb{R}^q$, are sequences 
+$ \vec{x}_0 \xrightarrow{\vec{u}_0} \vec{x}_1 \xrightarrow{\vec{u}_1} \vec{x}_2 \xrightarrow{\vec{u}_2} \ldots $, 
+%
+where $ \vec{x}_0 \in X_0$ and $\forall k\geq 0, \vec{u}_k \in U \text{ and } \vec{x}_{k+1} = \tau(\vec{x}_k,\vec{u}_k) $, 
+where 
+%
+\begin{equation}\label{equ:reachtraj}
+\tau(\vec{x}_k,\vec{u}_k) = 
+\big( \mat{A}\vec{x}_k +
+\mat{B}\vec{u}_k \mid \mat{G}\vec{x}_k \leq \vec{h}\big)\;. 
+\end{equation}
+%
+where $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
+%
+We extend the notation above to convex sets of initial conditions and inputs ($X_0$ and $U$), 
+and write $\tau(X_0,U)$ to denote the set of states $\{\vec{x} \mid \vec{x}_0 \in
+X_0 \wedge \vec{u} \in U \wedge \vec{x} = \tau(\vec{x}_0,\vec{u})\}$
+reached from $X_0$ by $\tau$ in one step. 
+%
+We furthermore write $\tau^n(X_0,U)$ to denote the set of states reached from
+$X_0$ via $\tau$ in $n$ steps (\emph{$n$-reach set}), i.e.\ for $n\geq 1$
+%
+\begin{align}\label{equ:reachset}
+\tau^n(X_0,U) = \{\vec{x}_n \mid &\vec{x}_0 \in X_0 \wedge \forall k\in [0,n-1]\nonumber\\ 
+ &\vec{u}_{k} \in U \wedge \vec{x}_{k+1}=\tau(\vec{x}_{k},\vec{u}_{k}) \} \;. 
+\end{align}
+%
+Since the transformations $\mat{A}$ and $\mat{B}$ are linear and
+vector sums preserve convexity, the sets $X_n = \tau^n(X_0,U)$ are also
+convex.
+
+We define the \emph{$n$-reach tube} 
+\begin{equation}\label{equ:reachtube}
+\hat{X}_n=\hat{\tau}^n(X_0,U)=\bigcup_{k\in[0,n]} \tau^k(X_0,U)
+\end{equation}
+as the union of the reachable sets over $n$ iterations.
+%
+Moreover, $\hat{X} 
+=\bigcup_{n\geq 0} \tau^n(X_0,U)$ 
+extends the previous notion over an 
+unbounded time horizon.
 
@@
 
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Semantics of LTI models}\label{sec:model_semantics}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%
-The traces of the model starting from an initial set $X_0\subseteq \mathbb{R}^p$, 
-with inputs restricted to $U \subseteq \mathbb{R}^q$, are sequences 
-$ \vec{x}_0 \xrightarrow{\vec{u}_0} \vec{x}_1 \xrightarrow{\vec{u}_1} \vec{x}_2 \xrightarrow{\vec{u}_2} \ldots $, 
-%
-where $ \vec{x}_0 \in X_0$ and $\forall k\geq 0, \vec{u}_k \in U \text{ and } \vec{x}_{k+1} = \tau(\vec{x}_k,\vec{u}_k) $, 
-where 
-%
-\begin{equation}\label{equ:reachtraj}
-\tau(\vec{x}_k,\vec{u}_k) = 
-\big( \mat{A}\vec{x}_k +
-\mat{B}\vec{u}_k \mid \mat{G}\vec{x}_k \leq \vec{h}\big)\;. 
-\end{equation}
-%
-where $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
-%
-We extend the notation above to convex sets of initial conditions and inputs ($X_0$ and $U$), 
-and write $\tau(X_0,U)$ to denote the set of states $\{\vec{x} \mid \vec{x}_0 \in
-X_0 \wedge \vec{u} \in U \wedge \vec{x} = \tau(\vec{x}_0,\vec{u})\}$
-reached from $X_0$ by $\tau$ in one step. 
-%
-We furthermore write $\tau^n(X_0,U)$ to denote the set of states reached from
-$X_0$ via $\tau$ in $n$ steps (\emph{$n$-reach set}), i.e.\ for $n\geq 1$
-%
-\begin{align}\label{equ:reachset}
-\tau^n(X_0,U) = \{\vec{x}_n \mid &\vec{x}_0 \in X_0 \wedge \forall k\in [0,n-1]\nonumber\\ 
- &\vec{u}_{k} \in U \wedge \vec{x}_{k+1}=\tau(\vec{x}_{k},\vec{u}_{k}) \} \;. 
-\end{align}
-%
-Since the transformations $\mat{A}$ and $\mat{B}$ are linear and
-vector sums preserve convexity, the sets $X_n = \tau^n(X_0,U)$ are also
-convex.
-
-We define the \emph{$n$-reach tube} 
-\begin{equation}\label{equ:reachtube}
-\hat{X}_n=\hat{\tau}^n(X_0,U)=\bigcup_{k\in[0,n]} \tau^k(X_0,U)
-\end{equation}
-as the union of the reachable sets over $n$ iterations.
-%
-Moreover, $\hat{X} 
-=\bigcup_{n\geq 0} \tau^n(X_0,U)$ 
-extends the previous notion over an 
-unbounded time horizon.
+ Our goal in this work is to synthesise both $\mat{K}$ and $\mat{L}$.
 
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
  Note that the discretization in Sec.~\ref{sec:ssrepresentation} only 
- allows us to observe the system at integer multiples of the sample time.
- As we are interested in ensuring that certain properties of the system hold at any given
- time (not just integer multiples of the sample time),
- we accelerate the dynamics of the system (according to the model semantics in Sec.~\ref{sec:model_semantics}) in order to compute the state $\vec{x}_T$  at a given time $T$.
+ allows us to evaluate the state of the system at integer multiples of the sample time.
+ However, in order to synthesise $\mat{K}$ and $\mat{L}$, 
+ we must be able to ensure that certain properties of the system hold at any given
+ time (not just integer multiples of the sample time).
+ Consequently, we accelerate the dynamics of the system (according to the model semantics in Sec.~\ref{sec:model_semantics}) in order to compute the state $\vec{x}_T$  at a given time $T$.
 
@@
  %
-\todo{Can the corallary be motivated? The general motivation of the section was observing the system at times that are not necessarily integer multiple of the sampling time...} 
  \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}_0 : k \in \mathbb{R}^+$ is a witness of the system at time $t=kT_d$.
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_r=A_d^r\vec{x}_0 : r \in \mathbb{R}^+$ is a witness of the system at time $t=rT_d$.
  \end{corollary}
+%
  % \begin{proof}
@@
  \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}_0+(\mat{I}-\mat{A}_d^k\mat{B}\vec{u}) : k \in \mathbb{R}^+$ is a witness of the system at time $kT_d$.
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then $\vec{x}_r=A_d^r\vec{x}_0+(\mat{I}-\mat{A}_d^r\mat{B}\vec{u}) : r \in \mathbb{R}^+$ is a witness of the system at time $rT_d$.
  \end{corollary}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\todo{the observer dynamics?}
-
-In most real implementations, the internal state of a plant cannot be
-directly measured but rather inferred from its
-effect on the output. A plant model that minimises the difference
-between the outputs is called an observer and it is a well known
-paradigm in the control literature~\cite{astrom1997computer}. Since we
-are interested in synthesising controllers with observer designs, in this
-section we will look at checking stability and safety in the presence of an observer.
+%% In most real implementations, the internal state of a plant cannot be
+%% directly measured but rather inferred from its
+%% effect on the output. A plant model that minimises the difference
+%% between the outputs is called an observer and it is a well known
+%% paradigm in the control literature~\cite{astrom1997computer}.
+
+Since we are interested in synthesising controllers with observer
+designs, in this section we will look at checking stability and safety
+in the presence of an observer.
 

### 2017-10-17 TACAS2018/paper.tex
edits sec 6

@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Error modelling and soundness}\label{sec:errors}
+\section{Error modelling}\label{sec:errors}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 
-%-------------------------------
-\section{Specification of control systems properties} 
-\label{sec:specification}
-%-------------------------------
-\todo{all this section needs to be merged with the next one and only
-discussed for an observed model.}
-
-%-------------------------------
-\subsection{Stability} 
-\label{ssec:stabspecification}
-%-------------------------------
-
+%% %-------------------------------
+%% \section{Specification of control systems properties} 
+%% \label{sec:specification}
+%% %-------------------------------
+
+%% %-------------------------------
+%% \subsection{Stability} 
+%% \label{ssec:stabspecification}
+%% %-------------------------------
+
+%% %-------------------------------
+%% \subsection{Safety} 
+%% \label{ssec:safespecification}
+%% %-------------------------------
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{Properties of a controllable observed system}\label{sec:cof_verification}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%% In most real implementations, the internal state of a plant cannot be
+%% directly measured but rather inferred from its
+%% effect on the output. A plant model that minimises the difference
+%% between the outputs is called an observer and it is a well known
+%% paradigm in the control literature~\cite{astrom1997computer}.
+
+Since we are interested in synthesising controllers with observer
+designs, in this section we will look at checking stability, safety
+and the response time in the presence of an observer.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Stability of an observed system}\label{sec:cof_stability}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 In this work we are interested in asymptotic stability: asymptotic
@@
 
-%-------------------------------
-\subsection{Safety} 
-\label{ssec:safespecification}
-%-------------------------------
-
-We are not limited to the synthesis of digital stabilizing controllers -- a
-well known task in the literature on digital control systems -- but target
-safety requirements with an overall approach that is sound and automated. 
-More specifically, we require that the closed-loop system meets given safety
-specifications.  A safety specification gives raise to a requirement on the
-states of the model, such that the feedback controller (namely the choice of
-the gains matrix~$K$) must ensure that the state never violates the
-requirement.  Note that a stable, closed-loop system is not necessarily a
-safe system: indeed, the state values may leave the safe part of the state
-space while they converge to the equilibrium, which is typical in the case
-of oscillatory dynamics.  In~this work, the safety property is expressed as:
-%
-\begin{align}
-\phi_\mathit{safety}\equiv& \underline{y} \leq y_k \leq \overline{y}
-\iff \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
-\label{eq:safetyspec}
-\end{align}
-
-where $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
-
-Furthermore, we also need to consider the 
-constraints 
-\begin{align}
-\phi_\mathit{input}\equiv \underline{u} \leq u_k \leq \overline{u}
-\label{eq:inputspec}
-\end{align}
-which comes from physical restrictions in the energy of the system, and
-\begin{align}
-\phi_\mathit{init}\equiv \mat{G}' \vec{x}_0 \leq \vec{h}'
-\label{eq:initspec}
-\end{align}
-
-%-------------------------------
-\subsection{Transient response} 
-\label{ssec:transientspecification}
-%-------------------------------
-In many cases the speed of the response, i.e. how fast it converges to the set point, is a requirement of great importance. 
-This is given as a settling time for the system to become stable.
-
-\begin{theorem}
-Given a set of eigenvalues for a discrete time model of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1\ n]$, the settling time of the system is upperbounded by
-\begin{equation}
-t_s<-log_{\overline{\lambda}}({p_s}) : \overline{\lambda} = \max(|\lambda_i|) \wedge \overline{\lambda}<1,\ \forall i \in [1\ n]
-\label{eq:set_time}
-\end{equation}
-where $0\leq p_s \leq 1$ is the desired percentage of the target within which the output must remain after $t_s$.
-\end{theorem}
-%\begin{proof}
-%In a SISO system, there are two values that typically define the
-%response-time of the system (using a step response).
-%%
-%\begin{enumerate}
-%\item The \emph{rise time} is defined as the time it takes the output to reach a percentage (eg $90\%$) of the target value given a step chnage in the input.
-%\item The \emph{settling time} is defined as the time it takes the output to stabilize within a margin of the target value (eg $10\%$).
-%\end{enumerate} 
-%%
-%In the case of first and second order systems, the decay is governed by the equations 
-%%
-%\begin{align*}
-%&y_{decay}=
-%&\left\{
-%\begin{array}{cc}
-%e^{-|\omega| t}& 1^{st} order\\
-%e^{\zeta |\omega| t}\left(\frac{\sin\left(|\omega| t\sqrt{1-\zeta^2}+\sin^{-1}\sqrt{1-\zeta^2}\right)}{\sqrt{1-\zeta^2}} \right)&\zeta<1\\
-%e^{-|\omega| t}-|\omega| t e^{-|\omega| t}&\zeta=1\\
-%\frac{|\omega| e^{-|\omega_2| t}-|\omega_2| e^{-|\omega| t}}{|\omega|-|\omega_2|}&\zeta>1\end{array}\right.
-%\end{align*}
-%where $|\omega|$ and $|\omega_2|$ are the magnitudes of the eigenvalues (roots) of the system and  $\zeta=-\cos(\theta)$ where $\theta$ is the polar angle of the conjugate pair if it exists ($\zeta \geq 1$ if it doesn't).
-%These equations become increasingly complicated for higher order systems.
-However, we note their strong dependency on the magnitude of the eigenvalues, and use this property to define an upperbound on the decay function.
-%All of the above equations will decay faster than $e^{-|\omega| t}$ given $|\omega| < |\omega_2|$, hence we may use this function as our upper bound.
-%
-%Given a closed loop single output LTI system of order $n$ with dynamics
-%\begin{equation}
-%\left\{\begin{array}{c}\vec{x}_k=\mat{A}\vec{x}_{k-1}\\ \vec{y}_k=\mat{C}\vec{x}_k\end{array}\right.
-\Rightarrow \left\{ \begin{array}{c}\vec{x}_k'=\mat{J}\vec{x}_{k-1}'\\ \vec{y}_k=\mat{C}\mat{S}\vec{x}_k'\end{array}\right.
-: \left\{ \begin{array}{c}\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \\ \vec{x}_k'=\mat{S}^{-1}\vec{x}_k\end{array}\right.
-%\label{eq:eigendynamics}
-%\end{equation}
-%%
-%the output decay is a linear combination of the decay of eigenvalues or
-%eigenvalue pairs.  Let $\mat{C}'\in \mathbb{R}^{1 \times n}=\mat{C}\mat{S}$. 
-%Since $\mat{C}'$ is constant, the output $y_k$ is a linear combination of
-%the states $\vec{x}'_k$.  We accelerate equation \eqref{eq:eigendynamics} to
-%obtain
-%%
-%\begin{align}
-%%\vec{x}_k'&=\mat{J}^k\vec{x}_0' \\
-%y_k&=\mat{C}'\mat{J}^k\vec{x}_0 = \sum_{i=0}^p \left( c_i \lambda_i^k + c_{il}\binom{k}{l} \lambda_i^{k-l}\right)\\
-%|y_k|&\leq \sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right||\lambda_i^k|
-%\end{align}
-%%
-%where the second  part of the equation corresponds to the upper diagonal
-%terms of the Jordan blocks.  We also have $|\lambda_i^k|\leq
-%|\overline{\omega}^k|$,hence
-%%
-%\begin{align}
-%|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right|
-%\end{align}
-%%
-%Since we are synthesising the eigenvalues, rather than solve this formula
-%for complex Jordan Shapes, we will restrict our synthesiser to provide
-%solutions with distinct eigenvalues (which is by far the most common case). 
-%Therefore the right hand terms dissappear and we obtain
-%%
-%\begin{align}
-%|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n |c_i|
-%\end{align}
-%
-%Hence the overall decay of the system is always smaller
-%than $d=e^{-|\overline{\omega}| t}$ where $0\leq d\leq 1$ is the remaining
-%percentage of the decay expressed.  Reversing we have
-%$t=-\frac{ln(d)}{|\overline{\omega}|}=-\frac{ln(d)}{ln(\overline{\lambda})}$. 
-%replacing for $p_s$ , $t_s$, and $\overline{\lambda}$ we get equation
-%\eqref{eq:set_time}
-%%
-%\qed
-%\end{proof}
-%
-We may now use this limit to express a constraint in terms of the
-coefficients for our synthesis process.  Let
-%
-\begin{equation}
-P=\prod_{i=0}^p (s-\lambda_i)=\sum_{j=0}^p c_js^j.
-\end{equation}
-%
-We use Jury's criterion to limit $|\lambda_i| \leq 1$.  Let us now define a
-transformation $\lambda_i'=\frac{\lambda_i}{\overline{\lambda}}$.  We want
-to ensure $\lambda_i' \leq 1$ which can be done by applying Jury's criterion
-to $P'=\prod_{i=0}^p (s-\lambda_i')=\sum_{j=0}^p c_j's^j$ where $c_j'$ are
-unknown.  However, if we replace for $\lambda_i$, we obtain
-%
-\begin{equation}
-P'=\prod_{i=0}^p (s-\lambda_i')=\prod_{i=0}^p \left(s-\frac{\lambda_i}{\overline{\lambda}}\right)=\sum_{j=0}^p \frac{c_j}{\overline{\lambda}^{p-j}}s^j
-\end{equation}
-%
-where all members are known, we may now synthesise coefficients that ensure
-the eigenvalues are smaller than a desired magnitude, thus ensuring that the
-settling time is too.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Verification of a Controllable Observed System}\label{sec:cof_verification}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%% In most real implementations, the internal state of a plant cannot be
-%% directly measured but rather inferred from its
-%% effect on the output. A plant model that minimises the difference
-%% between the outputs is called an observer and it is a well known
-%% paradigm in the control literature~\cite{astrom1997computer}.
-
-Since we are interested in synthesising controllers with observer
-designs, in this section we will look at checking stability and safety
-in the presence of an observer.
-
-%the challenges presented by the introduction of the observer.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Stability of an Observed System}\label{sec:cof_stability}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally ${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$ and ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d$ for a given time discretization.
@@
 
-As stated in Section~\ref{ssec:stabspecification}, we use Jury's Criterion on these polynomials
+As stated in Section~\ref{sec:cof_stability}, we use Jury's Criterion on these polynomials
 to assert the stability specification.
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Stability of an Observed System with FWL effects}\label{sec:cof_fwl_stability}
+\subsection{Stability of an observed system with FWL effects}\label{sec:cof_fwl_stability}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Safety of a Digitally Observed System}\label{sec:cof_safety}
+\subsection{Safety of a digitally observed system}\label{sec:cof_safety}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \todo{FWL effects here? they are implicit from equation \ref{eq:observer_LTI_FWL_cf}}
+
+We are not limited to the synthesis of digital stabilizing controllers -- a
+well known task in the literature on digital control systems -- but target
+safety requirements with an overall approach that is sound and automated. 
+More specifically, we require that the closed-loop system meets given safety
+specifications.  A safety specification gives raise to a requirement on the
+states of the model, such that the feedback controller (namely the choice of
+the gains matrix~$K$) must ensure that the state never violates the
+requirement.  Note that a stable, closed-loop system is not necessarily a
+safe system: indeed, the state values may leave the safe part of the state
+space while they converge to the equilibrium, which is typical in the case
+of oscillatory dynamics.  In~this work, the safety property is expressed as:
+%
+\begin{align}
+\phi_\mathit{safety}\equiv& \underline{y} \leq y_k \leq \overline{y}
+\iff \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
+\label{eq:safetyspec}
+\end{align}
+
+where $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
+
+Furthermore, we also need to consider the 
+constraints 
+\begin{align}
+\phi_\mathit{input}\equiv \underline{u} \leq u_k \leq \overline{u}
+\label{eq:inputspec}
+\end{align}
+which comes from physical restrictions in the energy of the system, and
+\begin{align}
+\phi_\mathit{init}\equiv \mat{G}' \vec{x}_0 \leq \vec{h}'
+\label{eq:initspec}
+\end{align}
+
+%==========
 
@@
 For efficiency purposes, the inequality in \eqref{eq:of_bounds} is transformed into reachable form using $\mat{T}_c, \mat{T}_o$ which reduces the complexity from $\mathcal{O}(p^2)$ to $\mathcal{O}(p)$.
+
+%-------------------------------
+\subsection{Transient response} 
+\label{ssec:transientspecification}
+%-------------------------------
+In many cases the speed of the response, i.e. how fast it converges to the set point, is a requirement of great importance. 
+This is given as a settling time for the system to become stable.
+
+\begin{theorem}
+Given a set of eigenvalues for a discrete time model of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1\ n]$, the settling time of the system is upperbounded by
+\begin{equation}
+t_s<-log_{\overline{\lambda}}({p_s}) : \overline{\lambda} = \max(|\lambda_i|) \wedge \overline{\lambda}<1,\ \forall i \in [1\ n]
+\label{eq:set_time}
+\end{equation}
+where $0\leq p_s \leq 1$ is the desired percentage of the target within which the output must remain after $t_s$.
+\end{theorem}
+%\begin{proof}
+%In a SISO system, there are two values that typically define the
+%response-time of the system (using a step response).
+%%
+%\begin{enumerate}
+%\item The \emph{rise time} is defined as the time it takes the output to reach a percentage (eg $90\%$) of the target value given a step chnage in the input.
+%\item The \emph{settling time} is defined as the time it takes the output to stabilize within a margin of the target value (eg $10\%$).
+%\end{enumerate} 
+%%
+%In the case of first and second order systems, the decay is governed by the equations 
+%%
+%\begin{align*}
+%&y_{decay}=
+%&\left\{
+%\begin{array}{cc}
+%e^{-|\omega| t}& 1^{st} order\\
+%e^{\zeta |\omega| t}\left(\frac{\sin\left(|\omega| t\sqrt{1-\zeta^2}+\sin^{-1}\sqrt{1-\zeta^2}\right)}{\sqrt{1-\zeta^2}} \right)&\zeta<1\\
+%e^{-|\omega| t}-|\omega| t e^{-|\omega| t}&\zeta=1\\
+%\frac{|\omega| e^{-|\omega_2| t}-|\omega_2| e^{-|\omega| t}}{|\omega|-|\omega_2|}&\zeta>1\end{array}\right.
+%\end{align*}
+%where $|\omega|$ and $|\omega_2|$ are the magnitudes of the eigenvalues (roots) of the system and  $\zeta=-\cos(\theta)$ where $\theta$ is the polar angle of the conjugate pair if it exists ($\zeta \geq 1$ if it doesn't).
+%These equations become increasingly complicated for higher order systems.
+However, we note their strong dependency on the magnitude of the eigenvalues, and use this property to define an upperbound on the decay function.
+%All of the above equations will decay faster than $e^{-|\omega| t}$ given $|\omega| < |\omega_2|$, hence we may use this function as our upper bound.
+%
+%Given a closed loop single output LTI system of order $n$ with dynamics
+%\begin{equation}
+%\left\{\begin{array}{c}\vec{x}_k=\mat{A}\vec{x}_{k-1}\\ \vec{y}_k=\mat{C}\vec{x}_k\end{array}\right.
+\Rightarrow \left\{ \begin{array}{c}\vec{x}_k'=\mat{J}\vec{x}_{k-1}'\\ \vec{y}_k=\mat{C}\mat{S}\vec{x}_k'\end{array}\right.
+: \left\{ \begin{array}{c}\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \\ \vec{x}_k'=\mat{S}^{-1}\vec{x}_k\end{array}\right.
+%\label{eq:eigendynamics}
+%\end{equation}
+%%
+%the output decay is a linear combination of the decay of eigenvalues or
+%eigenvalue pairs.  Let $\mat{C}'\in \mathbb{R}^{1 \times n}=\mat{C}\mat{S}$. 
+%Since $\mat{C}'$ is constant, the output $y_k$ is a linear combination of
+%the states $\vec{x}'_k$.  We accelerate equation \eqref{eq:eigendynamics} to
+%obtain
+%%
+%\begin{align}
+%%\vec{x}_k'&=\mat{J}^k\vec{x}_0' \\
+%y_k&=\mat{C}'\mat{J}^k\vec{x}_0 = \sum_{i=0}^p \left( c_i \lambda_i^k + c_{il}\binom{k}{l} \lambda_i^{k-l}\right)\\
+%|y_k|&\leq \sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right||\lambda_i^k|
+%\end{align}
+%%
+%where the second  part of the equation corresponds to the upper diagonal
+%terms of the Jordan blocks.  We also have $|\lambda_i^k|\leq
+%|\overline{\omega}^k|$,hence
+%%
+%\begin{align}
+%|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right|
+%\end{align}
+%%
+%Since we are synthesising the eigenvalues, rather than solve this formula
+%for complex Jordan Shapes, we will restrict our synthesiser to provide
+%solutions with distinct eigenvalues (which is by far the most common case). 
+%Therefore the right hand terms dissappear and we obtain
+%%
+%\begin{align}
+%|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n |c_i|
+%\end{align}
+%
+%Hence the overall decay of the system is always smaller
+%than $d=e^{-|\overline{\omega}| t}$ where $0\leq d\leq 1$ is the remaining
+%percentage of the decay expressed.  Reversing we have
+%$t=-\frac{ln(d)}{|\overline{\omega}|}=-\frac{ln(d)}{ln(\overline{\lambda})}$. 
+%replacing for $p_s$ , $t_s$, and $\overline{\lambda}$ we get equation
+%\eqref{eq:set_time}
+%%
+%\qed
+%\end{proof}
+%
+We may now use this limit to express a constraint in terms of the
+coefficients for our synthesis process.  Let
+%
+\begin{equation}
+P=\prod_{i=0}^p (s-\lambda_i)=\sum_{j=0}^p c_js^j.
+\end{equation}
+%
+We use Jury's criterion to limit $|\lambda_i| \leq 1$.  Let us now define a
+transformation $\lambda_i'=\frac{\lambda_i}{\overline{\lambda}}$.  We want
+to ensure $\lambda_i' \leq 1$ which can be done by applying Jury's criterion
+to $P'=\prod_{i=0}^p (s-\lambda_i')=\sum_{j=0}^p c_j's^j$ where $c_j'$ are
+unknown.  However, if we replace for $\lambda_i$, we obtain
+%
+\begin{equation}
+P'=\prod_{i=0}^p (s-\lambda_i')=\prod_{i=0}^p \left(s-\frac{\lambda_i}{\overline{\lambda}}\right)=\sum_{j=0}^p \frac{c_j}{\overline{\lambda}^{p-j}}s^j
+\end{equation}
+%
+where all members are known, we may now synthesise coefficients that ensure
+the eigenvalues are smaller than a desired magnitude, thus ensuring that the
+settling time is too.
 

### 2017-10-17 TACAS2018/paper.tex
Clarification

@@
 
-In order for the system to be in canonical form, we must however perform a transformation. The challenge however is that we want the state space dynamics in
-reachable form and the observer error dynamics in observable form. Let 
-\begin{equation}
-\left[\begin{array}{c}\vec{x}'\\ \vec{x}_e'\end{array}\right]=
-\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right] 
-\left[\begin{array}{c}\vec{x}\\ \vec{x}_e\end{array}\right]
-\end{equation}
-We can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
-\begin{align}
-\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
-=& \left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]
-\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
-+\mat{B}' \vec{r}_k
-+\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
-\nonumber\\
-\vec{y}_k
-=& \mat{C}_{t}\vec{x}_k% + \mat{D}_{d}\vec{u}_k
-\label{eq:observer_LTI_cf}
-\end{align}
-where
-{
-\setlength{\abovedisplayskip}{0pt}
-\setlength{\belowdisplayskip}{0pt}
-%\begin{align*}
-%
-%\mat{A}_{c}=&\left[
-%\begin{array}{ccccc}
-%0&1&0&\cdots&0\\
-%0&0&1&\cdots&0\\
-%\vdots&\vdots&\vdots&\ddots&\vdots\\
-%0&0&0&\cdots&1\\
-%k_n-a_n&\cdots&k_i-a_i&\cdots&k_1-a_1
-%\end{array}\right]
-%\label{eq:cf_SISO_2}
-%\end{align*}
+We want the state space dynamics in reachable form ($\mat{A}_c$) and the observer error dynamics in observable form ($\mat{A}_o$), i.e.
+with dynamics whose coefficients are represented solely by those of the characteristic polynomial as follows:
 \begin{align*}
@@
 \end{align*}
-}
-{\setlength{\belowdisplayskip}{0pt}
+where $\sum_{i=0}^p a_iz^i$ is the characteristic polynomial of the plant.
+This is achieved by the following transformation. Let
+\begin{equation}
+\left[\begin{array}{c}\vec{x}'\\ \vec{x}_e'\end{array}\right]=
+\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right] 
+\left[\begin{array}{c}\vec{x}\\ \vec{x}_e\end{array}\right]
+\end{equation}
+We can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
+\begin{align}
+\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
+=& \left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]
+\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
++\mat{B}' \vec{r}_k
++\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
+\nonumber\\
+\vec{y}_k
+=& \mat{C}_{t}\vec{x}_k% + \mat{D}_{d}\vec{u}_k
+\label{eq:observer_LTI_cf}
+\end{align}
+{%\setlength{\belowdisplayskip}{0pt}
 \begin{align*}

### 2017-10-17 TACAS2018/paper.tex
editing sec 6.1

--- 2017-10-17 TACAS2018/paper.tex
@@
 
-Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally ${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$ and ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d$ for a given time discretization.
-We will initially assume this for the description of the system and then introduce the errors caused  by misrepresentations.
-For simplicity of the description, we will agregate the noises as follows:
-\begin{align*}
-\eta_1&=\nu_1+\nu_1'+\nu_t\\
-\eta_2&=\nu_2+\nu_2'
-\end{align*}
+%Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally
+In this section we assume that
+${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$ and ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d$ for a given time discretization.
+%% We will initially assume this for the description of the system and then introduce the errors caused  by misrepresentations.
+For simplicity of the description, we agregate the noises as follows:
+$\eta_1=\nu_1+\nu_1'+\nu_t$ and $\eta_2=\nu_2+\nu_2'$,
 where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations.

### 2017-10-17 TACAS2018/paper.tex
sec 6.1

@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{State observer}
+\subsection{State observer}\label{sec:observer}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 executions to an equilibrium point, starting from any states in a
-neighborhood of the point.
+neighborhood of the point. In the rest of the paper we refer to the
+stability specification as $\phi_\mathit{stability}$.
 
@@
 
-A discrete-time LTI system is
-asymptotically stable if all the roots of its characteristic
+A discrete-time LTI system (as shown in Sec.~\ref{sec:ssrepresentation})
+is asymptotically stable if all the roots of its characteristic
 polynomial (i.e., the eigenvalues of the closed-loop matrix $A_d - B_d
@@
 (this simple sufficient condition can be generalised, however this is
-not necessary in our work).  In this paper, we express this stability
-specification $\phi_\mathit{stability}$ in terms of a check known as
+not necessary in our work).  We express the stability
+specification in terms of a check known as
 \emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic
-formula to select the entries of matrix $K$ so that the closed-loop
-dynamics are shaped as desired.
+formula over the coefficients of the characteristic polynomial.
+%% to select the entries of matrix $K$ so that the closed-loop
+%% dynamics are shaped as desired.
+
+In order to be able to apply Jury's criterion,
+in the rest of this section, we compute the  
+characteristic polynomial of the observer model.
+Note that in this section, we consider that the model is
+discretized in the time domain, but not in the value domain.
+This essentially means that
+${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$, ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d, \mat{L}=\mat{L}_{\langle C \rangle}$ and $\mat{K}=\mat{K}_{\langle C \rangle}$.
 
 %Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally
-In this section we assume that
-${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$ and ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d$ for a given time discretization.
+
 %% We will initially assume this for the description of the system and then introduce the errors caused  by misrepresentations.
@@
 where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations.
-A controllable and observable system will have the following dynamics:
+Then, a controllable and observable system will have the following dynamics:
 \begin{align}
@@
 \end{align}
-where $\vec{x}_e=\vec{x}-\hat{\vec{x}}$ is the estimation error of the state space by the observer, and $k_r$ is a reference gain required by the model.
+where $\vec{x}_e=\vec{x}-\hat{\vec{x}}$ is the estimation error of the state space by the observer.
+%, and $k_r$ is a reference gain required by the model.
 
@@
 ~and $\mat{R}_{cf}$%$\mat{R}_{cf}=\left[\begin{array}{cccc} mat{B}_c & \mat{A}_c\mat{B}_c & \cdots & \mat{A}_c^{p-1}\mat{B}_c \end{array}\right]$
-~are called reachability matrices (of the system and its Reachable Canonical Form respectively),
+~are called reachability matrices (of the system and its reachable canonical form, respectively),
 and $\mat{W}_o$%$\mat{W}_o=\left[\begin{array}{c} mat{C}\\ \mat{C}\mat{A}\\ \vdots \\ \mat{C}\mat{A}^{p-1} \end{array}\right]$
@@
 
-As stated in Section~\ref{sec:cof_stability}, we use Jury's Criterion on these polynomials
-to assert the stability specification.
+We get the stability specification by using Jury's Criterion on these polynomials.
 
@@
 
-Thus far we looked at checking stability
-%have presented a verification procedure for
-of a continuous plant in discretized time domain (i.e., the range of the quatizers is still
-$\mathbb{R}$).  The next step we must realize is that the controller and the
-observer exist in a digital program, hence their domain is
-$\mathbb{R}_{\langle C \rangle}$.  This has two separate effects on the
+While in the previous section, we assumed that
+${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$ and ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d$ for a given time discretization, in this section
+we take into consideration the numerical representation and namely the fact that the domain for both
+the controller and the observer is $\mathbb{R}_{\langle C \rangle}$.
+
+%% Thus far we looked at checking stability
+%% %have presented a verification procedure for
+%% of a continuous plant in discretized time domain (i.e., the range of the quatizers is still
+%% $\mathbb{R}$).  The next step we must realize is that the controller and the
+%% observer exist in a digital program, hence their domain is
+%% $\mathbb{R}_{\langle C \rangle}$.
+
+This has two separate effects on the
 model.  If we recall Equation~\eqref{eq:observer_LTI}, the matrices of the observer

### 2017-10-17 TACAS2018/paper.tex
sec 6.2

@@
 
-While in the previous section, we assumed that
-${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$ and ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d$ for a given time discretization, in this section
-we take into consideration the numerical representation and namely the fact that the domain for both
+In this section, we assume that the observer model is further discretised in
+the value domain, i.e., the domain for both
 the controller and the observer is $\mathbb{R}_{\langle C \rangle}$.
-
+%% While in the previous section, we assumed that
+%% ${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$ and ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d$ for a given time discretization, in this section
+%% we take into consideration the numerical representation and namely
 %% Thus far we looked at checking stability
@@
 %% $\mathbb{R}_{\langle C \rangle}$.
-
-This has two separate effects on the
-model.  If we recall Equation~\eqref{eq:observer_LTI}, the matrices of the observer
-and the controller are not necessarily those of the plant.  In fact we have
-$\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$, ${\mat{A}_d}_{\langle C
+%
+%% This has two separate effects on the
+%% model.  If we recall Equation~\eqref{eq:observer_LTI}, the matrices of the observer
+%% and the controller are not necessarily those of the plant.  In fact we have
+%% $\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$,
+This means that we have 
+${\mat{A}_d}_{\langle C
 \rangle},{\mat{B}_d}_{\langle C \rangle},{\mat{C}_d}_{\langle C \rangle},
@@
 diagonal.  We must therefore compensate for the errors introduced in order
-to find a stable solution.  We can use Gershgoring disks to limit the error
+to find a stable solution.  We can use Gershgoring \todo{citation} disks to limit the error
 in the expected eigenvalues.  Let $\delta_o=\max(|{\mat{A}_e}_{i,*}|_2)$
@@
 about the error with respect to the unit circle, which is equivalent to
-upper bounding the estimation of the largest eigenvalue.  Hence given a
+upper bounding the estimation of the largest eigenvalue.  Hence, given a
 desired upper value $\overline{\lambda}$, we apply Jury's criterion on the
@@
 
-As a final annotation, we remark that the safety specification must be
-applied to the model described in this section, accounting for the
-representation errors of the FWL domain.
+%% As a final annotation, we remark that the safety specification must be
+%% applied to the model described in this section, accounting for the
+%% representation errors of the FWL domain.
 
@@
 
-We are not limited to the synthesis of digital stabilizing controllers -- a
-well known task in the literature on digital control systems -- but target
-safety requirements with an overall approach that is sound and automated. 
-More specifically, we require that the closed-loop system meets given safety
-specifications.  A safety specification gives raise to a requirement on the
-states of the model, such that the feedback controller (namely the choice of
-the gains matrix~$K$) must ensure that the state never violates the
-requirement.  Note that a stable, closed-loop system is not necessarily a
-safe system: indeed, the state values may leave the safe part of the state
-space while they converge to the equilibrium, which is typical in the case
-of oscillatory dynamics.  In~this work, the safety property is expressed as:
+%% Now that we have established convergence, we may examine the safety
+%% specification of the state space.
+A safety specification gives raise to a requirement on the
+states of the model, such that the controller and the observer (namely the 
+matrices~$K$ and~$L$) must ensure that the state never violates the
+requirement.
+
+In~this work, the safety property is expressed as:
 %
@@
 \end{align}
-
+%
 where $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
+%
+%% \begin{align}
+%% \phi_\mathit{safety}\equiv& \underline{y} \leq y_k \leq \overline{y}
+%% \iff \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
+%% \label{eq:safetyspec}
+%% \end{align}
+%
+%% For an observed system, the safety specification is
+%% given by a constraint on the output which are considered
+%% safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in
+%% [\underline{y}\ \ \overline{y}]$)
+%% Whilst there are other properties we may
+%% include in the verification, we will solely focus on these for simplicity of
+%% the explanation.  We assume that we do not want saturation in our
+%% system, hence the control loop has only one mode.
+%% First we must
+%% translate the safety specification into the statespace.  Replacing on the
+%% second part of equation \eqref{eq:observer_LTI_cf} we obtain
+%% %
+%% \begin{equation}
+%% \phi_{safety} := \underline{y}<\mat{C}\vec{x}_k<\overline{y}, \forall k \geq 0
+%% \label{eq:of_bounds}
+%% \end{equation}
+%
+%% We are not limited to the synthesis of digital stabilizing controllers -- a
+%% well known task in the literature on digital control systems -- but target
+%% safety requirements with an overall approach that is sound and automated. 
+%% More specifically, we require that the closed-loop system meets given safety
+%% specifications.  A safety specification gives raise to a requirement on the
+%% states of the model, such that the feedback controller (namely the choice of
+%% the gains matrix~$K$) must ensure that the state never violates the
+%% requirement.  Note that a stable, closed-loop system is not necessarily a
+%% safe system: indeed, the state values may leave the safe part of the state
+%% space while they converge to the equilibrium, which is typical in the case
+%% of oscillatory dynamics.  In~this work, the safety property is expressed as:
+%% %
+%% \begin{align}
+%% \phi_\mathit{safety}\equiv& \underline{y} \leq y_k \leq \overline{y}
+%% \iff \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
+%% \label{eq:safetyspec}
+%% \end{align}
+
+%% where $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
 
@@
 
-%==========
-
-%% Now that we have established convergence, we may examine the safety
-%% specification of the state space.
-In the case of SISO systems, the safety specification is
-given by a range of the input and a range of the output which are considered
-safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in
-[\underline{y}\ \ \overline{y}]$)
-Whilst there are other properties we may
-include in the verification, we will solely focus on these for simplicity of
-the explanation.  We assume that we do not want saturation in our
-system, hence the control loop has only one mode.
-%We have also identified the quantization noise as a bounded non-deterministic input.
-First we must
-translate the safety specification into the statespace.  Replacing on the
-second part of equation \eqref{eq:observer_LTI_cf} we obtain
-%
-\begin{equation}
-\phi_{safety} := \underline{y}<\mat{C}\vec{x}_k<\overline{y}, \forall k \geq 0
-\label{eq:of_bounds}
-\end{equation}
-\todo{Using \eqref{eq:observer_LTI_cf} doesn't result in this.}
-%
-\todo{transient response?}
 %

### 2017-10-17 TACAS2018/paper.tex
sec 6.3 on safety

@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\todo{FWL effects here? they are implicit from equation \ref{eq:observer_LTI_FWL_cf}}
-
 %% Now that we have established convergence, we may examine the safety
@@
 A safety specification gives raise to a requirement on the
-states of the model, such that the controller and the observer (namely the 
-matrices~$K$ and~$L$) must ensure that the state never violates the
+states of the model, such that the controller
+must ensure that the state never violates the
 requirement.
-
 In~this work, the safety property is expressed as:
@@
 where $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
+%
+Note that FWL effects are not explicitly captured here
+as they are implicit from equation \ref{eq:observer_LTI_FWL_cf}.
 %
@@
 
-Furthermore, we also need to consider the 
-constraints 
-\begin{align}
-\phi_\mathit{input}\equiv \underline{u} \leq u_k \leq \overline{u}
-\label{eq:inputspec}
-\end{align}
+Furthermore, it is practically relevant to consider the 
+constraints $\phi_\mathit{input}$ on the input
+signal $u_{k}$ and $\phi_\mathit{init}$ on the initial states $x_0$,
+which we assume have given bounds:
+%\begin{align}
+$\phi_\mathit{input}\equiv \underline{u} \leq u_k \leq \overline{u}$
+%\label{eq:inputspec}
+%\end{align}
 which comes from physical restrictions in the energy of the system, and
-\begin{align}
-\phi_\mathit{init}\equiv \mat{G}' \vec{x}_0 \leq \vec{h}'
-\label{eq:initspec}
-\end{align}
+%\begin{align}
+$\phi_\mathit{init}\equiv \mat{G}' \vec{x}_0 \leq \vec{h}'$,
+where $\mat{G}'$ and $\vec{h}'$ describe the initial state-space.
+%\label{eq:initspec}
+%\end{align}
 

### 2017-10-17 TACAS2018/paper.tex
sec 6.4

@@
 %
-We may now use this limit to express a constraint in terms of the
-coefficients for our synthesis process.  Let
+We now use this limit to express a constraint in terms of the
+coefficients of the characteristic polynomial.  Let this
+polynomial be:
 %
 \begin{equation}
-P=\prod_{i=0}^p (s-\lambda_i)=\sum_{j=0}^p c_js^j.
+P(s)=\prod_{i=0}^p (s-\lambda_i)=\sum_{j=0}^p c_js^j.
 \end{equation}
 %
-We use Jury's criterion to limit $|\lambda_i| \leq 1$.  Let us now define a
+%We can use Jury's criterion to limit $|\lambda_i| \leq 1$.
+Let us now define a
 transformation $\lambda_i'=\frac{\lambda_i}{\overline{\lambda}}$.  We want
 to ensure $\lambda_i' \leq 1$ which can be done by applying Jury's criterion
-to $P'=\prod_{i=0}^p (s-\lambda_i')=\sum_{j=0}^p c_j's^j$ where $c_j'$ are
-unknown.  However, if we replace for $\lambda_i$, we obtain
+to $P'(s)=\prod_{i=0}^p (s-\lambda_i')=\sum_{j=0}^p c_j's^j$ where $c_j'$ are
+unknown.  By replacing $\lambda_i$, we obtain
 %
@@
 %
-where all members are known, we may now synthesise coefficients that ensure
-the eigenvalues are smaller than a desired magnitude, thus ensuring that the
-settling time is too.
+where all members are known. Thus, we can ensure that the settling time is smaller than
+a certain magnitude by ensuring that 
+the eigenvalues are smaller too (which we can do with Jury's criterion).
 

### 2017-10-17 TACAS2018/paper.tex
References

@@
 synthesise correct by construction minimal digital controllers.  Contrary to
-LTL models \todo{citation} that require thousands of states and elaborate algorithms to
-implement, these PID-like controllers are represented by a few parameters
+LTL models that require thousands of states and elaborate algorithms to
+implement \cite{reissig2017feedback}, these PID-like controllers are represented by a few parameters
 and only require a few lines of code, thus reducing the implementation cost
@@
 
-In this work, equations~\eqref{eq:ode1} and~\eqref{eq:ode2} are soundly discretized in time (see Appendix~\ref{sec:cont_aa}) \todo{or use another paper as reference and remove sec .1?} into
+In this work, equations~\eqref{eq:ode1} and~\eqref{eq:ode2} are soundly discretized in time~\cite{van1978computing,middleton1990digital} (see Appendix~\ref{sec:cont_aa}) into
 \begin{align}
@@
 %-------------------------------
-\subsection{Overapproximating continuous time dynamics using discrete models}
+\section{Overapproximating continuous time dynamics using discrete models}
 \label{sec:cont_aa}

### 2017-10-26 TACAS2018/paper.tex
Control Theory appendix

@@
 %\newtheorem{proof}{Proof}
+\newtheorem{assumption}{Assumption}
 
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsection{Accelerated dynamics for systems without inputs}\label{sec:real_discrete_no_inputs}
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- Given a specific time $T$, the state $\vec{x}_T$ present at $T$ can be expressed as a linear function of $\vec{x}_0$ as described below.
+ \subsection{Accelerated dynamics for continuous time systems without inputs}\label{sec:real_discrete_no_inputs}
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ Given a specific time $T$, the state $\vec{x}_T$ present at time $T$ can be expressed as a linear function of $\vec{x}_0$ as described below.
 Note that, as the system has no inputs, its dynamics are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.
@@
 \begin{align}
-|\vec{y}_{k}-{\vec{y}_{t_d}}_{k}|_1 \leq q_t, \text{ where } q_t=&(|\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})|_1+|\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}|_1)|U|_\infty
+|\vec{y}_{k}-{\vec{y}_{t_d}}_{k}|_\infty \leq q_t, \text{ where } q_t=&(|\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})|_1+|\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}|_1)|U|_\infty
 \end{align}
@@
 Within the controller, state values are manipulated at low precision.
-%alongside the vector multiplication $\mat{K}\vec{x}$.
 Furthermore, the quantizers for the DAC and the ADC introduce truncation errors
@@
 \begin{array}{cc}
-k_n-a_n&\begin{array}{cc}\cdots&k_1-a_1\end{array}\\
+k_{p-1}-a_{p-1}&\begin{array}{cc}\cdots&k_0-a_0\end{array}\\
 \mat{I}&\mat{0}
@@
 \begin{array}{ccc}
-a_n-l_n&&\mat{I}\\
+l_{p-1}-a_{p-1}&&\mat{I}\\
 &&\vdots\\
-a_1-l_1&&\mat{0}
+l_0-a_0&&\mat{0}
 \end{array}\right]
 \end{align*}
-where $\sum_{i=0}^p a_iz^i$ is the characteristic polynomial of the plant.
+where $\sum_{i=0}^p a_iz^i$ is the characteristic polynomial of the plant and $a_p=1$.
 This is achieved by the following transformation. Let
@@
 \begin{align*}
-P(z)=P_K(z)P_L(z)=\left(z^p+\sum_{i=1}^p{(a_i-k_i)z^{p-i}}\right) \left(z^p+\sum_{i=1}^p{(l_i-a_i)z^{p-i}}\right)
+P(z)=P_K(z)P_L(z)=\left(z^p+\sum_{i=0}^{p-1}{(a_i-k_i)z^{i}}\right) \left(z^p+\sum_{i=0}^{p-1}{(l_i-a_i)z^{i}}\right)
 \end{align*}
@@
 dimension for each matrix.  Unfortunately this means that although combined
-matrices such as $\mat{A}_t$ are in the reals, they suffer from the fixed
+matrices such as $\mat{A}_c$ are in the reals, they suffer from the fixed
 word restrictions in their composing matrices.
@@
 diagonal.  We must therefore compensate for the errors introduced in order
-to find a stable solution.  We can use Gershgoring \todo{citation} disks to limit the error
+to find a stable solution.  We can use Gershgoring disks~\cite{van1996matrix} to limit the error
 in the expected eigenvalues.  Let $\delta_o=\max(|{\mat{A}_e}_{i,*}|_2)$
@@
 %
-\begin{tabular}{| r | l | c | c | r | c | r |}
+\begin{tabular}{| r | l | c | c | c | r | r | r |}
 %
 \hline
-\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{order}  & \multicolumn{1}{|c|}{$\mat{K}$} & \multicolumn{3}{|c|}{$\mat{K}+\mat{L}+T_s$} \\
-   &                                  & & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{Max}\\\hline
-1  & DC Motor          & 2 & 2.1\,s& 16,16  &   4.1\,s &   4.1\,s\\
-2  & Helicopter        & 3  & 1.4\,s& 8.6\,s  &   54.9\,s &   t.o.\\
-3  & Inverted Pendulum & 4 &   0.6\,s& 16,24  &  308.4\,s &  308.4\,s\\
-4  & Magnetic Pointer  & 2  & 44.1\,s& 24,16  &  7.7\,s &  7.7\,s \\
-%5  & Magnetic Suspension & 2 & 0.6\,s& 16,24  &   0\,s &   0\,s\\
-5  & Pendulum          & 2 & 14.0\,s& 16,16  &   3.4\,s &   3.4\,s\\
-6  & Suspension        & 2 & 73.7\,s& 16,24  &   1316.2\,s &   1316.2\,s\\
-7  & Tape Driver       & 3 & 68.3\,s& 16,24  &   57.8\,s &   57.8\,s\\
-%9 & Satellite          & 2 &   0.7\,s& - &  - &  -\\ %unobservable
+\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{order} & \multicolumn{1}{|c|}{count} & \multicolumn{1}{|c|}{$\mat{K}$} & \multicolumn{3}{|c|}{$\mat{K}+\mat{L}+T_s$} \\
+   &                                 & & & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{Max}\\\hline
+1  & DC Motor          & 2 & 433 & 2.1\,s& 3.5\,s &   6.9\,s &   20.7\,s\\
+2  & Helicopter        & 3  & 54 & 1.4\,s& 8.8\,s  &   33.5\,s & 160.3\,s\\
+3  & Inverted Pendulum & 4 & 1 &   0.6\,s& 16,24  &  308.4\,s &  308.4\,s\\
+4  & Magnetic Pointer  & 2  & 246 & 44.1\,s& 7.7\,s  &  36.9\,s &  184.6\,s \\
+%5  & Magnetic Suspension & 2 & 1 & 0.6\,s& 16,24  &   0\,s &   0\,s\\
+5  & Pendulum          & 2 & 432 & 14.0\,s& 3.4\,s  &   26.9\,s &   156.8\,s\\
+6  & Suspension        & 2 & 1 & 73.7\,s& 16,24  &   1316.2\,s &   1316.2\,s\\
+7  & Tape Driver       & 3 & 488 & 68.3\,s& 12.4\,s  &   37.2\,s &   185.3\,s\\
+%9 & Satellite          & 2 & 1 &   0.7\,s& - &  - &  -\\ %unobservable
+   & Total                 &   & 1645 & & 3.4\,s & 20.1\,s & 1316.2 \,s\\
 \hline
@@
 \appendix
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{Control Theory} \label{sec:control_theory}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Since our models are being applied to linear control systems, and in particular to feedback systems with observers,
+we provide a summary of the important elements using control theory for their transfromations.
+
+%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%\subsection{Static Output Feedback and Pole Placement} \label{sec:pole_place}
+%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%
+%\begin{figure*}[htb]
+%\centering
+%
+%\tikzset{add/.style n args={4}{
+%    minimum width=6mm,
+%    path picture={
+%        \draw[circle] 
+%            (path picture bounding box.south east) -- (path picture bounding box.north west)
+%            (path picture bounding box.south west) -- (path picture bounding box.north east);
+%        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+%        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+%        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+%        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+%        }
+%    }
+% }
+%
+%\resizebox{1.0\textwidth}{!}{
+% \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
+%     semithick, initial text=, ampersand replacement=\&,]
+%
+%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
+%    \node[draw=none] (r) {$R(z)$};
+%%   \& \coordinate (aux0);
+%   \& \node[circle,add={-}{+}{}{}] (circle) {};
+%   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
+%   \& \node[rectangle,draw,
+%	minimum width=1cm,
+%	minimum height=1cm,
+%        label=\textbf{Controller}] (cz) {{\sc C(z)}};
+%   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
+%     
+%   \& complexnode/.pic={ 
+%      \node[rectangle,draw,
+%	minimum width=3cm,
+%	minimum height=1.6cm,
+%	label=\textbf{DAC},] (dac) {};
+%     \node[circle,add={}{+}{+}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
+%     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
+%     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
+%     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}   
+%   \& \node[rectangle,draw,
+%	minimum width=1cm,
+%	minimum height=1cm,
+%        label=\textbf{Plant}] (gs) {{\sc $G(s)$}};
+%   \node[draw=none] (ud) at ([xshift=-2cm,yshift=.15cm]gs)  {$U(s)$};
+%   \node[draw=none] (y) at ([xshift=2cm,yshift=.15cm]gs)  {$Y(s)$};
+%   \& complexnode/.pic={ 
+%     \node[rectangle,draw,
+%	minimum width=4cm,
+%	minimum height=1.6cm,
+%	label=\textbf{ADC},] (adc) {};
+%   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
+%   \coordinate (switch1) at ([xshift=-1cm]adc.center);
+%   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
+%   \node[circle,add={}{+}{+}{},fill=gray!20] (q1) at ([xshift=1cm]adc.center) {};} 
+%     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
+%   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
+%   \& \coordinate (aux1);
+%   \& \node[draw=none] (yz) {$Y(z)$};\\
+%   \& \coordinate (aux3); 
+%   \&
+%   \&
+%   \& 
+%   \& 
+%   \& \coordinate (aux2);\\
+%  };
+%
+%
+%  \path[->] (v1) edge (q1.north);
+%  \path[->] (v2) edge (q2.north);
+%  \path[->] (r) edge (circle.west);
+%  \path[->] (aux1) edge (yz);
+%  \path  
+%   (circle.east) edge (cz)
+%   (cz.east) edge (q2.west)
+%   (q2.east) edge (zoh.west)
+%   (zoh.east) edge (gs.west)
+%   (switch2) edge (q1.west)
+%   (q1.east) edge (aux1.west)
+%   (gs.east) edge (switch1.west)
+%   (aux1.south) edge (aux2.north)
+%   (aux2.west) edge (aux3.east); 
+%  \path[->]  (aux3.north) edge (circle.south);
+% \end{tikzpicture}
+%}
+% \caption{Closed-loop digital control system\label{fig:sampledsystem}}
+%\end{figure*}
+%
+%Given an unstable plant with divergent dynamics, the problem of stabilizing the output is to find a controller that
+%results in convergent closed loop dynamics. The term Static Output Feedback relates to the desired effect of
+%having a static output given a fixed reference signal.
+%In modern embedded systems, said controller is a digital program, which means that the closed loop dynamics are
+%subject to time and space discretization as described in sections \ref{sec:continuous_LTI} and \ref{sec:numeric_rep}.
+%In general terms, the controller is known to have discrete dynamics, whereas the plant has to be discretised based 
+%on the sample and hold characteristics. The ADC/DAC converters are considered to introduce a quantization noise on
+%the system as shown in Figure~\ref{fig:sampledsystem}.
+%Let the quantizer $Q1$ be the source of a non-deterministic noise $\nu_{1}$ and $Q2$ be the source of a non-deterministic noise
+%$\nu_{2}$.  The following equation models the system, encompassing the discretization of the plant:
+%%
+%\begin{equation}
+%Y(z)=C(z)G(z)(R(z)-Y(z))+\nu_{1}(z)+\nu_{2}(z)C(z)G(z),
+%\end{equation}
+%%
+%The above can be rewritten as follows:
+%%
+%\begin{equation}
+%\label{eq:outputfunctions}
+%Y(z)=H_1(z)R(z)+H_2(z)\nu_{1}(z)+H_3(z)\nu_{2}(z),
+%\end{equation}
+%%
+%where
+%%
+%\begin{align}
+%H_1(z)=\frac{C(z)G(z)}{1+C(z)G(z)},\\
+%H_2(z)=\frac{1}{1+C(z)G(z)},\\
+%H_3(z)=\frac{G(z)}{1+C(z)G(z)}.
+%\end{align}
+%%
+%
+%\begin{assumption}
+%\label{whitenoise}
+%%
+%The quantization noises $\nu_{1}$ (from $Q1$) and $\nu_{2}$ (from $Q2$) are
+%uncorrelated white noises and their amplitudes are always bounded by the
+%half of quantization step~\cite{astrom1997computer}, i.e., $\vert \nu_{1}
+%\vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$,
+%where $q_{1}$ and $q_{2}$, respectively, are the quantization steps of ADC
+%and DAC.
+%% 
+%\end{assumption}
+%
+%It is known that a discrete-time linear system is said to be Bounded-Input and Bounded-Output
+%(BIBO) stable if and only if every pole of its transfer function lies inside
+%the unit circle \cite{Astrom08}.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following
+%proposition states necessary conditions for BIBO stability of the closed-loop system
+%in Figure~\ref{fig:sampledsystem}, since the exogenous signals $R(z)$,
+%$\nu_{1}$, and $\nu_{2}$ are bounded. Hence, our close loop system is stable if the poles in
+%$H_1(z) , H_2(z) $ and $H_3(z)$ are inside the unit circle. Since all three transfer functions share the same poles,
+%we only need to look at the roots of the polynomial
+%$$C_n(z)G_n(z)+C_d(z)G_d(z) : C(z)=\frac{C_n(z)}{C_d(z)} \wedge G(z)=\frac{G_n(z)}{G_d(z)}$$
+%Any controller that ensures these roots lie within the unit circle is a stabilizing controller for the system.
+%
+%This same analysis can be applied to MIMO systems where there is a transfer functions of the system
+%for each combination of input-output. Rather than examine the transfer functions of these systems, we will first
+%look at minimal descrptions of the state space dynamics that will help us extract them with little extra effort whilst 
+%providing us with tools to analyse other properties.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Controllable Canonical Form} \label{sec:reachable}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Let us have a discrete time SISO system with an $p^{th},q^{th} \mid p\geq q$ order model
+$$y[k]=\sum_{i=1}^p a_{p-i}y[k-i]+\sum_{i=0}^{q-1} b_{p-i}u[k-i],$$
+where $y$ is the output of the system and $u$ its input.
+The equivalent LTI dynamics of such a model are:
+\begin{align}
+\label{eq:cf_SISO}
+\vec{x}_{k+1}=&\mat{A}_c\vec{x}_k+\mat{B}_cu_k : \vec{x}_k=[\begin{array}{cccc}y_k&y_{k-1}&\hdots&y_{k-(p-1)}\end{array}]^T\\
+y_k=&\mat{C}_c\vec{x}_k + b_0u_k\nonumber\\
+\mat{A}_c=&\left[
+\begin{array}{ccccc}
+-a_{p-1}&-a_{p-2}&\cdots&-a_1&-a_0\\
+1&0&0&\cdots&0\\
+0&1&0&\cdots&0\\
+\vdots&\ddots&\ddots&\ddots&\vdots\\
+0&\cdots&0&1&0
+\end{array}\right],
+\mat{B}_c=\left[
+\begin{array}{c}
+1\\0\\ \vdots\\ 0\\ 0
+\end{array}\right]\nonumber\\
+\mat{C}_c=&[\begin{array}{ccccc}b_0-a_0b_p&b_1-a_1b_p&\cdots&b_{p-1}-a_{p-1}b_p\end{array}] \text{ where } b_i=0 \mid i \in [0, p-q]\nonumber
+\end{align}
+
+where the coefficients $a_i$ describe the characteristic polynomial of the system. This matrix shape is
+called a Controllable Canonical Form because the dynamics of the feedback are directly related to these
+coefficients. Specifically, given a feedback controller $\mat{K}$ for any particular system, the closed loop dynamics
+are
+\begin{align}
+\vec{x}_{k+1}=(\mat{A}-\mat{B}\mat{K})\vec{x}
+\label{eq:closeloopdynamics}
+\end{align}
+which translated to Reachable Canonical Form will have the shape
+\begin{align}
+\mat{A}_c-\mat{B}_c\mat{K}_c=&\left[
+\begin{array}{ccccc}
+k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1&k_0-a_0\\
+1&0&0&\cdots&0\\
+0&1&0&\cdots&0\\
+\vdots&\ddots&\ddots&\ddots&\vdots\\
+0&0&\cdots&1&0
+\end{array}\right]
+\label{eq:cf_SISO_fb}
+\end{align}
+which means we can directly modify each coefficient by selecting a controller parameter.
+In the MIMO case, the Controllable Canonical Form has the following shape:
+\begin{align}
+\mat{A}_c=&\left[
+\begin{array}{ccccc}
+-\mat{a}_{p-1}\mat{M}_{p-1}&-\mat{a}_{p-2}\mat{M}_{p-2}&\cdots&-\mat{a}_{2}\mat{M}_{2}&-\mat{a}_0\mat{M}_0\\
+\mat{I}_{n-1}&0&0&\cdots&0\\
+0&\mat{I}_{n-2}&0&\cdots&0\\
+\vdots&\ddots&\ddots&\ddots&\vdots\\
+0&0&\cdots&\mat{I}_0&0
+\end{array}\right],
+\mat{B}_c=\left[
+\begin{array}{c}
+\mat{M}_0\\0\\ \vdots\\ 0\\ 0
+\end{array}\right]\nonumber\\
+\mat{C}_c=&[\begin{array}{ccccc}\mat{\Gamma}_{0}&\mat{\Gamma}_{1}&\cdots&\mat{\Gamma}_{p-1}\end{array}] 
+\label{eq:cf_MIMO}
+\end{align}
+with $\mat{I}_i,\mat{M}_i \in \mathbb{R}^{q_i \times q_i}, \mat{a}_i \in \mathbb{R}^{q \times q_i}, \mat{\Gamma}_i \in \mathbb{R}^o \text{ and }  \mat{\Gamma}_{i}=0 \mid i \in [0,p-q]$
+
+where $q$ is the number of inputs, $q_i$ the number of inputs with a transfer function of order of at least $i$, $\mat{I}_i$ an identity matrix, $\mat{M}_i$ an upper triangular matrix with 1s in its diagonal, $\mat{a_i}$ a matrix of coefficients of the $i^{th}$ order on its diagonal, and $o$ the number of outputs.
+Ideally, $\forall i>0, \mat{M}_i=\mat{I}_i$
+
+Any LTI system can be transformed into a controllable canonical form by a matrix $\mat{T}_c$ such that $\vec{x}=\mat{T}_c\hat{\vec{x}}$
+Then the dynamics of the controllable form are
+\begin{align}
+\hat{\vec{x}}_{k+1}=&\mat{A}_c\hat{\vec{x}}_k+\mat{B}_cu_k : \mat{A}_c=\mat{T}_c\mat{A}\mat{T}_c^{-1} \wedge \mat{B}_c=\mat{T}_c\mat{B}\\
+y_k=&\mat{C}_c\hat{\vec{x}}_k + b_0u_k : \mat{C}_c=\mat{C}\mat{T}_c^{-1}\nonumber
+\end{align}
+where $\mat{T}_c$ can be calculated as follows:
+
+Let 
+\begin{equation}
+\mat{R}=[\begin{array}{ccccc}\mat{B}&\mat{A}\mat{B}&\mat{A}^2\mat{B}&\hdots&\mat{A}^{p-1}\mat{B}\end{array}]
+\label{eq:rncf}
+\end{equation}
+be the reachability matrix of the system, and
+\begin{equation}
+\mat{R}_{c}=\left[\begin{array}{ccccc}1&a_{p-1}&a_{p-2}&\hdots&a_1\\0&1&a_{p-1}&\hdots&a_2\\ \vdots&\ddots&\ddots&\ddots&\ddots\end{array}\right]
+\label{eq:rcf}
+\end{equation}
+the reachability matrix of the canonical form. Then 
+\begin{equation}
+\mat{T}_c=\mat{R}_{c}\mat{R}^{-1}
+\label{eq:to_cf}
+\end{equation}
+
+%-------------------------------
+\subsection{Stability of a Controlled System} 
+\label{sec:closed_stability}
+%-------------------------------
+
+There are a number of algorithms that can be
+used for stability analysis~\cite{daes20161,Bessa16}.
+
+A discrete-time LTI system as \eqref{eq:closeloopdynamics} is
+asymptotically stable if all the roots of its characteristic
+polynomial (i.e., the eigenvalues of the closed-loop matrix $A_d - B_d
+K$) are inside the unity circle of the complex plane, i.e., their
+absolute values are strictly less than one~\cite{astrom1997computer}
+(this simple sufficient condition can be generalised, however this is
+not necessary in our work).  In this paper, we express this stability
+specification $\phi_\mathit{stability}$ in terms of a check known as
+\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic
+formula to select the entries of matrix $K$ so that the closed-loop
+dynamics are shaped as desired.
+
+Since the canonical forms used in this work use the coefficients of the
+characteristic polynomial $S(z)$ as opposed to its roots (which are
+extremely hard to calculate for a SAT solver), we choose Jury's
+criterion~\cite{astrom1997computer} to check the stability in the
+$z$-domain in view of its efficiency.
+
+We~consider the following form for $S(z)$:
+%
+\begin{equation*}
+S(z) = z^{p}+a_1z^{p-1}+\cdots+a_{p-1}z+a_p.
+\end{equation*}
+
+and build the matrix
+$\mat{M} \in \mathbb{R}^{p \times p}$ from its coefficients such that:
+%
+\begin{align*}
+\mat{M}_{1,j}&=a_j\\
+\mat{M}_{i+1,j}&=\left\{
+\begin{array}{ll}
+0,&j>p'\\
+\mat{M}_{i,j}-\mat{M}_{i,p'-j+1}\frac{\mat{M}_{i,1}}{\mat{M}_{i,p'}} &j\leq p'
+\end{array}
+\right.\\
+p'&=p-i+1
+\end{align*}
+%
+$S(z)$ is the characteristic polynomial of a stable system if and
+only if the following conditions hold~\cite{astrom1997computer}:
+\begin{align*}
+\phi_\mathit{stability}(S) \equiv
+(S(1) > 0) \wedge ((-1)^p S(-1) > 0) \wedge (|a_p| < 1) \wedge \bigwedge\limits_{i=1}^p (\mat{M}_{i,1} > 0).
+\end{align*}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Observable Canonical Form} \label{sec:observable}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+In most real implementations, the internal state of a plant cannot be
+directly measured but rather inferred from its effect on the output by
+using an observer.  Essentially, a state observer is a system that
+provides an estimate of the internal state of a given real system,
+from measurements of the input and output of the real system.
+
+A closed-loop digital control system with observer is shown in Fig.~\ref{fig:observersystem}.
+Note that the variables of a state observer are denoted by a "$~\hat{}~$" (e.g. {$\hat {\vec{x}}(k)$})
+to distinguish them from the variables of the actual physical system.
+Moreover, $\vec{y}_e=\hat{\vec{y}_k}-\vec{y}_k$ is the output estimation error defined
+as the difference between the real output $\vec{y}_k$ and estimated one $\hat{\vec{y}_k}$, whereas
+$\mat{L}$ is the error sensitivity matrix, which amplifies the output estimation error.
+The figure also contains references to $\nu_1$, $\nu_2$, $\nu_1'$, $\nu_2'$ and $\nu_t$, which
+denote noise and will be explained later in the paper.
+Lastly, $k_r$ is a reference gain required by the model.
+
+Presuming a sampled model of the plant as described in \eqref{eq:discretize}, the dynamics of the observer are:
+\begin{equation}
+\label{eq:to_of}
+\hat{\vec{x}}_{k+1}=({\mat{A}_d}_{\langle C \rangle}-\mat{L}{\mat{C}_d}_{\langle C \rangle})\hat{\vec{x}}_k+{\mat{B}_d}_{\langle C \rangle}\vec{u}+\mat{L}\vec{y}
+\end{equation}
+where the subindex ${\langle C \rangle}$ represents the domain of the controller $\mathbb{R}_{\langle C \rangle}$ such that ${\mat{A}_{\langle C \rangle}=\mathcal{F}_{\langle C \rangle}(\mat{A}_d)}$, ${\mat{B}_{\langle C \rangle}=\mathcal{F}_{\langle C \rangle}(\mat{B}_d)}$ and ${\mat{C}_{\langle C \rangle}=\mathcal{F}_{\langle C \rangle}(\mat{C}_d)}$.
+The differentiation between $\mat{*}_{\langle C \rangle}$ and $\mat{*}$ will be exploited later in this work. For the time being we will assume they are the same. 
+%is an observer of the system $\vec{x}_{k+1}=\mat{A}\vec{x}+\mat{B}\vec{u} : \vec{y}=\mat{C}\vec{x}$. 
+%$p_i$ are user selected values which will affect the error of the observer estimator. 
+Since the feedback of this system depends on $\mat{C}$ rather than $\mat{B}$, the Reachable
+Canonical form is no longer suitable. Hence we require an Observable Canonical Form.
+For SISO systems, this is:
+\begin{align}
+\label{of_SISO}
+\mat{A}_o=&\left[
+\begin{array}{cccccc}
+-a_{p-1}&1&0&0&\cdots&0\\
+-a_{p-2}&0&1&0&\cdots&0\\
+-a_{p-3}&0&0&1&\cdots&0\\
+\vdots&\vdots&\ddots&\ddots&\ddots&\vdots\\
+-a_0&0&0&0&\cdots&1
+\end{array}\right],
+\mat{B}_o=\left[
+\begin{array}{c}
+\Gamma_{p-1}\\ \Gamma_{p-2}\\ \vdots\\ \Gamma_0
+\end{array}\right]\\
+\mat{C}_o=&[\begin{array}{cccccc}\ \ \ \ 1&\ \ \ \ 0&0&0&\cdots&0\end{array}] \nonumber
+\end{align}
+
+We notice here that $\mat{A}_o=\mat{A}_c^T, \mat{C}_o=\mat{B}_c^T$
+and $\mat{B}_o=\mat{C}_c^T$, which also applies to the MIMO case.
+
+Let 
+\begin{equation}
+\label{eq:wnof}
+\mat{W}=\left[\begin{array}{c}\mat{C}\\ \mat{C}\mat{A}\\ \mat{C}\mat{A}^2\\ \vdots\\ \mat{C}\mat{A}^{p-1}\end{array}\right]
+\end{equation}
+be the observability matrix of the system, and
+\begin{equation}
+\label{eq:wof}
+\mat{W}_{o}=\mat{R}_{c}^{-1}
+\end{equation}
+the observability matrix of the canonical form (see eg~\cite{Astrom08}). The the matrix $\mat{T}_o=\mat{W}^{-1}\mat{W}_{o}$ will transform an observable system into its canonical form.
+For simplicity of the description, we agregate the noises as follows:
+$\eta_1=\nu_1+\nu_1'+\nu_t$ and $\eta_2=\nu_2+\nu_2'$,
+where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations (see section \ref{}).
+Assuming that the observer dynamics are an exact copy of the real ones, ($\mat{*}_{\langle C \rangle}=\mat{*}$), the closed loop dynamics of this system are given by:
+\begin{align}
+\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_{k+1}
+=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}&\mat{B}_d\mat{K}\\ \mat{0}&\mat{A}_d-\mat{L}\mat{C}_d\end{array}\right]
+\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_k
++\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}\end{array}\right]\left [\begin{array}{c}\vec{r}_k+\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
+\label{eq:observer_LTI}
+\end{align}
+where $\vec{x}_e=\vec{x}-\hat{\vec{x}}$ is the estimation error of the state space by the observer.
+Note that this matrix is not in canonical form. A transformation using both reachability and observability matrices is required. This is achieved as follows:
+By translating the coordinate system to 
+\begin{equation}
+\left[\begin{array}{c}\vec{x}'\\ \vec{x}_e'\end{array}\right]=
+\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right]
+\left[\begin{array}{c}\vec{x}\\ \vec{x}_e\end{array}\right]
+\end{equation}
+where $\mat{T}_c=\mat{R}_{c}\mat{R}^{-1}$ and $\mat{T}_o=\mat{W}^{-1}\mat{W}_{o}$, we can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
+\begin{align}
+\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
+=& \left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]
+\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
++\left[\begin{array}{cc}\mat{T}_c\mat{B}_d&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}\end{array}\right]\left [\begin{array}{c}\mat{k}_r\vec{r}_k+\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
+\vec{y}_k
+=& \mat{C}_{t}\vec{x}_k% + \mat{D}_{d}\vec{u}_k
+\label{eq:observer_LTI_cf}
+\end{align}
+where
+{
+\begin{align*}
+\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
+\mat{A}_{o}=&\mat{T}_o\left(\mat{A}_d-\mat{L}\mat{C}_d\right)\mat{T}_o^{-1}\\
+\mat{B}_{o}=&\mat{T}_c\mat{B}_d\mat{K}\mat{T}_o^{-1}&
+\mat{C}_t=&\mat{C}_d\mat{T}_c
+\end{align*}
+Replacing the matrices in \eqref{eq:observer_LTI_cf} with appropriate symbols:
+\begin{align}
+\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]&
+\mat{B}'=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}\end{array}\right]
+\label{eq:of_dynamics}
+\end{align}
+}
+we get
+\begin{displaymath}
+\tilde{\vec{x}}_{k+1}=\mat{A}' \tilde{\vec{x}}_{k}+\mat{B}' \tilde{\vec{u}}_k \text{ where }
+\tilde{\vec{x}}_k=\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k \text{ and }
+\tilde{\vec{u}}_k=\left [\begin{array}{c}\vec{r}_k+\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
+\label{eq:simple_observer_LTI}
+\end{displaymath}
+This has a similar structure to \eqref{eq:discretization} which will be helpful in our analysis.
+
+\begin{figure*}[htb]
+\centering
+\tikzset{add/.style n args={4}{
+    minimum width=6mm,
+    path picture={
+        \draw[circle] 
+            (path picture bounding box.south east) -- (path picture bounding box.north west)
+            (path picture bounding box.south west) -- (path picture bounding box.north east);
+        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+        }
+    }
+ }
+
+\resizebox{1.0\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
+     semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
+    \node[draw=none] (r) {$r_k$};
+    \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,] (gain)at ([xshift=1.2cm]r) {\sc $k_r$};
+
+   \& \node[circle,add={-}{+}{+}{}] (circle) {};
+   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$u_k$};
+   \node[draw=none] (v2p)  at ([yshift=1.2cm]circle) {$\nu_2'$};
+   \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Kd) at ([xshift=0,yshift=-5.5cm]circle)  {\sc $\mat{K}_{\langle C \rangle}$};
+   \coordinate (kdsouth) at ([yshift=-3cm]Kd);
+
+   \& complexnode/.pic={ 
+      \node[rectangle,dashed,draw,minimum width=3cm,minimum height=1.6cm,label=\textbf{DAC}] (dac) {};
+     \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
+     \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
+     \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
+     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {\sc ZOH};
+   }
+
+   \& complexnode/.pic={ 
+      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2.5cm,yshift=.5cm]plant.center)  {\sc $\mat{B}$};
+      \node[draw=none] (u) at ([xshift=-1cm,yshift=.15cm]B)  {$u(t)$};
+      \node[circle,add={+}{+}{}{}] (p1) at ([xshift=-1.3cm,yshift=.5cm]plant.center) {};
+      \node[draw=none] (xdot) at ([xshift=.85cm,yshift=.15cm]p1)  {$\dot{\vec{x}}(t)$};   
+      \node[rectangle,draw,minimum width=1cm] (int) at ([xshift=.5cm,yshift=.5cm]plant.center) {\sc $\int$};
+      \coordinate (xsouth) at ([xshift=1cm]int);
+      \node[draw=none] (x) at ([xshift=1cm,yshift=.15cm]int)  {$\vec{x}(t)$};   
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (C) at ([xshift=2.7cm,yshift=.5cm]plant.center)  {\sc $\mat{C}$};
+      \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]C)  {$\vec{y}(t)$};   
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (A) at ([xshift=.5cm,yshift=-1cm]plant.center)  {\sc $\mat{A}$};
+      \coordinate (aeast) at ([xshift=1cm]A);
+      \coordinate (awest) at ([xshift=-1.8cm]A);
+    }   
+    \node[circle,add={+}{+}{}{}]at ([xshift=2cm]C) (lag) {};
+    \node[draw=none] (vt)  at ([yshift=-1.5cm]lag) {$\nu_t$};
+   complexnode/.pic={ 
+      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=5cm,label=\textbf{Observer}] (observer)  at ([yshift=-5cm]plant.center) {};
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Bd) at ([xshift=-2.5cm]observer.center)  {\sc ${\mat{B}_d}_{\langle C \rangle}$};
+      \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]Bd)  {$u_k$};
+      \node[circle,add={+}{+}{+}{}] (o1) at ([xshift=-1.3cm]observer.center) {};
+      \node[draw=none] (xd) at ([xshift=.85cm,yshift=.15cm]o1)  {$\hat{\vec{x}}_{k+1}$};   
+      \node[rectangle,draw,minimum width=1cm] (delay) at ([xshift=.5cm]observer.center) {\sc $z^{-1}$};
+      \coordinate (xdsouth) at ([xshift=1.3cm]delay);
+      \coordinate (fbsouth) at ([xshift=1.3cm,yshift=-3cm]delay);
+      \node[draw=none] (xdp) at ([xshift=1cm,yshift=.15cm]delay)  {$\hat{\vec{x}}_k$};   
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Cd) at ([xshift=2.7cm]observer.center)  {\sc ${\mat{C}_d}_{\langle C \rangle}$};
+      \node[draw=none] (y) at ([xshift=.4cm,yshift=.8cm]Cd)  {$\hat{\vec{y}}_k$};   
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ad) at ([xshift=.5cm,yshift=-1.5cm]observer.center)  {\sc ${\mat{A}_d}_{\langle C \rangle}$};
+      \coordinate (adeast) at ([xshift=1.3cm]Ad);
+      \coordinate (adwest) at ([xshift=-1.8cm]Ad);
+      \node[circle,add={-}{}{+}{+}] (o2) at ([xshift=2.7cm,yshift=1.5cm]observer.center) {};
+      \node[draw=none] (v1p) at ([yshift=1.2cm]o2) {$\nu_1'$};
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ld) at ([xshift=.5cm,yshift=1.5cm]observer.center)  {\sc $\mat{L}_{\langle C \rangle}$};
+      \coordinate (ldwest) at ([xshift=-1.8cm]Ld);
+      \coordinate (bdwest) at ([xshift=-5.5cm]Bd);
+      \coordinate (uksouth) at ([xshift=-5.5cm,yshift=5.5cm]Bd);
+      \coordinate (o2east) at ([xshift=7.17cm]o2);
+    }
+
+   \& complexnode/.pic={ 
+     \node[rectangle,dashed,draw,minimum width=3.5cm,minimum height=1.6cm,label=\textbf{ADC},] (adc) {};
+     \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
+     \coordinate (switch1) at ([xshift=-1cm]adc.center);
+     \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
+     \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
+     \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
+     \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
+     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]q1)  {$\vec{y}_k$};       
+     \coordinate (ykeast) at ([xshift=1.9cm]q1);
+   } 
+   \& \coordinate (aux1);
+   \& \\
+  };
+
+  \path[->] (v1) edge (q1.south);
+  \path[->] (v2) edge (q2.south);
+  \path[->] (vt) edge (lag.south);
+  \path[->] (v1p) edge (o2.north);
+  \path[->] (v2p) edge (circle.north);
+  \path[->] (r) edge (gain.west);
+  \path[->] (gain.east) edge (circle.west);
+  \path[->] (circle.east) edge (q2.west);
+  \path       (q2.east) edge (zoh.west);
+  \path[->] (zoh.east) edge (B.west);
+  \path
+   (B.east) edge (p1.west)
+   (p1.east) edge (int.west)
+   (xsouth) edge (aeast)
+   (aeast) edge (A.east)
+   (A.west) edge (awest)
+   (awest) edge (p1.south)
+   (int.east) edge (C.west)
+   (C.east) edge (lag.west)
+   (lag.east) edge (switch1.west)
+   (switch2) edge (q1.west);
+  \path
+   (q1.east) edge (ykeast)
+   (ykeast) edge (o2east);
+  \path       (uksouth) edge (bdwest);
+  \path[->] (bdwest) edge (Bd.west);
+  \path
+   (Bd.east) edge (o1.west)
+   (o1.east) edge (delay.west)
+   (xdsouth) edge (adeast)
+   (adeast) edge (Ad.east)
+   (Ad.west) edge (adwest)
+   (adwest) edge (o1.south)
+   (o2.west) edge node {$\vec{y}_e$} (Ld.east)
+   (Ld.west) edge (ldwest)
+   (ldwest) edge (o1.north)
+   (delay.east) edge (Cd.west)
+   (Cd.north) edge (o2.south)
+   (o2east) edge (o2.east)
+   (xdsouth) edge (fbsouth)
+   (fbsouth) edge (kdsouth);
+  \path[->]  (kdsouth) edge (Kd.south);
+  \path[->] (Kd.north) edge (circle.south);
+ \end{tikzpicture}
+}
+ \caption{Closed-loop digital control system with observer\label{fig:observersystem}}
+\end{figure*}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Stability of an Observed System}\label{sec:cof_stability}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Careful examination of the matrices of the observed system\eqref{eq:of_dynamics} reveals that because $\mat{A}'$ is
+upper block diagonal, the spectrum of $\mat{A}'$ is equal to the union of
+the spectrum of $\mat{A}_{c}$ and $\mat{A}_{o}$, which can be calculated
+separately.  In other words, the characteristic polynomial of the closed loop is
+equal to the multiplication of the characteristic polynomials of the controller closed loop
+and the observer error when seen independently.
+%
+\begin{align*}
+P(z)=P_K(z)P_L(z)=\left(z^p+\sum_{i=0}^{p-1}{(a_i-k_i)z^{i}}\right) \left(z^p+\sum_{i=0}^{p-1}{(a_i-l_i)z^{i}}\right)
+\end{align*}
+
+We get the stability specification by appying Jury's Criterion to these polynomials.
 
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsubsection{Discrete dynamics using reals for systems without inputs}\label{asec:real_discrete_no_inputs}
+ \subsubsection{Accelerated dynamics for continuous time systems without inputs}\label{asec:real_discrete_no_inputs}
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsubsection{Discrete dynamics using reals for systems with parametric inputs}\label{asec:real_discrete_param_inputs}
+ \subsubsection{Accelerated dynamics for continuous time systems with parametric inputs}\label{asec:real_discrete_param_inputs}
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsubsection{Discrete dynamics using reals for systems with discrete time feedback inputs}\label{asec:real_discrete_feedback_inputs}
+ \subsubsection{Accelerated dynamics for continuous time systems with discrete time feedback inputs}\label{asec:real_discrete_feedback_inputs}
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2017-10-26 ase2017/time.m
added synthesis time script

@@ -1,0 +1,29 @@
+c = categorical({'cruise-HSCC','cruise','dc-motor','helicopter','invpendulum-cartpos','invpendulum-pendang', 'magnetic-pointer', 'magsuspension','pendulum','satellite', 'suspension','tapedriver','uscgtampa','flexible beam', 'uav', 'acrobot','guidance system', 'atenna'});
+
+ss= [4.596 0 10.86 1.314875 1.8225 65.912 1.342 281.0743333 25.452 6.172 281.0776667 15.672 1.320875 1.874 38.897 2.07225 1.718285714 1.857528571];
+tf = [497 0 34821 30222 1874 67895 1345 1647 1042 48576.33333 1350 471 0 67981 325.78 67981 48238 67234];
+
+bar(c,ss)
+legend('state-space')
+set(findall(gcf,'-property','LineWidth'),'LineWidth',2)
+set(findall(gcf,'-property','FontSize'),'FontSize',18);
+figure
+bar(c,tf)
+legend('transfer-function')
+set(findall(gcf,'-property','LineWidth'),'LineWidth',2)
+set(findall(gcf,'-property','FontSize'),'FontSize',18);
+
+figure
+data = [ss' tf'];
+bar(c,data)
+legend('state-space','transfer-function')
+set(findall(gcf,'-property','LineWidth'),'LineWidth',2)
+set(findall(gcf,'-property','FontSize'),'FontSize',18);
+
+figure
+plot(ss,'r');
+hold on
+plot(tf,'b');
+hold off
+legend('state-space','transfer-function')
+set(findall(gcf,'-property','FontSize'),'FontSize',18);

### 2017-10-26 TACAS2018/paper.tex

@@
 waiting for a new candidate solution.
+
+Our abstraction refinement CEGIS loop is similar to CEGIS with solution generalization \cite{}.
+However, it provides several improvements by exploiting modularity inside the loop.
+The novelty of our approach relies on the synthesis refinement phase, which enables us
+to generalise an existing candidate by means of optimisation. Rather than allow unsuitable
+candidates reach the verification phase, and possibly require further induction on the synthesiser,
+we use an optimizing algorithm which finds a local minima for the properties of interest. 
+This reduces the chances of the optimised candidate failing verification. Furthermore, it allows
+us to relax the quality of the synthesis, since unlikely candidates will still be optimised during this phase. 
+Optimization may also enter its own refinement loop, since it is possible for the
+counterexample to indicate which properties need optimizing (i.e. the ones that are failing).
 

### 2017-10-27 TACAS2018/paper.tex
norm notation

@@
 \usepackage{url}
+\usepackage{mathtools}
+
+\DeclarePairedDelimiter\norm{\lVert}{\rVert}
 
@@
  implementations.
- \item we present a model for soundly evaluating reachability in a combined 
+ \item We present a model for soundly evaluating reachability in a combined 
  continuous-discrete time/space. Sound tools for continuous time reachability 
@@
 \item We develop a model for inductive synthesis that combines CEGIS with
-abstraction refinement in order to minimize the synthesis cost. In particular
-we explore the idea of a multi-tiered model where different verification, 
-synthesis and modelling tools/modules explore different parts of the problem
-to deliver an optimal response.
+abstraction refinement and synthesis optimization in order to minimize the
+synthesis cost. In particular we explore the idea of a multi-tiered model where
+different verification, synthesis and modelling tools/modules explore different
+parts of the problem to deliver an optimal response.
 %
@@
 \begin{align}
-|\vec{y}_{k}-{\vec{y}_{t_d}}_{k}|_\infty \leq q_t, \text{ where } q_t=&(|\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})|_1+|\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}|_1)|U|_\infty
-\end{align}
-where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$.
+\norm{\vec{y}_{k}-{\vec{y}_{t_d}}_{k}}_1 \leq q_t, \text{ where } q_t=&(\norm{\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})}_1+\norm{\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}}_1)\norm{U}_1
+\end{align}
+where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$, and $\norm{\vec{x}}_1=\sum_{i=0}^{size(\vec{x})} |\vec{x}_i|$ is the $l_1$ norm (in for sets, $\norm{X}_1 = sup \norm{\vec{x}}_1 \mid \vec{x} \in X$).
 \end{theorem}
-%
-\todo{notation $| |_x$ ?}
 %
@@
 
-Our abstraction refinement CEGIS loop is similar to CEGIS with solution generalization \cite{}.
+Our abstraction refinement CEGIS loop is similar to CEGIS with counterexample generalization~\cite{david2017program}.
 However, it provides several improvements by exploiting modularity inside the loop.
@@
 numbers will incur errors that can be bound
-by~\cite{DBLP:conf/arith/BrainTRW15}.  We examine the most relevant ones:
+by~\cite{DBLP:conf/arith/BrainTRW15}.  
+We examine the most relevant ones:
 %
@@
 choice of $F$ is taken from the largest multiplication found (e.g.,
-$|\mat{A}|_1|\vec{x}|_\infty \mid \vec{x} \models \phi_\mathit{safety}$,
+$\norm{\mat{A}}_1\norm{\vec{x}}_1 \mid \vec{x} \models \phi_\mathit{safety}$,
 where $\phi_\mathit{safety}$ is defined in \ref{eq:safetyspec}). From these
@@
 \end{align*}
-The proof derives from $|\mat{K}\vec{x}| \leq |\mat{K}|_1|\vec{x}|_\infty$.
-
-%-------------------------------
-\section{Stability} 
-\label{appendix:stabspecification}
-%-------------------------------
-
-There are a number of algorithms that can be
-used for stability analysis~\cite{daes20161,Bessa16}.
-
-A discrete-time LTI system as \eqref{eq:closedloopss} is
-asymptotically stable if all the roots of its characteristic
-polynomial (i.e., the eigenvalues of the closed-loop matrix $A_d - B_d
-K$) are inside the unity circle of the complex plane, i.e., their
-absolute values are strictly less than one~\cite{astrom1997computer}
-(this simple sufficient condition can be generalised, however this is
-not necessary in our work).  In this paper, we express this stability
-specification $\phi_\mathit{stability}$ in terms of a check known as
-\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic
-formula to select the entries of matrix $K$ so that the closed-loop
-dynamics are shaped as desired.
-
-Since the canonical forms used in this work use the coefficients of the
-characteristic polynomial $S(z)$ as opposed to its roots (which are
-extremely hard to calculate for a SAT solver), we choose Jury's
-criterion~\cite{astrom1997computer} to check the stability in the
-$z$-domain in view of its efficiency.
-
-We~consider the following form for $S(z)$:
-%
-\begin{equation*}
-S(z) = z^{p}+a_1z^{p-1}+\cdots+a_{p-1}z+a_p.
-\end{equation*}
-
-and build the matrix
-$\mat{M} \in \mathbb{R}^{p \times p}$ from its coefficients such that:
-%
-\begin{align*}
-\mat{M}_{1,j}&=a_j\\
-\mat{M}_{i+1,j}&=\left\{
-\begin{array}{ll}
-0,&j>p'\\
-\mat{M}_{i,j}-\mat{M}_{i,p'-j+1}\frac{\mat{M}_{i,1}}{\mat{M}_{i,p'}} &j\leq p'
-\end{array}
-\right.\\
-p'&=p-i+1
-\end{align*}
-%
-$S(z)$ is the characteristic polynomial of a stable system if and
-only if the following conditions hold~\cite{astrom1997computer}:
-\begin{align*}
-\phi_\mathit{stability}(S) \equiv
-(S(1) > 0) \wedge ((-1)^p S(-1) > 0) \wedge (|a_p| < 1) \wedge \bigwedge\limits_{i=1}^p (\mat{M}_{i,1} > 0).
-\end{align*}
+The proof derives from $\norm{\mat{K}\vec{x}}_1 \leq \norm{\mat{K}}_1\norm{\vec{x}}_1$.
+
+%%-------------------------------
+%\section{Stability} 
+%\label{appendix:stabspecification}
+%%-------------------------------
+%
+%There are a number of algorithms that can be
+%used for stability analysis~\cite{daes20161,Bessa16}.
+%
+%A discrete-time LTI system as \eqref{eq:closedloopss} is
+%asymptotically stable if all the roots of its characteristic
+%polynomial (i.e., the eigenvalues of the closed-loop matrix $A_d - B_d
+%K$) are inside the unity circle of the complex plane, i.e., their
+%absolute values are strictly less than one~\cite{astrom1997computer}
+%(this simple sufficient condition can be generalised, however this is
+%not necessary in our work).  In this paper, we express this stability
+%specification $\phi_\mathit{stability}$ in terms of a check known as
+%\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic
+%formula to select the entries of matrix $K$ so that the closed-loop
+%dynamics are shaped as desired.
+%
+%
+%
+%Since the canonical forms used in this work use the coefficients of the
+%characteristic polynomial $S(z)$ as opposed to its roots (which are
+%extremely hard to calculate for a SAT solver), we choose Jury's
+%criterion~\cite{astrom1997computer} to check the stability in the
+%$z$-domain in view of its efficiency.
+%
+%We~consider the following form for $S(z)$:
+%%
+%\begin{equation*}
+%S(z) = z^{p}+a_1z^{p-1}+\cdots+a_{p-1}z+a_p.
+%\end{equation*}
+%
+%and build the matrix
+%$\mat{M} \in \mathbb{R}^{p \times p}$ from its coefficients such that:
+%%
+%\begin{align*}
+%\mat{M}_{1,j}&=a_j\\
+%\mat{M}_{i+1,j}&=\left\{
+%\begin{array}{ll}
+%0,&j>p'\\
+%\mat{M}_{i,j}-\mat{M}_{i,p'-j+1}\frac{\mat{M}_{i,1}}{\mat{M}_{i,p'}} &j\leq p'
+%\end{array}
+%\right.\\
+%p'&=p-i+1
+%\end{align*}
+%%
+%$S(z)$ is the characteristic polynomial of a stable system if and
+%only if the following conditions hold~\cite{astrom1997computer}:
+%\begin{align*}
+%\phi_\mathit{stability}(S) \equiv
+%(S(1) > 0) \wedge ((-1)^p S(-1) > 0) \wedge (|a_p| < 1) \wedge \bigwedge\limits_{i=1}^p (\mat{M}_{i,1} > 0).
+%\end{align*}
+%
 
@@
 \end{align}
-Rather than explicitly calculate this error, we will find an upper bound.
-Let $|U|_\infty=max(|\vec{u}|_\infty \mid \vec{u} \in U)$ be the maximum infinity norm of a vector set, propagating the error to the output $\vec{y}_k$ we have:
-\begin{align}
-|{\vec{y}_e}_{k}|_1 \subseteq &(\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})+\mat{C}\mat{A}_{t_s}\mat{B}_{t_d})U
+Rather than explicitly calculate this error, we will find an upper bound. Let $U = \bigcup \vec{u}_k$. Propagating the error to the output $\vec{y}_k$ we have:
+\begin{align}
+{\vec{y}_e}_{k} \subseteq &\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})U\oplus\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}U\\
+\Rightarrow \norm{{\vec{y}_e}_{k}}_1 \leq & (\norm{\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})}_1+\norm{\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}}_1)\norm{U}_1
 \end{align}

### 2017-10-27 TACAS2018/paper.tex
nudge

@@
 to find a stable solution.  We can use Gershgoring disks~\cite{van1996matrix} to limit the error
-in the expected eigenvalues.  Let $\delta_o=\max(|{\mat{A}_e}_{i,*}|_2)$
+in the expected eigenvalues.  Let $\delta_o=\max(\norm{{\mat{A}_e}_{i,*}}_2)$
 (\emph{i.e.} the largest row norm in $\mat{A}_e$) be the largest error bound
@@
 In the case of the reachable eigenvalues, the procedure is the same except
-that we obtain our bound $\delta_c=\max(|{\mat{A}_e}_{*,i}+{\mat{B}_e}_{*,i}|_2)$
+that we obtain our bound $\delta_c=\max(\norm{{\mat{A}_e}_{*,i}+{\mat{B}_e}_{*,i}}_2)$
 (\emph{i.e.} the largest column norm in $ \left[\begin{array}{c}\mat{A}_e\\ \mat{B}_e\end{array}\right]$) and
@@
 {\vec{\nu_e}}_i &\in \left[ -(p+2) \frac{q_c}{2}\ \ (p+2) \frac{q_c}{2}\right], i \in [1, p]\\
-\Rightarrow \nu_2' &\in \left[  -p(|\mat{K}_{\langle C \rangle}|_1+2) \frac{q_c}{2}\ \ p(|\mat{K}_{\langle C \rangle}|_1+2) \frac{q_c}{2}\right]
+\Rightarrow \nu_2' &\in \left[  -p(\norm{\mat{K}_{\langle C \rangle}}_1+2) \frac{q_c}{2}\ \ p(\norm{\mat{K}_{\langle C \rangle}}_1+2) \frac{q_c}{2}\right]
 \end{align*}
@@
 \begin{align*}
-\nu_1' &\in \left[  -p(|{\mat{C}_d}_{\langle C \rangle}|_1+2) \frac{q_c}{2}\ \ p(|{\mat{C}_d}_{\langle C \rangle}|_1+2) \frac{q_c}{2}\right]
+\nu_1' &\in \left[  -p(\norm{{\mat{C}_d}_{\langle C \rangle}}_1+2) \frac{q_c}{2}\ \ p(\norm{{\mat{C}_d}_{\langle C \rangle}}_1+2) \frac{q_c}{2}\right]
 \end{align*}
@@
 \begin{align}
-|{\vec{y}_e}_{k}|_1 \leq q_t, \text{ where } q_t=&(|\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})|_1+|\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}|_1)|U|_\infty
+\norm{{\vec{y}_e}_{k}}_1 \leq q_t, \text{ where } q_t=&(\norm{\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})}_1+\norm{\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}}_1)\norm{U}_1
 \end{align}

### 2017-11-02 TACAS2018/paper.tex
nudge

@@
 designs, in this section we will look at checking stability, safety
-and the response time in the presence of an observer.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Stability of an observed system}\label{sec:cof_stability}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-In this work we are interested in asymptotic stability: asymptotic
-stability is a property that amounts to convergence of the model
-executions to an equilibrium point, starting from any states in a
-neighborhood of the point. In the rest of the paper we refer to the
-stability specification as $\phi_\mathit{stability}$.
-
-%% There are a number of algorithms that can be
-%% used for stability analysis~\cite{daes20161,Bessa16}.
-
-A discrete-time LTI system (as shown in Sec.~\ref{sec:ssrepresentation})
-is asymptotically stable if all the roots of its characteristic
-polynomial (i.e., the eigenvalues of the closed-loop matrix $A_d - B_d
-K$) are inside the unity circle of the complex plane, i.e., their
-absolute values are strictly less than one~\cite{astrom1997computer}
-(this simple sufficient condition can be generalised, however this is
-not necessary in our work).  We express the stability
-specification in terms of a check known as
-\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic
-formula over the coefficients of the characteristic polynomial.
-%% to select the entries of matrix $K$ so that the closed-loop
-%% dynamics are shaped as desired.
-
-In order to be able to apply Jury's criterion,
-in the rest of this section, we compute the  
-characteristic polynomial of the observer model.
-Note that in this section, we consider that the model is
-discretized in the time domain, but not in the value domain.
-This essentially means that
-${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$, ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d, \mat{L}=\mat{L}_{\langle C \rangle}$ and $\mat{K}=\mat{K}_{\langle C \rangle}$.
-
-%Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally
-
-%% We will initially assume this for the description of the system and then introduce the errors caused  by misrepresentations.
-For simplicity of the description, we agregate the noises as follows:
-$\eta_1=\nu_1+\nu_1'+\nu_t$ and $\eta_2=\nu_2+\nu_2'$,
-where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations.
-Then, a controllable and observable system will have the following dynamics:
-\begin{align}
-\scriptstyle
-\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_{k+1}
-=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}&\mat{B}_d\mat{K}\\ \mat{0}&\mat{A}_d-\mat{L}\mat{C}_d\end{array}\right]
-\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_k
-+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
-+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}\end{array}\right]\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
-\label{eq:observer_LTI}
-\end{align}
-where $\vec{x}_e=\vec{x}-\hat{\vec{x}}$ is the estimation error of the state space by the observer.
-%, and $k_r$ is a reference gain required by the model.
-
-We want the state space dynamics in reachable form ($\mat{A}_c$) and the observer error dynamics in observable form ($\mat{A}_o$), i.e.
+and the response time in the presence of an observer. A full description of
+the theory related to the observer design is provided in appendix \ref{sec:control_theory}
+
+%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%\subsection{Stability of an observed system}\label{sec:cof_stability}
+%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%In this work we are interested in asymptotic stability: asymptotic
+%stability is a property that amounts to convergence of the model
+%executions to an equilibrium point, starting from any states in a
+%neighborhood of the point. In the rest of the paper we refer to the
+%stability specification as $\phi_\mathit{stability}$.
+%
+%A discrete-time LTI system (as shown in Sec.~\ref{sec:ssrepresentation})
+%is asymptotically stable if all the roots of its characteristic
+%polynomial (i.e., the eigenvalues of the closed-loop matrix $A_d - B_d
+%K$) are inside the unity circle of the complex plane, i.e., their
+%absolute values are strictly less than one~\cite{astrom1997computer}
+%(this simple sufficient condition can be generalised, however this is
+%not necessary in our work).  We express the stability
+%specification in terms of a check known as
+%\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic
+%formula over the coefficients of the characteristic polynomial.
+%
+%In order to be able to apply Jury's criterion,
+%in the rest of this section, we compute the  
+%characteristic polynomial of the observer model.
+%Note that in this section, we consider that the model is
+%discretized in the time domain, but not in the value domain.
+%This essentially means that
+%${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$, ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d, \mat{L}=\mat{L}_{\langle C \rangle}$ and $\mat{K}=\mat{K}_{\langle C \rangle}$.
+%
+%%Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally
+%
+%%% We will initially assume this for the description of the system and then introduce the errors caused  by misrepresentations.
+%For simplicity of the description, we agregate the noises as follows:
+%$\eta_1=\nu_1+\nu_1'+\nu_t$ and $\eta_2=\nu_2+\nu_2'$,
+%where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations.
+%Then, a controllable and observable system will have the following dynamics:
+%\begin{align}
+%\scriptstyle
+%\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_{k+1}
+%=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}&\mat{B}_d\mat{K}\\ \mat{0}&\mat{A}_d-\mat{L}\mat{C}_d\end{array}\right]
+%\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_k
+%+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
+%+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}\end{array}\right]\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
+%\label{eq:observer_LTI}
+%\end{align}
+%where $\vec{x}_e=\vec{x}-\hat{\vec{x}}$ is the estimation error of the state space by the observer.
+%%, and $k_r$ is a reference gain required by the model.
+%
+%We want the state space dynamics in reachable form ($\mat{A}_c$) and the observer error dynamics in observable form ($\mat{A}_o$), i.e.
 with dynamics whose coefficients are represented solely by those of the characteristic polynomial as follows:
-\begin{align*}
-\mat{A}_{c}=\left[
-\begin{array}{cc}
-k_{p-1}-a_{p-1}&\begin{array}{cc}\cdots&k_0-a_0\end{array}\\
-\mat{I}&\mat{0}
-\end{array}\right]&&
-\mat{A}_{o}=\left[
-\begin{array}{ccc}
-l_{p-1}-a_{p-1}&&\mat{I}\\
-&&\vdots\\
-l_0-a_0&&\mat{0}
-\end{array}\right]
-\end{align*}
-where $\sum_{i=0}^p a_iz^i$ is the characteristic polynomial of the plant and $a_p=1$.
-This is achieved by the following transformation. Let
-\begin{equation}
-\left[\begin{array}{c}\vec{x}'\\ \vec{x}_e'\end{array}\right]=
-\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right] 
-\left[\begin{array}{c}\vec{x}\\ \vec{x}_e\end{array}\right]
-\end{equation}
-We can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
-\begin{align}
-\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
-=& \left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]
-\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
-+\mat{B}' \vec{r}_k
-+\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
-\nonumber\\
-\vec{y}_k
-=& \mat{C}_{t}\vec{x}_k% + \mat{D}_{d}\vec{u}_k
-\label{eq:observer_LTI_cf}
-\end{align}
-{%\setlength{\belowdisplayskip}{0pt}
-\begin{align*}
-\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
-\mat{A}_{o}=&\mat{T}_o\left(\mat{A}_d-\mat{L}\mat{C}_d\right)\mat{T}_o^{-1}\\
-\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]&
-\mat{B}_{o}=&\mat{T}_c\mat{B}_d\mat{K}\mat{T}_o^{-1}\\
-\mat{B}'=&\left[\begin{array}{c}\mat{T}_c\mat{B}_d\mat{k}_r\\\mat{0}\end{array}\right]&
-\mat{B}_{\eta}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}\end{array}\right]\\
-\mat{T}_c=&\mat{R}_{cf}\mat{R}^{-1}&
-\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
-\mat{C}_t=&\mat{C}_d\mat{T}_c&
-\mat{L}=& \mat{T}_o^{-1}\left[ \begin{array}{ccc}l_1&\cdots&l_n\end{array}\right]^T
-\end{align*}
-}
-
-The matrices $\mat{R}$%$\mat{R}=\left[\begin{array}{cccc} \mat{B} & \mat{A}\mat{B} & \cdots & \mat{A}^{p-1}\mat{B} \end{array}\right]$
-~and $\mat{R}_{cf}$%$\mat{R}_{cf}=\left[\begin{array}{cccc} mat{B}_c & \mat{A}_c\mat{B}_c & \cdots & \mat{A}_c^{p-1}\mat{B}_c \end{array}\right]$
-~are called reachability matrices (of the system and its reachable canonical form, respectively),
-and $\mat{W}_o$%$\mat{W}_o=\left[\begin{array}{c} mat{C}\\ \mat{C}\mat{A}\\ \vdots \\ \mat{C}\mat{A}^{p-1} \end{array}\right]$
-~and $\mat{W}_{of}$%$\mat{W}_{of}=\left[\begin{array}{c} mat{C}_o\\ \mat{C}_o\mat{A}_o\\ \vdots \\ \mat{C}_o\mat{A}_o^{p-1} \end{array}\right]$
-~are its observability matrices  (of the system and its Observable Canonical Form respectively)~\cite{astrom1997computer}.
-
-Careful examination of the above matrices reveals that because the $\mat{A}'$ is
-upper block diagonal, the spectrum of $\mat{A}'$ is equal to the union of
-the spectrum of $\mat{A}_{c}$ and $\mat{A}_{o}$, which can be calculated
-separately.  In other words, the characteristic polynomial of the closed loop is
-equal to the multiplication of the characteristic polynomials of the controller
-and the observer when seen independently.
-%
-\begin{align*}
-P(z)=P_K(z)P_L(z)=\left(z^p+\sum_{i=0}^{p-1}{(a_i-k_i)z^{i}}\right) \left(z^p+\sum_{i=0}^{p-1}{(l_i-a_i)z^{i}}\right)
-\end{align*}
-
-We get the stability specification by using Jury's Criterion on these polynomials.
+%\begin{align*}
+%\mat{A}_{c}=\left[
+%\begin{array}{cc}
+%k_{p-1}-a_{p-1}&\begin{array}{cc}\cdots&k_0-a_0\end{array}\\
+%\mat{I}&\mat{0}
+%\end{array}\right]&&
+%\mat{A}_{o}=\left[
+%\begin{array}{ccc}
+%l_{p-1}-a_{p-1}&&\mat{I}\\
+%&&\vdots\\
+%l_0-a_0&&\mat{0}
+%\end{array}\right]
+%\end{align*}
+%where $\sum_{i=0}^p a_iz^i$ is the characteristic polynomial of the plant and $a_p=1$.
+%This is achieved by the following transformation. Let
+%\begin{equation}
+%\left[\begin{array}{c}\vec{x}'\\ \vec{x}_e'\end{array}\right]=
+%\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right] 
+%\left[\begin{array}{c}\vec{x}\\ \vec{x}_e\end{array}\right]
+%\end{equation}
+%We can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
+%\begin{align}
+%\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
+%=& \left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]
+%\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
+%+\mat{B}' \vec{r}_k
+%+\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
+%\nonumber\\
+%\vec{y}_k
+%=& \mat{C}_{t}\vec{x}_k% + \mat{D}_{d}\vec{u}_k
+%\label{eq:observer_LTI_cf}
+%\end{align}
+%{%\setlength{\belowdisplayskip}{0pt}
+%\begin{align*}
+%\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
+%\mat{A}_{o}=&\mat{T}_o\left(\mat{A}_d-\mat{L}\mat{C}_d\right)\mat{T}_o^{-1}\\
+%\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]&
+%\mat{B}_{o}=&\mat{T}_c\mat{B}_d\mat{K}\mat{T}_o^{-1}\\
+%\mat{B}'=&\left[\begin{array}{c}\mat{T}_c\mat{B}_d\mat{k}_r\\\mat{0}\end{array}\right]&
+%\mat{B}_{\eta}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}\end{array}\right]\\
+%\mat{T}_c=&\mat{R}_{cf}\mat{R}^{-1}&
+%\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
+%\mat{C}_t=&\mat{C}_d\mat{T}_c&
+%\mat{L}=& \mat{T}_o^{-1}\left[ \begin{array}{ccc}l_1&\cdots&l_n\end{array}\right]^T
+%\end{align*}
+%}
+%
+%The matrices $\mat{R}$%$\mat{R}=\left[\begin{array}{cccc} \mat{B} & \mat{A}\mat{B} & \cdots & \mat{A}^{p-1}\mat{B} \end{array}\right]$
+%~and $\mat{R}_{cf}$%$\mat{R}_{cf}=\left[\begin{array}{cccc} mat{B}_c & \mat{A}_c\mat{B}_c & \cdots & \mat{A}_c^{p-1}\mat{B}_c \end{array}\right]$
+%~are called reachability matrices (of the system and its reachable canonical form, respectively),
+%and $\mat{W}_o$%$\mat{W}_o=\left[\begin{array}{c} mat{C}\\ \mat{C}\mat{A}\\ \vdots \\ \mat{C}\mat{A}^{p-1} \end{array}\right]$
+%~and $\mat{W}_{of}$%$\mat{W}_{of}=\left[\begin{array}{c} mat{C}_o\\ \mat{C}_o\mat{A}_o\\ \vdots \\ \mat{C}_o\mat{A}_o^{p-1} \end{array}\right]$
+%~are its observability matrices  (of the system and its Observable Canonical Form respectively)~\cite{astrom1997computer}.
+%
+%Careful examination of the above matrices reveals that because the $\mat{A}'$ is
+%upper block diagonal, the spectrum of $\mat{A}'$ is equal to the union of
+%the spectrum of $\mat{A}_{c}$ and $\mat{A}_{o}$, which can be calculated
+%separately.  In other words, the characteristic polynomial of the closed loop is
+%equal to the multiplication of the characteristic polynomials of the controller
+%and the observer when seen independently.
+%%
+%\begin{align*}
+%P(z)=P_K(z)P_L(z)=\left(z^p+\sum_{i=0}^{p-1}{(a_i-k_i)z^{i}}\right) \left(z^p+\sum_{i=0}^{p-1}{(l_i-a_i)z^{i}}\right)
+%\end{align*}
+%
+%We get the stability specification by using Jury's Criterion on these polynomials.
 
@@
 \rangle}$ be the dynamics represented in $\mathbb{R}_{\langle C\rangle}^*$,
-%
-%and $\mat{A}_e=\mat{A}_d-{\mat{A}_d}_{\langle C \rangle}$, $\mat{B}_e=\mat{B}_d-{\mat{B}_d}_{\langle C \rangle}$,
-%and $\mat{C}_e=\mat{C}_d-{\mat{C}_d}_{\langle C \rangle}$ their corresponding errors.  
 Equation \eqref{eq:observer_LTI_cf} becomes:
@@
 \left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
-+\mat{B}_{c} \vec{r}_k
-+\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
++\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]\left [\begin{array}{c} \vec{r}_k + \vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
 \vec{y}_k=&\mat{C}_{t}\vec{x}_k'% + \mat{D}_{d}\vec{u}_k
@@
 \end{align}
-where
+where $\mat{T}_c$ and $\mat{T}_o$ trasfrom the system into canonical form~\cite{Astrom08} and
 {\setlength{\abovedisplayskip}{2pt}
@@
 \mat{C}_{e}=&\mat{C}_d-{\mat{C}_d}_{\langle C \rangle}\\
-\mat{T}_c=&\mat{R}_{cf}\mat{R}^{-1}&
-\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
-\mat{C}_t=&\mat{C}_d\mat{T}_c&
-\mat{L}_{\langle C \rangle}=& \mat{T}_o^{-1}\left[ \begin{array}{ccc}l_1&\cdots&l_n\end{array}\right]^T
+\mat{C}_t=&\mat{C}_d\mat{T}_c
 \end{align*}
@@
 \mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}+\mat{B}_{e}&\mat{B}_{o}\\ \mat{A}_{e}&\mat{A}_{o}\end{array}\right]&
-\mat{B}_{c}=&\left[\begin{array}{c}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}\mat{k}_r\\\mat{0}\end{array}\right]&
-\mat{B}_{\eta}=&\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]
+\mat{B}'=&\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]
 \end{align*}
 }
-The first effect of this new equation is that $\mat{A}'$ is no longer upper
+The first effect of this digitalization is that $\mat{A}'$ is no longer upper
 diagonal.  We must therefore compensate for the errors introduced in order
 to find a stable solution.  We can use Gershgoring disks~\cite{van1996matrix} to limit the error
-in the expected eigenvalues.  Let $\delta_o=\max(\norm{{\mat{A}_e}_{i,*}}_2)$
+in the expected eigenvalues.  Let $\delta_o=\max(\norm{{\mat{A}_e}_{i,*}}_1)$
 (\emph{i.e.} the largest row norm in $\mat{A}_e$) be the largest error bound
@@
 In the case of the reachable eigenvalues, the procedure is the same except
-that we obtain our bound $\delta_c=\max(\norm{{\mat{A}_e}_{*,i}+{\mat{B}_e}_{*,i}}_2)$
+that we obtain our bound $\delta_c=\max(\norm{{\mat{A}_e}_{*,i}+{\mat{B}_e}_{*,i}}_1)$
 (\emph{i.e.} the largest column norm in $ \left[\begin{array}{c}\mat{A}_e\\ \mat{B}_e\end{array}\right]$) and
@@
 \end{equation}
-
-%% As a final annotation, we remark that the safety specification must be
-%% applied to the model described in this section, accounting for the
-%% representation errors of the FWL domain.
 
@@
 \begin{theorem}
-Given a set of eigenvalues for a discrete time model of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1\ n]$, the settling time of the system is upperbounded by
+Given a set of eigenvalues for a discrete time model of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1, n]$, the settling time of the system is upperbounded by
 \begin{equation}
-t_s<-log_{\overline{\lambda}}({p_s}) : \overline{\lambda} = \max(|\lambda_i|) \wedge \overline{\lambda}<1,\ \forall i \in [1\ n]
+t_s<-log_{\overline{\lambda}}({p_s}) : \overline{\lambda} = \max(|\lambda_i|) \wedge \overline{\lambda}<1,\ \forall i \in [1, n]
 \label{eq:set_time}
@@
 
-\todo{this description does not mention two synthesis phases, which we should
-focus on more.}
+\todo{I assume the optimization problem is something like: ``find a controller and an observer that minimize some cost function''.
+What is the cost function in this case?
+I guess you want something like the
+  difference between the current candidate and the general solution? How would we capture that?}
+
+\todo{What is the optimization alg that you use? Point 4 below doesn't specify much.}
 
@@
 \end{equation}
-the observability matrix of the canonical form (see eg~\cite{Astrom08}). The the matrix $\mat{T}_o=\mat{W}^{-1}\mat{W}_{o}$ will transform an observable system into its canonical form.
+the observability matrix of the canonical form (see eg~\cite{Astrom08}). Then the matrix $\mat{T}_o=\mat{W}^{-1}\mat{W}_{o}$ will transform an observable system into its canonical form.
 For simplicity of the description, we agregate the noises as follows:

### 2017-11-09 TACAS2018/paper.tex
Optimization algorithm

--- 2017-11-02 TACAS2018/paper.tex
@@
 However, it provides several improvements by exploiting modularity inside the loop.
-The novelty of our approach relies on the synthesis refinement phase, which enables us
-to generalise an existing candidate by means of optimisation. Rather than allow unsuitable
-candidates reach the verification phase, and possibly require further induction on the synthesiser,
-we use an optimizing algorithm which finds a local minima for the properties of interest. 
-This reduces the chances of the optimised candidate failing verification. Furthermore, it allows
-us to relax the quality of the synthesis, since unlikely candidates will still be optimised during this phase. 
-Optimization may also enter its own refinement loop, since it is possible for the
-counterexample to indicate which properties need optimizing (i.e. the ones that are failing).
-
-\todo{I assume the optimization problem is something like: ``find a controller and an observer that minimize some cost function''.
-What is the cost function in this case?
-I guess you want something like the
-  difference between the current candidate and the general solution? How would we capture that?}
-
-\todo{What is the optimization alg that you use? Point 4 below doesn't specify much.}
+The novelty of our approach relies on the synthesis refinement phase, which
+enables us to generalise an existing candidate by means of optimisation. Rather
+than allow unsuitable candidates reach the verification phase, and possibly
+require further induction on the synthesiser, we use an optimizing algorithm
+which finds a local minima for the properties of interest.  This reduces the
+chances of the optimised candidate failing verification.  Furthermore, it
+allows us to relax the quality of the synthesis, since unlikely candidates will
+still be optimised during this phase. 
+The optimization is performed on an objective function which typically depends
+on a subset of the properties.  Hence the chosen optimization function depends
+on which properties fail verification. Optimization may also enter its own
+refinement loop, since it is possible for the counterexample to indicate which
+properties need optimizing (i.e. the ones that are failing).
+In our control synthesis problem, verification failures are typically due to
+safety (since stability and response time are maintained in the highest
+abstraction levels).  The optimization function therefore looks to minimize
+the reachspace by making the dynamics as convergent as possible (note that
+this also improves the response time of the system).
 
@@
 synthesise a refined solution. If the candidate is valid, we feed it to {\sc Discrete Time}. 
-\item {\sc Refine Synthesis} takes $\mat{K},\mat{L} \not \models \phi_{static}$ and synthesises $\mat{K}_{\langle C \rangle} = \mat{K}+\mat{\delta}_K, \mat{L}_{\langle C \rangle}=\mat{L}+\mat{\delta}_L, where \mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \models \phi_{static}$
+\item {\sc Refine Synthesis} takes $\mat{K},\mat{L} \not \models \phi_{static}$ and synthesises $\mat{K}_{\langle C \rangle} = \mat{K}+\mat{\delta}_K, \mat{L}_{\langle C \rangle}=\mat{L}+\mat{\delta}_L, where \mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \models \phi_{static}$.
+Furthermore we perform optimization based on the violation of the safe-space (if found).
+Given a closed loop controller or observer block ($\mat{A}_c$ or $\mat{A}_o$),
+we look for a constant $c \leq 1$ such that $\mat{B}\mat{K}'=(1-c)\mat{A}_d+c\mat{B}\mat{K} \mid \mat{K}' \models \phi_K$
+(and similarly for $\mat{L}'$.
 If we cannot synthesise a suitable candidate, we signal the {\sc Abstract} phase to refine $\phi_{synth}$ and request {\sc Synthesise} to produce a new candidate.
@@
 
+Our Synthesis Algorithm shows promise in exploiting modularity for
+improved response. It however relies on the use of application
+specific optimization which means that it is necessary to find adequate tools for
+exploring different types of properties.  Our results show significant
+improvement in terms of scalability over standard approaches with an ability to
+explore complex properties, hence many synthesis tasks may be derived
+from it. In particular we note that our synthesis loop should be targeted at
+systems where the solution space is formed by connected spaces where
+optimization algorithms or localized synthesis are likely to be achieved more
+efficiently than global synthesis.
+Finally our application to control synthesis provides a solid proof
+of concept for scalable optimal control synthesis of LTI systems. There is still
+a need to extend it it MIMO systems and analyse further properties, which may
+also require exploring other optimization methods for control systems.
+
 \newpage

### 2018-01-02 automatica/paper.tex
removed sections related to Transient Performance Specifications
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\title{Safe and Robust Formal Synthesis of Digital Controllers
-       for Continuous Plants with Transient Performance Specifications}
+\title{Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants}
 % Title, preferably not more
@@
 %-------------------------------
-
-%-------------------------------
-\subsection{Notation} 
-\label{ssec:notation}
-%-------------------------------
-
-\textcolor{red}{Elizabeth: we need to define the notation used throughout the paper.}
 
@@
 
-%---------------janus----------------
-\section{CEGIS of digital control system with transient specifications}
-\label{sec:method}
-%-------------------------------
-
-%-------------------------------
-\subsection{Synthesis in frequency domain}
-\label{ssec:frequencycegis}
-%-------------------------------
-
-%-------------------------------
-\subsection{Synthesis of state feedback controllers}
-\label{ssec:sscegis}
-%-------------------------------
-
-%-------------------------------
-\subsection{Synthesis of state observers}
-\label{ssec:sobsvcegis}
-%-------------------------------
-
 %-------------------------------

### 2018-01-02 automatica/paper.tex
Added comments related to observer and continuous time proof
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
reviewed Description of the benchmarks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Verification of a Conrollable Observed System}\label{sec:cof_verification}
+\section{Verification of a Controllable Observed System}\label{sec:cof_verification}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+\textcolor{red}{Dario: Do we still need this section? Where would the continuous time proof fit?}
 
@@
 
-The benchmark suite employed to evaluate the proposed technique is 
-composed by 18 MIMO models extracted from the literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS} and discretized with different sample time
-resulting in 167 benchmarks.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{DC Motor}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-DC Motor benchmark describes the velocity dynamics of a basic 
-brushed direct current electrical machine.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Automotive Cruise System}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-An automotive cruise control system is used to keep constant the speed 
-of an automobile  tracking a desired speed reference, compensating 
-disturbances and uncertainties related to relief and terrain.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Pendulum}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-A pendulum is system composed by a swinging point mass suspended from 
-a frictionless pivot through a negligible mass rod.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Inverted Pendulum}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-An inverted pendulum is a system similar to the pendulum but the point 
-mass must be equilibrated above the pivot point that is mounted on an 
+Our benchmark suite consists of 18 MIMO models extracted from the 
+control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS};
+these models are discretized with different sample times, which thus results in $167$ benchmarks
+to evaluate our proposal approach.
+
+The DC motor benchmark describes the velocity dynamics of a basic 
+brushed direct current electrical machine. The automotive cruise control system 
+benchmark is used to keep constant the speed of an automobile, 
+tracking a desired speed reference, compensating disturbances and 
+uncertainties related to relief and terrain.The pendulum benchmark consists of a swinging point mass suspended from 
+a frictionless pivot through a negligible mass rod, while the inverted pendulum 
+benchmark is a system similar to the pendulum, but the point 
+mass must be equilibrated above the pivot point, which is mounted on an 
 one degree of freedom cart that moves over a track through a DC motor.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Magnetic Suspension}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Magnetic suspension benchmark corresponds to the discrete model of a 
-simple eletromagnet-ball system where a steel ball is levitated in air 
+The magnetic suspension benchmark corresponds to the discrete model of a 
+simple eletromagnet-ball system, where a steel ball is levitated in air 
 by the action of an electromagnetic force generated by an electromagnet.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Magnetic Pointer}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Magnetic pointer is a pointer, that is usually employed in analogue 
+The magnetic pointer benchmark is a pointer usually employed in analogue 
 gauges and indicators, whose angular position dynamics is controlled 
-by a magnetic field.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{1/4 Car Suspension}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The 1/4 Car Suspension benchmark corresponds to the model of a single 
-wheel suspension system of a car, {\it i.e.} the relative motion dynamics 
-of a mass springer damp model that connects the car to one of its wheels.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Computer Tape Driver}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Computer Tape Drive is a computer storage device used to read and write 
-data on magnetic tapes.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Acrobot - Robot Manipulator}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The Acrobot benchmark corresponds to the model of an two-link 
+by a magnetic field. The 1/4 Car Suspension benchmark corresponds to the model of a single 
+wheel suspension system of a car, {\it i.e.}, the relative motion dynamics 
+of a mass springer damp model, which connects the car to one of its wheels.
+
+The Computer Tape Driver benchmark is a computer storage device used to read and write 
+data on magnetic tapes. The Acrobot benchmark corresponds to the model of a two-link 
 underactuated robot manipulator, named Acrobot, linearized by partial 
-feedback linearization~\cite{acrobot}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{High-order Systems from Chen et. al.}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-These benchmarks corresponds to a series of high-order system model 
+feedback linearization~\cite{acrobot}. The high-order system benchmarks correspond to a series of high-order control system model 
 generally used as example for order reduction techniques~\cite{CHEN1979389}.
- In this work, these benchmarks are used for evaluate the proposed control
- synthesis technique under critical conditions, {\it i.e.} with a greater 
- number of parameters to be considered.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Continuous Stirred Tank Reactor}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This benchmark describes a linear model for PH dynamics of a PH 
+Here, these benchmarks are used to evaluate the proposed control 
+synthesis technique under critical conditions, {\it i.e.}, with a large number of parameters 
+to be considered.
+
+The Continuous Stirred Tank Reactor benchmark describes a linear model for PH dynamics of a PH 
 neutralization process of an aqueous solution of sodium acetate with 
-hydrochloric acid in a continuous flow stirred-tank reactor.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Flexible Beam}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-A Flexible Beam is a plant usually employed in vibration studies. It is 
-composed by a flexible metallic structure with piezoceramic actuators 
-and sensors.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Helicopter Longitudinal Motion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+hydrochloric acid in a continuous flow stirred-tank reactor. The Flexible Beam benchmark is a plant 
+usually employed in vibration studies; it consists of a flexible metallic structure with piezoceramic actuators and sensors.
 The Helicopter Longitudinal Motion benchmark describes the dynamics of 
@@
 rotational motion around the longitudinal axis.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{USCG cutter Tampa Heading Angle}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The USCG cutter Tampa Heading Angle describes the heading angle 
-dynamics of a Coast Guard cutter.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Voltage regulator}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The voltage regulator benchmark~\cite{KOKOTOVIC198023} consists 
-in a linear model of a synchronous machine connected to an 
-infinite bus.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Guidance Control System}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The USCG cutter Tampa Heading Angle benchmark describes the heading angle 
+dynamics of a Coast Guard cutter. The voltage regulator benchmark~\cite{KOKOTOVIC198023} consists 
+of a linear model of a synchronous machine connected to an  infinite bus.
 
 The Guidance Control System benchmark is another high-order system 
-model used by Chen et al.~\cite{CHEN1979389}  in order reduction 
+model used by Chen et al.~\cite{CHEN1979389}  to evaluate reduction 
 techniques. Guidance systems are used to determine the path of an 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Satellite Attitude Control System}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This benchmark describes the dynamics of a satellite attitude, 
-{\it i.e.} the orientation angles. An attitude control system must 
+The Satellite Attitude Control System benchmark describes the dynamics of a satellite attitude, 
+{\it i.e.}, the orientation angles. An attitude control system must 
 maintain the desired orientation of satellite with respect to an 
-inertial frame during all the excursion.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Springer-mass damper}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The springer-mass damper systems are classic models for a lot of 
-mechanical systems dynamics. This benchmark describes a mass that is 
-fixed to a node through a springer and moves under the action of a 
+inertial frame during all the excursion. The springer-mass damper system benchmarks 
+are classic models for several mechanical systems dynamics. These benchmarks describe a mass,
+which is fixed to a node by means of a springer and moves under the action of a 
 input force, damping, and elastic force.

### 2018-01-02 automatica/paper.tex
reviewed Description of the benchmarks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS};
-these models are discretized with different sample times, which thus results in $167$ benchmarks
+these models are discretized with different sample times, which thus leads to $167$ different benchmarks
 to evaluate our proposal approach.
@@
 uncertainties related to relief and terrain.The pendulum benchmark consists of a swinging point mass suspended from 
-a frictionless pivot through a negligible mass rod, while the inverted pendulum 
+a frictionless pivot by means of a negligible mass rod, while the inverted pendulum 
 benchmark is a system similar to the pendulum, but the point 
@@
 by the action of an electromagnetic force generated by an electromagnet.
-The magnetic pointer benchmark is a pointer usually employed in analogue 
+The magnetic pointer benchmark is a pointer employed in analogue 
 gauges and indicators, whose angular position dynamics is controlled 
-by a magnetic field. The 1/4 Car Suspension benchmark corresponds to the model of a single 
+by a magnetic field. The 1/4 car suspension benchmark corresponds to the model of a single 
 wheel suspension system of a car, {\it i.e.}, the relative motion dynamics 
@@
 
-The Computer Tape Driver benchmark is a computer storage device used to read and write 
-data on magnetic tapes. The Acrobot benchmark corresponds to the model of a two-link 
-underactuated robot manipulator, named Acrobot, linearized by partial 
+The computer tape driver benchmark is a computer storage device used to read and write 
+data on magnetic tapes. The acrobot benchmark corresponds to the model of a two-link 
+underactuated robot manipulator, named acrobot, linearized by partial 
 feedback linearization~\cite{acrobot}. The high-order system benchmarks correspond to a series of high-order control system model 
@@
 
-The Continuous Stirred Tank Reactor benchmark describes a linear model for PH dynamics of a PH 
+The continuous stirred tank reactor benchmark describes a linear model for PH dynamics of a PH 
 neutralization process of an aqueous solution of sodium acetate with 
-hydrochloric acid in a continuous flow stirred-tank reactor. The Flexible Beam benchmark is a plant 
+hydrochloric acid in a continuous flow stirred-tank reactor. The flexible beam benchmark is a plant 
 usually employed in vibration studies; it consists of a flexible metallic structure with piezoceramic actuators and sensors.
-The Helicopter Longitudinal Motion benchmark describes the dynamics of 
+The helicopter longitudinal motion benchmark describes the dynamics of 
 transitional motion with respect to a longitudinal plane and the 
 rotational motion around the longitudinal axis.
-The USCG cutter Tampa Heading Angle benchmark describes the heading angle 
+The USCG cutter tampa heading angle benchmark describes the heading angle 
 dynamics of a Coast Guard cutter. The voltage regulator benchmark~\cite{KOKOTOVIC198023} consists 
@@
 
-The Guidance Control System benchmark is another high-order system 
+The guidance control system benchmark is another high-order system 
 model used by Chen et al.~\cite{CHEN1979389}  to evaluate reduction 
@@
 
-The Satellite Attitude Control System benchmark describes the dynamics of a satellite attitude, 
+The satellite attitude control system benchmark describes the dynamics of a satellite attitude, 
 {\it i.e.}, the orientation angles. An attitude control system must 
-maintain the desired orientation of satellite with respect to an 
-inertial frame during all the excursion. The springer-mass damper system benchmarks 
-are classic models for several mechanical systems dynamics. These benchmarks describe a mass,
+maintain the desired orientation of a satellite with respect to an 
+inertial frame during all the excursion. The springer-mass damper system benchmark 
+is classic model for several mechanical systems dynamics. This benchmark describes a mass,
 which is fixed to a node by means of a springer and moves under the action of a 

### 2018-01-10 TACAS2018/paper.tex
+ comments in observer paper

@@
 and the response time in the presence of an observer. A full description of
-the theory related to the observer design is provided in appendix \ref{sec:control_theory}
+the theory related to the observer design is provided in appendix \ref{sec:control_theory}.
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+\todo{Start by saying what stability means and that we must have the eigenalues
+  inside the unity circle and that we want to use Jury's criterion.
+  Then, explain what the challenges are for observed systems and how they are overcome. Potentially, the overcoming can be moved to appendix.}
 

### 2018-01-19 TACAS2018/paper.tex
authors

@@
 
+\renewcommand{\note}[1]{\textcolor{red}{[#1]}}
 \newcommand\tool{{\sf DSSynth}}
@@
 
-\author{Dario Cattaruzza, Alessandro Abate, Cristina David, Daniel Kroening}%\email{alessandro.abate@cs.ox.ac.uk}
+\author{Dario Cattaruzza, Cristina David, Alessandro Abate, Daniel Kroening}%\email{alessandro.abate@cs.ox.ac.uk}
 %\email{dario.cattaruzza@cs.ox.ac.uk}
@@
 We present a sound and automated approach to synthesizing safe,
-digital observer-based controllers for physical plants represented as
-linear, time-invariant models.  Models are given as dynamical
-equations with inputs, evolving over a continuous state space and
-accounting for errors caused by the digitization effects of the
+digital, observer-based controllers for physical plants represented as
+linear, time-invariant models.  Models are defined as differential 
+equations with inputs, evolving over a continuous state space. The synthesis 
+accounts for errors caused by the digitization effects introduced by the
 controller.  We use a two-stage counterexample-guided inductive
-synthesis (CEGIS) driven by abstraction refinement: (1) The first,
-coarse, synthesis stage uses a low resolution discretized model of the
+synthesis (CEGIS) scheme that driven by abstraction refinement. (1) The first,
+coarse, synthesis stage uses a low-resolution discretized version of the
 original one and, initially, only looks at static properties of the
-system.  (2) The second synthesis stage uses eigendecomposition to
+system \note{model}.  (2) The second synthesis stage uses matrix eigen-decomposition to
 refine the imprecise result computed by the first stage.  Whenever the
 second stage is unable to find a candidate solution, it triggers an
-abstraction refinement phase, resulting in a finer abstraction being
-fed back to the first stage.  This design resulted in a significant
-speed-up compared to a traditional single stage one.  We demonstrate
-the practical value of this approach by automatically synthesizing
+\note{keep? abstraction} refinement phase, resulting in a finer abstraction being
+fed back to the first stage. \note{This design yields a significant
+speed-up compared to a more traditional, single-stage CEGIS scheme [reviewer not familiar with that]}.  
+We demonstrate the practical value of this approach by automatically synthesizing
 safe observer-based controllers for physical plant models from the
@@
 
-\textbf{Discretization Effects --}
+\noindent\textbf{Discretization Effects --}
 The classical approach to control synthesis has often disregarded
@@
 We consider models of physical plants expressed as ordinary differential
-equations (ODEs), which we assume to be controllable:
+equations (ODEs), which we assume to be controllable \cite{Astrom08,astrom1997computer}:
 %
@@
 %
-where $t \in \mathbb R_0^+$, where $\mat{A}$ and $\mat{B}$ are matrices that 
-specify the continuous plant, and with initial states set as $x(0)$.
-
-Furthermore, we are interested in control systems with a derived
-output $\vec{y}$ that is a linear combination of its states and inputs:
+where $t \in \mathbb R_0^+$ denotes continuous time, 
+$\mat{A}$ and $\mat{B}$ are matrices that fully characterize the dynamics of the continuous plant, 
+and $x(0)$ is the initial state.
+
+We are interested in control systems with an output $\vec{y}$ that is a linear combination of its states and inputs:
 %, which may restrict the observability of the state-space from the output space.
@@
 \label{eq:ode2}  
-\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)
+\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t).
 \end{equation}
-
-In this work, equations~\eqref{eq:ode1} and~\eqref{eq:ode2} are soundly discretized in time~\cite{van1978computing,middleton1990digital} (see Appendix~\ref{sec:cont_aa}) into
+%
+%In this work, 
+Equations~\eqref{eq:ode1}-\eqref{eq:ode2} are soundly discretized in time~\cite{middleton1990digital,van1978computing} 
+(cf. Appendix~\ref{sec:cont_aa}) into
 \begin{align}
@@
 \vec{x}_{k+1} = \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k\\
-\vec{y}_{k} = \mat{C}_d \vec{x}_k + \mat{D}_d \vec{u}_k
-\end{align} 
-%
-where $k \in \mathbb N$ and $x_{0}=x(0)$ is the initial state. 
-$\mat{A}_d$, $\mat{B}_d$, $\mat{C}_d$ and $\mat{D}_d$ denote the matrices that describe the discretized plant dynamics, whereas $\mat{A}$, $\mat{B}$, $\mat{C}$ and $\mat{D}$ denote the continuous plant dynamics.
-In this work we assume $\mat{D}_d=\mat{D}=\mat{0}$.
-Also, since $\vec{y}$ can be directly derived from $\vec{x}$, we will omit discussing it in the following unless strictly necessary.
+\vec{y}_{k} = \mat{C}_d \vec{x}_k + \mat{D}_d \vec{u}_k, 
+\end{align} 
+%
+where $k \in \mathbb N$ is a discrete counter and $x_{0}=x(0)$ is the initial state. 
+Matrices $\mat{A}_d$, $\mat{B}_d$, $\mat{C}_d$ and $\mat{D}_d$ are equal-sized to $\mat{A}$, $\mat{B}$, $\mat{C}$ and $\mat{D}$ respectively,  
+and charactirize the discretized plant dynamics. 
+%, whereas the latter denote the continuous evolution.  
+In this work we make the standard assumption that $\mat{D}_d=\mat{D}=\mat{0}$ \cite{Astrom08}.  
+\note{Also, since $\vec{y}$ can be directly derived from $\vec{x}$, we will omit discussing it in the following unless strictly necessary.}
 %% We synthesize for requirements over this discrete-time domain. 
@@
 %
-The traces of the model starting from an initial set $X_0\subseteq \mathbb{R}^p$, 
+The traces of model \eqref{eq:plant}, 
+starting from an initial set $X_0\subseteq \mathbb{R}^p$, 
 with inputs restricted to $U \subseteq \mathbb{R}^q$, are sequences 
@@
 %
-where $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
+Here $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
 %

### 2018-01-19 TACAS2018/paper.tex
authors

@@
 %-------------------------------
-\subsection{State-space representation of LTI models}
+\subsection{State-space representations of LTI models}
 \label{sec:ssrepresentation}
@@
 
+\note{PLS ELIMINATE BOLD VARIABLES TO DENOTE VECTORS AND MATRICES. BTW, NOTATIONS BELOW ARE NOT CONSISTENT.}
+
 We consider models of physical plants expressed as ordinary differential
@@
 %In this work, 
-Equations~\eqref{eq:ode1}-\eqref{eq:ode2} are soundly discretized in time~\cite{middleton1990digital,van1978computing} 
+Equations~\eqref{eq:ode1}-\eqref{eq:ode2} are soundly discretized in time~\cite{middleton1990digital,van1978computing} \note{mention sample time, referred to later.}
 (cf. Appendix~\ref{sec:cont_aa}) into
@@
 \label{eq:plant}
+\left\{ 
+\begin{array}{l}
 \vec{x}_{k+1} = \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k\\
 \vec{y}_{k} = \mat{C}_d \vec{x}_k + \mat{D}_d \vec{u}_k, 
+\end{array}
+\right.
 \end{align} 
@@
 starting from an initial set $X_0\subseteq \mathbb{R}^p$, 
-with inputs restricted to $U \subseteq \mathbb{R}^q$, are sequences 
+with inputs taken from the set $U \subseteq \mathbb{R}^q$, are sequences 
 $ \vec{x}_0 \xrightarrow{\vec{u}_0} \vec{x}_1 \xrightarrow{\vec{u}_1} \vec{x}_2 \xrightarrow{\vec{u}_2} \ldots $, 
@@
 %
-Here $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
-%
-We extend the notation above to convex sets of initial conditions and inputs ($X_0$ and $U$), 
+Here $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe a safe set, within the state-space $\mathbb{R}^p$.
+%
+We generalize this notation to convex sets of initial conditions and inputs ($X_0$ and $U$, respectively), 
 and write $\tau(X_0,U)$ to denote the set of states $\{\vec{x} \mid \vec{x}_0 \in
@@
 We furthermore write $\tau^n(X_0,U)$ to denote the set of states reached from
-$X_0$ via $\tau$ in $n$ steps (\emph{$n$-reach set}), i.e.\ for $n\geq 1$
+$X_0$ via $\tau$ in $n$ steps (this is also known in literature \note{ref} as the \emph{$n$-reach set}), i.e.\ for $n\geq 1$
 %
 \begin{align}\label{equ:reachset}
-\tau^n(X_0,U) = \{\vec{x}_n \mid &\vec{x}_0 \in X_0 \wedge \forall k\in [0,n-1]\nonumber\\ 
- &\vec{u}_{k} \in U \wedge \vec{x}_{k+1}=\tau(\vec{x}_{k},\vec{u}_{k}) \} \;. 
-\end{align}
-%
-Since the transformations $\mat{A}$ and $\mat{B}$ are linear and
-vector sums preserve convexity, the sets $X_n = \tau^n(X_0,U)$ are also
-convex.
-
-We define the \emph{$n$-reach tube} 
+\tau^n(X_0,U) = \{\vec{x}_n \mid &\vec{x}_0 \in X_0 \wedge \forall k\in [0,n-1]
+%\nonumber\\ &
+\vec{u}_{k} \in U \wedge \vec{x}_{k+1}=\tau(\vec{x}_{k},\vec{u}_{k}) \} \;. 
+\end{align}
+%
+Since the transformations $\mat{A}$ and $\mat{B}$ are linear and vector sums preserve convexity \note{ref}, 
+the sets $X_n = \tau^n(X_0,U)$ are also convex.  
+We define the \emph{$n$-reach tube} as 
 \begin{equation}\label{equ:reachtube}
@@
 \end{equation}
-as the union of the reachable sets over $n$ iterations.
-%
-Moreover, $\hat{X} 
-=\bigcup_{n\geq 0} \tau^n(X_0,U)$ 
-extends the previous notion over an 
-unbounded time horizon.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{State observer}\label{sec:observer}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-In most real implementations, the internal state of a plant cannot be
-directly measured but rather inferred from its effect on the output by
-using an observer.  Essentially, a state observer is a system that
-provides an estimate of the internal state of a given real system,
-from measurements of the input and output of the real system.
+as the union of $k$-reach sets over $n$ iterations. 
+%
+Finally, set $\hat{X} =\bigcup_{n\geq 0} \tau^n(X_0,U)$ 
+generalises the previous notions over an unbounded time horizon.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{State observers}\label{sec:observer}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+In many models of real-world control systems, 
+the internal state $x$ cannot be directly measured,  
+but is rather inferred from its effect on the output $y$ by using an observer.  
+Essentially, a state observer is another dynamical model (below $\hat x$) 
+that provides an estimate of the internal state $x$ of the given model, 
+from measurements of the input and output of the system. \note{technical details in \ldots}
 
 A closed-loop digital control system with observer is shown in Fig.~\ref{fig:observersystem}. 
-Note that the variables of a state observer are denoted by a "$~\hat{}~$" (e.g. {$\hat {\vec{x}}(k)$})
-  to distinguish them from the variables of the actual physical system.
-  Moreover, $\vec{y}_e=\hat{\vec{y}_k}-\vec{y}_k$ is the output estimation error defined
-  as the difference between the real output $\vec{y}_k$ and estimated one $\hat{\vec{y}_k}$, whereas
-  $\mat{L}$ is the error sensitivity matrix, which amplifies the output estimation error.
-  The figure also contains references to $\nu_1$, $\nu_2$, $\nu_1'$, $\nu_2'$ and $\nu_t$, which
-  denote noise and will be explained later in the paper.
+Note that the variables of a state observer are denoted by $x_k$. 
+  Moreover, $y_e=\hat{y}_k - y_k$ is the output estimation error,  
+%  defined as the difference between the real output $\vec{y}_k$ and estimated one $\hat{\vec{y}_k}$, 
+  whereas $\mat{L}$ is an error gain matrix, which amplifies the output estimation error. 
+Figure \note{\ref{}} also contains references to $\nu_1$, $\nu_2$, $\nu_1'$, $\nu_2'$ and $\nu_t$, which
+  denote noise terms that will be explained later.   
 %%   With respect to noises (denoted by $\nu$), 
@@
   Lastly, $k_r$ is a reference gain required by the model.
+
+     Our goal in this work is to synthesise both $\mat{K}$ and $\mat{L}$. \note{K has not been discussed.}
 
@@
    \& complexnode/.pic={ 
-      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};
+      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Model}] (plant)  at ([yshift=-.5cm]dac.center) {};
       \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2.5cm,yshift=.5cm]plant.center)  {\sc $\mat{B}$};
@@
 
- Our goal in this work is to synthesise both $\mat{K}$ and $\mat{L}$.
-
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \section{Acceleration of continuous time systems}\label{sec:continuous_time_accel}
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
- Note that the discretization in Sec.~\ref{sec:ssrepresentation} only 
- allows us to evaluate the state of the system at integer multiples of the sample time.
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ \section{Acceleration of continuous-time models}\label{sec:continuous_time_accel}
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+The time discretization introduced in Sec.~\ref{sec:ssrepresentation} leads to evaluate the state of the model at integer multiples of the sample time. 
  However, in order to synthesise $\mat{K}$ and $\mat{L}$, 

### 2018-01-19 TACAS2018/paper.tex
authors

@@
 %  defined as the difference between the real output $\vec{y}_k$ and estimated one $\hat{\vec{y}_k}$, 
-  whereas $\mat{L}$ is an error gain matrix, which amplifies the output estimation error. 
+  whereas $\mat{L}$ is an error gain matrix that amplifies the output estimation error. 
 Figure \note{\ref{}} also contains references to $\nu_1$, $\nu_2$, $\nu_1'$, $\nu_2'$ and $\nu_t$, which
@@
 }
- \caption{Closed-loop digital control system with observer\label{fig:observersystem}}
+ \caption{Closed-loop digital control system with observer \note{it is unclear what we mean by digital here, we have only discretised time so far.}\label{fig:observersystem}}
 \end{figure*}
@@
  However, in order to synthesise $\mat{K}$ and $\mat{L}$, 
- we must be able to ensure that certain properties of the system hold at any given
- time (not just integer multiples of the sample time).
- Consequently, we accelerate the dynamics of the system (according to the model semantics in Sec.~\ref{sec:model_semantics}) in order to compute the state $\vec{x}_T$  at a given time $T$.
+ we must be able to ensure that certain properties of the system hold at any given (real) time. 
+ Consequently, we accelerate the dynamics of the system according to the model semantics in Sec.~\ref{sec:model_semantics} in order to compute the state $\vec{x}_T$  at a given time $T$ \note{unclear: we did not say what ``accelerate'' means, only mention we compute the state of the discrete-time model at time step T.}.
 
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsection{Accelerated dynamics for continuous time systems without inputs}\label{sec:real_discrete_no_inputs}
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- Given a specific time $T$, the state $\vec{x}_T$ present at time $T$ can be expressed as a linear function of $\vec{x}_0$ as described below.
-Note that, as the system has no inputs, its dynamics are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.
+ \subsection{Accelerated dynamics for continuous-time models without inputs}\label{sec:real_discrete_no_inputs}
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+ Given a specific time step $T$, 
+ the state $\vec{x}_T$ can be expressed as a linear function of $\vec{x}_0$ as described below. 
+ Note that, as the system has no inputs, its dynamics are simply described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.
 
@@
  Given $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, we have
+\note{unclear: next notation refers to discrete-time model}
  \begin{align}
@@
  \end{align}
-$\lambda_i \in \mat{J}$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.
+$\lambda_i \in \mat{J}$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$ \cite{Astrom08}.  
 We call $\vec{x}_T$ a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T.
@@
  %
+ \note{proof?}  
  \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_r=A_d^r\vec{x}_0 : r \in \mathbb{R}^+$ is a witness of the system at time $t=rT_d$.
+ If $\mat{J}$ is diagonal and there exists a discrete-dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_r=A_d^r\vec{x}_0 : r \in \mathbb{R}^+$ is a witness of the system at time $t=rT_d$.
  \end{corollary}
+  \note{proof?} 
 %

### 2018-01-19 TACAS2018/paper.tex
authors

@@
 %In this work, 
+\note{Observability requirement? Used later.}
 Equations~\eqref{eq:ode1}-\eqref{eq:ode2} are soundly discretized in time~\cite{middleton1990digital,van1978computing} \note{mention sample time, referred to later.}
@@
  we must be able to ensure that certain properties of the system hold at any given (real) time. 
- Consequently, we accelerate the dynamics of the system according to the model semantics in Sec.~\ref{sec:model_semantics} in order to compute the state $\vec{x}_T$  at a given time $T$ \note{unclear: we did not say what ``accelerate'' means, only mention we compute the state of the discrete-time model at time step T.}.
+ Consequently, we accelerate the dynamics of the system according to the model semantics in Sec.~\ref{sec:model_semantics} in order to compute the state $\vec{x}_T$  at a given time $T$ \note{unclear: we did not say what ``accelerate'' means, you only mention that we compute the state of the discrete-time (according to your notation) model at time step T.}.
 
@@
 We call $\vec{x}_T$ a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T. 
+\note{What exactly is a ``witness''? Do you mean ``the solution at that time''?}
  \end{theorem}
@@
  %
- \note{proof?}  
+ \note{proof? So what is the use of this theorem? How does it help to address the issue discussed at the beginning of the section?}  
  \begin{corollary}
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsection{Accelerated dynamics for systems with parametric inputs}\label{sec:real_discrete_param_inputs}
+ \subsection{Accelerated dynamics for models with parametric inputs}\label{sec:real_discrete_param_inputs}
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
  Next, we are interested in observing systems with parametric
- inputs, described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$.
+ inputs, described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ \note{confusing: if the input is parametric, it should not depend on time}. 
  For such systems, a witness $\vec{x}_T$ is computed next.
@@
  with $\mat{A}_T$ as per \eqref{eq:continuous_tube_dyn} is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$. 
+ \note{Just write u, w/o time dependence.}
 \end{theorem}
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsection{Accelerated dynamics for systems with discrete time feedback inputs}\label{sec:real_discrete_feedback_inputs}
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-The final case we analyse is that of hybrid time systems, where the
-plant dynamics evolve in continuous time while the feedback dynamics evolve
-in discrete time, i.e. a new input value is only produced for every sample interval.
-
+ \subsection{Accelerated dynamics for models with discrete-time feedback inputs}\label{sec:real_discrete_feedback_inputs}
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+The final case we analyse is that of hybrid-time models, 
+where the plant dynamics evolve in continuous time while the feedback dynamics evolve in discrete time, 
+namely a new input value is produced only at every sample time.
+%
 \begin{theorem}
@@
  \begin{align}
- \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
+ \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0, 
  \label{eq:cyber_feedback}
  \end{align}
- with $\mat{A}_T$ as per \eqref{eq:continuous_tube_dyn}, 
+ with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn}, 
  $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$ and 
@@
  \begin{align}
- \dot{\vec{x}}(t) &= \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\nonumber\\
- \vec{u}(t)&=\mat{K}\vec{x}_k  \mid  kT_s \leq t < (k+1)T_s
+ \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
+ \vec{u}(t)=\mat{K}\vec{x}_k,  
+ kT_s \leq t < (k+1)T_s. 
  \end{align}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Error modelling}\label{sec:errors}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Time delay on discrete time feedback systems} \label{sec:delay}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{Modelling Errors in the Control Loop}\label{sec:errors}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Time delay on discrete-time feedback models} \label{sec:delay}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
 A common ocurrence in digital systems is that they do not necessarily
@@
 \end{align}
-where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$, and $\norm{\vec{x}}_1=\sum_{i=0}^{size(\vec{x})} |\vec{x}_i|$ is the $l_1$ norm (in for sets, $\norm{X}_1 = sup \norm{\vec{x}}_1 \mid \vec{x} \in X$).
+where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$, and $\norm{\vec{x}}_1=\sum_{i=0}^{size(\vec{x})} |\vec{x}_i|$ is the $l_1$ norm (in for sets, $\norm{X}_1 = \sup \norm{\vec{x}}_1, \vec{x} \in X$).
 \end{theorem}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Errors generated by the numerical representation} 
+\subsection{Errors generated by numerical representations} 
 \label{sec:numeric_rep}
@@
 \begin{align}
-u_{k}&=\mathcal{F}_{\langle D \rangle}\left(-\mat{K}_{\langle C \rangle}\cdot\left(\mathcal{F}_{\langle C \rangle}\left(\mathcal{F}_{\langle A \rangle}(\vec{x}_{k})\right)\right) +\vec{\nu}_e\right)
+u_{k} =\mathcal{F}_{\langle D \rangle}\left(-\mat{K}_{\langle C \rangle}\cdot\left(\mathcal{F}_{\langle C \rangle}\left(\mathcal{F}_{\langle A \rangle}(\vec{x}_{k})\right)\right) +\vec{\nu}_e\right). 
 \label{eq:uk}
 \end{align}
-
+%
 This induces two types of the errors: first, the truncation
@@
 
-Previous studies~\cite{gangli1} show that the FWL affects the poles and
+Previous studies~\cite{gangli1} showed that the FWL affects the poles and
 zeros positions, degrading the closed-loop dynamics, causing steady-state
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Properties of a controllable observed system}\label{sec:cof_verification}
+\section{Properties of a controllable model with observer}\label{sec:cof_verification}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 composed by 18 MIMO models extracted from the literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15,maglev,converters}. 
-
-In the verification module, we use the tool Axelerator~\cite{} .
+In the verification module, we have used the tool Axelerator~\cite{} .
 
@@
 %-------------------------------
-The technique was applied  to the benchmarks and the results can be seen in table \ref{tab:results}
+The technique was applied  to the benchmarks and the results can be seen in Table \ref{tab:results}. 
 \begin{table}

### 2018-01-20 TACAS2018/paper.tex
Changes made offline on the Thesis repo

@@
 \newcommand{\jrronly}[1]{{}}
-\newcommand{\mat}[1]{\boldsymbol{#1}}
-\renewcommand{\vec}[1]{\boldsymbol{#1}}
+\newcommand{\mat}[1]{{#1}}
+\renewcommand{\vec}[1]{{#1}}
+
 %\newtheorem{theorem}{Theorem}
@@
 \renewcommand{\note}[1]{\textcolor{red}{[#1]}}
+\newcommand{\xmark}{\ding{55}}
 \newcommand\tool{{\sf DSSynth}}
@@
 %\email{kroening@cs.ox.ac.uk}
+
+\institute{University of Oxford}
 
@@
 original one and, initially, only looks at static properties of the
-system \note{model}.  (2) The second synthesis stage uses matrix eigen-decomposition to
-refine the imprecise result computed by the first stage.  Whenever the
-second stage is unable to find a candidate solution, it triggers an
-\note{keep? abstraction} refinement phase, resulting in a finer abstraction being
-fed back to the first stage. \note{This design yields a significant
-speed-up compared to a more traditional, single-stage CEGIS scheme [reviewer not familiar with that]}.  
+model.  (2) The second synthesis stage uses matrix eigen-decomposition 
+and objective functions to iteratively optimize results computed by the first stage.
+Whenever the optimization is unable to yield further results, it feeds back to the
+synthesiser in a traditional CEGIS manner. This design yields a significant
+speed-up compared to a traditional CEGIS scheme (i.e. without optimization).
 We demonstrate the practical value of this approach by automatically synthesizing
@@
 We make use of a two-stage counterexample-guided inductive
-synthesis (CEGIS) driven by abstraction refinement.
+synthesis (CEGIS) driven by optimization refinement.
 The first, coarse, synthesis stage uses a low resolution discretized model of a 
@@
 static properties  of the system. This largely reduces the complexity of
-the problem, enabling the synthesiser to offer fast response times. %% If any 
-%% of these parameters is inadequate, the refinement loop will supply a better
-%% abstraction to obtain a feasible answer.
+the problem, enabling the synthesiser to offer fast response times.
+
 Due to either numerical imprecision or overapproximations, the
 candidate solution presented by the first synthesiser will likely not
-meet the spec. A second synthesis stage, with a much more precise
-refinement including a mapping between the real and transformed spaces
-will create a candidate solution that is more adequate to the real
-model. This second stage uses perturbation analysis and therefore
-requires an initial solution to operate.  Whenever the second stage is
-unable to find a candidate solution, it triggers an abstraction
-refinement phase, resulting in a finer abstraction being fed back to
-the first stage.  The combined synthesisers are thus capable of
-reasoning about complex models with high computational efficiency due
-to their modularity.
+meet the spec. A second synthesis stage uses matrix eigen-decomposition 
+and objective functions to iteratively optimize results computed by the first
+stage.  Whenever the optimization is unable to yield further results, it feeds
+a counterexample to the first synthesiser in a traditional CEGIS manner.
+The combined synthesisers are thus capable of reasoning about complex
+models with high computational efficiency due to their modularity.
 
@@
 \subsection{State-space representations of LTI models}
-\label{sec:ssrepresentation}
+\label{sec:model}
 %-------------------------------
@@
 
-\note{PLS ELIMINATE BOLD VARIABLES TO DENOTE VECTORS AND MATRICES. BTW, NOTATIONS BELOW ARE NOT CONSISTENT.}
+\note{NOTATIONS BELOW ARE NOT CONSISTENT.}
 
@@
 \note{Observability requirement? Used later.}
-Equations~\eqref{eq:ode1}-\eqref{eq:ode2} are soundly discretized in time~\cite{middleton1990digital,van1978computing} \note{mention sample time, referred to later.}
-(cf. Appendix~\ref{sec:cont_aa}) into
+Equations~\eqref{eq:ode1}-\eqref{eq:ode2} are soundly discretized in
+time~\cite{middleton1990digital,van1978computing} at constant intervals whose
+duration we refer to as the sample time (cf. Appendix~\ref{sec:continuous_LTI}) into
 \begin{align}
@@
 In this work we make the standard assumption that $\mat{D}_d=\mat{D}=\mat{0}$ \cite{Astrom08}.  
-\note{Also, since $\vec{y}$ can be directly derived from $\vec{x}$, we will omit discussing it in the following unless strictly necessary.}
-%% We synthesize for requirements over this discrete-time domain. 
-%% Later, we will address the issue of variable quantization, 
-%% as introduced by the ADC/DAC conversion blocks (Fig.~\ref{fig:digitalsystem}).
+%Also, since $\vec{y}$ can be directly derived from $\vec{x}$, we will omit discussing it in the following unless strictly necessary.
 
@@
 %
-We furthermore write $\tau^n(X_0,U)$ to denote the set of states reached from
-$X_0$ via $\tau$ in $n$ steps (this is also known in literature \note{ref} as the \emph{$n$-reach set}), i.e.\ for $n\geq 1$
+We furthermore define the $n$-reach set $\tau^n(X_0,U)$ as the set of states reached from
+$X_0$ via $\tau$ in $n$ steps.
 %
@@
 \end{equation}
-as the union of $k$-reach sets over $n$ iterations. 
+as the union of $k$-reach sets over $n$ iterations  (transitive closure). 
 %
@@
 
-A closed-loop digital control system with observer is shown in Fig.~\ref{fig:observersystem}. 
+A closed-loop digital control system with observer is shown in Figure~\ref{fig:observersystem}. 
 Note that the variables of a state observer are denoted by $x_k$. 
@@
   whereas $\mat{L}$ is an error gain matrix that amplifies the output estimation error. 
-Figure \note{\ref{}} also contains references to $\nu_1$, $\nu_2$, $\nu_1'$, $\nu_2'$ and $\nu_t$, which
+Figure~\ref{fig:observersystem} also contains references to $\nu_1$, $\nu_2$, $\nu_1'$, $\nu_2'$ and $\nu_t$, which
   denote noise terms that will be explained later.   
@@
 
-\begin{figure*}[htb]
+\begin{figure*}[t!]
 \centering
@@
    \& complexnode/.pic={ 
-      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Model}] (plant)  at ([yshift=-.5cm]dac.center) {};
+      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Continuous Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};
       \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2.5cm,yshift=.5cm]plant.center)  {\sc $\mat{B}$};
@@
    complexnode/.pic={ 
-      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=5cm,label=\textbf{Observer}] (observer)  at ([yshift=-5cm]plant.center) {};
+      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=5cm,label=\textbf{Discrete Observer}] (observer)  at ([yshift=-5cm]plant.center) {};
       \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Bd) at ([xshift=-2.5cm]observer.center)  {\sc ${\mat{B}_d}_{\langle C \rangle}$};
@@
 }
- \caption{Closed-loop digital control system with observer \note{it is unclear what we mean by digital here, we have only discretised time so far.}\label{fig:observersystem}}
+ \caption{Closed-loop digital control system with observer \note{it is unclear what we mean by digital here, we have only discretised time so far.}\label{fig:observersystem2}}
 \end{figure*}
@@
 
-The time discretization introduced in Sec.~\ref{sec:ssrepresentation} leads to evaluate the state of the model at integer multiples of the sample time. 
+ The time discretization in Sec.~\ref{sec:model} only 
+ allows us to evaluate the state of the system at integer multiples of the sample time.
  However, in order to synthesise $\mat{K}$ and $\mat{L}$, 
  we must be able to ensure that certain properties of the system hold at any given (real) time. 
- Consequently, we accelerate the dynamics of the system according to the model semantics in Sec.~\ref{sec:model_semantics} in order to compute the state $\vec{x}_T$  at a given time $T$ \note{unclear: we did not say what ``accelerate'' means, you only mention that we compute the state of the discrete-time (according to your notation) model at time step T.}.
-
- %While this is adequate for the controller, it is not sufficient for verification. We must therefore establish a new model that allows us to observe the system at a given time $t$.
- %We achieve this by using acceleration as described below.
-
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsection{Accelerated dynamics for continuous-time models without inputs}\label{sec:real_discrete_no_inputs}
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
- Given a specific time step $T$, 
- the state $\vec{x}_T$ can be expressed as a linear function of $\vec{x}_0$ as described below. 
+ Consequently, we accelerate the dynamics of the system according to the model semantics in Sec.~\ref{sec:model_semantics} in order to compute the state $\vec{x}_T$  at a given time $T$.
+i.e.
+we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$.
+
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ \subsubsection{Accelerated dynamics for continuous-time models without inputs}\label{sec:cont_acc_no_inputs}
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a linear function of $\vec{x}_0$ as described below.
  Note that, as the system has no inputs, its dynamics are simply described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.
@@
  \begin{theorem}
- Given $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, we have
-\note{unclear: next notation refers to discrete-time model}
+ The solution to the differential equation $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$,
+ evaluated at time $T$ is
  \begin{align}
  \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x}_0\\
- \text{where }\mat{A}_{T}&= \mat{S}
+ \mat{A}_{T}&= \mat{S}
  \left [ \begin{array}{cccc}
- e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(1)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
+ e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(2)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
 0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
@@
  \label{eq:continuous_tube_dyn}\\
- &\text{and } s_i=\left\{\begin{array}{cc}1&gm(\lambda_i)>1\\0&gm(\lambda_i)=1\end{array}\right.,\nonumber
- \end{align}
-$\lambda_i \in \mat{J}$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$ \cite{Astrom08}.  
-We call $\vec{x}_T$ a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T. 
-\note{What exactly is a ``witness''? Do you mean ``the solution at that time''?}
+ &\text{where } s_i=\left\{\begin{array}{cc}1&gm(\lambda_i)>1\\0&gm(\lambda_i)=1\end{array}\right.,\nonumber
+ \end{align}
+$\lambda_i \in \mat{J}$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.
+$\vec{x}_T$ is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T.
  \end{theorem}
- %% We can apply Th.~\ref{eq:continuous_tube_dyn} to discretized systems without inputs in order to
- %% obtain a witness ..
- %
- \note{proof? So what is the use of this theorem? How does it help to address the issue discussed at the beginning of the section?}  
  \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete-dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_r=A_d^r\vec{x}_0 : r \in \mathbb{R}^+$ is a witness of the system at time $t=rT_d$.
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x} \text{ with } k \in \mathbb{R}^+$ is a witness of the system at time $t=kT_d$.
  \end{corollary}
-  \note{proof?} 
-%
- % \begin{proof}
-% Let us recall equation \ref{eq:discretize}. The discrete representation of the system dynamics discretised with sample time $T_1$ is ruled by the formula
-% $\mat{A}_1 = e^{\mat{A} T_1}$. From matrix theory, we have 
-%\begin{align}
-% e^{\mat{A}}&=\sum_{k=0}^\infty \frac{1}{k!}\mat{A}^k
-%\end{align} 
-%\begin{align} 
-% e^{\mat{S}\mat{J}\mat{S}^{-1}}&=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{S}\mat{J}\mat{S}^{-1}\right)^k
-% =\mat{S} \left (\sum_{k=0}^\infty \frac{1}{k!}\mat{J}^k\right) \mat{S}^{-1}\nonumber\\
-% &=\mat{S}e^{\mat{J}}\mat{S}^{-1}
-%\end{align} 
-%\begin{equation}
-%\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \Rightarrow \vec{A}_1 = \mat{S}\mat{J}_1\mat{S}^{-1}= \mat{S}e^{\mat{J} T_1}\mat{S}^{-1}.
-% \end{equation}
-% 
-% Let $\mat{J}$ be a diagonal matrix, such that 
-% $${\lambda_1}_i=e^{\lambda_i T_1}, \forall \lambda_i \in \mat{J}.$$
-% Let us now take a different sample rate $T_2$, such that 
-% $${\lambda_2}_i=e^{\lambda_i T_2}, \forall \lambda_i \in \mat{J}.$$
-% We can then say that 
-% \begin{equation}
-% {\lambda_2}_i=e^{\lambda_i T_1 \frac{T_2}{T_1}}={\lambda_1}_i^{\frac{T_2}{T_1}} \Rightarrow A_2=A_1^{\frac{T_2}{T_1}}.
-% \end{equation}
-% This proves the theorem for $gm(\lambda_i)=1$.
-% We now note that given an exponentiated Jordan form with geometric multiplicity, the upper diagonal terms can be
-% referenced to the original eigenvalues modified by the sampling rate.
-%  Let $\mat{J}\in \mathbb{R}^{p \times p}$ be a Jordan Canonical matrix.
-% Then
-%\begin{align}
-% \mat{J}_1&=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{J}T_1\right)^k=\sum_{k=0}^\infty \frac{1}{k!} \left [ \begin{array}{cccc}
-% \lambda_i^k  & \binom{k}{1}  \lambda^{k-1} & \hdots  & \binom{k}{p-1} \lambda_i^{k-p+1} \\
-%& \lambda_i^k  & \binom{k}{1}  \lambda_i^{k-1} & \vdots \\
-%\vdots & \ddots & \ddots & \vdots \\
-%& &  &\lambda_i^k \\
-%\end{array} \right ] T_1^k
-%\end{align}
-%The eigenvalues remain the same as in the diagonal case, but the upper triangular terms are of the form:
-%\begin{align}
-%\forall j>i, c_{ij}&=\sum_{k=j-i}^\infty \frac{1}{k!}\binom{k}{j-i} \lambda_i^{k-(j-i)}T_1^k\\
-%&=\frac{1}{(j-i)!}\sum_{k=j-i}^\infty \frac{1}{(k-(j-i))!} \lambda_i^{k-(j-i)}T_1^k\nonumber\\
-%&=\frac{T_1^{j-i}e^{\lambda_i T_1}}{(j-i)!}\nonumber
-%\end{align}
-%which completes the proof for $gm(\lambda_i)>1$.
-%\end{proof}
-
+\begin{proof}
+See Appendix~\ref{sec:proofs}
+\end{proof}
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
  Next, we are interested in observing systems with parametric
- inputs, described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ \note{confusing: if the input is parametric, it should not depend on time}. 
+ inputs, described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where $\forall t, \mat{B}\vec{u}(t)=\vec{u}(0)$. 
  For such systems, a witness $\vec{x}_T$ is computed next.
@@
  \vec{x}_T&=\vec{x}(t=T)=\mat{A}^{-1}\vec{x}_T'\nonumber\\
-\vec{x}_T'&=\mat{A}\mat{A}_T\vec{x}_0 + (\mat{I}-\mat{A}_T)\mat{B}\vec{u} : \forall t \leq T,\ \vec{u}(t)=\vec{u} 
+\vec{x}_T'&=\mat{A}\mat{A}_T\vec{x}_0 + (\mat{I}-\mat{A}_T)\mat{B}\vec{u} \text{ where } \forall t \leq T,\ \vec{u}(t)=\vec{u} 
  \end{align}
  with $\mat{A}_T$ as per \eqref{eq:continuous_tube_dyn} is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$.
- \note{Just write u, w/o time dependence.}
  \end{theorem}
  \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then $\vec{x}_r=A_d^r\vec{x}_0+(\mat{I}-\mat{A}_d^r\mat{B}\vec{u}) : r \in \mathbb{R}^+$ is a witness of the system at time $rT_d$.
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}+(\mat{I}-\mat{A}_d^k\mat{B}\vec{u}) \text{ with } k \in \mathbb{R}^+$ is the state of the system at time $kT_d$.
  \end{corollary}
-% \begin{proof}
-% We begin by expanding the equation
-% \begin{align}
-% \vec{x}_T&=\mat{A}^{-1}\vec{x}_T'\nonumber\\
-% &=\mat{A}_T\vec{x}_0 + \mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}\vec{u}\nonumber\\
-% &= \mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u}
-% \end{align}
-% where $\mat{A}_T=e^{\mat{A}T}$ and $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$ correspond to $\mat{A}_d$ and $\mat{B}_d$ in equation \eqref{eq:discretize}
-% \end{proof}
+\begin{proof}
+See Appendix~\ref{sec:proofs}
+\end{proof}
 
@@
  $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$ and 
- $\mat{A}_d, \mat{B}_d$ describing the discretized plant dynamics is a witness of the system
+ $\mat{A}_d, \mat{B}_d$ describing the discretized plant dynamics is the state of the system
  \begin{align}
@@
  \end{theorem}
-%
-%
-%\begin{proof}
-%Let $\mat{K}$ be a feedback controller such that $\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$. Let the output of
-%the feedback system be a zero order holder such that $\vec{u}(t+kT_s)=\vec{u}(kT_s) : 0 \leq t < T_s$.
-%The closed loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
-%\begin{equation}
-%\vec{x}_{k,t}=\mat{A}_t\vec{x}_k-\mat{B}_t\mat{K}\vec{x}_k = (\mat{A}_t-\mat{B}_t\mat{K})\vec{x}_k : 0 \leq t < T_s
-%\end{equation}
-%We further explore the dynamics across discrete time boundaries. Let $\mat{A}_d=\mat{A}_{T_s}$ and $\mat{B}_d=\mat{B}_{T_s}$
-%\begin{align}
-%\vec{x}_{k}&=\vec{x}_{k-1,T_s}= (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}\\
-%\vec{x}_{k,T_s} &= (\mat{A}_d-\mat{B}_d\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}
-%\end{align}
-%which accelerating results becomes
-%\begin{align}
-%\label{eq:feedback_sampled_cont}
-%\vec{x}_{k} &= (\mat{A}_d-\mat{B}_d\mat{K}) ^k\vec{x}_0\\
-%\vec{x}_{t} &= (\mat{A}_{t-kT_s}-\mat{B}_{t-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
-%\label{eq:feedback_cont}
-%\end{align}
-%\end{proof}
+\begin{proof}
+See Appendix~\ref{sec:proofs}
+\end{proof}
 
@@
 
-A common ocurrence in digital systems is that they do not necessarily
+A common occurrence in digital systems is that they do not necessarily
 satisfy the real-time specifications.  Delays due to processing time,
@@
 \begin{theorem}
-The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modelled as a non-deterministic noise signal upperbound by 
+The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modelled as a non-deterministic noise signal upper bound by
 \begin{align}
@@
 \end{align}
-where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$, and $\norm{\vec{x}}_1=\sum_{i=0}^{size(\vec{x})} |\vec{x}_i|$ is the $l_1$ norm (in for sets, $\norm{X}_1 = \sup \norm{\vec{x}}_1, \vec{x} \in X$).
+where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$, and $\norm{\vec{x}}_1=\sum_{i=0}^{size(\vec{x})} |\vec{x}_i|$ is the $l_1$ norm (in for sets, $\norm{X}_1 = sup \{\norm{\vec{x}}_1 \mid \vec{x} \in X\}$).
 \end{theorem}
-%
+
+\begin{proof}
+See Appendix~\ref{sec:proofs}
+\end{proof}
+We over-approximate the effects of this vector by introducing a noise signal at the output $\nu_t=[-q_t, q_t]$ and use the dynamics of the system without delay.
+
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 
-We will use the domain $\mathbb{R}_{\langle C \rangle} \mid \langle C \rangle = \langle M_c,F_c \rangle$
+We will use the domain $\mathbb{R}_{\langle C \rangle} \text{ where } \langle C \rangle = \langle M_c,F_c \rangle$
 to represent the fixed point precision of the controller, and 
 $\mathbb{R}_{\langle P \rangle} \supseteq \mathbb{R}_{\langle C \rangle}$
-to represent the domain of the plant model.
+to represent the domain of a digital model of the dynamics of a real plant when
+evaluated by a verification tool.
 Thus, any mathematical operations in our modelled digital controller will be executed in the
@@
 
-%% The physical plant operates in the reals, which means
-%% our verification phase must also account for the numerical error caused by representing the
-%% physical plant at the finite precision $\mathbb{R}_{\langle P \rangle}$.
-
-%% We will use these subindices to represent functions, number, vectors and matrices in their
-%% corresponding domains.
-
-%\todo{unclear}
-%We further note that by choosing $\langle C \rangle = \langle M_c,[E_c] \rangle$
-%we extend the following to floating point reasoning.
-
-%% \subsubsection{Effect on safety specification and stability}
-
-%% Let us first consider the effect of the quantization errors on safety. 
-%% Within the controller, state values are manipulated at low precision,
-%% alongside the vector multiplication $Kx$.
-%% %
-%% %computed considering the error introduced by the digital controller caused by performing the vector multiplication $Kx$ at low digital precision.
-%% The inputs are computed using the following equation: 
-%% %
-%% \begin{align*}
-%% u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})). 
-%% \end{align*}
-
-%% This induces two types of the errors detailed above: first, the truncation
-%% error due to representing $x_k$ as $\mathcal{F}{\langle I_c,F_c
-%% \rangle}(x_{k})$; and second, the rounding error introduced by the
-%% multiplication operation.  We represent these errors as non-deterministic
-%% additive noise.%, which might de-stabilize the closed-loop model.
-
-%% An additional error is due to the representation of the plant dynamics, namely 
-%% %
-%% \begin{align*}
-%% x_{k+1} &=\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
-%% \end{align*}
-%% We address this error by use of interval
-%% arithmetic~\cite{moore1966interval} in the verification phase.
-
-%% Previous studies~\cite{gangli1} show that the FWL affects the poles and
-%% zeros positions, degrading the closed-loop dynamics, causing steady-state
-%% errors (see Appendix~\ref{sec:appendix:LTIbackground} for details) and
-%% eventually de-stabilizing the system~\cite{Bessa16}.  However, since in this
-%% paper we require stability only as a precursor to safety, it is sufficient
-%% to check that the (perturbed, noisy) model converges to a neighborhood of
-%% the equilibrium within the safe set (see Appendix~\ref{sec:stab_FWL}).
-
-%% In the following, we shall disregard these steady-state errors (caused by
-%% FWL effects) when stability is ensured by synthesis, and then verify its
-%% safety accounting for the finite-precision errors.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Quantization errors} \label{sec:quantization}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Let us first consider the effect of the quantization errors. 
-Within the controller, state values are manipulated at low precision.
-Furthermore, the quantizers for the DAC and the ADC introduce truncation errors
-which we denote by the effect of the functions $\mathcal{F}_{\langle D \rangle}$
-and $\mathcal{F}_{\langle A \rangle}$, respectively. Finally, let us call $\vec{\nu}_e$ the
-error caused by the FWL effects on the observer
-\todo{the observer was not defined..}
-(\emph{i.e} the numerical errors 
-in the calculations as opposed to the estimation error).
-The inputs are computed using the following equation: 
-%
-\begin{align}
-u_{k} =\mathcal{F}_{\langle D \rangle}\left(-\mat{K}_{\langle C \rangle}\cdot\left(\mathcal{F}_{\langle C \rangle}\left(\mathcal{F}_{\langle A \rangle}(\vec{x}_{k})\right)\right) +\vec{\nu}_e\right). 
-\label{eq:uk}
-\end{align}
-%
-This induces two types of the errors: first, the truncation
-error due to the domain transformations $\mathcal{F}_{\langle *
-\rangle}(\cdot)$; and second, the rounding error introduced by the
-multiplication operation.  We represent these errors as non-deterministic
-additive noise. More details can be found in Appendix~\ref{appendix:quantization}.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Modelling errors}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Errors incurred by the use of numerical algorithms during synthesis are not
-accounted for but rather checked during the verification phase.  If the
-counterexample provided corresponds to a pre-existing one, the synthesiser
-then increases its precision to reduce this error.
-
-Previous studies~\cite{gangli1} showed that the FWL affects the poles and
-zeros positions, degrading the closed-loop dynamics, causing steady-state
-errors and eventually de-stabilizing the system~\cite{Bessa16}.  However,
-since the verifier also checks for the stability of the dynamics as a
-precursor to safety, this case is handled inside the loop.  In the
-following, we shall disregard these steady-state errors (caused by FWL
-effects) when stability is ensured by synthesis, and then verify its safety
-accounting for the finite-precision errors.
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Modeling quantization as noise} \label{sec:quantization-noise}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+In Figure \ref{fig:observersystem2} we introduced
+several sources of noise, which are due to quantization effects. We now describe
+their nature and create a sound model for them to be used during our synthesis
+and verification process.
+
+%Let us first consider the effect of the quantization errors. 
+%Within the controller, state values are manipulated at low precision.
+%Furthermore, the quantizers for the DAC and the ADC introduce truncation errors
+%which we denote by the effect of the functions $\mathcal{F}_{\langle D \rangle}$
+%and $\mathcal{F}_{\langle A \rangle}$, respectively. Finally, let us call $\vec{\nu}_e$ the
+%error caused by the FWL effects on the observer
+%\todo{the observer was not defined..}
+%(\emph{i.e} the numerical errors 
+%in the calculations as opposed to the estimation error).
+%The inputs are computed using the following equation: 
+%%
+%\begin{align}
+%u_{k}&=\mathcal{F}_{\langle D \rangle}\left(-\mat{K}_{\langle C \rangle}\cdot\left(\mathcal{F}_{\langle C \rangle}\left(\mathcal{F}_{\langle A \rangle}(\vec{x}_{k})\right)\right) +\vec{\nu}_e\right)
+%\label{eq:uk}
+%\end{align}
+%
+%This induces two types of the errors: first, the truncation
+%error due to the domain transformations $\mathcal{F}_{\langle *
+%\rangle}(\cdot)$; and second, the rounding error introduced by the
+%multiplication operation.  We represent these errors as non-deterministic
+%additive noise.
+
+During any given ADC conversion, the continuous signal will be sampled in
+the real domain and transformed by $\mathcal{F}_{\langle A \rangle}
+(x)$. This sampling uses a threshold which is defined by the
+less significant bit ($q_{a}=2^{-F_a}$) 
+of the ADC and some non-linearities of the circuitry.  The overall conversion is
+%
+$$\vec{y}_k=\mathcal{F}_{\langle A \rangle}\left(y(kT_s)\right), \text{ with }  \vec{y}_k \in \left[y(kT_s)-\frac{q_{a}}{2}, y(kT_s)+\frac{q_{a}}{2}\right] \,.$$
+%
+where $t = kT_s$, and $T_s$ is the sampling time and $k$ the current iteration of the loop.
+If we denote the error in the conversion by $\nu_k=y_k-y(t)$, then we may define
+some bounds for it $\nu_k \in [-\frac{q_{a}}{2}, \frac{q_{a}}{2}]$.
+
+We will assume, for the purposes of this analysis, that the domain of the
+ADC is that of the digital controller (i.e, the quantizer includes a digital
+gain added in the code resulting in $\mathbb{R}_{\langle A \rangle}=\mathbb{R}_{\langle C \rangle}$).
+The process of quantization in the DAC is
+similar except that it is calculating $\mathcal{F}_{\langle D\rangle}
+(\mathcal{F}_{\langle C \rangle} (x)) $.  If these domains
+are the same ($\mathbb{R}_{\langle D \rangle}=\mathbb{R}_{\langle C \rangle}$), or if the DAC
+resolution in higher than the ADCs ($\mathbb{R}_{\langle D \rangle}\supseteq\mathbb{R}_{\langle C \rangle}$), then the DAC quantization error is equal
+to zero.  From the above equations we can now define the ADC and DAC
+quantization noises ${\nu_1}_k \in [-\frac{q_a}{2}, \frac{q_a}{2}]$ and
+${\nu_2}_k \in [-\frac{q_d}{2}, \frac{q_d}{2}]$, where given the above assumptions $q_d=q_a=q_c$. 
+This is illustrated in Figure \ref{fig:observersystem2} where $Q_1$ is the quantizer of the ADC
+and $Q_2$ the quantizer for the DAC.  These bounds hold irrespective of
+whether the noise is correlated, hence we may use them to over-approximate
+the noise effect on the state space progression over time.  The
+resulting dynamics are
+%
+\begin{align*}
+%\label{eq:pre_quantization}
+\vec{x}_{k+1} = \mat{A}_d\vec{x}_k+\mat{B}_d({u}_k+{{\nu}_2}_k), \quad u_k = -\mat{K}\vec{x}_{k}+{{\nu}_1}_k, 
+\end{align*}
+%
+which result in the following closed-loop dynamics:
+%
+\begin{align*}
+%\label{eq:quantization}
+\vec{x}_{k+1} &= (\mat{A}_d-\mat{B}_d\mat{K}_d) \vec{x}_k+\mat{B}_d{{\nu}_2}_k +{{\nu}_1}_k \,. 
+\end{align*}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsubsection{Round-off errors}
+\label{sec:roundoff-noise}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Let $q_*=2^{-F_*}$ be the smallest difference
+between two numbers in their corresponding domains.  Assuming that our
+system truncates numbers to the nearest value, this means that the error
+$\delta$ introduced by the function $\mathcal{F}_{\langle * \rangle}$ is
+$\delta_*=\mathcal{F}_{\langle * \rangle}(x)-x \in \left[-\frac{q_*}{2}, 
+\frac{q_*}{2}\right]$.
+We note that in the case of floating point,the
+choice of $F_*$ is taken from the largest multiplication found (e.g.,
+$\norm{\mat{A}}_1\norm{\vec{x}}_1, \text{ where }  \vec{x} \models \phi_\mathit{safety}$,
+where $\phi_\mathit{safety}$ is defined in \ref{eq:safetyspec}). From these
+equations we can define:
+%
+\begin{align*}
+\nu_1 \in \left[-\frac{q_a}{2}, \frac{q_a}{2}\right] \cap  \left[-\frac{q_c}{2}, \frac{q_c}{2}\right],
+\nu_2 \in \left[-\frac{q_d}{2}, \frac{q_d}{2}\right]
+\end{align*}
+
+We may also bound $\nu_2'$ from \eqref{eq:uk} as follows:
+\begin{align*}
+\delta\left(\mat{K}_{\langle C\rangle} \vec{x}_{\langle C\rangle} \right) &\in \left[ -p \frac{q_c}{2},\, p \frac{q_c}{2}\right]\\
+{\vec{\nu_e}}_i &\in \left[ -(p+2) \frac{q_c}{2}, (p+2) \frac{q_c}{2}\right], i \in [1, ...\,,p]\\
+\Rightarrow \nu_2' &\in \left[  -p(\norm{\mat{K}_{\langle C \rangle}}_1+2) \frac{q_c}{2},\, p(\norm{\mat{K}_{\langle C \rangle}}_1+2) \frac{q_c}{2}\right]
+\end{align*}
+Similarly we also find
+\begin{align*}
+\nu_1' &\in \left[  -p(\norm{{\mat{C}_d}_{\langle C \rangle}}_1+2) \frac{q_c}{2},\, p(\norm{{\mat{C}_d}_{\langle C \rangle}}_1+2) \frac{q_c}{2}\right]
+\end{align*}
+The proof derives from $\norm{\mat{K}\vec{x}}_1 \leq \norm{\mat{K}}_1\norm{\vec{x}}_1$.
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%% In most real implementations, the internal state of a plant cannot be
-%% directly measured but rather inferred from its
-%% effect on the output. A plant model that minimises the difference
-%% between the outputs is called an observer and it is a well known
-%% paradigm in the control literature~\cite{astrom1997computer}.
 
@@
 
-%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%\subsection{Stability of an observed system}\label{sec:cof_stability}
-%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%In this work we are interested in asymptotic stability: asymptotic
-%stability is a property that amounts to convergence of the model
-%executions to an equilibrium point, starting from any states in a
-%neighborhood of the point. In the rest of the paper we refer to the
-%stability specification as $\phi_\mathit{stability}$.
-%
-%A discrete-time LTI system (as shown in Sec.~\ref{sec:ssrepresentation})
-%is asymptotically stable if all the roots of its characteristic
-%polynomial (i.e., the eigenvalues of the closed-loop matrix $A_d - B_d
-%K$) are inside the unity circle of the complex plane, i.e., their
-%absolute values are strictly less than one~\cite{astrom1997computer}
-%(this simple sufficient condition can be generalised, however this is
-%not necessary in our work).  We express the stability
-%specification in terms of a check known as
-%\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic
-%formula over the coefficients of the characteristic polynomial.
-%
-%In order to be able to apply Jury's criterion,
-%in the rest of this section, we compute the  
-%characteristic polynomial of the observer model.
-%Note that in this section, we consider that the model is
-%discretized in the time domain, but not in the value domain.
-%This essentially means that
-%${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$, ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d, \mat{L}=\mat{L}_{\langle C \rangle}$ and $\mat{K}=\mat{K}_{\langle C \rangle}$.
-%
-%%Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally
-%
-%%% We will initially assume this for the description of the system and then introduce the errors caused  by misrepresentations.
-%For simplicity of the description, we agregate the noises as follows:
-%$\eta_1=\nu_1+\nu_1'+\nu_t$ and $\eta_2=\nu_2+\nu_2'$,
-%where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations.
-%Then, a controllable and observable system will have the following dynamics:
-%\begin{align}
-%\scriptstyle
-%\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_{k+1}
-%=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}&\mat{B}_d\mat{K}\\ \mat{0}&\mat{A}_d-\mat{L}\mat{C}_d\end{array}\right]
-%\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_k
-%+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
-%+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}\end{array}\right]\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
-%\label{eq:observer_LTI}
-%\end{align}
-%where $\vec{x}_e=\vec{x}-\hat{\vec{x}}$ is the estimation error of the state space by the observer.
-%%, and $k_r$ is a reference gain required by the model.
-%
-%We want the state space dynamics in reachable form ($\mat{A}_c$) and the observer error dynamics in observable form ($\mat{A}_o$), i.e.
-with dynamics whose coefficients are represented solely by those of the characteristic polynomial as follows:
-%\begin{align*}
-%\mat{A}_{c}=\left[
-%\begin{array}{cc}
-%k_{p-1}-a_{p-1}&\begin{array}{cc}\cdots&k_0-a_0\end{array}\\
-%\mat{I}&\mat{0}
-%\end{array}\right]&&
-%\mat{A}_{o}=\left[
-%\begin{array}{ccc}
-%l_{p-1}-a_{p-1}&&\mat{I}\\
-%&&\vdots\\
-%l_0-a_0&&\mat{0}
-%\end{array}\right]
-%\end{align*}
-%where $\sum_{i=0}^p a_iz^i$ is the characteristic polynomial of the plant and $a_p=1$.
-%This is achieved by the following transformation. Let
-%\begin{equation}
-%\left[\begin{array}{c}\vec{x}'\\ \vec{x}_e'\end{array}\right]=
-%\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right] 
-%\left[\begin{array}{c}\vec{x}\\ \vec{x}_e\end{array}\right]
-%\end{equation}
-%We can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
-%\begin{align}
-%\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
-%=& \left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]
-%\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
-%+\mat{B}' \vec{r}_k
-%+\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
-%\nonumber\\
-%\vec{y}_k
-%=& \mat{C}_{t}\vec{x}_k% + \mat{D}_{d}\vec{u}_k
-%\label{eq:observer_LTI_cf}
-%\end{align}
-%{%\setlength{\belowdisplayskip}{0pt}
-%\begin{align*}
-%\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
-%\mat{A}_{o}=&\mat{T}_o\left(\mat{A}_d-\mat{L}\mat{C}_d\right)\mat{T}_o^{-1}\\
-%\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]&
-%\mat{B}_{o}=&\mat{T}_c\mat{B}_d\mat{K}\mat{T}_o^{-1}\\
-%\mat{B}'=&\left[\begin{array}{c}\mat{T}_c\mat{B}_d\mat{k}_r\\\mat{0}\end{array}\right]&
-%\mat{B}_{\eta}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}\end{array}\right]\\
-%\mat{T}_c=&\mat{R}_{cf}\mat{R}^{-1}&
-%\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
-%\mat{C}_t=&\mat{C}_d\mat{T}_c&
-%\mat{L}=& \mat{T}_o^{-1}\left[ \begin{array}{ccc}l_1&\cdots&l_n\end{array}\right]^T
-%\end{align*}
-%}
-%
-%The matrices $\mat{R}$%$\mat{R}=\left[\begin{array}{cccc} \mat{B} & \mat{A}\mat{B} & \cdots & \mat{A}^{p-1}\mat{B} \end{array}\right]$
-%~and $\mat{R}_{cf}$%$\mat{R}_{cf}=\left[\begin{array}{cccc} mat{B}_c & \mat{A}_c\mat{B}_c & \cdots & \mat{A}_c^{p-1}\mat{B}_c \end{array}\right]$
-%~are called reachability matrices (of the system and its reachable canonical form, respectively),
-%and $\mat{W}_o$%$\mat{W}_o=\left[\begin{array}{c} mat{C}\\ \mat{C}\mat{A}\\ \vdots \\ \mat{C}\mat{A}^{p-1} \end{array}\right]$
-%~and $\mat{W}_{of}$%$\mat{W}_{of}=\left[\begin{array}{c} mat{C}_o\\ \mat{C}_o\mat{A}_o\\ \vdots \\ \mat{C}_o\mat{A}_o^{p-1} \end{array}\right]$
-%~are its observability matrices  (of the system and its Observable Canonical Form respectively)~\cite{astrom1997computer}.
-%
-%Careful examination of the above matrices reveals that because the $\mat{A}'$ is
-%upper block diagonal, the spectrum of $\mat{A}'$ is equal to the union of
-%the spectrum of $\mat{A}_{c}$ and $\mat{A}_{o}$, which can be calculated
-%separately.  In other words, the characteristic polynomial of the closed loop is
-%equal to the multiplication of the characteristic polynomials of the controller
-%and the observer when seen independently.
-%%
-%\begin{align*}
-%P(z)=P_K(z)P_L(z)=\left(z^p+\sum_{i=0}^{p-1}{(a_i-k_i)z^{i}}\right) \left(z^p+\sum_{i=0}^{p-1}{(l_i-a_i)z^{i}}\right)
-%\end{align*}
-%
-%We get the stability specification by using Jury's Criterion on these polynomials.
-
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 
-\todo{Start by saying what stability means and that we must have the eigenalues
-  inside the unity circle and that we want to use Jury's criterion.
-  Then, explain what the challenges are for observed systems and how they are overcome. Potentially, the overcoming can be moved to appendix.}
+The ability of a system to remain within a bounded set of states is called stability.  
+There are different types of stability, such as Bounded Input/Bounded Output (BIBO)
+in which the requirement is that given a bounded input the output remains within
+certain limits, or asymptothic stability in which the output is expected to
+converge to a certain value. In our model, stability is directly related to
+convergence, which means it directly relates to the eigenvalues of the dynamics. 
+In this paper we use Jury's criterion~\ref{sec:closed_stability} to verify stability.
 
@@
 the controller and the observer is $\mathbb{R}_{\langle C \rangle}$.
-%% While in the previous section, we assumed that
-%% ${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$ and ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d$ for a given time discretization, in this section
-%% we take into consideration the numerical representation and namely
-%% Thus far we looked at checking stability
-%% %have presented a verification procedure for
-%% of a continuous plant in discretized time domain (i.e., the range of the quatizers is still
-%% $\mathbb{R}$).  The next step we must realize is that the controller and the
-%% observer exist in a digital program, hence their domain is
-%% $\mathbb{R}_{\langle C \rangle}$.
-%
-%% This has two separate effects on the
-%% model.  If we recall Equation~\eqref{eq:observer_LTI}, the matrices of the observer
-%% and the controller are not necessarily those of the plant.  In fact we have
-%% $\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$,
 This means that we have 
@@
 diagonal.  We must therefore compensate for the errors introduced in order
-to find a stable solution.  We can use Gershgoring disks~\cite{van1996matrix} to limit the error
+to find a stable solution.  We can use Gershgorin disks~\cite{van1996matrix} to limit the error
 in the expected eigenvalues.  Let $\delta_o=\max(\norm{{\mat{A}_e}_{i,*}}_1)$
 (\emph{i.e.} the largest row norm in $\mat{A}_e$) be the largest error bound
-for any eigenvalue in $\mat{A}_e$.  Then $\forall i \in [1, n],
+for any eigenvalue in $\mat{A}_e$.  Then $\forall i \in [1, ...\,,n],
 |{\lambda_o}_{i}-\hat{\lambda_o}_{i}|<\delta_o$,where ${\lambda_o}_{i}$ are the
@@
 \begin{equation}
-P_o'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j : \overline{\lambda'}=(1+\delta_o)\overline{\lambda}
+P_o'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_o)\overline{\lambda}
 \end{equation}
@@
 \begin{equation}
-P_r'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j : \overline{\lambda'}=(1+\delta_c)\overline{\lambda}
+P_r'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_c)\overline{\lambda}
 \end{equation}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%% Now that we have established convergence, we may examine the safety
-%% specification of the state space.
 A safety specification gives raise to a requirement on the
@@
 %
-where $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
+where $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe 
+a safe set, within the state-space $\mathbb{R}^p$.
 %
@@
 as they are implicit from equation \ref{eq:observer_LTI_FWL_cf}.
-%
-%% \begin{align}
-%% \phi_\mathit{safety}\equiv& \underline{y} \leq y_k \leq \overline{y}
-%% \iff \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
-%% \label{eq:safetyspec}
-%% \end{align}
-%
-%% For an observed system, the safety specification is
-%% given by a constraint on the output which are considered
-%% safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in
-%% [\underline{y}\ \ \overline{y}]$)
-%% Whilst there are other properties we may
-%% include in the verification, we will solely focus on these for simplicity of
-%% the explanation.  We assume that we do not want saturation in our
+%% We assume that we do not want saturation in our
 %% system, hence the control loop has only one mode.
@@
 %% \end{equation}
-%
-%% We are not limited to the synthesis of digital stabilizing controllers -- a
-%% well known task in the literature on digital control systems -- but target
-%% safety requirements with an overall approach that is sound and automated. 
-%% More specifically, we require that the closed-loop system meets given safety
-%% specifications.  A safety specification gives raise to a requirement on the
-%% states of the model, such that the feedback controller (namely the choice of
-%% the gains matrix~$K$) must ensure that the state never violates the
-%% requirement.  Note that a stable, closed-loop system is not necessarily a
-%% safe system: indeed, the state values may leave the safe part of the state
-%% space while they converge to the equilibrium, which is typical in the case
-%% of oscillatory dynamics.  In~this work, the safety property is expressed as:
-%% %
-%% \begin{align}
-%% \phi_\mathit{safety}\equiv& \underline{y} \leq y_k \leq \overline{y}
-%% \iff \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
-%% \label{eq:safetyspec}
-%% \end{align}
-
-%% where $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe the safe state-space.
 
@@
 which we assume have given bounds:
-%\begin{align}
 $\phi_\mathit{input}\equiv \underline{u} \leq u_k \leq \overline{u}$
-%\label{eq:inputspec}
-%\end{align}
 which comes from physical restrictions in the energy of the system, and
-%\begin{align}
 $\phi_\mathit{init}\equiv \mat{G}' \vec{x}_0 \leq \vec{h}'$,
 where $\mat{G}'$ and $\vec{h}'$ describe the initial state-space.
-%\label{eq:initspec}
-%\end{align}
 
@@
 
+%The second step is evaluating the progression of the system over time in order to calculate $\vec{x}_k$ to validte against this specification.
+For this step we require an initial set from which the system progresses.
+Obviously, this set $\vec{x}_0$ must satisfy the specification, otherwise the system will be unsafe to begin with.
+%We will accept a specification in the form $\mat{E}\mat{T}\vec{x}_0<\mat{f}$. The presence of $\mat{T}$ is because this will typically be given in the original state-space.
+%Accelerating \eqref{eq:observer_LTI_cf}, we obtain:
+%\begin{align}
+%\label{eq:acc_observer_LTI_cf}
+%\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_k
+%=&\mat{A}_t^k
+%\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_0
+%+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tp} \vec{r}_i
+%+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right] :
+% \left [\begin{array}{cc}\mat{E}\mat{T}&\mat{0}\end{array}\right] \left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_0<\mat{f}
+%\end{align}
+%which would still require us to verify the system for every $k$ up to infinity. Instead we will use abstract acceleration~\cite{}, which translates the formula into
+%\begin{align}
+%\label{eq:aa_observer_LTI_cf}
+%\hat{X}^\#
+%=&\mathcal{A}_t X_0+\mathcal{B}_{tp} R + \mathcal{B}_{tn} N\\
+%X_0 =&\left \{ \left[\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right] :
+% \left [\begin{array}{cc}\mat{E}\mat{T}&\mat{0}\end{array}\right] \left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_0<\mat{f} \right\}\nonumber\\
+% R =&\{r \mid \mat{E}_r < \vec{f}_r \}\nonumber\\
+% N=&\left \{ \left[\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right] \mid \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] \wedge \nu_2 \in \left[-\frac{q2}{2}, \frac{q2}{2}\right]  \right \}\nonumber
+%\end{align}
+%where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A}^k, \mathcal{B}_{tp}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tp}, \mathcal{B}_{tn}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tn}$ are abstract matrices for the system in \eqref{eq:observer_LTI_cf}.
+It is worth noting that $r$ is a non-deterministic parametric input (\emph{ie} $\forall k>0, r_{k+1} =r_k$) whereas the set N is composed of non-deterministic variable inputs.
+
 %-------------------------------
@@
 \begin{theorem}
-Given a set of eigenvalues for a discrete time model of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1, n]$, the settling time of the system is upperbounded by
+Given a set of eigenvalues for a discrete time model of an $p^{th}$ order system $\lambda_i =e^{\omega_i}, i \in [1, ...\,,p]$, the settling time of the system is upper-bounded by
 \begin{equation}
-t_s<-log_{\overline{\lambda}}({p_s}) : \overline{\lambda} = \max(|\lambda_i|) \wedge \overline{\lambda}<1,\ \forall i \in [1, n]
+t_s<-log_{\overline{\lambda}}({P_s}), \text{ where }  \overline{\lambda} = \max(|\lambda_i|) \text{ and } \overline{\lambda}<1,\ \forall i \in [1, ...\,,p]
 \label{eq:set_time}
 \end{equation}
-where $0\leq p_s \leq 1$ is the desired percentage of the target within which the output must remain after $t_s$.
+where $0\leq P_s \leq 1$ is the desired percentage of the target within which the output must remain after $t_s$.
 \end{theorem}
-%\begin{proof}
-%In a SISO system, there are two values that typically define the
-%response-time of the system (using a step response).
-%%
-%\begin{enumerate}
-%\item The \emph{rise time} is defined as the time it takes the output to reach a percentage (eg $90\%$) of the target value given a step chnage in the input.
-%\item The \emph{settling time} is defined as the time it takes the output to stabilize within a margin of the target value (eg $10\%$).
-%\end{enumerate} 
-%%
-%In the case of first and second order systems, the decay is governed by the equations 
-%%
-%\begin{align*}
-%&y_{decay}=
-%&\left\{
-%\begin{array}{cc}
-%e^{-|\omega| t}& 1^{st} order\\
-%e^{\zeta |\omega| t}\left(\frac{\sin\left(|\omega| t\sqrt{1-\zeta^2}+\sin^{-1}\sqrt{1-\zeta^2}\right)}{\sqrt{1-\zeta^2}} \right)&\zeta<1\\
-%e^{-|\omega| t}-|\omega| t e^{-|\omega| t}&\zeta=1\\
-%\frac{|\omega| e^{-|\omega_2| t}-|\omega_2| e^{-|\omega| t}}{|\omega|-|\omega_2|}&\zeta>1\end{array}\right.
-%\end{align*}
-%where $|\omega|$ and $|\omega_2|$ are the magnitudes of the eigenvalues (roots) of the system and  $\zeta=-\cos(\theta)$ where $\theta$ is the polar angle of the conjugate pair if it exists ($\zeta \geq 1$ if it doesn't).
-%These equations become increasingly complicated for higher order systems.
-However, we note their strong dependency on the magnitude of the eigenvalues, and use this property to define an upperbound on the decay function.
-%All of the above equations will decay faster than $e^{-|\omega| t}$ given $|\omega| < |\omega_2|$, hence we may use this function as our upper bound.
-%
-%Given a closed loop single output LTI system of order $n$ with dynamics
-%\begin{equation}
-%\left\{\begin{array}{c}\vec{x}_k=\mat{A}\vec{x}_{k-1}\\ \vec{y}_k=\mat{C}\vec{x}_k\end{array}\right.
-\Rightarrow \left\{ \begin{array}{c}\vec{x}_k'=\mat{J}\vec{x}_{k-1}'\\ \vec{y}_k=\mat{C}\mat{S}\vec{x}_k'\end{array}\right.
-: \left\{ \begin{array}{c}\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \\ \vec{x}_k'=\mat{S}^{-1}\vec{x}_k\end{array}\right.
-%\label{eq:eigendynamics}
-%\end{equation}
-%%
-%the output decay is a linear combination of the decay of eigenvalues or
-%eigenvalue pairs.  Let $\mat{C}'\in \mathbb{R}^{1 \times n}=\mat{C}\mat{S}$. 
-%Since $\mat{C}'$ is constant, the output $y_k$ is a linear combination of
-%the states $\vec{x}'_k$.  We accelerate equation \eqref{eq:eigendynamics} to
-%obtain
-%%
-%\begin{align}
-%%\vec{x}_k'&=\mat{J}^k\vec{x}_0' \\
-%y_k&=\mat{C}'\mat{J}^k\vec{x}_0 = \sum_{i=0}^p \left( c_i \lambda_i^k + c_{il}\binom{k}{l} \lambda_i^{k-l}\right)\\
-%|y_k|&\leq \sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right||\lambda_i^k|
-%\end{align}
-%%
-%where the second  part of the equation corresponds to the upper diagonal
-%terms of the Jordan blocks.  We also have $|\lambda_i^k|\leq
-%|\overline{\omega}^k|$,hence
-%%
-%\begin{align}
-%|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right|
-%\end{align}
-%%
-%Since we are synthesising the eigenvalues, rather than solve this formula
-%for complex Jordan Shapes, we will restrict our synthesiser to provide
-%solutions with distinct eigenvalues (which is by far the most common case). 
-%Therefore the right hand terms dissappear and we obtain
-%%
-%\begin{align}
-%|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n |c_i|
-%\end{align}
-%
-%Hence the overall decay of the system is always smaller
-%than $d=e^{-|\overline{\omega}| t}$ where $0\leq d\leq 1$ is the remaining
-%percentage of the decay expressed.  Reversing we have
-%$t=-\frac{ln(d)}{|\overline{\omega}|}=-\frac{ln(d)}{ln(\overline{\lambda})}$. 
-%replacing for $p_s$ , $t_s$, and $\overline{\lambda}$ we get equation
-%\eqref{eq:set_time}
-%%
-%\qed
-%\end{proof}
+
+\begin{proof}
+See Appendix~\ref{sec:proofs}
+\end{proof}
 %
@@
 
-%-------------------------------
-\section{Counterexample Guided Inductive Synthesis} 
-\label{ssec:cegis}
-%-------------------------------
-
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{Synthesising dynamics}\label{sec:dynamic_synth}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Using optimization refinement for CEGIS of control systems}\label{sec:cof_synth}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 In this section, we describe our technique for synthesizing safe
@@
 
+We build upon this paradigm to create CEGORS (Counter Example Guided, Optimization
+Refined Synthesis).  The main advantage of this approach, is that by optimizing the
+synthesis results with respect to some objective function, we are able to reduce the
+number of times the loop iterations, thus improving its performance.  Furthermore,
+because later stages of synthesis will use more complex abstractions, the reduction
+is on increasingly expensive formulas and therefore the improvent can be exponential.
 %% In order to synthesize closed-loop digital control systems, we use a program
@@
 
-Our approach is illustrated in Fig.~\ref{fig:CEGARIS}. It relies on the
-construction of an unsound abstract model that approximates the dynamics
-of the cyberphysical system in order to synthesise a candidate controller
-and observer and then verify its behaviour against a sound overapproximation
+Our approach is illustrated in Figure~\ref{fig:CEGORS}. It relies on the
+construction of an unsound abstract model ({\sc ABSTRACT} phase) that approximates the dynamics
+of the cyber-physical system in order to synthesise a candidate controller
+and observer and then verify their behaviour against a sound over-approximation
 of the concrete dynamics of the system for an infinite space over an infinite
@@
 The verifier's abstraction uses a CEGAR loop in order to minimise 
-overapproximation errors and provides counterexamples for both
+over-approximation errors and provides counterexamples for both
 discrete and continuous dynamics to feed a CEGIS loop on the synthesiser
@@
 
-Our abstraction refinement CEGIS loop is similar to CEGIS with counterexample generalization~\cite{david2017program}.
-However, it provides several improvements by exploiting modularity inside the loop.
+Our CEGORS loop is similar to CEGIS with solution generalization~\cite{david2017program}.
 The novelty of our approach relies on the synthesis refinement phase, which
@@
 still be optimised during this phase. 
-The optimization is performed on an objective function which typically depends
+The optimization is performed on an objective function which will typically depend
 on a subset of the properties.  Hence the chosen optimization function depends
-on which properties fail verification. Optimization may also enter its own
-refinement loop, since it is possible for the counterexample to indicate which
-properties need optimizing (i.e. the ones that are failing).
-In our control synthesis problem, verification failures are typically due to
-safety (since stability and response time are maintained in the highest
-abstraction levels).  The optimization function therefore looks to minimize
-the reachspace by making the dynamics as convergent as possible (note that
-this also improves the response time of the system).
-
-We find a controller for a continuous initial set of states and set of inputs,
-over an abstraction of the continuous dynamics \cite{cattaruzza2015unbounded}
-that conforms to witness proofs at specific times.
-Moreover, this approach uses abstraction refinement enabling us to always
-start with a very simple description regardless of the complexity of the
-overall dynamics, and only expand to more complex models when a solution
-cannot be found.
-
-The CEGIS loop for this approach is described next.
+on which properties fail verification. In our case, the minimal abstraction
+used by the synthesiser almost always ensures stability, so our objective function
+focuses on safety, although we manage to do optimizations that
+simultaneously target safety, stability and response time. This is done by
+making the dynamics as convergent as possible while maintaining the
+verification properties that exclude excesively convergent ones.
+
+%dcmt{this should go or be moved}
+%We find a controller for a continuous initial set of states and set of inputs,
+%over an abstraction of the continuous dynamics \cite{cattaruzza2015unbounded}
+%that conforms to witness proofs at specific times.
+%Moreover, this approach uses abstraction refinement enabling us to always
+%start with a very simple description regardless of the complexity of the
+%overall dynamics, and only expand to more complex models when a solution
+%cannot be found.
+
+The CEGORS loop for this approach is described next.
+
+%  The naive approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
+%  synthesizes a controller for an individual initial state
+%and input with a bounded time horizon and, subsequently, it generalizes it to all reachable states,
+%inputs, and time horizons during the verification phase.
+%Essentially, this approach relies on the explicit
+%simulation over a bounded time horizon of individual states that form
+%part of an uncountable space and tries to generalize it for an
+%infinite space over an infinite time horizon.
+%
+%Conversely, in this section, 
+%we  find a controller for a continuous initial set of states and set of inputs, 
+%  over an abstraction of the continuous dynamics that conforms to
+%  witness proofs at specific times. 
+%  Moreover, this approach uses abstraction refinement enabling us to 
+%  always start with a very simple description regardless of the complexity of the overall
+%dynamics, and only expand to more complex models when a solution
+%cannot be found.
+
+%\begin{enumerate}
+%\item Once we have a candidate solution, we perform a safety verification  of the 
+%  progression of the system from $\phi_\mathit{init}$ over time,
+%$x_{k+1} \models \phi_\mathit{safety}$. 
+%  In order to compute the progression of point $x_0$ at iteration $k$,
+%  we accelerate the dynamics of the closed-loop system and obtain:
+%\begin{align}
+%%\label{eq:acc_observer_LTI_cf}
+%x=&(A_d-B_dK)^kx_0
+%+\sum_{i=0}^{k-1} (A_d-B_dK)^i B_{n}(\nu_1+\nu_2+\nu_3), \text{ where }  B_n= [1\ 1 \cdots \ 1 ]^T
+%\end{align}
+%%
+%As this still requires us to verify the system for every $k$ up to infinity,
+%we use abstract acceleration again to obtain the reach tube, i.e., the set
+%of all reachable states at all times given an initial set
+%$\phi_\mathit{init}$:
+%\begin{align}
+%\label{eq:aa_observer_LTI_cf}
+%\hat{X}^\#
+%=&\mathcal{A} X_0 + \mathcal{B}_{n} N\\
+%X_0 =&\left \{x \mid x \models \phi_\mathit{init} \right\}\nonumber
+%\end{align}
+%%
+%where $\mathcal{A}=\bigcup_{k=1}^\infty (A_d-B_dK)t^k,
+%\mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k(A_d-B_dK)^iB_{n}$ are
+%abstract matrices for the closed-loop system~\cite{cattaruzza2015unbounded},
+%whereas the set $N$ is non-deterministically chosen.
+%
+%We next evaluate $\hat{X}^\# \models \phi_\mathit{safety}$.  If the
+%verification holds we have a solution, and exit the loop.  Otherwise, we
+%find a counterexample iteration $k$ and corresponding initial point $x_0$
+%for which the property does not hold, which we use to locally refine the
+%abstraction.  When the abstraction cannot be further refined, we provide
+%them to the {\sc abstract} phase.
+%
+%\end{enumerate}
 
@@
 \item Select a sample time that minimizes the magnitudes of the matrices used in both the
-implementation and the abstraction. This ensures that a small bitvector size is required for
+implementation and the abstraction. This ensures that a small bit vector size is required for
 the synthesis process.
-\item Build the Observer matrices ${\mat{A}_d}_{\langle C \rangle}$, ${\mat{B}_d}_{\langle C \rangle}$
-and ${\mat{C}_d}_{\langle C \rangle}$ using the truncation described in section \ref{sec:numeric_rep}.
-\item Transform the system into Canonical form and add nondeterminism for the errors
-using the techniques described in section \ref{sec:cof_fwl_stability}. The transformation
+\item Build the observer matrices ${\mat{A}_d}_{\langle C \rangle}$, ${\mat{B}_d}_{\langle C \rangle}$
+and ${\mat{C}_d}_{\langle C \rangle}$ using the truncation described in Section~\ref{sec:numeric_rep}.
+\item Transform the system into canonical form and add nondeterminism for the errors
+using the techniques described in Section~\ref{sec:cof_fwl_stability}. The transformation
 matrices will be needed to obtain an FWL compliant controller and observer.
@@
 error ($\mat{A}_e$,$\mat{B}_e$), and response time $\phi_{stability}(P_a,P_l,\overline{\lambda})$
-as described in section \ref{ssec:transientspecification}.
+as described in Section~\ref{sec:transientspecification}.
 \item Calculate the noise sets $\eta_1$ and $\eta_2$ from the equations
-described in sections \ref{sec:delay} and \ref{sec:quantization}.
+described in Section~\ref{sec:FWL_effects}.
 \item Calculate a set of initial bounds on $\mat{K}$, $\phi_\mathit{init}^{K}$,
 based on the input constraints.
-%
-$(\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-\mat{K} x_k)
+$(\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-\mat{K} \vec{x}_k)
 \Rightarrow \phi_\mathit{init}^{K}$.
 These bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space. 
-\item Select an initial width for the bitvectors representing the controller and the plant $\phi_{\langle C \rangle}, \phi_{\langle P \rangle}$. We will increase either precision as needed.
+\item Select an initial width for the bit vectors representing the controller and the plant $\phi_{\langle C \rangle}, \phi_{\langle P \rangle}$. We will increase either precision as needed.
 \end{enumerate}
@@
 controller and the observer.  If one of these results does not satisfy the tighter
-specification, it feeds back to the {\sc Refine Synthesis} phase which uses sensitivity analysis to
-synthesise a refined solution. If the candidate is valid, we feed it to {\sc Discrete Time}. 
-\item {\sc Refine Synthesis} takes $\mat{K},\mat{L} \not \models \phi_{static}$ and synthesises $\mat{K}_{\langle C \rangle} = \mat{K}+\mat{\delta}_K, \mat{L}_{\langle C \rangle}=\mat{L}+\mat{\delta}_L, where \mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \models \phi_{static}$.
-Furthermore we perform optimization based on the violation of the safe-space (if found).
-Given a closed loop controller or observer block ($\mat{A}_c$ or $\mat{A}_o$),
-we look for a constant $c \leq 1$ such that $\mat{B}\mat{K}'=(1-c)\mat{A}_d+c\mat{B}\mat{K} \mid \mat{K}' \models \phi_K$
-(and similarly for $\mat{L}'$.
-If we cannot synthesise a suitable candidate, we signal the {\sc Abstract} phase to refine $\phi_{synth}$ and request {\sc Synthesise} to produce a new candidate.
-Otherwise the refined candidate solution is given back to {\sc Verify Synthesis}.
-%
-\item {\sc Discrete Time} verifies $\phi_{safety}^{\infty}$ using discrete
-time dynamics.  If the verification fails, we report the counterexample to
-{\sc Refine Abstraction} including details of initial states and
-iterations that failed the specification.  
-\item {\sc Refine Abstraction} changes $\phi_{safety}$ to encompass any arising conterexample. 
-This can be done by increasing the time horizon $k$ for the safety specification of the violating initial condition and input.
+specification, it feeds back to the {\sc Optimise} phase which optimises
+an objective functiion in order to minimise the magnitude of the error in the verification.
+If the candidate is valid, we feed it to {\sc Discrete Time}.
+
+\item {\sc Optimise} 
+% starts by taking $\mat{K},\mat{L} \not \models \phi_{static}$
+% and synthesises $\mat{K}_{\langle C \rangle} = \mat{K}+\mat{\delta}_K, \mat{L}_{\langle C \rangle}=\mat{L}+\mat{\delta}_L$,
+% where $\mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \models \phi_{static}$.  
+% If $\mat{K},\mat{L} \models \phi_{static}$ but we have a counterexample for $\mat{K},\mat{L} \models \phi$,
+% then we proceed to optimise the controller.
+
+Our optimization is iterative, following two stages.  The first stage seeks to
+make the dynamics as convergent as possible, since convergent dynamics are
+less likely to stray outside of the safe region (we say less likely because the
+change in the eigenvectors changes the shape of the space and may cause some 
+trajectories to go further).  In this case, we take the largest eigenvalue and
+reduce it by a factor (smaller than .5) that still satisfies $\phi_{static}$.  The
+resulting observer controller is then verified against the full specification and
+the maximum deviation from the safe region is measured (maximum distance from
+the discovered reach set to the safety region, measured perpendicularly to any
+of the faces of the safe region). 
+While this number is monotonically decreasing we continue to iterate until
+it reaches a negative value (i.e. safe). If the number increases, we change
+our objective function to the second stage.
+
+In the second stage, at each iteration we take the complex eigenvalue
+with the largest phase (largest angle in the complex space), and reduce its
+imaginary component while maintaining the specification $\phi_{static}$.
+The process ends when no imaginary part can be further reduced.
+The resulting closed loop form converges faster than the original and may have a
+smaller rotation, which facilitates meeting the safety specification (we note
+that real convergent eigenvalues are trivially safe).
+
+If we cannot synthesise a suitable candidate using optimisation, we signal the
+{\sc Abstract} phase to refine $\phi_{synth}$ and request {\sc Synthesise} to
+produce a new candidate.  Otherwise the refined candidate solution is given back
+to {\sc Verify Synthesis}.
+%
+\item {\sc Discrete Time} verifies $\phi_{safety}^{\infty}$ (unbounded time)
+using discrete time dynamics.  If the verification fails, we report the
+counterexample to {\sc Refine Abstraction} including details of initial states
+and iterations that failed the specification.  
+\item {\sc Refine Abstraction} changes $\phi_{safety}$ to encompass any arising
+counterexample.  This can be done by increasing the time horizon $k$ for the
+safety specification of the violating initial condition and input.
 It also modifies $\phi_{static}$ to account for the counterexample.
-If the magnitude of the violation is small, {\sc Refine Synthesis} may find a new candidate, otherwise it will feed through to {\sc Abstract}.
+If the magnitude of the violation is small, {\sc Optimise} may find a new
+candidate, otherwise it will feed through to {\sc Abstract}.
 %
@@
 
-\begin{figure*}[htb]
+\begin{figure}[t!]
 {
@@
  \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=1cm] {
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.8cm, column sep=1.5cm] {
   \coordinate (aux1);\&\&
@@
   \coordinate (aux3) at ([xshift=3cm]aux2); \\
-  \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (model1) {{\sc 1. Abstract}};
-  \&\& complexnode/.pic={ 
+  \node[minimum width=2.2cm, minimum height=0.8cm, fill=orange!20] (model1) {{\sc 1. Abstract}};
+  \& complexnode/.pic={ 
      \node[rectangle,draw,dotted,
-	minimum width=8cm,
+	minimum width=9cm,
 	minimum height=1cm,
@@
 	label={\sc Model~~~~~~~~~~~},] (model) {};
-     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (model2) at ([xshift=-3cm]model.center) {{\sc 4. Refine}\\{\sc Synthesis}};
-     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (model3) at ([xshift=0cm]model.center) {{\sc 6. Refine}\\{\sc Abstraction}};
-     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (model4) at ([xshift=3cm]model.center) {{\sc 8. Sample}};
+     \node[minimum width=2.2cm, minimum height=0.8cm, fill=orange!20] (model2) at ([xshift=-3cm]model.center) {{\sc 4. Optimise}};
+     \node[minimum width=2.2cm, minimum height=0.8cm, fill=orange!20] (model3) at ([xshift=0cm]model.center) {{\sc 6. Refine}\\{\sc Abstraction}};
+     \node[minimum width=2.2cm, minimum height=0.8cm, fill=orange!20] (model4) at ([xshift=3cm]model.center) {{\sc 8. Sample}};
    } ;\\
-   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc 2.Synthesize}};
-   \&\&
+   \node[minimum width=2.2cm, minimum height=0.8cm, fill=purple!20] (synth) {{\sc 2. Synthesize}};
+   \&
    complexnode/.pic={ 
      \node[rectangle,draw,dotted,
-	minimum width=8cm,
+	minimum width=9cm,
 	minimum height=1cm,
@@
 	label={\sc Verify~~~~~~~~~~~},] (verif) {};
-     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-3cm]verif.center) {{\sc 3. Verify}\\{\sc Synthesis}};
-     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=0cm]verif.center) {{\sc 5. Discrete}\\{\sc Time}};
-     \node[minimum width=2cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=3cm]verif.center) {{\sc 7. Continuous}\\{\sc Time}};
+     \node[minimum width=2.2cm, minimum height=0.8cm, fill=blue!20] (verif1) at ([xshift=-3cm]verif.center) {{\sc 3. Verify}\\{\sc Synthesis}};
+     \node[minimum width=2.2cm, minimum height=0.8cm, fill=blue!20] (verif2) at ([xshift=0cm]verif.center) {{\sc 5. Discrete}\\{\sc Time}};
+     \node[minimum width=2.2cm, minimum height=0.8cm, fill=blue!20] (verif3) at ([xshift=3cm]verif.center) {{\sc 7. Continuous}\\{\sc Time}};
    } 
-   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
+   \& \coordinate (done);\\
    \& \\
-   \node[minimum height=0cm] (gp) {{\sf Program}\\{\sf Search}};
-   \&\&
+   \node[minimum width=2.2cm, minimum height=0.8cm] (gp) {{\sf Program}\\{\sf Search}};
+   \&
    complexnode/.pic={ 
      \coordinate (aux);
-   \node (bmc) at ([xshift=-3cm]aux.center) {\sf Eigensolver};
-   \node (fp)  at ([xshift=0cm]aux.center) {\sf Reachability \\ \sf Analysis};
-   \node (sv)  at ([xshift=3cm]aux.center) {\sf Reachability \\ \sf Analysis};
+   \node[minimum width=2.2cm, minimum height=0.8cm] (bmc) at ([xshift=-3cm]aux.center) {\sf Eigensolver};
+   \node[minimum width=2.2cm, minimum height=0.8cm] (fp)  at ([xshift=0cm]aux.center) {\sf Reachability \\ \sf Analysis};
+   \node[minimum width=2.2cm, minimum height=0.8cm] (sv)  at ([xshift=3cm]aux.center) {\sf Reachability \\ \sf Analysis};
    }   
@@
     ([xshift=-5em]bmc.north) edge node[align=center]  {PASS/\\C-ex} ([xshift=-5em]verif1.south)
-    (verif) edge node {PASS} (done)
+    (verif3.east) edge node {PASS} (done)
     ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
@@
 }
-\caption{CEGIS with Abstraction Refinement}
-\label{fig:CEGARIS}
-\end{figure*}
+\caption{CEGIS with Optimization Refinement. Orange boxes (light) are modelling
+stages, blue boxes (dark) are verification stages, and the red box is the synthesis stage.}
+\label{fig:CEGORS}
+\end{figure}
 
@@
 
-\jrronly{
-%-------------------------------
-\subsection{Description of the benchmarks}
-\label{exp:benchmarks}
-%-------------------------------
-}
-%\textcolor{red}{Iury: can you please describe the benchmarks?}
-
 The benchmark suite employed to evaluate the proposed technique is 
-composed by 18 MIMO models extracted from the literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15,maglev,converters}. 
+composed by 7 SISO models extracted from the literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15,maglev,converters}.
+In order to obtain statistically relevant results, we have taken these models
+and modified each possible combination of their parameters by a 10\% tolerance,
+thus creating hundreds of different benchmarks from this base.
 In the verification module, we have used the tool Axelerator~\cite{} .
-
-\jrronly{
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{DC Motor}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-DC Motor benchmark describes the velocity dynamics of a basic 
-brushed direct current electrical machine.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Automotive Cruise System}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-An automotive cruise control system is used to keep constant the speed 
-of an automobile  tracking a desired speed reference, compensating 
-disturbances and uncertainties related to relief and terrain.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Pendulum}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-A pendulum is system composed by a swinging point mass suspended from 
-a frictionless pivot through a negligible mass rod.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Inverted Pendulum}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-An inverted pendulum is a system similar to the pendulum but the point 
-mass must be equilibrated above the pivot point that is mounted on an 
-one degree of freedom cart that moves over a track through a DC motor.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Magnetic Suspension}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Magnetic suspension benchmark corresponds to the discrete model of a 
-simple eletromagnet-ball system where a steel ball is levitated in air 
-by the action of an electromagnetic force generated by an electromagnet.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Magnetic Pointer}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Magnetic pointer is a pointer, that is usually employed in analogue 
-gauges and indicators, whose angular position dynamics is controlled 
-by a magnetic field.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{1/4 Car Suspension}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The 1/4 Car Suspension benchmark corresponds to the model of a single 
-wheel suspension system of a car, {\it i.e.} the relative motion dynamics 
-of a mass springer damp model that connects the car to one of its wheels.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Computer Tape Driver}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Computer Tape Drive is a computer storage device used to read and write 
-data on magnetic tapes.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Acrobot - Robot Manipulator}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The Acrobot benchmark corresponds to the model of an two-link 
-underactuated robot manipulator, linearized by partial 
-feedback linearization~\cite{acrobot}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{High-order Systems from Chen et. al.}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-These benchmarks corresponds to a series of high-order system model 
-generally used as example for order reduction techniques~\cite{CHEN1979389}.
- In this work, these benchmarks are used for evaluate the proposed control
- synthesis technique under critical conditions, {\it i.e.} with a greater 
- number of parameters to be considered.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Continuous Stirred Tank Reactor}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This benchmark describes a linear model for PH dynamics of a PH 
-neutralization process of an aqueous solution of sodium acetate with 
-hydrochloric acid in a continuous flow stirred-tank reactor.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Flexible Beam}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-A Flexible Beam is a plant usually employed in vibration studies. It is 
-composed by a flexible metallic structure with piezoceramic actuators 
-and sensors.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Helicopter Longitudinal Motion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The Helicopter Longitudinal Motion benchmark describes the dynamics of 
-transitional motion with respect to a longitudinal plane and the 
-rotational motion around the longitudinal axis.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{USCG cutter Tampa Heading Angle}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The USCG cutter Tampa Heading Angle describes the heading angle 
-dynamics of a Coast Guard cutter.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Voltage regulator}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The voltage regulator benchmark~\cite{KOKOTOVIC198023} consists 
-in a linear model of a synchronous machine connected to an 
-infinite bus.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Guidance Control System}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The Guidance Control System benchmark is another high-order system 
-model used by Chen et al.~\cite{CHEN1979389}  in order reduction 
-techniques. Guidance systems are used to determine the path of an 
-autonomous vehicle movement.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Satellite Attitude Control System}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This benchmark describes the dynamics of a satellite attitude, 
-{\it i.e.} the orientation angles. An attitude control system must 
-maintain the desired orientation of satellite with respect to an 
-inertial frame during all the excursion.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph*{Springer-mass damper}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The springer-mass damper systems are classic models for a lot of 
-mechanical systems dynamics. This benchmark describes a mass that is 
-fixed to a node through a springer and moves under the action of a 
-input force, damping, and elastic force.
-
-}
 
@@
 %-------------------------------
-The technique was applied  to the benchmarks and the results can be seen in Table \ref{tab:results}. 
 \begin{table}
 \centering
-%
-\begin{tabular}{| r | l | c | c | c | r | r | r |}
+\footnotesize
+%
+\begin{tabular}{| r | l | c | c | r | r | r | r | r | r | r |}
 %
 \hline
-\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{order} & \multicolumn{1}{|c|}{count} & \multicolumn{1}{|c|}{$\mat{K}$} & \multicolumn{3}{|c|}{$\mat{K}+\mat{L}+T_s$} \\
-   &                                 & & & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{Max}\\\hline
-1  & DC Motor          & 2 & 433 & 2.1\,s& 3.5\,s &   6.9\,s &   20.7\,s\\
-2  & Helicopter        & 3  & 54 & 1.4\,s& 8.8\,s  &   33.5\,s & 160.3\,s\\
-3  & Inverted Pendulum & 4 & 1 &   0.6\,s& 16,24  &  308.4\,s &  308.4\,s\\
-4  & Magnetic Pointer  & 2  & 246 & 44.1\,s& 7.7\,s  &  36.9\,s &  184.6\,s \\
-%5  & Magnetic Suspension & 2 & 1 & 0.6\,s& 16,24  &   0\,s &   0\,s\\
-5  & Pendulum          & 2 & 432 & 14.0\,s& 3.4\,s  &   26.9\,s &   156.8\,s\\
-6  & Suspension        & 2 & 1 & 73.7\,s& 16,24  &   1316.2\,s &   1316.2\,s\\
-7  & Tape Driver       & 3 & 488 & 68.3\,s& 12.4\,s  &   37.2\,s &   185.3\,s\\
-%9 & Satellite          & 2 & 1 &   0.7\,s& - &  - &  -\\ %unobservable
-   & Total                 &   & 1645 & & 3.4\,s & 20.1\,s & 1316.2 \,s\\
+\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{order} & \multicolumn{1}{|c|}{count} & \multicolumn{2}{|c|}{CEGIS ($\mat{K}$)} & \multicolumn{5}{|c|}{CEGORS($\mat{K}+\mat{L}+T_s$)} \\
+   &                                 & & & \multicolumn{1}{|c|}{-AR1} & \multicolumn{1}{|c|}{-OR} & \multicolumn{1}{|c|}{-AR2} & \multicolumn{1}{|c|}{-OR} & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{Max}\\\hline
+1  & DC Motor          & 2 & 10 & 9.5\,s & 2.1\,s& 1.9\,s& 3.4\,s& 1.2\,s &   3.1\,s &   14.1\,s\\
+2  & Helicopter        & 3  & 10 & \xmark & 1.4\,s& \xmark & \xmark & 6.7\,s  &   18.9\,s & \xmark\\
+3  & Inverted Pendulum & 4 & 10 &   9.7\,s &   0.6\,s& \xmark &112.6\,s& 12.0\,s  &  18.1\,s &  414.0\,s\\
+4  & Magnetic Pointer  & 2  & 10 & \xmark & 44.1\,s& \xmark & \xmark& 4.6\,s  &  39.0\,s &  \xmark \\
+%5 & Magnetic Suspension          & 2 & 1 & 12.2\,s& 0.6\,s & & & N/A  &   N/A &   N/A\\
+5  & Pendulum          & 2 & 10 & 14.0\,s & 0.6\,s& 2.0\,s & 1.5\,s &1.2\,s  &   1.5\,s &   4.3\,s\\
+6  & Suspension        & 4 & 10 & 73.7\,s& 48.3\,s & \xmark & 110.2\,s &24.0\,s  &   46.1\,s &  557.9\,s\\
+7  & Tape Driver       & 3 & 10 & 10.1\,s& 12.4\,s& 140.3\,s &10.5\,s &2.6\,s  &   10.5\,s &   104.6\,s\\
+%9 & Satellite          & 2 & 1 & 9.4\,s& 0.7\,s & & & N/A  &   N/A &   N/A\\
+%   & Total                 &   & 2002 & & & & & 1.2\,s & 16.1\,s & 876.8\,s\\
 \hline
@@
 \vspace{0.05in}
-\caption{Experimental results\label{tab:results}}
+\caption{\label{tab:cegis_results}
+Experimental results.
+All times are median (except for Min and Max).
+\xmark~indicates failure to find a controller (in the median case it means that more than half of the times we failed to find a controller), either due to timeout or insufficient numeric precision (bitvectors are limited to 64bits).
+-AR1 is standard CEGIS, -AR2 uses Solution Generalization but no refinement.
+-OR means Abstraction Refinement but no optimization refinement.}
 \end{table}
+
+For the majority of our benchmarks, we observe that our approach is
+significantly faster than using standard CEGIS. We further note the cases where
+standard CEGIS times out, which represent an improvement of several orders of
+magnitude for our optimization approach.  The magnitude of the improvement is 
+largely dependent on the shape of the problem. 
+%When the tighter restriction isdependent on the optimization parameters the overall speed is
+
+The smaller benchmarks (order=2) tend to show little or no improvement when we
+apply CEGORS.  The reason is that for these benchmarks the synthesis time using
+Solution Generalization is already small, and the overhead of the abstraction is
+often equal or larger than the gain obtained.
+
+More interesting cases appear when we increase the order, showing initially that
+benchmarks that timed-out with AR1 (approx 20mins) are now running in under 2
+minutes using AR2. This is the result of removing several multiplications which are
+known to be difficult for SAT solvers.  Furthermore, when we introduce Optimization
+Refinement there is a further improvement up to an order of magnitude.  This second
+improvement is due to the elimination of counterexamples that would have been
+created without the refinement. Since further synthesis require increasingly
+complex models which are linear in the number of multiplications, eliminating 
+these results in large improvements.  In cases when the initial candidate is
+suitable, we gain nothing with the refinement and therefore find similar times.
+Improvements using this approach will therefore be observed in higher order
+systems or when the safety specification is tight and the original loop would
+require multiple counterexamples.
+
+The median run-times for our benchmark sets are under a minute, and the
+maximum observed synthesis time was under 10 minutes for a $4^{th}$ order system
+($8^{th}$ order considering the observer).  We consider these times
+short enough to be of practical use to control engineers.
+
+There are cases for which the system fails to find a controller.  We use a
+relatively short timeout, so it is possible longer timeouts would result in a
+valid solution. However, as stated before, the solution is sound but incomplete,
+so it is impossible to tell if a solution exists in these cases.
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Control Theory} \label{sec:control_theory}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Since our models are being applied to linear control systems, and in particular to feedback systems with observers,
-we provide a summary of the important elements using control theory for their transfromations.
-
-%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%\subsection{Static Output Feedback and Pole Placement} \label{sec:pole_place}
-%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%
-%\begin{figure*}[htb]
-%\centering
-%
-%\tikzset{add/.style n args={4}{
-%    minimum width=6mm,
-%    path picture={
-%        \draw[circle] 
-%            (path picture bounding box.south east) -- (path picture bounding box.north west)
-%            (path picture bounding box.south west) -- (path picture bounding box.north east);
-%        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
-%        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
-%        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
-%        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
-%        }
-%    }
-% }
-%
-%\resizebox{1.0\textwidth}{!}{
-% \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
-%     semithick, initial text=, ampersand replacement=\&,]
-%
-%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
-%    \node[draw=none] (r) {$R(z)$};
-%%   \& \coordinate (aux0);
-%   \& \node[circle,add={-}{+}{}{}] (circle) {};
-%   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
-%   \& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm,
-%        label=\textbf{Controller}] (cz) {{\sc C(z)}};
-%   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
-%     
-%   \& complexnode/.pic={ 
-%      \node[rectangle,draw,
-%	minimum width=3cm,
-%	minimum height=1.6cm,
-%	label=\textbf{DAC},] (dac) {};
-%     \node[circle,add={}{+}{+}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
-%     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
-%     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
-%     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}   
-%   \& \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm,
-%        label=\textbf{Plant}] (gs) {{\sc $G(s)$}};
-%   \node[draw=none] (ud) at ([xshift=-2cm,yshift=.15cm]gs)  {$U(s)$};
-%   \node[draw=none] (y) at ([xshift=2cm,yshift=.15cm]gs)  {$Y(s)$};
-%   \& complexnode/.pic={ 
-%     \node[rectangle,draw,
-%	minimum width=4cm,
-%	minimum height=1.6cm,
-%	label=\textbf{ADC},] (adc) {};
-%   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
-%   \coordinate (switch1) at ([xshift=-1cm]adc.center);
-%   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
-%   \node[circle,add={}{+}{+}{},fill=gray!20] (q1) at ([xshift=1cm]adc.center) {};} 
-%     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
-%   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
-%   \& \coordinate (aux1);
-%   \& \node[draw=none] (yz) {$Y(z)$};\\
-%   \& \coordinate (aux3); 
-%   \&
-%   \&
-%   \& 
-%   \& 
-%   \& \coordinate (aux2);\\
-%  };
-%
-%
-%  \path[->] (v1) edge (q1.north);
-%  \path[->] (v2) edge (q2.north);
-%  \path[->] (r) edge (circle.west);
-%  \path[->] (aux1) edge (yz);
-%  \path  
-%   (circle.east) edge (cz)
-%   (cz.east) edge (q2.west)
-%   (q2.east) edge (zoh.west)
-%   (zoh.east) edge (gs.west)
-%   (switch2) edge (q1.west)
-%   (q1.east) edge (aux1.west)
-%   (gs.east) edge (switch1.west)
-%   (aux1.south) edge (aux2.north)
-%   (aux2.west) edge (aux3.east); 
-%  \path[->]  (aux3.north) edge (circle.south);
-% \end{tikzpicture}
-%}
-% \caption{Closed-loop digital control system\label{fig:sampledsystem}}
-%\end{figure*}
-%
-%Given an unstable plant with divergent dynamics, the problem of stabilizing the output is to find a controller that
-%results in convergent closed loop dynamics. The term Static Output Feedback relates to the desired effect of
-%having a static output given a fixed reference signal.
-%In modern embedded systems, said controller is a digital program, which means that the closed loop dynamics are
-%subject to time and space discretization as described in sections \ref{sec:continuous_LTI} and \ref{sec:numeric_rep}.
-%In general terms, the controller is known to have discrete dynamics, whereas the plant has to be discretised based 
-%on the sample and hold characteristics. The ADC/DAC converters are considered to introduce a quantization noise on
-%the system as shown in Figure~\ref{fig:sampledsystem}.
-%Let the quantizer $Q1$ be the source of a non-deterministic noise $\nu_{1}$ and $Q2$ be the source of a non-deterministic noise
-%$\nu_{2}$.  The following equation models the system, encompassing the discretization of the plant:
-%%
-%\begin{equation}
-%Y(z)=C(z)G(z)(R(z)-Y(z))+\nu_{1}(z)+\nu_{2}(z)C(z)G(z),
-%\end{equation}
-%%
-%The above can be rewritten as follows:
-%%
-%\begin{equation}
-%\label{eq:outputfunctions}
-%Y(z)=H_1(z)R(z)+H_2(z)\nu_{1}(z)+H_3(z)\nu_{2}(z),
-%\end{equation}
-%%
-%where
-%%
-%\begin{align}
-%H_1(z)=\frac{C(z)G(z)}{1+C(z)G(z)},\\
-%H_2(z)=\frac{1}{1+C(z)G(z)},\\
-%H_3(z)=\frac{G(z)}{1+C(z)G(z)}.
-%\end{align}
-%%
-%
-%\begin{assumption}
-%\label{whitenoise}
-%%
-%The quantization noises $\nu_{1}$ (from $Q1$) and $\nu_{2}$ (from $Q2$) are
-%uncorrelated white noises and their amplitudes are always bounded by the
-%half of quantization step~\cite{astrom1997computer}, i.e., $\vert \nu_{1}
-%\vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$,
-%where $q_{1}$ and $q_{2}$, respectively, are the quantization steps of ADC
-%and DAC.
-%% 
-%\end{assumption}
-%
-%It is known that a discrete-time linear system is said to be Bounded-Input and Bounded-Output
-%(BIBO) stable if and only if every pole of its transfer function lies inside
-%the unit circle \cite{Astrom08}.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following
-%proposition states necessary conditions for BIBO stability of the closed-loop system
-%in Figure~\ref{fig:sampledsystem}, since the exogenous signals $R(z)$,
-%$\nu_{1}$, and $\nu_{2}$ are bounded. Hence, our close loop system is stable if the poles in
-%$H_1(z) , H_2(z) $ and $H_3(z)$ are inside the unit circle. Since all three transfer functions share the same poles,
-%we only need to look at the roots of the polynomial
-%$$C_n(z)G_n(z)+C_d(z)G_d(z) : C(z)=\frac{C_n(z)}{C_d(z)} \wedge G(z)=\frac{G_n(z)}{G_d(z)}$$
-%Any controller that ensures these roots lie within the unit circle is a stabilizing controller for the system.
-%
-%This same analysis can be applied to MIMO systems where there is a transfer functions of the system
-%for each combination of input-output. Rather than examine the transfer functions of these systems, we will first
-%look at minimal descrptions of the state space dynamics that will help us extract them with little extra effort whilst 
-%providing us with tools to analyse other properties.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Controllable Canonical Form} \label{sec:reachable}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Let us have a discrete time SISO system with an $p^{th},q^{th} \mid p\geq q$ order model
+\subsection{Discretization of linear time invariant dynamical systems}\label{sec:continuous_LTI}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Discretization of a continuous dynamical system turns the ODE into a difference
+equation, assuming zero-order hold for the input $\vec{u}$ (i.e. the value $u(t)$
+ is fixed for the integration period), %and continuous integration for the noise $\vec{w}$, 
+into
+\begin{align}
+\label{eq:discretization}
+\vec{x}_{k+1} &= \mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\% + \vec{w}_k\\
+y_k &= \mat{C}_d \vec{x}_ k + \mat{D}_d \vec{u}_ k 
+\end{align}
+%with covariance for $\vec{w}_k$, $N ( 0 , Q_d )$
+where
+\begin{align}
+\label{eq:discretize}
+\mat{A}_d &= e^{\mat{A} T_s} \\%= \mathcal{L}^{-1} { ( s \mat{I} - \mat{A} )^{-1} }_{t = T_s}\\
+\mat{B}_d &= \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B} = \mat{A}^{-1} ( \mat{A}_d - \mat{I} ) \mat{B}\\
+\mat{C}_d &= \mat{C}\\
+\mat{D}_d &= \mat{D} %\\
+%Q_d &= \int_{t = 0}^{T_s} e^{\mat{A} t} Q e^{\mat{A}^T t} dt
+\end{align}
+and $T_s$ is the sample time. Then
+\begin{align*}
+\forall k,  \vec{x}(kT_s)=\vec{x}_k \text{ and } \vec{y}(kT_s) = \vec{y}_k
+\end{align*}
+%Let $g_d(k)=\mathcal{G}(t,g(t),T)$ be a function that performs the discretization described above, where $g(t)$
+%represents the continuous dynamics and $g_d(k)$ the corresponding discrete dynamics. 
+%Let $G(s)=\mathcal{L}(g(t))$ and $G_d(z)=\mathcal{Z}(g_d(k))$ be the corresponding Laplace and Z-transforms
+%of $g(t)$ and $g_d(k)$. Given this relation, we have 
+%$$G_d(z)=G(z)|_{z=e^{sT}} \text{ where } g_d(k)=\mathcal{G}(t,g(t),T) \wedge T < \frac{1}{.5f_s}$$
+%Where $.5f_s$ is the Nyquist frequency of $g(t)$. This last restriction is introduced to avoid the effects of aliasing
+%which could cause non-existent `phantom' poles to appear otherwise at fractions of the true frequency they represent. 
+The eigenvalues of $\vec{A}_d$ %corresponding to the poles of $G_d(z)$,
+and those of $\vec{A}$ %corresponding to the poles of $G(s)$
+are related as follows:
+$\hat{\lambda}_i=e^{\lambda_iT_s} \text{ where } \hat{\lambda}_i \in \sigma(\vec{A}_d) \text{ and } \lambda_i \in \sigma(\vec{A})$
+where $\sigma(\cdot)$ is the spectrum of a matrix.
+The following remark is worth mentioning regarding the above.
+\begin{remark}
+The witnessed maximum amplitude of the discrete signals $\vec{x}_k,\vec{y}_k$
+may be smaller to that of $\vec{x}(t),\vec{y}(t)$ due to synchronism at
+fraction-frequency sampling. This means that safety verification of the state space
+must account for this condition.
+\end{remark}
+Imagine that a signal $\vec{x}(t)=sin\left({\omega_f t}\right)$. If we sample
+this signal at intervals $T_s=\frac{\pi}{\omega_f}$ starting at $t=0$, then all
+measured samples will be $0$.  For this reason, systems must be sampled at
+intervals smaller than the maximum composing frequency of the source signal
+$T_s<\frac{\pi}{\omega_max}$.  This is the so called Nyquist Criterion~\cite{Astrom08}.  
+The maximum amplitude of the original signal can be upper bounded from the
+observed values using the inverse cosine of the sampling function.
+Since equation \eqref{eq:discretization} models \eqref{eq:dynamical}, we may use the semantics defined in Section
+\ref{sec:model_semantics} to analyse continuous dynamical systems.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{Numeric representations and soundness} \label{sec:numeric_rep}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+In embedded software programs interacting and/or simulating physical plants it
+is of great importance to understand the effects of the chosen numeric
+representation for the continuous state-space. 
+These representations are almost invariably approximations to the original which
+are assumed to be precise enough as to not cause any trouble, but it is precisely
+this assumption that often results in the most difficult and dangerous errors.
+There are generally speaking two paradigms for representing numbers in programs:
+fixed and variable precision numbers.  We refer to both of these as finite word
+length representations (FWL).  In fact, these subdivide into multiple data types
+such as integer bit-vectors, fixed or floating point numbers and rationals). In 
+this section we will be discussing fixed and floating point numbers.
+On one hand, we have variable word length types which will attempt to use as
+much memory as needed to precisely represent the original domain (usually the
+reals). In this case the limitations are caused by memory and speed, both of
+which are directly affected by the increasingly larger word lengths. Multiple
+Precision Floating Point Arithmetic and Software Rationals are good examples of
+these cases. It is possible for some of these data types to have memory
+constraints, at which point they fall into the second category.
+Fixed precision data types are most common in software programs. Whether
+they be Floating Point or Fixed Point (of which integers are the special case
+for 0 decimal places) numbers, the problem arises in the misrepresentation of
+the reals (or equivalent data type being represented).
+Let $\mathbb{R}_{\langle M,F \rangle}$ be a fixed point domain with $M$ bits
+representing the binary word length of the representation and $F$ bits
+representing the pre-scaling $2^{-F}$ (\emph{i.e} the number of bits after
+the decimal place).  We note that a negative $F$ denotes an integer
+multiplication that adds $-F$ trailing zeros in the number represented by
+$M$.
+Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point
+domain with $M$ bits mantissa and $E$ bits exponent.  This domain
+corresponds to $$\mathbb{R}_{\langle M,[E] \rangle} = \bigcup_F
+\mathbb{R}_{\langle M,F \rangle} \text{ where } F \in [-2^{E-1}, ...\,,2^{E-1}]$$ This
+definition important because it means that the distance between any two
+numbers in the domain depends on the location of those numbers.  Since we
+have shown that a floating point domain is a union of a number of fixed
+point domains, we will continue our reasoning on fixed point only, which
+will apply to the floating point domain by extension.  Operations on these
+numbers will incur errors that can be bound
+by~\cite{DBLP:conf/arith/BrainTRW15}.  We examine the most relevant ones:
+%
+\begin{enumerate}
+\item Truncation\\
+Let $\mathcal{F}_{\langle M,F \rangle} : \mathbb{R} \rightarrow \mathbb{R}_{\langle M,F \rangle}$
+be a truncation function, defined as:
+\begin{align*}
+x_{\langle M,F \rangle}=\mathcal{F}_{\langle M,F \rangle}(x) = x-\delta \text{ where } \delta=mod_F(x, x_{\langle M,F \rangle})
+\end{align*} 
+where $mod_F(\cdot)$ is the modulus operation performed on the last bit of the representation ($2^{-F}$).\\
+The number $\delta$ corresponds to the truncation error of the representation and it will propagate across operations.
+\item Rounding\\
+Every time an operation is performed on a number in the $\mathbb{R}_{\langle M,F \rangle}$ domain, an error may be
+introduced due to truncation of the result. 
+The following errors appear in simple operations:
+\begin{enumerate}
+\item Addition/Subtraction
+\begin{align*}
+&x_{\langle M,F_1\rangle} \pm y_{\langle M,F_2\rangle}=z_{\langle M,F\rangle} + \delta,  F=\text{min}(F_1,F_2)\\
+&\text{ where } |\delta| \leq 2^{-F} \text{ and } F_1=F_2 \Rightarrow \delta=0.
+\end{align*}
+\item Multiplication
+\begin{align*}
+&x_{\langle M,F_1\rangle} * y_{\langle M,F_2\rangle}=z_{\langle M,F\rangle} + \delta, \text{ where } F=F_1+F_2 \text{ and } |\delta| \leq 2^{-F}
+\end{align*}
+%\item Division\\
+%The operations performed by our controllers in the FWL
+%domain do not include division.  However, we do use division in computations
+%at the precision of the plant.  Here the error depends on whether the
+%divisor is greater or smaller than the dividend:  $x_{\langle M,F_1\rangle} / y_{\langle M,F_2 \rangle} = c_3 + \delta_{T3}$
+%where $\delta_{T3}$ is $(\delta_{T2}\cdot x - \delta_{T1}\cdot y)/(\delta_{T2}^2 - \delta_{T2} y)$,
+\end{enumerate}
+We note here that not all systems truncate equally.  In the
+definition above $\delta$ may be positive or negative, and even this
+decision can be made dependent on the sign of $x$.  Common cases in computer
+systems are: round downwards (\emph{ie} to $-\infty$), round upwards
+(\emph{ie} to $+\infty$), and round to zero.  Rounding errors are cumulative
+which means the overall error will statistically increase with every
+operation, thus single transition algorithms can be more precise in this
+respect than iterative ones because they perform fewer operations needing
+rounding.
+\item Overflow\\
+Another source of error introduced by FWL representations is that of overflow.
+The finite word length set a maximum representable number in the domain
+$\pm \overline{M} \text{ where }  \overline{M}=2^{M-F}-2^{-F}$, which means that any number
+outside this range cannot be accurately represented by the domain (\emph{eg} $\delta=x-\overline{M}$).
+In the case of floating point, a special cases for infinity has been introduced, which addresses
+some of these issues, but once the error has gone to infinity, the numbers become meaningless.
+It is the responsibility of software designers and tools to account for overflows and either
+supply saturation functions to prevent them or raise alarms in their presence. In the case
+of verification, the latter is seen as a safety problem.
+\item Null/Zeno behaviour\\
+Whilst this work does not explore Zeno behaviours, it is worth noting that this
+effect may be caused by rounding errors in floating point programs. The reason for this
+is that if an operation contains two numbers which belong to disjoint sub-domains
+(\emph{ie} neither number can be represented in the domain of its counterpart), the
+resulting operation may become a no-op/skip, subsequently destabilizing the program.
+\end{enumerate}
+
+We will use the domain $\mathbb{R}_{\langle C \rangle} \text{ where } \langle C \rangle = \langle M_c,F_c \rangle$
+to represent a digital implementation of LTI dynamics which we will refer to as the controller, and 
+$\mathbb{R}_{\langle P \rangle} \supseteq \mathbb{R}_{\langle C \rangle}$
+to represent the domain of a digital model of the dynamics of a real plant when evaluated by a verification tool.
+Furthermore, we will refer to the errors incurred by the calculations performed in these domains as finite word length (FWL) effects.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{Control theory} \label{sec:control_theory}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+The semantics discussed in sections \ref{sec:model} do not describe all
+properties of interest in our systems.  In some cases, specific values or
+substructures define hidden properties which can only be inferred given an
+appropriate transformation.  Since our models are being applied to linear
+control systems, and in particular to feedback systems with observers, we
+provide a summary of the important elements using control theory for their
+transformations.
+
+A feedback system is one where the output is fed back into the input, thus
+making part or all of the system a closed system (i.e. no inputs).
+Such a system is exemplified in figure \ref{fig:sampledsystem}.  Since the
+feedback line creates a loop in the diagram this is known as a closed loop,
+and the overall behaviour of the resulting system is said to have closed loop dynamics.
+The feedback may be direct or have further transformations, some of which will
+be discussed in this section.  For the moment we will also point out that in the
+models we are interested in, this feedback is digital and thus creates some
+further considerations regarding discretization.
+
+The objective of the feedback is to adhere to some properties we decide to control.
+In most cases these properties include stability.  We define stability as the ability of
+the system output to remain bounded given a bounded input. This is known as BIBO
+stability. Further constraints to this property may be added to enforce stronger stability 
+(e.g. convergent).  We discuss the requirements we are interested in in the following.
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Static output feedback and pole placement} \label{sec:pole_place}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+\begin{figure*}[htb]
+\centering
+
+\tikzset{add/.style n args={4}{
+    minimum width=6mm,
+    path picture={
+        \draw[circle] 
+            (path picture bounding box.south east) -- (path picture bounding box.north west)
+            (path picture bounding box.south west) -- (path picture bounding box.north east);
+        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+        }
+    }
+ }
+
+\resizebox{1.0\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
+     semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
+    \node[draw=none] (r) {$R(z)$};
+%   \& \coordinate (aux0);
+   \& \node[circle,add={-}{+}{}{}] (circle) {};
+   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Controller}] (cz) {{\sc C(z)}};
+   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
+
+   \& complexnode/.pic={ 
+      \node[rectangle,draw,
+	minimum width=3cm,
+	minimum height=1.6cm,
+	label=\textbf{DAC},] (dac) {};
+     \node[circle,add={}{+}{+}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
+     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
+     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
+     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}   
+   \& \node[rectangle,draw,
+	minimum width=1cm,
+	minimum height=1cm,
+        label=\textbf{Plant}] (gs) {{\sc $G(s)$}};
+   \node[draw=none] (ud) at ([xshift=-2cm,yshift=.15cm]gs)  {$U(s)$};
+   \node[draw=none] (y) at ([xshift=2cm,yshift=.15cm]gs)  {$Y(s)$};
+   \& complexnode/.pic={ 
+     \node[rectangle,draw,
+	minimum width=4cm,
+	minimum height=1.6cm,
+	label=\textbf{ADC},] (adc) {};
+   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
+   \coordinate (switch1) at ([xshift=-1cm]adc.center);
+   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
+   \node[circle,add={}{+}{+}{},fill=gray!20] (q1) at ([xshift=1cm]adc.center) {};} 
+     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
+   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
+   \& \coordinate (aux1);
+   \& \node[draw=none] (yz) {$Y(z)$};\\
+   \& \coordinate (aux3); 
+   \&
+   \&
+   \& 
+   \& 
+   \& \coordinate (aux2);\\
+  };
+
+  \path[->] (v1) edge (q1.north);
+  \path[->] (v2) edge (q2.north);
+  \path[->] (r) edge (circle.west);
+  \path[->] (aux1) edge (yz);
+  \path  
+   (circle.east) edge (cz)
+   (cz.east) edge (q2.west)
+   (q2.east) edge (zoh.west)
+   (zoh.east) edge (gs.west)
+   (switch2) edge (q1.west)
+   (q1.east) edge (aux1.west)
+   (gs.east) edge (switch1.west)
+   (aux1.south) edge (aux2.north)
+   (aux2.west) edge (aux3.east); 
+  \path[->]  (aux3.north) edge (circle.south);
+ \end{tikzpicture}
+}
+ \caption{Closed loop digital control system\label{fig:sampledsystem}}
+\end{figure*}
+
+Given an unstable plant with divergent dynamics, the problem of stabilizing the
+output is to find a controller that results in convergent closed loop dynamics.
+The term Static Output Feedback relates to the desired effect of having a static
+output given a fixed reference signal.  In modern embedded systems, said
+controller is a digital program, which means that the closed loop dynamics are
+subject to time and space discretization as described in
+sections~\ref{sec:continuous_LTI} and~\ref{sec:numeric_rep}.
+In real a physical plant, these discretizations are performed by an
+Analog-to-Digital Converter(ADC) which samples the output of the plant at
+intervals $T_s$ (time discretization) and quantizes it to an FWL representation
+(space discretization).  Conversely, a Digital-to-Analog Converter(DAC)
+transforms a discretized value into a real input to the physical plant.
+In general terms, when analysing such systems, the controller is known to have
+discrete dynamics, whereas the plant must be discretised based on the sample
+and hold characteristics. The ADC/DAC converters are considered to introduce a
+quantization noise on the system as shown in Figure~\ref{fig:sampledsystem}.
+Let the quantizer~$Q1$ be the source of a non-deterministic noise~$\nu_{1}$
+and~$Q2$ be the source of a non-deterministic noise~$\nu_{2}$.
+Convergence of such a system is a frequency domain property, which is why we
+first analyse the system using its transfer function.  The transfer function of
+a system relates its input and output in the frequency domain (more generally
+in the Laplace domain for continuous time systems and the Z-domain for discrete
+time).  In the case of linear systems, these correspond to the characteristic
+polynomials of the system dynamics (i.e. the polynomial whose roots are the
+eigenvalues of the dynamics). The following equation models the system,
+encompassing the discretization of the plant:
+%
+\begin{equation}
+Y(z)=C(z)G(z)(R(z)-Y(z))+\nu_{1}(z)+\nu_{2}(z)C(z)G(z),
+\end{equation}
+%
+The above can be rewritten as follows:
+%
+\begin{equation}
+\label{eq:outputfunctions}
+Y(z)=H_1(z)R(z)+H_2(z)\nu_{1}(z)+H_3(z)\nu_{2}(z),
+\end{equation}
+%
+where
+%
+\begin{align}
+H_1(z)=\frac{C(z)G(z)}{1+C(z)G(z)},\\
+H_2(z)=\frac{1}{1+C(z)G(z)},\\
+H_3(z)=\frac{G(z)}{1+C(z)G(z)}.
+\end{align}
+%
+
+\begin{assumption}
+\label{whitenoise}
+%
+The quantization noises $\nu_{1}$ (from $Q1$) and $\nu_{2}$ (from $Q2$) are
+uncorrelated white noises and their amplitudes are always bounded by the
+half of quantization step~\cite{astrom1997computer}, i.e., $\vert \nu_{1}
+\vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$,
+where $q_{1}$ and $q_{2}$, respectively, are the quantization steps of ADC
+and DAC.
+% 
+\end{assumption}
+
+It is known that a discrete-time linear system is said to be Bounded-Input and Bounded-Output
+(BIBO) stable if and only if every pole of its transfer function lies inside
+the unit circle \cite{Astrom08}.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following
+proposition states necessary conditions for BIBO stability of the closed-loop system
+in Figure~\ref{fig:sampledsystem}, since the exogenous signals $R(z)$,
+$\nu_{1}$, and $\nu_{2}$ are bounded. Hence, our close loop system is stable if the poles in
+$H_1(z) , H_2(z) $ and $H_3(z)$ are inside the unit circle. Since all three transfer functions share the same poles,
+we only need to look at the roots of the polynomial
+$$C_n(z)G_n(z)+C_d(z)G_d(z) : C(z)=\frac{C_n(z)}{C_d(z)} \wedge G(z)=\frac{G_n(z)}{G_d(z)}$$
+Any controller that ensures these roots lie within the unit circle is a stabilizing controller for the system.
+
+This same analysis can be applied to MIMO systems where there is a transfer functions of the system
+for each combination of input-output. Rather than examine the transfer functions of these systems, we will first
+look at minimal descriptions of the state space dynamics that will help us extract them with little extra effort whilst 
+providing us with tools to analyse other properties.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Controllable canonical form} \label{sec:reachable}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Let us have a discrete time Single Input Single Output (SISO) system with a $p^{th},q^{th}$ order model with $p\geq q$.
 $$y[k]=\sum_{i=1}^p a_{p-i}y[k-i]+\sum_{i=0}^{q-1} b_{p-i}u[k-i],$$
@@
 \label{eq:cf_SISO}
-\vec{x}_{k+1}=&\mat{A}_c\vec{x}_k+\mat{B}_cu_k : \vec{x}_k=[\begin{array}{cccc}y_k&y_{k-1}&\hdots&y_{k-(p-1)}\end{array}]^T\\
+\vec{x}_{k+1}=&\mat{A}_c\vec{x}_k+\mat{B}_cu_k, \text{ where } \vec{x}_k=[\begin{array}{cccc}y_k&y_{k-1}&\hdots&y_{k-(p-1)}\end{array}]^T\\
 y_k=&\mat{C}_c\vec{x}_k + b_0u_k\nonumber\\
@@
 \end{array}\right]\nonumber\\
-\mat{C}_c=&[\begin{array}{ccccc}b_0-a_0b_p&b_1-a_1b_p&\cdots&b_{p-1}-a_{p-1}b_p\end{array}] \text{ where } b_i=0 \mid i \in [0, p-q]\nonumber
+\mat{C}_c=&[\begin{array}{ccccc}b_0-a_0b_p&b_1-a_1b_p&\cdots&b_{p-1}-a_{p-1}b_p\end{array}] \text{ where } b_i=0 \text{ and } i \in [0, ...\,,p-q]\nonumber
 \end{align}
@@
 called a Controllable Canonical Form because the dynamics of the feedback are directly related to these
-coefficients. Specifically, given a feedback controller $\mat{K}$ for any particular system, the closed loop dynamics
+coefficients. Specifically, given a feedback controller $\mat{K}_c$ for any particular system, the closed loop dynamics
 are
 \begin{align}
-\vec{x}_{k+1}=(\mat{A}-\mat{B}\mat{K})\vec{x}
+\vec{x}_{k+1}=(\mat{A}-\mat{B}\mat{K})\vec{x}_k
 \label{eq:closeloopdynamics}
@@
 \end{align}
-with $\mat{I}_i,\mat{M}_i \in \mathbb{R}^{q_i \times q_i}, \mat{a}_i \in \mathbb{R}^{q \times q_i}, \mat{\Gamma}_i \in \mathbb{R}^o \text{ and }  \mat{\Gamma}_{i}=0 \mid i \in [0,p-q]$
-
-where $q$ is the number of inputs, $q_i$ the number of inputs with a transfer function of order of at least $i$, $\mat{I}_i$ an identity matrix, $\mat{M}_i$ an upper triangular matrix with 1s in its diagonal, $\mat{a_i}$ a matrix of coefficients of the $i^{th}$ order on its diagonal, and $o$ the number of outputs.
+with $\mat{I}_i,\mat{M}_i \in \mathbb{R}^{q_i \times q_i}, \mat{a}_i \in \mathbb{R}^{q \times q_i}, \mat{\Gamma}_i \in \mathbb{R}^o \text{ and for }  i \in [0, ...\,,p-q], \mat{\Gamma}_{i}=0$, where $q$ is the number of inputs, $q_i$ the number of inputs with a transfer function of order of at least $i$, $\mat{I}_i$ an identity matrix, $\mat{M}_i$ an upper triangular matrix with 1s in its diagonal, $\mat{a_i}$ a matrix of coefficients of the $i^{th}$ order on its diagonal, and $o$ the number of outputs.
 Ideally, $\forall i>0, \mat{M}_i=\mat{I}_i$
@@
 \begin{align}
-\hat{\vec{x}}_{k+1}=&\mat{A}_c\hat{\vec{x}}_k+\mat{B}_cu_k : \mat{A}_c=\mat{T}_c\mat{A}\mat{T}_c^{-1} \wedge \mat{B}_c=\mat{T}_c\mat{B}\\
-y_k=&\mat{C}_c\hat{\vec{x}}_k + b_0u_k : \mat{C}_c=\mat{C}\mat{T}_c^{-1}\nonumber
+\hat{\vec{x}}_{k+1}=&\mat{A}_c\hat{\vec{x}}_k+\mat{B}_cu_k, \text{ where } \mat{A}_c=\mat{T}_c\mat{A}\mat{T}_c^{-1} \text{ and } \mat{B}_c=\mat{T}_c\mat{B}\\
+y_k=&\mat{C}_c\hat{\vec{x}}_k + b_0u_k, \text{ where } \mat{C}_c=\mat{C}\mat{T}_c^{-1}\nonumber
 \end{align}
@@
 %-------------------------------
-\subsection{Stability of a Controlled System} 
+\subsection{Stability of a controlled system} 
 \label{sec:closed_stability}
 %-------------------------------
-
 There are a number of algorithms that can be
@@
 (this simple sufficient condition can be generalised, however this is
-not necessary in our work).  In this paper, we express this stability
+not necessary in our work).  In this work, we express this stability
 specification $\phi_\mathit{stability}$ in terms of a check known as
@@
 characteristic polynomial $S(z)$ as opposed to its roots (which are
-extremely hard to calculate for a SAT solver), we choose Jury's
-criterion~\cite{astrom1997computer} to check the stability in the
-$z$-domain in view of its efficiency.
+comparatively hard to calculate for a SAT solver due to the number of
+multiplications involved), we choose Jury's criterion~\cite{astrom1997computer}
+to check the stability in the~$Z$-domain in view of its efficiency.
 
@@
 from measurements of the input and output of the real system.
-
-A closed-loop digital control system with observer is shown in Fig.~\ref{fig:observersystem}.
+This means that contrary to a stateless reactive controller, an observer
+controller has memory of the states (i.e. it is stateful).
+
+Take for example a system where we are given the position of a robot
+arm in a single axis.  Our objective is to move the arm to pick an object 
+from a known location along that axis.  The input of the robotic arm is an
+acceleration.  The position of the arm will vary depending on the speed, which
+in turn varies with the acceleration.  However, if we do not know the speed, we
+will not be able to reach our target smoothly.  An observer for this design could
+simply calculate the speed by keeping a memory (state) of the previous position
+and calculate the difference with the current position in the given time interval.
+
+A closed-loop digital control system with observer is shown in Figure~\ref{fig:observersystem}.
 Note that the variables of a state observer are denoted by a "$~\hat{}~$" (e.g. {$\hat {\vec{x}}(k)$})
@@
 The figure also contains references to $\nu_1$, $\nu_2$, $\nu_1'$, $\nu_2'$ and $\nu_t$, which
-denote noise and will be explained later in the paper.
+denote noise and will be explained later in the dissertation.
 Lastly, $k_r$ is a reference gain required by the model.
@@
 the observability matrix of the canonical form (see eg~\cite{Astrom08}). Then the matrix $\mat{T}_o=\mat{W}^{-1}\mat{W}_{o}$ will transform an observable system into its canonical form.
-For simplicity of the description, we agregate the noises as follows:
+For simplicity of the description, we aggregate the noises as follows:
 $\eta_1=\nu_1+\nu_1'+\nu_t$ and $\eta_2=\nu_2+\nu_2'$,
-where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations (see section \ref{}).
+where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations (see Section~\ref{sec:FWL_effects}).
 Assuming that the observer dynamics are an exact copy of the real ones, ($\mat{*}_{\langle C \rangle}=\mat{*}$), the closed loop dynamics of this system are given by:
@@
    \& complexnode/.pic={ 
-      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};
+      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Continuous Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};
       \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2.5cm,yshift=.5cm]plant.center)  {\sc $\mat{B}$};
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Stability of an Observed System}\label{sec:cof_stability}
+\subsection{Stability of an observed system}\label{sec:cof_stability}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 
-We get the stability specification by appying Jury's Criterion to these polynomials.
+We get the stability specification by applying Jury's Criterion to these polynomials.
+
+%For a stabilised closed loop, we need these roots to remain within the unit circle (left hand side of the plane for continuous time).
+%Whilst this is not a sufficient condition for verifying safety properties, it is a necessary one, therefore we will review this verification process.
+%The direct approach would be to calculate the roots of the polynomials (\emph{ie} the eigenvalues of the matrix), but this ends up being to costly, particularly in the case of synthesis, so we use an indirect method.
+%
+%Jury's criteria is a mathematical method used to verify whether the roots of the polynomial are within the unit circle by exploring solely the coefficients of the polynomial.
+In order to achieve this, we first create a matrix $\mat{M} \in \mathbb{R}^{(n+1) \times (n+1)}$ with zero-indexed coefficients $m_{i,j} : i,j \in [0,, ...\,,n]$ in the following form:
+%
+%\begin{equation}
+%\left[\begin{array}{ccccc}
+%c_0&c_1&\hdots&c_{n-1}&c_n\\
+%m_{\scriptscriptstyle 0,0}-m_{\scriptscriptstyle 0,n}^*\frac{m_{0,n}^*}{m_{0,0}}&m_{\scriptscriptstyle 0,1}-m_{\scriptscriptstyle 0,n-1}^*\frac{m_{0,n}^*}{m_{0,0}}&\hdots&m_{\scriptscriptstyle 0,n-1}-m_{\scriptscriptstyle 0,1}^*\frac{m_{0,n}^*}{m_{0,0}}&0\\
+%\vdots&\vdots&\vdots&\vdots&\vdots\\
+%m_{\scriptscriptstyle i-1,0}-m_{\scriptscriptstyle i-1,n-i+1-j}^*\frac{m_{i-1,n-i+1}^*}{m_{i-1,0}}&m_{\scriptscriptstyle i-1,1}-m_{\scriptscriptstyle i-1,n-i+1-j}^*\frac{m_{i-1,n-i+1}^*}{m_{i-1,0}}&\hdots&0&0\\
+%m_{\scriptscriptstyle n-1,0}-m_{\scriptscriptstyle n-1,1-j}^*\frac{m_{n-1,1}^*}{m_{n-1,0}}&0&\hdots&0&0\\
+%\end{array}\right]
+%\end{equation}
+%
+%The first row corresponds to the coefficients of the original polynomial.
+Notice also that every row has a polynomial one degree lower than the previous.
+The sufficient and necessary conditions for the polynomial in row 0 to have all of its roots inside the unit circle are~\cite{}:
+%\begin{align}
+%|c_n|<c_0&&
+%\sum_{i=0}^n c_i > 0&&
+%(-1)^n\sum_{i=0}^n c_i (-1)^{n-i}> 0&&
+%m_{i,0}>0
+%\end{align}
+%
+%Notice that in both our polynomials $c_0=1$ and we only use reals.
 
 %-------------------------------
-\section{Overapproximating continuous time dynamics using discrete models}
-\label{sec:cont_aa}
-%-------------------------------
-Our plant models derive from the discretization of
-continuous time systems.  We therefore seek to establish a sound
-overapproximation which does not only encompass the selected discretization,
-but any chosen discretization in the time domain.
-
-A dynamical system is a system in which a function describes the progression
-of a state over time.  In a continuous domain with linear dynamics, it is
-described by a first order Ordinary Differential Equation (ODE).
-\begin{equation}
-\dot{x}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)% +\vec{w}(t)
-\label{eq:dynamical}
-\end{equation}
-
-%where $\vec{w}$  is a continuous zero-mean white noise source with
-%covariance $N ( 0 , Q )$ 
-Furthermore, a control system may have a derived
-output that is a linear combination of its states and inputs, which may
-restrict the observability of the state-space from the output space.
-\begin{equation}
-\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)
-\end{equation}
-
-Discretization of a continuous dynamical system turns the ODE into a
-difference equation, assuming zero-order hold for the input $\vec{u}$
-%and continuous integration for the noise $\vec{w}$,
-to
-\begin{align}
-\label{eq:discretization}
-\vec{x}_{k+1} &= \mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\% + \vec{w}_k\\
-y_k &= \mat{C}_d \vec{x}_ k + \mat{D}_d \vec{u}_ k 
-\end{align}
-%with covariance for $\vec{w}_k$, $N ( 0 , Q_d )$
-where
-\begin{align}
-\label{eq:discretize}
-\mat{A}_d &= e^{\mat{A} T_s} = \mathcal{L}^{-1} { ( s \mat{I} - \mat{A} )^{-1} }_{t = T_s}\\
-\mat{B}_d &= \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B} = \mat{A}^{-1} ( \mat{A}_d - \mat{I} ) \mat{B}\\
-\mat{C}_d &= \mat{C}\\
-\mat{D}_d &= \mat{D}
-%\\Q_d &= \int_{t = 0}^{T_s} e^{\mat{A} t} Q e^{\mat{A}^T t} dt
-\end{align}
-and $T_s$ is the sample time. Then
-\begin{align*}
-\forall k, x(kT_s)=x_k \text{ and } y(kT_s) = y_k
-\end{align*}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Numerical representation} 
-\label{sec:numeric_rep}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-In embedded software programs interacting and/or simulating physical plants
-it is of great importance to understand the effects of the chosen numeric 
-representation for the continuous state-space and interacting discrete dynamics. 
-\jrronly{
-These representations are almost invariably approximations to the original
-which are assumed to be precise enough as to not cause any trouble,
-but it is precisely this assumption that often results in the most difficult and
-dangerous errors.
-There are generally speaking two formats for representing numbers in
-programs. On one hand we have variable word length types which will
-attempt to use as much memory as needed to precisely represent the
-original domain (usually the reals). In this case the limitations are caused
-by memory and speed, both of which are directly affected by the
-increasingly larger word lengths. Multiple precision floating-point arithmetic
-and software rationals are good examples of these cases. It is possible for
-some of these data types to have memory constraints, at which point they
-fall into the second category.
-Fixed precision data types are most common in software programs.
-}
-Whether they be floating point or fixed point
-\jrronly{ (of which integers are the special case for 0 decimal places) }
-numbers, the problem arises in the misrepresentation of the reals%
-\jrronly{ (or equivalent data type being represented) }.
-Let $\mathbb{R}_{\langle M,F \rangle}$ be a fixed point domain with $M$ bits
-representing the binary word length of the representation and $F$ bits
-representing the prescaling $2^{-F}$ (\emph{i.e} the number of bits after
-the decimal place).  We note that a negative $F$ denotes an integer
-multiplication that adds $-F$ trailing zeros in the number represented by
-$M$.
-Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point
-domain with $M$ bits mantissa and $E$ bits exponent.  This domain
-corresponds to $$\mathbb{R}_{\langle M,[E] \rangle} = \bigcup_F
-\mathbb{R}_{\langle M,F \rangle} \mid F \in [2^{1-E}, 2^{E-1}]$$ This
-definition important because it means that the distance between any two
-numbers in the domain depends on the location of those numbers.  Since we
-have shown that a floating point domain is a union of a number of fixed
-point domains, we will continue our reasoning on fixed point only, which
-will apply to the floating point domain by extension.  Operations on these
-numbers will incur errors that can be bound
-by~\cite{DBLP:conf/arith/BrainTRW15}.  
-We examine the most relevant ones:
-%
-\begin{enumerate}
-\item Truncation\\
-Let $\mathcal{F}_{\langle M,F \rangle} : \mathbb{R} \rightarrow \mathbb{R}_{\langle M,F \rangle}$
-be a truncation function, defined as:
-\begin{align*}
-x_{\langle M,F \rangle}=\mathcal{F}_{\langle M,F \rangle}(x) = x-\delta \mid \delta=mod_F(x,c x_{\langle M,F \rangle})
-\end{align*} 
-where $mod_F(\cdot)$ is the modulus operation performed on the last bit of the representation ($2^{-F}$).\\
-The number $\delta$ corresponds to the truncation error of the representation and it will propagate across operations.
-\jrronly{
-%
-It is worth mentioning that not all systems truncate equally.  In the
-definition above $\delta$ may be positive or negative, and even this
-decision can be made dependent on the sign of $x$.  Common cases in computer
-systems are: round downwards (\emph{ie} to $-\infty$), round upwards
-(\emph{ie} to $+\infty$), and round to zero.  Rounding errors are cumulative
-which means the overall error will statistically increase with every
-operation, thus algorithms performing fewer operations can be more precise
-in this respect than iterative ones.
-%
-}
-\item Rounding\\
-Every time an operation is performed on a number in the $\mathbb{R}_{\langle M,F \rangle}$ domain, an error may be
-introduced due to truncation of the result. 
-The following errors appear in simple operations:
-\begin{enumerate}
-\item Addition/Substraction
-\begin{align*}
-&x_{\langle M,F_1\rangle} \pm y_{\langle M,F_2\rangle}=z_{\langle M,F\rangle} + \delta,  F=\text{min}(F_1,F_2)\\
-&\text{ where } |\delta| \leq 2^{-F} \text{ and } F_1=F_2 \Rightarrow \delta=0.
-\end{align*}
-\item Multiplication
-\begin{align*}
-&x_{\langle M,F_1\rangle} * y_{\langle M,F_2\rangle}=z_{\langle M,F\rangle} + \delta, \text{ where } F=F_1+F_2 \text{ and } |\delta| \leq 2^{-F}
-\end{align*}
-%\item Division\\
-%The operations performed by our controllers in the FWL
-%domain do not include division.  However, we do use division in computations
-%at the precision of the plant.  Here the error depends on whether the
-%divisor is greater or smaller than the dividend:  $x_{\langle M,F_1\rangle} / y_{\langle M,F_2 \rangle} = c_3 + \delta_{T3}$
-%where $\delta_{T3}$ is $(\delta_{T2}\cdot x - \delta_{T1}\cdot y)/(\delta_{T2}^2 - \delta_{T2} y)$,
-\end{enumerate}
-
-\jrronly{
-\item Overflow\\
-Another source of error introduced by Finite Word Length representations is that of overflow.
-The finite word length set a maximum representable number in the domain
-$\pm \overline{M} \mid \overline{M}=2^{M-F}-2^{-F}$, which means that any number
-outside this range cannot be accurately represented by the domain (\emph{eg} $\delta=x-\overline{M}$).
-In the case of floating point, a special cases for infinity has been introduced, which addresses
-some of these issues, but once the error has gone to infinity, the numbers become meaningless.
-It is the responsibility of software designers and tools to account for overflows and either
-supply saturation functions to prevent them or raise alarms in their presence. In the case
-of verification, the latter is seen as a safety problem.
-\item Null/Zeno behaviour\\
-Whilst this work does not explore the effect of Zeno behaviours, it is worth noting that this
-effect may also be caused by rounding errors in floating point programs. The reason for this
-is that if an operation contains two numbers which belong to disjoint sub-domains
-(\emph{ie} neither number can be represented in the domain of its counterpart), the
-resulting operation may become a no-op/skip, subsequently destabilizing the program.
-}
-\end{enumerate}
-We will use the domain $\mathbb{R}_{\langle C \rangle} \mid \langle C \rangle = \langle M_c,F_c \rangle$
-to represent the fixed point precision of the controller, and 
-$\mathbb{R}_{\langle P \rangle} \supseteq \mathbb{R}_{\langle C \rangle}$
-to represent the domain of the plant model.
-Thus any mathematical operations in our modelled digital controller will be executed in the
-domain $\mathbb{R}_{\langle C \rangle}$, and all other calculations
-in our model will be carried out in the domain $\mathbb{R}_{\langle
-P \rangle}$.  The physical plant operates in the reals, which means
-our verification phase must also account for the numerical error caused by representing the
-physical plant at the finite precision $\mathbb{R}_{\langle P \rangle}$.
-
-We will use these subindices to represent functions, number, vectors and matrices in their
-corresponding domains. We further note that by choosing $\langle C \rangle = \langle M_c,[E_c] \rangle$
-we extend the following to floating point reasoning.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Quantization error}
-\label{appendix:quantization}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Let $q_c=2^{-F_c},q_a=2^{-F_a},q_d=2^{-F_d}$ be the smallest difference
-between two numbers in their corresponding domains.  Assuming that our
-system truncates numbers to the nearest value, this means thet the error
-$\delta$ introduced by the function $\mathcal{F}_{\langle * \rangle}$ is
-$\delta_*=\mathcal{F}_{\langle * \rangle}(x)-x \in \left[-\frac{q_*}{2}\
-\frac{q_*}{2}\right]$.  We note that in the case of floating point,the
-choice of $F$ is taken from the largest multiplication found (e.g.,
-$\norm{\mat{A}}_1\norm{\vec{x}}_1 \mid \vec{x} \models \phi_\mathit{safety}$,
-where $\phi_\mathit{safety}$ is defined in \ref{eq:safetyspec}). From these
-equations we can define:
-%
-\begin{align*}
-\nu_1 \in \left[-\frac{q_a}{2}\ \frac{q_a}{2}\right] \cap  \left[-\frac{q_c}{2}\ \frac{q_c}{2}\right],
-\nu_2 \in \left[-\frac{q_d}{2}\ \frac{q_d}{2}\right]
-\end{align*}
-
-We may also bound $\nu_2'$ from \eqref{eq:uk} as follollows:
-\begin{align*}
-\delta\left(\mat{K}_{\langle C\rangle} \vec{x}_{\langle C\rangle} \right) &\in \left[ -p \frac{q_c}{2}\ \ p \frac{q_c}{2}\right]\\
-{\vec{\nu_e}}_i &\in \left[ -(p+2) \frac{q_c}{2}\ \ (p+2) \frac{q_c}{2}\right], i \in [1, p]\\
-\Rightarrow \nu_2' &\in \left[  -p(\norm{\mat{K}_{\langle C \rangle}}_1+2) \frac{q_c}{2}\ \ p(\norm{\mat{K}_{\langle C \rangle}}_1+2) \frac{q_c}{2}\right]
-\end{align*}
-Similarly we also find
-\begin{align*}
-\nu_1' &\in \left[  -p(\norm{{\mat{C}_d}_{\langle C \rangle}}_1+2) \frac{q_c}{2}\ \ p(\norm{{\mat{C}_d}_{\langle C \rangle}}_1+2) \frac{q_c}{2}\right]
-\end{align*}
-The proof derives from $\norm{\mat{K}\vec{x}}_1 \leq \norm{\mat{K}}_1\norm{\vec{x}}_1$.
-
-%%-------------------------------
-%\section{Stability} 
-%\label{appendix:stabspecification}
-%%-------------------------------
-%
-%There are a number of algorithms that can be
-%used for stability analysis~\cite{daes20161,Bessa16}.
-%
-%A discrete-time LTI system as \eqref{eq:closedloopss} is
-%asymptotically stable if all the roots of its characteristic
-%polynomial (i.e., the eigenvalues of the closed-loop matrix $A_d - B_d
-%K$) are inside the unity circle of the complex plane, i.e., their
-%absolute values are strictly less than one~\cite{astrom1997computer}
-%(this simple sufficient condition can be generalised, however this is
-%not necessary in our work).  In this paper, we express this stability
-%specification $\phi_\mathit{stability}$ in terms of a check known as
-%\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic
-%formula to select the entries of matrix $K$ so that the closed-loop
-%dynamics are shaped as desired.
-%
-%
-%
-%Since the canonical forms used in this work use the coefficients of the
-%characteristic polynomial $S(z)$ as opposed to its roots (which are
-%extremely hard to calculate for a SAT solver), we choose Jury's
-%criterion~\cite{astrom1997computer} to check the stability in the
-%$z$-domain in view of its efficiency.
-%
-%We~consider the following form for $S(z)$:
-%%
-%\begin{equation*}
-%S(z) = z^{p}+a_1z^{p-1}+\cdots+a_{p-1}z+a_p.
-%\end{equation*}
-%
-%and build the matrix
-%$\mat{M} \in \mathbb{R}^{p \times p}$ from its coefficients such that:
-%%
-%\begin{align*}
-%\mat{M}_{1,j}&=a_j\\
-%\mat{M}_{i+1,j}&=\left\{
-%\begin{array}{ll}
-%0,&j>p'\\
-%\mat{M}_{i,j}-\mat{M}_{i,p'-j+1}\frac{\mat{M}_{i,1}}{\mat{M}_{i,p'}} &j\leq p'
-%\end{array}
-%\right.\\
-%p'&=p-i+1
-%\end{align*}
-%%
-%$S(z)$ is the characteristic polynomial of a stable system if and
-%only if the following conditions hold~\cite{astrom1997computer}:
-%\begin{align*}
-%\phi_\mathit{stability}(S) \equiv
-%(S(1) > 0) \wedge ((-1)^p S(-1) > 0) \wedge (|a_p| < 1) \wedge \bigwedge\limits_{i=1}^p (\mat{M}_{i,1} > 0).
-%\end{align*}
-%
-
-%-------------------------------
-\section{Proofs of theorems}
+\section{Proofs of theorems \label{sec:proofs}}
 %-------------------------------
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsubsection{Accelerated dynamics for continuous time systems without inputs}\label{asec:real_discrete_no_inputs}
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ \subsubsection{Accelerated dynamics for continuous time models without inputs}\label{sec:cont_acc_no_inputs}
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a linear function of $\vec{x}_0$ as described below.
+
  \begin{theorem}
- Given $\dot{\vec{x}}=\mat{A}\vec{x}$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, the expression
+ Given $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, we have
  \begin{align}
@@
  \left [ \begin{array}{cccc}
- e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(1)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
+ e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(2)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
 0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
@@
  \mat{S}^{-1}
- \label{appendix:continuous_tube_dyn}\\
+ \label{eq:continuous_tube_dyn}\\
  &\text{where } s_i=\left\{\begin{array}{cc}1&gm(\lambda_i)>1\\0&gm(\lambda_i)=1\end{array}\right.,\nonumber
@@
 $\lambda_i \in \mat{J}$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.  
-$\vec{x}_T$ is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}$ at time t=T.
+$\vec{x}_T$ is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T.
  \end{theorem}
  \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x} : k \in (0,\infty)$ is a witness of the system at time $t=kT_d$.
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x} \text{ with } k \in \mathbb{R}^+$ is the state of the system at time $t=kT_d$.
  \end{corollary}
@@
  referenced to the original eigenvalues modified by the sampling rate.
-  Let $\mat{J}\in \mathbb{R}^{p \times p}$ be a Jordan Canonical matrix.
+  Let $\mat{J}\in \mathbb{R}^{p \times p}$ be a Jordan Canonical matrix whose powers are described in Equation \eqref{jord:pow}
  Then
 \begin{align}
- \mat{J}_1&=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{J}T_1\right)^k=\sum_{k=0}^\infty \frac{1}{k!} \left [ \begin{array}{cccc}
+ \mat{J}_1&=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{J}T_1\right)^k\nonumber\\
+ &=\sum_{k=0}^\infty \frac{1}{k!} \left [ \begin{array}{cccc}
  \lambda_i^k  & \binom{k}{1}  \lambda^{k-1} & \hdots  & \binom{k}{p-1} \lambda_i^{k-p+1} \\
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsubsection{Accelerated dynamics for continuous time systems with parametric inputs}\label{asec:real_discrete_param_inputs}
+ \subsubsection{Accelerated dynamics for continuous time models with parametric inputs}\label{sec:cont_acc_param_inputs}
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
  \vec{x}_T&=\vec{x}(t=T)=\mat{A}^{-1}\vec{x}_T'\nonumber\\
-\vec{x}_T'&=\mat{A}\mat{A}_T\vec{x}_0 + (\mat{I}-\mat{A}_T)\mat{B}\vec{u} : \forall t \leq T,\ \vec{u}(t)=\vec{u} 
- \end{align}
- with $\mat{A}_T$ as per \eqref{eq:continuous_tube_dyn} is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$.
+\vec{x}_T'&=\mat{A}\mat{A}_T\vec{x}_0 + (\mat{I}-\mat{A}_T)\mat{B}\vec{u} \text{ where } \forall t \leq T,\ \vec{u}(t)=\vec{u} 
+ \end{align}
+ with $\mat{A}_T$ as per \eqref{eq:continuous_tube_dyn} is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$.
  \end{theorem}
  \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}+(\mat{I}-\mat{A}_d^k\mat{B}\vec{u}) : k \in (0,\infty)$ is a witness of the system at time $kT_d$.
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}+(\mat{I}-\mat{A}_d^k\mat{B}\vec{u}) \text{ with } k \in \mathbb{R}^+$ is the state of the system at time $kT_d$.
  \end{corollary}
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsubsection{Accelerated dynamics for continuous time systems with discrete time feedback inputs}\label{asec:real_discrete_feedback_inputs}
+ \subsubsection{Accelerated dynamics for continuous time models with discrete time feedback inputs}\label{asec:real_discrete_feedback_inputs}
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
  \begin{align}
- \vec{x}_{t} &= (\mat{A}_{t-kT_s}-\mat{B}_{t-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
+ \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
  \label{eq:cyber_feedback}
  \end{align}
- with $\mat{A}_t, \mat{B}_t$ as per \eqref{eq:continuous_tube_dyn} and $\mat{A}_d, \mat{B}_d$ as per equation \eqref{eq:discretize} is a witness of the system
- \begin{align}
- \dot{\vec{x}}_{t} &= \mat{A}\vec{x}+\mat{B}\vec{u}_t\nonumber\\
- \vec{u}_t&=\mat{K}\vec{x}_k  \mid  kT_s \leq t < (k+1)T_s
+ with $\mat{A}_T, \mat{B}_T$ as per \eqref{eq:continuous_tube_dyn} and $\mat{A}_d, \mat{B}_d$ as per equation \eqref{eq:discretize} is a witness of the system
+ \begin{align}
+ \dot{\vec{x}}({t}) &= \mat{A}\vec{x}+\mat{B}\vec{u}(t)\nonumber\\
+ \vec{u}(t)&=\mat{K}\vec{x}_k, \text{ where }  kT_s \leq t < (k+1)T_s
  \end{align}
@@
 Let $\mat{K}$ be a feedback controller such that $\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$. Let the output of
-the feedback system be a zero order holder such that $\vec{u}(t+kT_s)=\vec{u}(kT_s) : 0 \leq t < T_s$.
+the feedback system be a zero order holder such that $\vec{u}(t'+kT_s)=\vec{u}(kT_s), \text{ for }  0 \leq t' < T_s$.
 The closed loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
 \begin{equation}
-\vec{x}_{k,t}=\mat{A}_t\vec{x}_k-\mat{B}_t\mat{K}\vec{x}_k = (\mat{A}_t-\mat{B}_t\mat{K})\vec{x}_k : 0 \leq t < T_s
+\vec{x}_{k,t'}=\mat{A}_{t'}\vec{x}_k-\mat{B}_{t'}\mat{K}\vec{x}_k = (\mat{A}_{t'}-\mat{B}_{t'}\mat{K})\vec{x}_k, \text{ where }  0 \leq t' < T_s
 \end{equation}
@@
 \end{align}
-which accelerating results becomes
+which accelerating results and setting $T=kT_s+t'$ becomes
 \begin{align}
@@
 \vec{x}_{k} &= (\mat{A}_d-\mat{B}_d\mat{K}) ^k\vec{x}_0\\
-\vec{x}_{t} &= (\mat{A}_{t-kT_s}-\mat{B}_{t-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
+\vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
 \label{eq:feedback_cont}
@@
 \begin{theorem}
-The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modelled as a non-deterministic noise signal upperbound by 
-\begin{align}
-\norm{{\vec{y}_e}_{k}}_1 \leq q_t, \text{ where } q_t=&(\norm{\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})}_1+\norm{\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}}_1)\norm{U}_1
-\end{align}
+The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modelled as a non-deterministic noise signal upper bound by
+\begin{align}
+\norm{\vec{y}_{k}-{\vec{y}_{t_d}}_{k}}_1 \leq q_t, \text{ where } q_t=&(\norm{\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})}_1+\norm{\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}}_1)\norm{U}_1
+\end{align}
+where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$, and $\norm{\vec{x}}_1=\sum_{i=0}^{size(\vec{x})} |\vec{x}_i|$ is the $l_1$ norm (in for sets, $\norm{X}_1 = sup \{\norm{\vec{x}}_1 \mid \vec{x} \in X\}$).
 \end{theorem}
@@
 \end{proof}
-We overapproximate the effects of this vector by introducing a noise signal at the output $\nu_t=[-q_t\ q_t]$ and use the dynamics of the system without delay.
+We over-approximate the effects of this vector by introducing a noise signal at the output $\nu_t=[-q_t, q_t]$ and use the dynamics of the system without delay.
 
@@
 \subsection{Transient response} 
-\label{asec:transientspecification}
+\label{sec:transientspecification}
 %-------------------------------
-
 \begin{theorem}
-Given a set of eigenvalues for a discrete time model of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1\ n]$, the settling time of the system is upperbounded by
+Given a set of eigenvalues for a discrete time model of an $p^{th}$ order system $\lambda_i =e^{\omega_i}, i \in [1, ...\,,p]$, the settling time of the system is upper-bounded by
 \begin{equation}
-t_s<-log_{\overline{\lambda}}({p_s}) : \overline{\lambda} =\max(|\lambda_i|) \wedge \overline{\lambda}<1,\ \forall i \in [1\ n]
+t_s<-log_{\overline{\lambda}}({P_s}), \text{ where }  \overline{\lambda} = \max(|\lambda_i|) \text{ and } \overline{\lambda}<1,\ \forall i \in [1, ...\,,p]
 \label{eq:set_time}
 \end{equation}
-where $0\leq p_s \leq 1$ is the desired percentage of the target within to remain after $t_s$.
+where $0\leq P_s \leq 1$ is the desired percentage of the target within which the output must remain after $t_s$.
 \end{theorem}
@@
 
-Given a closed loop single output LTI system of order $n$ with dynamics
+Given a closed loop single output LTI system of order $p$ with dynamics
 \begin{equation}
 \left\{\begin{array}{c}\vec{x}_k=\mat{A}\vec{x}_{k-1}\\ \vec{y}_k=\mat{C}\vec{x}_k\end{array}\right.
-\Rightarrow \left\{ \begin{array}{c}\vec{x}_k'=\mat{J}\vec{x}_{k-1}'\\ \vec{y}_k=\mat{C}\mat{S}\vec{x}_k'\end{array}\right.
-: \left\{ \begin{array}{c}\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \\ \vec{x}_k'=\mat{S}^{-1}\vec{x}_k\end{array}\right.
+\Rightarrow \left\{ \begin{array}{c}\vec{x}_k'=\mat{J}\vec{x}_{k-1}'\\ \vec{y}_k=\mat{C}\mat{S}\vec{x}_k'\end{array}\right., \text{ where }  \left\{ \begin{array}{c}\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \\ \vec{x}_k'=\mat{S}^{-1}\vec{x}_k\end{array}\right.
 \label{eq:eigendynamics}
@@
 %
+%\begin{equation}
+%\left\{\begin{array}{c}\vec{x}_T=\mat{A}_T\vec{x}_{0}\\ \vec{y}_T=\mat{C}\vec{x}_T\end{array}\right.
+\Rightarrow \left\{ \begin{array}{c}\vec{x}_T'=\mat{J}_T\vec{x}_{0}'\\ \vec{y}_T=\mat{C}\mat{S}\vec{x}_T'\end{array}\right., \text{ where }  \left\{ \begin{array}{c}\mat{A}_T=\mat{S}\mat{J}_T\mat{S}^{-1} \\ \vec{x}_T'=\mat{S}^{-1}\vec{x}_T\end{array}\right.
+%\label{eq:eigendynamics}
+%\end{equation}
+%
 the output decay is a linear combination of the decay of eigenvalues or
-eigenvalue pairs.  Let $\mat{C}'\in \mathbb{R}^{1 \times n}=\mat{C}\mat{S}$. 
+eigenvalue pairs.  Let $\mat{C}'\in \mathbb{R}^{1 \times p}=\mat{C}\mat{S}$. 
 Since $\mat{C}'$ is constant, the output $y_k$ is a linear combination of
@@
 %
-\begin{align}
-%\vec{x}_k'&=\mat{J}^k\vec{x}_0' \\
-y_k&=\mat{C}'\mat{J}^k\vec{x}_0 = \sum_{i=0}^p \left( c_i \lambda_i^k + c_{il}\binom{k}{l} \lambda_i^{k-l}\right)\\
-|y_k|&\leq \sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right||\lambda_i^k|
-\end{align}
-%
+%Since $\mat{C}'$ is constant, the output $y_T$ is a linear combination of
+%the states $\vec{x}'_T$.  Expanding equation \eqref{eq:eigendynamics} we
+%obtain
+%
+\begin{align}
+y_k&=\mat{C}'\mat{J}^k\vec{x}_0 = \sum_{i=0}^p \left( c_i \lambda_i^k{\vec{x}_0}_i + \sum\limits_{j=1}^{gm(i)}c_{i+j}\binom{k}{j} \lambda_i^{k-j}{\vec{x}_0}_j\right)\\
+|y_k|&\leq \sum_{i=0}^p \left( c_i{\vec{x}_0}_i + \sum\limits_{j=1}^{gm(i)}c_{i+j}\binom{k}{j} \lambda_i^{-j}{\vec{x}_0}_j\right)|\lambda_i^k|
+%y_T&=\mat{C}'\mat{J}_T\vec{x}_0' = \sum_{i=0}^p e^{T\lambda_i}\left( c_i'{\vec{x}_0'}_i + \sum\limits_{j=1}^{gm(i)}c_{i+j}'T^j{\vec{x}_0'}_j\right)
+\end{align}
 where the second  part of the equation corresponds to the upper diagonal
@@
 \begin{align}
-|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right|
-\end{align}
-%
-Since we are synthesising the eigenvalues, rather than solve this formula
-for complex Jordan Shapes, we will restrict our synthesiser to provide
-solutions with distinct eigenvalues (which is by far the most common case). 
-Therefore the right hand terms dissappear and we obtain
-%
-\begin{align}
-|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n |c_i|
+|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^p \left|c_i + \sum\limits_{j=1}^{gm(i)}c_{i+j}\binom{k}{j} \lambda_i^{-j}\right|
+\end{align}
+%
+In the case of closed loop forms without geometric multiplicity (which is by far the most common case),
+the right hand terms disappear and we obtain
+%
+\begin{align}
+|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^p |c_i|
 \end{align}
@@
 %
-\qed
+
+In the case where we allow for geometric multiplicities, we need to compensate for
+the effects of $\binom{k}{j}$ \footnote{tighter bounds can be achieved by evaluating $\frac{\sum\limits_{j=1}^{gm(i)}c_{i+j}\binom{k}{j} \lambda_i^{-j}{\vec{x}_0}_j}{\sum\limits_{j=1}^{gm(i)}c_{i+j}{\vec{x}_0}_j}$}.
+We recall here that our interest is to reach
+within $10\%$ of the final value, and that for a given $k>\underline{k}$ the
+term $\lambda^k$ will converge faster than $\binom{k}{j}$ diverges.
+The requirements for $|\overline{\omega}|$ are calculated as follows:
+\begin{itemize}
+\item Find $\underline{k}=\frac{t_s}{T_s}$ where $t_s$ is the settling time and $T_s$ the sampling time.
+\item Calculate $|\overline{\omega}|=log_{t_s}\left(P_s\binom{\underline{k}}{gm-1}^{-1}\right)$,
+where $gm$ is the maximum desired geometric multiplicity.
+\item Ensure that $|\overline{\omega}| \leq \frac{\underline{k}}{\underline{k}+1}$ and that the
+synthesised closed loop does not have a larger gm than specified.
+\end{itemize}
+%\qed
 \end{proof}

### 2018-01-20 TACAS2018/paper.tex
nudge

@@
 software-implemented embedded controllers along with a model of a physical
-plant (observer).  Due to the complexity of such closed-loop systems, in
-this work we focus on linear models with known configurations, and perform
+plant (observer).  Due to the complexity of such closed-loop systems, we focus
+on linear models with known configurations, and perform
 parametric synthesis of controllers meeting a number of properties that
@@
 
-%The synthesiser uses a discrete time model that relates to the sampling
-%time.  It begins with a very simple abstraction of the real system which
-%only considers the static properties of the model.  It~also uses a very low
-%precision bit vector representation of the real dynamics in order to
-%minimise synthesis time.  
-%% A candidate solution is then passed to a set of verifiers which will
-%% evaluate the synthesised controller over an even more precise
-%% abstraction of the concrete domain in both discrete and continuous
-%% space/time.  The verification phase uses abstraction refinement when needed to ensure
-%% that rejected candidates are not being discarded due to the
-%% over-approximation.
-
-%% The nature of the counterexamples varies depending on
-%% the following conditions:
-%% %
-%% \begin{enumerate}
-%% %
-%% \item Initially, we look for possible errors caused by the restricted domain
-%% of the synthesisers (e.g., overflows and rounding).  These will typically 
-%% manifest in the static properties of the system. If an error is found, the
-%% modeller is signalled to increase the precision of the synthesisers.
-%% %
-%% \item Next we explore the nature of the discrete-time progression to mark
-%% a counterexample that relates to the progression of the system. If such a
-%% counterexample exists, we indicate its initial conditions and time horizon,
-%% thus instructing the synthesiser to refine its abstraction with respect to the
-%% set of initial states and number of iterations. 
-%% %
-%% \item Continuous time analysis indicates the need for decreasing the
-%% sampling time due to continuous excursions outside the safety region in
-%% between samples.  This changes the problem statement of the synthesiser to a
-%% new discrete-time model.
-%% %
-%% \item A final condition arises when a candidate solution cannot be found,
-%% thus requiring higher precision of the abstraction numerical representation. 
-%% We initially consider the plant representation to be too conservative and
-%% may eventually increase the controller FWL specification when no controller
-%% can be found for a given precision.
-%% %
-%% \end{enumerate}
-
 We provide experimental results showing that our approach is able to
@@
 \begin{enumerate}
-
+\item We develop a model for inductive synthesis that combines CEGIS with
+abstraction refinement and synthesis optimization in order to minimize the
+synthesis cost. 
+%
 \item We automatically generate \emph{correct-by-construction} digital
@@
  implementations.
+ %
  \item We present a model for soundly evaluating reachability in a combined 
@@
  combines both. 
-%
-\item We develop a model for inductive synthesis that combines CEGIS with
-abstraction refinement and synthesis optimization in order to minimize the
-synthesis cost. In particular we explore the idea of a multi-tiered model where
-different verification, synthesis and modelling tools/modules explore different
-parts of the problem to deliver an optimal response.
-%
 \end{enumerate}
@@
 
-\note{NOTATIONS BELOW ARE NOT CONSISTENT.}
-
 We consider models of physical plants expressed as ordinary differential
@@
 \label{eq:ode1}
-\dot{x}(t) = \mat{A}x(t)+ \mat{B} u(t), \quad x \in \mathbb{R}^p, u \in \mathbb{R}^q, \mat{A} \in \mathbb{R}^{p \times p}, \mat{B} \in \mathbb{R}^{p \times q},
+\dot{x}(t) = \mat{A}\vec{x}(t)+ \mat{B} \vec{u}(t), \quad \vec{x} \in \mathbb{R}^p, \vec{u} \in \mathbb{R}^q, \mat{A} \in \mathbb{R}^{p \times p}, \mat{B} \in \mathbb{R}^{p \times q},
 \end{align}
@@
 %
-where $k \in \mathbb N$ is a discrete counter and $x_{0}=x(0)$ is the initial state. 
+where $k \in \mathbb N$ is a discrete counter and $\vec{x}_{0}=\vec{x}(0)$ is the initial state. 
 Matrices $\mat{A}_d$, $\mat{B}_d$, $\mat{C}_d$ and $\mat{D}_d$ are equal-sized to $\mat{A}$, $\mat{B}$, $\mat{C}$ and $\mat{D}$ respectively,  
@@
 the internal state $x$ cannot be directly measured,  
-but is rather inferred from its effect on the output $y$ by using an observer.  
-Essentially, a state observer is another dynamical model (below $\hat x$) 
+but is rather inferred from its effect on the output $\vec{y}$ by using an observer.  
+Essentially, a state observer is another dynamical model (below $\hat{\vec{x}}$) 
 that provides an estimate of the internal state $x$ of the given model, 
-from measurements of the input and output of the system. \note{technical details in \ldots}
+from measurements of the input and output of the system (See~\ref{sec:observable}).
 
 A closed-loop digital control system with observer is shown in Figure~\ref{fig:observersystem}. 
-Note that the variables of a state observer are denoted by $x_k$. 
-  Moreover, $y_e=\hat{y}_k - y_k$ is the output estimation error,  
+The feedback controller $\mat{K}$ is driven by the observer state $\hat{\vec{x}}$.
+Moreover, $\vec{y}_e=\hat{\vec{y}}_k - \vec{y}_k$ is the output estimation error,  
 %  defined as the difference between the real output $\vec{y}_k$ and estimated one $\hat{\vec{y}_k}$, 
@@
   Lastly, $k_r$ is a reference gain required by the model.  
-
-     Our goal in this work is to synthesise both $\mat{K}$ and $\mat{L}$. \note{K has not been discussed.}
+  Our goal in this work is to synthesise both $\mat{K}$ and $\mat{L}$.
 
@@
 }
- \caption{Closed-loop digital control system with observer \note{it is unclear what we mean by digital here, we have only discretised time so far.}\label{fig:observersystem2}}
+ \caption{Closed-loop digital control system with observer where the controller and the observer are implemented in a discrete domain\label{fig:observersystem2}}
 \end{figure*}
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++ 
-
  The time discretization in Sec.~\ref{sec:model} only 
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsubsection{Accelerated dynamics for continuous-time models without inputs}\label{sec:cont_acc_no_inputs}
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+ \subsection{Accelerated dynamics for continuous-time models without inputs}\label{sec:cont_acc_no_inputs}
+ %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
  Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a linear function of $\vec{x}_0$ as described below.
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsection{Accelerated dynamics for models with discrete-time feedback inputs}\label{sec:real_discrete_feedback_inputs}
+ \subsection{Accelerated dynamics for models with discrete-time feedback}\label{sec:real_discrete_feedback_inputs}
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 
-We may also bound $\nu_2'$ from \eqref{eq:uk} as follows:
+We may also bound $\nu_2'$ as follows:
 \begin{align*}
@@
 +\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]\left [\begin{array}{c} \vec{r}_k + \vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
-\vec{y}_k=&\mat{C}_{t}\vec{x}_k'% + \mat{D}_{d}\vec{u}_k
+\vec{y}_k=&\mat{C}_d\mat{T}_c\vec{x}_k'% + \mat{D}_{d}\vec{u}_k
 \label{eq:observer_LTI_FWL_cf}
@@
 \mat{A}_{e}=&\mat{T}_o\left(\mat{A}_d-{\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}\mat{C}_e\right)\mat{T}_o^{-1}&
-\mat{C}_{e}=&\mat{C}_d-{\mat{C}_d}_{\langle C \rangle}\\
-\mat{C}_t=&\mat{C}_d\mat{T}_c
+\mat{C}_{e}=&\mat{C}_d-{\mat{C}_d}_{\langle C \rangle}
 \end{align*}
@@
 %%-------------------------------
-Since our synthesisers use abstract aproximations of the real dynamics, our solution is not complete.
-it is possible to have models where a true solution is not found although it exists.
-Soundness is ensured by the verifiers,but once again, since these use over-approximations of the real dynamics, they may also reject valid solutions, hence affecting completeness.
+%Since our synthesisers use abstract aproximations of the real dynamics, our solution is not complete.
+%it is possible to have models where a true solution is not found although it exists.
+%Soundness is ensured by the verifiers,but once again, since these use over-approximations of the real dynamics, they may also reject valid solutions, hence affecting completeness.
 

### 2018-01-23 TACAS2018/paper.tex
abstract editing

@@
 linear, time-invariant models.  Models are defined as differential
-equations with inputs, evolving over a continuous state space. The synthesis 
-accounts for errors caused by the digitization effects introduced by the
-controller.  We use a two-stage counterexample-guided inductive
-synthesis (CEGIS) scheme that driven by abstraction refinement. (1) The first,
-coarse, synthesis stage uses a low-resolution discretized version of the
-original one and, initially, only looks at static properties of the
-model.  (2) The second synthesis stage uses matrix eigen-decomposition 
-and objective functions to iteratively optimize results computed by the first stage.
-Whenever the optimization is unable to yield further results, it feeds back to the
-synthesiser in a traditional CEGIS manner. This design yields a significant
-speed-up compared to a traditional CEGIS scheme (i.e. without optimization).
-We demonstrate the practical value of this approach by automatically synthesizing
-safe observer-based controllers for physical plant models from the
-digital control literature.
+equations with inputs, evolving over a continuous state space. The
+synthesis accounts for errors caused by the digitization effects
+introduced by the controller.  We use an optimization-based
+counterexample-guided inductive synthesis (CEGIS) procedure that is
+driven by abstraction refinement, where in each iteration we take the
+following steps: (1) We start by only considering a low-resolution
+discretized model of the system and only static properties, which
+enables us to find candidate solutions fast.  (2) Once we have a
+candidate, we use matrix eigen-decomposition
+and objective functions to iteratively optimize it.
+%Whenever the optimization is unable to yield further results, it feeds back to the
+%synthesiser in a traditional CEGIS manner.
+This design yields a significant speed-up compared to a traditional
+CEGIS scheme (i.e. without optimization).  We demonstrate the
+practical value of this approach by automatically synthesizing safe
+observer-based controllers for physical plant models from the digital
+control literature.
 %

### 2018-01-23 TACAS2018/paper.tex
+comments for the experimental section

@@
 The models we consider have two sources of error that are due to numerical  
-representation which we commonly refer to as the FWL effect.
+representation which we commonly refer to as FWL effects.
 The first is the numerical error introduced by the
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\note{Add a summary sentence and move the rest to the appendix.}
 In Figure \ref{fig:observersystem2} we introduced
@@
 and modified each possible combination of their parameters by a 10\% tolerance,
-thus creating hundreds of different benchmarks from this base.
+thus creating hundreds \note{how many?} of different benchmarks from this base.
 In the verification module, we have used the tool Axelerator~\cite{} .
@@
 %-------------------------------
+\note{Start with a description of the results, e.g. ``We managed to synthesise controllers in X of the cases. Average time ... In the rest of the cases ...''}.
+
+\note{In order to show the improvements due to our optimization-enhanced CEGIS, we also compared our approach against a standard CEGIS procedure..}
+
+\note{remove some of the subcases of CEGIS and CEGORS. Those that are still used need to be explained in the actual section, not in the table's caption.}
+
 \begin{table}

### 2018-01-23 TACAS2018/paper.tex
edited the synthesis sec

@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Using optimization refinement for CEGIS of control systems}\label{sec:cof_synth}
+%\subsection{Using optimization refinement for CEGIS of control systems}\label{sec:cof_synth}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 We build upon this paradigm to create CEGORS (Counter Example Guided, Optimization
-Refined Synthesis).  The main advantage of this approach, is that by optimizing the
-synthesis results with respect to some objective function, we are able to reduce the
-number of times the loop iterations, thus improving its performance.  Furthermore,
-because later stages of synthesis will use more complex abstractions, the reduction
-is on increasingly expensive formulas and therefore the improvent can be exponential.
+Refined Synthesis) \note{not sure whether we need an acronym for this, we could just call it
+CEGIS with optimization and abstraction refinement}.
+Our approach is illustrated in Figure~\ref{fig:CEGORS} and consists of three main
+phases:
+  \note{explain broadly what each phase does}
+\begin{itemize}
+\item {\sc Abstract}: constructs of an unsound abstract model that over-approximates
+the dynamics of the system.
+\item {\sc synthesize}: generates a candidate controller and observer \note{are these obeying the stability spec?}.
+\item {\sc model}
+\item {\sc verify}: verifies the behaviour of the candidate controller and observer
+  against a sound over-approximation of the concrete dynamics of the system for an infinite space over an infinite time horizon.
+\end{itemize}
+
+The verifier's abstraction uses a CEGAR loop in order to minimise 
+over-approximation errors and provides counterexamples for both
+discrete and continuous dynamics to feed a CEGIS loop on the synthesiser
+waiting for a new candidate solution. \note{not sure about this sentence.
+  Which is the CEGAR loop?}
+
+The main advantage of this approach is two-fold:
+\begin{itemize}
+\item[1.] Optimizing the candidate solution in each
+  iteration of the CEGIS loop by computing the local optimum
+  enables us to obtain high quality counterexamples in the {\sc verify} phase.
+  In turn, this has the potential to reduce the number of iteration of the CEGIS
+  loop required to obtain a solution.
+  \note{probably explain high quality counterexample}
+\item[2.] We start with simpler (i.e. imprecise)
+  abstractions that get
+  refined into more complex ones as the procedure progresses. Thus, solutions
+  that don't require a high level of precision are obtained fast. 
+\end{itemize}
+
+%% because later stages of synthesis will use more complex abstractions, the reduction
+%% is on increasingly expensive formulas and therefore the improvent can be exponential.
+
 %% In order to synthesize closed-loop digital control systems, we use a program
@@
 
-Our approach is illustrated in Figure~\ref{fig:CEGORS}. It relies on the
-construction of an unsound abstract model ({\sc ABSTRACT} phase) that approximates the dynamics
-of the cyber-physical system in order to synthesise a candidate controller
-and observer and then verify their behaviour against a sound over-approximation
-of the concrete dynamics of the system for an infinite space over an infinite
-time horizon.
-The verifier's abstraction uses a CEGAR loop in order to minimise 
-over-approximation errors and provides counterexamples for both
-discrete and continuous dynamics to feed a CEGIS loop on the synthesiser
-waiting for a new candidate solution.
-
-Our CEGORS loop is similar to CEGIS with solution generalization~\cite{david2017program}.
-The novelty of our approach relies on the synthesis refinement phase, which
-enables us to generalise an existing candidate by means of optimisation. Rather
-than allow unsuitable candidates reach the verification phase, and possibly
-require further induction on the synthesiser, we use an optimizing algorithm
-which finds a local minima for the properties of interest.  This reduces the
-chances of the optimised candidate failing verification.  Furthermore, it
-allows us to relax the quality of the synthesis, since unlikely candidates will
-still be optimised during this phase. 
-The optimization is performed on an objective function which will typically depend
-on a subset of the properties.  Hence the chosen optimization function depends
-on which properties fail verification. In our case, the minimal abstraction
-used by the synthesiser almost always ensures stability, so our objective function
-focuses on safety, although we manage to do optimizations that
-simultaneously target safety, stability and response time. This is done by
-making the dynamics as convergent as possible while maintaining the
-verification properties that exclude excesively convergent ones.
+%%  It relies on the
+%% construction of an unsound abstract model ({\sc ABSTRACT} phase) that approximates the dynamics
+%% of the cyber-physical system in order to synthesise a candidate controller
+%% and observer and then verify their behaviour against a sound over-approximation
+%% of the concrete dynamics of the system for an infinite space over an infinite
+%% time horizon.
+
+%Our CEGORS loop is similar to CEGIS with solution generalization~\cite{david2017program}.
+
+%% The novelty of our approach relies on the synthesis refinement phase, which
+%% enables us to generalise an existing candidate by means of optimisation.
+%% Rather
+%% than allow unsuitable candidates reach the verification phase, and possibly
+%% require further induction on the synthesiser, we use an optimizing algorithm
+%% which finds a local minima for the properties of interest.  This reduces the
+%% chances of the optimised candidate failing verification.  Furthermore, it
+%% allows us to relax the quality of the synthesis, since unlikely candidates will
+%% still be optimised during this phase. 
+%% The optimization is performed on an objective function which will typically depend
+%% on a subset of the properties.  Hence the chosen optimization function depends
+%% on which properties fail verification.
+
+During the optimization, the minimal abstraction used by the synthesiser almost
+always ensures stability, so our objective function focuses on safety,
+although we manage to do optimizations that simultaneously target
+safety, stability and response time.
+\note{Are all the
+  candidates computed by {\sc synthesize} stable? State clearly if
+  so. You say ``almost always''.}
+This is done by making the
+dynamics as convergent as possible while maintaining the verification
+properties that exclude excesively convergent ones.
 
@@
 %cannot be found.
-
-The CEGORS loop for this approach is described next.
 
@@
 
-\begin{enumerate}
-\item 
-The {\sc ABSTRACT} module starts by creating an abstraction from the initial specification,
-\begin{enumerate}
+%\begin{enumerate}
+%\item
+
+The CEGORS loop for this approach is described next.
+\paragraph{1. {\sc abstract}} creates an abstraction from the initial specificationas follows:
+\begin{itemize}
 \item Select a sample time that minimizes the magnitudes of the matrices used in both the
@@
 error ($\mat{A}_e$,$\mat{B}_e$), and response time $\phi_{stability}(P_a,P_l,\overline{\lambda})$
-as described in Section~\ref{sec:transientspecification}.
+as described in Section~\ref{sec:transientspecification} \note{broken reference}.
 \item Calculate the noise sets $\eta_1$ and $\eta_2$ from the equations
-described in Section~\ref{sec:FWL_effects}.
+described in Section~\ref{sec:FWL_effects} \note{broken reference}.
 \item Calculate a set of initial bounds on $\mat{K}$, $\phi_\mathit{init}^{K}$,
@@
 \item Select an initial width for the bit vectors representing the controller and the plant $\phi_{\langle C \rangle}, \phi_{\langle P \rangle}$. We will increase either precision as needed.
-\end{enumerate}
+\end{itemize}
+\note{This paragraph needs to be moved before the itemize and it needs to be improved: give an intuition for what $\phi_{static}$ and $\phi_{synth}$ represent, e.g.
+the system's abstraction + stability spec + safety spec...}
 There are two abstractions created by these specifications: $\phi_{synth}$ which is given to the synthesiser and $\phi_{static}$ which is given to the synthesis refinement loop.
@@
 We only note that at all times $\phi_{static} \models \phi_{synth}$.
-
-\item In {\sc synthesize}, we synthesize a candidate controller $\mat{K}$
+%
+%\item
+\paragraph{2. {\sc synthesize}} generates a candidate controller $\mat{K}$
 and observer $\mat{L}$ that satisfy
@@
 %
-\item {\sc Verify Synthesis} verifies $\phi_{static}$ of  both the
-controller and the observer.  If one of these results does not satisfy the tighter
-specification, it feeds back to the {\sc Optimise} phase which optimises
-an objective functiion in order to minimise the magnitude of the error in the verification.
-If the candidate is valid, we feed it to {\sc Discrete Time}.
-
-\item {\sc Optimise} 
+%\item
+\paragraph{3. {\sc Verify Synthesis}} verifies $\phi_{static}$ of  both the
+controller and the observer.  If one of these results does not satisfy this tighter
+specification, it feeds back to the {\sc Optimise} phase.
+If the candidate is valid, we feed it to the next {\sc verify} stage, {\sc Discrete Time}.
+
+%\item
+\paragraph{4. {\sc Optimise}} computes the local optimum in the neighborhood of
+the current candidate solution. \note{is this really a local optimum?}
 % starts by taking $\mat{K},\mat{L} \not \models \phi_{static}$
@@
 % then we proceed to optimise the controller.
-
+%
 Our optimization is iterative, following two stages.  The first stage seeks to
@@
 change in the eigenvectors changes the shape of the space and may cause some 
-trajectories to go further).  In this case, we take the largest eigenvalue and
-reduce it by a factor (smaller than .5) that still satisfies $\phi_{static}$.  The
-resulting observer controller is then verified against the full specification and
-the maximum deviation from the safe region is measured (maximum distance from
-the discovered reach set to the safety region, measured perpendicularly to any
-of the faces of the safe region). 
-While this number is monotonically decreasing we continue to iterate until
-it reaches a negative value (i.e. safe). If the number increases, we change
-our objective function to the second stage.
+trajectories to go further).
+\note{Can we formally define the objective function?}
+
+In this case, we take the largest eigenvalue and reduce it by a factor
+(smaller than .5) that still satisfies $\phi_{static}$.  The resulting
+observer controller is then verified against the full specification
+\note{full specification?}
+and the maximum deviation from the safe region is measured (i.e. maximum
+distance from the discovered reach set to the safety region, measured
+perpendicularly to any of the faces of the safe region).  While this
+number is monotonically decreasing we continue to iterate until it
+reaches a negative value (i.e. safe). If the number increases, we
+change our objective function to the second stage.
+\note{again, formal description? what is the objective function in this stage?}
 
@@
 The resulting closed loop form converges faster than the original and may have a
-smaller rotation, which facilitates meeting the safety specification (we note
+smaller rotation, which facilitates meeting the safety specification
+\note{$\phi_{safety}$?}
+(we note
 that real convergent eigenvalues are trivially safe).
 
-If we cannot synthesise a suitable candidate using optimisation, we signal the
-{\sc Abstract} phase to refine $\phi_{synth}$ and request {\sc Synthesise} to
-produce a new candidate.  Otherwise the refined candidate solution is given back
-to {\sc Verify Synthesis}.
-%
-\item {\sc Discrete Time} verifies $\phi_{safety}^{\infty}$ (unbounded time)
+If we cannot optimize the candidate such that it passes the {\sc
+  verify synthesis} check, we signal the {\sc Abstract} phase to
+refine $\phi_{synth}$ and request {\sc Synthesise} to produce a new
+candidate.  Otherwise the refined candidate solution is given back to
+{\sc Verify Synthesis}.
+%
+%\item
+\paragraph{5. {\sc Discrete Time}} verifies $\phi_{safety}^{\infty}$ (unbounded time)
 using discrete time dynamics.  If the verification fails, we report the
@@
 and iterations that failed the specification.  
-\item {\sc Refine Abstraction} changes $\phi_{safety}$ to encompass any arising
+%\item
+\paragraph{6. {\sc Refine Abstraction}} changes $\phi_{safety}$ to encompass any arising
 counterexample.  This can be done by increasing the time horizon $k$ for the
@@
 %
-\item {\sc Continuous Time} verifies that the
+%\item
+\paragraph{7. {\sc Continuous Time}} verifies that the
 transitions between sample times meet the specification $\phi_{safety}^{\infty}$.  If
@@
 violation to the specification boundary is fed to {\sc Sample}. 
-\item {\sc Sample} will select a smaller suitable sample time and modify the abstractions to meet the discretization. 
+%\item
+\paragraph{8. {\sc Sample}} selects a smaller suitable sample time and modify the abstractions to meet the discretization. 
 It will then feed back to the abstraction refinement loop to look for a suitable action for the updated model.
@@
 
-\item If we reach the {\sc abstract} phase, it means that the candidate
+%\item
+If we reach the {\sc abstract} phase, it means that the candidate
   solution is not valid, in which case we must refine $\phi_{synth}$. If $\phi_{synth}$ cannot be further refined, 
   then we cannot synthesise a new candidate and return a synthesis failure.
-\end{enumerate}
+%\end{enumerate}
 

### 2018-01-23 TACAS2018/paper.tex
moved quantization noise to appendix

@@
 \subsection{Errors generated by numerical representations} 
-\label{sec:numeric_rep}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
+\label{sec:numeric_rep2}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+In Figure \ref{fig:observersystem2} we introduced several sources of noise,
+which are due to quantization effects.  These effects are caused by the use
+of imprecise numerical representations over the reals in the digital domain
+of the controller which is an important consideration when trying to synthesise
+sound controllers.
 The models we consider have two sources of error that are due to numerical  
@@
 $M$.
-%Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point
-%domain with $M$ bits mantissa and $E$ bits exponent.  This domain
-%corresponds to $$\mathbb{R}_{\langle M,[E] \rangle} = \bigcup_F
-%\mathbb{R}_{\langle M,F \rangle} \mid F \in [2^{1-E}, 2^{E-1}]$$ This
-%definition important because it means that the distance between any two
-%numbers in the domain depends on the location of those numbers.  Since
-%a floating point domain is a union of a number of fixed
-%point domains, we will continue our reasoning on fixed point only, which
-%will apply to the floating point domain by extension.  Operations on these
-%numbers will incur errors that can be bound
-%by~\cite{DBLP:conf/arith/BrainTRW15}.
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Modeling quantization as noise} \label{sec:quantization-noise}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\note{Add a summary sentence and move the rest to the appendix.}
-In Figure \ref{fig:observersystem2} we introduced
-several sources of noise, which are due to quantization effects. We now describe
-their nature and create a sound model for them to be used during our synthesis
-and verification process.
-
-%Let us first consider the effect of the quantization errors. 
-%Within the controller, state values are manipulated at low precision.
-%Furthermore, the quantizers for the DAC and the ADC introduce truncation errors
-%which we denote by the effect of the functions $\mathcal{F}_{\langle D \rangle}$
-%and $\mathcal{F}_{\langle A \rangle}$, respectively. Finally, let us call $\vec{\nu}_e$ the
-%error caused by the FWL effects on the observer
-%\todo{the observer was not defined..}
-%(\emph{i.e} the numerical errors 
-%in the calculations as opposed to the estimation error).
-%The inputs are computed using the following equation: 
-%%
-%\begin{align}
-%u_{k}&=\mathcal{F}_{\langle D \rangle}\left(-\mat{K}_{\langle C \rangle}\cdot\left(\mathcal{F}_{\langle C \rangle}\left(\mathcal{F}_{\langle A \rangle}(\vec{x}_{k})\right)\right) +\vec{\nu}_e\right)
-%\label{eq:uk}
-%\end{align}
-%
-%This induces two types of the errors: first, the truncation
-%error due to the domain transformations $\mathcal{F}_{\langle *
-%\rangle}(\cdot)$; and second, the rounding error introduced by the
-%multiplication operation.  We represent these errors as non-deterministic
-%additive noise.
-
-During any given ADC conversion, the continuous signal will be sampled in
-the real domain and transformed by $\mathcal{F}_{\langle A \rangle}
-(x)$. This sampling uses a threshold which is defined by the
-less significant bit ($q_{a}=2^{-F_a}$) 
-of the ADC and some non-linearities of the circuitry.  The overall conversion is
-%
-$$\vec{y}_k=\mathcal{F}_{\langle A \rangle}\left(y(kT_s)\right), \text{ with }  \vec{y}_k \in \left[y(kT_s)-\frac{q_{a}}{2}, y(kT_s)+\frac{q_{a}}{2}\right] \,.$$
-%
-where $t = kT_s$, and $T_s$ is the sampling time and $k$ the current iteration of the loop.
-If we denote the error in the conversion by $\nu_k=y_k-y(t)$, then we may define
-some bounds for it $\nu_k \in [-\frac{q_{a}}{2}, \frac{q_{a}}{2}]$.
-
-We will assume, for the purposes of this analysis, that the domain of the
-ADC is that of the digital controller (i.e, the quantizer includes a digital
-gain added in the code resulting in $\mathbb{R}_{\langle A \rangle}=\mathbb{R}_{\langle C \rangle}$).
-The process of quantization in the DAC is
-similar except that it is calculating $\mathcal{F}_{\langle D\rangle}
-(\mathcal{F}_{\langle C \rangle} (x)) $.  If these domains
-are the same ($\mathbb{R}_{\langle D \rangle}=\mathbb{R}_{\langle C \rangle}$), or if the DAC
-resolution in higher than the ADCs ($\mathbb{R}_{\langle D \rangle}\supseteq\mathbb{R}_{\langle C \rangle}$), then the DAC quantization error is equal
-to zero.  From the above equations we can now define the ADC and DAC
-quantization noises ${\nu_1}_k \in [-\frac{q_a}{2}, \frac{q_a}{2}]$ and
-${\nu_2}_k \in [-\frac{q_d}{2}, \frac{q_d}{2}]$, where given the above assumptions $q_d=q_a=q_c$. 
-This is illustrated in Figure \ref{fig:observersystem2} where $Q_1$ is the quantizer of the ADC
-and $Q_2$ the quantizer for the DAC.  These bounds hold irrespective of
-whether the noise is correlated, hence we may use them to over-approximate
-the noise effect on the state space progression over time.  The
-resulting dynamics are
-%
-\begin{align*}
-%\label{eq:pre_quantization}
-\vec{x}_{k+1} = \mat{A}_d\vec{x}_k+\mat{B}_d({u}_k+{{\nu}_2}_k), \quad u_k = -\mat{K}\vec{x}_{k}+{{\nu}_1}_k, 
-\end{align*}
-%
-which result in the following closed-loop dynamics:
-%
-\begin{align*}
-%\label{eq:quantization}
-\vec{x}_{k+1} &= (\mat{A}_d-\mat{B}_d\mat{K}_d) \vec{x}_k+\mat{B}_d{{\nu}_2}_k +{{\nu}_1}_k \,. 
-\end{align*}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Round-off errors}
-\label{sec:roundoff-noise}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Let $q_*=2^{-F_*}$ be the smallest difference
-between two numbers in their corresponding domains.  Assuming that our
-system truncates numbers to the nearest value, this means that the error
-$\delta$ introduced by the function $\mathcal{F}_{\langle * \rangle}$ is
-$\delta_*=\mathcal{F}_{\langle * \rangle}(x)-x \in \left[-\frac{q_*}{2}, 
-\frac{q_*}{2}\right]$.
-We note that in the case of floating point,the
-choice of $F_*$ is taken from the largest multiplication found (e.g.,
-$\norm{\mat{A}}_1\norm{\vec{x}}_1, \text{ where }  \vec{x} \models \phi_\mathit{safety}$,
-where $\phi_\mathit{safety}$ is defined in \ref{eq:safetyspec}). From these
-equations we can define:
-%
-\begin{align*}
-\nu_1 \in \left[-\frac{q_a}{2}, \frac{q_a}{2}\right] \cap  \left[-\frac{q_c}{2}, \frac{q_c}{2}\right],
-\nu_2 \in \left[-\frac{q_d}{2}, \frac{q_d}{2}\right]
-\end{align*}
-
-We may also bound $\nu_2'$ as follows:
-\begin{align*}
-\delta\left(\mat{K}_{\langle C\rangle} \vec{x}_{\langle C\rangle} \right) &\in \left[ -p \frac{q_c}{2},\, p \frac{q_c}{2}\right]\\
-{\vec{\nu_e}}_i &\in \left[ -(p+2) \frac{q_c}{2}, (p+2) \frac{q_c}{2}\right], i \in [1, ...\,,p]\\
-\Rightarrow \nu_2' &\in \left[  -p(\norm{\mat{K}_{\langle C \rangle}}_1+2) \frac{q_c}{2},\, p(\norm{\mat{K}_{\langle C \rangle}}_1+2) \frac{q_c}{2}\right]
-\end{align*}
-Similarly we also find
-\begin{align*}
-\nu_1' &\in \left[  -p(\norm{{\mat{C}_d}_{\langle C \rangle}}_1+2) \frac{q_c}{2},\, p(\norm{{\mat{C}_d}_{\langle C \rangle}}_1+2) \frac{q_c}{2}\right]
-\end{align*}
-The proof derives from $\norm{\mat{K}\vec{x}}_1 \leq \norm{\mat{K}}_1\norm{\vec{x}}_1$.
-
-%% %-------------------------------
-%% \section{Specification of control systems properties} 
-%% \label{sec:specification}
-%% %-------------------------------
-
-%% %-------------------------------
-%% \subsection{Stability} 
-%% \label{ssec:stabspecification}
-%% %-------------------------------
-
-%% %-------------------------------
-%% \subsection{Safety} 
-%% \label{ssec:safespecification}
-%% %-------------------------------
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \section{Properties of a controllable model with observer}\label{sec:cof_verification}
@@
 designs, in this section we will look at checking stability, safety
-and the response time in the presence of an observer. A full description of
-the theory related to the observer design is provided in appendix \ref{sec:control_theory}.
+and the response time in the presence of an observer. \footnote{A full description of
+the theory related to the observer design is provided in appendix \ref{sec:control_theory}.}
 
@@
 The ability of a system to remain within a bounded set of states is called stability.
-There are different types of stability, such as Bounded Input/Bounded Output (BIBO)
-in which the requirement is that given a bounded input the output remains within
-certain limits, or asymptothic stability in which the output is expected to
-converge to a certain value. In our model, stability is directly related to
-convergence, which means it directly relates to the eigenvalues of the dynamics. 
-In this paper we use Jury's criterion~\ref{sec:closed_stability} to verify stability.
+In this paper, we are interested in
+%% There are different types of stability, such as Bounded Input/Bounded Output (BIBO)
+%% in which the requirement is that given a bounded input the output remains within
+%% certain limits, or
+asymptothic stability, where the output is expected to
+converge to a certain value. %% In our model, we are concerned with the latter
+%% type of stability is directly related to
+%% convergence, which means it directly relates to the eigenvalues of the dynamics.
+As we want to use Jury's criterion~\cite{fadali}\footnote{More details on Jury's criterion can be found in~\ref{sec:closed_stability}}, which is expressed 
+by an easy algebraic formula, we must ... \note{summarise what we do in the rest of this section.}
 
@@
 and modified each possible combination of their parameters by a 10\% tolerance,
-thus creating hundreds \note{how many?} of different benchmarks from this base.
+thus creating seven hundred benchmarks from this base.
 In the verification module, we have used the tool Axelerator~\cite{} .
@@
 \hline
-\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{order} & \multicolumn{1}{|c|}{count} & \multicolumn{2}{|c|}{CEGIS ($\mat{K}$)} & \multicolumn{5}{|c|}{CEGORS($\mat{K}+\mat{L}+T_s$)} \\
-   &                                 & & & \multicolumn{1}{|c|}{-AR1} & \multicolumn{1}{|c|}{-OR} & \multicolumn{1}{|c|}{-AR2} & \multicolumn{1}{|c|}{-OR} & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{Max}\\\hline
-1  & DC Motor          & 2 & 10 & 9.5\,s & 2.1\,s& 1.9\,s& 3.4\,s& 1.2\,s &   3.1\,s &   14.1\,s\\
-2  & Helicopter        & 3  & 10 & \xmark & 1.4\,s& \xmark & \xmark & 6.7\,s  &   18.9\,s & \xmark\\
-3  & Inverted Pendulum & 4 & 10 &   9.7\,s &   0.6\,s& \xmark &112.6\,s& 12.0\,s  &  18.1\,s &  414.0\,s\\
-4  & Magnetic Pointer  & 2  & 10 & \xmark & 44.1\,s& \xmark & \xmark& 4.6\,s  &  39.0\,s &  \xmark \\
+\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{order} & \multicolumn{1}{|c|}{Number of} & \multicolumn{3}{|c|}{CEGIS} & \multicolumn{3}{|c|}{CEGORS} \\
+   &                                 & & \multicolumn{1}{|c|}{benchmarks}  & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{Max} & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{Max}\\\hline
+1  & DC Motor          & 2 & 100 & 9.5\,s & 1.9\,s& \xmark& 1.2\,s &   3.1\,s &   14.1\,s\\
+2  & Helicopter        & 3  & 100 & \xmark & \xmark & \xmark & 6.7\,s  &   18.9\,s & \xmark\\
+3  & Inverted Pendulum & 4 & 100 &   9.7\,s & \xmark &\xmark & 12.0\,s  &  18.1\,s &  414.0\,s\\
+4  & Magnetic Pointer  & 2  & 100 & \xmark & \xmark & \xmark& 4.6\,s  &  39.0\,s &  \xmark \\
 %5 & Magnetic Suspension          & 2 & 1 & 12.2\,s& 0.6\,s & & & N/A  &   N/A &   N/A\\
-5  & Pendulum          & 2 & 10 & 14.0\,s & 0.6\,s& 2.0\,s & 1.5\,s &1.2\,s  &   1.5\,s &   4.3\,s\\
-6  & Suspension        & 4 & 10 & 73.7\,s& 48.3\,s & \xmark & 110.2\,s &24.0\,s  &   46.1\,s &  557.9\,s\\
-7  & Tape Driver       & 3 & 10 & 10.1\,s& 12.4\,s& 140.3\,s &10.5\,s &2.6\,s  &   10.5\,s &   104.6\,s\\
+5  & Pendulum          & 2 & 100 & 14.0\,s & 2.0\,s & \xmark&1.2\,s  &   1.5\,s &   4.3\,s\\
+6  & Suspension        & 4 & 100 & 73.7\,s& \xmark & \xmark &24.0\,s  &   46.1\,s &  557.9\,s\\
+7  & Tape Driver       & 3 & 100 & 10.1\,s& 140.3\,s & \xmark &2.6\,s  &   10.5\,s &   104.6\,s\\
 %9 & Satellite          & 2 & 1 & 9.4\,s& 0.7\,s & & & N/A  &   N/A &   N/A\\
@@
 Experimental results.
-All times are median (except for Min and Max).
-\xmark~indicates failure to find a controller (in the median case it means that more than half of the times we failed to find a controller), either due to timeout or insufficient numeric precision (bitvectors are limited to 64bits).
--AR1 is standard CEGIS, -AR2 uses Solution Generalization but no refinement.
--OR means Abstraction Refinement but no optimization refinement.}
+Minimum, Maximum and Median times for standard CEGIS vs CEGORS on multiple benchmarks.
+\xmark~indicates failure to find a controller, either due to timeout or insufficient numeric precision (bitvectors are limited to 64bits).}
 \end{table}
@@
 More interesting cases appear when we increase the order, showing initially that
-benchmarks that timed-out with AR1 (approx 20mins) are now running in under 2
-minutes using AR2. This is the result of removing several multiplications which are
+benchmarks that timed-out using standard CEGIS are now running in under 2
+minutes using CEGORS. This is the result of removing several multiplications which are
 known to be difficult for SAT solvers.  Furthermore, when we introduce Optimization
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Modeling quantization as noise} \label{sec:quantization-noise}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+In Figure \ref{fig:observersystem2} we introduced
+several sources of noise, which are due to quantization effects. We now describe
+their nature and create a sound model for them to be used during our synthesis
+and verification process.
+
+%Let us first consider the effect of the quantization errors. 
+%Within the controller, state values are manipulated at low precision.
+%Furthermore, the quantizers for the DAC and the ADC introduce truncation errors
+%which we denote by the effect of the functions $\mathcal{F}_{\langle D \rangle}$
+%and $\mathcal{F}_{\langle A \rangle}$, respectively. Finally, let us call $\vec{\nu}_e$ the
+%error caused by the FWL effects on the observer
+%\todo{the observer was not defined..}
+%(\emph{i.e} the numerical errors 
+%in the calculations as opposed to the estimation error).
+%The inputs are computed using the following equation: 
+%%
+%\begin{align}
+%u_{k}&=\mathcal{F}_{\langle D \rangle}\left(-\mat{K}_{\langle C \rangle}\cdot\left(\mathcal{F}_{\langle C \rangle}\left(\mathcal{F}_{\langle A \rangle}(\vec{x}_{k})\right)\right) +\vec{\nu}_e\right)
+%\label{eq:uk}
+%\end{align}
+%
+%This induces two types of the errors: first, the truncation
+%error due to the domain transformations $\mathcal{F}_{\langle *
+%\rangle}(\cdot)$; and second, the rounding error introduced by the
+%multiplication operation.  We represent these errors as non-deterministic
+%additive noise.
+
+During any given ADC conversion, the continuous signal will be sampled in
+the real domain and transformed by $\mathcal{F}_{\langle A \rangle}
+(x)$. This sampling uses a threshold which is defined by the
+less significant bit ($q_{a}=2^{-F_a}$) 
+of the ADC and some non-linearities of the circuitry.  The overall conversion is
+%
+$$\vec{y}_k=\mathcal{F}_{\langle A \rangle}\left(y(kT_s)\right), \text{ with }  \vec{y}_k \in \left[y(kT_s)-\frac{q_{a}}{2}, y(kT_s)+\frac{q_{a}}{2}\right] \,.$$
+%
+where $t = kT_s$, and $T_s$ is the sampling time and $k$ the current iteration of the loop.
+If we denote the error in the conversion by $\nu_k=y_k-y(t)$, then we may define
+some bounds for it $\nu_k \in [-\frac{q_{a}}{2}, \frac{q_{a}}{2}]$.
+
+We will assume, for the purposes of this analysis, that the domain of the
+ADC is that of the digital controller (i.e, the quantizer includes a digital
+gain added in the code resulting in $\mathbb{R}_{\langle A \rangle}=\mathbb{R}_{\langle C \rangle}$).
+The process of quantization in the DAC is
+similar except that it is calculating $\mathcal{F}_{\langle D\rangle}
+(\mathcal{F}_{\langle C \rangle} (x)) $.  If these domains
+are the same ($\mathbb{R}_{\langle D \rangle}=\mathbb{R}_{\langle C \rangle}$), or if the DAC
+resolution in higher than the ADCs ($\mathbb{R}_{\langle D \rangle}\supseteq\mathbb{R}_{\langle C \rangle}$), then the DAC quantization error is equal
+to zero.  From the above equations we can now define the ADC and DAC
+quantization noises ${\nu_1}_k \in [-\frac{q_a}{2}, \frac{q_a}{2}]$ and
+${\nu_2}_k \in [-\frac{q_d}{2}, \frac{q_d}{2}]$, where given the above assumptions $q_d=q_a=q_c$. 
+This is illustrated in Figure \ref{fig:observersystem2} where $Q_1$ is the quantizer of the ADC
+and $Q_2$ the quantizer for the DAC.  These bounds hold irrespective of
+whether the noise is correlated, hence we may use them to over-approximate
+the noise effect on the state space progression over time.  The
+resulting dynamics are
+%
+\begin{align*}
+%\label{eq:pre_quantization}
+\vec{x}_{k+1} = \mat{A}_d\vec{x}_k+\mat{B}_d({u}_k+{{\nu}_2}_k), \quad u_k = -\mat{K}\vec{x}_{k}+{{\nu}_1}_k, 
+\end{align*}
+%
+which result in the following closed-loop dynamics:
+%
+\begin{align*}
+%\label{eq:quantization}
+\vec{x}_{k+1} &= (\mat{A}_d-\mat{B}_d\mat{K}_d) \vec{x}_k+\mat{B}_d{{\nu}_2}_k +{{\nu}_1}_k \,. 
+\end{align*}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Round-off errors}
+\label{sec:roundoff-noise}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Let $q_*=2^{-F_*}$ be the smallest difference
+between two numbers in their corresponding domains.  Assuming that our
+system truncates numbers to the nearest value, this means that the error
+$\delta$ introduced by the function $\mathcal{F}_{\langle * \rangle}$ is
+$\delta_*=\mathcal{F}_{\langle * \rangle}(x)-x \in \left[-\frac{q_*}{2}, 
+\frac{q_*}{2}\right]$.
+We note that in the case of floating point,the
+choice of $F_*$ is taken from the largest multiplication found (e.g.,
+$\norm{\mat{A}}_1\norm{\vec{x}}_1, \text{ where }  \vec{x} \models \phi_\mathit{safety}$,
+where $\phi_\mathit{safety}$ is defined in \ref{eq:safetyspec}). From these
+equations we can define:
+%
+\begin{align*}
+\nu_1 \in \left[-\frac{q_a}{2}, \frac{q_a}{2}\right] \cap  \left[-\frac{q_c}{2}, \frac{q_c}{2}\right],
+\nu_2 \in \left[-\frac{q_d}{2}, \frac{q_d}{2}\right]
+\end{align*}
+
+We may also bound $\nu_2'$ as follows:
+\begin{align*}
+\delta\left(\mat{K}_{\langle C\rangle} \vec{x}_{\langle C\rangle} \right) &\in \left[ -p \frac{q_c}{2},\, p \frac{q_c}{2}\right]\\
+{\vec{\nu_e}}_i &\in \left[ -(p+2) \frac{q_c}{2}, (p+2) \frac{q_c}{2}\right], i \in [1, ...\,,p]\\
+\Rightarrow \nu_2' &\in \left[  -p(\norm{\mat{K}_{\langle C \rangle}}_1+2) \frac{q_c}{2},\, p(\norm{\mat{K}_{\langle C \rangle}}_1+2) \frac{q_c}{2}\right]
+\end{align*}
+Similarly we also find
+\begin{align*}
+\nu_1' &\in \left[  -p(\norm{{\mat{C}_d}_{\langle C \rangle}}_1+2) \frac{q_c}{2},\, p(\norm{{\mat{C}_d}_{\langle C \rangle}}_1+2) \frac{q_c}{2}\right]
+\end{align*}
+The proof derives from $\norm{\mat{K}\vec{x}}_1 \leq \norm{\mat{K}}_1\norm{\vec{x}}_1$.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \section{Control theory} \label{sec:control_theory}

### 2018-01-23 TACAS2018/paper.tex
fixes on Cristinas comments

--- 2018-01-23 TACAS2018/paper.tex
@@
 \mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}+\mat{B}_{e}&\mat{B}_{o}\\ \mat{A}_{e}&\mat{A}_{o}\end{array}\right]&
-\mat{B}'=&\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]
+\mat{B}'=&\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]\\
+\eta_1=&\nu_1+\nu_1'+\nu_t& \eta_2=&\nu_2+\nu_2'
 \end{align*}
 }
+where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations (see Section~\ref{sec:quantization-noise}).
+
 The first effect of this digitalization is that $\mat{A}'$ is no longer upper
@@
 \subsection{Transient response} 
-\label{ssec:transientspecification}
+\label{sec:transientspecification}
 %-------------------------------
@@
 the dynamics of the system.
-\item {\sc synthesize}: generates a candidate controller and observer \note{are these obeying the stability spec?}.
-\item {\sc model}
+\item {\sc synthesize}: generates a candidate controller and observer.  Since
+  we are using coarse approximations, these do not necessarily meet any portion
+  of the specification, but either through optimization or refinement become
+  more precise (therefore more likely to meet the specification) with each iteration.
+\item {\sc model}: refines or redefines the abstractions needed by {\sc Abstract}
+  in order to reduce the probability of failure in the next iteration.
 \item {\sc verify}: verifies the behaviour of the candidate controller and observer
@@
 
-The verifier's abstraction uses a CEGAR loop in order to minimise 
-over-approximation errors and provides counterexamples for both
-discrete and continuous dynamics to feed a CEGIS loop on the synthesiser
-waiting for a new candidate solution. \note{not sure about this sentence.
-  Which is the CEGAR loop?}
+%The verifier's abstraction uses a CEGAR loop in order to minimise 
+%over-approximation errors and provides counterexamples for both
+%discrete and continuous dynamics to feed a CEGIS loop on the synthesiser
+%waiting for a new candidate solution. \note{not sure about this sentence.
+%  Which is the CEGAR loop?}
 
@@
 \begin{itemize}
-\item[1.] Optimizing the candidate solution in each
-  iteration of the CEGIS loop by computing the local optimum
-  enables us to obtain high quality counterexamples in the {\sc verify} phase.
-  In turn, this has the potential to reduce the number of iteration of the CEGIS
-  loop required to obtain a solution.
-  \note{probably explain high quality counterexample}
-\item[2.] We start with simpler (i.e. imprecise)
-  abstractions that get
+\item[1.] Optimizing the candidate solution in each iteration of the CEGIS loop
+  enables us to obtain better candidates that are more likely to meet the
+  specification or fail by a smaller margin.  This has the potential to reduce
+  the number of iteration of the CEGIS loop required to obtain a solution.
+\item[2.] We start with simpler (i.e. imprecise) abstractions that get
   refined into more complex ones as the procedure progresses. Thus, solutions
@@
 
-During the optimization, the minimal abstraction used by the synthesiser almost
-always ensures stability, so our objective function focuses on safety,
-although we manage to do optimizations that simultaneously target
-safety, stability and response time.
-\note{Are all the
-  candidates computed by {\sc synthesize} stable? State clearly if
-  so. You say ``almost always''.}
-This is done by making the
-dynamics as convergent as possible while maintaining the verification
-properties that exclude excesively convergent ones.
+We use two objective functions for optimization.  Both aim at reducing the
+size of the reach space of the closed loop system while maintaining other
+verification properties.  The first one aims at making the system as
+convergent as possible.  This does not only ensure stability, but reduces
+the response time of the system, moving away from the unsafe states faster.
+The second one seeks to minimize rotations.  If the system rotates slower, it
+is less likely to reach unsafe states before converging.
+In both cases, the shape of the eigenspace may affect us negativey, so we
+use a measure of the size of the reach space to guide our optimization.
 
@@
 error ($\mat{A}_e$,$\mat{B}_e$), and response time $\phi_{stability}(P_a,P_l,\overline{\lambda})$
-as described in Section~\ref{sec:transientspecification} \note{broken reference}.
+as described in Section~\ref{sec:transientspecification}.
 \item Calculate the noise sets $\eta_1$ and $\eta_2$ from the equations
-described in Section~\ref{sec:FWL_effects} \note{broken reference}.
+described in Section~\ref{sec:observable}.
 \item Calculate a set of initial bounds on $\mat{K}$, $\phi_\mathit{init}^{K}$,
@@
 %\item
-\paragraph{4. {\sc Optimise}} computes the local optimum in the neighborhood of
-the current candidate solution. \note{is this really a local optimum?}
-% starts by taking $\mat{K},\mat{L} \not \models \phi_{static}$
-% and synthesises $\mat{K}_{\langle C \rangle} = \mat{K}+\mat{\delta}_K, \mat{L}_{\langle C \rangle}=\mat{L}+\mat{\delta}_L$,
-% where $\mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \models \phi_{static}$.  
-% If $\mat{K},\mat{L} \models \phi_{static}$ but we have a counterexample for $\mat{K},\mat{L} \models \phi$,
-% then we proceed to optimise the controller.
-%
+\paragraph{4. {\sc Optimise}} refines the candidate solution towards
+a local optimum.  We seek to minimize the distance of the farthest point in the
+reach space to the closest point to it in the safe region
+\begin{equation}
+e=max(\{min(\{\vec{x}-\vec{g} \mid \vec{g}\in G\}) \mid \vec{x} \in \hat{X}_\infty \}.
+\label{eq:objective}
+\end{equation}
+
 Our optimization is iterative, following two stages.  The first stage seeks to
@@
 trajectories to go further).
-\note{Can we formally define the objective function?}
-
-In this case, we take the largest eigenvalue and reduce it by a factor
-(smaller than .5) that still satisfies $\phi_{static}$.  The resulting
-observer controller is then verified against the full specification
-\note{full specification?}
-and the maximum deviation from the safe region is measured (i.e. maximum
-distance from the discovered reach set to the safety region, measured
-perpendicularly to any of the faces of the safe region).  While this
-number is monotonically decreasing we continue to iterate until it
-reaches a negative value (i.e. safe). If the number increases, we
-change our objective function to the second stage.
-\note{again, formal description? what is the objective function in this stage?}
-
-In the second stage, at each iteration we take the complex eigenvalue
-with the largest phase (largest angle in the complex space), and reduce its
-imaginary component while maintaining the specification $\phi_{static}$.
+
+In this case, we take the largest eigenvalue and reduce it by a factor $f$
+that still satisfies the controller constraints ($f \overline{\lambda} \models \phi_{static}$).
+The resulting observer controller is then verified against the safety specification $\phi_{safety}$
+and the objective $e$ is measured (Equation \eqref{eq:objective}).
+If for each iteration $k$, the objective $e_k<e_{k-1}$, we continue to iterate until 
+$e_k \leq 0$ (i.e. we found a safe controller), otherwise we move to the second stage.
+
+In the second stage, we take the complex eigenvalue
+with the largest angle ($max\{|tan^{-1}\left(\frac{im(\lambda)}{re(\lambda)}\right)| \mid \lambda \in \Lambda\}$)
+and reduce its imaginary component only  ($re(\lambda) + f im(\lambda) \models \phi_{static}$).
 The process ends when no imaginary part can be further reduced.
-The resulting closed loop form converges faster than the original and may have a
-smaller rotation, which facilitates meeting the safety specification
-\note{$\phi_{safety}$?}
-(we note
-that real convergent eigenvalues are trivially safe).
+The resulting closed loop form converges faster than the original and has a
+smaller rotation, which facilitates meeting the safety specification $\phi_{safety}$
+(we note that real convergent eigenvalues are trivially safe).
 
@@
 $\eta_1=\nu_1+\nu_1'+\nu_t$ and $\eta_2=\nu_2+\nu_2'$,
-where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations (see Section~\ref{sec:FWL_effects}).
+where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations (see Section~\ref{sec:quantization-noise}).
 Assuming that the observer dynamics are an exact copy of the real ones, ($\mat{*}_{\langle C \rangle}=\mat{*}$), the closed loop dynamics of this system are given by:
@@
 \subsection{Transient response} 
-\label{sec:transientspecification}
+\label{sec:transientspecificationproof}
 %-------------------------------

### 2018-01-24 TACAS2018/paper.tex
ch 3

@@
 Equations~\eqref{eq:ode1}-\eqref{eq:ode2} are soundly discretized in
-time~\cite{middleton1990digital,van1978computing} at constant intervals whose
-duration we refer to as the sample time (cf. Appendix~\ref{sec:continuous_LTI}) into
+time~\cite{middleton1990digital,van1978computing} at constant intervals, whose 
+duration we refer to as the sample time (cf. Appendix~\ref{sec:continuous_LTI}), 
+into the difference equation 
 \begin{align}
@@
 %, whereas the latter denote the continuous evolution.  
-In this work we make the standard assumption that $\mat{D}_d=\mat{D}=\mat{0}$ \cite{Astrom08}.  
+In this work we raise the standard assumption that $\mat{D}_d=\mat{D}=\mat{0}$ \cite{Astrom08}.  
 %Also, since $\vec{y}$ can be directly derived from $\vec{x}$, we will omit discussing it in the following unless strictly necessary.
@@
 \tau(\vec{x}_k,\vec{u}_k) = 
-\big( \mat{A}\vec{x}_k +
-\mat{B}\vec{u}_k \mid \mat{G}\vec{x}_k \leq \vec{h}\big)\;. 
+\big\{ \mat{A}\vec{x}_k +
+\mat{B}\vec{u}_k \mid \mat{G}\vec{x}_k \leq \vec{h}\big\}\;. 
 \end{equation}
@@
 We generalize this notation to convex sets of initial conditions and inputs ($X_0$ and $U$, respectively), 
-and write $\tau(X_0,U)$ to denote the set of states $\{\vec{x} \mid \vec{x}_0 \in
-X_0 \wedge \vec{u} \in U \wedge \vec{x} = \tau(\vec{x}_0,\vec{u})\}$
+and write $\tau(X_0,U)$ to denote the set of states $\{\vec{x} \mid \vec{x} = \tau(\vec{x}_0,\vec{u}),\, \vec{x}_0 \in
+X_0,\, \vec{u} \in U \}$
 reached from $X_0$ by $\tau$ in one step. 
@@
 \begin{align}\label{equ:reachset}
-\tau^n(X_0,U) = \{\vec{x}_n \mid &\vec{x}_0 \in X_0 \wedge \forall k\in [0,n-1]
-%\nonumber\\ &
-\vec{u}_{k} \in U \wedge \vec{x}_{k+1}=\tau(\vec{x}_{k},\vec{u}_{k}) \} \;. 
+\tau^n(X_0,U) = \{\vec{x}_n \mid & 
+\vec{x}_{k+1}=\tau(\vec{x}_{k},\vec{u}_{k}) \, \forall k\in [0,n-1], \,
+\vec{x}_0 \in X_0, \,
+\vec{u}_{k} \in U  \} \;. 
 \end{align}
@@
 \end{equation}
-as the union of $k$-reach sets over $n$ iterations  (transitive closure). 
+as the union of $k$-reach sets over $n$ iterations (transitive closure \note{the T.Closure refers to the fixpoint, right? That is, it is what is defined next.}). 
 %
@@
 the internal state $x$ cannot be directly measured,  
-but is rather inferred from its effect on the output $\vec{y}$ by using an observer.  
-Essentially, a state observer is another dynamical model (below $\hat{\vec{x}}$) 
+but is rather inferred from its effect on the output $\vec{y}$ using an observer.  
+Essentially, a state observer is another dynamical model (denoted below with variable $\hat{\vec{x}}$) 
 that provides an estimate of the internal state $x$ of the given model, 
@@
 A closed-loop digital control system with observer is shown in Figure~\ref{fig:observersystem}. 
-The feedback controller $\mat{K}$ is driven by the observer state $\hat{\vec{x}}$.
+The feedback controller is driven by the observer state $\hat{\vec{x}}$, 
+and is characterised by a gain matrix $\mat{K}$ \note{has index in figure} that influences the closed-loop dynamics.  
 Moreover, $\vec{y}_e=\hat{\vec{y}}_k - \vec{y}_k$ is the output estimation error,  
 %  defined as the difference between the real output $\vec{y}_k$ and estimated one $\hat{\vec{y}_k}$, 
-  whereas $\mat{L}$ is an error gain matrix that amplifies the output estimation error. 
+  whereas $\mat{L}$ \note{with index in figure} is an error gain matrix that amplifies the output estimation error. 
 Figure~\ref{fig:observersystem} also contains references to $\nu_1$, $\nu_2$, $\nu_1'$, $\nu_2'$ and $\nu_t$, which
@@
 }
- \caption{Closed-loop digital control system with observer where the controller and the observer are implemented in a discrete domain\label{fig:observersystem2}}
+ \caption{Closed-loop digital control system with an observer, where the controller and the observer (bottom part) are implemented in a discrete domain, 
+ whereas the plant is continuous \label{fig:observersystem2}}
 \end{figure*}
@@
  However, in order to synthesise $\mat{K}$ and $\mat{L}$, 
- we must be able to ensure that certain properties of the system hold at any given (real) time. 
- Consequently, we accelerate the dynamics of the system according to the model semantics in Sec.~\ref{sec:model_semantics} in order to compute the state $\vec{x}_T$  at a given time $T$.
-i.e.
-we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$.
+ we must be able to ensure that certain properties of the plant hold at any given real time. 
+ In order to do so, 
+ we accelerate the dynamics of the system according to the model semantics in Sec.~\ref{sec:model_semantics} and compute the state $\vec{x}_T$  at a given time $T$, 
+% namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
+namely the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time $t=T$.
 
@@
  Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a linear function of $\vec{x}_0$ as described below.
- Note that, as the system has no inputs, its dynamics are simply described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.
+We assume that the system has no inputs, and its dynamics are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.
 
@@
  \begin{align}
- \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x}_0\\
+ \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x} (0)\\
  \mat{A}_{T}&= \mat{S}
@@
  \label{eq:continuous_tube_dyn}\\
- &\text{where } s_i=\left\{\begin{array}{cc}1&gm(\lambda_i)>1\\0&gm(\lambda_i)=1\end{array}\right.,\nonumber
- \end{align}
-$\lambda_i \in \mat{J}$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.
-$\vec{x}_T$ is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T.
+ &\text{where } s_i=\left\{\begin{array}{cc}1&\quad gm(\lambda_i)>1\\0&\quad gm(\lambda_i)=1\end{array}\right.,\nonumber
+ \end{align}
+$\lambda_i$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.  
+%$\vec{x}_T$ is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T.
  \end{theorem}
  \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x} \text{ with } k \in \mathbb{R}^+$ is a witness of the system at time $t=kT_d$.
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x} \text{ with } k \in \mathbb{R}^+$ \note{naturals N?} is a witness of the system at time $t=kT_d$.
  \end{corollary}
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- Next, we are interested in observing systems with parametric
- inputs, described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where $\forall t, \mat{B}\vec{u}(t)=\vec{u}(0)$. 
- For such systems, a witness $\vec{x}_T$ is computed next.
+ Next, we are interested in studying models with parametric inputs, 
+ which are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where $\forall t\geq 0, \mat{B}\vec{u}(t)=\vec{u}(0)$. 
+ For such models, a witness $\vec{x}_T$ is computed next.  
+ \note{Need to assume A invertible?}
 \begin{theorem}
@@
  \end{align}
- with $\mat{A}_T$ as per \eqref{eq:continuous_tube_dyn} is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$.
+ with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn}, 
+ is a witness of the model $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$.
  \end{theorem}
  \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}+(\mat{I}-\mat{A}_d^k\mat{B}\vec{u}) \text{ with } k \in \mathbb{R}^+$ is the state of the system at time $kT_d$.
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}+(\mat{I}-\mat{A}_d^k\mat{B}\vec{u}) \text{ with } k \in \mathbb{R}^+$ \note{naturals N?} is the state of the system at time $kT_d$.
  \end{corollary}
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsection{Accelerated dynamics for models with discrete-time feedback}\label{sec:real_discrete_feedback_inputs}
+ \subsection{Accelerated dynamics for models with a sampled-time feedback}\label{sec:real_discrete_feedback_inputs}
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 where the plant dynamics evolve in continuous time while the feedback dynamics evolve in discrete time, 
-namely a new input value is produced only at every sample time.
+namely a new input value is produced only at every sample time but implemented onto the continuous-time plant dynamics. 
+ \note{Need to assume A invertible?}
 %
@@
  with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn}, 
- $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$ and 
- $\mat{A}_d, \mat{B}_d$ describing the discretized plant dynamics is the state of the system
+ and where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$ and 
+ $\mat{A}_d, \mat{B}_d$ describe the discretized plant dynamics, 
+ is the state of the model 
  \begin{align}
  \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
- \vec{u}(t)=\mat{K}\vec{x}_k,  
+ \vec{u}(t)=\mat{K}\vec{x}_k,  \,
  kT_s \leq t < (k+1)T_s. 

### 2018-01-24 TACAS2018/paper.tex
ch 4

@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Modelling Errors in the Control Loop}\label{sec:errors}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{Modelling errors in the control loop}\label{sec:errors}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+A common occurrence in digital systems is that they do not necessarily satisfy real-time specifications, 
+in view of many errors introduced in the dynamics. 
+Errors might results from delays due to processing time,
+corruptions over communication lines in the control loop, 
+approximations due to digitalisation.
 
@@
 
-A common occurrence in digital systems is that they do not necessarily
-satisfy the real-time specifications.  Delays due to processing time,
-communication lines, or other mechanisms will cause disturbances in the
-control loop.  In our model these delays are all deferred to the ZOH, i.e.,
-we presume that everything that happens in the digital world takes place at
-the sampling instance $t$ and the output of the result is delayed at the DAC
-when it is fed back into the real world.  We~will also presume that this
-delay is much smaller than the sampling time.
+In our model delays are all deferred to the ZOH \note{acronym undefined - define these and others, with reference to the Figure 1 above}, 
+i.e., we presume that \note{qualitative: everything that happens in the digital world takes place at
+the sampling instance $t$} and the output of the result is delayed at the DAC 
+when it is fed back into the real world.  
+We will also presume that this delay is much smaller than the sampling time \note{does this assumption make practical sense? why? add reference?}.
 
@@
 \end{align}
-where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$, and $\norm{\vec{x}}_1=\sum_{i=0}^{size(\vec{x})} |\vec{x}_i|$ is the $l_1$ norm (in for sets, $\norm{X}_1 = sup \{\norm{\vec{x}}_1 \mid \vec{x} \in X\}$).
+where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$, and $\norm{\vec{x}}_1=\sum_{i=0}^{size(\vec{x})} |\vec{x}_i|$ is the $l_1$ norm (\note{what?
+unclear?} in for sets, $\norm{X}_1 = sup \{\norm{\vec{x}}_1 \mid \vec{x} \in X\}$).
 \end{theorem}
@@
 The models we consider have two sources of error that are due to numerical  
-representation which we commonly refer to as FWL effects.
+representation which we commonly refer to as FWL \note{undefined acronym} effects.
 The first is the numerical error introduced by the
@@
 $M$. 
-
 We will use the domain $\mathbb{R}_{\langle C \rangle} \text{ where } \langle C \rangle = \langle M_c,F_c \rangle$
@@
 
-Since we are interested in synthesising controllers with observer
-designs, in this section we will look at checking stability, safety
-and the response time in the presence of an observer. \footnote{A full description of
+Since we are interested in synthesising controllers with observers, 
+in this section we will look at checking stability, safety and the response time in the presence of an observer. \footnote{A full description of
 the theory related to the observer design is provided in appendix \ref{sec:control_theory}.}
@@
 observed values using the inverse cosine of the sampling function.
-Since equation \eqref{eq:discretization} models \eqref{eq:dynamical}, we may use the semantics defined in Section
+Since equation \eqref{eq:discretization} models \eqref{eq:dynamical} \note{fix ref}, we may use the semantics defined in Section
 \ref{sec:model_semantics} to analyse continuous dynamical systems.
@@
 \end{align}
-which completes the proof for $gm(\lambda_i)>1$.
+which completes the proof for $gm(\lambda_i)>1$. \qed
 \end{proof}

### 2018-01-24 TACAS2018/paper.tex
changed CEGORS to CEGIS-OR

@@
 
-We build upon this paradigm to create CEGORS (Counter Example Guided, Optimization
-Refined Synthesis) \note{not sure whether we need an acronym for this, we could just call it
-CEGIS with optimization and abstraction refinement}.
-Our approach is illustrated in Figure~\ref{fig:CEGORS} and consists of three main
+We build upon this paradigm to create CEGIS-OR (CEGIS with Optimization
+Refinement).
+Our approach is illustrated in Figure~\ref{fig:CEGIS-OR} and consists of three main
 phases:
@@
 
-%Our CEGORS loop is similar to CEGIS with solution generalization~\cite{david2017program}.
+%Our CEGIS-OR loop is similar to CEGIS with solution generalization~\cite{david2017program}.
 
@@
 
-The CEGORS loop for this approach is described next.
+The CEGIS-OR loop for this approach is described next.
 \paragraph{1. {\sc abstract}} creates an abstraction from the initial specificationas follows:
@@
 stages, blue boxes (dark) are verification stages, and the red box is the synthesis stage.}
-\label{fig:CEGORS}
+\label{fig:CEGIS-OR}
 \end{figure}
@@
 
-\note{remove some of the subcases of CEGIS and CEGORS. Those that are still used need to be explained in the actual section, not in the table's caption.}
+\note{remove some of the subcases of CEGIS and CEGIS-OR. Those that are still used need to be explained in the actual section, not in the table's caption.}
 
@@
 \hline
-\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{order} & \multicolumn{1}{|c|}{Number of} & \multicolumn{3}{|c|}{CEGIS} & \multicolumn{3}{|c|}{CEGORS} \\
+\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{order} & \multicolumn{1}{|c|}{Number of} & \multicolumn{3}{|c|}{CEGIS} & \multicolumn{3}{|c|}{CEGIS-OR} \\
    &                                 & & \multicolumn{1}{|c|}{benchmarks}  & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{Max} & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{Max}\\\hline
@@
 Experimental results.
-Minimum, Maximum and Median times for standard CEGIS vs CEGORS on multiple benchmarks.
+Minimum, Maximum and Median times for standard CEGIS vs CEGIS-OR on multiple benchmarks.
 \xmark~indicates failure to find a controller, either due to timeout or insufficient numeric precision (bitvectors are limited to 64bits).}
@@
 The smaller benchmarks (order=2) tend to show little or no improvement when we
-apply CEGORS.  The reason is that for these benchmarks the synthesis time using
+apply CEGIS-OR.  The reason is that for these benchmarks the synthesis time using
 Solution Generalization is already small, and the overhead of the abstraction is
@@
 benchmarks that timed-out using standard CEGIS are now running in under 2
-minutes using CEGORS. This is the result of removing several multiplications which are
+minutes using CEGIS-OR. This is the result of removing several multiplications which are
 known to be difficult for SAT solvers.  Furthermore, when we introduce Optimization

### 2018-01-25 TACAS2018/paper.tex
editing + comments for the cegis sec

@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Synthesising dynamics}\label{sec:dynamic_synth}
+\section{Synthesising digital controllers with state observers}\label{sec:dynamic_synth}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 engine.
-
+%
 We build upon this paradigm to create CEGIS-OR (CEGIS with Optimization
-Refinement).
-Our approach is illustrated in Figure~\ref{fig:CEGIS-OR} and consists of three main
+and Refinement).
+Our approach is illustrated in Figure~\ref{fig:CEGIS-OR} and consists of four main
 phases:
-  \note{explain broadly what each phase does}
 \begin{itemize}
-\item {\sc Abstract}: constructs of an unsound abstract model that over-approximates
+\item {\sc Abstract}: constructs an unsound abstract model that over-approximates
 the dynamics of the system.
-\item {\sc synthesize}: generates a candidate controller and observer.  Since
-  we are using coarse approximations, these do not necessarily meet any portion
-  of the specification, but either through optimization or refinement become
-  more precise (therefore more likely to meet the specification) with each iteration.
-\item {\sc model}: refines or redefines the abstractions needed by {\sc Abstract}
+\note{what does it mean to be over-approximating but unsound?}
+\item {\sc synthesize}: generates a candidate controller and observer.
+  As it makes use of the potentially coarse abstraction constructed by {\sc Abstract},
+  the candidate doesn't necessarily meet the stability or safety specification.
+  %% these do not necessarily meet any portion
+  %% of the specification, but either through optimization or refinement become
+  %% more precise (therefore more likely to meet the specification) with each iteration.
+\item {\sc model}: refines the abstraction needed by {\sc Abstract}
   in order to reduce the probability of failure in the next iteration.
+  \note{{\sc abstract} doesn't need an abstraction.}
+  \note{how about optimization?}
 \item {\sc verify}: verifies the behaviour of the candidate controller and observer
-  against a sound over-approximation of the concrete dynamics of the system for an infinite space over an infinite time horizon.
+  against a sound over-approximation of the concrete dynamics of the system for an infinite space over an infinite time horizon. If the verification fails, produces a counterexample
+  describing the reason for failure.
 \end{itemize}
+
+\note{this needs to be integrated in the above enumeration}
+Our optimization procedure aims at reducing the
+size of the reach space of the closed loop system while maintaining other
+verification properties. \note{what are other verification properties?
+if you mean safety and stability say so.}
+%% The first one aims at making the system as
+%% convergent as possible.  This does not only ensure stability, but reduces
+%% the response time of the system, moving away from the unsafe states faster.
+%% The second one seeks to minimize rotations.  If the system rotates slower, it
+%% is less likely to reach unsafe states before converging.
+%% In both cases, the shape of the eigenspace may affect us negativey, so we
+%% use a measure of the size of the reach space to guide our optimization.
 
@@
 \begin{itemize}
-\item[1.] Optimizing the candidate solution in each iteration of the CEGIS loop
-  enables us to obtain better candidates that are more likely to meet the
-  specification or fail by a smaller margin.  This has the potential to reduce
-  the number of iteration of the CEGIS loop required to obtain a solution.
-\item[2.] We start with simpler (i.e. imprecise) abstractions that get
+\item[1.] We start with simpler (i.e. imprecise) abstractions that get
   refined into more complex ones as the procedure progresses. Thus, solutions
   that don't require a high level of precision are obtained fast. 
+\item[2.] Although {\sc synthesize} makes use of a potentially coarse abstraction,
+  by optimizing the candidate solution in each iteration of the CEGIS loop
+  we obtain better candidates that are more likely to meet the
+  specification or produce high quality counterexamples in the
+  {\sc verify} phase.
+  This has the potential to reduce
+  the number of iterations of the CEGIS loop required to obtain a solution.
 \end{itemize}
@@
 %% on which properties fail verification.
-
-We use two objective functions for optimization.  Both aim at reducing the
-size of the reach space of the closed loop system while maintaining other
-verification properties.  The first one aims at making the system as
-convergent as possible.  This does not only ensure stability, but reduces
-the response time of the system, moving away from the unsafe states faster.
-The second one seeks to minimize rotations.  If the system rotates slower, it
-is less likely to reach unsafe states before converging.
-In both cases, the shape of the eigenspace may affect us negativey, so we
-use a measure of the size of the reach space to guide our optimization.
 
@@
 
-The CEGIS-OR loop for this approach is described next.
+\note{the next paragraph doesn't sound right, we need to separate the notions
+  of abstraction and specification. they should not be the same. for now, just give an
+intuition and we'll think more...}
+
+The CEGIS-OR loop for this approach is described next.  \note{give an
+  intuition for what $\phi_{static}$ and $\phi_{synth}$ represent,
+  e.g. the system's abstraction + stability spec + safety spec...}
+Note that we make use of two abstractions corresponding to two
+specifications: $\phi_{synth}$ used by the synthesiser and
+$\phi_{static}$ which is given to the synthesis refinement loop. These
+abstractions will be refined independently, so we will not detail what
+each will contain at a given stage. We only note that at all times
+$\phi_{static} \models \phi_{synth}$.
+
 \paragraph{1. {\sc abstract}} creates an abstraction from the initial specificationas follows:
@@
 \end{itemize}
-\note{This paragraph needs to be moved before the itemize and it needs to be improved: give an intuition for what $\phi_{static}$ and $\phi_{synth}$ represent, e.g.
-the system's abstraction + stability spec + safety spec...}
-There are two abstractions created by these specifications: $\phi_{synth}$ which is given to the synthesiser and $\phi_{static}$ which is given to the synthesis refinement loop.
-These abstractions will be refined independently, so we will not detail what each will contain at a given stage.
-We only note that at all times $\phi_{static} \models \phi_{synth}$.
 %

### 2018-01-25 TACAS2018/paper.tex
more editing of the synthesis sec

@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
 In this section, we describe our technique for synthesizing safe
@@
 generalisation based on counterexamples provided by a verification
-engine.
-%
-We build upon this paradigm to create CEGIS-OR (CEGIS with Optimization
-and Refinement).
+engine. In each iteration, an inductive synthesiser produces a
+candidate solution that obeys the specification for a limited number
+of inputs. Subsequently, this candidate is passed to a verification
+oracle that checks it against the specification for all possible
+inputs. If the verification fails, then the witness counterexample is
+passed back to the synthesis phase, where it is added to the set of
+inputs to be considered in the next loop iteration. Otherwise, we are
+done.
+
+%
+We enhance the standard CEGIS architecture with abstraction refinement
+and optimization, resulting in CEGIS-OR (CEGIS with Optimization and
+Refinement).  By using abstraction refinement, CEGIS-OR tackles the
+scalability issues inherent in program synthesis as it allows using
+potentially coarse abstractions of a system that are only refined on
+demand.  Given that the use of coarse abstractions could result in low
+quality candidate solutions (i.e. candidates that fail the
+specification on a very large number of inputs), after each synthesis
+phase we use optimization techniques to improve the produced
+candidates.  In particular, our optimization procedure aims at
+reducing the size of the reach space of the closed loop system while
+maintaining other verification properties. \note{what are other
+  verification properties?  if you mean safety and stability say so.}
+
 Our approach is illustrated in Figure~\ref{fig:CEGIS-OR} and consists of four main
@@
 
-\note{this needs to be integrated in the above enumeration}
-Our optimization procedure aims at reducing the
-size of the reach space of the closed loop system while maintaining other
-verification properties. \note{what are other verification properties?
-if you mean safety and stability say so.}
 %% The first one aims at making the system as
@@
 \begin{itemize}
-\item[1.] We start with simpler (i.e. imprecise) abstractions that get
+\item[1.] We start with coarse abstractions that get
   refined into more complex ones as the procedure progresses. Thus, solutions

### 2018-01-25 TACAS2018/paper.tex
description of properties

@@
 artifacts specific to digital control, such as the effects of
-finite-precision arithmetic, time discretization and quantization errors
+finite-precision arithmetic (referred to here as Finite Word Length or FWL effects), time discretization and quantization errors
 introduced by A/D and D/A conversion.
@@
 on different aspects of discretization, including delayed
-response~\cite{Duggirala2015} and finite word length (FWL) semantics, with
+response~\cite{Duggirala2015} and Finite Word Length (FWL) semantics, with
 the goal either to verify (e.g.,~\cite{daes20161}) or to optimize
@@
 \end{equation}
-as the union of $k$-reach sets over $n$ iterations (transitive closure \note{the T.Closure refers to the fixpoint, right? That is, it is what is defined next.}). 
+as the union of $k$-reach sets over $n$ iterations. 
 %
 Finally, set $\hat{X} =\bigcup_{n\geq 0} \tau^n(X_0,U)$ 
-generalises the previous notions over an unbounded time horizon.
+generalises the previous notions over an unbounded time horizon (transitive closure).
 
@@
 The feedback controller is driven by the observer state $\hat{\vec{x}}$, 
-and is characterised by a gain matrix $\mat{K}$ \note{has index in figure} that influences the closed-loop dynamics.  
+and is characterised by a gain matrix $\mat{K}_{\langle C \rangle}$ that influences the closed-loop dynamics.  
 Moreover, $\vec{y}_e=\hat{\vec{y}}_k - \vec{y}_k$ is the output estimation error,  
 %  defined as the difference between the real output $\vec{y}_k$ and estimated one $\hat{\vec{y}_k}$, 
-  whereas $\mat{L}$ \note{with index in figure} is an error gain matrix that amplifies the output estimation error. 
+  whereas $\mat{L}_{\langle C \rangle}$ is an error gain matrix that amplifies the output estimation error. 
 Figure~\ref{fig:observersystem} also contains references to $\nu_1$, $\nu_2$, $\nu_1'$, $\nu_2'$ and $\nu_t$, which
@@
   Lastly, $k_r$ is a reference gain required by the model.  
-  Our goal in this work is to synthesise both $\mat{K}$ and $\mat{L}$.
+  Our goal in this work is to synthesise both $\mat{K}_{\langle C \rangle}$ and $\mat{L}_{\langle C \rangle}$.
 
@@
  allows us to evaluate the state of the system at integer multiples of the sample time.
- However, in order to synthesise $\mat{K}$ and $\mat{L}$, 
+ However, in order to synthesise $\mat{K}=\mat{K}_{\langle C \rangle}$ and $\mat{L}=\mat{L}_{\langle C \rangle}$, 
  we must be able to ensure that certain properties of the plant hold at any given real time.
@@
  \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x} \text{ with } k \in \mathbb{R}^+$ \note{naturals N?} is a witness of the system at time $t=kT_d$.
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x} \text{ with } T \in \mathbb{R}^+$ is the state of the system at time $t=T$.
  \end{corollary}
@@
  which are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where $\forall t\geq 0, \mat{B}\vec{u}(t)=\vec{u}(0)$. 
- For such models, a witness $\vec{x}_T$ is computed next.  
- \note{Need to assume A invertible?}
+ We will assume $\mat{A}$ is invertible when there are geometric multiplicities $>1$.
+ For such models, a the state $\vec{x}_T$ is computed next.  
 \begin{theorem}
@@
  with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn}, 
- is a witness of the model $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$.
+ is the state of the model $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$.
  \end{theorem}
  \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}+(\mat{I}-\mat{A}_d^k\mat{B}\vec{u}) \text{ with } k \in \mathbb{R}^+$ \note{naturals N?} is the state of the system at time $kT_d$.
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}\vec{u}) \text{ with } T \in \mathbb{R}^+$ is the state of the system at time $T$.
  \end{corollary}
@@
 namely a new input value is produced only at every sample time but implemented onto the continuous-time plant dynamics. 
- \note{Need to assume A invertible?}
+We will assume $\mat{A}$ is invertible, since otherwise $B_T$ would have to be calculated by integration which is impractical.
+
 %
@@
 
-In our model delays are all deferred to the ZOH \note{acronym undefined - define these and others, with reference to the Figure 1 above}, 
-i.e., we presume that \note{qualitative: everything that happens in the digital world takes place at
-the sampling instance $t$} and the output of the result is delayed at the DAC 
-when it is fed back into the real world.  
-We will also presume that this delay is much smaller than the sampling time \note{does this assumption make practical sense? why? add reference?}.
+In our model, delays are all deferred to the Zero Order Holder (ZOH) of the DAC (See Figure \ref{fig:observersystem2}). 
+Everything that happens in the digital world takes place at times $t=kT_s, k \in \mathbb{N}$ (discrete time progression),
+and the output of the result is delayed at the DAC when it is fed back into the continuous time domain at time ($t=kT_s+t_d$).
 
@@
 \end{align}
-where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$, and $\norm{\vec{x}}_1=\sum_{i=0}^{size(\vec{x})} |\vec{x}_i|$ is the $l_1$ norm (\note{what?
-unclear?} in for sets, $\norm{X}_1 = sup \{\norm{\vec{x}}_1 \mid \vec{x} \in X\}$).
+where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$, and $\norm{\vec{x}}_1=\sum_{i=0}^{size(\vec{x})} |\vec{x}_i|$ is the $l_1$ norm (which we extend to sets as $\norm{X}_1 = sup \{\norm{\vec{x}}_1 \mid \vec{x} \in X\}$).
 \end{theorem}
@@
 We over-approximate the effects of this vector by introducing a noise signal at the output $\nu_t=[-q_t, q_t]$ and use the dynamics of the system without delay.
+This noise will be small when the delay is much smaller than the sampling time.
 
@@
 sound controllers.
-The models we consider have two sources of error that are due to numerical  
-representation which we commonly refer to as FWL \note{undefined acronym} effects.
+The models we consider have two sources of error that are due to Finite Word Length (FWL)
+representation.
 The first is the numerical error introduced by the
@@
 The ability of a system to remain within a bounded set of states is called stability.
-In this paper, we are interested in
-%% There are different types of stability, such as Bounded Input/Bounded Output (BIBO)
-%% in which the requirement is that given a bounded input the output remains within
-%% certain limits, or
-asymptothic stability, where the output is expected to
-converge to a certain value. %% In our model, we are concerned with the latter
-%% type of stability is directly related to
-%% convergence, which means it directly relates to the eigenvalues of the dynamics.
+In this paper, we are interested in asymptothic stability, where the output is expected to
+converge to a certain value.  
 As we want to use Jury's criterion~\cite{fadali}\footnote{More details on Jury's criterion can be found in~\ref{sec:closed_stability}}, which is expressed 
-by an easy algebraic formula, we must ... \note{summarise what we do in the rest of this section.}
+by an easy algebraic formula, we transform the model into a representation that contains the desired coefficients expressed as sums of values (no multiplications).
+Such representations are called Controllable and Observable Canonical Forms~\cite{Astrom08} \footnote{See~\ref{sec:reachable} and~\ref{sec:observable}}.
+In this section we explore the implications of using these canonical forms alongside an FWL representation.
 
@@
 \begin{align*}
-\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
+\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_{\langle C \rangle}\right)\mat{T}_c^{-1}&
 \mat{A}_{o}=&\mat{T}_o\left({\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}{\mat{C}_d}_{\langle C \rangle}\right)\mat{T}_o^{-1}\\
@@
 the eigenvalues are smaller too (which we can do with Jury's criterion).
+We will use $\phi_{stability}$ to refer to the combined stability and transient response specifications.
 
@@
 \begin{itemize}
-\item {\sc Abstract}: constructs an unsound abstract model that over-approximates
+\item {\sc Abstract}: constructs an unsound abstract model that approximates
 the dynamics of the system.
-\note{what does it mean to be over-approximating but unsound?}
 \item {\sc synthesize}: generates a candidate controller and observer.
@@
   the candidate doesn't necessarily meet the stability or safety specification.
-  %% these do not necessarily meet any portion
-  %% of the specification, but either through optimization or refinement become
-  %% more precise (therefore more likely to meet the specification) with each iteration.
-\item {\sc model}: refines the abstraction needed by {\sc Abstract}
-  in order to reduce the probability of failure in the next iteration.
-  \note{{\sc abstract} doesn't need an abstraction.}
-  \note{how about optimization?}
+\item {\sc model}: defines the properties needed by {\sc Abstract} and {\sc Optimise} to create 
+  adequate abstractions at each stage in order to reduce the probability
+  of failure in the next iteration.  Our optimization procedure aims at reducing the
+  size of the reach space of the closed loop system while preserving the verification
+  properties (safety, stability and response time).  This phase will first attempt this objective
+  and failing this feed the {\sc Abstract} phase the necessary information to produce a better candidate.
 \item {\sc verify}: verifies the behaviour of the candidate controller and observer
-  against a sound over-approximation of the concrete dynamics of the system for an infinite space over an infinite time horizon. If the verification fails, produces a counterexample
-  describing the reason for failure.
+  against a sound over-approximation of the concrete dynamics of the system for an infinite space over an infinite time horizon.
+If the verification fails, produces a counterexample describing the reason for failure.
 \end{itemize}
-
-%% The first one aims at making the system as
-%% convergent as possible.  This does not only ensure stability, but reduces
-%% the response time of the system, moving away from the unsafe states faster.
-%% The second one seeks to minimize rotations.  If the system rotates slower, it
-%% is less likely to reach unsafe states before converging.
-%% In both cases, the shape of the eigenspace may affect us negativey, so we
-%% use a measure of the size of the reach space to guide our optimization.
-
-%The verifier's abstraction uses a CEGAR loop in order to minimise 
-%over-approximation errors and provides counterexamples for both
-%discrete and continuous dynamics to feed a CEGIS loop on the synthesiser
-%waiting for a new candidate solution. \note{not sure about this sentence.
-%  Which is the CEGAR loop?}
 
@@
 
-\note{the next paragraph doesn't sound right, we need to separate the notions
-  of abstraction and specification. they should not be the same. for now, just give an
-intuition and we'll think more...}
-
-The CEGIS-OR loop for this approach is described next.  \note{give an
-  intuition for what $\phi_{static}$ and $\phi_{synth}$ represent,
-  e.g. the system's abstraction + stability spec + safety spec...}
-Note that we make use of two abstractions corresponding to two
+The CEGIS-OR loop for this approach is described next.
+We make use of two abstractions corresponding to two
 specifications: $\phi_{synth}$ used by the synthesiser and
-$\phi_{static}$ which is given to the synthesis refinement loop. These
-abstractions will be refined independently, so we will not detail what
-each will contain at a given stage. We only note that at all times
-$\phi_{static} \models \phi_{synth}$.
+$\phi_{static}$ which is given to the synthesis refinement loop. 
+Both specifications will be updated during execution and new abstractions will be constructed for each.
+Let us define the properties 
+\begin{align*}
+\phi_{FWL}^C&:= \mat{K}=\mat{K}_{\langle C \rangle} \wedge \mat{L}=\mat{L}_{\langle C \rangle}\\
+\phi_{sample}^{d}&:= \mat{A}_d, \mat{B}_d, \mat{C}_d
+\end{align*}
+We start our loop with 
+\begin{align*}
+\phi_{synth}&:=\phi_{sample}^{d} \wedge \phi_{stability} \wedge \phi_{input} \wedge \phi_{init}\\
+\phi_{static}&:=\phi_{synth} \wedge \phi_{FWL}^C.
+\end{align*}
+When a counterexample is found, we add it to $\phi_{synth} = \phi_{synth} \wedge \phi_{safety}^k$, 
+where k is the iteration found for the counterexample.
+The ${\sc Abstract}$ phase will then construct a abstraction (in the form of a program) that meets this property (unsoundly since the program uses FWL).
+It is also possible, when the modeller is unable to increase $k$, to change $\phi_{synth} = \phi_{synth} \wedge \phi_{sample}^{d'}$ or $\phi_{synth} = \phi_{synth} \wedge \phi_{FWL}^C$.
+What we point out here is that these specifications may grow up to the full specification, thus making for increasingly complex astractions.
+Finally, we also note that the abstract phase uses a given precision ($\phi_{FWL}^P$) which we will increase when no candidates can be generated for a given $\phi_{synth}$.
+In the modeller, $\phi_{static} = \phi_{static} \wedge \phi_{safety}^{k'} \wedge \phi{objective}$ where $k' \geq k$, and $\phi{objective}$ defines a set of rules for the current optimization stage (see {\sc Opimise}).
+We only note that at all times $\phi_{static} \models \phi_{synth}$.
+Let us see how the loop updates these specifications.
 
@@
 
-\note{In order to show the improvements due to our optimization-enhanced CEGIS, we also compared our approach against a standard CEGIS procedure..}
-
-\note{remove some of the subcases of CEGIS and CEGIS-OR. Those that are still used need to be explained in the actual section, not in the table's caption.}
-
 \begin{table}
@@
 
-For the majority of our benchmarks, we observe that our approach is
-significantly faster than using standard CEGIS. We further note the cases where
-standard CEGIS times out, which represent an improvement of several orders of
-magnitude for our optimization approach.  The magnitude of the improvement is 
-largely dependent on the shape of the problem. 
-%When the tighter restriction isdependent on the optimization parameters the overall speed is
+In order to show the improvements due to our optimization-enhanced CEGIS, we
+compared our approach against a standard CEGIS procedure.  For the majority of
+our benchmarks, we observe that our approach is significantly faster than
+standard CEGIS. We further note the cases where standard CEGIS times out, which
+represent an improvement of several orders of magnitude for our optimization
+approach.  The magnitude of the improvement is largely dependent on the shape
+of the problem.
 
@@
  \end{theorem}
- \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x} \text{ with } k \in \mathbb{R}^+$ is the state of the system at time $t=kT_d$.
- \end{corollary}
+  If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x} \text{ with } T \in \mathbb{R}^+$ is the state of the system at time $t=T$.
  \begin{proof}
@@
  \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}+(\mat{I}-\mat{A}_d^k\mat{B}\vec{u}) \text{ with } k \in \mathbb{R}^+$ is the state of the system at time $kT_d$.
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}\vec{u}) \text{ with } k \in \mathbb{R}^+$ is the state of the system at time $kT_d$.
  \end{corollary}

### 2018-01-26 TACAS2018/paper.tex
ch 4

@@
 \tau^n(X_0,U) = \{\vec{x}_n \mid & 
-\vec{x}_{k+1}=\tau(\vec{x}_{k},\vec{u}_{k}) \, \forall k\in [0,n-1], \,
-\vec{x}_0 \in X_0, \,
-\vec{u}_{k} \in U  \} \;. 
+\forall k\in [0,n-1] \, \vec{x}_{k+1}=\tau(\vec{x}_{k},\vec{u}_{k}), \,
+\vec{u}_{k} \in U, \,   
+\vec{x}_0 \in X_0
+\} \;. 
 \end{align}
@@
 the internal state $x$ cannot be directly measured,  
-but is rather inferred from its effect on the output $\vec{y}$ using an observer.  
-Essentially, a state observer is another dynamical model (denoted below with variable $\hat{\vec{x}}$) 
+but is rather inferred from its effect on the output $\vec{y}$ using an observer~~\cite{Astrom08}.  
+Essentially, a state observer is a new dynamical model (with variable denoted below as $\hat{\vec{x}}$) 
 that provides an estimate of the internal state $x$ of the given model, 
-from measurements of the input and output of the system (See~\ref{sec:observable}).
+from measurements of its inputs and outputs (See~\ref{sec:observable}).
 
 A closed-loop digital control system with observer is shown in Figure~\ref{fig:observersystem}. 
-The feedback controller is driven by the observer state $\hat{\vec{x}}$, 
-and is characterised by a gain matrix $\mat{K}_{\langle C \rangle}$ that influences the closed-loop dynamics.  
-Moreover, $\vec{y}_e=\hat{\vec{y}}_k - \vec{y}_k$ is the output estimation error,  
+The linear feedback controller *bottom left) and is characterised by a gain matrix $\mat{K}_{\langle C \rangle}$ that influences the closed-loop dynamics, 
+and is driven by the observer state $\hat{\vec{x}}$.  
+Moreover, $\vec{y}_e=\hat{\vec{y}} - \vec{y}$ is the output estimation error,  
 %  defined as the difference between the real output $\vec{y}_k$ and estimated one $\hat{\vec{y}_k}$, 
-  whereas $\mat{L}_{\langle C \rangle}$ is an error gain matrix that amplifies the output estimation error. 
+ which is amplified by a gain matrix $\mat{L}_{\langle C \rangle}$. 
 Figure~\ref{fig:observersystem} also contains references to $\nu_1$, $\nu_2$, $\nu_1'$, $\nu_2'$ and $\nu_t$, which
@@
   Lastly, $k_r$ is a reference gain required by the model.  
-  Our goal in this work is to synthesise both $\mat{K}_{\langle C \rangle}$ and $\mat{L}_{\langle C \rangle}$.
+  Our goal in this work is to synthesise both $\mat{K}_{\langle C \rangle}$ and $\mat{L}_{\langle C \rangle}$, 
+  so that specific closed-loop properties of the overall interconnection are satisfied.
 
@@
  The time discretization in Sec.~\ref{sec:model} only 
- allows us to evaluate the state of the system at integer multiples of the sample time.
+ allows us to evaluate the state of the plant at integer multiples of the sample time.
  However, in order to synthesise $\mat{K}=\mat{K}_{\langle C \rangle}$ and $\mat{L}=\mat{L}_{\langle C \rangle}$, 
@@
  In order to do so, 
- we accelerate the dynamics of the system according to the model semantics in Sec.~\ref{sec:model_semantics} and compute the state $\vec{x}_T$  at a given time $T$, 
+ we accelerate the dynamics of the plant according to the model semantics in Sec.~\ref{sec:model_semantics} and compute the state $\vec{x}_T$  at a given time $T$, 
 % namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsection{Accelerated dynamics for continuous-time models without inputs}\label{sec:cont_acc_no_inputs}
+ \subsection{Accelerated\! dynamics\! for\! continuous-time\! models\! without\! inputs}\label{sec:cont_acc_no_inputs}
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
  Next, we are interested in studying models with parametric inputs, 
- which are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where $\forall t\geq 0, \mat{B}\vec{u}(t)=\vec{u}(0)$. 
- We will assume $\mat{A}$ is invertible when there are geometric multiplicities $>1$.
+ which are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where $\forall t\geq 0, \mat{B}\vec{u}(t)=\vec{u}$. 
+ We will assume $\mat{A}$ is invertible when there are non-trivial geometric multiplicities.
  For such models, a the state $\vec{x}_T$ is computed next.  
 \begin{theorem}
-The expression
+The state of the model $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$ is 
  \begin{align}
  \vec{x}_T&=\vec{x}(t=T)=\mat{A}^{-1}\vec{x}_T'\nonumber\\
-\vec{x}_T'&=\mat{A}\mat{A}_T\vec{x}_0 + (\mat{I}-\mat{A}_T)\mat{B}\vec{u} \text{ where } \forall t \leq T,\ \vec{u}(t)=\vec{u} 
- \end{align}
- with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn}, 
- is the state of the model $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$.
+\vec{x}_T'&=\mat{A}\mat{A}_T\vec{x}_0 + (\mat{I}-\mat{A}_T)\mat{B}\vec{u} 
+ \end{align}
+ \note{can you simplify in a single line?}
+ where $\forall t \leq T,\ \vec{u}(t)=\vec{u}$,  
+ and $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn}.  
  \end{theorem}
  \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}\vec{u}) \text{ with } T \in \mathbb{R}^+$ is the state of the system at time $T$.
+ If $\mat{J}$ is diagonal and there exists \note{there always exist one, since you define it from A} a discrete matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, 
+ then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}\vec{u}) \text{ with } T \in \mathbb{R}^+$ \note{the formula appears to not be working for T=0 - why?
+Also, it is not clear what the real-power of a matrix A is?} is the state of the system at time $T$.
  \end{corollary}

### 2018-01-26 TACAS2018/paper.tex
ch 4

@@
  \caption{Closed-loop digital control system with an observer, where the controller and the observer (bottom part) are implemented in a discrete domain, 
- whereas the plant is continuous \label{fig:observersystem2}}
+ whereas the plant is continuous \note{comment on C index in some of the matrices} \label{fig:observersystem2}}
 \end{figure*}
@@
 namely the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time $t=T$.
+
+\note{ [add?] In this section we work with fully observed models, namely where $y = x$. }
 
@@
  which are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where $\forall t\geq 0, \mat{B}\vec{u}(t)=\vec{u}$. 
- We will assume $\mat{A}$ is invertible when there are non-trivial geometric multiplicities.
+ We will assume $\mat{A}$ is invertible \note{else?} when there are non-trivial geometric multiplicities \note{why?}.
  For such models, a the state $\vec{x}_T$ is computed next.  
@@
 The final case we analyse is that of hybrid-time models, 
-where the plant dynamics evolve in continuous time while the feedback dynamics evolve in discrete time, 
-namely a new input value is produced only at every sample time but implemented onto the continuous-time plant dynamics. 
-We will assume $\mat{A}$ is invertible, since otherwise $B_T$ would have to be calculated by integration which is impractical.
+where the plant dynamics evolve in continuous time while the feedback dynamics evolve in discrete time.  
+A new input value is produced only at every sample time but implemented over the continuous-time plant dynamics. 
+We assume that $\mat{A}$ is invertible, since otherwise the term $B_T$ below would have to be calculated by integration, which is impractical.
 
@@
  with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn}, 
- and where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$ and 
- $\mat{A}_d, \mat{B}_d$ describe the discretized plant dynamics, 
+ and where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$, 
+ and $\mat{A}_d, \mat{B}_d$ describe the discretized plant dynamics with sample time $T_s$, 
  is the state of the model 
@@
 In our model, delays are all deferred to the Zero Order Holder (ZOH) of the DAC (See Figure \ref{fig:observersystem2}). 
-Everything that happens in the digital world takes place at times $t=kT_s, k \in \mathbb{N}$ (discrete time progression),
-and the output of the result is delayed at the DAC when it is fed back into the continuous time domain at time ($t=kT_s+t_d$).
+In the digital world everything takes place at times $t=kT_s, k \in \mathbb{N}$ (discrete time progression),
+and the output signal is delayed at the DAC when fed back to the continuous-time domain at time ($t=kT_s+t_d$).
 
 \begin{theorem}
-The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modelled as a non-deterministic noise signal upper bound by
+The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modelled as a non-deterministic disturbance signal \note{where is the signal placed?
+is it in  the figure above?} upper bounded by
 \begin{align}
@@
 \end{align}
-where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$, and $\norm{\vec{x}}_1=\sum_{i=0}^{size(\vec{x})} |\vec{x}_i|$ is the $l_1$ norm (which we extend to sets as $\norm{X}_1 = sup \{\norm{\vec{x}}_1 \mid \vec{x} \in X\}$).
+where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$, 
+and $\norm{\vec{x}}_1=\sum_{i=0}^{size(\vec{x})} |\vec{x}_i|$ is the $l_1$ norm, 
+which we extend to sets as $\norm{X}_1 = \sup \{\norm{\vec{x}}_1, \vec{x} \in X\}$. 
 \end{theorem}
-
+%
 \begin{proof}
@@
 \end{proof}
-We over-approximate the effects of this vector by introducing a noise signal at the output $\nu_t=[-q_t, q_t]$ and use the dynamics of the system without delay.
-This noise will be small when the delay is much smaller than the sampling time.
+This results allows to over-approximate the effects of the delay by introducing a disturbance signal $\nu_t=[-q_t, q_t]$ at the output \note{Fig 1?}.
+ %and use the dynamics of the system without delay.  
+ This noise will be small when the delay is much smaller than the sampling time \note{where do you see this in the formula above?}.
 
@@
 
-In Figure \ref{fig:observersystem2} we introduced several sources of noise,
-which are due to quantization effects.  These effects are caused by the use
-of imprecise numerical representations over the reals in the digital domain
-of the controller which is an important consideration when trying to synthesise
-sound controllers.
-The models we consider have two sources of error that are due to Finite Word Length (FWL)
-representation.
-The first is the numerical error introduced by the
-fixed-point numbers employed to model the plant, i.e., to represent the
-plant dynamics $A_d$, $B_d$, $C_d$, $D_d$, $x_k$ and $y_k$.
-The second is the quantization error
-introduced by the digital controller, which performs operations on
-fixed-point numbers.  In this section we outline the notation for the
-representation of numbers, and briefly describe the errors
-introduced.  A~formal discussion is in
-Appendix~\ref{sec:numeric_rep}.
+In Figure \ref{fig:observersystem2} we have introduced sources of noise that are due to quantization effects.  
+These effects are caused by imprecise numerical representations of real numbers in the digital domain of the controller: 
+these play an important role in the synthesis of sound controllers. 
+The model has two sources of error are due to Finite Word Length (FWL) representations. 
+The first is the numerical error introduced by the fixed-point numbers employed to model the plant, 
+i.e., to represent the plant dynamics $A_d$, $B_d$, $C_d$, $D_d$, $x_k$ and $y_k$. 
+The second is the quantization error introduced by the digital controller, 
+which performs operations over fixed-point numbers.  
+In this section we outline the notation for the finite representation of numbers, 
+and briefly describe the introduced errors.  
+A formal discussion is in Appendix~\ref{sec:numeric_rep}.
 
@@
 representing the binary word length of the representation and $F$ bits
-representing the prescaling $2^{-F}$ (\emph{i.e} the number of bits after
+representing the pre-scaling $2^{-F}$ (\emph{i.e} the number of bits after
 the decimal place).  We note that a negative $F$ denotes an integer
@@
 to represent the domain of a digital model of the dynamics of a real plant when
-evaluated by a verification tool.
-Thus, any mathematical operations in our modelled digital controller will be executed in the
+evaluated by a verification tool. \note{refer back to notation in Figure 1.}
+Thus, any mathematical operation within the digital controller is executed in the
 domain $\mathbb{R}_{\langle C \rangle}$, and all other calculations
 in our model will be carried out in the domain $\mathbb{R}_{\langle P \rangle}$.
-Given ${\langle M,F \rangle}$ we use $\mathcal{F}_{\langle M,F \rangle} : \mathbb{R} \rightarrow \mathbb{R}_{\langle M,F \rangle}$ as the truncation function.
+Given ${\langle M,F \rangle}$, 
+we denote as $\mathcal{F}_{\langle M,F \rangle} : \mathbb{R} \rightarrow \mathbb{R}_{\langle M,F \rangle}$ the corresponding truncation function.
 
@@
 Since we are interested in synthesising controllers with observers, 
-in this section we will look at checking stability, safety and the response time in the presence of an observer. \footnote{A full description of
-the theory related to the observer design is provided in appendix \ref{sec:control_theory}.}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Stability of an observed system with FWL effects}\label{sec:cof_fwl_stability}
+in this section we will look at checking stability, safety and the response time in the presence of an observer.\footnote{A full description of
+the theory related to observer design is in Appendix \ref{sec:control_theory}.}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Stability of an observed model with FWL effects}\label{sec:cof_fwl_stability}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 converge to a certain value.  
-As we want to use Jury's criterion~\cite{fadali}\footnote{More details on Jury's criterion can be found in~\ref{sec:closed_stability}}, which is expressed 
+As we want to use Jury's criterion~\cite{fadali}\footnote{More details on Jury's criterion is in Appendix~\ref{sec:closed_stability}}, which is expressed 
 by an easy algebraic formula, we transform the model into a representation that contains the desired coefficients expressed as sums of values (no multiplications).
-Such representations are called Controllable and Observable Canonical Forms~\cite{Astrom08} \footnote{See~\ref{sec:reachable} and~\ref{sec:observable}}.
+Such representations are called Controllable and Observable Canonical Forms~\cite{Astrom08} \footnote{See parts~\ref{sec:reachable} and~\ref{sec:observable} in the Appendix}.
 In this section we explore the implications of using these canonical forms alongside an FWL representation.

### 2018-01-26 TACAS2018/paper.tex
ch 4

@@
 
-The ability of a system to remain within a bounded set of states is called stability.
-In this paper, we are interested in asymptothic stability, where the output is expected to
-converge to a certain value.  
-As we want to use Jury's criterion~\cite{fadali}\footnote{More details on Jury's criterion is in Appendix~\ref{sec:closed_stability}}, which is expressed 
-by an easy algebraic formula, we transform the model into a representation that contains the desired coefficients expressed as sums of values (no multiplications).
-Such representations are called Controllable and Observable Canonical Forms~\cite{Astrom08} \footnote{See parts~\ref{sec:reachable} and~\ref{sec:observable} in the Appendix}.
-In this section we explore the implications of using these canonical forms alongside an FWL representation.
-
-In this section, we assume that the observer model is further discretised in
-the value domain, i.e., the domain for both
-the controller and the observer is $\mathbb{R}_{\langle C \rangle}$.
+Stability denotes the property of a model to remain within a bounded set of states around an equilibrium point. 
+In this paper, we are interested in asymptotic stability, where the output is expected to converge to a certain steady state value.  
+We specify model stability via Jury's criterion~\cite{fadali}\footnote{More details on Jury's criterion is in Appendix~\ref{sec:closed_stability}}, 
+which allows for an expression with an algebraic formula. 
+We transform the model into a representation that contains the desired coefficients expressed as sums of values (with no multiplications).  
+Such a representation is called Controllable and Observable Canonical Form~\cite{Astrom08} \footnote{See parts~\ref{sec:reachable} and~\ref{sec:observable} in the Appendix}.  
+In this Section we explore the implications of using these canonical forms alongside an FWL representation.
+
+We assume that the domain of the observer model is further discretised, 
+i.e., the domain for both the controller and the observer is $\mathbb{R}_{\langle C \rangle}$.
 This means that we have 
@@
 \mathbb{R}_{\langle C \rangle}^*$ where $*$ represents the appropriate
-dimension for each matrix.  Unfortunately this means that although combined
-matrices such as $\mat{A}_c$ are in the reals, they suffer from the fixed
-word restrictions in their composing matrices.
-
-When our observer is implemented using a finite precision controller, new
+dimension for each matrix.  \note{unclear next:} Unfortunately this means that although combined
+matrices such as $\mat{A}_c$ are in the reals, they suffer from the fixed-word restrictions in their composing matrices.
+
+When our observer is implemented using a finite-precision controller, new
 problems arise due to the FWL effects.  Let ${\mat{A}_d}_{\langle C
@@
 +\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]\left [\begin{array}{c} \vec{r}_k + \vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
-\vec{y}_k=&\mat{C}_d\mat{T}_c\vec{x}_k'% + \mat{D}_{d}\vec{u}_k
+\vec{y}_k=&\mat{C}_d\mat{T}_c\vec{x}_k', 
+% + \mat{D}_{d}\vec{u}_k
 \label{eq:observer_LTI_FWL_cf}
@@
 \mat{B}'=&\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]\\
-\eta_1=&\nu_1+\nu_1'+\nu_t& \eta_2=&\nu_2+\nu_2'
+\eta_1=&\nu_1+\nu_1'+\nu_t& \eta_2=&\nu_2+\nu_2',
 \end{align*}
 }
+\note{it is very hard if not impossible to understand these operations without having thoroughly gone through the whole Appendix, which is unlikely for a reviewer to do.}
 where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations (see Section~\ref{sec:quantization-noise}).
@@
 \begin{align}
-  \phi_\mathit{safety}\equiv& \underline{y} \leq y_k \leq \overline{y}
-\iff \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
+  \phi_\mathit{safety}: = & \underline{y} \leq y_k \leq \overline{y}
+\equiv \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
 \label{eq:safetyspec}
@@
 Note that FWL effects are not explicitly captured here
-as they are implicit from equation \ref{eq:observer_LTI_FWL_cf}.
+as they are implicit from Equation \ref{eq:observer_LTI_FWL_cf}.
 %% We assume that we do not want saturation in our
@@
 signal $u_{k}$ and $\phi_\mathit{init}$ on the initial states $x_0$,
-which we assume have given bounds:
-$\phi_\mathit{input}\equiv \underline{u} \leq u_k \leq \overline{u}$
-which comes from physical restrictions in the energy of the system, and
+which we assume have given bounds, namely 
+$\phi_\mathit{input} := \underline{u} \leq u_k \leq \overline{u}$, 
+which comes from physical restrictions in the energy of the system; and
 $\phi_\mathit{init}\equiv \mat{G}' \vec{x}_0 \leq \vec{h}'$,

### 2018-01-26 TACAS2018/paper.tex
sec 6

@@
 \end{align}
+\note{what is ts, as opposed to Ts?}
 where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$, 
@@
 which allows for an expression with an algebraic formula. 
-We transform the model into a representation that contains the desired coefficients expressed as sums of values (with no multiplications).  
+We transform the model into a representation that contains \note{unclear next} the desired coefficients expressed as sums of values (with no multiplications) \note{why is this form important?}.  
 Such a representation is called Controllable and Observable Canonical Form~\cite{Astrom08} \footnote{See parts~\ref{sec:reachable} and~\ref{sec:observable} in the Appendix}.  
@@
 \mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \in
-\mathbb{R}_{\langle C \rangle}^*$ where $*$ represents the appropriate
+\mathbb{R}_{\langle C \rangle}^*$, where $*$ represents the appropriate
 dimension for each matrix.  \note{unclear next:} Unfortunately this means that although combined
@@
 \rangle}$ be the dynamics represented in $\mathbb{R}_{\langle C\rangle}^*$,
-Equation \eqref{eq:observer_LTI_cf} becomes:
+\note{You cannot refer to a formula in the appendix} Equation \eqref{eq:observer_LTI_cf} becomes:
 %
@@
 \end{align}
-where $\mat{T}_c$ and $\mat{T}_o$ trasfrom the system into canonical form~\cite{Astrom08} and
+\note{what is the meaning of the new dashed variables?}
+where $\mat{T}_c$ and $\mat{T}_o$ trasform the system into canonical form~\cite{Astrom08} \note{this statement will not be understood} and
 {\setlength{\abovedisplayskip}{2pt}
@@
 
+\note{the remainder of this section is not self contained and totally unclear.}
+
 The first effect of this digitalization is that $\mat{A}'$ is no longer upper
-diagonal.  We must therefore compensate for the errors introduced in order
+diagonal \note{you mean, unlike the Cont-Obs form of A -- this will not be clear to the reader.}.  We must therefore compensate for the errors introduced in order
 to find a stable solution.  We can use Gershgorin disks~\cite{van1996matrix} to limit the error
@@
 %-------------------------------
-In many cases the speed of the response, i.e. how fast it converges to the set point, is a requirement of great importance. 
-This is given as a settling time for the system to become stable.
+In many cases the speed of the response \note{you mean the step response - this concept is undefined}, i.e. how fast it converges to the set point, is a requirement of great importance. 
+This is given as a ``settling time.''
 
@@
 \end{equation}
-where $0\leq P_s \leq 1$ is the desired percentage of the target within which the output must remain after $t_s$.
+\note{you are assuming that the DT model has stable dynamics?}
+where $0\leq P_s \leq 1$ is the desired percentage \note{you mean portion?} of the target within which the output must remain after $t_s$.
 \end{theorem}

### 2018-01-26 TACAS2018/paper.tex
sec 6

@@
 In this section, we describe our technique for synthesizing safe
-digital feedback controllers using CEGIS. Broadly speaking, CEGIS
+digital feedback controllers using CEGIS \note{add ref}. Broadly speaking, CEGIS
 denotes an iterative technique where each iteration performs inductive
@@
 candidates.  In particular, our optimization procedure aims at
-reducing the size of the reach space of the closed loop system while
+reducing the size of the reach space \note{define reach space} of the closed loop system while
 maintaining other verification properties. \note{what are other
@@
 The benchmark suite employed to evaluate the proposed technique is 
-composed by 7 SISO models extracted from the literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15,maglev,converters}.
+composed by seven SISO \note{defined SISO} models extracted from the control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15,maglev,converters}.
 In order to obtain statistically relevant results, we have taken these models

### 2018-01-27 TACAS2018/paper.tex
Alessandro's comments

@@
 %
-Finally, set $\hat{X} =\bigcup_{n\geq 0} \tau^n(X_0,U)$ 
-generalises the previous notions over an unbounded time horizon (transitive closure).
+Finally, set $\hat{X} =\bigcup_{n\geq 0} \tau^n(X_0,U)$ which we refer to as
+the reach space of the system generalises the previous notions over an unbounded
+time horizon (transitive closure).
 
@@
 }
- \caption{Closed-loop digital control system with an observer, where the controller and the observer (bottom part) are implemented in a discrete domain, 
- whereas the plant is continuous \note{comment on C index in some of the matrices} \label{fig:observersystem2}}
+ \caption{Closed-loop digital control system with an observer, where the controller and the observer (bottom part) are implemented in a discrete domain (identified by the subindex $\langle C \rangle$), whereas the plant is continuous \label{fig:observersystem2}}
 \end{figure*}
@@
  which are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where $\forall t\geq 0, \mat{B}\vec{u}(t)=\vec{u}$. 
- We will assume $\mat{A}$ is invertible \note{else?} when there are non-trivial geometric multiplicities \note{why?}.
  For such models, a the state $\vec{x}_T$ is computed next.  
@@
  \begin{align}
- \vec{x}_T&=\vec{x}(t=T)=\mat{A}^{-1}\vec{x}_T'\nonumber\\
-\vec{x}_T'&=\mat{A}\mat{A}_T\vec{x}_0 + (\mat{I}-\mat{A}_T)\mat{B}\vec{u} 
- \end{align}
- \note{can you simplify in a single line?}
- where $\forall t \leq T,\ \vec{u}(t)=\vec{u}$,  
- and $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn}.  
+ \vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u} \text{ where } \mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B} 
+ \end{align}
+ where $\forall t \leq T,\ \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn}
+ \footnote{when $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$}.
  \end{theorem}
  \begin{corollary}
- If $\mat{J}$ is diagonal and there exists \note{there always exist one, since you define it from A} a discrete matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, 
- then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}\vec{u}) \text{ with } T \in \mathbb{R}^+$ \note{the formula appears to not be working for T=0 - why?
-Also, it is not clear what the real-power of a matrix A is?} is the state of the system at time $T$.
+ If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, 
+ then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u}) \text{ with } T \in \mathbb{R}_0^+$ (where $\mat{A}_d^{\frac{T}{T_d}} = e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the system at time $T$.
  \end{corollary}
@@
 \begin{theorem}
-The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modelled as a non-deterministic disturbance signal \note{where is the signal placed?
-is it in  the figure above?} upper bounded by
+The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modelled as a non-deterministic disturbance signal ($\nu_t$ in Figure \ref{fig:observersystem2}) upper bounded by
 \begin{align}
@@
 \end{align}
-\note{what is ts, as opposed to Ts?}
-where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$, 
+where $\vec{y}_{t_d}$ is the output of the system with delay $t_d$, $t_s=T_s-t_d$,
 and $\norm{\vec{x}}_1=\sum_{i=0}^{size(\vec{x})} |\vec{x}_i|$ is the $l_1$ norm, 
@@
 \end{proof}
-This results allows to over-approximate the effects of the delay by introducing a disturbance signal $\nu_t=[-q_t, q_t]$ at the output \note{Fig 1?}.
+This results allows to over-approximate the effects of the delay by introducing a disturbance signal $\nu_t=[-q_t, q_t]$ at the output.
  %and use the dynamics of the system without delay.  
- This noise will be small when the delay is much smaller than the sampling time \note{where do you see this in the formula above?}.
+ This noise will be small when the delay is much smaller than the sampling time ($t_s\approx T_s$ and $\mat{B}_{t_d} \approx 0$).
 
@@
 which allows for an expression with an algebraic formula. 
-We transform the model into a representation that contains \note{unclear next} the desired coefficients expressed as sums of values (with no multiplications) \note{why is this form important?}.  
+We transform the model into a representation that contains the coefficients of the characteristic polynomial (used by Jury's criterion) expressed as sums of controller and plant values (with no multiplications, which are expensive for the SAT solver).
 Such a representation is called Controllable and Observable Canonical Form~\cite{Astrom08} \footnote{See parts~\ref{sec:reachable} and~\ref{sec:observable} in the Appendix}.  
@@
 \mathbb{R}_{\langle C \rangle}^*$, where $*$ represents the appropriate
-dimension for each matrix.  \note{unclear next:} Unfortunately this means that although combined
-matrices such as $\mat{A}_c$ are in the reals, they suffer from the fixed-word restrictions in their composing matrices.
-
-When our observer is implemented using a finite-precision controller, new
-problems arise due to the FWL effects.  Let ${\mat{A}_d}_{\langle C
-\rangle}$, ${\mat{B}_d}_{\langle C \rangle}$ and ${\mat{C}_d}_{\langle C
-\rangle}$ be the dynamics represented in $\mathbb{R}_{\langle C\rangle}^*$,
-\note{You cannot refer to a formula in the appendix} Equation \eqref{eq:observer_LTI_cf} becomes:
+dimension for each matrix.
+New problems arise due to the FWL effects on these matrices.  The Canonical
+form of the resulting system is expressed by the formula:
 %
@@
 \end{align}
-\note{what is the meaning of the new dashed variables?}
-where $\mat{T}_c$ and $\mat{T}_o$ trasform the system into canonical form~\cite{Astrom08} \note{this statement will not be understood} and
+where $\mat{T}_c$ and $\mat{T}_o$ trasform the system into Canonical Form~\cite{Astrom08}, $\vec{x}'$ and $\vec{x}_e'$ are the state of the system and the error of the observer evaluated in the transformed domain \note{this statement will not be understood} and
 {\setlength{\abovedisplayskip}{2pt}
@@
 
-The first effect of this digitalization is that $\mat{A}'$ is no longer upper
-diagonal \note{you mean, unlike the Cont-Obs form of A -- this will not be clear to the reader.}.  We must therefore compensate for the errors introduced in order
-to find a stable solution.  We can use Gershgorin disks~\cite{van1996matrix} to limit the error
+The first effect of this digitalization is that $\mat{A}'$ is not upper
+diagonal (if $\mat{A}_e$ were $0$ we could analize the eigenvalues of $\mat{A}_c+\mat{B}_e$ and $\mat{A}_o$ separately).
+We must therefore compensate for the errors introduced in order
+to find a stable solution (since our criteria are based on the above separation).  
+We can use Gershgorin disks~\cite{van1996matrix} to limit the error
 in the expected eigenvalues.  Let $\delta_o=\max(\norm{{\mat{A}_e}_{i,*}}_1)$
@@
 \begin{theorem}
-Given a set of eigenvalues for a discrete time model of an $p^{th}$ order system $\lambda_i =e^{\omega_i}, i \in [1, ...\,,p]$, the settling time of the system is upper-bounded by
+Given a set of eigenvalues for a discrete time model of a $p^{th}$ order stable system $\{\lambda_i =e^{\omega_i} \mid i \in [1, ...\,,p], |\lambda_i| \leq 1 \}$, the settling time of the system is upper-bounded by
 \begin{equation}
@@
 \end{equation}
-\note{you are assuming that the DT model has stable dynamics?}
-where $0\leq P_s \leq 1$ is the desired percentage \note{you mean portion?} of the target within which the output must remain after $t_s$.
+where $0\leq P_s \leq 1$ is the desired portion of the target within which the output must remain after $t_s$.
 \end{theorem}
@@
 In this section, we describe our technique for synthesizing safe
-digital feedback controllers using CEGIS \note{add ref}. Broadly speaking, CEGIS
+digital feedback controllers using CEGIS~\cite{DBLP:conf/asplos/2006}. Broadly speaking, CEGIS
 denotes an iterative technique where each iteration performs inductive
@@
 candidates.  In particular, our optimization procedure aims at
-reducing the size of the reach space \note{define reach space} of the closed loop system while
-maintaining other verification properties. \note{what are other
-  verification properties?  if you mean safety and stability say so.}
+reducing the size of the reach space of the closed loop system while
+maintaining other verification properties (safety, stability, and response time).
 

### 2018-01-27 TACAS2018/paper.tex
Moved property updates to corresponding sections

@@
 \begin{align*}
-\phi_{FWL}^C&:= \mat{K}=\mat{K}_{\langle C \rangle} \wedge \mat{L}=\mat{L}_{\langle C \rangle}\\
-\phi_{sample}^{d}&:= \mat{A}_d, \mat{B}_d, \mat{C}_d
+\phi_{\langle C \rangle}&:= \mat{K}=\mat{K}_{\langle C \rangle} \wedge \mat{L}=\mat{L}_{\langle C \rangle}\\
+\phi_{dynamics}^{T_d}&:= \mat{A}_d, \mat{B}_d, \mat{C}_d
 \end{align*}
+The first one defines the word length of the digital controller ($\mathbb{R}_{\langle C \rangle}$) and its effect on the system dynamics.
+The second one defines the sampling time ($T_d$) and its effect on the system dynamics (as per Section \ref{sec:continuous_time_accel}).
 We start our loop with 
 \begin{align*}
-\phi_{synth}&:=\phi_{sample}^{d} \wedge \phi_{stability} \wedge \phi_{input} \wedge \phi_{init}\\
-\phi_{static}&:=\phi_{synth} \wedge \phi_{FWL}^C.
+\phi_{synth}&:=\phi_{dynamics}^{T_d} \wedge \phi_{stability} \wedge \phi_{input} \wedge \phi_{init}\\
+\phi_{static}&:=\phi_{synth} \wedge \phi_{\langle C \rangle}.
 \end{align*}
-When a counterexample is found, we add it to $\phi_{synth} = \phi_{synth} \wedge \phi_{safety}^k$, 
-where k is the iteration found for the counterexample.
-The ${\sc Abstract}$ phase will then construct a abstraction (in the form of a program) that meets this property (unsoundly since the program uses FWL).
-It is also possible, when the modeller is unable to increase $k$, to change $\phi_{synth} = \phi_{synth} \wedge \phi_{sample}^{d'}$ or $\phi_{synth} = \phi_{synth} \wedge \phi_{FWL}^C$.
-What we point out here is that these specifications may grow up to the full specification, thus making for increasingly complex astractions.
-Finally, we also note that the abstract phase uses a given precision ($\phi_{FWL}^P$) which we will increase when no candidates can be generated for a given $\phi_{synth}$.
-In the modeller, $\phi_{static} = \phi_{static} \wedge \phi_{safety}^{k'} \wedge \phi{objective}$ where $k' \geq k$, and $\phi{objective}$ defines a set of rules for the current optimization stage (see {\sc Opimise}).
-We only note that at all times $\phi_{static} \models \phi_{synth}$.
+These specifications will vary as the loop progresses.  We only note that at all times $\phi_{static} \models \phi_{synth}$.
 Let us see how the loop updates these specifications.
 
-\paragraph{1. {\sc abstract}} creates an abstraction from the initial specificationas follows:
+\paragraph{1. {\sc abstract}} creates an abstraction from the initial specification as follows:
 \begin{itemize}
-\item Select a sample time that minimizes the magnitudes of the matrices used in both the
+\item Select a sample time ($T_d$) that minimizes the magnitudes of the matrices used in both the
 implementation and the abstraction. This ensures that a small bit vector size is required for
@@
 \item Build the observer matrices ${\mat{A}_d}_{\langle C \rangle}$, ${\mat{B}_d}_{\langle C \rangle}$
-and ${\mat{C}_d}_{\langle C \rangle}$ using the truncation described in Section~\ref{sec:numeric_rep}.
+and ${\mat{C}_d}_{\langle C \rangle}$ using the truncation described in Section~\ref{sec:numeric_rep2}.
 \item Transform the system into canonical form and add nondeterminism for the errors
-using the techniques described in Section~\ref{sec:cof_fwl_stability}. The transformation
-matrices will be needed to obtain an FWL compliant controller and observer.
+using the techniques described in Section~\ref{sec:cof_fwl_stability}. 
+%The transformation matrices will be needed to obtain an FWL compliant controller and observer.
 \item Compute the characteristic polynomial of the matrix $(\mat{A}_d-\mat{B}_d\mat{K}_{\langle C \rangle})$
@@
 \item Calculate the noise sets $\eta_1$ and $\eta_2$ from the equations
-described in Section~\ref{sec:observable}.
+described in Section~\ref{sec:cof_fwl_stability}.
 \item Calculate a set of initial bounds on $\mat{K}$, $\phi_\mathit{init}^{K}$,
@@
 \end{itemize}
+When a counterexample is found, we add it to $\phi_{synth} = \phi_{synth} \wedge \phi_{safety}^k$, 
+where k is the iteration found for the counterexample.  The ${\sc Abstract}$
+phase will then construct a abstraction (in the form of a program) that meets
+this property (unsoundly since the program uses FWL).
+
 %
@@
 If there is no candidate solution we return FAIL and signal {\sc Abstract}. Based on the current abstraction,
-{\sc  Abstract} may choose to increase the precision, refine the abstraction, or return a synthesis failure.
+{\sc  Abstract} may choose to increase the precision ($\phi_{\langle P \rangle}$), or return a synthesis failure.
 If we have a candidate solution we will feed it to the verifier chain in order to validate it.
@@
 
-If we cannot optimize the candidate such that it passes the {\sc
-  verify synthesis} check, we signal the {\sc Abstract} phase to
+We denote these sets of rules as $\phi_{objective}$ (which varies depending on which optimization stage we're in).
+At each optimizing iteration, the modeller updates $\phi_{static} = \phi_{static} \wedge \phi_{objective}$% \wedge \phi_{safety}^{k'} $ where $k' \geq k$.
+
+If we cannot optimize the candidate, we signal the {\sc Abstract} phase to
 refine $\phi_{synth}$ and request {\sc Synthesise} to produce a new
-candidate.  Otherwise the refined candidate solution is given back to
+candidate.  Otherwise the optimised candidate solution is given back to
 {\sc Verify Synthesis}.
-%
+
 %\item
@@
 %\item
-\paragraph{6. {\sc Refine Abstraction}} changes $\phi_{safety}$ to encompass any arising
-counterexample.  This can be done by increasing the time horizon $k$ for the
+\paragraph{6. {\sc Refine Abstraction}} changes $\phi_{static} = \phi_{static} \wedge \phi_{safety}^k$
+to encompass any arising counterexample.  This is done by increasing the time horizon $k$ for the
 safety specification of the violating initial condition and input.
-It also modifies $\phi_{static}$ to account for the counterexample.
 If the magnitude of the violation is small, {\sc Optimise} may find a new
@@
 %\item
-\paragraph{8. {\sc Sample}} selects a smaller suitable sample time and modify the abstractions to meet the discretization. 
+\paragraph{8. {\sc Sample}} selects a smaller suitable sample time and modify the abstractions to meet the discretization 
+($\phi_{synth} = \phi_{synth} \wedge \phi_{sample}^{T_d'}$ and $\phi_{static} = \phi_{static} \wedge \phi_{sample}^{T_d'}$).
 It will then feed back to the abstraction refinement loop to look for a suitable action for the updated model.
-%
-
-%\item
-If we reach the {\sc abstract} phase, it means that the candidate
-  solution is not valid, in which case we must refine $\phi_{synth}$. If $\phi_{synth}$ cannot be further refined, 
-  then we cannot synthesise a new candidate and return a synthesis failure.
 %\end{enumerate}
@@
 The benchmark suite employed to evaluate the proposed technique is 
-composed by seven SISO \note{defined SISO} models extracted from the control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15,maglev,converters}.
+composed by seven models extracted from the control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15,maglev,converters}.
 In order to obtain statistically relevant results, we have taken these models

### 2018-01-27 TACAS2018/paper.tex
results intro

@@
 %-------------------------------
-In many cases the speed of the response \note{you mean the step response - this concept is undefined}, i.e. how fast it converges to the set point, is a requirement of great importance. 
+In many cases the response time of the system\note{you mean the step response - this concept is undefined}, i.e. how fast it converges to the set point, is a requirement of great importance. 
 This is given as a ``settling time.''
@@
 %-------------------------------
-\note{Start with a description of the results, e.g. ``We managed to synthesise controllers in X of the cases. Average time ... In the rest of the cases ...''}.
 
@@
 
+Using the described technique we managed to synthesize controllers for X benchmarks, with a median synthesis time of $18.8$ seconds.
+%and the maximum observed synthesis time was under 10 minutes for a $4^{th}$ order system ($8^{th}$ order considering the observer).
+We consider these times short enough to be of practical use to control engineers.
+There are cases for which the system fails to find a controller.  We use a
+relatively short timeout, so it is possible longer timeouts would result in a
+valid solution. However, as stated before, the solution is sound but incomplete,
+so it is impossible to tell if a solution exists in these cases.
+
 In order to show the improvements due to our optimization-enhanced CEGIS, we
@@
 require multiple counterexamples.
-
-The median run-times for our benchmark sets are under a minute, and the
-maximum observed synthesis time was under 10 minutes for a $4^{th}$ order system
-($8^{th}$ order considering the observer).  We consider these times
-short enough to be of practical use to control engineers.
-
-There are cases for which the system fails to find a controller.  We use a
-relatively short timeout, so it is possible longer timeouts would result in a
-valid solution. However, as stated before, the solution is sound but incomplete,
-so it is impossible to tell if a solution exists in these cases.
 

### 2018-01-27 TACAS2018/paper.tex

@@
 specifications: $\phi_{synth}$ used by the synthesiser and
-$\phi_{static}$ which is given to the synthesis refinement loop. 
-Both specifications will be updated during execution and new abstractions will be constructed for each.
+$\phi_{static}$ which is given to the optimiser. 
+Both specifications are updated during execution and new abstractions are constructed for each.
 Let us define the properties 
@@
 \phi_{\langle C \rangle}&:= \mat{K}=\mat{K}_{\langle C \rangle} \wedge \mat{L}=\mat{L}_{\langle C \rangle}\\
-\phi_{dynamics}^{T_d}&:= \mat{A}_d, \mat{B}_d, \mat{C}_d
+\phi_{dynamics}^{T_d}&:= \{\mat{A}_d, \mat{B}_d, \mat{C}_d \mid \mat{A}_d=e^{\mat{A}T_d}\}
 \end{align*}
-The first one defines the word length of the digital controller ($\mathbb{R}_{\langle C \rangle}$) and its effect on the system dynamics.
-The second one defines the sampling time ($T_d$) and its effect on the system dynamics (as per Section \ref{sec:continuous_time_accel}).
+$\phi_{\langle C \rangle}$ defines the word length of the digital controller ($\mathbb{R}_{\langle C \rangle}$)
+and $\phi_{dynamics}^{T_d}$ defines the sampling time ($T_d$) and its effect on the system dynamics (as per Section \ref{sec:continuous_time_accel}).
 We start our loop with 
@@
 \end{align*}
-These specifications will vary as the loop progresses.  We only note that at all times $\phi_{static} \models \phi_{synth}$.
+These specifications will vary as the loop progresses.  However, at all times $\phi_{static} \models \phi_{synth}$.
 Let us see how the loop updates these specifications.

### 2018-01-27 TACAS2018/paper.tex
changes synthesis section

@@
 
-The CEGIS-OR loop for this approach is described next.
-We make use of two abstractions corresponding to two
-specifications: $\phi_{synth}$ used by the synthesiser and
-$\phi_{static}$ which is given to the optimiser. 
-Both specifications are updated during execution and new abstractions are constructed for each.
-Let us define the properties 
-\begin{align*}
-\phi_{\langle C \rangle}&:= \mat{K}=\mat{K}_{\langle C \rangle} \wedge \mat{L}=\mat{L}_{\langle C \rangle}\\
-\phi_{dynamics}^{T_d}&:= \{\mat{A}_d, \mat{B}_d, \mat{C}_d \mid \mat{A}_d=e^{\mat{A}T_d}\}
-\end{align*}
-$\phi_{\langle C \rangle}$ defines the word length of the digital controller ($\mathbb{R}_{\langle C \rangle}$)
-and $\phi_{dynamics}^{T_d}$ defines the sampling time ($T_d$) and its effect on the system dynamics (as per Section \ref{sec:continuous_time_accel}).
-We start our loop with 
-\begin{align*}
-\phi_{synth}&:=\phi_{dynamics}^{T_d} \wedge \phi_{stability} \wedge \phi_{input} \wedge \phi_{init}\\
-\phi_{static}&:=\phi_{synth} \wedge \phi_{\langle C \rangle}.
-\end{align*}
-These specifications will vary as the loop progresses.  However, at all times $\phi_{static} \models \phi_{synth}$.
-Let us see how the loop updates these specifications.
-
-\paragraph{1. {\sc abstract}} creates an abstraction from the initial specification as follows:
+%The CEGIS-OR loop for this approach is described next.
+Throughout the CEGIS-OR loop we make use of a specification $\phi$
+which encompasses the abstraction of the system's dynamics.
+Note that, given that the system's abstraction gets refined
+in each iteration, $\phi$ will also be adjusted appropriately.
+Initially, $\phi$ is given by: 
+$\phi=\phi_{stability} \wedge \phi_{input} \wedge \phi_{init}$.
+
+%% We make use of two abstractions corresponding to two
+%% specifications: $\phi_{synth}$ used by the synthesiser and
+%% $\phi_{static}$ which is given to the optimiser. 
+%% While both specifications are updated during execution, for now we describe their
+%% meaning at the beginning of the synthesis process.
+%% If we denote by $\phi_{dynamics}^{T_d}$ the discretized system's dynamics with respect to the
+%% sampling time ($T_d$),
+%% $\phi_{dynamics}^{T_d}:= \{\mat{A}_d, \mat{B}_d, \mat{C}_d \mid \mat{A}_d=e^{\mat{A}T_d}\},$
+%% then initially $\phi_{synth}$ and $\phi_{static}$ are equal to:
+
+Note that there is a major difference between
+the way $\phi$ is being used in different phases in Figure~\ref{fig:CEGIS-OR}: while the
+{\sc synthesise} phase checks $\phi$ by using the plant's precision
+$\mathbb{R}_{\langle P \rangle}$ for the controller, observer and
+plant, the {\sc model} and {\sc verify} phases use reals to represent
+the plant and $\mathbb{R}_{\langle C \rangle}$ for the controller and
+the observer. The reason for this is that, as we want the
+synthesis to be fast, we allow it to generate unsound results
+and we restore soundness during the verification and modeling stages.
+%% While these specifications are updated throughout the synthesis process (as appropriately described below), at all times $\phi_{static} \models \phi_{synth}$.
+%Let us see how the loop updates these specifications.
+
+Next, we describe the CEGIS-OR loop in Figure~\ref{fig:CEGIS-OR}:
+\paragraph{1. {\sc abstract}} computes an initial version of $\phi$
+and decides the sample time $T_d$,
+the plant's precision $\mathbb{R}_{\langle P \rangle}$ and the controller's precision
+$\mathbb{R}_{\langle C \rangle}$.
+ %width for the bit vectors
+ %for representing the controller and the plant, respectively.
+%
+%For this creates an abstraction from the initial specification as follows:
 \begin{itemize}
@@
 the synthesis process.
+\note{implementation and abstraction?}
+\item Select initial precisions $\mathbb{R}_{\langle P \rangle}$ and $\mathbb{R}_{\langle C \rangle}$
+  %width for the bit vectors
+  for representing the controller and the plant, respectively. These will be increased as needed.
+ % $\phi_{\langle C \rangle}, \phi_{\langle P \rangle}$. We will increase either precision as needed. 
 \item Build the observer matrices ${\mat{A}_d}_{\langle C \rangle}$, ${\mat{B}_d}_{\langle C \rangle}$
-and ${\mat{C}_d}_{\langle C \rangle}$ using the truncation described in Section~\ref{sec:numeric_rep2}.
+and ${\mat{C}_d}_{\langle C \rangle}$. % using the truncation described in Section~\ref{sec:numeric_rep2}.
 \item Transform the system into canonical form and add nondeterminism for the errors
-using the techniques described in Section~\ref{sec:cof_fwl_stability}. 
+as described in Section~\ref{sec:cof_fwl_stability}. 
 %The transformation matrices will be needed to obtain an FWL compliant controller and observer.
-\item Compute the characteristic polynomial of the matrix $(\mat{A}_d-\mat{B}_d\mat{K}_{\langle C \rangle})$
-as $P_a(z) = z^p+\sum_{i=1}^p{(a_i-k_i)z^{p-i}}$. 
-\item Compute the characteristic polynomial of the matrix $({\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}{\mat{C}_d}_{\langle C \rangle})$
-as $P_l(z) = z^p+\sum_{i=1}^p{(l_i-a_i)z^{p-i}}$. 
-\item Create a stability specification based on the characteristic polynomials, perturbation
-error ($\mat{A}_e$,$\mat{B}_e$), and response time $\phi_{stability}(P_a,P_l,\overline{\lambda})$
-as described in Section~\ref{sec:transientspecification}.
 \item Calculate the noise sets $\eta_1$ and $\eta_2$ from the equations
 described in Section~\ref{sec:cof_fwl_stability}.
+\item Compute necessary characteristic polynomials. 
+%% \item Compute the characteristic polynomial of the matrix $(\mat{A}_d-\mat{B}_d\mat{K}_{\langle C \rangle})$
+%% as $P_a(z) = z^p+\sum_{i=1}^p{(a_i-k_i)z^{p-i}}$. 
+%% \item Compute the characteristic polynomial of the matrix $({\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}{\mat{C}_d}_{\langle C \rangle})$
+%% as $P_l(z) = z^p+\sum_{i=1}^p{(l_i-a_i)z^{p-i}}$. 
+\item Create a stability specification $\phi_{stability}$ based on the characteristic polynomials, perturbation
+error ($\mat{A}_e$,$\mat{B}_e$), and response time %%(P_a,P_l,\overline{\lambda})$
+as described in Section~\ref{sec:transientspecification}.
+\note{could not find perturbation error anywhere}
 \item Calculate a set of initial bounds on $\mat{K}$, $\phi_\mathit{init}^{K}$,
@@
 These bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space. 
-\item Select an initial width for the bit vectors representing the controller and the plant $\phi_{\langle C \rangle}, \phi_{\langle P \rangle}$. We will increase either precision as needed.
+%% \item Under certain circumstances (i.e. when {\sc optimize} did not manage to improve the s) When a counterexample is found, we add it to $\phi_{synth} = \phi_{synth} \wedge \phi_{safety}^k$, 
+%% where k is the iteration found for the counterexample.  The ${\sc Abstract}$
+%% phase will then construct a abstraction (in the form of a program) that meets
+%% this property (unsoundly since the program uses FWL).
 \end{itemize}
-When a counterexample is found, we add it to $\phi_{synth} = \phi_{synth} \wedge \phi_{safety}^k$, 
-where k is the iteration found for the counterexample.  The ${\sc Abstract}$
-phase will then construct a abstraction (in the form of a program) that meets
-this property (unsoundly since the program uses FWL).
-
+\note{$\phi_{safety}^k$ is undefined!!!}
 %
@@
 $\phi_{synth}$ by invoking a SAT solver.
-There are two exit conditions:
-If there is no candidate solution we return FAIL and signal {\sc Abstract}. Based on the current abstraction,
-{\sc  Abstract} may choose to increase the precision ($\phi_{\langle P \rangle}$), or return a synthesis failure.
-If we have a candidate solution we will feed it to the verifier chain in order to validate it.
+If there is no candidate solution it signals {\sc Abstract}, 
+which may choose to increase the plant's precision or return a synthesis failure.
+If {\sc synthesize} generates a candidate solution, it is fed to the {\sc verify} chain in order to validate it.
 %
 %\item
-\paragraph{3. {\sc Verify Synthesis}} verifies $\phi_{static}$ of  both the
-controller and the observer.  If one of these results does not satisfy this tighter
-specification, it feeds back to the {\sc Optimise} phase.
-If the candidate is valid, we feed it to the next {\sc verify} stage, {\sc Discrete Time}.
+\paragraph{3. {\sc Verify Synthesis}} verifies that the candidate controller
+and observer obey $\phi$ (remember that we now use
+$\mathbb{R}_{\langle C \rangle}$ for the controller's representation
+and reals for the plant).  If the verification fails, the candidate is
+fed to the {\sc Optimise} phase.  If the candidate is valid, we feed
+it to the next {\sc verify} stage, {\sc Discrete Time}.
 
 %\item
-\paragraph{4. {\sc Optimise}} refines the candidate solution towards
-a local optimum.  We seek to minimize the distance of the farthest point in the
+\paragraph{4. {\sc Optimise}} optimises the failed candidate solution.
+We seek to minimize the distance of the farthest point in the
 reach space to the closest point to it in the safe region
 \begin{equation}
-e=max(\{min(\{\vec{x}-\vec{g} \mid \vec{g}\in G\}) \mid \vec{x} \in \hat{X}_\infty \}.
+e=max(\{min(\{\vec{x}-\vec{g} \mid \vec{g}\in G\}) \mid \vec{x} \in \hat{X}_\infty \}).
 \label{eq:objective}
@@
 
-Our optimization is iterative, following two stages.  The first stage seeks to
-make the dynamics as convergent as possible, since convergent dynamics are
-less likely to stray outside of the safe region (we say less likely because the
-change in the eigenvectors changes the shape of the space and may cause some 
-trajectories to go further).
-
-In this case, we take the largest eigenvalue and reduce it by a factor $f$
-that still satisfies the controller constraints ($f \overline{\lambda} \models \phi_{static}$).
-The resulting observer controller is then verified against the safety specification $\phi_{safety}$
-and the objective $e$ is measured (Equation \eqref{eq:objective}).
-If for each iteration $k$, the objective $e_k<e_{k-1}$, we continue to iterate until 
-$e_k \leq 0$ (i.e. we found a safe controller), otherwise we move to the second stage.
+Our optimization is iterative, following two stages.  The first stage
+seeks to make the dynamics as convergent as possible, since convergent
+dynamics are less likely to stray outside of the safe region (we say
+less likely because the change in the eigenvectors changes the shape
+of the space and may cause some trajectories to go further). For this
+purpose, we take the largest eigenvalue and reduce it by a factor $f$
+that still satisfies the controller constraints ($f \overline{\lambda}
+\models \phi$).  The resulting observer and controller are then
+verified against the safety specification $\phi_{safety}$ and the
+objective $e$ is measured (Equation \eqref{eq:objective}).  If for
+each iteration $k$, the objective $e_k<e_{k-1}$, we continue to
+iterate until $e_k \leq 0$ (i.e. we found a safe controller),
+otherwise we move to the second stage.
 
@@
 with the largest angle ($max\{|tan^{-1}\left(\frac{im(\lambda)}{re(\lambda)}\right)| \mid \lambda \in \Lambda\}$)
-and reduce its imaginary component only  ($re(\lambda) + f im(\lambda) \models \phi_{static}$).
+and reduce its imaginary component only  ($re(\lambda) + f im(\lambda) \models \phi$).
 The process ends when no imaginary part can be further reduced.
 The resulting closed loop form converges faster than the original and has a
-smaller rotation, which facilitates meeting the safety specification $\phi_{safety}$
-(we note that real convergent eigenvalues are trivially safe).
-
-We denote these sets of rules as $\phi_{objective}$ (which varies depending on which optimization stage we're in).
-At each optimizing iteration, the modeller updates $\phi_{static} = \phi_{static} \wedge \phi_{objective}$% \wedge \phi_{safety}^{k'} $ where $k' \geq k$.
+smaller rotation, which facilitates meeting the safety specification $\phi_{safety}$.
+%(we note that real convergent eigenvalues are trivially safe).
+
+%% We denote these sets of rules as $\phi_{objective}$ (which varies depending on which optimization stage we're in).
+%% At each optimizing iteration, the modeller updates $\phi_{static} = \phi_{static} \wedge \phi_{objective}$% \wedge \phi_{safety}^{k'} $ where $k' \geq k$.
 
 If we cannot optimize the candidate, we signal the {\sc Abstract} phase to
-refine $\phi_{synth}$ and request {\sc Synthesise} to produce a new
+refine $\phi$ and request {\sc Synthesise} to produce a new
 candidate.  Otherwise the optimised candidate solution is given back to
@@
     ([xshift=-5em]gp.north) edge node[align=center] {FAIL/\\$\mat{K}$,$\mat{L}$} ([xshift=-5em]synth.south)
-    ([xshift=5em]model1.south) edge node[align=center,xshift=-.65cm] {$\langle P \rangle$} ([xshift=5em]synth.north) node[align=left,yshift=-0.7cm,xshift=.8cm] {{$\phi_{stability}$}\\{$\phi_{safety}$}\\ {$\phi_{init}^K$}}
+   ([xshift=5em]model1.south) edge node[align=center,xshift=-.7cm] {$\mathbb{R}_{\langle P \rangle}$} 
+([xshift=5em]synth.north)
+   node[align=left,yshift=-0.7cm,xshift=.5cm] {{$\phi$}\\{$\phi_{init}^K$}} %{$\phi_{safety}$}\\ 
    ([xshift=-5em]synth.north) edge node[align=center] {FAIL} ([xshift=-5em]model1.south);

### 2018-01-27 TACAS2018/paper.tex
modified the CEGIS figure

@@
   \& complexnode/.pic={
-     \node[rectangle,draw,dotted,
-	minimum width=9cm,
-	minimum height=1cm,
-        pattern=north west lines, pattern color=gray!20,
-	label={\sc Model~~~~~~~~~~~},] (model) {};
-     \node[minimum width=2.2cm, minimum height=0.8cm, fill=orange!20] (model2) at ([xshift=-3cm]model.center) {{\sc 4. Optimise}};
-     \node[minimum width=2.2cm, minimum height=0.8cm, fill=orange!20] (model3) at ([xshift=0cm]model.center) {{\sc 6. Refine}\\{\sc Abstraction}};
-     \node[minimum width=2.2cm, minimum height=0.8cm, fill=orange!20] (model4) at ([xshift=3cm]model.center) {{\sc 8. Sample}};
+    \coordinate (model);
+    \node[minimum width=2.2cm, minimum height=0.8cm, fill=orange!20] (model2) at ([xshift=-3cm]model.center) {{\sc 4. Refine Abstraction}\\{\sc and Optimise}};
+     \coordinate (model3) at ([xshift=0cm]model.center);
+     \coordinate (model4) at ([xshift=3cm]model.center);
    } ;\\
@@
     (verif2.east) edge node {PASS} (verif3.west)
-    (verif3.north) edge node {C-ex} (model4.south)
-    (model3.west) edge node {$k$,$X_0'$} (model2.east)
-    (model4.west) edge node {$T_s$} (model3.east)
+    (verif3.north) edge[-] node {C-ex} (model4.south)
+    %(model2.west) edge node {$k$,$X_0'$} (model2.east)
+    (model4.west) edge node {} (model2.east)
     ([xshift=-5em]fp.north) edge node[align=center]  {PASS/\\C-ex} ([xshift=-5em]verif2.south)

### 2018-01-27 TACAS2018/paper.tex
synthesis section rewrite

@@
 reducing the size of the reach space of the closed loop system while
-maintaining other verification properties (safety, stability, and response time).
-
-Our approach is illustrated in Figure~\ref{fig:CEGIS-OR} and consists of four main
-phases:
-\begin{itemize}
-\item {\sc Abstract}: constructs an unsound abstract model that approximates
-the dynamics of the system.
-\item {\sc synthesize}: generates a candidate controller and observer.
-  As it makes use of the potentially coarse abstraction constructed by {\sc Abstract},
-  the candidate doesn't necessarily meet the stability or safety specification.
-\item {\sc model}: defines the properties needed by {\sc Abstract} and {\sc Optimise} to create 
-  adequate abstractions at each stage in order to reduce the probability
-  of failure in the next iteration.  Our optimization procedure aims at reducing the
-  size of the reach space of the closed loop system while preserving the verification
-  properties (safety, stability and response time).  This phase will first attempt this objective
-  and failing this feed the {\sc Abstract} phase the necessary information to produce a better candidate.
-\item {\sc verify}: verifies the behaviour of the candidate controller and observer
-  against a sound over-approximation of the concrete dynamics of the system for an infinite space over an infinite time horizon.
+maintaining other properties (safety, stability, and response time).
+
+%% Our approach is illustrated in Figure~\ref{fig:CEGIS-OR} and consists of four main
+%% phases:
+%% \begin{itemize}
+%% \item {\sc Abstract}: constructs an unsound abstract model that approximates
+%% the dynamics of the system.
+%% \item {\sc synthesize}: generates a candidate controller and observer.
+%%   As it makes use of the potentially coarse abstraction constructed by {\sc Abstract},
+%%   the candidate doesn't necessarily meet the stability or safety specification.
+%% \item {\sc model}: defines the properties needed by {\sc Abstract} and {\sc Optimize} to create 
+%%   adequate abstractions at each stage in order to reduce the probability
+%%   of failure in the next iteration.  Our optimization procedure aims at reducing the
+%%   size of the reach space of the closed loop system while preserving the verification
+%%   properties (safety, stability and response time).  This phase will first attempt this objective
+%%   and failing this feed the {\sc Abstract} phase the necessary information to produce a better candidate.
+%% \item {\sc verify}: verifies the behaviour of the candidate controller and observer
+%%   against a sound over-approximation of the concrete dynamics of the system for an infinite space over an infinite time horizon.
 If the verification fails, produces a counterexample describing the reason for failure.
-\end{itemize}
+%% \end{itemize}
 
@@
 Next, we describe the CEGIS-OR loop in Figure~\ref{fig:CEGIS-OR}:
-\paragraph{1. {\sc abstract}} computes an initial version of $\phi$
+\paragraph{\underline{{\sc abstract}}} computes an initial version of $\phi$
 and decides the sample time $T_d$,
@@
 the synthesis process.
-\note{implementation and abstraction?}
+\note{do you mean small plant precision?}
 \item Select initial precisions $\mathbb{R}_{\langle P \rangle}$ and $\mathbb{R}_{\langle C \rangle}$
@@
 These bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space. 
-%% \item Under certain circumstances (i.e. when {\sc optimize} did not manage to improve the s) When a counterexample is found, we add it to $\phi_{synth} = \phi_{synth} \wedge \phi_{safety}^k$, 
-%% where k is the iteration found for the counterexample.  The ${\sc Abstract}$
-%% phase will then construct a abstraction (in the form of a program) that meets
-%% this property (unsoundly since the program uses FWL).
 \end{itemize}
 \note{$\phi_{safety}^k$ is undefined!!!}
-%
-%\item
-\paragraph{2. {\sc synthesize}} generates a candidate controller $\mat{K}$
+\paragraph{\underline{{\sc synthesize}}} generates a candidate controller $\mat{K}$
 and observer $\mat{L}$ that satisfy
-$\phi_{synth}$ by invoking a SAT solver.
+$\phi$ by invoking a SAT solver.
 If there is no candidate solution it signals {\sc Abstract}, 
@@
 %\item
-\paragraph{3. {\sc Verify Synthesis}} verifies that the candidate controller
+\paragraph{\underline{{\sc Verify}}} checks whether the candidate
+solution found by {\sc synthesize} is a solution for the whole synthesis
+problem. It does this in three subsequent stages as explained below.
+If  in any of the stages the verification fails, then
+a counterexample is fed to the {\sc refine abstraction and optimize} phase,
+including details of initial states
+and iterations that failed the specification.
+\begin{itemize}
+\item {\sc verify synthesis}
+verifies that the candidate controller
 and observer obey $\phi$ (remember that we now use
 $\mathbb{R}_{\langle C \rangle}$ for the controller's representation
-and reals for the plant).  If the verification fails, the candidate is
-fed to the {\sc Optimise} phase.  If the candidate is valid, we feed
+and reals for the plant).  %% If the verification fails, the candidate is
+%% fed to the {\sc Optimise} phase.
+If the candidate is valid, we feed
 it to the next {\sc verify} stage, {\sc Discrete Time}.
+\item {\sc Discrete Time} verifies $\phi_{safety}^{\infty}$ (unbounded time)
+using discrete time dynamics.  %% If the verification fails, we report the
+%% counterexample to {\sc Refine Abstraction} including details of initial states
+%% and iterations that failed the specification.
+\item {\sc Continuous Time} verifies that the
+transitions between sample times meet the specification $\phi_{safety}^{\infty}$.  %% If
+%% a counterexample is found, information about the maximum distance of the
+%% violation to the specification boundary is fed to {\sc Sample}. 
+\end{itemize}
 
 %\item
-\paragraph{4. {\sc Optimise}} optimises the failed candidate solution.
-We seek to minimize the distance of the farthest point in the
+
+\paragraph{\underline{{\sc Refine Abstraction and optimize}}} refines the
+system's abstraction as well as optimizes the current candidate
+solution.
+%
+%% When a counterexample is found, we add it to $\phi_{synth} = \phi_{synth} \wedge \phi_{safety}^k$, 
+%% where k is the iteration found for the counterexample.  
+First, the system's abstraction must be refined in order to eliminate
+the newly received counterexample. For this purpose,
+we increase the time horizon $k$ for the
+safety specification so that it captures the violating iteration
+(for the given initial state) and adjust $\phi$:
+$\phi = \phi \wedge \phi_{safety}^k$.
+If the counterexample is provided by the {\sc continuous time} stage,
+then we must select a smaller suitable sample time to be used
+for the plant's discretization.
+%% and modify the abstractions to meet the discretization 
+%% ($\phi_{synth} = \phi_{synth} \wedge \phi_{sample}^{T_d'}$ and $\phi_{static} = \phi_{static} \wedge \phi_{sample}^{T_d'}$).
+%% It will then feed back to the abstraction refinement loop to look for a suitable action for the updated model.
+%\end{enumerate}
+
+Secondly, we try to optimizes the failed candidate solution.
+For this purpose, we seek to minimize the distance of the farthest point in the
 reach space to the closest point to it in the safe region
@@
 
-If we cannot optimize the candidate, we signal the {\sc Abstract} phase to
-refine $\phi$ and request {\sc Synthesise} to produce a new
-candidate.  Otherwise the optimised candidate solution is given back to
+If we cannot optimize the candidate  we signal the {\sc Abstract} phase to potentially 
+increase the precision and 
+%phase to
+%refine $\phi$ and
+request {\sc Synthesise} to produce a new
+candidate.  Otherwise the optimized candidate solution is given back to
 {\sc Verify Synthesis}.
-
-%\item
-\paragraph{5. {\sc Discrete Time}} verifies $\phi_{safety}^{\infty}$ (unbounded time)
-using discrete time dynamics.  If the verification fails, we report the
-counterexample to {\sc Refine Abstraction} including details of initial states
-and iterations that failed the specification.  
-%\item
-\paragraph{6. {\sc Refine Abstraction}} changes $\phi_{static} = \phi_{static} \wedge \phi_{safety}^k$
-to encompass any arising counterexample.  This is done by increasing the time horizon $k$ for the
-safety specification of the violating initial condition and input.
-If the magnitude of the violation is small, {\sc Optimise} may find a new
-candidate, otherwise it will feed through to {\sc Abstract}.
-%
-%\item
-\paragraph{7. {\sc Continuous Time}} verifies that the
-transitions between sample times meet the specification $\phi_{safety}^{\infty}$.  If
-a counterexample is found, information about the maximum distance of the
-violation to the specification boundary is fed to {\sc Sample}. 
-%\item
-\paragraph{8. {\sc Sample}} selects a smaller suitable sample time and modify the abstractions to meet the discretization 
-($\phi_{synth} = \phi_{synth} \wedge \phi_{sample}^{T_d'}$ and $\phi_{static} = \phi_{static} \wedge \phi_{sample}^{T_d'}$).
-It will then feed back to the abstraction refinement loop to look for a suitable action for the updated model.
-%\end{enumerate}
+\note{when is the precision increased in abstract?}
 
@@
     \coordinate (model);
-    \node[minimum width=2.2cm, minimum height=0.8cm, fill=orange!20] (model2) at ([xshift=-3cm]model.center) {{\sc 4. Refine Abstraction}\\{\sc and Optimise}};
+    \node[minimum width=2.2cm, minimum height=0.8cm, fill=orange!20] (model2) at ([xshift=-3cm]model.center) {{\sc 4. Refine Abstraction}\\{\sc and Optimize}};
      \coordinate (model3) at ([xshift=0cm]model.center);
@@
     ([xshift=-5em]sv.north) edge node[align=center]  {PASS/\\C-ex} ([xshift=-5em]verif3.south)
-    ([xshift=5em]verif1.south) edge node[align=center] {$\mat{A}'$} ([xshift=5em]bmc.north)
-    ([xshift=5em]verif2.south) edge node[align=center] {$\mat{A}'$,$\mat{B}'$,$\phi$} ([xshift=5em]fp.north)
-    ([xshift=5em]verif3.south) edge node[align=center] {{$\mat{A}$,$\mat{B}$,$\mat{C}$}\\{$\mat{A}'$,$\mat{B}'$,$\phi$}} ([xshift=5em]sv.north)
+    ([xshift=5em]verif1.south) edge node[align=center] {} ([xshift=5em]bmc.north)
+    ([xshift=5em]verif2.south) edge node[align=center] {} ([xshift=5em]fp.north)
+    ([xshift=5em]verif3.south) edge node[align=center] {} ([xshift=5em]sv.north)
     ([xshift=-5em]bmc.north) edge node[align=center]  {PASS/\\C-ex} ([xshift=-5em]verif1.south)

### 2018-01-27 TACAS2018/paper.tex
sec 6

@@
 }
- \caption{Closed-loop digital control system with an observer, where the controller and the observer (bottom part) are implemented in a discrete domain (identified by the subindex $\langle C \rangle$), whereas the plant is continuous \label{fig:observersystem2}}
+ \caption{Closed-loop digital control system with an observer, where the controller and the observer (bottom part) are implemented in a discrete domain (quantities within this domain are identified by the index $\langle C \rangle$), whereas the plant is continuous \label{fig:observersystem2}}
 \end{figure*}
@@
 
- Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a linear function of $\vec{x}_0$ as described below.
-We assume that the system has no inputs, and its dynamics are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.
+ Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a linear function of $\vec{x}_0$ as shown below.
+We assume that the system has no inputs, so its dynamics are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.
 
@@
  \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x} \text{ with } T \in \mathbb{R}^+$ is the state of the system at time $t=T$.
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x} \text{ with } T \in \mathbb{R}^+_0$ is the state of the system at time $t=T$.
  \end{corollary}
@@
  which are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where $\forall t\geq 0, \mat{B}\vec{u}(t)=\vec{u}$. 
+ \note{you mean u(t) = u?}
  For such models, a the state $\vec{x}_T$ is computed next.  
@@
  \end{align}
- where $\forall t \leq T,\ \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn}
+ where $\forall t \leq T,\ \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn} \note{pls no fwd ref to the appendix- can you use (8)?}
  \footnote{when $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$}.
@@
  If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, 
- then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u}) \text{ with } T \in \mathbb{R}_0^+$ (where $\mat{A}_d^{\frac{T}{T_d}} = e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the system at time $T$.
+ then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u}) \text{ with } T \in \mathbb{R}_0^+$ \note{here there must be an x that is actually a x0?} (where $\mat{A}_d^{\frac{T}{T_d}} = e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the system at time $T$.
  \end{corollary}
@@
  \end{align}
- with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn}, 
+ with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn} \note{no ref to appendix}, 
  and where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$, 

### 2018-01-27 TACAS2018/paper.tex
sec 6

@@
 
-Stability denotes the property of a model to remain within a bounded set of states around an equilibrium point. 
-In this paper, we are interested in asymptotic stability, where the output is expected to converge to a certain steady state value.  
-We specify model stability via Jury's criterion~\cite{fadali}\footnote{More details on Jury's criterion is in Appendix~\ref{sec:closed_stability}}, 
-which allows for an expression with an algebraic formula. 
-We transform the model into a representation that contains the coefficients of the characteristic polynomial (used by Jury's criterion) expressed as sums of controller and plant values (with no multiplications, which are expensive for the SAT solver).
-Such a representation is called Controllable and Observable Canonical Form~\cite{Astrom08} \footnote{See parts~\ref{sec:reachable} and~\ref{sec:observable} in the Appendix}.  
-In this Section we explore the implications of using these canonical forms alongside an FWL representation.
+Stability denotes the property of a model to unfold staying within a bounded set around an equilibrium point. 
+In this paper, we are interested in asymptotic stability, where the model is further expected to converge to the steady state value (i.e., the equilibrium point).   
+%
+We specify model stability via Jury's criterion~\cite{fadali}\footnote{More details on Jury's criterion is in Appendix~\ref{sec:closed_stability}.}, 
+which boils down to a requirement expressed as an algebraic formula - a SAT solver will manipulate its coefficients. 
+%
+We transform the model into a representation that contains the coefficients of its characteristic polynomial, which are used in Jury's criterion, 
+that are expressed as sums of controller and plant values: 
+this representation has no multiplications, which are expensive for a SAT solver.   
+%
+Such a representation is known as 
+% is called Controllable and Observable 
+``canonical form''~\cite{Astrom08}\footnote{See parts~\ref{sec:reachable} and~\ref{sec:observable} in the Appendix.} 
+and is dynamically equivalent to the given model.  
+In this Section we explore the implications of using this canonical form, 
+alongside the use of a FWL representation.
+
+\medskip
 
@@
 dimension for each matrix.
-New problems arise due to the FWL effects on these matrices.  The Canonical
-form of the resulting system is expressed by the formula:
+New problems arise due to the FWL effects on these matrices.  
+The canonical form of the resulting model is expressed by:
 %
@@
 +\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]\left [\begin{array}{c} \vec{r}_k + \vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
-\vec{y}_k=&\mat{C}_d\mat{T}_c\vec{x}_k', 
+\vec{y}_k= &\mat{C}_d\mat{T}_c\vec{x}_k', 
 % + \mat{D}_{d}\vec{u}_k
@@
 \end{align}
-where $\mat{T}_c$ and $\mat{T}_o$ trasform the system into Canonical Form~\cite{Astrom08}, $\vec{x}'$ and $\vec{x}_e'$ are the state of the system and the error of the observer evaluated in the transformed domain \note{this statement will not be understood} and
+where the matrices $\mat{T}_c$ and $\mat{T}_o$ linearly transform the model into canonical form~\cite{Astrom08}, $\vec{x}'$ and $\vec{x}_e'$ are the state of the system and the error of the observer evaluated in the transformed domain,
+and we have introduced the following terms: 
 {\setlength{\abovedisplayskip}{2pt}
@@
 \note{it is very hard if not impossible to understand these operations without having thoroughly gone through the whole Appendix, which is unlikely for a reviewer to do.}
-where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations (see Section~\ref{sec:quantization-noise}).
+Here $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations (see Section~\ref{sec:quantization-noise}).
 
@@
 \begin{align}
-  \phi_\mathit{safety}: = & \underline{y} \leq y_k \leq \overline{y}
-\equiv \forall k\geq 0.\, \mat{G}\vec{x}_k \leq \vec{h},
+  \phi_\mathit{safety}: = & \, \underline{y} \leq y_k \leq \overline{y}
+\equiv \forall k\geq 0 \, \mat{G}\vec{x}_k \leq \vec{h},
 \label{eq:safetyspec}
@@
 $\phi_\mathit{init}\equiv \mat{G}' \vec{x}_0 \leq \vec{h}'$,
-where $\mat{G}'$ and $\vec{h}'$ describe the initial state-space.
+where $\mat{G}'$ and $\vec{h}'$ limits the initial conditions of the model.
 

### 2018-01-27 TACAS2018/paper.tex
sec 6

@@
 digital feedback controllers using CEGIS~\cite{DBLP:conf/asplos/2006}. Broadly speaking, CEGIS
-denotes an iterative technique where each iteration performs inductive
+denotes an iterative technique where each step performs inductive
 generalisation based on counterexamples provided by a verification
@@
 passed back to the synthesis phase, where it is added to the set of
-inputs to be considered in the next loop iteration. Otherwise, we are
-done.
-
-%
-We enhance the standard CEGIS architecture with abstraction refinement
-and optimization, resulting in CEGIS-OR (CEGIS with Optimization and
-Refinement).  By using abstraction refinement, CEGIS-OR tackles the
+inputs to be considered in the next loop iteration. Otherwise, the process terminates.
+
+%
+We enhance the standard CEGIS architecture \cite{abate2017automated} with an abstraction-refinement approach 
+and with optimization, resulting in the novel CEGIS-OR (CEGIS with Optimization and Refinement).  
+By using abstraction refinement, CEGIS-OR tackles the
 scalability issues inherent in program synthesis as it allows using
-potentially coarse abstractions of a system that are only refined on
-demand.  Given that the use of coarse abstractions could result in low
-quality candidate solutions (i.e. candidates that fail the
-specification on a very large number of inputs), after each synthesis
+potentially coarse abstractions of the given model that are only refined on
+demand.  Since the use of coarse abstractions may result in low-quality candidate solutions 
+(i.e. candidates that fail the specification on a very large number of inputs), after each synthesis
 phase we use optimization techniques to improve the produced
 candidates.  In particular, our optimization procedure aims at
-reducing the size of the reach space of the closed loop system while
-maintaining other properties (safety, stability, and response time).
+reducing the size of the reach space of the closed loop system, 
+while maintaining other dynamical properties (safety, stability, and response time).
 
@@
 
-The main advantage of this approach is two-fold:
+The main advantage of the new CEGIS-OR is twofold:
 \begin{itemize}
@@
   refined into more complex ones as the procedure progresses. Thus, solutions
-  that don't require a high level of precision are obtained fast. 
+  that do not require a high level of precision are obtained faster. 
 \item[2.] Although {\sc synthesize} makes use of a potentially coarse abstraction,
@@
   This has the potential to reduce
-  the number of iterations of the CEGIS loop required to obtain a solution.
+  the overall number of iterations of the CEGIS loop required to obtain a complete solution.
 \end{itemize}
@@
 %The CEGIS-OR loop for this approach is described next.
-Throughout the CEGIS-OR loop we make use of a specification $\phi$
-which encompasses the abstraction of the system's dynamics.
-Note that, given that the system's abstraction gets refined
-in each iteration, $\phi$ will also be adjusted appropriately.
-Initially, $\phi$ is given by: 
-$\phi=\phi_{stability} \wedge \phi_{input} \wedge \phi_{init}$.
+Throughout the CEGIS-OR loop we make use of a specification $\phi$ that deals with the abstraction of the model dynamics.
+Note that since the model abstraction gets refined at each iteration, 
+$\phi$ will also be adjusted accordingly.
+Initially, $\phi$ is simply given as the defined 
+$\phi := \phi_{stability} \wedge \phi_{input} \wedge \phi_{init}$.
 
@@
 the way $\phi$ is being used in different phases in Figure~\ref{fig:CEGIS-OR}: while the
-{\sc synthesise} phase checks $\phi$ by using the plant's precision
+{\sc synthesise} phase checks $\phi$ by using the plant precision
 $\mathbb{R}_{\langle P \rangle}$ for the controller, observer and
@@
 
-Next, we describe the CEGIS-OR loop in Figure~\ref{fig:CEGIS-OR}:
+\medskip
+
+Next, we describe the CEGIS-OR loop in Figure~\ref{fig:CEGIS-OR}.
+
 \paragraph{\underline{{\sc abstract}}} computes an initial version of $\phi$
 and decides the sample time $T_d$,
-the plant's precision $\mathbb{R}_{\langle P \rangle}$ and the controller's precision
+the plant precision $\mathbb{R}_{\langle P \rangle}$ and the controller's precision
 $\mathbb{R}_{\langle C \rangle}$.

### 2018-01-27 TACAS2018/paper.tex
sec 7

@@
 and decides the sample time $T_d$,
-the plant precision $\mathbb{R}_{\langle P \rangle}$ and the controller's precision
+the plant precision $\mathbb{R}_{\langle P \rangle}$ and the controller precision
 $\mathbb{R}_{\langle C \rangle}$.
@@
 \note{$\phi_{safety}^k$ is undefined!!!}
-\paragraph{\underline{{\sc synthesize}}} generates a candidate controller $\mat{K}$
-and observer $\mat{L}$ that satisfy
+\paragraph{\underline{{\sc synthesize}}} generates a candidate controller matrix $\mat{K}$
+and observer matrix $\mat{L}$ that satisfy
 $\phi$ by invoking a SAT solver.
 If there is no candidate solution it signals {\sc Abstract}, 
-which may choose to increase the plant's precision or return a synthesis failure.
+which may choose to increase the plant precision or return a synthesis failure.
 If {\sc synthesize} generates a candidate solution, it is fed to the {\sc verify} chain in order to validate it.
@@
 and observer obey $\phi$ (remember that we now use
-$\mathbb{R}_{\langle C \rangle}$ for the controller's representation
+$\mathbb{R}_{\langle C \rangle}$ for the controller representation
 and reals for the plant).  %% If the verification fails, the candidate is
@@
 \paragraph{\underline{{\sc Refine Abstraction and optimize}}} refines the
-system's abstraction as well as optimizes the current candidate
+model abstraction as well as optimizes the current candidate
 solution.
@@
 %% where k is the iteration found for the counterexample.  
-First, the system's abstraction must be refined in order to eliminate
+First, the model abstraction must be refined in order to eliminate
 the newly received counterexample. For this purpose,
@@
 safety specification so that it captures the violating iteration
-(for the given initial state) and adjust $\phi$:
-$\phi = \phi \wedge \phi_{safety}^k$.
+(for the given initial state) and adjust $\phi$ as 
+$\phi := \phi \wedge \phi_{safety}^k$.
 If the counterexample is provided by the {\sc continuous time} stage,
 then we must select a smaller suitable sample time to be used
-for the plant's discretization.
+for the model discretization.
 %% and modify the abstractions to meet the discretization 
@@
 \begin{equation}
-e=max(\{min(\{\vec{x}-\vec{g} \mid \vec{g}\in G\}) \mid \vec{x} \in \hat{X}_\infty \}).
+e = \max(\{\min(\{\vec{x}-\vec{g}, \vec{g}\in G\}), \vec{x} \in \hat{X}_\infty \}).
 \label{eq:objective}
@@
 verified against the safety specification $\phi_{safety}$ and the
-objective $e$ is measured (Equation \eqref{eq:objective}).  If for
+objective $e$ is measured as in Equation \eqref{eq:objective}.   If for
 each iteration $k$, the objective $e_k<e_{k-1}$, we continue to
@@
 }
-\caption{CEGIS with Optimization Refinement. Orange boxes (light) are modelling
+\caption{CEGIS-OR: CEGIS with Optimization Refinement. Orange boxes (light) are modelling
 stages, blue boxes (dark) are verification stages, and the red box is the synthesis stage.}
@@
 
-Our Synthesis Algorithm shows promise in exploiting modularity for
-improved response. It however relies on the use of application
-specific optimization which means that it is necessary to find adequate tools for
-exploring different types of properties.  Our results show significant
-improvement in terms of scalability over standard approaches with an ability to
-explore complex properties, hence many synthesis tasks may be derived
-from it. In particular we note that our synthesis loop should be targeted at
-systems where the solution space is formed by connected spaces where
+CEGIS-OR shows promise in exploiting modularity for improved response. 
+It however relies on the use of application-specific optimization, 
+which requires adequate tools for exploring different types of properties.  
+Our results show significant improvement in terms of scalability over standard CEGIS approaches, 
+with an ability to explore complex properties, hence many synthesis tasks may be tackled with it. 
+In particular we note that our synthesis loop should be targeted at 
+models where the solution space is formed by connected spaces where
 optimization algorithms or localized synthesis are likely to be achieved more
-efficiently than global synthesis.
+efficiently than global synthesis \note{such solution spaces are unlikely classifiable a priori}. 
 Finally our application to control synthesis provides a solid proof
-of concept for scalable optimal control synthesis of LTI systems. There is still
-a need to extend it it MIMO systems and analyse further properties, which may
-also require exploring other optimization methods for control systems.
+of concept for scalable optimal control synthesis of LTI systems.
+
+There is still a need to extend CEGIS-OR to MIMO models and to analyse more general properties, 
+which may also require exploring other optimization methods for control systems.
 

### 2018-01-28 TACAS2018/paper.tex
fixes

@@
  \mat{S}^{-1}
- \label{eq:continuous_tube_dyn}\\
+ \label{eq:continuous_tube_dyn2}\\
  &\text{where } s_i=\left\{\begin{array}{cc}1&\quad gm(\lambda_i)>1\\0&\quad gm(\lambda_i)=1\end{array}\right.,\nonumber
@@
  Next, we are interested in studying models with parametric inputs, 
- which are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where $\forall t\geq 0, \mat{B}\vec{u}(t)=\vec{u}$. 
- \note{you mean u(t) = u?}
+ which are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where $\forall t\geq 0, \vec{u}(t)=\vec{u}$. 
  For such models, a the state $\vec{x}_T$ is computed next.  
@@
  \end{align}
- where $\forall t \leq T,\ \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn} \note{pls no fwd ref to the appendix- can you use (8)?}
+ where $\forall t \leq T,\ \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}
  \footnote{when $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$}.
@@
  If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, 
- then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u}) \text{ with } T \in \mathbb{R}_0^+$ \note{here there must be an x that is actually a x0?} (where $\mat{A}_d^{\frac{T}{T_d}} = e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the system at time $T$.
+ then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u}) \text{ with } T \in \mathbb{R}_0^+$ (where $\mat{A}_d^{\frac{T}{T_d}} = e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the system at time $T$.
  \end{corollary}
@@
  \end{align}
- with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn} \note{no ref to appendix}, 
+ with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, 
  and where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$, 
@@
 \begin{align}
-  \phi_\mathit{safety}: = & \, \underline{y} \leq y_k \leq \overline{y}
-\equiv \forall k\geq 0 \, \mat{G}\vec{x}_k \leq \vec{h},
+\phi_\mathit{safety}^n: = & \forall k \in [0, ... , n], \mat{G}\vec{x}_k \leq \vec{h} \text{ and } \underline{y} \leq y_k \leq \overline{y}\nonumber\\
+\phi_\mathit{safety}: = & \phi_\mathit{safety}^\infty
 \label{eq:safetyspec}
@@
 as they are implicit from Equation \ref{eq:observer_LTI_FWL_cf}.
-%% We assume that we do not want saturation in our
-%% system, hence the control loop has only one mode.
-%% First we must
-%% translate the safety specification into the statespace.  Replacing on the
-%% second part of equation \eqref{eq:observer_LTI_cf} we obtain
-%% %
-%% \begin{equation}
-%% \phi_{safety} := \underline{y}<\mat{C}\vec{x}_k<\overline{y}, \forall k \geq 0
-%% \label{eq:of_bounds}
-%% \end{equation}
 
@@
 \item Select a sample time ($T_d$) that minimizes the magnitudes of the matrices used in both the
-implementation and the abstraction. This ensures that a small bit vector size is required for
+implementation and the abstraction. This ensures that a small word length for the plant precision is required for
 the synthesis process.
-\note{do you mean small plant precision?}
 \item Select initial precisions $\mathbb{R}_{\langle P \rangle}$ and $\mathbb{R}_{\langle C \rangle}$
@@
 %% as $P_l(z) = z^p+\sum_{i=1}^p{(l_i-a_i)z^{p-i}}$. 
-\item Create a stability specification $\phi_{stability}$ based on the characteristic polynomials, perturbation
+\item Create a stability specification $\phi_{stability}$ based on the characteristic polynomials, FWL
 error ($\mat{A}_e$,$\mat{B}_e$), and response time %%(P_a,P_l,\overline{\lambda})$
 as described in Section~\ref{sec:transientspecification}.
-\note{could not find perturbation error anywhere}
 \item Calculate a set of initial bounds on $\mat{K}$, $\phi_\mathit{init}^{K}$,
@@
 \end{itemize}
-\note{$\phi_{safety}^k$ is undefined!!!}
 \paragraph{\underline{{\sc synthesize}}} generates a candidate controller matrix $\mat{K}$
@@
 it to the next {\sc verify} stage, {\sc Discrete Time}.
-\item {\sc Discrete Time} verifies $\phi_{safety}^{\infty}$ (unbounded time)
+\item {\sc Discrete Time} verifies $\phi_\mathit{safety}^{\infty}$ (unbounded time)
 using discrete time dynamics.  %% If the verification fails, we report the
@@
 \item {\sc Continuous Time} verifies that the
-transitions between sample times meet the specification $\phi_{safety}^{\infty}$.  %% If
+transitions between sample times meet the specification $\phi_\mathit{safety}^{\infty}$.  %% If
 %% a counterexample is found, information about the maximum distance of the
@@
 %
-%% When a counterexample is found, we add it to $\phi_{synth} = \phi_{synth} \wedge \phi_{safety}^k$, 
-%% where k is the iteration found for the counterexample.  
 First, the model abstraction must be refined in order to eliminate
 the newly received counterexample. For this purpose,
-we increase the time horizon $k$ for the
+we increase the time horizon $n$ for the
 safety specification so that it captures the violating iteration
 (for the given initial state) and adjust $\phi$ as 
-$\phi := \phi \wedge \phi_{safety}^k$.
+$\phi := \phi \wedge \phi_\mathit{safety}^n$.
 If the counterexample is provided by the {\sc continuous time} stage,
@@
 \models \phi$).  The resulting observer and controller are then
-verified against the safety specification $\phi_{safety}$ and the
+verified against the safety specification $\phi_\mathit{safety}$ and the
 objective $e$ is measured as in Equation \eqref{eq:objective}.   If for
@@
 The resulting closed loop form converges faster than the original and has a
-smaller rotation, which facilitates meeting the safety specification $\phi_{safety}$.
+smaller rotation, which facilitates meeting the safety specification $\phi_\mathit{safety}$.
 %(we note that real convergent eigenvalues are trivially safe).
@@
 %% We denote these sets of rules as $\phi_{objective}$ (which varies depending on which optimization stage we're in).
-%% At each optimizing iteration, the modeller updates $\phi_{static} = \phi_{static} \wedge \phi_{objective}$% \wedge \phi_{safety}^{k'} $ where $k' \geq k$.
+%% At each optimizing iteration, the modeller updates $\phi_{static} = \phi_{static} \wedge \phi_{objective}$% \wedge \phi_\mathit{safety}^{n'} $ where $n' \geq n$.
 
@@
 ([xshift=5em]synth.north)
-   node[align=left,yshift=-0.7cm,xshift=.5cm] {{$\phi$}\\{$\phi_{init}^K$}} %{$\phi_{safety}$}\\ 
+   node[align=left,yshift=-0.7cm,xshift=.5cm] {{$\phi$}\\{$\phi_{init}^K$}} %{$\phi_\mathit{safety}$}\\ 
    ([xshift=-5em]synth.north) edge node[align=center] {FAIL} ([xshift=-5em]model1.south);

### 2018-01-28 TACAS2018/paper.tex
nudge

@@
 \begin{itemize}
-\item Select a sample time ($T_d$) that minimizes the magnitudes of the matrices used in both the
-implementation and the abstraction. This ensures that a small word length for the plant precision is required for
+\item Select a sample time ($T_d$) that minimizes the magnitudes of the used matrices.
+This ensures that a small word length for the plant precision is required for
 the synthesis process.
@@
 
-If we cannot optimize the candidate  we signal the {\sc Abstract} phase to potentially 
-increase the precision and 
-%phase to
-%refine $\phi$ and
-request {\sc Synthesise} to produce a new
+If we cannot optimize the candidate  we signal the {\sc Abstract} phase to 
+use the updated $\phi_\mathit{synth}$ and request {\sc Synthesise} to produce a new
 candidate.  Otherwise the optimized candidate solution is given back to
 {\sc Verify Synthesis}.
-\note{when is the precision increased in abstract?}
 
@@
 models where the solution space is formed by connected spaces where
-optimization algorithms or localized synthesis are likely to be achieved more
+optimization algorithms or localized synthesis are likely to be more
 efficiently than global synthesis \note{such solution spaces are unlikely classifiable a priori}. 

### 2018-01-28 TACAS2018/paper.tex
rewrote the CEGIS parts in the intro

--- 2018-01-27 TACAS2018/paper.tex
@@
 
-We make use of a two-stage counterexample-guided inductive
-synthesis (CEGIS) driven by optimization refinement.
-The first, coarse, synthesis stage uses a low resolution discretized model of a 
-transformation of the original model. Furthermore, it only looks initially at
-static properties  of the system. This largely reduces the complexity of
-the problem, enabling the synthesiser to offer fast response times.
-
-Due to either numerical imprecision or overapproximations, the
-candidate solution presented by the first synthesiser will likely not
-meet the spec. A second synthesis stage uses matrix eigen-decomposition 
-and objective functions to iteratively optimize results computed by the first
-stage.  Whenever the optimization is unable to yield further results, it feeds
-a counterexample to the first synthesiser in a traditional CEGIS manner.
-The combined synthesisers are thus capable of reasoning about complex
-models with high computational efficiency due to their modularity.
+We use a CounterExample-Guided Inductive Synthesis (CEGIS)
+\cite{jha-icse10,DBLP:conf/pldi/Solar-LezamaRBE05} approach,
+which we enhance with abstraction refinement and optimization
+resulting in the novel CEGIS-OR (CEGIS with Optimization and
+Refinement).  This design uses an iterative process where each
+iteration performs inductive generalisation based on counterexamples
+provided by a verification oracle.  Essentially, the inductive
+generalisation uses information about a limited number of inputs to
+make claims in the form of candidate solutions about all the possible
+inputs.  By using abstraction refinement, CEGIS-OR allows us to handle
+complex systems which are initially represented by coarse abstractions
+that only get refined on demand.  Consequently, solutions that do not
+require a high level of precision are obtained fast.  Since the use
+of coarse abstractions may result in low-quality candidate solutions
+(i.e. candidates that fail the specification on a very large number of
+inputs), after each inductive generalization phase we use optimization
+techniques to improve the produced candidates.  In particular, our
+optimization procedure aims at reducing the size of the reach space of
+the closed loop system, while maintaining other dynamical properties
+of interest (safety, stability, and response time).
+
+%% We make use of a two-stage counterexample-guided inductive
+%% synthesis (CEGIS) driven by optimization refinement.
+%% The first, coarse, synthesis stage uses a low resolution discretized model of a 
+%% transformation of the original model. Furthermore, it only looks initially at
+%% static properties  of the system. This largely reduces the complexity of
+%% the problem, enabling the synthesiser to offer fast response times.
+
+%% Due to either numerical imprecision or overapproximations, the
+%% candidate solution presented by the first synthesiser will likely not
+%% meet the spec. A second synthesis stage uses matrix eigen-decomposition 
+%% and objective functions to iteratively optimize results computed by the first
+%% stage.  Whenever the optimization is unable to yield further results, it feeds
+%% a counterexample to the first synthesiser in a traditional CEGIS manner.
+%% The combined synthesisers are thus capable of reasoning about complex
+%% models with high computational efficiency due to their modularity.
 
@@
 \item We develop a model for inductive synthesis that combines CEGIS with
-abstraction refinement and synthesis optimization in order to minimize the
-synthesis cost. 
+  abstraction refinement and optimization in order to handle complex
+  systems. 
 %
@@
   observers are much more complex and difficult to synthesise than standard
-  full-state feedback controllers.
+  full-state feedback controllers (hence the need for abstraction refinement).
 %
@@
 %
-We enhance the standard CEGIS architecture \cite{abate2017automated} with an abstraction-refinement approach 
-and with optimization, resulting in the novel CEGIS-OR (CEGIS with Optimization and Refinement).  
-By using abstraction refinement, CEGIS-OR tackles the
+We enhance the standard CEGIS architecture %\cite{abate2017automated}
+with an abstraction-refinement approach and with optimization,
+resulting in the novel CEGIS-OR (CEGIS with Optimization and
+Refinement).  By using abstraction refinement, CEGIS-OR tackles the
 scalability issues inherent in program synthesis as it allows using
-potentially coarse abstractions of the given model that are only refined on
-demand.  Since the use of coarse abstractions may result in low-quality candidate solutions 
-(i.e. candidates that fail the specification on a very large number of inputs), after each synthesis
+potentially coarse abstractions of the given model that are only
+refined on demand.  Since the use of coarse abstractions may result in
+low-quality candidate solutions (i.e. candidates that fail the
+specification on a very large number of inputs), after each synthesis
 phase we use optimization techniques to improve the produced
 candidates.  In particular, our optimization procedure aims at
-reducing the size of the reach space of the closed loop system, 
-while maintaining other dynamical properties (safety, stability, and response time).
+reducing the size of the reach space of the closed loop system, while
+maintaining other dynamical properties (safety, stability, and
+response time).
 
@@
 
-Secondly, we try to optimizes the failed candidate solution.
+Secondly, we try to optimize the failed candidate solution.
 For this purpose, we seek to minimize the distance of the farthest point in the

### 2018-01-28 TACAS2018/paper.tex
sec 7

@@
 In this section, we describe our technique for synthesizing safe
-digital feedback controllers using CEGIS~\cite{DBLP:conf/asplos/2006}. Broadly speaking, CEGIS
+digital feedback controllers using CEGIS. Broadly speaking, CEGIS
 denotes an iterative technique where each step performs inductive
@@
 %
-We enhance the standard CEGIS architecture %\cite{abate2017automated}
+We enhance the standard CEGIS architecture 
 with an abstraction-refinement approach and with optimization,
@@
 If we cannot optimize the candidate  we signal the {\sc Abstract} phase to 
-use the updated $\phi_\mathit{synth}$ and request {\sc Synthesise} to produce a new
+use the updated $\phi$ and request {\sc Synthesise} to produce a new
 candidate.  Otherwise the optimized candidate solution is given back to

### 2018-01-28 TACAS2018/paper.tex
abstract

@@
 synthesis accounts for errors caused by the digitization effects
-introduced by the controller.  We use an optimization-based
-counterexample-guided inductive synthesis (CEGIS) procedure that is
-driven by abstraction refinement, where in each iteration we take the
-following steps: (1) We start by only considering a low-resolution
-discretized model of the system and only static properties, which
-enables us to find candidate solutions fast.  (2) Once we have a
-candidate, we use matrix eigen-decomposition
-and objective functions to iteratively optimize it.
+introduced by the controller.  We use a counterexample-guided
+inductive synthesis procedure enhanced with abstraction
+refinement and optimization, which allows us to start by considering
+a low-resolution discretized model of the system and %, which enables us to
+find candidate solutions fast. This model gets refined on demand.
+Moreover, in order to improve our chances of finding a solution even
+when considering coarse abstractions of the system, in each iteration of the CEGIS
+loop we use matrix eigen-decomposition to optimize our candidate.
+%% Once we have a candidate, we use matrix eigen-decomposition
+%% and objective functions to iteratively optimize it.
 %Whenever the optimization is unable to yield further results, it feeds back to the
@@
 This design yields a significant speed-up compared to a traditional
-CEGIS scheme (i.e. without optimization).  We demonstrate the
-practical value of this approach by automatically synthesizing safe
-observer-based controllers for physical plant models from the digital
-control literature.
+CEGIS scheme (i.e. without abstraction refinement and optimization).
+We demonstrate the practical value of this approach by automatically
+synthesizing safe observer-based controllers for physical plant models
+from the digital control literature.
 %

### 2018-01-28 TACAS2018/paper.tex
related work
sec 3 + 4

@@
 
+Note that, while we have several reference to the appendix throughout
+the paper, the paper can be read on its own and these references are
+only meant as an aid for the reader less familiar with control theory or
+for the proofs of theorems.
+
 %-------------------------------
@@
 properties available cover more detail.  However, relying on state-space
-discretization \mbox{Pessoa} is likely to incur in scalability limitations. 
+discretization \mbox{Pessoa} is likely to incur scalability limitations. 
 Along this research line, \cite{Anta2010,liu16} studies the synthesis of
@@
 \end{equation}
+\note{do we actually need to mention the safety spec here given that it is formally introduced only in Sec~\ref{sec:cof_safety}?}
 %
@@
 the reach space of the system generalises the previous notions over an unbounded
-time horizon (transitive closure).
+time horizon (transitive closure). \note{this sentence is grammatically incorrect.}
 
@@
 the internal state $x$ cannot be directly measured,  
-but is rather inferred from its effect on the output $\vec{y}$ using an observer~~\cite{Astrom08}.  
+but is rather inferred from its effect on the output $\vec{y}$ using an observer~\cite{Astrom08}.  
 Essentially, a state observer is a new dynamical model (with variable denoted below as $\hat{\vec{x}}$) 
 that provides an estimate of the internal state $x$ of the given model, 
-from measurements of its inputs and outputs (See~\ref{sec:observable}).
+from measurements of its inputs and outputs (see Appendix~\ref{sec:observable}).
 
 A closed-loop digital control system with observer is shown in Figure~\ref{fig:observersystem}. 
-The linear feedback controller *bottom left) and is characterised by a gain matrix $\mat{K}_{\langle C \rangle}$ that influences the closed-loop dynamics, 
+The linear feedback controller (bottom left) is characterised by a gain matrix $\mat{K}_{\langle C \rangle}$ that influences the closed-loop dynamics, 
 and is driven by the observer state $\hat{\vec{x}}$.  
@@
  which are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where $\forall t\geq 0, \vec{u}(t)=\vec{u}$. 
- For such models, a the state $\vec{x}_T$ is computed next.  
+ For such models, a state $\vec{x}_T$ is computed next.  
 \begin{theorem}
@@
 A new input value is produced only at every sample time but implemented over the continuous-time plant dynamics. 
-We assume that $\mat{A}$ is invertible, since otherwise the term $B_T$ below would have to be calculated by integration, which is impractical.
+We assume that $\mat{A}$ is invertible, since otherwise the term $B_T$ below would have to be calculated by integration, which is impractical. \note{can we say something like: for simplicity and
+without loss of generality, or is this assumption restrictive?}
 
@@
 in view of many errors introduced in the dynamics. 
-Errors might results from delays due to processing time,
+Errors might result from delays due to processing time,
 corruptions over communication lines in the control loop, 

### 2018-01-28 TACAS2018/paper.tex
sec 5+6

@@
 \end{proof}
-This results allows to over-approximate the effects of the delay by introducing a disturbance signal $\nu_t=[-q_t, q_t]$ at the output.
+This result allows to over-approximate the effects of the delay by introducing a disturbance signal $\nu_t=[-q_t, q_t]$ at the output.
  %and use the dynamics of the system without delay.  
@@
 In Figure \ref{fig:observersystem2} we have introduced sources of noise that are due to quantization effects.  
-These effects are caused by imprecise numerical representations of real numbers in the digital domain of the controller: 
-these play an important role in the synthesis of sound controllers. 
-The model has two sources of error are due to Finite Word Length (FWL) representations. 
+These effects are caused by imprecise numerical representations of real numbers in the digital domain of the controller and play an important role in the synthesis of sound controllers. 
+The model has two sources of error due to Finite Word Length (FWL) representations. 
 The first is the numerical error introduced by the fixed-point numbers employed to model the plant, 
@@
 
+\note{Can we just mention what each $\nu_1$, $\nu_2$, $\nu_1'$, $\nu_2'$ and $\nu_t$ in Figure~\ref{fig:observersystem} denotes -- just in plain english?
+In sec 3.3 we say that they will be explained later but they never are.}
+
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 We specify model stability via Jury's criterion~\cite{fadali}\footnote{More details on Jury's criterion is in Appendix~\ref{sec:closed_stability}.}, 
-which boils down to a requirement expressed as an algebraic formula - a SAT solver will manipulate its coefficients. 
-%
-We transform the model into a representation that contains the coefficients of its characteristic polynomial, which are used in Jury's criterion, 
-that are expressed as sums of controller and plant values: 
-this representation has no multiplications, which are expensive for a SAT solver.   
+which boils down to a requirement expressed as an algebraic formula - a SAT solver will manipulate the coefficients of the model's characteristic polynomial. 
+%
+To facilitate the use of Jury's criterion, we transform the model into
+a representation that contains the coefficients of its characteristic
+polynomial expressed as sums of controller and plant values: this
+representation has no multiplications, which are expensive for a SAT
+solver.
 %
@@
 and is dynamically equivalent to the given model.  
-In this Section we explore the implications of using this canonical form, 
+In this section we explore the implications of using this canonical form, 
 alongside the use of a FWL representation.
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-A safety specification gives raise to a requirement on the
-states of the model, such that the controller
-must ensure that the state never violates the
-requirement.
-In~this work, the safety property is expressed as:
+A safety specification gives raise to a requirement on the states of
+the model. Consequently, the controller must ensure that the state
+never violates the requirement.  In~this work, the safety property is
+expressed as:
 %
@@
 the eigenvalues are smaller too (which we can do with Jury's criterion).
+
 We will use $\phi_{stability}$ to refer to the combined stability and transient response specifications.

### 2018-01-28 TACAS2018/paper.tex
more changes

@@
 
+\note{something like this (also, we should probably still remove some of the obvious references where they can find material themselves): }
 Note that, while we have several reference to the appendix throughout
@@
 A closed-loop digital control system with observer is shown in Figure~\ref{fig:observersystem}. 
-The linear feedback controller (bottom left) is characterised by a gain matrix $\mat{K}_{\langle C \rangle}$ that influences the closed-loop dynamics, 
+The linear feedback controller (bottom left) is characterized by a gain matrix $\mat{K}_{\langle C \rangle}$ that influences the closed-loop dynamics, 
 and is driven by the observer state $\hat{\vec{x}}$.  
@@
 which is amplified by a gain matrix $\mat{L}_{\langle C \rangle}$.
+Note that the controller and the observer are implemented in a discrete domain 
+(quantities within this domain are identified by the index $\langle C \rangle$), whereas the plant is continuous.
 Figure~\ref{fig:observersystem} also contains references to $\nu_1$, $\nu_2$, $\nu_1'$, $\nu_2'$ and $\nu_t$, which
@@
 }
- \caption{Closed-loop digital control system with an observer, where the controller and the observer (bottom part) are implemented in a discrete domain (quantities within this domain are identified by the index $\langle C \rangle$), whereas the plant is continuous \label{fig:observersystem2}}
+\caption{Closed-loop digital control system with an observer, where the controller and the observer (bottom part) are implemented in a discrete domain,
+  %(quantities within this domain are identified by the index $\langle C \rangle$),
+  whereas the plant is continuous. \label{fig:observersystem2}}
 \end{figure*}

### 2018-01-28 TACAS2018/paper.tex
sec 7

@@
 %
-We enhance the standard CEGIS architecture 
-with an abstraction-refinement approach and with optimization,
-resulting in the novel CEGIS-OR (CEGIS with Optimization and
-Refinement).  By using abstraction refinement, CEGIS-OR tackles the
-scalability issues inherent in program synthesis as it allows using
-potentially coarse abstractions of the given model that are only
-refined on demand.  Since the use of coarse abstractions may result in
+We enhance the standard CEGIS architecture with an
+abstraction-refinement approach and with optimization, resulting in
+the novel CEGIS-OR (CEGIS with Optimization and Refinement).  By using
+abstraction refinement, CEGIS-OR tackles the scalability issues
+inherent in program synthesis as it allows us to handle complex
+systems, which we coarsely abstract and only refine on demand.
+%potentially coarse abstractions of the given model that are only
+%refined on demand.
+Since the use of coarse abstractions may result in
 low-quality candidate solutions (i.e. candidates that fail the

### 2018-01-28 TACAS2018/paper.tex
removed some todos
nudge

@@
 \begin{equation}\label{equ:reachtraj}
-\tau(\vec{x}_k,\vec{u}_k) = 
-\big\{ \mat{A}\vec{x}_k +
-\mat{B}\vec{u}_k \mid \mat{G}\vec{x}_k \leq \vec{h}\big\}\;. 
+\tau(\vec{x}_k,\vec{u}_k) = %\big\{ 
+\mat{A}\vec{x}_k + \mat{B}\vec{u}_k
+ %\mid \mat{G}\vec{x}_k \leq \vec{h}\big\}\;. 
 \end{equation}
-\note{do we actually need to mention the safety spec here given that it is formally introduced only in Sec~\ref{sec:cof_safety}?}
-%
-Here $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe a safe set, within the state-space $\mathbb{R}^p$.
+%\note{do we actually need to mention the safety spec here given that it is formally introduced only in Sec~\ref{sec:cof_safety}?}
+%
+%Here $\mat{G}$ and $\vec{h}$ define a set of inequalities that describe a safe set, within the state-space $\mathbb{R}^p$.
 %
@@
 %
-Finally, set $\hat{X} =\bigcup_{n\geq 0} \tau^n(X_0,U)$ which we refer to as
-the reach space of the system generalises the previous notions over an unbounded
-time horizon (transitive closure). \note{this sentence is grammatically incorrect.}
+Finally, the set $\hat{X} =\bigcup_{n\geq 0} \tau^n(X_0,U)$, which we refer to as
+the reach space of the system, generalises the previous notions over an unbounded
+time horizon (transitive closure).
 
@@
 (quantities within this domain are identified by the index $\langle C \rangle$), whereas the plant is continuous.
-Figure~\ref{fig:observersystem} also contains references to $\nu_1$, $\nu_2$, $\nu_1'$, $\nu_2'$ and $\nu_t$, which
-  denote noise terms that will be explained later.   
-%%   With respect to noises (denoted by $\nu$), 
-%% $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations.
+We futher model the effects of using a discrete controller as the noise signals $\nu_1$(ADC quantization), $\nu_2$ (DAC quantization), $\nu_1'$ (rounding of the observer state error),
+$\nu_2'$ (rounding of the observer state), and $\nu_t$ (output delay of the digital system) 
   Lastly, $k_r$ is a reference gain required by the model.  
@@
 
-\note{ [add?] In this section we work with fully observed models, namely where $y = x$. }
-
+%\note{ [add?] In this section we work with fully observed models, namely where $y = x$. } 
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 A new input value is produced only at every sample time but implemented over the continuous-time plant dynamics. 
-We assume that $\mat{A}$ is invertible, since otherwise the term $B_T$ below would have to be calculated by integration, which is impractical. \note{can we say something like: for simplicity and
-without loss of generality, or is this assumption restrictive?}
-
 %
@@
  with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, 
- and where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$, 
+ and where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$
+  \footnote{as before, when $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$},
  and $\mat{A}_d, \mat{B}_d$ describe the discretized plant dynamics with sample time $T_s$, 
@@
 we denote as $\mathcal{F}_{\langle M,F \rangle} : \mathbb{R} \rightarrow \mathbb{R}_{\langle M,F \rangle}$ the corresponding truncation function.
-
-\note{Can we just mention what each $\nu_1$, $\nu_2$, $\nu_1'$, $\nu_2'$ and $\nu_t$ in Figure~\ref{fig:observersystem} denotes -- just in plain english?
-In sec 3.3 we say that they will be explained later but they never are.}
 
@@
 with an ability to explore complex properties, hence many synthesis tasks may be tackled with it. 
-In particular we note that our synthesis loop should be targeted at 
+In particular we note that our synthesis loop is more efficient for
 models where the solution space is formed by connected spaces where
 optimization algorithms or localized synthesis are likely to be more
-efficiently than global synthesis \note{such solution spaces are unlikely classifiable a priori}. 
+efficiently than global synthesis. 
 Finally our application to control synthesis provides a solid proof
@@
 
-\todo{preliminaries should also contain the observer model.}
-\todo{why is sec 4 not considering the observer model or a system with output?}
-\todo{sec 6 needs to be merged into 7.}
-\todo{transient response for an observed model?}
-
 \end{document}

### 2018-01-29 TACAS2018/paper.tex
sec 7

@@
 of inputs. Subsequently, this candidate is passed to a verification
-oracle that checks it against the specification for all possible
+phase that checks it against the specification for all possible
 inputs. If the verification fails, then the witness counterexample is
@@
 inherent in program synthesis as it allows us to handle complex
-systems, which we coarsely abstract and only refine on demand.
+systems, which we coarsely abstract and only refine on demand --
+refinements are triggered by counterexamples returned by the
+verification phase.
 %potentially coarse abstractions of the given model that are only

### 2018-01-29 TACAS2018/paper.tex
reference

@@
 
-We are interested in control systems with an output $\vec{y}$ that is a linear combination of its states and inputs:
+We are interested in control systems with an output $\vec{y}$ that is a linear combination of its states and inputs
+\footnote{This restricts the observability of the state-space $\vec{x}$, since we can only measure $\vec{y}$}:
 %, which may restrict the observability of the state-space from the output space.
@@
 %In this work, 
-\note{Observability requirement? Used later.}
 Equations~\eqref{eq:ode1}-\eqref{eq:ode2} are soundly discretized in
@@
 %
-Since the transformations $\mat{A}$ and $\mat{B}$ are linear and vector sums preserve convexity \note{ref}, 
+Since the transformations $\mat{A}$ and $\mat{B}$ are linear and linear transformations preserve convexity~\cite{boyd2004convex}, 
 the sets $X_n = \tau^n(X_0,U)$ are also convex.  
@@
 %
-We specify model stability via Jury's criterion~\cite{fadali}\footnote{More details on Jury's criterion is in Appendix~\ref{sec:closed_stability}.}, 
+We specify model stability via Jury's criterion~\cite{fadali},%\footnote{More details on Jury's criterion is in Appendix~\ref{sec:closed_stability}.}, 
 which boils down to a requirement expressed as an algebraic formula - a SAT solver will manipulate the coefficients of the model's characteristic polynomial. 
@@
 % is called Controllable and Observable 
-``canonical form''~\cite{Astrom08}\footnote{See parts~\ref{sec:reachable} and~\ref{sec:observable} in the Appendix.} 
+``canonical form''~\cite{Astrom08} %\footnote{See parts~\ref{sec:reachable} and~\ref{sec:observable} in the Appendix.} 
 and is dynamically equivalent to the given model.  
@@
 \note{it is very hard if not impossible to understand these operations without having thoroughly gone through the whole Appendix, which is unlikely for a reviewer to do.}
-Here $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations (see Section~\ref{sec:quantization-noise}).
+Here $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations \footnote{see Appendix~\ref{sec:quantization-noise}}.
 
@@
    &                                 & & \multicolumn{1}{|c|}{benchmarks}  & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{Max} & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{Max}\\\hline
-1  & DC Motor          & 2 & 100 & 9.5\,s & 1.9\,s& \xmark& 1.2\,s &   3.1\,s &   14.1\,s\\
-2  & Helicopter        & 3  & 100 & \xmark & \xmark & \xmark & 6.7\,s  &   18.9\,s & \xmark\\
-3  & Inverted Pendulum & 4 & 100 &   9.7\,s & \xmark &\xmark & 12.0\,s  &  18.1\,s &  414.0\,s\\
-4  & Magnetic Pointer  & 2  & 100 & \xmark & \xmark & \xmark& 4.6\,s  &  39.0\,s &  \xmark \\
+1  & DC Motor          & 2 & 100 & 1.3\,s & 26.9\,s& \xmark (22)& 1.1\,s &   3.8\,s &   \xmark (2)\\
+2  & Helicopter        & 3  & 100 & 57.2\,s & \xmark (54) & \xmark (54) & 7.1\,s  &   18.0\,s & \xmark (9)\\
+3  & Inverted Pendulum & 4 & 100 &   9.7\,s & \xmark &\xmark () & 12.0\,s  &  18.1\,s &  \xmark ()\\
+4  & Magnetic Pointer  & 2  & 100 & 5.7\,s & 229.9\,s & \xmark (38) & 3.9\,s  &  11.4\,s &  \xmark (5) \\
 %5 & Magnetic Suspension          & 2 & 1 & 12.2\,s& 0.6\,s & & & N/A  &   N/A &   N/A\\
-5  & Pendulum          & 2 & 100 & 14.0\,s & 2.0\,s & \xmark&1.2\,s  &   1.5\,s &   4.3\,s\\
-6  & Suspension        & 4 & 100 & 73.7\,s& \xmark & \xmark &24.0\,s  &   46.1\,s &  557.9\,s\\
-7  & Tape Driver       & 3 & 100 & 10.1\,s& 140.3\,s & \xmark &2.6\,s  &   10.5\,s &   104.6\,s\\
+5  & Pendulum          & 2 & 100 & 14.0\,s & 2.0\,s & \xmark ()&0.7\,s  &   6.3\,s & \xmark  (3)\\
+6  & Suspension        & 4 & 100 & 73.7\,s& \xmark & \xmark ()&24.0\,s  &   46.1\,s & \xmark ()\\
+7  & Tape Driver       & 3 & 100 & 10.1\,s& 140.3\,s & \xmark ()&2.6\,s  &   10.5\,s & \xmark ()\\
 %9 & Satellite          & 2 & 1 & 9.4\,s& 0.7\,s & & & N/A  &   N/A &   N/A\\
@@
 \caption{\label{tab:cegis_results}
-Experimental results.
-Minimum, Maximum and Median times for standard CEGIS vs CEGIS-OR on multiple benchmarks.
-\xmark~indicates failure to find a controller, either due to timeout or insufficient numeric precision (bitvectors are limited to 64bits).}
+Experimental results. Minimum, Maximum and Median times for standard CEGIS vs CEGIS-OR on multiple benchmarks. \xmark~indicates timeout, with the number of benchmarks that timed out in parenthesis.}
 \end{table}

### 2018-01-29 TACAS2018/paper.tex
ch 6

@@
 We are interested in control systems with an output $\vec{y}$ that is a linear combination of its states and inputs
-\footnote{This restricts the observability of the state-space $\vec{x}$, since we can only measure $\vec{y}$}:
+\footnote{This restricts the observability of the state-space $\vec{x}$, since we can only measure $\vec{y}$. 
+\note{what does this mean? do you assume observability? don't you need that if you later compute the observable canonical form?}}:
 %, which may restrict the observability of the state-space from the output space.
@@
 %
-%In this work, 
+\note{what is the dimension of C, D?}
 Equations~\eqref{eq:ode1}-\eqref{eq:ode2} are soundly discretized in
@@
  The solution to the differential equation $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$,
+ \note{matrices S are not defined}
  evaluated at time $T$ is
@@
 %$\vec{x}_T$ is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T. 
+\note{so: the statement of this theorem is a standard result in the control literature - why is this a new theorem? we do not prove anything new here.}
  \end{theorem}
@@
  If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x} \text{ with } T \in \mathbb{R}^+_0$ is the state of the system at time $t=T$.
+\note{there needs to be an x0}
+ \note{so I assume this is the new contribution?}
  \end{corollary}

### 2018-01-29 TACAS2018/paper.tex
nudge

@@
 to represent the domain of a digital model of the dynamics of a real plant when
-evaluated by a verification tool. \note{refer back to notation in Figure 1.}
+evaluated by a verification tool.  Elements in this domain are marked with an
+underscore~${\langle C \rangle}$ (see Figure \ref{fig:observersystem2}).
 Thus, any mathematical operation within the digital controller is executed in the
@@
 %5 & Magnetic Suspension          & 2 & 1 & 12.2\,s& 0.6\,s & & & N/A  &   N/A &   N/A\\
-5  & Pendulum          & 2 & 100 & 14.0\,s & 2.0\,s & \xmark ()&0.7\,s  &   6.3\,s & \xmark  (3)\\
+5  & Pendulum          & 2 & 100 & 14.0\,s & 2.0\,s & \xmark ()&0.4\,s  &   4.9\,s & \xmark  (6)\\
 6  & Suspension        & 4 & 100 & 73.7\,s& \xmark & \xmark ()&24.0\,s  &   46.1\,s & \xmark ()\\
@@
 There are cases for which the system fails to find a controller.  We use a
-relatively short timeout, so it is possible longer timeouts would result in a
+relatively short timeout, so it is possible that longer timeouts would result in a
 valid solution. However, as stated before, the solution is sound but incomplete,
@@
 our benchmarks, we observe that our approach is significantly faster than
-standard CEGIS. We further note the cases where standard CEGIS times out, which
-represent an improvement of several orders of magnitude for our optimization
-approach.  The magnitude of the improvement is largely dependent on the shape
-of the problem.
-
-The smaller benchmarks (order=2) tend to show little or no improvement when we
-apply CEGIS-OR.  The reason is that for these benchmarks the synthesis time using
-Solution Generalization is already small, and the overhead of the abstraction is
-often equal or larger than the gain obtained.
+standard CEGIS. We further note that the number of times standard CEGIS times
+out is much larger than CEGIS-OR which results in more found solutions.
+The magnitude of the improvement is however, largely dependent on the shape of the problem.
 

### 2018-01-29 TACAS2018/paper.tex
Reducing the appendix

@@
 We are interested in control systems with an output $\vec{y}$ that is a linear combination of its states and inputs
-\footnote{This restricts the observability of the state-space $\vec{x}$, since we can only measure $\vec{y}$. 
-\note{what does this mean? do you assume observability? don't you need that if you later compute the observable canonical form?}}:
+\footnote{Since we can only measure $\vec{y}$, the state-space $\vec{x}$ is not fully observable}.
 %, which may restrict the observability of the state-space from the output space.
@@
 \label{eq:ode2}  
-\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t).
+\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t), \vec{y} \in \mathbb{R}^o, \mat{C} \in \mathbb{R}^{o \times p}, \mat{D} \in \mathbb{R}^{o \times q}
 \end{equation}
 %
-\note{what is the dimension of C, D?}
 Equations~\eqref{eq:ode1}-\eqref{eq:ode2} are soundly discretized in
@@
   %(quantities within this domain are identified by the index $\langle C \rangle$),
-  whereas the plant is continuous. \label{fig:observersystem2}}
+  whereas the plant is continuous. \label{fig:observersystem}}
 \end{figure*}
@@
 
- \begin{theorem}
- The solution to the differential equation $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$,
- \note{matrices S are not defined}
+ \begin{lemma}
+ The solution to the differential equation $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, and $\mat{S}$ are the generalized eigenvectors of $\mat{A}$,
  evaluated at time $T$ is
@@
 %$\vec{x}_T$ is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T. 
-\note{so: the statement of this theorem is a standard result in the control literature - why is this a new theorem? we do not prove anything new here.}
- \end{theorem}
- \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x} \text{ with } T \in \mathbb{R}^+_0$ is the state of the system at time $t=T$.
-\note{there needs to be an x0}
- \note{so I assume this is the new contribution?}
- \end{corollary}
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0 \text{ with } T \in \mathbb{R}^+_0$ is the state of the system at time $t=T$.
+ \end{lemma}
 \begin{proof}
@@
 
-In our model, delays are all deferred to the Zero Order Holder (ZOH) of the DAC (See Figure \ref{fig:observersystem2}). 
+In our model, delays are all deferred to the Zero Order Holder (ZOH) of the DAC (See Figure \ref{fig:observersystem}). 
 In the digital world everything takes place at times $t=kT_s, k \in \mathbb{N}$ (discrete time progression),
@@
 \begin{theorem}
-The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modelled as a non-deterministic disturbance signal ($\nu_t$ in Figure \ref{fig:observersystem2}) upper bounded by
+The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modelled as a non-deterministic disturbance signal ($\nu_t$ in Figure \ref{fig:observersystem}) upper bounded by
 \begin{align}
@@
 
-In Figure \ref{fig:observersystem2} we have introduced sources of noise that are due to quantization effects.  
+In Figure \ref{fig:observersystem} we have introduced sources of noise that are due to quantization effects.  
 These effects are caused by imprecise numerical representations of real numbers in the digital domain of the controller and play an important role in the synthesis of sound controllers. 
@@
 evaluated by a verification tool.  Elements in this domain are marked with an
-underscore~${\langle C \rangle}$ (see Figure \ref{fig:observersystem2}).
+underscore~${\langle C \rangle}$ (see Figure \ref{fig:observersystem}).
 Thus, any mathematical operation within the digital controller is executed in the
@@
 \left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
-+\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]\left [\begin{array}{c} \vec{r}_k + \vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
-\vec{y}_k= &\mat{C}_d\mat{T}_c\vec{x}_k', 
++\mat{B}'\left [\begin{array}{c} \vec{r}_k + \nu_2+\nu_2'\\ \nu_1+\nu_1'+\nu_t\end{array}\right]%\nonumber\\
+%\vec{y}_k= &\mat{C}_d\mat{T}_c\vec{x}_k', 
 % + \mat{D}_{d}\vec{u}_k
@@
 \end{align}
-where the matrices $\mat{T}_c$ and $\mat{T}_o$ linearly transform the model into canonical form~\cite{Astrom08}, $\vec{x}'$ and $\vec{x}_e'$ are the state of the system and the error of the observer evaluated in the transformed domain,
-and we have introduced the following terms: 
-{\setlength{\abovedisplayskip}{2pt}
-\setlength{\belowdisplayskip}{2pt}
-\begin{align*}
-\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_{\langle C \rangle}\right)\mat{T}_c^{-1}&
-\mat{A}_{o}=&\mat{T}_o\left({\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}{\mat{C}_d}_{\langle C \rangle}\right)\mat{T}_o^{-1}\\
-\mat{B}_{o}=&\mat{T}_c{\mat{B}_d}_{\langle C \rangle}\mat{K}_{\langle C \rangle}\mat{T}_o^{-1}&
-\mat{B}_{e}=&\mat{T}_c(\mat{B}_d-{\mat{B}_d}_{\langle C \rangle})\mat{K}_{\langle C \rangle}\mat{T}_o^{-1}\\
-\mat{A}_{e}=&\mat{T}_o\left(\mat{A}_d-{\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}\mat{C}_e\right)\mat{T}_o^{-1}&
-\mat{C}_{e}=&\mat{C}_d-{\mat{C}_d}_{\langle C \rangle}
-\end{align*}
-}
-{\setlength{\abovedisplayskip}{0pt}
-\begin{align*}
-\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}+\mat{B}_{e}&\mat{B}_{o}\\ \mat{A}_{e}&\mat{A}_{o}\end{array}\right]&
-\mat{B}'=&\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]\\
-\eta_1=&\nu_1+\nu_1'+\nu_t& \eta_2=&\nu_2+\nu_2',
-\end{align*}
-}
-\note{it is very hard if not impossible to understand these operations without having thoroughly gone through the whole Appendix, which is unlikely for a reviewer to do.}
+where $\vec{x}'$ and $\vec{x}_e'$ are the state of the system and the error of the observer evaluated in the transformed domain, 
+$\mat{A}_{c}$ the closed loop dynamics of the controller, $\mat{A}_{o}$ the closed loop dynamics of the observer, $\mat{B}_{o}$ the feedback gain, 
+ $\mat{B}'$ the noise sensitivity, and $\mat{A}_{e}$ and $\mat{B}_{e}$ the error introduced on these matrices by the FWL representation.
+%and we have introduced the following terms: 
+%{\setlength{\abovedisplayskip}{2pt}
+%\setlength{\belowdisplayskip}{2pt}
+%\begin{align*}
+%\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_{\langle C \rangle}\right)\mat{T}_c^{-1}&
+%\mat{A}_{o}=&\mat{T}_o\left({\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}{\mat{C}_d}_{\langle C \rangle}\right)\mat{T}_o^{-1}\\
+%\mat{B}_{o}=&\mat{T}_c{\mat{B}_d}_{\langle C \rangle}\mat{K}_{\langle C \rangle}\mat{T}_o^{-1}&
+%\mat{B}_{e}=&\mat{T}_c(\mat{B}_d-{\mat{B}_d}_{\langle C \rangle})\mat{K}_{\langle C \rangle}\mat{T}_o^{-1}\\
+%\mat{A}_{e}=&\mat{T}_o\left(\mat{A}_d-{\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}\mat{C}_e\right)\mat{T}_o^{-1}&
+%\mat{C}_{e}=&\mat{C}_d-{\mat{C}_d}_{\langle C \rangle}
+%\end{align*}
+%}
+%{\setlength{\abovedisplayskip}{0pt}
+%\begin{align*}
+%\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}+\mat{B}_{e}&\mat{B}_{o}\\ \mat{A}_{e}&\mat{A}_{o}\end{array}\right]&
+%\mat{B}'=&\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]\\
+%\eta_1=&\nu_1+\nu_1'+\nu_t& \eta_2=&\nu_2+\nu_2',
+%\end{align*}
+%}
 Here $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations \footnote{see Appendix~\ref{sec:quantization-noise}}.
@@
 
-The first effect of this digitalization is that $\mat{A}'$ is not upper
-diagonal (if $\mat{A}_e$ were $0$ we could analize the eigenvalues of $\mat{A}_c+\mat{B}_e$ and $\mat{A}_o$ separately).
-We must therefore compensate for the errors introduced in order
-to find a stable solution (since our criteria are based on the above separation).  
-We can use Gershgorin disks~\cite{van1996matrix} to limit the error
+In a continuous time domain, the characteristic polynomial
+of the closed loop dynamics is defined by the characteristic polynomials of~$\mat{A}_c$
+and~$\mat{A}_o$.  The introduction of the FWL errors causes this to no longer
+be true.  We must therefore find a suitable solution to maintain this separation.
+Gershgorin disks~\cite{van1996matrix} allow us to limit the error
 in the expected eigenvalues.  Let $\delta_o=\max(\norm{{\mat{A}_e}_{i,*}}_1)$
@@
 %-------------------------------
-In many cases the response time of the system\note{you mean the step response - this concept is undefined}, i.e. how fast it converges to the set point, is a requirement of great importance. 
+In many cases the response time of the system, i.e. how fast it converges to the set point, is a requirement of great importance. 
 This is given as a ``settling time.''
@@
 \# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{order} & \multicolumn{1}{|c|}{Number of} & \multicolumn{3}{|c|}{CEGIS} & \multicolumn{3}{|c|}{CEGIS-OR} \\
-   &                                 & & \multicolumn{1}{|c|}{benchmarks}  & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{Max} & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{Max}\\\hline
-1  & DC Motor          & 2 & 100 & 1.3\,s & 26.9\,s& \xmark (22)& 1.1\,s &   3.8\,s &   \xmark (2)\\
-2  & Helicopter        & 3  & 100 & 57.2\,s & \xmark (54) & \xmark (54) & 7.1\,s  &   18.0\,s & \xmark (9)\\
-3  & Inverted Pendulum & 4 & 100 &   9.7\,s & \xmark &\xmark () & 12.0\,s  &  18.1\,s &  \xmark ()\\
-4  & Magnetic Pointer  & 2  & 100 & 5.7\,s & 229.9\,s & \xmark (38) & 3.9\,s  &  11.4\,s &  \xmark (5) \\
+   &                                 & & \multicolumn{1}{|c|}{benchmarks}  & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{t.o.} & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{t.o.}\\\hline
+1  & DC Motor          & 2 & 100 & 1.3\,s & 26.9\,s& 22& 1.1\,s &   3.8\,s & 2\\
+2  & Helicopter        & 3  & 100 & 57.2\,s & t.o. & 54 & 7.1\,s  &   18.0\,s & 9\\
+3  & Inverted Pendulum & 4 & 100 &   9.7\,s & \xmark &\xmark & 12.0\,s  &  18.1\,s &\\
+4  & Magnetic Pointer  & 2  & 100 & 5.7\,s & 229.9\,s & 38 & 3.9\,s  &  11.4\,s & 5 \\
 %5 & Magnetic Suspension          & 2 & 1 & 12.2\,s& 0.6\,s & & & N/A  &   N/A &   N/A\\
-5  & Pendulum          & 2 & 100 & 14.0\,s & 2.0\,s & \xmark ()&0.4\,s  &   4.9\,s & \xmark  (6)\\
-6  & Suspension        & 4 & 100 & 73.7\,s& \xmark & \xmark ()&24.0\,s  &   46.1\,s & \xmark ()\\
-7  & Tape Driver       & 3 & 100 & 10.1\,s& 140.3\,s & \xmark ()&2.6\,s  &   10.5\,s & \xmark ()\\
+5  & Pendulum          & 2 & 100 & 14.0\,s & 2.0\,s & \xmark&0.4\,s  &   4.9\,s & 6\\
+6  & Suspension        & 4 & 100 & 73.7\,s& \xmark & \xmark&24.0\,s  &   46.1\,s & \xmark\\
+7  & Tape Driver       & 3 & 100 & 10.1\,s& 140.3\,s & \xmark&2.6\,s  &   10.5\,s & \xmark\\
 %9 & Satellite          & 2 & 1 & 9.4\,s& 0.7\,s & & & N/A  &   N/A &   N/A\\
@@
 \caption{\label{tab:cegis_results}
-Experimental results. Minimum, Maximum and Median times for standard CEGIS vs CEGIS-OR on multiple benchmarks. \xmark~indicates timeout, with the number of benchmarks that timed out in parenthesis.}
+Experimental results. Minimum, and Median times for standard CEGIS vs CEGIS-OR on multiple benchmarks. t.o.~indicates timeouts.}
 \end{table}
@@
 \appendix
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Discretization of linear time invariant dynamical systems}\label{sec:continuous_LTI}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Discretization of a continuous dynamical system turns the ODE into a difference
-equation, assuming zero-order hold for the input $\vec{u}$ (i.e. the value $u(t)$
- is fixed for the integration period), %and continuous integration for the noise $\vec{w}$, 
-into
-\begin{align}
-\label{eq:discretization}
-\vec{x}_{k+1} &= \mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\% + \vec{w}_k\\
-y_k &= \mat{C}_d \vec{x}_ k + \mat{D}_d \vec{u}_ k 
-\end{align}
-%with covariance for $\vec{w}_k$, $N ( 0 , Q_d )$
-where
-\begin{align}
-\label{eq:discretize}
-\mat{A}_d &= e^{\mat{A} T_s} \\%= \mathcal{L}^{-1} { ( s \mat{I} - \mat{A} )^{-1} }_{t = T_s}\\
-\mat{B}_d &= \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B} = \mat{A}^{-1} ( \mat{A}_d - \mat{I} ) \mat{B}\\
-\mat{C}_d &= \mat{C}\\
-\mat{D}_d &= \mat{D} %\\
-%Q_d &= \int_{t = 0}^{T_s} e^{\mat{A} t} Q e^{\mat{A}^T t} dt
-\end{align}
-and $T_s$ is the sample time. Then
-\begin{align*}
-\forall k,  \vec{x}(kT_s)=\vec{x}_k \text{ and } \vec{y}(kT_s) = \vec{y}_k
-\end{align*}
-%Let $g_d(k)=\mathcal{G}(t,g(t),T)$ be a function that performs the discretization described above, where $g(t)$
-%represents the continuous dynamics and $g_d(k)$ the corresponding discrete dynamics. 
-%Let $G(s)=\mathcal{L}(g(t))$ and $G_d(z)=\mathcal{Z}(g_d(k))$ be the corresponding Laplace and Z-transforms
-%of $g(t)$ and $g_d(k)$. Given this relation, we have 
-%$$G_d(z)=G(z)|_{z=e^{sT}} \text{ where } g_d(k)=\mathcal{G}(t,g(t),T) \wedge T < \frac{1}{.5f_s}$$
-%Where $.5f_s$ is the Nyquist frequency of $g(t)$. This last restriction is introduced to avoid the effects of aliasing
-%which could cause non-existent `phantom' poles to appear otherwise at fractions of the true frequency they represent. 
-The eigenvalues of $\vec{A}_d$ %corresponding to the poles of $G_d(z)$,
-and those of $\vec{A}$ %corresponding to the poles of $G(s)$
-are related as follows:
-$\hat{\lambda}_i=e^{\lambda_iT_s} \text{ where } \hat{\lambda}_i \in \sigma(\vec{A}_d) \text{ and } \lambda_i \in \sigma(\vec{A})$
-where $\sigma(\cdot)$ is the spectrum of a matrix.
-The following remark is worth mentioning regarding the above.
-\begin{remark}
-The witnessed maximum amplitude of the discrete signals $\vec{x}_k,\vec{y}_k$
-may be smaller to that of $\vec{x}(t),\vec{y}(t)$ due to synchronism at
-fraction-frequency sampling. This means that safety verification of the state space
-must account for this condition.
-\end{remark}
-Imagine that a signal $\vec{x}(t)=sin\left({\omega_f t}\right)$. If we sample
-this signal at intervals $T_s=\frac{\pi}{\omega_f}$ starting at $t=0$, then all
-measured samples will be $0$.  For this reason, systems must be sampled at
-intervals smaller than the maximum composing frequency of the source signal
-$T_s<\frac{\pi}{\omega_max}$.  This is the so called Nyquist Criterion~\cite{Astrom08}.  
-The maximum amplitude of the original signal can be upper bounded from the
-observed values using the inverse cosine of the sampling function.
-Since equation \eqref{eq:discretization} models \eqref{eq:dynamical} \note{fix ref}, we may use the semantics defined in Section
-\ref{sec:model_semantics} to analyse continuous dynamical systems.
 
@@
 of verification, the latter is seen as a safety problem.
-\item Null/Zeno behaviour\\
-Whilst this work does not explore Zeno behaviours, it is worth noting that this
-effect may be caused by rounding errors in floating point programs. The reason for this
-is that if an operation contains two numbers which belong to disjoint sub-domains
-(\emph{ie} neither number can be represented in the domain of its counterpart), the
-resulting operation may become a no-op/skip, subsequently destabilizing the program.
 \end{enumerate}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-In Figure \ref{fig:observersystem2} we introduced
+In Figure \ref{fig:observersystem} we introduced
 several sources of noise, which are due to quantization effects. We now describe
@@
 ${\nu_2}_k \in [-\frac{q_d}{2}, \frac{q_d}{2}]$, where given the above assumptions $q_d=q_a=q_c$. 
-This is illustrated in Figure \ref{fig:observersystem2} where $Q_1$ is the quantizer of the ADC
+This is illustrated in Figure \ref{fig:observersystem} where $Q_1$ is the quantizer of the ADC
 and $Q_2$ the quantizer for the DAC.  These bounds hold irrespective of
@@
 making part or all of the system a closed system (i.e. no inputs).
-Such a system is exemplified in figure \ref{fig:sampledsystem}.  Since the
+Such a system is exemplified in figure \ref{fig:observersystem}.  Since the
 feedback line creates a loop in the diagram this is known as a closed loop,
@@
 (e.g. convergent).  We discuss the requirements we are interested in in the following.
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Static output feedback and pole placement} \label{sec:pole_place}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-\begin{figure*}[htb]
-\centering
-
-\tikzset{add/.style n args={4}{
-    minimum width=6mm,
-    path picture={
-        \draw[circle] 
-            (path picture bounding box.south east) -- (path picture bounding box.north west)
-            (path picture bounding box.south west) -- (path picture bounding box.north east);
-        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
-        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
-        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
-        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
-        }
-    }
- }
-
-\resizebox{1.0\textwidth}{!}{
- \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
-     semithick, initial text=, ampersand replacement=\&,]
-
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
-    \node[draw=none] (r) {$R(z)$};
-%   \& \coordinate (aux0);
-   \& \node[circle,add={-}{+}{}{}] (circle) {};
-   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$e(z)$};
-   \& \node[rectangle,draw,
-	minimum width=1cm,
-	minimum height=1cm,
-        label=\textbf{Controller}] (cz) {{\sc C(z)}};
-   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$U(z)$};
-
-   \& complexnode/.pic={ 
-      \node[rectangle,draw,
-	minimum width=3cm,
-	minimum height=1.6cm,
-	label=\textbf{DAC},] (dac) {};
-     \node[circle,add={}{+}{+}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
-     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
-     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu_2(z)$};
-     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}   
-   \& \node[rectangle,draw,
-	minimum width=1cm,
-	minimum height=1cm,
-        label=\textbf{Plant}] (gs) {{\sc $G(s)$}};
-   \node[draw=none] (ud) at ([xshift=-2cm,yshift=.15cm]gs)  {$U(s)$};
-   \node[draw=none] (y) at ([xshift=2cm,yshift=.15cm]gs)  {$Y(s)$};
-   \& complexnode/.pic={ 
-     \node[rectangle,draw,
-	minimum width=4cm,
-	minimum height=1.6cm,
-	label=\textbf{ADC},] (adc) {};
-   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
-   \coordinate (switch1) at ([xshift=-1cm]adc.center);
-   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
-   \node[circle,add={}{+}{+}{},fill=gray!20] (q1) at ([xshift=1cm]adc.center) {};} 
-     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
-   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu_1(z)$};
-   \& \coordinate (aux1);
-   \& \node[draw=none] (yz) {$Y(z)$};\\
-   \& \coordinate (aux3); 
-   \&
-   \&
-   \& 
-   \& 
-   \& \coordinate (aux2);\\
-  };
-
-  \path[->] (v1) edge (q1.north);
-  \path[->] (v2) edge (q2.north);
-  \path[->] (r) edge (circle.west);
-  \path[->] (aux1) edge (yz);
-  \path  
-   (circle.east) edge (cz)
-   (cz.east) edge (q2.west)
-   (q2.east) edge (zoh.west)
-   (zoh.east) edge (gs.west)
-   (switch2) edge (q1.west)
-   (q1.east) edge (aux1.west)
-   (gs.east) edge (switch1.west)
-   (aux1.south) edge (aux2.north)
-   (aux2.west) edge (aux3.east); 
-  \path[->]  (aux3.north) edge (circle.south);
- \end{tikzpicture}
-}
- \caption{Closed loop digital control system\label{fig:sampledsystem}}
-\end{figure*}
-
-Given an unstable plant with divergent dynamics, the problem of stabilizing the
-output is to find a controller that results in convergent closed loop dynamics.
-The term Static Output Feedback relates to the desired effect of having a static
-output given a fixed reference signal.  In modern embedded systems, said
-controller is a digital program, which means that the closed loop dynamics are
-subject to time and space discretization as described in
-sections~\ref{sec:continuous_LTI} and~\ref{sec:numeric_rep}.
-In real a physical plant, these discretizations are performed by an
-Analog-to-Digital Converter(ADC) which samples the output of the plant at
-intervals $T_s$ (time discretization) and quantizes it to an FWL representation
-(space discretization).  Conversely, a Digital-to-Analog Converter(DAC)
-transforms a discretized value into a real input to the physical plant.
-In general terms, when analysing such systems, the controller is known to have
-discrete dynamics, whereas the plant must be discretised based on the sample
-and hold characteristics. The ADC/DAC converters are considered to introduce a
-quantization noise on the system as shown in Figure~\ref{fig:sampledsystem}.
-Let the quantizer~$Q1$ be the source of a non-deterministic noise~$\nu_{1}$
-and~$Q2$ be the source of a non-deterministic noise~$\nu_{2}$.
-Convergence of such a system is a frequency domain property, which is why we
-first analyse the system using its transfer function.  The transfer function of
-a system relates its input and output in the frequency domain (more generally
-in the Laplace domain for continuous time systems and the Z-domain for discrete
-time).  In the case of linear systems, these correspond to the characteristic
-polynomials of the system dynamics (i.e. the polynomial whose roots are the
-eigenvalues of the dynamics). The following equation models the system,
-encompassing the discretization of the plant:
-%
-\begin{equation}
-Y(z)=C(z)G(z)(R(z)-Y(z))+\nu_{1}(z)+\nu_{2}(z)C(z)G(z),
-\end{equation}
-%
-The above can be rewritten as follows:
-%
-\begin{equation}
-\label{eq:outputfunctions}
-Y(z)=H_1(z)R(z)+H_2(z)\nu_{1}(z)+H_3(z)\nu_{2}(z),
-\end{equation}
-%
-where
-%
-\begin{align}
-H_1(z)=\frac{C(z)G(z)}{1+C(z)G(z)},\\
-H_2(z)=\frac{1}{1+C(z)G(z)},\\
-H_3(z)=\frac{G(z)}{1+C(z)G(z)}.
-\end{align}
-%
-
-\begin{assumption}
-\label{whitenoise}
-%
-The quantization noises $\nu_{1}$ (from $Q1$) and $\nu_{2}$ (from $Q2$) are
-uncorrelated white noises and their amplitudes are always bounded by the
-half of quantization step~\cite{astrom1997computer}, i.e., $\vert \nu_{1}
-\vert \leq \frac{q_{1}}{2}$ and $\vert \nu_{2} \vert \leq \frac{q_{2}}{2}$,
-where $q_{1}$ and $q_{2}$, respectively, are the quantization steps of ADC
-and DAC.
-% 
-\end{assumption}
-
-It is known that a discrete-time linear system is said to be Bounded-Input and Bounded-Output
-(BIBO) stable if and only if every pole of its transfer function lies inside
-the unit circle \cite{Astrom08}.  Analyzing Eq.~\eqref{eq:outputfunctions}, the following
-proposition states necessary conditions for BIBO stability of the closed-loop system
-in Figure~\ref{fig:sampledsystem}, since the exogenous signals $R(z)$,
-$\nu_{1}$, and $\nu_{2}$ are bounded. Hence, our close loop system is stable if the poles in
-$H_1(z) , H_2(z) $ and $H_3(z)$ are inside the unit circle. Since all three transfer functions share the same poles,
-we only need to look at the roots of the polynomial
-$$C_n(z)G_n(z)+C_d(z)G_d(z) : C(z)=\frac{C_n(z)}{C_d(z)} \wedge G(z)=\frac{G_n(z)}{G_d(z)}$$
-Any controller that ensures these roots lie within the unit circle is a stabilizing controller for the system.
-
-This same analysis can be applied to MIMO systems where there is a transfer functions of the system
-for each combination of input-output. Rather than examine the transfer functions of these systems, we will first
-look at minimal descriptions of the state space dynamics that will help us extract them with little extra effort whilst 
-providing us with tools to analyse other properties.
 
@@
 
-\begin{figure*}[htb]
-\centering
-\tikzset{add/.style n args={4}{
-    minimum width=6mm,
-    path picture={
-        \draw[circle] 
-            (path picture bounding box.south east) -- (path picture bounding box.north west)
-            (path picture bounding box.south west) -- (path picture bounding box.north east);
-        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
-        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
-        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
-        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
-        }
-    }
- }
-
-\resizebox{1.0\textwidth}{!}{
- \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
-     semithick, initial text=, ampersand replacement=\&,]
-
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
-    \node[draw=none] (r) {$r_k$};
-    \node[rectangle,draw,
-	minimum width=1cm,
-	minimum height=1cm,] (gain)at ([xshift=1.2cm]r) {\sc $k_r$};
-
-   \& \node[circle,add={-}{+}{+}{}] (circle) {};
-   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$u_k$};
-   \node[draw=none] (v2p)  at ([yshift=1.2cm]circle) {$\nu_2'$};
-   \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Kd) at ([xshift=0,yshift=-5.5cm]circle)  {\sc $\mat{K}_{\langle C \rangle}$};
-   \coordinate (kdsouth) at ([yshift=-3cm]Kd);
-
-   \& complexnode/.pic={ 
-      \node[rectangle,dashed,draw,minimum width=3cm,minimum height=1.6cm,label=\textbf{DAC}] (dac) {};
-     \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
-     \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
-     \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
-     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {\sc ZOH};
-   }
-
-   \& complexnode/.pic={ 
-      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Continuous Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2.5cm,yshift=.5cm]plant.center)  {\sc $\mat{B}$};
-      \node[draw=none] (u) at ([xshift=-1cm,yshift=.15cm]B)  {$u(t)$};
-      \node[circle,add={+}{+}{}{}] (p1) at ([xshift=-1.3cm,yshift=.5cm]plant.center) {};
-      \node[draw=none] (xdot) at ([xshift=.85cm,yshift=.15cm]p1)  {$\dot{\vec{x}}(t)$};   
-      \node[rectangle,draw,minimum width=1cm] (int) at ([xshift=.5cm,yshift=.5cm]plant.center) {\sc $\int$};
-      \coordinate (xsouth) at ([xshift=1cm]int);
-      \node[draw=none] (x) at ([xshift=1cm,yshift=.15cm]int)  {$\vec{x}(t)$};   
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (C) at ([xshift=2.7cm,yshift=.5cm]plant.center)  {\sc $\mat{C}$};
-      \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]C)  {$\vec{y}(t)$};   
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (A) at ([xshift=.5cm,yshift=-1cm]plant.center)  {\sc $\mat{A}$};
-      \coordinate (aeast) at ([xshift=1cm]A);
-      \coordinate (awest) at ([xshift=-1.8cm]A);
-    }   
-    \node[circle,add={+}{+}{}{}]at ([xshift=2cm]C) (lag) {};
-    \node[draw=none] (vt)  at ([yshift=-1.5cm]lag) {$\nu_t$};
-   complexnode/.pic={ 
-      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=5cm,label=\textbf{Discrete Observer}] (observer)  at ([yshift=-5cm]plant.center) {};
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Bd) at ([xshift=-2.5cm]observer.center)  {\sc ${\mat{B}_d}_{\langle C \rangle}$};
-      \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]Bd)  {$u_k$};
-      \node[circle,add={+}{+}{+}{}] (o1) at ([xshift=-1.3cm]observer.center) {};
-      \node[draw=none] (xd) at ([xshift=.85cm,yshift=.15cm]o1)  {$\hat{\vec{x}}_{k+1}$};   
-      \node[rectangle,draw,minimum width=1cm] (delay) at ([xshift=.5cm]observer.center) {\sc $z^{-1}$};
-      \coordinate (xdsouth) at ([xshift=1.3cm]delay);
-      \coordinate (fbsouth) at ([xshift=1.3cm,yshift=-3cm]delay);
-      \node[draw=none] (xdp) at ([xshift=1cm,yshift=.15cm]delay)  {$\hat{\vec{x}}_k$};   
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Cd) at ([xshift=2.7cm]observer.center)  {\sc ${\mat{C}_d}_{\langle C \rangle}$};
-      \node[draw=none] (y) at ([xshift=.4cm,yshift=.8cm]Cd)  {$\hat{\vec{y}}_k$};   
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ad) at ([xshift=.5cm,yshift=-1.5cm]observer.center)  {\sc ${\mat{A}_d}_{\langle C \rangle}$};
-      \coordinate (adeast) at ([xshift=1.3cm]Ad);
-      \coordinate (adwest) at ([xshift=-1.8cm]Ad);
-      \node[circle,add={-}{}{+}{+}] (o2) at ([xshift=2.7cm,yshift=1.5cm]observer.center) {};
-      \node[draw=none] (v1p) at ([yshift=1.2cm]o2) {$\nu_1'$};
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ld) at ([xshift=.5cm,yshift=1.5cm]observer.center)  {\sc $\mat{L}_{\langle C \rangle}$};
-      \coordinate (ldwest) at ([xshift=-1.8cm]Ld);
-      \coordinate (bdwest) at ([xshift=-5.5cm]Bd);
-      \coordinate (uksouth) at ([xshift=-5.5cm,yshift=5.5cm]Bd);
-      \coordinate (o2east) at ([xshift=7.17cm]o2);
-    }
-
-   \& complexnode/.pic={ 
-     \node[rectangle,dashed,draw,minimum width=3.5cm,minimum height=1.6cm,label=\textbf{ADC},] (adc) {};
-     \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
-     \coordinate (switch1) at ([xshift=-1cm]adc.center);
-     \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
-     \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
-     \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
-     \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
-     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]q1)  {$\vec{y}_k$};       
-     \coordinate (ykeast) at ([xshift=1.9cm]q1);
-   } 
-   \& \coordinate (aux1);
-   \& \\
-  };
-
-  \path[->] (v1) edge (q1.south);
-  \path[->] (v2) edge (q2.south);
-  \path[->] (vt) edge (lag.south);
-  \path[->] (v1p) edge (o2.north);
-  \path[->] (v2p) edge (circle.north);
-  \path[->] (r) edge (gain.west);
-  \path[->] (gain.east) edge (circle.west);
-  \path[->] (circle.east) edge (q2.west);
-  \path       (q2.east) edge (zoh.west);
-  \path[->] (zoh.east) edge (B.west);
-  \path
-   (B.east) edge (p1.west)
-   (p1.east) edge (int.west)
-   (xsouth) edge (aeast)
-   (aeast) edge (A.east)
-   (A.west) edge (awest)
-   (awest) edge (p1.south)
-   (int.east) edge (C.west)
-   (C.east) edge (lag.west)
-   (lag.east) edge (switch1.west)
-   (switch2) edge (q1.west);
-  \path
-   (q1.east) edge (ykeast)
-   (ykeast) edge (o2east);
-  \path       (uksouth) edge (bdwest);
-  \path[->] (bdwest) edge (Bd.west);
-  \path
-   (Bd.east) edge (o1.west)
-   (o1.east) edge (delay.west)
-   (xdsouth) edge (adeast)
-   (adeast) edge (Ad.east)
-   (Ad.west) edge (adwest)
-   (adwest) edge (o1.south)
-   (o2.west) edge node {$\vec{y}_e$} (Ld.east)
-   (Ld.west) edge (ldwest)
-   (ldwest) edge (o1.north)
-   (delay.east) edge (Cd.west)
-   (Cd.north) edge (o2.south)
-   (o2east) edge (o2.east)
-   (xdsouth) edge (fbsouth)
-   (fbsouth) edge (kdsouth);
-  \path[->]  (kdsouth) edge (Kd.south);
-  \path[->] (Kd.north) edge (circle.south);
- \end{tikzpicture}
-}
- \caption{Closed-loop digital control system with observer\label{fig:observersystem}}
-\end{figure*}
-
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 %-------------------------------
+\setcounter{lemma}{0}
 \setcounter{theorem}{0}
@@
 
- \begin{theorem}
+ \begin{lemma}
  Given $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, we have
@@
 $\vec{x}_T$ is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T.
- \end{theorem}
-  If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x} \text{ with } T \in \mathbb{R}^+$ is the state of the system at time $t=T$.
+  If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0 \text{ with } T \in \mathbb{R}^+$ is the state of the system at time $t=T$.
+ \end{lemma}
  \begin{proof}

### 2018-01-30 TACAS2018/paper.tex
cleanup

@@
 time~\cite{middleton1990digital,van1978computing} at constant intervals, whose 
-duration we refer to as the sample time (cf. Appendix~\ref{sec:continuous_LTI}), 
+duration we refer to as the sample time $T_s$, 
 into the difference equation 
@@
 \left\{
-\begin{array}{l}
-\vec{x}_{k+1} = \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k\\
-\vec{y}_{k} = \mat{C}_d \vec{x}_k + \mat{D}_d \vec{u}_k, 
+\begin{array}{rl}
+\vec{x}_{k+1} =& \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k\\
+\vec{y}_{k} =& \mat{C} \vec{x}_k + \mat{D} \vec{u}_k, 
 \end{array}
 \right.
+\text{ where }
+\left\{
+\begin{array}{l}
+\mat{A}_d=e^\mat{A}\\
+\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}
+\end{array}
+\right.,
 \end{align} 
 %
-where $k \in \mathbb N$ is a discrete counter and $\vec{x}_{0}=\vec{x}(0)$ is the initial state. 
-Matrices $\mat{A}_d$, $\mat{B}_d$, $\mat{C}_d$ and $\mat{D}_d$ are equal-sized to $\mat{A}$, $\mat{B}$, $\mat{C}$ and $\mat{D}$ respectively,  
-and charactirize the discretized plant dynamics. 
-%, whereas the latter denote the continuous evolution.  
-In this work we raise the standard assumption that $\mat{D}_d=\mat{D}=\mat{0}$ \cite{Astrom08}.  
+%where $\mat{A}_d=e^\mat{A}$, $\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$,
+$k \in \mathbb N$ is a discrete counter and $\vec{x}_{0}=\vec{x}(0)$ is the initial state. 
+In this work we raise the standard assumption that $\mat{D}=\mat{0}$ \cite{Astrom08}.  
 %Also, since $\vec{y}$ can be directly derived from $\vec{x}$, we will omit discussing it in the following unless strictly necessary.
@@
       \node[draw=none] (xdp) at ([xshift=1cm,yshift=.15cm]delay)  {$\hat{\vec{x}}_k$};   
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Cd) at ([xshift=2.7cm]observer.center)  {\sc ${\mat{C}_d}_{\langle C \rangle}$};
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Cd) at ([xshift=2.7cm]observer.center)  {\sc $\mat{C}_{\langle C \rangle}$};
       \node[draw=none] (y) at ([xshift=.4cm,yshift=.8cm]Cd)  {$\hat{\vec{y}}_k$};   
@@
 %
-We specify model stability via Jury's criterion~\cite{fadali},%\footnote{More details on Jury's criterion is in Appendix~\ref{sec:closed_stability}.}, 
+We specify model stability via Jury's criterion~\cite{fadali}, %\footnote{More details on Jury's criterion is in Appendix~\ref{sec:closed_stability}.}, 
  which boils down to a requirement expressed as an algebraic formula - a SAT solver will manipulate the coefficients of the model's characteristic polynomial. 
@@
 ${\mat{A}_d}_{\langle C
-\rangle},{\mat{B}_d}_{\langle C \rangle},{\mat{C}_d}_{\langle C \rangle},
+\rangle},{\mat{B}_d}_{\langle C \rangle},\mat{C}_{\langle C \rangle},
 \mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \in
@@
 +\mat{B}'\left [\begin{array}{c} \vec{r}_k + \nu_2+\nu_2'\\ \nu_1+\nu_1'+\nu_t\end{array}\right]%\nonumber\\
-%\vec{y}_k= &\mat{C}_d\mat{T}_c\vec{x}_k', 
+%\vec{y}_k= &\mat{C}\mat{T}_c\vec{x}_k', 
 % + \mat{D}_{d}\vec{u}_k
@@
 $\mat{A}_{c}$ the closed loop dynamics of the controller, $\mat{A}_{o}$ the closed loop dynamics of the observer, $\mat{B}_{o}$ the feedback gain, 
- $\mat{B}'$ the noise sensitivity, and $\mat{A}_{e}$ and $\mat{B}_{e}$ the error introduced on these matrices by the FWL representation.
+ $\mat{B}'$ the noise sensitivity, and $\mat{A}_{e}$ and $\mat{B}_{e}$ the error caused by the FWL representation.
 %and we have introduced the following terms: 
@@
 %\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_{\langle C \rangle}\right)\mat{T}_c^{-1}&
-%\mat{A}_{o}=&\mat{T}_o\left({\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}{\mat{C}_d}_{\langle C \rangle}\right)\mat{T}_o^{-1}\\
+%\mat{A}_{o}=&\mat{T}_o\left({\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}\mat{C}_{\langle C \rangle}\right)\mat{T}_o^{-1}\\
 %\mat{B}_{o}=&\mat{T}_c{\mat{B}_d}_{\langle C \rangle}\mat{K}_{\langle C \rangle}\mat{T}_o^{-1}&
@@
 %\mat{A}_{e}=&\mat{T}_o\left(\mat{A}_d-{\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}\mat{C}_e\right)\mat{T}_o^{-1}&
-%\mat{C}_{e}=&\mat{C}_d-{\mat{C}_d}_{\langle C \rangle}
+%\mat{C}_{e}=&\mat{C}-\mat{C}_{\langle C \rangle}
 %\end{align*}
@@
 for any eigenvalue in $\mat{A}_e$.  Then $\forall i \in [1, ...\,,n],
-|{\lambda_o}_{i}-\hat{\lambda_o}_{i}|<\delta_o$,where ${\lambda_o}_{i}$ are the
+|{\lambda_o}_{i}-\hat{\lambda_o}_{i}|<\delta_o$, where ${\lambda_o}_{i}$ are the
 true eigenvalues of the observer and $\hat{\lambda_o}_{i}$ the eigenvalues of
@@
 %% sampling time ($T_d$),
-%% $\phi_{dynamics}^{T_d}:= \{\mat{A}_d, \mat{B}_d, \mat{C}_d \mid \mat{A}_d=e^{\mat{A}T_d}\},$
+%% $\phi_{dynamics}^{T_d}:= \{\mat{A}_d, \mat{B}_d, \mat{C} \mid \mat{A}_d=e^{\mat{A}T_d}\},$
 %% then initially $\phi_{synth}$ and $\phi_{static}$ are equal to:
@@
 \item Select initial precisions $\mathbb{R}_{\langle P \rangle}$ and $\mathbb{R}_{\langle C \rangle}$
-  %width for the bit vectors
   for representing the controller and the plant, respectively. These will be increased as needed.
@@
 \item Build the observer matrices ${\mat{A}_d}_{\langle C \rangle}$, ${\mat{B}_d}_{\langle C \rangle}$
-and ${\mat{C}_d}_{\langle C \rangle}$. % using the truncation described in Section~\ref{sec:numeric_rep2}.
+and $\mat{C}_{\langle C \rangle}$. % using the truncation described in Section~\ref{sec:numeric_rep2}.
 \item Transform the system into canonical form and add nondeterminism for the errors
@@
 %% as $P_a(z) = z^p+\sum_{i=1}^p{(a_i-k_i)z^{p-i}}$. 
-%% \item Compute the characteristic polynomial of the matrix $({\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}{\mat{C}_d}_{\langle C \rangle})$
+%% \item Compute the characteristic polynomial of the matrix $({\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}\mat{C}_{\langle C \rangle})$
 %% as $P_l(z) = z^p+\sum_{i=1}^p{(l_i-a_i)z^{p-i}}$. 
@@
 3  & Inverted Pendulum & 4 & 100 &   9.7\,s & \xmark &\xmark & 12.0\,s  &  18.1\,s &\\
-4  & Magnetic Pointer  & 2  & 100 & 5.7\,s & 229.9\,s & 38 & 3.9\,s  &  11.4\,s & 5 \\
+4  & Magnetic Pointer  & 2  & 100 & 5.7\,s & 229.9\,s & 38 & 3.0\,s  &  9.5\,s & 7 \\
 %5 & Magnetic Suspension          & 2 & 1 & 12.2\,s& 0.6\,s & & & N/A  &   N/A &   N/A\\
-5  & Pendulum          & 2 & 100 & 14.0\,s & 2.0\,s & \xmark&0.4\,s  &   4.9\,s & 6\\
+5  & Pendulum          & 2 & 100 & 0.8\,s & 53.6\,s & 33 &0.4\,s  &   4.9\,s & 6\\
 6  & Suspension        & 4 & 100 & 73.7\,s& \xmark & \xmark&24.0\,s  &   46.1\,s & \xmark\\
-7  & Tape Driver       & 3 & 100 & 10.1\,s& 140.3\,s & \xmark&2.6\,s  &   10.5\,s & \xmark\\
+7  & Tape Driver       & 3 & 100 & 10.1\,s& 140.3\,s & \xmark&3.4\,s  &   19.3\,s & 8\\
 %9 & Satellite          & 2 & 1 & 9.4\,s& 0.7\,s & & & N/A  &   N/A &   N/A\\
@@
 \begin{align*}
-\nu_1' &\in \left[  -p(\norm{{\mat{C}_d}_{\langle C \rangle}}_1+2) \frac{q_c}{2},\, p(\norm{{\mat{C}_d}_{\langle C \rangle}}_1+2) \frac{q_c}{2}\right]
+\nu_1' &\in \left[  -p(\norm{\mat{C}_{\langle C \rangle}}_1+2) \frac{q_c}{2},\, p(\norm{\mat{C}_{\langle C \rangle}}_1+2) \frac{q_c}{2}\right]
 \end{align*}
@@
 stability. Further constraints to this property may be added to enforce stronger stability 
-(e.g. convergent).  We discuss the requirements we are interested in in the following.
+(e.g. convergent).  Generally speaking, we wish to simplify the model of the system to
+so that the values of the controller can be directly related to the effect they have on the
+dynamics of the closed loop.  Such representation is called a Canonical form and its shape
+and transformation depend on the shape of the controller.  We discuss the requirements
+we are interested in in the following.
 
@@
 Then the dynamics of the controllable form are
-\begin{align}
+\begin{align*}
 \hat{\vec{x}}_{k+1}=&\mat{A}_c\hat{\vec{x}}_k+\mat{B}_cu_k, \text{ where } \mat{A}_c=\mat{T}_c\mat{A}\mat{T}_c^{-1} \text{ and } \mat{B}_c=\mat{T}_c\mat{B}\\
 y_k=&\mat{C}_c\hat{\vec{x}}_k + b_0u_k, \text{ where } \mat{C}_c=\mat{C}\mat{T}_c^{-1}\nonumber
-\end{align}
+\end{align*}
 where $\mat{T}_c$ can be calculated as follows:
@@
 Let 
-\begin{equation}
+\begin{equation*}
 \mat{R}=[\begin{array}{ccccc}\mat{B}&\mat{A}\mat{B}&\mat{A}^2\mat{B}&\hdots&\mat{A}^{p-1}\mat{B}\end{array}]
 \label{eq:rncf}
-\end{equation}
+\end{equation*}
 be the reachability matrix of the system, and
-\begin{equation}
+\begin{equation*}
 \mat{R}_{c}=\left[\begin{array}{ccccc}1&a_{p-1}&a_{p-2}&\hdots&a_1\\0&1&a_{p-1}&\hdots&a_2\\ \vdots&\ddots&\ddots&\ddots&\ddots\end{array}\right]
 \label{eq:rcf}
-\end{equation}
+\end{equation*}
 the reachability matrix of the canonical form. Then 
-\begin{equation}
+\begin{equation*}
 \mat{T}_c=\mat{R}_{c}\mat{R}^{-1}
 \label{eq:to_cf}
-\end{equation}
+\end{equation*}
 
@@
 
-Presuming a sampled model of the plant as described in \eqref{eq:discretize}, the dynamics of the observer are:
+Presuming a sampled model of the plant as described in \eqref{eq:plant}, the dynamics of the observer are:
 \begin{equation}
 \label{eq:to_of}
-\hat{\vec{x}}_{k+1}=({\mat{A}_d}_{\langle C \rangle}-\mat{L}{\mat{C}_d}_{\langle C \rangle})\hat{\vec{x}}_k+{\mat{B}_d}_{\langle C \rangle}\vec{u}+\mat{L}\vec{y}
+\hat{\vec{x}}_{k+1}=({\mat{A}_d}_{\langle C \rangle}-\mat{L}\mat{C}_{\langle C \rangle})\hat{\vec{x}}_k+{\mat{B}_d}_{\langle C \rangle}\vec{u}+\mat{L}\vec{y}
 \end{equation}
-where the subindex ${\langle C \rangle}$ represents the domain of the controller $\mathbb{R}_{\langle C \rangle}$ such that ${\mat{A}_{\langle C \rangle}=\mathcal{F}_{\langle C \rangle}(\mat{A}_d)}$, ${\mat{B}_{\langle C \rangle}=\mathcal{F}_{\langle C \rangle}(\mat{B}_d)}$ and ${\mat{C}_{\langle C \rangle}=\mathcal{F}_{\langle C \rangle}(\mat{C}_d)}$.
+where the subindex ${\langle C \rangle}$ represents the domain of the controller $\mathbb{R}_{\langle C \rangle}$ such that ${\mat{A}_{\langle C \rangle}=\mathcal{F}_{\langle C \rangle}(\mat{A}_d)}$, ${\mat{B}_{\langle C \rangle}=\mathcal{F}_{\langle C \rangle}(\mat{B}_d)}$ and ${\mat{C}_{\langle C \rangle}=\mathcal{F}_{\langle C \rangle}(\mat{C})}$.
 The differentiation between $\mat{*}_{\langle C \rangle}$ and $\mat{*}$ will be exploited later in this work. For the time being we will assume they are the same. 
@@
 For SISO systems, this is:
-\begin{align}
+\begin{align*}
 \label{of_SISO}
@@
 \mat{C}_o=&[\begin{array}{cccccc}\ \ \ \ 1&\ \ \ \ 0&0&0&\cdots&0\end{array}] \nonumber
-\end{align}
+\end{align*}
 
@@
 Let 
-\begin{equation}
+\begin{equation*}
 \label{eq:wnof}
 \mat{W}=\left[\begin{array}{c}\mat{C}\\ \mat{C}\mat{A}\\ \mat{C}\mat{A}^2\\ \vdots\\ \mat{C}\mat{A}^{p-1}\end{array}\right]
-\end{equation}
+\end{equation*}
 be the observability matrix of the system, and
-\begin{equation}
+\begin{equation*}
 \label{eq:wof}
 \mat{W}_{o}=\mat{R}_{c}^{-1}
-\end{equation}
+\end{equation*}
 the observability matrix of the canonical form (see eg~\cite{Astrom08}). Then the matrix $\mat{T}_o=\mat{W}^{-1}\mat{W}_{o}$ will transform an observable system into its canonical form.
@@
 \left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_{k+1}
-=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}&\mat{B}_d\mat{K}\\ \mat{0}&\mat{A}_d-\mat{L}\mat{C}_d\end{array}\right]
+=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}&\mat{B}_d\mat{K}\\ \mat{0}&\mat{A}_d-\mat{L}\mat{C}\end{array}\right]
 \left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_k
@@
 By translating the coordinate system to 
-\begin{equation}
+\begin{equation*}
 \left[\begin{array}{c}\vec{x}'\\ \vec{x}_e'\end{array}\right]=
@@
 \left[\begin{array}{c}\vec{x}\\ \vec{x}_e\end{array}\right]
-\end{equation}
+\end{equation*}
 where $\mat{T}_c=\mat{R}_{c}\mat{R}^{-1}$ and $\mat{T}_o=\mat{W}^{-1}\mat{W}_{o}$, we can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
@@
 \mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
-\mat{A}_{o}=&\mat{T}_o\left(\mat{A}_d-\mat{L}\mat{C}_d\right)\mat{T}_o^{-1}\\
+\mat{A}_{o}=&\mat{T}_o\left(\mat{A}_d-\mat{L}\mat{C}\right)\mat{T}_o^{-1}\\
 \mat{B}_{o}=&\mat{T}_c\mat{B}_d\mat{K}\mat{T}_o^{-1}&
-\mat{C}_t=&\mat{C}_d\mat{T}_c
+\mat{C}_t=&\mat{C}\mat{T}_c
 \end{align*}
@@
 \end{displaymath}
-This has a similar structure to \eqref{eq:discretization} which will be helpful in our analysis.
+This has a similar structure to \eqref{equ:reachtraj} which will be helpful in our analysis.
 
@@
  \begin{proof}
- Let us recall equation \ref{eq:discretize}. The discrete representation of the system dynamics discretised with sample time $T_1$ is ruled by the formula
+ Let us recall equation \ref{eq:plant}. The discrete representation of the system dynamics discretised with sample time $T_1$ is ruled by the formula
  $\mat{A}_1 = e^{\mat{A} T_1}$. From matrix theory, we have 
-\begin{align}
+\begin{align*}
  e^{\mat{A}}&=\sum_{k=0}^\infty \frac{1}{k!}\mat{A}^k
-\end{align} 
-\begin{align} 
+\end{align*} 
+\begin{align*} 
  e^{\mat{S}\mat{J}\mat{S}^{-1}}&=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{S}\mat{J}\mat{S}^{-1}\right)^k
@@
  &=\mat{S}e^{\mat{J}}\mat{S}^{-1}
-\end{align} 
-\begin{equation}
+\end{align*} 
+\begin{equation*}
 \mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \Rightarrow \vec{A}_1 = \mat{S}\mat{J}_1\mat{S}^{-1}= \mat{S}e^{\mat{J} T_1}\mat{S}^{-1}.
- \end{equation}
+ \end{equation*}
 
@@
  We can then say that 
- \begin{equation}
+ \begin{equation*}
  {\lambda_2}_i=e^{\lambda_i T_1 \frac{T_2}{T_1}}={\lambda_1}_i^{\frac{T_2}{T_1}} \Rightarrow A_2=A_1^{\frac{T_2}{T_1}}.
- \end{equation}
+ \end{equation*}
  This proves the theorem for $gm(\lambda_i)=1$.
@@
  referenced to the original eigenvalues modified by the sampling rate.
-  Let $\mat{J}\in \mathbb{R}^{p \times p}$ be a Jordan Canonical matrix whose powers are described in Equation \eqref{jord:pow}
- Then
-\begin{align}
+  Let $\mat{J}\in \mathbb{R}^{p \times p}$ be a Jordan Canonical matrix, then
+\begin{align*}
  \mat{J}_1&=\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{J}T_1\right)^k\nonumber\\
@@
 \end{array} \right ] T_1^k
-\end{align}
+\end{align*}
 The eigenvalues remain the same as in the diagonal case, but the upper triangular terms are of the form:
-\begin{align}
+\begin{align*}
 \forall j>i, c_{ij}&=\sum_{k=j-i}^\infty \frac{1}{k!}\binom{k}{j-i} \lambda_i^{k-(j-i)}T_1^k\\
@@
 &=\frac{T_1^{j-i}e^{\lambda_i T_1}}{(j-i)!}\nonumber
-\end{align}
+\end{align*}
 which completes the proof for $gm(\lambda_i)>1$. \qed
@@
  \begin{align}
- \vec{x}_T&=\vec{x}(t=T)=\mat{A}^{-1}\vec{x}_T'\nonumber\\
-\vec{x}_T'&=\mat{A}\mat{A}_T\vec{x}_0 + (\mat{I}-\mat{A}_T)\mat{B}\vec{u} \text{ where } \forall t \leq T,\ \vec{u}(t)=\vec{u} 
+ \vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u} \text{ where } \mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B} 
+ \label{eq:param_discretize}
  \end{align}
@@
  \begin{proof}
- We begin by expanding the equation
- \begin{align}
- \vec{x}_T&=\mat{A}^{-1}\vec{x}_T'\nonumber\\
- &=\mat{A}_T\vec{x}_0 + \mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}\vec{u}\nonumber\\
- &= \mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u}
- \end{align}
- where $\mat{A}_T=e^{\mat{A}T}$ and $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$ correspond to $\mat{A}_d$ and $\mat{B}_d$ in equation \eqref{eq:discretize}
+ The first part of the equation ($\mat{A}_T\vec{x}_0$) is proven in the previous section.  As for the second part, we have from equation \eqref{eq:plant}
+that $\mat{B}_T = \int_{t = 0}^{T} e^{\mat{A} t} dt\ \mat{B}$ which expands to $\mat{B}_T= (\mat{A}^{-1} e^{\mat{A}T}-\mat{A}^{-1} e^{\mat{A} 0}) \mat{B}=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$, thus proving the theorem.
  \end{proof}
@@
  \end{align}
- with $\mat{A}_T, \mat{B}_T$ as per \eqref{eq:continuous_tube_dyn} and $\mat{A}_d, \mat{B}_d$ as per equation \eqref{eq:discretize} is a witness of the system
- \begin{align}
+ with $\mat{A}_T, \mat{B}_T$ as per \eqref{eq:continuous_tube_dyn} and \eqref{eq:param_discretize} and $\mat{A}_d, \mat{B}_d$ as per equation \eqref{eq:plant} is the state of the system
+ \begin{align*}
  \dot{\vec{x}}({t}) &= \mat{A}\vec{x}+\mat{B}\vec{u}(t)\nonumber\\
  \vec{u}(t)&=\mat{K}\vec{x}_k, \text{ where }  kT_s \leq t < (k+1)T_s
- \end{align}
+ \end{align*}
  \end{theorem}
@@
 The closed loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
-\begin{equation}
+\begin{equation*}
 \vec{x}_{k,t'}=\mat{A}_{t'}\vec{x}_k-\mat{B}_{t'}\mat{K}\vec{x}_k = (\mat{A}_{t'}-\mat{B}_{t'}\mat{K})\vec{x}_k, \text{ where }  0 \leq t' < T_s
-\end{equation}
+\end{equation*}
 We further explore the dynamics across discrete time boundaries. Let $\mat{A}_d=\mat{A}_{T_s}$ and $\mat{B}_d=\mat{B}_{T_s}$
-\begin{align}
+\begin{align*}
 \vec{x}_{k}&=\vec{x}_{k-1,T_s}= (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}\\
 \vec{x}_{k,T_s} &= (\mat{A}_d-\mat{B}_d\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}
-\end{align}
+\end{align*}
 which accelerating results and setting $T=kT_s+t'$ becomes
@@
 %
-\begin{align}
+\begin{align*}
 \vec{x}_{k} &=\mat{A}_{t_s}(\mat{A}_{t_d}\vec{x}_{k-1}-\mat{B}_{t_d}\mat{K}\vec{x}_{k-2})-\mat{B}\mat{K}\vec{x}_{k-1}\nonumber\\
@@
 \label{eq:delay_cont}
-\end{align}
+\end{align*}
 %
@@
 %
-\begin{align}
+\begin{align*}
 {\vec{x}_e}_{k}=&(\mat{B}_{T_s}-\mat{B}_{t_s})\mat{K}\vec{x}_{k-1}-\mat{A}_{t_s}\mat{B}_{t_d}\mat{K}\vec{x}_{k-2}\nonumber\\
 =&(\mat{B}_{T_s}-\mat{B}_{t_s})\vec{u}_{k}-\mat{A}_{t_s}\mat{B}_{t_d}\vec{u}_{k-1}
-\end{align}
+\end{align*}
 Rather than explicitly calculate this error, we will find an upper bound. Let $U = \bigcup \vec{u}_k$. Propagating the error to the output $\vec{y}_k$ we have:
-\begin{align}
+\begin{align*}
 {\vec{y}_e}_{k} \subseteq &\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})U\oplus\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}U\\
 \Rightarrow \norm{{\vec{y}_e}_{k}}_1 \leq & (\norm{\mat{C}(\mat{B}_{T_s}-\mat{B}_{t_s})}_1+\norm{\mat{C}\mat{A}_{t_s}\mat{B}_{t_d}}_1)\norm{U}_1
-\end{align}
+\end{align*}
 \end{proof}
@@
 %
-\begin{align}
+\begin{align*}
 y_k&=\mat{C}'\mat{J}^k\vec{x}_0 = \sum_{i=0}^p \left( c_i \lambda_i^k{\vec{x}_0}_i + \sum\limits_{j=1}^{gm(i)}c_{i+j}\binom{k}{j} \lambda_i^{k-j}{\vec{x}_0}_j\right)\\
@@
 %y_T&=\mat{C}'\mat{J}_T\vec{x}_0' = \sum_{i=0}^p e^{T\lambda_i}\left( c_i'{\vec{x}_0'}_i + \sum\limits_{j=1}^{gm(i)}c_{i+j}'T^j{\vec{x}_0'}_j\right)
-\end{align}
+\end{align*}
 where the second  part of the equation corresponds to the upper diagonal
@@
 %
-\begin{align}
+\begin{align*}
 |y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^p \left|c_i + \sum\limits_{j=1}^{gm(i)}c_{i+j}\binom{k}{j} \lambda_i^{-j}\right|
-\end{align}
+\end{align*}
 %
@@
 %
-\begin{align}
+\begin{align*}
 |y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^p |c_i|
-\end{align}
+\end{align*}
 

### 2018-01-30 TACAS2018/paper.tex
more  results
sec 8

@@
  \end{align}
+\note{shouldn't K be denoted with index, so that it belongs to the domain of the controller?}
  \end{theorem}
@@
 %}
-Here $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations \footnote{see Appendix~\ref{sec:quantization-noise}}.
+Here $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations (details are in Appendix~\ref{sec:quantization-noise}).
 
@@
 for any eigenvalue in $\mat{A}_e$.  Then $\forall i \in [1, ...\,,n],
-|{\lambda_o}_{i}-\hat{\lambda_o}_{i}|<\delta_o$, where ${\lambda_o}_{i}$ are the
-true eigenvalues of the observer and $\hat{\lambda_o}_{i}$ the eigenvalues of
+|{\lambda_o}_{i}-\hat{\lambda}_{oi}|<\delta_o$, where ${\lambda_o}_{i}$ are the
+true eigenvalues of the observer and $\hat{\lambda}_{oi}$ the eigenvalues of
 the perturbed observer.  We note that in the case of stability we only care
@@
 \begin{equation}
-P_o'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_o)\overline{\lambda}
+P_o'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_o)\overline{\lambda}. 
 \end{equation}
@@
 \begin{equation}
-P_r'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_c)\overline{\lambda}
+P_r'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_c)\overline{\lambda}. 
 \end{equation}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-A safety specification gives raise to a requirement on the states of
+A safety specification leads to a requirement on the states of
 the model. Consequently, the controller must ensure that the state
@@
 as described in Section~\ref{sec:transientspecification}.
-\item Calculate a set of initial bounds on $\mat{K}$, $\phi_\mathit{init}^{K}$,
+\item Calculate a set of initial bounds on $\mat{K}$, 
+\note{shouldn't K be denoted with index, so that it belongs to the domain of the controller? Recall the notations used in the Figure.}
+$\phi_\mathit{init}^{K}$,
 based on the input constraints.
@@
 \begin{equation}
-e = \max(\{\min(\{\vec{x}-\vec{g}, \vec{g}\in G\}), \vec{x} \in \hat{X}_\infty \}).
+e = \max\{\min\{\vec{x}-\vec{g}, \vec{g}\in G\}, \vec{x} \in \hat{X}_\infty \}.
 \label{eq:objective}
@@
 that still satisfies the controller constraints ($f \overline{\lambda}
-\models \phi$).  The resulting observer and controller are then
+\models \phi$ \note{wrong notation: it's not that the eigenvalue satisfies a constraint - rather, the corresponding model does? }).  The resulting observer and controller are then
 verified against the safety specification $\phi_\mathit{safety}$ and the
@@
 In the second stage, we take the complex eigenvalue
-with the largest angle ($max\{|tan^{-1}\left(\frac{im(\lambda)}{re(\lambda)}\right)| \mid \lambda \in \Lambda\}$)
-and reduce its imaginary component only  ($re(\lambda) + f im(\lambda) \models \phi$).
+with the largest angle ($\max\{|\tan^{-1}\left(\frac{im(\lambda)}{re(\lambda)}\right)| \mid \lambda \in \Lambda\}$)
+and reduce its imaginary component only  ($re(\lambda) + f\, im(\lambda) \models \phi$).
 The process ends when no imaginary part can be further reduced.
@@
 \caption{CEGIS-OR: CEGIS with Optimization Refinement. Orange boxes (light) are modelling
-stages, blue boxes (dark) are verification stages, and the red box is the synthesis stage.}
+stages, blue boxes (dark) are verification stages, and the red box is the synthesis stage. 
+\note{shouldn't K-L be denoted with index, so that it belongs to the domain of the controller?}}
 \label{fig:CEGIS-OR}
@@
 thus creating seven hundred benchmarks from this base.
-In the verification module, we have used the tool Axelerator~\cite{} .
+In the verification module, we have used the tool \note{Axelerator~\cite{}}.
 
@@
 2  & Helicopter        & 3  & 100 & 57.2\,s & t.o. & 54 & 7.1\,s  &   18.0\,s & 9\\
-3  & Inverted Pendulum & 4 & 100 &   9.7\,s & \xmark &\xmark & 12.0\,s  &  18.1\,s &\\
+3  & Inverted Pendulum & 4 & 100 &   & \xmark &\xmark & 20.0\,s  &  348.1\,s & 19\\
 4  & Magnetic Pointer  & 2  & 100 & 5.7\,s & 229.9\,s & 38 & 3.0\,s  &  9.5\,s & 7 \\
@@
 5  & Pendulum          & 2 & 100 & 0.8\,s & 53.6\,s & 33 &0.4\,s  &   4.9\,s & 6\\
-6  & Suspension        & 4 & 100 & 73.7\,s& \xmark & \xmark&24.0\,s  &   46.1\,s & \xmark\\
-7  & Tape Driver       & 3 & 100 & 10.1\,s& 140.3\,s & \xmark&3.4\,s  &   19.3\,s & 8\\
+6  & Suspension        & 4 & 100 & & & \xmark& &  & \xmark\\
+7  & Tape Driver       & 3 & 100 & 4.0\,s& 17.7\,s & 11&3.1\,s  &   16.8\,s & 8\\
 %9 & Satellite          & 2 & 1 & 9.4\,s& 0.7\,s & & & N/A  &   N/A &   N/A\\
@@
 \caption{\label{tab:cegis_results}
-Experimental results. Minimum, and Median times for standard CEGIS vs CEGIS-OR on multiple benchmarks. t.o.~indicates timeouts.}
+Experimental results.
+Minimum, and Median times for standard CEGIS vs CEGIS-OR on multiple benchmarks.
+t.o.~indicates timeouts.
+\note{It is unclear what the difference is btw t.o.
+used in the third column header, and that used within the table - the latter is corresponding to a cross?} \note{recall what a model order is.}}
 \end{table}
 
-Using the described technique we managed to synthesize controllers for X benchmarks, with a median synthesis time of $18.8$ seconds.
+Using the described technique we managed to synthesize controllers for \note{X} benchmarks, with a median synthesis time of $18.8$ seconds.
 %and the maximum observed synthesis time was under 10 minutes for a $4^{th}$ order system ($8^{th}$ order considering the observer).
@@
 There are cases for which the system fails to find a controller.  We use a
-relatively short timeout, so it is possible that longer timeouts would result in a
+relatively short timeout, so it is possible that longer timeouts would instead lead to a
 valid solution. However, as stated before, the solution is sound but incomplete,

### 2018-01-31 TACAS2018/paper.tex
canonical forms

@@
 %
+{\setlength{\belowdisplayskip}{2pt}
 \begin{align}
@@
 \end{align}
+}
+{\setlength{\abovedisplayskip}{2pt}
+\setlength{\belowdisplayskip}{2pt}
+\begin{align*}
+\mat{A}_c=&\left[\begin{array}{cc}
+\begin{array}{ccc}k_{n-1}-a_{n-1}&\cdots&k_1-a_1\end{array}&k_0-a_0\\
+\mat{I}&\begin{array}{c}0\\ \vdots \\ 0\end{array}
+\end{array}\right]&
+\mat{A}_o=&\left[\begin{array}{cc}
+\begin{array}{c}l_{n-1}-a_{n-1}\\ \vdots\\ l_1-a_1\end{array}&\mat{I}\\
+l_0-a_0&\begin{array}{ccc}0&\cdots&0\end{array}
+\end{array}\right]
+\end{align*}
+}
+
 where $\vec{x}'$ and $\vec{x}_e'$ are the state of the system and the error of the observer evaluated in the transformed domain, 
-$\mat{A}_{c}$ the closed loop dynamics of the controller, $\mat{A}_{o}$ the closed loop dynamics of the observer, $\mat{B}_{o}$ the feedback gain, 
+$\mat{A}_{c}$ the closed loop dynamics of the controller in canonical form, $\mat{A}_{o}$ the closed loop dynamics of the observer in canonical form, $\mat{B}_{o}$ the feedback gain, 
  $\mat{B}'$ the noise sensitivity, and $\mat{A}_{e}$ and $\mat{B}_{e}$ the error caused by the FWL representation.
@@
 
-\note{the remainder of this section is not self contained and totally unclear.}
-
 In a continuous time domain, the characteristic polynomial
@@
 be true.  We must therefore find a suitable solution to maintain this separation.
+
 Gershgorin disks~\cite{van1996matrix} allow us to limit the error
@@
 \begin{equation}
-P_o'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_o)\overline{\lambda}. 
+P_o'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_o)\overline{\lambda} \text{ and } c_j=l_j-a_j.
 \end{equation}
@@
 \begin{equation}
-P_r'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_c)\overline{\lambda}. 
+P_r'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_c)\overline{\lambda} \text{ and } c_j=k_j-a_j.
 \end{equation}
@@
 5  & Pendulum          & 2 & 100 & 0.8\,s & 53.6\,s & 33 &0.4\,s  &   4.9\,s & 6\\
-6  & Suspension        & 4 & 100 & & & \xmark& &  & \xmark\\
+6  & Suspension        & 4 & 100 & & & \xmark& 14.8\,s&166.9\,s  & 26 \\
 7  & Tape Driver       & 3 & 100 & 4.0\,s& 17.7\,s & 11&3.1\,s  &   16.8\,s & 8\\

### 2018-01-31 TACAS2018/paper.tex
sec 7+8

--- 2018-01-30 TACAS2018/paper.tex
@@
 purpose, we take the largest eigenvalue and reduce it by a factor $f$
-that still satisfies the controller constraints ($f \overline{\lambda}
-\models \phi$).  The resulting observer and controller are then
+that still satisfies the controller constraints.
+The resulting observer and controller are then
 verified against the safety specification $\phi_\mathit{safety}$ and the
@@
 with the largest angle ($max\{|tan^{-1}\left(\frac{im(\lambda)}{re(\lambda)}\right)| \mid \lambda \in \Lambda\}$)
-and reduce its imaginary component only  ($re(\lambda) + f im(\lambda) \models \phi$).
+and reduce its imaginary component only.
 The process ends when no imaginary part can be further reduced.
@@
 \caption{\label{tab:cegis_results}
-Experimental results. Minimum, and Median times for standard CEGIS vs CEGIS-OR on multiple benchmarks. t.o.~indicates timeouts.}
+Experimental results. Minimum, and Median times for standard CEGIS vs CEGIS-OR on multiple benchmarks. the t.o. column ~indicates number of timeouts.}
 \end{table}
@@
 so it is impossible to tell if a solution exists in these cases. 
+\note{I don't think this is stated before so explain it here.}
 
@@
 
-More interesting cases appear when we increase the order, showing initially that
-benchmarks that timed-out using standard CEGIS are now running in under 2
-minutes using CEGIS-OR. This is the result of removing several multiplications which are
-known to be difficult for SAT solvers.  Furthermore, when we introduce Optimization
-Refinement there is a further improvement up to an order of magnitude.  This second
-improvement is due to the elimination of counterexamples that would have been
-created without the refinement. Since further synthesis require increasingly
-complex models which are linear in the number of multiplications, eliminating 
-these results in large improvements.  In cases when the initial candidate is
-suitable, we gain nothing with the refinement and therefore find similar times.
-Improvements using this approach will therefore be observed in higher order
-systems or when the safety specification is tight and the original loop would
-require multiple counterexamples.
+More interesting cases appear when we increase the order, showing
+initially that benchmarks that timed-out using standard CEGIS are now
+running in under 2 minutes using CEGIS-OR. This is the result of
+removing several multiplications which are known to be difficult for
+SAT solvers.  Furthermore, when we introduce Optimization Refinement
+there is a further improvement up to an order of magnitude.  This
+second improvement is due to the elimination of counterexamples that
+would have been created without the refinement. Since further
+synthesis require increasingly complex models which are linear in the
+number of multiplications, eliminating these results in large
+improvements.  In cases when the initial candidate is suitable, we
+gain nothing with the refinement.  Improvements using this approach
+will therefore be observed in higher order systems or when the safety
+specification is tight and the original loop would require multiple
+counterexamples.
 

### 2018-01-31 TACAS2018/paper.tex
nudge

--- 2018-01-31 TACAS2018/paper.tex
@@
 purpose, we take the largest eigenvalue and reduce it by a factor $f$
-that still satisfies the controller constraints ($f \overline{\lambda}
-\models \phi$ \note{wrong notation: it's not that the eigenvalue satisfies a constraint - rather, the corresponding model does? }).  The resulting observer and controller are then
+that still satisfies the controller constraints $\phi_\mathit{init}^{K}$.
+%($f \overline{\lambda}\models \phi$ \note{wrong notation: it's not that the eigenvalue satisfies a constraint - rather, the corresponding model does? }). 
+The resulting observer and controller are then
 verified against the safety specification $\phi_\mathit{safety}$ and the
@@
 thus creating seven hundred benchmarks from this base.
-In the verification module, we have used the tool \note{Axelerator~\cite{}}.
+%In the verification module, we have used the tool \note{Axelerator~\cite{}}.
 
@@
 %
-\begin{tabular}{| r | l | c | c | r | r | r | r | r | r | r |}
+\begin{tabular}{| r | l | c | c | r | r | r | r | r | r | r | r | r |}
 %
 \hline
-\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{order} & \multicolumn{1}{|c|}{Number of} & \multicolumn{3}{|c|}{CEGIS} & \multicolumn{3}{|c|}{CEGIS-OR} \\
-   &                                 & & \multicolumn{1}{|c|}{benchmarks}  & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{t.o.} & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{t.o.}\\\hline
-1  & DC Motor          & 2 & 100 & 1.3\,s & 26.9\,s& 22& 1.1\,s &   3.8\,s & 2\\
-2  & Helicopter        & 3  & 100 & 57.2\,s & t.o. & 54 & 7.1\,s  &   18.0\,s & 9\\
-3  & Inverted Pendulum & 4 & 100 &   & \xmark &\xmark & 20.0\,s  &  348.1\,s & 19\\
-4  & Magnetic Pointer  & 2  & 100 & 5.7\,s & 229.9\,s & 38 & 3.0\,s  &  9.5\,s & 7 \\
+\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{order} & \multicolumn{1}{|c|}{No.} & \multicolumn{4}{|c|}{CEGIS} & \multicolumn{4}{|c|}{CEGIS-OR} \\
+   &                                 & & \multicolumn{1}{|c|}{}  & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{t.o.} & \multicolumn{1}{|c|}{found} & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{t.o.} & \multicolumn{1}{|c|}{found}\\\hline
+1  & DC Motor          & 2 & 100 & 1.3\,s & 26.9\,s& 22& 20& 1.1\,s &   3.8\,s & 2 & 58\\
+2  & Helicopter        & 3  & 100 & 57.2\,s & t.o. & 54 & 15 & 7.1\,s  &   18.0\,s & 9 & 90\\
+3  & Inverted Pendulum & 4 & 100 &  277\,s& t.o. & 25& 0 & 20.0\,s  &  t.o. & 37 & 19\\
+4  & Magnetic Pointer  & 2  & 100 & 5.7\,s & 229.9\,s & 38 & 42 & 3.0\,s  &  9.5\,s & 5 & 95 \\
 %5 & Magnetic Suspension          & 2 & 1 & 12.2\,s& 0.6\,s & & & N/A  &   N/A &   N/A\\
-5  & Pendulum          & 2 & 100 & 0.8\,s & 53.6\,s & 33 &0.4\,s  &   4.9\,s & 6\\
-6  & Suspension        & 4 & 100 & & & \xmark& 14.8\,s&166.9\,s  & 26 \\
-7  & Tape Driver       & 3 & 100 & 4.0\,s& 17.7\,s & 11&3.1\,s  &   16.8\,s & 8\\
+5  & Pendulum          & 2 & 100 & 0.8\,s & 53.6\,s & 27 & 71 &0.4\,s  &   4.9\,s & 6 & 92\\
+6  & Suspension        & 4 & 100 &15.0\,s & 146.3\,s & 25 & 62 & 14.8\,s&166.9\,s  & 26 & 73\\
+7  & Tape Driver       & 3 & 100 & 4.0\,s& 17.7\,s & 11 & 80 &3.1\,s  &   16.8\,s & 8 & 82\\
 %9 & Satellite          & 2 & 1 & 9.4\,s& 0.7\,s & & & N/A  &   N/A &   N/A\\
@@
 \caption{\label{tab:cegis_results}
-Experimental results.
-Minimum, and Median times for standard CEGIS vs CEGIS-OR on multiple benchmarks.
-t.o.~indicates timeouts.
-\note{It is unclear what the difference is btw t.o.
-used in the third column header, and that used within the table - the latter is corresponding to a cross?} \note{recall what a model order is.}}
+Experimental results. Minimum, and Median times for standard CEGIS vs CEGIS-OR on multiple benchmarks. No. indicates Number of benchmarks,
+ t.o.~indicates timeouts (in the median case, it indicates more than half of the benchmarks timed out). Order is the number of states of the system.}
 \end{table}
 
-Using the described technique we managed to synthesize controllers for \note{X} benchmarks, with a median synthesis time of $18.8$ seconds.
+Using the described technique we managed to synthesize controllers for $509$ benchmarks (compared to $290$ found by our baseline), with a median synthesis time of $16.8$ seconds.
 %and the maximum observed synthesis time was under 10 minutes for a $4^{th}$ order system ($8^{th}$ order considering the observer).
@@
 standard CEGIS. We further note that the number of times standard CEGIS times
-out is much larger than CEGIS-OR which results in more found solutions.
+out is much larger than CEGIS-OR which results in more found solutions by the latter.
 The magnitude of the improvement is however, largely dependent on the shape of the problem.
 
-More interesting cases appear when we increase the order, showing initially that
-benchmarks that timed-out using standard CEGIS are now running in under 2
-minutes using CEGIS-OR. This is the result of removing several multiplications which are
-known to be difficult for SAT solvers.  Furthermore, when we introduce Optimization
-Refinement there is a further improvement up to an order of magnitude.  This second
-improvement is due to the elimination of counterexamples that would have been
+There are cases where newly found controllers are not due to the elimination of
+timeouts, but to the fact that the optimiser can reason about infinite precision
+numbers and may therefore find solutions that are not available using 64 bit 
+plant precision (the maximum allowed by our SAT solving tool).
+
+This largest improvement however, is due to the elimination of counterexamples that would have been
 created without the refinement. Since further synthesis require increasingly
@@
 suitable, we gain nothing with the refinement and therefore find similar times.
-Improvements using this approach will therefore be observed in higher order
-systems or when the safety specification is tight and the original loop would
-require multiple counterexamples.
+Improvements using this approach will therefore be observed when the safety
+specification is tight and the original loop would require multiple counterexamples.
 

### 2018-01-31 TACAS2018/paper.tex

--- 2018-01-31 TACAS2018/paper.tex
@@
 %
-{\setlength{\belowdisplayskip}{2pt}
 \begin{align}
@@
 \end{align}
-}
-{\setlength{\abovedisplayskip}{2pt}
-\setlength{\belowdisplayskip}{2pt}
-\begin{align*}
-\mat{A}_c=&\left[\begin{array}{cc}
-\begin{array}{ccc}k_{n-1}-a_{n-1}&\cdots&k_1-a_1\end{array}&k_0-a_0\\
-\mat{I}&\begin{array}{c}0\\ \vdots \\ 0\end{array}
-\end{array}\right]&
-\mat{A}_o=&\left[\begin{array}{cc}
-\begin{array}{c}l_{n-1}-a_{n-1}\\ \vdots\\ l_1-a_1\end{array}&\mat{I}\\
-l_0-a_0&\begin{array}{ccc}0&\cdots&0\end{array}
-\end{array}\right]
-\end{align*}
-}
-
 where $\vec{x}'$ and $\vec{x}_e'$ are the state of the system and the error of the observer evaluated in the transformed domain, 
-$\mat{A}_{c}$ the closed loop dynamics of the controller in canonical form, $\mat{A}_{o}$ the closed loop dynamics of the observer in canonical form, $\mat{B}_{o}$ the feedback gain, 
+$\mat{A}_{c}$ the closed loop dynamics of the controller, $\mat{A}_{o}$ the closed loop dynamics of the observer, $\mat{B}_{o}$ the feedback gain, 
  $\mat{B}'$ the noise sensitivity, and $\mat{A}_{e}$ and $\mat{B}_{e}$ the error caused by the FWL representation.
@@
 
+\note{the remainder of this section is not self contained and totally unclear.}
+
 In a continuous time domain, the characteristic polynomial
@@
 be true.  We must therefore find a suitable solution to maintain this separation.
-
 Gershgorin disks~\cite{van1996matrix} allow us to limit the error
@@
 \begin{equation}
-P_o'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_o)\overline{\lambda} \text{ and } c_j=l_j-a_j.
+P_o'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_o)\overline{\lambda}. 
 \end{equation}
@@
 \begin{equation}
-P_r'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_c)\overline{\lambda} \text{ and } c_j=k_j-a_j.
+P_r'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_c)\overline{\lambda}. 
 \end{equation}
@@
 and reduce its imaginary component only  ($re(\lambda) + f\, im(\lambda) \models \phi$).
+\note{notation again.}
 The process ends when no imaginary part can be further reduced.
@@
 5  & Pendulum          & 2 & 100 & 0.8\,s & 53.6\,s & 33 &0.4\,s  &   4.9\,s & 6\\
-6  & Suspension        & 4 & 100 & & & \xmark& 14.8\,s&166.9\,s  & 26 \\
+6  & Suspension        & 4 & 100 & & & \xmark& &  & \xmark\\
 7  & Tape Driver       & 3 & 100 & 4.0\,s& 17.7\,s & 11&3.1\,s  &   16.8\,s & 8\\
@@
 Minimum, and Median times for standard CEGIS vs CEGIS-OR on multiple benchmarks.
-t.o.~indicates timeouts.
+the t.o.
+column ~indicates number of timeouts.
 \note{It is unclear what the difference is btw t.o.
@@
 standard CEGIS. We further note that the number of times standard CEGIS times
-out is much larger than CEGIS-OR which results in more found solutions.
-The magnitude of the improvement is however, largely dependent on the shape of the problem.
-
-More interesting cases appear when we increase the order, showing initially that
-benchmarks that timed-out using standard CEGIS are now running in under 2
-minutes using CEGIS-OR. This is the result of removing several multiplications which are
-known to be difficult for SAT solvers.  Furthermore, when we introduce Optimization
-Refinement there is a further improvement up to an order of magnitude.  This second
-improvement is due to the elimination of counterexamples that would have been
-created without the refinement. Since further synthesis require increasingly
-complex models which are linear in the number of multiplications, eliminating 
-these results in large improvements.  In cases when the initial candidate is
-suitable, we gain nothing with the refinement and therefore find similar times.
-Improvements using this approach will therefore be observed in higher order
-systems or when the safety specification is tight and the original loop would
-require multiple counterexamples.
+out is much larger than CEGIS-OR which results in more found solutions.e
+
+%% We observe that the magnitude of the improvement is however, largely dependent on the shape of the problem.
+
+Overall, we observed more improvements with CEGIS-OR for
+higher order systems or systems where the safety
+specification is tight, meaning that the standard CEGIS loop would require many iterations.
+%  We obtain the most improvements for the models with large orders?}
+%More interesting cases appear when we increase the order, showing
+For instance, benchmark X, which timed-out when using standard CEGIS,
+is running under 2 minutes using CEGIS-OR. This is the result of
+removing several multiplications which are known to be difficult for
+SAT solvers \note{I'm not sure readers will relate to where this is happening in the paper. is it the fact that you use that canonical form? then say that. however, i would have thought you do that in
+both approaches..}.
+Another factor that brings an improvement of one order of
+magnitude is the Abstraction Refinement and Optimization in CEGIS-OR
+\note{on average/an improvement of up to an order of magnitude/for some specific case?}.
+While abstraction refinement enables us to start with coarse abstractions
+that are only refined on demand, 
+the optimization
+allows to locally improve candidate solutions and avoid entire iterations of the CEGIS loop
+(which would have also required more refined abstractions).
+%% elimination of counterexamples that
+%% would have been created without the refinement. Since further
+%% synthesis require increasingly complex models which are linear in the
+%% number of multiplications, eliminating these results in large
+%% improvements.
+While some systems might still require a very pecise
+abstraction resulting in many refinements
+(this is generally the cause of time-outs in CEGIS-OR),
+others allow us to find solutions with rather coarse
+abstractions (this is reflected in the smaller minimum
+times obtained with CEGIS-OR).
+
+%% Additionally, as abstraction refinement allows us to start with coarse initial
+%% abstraction, CEGIS-OR has smaller minimum times than CEGIS, obtained
+%% when the initial coarse abstractions were sufficient to synthesise a
+%% solution.
+
+%% In cases when the initial candidate is suitable, we
+%% gain nothing with the refinement.
+%% Overall, we observed more improvements with CEGIS-OR for
+%% higher order systems or systems where the safety
+%% specification is tight, where the standard CEGIS loop would require many iterations.
+%multiple counterexamples.
 

### 2018-01-31 TACAS2018/paper.tex
Reducing the appendix

--- 2018-01-31 TACAS2018/paper.tex
@@
  \item We present a model for soundly evaluating reachability in a combined 
- continuous-discrete time/space. Sound tools for continuous time reachability 
- are scarce and to the authors' knowledge no tool provides a model that 
- combines both. 
+ continuous-discrete time/space. 
+% Sound tools for continuous time reachability are scarce and to the authors'
+% knowledge no tool provides a model that combines both. 
 \end{enumerate}
 
-\note{something like this (also, we should probably still remove some of the obvious references where they can find material themselves): }
+\note{
 Note that, while we have several reference to the appendix throughout
@@
 for the proofs of theorems.
+}
 
@@
 \mat{A}_c=&\left[\begin{array}{cc}
-\begin{array}{ccc}k_{n-1}-a_{n-1}&\cdots&k_1-a_1\end{array}&k_0-a_0\\
+\begin{array}{ccc}k_{p-1}-a_{p-1}&\cdots&k_1-a_1\end{array}&k_0-a_0\\
 \mat{I}&\begin{array}{c}0\\ \vdots \\ 0\end{array}
@@
 \mat{A}_o=&\left[\begin{array}{cc}
-\begin{array}{c}l_{n-1}-a_{n-1}\\ \vdots\\ l_1-a_1\end{array}&\mat{I}\\
+\begin{array}{c}l_{p-1}-a_{p-1}\\ \vdots\\ l_1-a_1\end{array}&\mat{I}\\
 l_0-a_0&\begin{array}{ccc}0&\cdots&0\end{array}
@@
 of the closed loop dynamics is defined by the characteristic polynomials of~$\mat{A}_c$
-and~$\mat{A}_o$.  The introduction of the FWL errors causes this to no longer
+and~$\mat{A}_o$.  
+\begin{align*}
+P(z)=P_K(z)P_L(z)=\left(z^p+\sum_{i=0}^{p-1}{(a_i-k_i)z^{i}}\right) \left(z^p+\sum_{i=0}^{p-1}{(a_i-l_i)z^{i}}\right)
+\end{align*}
+The introduction of the FWL errors causes this to no longer
 be true.  We must therefore find a suitable solution to maintain this separation.
@@
 which means we can directly modify each coefficient by selecting a controller parameter.
-In the MIMO case, the Controllable Canonical Form has the following shape:
-\begin{align}
-\mat{A}_c=&\left[
-\begin{array}{ccccc}
--\mat{a}_{p-1}\mat{M}_{p-1}&-\mat{a}_{p-2}\mat{M}_{p-2}&\cdots&-\mat{a}_{2}\mat{M}_{2}&-\mat{a}_0\mat{M}_0\\
-\mat{I}_{n-1}&0&0&\cdots&0\\
-0&\mat{I}_{n-2}&0&\cdots&0\\
-\vdots&\ddots&\ddots&\ddots&\vdots\\
-0&0&\cdots&\mat{I}_0&0
-\end{array}\right],
-\mat{B}_c=\left[
-\begin{array}{c}
-\mat{M}_0\\0\\ \vdots\\ 0\\ 0
-\end{array}\right]\nonumber\\
-\mat{C}_c=&[\begin{array}{ccccc}\mat{\Gamma}_{0}&\mat{\Gamma}_{1}&\cdots&\mat{\Gamma}_{p-1}\end{array}] 
-\label{eq:cf_MIMO}
-\end{align}
-with $\mat{I}_i,\mat{M}_i \in \mathbb{R}^{q_i \times q_i}, \mat{a}_i \in \mathbb{R}^{q \times q_i}, \mat{\Gamma}_i \in \mathbb{R}^o \text{ and for }  i \in [0, ...\,,p-q], \mat{\Gamma}_{i}=0$, where $q$ is the number of inputs, $q_i$ the number of inputs with a transfer function of order of at least $i$, $\mat{I}_i$ an identity matrix, $\mat{M}_i$ an upper triangular matrix with 1s in its diagonal, $\mat{a_i}$ a matrix of coefficients of the $i^{th}$ order on its diagonal, and $o$ the number of outputs.
-Ideally, $\forall i>0, \mat{M}_i=\mat{I}_i$
 
@@
 \end{align*}
-where $\mat{T}_c$ can be calculated as follows:
-
-Let 
-\begin{equation*}
-\mat{R}=[\begin{array}{ccccc}\mat{B}&\mat{A}\mat{B}&\mat{A}^2\mat{B}&\hdots&\mat{A}^{p-1}\mat{B}\end{array}]
-\label{eq:rncf}
-\end{equation*}
-be the reachability matrix of the system, and
-\begin{equation*}
-\mat{R}_{c}=\left[\begin{array}{ccccc}1&a_{p-1}&a_{p-2}&\hdots&a_1\\0&1&a_{p-1}&\hdots&a_2\\ \vdots&\ddots&\ddots&\ddots&\ddots\end{array}\right]
-\label{eq:rcf}
-\end{equation*}
-the reachability matrix of the canonical form. Then 
-\begin{equation*}
-\mat{T}_c=\mat{R}_{c}\mat{R}^{-1}
-\label{eq:to_cf}
-\end{equation*}
+%where $\mat{T}_c$ can be calculated as follows:
+%
+%Let 
+%\begin{equation*}
+%\mat{R}=[\begin{array}{ccccc}\mat{B}&\mat{A}\mat{B}&\mat{A}^2\mat{B}&\hdots&\mat{A}^{p-1}\mat{B}\end{array}]
+%\label{eq:rncf}
+%\end{equation*}
+%be the reachability matrix of the system, and
+%\begin{equation*}
+%\mat{R}_{c}=\left[\begin{array}{ccccc}1&a_{p-1}&a_{p-2}&\hdots&a_1\\0&1&a_{p-1}&\hdots&a_2\\ \vdots&\ddots&\ddots&\ddots&\ddots\end{array}\right]
+%\label{eq:rcf}
+%\end{equation*}
+%the reachability matrix of the canonical form. Then 
+%\begin{equation*}
+%\mat{T}_c=\mat{R}_{c}\mat{R}^{-1}
+%\label{eq:to_cf}
+%\end{equation*}
 
@@
 \begin{align*}
-\label{of_SISO}
 \mat{A}_o=&\left[
@@
 \end{align*}
-
-We notice here that $\mat{A}_o=\mat{A}_c^T, \mat{C}_o=\mat{B}_c^T$
-and $\mat{B}_o=\mat{C}_c^T$, which also applies to the MIMO case.
-
-Let 
-\begin{equation*}
-\label{eq:wnof}
-\mat{W}=\left[\begin{array}{c}\mat{C}\\ \mat{C}\mat{A}\\ \mat{C}\mat{A}^2\\ \vdots\\ \mat{C}\mat{A}^{p-1}\end{array}\right]
-\end{equation*}
-be the observability matrix of the system, and
-\begin{equation*}
-\label{eq:wof}
-\mat{W}_{o}=\mat{R}_{c}^{-1}
-\end{equation*}
-the observability matrix of the canonical form (see eg~\cite{Astrom08}). Then the matrix $\mat{T}_o=\mat{W}^{-1}\mat{W}_{o}$ will transform an observable system into its canonical form.
+We notice here that $\mat{A}_o=\mat{T}_o\mat{A}\mat{T}_o^{-1}=\mat{A}_c^T, \mat{C}_o=\mat{C}\mat{T}_o^{-1}=\mat{B}_c^T$
+and $\mat{B}_o=\mat{T}_o\mat{B}=\mat{C}_c^T$, where $\mat{T}_o$ is a transformtion of the system into observable canonical form%, which also applies to the MIMO case.
+%Let 
+%\begin{equation*}
+%\label{eq:wnof}
+%\mat{W}=\left[\begin{array}{c}\mat{C}\\ \mat{C}\mat{A}\\ \mat{C}\mat{A}^2\\ \vdots\\ \mat{C}\mat{A}^{p-1}\end{array}\right]
+%\end{equation*}
+%be the observability matrix of the system, and
+%\begin{equation*}
+%\label{eq:wof}
+%\mat{W}_{o}=\mat{R}_{c}^{-1}
+%\end{equation*}
+%the observability matrix of the canonical form (see eg~\cite{Astrom08}). Then the matrix $\mat{T}_o=\mat{W}^{-1}\mat{W}_{o}$ will transform an observable system into its canonical form.
+
 For simplicity of the description, we aggregate the noises as follows:
@@
 \end{equation*}
-where $\mat{T}_c=\mat{R}_{c}\mat{R}^{-1}$ and $\mat{T}_o=\mat{W}^{-1}\mat{W}_{o}$, we can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
+%where $\mat{T}_c=\mat{R}_{c}\mat{R}^{-1}$ and $\mat{T}_o=\mat{W}^{-1}\mat{W}_{o}$, 
+we can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
 \begin{align}

### 2018-01-31 TACAS2018/paper.tex

--- 2018-01-31 TACAS2018/paper.tex
@@
 standard CEGIS. We further note that the number of times standard CEGIS times
-out is much larger than CEGIS-OR which results in more found solutions by the latter.
-The magnitude of the improvement is however, largely dependent on the shape of the problem.
+out is much larger than CEGIS-OR which results in more found solutions.e
+
+%% We observe that the magnitude of the improvement is however, largely dependent on the shape of the problem.
+
+Overall, we observed more improvements with CEGIS-OR for
+higher order systems or systems where the safety
+specification is tight, meaning that the standard CEGIS loop would require many iterations.
+%  We obtain the most improvements for the models with large orders?}
+%More interesting cases appear when we increase the order, showing
+%% For instance, benchmark X, which timed-out when using standard CEGIS,
+%% is running under 2 minutes using CEGIS-OR. This is the result of
+%% removing several multiplications which are known to be difficult for
+%% SAT solvers \note{I'm not sure readers will relate to where this is happening in the paper.
+is it the fact that you use that canonical form?
+then say that.
+however, i would have thought you do that in
+%% both approaches..}.
+These improvements are due to the Abstraction Refinement and Optimization in CEGIS-OR.
+While abstraction refinement enables us to start with coarse abstractions
+that are only refined on demand, 
+the optimization
+allows to locally improve candidate solutions and avoid entire iterations of the CEGIS loop
+(which would have also required more refined abstractions).
+%% elimination of counterexamples that
+%% would have been created without the refinement. Since further
+%% synthesis require increasingly complex models which are linear in the
+%% number of multiplications, eliminating these results in large
+%% improvements.
+While some systems might still require a very pecise
+abstraction resulting in many refinements
+(this is generally the cause of time-outs in CEGIS-OR),
+others allow us to find solutions with rather coarse
+abstractions (this is reflected in the smaller minimum
+times obtained with CEGIS-OR).
+
+%% Additionally, as abstraction refinement allows us to start with coarse initial
+%% abstraction, CEGIS-OR has smaller minimum times than CEGIS, obtained
+%% when the initial coarse abstractions were sufficient to synthesise a
+%% solution.
+
+%% In cases when the initial candidate is suitable, we
+%% gain nothing with the refinement.
+%% Overall, we observed more improvements with CEGIS-OR for
+%% higher order systems or systems where the safety
+%% specification is tight, where the standard CEGIS loop would require many iterations.
+%multiple counterexamples.
+%% =======
+%% out is much larger than CEGIS-OR which results in more found solutions by the latter.
+%% The magnitude of the improvement is however, largely dependent on the shape of the problem.
+
+%% This largest improvement however, is due to the elimination of counterexamples that would have been
+%% created without the refinement. Since further synthesis require increasingly
+%% complex models which are linear in the number of multiplications, eliminating 
+%% these results in large improvements.  In cases when the initial candidate is
+%% suitable, we gain nothing with the refinement and therefore find similar times.
+%% Improvements using this approach will therefore be observed when the safety
+%% specification is tight and the original loop would require multiple counterexamples.
+%% >>>>>>> 24cc6678b474c2e2bd6bed94342b2d9daca1abee
 
@@
 plant precision (the maximum allowed by our SAT solving tool).
-
-This largest improvement however, is due to the elimination of counterexamples that would have been
-created without the refinement. Since further synthesis require increasingly
-complex models which are linear in the number of multiplications, eliminating 
-these results in large improvements.  In cases when the initial candidate is
-suitable, we gain nothing with the refinement and therefore find similar times.
-Improvements using this approach will therefore be observed when the safety
-specification is tight and the original loop would require multiple counterexamples.
 

### 2018-01-31 TACAS2018/paper.tex
sec 6.1 comments

@@
 New problems arise due to the FWL effects on these matrices.
+\note{which are reflected in the canonical form of the resulting model or something else to
+  connect the two sentences?} 
 The canonical form of the resulting model is expressed by:
@@
 The introduction of the FWL errors causes this to no longer
-be true.  We must therefore find a suitable solution to maintain this separation.
+be true.  We must therefore find a suitable solution to maintain this separation
+\note{which separation?}.
 

### 2018-01-31 TACAS2018/paper.tex
Fixes to results

@@
  \end{align}
-\note{shouldn't K be denoted with index, so that it belongs to the domain of the controller?}
  \end{theorem}
@@
 stages, blue boxes (dark) are verification stages, and the red box is the synthesis stage. 
-\note{shouldn't K-L be denoted with index, so that it belongs to the domain of the controller?}}
+\note{shouldn't K-L be $\mat{K}_{\langle C \rangle},\mat{L}_{\langle C \rangle}$?}}
 \label{fig:CEGIS-OR}
@@
 2  & Helicopter        & 3  & 100 & 57.2\,s & t.o. & 54 & 15 & 7.1\,s  &   18.0\,s & 9 & 90\\
-3  & Inverted Pendulum & 4 & 100 &  277\,s& t.o. & 25& 0 & 20.0\,s  &  t.o. & 37 & 19\\
+3  & Inverted Pendulum & 4 & 100 &  277\,s& t.o. & 32& 0 & 20.0\,s  &  t.o. & 37 & 19\\
 4  & Magnetic Pointer  & 2  & 100 & 5.7\,s & 229.9\,s & 38 & 42 & 3.0\,s  &  9.5\,s & 5 & 95 \\
@@
 5  & Pendulum          & 2 & 100 & 0.8\,s & 53.6\,s & 27 & 71 &0.4\,s  &   4.9\,s & 6 & 92\\
-6  & Suspension        & 4 & 100 &15.0\,s & 146.3\,s & 25 & 62 & 14.8\,s&166.9\,s  & 26 & 73\\
+6  & Suspension        & 4 & 100 &15.0\,s & 177.2\,s & 30 & 70 & 14.8\,s&166.9\,s  & 26 & 73\\
 7  & Tape Driver       & 3 & 100 & 4.0\,s& 17.7\,s & 11 & 80 &3.1\,s  &   16.8\,s & 8 & 82\\
@@
 We consider these times short enough to be of practical use to control engineers.
-There are cases for which the system fails to find a controller.  We use a
+In those cases for which the system fails to find a controller, we use a
 relatively short timeout, so it is possible that longer timeouts would instead lead to a
-valid solution. However, as stated before, the solution is sound but incomplete,
-so it is impossible to tell if a solution exists in these cases. 
-\note{I don't think this is stated before so explain it here.}
+valid solution. However, the solution is sound but incomplete, 
+since we use approximations and over-approximations that may exclude
+valid candidates in early stages, so it is impossible to tell if a solution exists in these cases.
 
@@
 Overall, we observed more improvements with CEGIS-OR for
-higher order systems or systems where the safety
-specification is tight, meaning that the standard CEGIS loop would require many iterations.
+systems where the safety specification is tight, 
+meaning that the standard CEGIS loop would require many iterations.
 %  We obtain the most improvements for the models with large orders?}
@@
 times obtained with CEGIS-OR). 
+Since further synthesis require increasingly
+complex models which are linear in the number of multiplications,
+eliminating  these results in large improvements.  In cases when the initial candidate is
+suitable, we gain nothing with the refinement and therefore find similar times.
 
@@
 
-There are cases where newly found controllers are not due to the elimination of
-timeouts, but to the fact that the optimiser can reason about infinite precision
+There are cases where newly found controllers are not due to time improvements,
+but to the fact that the optimiser can reason about infinite precision
 numbers and may therefore find solutions that are not available using 64 bit 
@@
 
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Stability of an observed system}\label{sec:cof_stability}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Careful examination of the matrices of the observed system\eqref{eq:of_dynamics} reveals that because $\mat{A}'$ is
-upper block diagonal, the spectrum of $\mat{A}'$ is equal to the union of
-the spectrum of $\mat{A}_{c}$ and $\mat{A}_{o}$, which can be calculated
-separately.  In other words, the characteristic polynomial of the closed loop is
-equal to the multiplication of the characteristic polynomials of the controller closed loop
-and the observer error when seen independently.
-%
-\begin{align*}
-P(z)=P_K(z)P_L(z)=\left(z^p+\sum_{i=0}^{p-1}{(a_i-k_i)z^{i}}\right) \left(z^p+\sum_{i=0}^{p-1}{(a_i-l_i)z^{i}}\right)
-\end{align*}
-
-We get the stability specification by applying Jury's Criterion to these polynomials.
+%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%\subsection{Stability of an observed system}\label{sec:cof_stability}
+%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%
+%Careful examination of the matrices of the observed system\eqref{eq:of_dynamics} reveals that because $\mat{A}'$ is
+%upper block diagonal, the spectrum of $\mat{A}'$ is equal to the union of
+%the spectrum of $\mat{A}_{c}$ and $\mat{A}_{o}$, which can be calculated
+%separately.  In other words, the characteristic polynomial of the closed loop is
+%equal to the multiplication of the characteristic polynomials of the controller closed loop
+%and the observer error when seen independently.
+%%
+%\begin{align*}
+%P(z)=P_K(z)P_L(z)=\left(z^p+\sum_{i=0}^{p-1}{(a_i-k_i)z^{i}}\right) \left(z^p+\sum_{i=0}^{p-1}{(a_i-l_i)z^{i}}\right)
+%\end{align*}
+%
+%We get the stability specification by applying Jury's Criterion to these polynomials.
 
@@
 %
-In the case of first and second order systems, the decay is governed by the equations 
-%
-\begin{align*}
-&y_{decay}=
-&\left\{
-\begin{array}{cc}
-e^{-|\omega| t}& 1^{st} order\\
-e^{\zeta |\omega| t}\left(\frac{\sin\left(|\omega| t\sqrt{1-\zeta^2}+\sin^{-1}\sqrt{1-\zeta^2}\right)}{\sqrt{1-\zeta^2}} \right)&\zeta<1\\
-e^{-|\omega| t}-|\omega| t e^{-|\omega| t}&\zeta=1\\
-\frac{|\omega| e^{-|\omega_2| t}-|\omega_2| e^{-|\omega| t}}{|\omega|-|\omega_2|}&\zeta>1\end{array}\right.
-\end{align*}
-where $|\omega|$ and $|\omega_2|$ are the magnitudes of the eigenvalues (roots) of the system and  $\zeta=-\cos(\theta)$ where $\theta$ is the polar angle of the conjugate pair if it exists ($\zeta \geq 1$ if it doesn't).
-These equations become increasingly complicated for higher order systems.
+%In the case of first and second order systems, the decay is governed by the equations 
+%%
+%\begin{align*}
+%&y_{decay}=
+%&\left\{
+%\begin{array}{cc}
+%e^{-|\omega| t}& 1^{st} order\\
+%e^{\zeta |\omega| t}\left(\frac{\sin\left(|\omega| t\sqrt{1-\zeta^2}+\sin^{-1}\sqrt{1-\zeta^2}\right)}{\sqrt{1-\zeta^2}} \right)&\zeta<1\\
+%e^{-|\omega| t}-|\omega| t e^{-|\omega| t}&\zeta=1\\
+%\frac{|\omega| e^{-|\omega_2| t}-|\omega_2| e^{-|\omega| t}}{|\omega|-|\omega_2|}&\zeta>1\end{array}\right.
+%\end{align*}
+%where $|\omega|$ and $|\omega_2|$ are the magnitudes of the eigenvalues (roots) of the system and  $\zeta=-\cos(\theta)$ where $\theta$ is the polar angle of the conjugate pair if it exists ($\zeta \geq 1$ if it doesn't).
+%These equations become increasingly complicated for higher order systems.
 However, we note their strong dependency on the magnitude of the eigenvalues, and use this property to define an upperbound on the decay function.
-All of the above equations will decay faster than $e^{-|\omega| t}$ given $|\omega| < |\omega_2|$, hence we may use this function as our upper bound.
+%All of the above equations will decay faster than $e^{-|\omega| t}$ given $|\omega| < |\omega_2|$, hence we may use this function as our upper bound.
 
@@
 terms of the Jordan blocks.  We also have $|\lambda_i^k|\leq
-|\overline{\omega}^k|$,hence
+|\overline{\omega}^k|$, where $|\overline{\omega}^k|$ is the norm of the largest
+eigenvalue in the system. Hence
 %

### 2018-01-31 TACAS2018/paper.tex
fixes

@@
 New problems arise due to the FWL effects on these matrices.
-\note{which are reflected in the canonical form of the resulting model or something else to
-  connect the two sentences?} 
-The canonical form of the resulting model is expressed by:
+These are reflected in the canonical form of the resulting model,
+which is expressed by:
 %
@@
 The introduction of the FWL errors causes this to no longer
-be true.  We must therefore find a suitable solution to maintain this separation
-\note{which separation?}.
+be true.  We must therefore find a suitable solution to maintain this separation of polynomials.
 
@@
 \begin{equation}
-P_o'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_o)\overline{\lambda} \text{ and } c_j=l_j-a_j.
+P_L'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_o)\overline{\lambda} \text{ and } c_j=l_j-a_j.
 \end{equation}
@@
 \begin{equation}
-P_r'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_c)\overline{\lambda} \text{ and } c_j=k_j-a_j.
+P_K'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_c)\overline{\lambda} \text{ and } c_j=k_j-a_j.
 \end{equation}
@@
 error ($\mat{A}_e$,$\mat{B}_e$), and response time %%(P_a,P_l,\overline{\lambda})$
-as described in Section~\ref{sec:transientspecification}.
+as described in Section~\ref{sec:cof_verification}.%sec:transientspecification}.
 \item Calculate a set of initial bounds on $\mat{K}$, 
-\note{shouldn't K be denoted with index, so that it belongs to the domain of the controller? Recall the notations used in the Figure.}
+%\note{shouldn't K be denoted with index, so that it belongs to the domain of the controller? Recall the notations used in the Figure.}
 $\phi_\mathit{init}^{K}$,
@@
 with the largest angle ($\max\{|\tan^{-1}\left(\frac{im(\lambda)}{re(\lambda)}\right)| \mid \lambda \in \Lambda\}$)
-and reduce its imaginary component only  ($re(\lambda) + f\, im(\lambda) \models \phi$).
-\note{notation again.}
+and reduce its imaginary component only  ($re(\lambda) + f\, im(\lambda)$ such that the new controller satisfies $\phi_\mathit{init}^K$).
 The process ends when no imaginary part can be further reduced.
@@
     ([xshift=-5em]verif1.north) edge node[align=center]  {C-ex} ([xshift=-5em]model2.south)
-    ([xshift=5em]model2.south) edge node[align=center]  {$\mat{K}'$,$\mat{L}'$} ([xshift=5em]verif1.north)
+    ([xshift=5em]model2.south) edge node[align=center]  {$\mat{K}_{\langle C \rangle}$,$\mat{L}_{\langle C \rangle}$} ([xshift=5em]verif1.north)
     (model2.west) edge node[align=center] {$\phi$} (model1.east);
@@
 stages, blue boxes (dark) are verification stages, and the red box is the synthesis stage. 
-\note{shouldn't K-L be $\mat{K}_{\langle C \rangle},\mat{L}_{\langle C \rangle}$?}}
+We use $\mat{K}, \mat{L}$ because the synthesiser does not always meet the FWL specification. 
+%\note{shouldn't K-L be $\mat{K}_{\langle C \rangle},\mat{L}_{\langle C \rangle}$?}
+}
 \label{fig:CEGIS-OR}
@@
 $M$.
-Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point
-domain with $M$ bits mantissa and $E$ bits exponent.  This domain
-corresponds to $$\mathbb{R}_{\langle M,[E] \rangle} = \bigcup_F
-\mathbb{R}_{\langle M,F \rangle} \text{ where } F \in [-2^{E-1}, ...\,,2^{E-1}]$$ This
-definition important because it means that the distance between any two
-numbers in the domain depends on the location of those numbers.  Since we
-have shown that a floating point domain is a union of a number of fixed
-point domains, we will continue our reasoning on fixed point only, which
-will apply to the floating point domain by extension.  Operations on these
-numbers will incur errors that can be bound
+%Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point
+%domain with $M$ bits mantissa and $E$ bits exponent.  This domain
+%corresponds to $$\mathbb{R}_{\langle M,[E] \rangle} = \bigcup_F
+%\mathbb{R}_{\langle M,F \rangle} \text{ where } F \in [-2^{E-1}, ...\,,2^{E-1}]$$ This
+%definition important because it means that the distance between any two
+%numbers in the domain depends on the location of those numbers.  Since we
+%have shown that a floating point domain is a union of a number of fixed
+%point domains, we will continue our reasoning on fixed point only, which
+%will apply to the floating point domain by extension.  
+Operations on these numbers will incur errors that can be bound
 by~\cite{DBLP:conf/arith/BrainTRW15}.  We examine the most relevant ones:
@@
 
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Observable canonical form} \label{sec:observable}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-In most real implementations, the internal state of a plant cannot be
-directly measured but rather inferred from its effect on the output by
-using an observer.  Essentially, a state observer is a system that
-provides an estimate of the internal state of a given real system,
-from measurements of the input and output of the real system.
-This means that contrary to a stateless reactive controller, an observer
-controller has memory of the states (i.e. it is stateful).
-
-Take for example a system where we are given the position of a robot
-arm in a single axis.  Our objective is to move the arm to pick an object 
-from a known location along that axis.  The input of the robotic arm is an
-acceleration.  The position of the arm will vary depending on the speed, which
-in turn varies with the acceleration.  However, if we do not know the speed, we
-will not be able to reach our target smoothly.  An observer for this design could
-simply calculate the speed by keeping a memory (state) of the previous position
-and calculate the difference with the current position in the given time interval.
-
-A closed-loop digital control system with observer is shown in Figure~\ref{fig:observersystem}.
-Note that the variables of a state observer are denoted by a "$~\hat{}~$" (e.g. {$\hat {\vec{x}}(k)$})
-to distinguish them from the variables of the actual physical system.
-Moreover, $\vec{y}_e=\hat{\vec{y}_k}-\vec{y}_k$ is the output estimation error defined
-as the difference between the real output $\vec{y}_k$ and estimated one $\hat{\vec{y}_k}$, whereas
-$\mat{L}$ is the error sensitivity matrix, which amplifies the output estimation error.
-The figure also contains references to $\nu_1$, $\nu_2$, $\nu_1'$, $\nu_2'$ and $\nu_t$, which
-denote noise and will be explained later in the dissertation.
-Lastly, $k_r$ is a reference gain required by the model.
-
-Presuming a sampled model of the plant as described in \eqref{eq:plant}, the dynamics of the observer are:
-\begin{equation}
-\label{eq:to_of}
-\hat{\vec{x}}_{k+1}=({\mat{A}_d}_{\langle C \rangle}-\mat{L}\mat{C}_{\langle C \rangle})\hat{\vec{x}}_k+{\mat{B}_d}_{\langle C \rangle}\vec{u}+\mat{L}\vec{y}
-\end{equation}
-where the subindex ${\langle C \rangle}$ represents the domain of the controller $\mathbb{R}_{\langle C \rangle}$ such that ${\mat{A}_{\langle C \rangle}=\mathcal{F}_{\langle C \rangle}(\mat{A}_d)}$, ${\mat{B}_{\langle C \rangle}=\mathcal{F}_{\langle C \rangle}(\mat{B}_d)}$ and ${\mat{C}_{\langle C \rangle}=\mathcal{F}_{\langle C \rangle}(\mat{C})}$.
-The differentiation between $\mat{*}_{\langle C \rangle}$ and $\mat{*}$ will be exploited later in this work. For the time being we will assume they are the same. 
-%is an observer of the system $\vec{x}_{k+1}=\mat{A}\vec{x}+\mat{B}\vec{u} : \vec{y}=\mat{C}\vec{x}$. 
-%$p_i$ are user selected values which will affect the error of the observer estimator. 
-Since the feedback of this system depends on $\mat{C}$ rather than $\mat{B}$, the Reachable
-Canonical form is no longer suitable. Hence we require an Observable Canonical Form.
-For SISO systems, this is:
-\begin{align*}
-\mat{A}_o=&\left[
-\begin{array}{cccccc}
--a_{p-1}&1&0&0&\cdots&0\\
--a_{p-2}&0&1&0&\cdots&0\\
--a_{p-3}&0&0&1&\cdots&0\\
-\vdots&\vdots&\ddots&\ddots&\ddots&\vdots\\
--a_0&0&0&0&\cdots&1
-\end{array}\right],
-\mat{B}_o=\left[
-\begin{array}{c}
-\Gamma_{p-1}\\ \Gamma_{p-2}\\ \vdots\\ \Gamma_0
-\end{array}\right]\\
-\mat{C}_o=&[\begin{array}{cccccc}\ \ \ \ 1&\ \ \ \ 0&0&0&\cdots&0\end{array}] \nonumber
-\end{align*}
-We notice here that $\mat{A}_o=\mat{T}_o\mat{A}\mat{T}_o^{-1}=\mat{A}_c^T, \mat{C}_o=\mat{C}\mat{T}_o^{-1}=\mat{B}_c^T$
-and $\mat{B}_o=\mat{T}_o\mat{B}=\mat{C}_c^T$, where $\mat{T}_o$ is a transformtion of the system into observable canonical form%, which also applies to the MIMO case.
-%Let 
+%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%\subsection{Observable canonical form} \label{sec:observable}
+%%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%In most real implementations, the internal state of a plant cannot be
+%directly measured but rather inferred from its effect on the output by
+%using an observer.  Essentially, a state observer is a system that
+%provides an estimate of the internal state of a given real system,
+%from measurements of the input and output of the real system.
+%This means that contrary to a stateless reactive controller, an observer
+%controller has memory of the states (i.e. it is stateful).
+%
+%Take for example a system where we are given the position of a robot
+%arm in a single axis.  Our objective is to move the arm to pick an object 
+%from a known location along that axis.  The input of the robotic arm is an
+%acceleration.  The position of the arm will vary depending on the speed, which
+%in turn varies with the acceleration.  However, if we do not know the speed, we
+%will not be able to reach our target smoothly.  An observer for this design could
+%simply calculate the speed by keeping a memory (state) of the previous position
+%and calculate the difference with the current position in the given time interval.
+%
+%A closed-loop digital control system with observer is shown in Figure~\ref{fig:observersystem}.
+%Note that the variables of a state observer are denoted by a "$~\hat{}~$" (e.g. {$\hat {\vec{x}}(k)$})
+%to distinguish them from the variables of the actual physical system.
+%Moreover, $\vec{y}_e=\hat{\vec{y}_k}-\vec{y}_k$ is the output estimation error defined
+%as the difference between the real output $\vec{y}_k$ and estimated one $\hat{\vec{y}_k}$, whereas
+%$\mat{L}$ is the error sensitivity matrix, which amplifies the output estimation error.
+%The figure also contains references to $\nu_1$, $\nu_2$, $\nu_1'$, $\nu_2'$ and $\nu_t$, which
+%denote noise and will be explained later in the dissertation.
+%Lastly, $k_r$ is a reference gain required by the model.
+%
+%Presuming a sampled model of the plant as described in \eqref{eq:plant}, the dynamics of the observer are:
+%\begin{equation}
+%\label{eq:to_of}
+%\hat{\vec{x}}_{k+1}=({\mat{A}_d}_{\langle C \rangle}-\mat{L}\mat{C}_{\langle C \rangle})\hat{\vec{x}}_k+{\mat{B}_d}_{\langle C \rangle}\vec{u}+\mat{L}\vec{y}
+%\end{equation}
+%where the subindex ${\langle C \rangle}$ represents the domain of the controller $\mathbb{R}_{\langle C \rangle}$ such that ${\mat{A}_{\langle C \rangle}=\mathcal{F}_{\langle C \rangle}(\mat{A}_d)}$, ${\mat{B}_{\langle C \rangle}=\mathcal{F}_{\langle C \rangle}(\mat{B}_d)}$ and ${\mat{C}_{\langle C \rangle}=\mathcal{F}_{\langle C \rangle}(\mat{C})}$.
+%The differentiation between $\mat{*}_{\langle C \rangle}$ and $\mat{*}$ will be exploited later in this work. For the time being we will assume they are the same. 
+%%is an observer of the system $\vec{x}_{k+1}=\mat{A}\vec{x}+\mat{B}\vec{u} : \vec{y}=\mat{C}\vec{x}$. 
+%%$p_i$ are user selected values which will affect the error of the observer estimator. 
+%Since the feedback of this system depends on $\mat{C}$ rather than $\mat{B}$, the Reachable
+%Canonical form is no longer suitable. Hence we require an Observable Canonical Form.
+%For SISO systems, this is:
+%\begin{align*}
+%\mat{A}_o=&\left[
+%\begin{array}{cccccc}
+%-a_{p-1}&1&0&0&\cdots&0\\
+%-a_{p-2}&0&1&0&\cdots&0\\
+%-a_{p-3}&0&0&1&\cdots&0\\
+%\vdots&\vdots&\ddots&\ddots&\ddots&\vdots\\
+%-a_0&0&0&0&\cdots&1
+%\end{array}\right],
+%\mat{B}_o=\left[
+%\begin{array}{c}
+%\Gamma_{p-1}\\ \Gamma_{p-2}\\ \vdots\\ \Gamma_0
+%\end{array}\right]\\
+%\mat{C}_o=&[\begin{array}{cccccc}\ \ \ \ 1&\ \ \ \ 0&0&0&\cdots&0\end{array}] \nonumber
+%\end{align*}
+%We notice here that $\mat{A}_o=\mat{T}_o\mat{A}\mat{T}_o^{-1}=\mat{A}_c^T, \mat{C}_o=\mat{C}\mat{T}_o^{-1}=\mat{B}_c^T$
+%and $\mat{B}_o=\mat{T}_o\mat{B}=\mat{C}_c^T$, where $\mat{T}_o$ is a transformtion of the system into observable canonical form%, which also applies to the MIMO case.
+%%Let 
+%%\begin{equation*}
+%%\label{eq:wnof}
+%%\mat{W}=\left[\begin{array}{c}\mat{C}\\ \mat{C}\mat{A}\\ \mat{C}\mat{A}^2\\ \vdots\\ \mat{C}\mat{A}^{p-1}\end{array}\right]
+%%\end{equation*}
+%%be the observability matrix of the system, and
+%%\begin{equation*}
+%%\label{eq:wof}
+%%\mat{W}_{o}=\mat{R}_{c}^{-1}
+%%\end{equation*}
+%%the observability matrix of the canonical form (see eg~\cite{Astrom08}). Then the matrix $\mat{T}_o=\mat{W}^{-1}\mat{W}_{o}$ will transform an observable system into its canonical form.
+%
+%For simplicity of the description, we aggregate the noises as follows:
+%$\eta_1=\nu_1+\nu_1'+\nu_t$ and $\eta_2=\nu_2+\nu_2'$,
+%where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations (see Section~\ref{sec:quantization-noise}).
+%Assuming that the observer dynamics are an exact copy of the real ones, ($\mat{*}_{\langle C \rangle}=\mat{*}$), the closed loop dynamics of this system are given by:
+%\begin{align}
+%\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_{k+1}
+%=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}&\mat{B}_d\mat{K}\\ \mat{0}&\mat{A}_d-\mat{L}\mat{C}\end{array}\right]
+%\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_k
+%+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}\end{array}\right]\left [\begin{array}{c}\vec{r}_k+\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
+%\label{eq:observer_LTI}
+%\end{align}
+%where $\vec{x}_e=\vec{x}-\hat{\vec{x}}$ is the estimation error of the state space by the observer.
+%Note that this matrix is not in canonical form. A transformation using both reachability and observability matrices is required. This is achieved as follows:
+%By translating the coordinate system to 
 %\begin{equation*}
-%\label{eq:wnof}
-%\mat{W}=\left[\begin{array}{c}\mat{C}\\ \mat{C}\mat{A}\\ \mat{C}\mat{A}^2\\ \vdots\\ \mat{C}\mat{A}^{p-1}\end{array}\right]
+%\left[\begin{array}{c}\vec{x}'\\ \vec{x}_e'\end{array}\right]=
+%\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right]
+%\left[\begin{array}{c}\vec{x}\\ \vec{x}_e\end{array}\right]
 %\end{equation*}
-%be the observability matrix of the system, and
-%\begin{equation*}
-%\label{eq:wof}
-%\mat{W}_{o}=\mat{R}_{c}^{-1}
-%\end{equation*}
-%the observability matrix of the canonical form (see eg~\cite{Astrom08}). Then the matrix $\mat{T}_o=\mat{W}^{-1}\mat{W}_{o}$ will transform an observable system into its canonical form.
-
-For simplicity of the description, we aggregate the noises as follows:
-$\eta_1=\nu_1+\nu_1'+\nu_t$ and $\eta_2=\nu_2+\nu_2'$,
-where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations (see Section~\ref{sec:quantization-noise}).
-Assuming that the observer dynamics are an exact copy of the real ones, ($\mat{*}_{\langle C \rangle}=\mat{*}$), the closed loop dynamics of this system are given by:
-\begin{align}
-\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_{k+1}
-=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}&\mat{B}_d\mat{K}\\ \mat{0}&\mat{A}_d-\mat{L}\mat{C}\end{array}\right]
-\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_k
-+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}\end{array}\right]\left [\begin{array}{c}\vec{r}_k+\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
-\label{eq:observer_LTI}
-\end{align}
-where $\vec{x}_e=\vec{x}-\hat{\vec{x}}$ is the estimation error of the state space by the observer.
-Note that this matrix is not in canonical form. A transformation using both reachability and observability matrices is required. This is achieved as follows:
-By translating the coordinate system to 
-\begin{equation*}
-\left[\begin{array}{c}\vec{x}'\\ \vec{x}_e'\end{array}\right]=
-\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right]
-\left[\begin{array}{c}\vec{x}\\ \vec{x}_e\end{array}\right]
-\end{equation*}
-%where $\mat{T}_c=\mat{R}_{c}\mat{R}^{-1}$ and $\mat{T}_o=\mat{W}^{-1}\mat{W}_{o}$, 
-we can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
-\begin{align}
-\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
-=& \left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]
-\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
-+\left[\begin{array}{cc}\mat{T}_c\mat{B}_d&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}\end{array}\right]\left [\begin{array}{c}\mat{k}_r\vec{r}_k+\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
-\vec{y}_k
-=& \mat{C}_{t}\vec{x}_k% + \mat{D}_{d}\vec{u}_k
-\label{eq:observer_LTI_cf}
-\end{align}
-where
-{
-\begin{align*}
-\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
-\mat{A}_{o}=&\mat{T}_o\left(\mat{A}_d-\mat{L}\mat{C}\right)\mat{T}_o^{-1}\\
-\mat{B}_{o}=&\mat{T}_c\mat{B}_d\mat{K}\mat{T}_o^{-1}&
-\mat{C}_t=&\mat{C}\mat{T}_c
-\end{align*}
-Replacing the matrices in \eqref{eq:observer_LTI_cf} with appropriate symbols:
-\begin{align}
-\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]&
-\mat{B}'=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}\end{array}\right]
-\label{eq:of_dynamics}
-\end{align}
-}
-we get
-\begin{displaymath}
-\tilde{\vec{x}}_{k+1}=\mat{A}' \tilde{\vec{x}}_{k}+\mat{B}' \tilde{\vec{u}}_k \text{ where }
-\tilde{\vec{x}}_k=\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k \text{ and }
-\tilde{\vec{u}}_k=\left [\begin{array}{c}\vec{r}_k+\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
-\label{eq:simple_observer_LTI}
-\end{displaymath}
-This has a similar structure to \eqref{equ:reachtraj} which will be helpful in our analysis.
+%%where $\mat{T}_c=\mat{R}_{c}\mat{R}^{-1}$ and $\mat{T}_o=\mat{W}^{-1}\mat{W}_{o}$, 
+%we can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
+%\begin{align}
+%\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
+%=& \left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]
+%\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
+%+\left[\begin{array}{cc}\mat{T}_c\mat{B}_d&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}\end{array}\right]\left [\begin{array}{c}\mat{k}_r\vec{r}_k+\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
+%\vec{y}_k
+%=& \mat{C}_{t}\vec{x}_k% + \mat{D}_{d}\vec{u}_k
+%\label{eq:observer_LTI_cf}
+%\end{align}
+%where
+%{
+%\begin{align*}
+%\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
+%\mat{A}_{o}=&\mat{T}_o\left(\mat{A}_d-\mat{L}\mat{C}\right)\mat{T}_o^{-1}\\
+%\mat{B}_{o}=&\mat{T}_c\mat{B}_d\mat{K}\mat{T}_o^{-1}&
+%\mat{C}_t=&\mat{C}\mat{T}_c
+%\end{align*}
+%Replacing the matrices in \eqref{eq:observer_LTI_cf} with appropriate symbols:
+%\begin{align}
+%\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]&
+%\mat{B}'=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}\end{array}\right]
+%\label{eq:of_dynamics}
+%\end{align}
+%}
+%we get
+%\begin{displaymath}
+%\tilde{\vec{x}}_{k+1}=\mat{A}' \tilde{\vec{x}}_{k}+\mat{B}' \tilde{\vec{u}}_k \text{ where }
+%\tilde{\vec{x}}_k=\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k \text{ and }
+%\tilde{\vec{u}}_k=\left [\begin{array}{c}\vec{r}_k+\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
+%\label{eq:simple_observer_LTI}
+%\end{displaymath}
+%This has a similar structure to \eqref{equ:reachtraj} which will be helpful in our analysis.
 
@@
 %-------------------------------
-\subsection{Transient response} 
+\subsubsection{Transient response} 
 \label{sec:transientspecificationproof}

### 2018-01-31 TACAS2018/paper.tex
nudge

@@
 
-\note{
-Note that, while we have several reference to the appendix throughout
-the paper, the paper can be read on its own and these references are
-only meant as an aid for the reader less familiar with control theory or
-for the proofs of theorems.
-}
+%\note{
+%Note that, while we have several reference to the appendix throughout
+%the paper, the paper can be read on its own and these references are
+%only meant as an aid for the reader less familiar with control theory or
+%for the proofs of theorems.
+%}
 
@@
 Since we are interested in synthesising controllers with observers, 
-in this section we will look at checking stability, safety and the response time in the presence of an observer.\footnote{A full description of
-the theory related to observer design is in Appendix \ref{sec:control_theory}.}
+in this section we will look at checking stability, safety and the response time in the presence of an observer.
+%\footnote{A full description of the theory related to observer design is in Appendix \ref{sec:control_theory}.}
 

### 2018-01-31 TACAS2018/paper.tex
nudge

@@
 smaller rotation, which facilitates meeting the safety specification $\phi_\mathit{safety}$.
-%(we note that real convergent eigenvalues are trivially safe).
-
-%% We denote these sets of rules as $\phi_{objective}$ (which varies depending on which optimization stage we're in).
-%% At each optimizing iteration, the modeller updates $\phi_{static} = \phi_{static} \wedge \phi_{objective}$% \wedge \phi_\mathit{safety}^{n'} $ where $n' \geq n$.
-
+
+We must point out that the optimizer tool uses infinite precision for the plant, and
+may therefore find solutions that the synthesiser can't due to the use of limited precision.
 If we cannot optimize the candidate  we signal the {\sc Abstract} phase to 
@@
    \path
-    (synth.east) edge node[xshift=-0.5em,align=center] {$\mat{K}$,$\mat{L}$} (verif1.west)
+    (synth.east) edge node[xshift=-0.5em,align=center] {{$\mat{K}_{\langle P \rangle}$}\\{$\mat{L}_{\langle P \rangle}$}} (verif1.west)
     (verif1.east) edge node {PASS} (verif2.west)
@@
     ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
-    ([xshift=-5em]gp.north) edge node[align=center] {FAIL/\\$\mat{K}$,$\mat{L}$} ([xshift=-5em]synth.south)
+    ([xshift=-5em]gp.north) edge node[align=center] {FAIL/\\$\mat{K}_{\langle P \rangle}$,$\mat{L}_{\langle P \rangle}$} ([xshift=-5em]synth.south)
    ([xshift=5em]model1.south) edge node[align=center,xshift=-.7cm] {$\mathbb{R}_{\langle P \rangle}$} 
@@
 stages, blue boxes (dark) are verification stages, and the red box is the synthesis stage. 
-We use $\mat{K}, \mat{L}$ because the synthesiser does not always meet the FWL specification. 
 %\note{shouldn't K-L be $\mat{K}_{\langle C \rangle},\mat{L}_{\langle C \rangle}$?}
@@
 2  & Helicopter        & 3  & 100 & 57.2\,s & t.o. & 54 & 15 & 7.1\,s  &   18.0\,s & 9 & 90\\
-3  & Inverted Pendulum & 4 & 100 &  277\,s& t.o. & 32& 0 & 20.0\,s  &  t.o. & 37 & 19\\
+3  & Inverted Pendulum & 4 & 100 &  277\,s& t.o. & 36& 0 & 20.0\,s  &  t.o. & 37 & 19\\
 4  & Magnetic Pointer  & 2  & 100 & 5.7\,s & 229.9\,s & 38 & 42 & 3.0\,s  &  9.5\,s & 5 & 95 \\
@@
 relatively short timeout, so it is possible that longer timeouts would instead lead to a
-valid solution. However, the solution is sound but incomplete, 
-since we use approximations and over-approximations that may exclude
-valid candidates in early stages, so it is impossible to tell if a solution exists in these cases.
+valid solution. However, there are cases where a solution may not be found due the
+approximations in the synthesiser that would prevent a true candidate from being found
+or over-approximations in the verifier that may reject a valid candidate.
+It is impossible at this stage for us to differentiate these from case where a controller does not exist.
 
@@
 
-There are cases where newly found controllers are not due to time improvements,
-but to the fact that the optimiser can reason about infinite precision
-numbers and may therefore find solutions that are not available using 64 bit 
-plant precision (the maximum allowed by our SAT solving tool).
+There are cases where newly found controllers are due to the fact that the
+optimiser can reason about infinite precision numbers and may therefore find
+solutions that are not available using 64 bit plant precision (the maximum
+allowed by the synthesiser in our implementation of standard CEGIS).
 

### 2018-01-31 TACAS2018/paper.tex
nudge

@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
 In many models of real-world control systems, 
@@
 that provides an estimate of the internal state $x$ of the given model, 
-from measurements of its inputs and outputs (see Appendix~\ref{sec:observable}).
+from measurements of its inputs and outputs.
 
@@
 \end{figure*}
-
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
  Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a linear function of $\vec{x}_0$ as shown below.
@@
  where $\forall t \leq T,\ \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}
- \footnote{when $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$}.
+ \footnote{when $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]T}$}.
  \end{theorem}
@@
  and where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$
-  \footnote{as before, when $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$},
+  \footnote{as before, when $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]T}$},
  and $\mat{A}_d, \mat{B}_d$ describe the discretized plant dynamics with sample time $T_s$, 
@@
 times obtained with CEGIS-OR). 
-Since further synthesis require increasingly
-complex models which are linear in the number of multiplications,
-eliminating  these results in large improvements.  In cases when the initial candidate is
-suitable, we gain nothing with the refinement and therefore find similar times.
+%Since further synthesis require increasingly
+%complex models which are linear in the number of multiplications,
+%eliminating  these results in large improvements.  In cases when the initial candidate is
+%suitable, we gain nothing with the refinement and therefore find similar times.
 

### 2018-01-31 TACAS2018/paper.tex
ch 6

--- 2018-01-31 TACAS2018/paper.tex
@@
 the approach to the recent setup of Network Control Systems.
+
+\smallskip
 
@@
 
-We are interested in control systems with an output $\vec{y}$ that is a linear combination of its states and inputs
-\footnote{Since we can only measure $\vec{y}$, the state-space $\vec{x}$ is not fully observable}.
+We are interested in control systems with an output $\vec{y}$ that is a linear combination of its states and inputs\footnote{Notice that since we can only measure $\vec{y}$, the state-space $\vec{x}$ is not fully observable.}.
 %, which may restrict the observability of the state-space from the output space.
@@
 \label{eq:ode2}  
-\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t), \vec{y} \in \mathbb{R}^o, \mat{C} \in \mathbb{R}^{o \times p}, \mat{D} \in \mathbb{R}^{o \times q}
+\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t), \vec{y} \in \mathbb{R}^o, \mat{C} \in \mathbb{R}^{o \times p}, \mat{D} \in \mathbb{R}^{o \times q}. 
 \end{equation}
@@
 %
+\note{Ad is ill defined?}
 %where $\mat{A}_d=e^\mat{A}$, $\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$,
@@
 the internal state $x$ cannot be directly measured,  
-but is rather inferred from its effect on the output $\vec{y}$ using an observer~\cite{Astrom08}.  
-Essentially, a state observer is a new dynamical model (with variable denoted below as $\hat{\vec{x}}$) 
+but is rather inferred from its effect on the measured output $\vec{y}$ using an observer~\cite{Astrom08}.  
+Essentially, a state observer is a new dynamical model (with variable denoted as $\hat{\vec{x}}$) 
 that provides an estimate of the internal state $x$ of the given model, 
-from measurements of its inputs and outputs (see Appendix~\ref{sec:observable}).
-
-A closed-loop digital control system with observer is shown in Figure~\ref{fig:observersystem}. 
+from measurements of its inputs and outputs \note{(see Appendix~\ref{sec:observable})}.
+
+A closed-loop digital control interconnection with observer is shown in Figure~\ref{fig:observersystem}. 
 The linear feedback controller (bottom left) is characterized by a gain matrix $\mat{K}_{\langle C \rangle}$ that influences the closed-loop dynamics, 
 and is driven by the observer state $\hat{\vec{x}}$.  
-Moreover, $\vec{y}_e=\hat{\vec{y}} - \vec{y}$ is the output estimation error,  
+Moreover, $\vec{y}_e=\hat{\vec{y}} - \vec{y}$ is the error on the output estimator,  
 %  defined as the difference between the real output $\vec{y}_k$ and estimated one $\hat{\vec{y}_k}$, 
@@
 Note that the controller and the observer are implemented in a discrete domain 
-(quantities within this domain are identified by the index $\langle C \rangle$), whereas the plant is continuous.
-We futher model the effects of using a discrete controller as the noise signals $\nu_1$(ADC quantization), $\nu_2$ (DAC quantization), $\nu_1'$ (rounding of the observer state error),
+(quantities within this domain are identified by the index $\langle C \rangle$), 
+whereas the plant evolves in a continuous domain. 
+We further model the effects of using a discrete controller as the noise signals $\nu_1$(ADC quantization), $\nu_2$ (DAC quantization), $\nu_1'$ (rounding of the observer state error),
 $\nu_2'$ (rounding of the observer state), and $\nu_t$ (output delay of the digital system) 
   Lastly, $k_r$ is a reference gain required by the model.
+
   Our goal in this work is to synthesise both $\mat{K}_{\langle C \rangle}$ and $\mat{L}_{\langle C \rangle}$, 
@@
 }
-\caption{Closed-loop digital control system with an observer, where the controller and the observer (bottom part) are implemented in a discrete domain,
+\caption{Closed-loop digital control interconnection with an observer, where the controller and the observer (bottom part) are implemented in a discrete domain,
   %(quantities within this domain are identified by the index $\langle C \rangle$),
-  whereas the plant is continuous. \label{fig:observersystem}}
+  whereas the plant (top part) is continuous. \label{fig:observersystem}}
 \end{figure*}
@@
  which are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where $\forall t\geq 0, \vec{u}(t)=\vec{u}$. 
- For such models, a state $\vec{x}_T$ is computed next.  
+ For such models, a state $\vec{x}_T$ is computed next.  \note{The next result is again known from literature, it's not a new theorem.}
 \begin{theorem}
@@
  \end{align}
- where $\forall t \leq T,\ \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}
- \footnote{when $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$}.
+ where $\forall t \leq T,\ \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}\footnote{When $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$}.
  \end{theorem}
@@
  with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, 
- and where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$
-  \footnote{as before, when $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$},
+ and where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$, 
+%  \footnote{as before, when $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$},
  and $\mat{A}_d, \mat{B}_d$ describe the discretized plant dynamics with sample time $T_s$, 
@@
 corruptions over communication lines in the control loop, 
-approximations due to digitalisation.
+and approximations due to digitalisation.
 
@@
 
-Stability denotes the property of a model to unfold staying within a bounded set around an equilibrium point. 
+Stability qualitatively denotes the property of a model to evolve within a bounded set around an equilibrium point. 
 In this paper, we are interested in asymptotic stability, where the model is further expected to converge to the steady state value (i.e., the equilibrium point).   
 %
-We specify model stability via Jury's criterion~\cite{fadali}, %\footnote{More details on Jury's criterion is in Appendix~\ref{sec:closed_stability}.}, 
- which boils down to a requirement expressed as an algebraic formula - a SAT solver will manipulate the coefficients of the model's characteristic polynomial. 
-%
-To facilitate the use of Jury's criterion, we transform the model into
+We specify model stability via Jury's criterion~\cite{fadali}, 
+as classical in Control Theory,  %\footnote{More details on Jury's criterion is in Appendix~\ref{sec:closed_stability}.}, 
+ which boils down to a requirement expressed as an algebraic formula 
+ on the characteristic polynomial of the model - a SAT solver will manipulate its coefficients. 
+%
+In order to facilitate the use of Jury's criterion, we transform the model into
 a representation that contains the coefficients of its characteristic
-polynomial expressed as sums of controller and plant values: this
-representation has no multiplications, which are expensive for a SAT
-solver.
-%
-Such a representation is known as 
+polynomial expressed as sums of controller and plant values. 
+The benefit of this representation is that it has no multiplications, which are expensive to handle by SAT solvers. 
+%
+Such a representation is a model known as 
 % is called Controllable and Observable 
@@
 and is dynamically equivalent to the given model.  
-In this section we explore the implications of using this canonical form, 
-alongside the use of a FWL representation.
+In this section we explore the implications of using the canonical form, 
+alongside the use of FWL representations.
 
@@
 
-We assume that the domain of the observer model is further discretised, 
+We assume that the domain of the observer model is discretised, 
 i.e., the domain for both the controller and the observer is $\mathbb{R}_{\langle C \rangle}$.
-This means that we have 
+This means that we have matrices 
 ${\mat{A}_d}_{\langle C
@@
 \mat{K}_{\langle C \rangle}, \mat{L}_{\langle C \rangle} \in
-\mathbb{R}_{\langle C \rangle}^*$, where $*$ represents the appropriate
-dimension for each matrix.
-New problems arise due to the FWL effects on these matrices.
+\mathbb{R}_{\langle C \rangle}^*$, 
+where $*$ represents the appropriate dimension for each matrix.
+New problems arise due to FWL effects on these matrices. 
 These are reflected in the canonical form of the resulting model,
@@
 \left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
-+\mat{B}'\left [\begin{array}{c} \vec{r}_k + \nu_2+\nu_2'\\ \nu_1+\nu_1'+\nu_t\end{array}\right]%\nonumber\\
++\mat{B}'\left [\begin{array}{c} \vec{r}_k + \nu_2+\nu_2'\\ \nu_1+\nu_1'+\nu_t\end{array}\right], %\nonumber\\
 %\vec{y}_k= &\mat{C}\mat{T}_c\vec{x}_k', 
@@
 l_0-a_0&\begin{array}{ccc}0&\cdots&0\end{array}
-\end{array}\right]
+\end{array}\right], 
 \end{align*}
 }
-
-where $\vec{x}'$ and $\vec{x}_e'$ are the state of the system and the error of the observer evaluated in the transformed domain, 
-$\mat{A}_{c}$ the closed loop dynamics of the controller in canonical form, $\mat{A}_{o}$ the closed loop dynamics of the observer in canonical form, $\mat{B}_{o}$ the feedback gain, 
- $\mat{B}'$ the noise sensitivity, and $\mat{A}_{e}$ and $\mat{B}_{e}$ the error caused by the FWL representation.
+where $\vec{x}'$ is the state of the model in canonical form and $\vec{x}_e'$ is the error of the observer evaluated in the transformed domain; 
+further, $\mat{A}_{c}$ the closed-loop matrix of the controller in canonical form, 
+$\mat{A}_{o}$ the closed-loop matrix of the observer in canonical form, 
+$\mat{B}_{o}$ the a feedback gain matrix, 
+ $\mat{B}'$ the noise sensitivity matrix, 
+\note{[next is unclear - how are matrices related to FWL errors?
+are they related to the quantities discussed in the previous section 5.2?] and $\mat{A}_{e}$ and $\mat{B}_{e}$ are the error caused by the FWL representation}.
 %and we have introduced the following terms: 
@@
 %}
-Here $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations (details are in Appendix~\ref{sec:quantization-noise}).
+Moreover, $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations (details are in Appendix~\ref{sec:quantization-noise}).
 

### 2018-01-31 TACAS2018/paper.tex
more on Alessandro's comments

@@
 \begin{array}{l}
-\mat{A}_d=e^\mat{A}\\
+\mat{A}_d=e^{\mat{A}T_s}\\
 \mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}
@@
 %
-\note{Ad is ill defined?}
 %where $\mat{A}_d=e^\mat{A}$, $\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$,
@@
 that provides an estimate of the internal state $x$ of the given model, 
-from measurements of its inputs and outputs \note{(see Appendix~\ref{sec:observable})}.
+from measurements of its inputs and outputs.
 
@@
 Lastly, $k_r$ is a reference gain required by the model.  
-
 Our goal in this work is to synthesise both $\mat{K}_{\langle C \rangle}$ and $\mat{L}_{\langle C \rangle}$, 
@@
 
+\note{Much like we did in the earlier work, we should emphasise we look at the closed-loop interconnection from the perspective of the digital controller? }
+
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
  \end{lemma}
-\begin{proof}
-See Appendix~\ref{sec:proofs}
-\end{proof}
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
  which are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where $\forall t\geq 0, \vec{u}(t)=\vec{u}$. 
- For such models, a state $\vec{x}_T$ is computed next.  \note{The next result is again known from literature, it's not a new theorem.}
-\begin{theorem}
+ For such models, a state $\vec{x}_T$ is computed next.
+\begin{lemma}
 The state of the model $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$ is 
@@
  \vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u} \text{ where } \mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B} 
+ \label{eq:continuous_tube_param}
  \end{align}
- where $\forall t \leq T,\ \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}\footnote{When $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$}.
- \end{theorem}
- \begin{corollary}
+ where $\forall t \leq T,\ \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}
+ \footnote{When $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$}.
  If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, 
  then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u}) \text{ with } T \in \mathbb{R}_0^+$ (where $\mat{A}_d^{\frac{T}{T_d}} = e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the system at time $T$.
- \end{corollary}
-\begin{proof}
-See Appendix~\ref{sec:proofs}
-\end{proof}
+ \end{lemma}
 
@@
  \end{align}
- with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, 
- and where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$, 
-%  \footnote{as before, when $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$},
- and $\mat{A}_d, \mat{B}_d$ describe the discretized plant dynamics with sample time $T_s$, 
+ with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, $\mat{B}_T$ as in \eqref{eq:continuous_tube_param}, 
+ and $\mat{A}_d=\mat{A}_{T_s}, \mat{B}_d=\mat{B}_{T_s}$ describe the discretized plant dynamics with sample time $T_s$, 
  is the state of the model 
- \begin{align}
+ \begin{align*}
  \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
@@
  kT_s \leq t < (k+1)T_s. 
- \end{align}
+ \end{align*}
  \end{theorem}
@@
  on the characteristic polynomial of the model - a SAT solver will manipulate its coefficients. 
+ \note{unclear really how SAT relates to manipulating real coefficients.... }
 %
@@
 where $*$ represents the appropriate dimension for each matrix.
-New problems arise due to FWL effects on these matrices. 
-These are reflected in the canonical form of the resulting model,
+New problems arise due to the FWL truncation of these matrices. 
+These are reflected in the canonical form of the resulting model (see $\mat{A}_e$ and $\mat{B}_e$),
 which is expressed by:
@@
  $\mat{B}'$ the noise sensitivity matrix, 
-\note{[next is unclear - how are matrices related to FWL errors?
-are they related to the quantities discussed in the previous section 5.2?] and $\mat{A}_{e}$ and $\mat{B}_{e}$ are the error caused by the FWL representation}.
+and $\mat{A}_{e}$ and $\mat{B}_{e}$ are the error caused by the FWL truncation, seen after the transformation to canonical form.
 %and we have introduced the following terms: 
@@
 %}
-Moreover, $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations (details are in Appendix~\ref{sec:quantization-noise}).
-
-In a continuous time domain, the characteristic polynomial
+Moreover, $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations \note{[How is this related to the previously mentioned FWL errors?]} Full details are in Appendix~\ref{sec:quantization-noise}.
+
+In a real domain $\mathbb{R}$, the characteristic polynomial
 of the closed loop dynamics is defined by the characteristic polynomials of~$\mat{A}_c$
@@
 \end{align*}
+\note{we should perhaps provide a qualitative hint on what are the conditions of JC? I'm afraid leaving it to the polynomials here isn't quite complete or clear.}
 The introduction of the FWL errors causes this to no longer
-be true.  We must therefore find a suitable solution to maintain this separation of polynomials.
+be true.  We must therefore find a suitable solution to maintain this independence of polynomials.
 
@@
 |{\lambda_o}_{i}-\hat{\lambda}_{oi}|<\delta_o$, where ${\lambda_o}_{i}$ are the
-true eigenvalues of the observer and $\hat{\lambda}_{oi}$ the eigenvalues of
-the perturbed observer.  We note that in the case of stability we only care
-about the error with respect to the unit circle, which is equivalent to
+true eigenvalues of the observer $\mat{A}_o$ and $\hat{\lambda}_{oi}$
+the corresponding eigenvalues of the closed loop. We note that in the case of
+stability we only care that their norms are smaller than one, which is equivalent to
 upper bounding the estimation of the largest eigenvalue.  Hence, given a
-desired upper value $\overline{\lambda}$, we apply Jury's criterion on the
-polynomial.
+desired upper value $\overline{\lambda}$ (see Section \ref{sec:transientspecification}), we apply Jury's criterion on the
+polynomial
 %
@@
 %
-In the case of the reachable eigenvalues, the procedure is the same except
-that we obtain our bound $\delta_c=\max(\norm{{\mat{A}_e}_{*,i}+{\mat{B}_e}_{*,i}}_1)$
+In the case of $\mat{A}_c$, the procedure is the same except
+that we obtain our bound $\delta_c=\max(\norm{{\mat{A}_e}_{*,i}+{\mat{B}_e}_{*,i}}_1)$ \note{why? explain in close connection with formulae used.}
 (\emph{i.e.} the largest column norm in $ \left[\begin{array}{c}\mat{A}_e\\ \mat{B}_e\end{array}\right]$) and
@@
 Note that FWL effects are not explicitly captured here
-as they are implicit from Equation \ref{eq:observer_LTI_FWL_cf}.
+as they are implicit from Equation \eqref{eq:observer_LTI_FWL_cf}.
 
@@
 We now use this limit to express a constraint in terms of the
-coefficients of the characteristic polynomial.  Let this
-polynomial be:
+coefficients of the characteristic polynomial.  
+\note{relate to polynomials sued above.}
+Let this polynomial be:
 %
 \begin{equation}
-P(s)=\prod_{i=0}^p (s-\lambda_i)=\sum_{j=0}^p c_js^j.
+P(z)=\prod_{i=0}^p (z-\lambda_i)=\sum_{j=0}^p c_jz^j.
 \end{equation}
@@
 to ensure $\lambda_i' \leq 1$ which can be done by applying Jury's criterion
-to $P'(s)=\prod_{i=0}^p (s-\lambda_i')=\sum_{j=0}^p c_j's^j$ where $c_j'$ are
+to $P'(z)=\prod_{i=0}^p (z-\lambda_i')=\sum_{j=0}^p c_j'z^j$ where $c_j'$ are
 unknown.  By replacing $\lambda_i$, we obtain
@@
 \begin{equation}
-P'=\prod_{i=0}^p (s-\lambda_i')=\prod_{i=0}^p \left(s-\frac{\lambda_i}{\overline{\lambda}}\right)=\sum_{j=0}^p \frac{c_j}{\overline{\lambda}^{p-j}}s^j
+P'=\prod_{i=0}^p (z-\lambda_i')=\prod_{i=0}^p \left(z-\frac{\lambda_i}{\overline{\lambda}}\right)=\sum_{j=0}^p \frac{c_j}{\overline{\lambda}^{p-j}}z^j, 
 \end{equation}
 %
-where all members are known. Thus, we can ensure that the settling time is smaller than
+where all values are known. Thus, we can ensure that the settling time is smaller than
 a certain magnitude by ensuring that 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+\note{At times the gain matrices K, L, do not appear with C/P indices  -  clarify why. }
 
@@
 We must point out that the optimizer tool uses infinite precision for the plant, and
-may therefore find solutions that the synthesiser can't due to the use of limited precision.
+may therefore find solutions that the synthesiser cannot, due to the use of limited precision.
 If we cannot optimize the candidate  we signal the {\sc Abstract} phase to 
@@
 2  & Helicopter        & 3  & 100 & 57.2\,s & t.o. & 54 & 15 & 7.1\,s  &   18.0\,s & 9 & 90\\
-3  & Inverted Pendulum & 4 & 100 &  277\,s& t.o. & 36& 0 & 20.0\,s  &  t.o. & 37 & 19\\
+3  & Inverted Pendulum & 4 & 100 &  277\,s& t.o. & 42& 0 & 20.0\,s  &  t.o. & 37 & 19\\
 4  & Magnetic Pointer  & 2  & 100 & 5.7\,s & 229.9\,s & 38 & 42 & 3.0\,s  &  9.5\,s & 5 & 95 \\
@@
 Experimental results. Minimum, and Median times for standard CEGIS vs CEGIS-OR on multiple benchmarks. No. indicates Number of benchmarks,
- t.o.~indicates timeouts (in the median case, it indicates more than half of the benchmarks timed out). Order is the number of states of the system.}
+ t.o.~indicates timeouts (in the median case, it indicates more than half of the benchmarks timed out). The order denotes the number of variables of a model.}
 \end{table}
 
-Using the described technique we managed to synthesize controllers for $509$ benchmarks (compared to $290$ found by our baseline), with a median synthesis time of $16.8$ seconds.
+Using the described technique we managed to synthesize controllers for $509$ benchmarks (compared to $290$ found by our baseline), with a median time of $16.8$ seconds.
 %and the maximum observed synthesis time was under 10 minutes for a $4^{th}$ order system ($8^{th}$ order considering the observer).
 We consider these times short enough to be of practical use to control engineers.
-In those cases for which the system fails to find a controller, we use a
-relatively short timeout, so it is possible that longer timeouts would instead lead to a
+Regarding the cases for which we fail to find a controller, we note that we use a
+relatively short timeout (5 minutes), so it is possible that longer timeouts would instead lead to a
 valid solution. However, there are cases where a solution may not be found due the
@@
 or over-approximations in the verifier that may reject a valid candidate.
-It is impossible at this stage for us to differentiate these from case where a controller does not exist.
+It is impossible for us to differentiate these from case where a controller does not exist.
 
@@
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\begin{theorem}
+\begin{lemma}
 The expression
@@
  with $\mat{A}_T$ as per \eqref{eq:continuous_tube_dyn} is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$.
- \end{theorem}
- \begin{corollary}
  If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}\vec{u}) \text{ with } k \in \mathbb{R}^+$ is the state of the system at time $kT_d$.
- \end{corollary}
+ \end{lemma}
  \begin{proof}

### 2018-01-31 TACAS2018/paper.tex
small change to sec 8

@@
 optimiser can reason about infinite precision numbers and may therefore find
-solutions that are not available using 64 bit plant precision (the maximum
-allowed by the synthesiser in our implementation of standard CEGIS).
+solutions that are not available using 64 bit plant precision, which
+is the maximum allowed by the {\sc synthesize} phase in our implementation
+(in standard CEGIS {\sc synthesize} is the only phase that can generate a
+candidate controller).
 

### 2018-01-31 TACAS2018/paper.tex
More on Alessandro's comments

@@
  which boils down to a requirement expressed as an algebraic formula 
- on the characteristic polynomial of the model - a SAT solver will manipulate its coefficients. 
- \note{unclear really how SAT relates to manipulating real coefficients.... }
+ on the characteristic polynomial of the model.% - a SAT solver will manipulate its coefficients. 
 %
@@
 polynomial expressed as sums of controller and plant values. 
-The benefit of this representation is that it has no multiplications, which are expensive to handle by SAT solvers. 
+The benefit of this representation is that it has no multiplications, which are expensive to handle by SAT solvers (used by the synthesiser). 
 %
@@
 \end{align*}
-\note{we should perhaps provide a qualitative hint on what are the conditions of JC? I'm afraid leaving it to the polynomials here isn't quite complete or clear.}
+Jury's criteria uses these coefficients to ensure that no root of the polynomial has a magnitude greater than one.
+%\note{we should perhaps provide a qualitative hint on what are the conditions of JC? I'm afraid leaving it to the polynomials here isn't quite complete or clear.}
 The introduction of the FWL errors causes this to no longer
-be true.  We must therefore find a suitable solution to maintain this independence of polynomials.
+be true.
+We must therefore find a suitable solution to maintain this independence of polynomials and use the given coefficients by bounding their error w.r.t.
+the true coefficients of the closed loop matrix.
 
@@
 \begin{equation}
-P_L'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_o)\overline{\lambda} \text{ and } c_j=l_j-a_j.
+P_L'(z)=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}z^j, \text{ where }  \overline{\lambda'}=(1+\delta_o)\overline{\lambda} \text{ and } c_j=l_j-a_j.
 \end{equation}
 %
-In the case of $\mat{A}_c$, the procedure is the same except
-that we obtain our bound $\delta_c=\max(\norm{{\mat{A}_e}_{*,i}+{\mat{B}_e}_{*,i}}_1)$ \note{why? explain in close connection with formulae used.}
+In the case of $\mat{A}_c$, the procedure is the same except that we need to look at the colums shared with $\mat{A}_c$.
+Thus we obtain our bound $\delta_c=\max(\norm{{\mat{A}_e}_{*,i}+{\mat{B}_e}_{*,i}}_1)$
 (\emph{i.e.} the largest column norm in $ \left[\begin{array}{c}\mat{A}_e\\ \mat{B}_e\end{array}\right]$) and
@@
 \begin{equation}
-P_K'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j, \text{ where }  \overline{\lambda'}=(1+\delta_c)\overline{\lambda} \text{ and } c_j=k_j-a_j.
+P_K'(z)=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}z^j, \text{ where }  \overline{\lambda'}=(1+\delta_c)\overline{\lambda} \text{ and } c_j=k_j-a_j.
 \end{equation}
@@
 We now use this limit to express a constraint in terms of the
-coefficients of the characteristic polynomial.  
-\note{relate to polynomials sued above.}
+coefficients of the characteristic polynomial $P_K'(z)P_L'(z)$.
 Let this polynomial be:
@@
 \begin{equation}
-P'=\prod_{i=0}^p (z-\lambda_i')=\prod_{i=0}^p \left(z-\frac{\lambda_i}{\overline{\lambda}}\right)=\sum_{j=0}^p \frac{c_j}{\overline{\lambda}^{p-j}}z^j, 
+P'(z)=\prod_{i=0}^p (z-\lambda_i')=\prod_{i=0}^p \left(z-\frac{\lambda_i}{\overline{\lambda}}\right)=\sum_{j=0}^p \frac{c_j}{\overline{\lambda}^{p-j}}z^j, 
 \end{equation}
@@
  \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.8cm, column sep=1.5cm] {
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.8cm, column sep=.8cm] {
   \coordinate (aux1);\&\&
@@
   \coordinate (aux3) at ([xshift=3cm]aux2); \\
-  \node[minimum width=2.2cm, minimum height=0.8cm, fill=orange!20] (model1) {{\sc 1. Abstract}};
+  \node[minimum width=2cm, minimum height=0.8cm, fill=orange!20] (model1) {{\sc 1. Abstract}};
   \& complexnode/.pic={
     \coordinate (model);
-    \node[minimum width=2.2cm, minimum height=0.8cm, fill=orange!20] (model2) at ([xshift=-3cm]model.center) {{\sc 4. Refine Abstraction}\\{\sc and Optimize}};
+    \node[minimum width=2cm, minimum height=0.8cm, fill=orange!20] (model2) at ([xshift=-3cm]model.center) {{\sc 4. Refine Abstraction}\\{\sc and Optimize}};
      \coordinate (model3) at ([xshift=0cm]model.center);
@@
    } ;\\
-   \node[minimum width=2.2cm, minimum height=0.8cm, fill=purple!20] (synth) {{\sc 2. Synthesize}};
+   \node[minimum width=2cm, minimum height=0.8cm, fill=purple!20] (synth) {{\sc 2. Synthesize}};
    \&
@@
      \node[rectangle,draw,dotted,
-	minimum width=9cm,
+	minimum width=8cm,
 	minimum height=1cm,
         pattern=north west lines, pattern color=gray!20,
-	label={\sc Verify~~~~~~~~~~~},] (verif) {};
-     \node[minimum width=2.2cm, minimum height=0.8cm, fill=blue!20] (verif1) at ([xshift=-3cm]verif.center) {{\sc 3. Verify}\\{\sc Synthesis}};
-     \node[minimum width=2.2cm, minimum height=0.8cm, fill=blue!20] (verif2) at ([xshift=0cm]verif.center) {{\sc 5. Discrete}\\{\sc Time}};
-     \node[minimum width=2.2cm, minimum height=0.8cm, fill=blue!20] (verif3) at ([xshift=3cm]verif.center) {{\sc 7. Continuous}\\{\sc Time}};
+	label={\sc Verify~~~~~~~~~~~},
+        column sep=.7cm] (verif) {};
+     \node[minimum width=1.8cm, minimum height=0.8cm, fill=blue!20] (verif1) at ([xshift=-3cm]verif.center) {{\sc 3. Verify}\\{\sc Synthesis}};
+     \node[minimum width=1.8cm, minimum height=0.8cm, fill=blue!20] (verif2) at ([xshift=0cm]verif.center) {{\sc 5. Discrete}\\{\sc Time}};
+     \node[minimum width=1.8cm, minimum height=0.8cm, fill=blue!20] (verif3) at ([xshift=3cm]verif.center) {{\sc 7. Continuous}\\{\sc Time}};
    } 
@@
    \& \\
-   \node[minimum width=2.2cm, minimum height=0.8cm] (gp) {{\sf Program}\\{\sf Search}};
+   \node[minimum width=2cm, minimum height=0.8cm] (gp) {{\sf Program}\\{\sf Search}};
    \&
@@
      \coordinate (aux);
-   \node[minimum width=2.2cm, minimum height=0.8cm] (bmc) at ([xshift=-3cm]aux.center) {\sf Eigensolver};
-   \node[minimum width=2.2cm, minimum height=0.8cm] (fp)  at ([xshift=0cm]aux.center) {\sf Reachability \\ \sf Analysis};
-   \node[minimum width=2.2cm, minimum height=0.8cm] (sv)  at ([xshift=3cm]aux.center) {\sf Reachability \\ \sf Analysis};
+   \node[minimum width=1.8cm, minimum height=0.8cm] (bmc) at ([xshift=-3cm]aux.center) {\sf Eigensolver};
+   \node[minimum width=1.8cm, minimum height=0.8cm] (fp)  at ([xshift=0cm]aux.center) {\sf Reachability \\ \sf Analysis};
+   \node[minimum width=1.8cm, minimum height=0.8cm] (sv)  at ([xshift=3cm]aux.center) {\sf Reachability \\ \sf Analysis};
    }   

### 2018-01-31 TACAS2018/paper.tex
changed reals to infinite precision

@@
 we denote as $\mathcal{F}_{\langle M,F \rangle} : \mathbb{R} \rightarrow \mathbb{R}_{\langle M,F \rangle}$ the corresponding truncation function. 
+We further note that the results of mathematical operations in these domains are also truncated. This is referred to as roundoff errors.
 
@@
 %}
-Moreover, $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations \note{[How is this related to the previously mentioned FWL errors?]} Full details are in Appendix~\ref{sec:quantization-noise}.
+Moreover, $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations.
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-\note{At times the gain matrices K, L, do not appear with C/P indices  -  clarify why. }
 
@@
 $\mathbb{R}_{\langle P \rangle}$ for the controller, observer and
-plant, the {\sc model} and {\sc verify} phases use reals to represent
+plant, the {\sc model} and {\sc verify} phases use infinite precision ($\mathbb{R}$) to represent
 the plant and $\mathbb{R}_{\langle C \rangle}$ for the controller and
@@
 and we restore soundness during the verification and modeling stages. 
+Since we use different precisions at different stages, we will often use $\mat{K}$ and $\mat{L}$ to indicate that the domain they belong to is unspecified
+(these are always truncated to the corresponding domain at each stage).
 %% While these specifications are updated throughout the synthesis process (as appropriately described below), at all times $\phi_{static} \models \phi_{synth}$.
@@
 \end{itemize}
-\paragraph{\underline{{\sc synthesize}}} generates a candidate controller matrix $\mat{K}$
-and observer matrix $\mat{L}$ that satisfy
+\paragraph{\underline{{\sc synthesize}}} generates a candidate controller matrix $\mat{K}_{\langle P \rangle}$
+and observer matrix $\mat{L}_{\langle P \rangle}$ that satisfy
 $\phi$ by invoking a SAT solver.
@@
 $\mathbb{R}_{\langle C \rangle}$ for the controller representation
-and reals for the plant).  %% If the verification fails, the candidate is
+and $\mathbb{R}$ for the plant).  %% If the verification fails, the candidate is
 %% fed to the {\sc Optimise} phase.

### 2018-01-31 TACAS2018/paper.tex
Spell checking (americanized) removed authors

@@
 
-\author{Dario Cattaruzza, Cristina David, Alessandro Abate, Daniel Kroening}%\email{alessandro.abate@cs.ox.ac.uk}
+\author{%Dario Cattaruzza, Cristina David, Alessandro Abate, Daniel Kroening
+}%\email{alessandro.abate@cs.ox.ac.uk}
 %\email{dario.cattaruzza@cs.ox.ac.uk}
@@
 
-\institute{University of Oxford}
+\institute{%University of Oxford
+}
 
@@
 classical stability.  Recent work~\cite{abate2017automated} described a
-method for synthesising safe digital stabilizing controllers for fully
+method for synthesizing safe digital stabilizing controllers for fully
 observable LTI plants.  This work differs from the vast majority of existing
 approaches in that it explores the continuous space of the system to
-synthesise correct by construction minimal digital controllers.  Contrary to
+synthesize correct by construction minimal digital controllers.  Contrary to
 LTL models that require thousands of states and elaborate algorithms to
@@
 However,~\cite{abate2017automated}~is restricted to fully observed
-systems (i.e., where all the states are known) modelled in discrete time,
-and furthemore explores only a limited set of properties that engineers
+systems (i.e., where all the states are known) modeled in discrete time,
+and furthermore explores only a limited set of properties that engineers
 are interested in. Conversely, 
@@
 directly measured but rather inferred from its
-effect on the output. A plant model that minimises the difference
+effect on the output. A plant model that minimizes the difference
 between its output and the real plant output is called an observer and it is a well known
@@
 parametric synthesis of controllers meeting a number of properties that
-define their desired behaviour.
+define their desired behavior.
 
@@
 quantizers (A/D and D/A converters) and of time discretization, as well as
-representation errors introduced by modelling artifacts such as an
+representation errors introduced by modeling artifacts such as an
 observer~\cite{astrom1997computer} in a finite precision domain, while
 reasoning about high level properties such as stability, robustness, safety,
-and response time, which define the behaviour of the system.  In particular,
+and response time, which define the behavior of the system.  In particular,
 safety requirements are frequently overlooked in conventional feedback
@@
 Refinement).  This design uses an iterative process where each
-iteration performs inductive generalisation based on counterexamples
+iteration performs inductive generalization based on counterexamples
 provided by a verification oracle.  Essentially, the inductive
-generalisation uses information about a limited number of inputs to
+generalization uses information about a limited number of inputs to
 make claims in the form of candidate solutions about all the possible
@@
   alongside stability and response time specifications.  We note that
-  observers are much more complex and difficult to synthesise than standard
+  observers are much more complex and difficult to synthesize than standard
   full-state feedback controllers (hence the need for abstraction refinement).
@@
 Finally, the set $\hat{X} =\bigcup_{n\geq 0} \tau^n(X_0,U)$, which we refer to as
-the reach space of the system, generalises the previous notions over an unbounded
+the reach space of the system, generalizes the previous notions over an unbounded
 time horizon (transitive closure).
@@
 Lastly, $k_r$ is a reference gain required by the model.  
-Our goal in this work is to synthesise both $\mat{K}_{\langle C \rangle}$ and $\mat{L}_{\langle C \rangle}$, 
+Our goal in this work is to synthesize both $\mat{K}_{\langle C \rangle}$ and $\mat{L}_{\langle C \rangle}$, 
  so that specific closed-loop properties of the overall interconnection are satisfied.
@@
 
-\note{Much like we did in the earlier work, we should emphasise we look at the closed-loop interconnection from the perspective of the digital controller? }
+%\note{Much like we did in the earlier work, we should emphasise we look at the closed-loop interconnection from the perspective of the digital controller? }
 
@@
  allows us to evaluate the state of the plant at integer multiples of the sample time.
- However, in order to synthesise $\mat{K}=\mat{K}_{\langle C \rangle}$ and $\mat{L}=\mat{L}_{\langle C \rangle}$, 
+ However, in order to synthesize $\mat{K}=\mat{K}_{\langle C \rangle}$ and $\mat{L}=\mat{L}_{\langle C \rangle}$, 
  we must be able to ensure that certain properties of the plant hold at any given real time.
@@
 
-The final case we analyse is that of hybrid-time models, 
+The final case we analyze is that of hybrid-time models, 
 where the plant dynamics evolve in continuous time while the feedback dynamics evolve in discrete time.  
@@
  \end{align*}
+ For the proof see Appendix~\ref{sec:proofs}
  \end{theorem}
-\begin{proof}
-See Appendix~\ref{sec:proofs}
-\end{proof}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Modelling errors in the control loop}\label{sec:errors}
+%\begin{proof}
+%See Appendix~\ref{sec:proofs}
+%\end{proof}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{Modeling errors in the control loop}\label{sec:errors}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 corruptions over communication lines in the control loop, 
-and approximations due to digitalisation.
+and approximations due to digitalization.
 
@@
 \begin{theorem}
-The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modelled as a non-deterministic disturbance signal ($\nu_t$ in Figure \ref{fig:observersystem}) upper bounded by
+The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modeled as a non-deterministic disturbance signal ($\nu_t$ in Figure \ref{fig:observersystem}) upper bounded by
 \begin{align}
@@
 which we extend to sets as $\norm{X}_1 = \sup \{\norm{\vec{x}}_1, \vec{x} \in X\}$.  
+For the proof see Appendix~\ref{sec:proofs}
 \end{theorem}
 %
-\begin{proof}
-See Appendix~\ref{sec:proofs}
-\end{proof}
+%\begin{proof}
+%See Appendix~\ref{sec:proofs}
+%\end{proof}
 This result allows to over-approximate the effects of the delay by introducing a disturbance signal $\nu_t=[-q_t, q_t]$ at the output.
@@
 
-Since we are interested in synthesising controllers with observers, 
+Since we are interested in synthesizing controllers with observers, 
 in this section we will look at checking stability, safety and the response time in the presence of an observer.
@@
  which boils down to a requirement expressed as an algebraic formula 
- on the characteristic polynomial of the model.% - a SAT solver will manipulate its coefficients. 
-%
+ on the characteristic polynomial of the model.
 In order to facilitate the use of Jury's criterion, we transform the model into
@@
 polynomial expressed as sums of controller and plant values. 
-The benefit of this representation is that it has no multiplications, which are expensive to handle by SAT solvers (used by the synthesiser). 
+The benefit of this representation is that it has no multiplications, which are expensive to handle by SAT solvers (used by the synthesizer). 
 %
@@
 
-We assume that the domain of the observer model is discretised, 
+We assume that the domain of the observer model is discretized, 
 i.e., the domain for both the controller and the observer is $\mathbb{R}_{\langle C \rangle}$.
@@
 %}
-Moreover, $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations.
+Moreover, $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by round-offs in the FWL operations.
 
@@
 %
-In the case of $\mat{A}_c$, the procedure is the same except that we need to look at the colums shared with $\mat{A}_c$.
+In the case of $\mat{A}_c$, the procedure is the same except that we need to look at the columns shared with $\mat{A}_c$.
 Thus we obtain our bound $\delta_c=\max(\norm{{\mat{A}_e}_{*,i}+{\mat{B}_e}_{*,i}}_1)$
@@
 \end{equation}
-where $0\leq P_s \leq 1$ is the desired portion of the target within which the output must remain after $t_s$.
+where $0\leq P_s \leq 1$ is the desired portion of the target within which the output must remain after $t_s$.  For the proof see Appendix~\ref{sec:proofs}
 \end{theorem}
 
-\begin{proof}
-See Appendix~\ref{sec:proofs}
-\end{proof}
+%\begin{proof}
+%See Appendix~\ref{sec:proofs}
+%\end{proof}
 %
@@
 denotes an iterative technique where each step performs inductive
-generalisation based on counterexamples provided by a verification
-engine. In each iteration, an inductive synthesiser produces a
+generalization based on counterexamples provided by a verification
+engine. In each iteration, an inductive synthesizer produces a
 candidate solution that obeys the specification for a limited number
@@
 %%   and failing this feed the {\sc Abstract} phase the necessary information to produce a better candidate.
-%% \item {\sc verify}: verifies the behaviour of the candidate controller and observer
+%% \item {\sc verify}: verifies the behavior of the candidate controller and observer
 %%   against a sound over-approximation of the concrete dynamics of the system for an infinite space over an infinite time horizon.
@@
 %% because later stages of synthesis will use more complex abstractions, the reduction
-%% is on increasingly expensive formulas and therefore the improvent can be exponential.
+%% is on increasingly expensive formulas and therefore the improvement can be exponential.
 
@@
 %% abstractions relating to quantization and safety which allow us to create models
-%% for the synthesisers. This specification (which we refer to as $\phi$) is passed to
+%% for the synthesizers. This specification (which we refer to as $\phi$) is passed to
 %% the Bounded Model Checker CBMC~\cite{ClarkeKL04} which uses SAT solving to
@@
 %% construction of an unsound abstract model ({\sc ABSTRACT} phase) that approximates the dynamics
-%% of the cyber-physical system in order to synthesise a candidate controller
-%% and observer and then verify their behaviour against a sound over-approximation
+%% of the cyber-physical system in order to synthesize a candidate controller
+%% and observer and then verify their behavior against a sound over-approximation
 %% of the concrete dynamics of the system for an infinite space over an infinite
@@
 %% The novelty of our approach relies on the synthesis refinement phase, which
-%% enables us to generalise an existing candidate by means of optimisation.
+%% enables us to generalize an existing candidate by means of optimization.
 %% Rather
 %% than allow unsuitable candidates reach the verification phase, and possibly
-%% require further induction on the synthesiser, we use an optimizing algorithm
+%% require further induction on the synthesizer, we use an optimizing algorithm
 %% which finds a local minima for the properties of interest.  This reduces the
-%% chances of the optimised candidate failing verification.  Furthermore, it
+%% chances of the optimized candidate failing verification.  Furthermore, it
 %% allows us to relax the quality of the synthesis, since unlikely candidates will
-%% still be optimised during this phase. 
+%% still be optimized during this phase. 
 %% The optimization is performed on an objective function which will typically depend
@@
 the way $\phi$ is being used in different phases in Figure~\ref{fig:CEGIS-OR}: while the
-{\sc synthesise} phase checks $\phi$ by using the plant precision
+{\sc synthesize} phase checks $\phi$ by using the plant precision
 $\mathbb{R}_{\langle P \rangle}$ for the controller, observer and
@@
 and $\mathbb{R}$ for the plant).  %% If the verification fails, the candidate is
-%% fed to the {\sc Optimise} phase.
+%% fed to the {\sc Optimize} phase.
 If the candidate is valid, we feed
@@
 reach space to the closest point to it in the safe region
-\begin{equation}
+$%\begin{equation}
 e = \max\{\min\{\vec{x}-\vec{g}, \vec{g}\in G\}, \vec{x} \in \hat{X}_\infty \}.
-\label{eq:objective}
-\end{equation}
+%\label{eq:objective}
+$%\end{equation}
 
@@
 verified against the safety specification $\phi_\mathit{safety}$ and the
-objective $e$ is measured as in Equation \eqref{eq:objective}.   If for
-each iteration $k$, the objective $e_k<e_{k-1}$, we continue to
+objective $e$ is measured. % as in Equation \eqref{eq:objective}.   
+If for each iteration $k$, the objective $e_k<e_{k-1}$, we continue to
 iterate until $e_k \leq 0$ (i.e. we found a safe controller),
@@
 We must point out that the optimizer tool uses infinite precision for the plant, and
-may therefore find solutions that the synthesiser cannot, due to the use of limited precision.
+may therefore find solutions that the synthesizer cannot, due to the use of limited precision.
 If we cannot optimize the candidate  we signal the {\sc Abstract} phase to 
-use the updated $\phi$ and request {\sc Synthesise} to produce a new
+use the updated $\phi$ and request {\sc Synthesize} to produce a new
 candidate.  Otherwise the optimized candidate solution is given back to
@@
 }
-\caption{CEGIS-OR: CEGIS with Optimization Refinement. Orange boxes (light) are modelling
+\caption{CEGIS-OR: CEGIS with Optimization Refinement. Orange boxes (light) are modeling
 stages, blue boxes (dark) are verification stages, and the red box is the synthesis stage. 
@@
 2  & Helicopter        & 3  & 100 & 57.2\,s & t.o. & 54 & 15 & 7.1\,s  &   18.0\,s & 9 & 90\\
-3  & Inverted Pendulum & 4 & 100 &  277\,s& t.o. & 42& 0 & 20.0\,s  &  t.o. & 37 & 19\\
+3  & Inverted Pendulum & 4 & 100 &  277\,s& t.o. & 59& 0 & 20.0\,s  &  t.o. & 50 & 20\\
 4  & Magnetic Pointer  & 2  & 100 & 5.7\,s & 229.9\,s & 38 & 42 & 3.0\,s  &  9.5\,s & 5 & 95 \\
@@
 valid solution. However, there are cases where a solution may not be found due the
-approximations in the synthesiser that would prevent a true candidate from being found
+approximations in the synthesizer that would prevent a true candidate from being found
 or over-approximations in the verifier that may reject a valid candidate.
@@
 %% improvements.
-While some systems might still require a very pecise
+While some systems might still require a very precise
 abstraction resulting in many refinements
@@
 %% abstraction, CEGIS-OR has smaller minimum times than CEGIS, obtained
-%% when the initial coarse abstractions were sufficient to synthesise a
+%% when the initial coarse abstractions were sufficient to synthesize a
 %% solution.
@@
 
-There are cases where newly found controllers are due to the fact that the
-optimiser can reason about infinite precision numbers and may therefore find
-solutions that are not available using 64 bit plant precision, which
-is the maximum allowed by the {\sc synthesize} phase in our implementation
-(in standard CEGIS {\sc synthesize} is the only phase that can generate a
-candidate controller).
+%There are cases where newly found controllers are due to the fact that the
+%optimizer can reason about infinite precision numbers and may therefore find
+%solutions that are not available using 64 bit plant precision, which
+%is the maximum allowed by the {\sc synthesize} phase in our implementation
+%(in standard CEGIS {\sc synthesize} is the only phase that can generate a
+%candidate controller).
 
@@
 %%-------------------------------
-%Since our synthesisers use abstract aproximations of the real dynamics, our solution is not complete.
+%Since our synthesizers use abstract aproximations of the real dynamics, our solution is not complete.
 %it is possible to have models where a true solution is not found although it exists.
@@
 
-There is still a need to extend CEGIS-OR to MIMO models and to analyse more general properties, 
+There is still a need to extend CEGIS-OR to MIMO models and to analyze more general properties, 
 which may also require exploring other optimization methods for control systems.
@@
 feedback line creates a loop in the diagram this is known as a closed loop,
-and the overall behaviour of the resulting system is said to have closed loop dynamics.
+and the overall behavior of the resulting system is said to have closed loop dynamics.
 The feedback may be direct or have further transformations, some of which will
@@
 absolute values are strictly less than one~\cite{astrom1997computer}
-(this simple sufficient condition can be generalised, however this is
+(this simple sufficient condition can be generalized, however this is
 not necessary in our work).  In this work, we express this stability
@@
  \begin{proof}
- Let us recall equation \ref{eq:plant}. The discrete representation of the system dynamics discretised with sample time $T_1$ is ruled by the formula
+ Let us recall equation \ref{eq:plant}. The discrete representation of the system dynamics discretized with sample time $T_1$ is ruled by the formula
  $\mat{A}_1 = e^{\mat{A} T_1}$. From matrix theory, we have 
@@
 
-The final case we analyse here is that of hybrid time systems, where the
+The final case we analyze here is that of hybrid time systems, where the
 plant dynamics evolve in continuous time while the feedback dynamics evolve
@@
 \begin{theorem}
-The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modelled as a non-deterministic noise signal upper bound by
+The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modeled as a non-deterministic noise signal upper bound by 
 \begin{align}
@@
 \begin{enumerate}
-\item The \emph{rise time} is defined as the time it takes the output to reach a percentage (eg $90\%$) of the target value given a step chnage in the input.
+\item The \emph{rise time} is defined as the time it takes the output to reach a percentage (eg $90\%$) of the target value given a step change in the input.
 \item The \emph{settling time} is defined as the time it takes the output to stabilize within a margin of the target value (eg $10\%$).
@@
 \item Ensure that $|\overline{\omega}| \leq \frac{\underline{k}}{\underline{k}+1}$ and that the
-synthesised closed loop does not have a larger gm than specified.
+synthesized closed loop does not have a larger gm than specified.
 \end{itemize}

### 2018-01-31 TACAS2018/paper.tex
wording abstract

@@
 
-\author{%Dario Cattaruzza, Cristina David, Alessandro Abate, Daniel Kroening
+\author{Anonymous%Dario Cattaruzza, Cristina David, Alessandro Abate, Daniel Kroening
 }%\email{alessandro.abate@cs.ox.ac.uk}
@@
 %
-We present a sound and automated approach to synthesizing safe,
-digital, observer-based controllers for physical plants represented as
-linear, time-invariant models.  Models are defined as differential
-equations with inputs, evolving over a continuous state space. The
-synthesis accounts for errors caused by the digitization effects
-introduced by the controller.  We use a counterexample-guided
-inductive synthesis procedure enhanced with abstraction
-refinement and optimization, which allows us to start by considering
-a low-resolution discretized model of the system and %, which enables us to
-find candidate solutions fast. This model gets refined on demand.
-Moreover, in order to improve our chances of finding a solution even
-when considering coarse abstractions of the system, in each iteration of the CEGIS
-loop we use matrix eigen-decomposition to optimize our candidate.
+We present a sound and automated approach to synthesizing safe, digital,
+observer-based controllers for physical plants represented as linear,
+time-invariant models.  Models are defined as differential equations with
+inputs, evolving over a continuous state space.  The synthesis accounts for
+errors caused by the digitization effects introduced by the controller. 
+We~use counterexample-guided inductive synthesis enhanced with abstraction
+refinement and optimization, which allows us to start with a low-resolution
+discretized model and find candidate solutions fast.  This model is refined
+on demand.  Moreover, in order to improve our chances of finding a solution
+even when considering coarse abstractions of the system, in each iteration
+of the CEGIS loop we use matrix eigen-decomposition to optimize our
+candidate.
+%
 %% Once we have a candidate, we use matrix eigen-decomposition
@@
 %synthesiser in a traditional CEGIS manner.
-This design yields a significant speed-up compared to a traditional
-CEGIS scheme (i.e. without abstraction refinement and optimization).
-We demonstrate the practical value of this approach by automatically
-synthesizing safe observer-based controllers for physical plant models
-from the digital control literature.
+%
+This design yields a significant speed-up compared to traditional CEGIS
+(i.e., without abstraction refinement and optimization).  We~demonstrate the
+practical value of this approach by automatically synthesizing safe
+observer-based controllers for physical plant models from the digital
+control literature.
 %

### 2018-01-31 TACAS2018/paper.tex
line breaks

@@
 control tasks, with significant impact in numerous application areas such as
-life sciences, environmental control and robotics~\cite{astrom1997computer,Franklin15}.  Correct synthesis is non-trivial, even in cases with
+life sciences, environmental control and robotics~\cite{astrom1997computer,
+Franklin15}.  Correct synthesis is non-trivial, even in cases with
 restricted dynamics.  We examine the case of Linear Time Invariant (LTI)
@@
 artifacts specific to digital control, such as the effects of
-finite-precision arithmetic (referred to here as Finite Word Length or FWL effects), time discretization and quantization errors
-introduced by A/D and D/A conversion.
+finite-precision arithmetic (referred to here as Finite Word Length or FWL
+effects), time discretization and quantization errors introduced by A/D and
+D/A conversion.
 
@@
 LTL models that require thousands of states and elaborate algorithms to
-implement \cite{reissig2017feedback}, these PID-like controllers are represented by a few parameters
-and only require a few lines of code, thus reducing the implementation cost
-and execution time while remaining resilient to the effects of digitalization.
-However,~\cite{abate2017automated}~is restricted to fully observed
-systems (i.e., where all the states are known) modeled in discrete time,
-and furthermore explores only a limited set of properties that engineers
-are interested in. Conversely, 
-in most real implementations, the internal state of a plant cannot be
-directly measured but rather inferred from its
-effect on the output. A plant model that minimizes the difference
-between its output and the real plant output is called an observer and it is a well known
-paradigm in the control literature~\cite{astrom1997computer}.
+implement \cite{reissig2017feedback}, these PID-like controllers are
+represented by a few parameters and only require a few lines of code, thus
+reducing the implementation cost and execution time while remaining
+resilient to the effects of digitalization. 
+However,~\cite{abate2017automated}~is restricted to fully observed systems
+(i.e., where all the states are known) modeled in discrete time, and
+furthermore explores only a limited set of properties that engineers are
+interested in.  Conversely, in most real implementations, the internal state
+of a plant cannot be directly measured but rather inferred from its effect
+on the output.  A plant model that minimizes the difference between its
+output and the real plant output is called an observer and it is a well
+known paradigm in the control literature~\cite{astrom1997computer}.
 
@@
 %% a-posteriori verification.
-Specifically, we synthesize stable,
-software-implemented embedded controllers along with a model of a physical
-plant (observer).  Due to the complexity of such closed-loop systems, we focus
-on linear models with known configurations, and perform
-parametric synthesis of controllers meeting a number of properties that
-define their desired behavior.
+%
+Specifically, we synthesize stable, software-implemented embedded
+controllers along with a model of a physical plant (observer).  Due to the
+complexity of such closed-loop systems, we focus on linear models with known
+configurations, and perform parametric synthesis of controllers meeting a
+number of properties that define their desired behavior.
 
@@
 
-We use a CounterExample-Guided Inductive Synthesis (CEGIS)
-\cite{jha-icse10,DBLP:conf/pldi/Solar-LezamaRBE05} approach,
-which we enhance with abstraction refinement and optimization
-resulting in the novel CEGIS-OR (CEGIS with Optimization and
-Refinement).  This design uses an iterative process where each
-iteration performs inductive generalization based on counterexamples
-provided by a verification oracle.  Essentially, the inductive
-generalization uses information about a limited number of inputs to
-make claims in the form of candidate solutions about all the possible
+We use a CounterExample-Guided Inductive Synthesis (CEGIS)~\cite{jha-icse10,
+DBLP:conf/pldi/Solar-LezamaRBE05} approach, which we enhance with
+abstraction refinement and optimization resulting in the novel CEGIS-OR
+(CEGIS with Optimization and Refinement).  This design uses an iterative
+process where each iteration performs inductive generalization based on
+counterexamples provided by a verification oracle.  Essentially, the
+inductive generalization uses information about a limited number of inputs
+to make claims in the form of candidate solutions about all the possible
 inputs.  By using abstraction refinement, CEGIS-OR allows us to handle
-complex systems which are initially represented by coarse abstractions
-that only get refined on demand.  Consequently, solutions that do not
-require a high level of precision are obtained fast.  Since the use
-of coarse abstractions may result in low-quality candidate solutions
-(i.e. candidates that fail the specification on a very large number of
-inputs), after each inductive generalization phase we use optimization
-techniques to improve the produced candidates.  In particular, our
-optimization procedure aims at reducing the size of the reach space of
-the closed loop system, while maintaining other dynamical properties
-of interest (safety, stability, and response time).
+complex systems which are initially represented by coarse abstractions that
+only get refined on demand.  Consequently, solutions that do not require a
+high level of precision are obtained fast.  Since the use of coarse
+abstractions may result in low-quality candidate solutions (i.e.  candidates
+that fail the specification on a very large number of inputs), after each
+inductive generalization phase we use optimization techniques to improve the
+produced candidates.  In particular, our optimization procedure aims at
+reducing the size of the reach space of the closed loop system, while
+maintaining other dynamical properties of interest (safety, stability, and
+response time).
 
@@
 parameters are stable by design.  The analyses
-in~\cite{DBLP:conf/hybrid/RouxJG15,DBLP:conf/hybrid/WangGRJF16} rely on an
+in~\cite{DBLP:conf/hybrid/RouxJG15, DBLP:conf/hybrid/WangGRJF16} rely on an
 invariant computation on the discrete system dynamics using Semi-Definite
@@
 We consider models of physical plants expressed as ordinary differential
-equations (ODEs), which we assume to be controllable \cite{Astrom08,astrom1997computer}:
+equations (ODEs), which we assume to be controllable~\cite{Astrom08,
+astrom1997computer}:
 %
@@
 %
-where $t \in \mathbb R_0^+$ denotes continuous time, 
-$\mat{A}$ and $\mat{B}$ are matrices that fully characterize the dynamics of the continuous plant, 
+where $t \in \mathbb R_0^+$ denotes continuous time, $\mat{A}$ and $\mat{B}$
+are matrices that fully characterize the dynamics of the continuous plant,
 and $x(0)$ is the initial state.
@@
 Equations~\eqref{eq:ode1}-\eqref{eq:ode2} are soundly discretized in
-time~\cite{middleton1990digital,van1978computing} at constant intervals, whose 
-duration we refer to as the sample time $T_s$, 
-into the difference equation 
+time~\cite{middleton1990digital,van1978computing} at constant intervals,
+whose duration we refer to as the sample time $T_s$, into the difference
+equation
+%
 \begin{align}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-In many models of real-world control systems, 
-the internal state $x$ cannot be directly measured,  
-but is rather inferred from its effect on the measured output $\vec{y}$ using an observer~\cite{Astrom08}.  
-Essentially, a state observer is a new dynamical model (with variable denoted as $\hat{\vec{x}}$) 
-that provides an estimate of the internal state $x$ of the given model, 
-from measurements of its inputs and outputs.
-
-A closed-loop digital control interconnection with observer is shown in Figure~\ref{fig:observersystem}. 
-The linear feedback controller (bottom left) is characterized by a gain matrix $\mat{K}_{\langle C \rangle}$ that influences the closed-loop dynamics, 
-and is driven by the observer state $\hat{\vec{x}}$.  
-Moreover, $\vec{y}_e=\hat{\vec{y}} - \vec{y}$ is the error on the output estimator,  
+
+In many models of real-world control systems, the internal state $x$ cannot
+be directly measured, but is rather inferred from its effect on the measured
+output $\vec{y}$ using an observer~\cite{Astrom08}.  Essentially, a state
+observer is a new dynamical model (with variable denoted as $\hat{\vec{x}}$)
+that provides an estimate of the internal state $x$ of the given model, from
+measurements of its inputs and outputs.
+
+A closed-loop digital control interconnection with observer is shown in
+Figure~\ref{fig:observersystem}.  The linear feedback controller (bottom
+left) is characterized by a gain matrix $\mat{K}_{\langle C \rangle}$ that
+influences the closed-loop dynamics, and is driven by the observer state
+$\hat{\vec{x}}$.  Moreover, $\vec{y}_e=\hat{\vec{y}} - \vec{y}$ is the error
+on the output estimator,
 %  defined as the difference between the real output $\vec{y}_k$ and estimated one $\hat{\vec{y}_k}$, 
-which is amplified by a gain matrix $\mat{L}_{\langle C \rangle}$.
-Note that the controller and the observer are implemented in a discrete domain 
-(quantities within this domain are identified by the index $\langle C \rangle$), 
-whereas the plant evolves in a continuous domain. 
-We further model the effects of using a discrete controller as the noise signals $\nu_1$(ADC quantization), $\nu_2$ (DAC quantization), $\nu_1'$ (rounding of the observer state error),
-$\nu_2'$ (rounding of the observer state), and $\nu_t$ (output delay of the digital system) 
-Lastly, $k_r$ is a reference gain required by the model.  
-Our goal in this work is to synthesize both $\mat{K}_{\langle C \rangle}$ and $\mat{L}_{\langle C \rangle}$, 
- so that specific closed-loop properties of the overall interconnection are satisfied.
+which is amplified by a gain matrix $\mat{L}_{\langle C \rangle}$.  Note
+that the controller and the observer are implemented in a discrete domain
+(quantities within this domain are identified by the index $\langle C
+\rangle$), whereas the plant evolves in a continuous domain.  We further
+model the effects of using a discrete controller as the noise signals
+$\nu_1$(ADC quantization), $\nu_2$ (DAC quantization), $\nu_1'$ (rounding of
+the observer state error), $\nu_2'$ (rounding of the observer state), and
+$\nu_t$ (output delay of the digital system) Lastly, $k_r$ is a reference
+gain required by the model.  Our goal in this work is to synthesize both
+$\mat{K}_{\langle C \rangle}$ and $\mat{L}_{\langle C \rangle}$, so that
+specific closed-loop properties of the overall interconnection are
+satisfied.
 
@@
 
-A common occurrence in digital systems is that they do not necessarily satisfy real-time specifications, 
-in view of many errors introduced in the dynamics. 
-Errors might result from delays due to processing time,
-corruptions over communication lines in the control loop, 
-and approximations due to digitalization.
+A common occurrence in digital systems is that they do not necessarily
+satisfy real-time specifications, in view of many errors introduced in the
+dynamics.  Errors might result from delays due to processing time,
+corruptions over communication lines in the control loop, and approximations
+due to digitalization.
 
@@
 
-In our model, delays are all deferred to the Zero Order Holder (ZOH) of the DAC (See Figure \ref{fig:observersystem}). 
-In the digital world everything takes place at times $t=kT_s, k \in \mathbb{N}$ (discrete time progression),
-and the output signal is delayed at the DAC when fed back to the continuous-time domain at time ($t=kT_s+t_d$).
+In our model, delays are all deferred to the Zero Order Holder (ZOH) of the
+DAC (See Figure \ref{fig:observersystem}).  In the digital world everything
+takes place at times $t=kT_s, k \in \mathbb{N}$ (discrete time progression),
+and the output signal is delayed at the DAC when fed back to the
+continuous-time domain at time ($t=kT_s+t_d$).
 
@@
 
-In Figure \ref{fig:observersystem} we have introduced sources of noise that are due to quantization effects.  
-These effects are caused by imprecise numerical representations of real numbers in the digital domain of the controller and play an important role in the synthesis of sound controllers. 
-The model has two sources of error due to Finite Word Length (FWL) representations. 
-The first is the numerical error introduced by the fixed-point numbers employed to model the plant, 
-i.e., to represent the plant dynamics $A_d$, $B_d$, $C_d$, $D_d$, $x_k$ and $y_k$. 
-The second is the quantization error introduced by the digital controller, 
-which performs operations over fixed-point numbers.  
-In this section we outline the notation for the finite representation of numbers, 
-and briefly describe the introduced errors.  
-A formal discussion is in Appendix~\ref{sec:numeric_rep}.
+In Figure~\ref{fig:observersystem} we have introduced sources of noise that
+are due to quantization effects.  These effects are caused by imprecise
+numerical representations of real numbers in the digital domain of the
+controller and play an important role in the synthesis of sound controllers. 
+The model has two sources of error due to Finite Word Length (FWL)
+representations.  The first is the numerical error introduced by the
+fixed-point numbers employed to model the plant, i.e., to represent the
+plant dynamics $A_d$, $B_d$, $C_d$, $D_d$, $x_k$ and $y_k$.  The second is
+the quantization error introduced by the digital controller, which performs
+operations over fixed-point numbers.  In this section we outline the
+notation for the finite representation of numbers, and briefly describe the
+introduced errors.  A formal discussion is in
+Appendix~\ref{sec:numeric_rep}.
 
@@
 the decimal place).  We note that a negative $F$ denotes an integer
-multiplication that adds $-F$ trailing zeros in the number represented by
-$M$. 
-We will use the domain $\mathbb{R}_{\langle C \rangle} \text{ where } \langle C \rangle = \langle M_c,F_c \rangle$
-to represent the fixed point precision of the controller, and 
-$\mathbb{R}_{\langle P \rangle} \supseteq \mathbb{R}_{\langle C \rangle}$
-to represent the domain of a digital model of the dynamics of a real plant when
-evaluated by a verification tool.  Elements in this domain are marked with an
-underscore~${\langle C \rangle}$ (see Figure \ref{fig:observersystem}).
-Thus, any mathematical operation within the digital controller is executed in the
-domain $\mathbb{R}_{\langle C \rangle}$, and all other calculations
-in our model will be carried out in the domain $\mathbb{R}_{\langle P \rangle}$.
-Given ${\langle M,F \rangle}$, 
-we denote as $\mathcal{F}_{\langle M,F \rangle} : \mathbb{R} \rightarrow \mathbb{R}_{\langle M,F \rangle}$ the corresponding truncation function. 
-We further note that the results of mathematical operations in these domains are also truncated. This is referred to as roundoff errors.
+multiplication that adds $-F$ trailing zeros in the number represented
+by~$M$.  We will use the domain $\mathbb{R}_{\langle C \rangle}
+\text{ where } \langle C \rangle = \langle M_c,F_c \rangle$ to represent the fixed point
+precision of the controller, and $\mathbb{R}_{\langle P \rangle} \supseteq
+\mathbb{R}_{\langle C \rangle}$ to represent the domain of a digital model
+of the dynamics of a real plant when evaluated by a verification tool. 
+Elements in this domain are marked with an underscore~${\langle C \rangle}$
+(see Figure \ref{fig:observersystem}).  Thus, any mathematical operation
+within the digital controller is executed in the domain $\mathbb{R}_{\langle
+C \rangle}$, and all other calculations in our model will be carried out in
+the domain $\mathbb{R}_{\langle P \rangle}$.  Given ${\langle M,F \rangle}$,
+we denote as $\mathcal{F}_{\langle M,F \rangle} : \mathbb{R} \rightarrow
+\mathbb{R}_{\langle M,F \rangle}$ the corresponding truncation function.  We
+further note that the results of mathematical operations in these domains
+are also truncated.  This is referred to as roundoff errors.
 
@@
 
-Since we are interested in synthesizing controllers with observers, 
-in this section we will look at checking stability, safety and the response time in the presence of an observer.
+Since we are interested in synthesizing controllers with observers, in this
+section we will look at checking stability, safety and the response time in
+the presence of an observer.
+
 %\footnote{A full description of the theory related to observer design is in Appendix \ref{sec:control_theory}.}
@@
 
-Stability qualitatively denotes the property of a model to evolve within a bounded set around an equilibrium point. 
-In this paper, we are interested in asymptotic stability, where the model is further expected to converge to the steady state value (i.e., the equilibrium point).   
+Stability qualitatively denotes the property of a model to evolve within a
+bounded set around an equilibrium point.  In this paper, we are interested
+in asymptotic stability, where the model is further expected to converge to
+the steady state value (i.e., the equilibrium point).
 %
@@
 as classical in Control Theory,  %\footnote{More details on Jury's criterion is in Appendix~\ref{sec:closed_stability}.}, 
- which boils down to a requirement expressed as an algebraic formula 
- on the characteristic polynomial of the model.
-In order to facilitate the use of Jury's criterion, we transform the model into
-a representation that contains the coefficients of its characteristic
-polynomial expressed as sums of controller and plant values. 
-The benefit of this representation is that it has no multiplications, which are expensive to handle by SAT solvers (used by the synthesizer). 
+which boils down to a requirement expressed as an algebraic formula on the
+characteristic polynomial of the model.  In order to facilitate the use of
+Jury's criterion, we transform the model into a representation that contains
+the coefficients of its characteristic polynomial expressed as sums of
+controller and plant values.  The benefit of this representation is that it
+has no multiplications, which are expensive to handle by SAT solvers (used
+by the synthesizer).
 %
@@
 }
-where $\vec{x}'$ is the state of the model in canonical form and $\vec{x}_e'$ is the error of the observer evaluated in the transformed domain; 
-further, $\mat{A}_{c}$ the closed-loop matrix of the controller in canonical form, 
-$\mat{A}_{o}$ the closed-loop matrix of the observer in canonical form, 
-$\mat{B}_{o}$ the a feedback gain matrix, 
- $\mat{B}'$ the noise sensitivity matrix, 
-and $\mat{A}_{e}$ and $\mat{B}_{e}$ are the error caused by the FWL truncation, seen after the transformation to canonical form.
+%
+where $\vec{x}'$ is the state of the model in canonical form and
+$\vec{x}_e'$ is the error of the observer evaluated in the transformed
+domain; further, $\mat{A}_{c}$ the closed-loop matrix of the controller in
+canonical form, $\mat{A}_{o}$ the closed-loop matrix of the observer in
+canonical form, $\mat{B}_{o}$ the a feedback gain matrix, $\mat{B}'$ the
+noise sensitivity matrix, and $\mat{A}_{e}$ and $\mat{B}_{e}$ are the error
+caused by the FWL truncation, seen after the transformation to canonical
+form.
+
 %and we have introduced the following terms: 
@@
 %}
-Moreover, $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by round-offs in the FWL operations.
-
-In a real domain $\mathbb{R}$, the characteristic polynomial
-of the closed loop dynamics is defined by the characteristic polynomials of~$\mat{A}_c$
+%
+Moreover, $\nu_1$ and $\nu_2$ are the quantization noises introduced by the
+ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$
+and $\nu_2'$ are quantization noises caused by round-offs in the FWL
+operations.
+
+In a real domain $\mathbb{R}$, the characteristic polynomial of the closed
+loop dynamics is defined by the characteristic polynomials of~$\mat{A}_c$
 and~$\mat{A}_o$.
+%
 \begin{align*}
@@
 \end{align*}
-Jury's criteria uses these coefficients to ensure that no root of the polynomial has a magnitude greater than one.
+%
+Jury's criteria uses these coefficients to ensure that no root of the
+polynomial has a magnitude greater than one.
+%
 %\note{we should perhaps provide a qualitative hint on what are the conditions of JC? I'm afraid leaving it to the polynomials here isn't quite complete or clear.}
-The introduction of the FWL errors causes this to no longer
-be true.
-We must therefore find a suitable solution to maintain this independence of polynomials and use the given coefficients by bounding their error w.r.t.
+%
+The introduction of the FWL errors causes this to no longer be true. 
+We~must therefore find a suitable solution to maintain this independence of
+polynomials and use the given coefficients by bounding their error w.r.t. 
 the true coefficients of the closed loop matrix.
 
-Gershgorin disks~\cite{van1996matrix} allow us to limit the error
-in the expected eigenvalues.  Let $\delta_o=\max(\norm{{\mat{A}_e}_{i,*}}_1)$
+Gershgorin disks~\cite{van1996matrix} allow us to limit the error in the
+expected eigenvalues.  Let $\delta_o=\max(\norm{{\mat{A}_e}_{i,*}}_1)$
 (\emph{i.e.} the largest row norm in $\mat{A}_e$) be the largest error bound
 for any eigenvalue in $\mat{A}_e$.  Then $\forall i \in [1, ...\,,n],
-|{\lambda_o}_{i}-\hat{\lambda}_{oi}|<\delta_o$, where ${\lambda_o}_{i}$ are the
-true eigenvalues of the observer $\mat{A}_o$ and $\hat{\lambda}_{oi}$
-the corresponding eigenvalues of the closed loop. We note that in the case of
-stability we only care that their norms are smaller than one, which is equivalent to
-upper bounding the estimation of the largest eigenvalue.  Hence, given a
-desired upper value $\overline{\lambda}$ (see Section \ref{sec:transientspecification}), we apply Jury's criterion on the
+|{\lambda_o}_{i}-\hat{\lambda}_{oi}|<\delta_o$, where ${\lambda_o}_{i}$ are
+the true eigenvalues of the observer $\mat{A}_o$ and $\hat{\lambda}_{oi}$
+the corresponding eigenvalues of the closed loop.  We note that in the case
+of stability we only care that their norms are smaller than one, which is
+equivalent to upper bounding the estimation of the largest eigenvalue. 
+Hence, given a desired upper value $\overline{\lambda}$ (see Section
+\ref{sec:transientspecification}), we apply Jury's criterion on the
 polynomial
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-A safety specification leads to a requirement on the states of
-the model. Consequently, the controller must ensure that the state
-never violates the requirement.  In~this work, the safety property is
-expressed as:
+
+A safety specification leads to a requirement on the states of the model. 
+Consequently, the controller must ensure that the state never violates the
+requirement.  In~this work, the safety property is expressed as:
 %
@@
 
-Furthermore, it is practically relevant to consider the 
-constraints $\phi_\mathit{input}$ on the input
-signal $u_{k}$ and $\phi_\mathit{init}$ on the initial states $x_0$,
-which we assume have given bounds, namely 
-$\phi_\mathit{input} := \underline{u} \leq u_k \leq \overline{u}$, 
-which comes from physical restrictions in the energy of the system; and
-$\phi_\mathit{init}\equiv \mat{G}' \vec{x}_0 \leq \vec{h}'$,
-where $\mat{G}'$ and $\vec{h}'$ limits the initial conditions of the model.
+Furthermore, it is practically relevant to consider the constraints
+$\phi_\mathit{input}$ on the input signal $u_{k}$ and $\phi_\mathit{init}$
+on the initial states $x_0$, which we assume have given bounds, namely
+$\phi_\mathit{input} := \underline{u} \leq u_k \leq \overline{u}$, which
+comes from physical restrictions in the energy of the system; and
+$\phi_\mathit{init}\equiv \mat{G}' \vec{x}_0 \leq \vec{h}'$, where
+$\mat{G}'$ and $\vec{h}'$ limits the initial conditions of the model.
 
@@
 %-------------------------------
-In many cases the response time of the system, i.e. how fast it converges to the set point, is a requirement of great importance. 
-This is given as a ``settling time.''
+
+In many cases the response time of the system, i.e.  how fast it converges
+to the set point, is a requirement of great importance.  This is given as a
+``settling time''.
 
 \begin{theorem}
-Given a set of eigenvalues for a discrete time model of a $p^{th}$ order stable system $\{\lambda_i =e^{\omega_i} \mid i \in [1, ...\,,p], |\lambda_i| \leq 1 \}$, the settling time of the system is upper-bounded by
+%
+Given a set of eigenvalues for a discrete time model of a $p^{th}$ order
+stable system $\{\lambda_i =e^{\omega_i} \mid i \in [1, ...\,,p],
+|\lambda_i| \leq 1 \}$, the settling time of the system is upper-bounded by
+%
 \begin{equation}
@@
 \end{equation}
-where $0\leq P_s \leq 1$ is the desired portion of the target within which the output must remain after $t_s$.  For the proof see Appendix~\ref{sec:proofs}
+%
+where $0\leq P_s \leq 1$ is the desired portion of the target within which
+the output must remain after $t_s$.  For the proof see
+Appendix~\ref{sec:proofs}
+%
 \end{theorem}
@@
 
-In this section, we describe our technique for synthesizing safe
-digital feedback controllers using CEGIS. Broadly speaking, CEGIS
-denotes an iterative technique where each step performs inductive
-generalization based on counterexamples provided by a verification
-engine. In each iteration, an inductive synthesizer produces a
-candidate solution that obeys the specification for a limited number
-of inputs. Subsequently, this candidate is passed to a verification
-phase that checks it against the specification for all possible
-inputs. If the verification fails, then the witness counterexample is
-passed back to the synthesis phase, where it is added to the set of
-inputs to be considered in the next loop iteration. Otherwise, the process terminates.
+In this section, we describe our technique for synthesizing safe digital
+feedback controllers using CEGIS.  Broadly speaking, CEGIS denotes an
+iterative technique where each step performs inductive generalization based
+on counterexamples provided by a verification engine.  In each iteration, an
+inductive synthesizer produces a candidate solution that obeys the
+specification for a limited number of inputs.  Subsequently, this candidate
+is passed to a verification phase that checks it against the specification
+for all possible inputs.  If the verification fails, then the witness
+counterexample is passed back to the synthesis phase, where it is added to
+the set of inputs to be considered in the next loop iteration.  Otherwise,
+the process terminates.
 
@@
 %The CEGIS-OR loop for this approach is described next.
-Throughout the CEGIS-OR loop we make use of a specification $\phi$ that deals with the abstraction of the model dynamics.
-Note that since the model abstraction gets refined at each iteration, 
-$\phi$ will also be adjusted accordingly.
-Initially, $\phi$ is simply given as the defined 
-$\phi := \phi_{stability} \wedge \phi_{input} \wedge \phi_{init}$.
+
+Throughout the CEGIS-OR loop we make use of a specification $\phi$ that
+deals with the abstraction of the model dynamics.  Note that since the model
+abstraction gets refined at each iteration, $\phi$ will also be adjusted
+accordingly.  Initially, $\phi$ is simply given as the defined $\phi :=
+\phi_{stability} \wedge \phi_{input} \wedge \phi_{init}$.
 
@@
 
-Note that there is a major difference between
-the way $\phi$ is being used in different phases in Figure~\ref{fig:CEGIS-OR}: while the
-{\sc synthesize} phase checks $\phi$ by using the plant precision
-$\mathbb{R}_{\langle P \rangle}$ for the controller, observer and
-plant, the {\sc model} and {\sc verify} phases use infinite precision ($\mathbb{R}$) to represent
-the plant and $\mathbb{R}_{\langle C \rangle}$ for the controller and
-the observer. The reason for this is that, as we want the
-synthesis to be fast, we allow it to generate unsound results
-and we restore soundness during the verification and modeling stages. 
-Since we use different precisions at different stages, we will often use $\mat{K}$ and $\mat{L}$ to indicate that the domain they belong to is unspecified
-(these are always truncated to the corresponding domain at each stage).
+Note that there is a major difference between the way $\phi$ is being used
+in different phases in Figure~\ref{fig:CEGIS-OR}: while the {\sc synthesize}
+phase checks $\phi$ by using the plant precision $\mathbb{R}_{\langle P
+\rangle}$ for the controller, observer and plant, the {\sc model} and {\sc
+verify} phases use infinite precision ($\mathbb{R}$) to represent the plant
+and $\mathbb{R}_{\langle C \rangle}$ for the controller and the observer. 
+The reason for this is that, as we want the synthesis to be fast, we allow
+it to generate unsound results and we restore soundness during the
+verification and modeling stages.  Since we use different precisions at
+different stages, we will often use $\mat{K}$ and $\mat{L}$ to indicate that
+the domain they belong to is unspecified (these are always truncated to the
+corresponding domain at each stage).
+%
 %% While these specifications are updated throughout the synthesis process (as appropriately described below), at all times $\phi_{static} \models \phi_{synth}$.
@@
 
-In the second stage, we take the complex eigenvalue
-with the largest angle ($\max\{|\tan^{-1}\left(\frac{im(\lambda)}{re(\lambda)}\right)| \mid \lambda \in \Lambda\}$)
-and reduce its imaginary component only  ($re(\lambda) + f\, im(\lambda)$ such that the new controller satisfies $\phi_\mathit{init}^K$).
-The process ends when no imaginary part can be further reduced.
-The resulting closed loop form converges faster than the original and has a
-smaller rotation, which facilitates meeting the safety specification $\phi_\mathit{safety}$.
-
-We must point out that the optimizer tool uses infinite precision for the plant, and
-may therefore find solutions that the synthesizer cannot, due to the use of limited precision.
-If we cannot optimize the candidate  we signal the {\sc Abstract} phase to 
-use the updated $\phi$ and request {\sc Synthesize} to produce a new
-candidate.  Otherwise the optimized candidate solution is given back to
-{\sc Verify Synthesis}.
+In the second stage, we take the complex eigenvalue with the largest angle
+($\max\{|\tan^{-1}\left(\frac{im(\lambda)}{re(\lambda)}\right)| \mid \lambda
+\in \Lambda\}$) and reduce its imaginary component only ($re(\lambda) + f\,
+im(\lambda)$ such that the new controller satisfies $\phi_\mathit{init}^K$). 
+The process ends when no imaginary part can be further reduced.  The
+resulting closed loop form converges faster than the original and has a
+smaller rotation, which facilitates meeting the safety specification
+$\phi_\mathit{safety}$.
+
+We must point out that the optimizer tool uses infinite precision for the
+plant, and may therefore find solutions that the synthesizer cannot, due to
+the use of limited precision.  If we cannot optimize the candidate we signal
+the {\sc Abstract} phase to use the updated $\phi$ and request {\sc
+Synthesize} to produce a new candidate.  Otherwise the optimized candidate
+solution is given back to {\sc Verify Synthesis}.
 
@@
 
-The benchmark suite employed to evaluate the proposed technique is 
-composed by seven models extracted from the control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15,maglev,converters}.
-In order to obtain statistically relevant results, we have taken these models
-and modified each possible combination of their parameters by a 10\% tolerance,
-thus creating seven hundred benchmarks from this base.
+The benchmark suite employed to evaluate the proposed technique is composed
+by seven models extracted from the control literature~\cite{acrobot, cstr,
+CHEN1979389, KOKOTOVIC198023, gajic2008optimal, Franklin15, maglev,
+converters}.  In order to obtain statistically relevant results, we have
+taken these models and modified each possible combination of their
+parameters by a 10\% tolerance, thus creating seven hundred benchmarks from
+this base.
+
 %In the verification module, we have used the tool \note{Axelerator~\cite{}}.
@@
 \caption{\label{tab:cegis_results}
-Experimental results. Minimum, and Median times for standard CEGIS vs CEGIS-OR on multiple benchmarks. No. indicates Number of benchmarks,
- t.o.~indicates timeouts (in the median case, it indicates more than half of the benchmarks timed out). The order denotes the number of variables of a model.}
+Experimental results.  Minimum, and Median times for standard CEGIS vs
+CEGIS-OR on multiple benchmarks.  No.  indicates Number of benchmarks,
+t.o.~indicates timeouts (in the median case, it indicates more than half of
+the benchmarks timed out).  The order denotes the number of variables of a
+model.}
+%
 \end{table}
 
-Using the described technique we managed to synthesize controllers for $509$ benchmarks (compared to $290$ found by our baseline), with a median time of $16.8$ seconds.
+Using the described technique we managed to synthesize controllers for $509$
+benchmarks (compared to $290$ found by our baseline), with a median time of
+$16.8$ seconds.
+%
 %and the maximum observed synthesis time was under 10 minutes for a $4^{th}$ order system ($8^{th}$ order considering the observer).
-We consider these times short enough to be of practical use to control engineers.
-Regarding the cases for which we fail to find a controller, we note that we use a
-relatively short timeout (5 minutes), so it is possible that longer timeouts would instead lead to a
-valid solution. However, there are cases where a solution may not be found due the
-approximations in the synthesizer that would prevent a true candidate from being found
-or over-approximations in the verifier that may reject a valid candidate.
-It is impossible for us to differentiate these from case where a controller does not exist.
+We consider these times short enough to be of practical use to control
+engineers.  Regarding the cases for which we fail to find a controller, we
+note that we use a relatively short timeout (5 minutes), so it is possible
+that longer timeouts would instead lead to a valid solution.  However, there
+are cases where a solution may not be found due the approximations in the
+synthesizer that would prevent a true candidate from being found or
+over-approximations in the verifier that may reject a valid candidate.  It
+is impossible for us to differentiate these from case where a controller
+does not exist.
 
 In order to show the improvements due to our optimization-enhanced CEGIS, we
-compared our approach against a standard CEGIS procedure.  For the majority of
-our benchmarks, we observe that our approach is significantly faster than
-standard CEGIS. We further note that the number of times standard CEGIS times
-out is much larger than CEGIS-OR which results in more found solutions.e
+compared our approach against a standard CEGIS procedure.  For the majority
+of our benchmarks, we observe that our approach is significantly faster than
+standard CEGIS.  We further note that the number of times standard CEGIS
+times out is much larger than CEGIS-OR which results in more found
+solutions.
 
@@
 CEGIS-OR shows promise in exploiting modularity for improved response. 
-It however relies on the use of application-specific optimization, 
-which requires adequate tools for exploring different types of properties.  
-Our results show significant improvement in terms of scalability over standard CEGIS approaches, 
-with an ability to explore complex properties, hence many synthesis tasks may be tackled with it. 
-In particular we note that our synthesis loop is more efficient for
-models where the solution space is formed by connected spaces where
-optimization algorithms or localized synthesis are likely to be more
-efficiently than global synthesis. 
-Finally our application to control synthesis provides a solid proof
-of concept for scalable optimal control synthesis of LTI systems.
-
-There is still a need to extend CEGIS-OR to MIMO models and to analyze more general properties, 
-which may also require exploring other optimization methods for control systems.
+It~however relies on the use of application-specific optimization, which
+requires adequate tools for exploring different types of properties.  Our
+results show significant improvement in terms of scalability over standard
+CEGIS approaches, with an ability to explore complex properties, hence many
+synthesis tasks may be tackled with it.  In particular we note that our
+synthesis loop is more efficient for models where the solution space is
+formed by connected spaces where optimization algorithms or localized
+synthesis are likely to be more efficiently than global synthesis.  Finally
+our application to control synthesis provides a solid proof of concept for
+scalable optimal control synthesis of LTI systems.
+
+There is still a need to extend CEGIS-OR to MIMO models and to analyze more
+general properties, which may also require exploring other optimization
+methods for control systems.
 
@@
 
-In embedded software programs interacting and/or simulating physical plants it
-is of great importance to understand the effects of the chosen numeric
-representation for the continuous state-space. 
-These representations are almost invariably approximations to the original which
-are assumed to be precise enough as to not cause any trouble, but it is precisely
-this assumption that often results in the most difficult and dangerous errors.
-There are generally speaking two paradigms for representing numbers in programs:
-fixed and variable precision numbers.  We refer to both of these as finite word
-length representations (FWL).  In fact, these subdivide into multiple data types
-such as integer bit-vectors, fixed or floating point numbers and rationals). In 
-this section we will be discussing fixed and floating point numbers.
-On one hand, we have variable word length types which will attempt to use as
-much memory as needed to precisely represent the original domain (usually the
-reals). In this case the limitations are caused by memory and speed, both of
-which are directly affected by the increasingly larger word lengths. Multiple
-Precision Floating Point Arithmetic and Software Rationals are good examples of
-these cases. It is possible for some of these data types to have memory
-constraints, at which point they fall into the second category.
-Fixed precision data types are most common in software programs. Whether
-they be Floating Point or Fixed Point (of which integers are the special case
-for 0 decimal places) numbers, the problem arises in the misrepresentation of
-the reals (or equivalent data type being represented).
-Let $\mathbb{R}_{\langle M,F \rangle}$ be a fixed point domain with $M$ bits
-representing the binary word length of the representation and $F$ bits
-representing the pre-scaling $2^{-F}$ (\emph{i.e} the number of bits after
-the decimal place).  We note that a negative $F$ denotes an integer
-multiplication that adds $-F$ trailing zeros in the number represented by
-$M$.
+In embedded software programs interacting and/or simulating physical plants
+it is of great importance to understand the effects of the chosen numeric
+representation for the continuous state-space.  These representations are
+almost invariably approximations to the original which are assumed to be
+precise enough as to not cause any trouble, but it is precisely this
+assumption that often results in the most difficult and dangerous errors. 
+There are generally speaking two paradigms for representing numbers in
+programs: fixed and variable precision numbers.  We refer to both of these
+as finite word length representations (FWL).  In fact, these subdivide into
+multiple data types such as integer bit-vectors, fixed or floating point
+numbers and rationals).  In this section we will be discussing fixed and
+floating point numbers.  On one hand, we have variable word length types
+which will attempt to use as much memory as needed to precisely represent
+the original domain (usually the reals).  In this case the limitations are
+caused by memory and speed, both of which are directly affected by the
+increasingly larger word lengths.  Multiple Precision Floating Point
+Arithmetic and Software Rationals are good examples of these cases.  It is
+possible for some of these data types to have memory constraints, at which
+point they fall into the second category.  Fixed precision data types are
+most common in software programs.  Whether they be Floating Point or Fixed
+Point (of which integers are the special case for 0 decimal places) numbers,
+the problem arises in the misrepresentation of the reals (or equivalent data
+type being represented).  Let $\mathbb{R}_{\langle M,F \rangle}$ be a fixed
+point domain with $M$ bits representing the binary word length of the
+representation and $F$ bits representing the pre-scaling $2^{-F}$
+(\emph{i.e} the number of bits after the decimal place).  We note that a
+negative $F$ denotes an integer multiplication that adds $-F$ trailing zeros
+in the number represented by~$M$.
+%
 %Let also $\mathbb{R}_{\langle M,[E] \rangle}$ be a floating point
@@
 \end{enumerate}
-We note here that not all systems truncate equally.  In the
-definition above $\delta$ may be positive or negative, and even this
-decision can be made dependent on the sign of $x$.  Common cases in computer
-systems are: round downwards (\emph{ie} to $-\infty$), round upwards
-(\emph{ie} to $+\infty$), and round to zero.  Rounding errors are cumulative
-which means the overall error will statistically increase with every
-operation, thus single transition algorithms can be more precise in this
-respect than iterative ones because they perform fewer operations needing
-rounding.
+%
+We note here that not all systems truncate equally.  In the definition above
+$\delta$ may be positive or negative, and even this decision can be made
+dependent on the sign of $x$.  Common cases in computer systems are: round
+downwards (\emph{ie} to $-\infty$), round upwards (\emph{ie} to $+\infty$),
+and round to zero.  Rounding errors are cumulative which means the overall
+error will statistically increase with every operation, thus single
+transition algorithms can be more precise in this respect than iterative
+ones because they perform fewer operations needing rounding.
+
 \item Overflow\\
-Another source of error introduced by FWL representations is that of overflow.
-The finite word length set a maximum representable number in the domain
-$\pm \overline{M} \text{ where }  \overline{M}=2^{M-F}-2^{-F}$, which means that any number
-outside this range cannot be accurately represented by the domain (\emph{eg} $\delta=x-\overline{M}$).
-In the case of floating point, a special cases for infinity has been introduced, which addresses
-some of these issues, but once the error has gone to infinity, the numbers become meaningless.
-It is the responsibility of software designers and tools to account for overflows and either
-supply saturation functions to prevent them or raise alarms in their presence. In the case
-of verification, the latter is seen as a safety problem.
+%
+Another source of error introduced by FWL representations is that of
+overflow.  The finite word length set a maximum representable number in the
+domain $\pm \overline{M} \text{ where } \overline{M}=2^{M-F}-2^{-F}$, which
+means that any number outside this range cannot be accurately represented by
+the domain (\emph{eg} $\delta=x-\overline{M}$).  In the case of floating
+point, a special cases for infinity has been introduced, which addresses
+some of these issues, but once the error has gone to infinity, the numbers
+become meaningless.  It is the responsibility of software designers and
+tools to account for overflows and either supply saturation functions to
+prevent them or raise alarms in their presence.  In the case of
+verification, the latter is seen as a safety problem.
+%
 \end{enumerate}
 
-We will use the domain $\mathbb{R}_{\langle C \rangle} \text{ where } \langle C \rangle = \langle M_c,F_c \rangle$
-to represent a digital implementation of LTI dynamics which we will refer to as the controller, and 
-$\mathbb{R}_{\langle P \rangle} \supseteq \mathbb{R}_{\langle C \rangle}$
-to represent the domain of a digital model of the dynamics of a real plant when evaluated by a verification tool.
-Furthermore, we will refer to the errors incurred by the calculations performed in these domains as finite word length (FWL) effects.
+We will use the domain $\mathbb{R}_{\langle C \rangle} \text{ where }
+\langle C \rangle = \langle M_c,F_c \rangle$ to represent a digital
+implementation of LTI dynamics which we will refer to as the controller, and
+$\mathbb{R}_{\langle P \rangle} \supseteq \mathbb{R}_{\langle C \rangle}$ to
+represent the domain of a digital model of the dynamics of a real plant when
+evaluated by a verification tool.  Furthermore, we will refer to the errors
+incurred by the calculations performed in these domains as finite word
+length (FWL) effects.
 
@@
 During any given ADC conversion, the continuous signal will be sampled in
-the real domain and transformed by $\mathcal{F}_{\langle A \rangle}
-(x)$. This sampling uses a threshold which is defined by the
-less significant bit ($q_{a}=2^{-F_a}$) 
-of the ADC and some non-linearities of the circuitry.  The overall conversion is
+the real domain and transformed by $\mathcal{F}_{\langle A \rangle} (x)$. 
+This sampling uses a threshold which is defined by the less significant bit
+($q_{a}=2^{-F_a}$) of the ADC and some non-linearities of the circuitry. 
+The overall conversion is
 %
@@
 %
-where $t = kT_s$, and $T_s$ is the sampling time and $k$ the current iteration of the loop.
-If we denote the error in the conversion by $\nu_k=y_k-y(t)$, then we may define
-some bounds for it $\nu_k \in [-\frac{q_{a}}{2}, \frac{q_{a}}{2}]$.
+where $t = kT_s$, and $T_s$ is the sampling time and $k$ the current
+iteration of the loop.  If we denote the error in the conversion by
+$\nu_k=y_k-y(t)$, then we may define some bounds for it $\nu_k \in
+[-\frac{q_{a}}{2}, \frac{q_{a}}{2}]$.
 
@@
 ADC is that of the digital controller (i.e, the quantizer includes a digital
-gain added in the code resulting in $\mathbb{R}_{\langle A \rangle}=\mathbb{R}_{\langle C \rangle}$).
-The process of quantization in the DAC is
-similar except that it is calculating $\mathcal{F}_{\langle D\rangle}
-(\mathcal{F}_{\langle C \rangle} (x)) $.  If these domains
-are the same ($\mathbb{R}_{\langle D \rangle}=\mathbb{R}_{\langle C \rangle}$), or if the DAC
-resolution in higher than the ADCs ($\mathbb{R}_{\langle D \rangle}\supseteq\mathbb{R}_{\langle C \rangle}$), then the DAC quantization error is equal
-to zero.  From the above equations we can now define the ADC and DAC
-quantization noises ${\nu_1}_k \in [-\frac{q_a}{2}, \frac{q_a}{2}]$ and
-${\nu_2}_k \in [-\frac{q_d}{2}, \frac{q_d}{2}]$, where given the above assumptions $q_d=q_a=q_c$. 
-This is illustrated in Figure \ref{fig:observersystem} where $Q_1$ is the quantizer of the ADC
-and $Q_2$ the quantizer for the DAC.  These bounds hold irrespective of
-whether the noise is correlated, hence we may use them to over-approximate
-the noise effect on the state space progression over time.  The
-resulting dynamics are
+gain added in the code resulting in $\mathbb{R}_{\langle A
+\rangle}=\mathbb{R}_{\langle C \rangle}$).  The process of quantization in
+the DAC is similar except that it is calculating $\mathcal{F}_{\langle
+D\rangle} (\mathcal{F}_{\langle C \rangle} (x)) $.  If these domains are the
+same ($\mathbb{R}_{\langle D \rangle}=\mathbb{R}_{\langle C \rangle}$), or
+if the DAC resolution in higher than the ADCs ($\mathbb{R}_{\langle D
+\rangle}\supseteq\mathbb{R}_{\langle C \rangle}$), then the DAC quantization
+error is equal to zero.  From the above equations we can now define the ADC
+and DAC quantization noises ${\nu_1}_k \in [-\frac{q_a}{2}, \frac{q_a}{2}]$
+and ${\nu_2}_k \in [-\frac{q_d}{2}, \frac{q_d}{2}]$, where given the above
+assumptions $q_d=q_a=q_c$.  This is illustrated in Figure
+\ref{fig:observersystem} where $Q_1$ is the quantizer of the ADC and $Q_2$
+the quantizer for the DAC.  These bounds hold irrespective of whether the
+noise is correlated, hence we may use them to over-approximate the noise
+effect on the state space progression over time.  The resulting dynamics are
 %
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Control theory} \label{sec:control_theory}
+\section{Control theory}\label{sec:control_theory}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 A feedback system is one where the output is fed back into the input, thus
-making part or all of the system a closed system (i.e. no inputs).
-Such a system is exemplified in figure \ref{fig:observersystem}.  Since the
+making part or all of the system a closed system (i.e.  no inputs).  Such a
+system is exemplified in Figure~\ref{fig:observersystem}.  Since the
 feedback line creates a loop in the diagram this is known as a closed loop,
-and the overall behavior of the resulting system is said to have closed loop dynamics.
-The feedback may be direct or have further transformations, some of which will
-be discussed in this section.  For the moment we will also point out that in the
-models we are interested in, this feedback is digital and thus creates some
-further considerations regarding discretization.
-
-The objective of the feedback is to adhere to some properties we decide to control.
-In most cases these properties include stability.  We define stability as the ability of
-the system output to remain bounded given a bounded input. This is known as BIBO
-stability. Further constraints to this property may be added to enforce stronger stability 
-(e.g. convergent).  Generally speaking, we wish to simplify the model of the system to
-so that the values of the controller can be directly related to the effect they have on the
-dynamics of the closed loop.  Such representation is called a Canonical form and its shape
-and transformation depend on the shape of the controller.  We discuss the requirements
-we are interested in in the following.
+and the overall behavior of the resulting system is said to have closed loop
+dynamics.  The feedback may be direct or have further transformations, some
+of which will be discussed in this section.  For the moment we will also
+point out that in the models we are interested in, this feedback is digital
+and thus creates some further considerations regarding discretization.
+
+The objective of the feedback is to adhere to some properties we decide to
+control.  In most cases these properties include stability.  We define
+stability as the ability of the system output to remain bounded given a
+bounded input.  This is known as BIBO stability.  Further constraints to
+this property may be added to enforce stronger stability (e.g.  convergent). 
+Generally speaking, we wish to simplify the model of the system to so that
+the values of the controller can be directly related to the effect they have
+on the dynamics of the closed loop.  Such representation is called a
+Canonical form and its shape and transformation depend on the shape of the
+controller.  We discuss the requirements we are interested in in the
+following.
 
@@
 \end{align}
-
-where the coefficients $a_i$ describe the characteristic polynomial of the system. This matrix shape is
-called a Controllable Canonical Form because the dynamics of the feedback are directly related to these
-coefficients. Specifically, given a feedback controller $\mat{K}_c$ for any particular system, the closed loop dynamics
-are
+%
+where the coefficients $a_i$ describe the characteristic polynomial of the
+system.  This matrix shape is called a Controllable Canonical Form because
+the dynamics of the feedback are directly related to these coefficients. 
+Specifically, given a feedback controller $\mat{K}_c$ for any particular
+system, the closed loop dynamics are
+%
 \begin{align}
@@
 \end{align}
-which means we can directly modify each coefficient by selecting a controller parameter.
-
-Any LTI system can be transformed into a controllable canonical form by a matrix $\mat{T}_c$ such that $\vec{x}=\mat{T}_c\hat{\vec{x}}$
-Then the dynamics of the controllable form are
+%
+which means we can directly modify each coefficient by selecting a
+controller parameter.
+
+Any LTI system can be transformed into a controllable canonical form by a
+matrix $\mat{T}_c$ such that $\vec{x}=\mat{T}_c\hat{\vec{x}}$ Then the
+dynamics of the controllable form are
+%
 \begin{align*}
@@
 
-A discrete-time LTI system as \eqref{eq:closeloopdynamics} is
-asymptotically stable if all the roots of its characteristic
-polynomial (i.e., the eigenvalues of the closed-loop matrix $A_d - B_d
-K$) are inside the unity circle of the complex plane, i.e., their
-absolute values are strictly less than one~\cite{astrom1997computer}
-(this simple sufficient condition can be generalized, however this is
-not necessary in our work).  In this work, we express this stability
-specification $\phi_\mathit{stability}$ in terms of a check known as
-\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic
-formula to select the entries of matrix $K$ so that the closed-loop
-dynamics are shaped as desired.
+A discrete-time LTI system as \eqref{eq:closeloopdynamics} is asymptotically
+stable if all the roots of its characteristic polynomial (i.e., the
+eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
+circle of the complex plane, i.e., their absolute values are strictly less
+than one~\cite{astrom1997computer} (this simple sufficient condition can be
+generalized, however this is not necessary in our work).  In this work, we
+express this stability specification $\phi_\mathit{stability}$ in terms of a
+check known as \emph{Jury's criterion}~\cite{fadali}: this is an easy
+algebraic formula to select the entries of matrix $K$ so that the
+closed-loop dynamics are shaped as desired.
 
@@
 \begin{proof}
-Let $\mat{K}$ be a feedback controller such that $\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$. Let the output of
-the feedback system be a zero order holder such that $\vec{u}(t'+kT_s)=\vec{u}(kT_s), \text{ for }  0 \leq t' < T_s$.
-The closed loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
+%
+Let $\mat{K}$ be a feedback controller such that
+$\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$.  Let the output of the
+feedback system be a zero order holder such that
+$\vec{u}(t'+kT_s)=\vec{u}(kT_s), \text{ for } 0 \leq t' < T_s$.  The closed
+loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
+%
 \begin{equation*}
@@
 %
-In the case of closed loop forms without geometric multiplicity (which is by far the most common case),
-the right hand terms disappear and we obtain
+In the case of closed loop forms without geometric multiplicity (which is by
+far the most common case), the right hand terms disappear and we obtain
 %
@@
 
-Hence the overall decay of the system is always smaller
-than $d=e^{-|\overline{\omega}| t}$ where $0\leq d\leq 1$ is the remaining
+Hence, the overall decay of the system is always smaller than
+$d=e^{-|\overline{\omega}| t}$ where $0\leq d\leq 1$ is the remaining
 percentage of the decay expressed.  Reversing we have
 $t=-\frac{ln(d)}{|\overline{\omega}|}=-\frac{ln(d)}{ln(\overline{\lambda})}$. 
-replacing for $p_s$ , $t_s$, and $\overline{\lambda}$ we get equation
-\eqref{eq:set_time}
-%
-
-In the case where we allow for geometric multiplicities, we need to compensate for
-the effects of $\binom{k}{j}$ \footnote{tighter bounds can be achieved by evaluating $\frac{\sum\limits_{j=1}^{gm(i)}c_{i+j}\binom{k}{j} \lambda_i^{-j}{\vec{x}_0}_j}{\sum\limits_{j=1}^{gm(i)}c_{i+j}{\vec{x}_0}_j}$}.
-We recall here that our interest is to reach
-within $10\%$ of the final value, and that for a given $k>\underline{k}$ the
-term $\lambda^k$ will converge faster than $\binom{k}{j}$ diverges.
-The requirements for $|\overline{\omega}|$ are calculated as follows:
+replacing for $p_s$ , $t_s$, and $\overline{\lambda}$ we get
+equation~\eqref{eq:set_time}.
+%
+
+In the case where we allow for geometric multiplicities, we need to
+compensate for the effects of $\binom{k}{j}$ \footnote{tighter bounds can be
+achieved by evaluating $\frac{\sum\limits_{j=1}^{gm(i)}c_{i+j}\binom{k}{j}
+\lambda_i^{-j}{\vec{x}_0}_j}{\sum\limits_{j=1}^{gm(i)}c_{i+j}{\vec{x}_0}_j}$}. 
+We recall here that our interest is to reach within $10\%$ of the final
+value, and that for a given $k>\underline{k}$ the term $\lambda^k$ will
+converge faster than $\binom{k}{j}$ diverges.  The requirements for
+$|\overline{\omega}|$ are calculated as follows:
+%
 \begin{itemize}

### 2018-01-31 TACAS2018/paper.tex
cite package
wording intro

@@
 \usepackage{mathtools}
+\usepackage{cite}
 
@@
 life sciences, environmental control and robotics~\cite{astrom1997computer,
-Franklin15}.  Correct synthesis is non-trivial, even in cases with
-restricted dynamics.  We examine the case of Linear Time Invariant (LTI)
-models, for which the synthesis of controllers is well understood.  However,
-the use of digital control architectures adds new challenges caused by
-artifacts specific to digital control, such as the effects of
-finite-precision arithmetic (referred to here as Finite Word Length or FWL
-effects), time discretization and quantization errors introduced by A/D and
-D/A conversion.
+Franklin15}.  Correct synthesis of control software for such platforms is
+non-trivial, even in cases with restricted dynamics.  We consider the case
+of Linear Time Invariant (LTI) models, for which the synthesis of
+controllers is well understood.  However, the use of digital control
+architectures adds new challenges caused by artifacts specific to digital
+control, such as the effects of finite-precision arithmetic (referred to
+here as Finite Word Length or FWL effects), time discretization and
+quantization errors introduced by A/D and D/A conversion.
 
@@
 approaches in that it explores the continuous space of the system to
-synthesize correct by construction minimal digital controllers.  Contrary to
-LTL models that require thousands of states and elaborate algorithms to
-implement \cite{reissig2017feedback}, these PID-like controllers are
-represented by a few parameters and only require a few lines of code, thus
+synthesize correct-by-construction minimal digital controllers.  In contrast
+to LTL models, which require thousands of states and elaborate algorithms to
+implement~\cite{reissig2017feedback}, these PID-like controllers are
+represented by a few parameters and only require few lines of code, thus
 reducing the implementation cost and execution time while remaining
@@
 (i.e., where all the states are known) modeled in discrete time, and
-furthermore explores only a limited set of properties that engineers are
-interested in.  Conversely, in most real implementations, the internal state
-of a plant cannot be directly measured but rather inferred from its effect
-on the output.  A plant model that minimizes the difference between its
-output and the real plant output is called an observer and it is a well
-known paradigm in the control literature~\cite{astrom1997computer}.
+furthermore explores only a subset of the properties that engineers are
+interested in.  By contrast, in most real implementations, the internal
+state of a plant cannot be directly measured but has to be inferred from its
+effect on the output.  A plant model that minimizes the difference between
+its output and the real output of the plant is called an \emph{observer} and
+it is a well known paradigm in the control
+literature~\cite{astrom1997computer}.
 
@@
 By~combining state-of-the-art synthesis and verification engines we
-automatically generate digital observer controllers for a given continuous
-plant model that are correct by construction.  %% This approach delivers a high
+automatically generate digital \emph{observer controllers} for a given
+continuous plant model that are correct by construction.
+%
+%% This approach delivers a high
 %% degree of automation, promises to reduce the cost and time of development of

### 2018-01-31 TACAS2018/paper.tex
wording

@@
 exhibits continuous behavior whereas the controller operates in discrete
-time and over a quantized domain.  Our model evaluates the effects of the
+time and over a quantized domain.  Our model incorporates the effects of the
 quantizers (A/D and D/A converters) and of time discretization, as well as
 representation errors introduced by modeling artifacts such as an
-observer~\cite{astrom1997computer} in a finite precision domain, while
-reasoning about high level properties such as stability, robustness, safety,
+observer~\cite{astrom1997computer} in a finite-precision domain, while
+reasoning about high-level properties such as stability, robustness, safety,
 and response time, which define the behavior of the system.  In particular,
@@
 inputs.  By using abstraction refinement, CEGIS-OR allows us to handle
-complex systems which are initially represented by coarse abstractions that
+complex systems, which are initially represented by coarse abstractions that
 only get refined on demand.  Consequently, solutions that do not require a
 high level of precision are obtained fast.  Since the use of coarse
-abstractions may result in low-quality candidate solutions (i.e.  candidates
-that fail the specification on a very large number of inputs), after each
-inductive generalization phase we use optimization techniques to improve the
-produced candidates.  In particular, our optimization procedure aims at
-reducing the size of the reach space of the closed loop system, while
-maintaining other dynamical properties of interest (safety, stability, and
-response time).
+abstractions may result in low-quality candidate solutions (i.e., candidates
+that fail the specification on a very large number of inputs), we use
+optimization techniques after each inductive generalization phase to improve
+the produced candidates.  In particular, our optimization procedure reduces
+the size of the reach space of the closed loop system, while maintaining
+other dynamical properties of interest (safety, stability, and response
+time).
 
@@
 
-We provide experimental results showing that our approach is able to
-efficiently synthesize safe controllers for a set of physical
-plant models taken from the digital control literature.
+We provide experimental results that show that our approach is able to
+efficiently synthesize safe controllers for a set of physical plant models
+taken from the digital control literature.
 
@@
 \begin{enumerate}
+%
 \item We develop a model for inductive synthesis that combines CEGIS with
@@
  continuous-discrete time/space. 
+%
 % Sound tools for continuous time reachability are scarce and to the authors'
@@
 linear dynamics for the digital controller, it avoids problems related to
-finite precision arithmetic, but potentially suffers from state-space
-explosion.  Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same
+finite-precision arithmetic, but potentially suffers from state-space
+explosion.  Moreover, in~\cite{DBLP:conf/emsoft/RavanbakhshS16} the same
 authors use a CEGIS-based approach for synthesizing continuous-time
@@
 The work in~\cite{hscc-paper} synthesizes stabilizing controllers for
-continuous plants
-%given as transfer functions
-by exploiting bit-accurate verification of software-implemented
-digital controllers~\cite{Bessa16} but it is restricted to closed-loop
-systems given as transfer function models.
+continuous plants by exploiting bit-accurate verification of
+software-implemented digital controllers~\cite{Bessa16} but it is restricted
+to closed-loop systems given as transfer function models.
 
@@
 properties available cover more detail.  However, relying on state-space
-discretization \mbox{Pessoa} is likely to incur scalability limitations. 
-Along this research line, \cite{Anta2010,liu16} studies the synthesis of
-digital controllers for continuous dynamics, and \cite{zamani2014} extends
+discretization, \mbox{Pessoa} is likely to incur scalability limitations. 
+Along this research line, \cite{Anta2010, liu16} study the synthesis of
+digital controllers for continuous dynamics, and~\cite{zamani2014} extends
 the approach to the recent setup of Network Control Systems.
@@
 \noindent\textbf{Discretization Effects --}
+%
 The classical approach to control synthesis has often disregarded
@@
 the deviation introduced by FWL does not make the digital system unstable. 
-A~more recent approach~\cite{DBLP:journals/automatica/WuLCC09} uses
+A~more recent approach~\cite{DBLP:journals/automatica/WuLCC09} uses the
 $\mu$-calculus to directly model the digital controller so that the selected
@@
 symbolic execution: to account for rounding errors, an upper bound is
-introduced in the verification phase.  The work in
-\cite{picasso2003stabilization} introduces invariant sets as a mechanism to
-bound the quantization error effect on stabilization as an invariant set
-that always converges toward the controllable set.  Similarly,
-\cite{liberzon2003hybrid} evaluates the quantization error dynamics and
-bounds its trajectory to a known region over a finite time period.  This
-technique works for both linear and non-linear systems.
+introduced in the verification phase.  The work
+in~\cite{picasso2003stabilization} introduces invariant sets as a mechanism
+to bound the quantization error effect on stabilization as an invariant set
+that always converges toward the controllable set. 
+Similarly, \cite{liberzon2003hybrid} evaluates the quantization error
+dynamics and bounds its trajectory to a known region over a finite time
+period.  This technique works for both linear and non-linear systems.
 
@@
 \label{eq:ode1}
-\dot{x}(t) = \mat{A}\vec{x}(t)+ \mat{B} \vec{u}(t), \quad \vec{x} \in \mathbb{R}^p, \vec{u} \in \mathbb{R}^q, \mat{A} \in \mathbb{R}^{p \times p}, \mat{B} \in \mathbb{R}^{p \times q},
+\dot{x}(t) = \mat{A}\vec{x}(t)+ \mat{B} \vec{u}(t), \quad 
+\vec{x} \in \mathbb{R}^p, \vec{u} \in \mathbb{R}^q,
+\mat{A} \in \mathbb{R}^{p \times p},
+\mat{B} \in \mathbb{R}^{p \times q},
 \end{align}
@@
 
-We are interested in control systems with an output $\vec{y}$ that is a linear combination of its states and inputs\footnote{Notice that since we can only measure $\vec{y}$, the state-space $\vec{x}$ is not fully observable.}.
+We are interested in control systems with an output $\vec{y}$ that is a
+linear combination of its states and inputs\footnote{Notice that since we
+can only measure $\vec{y}$, the state-space $\vec{x}$ is not fully
+observable.}.
+%
 %, which may restrict the observability of the state-space from the output space.
@@
 \label{eq:ode2}  
-\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t), \vec{y} \in \mathbb{R}^o, \mat{C} \in \mathbb{R}^{o \times p}, \mat{D} \in \mathbb{R}^{o \times q}. 
+\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t),
+\vec{y} \in \mathbb{R}^o,
+\mat{C} \in \mathbb{R}^{o \times p},
+\mat{D} \in \mathbb{R}^{o \times q}. 
 \end{equation}
@@
 %where $\mat{A}_d=e^\mat{A}$, $\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$,
-$k \in \mathbb N$ is a discrete counter and $\vec{x}_{0}=\vec{x}(0)$ is the initial state. 
-In this work we raise the standard assumption that $\mat{D}=\mat{0}$ \cite{Astrom08}.  
+%
+$k \in \mathbb N$ is a discrete counter and $\vec{x}_{0}=\vec{x}(0)$ is the
+initial state.  In this work we raise the standard assumption that
+$\mat{D}=\mat{0}$~\cite{Astrom08}.
+%
 %Also, since $\vec{y}$ can be directly derived from $\vec{x}$, we will omit discussing it in the following unless strictly necessary.
@@
 %
-The traces of model \eqref{eq:plant}, 
-starting from an initial set $X_0\subseteq \mathbb{R}^p$, 
-with inputs taken from the set $U \subseteq \mathbb{R}^q$, are sequences 
+The traces of model \eqref{eq:plant}, starting from an initial set
+$X_0\subseteq \mathbb{R}^p$, with inputs taken from the set $U \subseteq
+\mathbb{R}^q$, are sequences
 $ \vec{x}_0 \xrightarrow{\vec{u}_0} \vec{x}_1 \xrightarrow{\vec{u}_1} \vec{x}_2 \xrightarrow{\vec{u}_2} \ldots $, 
@@
 %
-We generalize this notation to convex sets of initial conditions and inputs ($X_0$ and $U$, respectively), 
-and write $\tau(X_0,U)$ to denote the set of states $\{\vec{x} \mid \vec{x} = \tau(\vec{x}_0,\vec{u}),\, \vec{x}_0 \in
-X_0,\, \vec{u} \in U \}$
-reached from $X_0$ by $\tau$ in one step. 
-%
-We furthermore define the $n$-reach set $\tau^n(X_0,U)$ as the set of states reached from
-$X_0$ via $\tau$ in $n$ steps.
+We generalize this notation to convex sets of initial conditions and inputs
+($X_0$ and $U$, respectively), and write $\tau(X_0,U)$ to denote the set of
+states $\{\vec{x} \mid \vec{x} = \tau(\vec{x}_0,\vec{u}),\, \vec{x}_0 \in
+X_0,\, \vec{u} \in U \}$ reached from $X_0$ by $\tau$ in one step.
+%
+We furthermore define the $n$-reach set $\tau^n(X_0,U)$ as the set of states
+reached from $X_0$ via $\tau$ in $n$ steps.
 %
@@
 %
-Since the transformations $\mat{A}$ and $\mat{B}$ are linear and linear transformations preserve convexity~\cite{boyd2004convex}, 
-the sets $X_n = \tau^n(X_0,U)$ are also convex.  
-We define the \emph{$n$-reach tube} as 
+Since the transformations $\mat{A}$ and $\mat{B}$ are linear and linear
+transformations preserve convexity~\cite{boyd2004convex}, the sets $X_n =
+\tau^n(X_0,U)$ are also convex.  We define the \emph{$n$-reach tube} as
+%
 \begin{equation}\label{equ:reachtube}
@@
 \end{equation}
+%
 as the union of $k$-reach sets over $n$ iterations. 
 %
-Finally, the set $\hat{X} =\bigcup_{n\geq 0} \tau^n(X_0,U)$, which we refer to as
-the reach space of the system, generalizes the previous notions over an unbounded
-time horizon (transitive closure).
+Finally, the set $\hat{X} =\bigcup_{n\geq 0} \tau^n(X_0,U)$, which we refer
+to as the reach space of the system, generalizes the previous notions over
+an unbounded time horizon (transitive closure).
 
@@
 
-A closed-loop digital control interconnection with observer is shown in
-Figure~\ref{fig:observersystem}.  The linear feedback controller (bottom
-left) is characterized by a gain matrix $\mat{K}_{\langle C \rangle}$ that
-influences the closed-loop dynamics, and is driven by the observer state
-$\hat{\vec{x}}$.  Moreover, $\vec{y}_e=\hat{\vec{y}} - \vec{y}$ is the error
-on the output estimator,
+A closed-loop digital control interconnection with an observer is
+illustrated in Figure~\ref{fig:observersystem}.  The linear feedback
+controller (bottom left) is characterized by a gain matrix $\mat{K}_{\langle
+C \rangle}$ that influences the closed-loop dynamics, and is driven by the
+observer state $\hat{\vec{x}}$.  Moreover, $\vec{y}_e=\hat{\vec{y}} -
+\vec{y}$ is the error on the output estimator,
+%
 %  defined as the difference between the real output $\vec{y}_k$ and estimated one $\hat{\vec{y}_k}$, 
+%
 which is amplified by a gain matrix $\mat{L}_{\langle C \rangle}$.  Note
@@
 (quantities within this domain are identified by the index $\langle C
-\rangle$), whereas the plant evolves in a continuous domain.  We further
+\rangle$), whereas the plant evolves in a continuous domain.  We~further
 model the effects of using a discrete controller as the noise signals
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- The time discretization in Sec.~\ref{sec:model} only 
- allows us to evaluate the state of the plant at integer multiples of the sample time.
- However, in order to synthesize $\mat{K}=\mat{K}_{\langle C \rangle}$ and $\mat{L}=\mat{L}_{\langle C \rangle}$, 
- we must be able to ensure that certain properties of the plant hold at any given real time.
- In order to do so, 
- we accelerate the dynamics of the plant according to the model semantics in Sec.~\ref{sec:model_semantics} and compute the state $\vec{x}_T$  at a given time $T$, 
+
+The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
+the state of the plant at integer multiples of the sample time.  However, in
+order to synthesize $\mat{K}=\mat{K}_{\langle C \rangle}$ and
+$\mat{L}=\mat{L}_{\langle C \rangle}$, we must be able to ensure that
+certain properties of the plant hold at any given real time.  In order to do
+so, we accelerate the dynamics of the plant according to the model semantics
+in Sec.~\ref{sec:model_semantics} and compute the state $\vec{x}_T$ at a
+given time $T$,
+%
 % namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
-namely the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time $t=T$.
+%
+namely the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time
+$t=T$.
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a linear function of $\vec{x}_0$ as shown below.
-We assume that the system has no inputs, so its dynamics are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.
+%
+Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a
+linear function of $\vec{x}_0$ as shown below.  We assume that the system
+has no inputs, so its dynamics are described by
+$\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.
 
@@
 evaluated at time $T$ is
+%
 \begin{align}
@@
 \end{align}
+%
 $\lambda_i$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.
+%
 %$\vec{x}_T$ is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T. 
@@
 \end{lemma}
+
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- Next, we are interested in studying models with parametric inputs, 
- which are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where $\forall t\geq 0, \vec{u}(t)=\vec{u}$. 
- For such models, a state $\vec{x}_T$ is computed next.
+
+Next, we are interested in studying models with parametric inputs, which are
+described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where
+$\forall t\geq 0, \vec{u}(t)=\vec{u}$.  For such models, a state $\vec{x}_T$
+is computed next.
+%
 \begin{lemma}
-The state of the model $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$ is 
+%
+The state of the model
+$\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a
+parametric input $\vec{u}$ is
+%
 \begin{align}
@@
 \end{align}
- where $\forall t \leq T,\ \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}
- \footnote{When $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$}.
- If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, 
- then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u}) \text{ with } T \in \mathbb{R}_0^+$ (where $\mat{A}_d^{\frac{T}{T_d}} = e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the system at time $T$.
+%
+where $\forall t \leq T,\ \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in
+\eqref{eq:continuous_tube_dyn2} \footnote{When $\mat{A}$ is not invertible,
+we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\
+0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$}. 
+If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that
+$A_d=e^{\mat{A} T_d}$, then
+$\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u})
+\text{ with } T \in \mathbb{R}_0^+$ (where $\mat{A}_d^{\frac{T}{T_d}} =
+e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the
+system at time $T$.
+%
 \end{lemma}
@@
 
-The final case we analyze is that of hybrid-time models, 
-where the plant dynamics evolve in continuous time while the feedback dynamics evolve in discrete time.  
-A new input value is produced only at every sample time but implemented over the continuous-time plant dynamics. 
+The final case we analyze is that of hybrid-time models, where the plant
+dynamics evolve in continuous time while the feedback dynamics evolve in
+discrete time.  A new input value is produced only at every sample time but
+implemented over the continuous-time plant dynamics.
 %

### 2018-01-31 TACAS2018/paper.tex
formatting

@@
 to make claims in the form of candidate solutions about all the possible
-inputs.  By using abstraction refinement, CEGIS-OR allows us to handle
+inputs.  By~using abstraction refinement, CEGIS-OR allows us to handle
 complex systems, which are initially represented by coarse abstractions that

### 2018-01-31 TACAS2018/paper.tex
spacing
rage

@@
 \dot{x}(t) = \mat{A}\vec{x}(t)+ \mat{B} \vec{u}(t), \quad 
-\vec{x} \in \mathbb{R}^p, \vec{u} \in \mathbb{R}^q,
-\mat{A} \in \mathbb{R}^{p \times p},
+\vec{x} \in \mathbb{R}^p, \vec{u} \in \mathbb{R}^q,\,
+\mat{A} \in \mathbb{R}^{p \times p},\,
 \mat{B} \in \mathbb{R}^{p \times q},
@@
 %
-Equations~\eqref{eq:ode1}-\eqref{eq:ode2} are soundly discretized in
+Equations~\eqref{eq:ode1}--\eqref{eq:ode2} are soundly discretized in
 time~\cite{middleton1990digital,van1978computing} at constant intervals,

### 2018-01-31 TACAS2018/paper.tex
nudge

@@
 %
-Equations~\eqref{eq:ode1}--\eqref{eq:ode2} are soundly discretized in
+Equations~\eqref{eq:ode1} and \eqref{eq:ode2} are soundly discretized in
 time~\cite{middleton1990digital,van1978computing} at constant intervals,

### 2018-01-31 TACAS2018/paper.tex
wording

@@
 %
-$k \in \mathbb N$ is a discrete counter and $\vec{x}_{0}=\vec{x}(0)$ is the
-initial state.  In this work we raise the standard assumption that
+where $k \in \mathbb N$ is a discrete counter and $\vec{x}_{0}=\vec{x}(0)$
+is the initial state.  In this work we apply the standard assumption that
 $\mat{D}=\mat{0}$~\cite{Astrom08}.
@@
 \mathbb{R}^q$, are sequences
-$ \vec{x}_0 \xrightarrow{\vec{u}_0} \vec{x}_1 \xrightarrow{\vec{u}_1} \vec{x}_2 \xrightarrow{\vec{u}_2} \ldots $, 
-%
-where $ \vec{x}_0 \in X_0$ and $\forall k\geq 0, \vec{u}_k \in U \text{ and } \vec{x}_{k+1} = \tau(\vec{x}_k,\vec{u}_k) $, 
+%
+$ \vec{x}_0 \xrightarrow{\vec{u}_0} \vec{x}_1 \xrightarrow{\vec{u}_1} \vec{x}_2 \xrightarrow{\vec{u}_2} \ldots $
+%
+where
+%
+$ \vec{x}_0 \in X_0$ and $\forall k\geq 0, \vec{u}_k \in U \text{ and } \vec{x}_{k+1} = \tau(\vec{x}_k,\vec{u}_k) $, 
 where 
@@
 \tau(\vec{x}_k,\vec{u}_k) = %\big\{ 
-\mat{A}\vec{x}_k + \mat{B}\vec{u}_k
+\mat{A}\vec{x}_k + \mat{B}\vec{u}_k \;.
  %\mid \mat{G}\vec{x}_k \leq \vec{h}\big\}\;. 
@@
 
-In many models of real-world control systems, the internal state $x$ cannot
-be directly measured, but is rather inferred from its effect on the measured
-output $\vec{y}$ using an observer~\cite{Astrom08}.  Essentially, a state
+In many real-world control systems the internal state $x$ cannot be directly
+measured, but is rather inferred from its effect on the measured
+output~$\vec{y}$ using an observer~\cite{Astrom08}.  Essentially, a state
 observer is a new dynamical model (with variable denoted as $\hat{\vec{x}}$)
-that provides an estimate of the internal state $x$ of the given model, from
+that provides an estimate of the internal state $x$ of the given model using
 measurements of its inputs and outputs.
@@
 the observer state error), $\nu_2'$ (rounding of the observer state), and
-$\nu_t$ (output delay of the digital system) Lastly, $k_r$ is a reference
+$\nu_t$ (output delay of the digital system).  Finally, $k_r$ is a reference
 gain required by the model.  Our goal in this work is to synthesize both
-$\mat{K}_{\langle C \rangle}$ and $\mat{L}_{\langle C \rangle}$, so that
-specific closed-loop properties of the overall interconnection are
+$\mat{K}_{\langle C \rangle}$ and $\mat{L}_{\langle C \rangle}$ so that
+specific closed-loop properties of the overall system are
 satisfied.

### 2018-01-31 TACAS2018/paper.tex
forall

@@
 $\mat{L}=\mat{L}_{\langle C \rangle}$, we must be able to ensure that
-certain properties of the plant hold at any given real time.  In order to do
-so, we accelerate the dynamics of the plant according to the model semantics
-in Sec.~\ref{sec:model_semantics} and compute the state $\vec{x}_T$ at a
-given time $T$,
+certain properties of the plant hold at any given point in time.  In order
+to do so, we accelerate the dynamics of the plant according to the model
+semantics in Sec.~\ref{sec:model_semantics} and compute the state
+$\vec{x}_T$ at a given time $T$,
 %
@@
 described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where
-$\forall t\geq 0, \vec{u}(t)=\vec{u}$.  For such models, a state $\vec{x}_T$
+$\forall t\geq 0.\,\vec{u}(t)=\vec{u}$.  For such models, a state $\vec{x}_T$
 is computed next.
@@
 %
-where $\forall t \leq T,\ \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in
+where $\forall t \leq T.\, \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in
 \eqref{eq:continuous_tube_dyn2} \footnote{When $\mat{A}$ is not invertible,
@@
 (\emph{i.e.} the largest row norm in $\mat{A}_e$) be the largest error bound
-for any eigenvalue in $\mat{A}_e$.  Then $\forall i \in [1, ...\,,n],
+for any eigenvalue in $\mat{A}_e$.  Then $\forall i \in \{1, \ldots,n\},
 |{\lambda_o}_{i}-\hat{\lambda}_{oi}|<\delta_o$, where ${\lambda_o}_{i}$ are
@@
 \begin{align}
-\phi_\mathit{safety}^n: = & \forall k \in [0, ... , n], \mat{G}\vec{x}_k \leq \vec{h} \text{ and } \underline{y} \leq y_k \leq \overline{y}\nonumber\\
+\phi_\mathit{safety}^n: = & \forall k \in \{0, \ldots , n\},
+  \mat{G}\vec{x}_k \leq \vec{h} \text{ and } \underline{y} \leq y_k \leq \overline{y}\nonumber\\
 \phi_\mathit{safety}: = & \phi_\mathit{safety}^\infty
@@
 \begin{equation}
-t_s<-log_{\overline{\lambda}}({P_s}), \text{ where }  \overline{\lambda} = \max(|\lambda_i|) \text{ and } \overline{\lambda}<1,\ \forall i \in [1, ...\,,p]
+%
+t_s<-log_{\overline{\lambda}}({P_s}), \text{ where }
+  \overline{\lambda} = \max(|\lambda_i|) \text{ and }
+  \overline{\lambda}<1,\ \forall i \in \{1, \ldots,p\}
+%
 \label{eq:set_time}
@@
 \begin{align*}
-\forall j>i, c_{ij}&=\sum_{k=j-i}^\infty \frac{1}{k!}\binom{k}{j-i} \lambda_i^{k-(j-i)}T_1^k\\
+\forall j>i.\, c_{ij}&=\sum_{k=j-i}^\infty \frac{1}{k!}\binom{k}{j-i} \lambda_i^{k-(j-i)}T_1^k\\
 &=\frac{1}{(j-i)!}\sum_{k=j-i}^\infty \frac{1}{(k-(j-i))!} \lambda_i^{k-(j-i)}T_1^k\nonumber\\
@@
 \begin{equation}
-t_s<-log_{\overline{\lambda}}({P_s}), \text{ where }  \overline{\lambda} = \max(|\lambda_i|) \text{ and } \overline{\lambda}<1,\ \forall i \in [1, ...\,,p]
+t_s<-log_{\overline{\lambda}}({P_s}), \text{ where }  \overline{\lambda} = \max(|\lambda_i|) \text{ and } \overline{\lambda}<1,\ \forall i \in \{1, \ldots,p\}
 \label{eq:set_time}

### 2018-01-31 TACAS2018/paper.tex
wording

@@
 we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\
-0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$}. 
+0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$.}. 
 If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that
@@
 dynamics evolve in continuous time while the feedback dynamics evolve in
-discrete time.  A new input value is produced only at every sample time but
+discrete time.  A~new input value is produced only at every sample time but
 implemented over the continuous-time plant dynamics.
@@
 The expression
+%
  \begin{align}
@@
  \end{align}
- with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, $\mat{B}_T$ as in \eqref{eq:continuous_tube_param}, 
- and $\mat{A}_d=\mat{A}_{T_s}, \mat{B}_d=\mat{B}_{T_s}$ describe the discretized plant dynamics with sample time $T_s$, 
- is the state of the model 
+%
+with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, $\mat{B}_T$ as in
+\eqref{eq:continuous_tube_param}, and where $\mat{A}_d=\mat{A}_{T_s},
+\mat{B}_d=\mat{B}_{T_s}$ describe the discretized plant dynamics with
+sample time $T_s$, is the state of the model
+%
 \begin{align*}
@@
  \vec{u}(t)=\mat{K}\vec{x}_k,  \,
- kT_s \leq t < (k+1)T_s. 
+ kT_s \leq t < (k+1)T_s \,. 
 \end{align*}
+%
 For the proof see Appendix~\ref{sec:proofs}
+%
 \end{theorem}
@@
 DAC (See Figure \ref{fig:observersystem}).  In the digital world everything
-takes place at times $t=kT_s, k \in \mathbb{N}$ (discrete time progression),
-and the output signal is delayed at the DAC when fed back to the
-continuous-time domain at time ($t=kT_s+t_d$).
+takes place at times $t=kT_s$ for $k \in \mathbb{N}$ (discrete time
+progression), and the output signal is delayed at the DAC when fed back to
+the continuous-time domain at time ($t=kT_s+t_d$).
 
 \begin{theorem}
-The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a discrete feedback controller for a continuous LTI system can be modeled as a non-deterministic disturbance signal ($\nu_t$ in Figure \ref{fig:observersystem}) upper bounded by
+%
+The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a
+discrete feedback controller for a continuous LTI system can be modeled as a
+non-deterministic disturbance signal ($\nu_t$ in
+Figure~\ref{fig:observersystem}) upper bounded by
+%
 \begin{align}

### 2018-01-31 TACAS2018/paper.tex
wording

@@
 %
-For the proof see Appendix~\ref{sec:proofs}
+For the proof see Appendix~\ref{sec:proofs}.
 %
@@
 representing the binary word length of the representation and $F$ bits
-representing the pre-scaling $2^{-F}$ (\emph{i.e} the number of bits after
+representing the pre-scaling $2^{-F}$ (i.e., the number of bits after
 the decimal place).  We note that a negative $F$ denotes an integer
@@
 Elements in this domain are marked with an underscore~${\langle C \rangle}$
-(see Figure \ref{fig:observersystem}).  Thus, any mathematical operation
+(Figure~\ref{fig:observersystem}).  Thus, any mathematical operation
 within the digital controller is executed in the domain $\mathbb{R}_{\langle
@@
 as classical in Control Theory,  %\footnote{More details on Jury's criterion is in Appendix~\ref{sec:closed_stability}.}, 
-which boils down to a requirement expressed as an algebraic formula on the
+which is given as a requirement expressed as an algebraic formula on the
 characteristic polynomial of the model.  In order to facilitate the use of

### 2018-01-31 TACAS2018/paper.tex
wording

@@
 \end{array}\right], 
-\end{align*}
-}
+\end{align*}}
 %
@@
 expected eigenvalues.  Let $\delta_o=\max(\norm{{\mat{A}_e}_{i,*}}_1)$
-(\emph{i.e.} the largest row norm in $\mat{A}_e$) be the largest error bound
-for any eigenvalue in $\mat{A}_e$.  Then $\forall i \in \{1, \ldots,n\},
+(i.e., the largest row norm in $\mat{A}_e$) be the largest error bound
+for any eigenvalue in $\mat{A}_e$.  Then $\forall i \in \{1, \ldots,n\}.\,
 |{\lambda_o}_{i}-\hat{\lambda}_{oi}|<\delta_o$, where ${\lambda_o}_{i}$ are
@@
 %
-In the case of $\mat{A}_c$, the procedure is the same except that we need to look at the columns shared with $\mat{A}_c$.
-Thus we obtain our bound $\delta_c=\max(\norm{{\mat{A}_e}_{*,i}+{\mat{B}_e}_{*,i}}_1)$
-(\emph{i.e.} the largest column norm in $ \left[\begin{array}{c}\mat{A}_e\\ \mat{B}_e\end{array}\right]$) and
-apply Jury's Criterion over
+In the case of $\mat{A}_c$, the procedure is the same except that we need to
+look at the columns shared with $\mat{A}_c$.  Thus we obtain our bound
+$\delta_c=\max(\norm{{\mat{A}_e}_{*,i}+{\mat{B}_e}_{*,i}}_1)$ (i.e.,
+the largest column norm in $ \left[\begin{array}{c}\mat{A}_e\\
+\mat{B}_e\end{array}\right]$) and apply Jury's Criterion over
 %
@@
 
-In many cases the response time of the system, i.e.  how fast it converges
-to the set point, is a requirement of great importance.  This is given as a
+In many cases the response time of the system, i.e., how fast it converges
+to the set point, is a high-priority requirement.  This is given as a
 ``settling time''.
@@
 Given a set of eigenvalues for a discrete time model of a $p^{th}$ order
-stable system $\{\lambda_i =e^{\omega_i} \mid i \in [1, ...\,,p],
+stable system $\{\lambda_i =e^{\omega_i} \mid i \in \{1, \ldots,p\},
 |\lambda_i| \leq 1 \}$, the settling time of the system is upper-bounded by
@@
 where $0\leq P_s \leq 1$ is the desired portion of the target within which
-the output must remain after $t_s$.  For the proof see
-Appendix~\ref{sec:proofs}
+the output must remain after $t_s$.  The proof is in
+Appendix~\ref{sec:proofs}.
 %
@@
 transformation $\lambda_i'=\frac{\lambda_i}{\overline{\lambda}}$.  We want
-to ensure $\lambda_i' \leq 1$ which can be done by applying Jury's criterion
+to ensure $\lambda_i' \leq 1$, which can be done by applying Jury's criterion
 to $P'(z)=\prod_{i=0}^p (z-\lambda_i')=\sum_{j=0}^p c_j'z^j$ where $c_j'$ are
@@
 %
-where all values are known. Thus, we can ensure that the settling time is smaller than
-a certain magnitude by ensuring that 
-the eigenvalues are smaller too (which we can do with Jury's criterion).
-
-We will use $\phi_{stability}$ to refer to the combined stability and transient response specifications.
+where all values are known.  Thus, we can ensure that the settling time is
+smaller than a certain magnitude by ensuring that the eigenvalues are
+smaller too (which we can do with Jury's criterion).
+
+We will use $\phi_\mathit{stability}$ to refer to the combined stability and
+transient response specifications.
 
@@
 In this section, we describe our technique for synthesizing safe digital
-feedback controllers using CEGIS.  Broadly speaking, CEGIS denotes an
-iterative technique where each step performs inductive generalization based
-on counterexamples provided by a verification engine.  In each iteration, an
-inductive synthesizer produces a candidate solution that obeys the
-specification for a limited number of inputs.  Subsequently, this candidate
-is passed to a verification phase that checks it against the specification
-for all possible inputs.  If the verification fails, then the witness
-counterexample is passed back to the synthesis phase, where it is added to
-the set of inputs to be considered in the next loop iteration.  Otherwise,
-the process terminates.
-
-%
-We enhance the standard CEGIS architecture with an
-abstraction-refinement approach and with optimization, resulting in
-the novel CEGIS-OR (CEGIS with Optimization and Refinement).  By using
-abstraction refinement, CEGIS-OR tackles the scalability issues
-inherent in program synthesis as it allows us to handle complex
-systems, which we coarsely abstract and only refine on demand --
-refinements are triggered by counterexamples returned by the
-verification phase.
+feedback controllers.  We use CEGIS, which is an iterative technique where
+each step performs inductive generalization based on counterexamples
+provided by a verification engine.  In each iteration, an inductive
+synthesizer produces a candidate solution that obeys the specification for a
+limited number of inputs.  Subsequently, this candidate is passed to a
+verification phase that checks it against the specification for all possible
+inputs.  If the verification fails, then the witness counterexample is
+passed back to the synthesis phase, where it is added to the set of inputs
+to be considered in the next loop iteration.  Otherwise, the process
+terminates.
+
+We enhance the standard CEGIS architecture with an abstraction-refinement
+approach and with optimization.  We call the resulting new technique
+\emph{CEGIS-OR} (CEGIS with Optimization and Refinement).  By using
+abstraction refinement, CEGIS-OR addresses the scalability issues inherent
+in program synthesis and enables us to handle complex systems, which we
+coarsely abstract and only refine on demand -- refinements are triggered by
+counterexamples returned by the verification phase.
+%
 %potentially coarse abstractions of the given model that are only
 %refined on demand.
-Since the use of coarse abstractions may result in
-low-quality candidate solutions (i.e. candidates that fail the
-specification on a very large number of inputs), after each synthesis
-phase we use optimization techniques to improve the produced
-candidates.  In particular, our optimization procedure aims at
-reducing the size of the reach space of the closed loop system, while
-maintaining other dynamical properties (safety, stability, and
+%
+Since the use of coarse abstractions may result in low-quality candidate
+solutions (i.e.  candidates that fail the specification on a very large
+number of inputs), after each synthesis phase we use optimization techniques
+to improve the produced candidates.  In particular, our optimization
+procedure aims at reducing the size of the reach space of the closed loop
+system, while maintaining other dynamical properties (safety, stability, and
 response time).
@@
 CHEN1979389, KOKOTOVIC198023, gajic2008optimal, Franklin15, maglev,
-converters}.  In order to obtain statistically relevant results, we have
+converters}.  In~order to obtain statistically relevant results, we have
 taken these models and modified each possible combination of their
@@
 requires adequate tools for exploring different types of properties.  Our
-results show significant improvement in terms of scalability over standard
+results show significant improvements in terms of scalability over standard
 CEGIS approaches, with an ability to explore complex properties, hence many
-synthesis tasks may be tackled with it.  In particular we note that our
+synthesis tasks may be solved with it.  In particular, we note that our
 synthesis loop is more efficient for models where the solution space is
 formed by connected spaces where optimization algorithms or localized
-synthesis are likely to be more efficiently than global synthesis.  Finally
+synthesis are likely to be more efficiently than global synthesis.  Finally,
 our application to control synthesis provides a solid proof of concept for

### 2018-01-31 TACAS2018/paper.tex
wording

@@
 There are generally speaking two paradigms for representing numbers in
-programs: fixed and variable precision numbers.  We refer to both of these
+programs: fixed and variable precision numbers.  We~refer to both of these
 as finite word length representations (FWL).  In fact, these subdivide into
@@
 dependent on the sign of $x$.  Common cases in computer systems are: round
-downwards (\emph{ie} to $-\infty$), round upwards (\emph{ie} to $+\infty$),
-and round to zero.  Rounding errors are cumulative which means the overall
-error will statistically increase with every operation, thus single
-transition algorithms can be more precise in this respect than iterative
-ones because they perform fewer operations needing rounding.
+downwards (i.e., to $-\infty$), round upwards (i.e., to $+\infty$), and
+round to zero.  Rounding errors are cumulative which means the overall error
+will statistically increase with every operation, thus single transition
+algorithms can be more precise in this respect than iterative ones because
+they perform fewer operations needing rounding.
 
@@
 
-The semantics discussed in sections \ref{sec:model} do not describe all
+The semantics discussed in Sec.~\ref{sec:model} do not describe all
 properties of interest in our systems.  In some cases, specific values or
@@
 A feedback system is one where the output is fed back into the input, thus
-making part or all of the system a closed system (i.e.  no inputs).  Such a
+making part or all of the system a closed system (i.e., no inputs).  Such a
 system is exemplified in Figure~\ref{fig:observersystem}.  Since the
@@
 %-------------------------------
-\section{Proofs of theorems \label{sec:proofs}}
+\section{Proofs of Theorems\label{sec:proofs}}
 %-------------------------------
@@
 \begin{enumerate}
-\item The \emph{rise time} is defined as the time it takes the output to reach a percentage (eg $90\%$) of the target value given a step change in the input.
-\item The \emph{settling time} is defined as the time it takes the output to stabilize within a margin of the target value (eg $10\%$).
+%
+\item The \emph{rise time} is defined as the time it takes the output to
+reach a percentage (e.g., $90\%$) of the target value given a step change in
+the input.
+%
+\item The \emph{settling time} is defined as the time it takes the output to
+stabilize within a margin of the target value (e.g., $10\%$).
+%
 \end{enumerate} 
@@
 \begin{align*}
-|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^p \left|c_i + \sum\limits_{j=1}^{gm(i)}c_{i+j}\binom{k}{j} \lambda_i^{-j}\right|
+|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^p \left|c_i + \sum\limits_{j=1}^{gm(i)}c_{i+j}\binom{k}{j} \lambda_i^{-j}\right|\;.
 \end{align*}
 %
-In the case of closed loop forms without geometric multiplicity (which is by
-far the most common case), the right hand terms disappear and we obtain
+In the case of closed loop forms without geometric multiplicity (which is
+the most common case), the right-hand terms disappear and we obtain
 %
 \begin{align*}
-|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^p |c_i|
+|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^p |c_i|\;.
 \end{align*}
@@
 In the case where we allow for geometric multiplicities, we need to
-compensate for the effects of $\binom{k}{j}$ \footnote{tighter bounds can be
-achieved by evaluating $\frac{\sum\limits_{j=1}^{gm(i)}c_{i+j}\binom{k}{j}
-\lambda_i^{-j}{\vec{x}_0}_j}{\sum\limits_{j=1}^{gm(i)}c_{i+j}{\vec{x}_0}_j}$}. 
+compensate for the effects of $\binom{k}{j}$ \footnote{Tighter bounds can be
+obtained by evaluating $\frac{\sum\limits_{j=1}^{gm(i)}c_{i+j}\binom{k}{j}
+\lambda_i^{-j}{\vec{x}_0}_j}{\sum\limits_{j=1}^{gm(i)}c_{i+j}{\vec{x}_0}_j}$.}. 
 We recall here that our interest is to reach within $10\%$ of the final
@@
 \begin{itemize}
+%
 \item Find $\underline{k}=\frac{t_s}{T_s}$ where $t_s$ is the settling time and $T_s$ the sampling time.
+%
 \item Calculate $|\overline{\omega}|=log_{t_s}\left(P_s\binom{\underline{k}}{gm-1}^{-1}\right)$,
 where $gm$ is the maximum desired geometric multiplicity.
+%
 \item Ensure that $|\overline{\omega}| \leq \frac{\underline{k}}{\underline{k}+1}$ and that the
-synthesized closed loop does not have a larger gm than specified.
+synthesized closed loop does not have a larger $gm$ than specified.
+%
 \end{itemize}

### 2018-01-31 TACAS2018/paper.tex
wording

@@
 programs: fixed and variable precision numbers.  We~refer to both of these
-as finite word length representations (FWL).  In fact, these subdivide into
-multiple data types such as integer bit-vectors, fixed or floating point
-numbers and rationals).  In this section we will be discussing fixed and
-floating point numbers.  On one hand, we have variable word length types
-which will attempt to use as much memory as needed to precisely represent
-the original domain (usually the reals).  In this case the limitations are
-caused by memory and speed, both of which are directly affected by the
-increasingly larger word lengths.  Multiple Precision Floating Point
-Arithmetic and Software Rationals are good examples of these cases.  It is
-possible for some of these data types to have memory constraints, at which
-point they fall into the second category.  Fixed precision data types are
-most common in software programs.  Whether they be Floating Point or Fixed
-Point (of which integers are the special case for 0 decimal places) numbers,
-the problem arises in the misrepresentation of the reals (or equivalent data
-type being represented).  Let $\mathbb{R}_{\langle M,F \rangle}$ be a fixed
-point domain with $M$ bits representing the binary word length of the
-representation and $F$ bits representing the pre-scaling $2^{-F}$
-(\emph{i.e} the number of bits after the decimal place).  We note that a
-negative $F$ denotes an integer multiplication that adds $-F$ trailing zeros
-in the number represented by~$M$.
+as finite word length representations (FWL).  They subdivide into a variety
+of data types such as integer bit-vectors, fixed or floating point numbers
+and rationals).  In this section we will be discussing fixed and floating
+point numbers.
+
+On one hand, we have variable word length types, which will use as much
+memory as needed to precisely represent the original domain (usually the
+reals).  In this case, the limitations are caused by memory and speed, both
+of which are directly affected by the increasingly larger word lengths. 
+Multiple Precision Floating Point Arithmetic and Software Rationals are good
+examples of these cases.  It is possible for some of these data types to
+have memory constraints, at which point they fall into the second category. 
+Fixed precision data types are most common in software programs.  Whether
+they be Floating Point or Fixed Point (of which integers are the special
+case for 0 decimal places) numbers, the problem arises in the
+misrepresentation of the reals (or equivalent data type being represented). 
+Let $\mathbb{R}_{\langle M,F \rangle}$ be a fixed point domain with $M$ bits
+representing the binary word length of the representation and $F$ bits
+representing the pre-scaling $2^{-F}$ (i.e., the number of bits after
+the decimal place).  We note that a negative $F$ denotes an integer
+multiplication that adds $-F$ trailing zeros in the number represented
+by~$M$.
 %
@@
 %\todo{the observer was not defined..}
-%(\emph{i.e} the numerical errors 
+%(i.e., the numerical errors 
 %in the calculations as opposed to the estimation error).

### 2018-02-01 CAV2018/paper.tex
submitted to CAV 2018
proper macro for log

--- 2018-01-31 TACAS2018/paper.tex
@@
 %
-t_s<-log_{\overline{\lambda}}({P_s}), \text{ where }
+t_s<-\log_{\overline{\lambda}}({P_s}), \text{ where }
   \overline{\lambda} = \max(|\lambda_i|) \text{ and }
@@
 2  & Helicopter        & 3  & 100 & 57.2\,s & t.o. & 54 & 15 & 7.1\,s  &   18.0\,s & 9 & 90\\
-3  & Inverted Pendulum & 4 & 100 &  277\,s& t.o. & 59& 0 & 20.0\,s  &  t.o. & 50 & 20\\
+3  & Inverted Pendulum & 4 & 100 &  277\,s& t.o. & 82& 0 & 20.0\,s  &  t.o. & 55 & 20\\
 4  & Magnetic Pointer  & 2  & 100 & 5.7\,s & 229.9\,s & 38 & 42 & 3.0\,s  &  9.5\,s & 5 & 95 \\
@@
 \begin{equation}
-t_s<-log_{\overline{\lambda}}({P_s}), \text{ where }  \overline{\lambda} = \max(|\lambda_i|) \text{ and } \overline{\lambda}<1,\ \forall i \in \{1, \ldots,p\}
+t_s<-\log_{\overline{\lambda}}({P_s}), \text{ where }  \overline{\lambda} = \max(|\lambda_i|) \text{ and } \overline{\lambda}<1,\ \forall i \in \{1, \ldots,p\}
 \label{eq:set_time}
@@
 %
-\item Calculate $|\overline{\omega}|=log_{t_s}\left(P_s\binom{\underline{k}}{gm-1}^{-1}\right)$,
+\item Calculate $|\overline{\omega}|=\log_{t_s}\left(P_s\binom{\underline{k}}{gm-1}^{-1}\right)$,
 where $gm$ is the maximum desired geometric multiplicity.

### 2018-02-01 CAV2018/paper.tex
dot

@@
 We will assume, for the purposes of this analysis, that the domain of the
-ADC is that of the digital controller (i.e, the quantizer includes a digital
+ADC is that of the digital controller (i.e., the quantizer includes a digital
 gain added in the code resulting in $\mathbb{R}_{\langle A

### 2018-02-01 CAV2018/paper.tex
add authors
formatting

@@
 Franklin15}.  Correct synthesis of control software for such platforms is
-non-trivial, even in cases with restricted dynamics.  We consider the case
+non-trivial, even in cases with restricted dynamics.  We~consider the case
 of Linear Time Invariant (LTI) models, for which the synthesis of
@@
 $\phi := \phi \wedge \phi_\mathit{safety}^n$.
-If the counterexample is provided by the {\sc continuous time} stage,
+If~the counterexample is provided by the {\sc continuous time} stage,
 then we must select a smaller suitable sample time to be used

### 2018-02-14 automatica/paper.tex
updated sections of the automatica journal
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \begin{abstract}                          % Abstract of not more than 200 words.
-\textcolor{red}{Lucas: We have to write a new abstract.}
+\textcolor{red}{Cristina: Can you please write an initial version of the abstract.}
 \end{abstract}
@@
 
-\textcolor{red}{Pascal: can you please describe here the experimental results?}
+\textcolor{red}{Lucas describe here the experimental results}
 
@@
 
-\textcolor{red}{Pascal: can you please describe here the threats to validity?}
+\textcolor{red}{Lucas: describe here the threats to validity}
 
@@
 
-\textcolor{red}{Lucas: We need to write a new conclusions about this work.}
+\textcolor{red}{Cristina: Can you please write an initial version of the conclusions?}
 

### 2018-02-15 automatica/paper.tex
Start merge of CAV 18 sections

@@
 \renewcommand{\vec}[1]{\boldsymbol{#1}}
+\newtheorem{lemma}{Lemma}
 \newtheorem{theorem}{Theorem}
@@
 %-------------------------------
+
+%-------------------------------
+\subsection{State-space representations of LTI models}
+\label{sec:model}
+%-------------------------------
+
+%% A dynamical system is a system in which a function describes the progression
+%% of a state over time.  In a continuous domain with linear dynamics, it is
+%% described by a first order Ordinary Differential Equation (ODE).
+%% \begin{equation}
+%% \dot{x}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)% +\vec{w}(t)
+%% \label{eq:dynamical}
+%% \end{equation}
+
+We consider models of physical plants expressed as ordinary differential
+equations (ODEs), which we assume to be controllable~\cite{Astrom08,
+astrom1997computer}:
+%
+\begin{align}
+\label{eq:ode1}
+\dot{x}(t) = \mat{A}\vec{x}(t)+ \mat{B} \vec{u}(t), \quad 
+\vec{x} \in \mathbb{R}^p, \vec{u} \in \mathbb{R}^q,\,
+\mat{A} \in \mathbb{R}^{p \times p},\,
+\mat{B} \in \mathbb{R}^{p \times q},
+\end{align}
+%
+where $t \in \mathbb R_0^+$ denotes continuous time, $\mat{A}$ and $\mat{B}$
+are matrices that fully characterize the dynamics of the continuous plant,
+and $x(0)$ is the initial state.
+
+We are interested in control systems with an output $\vec{y}$ that is a
+linear combination of its states and inputs\footnote{Notice that since we
+can only measure $\vec{y}$, the state-space $\vec{x}$ is not fully
+observable.}.
+%
+%, which may restrict the observability of the state-space from the output space.
+\begin{equation}
+\label{eq:ode2}  
+\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t),
+\vec{y} \in \mathbb{R}^o,
+\mat{C} \in \mathbb{R}^{o \times p},
+\mat{D} \in \mathbb{R}^{o \times q}. 
+\end{equation}
+%
+Equations~\eqref{eq:ode1} and \eqref{eq:ode2} are soundly discretized in
+time~\cite{middleton1990digital,van1978computing} at constant intervals,
+whose duration we refer to as the sample time $T_s$, into the difference
+equation
+%
+\begin{align}
+\label{eq:plant}
+\left\{
+\begin{array}{rl}
+\vec{x}_{k+1} =& \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k\\
+\vec{y}_{k} =& \mat{C} \vec{x}_k + \mat{D} \vec{u}_k, 
+\end{array}
+\right.
+\text{ where }
+\left\{
+\begin{array}{l}
+\mat{A}_d=e^{\mat{A}T_s}\\
+\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}
+\end{array}
+\right.,
+\end{align} 
+%
+%where $\mat{A}_d=e^\mat{A}$, $\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$,
+%
+where $k \in \mathbb N$ is a discrete counter and $\vec{x}_{0}=\vec{x}(0)$
+is the initial state.  In this work we apply the standard assumption that
+$\mat{D}=\mat{0}$~\cite{Astrom08}.
+%
+%Also, since $\vec{y}$ can be directly derived from $\vec{x}$, we will omit discussing it in the following unless strictly necessary.
 
@@
 
-%-------------------------------
-\subsection{Overapproximating continuous time dynamics using discrete models}
-\label{sec:cont_aa}
-%-------------------------------
-
-Thus far we wave discussed the Abstract Accelertion of Discrete Time
-systems.  However, our plant models derive from the discretization of
-continuous time systems.  We therefore seek to establish a sound
-overapproximation which does not only encompass the selected discretization,
-but any chosen discretization in the time domain.
-
-A dynamical system is a system in which a function describes the progression
-of a state over time.  In a continuous domain with linear dynamics, it is
-described by a first order Ordinary Differential Equation (ODE).
-%
-\begin{equation}
-\dot{x}(t)=\mat{A}_o\vec{x}(t)+\mat{B}_o\vec{u}(t) +\vec{w}(t)
-\label{eq:dynamical}
-\end{equation}
-%
-where $\vec{w}$  is a continuous zero-mean white noise source with
-covariance $N ( 0 , Q )$ Furthermore, a control system may have a derived
-output that is a linear combination of its states and inputs, which may
-restricts the observability of the statespace from the output space.
-%
-\begin{equation}
-\vec{y}(t)=\mat{C}_o\vec{x}(t)+\mat{D}_o\vec{u}(t)
-\end{equation}
-%
-Discretization of a continuous dynamical system turns the ODE into a
-difference equation, assuming zero-order hold for the input $\vec{u}$ and
-continuous integration for the noise $\vec{w}$, to
+%%-------------------------------
+%\subsection{Overapproximating continuous time dynamics using discrete models}
+%\label{sec:cont_aa}
+%%-------------------------------
+%
+%Thus far we wave discussed the Abstract Accelertion of Discrete Time
+%systems.  However, our plant models derive from the discretization of
+%continuous time systems.  We therefore seek to establish a sound
+%overapproximation which does not only encompass the selected discretization,
+%but any chosen discretization in the time domain.
+%
+%A dynamical system is a system in which a function describes the progression
+%of a state over time.  In a continuous domain with linear dynamics, it is
+%described by a first order Ordinary Differential Equation (ODE).
+%%
+%\begin{equation}
+%\dot{x}(t)=\mat{A}_o\vec{x}(t)+\mat{B}_o\vec{u}(t)
+%\label{eq:dynamical}
+%\end{equation}
+%%
+%Furthermore, a control system may have a derived
+%output that is a linear combination of its states and inputs, which may
+%restricts the observability of the statespace from the output space.
+%%
+%\begin{equation}
+%\vec{y}(t)=\mat{C}_o\vec{x}(t)+\mat{D}_o\vec{u}(t)
+%\end{equation}
+%%
+%Discretization of a continuous dynamical system turns the ODE into a
+%difference equation, assuming zero-order hold for the input $\vec{u}$, to
+%%
+%\begin{align}
+%\label{eq:discretization}
+%\vec{x}_{k+1} &= \mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
+%y_k &= \mat{C}_d \vec{x}_ k + \mat{D}_d \vec{u}_ k 
+%\end{align}
+%where
+%\begin{align}
+%\label{eq:discretize}
+%\mat{A}_d &= e^{\mat{A}_o T_s} = \mathcal{L}^{-1} { ( s \mat{I} - \mat{A}_o )^{-1} }_{t = T_s}\\
+%\mat{B}_d &= \int_{t = 0}^{T_s} e^{\mat{A}_o t} dt\ \mat{B}_o = \mat{A}_o^{-1} ( \mat{A}_d - \mat{I} ) \mat{B}_o\\
+%\mat{C}_d &= \mat{C}_o\\
+%\mat{D}_d &= \mat{D}_o \\
+%\end{align}
+%and $T_s$ is the sample time. Then
+%\begin{align*}
+%x(kT)=x_k \wedge y(kT) = y_k, \forall k
+%\end{align*}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Acceleration of continuous-time models}\label{sec:continuous_time_accel}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
+the state of the plant at integer multiples of the sample time.  However, in
+order to synthesize $\mat{K}=\mat{K}_{\langle C \rangle}$ and
+$\mat{L}=\mat{L}_{\langle C \rangle}$, we must be able to ensure that
+certain properties of the plant hold at any given point in time.  In order
+to do so, we accelerate the dynamics of the plant according to the model
+semantics in Sec.~\ref{sec:model} and compute the state
+$\vec{x}_T$ at a given time $T$,
+%
+% namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
+%
+namely the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time
+$t=T$.
+
+%\note{ [add?] In this section we work with fully observed models, namely where $y = x$. } 
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsubsection{Accelerated\! dynamics\! for\! continuous-time\! models\! without\! inputs}\label{sec:cont_acc_no_inputs}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%
+Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a
+linear function of $\vec{x}_0$ as shown below.  We assume that the system
+has no inputs, so its dynamics are described by
+$\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.
+
+\begin{lemma}
+The solution to the differential equation $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, and $\mat{S}$ are the generalized eigenvectors of $\mat{A}$,
+evaluated at time $T$ is
 %
 \begin{align}
-\label{eq:discretization}
-\vec{x}_{k+1} &= \mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k + \vec{w}_k\\
-y_k &= \mat{C}_d \vec{x}_ k + \mat{D}_d \vec{u}_ k 
-\end{align}
-with covariance for $\vec{w}_k$, $N ( 0 , Q_d )$
-where
-\begin{align}
-\label{eq:discretize}
-\mat{A}_d &= e^{\mat{A}_o T_s} = \mathcal{L}^{-1} { ( s \mat{I} - \mat{A}_o )^{-1} }_{t = T_s}\\
-\mat{B}_d &= \int_{t = 0}^{T_s} e^{\mat{A}_o t} dt\ \mat{B}_o = \mat{A}_o^{-1} ( \mat{A}_d - \mat{I} ) \mat{B}_o\\
-\mat{C}_d &= \mat{C}_o\\
-\mat{D}_d &= \mat{D}_o \\
-Q_d &= \int_{t = 0}^{T_s} e^{\mat{A}_o t} Q e^{\mat{A}_o^T t} dt
-\end{align}
-and $T_s$ is the sample time. Then
-\begin{align*}
-x(kT)=x_k \wedge y(kT) = y_k, \forall k
-\end{align*}
-
-%-------------------------------
- \subsubsection{A discrete time model using reals}
- \label{sec:real_aa}
-%-------------------------------
-
- \begin{theorem}
- The expression
- \begin{align}
- \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x}_0 : \dot{\vec{x}}=\mat{A}\vec{x} \wedge \mat{A}=\mat{S}\mat{J}\mat{S}^{-1}\nonumber\\
+ \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x} (0)\\
  \mat{A}_{T}&= \mat{S}
  \left [ \begin{array}{cccc}
- e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \hdots  & s_i\frac{T^{p-i}e^{T\lambda_i}}{(p-i)!} \\
+ e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(2)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
 0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
@@
 \end{array} \right ]
- \mat{S}^{-1}\nonumber\\
- s_i&=\left\{\begin{array}{cc}1&gm(\lambda_i)>1\\0&gm(\lambda_i)=1\end{array}\right.
- \label{eq:continuous_tube_dyn}
+ \mat{S}^{-1}
+ \label{eq:continuous_tube_dyn2}\\
+ &\text{where } s_i=\left\{\begin{array}{cc}1&\quad gm(\lambda_i)>1\\0&\quad gm(\lambda_i)=1\end{array}\right.,\nonumber
 \end{align}
- where $\lambda_i \in \mat{J}$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$ is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}$ at time t=T.
- \end{theorem}
- \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x} : k \in (0,\infty)$ is a witness of the system at time $t=kT_d$.
- \end{corollary}
- \begin{proof}
- Let us recall equation \ref{eq:discretize}. The discrete representation of the system dynamics discretized with sample time $T_1$ is ruled by the formula
- $\mat{A}_1 = e^{\mat{A} T_1}$. From matrix theory, we have 
+%
+$\lambda_i$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.
+%
+%$\vec{x}_T$ is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T. 
+If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0 \text{ with } T \in \mathbb{R}^+_0$ is the state of the system at time $t=T$.
+\end{lemma}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsubsection{Accelerated dynamics for models with parametric inputs}\label{sec:real_discrete_param_inputs}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Next, we are interested in studying models with parametric inputs, which are
+described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where
+$\forall t\geq 0.\,\vec{u}(t)=\vec{u}$.  For such models, a state $\vec{x}_T$
+is computed next.
+%
+\begin{lemma}
+%
+The state of the model
+$\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a
+parametric input $\vec{u}$ is
+%
 \begin{align}
- e^{\mat{A}}&=\sum_{k=0}^\infty \frac{1}{k!}\mat{A}^k
+\vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u} \text{ where } \mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B} 
+\label{eq:continuous_tube_param}
 \end{align}
-\begin{align} 
- e^{\mat{S}\mat{J}\mat{S}^{-1}}&=\sum_{k=0}^\infty \frac{1}{k!}(\mat{S}\mat{J}\mat{S}^{-1})^k
- =\mat{S} \left (\sum_{k=0}^\infty \frac{1}{k!}\mat{J}^k\right) \mat{S}^{-1}
- =\mat{S}e^{\mat{J}}\mat{S}^{-1}
-\end{align} 
-\begin{equation}
-\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \Rightarrow \vec{A}_1 = \mat{S}\mat{J}_1\mat{S}^{-1}= \mat{S}e^{\mat{J} T_1}\mat{S}^{-1}.
- \end{equation}
-
- Let $\mat{J}$ be a diagonal matrix, such that 
- $${\lambda_1}_i=e^{\lambda_i T_1}, \forall \lambda_i \in \mat{J}.$$
- Let us now take a different sample rate $T_2$, such that 
- $${\lambda_2}_i=e^{\lambda_i T_2}, \forall \lambda_i \in \mat{J}.$$
- We can then say that 
- \begin{equation}
- {\lambda_2}_i=e^{\lambda_i T_1 \frac{T_2}{T_1}}={\lambda_1}_i^{\frac{T_2}{T_1}} \Rightarrow A_2=A_1^{\frac{T_2}{T_1}}.
- \end{equation}
- This proves the theorem for $gm(\lambda_i)=1$.
- We now note that given an exponentiated Jordan form with geometric multiplicity, the upper diagonal terms can be
- referenced to the original eigenvalues modified by the sampling rate.
-  Let $\mat{J}\in \mathbb{R}^{p \times p}$ be a Jordan Canonical matrix. Then
-\begin{align}
- \mat{J}_1=&\sum_{k=0}^\infty \frac{1}{k!}\left(\mat{J}T_1\right)^k\nonumber\\
- =&\sum_{k=0}^\infty \frac{1}{k!} \left [ \begin{array}{cccc}
- \lambda_i^k  & \binom{k}{1}  \lambda^{k-1} & \hdots  & \binom{k}{p-1} \lambda_i^{k-p+1} \\
-& \lambda_i^k  & \binom{k}{1}  \lambda_i^{k-1} & \vdots \\
-\vdots & \ddots & \ddots & \vdots \\
-& &  &\lambda_i^k \\
-\end{array} \right ] T_1^k
-\end{align}
-%
-The eigenvalues remain the same as in the diagonal case, but the upper triangular terms are of the form:
-%
-\begin{align}
-\forall j>i, c_{ij}&=\sum_{k=j-i}^\infty \frac{1}{k!}\binom{k}{j-i} \lambda_i^{k-(j-i)}T_1^k\\
-&=\frac{1}{(j-i)!}\sum_{k=j-i}^\infty \frac{1}{(k-(j-i))!} \lambda_i^{k-(j-i)}T_1^k\nonumber\\
-&=\frac{T_1^{j-i}e^{\lambda_i T_1}}{(j-i)!}\nonumber
-\end{align}
-which completes the proof for $gm(\lambda_i)>1$.
-\end{proof}
-
+%
+where $\forall t \leq T.\, \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in
+\eqref{eq:continuous_tube_dyn2} \footnote{When $\mat{A}$ is not invertible,
+we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\
+0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$.}. 
+If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that
+$A_d=e^{\mat{A} T_d}$, then
+$\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u})
+\text{ with } T \in \mathbb{R}_0^+$ (where $\mat{A}_d^{\frac{T}{T_d}} =
+e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the
+system at time $T$.
+%
+\end{lemma}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsubsection{Accelerated dynamics for models with a sampled-time feedback}\label{sec:real_discrete_feedback_inputs}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+The final case we analyze is that of hybrid-time models, where the plant
+dynamics evolve in continuous time while the feedback dynamics evolve in
+discrete time.  A~new input value is produced only at every sample time but
+implemented over the continuous-time plant dynamics.
+%
 \begin{theorem}
 The expression
+%
  \begin{align}
- \vec{x}_T&=\vec{x}(t=T)=\mat{A}^{-1}\vec{x}_T'\nonumber\\
-\vec{x}_T'&=\mat{A}\mat{A}_T\vec{x}_0 + (\mat{I}-\mat{A}_T)\mat{B}\vec{u} : \forall t \leq T,\ \vec{u}(t)=\vec{u} 
+ \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0, 
+ \label{eq:cyber_feedback}
  \end{align}
- with $\mat{A}_T$ as per \eqref{eq:continuous_tube_dyn} is a witness of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$.
+%
+with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, $\mat{B}_T$ as in
+\eqref{eq:continuous_tube_param}, and where $\mat{A}_d=\mat{A}_{T_s}$,
+$\mat{B}_d=\mat{B}_{T_s}$ describe the discretized plant dynamics with
+sample time $T_s$, is the state of the model
+%
+\begin{align*}
+ \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
+ \vec{u}(t)=\mat{K}\vec{x}_k,  \,
+ kT_s \leq t < (k+1)T_s \,. 
+\end{align*}
+%
 \end{theorem}
- \begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then $\vec{x}_k=A_d^k\vec{x}+(\mat{I}-\mat{A}_d^k\mat{B}\vec{u}) : k \in (0,\infty)$ is a witness of the system at time $kT_d$.
- \end{corollary}
 \begin{proof}
- We begin by expanding the equation
- \begin{align}
- \vec{x}_T&=\mat{A}^{-1}\vec{x}_T'\\
- \vec{x}_T'&=\mat{A}_T\vec{x}_0 + \mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}\vec{u} = \mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u}\nonumber
- \end{align}
- where $\mat{A}_T=e^{\mat{A}T}$ and $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$ correspond to $\mat{A}_d$ and $\mat{B}_d$ in equation \eqref{eq:discretize}
- \end{proof}
- \begin{theorem}
-Let $\mat{A}_b$ be a spherical overapproximation of $\mat{A}$ and $U_b$ a spherical overapproximation of $U$ centered at $\vec{u}_c$
-\begin{align}
-\mat{A}_b&=\mat{S} \mat{J}_b \mat{S}^{-1}\\
-\mat{J}_{bs}&=\lambda_{bs}\mat{I} \wedge \lambda_{bs}=|| \mat{J}_s ||=
-\max_{\vec{u} \subseteq U_b'} \frac{|| \mat{J}_s\vec{u}_s ||}{||
-  \vec{u}_s ||}\nonumber
-\label{eq:induced}
-\end{align}
-where $|| \mat{J}_s ||$ is the induced matrix norm, $s$ indicates the index of each Jordan block, and $\vec{u}_s$ is the corresponding subvector of $\vec{u}$ (\emph{ie} the subspace of $\vec{u}$ on which $\mat{J}_s$ operates).
-Directly from the definition of the matrix norm, we have 
-\begin{equation}
-||\mat{J}_s\vec{u}_s|| \leq ||\mat{J}_s||\,||\vec{u}_s||, 
-\label{eq:overinduced}
-\end{equation}
-and $\mat{J}_{b} U_b$ is the smallest ball that over-approximates $\mat{J}  U_d$.
-
-The expression
- \begin{align}
- \label{eq:contu_reachset}
-X_T^\sharp &=\mat{A}^{-1}X_T'\supseteq X_T\\
-X_T'&=\mat{A}\mat{A}_TX_0 \oplus (\mat{I}-\mat{A}_{bT})\mat{B}U_b \oplus (\mat{I}-\mat{A}_T)\mat{B}\vec{u}_c\nonumber
- \end{align}
- is an overapproximation of the reach set  at time $t=T$ of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t) + \mat{B}\vec{u}(t)$ given $\vec{x}(0) \in X_0$ and $\vec{u}(t) \in U$.
- \end{theorem}
-\begin{corollary}
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d :  A_d=e^{\mat{A} T_d}$, then 
- \begin{equation}
- \tiny
- X_k=A_d^kX_0 \oplus (\mat{I}-\mat{A}_{bd}^k)(\mat{I}-\mat{A}_{bd})^{-1}\mat{B}U_b \oplus (\mat{I}-\mat{A}_d^k)(\mat{I}-\mat{A}_d)^{-1}\mat{B}\vec{u}_c\nonumber\\
- k \in (0,\infty)
- \end{equation}
-  is a witness of the system at time $kT_d$, where $\mat{A}_{bd}$ is a spherical overapproximation of $\mat{A}_d$
-\end{corollary}
- \begin{proof}
-Let $U'=\mat{B}U$, with $\vec{u}'$ its geometrical centre and $U_b'$ the smallest sphere centered at $\vec{u}'$ containing all points in $U'$.
-Then $U'\subseteq U_b' \oplus \vec{u}_c' \Rightarrow (\mat{I}-\mat{A}_T)U' \subseteq (\mat{I}-\mat{A}_T)U_b' \oplus (\mat{I}-\mat{A}_T)\vec{u}_c'$.
-Since $ (\mat{I}-\mat{A}_{bT})U_b'\supseteq  (\mat{I}-\mat{A}_T)U_b'$, then $(\mat{I}-\mat{A}_T)U' \subseteq (\mat{I}-\mat{A}_{bT})U_b' \oplus (\mat{I}-\mat{A}_T)\vec{u}_c'$ thus proving the theorem for $\vec{u}(t)=\vec{u}_0 : t \in [0\ T]$.
-
-For the continuous time interval, let us look at the solution for the differential equation at time $T$ with a non-deterministic input $\vec{u}$.
-\begin{equation*}
-\vec{x}_T=e^AT\vec{x}_0+\int_{t = 0}^{T_s} e^{\mat{A} t} \mat{B} \vec{u}(t) dt
-\end{equation*}
-We will first divide this equation into 
+%
+Let $\mat{K}$ be a feedback controller such that
+$\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$.  Let the output of the
+feedback system be a zero order holder such that
+$\vec{u}(t'+kT_s)=\vec{u}(kT_s), \text{ for } 0 \leq t' < T_s$.  The closed
+loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
+%
 \begin{align*}
-\vec{x}_T&=e^AT\vec{x}_0+\int_{t = 0}^{T} e^{\mat{A} t} \mat{B} \vec{u}_c dt +\int_{t = 0}^{T_s} e^{\mat{A} t} \mat{B} (\vec{u}(t)-\vec{u}_c) dt\\
-&=A_T\vec{x}_0+B_T\vec{u}_c+\int_{t = 0}^{T} \mat{S}e^{\mat{J} t} \mat{S}^{-1}\mat{B} (\vec{u}(t)-\vec{u}_c) dt\\
-&=A_T\vec{x}_0+B_T\vec{u}_c+\mat{S}\int_{t = 0}^{T} e^{\mat{J} t} \vec{u}_{j}'(t) dt\\
-&=A_T\vec{x}_0+B_T\vec{u}_c+\mat{S}\int_{t = 0}^{T} \sum_{k=0}^\infty \frac{1}{k!} \mat{J}^k t^k \vec{u}_{j}'(t) dt\\
-&=A_T\vec{x}_0+B_T\vec{u}_c+\mat{S}\sum_{k=0}^\infty \frac{1}{k!} \int_{t = 0}^{T} t^k \mat{J}^k \vec{u}_{j}'(t) dt
+\vec{x}_{k,t'}=\mat{A}_{t'}\vec{x}_k-\mat{B}_{t'}\mat{K}\vec{x}_k = (\mat{A}_{t'}-\mat{B}_{t'}\mat{K})\vec{x}_k,
 \end{align*}
-It follows from equation \eqref{eq:overinduced} that $\mat{J}^k \vec{u}_{j}'(t) \subseteq \mat{J}_b^k U_{bj}'$ (where $U_{bj}'=\mat{S}^{-1}U_b'$), hence
+where $0 \leq t' < T_s$
+We further explore the dynamics across discrete time boundaries. Let $\mat{A}_d=\mat{A}_{T_s}$ and $\mat{B}_d=\mat{B}_{T_s}$
 \begin{align*}
-&X_T \subseteq A_TX_0+B_T\vec{u}_c+\mat{S}\sum_{k=0}^\infty \frac{1}{k!} \int_{t = 0}^{T} t^k \mat{J}_b^k U_{bj}' dt\\
-\Rightarrow &X_T \subseteq A_TX_0+B_T\vec{u}_c+\mat{S} \int_{t = 0}^{T} \sum_{k=0}^\infty \frac{1}{k!}\mat{J}_b^k t^k U_{bj}' dt\\
-\Rightarrow &X_T \subseteq A_TX_0+B_T\vec{u}_c+\int_{t = 0}^{T_s} e^{\mat{A}_b t} U_b' dt\\
-\Rightarrow &X_T \subseteq A_TX_0+B_T\vec{u}_c+ \mat{A}^{-1}(\mat{I}-\mat{A}_{bT}) \mat{B} U_b
-\end{align*}
-Multiplying by $\mat{A}$ we get $X_T'$ as in \eqref{eq:contu_reachset}, thus proving the theorem.
-\end{proof}
-
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
- \subsubsection{Discrete dynamics using reals for systems with discrete time feedback inputs}\label{sec:real_discrete_feedback_inputs}
- %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-The final case we analyse here is that of hybrid time systems, where the plant dynamics evolve in continuous time
-while the feedback dynamics evolve in discrete time.
-
-\begin{theorem}
-The expression
- \begin{align}
- \vec{x}_{t} &= (\mat{A}_{t-kT_s}-\mat{B}_{t-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
- \end{align}
- with $\mat{A}_t, \mat{B}_t$ as per \eqref{eq:continuous_tube_dyn} and $\mat{A}_d, \mat{B}_d$ as per equation \eqref{eq:discretize} is a witness of the system
- \begin{align}
- \dot{\vec{x}}_{t} &= \mat{A}\vec{x}+\mat{B}\vec{u}_t\nonumber\\
- \vec{u}_t=\mat{K}\vec{x}_k  : kT_s \leq t < (k+1)T_s
- \end{align}
- \end{theorem}
-
-\begin{proof}
-Let $\mat{K}$ be a feedback controller such that $\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$. Let the output of
-the feedback system be a zero order holder such that $\vec{u}(t+kT_s)=\vec{u}(kT_s) : 0 \leq t < T_s$.
-The closed loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
-\begin{equation}
-\vec{x}_{k,t}=\mat{A}_t\vec{x}_k-\mat{B}_t\mat{K}\vec{x}_k = (\mat{A}_t-\mat{B}_t\mat{K})\vec{x}_k : 0 \leq t < T_s
-\end{equation}
-We further explore the dynamics across discrete time boundaries. Let $\mat{A}_d=\mat{A}_{T_s}$ and $\mat{B}_d=\mat{B}_{T_s}$
-\begin{align}
 \vec{x}_{k}&=\vec{x}_{k-1,T_s}= (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}\\
 \vec{x}_{k,T_s} &= (\mat{A}_d-\mat{B}_d\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}
-\end{align}
-which accelerating results becomes
+\end{align*}
+which accelerating results and setting $T=kT_s+t'$ becomes
 \begin{align}
+\label{eq:feedback_sampled_cont}
 \vec{x}_{k} &= (\mat{A}_d-\mat{B}_d\mat{K}) ^k\vec{x}_0\\
-\vec{x}_{t} &= (\mat{A}_{t-kT_s}-\mat{B}_{t-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
+\vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
+\label{eq:feedback_cont}
 \end{align}

### 2018-02-19 automatica/paper.tex
described experimental objectives
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\textcolor{red}{Lucas: describe here the experimental objectives.}
+Using the state-space models given in Section~\ref{exp:benchmarks}, 
+our evaluation has the following two experimental goals:
+
+\begin{enumerate}
+
+\item[EG1] \textbf{(Performance)} Show that both the multi-staged and the abstraction-based
+CEGIS approaches are able to generate FWL digital controllers using floating-point arithmetic 
+in a reasonable amount of time.
+
+\item[EG2] \textbf{(sanity check)} Confirm the
+stability and safety of the synthesized controllers outside of our model.
+
+\end{enumerate}
 

### 2018-02-19 automatica/paper.tex
improved the description of the benchmarks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-Our benchmark suite consists of 18 MIMO models extracted from the 
+Our benchmark suite consists of 18 SISO models extracted from the 
 control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS};
-these models are discretized with different sample times, which thus leads to $167$ different benchmarks
+these models are discretized with different sample times, leading to $167$ different benchmarks
 to evaluate our proposal approach.
 
-The DC motor benchmark describes the velocity dynamics of a basic 
-brushed direct current electrical machine. The automotive cruise control system 
-benchmark is used to keep constant the speed of an automobile, 
-tracking a desired speed reference, compensating disturbances and 
-uncertainties related to relief and terrain.The pendulum benchmark consists of a swinging point mass suspended from 
-a frictionless pivot by means of a negligible mass rod, while the inverted pendulum 
-benchmark is a system similar to the pendulum, but the point 
+The \textit{DC motor} plant describes the velocity dynamics of a basic 
+brushed direct current electrical machine. 
+The \textit{automotive cruise control system} plant is used to keep constant 
+the speed of an automobile, tracking a desired speed reference, 
+compensating disturbances and uncertainties related to relief and terrain.
+The \textit{pendulum} plant consists of a swinging point mass suspended from 
+a frictionless pivot by means of a negligible mass rod, while the 
+\textit{inverted pendulum} plant describes a system similar to the pendulum, but the point 
 mass must be equilibrated above the pivot point, which is mounted on an 
@@
 
-The magnetic suspension benchmark corresponds to the discrete model of a 
+The \textit{magnetic suspension} plant corresponds to the discrete model of a 
 simple eletromagnet-ball system, where a steel ball is levitated in air 
 by the action of an electromagnetic force generated by an electromagnet.
-The magnetic pointer benchmark is a pointer employed in analogue 
+The \textit{magnetic pointer} plant describes a pointer employed in analogue 
 gauges and indicators, whose angular position dynamics is controlled 
-by a magnetic field. The 1/4 car suspension benchmark corresponds to the model of a single 
+by a magnetic field. 
+The \textit{1/4 car suspension} plant corresponds to the model of a single 
 wheel suspension system of a car, {\it i.e.}, the relative motion dynamics 
@@
 
-The computer tape driver benchmark is a computer storage device used to read and write 
-data on magnetic tapes. The acrobot benchmark corresponds to the model of a two-link 
+The \textit{computer tape driver} plant describes a computer storage device used to read and write 
+data on magnetic tapes. The \textit{acrobot} plant corresponds to the model of a two-link 
 underactuated robot manipulator, named acrobot, linearized by partial 
-feedback linearization~\cite{acrobot}. The high-order system benchmarks correspond to a series of high-order control system model 
+feedback linearization~\cite{acrobot}. 
+The \textit{high-order system} plants correspond to a series of high-order control system model 
 generally used as example for order reduction techniques~\cite{CHEN1979389}.
-Here, these benchmarks are used to evaluate the proposed control 
-synthesis technique under critical conditions, {\it i.e.}, with a large number of parameters 
-to be considered.
-
-The continuous stirred tank reactor benchmark describes a linear model for PH dynamics of a PH 
+%Here, these benchmarks are used to evaluate the proposed control 
+%synthesis technique under critical conditions, {\it i.e.}, with a large number of parameters 
+%to be considered.
+
+The \textit{continuous stirred tank reactor} plant describes a linear model for PH dynamics of a PH 
 neutralization process of an aqueous solution of sodium acetate with 
-hydrochloric acid in a continuous flow stirred-tank reactor. The flexible beam benchmark is a plant 
-usually employed in vibration studies; it consists of a flexible metallic structure with piezoceramic actuators and sensors.
-The helicopter longitudinal motion benchmark describes the dynamics of 
+hydrochloric acid in a continuous flow stirred-tank reactor. 
+The \textit{flexible beam} is a plant employed in vibration studies; the physical system consists of a flexible 
+metallic structure with piezoceramic actuators and sensors.
+The \textit{helicopter longitudinal motion} plant describes the dynamics of 
 transitional motion with respect to a longitudinal plane and the 
 rotational motion around the longitudinal axis.
-The USCG cutter tampa heading angle benchmark describes the heading angle 
-dynamics of a Coast Guard cutter. The voltage regulator benchmark~\cite{KOKOTOVIC198023} consists 
-of a linear model of a synchronous machine connected to an  infinite bus.
-
-The guidance control system benchmark is another high-order system 
+The \textit{USCG cutter tampa heading angle} plant describes the heading angle 
+dynamics of a Coast Guard cutter. 
+The \textit{voltage regulator} plant consists of a linear model of a synchronous 
+machine connected to an  infinite bus~\cite{KOKOTOVIC198023}.
+
+The \textit{guidance control system} plant is another high-order system 
 model used by Chen et al.~\cite{CHEN1979389}  to evaluate reduction 
-techniques. Guidance systems are used to determine the path of an 
-autonomous vehicle movement.
-
-The satellite attitude control system benchmark describes the dynamics of a satellite attitude, 
+techniques, which is used to determine the path of an autonomous vehicle movement.
+The \textit{satellite attitude control system} plant describes the dynamics of a satellite attitude, 
 {\it i.e.}, the orientation angles. An attitude control system must 
 maintain the desired orientation of a satellite with respect to an 
-inertial frame during all the excursion. The springer-mass damper system benchmark 
-is classic model for several mechanical systems dynamics. This benchmark describes a mass,
-which is fixed to a node by means of a springer and moves under the action of a 
-input force, damping, and elastic force.
+inertial frame during all the excursion. 
+The \textit{springer-mass damper system} plant is classic model for several mechanical 
+systems dynamics. This benchmark describes a mass, which is fixed to a node by means 
+of a springer and moves under the action of a input force, damping, and elastic force.
 

### 2018-02-19 automatica/paper.tex
change cristina's affiliation + changes to the intro

@@
 %\newcommand{\tool}{{\sf DSSynth}\xspace}
+\newcommand{\addtodo}[1]{\textcolor{red}{[#1]}}
 \newcommand{\mat}[1]{\boldsymbol{#1}}
@@
 \author[oxford,manaus]{Lucas Cordeiro}\ead{lucas.cordeiro@cs.ox.ac.uk},
-\author[oxford]{Cristina David}\ead{cristina.david@cs.ox.ac.uk},
+\author[cambridge]{Cristina David}\ead{cd652@cam.ac.uk},
 \author[oxford]{Pascal Kessel}\ead{pascal.kesseli@stx.ox.ac.uk},
@@
 \address[oxford]{University of Oxford, UK}
+\address[cambridge]{University of Cambridge, UK}
 \address[manaus]{Federal University of Amazonas, Brazil}
@@
 life sciences, environmental control and robotics~\cite{astrom1997computer,
-Franklin15}.  Correct synthesis is non-trivial, even in cases with
+Franklin15}.  Correct synthesis of control software
+for such platforms is non-trivial, even in cases with
 restriceted dynamics.  We examine the case of Linear Time Invariant (LTI)
-Models, for which the synthesis of controllers is well understood.  However,
+models, for which the synthesis of controllers is well understood.  However,
 the use of digital control architectures adds new challenges caused by
@@
 
-While research on digital control is well developed~\cite{astrom1997computer},
-automated and sound control synthesis is challenging, particularly when the
-synthesis objective goes beyond classical stability.  There are recent methods
-for verifying reachability properties of a given controller~\cite{FLD+11}.
-However, these methods have not been generalized to control synthesis.  
-Note that a synthesis algorithm that guarantees stability does not
-ensure safety: the system might transitively visit an unsafe state resulting
-in unrecoverable failure. Programming expertise is a key
-barrier to broad adoption of correct digital controllers, and requires
-considerable knowledge outside of the expertise of many control engineers.
-
-Beyond classical a-posteriori validation in digital control, there has been
-plenty of previous work aiming at \emph{verifying} a given designed
-controller, which however broadly lack automation.  Recent work has studied
-the stability of digital controllers considering implementation aspects,
-i.e., fixed-point arithmetic and the word length~\cite{Bessa16}.  They
-exploit advances in bit-accurate verification of C programs to obtain a
-verifier for software-implemented digital control.
-
-By contrast, we leverage a very recent step-change in the automation and
-scalability of \emph{program synthesis}.  Program synthesis engines use a
-specification as the starting point, and subsequently generate a sequence of
-candidate programs from a given template.  The candidate programs are
-iteratively refined to eventually satisfy the specification.  Program
+In this paper we develop an automatic technique for generating digital
+controllers for a given continuous plant model that are correct by
+construction.  Specifically, we synthesize stable and safe,
+software-implemented embedded controllers.  Due to the complexity of
+such closed-loop systems, we focus on linear models with known
+configurations, and perform parametric synthesis of controllers
+meeting a number of properties that define their desired behavior.
+
+%% While research on digital control is well developed~\cite{astrom1997computer},
+%% automated and sound control synthesis is challenging, particularly when the
+%% synthesis objective goes beyond classical stability.  There are recent methods
+%% for verifying reachability properties of a given controller~\cite{FLD+11}.
+%% However, these methods have not been generalized to control synthesis.  
+%% Note that a synthesis algorithm that guarantees stability does not
+%% ensure safety: the system might transitively visit an unsafe state resulting
+%% in unrecoverable failure. %% Programming expertise is a key
+%% barrier to broad adoption of correct digital controllers, and requires
+%% considerable knowledge outside of the expertise of many control engineers.
+
+%% Beyond classical a-posteriori validation in digital control, there has been
+%% plenty of previous work aiming at \emph{verifying} a given designed
+%% controller, which however broadly lack automation.  Recent work has studied
+%% the stability of digital controllers considering implementation aspects,
+%% i.e., fixed-point arithmetic and the word length~\cite{Bessa16}.  They
+%% exploit advances in bit-accurate verification of C programs to obtain a
+%% verifier for software-implemented digital control.
+
+\addtodo{change this}
+For this purpose, we leverage a very recent step-change in the automation and
+scalability of \emph{program synthesis}.  %% Program synthesis engines use a
+%% specification as the starting point, and subsequently generate a sequence of
+%% candidate programs from a given template.  The candidate programs are
+%% iteratively refined to eventually satisfy the specification.
+Program
 synthesizers implementing Counter-Example Guided Inductive Synthesis
@@
 
-By combining state-of-the-art synthesis engines we present a tool that
-automatically generates digital controllers for a given continuous plant
-model that are correct by construction.  This approach delivers a high
-degree of automation, promises to reduce the cost and time of development of
-digital control dramatically, and requires considerably less expertise than
-a-posteriori verification.  Specifically, we synthesize stable,
-software-implemented embedded controllers along with a model of a physical
-plant.  Due to the complexity of such closed-loop systems, in this work we
-focus on linear models with known configurations, and perform parametric
-synthesis of stabilizing digital controllers with a number of properties that
-define their desired behaviour.
+%% By combining state-of-the-art synthesis engines we present a tool that
+%% automatically generates digital controllers for a given continuous plant
+%% model that are correct by construction.  This approach delivers a high
+%% degree of automation, promises to reduce the cost and time of development of
+%% digital control dramatically, and requires considerably less expertise than
+%% a-posteriori verification.  Specifically, we synthesize stable,
+%% software-implemented embedded controllers along with a model of a physical
+%% plant.  Due to the complexity of such closed-loop systems, in this work we
+%% focus on linear models with known configurations, and perform parametric
+%% synthesis of stabilizing digital controllers with a number of properties that
+%% define their desired behaviour.
 
@@
 
-Using state of the art verifiers, we evaluate these models against
-automatically synthesised controllers using CEGIS-based synsthesis that
-incorporate the above mentioned artifacts in different models of
-Single-Input/Single-Output (SISO) systems.  We offer three modes of
+%% Using state of the art verifiers, we evaluate these models against
+%% automatically synthesised controllers using CEGIS-based synsthesis that
+%% incorporate the above mentioned artifacts in different models of
+%% Single-Input/Single-Output (SISO) systems.
+\addtodo{I guess this should be two}
+We offer three modes of
 operation that address different aspects of the problem.

### 2018-02-19 automatica/paper.tex
abstract + comments

@@
 \begin{abstract}                          % Abstract of not more than 200 words.
-\textcolor{red}{Cristina: Can you please write an initial version of the abstract.}
+%\textcolor{red}{Cristina: Can you please write an initial version of the abstract.}
+We present a sound and automated approach to synthesizing safe,
+digital controllers for physical plants represented as linear,
+time-invariant models. Models are defined as differential equations
+with inputs, evolving over a continuous state space. The synthesis
+accounts for errors caused by the digitization effects introduced by
+the controller. Our approach uses counterexample-guided inductive
+synthesis (CEGIS): an inductive generalisation phase produces a
+possible solution that is known to stabilize the system but that may
+not be safe for all initial conditions. Safety is then verified either
+via BMC or abstract acceleration; if the verification step fails, a
+counterexample is provided to the inductive generalisation and the
+process iterates until a safe controller is obtained.  We demonstrate
+the practical value of this approach by automatically synthesizing
+safe controllers for physical plant models from the digital control
+literature.
 \end{abstract}
@@
 
-Modern implementations of embedded control systems have proliferated with
-the availability of low-cost devices that can perform highly non-trivial
-control tasks, with significant impact in numerous application areas such as
-life sciences, environmental control and robotics~\cite{astrom1997computer,
-Franklin15}.  Correct synthesis of control software
-for such platforms is non-trivial, even in cases with
-restriceted dynamics.  We examine the case of Linear Time Invariant (LTI)
-models, for which the synthesis of controllers is well understood.  However,
-the use of digital control architectures adds new challenges caused by
-artifacts specific to digital control, such as the effects of
-finite-precision arithmetic, time discretization and quantization noise
-introduced by A/D and D/A conversion.
+Modern implementations of embedded control systems have proliferated
+with the availability of low-cost devices that can perform highly
+non-trivial control tasks, with significant impact in numerous
+application areas such as life sciences, environmental control and
+robotics~\cite{astrom1997computer, Franklin15}.  Correct synthesis of
+control software for such platforms is non-trivial, even in cases with
+restriceted dynamics.  We examine the case of Linear Time Invariant
+(LTI) models, for which the synthesis of controllers is well
+understood.  However, the use of digital control architectures adds
+new challenges caused by artifacts specific to digital control, such
+as the effects of finite-precision arithmetic, time discretization and
+quantization noise introduced by A/D and D/A conversion.
 
@@
 
-\addtodo{change this}
+\addtodo{CD: change this}
 For this purpose, we leverage a very recent step-change in the automation and
@@
 %% Single-Input/Single-Output (SISO) systems.
-\addtodo{I guess this should be two}
+\addtodo{CD: I guess this should be two}
 We offer three modes of
@@
 
+\addtodo{CD: the novelty compared to CAV'17 needs to be clarified}
 In summary, this paper makes the following original contributions.

### 2018-02-20 automatica/paper.tex
more changes to the intro

@@
 %% Single-Input/Single-Output (SISO) systems.
-\addtodo{CD: I guess this should be two}
-We offer three modes of
-operation that address different aspects of the problem.
-
-{\em The first  approach} uses a transfer-function based analysis that
-solves the problem of robust stability for closed loop systems for a
-collection of unstable plants.  Inthis case, there is no safety
-specification since we are working in the frequency domain.
-
-{\em The second approach} uses a na\"ive technique that starts by devising a
+In this paper we present two novel approaches for the synthesis of digital controllers,
+which we briefly describe next.
+%% offer three modes of
+%% operation that address different aspects of the problem.
+%% {\em The first  approach} uses a transfer-function based analysis that
+%% solves the problem of robust stability for closed loop systems for a
+%% collection of unstable plants.  Inthis case, there is no safety
+%% specification since we are working in the frequency domain.
+{\em The first approach} uses a na\"ive technique that starts by devising a
 digital controller that stabilizes the system while remaining safe for a
@@
 
-Instead of unfolding the dynamics, {\em the third approach}
+Instead of unfolding the dynamics, {\em the second approach}
 employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to
@@
 
+  % Additions from CAV:
+  % continuous time
+  % response time
+  % floating point ?
 \item We automatically generate {\em correct-by-construction} digital
@@
   synthesis is non-trivial and addresses challenges specific to control
-  systems, such as quantizers and FWL.  In particular, we
-  have found that a two-stage verification engine that continuously refines
-  the precision of the fixed-point representation of the plant yields a
-  speed-up of two orders of magnitude over a conventional one-stage
-  verification engine.
-%
-\item  We compute state-feedback controllers that 
+  systems, such as quantizers and FWL.  %% In particular, we
+  %% have found that a two-stage verification engine that continuously refines
+  %% the precision of the fixed-point representation of the plant yields a
+  %% speed-up of two orders of magnitude over a conventional one-stage
+  %% verification engine.
+%
+  %\item  We compute
+  The computed state-feedback controllers 
   guarantee a given safety property alongside stability and response time
@@
 %
-\item We provide three novel algorithms: the first, na\"ive one, relies on
+\item We provide two novel algorithms: the first, na\"ive one, relies on
   an unfolding of the dynamics up to a completeness threshold, while the
   second one is abstraction-based and leverages abstraction refinement and
-  acceleration to improve scalability while retaining soundness.  A third
-  algorithm evaluates systems using transfer functions where no state-space
-  description is given.  All three approaches provide sound synthesis of
+  acceleration to improve scalability while retaining soundness.  %% A third
+  %% algorithm evaluates systems using transfer functions where no state-space
+  %% description is given.
+  Both approaches provide sound synthesis of
   feedback controllers and consider the various sources of imprecision in

### 2018-02-20 automatica/paper.tex
+ comment

@@
   % continuous time
-  % response time
-  % floating point ?
+  % response time ?
+  % floating point 
 \item We automatically generate {\em correct-by-construction} digital
@@
   guarantee a given safety property alongside stability and response time
-  specifications.  Existing methods for controller synthesis rely on transfer
+  specifications \addtodo{CD: Do we actually consider response time in this paper?}.
+  Existing methods for controller synthesis rely on transfer
   function representations, which are inadequate to prove safety requirements.

### 2018-02-26 automatica/paper.tex
removed response time and transient analysis terms
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2018-02-20 automatica/paper.tex
@@
 \begin{keyword}                           % Five to ten keywords,  
-Digital Control; A/D converters; Control System Synthesis; Transient Analysis; Safety Analysis; Quantization Errors; Sampling.               % chosen from the IFAC 
+Digital Control; A/D converters; Control System Synthesis; Safety Analysis; Quantization Errors; Sampling.               % chosen from the IFAC 
 \end{keyword}                             % keyword list or with the 
@@
 precision domain, while reasoning about high level properties such as
-stability, robustness, safety, and response time, which define the behaviour
+stability, robustness, and safety, which define the behaviour
 of the system.  In particular, safety requirements are frequently overlooked
@@
   % continuous time
-  % response time
-  % floating point ?
+  % floating point 
 \item We automatically generate {\em correct-by-construction} digital
@@
   The computed state-feedback controllers 
-  guarantee a given safety property alongside stability and response time
+  guarantee a given safety property alongside stability and safety
   specifications. Existing methods for controller synthesis rely on transfer
@@
 %-------------------------------
-\subsection{Formal specification of transient response} 
-\label{ssec:transientspecification}
-%-------------------------------
-
-In a SISO system, there are 2 values that typically define the response-time of the system (using a step response).
-\begin{enumerate}
-\item The \emph{rise time} is defined as the time it takes the output to reach a percentage (eg $90\%$) of the target value given a step chnage in the input.
-\item The \emph{settling time} is defined as the time it takes the output to stabilize within a margin of the target value (eg $10\%$).
-\end{enumerate} 
-In the case of first and second order systems (with ), the decay is governed by the equations 
-\begin{align*}
-&y_{decay}=
-&\left\{
-\begin{array}{cc}
-e^{-|\omega| t}& 1^{st} order\\
-e^{\zeta |\omega| t}\left(\frac{\sin\left(|\omega| t\sqrt{1-\zeta^2}+\sin^{-1}\sqrt{1-\zeta^2}\right)}{\sqrt{1-\zeta^2}} \right)&\zeta<1\\
-e^{-|\omega| t}-|\omega| t e^{-|\omega| t}&\zeta=1\\
-\frac{|\omega| e^{-|\omega_2| t}-|\omega_2| e^{-|\omega| t}}{|\omega|-|\omega_2|}&\zeta>1\end{array}\right.
-\end{align*}
-where $|\omega|$ and $|\omega_2|$ are the magnitudes of the eigenvalues (roots) of the system and  $\zeta=-\cos(\theta)$ where $\theta$ is the polar angle of the conjugate pair if it exists ($\zeta \geq 1$ if it doesn't).
-These equations become increasingly complicated for higher order systems.
+%\subsection{Formal specification of transient response} 
+%\label{ssec:transientspecification}
+%-------------------------------
+
+%In a SISO system, there are 2 values that typically define the response-time of the system (using a step response).
+%\begin{enumerate}
+%\item The \emph{rise time} is defined as the time it takes the output to reach a percentage (eg $90\%$) of the target value given a step chnage in the input.
+%\item The \emph{settling time} is defined as the time it takes the output to stabilize within a margin of the target value (eg $10\%$).
+%\end{enumerate} 
+%In the case of first and second order systems (with ), the decay is governed by the equations 
+%\begin{align*}
+%&y_{decay}=
+%&\left\{
+%\begin{array}{cc}
+%e^{-|\omega| t}& 1^{st} order\\
+%e^{\zeta |\omega| t}\left(\frac{\sin\left(|\omega| t\sqrt{1-\zeta^2}+\sin^{-1}\sqrt{1-\zeta^2}\right)}{\sqrt{1-\zeta^2}} \right)&\zeta<1\\
+%e^{-|\omega| t}-|\omega| t e^{-|\omega| t}&\zeta=1\\
+%\frac{|\omega| e^{-|\omega_2| t}-|\omega_2| e^{-|\omega| t}}{|\omega|-|\omega_2|}&\zeta>1\end{array}\right.
+%\end{align*}
+%where $|\omega|$ and $|\omega_2|$ are the magnitudes of the eigenvalues (roots) of the system and  $\zeta=-\cos(\theta)$ where $\theta$ is the polar angle of the conjugate pair if it exists ($\zeta \geq 1$ if it doesn't).
+%These equations become increasingly complicated for higher order systems.
 However, we note their strong dependency on the magnitude of the eigenvalues, and use this property to define an upperbound on the decay function.
-All of the above equations will decay faster than $e^{-|\omega| t}$ given $|\omega| < |\omega_2|$, hence we may use this function as our upper bound.
-\begin{theorem}
-Given a set of eigenvalues for a discrete time model of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1\ n]$, the settling time of the system is upperbounded by
-\begin{equation}
-t_s<-log_{|\overline{\lambda}|}({p_s}) : |\overline{\lambda}| =\max(|\lambda_i|) \wedge |\overline{\lambda}|<1,\ \forall i \in [1\ n]
-\label{eq:set_time}
-\end{equation}
-where $0\leq p_s \leq 1$ is the desired percentage of the target within to remain after $t_s$.
-\end{theorem} 
-\begin{proof}
-Given a closed loop single output LTI system of order $n$ with dynamics
-\begin{equation}
-\left\{\begin{array}{c}\vec{x}_k=\mat{A}\vec{x}_{k-1}\\ \vec{y}_k=\mat{C}\vec{x}_k\end{array}\right.
+%All of the above equations will decay faster than $e^{-|\omega| t}$ given $|\omega| < |\omega_2|$, hence we may use this function as our upper bound.
+%\begin{theorem}
+%Given a set of eigenvalues for a discrete time model of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1\ n]$, the settling time of the system is upperbounded by
+%\begin{equation}
+%t_s<-log_{|\overline{\lambda}|}({p_s}) : |\overline{\lambda}| =\max(|\lambda_i|) \wedge |\overline{\lambda}|<1,\ \forall i \in [1\ n]
+%\label{eq:set_time}
+%\end{equation}
+%where $0\leq p_s \leq 1$ is the desired percentage of the target within to remain after $t_s$.
+%\end{theorem} 
+%\begin{proof}
+%Given a closed loop single output LTI system of order $n$ with dynamics
+%\begin{equation}
+%\left\{\begin{array}{c}\vec{x}_k=\mat{A}\vec{x}_{k-1}\\ \vec{y}_k=\mat{C}\vec{x}_k\end{array}\right.
 \Rightarrow \left\{ \begin{array}{c}\vec{x}_k'=\mat{J}\vec{x}_{k-1}'\\ \vec{y}_k=\mat{C}\mat{S}\vec{x}_k'\end{array}\right.
 : \left\{ \begin{array}{c}\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \\ \vec{x}_k'=\mat{S}^{-1}\vec{x}_k\end{array}\right.
-\label{eq:eigendynamics}
-\end{equation}
-%
-the output decay is a linear combination of the decay of eigenvalues or
-eigenvalue pairs.  
-Let $\mat{C}'\in \mathbb{R}^{1 \times n}=\mat{C}\mat{S}$.
+%\label{eq:eigendynamics}
+%\end{equation}
+%
+%the output decay is a linear combination of the decay of eigenvalues or
+%eigenvalue pairs.  
+%Let $\mat{C}'\in \mathbb{R}^{1 \times n}=\mat{C}\mat{S}$.
 Since $\mat{C}'$ is constant, the output $y_k$ is a linear combination of the states $\vec{x}'_k$.
 We accelerate equation \eqref{eq:eigendynamics} to obtain
-\begin{align}
-%\vec{x}_k'&=\mat{J}^k\vec{x}_0' \\
-y_k&=\mat{C}'\mat{J}^k\vec{x}_0 = \sum_{i=0}^n \left( c_i \lambda_i^k + c_{il}\binom{k}{l} \lambda_i^{k-l}\right)\\
-|y_k|&\leq \sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right||\lambda_i^k|
-\end{align}
-where the second  part of the equation corresponds to the upper diagonal terms of the Jordan blocks. We also have $|\lambda_i^k|\leq |\overline{\omega}^k|$,hence
-\begin{align}
-|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right|
-\end{align}
-Since we are synthesising the eigenvalues, rather than solve this formula for complex Jordan Shapes, we will restrict our synthesiser to provide solutions with distinct eigenvalues (which is by far the most common case).
+%\begin{align}
+%y_k&=\mat{C}'\mat{J}^k\vec{x}_0 = \sum_{i=0}^n \left( c_i \lambda_i^k + c_{il}\binom{k}{l} \lambda_i^{k-l}\right)\\
+%|y_k|&\leq \sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right||\lambda_i^k|
+%\end{align}
+%where the second  part of the equation corresponds to the upper diagonal terms of the Jordan blocks. We also have $|\lambda_i^k|\leq |\overline{\omega}^k|$,hence
+%\begin{align}
+%|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right|
+%\end{align}
+%Since we are synthesising the eigenvalues, rather than solve this formula for complex Jordan Shapes, we will restrict our synthesiser to provide solutions with distinct eigenvalues (which is by far the most common case).
 Therefore the right hand terms dissappear and we end up with
-\begin{align}
-|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n |c_i|
-\end{align}
-
-Hence the overall decay of the system is always smaller
-than $p=e^{-|\overline{\omega}| t}$ where $0\leq p\leq 1$ is the remaining
-percentage of the decay expressed.  reversing we have
-$t=-\frac{ln(p)}{|\overline{\omega}|}=-\frac{ln(p)}{ln(|\overline{\lambda}|)}$. 
-replacing for $p_s$ , $t_s$, and $\overline{\lambda}$ we get equation
-\eqref{eq:set_time}
-%
-\qed
-\end{proof}
-%
-We may now use this limit to express a constraint in terms of the
-coefficients for our synthesis process.  Let
-%
-\begin{equation}
-P=\prod_{i=0}^n (s-\lambda_i)=\sum_{j=0}^n c_js^j.
-\end{equation}
-%
-We use Jury's criterion to limit $|\lambda_i| \leq 1$.  Let us now define a
-transformation $\lambda_i'=\frac{\lambda_i}{\overline{\lambda}}$.  We want
-to ensure $\lambda_i' \leq 1$ which can be done by applying Jury's criterion
-to $P'=\prod_{i=0}^n (s-\lambda_i')=\sum_{j=0}^n c_j's^j$ where $c_j'$ are
-unknown.  However, if we replace for $\lambda_i$, we obtain
-%
-\begin{equation}
-P'=\prod_{i=0}^n (s-\lambda_i')=\prod_{i=0}^n \left(s-\frac{\lambda_i}{\overline{\lambda}}\right)=\sum_{j=0}^n \frac{c_j}{\overline{\lambda}^{n-j}}s^j
-\end{equation}
-%
-where all members are known, we may now synthesise coefficients that ensure
-the eigenvalues are smaller than a desired magnitue, thus ensuring that the
-settling time is too.
+%\begin{align}
+%|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n |c_i|
+%\end{align}
+
+%Hence the overall decay of the system is always smaller
+%than $p=e^{-|\overline{\omega}| t}$ where $0\leq p\leq 1$ is the remaining
+%percentage of the decay expressed.  reversing we have
+%$t=-\frac{ln(p)}{|\overline{\omega}|}=-\frac{ln(p)}{ln(|\overline{\lambda}|)}$. 
+%replacing for $p_s$ , $t_s$, and $\overline{\lambda}$ we get equation
+%\eqref{eq:set_time}
+%
+%\qed
+%\end{proof}
+%
+%We may now use this limit to express a constraint in terms of the
+%coefficients for our synthesis process.  Let
+%
+%\begin{equation}
+%P=\prod_{i=0}^n (s-\lambda_i)=\sum_{j=0}^n c_js^j.
+%\end{equation}
+%
+%We use Jury's criterion to limit $|\lambda_i| \leq 1$.  Let us now define a
+%transformation $\lambda_i'=\frac{\lambda_i}{\overline{\lambda}}$.  We want
+%to ensure $\lambda_i' \leq 1$ which can be done by applying Jury's criterion
+%to $P'=\prod_{i=0}^n (s-\lambda_i')=\sum_{j=0}^n c_j's^j$ where $c_j'$ are
+%unknown.  However, if we replace for $\lambda_i$, we obtain
+%
+%\begin{equation}
+%P'=\prod_{i=0}^n (s-\lambda_i')=\prod_{i=0}^n \left(s-\frac{\lambda_i}{\overline{\lambda}}\right)=\sum_{j=0}^n \frac{c_j}{\overline{\lambda}^{n-j}}s^j
+%\end{equation}
+%
+%where all members are known, we may now synthesise coefficients that ensure
+%the eigenvalues are smaller than a desired magnitue, thus ensuring that the
+%settling time is too.
 

### 2018-02-26 automatica/paper.tex
removed sections related to Observed Systems
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \renewcommand{\vec}[1]{\boldsymbol{#1}}
+\newcommand{\comment}[1]{}
 \newtheorem{lemma}{Lemma}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Verification of a Controllable Observed System}\label{sec:cof_verification}
+%\section{Verification of a Controllable Observed System}\label{sec:cof_verification}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 
-\textcolor{red}{Dario: Do we still need this section? Where would the continuous time proof fit?}
-
-\begin{figure*}[htb]
-\centering
-
-\tikzset{add/.style n args={4}{
-    minimum width=6mm,
-    path picture={
-        \draw[circle] 
-            (path picture bounding box.south east) -- (path picture bounding box.north west)
-            (path picture bounding box.south west) -- (path picture bounding box.north east);
-        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
-        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
-        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
-        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
-        }
-    }
- }
-
-\resizebox{1.0\textwidth}{!}{
- \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
-     semithick, initial text=, ampersand replacement=\&,]
-
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
-    \node[draw=none] (r) {$r_k$};
-    \node[rectangle,draw,
-	minimum width=1cm,
-	minimum height=1cm,] (gain)at ([xshift=1.2cm]r) {\sc $k_r$};
-
-   \& \node[circle,add={-}{+}{}{}] (circle) {};
-   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$u_k$};
-   \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Kd) at ([xshift=0,yshift=-5.5cm]circle)  {\sc $\mat{K}_d$};
-   \coordinate (kdsouth) at ([yshift=-3cm]Kd);
-
-   \& complexnode/.pic={ 
-      \node[rectangle,dashed,draw,minimum width=3cm,minimum height=1.6cm,label=\textbf{DAC}] (dac) {};
-     \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
-     \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
-     \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
-     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {\sc ZOH};
-   }
-
-   \& complexnode/.pic={ 
-      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2.5cm,yshift=.5cm]plant.center)  {\sc $\mat{B}$};
-      \node[draw=none] (u) at ([xshift=-1cm,yshift=.15cm]B)  {$u(t)$};
-      \node[circle,add={+}{+}{}{}] (p1) at ([xshift=-1.3cm,yshift=.5cm]plant.center) {};
-      \node[draw=none] (xdot) at ([xshift=.85cm,yshift=.15cm]p1)  {$\dot{\vec{x}}(t)$};   
-      \node[rectangle,draw,minimum width=1cm] (int) at ([xshift=.5cm,yshift=.5cm]plant.center) {\sc $\int$};
-      \coordinate (xsouth) at ([xshift=1cm]int);
-      \node[draw=none] (x) at ([xshift=1cm,yshift=.15cm]int)  {$\vec{x}(t)$};   
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (C) at ([xshift=2.7cm,yshift=.5cm]plant.center)  {\sc $\mat{C}$};
-      \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]C)  {$\vec{y}(t)$};   
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (A) at ([xshift=.5cm,yshift=-1cm]plant.center)  {\sc $\mat{A}$};
-      \coordinate (aeast) at ([xshift=1cm]A);
-      \coordinate (awest) at ([xshift=-1.8cm]A);
-    }
-
-   complexnode/.pic={ 
-      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=5cm,label=\textbf{Observer}] (observer)  at ([yshift=-5cm]plant.center) {};
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Bd) at ([xshift=-2.5cm]observer.center)  {\sc $\mat{B}_o$};
-      \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]Bd)  {$u_k$};
-      \node[circle,add={+}{+}{+}{}] (o1) at ([xshift=-1.3cm]observer.center) {};
-      \node[draw=none] (xd) at ([xshift=.85cm,yshift=.15cm]o1)  {$\hat{\vec{x}}_{k+1}$};   
-      \node[rectangle,draw,minimum width=1cm] (delay) at ([xshift=.5cm]observer.center) {\sc $z^{-1}$};
-      \coordinate (xdsouth) at ([xshift=1.3cm]delay);
-      \coordinate (fbsouth) at ([xshift=1.3cm,yshift=-3cm]delay);
-      \node[draw=none] (xdp) at ([xshift=1cm,yshift=.15cm]delay)  {$\hat{\vec{x}}_k$};   
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Cd) at ([xshift=2.7cm]observer.center)  {\sc $\mat{C}_o$};
-      \node[draw=none] (y) at ([xshift=.4cm,yshift=.8cm]Cd)  {$\hat{\vec{y}}_k$};   
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ad) at ([xshift=.5cm,yshift=-1.5cm]observer.center)  {\sc $\mat{A}_o$};
-      \coordinate (adeast) at ([xshift=1.3cm]Ad);
-      \coordinate (adwest) at ([xshift=-1.8cm]Ad);
-      \node[circle,add={-}{}{}{+}] (o2) at ([xshift=2.7cm,yshift=1.5cm]observer.center) {};
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ld) at ([xshift=.5cm,yshift=1.5cm]observer.center)  {\sc $\mat{L}_d$};
-      \coordinate (ldwest) at ([xshift=-1.8cm]Ld);
-      \coordinate (bdwest) at ([xshift=-5.5cm]Bd);
-      \coordinate (uksouth) at ([xshift=-5.5cm,yshift=5.5cm]Bd);
-      \coordinate (o2east) at ([xshift=6.3cm]o2);
-    }
-
-   \& complexnode/.pic={ 
-     \node[rectangle,dashed,draw,minimum width=3.5cm,minimum height=1.6cm,label=\textbf{ADC},] (adc) {};
-     \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
-     \coordinate (switch1) at ([xshift=-1cm]adc.center);
-     \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
-     \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
-     \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
-     \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
-     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]q1)  {$\vec{y}_k$};       
-     \coordinate (ykeast) at ([xshift=1.9cm]q1);
-   } 
-   \& \coordinate (aux1);
-   \& \\
-  };
-
-  \path[->] (v1) edge (q1.south);
-  \path[->] (v2) edge (q2.south);
-  \path[->] (r) edge (gain.west);
-  \path[->] (gain.east) edge (circle.west);
-  \path[->] (circle.east) edge (q2.west);
-  \path       (q2.east) edge (zoh.west);
-  \path[->] (zoh.east) edge (B.west);
-  \path
-   (B.east) edge (p1.west)
-   (p1.east) edge (int.west)
-   (xsouth) edge (aeast)
-   (aeast) edge (A.east)
-   (A.west) edge (awest)
-   (awest) edge (p1.south)
-   (int.east) edge (C.west)
-   (C.east) edge (switch1.west)
-   (switch2) edge (q1.west);
-  \path
-   (q1.east) edge (ykeast)
-   (ykeast) edge (o2east);
-  \path       (uksouth) edge (bdwest);
-  \path[->] (bdwest) edge (Bd.west);
-  \path
-   (Bd.east) edge (o1.west)
-   (o1.east) edge (delay.west)
-   (xdsouth) edge (adeast)
-   (adeast) edge (Ad.east)
-   (Ad.west) edge (adwest)
-   (adwest) edge (o1.south)
-   (o2.west) edge (Ld.east)
-   (Ld.west) edge (ldwest)
-   (ldwest) edge (o1.north)
-   (delay.east) edge (Cd.west)
-   (Cd.north) edge (o2.south)
-   (o2east) edge (o2.east)
-   (xdsouth) edge (fbsouth)
-   (fbsouth) edge (kdsouth);
-  \path[->]  (kdsouth) edge (Kd.south);
-  \path (Kd.north) edge (circle.south);
- \end{tikzpicture}
-}
- \caption{Closed-loop digital control system with observer\label{fig:observersystem}}
-\end{figure*}
+%\begin{figure*}[htb]
+%\centering
+
+%\tikzset{add/.style n args={4}{
+%    minimum width=6mm,
+%    path picture={
+%        \draw[circle] 
+%            (path picture bounding box.south east) -- (path picture bounding box.north west)
+%            (path picture bounding box.south west) -- (path picture bounding box.north east);
+%        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+%        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+%        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+%        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+%        }
+%    }
+% }
+
+%\resizebox{1.0\textwidth}{!}{
+% \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
+%     semithick, initial text=, ampersand replacement=\&,]
+
+%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
+%    \node[draw=none] (r) {$r_k$};
+%    \node[rectangle,draw,
+%	minimum width=1cm,
+%	minimum height=1cm,] (gain)at ([xshift=1.2cm]r) {\sc $k_r$};
+
+%   \& \node[circle,add={-}{+}{}{}] (circle) {};
+%   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$u_k$};
+%   \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Kd) at ([xshift=0,yshift=-5.5cm]circle)  {\sc $\mat{K}_d$};
+%   \coordinate (kdsouth) at ([yshift=-3cm]Kd);
+
+%   \& complexnode/.pic={ 
+%     \node[rectangle,dashed,draw,minimum width=3cm,minimum height=1.6cm,label=\textbf{DAC}] (dac) {};
+%     \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
+%     \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
+%     \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
+%     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {\sc ZOH};
+%   }
+
+%   \& complexnode/.pic={ 
+%      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};
+%      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2.5cm,yshift=.5cm]plant.center)  {\sc $\mat{B}$};
+%      \node[draw=none] (u) at ([xshift=-1cm,yshift=.15cm]B)  {$u(t)$};
+%      \node[circle,add={+}{+}{}{}] (p1) at ([xshift=-1.3cm,yshift=.5cm]plant.center) {};
+%      \node[draw=none] (xdot) at ([xshift=.85cm,yshift=.15cm]p1)  {$\dot{\vec{x}}(t)$};   
+%      \node[rectangle,draw,minimum width=1cm] (int) at ([xshift=.5cm,yshift=.5cm]plant.center) {\sc $\int$};
+%      \coordinate (xsouth) at ([xshift=1cm]int);
+%      \node[draw=none] (x) at ([xshift=1cm,yshift=.15cm]int)  {$\vec{x}(t)$};   
+%      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (C) at ([xshift=2.7cm,yshift=.5cm]plant.center)  {\sc $\mat{C}$};
+%      \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]C)  {$\vec{y}(t)$};   
+%      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (A) at ([xshift=.5cm,yshift=-1cm]plant.center)  {\sc $\mat{A}$};
+%      \coordinate (aeast) at ([xshift=1cm]A);
+%      \coordinate (awest) at ([xshift=-1.8cm]A);
+%    }
+
+%   complexnode/.pic={ 
+%      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=5cm,label=\textbf{Observer}] (observer)  at ([yshift=-5cm]plant.center) {};
+%      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Bd) at ([xshift=-2.5cm]observer.center)  {\sc $\mat{B}_o$};
+%      \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]Bd)  {$u_k$};
+%      \node[circle,add={+}{+}{+}{}] (o1) at ([xshift=-1.3cm]observer.center) {};
+%      \node[draw=none] (xd) at ([xshift=.85cm,yshift=.15cm]o1)  {$\hat{\vec{x}}_{k+1}$};   
+%      \node[rectangle,draw,minimum width=1cm] (delay) at ([xshift=.5cm]observer.center) {\sc $z^{-1}$};
+%      \coordinate (xdsouth) at ([xshift=1.3cm]delay);
+%      \coordinate (fbsouth) at ([xshift=1.3cm,yshift=-3cm]delay);
+%      \node[draw=none] (xdp) at ([xshift=1cm,yshift=.15cm]delay)  {$\hat{\vec{x}}_k$};   
+%      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Cd) at ([xshift=2.7cm]observer.center)  {\sc $\mat{C}_o$};
+%      \node[draw=none] (y) at ([xshift=.4cm,yshift=.8cm]Cd)  {$\hat{\vec{y}}_k$};   
+%      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ad) at ([xshift=.5cm,yshift=-1.5cm]observer.center)  {\sc $\mat{A}_o$};
+%      \coordinate (adeast) at ([xshift=1.3cm]Ad);
+%      \coordinate (adwest) at ([xshift=-1.8cm]Ad);
+%      \node[circle,add={-}{}{}{+}] (o2) at ([xshift=2.7cm,yshift=1.5cm]observer.center) {};
+%      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ld) at ([xshift=.5cm,yshift=1.5cm]observer.center)  {\sc $\mat{L}_d$};
+%      \coordinate (ldwest) at ([xshift=-1.8cm]Ld);
+%      \coordinate (bdwest) at ([xshift=-5.5cm]Bd);
+%      \coordinate (uksouth) at ([xshift=-5.5cm,yshift=5.5cm]Bd);
+%      \coordinate (o2east) at ([xshift=6.3cm]o2);
+%    }
+
+%   \& complexnode/.pic={ 
+%     \node[rectangle,dashed,draw,minimum width=3.5cm,minimum height=1.6cm,label=\textbf{ADC},] (adc) {};
+%     \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
+%     \coordinate (switch1) at ([xshift=-1cm]adc.center);
+%     \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
+%     \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
+%     \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
+%     \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
+%     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]q1)  {$\vec{y}_k$};       
+%     \coordinate (ykeast) at ([xshift=1.9cm]q1);
+%   } 
+%   \& \coordinate (aux1);
+%   \& \\
+%  };
+
+  %\path[->] (v1) edge (q1.south);
+  %\path[->] (v2) edge (q2.south);
+  %\path[->] (r) edge (gain.west);
+  %\path[->] (gain.east) edge (circle.west);
+  %\path[->] (circle.east) edge (q2.west);
+  %\path       (q2.east) edge (zoh.west);
+  %\path[->] (zoh.east) edge (B.west);
+  %\path
+  %(B.east) edge (p1.west)
+  %(p1.east) edge (int.west)
+%  (xsouth) edge (aeast)
+%   (aeast) edge (A.east)
+%   (A.west) edge (awest)
+%   (awest) edge (p1.south)
+%   (int.east) edge (C.west)
+%   (C.east) edge (switch1.west)
+%   (switch2) edge (q1.west);
+%  \path
+%   (q1.east) edge (ykeast)
+%   (ykeast) edge (o2east);
+%  \path       (uksouth) edge (bdwest);
+%  \path[->] (bdwest) edge (Bd.west);
+%  \path
+%   (Bd.east) edge (o1.west)
+%   (o1.east) edge (delay.west)
+%   (xdsouth) edge (adeast)
+%   (adeast) edge (Ad.east)
+%   (Ad.west) edge (adwest)
+%   (adwest) edge (o1.south)
+%   (o2.west) edge (Ld.east)
+%   (Ld.west) edge (ldwest)
+%   (ldwest) edge (o1.north)
+%   (delay.east) edge (Cd.west)
+%   (Cd.north) edge (o2.south)
+%   (o2east) edge (o2.east)
+%   (xdsouth) edge (fbsouth)
+ %  (fbsouth) edge (kdsouth);
+%\path[->]  (kdsouth) edge (Kd.south);
+%\path (Kd.north) edge (circle.south);
+% \end{tikzpicture}
+%}
+ %\caption{Closed-loop digital control system with observer\label{fig:observersystem}}
+%\end{figure*}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Stability of an Observed System}\label{sec:cof_stability}
+%\subsection{Stability of an Observed System}\label{sec:cof_stability}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\comment{
 Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally $\mat{A}_o=\mat{A}_d$, $\mat{B}_o=\mat{B}_d$ and $\mat{C}_o=\mat{C}_d$ for a given time discretization.
@@
 representation errors of the FWL domain.
+}
 

### 2018-02-26 automatica/paper.tex
sections 2 and 3

@@
 \newtheorem{proof}{Proof}
+
+\renewcommand{\note}[1]{\textcolor{red}{[#1]}}
 
@@
 
+\note{Add note explaining relationship of this work with previously published papers. }
+
 %-------------------------------
@@
 equations (ODEs), which we assume to be controllable~\cite{Astrom08,
-astrom1997computer}:
+astrom1997computer}: \note{Pls eliminate vector quantities, unless strictly needed.}
 %
@@
 We are interested in control systems with an output $\vec{y}$ that is a
-linear combination of its states and inputs\footnote{Notice that since we
+linear combination of its states and inputs
+\note{Do we need the output map? Where is it used?}
+\footnote{Notice that since we
 can only measure $\vec{y}$, the state-space $\vec{x}$ is not fully
@@
 where $k \in \mathbb N$ is a discrete counter and $\vec{x}_{0}=\vec{x}(0)$
-is the initial state.  In this work we apply the standard assumption that
+is the initial state.  
+\note{Next needed?}
+In this work we apply the standard assumption that
 $\mat{D}=\mat{0}$~\cite{Astrom08}.
@@
 
-Introduce set $X=\{ \vec{x} : \mat{C}\vec{x} \leq \vec{d}\}$. 
+Introduce set $X=\{ \vec{x} : \mat{C}\vec{x} \leq \vec{d}\}$. \note{This notation clashes with that of the output map for the LTI model. }
 The linear transformation $\vec{x}'=\mat{S}^{-1}\vec{x}$ leads to set 
@@
 transform equation \eqref{eq:aa_reachtube} into: 
+\note{The second condition has already been defined above.}
 %
@@
 %
-\item Then we restore soundness to the results using the methods described in Section \ref{sec:eigensolver} (lines \ref{alg:soundEigenvalues}-\ref{alg:soundEigenvectors}). 
+\item Then we restore soundness to the results using the methods described in Section \ref{sec:eigensolver} (lines \ref{alg:soundEigenvalues}-\ref{alg:soundEigenvectors}). \note{wrong ref.}
 %
@@
 \item Extract the vertices of the eigen-polyhedron $X_0'$ using the sound over-approximation of the double description algorithm \cite{fukuda1996double} from Section \ref{sec:dd} (line \ref{alg:getVertices}).
+\note{wrong refs.} 
 It is worth noting that this algorithm uses a simplex to seed it: we will first discuss the simplex algorithm, which is also needed at the next step, and then the vertex enumeration algorithm used at this stage.
@@
 functions using the abstract dynamics as a simplex Tableau, and via a sound
-simplex described in Section \ref{sec:simplex}.  The objective functions are
+simplex described in Section \ref{sec:simplex}.  \note{fix ref.} The objective functions are
 defined by the vertices of $X'_0$, denote as $V_0$, and by the desired
@@
 The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
-the state of the plant at integer multiples of the sample time.  However, in
+the state of the plant at integer multiples of the sample time.  
+\note{Unlike the CAV18 paper, these gain matrices have not been discussed yet. }
+However, in
 order to synthesize $\mat{K}=\mat{K}_{\langle C \rangle}$ and
-$\mat{L}=\mat{L}_{\langle C \rangle}$, we must be able to ensure that
+$\mat{L}=\mat{L}_{\langle C \rangle}$ \note{Do we need this second matrix?}, we must be able to ensure that
 certain properties of the plant hold at any given point in time.  In order
@@
 %
+\note{Matrix K has not been introduced yet. }
 \begin{theorem}

### 2018-02-27 automatica/paper.tex
added Dario's changes to the Automatica paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2018-02-26 automatica/paper.tex
@@
 equations (ODEs), which we assume to be controllable~\cite{Astrom08,
-astrom1997computer}:
+astrom1997computer}: \note{Pls eliminate vector quantities, unless strictly needed. What do you mean by vector quantities?}
 %
@@
 
-We are interested in control systems with an output $\vec{y}$ that is a
-linear combination of its states and inputs\footnote{Notice that since we
-can only measure $\vec{y}$, the state-space $\vec{x}$ is not fully
-observable.}.
-%
-%, which may restrict the observability of the state-space from the output space.
-\begin{equation}
-\label{eq:ode2}  
-\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t),
-\vec{y} \in \mathbb{R}^o,
-\mat{C} \in \mathbb{R}^{o \times p},
-\mat{D} \in \mathbb{R}^{o \times q}. 
-\end{equation}
-%
-Equations~\eqref{eq:ode1} and \eqref{eq:ode2} are soundly discretized in
+Equation~\eqref{eq:ode1} is soundly discretized in
 time~\cite{middleton1990digital,van1978computing} at constant intervals,
@@
 \label{eq:plant}
-\left\{
-\begin{array}{rl}
-\vec{x}_{k+1} =& \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k\\
-\vec{y}_{k} =& \mat{C} \vec{x}_k + \mat{D} \vec{u}_k, 
-\end{array}
-\right.
+\vec{x}_{k+1} =& \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k
 \text{ where }
@@
 \end{align} 
-%
-%where $\mat{A}_d=e^\mat{A}$, $\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$,
-%
 where $k \in \mathbb N$ is a discrete counter and $\vec{x}_{0}=\vec{x}(0)$
-is the initial state.  In this work we apply the standard assumption that
-$\mat{D}=\mat{0}$~\cite{Astrom08}.
-%
-%Also, since $\vec{y}$ can be directly derived from $\vec{x}$, we will omit discussing it in the following unless strictly necessary.
+is the initial state.
 
@@
 
-Introduce set $X=\{ \vec{x} : \mat{C}\vec{x} \leq \vec{d}\}$. 
+Introduce set $X=\{ \vec{x} \mid \mat{C}\vec{x} \leq \vec{d}\}$. %\note{This notation clashes with that of the output map for the LTI model. }
 The linear transformation $\vec{x}'=\mat{S}^{-1}\vec{x}$ leads to set 
@@
 \begin{equation}
-\hat{X}' \subseteq {\hat{X}'^\sharp} = \mathcal{J}X_0', \text{ such that } \bigcup_{k \in [0\ \ \infty)}\mat{J}^k \subseteq \mathcal{J}, 
+\hat{X}' \subseteq {\hat{X}'^\sharp} = \mathcal{J}X_0', 
 \end{equation}
@@
 %
-\item Then we restore soundness to the results using the methods described in Section \ref{sec:eigensolver} (lines \ref{alg:soundEigenvalues}-\ref{alg:soundEigenvectors}). 
+\item Then we restore soundness to the results using the methods described in \cite{cattaruzza2017sound} (lines \ref{alg:soundEigenvalues}-\ref{alg:soundEigenvectors}).
 %
@@
 %
-\item Extract the vertices of the eigen-polyhedron $X_0'$ using the sound over-approximation of the double description algorithm \cite{fukuda1996double} from Section \ref{sec:dd} (line \ref{alg:getVertices}).
-It is worth noting that this algorithm uses a simplex to seed it: we will first discuss the simplex algorithm, which is also needed at the next step, and then the vertex enumeration algorithm used at this stage.
+\item Extract the vertices of the eigen-polyhedron $X_0'$ using the algorithms described in \cite{cattaruzza2015unbounded,cattaruzza2017sound} (line \ref{alg:getVertices}). 
 %
@@
 functions using the abstract dynamics as a simplex Tableau, and via a sound
-simplex described in Section \ref{sec:simplex}.  The objective functions are
+simplex described in \cite{cattaruzza2017sound}.  The objective functions are
 defined by the vertices of $X'_0$, denote as $V_0$, and by the desired
@@
 The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
-the state of the plant at integer multiples of the sample time.  However, in
-order to synthesize $\mat{K}=\mat{K}_{\langle C \rangle}$ and
-$\mat{L}=\mat{L}_{\langle C \rangle}$, we must be able to ensure that
+the state of the plant at integer multiples of the sample time.  
+\note{Unlike the CAV18 paper, these gain matrices have not been discussed yet. }
+However, in
+order to synthesize $\mat{K}=\mat{K}_{\langle C \rangle}$, we must be able to ensure that
 certain properties of the plant hold at any given point in time.  In order
@@
 \begin{align}
-\vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u} \text{ where } \mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B} 
+\vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u}
 \label{eq:continuous_tube_param}
@@
 %
-where $\forall t \leq T.\, \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in
+where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$, $\forall t \leq T.\, \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in
 \eqref{eq:continuous_tube_dyn2} \footnote{When $\mat{A}$ is not invertible,

### 2018-02-27 automatica/paper.tex
sections 2 and 3

@@
 response~\cite{Duggirala2015} and finite word length (FWL) semantics, with
-the goal either to verify (e.g.,~\cite{daes20161}) or to optimize
-(e.g.,~\cite{oudjida2014design}) given implementations.
+the goal either to verify~\cite{daes20161} or to optimize~\cite{oudjida2014design} given implementations.
 
@@
 We consider models of physical plants expressed as ordinary differential
-equations (ODEs), which we assume to be controllable~\cite{Astrom08,
-astrom1997computer}: \note{Pls eliminate vector quantities, unless strictly needed. What do you mean by vector quantities?}
+equations, which we assume to be controllable~\cite{Astrom08,
+astrom1997computer}: \note{Pls eliminate bold quantities, unless strictly needed. }
 %
@@
 %-------------------------------
-\subsection{Abstract Acceleration} 
+\subsection{Abstract Acceleration of Linear Dynamics} 
 \label{ssec:aa}
@@
 
-For abstraction based synthesis, we will use Abstract
-Acceleration~\cite{JSS14,cattaruzza2015unbounded}.  Given an iterative
-program with dynamics
+We recall a technique called \emph{Abstract Acceleration}~\cite{JSS14,cattaruzza2015unbounded}, 
+which will be key for abstraction-based synthesis.  
+\note{This clashes with the model introduced above, with inputs - motivate why?}
+Given a model of an iterative program with dynamics
+\note{Pls eliminate unnecessary ``logical'' notation - we have discussed this already for the CAV18 submission, do we need to go through this again????}
 %
 \begin{equation}
-\vec{x}_{k+1}=\mat{A}\vec{x}_k : \vec{x}_k \in \mathbb{R}^n \wedge \mat{A} \in \mathbb{R}^{n \times n} \wedge k \in [0\ \ \infty),
+\vec{x}_{k+1}=\mat{A}\vec{x}_k : \vec{x}_k \in \mathbb{R}^n \wedge \mat{A} \in \mathbb{R}^{n \times n} \wedge k \in \mathbb N_0,
 \end{equation}
 %
+\note{material has been blindly pasted here - dimensions are all screwed up.}
 we want to find all possible states visited over an infinite time horizon
-starting at an initial set $X_0$.  We call this set the \emph{reach tube} of
+starting at an initial set $X_0$.  
+This set is known as the \emph{reach tube} of
 the model:
@@
 \begin{equation}
-\hat{X} = \{ \vec{x}_k : k \in [0\ \infty) \wedge \vec{x}_0 \in X_0 \wedge \vec{x}_{k+1}=\mat{A}\vec{x}_k\}.
+\hat{X} = \{ \vec{x}_k : k \in \mathbb N_0 \wedge \vec{x}_0 \in X_0 \wedge \vec{x}_{k+1}=\mat{A}\vec{x}_k\}.
 \end{equation}
@@
 It is easy to see that the infinite number of iterations would result in an
-unbounded cumulative rounding error, but using Abstract Acceleration we
+unbounded cumulative rounding error \note{why do we bring in the discussion on the rounding error here?
+why do we claim AA solves it?
+Is this the best manner to motivate the AA technique?}, but using Abstract Acceleration we
 transform this problem into a one-step solution.  We first change the
@@
 
-Introduce set $X=\{ \vec{x} \mid \mat{C}\vec{x} \leq \vec{d}\}$. %\note{This notation clashes with that of the output map for the LTI model. }
+Introduce set $X=\{ \vec{x} \mid \mat{C}\vec{x} \leq \vec{d}\}$. 
+\note{Why are we interested in this set? What does this set represent?}
 The linear transformation $\vec{x}'=\mat{S}^{-1}\vec{x}$ leads to set 

### 2018-02-27 automatica/paper.tex
adjusted mat and vec macro to eliminate bold

@@
 \newcommand{\addtodo}[1]{\textcolor{red}{[#1]}}
-\newcommand{\mat}[1]{\boldsymbol{#1}}
-\renewcommand{\vec}[1]{\boldsymbol{#1}}
+\newcommand{\mat}[1]{{#1}}
+\renewcommand{\vec}[1]{{#1}}
 \newcommand{\comment}[1]{}
@@
 equations, which we assume to be controllable~\cite{Astrom08,
-astrom1997computer}: \note{Pls eliminate bold quantities, unless strictly needed. }
+astrom1997computer}: %\note{Pls eliminate bold quantities, unless strictly needed. }
 %

### 2018-02-27 automatica/paper.tex
intro change

@@
 
-\addtodo{CD: change this}
-For this purpose, we leverage a very recent step-change in the automation and
-scalability of \emph{program synthesis}.  %% Program synthesis engines use a
-%% specification as the starting point, and subsequently generate a sequence of
-%% candidate programs from a given template.  The candidate programs are
-%% iteratively refined to eventually satisfy the specification.
-Program
-synthesizers implementing Counter-Example Guided Inductive Synthesis
-(CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} are now able to generate
-programs for highly non-trivial specifications with a very high degree of
-automation.  Modern synthesis engines combine automated testing, genetic
-algorithms, and SMT-based automated
-reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}.
+%% we leverage a very recent step-change in the automation and
+%% scalability of \emph{program synthesis}.  %% Program synthesis engines use a
+%% %% specification as the starting point, and subsequently generate a sequence of
+%% %% candidate programs from a given template.  The candidate programs are
+%% %% iteratively refined to eventually satisfy the specification.
+%% Program
+%% synthesizers implementing Counter-Example Guided Inductive Synthesis
+%% (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} are now able to generate
+%% programs for highly non-trivial specifications with a very high degree of
+%% automation.  Modern synthesis engines combine automated testing, genetic
+%% algorithms, and SMT-based automated
+%% reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}.
 
@@
 In this paper we present two novel approaches for the synthesis of digital controllers, 
-which we briefly describe next.
+both of which use a CounterExample-Guided Inductive Synthesis (CEGIS)~\cite{jha-icse10,
+DBLP:conf/pldi/Solar-LezamaRBE05} as described next.
+
 %% offer three modes of

### 2018-02-27 automatica/paper.tex
added contributions over CAV'17

@@
 \end{enumerate}
+
+This paper represents an extension of \cite{DBLP:conf/cav/AbateBCCDKKP17} 
+in the following directions:
+\begin{itemize}
+\item While \cite{DBLP:conf/cav/AbateBCCDKKP17} is restricted to systems
+  modeled in discrete time, in the current paper we present a model for
+  soundly evaluating reachability in a combined continuous-discrete time/space.
+\item A further limitation of the work in \cite{DBLP:conf/cav/AbateBCCDKKP17}
+  is its restriction to fixed-point arithmetic, meaning that fixed-point numbers
+  were employed for the representation of both the plant and the controller, as well as for
+  the operations performed by each of them.
+  Conversely, in the current paper we also make use of floating-point arithmetic
+  and compare the two approaches. Additionally, we enhance the implementation with an SMT backend, allowing us to also use reals in order to represent the states of the plant.
+\end{itemize}
 
@@
 
-\note{Add note explaining relationship of this work with previously published papers. }
+%\note{Add note explaining relationship of this work with previously published papers. }
 

### 2018-02-27 automatica/paper.tex
combined contributions and extensions over cav'17

@@
 
-\addtodo{CD: the novelty compared to CAV'17 needs to be clarified}
-In summary, this paper makes the following original contributions.
+%% \addtodo{CD: the novelty compared to CAV'17 needs to be clarified}
+This paper represents an extension of \cite{DBLP:conf/cav/AbateBCCDKKP17}
+and makes the following contributions, where the fourth and he fifth denote
+extensions over \cite{DBLP:conf/cav/AbateBCCDKKP17}.
 %
@@
   safety of our controllers in a hybrid continuous-digital domain.
-\end{enumerate}
-
-This paper represents an extension of \cite{DBLP:conf/cav/AbateBCCDKKP17} 
-in the following directions:
-\begin{itemize}
+
 \item While \cite{DBLP:conf/cav/AbateBCCDKKP17} is restricted to systems
@@
   and compare the two approaches. Additionally, we enhance the implementation with an SMT backend, allowing us to also use reals in order to represent the states of the plant.
-\end{itemize}
+\end{enumerate}
 

### 2018-02-27 automatica/paper.tex
fixed the paper structure (previously most of the paper was a subsection of sec 3)

@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Acceleration of continuous-time models}\label{sec:continuous_time_accel}
+\section{Acceleration of continuous-time models}\label{sec:continuous_time_accel}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Accelerated\! dynamics\! for\! continuous-time\! models\! without\! inputs}\label{sec:cont_acc_no_inputs}
+\subsection{Accelerated\! dynamics\! for\! continuous-time\! models\! without\! inputs}\label{sec:cont_acc_no_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Accelerated dynamics for models with parametric inputs}\label{sec:real_discrete_param_inputs}
+\subsection{Accelerated dynamics for models with parametric inputs}\label{sec:real_discrete_param_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Accelerated dynamics for models with a sampled-time feedback}\label{sec:real_discrete_feedback_inputs}
+\subsection{Accelerated dynamics for models with a sampled-time feedback}\label{sec:real_discrete_feedback_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 %-------------------------------
- \subsubsection{Finding Abstract Supports for Continuous Dynamics}
+ \subsection{Finding Abstract Supports for Continuous Dynamics}
  \label{sec:cont_aasup}
@@
 %-------------------------------
-\subsection{Counterexample Guided Inductive Synthesis} 
+\section{Counterexample Guided Inductive Synthesis} 
 \label{ssec:cegis}
@@
 %-------------------------------
-\subsubsection{CEGIS of digital controllers} 
+\subsection{CEGIS of digital controllers} 
 \label{sssec:cegisdig}
@@
 
-\subsubsection{Effect on safety specification and stability}
+\subsection{Effect on safety specification and stability}
 

### 2018-02-28 benchmarks/matlab/bioreactor.m
New benchmarks

@@ -1,0 +1,99 @@
+%%%%%%%%%%
+% 
+% Bioreactor 
+% 
+% Extracted from:
+%   Closed loop identification of transfer function model for unstable 
+%   bioreactors for tuning PID controllers. In Bioprocess Engineering,
+%   vol. 22 , no. 2, 
+%   pp. 185-188, Feb 2000.
+%   DOI: 10.1007/s004499900077
+% Written by:
+%   Iury Bessa
+%   Manaus, 2018
+%%%%%%%%%%
+%% Continuous-time transfer function
+
+bioreact=tf([-5.9],[5.89,-1],'InputDelay',1);
+bioreact_wo_delay=tf(bioreact.num,bioreact.den);
+
+
+%% Discretizing with Ts=0.8
+
+ts=0.8;
+pade_delay1=thiran(bioreact.InputDelay,ts);
+bioreact_tf_disc1=pade_delay1*c2d(bioreact,ts);
+bioreact_ss_disc1=ss(bioreact_tf_disc1);
+
+%% Discretizing with Ts=0.5
+
+ts=0.5;
+pade_delay2=thiran(bioreact.InputDelay,ts);
+bioreact_tf_disc2=pade_delay2*c2d(bioreact,ts);
+bioreact_ss_disc2=ss(bioreact_tf_disc2);
+
+
+%% Discretizing with Ts=1
+
+ts=1;
+pade_delay3=thiran(bioreact.InputDelay,ts);
+bioreact_tf_disc3=pade_delay3*c2d(bioreact,ts);
+bioreact_ss_disc3=ss(bioreact_tf_disc3);
+
+
+%% Discretizing with Ts=1.2
+
+ts=1.2;
+pade_delay4=thiran(bioreact.InputDelay,ts);
+bioreact_tf_disc4=pade_delay4*c2d(bioreact,ts);
+bioreact_ss_disc4=ss(bioreact_tf_disc4);
+
+
+%% Discretizing with Ts=1.5
+
+ts=1.5;
+pade_delay5=thiran(bioreact.InputDelay,ts);
+bioreact_tf_disc5=pade_delay5*c2d(bioreact,ts);
+bioreact_ss_disc5=ss(bioreact_tf_disc5);
+
+
+
+%% Discretizing with Ts=1.8
+
+ts=1.8;
+pade_delay6=thiran(bioreact.InputDelay,ts);
[…]

### 2018-02-28 benchmarks/matlab/cstr2.m

@@ -1,0 +1,69 @@
+%%%%%%%%%%
+% 
+% Reaction temperature of a continuous stirred tank reactor (cstrtemp)
+% 
+% Extracted from:
+%   Advanced PID Control. 
+%   Karl J. Åström , Tore Hägglund
+% Written by:
+%   Iury Bessa
+%   Manaus, 2018
+%%%%%%%%%%
+%% Continous-time transfer function
+
+cstrtempct=tf([0.15,0.0063],[1,0.048631,-0.003359]);
+
+
+%% Discretizing with Ts=0.5
+
+ts=0.5;
+cstrtemp_tf_disc1=c2d(cstrtempct,ts);
+cstrtemp_ss_disc1=ss(cstrtemp_tf_disc1);
+
+%% Discretizing with Ts=0.2
+
+ts=0.2;
+cstrtemp_tf_disc2=c2d(cstrtempct,ts);
+cstrtemp_ss_disc2=ss(cstrtemp_tf_disc2);
+
+
+%% Discretizing with Ts=1
+
+ts=1;
+cstrtemp_tf_disc3=c2d(cstrtempct,ts);
+cstrtemp_ss_disc3=ss(cstrtemp_tf_disc3);
+
+%% Discretizing with Ts=1.5
+
+ts=1.5;
+cstrtemp_tf_disc4=c2d(cstrtempct,ts);
+cstrtemp_ss_disc4=ss(cstrtemp_tf_disc4);
+
+
+%% Discretizing with Ts=2
+
+ts=1;
+cstrtemp_tf_disc5=c2d(cstrtempct,ts);
+cstrtemp_ss_disc5=ss(cstrtemp_tf_disc5);
+
+%% Discretizing with Ts=5
+
+ts=0.005;
+cstrtemp_tf_disc6=c2d(cstrtempct,ts);
+cstrtemp_ss_disc6=ss(cstrtemp_tf_disc6);
+
+%% Discretizing with Ts=0.8
+
+ts=0.8;
+cstrtemp_tf_disc7=c2d(cstrtempct,ts);
+cstrtemp_ss_disc7=ss(cstrtemp_tf_disc7);
+
+%% Saving
+
+save('benchmark_tf','cstrtemp_tf_disc1','cstrtemp_tf_disc2','cstrtemp_tf_disc3',...
+    'cstrtemp_tf_disc4','cstrtemp_tf_disc5','cstrtemp_tf_disc6','cstrtemp_tf_disc7',...
[…]

### 2018-02-28 benchmarks/matlab/steamdrum.m

@@ -1,0 +1,91 @@
+%%%%%%%%%%
+% 
+% Level control of boiler steam drum
+% 
+% Extracted from:
+%   Luyben, W.L., 1998. External versus internal unstable processes. 
+%   Ind. Eng. Chem. Res. 37, 2713–2720
+%   DOI: 10.1021/ie9800400
+% Written by:
+%   Iury Bessa
+%   Manaus, 2018
+%%%%%%%%%%
+%% Continuous-time transfer function
+
+steamdrum=0.547*tf([-0.418],[1.06,1,0],'InputDelay',0.1);
+steamdrum_wo_delay=tf(steamdrum.num,steamdrum.den);
+
+
+%% Discretizing with Ts=0.1
+
+ts=0.1;
+pade_delay1=thiran(steamdrum.InputDelay,ts);
+steamdrum_tf_disc1=pade_delay1*c2d(steamdrum,ts);
+steamdrum_ss_disc1=ss(steamdrum_tf_disc1);
+
+%% Discretizing with Ts=0.2
+
+ts=0.2;
+pade_delay2=thiran(steamdrum.InputDelay,ts);
+steamdrum_tf_disc2=pade_delay2*c2d(steamdrum,ts);
+steamdrum_ss_disc2=ss(steamdrum_tf_disc2);
+
+
+%% Discretizing with Ts=0.25
+
+ts=0.25;
+pade_delay3=thiran(steamdrum.InputDelay,ts);
+steamdrum_tf_disc3=pade_delay3*c2d(steamdrum,ts);
+steamdrum_ss_disc3=ss(steamdrum_tf_disc3);
+
+
+%% Discretizing with Ts=0.6
+
+ts=0.6;
+pade_delay4=thiran(steamdrum.InputDelay,ts);
+steamdrum_tf_disc4=pade_delay4*c2d(steamdrum,ts);
+steamdrum_ss_disc4=ss(steamdrum_tf_disc4);
+
+
+%% Discretizing with Ts=0.75
+
+ts=0.75;
+pade_delay5=thiran(steamdrum.InputDelay,ts);
+steamdrum_tf_disc5=pade_delay5*c2d(steamdrum,ts);
+steamdrum_ss_disc5=ss(steamdrum_tf_disc5);
+
+
+
+%% Discretizing with Ts=1.2
+
+ts=1.2;
+pade_delay6=thiran(steamdrum.InputDelay,ts);
[…]

### 2018-02-28 automatica/paper.tex

@@
 is the initial state.
+
+The linear feedback controller is characterized by a gain matrix
+$\mat{K}$ that influences the closed-loop dynamics
+(Fig.~\ref{fig:digitalsystem}).  Later, we will address the issue of
+variable quantization, as introduced by the ADC/DAC conversion blocks.
+
+\begin{figure*}[htb]
+\centering
+
+\tikzset{add/.style n args={4}{
+    minimum width=6mm,
+    path picture={
+        \draw[circle] 
+            (path picture bounding box.south east) -- (path picture bounding box.north west)
+            (path picture bounding box.south west) -- (path picture bounding box.north east);
+        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+        }
+    }
+ }
+
+\resizebox{1.0\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
+     semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
+    \node[draw=none] (r) {$r_k$};
+
+   \& \node[circle,add={-}{+}{}{}] (circle) {};
+   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$u_k$};
+   \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Kd) at ([xshift=0,yshift=-1.5cm]circle)  {\sc $\mat{K}$};
+   \coordinate (kdsouth) at ([yshift=-2cm]Kd);
+
+   \& complexnode/.pic={ 
+      \node[rectangle,dashed,draw,minimum width=3cm,minimum height=1.6cm,label=\textbf{DAC}] (dac) {};
+     \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
+     \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
+     \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
+     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {\sc ZOH};
+   }
+
+   \& complexnode/.pic={ 
+      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2.5cm,yshift=.5cm]plant.center)  {\sc $\mat{B}$};
+      \node[draw=none] (u) at ([xshift=-1cm,yshift=.15cm]B)  {$u(t)$};
+      \node[circle,add={+}{+}{}{}] (p1) at ([xshift=-1.3cm,yshift=.5cm]plant.center) {};
+      \node[draw=none] (xdot) at ([xshift=.85cm,yshift=.15cm]p1)  {$\dot{\vec{x}}(t)$};   
+      \node[rectangle,draw,minimum width=1cm] (int) at ([xshift=.5cm,yshift=.5cm]plant.center) {\sc $\int$};
+      \coordinate (xsouth) at ([xshift=1cm]int);
+      \node[draw=none] (x) at ([xshift=1cm,yshift=.15cm]int)  {$\vec{x}(t)$};
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (A) at ([xshift=.5cm,yshift=-1cm]plant.center)  {\sc $\mat{A}$};
+      \coordinate (aeast) at ([xshift=1cm]A);
+      \coordinate (awest) at ([xshift=-1.8cm]A);
+    }
+
+   \& complexnode/.pic={ 
+     \node[rectangle,dashed,draw,minimum width=3.5cm,minimum height=1.6cm,label=\textbf{ADC},] (adc) {};
+     \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
+     \coordinate (switch1) at ([xshift=-1cm]adc.center);
+     \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
+     \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
+     \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
+     \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
+     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]q1)  {$\vec{x}_k$};       
+     \coordinate (ykeast) at ([xshift=1.9cm]q1);
+     \coordinate (yksouth) at ([xshift=1.9cm,yshift=-3.5cm]q1);
+   } 
+   \& \coordinate (aux1);
+   \& \\
+  };
+
+  \path[->] (v1) edge (q1.south);
+  \path[->] (v2) edge (q2.south);
+  \path[->] (r) edge (circle.west);
+  \path[->] (circle.east) edge (q2.west);
+  \path       (q2.east) edge (zoh.west);
+  \path[->] (zoh.east) edge (B.west);
+  \path
+   (B.east) edge (p1.west)
+   (p1.east) edge (int.west)
+   (xsouth) edge (aeast)
+   (aeast) edge (A.east)
+   (A.west) edge (awest)
+   (awest) edge (p1.south)
+   (int.east) edge (switch1.west)
+   (switch2) edge (q1.west);
+  \path
+   (q1.east) edge (ykeast)
+   (ykeast) edge (yksouth)
+   (yksouth) edge (kdsouth);
+  \path[->]  (kdsouth) edge (Kd.south);
+  \path (Kd.north) edge (circle.south);
+ \end{tikzpicture}
+}
+ \caption{Closed-loop digital control system 
+ \label{fig:digitalsystem}}
+\end{figure*}
 
@@
 the state of the plant at integer multiples of the sample time.  
-\note{Unlike the CAV18 paper, these gain matrices have not been discussed yet. }
+%\note{Unlike the CAV18 paper, these gain matrices have not been discussed yet. }
 However, in
-order to synthesize $\mat{K}=\mat{K}_{\langle C \rangle}$, we must be able to ensure that
+order to synthesize $\mat{K}$, we must be able to ensure that
 certain properties of the plant hold at any given point in time.  In order
@@
 %
-\note{Matrix K has not been introduced yet. }
+%\note{Matrix K has not been introduced yet. }
 \begin{theorem}

### 2018-03-07 automatica/paper.tex
Integrated Dario's changes into the paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 In this paper we present two novel approaches for the synthesis of digital controllers, 
-both of which use a CounterExample-Guided Inductive Synthesis (CEGIS)~\cite{jha-icse10,
-DBLP:conf/pldi/Solar-LezamaRBE05} as described next.
+both of which use a CounterExample-Guided Inductive Synthesis (CEGIS)~\cite{%jha-icse10,
+DBLP:conf/asplos/Solar-LezamaTBSS06} as described next.
 
@@
 $\mat{K}$ that influences the closed-loop dynamics
-(Fig.~\ref{fig:digitalsystem}).  Later, we will address the issue of
+(Fig.~\ref{fig:digitalsystem}) such that
+\begin{equation*}
+\vec{u}_k=\mat{K}\vec{x}_k \Rightarrow \vec{x}_{k+1}=(\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_k
+\end{equation*}
+Which corresponds to a closed loop system without inputs. Later, we will address the issue of
 variable quantization, as introduced by the ADC/DAC conversion blocks.
@@
 which will be key for abstraction-based synthesis.  
-\note{This clashes with the model introduced above, with inputs - motivate why?}
+%\note{This clashes with the model introduced above, with inputs - motivate why? I've added the motivation above by introducing the closed  loop}
 Given a model of an iterative program with dynamics
-\note{Pls eliminate unnecessary ``logical'' notation - we have discussed this already for the CAV18 submission, do we need to go through this again????}
 %
 \begin{equation}
-\vec{x}_{k+1}=\mat{A}\vec{x}_k : \vec{x}_k \in \mathbb{R}^n \wedge \mat{A} \in \mathbb{R}^{n \times n} \wedge k \in \mathbb N_0,
+\vec{x}_{k+1}=\mat{A}\vec{x}_k \text{ where } \vec{x}_k \in \mathbb{R}^p, \mat{A} \in \mathbb{R}^{p \times p} \text{ and } k \in \mathbb N_0,
 \end{equation}
 %
-\note{material has been blindly pasted here - dimensions are all screwed up.}
 we want to find all possible states visited over an infinite time horizon
@@
 \begin{equation}
-\hat{X} = \{ \vec{x}_k : k \in \mathbb N_0 \wedge \vec{x}_0 \in X_0 \wedge \vec{x}_{k+1}=\mat{A}\vec{x}_k\}.
+\hat{X} = \{ \vec{x}_k \mid k \in \mathbb N_0, \vec{x}_0 \in X_0 \text{ and } \vec{x}_{k+1}=\mat{A}\vec{x}_k\}.
 \end{equation}
 %
-It is easy to see that the infinite number of iterations would result in an
-unbounded cumulative rounding error \note{why do we bring in the discussion on the rounding error here?
-why do we claim AA solves it?
-Is this the best manner to motivate the AA technique?}, but using Abstract Acceleration we
+Using Abstract Acceleration we
 transform this problem into a one-step solution.  We first change the
@@
 \begin{equation}
-\hat{X} = \{ \vec{x}_k=\mat{A}^k\vec{x}_0 : k \in [0\ \infty) \wedge \vec{x}_0 \in X_0 \}, 
+\hat{X} = \{ \vec{x}_k=\mat{A}^k\vec{x}_0 \mid k \in N_0 \text{ and } \vec{x}_0 \in X_0 \}, 
 \end{equation}
@@
 
-Introduce set $X=\{ \vec{x} \mid \mat{C}\vec{x} \leq \vec{d}\}$. 
-\note{Why are we interested in this set? What does this set represent?}
-The linear transformation $\vec{x}'=\mat{S}^{-1}\vec{x}$ leads to set 
+Since abstract acceleration operates in the eigenspace, wemust deal with some preliminary transformations.
+Given a set $X=\{ \vec{x} \mid \mat{C}\vec{x} \leq \vec{d}\}$,
+%\note{Why are we interested in this set? What does this set represent?}
+the linear transformation $\vec{x}'=\mat{S}^{-1}\vec{x}$ leads to the set 
 %
 \begin{equation}
-X'= \mat{S}^{-1}X = \{\vec{x}' : \mat{C}\mat{S}\vec{x}'\leq \vec{d}\}.  
+X'= \mat{S}^{-1}X = \{\vec{x}' \mid \mat{C}\mat{S}\vec{x}'\leq \vec{d}\}.  
 \label{eq:eigenInit}
@@
 \begin{equation*}
-\vec{w}_{ij}= \vec{v}_i \circ \vec{t}_j : \vec{v}_i \in V_0 \wedge \vec{t}_j \in T,
+\vec{w}_{ij}= \vec{v}_i \circ \vec{t}_j \text{ with } \vec{v}_i \in V_0 \text{ and } \vec{t}_j \in T,
 \end{equation*}

### 2018-03-08 benchmarks/matlab/parserss2ss.m
adding Ts info in .ss

@@ -19,6 +19,7 @@ A = system.A;
 B = system.B;
 C = system.C;
 D = system.D;
+sampletime = system.Ts;
 
 [rA,cA] = size(A);
 nStates = rA;
@@ -41,6 +42,7 @@ fprintf(fid,'B = %s \n', matrix2string(B));
 fprintf(fid,'C = %s \n', matrix2string(C));
 fprintf(fid,'D = %s \n', matrix2string(D));
 fprintf(fid,'inputs = %s \n', matrix2string(inputs));
+fprintf(fid,'Ts = %s \n', num2str(sampletime));
 if isempty(K) == 0
    fprintf(fid,'K = %s \n', matrix2string(K));
 end

### 2018-03-08 automatica/paper.tex

@@
 
-The linear feedback controller is characterized by a gain matrix
-$\mat{K}$ that influences the closed-loop dynamics
-(Fig.~\ref{fig:digitalsystem}) such that
+Later, we will address the issue of variable quantization, as introduced by the ADC/DAC conversion blocks.
+Models \eqref{eq:ode1} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t)$ and  $u_k$, respectively. 
+Feedback architectures can be employed to manipulate the properties and behaviors of the continuous process (the plant).   
+We are interested in the synthesis of digital feedback control algorithms, 
+as implemented on Field-Programmable Gate Arrays or Digital Signal Processors. 
+The most basic feedback architecture is the state feedback one, 
+where the control action $u_k$ (notice we work with the discretized signal) is computed by: 
+%
 \begin{equation*}
-\vec{u}_k=\mat{K}\vec{x}_k \Rightarrow \vec{x}_{k+1}=(\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_k
+%\label{eq:controlaction}
+u_k = r_{k} - K x_k. 
 \end{equation*}
-Which corresponds to a closed loop system without inputs. Later, we will address the issue of
-variable quantization, as introduced by the ADC/DAC conversion blocks.
+
+where $K \in \mathbb{R}^{m \times n}$ is a state-feedback gain matrix, 
+and $r_{k}$ is a reference signal (again digital). We will assume $r_k=0$, thus 
+\begin{equation}
+\vec{x}_{k+1}=(\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_k
+\end{equation}
+Which corresponds to a closed loop system without inputs.
 
@@
 \end{figure*}
-
-%-------------------------------
-\subsection{Abstract Acceleration of Linear Dynamics} 
-\label{ssec:aa}
-%-------------------------------
-
-We recall a technique called \emph{Abstract Acceleration}~\cite{JSS14,cattaruzza2015unbounded}, 
-which will be key for abstraction-based synthesis.  
-%\note{This clashes with the model introduced above, with inputs - motivate why? I've added the motivation above by introducing the closed  loop}
-Given a model of an iterative program with dynamics
-%
-\begin{equation}
-\vec{x}_{k+1}=\mat{A}\vec{x}_k \text{ where } \vec{x}_k \in \mathbb{R}^p, \mat{A} \in \mathbb{R}^{p \times p} \text{ and } k \in \mathbb N_0,
-\end{equation}
-%
-we want to find all possible states visited over an infinite time horizon
-starting at an initial set $X_0$.  
-This set is known as the \emph{reach tube} of
-the model:
-%
-\begin{equation}
-\hat{X} = \{ \vec{x}_k \mid k \in \mathbb N_0, \vec{x}_0 \in X_0 \text{ and } \vec{x}_{k+1}=\mat{A}\vec{x}_k\}.
-\end{equation}
-%
-Using Abstract Acceleration we
-transform this problem into a one-step solution.  We first change the
-problem statement by means of acceleration into
-%
-\begin{equation}
-\hat{X} = \{ \vec{x}_k=\mat{A}^k\vec{x}_0 \mid k \in N_0 \text{ and } \vec{x}_0 \in X_0 \}, 
-\end{equation}
-%
-and further define new model semantics and corresponding set: 
-%
-\begin{equation}\label{eq:aa_reachtube}
-\hat{X} \subseteq \hat{X}^\sharp = \mathcal{A}X_0, \text{ such that } \bigcup_{k \in [0\ \infty)} \mat{A}^k \subseteq \mathcal{A}, 
-\end{equation}
-%
-where the newly introduced \emph{abstract reach tube} $\hat{X}^\sharp$ is an
-over-approximation of the reach tube of the model \cite{JSS14}.  All we need
-to do is define the nature of $\mathcal{A}X_0$.
-
-Let $\mat{S}\mat{J}\mat{S}^{-1}=\mat{A}$ be the eigen-decomposition of
-$\mat{A}$, where $\mat{S}$ is the set of generalised eigenvectors of
-$\mat{A}$ and $\mat{J}$ is the Jordan Form containing the eigenvalues of
-$\mat{A}$ in its main diagonal.  We correspondingly define
-$\mathcal{J}=\mat{S}^{-1}\mathcal{A}\mat{S}$, which is such that
-$\mathcal{J} \supseteq \bigcup_{k \in [0\ \infty)} \mat{J}^k$.
-
-Since abstract acceleration operates in the eigenspace, wemust deal with some preliminary transformations.
-Given a set $X=\{ \vec{x} \mid \mat{C}\vec{x} \leq \vec{d}\}$,
-%\note{Why are we interested in this set? What does this set represent?}
-the linear transformation $\vec{x}'=\mat{S}^{-1}\vec{x}$ leads to the set 
-%
-\begin{equation}
-X'= \mat{S}^{-1}X = \{\vec{x}' \mid \mat{C}\mat{S}\vec{x}'\leq \vec{d}\}.  
-\label{eq:eigenInit}
-\end{equation}
-%
-Analogously, let $X_0'=\mat{S}^{-1}X_0$ and
-${\hat{X}'^\sharp}=\mat{S}^{-1}{\hat{X}^\sharp}$ be the initial set and the
-abstract reach tube mapped onto the eigenspace of matrix $\mat{A}$.  We may
-transform equation \eqref{eq:aa_reachtube} into: 
-%
-\begin{equation}
-\hat{X}' \subseteq {\hat{X}'^\sharp} = \mathcal{J}X_0', 
-\end{equation}
-%
-where $\hat{X}'=\mat{S}^{-1}\hat{X}$ and $\mathcal{J}$ is a convex
-polyhedron representing restrictions on the eigenvalues of $\mat{A}$. 
-$\hat{X}'^\sharp$ is calculated by applying a simplex algorithm with a
-tableau defined by $\mathcal{J}$ and objective functions derived from each
-vertex of $X_0'$ (step \eqref{alg:getReachTube} in Algorithm
-\ref{alg:findReachTube} below).  We note, however, that if we wish to use
-numerical analysis in the decomposition of $\mat{A}$, the Tableau in
-$\mathcal{J}$ contains small intervals given by the errors, which cannot be
-processed efficiently by a regular simplex and require a new procedure.
-
-The calculation of the abstract reach tube via abstract acceleration is
-encompassed in Algorithm~\ref{alg:findReachTube}, which can be summarised as
-follows (its steps are denoted in parentheses):
-%
-\begin{enumerate}
-%
-\item We perform unsound eigen-decomposition using an existing algebra package (lines \ref{alg:calcEigenvalues}-\ref{alg:calcEigenvectors}).
-%
-\item Then we restore soundness to the results using the methods described in \cite{cattaruzza2017sound} (lines \ref{alg:soundEigenvalues}-\ref{alg:soundEigenvectors}).
-%
-\item The inverse of the matrix of eigenvectors is calculated after soundness is restored, using interval arithmetic in order to ensure its soundness (line \ref{alg:inverse}).
-%
-\item The abstract dynamics are obtained by evaluating the convex hull of all powers of eigenvalues up to the desired number of iterations as described in \cite{cattaruzza2015unbounded} (line \ref{alg:aa}).
-%
-\item Using Equation \eqref{eq:eigenInit}, transform the initial state into the eigenspace (line \ref{alg:eigeninit}).
-%
-\item Extract the vertices of the eigen-polyhedron $X_0'$ using the algorithms described in \cite{cattaruzza2015unbounded,cattaruzza2017sound} (line \ref{alg:getVertices}). 
-%
-\item Calculate the mapped \emph{abstract reach tube} ${\hat{X}'^\sharp}$
-that over-approximates the image of the reach tube in the eigenspace (line
-\ref{alg:getReachTube}).  This is achieved by evaluating a set of objective
-functions using the abstract dynamics as a simplex Tableau, and via a sound
-simplex described in \cite{cattaruzza2017sound}.  The objective functions are
-defined by the vertices of $X'_0$, denote as $V_0$, and by the desired
-template directions, such that
-%
-\begin{equation*}
-\vec{w}_{ij}= \vec{v}_i \circ \vec{t}_j \text{ with } \vec{v}_i \in V_0 \text{ and } \vec{t}_j \in T,
-\end{equation*}
-%
-where $T$ is the set of template directions, and $\circ$ denotes a
-component-wise multiplication yielding a vector.
-%
-\item Using Equation~\eqref{eq:eigenInit}, find the reach tube
-$\hat{X}^\sharp=\mat{S}{\hat{X}'^\sharp}$ (line \ref{alg:getNormReachTube}).
-%
-\end{enumerate}
-
-\begin{algorithm}[]
-\small
-\begin{algorithmic}[1]
-\Function{$\mathit{findAbstractReachTube}()$}{}
-\State $\hat{\mat{J}}=$ calculateEigenvalues($ \mat{A}$)
-\label{alg:calcEigenvalues}
-\State $\hat{\mat{S}}=$ calculateEigenvectors($ \mat{A}$)
-\label{alg:calcEigenvectors}
-\State $[\mat{J}]=$ soundifyEigenvalues($\mat{A},\mat{J},\mat{S}$)
-\label{alg:soundEigenvalues}
-\State $[\mat{S}]=$ soundifyEigenvectors($\mat{A},[\mat{J}],\mat{S}$)
-\label{alg:soundEigenvectors}
-\State $[\mat{S}]^{-1}=$ calculateInverse($[\mat{S}]$)
-\label{alg:inverse}
-\State $\mathcal{J}=getAbstractDynamics([\mat{J}])$
-\label{alg:aa}
-\State $[X_0']=$ transformInitialSpace($X_0,\mat{S}$)
-\label{alg:eigeninit}
-\State $[V_0]=$ getVertices($[X_0']$)
-\label{alg:getVertices}
-\State ${\hat{X}'^\sharp}=$ getReachTube($\mathcal{J},[V_0]$)
-\label{alg:getReachTube}
-\State ${\hat{X}^\sharp}=$ transformReachTube(${\hat{X}'^\sharp},[\mat{S}]^{-1}$)
-\label{alg:getNormReachTube}
-\EndFunction
-\end{algorithmic}
-\caption{Calculation of Abstract Reach Tube Using Abstract Acceleration}
-\label{alg:findReachTube}
-\end{algorithm}
-
-%%-------------------------------
-%\subsection{Overapproximating continuous time dynamics using discrete models}
-%\label{sec:cont_aa}
-%%-------------------------------
-%
-%Thus far we wave discussed the Abstract Accelertion of Discrete Time
-%systems.  However, our plant models derive from the discretization of
-%continuous time systems.  We therefore seek to establish a sound
-%overapproximation which does not only encompass the selected discretization,
-%but any chosen discretization in the time domain.
-%
-%A dynamical system is a system in which a function describes the progression
-%of a state over time.  In a continuous domain with linear dynamics, it is
-%described by a first order Ordinary Differential Equation (ODE).
-%%
-%\begin{equation}
-%\dot{x}(t)=\mat{A}_o\vec{x}(t)+\mat{B}_o\vec{u}(t)
-%\label{eq:dynamical}
-%\end{equation}
-%%
-%Furthermore, a control system may have a derived
-%output that is a linear combination of its states and inputs, which may
-%restricts the observability of the statespace from the output space.
-%%
-%\begin{equation}
-%\vec{y}(t)=\mat{C}_o\vec{x}(t)+\mat{D}_o\vec{u}(t)
-%\end{equation}
-%%
-%Discretization of a continuous dynamical system turns the ODE into a
-%difference equation, assuming zero-order hold for the input $\vec{u}$, to
-%%
-%\begin{align}
-%\label{eq:discretization}
-%\vec{x}_{k+1} &= \mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
-%y_k &= \mat{C}_d \vec{x}_ k + \mat{D}_d \vec{u}_ k 
-%\end{align}
-%where
-%\begin{align}
-%\label{eq:discretize}
-%\mat{A}_d &= e^{\mat{A}_o T_s} = \mathcal{L}^{-1} { ( s \mat{I} - \mat{A}_o )^{-1} }_{t = T_s}\\
-%\mat{B}_d &= \int_{t = 0}^{T_s} e^{\mat{A}_o t} dt\ \mat{B}_o = \mat{A}_o^{-1} ( \mat{A}_d - \mat{I} ) \mat{B}_o\\
-%\mat{C}_d &= \mat{C}_o\\
-%\mat{D}_d &= \mat{D}_o \\
-%\end{align}
-%and $T_s$ is the sample time. Then
-%\begin{align*}
-%x(kT)=x_k \wedge y(kT) = y_k, \forall k
-%\end{align*}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Acceleration of continuous-time models}\label{sec:continuous_time_accel}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
-the state of the plant at integer multiples of the sample time.  
-%\note{Unlike the CAV18 paper, these gain matrices have not been discussed yet. }
-However, in
-order to synthesize $\mat{K}$, we must be able to ensure that
-certain properties of the plant hold at any given point in time.  In order
-to do so, we accelerate the dynamics of the plant according to the model
-semantics in Sec.~\ref{sec:model} and compute the state
-$\vec{x}_T$ at a given time $T$,
-%
-% namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
-%
-namely the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time
-$t=T$.
-
-%\note{ [add?] In this section we work with fully observed models, namely where $y = x$. } 
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Accelerated\! dynamics\! for\! continuous-time\! models\! without\! inputs}\label{sec:cont_acc_no_inputs}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%
-Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a
-linear function of $\vec{x}_0$ as shown below.  We assume that the system
-has no inputs, so its dynamics are described by
-$\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.
-
-\begin{lemma}
-The solution to the differential equation $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, and $\mat{S}$ are the generalized eigenvectors of $\mat{A}$,
-evaluated at time $T$ is
-%
-\begin{align}
- \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x} (0)\\
- \mat{A}_{T}&= \mat{S}
- \left [ \begin{array}{cccc}
- e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(2)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
-0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
-\vdots & & \ddots & \vdots \\
-0 & \cdots & 0  &e^{T\lambda_i} \\
-\end{array} \right ]
- \mat{S}^{-1}
- \label{eq:continuous_tube_dyn2}\\
- &\text{where } s_i=\left\{\begin{array}{cc}1&\quad gm(\lambda_i)>1\\0&\quad gm(\lambda_i)=1\end{array}\right.,\nonumber
-\end{align}
-%
-$\lambda_i$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.
-%
-%$\vec{x}_T$ is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T. 
-If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0 \text{ with } T \in \mathbb{R}^+_0$ is the state of the system at time $t=T$.
-\end{lemma}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Accelerated dynamics for models with parametric inputs}\label{sec:real_discrete_param_inputs}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Next, we are interested in studying models with parametric inputs, which are
-described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where
-$\forall t\geq 0.\,\vec{u}(t)=\vec{u}$.  For such models, a state $\vec{x}_T$
-is computed next.
-%
-\begin{lemma}
-%
-The state of the model
-$\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a
-parametric input $\vec{u}$ is
-%
-\begin{align}
-\vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u}
-\label{eq:continuous_tube_param}
-\end{align}
-%
-where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$, $\forall t \leq T.\, \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in
-\eqref{eq:continuous_tube_dyn2} \footnote{When $\mat{A}$ is not invertible,
-we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\
-0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$.}. 
-If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that
-$A_d=e^{\mat{A} T_d}$, then
-$\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u})
-\text{ with } T \in \mathbb{R}_0^+$ (where $\mat{A}_d^{\frac{T}{T_d}} =
-e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the
-system at time $T$.
-%
-\end{lemma}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Accelerated dynamics for models with a sampled-time feedback}\label{sec:real_discrete_feedback_inputs}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-The final case we analyze is that of hybrid-time models, where the plant
-dynamics evolve in continuous time while the feedback dynamics evolve in
-discrete time.  A~new input value is produced only at every sample time but
-implemented over the continuous-time plant dynamics.
-%
-%\note{Matrix K has not been introduced yet. }
-\begin{theorem}
-The expression
-%
- \begin{align}
- \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0, 
- \label{eq:cyber_feedback}
- \end{align}
-%
-with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, $\mat{B}_T$ as in
-\eqref{eq:continuous_tube_param}, and where $\mat{A}_d=\mat{A}_{T_s}$,
-$\mat{B}_d=\mat{B}_{T_s}$ describe the discretized plant dynamics with
-sample time $T_s$, is the state of the model
-%
-\begin{align*}
- \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
- \vec{u}(t)=\mat{K}\vec{x}_k,  \,
- kT_s \leq t < (k+1)T_s \,. 
-\end{align*}
-%
-\end{theorem}
-\begin{proof}
-%
-Let $\mat{K}$ be a feedback controller such that
-$\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$.  Let the output of the
-feedback system be a zero order holder such that
-$\vec{u}(t'+kT_s)=\vec{u}(kT_s), \text{ for } 0 \leq t' < T_s$.  The closed
-loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
-%
-\begin{align*}
-\vec{x}_{k,t'}=\mat{A}_{t'}\vec{x}_k-\mat{B}_{t'}\mat{K}\vec{x}_k = (\mat{A}_{t'}-\mat{B}_{t'}\mat{K})\vec{x}_k,
-\end{align*}
-where $0 \leq t' < T_s$
-We further explore the dynamics across discrete time boundaries. Let $\mat{A}_d=\mat{A}_{T_s}$ and $\mat{B}_d=\mat{B}_{T_s}$
-\begin{align*}
-\vec{x}_{k}&=\vec{x}_{k-1,T_s}= (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}\\
-\vec{x}_{k,T_s} &= (\mat{A}_d-\mat{B}_d\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}
-\end{align*}
-which accelerating results and setting $T=kT_s+t'$ becomes
-\begin{align}
-\label{eq:feedback_sampled_cont}
-\vec{x}_{k} &= (\mat{A}_d-\mat{B}_d\mat{K}) ^k\vec{x}_0\\
-\vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
-\label{eq:feedback_cont}
-\end{align}
-\end{proof}
-
-%-------------------------------
- \subsection{Finding Abstract Supports for Continuous Dynamics}
- \label{sec:cont_aasup}
-%-------------------------------
-
-In the case of Discrete dynamics, support functions can be found by
-evaluating hyperplanes of consecutive exponents of the eigenvalues using
-differences.  In the case of continuous time, this translates to calculating
-derivatives.  Once again, when the sets are known to be convex, we may
-calculate the normal vector to this derivative and evaluate its support
-function on the selected iteration.  The direction of the vector is
-determined by evaluating the support function of another point in the curve,
-which is known to be smaller than that of the selected point.  The
-corresponding derivatives are:
-%
-\begin{enumerate}
-%
-\item for real eigenvalues: we first calculate the slope of the tangent
-between the two progressions: $\frac{d f(k)}{d g(k)}=\frac{f'(k)}{g'(k)}$. 
-Hence $\frac{d \lambda_1^k}{d \lambda_2^k}=\frac{log(\lambda_1)
-\lambda_1^k}{log(\lambda_2) \lambda_2^k}$.  From this we know that the polar
-angle of the support vector is $\psi = \tan^{-1}(\frac{log(\lambda_1)
-\lambda_1^k}{log(\lambda_2) \lambda_2^k})+\frac{\pi}{2}$
-%
-\item for conjugate eigenvalue pairs: the pair forms a logarithmic spiral. 
-The tangent of a spiral with polar equation $r=a e^{b\theta}$ will have a
-derivative $\frac{d r}{d \theta}=b a e^{b\theta}=b r$, hence the angle of
-the vector normal to the curve is $\tan^{-1}(\frac{r}{\frac{d r}{d
-\theta}})+\frac{\pi}{2}=\tan^{-1}(\frac{1}{b})+\frac{\pi}{2}$
-%
-\item for Jordan blocks with $gm>1$: in the case of real eigenvalues, we
-follow the same procedure as in the real case, but considering that the
-equation for each eigenvalue is $\frac{k^j}{j!}e^{\lambda k}$ where $j$ is
-the index of the term within the Jordan block (note that when $j=0$ the term
-is the same as for real eigenvalues above).  The derivatives f'(k),g'(k) are
-in the form $(j+k*log(\lambda))\frac{k^{j-1}}{j!}e^{\lambda k}$.
-%
-\item for any combination of complex eigenvalues we use the above equations
-using the envelope of their magnitude (ie $|\lambda|$).
-%
-\end{enumerate}
 
@@
 \end{figure*}
+
+%-------------------------------
+\subsection{Abstract Acceleration of Linear Dynamics} 
+\label{ssec:aa}
+%-------------------------------
+
+We recall a technique called \emph{Abstract Acceleration}~\cite{JSS14,cattaruzza2015unbounded}, 
+which will be key for abstraction-based synthesis.  
+%\note{This clashes with the model introduced above, with inputs - motivate why? I've added the motivation above by introducing the closed  loop}
+Given a model of an iterative program with dynamics
+%
+\begin{equation}
+\vec{x}_{k+1}=\mat{A}\vec{x}_k \text{ where } \vec{x}_k \in \mathbb{R}^p, \mat{A} \in \mathbb{R}^{p \times p} \text{ and } k \in \mathbb N_0,
+\end{equation}
+%
+we want to find all possible states visited over an infinite time horizon
+starting at an initial set $X_0$.  
+This set is known as the \emph{reach tube} of
+the model:
+%
+\begin{equation}
+\hat{X} = \{ \vec{x}_k \mid k \in \mathbb N_0, \vec{x}_0 \in X_0 \text{ and } \vec{x}_{k+1}=\mat{A}\vec{x}_k\}.
+\end{equation}
+%
+Using Abstract Acceleration we
+transform this problem into a one-step solution.  We first change the
+problem statement by means of acceleration into
+%
+\begin{equation}
+\hat{X} = \{ \vec{x}_k=\mat{A}^k\vec{x}_0 \mid k \in N_0 \text{ and } \vec{x}_0 \in X_0 \}, 
+\end{equation}
+%
+and further define new model semantics and corresponding set: 
+%
+\begin{equation}\label{eq:aa_reachtube}
+\hat{X} \subseteq \hat{X}^\sharp = \mathcal{A}X_0, \text{ such that } \bigcup_{k \in [0\ \infty)} \mat{A}^k \subseteq \mathcal{A}, 
+\end{equation}
+%
+where the newly introduced \emph{abstract reach tube} $\hat{X}^\sharp$ is an
+over-approximation of the reach tube of the model \cite{JSS14}.  
+In this work we use an extension of the abstract acceleration model for
+continuous time. For this reason we must first look at the accelerationm of continuous time dynamics.
+
+%All we need to do is define the nature of $\mathcal{A}X_0$.
+%Let $\mat{S}\mat{J}\mat{S}^{-1}=\mat{A}$ be the eigen-decomposition of
+%$\mat{A}$, where $\mat{S}$ is the set of generalised eigenvectors of
+%$\mat{A}$ and $\mat{J}$ is the Jordan Form containing the eigenvalues of
+%$\mat{A}$ in its main diagonal.  We correspondingly define
+%$\mathcal{J}=\mat{S}^{-1}\mathcal{A}\mat{S}$, which is such that
+%$\mathcal{J} \supseteq \bigcup_{k \in [0\ \infty)} \mat{J}^k$.
+%
+%Since abstract acceleration operates in the eigenspace, wemust deal with some preliminary transformations.
+%Given a set $X=\{ \vec{x} \mid \mat{C}\vec{x} \leq \vec{d}\}$,
+%the linear transformation $\vec{x}'=\mat{S}^{-1}\vec{x}$ leads to the set 
+%%
+%\begin{equation}
+%X'= \mat{S}^{-1}X = \{\vec{x}' \mid \mat{C}\mat{S}\vec{x}'\leq \vec{d}\}.  
+%\label{eq:eigenInit}
+%\end{equation}
+%%
+%Analogously, let $X_0'=\mat{S}^{-1}X_0$ and
+%${\hat{X}'^\sharp}=\mat{S}^{-1}{\hat{X}^\sharp}$ be the initial set and the
+%abstract reach tube mapped onto the eigenspace of matrix $\mat{A}$.  We may
+%transform equation \eqref{eq:aa_reachtube} into: 
+%%
+%\begin{equation}
+%\hat{X}' \subseteq {\hat{X}'^\sharp} = \mathcal{J}X_0', 
+%\end{equation}
+%%
+%where $\hat{X}'=\mat{S}^{-1}\hat{X}$ and $\mathcal{J}$ is a convex
+%polyhedron representing restrictions on the eigenvalues of $\mat{A}$. 
+%$\hat{X}'^\sharp$ is calculated by applying a simplex algorithm with a
+%tableau defined by $\mathcal{J}$ and objective functions derived from each
+%vertex of $X_0'$ (step \eqref{alg:getReachTube} in Algorithm
+%\ref{alg:findReachTube} below).  We note, however, that if we wish to use
+%numerical analysis in the decomposition of $\mat{A}$, the Tableau in
+%$\mathcal{J}$ contains small intervals given by the errors, which cannot be
+%processed efficiently by a regular simplex and require a new procedure.
+%
+%The calculation of the abstract reach tube via abstract acceleration is
+%encompassed in Algorithm~\ref{alg:findReachTube}, which can be summarised as
+%follows (its steps are denoted in parentheses):
+%%
+%\begin{enumerate}
+%%
+%\item We perform unsound eigen-decomposition using an existing algebra package (lines \ref{alg:calcEigenvalues}-\ref{alg:calcEigenvectors}).
+%%
+%\item Then we restore soundness to the results using the methods described in \cite{cattaruzza2017sound} (lines \ref{alg:soundEigenvalues}-\ref{alg:soundEigenvectors}).
+%%
+%\item The inverse of the matrix of eigenvectors is calculated after soundness is restored, using interval arithmetic in order to ensure its soundness (line \ref{alg:inverse}).
+%%
+%\item The abstract dynamics are obtained by evaluating the convex hull of all powers of eigenvalues up to the desired number of iterations as described in \cite{cattaruzza2015unbounded} (line \ref{alg:aa}).
+%%
+%\item Using Equation \eqref{eq:eigenInit}, transform the initial state into the eigenspace (line \ref{alg:eigeninit}).
+%%
+%\item Extract the vertices of the eigen-polyhedron $X_0'$ using the algorithms described in \cite{cattaruzza2015unbounded,cattaruzza2017sound} (line \ref{alg:getVertices}). 
+%%
+%\item Calculate the mapped \emph{abstract reach tube} ${\hat{X}'^\sharp}$
+%that over-approximates the image of the reach tube in the eigenspace (line
+%\ref{alg:getReachTube}).  This is achieved by evaluating a set of objective
+%functions using the abstract dynamics as a simplex Tableau, and via a sound
+%simplex described in \cite{cattaruzza2017sound}.  The objective functions are
+%defined by the vertices of $X'_0$, denote as $V_0$, and by the desired
+%template directions, such that
+%%
+%\begin{equation*}
+%\vec{w}_{ij}= \vec{v}_i \circ \vec{t}_j \text{ with } \vec{v}_i \in V_0 \text{ and } \vec{t}_j \in T,
+%\end{equation*}
+%%
+%where $T$ is the set of template directions, and $\circ$ denotes a
+%component-wise multiplication yielding a vector.
+%%
+%\item Using Equation~\eqref{eq:eigenInit}, find the reach tube
+%$\hat{X}^\sharp=\mat{S}{\hat{X}'^\sharp}$ (line \ref{alg:getNormReachTube}).
+%%
+%\end{enumerate}
+%
+%\begin{algorithm}[]
+%\small
+%\begin{algorithmic}[1]
+%\Function{$\mathit{findAbstractReachTube}()$}{}
+%\State $\hat{\mat{J}}=$ calculateEigenvalues($ \mat{A}$)
+%\label{alg:calcEigenvalues}
+%\State $\hat{\mat{S}}=$ calculateEigenvectors($ \mat{A}$)
+%\label{alg:calcEigenvectors}
+%\State $[\mat{J}]=$ soundifyEigenvalues($\mat{A},\mat{J},\mat{S}$)
+%\label{alg:soundEigenvalues}
+%\State $[\mat{S}]=$ soundifyEigenvectors($\mat{A},[\mat{J}],\mat{S}$)
+%\label{alg:soundEigenvectors}
+%\State $[\mat{S}]^{-1}=$ calculateInverse($[\mat{S}]$)
+%\label{alg:inverse}
+%\State $\mathcal{J}=getAbstractDynamics([\mat{J}])$
+%\label{alg:aa}
+%\State $[X_0']=$ transformInitialSpace($X_0,\mat{S}$)
+%\label{alg:eigeninit}
+%\State $[V_0]=$ getVertices($[X_0']$)
+%\label{alg:getVertices}
+%\State ${\hat{X}'^\sharp}=$ getReachTube($\mathcal{J},[V_0]$)
+%\label{alg:getReachTube}
+%\State ${\hat{X}^\sharp}=$ transformReachTube(${\hat{X}'^\sharp},[\mat{S}]^{-1}$)
+%\label{alg:getNormReachTube}
+%\EndFunction
+%\end{algorithmic}
+%\caption{Calculation of Abstract Reach Tube Using Abstract Acceleration}
+%\label{alg:findReachTube}
+%\end{algorithm}
+
+%%-------------------------------
+%\subsection{Overapproximating continuous time dynamics using discrete models}
+%\label{sec:cont_aa}
+%%-------------------------------
+%
+%Thus far we wave discussed the Abstract Accelertion of Discrete Time
+%systems.  However, our plant models derive from the discretization of
+%continuous time systems.  We therefore seek to establish a sound
+%overapproximation which does not only encompass the selected discretization,
+%but any chosen discretization in the time domain.
+%
+%A dynamical system is a system in which a function describes the progression
+%of a state over time.  In a continuous domain with linear dynamics, it is
+%described by a first order Ordinary Differential Equation (ODE).
+%%
+%\begin{equation}
+%\dot{x}(t)=\mat{A}_o\vec{x}(t)+\mat{B}_o\vec{u}(t)
+%\label{eq:dynamical}
+%\end{equation}
+%%
+%Furthermore, a control system may have a derived
+%output that is a linear combination of its states and inputs, which may
+%restricts the observability of the statespace from the output space.
+%%
+%\begin{equation}
+%\vec{y}(t)=\mat{C}_o\vec{x}(t)+\mat{D}_o\vec{u}(t)
+%\end{equation}
+%%
+%Discretization of a continuous dynamical system turns the ODE into a
+%difference equation, assuming zero-order hold for the input $\vec{u}$, to
+%%
+%\begin{align}
+%\label{eq:discretization}
+%\vec{x}_{k+1} &= \mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
+%y_k &= \mat{C}_d \vec{x}_ k + \mat{D}_d \vec{u}_ k 
+%\end{align}
+%where
+%\begin{align}
+%\label{eq:discretize}
+%\mat{A}_d &= e^{\mat{A}_o T_s} = \mathcal{L}^{-1} { ( s \mat{I} - \mat{A}_o )^{-1} }_{t = T_s}\\
+%\mat{B}_d &= \int_{t = 0}^{T_s} e^{\mat{A}_o t} dt\ \mat{B}_o = \mat{A}_o^{-1} ( \mat{A}_d - \mat{I} ) \mat{B}_o\\
+%\mat{C}_d &= \mat{C}_o\\
+%\mat{D}_d &= \mat{D}_o \\
+%\end{align}
+%and $T_s$ is the sample time. Then
+%\begin{align*}
+%x(kT)=x_k \wedge y(kT) = y_k, \forall k
+%\end{align*}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{Acceleration of continuous-time models}\label{sec:continuous_time_accel}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
+the state of the plant at integer multiples of the sample time.  
+%\note{Unlike the CAV18 paper, these gain matrices have not been discussed yet. }
+However, in
+order to synthesize $\mat{K}$, we must be able to ensure that
+certain properties of the plant hold at any given point in time.  In order
+to do so, we accelerate the dynamics of the plant according to the model
+semantics in Sec.~\ref{sec:model} and compute the state
+$\vec{x}_T$ at a given time $T$,
+%
+% namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
+%
+namely the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time
+$t=T$.
+
+%\note{ [add?] In this section we work with fully observed models, namely where $y = x$. } 
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Accelerated\! dynamics\! for\! continuous-time\! models\! without\! inputs}\label{sec:cont_acc_no_inputs}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+%
+Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a
+linear function of $\vec{x}_0$ as shown below.  We assume that the system
+has no inputs, so its dynamics are described by
+$\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.
+
+\begin{lemma}
+The solution to the differential equation $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, and $\mat{S}$ are the generalized eigenvectors of $\mat{A}$,
+evaluated at time $T$ is
+%
+\begin{align}
+ \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x} (0)\\
+ \mat{A}_{T}&= \mat{S}
+ \left [ \begin{array}{cccc}
+ e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(2)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
+0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
+\vdots & & \ddots & \vdots \\
+0 & \cdots & 0  &e^{T\lambda_i} \\
+\end{array} \right ]
+ \mat{S}^{-1}
+ \label{eq:continuous_tube_dyn2}\\
+ &\text{where } s_i=\left\{\begin{array}{cc}1&\quad gm(\lambda_i)>1\\0&\quad gm(\lambda_i)=1\end{array}\right.,\nonumber
+\end{align}
+%
+$\lambda_i$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.
+%
+%$\vec{x}_T$ is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T. 
+If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0 \text{ with } T \in \mathbb{R}^+_0$ is the state of the system at time $t=T$.
+\end{lemma}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Accelerated dynamics for models with parametric inputs}\label{sec:real_discrete_param_inputs}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Next, we are interested in studying models with parametric inputs, which are
+described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where
+$\forall t\geq 0.\,\vec{u}(t)=\vec{u}$.  For such models, a state $\vec{x}_T$
+is computed next.
+%
+\begin{lemma}
+%
+The state of the model
+$\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a
+parametric input $\vec{u}$ is
+%
+\begin{align}
+\vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u}
+\label{eq:continuous_tube_param}
+\end{align}
+%
+where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$, $\forall t \leq T.\, \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in
+\eqref{eq:continuous_tube_dyn2} \footnote{When $\mat{A}$ is not invertible,
+we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\
+0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$.}. 
+If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that
+$A_d=e^{\mat{A} T_d}$, then
+$\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u})
+\text{ with } T \in \mathbb{R}_0^+$ (where $\mat{A}_d^{\frac{T}{T_d}} =
+e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the
+system at time $T$.
+%
+\end{lemma}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsection{Accelerated dynamics for models with a sampled-time feedback}\label{sec:real_discrete_feedback_inputs}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+The final case we analyze is that of hybrid-time models, where the plant
+dynamics evolve in continuous time while the feedback dynamics evolve in
+discrete time.  A~new input value is produced only at every sample time but
+implemented over the continuous-time plant dynamics.
+%
+%\note{Matrix K has not been introduced yet. }
+\begin{theorem}
+The expression
+%
+ \begin{align}
+ \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0, 
+ \label{eq:cyber_feedback}
+ \end{align}
+%
+with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, $\mat{B}_T$ as in
+\eqref{eq:continuous_tube_param}, and where $\mat{A}_d=\mat{A}_{T_s}$,
+$\mat{B}_d=\mat{B}_{T_s}$ describe the discretized plant dynamics with
+sample time $T_s$, is the state of the model
+%
+\begin{align*}
+ \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
+ \vec{u}(t)=\mat{K}\vec{x}_k,  \,
+ kT_s \leq t < (k+1)T_s \,. 
+\end{align*}
+%
+\end{theorem}
+\begin{proof}
+%
+Let $\mat{K}$ be a feedback controller such that
+$\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$.  Let the output of the
+feedback system be a zero order holder such that
+$\vec{u}(t'+kT_s)=\vec{u}(kT_s), \text{ for } 0 \leq t' < T_s$.  The closed
+loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
+%
+\begin{align*}
+\vec{x}_{k,t'}=\mat{A}_{t'}\vec{x}_k-\mat{B}_{t'}\mat{K}\vec{x}_k = (\mat{A}_{t'}-\mat{B}_{t'}\mat{K})\vec{x}_k,
+\end{align*}
+where $0 \leq t' < T_s$
+We further explore the dynamics across discrete time boundaries. Let $\mat{A}_d=\mat{A}_{T_s}$ and $\mat{B}_d=\mat{B}_{T_s}$
+\begin{align*}
+\vec{x}_{k}&=\vec{x}_{k-1,T_s}= (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}\\
+\vec{x}_{k,T_s} &= (\mat{A}_d-\mat{B}_d\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}
+\end{align*}
+which accelerating results and setting $T=kT_s+t'$ becomes
+\begin{align}
+\label{eq:feedback_sampled_cont}
+\vec{x}_{k} &= (\mat{A}_d-\mat{B}_d\mat{K}) ^k\vec{x}_0\\
+\vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
+\label{eq:feedback_cont}
+\end{align}
+\end{proof}
+
+%-------------------------------
+ \subsection{Finding Abstract Supports for Continuous Dynamics}
+ \label{sec:cont_aasup}
+%-------------------------------
+
+Now that we have defined the dynamics of continuous time, we can use abstract acceleration techniques to evaluate
+the above model such that
+\begin{equation}\label{eq:aa_cont_amatrix}
+\bigcup_{T \in [0, T_s], k \in N_0} (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k \subseteq \mathcal{A}.
+\end{equation}
+
+Abstract acceleration works by finding support functions of the set that encompasses the matrices $\mat{A}^k$.
+Support functions are scalars that measure the distance of a hyperplane tangent to the set boundary to the origin.
+In the case of continuous spaces, this translates to calculating the derivatives of the envelope in order to find the direction of the support vector (normal to the hyperplane), and calculating the distance to the corresponding point where the hyperplane touches the set (at which the derivative was calculated).
+The direction of the vector is determined by evaluating the support function of another point in the curve,
+which is known to be smaller than that of the selected point, and the chosen hyperplanes are aligned with the eigenvectors, hence we only look at eigenvalue pairs to calculate the derivatives~\cite{cattaruzza2015unbounded}.
+The corresponding derivatives are:
+%
+\begin{enumerate}
+%
+\item for real eigenvalues: we first calculate the slope of the tangent
+between the two progressions: $\frac{d f(k)}{d g(k)}=\frac{f'(k)}{g'(k)}$. 
+Hence $\frac{d \lambda_1^k}{d \lambda_2^k}=\frac{log(\lambda_1)
+\lambda_1^k}{log(\lambda_2) \lambda_2^k}$.  From this we know that the polar
+angle of the support vector is $\psi = \tan^{-1}(\frac{log(\lambda_1)
+\lambda_1^k}{log(\lambda_2) \lambda_2^k})+\frac{\pi}{2}$
+%
+\item for conjugate eigenvalue pairs: the pair forms a logarithmic spiral. 
+The tangent of a spiral with polar equation $r=a e^{b\theta}$ will have a
+derivative $\frac{d r}{d \theta}=b a e^{b\theta}=b r$, hence the angle of
+the vector normal to the curve is $\tan^{-1}(\frac{r}{\frac{d r}{d
+\theta}})+\frac{\pi}{2}=\tan^{-1}(\frac{1}{b})+\frac{\pi}{2}$
+%
+\item for Jordan blocks with $gm>1$: in the case of real eigenvalues, we
+follow the same procedure as in the real case, but considering that the
+equation for each eigenvalue is $\frac{k^j}{j!}e^{\lambda k}$ where $j$ is
+the index of the term within the Jordan block (note that when $j=0$ the term
+is the same as for real eigenvalues above).  The derivatives f'(k),g'(k) are
+in the form $(j+k*log(\lambda))\frac{k^{j-1}}{j!}e^{\lambda k}$.
+%
+\item for any combination of complex eigenvalues we use the above equations
+using the envelope of their magnitude (ie $|\lambda|$).
+%
+\end{enumerate}
 

### 2018-03-12 automatica/paper.tex
Minor fixes

@@
 \begin{split}
-N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q_1}{2}\ \ \frac{q_1}{2}\right] 
+N=\left \{ \nu_1+\nu_2+ \nu_3 \mid \nu_1 \in \left[-\frac{q_1}{2}\ \ \frac{q_1}{2}\right] 
 \wedge \right. \\ \left. \nu_2 \in \left[-\frac{q_2}{2}\ \ \frac{q_2}{2}\right]  \wedge  \nu_3 \in \left[-q_3\ \ q_3\right]  \right \}
@@
 =\mathcal{A} X_0 + \mathcal{B}_{n} N, \quad
-X_0 =\left \{x : x \models \phi_\mathit{init} \right\}, 
+X_0 =\left \{x \mid x \models \phi_\mathit{init} \right\}, 
 \end{align}
@@
 %-------------------------------
-\subsection{Abstract Acceleration of Linear Dynamics} 
+\section{Abstract Acceleration of Linear Dynamics} 
 \label{ssec:aa}
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Acceleration of continuous-time models}\label{sec:continuous_time_accel}
+\subsection{Acceleration of continuous-time models}\label{sec:continuous_time_accel}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Accelerated\! dynamics\! for\! continuous-time\! models\! without\! inputs}\label{sec:cont_acc_no_inputs}
+\subsubsection{Accelerated\! dynamics\! for\! continuous-time\! models\! without\! inputs}\label{sec:cont_acc_no_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Accelerated dynamics for models with parametric inputs}\label{sec:real_discrete_param_inputs}
+\subsubsection{Accelerated dynamics for models with parametric inputs}\label{sec:real_discrete_param_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Accelerated dynamics for models with a sampled-time feedback}\label{sec:real_discrete_feedback_inputs}
+\subsubsection{Accelerated dynamics for models with a sampled-time feedback}\label{sec:real_discrete_feedback_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2018-03-13 automatica/paper.tex
revised intro

@@
 control software for such platforms is non-trivial, even in cases with
-restriceted dynamics.  We examine the case of Linear Time Invariant
-(LTI) models, for which the synthesis of controllers is well
-understood.  However, the use of digital control architectures adds
-new challenges caused by artifacts specific to digital control, such
-as the effects of finite-precision arithmetic, time discretization and
-quantization noise introduced by A/D and D/A conversion.
-
-In this paper we develop an automatic technique for generating digital
-controllers for a given continuous plant model that are correct by
-construction.  Specifically, we synthesize stable and safe,
+restricted dynamics.
+
+In this paper, we examine the case of Linear Time Invariant (LTI)
+models, for which the synthesis of controllers is well understood.
+However, the use of digital control architectures adds new challenges
+caused by artifacts specific to digital control, such as the effects
+of finite-precision arithmetic, time discretization and quantization
+noise introduced by A/D and D/A conversion.
+%
+Given an LTI model, we develop an automatic technique for generating
+correct by construction digital controllers that addresses all these
+challenges. Specifically, we synthesize stable and safe,
 software-implemented embedded controllers.  Due to the complexity of
 such closed-loop systems, we focus on linear models with known
-configurations, and perform parametric synthesis of controllers
-meeting a number of properties that define their desired behavior.
+configurations, and perform parametric synthesis of controllers.
+%meeting a number of properties that define their desired behavior.
 
@@
 
-Our work addresses challenging aspects of the control synthesis problem.  We
-perform digital control synthesis over a hybrid model, where the plant
-exhibits continuous behavior whereas the controller operates in discrete
-time and over a quantized domain.  In particular, our model evaluates the
-effects of the quantizers (A/D and D/A converters) and of time
-discretization, as well as representation errors introduced by in modelling
-artifacts such as an observer~\cite{astrom1997computer} in a finite
-precision domain, while reasoning about high level properties such as
-stability, robustness, and safety, which define the behaviour
-of the system.  In particular, safety requirements are frequently overlooked
-in conventional feedback control synthesis, but play an important role in
-systems engineering.
+Our work addresses challenging aspects of the control synthesis
+problem.  We perform digital control synthesis over a hybrid model,
+where the plant exhibits continuous behavior whereas the controller
+operates in discrete time and over a quantized domain.  In particular,
+our model evaluates the effects of the quantizers (A/D and D/A
+converters) and of time discretization, as well as representation
+errors introduced by modeling %% artifacts such as an
+%% observer~\cite{astrom1997computer}
+in a finite precision domain, while reasoning about high level
+properties such as stability, robustness, and safety, which define the
+behaviour of the system.  Notably, safety requirements are
+frequently overlooked in conventional feedback control synthesis, but
+play an important role in systems engineering.
 
@@
 This paper represents an extension of \cite{DBLP:conf/cav/AbateBCCDKKP17}
-and makes the following contributions, where the fourth and he fifth denote
+and makes the following contributions, where the fourth and the fifth denote
 extensions over \cite{DBLP:conf/cav/AbateBCCDKKP17}.

### 2018-03-13 automatica/paper.tex
more revised intro

@@
 %% Single-Input/Single-Output (SISO) systems.
-In this paper we present two novel approaches for the synthesis of digital controllers, 
-both of which use a CounterExample-Guided Inductive Synthesis (CEGIS)~\cite{%jha-icse10,
-DBLP:conf/asplos/Solar-LezamaTBSS06} as described next.
+In this paper we present two novel approaches for the synthesis of
+digital controllers, both of which make use of CounterExample-Guided
+Inductive Synthesis (CEGIS)~\cite{jha-icse10,
+  DBLP:conf/asplos/Solar-LezamaTBSS06}, an approach to program
+synthesis very popular in the recent years.  CEGIS denotes an
+iterative process, where each iteration performs inductive
+generalisation based on counterexamples provided by a verification
+oracle. Essentially, the inductive generalisation uses information
+about a limited number of inputs to make claims about all the possible
+inputs in the form of candidate solutions. Our two instantiations of
+CEGIS are described next.
 

### 2018-03-13 automatica/paper.tex
small change in intro

@@
   DBLP:conf/asplos/Solar-LezamaTBSS06}, an approach to program
-synthesis very popular in the recent years.  CEGIS denotes an
+synthesis that became very popular in the recent years.  CEGIS denotes an
 iterative process, where each iteration performs inductive

### 2018-03-13 automatica/paper.tex
revised sec 2

@@
 
-\textbf{CEGIS -}
-Program synthesis is the problem of computing correct-by-design programs
-from high-level specifications. Algorithms for this problem have made
-substantial progress in recent years, for instance~\cite{itzhaky2010simple} 
-to inductively synthesize invariants for the generation of desired programs.
+\textbf{CEGIS -} Program synthesis is the problem of computing
+correct-by-design programs from high-level specifications. Algorithms
+for this problem have made substantial progress in recent years, in
+particular CEGIS, which is a recent approach to inductive synthesis
+borrowing ideas from Counter-Example Guided Abstraction Refinement
+(CEGAR)~\cite{DBLP:conf/cav/ClarkeGJLV00} and
+superoptimisation~\cite{DBLP:conf/iclp/BrainCVF06,
+  DBLP:conf/asplos/Massalin87}.  This approach uses an iterative
+process where each iteration performs inductive generalisation based
+on counterexamples provided by a verification oracle.  In the absence
+of complete specifications, oracles are queried to distinguish between
+non-equivalent
+programs~\cite{jha-icse10,DBLP:conf/fmcad/AlurBJMRSSSTU13}.
+
+%% for instance~\cite{itzhaky2010simple} 
+%% to inductively synthesize invariants for the generation of desired programs.
 

### 2018-03-13 automatica/paper.tex
small change in intro

@@
 Inductive Synthesis (CEGIS)~\cite{jha-icse10,
-  DBLP:conf/asplos/Solar-LezamaTBSS06}, an approach to program
-synthesis that became very popular in the recent years.  CEGIS denotes an
+  DBLP:conf/asplos/Solar-LezamaTBSS06}, a technique
+that became very popular in the recent years.  CEGIS denotes an
 iterative process, where each iteration performs inductive

### 2018-03-13 automatica/paper.tex
prelims

@@
 \section{Preliminaries}
-\label{sec:preliminaries}
-%-------------------------------
-
-%-------------------------------
-\subsection{State-space representations of LTI models}
+%\label{sec:preliminaries}
 \label{sec:model}
+%-------------------------------
+
+%-------------------------------
+%\subsection{State-space representations of LTI models}
+%\label{sec:model}
 %-------------------------------
@@
 We consider models of physical plants expressed as ordinary differential
-equations, which we assume to be controllable~\cite{Astrom08,
-astrom1997computer}: %\note{Pls eliminate bold quantities, unless strictly needed. }
+equations, which we assume to be controllable~\cite{Astrom08}: 
 %
@@
 \label{eq:ode1}
-\dot{x}(t) = \mat{A}\vec{x}(t)+ \mat{B} \vec{u}(t), \quad 
-\vec{x} \in \mathbb{R}^p, \vec{u} \in \mathbb{R}^q,\,
-\mat{A} \in \mathbb{R}^{p \times p},\,
-\mat{B} \in \mathbb{R}^{p \times q},
+\dot{x}(t) = \mat{A}\vec{x}(t)+ \mat{B} \vec{u}(t), 
 \end{align}
 %
-where $t \in \mathbb R_0^+$ denotes continuous time, $\mat{A}$ and $\mat{B}$
-are matrices that fully characterize the dynamics of the continuous plant,
-and $x(0)$ is the initial state.
-
-Equation~\eqref{eq:ode1} is soundly discretized in
-time~\cite{middleton1990digital,van1978computing} at constant intervals,
-whose duration we refer to as the sample time $T_s$, into the difference
-equation
+where 
+$\vec{x} \in \mathbb{R}^p$,  
+$\vec{u} \in \mathbb{R}^q$, 
+$\mat{A} \in \mathbb{R}^{p \times p}$, 
+$\mat{B} \in \mathbb{R}^{p \times q}$,
+and $t \in \mathbb R_0^+$ denotes continuous time. 
+%$\mat{A}$ and $\mat{B}$ are matrices that fully characterize the dynamics of the continuous plant,
+We denote with $x(0)$ the initial state of the model.
+
+Equation~\eqref{eq:ode1} is soundly discretized in time~\cite{middleton1990digital,van1978computing} at constant time intervals,
+of duration $T_s$ (the sample time), 
+into the difference equation
 %
@@
 \label{eq:plant}
-\vec{x}_{k+1} =& \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k
-\text{ where }
-\left\{
-\begin{array}{l}
-\mat{A}_d=e^{\mat{A}T_s}\\
-\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}
-\end{array}
-\right.,
+\vec{x}_{k+1} =& \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k, 
 \end{align} 
-where $k \in \mathbb N$ is a discrete counter and $\vec{x}_{0}=\vec{x}(0)$
-is the initial state.
-
-Later, we will address the issue of variable quantization, as introduced by the ADC/DAC conversion blocks.
+where 
+$\mat{A}_d=e^{\mat{A}T_s}$ and 
+$\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$, 
+and where $k \in \mathbb N$ is a discrete counter and $\vec{x}_{0}=\vec{x}(0)$ denotes the initial state.
+
 Models \eqref{eq:ode1} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t)$ and  $u_k$, respectively. 
-Feedback architectures can be employed to manipulate the properties and behaviors of the continuous process (the plant).   
+Feedback architectures can be employed to manipulate the properties and behaviors of the plant.   
 We are interested in the synthesis of digital feedback control algorithms, 
-as implemented on Field-Programmable Gate Arrays or Digital Signal Processors. 
-The most basic feedback architecture is the state feedback one, 
-where the control action $u_k$ (notice we work with the discretized signal) is computed by: 
-%
-\begin{equation*}
-%\label{eq:controlaction}
-u_k = r_{k} - K x_k. 
-\end{equation*}
-
-where $K \in \mathbb{R}^{m \times n}$ is a state-feedback gain matrix, 
-and $r_{k}$ is a reference signal (again digital). We will assume $r_k=0$, thus 
-\begin{equation}
-\vec{x}_{k+1}=(\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_k
-\end{equation}
-Which corresponds to a closed loop system without inputs.
+as practically implemented on Field-Programmable Gate Arrays or Digital Signal Processors. 
+Later, we will address the issue of variable quantization, 
+introduced by ADC/DAC conversion blocks of Figure \ref{DSSynth_process}, 
+as classically studied in \cite{astrom1997computer}.
+
+We consider state feedback control architectures, 
+where $u_k$ (notice we work with the discretized signal) is $u_k = r_{k} - K x_k$. 
+Here $K \in \mathbb{R}^{m \times n}$ is a state-feedback gain matrix, 
+and $r_{k}$ is a reference signal (again digital). 
+We will assume $r_k=0$, thus 
+$\vec{x}_{k+1}=(\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_k$.
 

### 2018-03-13 automatica/paper.tex
prelims

@@
 $\vec{x}_{k+1}=(\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_k$.
+
+\textcolor{red}{[Where are we defining the specifications/properties of interest?]}
+
+\textcolor{red}{[Where are the specifics of the errors due to discretisation/quantisation discussed?]}
 
@@
 number of assumptions on the polynomial coefficients, following Jury's
-Criteria, as well as the restrictions on the representation of these
+criterion, as well as the restrictions on the representation of these
 coefficients.% as discussed in detail in Section~\ref{synthesis-elements}.

### 2018-03-13 automatica/paper.tex
specs

@@
 
+\textcolor{red}{[Why are these specs discussed only here? Isn't this way too late? ]}
+
 %-------------------------------
@@
 %and another one based on Jury's criterion~\cite{astrom1997computer}.  
-Here we choose Jury's criterion~\cite{astrom1997computer} in view of its efficiency 
+Here we choose Jury stability criterion~\cite{astrom1997computer} in view of its efficiency 
 and ease of integration within \tool: 
-we employ this method to check the stability in the $z$-domain for the
-characteristic polynomial $S(z)$.
+this method checks the stability working in the $z$-domain of the characteristic polynomial $S(z)$,  
 %
@@
 %
-We~consider the following form for $S(z)$:
+considered in its general form as 
+% for $S(z)$:
 %
@@
 %\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?} 
-
 % Assuming that $\hat{G}(z) = \frac{\hat{N_G}(z)}{\hat{D_G}(z)}$
@@
 % $$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$
-Next, the following matrix
+The following matrix
 $M = [m_{ij}]_{(2N-2)\times N}$ is built from $S(z)$ coefficients:
@@
 and where $k \in \mathbb{Z}$ is such that $0 < k < N - 2$. 
-We have that~\cite{astrom1997computer} 
-$S(z)$ is the
-characteristic polynomial of a stable system if and only if the following four conditions hold:
+We have that $S(z)$ is the characteristic polynomial of a stable system if and only if the following four conditions hold~\cite{astrom1997computer}:
 %\begin{itemize}
@@
 $
-\phi_\mathit{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
+\phi_\mathit{stability} := (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
 $
@@
 safety requirements with an overall approach that is sound and automated. 
-More specifically, we require that the closed-loop system
- meets given safety specifications.  A safety
-specification gives raise to a requirement on the states of the model, such
-that the feedback controller (namely the choice of the gains matrix~$K$)
-must ensure that the state never violates the requirement.  Note that a
-stable, closed-loop system is not necessarily a safe system: indeed, the
-state values may leave the safe part of the state space while they converge
-to the equilibrium, which is typical in the case of oscillatory dynamics. 
+%More specifically, we require that the closed-loop system meets given safety specifications.  
+A safety specification translates to a requirement on the states of the closed-loop model, 
+and the feedback controller (namely the choice of the gains matrix~$K$) 
+must ensure that the state never violates the requirement.  
+Note that a stable, closed-loop model is not necessarily a safe system: 
+indeed, the state values may leave the safe part of the state space while they converge
+to the equilibrium, which is typical in the case of oscillatory convergent dynamics. 
 %However, a safe system will always be stable.  
@@
 \label{eq:safetyliteral}
-\phi_\mathit{safety}\iff \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
+\phi_\mathit{safety} := \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
 \end{equation}
@@
 
-Furthermore, it is practically relevant to consider the 
-constraints $\phi_\mathit{input}$ on the input
-signal $u_{k}$ and $\phi_\mathit{init}$ on the initial states $x_0$,
-which we assume have given bounds:
-$\phi_\mathit{input} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
-$\phi_\mathit{init} = \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$
-For the former, this means that the control input might saturates in view of
-physical constraints.
+Furthermore, it is practically relevant to consider constraints $\phi_\mathit{input}$ on the input
+signal $u_{k}$ and requirements $\phi_\mathit{init}$ on the initial states $x_0$, 
+both of which we be expressed via given bounds as: 
+$\phi_\mathit{input} := {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
+and $\phi_\mathit{init} := \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}$. 
+For the input signal, these requirements practically mean that the control input saturates in view of physical constraints.
 

### 2018-03-13 automatica/paper.tex
sec 5

@@
 %
+\textcolor{red}{[these specifications are (wrongly) introduced only in a later part of the manuscript!]}
 $$(\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-K x_k)
@@
 
-We recall a technique called \emph{Abstract Acceleration}~\cite{JSS14,cattaruzza2015unbounded}, 
-which will be key for abstraction-based synthesis.  
+We recall a recently introduced technique called \emph{Abstract Acceleration}~\cite{JSS14,cattaruzza2015unbounded}, 
+which will be key in this work for abstraction-based synthesis.  
 %\note{This clashes with the model introduced above, with inputs - motivate why? I've added the motivation above by introducing the closed  loop}
@@
 %
+\textcolor{red}{[we should use the notations (with the `d' subscript) in the Preliminaries section.]}
 we want to find all possible states visited over an infinite time horizon
@@
 In this work we use an extension of the abstract acceleration model for
-continuous time. For this reason we must first look at the accelerationm of continuous time dynamics.
+continuous time. 
+% and  For this reason we must first look at the acceleration of continuous-time dynamics.
 
@@
 order to synthesize $\mat{K}$, we must be able to ensure that
-certain properties of the plant hold at any given point in time.  In order
+certain properties \textcolor{red}{[unknown because undefined at this point \ldots]} of the plant hold at any given point in time.  In order
 to do so, we accelerate the dynamics of the plant according to the model
@@
 
-\textcolor{red}{Elizabeth: this section needs to be updated to describe about floating-point arithmetic.}
-
-The models we consider have two sources of error that are due to numerical  
-representation.  The first is the numerical error introduced by the
+\textcolor{red}{Elizabeth: this section needs to be updated to describe floating-point arithmetics.}
+
+The models we consider have two sources of error that are due to numerical representations.  
+The first is the numerical error introduced by the
 fixed-point numbers employed to model the plant, i.e., to represent the
@@
 introduced by the digital controller, which performs operations on
-fixed-point numbers.  In this section we outline the notation for the
+fixed-point numbers.  
+\textcolor{red}{[what about the DAC/ADC errors?]}
+In this section we outline the notation for the
 fixed-point representation of numbers, and briefly describe the errors

### 2018-03-14 automatica/paper.tex
update benchmark description

@@
 
-The \textit{continuous stirred tank reactor} plant describes a linear model for PH dynamics of a PH 
-neutralization process of an aqueous solution of sodium acetate with 
-hydrochloric acid in a continuous flow stirred-tank reactor. 
+There are two \textit{continuous stirred tank reactor} models that describes the PH dynamics of a neutralization 
+reaction of an aqueous solution of sodium acetate with  hydrochloric acid (CSTR1)~\cite{cstr} and the temperature of a 
+exothermic reaction~\cite{astrom2006advanced} in a continuous flow stirred-tank  reactor. The \textit{bioreactor} 
+benchmark is a linear model identified by least squares for the cell mass concentration controlled through dilution 
+rate of a bioreactor~\cite{bioreactor}. The \textit{steam drum} benchmark describes the linear model for the 
+level dynamics of a  boiler steam drum~\cite{boiler}.
 The \textit{flexible beam} is a plant employed in vibration studies; the physical system consists of a flexible 

### 2018-03-14 automatica/paper.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-There are two \textit{continuous stirred tank reactor} models that describes the PH dynamics of a neutralization 
+There are two \textit{continuous stirred tank reactor} models that describe the PH dynamics of a neutralization 
 reaction of an aqueous solution of sodium acetate with hydrochloric acid (CSTR1)~\cite{cstr} and the temperature of a 

### 2018-03-14 automatica/paper.tex
intro

--- 2018-03-14 automatica/paper.tex
@@
 
-We provide experimental results showing that all our approaches are able to
+We provide experimental results showing that both our approaches are able to
 efficiently synthesize safe controllers for a set of intricate physical
 plant models taken from the digital control literature.
+\addtodo{add more here once we have the experimental results ready}
 

### 2018-03-14 automatica/paper.tex
removed abbreviation
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 There are two \textit{continuous stirred tank reactor} models that describe the PH dynamics of a neutralization 
-reaction of an aqueous solution of sodium acetate with hydrochloric acid (CSTR1)~\cite{cstr} and the temperature of a 
+reaction of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and the temperature of a 
 exothermic reaction~\cite{astrom2006advanced} in a continuous flow stirred-tank reactor. The \textit{bioreactor} 

### 2018-03-14 automatica/paper.tex
moved the DSSynth tool description
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
reviewed the section about the DSSynth tool
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 Later, we will address the issue of variable quantization, 
-introduced by ADC/DAC conversion blocks of Figure \ref{DSSynth_process}, 
+introduced by ADC/DAC conversion blocks of Figure \ref{fig:digitalsystem}, 
 as classically studied in \cite{astrom1997computer}.
@@
 %-------------------------------
-
-In order to synthesize closed-loop digital control systems, we use a program
-synthesis engine.  Our program synthesizer implements Counter-Example Guided
-Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}.  We
-start by presenting its general architecture followed by describing the
-parts specific to closed-loop control systems.  A high-level view of the
-synthesis process is given in Figure~\ref{DSSynth_process}.  Steps $1$ to
-$3$ are performed by the user and Steps~A to D are automatically performed
-by our tool for Digital Systems Synthesis, named \tool.
-
-CEGIS-based control synthesis requires a formal verifier to check whether a
-candidate controller meets the requirements when combined with the plant. 
-We use the Digital-System Verifier (DSVerifier)~\cite{IsmailBCFF15} in the
-verification module for \tool.  It checks the stability of closed-loop control systems and
-considers finite-word length (FWL) effects in the digital controller and
-uncertainty parameters in the plant model (plant intervals)~\cite{Bessa16}.
-
-%
-%, which accepts the
-%digital controller transfer functions together with the plant model.  For
-%any digital controller, implementation details should be provided ({\it
-%e.g.}, number of bits, realization, and sample time).
-
-\begin{figure*}[t]
-\centering
-\includegraphics[width=\textwidth]{figures/synthesis-flow.pdf}
-\vspace{0.1cm}
-\caption{Overview of the synthesis process\label{DSSynth_process}}
-\end{figure*}
-
-%In Step $1$, the user provides inputs $G(z)$ and $\Delta{G}(z)$
-%%$\%$ ({\it i.e.}, $\Delta{G}(z)$ as a percentage of $G(z)$)
-%, which contain the plant model and the
-%interval, respectively.  In Step $2$, a digital controller must be designed
-%with any preferred method, where $C(z)$ is obtained.  The controller
-%numerical representation and realization form are chosen in Steps $3$ and
-%$4$, respectively.  In Step $5$, the user finally configures the
-%verification parameters ({\it e.g.}, verification time, properties, and BMC
-%tool).  After that, DSVerifier verification engine performs an (automatic)
-%verification of the desired property $\phi$ ({\it i.e.}, stability).  The
-%user steps described in Steps $1$--$5$ result in an ANSI-C code that should
-%be used as an input for DSVerifier.
-
-Given a plant model in ANSI-C syntax as input (Steps 1--3), \tool constructs
-a non-deterministic model to represent the plant family, i.e., it addresses
-plant variations as interval sets (Step~A), and formulates a function
-(Step~B) using implementation details provided in Steps~$2$ and $3$ to
-calculate the controller parameters to be synthesized (Step~C).  Note that
-\tool synthesizes the controller for the desired numerical representation
-and realization form.  Finally, \tool builds an intermediate ANSI-C code for
-the digital system implementation, which is used as input for the CEGIS
-engine (Step~D).
-
-This intermediate ANSI-C code model contains a specification $\phi$ for the
-property of interest (i.e., robust stability) and is passed to the
-Counterexample-Guided Inductive Synthesis (CEGIS) module of
-CBMC~\cite{ClarkeKL04}, where the controller is marked as the input variable
-to synthesize.  CEGIS employs an iterative, counterexample-guided refinement
-process.%, which is explained in detail in Section~\ref{synthesizer-general}. 
-CEGIS reports a successful synthesis result if it generates a controller
-that is safe with respect to~$\phi$.  In particular, the ANSI-C code model
-guarantees that a synthesized solution is complete and sound with respect to
-the stability property~$\phi$, since it does not depend on system inputs and
-outputs.  In the case of stability, the specification~$\phi$ consists of a
-number of assumptions on the polynomial coefficients, following Jury's
-criterion, as well as the restrictions on the representation of these
-coefficients.% as discussed in detail in Section~\ref{synthesis-elements}.
 
@@
 %-------------------------------
+\section{DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants}
+\label{sec:dssynthtool}
+%-------------------------------
+
+\begin{figure*}[t]
+\centering
+\includegraphics[width=0.7\textwidth]{figures/synthesis-flow.pdf}
+\caption{Phases of the controller synthesis}
+\label{fig:synthesis-flow}
+\end{figure*}
+
+The proposed synthesis methodology for closed-loop digital control
+systems is based on the Digital-System Synthesizer 
+(DSSynth) tool~\cite{DBLP:conf/kbse/AbateBCCCDKKP17}, 
+which can be split into two main stages as follows: manual and 
+automated steps, as illustrated in Fig.~\ref{fig:synthesis-flow}.
+
+In Step~1, the user selects the digital controller representation, which
+can be a transfer function or a state-space model.  In Step~2, the
+physical plant in the form of Equation~\eqref{eq:ode1} must be
+given~\cite{astrom1997computer}.  Finally, in Step~3, the numerical
+representation for the digital controller implementation must be set by the
+user, i.e., the FWL format that defines the number of bits of the integer
+and fractional parts as well as the dynamic range inputs.  The input 
+provided by the user is a specification of the physical plant.
+
+After that, the automated synthesis process starts with Step~A, where the
+\tool translates the digital system specification from the MATLAB format
+into an ANSI-C program.  In Step~B, our CEGIS engine is invoked to
+synthesize the digital controller w.r.t.~the digital system specification. 
+Finally, in Step~C, the synthesized digital controller is produced.  The
+output generated by the \tool is the synthesized digital controller
+represented either in transfer function or state-space equation.  The
+synthesis is considered to be \emph{successful} if a digital controller is
+correctly synthesized w.r.t.~FWL effects; otherwise, if any parameter is
+incorrectly defined in previous steps, or if there is no solution (no
+controller) for the respective physical plant (given the implementation
+requirements), then the synthesis is considered to have \emph{failed}.
+
+Our CEGIS engine is implemented as an integrated module within the C bounded
+model checker (CBMC)~\cite{ClarkeKL04}.  CBMC transforms the ANSI-C representation
+of our closed-loop control system model into its internal representation (IR).  We
+instrument this IR for each synthesis or verification scenario accordingly,
+and use CBMC as an oracle to answer our queries.  CBMC itself relies on an
+underlying SAT or SMT solver to solve verification conditions.  We~model FWL
+effects, time discretization and the presence of quantization noise
+explicitly using CBMC's nondeterminism API (e.g., \texttt{nondet},
+\texttt{CPROVER\_assume} intrinsic functions).  Our module is included in
+CBMC~5.7 and is available for
+download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}
+\textcolor{red}{Lucas: I'll need support from Pascal to create this VirtualBoxOVA}
+We further created a VirtualBox OVA image with our tool pre-installed,
+including our MATLAB-generated benchmarks and benchmark shell script with
+instructions to run all benchmarks and reproduce our
+experiments.\footnote{\url{XXXXXXXXXX}}
+
+\textcolor{red}{This paragraph needs to be updated by Elizabeth and Dario.}
+
+The entire implementation consists of $XXX$ and $XXX$ lines of C code in the naive and abstract
+accelerator back-ends, respectively, $XXXX$ lines of C code for utility functions such as interval, 
+fixed- and floating-point arithmetic, as well as $1000$ lines of C++ code in the control synthesis
+module in CEGIS CBMC.  We evaluate \tool using $XXX$ SISO control system
+benchmarks.
+
+%-------------------------------
 \section{Experimental Evaluation}

### 2018-03-14 automatica/paper.tex
reviewed the DSSynth tool description
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-In Step~1, the user selects the digital controller representation, which
-can be a transfer function or a state-space model.  In Step~2, the
-physical plant in the form of Equation~\eqref{eq:ode1} must be
+In Step~1, the user selects the closed-loop digital control
+system representation, which can be a transfer function or a state-space model.  
+In Step~2, the physical plant (e.g., in the form of Equation~\eqref{eq:ode1}) must be
 given~\cite{astrom1997computer}.  Finally, in Step~3, the numerical
@@
 user, i.e., the FWL format that defines the number of bits of the integer
-and fractional parts as well as the dynamic range inputs.  The input 
+and fractional parts when using fixed-point arithmetic or half- and single-precision 
+when using floating-point arithmetic as well as the dynamic range inputs.  The input 
 provided by the user is a specification of the physical plant.
@@
 After that, the automated synthesis process starts with Step~A, where the
-\tool translates the digital system specification from the MATLAB format
-into an ANSI-C program.  In Step~B, our CEGIS engine is invoked to
+\tool~translates the digital system specification into an ANSI-C program.  
+In Step~B, our CEGIS engine is invoked to
 synthesize the digital controller w.r.t.~the digital system specification. 
 Finally, in Step~C, the synthesized digital controller is produced.  The
-output generated by the \tool is the synthesized digital controller
+output generated by the \tool~is the synthesized digital controller
 represented either in transfer function or state-space equation.  The
@@
 explicitly using CBMC's nondeterminism API (e.g., \texttt{nondet},
-\texttt{CPROVER\_assume} intrinsic functions).  Our module is included in
+\texttt{CPROVER\_assume} intrinsic functions).  Our module is included into
 CBMC~5.7 and is available for
@@
 fixed- and floating-point arithmetic, as well as $1000$ lines of C++ code in the control synthesis
-module in CEGIS CBMC.  We evaluate \tool using $XXX$ SISO control system
+module in CEGIS CBMC.  We evaluate \tool~using $XXX$ SISO control system
 benchmarks.

### 2018-03-15 automatica/paper.tex
+ preliminaries on CEGIS

@@
 \usetikzlibrary{patterns}
+
+\tikzset{
+    %Define style for boxes
+    box/.style={
+           rectangle,
+           rounded corners,
+           draw=black, very thick,
+           fill=yellow!20,
+           text width=10em,
+           minimum height=2em,
+           text centered},
+ % 
+  futurebox/.style={
+           rectangle,
+           rounded corners,
+           draw=black, very thick,
+           fill=blue!10,
+           text width=10em,
+           minimum height=2em,
+           text centered},
+ % 
+  longfuturebox/.style={
+           rectangle,
+           rounded corners,
+           draw=black, very thick,
+           fill=purple!20,
+           text width=10em,
+           minimum height=2em,
+           text centered},
+%
+    % Define arrow style
+    arrow/.style={
+           ->,
+           thick,
+           shorten <=2pt,
+           shorten >=2pt,}
+}
+
 \usepackage{url}
@@
 %% \end{equation}
+
+%-------------------------------
+\subsection{State-space representation of physical systems}
+\label{sec:model}
+%-------------------------------
 
@@
 %-------------------------------
-\section{Counterexample Guided Inductive Synthesis} 
+\subsection{Counterexample Guided Inductive Synthesis} 
 \label{ssec:cegis}
@@
 
-%-------------------------------
-\subsection{CEGIS of digital controllers} 
+\begin{figure*}
+%\hspace{-2cm}
+\centering
+\resizebox{.57\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto,
+ semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
+},
+          row sep=1cm, column sep=3cm] {
+   \node[fill=gray!20] (synth) {{\sc Synthesize}};
+   \&
+   \node[fill=gray!20] (verif) {{\sc Verify}};
+   \&
+   \node[ellipse,fill=gray!20] (done) {{\sc Done}}; 
+    \\
+  };
+
+   \path
+   ([yshift=2em]synth.east) edge node[align=center] {Candidate solution} ([yshift=2em]verif.west)
+    ([yshift=-2em]verif.west) edge node[align=center] {Counter-example} ([yshift=-2em]synth.east)
+    (verif) edge node {} (done);
+ \end{tikzpicture}
+}
+ \caption{The CEGIS framework. \label{fig:CEGIS}}
+\end{figure*}
+
+In this section, we give a brief description of the CEGIS framework, as illustrated in Figure~\ref{fig:CEGIS}.
+
+The input specification provided to CEGIS is of the form
+$\exists P .\, \forall a.\, \sigma(a, P)$, where $P$ ranges over functions
+(where a function is represented by the program computing it),
+$a$ ranges over ground terms, and $\sigma$ is a quantifier-free formula. 
+We~interpret the ground terms over some finite domain~$\mathcal{D}$.
+%
+
+The design of our synthesizer consists of two phases, an inductive
+synthesis phase (denoted by {\sc Synthesize} in
+Figure~\ref{fig:CEGIS}) and a validation phase (denoted by {\sc
+  Verify}), which interact via a finite set of test vectors {\sc
+  inputs} that is updated incrementally.  Given the aforementioned
+specification $\sigma$, the inductive synthesis procedure tries to
+find an existential witness $P$ satisfying the specification
+$\sigma(a, P)$ for all $a$ in {\sc inputs} (as opposed to all $a \in
+\mathcal{D}$).
+%
+If the synthesis phase succeeds in finding a witness~$P$, this witness is a
+candidate solution to the full synthesis formula.  We pass this candidate
+solution to the validation phase, which checks whether it is a full solution
+(i.e., $P$ satisfies the specification $\sigma(a, P)$ for all
+$a\in\mathcal{D}$).  If this is the case, then the algorithm terminates. 
+Otherwise, additional information is provided to the inductive synthesis
+phase in the form of a new counterexample that is added to the {\sc inputs}
+set and the loop iterates again.  %% More details about the general
+%% architecture of the synthesizer can be found
+%% in~\cite{DBLP:conf/lpar/DavidKL15}.
+
+%-------------------------------
+\section{CEGIS of digital controllers} 
 \label{sssec:cegisdig}
@@
 %-------------------------------
-\subsubsection{Naive approach} 
+\subsection{Naive approach} 
 \label{sssec:naive}
@@
 %-------------------------------
-\subsubsection{Abstraction-based CEGIS} 
+\subsection{Abstraction-based CEGIS} 
 \label{sssec:abstraction}

### 2018-03-15 automatica/paper.tex
integrated the control properties within the cegis description

@@
 %% in~\cite{DBLP:conf/lpar/DavidKL15}.
+
+%-------------------------------
+\section{Formal specification of control systems properties} 
+\label{sec:specification}
+%-------------------------------
+
+While in the previous section we discussed the generic CEGIS
+framework, in the rest of the paper we will explain how we adapt it to
+the synthesis of digital controllers. For this purpose, we start by
+describing the specific property that we pass to the synthesizer as
+the specification $\sigma$. Namely, we are interested in capturing
+stability and safety, which we discuss in Sections~\ref{ssec:stabspecification}
+and~\ref{ssec:safespecification}, respectively.
+
+%-------------------------------
+\subsection{Formal specification of stability} 
+\label{ssec:stabspecification}
+%-------------------------------
+
+  There are a number of algorithms in our verification engine that can
+  be used for stability analysis~\cite{daes20161, Bessa16}.
+%one based on Schur's decomposition
+%and another one based on Jury's criterion~\cite{astrom1997computer}.  
+Here we choose Jury stability criterion~\cite{astrom1997computer} in view of its efficiency 
+and ease of integration within our implementation: 
+this method checks the stability working in the $z$-domain of the characteristic polynomial $S(z)$,  
+%
+% of the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$, where $Y(z)$ is the closed-loop system output and U(z) is the controller output. 
+%% \red{[unclear: what matrix? We need to clarify the relationship
+%% between the char. poly. $S(z)$ and the later quantities $\Delta
+%% N_{G}(z), \Delta D_{G}(z)$ and corresponding controller's
+%% structure.]}.
+%
+considered in its general form as 
+% for $S(z)$:
+%
+\begin{equation*}
+S(z) = a_0z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N=0, a_0\neq0. 
+\end{equation*}
+%\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?} 
+% Assuming that $\hat{G}(z) = \frac{\hat{N_G}(z)}{\hat{D_G}(z)}$
+% and $\hat{C}(z) = \frac{\hat{N_C}(z)}{\hat{D_C}(z)}$, then:
+% $$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$
+The following matrix
+$M = [m_{ij}]_{(2N-2)\times N}$ is built from $S(z)$ coefficients:
+%
+$$
+M=\left( 
+\begin{array}{c}
+V^{(0)}\\
+V^{(1)}\\
+\vdots\\
+V^{(N-2)}
+\end{array}
+\right), 
+$$
+%
+where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ such that:
+%
+$$
+v_{ij}^{(0)}=\left\{
+\begin{array}{ll}
+a_{j-1}, & \mbox{if}~i=1\\
+v_{(1)(N-j+1)}^{0},&\mbox{if}~i=2
+\end{array}
+\right.
+$$
+%
+$$
+v_{ij}^{(k)}=\left\{
+\begin{array}{ll}
+0,&\mbox{if}~j>n-k\\
+v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \mbox{if}~j\leq n-k ~\mbox{and}~i=1\\
+v_{(1)(N-j+1)}^{k},& \mbox{if}~j\leq n-k ~\mbox{and}~i=2\\
+\end{array}
+\right.
+$$
+%
+and where $k \in \mathbb{Z}$ is such that $0 < k < N - 2$. 
+We have that $S(z)$ is the characteristic polynomial of a stable system if and only if the following four conditions hold~\cite{astrom1997computer}:
+%\begin{itemize}
+%\item 
+$R_1: S(1) > 0$;
+%\item 
+$R_2: (−1)^N S(−1) > 0$;
+%\item 
+$R_3: |a_0| < a_N$;
+%\item 
+$R_4: m_{11} > 0 \wedge\allowbreak
+      m_{31}>0 \wedge\allowbreak
+      m_{51}>0 \wedge \ldots \wedge\allowbreak
+      m_{(2N{-}3)(1)}>0$.
+%\end{itemize}
+%
+The stability property is then encoded by a constraint of the form:
+$
+\phi_\mathit{stability} := (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
+$
+
+%-------------------------------
+\subsection{Formal specification of safety} 
+\label{ssec:safespecification}
+%-------------------------------
+
+We are not limited to the synthesis of digital stabilizing controllers -- a
+well known task in the literature on digital control systems -- but target
+safety requirements with an overall approach that is sound and automated. 
+%More specifically, we require that the closed-loop system meets given safety specifications.  
+A safety specification translates to a requirement on the states of the closed-loop model, 
+and the feedback controller (namely the choice of the gains matrix~$K$) 
+must ensure that the state never violates the requirement.  
+Note that a stable, closed-loop model is not necessarily a safe system: 
+indeed, the state values may leave the safe part of the state space while they converge
+to the equilibrium, which is typical in the case of oscillatory convergent dynamics. 
+%However, a safe system will always be stable.  
+In~this work, the safety property is expressed as:
+%
+\begin{equation}
+\label{eq:safetyliteral}
+\phi_\mathit{safety} := \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
+\end{equation}
+%
+%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
+%
+where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
+for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
+instant, respectively.  This means that the states will always be within an $n$-dimensional hyper-box.
+
+Furthermore, it is practically relevant to consider constraints $\phi_\mathit{input}$ on the input
+signal $u_{k}$ and requirements $\phi_\mathit{init}$ on the initial states $x_0$, 
+both of which we be expressed via given bounds as: 
+$\phi_\mathit{input} := {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
+and $\phi_\mathit{init} := \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}$. 
+For the input signal, these requirements practically mean that the control input saturates in view of physical constraints.
 
@@
 safety accounting for the finite-precision errors.
-
-%-------------------------------
-\section{Formal specification of control systems properties} 
-\label{sec:specification}
-%-------------------------------
-
-\textcolor{red}{[Why are these specs discussed only here? Isn't this way too late? ]}
-
-%-------------------------------
-\subsection{Formal specification of stability} 
-\label{ssec:stabspecification}
-%-------------------------------
-
-Next, we describe the specific property that we pass to the program
-synthesizer as the specification $\sigma$.  There are a number of 
-algorithms in our verification engine that can be used for stability analysis~\cite{daes20161, Bessa16}.  
-%one based on Schur's decomposition
-%and another one based on Jury's criterion~\cite{astrom1997computer}.  
-Here we choose Jury stability criterion~\cite{astrom1997computer} in view of its efficiency 
-and ease of integration within \tool: 
-this method checks the stability working in the $z$-domain of the characteristic polynomial $S(z)$,  
-%
-% of the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$, where $Y(z)$ is the closed-loop system output and U(z) is the controller output. 
-%% \red{[unclear: what matrix? We need to clarify the relationship
-%% between the char. poly. $S(z)$ and the later quantities $\Delta
-%% N_{G}(z), \Delta D_{G}(z)$ and corresponding controller's
-%% structure.]}.
-%
-considered in its general form as 
-% for $S(z)$:
-%
-\begin{equation*}
-S(z) = a_0z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N=0, a_0\neq0. 
-\end{equation*}
-%\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?} 
-% Assuming that $\hat{G}(z) = \frac{\hat{N_G}(z)}{\hat{D_G}(z)}$
-% and $\hat{C}(z) = \frac{\hat{N_C}(z)}{\hat{D_C}(z)}$, then:
-% $$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$
-The following matrix
-$M = [m_{ij}]_{(2N-2)\times N}$ is built from $S(z)$ coefficients:
-%
-$$
-M=\left( 
-\begin{array}{c}
-V^{(0)}\\
-V^{(1)}\\
-\vdots\\
-V^{(N-2)}
-\end{array}
-\right), 
-$$
-%
-where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ such that:
-%
-$$
-v_{ij}^{(0)}=\left\{
-\begin{array}{ll}
-a_{j-1}, & \mbox{if}~i=1\\
-v_{(1)(N-j+1)}^{0},&\mbox{if}~i=2
-\end{array}
-\right.
-$$
-%
-$$
-v_{ij}^{(k)}=\left\{
-\begin{array}{ll}
-0,&\mbox{if}~j>n-k\\
-v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \mbox{if}~j\leq n-k ~\mbox{and}~i=1\\
-v_{(1)(N-j+1)}^{k},& \mbox{if}~j\leq n-k ~\mbox{and}~i=2\\
-\end{array}
-\right.
-$$
-%
-and where $k \in \mathbb{Z}$ is such that $0 < k < N - 2$. 
-We have that $S(z)$ is the characteristic polynomial of a stable system if and only if the following four conditions hold~\cite{astrom1997computer}:
-%\begin{itemize}
-%\item 
-$R_1: S(1) > 0$;
-%\item 
-$R_2: (−1)^N S(−1) > 0$;
-%\item 
-$R_3: |a_0| < a_N$;
-%\item 
-$R_4: m_{11} > 0 \wedge\allowbreak
-      m_{31}>0 \wedge\allowbreak
-      m_{51}>0 \wedge \ldots \wedge\allowbreak
-      m_{(2N{-}3)(1)}>0$.
-%\end{itemize}
-%
-The stability property is then encoded by a constraint of the form:
-$
-\phi_\mathit{stability} := (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
-$
-
-%-------------------------------
-\subsection{Formal specification of safety} 
-\label{ssec:safespecification}
-%-------------------------------
-
-We are not limited to the synthesis of digital stabilizing controllers -- a
-well known task in the literature on digital control systems -- but target
-safety requirements with an overall approach that is sound and automated. 
-%More specifically, we require that the closed-loop system meets given safety specifications.  
-A safety specification translates to a requirement on the states of the closed-loop model, 
-and the feedback controller (namely the choice of the gains matrix~$K$) 
-must ensure that the state never violates the requirement.  
-Note that a stable, closed-loop model is not necessarily a safe system: 
-indeed, the state values may leave the safe part of the state space while they converge
-to the equilibrium, which is typical in the case of oscillatory convergent dynamics. 
-%However, a safe system will always be stable.  
-In~this work, the safety property is expressed as:
-%
-\begin{equation}
-\label{eq:safetyliteral}
-\phi_\mathit{safety} := \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
-\end{equation}
-%
-%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
-%
-where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
-for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
-instant, respectively.  This means that the states will always be within an $n$-dimensional hyper-box.
-
-Furthermore, it is practically relevant to consider constraints $\phi_\mathit{input}$ on the input
-signal $u_{k}$ and requirements $\phi_\mathit{init}$ on the initial states $x_0$, 
-both of which we be expressed via given bounds as: 
-$\phi_\mathit{input} := {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
-and $\phi_\mathit{init} := \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}$. 
-For the input signal, these requirements practically mean that the control input saturates in view of physical constraints.
 

### 2018-03-15 automatica/paper.tex
changes \sigma to \phi for consistency

@@
 The input specification provided to CEGIS is of the form
-$\exists P .\, \forall a.\, \sigma(a, P)$, where $P$ ranges over functions
+$\exists P .\, \forall a.\, \phi(a, P)$, where $P$ ranges over functions
 (where a function is represented by the program computing it),
-$a$ ranges over ground terms, and $\sigma$ is a quantifier-free formula. 
+$a$ ranges over ground terms, and $\phi$ is a quantifier-free formula. 
 We~interpret the ground terms over some finite domain~$\mathcal{D}$.
@@
   inputs} that is updated incrementally.  Given the aforementioned
-specification $\sigma$, the inductive synthesis procedure tries to
+specification $\phi$, the inductive synthesis procedure tries to
 find an existential witness $P$ satisfying the specification
-$\sigma(a, P)$ for all $a$ in {\sc inputs} (as opposed to all $a \in
+$\phi(a, P)$ for all $a$ in {\sc inputs} (as opposed to all $a \in
 \mathcal{D}$).
@@
 solution to the validation phase, which checks whether it is a full solution
-(i.e., $P$ satisfies the specification $\sigma(a, P)$ for all
+(i.e., $P$ satisfies the specification $\phi(a, P)$ for all
 $a\in\mathcal{D}$).  If this is the case, then the algorithm terminates. 
@@
 describing the specific property that we pass to the synthesizer as
-the specification $\sigma$. Namely, we are interested in capturing
+the specification $\phi$. Namely, we are interested in capturing
 stability and safety, which we discuss in Sections~\ref{ssec:stabspecification}

### 2018-03-15 automatica/paper.tex
introduction to the cegis for control sec
sec 3

@@
 
-%\author[Paestum]{Marcus Tullius Cicero}\ead{cicero@senate.ir},    % Add the 
-%\author[Rome]{Julius Caesar}\ead{julius@caesar.ir},               % e-mail address 
-%\author[Baiae]{Publius Maro Vergilius}\ead{vergilius@culture.ir}  % (ead) as shown
-
-%\address[Paestum]{Buckingham Palace, Paestum}  % Please supply                                              
-%\address[Rome]{Senate House, Rome}             % full addresses
-%\address[Baiae]{The White House, Baiae}        % here.
-
 \begin{keyword}                           % Five to ten keywords,  
-Digital Control; A/D converters; Control System Synthesis; Safety Analysis; Quantization Errors; Sampling.               % chosen from the IFAC 
+Digital control synthesis; Safety requirements; A/D converters; Quantization errors; Sampling.               % chosen from the IFAC 
 \end{keyword}                             % keyword list or with the 
@@
 
-\textcolor{red}{[Where are we defining the specifications/properties of interest?]}
-
-\textcolor{red}{[Where are the specifics of the errors due to discretisation/quantisation discussed?]}
+%-------------------------------
+\subsection{\textcolor{red}{[Elizabeth: please add the specifics of the errors due to discretisation/quantisation, with reference to Fig. \ref{fig:digitalsystem}]}}
+%\label{sec:}
+%-------------------------------
 
@@
 %-------------------------------
-\subsection{Counterexample Guided Inductive Synthesis} 
+\subsection{Counterexample Guided Inductive Synthesis - CEGIS} 
 \label{ssec:cegis}
@@
 
-The input specification provided to CEGIS is of the form
-$\exists P .\, \forall a.\, \phi(a, P)$, where $P$ ranges over functions
-(where a function is represented by the program computing it),
-$a$ ranges over ground terms, and $\phi$ is a quantifier-free formula. 
-We~interpret the ground terms over some finite domain~$\mathcal{D}$.
-%
-
-The design of our synthesizer consists of two phases, an inductive
-synthesis phase (denoted by {\sc Synthesize} in
+We consider an input specification of the form $\exists P .\, \forall a.\, \phi(a, P)$, 
+where $P$ ranges over functions (where a function is represented by the program computing it),
+$a$ ranges over ground terms, 
+and $\phi$ is a quantifier-free formula. 
+We~interpret the ground terms over some finite [CHECK: finite? are we doing only SAT or also SMT?] domain~$\mathcal{D}$. 
+This is a synthesis problem, where the objective is indeed to select a valid $P$ satisfying $\phi$ over all the $a$ terms. 
+CEGIS breaks down this generally hard synthesis problem into two easier parts.
+
+The design consists of two phases, an inductive synthesis phase (denoted by {\sc Synthesize} in
 Figure~\ref{fig:CEGIS}) and a validation phase (denoted by {\sc
-  Verify}), which interact via a finite set of test vectors {\sc
-  inputs} that is updated incrementally.  Given the aforementioned
-specification $\phi$, the inductive synthesis procedure tries to
+  Verify}), which interact via a finite set of tests {\sc
+  inputs} that is updated incrementally.  Given the specification $\phi$, the inductive synthesis procedure tries to
 find an existential witness $P$ satisfying the specification
@@
 %% in~\cite{DBLP:conf/lpar/DavidKL15}.
+[COMMENT ON TERMINATION?]
 
@@
 
-%-------------------------------
-\subsection{Naive approach} 
+In this section we discuss two instantiations of CEGIS: the first,
+na\"ive one, relies on an unfolding of the dynamics up to a
+completeness threshold, while the second one is abstraction-based and
+leverages abstraction refinement and acceleration to improve
+scalability while retaining soundness.
+
+%-------------------------------
+\subsection{Na\"ive approach} 
 \label{sssec:naive}

### 2018-03-15 automatica/paper.tex
sec 3

@@
 %-------------------------------
-\subsection{\textcolor{red}{[Elizabeth: please add the specifics of the errors due to discretisation/quantisation, with reference to Fig. \ref{fig:digitalsystem}]}}
+\subsection{\textcolor{red}{[Elizabeth: please add the specifics of the errors due to discretisation/quantisation, with reference to Fig.
+\ref{fig:digitalsystem}] and to what has been discussed in the Introductory section.}}
 %\label{sec:}
@@
 
-In this section, we give a brief description of the CEGIS framework, as illustrated in Figure~\ref{fig:CEGIS}.
+In this section, we give a brief description of the CEGIS framework, as illustrated in Figure~\ref{fig:CEGIS}. [ADD REFERENCE(S).]
 
@@
 %-------------------------------
+\subsection{Abstract Acceleration of Linear Dynamics} 
+\label{ssec:aa}
+%-------------------------------
+
+We recall a recently introduced technique called \emph{Abstract Acceleration}~\cite{JSS14,cattaruzza2015unbounded}, 
+which will be key in this work for abstraction-based synthesis.  
+%\note{This clashes with the model introduced above, with inputs - motivate why? I've added the motivation above by introducing the closed  loop}
+Given a model of an iterative program with dynamics
+%
+\begin{equation}
+\vec{x}_{k+1}=\mat{A_d}\vec{x}_k \text{ where } \vec{x}_k \in \mathbb{R}^p, \mat{A_d} \in \mathbb{R}^{p \times p} \text{ and } k \in \mathbb N_0,
+\end{equation}
+%
+\textcolor{red}{[I have modified the notations with the `d' subscript as above.]}
+we want to find all possible states visited over an infinite time horizon
+starting at an initial set $X_0$.  
+This set is known as the \emph{reach tube} of
+the model:
+%
+\begin{equation}
+\hat{X} = \{ \vec{x}_k: k \in \mathbb N_0, \vec{x}_0 \in X_0 \text{ and } \vec{x}_{k+1}=\mat{A_d}\vec{x}_k\}.
+\end{equation}
+%
+Using Abstract Acceleration we transform this sequential reachability problem into a one-step problem.  
+We first modify the problem statement by means of acceleration into
+%
+\begin{equation}
+\hat{X} = \{ \vec{x}_k=\mat{A_d}^k\vec{x}_0 : k \in N_0 \text{ and } \vec{x}_0 \in X_0 \}, 
+\end{equation}
+%
+and further define new model semantics and corresponding set: 
+%
+\begin{equation}\label{eq:aa_reachtube}
+\hat{X} \subseteq \hat{X}^\sharp = \mathcal{A}X_0, \text{ such that } \bigcup_{k \in [0\ \infty)} \mat{A_d}^k \subseteq \mathcal{A}, 
+\end{equation}
+%
+where the newly introduced \emph{abstract reach tube} $\hat{X}^\sharp$ is an
+over-approximation of the reach tube of the model \cite{JSS14}.  
+In this work we extend the abstract acceleration algorithm to continuous-time models. 
+% and  For this reason we must first look at the acceleration of continuous-time dynamics.
+
+%All we need to do is define the nature of $\mathcal{A}X_0$.
+%Let $\mat{S}\mat{J}\mat{S}^{-1}=\mat{A}$ be the eigen-decomposition of
+%$\mat{A}$, where $\mat{S}$ is the set of generalised eigenvectors of
+%$\mat{A}$ and $\mat{J}$ is the Jordan Form containing the eigenvalues of
+%$\mat{A}$ in its main diagonal.  We correspondingly define
+%$\mathcal{J}=\mat{S}^{-1}\mathcal{A}\mat{S}$, which is such that
+%$\mathcal{J} \supseteq \bigcup_{k \in [0\ \infty)} \mat{J}^k$.
+%
+%Since abstract acceleration operates in the eigenspace, wemust deal with some preliminary transformations.
+%Given a set $X=\{ \vec{x} \mid \mat{C}\vec{x} \leq \vec{d}\}$,
+%the linear transformation $\vec{x}'=\mat{S}^{-1}\vec{x}$ leads to the set 
+%%
+%\begin{equation}
+%X'= \mat{S}^{-1}X = \{\vec{x}' \mid \mat{C}\mat{S}\vec{x}'\leq \vec{d}\}.  
+%\label{eq:eigenInit}
+%\end{equation}
+%%
+%Analogously, let $X_0'=\mat{S}^{-1}X_0$ and
+%${\hat{X}'^\sharp}=\mat{S}^{-1}{\hat{X}^\sharp}$ be the initial set and the
+%abstract reach tube mapped onto the eigenspace of matrix $\mat{A}$.  We may
+%transform equation \eqref{eq:aa_reachtube} into: 
+%%
+%\begin{equation}
+%\hat{X}' \subseteq {\hat{X}'^\sharp} = \mathcal{J}X_0', 
+%\end{equation}
+%%
+%where $\hat{X}'=\mat{S}^{-1}\hat{X}$ and $\mathcal{J}$ is a convex
+%polyhedron representing restrictions on the eigenvalues of $\mat{A}$. 
+%$\hat{X}'^\sharp$ is calculated by applying a simplex algorithm with a
+%tableau defined by $\mathcal{J}$ and objective functions derived from each
+%vertex of $X_0'$ (step \eqref{alg:getReachTube} in Algorithm
+%\ref{alg:findReachTube} below).  We note, however, that if we wish to use
+%numerical analysis in the decomposition of $\mat{A}$, the Tableau in
+%$\mathcal{J}$ contains small intervals given by the errors, which cannot be
+%processed efficiently by a regular simplex and require a new procedure.
+%
+%The calculation of the abstract reach tube via abstract acceleration is
+%encompassed in Algorithm~\ref{alg:findReachTube}, which can be summarised as
+%follows (its steps are denoted in parentheses):
+%%
+%\begin{enumerate}
+%%
+%\item We perform unsound eigen-decomposition using an existing algebra package (lines \ref{alg:calcEigenvalues}-\ref{alg:calcEigenvectors}).
+%%
+%\item Then we restore soundness to the results using the methods described in \cite{cattaruzza2017sound} (lines \ref{alg:soundEigenvalues}-\ref{alg:soundEigenvectors}).
+%%
+%\item The inverse of the matrix of eigenvectors is calculated after soundness is restored, using interval arithmetic in order to ensure its soundness (line \ref{alg:inverse}).
+%%
+%\item The abstract dynamics are obtained by evaluating the convex hull of all powers of eigenvalues up to the desired number of iterations as described in \cite{cattaruzza2015unbounded} (line \ref{alg:aa}).
+%%
+%\item Using Equation \eqref{eq:eigenInit}, transform the initial state into the eigenspace (line \ref{alg:eigeninit}).
+%%
+%\item Extract the vertices of the eigen-polyhedron $X_0'$ using the algorithms described in \cite{cattaruzza2015unbounded,cattaruzza2017sound} (line \ref{alg:getVertices}). 
+%%
+%\item Calculate the mapped \emph{abstract reach tube} ${\hat{X}'^\sharp}$
+%that over-approximates the image of the reach tube in the eigenspace (line
+%\ref{alg:getReachTube}).  This is achieved by evaluating a set of objective
+%functions using the abstract dynamics as a simplex Tableau, and via a sound
+%simplex described in \cite{cattaruzza2017sound}.  The objective functions are
+%defined by the vertices of $X'_0$, denote as $V_0$, and by the desired
+%template directions, such that
+%%
+%\begin{equation*}
+%\vec{w}_{ij}= \vec{v}_i \circ \vec{t}_j \text{ with } \vec{v}_i \in V_0 \text{ and } \vec{t}_j \in T,
+%\end{equation*}
+%%
+%where $T$ is the set of template directions, and $\circ$ denotes a
+%component-wise multiplication yielding a vector.
+%%
+%\item Using Equation~\eqref{eq:eigenInit}, find the reach tube
+%$\hat{X}^\sharp=\mat{S}{\hat{X}'^\sharp}$ (line \ref{alg:getNormReachTube}).
+%%
+%\end{enumerate}
+%
+%\begin{algorithm}[]
+%\small
+%\begin{algorithmic}[1]
+%\Function{$\mathit{findAbstractReachTube}()$}{}
+%\State $\hat{\mat{J}}=$ calculateEigenvalues($ \mat{A}$)
+%\label{alg:calcEigenvalues}
+%\State $\hat{\mat{S}}=$ calculateEigenvectors($ \mat{A}$)
+%\label{alg:calcEigenvectors}
+%\State $[\mat{J}]=$ soundifyEigenvalues($\mat{A},\mat{J},\mat{S}$)
+%\label{alg:soundEigenvalues}
+%\State $[\mat{S}]=$ soundifyEigenvectors($\mat{A},[\mat{J}],\mat{S}$)
+%\label{alg:soundEigenvectors}
+%\State $[\mat{S}]^{-1}=$ calculateInverse($[\mat{S}]$)
+%\label{alg:inverse}
+%\State $\mathcal{J}=getAbstractDynamics([\mat{J}])$
+%\label{alg:aa}
+%\State $[X_0']=$ transformInitialSpace($X_0,\mat{S}$)
+%\label{alg:eigeninit}
+%\State $[V_0]=$ getVertices($[X_0']$)
+%\label{alg:getVertices}
+%\State ${\hat{X}'^\sharp}=$ getReachTube($\mathcal{J},[V_0]$)
+%\label{alg:getReachTube}
+%\State ${\hat{X}^\sharp}=$ transformReachTube(${\hat{X}'^\sharp},[\mat{S}]^{-1}$)
+%\label{alg:getNormReachTube}
+%\EndFunction
+%\end{algorithmic}
+%\caption{Calculation of Abstract Reach Tube Using Abstract Acceleration}
+%\label{alg:findReachTube}
+%\end{algorithm}
+
+%%-------------------------------
+%\subsection{Overapproximating continuous time dynamics using discrete models}
+%\label{sec:cont_aa}
+%%-------------------------------
+%
+%Thus far we wave discussed the Abstract Accelertion of Discrete Time
+%systems.  However, our plant models derive from the discretization of
+%continuous time systems.  We therefore seek to establish a sound
+%overapproximation which does not only encompass the selected discretization,
+%but any chosen discretization in the time domain.
+%
+%A dynamical system is a system in which a function describes the progression
+%of a state over time.  In a continuous domain with linear dynamics, it is
+%described by a first order Ordinary Differential Equation (ODE).
+%%
+%\begin{equation}
+%\dot{x}(t)=\mat{A}_o\vec{x}(t)+\mat{B}_o\vec{u}(t)
+%\label{eq:dynamical}
+%\end{equation}
+%%
+%Furthermore, a control system may have a derived
+%output that is a linear combination of its states and inputs, which may
+%restricts the observability of the statespace from the output space.
+%%
+%\begin{equation}
+%\vec{y}(t)=\mat{C}_o\vec{x}(t)+\mat{D}_o\vec{u}(t)
+%\end{equation}
+%%
+%Discretization of a continuous dynamical system turns the ODE into a
+%difference equation, assuming zero-order hold for the input $\vec{u}$, to
+%%
+%\begin{align}
+%\label{eq:discretization}
+%\vec{x}_{k+1} &= \mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
+%y_k &= \mat{C}_d \vec{x}_ k + \mat{D}_d \vec{u}_ k 
+%\end{align}
+%where
+%\begin{align}
+%\label{eq:discretize}
+%\mat{A}_d &= e^{\mat{A}_o T_s} = \mathcal{L}^{-1} { ( s \mat{I} - \mat{A}_o )^{-1} }_{t = T_s}\\
+%\mat{B}_d &= \int_{t = 0}^{T_s} e^{\mat{A}_o t} dt\ \mat{B}_o = \mat{A}_o^{-1} ( \mat{A}_d - \mat{I} ) \mat{B}_o\\
+%\mat{C}_d &= \mat{C}_o\\
+%\mat{D}_d &= \mat{D}_o \\
+%\end{align}
+%and $T_s$ is the sample time. Then
+%\begin{align*}
+%x(kT)=x_k \wedge y(kT) = y_k, \forall k
+%\end{align*}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsubsection{Acceleration of continuous-time models}
+\label{sec:continuous_time_accel}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
+the state of the plant at integer multiples of the sample time.  
+%\note{Unlike the CAV18 paper, these gain matrices have not been discussed yet. }
+However, in order to synthesize $\mat{K}$, 
+we must be able to ensure that given properties of the plant hold at any given point in time.  
+In order to do so, we accelerate the dynamics of the plant according to the model
+semantics in Sec.~\ref{sec:model} and compute the state
+$\vec{x}_T$ at a given time $T$,
+%
+% namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
+%
+namely the state $\vec{x}(t)$ of the model 
+%$\dot{\vec{x}}(t)=\mat{A}
+at time $t=T$.
+
+\textcolor{red}{[The following three subsections take too much space, plus the results are mostly known or easily derivable with simple algebra: we need to shorten and simplify it.
+Dario: can you give it a crack?]}
+
+%\note{ [add?] In this section we work with fully observed models, namely where $y = x$. } 
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsubsection{Accelerated\! dynamics\! for\! continuous-time\! models\! without\! inputs}\label{sec:cont_acc_no_inputs}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+% 
+Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a
+linear function of $\vec{x}_0$ as shown below.  We assume that the system
+has no inputs, so its dynamics are described by
+$\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.
+
+\begin{lemma}
+The solution to the differential equation $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, and $\mat{S}$ are the generalized eigenvectors of $\mat{A}$,
+evaluated at time $T$ is
+%
+\begin{align}
+ \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x} (0)\\
+ \mat{A}_{T}&= \mat{S}
+ \left [ \begin{array}{cccc}
+ e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(2)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
+0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
+\vdots & & \ddots & \vdots \\
+0 & \cdots & 0  &e^{T\lambda_i} \\
+\end{array} \right ]
+ \mat{S}^{-1}
+ \label{eq:continuous_tube_dyn2}\\
+ &\text{where } s_i=\left\{\begin{array}{cc}1&\quad gm(\lambda_i)>1\\0&\quad gm(\lambda_i)=1\end{array}\right.,\nonumber
+\end{align}
+%
+$\lambda_i$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.
+%
+%$\vec{x}_T$ is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T. 
+If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0 \text{ with } T \in \mathbb{R}^+_0$ is the state of the system at time $t=T$.
+\end{lemma}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsubsection{Accelerated dynamics for models with parametric inputs}\label{sec:real_discrete_param_inputs}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+Next, we are interested in studying models with parametric inputs, which are
+described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where
+$\forall t\geq 0.\,\vec{u}(t)=\vec{u}$.  For such models, a state $\vec{x}_T$
+is computed next.
+%
+\begin{lemma}
+%
+The state of the model
+$\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a
+parametric input $\vec{u}$ is
+%
+\begin{align}
+\vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u}
+\label{eq:continuous_tube_param}
+\end{align}
+%
+where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$, $\forall t \leq T.\, \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in
+\eqref{eq:continuous_tube_dyn2} \footnote{When $\mat{A}$ is not invertible,
+we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\
+0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$.}. 
+If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that
+$A_d=e^{\mat{A} T_d}$, then
+$\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u})
+\text{ with } T \in \mathbb{R}_0^+$ (where $\mat{A}_d^{\frac{T}{T_d}} =
+e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the
+system at time $T$.
+%
+\end{lemma}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsubsection{Accelerated dynamics for models with a sampled-time feedback}\label{sec:real_discrete_feedback_inputs}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+The final case we analyze is that of hybrid-time models, where the plant
+dynamics evolve in continuous time while the feedback dynamics evolve in
+discrete time.  A~new input value is produced only at every sample time but
+implemented over the continuous-time plant dynamics.
+%
+%\note{Matrix K has not been introduced yet. }
+\begin{theorem}
+The expression
+%
+ \begin{align}
+ \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0, 
+ \label{eq:cyber_feedback}
+ \end{align}
+%
+with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, $\mat{B}_T$ as in
+\eqref{eq:continuous_tube_param}, and where $\mat{A}_d=\mat{A}_{T_s}$,
+$\mat{B}_d=\mat{B}_{T_s}$ describe the discretized plant dynamics with
+sample time $T_s$, is the state of the model
+%
+\begin{align*}
+ \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
+ \vec{u}(t)=\mat{K}\vec{x}_k,  \,
+ kT_s \leq t < (k+1)T_s \,. 
+\end{align*}
+%
+\end{theorem}
+\begin{proof}
+%
+Let $\mat{K}$ be a feedback controller such that
+$\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$.  Let the output of the
+feedback system be a zero order holder such that
+$\vec{u}(t'+kT_s)=\vec{u}(kT_s), \text{ for } 0 \leq t' < T_s$.  The closed
+loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
+%
+\begin{align*}
+\vec{x}_{k,t'}=\mat{A}_{t'}\vec{x}_k-\mat{B}_{t'}\mat{K}\vec{x}_k = (\mat{A}_{t'}-\mat{B}_{t'}\mat{K})\vec{x}_k,
+\end{align*}
+where $0 \leq t' < T_s$
+We further explore the dynamics across discrete time boundaries. Let $\mat{A}_d=\mat{A}_{T_s}$ and $\mat{B}_d=\mat{B}_{T_s}$
+\begin{align*}
+\vec{x}_{k}&=\vec{x}_{k-1,T_s}= (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}\\
+\vec{x}_{k,T_s} &= (\mat{A}_d-\mat{B}_d\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}
+\end{align*}
+which accelerating results and setting $T=kT_s+t'$ becomes
+\begin{align}
+\label{eq:feedback_sampled_cont}
+\vec{x}_{k} &= (\mat{A}_d-\mat{B}_d\mat{K}) ^k\vec{x}_0\\
+\vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
+\label{eq:feedback_cont}
+\end{align}
+\end{proof}
+
+%-------------------------------
+ \subsubsection{Finding Abstract Supports for Continuous Dynamics}
+ \label{sec:cont_aasup}
+%-------------------------------
+
+\textcolor{red}{[This paragraph is highly unclear - Dario: can you please update it?]}
+
+Now that we have defined the dynamics of continuous time, we can use abstract acceleration techniques to evaluate
+the above model such that
+\begin{equation}\label{eq:aa_cont_amatrix}
+\bigcup_{T \in [0, T_s], k \in N_0} (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k \subseteq \mathcal{A}.
+\end{equation}
+
+Abstract acceleration works by finding support functions of the set that encompasses the matrices $\mat{A}^k$.
+Support functions are scalars that measure the distance of a hyperplane tangent to the set boundary to the origin.
+In the case of continuous spaces, this translates to calculating the derivatives of the envelope in order to find the direction of the support vector (normal to the hyperplane), and calculating the distance to the corresponding point where the hyperplane touches the set (at which the derivative was calculated).
+The direction of the vector is determined by evaluating the support function of another point in the curve,
+which is known to be smaller than that of the selected point, and the chosen hyperplanes are aligned with the eigenvectors, hence we only look at eigenvalue pairs to calculate the derivatives~\cite{cattaruzza2015unbounded}.
+The corresponding derivatives are:
+%
+\begin{enumerate}
+%
+\item for real eigenvalues: we first calculate the slope of the tangent
+between the two progressions: $\frac{d f(k)}{d g(k)}=\frac{f'(k)}{g'(k)}$. 
+Hence $\frac{d \lambda_1^k}{d \lambda_2^k}=\frac{log(\lambda_1)
+\lambda_1^k}{log(\lambda_2) \lambda_2^k}$.  From this we know that the polar
+angle of the support vector is $\psi = \tan^{-1}(\frac{log(\lambda_1)
+\lambda_1^k}{log(\lambda_2) \lambda_2^k})+\frac{\pi}{2}$
+%
+\item for conjugate eigenvalue pairs: the pair forms a logarithmic spiral. 
+The tangent of a spiral with polar equation $r=a e^{b\theta}$ will have a
+derivative $\frac{d r}{d \theta}=b a e^{b\theta}=b r$, hence the angle of
+the vector normal to the curve is $\tan^{-1}(\frac{r}{\frac{d r}{d
+\theta}})+\frac{\pi}{2}=\tan^{-1}(\frac{1}{b})+\frac{\pi}{2}$
+%
+\item for Jordan blocks with $gm>1$: in the case of real eigenvalues, we
+follow the same procedure as in the real case, but considering that the
+equation for each eigenvalue is $\frac{k^j}{j!}e^{\lambda k}$ where $j$ is
+the index of the term within the Jordan block (note that when $j=0$ the term
+is the same as for real eigenvalues above).  The derivatives f'(k),g'(k) are
+in the form $(j+k*log(\lambda))\frac{k^{j-1}}{j!}e^{\lambda k}$.
+%
+\item for any combination of complex eigenvalues we use the above equations
+using the envelope of their magnitude (ie $|\lambda|$).
+%
+\end{enumerate}
+
+%%-------------------------------
+%\subsection{State-space representation of physical systems} 
+%\label{ssec:ssrepresentation}
+%%-------------------------------
+%
+%We consider models of physical plants expressed as ordinary differential
+%equations (ODEs), which we assume to be controllable and under full state
+%information (i.e., we have access to all the model variables):
+%%
+%\begin{align}
+%\label{eq:ode}
+%\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, \\ \nonumber A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}, 
+%\end{align}
+%%
+%where $t \in \mathbb R_0^+$, where $A$ and $B$ are matrices that fully
+%specify the continuous plant, and with initial states set as $x(0)$.  While
+%ideally we intend to work on the continuous-time plant, in this work
+%Eq.~\eqref{eq:ode} is soundly discretized in time~\cite{fadali} into
+%%
+%\begin{align}
+%\label{eq:plant}
+%x_{k+1} = A_d x_k+ B_d u_k
+%\end{align} 
+%%
+%where $k \in \mathbb N$ and $x_{0}=x(0)$ is the initial state. 
+%$A_d$ and $B_d$ denote the matrices that describe the discretized plant dynamics, whereas
+%$A$ and $B$ denote the continuous plant dynamics.  
+%We synthesize for requirements over this discrete-time domain. 
+%Later, we will address the issue of variable quantization, 
+%as introduced by the ADC/DAC conversion blocks 
+%(\textcolor{red}{we should include a figure that describes the control system model that we tackle}).
+%
+%
+%
+%%-------------------------------
+%\subsection{Controller synthesis via state feedback}
+%\label{ssec:statefeedbackcontrol}
+%%-------------------------------
+%
+%Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t)$ and  $u_k$, respectively. 
+%Feedback architectures can be employed to manipulate the properties and behaviors of the continuous process (the plant).   
+%We are interested in the synthesis of digital feedback control algorithms, 
+%as implemented on Field-Programmable Gate Arrays or Digital Signal Processors. 
+%The most basic feedback architecture is the state feedback one, 
+%where the control action $u_k$ (notice we work with the discretized signal) is computed by: 
+%%
+%\begin{equation}
+%\label{eq:controlaction}
+%u_k = r_{k} - K x_k. 
+%\end{equation}
+%%
+%Here, $K \in \mathbb{R}^{m \times n}$ is a state-feedback gain matrix, 
+%and $r_{k}$ is a reference signal (again digital).   
+%%
+%The closed-loop model then takes the form 
+%\begin{align}
+%\label{eq:closedloopss}
+%x_{k+1} = ( A_d - B_d K ) x_k + B_d r_k.
+%\end{align}
+%%
+%The gain matrix $K$ can be set so that the closed-loop discrete dynamics are
+%shaped as desired, for instance according to a specific stability goal or
+%around a specific dynamical behavior \cite{astrom1997computer}.  As argued
+%later in this work, we will target more complex objectives, such as
+%quantitative safety requirements, which are not typical in the digital
+%control literature.  Further, we will embrace the digital nature of the
+%controller, which manipulates quantized signals as discrete quantities represented with finite precision. 
+%
+%%-------------------------------
+%\subsection{Stability of closed-loop systems}
+%\label{ssec:stability}
+%%-------------------------------
+%
+%In this work we employ asymptotic stability in the CEGIS loop,  
+%as an objective for guessing controllers that are later proven sound over safety requirements.  
+%Asymptotic stability is a property that amounts to convergence of the model executions to an equilibrium point, 
+%starting from any states in a neighborhood of the point (see Figure~\ref{fig:ct} for the portrait of a stable execution, converging to the origin).  
+%In the case of linear systems as in~\eqref{eq:closedloopss}, 
+%considered with a zero reference signal, 
+%the equilibrium point of interest is the origin. 
+%
+%A discrete-time LTI system as \eqref{eq:closedloopss} is asymptotically
+%stable if all the roots of its characteristic polynomial (i.e., the
+%eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
+%circle of the complex plane, i.e., their absolute values are strictly less than
+%one~\cite{astrom1997computer} (this simple sufficient condition can be generalised, 
+%however this is not necessary in our work).  
+%In this paper, we express this stability specification $\phi_\mathit{stability}$ in terms of a check known as
+%\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic formula to
+%select the entries of matrix $K$ so that the closed-loop dynamics are shaped
+%as desired.
+%
+%%-------------------------------
+%\subsection{Safety specifications for dynamical systems}
+%\label{ssec:safety}
+%%-------------------------------
+%
+%We are not limited to the synthesis of digital stabilizing controllers -- a
+%well known task in the literature on digital control systems -- but target
+%safety requirements with an overall approach that is sound and automated. 
+%More specifically, we require that the closed-loop system
+%\eqref{eq:closedloopss} meets given safety specifications.  A safety
+%specification gives raise to a requirement on the states of the model, such
+%that the feedback controller (namely the choice of the gains matrix~$K$)
+%must ensure that the state never violates the requirement.  Note that a
+%stable, closed-loop system is not necessarily a safe system: indeed, the
+%state values may leave the safe part of the state space while they converge
+%to the equilibrium, which is typical in the case of oscillatory dynamics. 
+%In~this work, the safety property is expressed as:
+%%
+%\begin{equation}
+%\label{eq:safetyliteral}
+%\phi_\mathit{safety}\iff \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
+%\end{equation}
+%where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
+%for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
+%instant, respectively.  This means that the states will always be within an $n$-dimensional hyper-box.
+%
+%Furthermore, it is practically relevant to consider the 
+%constraints $\phi_\mathit{input}$ on the input
+%signal $u_{k}$ and $\phi_\mathit{init}$ on the initial states $x_0$,
+%which we assume have given bounds:
+%$\phi_\mathit{input} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
+%$\phi_\mathit{init} = \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$
+%For the former, this means that the control input might saturates in view of
+%physical constraints.
+%
+%%-------------------------------
+%\subsection{Performance specifications for dynamical systems}
+%\label{ssec:performance}
+%%-------------------------------
+%
+%\textcolor{red}{we should describe here about the performance specifications for dynamical systems.}
+
+%-------------------------------
 \section{CEGIS of digital controllers} 
@@
 %-------------------------------
+
+\textcolor{red}{[Elizabeth: please rewrite this]}
 
@@
 
+\textcolor{red}{[Dario: once Elizabeth has updated the description of the naive approach, can you update the following part, aligning it with hers?]}
+
 %  The na\"ive approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
@@
 %
-\textcolor{red}{[these specifications are (wrongly) introduced only in a later part of the manuscript!]}
 $$(\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-K x_k)
@@
 \end{figure*}
-
-%-------------------------------
-\section{Abstract Acceleration of Linear Dynamics} 
-\label{ssec:aa}
-%-------------------------------
-
-We recall a recently introduced technique called \emph{Abstract Acceleration}~\cite{JSS14,cattaruzza2015unbounded}, 
-which will be key in this work for abstraction-based synthesis.  
-%\note{This clashes with the model introduced above, with inputs - motivate why? I've added the motivation above by introducing the closed  loop}
-Given a model of an iterative program with dynamics
-%
-\begin{equation}
-\vec{x}_{k+1}=\mat{A}\vec{x}_k \text{ where } \vec{x}_k \in \mathbb{R}^p, \mat{A} \in \mathbb{R}^{p \times p} \text{ and } k \in \mathbb N_0,
-\end{equation}
-%
-\textcolor{red}{[we should use the notations (with the `d' subscript) in the Preliminaries section.]}
-we want to find all possible states visited over an infinite time horizon
-starting at an initial set $X_0$.  
-This set is known as the \emph{reach tube} of
-the model:
-%
-\begin{equation}
-\hat{X} = \{ \vec{x}_k \mid k \in \mathbb N_0, \vec{x}_0 \in X_0 \text{ and } \vec{x}_{k+1}=\mat{A}\vec{x}_k\}.
-\end{equation}
-%
-Using Abstract Acceleration we
-transform this problem into a one-step solution.  We first change the
-problem statement by means of acceleration into
-%
-\begin{equation}
-\hat{X} = \{ \vec{x}_k=\mat{A}^k\vec{x}_0 \mid k \in N_0 \text{ and } \vec{x}_0 \in X_0 \}, 
-\end{equation}
-%
-and further define new model semantics and corresponding set: 
-%
-\begin{equation}\label{eq:aa_reachtube}
-\hat{X} \subseteq \hat{X}^\sharp = \mathcal{A}X_0, \text{ such that } \bigcup_{k \in [0\ \infty)} \mat{A}^k \subseteq \mathcal{A}, 
-\end{equation}
-%
-where the newly introduced \emph{abstract reach tube} $\hat{X}^\sharp$ is an
-over-approximation of the reach tube of the model \cite{JSS14}.  
-In this work we use an extension of the abstract acceleration model for
-continuous time. 
-% and  For this reason we must first look at the acceleration of continuous-time dynamics.
-
-%All we need to do is define the nature of $\mathcal{A}X_0$.
-%Let $\mat{S}\mat{J}\mat{S}^{-1}=\mat{A}$ be the eigen-decomposition of
-%$\mat{A}$, where $\mat{S}$ is the set of generalised eigenvectors of
-%$\mat{A}$ and $\mat{J}$ is the Jordan Form containing the eigenvalues of
-%$\mat{A}$ in its main diagonal.  We correspondingly define
-%$\mathcal{J}=\mat{S}^{-1}\mathcal{A}\mat{S}$, which is such that
-%$\mathcal{J} \supseteq \bigcup_{k \in [0\ \infty)} \mat{J}^k$.
-%
-%Since abstract acceleration operates in the eigenspace, wemust deal with some preliminary transformations.
-%Given a set $X=\{ \vec{x} \mid \mat{C}\vec{x} \leq \vec{d}\}$,
-%the linear transformation $\vec{x}'=\mat{S}^{-1}\vec{x}$ leads to the set 
-%%
-%\begin{equation}
-%X'= \mat{S}^{-1}X = \{\vec{x}' \mid \mat{C}\mat{S}\vec{x}'\leq \vec{d}\}.  
-%\label{eq:eigenInit}
-%\end{equation}
-%%
-%Analogously, let $X_0'=\mat{S}^{-1}X_0$ and
-%${\hat{X}'^\sharp}=\mat{S}^{-1}{\hat{X}^\sharp}$ be the initial set and the
-%abstract reach tube mapped onto the eigenspace of matrix $\mat{A}$.  We may
-%transform equation \eqref{eq:aa_reachtube} into: 
-%%
-%\begin{equation}
-%\hat{X}' \subseteq {\hat{X}'^\sharp} = \mathcal{J}X_0', 
-%\end{equation}
-%%
-%where $\hat{X}'=\mat{S}^{-1}\hat{X}$ and $\mathcal{J}$ is a convex
-%polyhedron representing restrictions on the eigenvalues of $\mat{A}$. 
-%$\hat{X}'^\sharp$ is calculated by applying a simplex algorithm with a
-%tableau defined by $\mathcal{J}$ and objective functions derived from each
-%vertex of $X_0'$ (step \eqref{alg:getReachTube} in Algorithm
-%\ref{alg:findReachTube} below).  We note, however, that if we wish to use
-%numerical analysis in the decomposition of $\mat{A}$, the Tableau in
-%$\mathcal{J}$ contains small intervals given by the errors, which cannot be
-%processed efficiently by a regular simplex and require a new procedure.
-%
-%The calculation of the abstract reach tube via abstract acceleration is
-%encompassed in Algorithm~\ref{alg:findReachTube}, which can be summarised as
-%follows (its steps are denoted in parentheses):
-%%
-%\begin{enumerate}
-%%
-%\item We perform unsound eigen-decomposition using an existing algebra package (lines \ref{alg:calcEigenvalues}-\ref{alg:calcEigenvectors}).
-%%
-%\item Then we restore soundness to the results using the methods described in \cite{cattaruzza2017sound} (lines \ref{alg:soundEigenvalues}-\ref{alg:soundEigenvectors}).
-%%
-%\item The inverse of the matrix of eigenvectors is calculated after soundness is restored, using interval arithmetic in order to ensure its soundness (line \ref{alg:inverse}).
-%%
-%\item The abstract dynamics are obtained by evaluating the convex hull of all powers of eigenvalues up to the desired number of iterations as described in \cite{cattaruzza2015unbounded} (line \ref{alg:aa}).
-%%
-%\item Using Equation \eqref{eq:eigenInit}, transform the initial state into the eigenspace (line \ref{alg:eigeninit}).
-%%
-%\item Extract the vertices of the eigen-polyhedron $X_0'$ using the algorithms described in \cite{cattaruzza2015unbounded,cattaruzza2017sound} (line \ref{alg:getVertices}). 
-%%
-%\item Calculate the mapped \emph{abstract reach tube} ${\hat{X}'^\sharp}$
-%that over-approximates the image of the reach tube in the eigenspace (line
-%\ref{alg:getReachTube}).  This is achieved by evaluating a set of objective
-%functions using the abstract dynamics as a simplex Tableau, and via a sound
-%simplex described in \cite{cattaruzza2017sound}.  The objective functions are
-%defined by the vertices of $X'_0$, denote as $V_0$, and by the desired
-%template directions, such that
-%%
-%\begin{equation*}
-%\vec{w}_{ij}= \vec{v}_i \circ \vec{t}_j \text{ with } \vec{v}_i \in V_0 \text{ and } \vec{t}_j \in T,
-%\end{equation*}
-%%
-%where $T$ is the set of template directions, and $\circ$ denotes a
-%component-wise multiplication yielding a vector.
-%%
-%\item Using Equation~\eqref{eq:eigenInit}, find the reach tube
-%$\hat{X}^\sharp=\mat{S}{\hat{X}'^\sharp}$ (line \ref{alg:getNormReachTube}).
-%%
-%\end{enumerate}
-%
-%\begin{algorithm}[]
-%\small
-%\begin{algorithmic}[1]
-%\Function{$\mathit{findAbstractReachTube}()$}{}
-%\State $\hat{\mat{J}}=$ calculateEigenvalues($ \mat{A}$)
-%\label{alg:calcEigenvalues}
-%\State $\hat{\mat{S}}=$ calculateEigenvectors($ \mat{A}$)
-%\label{alg:calcEigenvectors}
-%\State $[\mat{J}]=$ soundifyEigenvalues($\mat{A},\mat{J},\mat{S}$)
-%\label{alg:soundEigenvalues}
-%\State $[\mat{S}]=$ soundifyEigenvectors($\mat{A},[\mat{J}],\mat{S}$)
-%\label{alg:soundEigenvectors}
-%\State $[\mat{S}]^{-1}=$ calculateInverse($[\mat{S}]$)
-%\label{alg:inverse}
-%\State $\mathcal{J}=getAbstractDynamics([\mat{J}])$
-%\label{alg:aa}
-%\State $[X_0']=$ transformInitialSpace($X_0,\mat{S}$)
-%\label{alg:eigeninit}
-%\State $[V_0]=$ getVertices($[X_0']$)
-%\label{alg:getVertices}
-%\State ${\hat{X}'^\sharp}=$ getReachTube($\mathcal{J},[V_0]$)
-%\label{alg:getReachTube}
-%\State ${\hat{X}^\sharp}=$ transformReachTube(${\hat{X}'^\sharp},[\mat{S}]^{-1}$)
-%\label{alg:getNormReachTube}
-%\EndFunction
-%\end{algorithmic}
-%\caption{Calculation of Abstract Reach Tube Using Abstract Acceleration}
-%\label{alg:findReachTube}
-%\end{algorithm}
-
-%%-------------------------------
-%\subsection{Overapproximating continuous time dynamics using discrete models}
-%\label{sec:cont_aa}
-%%-------------------------------
-%
-%Thus far we wave discussed the Abstract Accelertion of Discrete Time
-%systems.  However, our plant models derive from the discretization of
-%continuous time systems.  We therefore seek to establish a sound
-%overapproximation which does not only encompass the selected discretization,
-%but any chosen discretization in the time domain.
-%
-%A dynamical system is a system in which a function describes the progression
-%of a state over time.  In a continuous domain with linear dynamics, it is
-%described by a first order Ordinary Differential Equation (ODE).
-%%
-%\begin{equation}
-%\dot{x}(t)=\mat{A}_o\vec{x}(t)+\mat{B}_o\vec{u}(t)
-%\label{eq:dynamical}
-%\end{equation}
-%%
-%Furthermore, a control system may have a derived
-%output that is a linear combination of its states and inputs, which may
-%restricts the observability of the statespace from the output space.
-%%
-%\begin{equation}
-%\vec{y}(t)=\mat{C}_o\vec{x}(t)+\mat{D}_o\vec{u}(t)
-%\end{equation}
-%%
-%Discretization of a continuous dynamical system turns the ODE into a
-%difference equation, assuming zero-order hold for the input $\vec{u}$, to
-%%
-%\begin{align}
-%\label{eq:discretization}
-%\vec{x}_{k+1} &= \mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
-%y_k &= \mat{C}_d \vec{x}_ k + \mat{D}_d \vec{u}_ k 
-%\end{align}
-%where
-%\begin{align}
-%\label{eq:discretize}
-%\mat{A}_d &= e^{\mat{A}_o T_s} = \mathcal{L}^{-1} { ( s \mat{I} - \mat{A}_o )^{-1} }_{t = T_s}\\
-%\mat{B}_d &= \int_{t = 0}^{T_s} e^{\mat{A}_o t} dt\ \mat{B}_o = \mat{A}_o^{-1} ( \mat{A}_d - \mat{I} ) \mat{B}_o\\
-%\mat{C}_d &= \mat{C}_o\\
-%\mat{D}_d &= \mat{D}_o \\
-%\end{align}
-%and $T_s$ is the sample time. Then
-%\begin{align*}
-%x(kT)=x_k \wedge y(kT) = y_k, \forall k
-%\end{align*}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Acceleration of continuous-time models}\label{sec:continuous_time_accel}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
-the state of the plant at integer multiples of the sample time.  
-%\note{Unlike the CAV18 paper, these gain matrices have not been discussed yet. }
-However, in
-order to synthesize $\mat{K}$, we must be able to ensure that
-certain properties \textcolor{red}{[unknown because undefined at this point \ldots]} of the plant hold at any given point in time.  In order
-to do so, we accelerate the dynamics of the plant according to the model
-semantics in Sec.~\ref{sec:model} and compute the state
-$\vec{x}_T$ at a given time $T$,
-%
-% namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
-%
-namely the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time
-$t=T$.
-
-%\note{ [add?] In this section we work with fully observed models, namely where $y = x$. } 
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Accelerated\! dynamics\! for\! continuous-time\! models\! without\! inputs}\label{sec:cont_acc_no_inputs}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%
-Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a
-linear function of $\vec{x}_0$ as shown below.  We assume that the system
-has no inputs, so its dynamics are described by
-$\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.
-
-\begin{lemma}
-The solution to the differential equation $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, and $\mat{S}$ are the generalized eigenvectors of $\mat{A}$,
-evaluated at time $T$ is
-%
-\begin{align}
- \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x} (0)\\
- \mat{A}_{T}&= \mat{S}
- \left [ \begin{array}{cccc}
- e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(2)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
-0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
-\vdots & & \ddots & \vdots \\
-0 & \cdots & 0  &e^{T\lambda_i} \\
-\end{array} \right ]
- \mat{S}^{-1}
- \label{eq:continuous_tube_dyn2}\\
- &\text{where } s_i=\left\{\begin{array}{cc}1&\quad gm(\lambda_i)>1\\0&\quad gm(\lambda_i)=1\end{array}\right.,\nonumber
-\end{align}
-%
-$\lambda_i$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.
-%
-%$\vec{x}_T$ is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T. 
-If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0 \text{ with } T \in \mathbb{R}^+_0$ is the state of the system at time $t=T$.
-\end{lemma}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Accelerated dynamics for models with parametric inputs}\label{sec:real_discrete_param_inputs}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Next, we are interested in studying models with parametric inputs, which are
-described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where
-$\forall t\geq 0.\,\vec{u}(t)=\vec{u}$.  For such models, a state $\vec{x}_T$
-is computed next.
-%
-\begin{lemma}
-%
-The state of the model
-$\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a
-parametric input $\vec{u}$ is
-%
-\begin{align}
-\vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u}
-\label{eq:continuous_tube_param}
-\end{align}
-%
-where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$, $\forall t \leq T.\, \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in
-\eqref{eq:continuous_tube_dyn2} \footnote{When $\mat{A}$ is not invertible,
-we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\
-0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$.}. 
-If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that
-$A_d=e^{\mat{A} T_d}$, then
-$\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u})
-\text{ with } T \in \mathbb{R}_0^+$ (where $\mat{A}_d^{\frac{T}{T_d}} =
-e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the
-system at time $T$.
-%
-\end{lemma}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Accelerated dynamics for models with a sampled-time feedback}\label{sec:real_discrete_feedback_inputs}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-The final case we analyze is that of hybrid-time models, where the plant
-dynamics evolve in continuous time while the feedback dynamics evolve in
-discrete time.  A~new input value is produced only at every sample time but
-implemented over the continuous-time plant dynamics.
-%
-%\note{Matrix K has not been introduced yet. }
-\begin{theorem}
-The expression
-%
- \begin{align}
- \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0, 
- \label{eq:cyber_feedback}
- \end{align}
-%
-with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, $\mat{B}_T$ as in
-\eqref{eq:continuous_tube_param}, and where $\mat{A}_d=\mat{A}_{T_s}$,
-$\mat{B}_d=\mat{B}_{T_s}$ describe the discretized plant dynamics with
-sample time $T_s$, is the state of the model
-%
-\begin{align*}
- \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
- \vec{u}(t)=\mat{K}\vec{x}_k,  \,
- kT_s \leq t < (k+1)T_s \,. 
-\end{align*}
-%
-\end{theorem}
-\begin{proof}
-%
-Let $\mat{K}$ be a feedback controller such that
-$\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$.  Let the output of the
-feedback system be a zero order holder such that
-$\vec{u}(t'+kT_s)=\vec{u}(kT_s), \text{ for } 0 \leq t' < T_s$.  The closed
-loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
-%
-\begin{align*}
-\vec{x}_{k,t'}=\mat{A}_{t'}\vec{x}_k-\mat{B}_{t'}\mat{K}\vec{x}_k = (\mat{A}_{t'}-\mat{B}_{t'}\mat{K})\vec{x}_k,
-\end{align*}
-where $0 \leq t' < T_s$
-We further explore the dynamics across discrete time boundaries. Let $\mat{A}_d=\mat{A}_{T_s}$ and $\mat{B}_d=\mat{B}_{T_s}$
-\begin{align*}
-\vec{x}_{k}&=\vec{x}_{k-1,T_s}= (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}\\
-\vec{x}_{k,T_s} &= (\mat{A}_d-\mat{B}_d\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}
-\end{align*}
-which accelerating results and setting $T=kT_s+t'$ becomes
-\begin{align}
-\label{eq:feedback_sampled_cont}
-\vec{x}_{k} &= (\mat{A}_d-\mat{B}_d\mat{K}) ^k\vec{x}_0\\
-\vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
-\label{eq:feedback_cont}
-\end{align}
-\end{proof}
-
-%-------------------------------
- \subsection{Finding Abstract Supports for Continuous Dynamics}
- \label{sec:cont_aasup}
-%-------------------------------
-
-Now that we have defined the dynamics of continuous time, we can use abstract acceleration techniques to evaluate
-the above model such that
-\begin{equation}\label{eq:aa_cont_amatrix}
-\bigcup_{T \in [0, T_s], k \in N_0} (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k \subseteq \mathcal{A}.
-\end{equation}
-
-Abstract acceleration works by finding support functions of the set that encompasses the matrices $\mat{A}^k$.
-Support functions are scalars that measure the distance of a hyperplane tangent to the set boundary to the origin.
-In the case of continuous spaces, this translates to calculating the derivatives of the envelope in order to find the direction of the support vector (normal to the hyperplane), and calculating the distance to the corresponding point where the hyperplane touches the set (at which the derivative was calculated).
-The direction of the vector is determined by evaluating the support function of another point in the curve,
-which is known to be smaller than that of the selected point, and the chosen hyperplanes are aligned with the eigenvectors, hence we only look at eigenvalue pairs to calculate the derivatives~\cite{cattaruzza2015unbounded}.
-The corresponding derivatives are:
-%
-\begin{enumerate}
-%
-\item for real eigenvalues: we first calculate the slope of the tangent
-between the two progressions: $\frac{d f(k)}{d g(k)}=\frac{f'(k)}{g'(k)}$. 
-Hence $\frac{d \lambda_1^k}{d \lambda_2^k}=\frac{log(\lambda_1)
-\lambda_1^k}{log(\lambda_2) \lambda_2^k}$.  From this we know that the polar
-angle of the support vector is $\psi = \tan^{-1}(\frac{log(\lambda_1)
-\lambda_1^k}{log(\lambda_2) \lambda_2^k})+\frac{\pi}{2}$
-%
-\item for conjugate eigenvalue pairs: the pair forms a logarithmic spiral. 
-The tangent of a spiral with polar equation $r=a e^{b\theta}$ will have a
-derivative $\frac{d r}{d \theta}=b a e^{b\theta}=b r$, hence the angle of
-the vector normal to the curve is $\tan^{-1}(\frac{r}{\frac{d r}{d
-\theta}})+\frac{\pi}{2}=\tan^{-1}(\frac{1}{b})+\frac{\pi}{2}$
-%
-\item for Jordan blocks with $gm>1$: in the case of real eigenvalues, we
-follow the same procedure as in the real case, but considering that the
-equation for each eigenvalue is $\frac{k^j}{j!}e^{\lambda k}$ where $j$ is
-the index of the term within the Jordan block (note that when $j=0$ the term
-is the same as for real eigenvalues above).  The derivatives f'(k),g'(k) are
-in the form $(j+k*log(\lambda))\frac{k^{j-1}}{j!}e^{\lambda k}$.
-%
-\item for any combination of complex eigenvalues we use the above equations
-using the envelope of their magnitude (ie $|\lambda|$).
-%
-\end{enumerate}
-
-%%-------------------------------
-%\subsection{State-space representation of physical systems} 
-%\label{ssec:ssrepresentation}
-%%-------------------------------
-%
-%We consider models of physical plants expressed as ordinary differential
-%equations (ODEs), which we assume to be controllable and under full state
-%information (i.e., we have access to all the model variables):
-%%
-%\begin{align}
-%\label{eq:ode}
-%\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, \\ \nonumber A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}, 
-%\end{align}
-%%
-%where $t \in \mathbb R_0^+$, where $A$ and $B$ are matrices that fully
-%specify the continuous plant, and with initial states set as $x(0)$.  While
-%ideally we intend to work on the continuous-time plant, in this work
-%Eq.~\eqref{eq:ode} is soundly discretized in time~\cite{fadali} into
-%%
-%\begin{align}
-%\label{eq:plant}
-%x_{k+1} = A_d x_k+ B_d u_k
-%\end{align} 
-%%
-%where $k \in \mathbb N$ and $x_{0}=x(0)$ is the initial state. 
-%$A_d$ and $B_d$ denote the matrices that describe the discretized plant dynamics, whereas
-%$A$ and $B$ denote the continuous plant dynamics.  
-%We synthesize for requirements over this discrete-time domain. 
-%Later, we will address the issue of variable quantization, 
-%as introduced by the ADC/DAC conversion blocks 
-%(\textcolor{red}{we should include a figure that describes the control system model that we tackle}).
-%
-%
-%
-%%-------------------------------
-%\subsection{Controller synthesis via state feedback}
-%\label{ssec:statefeedbackcontrol}
-%%-------------------------------
-%
-%Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t)$ and  $u_k$, respectively. 
-%Feedback architectures can be employed to manipulate the properties and behaviors of the continuous process (the plant).   
-%We are interested in the synthesis of digital feedback control algorithms, 
-%as implemented on Field-Programmable Gate Arrays or Digital Signal Processors. 
-%The most basic feedback architecture is the state feedback one, 
-%where the control action $u_k$ (notice we work with the discretized signal) is computed by: 
-%%
-%\begin{equation}
-%\label{eq:controlaction}
-%u_k = r_{k} - K x_k. 
-%\end{equation}
-%%
-%Here, $K \in \mathbb{R}^{m \times n}$ is a state-feedback gain matrix, 
-%and $r_{k}$ is a reference signal (again digital).   
-%%
-%The closed-loop model then takes the form 
-%\begin{align}
-%\label{eq:closedloopss}
-%x_{k+1} = ( A_d - B_d K ) x_k + B_d r_k.
-%\end{align}
-%%
-%The gain matrix $K$ can be set so that the closed-loop discrete dynamics are
-%shaped as desired, for instance according to a specific stability goal or
-%around a specific dynamical behavior \cite{astrom1997computer}.  As argued
-%later in this work, we will target more complex objectives, such as
-%quantitative safety requirements, which are not typical in the digital
-%control literature.  Further, we will embrace the digital nature of the
-%controller, which manipulates quantized signals as discrete quantities represented with finite precision. 
-%
-%%-------------------------------
-%\subsection{Stability of closed-loop systems}
-%\label{ssec:stability}
-%%-------------------------------
-%
-%In this work we employ asymptotic stability in the CEGIS loop,  
-%as an objective for guessing controllers that are later proven sound over safety requirements.  
-%Asymptotic stability is a property that amounts to convergence of the model executions to an equilibrium point, 
-%starting from any states in a neighborhood of the point (see Figure~\ref{fig:ct} for the portrait of a stable execution, converging to the origin).  
-%In the case of linear systems as in~\eqref{eq:closedloopss}, 
-%considered with a zero reference signal, 
-%the equilibrium point of interest is the origin. 
-%
-%A discrete-time LTI system as \eqref{eq:closedloopss} is asymptotically
-%stable if all the roots of its characteristic polynomial (i.e., the
-%eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
-%circle of the complex plane, i.e., their absolute values are strictly less than
-%one~\cite{astrom1997computer} (this simple sufficient condition can be generalised, 
-%however this is not necessary in our work).  
-%In this paper, we express this stability specification $\phi_\mathit{stability}$ in terms of a check known as
-%\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic formula to
-%select the entries of matrix $K$ so that the closed-loop dynamics are shaped
-%as desired.
-%
-%%-------------------------------
-%\subsection{Safety specifications for dynamical systems}
-%\label{ssec:safety}
-%%-------------------------------
-%
-%We are not limited to the synthesis of digital stabilizing controllers -- a
-%well known task in the literature on digital control systems -- but target
-%safety requirements with an overall approach that is sound and automated. 
-%More specifically, we require that the closed-loop system
-%\eqref{eq:closedloopss} meets given safety specifications.  A safety
-%specification gives raise to a requirement on the states of the model, such
-%that the feedback controller (namely the choice of the gains matrix~$K$)
-%must ensure that the state never violates the requirement.  Note that a
-%stable, closed-loop system is not necessarily a safe system: indeed, the
-%state values may leave the safe part of the state space while they converge
-%to the equilibrium, which is typical in the case of oscillatory dynamics. 
-%In~this work, the safety property is expressed as:
-%%
-%\begin{equation}
-%\label{eq:safetyliteral}
-%\phi_\mathit{safety}\iff \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
-%\end{equation}
-%where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
-%for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
-%instant, respectively.  This means that the states will always be within an $n$-dimensional hyper-box.
-%
-%Furthermore, it is practically relevant to consider the 
-%constraints $\phi_\mathit{input}$ on the input
-%signal $u_{k}$ and $\phi_\mathit{init}$ on the initial states $x_0$,
-%which we assume have given bounds:
-%$\phi_\mathit{input} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
-%$\phi_\mathit{init} = \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$
-%For the former, this means that the control input might saturates in view of
-%physical constraints.
-%
-%%-------------------------------
-%\subsection{Performance specifications for dynamical systems}
-%\label{ssec:performance}
-%%-------------------------------
-%
-%\textcolor{red}{we should describe here about the performance specifications for dynamical systems.}
 

### 2018-03-16 automatica/paper.tex
Addressing some of Alessandro's comments

@@
 \begin{equation}
-\hat{X} = \{ \vec{x}_k=\mat{A_d}^k\vec{x}_0 : k \in N_0 \text{ and } \vec{x}_0 \in X_0 \}, 
+\hat{X} = \{ \vec{x}_k=\mat{A_d}^k\vec{x}_0 \mid k \in N_0 \text{ and } \vec{x}_0 \in X_0 \}, 
 \end{equation}
@@
 Dario: can you give it a crack?]}
+\textcolor{blue}{[I merged the first two]}
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Accelerated\! dynamics\! for\! continuous-time\! models\! without\! inputs}\label{sec:cont_acc_no_inputs}
+\subsubsection{Accelerated\! dynamics\! for\! continuous-time\! models\! with\! parametric\! inputs}\label{sec:real_discrete_param_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a
-linear function of $\vec{x}_0$ as shown below.  We assume that the system
-has no inputs, so its dynamics are described by
-$\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.
+linear function of $\vec{x}_0$ and $\vec{u}$ as shown below.
 
 \begin{lemma}
-The solution to the differential equation $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, and $\mat{S}$ are the generalized eigenvectors of $\mat{A}$,
+The solution to the differential equation $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where
+$\forall t\geq 0.\,\vec{u}(t)=\vec{u}$, $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, and $\mat{S}$ are the generalized eigenvectors of $\mat{A}$,
 evaluated at time $T$ is
@@
 \begin{align}
- \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x} (0)\\
+\label{eq:continuous_tube_param}
+\vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u}\\
  \mat{A}_{T}&= \mat{S}
@@
  \label{eq:continuous_tube_dyn2}\\
+ \mat{B}_T&=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}
+ \footnote{When $\mat{A}$ is not invertible,
+we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\
+0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$.}\\
  &\text{where } s_i=\left\{\begin{array}{cc}1&\quad gm(\lambda_i)>1\\0&\quad gm(\lambda_i)=1\end{array}\right.,\nonumber
@@
 %
-%$\vec{x}_T$ is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T. 
-If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0 \text{ with } T \in \mathbb{R}^+_0$ is the state of the system at time $t=T$.
-\end{lemma}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Accelerated dynamics for models with parametric inputs}\label{sec:real_discrete_param_inputs}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Next, we are interested in studying models with parametric inputs, which are
-described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where
-$\forall t\geq 0.\,\vec{u}(t)=\vec{u}$.  For such models, a state $\vec{x}_T$
-is computed next.
-%
-\begin{lemma}
-%
-The state of the model
-$\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a
-parametric input $\vec{u}$ is
-%
-\begin{align}
-\vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u}
-\label{eq:continuous_tube_param}
-\end{align}
-%
-where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$, $\forall t \leq T.\, \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in
-\eqref{eq:continuous_tube_dyn2} \footnote{When $\mat{A}$ is not invertible,
-we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\
-0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$.}. 
-If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that
-$A_d=e^{\mat{A} T_d}$, then
-$\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u})
-\text{ with } T \in \mathbb{R}_0^+$ (where $\mat{A}_d^{\frac{T}{T_d}} =
-e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the
-system at time $T$.
-%
+
+If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then 
+$$\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}})\mat{B}_d\vec{u}
+\text{ with } T \in \mathbb{R}_0^+$$
+where $\mat{A}_d^{\frac{T}{T_d}} =e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$,
+is the state of the system at time $t=T$. 
 \end{lemma}
@@
 \textcolor{red}{[This paragraph is highly unclear - Dario: can you please update it?]}
-
-Now that we have defined the dynamics of continuous time, we can use abstract acceleration techniques to evaluate
-the above model such that
+\textcolor{blue}{[is  this better?]}
+
+Just as the accelerated dynamics in equation \eqref{eq:feedback_sampled_cont} can be abstacted using \eqref{eq:aa_reachtube} (where $\bigcup_{k \in N_0} (\mat{A}_d-\mat{B}_d\mat{K}) ^k \subseteq \mathcal{A}$),
+we use the same principle on equation \eqref{eq:feedback_cont} to obtain 
 \begin{equation}\label{eq:aa_cont_amatrix}
@@
 
-Abstract acceleration works by finding support functions of the set that encompasses the matrices $\mat{A}^k$.
+We describe now how to obtain such a set. Abstract acceleration works by finding support functions of the set that encompasses the matrices $\mat{A}^k$.
 Support functions are scalars that measure the distance of a hyperplane tangent to the set boundary to the origin.
@@
   further constrain the characteristic polynomial %\blue{[again, check the coefficients of the characteristic polynomial.]I don't find any error} 
-$z^n+\sum_{i=1}^n(a_i-k_i)z^{n-i}=\prod_{i=1}^n (z-\lambda_i) : |\lambda_i|<1 \wedge \lambda_i \models \phi_{\Lambda}$.
+$z^n+\sum_{i=1}^n(a_i-k_i)z^{n-i}=\prod_{i=1}^n (z-\lambda_i) \text{ where } |\lambda_i|<1 \wedge \lambda_i \models \phi_{\Lambda}$.
 These constraints correspond to specific iterations for which the system may be unsafe.

### 2018-03-16 automatica/paper.tex
title
section 3

@@
 
-\title{Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants}
+\title{Safe and Robust Formal Synthesis of Digital Controllers\\
+for Continuous Plants}
 % Title, preferably not more
@@
 %-------------------------------
-\section{Formal specification of control systems properties} 
+\section{Formal specification of model properties} 
 \label{sec:specification}
@@
 %-------------------------------
-\subsection{Abstract Acceleration of Linear Dynamics} 
+\subsection{Abstract acceleration of linear dynamics} 
 \label{ssec:aa}
@@
 %
-\textcolor{red}{[I have modified the notations with the `d' subscript as above.]}
 we want to find all possible states visited over an infinite time horizon
 starting at an initial set $X_0$.  
-This set is known as the \emph{reach tube} of
-the model:
+This set is known as the \emph{reach tube} of the model:
 %
@@
 Using Abstract Acceleration we transform this sequential reachability problem into a one-step problem. 
-We first modify the problem statement by means of acceleration into
+This has a lot of benefits ~\cite{JSS14}, not least in terms of numerical error propagation.   
+In order to attain this, 
+the problem statement is modified, by means of acceleration, into 
 %
@@
 %
-and further define new model semantics and corresponding set: 
+and new model semantics and corresponding set are further defined as 
 %
@@
 over-approximation of the reach tube of the model \cite{JSS14}.  
-In this work we extend the abstract acceleration algorithm to continuous-time models. 
+\cite{cattaruzza2015unbounded} extends this to LTI models with inputs, 
+whereas we next extend the algorithm to continuous-time models, in view of the overall goal of this work. 
 % and  For this reason we must first look at the acceleration of continuous-time dynamics.
@@
 we must be able to ensure that given properties of the plant hold at any given point in time.  
-In order to do so, we accelerate the dynamics of the plant according to the model
-semantics in Sec.~\ref{sec:model} and compute the state
-$\vec{x}_T$ at a given time $T$,
-%
-% namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
-%
-namely the state $\vec{x}(t)$ of the model 
-%$\dot{\vec{x}}(t)=\mat{A}
-at time $t=T$.
-
-\textcolor{red}{[The following three subsections take too much space, plus the results are mostly known or easily derivable with simple algebra: we need to shorten and simplify it.
+In order to do so, we accelerate the dynamics of the plant according to the continuous-time model
+semantics in Sec.~\ref{sec:model}. 
+% and compute the state $\vec{x}_T$ at a given time $T$,
+%%
+%% namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
+%%
+%namely the state $\vec{x}(t)$ of the model 
+%%$\dot{\vec{x}}(t)=\mat{A}
+%at time $t=T$.
+
+%\textcolor{red}{[The following three subsections take too much space, plus the results are mostly known or easily derivable with simple algebra: we need to shorten and simplify it.
 Dario: can you give it a crack?]}
-\textcolor{blue}{[I merged the first two]}
+%\textcolor{blue}{[I merged the first two]}
 
@@
 
-\textcolor{red}{[This paragraph is highly unclear - Dario: can you please update it?]}
-\textcolor{blue}{[is  this better?]}
-
 Just as the accelerated dynamics in equation \eqref{eq:feedback_sampled_cont} can be abstacted using \eqref{eq:aa_reachtube} (where $\bigcup_{k \in N_0} (\mat{A}_d-\mat{B}_d\mat{K}) ^k \subseteq \mathcal{A}$),
@@
 \end{equation}
+
+\textcolor{red}{[The next discussion is highly unclear - Dario: can you please update it?]}
 

### 2018-03-16 automatica/paper.tex
section 3
Further corrections

@@
 \textcolor{red}{[The next discussion is highly unclear - Dario: can you please update it?]}
-
-We describe now how to obtain such a set. Abstract acceleration works by finding support functions of the set that encompasses the matrices $\mat{A}^k$.
-Support functions are scalars that measure the distance of a hyperplane tangent to the set boundary to the origin.
-In the case of continuous spaces, this translates to calculating the derivatives of the envelope in order to find the direction of the support vector (normal to the hyperplane), and calculating the distance to the corresponding point where the hyperplane touches the set (at which the derivative was calculated).
-The direction of the vector is determined by evaluating the support function of another point in the curve,
-which is known to be smaller than that of the selected point, and the chosen hyperplanes are aligned with the eigenvectors, hence we only look at eigenvalue pairs to calculate the derivatives~\cite{cattaruzza2015unbounded}.
+\textcolor{blue}{[how about this?]}
+
+We next describe how to obtain such a set. 
+Our overapproximation of the set is a polyhedron, which is defined by an
+intersection of hypeplanes. The smallest polyhedra that can be obtained are
+those whose faces touch the set, which they must do at a point tangential to
+the hyperplane. Rather than pick a set of directions and find such points, we
+will start from the points and find their tangents. Furthermore, to simplify the
+procedure, we will only look at two dimensional cuts of the space 
+(see~\cite{cattaruzza2015unbounded}). This means that for every point we
+choose is a vertex of the polyhedron.
+Finding out which side of the hyperplane corresponds to the inside of the
+polyhedron is achieved by looking at any other point in the original set and
+checking on which side of the hyperplane it lays.
+
+%Abstract acceleration works by finding support functions of the set that encompasses the matrices $\mat{A}^k$.
+%Support functions are scalars that measure the distance of a hyperplane tangent to the set boundary to the origin.
+%In the case of continuous spaces, this translates to calculating the derivatives of the envelope in order to find the direction of the support vector (normal to the hyperplane), and calculating the distance to the corresponding point where the hyperplane touches the set (at which the derivative was calculated).
+%The direction of the vector is determined by evaluating the support function of another point in the curve,
+%which is known to be smaller than that of the selected point, and the chosen hyperplanes are aligned with the eigenvectors, hence we only look at eigenvalue pairs to calculate the derivatives~\cite{cattaruzza2015unbounded}.
+
+\textcolor{red}{[Next part highly nebulous]} 
+\textcolor{blue}{[This is just the math that calculates the tangents of x-y pairs given the progression of x and y. Given the above description,is it necessary to include it?]}
+
 The corresponding derivatives are:

### 2018-03-17 automatica/paper.tex
edits intro

@@
 Given an LTI model, we develop an automatic technique for generating
-correct by construction digital controllers that addresses all these
+correct-by-construction digital controllers that addresses all these
 challenges. Specifically, we synthesize stable and safe,
@@
   DBLP:conf/asplos/Solar-LezamaTBSS06}, a technique
-that became very popular in the recent years.  CEGIS denotes an
+that became very popular in the recent years.  CEGIS is an
 iterative process, where each iteration performs inductive
@@
 oracle. Essentially, the inductive generalisation uses information
-about a limited number of inputs to make claims about all the possible
-inputs in the form of candidate solutions. Our two instantiations of
-CEGIS are described next.
+about a limited number of inputs to compute a candidate solution
+for all the possible. Our two instantiations of CEGIS are
+described next.
 
@@
 %% specification since we are working in the frequency domain.
-{\em The first approach} uses a na\"ive technique that starts by devising a
+
+\emph{The first approach} uses a na\"ive technique that starts by devising a
 digital controller that stabilizes the system while remaining safe for a
@@
 unbounded safety by unfolding the dynamics of the system, considering the
-full hyper-cube of initial states, and checking a {\em completeness
+full hyper-cube of initial states, and checking a \emph{completeness
 threshold}~\cite{DBLP:conf/vmcai/KroeningS03}, i.e., the number of
@@
 
-Instead of unfolding the dynamics, {\em the second approach}
-employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to
+Instead of unfolding the dynamics, \emph{the second approach}
+employs \emph{abstract acceleration}~\cite{cattaruzza2015unbounded} to
 evaluate all possible progressions of the system simultaneously. 
-Additionally, this approach uses {\em abstraction refinement},
+Additionally, this approach uses \emph{abstraction refinement},
 enabling us to always start with a very simple description regardless of the
@@
 %% \addtodo{CD: the novelty compared to CAV'17 needs to be clarified}
-This paper represents an extension of \cite{DBLP:conf/cav/AbateBCCDKKP17}
-and makes the following contributions, where the fourth and the fifth denote
-extensions over \cite{DBLP:conf/cav/AbateBCCDKKP17}.
+This paper is an extension of~\cite{DBLP:conf/cav/AbateBCCDKKP17}
+and makes the following contributions, where the fourth and the fifth are
+extensions over~\cite{DBLP:conf/cav/AbateBCCDKKP17}.
 %
@@
   % floating point 
-\item We automatically generate {\em correct-by-construction} digital
+\item We automatically generate \emph{correct-by-construction} digital
   controllers using an inductive synthesis approach.  Our application of program
@@
 
-\item While \cite{DBLP:conf/cav/AbateBCCDKKP17} is restricted to systems
+\item While~\cite{DBLP:conf/cav/AbateBCCDKKP17} is restricted to systems
   modeled in discrete time, in the current paper we present a model for
   soundly evaluating reachability in a combined continuous-discrete time/space.
-\item A further limitation of the work in \cite{DBLP:conf/cav/AbateBCCDKKP17}
-  is its restriction to fixed-point arithmetic, meaning that fixed-point numbers
-  were employed for the representation of both the plant and the controller, as well as for
-  the operations performed by each of them.
-  Conversely, in the current paper we also make use of floating-point arithmetic
-  and compare the two approaches. Additionally, we enhance the implementation with an SMT backend, allowing us to also use reals in order to represent the states of the plant.
+
+\item A further limitation of the work in~\cite{DBLP:conf/cav/AbateBCCDKKP17}
+  is its restriction to fixed-point arithmetic, meaning that fixed-point
+  numbers were employed for the representation of both the plant and the
+  controller, as well as for the operations performed by each of them. 
+  Conversely, in the current paper we also make use of floating-point
+  arithmetic and compare the two approaches.  Additionally, we enhance the
+  implementation with an SMT backend, allowing us to also use reals in order
+  to represent the states of the plant.
+
 \end{enumerate}
@@
 
-\textbf{CEGIS -} Program synthesis is the problem of computing
+\textbf{CEGIS --} Program synthesis is the problem of computing
 correct-by-design programs from high-level specifications. Algorithms

### 2018-03-17 automatica/paper.tex
line break

@@
 traces of the model, alongside the numerical soundness required by the
-effects of discretisation and finite-precision errors.  A state-space model
+effects of discretisation and finite-precision errors.  A~state-space model
 has known advantages over the transfer function

### 2018-03-17 automatica/paper.tex
nudge

@@
 
-\textbf{Discretization Effects -}
+\textbf{Discretization Effects --}
 The classical approach to control synthesis has often disregarded
@@
 response~\cite{Duggirala2015} and finite word length (FWL) semantics, with
-the goal either to verify~\cite{daes20161} or to optimize~\cite{oudjida2014design} given implementations.
+the goal either to verify~\cite{daes20161} or to
+optimize~\cite{oudjida2014design} given implementations.
 
@@
 symbolic execution: to account for rounding errors, an upper bound is
-introduced in the verification phase.  The work in
-\cite{picasso2003stabilization} introduces invariant sets as a mechanism to
+introduced in the verification phase.  The work
+in~\cite{picasso2003stabilization} introduces invariant sets as a mechanism to
 bound the quantization error effect on stabilization as an invariant set

### 2018-03-19 automatica/paper.tex
inconsolata

--- 2018-03-17 automatica/paper.tex
@@
 \usepackage{pifont}
+\usepackage{inconsolata}
 \usepackage{todonotes}
@@
 Given an LTI model, we develop an automatic technique for generating
-correct-by-construction digital controllers that addresses all these
+correct by construction digital controllers that addresses all these
 challenges. Specifically, we synthesize stable and safe,
@@
   DBLP:conf/asplos/Solar-LezamaTBSS06}, a technique
-that became very popular in the recent years.  CEGIS is an
+that became very popular in the recent years.  CEGIS denotes an
 iterative process, where each iteration performs inductive
@@
 oracle. Essentially, the inductive generalisation uses information
-about a limited number of inputs to compute a candidate solution
-for all the possible. Our two instantiations of CEGIS are
-described next.
+about a limited number of inputs to make claims about all the possible
+inputs in the form of candidate solutions. Our two instantiations of
+CEGIS are described next.
 
@@
 %% specification since we are working in the frequency domain.
-
-\emph{The first approach} uses a na\"ive technique that starts by devising a
+{\em The first approach} uses a na\"ive technique that starts by devising a
 digital controller that stabilizes the system while remaining safe for a
@@
 unbounded safety by unfolding the dynamics of the system, considering the
-full hyper-cube of initial states, and checking a \emph{completeness
+full hyper-cube of initial states, and checking a {\em completeness
 threshold}~\cite{DBLP:conf/vmcai/KroeningS03}, i.e., the number of
@@
 
-Instead of unfolding the dynamics, \emph{the second approach}
-employs \emph{abstract acceleration}~\cite{cattaruzza2015unbounded} to
+Instead of unfolding the dynamics, {\em the second approach}
+employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to
 evaluate all possible progressions of the system simultaneously. 
-Additionally, this approach uses \emph{abstraction refinement},
+Additionally, this approach uses {\em abstraction refinement},
 enabling us to always start with a very simple description regardless of the
@@
 %% \addtodo{CD: the novelty compared to CAV'17 needs to be clarified}
-This paper is an extension of~\cite{DBLP:conf/cav/AbateBCCDKKP17}
-and makes the following contributions, where the fourth and the fifth are
-extensions over~\cite{DBLP:conf/cav/AbateBCCDKKP17}.
+This paper represents an extension of \cite{DBLP:conf/cav/AbateBCCDKKP17}
+and makes the following contributions, where the fourth and the fifth denote
+extensions over \cite{DBLP:conf/cav/AbateBCCDKKP17}.
 %
@@
   % floating point 
-\item We automatically generate \emph{correct-by-construction} digital
+\item We automatically generate {\em correct-by-construction} digital
   controllers using an inductive synthesis approach.  Our application of program
@@
 
-\item While~\cite{DBLP:conf/cav/AbateBCCDKKP17} is restricted to systems
+\item While \cite{DBLP:conf/cav/AbateBCCDKKP17} is restricted to systems
   modeled in discrete time, in the current paper we present a model for
   soundly evaluating reachability in a combined continuous-discrete time/space.
-
-\item A further limitation of the work in~\cite{DBLP:conf/cav/AbateBCCDKKP17}
-  is its restriction to fixed-point arithmetic, meaning that fixed-point
-  numbers were employed for the representation of both the plant and the
-  controller, as well as for the operations performed by each of them. 
-  Conversely, in the current paper we also make use of floating-point
-  arithmetic and compare the two approaches.  Additionally, we enhance the
-  implementation with an SMT backend, allowing us to also use reals in order
-  to represent the states of the plant.
-
+\item A further limitation of the work in \cite{DBLP:conf/cav/AbateBCCDKKP17}
+  is its restriction to fixed-point arithmetic, meaning that fixed-point numbers
+  were employed for the representation of both the plant and the controller, as well as for
+  the operations performed by each of them.
+  Conversely, in the current paper we also make use of floating-point arithmetic
+  and compare the two approaches. Additionally, we enhance the implementation with an SMT backend, allowing us to also use reals in order to represent the states of the plant.
 \end{enumerate}
@@
 
-\textbf{CEGIS --} Program synthesis is the problem of computing
+\textbf{CEGIS -} Program synthesis is the problem of computing
 correct-by-design programs from high-level specifications. Algorithms
@@
 %-------------------------------
-\section{Formal specification of model properties} 
+\section{Formal specification of control systems properties} 
 \label{sec:specification}
@@
 %-------------------------------
-\subsection{Abstract acceleration of linear dynamics} 
+\subsection{Abstract Acceleration of Linear Dynamics} 
 \label{ssec:aa}
@@
 %
+\textcolor{red}{[I have modified the notations with the `d' subscript as above.]}
 we want to find all possible states visited over an infinite time horizon
 starting at an initial set $X_0$.  
-This set is known as the \emph{reach tube} of the model:
+This set is known as the \emph{reach tube} of
+the model:
 %
@@
 Using Abstract Acceleration we transform this sequential reachability problem into a one-step problem.  
-This has a lot of benefits ~\cite{JSS14}, not least in terms of numerical error propagation.   
-In order to attain this, 
-the problem statement is modified, by means of acceleration, into 
+We first modify the problem statement by means of acceleration into
 %
@@
 %
-and new model semantics and corresponding set are further defined as 
+and further define new model semantics and corresponding set: 
 %
@@
 over-approximation of the reach tube of the model \cite{JSS14}.  
-\cite{cattaruzza2015unbounded} extends this to LTI models with inputs, 
-whereas we next extend the algorithm to continuous-time models, in view of the overall goal of this work. 
+In this work we extend the abstract acceleration algorithm to continuous-time models. 
 % and  For this reason we must first look at the acceleration of continuous-time dynamics.
@@
 we must be able to ensure that given properties of the plant hold at any given point in time.  
-In order to do so, we accelerate the dynamics of the plant according to the continuous-time model
-semantics in Sec.~\ref{sec:model}. 
-% and compute the state $\vec{x}_T$ at a given time $T$,
-%%
-%% namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
-%%
-%namely the state $\vec{x}(t)$ of the model 
-%%$\dot{\vec{x}}(t)=\mat{A}
-%at time $t=T$.
-
-%\textcolor{red}{[The following three subsections take too much space, plus the results are mostly known or easily derivable with simple algebra: we need to shorten and simplify it.
+In order to do so, we accelerate the dynamics of the plant according to the model
+semantics in Sec.~\ref{sec:model} and compute the state
+$\vec{x}_T$ at a given time $T$,
+%
+% namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
+%
+namely the state $\vec{x}(t)$ of the model 
+%$\dot{\vec{x}}(t)=\mat{A}
+at time $t=T$.
+
+\textcolor{red}{[The following three subsections take too much space, plus the results are mostly known or easily derivable with simple algebra: we need to shorten and simplify it.
 Dario: can you give it a crack?]}
-%\textcolor{blue}{[I merged the first two]}
+\textcolor{blue}{[I merged the first two]}
 
@@
 
+\textcolor{red}{[This paragraph is highly unclear - Dario: can you please update it?]}
+\textcolor{blue}{[is  this better?]}
+
 Just as the accelerated dynamics in equation \eqref{eq:feedback_sampled_cont} can be abstacted using \eqref{eq:aa_reachtube} (where $\bigcup_{k \in N_0} (\mat{A}_d-\mat{B}_d\mat{K}) ^k \subseteq \mathcal{A}$),
@@
 
-\textcolor{red}{[The next discussion is highly unclear - Dario: can you please update it?]}
-\textcolor{blue}{[how about this?]}
-
-We next describe how to obtain such a set. 
-Our overapproximation of the set is a polyhedron, which is defined by an
-intersection of hypeplanes. The smallest polyhedra that can be obtained are
-those whose faces touch the set, which they must do at a point tangential to
-the hyperplane. Rather than pick a set of directions and find such points, we
-will start from the points and find their tangents. Furthermore, to simplify the
-procedure, we will only look at two dimensional cuts of the space 
-(see~\cite{cattaruzza2015unbounded}). This means that for every point we
-choose is a vertex of the polyhedron.
-Finding out which side of the hyperplane corresponds to the inside of the
-polyhedron is achieved by looking at any other point in the original set and
-checking on which side of the hyperplane it lays.
-
-%Abstract acceleration works by finding support functions of the set that encompasses the matrices $\mat{A}^k$.
-%Support functions are scalars that measure the distance of a hyperplane tangent to the set boundary to the origin.
-%In the case of continuous spaces, this translates to calculating the derivatives of the envelope in order to find the direction of the support vector (normal to the hyperplane), and calculating the distance to the corresponding point where the hyperplane touches the set (at which the derivative was calculated).
-%The direction of the vector is determined by evaluating the support function of another point in the curve,
-%which is known to be smaller than that of the selected point, and the chosen hyperplanes are aligned with the eigenvectors, hence we only look at eigenvalue pairs to calculate the derivatives~\cite{cattaruzza2015unbounded}.
-
-\textcolor{red}{[Next part highly nebulous]} 
-\textcolor{blue}{[This is just the math that calculates the tangents of x-y pairs given the progression of x and y. Given the above description,is it necessary to include it?]}
-
+We describe now how to obtain such a set. Abstract acceleration works by finding support functions of the set that encompasses the matrices $\mat{A}^k$.
+Support functions are scalars that measure the distance of a hyperplane tangent to the set boundary to the origin.
+In the case of continuous spaces, this translates to calculating the derivatives of the envelope in order to find the direction of the support vector (normal to the hyperplane), and calculating the distance to the corresponding point where the hyperplane touches the set (at which the derivative was calculated).
+The direction of the vector is determined by evaluating the support function of another point in the curve,
+which is known to be smaller than that of the selected point, and the chosen hyperplanes are aligned with the eigenvectors, hence we only look at eigenvalue pairs to calculate the derivatives~\cite{cattaruzza2015unbounded}.
 The corresponding derivatives are:

### 2018-03-20 automatica/paper.tex
comment on termination
naive back end handles fixed or float

--- 2018-03-17 automatica/paper.tex
@@
 [COMMENT ON TERMINATION?]
-
+CEGIS in general is not guaranteed to terminate if the search space is infinite. 
 %-------------------------------
@@
 initial states.  This is sound if the current $k$ is greater than the completeness
-threshold.  We~also assume some precision $\langle I_p,F_p\rangle$ for the
+threshold.  We~also assume some (fixed or floating point) precision $\langle I_p,F_p\rangle$ for the
 plant and a sampling rate.  The checks that these assumptions hold are

### 2018-03-21 automatica/paper.tex
stuff about errors

@@
 %-------------------------------
-\subsection{\textcolor{red}{[Elizabeth: please add the specifics of the errors due to discretisation/quantisation, with reference to Fig.
-\ref{fig:digitalsystem}] and to what has been discussed in the Introductory section.}}
-%\label{sec:}
-%-------------------------------
+\subsection{Errors}
+
+We account for the presence of errors originating from a number of sources, shown in Figure~\ref{}:
+\begin{itemize}
+\item We represent the plant variables $x(t)$ and $u(t)$, which are real numbers, at a finite precision in our model, and so it is necessary to account for the errors introduced by this representation.
+We account for these errors in both back ends by using interval arithmetic, detailed in section~\ref{}.
+\item The quantisation errors by the ADC, which converts the analogue signal $x(t)$ into
+the digital signal $x_k$ which is fed into the controller. We account for this error in 
+the acceleration based back-end by introducing a noise signal $\nu_1$ that over-approximates this error, 
+shown in the figure. Further details are found in section~\ref{}. 
+In the naive back end we use bit-precise modelling in CBMC~\cite{} to accurately model this deterministic
+conversion. 
+\item The representation errors due to performing finite-precision arithmetic in the controller. 
+In the acceleration based back-end, this is again treated by the introduction of noise that bounds the error.
+The naive back end uses the bit-precise modelling of finite-precision arithmetic in CBMC. We assume that the controller
+represents numbers to the same precision as the ADC.
+\item We assume that the DAC converts numbers from the same precision as the controller to an analogue signal. 
+As a result we can ignore any errors introduced by the DAC
+\end{itemize}
 
@@
 
-The models we consider have two sources of error that are due to numerical representations.  
-The first is the numerical error introduced by the
-fixed-point numbers employed to model the plant, i.e., to represent the
-plant dynamics $A_d$, $B_d$ and $x_k$.  The second is the quantization error
-introduced by the digital controller, which performs operations on
-fixed-point numbers.  
-\textcolor{red}{[what about the DAC/ADC errors?]}
-In this section we outline the notation for the
-fixed-point representation of numbers, and briefly describe the errors
-introduced.  A~formal discussion is in
-%Appendix~\ref{appendix:numerical_errors}.
+As discussed in section~\ref{sec:}, the models we consider have errors due to several sources; the numerical error introduced by the precision used to represent the plant, the error introduced by the ADC conversion, and the error introduced by the precision used to represent the controller.
+First we consider the numerical errors introduced by the finite precision numbers (either fixed or floating point) used to model the plant and used by the digital controller.
+Then we account for the quantization errors introduced by the ADC.
+
+\subsection{Errors due to numerical representation}
+First consider the case where we use fixed-point representations, and synthesise fixed-point controllers.
 
@@
 will introduce errors, for which an upper bound can be
-given~\cite{DBLP:conf/arith/BrainTRW15}.
-
-We will use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real
+given~\cite{DBLP:conf/arith/BrainTRW15}:
+
+\begin{enumerate}
+
+\item {\bf Truncation:} Let $x$ be a real number, and $\mathcal{F}_{\langle
+I,F \rangle}(x)$ be the same number represented in a fixed-point domain as
+above.  Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the
+error $ \delta_T=x\ \%_{c_m}\ \tilde x$, and $\%_{c_m}$ is the modulus
+operation performed on the last bit. 
+Thus, $\delta_T$ is the truncation error and it will propagate across
+operations.
+%
+\item {\bf Rounding:} The following errors appear in basic operations.  Let
+$c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be
+the truncation errors caused by representing $c_1$ and $c_2$ in the
+fixed-point domain as above.
+%
+\begin{enumerate}
+%
+\item Addition/Subtraction: these operations only propagate errors coming
+from truncation of the operands, namely $\mathcal{F}_{\langle I,F
+\rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3$
+with $|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
+%
+\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) \cdot
+\mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3|
+\leq |\delta_{T1}\cdot\mathcal{F}_{\langle I,F \rangle}(c_2)|\allowbreak +
+|\delta_{T2}\cdot\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where
+$c_m=2^{-F}$ as above.
+%
+\item Division: the operations performed by our controllers in the FWL
+domain do not include division.  However, we do use division in computations
+at the precision of the plant.  Here the error depends on whether the
+divisor is greater or smaller than the dividend:  $\mathcal{F}_{\langle I,F
+\rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_{T3}$
+where $\delta_{T3}$ is $(\delta_{T2}\cdot c_1 - \delta_{T1}\cdot
+c_2)/(\delta_{T2}^2 - \delta_{T2} c_2)$,
+%
+%$\mathcal{F}_{\langle I,F \rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) =  (c_1 - \delta_{T1})/ (c_2 + \delta_{T2}) + c_m $, where $c_m=2^{-F}$ as above.
+\end{enumerate}
+
+\item {\bf Overflow:}
+The maximum size of a real number $x$ that can be represented in a fixed
+point domain as $\mathcal{F}_{\langle I,F \rangle}(x)$ is $\pm
+(2^{I-1}+1-2^{-F})$.  Numbers outside this range cannot be represented by
+the domain.  We check that overflow does not occur.
+
+\end{enumerate}
+
+\subsection{Notation}
+In this paper we will use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real
 number $x$ represented at the fixed-point precision of the controller, and
@@
 precision $\mathcal{F}_{\langle I_p,F_p \rangle}$.
+
+\subsection{Floating point representation}
+
+Let $\mathcal{F}_{\langle E,M \rangle}(x)$ denote a real number $x$
+represented in a floating point domain, with $E$ bits representing the exponent
+part and $M$ bits representing the mantissa part. Bounds for errors introduced by performing basic mathematical operators at this precision can be derived~\cite{DBLP:conf/arith/BrainTRW15}.
+
+We use $\mathcal{F}_{\langle E_c,M_c \rangle}(x)$ to denote a real number represented at the floating-point precision of the controller, and $\mathcal{F}_{\langle E_p,M_p \rangle}(x)$ to denote a real number represented at the fixed-point precision of the plant model.
+We apply the same principles as in the preceding section when selection the plant precision.
+
+\subsection{ADC/DAC quantization errors} 
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+In this section we describe how quantization errors can be modelled as noise.
+Note that this is only applicable to the acceleration back end, as the naive back end makes use of CBMC's bit-precise model checking capabilities to account for these deterministic errors.
+
+During any given ADC conversion, the continuous signal will be sampled in
+the real domain and transformed by $\mathcal{F}\langle I_{c},F_{c} \rangle
+(x)$ (assuming the ADC discretization is the same as the digital
+implementation).  This sampling uses a threshold which is defined by the
+less significant bit ($q_{c}=c_{m_c}=2^{-F_c}$) 
+%\blue{[this quantity was named $c_m$ above and in other parts of the paper - please uniformise notations]}
+of the ADC and some non-linearities of the circuitry.  The overall conversion is
+%
+$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k :
+y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right] \,.$$
+%
+If we denote the error in the conversion by $\nu_k=y_k-y(t)$ where $t = nk$,
+and $n$ is the sampling time and $k$ the number of steps, then we may define
+some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
+
+We will assume, for the purposes of this analysis, that the domain of the
+ADC is that of the digital controller (i.e, the quantizer includes any
+digital gain added in the code).  The process of quantization in the DAC is
+similar except that it is calculating $\mathcal{F}\langle I_{dac},F_{dac}
+\rangle (\mathcal{F}\langle I_{c},F_{c} \rangle (x)) $.  If these domains
+are the same ($I_{c}=I_{dac},\allowbreak F_{c}=F_{dac}$), or if the DAC
+resolution in higher than the ADCs, then the DAC quantization error is equal
+to zero.  From the above equations we can now define the ADC and DAC
+quantization noises ${\nu_1}_k \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}]$ and
+${\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}]$, where $q_1=q_{c}$ and 
+$q_2=q_\mathit{dac}$.  This is illustrated in
+Fig.~\ref{fig:digitalsystem} where $Q_1$ is the quantizer of the ADC
+and $Q_2$ the quantizer for the DAC.  These bounds hold irrespective of
+whether the noise is correlated, hence we may use them to over-approximate
+the noise effect on the state space progression over time.  The
+resulting dynamics are
+%
+\begin{align*}
+%\label{eq:pre_quantization}
+{x}_{k+1} = {A}_d{x}_k+{B}_d({u}_k+{{\nu}_2}_k), \quad u_k = -K{x}_{k}+{{\nu}_1}_k, 
+\end{align*}
+%
+which result in the following closed-loop dynamics:
+%
+\begin{align*}
+%\label{eq:quantization}
+{x}_{k+1} &= ({A}_d-{B}_d{K}_d) {x}_k+{B}_d{{\nu}_2}_k +{{\nu}_1}_k \,. 
+\end{align*}
 

### 2018-03-27 automatica/paper.tex
Addressed comments in sec 3.3

@@
 
-In this section, we give a brief description of the CEGIS framework, as illustrated in Figure~\ref{fig:CEGIS}. [ADD REFERENCE(S).]
+In this section, we give a brief description of the CEGIS framework~\cite{jha-icse10,
+  DBLP:conf/asplos/Solar-LezamaTBSS06}, as illustrated in Figure~\ref{fig:CEGIS}.
 
@@
 and $\phi$ is a quantifier-free formula. 
-We~interpret the ground terms over some finite [CHECK: finite? are we doing only SAT or also SMT?] domain~$\mathcal{D}$. 
+We~interpret the ground terms over some domain~$\mathcal{D}$. 
 This is a synthesis problem, where the objective is indeed to select a valid $P$ satisfying $\phi$ over all the $a$ terms.
-CEGIS breaks down this generally hard synthesis problem into two easier parts.
-
-The design consists of two phases, an inductive synthesis phase (denoted by {\sc Synthesize} in
+
+CEGIS breaks down this generally hard synthesis problem into two easier parts:
+%The design consists of two phases,
+an inductive synthesis phase (denoted by {\sc Synthesize} in
 Figure~\ref{fig:CEGIS}) and a validation phase (denoted by {\sc
   Verify}), which interact via a finite set of tests {\sc
-  inputs} that is updated incrementally.  Given the specification $\phi$, the inductive synthesis procedure tries to
+  inputs} that is updated incrementally.
+Given the specification $\phi$, the inductive synthesis procedure tries to
 find an existential witness $P$ satisfying the specification
@@
 %% in~\cite{DBLP:conf/lpar/DavidKL15}.
-[COMMENT ON TERMINATION?]
-CEGIS in general is not guaranteed to terminate if the search space is infinite. 
+If the solution space is finite then the CEGIS loop is guaranteed to
+terminate by either finding a solution or showing that no solution
+exists.
 %-------------------------------

### 2018-03-29 automatica/paper.tex
explanation of bit precise modelling

@@
 conversion.
+In other words, CBMC constructs a boolean formula which explicitly unwinds the transition system for any symbolically represented input state, bounded by the initial conditions, and performs the ADC conversion precisely on that symbolically represented input state.
+When we verify safety, the boolean formula is satisfied only if there is an input state value for which the subsequent trace through the transition system eventually violates the safety property.
 \item The representation errors due to performing finite-precision arithmetic in the controller. 
 In the acceleration based back-end, this is again treated by the introduction of noise that bounds the error.
-The naive back end uses the bit-precise modelling of finite-precision arithmetic in CBMC. We assume that the controller
+The naive back end uses the bit-precise modelling of finite-precision arithmetic in CBMC, in the same way as we handled the ADC conversion. We assume that the controller
 represents numbers to the same precision as the ADC.

### 2018-04-03 automatica/paper.tex
added experimental results table
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \newtheorem{proof}{Proof}
+
+\newcommand{\xmark}{\ding{55}}
 
@@
 
+We provide the results in Table~\ref{tab:results}.  Here \textit{Benchmark} is
+the name of the respective benchmark, \textit{Order} is the number of
+continuous variables, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the
+fixed-point precision used to model the plant, while \textit{Time} is the
+total time required to synthesize a controller for the given
+plant with one of the two methods.  Timeouts are indicated by~\xmark.  The
+precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
+chosen to be $I_c = 8$, $F_c = 8$.
+
+\begin{table*}
+\centering
+\begin{tabular}{| r | l | c | c | r | c | r |}
+%
+\hline
+\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
+   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
+1  & Cruise Control  & 1 &   &  &  &   \\
+2  & DC Motor          & 2 &   &  &  &  \\
+3  & Helicopter        & 3 &  &   &  &   \\
+4  & Inverted Pendulum & 4 &   &  &  &  \\
+5  & Magnetic Pointer  & 2 & &  &  &   \\
+6  & Magnetic Suspension & 2 &  & & &  \\
+7  & Pendulum          & 2 &   & & &    \\
+8  & Suspension        & 2 &  & & &   \\
+9  & Tape Driver       & 3 &   & & &  \\
+10 & Satellite          & 2 &   &  & &   \\\hline
+%
+\end{tabular}
+\vspace{0.05in}
+\caption{Experimental results\label{tab:results}}
+\end{table*}
+
 %-------------------------------

### 2018-04-03 automatica/paper.tex
added additional columns to the table
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2018-03-29 automatica/paper.tex
@@
 
+We provide the results in Table~\ref{tab:results}.  Here 
+\textit{Benchmark} is the name of the respective benchmark, 
+\textit{Order} is the number of continuous variables, 
+$\mathcal{F}_{\langle I_p,F_p \rangle}$ and $\mathcal{F}_{\langle p \rangle}$  
+are the fixed- and floating-point precision used to model the plant, respectively;
+while \textit{Time} is the total time required to synthesize a controller for the given
+plant with one of the two methods.  Timeouts are indicated by~\xmark.  The
+precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
+chosen to be $I_c = 8$, $F_c = 8$ for fixed-point and 
+$\mathcal{F}_{\langle p \rangle}$ is chosen to be half-precision for floating-point.
+
+\begin{table*}
+\centering
+\begin{tabular}{| r | l | c | c | r | c | r | c | r | c | r |}
+%
+\hline
+\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                 & \multicolumn{4}{|c|}{Abstraction} \\
+   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
+1  & Cruise Control  & 1 &   &  &  &  & & & &\\
+2  & DC Motor          & 2 &   &  &  &  & & & &\\
+3  & Helicopter        & 3 &  &   &  &  & & & &\\
+4  & Inverted Pendulum & 4 &   &  &  & & & & &\\
+5  & Magnetic Pointer  & 2 & &  &  &  & & & &\\
+6  & Magnetic Suspension & 2 &  & & & & & & &\\
+7  & Pendulum          & 2 &   & & & & & & &\\
+8  & Suspension        & 2 &  & & & & & & &\\
+9  & Tape Driver       & 3 &   & & & & & & &\\
+10 & Satellite          & 2 &   &  & & & & & &\\\hline
+%
+\end{tabular}
+\vspace{0.05in}
+\caption{Experimental results\label{tab:results}}
+\end{table*}
+
 %-------------------------------

### 2018-04-03 automatica/paper.tex
added additional benchmarks to the table
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2018-03-29 automatica/paper.tex
@@
 
+We provide the results in Table~\ref{tab:results}.  Here 
+\textit{Benchmark} is the name of the respective benchmark, 
+\textit{Order} is the number of continuous variables, 
+$\mathcal{F}_{\langle I_p,F_p \rangle}$ and $\mathcal{F}_{\langle p \rangle}$  
+are the fixed- and floating-point precision used to model the plant, respectively;
+while \textit{Time} is the total time required to synthesize a controller for the given
+plant with one of the two methods.  Timeouts are indicated by~\xmark.  The
+precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
+chosen to be $I_c = 8$, $F_c = 8$ for fixed-point and 
+$\mathcal{F}_{\langle p \rangle}$ is chosen to be half-precision for floating-point.
+
+\begin{table*}
+\centering
+\begin{tabular}{| r | l | c | c | r | c | r | c | r | c | r |}
+%
+\hline
+\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                 & \multicolumn{4}{|c|}{Abstraction} \\
+   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
+1  & Cruise Control  & 1 &   &  &  &  & & & &\\
+2  & DC Motor          & 2 &   &  &  &  & & & &\\
+3  & Helicopter        & 3 &  &   &  &  & & & &\\
+4  & Inverted Pendulum & 4 &   &  &  & & & & &\\
+5  & Magnetic Pointer  & 2 & &  &  &  & & & &\\
+6  & Magnetic Suspension & 2 &  & & & & & & &\\
+7  & Pendulum          & 2 &   & & & & & & &\\
+8  & Suspension        & 2 &  & & & & & & &\\
+9  & Tape Driver       & 3 &   & & & & & & &\\
+10 & Satellite          & 2 &   &  & & & & & &\\
+12 & Voltage Regulator & &   &  & & & & & &\\
+13 & Guidance Control  & &   &  & & & & & &\\
+14 & Spring Mass   & &   &  & & & & & &\\
+\hline
+%
+\end{tabular}
+\vspace{0.05in}
+\caption{Experimental results\label{tab:results}}
+\end{table*}
+
 %-------------------------------

### 2018-04-06 benchmarks/matlab/get_inputs.m
inputs of new benchmarks

@@ -1,7 +1,7 @@
 function INPUT = get_inputs(Name)
 
-INPUT_10 = {'ballmaglev','pendulum','satellite', 'usgtampa', 'invpendulum_pendang'};
-INPUT_100 = {'magneticpointer', 'invpendulum_cartpos'};    
+INPUT_10 = {'ballmaglev','pendulum','satellite', 'usgtampa', 'invpendulum_pendang','bioreact'};
+INPUT_100 = {'magneticpointer', 'invpendulum_cartpos','steamdrum','cstrtemp'};    
 INPUT_1000 = {'magsuspension'};
 INPUT_1000000 = {'suspension'};
 

### 2018-04-06 CAV2018/paper.tex
comma

@@
 \begin{align}
-\vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u} \text{ where } \mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B} 
+\vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u} \text{ where } \mat{B}_T=\mat{A}^{-1}(\mat{A}_T-\mat{I})\mat{B} 
 \label{eq:continuous_tube_param}
@@
 we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\
-0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$.}. 
+0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]t}$.}. 
 If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that
 $A_d=e^{\mat{A} T_d}$, then
-$\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u})
+$\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+\mat{A}^{-1}(\mat{A}_d^{\frac{T}{T_d}}-\mat{I})\mat{B}_d\vec{u}
 \text{ with } T \in \mathbb{R}_0^+$ (where $\mat{A}_d^{\frac{T}{T_d}} =
@@
  \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
- \vec{u}(t)=\mat{K}\vec{x}_k,  \,
+ \vec{u}(t)=-\mat{K}\vec{x}_k,  \,
  kT_s \leq t < (k+1)T_s \,. 
@@
 accordingly.  Initially, $\phi$ is simply given as the defined $\phi :=
-\phi_{stability} \wedge \phi_{input} \wedge \phi_{init}$.
+\phi_\mathit{stability} \wedge \phi_\mathit{input} \wedge \phi_\mathit{init}$.
 
@@
 ([xshift=5em]synth.north)
-   node[align=left,yshift=-0.7cm,xshift=.5cm] {{$\phi$}\\{$\phi_{init}^K$}} %{$\phi_\mathit{safety}$}\\ 
+   node[align=left,yshift=-0.7cm,xshift=.5cm] {{$\phi$}\\{$\phi_\mathit{init}^K$}} %{$\phi_\mathit{safety}$}\\ 
    ([xshift=-5em]synth.north) edge node[align=center] {FAIL} ([xshift=-5em]model1.south);
@@
 %
-$$\vec{y}_k=\mathcal{F}_{\langle A \rangle}\left(y(kT_s)\right), \text{ with }  \vec{y}_k \in \left[y(kT_s)-\frac{q_{a}}{2}, y(kT_s)+\frac{q_{a}}{2}\right] \,.$$
+$$\vec{y}_k=\mathcal{F}_{\langle A \rangle}\left(y(kT_s)\right)
+  \text{ with }  \vec{y}_k \in \left[y(kT_s)-\frac{q_{a}}{2}, y(kT_s)+\frac{q_{a}}{2}\right] \,.$$
 %
@@
  \begin{align}
- \vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u} \text{ where } \mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B} 
+ \vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u} \text{ where } \mat{B}_T=\mat{A}^{-1}(\mat{A}_T-\mat{I})\mat{B} 
  \label{eq:param_discretize}
@@
  with $\mat{A}_T$ as per \eqref{eq:continuous_tube_dyn} is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$.
- If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}\vec{u}) \text{ with } k \in \mathbb{R}^+$ is the state of the system at time $kT_d$.
+ If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}+\mat{A}^{-1}(\mat{A}_d^{\frac{T}{T_d}}-\mat{I})\mat{B}\vec{u} \text{ with } k \in \mathbb{R}^+$ is the state of the system at time $kT_d$.
  \end{lemma}
@@
  The first part of the equation ($\mat{A}_T\vec{x}_0$) is proven in the previous section.  As for the second part, we have from equation \eqref{eq:plant}
-that $\mat{B}_T = \int_{t = 0}^{T} e^{\mat{A} t} dt\ \mat{B}$ which expands to $\mat{B}_T= (\mat{A}^{-1} e^{\mat{A}T}-\mat{A}^{-1} e^{\mat{A} 0}) \mat{B}=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$, thus proving the theorem.
+that $\mat{B}_T = \int_{t = 0}^{T} e^{\mat{A} t} dt\ \mat{B}$ which expands to $\mat{B}_T= (\mat{A}^{-1} e^{\mat{A}T}-\mat{A}^{-1} e^{\mat{A} 0}) \mat{B}=\mat{A}^{-1}(\mat{A}_T-\mat{I})\mat{B}$, thus proving the theorem.
  \end{proof}
@@
  \dot{\vec{x}}({t}) &= \mat{A}\vec{x}+\mat{B}\vec{u}(t)\nonumber\\
- \vec{u}(t)&=\mat{K}\vec{x}_k, \text{ where }  kT_s \leq t < (k+1)T_s
+ \vec{u}(t)&=-\mat{K}\vec{x}_k, \text{ where }  kT_s \leq t < (k+1)T_s
  \end{align*}

### 2018-04-11 CAV2018/paper.tex
corrections based on cav2018 reviews

@@
 state of a plant cannot be directly measured but has to be inferred from its
-effect on the output.  A plant model that minimizes the difference between
-its output and the real output of the plant is called an \emph{observer} and
-it is a well known paradigm in the control
-literature~\cite{astrom1997computer}.
+effect on the output. A system that converges to the internal state of the plant
+from measurements of its input and output is called an \emph{observer}, and
+it is a well known paradigm in the control literature~\cite{astrom1997computer}.
 
@@
 We use a CounterExample-Guided Inductive Synthesis (CEGIS)~\cite{jha-icse10,
-DBLP:conf/pldi/Solar-LezamaRBE05} approach, which we enhance with
+DBLP:conf/asplos/Solar-LezamaTBSS06} approach, which we enhance with
 abstraction refinement and optimization resulting in the novel CEGIS-OR
@@
 linear combination of its states and inputs\footnote{Notice that since we
-can only measure $\vec{y}$, the state-space $\vec{x}$ is not fully
-observable.}.
+can only measure $\vec{y}$, the state $\vec{x}$ cannot be measured directly.}.
 %
@@
 \tau(\vec{x}_k,\vec{u}_k) = %\big\{ 
-\mat{A}\vec{x}_k + \mat{B}\vec{u}_k \;.
+\mat{A}_d\vec{x}_k + \mat{B}_d\vec{u}_k \;.
  %\mid \mat{G}\vec{x}_k \leq \vec{h}\big\}\;. 
@@
 with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, $\mat{B}_T$ as in
-\eqref{eq:continuous_tube_param}, and where $\mat{A}_d=\mat{A}_{T_s},
+\eqref{eq:continuous_tube_param}, $T \in [kT_s, (k+1)T_s]$, and where $\mat{A}_d=\mat{A}_{T_s},
 \mat{B}_d=\mat{B}_{T_s}$ describe the discretized plant dynamics with
@@
 %
-The error introduced by a delay $t_d$ in the control output $\vec{u}_k$ of a
-discrete feedback controller for a continuous LTI system can be modeled as a
-non-deterministic disturbance signal ($\nu_t$ in
+The error introduced by a delay $t_d$ in the control input $\vec{u}_k$ updated
+by a discrete feedback controller for a continuous LTI system can be modeled as
+a non-deterministic disturbance signal ($\nu_t$ in
 Figure~\ref{fig:observersystem}) upper bounded by

### 2018-04-17 automatica/paper.tex
added all benchmarks to Table 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2018-04-03 automatica/paper.tex
@@
    &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
-1  & Cruise Control  & 1 &   &  &  &  & & & &\\
-2  & DC Motor          & 2 &   &  &  &  & & & &\\
-3  & Helicopter        & 3 &  &   &  &  & & & &\\
-4  & Inverted Pendulum & 4 &   &  &  & & & & &\\
-5  & Magnetic Pointer  & 2 & &  &  &  & & & &\\
-6  & Magnetic Suspension & 2 &  & & & & & & &\\
-7  & Pendulum          & 2 &   & & & & & & &\\
-8  & Suspension        & 2 &  & & & & & & &\\
-9  & Tape Driver       & 3 &   & & & & & & &\\
-10 & Satellite          & 2 &   &  & & & & & &\\\hline
+1  & Acrobot  & &   &  &  &  & & & &\\
+2  & Antenna  & &   &  &  &  & & & &\\
+3  & Ballmaglev  & &  &   &  &  & & & &\\
+4  & Bioreact & &   &  &  & & & & &\\
+5  & Chen\_ex1  & & &  &  &  & & & &\\
+6  & Chen\_ex2 & &  & & & & & & &\\
+7  & Chen\_ex3 & &   & & & & & & &\\
+8  & Chen\_ex4 & &  & & & & & & &\\
+9  & Cruise  & &  & & & & & & &\\
+10 & CruiseHSCC  & &   &  & & & & & &\\
+12 & Cstr & &   &  & & & & & &\\
+13 & Cstr tmp  & &   &  & & & & & &\\
+14 & DCmotor   & &   &  & & & & & &\\
+15 & Flexbeam   & &   &  & & & & & &\\
+16 & Guidance chen   & &   &  & & & & & &\\
+17 & Helicopter   & &   &  & & & & & &\\
+18 & Invpendulum\_cart   & &   &  & & & & & &\\
+19 & Invpendulum\_pen   & &   &  & & & & & &\\
+20 & Magpointer   & &   &  & & & & & &\\
+21 & Magsuspension  & &   &  & & & & & &\\
+22 & Pendulum   & &   &  & & & & & &\\
+23 & Regulator   & &   &  & & & & & &\\
+24 & Invpendulum\_pen   & &   &  & & & & & &\\
+25 & Spring mass dump   & &   &  & & & & & &\\
+26 & streamdrum   & &   &  & & & & & &\\
+27 & Suspension  & &   &  & & & & & &\\
+28 & Tapedriver   & &   &  & & & & & &\\
+\hline
 %

### 2018-04-17 automatica/paper.tex
added number of state variables
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2018-04-03 automatica/paper.tex
@@
    &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
-1  & Cruise Control  & 1 &   &  &  &  & & & &\\
-2  & DC Motor          & 2 &   &  &  &  & & & &\\
-3  & Helicopter        & 3 &  &   &  &  & & & &\\
-4  & Inverted Pendulum & 4 &   &  &  & & & & &\\
-5  & Magnetic Pointer  & 2 & &  &  &  & & & &\\
-6  & Magnetic Suspension & 2 &  & & & & & & &\\
-7  & Pendulum          & 2 &   & & & & & & &\\
-8  & Suspension        & 2 &  & & & & & & &\\
-9  & Tape Driver       & 3 &   & & & & & & &\\
-10 & Satellite          & 2 &   &  & & & & & &\\\hline
+1  & Acrobot  & 4 &   &  &  &  & & & &\\
+2  & Antenna  & 6 &   &  &  &  & & & &\\
+3  & Ballmaglev  & 3 &  &   &  &  & & & &\\
+4  & Bioreact & 3 &   &  &  & & & & &\\
+5  & Chen\_ex1  & 3 & &  &  &  & & & &\\
+6  & Chen\_ex2 & 8 &  & & & & & & &\\
+7  & Chen\_ex3 & 7 &   & & & & & & &\\
+8  & Chen\_ex4 & 9 &  & & & & & & &\\
+9  & Cruise  & 1 &  & & & & & & &\\
+10 & CruiseHSCC  & 1 &   &  & & & & & &\\
+12 & Cstr & 1 & &  & & & & & &\\
+13 & Cstrtmp  & 1 &   &  & & & & & &\\
+14 & DCmotor   & 2 &   &  & & & & & &\\
+15 & Flexbeam   & 6 &   &  & & & & & &\\
+16 & Guidance chen  & 5 &   &  & & & & & &\\
+17 & Helicopter   & 3 &   &  & & & & & &\\
+18 & Invpendulum\_cartpos & 4 &   &  & & & & & &\\
+19 & Invpendulum\_penang   & 2 &   &  & & & & & &\\
+20 & Magpointer   & 2 &  &  & & & & & &\\
+21 & Magsuspension  & 2 &   &  & & & & & &\\
+22 & Pendulum   & 2 & &  & & & & & &\\
+23 & Regulator   & 5 &   &  & & & & & &\\
+24 & Springmassdamper & 2 &   &  & & & & & &\\
+25 & streamdrum   & 3 &   &  & & & & & &\\
+26 & Suspension  & 4 &   &  & & & & & &\\
+27 & Tapedriver   & 3 &   &  & & & & & &\\
+\hline
 %

### 2018-04-17 automatica/paper.tex
nudge Fig 2

@@
 },
-          row sep=1cm, column sep=3cm] {
-   \node[fill=gray!20] (synth) {{\sc Synthesize}};
+          row sep=1cm, column sep=3.5cm] {
+   \node[fill=gray!20,minimum height=1cm] (synth) {{\sc Synthesize}};
    \&
-   \node[fill=gray!20] (verif) {{\sc Verify}};
+   \node[fill=gray!20,minimum height=1cm] (verif) {{\sc Verify}};
    \&
@@
    ([yshift=2em]synth.east) edge node[align=center] {Candidate solution} ([yshift=2em]verif.west)
-    ([yshift=-2em]verif.west) edge node[align=center] {Counter-example} ([yshift=-2em]synth.east)
+    ([yshift=-2em]verif.west) edge node[align=center] {Counterexample} ([yshift=-2em]synth.east)
     (verif) edge node {} (done);
@@
 }
- \caption{The CEGIS framework. \label{fig:CEGIS}}
+ \caption{The CEGIS framework\label{fig:CEGIS}}
 \end{figure*}

### 2018-04-17 CAV2018/paper.tex
More changes from CAV reviews
switch to lipics format

@@
 %\documentclass[sigconf]{acmart}
-\documentclass[sigconf]{llncs}
+%\documentclass[sigconf]{llncs}
+\documentclass[a4paper,UKenglish]{lipics-v2018}
 
@@
 
-\renewcommand{\note}[1]{\textcolor{red}{[#1]}}
+\newcommand{\note}[1]{\textcolor{red}{[#1]}}
 \newcommand{\xmark}{\ding{55}}
@@
 
-\begin{document}
-
 \title{Formal Synthesis of Digital Controllers for Observable Continuous
@@
 
-\author{Anonymous%Dario Cattaruzza, Cristina David, Alessandro Abate, Daniel Kroening
-}%\email{alessandro.abate@cs.ox.ac.uk}
+\titlerunning{Formal Synthesis of Digital Controllers for Observable Continuous Plants}
+
+\author{}{}{}{}{}
+
+%\email{alessandro.abate@cs.ox.ac.uk}
 %\email{dario.cattaruzza@cs.ox.ac.uk}
@@
 
-\institute{%University of Oxford
-}
+%\institute{University of Oxford}
 
@@
 
+\authorrunning{}
+
+\begin{document}
 \maketitle
@@
 \Rightarrow \phi_\mathit{init}^{K}$.
-These bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
+These bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space (by direct inclusion in the SAT formula).
 \end{itemize}
@@
 %-------------------------------
-\setcounter{lemma}{0}
-\setcounter{theorem}{0}
-\setcounter{corollary}{0}
+%\setcounter{lemma}{0}
+%\setcounter{theorem}{0}
+%\setcounter{corollary}{0}
  %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2018-04-17 CAV2018/paper.tex
paragraph -> subsection

@@
 
-\paragraph{\underline{{\sc abstract}}} computes an initial version of $\phi$
+\subsection*{\underline{{\sc abstract}}} computes an initial version of $\phi$
 and decides the sample time $T_d$,
@@
 \end{itemize}
-\paragraph{\underline{{\sc synthesize}}} generates a candidate controller matrix $\mat{K}_{\langle P \rangle}$
+\subsection*{\underline{{\sc synthesize}}} generates a candidate controller matrix $\mat{K}_{\langle P \rangle}$
 and observer matrix $\mat{L}_{\langle P \rangle}$ that satisfy
@@
 %\item
-\paragraph{\underline{{\sc Verify}}} checks whether the candidate
+\subsection*{\underline{{\sc Verify}}} checks whether the candidate
 solution found by {\sc synthesize} is a solution for the whole synthesis
@@
 
-\paragraph{\underline{{\sc Refine Abstraction and optimize}}} refines the
+\subsection*{\underline{{\sc Refine Abstraction and optimize}}} refines the
 model abstraction as well as optimizes the current candidate

### 2018-04-18 CAV2018/paper.tex
+ authors (in the order used by Dario on easychair)
revise intro to compare CEGIS-OR to the abstraction refinement step in CAV'17

@@
 
-\author{}{}{}{}{}
+\author{Dario Cattaruzza}{University of Oxford}{}{}{}
+\author{Cristina David}{University of Cambridge, Diffblue}{}{}{}
+\author{Alessandro Abate}{University of Oxford}{}{}{}
+\author{Daniel Kroening}{University of Oxford, Diffblue}{}{}{}
+
+\authorrunning{Cattaruzza, David, Abate, Kroening}
 
@@
 %\email{dario.cattaruzza@cs.ox.ac.uk}
-%\author{Cristina David}\email{cristina.david@cs.ox.ac.uk}
+%\email{cristina.david@cs.ox.ac.uk}
 %\email{kroening@cs.ox.ac.uk}
@@
 %\end{frontmatter}
-
-\authorrunning{}
 
@@
 While research on digital control is well
-developed~\cite{astrom1997computer}, automated and sound control synthesis
-is challenging, particularly when the synthesis objective goes beyond
-classical stability.  Recent work~\cite{abate2017automated} described a
-method for synthesizing safe digital stabilizing controllers for fully
-observable LTI plants.  This work differs from the vast majority of existing
-approaches in that it explores the continuous space of the system to
-synthesize correct-by-construction minimal digital controllers.  In contrast
-to LTL models, which require thousands of states and elaborate algorithms to
-implement~\cite{reissig2017feedback}, these PID-like controllers are
-represented by a few parameters and only require few lines of code, thus
-reducing the implementation cost and execution time while remaining
-resilient to the effects of digitalization. 
-However,~\cite{abate2017automated}~is restricted to fully observed systems
-(i.e., where all the states are known) modeled in discrete time, and
-furthermore explores only a subset of the properties that engineers are
-interested in.  By contrast, in most real implementations, the internal
-state of a plant cannot be directly measured but has to be inferred from its
-effect on the output. A system that converges to the internal state of the plant
-from measurements of its input and output is called an \emph{observer}, and
-it is a well known paradigm in the control literature~\cite{astrom1997computer}.
+developed~\cite{astrom1997computer}, automated and sound control
+synthesis is challenging, particularly when the synthesis objective
+goes beyond classical stability.  Recent
+work~\cite{abate2017automated} described a method for synthesizing
+safe digital stabilizing controllers for fully observable LTI plants.
+This work differs from the vast majority of existing approaches in
+that it explores the continuous space of the system to synthesize
+correct-by-construction minimal digital controllers.  In contrast to
+LTL models, which require thousands of states and elaborate algorithms
+to implement~\cite{reissig2017feedback}, these PID-like controllers
+are represented by a few parameters and only require few lines of
+code, thus reducing the implementation cost and execution time while
+remaining resilient to the effects of digitalization.
+However,~\cite{abate2017automated}~is restricted to fully observed
+systems (i.e., where all the states are known) modeled in discrete
+time, and furthermore explores only a subset of the properties that
+engineers are interested in.  By contrast, in most real
+implementations, the internal state of a plant cannot be directly
+measured but has to be inferred from its effect on the output. A
+system that converges to the internal state of the plant from
+measurements of its input and output is called an \emph{observer}, and
+it is a well known paradigm in the control
+literature~\cite{astrom1997computer}.
 
@@
 
-We use a CounterExample-Guided Inductive Synthesis (CEGIS)~\cite{jha-icse10,
-DBLP:conf/asplos/Solar-LezamaTBSS06} approach, which we enhance with
-abstraction refinement and optimization resulting in the novel CEGIS-OR
-(CEGIS with Optimization and Refinement).  This design uses an iterative
-process where each iteration performs inductive generalization based on
-counterexamples provided by a verification oracle.  Essentially, the
-inductive generalization uses information about a limited number of inputs
-to make claims in the form of candidate solutions about all the possible
-inputs.  By~using abstraction refinement, CEGIS-OR allows us to handle
-complex systems, which are initially represented by coarse abstractions that
-only get refined on demand.  Consequently, solutions that do not require a
-high level of precision are obtained fast.  Since the use of coarse
-abstractions may result in low-quality candidate solutions (i.e., candidates
-that fail the specification on a very large number of inputs), we use
+We use a CounterExample-Guided Inductive Synthesis
+(CEGIS)~\cite{jha-icse10, DBLP:conf/asplos/Solar-LezamaTBSS06}
+approach, which we enhance with abstraction refinement and
+optimization resulting in the novel CEGIS-OR (CEGIS with Optimization
+and Refinement).  This design uses an iterative process where each
+iteration performs inductive generalization based on counterexamples
+provided by a verification oracle.  Essentially, the inductive
+generalization uses information about a limited number of inputs to
+make claims in the form of candidate solutions about all the possible
+inputs.  Similar to \cite{DBLP:conf/cav/AbateBCCDKKP17}, the use of
+abstraction refinement is meant to allow CEGIS-OR to handle complex
+systems, which are initially represented by coarse abstractions that
+only get refined on demand.  However, the problem we observed with
+this approach is that the use of coarse abstractions often results in
+low-quality candidate solutions (i.e., candidates that fail the
+specification on a very large number of inputs) and, consequently, there
+are very few solutions obtained at such low levels of precision.
+%% Consequently, solutions that do not require a
+%% high level of precision are obtained fast.  Since the use of coarse
+%% abstractions may result in low-quality candidate solutions (i.e., candidates
+%% that fail the specification on a very large number of inputs),
+In this paper, we address this problem by using 
 optimization techniques after each inductive generalization phase to improve
@@
 time).
+Consequently, solutions that do not require a
+high level of precision can indeed be obtained fast.
 

### 2018-04-18 CAV2018/paper.tex
change citation from arxiv to CAV'17 paper

@@
 goes beyond classical stability.  Recent
-work~\cite{abate2017automated} described a method for synthesizing
+work~\cite{DBLP:conf/cav/AbateBCCDKKP17} described a method for synthesizing
 safe digital stabilizing controllers for fully observable LTI plants.
@@
 remaining resilient to the effects of digitalization.
-However,~\cite{abate2017automated}~is restricted to fully observed
+However,~\cite{DBLP:conf/cav/AbateBCCDKKP17}~is restricted to fully observed
 systems (i.e., where all the states are known) modeled in discrete
@@
 
-In this paper we build on the ideas presented in~\cite{abate2017automated}
+In this paper we build on the ideas presented in~\cite{DBLP:conf/cav/AbateBCCDKKP17}
 and develop a new technique that addresses most of these limitations. 

### 2018-04-18 CAV2018/paper.tex
additional explanation regarding the optimization step in sec 7

@@
 approach and with optimization.  We call the resulting new technique
-\emph{CEGIS-OR} (CEGIS with Optimization and Refinement).  By using
+CEGIS-OR (CEGIS with Optimization and Refinement).  By using
 abstraction refinement, CEGIS-OR addresses the scalability issues inherent
@@
 \begin{itemize}
-\item[1.] We start with coarse abstractions that get
-  refined into more complex ones as the procedure progresses. Thus, solutions
-  that do not require a high level of precision are obtained faster. 
+\item[1.] We start with coarse abstractions that get refined into more
+  complex ones as the procedure progresses. Thus, solutions that do
+  not require a high level of precision are obtained faster.  Note
+  that the optimization step plays an important role here given that,
+  in its absence, the use of coarse abstractions often results in
+  low-quality candidate solutions (i.e., candidates that fail the
+  specification on a very large number of inputs) and, consequently,
+  there are very few solutions obtained at such low levels of
+  precision.
 \item[2.] Although {\sc synthesize} makes use of a potentially coarse abstraction,

### 2018-04-18 benchmark-runner/float-benchmark-individual-runner.sh
Floating point benchmark runner fixes

@@ -4,6 +4,7 @@ export PATH=${PATH}:/media/sf_Documents/cbmc5.7/src/cbmc
 
 status_output_file='output.txt'
 synthesis_file='FWL_LTI.c'
+no_speed_file='FWL_LTI_NOSPD.c';
 nudge_file='FWL_LTI_NT.c'
 width_check_file='width_LTI.c'
 script_base_directory=`pwd`
@@ -210,6 +211,9 @@ while [ $((integer_width+radix_width)) -le ${max_length} ]; do
     elif [ "${nudge}" = "-CNF" ]; then
       echo_log "cbmc ${mode} -D _CONTROL_FLOAT_WIDTH=$((integer_width+radix_width)) -D _CONTROL_RADIX_WIDTH=${radix_width} \"${working_directory}/${nudge_file}\" --stop-on-fail >${working_directory}/${cbmc_log_file}"
       timeout --preserve-status --kill-after=${kill_time} ${timeout_time} /media/sf_Documents/cbmc5.7/src/cbmc/cbmc ${mode} -D _CONTROL_FLOAT_WIDTH=$((integer_width+radix_width)) -D _CONTORL_RADIX_WIDTH=${radix_width} "${working_directory}/${nudge_file}" --stop-on-fail >${working_directory}/${cbmc_log_file} 2>&1
+    elif [ "${speed}" = "1" ]; then
+      echo_log "cbmc ${mode} -D _CONTROL_FLOAT_WIDTH=$((integer_width+radix_width)) -D _CONTROL_RADIX_WIDTH=${radix_width} \"${working_directory}/${no_speed_file}\" --stop-on-fail >${working_directory}/${cbmc_log_file}"
+      timeout --preserve-status --kill-after=${kill_time} ${timeout_time} /media/sf_Documents/cbmc5.7/src/cbmc/cbmc ${mode} -D _CONTROL_FLOAT_WIDTH=$((integer_width+radix_width)) -D _CONTORL_RADIX_WIDTH=${radix_width} "${working_directory}/${no_speed_file}" --stop-on-fail >${working_directory}/${cbmc_log_file} 2>&1
     else
       echo_log "cbmc ${mode} -D _CONTROL_FLOAT_WIDTH=$((integer_width+radix_width)) -D _CONTROL_RADIX_WIDTH=${radix_width} \"${working_directory}/${synthesis_file}\" --stop-on-fail >${working_directory}/${cbmc_log_file}"
[…]

### 2018-04-18 CAV2018/paper.tex
Floating point benchmark runner fixes
Updated benchmark references in reviewers questions

@@
 \documentclass[a4paper,UKenglish]{lipics-v2018}
-
 \usepackage{microtype}
@@
 %\email{cristina.david@cs.ox.ac.uk}
-%\email{kroening@cs.ox.ac.uk}
+%\author{Daniel Kroening}\email{kroening@cs.ox.ac.uk}
 
@@
 %\begin{keyword}        
-%Digital Control; A/D converters; Control System Synthesis; Safety Analysis; Quantization Errors; Observer-based Controller. Sampling.
+\keywords {Digital Control; A/D converters; Control System Synthesis; Safety Analysis; Quantization Errors; Observer-based Controller. Sampling.}
 %\end{keyword}
@@
 and $\norm{\vec{x}}_1=\sum_{i=0}^{size(\vec{x})} |\vec{x}_i|$ is the $l_1$ norm, 
-which we extend to sets as $\norm{X}_1 = \sup \{\norm{\vec{x}}_1, \vec{x} \in X\}$.  
+which we extend to sets as $\norm{X}_1 = \sup \{\norm{\vec{x}}_1, \vec{x} \in X\}$.\\ 
 For the proof see Appendix~\ref{sec:proofs}
@@
 \phi_\mathit{safety}^n: = & \forall k \in \{0, \ldots , n\},
-  \mat{G}\vec{x}_k \leq \vec{h} \text{ and } \underline{y} \leq y_k \leq \overline{y}\nonumber\\
+  \mat{G}\vec{x}_k \leq \vec{h} \text{ and } \underline{y} \leq y_k \leq \overline{y} \nonumber\\ 
 \phi_\mathit{safety}: = & \phi_\mathit{safety}^\infty
@@
 %
-Note that FWL effects are not explicitly captured here
+FWL effects are not explicitly captured here
 as they are implicit from Equation \eqref{eq:observer_LTI_FWL_cf}.
@@
 
-We must point out that the optimizer tool uses infinite precision for the
+The optimizer tool uses infinite precision for the
 plant, and may therefore find solutions that the synthesizer cannot, due to
@@
 taken these models and modified each possible combination of their
-parameters by a 10\% tolerance, thus creating seven hundred benchmarks from
-this base.
+parameters by a 10\% tolerance, thus creating seven hundred total benchmarks.
 
@@
 \hline
-\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{order} & \multicolumn{1}{|c|}{No.} & \multicolumn{4}{|c|}{CEGIS} & \multicolumn{4}{|c|}{CEGIS-OR} \\
+\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{p} & \multicolumn{1}{|c|}{No.} & \multicolumn{4}{|c|}{CEGIS-AR} & \multicolumn{4}{|c|}{CEGIS-OR} \\
    &                                 & & \multicolumn{1}{|c|}{}  & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{t.o.} & \multicolumn{1}{|c|}{found} & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{t.o.} & \multicolumn{1}{|c|}{found}\\\hline
@@
 \caption{\label{tab:cegis_results}
-Experimental results.  Minimum, and Median times for standard CEGIS vs
-CEGIS-OR on multiple benchmarks.  No.  indicates Number of benchmarks,
-t.o.~indicates timeouts (in the median case, it indicates more than half of
-the benchmarks timed out).  The order denotes the number of variables of a
-model.}
-%
+Experimental results.  Minimum, and Median times for standard CEGIS-AR (with
+abstraction refinement~\cite{DBLP:conf/cav/AbateBCCDKKP17}) vs CEGIS-OR on
+multiple benchmarks.  No.  indicates Number of benchmarks, t.o.~indicates
+timeouts (in the median case, it indicates more than half of the benchmarks
+timed out).  p denotes the number of variables of a model.}
 \end{table}
@@
 
+We found that on average, observer synthesis is over an order of magnitude slower
+than full state controller synthesis for the given benchmarks (SAT has
+a worst case exponential time complexity, and typical polynomial time, so higher
+order systems will show larger differences).
 In order to show the improvements due to our optimization-enhanced CEGIS, we
-compared our approach against a standard CEGIS procedure.  For the majority
-of our benchmarks, we observe that our approach is significantly faster than
-standard CEGIS.  We further note that the number of times standard CEGIS
-times out is much larger than CEGIS-OR which results in more found
-solutions.
+compared our approach against a standard CEGIS with abstraction refinement
+procedure~\cite{DBLP:conf/cav/AbateBCCDKKP17} (We note that the naive approach
+in~\cite{DBLP:conf/cav/AbateBCCDKKP17} cannot handle the continuous time case.  
+Furthermore, since it is in general slower than the abstraction refinement
+version, the latter is a more representative benchmark).
+For the majority of our benchmarks, we observe that our approach is
+significantly faster than~\cite{DBLP:conf/cav/AbateBCCDKKP17}. 
+We further note that the number of times CEGIS times out is much larger than
+CEGIS-OR which results in more found solutions.
 

### 2018-04-20 CONCUR2018/paper.tex
revised experimental section

--- 2018-04-18 CAV2018/paper.tex
@@
 \hline
-\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{p} & \multicolumn{1}{|c|}{No.} & \multicolumn{4}{|c|}{CEGIS-AR} & \multicolumn{4}{|c|}{CEGIS-OR} \\
+\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{p} & \multicolumn{1}{|c|}{No.} & \multicolumn{4}{|c|}{CEGIS\cite{DBLP:conf/cav/AbateBCCDKKP17}} & \multicolumn{4}{|c|}{CEGIS-OR} \\
    &                                 & & \multicolumn{1}{|c|}{}  & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{t.o.} & \multicolumn{1}{|c|}{found} & \multicolumn{1}{|c|}{Min} & \multicolumn{1}{|c|}{Median} & \multicolumn{1}{|c|}{t.o.} & \multicolumn{1}{|c|}{found}\\\hline
@@
 \end{tabular}
-\vspace{0.05in}
+%\vspace{0.05in}
 \caption{\label{tab:cegis_results}
@@
 over-approximations in the verifier that may reject a valid candidate.  It
-is impossible for us to differentiate these from case where a controller
+is impossible for us to differentiate these from the case where a controller
 does not exist.
 
-We found that on average, observer synthesis is over an order of magnitude slower
-than full state controller synthesis for the given benchmarks (SAT has
-a worst case exponential time complexity, and typical polynomial time, so higher
-order systems will show larger differences).
-In order to show the improvements due to our optimization-enhanced CEGIS, we
-compared our approach against a standard CEGIS with abstraction refinement
-procedure~\cite{DBLP:conf/cav/AbateBCCDKKP17} (We note that the naive approach
-in~\cite{DBLP:conf/cav/AbateBCCDKKP17} cannot handle the continuous time case.  
-Furthermore, since it is in general slower than the abstraction refinement
-version, the latter is a more representative benchmark).
+In order to show the improvements due to our optimization-enhanced
+CEGIS, we compared our approach against the CEGIS approach with
+abstraction refinement described
+in~\cite{DBLP:conf/cav/AbateBCCDKKP17}.  We note that,
+while~\cite{DBLP:conf/cav/AbateBCCDKKP17} presents two approaches, one
+of them (referred to as the naive approach
+in~\cite{DBLP:conf/cav/AbateBCCDKKP17}) cannot handle the continuous
+time case and thus we can only compare against the abstraction-based
+one (referred to as CEGIS~\cite{DBLP:conf/cav/AbateBCCDKKP17} in Table~\ref{tab:cegis_results}).  %% Furthermore, since it is in general slower than the abstraction
+%% refinement version, the latter is a more representative benchmark).
 For the majority of our benchmarks, we observe that our approach is
-significantly faster than~\cite{DBLP:conf/cav/AbateBCCDKKP17}. 
-We further note that the number of times CEGIS times out is much larger than
-CEGIS-OR which results in more found solutions.
+significantly faster than CEGIS~\cite{DBLP:conf/cav/AbateBCCDKKP17}.  %% We
+%% further note that the number of times CEGIS times out is much larger
+%% than CEGIS-OR which results in more found solutions.
 
@@
 systems where the safety specification is tight, 
-meaning that the standard CEGIS loop would require many iterations.
+meaning that the CEGIS~\cite{DBLP:conf/cav/AbateBCCDKKP17}
+loop would require many iterations.
 %  We obtain the most improvements for the models with large orders?}
@@
 %% both approaches..}.
-These improvements are due to the Abstraction Refinement and Optimization in CEGIS-OR.
-While abstraction refinement enables us to start with coarse abstractions
-that are only refined on demand, 
-the optimization
-allows to locally improve candidate solutions and avoid entire iterations of the CEGIS loop
-(which would have also required more refined abstractions).
+These improvements are due to the interplay between Abstraction
+Refinement and Optimization in CEGIS-OR.  While abstraction refinement
+enables us to start with coarse abstractions that are only refined on
+demand, the optimization allows to locally improve candidate solutions
+and avoid entire iterations of the
+CEGIS~\cite{DBLP:conf/cav/AbateBCCDKKP17} loop (which would have also
+required more refined abstractions).
 %% elimination of counterexamples that
@@
 %% improvements.
-While some systems might still require a very precise
-abstraction resulting in many refinements
-(this is generally the cause of time-outs in CEGIS-OR),
-others allow us to find solutions with rather coarse
-abstractions (this is reflected in the smaller minimum
-times obtained with CEGIS-OR). 
+While some systems might still require a very precise abstraction
+resulting in many refinements (this is generally the cause of
+time-outs in CEGIS-OR), others allow us to find solutions with rather
+coarse abstractions (this is reflected in the smaller minimum times
+obtained with CEGIS-OR).
+
+With respect to the additional complexity introduced by the synthesis
+of observer-based controllers compared to fully observed systems, we
+found that on average, observer synthesis is over an order of
+magnitude slower than full state controller synthesis for the given
+benchmarks. This is due to the fact that the introduction of the
+observer doubles the order of the model.
+
+%% (SAT has a worst case exponential time complexity, and
+%% typical polynomial time, so higher order systems will show larger
+%% differences).
+
 %Since further synthesis require increasingly

### 2018-04-23 CONCUR2018/paper.tex
abstract

@@
 refinement and optimization, which allows us to start with a low-resolution
-discretized model and find candidate solutions fast.  This model is refined
-on demand.  Moreover, in order to improve our chances of finding a solution
-even when considering coarse abstractions of the system, in each iteration
-of the CEGIS loop we use matrix eigen-decomposition to optimize our
-candidate.
+discretized model and to find candidate solutions fast, or to refine this model on demand.  
+Moreover, in order to improve our chances of finding a solution
+even when considering coarse abstractions of the system, 
+ in each iteration  we 
+%of the CEGIS loop we use matrix eigen-decomposition to 
+optimize our candidate.
 %
@@
 This design yields a significant speed-up compared to traditional CEGIS
-(i.e., without abstraction refinement and optimization).  We~demonstrate the
+(i.e., without abstraction refinement or optimization).  We~demonstrate the
 practical value of this approach by automatically synthesizing safe

### 2018-04-23 CONCUR2018/paper.tex
fixes

@@
 \item We automatically generate \emph{correct-by-construction} digital
-  state-feedback observer controllers that guarantee a given safety property
+  observer-based feedback controllers that guarantee a given safety property
   alongside stability and response time specifications.  We note that
   observers are much more complex and difficult to synthesize than standard
-  full-state feedback controllers (hence the need for abstraction refinement).
-%
-\item  Our synthesis addresses challenges created by digitalization errors
- such as quantization, and time discretization as well as delays in the
- sampling and processing times which introduce control errors in real
+  full state feedback controllers (hence the need for the abstraction/refinement procedure). 
+%
+\item  Our synthesis addresses challenges created by digitalization errors, 
+ such as quantization, and time discretization, as well as delays in the
+ sampling and processing times, all of which introduce control errors in real
  implementations.
@@
 linear combination of its states and inputs\footnote{Notice that since we
-can only measure $\vec{y}$, the state $\vec{x}$ cannot be measured directly.}.
+can only measure $\vec{y}$, the state $\vec{x}$ cannot be measured directly.}, namely 
 %
@@
 \begin{equation}\label{equ:reachtube}
-\hat{X}_n=\hat{\tau}^n(X_0,U)=\bigcup_{k\in[0,n]} \tau^k(X_0,U)
+\hat{X}_n=\hat{\tau}^n(X_0,U)=\bigcup_{k\in[0,n]} \tau^k(X_0,U), 
 \end{equation}
 %
-as the union of $k$-reach sets over $n$ iterations. 
+namely as the union of $k$-reach sets over $n$ iterations. 
 %
@@
 namely the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time
-$t=T$.
+$t=T$. \textcolor{red}{[ADD REFERENCE TO PUBLISHED WORK ON ABSTRACT ACCELERATION.]}
 
@@
 which we extend to sets as $\norm{X}_1 = \sup \{\norm{\vec{x}}_1, \vec{x} \in X\}$.\\ 
-For the proof see Appendix~\ref{sec:proofs}
+For the proof see Appendix~\ref{sec:proofs}. 
 \end{theorem}
@@
 loop dynamics is defined by the characteristic polynomials of~$\mat{A}_c$
-and~$\mat{A}_o$.
+and~$\mat{A}_o$ as 
 %
 \begin{align*}
-P(z)=P_K(z)P_L(z)=\left(z^p+\sum_{i=0}^{p-1}{(a_i-k_i)z^{i}}\right) \left(z^p+\sum_{i=0}^{p-1}{(a_i-l_i)z^{i}}\right)
+P(z)=P_K(z)P_L(z)=\left(z^p+\sum_{i=0}^{p-1}{(a_i-k_i)z^{i}}\right) \left(z^p+\sum_{i=0}^{p-1}{(a_i-l_i)z^{i}}\right). 
 \end{align*}
 %
-Jury's criteria uses these coefficients to ensure that no root of the
+Jury's criterion~\cite{fadali} uses these coefficients to ensure that no root of the
 polynomial has a magnitude greater than one. 
@@
 the largest column norm in $ \left[\begin{array}{c}\mat{A}_e\\
-\mat{B}_e\end{array}\right]$) and apply Jury's Criterion over
+\mat{B}_e\end{array}\right]$) and apply Jury's criterion over
 %
@@
 \phi_\mathit{safety}^n: = & \forall k \in \{0, \ldots , n\},
-  \mat{G}\vec{x}_k \leq \vec{h} \text{ and } \underline{y} \leq y_k \leq \overline{y} \nonumber\\ 
-\phi_\mathit{safety}: = & \phi_\mathit{safety}^\infty
+  \mat{G}\vec{x}_k \leq \vec{h} \text{ and } \underline{y} \leq y_k \leq \overline{y}, \nonumber\\ 
+\phi_\mathit{safety}: = & \phi_\mathit{safety}^\infty, 
 \label{eq:safetyspec}
@@
   \overline{\lambda} = \max(|\lambda_i|) \text{ and }
-  \overline{\lambda}<1,\ \forall i \in \{1, \ldots,p\}
+  \overline{\lambda}<1,\ \forall i \in \{1, \ldots,p\}, 
 %
@@
 
-Next, we describe the CEGIS-OR loop in Figure~\ref{fig:CEGIS-OR}.
+Next, we describe the salient blocks in the CEGIS-OR loop of Figure~\ref{fig:CEGIS-OR}.
 
@@
 
-In the second stage, we take the complex eigenvalue with the largest angle
-($\max\{|\tan^{-1}\left(\frac{im(\lambda)}{re(\lambda)}\right)| \mid \lambda
-\in \Lambda\}$) and reduce its imaginary component only ($re(\lambda) + f\,
+In the second stage, we take the complex eigenvalue with the largest angle, 
+which is characterised by $\max\{|\tan^{-1}\left(\frac{im(\lambda)}{re(\lambda)}\right)|, \lambda
+\in \Lambda\}$, and reduce its imaginary component only ($re(\lambda) + f\,
 im(\lambda)$ such that the new controller satisfies $\phi_\mathit{init}^K$). 
@@
 \begin{table}
-\centering
+%\centering
+\hspace{-0.25in}
 \footnotesize

### 2018-04-23 CONCUR2018/paper.tex
Minor fixes

@@
 in~\cite{DBLP:conf/cav/AbateBCCDKKP17}) cannot handle the continuous
-time case and thus we can only compare against the abstraction-based
+time case and thus we can only compare against the faster, abstraction-based
 one (referred to as CEGIS~\cite{DBLP:conf/cav/AbateBCCDKKP17} in Table~\ref{tab:cegis_results}).  %% Furthermore, since it is in general slower than the abstraction

### 2018-04-23 benchmark-runner/float-all-benchmarks-runner.sh

@@ -7,17 +7,34 @@ else
   precision=0
 fi
 if [ -n $2 ];then
-  ./float-multi-benchmark-runner.sh 'dcmotor2_ss' ${precision} CEGIS '-NNF' 1 10 "$2"
-#  ./float-multi-benchmark-runner.sh 'helicopter2_ss' ${precision} CEGIS '-NNF' 1 10 "$2"
-#  ./float-multi-benchmark-runner.sh 'magneticpointer2_ss' ${precision} CEGIS '-NNF' 1 10 "$2"
-#  ./float-multi-benchmark-runner.sh 'satellite2_ss' ${precision} CEGIS '-NNF' 1 10 "$2"
-#  ./float-multi-benchmark-runner.sh 'invpendulum_cartpos2_ss' ${precision} CEGIS '-NNF' 1 10 "$2"
-#  ./float-multi-benchmark-runner.sh 'suspension2_ss' CEGIS ${precision} '-NNF' 1 10 "$2"
-#  ./float-multi-benchmark-runner.sh 'tapedriver_ss2_ss' ${precision} CEGIS '-NNF' 1 10 "$2"
-#  ./float-multi-benchmark-runner.sh 'pendulum2_ss' ${precision} CEGIS '-NNF' 1 10 "$2"
-#  ./float-multi-benchmark-runner.sh 'cruise2_ss' ${precision} CEGIS '-NNF' 1 10 "$2"
-#  ./float-multi-benchmark-runner.sh 'magsuspension2_ss' ${precision} CEGIS '-NNF' 1 10 "$2"
-#  ./float-multi-benchmark-runner.sh 'invpendulum_pendang2_ss' ${precision} CEGIS '-NNF' 1 10 "$2"
+  ./float-multi-benchmark-runner.sh 'dcmotor' ${precision} CEGIS '-NNF' 1 10 "$2"
+#  ./float-multi-benchmark-runner.sh 'helicopter' ${precision} CEGIS '-NNF' 1 10 "$2"
+#  ./float-multi-benchmark-runner.sh 'magneticpointer' ${precision} CEGIS '-NNF' 1 10 "$2"
+#  ./float-multi-benchmark-runner.sh 'satellite' ${precision} CEGIS '-NNF' 1 10 "$2"
+#  ./float-multi-benchmark-runner.sh 'invpendulum_cartpos' ${precision} CEGIS '-NNF' 1 10 "$2"
[…]

### 2018-04-23 automatica/paper.tex
results

@@
 3  & Ballmaglev  & 3 &  &   &  &  & & & &\\
-4  & Bioreact & 3 &   &  &  & & & & &\\
-5  & Chen\_ex1  & 3 & &  &  &  & & & &\\
-6  & Chen\_ex2 & 8 &  & & & & & & &\\
+4  & Bioreact & 3 & 16,8 & 11200ms & 16,10 &14600ms & & & &\\
+5  & Chen\_ex1& 3 & 16,8 & 7278ms  & 16,10 & 9196ms & & & &\\
+6  & Chen\_ex2 & 8& & & 32,23 & 4683872ms &  & & &\\
 7  & Chen\_ex3 & 7 &   & & & & & & &\\
 8  & Chen\_ex4 & 9 &  & & & & & & &\\
-9  & Cruise  & 1 &  & & & & & & &\\
-10 & CruiseHSCC  & 1 &   &  & & & & & &\\
+9  & Cruise    & 1 & 16,8 & 6563ms & 16,10 & 6543ms &  & & &\\
+10 & CruiseHSCC & 1 & 16,8 & 6587ms & 16,10 & 6567ms &  & & &\\
 12 & Cstr & 1 & &  & & & & & &\\
 13 & Cstrtmp  & 1 &   &  & & & & & &\\
-14 & DCmotor   & 2 &   &  & & & & & &\\
+14 & DCmotor   & 2 & 16,8  & 6879ms & 16,10 & 7786ms & & & &\\
 15 & Flexbeam   & 6 &   &  & & & & & &\\
 16 & Guidance chen  & 5 &   &  & & & & & &\\
-17 & Helicopter   & 3 &   &  & & & & & &\\
+17 & Helicopter   & 3 & 16,8 & 13728ms & 32,23 & 148012ms & & & &\\
 18 & Invpendulum\_cartpos & 4 &   &  & & & & & &\\
-19 & Invpendulum\_penang   & 2 &   &  & & & & & &\\
-20 & Magpointer   & 2 &  &  & & & & & &\\
-21 & Magsuspension  & 2 &   &  & & & & & &\\
-22 & Pendulum   & 2 & &  & & & & & &\\
+19 & Invpendulum\_pendang & 2 & 24,12 & 9741ms & 16,10 & 28135ms & & & &\\
+20 & Magpointer   & 2 & 16,8 & 10093ms & 16,10 & 20407ms & & & &\\
+21 & Magsuspension  & 2 & 12,12  &22146ms  & 16,10 & 34808ms & & & &\\
+22 & Pendulum   & 2 & 16,8 & 8503ms & 32,23 & 23987ms & & & &\\
 23 & Regulator   & 5 &   &  & & & & & &\\
 24 & Springmassdamper & 2 &   &  & & & & & &\\
-25 & streamdrum   & 3 &   &  & & & & & &\\
-26 & Suspension  & 4 &   &  & & & & & &\\
-27 & Tapedriver   & 3 &   &  & & & & & &\\
+25 & streamdrum   & 3 & 16,8  & 332422ms & 16,10 & 590501ms & & & &\\
+26 & Suspension  & 4 & 16,8  & 17206ms & 16,10 &1372945ms & & & &\\
+27 & Tapedriver   & 3 & 16,8  & 8188ms & & & & & &\\
 \hline

### 2018-04-23 CONCUR2018/paper.tex
nudge

@@
 namely the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time
-$t=T$. \textcolor{red}{[ADD REFERENCE TO PUBLISHED WORK ON ABSTRACT ACCELERATION.]}
+$t=T$, and then use abstraction~\cite{JSS14,cattaruzza2015unbounded} to overapproximate $\hat{X}_n$.
 
@@
 resulting closed loop form converges faster than the original and has a
-smaller rotation, which facilitates meeting the safety specification
+smaller rotation, which facilitates meeting the specification
 $\phi_\mathit{safety}$.
@@
 
-With respect to the additional complexity introduced by the synthesis
-of observer-based controllers compared to fully observed systems, we
-found that on average, observer synthesis is over an order of
-magnitude slower than full state controller synthesis for the given
-benchmarks. This is due to the fact that the introduction of the
+Given the nature of the specifications, observer synthesis cannot be directly compared to full state controller synthesis. 
+On average, we found the former to be over an order of magnitude slower for the given benchmarks, largely due to the fact that the introduction of the
 observer doubles the order of the model.

### 2018-04-23 CONCUR2018/paper.tex
another nudge

@@
 satisfied.
+
+We note that the introduction of an observer doubles the size of the model w.r.t.
+a full state controller, which will have an average polynomial, worst case
+exponential time increase in the sysnthesis engine.
 
@@
 
-Given the nature of the specifications, observer synthesis cannot be directly compared to full state controller synthesis. 
-On average, we found the former to be over an order of magnitude slower for the given benchmarks, largely due to the fact that the introduction of the
-observer doubles the order of the model.
-
 %% (SAT has a worst case exponential time complexity, and

### 2018-04-23 CONCUR2018/paper.tex
nudge
+ copyright and subjclass

@@
 \authorrunning{Cattaruzza, David, Abate, Kroening}
+
+\Copyright{Cattaruzza, David, Abate, Kroening}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+
+\subjclass{Computer systems organization~Embedded software}% mandatory: Please choose ACM 2012 classifications from https://www.acm.org/publications/class-2012 or https://dl.acm.org/ccs/ccs_flat.cfm .
+E.g., cite as "General and reference $\rightarrow$ General literature" or \ccsdesc[100]{General and reference~General literature}.
 

### 2018-04-25 automatica/paper.tex
updating the benckmark description

@@
 Our benchmark suite consists of 18 SISO models extracted from the 
-control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS};
+control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal};
 these models are discretized with different sample times, leading to $167$ different benchmarks
@@
 
-The \textit{DC motor} plant describes the velocity dynamics of a basic 
-brushed direct current electrical machine. 
-The \textit{automotive cruise control system} plant is used to keep constant 
-the speed of an automobile, tracking a desired speed reference, 
+The \textit{acrobot} plant corresponds to the model of a two-link 
+underactuated robot manipulator, named acrobot, linearized by partial 
+feedback linearization~\cite{acrobot}.The \textit{antenna} benchmark 
+describes the dynamics of the dynamics of the azimuth angle of an antenna 
+motion system composed a gearbox, DC motor and amplifiers~\cite{gajic2008optimal}. 
+The \textit{ballmaglev} plant corresponds to the discrete model of a simple 
+eletromagnet-ball system, where a steel ball is levitated in air by the action 
+of an electromagnetic force generated by an electromagnet~\cite{Franklin15}. 
+The \textit{bioreactor} benchmark is a linear model identified by least squares 
+for the cell mass concentration controlled through dilution rate of a 
+bioreactor~\cite{bioreactor}.
+
+The \textit{Chen\_ex1}, \textit{Chen\_ex2} and \textit{Chen\_ex3} benchmarks 
+correspond to high-order control system discrete models generally used as 
+case study for model order reduction techniques~\cite{CHEN1979389}. The benchmarks 
+\textit{Cruise}~\cite{Franklin15} and \textit{CruiseHSCC}~\cite{Astrom08} are 
+automotive  cruise control models. Automotive cruise control is used to keep 
+constant the speed of an automobile, tracking a desired speed reference, 
 compensating disturbances and uncertainties related to relief and terrain.
-The \textit{pendulum} plant consists of a swinging point mass suspended from 
-a frictionless pivot by means of a negligible mass rod, while the 
-\textit{inverted pendulum} plant describes a system similar to the pendulum, but the point 
-mass must be equilibrated above the pivot point, which is mounted on an 
-one degree of freedom cart that moves over a track through a DC motor.
-
-The \textit{magnetic suspension} plant corresponds to the discrete model of a 
-simple eletromagnet-ball system, where a steel ball is levitated in air 
-by the action of an electromagnetic force generated by an electromagnet.
-The \textit{magnetic pointer} plant describes a pointer employed in analogue 
-gauges and indicators, whose angular position dynamics is controlled 
-by a magnetic field. 
-The \textit{1/4 car suspension} plant corresponds to the model of a single 
-wheel suspension system of a car, {\it i.e.}, the relative motion dynamics 
-of a mass springer damp model, which connects the car to one of its wheels.
-
-The \textit{computer tape driver} plant describes a computer storage device used to read and write 
-data on magnetic tapes. The \textit{acrobot} plant corresponds to the model of a two-link 
-underactuated robot manipulator, named acrobot, linearized by partial 
-feedback linearization~\cite{acrobot}. 
-The \textit{high-order system} plants correspond to a series of high-order control system model 
-generally used as example for order reduction techniques~\cite{CHEN1979389}.
+
+There are two continuous stirred tank reactor models named \textit{cstr} and 
+\textit{cstrtmp} that describe the PH dynamics of a neutralization reaction 
+of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
+the temperature of a exothermic reaction~\cite{astrom2006advanced} in a continuous 
+flow stirred-tank reactor. The \textit{DC motor} plant describes the velocity 
+dynamics of a basic brushed direct current electrical machine.
+
+The \textit{Flexbeam} benchmark is a plant employed in vibration studies; the 
+physical  system consists of a flexible metallic structure with piezoceramic 
+actuators and sensors. The \textit{guidance chen} benchmark is another 
+high-order system model used by Chen et al.~\cite{CHEN1979389}  to evaluate 
+model order reduction techniques; it corresponds to a guidance control system model,
+which is used to determine the path of an autonomous vehicle movement. The 
+\textit{helicopter} benchmark plant describes the dynamics of transitional motion 
+with respect to a longitudinal plane and the rotational motion around the longitudinal 
+axis for a coaxial helicopter.
+
+The \textit{Invpendulum\_cartpos} and \textit{Invpendulum\_pendang} benchmarks
+are models for the cart position and the pendulum angle of an inverted pendulum 
+plant composed by a point mass must be equilibrated above the pivot point, which is 
+mounted on an one degree of freedom cart that moves over a track through a DC motor.
+
+The \textit{magpointer} corresponds to a magnetic pointer plant composed by a pointer 
+employed in analogue gauges and indicators, whose angular position dynamics is 
+controlled by a magnetic field. The \textit{magsuspension} describes the dynamic of
+a magnetic car suspension system. The \textit{pendulum} plant consists of a swinging 
+point mass suspended from a frictionless pivot by means of a negligible mass rod.
+
+The \textit{Regulator} plant consists of a linear model of a synchronous electrical
+machine connected to an  infinite bus~\cite{KOKOTOVIC198023}. The 
+\textit{springer-mass damper system} plant is classic model for several mechanical 
+systems dynamics. This benchmark describes a mass, which is fixed to a node by means 
+of a springer and moves under the action of a input force, damping, and elastic force.
+The \textit{steam drum} benchmark describes the linear model for the level dynamics 
+of a  boiler steam drum~\cite{boiler}.
+
+The \textit{suspension} benchmark corresponds to the model of a single wheel suspension 
+system of a car, {\it i.e.}, the relative motion dynamics of a mass springer damp model, 
+which connects the car to one of its wheels.  The \textit{tapedriver} benchmark
+corresponds to the model of computer tape driver, \textit{i.e.}, a computer storage device 
+used to read and write data on magnetic tapes.
+
+%The \textit{USCG cutter tampa heading angle} plant describes the heading angle dynamics of a Coast 
+%Guard cutter. The \textit{satellite attitude control system} plant describes the dynamics of a satellite 
+%attitude, {\it i.e.}, the orientation angles. An attitude control system must maintain the desired 
+%orientation of a satellite with respect to an 
+%inertial frame during all the excursion.
+
 %Here, these benchmarks are used to evaluate the proposed control 
@@
 %to be considered.
-
-There are two \textit{continuous stirred tank reactor} models that describe the PH dynamics of a neutralization 
-reaction of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and the temperature of a 
-exothermic reaction~\cite{astrom2006advanced} in a continuous flow stirred-tank reactor. The \textit{bioreactor} 
-benchmark is a linear model identified by least squares for the cell mass concentration controlled through dilution 
-rate of a bioreactor~\cite{bioreactor}. The \textit{steam drum} benchmark describes the linear model for the 
-level dynamics of a  boiler steam drum~\cite{boiler}.
-The \textit{flexible beam} is a plant employed in vibration studies; the physical system consists of a flexible 
-metallic structure with piezoceramic actuators and sensors.
-The \textit{helicopter longitudinal motion} plant describes the dynamics of 
-transitional motion with respect to a longitudinal plane and the 
-rotational motion around the longitudinal axis.
-The \textit{USCG cutter tampa heading angle} plant describes the heading angle 
-dynamics of a Coast Guard cutter. 
-The \textit{voltage regulator} plant consists of a linear model of a synchronous 
-machine connected to an  infinite bus~\cite{KOKOTOVIC198023}.
-
-The \textit{guidance control system} plant is another high-order system 
-model used by Chen et al.~\cite{CHEN1979389}  to evaluate reduction 
-techniques, which is used to determine the path of an autonomous vehicle movement.
-The \textit{satellite attitude control system} plant describes the dynamics of a satellite attitude, 
-{\it i.e.}, the orientation angles. An attitude control system must 
-maintain the desired orientation of a satellite with respect to an 
-inertial frame during all the excursion. 
-The \textit{springer-mass damper system} plant is classic model for several mechanical 
-systems dynamics. This benchmark describes a mass, which is fixed to a node by means 
-of a springer and moves under the action of a input force, damping, and elastic force.
 

### 2018-04-29 SYNT_abstract/abstract.tex
abstract for synt

\documentclass[submission]{eptcs}
\providecommand{\event}{SYNT 2018} % Name of the event you are submitting to
\usepackage{breakurl}             % Not needed if you use pdflatex only.
\usepackage{underscore}           % Only needed if you use pdflatex.

\title{Safe Formal Synthesis of Digital Controllers\\
for Continuous Plants}
%\author{Elizabeth Polgreen
%\institute{NICTA\\ Sydney, Australia}
%\institute{School of Computer Science and Engineering\\
%University of New South Wales\thanks{A fine university.}\\
%Sydney, Australia}
%\email{rvg@cs.stanford.edu}
%\and
%Co Author \qquad\qquad Yet S. Else
%\institute{Stanford Univeristy\\
%California, USA}
%\email{\quad is@gmail.com \quad\qquad somebody@else.org}
%}
\def\titlerunning{Synthesis of Digital Controllers}
\def\authorrunning{R.J. van Glabbeek, C. Author \& Y.S. Else}
\begin{document}
\maketitle

\begin{abstract}
We present a sound and automated approach to synthesizing safe,
digital controllers for physical plants represented as linear,
time-invariant models. The synthesis
accounts for errors caused by the digitization effects introduced by
digital controllers operating in either fixed-point or floating-point arithmetic. 
Our approach uses counterexample-guided inductive
synthesis (CEGIS): an inductive generalisation phase produces a
possible solution that is safe for some possible initial conditions but may
not be safe for all initial conditions. Safety for all initial conditions
is then verified either
via BMC or abstract acceleration; if the verification step fails, a
counterexample is provided to the inductive generalisation and the
process iterates until a safe controller is obtained.  We demonstrate
the practical value of this approach by automatically synthesizing
safe controllers for physical plant models from the digital control
literature.
\end{abstract}

\section{Introduction}

Embedded control systems using fixed and floating-point arithmetic 
have become widespread
as the availability of low-cost devices that can perform highly
non-trivial control tasks has increased. Correct synthesis of
control software for such platforms is non-trivial due to the digital representation of continuous variables
that is used by the controller. This digital representation introduces 
errors due to finite-precision arithmetic, time discretization and 
A/D and D/A conversion.

%
Given an LTI model, we present two automated approaches for generating
correct-by-construction digital controllers that address all these
challenges and satisfy a safety property given for the system. Both approaches make use of CounterExample-Guided
Inductive Synthesis (CEGIS)~\cite{jha-icse10,
  DBLP:conf/asplos/Solar-LezamaTBSS06}.  CEGIS is an
iterative process, where each iteration performs inductive
generalisation based on counterexamples provided by a verification
oracle. The inductive generalisation uses information
about a limited number of inputs to compute a candidate solution
for all the possible. Our two instantiations of CEGIS are
described next.

\emph{The first approach} starts by devising a
digital controller that stabilizes the system while remaining safe for a
pre-selected time horizon and a single initial state; then, it verifies
unbounded safety by unfolding the dynamics of the system, considering the
full hyper-cube of initial states, and checking a \emph{completeness
threshold}~\cite{DBLP:conf/vmcai/KroeningS03}, i.e., the number of
iterations required to sufficiently unwind the closed-loop state-space
system such that the boundaries are not violated for any larger number of
iterations.  As~it requires unfolding up to the completeness threshold, this
approach can be computationally expensive if the completeness threshold is large.

\emph{The second approach}
employs \emph{abstract acceleration}~\cite{cattaruzza2015unbounded} to
evaluate all possible progressions of the system simultaneously. 
This approach uses \emph{abstraction refinement},
enabling us to always start with a very simple description regardless of the
dynamics complexity, and only expand to more complex models
when a solution cannot be found.

We provide experimental results showing that both our approaches are able to
efficiently synthesize safe controllers for a set of intricate physical
plant models taken from the digital control literature.

\bibliographystyle{eptcs}       
\bibliography{../automatica/paper}  
\end{document}

### 2018-04-29 SYNT_abstract/abstract.tex
abstract

@@
 
-\title{Safe Formal Synthesis of Digital Controllers\\
+\title{Safe, Automated and Formal Synthesis of Digital Controllers 
 for Continuous Plants}
@@
 %}
-\def\titlerunning{Synthesis of Digital Controllers}
-\def\authorrunning{R.J. van Glabbeek, C. Author \& Y.S. Else}
+%\def\titlerunning{Synthesis of Digital Controllers}
+%\def\authorrunning{R.J. van Glabbeek, C. Author \& Y.S. Else}
 \begin{document}
@@
 is then verified either
-via BMC or abstract acceleration; if the verification step fails, a
+via bounded model checking or abstract acceleration; if the verification step fails, a
 counterexample is provided to the inductive generalisation and the
@@
 non-trivial control tasks has increased. Correct synthesis of
-control software for such platforms is non-trivial due to the digital representation of continuous variables
+control software for such platforms is non-trivial due to the digital representation of continuous quantities 
 that is used by the controller. This digital representation introduces 
 errors due to finite-precision arithmetic, time discretization and 
-A/D and D/A conversion.
+A/D - D/A conversions.
 
 %
-Given an LTI model, we present two automated approaches for generating
+Given an LTI model of a physical (continuous) plant, we present two automated approaches for generating
 correct-by-construction digital controllers that address all these
-challenges and satisfy a safety property given for the system. Both approaches make use of CounterExample-Guided
+challenges and satisfy a safety property for the physical plant. 
+Both approaches make use of CounterExample-Guided
 Inductive Synthesis (CEGIS)~\cite{jha-icse10,
@@
 iterative process, where each iteration performs inductive
-generalisation based on counterexamples provided by a verification
-oracle. The inductive generalisation uses information
+generalisation based on counterexamples provided by a verification module. 
+The inductive generalisation step uses information 
 about a limited number of inputs to compute a candidate solution
-for all the possible. Our two instantiations of CEGIS are
+for all the possible inputs. Our two instantiations of CEGIS are
 described next.
@@
 \emph{The first approach} starts by devising a
-digital controller that stabilizes the system while remaining safe for a
+digital controller that stabilizes the system's model, while remaining safe for a
 pre-selected time horizon and a single initial state; then, it verifies
-unbounded safety by unfolding the dynamics of the system, considering the
-full hyper-cube of initial states, and checking a \emph{completeness
+unbounded-time safety by unfolding the dynamics of the LTI model, considering the
+full set of initial states, and checking a \emph{completeness
 threshold}~\cite{DBLP:conf/vmcai/KroeningS03}, i.e., the number of
 iterations required to sufficiently unwind the closed-loop state-space
-system such that the boundaries are not violated for any larger number of
+model such that the boundaries are not violated for any larger number of
 iterations.  As~it requires unfolding up to the completeness threshold, this
@@
 employs \emph{abstract acceleration}~\cite{cattaruzza2015unbounded} to
-evaluate all possible progressions of the system simultaneously. 
+evaluate all possible progressions of the LTI model simultaneously. 
 This approach uses \emph{abstraction refinement},

### 2018-04-30 automatica/paper.tex
updated description related to the number of benchmarks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-Our benchmark suite consists of 18 SISO models extracted from the 
+Our benchmark suite consists of 27 SISO models extracted from the 
 control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal};
-these models are discretized with different sample times, leading to $167$ different benchmarks
+these models are discretized with different sample times, leading to $191$ different benchmarks
 to evaluate our proposal approach.

### 2018-04-30 automatica/paper.tex
fixed typos in the description of the benchmarks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 these models are discretized with different sample times, leading to $191$ different benchmarks
-to evaluate our proposal approach.
+to evaluate the Na\"ive (Multi-staged) and Abstraction-based CEGIS approaches.
 
@@
 feedback linearization~\cite{acrobot}.The \textit{antenna} benchmark 
-describes the dynamics of the dynamics of the azimuth angle of an antenna 
-motion system composed a gearbox, DC motor and amplifiers~\cite{gajic2008optimal}. 
+describes the dynamics of the azimuth angle of an antenna 
+motion system composed by a gearbox, DC motor and amplifiers~\cite{gajic2008optimal}. 
 The \textit{ballmaglev} plant corresponds to the discrete model of a simple 
@@
 There are two continuous stirred tank reactor models named \textit{cstr} and 
-\textit{cstrtmp} that describe the PH dynamics of a neutralization reaction 
+\textit{cstrtmp}, which describe the PH dynamics of a neutralization reaction 
 of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
@@
 are models for the cart position and the pendulum angle of an inverted pendulum 
-plant composed by a point mass must be equilibrated above the pivot point, which is 
+plant composed by a point mass, which must be equilibrated above the pivot point and is 
 mounted on an one degree of freedom cart that moves over a track through a DC motor.
@@
 machine connected to an infinite bus~\cite{KOKOTOVIC198023}. The 
-\textit{springer-mass damper system} plant is classic model for several mechanical 
+\textit{springer-mass damper system} plant is a classic model for several mechanical 
 systems dynamics. This benchmark describes a mass, which is fixed to a node by means 
-of a springer and moves under the action of a input force, damping, and elastic force.
+of a springer and moves under the action of an input force, damping, and elastic force.
 The \textit{steam drum} benchmark describes the linear model for the level dynamics 
@@
 which connects the car to one of its wheels.  The \textit{tapedriver} benchmark
-corresponds to the model of computer tape driver, \textit{i.e.}, a computer storage device 
+corresponds to the model of a computer tape driver, \textit{i.e.}, a computer storage device 
 used to read and write data on magnetic tapes.

### 2018-04-30 automatica/paper.tex
added identification to the benchmarks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-Our benchmark suite consists of 27 SISO models extracted from the 
+Our benchmark suite consists of 26 SISO models extracted from the 
 control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal};
@@
 
-The \textit{acrobot} plant corresponds to the model of a two-link 
+The \textit{acrobot} (\#1) plant corresponds to the model of a two-link 
 underactuated robot manipulator, named acrobot, linearized by partial 
-feedback linearization~\cite{acrobot}.The \textit{antenna} benchmark 
+feedback linearization~\cite{acrobot}.The \textit{antenna} benchmark (\#2) 
 describes the dynamics of the azimuth angle of an antenna 
 motion system composed by a gearbox, DC motor and amplifiers~\cite{gajic2008optimal}. 
-The \textit{ballmaglev} plant corresponds to the discrete model of a simple 
+The \textit{ballmaglev} (\#3) plant corresponds to the discrete model of a simple 
 eletromagnet-ball system, where a steel ball is levitated in air by the action 
 of an electromagnetic force generated by an electromagnet~\cite{Franklin15}. 
-The \textit{bioreactor} benchmark is a linear model identified by least squares 
+The \textit{bioreactor} benchmark (\#4) is a linear model identified by least squares 
 for the cell mass concentration controlled through dilution rate of a 
@@
 
-The \textit{Chen\_ex1}, \textit{Chen\_ex2} and \textit{Chen\_ex3} benchmarks 
-correspond to high-order control system discrete models generally used as 
+The \textit{Chen\_ex1}, \textit{Chen\_ex2}, \textit{Chen\_ex3} and \textit{Chen\_ex4} 
+benchmarks (\#5-8) correspond to high-order control system discrete models generally used as 
 case study for model order reduction techniques~\cite{CHEN1979389}. The benchmarks 
-\textit{Cruise}~\cite{Franklin15} and \textit{CruiseHSCC}~\cite{Astrom08} are 
+\textit{Cruise}~\cite{Franklin15} (\#9) and \textit{CruiseHSCC}~\cite{Astrom08} (\#10) are 
 automotive cruise control models. Automotive cruise control is used to keep 
@@
 
-There are two continuous stirred tank reactor models named \textit{cstr} and 
-\textit{cstrtmp}, which describe the PH dynamics of a neutralization reaction 
+There are two continuous stirred tank reactor models named \textit{cstr} (\#11) and 
+\textit{cstrtmp} (\#12), which describe the PH dynamics of a neutralization reaction 
 of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
 the temperature of a exothermic reaction~\cite{astrom2006advanced} in a continuous 
-flow stirred-tank reactor. The \textit{DC motor} plant describes the velocity 
+flow stirred-tank reactor. The \textit{DC motor} plant (\#13) describes the velocity 
 dynamics of a basic brushed direct current electrical machine.
 
-The \textit{Flexbeam} benchmark is a plant employed in vibration studies; the 
+The \textit{Flexbeam} benchmark (\#14) is a plant employed in vibration studies; the 
 physical  system consists of a flexible metallic structure with piezoceramic 
-actuators and sensors. The \textit{guidance chen} benchmark is another 
+actuators and sensors. The \textit{guidance chen} benchmark (\#15) is another 
 high-order system model used by Chen et al.~\cite{CHEN1979389}  to evaluate 
@@
 which is used to determine the path of an autonomous vehicle movement. The 
-\textit{helicopter} benchmark plant describes the dynamics of transitional motion 
+\textit{helicopter} benchmark plant (\#16) describes the dynamics of transitional motion 
 with respect to a longitudinal plane and the rotational motion around the longitudinal 
@@
 
-The \textit{Invpendulum\_cartpos} and \textit{Invpendulum\_pendang} benchmarks
+The benchmarks \textit{Invpendulum\_cartpos} (\#17) and \textit{Invpendulum\_pendang} (\#18)
 are models for the cart position and the pendulum angle of an inverted pendulum 
@@
 
-The \textit{magpointer} corresponds to a magnetic pointer plant composed by a pointer 
+The \textit{magpointer} (\#19) corresponds to a magnetic pointer plant composed by a pointer 
 employed in analogue gauges and indicators, whose angular position dynamics is 
-controlled by a magnetic field. The \textit{magsuspension} describes the dynamic of
-a magnetic car suspension system. The \textit{pendulum} plant consists of a swinging 
+controlled by a magnetic field. The \textit{magsuspension} describes (\#20) the dynamic of
+a magnetic car suspension system. The \textit{pendulum} (\#21) plant consists of a swinging 
 point mass suspended from a frictionless pivot by means of a negligible mass rod.
 
-The \textit{Regulator} plant consists of a linear model of a synchronous electrical
+The \textit{Regulator} (\#22) plant consists of a linear model of a synchronous electrical
 machine connected to an infinite bus~\cite{KOKOTOVIC198023}. The 
-\textit{springer-mass damper system} plant is a classic model for several mechanical 
+\textit{springer-mass damper system} plant (\#23) is a classic model for several mechanical 
 systems dynamics. This benchmark describes a mass, which is fixed to a node by means 
 of a springer and moves under the action of an input force, damping, and elastic force.
-The \textit{steam drum} benchmark describes the linear model for the level dynamics 
+The \textit{steam drum} benchmark (\#24) describes the linear model for the level dynamics 
 of a  boiler steam drum~\cite{boiler}.
 
-The \textit{suspension} benchmark corresponds to the model of a single wheel suspension 
+The \textit{suspension} (\#25) benchmark corresponds to the model of a single wheel suspension 
 system of a car, {\it i.e.}, the relative motion dynamics of a mass springer damp model, 
-which connects the car to one of its wheels.  The \textit{tapedriver} benchmark
+which connects the car to one of its wheels.  The \textit{tapedriver} benchmark (\#26)
 corresponds to the model of a computer tape driver, \textit{i.e.}, a computer storage device 
@@
 10 & CruiseHSCC & 1 & 16,8 & 6587ms & 16,10 & 6567ms &  & & &\\
-12 & Cstr & 1 & &  & & & & & &\\
-13 & Cstrtmp  & 1 &   &  & & & & & &\\
-14 & DCmotor   & 2 & 16,8  & 6879ms & 16,10 & 7786ms & & & &\\
-15 & Flexbeam   & 6 &   &  & & & & & &\\
-16 & Guidance chen  & 5 &   &  & & & & & &\\
-17 & Helicopter   & 3 & 16,8 & 13728ms & 32,23 & 148012ms & & & &\\
-18 & Invpendulum\_cartpos & 4 &   &  & & & & & &\\
-19 & Invpendulum\_pendang & 2 & 24,12 & 9741ms & 16,10 & 28135ms & & & &\\
-20 & Magpointer   & 2 & 16,8 & 10093ms & 16,10 & 20407ms & & & &\\
-21 & Magsuspension  & 2 & 12,12  &22146ms  & 16,10 & 34808ms & & & &\\
-22 & Pendulum   & 2 & 16,8 & 8503ms & 32,23 & 23987ms & & & &\\
-23 & Regulator   & 5 &   &  & & & & & &\\
-24 & Springmassdamper & 2 &   &  & & & & & &\\
-25 & streamdrum   & 3 & 16,8  & 332422ms & 16,10 & 590501ms & & & &\\
-26 & Suspension  & 4 & 16,8  & 17206ms & 16,10 &1372945ms & & & &\\
-27 & Tapedriver   & 3 & 16,8  & 8188ms & & & & & &\\
+11 & Cstr & 1 & &  & & & & & &\\
+12 & Cstrtmp  & 1 &   &  & & & & & &\\
+13 & DCmotor   & 2 & 16,8  & 6879ms & 16,10 & 7786ms & & & &\\
+14 & Flexbeam   & 6 &   &  & & & & & &\\
+15 & Guidance chen  & 5 &   &  & & & & & &\\
+16 & Helicopter   & 3 & 16,8 & 13728ms & 32,23 & 148012ms & & & &\\
+17 & Invpendulum\_cartpos & 4 &   &  & & & & & &\\
+18 & Invpendulum\_pendang & 2 & 24,12 & 9741ms & 16,10 & 28135ms & & & &\\
+19 & Magpointer   & 2 & 16,8 & 10093ms & 16,10 & 20407ms & & & &\\
+20 & Magsuspension  & 2 & 12,12  &22146ms  & 16,10 & 34808ms & & & &\\
+21 & Pendulum   & 2 & 16,8 & 8503ms & 32,23 & 23987ms & & & &\\
+22 & Regulator   & 5 &   &  & & & & & &\\
+23 & Springmassdamper & 2 &   &  & & & & & &\\
+24 & streamdrum   & 3 & 16,8  & 332422ms & 16,10 & 590501ms & & & &\\
+25 & Suspension  & 4 & 16,8  & 17206ms & 16,10 &1372945ms & & & &\\
+26 & Tapedriver   & 3 & 16,8  & 8188ms & & & & & &\\
 \hline

### 2018-04-30 SYNT_abstract/abstract.tex
small wording

@@
 Our approach uses counterexample-guided inductive
-synthesis (CEGIS): an inductive generalisation phase produces a
+synthesis (CEGIS): in the first phase an inductive generalisation engine produces a
 possible solution that is safe for some possible initial conditions but may
 not be safe for all initial conditions. Safety for all initial conditions
-is then verified either
+is then verified in a second phase either
 via bounded model checking or abstract acceleration; if the verification step fails, a

### 2018-04-30 SYNT_abstract/abstract.tex
+ cite CAV'17
added description about DSSynth
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 accounts for errors caused by the digitization effects introduced by
-digital controllers operating in either fixed-point or floating-point arithmetic. 
+digital controllers operating in either fixed- or floating-point arithmetic. 
 Our approach uses counterexample-guided inductive
@@
 counterexample is provided to the inductive generalisation and the
-process iterates until a safe controller is obtained.  We demonstrate
-the practical value of this approach by automatically synthesizing
-safe controllers for physical plant models from the digital control
-literature.
+process iterates until a safe controller is obtained.  We implemented our approach
+in a tool named DSSynth (Digital-System Synthesizer) and demonstrate
+its practical value by automatically synthesizing safe controllers for physical 
+plant models from the digital control literature.
 \end{abstract}
@@
 approach can be computationally expensive if the completeness threshold is large.
-
+%
 \emph{The second approach}
@@
 
+This abstract contains material published in \cite{DBLP:conf/kbse/AbateBCCCDKKP17,DBLP:conf/cav/AbateBCCDKKP17}.
+
 \bibliographystyle{eptcs}       

### 2018-05-01 SYNT_abstract/abstract.tex
shortening to 1 page & adding authors

@@
 for Continuous Plants}
-%\author{Elizabeth Polgreen
-%\institute{NICTA\\ Sydney, Australia}
+
+\author{Alessandro Abate
+\institute{University of Oxford}
+\and
+Iury Bessa
+\institute{Federal University of \\Amazonas, Brazil}
+\and
+Dario Cattaruzza
+\institute{University of Oxford}
+\and
+Lucas Cordeiro
+\institute{University of Oxford}
+\and
+Cristina David
+\institute{University of Cambridge}
+\and
+Pascal Kesseli
+\institute{University of Oxford}
+\and
+Daniel Kroening
+\institute{University of Oxford}
+\and
+Elizabeth Polgreen
+\institute{University of Oxford}
+}
+
 %\institute{School of Computer Science and Engineering\\
@@
 %}
-%\def\titlerunning{Synthesis of Digital Controllers}
-%\def\authorrunning{R.J. van Glabbeek, C. Author \& Y.S. Else}
+\def\titlerunning{Synthesis of Digital Controllers}
+\def\authorrunning{Abate et al.}
 \begin{document}
@@
 control software for such platforms is non-trivial due to the digital representation of continuous quantities 
-that is used by the controller. This digital representation introduces 
+used by the controller. This representation introduces 
 errors due to finite-precision arithmetic, time discretization and 
-A/D - D/A conversions.
-
-%
-Given an LTI model of a physical (continuous) plant, we present two automated approaches for generating
+A/D - D/A conversions. Given an LTI model of a physical (continuous) plant, we present two automated approaches for generating
 correct-by-construction digital controllers that address all these
@@
 generalisation based on counterexamples provided by a verification module. 
-The inductive generalisation step uses information 
-about a limited number of inputs to compute a candidate solution
-for all the possible inputs. Our two instantiations of CEGIS are
+%The inductive generalisation step uses information 
+%about a limited number of inputs to compute a candidate solution
+%for all the possible inputs. 
+Our two instantiations of CEGIS are
 described next.
@@
 unbounded-time safety by unfolding the dynamics of the LTI model, considering the
-full set of initial states, and checking a \emph{completeness
-threshold}~\cite{DBLP:conf/vmcai/KroeningS03}, i.e., the number of
-iterations required to sufficiently unwind the closed-loop state-space
-model such that the boundaries are not violated for any larger number of
-iterations.  As~it requires unfolding up to the completeness threshold, this
-approach can be computationally expensive if the completeness threshold is large.
+full set of initial states, and checking a completeness
+threshold~\cite{DBLP:conf/vmcai/KroeningS03}.%, i.e., the number of
+%iterations required to sufficiently unwind the closed-loop state-space
+%model such that the boundaries are not violated for any larger number of
+%iterations.  %As~it requires unfolding up to the completeness threshold, this
+%approach can be computationally expensive if the completeness threshold is large.
 %
@@
 This approach uses \emph{abstraction refinement},
-enabling us to always start with a very simple description regardless of the
+enabling us to start with a simple description regardless of the
 dynamics complexity, and only expand to more complex models
@@
 We provide experimental results showing that both our approaches are able to
-efficiently synthesize safe controllers for a set of intricate physical
-plant models taken from the digital control literature.
+synthesize safe controllers for a set of physical
+plant models taken from digital control literature.
 

### 2018-05-04 automatica/paper.tex
Updated Axelerator results

@@
 %\item 
-$R_2: (−1)^N S(−1) > 0$;
+$R_2: (-1)^N S(-1) > 0$;
 %\item 
@@
 3  & Ballmaglev  & 3 &  &   &  &  & & & &\\
-4  & Bioreact & 3 & 16,8 & 11200ms & 16,10 &14600ms & & & &\\
-5  & Chen\_ex1& 3 & 16,8 & 7278ms  & 16,10 & 9196ms & & & &\\
+4  & Bioreact & 3 & 16,8 & 11200ms & 16,10 &14600ms & 24,14 & 425ms& 16,10 & 502ms\\
+5  & Chen\_ex1& 3 & 16,8 & 7278ms  & 16,10 & 9196ms & & & 16,10 & 1398ms\\
 6  & Chen\_ex2 & 8& & & 32,23 & 4683872ms &  & & &\\
@@
 8  & Chen\_ex4 & 9 &  & & & & & & &\\
-9  & Cruise    & 1 & 16,8 & 6563ms & 16,10 & 6543ms &  & & &\\
-10 & CruiseHSCC & 1 & 16,8 & 6587ms & 16,10 & 6567ms &  & & &\\
+9  & Cruise    & 1 & 16,8 & 6563ms & 16,10 & 6543ms & 24,14 & 295ms& 16,10 & 306ms\\
+10 & CruiseHSCC & 1 & 16,8 & 6587ms & 16,10 & 6567ms &  24,14 &293ms& 16,10 & 313ms\\
 11 & Cstr & 1 & &  & & & & & &\\
-12 & Cstrtmp  & 1 &   &  & & & & & &\\
-13 & DCmotor   & 2 & 16,8  & 6879ms & 16,10 & 7786ms & & & &\\
-14 & Flexbeam   & 6 &   &  & & & & & &\\
+12 & Cstrtmp  & 1 &   &  & & & 24,14 &478ms& &\\
+13 & DCmotor   & 2 & 16,8  & 6879ms & 16,10 & 7786ms & 24,14 & 435ms& 16,10 & 520ms\\
+14 & Flexbeam   & 6 &   &  & & & 24,14 &72079ms& &\\
 15 & Guidance chen  & 5 &   &  & & & & & &\\
-16 & Helicopter   & 3 & 16,8 & 13728ms & 32,23 & 148012ms & & & &\\
+16 & Helicopter   & 3 & 16,8 & 13728ms & 32,23 & 148012ms & 24,14 & 727ms& 16,10 &1075ms\\
 17 & Invpendulum\_cartpos & 4 &   &  & & & & & &\\
-18 & Invpendulum\_pendang & 2 & 24,12 & 9741ms & 16,10 & 28135ms & & & &\\
-19 & Magpointer   & 2 & 16,8 & 10093ms & 16,10 & 20407ms & & & &\\
-20 & Magsuspension  & 2 & 12,12  &22146ms  & 16,10 & 34808ms & & & &\\
-21 & Pendulum   & 2 & 16,8 & 8503ms & 32,23 & 23987ms & & & &\\
+18 & Invpendulum\_pendang & 2 & 24,12 & 9741ms & 16,10 & 28135ms & 24,14 & 432ms& 16,10 &466ms\\
+19 & Magpointer   & 2 & 16,8 & 10093ms & 16,10 & 20407ms & 24,14  & 916ms& 16,10 &1244ms\\
+20 & Magsuspension  & 2 & 12,12  &22146ms  & 16,10 & 34808ms & 24,14 & 443ms & 16,10 &569ms\\
+21 & Pendulum   & 2 & 16,8 & 8503ms & 32,23 & 23987ms & 24,14 & 395ms& 16,10 &473ms\\
 22 & Regulator   & 5 &   &  & & & & & &\\
 23 & Springmassdamper & 2 &   &  & & & & & &\\
-24 & streamdrum   & 3 & 16,8  & 332422ms & 16,10 & 590501ms & & & &\\
-25 & Suspension  & 4 & 16,8  & 17206ms & 16,10 &1372945ms & & & &\\
-26 & Tapedriver   & 3 & 16,8  & 8188ms & & & & & &\\
+24 & streamdrum   & 3 & 16,8  & 332422ms & 16,10 & 590501ms & 24,14 & 701ms& 16,10 &1225ms\\
+25 & Suspension  & 4 & 16,8  & 17206ms & 16,10 &1372945ms & 56,30 & 15268ms& 16,10 &4374ms\\
+26 & Tapedriver   & 3 & 16,8  & 8188ms & & & 64,22 & 2026ms& 16,10 &1090ms\\
 \hline

### 2018-05-08 automatica/paper.tex
sections 2-3

@@
 \textbf{Discretization Effects --}
-The classical approach to control synthesis has often disregarded
-digitalization effects, whereas more recently modern techniques have focused
-on different aspects of discretization, including delayed
-response~\cite{Duggirala2015} and finite word length (FWL) semantics, with
-the goal either to verify~\cite{daes20161} or to
-optimize~\cite{oudjida2014design} given implementations.
+Classical work in control synthesis has often disregarded digitalization effects, 
+\note{[this paragraph needs more work:]
+whereas recent results in digital control have focused on separate aspects of discretization, 
+including delayed response~\cite{Duggirala2015} and finite word length (FWL) semantics, 
+with the goal either to verify~\cite{daes20161} or to optimize~\cite{oudjida2014design} given implementations. }
 
 There are two different problems that arise from FWL semantics.  The first
-is the error in the dynamics caused by the inability to represent the exact
+is the error in the model dynamics caused by the inability to represent the exact
 state of the physical system, while the second relates to rounding and
-saturation errors during computation.  In~\cite{fialho1994stability}, a
-stability measure based on the error of the digital dynamics ensures that
-the deviation introduced by FWL does not make the digital system unstable. 
-A~more recent approach~\cite{DBLP:journals/automatica/WuLCC09} uses
-$\mu$-calculus to directly model the digital controller so that the selected
-parameters are stable by design.  The analyses
-in~\cite{DBLP:conf/hybrid/RouxJG15, DBLP:conf/hybrid/WangGRJF16} rely on an
-invariant computation on the discrete system dynamics using Semi-Definite
-Programming (SDP).  While the former uses bounded-input and bounded-output
+saturation errors during model manipulation.  
+In~\cite{fialho1994stability}, a stability measure based on the error of the digital dynamics ensures that
+the deviation introduced by FWL does not lead to instability.  
+\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$-calculus to directly model the digital controller so that selected
+parameters result by design in stable dynamics.  
+The analyses in~\cite{DBLP:conf/hybrid/RouxJG15, DBLP:conf/hybrid/WangGRJF16} rely on an
+invariant computation on the discrete dynamics using Semi-Definite
+Programming (SDP):  while the former contribution uses bounded-input and bounded-output
 (BIBO) properties to determine stability, the latter uses Lyapunov-based
 quadratic invariants.  In both cases, the SDP solver uses floating-point
-arithmetic and soundness is checked by bounding the error.  An alternative
-is~\cite{park2016scalable}, where the verification of given control code is
+arithmetic and soundness is checked by bounding the error.  
+An alternative is~\cite{park2016scalable}, where the verification of given control code is
 performed against a known model by extracting an LTI model of the code by
 symbolic execution: to account for rounding errors, an upper bound is
-introduced in the verification phase.  The work
-in~\cite{picasso2003stabilization} introduces invariant sets as a mechanism to
-bound the quantization error effect on stabilization as an invariant set
-that always converges toward the controllable set.  Similarly,
-\cite{liberzon2003hybrid} evaluates the quantization error dynamics and
-bounds its trajectory to a known region over a finite time period.  This
-technique works for both linear and non-linear systems.
+introduced in the verification phase.  
+The work in~\cite{picasso2003stabilization} introduces invariant sets as a mechanism to
+bound the quantization error effect on stabilization.  
+% as an invariant set that always converges toward the controllable set.  
+Similarly, 
+\cite{liberzon2003hybrid} evaluates the quantization error dynamics and \note{[unclear] bounds its trajectory to a known region over a finite time period}.   
+%This technique works for both linear and non-linear systems.
 
@@
 
-Equation~\eqref{eq:ode1} is soundly discretized in time~\cite{middleton1990digital,van1978computing} at constant time intervals,
+Equation~\eqref{eq:ode1} is 
+%soundly 
+discretized in time~\cite{middleton1990digital,van1978computing} at constant time intervals,
 of duration $T_s$ (the sample time), 
@@
 $\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$, 
-and where $k \in \mathbb N$ is a discrete counter and $\vec{x}_{0}=\vec{x}(0)$ denotes the initial state.
+$k \in \mathbb N$ is a discrete counter and where $\vec{x}_{0}=\vec{x}(0)$ denotes the initial state.
 
 Models \eqref{eq:ode1} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t)$ and  $u_k$, respectively. 
-Feedback architectures can be employed to manipulate the properties and behaviors of the plant.   
-We are interested in the synthesis of digital feedback control algorithms, 
+Feedback architectures can be employed to manipulate the properties and behaviors of the plant:    
+we are interested in the synthesis of digital feedback controllers $u_k$,  
 as practically implemented on Field-Programmable Gate Arrays or Digital Signal Processors. 
-Later, we will address the issue of variable quantization, 
+\note{next: why only this single issue, rather than all discretisation effects as presented earlier?} Later, we will address the issue of variable quantization, 
 introduced by ADC/DAC conversion blocks of Figure \ref{fig:digitalsystem}, 
@@
 
-We account for the presence of errors originating from a number of sources, shown in Figure~\ref{}:
+\note{back end vs back-end?}
+
+We account for the presence of errors originating from a number of sources, shown in Figure~\ref{} \note{fix}:
 \begin{itemize}
-\item We represent the plant variables $x(t)$ and $u(t)$, which are real numbers, at a finite precision in our model, and so it is necessary to account for the errors introduced by this representation.
-We account for these errors in both back ends by using interval arithmetic, detailed in section~\ref{}.
-\item The quantisation errors by the ADC, which converts the analogue signal $x(t)$ into
-the digital signal $x_k$ which is fed into the controller. We account for this error in 
-the acceleration based back-end by introducing a noise signal $\nu_1$ that over-approximates this error, 
-shown in the figure. Further details are found in section~\ref{}. 
-In the naive back end we use bit-precise modelling in CBMC~\cite{} to accurately model this deterministic
-conversion.
-In other words, CBMC constructs a boolean formula which explicitly unwinds the transition system for any symbolically represented input state, bounded by the initial conditions, and performs the ADC conversion precisely on that symbolically represented input state.
-When we verify safety, the boolean formula is satisfied only if there is an input state value for which the subsequent trace through the transition system eventually violates the safety property.
-\item The representation errors due to performing finite-precision arithmetic in the controller. 
-In the acceleration based back-end, this is again treated by the introduction of noise that bounds the error.
-The naive back end uses the bit-precise modelling of finite-precision arithmetic in CBMC, in the same way as we handled the ADC conversion. We assume that the controller
-represents numbers to the same precision as the ADC.
-\item We assume that the DAC converts numbers from the same precision as the controller to an analogue signal. 
-As a result we can ignore any errors introduced by the DAC
+\item We represent the plant variables $x(t)$ and $u(t)$, which are continuous quantities, with finite precision in our model. 
+It is necessary to account for the errors introduced by this representation: 
+we account for these errors in both back ends \note{did we explain the two back ends already?} by using interval arithmetic, as detailed in section~\ref{} \note{fix}. 
+\item The quantisation errors by the ADC, which converts the analogue signal $x(t)$ into the digital signal $x_k$, 
+which is then fed into the controller \note{cf. Figure~\ref{} }. 
+We account for this error in the acceleration-based back-end by introducing a noise signal $\nu_1$ that over-approximates it. Further details are found in section~\ref{}.  
+In the naive back-end we use bit-precise modelling in \note{[clear? discussed before?] CBMC}~\cite{} to accurately encompass this conversion.   
+In other words, CBMC constructs a boolean formula that explicitly unwinds the transition system for any \note{[unclear] symbolically represented} input state, 
+\note{[unclear how the initial conditions bound the input state? use formulas or figure to explain.] bounded by the initial conditions}, 
+and performs the ADC conversion precisely on that symbolically represented input state. 
+When we check for a safety property, 
+the boolean formula is satisfied only if there is an input state value for which the subsequent trace through the transition system eventually violates the safety property.  
+\item The representation errors due to performing finite-precision arithmetic in the controller block. 
+In the acceleration-based back-end, 
+this is again treated by the introduction of a noise signal that bounds the error. 
+The naive back-end uses the bit-precise modelling of finite-precision arithmetic in CBMC, 
+in the same way as we handled the ADC conversion. 
+We assume that the controller represents numbers to the same precision as the ADC \note{why is this legit?}. 
+\item We assume \note{why is this reasonable?} that the DAC converts numbers to analogue signals with the same precision as the controller. 
+As a result we can ignore any additional errors introduced by the DAC.  
 \end{itemize}

### 2018-05-08 automatica/paper.tex
changed affiliation
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \author[oxford]{Dario Cattaruzza}\ead{dario.cattaruzza@cs.ox.ac.uk},
-\author[oxford,manaus]{Lucas Cordeiro}\ead{lucas.cordeiro@cs.ox.ac.uk},
+\author[manchester]{Lucas Cordeiro}\ead{lucas.cordeiro@manchester.ac.uk},
 \author[cambridge]{Cristina David}\ead{cd652@cam.ac.uk},
@@
 \address[cambridge]{University of Cambridge, UK}
+\address[manchester]{University of Manchester, UK}
 \address[manaus]{Federal University of Amazonas, Brazil}
@@
 \begin{keyword}                           % Five to ten keywords,  
-Digital control synthesis; Safety requirements; A/D converters; Quantization errors; Sampling.               % chosen from the IFAC 
+Digital control synthesis; Safety requirements; Analog/Digital conversion; Quantization errors; Sampling.               % chosen from the IFAC 
 \end{keyword}                             % keyword list or with the 
@@
 non-trivial control tasks, with significant impact in numerous
-application areas such as life sciences, environmental control and
-robotics~\cite{astrom1997computer, Franklin15}.  Correct synthesis of
-control software for such platforms is non-trivial, even in cases with
-restricted dynamics.
+application areas such as the life sciences, high-precision control, 
+automotive and robotics~\cite{astrom1997computer, Franklin15}.  
+Provably correct synthesis of control software for such platforms is non-trivial, 
+even in cases with unsophisticated dynamics.
 
@@
 However, the use of digital control architectures adds new challenges
-caused by artifacts specific to digital control, such as the effects
+caused by artefacts specific to digital control, such as the effects
 of finite-precision arithmetic, time discretization and quantization
@@
 correct-by-construction digital controllers that addresses all these
-challenges. Specifically, we synthesize stable and safe,
-software-implemented embedded controllers.  Due to the complexity of
-such closed-loop systems, we focus on linear models with known
-configurations, and perform parametric synthesis of controllers.
+challenges. Specifically, we automatically synthesize stable and safe,
+software-implemented embedded controllers.  
+%Due to the complexity of
+%such closed-loop systems, we focus on linear models with known
+%configurations, and perform parametric synthesis of controllers.
 %meeting a number of properties that define their desired behavior.
@@
 
-Our work addresses challenging aspects of the control synthesis
-problem.  We perform digital control synthesis over a hybrid model,
-where the plant exhibits continuous behavior whereas the controller
-operates in discrete time and over a quantized domain.  In particular,
-our model evaluates the effects of the quantizers (A/D and D/A
+Our work addresses challenging aspects of the control synthesis problem:  
+we perform digital control synthesis over a ``hybrid model'',
+namely a model encompassing a plant exhibiting continuous behavior, 
+whereas the controller operates in discrete time and over a quantized domain.  
+In particular, our model evaluates the effects of the quantizers (A/D and D/A
 converters) and of time discretization, as well as representation
-errors introduced by modeling %% artifacts such as an
+errors introduced by working  %% artifacts such as an
 %% observer~\cite{astrom1997computer}
-in a finite precision domain, while reasoning about high level
-properties such as stability, robustness, and safety, which define the
-behaviour of the system.  Notably, safety requirements are
-frequently overlooked in conventional feedback control synthesis, but
-play an important role in systems engineering.
+in a finite-precision domain. 
+We reason about high level properties such as stability, robustness, and safety, which define the
+behaviour of the whole model.  
+Notably, safety requirements are frequently overlooked in conventional feedback control synthesis, but
+play a key role in systems engineering, particularly in safety-critical applications.
 

### 2018-05-08 automatica/paper.tex
sections 2-3
changed time scale
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 3  & Ballmaglev  & 3 &  &   &  &  & & & &\\
-4  & Bioreact & 3 & 16,8 & 11200ms & 16,10 &14600ms & 24,14 & 425ms& 16,10 & 502ms\\
-5  & Chen\_ex1& 3 & 16,8 & 7278ms  & 16,10 & 9196ms & & & 16,10 & 1398ms\\
-6  & Chen\_ex2 & 8& & & 32,23 & 4683872ms &  & & &\\
+4  & Bioreact & 3 & 16,8 & 11.2\,s & 16,10 &14.6\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
+5  & Chen\_ex1& 3 & 16,8 & 7.2\,s  & 16,10 & 9.2\,s & & & 16,10 & 1.4\,s\\
+6  & Chen\_ex2 & 8& & & 32,23 & 4683.8\,s &  & & &\\
 7  & Chen\_ex3 & 7 &   & & & & & & &\\
 8  & Chen\_ex4 & 9 &  & & & & & & &\\
-9  & Cruise    & 1 & 16,8 & 6563ms & 16,10 & 6543ms & 24,14 & 295ms& 16,10 & 306ms\\
-10 & CruiseHSCC & 1 & 16,8 & 6587ms & 16,10 & 6567ms &  24,14 &293ms& 16,10 & 313ms\\
+9  & Cruise    & 1 & 16,8 & 6.6\,s & 16,10 & 6.5\,s & 24,14 & 0.3\,s& 16,10 & 0.3\,s\\
+10 & CruiseHSCC & 1 & 16,8 & 6.6\,s & 16,10 & 6.6\,s &  24,14 & 0.3\,s & 16,10 & 0.3\,s \\
 11 & Cstr & 1 & &  & & & & & &\\
-12 & Cstrtmp  & 1 &   &  & & & 24,14 &478ms& &\\
-13 & DCmotor   & 2 & 16,8  & 6879ms & 16,10 & 7786ms & 24,14 & 435ms& 16,10 & 520ms\\
-14 & Flexbeam   & 6 &   &  & & & 24,14 &72079ms& &\\
+12 & Cstrtmp  & 1 &   &  & & & 24,14 & 0.5\,s & &\\
+13 & DCmotor   & 2 & 16,8  & 6.9\,s & 16,10 & 7.8\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s \\
+14 & Flexbeam   & 6 &   &  & & & 24,14 & 72.1\,s & &\\
 15 & Guidance chen  & 5 &   &  & & & & & &\\
-16 & Helicopter   & 3 & 16,8 & 13728ms & 32,23 & 148012ms & 24,14 & 727ms& 16,10 &1075ms\\
+16 & Helicopter   & 3 & 16,8 & 13.8\,s & 32,23 & 148\,s & 24,14 & 0.8\,s& 16,10 & 1.1\,s\\
 17 & Invpendulum\_cartpos & 4 &   &  & & & & & &\\
-18 & Invpendulum\_pendang & 2 & 24,12 & 9741ms & 16,10 & 28135ms & 24,14 & 432ms& 16,10 &466ms\\
-19 & Magpointer   & 2 & 16,8 & 10093ms & 16,10 & 20407ms & 24,14  & 916ms& 16,10 &1244ms\\
-20 & Magsuspension  & 2 & 12,12  &22146ms  & 16,10 & 34808ms & 24,14 & 443ms & 16,10 &569ms\\
-21 & Pendulum   & 2 & 16,8 & 8503ms & 32,23 & 23987ms & 24,14 & 395ms& 16,10 &473ms\\
+18 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 16,10 & 28.2\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
+19 & Magpointer   & 2 & 16,8 & 10.1\,s & 16,10 & 20.4\,s & 24,14  & 1\,s& 16,10 & 1.3\,s\\
+20 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 34.8\,s & 24,14 & 0.5\,s & 16,10 & 0.6\,s\\
+21 & Pendulum   & 2 & 16,8 & 8.5\,s & 32,23 & 24\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
 22 & Regulator   & 5 &   &  & & & & & &\\
 23 & Springmassdamper & 2 &   &  & & & & & &\\
-24 & streamdrum   & 3 & 16,8  & 332422ms & 16,10 & 590501ms & 24,14 & 701ms& 16,10 &1225ms\\
-25 & Suspension  & 4 & 16,8  & 17206ms & 16,10 &1372945ms & 56,30 & 15268ms& 16,10 &4374ms\\
-26 & Tapedriver   & 3 & 16,8  & 8188ms & & & 64,22 & 2026ms& 16,10 &1090ms\\
+24 & streamdrum   & 3 & 16,8  & 332.5\,s & 16,10 & 590.5\,s & 24,14 & 0.7\,s & 16,10 &1.3\,s\\
+25 & Suspension  & 4 & 16,8  & 17.2\,s & 16,10 &1373\,s & 56,30 & 15.3\,s & 16,10 & 4.4\,s\\
+26 & Tapedriver   & 3 & 16,8  & 8.2\,s & & & 64,22 & 2.1\,s & 16,10 & 1.1\,s\\
 \hline

### 2018-05-08 automatica/paper.tex
sections 2-3

--- 2018-05-08 automatica/paper.tex
@@
 \author[oxford]{Dario Cattaruzza}\ead{dario.cattaruzza@cs.ox.ac.uk},
-\author[manchester]{Lucas Cordeiro}\ead{lucas.cordeiro@manchester.ac.uk},
+\author[oxford,manaus]{Lucas Cordeiro}\ead{lucas.cordeiro@cs.ox.ac.uk},
 \author[cambridge]{Cristina David}\ead{cd652@cam.ac.uk},
@@
 \address[cambridge]{University of Cambridge, UK}
-\address[manchester]{University of Manchester, UK}
 \address[manaus]{Federal University of Amazonas, Brazil}
@@
 In this paper we present two novel approaches for the synthesis of
-digital controllers, both of which make use of CounterExample-Guided
+digital controllers, both of which make use of the framework known as CounterExample-Guided
 Inductive Synthesis (CEGIS)~\cite{jha-icse10,
-  DBLP:conf/asplos/Solar-LezamaTBSS06}, a technique
-that became very popular in the recent years.  CEGIS is an
-iterative process, where each iteration performs inductive
+  DBLP:conf/asplos/Solar-LezamaTBSS06}, 
+a technique from formal methods that has recently shown much promise and which we export in this work to a control-theoretical setup.  
+CEGIS is an iterative process, where each iteration performs inductive
 generalisation based on counterexamples provided by a verification
-oracle. Essentially, the inductive generalisation uses information
+oracle \note{see Figure xxx}. The inductive generalisation uses information 
 about a limited number of inputs to compute a candidate solution
-for all the possible. Our two instantiations of CEGIS are
-described next.
+for the entire range of possible inputs. Our two instantiations of CEGIS are described next.
 
@@
 \emph{The first approach} uses a na\"ive technique that starts by devising a
-digital controller that stabilizes the system while remaining safe for a
+digital controller that stabilizes the plant model while remaining safe for a
 pre-selected time horizon and a single initial state; then, it verifies
-unbounded safety by unfolding the dynamics of the system, considering the
-full hyper-cube of initial states, and checking a \emph{completeness
+unbounded-time safety by unfolding the model dynamics, considering the 
+full set of initial states, and checking a \emph{completeness
 threshold}~\cite{DBLP:conf/vmcai/KroeningS03}, i.e., the number of
 iterations required to sufficiently unwind the closed-loop state-space
-system such that the boundaries are not violated for any larger number of
-iterations.  As~it requires unfolding up to the completeness threshold, this
+model such that the safety boundaries are not violated for any larger number of
+iterations.  Requiring unfolding up to the completeness threshold, this
 approach is computationally expensive.
@@
 employs \emph{abstract acceleration}~\cite{cattaruzza2015unbounded} to
-evaluate all possible progressions of the system simultaneously. 
-Additionally, this approach uses \emph{abstraction refinement},
-enabling us to always start with a very simple description regardless of the
-dynamics complexity, and only expand to more complex models
+evaluate all possible progressions of the model simultaneously. 
+Additionally, this approach uses \emph{abstraction refinement} \note{add cit.},
+enabling one to start with a very simple (abstract) description of the model 
+regardless of the complexity of its dynamics, and to refine to more complex models only 
 when a solution cannot be found.

### 2018-05-08 automatica/paper.tex
added time out to Table 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

--- 2018-05-08 automatica/paper.tex
@@
 
+For the majority of our benchmarks, we observe that the abstraction-based
+back-end is faster than the basic multi-staged verification approach, and
+finds one solution more (9) than the multi-staged back-end (8).  In direct
+comparison, the abstraction-based approach is on average able to find a
+solution in approximately 70\% of the time required using the multi-staged
+back-end, and has a median run-time 1.4\,s, which is seven times smaller
+than the multi-staged approach.  The two back-ends complement each other in
+benchmark coverage and together solve all benchmarks in the set.  On average
+our engine spent 52\% in the synthesis and 48\% in the verification phase.
+
 \begin{table*}
@@
    &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
-1  & Acrobot  & 4 &   &  &  &  & & & &\\
-2  & Antenna  & 6 &   &  &  &  & & & &\\
-3  & Ballmaglev  & 3 &  &   &  &  & & & &\\
-4  & Bioreact & 3 & 16,8 & 11200ms & 16,10 &14600ms & 24,14 & 425ms& 16,10 & 502ms\\
-5  & Chen\_ex1& 3 & 16,8 & 7278ms  & 16,10 & 9196ms & & & 16,10 & 1398ms\\
-6  & Chen\_ex2 & 8& & & 32,23 & 4683872ms &  & & &\\
-7  & Chen\_ex3 & 7 &   & & & & & & &\\
-8  & Chen\_ex4 & 9 &  & & & & & & &\\
-9  & Cruise    & 1 & 16,8 & 6563ms & 16,10 & 6543ms & 24,14 & 295ms& 16,10 & 306ms\\
-10 & CruiseHSCC & 1 & 16,8 & 6587ms & 16,10 & 6567ms &  24,14 &293ms& 16,10 & 313ms\\
-11 & Cstr & 1 & &  & & & & & &\\
-12 & Cstrtmp  & 1 &   &  & & & 24,14 &478ms& &\\
-13 & DCmotor   & 2 & 16,8  & 6879ms & 16,10 & 7786ms & 24,14 & 435ms& 16,10 & 520ms\\
-14 & Flexbeam   & 6 &   &  & & & 24,14 &72079ms& &\\
-15 & Guidance chen  & 5 &   &  & & & & & &\\
-16 & Helicopter   & 3 & 16,8 & 13728ms & 32,23 & 148012ms & 24,14 & 727ms& 16,10 &1075ms\\
-17 & Invpendulum\_cartpos & 4 &   &  & & & & & &\\
-18 & Invpendulum\_pendang & 2 & 24,12 & 9741ms & 16,10 & 28135ms & 24,14 & 432ms& 16,10 &466ms\\
-19 & Magpointer   & 2 & 16,8 & 10093ms & 16,10 & 20407ms & 24,14  & 916ms& 16,10 &1244ms\\
-20 & Magsuspension  & 2 & 12,12  &22146ms  & 16,10 & 34808ms & 24,14 & 443ms & 16,10 &569ms\\
-21 & Pendulum   & 2 & 16,8 & 8503ms & 32,23 & 23987ms & 24,14 & 395ms& 16,10 &473ms\\
-22 & Regulator   & 5 &   &  & & & & & &\\
-23 & Springmassdamper & 2 &   &  & & & & & &\\
-24 & streamdrum   & 3 & 16,8  & 332422ms & 16,10 & 590501ms & 24,14 & 701ms& 16,10 &1225ms\\
-25 & Suspension  & 4 & 16,8  & 17206ms & 16,10 &1372945ms & 56,30 & 15268ms& 16,10 &4374ms\\
-26 & Tapedriver   & 3 & 16,8  & 8188ms & & & 64,22 & 2026ms& 16,10 &1090ms\\
+1  & Acrobot  & 4 &  & \xmark &  & ~\xmark & & ~\xmark &  & ~\xmark \\
+2  & Antenna  & 6 &  & ~\xmark &  & ~\xmark & & ~\xmark & & ~\xmark\\
+3  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark & & ~\xmark & & ~\xmark\\
+4  & Bioreact & 3 & 16,8 & 11.2\,s & 16,10 &14.6\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
+5  & Chen\_ex1& 3 & 16,8 & 7.2\,s  & 16,10 & 9.2\,s & & ~\xmark & 16,10 & 1.4\,s\\
+6  & Chen\_ex2 & 8& & ~\xmark & 32,23 & 4683.8\,s &  & ~\xmark & & ~\xmark\\
+7  & Chen\_ex3 & 7 &   & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+8  & Chen\_ex4 & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+9  & Cruise    & 1 & 16,8 & 6.6\,s & 16,10 & 6.5\,s & 24,14 & 0.3\,s& 16,10 & 0.3\,s\\
+10 & CruiseHSCC & 1 & 16,8 & 6.6\,s & 16,10 & 6.6\,s &  24,14 & 0.3\,s & 16,10 & 0.3\,s \\
+11 & Cstr & 1 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+12 & Cstrtmp  & 1 &  & ~\xmark & & ~\xmark & 24,14 & 0.5\,s & & ~\xmark\\
+13 & DCmotor   & 2 & 16,8  & 6.9\,s & 16,10 & 7.8\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s \\
+14 & Flexbeam   & 6 & & ~\xmark & & ~\xmark & 24,14 & 72.1\,s & & ~\xmark\\
+15 & Guidance chen  & 5 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+16 & Helicopter   & 3 & 16,8 & 13.8\,s & 32,23 & 148\,s & 24,14 & 0.8\,s& 16,10 & 1.1\,s\\
+17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+18 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 16,10 & 28.2\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
+19 & Magpointer   & 2 & 16,8 & 10.1\,s & 16,10 & 20.4\,s & 24,14  & 1\,s& 16,10 & 1.3\,s\\
+20 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 34.8\,s & 24,14 & 0.5\,s & 16,10 & 0.6\,s\\
+21 & Pendulum   & 2 & 16,8 & 8.5\,s & 32,23 & 24\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
+22 & Regulator   & 5 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+24 & streamdrum   & 3 & 16,8  & 332.5\,s & 16,10 & 590.5\,s & 24,14 & 0.7\,s & 16,10 &1.3\,s\\
+25 & Suspension  & 4 & 16,8  & 17.2\,s & 16,10 &1373\,s & 56,30 & 15.3\,s & 16,10 & 4.4\,s\\
+26 & Tapedriver   & 3 & 16,8  & 8.2\,s & & ~\xmark & 64,22 & 2.1\,s & 16,10 & 1.1\,s\\
 \hline

### 2018-05-08 automatica/paper.tex
described the fixed-point results
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-For the majority of our benchmarks, we observe that the abstraction-based
+We split our evaluation into two sets of results: fixed- and floating-point. 
+For the majority of the fixed-point benchmarks, we observe that the abstraction-based
 back-end is faster than the basic multi-staged verification approach, and
-finds one solution more (9) than the multi-staged back-end (8).  In direct
+finds one solution more (14) than the multi-staged back-end (13).  In direct
 comparison, the abstraction-based approach is on average able to find a
-solution in approximately 70\% of the time required using the multi-staged
-back-end, and has a median run-time 1.4\,s, which is seven times smaller
+solution in approximately 53\% of the time required using the multi-staged
+back-end, and has a median run-time 0.5\,s, which is twenty times smaller
 than the multi-staged approach.  The two back-ends complement each other in
-benchmark coverage and together solve all benchmarks in the set.  On average
-our engine spent 52\% in the synthesis and 48\% in the verification phase.
+benchmark coverage and together solve 58\% of the benchmarks.
 

### 2018-05-08 automatica/paper.tex
described the floating-point results
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\textcolor{red}{Lucas describe here the experimental results}
-
 We provide the results in Table~\ref{tab:results}.  Here 
@@
 benchmark coverage and together solve 58\% of the benchmarks.
+%
+For the majority of the floating-point benchmarks, we also observe that the abstraction-based
+back-end is much faster than the basic multi-staged verification approach, but both
+back-ends find the same amount of solutions (13).  In direct
+comparison, the abstraction-based approach is on average able to find a
+solution in approximately 50\% of the time required using the multi-staged
+back-end, and has a median run-time 0.6\,s, which is forty times smaller
+than the multi-staged approach.  The two back-ends complement each other in
+benchmark coverage and together solve 54\% of the benchmarks.
 

### 2018-05-08 automatica/paper.tex
sections 2-3

--- 2018-05-08 automatica/paper.tex
@@
 This paper is an extension of~\cite{DBLP:conf/cav/AbateBCCDKKP17}
-and makes the following contributions, where the fourth and the fifth are
-extensions over~\cite{DBLP:conf/cav/AbateBCCDKKP17}.
+and makes the following contributions (the fourth and the fifth are
+specific extensions over~\cite{DBLP:conf/cav/AbateBCCDKKP17}): 
 %
@@
 \item We automatically generate \emph{correct-by-construction} digital
-  controllers using an inductive synthesis approach.  Our application of program
-  synthesis is non-trivial and addresses challenges specific to control
-  systems, such as quantizers and FWL.  %% In particular, we
+  controllers using an inductive synthesis approach (CEGIS).  
+  This application is non-trivial and addresses challenges specific to digital control
+  systems, such as the presence of A/D quantizers and FWL operations.  %% In particular, we
   %% have found that a two-stage verification engine that continuously refines
@@
   %\item  We compute
-  The computed state-feedback controllers 
-  guarantee a given safety property alongside stability and safety
-  specifications. Existing methods for controller synthesis rely on transfer
-  function representations, which are inadequate to prove safety requirements.
-%
-\item We provide two novel algorithms: the first, na\"ive one, relies on
+  The automatically computed state-feedback controllers 
+  guarantee a given safety specification alongside a stability property. 
+  \note{[this statement is way too broad] Existing methods for controller synthesis rely on transfer 
+  function representations, which are inadequate to prove safety requirements. } 
+%
+\item We provide two novel algorithms: the first, a na\"ive approach, relies on 
   an unfolding of the dynamics up to a completeness threshold, while the
-  second one is abstraction-based and leverages abstraction refinement and
+  second one is abstraction-based and leverages abstraction/refinement and
   acceleration to improve scalability while retaining soundness.  %% A third
@@
 %
-\item We develop a model for different sources of quantization error and
-  their effect on reachability properties.  We give bounds that ensure the
-  safety of our controllers in a hybrid continuous-digital domain.
-
-\item While~\cite{DBLP:conf/cav/AbateBCCDKKP17} is restricted to systems
-  modeled in discrete time, in the current paper we present a model for
-  soundly evaluating reachability in a combined continuous-discrete time/space.
+\item We develop a model for different sources of quantization error and account for 
+  their effect on safety.  We give bounds that ensure the
+  safety of our controllers in a hybrid (i.e., continuous/digital) domain.
+
+\item While~\cite{DBLP:conf/cav/AbateBCCDKKP17} is restricted to models in discrete time, in the current paper we present an approach for
+  soundly evaluating safety in combined continuous-discrete time and space.
 
@@
   is its restriction to fixed-point arithmetic, meaning that fixed-point
-  numbers were employed for the representation of both the plant and the
+  numbers are employed for the representation of both the plant and the
   controller, as well as for the operations performed by each of them. 
   Conversely, in the current paper we also make use of floating-point
-  arithmetic and compare the two approaches.  Additionally, we enhance the
-  implementation with an SMT backend, allowing us to also use reals in order
+  arithmetic, and compare the two approaches.  Additionally, we enhance the
+  implementation with an SMT back-end, allowing us to also use reals in order
   to represent the states of the plant.
@@
 superoptimisation~\cite{DBLP:conf/iclp/BrainCVF06,
-  DBLP:conf/asplos/Massalin87}.  This approach uses an iterative
-process where each iteration performs inductive generalisation based
+  DBLP:conf/asplosss/Massalin87}.  
+\note{might be confusing that we relate the CEGAR architecture also to Abstract Acceleration?}   
+This approach uses an iterative
+process \note{cf. Fig. XX}, where each iteration performs inductive generalisation based
 on counterexamples provided by a verification oracle.  In the absence
@@
 Program synthesizers are an ideal fit for the synthesis of digital controllers, since
-the semantics of programs capture the effects of finite-precision arithmetic
-precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
+the semantics of programs precisely capture the effects of finite-precision arithmetic.  
+In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS 
 for the synthesis of switching controllers for stabilizing continuous-time
@@
 switching controllers with a guaranteed minimum dwell time in each mode. 
-However, both approaches are unsuitable for the kind of control we seek to
+However, both approaches are unsuitable for the kind of controllers that we seek to
 synthesize.
@@
 traces of the model, alongside the numerical soundness required by the
-effects of discretisation and finite-precision errors.  A~state-space model
+effects of discretisation and finite-precision errors.  
+\note{Next paragraph is naive for a control audience - amend} 
+A~state-space model
 has known advantages over the transfer function
@@
 more detail.  However, relying on state-space discretization \mbox{Pessoa}
-is likely to incur in scalability limitations.  Along this research line,
+is likely to incur in scalability limitations.  \note{Mention SCOTS?}
+Along this research line,
 \cite{Anta2010,liu16} studies the synthesis of digital controllers for
-continuous dynamics, and \cite{zamani2014} extends the approach to the
-recent setup of Network Control Systems.
-
-\textbf{Discretization Effects --}
+continuous dynamics, and \cite{zamani2014} extends the approach to the Network Control Systems setup.
+
+\textbf{Discretization Effects in Control Design --}
 Classical work in control synthesis has often disregarded digitalization effects, 
@@
 
-For the majority of our benchmarks, we observe that the abstraction-based
-back-end is faster than the basic multi-staged verification approach, and
-finds one solution more (9) than the multi-staged back-end (8).  In direct
-comparison, the abstraction-based approach is on average able to find a
-solution in approximately 70\% of the time required using the multi-staged
-back-end, and has a median run-time 1.4\,s, which is seven times smaller
-than the multi-staged approach.  The two back-ends complement each other in
-benchmark coverage and together solve all benchmarks in the set.  On average
-our engine spent 52\% in the synthesis and 48\% in the verification phase.
-
 \begin{table*}
@@
    &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
-1  & Acrobot  & 4 &  & \xmark &  & ~\xmark & & ~\xmark &  & ~\xmark \\
-2  & Antenna  & 6 &  & ~\xmark &  & ~\xmark & & ~\xmark & & ~\xmark\\
-3  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark & & ~\xmark & & ~\xmark\\
-4  & Bioreact & 3 & 16,8 & 11.2\,s & 16,10 &14.6\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
-5  & Chen\_ex1& 3 & 16,8 & 7.2\,s  & 16,10 & 9.2\,s & & ~\xmark & 16,10 & 1.4\,s\\
-6  & Chen\_ex2 & 8& & ~\xmark & 32,23 & 4683.8\,s &  & ~\xmark & & ~\xmark\\
-7  & Chen\_ex3 & 7 &   & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-8  & Chen\_ex4 & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-9  & Cruise    & 1 & 16,8 & 6.6\,s & 16,10 & 6.5\,s & 24,14 & 0.3\,s& 16,10 & 0.3\,s\\
-10 & CruiseHSCC & 1 & 16,8 & 6.6\,s & 16,10 & 6.6\,s &  24,14 & 0.3\,s & 16,10 & 0.3\,s \\
-11 & Cstr & 1 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-12 & Cstrtmp  & 1 &  & ~\xmark & & ~\xmark & 24,14 & 0.5\,s & & ~\xmark\\
-13 & DCmotor   & 2 & 16,8  & 6.9\,s & 16,10 & 7.8\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s \\
-14 & Flexbeam   & 6 & & ~\xmark & & ~\xmark & 24,14 & 72.1\,s & & ~\xmark\\
-15 & Guidance chen  & 5 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-16 & Helicopter   & 3 & 16,8 & 13.8\,s & 32,23 & 148\,s & 24,14 & 0.8\,s& 16,10 & 1.1\,s\\
-17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-18 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 16,10 & 28.2\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
-19 & Magpointer   & 2 & 16,8 & 10.1\,s & 16,10 & 20.4\,s & 24,14  & 1\,s& 16,10 & 1.3\,s\\
-20 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 34.8\,s & 24,14 & 0.5\,s & 16,10 & 0.6\,s\\
-21 & Pendulum   & 2 & 16,8 & 8.5\,s & 32,23 & 24\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
-22 & Regulator   & 5 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-24 & streamdrum   & 3 & 16,8  & 332.5\,s & 16,10 & 590.5\,s & 24,14 & 0.7\,s & 16,10 &1.3\,s\\
-25 & Suspension  & 4 & 16,8  & 17.2\,s & 16,10 &1373\,s & 56,30 & 15.3\,s & 16,10 & 4.4\,s\\
-26 & Tapedriver   & 3 & 16,8  & 8.2\,s & & ~\xmark & 64,22 & 2.1\,s & 16,10 & 1.1\,s\\
+1  & Acrobot  & 4 &   &  &  &  & & & &\\
+2  & Antenna  & 6 &   &  &  &  & & & &\\
+3  & Ballmaglev  & 3 &  &   &  &  & & & &\\
+4  & Bioreact & 3 & 16,8 & 11200ms & 16,10 &14600ms & 24,14 & 425ms& 16,10 & 502ms\\
+5  & Chen\_ex1& 3 & 16,8 & 7278ms  & 16,10 & 9196ms & & & 16,10 & 1398ms\\
+6  & Chen\_ex2 & 8& & & 32,23 & 4683872ms &  & & &\\
+7  & Chen\_ex3 & 7 &   & & & & & & &\\
+8  & Chen\_ex4 & 9 &  & & & & & & &\\
+9  & Cruise    & 1 & 16,8 & 6563ms & 16,10 & 6543ms & 24,14 & 295ms& 16,10 & 306ms\\
+10 & CruiseHSCC & 1 & 16,8 & 6587ms & 16,10 & 6567ms &  24,14 &293ms& 16,10 & 313ms\\
+11 & Cstr & 1 & &  & & & & & &\\
+12 & Cstrtmp  & 1 &   &  & & & 24,14 &478ms& &\\
+13 & DCmotor   & 2 & 16,8  & 6879ms & 16,10 & 7786ms & 24,14 & 435ms& 16,10 & 520ms\\
+14 & Flexbeam   & 6 &   &  & & & 24,14 &72079ms& &\\
+15 & Guidance chen  & 5 &   &  & & & & & &\\
+16 & Helicopter   & 3 & 16,8 & 13728ms & 32,23 & 148012ms & 24,14 & 727ms& 16,10 &1075ms\\
+17 & Invpendulum\_cartpos & 4 &   &  & & & & & &\\
+18 & Invpendulum\_pendang & 2 & 24,12 & 9741ms & 16,10 & 28135ms & 24,14 & 432ms& 16,10 &466ms\\
+19 & Magpointer   & 2 & 16,8 & 10093ms & 16,10 & 20407ms & 24,14  & 916ms& 16,10 &1244ms\\
+20 & Magsuspension  & 2 & 12,12  &22146ms  & 16,10 & 34808ms & 24,14 & 443ms & 16,10 &569ms\\
+21 & Pendulum   & 2 & 16,8 & 8503ms & 32,23 & 23987ms & 24,14 & 395ms& 16,10 &473ms\\
+22 & Regulator   & 5 &   &  & & & & & &\\
+23 & Springmassdamper & 2 &   &  & & & & & &\\
+24 & streamdrum   & 3 & 16,8  & 332422ms & 16,10 & 590501ms & 24,14 & 701ms& 16,10 &1225ms\\
+25 & Suspension  & 4 & 16,8  & 17206ms & 16,10 &1372945ms & 56,30 & 15268ms& 16,10 &4374ms\\
+26 & Tapedriver   & 3 & 16,8  & 8188ms & & & 64,22 & 2026ms& 16,10 &1090ms\\
 \hline

### 2018-05-08 automatica/paper.tex

@@
 
+We split our evaluation into two sets of results: fixed- and floating-point. 
+For the majority of the fixed-point benchmarks, we observe that the abstraction-based
+back-end is faster than the basic multi-staged verification approach, and
+finds one solution more (14) than the multi-staged back-end (13).  In direct
+comparison, the abstraction-based approach is on average able to find a
+solution in approximately 53\% of the time required using the multi-staged
+back-end, and has a median run-time 0.5\,s, which is twenty times smaller
+than the multi-staged approach.  The two back-ends complement each other in
+benchmark coverage and together solve 58\% of the benchmarks.
+%
+For the majority of the floating-point benchmarks, we also observe that the abstraction-based
+back-end is much faster than the basic multi-staged verification approach, but both
+back-ends find the same amount of solutions (13).  In direct
+comparison, the abstraction-based approach is on average able to find a
+solution in approximately 50\% of the time required using the multi-staged
+back-end, and has a median run-time 0.6\,s, which is forty times smaller
+than the multi-staged approach.  The two back-ends complement each other in
+benchmark coverage and together solve 54\% of the benchmarks.
+
 \begin{table*}

### 2018-05-08 automatica/paper.tex
described Threats to validity section
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
+The median run-time for our benchmark set is 6.6\,s for fixed-point and 5.45\,s for floating-point. 
+We consider these times short enough to be of practical use to control engineers, and thus affirm EG1.
+
+There are a few instances for which the system fails to find a controller. 
+For the na\"ive approach, the completeness threshold may be too large, thus
+causing a timeout.  On the other hand, the abstraction-based approach may
+require a very precise abstraction, resulting in too many refinements and,
+consequently, in a timeout.  Yet another source of incompleteness is the
+inability of the {\sc synthesize} phase to use a large enough precision for
+the plant model.
+
 %-------------------------------
@@
 
-\textcolor{red}{Lucas: describe here the threats to validity}
+\textit{Benchmark selection:} We report an assessment of both our approaches
+over a diverse set of real-world benchmarks.  Nevertheless, this set of
+benchmarks is limited within the scope of this paper and the performance may
+not generalize to other benchmarks.\\
+%
+\textit{Plant precision and discretization heuristics:} Our algorithm to
+select suitable FWL word widths to model the plant behavior 
+increases the precision by 8 bits at each step 
+in order to be compliant with the CBMC type API. 
+Similarly, for discretization, we run multiple discretizations for each
+benchmark and retain the fastest run.
+This works sufficiently well for our benchmarks, but
+performance may suffer in some cases, for example if the completeness
+threshold is high.\\
+%
+\textit{Abstraction on other properties:} The performance gain from abstract
+acceleration may not hold for more complex properties than safety, for
+instance ``eventually reach and always remain in a given safe set''.
 

### 2018-05-08 automatica/paper.tex
section 3

--- 2018-05-08 automatica/paper.tex
@@
 
-\title{Safe and Robust Formal Synthesis of Digital Controllers\\
+\title{Automated Formal Synthesis of Safe Digital Controllers\\
 for Continuous Plants}
@@
   DBLP:conf/asplos/Solar-LezamaTBSS06}, 
+  \note{we need to agree on how to spell out CEGIS}
 a technique from formal methods that has recently shown much promise and which we export in this work to a control-theoretical setup.  
@@
 }
- \caption{The CEGIS framework\label{fig:CEGIS}}
+ \caption{The CEGIS framework\label{fig:CEGIS} \note{can we fit this figure within one column, and place it close to Sec 3.3?}}
 \end{figure*}
@@
 In this section, we give a brief description of the CEGIS framework~\cite{jha-icse10,
-  DBLP:conf/asplos/Solar-LezamaTBSS06}, as illustrated in Figure~\ref{fig:CEGIS}.
+  DBLP:conf/asplos/Solar-LezamaTBSS06}, which is illustrated in Figure~\ref{fig:CEGIS}. 
+  CEGIS has been recently used for the automated synthesis of software programs, 
+  and its setup is naturally that of mathematical logic.
 
@@
 $a$ ranges over ground terms, 
-and $\phi$ is a quantifier-free formula. 
+and $\phi$ is a quantifier-free logical formula. 
 We~interpret the ground terms over some domain~$\mathcal{D}$. 
@@
 %-------------------------------
-\section{Formal specification of model properties} 
+\section{Formal specification of properties on a model} 
 \label{sec:specification}
@@
 
-While in the previous section we discussed the generic CEGIS
+While in the previous section we have discussed the generic CEGIS
 framework, in the rest of the paper we will explain how we adapt it to

### 2018-05-08 automatica/paper.tex
section 4

@@
 
-We recall a recently introduced technique called \emph{Abstract Acceleration}~\cite{JSS14,cattaruzza2015unbounded}, 
+We recall a technique called \emph{Abstract Acceleration}~\cite{JSS14,cattaruzza2015unbounded}, 
 which will be key in this work for abstraction-based synthesis.  
-%\note{This clashes with the model introduced above, with inputs - motivate why? I've added the motivation above by introducing the closed  loop}
-Given a model of an iterative program with dynamics
-%
-\begin{equation}
-\vec{x}_{k+1}=\mat{A_d}\vec{x}_k \text{ where } \vec{x}_k \in \mathbb{R}^p, \mat{A_d} \in \mathbb{R}^{p \times p} \text{ and } k \in \mathbb N_0,
-\end{equation}
-%
-we want to find all possible states visited over an infinite time horizon
-starting at an initial set $X_0$.  
+Abstract Acceleration allows one to perform reachability analysis of dynamical models, 
+and as such can be employed for safety verification. 
+% 
+Given an autonomous model of an iterative program with dynamics 
+%
+$\vec{x}_{k+1}=\mat{A_d}\vec{x}_k$, 
+where $\vec{x}_k \in \mathbb{R}^p$, $\mat{A_d} \in \mathbb{R}^{p \times p}$ and $k \in \mathbb N_0$, 
+%\end{equation}
+%
+we want to find all possible states visited over an infinite time horizon starting at a given initial set $X_0$.  
 This set is known as the \emph{reach tube} of the model: 
@@
 In order to attain this, 
-the problem statement is modified, by means of acceleration, into 
+the problem statement is modified 
+%, by means of acceleration, 
+into 
 %
 \begin{equation}
-\hat{X} = \{ \vec{x}_k=\mat{A_d}^k\vec{x}_0 \mid k \in N_0 \text{ and } \vec{x}_0 \in X_0 \}, 
+\hat{X} = \{ \vec{x}_k=\mat{A_d}^k\vec{x}_0: k \in N_0 \text{ and } \vec{x}_0 \in X_0 \}, 
 \end{equation}
 %
-and new model semantics and corresponding set are further defined as 
+and a new 
+%model semantics and corresponding 
+set $\hat{X}^\sharp$ is further defined as 
 %
@@
 where the newly introduced \emph{abstract reach tube} $\hat{X}^\sharp$ is an
-over-approximation of the reach tube of the model \cite{JSS14}.  
-\cite{cattaruzza2015unbounded} extends this to LTI models with inputs, 
-whereas we next extend the algorithm to continuous-time models, in view of the overall goal of this work. 
+over-approximation of the reach tube of the model: 
+\cite{JSS14} details algorithms to compute such set, 
+whereas \cite{cattaruzza2015unbounded} extends this to LTI models with inputs as in \note{Eqn. XX}.  
+In view of the overall goal of this work, 
+we extend the algorithm to continuous-time models.  
 % and  For this reason we must first look at the acceleration of continuous-time dynamics.
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Acceleration of continuous-time models}
-\label{sec:continuous_time_accel}
+%\subsubsection{Acceleration of continuous-time models}
+%\label{sec:continuous_time_accel}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 %\note{Unlike the CAV18 paper, these gain matrices have not been discussed yet. }
-However, in order to synthesize $\mat{K}$, 
-we must be able to ensure that given properties of the plant hold at any given point in time.  
+However, in order to synthesize a soundly safe controller, 
+% $\mat{K}$, 
+we must be able to ensure that the safety of the plant holds at any continuous point in time.  
 In order to do so, we accelerate the dynamics of the plant according to the continuous-time model
@@
 Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a
-linear function of $\vec{x}_0$ and $\vec{u}$ as shown below.
+linear function of initial state $\vec{x}_0$ and parametric input $\vec{u}$ as follows.
 

### 2018-05-08 automatica/paper.tex
section 4

@@
 The solution to the differential equation $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where
-$\forall t\geq 0.\,\vec{u}(t)=\vec{u}$, $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, and $\mat{S}$ are the generalized eigenvectors of $\mat{A}$,
+$\forall t\geq 0\,\vec{u}(t)=\vec{u}$, $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, and $\mat{S}$ are the generalized eigenvectors of $\mat{A}$,
 evaluated at time $T$ is
@@
 
-If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then 
-$$\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}})\mat{B}_d\vec{u}
-\text{ with } T \in \mathbb{R}_0^+$$
-where $\mat{A}_d^{\frac{T}{T_d}} =e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$,
-is the state of the system at time $t=T$. 
+If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, 
+then $\forall T \in \mathbb{R}_0^+$ 
+$$
+\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}})\mat{B}_d\vec{u}, 
+$$
+where $\mat{A}_d^{\frac{T}{T_d}} =e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$. 
+%is the state of the system at time $t=T$. 
 \end{lemma}

### 2018-05-08 automatica/paper.tex
section 4

@@
 
-If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, 
-then $\forall T \in \mathbb{R}_0^+$ 
+If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ \note{when could that not exist?} such that $A_d=e^{\mat{A} T_d}$, 
+then $\forall T \in \mathbb{R}_0^+$ we obtain the known expression 
 $$
@@
 
-The final case we analyze is that of hybrid-time models, where the plant
-dynamics evolve in continuous time while the feedback dynamics evolve in
-discrete time.  A~new input value is produced only at every sample time but
-implemented over the continuous-time plant dynamics.
+We analyze the case of hybrid-time models, 
+namely where the plant dynamics evolve in continuous time, 
+while the feedback dynamics evolve in discrete time.  
+A new input value is accepted by the plant only at sample times $T_s$. \note{Confusing $T_s$ vs $T_d$.} 
+%but implemented over the continuous-time plant dynamics.
 %

### 2018-05-08 automatica/paper.tex
section 4

@@
 %-------------------------------
- \subsubsection{Finding Abstract Supports for Continuous Dynamics}
+ \subsubsection{Abstract Supports for Continuous Dynamics}
  \label{sec:cont_aasup}
@@
 
-Just as the accelerated dynamics in equation \eqref{eq:feedback_sampled_cont} can be abstacted using \eqref{eq:aa_reachtube} (where $\bigcup_{k \in N_0} (\mat{A}_d-\mat{B}_d\mat{K}) ^k \subseteq \mathcal{A}$),
-we use the same principle on equation \eqref{eq:feedback_cont} to obtain 
+Just as the accelerated dynamics in Eqn.
+\eqref{eq:feedback_sampled_cont} can be abstracted using \eqref{eq:aa_reachtube} (where $\bigcup_{k \in N_0} (\mat{A}_d-\mat{B}_d\mat{K}) ^k \subseteq \mathcal{A}$),
+we use the same principle on Eqn. \eqref{eq:feedback_cont} to obtain 
 \begin{equation}\label{eq:aa_cont_amatrix}
@@
 
-We next describe how to obtain such a set. 
-Our overapproximation of the set is a polyhedron, which is defined by an
-intersection of hypeplanes. The smallest polyhedra that can be obtained are
-those whose faces touch the set, which they must do at a point tangential to
-the hyperplane. Rather than pick a set of directions and find such points, we
-will start from the points and find their tangents. Furthermore, to simplify the
-procedure, we will only look at two dimensional cuts of the space 
-(see~\cite{cattaruzza2015unbounded}). This means that for every point we
-choose is a vertex of the polyhedron.
+We next describe how to obtain an over-approximation of such a set. 
+This is defined as a polyhedron, expressed as an intersection of hyperplanes. 
+A tight polyhedron that can be obtained with faces (hyperplanes) that touch the set. 
+%, which they must do at a point tangential to the hyperplane. 
+Rather than pick \note{[concept undefined:] a set of directions} and find such points, 
+we will start from the points and find their tangents \note{there can be just a single tangent, or possibly multiple ones?}.  
+Furthermore, to simplify the procedure, 
+we will only look at \note{[qualitative:] two dimensional cuts of the space}  
+(see~\cite{cattaruzza2015unbounded}):  
+this means that for every point we choose is a vertex of the polyhedron \note{??}. 
 Finding out which side of the hyperplane corresponds to the inside of the
@@
 \textcolor{blue}{[This is just the math that calculates the tangents of x-y pairs given the progression of x and y. Given the above description,is it necessary to include it?]}
+\note{I would cut the next part, if possible.
+However, the explanation above is not clear.
+It seems like you're just finding a convex hull.
+You have not introduced the notion of directions.
+The paragraph above requires brand new thinking.
+}
 
@@
 %-------------------------------
-\section{CEGIS of digital controllers} 
+\section{Synthesis of digital controllers with CEGIS} 
 \label{sssec:cegisdig}
@@
 
-\textcolor{red}{[Elizabeth: please rewrite this]}
+\textcolor{red}{[We call this approach either naive or multi-stage. Let us pick a single attribute, which I recommend to be the latter (multi-stage). Naive is excessively debutant.]}
 

### 2018-05-08 automatica/paper.tex
section 4

@@
 %-------------------------------
-\subsection{Abstract acceleration of linear dynamics} 
+\subsection{Abstract acceleration of linear dynamics \note{Shall we move the material on AAccel to the Preliminaries?}} 
 \label{ssec:aa}
@@
 
-An overview of the algorithm for controller synthesis is given in
-Fig.~\ref{fig:CEGIS-precision-increment}.  One important observation is that
-we verify and synthesize a controller over $k$ time steps.  We~then compute
-a completeness threshold $\overline{k}$~\cite{DBLP:conf/vmcai/KroeningS03}
+An overview of the algorithm for controller synthesis is given in Fig.~\ref{fig:CEGIS-precision-increment}.  
+One important observation is that we verify and synthesize a controller over a finite number ($k$) of time steps.  
+We then compute a completeness threshold $\overline{k}$~\cite{DBLP:conf/vmcai/KroeningS03} 
 for this controller, and verify correctness for $\overline{k}$ time steps. 
-Essentially, $\overline{k}$ is the number of iterations required to
-sufficiently unwind the closed-loop state-space system, 
-which ensures that the boundaries are not violated for any other $k{>}\overline{k}$.
+As we will later argue, $\overline{k}$ is the number of iterations required to sufficiently unwind the closed-loop state-space model,  
+ensuring that the boundaries are not violated for any other $k{>}\overline{k}$.
 
@@
 
-Next, we describe the different phases in Fig.~\ref{fig:CEGIS-precision-increment}
-(blocks 1 to 4) in detail.
+Next, we describe in detail the different phases in Fig.~\ref{fig:CEGIS-precision-increment} (blocks 1 to 4).
 

### 2018-05-10 automatica/paper.tex
section 4
consensus on how to write counterexample guided inductive synthesis

@@
 In this paper we present two novel approaches for the synthesis of
-digital controllers, both of which make use of the framework known as CounterExample-Guided
-Inductive Synthesis (CEGIS)~\cite{jha-icse10,
+digital controllers, both of which make use of the framework known as counterexample guided
+inductive synthesis (CEGIS)~\cite{jha-icse10,
   DBLP:conf/asplos/Solar-LezamaTBSS06}, 
-  \note{we need to agree on how to spell out CEGIS}
   a technique from formal methods that has recently shown much promise and which we export in this work to a control-theoretical setup.  
@@
 particular CEGIS, which is a recent approach to inductive synthesis
-borrowing ideas from Counter-Example Guided Abstraction Refinement
+borrowing ideas from counterexample guided abstraction refinement
 (CEGAR)~\cite{DBLP:conf/cav/ClarkeGJLV00} and
@@
 %-------------------------------
-\subsection{Description of the benchmarks}
+\subsection{Description of the control benchmarks}
 \label{exp:benchmarks}

### 2018-05-10 automatica/paper.tex
typo

--- 2018-05-08 automatica/paper.tex
@@
 10 & CruiseHSCC & 1 & 16,8 & 6.6\,s & 16,10 & 6.6\,s &  24,14 & 0.3\,s & 16,10 & 0.3\,s \\
-11 & Cstr & 1 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-12 & Cstrtmp  & 1 &  & ~\xmark & & ~\xmark & 24,14 & 0.5\,s & & ~\xmark\\
+11 & Cstr & 3 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+12 & Cstrtmp  & 3 &  & ~\xmark & & ~\xmark & 24,14 & 0.5\,s & & ~\xmark\\
 13 & DCmotor   & 2 & 16,8  & 6.9\,s & 16,10 & 7.8\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s \\

### 2018-05-10 automatica/paper.tex
changes

@@
 
-\note{back end vs back-end?}
-
 We account for the presence of errors originating from a number of sources, shown in Figure~\ref{} \note{fix}:
@@
 It is necessary to account for the errors introduced by this representation: 
-we account for these errors in both back ends \note{did we explain the two back ends already?} by using interval arithmetic, as detailed in section~\ref{} \note{fix}. 
+we account for these errors in both approaches \note{did we explain the two back ends already?. Yes. In the introduction.} by using interval arithmetic, as detailed in section~\ref{} \note{fix}. 
 \item The quantisation errors by the ADC, which converts the analogue signal $x(t)$ into the digital signal $x_k$, 
@@
 We account for this error in the acceleration-based back-end by introducing a noise signal $\nu_1$ that over-approximates it. Further details are found in section~\ref{}.  
-In the naive back-end we use bit-precise modelling in \note{[clear? discussed before?] CBMC}~\cite{} to accurately encompass this conversion.   
-In other words, CBMC constructs a boolean formula that explicitly unwinds the transition system for any \note{[unclear] symbolically represented} input state, 
-\note{[unclear how the initial conditions bound the input state? use formulas or figure to explain.] bounded by the initial conditions}, 
-and performs the ADC conversion precisely on that symbolically represented input state. 
+In the multi-stage back-end we use bit-precise modelling in CBMC~\cite{}, a bounded model checker for C-programs, to accurately encompass this conversion.   
+In other words, CBMC constructs a boolean formula that explicitly unwinds the transition system for symbolically represented inital states. The 
+possible bounds that this symbolically represented initial state may take are restricted by upper and lower bounds as described in section~\label{ssec:safespecification}.
+The boolean formula constructed by CBMC models the ADC conversions precisely on the symbolically represented states at every time step. 
 When we check for a safety property, 
@@
 this is again treated by the introduction of a noise signal that bounds the error. 
-The naive back-end uses the bit-precise modelling of finite-precision arithmetic in CBMC, 
+The multi-stage back-end uses the bit-precise modelling of finite-precision arithmetic in CBMC, 
 in the same way as we handled the ADC conversion. 
-We assume that the controller represents numbers to the same precision as the ADC \note{why is this legit?}. 
-\item We assume \note{why is this reasonable?} that the DAC converts numbers to analogue signals with the same precision as the controller. 
-As a result we can ignore any additional errors introduced by the DAC.  
+We assume that the controller represents numbers at the same precision as the ADC. 
+\item We assume that the DAC converts numbers to analogue signals with the same precision as the controller, or to a greater precision. 
+As a result we can ignore any additional errors introduced by the DAC. This assumption and the previous assumption are reasonable
+assumptions based on the availability and cost of popular hardware. 
 \end{itemize}
@@
 %-------------------------------
-\subsection{Na\"ive approach} 
+\subsection{Multi-stage approach} 
 \label{sssec:naive}
 %-------------------------------
-
-\textcolor{red}{[We call this approach either naive or multi-stage. Let us pick a single attribute, which I recommend to be the latter (multi-stage). Naive is excessively debutant.]}
 
@@
 
-\textcolor{red}{[Dario: once Elizabeth has updated the description of the naive approach, can you update the following part, aligning it with hers?]}
+\textcolor{red}{[Dario: can you update the following part, aligning it with hers?]}
 
@@
 
-\textcolor{red}{Elizabeth: this section needs to be updated to describe floating-point arithmetics.}
-
 As discussed in section~\ref{sec:}, the models we consider have errors due to several sources; the numerical error introduced by the precision used to represent the plant, the error introduced by the ADC conversion, and the error introduced by the precision used to represent the controller.
@@
 In this section we describe how quantization errors can be modelled as noise.
-Note that this is only applicable to the acceleration back end, as the naive back end makes use of CBMC's bit-precise model checking capabilities to account for these deterministic errors.
+Note that this is only applicable to the acceleration back end, as the multi-stage back end makes use of CBMC's bit-precise model checking capabilities to account for these deterministic errors.
 
@@
 
-The entire implementation consists of $XXX$ and $XXX$ lines of C code in the naive and abstract
+The entire implementation consists of $XXX$ and $XXX$ lines of C code in the multi-stage and abstract
 accelerator back-ends, respectively, $XXXX$ lines of C code for utility functions such as interval, 

### 2018-05-10 automatica/paper.tex
revised contributions to address comment

--- 2018-05-10 automatica/paper.tex
@@
   controllers using an inductive synthesis approach (CEGIS).  
-  This application is non-trivial and addresses challenges specific to digital control
-  systems, such as the presence of A/D quantizers and FWL operations.  %% In particular, we
-  %% have found that a two-stage verification engine that continuously refines
-  %% the precision of the fixed-point representation of the plant yields a
-  %% speed-up of two orders of magnitude over a conventional one-stage
-  %% verification engine.
-%
-  %\item  We compute
-  The automatically computed state-feedback controllers 
-  guarantee a given safety specification alongside a stability property. 
-  \note{[this statement is way too broad] Existing methods for controller synthesis rely on transfer 
-  function representations, which are inadequate to prove safety requirements. } 
-%
+  %% This application is non-trivial and addresses challenges specific to digital control
+  %% systems, such as the presence of A/D quantizers and FWL operations.  
+  In addition a stability property, the automatically computed state-feedback
+  controllers must also guarantee a given safety specification.
+  The implication is that, as opposed to existing
+  methods for controller synthesis which rely on transfer function
+  representations, we must consider a state-space representation of
+  the physical system. Such a representation requires ensuring the
+  specification over actual traces of the model, alongside the
+  numerical soundness required by the effects of discretisation and
+  finite-precision errors.
+
+%%   \note{[this statement is way too broad] Existing methods for controller synthesis rely on transfer 
+%%   function representations, which are inadequate to prove safety requirements. } 
+%% %
 \item We provide two novel algorithms: the first, a na\"ive approach, relies on 

### 2018-05-10 automatica/paper.tex
removed redundant CEGIS description

@@
 generalisation based on counterexamples provided by a verification
-oracle \note{see Figure xxx}. The inductive generalisation uses information 
+oracle (see Section~\ref{ssec:cegis}). The inductive generalisation uses information 
 about a limited number of inputs to compute a candidate solution
@@
 for this problem have made substantial progress in recent years, in
-particular CEGIS, which is a recent approach to inductive synthesis
-borrowing ideas from counterexample guided abstraction refinement
-(CEGAR)~\cite{DBLP:conf/cav/ClarkeGJLV00} and
-superoptimisation~\cite{DBLP:conf/iclp/BrainCVF06,
-  DBLP:conf/asplosss/Massalin87}.  
-\note{might be confusing that we relate the CEGAR architecture also to Abstract Acceleration?}   
-This approach uses an iterative
-process \note{cf. Fig. XX}, where each iteration performs inductive generalisation based
-on counterexamples provided by a verification oracle.  In the absence
-of complete specifications, oracles are queried to distinguish between
-non-equivalent
-programs~\cite{jha-icse10,DBLP:conf/fmcad/AlurBJMRSSSTU13}.
+particular CEGIS, which is a recent approach to inductive synthesis.
+%% borrowing ideas from counterexample guided abstraction refinement
+%% (CEGAR)~\cite{DBLP:conf/cav/ClarkeGJLV00} and
+%% superoptimisation~\cite{DBLP:conf/iclp/BrainCVF06,
+%%   DBLP:conf/asplosss/Massalin87}.  
+%% \note{might be confusing that we relate the CEGAR architecture also to Abstract Acceleration?}   
+%% This approach uses an iterative
+%% process (see Section~\ref{ssec:cegis}), where each iteration performs inductive generalisation based
+%% on counterexamples provided by a verification oracle.  In the absence
+%% of complete specifications, oracles are queried to distinguish between
+%% non-equivalent
+%% programs~\cite{jha-icse10,DBLP:conf/fmcad/AlurBJMRSSSTU13}.
 

### 2018-05-10 automatica/paper.tex
changed the CEGIS figure to single column + moved figures around

@@
 %-------------------------------
-
-We consider models of physical plants expressed as ordinary differential
-equations, which we assume to be controllable~\cite{Astrom08}: 
-%
-\begin{align}
-\label{eq:ode1}
-\dot{x}(t) = \mat{A}\vec{x}(t)+ \mat{B} \vec{u}(t), 
-\end{align}
-%
-where 
-$\vec{x} \in \mathbb{R}^p$,  
-$\vec{u} \in \mathbb{R}^q$, 
-$\mat{A} \in \mathbb{R}^{p \times p}$, 
-$\mat{B} \in \mathbb{R}^{p \times q}$,
-and $t \in \mathbb R_0^+$ denotes continuous time. 
-%$\mat{A}$ and $\mat{B}$ are matrices that fully characterize the dynamics of the continuous plant,
-We denote with $x(0)$ the initial state of the model.
-
-Equation~\eqref{eq:ode1} is 
-%soundly 
-discretized in time~\cite{middleton1990digital,van1978computing} at constant time intervals,
-of duration $T_s$ (the sample time), 
-into the difference equation
-%
-\begin{align}
-\label{eq:plant}
-\vec{x}_{k+1} =& \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k, 
-\end{align} 
-where 
-$\mat{A}_d=e^{\mat{A}T_s}$ and 
-$\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$, 
-$k \in \mathbb N$ is a discrete counter and where $\vec{x}_{0}=\vec{x}(0)$ denotes the initial state.
-
-Models \eqref{eq:ode1} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t)$ and  $u_k$, respectively. 
-Feedback architectures can be employed to manipulate the properties and behaviors of the plant:    
-we are interested in the synthesis of digital feedback controllers $u_k$,  
-as practically implemented on Field-Programmable Gate Arrays or Digital Signal Processors. 
-\note{next: why only this single issue, rather than all discretisation effects as presented earlier?} Later, we will address the issue of variable quantization, 
-introduced by ADC/DAC conversion blocks of Figure \ref{fig:digitalsystem}, 
-as classically studied in \cite{astrom1997computer}.
-
-We consider state feedback control architectures, 
-where $u_k$ (notice we work with the discretized signal) is $u_k = r_{k} - K x_k$. 
-Here $K \in \mathbb{R}^{m \times n}$ is a state-feedback gain matrix, 
-and $r_{k}$ is a reference signal (again digital). 
-We will assume $r_k=0$, thus 
-$\vec{x}_{k+1}=(\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_k$.
-
-%-------------------------------
-\subsection{Errors}
-
-\note{back end vs back-end?}
-
-We account for the presence of errors originating from a number of sources, shown in Figure~\ref{} \note{fix}:
-\begin{itemize}
-\item We represent the plant variables $x(t)$ and $u(t)$, which are continuous quantities, with finite precision in our model. 
-It is necessary to account for the errors introduced by this representation: 
-we account for these errors in both back ends \note{did we explain the two back ends already?} by using interval arithmetic, as detailed in section~\ref{} \note{fix}. 
-\item The quantisation errors by the ADC, which converts the analogue signal $x(t)$ into the digital signal $x_k$, 
-which is then fed into the controller \note{cf. Figure~\ref{} }. 
-We account for this error in the acceleration-based back-end by introducing a noise signal $\nu_1$ that over-approximates it. Further details are found in section~\ref{}.  
-In the naive back-end we use bit-precise modelling in \note{[clear? discussed before?] CBMC}~\cite{} to accurately encompass this conversion.   
-In other words, CBMC constructs a boolean formula that explicitly unwinds the transition system for any \note{[unclear] symbolically represented} input state, 
-\note{[unclear how the initial conditions bound the input state? use formulas or figure to explain.] bounded by the initial conditions}, 
-and performs the ADC conversion precisely on that symbolically represented input state. 
-When we check for a safety property, 
-the boolean formula is satisfied only if there is an input state value for which the subsequent trace through the transition system eventually violates the safety property.  
-\item The representation errors due to performing finite-precision arithmetic in the controller block. 
-In the acceleration-based back-end, 
-this is again treated by the introduction of a noise signal that bounds the error. 
-The naive back-end uses the bit-precise modelling of finite-precision arithmetic in CBMC, 
-in the same way as we handled the ADC conversion. 
-We assume that the controller represents numbers to the same precision as the ADC \note{why is this legit?}. 
-\item We assume \note{why is this reasonable?} that the DAC converts numbers to analogue signals with the same precision as the controller. 
-As a result we can ignore any additional errors introduced by the DAC.  
-\end{itemize}
 
@@
 
+We consider models of physical plants expressed as ordinary differential
+equations, which we assume to be controllable~\cite{Astrom08}: 
+%
+\begin{align}
+\label{eq:ode1}
+\dot{x}(t) = \mat{A}\vec{x}(t)+ \mat{B} \vec{u}(t), 
+\end{align}
+%
+where 
+$\vec{x} \in \mathbb{R}^p$,  
+$\vec{u} \in \mathbb{R}^q$, 
+$\mat{A} \in \mathbb{R}^{p \times p}$, 
+$\mat{B} \in \mathbb{R}^{p \times q}$,
+and $t \in \mathbb R_0^+$ denotes continuous time. 
+%$\mat{A}$ and $\mat{B}$ are matrices that fully characterize the dynamics of the continuous plant,
+We denote with $x(0)$ the initial state of the model.
+
+Equation~\eqref{eq:ode1} is 
+%soundly 
+discretized in time~\cite{middleton1990digital,van1978computing} at constant time intervals,
+of duration $T_s$ (the sample time), 
+into the difference equation
+%
+\begin{align}
+\label{eq:plant}
+\vec{x}_{k+1} =& \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k, 
+\end{align} 
+where 
+$\mat{A}_d=e^{\mat{A}T_s}$ and 
+$\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$, 
+$k \in \mathbb N$ is a discrete counter and where $\vec{x}_{0}=\vec{x}(0)$ denotes the initial state.
+
+Models \eqref{eq:ode1} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t)$ and  $u_k$, respectively. 
+Feedback architectures can be employed to manipulate the properties and behaviors of the plant:    
+we are interested in the synthesis of digital feedback controllers $u_k$,  
+as practically implemented on Field-Programmable Gate Arrays or Digital Signal Processors. 
+\note{next: why only this single issue, rather than all discretisation effects as presented earlier?} Later, we will address the issue of variable quantization, 
+introduced by ADC/DAC conversion blocks of Figure \ref{fig:digitalsystem}, 
+as classically studied in \cite{astrom1997computer}.
+
+We consider state feedback control architectures, 
+where $u_k$ (notice we work with the discretized signal) is $u_k = r_{k} - K x_k$. 
+Here $K \in \mathbb{R}^{m \times n}$ is a state-feedback gain matrix, 
+and $r_{k}$ is a reference signal (again digital). 
+We will assume $r_k=0$, thus 
+$\vec{x}_{k+1}=(\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_k$.
+
+%-------------------------------
+\subsection{Errors}
+
+\note{back end vs back-end?}
+
+We account for the presence of errors originating from a number of sources, shown in Figure~\ref{} \note{fix}:
+\begin{itemize}
+\item We represent the plant variables $x(t)$ and $u(t)$, which are continuous quantities, with finite precision in our model. 
+It is necessary to account for the errors introduced by this representation: 
+we account for these errors in both back ends \note{did we explain the two back ends already?} by using interval arithmetic, as detailed in section~\ref{} \note{fix}. 
+\item The quantisation errors by the ADC, which converts the analogue signal $x(t)$ into the digital signal $x_k$, 
+which is then fed into the controller \note{cf. Figure~\ref{} }. 
+We account for this error in the acceleration-based back-end by introducing a noise signal $\nu_1$ that over-approximates it. Further details are found in section~\ref{}.  
+In the naive back-end we use bit-precise modelling in \note{[clear? discussed before?] CBMC}~\cite{} to accurately encompass this conversion.   
+In other words, CBMC constructs a boolean formula that explicitly unwinds the transition system for any \note{[unclear] symbolically represented} input state, 
+\note{[unclear how the initial conditions bound the input state? use formulas or figure to explain.] bounded by the initial conditions}, 
+and performs the ADC conversion precisely on that symbolically represented input state. 
+When we check for a safety property, 
+the boolean formula is satisfied only if there is an input state value for which the subsequent trace through the transition system eventually violates the safety property.  
+\item The representation errors due to performing finite-precision arithmetic in the controller block. 
+In the acceleration-based back-end, 
+this is again treated by the introduction of a noise signal that bounds the error. 
+The naive back-end uses the bit-precise modelling of finite-precision arithmetic in CBMC, 
+in the same way as we handled the ADC conversion. 
+We assume that the controller represents numbers to the same precision as the ADC \note{why is this legit?}. 
+\item We assume \note{why is this reasonable?} that the DAC converts numbers to analogue signals with the same precision as the controller. 
+As a result we can ignore any additional errors introduced by the DAC.  
+\end{itemize}
+
 %-------------------------------
@@
 
-\begin{figure*}
+\begin{figure}
 %\hspace{-2cm}
 \centering
-\resizebox{.57\textwidth}{!}{
+\resizebox{.48\textwidth}{!}{
  \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto,
@@
 },
-          row sep=1cm, column sep=3.5cm] {
+          row sep=1cm, column sep=2cm] {
    \node[fill=gray!20,minimum height=1cm] (synth) {{\sc Synthesize}};
@@
    \path
-   ([yshift=2em]synth.east) edge node[align=center] {Candidate solution} ([yshift=2em]verif.west)
-    ([yshift=-2em]verif.west) edge node[align=center] {Counterexample} ([yshift=-2em]synth.east)
+   ([yshift=2em]synth.east) edge node[align=center] {Candidate} ([yshift=2em]verif.west)
+    ([yshift=-2em]verif.west) edge node[align=center] {Counterex} ([yshift=-2em]synth.east)
     (verif) edge node {} (done);
@@
 }
- \caption{The CEGIS framework\label{fig:CEGIS} \note{can we fit this figure within one column, and place it close to Sec 3.3?}}
-\end{figure*}
+ \caption{The CEGIS framework\label{fig:CEGIS}}
+\end{figure}
 

### 2018-05-10 automatica/paper.tex
section 8

@@
 control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal};
-these models are discretized with different sample times, leading to $191$ different benchmarks
-to evaluate the Na\"ive (Multi-staged) and Abstraction-based CEGIS approaches.
+these models are discretized with different sampling times, 
+leading to $191$ different benchmarks to evaluate the Multi-staged and Abstraction-based CEGIS algorithms.
 
 The \textit{acrobot} (\#1) plant corresponds to the model of a two-link 
-underactuated robot manipulator, named acrobot, linearized by partial 
-feedback linearization~\cite{acrobot}.The \textit{antenna} benchmark (\#2) 
+underactuated robot manipulator, 
+%named acrobot, 
+linearized by partial feedback linearization~\cite{acrobot}.The \textit{antenna} benchmark (\#2) 
 describes the dynamics of the azimuth angle of an antenna 
-motion system composed by a gearbox, DC motor and amplifiers~\cite{gajic2008optimal}. 
-The \textit{ballmaglev} (\#3) plant corresponds to the discrete model of a simple 
-eletromagnet-ball system, where a steel ball is levitated in air by the action 
-of an electromagnetic force generated by an electromagnet~\cite{Franklin15}. 
-The \textit{bioreactor} benchmark (\#4) is a linear model identified by least squares 
-for the cell mass concentration controlled through dilution rate of a 
-bioreactor~\cite{bioreactor}.
+motion system composed by a gearbox, a DC motor and amplifiers~\cite{gajic2008optimal}. 
+The \textit{ballmaglev} (\#3) plant corresponds to the model of a simple 
+eletromagnet-ball system, where a steel ball can be levitated by the force generated by an electromagnet~\cite{Franklin15}.  
+The \textit{bioreactor} benchmark (\#4) is a linear model 
+%identified by least squares 
+of the cell mass concentration controlled through the dilution rate of a bioreactor~\cite{bioreactor}.
 
 The \textit{Chen\_ex1}, \textit{Chen\_ex2}, \textit{Chen\_ex3} and \textit{Chen\_ex4} 
-benchmarks (\#5-8) correspond to high-order control system discrete models generally used as 
-case study for model order reduction techniques~\cite{CHEN1979389}. The benchmarks 
-\textit{Cruise}~\cite{Franklin15} (\#9) and \textit{CruiseHSCC}~\cite{Astrom08} (\#10) are 
-automotive cruise control models. Automotive cruise control is used to keep 
-constant the speed of an automobile, tracking a desired speed reference, 
-compensating disturbances and uncertainties related to relief and terrain.
-
-There are two continuous stirred tank reactor models named \textit{cstr} (\#11) and 
-\textit{cstrtmp} (\#12), which describe the PH dynamics of a neutralization reaction 
+benchmarks (\#5-8) correspond to high-order control system 
+%discrete 
+models employed as case studies for model-order reduction techniques~\cite{CHEN1979389}. 
+The benchmarks \textit{Cruise}~\cite{Franklin15} (\#9) and \textit{CruiseHSCC}~\cite{Astrom08} (\#10) deal with 
+automotive cruise control models, where control is used to keep 
+constant the speed of an automobile, tracking a desired speed reference, and compensating disturbances and uncertainties. % related to relief and terrain.
+
+%There are two continuous stirred tank reactor models named 
+\textit{cstr} (\#11) and \textit{cstrtmp} (\#12) describe the PH dynamics of a neutralization reaction 
 of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 

### 2018-05-10 automatica/paper.tex
section 8

@@
 
-%-------------------------------
-\subsection{Description of the control benchmarks}
-\label{exp:benchmarks}
-%-------------------------------
-
-%\textcolor{red}{Iury: can you please describe the benchmarks?}
-
 Our benchmark suite consists of 26 SISO models extracted from the 
@@
 leading to $191$ different benchmarks to evaluate the Multi-staged and Abstraction-based CEGIS algorithms.
+
+%-------------------------------
+\subsection{Description of the control benchmarks}
+\label{exp:benchmarks}
+%-------------------------------
 
@@
 %There are two continuous stirred tank reactor models named 
-\textit{cstr} (\#11) and \textit{cstrtmp} (\#12) describe the PH dynamics of a neutralization reaction 
+\textit{cstr} (\#11) and \textit{cstrtmp} (\#12) describe the PH dynamics of a reaction 
 of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
-the temperature of a exothermic reaction~\cite{astrom2006advanced} in a continuous 
-flow stirred-tank reactor. The \textit{DC motor} plant (\#13) describes the velocity 
-dynamics of a basic brushed direct current electrical machine.
-
-The \textit{Flexbeam} benchmark (\#14) is a plant employed in vibration studies; the 
-physical  system consists of a flexible metallic structure with piezoceramic 
-actuators and sensors. The \textit{guidance chen} benchmark (\#15) is another 
-high-order system model used by Chen et al.~\cite{CHEN1979389}  to evaluate 
-model order reduction techniques; it corresponds to a guidance control system model,
-which is used to determine the path of an autonomous vehicle movement. The 
-\textit{helicopter} benchmark plant (\#16) describes the dynamics of transitional motion 
-with respect to a longitudinal plane and the rotational motion around the longitudinal 
-axis for a coaxial helicopter.
-
-The benchmarks \textit{Invpendulum\_cartpos} (\#17) and \textit{Invpendulum\_pendang} (\#18)
-are models for the cart position and the pendulum angle of an inverted pendulum 
-plant composed by a point mass, which must be equilibrated above the pivot point and is 
-mounted on an one degree of freedom cart that moves over a track through a DC motor.
-
-The \textit{magpointer} (\#19) corresponds to a magnetic pointer plant composed by a pointer 
-employed in analogue gauges and indicators, whose angular position dynamics is 
-controlled by a magnetic field. The \textit{magsuspension} describes (\#20) the dynamic of
-a magnetic car suspension system. The \textit{pendulum} (\#21) plant consists of a swinging 
-point mass suspended from a frictionless pivot by means of a negligible mass rod.
-
-The \textit{Regulator} (\#22) plant consists of a linear model of a synchronous electrical
-machine connected to an infinite bus~\cite{KOKOTOVIC198023}. The 
-\textit{springer-mass damper system} plant (\#23) is a classic model for several mechanical 
-systems dynamics. This benchmark describes a mass, which is fixed to a node by means 
-of a springer and moves under the action of an input force, damping, and elastic force.
-The \textit{steam drum} benchmark (\#24) describes the linear model for the level dynamics 
-of a  boiler steam drum~\cite{boiler}.
-
-The \textit{suspension} (\#25) benchmark corresponds to the model of a single wheel suspension 
-system of a car, {\it i.e.}, the relative motion dynamics of a mass springer damp model, 
-which connects the car to one of its wheels.  The \textit{tapedriver} benchmark (\#26)
-corresponds to the model of a computer tape driver, \textit{i.e.}, a computer storage device 
-used to read and write data on magnetic tapes.
+the temperature of a reaction~\cite{astrom2006advanced} in a 
+%continuous flow stirred-
+tank reactor. The \textit{DC motor} plant (\#13) describes the velocity 
+dynamics of a 
+%basic brushed 
+direct-current electrical machine.
+
+The \textit{Flexbeam} benchmark (\#14) is 
+%a plant 
+employed in vibration studies and models  
+%the physical system consists of 
+a flexible metallic structure with sensors and actuators. 
+The \textit{guidance chen} benchmark (\#15) is a high-order system model used by Chen et al.~\cite{CHEN1979389} to evaluate 
+model-order reduction techniques; it models a guidance control system, 
+which is used to determine the path of an autonomous vehicle. 
+The \textit{helicopter} benchmark plant (\#16) describes the transitional and rotational dynamics 
+%of transitional motion with respect to a longitudinal plane and the rotational motion around the longitudinal axis for 
+of a coaxial helicopter.
+
+\textit{Invpendulum\_cartpos} (\#17) and \textit{Invpendulum\_pendang} (\#18) 
+are models for the cart position and the angle of an inverted pendulum placed on the cart,  
+%plant composed by a point mass, which must be equilibrated above the pivot point and is mounted on an one degree of freedom cart that 
+which moves over a track through a DC motor.
+
+The \textit{magpointer} (\#19) describes a magnetic pointer, 
+% plant composed by a pointer employed in analogue gauges and indicators, 
+whose angular position dynamics is controlled by a magnetic field. 
+The \textit{magsuspension} describes (\#20) the dynamic of a magnetic car suspension system. 
+The \textit{pendulum} (\#21) plant consists of a swinging point mass suspended from a frictionless pivot by means of a rod with negligible mass.
+
+The \textit{Regulator} (\#22) consists of a linear model of a synchronous electrical machine% connected to an infinite bus
+~\cite{KOKOTOVIC198023}. 
+The \textit{springer-mass damper system} plant (\#23) is a standard model for the dynamics of several mechanical systems. 
+%This benchmark describes a mass, which is fixed to a node by means of a springer and moves under the action of an input force, damping, and elastic force.
+The \textit{steam drum} benchmark (\#24) describes a linear model for the level dynamics of a boiler steam drum~\cite{boiler}.
+
+The \textit{suspension} (\#25) models a single-wheel suspension system of a car, 
+namely the relative motion dynamics of a mass springer damp model, which connects the car to one of its wheels.  
+The \textit{tapedriver} benchmark (\#26) models a computer tape driver, 
+that is a computer storage device used to read and write data on magnetic tapes.
 

### 2018-05-10 automatica/paper.tex
section 8

@@
 
-Using the state-space models given in Section~\ref{exp:benchmarks}, 
-our evaluation has the following two experimental goals:
+Using the state-space models described in Section~\ref{exp:benchmarks}, 
+the evaluation study has the following two experimental goals:
 
@@
 
-\item[EG2] \textbf{(sanity check)} Confirm the
-stability and safety of the synthesized controllers outside of our model.
+\item[EG2] \textbf{(Sanity check)} Confirm the
+stability and safety of the synthesized controllers \note{[this is unclear, rephrase:]outside of our model.}
 
@@
 
-We provide the results in Table~\ref{tab:results}.  Here 
-\textit{Benchmark} is the name of the respective benchmark, 
-\textit{Order} is the number of continuous variables, 
+We provide the results in Table~\ref{tab:results}, 
+where \textit{Benchmark} is the name of the respective benchmark, 
+\textit{Order} is the number of continuous variables of the model, 
 $\mathcal{F}_{\langle I_p,F_p \rangle}$ and $\mathcal{F}_{\langle p \rangle}$  
-are the fixed- and floating-point precision used to model the plant, respectively;
-while \textit{Time} is the total time required to synthesize a controller for the given
-plant with one of the two methods.  Timeouts are indicated by~\xmark.  The
-precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
-chosen to be $I_c = 8$, $F_c = 8$ for fixed-point and 
-$\mathcal{F}_{\langle p \rangle}$ is chosen to be half-precision for floating-point.
-
-We split our evaluation into two sets of results: fixed- and floating-point. 
+are the fixed- and floating-point precisions used to model the plant, respectively,  
+and \textit{Time} is the total time required to synthesize a controller for the given plant.    
+Timeouts are indicated by~\xmark.  \note{ we should distinguish between timeouts and failures to synthesise. }
+The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
+chosen to be $I_c = 8$, $F_c = 8$ for fixed-point, whereas  
+$\mathcal{F}_{\langle p \rangle}$ is chosen to be half-precision for floating-point. \note{what about $\mathcal{F}_{\langle I_p,F_p \rangle}$?}
+
+We separate our evaluation into two sets of results: fixed- and floating-point. 
 For the majority of the fixed-point benchmarks, we observe that the abstraction-based

### 2018-05-10 automatica/paper.tex
section 8

@@
 
+\note{Perhaps rather than `safety check' we could speak about robustness to changes in sampling time.}
+
 %-------------------------------
@@
 We separate our evaluation into two sets of results: fixed- and floating-point. 
-For the majority of the fixed-point benchmarks, we observe that the abstraction-based
+For the majority of the {\it fixed-point} benchmarks, we observe that the abstraction-based
 back-end is faster than the basic multi-staged verification approach, and
-finds one solution more (14) than the multi-staged back-end (13).  In direct
-comparison, the abstraction-based approach is on average able to find a
+finds a solution for more benchmarks (14) than the multi-staged back-end (13) \note{we should clarify that this is out of 26 in total, not 191?}.  
+In direct comparison, the abstraction-based approach is on average able to find a
 solution in approximately 53\% of the time required using the multi-staged
 back-end, and has a median run-time 0.5\,s, which is twenty times smaller
-than the multi-staged approach.  The two back-ends complement each other in
-benchmark coverage and together solve 58\% of the benchmarks.
-%
-For the majority of the floating-point benchmarks, we also observe that the abstraction-based
-back-end is much faster than the basic multi-staged verification approach, but both
-back-ends find the same amount of solutions (13).  In direct
-comparison, the abstraction-based approach is on average able to find a
+than the multi-staged approach.  The two back-ends complement each other in terms of 
+benchmark coverage, and together solve 58\% of the benchmarks \note{only? this does not sound much really}.  
+%
+For the majority of the benchmarks with {\it floating-point} implementation, 
+we also observe that the abstraction-based back-end is much faster than the basic multi-staged verification approach, 
+but both back-ends find the same amount of solutions (13).  
+In direct comparison, the abstraction-based approach is on average able to find a
 solution in approximately 50\% of the time required using the multi-staged
@@
 than the multi-staged approach.  The two back-ends complement each other in
-benchmark coverage and together solve 54\% of the benchmarks.
+benchmark coverage and together solve 54\% of the benchmarks \note{somewhat underwhelming}.
 
@@
 
-The median run-time for our benchmark set is 6.6\,s for fixed-point and 5.45\,s for floating-point. 
-We consider these times short enough to be of practical use to control engineers, and thus affirm EG1.
-
-There are a few instances for which the system fails to find a controller. 
-For the na\"ive approach, the completeness threshold may be too large, thus
-causing a timeout.  On the other hand, the abstraction-based approach may
-require a very precise abstraction, resulting in too many refinements and,
-consequently, in a timeout.  Yet another source of incompleteness is the
-inability of the {\sc synthesize} phase to use a large enough precision for
+The median run-time for \note{the successful} benchmarks is 6.6\,s for the fixed-point and 5.45\,s for floating-point implementations, respectively.  
+We consider these times short enough to be of practical use to control engineers, and thus affirm the validity of EG1.
+
+There are \note{a few [you mean half!]} instances for which both approaches fail to synthesise a controller.  
+For the multi-stage approach, the completeness threshold may be too large, thus causing a timeout.  
+On the other hand, the abstraction-based approach may require a very precise abstraction, resulting in too many refinements and, consequently, again in a timeout.  
+Yet another source of incompleteness is the inability of the {\sc synthesize} phase to use a large enough precision for
 the plant model.
@@
 
+\note{So, what about EG2? Shall we assert it? }
+
 %-------------------------------
@@
 
-\textcolor{red}{Cristina: Can you please write an initial version of the conclusions?}
+We have presented two automated approaches to synthesize digital
+state-feedback controllers that ensure both stability and safety over state-space models.   
+The first approach relies on unfolding of the closed-loop model dynamics up to a completeness threshold, while the second
+one applies abstraction-refinement and acceleration to increase speed, whilst retaining soundness.
+%
+Both approaches are novel within the control literature: they give a fully
+automated synthesis method that is algorithmically and numerically sound,
+considering various error sources in the implementation of the digital
+control algorithm and in the computational modeling of plant dynamics.
+%
+Our experimental results show that both approaches are able to synthesize fully automatically 
+safe controllers for most benchmarks, which have been derived from the control literature, 
+within a reasonable amount of time.
+
+\note{Let us collect here the main extensions we regard to be relevant: \\ 
+models with partial observations; \\ 
+implementation with SMT; \\ 
+continuous-time; \\ 
+more complex specs; \\ 
+\ldots }
 

### 2018-05-11 automatica/paper.tex
section 4

@@
 
-\title{Automated Formal Synthesis of Safe Digital Controllers\\
+\title{Automated Formal Synthesis\\ 
+of Safe Digital Controllers 
 for Continuous Plants}
@@
 
+\note{Anticipate here connection with characteristic polynomial?}
+
 %-------------------------------
@@
 %-------------------------------
-\subsection{Counterexample Guided Inductive Synthesis - CEGIS} 
+\subsection{Counterexample-Guided Inductive Synthesis} 
 \label{ssec:cegis}
@@
 
-We consider an input specification of the form $\exists P .\, \forall a.\, \phi(a, P)$, 
+We consider an input specification of the form 
+$$
+\exists P .\, \forall a.\, \phi(a, P),
+$$  
 where $P$ ranges over functions (where a function is represented by the program computing it),
@@
 exists.
+
+\note{In the context of the formal synthesis of safe controllers, 
+the CEGIS architecture is applicable as follows: \ldots }
+
 %-------------------------------
@@
 
-While in the previous section we have discussed the generic CEGIS
-framework, in the rest of the paper we will explain how we adapt it to
-the synthesis of digital controllers. For this purpose, we start by
-describing the specific property that we pass to the synthesizer as
-the specification $\phi$. Namely, we are interested in capturing
-stability and safety, which we discuss in Sections~\ref{ssec:stabspecification}
-and~\ref{ssec:safespecification}, respectively.
+%While in the previous section we have discussed the generic CEGIS framework, 
+In the rest of the paper we explain how to adapt the generic CEGIS framework to the synthesis of digital controllers. 
+We start by describing the specific property that we pass to the synthesizer as the specification $\phi$. 
+Namely, we are interested in capturing stability and safety, 
+which we discuss in Sections~\ref{ssec:stabspecification} and~\ref{ssec:safespecification}, respectively.
 
@@
 
-  There are a number of algorithms in our verification engine that can
-  be used for stability analysis~\cite{daes20161, Bessa16}.
+There are a number of procedures that can be used for stability analysis of dynamical models~\cite{daes20161, Bessa16}, 
+which can fit our automatic verification engine.  
 %one based on Schur's decomposition
 %and another one based on Jury's criterion~\cite{astrom1997computer}.  
-Here we choose Jury stability criterion~\cite{astrom1997computer} in view of its efficiency 
-and ease of integration within our implementation: 
-this method checks the stability working in the $z$-domain of the characteristic polynomial $S(z)$,  
+Here we choose Jury stability criterion~\cite{astrom1997computer}, 
+in view of its efficiency and ease of integration within our implementation.  
+This method checks the stability working in the complex domain of the characteristic polynomial $S(z)$,  
 %
@@
 \begin{equation*}
-S(z) = a_0z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N=0, a_0\neq0. 
+S(z) = a_0z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N,\,\, a_0\neq0. 
 \end{equation*}
+\note{The characteristic polynomial $S(z)$ represents the dynamical model in \ldots }
 %\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?} 
@@
 % $$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$
-The following matrix
-$M = [m_{ij}]_{(2N-2)\times N}$ is built from $S(z)$ coefficients:
+The following matrix $M$ with dimension $(2N-2)\times N$ and elements $m_{(\cdot),(\cdot)}$ is built from the coefficients of $S(z)$ as:  
 %
@@
 %
-where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ such that:
+where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ is such that:
 %
@@
 and where $k \in \mathbb{Z}$ is such that $0 < k < N - 2$.
-We have that $S(z)$ is the characteristic polynomial of a stable system if and only if the following four conditions hold~\cite{astrom1997computer}:
+
+We have that $S(z)$ is the characteristic polynomial of a stable system if and only if the following four conditions $R_i, i = 1,2,3,4,$ hold~\cite{astrom1997computer}:
 %\begin{itemize}
@@
 %\end{itemize}
-%
-The stability property is then encoded by a constraint of the form:
+
+The stability property is finally encoded by a constraint expressed as the following formula: 
 $
@@
 %More specifically, we require that the closed-loop system meets given safety specifications.  
-A safety specification translates to a requirement on the states of the closed-loop model, 
-and the feedback controller (namely the choice of the gains matrix~$K$) 
-must ensure that the state never violates the requirement.  
-Note that a stable, closed-loop model is not necessarily a safe system: 
+A safety specification translates into a requirement on the states of the closed-loop model, 
+which hinges on the choice of the feedback controller (namely the choice of the gains in the matrix~$K$):  
+we must ensure that the states of the closed-loop model never violate this requirement, expressed as a given subset of the state space.
+
+Note that a stable closed-loop model is not necessarily a safe model: 
 indeed, the state values may leave the safe part of the state space while they converge

### 2018-05-11 automatica/paper.tex
section 4

@@
 indeed, the state values may leave the safe part of the state space while they converge
-to the equilibrium, which is typical in the case of oscillatory convergent dynamics. 
+to the equilibrium, which is typical in the case of oscillatory and convergent dynamics. 
 %However, a safe system will always be stable.  
-In~this work, the safety property is expressed as:
+In~this work, the safety property is expressed as the formula:
 %
@@
 where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
-for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
-instant, respectively.  This means that the states will always be within an $n$-dimensional hyper-box.
+for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$, ranging over the $k$-th time step.  
+This means that the states are required to remain within an $n$-dimensional hyper-box at any point in time.
 
@@
 while the feedback dynamics evolve in discrete time.  
-A new input value is accepted by the plant only at sample times $T_s$. \note{Confusing $T_s$ vs $T_d$.} 
+A new input value is accepted by the plant only at sample times $T_s$. \note{Confusing use of $T_s$ vs $T_d$ - please clarify.} 
 %but implemented over the continuous-time plant dynamics.
@@
 \begin{proof}
+\note{let us not number the proofs.}
 %

### 2018-05-11 automatica/paper.tex
section 4

@@
 
-In this section we discuss two instantiations of CEGIS: the first,
-na\"ive one, relies on an unfolding of the dynamics up to a
-completeness threshold, while the second one is abstraction-based and
-leverages abstraction refinement and acceleration to improve
-scalability while retaining soundness.
+In this section we discuss two instantiations of CEGIS: 
+the first one,
+named {\it multi-stage} approach, 
+relies on an unfolding of the dynamics up to a completeness threshold; 
+the second one is {\it abstraction-based}, 
+and it leverages abstraction-refinement \note{ cit.} and acceleration \note{ref to relevant section} to improve scalability,  
+while retaining soundness.
 
@@
 
-An overview of the algorithm for controller synthesis is given in Fig.~\ref{fig:CEGIS-precision-increment}.  
-One important observation is that we verify and synthesize a controller over a finite number ($k$) of time steps.  
-We then compute a completeness threshold $\overline{k}$~\cite{DBLP:conf/vmcai/KroeningS03} 
-for this controller, and verify correctness for $\overline{k}$ time steps. 
-As we will later argue, $\overline{k}$ is the number of iterations required to sufficiently unwind the closed-loop state-space model,  
-ensuring that the boundaries are not violated for any other $k{>}\overline{k}$.
+An overview of the algorithm for controller synthesis is given in Figure~\ref{fig:CEGIS-precision-increment}.   
+One important point is that we formally synthesize a controller over a finite number ($k$) of time steps.  
+We then compute a completeness threshold $\overline{k}$~\cite{DBLP:conf/vmcai/KroeningS03} for this controller, 
+and verify the correct behaviour for $\overline{k}$ time steps. 
+As we will later argue, $\overline{k}$ is the number of iterations required to sufficiently unwind the dynamics of the closed-loop state-space model,  
+ensuring that the safety boundaries are not violated for any other $k{>}\overline{k}$.
 
@@
 
-Next, we describe in detail the different phases in Fig.~\ref{fig:CEGIS-precision-increment} (blocks 1 to 4).
+Next, 
+with reference to the CEGIS scheme in Figure~\ref{fig:CEGIS}, 
+we describe in detail the different phases in Fig.~\ref{fig:CEGIS-precision-increment} (blocks 1 to 4).
 

### 2018-05-11 automatica/paper.tex
section 5

@@
 %-------------------------------
-\subsection{Multi-stage approach} 
+\subsection{Multi-stage CEGIS} 
 \label{sssec:naive}
@@
 
+\note{we need to refer to the parts of Algorithm 1 more closely - point to specific lines in the explanation below.}
+
 %\todo{please eventually itemize next}
@@
 candidate solution $K$ that satisfies both the stability criteria and the
-safety specification.  To synthesize a controller that satisfies the
+safety specification.
+
+To synthesize a controller that satisfies the
 stability criteria, we require that a computed polynomial satisfies Jury's
-criterion~\cite{fadali}.  The details of this calculation can be found in
+criterion~\cite{fadali} \note{use specific formula}.  The details of this calculation can be found in
 the Appendix.
 
-Regarding the second requirement, we synthesize a safe controller by
-unfolding the transition system $k$ steps and by picking a controller $K$
-and a single initial state, such that the states at each step do not violate
-the safety criteria.  That is, we ask the bounded model checker if there
-exists a $K$ that is safe for at least one $x_0$ in our set of all possible
-initial states.  This is sound if the current $k$ is greater than the completeness
-threshold.  We~also assume some (fixed or floating point) precision $\langle I_p,F_p\rangle$ for the
-plant and a sampling rate.  The checks that these assumptions hold are
-performed by subsequent {\sc verify} stages.
+Regarding the second requirement, 
+we fix an index $k$, 
+and we synthesize a safe controller by
+unfolding the transition system $k$ steps and by selecting a controller $K$ and a single initial state, 
+such that the states at each step do not violate the safety criteria \note{use specific formula}.  
+That is, we ask the bounded model checker \note{have we discussed the BMC earlier?} if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states.  
+This is sound if the current $k$ is greater than the completeness threshold (see later step).  
+We~also assume some (fixed or floating point) precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  
+The checks that these assumptions hold are performed by subsequent {\sc verify} stages. 
+\note{we have not discussed the bounds on the input signal. }
 
@@
 state, is safe for \emph{all} possible initial states, i.e., does not reach
-an unsafe state within $k$ steps where we assume $k$ to be under the
-completeness threshold.  After unfolding the transition system corresponding
+an unsafe state within $k$ steps \note{where we assume $k$ to be under the
+completeness threshold}.  After unfolding the transition system corresponding
 to the previously synthesized controller $k$ steps, we check that the safety
@@
 given above and illustrated in Fig.~\ref{fig:ct}. 
+\note{it is not clear how we find $\overline{k}$.}
 
@@
 computationally expensive if the bounds on the allowed initial states are
-large.
+large. \note{we have not discussed the bounds on the input signal. }
 
@@
 
-Essentially, this approach relies on the symbolic simulation over a bounded
+This approach relies on the symbolic simulation over a bounded
 time horizon of individual initial states and inputs that form part of an

### 2018-05-11 automatica/paper.tex
section 5

@@
 
-This approach relies on the symbolic simulation over a bounded
-time horizon of individual initial states and inputs that form part of an
-uncountable space and tries to generalize it for an infinite space over an
-infinite time horizon.
+The multi-staged approach above relies on the symbolic simulation over a bounded time horizon of individual initial states and inputs, 
+%that form part of an uncountable space,
+and on the generalization to continuous sets and over an infinite time horizon.
 
@@
 
-Conversely, in this section, we find a controller for a continuous initial
-set of states and set of inputs, over an abstraction of the continuous
-dynamics \cite{cattaruzza2015unbounded} that conforms to witness proofs at
-specific times.  %% It further generalizes the
-Moreover, this approach uses abstraction refinement enabling us to always
-start with a very simple description regardless of the complexity of the
-overall dynamics, and only expand to more complex models when a solution
-cannot be found.
-
-The CEGIS loop for this approach is illustrated in Fig.~\ref{fig:CEGARIS}.
-
+Conversely, in this section we synthesise a controller for continuous set of initial states and of inputs, 
+over an abstraction of the continuous dynamics \cite{cattaruzza2015unbounded} \note{that conforms to witness proofs at specific times}.   
+Moreover, this approach uses abstraction-refinement, 
+enabling one to start with a very simple description of the dynamics regardless of the model complexity (abstraction step), 
+and only to elaborate this description 
+%to more complex models 
+when a solution cannot be found (refinement step).
+
+The CEGIS loop for this approach is illustrated in Figure~\ref{fig:CEGARIS}. 
+%
 % Now that we have explained the verification process, we may proceed to describe the synthesis procedure, which is illustrated in figure \ref{fig:CEGARIS}.
@@
 % the quantization noise as a bounded non-deterministic input.
-
+It comprises the following steps:  
 \begin{enumerate}
@@
 $P_a(z) = z^n+\sum_{i=1}^n{(a_i-k_i)z^{n-i}}$. 
+\note{are we assuming to be working with a controllable form?}   
 %\blue{[shouldn't there be a b term in the polynomial's coefficients here? No. the polynomial only evaluates the poles]}

### 2018-05-11 automatica/paper.tex
section 5

@@
 $P_a(z) = z^n+\sum_{i=1}^n{(a_i-k_i)z^{n-i}}$. 
-\note{are we assuming to be working with a controllable form?}   
+\note{are we assuming to be working with a controllable form?
+should we emphasize that some elements are known, others are parameters?
+also, why do we use a different notation for this char poly than before?}
 %\blue{[shouldn't there be a b term in the polynomial's coefficients here? No. the polynomial only evaluates the poles]}
@@
 
-\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
-%
-\begin{equation}
+\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors as follows: 
+%($\frac{q_1}{2},\frac{q_2}{2},q_3$)
+\note{so here you're summing three intervals, not taking their intersection (weird usage of logical AND), right? please clarify. }
+\begin{align*}
 \nonumber
 \begin{split}
-N=\left \{ \nu_1+\nu_2+ \nu_3 \mid \nu_1 \in \left[-\frac{q_1}{2}\ \ \frac{q_1}{2}\right] 
-\wedge \right. \\ \left. \nu_2 \in \left[-\frac{q_2}{2}\ \ \frac{q_2}{2}\right]  \wedge  \nu_3 \in \left[-q_3\ \ q_3\right]  \right \}
+N=\left \{ \nu_1+\nu_2+ \nu_3: \nu_1 \in \left[-\frac{q_1}{2}\ \ \frac{q_1}{2}\right] 
+\wedge \right. \\ \left. \nu_2 \in \left[-\frac{q_2}{2}\ \ \frac{q_2}{2}\right]  \wedge  \nu_3 \in \left[-q_3\ \ q_3\right]  \right \}, 
 \end{split}
-\end{equation}
-
-%
-where  $q_1$ is the error introduced by the truncation in the ADC, $q_2$ is
-the error introduced by the DAC and $q_3$ is the maximum truncation and
-rounding error in $u_k=-K \cdot \mathcal{F}_{\langle I_c,F_c \rangle}(x_k)$ as
-discussed in Section~\ref{sec:numeric_rep}. % More details on how to model
+\end{align*}
+%
+\note{pls refer to Figure 1, where however we had used capitalised Q1 and Q2 - pls fix.} 
+where  $q_1$ is the error introduced by the truncation in the ADC, 
+$q_2$ is the error introduced by the DAC, 
+and $q_3$ is the maximum truncation and rounding error in $u_k=-K \cdot \mathcal{F}_{\langle I_c,F_c \rangle}(x_k)$, 
+as further discussed in Section~\ref{sec:numeric_rep}. % More details on how to model
 %quantization as noise are given in
@@
 %
-$$(\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-K x_k)
-\Rightarrow \phi_\mathit{init}^{K}$$
+$$(\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-K x_k)\Rightarrow \phi_\mathit{init}^{K}
+$$
+\note{please explain the equation here: 
+what does the logical implication mean? 
+on the antecedent of this logical implication, you're taking the conjunction of two logical formulae (expressing two sets) and of a linear arithmetic expression}
 Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.

### 2018-05-11 automatica/paper.tex
section 5

@@
 
-\textcolor{red}{[Dario: can you update the following part, aligning it with hers?]}
+%\textcolor{red}{[Dario: can you update the following part, aligning it with hers?]}
 
@@
 Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space. 
+\note{In Figure 1, you're using a different formula than $\phi_\mathit{init}^{K}$, why? }
 
@@
 % safety specification $\phi_\mathit{safety}$.
-  $K \in \mathbb{R}\langle I_c,F_c\rangle^n$ that satisfies
+  $K \in \mathbb{R}\langle I_c,F_c\rangle^n$ 
+  \note{we have not introduced this notation, so this is not clear.}
+  that satisfies
   $\phi_\mathit{stability} \wedge \phi_\mathit{safety} \wedge \phi_\mathit{init}^{K}$ by invoking a SAT solver. 
+  \note{the corresponding block in the figure accepts two inputs - can you comment on them?
+also: is this SAT solving step obvious?
+Sat solvers resolve Boolean formulae, but here we have something else.
+}
 %%   We obtain it by solving the SAT formula 
@@
   In order to compute the progression of point $x_0$ at iteration $k$,
-  we accelerate the dynamics of the closed-loop system and obtain:
+  we consider the solution of the closed-loop model 
   %we take the
@@
 \scriptsize
-\begin{equation}
+\begin{align*}
 %\begin{split}
-x=(A_d-B_dK)^kx_0+ \sum_{i=0}^{k-1} (A_d-B_dK)^i B_{n}(\nu_1+\nu_2+\nu_3)% 
+x=(A_d-B_dK)^kx_0+ \sum_{i=0}^{k-1} (A_d-B_dK)^i B_{n}(\nu_1+\nu_2+\nu_3), 
 %\end{split}
-\end{equation}
-\begin{equation}
-B_n= [1 \cdots 1]^T
-\end{equation}
+\end{align*}
 }
+where $B_n= [1 \cdots 1]^T$. 
 %\label{eq:acc_observer_LTI_cf}
 %+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i 
-
-%
-As this still requires us to verify the system for every $k$ up to infinity,
-we use abstract acceleration again to obtain the reach-tube, i.e., the set
-of all reachable states at all times given an initial set
+%
+As we require to verify the system for every $k$ up to infinity, 
+we use Abstract Acceleration again to compute the reach-tube, 
+i.e., the set of all reachable states at all times given an initial set
 $\phi_\mathit{init}$:
@@
 \hat{X}^\#
-=\mathcal{A} X_0 + \mathcal{B}_{n} N, \quad
-X_0 =\left \{x \mid x \models \phi_\mathit{init} \right\}, 
+=\mathcal{A} X_0 + \mathcal{B}_{n} N, \,
+X_0 =\left \{x: x \models \phi_\mathit{init} \right\}, 
 \end{align} 
@@
 abstract matrices for the closed-loop system~\cite{cattaruzza2015unbounded},
-whereas the set $N$ is non-deterministically chosen.
-
-We next evaluate $\hat{X}^\# \models \phi_\mathit{safety}$.  If the
-verification holds we have a solution, and exit the loop.  Otherwise, we
+whereas the set $N$ is \note{non-deterministically chosen [obtained from above]}.
+
+We next evaluate whether $\hat{X}^\# \models \phi_\mathit{safety}$.  
+If the verification holds we have a solution, and exit the loop.  Otherwise, we
 find a counterexample iteration $k$ and corresponding initial point $x_0$

### 2018-05-11 automatica/paper.tex
section 5

@@
 find a counterexample iteration $k$ and corresponding initial point $x_0$
-for which the property does not hold, which we use to locally refine the
-abstraction.  When the abstraction cannot be further refined, we provide
-them to the {\sc abstract} phase.
+for which the property does not hold, which we use to \note{locally refine the
+abstraction [how?]}.  When the abstraction cannot be further refined, we provide $(k, x_0)$ to the {\sc abstract} phase.
 %

### 2018-05-11 automatica/paper.tex
section 5

@@
 Sat solvers resolve Boolean formulae, but here we have something else.
+So, explain block `Program search'.
 }
@@
 
-We next evaluate whether $\hat{X}^\# \models \phi_\mathit{safety}$.  
-If the verification holds we have a solution, and exit the loop.  Otherwise, we
+ \note{Ref Abstraction Verifier in Figure?}
+We next evaluate whether $\hat{X}^\# \models \phi_\mathit{safety}$ \note{how?}. 
+If the verification holds we have a solution, and exit the loop \note{ref PASS?}.  Otherwise, we
 find a counterexample iteration $k$ and corresponding initial point $x_0$
@@
 \begin{enumerate}
-\item Find the constraints that invalidate the property
- as a set of counterexamples for the eigenvalues, which we define as $\phi_\Lambda$. This is a constraint in the spectrum i.e., transfer function) of the closed loop dynamics. 
+\item Find the constraints that invalidate the property as a set of counterexamples for the eigenvalues \note{sure, but how?}, which we define as $\phi_\Lambda$. 
+This is a constraint in the spectrum i.e., transfer function) of the closed-loop dynamics.  
 \item We use $\phi_\Lambda$ to
@@
 These constraints correspond to specific iterations for which the system may be unsafe.
-\item Pass the refined abstraction $\phi(K)$ with the new constraints and the list of iterations $k$ to the {\sc synthesize} phase.
+\item Pass the refined abstraction $\phi(K)$ with the new constraints and the list of iterations $k$ to the {\sc synthesize} phase \note{(step (2))}.
   %, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again. 
@@
 
-As discussed in section~\ref{sec:}, the models we consider have errors due to several sources; the numerical error introduced by the precision used to represent the plant, the error introduced by the ADC conversion, and the error introduced by the precision used to represent the controller.
+As discussed in \note{Section~\ref{sec:}}, 
+the models we consider have to account for errors from several sources: 
+the numerical error introduced by the precision used to represent the plant, the error introduced by the ADC conversion, and the error introduced by the precision used to represent the controller.
 First we consider the numerical errors introduced by the finite precision numbers (either fixed or floating point) used to model the plant and used by the digital controller.

### 2018-05-11 benchmark-runner/universalrunner/safety_stability.c
fix higher dimension bug in safety_stability.c

@@ -49,7 +49,7 @@ __plant_typet internal_pow(__plant_typet a, unsigned int b){
 int check_stability(){
 
 
-  #if NSTATES==1
+ #if NSTATES==1
   if(greaterthan(_AminusBK[0][0], one_type) || lessthan(_AminusBK[0][0], minusone))
     {return 0;}
   else
@@ -457,83 +457,26 @@ void assume_corner_cases_for_states(void) {
                 || _controller_states[0] == INITIALSTATE_LOWERBOUND && _controller_states[1] == INITIALSTATE_LOWERBOUND && _controller_states[2] == INITIALSTATE_UPPERBOUND
                 || _controller_states[0] == INITIALSTATE_LOWERBOUND && _controller_states[1] == INITIALSTATE_LOWERBOUND && _controller_states[2] == INITIALSTATE_LOWERBOUND);
   #elif NSTATES == 4
-  __CPROVER_assume(_controller_states[0] == INITIALSTATE_UPPERBOUND && _controller_states[1] == INITIALSTATE_UPPERBOUND && _controller_states[2] == INITIALSTATE_UPPERBOUND && _controller_states[3] == INITIALSTATE_UPPERBOUND
-                || _controller_states[0] == INITIALSTATE_UPPERBOUND && _controller_states[1] == INITIALSTATE_UPPERBOUND && _controller_states[2] == INITIALSTATE_UPPERBOUND && _controller_states[3] == INITIALSTATE_LOWERBOUND
-                || _controller_states[0] == INITIALSTATE_UPPERBOUND && _controller_states[1] == INITIALSTATE_UPPERBOUND && _controller_states[2] == INITIALSTATE_LOWERBOUND && _controller_states[3] == INITIALSTATE_UPPERBOUND
-                || _controller_states[0] == INITIALSTATE_UPPERBOUND && _controller_states[1] == INITIALSTATE_UPPERBOUND && _controller_states[2] == INITIALSTATE_LOWERBOUND && _controller_states[3] == INITIALSTATE_LOWERBOUND
-                || _controller_states[0] == INITIALSTATE_UPPERBOUND && _controller_states[1] == INITIALSTATE_LOWERBOUND && _controller_states[2] == INITIALSTATE_UPPERBOUND && _controller_states[3] == INITIALSTATE_UPPERBOUND
[…]

### 2018-05-11 automatica/paper.tex
section 5

@@
 the models we consider have to account for errors from several sources: 
-the numerical error introduced by the precision used to represent the plant, the error introduced by the ADC conversion, and the error introduced by the precision used to represent the controller.
+the numerical error introduced by the finite precision used to represent the plant \note{(and its operations)},  
+the error introduced by the ADC\note{/DAC?} conversion, 
+and the error introduced by the limited precision used to represent the controller. 
 First we consider the numerical errors introduced by the finite precision numbers (either fixed or floating point) used to model the plant and used by the digital controller. 
-Then we account for the quantization errors introduced by the ADC.
+Then we account for the quantization errors introduced by the ADC\note{/DAC?}.
 

### 2018-05-11 automatica/paper.tex
section 6

@@
 and the error introduced by the limited precision used to represent the controller. 
-First we consider the numerical errors introduced by the finite precision numbers (either fixed or floating point) used to model the plant and used by the digital controller. 
+First we consider the numerical errors introduced by the finite precision numbers (either fixed- or floating-point) used to model the plant and used by the digital controller. 
 Then we account for the quantization errors introduced by the ADC\note{/DAC?}.
 
-\subsection{Errors due to numerical representation}
-First consider the case where we use fixed-point representations, and synthesise fixed-point controllers.
+\subsection{Errors due to numerical representations}
+
+Let us first consider the case of fixed-point representation of the model, 
+and of synthesis of fixed-point controllers.
 
@@
 
-\subsection{Notation}
+\subsection{Notations}
+
+\note{If these notations are used in earlier Sections, shall we anticipate the paragraph to the preliminaries? }
+
 In this paper we will use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real
@@
 are determined by the controller.  We pick $I_p$ and $F_p$ for our synthesis
-such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$).  Thus any
-mathematical operations in our modelled digital controller will be in the
+such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$ \note{why is this reasonable?}).  
+Thus any mathematical operations in our modelled digital controller will be in the
 range of $\mathcal{F}_{\langle I_c,F_c \rangle}$, and all other calculations
@@
 
-\subsection{Floating point representation}
+\note{also introduce notations for floats?}
+
+\subsection{Floating-point representation}
+
+\note{Notice that this notation is different than the one used in the results section. pls fix. }
 

### 2018-05-14 automatica/paper.tex
Some fixes

@@
 \renewcommand{\note}[1]{\textcolor{red}{[#1]}}
+\newcommand{\reply}[1]{\textcolor{blue}{[#1]}}
 
@@
 
-If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ \note{when could that not exist?} such that $A_d=e^{\mat{A} T_d}$, 
+If $\mat{J}$ is diagonal and there exists a sampling time $T_s$ such that $A_d=e^{\mat{A} T_s}$, 
 then $\forall T \in \mathbb{R}_0^+$ we obtain the known expression 
 $$
-\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}})\mat{B}_d\vec{u}, 
+\vec{x}_T=A_d^{\frac{T}{T_s}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_s}})\mat{B}_d\vec{u}, 
 $$
-where $\mat{A}_d^{\frac{T}{T_d}} =e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$. 
+where $\mat{A}_d^{\frac{T}{T_s}} =e^{log(\mat{A}_d) \frac{T}{T_s}} = e^{\mat{A} T}$. 
 %is the state of the system at time $t=T$. 
@@
 while the feedback dynamics evolve in discrete time.  
-A new input value is accepted by the plant only at sample times $T_s$. \note{Confusing use of $T_s$ vs $T_d$ - please clarify.} 
+A new input value is accepted by the plant only at sample times $T_s$.
 %but implemented over the continuous-time plant dynamics.
@@
 
-\textcolor{red}{[The next discussion is highly unclear - Dario: can you please update it?]}
-\textcolor{blue}{[how about this?]}
-
 We next describe how to obtain an over-approximation of such a set. 
@@
 A tight polyhedron that can be obtained with faces (hyperplanes) that touch the set. 
-%, which they must do at a point tangential to the hyperplane. 
-Rather than pick \note{[concept undefined:] a set of directions} and find such points, 
-we will start from the points and find their tangents \note{there can be just a single tangent, or possibly multiple ones?}.  
-Furthermore, to simplify the procedure, 
-we will only look at \note{[qualitative:] two dimensional cuts of the space}  
-(see~\cite{cattaruzza2015unbounded}):  
-this means that for every point we choose is a vertex of the polyhedron \note{??}. 
-Finding out which side of the hyperplane corresponds to the inside of the
-polyhedron is achieved by looking at any other point in the original set and
-checking on which side of the hyperplane it lays.
+\reply{This is achieved by picking a number of points in the set, and finding a hyperplane
+tangent to that point w.r.t. dynamics.  Inorder to simplify this procedure, we
+look at two-dimensional cuts of the space, one at a time (i.e., for every pair
+of eigenvalues of the closed loop dynamics, we find a hyperplane tangent to
+the progression of that pair in a two dimensional space and use it as a face of
+the polyhedron).  The difference with~\cite{cattaruzza2015unbounded} is that
+in the continuous case, the tangent is found by derivation rather than
+differentialtion, thus including all intermediate points in the arc.}
 
@@
 %which is known to be smaller than that of the selected point, and the chosen hyperplanes are aligned with the eigenvectors, hence we only look at eigenvalue pairs to calculate the derivatives~\cite{cattaruzza2015unbounded}.
-
-\textcolor{red}{[Next part highly nebulous]} 
-\textcolor{blue}{[This is just the math that calculates the tangents of x-y pairs given the progression of x and y. Given the above description,is it necessary to include it?]}
-\note{I would cut the next part, if possible.
-However, the explanation above is not clear.
-It seems like you're just finding a convex hull.
-You have not introduced the notion of directions.
-The paragraph above requires brand new thinking.
-}
-
-The corresponding derivatives are:
-%
-\begin{enumerate}
-%
-\item for real eigenvalues: we first calculate the slope of the tangent
-between the two progressions: $\frac{d f(k)}{d g(k)}=\frac{f'(k)}{g'(k)}$. 
-Hence $\frac{d \lambda_1^k}{d \lambda_2^k}=\frac{log(\lambda_1)
-\lambda_1^k}{log(\lambda_2) \lambda_2^k}$.  From this we know that the polar
-angle of the support vector is $\psi = \tan^{-1}(\frac{log(\lambda_1)
-\lambda_1^k}{log(\lambda_2) \lambda_2^k})+\frac{\pi}{2}$
-%
-\item for conjugate eigenvalue pairs: the pair forms a logarithmic spiral. 
-The tangent of a spiral with polar equation $r=a e^{b\theta}$ will have a
-derivative $\frac{d r}{d \theta}=b a e^{b\theta}=b r$, hence the angle of
-the vector normal to the curve is $\tan^{-1}(\frac{r}{\frac{d r}{d
-\theta}})+\frac{\pi}{2}=\tan^{-1}(\frac{1}{b})+\frac{\pi}{2}$
-%
-\item for Jordan blocks with $gm>1$: in the case of real eigenvalues, we
-follow the same procedure as in the real case, but considering that the
-equation for each eigenvalue is $\frac{k^j}{j!}e^{\lambda k}$ where $j$ is
-the index of the term within the Jordan block (note that when $j=0$ the term
-is the same as for real eigenvalues above).  The derivatives f'(k),g'(k) are
-in the form $(j+k*log(\lambda))\frac{k^{j-1}}{j!}e^{\lambda k}$.
-%
-\item for any combination of complex eigenvalues we use the above equations
-using the envelope of their magnitude (ie $|\lambda|$).
-%
-\end{enumerate}
 
@@
 stability criteria, we require that a computed polynomial satisfies Jury's
-criterion~\cite{fadali} \note{use specific formula}.  The details of this calculation can be found in
-the Appendix.
+criterion~\cite{fadali} (\reply{see Section~\ref{ssec:stabspecification}}).
 
@@
 Conversely, in this section we synthesise a controller for continuous set of initial states and of inputs, 
-over an abstraction of the continuous dynamics \cite{cattaruzza2015unbounded} \note{that conforms to witness proofs at specific times}.   
+over an abstraction of the continuous dynamics \cite{cattaruzza2015unbounded} that conforms to witness proofs at specific times.   
 Moreover, this approach uses abstraction-refinement, 
@@
 %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
-\note{so here you're summing three intervals, not taking their intersection (weird usage of logical AND), right? please clarify. }
 \begin{align*}
@@
 \begin{split}
-N=\left \{ \nu_1+\nu_2+ \nu_3: \nu_1 \in \left[-\frac{q_1}{2}\ \ \frac{q_1}{2}\right] 
-\wedge \right. \\ \left. \nu_2 \in \left[-\frac{q_2}{2}\ \ \frac{q_2}{2}\right]  \wedge  \nu_3 \in \left[-q_3\ \ q_3\right]  \right \}, 
+N=\left \{ \nu_1+\nu_2+ \nu_3: \nu_1 \in \left[-\frac{q_1}{2}\ \ \frac{q_1}{2}\right] , \right.
+\\ \left.
+\nu_2 \in \left[-\frac{q_2}{2}\ \ \frac{q_2}{2}\right],  \nu_3 \in \left[-q_3\ \ q_3\right]  \right \},
 \end{split}
@@
 % safety specification $\phi_\mathit{safety}$.
-  $K \in \mathbb{R}\langle I_c,F_c\rangle^n$ 
-  \note{we have not introduced this notation, so this is not clear.}
+  $K$ 
   that satisfies
@@
 abstract matrices for the closed-loop system~\cite{cattaruzza2015unbounded},
-whereas the set $N$ is \note{non-deterministically chosen [obtained from above]}.
+whereas the set $N$ is obtained from above.
 
@@
 These constraints correspond to specific iterations for which the system may be unsafe.
-\item Pass the refined abstraction $\phi(K)$ with the new constraints and the list of iterations $k$ to the {\sc synthesize} phase \note{(step (2))}.
+\item Pass the refined abstraction $\phi(K)$ with the new constraints and the list of iterations $k$ to the {\sc synthesize} phase (step (2)).
   %, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again. 
@@
   \path
-    (pre.east) edge node[align=center] {$P_a$, $N$,\\ $\phi_\mathit{init}^k$} (abstract.west)
+    (pre.east) edge node[align=center] {$P_a$, $N$,\\ $\phi_\mathit{init}^K$} (abstract.west)
     (abstract.south) edge node{$(\phi(K), k)$} (synth.north)
@@
 the models we consider have to account for errors from several sources: 
-the numerical error introduced by the finite precision used to represent the plant \note{(and its operations)},  
-the error introduced by the ADC\note{/DAC?} conversion, 
+the numerical error introduced by the finite precision used to represent the plant (and its operations),  
+the error introduced by the ADC/DAC conversions, 
 and the error introduced by the limited precision used to represent the controller. 
 First we consider the numerical errors introduced by the finite precision numbers (either fixed- or floating-point) used to model the plant and used by the digital controller. 
-Then we account for the quantization errors introduced by the ADC\note{/DAC?}.
+Then we account for the quantization errors introduced by the ADC/DAC.
 
@@
 are determined by the controller.  We pick $I_p$ and $F_p$ for our synthesis
-such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$ \note{why is this reasonable?}).  
+such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$ (\reply{so that our controller can be represented accurately in the plant domain}).  
 Thus any mathematical operations in our modelled digital controller will be in the

### 2018-05-14 benchmark-runner/universalrunner/benchmark.h

@@ -7,21 +7,21 @@
 
 #ifndef BENCHMARK_H_
 #define BENCHMARK_H_
+#define INTERVAL 1
 #ifndef INT_BITS
   #define INT_BITS 6
   #define FRAC_BITS 10
 #endif
-#define NSTATES 3
+#define NSTATES 2
 #include "control_types.h"
 
 #define NINPUTS 1
 #define NOUTPUTS 1
 #define INPUT_UPPERBOUND (__plant_precisiont)1
 #define INPUT_LOWERBOUND (__plant_precisiont)-1
-const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(0.9905),interval(0.075687),interval(0.021033) },
-                                                        {interval (0.125),interval(0),interval(0) },
-                                                        { interval(0),(0.015625),(0) }};
-const __plant_typet _controller_B[NSTATES] = { interval(16), interval(0),interval( 0) };
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.00003),interval(-0.00003)},
+                                                        {interval (1),interval(0) }};
+const __plant_typet _controller_B[NSTATES] = { interval(0.0078125), interval(0) };
 
 
 

### 2018-05-14 benchmark-runner/universalrunner/intervals.h

@@ -19,6 +19,7 @@ control_typet _dbl_max;
 control_typet _dbl_min;
 signed long int _fxp_one;
 control_typet _dbl_lsb;
+struct intervalt noise;
 
 void get_bounds()
 {
@@ -445,7 +446,6 @@ void bound_error(int_matrixt closed_loop,int_vectort K,int_vectort error_coeffs)
   }
   int_matrixt invIminA;
   inverse(invIminA,IminA);
-  struct intervalt noise;
   if (K[0].low>=0)
   {
    noise.low=K[0].low;

### 2018-05-14 benchmark-runner/universalrunner/safety_stability.c

@@ -405,6 +405,10 @@ int check_safety(void)
 
     #ifdef INTERVAL
       matrix_vector_mult(_AminusBK,_controller_states);
+      for (int j=0; j < NSTATES; j++)
+      {
+        _controller_states[j]=interval_add(_controller_states[j], noise);
+      }
     #endif
     #ifndef INTERVAL
         states_equals_A_states_plus_B_inputs(); //update states one time step
@@ -413,7 +417,7 @@ int check_safety(void)
     for(int i=0; i<NSTATES; i++)
     {
       #ifdef INTERVAL
-      if(_controller_states[i].low-error_coeffs[i].high>SAFE_STATE_UPPERBOUND || _controller_states[i].high+error_coeffs[i].high<SAFE_STATE_LOWERBOUND)
+      if(_controller_states[i].low/*-error_coeffs[i].high*/>SAFE_STATE_UPPERBOUND || _controller_states[i].high/*+error_coeffs[i].high*/<SAFE_STATE_LOWERBOUND)
         {return 0;}
       #else
       if(_controller_states[i]>SAFE_STATE_UPPERBOUND || _controller_states[i]<SAFE_STATE_LOWERBOUND)

### 2018-05-15 automatica/paper.tex
Corrections to Alessandro's comments

@@
 unfolding the transition system $k$ steps and by selecting a controller $K$ and a single initial state, 
-such that the states at each step do not violate the safety criteria \note{use specific formula}.  
+such that the states at each step do not violate the safety criteria (\reply{see Section~\ref{ssec:safespecification}}).  
 That is, we ask the bounded model checker \note{have we discussed the BMC earlier?} if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states.  
@@
 \item Compute the characteristic polynomial of the matrix $(A_d-B_dK)$ as 
-$P_a(z) = z^n+\sum_{i=1}^n{(a_i-k_i)z^{n-i}}$. 
+$P_a(z) = z^n+\sum_{i=1}^n{(a_i-k_i)z^{n-i}}$.  As with the na\"ive approach, this polynomial must satisfy Jury's criterion.
 \note{are we assuming to be working with a controllable form?
 should we emphasize that some elements are known, others are parameters?
-also, why do we use a different notation for this char poly than before?}
+also, why do we use a different notation for this char poly than before?
+\reply{[we don't need to talk about controllable form a we only use the characteristic polynomial, but we describe it in more detail because we work directly with the shape indicated here (a-k).}}   
 %\blue{[shouldn't there be a b term in the polynomial's coefficients here? No. the polynomial only evaluates the poles]}
@@
 %
-\note{pls refer to Figure 1, where however we had used capitalised Q1 and Q2 - pls fix.} 
-where  $q_1$ is the error introduced by the truncation in the ADC, 
-$q_2$ is the error introduced by the DAC, 
+where  $q_1$ is the error introduced by the truncation in the ADC (Q1 in Fig. \ref{fig:digitalsystem}), 
+$q_2$ is the error introduced by the DAC (Q2 in Fig. \ref{fig:digitalsystem}), 
 and $q_3$ is the maximum truncation and rounding error in $u_k=-K \cdot \mathcal{F}_{\langle I_c,F_c \rangle}(x_k)$, 
@@
 
-\item Calculate a set of initial bounds on $K$, $\phi_\mathit{init}^{K}$,
+\item Calculate a set of initial bounds on $K$, $\phi(K)=\phi_\mathit{init}^{K}$,
 based on the input constraints %\blue{[how is this practically done?With the equation below]}.  
 %
-$$(\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-K x_k)\Rightarrow \phi_\mathit{init}^{K}
+$$\phi_\mathit{init}^{K} := (\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-K x_k)
 $$
-\note{please explain the equation here: 
-what does the logical implication mean? 
-on the antecedent of this logical implication, you're taking the conjunction of two logical formulae (expressing two sets) and of a linear arithmetic expression}
 Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
-\note{In Figure 1, you're using a different formula than $\phi_\mathit{init}^{K}$, why? }
+\reply{The specification $\phi(K)$ will later be updated by the  {\sc abstract} phase to include the abstraction refinements.}
 
@@
   $\phi_\mathit{stability} \wedge \phi_\mathit{safety} \wedge \phi_\mathit{init}^{K}$ by invoking a SAT solver.  
+  The safety specification in the SAT formula is an over-approximation that has constraints for a given set of iterations ($k$) and initial values
   \note{the corresponding block in the figure accepts two inputs - can you comment on them?
@@
 So, explain block `Program search'.
-}
+\reply{the SAT solving and program search are exactly as in the naive approach.
+Only the formula changes.} }
 %%   We obtain it by solving the SAT formula 
@@
  \note{Ref Abstraction Verifier in Figure?}
-We next evaluate whether $\hat{X}^\# \models \phi_\mathit{safety}$ \note{how?}. 
-If the verification holds we have a solution, and exit the loop \note{ref PASS?}.  Otherwise, we
+\reply{We next evaluate whether $\hat{X}^\# \models \phi_\mathit{safety}$ using set inclusion (in our case, the faces of the polyhedra described by $\hat{X}^\#$ and $\phi_\mathit{safety}$ are aligned, so we only need to check that all the supports of $\hat{X}^\#$ are smaller).}
+If the verification holds we have a solution, and exit the loop with a PASS.  Otherwise, we
 find a counterexample iteration $k$ and corresponding initial point $x_0$
-for which the property does not hold, which we use to \note{locally refine the
-abstraction [how?]}.  When the abstraction cannot be further refined, we provide $(k, x_0)$ to the {\sc abstract} phase.
+for which the property does not hold, which we use to \reply{locally refine the
+abstraction by adding the constraint $\mat{A}^k\vec{x}_0 \models \phi_\mathit{safety}$}.  When the abstraction cannot be further refined, we provide $(k, x_0)$ to the {\sc abstract} phase.
 %
@@
 \begin{enumerate}
-\item Find the constraints that invalidate the property as a set of counterexamples for the eigenvalues \note{sure, but how?}, which we define as $\phi_\Lambda$. 
+\item Find the constraints that invalidate the property \reply{($\{ k, x_0 : \mat{A}^k\vec{x}_0 \not \models \phi_\mathit{safety}\}$) as a set of counterexamples for the eigenvalues, which we define as $\phi_\Lambda=\{ k, x_0 : \mat{J}^k\mat{S}^{-1}\vec{x}_0 \models \phi_\mathit{safety}\}$}.
 This is a constraint in the spectrum i.e., transfer function) of the closed-loop dynamics.  
@@
   \path
-    ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {$K$} ([xshift=0.6cm]synth.south) 
-    ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$(\phi(K),k)$} ([xshift=-.6cm]KSAT.north)
+    ([xshift=-.6cm]KSAT.north) edge[left] node[xshift=-.1cm] {UNSAT / $K$} ([xshift=-0.6cm]synth.south) 
+    ([xshift=.6cm]synth.south) edge node[align=center,xshift=.1cm] {$(\phi(K),k)$} ([xshift=.6cm]KSAT.north)
     ([yshift=.5cm]AAV.east) edge node{\sl $\hat{X}^\#$} ([yshift=.5cm]AAC.west)
@@
 are determined by the controller.  We pick $I_p$ and $F_p$ for our synthesis
-such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$ (\reply{so that our controller can be represented accurately in the plant domain}).  
+such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$, \reply{so that our controller can be represented accurately in the plant domain}).  
 Thus any mathematical operations in our modelled digital controller will be in the

### 2018-05-15 automatica/paper.tex
rephrased the objective EG2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-\item[EG2] \textbf{(Sanity check)} Confirm the
-stability and safety of the synthesized controllers \note{[this is unclear, rephrase:]outside of our model.}
+\item[EG2] \textbf{(Sanity check)} \textcolor{blue}{Confirm the stability and safety of the synthesized controllers outside 
+of our model representation using MATLAB}.
 

### 2018-05-15 automatica/paper.tex
expanded the description of floating-point format
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 We provide the results in Table~\ref{tab:results}, 
-where \textit{Benchmark} is the name of the respective benchmark, 
-\textit{Order} is the number of continuous variables of the model, 
-$\mathcal{F}_{\langle I_p,F_p \rangle}$ and $\mathcal{F}_{\langle p \rangle}$  
-are the fixed- and floating-point precisions used to model the plant, respectively,  
+where \textit{Benchmark} is the name of the respective benchmark; 
+\textit{Order} is the number of continuous variables of the model; \textcolor{blue}{ 
+$\mathcal{F}_{\langle I_p,F_p \rangle}$, where $I_p$ and $F_p$ indicate the integer and fractional parts,  
+and \textcolor{blue}{ $\mathcal{F}_{\langle W_p,F_p \rangle}$}, where $W_p$ and $F_p$ indicate the total word-length and fractional part, 
+are the fixed- and floating-point precisions used to model the plant, respectively; } 
 and \textit{Time} is the total time required to synthesize a controller for the given plant.    
-Timeouts are indicated by~\xmark.  \note{ we should distinguish between timeouts and failures to synthesise. }
+Timeouts are indicated by~\xmark, \textcolor{blue}{while failures to synthesise the digital controllers are indicated by $\dagger$}.
 The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
-chosen to be $I_c = 8$, $F_c = 8$ for fixed-point, whereas  
-$\mathcal{F}_{\langle p \rangle}$ is chosen to be half-precision for floating-point. \note{what about $\mathcal{F}_{\langle I_p,F_p \rangle}$?}
+chosen to be $I_c = 8$, $F_c = 8$ for fixed-point, \textcolor{blue}{whereas  
+$\mathcal{F}_{\langle W_c, F_c \rangle}$ is chosen to be $W_c = 16$ and $F_c = 10$
+for half-precision floating-point format}.
 
@@
 \# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                 & \multicolumn{4}{|c|}{Abstraction} \\
-   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
+   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle W_p, F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle W_p, F_p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
 1  & Acrobot  & 4 &  & \xmark &  & ~\xmark & & ~\xmark &  & ~\xmark \\

### 2018-05-15 automatica/paper.tex
address abate's comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 
-The median run-time for \note{the successful} benchmarks is 6.6\,s for the fixed-point and 5.45\,s for floating-point implementations, respectively.  
+The median run-time for \textcolor{blue}{the successful} benchmarks is 6.6\,s for the fixed-point and 5.45\,s for floating-point implementations, respectively.  
 We consider these times short enough to be of practical use to control engineers, and thus affirm the validity of EG1.
 
-There are \note{a few [you mean half!]} instances for which both approaches fail to synthesise a controller.  
+\textcolor{blue}{Both approaches fail to synthesise a controller half of the instances.}  
 For the multi-stage approach, the completeness threshold may be too large, thus causing a timeout.  

### 2018-05-15 automatica/paper.tex
address abate's comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 For the majority of the {\it fixed-point} benchmarks, we observe that the abstraction-based
-back-end is faster than the basic multi-staged verification approach, and
-finds a solution for more benchmarks (14) than the multi-staged back-end (13) \note{we should clarify that this is out of 26 in total, not 191?}.  
+back-end is faster than the basic multi-staged verification approach; \textcolor{blue}{additionally, 
+from 26 benchmarks, we observed that the abstraction-based back-end finds a solution for more benchmarks 
+(14) than the multi-staged back-end (13)}.
+%\note{we should clarify that this is out of 26 in total, not 191?}  
 In direct comparison, the abstraction-based approach is on average able to find a
@@
 
-\textcolor{blue}{Both approaches fail to synthesise a controller half of the instances.}  
+\textcolor{blue}{Both approaches fail to synthesise a controller for half of the instances.}  
 For the multi-stage approach, the completeness threshold may be too large, thus causing a timeout.  

### 2018-05-16 automatica/paper.tex
fixes

@@
 evaluate all possible progressions of the model simultaneously. 
-Additionally, this approach uses \emph{abstraction refinement} \note{add cit.},
+Additionally, this approach uses \emph{abstraction refinement} \cite{DBLP:conf/cav/ClarkeGJLV00},
 enabling one to start with a very simple (abstract) description of the model 
@@
 \note{Next paragraph is naive for a control audience - amend} 
-A~state-space model
-has known advantages over the transfer function
-representation~\cite{Franklin15}: it naturally generalizes to multivariate
-systems (i.e., with multiple inputs and outputs); and it allows synthesis of
-control systems with guarantees on the internal dynamics, e.g., to
-synthesize controllers that make the closed-loop system \emph{safe}.  Our
-work focuses on the \emph{safety} of internal states, which is usually
-overlooked in the literature.  Moreover, our work integrates an
-abstraction/refinement (CEGAR) step inside the main CEGIS loop.
-
-The tool Pessoa~\cite{mazo2010pessoa} synthesizes correct-by-design embedded
-control software in a Matlab toolbox.  It is based on the abstraction of a
-physical system to an equivalent finite-state machine and on the computation
-of reachability properties thereon.  Based on this safety specification,
-\mbox{Pessoa} can synthesize embedded controller software for a range of
-properties.  The embedded controller software can be more complicated than
-the state-feedback control we synthesize, and the properties available cover
-more detail.  However, relying on state-space discretization \mbox{Pessoa}
-is likely to incur in scalability limitations.  \note{Mention SCOTS?}
-Along this research line,
-\cite{Anta2010,liu16} studies the synthesis of digital controllers for
-continuous dynamics, and \cite{zamani2014} extends the approach to the Network Control Systems setup.
+A~state-space model has known advantages over the transfer function
+representation~\cite{Franklin15}, as 
+% it naturally generalizes to multivariate systems (i.e., with multiple inputs and outputs); and 
+it allows synthesis of controllers with guarantees on the internal dynamics, e.g., 
+%to synthesize controllers that make the closed-loop model 
+\emph{safety}.  Our work indeed focuses on the \emph{safety} of internal states, which is usually
+overlooked in the standard control literature with its default focus on stability properties.  
+Moreover, our work integrates an abstraction/refinement (CEGAR) step inside the main CEGIS loop.
+
+The approach underpinning tools such as Pessoa~\cite{mazo2010pessoa} and related extensions \cite{Anta2010,liu16} and applications \cite{zamani2014}, 
+synthesizes correct-by-design embedded control software for LTI models.    
+It is based on the abstraction of the model to a finite-state machine, 
+and on the formal control synthesis over safety- and reachability-based temporal properties thereon.  
+%Based on this safety specification, \mbox{Pessoa} can synthesize embedded controller software for a range of
+%properties.  
+The controller software can then be refined (implemented) over the concrete LTI model. 
+%can be more complicated than
+%the state-feedback control we synthesize, and the properties available cover more detail.  
+However, relying on state-space discretization \mbox{Pessoa} is likely to incur in scalability limitations.   
+%Along this research line, \cite{Anta2010,liu16} studies the synthesis of digital controllers for
+%continuous dynamics, and \cite{zamani2014} extends the approach to the Network Control Systems setup.
 

### 2018-05-16 automatica/paper.tex
fixes

@@
 
-\emph{The first approach} uses a na\"ive technique that starts by devising a
+\emph{The first approach} uses a multi-staged technique that starts by devising a
 digital controller that stabilizes the plant model while remaining safe for a
@@
 %% %
-\item We provide two novel algorithms: the first, a na\"ive approach, relies on 
+\item We provide two novel algorithms: the first, a multi-staged approach, relies on 
   an unfolding of the dynamics up to a completeness threshold, while the
@@
 \cite{JSS14} details algorithms to compute such set, 
-whereas \cite{cattaruzza2015unbounded} extends this to LTI models with inputs as in \note{Eqn. XX}.  
+whereas \cite{cattaruzza2015unbounded} extends this to LTI models with inputs as in Eqn. \eqref{eq:plant}.  
 In view of the overall goal of this work, 
@@
 This is defined as a polyhedron, expressed as an intersection of hyperplanes. 
-A tight polyhedron that can be obtained with faces (hyperplanes) that touch the set. 
-\reply{This is achieved by picking a number of points in the set, and finding a hyperplane
-tangent to that point w.r.t. dynamics.  Inorder to simplify this procedure, we
-look at two-dimensional cuts of the space, one at a time (i.e., for every pair
-of eigenvalues of the closed loop dynamics, we find a hyperplane tangent to
+A tight polyhedron can be obtained with hyperplanes that are tangent to the set,  
+which is achieved by selecting a number of points \note{on the boundary} of the set, 
+and finding corresponding hyperplanes that are tangent to those points with respect to the dynamics.  
+\note{[you are essentially taking the Lie derivative of the set wrt the dynamics at the selected point?]}
+In order to simplify this procedure, we look at two-dimensional cuts \note{projection?} of the space, one at a time (i.e., for every pair
+of eigenvalues of the closed-loop dynamics, we find a hyperplane tangent to
 the progression of that pair in a two dimensional space and use it as a face of
 the polyhedron).  The difference with~\cite{cattaruzza2015unbounded} is that
-in the continuous case, the tangent is found by derivation rather than
-differentialtion, thus including all intermediate points in the arc.}
+in the continuous case, the tangent is found by derivation \note{cf. `Lie derivative' above} rather than
+differentialtion, thus including all intermediate points \note{[?] in the arc}.
 
@@
 the second one is {\it abstraction-based}, 
-and it leverages abstraction-refinement \note{ cit.} and acceleration \note{ref to relevant section} to improve scalability,  
+and it leverages abstraction-refinement \cite{DBLP:conf/cav/ClarkeGJLV00} and acceleration (cf. Sec.~\ref{ssec:aa}) to improve scalability,  
 while retaining soundness.
@@
 stability criteria, we require that a computed polynomial satisfies Jury's
-criterion~\cite{fadali} (\reply{see Section~\ref{ssec:stabspecification}}).
+criterion~\cite{fadali} (see Section~\ref{ssec:stabspecification}).
 
@@
 unfolding the transition system $k$ steps and by selecting a controller $K$ and a single initial state, 
-such that the states at each step do not violate the safety criteria (\reply{see Section~\ref{ssec:safespecification}}).  
+such that the states at each step do not violate the safety criteria (see Section~\ref{ssec:safespecification}).    
 That is, we ask the bounded model checker \note{have we discussed the BMC earlier?} if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states.  
@@
 
-%  The na\"ive approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
+%  The multi-staged approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
   %uses a multi-staged verification phase and performs solution generalization based on
@@
 
-%% Our na\"ive approach
+%% Our multi-staged approach
 %% creates an abstraction of the system by establishing bounds on the
@@
 \item Compute the characteristic polynomial of the matrix $(A_d-B_dK)$ as 
-$P_a(z) = z^n+\sum_{i=1}^n{(a_i-k_i)z^{n-i}}$.  As with the na\"ive approach, this polynomial must satisfy Jury's criterion.
+$P_a(z) = z^n+\sum_{i=1}^n{(a_i-k_i)z^{n-i}}$.  As with the multi-staged approach, this polynomial must satisfy Jury's criterion.
 \note{are we assuming to be working with a controllable form?
@@
 \reply{[we don't need to talk about controllable form a we only use the characteristic polynomial, but we describe it in more detail because we work directly with the shape indicated here (a-k).}}   
+\note{but, this very shape of the characteristic polynomial holds only for LTI models in controllable canonical form.}
 %\blue{[shouldn't there be a b term in the polynomial's coefficients here? No. the polynomial only evaluates the poles]}
@@
 are determined by the controller.  We pick $I_p$ and $F_p$ for our synthesis
-such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$, \reply{so that our controller can be represented accurately in the plant domain}).  
+such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$, so that our controller can be represented accurately in the plant domain).  
 Thus any mathematical operations in our modelled digital controller will be in the

### 2018-05-16 automatica/paper.tex
formatting
re-doing errors

@@
   DBLP:conf/asplos/Solar-LezamaTBSS06}, 
-  a technique from formal methods that has recently shown much promise and which we export in this work to a control-theoretical setup.  
+  a technique from formal methods that has recently shown much promise and which we 
+  export in this work to a control-theoretical setup.  
 CEGIS is an iterative process, where each iteration performs inductive
@@
 
-\item While~\cite{DBLP:conf/cav/AbateBCCDKKP17} is restricted to models in discrete time, in the current paper we present an approach for
+\item While~\cite{DBLP:conf/cav/AbateBCCDKKP17} is restricted to models in discrete 
+time, in the current paper we present an approach for
   soundly evaluating safety in combined continuous-discrete time and space.
@@
 
-\note{back end vs back-end?}
-
-We account for the presence of errors originating from a number of sources, shown in Figure~\ref{} \note{fix}:
+We account for the presence of errors originating from a number of sources, shown in Figure~\ref{fig:digitalsystem}:
 \begin{itemize}
@@
 It is necessary to account for the errors introduced by this representation: 
-we account for these errors in both back ends \note{did we explain the two back ends already?} by using interval arithmetic, as detailed in section~\ref{} \note{fix}. 
+we account for these errors in both approaches by using standard interval arithmetic. 
 \item The quantisation errors by the ADC, which converts the analogue signal $x(t)$ into the digital signal $x_k$, 
-which is then fed into the controller \note{cf. Figure~\ref{} }. 
-We account for this error in the acceleration-based back-end by introducing a noise signal $\nu_1$ that over-approximates it. Further details are found in section~\ref{}.  
-In the naive back-end we use bit-precise modelling in \note{[clear? discussed before?] CBMC}~\cite{} to accurately encompass this conversion.   
-In other words, CBMC constructs a boolean formula that explicitly unwinds the transition system for any \note{[unclear] symbolically represented} input state, 
-\note{[unclear how the initial conditions bound the input state? use formulas or figure to explain.] bounded by the initial conditions}, 
-and performs the ADC conversion precisely on that symbolically represented input state. 
-When we check for a safety property, 
-the boolean formula is satisfied only if there is an input state value for which the subsequent trace through the transition system eventually violates the safety property.  
+which is then fed into the controller cf. Figure~\ref{fig:digitalsystem}. 
+We account for this error in the acceleration-based back-end by introducing a noise signal $\nu_1$ that over-approximates it. Further details are found in section~\ref{sssec:abstraction}.  
+In the multi-stage back-end we use bit-precise modelling in CBMC~\cite{ClarkeKL04}, a bounded model checker for C-programs, to accurately encompass this conver- sion.
+In other words, CBMC constructs a boolean formula that explicitly unwinds the transition system for symbolically represented inital states.
+The possi- ble bounds that this symbolically represented initial state may take are restricted by upper and lower bounds as described in section .
+The boolean formula constructed by CBMC models the ADC conversions precisely on the symbolically represented states at every time step.
+When we check for a safety prop- erty, the boolean formula is satisfied only if there is an input state value for which the subsequent trace through the transition system eventually violates the safety property.
 \item The representation errors due to performing finite-precision arithmetic in the controller block. 
@@
 in the same way as we handled the ADC conversion. 
-We assume that the controller represents numbers to the same precision as the ADC \note{why is this legit?}. 
-\item We assume \note{why is this reasonable?} that the DAC converts numbers to analogue signals with the same precision as the controller. 
-As a result we can ignore any additional errors introduced by the DAC.  
+We assume that the ADC represents numbers to the same precision as the controller, or higher, and thus the precision is limited by the controller. 
+\item We assume that the DAC converts numbers to analogue signals with the same precision as the controller. 
+As a result we can ignore any additional errors introduced by the DAC.  Both the assumptions about the ADC and the DAC are reasonable assumptions based on commonly available hardware. 
 \end{itemize}
@@
 are determined by the controller.  We pick $I_p$ and $F_p$ for our synthesis
-such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$, so that our controller can be represented accurately in the plant domain).  
+such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$, so that our controller 
+can be represented accurately in the plant domain).  
 Thus any mathematical operations in our modelled digital controller will be in the
@@
 represented in a floating point domain, with $E$ bits representing the exponent
-part and $M$ bits representing the mantissa part. Bounds for errors introduced by performing basic mathematical operators at this precision can be derived~\cite{DBLP:conf/arith/BrainTRW15}.
-
-We use $\mathcal{F}_{\langle E_c,M_c \rangle}(x)$ to denote a real number represented at the floating-point precision of the controller, and $\mathcal{F}_{\langle E_p,M_p \rangle}(x)$ to denote a real number represented at the fixed-point precision of the plant model.
-We apply the same principles as in the preceding section when selection the plant precision.
+part and $M$ bits representing the mantissa part. Bounds for errors introduced by 
+performing basic mathematical operators at this precision can be derived~\cite{DBLP:conf/arith/BrainTRW15}.
+
+We use $\mathcal{F}_{\langle E_c,M_c \rangle}(x)$ to denote a real number 
+represented at the floating-point precision of the controller, and 
+$\mathcal{F}_{\langle E_p,M_p \rangle}(x)$ to denote a real number 
+represented at the fixed-point precision of the plant model. We apply 
+the same principles as in the preceding section when selection the plant precision.
 
@@
 In this section we describe how quantization errors can be modelled as noise. 
-Note that this is only applicable to the acceleration back end, as the multi-stage back end makes use of CBMC's bit-precise model checking capabilities to account for these deterministic errors.
+Note that this is only applicable to the acceleration back end, as the multi-stage back 
+end makes use of CBMC's bit-precise model checking capabilities to account 
+for these deterministic errors.
 

### 2018-05-16 automatica/paper.tex
fixing fixedpoint notation

@@
 \subsection{Errors}
+\label{sec:errors}
 
@@
 
+\subsection{Notation for fixed-point precision}
+
+In this paper we will use $\mathcal{F}_{\langle I,F \rangle}(x)$ to denote a real number
+$x$ represented at a fixed-point precision using $I$ bits to represent the integer part of the number
+and $F$ bits to represented the decimal part.
+
+$\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real
+number $x$ represented at the fixed-point precision of the controller, and
+$\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$
+represented at the fixed-point precision of the plant model ($I_c$ and $F_c$
+are determined by the controller.  We pick $I_p$ and $F_p$ for our synthesis
+such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$, so that our controller 
+can be represented accurately in the plant domain).  
+Thus any mathematical operations in our modelled digital controller will be in the
+range of $\mathcal{F}_{\langle I_c,F_c \rangle}$, and all other calculations
+in our model will be carried out in the range of $\mathcal{F}_{\langle
+I_p,F_p \rangle}$.  The physical plant operates in the reals, which means
+our verification phase must also account for the numerical error and
+quantization errors caused by representing the physical plant at the finite
+precision $\mathcal{F}_{\langle I_p,F_p \rangle}$.
+
+We use $\mathcal{F}_{\langle E,M \rangle}(x)$ to denote a real number $x$
+represented in a floating point domain, with $E$ bits representing the exponent
+part and $M$ bits representing the mantissa part.
+
+We use $\mathcal{F}_{\langle E_c,M_c \rangle}(x)$ to denote a real number 
+represented at the floating-point precision of the controller, and 
+$\mathcal{F}_{\langle E_p,M_p \rangle}(x)$ to denote a real number 
+represented at the fixed-point precision of the plant model. 
 %-------------------------------
@@
 such that the states at each step do not violate the safety criteria (see Section~\ref{ssec:safespecification}).    
-That is, we ask the bounded model checker \note{have we discussed the BMC earlier?} if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states.  
-This is sound if the current $k$ is greater than the completeness threshold (see later step).  
+That is, we ask the bounded model checker~\cite{ClarkeKL04} if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states, and a given fixed point precision for the controller, and where the input signal remains within the specified bounds.
+This approach sound if the current $k$ is greater than the completeness threshold (see later step).  
 We~also assume some (fixed or floating point) precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  
 The checks that these assumptions hold are performed by subsequent {\sc verify} stages.
-\note{we have not discussed the bounds on the input signal. }
 
@@
 
-\item The first {\sc verify} stage, {\sc safety}, checks that the candidate
+\item The first {\sc verify} stage, {\sc safety}, shown in alg.~\ref{alg:safetycheck}, checks that the candidate
 solution $K$, which we synthesized to be safe for at least one initial
 state, is safe for \emph{all} possible initial states, i.e., does not reach
-an unsafe state within $k$ steps \note{where we assume $k$ to be under the
-completeness threshold}.  After unfolding the transition system corresponding
+an unsafe state within $k$ steps.  After unfolding the transition system corresponding
 to the previously synthesized controller $k$ steps, we check that the safety
-specification holds for any initial state. This is shown in Alg.~~\ref{alg:safetycheck}.
+specification holds for any initial state.
 
@@
 completeness threshold $\overline{k}$ for the current candidate controller $K$ and
-check that $k{\geq}\overline{k}$.  This is done according to the argument
-given above and illustrated in Fig.~\ref{fig:ct}. 
-\note{it is not clear how we find $\overline{k}$.}
+check that $k{\geq}\overline{k}$.  This is done by computing the number of time steps
+required for the states to have completed a 360\textdegree circle as illustrated in Fig.~\ref{fig:ct}.
 
@@
 
-Checking that the safety specification holds for any initial state can be
-computationally expensive if the bounds on the allowed initial states are
-large. \note{we have not discussed the bounds on the input signal. }
+%Checking that the safety specification holds for any initial state can be
+%computationally expensive if the bounds on the allowed initial states are
+%large. \note{we have not discussed the bounds on the input signal. }
 
@@
 
-As discussed in \note{Section~\ref{sec:}}, 
+As discussed in Section~\ref{sec:errors}, 
 the models we consider have to account for errors from several sources: 
@@
 
-Let $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$
+Recall we use $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$
 represented in a fixed point domain, with $I$ bits representing the integer
@@
 
-\subsection{Notations}
-
-\note{If these notations are used in earlier Sections, shall we anticipate the paragraph to the preliminaries? }
-
-In this paper we will use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real
-number $x$ represented at the fixed-point precision of the controller, and
-$\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$
-represented at the fixed-point precision of the plant model ($I_c$ and $F_c$
-are determined by the controller.  We pick $I_p$ and $F_p$ for our synthesis
-such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$, so that our controller 
-can be represented accurately in the plant domain).  
-Thus any mathematical operations in our modelled digital controller will be in the
-range of $\mathcal{F}_{\langle I_c,F_c \rangle}$, and all other calculations
-in our model will be carried out in the range of $\mathcal{F}_{\langle
-I_p,F_p \rangle}$.  The physical plant operates in the reals, which means
-our verification phase must also account for the numerical error and
-quantization errors caused by representing the physical plant at the finite
-precision $\mathcal{F}_{\langle I_p,F_p \rangle}$.
-
-\note{also introduce notations for floats?}
-
-\subsection{Floating-point representation}
-
-\note{Notice that this notation is different than the one used in the results section. pls fix. }
-
-Let $\mathcal{F}_{\langle E,M \rangle}(x)$ denote a real number $x$
-represented in a floating point domain, with $E$ bits representing the exponent
-part and $M$ bits representing the mantissa part. Bounds for errors introduced by 
-performing basic mathematical operators at this precision can be derived~\cite{DBLP:conf/arith/BrainTRW15}.
-
-We use $\mathcal{F}_{\langle E_c,M_c \rangle}(x)$ to denote a real number 
-represented at the floating-point precision of the controller, and 
-$\mathcal{F}_{\langle E_p,M_p \rangle}(x)$ to denote a real number 
-represented at the fixed-point precision of the plant model. We apply 
-the same principles as in the preceding section when selection the plant precision.
-
-\subsection{ADC/DAC quantization errors} 
+Similar bounds for errors introduced by 
+performing basic mathematical operators in floating-point precision can be derived~\cite{DBLP:conf/arith/BrainTRW15}.
+
+\subsection{ADC/DAC quantization errors modelled as noise} 
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 During any given ADC conversion, the continuous signal will be sampled in
-the real domain and transformed by $\mathcal{F}\langle I_{c},F_{c} \rangle
+the real domain and transformed by $\mathcal{F}_{\langle I_{c},F_{c} \rangle}
 (x)$ (assuming the ADC discretization is the same as the digital
@@
 %
-$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k :
+$$\mathcal{F}_{\langle I_{c},F_{c} \rangle}(y(t)) = y_k :
 y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right] \,.$$
@@
 
-We will assume, for the purposes of this analysis, that the domain of the
+As stated before, we assume that the domain of the
 ADC is that of the digital controller (i.e, the quantizer includes any
 digital gain added in the code).  The process of quantization in the DAC is
-similar except that it is calculating $\mathcal{F}\langle I_{dac},F_{dac}
-\rangle (\mathcal{F}\langle I_{c},F_{c} \rangle (x)) $.  If these domains
+similar except that it is calculating $\mathcal{F}_{\langle I_{dac},F_{dac}
+\rangle} (\mathcal{F}_{\langle I_{c},F_{c} \rangle }(x)) $.  If these domains
 are the same ($I_{c}=I_{dac},\allowbreak F_{c}=F_{dac}$), or if the DAC
@@
 This induces two types of the errors detailed above: first, the truncation
-error due to representing $x_k$ as $\mathcal{F}{\langle I_c,F_c
+error due to representing $x_k$ as $\mathcal{F}_{\langle I_c,F_c
 \rangle}(x_{k})$; and second, the rounding error introduced by the
@@
 \# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                 & \multicolumn{4}{|c|}{Abstraction} \\
-   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle W_p, F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle W_p, F_p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
+   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
 1  & Acrobot  & 4 &  & \xmark &  & ~\xmark & & ~\xmark &  & ~\xmark \\

### 2018-05-16 automatica/paper.tex
fixes

@@
 
-\note{Anticipate here connection with characteristic polynomial?}
+\note{Anticipate here connection with characteristic polynomial? See Section 4.}
 
@@
 \end{equation*}
-\note{The characteristic polynomial $S(z)$ represents the dynamical model in \ldots }
+\note{The characteristic polynomial $S(z)$ represents the dynamical model in \ldots [clarify whether we use the CPol to describe the open- or closed-loop model. Relate parameters to matrices A,B,K. ]}
 %\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?} 
@@
 with reference to the CEGIS scheme in Figure~\ref{fig:CEGIS}, 
-we describe in detail the different phases in Fig.~\ref{fig:CEGIS-precision-increment} (blocks 1 to 4).
+we describe in detail the different phases in Fig.~\ref{fig:CEGIS-precision-increment} (shaded blocks 1 to 4).
 
@@
 
-\item The first {\sc verify} stage, {\sc safety}, shown in alg.~\ref{alg:safetycheck}, checks that the candidate
+\item The first {\sc verify} stage, {\sc safety}, shown in Alg.~\ref{alg:safetycheck}, checks that the candidate
 solution $K$, which we synthesized to be safe for at least one initial
@@
 \item The second {\sc verify} stage, {\sc precision}, 
- restores soundness with respect to the plant's precision
+ restores soundness with respect to the plant precision
 by using interval arithmetic \cite{moore1966interval} to validate the 
@@
 check that $k{\geq}\overline{k}$.  This is done by computing the number of time steps
-required for the states to have completed a 360\textdegree circle as illustrated in Fig.~\ref{fig:ct}.
+required for the states to have completed a 360\textdegree circle, as illustrated in Fig.~\ref{fig:ct}. 
+\note{This is only for spiralling dynamics.}
 

### 2018-05-16 automatica/paper.tex
fixes

@@
 \end{equation*}
-\note{The characteristic polynomial $S(z)$ represents the dynamical model in \ldots [clarify whether we use the CPol to describe the open- or closed-loop model. Relate parameters to matrices A,B,K. ]}
+\note{The characteristic polynomial $S(z)$ represents the dynamical model in \ldots [clarify whether we use the CPol to describe the open- or closed-loop model.
+Relate parameters to matrices A,B,K.
+Notice that these parameters are used later in the Section where AA-based backend is explained.]}
 %\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?} 
@@
 
-\note{we need to refer to the parts of Algorithm 1 more closely - point to specific lines in the explanation below.}
+%\note{we need to refer to the parts of Algorithm 1 more closely - point to specific lines in the explanation below.}
 
@@
 \State assert($ \underline{u}  \leq u \leq \overline{u}$)
- \State set $x_0$ to be a vertex state, e.g., $[\underline{x_0},\underline{x_0}]$	
+ \State set $x_0$ to be a \note{vertex state}, e.g., $[\underline{x_0},\underline{x_0}]$	
 \For {($c=0;~c < 2^\mathit{Num\_States};~c\mbox{++}$)}
@@
 required for the states to have completed a 360\textdegree circle, as illustrated in Fig.~\ref{fig:ct}. 
-\note{This is only for spiralling dynamics.}
+\note{This is only for spiralling dynamics - more generally, we need to clarify how the CT is computed. }
 
@@
 over an abstraction of the continuous dynamics \cite{cattaruzza2015unbounded} that conforms to witness proofs at specific times.   
-Moreover, this approach uses abstraction-refinement, 
+Moreover, this approach uses abstraction-refinement \cite{DBLP:conf/cav/ClarkeGJLV00},  
 enabling one to start with a very simple description of the dynamics regardless of the model complexity (abstraction step), 
@@
 \item Calculate a set of initial bounds on $K$, $\phi(K)=\phi_\mathit{init}^{K}$,
-based on the input constraints %\blue{[how is this practically done?With the equation below]}.  
-%
-$$\phi_\mathit{init}^{K} := (\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-K x_k)
+based on the constraints %\blue{[how is this practically done?With the equation below]}.  
+%
+$$
+\phi_\mathit{init}^{K} := (\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-K x_k)
 $$
 Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
-\reply{The specification $\phi(K)$ will later be updated by the  {\sc abstract} phase to include the abstraction refinements.}
+The specification $\phi(K)$ will later be updated by the  {\sc abstract} phase to include the possible refinements.
 
@@
   that satisfies
-  $\phi_\mathit{stability} \wedge \phi_\mathit{safety} \wedge \phi_\mathit{init}^{K}$ by invoking a SAT solver.  
+  $\phi_\mathit{stability} \wedge \phi_\mathit{safety} \wedge \phi_\mathit{init}^{K}$ \note{you mean $\phi (K)$?} by invoking a SAT solver.  
   The safety specification in the SAT formula is an over-approximation that has constraints for a given set of iterations ($k$) and initial values

### 2018-05-16 automatica/paper.tex
fixes

@@
   $\phi_\mathit{stability} \wedge \phi_\mathit{safety} \wedge \phi_\mathit{init}^{K}$ \note{you mean $\phi (K)$?} by invoking a SAT solver.  
-  The safety specification in the SAT formula is an over-approximation that has constraints for a given set of iterations ($k$) and initial values
-  \note{the corresponding block in the figure accepts two inputs - can you comment on them?
-also: is this SAT solving step obvious?
-Sat solvers resolve Boolean formulae, but here we have something else.
-So, explain block `Program search'.
-\reply{the SAT solving and program search are exactly as in the naive approach.
-Only the formula changes.} }
+  The safety specification in the SAT formula \note{[clarify:] is an over-approximation} that has constraints for a given set of iterations ($k$) \note{and initial values [conditions?]}.  
+ The program search algorithm is as in the multi-staged approach.  
 %%   We obtain it by solving the SAT formula 
@@
 %
-As we require to verify the system for every $k$ up to infinity, 
+As we require to verify the closed-loop model for any $k$ up to infinity, 
 we use Abstract Acceleration again to compute the reach-tube, 
@@
 abstract matrices for the closed-loop system~\cite{cattaruzza2015unbounded},
-whereas the set $N$ is obtained from above.
-
- \note{Ref Abstraction Verifier in Figure?}
-\reply{We next evaluate whether $\hat{X}^\# \models \phi_\mathit{safety}$ using set inclusion (in our case, the faces of the polyhedra described by $\hat{X}^\#$ and $\phi_\mathit{safety}$ are aligned, so we only need to check that all the supports of $\hat{X}^\#$ are smaller).}
+whereas the set $N$ is obtained above.
+
+We next evaluate whether $\hat{X}^\# \models \phi_\mathit{safety}$ using set inclusion, cf. Section \ref{sec:cont_aasup}: 
+the faces of the polyhedra described by $\hat{X}^\#$ and $\phi_\mathit{safety}$ are aligned, so we only need to check that all the supports of $\hat{X}^\#$ are smaller.   
 If the verification holds we have a solution, and exit the loop with a PASS.  Otherwise, we
-find a counterexample iteration $k$ and corresponding initial point $x_0$
-for which the property does not hold, which we use to \reply{locally refine the
-abstraction by adding the constraint $\mat{A}^k\vec{x}_0 \models \phi_\mathit{safety}$}.  When the abstraction cannot be further refined, we provide $(k, x_0)$ to the {\sc abstract} phase.
+find a counterexample iteration $k$ and corresponding initial condition $x_0$
+for which the property does not hold, which we use to locally refine the
+abstraction by adding the constraint $\mat{A}^k\vec{x}_0 \models \phi_\mathit{safety}$ \note{how is this local refinement practically performed?}.  
+When the abstraction cannot be further refined, we provide $(k, x_0)$ to the {\sc abstract} phase.
 %
@@
 \item Find the constraints that invalidate the property \reply{($\{ k, x_0 : \mat{A}^k\vec{x}_0 \not \models \phi_\mathit{safety}\}$) as a set of counterexamples for the eigenvalues, which we define as $\phi_\Lambda=\{ k, x_0 : \mat{J}^k\mat{S}^{-1}\vec{x}_0 \models \phi_\mathit{safety}\}$}.
-This is a constraint in the spectrum i.e., transfer function) of the closed-loop dynamics.  
+This is a constraint for the spectrum of the closed-loop dynamics.  
 \item We use $\phi_\Lambda$ to

### 2018-05-16 automatica/paper.tex
fixes

@@
 %-------------------------------
- \subsubsection{Abstract Supports for Continuous Dynamics}
+ \subsubsection{Abstract Supports for Continuous-Time Dynamics}
  \label{sec:cont_aasup}
@@
 differentialtion, thus including all intermediate points \note{[?] in the arc}.
+
+\note{So the case study section should emphasise that the AA-based back-end can handle continuous-time benchmarks/models? 
+It seems like the discussion in this section is not reflected on the case study section yet. }
 
@@
 whereas the set $N$ is obtained above.
+
+\note{What about the continuous-time abstract acceleration? Where in the case studies? }
 
@@
 
-\item[EG2] \textbf{(Sanity check)} \textcolor{blue}{Confirm the stability and safety of the synthesized controllers outside 
-of our model representation using MATLAB}.
+\item[EG2] \textbf{(Sanity check)} Confirm the stability and safety of the synthesized controllers outside 
+of our model representation using MATLAB. \note{Where is this done?}
 
 \end{enumerate}
-
-\note{Perhaps rather than `safety check' we could speak about robustness to changes in sampling time.}
 
@@
 and \textit{Time} is the total time required to synthesize a controller for the given plant.    
-Timeouts are indicated by~\xmark, \textcolor{blue}{while failures to synthesise the digital controllers are indicated by $\dagger$}.
+Timeouts are indicated by~\xmark, while failures to synthesise the digital controllers are indicated by $\dagger$.  
 The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
@@
 benchmarks is limited within the scope of this paper and the performance may
-not generalize to other benchmarks.\\
-%
+not generalize to other benchmarks.\note{is this where we attempt asserting EG2?}
+
 \textit{Plant precision and discretization heuristics:} Our algorithm to
@@
 performance may suffer in some cases, for example if the completeness
-threshold is high.\\
-%
+threshold is high.
+
 \textit{Abstraction on other properties:} The performance gain from abstract

### 2018-05-16 automatica/paper.tex
fixes

@@
 part and $M$ bits representing the mantissa part. 
-
-We use $\mathcal{F}_{\langle E_c,M_c \rangle}(x)$ to denote a real number 
+In particular, we use $\mathcal{F}_{\langle E_c,M_c \rangle}(x)$ to denote a real number 
 represented at the floating-point precision of the controller, and 

### 2018-05-16 automatica/paper.tex
added description about EG2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@
 \item[EG2] \textbf{(Sanity check)} Confirm the stability and safety of the synthesized controllers outside 
-of our model representation using MATLAB. \note{Where is this done?}
+of our model representation using MATLAB. 
+%\note{Where is this done?}
 
@@
 
+\textcolor{blue}{The synthesized controllers are confirmed to be safe outside of our model
+representation using MATLAB, achieving EG2.  A~link to the full
+experimental environment, including scripts to reproduce the results, all
+benchmarks and the tool, is provided in the
+footnote as an Open Virtual Appliance (OVA).\footnote{\url{XXXX}}
+The provided experimental environment runs multiple discretisations for each
+benchmark, and lists the fastest as the result synthesis time.}
+
 %-------------------------------
@@
 benchmarks is limited within the scope of this paper and the performance may
-not generalize to other benchmarks.\note{is this where we attempt asserting EG2?}
+not generalize to other benchmarks.
+%\note{is this where we attempt asserting EG2?}
 
@@
 
-\note{So, what about EG2? Shall we assert it? }
+%\note{So, what about EG2? Shall we assert it? }
 

### 2018-05-16 automatica/paper.tex
fixes

@@
 A tight polyhedron can be obtained with hyperplanes that are tangent to the set,  
-which is achieved by selecting a number of points \note{on the boundary} of the set, 
+which is achieved by selecting a number of points on the boundary of the set, 
 and finding corresponding hyperplanes that are tangent to those points with respect to the dynamics.  
@@
 $P_a(z) = z^n+\sum_{i=1}^n{(a_i-k_i)z^{n-i}}$.  As with the multi-staged approach, this polynomial must satisfy Jury's criterion.
-\note{are we assuming to be working with a controllable form?
-should we emphasize that some elements are known, others are parameters?
-also, why do we use a different notation for this char poly than before?
-\reply{[we don't need to talk about controllable form a we only use the characteristic polynomial, but we describe it in more detail because we work directly with the shape indicated here (a-k).}}   
-\note{but, this very shape of the characteristic polynomial holds only for LTI models in controllable canonical form.}
+\reply{The polynomial $P_a(z)$ is obtained by transforming the system into controllable form( See~\cite{astrom1997computer}, where both the dynamics and the controller are multiplied by a matrix $\mat{T}$ (derived from $\mat{A}$ and $\mat{B}$), which is given to the synthesiser.
+The synthesizer is thus able to provide a $\mat{K}$ such that $k_i$ are the elements  of $\mat{K}\mat{T}^{-1}$.
+}
 %\blue{[shouldn't there be a b term in the polynomial's coefficients here? No. the polynomial only evaluates the poles]}
@@
   that satisfies
-  $\phi_\mathit{stability} \wedge \phi_\mathit{safety} \wedge \phi_\mathit{init}^{K}$ \note{you mean $\phi (K)$?} by invoking a SAT solver.  
-  The safety specification in the SAT formula \note{[clarify:] is an over-approximation} that has constraints for a given set of iterations ($k$) \note{and initial values [conditions?]}.  
+  $\phi_\mathit{stability} \wedge \phi (K)$ by invoking a SAT solver.  
+  The safety specification given to the SAT formula is an over-approximation of the original safety specification that only has constraints for a given set of iterations ($k$) and initial values.  
  The program search algorithm is as in the multi-staged approach.  
@@
 for which the property does not hold, which we use to locally refine the
-abstraction by adding the constraint $\mat{A}^k\vec{x}_0 \models \phi_\mathit{safety}$ \note{how is this local refinement practically performed?}.  
+abstraction by adding the constraint $\mat{A}^k\vec{x}_0 \models \phi_\mathit{safety}$ (which is calculated explicitly using acceleration for the given $k$ and $\vec{x}_0$).  
 When the abstraction cannot be further refined, we provide $(k, x_0)$ to the {\sc abstract} phase.
@@
 \begin{enumerate}
-\item Find the constraints that invalidate the property \reply{($\{ k, x_0 : \mat{A}^k\vec{x}_0 \not \models \phi_\mathit{safety}\}$) as a set of counterexamples for the eigenvalues, which we define as $\phi_\Lambda=\{ k, x_0 : \mat{J}^k\mat{S}^{-1}\vec{x}_0 \models \phi_\mathit{safety}\}$}.
+\item Find the constraints that invalidate the property ($\{ k, x_0 : \mat{A}^k\vec{x}_0 \not \models \phi_\mathit{safety}\}$) as a set of counterexamples for the eigenvalues, which we define as $\phi_\Lambda=\{ k, x_0 : \mat{J}^k\mat{S}^{-1}\vec{x}_0 \models \phi_\mathit{safety}\}$.
 This is a constraint for the spectrum of the closed-loop dynamics.  

### 2018-05-16 automatica/paper.tex
intro

@@
 \begin{keyword}                           % Five to ten keywords,  
-Digital control synthesis; Safety requirements; Analog/Digital conversion; Quantization errors; Sampling.               % chosen from the IFAC 
+Digital control synthesis; Safety requirements; Analog/Digital conversion; Quantization errors; Time sampling.               % chosen from the IFAC 
 \end{keyword}                             % keyword list or with the 
@@
 Notably, safety requirements are frequently overlooked in conventional feedback control synthesis, but
-play a key role in systems engineering, particularly in safety-critical applications.
+play a key role in systems engineering, particularly for safety-critical applications of clear concern in modern autonomy contexts.
 
@@
 evaluate all possible progressions of the model simultaneously. 
-Additionally, this approach uses \emph{abstraction refinement} \cite{DBLP:conf/cav/ClarkeGJLV00},
+Additionally, this approach uses the \emph{abstraction-refinement} template \cite{DBLP:conf/cav/ClarkeGJLV00},
 enabling one to start with a very simple (abstract) description of the model 
@@
 \item We develop a model for different sources of quantization error and account for 
-  their effect on safety.  We give bounds that ensure the
+  their effect on safety.  We provide bounds that ensure the
   safety of our controllers in a hybrid (i.e., continuous/digital) domain.
@@
 \item While~\cite{DBLP:conf/cav/AbateBCCDKKP17} is restricted to models in discrete 
-time, in the current paper we present an approach for
-  soundly evaluating safety in combined continuous-discrete time and space.
+time, \note{in the current paper we present an approach for
+  soundly evaluating safety in combined continuous-discrete time and space. [this is via the AA-based back-end. However this part is not in the experiments, afaik.]}
 
@@
   Conversely, in the current paper we also make use of floating-point
-  arithmetic, and compare the two approaches.  Additionally, we enhance the
+  arithmetic, and compare the two approaches.  \note{Additionally, we enhance the
   implementation with an SMT back-end, allowing us to also use reals in order
-  to represent the states of the plant.
+  to represent the states of the plant.}
+
+\item \note{Shall we mention the broader set of benchmarks?}
 
@@
 %to synthesize controllers that make the closed-loop model 
-\emph{safety}.  Our work indeed focuses on the \emph{safety} of internal states, which is usually
-overlooked in the standard control literature with its default focus on stability properties.  
-Moreover, our work integrates an abstraction/refinement (CEGAR) step inside the main CEGIS loop.
-
-The approach underpinning tools such as Pessoa~\cite{mazo2010pessoa} and related extensions \cite{Anta2010,liu16} and applications \cite{zamani2014}, 
+\emph{safety}.  Our work indeed focuses on the safety of internal states, 
+which is by and large overlooked in the standard (digital) control literature, 
+by default focussed on stability properties.  
+Moreover, our work integrates an abstraction-refinement (CEGAR) step inside the main CEGIS loop.
+
+The technique underpinning tools such as Pessoa~\cite{mazo2010pessoa} and related extensions \cite{Anta2010,liu16} and applications \cite{zamani2014}, 
 synthesizes correct-by-design embedded control software for LTI models.    

### 2018-05-16 automatica/paper.tex
fixes

@@
 \item We represent the plant variables $x(t)$ and $u(t)$, which are continuous quantities, with finite precision in our model. 
-It is necessary to account for the errors introduced by this representation: 
-we account for these errors in both approaches by using standard interval arithmetic. 
+It is necessary to account for the errors introduced by this representation, 
+which we do using standard interval arithmetic. 
 \item The quantisation errors by the ADC, which converts the analogue signal $x(t)$ into the digital signal $x_k$, 
 which is then fed into the controller cf. Figure~\ref{fig:digitalsystem}. 
-We account for this error in the acceleration-based back-end by introducing a noise signal $\nu_1$ that over-approximates it. Further details are found in section~\ref{sssec:abstraction}.  
-In the multi-stage back-end we use bit-precise modelling in CBMC~\cite{ClarkeKL04}, a bounded model checker for C-programs, to accurately encompass this conver- sion.
-In other words, CBMC constructs a boolean formula that explicitly unwinds the transition system for symbolically represented inital states.
-The possi- ble bounds that this symbolically represented initial state may take are restricted by upper and lower bounds as described in section .
-The boolean formula constructed by CBMC models the ADC conversions precisely on the symbolically represented states at every time step.
-When we check for a safety prop- erty, the boolean formula is satisfied only if there is an input state value for which the subsequent trace through the transition system eventually violates the safety property.
+We account for this error in the acceleration-based back-end by introducing a noise signal $\nu_1$ that over-approximates it. 
+Further details are found in Section~\ref{sssec:abstraction}.  
+In the multi-stage back-end we use bit-precise modelling in CBMC~\cite{ClarkeKL04}, a bounded model checker for C-programs, to accurately encompass this conversion. 
+In other words, CBMC constructs a Boolean formula that explicitly unwinds the transition system for symbolically represented initial states. 
+\note{[rephrase:] The possible bounds that this symbolically represented initial state may take are restricted by upper and lower bounds as described in section . } 
+The Boolean formula constructed by CBMC models the ADC conversions precisely on the symbolically represented states at every time step. 
+When we check for a safety property, the Boolean formula is satisfied only if there is an input state value for which the subsequent trace through the transition system eventually violates the safety property.
 \item The representation errors due to performing finite-precision arithmetic in the controller block. 
@@
 this is again treated by the introduction of a noise signal that bounds the error. 
-The naive back-end uses the bit-precise modelling of finite-precision arithmetic in CBMC, 
-in the same way as we handled the ADC conversion. 
-We assume that the ADC represents numbers to the same precision as the controller, or higher, and thus the precision is limited by the controller. 
+The multi-stage back-end uses the bit-precise modelling of finite-precision arithmetic in CBMC, 
+in the same way as the ADC conversion was handled. 
+We assume that the ADC represents numbers with a higher precision than the controller \note{why is this reasonable?}, 
+and thus the precision is limited by the controller. 
 \item We assume that the DAC converts numbers to analogue signals with the same precision as the controller. 
@@
 
-\subsection{Notation for fixed-point precision}
-
-In this paper we will use $\mathcal{F}_{\langle I,F \rangle}(x)$ to denote a real number
-$x$ represented at a fixed-point precision using $I$ bits to represent the integer part of the number
-and $F$ bits to represented the decimal part.
-
-$\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real
-number $x$ represented at the fixed-point precision of the controller, and
-$\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$
-represented at the fixed-point precision of the plant model ($I_c$ and $F_c$
-are determined by the controller.  We pick $I_p$ and $F_p$ for our synthesis
+\subsection{Notation for fixed- and floating-point precision}
+
+In this paper we will use $\mathcal{F}_{\langle I,F \rangle}(x)$ to denote a real number $x$ expressed at a fixed-point precision, 
+using $I$ bits to represent the integer part of the number and $F$ bits to represent the decimal part.
+
+$\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ denotes a real number $x$ represented at the fixed-point precision of the controller, 
+and $\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ denotes a real number $x$
+represented at the fixed-point precision of the plant model. 
+$I_c$ and $F_c$ are determined by the controller.  We pick $I_p$ and $F_p$ for our synthesis
 such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$, so that our controller 
-can be represented accurately in the plant domain).  
+can be represented accurately in the plant domain.    
 Thus any mathematical operations in our modelled digital controller will be in the
@@
 $\mathcal{F}_{\langle E_p,M_p \rangle}(x)$ to denote a real number 
-represented at the fixed-point precision of the plant model. 
+represented at the fixed-point precision of the plant model.  \note{no assumptions on relative value btw controller and plant?}
+
 %-------------------------------

### 2018-05-16 automatica/paper.tex
fixes

@@
 \label{eq:safetyliteral}
-\phi_\mathit{safety} := \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
+\phi_\mathit{safety} := \forall k\ge 0,\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
 \end{equation}
@@
 both of which we be expressed via given bounds as: 
-$\phi_\mathit{input} := {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
+$\phi_\mathit{input} := {\forall k\ge 0, \underline{u} \leq u_{k} \leq \overline{u}} $, 
 and $\phi_\mathit{init} := \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}$. 
@@
 %-------------------------------
- \subsubsection{Abstract Supports for Continuous-Time Dynamics}
+ \subsubsection{Abstract supports for continuous-time models}
  \label{sec:cont_aasup}
@@
 the second one is {\it abstraction-based}, 
-and it leverages abstraction-refinement \cite{DBLP:conf/cav/ClarkeGJLV00} and acceleration (cf. Sec.~\ref{ssec:aa}) to improve scalability,  
+and it leverages abstraction-refinement \cite{DBLP:conf/cav/ClarkeGJLV00} and abstract acceleration (cf. Sec.~\ref{ssec:aa}) to improve scalability,  
 while retaining soundness.
@@
 \State assert($ \underline{u}  \leq u \leq \overline{u}$)
- \State set $x_0$ to be a \note{vertex state}, e.g., $[\underline{x_0},\underline{x_0}]$	
-\For {($c=0;~c < 2^\mathit{Num\_States};~c\mbox{++}$)}
+ \State set $x_0$ to be a \note{vertex state[?]}, e.g., $[\underline{x_0},\underline{x_0}]$	
+\For {($c=0;~c < 2^\mathit{Num\_States};~c\mbox{++}$) }
   %\State assert($ \underline{x_0}  \leq x_0 \leq \overline{x_0}$)
@@
   	\EndFor
-  	\State set $x_0$ to be a new vertex state
+  	\State set $x_0$ to be a new \note{vertex state}
   	\EndFor
@@
 
-\item The first {\sc verify} stage, {\sc safety}, shown in Alg.~\ref{alg:safetycheck}, checks that the candidate
+\item The first {\sc verify} stage, {\sc safety}, shown in Alg.~\ref{alg:safetycheck} \note{Num\_States = ?, plant\_typet = ? controller_typet =?}, checks that the candidate
 solution $K$, which we synthesized to be safe for at least one initial
@@
 required for the states to have completed a 360\textdegree circle, as illustrated in Fig.~\ref{fig:ct}. 
-\note{This is only for spiralling dynamics - more generally, we need to clarify how the CT is computed. }
+\note{This is only for spiralling dynamics - more generally, we need to clarify how the CT is computed. Shall we add the CAV17 proof?}
 

### 2018-05-16 automatica/paper.tex
fixes

@@
 
-\item The first {\sc verify} stage, {\sc safety}, shown in Alg.~\ref{alg:safetycheck} \note{Num\_States = ?, plant\_typet = ? controller_typet =?}, checks that the candidate
+\item The first {\sc verify} stage, {\sc safety}, shown in Alg.~\ref{alg:safetycheck} \note{$Num\_States = ?, plant\_typet = ? controller_typet =?$}, checks that the candidate
 solution $K$, which we synthesized to be safe for at least one initial
@@
 above.  Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the
-error $ \delta_T=x\ \%_{c_m}\ \tilde x$, and $\%_{c_m}$ is the modulus
+error $ \delta_T=x\ \%_{c_m}\ \tilde x$ \note{define tilde x}, and $\%_{c_m}$ is the modulus
 operation performed on the last bit. 
@@
 %
-\item {\bf Rounding:} The following errors appear in basic operations.  Let
-$c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be
-the truncation errors caused by representing $c_1$ and $c_2$ in the
-fixed-point domain as above.
+\item {\bf Rounding:} The following errors are due to basic arithmetic operations.  
+Let $c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be
+the truncation errors caused by representing $c_1$ and $c_2$ in a fixed-point domain.
 %
@@
 %
-\item Division: the operations performed by our controllers in the FWL
-domain do not include division.  However, we do use division in computations
-at the precision of the plant.  Here the error depends on whether the
-divisor is greater or smaller than the dividend:  $\mathcal{F}_{\langle I,F
-\rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_{T3}$
+\item Division: the operations performed by the controllers in the FWL
+domain do not include division.  However, we do use division in computations within the plant.  
+Here the error depends on whether the divisor is greater or smaller than the dividend:  $\mathcal{F}_{\langle I,F
+\rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_{T3}$, 
 where $\delta_{T3}$ is $(\delta_{T2}\cdot c_1 - \delta_{T1}\cdot
@@
 (2^{I-1}+1-2^{-F})$.  Numbers outside this range cannot be represented by
-the domain.  We check that overflow does not occur.
+the domain.  We check that overflow does not occur \note{and if it does \ldots}.
 

### 2018-05-16 automatica/paper.tex
fixes

@@
 %
+\note{what is signal y here? how are these formulae related to those in the section on the AA-based back-end?}
 If we denote the error in the conversion by $\nu_k=y_k-y(t)$ where $t = nk$,
@@
 are the same ($I_{c}=I_{dac},\allowbreak F_{c}=F_{dac}$), or if the DAC
-resolution in higher than the ADCs, then the DAC quantization error is equal
+resolution in higher than the ADC, then the DAC quantization error is equal
 to zero.  From the above equations we can now define the ADC and DAC
@@
 \rangle}(x_{k})$; and second, the rounding error introduced by the
-multiplication operation.  We represent these errors as non-deterministic
-additive noise.
+multiplication operation.  
+\note{ We represent these errors as non-deterministic
+additive noise. }
 

### 2018-05-27 benchmark-runner/universalrunner/intervals.h
correction of 0 noise interval

@@ -446,17 +446,9 @@ void bound_error(int_matrixt closed_loop,int_vectort K,int_vectort error_coeffs)
   }
   int_matrixt invIminA;
   inverse(invIminA,IminA);
-  if (K[0].low>=0)
-  {
-   noise.low=K[0].low;
-   noise.high=K[0].high;
-  }
-  else
-  {
-   noise.low=-K[0].high;
-   noise.high=-K[0].low;
-  }
-  for (i=1;i<NSTATES;i++)
+  noise.low=-1;
+  noise.high=1;
+  for (i=0;i<NSTATES;i++)
   {
    if (K[i].low>=0)
    {

### 2018-05-27 automatica/paper.tex
Addressing some comments

@@
 %
-$$\mathcal{F}_{\langle I_{c},F_{c} \rangle}(y(t)) = y_k :
-y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right] \,.$$
-%
-\note{what is signal y here? how are these formulae related to those in the section on the AA-based back-end?}
-If we denote the error in the conversion by $\nu_k=y_k-y(t)$ where $t = nk$,
+$$\mathcal{F}_{\langle I_{c},F_{c} \rangle}(x(t)) = x_k :
+(x_k)_i \in \left[x_i(t)-\frac{q_{c}}{2}\ \ \ \ x_i(t)+\frac{q_{c}}{2}\right] \,.$$
+%
+\reply{where $x_i$ is the $i^{th}$ component of the vector $x$.}
+If we denote the error in the conversion by $\nu_k=x_k-x(t)$ where $t = nk$,
 and $n$ is the sampling time and $k$ the number of steps, then we may define
-some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
+some bounds for it $(\nu_k)_i \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
 
@@
 10 & CruiseHSCC & 1 & 16,8 & 6.6\,s & 16,10 & 6.6\,s &  24,14 & 0.3\,s & 16,10 & 0.3\,s \\
-11 & Cstr & 3 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+11 & Cstr & 3 & & ~\xmark & & ~\xmark & & ~\xmark & & 181045~\xmark\\
 12 & Cstrtmp  & 3 &  & ~\xmark & & ~\xmark & 24,14 & 0.5\,s & & ~\xmark\\
@@
 21 & Pendulum   & 2 & 16,8 & 8.5\,s & 32,23 & 24\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
-22 & Regulator   & 5 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+22 & Regulator   & 5 & & ~\xmark & & ~\xmark & &~\xmark  & & 529404~\xmark\\
+23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & 14075~\xmark\\
 24 & streamdrum   & 3 & 16,8  & 332.5\,s & 16,10 & 590.5\,s & 24,14 & 0.7\,s & 16,10 &1.3\,s\\

### 2018-06-01 automatica/paper.tex
temporary results

@@
 1  & Acrobot  & 4 &  & \xmark &  & ~\xmark & & ~\xmark &  & ~\xmark \\
-2  & Antenna  & 6 &  & ~\xmark &  & ~\xmark & & ~\xmark & & ~\xmark\\
+2  & Antenna  & 6 &  & ~\xmark &  & ~\xmark & & ~\xmark & & 2903s~\xmark\\
 3  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark & & ~\xmark & & ~\xmark\\
@@
 10 & CruiseHSCC & 1 & 16,8 & 6.6\,s & 16,10 & 6.6\,s &  24,14 & 0.3\,s & 16,10 & 0.3\,s \\
-11 & Cstr & 3 & & ~\xmark & & ~\xmark & & ~\xmark & & 181045~\xmark\\
+11 & Cstr & 3 & & ~\xmark & & ~\xmark & & ~\xmark & & 181s~\xmark\\
 12 & Cstrtmp  & 3 &  & ~\xmark & & ~\xmark & 24,14 & 0.5\,s & & ~\xmark\\
-13 & DCmotor   & 2 & 16,8  & 6.9\,s & 16,10 & 7.8\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s \\
+13 & DCmotor   & 2 & 16,8  & 6.9\,s & 16,10 & 7.8\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s (4.0\,s) \\
 14 & Flexbeam   & 6 & & ~\xmark & & ~\xmark & 24,14 & 72.1\,s & & ~\xmark\\
 15 & Guidance chen  & 5 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-16 & Helicopter   & 3 & 16,8 & 13.8\,s & 32,23 & 148\,s & 24,14 & 0.8\,s& 16,10 & 1.1\,s\\
+16 & Helicopter   & 3 & 16,8 & 13.8\,s & 32,23 & 148\,s & 24,14 & 0.8\,s& 16,10 & 1.1\,s (56.6\,s)\\
 17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
 18 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 16,10 & 28.2\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
-19 & Magpointer   & 2 & 16,8 & 10.1\,s & 16,10 & 20.4\,s & 24,14  & 1\,s& 16,10 & 1.3\,s\\
-20 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 34.8\,s & 24,14 & 0.5\,s & 16,10 & 0.6\,s\\
-21 & Pendulum   & 2 & 16,8 & 8.5\,s & 32,23 & 24\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
-22 & Regulator   & 5 & & ~\xmark & & ~\xmark & &~\xmark  & & 529404~\xmark\\
-23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & 14075~\xmark\\
+19 & Magpointer   & 2 & 16,8 & 10.1\,s & 16,10 & 20.4\,s & 24,14  & 1\,s& 16,10 & 1.3\,s (\xmark)\\
+20 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 34.8\,s & 24,14 & 0.5\,s & 16,10 & 0.6\,s (\xmark)\\
+21 & Pendulum   & 2 & 16,8 & 8.5\,s & 32,23 & 24\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s (2.4\,s)\\
+22 & Regulator   & 5 & & ~\xmark & & ~\xmark & &~\xmark  & & 529s~\xmark\\
+23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & 14.1s~\xmark\\
 24 & streamdrum   & 3 & 16,8  & 332.5\,s & 16,10 & 590.5\,s & 24,14 & 0.7\,s & 16,10 &1.3\,s\\
-25 & Suspension  & 4 & 16,8  & 17.2\,s & 16,10 &1373\,s & 56,30 & 15.3\,s & 16,10 & 4.4\,s\\
-26 & Tapedriver   & 3 & 16,8  & 8.2\,s & & ~\xmark & 64,22 & 2.1\,s & 16,10 & 1.1\,s\\
+25 & Suspension  & 4 & 16,8  & 17.2\,s & 16,10 &1373\,s & 56,30 & 15.3\,s & 16,10 & 4.4\,s (313.6\,s)\\
+26 & Tapedriver   & 3 & 16,8  & 8.2\,s & & ~\xmark & 64,22 & 2.1\,s & 16,10 & 1.1\,s (6.0\,s)\\
 \hline

### 2018-06-01 benchmark-runner/float-benchmark-individual-runner.sh

@@ -118,7 +118,7 @@ output_lower_bound=$(extract_output_lower_bound "${spec_content}")
 output_upper_bound=$(extract_output_upper_bound "${spec_content}")
 sampling="$(extract_spec_interval "${spec_content}" 'sampling')"
 if [ ${sampling} ]; then
-  sampling="-sample \"${sampling}\""
+  sampling="-cont -sample \"${sampling}\""
 fi
 speed=1
 if [ -n "$7" ]; then

### 2018-06-15 automatica/paper.tex
Added SymEx section
SymEx section draft, detail level to be decided.

@@
 \note{Anticipate here connection with characteristic polynomial? See Section 4.}
+
+\subsection{Symbolic execution}
+We use the bounded model checker CBMC~\cite{ClarkeKL04} to model controller behaviour on digitial signals with finite
+bit-precision.  We express these controller semantics as C programs, which is CBMC's preferred input language.  CBMC
+symbolically executes every instruction in an input program by translating it to a boolean satisfiability problem.  At
+the end of this process, the entire input program is translated to a boolean satisfiability formula which is satisfiable
+iff a certain property about the program holds.  CBMC's API allows to specify these properties in the form of assertions
+in the input program, and we use these properties to express that our generated controllers are modelled in a stable and
+safe fashion. \note{Do we need more details here? Should we explain e.g. SSA or give examples of how assignments, loops,
+etc. are turned into formulas? Part of Sec.~\ref{sec:errors} can probably be moved here.}
 

### 2018-11-23 automatica/paper.tex
results

@@
    &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
-1  & Acrobot  & 4 &  & \xmark &  & ~\xmark & & ~\xmark &  & ~\xmark \\
+1  & Acrobot     & 4 & 16,8 & 61959.4\,s &  & ~\xmark & & ~\xmark &  & ~\xmark \\
 2  & Antenna     & 6 &  & ~\xmark &  & ~\xmark & & ~\xmark & & 2903s~\xmark\\
 3  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark & & ~\xmark & & ~\xmark\\
-4  & Bioreact & 3 & 16,8 & 11.2\,s & 16,10 &14.6\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
-5  & Chen\_ex1& 3 & 16,8 & 7.2\,s  & 16,10 & 9.2\,s & & ~\xmark & 16,10 & 1.4\,s\\
+4  & Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &14.6\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
+5  & Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 9.2\,s & & ~\xmark & 16,10 & 1.4\,s\\
 6  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 4683.8\,s &  & ~\xmark & & ~\xmark\\
@@
 8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-9  & Cruise    & 1 & 16,8 & 6.6\,s & 16,10 & 6.5\,s & 24,14 & 0.3\,s& 16,10 & 0.3\,s\\
-10 & CruiseHSCC & 1 & 16,8 & 6.6\,s & 16,10 & 6.6\,s &  24,14 & 0.3\,s & 16,10 & 0.3\,s \\
+9  & Cruise      & 1 & 16,8 & 9.6\,s & 16,10 & 6.5\,s & 24,14 & 0.3\,s& 16,10 & 0.3\,s\\
+10 & CruiseHSCC & 1 & 16,8 & 9.6\,s & 16,10 & 6.6\,s &  24,14 & 0.3\,s & 16,10 & 0.3\,s \\
 11 & Cstr & 3 & & ~\xmark & & ~\xmark & & ~\xmark & & 181s~\xmark\\
 12 & Cstrtmp  & 3 &  & ~\xmark & & ~\xmark & 24,14 & 0.5\,s & & ~\xmark\\
-13 & DCmotor   & 2 & 16,8  & 6.9\,s & 16,10 & 7.8\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s (4.0\,s) \\
+13 & DCmotor   & 2 & 16,8  & 11.3\,s & 16,10 & 7.8\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s (4.0\,s) \\
 14 & Flexbeam   & 6 & & ~\xmark & & ~\xmark & 24,14 & 72.1\,s & & ~\xmark\\

### 2018-12-20 automatica/paper.tex
start of ifdef's for axelerator

@@
 possible solution that is known to stabilize the system but that may
-not be safe for all initial conditions. Safety is then verified either
-via BMC or abstract acceleration; if the verification step fails, a
+not be safe for all initial conditions. 
+\ifx\axelerator
+Safety is then verified either
+via Bounded Model Checking or abstract acceleration;
+\else
+Safety is then verified via Bounded Model Checking;
+\fi 
+if the verification step fails, a
 counterexample is provided to the inductive generalisation and the
@@
 of finite-precision arithmetic, time discretization and quantization
-noise introduced by A/D and D/A conversion.
+errors introduced by A/D and D/A conversion.
 %
@@
 correct-by-construction digital controllers that addresses all these
-challenges. Specifically, we automatically synthesize stable and safe,
+challenges. Specifically, we automatically synthesize %stable and 
+safe,
 software-implemented embedded controllers.  
@@
 In particular, our model evaluates the effects of the quantizers (A/D and D/A
-converters) and of time discretization, as well as representation
+converters), as well as representation
 errors introduced by working  %% artifacts such as an
@@
 in a finite-precision domain. 
-We reason about high level properties such as stability, robustness, and safety, which define the
-behaviour of the whole model.  
-Notably, safety requirements are frequently overlooked in conventional feedback control synthesis, but
+We reason safety requirements, which are frequently overlooked in conventional feedback control synthesis, but
 play a key role in systems engineering, particularly for safety-critical applications of clear concern in modern autonomy contexts.
@@
 %% Single-Input/Single-Output (SISO) systems.
+\ifx\axelerator
 In this paper we present two novel approaches for the synthesis of
-digital controllers, both of which make use of the framework known as counterexample guided
+digital controllers, both of which make 
+\else
+In this paper we present a novel approach for the synthesis of digital controllers,
+making 
+\fi
+use of the framework known as counterexample guided
 inductive synthesis (CEGIS)~\cite{jha-icse10,
@@
 %% specification since we are working in the frequency domain.
-
-\emph{The first approach} uses a multi-staged technique that starts by devising a
+\ifx\axelerator
+\emph{The first approach} 
+\else
+Our approach
+\fi
+uses a multi-staged technique that starts by devising a
 digital controller that stabilizes the plant model while remaining safe for a
@@
 model such that the safety boundaries are not violated for any larger number of
-iterations.  Requiring unfolding up to the completeness threshold, this
-approach is computationally expensive.
-
+iterations.
+
+\ifx\axelerator
 Instead of unfolding the dynamics, \emph{the second approach}
@@
 when a solution cannot be found.
+\fi
 
@@
 This paper is an extension of~\cite{DBLP:conf/cav/AbateBCCDKKP17}
-and makes the following contributions (the fourth and the fifth are
-specific extensions over~\cite{DBLP:conf/cav/AbateBCCDKKP17}): 
+and makes the following contributions (the fourth is a 
+specific extension to~\cite{DBLP:conf/cav/AbateBCCDKKP17}): 
 %
@@
 %% %
+\ifx\axelerator
 \item We provide two novel algorithms: the first, a multi-staged approach, relies on 
@@
   plant. 
+\else  
+\item We present a novel multi-staged approach to synthesising digital controllers, using on 
+  an unfolding of the dynamics up to a completeness threshold, and bit precise Bounded Model
+  Checking to account for sources of imprecision in the implementation of the digital control algorithm
+  and the modelling of the plant.
+  \fi
+
 %
@@
 
-\item While~\cite{DBLP:conf/cav/AbateBCCDKKP17} is restricted to models in discrete 
-time, \note{in the current paper we present an approach for
-  soundly evaluating safety in combined continuous-discrete time and space. [this is via the AA-based back-end. However this part is not in the experiments, afaik.]}
-
-\item A further limitation of the work in~\cite{DBLP:conf/cav/AbateBCCDKKP17} 
+%\item While~\cite{DBLP:conf/cav/AbateBCCDKKP17} is restricted to models in discrete 
+%time, \note{in the current paper we present an approach for
+%  soundly evaluating safety in combined continuous-discrete time and space. [this is via the AA-based back-end. However this part is not in the experiments, afaik.]}
+
+\item A limitation of the work in~\cite{DBLP:conf/cav/AbateBCCDKKP17} 
   is its restriction to fixed-point arithmetic, meaning that fixed-point
@@
   Conversely, in the current paper we also make use of floating-point
-  arithmetic, and compare the two approaches.  \note{Additionally, we enhance the
-  implementation with an SMT back-end, allowing us to also use reals in order
-  to represent the states of the plant.}
-
-\item \note{Shall we mention the broader set of benchmarks?}
+  arithmetic.  
+  %\note{Additionally, we enhance the
+  %implementation with an SMT back-end, allowing us to also use reals in order
+  %to represent the states of the plant.}
 
@@
 effects of discretisation and finite-precision errors.
-\note{Next paragraph is naive for a control audience - amend} 
+
 A~state-space model has known advantages over the transfer function
@@
 \textbf{Discretization Effects in Control Design --}
-Classical work in control synthesis has often disregarded digitalization effects, 
-\note{[this paragraph needs more work:]
-whereas recent results in digital control have focused on separate aspects of discretization, 
+Classical work in control synthesis has often disregarded digitalization effects.
+Recent results in digital control, however, have focused on separate aspects of discretization, 
 including delayed response~\cite{Duggirala2015} and finite word length (FWL) semantics, 
-with the goal either to verify~\cite{daes20161} or to optimize~\cite{oudjida2014design} given implementations. }
+with the goal either to verify~\cite{daes20161} the correctness of the implementation or to optimize~\cite{oudjida2014design} the design.
 
 There are two different problems that arise from FWL semantics.  The first
-is the error in the model dynamics caused by the inability to represent the exact
+is the error caused by the inability to represent the exact
 state of the physical system, while the second relates to rounding and
-saturation errors during model manipulation.  
+saturation errors during mathematical operations.  
 In~\cite{fialho1994stability}, a stability measure based on the error of the digital dynamics ensures that
@@
 as practically implemented on Field-Programmable Gate Arrays or Digital Signal Processors. 
-\note{next: why only this single issue, rather than all discretisation effects as presented earlier?} Later, we will address the issue of variable quantization, 
-introduced by ADC/DAC conversion blocks of Figure \ref{fig:digitalsystem}, 
-as classically studied in \cite{astrom1997computer}.
+%This requires us to consider the errors introduced by, we will address the issue of variable quantization, 
+%introduced by ADC/DAC conversion blocks of Figure \ref{fig:digitalsystem}, 
+%as classically studied in \cite{astrom1997computer}.
 
@@
 in the input program, and we use these properties to express that our generated controllers are modelled in a stable and
-safe fashion. \note{Do we need more details here? Should we explain e.g. SSA or give examples of how assignments, loops,
-etc. are turned into formulas? Part of Sec.~\ref{sec:errors} can probably be moved here.}
+safe fashion. %\note{Do we need more details here? Should we explain e.g. SSA or give examples of how assignments, loops,
+%etc. are turned into formulas? Part of Sec.~\ref{sec:errors} can probably be moved here.}
 
@@
 which is then fed into the controller cf. Figure~\ref{fig:digitalsystem}. 
+\ifx\axelerator
 We account for this error in the acceleration-based back-end by introducing a noise signal $\nu_1$ that over-approximates it. 
 Further details are found in Section~\ref{sssec:abstraction}.  
-In the multi-stage back-end we use bit-precise modelling in CBMC~\cite{ClarkeKL04}, a bounded model checker for C-programs, to accurately encompass this conversion. 
+In the multi-stage back-end we
+\else
+We
+\fi
+use bit-precise modelling in CBMC~\cite{ClarkeKL04}, a bounded model checker for C-programs, to accurately encompass this conversion. 
 In other words, CBMC constructs a Boolean formula that explicitly unwinds the transition system for symbolically represented initial states. 
-\note{[rephrase:] The possible bounds that this symbolically represented initial state may take are restricted by upper and lower bounds as described in section . } 
+The values that the symbolically represented initial state may take are restricted by upper and lower bounds as described in section~\ref{}.
 The Boolean formula constructed by CBMC models the ADC conversions precisely on the symbolically represented states at every time step. 
 When we check for a safety property, the Boolean formula is satisfied only if there is an input state value for which the subsequent trace through the transition system eventually violates the safety property.
+
 \item The representation errors due to performing finite-precision arithmetic in the controller block. 
+\ifx\axelerator
 In the acceleration-based back-end, 
 this is again treated by the introduction of a noise signal that bounds the error. 
-The multi-stage back-end uses the bit-precise modelling of finite-precision arithmetic in CBMC, 
+The multi-stage back-end uses 
+\else
+We use
+\fi
+the bit-precise modelling of finite-precision arithmetic in CBMC, 
 in the same way as the ADC conversion was handled. 
-We assume that the ADC represents numbers with a higher precision than the controller \note{why is this reasonable?}, 
-and thus the precision is limited by the controller. 
+We assume that the ADC represents numbers with a higher precision than the controller, 
+and thus the precision is limited by the controller. This is a reasonable assumption based on commonly available hardware.
 \item We assume that the DAC converts numbers to analogue signals with the same precision as the controller. 
-As a result we can ignore any additional errors introduced by the DAC.  Both the assumptions about the ADC and the DAC are reasonable assumptions based on commonly available hardware. 
+As a result we can ignore any additional errors introduced by the DAC. Again, this assumption is reasonable based on commonly available hardware. 
 \end{itemize}

### 2018-12-20 automatica/paper.tex
Removing commented out text
in the event that we want it back, we can use git history

@@
 
-%All we need to do is define the nature of $\mathcal{A}X_0$.
-%Let $\mat{S}\mat{J}\mat{S}^{-1}=\mat{A}$ be the eigen-decomposition of
-%$\mat{A}$, where $\mat{S}$ is the set of generalised eigenvectors of
-%$\mat{A}$ and $\mat{J}$ is the Jordan Form containing the eigenvalues of
-%$\mat{A}$ in its main diagonal.  We correspondingly define
-%$\mathcal{J}=\mat{S}^{-1}\mathcal{A}\mat{S}$, which is such that
-%$\mathcal{J} \supseteq \bigcup_{k \in [0\ \infty)} \mat{J}^k$.
-%
-%Since abstract acceleration operates in the eigenspace, wemust deal with some preliminary transformations.
-%Given a set $X=\{ \vec{x} \mid \mat{C}\vec{x} \leq \vec{d}\}$,
-%the linear transformation $\vec{x}'=\mat{S}^{-1}\vec{x}$ leads to the set 
-%%
-%\begin{equation}
-%X'= \mat{S}^{-1}X = \{\vec{x}' \mid \mat{C}\mat{S}\vec{x}'\leq \vec{d}\}.  
-%\label{eq:eigenInit}
-%\end{equation}
-%%
-%Analogously, let $X_0'=\mat{S}^{-1}X_0$ and
-%${\hat{X}'^\sharp}=\mat{S}^{-1}{\hat{X}^\sharp}$ be the initial set and the
-%abstract reach tube mapped onto the eigenspace of matrix $\mat{A}$.  We may
-%transform equation \eqref{eq:aa_reachtube} into: 
-%%
-%\begin{equation}
-%\hat{X}' \subseteq {\hat{X}'^\sharp} = \mathcal{J}X_0', 
-%\end{equation}
-%%
-%where $\hat{X}'=\mat{S}^{-1}\hat{X}$ and $\mathcal{J}$ is a convex
-%polyhedron representing restrictions on the eigenvalues of $\mat{A}$. 
-%$\hat{X}'^\sharp$ is calculated by applying a simplex algorithm with a
-%tableau defined by $\mathcal{J}$ and objective functions derived from each
-%vertex of $X_0'$ (step \eqref{alg:getReachTube} in Algorithm
-%\ref{alg:findReachTube} below).  We note, however, that if we wish to use
-%numerical analysis in the decomposition of $\mat{A}$, the Tableau in
-%$\mathcal{J}$ contains small intervals given by the errors, which cannot be
-%processed efficiently by a regular simplex and require a new procedure.
-%
-%The calculation of the abstract reach tube via abstract acceleration is
-%encompassed in Algorithm~\ref{alg:findReachTube}, which can be summarised as
-%follows (its steps are denoted in parentheses):
-%%
-%\begin{enumerate}
-%%
-%\item We perform unsound eigen-decomposition using an existing algebra package (lines \ref{alg:calcEigenvalues}-\ref{alg:calcEigenvectors}).
-%%
-%\item Then we restore soundness to the results using the methods described in \cite{cattaruzza2017sound} (lines \ref{alg:soundEigenvalues}-\ref{alg:soundEigenvectors}).
-%%
-%\item The inverse of the matrix of eigenvectors is calculated after soundness is restored, using interval arithmetic in order to ensure its soundness (line \ref{alg:inverse}).
-%%
-%\item The abstract dynamics are obtained by evaluating the convex hull of all powers of eigenvalues up to the desired number of iterations as described in \cite{cattaruzza2015unbounded} (line \ref{alg:aa}).
-%%
-%\item Using Equation \eqref{eq:eigenInit}, transform the initial state into the eigenspace (line \ref{alg:eigeninit}).
-%%
-%\item Extract the vertices of the eigen-polyhedron $X_0'$ using the algorithms described in \cite{cattaruzza2015unbounded,cattaruzza2017sound} (line \ref{alg:getVertices}). 
-%%
-%\item Calculate the mapped \emph{abstract reach tube} ${\hat{X}'^\sharp}$
-%that over-approximates the image of the reach tube in the eigenspace (line
-%\ref{alg:getReachTube}).  This is achieved by evaluating a set of objective
-%functions using the abstract dynamics as a simplex Tableau, and via a sound
-%simplex described in \cite{cattaruzza2017sound}.  The objective functions are
-%defined by the vertices of $X'_0$, denote as $V_0$, and by the desired
-%template directions, such that
-%%
-%\begin{equation*}
-%\vec{w}_{ij}= \vec{v}_i \circ \vec{t}_j \text{ with } \vec{v}_i \in V_0 \text{ and } \vec{t}_j \in T,
-%\end{equation*}
-%%
-%where $T$ is the set of template directions, and $\circ$ denotes a
-%component-wise multiplication yielding a vector.
-%%
-%\item Using Equation~\eqref{eq:eigenInit}, find the reach tube
-%$\hat{X}^\sharp=\mat{S}{\hat{X}'^\sharp}$ (line \ref{alg:getNormReachTube}).
-%%
-%\end{enumerate}
-%
-%\begin{algorithm}[]
-%\small
-%\begin{algorithmic}[1]
-%\Function{$\mathit{findAbstractReachTube}()$}{}
-%\State $\hat{\mat{J}}=$ calculateEigenvalues($ \mat{A}$)
-%\label{alg:calcEigenvalues}
-%\State $\hat{\mat{S}}=$ calculateEigenvectors($ \mat{A}$)
-%\label{alg:calcEigenvectors}
-%\State $[\mat{J}]=$ soundifyEigenvalues($\mat{A},\mat{J},\mat{S}$)
-%\label{alg:soundEigenvalues}
-%\State $[\mat{S}]=$ soundifyEigenvectors($\mat{A},[\mat{J}],\mat{S}$)
-%\label{alg:soundEigenvectors}
-%\State $[\mat{S}]^{-1}=$ calculateInverse($[\mat{S}]$)
-%\label{alg:inverse}
-%\State $\mathcal{J}=getAbstractDynamics([\mat{J}])$
-%\label{alg:aa}
-%\State $[X_0']=$ transformInitialSpace($X_0,\mat{S}$)
-%\label{alg:eigeninit}
-%\State $[V_0]=$ getVertices($[X_0']$)
-%\label{alg:getVertices}
-%\State ${\hat{X}'^\sharp}=$ getReachTube($\mathcal{J},[V_0]$)
-%\label{alg:getReachTube}
-%\State ${\hat{X}^\sharp}=$ transformReachTube(${\hat{X}'^\sharp},[\mat{S}]^{-1}$)
-%\label{alg:getNormReachTube}
-%\EndFunction
-%\end{algorithmic}
-%\caption{Calculation of Abstract Reach Tube Using Abstract Acceleration}
-%\label{alg:findReachTube}
-%\end{algorithm}
-
-%%-------------------------------
-%\subsection{Overapproximating continuous time dynamics using discrete models}
-%\label{sec:cont_aa}
-%%-------------------------------
-%
-%Thus far we wave discussed the Abstract Accelertion of Discrete Time
-%systems.  However, our plant models derive from the discretization of
-%continuous time systems.  We therefore seek to establish a sound
-%overapproximation which does not only encompass the selected discretization,
-%but any chosen discretization in the time domain.
-%
-%A dynamical system is a system in which a function describes the progression
-%of a state over time.  In a continuous domain with linear dynamics, it is
-%described by a first order Ordinary Differential Equation (ODE).
-%%
-%\begin{equation}
-%\dot{x}(t)=\mat{A}_o\vec{x}(t)+\mat{B}_o\vec{u}(t)
-%\label{eq:dynamical}
-%\end{equation}
-%%
-%Furthermore, a control system may have a derived
-%output that is a linear combination of its states and inputs, which may
-%restricts the observability of the statespace from the output space.
-%%
-%\begin{equation}
-%\vec{y}(t)=\mat{C}_o\vec{x}(t)+\mat{D}_o\vec{u}(t)
-%\end{equation}
-%%
-%Discretization of a continuous dynamical system turns the ODE into a
-%difference equation, assuming zero-order hold for the input $\vec{u}$, to
-%%
-%\begin{align}
-%\label{eq:discretization}
-%\vec{x}_{k+1} &= \mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
-%y_k &= \mat{C}_d \vec{x}_ k + \mat{D}_d \vec{u}_ k 
-%\end{align}
-%where
-%\begin{align}
-%\label{eq:discretize}
-%\mat{A}_d &= e^{\mat{A}_o T_s} = \mathcal{L}^{-1} { ( s \mat{I} - \mat{A}_o )^{-1} }_{t = T_s}\\
-%\mat{B}_d &= \int_{t = 0}^{T_s} e^{\mat{A}_o t} dt\ \mat{B}_o = \mat{A}_o^{-1} ( \mat{A}_d - \mat{I} ) \mat{B}_o\\
-%\mat{C}_d &= \mat{C}_o\\
-%\mat{D}_d &= \mat{D}_o \\
-%\end{align}
-%and $T_s$ is the sample time. Then
-%\begin{align*}
-%x(kT)=x_k \wedge y(kT) = y_k, \forall k
-%\end{align*}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%\subsubsection{Acceleration of continuous-time models}
-%\label{sec:continuous_time_accel}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
 The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
@@
 semantics in Sec.~\ref{sec:model}.
-% and compute the state $\vec{x}_T$ at a given time $T$,
-%%
-%% namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
-%%
-%namely the state $\vec{x}(t)$ of the model 
-%%$\dot{\vec{x}}(t)=\mat{A}
-%at time $t=T$.
-
-%\textcolor{red}{[The following three subsections take too much space, plus the results are mostly known or easily derivable with simple algebra: we need to shorten and simplify it.
-Dario: can you give it a crack?]}
-%\textcolor{blue}{[I merged the first two]}
-
-%\note{ [add?] In this section we work with fully observed models, namely where $y = x$. } 
+
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 
-%Abstract acceleration works by finding support functions of the set that encompasses the matrices $\mat{A}^k$.
-%Support functions are scalars that measure the distance of a hyperplane tangent to the set boundary to the origin.
-%In the case of continuous spaces, this translates to calculating the derivatives of the envelope in order to find the direction of the support vector (normal to the hyperplane), and calculating the distance to the corresponding point where the hyperplane touches the set (at which the derivative was calculated).
-%The direction of the vector is determined by evaluating the support function of another point in the curve,
-%which is known to be smaller than that of the selected point, and the chosen hyperplanes are aligned with the eigenvectors, hence we only look at eigenvalue pairs to calculate the derivatives~\cite{cattaruzza2015unbounded}.
-
-%%-------------------------------
-%\subsection{State-space representation of physical systems} 
-%\label{ssec:ssrepresentation}
-%%-------------------------------
-%
-%We consider models of physical plants expressed as ordinary differential
-%equations (ODEs), which we assume to be controllable and under full state
-%information (i.e., we have access to all the model variables):
-%%
-%\begin{align}
-%\label{eq:ode}
-%\dot{x}(t) = Ax(t)+ B u(t), \quad x \in \mathbb{R}^{n}, u \in \mathbb{R}^m, \\ \nonumber A \in \mathbb{R}^{n \times n}, B \in \mathbb{R}^{n \times m}, 
-%\end{align}
-%%
-%where $t \in \mathbb R_0^+$, where $A$ and $B$ are matrices that fully
-%specify the continuous plant, and with initial states set as $x(0)$.  While
-%ideally we intend to work on the continuous-time plant, in this work
-%Eq.~\eqref{eq:ode} is soundly discretized in time~\cite{fadali} into
-%%
-%\begin{align}
-%\label{eq:plant}
-%x_{k+1} = A_d x_k+ B_d u_k
-%\end{align} 
-%%
-%where $k \in \mathbb N$ and $x_{0}=x(0)$ is the initial state. 
-%$A_d$ and $B_d$ denote the matrices that describe the discretized plant dynamics, whereas
-%$A$ and $B$ denote the continuous plant dynamics.  
-%We synthesize for requirements over this discrete-time domain. 
-%Later, we will address the issue of variable quantization, 
-%as introduced by the ADC/DAC conversion blocks 
-%(\textcolor{red}{we should include a figure that describes the control system model that we tackle}).
-%
-%
-%
-%%-------------------------------
-%\subsection{Controller synthesis via state feedback}
-%\label{ssec:statefeedbackcontrol}
-%%-------------------------------
-%
-%Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t)$ and  $u_k$, respectively. 
-%Feedback architectures can be employed to manipulate the properties and behaviors of the continuous process (the plant).   
-%We are interested in the synthesis of digital feedback control algorithms, 
-%as implemented on Field-Programmable Gate Arrays or Digital Signal Processors. 
-%The most basic feedback architecture is the state feedback one, 
-%where the control action $u_k$ (notice we work with the discretized signal) is computed by: 
-%%
-%\begin{equation}
-%\label{eq:controlaction}
-%u_k = r_{k} - K x_k. 
-%\end{equation}
-%%
-%Here, $K \in \mathbb{R}^{m \times n}$ is a state-feedback gain matrix, 
-%and $r_{k}$ is a reference signal (again digital).   
-%%
-%The closed-loop model then takes the form 
-%\begin{align}
-%\label{eq:closedloopss}
-%x_{k+1} = ( A_d - B_d K ) x_k + B_d r_k.
-%\end{align}
-%%
-%The gain matrix $K$ can be set so that the closed-loop discrete dynamics are
-%shaped as desired, for instance according to a specific stability goal or
-%around a specific dynamical behavior \cite{astrom1997computer}.  As argued
-%later in this work, we will target more complex objectives, such as
-%quantitative safety requirements, which are not typical in the digital
-%control literature.  Further, we will embrace the digital nature of the
-%controller, which manipulates quantized signals as discrete quantities represented with finite precision. 
-%
-%%-------------------------------
-%\subsection{Stability of closed-loop systems}
-%\label{ssec:stability}
-%%-------------------------------
-%
-%In this work we employ asymptotic stability in the CEGIS loop,  
-%as an objective for guessing controllers that are later proven sound over safety requirements.  
-%Asymptotic stability is a property that amounts to convergence of the model executions to an equilibrium point, 
-%starting from any states in a neighborhood of the point (see Figure~\ref{fig:ct} for the portrait of a stable execution, converging to the origin).  
-%In the case of linear systems as in~\eqref{eq:closedloopss}, 
-%considered with a zero reference signal, 
-%the equilibrium point of interest is the origin. 
-%
-%A discrete-time LTI system as \eqref{eq:closedloopss} is asymptotically
-%stable if all the roots of its characteristic polynomial (i.e., the
-%eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
-%circle of the complex plane, i.e., their absolute values are strictly less than
-%one~\cite{astrom1997computer} (this simple sufficient condition can be generalised, 
-%however this is not necessary in our work).  
-%In this paper, we express this stability specification $\phi_\mathit{stability}$ in terms of a check known as
-%\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic formula to
-%select the entries of matrix $K$ so that the closed-loop dynamics are shaped
-%as desired.
-%
-%%-------------------------------
-%\subsection{Safety specifications for dynamical systems}
-%\label{ssec:safety}
-%%-------------------------------
-%
-%We are not limited to the synthesis of digital stabilizing controllers -- a
-%well known task in the literature on digital control systems -- but target
-%safety requirements with an overall approach that is sound and automated. 
-%More specifically, we require that the closed-loop system
-%\eqref{eq:closedloopss} meets given safety specifications.  A safety
-%specification gives raise to a requirement on the states of the model, such
-%that the feedback controller (namely the choice of the gains matrix~$K$)
-%must ensure that the state never violates the requirement.  Note that a
-%stable, closed-loop system is not necessarily a safe system: indeed, the
-%state values may leave the safe part of the state space while they converge
-%to the equilibrium, which is typical in the case of oscillatory dynamics. 
-%In~this work, the safety property is expressed as:
-%%
-%\begin{equation}
-%\label{eq:safetyliteral}
-%\phi_\mathit{safety}\iff \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
-%\end{equation}
-%where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
-%for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
-%instant, respectively.  This means that the states will always be within an $n$-dimensional hyper-box.
-%
-%Furthermore, it is practically relevant to consider the 
-%constraints $\phi_\mathit{input}$ on the input
-%signal $u_{k}$ and $\phi_\mathit{init}$ on the initial states $x_0$,
-%which we assume have given bounds:
-%$\phi_\mathit{input} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
-%$\phi_\mathit{init} = \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$
-%For the former, this means that the control input might saturates in view of
-%physical constraints.
-%
-%%-------------------------------
-%\subsection{Performance specifications for dynamical systems}
-%\label{ssec:performance}
-%%-------------------------------
-%
-%\textcolor{red}{we should describe here about the performance specifications for dynamical systems.}
-
+\fi
 %-------------------------------
@@
 
-%\textcolor{red}{[Dario: can you update the following part, aligning it with hers?]}
-
-%  The multi-staged approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
-  %uses a multi-staged verification phase and performs solution generalization based on
-%the plant precision, the number of loop unrollings, 
-  %and the sampling rate. Essentially, it
-%  synthesizes a controller for an individual initial state
-%and input with a bounded time horizon and, subsequently, it generalizes it to all reachable states,
-%inputs, and time horizons during the verification phase.
-
 The multi-staged approach above relies on the symbolic simulation over a bounded time horizon of individual initial states and inputs, 
-%that form part of an uncountable space,
 and on the generalization to continuous sets and over an infinite time horizon.
-
-  %% solution over all times by refining the number of witnesses.  
-  %% In order to perform the safety check, this approach uses abstract acceleration
-  %% \cite{cattaruzza2015unbounded} to compute the controller's set of states. 
-  %% \todo{clarify: what is the ``set of states'' of the controller? }
-%\end{itemize}
-
-%% The verification of a hybrid continuous/discrete system over an
-%% unbounded time, requires the non-deterministic simulation of an
-%% infinite set of states, which is undecidable.
-
-%% Our multi-staged approach
-%% creates an abstraction of the system by establishing bounds on the
-%% error between such a system and a discrete-time/continuous-space
-%% model.  This model is still however, quite complex, hard to verify,
-%% and many of the states involved are inconsequential to the safety
-%% specification.
 
@@
 %
-% Now that we have explained the verification process, we may proceed to describe the synthesis procedure, which is illustrated in figure \ref{fig:CEGARIS}.
-% Our model, rather than look at a bisimulation \todo{specific notion that has not been formally define - do not use} in discrete time, explores a much higher abstraction, 
-% evaluating the unbounded time-continuous space reach tube as a set of inequalities that represent only the safety specification.
-% We have also identified 
-% the quantization noise as a bounded non-deterministic input.
+
 It comprises the following steps:  
@@
 }
-%\blue{[shouldn't there be a b term in the polynomial's coefficients here? No. the polynomial only evaluates the poles]}
-%%   A controllable system with quantization will have the following dynamics, where
-%% we use underscript ``n'' to denote a noise term,
-%% ``cf'' to denote Controllable Canonical Form,
-%% $\nu_1$, $\nu_2$ are quantization errors
-%% caused by the ADC and DAC conversions, respectively, 
-%% and $\nu_3$ is the round-off error.
-%% \todo{Why do we use $_t$ here?}
-%% %
-%% \begin{align}
-%% \label{eq:observer_LTI_cf}
-%% x_{k+1}=&\mat{A}_{t}x_k+\mat{B}_{t} r_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)
-%% \end{align}
-%% \begin{align*}
-%% \mat{A}_{t}=&\mat{T}\mat{A}_d\mat{T}^{-1}&
-%% \mat{B}_{t}=&\mat{T}\mat{B}_d&
-%% \mat{B}_{n}=&[1 \cdots 1]^T&
-%% \mat{T}=&\mat{W}_{cf}\mat{W}^{-1}&
-%% \end{align*}
-
-%% \begin{align*}
-%% \mat{A}_{t}=\mat{T}\mat{A}_d\mat{T}^{-1}=&\left[
-%% \begin{array}{ccccc}
-%% 0&1&0&\cdots&0\\
-%% 0&0&1&\cdots&0\\
-%% \vdots&\vdots&\vdots&\ddots&\vdots\\
-%% 0&0&0&\cdots&1\\
-%% k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
-%% \end{array}\right]
-%% \label{eq:cf_SISO_2}
-%% \end{align*}
-
-%% \begin{enumerate}
-%% \item Calculate $\mat{T}$ as $\mat{W}_{cf}\mat{W}^{-1}$. %using equations \eqref{eq:rncf}\eqref{eq:rcf}\eqref{eq:to_cf}
-%% \item Extract the characteristic polynomial of the above matrix:
-%% %
-%\begin{align*}
-%$P_a = z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}$
-%\end{align*}
 
@@
 \item In the {\sc synthesize} phase, we synthesize a candidate controller
-%We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability 
-% specification defined by Jury's 
-%criteria. %, and try to synthesise a controller that meets these specs.
-% For a stabilized closed-loop, which is necessary for our safety property, we need
-% these roots to remain within the unit circle, which we verify using Jury's criteria.
-% Notice that in our polynomials $c_0=1$ and we only use reals.
-% Once we have established convergence, we may examine the 
-% safety specification $\phi_\mathit{safety}$.
   $K$ 
@@
  The program search algorithm is as in the multi-staged approach.  
-%%   We obtain it by solving the SAT formula 
-%% $$\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_\mathit{safety}$$ 
-%% that satisfies the input constraint and Jury's criteria for 
-%% $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \tilde{\mat{K}}=\mat{K}\mat{T}$,
-%% where $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ is a program describing Jury's method.
 If there is no candidate solution we return UNSAT and exit the loop. 
@@
   progression of the system from $\phi_\mathit{init}$ over time,
-$x_{k} \models \phi_\mathit{safety}$. %\blue{why $k+1$ here?}. %% For this purpose we require 
-%% an initial set $\phi_\mathit{init}= x_0 \in [\underline{x_0} \ \overline{x_0}]$ 
-%% from which the system progresses.
-% Obviously, this set $x_0$ 
-% must satisfy the specification; otherwise, the system will be unsafe to begin with.
-% We accept a specification in the form $\mat{E}\mat{T}x_0<\mat{f}$. 
-% The presence of $\mat{T}$ is because this will typically be given in the original 
-% state-space.
-%% Next, we use abstract acceleration to get a second abstraction that 
-  %% encompasses the accelerated continuous reach-tube over an unbounded time.
+$x_{k} \models \phi_\mathit{safety}$. 
   In order to compute the progression of point $x_0$ at iteration $k$,
@@
 %-------------------------------
-%\subsection{Formal specification of transient response} 
-%\label{ssec:transientspecification}
-%-------------------------------
-
-%In a SISO system, there are 2 values that typically define the response-time of the system (using a step response).
-%\begin{enumerate}
-%\item The \emph{rise time} is defined as the time it takes the output to reach a percentage (eg $90\%$) of the target value given a step chnage in the input.
-%\item The \emph{settling time} is defined as the time it takes the output to stabilize within a margin of the target value (eg $10\%$).
-%\end{enumerate} 
-%In the case of first and second order systems (with ), the decay is governed by the equations 
-%\begin{align*}
-%&y_{decay}=
-%&\left\{
-%\begin{array}{cc}
-%e^{-|\omega| t}& 1^{st} order\\
-%e^{\zeta |\omega| t}\left(\frac{\sin\left(|\omega| t\sqrt{1-\zeta^2}+\sin^{-1}\sqrt{1-\zeta^2}\right)}{\sqrt{1-\zeta^2}} \right)&\zeta<1\\
-%e^{-|\omega| t}-|\omega| t e^{-|\omega| t}&\zeta=1\\
-%\frac{|\omega| e^{-|\omega_2| t}-|\omega_2| e^{-|\omega| t}}{|\omega|-|\omega_2|}&\zeta>1\end{array}\right.
-%\end{align*}
-%where $|\omega|$ and $|\omega_2|$ are the magnitudes of the eigenvalues (roots) of the system and  $\zeta=-\cos(\theta)$ where $\theta$ is the polar angle of the conjugate pair if it exists ($\zeta \geq 1$ if it doesn't).
-%These equations become increasingly complicated for higher order systems.
-However, we note their strong dependency on the magnitude of the eigenvalues, and use this property to define an upperbound on the decay function.
-%All of the above equations will decay faster than $e^{-|\omega| t}$ given $|\omega| < |\omega_2|$, hence we may use this function as our upper bound.
-%\begin{theorem}
-%Given a set of eigenvalues for a discrete time model of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1\ n]$, the settling time of the system is upperbounded by
-%\begin{equation}
-%t_s<-log_{|\overline{\lambda}|}({p_s}) : |\overline{\lambda}| =\max(|\lambda_i|) \wedge |\overline{\lambda}|<1,\ \forall i \in [1\ n]
-%\label{eq:set_time}
-%\end{equation}
-%where $0\leq p_s \leq 1$ is the desired percentage of the target within to remain after $t_s$.
-%\end{theorem} 
-%\begin{proof}
-%Given a closed loop single output LTI system of order $n$ with dynamics
-%\begin{equation}
-%\left\{\begin{array}{c}\vec{x}_k=\mat{A}\vec{x}_{k-1}\\ \vec{y}_k=\mat{C}\vec{x}_k\end{array}\right.
-\Rightarrow \left\{ \begin{array}{c}\vec{x}_k'=\mat{J}\vec{x}_{k-1}'\\ \vec{y}_k=\mat{C}\mat{S}\vec{x}_k'\end{array}\right.
-: \left\{ \begin{array}{c}\mat{A}=\mat{S}\mat{J}\mat{S}^{-1} \\ \vec{x}_k'=\mat{S}^{-1}\vec{x}_k\end{array}\right.
-%\label{eq:eigendynamics}
-%\end{equation}
-%
-%the output decay is a linear combination of the decay of eigenvalues or
-%eigenvalue pairs.  
-%Let $\mat{C}'\in \mathbb{R}^{1 \times n}=\mat{C}\mat{S}$.
-Since $\mat{C}'$ is constant, the output $y_k$ is a linear combination of the states $\vec{x}'_k$.
-We accelerate equation \eqref{eq:eigendynamics} to obtain
-%\begin{align}
-%y_k&=\mat{C}'\mat{J}^k\vec{x}_0 = \sum_{i=0}^n \left( c_i \lambda_i^k + c_{il}\binom{k}{l} \lambda_i^{k-l}\right)\\
-%|y_k|&\leq \sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right||\lambda_i^k|
-%\end{align}
-%where the second  part of the equation corresponds to the upper diagonal terms of the Jordan blocks. We also have $|\lambda_i^k|\leq |\overline{\omega}^k|$,hence
-%\begin{align}
-%|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n \left|c_i + c_{il}\binom{k}{l} \lambda_i^{-l}\right|
-%\end{align}
-%Since we are synthesising the eigenvalues, rather than solve this formula for complex Jordan Shapes, we will restrict our synthesiser to provide solutions with distinct eigenvalues (which is by far the most common case).
-Therefore the right hand terms dissappear and we end up with
-%\begin{align}
-%|y_k|&\leq |\overline{\omega}^k|\sum_{i=0}^n |c_i|
-%\end{align}
-
-%Hence the overall decay of the system is always smaller
-%than $p=e^{-|\overline{\omega}| t}$ where $0\leq p\leq 1$ is the remaining
-%percentage of the decay expressed.  reversing we have
-%$t=-\frac{ln(p)}{|\overline{\omega}|}=-\frac{ln(p)}{ln(|\overline{\lambda}|)}$. 
-%replacing for $p_s$ , $t_s$, and $\overline{\lambda}$ we get equation
-%\eqref{eq:set_time}
-%
-%\qed
-%\end{proof}
-%
-%We may now use this limit to express a constraint in terms of the
-%coefficients for our synthesis process.  Let
-%
-%\begin{equation}
-%P=\prod_{i=0}^n (s-\lambda_i)=\sum_{j=0}^n c_js^j.
-%\end{equation}
-%
-%We use Jury's criterion to limit $|\lambda_i| \leq 1$.  Let us now define a
-%transformation $\lambda_i'=\frac{\lambda_i}{\overline{\lambda}}$.  We want
-%to ensure $\lambda_i' \leq 1$ which can be done by applying Jury's criterion
-%to $P'=\prod_{i=0}^n (s-\lambda_i')=\sum_{j=0}^n c_j's^j$ where $c_j'$ are
-%unknown.  However, if we replace for $\lambda_i$, we obtain
-%
-%\begin{equation}
-%P'=\prod_{i=0}^n (s-\lambda_i')=\prod_{i=0}^n \left(s-\frac{\lambda_i}{\overline{\lambda}}\right)=\sum_{j=0}^n \frac{c_j}{\overline{\lambda}^{n-j}}s^j
-%\end{equation}
-%
-%where all members are known, we may now synthesise coefficients that ensure
-%the eigenvalues are smaller than a desired magnitue, thus ensuring that the
-%settling time is too.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%\section{Verification of a Controllable Observed System}\label{sec:cof_verification}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-%\begin{figure*}[htb]
-%\centering
-
-%\tikzset{add/.style n args={4}{
-%    minimum width=6mm,
-%    path picture={
-%        \draw[circle] 
-%            (path picture bounding box.south east) -- (path picture bounding box.north west)
-%            (path picture bounding box.south west) -- (path picture bounding box.north east);
-%        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
-%        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
-%        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
-%        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
-%        }
-%    }
-% }
-
-%\resizebox{1.0\textwidth}{!}{
-% \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
-%     semithick, initial text=, ampersand replacement=\&,]
-
-%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
-%    \node[draw=none] (r) {$r_k$};
-%    \node[rectangle,draw,
-%	minimum width=1cm,
-%	minimum height=1cm,] (gain)at ([xshift=1.2cm]r) {\sc $k_r$};
-
-%   \& \node[circle,add={-}{+}{}{}] (circle) {};
-%   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$u_k$};
-%   \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Kd) at ([xshift=0,yshift=-5.5cm]circle)  {\sc $\mat{K}_d$};
-%   \coordinate (kdsouth) at ([yshift=-3cm]Kd);
-
-%   \& complexnode/.pic={ 
-%     \node[rectangle,dashed,draw,minimum width=3cm,minimum height=1.6cm,label=\textbf{DAC}] (dac) {};
-%     \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
-%     \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
-%     \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
-%     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {\sc ZOH};
-%   }
-
-%   \& complexnode/.pic={ 
-%      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};
-%      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2.5cm,yshift=.5cm]plant.center)  {\sc $\mat{B}$};
-%      \node[draw=none] (u) at ([xshift=-1cm,yshift=.15cm]B)  {$u(t)$};
-%      \node[circle,add={+}{+}{}{}] (p1) at ([xshift=-1.3cm,yshift=.5cm]plant.center) {};
-%      \node[draw=none] (xdot) at ([xshift=.85cm,yshift=.15cm]p1)  {$\dot{\vec{x}}(t)$};   
-%      \node[rectangle,draw,minimum width=1cm] (int) at ([xshift=.5cm,yshift=.5cm]plant.center) {\sc $\int$};
-%      \coordinate (xsouth) at ([xshift=1cm]int);
-%      \node[draw=none] (x) at ([xshift=1cm,yshift=.15cm]int)  {$\vec{x}(t)$};   
-%      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (C) at ([xshift=2.7cm,yshift=.5cm]plant.center)  {\sc $\mat{C}$};
-%      \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]C)  {$\vec{y}(t)$};   
-%      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (A) at ([xshift=.5cm,yshift=-1cm]plant.center)  {\sc $\mat{A}$};
-%      \coordinate (aeast) at ([xshift=1cm]A);
-%      \coordinate (awest) at ([xshift=-1.8cm]A);
-%    }
-
-%   complexnode/.pic={ 
-%      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=5cm,label=\textbf{Observer}] (observer)  at ([yshift=-5cm]plant.center) {};
-%      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Bd) at ([xshift=-2.5cm]observer.center)  {\sc $\mat{B}_o$};
-%      \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]Bd)  {$u_k$};
-%      \node[circle,add={+}{+}{+}{}] (o1) at ([xshift=-1.3cm]observer.center) {};
-%      \node[draw=none] (xd) at ([xshift=.85cm,yshift=.15cm]o1)  {$\hat{\vec{x}}_{k+1}$};   
-%      \node[rectangle,draw,minimum width=1cm] (delay) at ([xshift=.5cm]observer.center) {\sc $z^{-1}$};
-%      \coordinate (xdsouth) at ([xshift=1.3cm]delay);
-%      \coordinate (fbsouth) at ([xshift=1.3cm,yshift=-3cm]delay);
-%      \node[draw=none] (xdp) at ([xshift=1cm,yshift=.15cm]delay)  {$\hat{\vec{x}}_k$};   
-%      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Cd) at ([xshift=2.7cm]observer.center)  {\sc $\mat{C}_o$};
-%      \node[draw=none] (y) at ([xshift=.4cm,yshift=.8cm]Cd)  {$\hat{\vec{y}}_k$};   
-%      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ad) at ([xshift=.5cm,yshift=-1.5cm]observer.center)  {\sc $\mat{A}_o$};
-%      \coordinate (adeast) at ([xshift=1.3cm]Ad);
-%      \coordinate (adwest) at ([xshift=-1.8cm]Ad);
-%      \node[circle,add={-}{}{}{+}] (o2) at ([xshift=2.7cm,yshift=1.5cm]observer.center) {};
-%      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Ld) at ([xshift=.5cm,yshift=1.5cm]observer.center)  {\sc $\mat{L}_d$};
-%      \coordinate (ldwest) at ([xshift=-1.8cm]Ld);
-%      \coordinate (bdwest) at ([xshift=-5.5cm]Bd);
-%      \coordinate (uksouth) at ([xshift=-5.5cm,yshift=5.5cm]Bd);
-%      \coordinate (o2east) at ([xshift=6.3cm]o2);
-%    }
-
-%   \& complexnode/.pic={ 
-%     \node[rectangle,dashed,draw,minimum width=3.5cm,minimum height=1.6cm,label=\textbf{ADC},] (adc) {};
-%     \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
-%     \coordinate (switch1) at ([xshift=-1cm]adc.center);
-%     \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
-%     \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
-%     \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
-%     \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
-%     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]q1)  {$\vec{y}_k$};       
-%     \coordinate (ykeast) at ([xshift=1.9cm]q1);
-%   } 
-%   \& \coordinate (aux1);
-%   \& \\
-%  };
-
-  %\path[->] (v1) edge (q1.south);
-  %\path[->] (v2) edge (q2.south);
-  %\path[->] (r) edge (gain.west);
-  %\path[->] (gain.east) edge (circle.west);
-  %\path[->] (circle.east) edge (q2.west);
-  %\path       (q2.east) edge (zoh.west);
-  %\path[->] (zoh.east) edge (B.west);
-  %\path
-  %(B.east) edge (p1.west)
-  %(p1.east) edge (int.west)
-%  (xsouth) edge (aeast)
-%   (aeast) edge (A.east)
-%   (A.west) edge (awest)
-%   (awest) edge (p1.south)
-%   (int.east) edge (C.west)
-%   (C.east) edge (switch1.west)
-%   (switch2) edge (q1.west);
-%  \path
-%   (q1.east) edge (ykeast)
-%   (ykeast) edge (o2east);
-%  \path       (uksouth) edge (bdwest);
-%  \path[->] (bdwest) edge (Bd.west);
-%  \path
-%   (Bd.east) edge (o1.west)
-%   (o1.east) edge (delay.west)
-%   (xdsouth) edge (adeast)
-%   (adeast) edge (Ad.east)
-%   (Ad.west) edge (adwest)
-%   (adwest) edge (o1.south)
-%   (o2.west) edge (Ld.east)
-%   (Ld.west) edge (ldwest)
-%   (ldwest) edge (o1.north)
-%   (delay.east) edge (Cd.west)
-%   (Cd.north) edge (o2.south)
-%   (o2east) edge (o2.east)
-%   (xdsouth) edge (fbsouth)
- %  (fbsouth) edge (kdsouth);
-%\path[->]  (kdsouth) edge (Kd.south);
-%\path (Kd.north) edge (circle.south);
-% \end{tikzpicture}
-%}
- %\caption{Closed-loop digital control system with observer\label{fig:observersystem}}
-%\end{figure*}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-%\subsection{Stability of an Observed System}\label{sec:cof_stability}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\comment{
-Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally $\mat{A}_o=\mat{A}_d$, $\mat{B}_o=\mat{B}_d$ and $\mat{C}_o=\mat{C}_d$ for a given time discretization.
-A controllable and observable system will have the following dynamics:
-\begin{align}
-\tiny
-\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_{k+1}
-&\tiny=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}_d&\mat{B}_d\mat{K}_d\\ \mat{0}&\mat{A}_d-\mat{L}_d\mat{C}_d\end{array}\right]
-\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_k\nonumber\\
-&\tiny+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
-+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}_d\end{array}\right]\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]
-\label{eq:observer_LTI}
-\end{align}
-In order for the system to be in canonical form, we must however perform a transformation. The challenge however is that we want the state space dynamics in
-reachable form and the observer error dynamics in observable form. Let 
-\begin{equation}
-\left[\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e'\end{array}\right]=
-\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right] 
-\left[\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e\end{array}\right]
-\end{equation}
-We can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
-
-\begin{align}
-\left [\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e' \end{array}\right]_{k+1}
-=&\left [\begin{array}{cc}\mat{A}_{tp}&\mat{B}_{to}\\ \mat{0}&\mat{A}_{to}\end{array}\right]
-\left [\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e' \end{array}\right]_k
-+\mat{B}_{tp} \vec{r}_k
-+\mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]\nonumber\\
-\vec{y}_k=&\mat{C}_{t}\vec{x}_k + \mat{D}_{d}\vec{u}_k
-\label{eq:observer_LTI_cf}
-\end{align}
-\begin{align*}
-\mat{A}_{tp}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_d\right)\mat{T}_c^{-1}&
-\mat{A}_{to}=&\mat{T}_o\left(\mat{A}_d-\mat{L}_d\mat{C}_d\right)\mat{T}_o^{-1}\\
-\mat{A}_t=&\left [\begin{array}{cc}\mat{A}_{tp}&\mat{B}_{to}\\ \mat{0}&\mat{A}_{to}\end{array}\right]&
-\mat{B}_{to}=&\mat{T}_c\mat{B}_d\mat{K}_d\mat{T}_o^{-1}\\
-\mat{B}_{tp}=&\left[\begin{array}{c}\mat{T}_c\mat{B}_d\mat{k}_r\\\mat{0}\end{array}\right]&
-\mat{B}_{tn}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_d\end{array}\right]\\
-\mat{T}_с=&\mat{R}_{cf}\mat{R}^{-1}&
-\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
-\mat{L}_d=& \mat{T}_o^{-1}\left[ \begin{array}{c}p_1\\p_2\\p_n\end{array}\right]&
-\mat{C}_t=&\mat{C}_d\mat{T}_c
-\end{align*}
-
-\begin{align*}
-\mat{A}_{tp}=&\left[
-\begin{array}{ccccc}
-0&1&0&\cdots&0\\
-0&0&1&\cdots&0\\
-\vdots&\vdots&\vdots&\ddots&\vdots\\
-0&0&0&\cdots&1\\
-k_n-a_n&k_{n-1}-a_{n-1}&k_{n-2}-a_{n-2}&\cdots&k_1-a_1
-\end{array}\right]
-\label{eq:cf_SISO_2}
-\end{align*}
-
-Careful examination of these matrices reveals that because the $\mat{A}_t$ is upper block diagonal, the spectrum of $\mat{A}_t$ is equal to the union of the spectrum of $\mat{A}_{tp}$ and $\mat{A}_{to}$ which can be calculated separately.
-Additionally, these correspond to the roots of the polynomials
-\begin{align*}
-\left(z^n+\sum_{i=1}^p{(a_i-k_i)z^{n-i}}\right) \left(z^n+\sum_{i=1}^p{(p_i-a_i)z^{n-i}}\right)
-\end{align*}
-
-As stated in Section~\ref{ssec:stabspecification}, we use Jury's Criterion
-to assert this specification.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Safety of an Observed System}\label{sec:cof_safety}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Now that we have established convergence, we may examine the safety
-specification of the state space.  In the case of SISO systems, this is
-given by a range of the input and a range of the output which are considered
-safe ($\vec{u}_k \in [\underline{u}\ \ \overline{u}] \wedge \vec{y}_k \in
-[\underline{y}\ \ \overline{y}]$).  Whilst there are other properties we may
-include in the verification, we will solely focus on these for simplicity of
-the explanation.  We will assume that we do not want saturation in our
-system, hence the control loop has only one mode.  We have also identified
-the quantization noise as a bounded non-deterministic input.  First we must
-translate the safety specification into the statespace.  Replacing on the
-second part of equation \eqref{eq:observer_LTI_cf} we obtain
-%
-\begin{equation}
-\Psi := \underline{y}-\overline{\mat{B}\vec{u}}<\mat{C}_t\vec{x}_k<\overline{y}-\underline{\mat{B}\vec{u}}
-\label{eq:of_bounds}
-\end{equation}
-Note that we use the bounds of the input after the transformation by $\mat{B}$ since the matrix may reverse the bounds.
-Equation \eqref{eq:of_bounds} can be solved using linear programming as it describes a polyhedral region in $\mathbb{R}^n$.
-The second step is evaluating the progression of the system over time in order to calculate $\vec{x}_k$ to validte against this specification.
-For this step we require an initial set from which the system progresses.
-Obviously, this set $\vec{x}_0$ must satisfy the specification, otherwise the system will be unsafe to begin with.
-We will accept a specification in the form $\mat{E}\mat{T}\vec{x}_0<\mat{f}$. The presence of $\mat{T}$ is because this will typically be given in the original state-space.
-Accelerating \eqref{eq:observer_LTI_cf}, we obtain:
-\begin{align}
-\label{eq:acc_observer_LTI_cf}
-\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_k
-=&\mat{A}_t^k
-\left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_0
-+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tp} \vec{r}_i
-+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right] \nonumber\\
-:&\left [\begin{array}{cc}\mat{E}\mat{T}&\mat{0}\end{array}\right] \left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_0<\mat{f}
-\end{align}
-which would still require us to verify the system for every $k$ up to infinity. Instead we will use abstract acceleration~\cite{}, which translates the formula into
-\begin{align}
-\label{eq:aa_observer_LTI_cf}
-\hat{X}^\#
-=&\mathcal{A}_t X_0+\mathcal{B}_{tp} R + \mathcal{B}_{tn} N\\
-X_0 =&\left \{ \left[\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right] :
- \left [\begin{array}{cc}\mat{E}\mat{T}&\mat{0}\end{array}\right] \left [\begin{array}{c}\vec{x}\\ \hat{\vec{x}}_e \end{array}\right]_0<\mat{f} \right\}\nonumber\\
- R =&\{r : \mat{E}_r < \vec{f}_r \}\nonumber\\
- N=&\left \{ \left[\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right] : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] \wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \right \}\nonumber
-\end{align}
-%
-where $\mathcal{A}_t=\bigcup_{k=1}^\infty \mat{A}^k,
-\mathcal{B}_{tp}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tp},
-\mathcal{B}_{tn}=\bigcup_{k=1}^\infty \sum_{i=0}^k\mat{A}^i\mat{B}_{tn}$ are
-abstract matrices for the system in \eqref{eq:observer_LTI_cf}.  It is worth
-noting that $r$ is a non-deterministic parametric input (\emph{ie} $\forall
-k>0, r_{k+1} =r_k$) whereas the set N is composed of non-deterministic
-variable inputs.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsection{Stability of an Digitally Observed System}\label{sec:cof_fwl_stability}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-Thus far we have presented a verification procedure for a continuous plant
-in discretized time domain (\emph{ie} the range of the quatizers is still
-$\mathbb{R}$.  The next step we must reaize is that the controller and the
-observer exist in a digital program, hence their domain is
-$\mathbb{R}\langle I,F,E\rangle$.  This has two separate effects on the
-model.  If we recall equation \eqref{eq:to_of}, the matrices of the observer
-and the controller are not necessarily those of the plant.  In fact we have
-$\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$, $\mat{A}_o,\mat{B}_o,\mat{C}_o,
-\mat{K}_d, \mat{L}_d \in \mathbb{R}\langle I,F,E\rangle^*$ Where $*$
-represents the appropriate dimension for each matrix.  Unfortunately this
-means that although combined matrices such as $\mat{A}_t$ are in the reals,
-they suffer from the fixed word restrictions in their composing matrices.
-
-When our observer is implemented using a finite precision controller, new
-problems arise due to the FWL effects.  Let $\mat{A}_o$, $\mat{B}_o$ and
-$\mat{C}_o$ be the dynamics represented in $\mathbb{R} \langle I , F, E
-\rangle$, and $\mat{A}_e=\mat{A}_d-\mat{A}_o$,
-$\mat{B}_e=\mat{B}_d-\mat{B}_o$, and $\mat{C}_e=\mat{C}_d-\mat{C}_o$ their
-corresponding errors.  Equation \eqref{eq:observer_LTI_cf} will become
-%
-\begin{align}
-\tiny
-\left [\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e' \end{array}\right]_{k+1}
-=&\tiny \left [\begin{array}{cc}\mat{A}_{tp}+\mat{B}_{eo}&\mat{B}_{to}\\ \mat{A}_{eo}&\mat{A}_{to}\end{array}\right]
-\left [\begin{array}{c}\vec{x}'\\ \hat{\vec{x}}_e' \end{array}\right]_k
-+\mat{B}_{tp} \vec{r}_k
-+\mat{B}_{tn}\left [\begin{array}{c}\vec{\nu}_2\\ \vec{\nu}_1\end{array}\right]\nonumber\\
-\tiny\vec{y}_k=&\tiny\mat{C}_{t}\vec{x}_k + \mat{D}_{d}\vec{u}_k
-\label{eq:observer_LTI_FWL_cf}
-\end{align}
-\begin{align*}
-\mat{A}_{tp}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}_d\right)\mat{T}_c^{-1}&
-\mat{A}_{to}=&\mat{T}_o\left(\mat{A}_o-\mat{L}_o\mat{C}_o\right)\mat{T}_o^{-1}\\
-\mat{A}_t=&\left [\begin{array}{cc}\mat{A}_{tp}&\mat{B}_{to}\\ \mat{0}&\mat{A}_{to}\end{array}\right]&
-\mat{B}_{to}=&\mat{T}_c\mat{B}_o\mat{K}_d\mat{T}_o^{-1}\\
-\mat{B}_{tp}=&\left[\begin{array}{c}\mat{T}_c\mat{B}_o\mat{k}_r\\\mat{0}\end{array}\right]&
-\mat{B}_{tn}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_o&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_d\end{array}\right]\\
-\mat{T}_с=&\mat{R}_{cf}\mat{R}^{-1}&
-\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
-\mat{L}_d=& \mat{T}_o^{-1}\left[ \begin{array}{c}p_1\\p_2\\p_n\end{array}\right]&
-\mat{A}_{eo}=&\mat{T}_o\left(\mat{A}_e-\mat{L}_o\mat{C}_e\right)\mat{T}_o^{-1}\\
-\mat{B}_{eo}=&\mat{T}_c\mat{B}_e\mat{K}_d\mat{T}_o^{-1}&
-\mat{C}_t=&\mat{C}_d\mat{T}_c
-\end{align*}
-
-The first effect of this new equation is that the matrix is no longer upper
-diagonal.  We must therefore compensate for the errors introduced in order
-to find a stable solution.  We can use Gershgoring disks to limit the error
-in the expected eigenvalues.  Let $\delta_o=\max(|\mat{A}_{ei*}|_2)$
-(\emph{i.e.} the largest row norm in $\mat{A}_e$) be the largest error bound
-for any eigenvalue in $\mat{A}_e$.  Then $\forall i \in [1\ n],
-|\lambda_{oi}-\hat{\lambda}_{oi}|<\delta_o$,where $\lambda_{oi}$ are the
-true eigenvalues of the observer and $\hat{\lambda}_{oi}$ the eigenvalues of
-the perturbed observer.  We note that in the case of stability we only care
-about the error with respect to the unit circle, which is equivalent to
-upper bounding the estimation of the largest eigenvalue.  Hence given a
-desired upper value $\overline{\lambda}$, we apply Iurys criterion on the
-polynomial.
-%
-\begin{equation}
-P_o'=\sum_{j=0}^n c_j\overline{\lambda'}^{n-j}s^j : \overline{\lambda'}=(1+\delta_o)\overline{\lambda}
-\end{equation}
-%
-In the case of the reachable eigenvalues, the procedure is the same except
-that we obtain our bound $\delta_c=\max(|\mat{A}_{e*i}+\mat{B}_{e*i}|_2)$
-(\emph{i.e.} the largest column norm in $[\mat{A}_e\ \mat{B}_e]^T$) and
-apply Jury's Criterion over
-%
-\begin{equation}
-P_r'=\sum_{j=0}^n c_j\overline{\lambda'}^{n-j}s^j : \overline{\lambda'}=(1+\delta_c)\overline{\lambda}
-\end{equation}
-
-As a final annotation, we remark that the safety specification must be
-applied to the model described in this section, accounting for the
-representation errors of the FWL domain.
-}
-
-%-------------------------------
 \section{DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants}

### 2018-12-20 automatica/paper.tex
more ifdefs for axelerator

@@
 
-\note{In the context of the formal synthesis of safe controllers, 
-the CEGIS architecture is applicable as follows: \ldots }
+In the context of the formal synthesis of safe controllers, 
+the set of possible {\sc inputs} corresponds to the set of possible initial states and the 
+candidate program $P$ is a candidate controllers $K$. The synthesis block generates a candidate
+controller that works for a subset of the possible initial states, and the verifier checks whether 
+the controller works for all possible initial states.
 
@@
 We start by describing the specific property that we pass to the synthesizer as the specification $\phi$. 
-Namely, we are interested in capturing stability and safety, 
-which we discuss in Sections~\ref{ssec:stabspecification} and~\ref{ssec:safespecification}, respectively.
+Namely, we are interested in capturing safety, 
+which we discuss in Section~\ref{ssec:safespecification}. We use a stability specification 
+in order to narrow the search space of possible controllers, as discussed in Section~\ref{ssec:stabspecification}.
 
@@
 
-We are not limited to the synthesis of digital stabilizing controllers -- a
-well known task in the literature on digital control systems -- but target
-safety requirements with an overall approach that is sound and automated. 
+%We are not limited to the synthesis of digital stabilizing controllers -- a
+%well known task in the literature on digital control systems -- but target
+%safety requirements with an overall approach that is sound and automated. 
 %More specifically, we require that the closed-loop system meets given safety specifications.  
+We target synthesis of safe digital controllers with an overall approach that is sound and automated.
 A safety specification translates into a requirement on the states of the closed-loop model, 
@@
 %-------------------------------
+\ifx\axelerator
 \subsection{Abstract acceleration of linear dynamics \note{Shall we move the material on AAccel to the Preliminaries?}} 
@@
 
-In this section we discuss two instantiations of CEGIS: 
+In this section we discuss 
+\ifx\axelerator
+two instantiations of CEGIS: 
 the first one,
@@
 while retaining soundness. 
-
+\else
+the instantiation of CEGIS we use to synthesise safe digital controllers. We use a multi-stage approach
+that unwinds the dynamics yup to a completeness threshold, verifying soundness using bit-precise bounded model checking.
+\fi
+
+\ifx\axelerator
 %-------------------------------
@@
 %-------------------------------
+\fi
 
@@
 
+\ifx\axelerator
 %-------------------------------
@@
 \item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors as follows:
-%($\frac{q_1}{2},\frac{q_2}{2},q_3$)
+
 \begin{align*}
@@
 and $q_3$ is the maximum truncation and rounding error in $u_k=-K \cdot \mathcal{F}_{\langle I_c,F_c \rangle}(x_k)$, 
-as further discussed in Section~\ref{sec:numeric_rep}. % More details on how to model
-%quantization as noise are given in
-%Appendix~\ref{appendix:quantization-noise}.
+as further discussed in Section~\ref{sec:numeric_rep}.
 
@@
 If there is no candidate solution we return UNSAT and exit the loop. 
-\item Once we have a candidate solution, we perform a safety verification % If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
-  %
+\item Once we have a candidate solution, we perform a safety verification 
   of the 
@@
   we consider the solution of the closed-loop model
-  %we take the
-  %the closed-loop model:
-  %$x_{k+1}=\mat{A}_{t}x_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)$
-  %and accelerate it to:
-%
+
 {
@@
 where $B_n= [1 \cdots 1]^T$. 
-%\label{eq:acc_observer_LTI_cf}
-%+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i 
-%
 As we require to verify the closed-loop model for any $k$ up to infinity, 
@@
 When the abstraction cannot be further refined, we provide $(k, x_0)$ to the {\sc abstract} phase.
-%
-%\todo{we should have a better argument here.}
-%\end{enumerate} 
+
 \item If we reach the {\sc abstract} phase, it means that the candidate solution is not valid,
@@
 
+\fi
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 
+\ifx\axelerator
 \subsection{ADC/DAC quantization errors modelled as noise} 
@@
 \end{align*}
+
+\fi
 

### 2019-01-08 automatica/paper.tex
fix
email addresses

@@
 \author[cambridge]{Cristina David}\ead{cd652@cam.ac.uk},
-\author[oxford]{Pascal Kessel}\ead{pascal.kesseli@stx.ox.ac.uk},
+\author[oxford]{Pascal Kessel}\ead{pascal.kesseli@cs.ox.ac.uk},
 \author[oxford]{Daniel Kroening}\ead{kroening@cs.ox.ac.uk},
-\author[oxford]{Elizabeth Polgreen}\ead{elizabeth.polgreen@linacre.ox.ac.uk}
+\author[oxford]{Elizabeth Polgreen}\ead{elizabeth.polgreen@cs.ox.ac.uk}
 
@@
 multiplication operation.
-\note{ We represent these errors as non-deterministic
-additive noise. }
 

### 2019-01-08 automatica/paper.tex
wording: precision

@@
 converters), as well as representation
-errors introduced by working  %% artifacts such as an
+errors introduced by the controller working  %% artifacts such as an
 %% observer~\cite{astrom1997computer}
-in a finite-precision domain. 
+in a finite-precision domain. Our model also accounts for representation errors introduced
+by our modelling of the plant using finite precision arithmetic. 
 We reason safety requirements, which are frequently overlooked in conventional feedback control synthesis, but

### 2019-01-08 automatica/paper.tex
grammar

@@
 We consider models of physical plants expressed as ordinary differential
-equations, which we assume to be controllable~\cite{Astrom08}: 
+equations, which we assume are controllable~\cite{Astrom08}: 
 %
@@
 \item We represent the plant variables $x(t)$ and $u(t)$, which are continuous quantities, with finite precision in our model. 
-It is necessary to account for the errors introduced by this representation, 
 which we do using standard interval arithmetic. 

### 2019-01-08 automatica/paper.tex
fix
typo

@@
 $\mathcal{F}_{\langle E_p,M_p \rangle}(x)$ to denote a real number 
-represented at the fixed-point precision of the plant model.  \note{no assumptions on relative value btw controller and plant?}
+represented at the fixed-point precision of the plant model.
 
@@
 That is, we ask the bounded model checker~\cite{ClarkeKL04} if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states, and a given fixed point precision for the controller, and where the input signal remains within the specified bounds.
-This approach sound if the current $k$ is greater than the completeness threshold (see later step).  
+This approach is sound if the current $k$ is greater than the completeness threshold (see later step).  
 We~also assume some (fixed or floating point) precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  
@@
 (2^{I-1}+1-2^{-F})$.  Numbers outside this range cannot be represented by
-the domain.  We check that overflow does not occur \note{and if it does \ldots}.
+the domain.  If overflow occurs, the interval bound becomes infinite.
 

### 2019-01-08 automatica/paper.tex
massive rewriting
should probably be split into separate commits, but i gave up

@@
 
-We provide experimental results showing that both our approaches are able to
+We provide experimental results showing that we are able to
 efficiently synthesize safe controllers for a set of intricate physical
 plant models taken from the digital control literature.
-\addtodo{add more here once we have the experimental results ready}
+%\addtodo{add more here once we have the experimental results ready}
 
@@
 
-\note{Anticipate here connection with characteristic polynomial? See Section 4.}
-
-\subsection{Symbolic execution}
+The gain matrix $K$ can be set so that the closed-loop discrete dynamics are
+shaped as desired, for instance according to a specific stability goal or
+around a specific dynamical behavior \cite{astrom1997computer}.  As argued
+later in this work, we will target more complex objectives, such as
+quantitative safety requirements, which are not typical in the digital
+control literature.  Further, we will embrace the digital nature of the
+controller, which manipulates quantized signals as discrete quantities represented with finite precision.
+
+\subsection{Stability of closed-loop systems}
+
+In this work we employ asymptotic stability in the CEGIS loop,  
+as an objective for guessing controllers that are later proven sound over safety requirements.  
+Asymptotic stability is a property that amounts to convergence of the model executions to an equilibrium point, 
+starting from any states in a neighborhood of the point (see Figure~\ref{fig:ct} for the portrait of a stable execution, converging to the origin).   
+In the case of linear systems as in~\eqref{eq:closedloopss}, 
+considered with a zero reference signal, 
+the equilibrium point of interest is the origin.
+
+A discrete-time LTI system as \eqref{eq:closedloopss} is asymptotically
+stable if all the roots of its characteristic polynomial (i.e., the
+eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
+circle of the complex plane, i.e., their absolute values are strictly less than
+one~\cite{astrom1997computer} (this simple sufficient condition can be generalised, 
+however this is not necessary in our work).  
+In this paper, we express this stability specification $\phi_\mathit{stability}$ in terms of a check known as
+\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic formula to
+select the entries of matrix $K$ so that the closed-loop dynamics are shaped
+as desired.
+
+\subsection{Safety of closed-loop systems}
+
+We are not limited to the synthesis of digital stabilizing controllers -- a
+well known task in the literature on digital control systems -- but target
+safety requirements with an overall approach that is sound and automated. 
+More specifically, we require that the closed-loop system
+\eqref{eq:closedloopss} meets given safety specifications.  A safety
+specification gives raise to a requirement on the states of the model, such
+that the feedback controller (namely the choice of the gains matrix~$K$)
+must ensure that the state never violates the requirement.  Note that a
+stable, closed-loop system is not necessarily a safe system: indeed, the
+state values may leave the safe part of the state space while they converge
+to the equilibrium, which is typical in the case of oscillatory dynamics. 
+%However, a safe system will always be stable.  
+In~this work, the safety property is expressed as:
+%
+\begin{equation}
+\label{eq:safetyliteral}
+\phi_\mathit{safety}\iff \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
+\end{equation}
+%
+%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
+%
+where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
+for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
+instant, respectively.  This means that the states will always be within an $n$-dimensional hyper-box.
+
+Furthermore, it is practically relevant to consider the 
+constraints $\phi_\mathit{input}$ on the input
+signal $u_{k}$ and $\phi_\mathit{init}$ on the initial states $x_0$,
+which we assume have given bounds:
+$\phi_\mathit{input} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
+$\phi_\mathit{init} = \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$
+For the former, this means that the control input might saturates in view of
+physical constraints.
+
+\subsection{Bounded Model Checking}
 We use the bounded model checker CBMC~\cite{ClarkeKL04} to model controller behaviour on digitial signals with finite
-bit-precision.  We express these controller semantics as C programs, which is CBMC's preferred input language.  CBMC
-symbolically executes every instruction in an input program by translating it to a boolean satisfiability problem.  At
+bit-precision.  
+We express these controller semantics as C programs, which is CBMC's preferred input language.  
+CBMC
+symbolically executes every instruction in an input program by translating it to a boolean satisfiability problem.  
+At
 the end of this process, the entire input program is translated to a boolean satisfiability formula which is satisfiable
-iff a certain property about the program holds.  CBMC's API allows to specify these properties in the form of assertions
-in the input program, and we use these properties to express that our generated controllers are modelled in a stable and
-safe fashion. %\note{Do we need more details here? Should we explain e.g. SSA or give examples of how assignments, loops,
+iff a certain property about the program holds.  
+CBMC's API allows to specify these properties in the form of assertions
+in the input program, and we use these properties to express that our generated controllers are stable and safe.
+%\note{Do we need more details here? Should we explain e.g. SSA or give examples of how assignments, loops,
 %etc. are turned into formulas? Part of Sec.~\ref{sec:errors} can probably be moved here.}
@@
 %-------------------------------
-\subsection{Errors}
+\subsection{Finite precision errors}
 \label{sec:errors}
 
-We account for the presence of errors originating from a number of sources, shown in Figure~\ref{fig:digitalsystem}:
+The key contribution of our work is that, when synthesising controllers, we precisely model the finite-precision arithmetic in the digital controller, guaranteeing that the controllers are safe.
+The finite precision arithmetic introduces the following errors, shown in Figure~\ref{fig:digitalsystem}.
+These errors are present in the real world, and we must model them accurately
+in order to capture the full behaviour of the system. Details of how we model this arithmetic are in Section~\ref{sec:}:
+
 \begin{itemize}
-\item We represent the plant variables $x(t)$ and $u(t)$, which are continuous quantities, with finite precision in our model. 
-which we do using standard interval arithmetic. 
-\item The quantisation errors by the ADC, which converts the analogue signal $x(t)$ into the digital signal $x_k$, 
-which is then fed into the controller cf. Figure~\ref{fig:digitalsystem}. 
-\ifx\axelerator
-We account for this error in the acceleration-based back-end by introducing a noise signal $\nu_1$ that over-approximates it. 
-Further details are found in Section~\ref{sssec:abstraction}.  
-In the multi-stage back-end we
-\else
-We
-\fi
-use bit-precise modelling in CBMC~\cite{ClarkeKL04}, a bounded model checker for C-programs, to accurately encompass this conversion. 
-In other words, CBMC constructs a Boolean formula that explicitly unwinds the transition system for symbolically represented initial states. 
-The values that the symbolically represented initial state may take are restricted by upper and lower bounds as described in section~\ref{}.
-The Boolean formula constructed by CBMC models the ADC conversions precisely on the symbolically represented states at every time step. 
-When we check for a safety property, the Boolean formula is satisfied only if there is an input state value for which the subsequent trace through the transition system eventually violates the safety property.
-
-\item The representation errors due to performing finite-precision arithmetic in the controller block. 
-\ifx\axelerator
-In the acceleration-based back-end, 
-this is again treated by the introduction of a noise signal that bounds the error. 
-The multi-stage back-end uses 
-\else
-We use
-\fi
-the bit-precise modelling of finite-precision arithmetic in CBMC, 
-in the same way as the ADC conversion was handled. 
-We assume that the ADC represents numbers with a higher precision than the controller, 
-and thus the precision is limited by the controller. This is a reasonable assumption based on commonly available hardware.
-\item We assume that the DAC converts numbers to analogue signals with the same precision as the controller. 
+
+\item The ADC introduces quantisation errors when it converts the analogue signal $x(t)$ into the digital signal $x_k$. This signal is then fed into the controller cf. Figure~\ref{fig:digitalsystem}.
+
+\item The controller block performs arithmetic at a finite-precision, which introduces additional errors on top of the error introduced by the ADC.
+We assume the ADC represents numbers with at least the same precision
+as the controller and thus the precision is limited by the controller. This is a reasonable assumption based on commonly available hardware.
+
+\item The DAC could potentially introduce further errors. However, we assume that the DAC converts numbers to analogue signals with the same precision as the controller. 
 As a result we can ignore any additional errors introduced by the DAC. Again, this assumption is reasonable based on commonly available hardware. 
@@
 
+The arithmetic and representations used in our modelling are also carried out at a finite precision, and so we must also account for the errors in our own modelling.
+Specifically our model of the plant variables  $x(t)$ and $u(t)$, which are, in reality, continuous quantities, with finite precision in our model.
+We guarantee that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller and we use interval arithmetic to bound the errors, as detailed in Section~\ref{sec:}.
+
 \subsection{Notation for fixed- and floating-point precision}  
-
 In this paper we will use $\mathcal{F}_{\langle I,F \rangle}(x)$ to denote a real number $x$ expressed at a fixed-point precision, 
@@
 \end{equation*}
-\note{The characteristic polynomial $S(z)$ represents the dynamical model in \ldots [clarify whether we use the CPol to describe the open- or closed-loop model.
+An LTI system is stable if all the roots of its characteristic polynomial $S(z)$ (i.e., the 
+eigen values of the closed loop matrix $A_d-B_dK$) are inside the unit circle of the complex plane, 
+i.e., their absolute values are less than one.
+
+%\note{The characteristic polynomial $S(z)$ represents the dynamical model in \ldots [clarify whether we use the CPol to describe the open- or closed-loop model.
 Relate parameters to matrices A,B,K.
 Notice that these parameters are used later in the Section where AA-based backend is explained.]}
-%\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?} 
-% Assuming that $\hat{G}(z) = \frac{\hat{N_G}(z)}{\hat{D_G}(z)}$
-% and $\hat{C}(z) = \frac{\hat{N_C}(z)}{\hat{D_C}(z)}$, then:
-% $$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$
+
 The following matrix $M$ with dimension $(2N-2)\times N$ and elements $m_{(\cdot),(\cdot)}$ is built from the coefficients of $S(z)$ as:  
@@
 \State assert($ \underline{u}  \leq u \leq \overline{u}$)
- \State set $x_0$ to be a \note{vertex state[?]}, e.g., $[\underline{x_0},\underline{x_0}]$	
+ \State set $x_0$ to be a vertex state, e.g., $[\underline{x_0},\underline{x_0}]$	
 \For {($c=0;~c < 2^\mathit{Num\_States};~c\mbox{++}$) }
@@
   	\EndFor
-  	\State set $x_0$ to be a new \note{vertex state}
+  	\State set $x_0$ to be a new vertex state
   	\EndFor
@@
 
-\item The first {\sc verify} stage, {\sc safety}, shown in Alg.~\ref{alg:safetycheck} \note{$Num\_States = ?, plant\_typet = ? controller_typet =?$}, checks that the candidate
+\item The first {\sc verify} stage, {\sc safety} is shown in Alg.~\ref{alg:safetycheck}. 
+The algorithm checks that the candidate
 solution $K$, which we synthesized to be safe for at least one initial
@@
 
+We use $(controller\_typet)$ to denote a
+cast or conversion to the controller precision, and $(plant\_typet)$ to denote a cast or conversion to the 
+plant precision. A \emph{vertex state} is defined as a state where all values are either equal to the upper or lower
+bound of the initial states. It is sufficient to verify that the controller is safe for all vertex
+states, and the proof is shown later in this section. We thus only need to iterate through the $2^{Num\_States}$ vertex
+states, where $Num\_States$ is the number of dimensions in $x$.
+
+\begin{theorem} 
+If a controller is safe for each of the corner cases of our hypercube of
+allowed initial states, i.e., the vertex states, it is safe for any initial state in the hypercube. 
+\end{theorem}
+
+Thus we only need to check $2^n$ initial states, where $n$
+is the dimension of the state space (number of continuous variables). 
+\begin{proof}
+Consider the set of initial states, $X_0$, which we assume to be convex since it is a hypercube. 
+Name $v_i$ its vertexes, where $i=1,\ldots, 2^n$.  
+Thus any point $x \in X_0$ can be expressed by convexity as $x = \sum_{i=1}^{2^n} \alpha_i v_i$, 
+where $\sum_{i=1}^{2^n} \alpha_i =1$. Then if $x_0=x$, we obtain 
+\begin{align*}
+x_k   &= (A_d - B_d K)^k x \\
+&= (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i \\
+      &= \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i \\
+      &= \sum_{i=1}^{2^n} \alpha_i x_k^i, 
+ \end{align*}     
+%
+where $x_k^i$ denotes the trajectories obtained from the single vertex
+$v_i$.  We~conclude that any $k$-step trajectory is encompassed, within a
+convex set, by those generated from the vertices. 
+\qed
+\end{proof}
+
 \item The second {\sc verify} stage, {\sc precision}, 
@@
 required for the states to have completed a 360\textdegree circle, as illustrated in Fig.~\ref{fig:ct}.
-\note{This is only for spiralling dynamics - more generally, we need to clarify how the CT is computed. Shall we add the CAV17 proof?}
+
+\begin{theorem} There exists a finite $\overline{k}$ such that it is
+sufficient to unwind the closed-loop state-space system up to $\overline{k}$
+in order to ensure that $\phi_\mathit{safety}$ holds. 
+\end{theorem}
+
+\begin{proof}
+%
+A stable control system is known to have converging dynamics.  Assume the
+closed-loop matrix eigenvalues are not repeated (which is sensible to do,
+since we select them).  The distance of the trajectory from the reference
+point (origin) decreases over time within subspaces related to real-valued
+eigenvalues; however, this is not the case in general when dealing with
+complex eigenvalues.  Consider the closed-loop matrix that updates the
+states in every discrete time step, and select the eigenvalue $\vartheta$
+with the smallest (non-trivial) imaginary value.  Between every pair of
+consecutive time steps $k\,T_s$ and $(k+1)\,T_s$, the dynamics projected on
+the corresponding eigenspace rotate $\vartheta T_s$ radians.  Thus, taking
+$\overline{k}$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, after
+$k{\geq}\overline{k}$ steps we have completed a full rotation, which results
+in a point closer to the origin.  The synthesized $\overline{k}$ is the completeness threshold.
+\qed 
+%
+\end{proof}
 
@@
 As discussed in Section~\ref{sec:errors}, 
-the models we consider have to account for errors from several sources: 
-the numerical error introduced by the finite precision used to represent the plant (and its operations),  
-the error introduced by the ADC/DAC conversions, 
+the models we consider must account for errors from several sources: 
+we must bound the numerical error introduced by the finite precision we use to represent the plant (and its operations), and precisely model
+the error introduced by the ADC/DAC conversions
 and the error introduced by the limited precision used to represent the controller. 
-First we consider the numerical errors introduced by the finite precision numbers (either fixed- or floating-point) used to model the plant and used by the digital controller. 
-Then we account for the quantization errors introduced by the ADC/DAC.
-
-\subsection{Errors due to numerical representations}
-
-Let us first consider the case of fixed-point representation of the model, 
-and of synthesis of fixed-point controllers.
-
-Recall we use $\mathcal{F}_{\langle I,F \rangle}(x)$ denote a real number $x$
-represented in a fixed point domain, with $I$ bits representing the integer
-part and $F$ bits representing the decimal part.  The smallest number that
-can be represented in this domain is $c_m=2^{-F}$.  Any mathematical
-operations performed at the precision $\mathcal{F}_{\langle I,F \rangle}(x)$
-will introduce errors, for which an upper bound can be
-given~\cite{DBLP:conf/arith/BrainTRW15}:
+We use interval arithmetic to bound the error introduced by the finite precision plant, and bounded model checking to precisely model the error introduced by the ADC/DAC and the finite precision controller.
+
+\subsection{Bit-precise symbolic model checking}
+As described in section~\ref{sec:preliminaries}, we use CBMC, a bit-precise bounded model checker to synthesise and verify candidate controllers.
+CBMC performs precisely the fixed or floating point arithmetic used in the controller, as well as the ADC/DAC conversions, according to the IEEE standards.
+
+\subsection{Interval arithmetic over errors in numeric representation} 
+We use finite-precision arithmetic to model the plant. This is an approximation that speeds up each CEGIS
+iteration but necessitates a further stage where we verify that the errors introduced by the
+approximation have not caused us to generate a controller that is unsafe when executed with real numbers 
+for the plant. In this stage, we represent the plant using double precision floating point
+and we use the Boost interval arithmetic library~\cite{} to bound the error in this representation.
+We use a compositional numeric library to perform the fixed point arithmetic for the controller~\cite{}.
+We check the controller is safe starting from each vertex state, which we have shown to be sufficient to prove safety from any initial state in the hypercube of possible initial states.
+
+We outline here the mathematics behind bounding the errors on the double precision floating point.
+Recall we use $\mathcal{F}_{\langle E,M \rangle}(x)$ denote a real number $x$
+represented in a floating point domain, with $E$ bits representing the exponent and $M$ bits representing the mantissa part. Any representation of a real number using the floating point domain will
+introduce an error, for which an upper bound can be given~\cite{DBLP:conf/arith/BrainTRW15}.
+For each number represented in floating point, we store an interval that encompasses this error.
+Further
+mathematical
+operations performed at the precision $\mathcal{F}_{\langle E,M \rangle}(x)$
+will propagate these errors forward and 
+introduce further errors for which bounds can be derived~\cite{DBLP:conf/arith/BrainTRW15}.
+
+The fixed point arithmetic of the digital controller is performed on the upper and lower limit of each interval independently. Since the precision of the floating point is greater than the precision
+of the controller, this is guaranteed to bound the real behaviour of the controller.
+
+\ifx\axelerator
 
@@
 
-\ifx\axelerator
 \subsection{ADC/DAC quantization errors modelled as noise} 
@@
 We separate our evaluation into two sets of results: fixed- and floating-point. 
-For the majority of the {\it fixed-point} benchmarks, we observe that the abstraction-based
-back-end is faster than the basic multi-staged verification approach; \textcolor{blue}{additionally, 
-from 26 benchmarks, we observed that the abstraction-based back-end finds a solution for more benchmarks 
-(14) than the multi-staged back-end (13)}.
-%\note{we should clarify that this is out of 26 in total, not 191?}  
-In direct comparison, the abstraction-based approach is on average able to find a
-solution in approximately 53\% of the time required using the multi-staged
-back-end, and has a median run-time 0.5\,s, which is twenty times smaller
-than the multi-staged approach.  The two back-ends complement each other in terms of 
-benchmark coverage, and together solve 58\% of the benchmarks \note{only? this does not sound much really}.  
-%
-For the majority of the benchmarks with {\it floating-point} implementation, 
-we also observe that the abstraction-based back-end is much faster than the basic multi-staged verification approach, 
-but both back-ends find the same amount of solutions (13).  
-In direct comparison, the abstraction-based approach is on average able to find a
-solution in approximately 50\% of the time required using the multi-staged
-back-end, and has a median run-time 0.6\,s, which is forty times smaller
-than the multi-staged approach.  The two back-ends complement each other in
-benchmark coverage and together solve 54\% of the benchmarks \note{somewhat underwhelming}.
+%For the majority of the {\it fixed-point} benchmarks, we observe that the abstraction-based
+%back-end is faster than the basic multi-staged verification approach; \textcolor{blue}{additionally, 
+%from 26 benchmarks, we observed that the abstraction-based back-end finds a solution for more benchmarks 
+%(14) than the multi-staged back-end (13)}.
+%%\note{we should clarify that this is out of 26 in total, not 191?}  
+%In direct comparison, the abstraction-based approach is on average able to find a
+%solution in approximately 53\% of the time required using the multi-staged
+%back-end, and has a median run-time 0.5\,s, which is twenty times smaller
+%than the multi-staged approach.  The two back-ends complement each other in terms of 
+%benchmark coverage, and together solve 58\% of the benchmarks \note{only? this does not sound much really}.  
+%%
+%For the majority of the benchmarks with {\it floating-point} implementation, 
+%we also observe that the abstraction-based back-end is much faster than the basic multi-staged verification approach, 
+%but both back-ends find the same amount of solutions (13).  
+%In direct comparison, the abstraction-based approach is on average able to find a
+%solution in approximately 50\% of the time required using the multi-staged
+%back-end, and has a median run-time 0.6\,s, which is forty times smaller
+%than the multi-staged approach.  The two back-ends complement each other in
+%benchmark coverage and together solve 54\% of the benchmarks \note{somewhat underwhelming}.
+
+%\begin{table*}
+%\centering
+%\begin{tabular}{| r | l | c | c | r | c | r | c | r | c | r |}
+%%
+%\hline
+%\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                 & \multicolumn{4}{|c|}{Abstraction} \\
+%   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
+%1  & Acrobot     & 4 & 16,8 & 61959.4\,s &  & ~\xmark & & ~\xmark &  & ~\xmark \\
+%2  & Antenna     & 6 &  & ~\xmark &  & ~\xmark & & ~\xmark & & 2903s~\xmark\\
+%3  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark & & ~\xmark & & ~\xmark\\
+%4  & Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &14.6\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
+%5  & Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 9.2\,s & & ~\xmark & 16,10 & 1.4\,s\\
+%6  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 4683.8\,s &  & ~\xmark & & ~\xmark\\
+%7  & Chen\_ex3   & 7 &   & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+%8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+%9  & Cruise      & 1 & 16,8 & 9.6\,s & 16,10 & 6.5\,s & 24,14 & 0.3\,s& 16,10 & 0.3\,s\\
+%10 & CruiseHSCC & 1 & 16,8 & 9.6\,s & 16,10 & 6.6\,s &  24,14 & 0.3\,s & 16,10 & 0.3\,s \\
+%11 & Cstr & 3 & & ~\xmark & & ~\xmark & & ~\xmark & & 181s~\xmark\\
+%12 & Cstrtmp  & 3 &  & ~\xmark & & ~\xmark & 24,14 & 0.5\,s & & ~\xmark\\
+%13 & DCmotor   & 2 & 16,8  & 11.3\,s & 16,10 & 7.8\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s (4.0\,s) \\
+%14 & Flexbeam   & 6 & & ~\xmark & & ~\xmark & 24,14 & 72.1\,s & & ~\xmark\\
+%15 & Guidance chen  & 5 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+%16 & Helicopter   & 3 & 16,8 & 13.8\,s & 32,23 & 148\,s & 24,14 & 0.8\,s& 16,10 & 1.1\,s (56.6\,s)\\
+%17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+%18 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 16,10 & 28.2\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
+%19 & Magpointer   & 2 & 16,8 & 10.1\,s & 16,10 & 20.4\,s & 24,14  & 1\,s& 16,10 & 1.3\,s (\xmark)\\
+%20 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 34.8\,s & 24,14 & 0.5\,s & 16,10 & 0.6\,s (\xmark)\\
+%21 & Pendulum   & 2 & 16,8 & 8.5\,s & 32,23 & 24\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s (2.4\,s)\\
+%22 & Regulator   & 5 & & ~\xmark & & ~\xmark & &~\xmark  & & 529s~\xmark\\
+%23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & 14.1s~\xmark\\
+%24 & streamdrum   & 3 & 16,8  & 332.5\,s & 16,10 & 590.5\,s & 24,14 & 0.7\,s & 16,10 &1.3\,s\\
+%25 & Suspension  & 4 & 16,8  & 17.2\,s & 16,10 &1373\,s & 56,30 & 15.3\,s & 16,10 & 4.4\,s (313.6\,s)\\
+%26 & Tapedriver   & 3 & 16,8  & 8.2\,s & & ~\xmark & 64,22 & 2.1\,s & 16,10 & 1.1\,s (6.0\,s)\\
+%\hline
+%%
+%\end{tabular}
+%\vspace{0.05in}
+%\caption{Experimental results\label{tab:results}}
+%\end{table*}
 
@@
 \centering
-\begin{tabular}{| r | l | c | c | r | c | r | c | r | c | r |}
+\begin{tabular}{| r | l | c | c | r | c | r |}
 %
 \hline
-\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                 & \multicolumn{4}{|c|}{Abstraction} \\
-   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
-1  & Acrobot     & 4 & 16,8 & 61959.4\,s &  & ~\xmark & & ~\xmark &  & ~\xmark \\
-2  & Antenna     & 6 &  & ~\xmark &  & ~\xmark & & ~\xmark & & 2903s~\xmark\\
-3  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark & & ~\xmark & & ~\xmark\\
-4  & Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &14.6\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
-5  & Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 9.2\,s & & ~\xmark & 16,10 & 1.4\,s\\
-6  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 4683.8\,s &  & ~\xmark & & ~\xmark\\
-7  & Chen\_ex3   & 7 &   & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-9  & Cruise      & 1 & 16,8 & 9.6\,s & 16,10 & 6.5\,s & 24,14 & 0.3\,s& 16,10 & 0.3\,s\\
-10 & CruiseHSCC & 1 & 16,8 & 9.6\,s & 16,10 & 6.6\,s &  24,14 & 0.3\,s & 16,10 & 0.3\,s \\
-11 & Cstr & 3 & & ~\xmark & & ~\xmark & & ~\xmark & & 181s~\xmark\\
-12 & Cstrtmp  & 3 &  & ~\xmark & & ~\xmark & 24,14 & 0.5\,s & & ~\xmark\\
-13 & DCmotor   & 2 & 16,8  & 11.3\,s & 16,10 & 7.8\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s (4.0\,s) \\
-14 & Flexbeam   & 6 & & ~\xmark & & ~\xmark & 24,14 & 72.1\,s & & ~\xmark\\
-15 & Guidance chen  & 5 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-16 & Helicopter   & 3 & 16,8 & 13.8\,s & 32,23 & 148\,s & 24,14 & 0.8\,s& 16,10 & 1.1\,s (56.6\,s)\\
-17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-18 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 16,10 & 28.2\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
-19 & Magpointer   & 2 & 16,8 & 10.1\,s & 16,10 & 20.4\,s & 24,14  & 1\,s& 16,10 & 1.3\,s (\xmark)\\
-20 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 34.8\,s & 24,14 & 0.5\,s & 16,10 & 0.6\,s (\xmark)\\
-21 & Pendulum   & 2 & 16,8 & 8.5\,s & 32,23 & 24\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s (2.4\,s)\\
-22 & Regulator   & 5 & & ~\xmark & & ~\xmark & &~\xmark  & & 529s~\xmark\\
-23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & 14.1s~\xmark\\
-24 & streamdrum   & 3 & 16,8  & 332.5\,s & 16,10 & 590.5\,s & 24,14 & 0.7\,s & 16,10 &1.3\,s\\
-25 & Suspension  & 4 & 16,8  & 17.2\,s & 16,10 &1373\,s & 56,30 & 15.3\,s & 16,10 & 4.4\,s (313.6\,s)\\
-26 & Tapedriver   & 3 & 16,8  & 8.2\,s & & ~\xmark & 64,22 & 2.1\,s & 16,10 & 1.1\,s (6.0\,s)\\
+\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                  \\
+   &     & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$}& \multicolumn{1}{|c|}{Time}  \\\hline
+1  & Acrobot     & 4 & 16,8 & 61959.4\,s &  & ~\xmark \\
+%2  & Antenna     & 6 &  & ~\xmark &  & ~\xmark & \\
+2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
+3  & Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &14.6\,s \\
+4  & Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 9.2\,s \\
+5  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 4683.8\,s \\
+%7  & Chen\_ex3   & 7 &   & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+%8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+6  & Cruise      & 1 & 16,8 & 9.6\,s & 16,10 & 6.5\,s \\
+7 & CruiseHSCC & 1 & 16,8 & 9.6\,s & 16,10 & 6.6\,s  \\
+8 & Cstr & 3 & & ~\xmark & & ~\xmark \\
+9 & Cstrtmp  & 3 &  & ~\xmark & & ~\xmark \\
+10 & DCmotor   & 2 & 16,8  & 11.3\,s & 16,10 & 7.8\,s  \\
+11 & Flexbeam   & 6 & & ~\xmark & & ~\xmark \\
+12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
+13 & Helicopter   & 3 & 16,8 & 13.8\,s & 32,23 & 148\,s \\
+%17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+14 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 16,10 & 28.2\,s\\
+15 & Magpointer   & 2 & 16,8 & 10.1\,s & 16,10 & 20.4\,s \\
+16 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 34.8\,s \\
+17 & Pendulum   & 2 & 16,8 & 8.5\,s & 32,23 & 24\,s\\
+%22 & Regulator   & 5 & & ~\xmark & & ~\xmark & &~\xmark  & & 529s~\xmark\\
+%23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & 14.1s~\xmark\\
+18 & streamdrum   & 3 & 16,8  & 332.5\,s & 16,10 & 590.5\,s \\
+19 & Suspension  & 4 & 16,8  & 17.2\,s & 16,10 &1373\,s \\
+20 & Tapedriver   & 3 & 16,8  & 8.2\,s & & ~\xmark \\
 \hline
@@
 
-\textcolor{blue}{Both approaches fail to synthesise a controller for half of the instances.}  
+\textcolor{blue}{We fail to synthesise a controller for several instances.}  
 For the multi-stage approach, the completeness threshold may be too large, thus causing a timeout. 
-On the other hand, the abstraction-based approach may require a very precise abstraction, resulting in too many refinements and, consequently, again in a timeout.  
+A controller simply may not exist for these benchmarks at this given time discretisation and controller
+precision.  
 Yet another source of incompleteness is the inability of the {\sc synthesize} phase to use a large enough precision for
@@
 
-\textit{Abstraction on other properties:} The performance gain from abstract
-acceleration may not hold for more complex properties than safety, for
-instance ``eventually reach and always remain in a given safe set''.
+%\textit{Abstraction on other properties:} The performance gain from abstract
+%acceleration may not hold for more complex properties than safety, for
+%instance ``eventually reach and always remain in a given safe set''.
 
@@
 
-We have presented two automated approaches to synthesize digital
+We have presented an automated approach to synthesize digital
 state-feedback controllers that ensure both stability and safety over state-space models.   
-The first approach relies on unfolding of the closed-loop model dynamics up to a completeness threshold, while the second
-one applies abstraction-refinement and acceleration to increase speed, whilst retaining soundness.
-%
-Both approaches are novel within the control literature: they give a fully
+%The first approach relies on unfolding of the closed-loop model dynamics up to a completeness threshold, while the second
+%one applies abstraction-refinement and acceleration to increase speed, whilst retaining soundness.
+%
+Our approach is novel within the control literature: we give a fully
 automated synthesis method that is algorithmically and numerically sound,
@@
 %
-Our experimental results show that both approaches are able to synthesize fully automatically 
+Our experimental results show we are able to synthesize fully automatically 
 safe controllers for most benchmarks, which have been derived from the control literature, 
@@
 
-\note{Let us collect here the main extensions we regard to be relevant: \\ 
-models with partial observations; \\ 
-implementation with SMT; \\ 
-continuous-time; \\ 
-more complex specs; \\ 
-\ldots }
+%
+%\note{Let us collect here the main extensions we regard to be relevant: \\ 
+%models with partial observations; \\ 
+%implementation with SMT; \\ 
+%continuous-time; \\ 
+%more complex specs; \\ 
+%\ldots }
 

### 2019-01-09 automatica/paper.tex
todo
remove bit about lines of code

@@
 download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}
-\textcolor{red}{Lucas: I'll need support from Pascal to create this VirtualBoxOVA}
 We further created a VirtualBox OVA image with our tool pre-installed,
@@
 instructions to run all benchmarks and reproduce our
-experiments.\footnote{\url{XXXXXXXXXX}}
-
-\textcolor{red}{This paragraph needs to be updated by Elizabeth and Dario.}
-
-The entire implementation consists of $XXX$ and $XXX$ lines of C code in the multi-stage and abstract
-accelerator back-ends, respectively, $XXXX$ lines of C code for utility functions such as interval, 
-fixed- and floating-point arithmetic, as well as $1000$ lines of C++ code in the control synthesis
-module in CEGIS CBMC.  We evaluate \tool~using $XXX$ SISO control system
-benchmarks.
+experiments.\footnote{\note{\url{XXXXXXXXXX}}}
+%
+%\textcolor{red}{This paragraph needs to be updated by Elizabeth and Dario.}
+%
+%The entire implementation consists of $XXX$ and $XXX$ lines of C code in the multi-stage and abstract
+%accelerator back-ends, respectively, $XXXX$ lines of C code for utility functions such as interval, 
+%fixed- and floating-point arithmetic, as well as $1000$ lines of C++ code in the control synthesis
+%module in CEGIS CBMC.  We evaluate \tool~using $XXX$ SISO control system
+%benchmarks.
 
@@
 %-------------------------------
-
+\note{redo number and remove benchmarks that we can't solve}
 The \textit{acrobot} (\#1) plant corresponds to the model of a two-link 

### 2019-01-09 automatica/paper.tex
messing with benchmark section

@@
 
-Our benchmark suite consists of 26 SISO models extracted from the 
-control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal};
-these models are discretized with different sampling times, 
-leading to $191$ different benchmarks to evaluate the Multi-staged and Abstraction-based CEGIS algorithms.
+Our benchmark suite consists of 20 SISO models extracted from the 
+control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal}.
+The models are discretized with sampling times ranging from 1.5s to 0.005s, and if CEGIS is unable to 
+synthesise a controller for a given sampling time, CEGIS heuristically selects a new sampling time.
 
@@
 %-------------------------------
-\note{redo number and remove benchmarks that we can't solve}
-The \textit{acrobot} (\#1) plant corresponds to the model of a two-link 
+
+The \textit{acrobot}plant corresponds to the model of a two-link 
 underactuated robot manipulator, 
 %named acrobot, 
-linearized by partial feedback linearization~\cite{acrobot}.The \textit{antenna} benchmark (\#2) 
-describes the dynamics of the azimuth angle of an antenna 
-motion system composed by a gearbox, a DC motor and amplifiers~\cite{gajic2008optimal}. 
-The \textit{ballmaglev} (\#3) plant corresponds to the model of a simple 
+linearized by partial feedback linearization~\cite{acrobot}.
+%The \textit{antenna} benchmark (\#2) 
+%describes the dynamics of the azimuth angle of an antenna 
+%motion system composed by a gearbox, a DC motor and amplifiers~\cite{gajic2008optimal}. 
+The \textit{ballmaglev}  plant corresponds to the model of a simple 
 eletromagnet-ball system, where a steel ball can be levitated by the force generated by an electromagnet~\cite{Franklin15}.  
-The \textit{bioreactor} benchmark (\#4) is a linear model 
+The \textit{bioreactor} benchmark  is a linear model 
 %identified by least squares 
@@
 
-The \textit{Chen\_ex1}, \textit{Chen\_ex2}, \textit{Chen\_ex3} and \textit{Chen\_ex4} 
-benchmarks (\#5-8) correspond to high-order control system 
+The \textit{Chen\_ex1} and \textit{Chen\_ex2}
+benchmarks correspond to high-order control system 
 %discrete 
 models employed as case studies for model-order reduction techniques~\cite{CHEN1979389}. 
-The benchmarks \textit{Cruise}~\cite{Franklin15} (\#9) and \textit{CruiseHSCC}~\cite{Astrom08} (\#10) deal with 
+The benchmarks \textit{Cruise}~\cite{Franklin15} and \textit{CruiseHSCC}~\cite{Astrom08} deal with 
 automotive cruise control models, where control is used to keep 
@@
 %There are two continuous stirred tank reactor models named 
-\textit{cstr} (\#11) and \textit{cstrtmp} (\#12) describe the PH dynamics of a reaction 
+\textit{cstr}  and \textit{cstrtmp}  describe the PH dynamics of a reaction 
 of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
@@
 %continuous flow stirred-
-tank reactor. The \textit{DC motor} plant (\#13) describes the velocity 
+tank reactor. The \textit{DC motor} plant  describes the velocity 
 dynamics of a 
@@
 
-The \textit{Flexbeam} benchmark (\#14) is 
+The \textit{Flexbeam} benchmark  is 
 %a plant 
@@
 a flexible metallic structure with sensors and actuators. 
-The \textit{guidance chen} benchmark (\#15) is a high-order system model used by Chen et al.~\cite{CHEN1979389} to evaluate 
+The \textit{guidance chen} benchmark ( is a high-order system model used by Chen et al.~\cite{CHEN1979389} to evaluate 
 model-order reduction techniques; it models a guidance control system, 
 which is used to determine the path of an autonomous vehicle. 
-The \textit{helicopter} benchmark plant (\#16) describes the transitional and rotational dynamics 
+The \textit{helicopter} benchmark plant  describes the transitional and rotational dynamics 
 %of transitional motion with respect to a longitudinal plane and the rotational motion around the longitudinal axis for 
@@
 
-\textit{Invpendulum\_cartpos} (\#17) and \textit{Invpendulum\_pendang} (\#18) 
-are models for the cart position and the angle of an inverted pendulum placed on the cart,  
+%\textit{Invpendulum\_cartpos}  and 
+The \textit{Invpendulum\_pendang}  
+describes a model for the cart position and the angle of an inverted pendulum placed on the cart,  
 %plant composed by a point mass, which must be equilibrated above the pivot point and is mounted on an one degree of freedom cart that 
@@
 
-The \textit{magpointer} (\#19) describes a magnetic pointer, 
+The \textit{magpointer}  describes a magnetic pointer, 
 % plant composed by a pointer employed in analogue gauges and indicators, 
 whose angular position dynamics is controlled by a magnetic field. 
-The \textit{magsuspension} describes (\#20) the dynamic of a magnetic car suspension system. 
-The \textit{pendulum} (\#21) plant consists of a swinging point mass suspended from a frictionless pivot by means of a rod with negligible mass.
-
-The \textit{Regulator} (\#22) consists of a linear model of a synchronous electrical machine% connected to an infinite bus
+The \textit{magsuspension} describes  the dynamic of a magnetic car suspension system. 
+The \textit{pendulum}  plant consists of a swinging point mass suspended from a frictionless pivot by means of a rod with negligible mass.
+
+The \textit{Regulator} consists of a linear model of a synchronous electrical machine% connected to an infinite bus
 ~\cite{KOKOTOVIC198023}. 
-The \textit{springer-mass damper system} plant (\#23) is a standard model for the dynamics of several mechanical systems. 
+The \textit{springer-mass damper system} plant is a standard model for the dynamics of several mechanical systems. 
 %This benchmark describes a mass, which is fixed to a node by means of a springer and moves under the action of an input force, damping, and elastic force.
-The \textit{steam drum} benchmark (\#24) describes a linear model for the level dynamics of a boiler steam drum~\cite{boiler}.
-
-The \textit{suspension} (\#25) models a single-wheel suspension system of a car, 
+The \textit{steam drum} benchmark describes a linear model for the level dynamics of a boiler steam drum~\cite{boiler}.
+
+The \textit{suspension} models a single-wheel suspension system of a car, 
 namely the relative motion dynamics of a mass springer damp model, which connects the car to one of its wheels.  
-The \textit{tapedriver} benchmark (\#26) models a computer tape driver, 
+The \textit{tapedriver} benchmark  models a computer tape driver, 
 that is a computer storage device used to read and write data on magnetic tapes.
@@
 %2  & Antenna     & 6 &  & ~\xmark &  & ~\xmark & \\
-2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
-3  & Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &14.6\,s \\
-4  & Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 9.2\,s \\
-5  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 4683.8\,s \\
-%7  & Chen\_ex3   & 7 &   & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+%2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
+2  & Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &14.6\,s \\
+3  & Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 9.2\,s \\
+4  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 4683.8\,s \\
+5  & Chen\_ex3   & 7 & 16,8  & 11.4\,s & 16,10 & 67.6\,s \\
 %8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
@@
 7 & CruiseHSCC & 1 & 16,8 & 9.6\,s & 16,10 & 6.6\,s  \\
-8 & Cstr & 3 & & ~\xmark & & ~\xmark \\
+8 & Cstr & 3 & & ~\xmark & & 19.842\,s \\
 9 & Cstrtmp  & 3 &  & ~\xmark & & ~\xmark \\

### 2019-01-09 automatica/paper.tex
tmp results update
(not final)

@@
    &     & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$}& \multicolumn{1}{|c|}{Time}  \\\hline
-1  & Acrobot     & 4 & 16,8 & 61959.4\,s &  & ~\xmark \\
+1  & Acrobot     & 4 & 16,8 & 61529.8\,s &  & ~\xmark \\
 %2  & Antenna     & 6 &  & ~\xmark &  & ~\xmark & \\
 %2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
-2  & Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &14.6\,s \\
-3  & Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 9.2\,s \\
-4  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 4683.8\,s \\
-5  & Chen\_ex3   & 7 & 16,8  & 11.4\,s & 16,10 & 67.6\,s \\
+2  & Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &21.8\,s \\
+3  & Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 12.1\,s \\
+4  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 3535s.1\,s \\
+5  & Chen\_ex3   & 7 & 16,8  & 11.4\,s & 16,10 & 59.1\,s \\
 %8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-6  & Cruise      & 1 & 16,8 & 9.6\,s & 16,10 & 6.5\,s \\
-7 & CruiseHSCC & 1 & 16,8 & 9.6\,s & 16,10 & 6.6\,s  \\
+6  & Cruise      & 1 & 16,8 & 9.7\,s & 16,10 & 9.7\,s \\
+7 & CruiseHSCC & 1 & 16,8 & 9.7\,s & 16,10 & 9.7\,s  \\
 8 & Cstr & 3 & & ~\xmark & & 19.842\,s \\
-9 & Cstrtmp  & 3 &  & ~\xmark & & ~\xmark \\
-10 & DCmotor   & 2 & 16,8  & 11.3\,s & 16,10 & 7.8\,s  \\
-11 & Flexbeam   & 6 & & ~\xmark & & ~\xmark \\
-12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
-13 & Helicopter   & 3 & 16,8 & 13.8\,s & 32,23 & 148\,s \\
+9 & Cstrtmp  & 3 & 16,8 & 12.5\,s &16,10 & 14.4\,s \\
+10 & DCmotor   & 2 & 16,8  & 10.0\,s & 16,10 & 11.4\,s  \\
+11 & Flexbeam   & 6 & & ~\xmark & 16, 10 & 10916.1\,s \\
+%12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
+12 & Helicopter   & 3 &  & ~\xmark & 16,10 & 28.7\,s \\
 %17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-14 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 16,10 & 28.2\,s\\
-15 & Magpointer   & 2 & 16,8 & 10.1\,s & 16,10 & 20.4\,s \\
-16 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 34.8\,s \\
-17 & Pendulum   & 2 & 16,8 & 8.5\,s & 32,23 & 24\,s\\
-%22 & Regulator   & 5 & & ~\xmark & & ~\xmark & &~\xmark  & & 529s~\xmark\\
-%23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & 14.1s~\xmark\\
-18 & streamdrum   & 3 & 16,8  & 332.5\,s & 16,10 & 590.5\,s \\
-19 & Suspension  & 4 & 16,8  & 17.2\,s & 16,10 &1373\,s \\
-20 & Tapedriver   & 3 & 16,8  & 8.2\,s & & ~\xmark \\
+13 & Invpendulum\_pendang & 2 &  & ~\xmark & 16,10 & 13.8\,s\\
+14 & Magpointer   & 2 &  & ~\xmark & 16,10 & 80.7\,s \\
+15 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 42.3\,s \\
+16 & Pendulum   & 2 & 16,8 & 13.6\,s & 16,10 & 16.1\,s\\
+17 & Regulator   & 5 & & ~\xmark & 16,10 & 996.4\,s\\
+18 & Springmassdamper & 2 & & ~\xmark &16,10 & 16.0s \\
+19 & Streamdrum   & 3 & 16,8  & 700.9s & 16,10 & 24.4\,s \\
+20 & Suspension  & 4 & 16,8  & 11.4\,s & 16,10 &15.4\,s \\
+21 & Tapedriver   & 3 & 16,8  & 11.1\,s &16,10 & 13.2\,s \\
 \hline

### 2019-01-11 automatica/paper.tex
results

--- 2019-01-09 automatica/paper.tex
@@
 We separate our evaluation into two sets of results: fixed- and floating-point. 
+We are able to synthesise more floating point controllers than fixed point controllers, likely because the
+floating point controllers are at a higher precision than the fixed point. It may be that the precision of the fixed-point
+controllers is too low to be able to meet the safety specification. The floating point controllers take longer to synthesise
+than the fixed point controllers.
 %For the majority of the {\it fixed-point} benchmarks, we observe that the abstraction-based
@@
 \centering
-\begin{tabular}{| r | l | c | c | r | c | r |}
+\begin{tabular}{| l | c | c | r | c | r |}
 %
 \hline
-\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                  \\
-   &     & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$}& \multicolumn{1}{|c|}{Time}  \\\hline
-1  & Acrobot     & 4 & 16,8 & 61959.4\,s &  & ~\xmark \\
-%2  & Antenna     & 6 &  & ~\xmark &  & ~\xmark & \\
+% \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Run-time} \\
+ Benchmark  &  Order  & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Time & $\mathcal{F}_{\langle E_p, M_p \rangle}$ & Time \\\hline
+%1  & Acrobot     & 4 & 16,8 & 61529.8\,s &  & ~\xmark \\
+ Antenna     & 6 &  & ~\xmark & 16,10 & 817.4\,s \\
 %2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
-2  & Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &14.6\,s \\
-3  & Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 9.2\,s \\
-4  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 4683.8\,s \\
-5  & Chen\_ex3   & 7 & 16,8  & 11.4\,s & 16,10 & 67.6\,s \\
+ Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &23.6\,s \\
+ Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 12.7\,s \\
+%4  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 3535s.1\,s \\
+ Chen\_ex3   & 7 & 16,8  & 11.4\,s & 16,10 & 59.1\,s \\
 %8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-6  & Cruise      & 1 & 16,8 & 9.6\,s & 16,10 & 6.5\,s \\
-7 & CruiseHSCC & 1 & 16,8 & 9.6\,s & 16,10 & 6.6\,s  \\
-8 & Cstr & 3 & & ~\xmark & & 19.842\,s \\
-9 & Cstrtmp  & 3 &  & ~\xmark & & ~\xmark \\
-10 & DCmotor   & 2 & 16,8  & 11.3\,s & 16,10 & 7.8\,s  \\
-11 & Flexbeam   & 6 & & ~\xmark & & ~\xmark \\
-12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
-13 & Helicopter   & 3 & 16,8 & 13.8\,s & 32,23 & 148\,s \\
+ Cruise      & 1 & 16,8 & 9.7\,s & 16,10 & 10.3\,s \\
+ CruiseHSCC & 1 & 16,8 & 9.7\,s & 16,10 & 10.3\,s  \\
+ Cstr & 3 & & ~\xmark & 16,10 & 21.4\,s \\
+ Cstrtmp  & 3 & 16,8 & 12.5\,s &16,10 & 15.4\,s \\
+ DCmotor   & 2 & 16,8  & 10.0\,s & 16,10 & 11.4\,s  \\
+%11 & Flexbeam   & 6 & & ~\xmark & 16, 10 & 10916.1\,s \\
+%12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
+ Helicopter   & 3 &  & ~\xmark & 16,10 & 32.0\,s \\
 %17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-14 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 16,10 & 28.2\,s\\
-15 & Magpointer   & 2 & 16,8 & 10.1\,s & 16,10 & 20.4\,s \\
-16 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 34.8\,s \\
-17 & Pendulum   & 2 & 16,8 & 8.5\,s & 32,23 & 24\,s\\
-%22 & Regulator   & 5 & & ~\xmark & & ~\xmark & &~\xmark  & & 529s~\xmark\\
-%23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & 14.1s~\xmark\\
-18 & streamdrum   & 3 & 16,8  & 332.5\,s & 16,10 & 590.5\,s \\
-19 & Suspension  & 4 & 16,8  & 17.2\,s & 16,10 &1373\,s \\
-20 & Tapedriver   & 3 & 16,8  & 8.2\,s & & ~\xmark \\
+ Invpendulum\_pendang & 2 & 16,8  & 10.7 & 16,10 & 14.8\,s\\
+ Magpointer   & 2 &  & ~\xmark & 16,10 & 86.0\,s \\
+ Magsuspension  & 2 & 12,12  & 39.0\,s  & 16,10 & 43.2\,s \\
+ Pendulum   & 2 & 16,8 & 13.2\,s & 16,10 & 16.6\,s\\
+ Regulator   & 5 & 16,8 & 1532.7\,s & 16,10 & 999.6\,s\\
+ Springmassdamper & 2 & & ~\xmark &16,10 & 24.2s \\
+ Steamdrum   & 3 & 16,8  & 700.9s & 16,10 & 24.4\,s \\
+ Suspension  & 4 & 16,8  & 11.4\,s & 16,10 &15.4\,s \\
+ Tapedriver   & 3 & 16,8  & 11.4\,s &16,10 & 13.3\,s \\
 \hline
@@
 
-The median run-time for \textcolor{blue}{the successful} benchmarks is 6.6\,s for the fixed-point and 5.45\,s for floating-point implementations, respectively.  
+The mean run-time for \textcolor{blue}{the successful} benchmarks is 152.6\,s for the fixed-point and 117.5\,s for floating-point implementations, respectively.
+The mean run-time for \textcolor{blue}{the successful} benchmarks is 16\,s for the fixed-point and 11\,s for floating-point implementations, respectively.
 We consider these times short enough to be of practical use to control engineers, and thus affirm the validity of EG1.
@@
 \textcolor{blue}{We fail to synthesise a controller for several instances.}  
-For the multi-stage approach, the completeness threshold may be too large, thus causing a timeout. 
-A controller simply may not exist for these benchmarks at this given time discretisation and controller
+The completeness threshold may be too large, thus causing a timeout, or controller simply may not exist for these benchmarks at this given time discretisation and controller
 precision.

### 2019-01-11 benchmark-runner/completeness-threshold-float-benchmark-runner.sh
tweaks to script

@@ -101,12 +101,17 @@ if [ "$1" == "dkr13" ]; then
 benchmark_dirs=(${BENCHMARK_BASE_DIR}/magneticpointer/ ${BENCHMARK_BASE_DIR}/magsuspension/ ${BENCHMARK_BASE_DIR}/pendulum/ ${BENCHMARK_BASE_DIR}/regulator/ ${BENCHMARK_BASE_DIR}/springmassdamperHSCC/ ${BENCHMARK_BASE_DIR}/steamdrum/ ${BENCHMARK_BASE_DIR}/suspension/ ${BENCHMARK_BASE_DIR}/tapedriver/ ${BENCHMARK_BASE_DIR}/usgtampa/) 
 fi
 
+#dkr13
+if [ "$1" == "dkr14" ]; then
+benchmark_dirs=(${BENCHMARK_BASE_DIR}/uscgtampa/)
+fi
+
 working_directory_base="/tmp/control_synthesis-float-${working_directory_base_suffix}"
 mkdir -p ${working_directory_base} 2>/dev/null
 
 for benchmark_dir in ${benchmark_dirs[@]}; do
   echo "benchmark dir $benchmark_dir"	
- time_tmp_file=/tmp/times${working_directory_base_suffix}.log
+ time_tmp_file=/tmp/times${working_directory_base_suffix}_float.log
  times >${time_tmp_file}; start_time=$(get_current_cpu_millis)
 
  for benchmark in ${benchmark_dir}*.h; do

### 2019-01-11 benchmark-runner/completeness-threshold-ss-benchmark-runner.sh

@@ -30,6 +30,7 @@ function echo_log {
 function echo_success_message {
  start_time=$1
  end_time=$2
+ echo_log "start time: $start_time, end time: $end_time"
  runtime=$((end_time-start_time))
  echo_log 'SYNTHESIS SUCCESSFUL'
  echo_log "<control_synthesis_time>${runtime}</control_synthesis_time>"
@@ -76,6 +77,7 @@ function compile_precision_check {
 function get_current_cpu_millis {
  cat ${time_tmp_file} >>${log_file}
  formula=$(sed -r 's/([0-9]+(\.[0-9]+)?)m([0-9]+)\.0*([0-9]+)?s/60000*\1+1000*\3+\4/g' ${time_tmp_file} | tr '\n' ' ' | sed -r 's/ /+/g' | sed -r 's/(.*)[+]$/\1/' | sed -r 's/(.*)[+]$/\1/' | sed -r 's/[+]+/+/')
+ 
  echo $((${formula}))
 }
 
@@ -102,7 +104,17 @@ fi
 
 #dkr15
 if [ "$1" == "dkr15" ]; then
-benchmark_dirs=(${BENCHMARK_BASE_DIR}/tapedriver/)
+benchmark_dirs=(${BENCHMARK_BASE_DIR}/chen_ex2/ ${BENCHMARK_BASE_DIR}/chen_ex3/ ${BENCHMARK_BASE_DIR}/antenna/)
+fi
+
+#dkr15
+if [ "$1" == "dkr16" ]; then
+benchmark_dirs=(${BENCHMARK_BASE_DIR}/chen_ex4/ ${BENCHMARK_BASE_DIR}/flexbeam/)
+fi
+
+#dkr15
+if [ "$1" == "dkr17" ]; then
+benchmark_dirs=(${BENCHMARK_BASE_DIR}/bioreact/ )
 fi
 
 working_directory_base="/tmp/control_synthesis-fixed-ss-${working_directory_base_suffix}"
@@ -110,15 +122,16 @@ mkdir -p ${working_directory_base} 2>/dev/null
 
 for benchmark_dir in ${benchmark_dirs[@]}; do
   echo "benchmark dir $benchmark_dir"	
- time_tmp_file=/tmp/times${working_directory_base_suffix}.log
+ time_tmp_file=/tmp/times${working_directory_base_suffix}_ss.log
  times >${time_tmp_file}; start_time=$(get_current_cpu_millis)
[…]

### 2019-01-11 benchmark-runner/universalrunner/control_types.hpp
increase precision for plant in precision check

@@ -9,13 +9,14 @@
 #include "half.hpp"
 #endif
 
-typedef double __plant_precisiont;
+typedef long double __plant_precisiont;
 
 #define CONTROL_WIDTH (INT_BITS + FRAC_BITS)
 
 #ifndef FLOAT
-typedef __int128 uint128_t;
-typedef __int128 int128_t;
+//typedef __int128 uint128_t;
+
+//typedef __int128 int128_t;
 #if CONTROL_WIDTH == 8u
 typedef int8_t __controller_base_typet;
 #elif CONTROL_WIDTH == 16u

### 2019-01-12 automatica/paper.tex
wordings

@@
 namely a model encompassing a plant exhibiting continuous behavior, 
-whereas the controller operates in discrete time and over a quantized domain.  
+and a controller operating in discrete time and over a quantized domain.  
 In particular, our model evaluates the effects of the quantizers (A/D and D/A
@@
 by our modelling of the plant using finite precision arithmetic. 
-We reason safety requirements, which are frequently overlooked in conventional feedback control synthesis, but
+We reason about safety requirements, which are frequently overlooked in conventional feedback control synthesis, but
 play a key role in systems engineering, particularly for safety-critical applications of clear concern in modern autonomy contexts.
@@
   %% systems, such as the presence of A/D quantizers and FWL operations.  
-  In addition a stability property, the automatically computed state-feedback
-  controllers must also guarantee a given safety specification.
+  The automatically computed state-feedback
+  controllers guarantee a given safety specification.
   The implication is that, as opposed to existing
@@
 \else  
-\item We present a novel multi-staged approach to synthesising digital controllers, using on 
+\item We present a novel multi-staged approach to synthesising digital controllers, using 
   an unfolding of the dynamics up to a completeness threshold, and bit precise Bounded Model
-  Checking to account for sources of imprecision in the implementation of the digital control algorithm
-  and the modelling of the plant.
+  Checking to account for fixed-point arithmetic used in the implementation of the digital control algorithm
+  and interval arithmetic to account for the imprecision in the modelling of the plant. 
   \fi
@@
 
-The technique underpinning tools such as Pessoa~\cite{mazo2010pessoa} and related extensions \cite{Anta2010,liu16} and applications \cite{zamani2014}, 
+The technique underpinning tools such as Pessoa~\cite{mazo2010pessoa}, related extensions \cite{Anta2010,liu16} and applications \cite{zamani2014}, 
 synthesizes correct-by-design embedded control software for LTI models.    

### 2019-01-12 benchmarks/matlab/get_charpoly.m

@@ -4,7 +4,7 @@ filename = strcat('charpolys.h')
 fileID = fopen(filename,'w');
 fprintf(fileID, '#if NSTATES==1\n\n');
 
-for n=2:8
+for n=9
     
 %A = sym('A',[n,n]);
 %B = sym('B',[n,1]);

### 2019-01-13 automatica/paper.tex
changes

@@
 
-The technique underpinning tools such as Pessoa~\cite{mazo2010pessoa}, related extensions \cite{Anta2010,liu16} and applications \cite{zamani2014}, 
+The technique underpinning tools such as Pessoa~\cite{mazo2010pessoa}, related extensions \cite{Anta2010,liu16}, and applications \cite{zamani2014}
 synthesizes correct-by-design embedded control software for LTI models.    
@@
 %properties.  
-The controller software can then be refined (implemented) over the concrete LTI model. 
+The controller software can then be implemented over the concrete LTI model. 
 %can be more complicated than
 %the state-feedback control we synthesize, and the properties available cover more detail.  
-However, relying on state-space discretization \mbox{Pessoa} is likely to incur in scalability limitations.   
+However, relying on state-space discretization, \mbox{Pessoa} is likely to incur scalability limitations.   
 %Along this research line, \cite{Anta2010,liu16} studies the synthesis of digital controllers for
@@
 
-There are two different problems that arise from FWL semantics.  The first
+There are two different problems that arise from FWL semantics in digital controllers.  The first
 is the error caused by the inability to represent the exact
@@
 Similarly, 
-\cite{liberzon2003hybrid} evaluates the quantization error dynamics and \note{[unclear] bounds its trajectory to a known region over a finite time period}.   
+\cite{liberzon2003hybrid} evaluates the quantization error dynamics and calculates an upper and lower
+bound for the possible trajectory of the system up to a finite time. 
 %This technique works for both linear and non-linear systems.
@@
 around a specific dynamical behavior \cite{astrom1997computer}.  As argued
-later in this work, we will target more complex objectives, such as
+later in this work, we will target a more complex objective,
 quantitative safety requirements, which are not typical in the digital
-control literature.  Further, we will embrace the digital nature of the
-controller, which manipulates quantized signals as discrete quantities represented with finite precision.
+control literature. We will precisely account for the digital nature
+of the controller, which manipulates quantised signals as discrete quantities represented with
+finite precision.
+
+% Further, we will embrace the digital nature of the
+%controller, which manipulates quantized signals as discrete quantities represented with finite precision.
 
@@
 In this work we employ asymptotic stability in the CEGIS loop,  
-as an objective for guessing controllers that are later proven sound over safety requirements.  
+as a means for reducing the search space of possible safe controller. As discussed later, a safe controller is necessarily asymptotically stable, although the reverse is not true.
+%as an objective for guessing controllers that are later proven sound over safety requirements.  
 Asymptotic stability is a property that amounts to convergence of the model executions to an equilibrium point, 
 starting from any states in a neighborhood of the point (see Figure~\ref{fig:ct} for the portrait of a stable execution, converging to the origin).   
-In the case of linear systems as in~\eqref{eq:closedloopss}, 
+In the case of linear systems %as in~\eqref{eq:closedloopss}, 
 considered with a zero reference signal, 
@@
 
-A discrete-time LTI system as \eqref{eq:closedloopss} is asymptotically
+A discrete-time LTI system %as \eqref{eq:closedloopss} 
+is asymptotically
 stable if all the roots of its characteristic polynomial (i.e., the
@@
 \eqref{eq:closedloopss} meets given safety specifications.  A safety
-specification gives raise to a requirement on the states of the model, such
-that the feedback controller (namely the choice of the gains matrix~$K$)
+specification gives rise to a requirement on the states of the model, such
+that the feedback controller (namely the choice of the gain matrix~$K$)
 must ensure that the state never violates the requirement.  Note that a
@@
 for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
-instant, respectively.  This means that the states will always be within an $n$-dimensional hyper-box.
+instant, respectively.  This requires that the states will always be within an $n$-dimensional hyper-box.
 
@@
 
-The key contribution of our work is that, when synthesising controllers, we precisely model the finite-precision arithmetic in the digital controller, guaranteeing that the controllers are safe.
+The key contribution of our work is that, when synthesising controllers, we precisely model the finite-precision arithmetic in the digital controller, guaranteeing that these controllers implemented with finite-precision arithmetic are safe.
 The finite precision arithmetic introduces the following errors, shown in Figure~\ref{fig:digitalsystem}.
@@
 \item The DAC could potentially introduce further errors. However, we assume that the DAC converts numbers to analogue signals with the same precision as the controller. 
-As a result we can ignore any additional errors introduced by the DAC. Again, this assumption is reasonable based on commonly available hardware. 
+As a result we can ignore any additional errors introduced by the DAC.
+Again, this assumption is reasonable based on commonly available hardware.
+It would, however, be straight forward to account for a DAC or ADC of different precision to the controller in our algorithm if necessary.
 \end{itemize}
@@
 We~interpret the ground terms over some domain~$\mathcal{D}$. 
-This is a synthesis problem, where the objective is indeed to select a valid $P$ satisfying $\phi$ over all the $a$ terms.
+This is a synthesis problem, where the objective is to synthesise a valid $P$ that satisfies $\phi$ over all the $a$ terms.
 
@@
 the set of possible {\sc inputs} corresponds to the set of possible initial states and the 
-candidate program $P$ is a candidate controllers $K$. The synthesis block generates a candidate
+candidate program $P$ is a candidate controller $K$. The synthesis block generates a candidate
 controller that works for a subset of the possible initial states, and the verifier checks whether 
@@
 %-------------------------------
-\subsection{Formal specification of stability} 
+\subsection{Jury's stability criteria} 
 \label{ssec:stabspecification}
@@
 
-There are a number of procedures that can be used for stability analysis of dynamical models~\cite{daes20161, Bessa16}, 
-which can fit our automatic verification engine.  
+There are a number of procedures that can be used for stability analysis of dynamical models\note{~\cite{daes20161, Bessa16} is self-citation really the best citation for this statement??}.
+%which can fit our automatic verification engine.  
 %one based on Schur's decomposition
@@
 
+\ifx\safetyrep
 %-------------------------------
@@
 For the input signal, these requirements practically mean that the control input saturates in view of physical constraints. 
+\fi
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{Numerical representation and soundness} 
+\label{sec:numeric_rep}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+As discussed in Section~\ref{sec:errors}, 
+the models we consider must account for errors from several sources: 
+we must bound the numerical error introduced by the finite precision we use to represent the plant (and its operations), and precisely model
+the error introduced by the ADC/DAC conversions
+and the error introduced by the limited precision used to represent the controller. 
+We use interval arithmetic to bound the error introduced by the finite precision plant, and bounded model checking to precisely model the error introduced by the ADC/DAC and the finite precision controller.
+
+\subsection{Bit-precise symbolic model checking}
+As described in section~\ref{sec:preliminaries}, we use CBMC, a bit-precise bounded model checker to synthesise and verify candidate controllers.
+CBMC performs precisely the fixed or floating point arithmetic used in the controller, as well as the ADC/DAC conversions, according to the IEEE standards.
+
+\subsection{Interval arithmetic over errors in numeric representation} 
+We use finite-precision arithmetic to model the plant. This is an approximation that speeds up each CEGIS
+iteration but necessitates a further stage where we verify that the errors introduced by the
+approximation have not caused us to generate a controller that is unsafe when executed with real numbers 
+for the plant. In this stage, we represent the plant using double precision floating point
+and we use the Boost interval arithmetic library~\cite{} to bound the error in this representation.
+We use a compositional numeric library to perform the fixed point arithmetic for the controller~\cite{}.
+We check the controller is safe starting from each vertex state, which we have shown to be sufficient to prove safety from any initial state in the hypercube of possible initial states.
+
+We outline here the mathematics behind bounding the errors on the double precision floating point.
+Recall we use $\mathcal{F}_{\langle E,M \rangle}(x)$ denote a real number $x$
+represented in a floating point domain, with $E$ bits representing the exponent and $M$ bits representing the mantissa part. Any representation of a real number using the floating point domain will
+introduce an error, for which an upper bound can be given~\cite{DBLP:conf/arith/BrainTRW15}.
+For each number represented in floating point, we store an interval that encompasses this error.
+Further
+mathematical
+operations performed at the precision $\mathcal{F}_{\langle E,M \rangle}(x)$
+will propagate these errors forward and 
+introduce further errors for which bounds can be derived~\cite{DBLP:conf/arith/BrainTRW15}.
+
+The fixed point arithmetic of the digital controller is performed on the upper and lower limit of each interval independently. Since the precision of the floating point is greater than the precision
+of the controller, this is guaranteed to bound the real behaviour of the controller.
+
+\ifx\axelerator
+
+\begin{enumerate}
+
+\item {\bf Truncation:} Let $x$ be a real number, and $\mathcal{F}_{\langle
+I,F \rangle}(x)$ be the same number represented in a fixed-point domain as
+above.  Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the
+error $ \delta_T=x\ \%_{c_m}\ \tilde x$ \note{define tilde x}, and $\%_{c_m}$ is the modulus
+operation performed on the last bit. 
+Thus, $\delta_T$ is the truncation error and it will propagate across
+operations.
+%
+\item {\bf Rounding:} The following errors are due to basic arithmetic operations.  
+Let $c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be
+the truncation errors caused by representing $c_1$ and $c_2$ in a fixed-point domain.
+%
+\begin{enumerate}
+%
+\item Addition/Subtraction: these operations only propagate errors coming
+from truncation of the operands, namely $\mathcal{F}_{\langle I,F
+\rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3$
+with $|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
+%
+\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) \cdot
+\mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3|
+\leq |\delta_{T1}\cdot\mathcal{F}_{\langle I,F \rangle}(c_2)|\allowbreak +
+|\delta_{T2}\cdot\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where
+$c_m=2^{-F}$ as above.
+%
+\item Division: the operations performed by the controllers in the FWL
+domain do not include division.  However, we do use division in computations within the plant.  
+Here the error depends on whether the divisor is greater or smaller than the dividend:  $\mathcal{F}_{\langle I,F
+\rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_{T3}$, 
+where $\delta_{T3}$ is $(\delta_{T2}\cdot c_1 - \delta_{T1}\cdot
+c_2)/(\delta_{T2}^2 - \delta_{T2} c_2)$,
+%
+%$\mathcal{F}_{\langle I,F \rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) =  (c_1 - \delta_{T1})/ (c_2 + \delta_{T2}) + c_m $, where $c_m=2^{-F}$ as above.
+\end{enumerate}
+
+\item {\bf Overflow:}
+The maximum size of a real number $x$ that can be represented in a fixed
+point domain as $\mathcal{F}_{\langle I,F \rangle}(x)$ is $\pm
+(2^{I-1}+1-2^{-F})$.  Numbers outside this range cannot be represented by
+the domain.  If overflow occurs, the interval bound becomes infinite.
+
+\end{enumerate}
+
+Similar bounds for errors introduced by 
+performing basic mathematical operators in floating-point precision can be derived~\cite{DBLP:conf/arith/BrainTRW15}.
+
+\subsection{ADC/DAC quantization errors modelled as noise} 
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+In this section we describe how quantization errors can be modelled as noise. 
+Note that this is only applicable to the acceleration back end, as the multi-stage back 
+end makes use of CBMC's bit-precise model checking capabilities to account 
+for these deterministic errors.
+
+During any given ADC conversion, the continuous signal will be sampled in
+the real domain and transformed by $\mathcal{F}_{\langle I_{c},F_{c} \rangle}
+(x)$ (assuming the ADC discretization is the same as the digital
+implementation).  This sampling uses a threshold which is defined by the
+less significant bit ($q_{c}=c_{m_c}=2^{-F_c}$) 
+%\blue{[this quantity was named $c_m$ above and in other parts of the paper - please uniformise notations]}
+of the ADC and some non-linearities of the circuitry.  The overall conversion is
+%
+$$\mathcal{F}_{\langle I_{c},F_{c} \rangle}(x(t)) = x_k :
+(x_k)_i \in \left[x_i(t)-\frac{q_{c}}{2}\ \ \ \ x_i(t)+\frac{q_{c}}{2}\right] \,.$$
+%
+\reply{where $x_i$ is the $i^{th}$ component of the vector $x$.}
+If we denote the error in the conversion by $\nu_k=x_k-x(t)$ where $t = nk$,
+and $n$ is the sampling time and $k$ the number of steps, then we may define
+some bounds for it $(\nu_k)_i \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
+
+As stated before, we assume that the domain of the
+ADC is that of the digital controller (i.e, the quantizer includes any
+digital gain added in the code).  The process of quantization in the DAC is
+similar except that it is calculating $\mathcal{F}_{\langle I_{dac},F_{dac}
+\rangle} (\mathcal{F}_{\langle I_{c},F_{c} \rangle }(x)) $.  If these domains
+are the same ($I_{c}=I_{dac},\allowbreak F_{c}=F_{dac}$), or if the DAC
+resolution in higher than the ADC, then the DAC quantization error is equal
+to zero.  From the above equations we can now define the ADC and DAC
+quantization noises ${\nu_1}_k \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}]$ and
+${\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}]$, where $q_1=q_{c}$ and 
+$q_2=q_\mathit{dac}$.  This is illustrated in
+Fig.~\ref{fig:digitalsystem} where $Q_1$ is the quantizer of the ADC
+and $Q_2$ the quantizer for the DAC.  These bounds hold irrespective of
+whether the noise is correlated, hence we may use them to over-approximate
+the noise effect on the state space progression over time.  The
+resulting dynamics are
+%
+\begin{align*}
+%\label{eq:pre_quantization}
+{x}_{k+1} = {A}_d{x}_k+{B}_d({u}_k+{{\nu}_2}_k), \quad u_k = -K{x}_{k}+{{\nu}_1}_k, 
+\end{align*}
+%
+which result in the following closed-loop dynamics:
+%
+\begin{align*}
+%\label{eq:quantization}
+{x}_{k+1} &= ({A}_d-{B}_d{K}_d) {x}_k+{B}_d{{\nu}_2}_k +{{\nu}_1}_k \,. 
+\end{align*}
+
+\fi
+
+\subsection{Effect on safety specification and stability}
+
+In this section we will quantify how the finite precision arithmetic in a digital controller affects the
+safety and stability properties of an LTI system
+
+\subsubsection{Safety of closed-loop models with finite precision controller error}
+Let us first consider the effect of the quantization errors on safety. 
+Within the controller, state values are manipulated at low precision,
+alongside the vector multiplication $Kx$.
+The inputs are computed using the following equation: 
+%
+\begin{align*}
+u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})). 
+\end{align*}
+
+This induces two types of the errors detailed above: first, the truncation
+error due to representing $x_k$ as $\mathcal{F}_{\langle I_c,F_c
+\rangle}(x_{k})$; and second, the rounding error introduced by the
+multiplication operation. This error is behaviour modelled by the bounded model checking.
+
+An additional error is due to the representation of the plant dynamics, namely 
+%
+{\scriptsize
+\begin{equation}
+x_{k+1} =\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
+\end{equation}
+}
+We address this error by use of interval
+arithmetic~\cite{moore1966interval} in the verification phase.
+
+\subsubsection{Stability of closed-loop models with fixed-point controller error}
+%-------------------------------
+\label{sec:stab_FWL}
+The proof of Jury's criterion~\cite{fadali} relies on the fact that the relationship between states and
+next states is defined by $x_{k+1} = (A_d - B_dK) x_k$, all computed
+at infinite precision.  When we employ a FWL digital controller, the
+operation becomes:
+%
+\begin{align*}
+x_{k+1} &= A_d \cdot x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
+x_{k+1} &= (A_d  - B_dK) \cdot x_k + B_dK\delta, 
+%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
+\end{align*}
+%
+where $\delta$ is the maximum error that can be introduced by the FWL
+controller in one step, i.e., by reading the states values once and
+multiplying by $K$ once.  We derive the closed form expression for $x_n$ as
+follows:
+%
+\small
+\begin{align*}
+x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
+x_{2} %&= (A_d  - B_dK)((A_d  - B_dK)x_0 + B_dK\delta ) + B_dK\delta \\
+ &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
+%x_{3}  &=(A_d  - B_dK)^3x_0 + (A_d  - B_dK)^2B_dK\delta + (A_d  - B_dK)B_dK\delta + B_dK\delta\\
+x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta +\\
+&\phantom{{}=1} ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
+  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{i=n-1}(A_d - B_dK)^iB_dk\delta. 
+\end{align*}
+\normalsize
+The definition of asymptotic stability is that the system converges to a
+reference signal, in this case we use no reference signal so an
+asymptotically stable system will converge to the origin.  We know that the
+original system with an infinite-precision controller is stable, because we
+have synthesized it to meet Jury's criterion.  Hence, $(A_d - B_dK)^n x_0$ 
+must converge to zero.
+
+%T%o show that a fixed-point implementation of the same controller will
+%converge to a finite value, we need to show that the infinite sum converges. 
+The power series of matrices
+converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less
+than~1 as follows:
+%
+%\begin{align*}
+$\sum_{i=0}^{\infty}T^i  = (I - T)^{-1}$, 
+%\end{align*}
+%
+where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge to the value 
+%
+\begin{align*}
+0 + (I - A_d + B_dK)^{-1}B_dk\delta \,. 
+\end{align*}
+%
+As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the
+safe space, then the synthesized fixed-point controller results in a safe
+closed-loop model.  The convergence to a finite value, however, will not
+make it asymptomatically stable.
+However,
+since in this paper we require stability only as a precursor to safety, it
+is sufficient to check that the (perturbed, noisy) model converges to a
+neighborhood of the equilibrium within the safe set.
+
+We can thus disregard these steady-state errors (caused by
+FWL effects) when stability is ensured by synthesis, and then verify its
+safety accounting for the finite-precision errors.
 
@@
 \fi
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Numerical representation and soundness} 
-\label{sec:numeric_rep}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-As discussed in Section~\ref{sec:errors}, 
-the models we consider must account for errors from several sources: 
-we must bound the numerical error introduced by the finite precision we use to represent the plant (and its operations), and precisely model
-the error introduced by the ADC/DAC conversions
-and the error introduced by the limited precision used to represent the controller. 
-We use interval arithmetic to bound the error introduced by the finite precision plant, and bounded model checking to precisely model the error introduced by the ADC/DAC and the finite precision controller.
-
-\subsection{Bit-precise symbolic model checking}
-As described in section~\ref{sec:preliminaries}, we use CBMC, a bit-precise bounded model checker to synthesise and verify candidate controllers.
-CBMC performs precisely the fixed or floating point arithmetic used in the controller, as well as the ADC/DAC conversions, according to the IEEE standards.
-
-\subsection{Interval arithmetic over errors in numeric representation} 
-We use finite-precision arithmetic to model the plant. This is an approximation that speeds up each CEGIS
-iteration but necessitates a further stage where we verify that the errors introduced by the
-approximation have not caused us to generate a controller that is unsafe when executed with real numbers 
-for the plant. In this stage, we represent the plant using double precision floating point
-and we use the Boost interval arithmetic library~\cite{} to bound the error in this representation.
-We use a compositional numeric library to perform the fixed point arithmetic for the controller~\cite{}.
-We check the controller is safe starting from each vertex state, which we have shown to be sufficient to prove safety from any initial state in the hypercube of possible initial states.
-
-We outline here the mathematics behind bounding the errors on the double precision floating point.
-Recall we use $\mathcal{F}_{\langle E,M \rangle}(x)$ denote a real number $x$
-represented in a floating point domain, with $E$ bits representing the exponent and $M$ bits representing the mantissa part. Any representation of a real number using the floating point domain will
-introduce an error, for which an upper bound can be given~\cite{DBLP:conf/arith/BrainTRW15}.
-For each number represented in floating point, we store an interval that encompasses this error.
-Further
-mathematical
-operations performed at the precision $\mathcal{F}_{\langle E,M \rangle}(x)$
-will propagate these errors forward and 
-introduce further errors for which bounds can be derived~\cite{DBLP:conf/arith/BrainTRW15}.
-
-The fixed point arithmetic of the digital controller is performed on the upper and lower limit of each interval independently. Since the precision of the floating point is greater than the precision
-of the controller, this is guaranteed to bound the real behaviour of the controller.
-
-\ifx\axelerator
-
-\begin{enumerate}
-
-\item {\bf Truncation:} Let $x$ be a real number, and $\mathcal{F}_{\langle
-I,F \rangle}(x)$ be the same number represented in a fixed-point domain as
-above.  Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the
-error $ \delta_T=x\ \%_{c_m}\ \tilde x$ \note{define tilde x}, and $\%_{c_m}$ is the modulus
-operation performed on the last bit. 
-Thus, $\delta_T$ is the truncation error and it will propagate across
-operations.
-%
-\item {\bf Rounding:} The following errors are due to basic arithmetic operations.  
-Let $c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be
-the truncation errors caused by representing $c_1$ and $c_2$ in a fixed-point domain.
-%
-\begin{enumerate}
-%
-\item Addition/Subtraction: these operations only propagate errors coming
-from truncation of the operands, namely $\mathcal{F}_{\langle I,F
-\rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3$
-with $|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
-%
-\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) \cdot
-\mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3|
-\leq |\delta_{T1}\cdot\mathcal{F}_{\langle I,F \rangle}(c_2)|\allowbreak +
-|\delta_{T2}\cdot\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where
-$c_m=2^{-F}$ as above.
-%
-\item Division: the operations performed by the controllers in the FWL
-domain do not include division.  However, we do use division in computations within the plant.  
-Here the error depends on whether the divisor is greater or smaller than the dividend:  $\mathcal{F}_{\langle I,F
-\rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_{T3}$, 
-where $\delta_{T3}$ is $(\delta_{T2}\cdot c_1 - \delta_{T1}\cdot
-c_2)/(\delta_{T2}^2 - \delta_{T2} c_2)$,
-%
-%$\mathcal{F}_{\langle I,F \rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) =  (c_1 - \delta_{T1})/ (c_2 + \delta_{T2}) + c_m $, where $c_m=2^{-F}$ as above.
-\end{enumerate}
-
-\item {\bf Overflow:}
-The maximum size of a real number $x$ that can be represented in a fixed
-point domain as $\mathcal{F}_{\langle I,F \rangle}(x)$ is $\pm
-(2^{I-1}+1-2^{-F})$.  Numbers outside this range cannot be represented by
-the domain.  If overflow occurs, the interval bound becomes infinite.
-
-\end{enumerate}
-
-Similar bounds for errors introduced by 
-performing basic mathematical operators in floating-point precision can be derived~\cite{DBLP:conf/arith/BrainTRW15}.
-
-\subsection{ADC/DAC quantization errors modelled as noise} 
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-In this section we describe how quantization errors can be modelled as noise. 
-Note that this is only applicable to the acceleration back end, as the multi-stage back 
-end makes use of CBMC's bit-precise model checking capabilities to account 
-for these deterministic errors.
-
-During any given ADC conversion, the continuous signal will be sampled in
-the real domain and transformed by $\mathcal{F}_{\langle I_{c},F_{c} \rangle}
-(x)$ (assuming the ADC discretization is the same as the digital
-implementation).  This sampling uses a threshold which is defined by the
-less significant bit ($q_{c}=c_{m_c}=2^{-F_c}$) 
-%\blue{[this quantity was named $c_m$ above and in other parts of the paper - please uniformise notations]}
-of the ADC and some non-linearities of the circuitry.  The overall conversion is
-%
-$$\mathcal{F}_{\langle I_{c},F_{c} \rangle}(x(t)) = x_k :
-(x_k)_i \in \left[x_i(t)-\frac{q_{c}}{2}\ \ \ \ x_i(t)+\frac{q_{c}}{2}\right] \,.$$
-%
-\reply{where $x_i$ is the $i^{th}$ component of the vector $x$.}
-If we denote the error in the conversion by $\nu_k=x_k-x(t)$ where $t = nk$,
-and $n$ is the sampling time and $k$ the number of steps, then we may define
-some bounds for it $(\nu_k)_i \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
-
-As stated before, we assume that the domain of the
-ADC is that of the digital controller (i.e, the quantizer includes any
-digital gain added in the code).  The process of quantization in the DAC is
-similar except that it is calculating $\mathcal{F}_{\langle I_{dac},F_{dac}
-\rangle} (\mathcal{F}_{\langle I_{c},F_{c} \rangle }(x)) $.  If these domains
-are the same ($I_{c}=I_{dac},\allowbreak F_{c}=F_{dac}$), or if the DAC
-resolution in higher than the ADC, then the DAC quantization error is equal
-to zero.  From the above equations we can now define the ADC and DAC
-quantization noises ${\nu_1}_k \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}]$ and
-${\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}]$, where $q_1=q_{c}$ and 
-$q_2=q_\mathit{dac}$.  This is illustrated in
-Fig.~\ref{fig:digitalsystem} where $Q_1$ is the quantizer of the ADC
-and $Q_2$ the quantizer for the DAC.  These bounds hold irrespective of
-whether the noise is correlated, hence we may use them to over-approximate
-the noise effect on the state space progression over time.  The
-resulting dynamics are
-%
-\begin{align*}
-%\label{eq:pre_quantization}
-{x}_{k+1} = {A}_d{x}_k+{B}_d({u}_k+{{\nu}_2}_k), \quad u_k = -K{x}_{k}+{{\nu}_1}_k, 
-\end{align*}
-%
-which result in the following closed-loop dynamics:
-%
-\begin{align*}
-%\label{eq:quantization}
-{x}_{k+1} &= ({A}_d-{B}_d{K}_d) {x}_k+{B}_d{{\nu}_2}_k +{{\nu}_1}_k \,. 
-\end{align*}
-
-\fi
-
-\subsection{Effect on safety specification and stability}
-
-Let us first consider the effect of the quantization errors on safety. 
-Within the controller, state values are manipulated at low precision,
-alongside the vector multiplication $Kx$.
-The inputs are computed using the following equation: 
-%
-\begin{align*}
-u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})). 
-\end{align*}
-
-This induces two types of the errors detailed above: first, the truncation
-error due to representing $x_k$ as $\mathcal{F}_{\langle I_c,F_c
-\rangle}(x_{k})$; and second, the rounding error introduced by the
-multiplication operation.
-
-An additional error is due to the representation of the plant dynamics, namely 
-%
-{\scriptsize
-\begin{equation}
-x_{k+1} =\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
-\end{equation}
-}
-We address this error by use of interval
-arithmetic~\cite{moore1966interval} in the verification phase.
-
-Previous studies~\cite{gangli1} show that the FWL affects the poles and
-zeros positions, degrading the closed-loop dynamics, causing steady-state
-errors and eventually de-stabilizing the system~\cite{Bessa16}.  However,
-since in this paper we require stability only as a precursor to safety, it
-is sufficient to check that the (perturbed, noisy) model converges to a
-neighborhood of the equilibrium within the safe set.
-
-In the following, we shall disregard these steady-state errors (caused by
-FWL effects) when stability is ensured by synthesis, and then verify its
-safety accounting for the finite-precision errors.
 

### 2019-01-13 automatica/paper.tex
labels, citation

@@
 \subsection{Bounded Model Checking}
+\label{sec:BMC}
 We use the bounded model checker CBMC~\cite{ClarkeKL04} to model controller behaviour on digitial signals with finite
@@
 \subsection{Bit-precise symbolic model checking}
-As described in section~\ref{sec:preliminaries}, we use CBMC, a bit-precise bounded model checker to synthesise and verify candidate controllers.
+As described in section~\ref{sec:BMC}, we use CBMC, a bit-precise bounded model checker to synthesise and verify candidate controllers.
 CBMC performs precisely the fixed or floating point arithmetic used in the controller, as well as the ADC/DAC conversions, according to the IEEE standards.
@@
 for the plant. In this stage, we represent the plant using double precision floating point
-and we use the Boost interval arithmetic library~\cite{} to bound the error in this representation.
+and we use the Boost interval arithmetic library~\cite{DBLP:journals/tcs/BronnimannMP06} to bound the error in this representation.
 We use a compositional numeric library to perform the fixed point arithmetic for the controller~\cite{}.

### 2019-01-13 automatica/paper.tex
tweak benchmark desc

@@
 
-The \textit{acrobot}plant corresponds to the model of a two-link 
-underactuated robot manipulator, 
+%The \textit{acrobot}plant corresponds to the model of a two-link 
+%underactuated robot manipulator, 
 %named acrobot, 
-linearized by partial feedback linearization~\cite{acrobot}.
-%The \textit{antenna} benchmark (\#2) 
-%describes the dynamics of the azimuth angle of an antenna 
-%motion system composed by a gearbox, a DC motor and amplifiers~\cite{gajic2008optimal}. 
-The \textit{ballmaglev}  plant corresponds to the model of a simple 
-eletromagnet-ball system, where a steel ball can be levitated by the force generated by an electromagnet~\cite{Franklin15}.  
+%linearized by partial feedback linearization~\cite{acrobot}.
+The \textit{antenna} benchmark (\#2) 
+describes the dynamics of the azimuth angle of an antenna 
+motion system composed by a gearbox, a DC motor and amplifiers~\cite{gajic2008optimal}. 
+%The \textit{ballmaglev}  plant corresponds to the model of a simple 
+%eletromagnet-ball system, where a steel ball can be levitated by the force generated by an electromagnet~\cite{Franklin15}.  
 The \textit{bioreactor} benchmark  is a linear model 
@@
 
-The \textit{Chen\_ex1} and \textit{Chen\_ex2}
+The \textit{Chen\_ex1} and \textit{Chen\_ex3}
 benchmarks correspond to high-order control system 
@@
 
-The \textit{Flexbeam} benchmark  is 
+%The \textit{Flexbeam} benchmark  is 
 %a plant 
-employed in vibration studies and models  
+%employed in vibration studies and models  
 %the physical system consists of 
-a flexible metallic structure with sensors and actuators. 
+%a flexible metallic structure with sensors and actuators. 
 The \textit{guidance chen} benchmark ( is a high-order system model used by Chen et al.~\cite{CHEN1979389} to evaluate 

### 2019-01-14 automatica/paper.tex
american spelling

@@
 \else  
-\item We present a novel multi-staged approach to synthesising digital controllers, using 
+\item We present a novel multi-staged approach to synthesizing digital controllers, using 
   an unfolding of the dynamics up to a completeness threshold, and bit precise Bounded Model
@@
 
-%-------------------------------
+%-------------------------------s
 \subsection{Finite precision errors}
@@
 
-The key contribution of our work is that, when synthesising controllers, we precisely model the finite-precision arithmetic in the digital controller, guaranteeing that these controllers implemented with finite-precision arithmetic are safe.
+The key contribution of our work is that, when synthesizing controllers, we precisely model the finite-precision arithmetic in the digital controller, guaranteeing that these controllers implemented with finite-precision arithmetic are safe.
 The finite precision arithmetic introduces the following errors, shown in Figure~\ref{fig:digitalsystem}.

### 2019-01-14 automatica/paper.tex
tweaks

@@
 the controller. Our approach uses counterexample-guided inductive
-synthesis (CEGIS): an inductive generalisation phase produces a
+synthesis (CEGIS): an inductive generalization phase produces a
 possible solution that is known to stabilize the system but that may
@@
 if the verification step fails, a
-counterexample is provided to the inductive generalisation and the
+counterexample is provided to the inductive generalization and the
 process iterates until a safe controller is obtained.  We demonstrate
@@
 CEGIS is an iterative process, where each iteration performs inductive
-generalisation based on counterexamples provided by a verification
-oracle (see Section~\ref{ssec:cegis}). The inductive generalisation uses information 
+generalization based on counterexamples provided by a verification
+oracle (see Section~\ref{ssec:cegis}). The inductive generalization uses information 
 about a limited number of inputs to compute a candidate solution
@@
 %% This approach uses an iterative
-%% process (see Section~\ref{ssec:cegis}), where each iteration performs inductive generalisation based
+%% process (see Section~\ref{ssec:cegis}), where each iteration performs inductive generalization based
 %% on counterexamples provided by a verification oracle.  In the absence
@@
 circle of the complex plane, i.e., their absolute values are strictly less than
-one~\cite{astrom1997computer} (this simple sufficient condition can be generalised, 
+one~\cite{astrom1997computer} (this simple sufficient condition can be generalized, 
 however this is not necessary in our work).  
@@
 \label{sec:BMC}
-We use the bounded model checker CBMC~\cite{ClarkeKL04} to model controller behaviour on digitial signals with finite
+We use the bounded model checker CBMC~\cite{ClarkeKL04} to model controller behaviour on digital signals with finite
 bit-precision.  
@@
 which we discuss in Section~\ref{ssec:safespecification}. We use a stability specification 
-in order to narrow the search space of possible controllers, as discussed in Section~\ref{ssec:stabspecification}.
+in order to narrow the search space of possible controllers, as detailed in Section~\ref{ssec:stabspecification}.
 
@@
 the error introduced by the ADC/DAC conversions
-and the error introduced by the limited precision used to represent the controller. 
+and the behaviour of the limited precision arithmetic used by the controller. 
 We use interval arithmetic to bound the error introduced by the finite precision plant, and bounded model checking to precisely model the error introduced by the ADC/DAC and the finite precision controller.
@@
 and we use the Boost interval arithmetic library~\cite{DBLP:journals/tcs/BronnimannMP06} to bound the error in this representation.
-We use a compositional numeric library to perform the fixed point arithmetic for the controller~\cite{}.
-We check the controller is safe starting from each vertex state, which we have shown to be sufficient to prove safety from any initial state in the hypercube of possible initial states.
+We use a compositional numeric library to model the fixed point arithmetic for the controller~\cite{} within
+double precision floating point numbers. We check the controller is safe starting from each vertex state, which we
+will show to be sufficient to prove safety from any initial state in the hypercube of possible initial states.
 
@@
 \else
-the instantiation of CEGIS we use to synthesise safe digital controllers. We use a multi-stage approach
-that unwinds the dynamics yup to a completeness threshold, verifying soundness using bit-precise bounded model checking.
+the instantiation of CEGIS we use to synthesise safe digital controllers, accounting for the precision issues detailed in previous sections. We use a multi-stage approach
+that unwinds the dynamics up to a completeness threshold, modelling finite-precision arithmetic using bit-precise bounded model checking, and then verifying soundness of the resulting controller using interval arithmetic.
 \fi
@@
 
-Regarding the second requirement, 
-we fix an index $k$, 
+We fix an index $k$, 
 and we synthesize a safe controller by
@@
  \State set $x_0$ to be a vertex state, e.g., $[\underline{x_0},\underline{x_0}]$	
-\For {($c=0;~c < 2^\mathit{Num\_States};~c\mbox{++}$) }
+\For {($c=0;~c < 2^n;~c\mbox{++}$) }
   %\State assert($ \underline{x_0}  \leq x_0 \leq \overline{x_0}$)
@@
 states, and the proof is shown later in this section. We thus only need to iterate through the $2^{Num\_States}$ vertex
-states, where $Num\_States$ is the number of dimensions in $x$.
+states, where $n$ is dimension of the state space (number of continuous variables).
 
@@
 Thus we only need to check $2^n$ initial states, where $n$
-is the dimension of the state space (number of continuous variables). 
+is the dimension of the state space, as before. 
 \begin{proof}
 Consider the set of initial states, $X_0$, which we assume to be convex since it is a hypercube. 
-Name $v_i$ its vertexes, where $i=1,\ldots, 2^n$.  
+Name $v_i$ its vertices, where $i=1,\ldots, 2^n$.  
 Thus any point $x \in X_0$ can be expressed by convexity as $x = \sum_{i=1}^{2^n} \alpha_i v_i$, 

### 2019-01-18 automatica/paper.tex
section 3

@@
 %$\mat{A}$ and $\mat{B}$ are matrices that fully characterize the dynamics of the continuous plant,
-We denote with $x(0)$ the initial state of the model.
+We denote with $x(0)$ the model initial condition, which can be non-deterministic.
 
@@
 %soundly 
-discretized in time~\cite{middleton1990digital,van1978computing} at constant time intervals,
-of duration $T_s$ (the sample time), 
+discretized in time~\cite{middleton1990digital,van1978computing} with constant sampling intervals, 
+each of duration $T_s$ (the sample time), 
 into the difference equation
@@
 
+\subsection{Digital control synthesis}
+
 Models \eqref{eq:ode1} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t)$ and  $u_k$, respectively. 
-Feedback architectures can be employed to manipulate the properties and behaviors of the plant:    
+Feedback architectures can be employed to manipulate properties and behaviors of the plant:    
 we are interested in the synthesis of digital feedback controllers $u_k$,  
-as practically implemented on Field-Programmable Gate Arrays or Digital Signal Processors. 
+as practically implemented on Field-Programmable Gate Arrays or Digital Signal Processors,  
 %This requires us to consider the errors introduced by, we will address the issue of variable quantization, 
 %introduced by ADC/DAC conversion blocks of Figure \ref{fig:digitalsystem}, 
-%as classically studied in \cite{astrom1997computer}.
+and as classically studied in \cite{astrom1997computer}.
 
@@
 where $u_k$ (notice we work with the discretized signal) is $u_k = r_{k} - K x_k$. 
-Here $K \in \mathbb{R}^{m \times n}$ is a state-feedback gain matrix, 
+Here $K \in \mathbb{R}^{m \times n}$ \note{wrong dimensions?} is a state-feedback gain matrix, 
 and $r_{k}$ is a reference signal (again digital). 
-We will assume $r_k=0$, thus 
+We will assume $r_k=0$, thus obtaining the closed-loop model 
 $\vec{x}_{k+1}=(\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_k$.
@@
 shaped as desired, for instance according to a specific stability goal or
-around a specific dynamical behavior \cite{astrom1997computer}.  As argued
-later in this work, we will target a more complex objective,
-quantitative safety requirements, which are not typical in the digital
-control literature. We will precisely account for the digital nature
+around a dynamical behavior of interest \cite{astrom1997computer}.  As argued
+later in this work, we will target a less standard objective,
+namely a quantitative safety requirement, which opens up to more complex specifications \note{[belta, tabuada]}. 
+This is not typical in the digital control literature. We will further precisely account for the digital nature
 of the controller, which manipulates quantised signals as discrete quantities represented with
-finite precision.
+finite precision. The new approach is fully automated and leverages an approach based on CEGIS.
 
@@
 
+\note{Ref to Fig. \ref{fig:digitalsystem} anywhere?}
+
 \subsection{Stability of closed-loop systems}
 
-In this work we employ asymptotic stability in the CEGIS loop,  
-as a means for reducing the search space of possible safe controller. As discussed later, a safe controller is necessarily asymptotically stable, although the reverse is not true.
+In this work we employ the notion of asymptotic stability within the CEGIS loop,  
+as a means for reducing the search space of possible safe controllers. 
+\note{next statement is not true - also, we have not defined safety} 
+As discussed later, a safe controller is necessarily asymptotically stable, although the reverse is not true. 
 %as an objective for guessing controllers that are later proven sound over safety requirements.  
-Asymptotic stability is a property that amounts to convergence of the model executions to an equilibrium point, 
-starting from any states in a neighborhood of the point (see Figure~\ref{fig:ct} for the portrait of a stable execution, converging to the origin).   
+Qualitatively, (local) asymptotic stability is a property denoting the convergence of the model executions towards an equilibrium point, 
+starting from any states in a neighborhood of the point. 
 In the case of linear systems %as in~\eqref{eq:closedloopss}, 
 considered with a zero reference signal, 
-the equilibrium point of interest is the origin.
-
-A discrete-time LTI system %as \eqref{eq:closedloopss} 
-is asymptotically
-stable if all the roots of its characteristic polynomial (i.e., the
+the equilibrium point of interest is the origin (see Figure~\ref{fig:ct} for the portrait of an asymptotically stable execution, converging to the origin).
+
+Of interest for this work, 
+it can be shown that a discrete-time LTI system %as \eqref{eq:closedloopss} 
+is asymptotically stable if all the roots of its characteristic polynomial (i.e., the
 eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
-circle of the complex plane, i.e., their absolute values are strictly less than
-one~\cite{astrom1997computer} (this simple sufficient condition can be generalized, 
-however this is not necessary in our work).  
-In this paper, we express this stability specification $\phi_\mathit{stability}$ in terms of a check known as
-\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic formula to
-select the entries of matrix $K$ so that the closed-loop dynamics are shaped
-as desired.
+circle of the complex plane, i.e., if their absolute values are strictly less than
+one~\cite{astrom1997computer}. 
+Whilst this simple sufficient condition can be either generalized or strengthen to be necessary, 
+this is not necessary in the context of this work.    
+What is technically key is that in this paper, 
+we shall express this asymptotic stability as a specification $\phi_\mathit{stability}$, 
+and encode it in terms of a check known as \emph{Jury's criterion}~\cite{fadali}: 
+this is an easy algebraic formula to check the entries of matrix $K$, 
+so that the closed-loop dynamics are shaped as desired.
 
@@
 safety requirements with an overall approach that is sound and automated. 
-More specifically, we require that the closed-loop system
-\eqref{eq:closedloopss} meets given safety specifications.  A safety
-specification gives rise to a requirement on the states of the model, such
+More specifically, we require that the closed-loop model 
+%\eqref{eq:closedloopss} 
+meets a given safety specification.  
+A safety specification gives rise to a requirement on the states of the model, such
 that the feedback controller (namely the choice of the gain matrix~$K$)
-must ensure that the state never violates the requirement.  Note that a
+must ensure that the state never violates the requirement.  Note that an asymptotically 
 stable, closed-loop system is not necessarily a safe system: indeed, the 
@@
 where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
-for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
-instant, respectively.  This requires that the states will always be within an $n$-dimensional hyper-box.
+for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ 
+\note{Fix/align dimensions of main model} 
+at the $k$-th instant, respectively.  This requires that the states will always be within an $n$-dimensional hyper-box.
 
@@
 $\phi_\mathit{input} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
-$\phi_\mathit{init} = \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$
-For the former, this means that the control input might saturates in view of
-physical constraints.
+\note{here you're assuming that u is 1-dim. This needs to be said somewhere. }
+and $\phi_\mathit{init} = \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$
+The former constraint expresses that control input, possibly shaped via state-feedback, 
+might saturates in view of physical constraints.
 
@@
 \label{sec:BMC}
-We use the bounded model checker CBMC~\cite{ClarkeKL04} to model controller behaviour on digital signals with finite
-bit-precision.  
-We express these controller semantics as C programs, which is CBMC's preferred input language.  
-CBMC
-symbolically executes every instruction in an input program by translating it to a boolean satisfiability problem.  
-At
-the end of this process, the entire input program is translated to a boolean satisfiability formula which is satisfiable
-iff a certain property about the program holds.  
-CBMC's API allows to specify these properties in the form of assertions
-in the input program, and we use these properties to express that our generated controllers are stable and safe.
+
+We employ the bounded model checker CBMC~\cite{ClarkeKL04} \note{newer reference?} to model the controller behavior on digital signals with finite bit-precision.  
+We express the controller semantics as C programs, which is CBMC's preferable input language.  
+CBMC symbolically executes every instruction in an input program by translating it to a boolean satisfiability problem \note{merge this sentence with next?}.  
+At the end of this process, the entire input program is translated to a boolean satisfiability formula which is satisfiable iff a certain property about the program holds.  
+CBMC's API allows to specify these properties in the form of assertions in the input program: 
+we set these properties to express that our controllers generate (asymptotically stable and) safe dynamics. 
 %\note{Do we need more details here? Should we explain e.g. SSA or give examples of how assignments, loops,
@@
 %-------------------------------s
-\subsection{Finite precision errors}
+\subsection{Errors from finite-precision arithmetics}
 \label{sec:errors}
 
-The key contribution of our work is that, when synthesizing controllers, we precisely model the finite-precision arithmetic in the digital controller, guaranteeing that these controllers implemented with finite-precision arithmetic are safe.
-The finite precision arithmetic introduces the following errors, shown in Figure~\ref{fig:digitalsystem}.
-These errors are present in the real world, and we must model them accurately
-in order to capture the full behaviour of the system. Details of how we model this arithmetic are in Section~\ref{sec:}:
+A key contribution of this work is that, when synthesizing controllers, it precisely models the finite-precision arithmetic in the digital controller, guaranteeing that these controllers implemented with finite-precision arithmetic are safe.
+Finite-precision arithmetic introduces errors, as shown in Figure~\ref{fig:digitalsystem}. 
+Details of how we model this arithmetic are in Section~\ref{sec:} \note{fix?}. 
+These errors are present in the real world, and we must model them accurately in order to capture the full behaviour of the model:
 
@@
 
-\item The ADC introduces quantisation errors when it converts the analogue signal $x(t)$ into the digital signal $x_k$. This signal is then fed into the controller cf. Figure~\ref{fig:digitalsystem}.
-
-\item The controller block performs arithmetic at a finite-precision, which introduces additional errors on top of the error introduced by the ADC.
-We assume the ADC represents numbers with at least the same precision
-as the controller and thus the precision is limited by the controller. This is a reasonable assumption based on commonly available hardware.
-
-\item The DAC could potentially introduce further errors. However, we assume that the DAC converts numbers to analogue signals with the same precision as the controller. 
+\item The ADC introduces quantisation errors when it converts the analog signal $x(t)$ into a digital signal $x_k$, which is then fed into the controller.  
+% cf. Figure~\ref{fig:digitalsystem}.
+
+\item The controller block performs arithmetic at finite precision, 
+which introduces additional errors on top of that introduced by the ADC. 
+We assume the ADC represents numbers with at least the same precision as the controller, 
+and thus focus on the precision limited by the controller. 
+This is a reasonable assumption based on commonly available hardware.
+
+\item The DAC can potentially introduce further errors. 
+However, we assume that the DAC converts numbers to analog signals with the same precision as the controller. 
 As a result we can ignore any additional errors introduced by the DAC. 
-Again, this assumption is reasonable based on commonly available hardware.
-It would, however, be straight forward to account for a DAC or ADC of different precision to the controller in our algorithm if necessary.
+Again, this assumption is practically reasonable. 
+It would, however, be straightforward to account for a DAC or ADC of different precision to the controller in our algorithm, if necessary. 
 \end{itemize}

### 2019-01-18 automatica/paper.tex
section 3

@@
 
-The arithmetic and representations used in our modelling are also carried out at a finite precision, and so we must also account for the errors in our own modelling.
-Specifically our model of the plant variables  $x(t)$ and $u(t)$, which are, in reality, continuous quantities, with finite precision in our model.
-We guarantee that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller and we use interval arithmetic to bound the errors, as detailed in Section~\ref{sec:}.
+The representations used in the plant model and its arithmetic operations are also carried out at a finite precision, 
+thus we must account for the corresponding errors.  
+\note{rephrase next:} Specifically, our model of the plant variables $x(t)$ and $u(t)$, which are, in reality, continuous quantities, with finite precision in our model. 
+We guarantee that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller and we use interval arithmetic to bound the errors, as detailed in Section~\ref{sec:} \note{fix?}.
 
 \subsection{Notation for fixed- and floating-point precision}
+
 In this paper we will use $\mathcal{F}_{\langle I,F \rangle}(x)$ to denote a real number $x$ expressed at a fixed-point precision, 
-using $I$ bits to represent the integer part of the number and $F$ bits to represent the decimal part.
-
+using $I$ bits to represent the integer part of the number and $F$ bits to represent its decimal part.  
 $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ denotes a real number $x$ represented at the fixed-point precision of the controller, 
@@
 in our model will be carried out in the range of $\mathcal{F}_{\langle
-I_p,F_p \rangle}$.  The physical plant operates in the reals, which means
-our verification phase must also account for the numerical error and
-quantization errors caused by representing the physical plant at the finite
+I_p,F_p \rangle}$.
+
+Notice that the physical plant model operates over real-valued signals, 
+which means that our verification phase must also account for the numerical error, 
+as well as quantization errors caused by representing the physical plant at finite 
 precision $\mathcal{F}_{\langle I_p,F_p \rangle}$.
 
-We use $\mathcal{F}_{\langle E,M \rangle}(x)$ to denote a real number $x$
-represented in a floating point domain, with $E$ bits representing the exponent
-part and $M$ bits representing the mantissa part. 
-In particular, we use $\mathcal{F}_{\langle E_c,M_c \rangle}(x)$ to denote a real number 
-represented at the floating-point precision of the controller, and 
-$\mathcal{F}_{\langle E_p,M_p \rangle}(x)$ to denote a real number 
-represented at the fixed-point precision of the plant model.
+We use $\mathcal{F}_{\langle E,M \rangle}(x)$ to denote a real number $x$ represented in a floating point domain, 
+with $E$ bits representing the exponent part and $M$ bits representing the mantissa part. 
+In particular, 
+we use $\mathcal{F}_{\langle E_c,M_c \rangle}(x)$ to denote a real number 
+represented at the floating-point precision of the controller, 
+whereas $\mathcal{F}_{\langle E_p,M_p \rangle}(x)$ denotes a real number represented at the fixed-point precision of the plant model.
 
@@
   DBLP:conf/asplos/Solar-LezamaTBSS06}, which is illustrated in Figure~\ref{fig:CEGIS}. 
-  CEGIS has been recently used for the automated synthesis of software programs, 
-  and its setup is naturally that of mathematical logic.
-
-We consider an input specification of the form 
+  CEGIS has been recently developed for the automated synthesis of software programs, 
+  and its setup is naturally that of mathematical logic. We consider an input specification of the form 
 $$
@@
 We~interpret the ground terms over some domain~$\mathcal{D}$. 
-This is a synthesis problem, where the objective is to synthesise a valid $P$ that satisfies $\phi$ over all the $a$ terms.
+This is a design problem, where the objective is to synthesise a valid $P$ that satisfies $\phi$ over all the $a$ terms.
 

### 2019-01-19 automatica/paper.tex
section 4

@@
 later in this work, we will target a less standard objective,
-namely a quantitative safety requirement, which opens up to more complex specifications \note{[belta, tabuada]}. 
+namely a quantitative safety requirement, which opens up to more complex specifications \cite{BYG16, Tab09}. 
 This is not typical in the digital control literature. We will further precisely account for the digital nature
@@
 \label{eq:safetyliteral}
-\phi_\mathit{safety}\iff \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
+\phi_\mathit{safety} = \left\{ \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}}\right\},
 \end{equation}
@@
 which we assume have given bounds:
-$\phi_\mathit{input} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} $, 
+$\phi_\mathit{input} = \{\forall k.\underline{u} \leq u_{k} \leq \overline{u}\} $, 
 \note{here you're assuming that u is 1-dim. This needs to be said somewhere. }
-and $\phi_\mathit{init} = \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}.$
+and $\phi_\mathit{init} = \{ \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}\}$. 
 The former constraint expresses that control input, possibly shaped via state-feedback, 
@@
 
-We use $\mathcal{F}_{\langle E,M \rangle}(x)$ to denote a real number $x$ represented in a floating point domain, 
+We further employ $\mathcal{F}_{\langle E,M \rangle}(x)$ to denote a real number $x$ represented in a floating point domain, 
 with $E$ bits representing the exponent part and $M$ bits representing the mantissa part. 
@@
 %While in the previous section we have discussed the generic CEGIS framework, 
-In the rest of the paper we explain how to adapt the generic CEGIS framework to the synthesis of digital controllers. 
-We start by describing the specific property that we pass to the synthesizer as the specification $\phi$. 
-Namely, we are interested in capturing safety, 
-which we discuss in Section~\ref{ssec:safespecification}. We use a stability specification 
-in order to narrow the search space of possible controllers, as detailed in Section~\ref{ssec:stabspecification}.
-
-%-------------------------------
-\subsection{Jury's stability criteria} 
+We are now equipped to apply the general CEGIS framework to the synthesis of digital controllers. 
+We start by describing the property that we pass to the synthesizer as the specification $\phi$. 
+Namely, as are interested in capturing safety (to be discussed in Section~\ref{ssec:safespecification}) \note{fix?},  
+we use a stability specification to narrow the search space of possible controllers, as detailed in Section~\ref{ssec:stabspecification}.
+
+%-------------------------------
+\subsection{Jury's stability criterion} 
 \label{ssec:stabspecification}
@@
 
-There are a number of procedures that can be used for stability analysis of dynamical models\note{~\cite{daes20161, Bessa16} is self-citation really the best citation for this statement??}.
+\note{reminder AA: check throughout use of 'model vs system'}
+
+There are a number of well known procedures to perform stability analysis of dynamical models~\cite{Astrom08}. 
 %which can fit our automatic verification engine.  
@@
 %and another one based on Jury's criterion~\cite{astrom1997computer}.  
-Here we choose Jury stability criterion~\cite{astrom1997computer}, 
+Here we select the Jury stability criterion~\cite{astrom1997computer}, 
 in view of its efficiency and ease of integration within our implementation.  
-This method checks the stability working in the complex domain of the characteristic polynomial $S(z)$,  
+This method checks the stability working in the complex domain of the characteristic polynomial $S(z)$ \note{could be better and formally introduced in earlier section?},  
 %
@@
 \end{equation*}
-An LTI system is stable if all the roots of its characteristic polynomial $S(z)$ (i.e., the 
-eigen values of the closed loop matrix $A_d-B_dK$) are inside the unit circle of the complex plane, 
-i.e., their absolute values are less than one.
+\note{clarify degree $N$ vs model dimensions} 
+An closed-loop LTI model is stable~\cite{astrom1997computer} \note{asymptotically?} if \note{make sure: only sufficient condition?}all the roots of its characteristic polynomial $S(z)$ (i.e., the 
+eigenvalues of the matrix $A_d-B_dK$) are inside the unit circle in the complex plane, 
+i.e., if their absolute values are less than one.
 
@@
 
-The stability property is finally encoded by a constraint expressed as the following formula: 
+The \note{asympt?} stability property is finally encoded by a constraint expressed as the following formula: 
 $
-\phi_\mathit{stability} := (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
+\phi_\mathit{stability} = \{R_1 \wedge R_2 \wedge R_3 \wedge R_4\}.
 $
@@
 As discussed in Section~\ref{sec:errors}, 
-the models we consider must account for errors from several sources: 
-we must bound the numerical error introduced by the finite precision we use to represent the plant (and its operations), and precisely model
-the error introduced by the ADC/DAC conversions
-and the behaviour of the limited precision arithmetic used by the controller. 
-We use interval arithmetic to bound the error introduced by the finite precision plant, and bounded model checking to precisely model the error introduced by the ADC/DAC and the finite precision controller.
+the considered models must account for errors deriving from several sources: 
+we must bound the numerical error introduced by the finite-precision representation of the plant (and its operations), 
+and precisely model the error introduced by the ADC/DAC conversions, 
+as well as the behaviour of the limited-precision arithmetic used by the controller. 
+We use interval arithmetic to bound the error introduced by the finite-precision plant, 
+and bounded model checking to precisely model the error introduced by the ADC/DAC and the finite-precision controller.
 
@@
 As described in section~\ref{sec:BMC}, we use CBMC, a bit-precise bounded model checker to synthesise and verify candidate controllers. 
-CBMC performs precisely the fixed or floating point arithmetic used in the controller, as well as the ADC/DAC conversions, according to the IEEE standards.
+CBMC manipulates precisely the fixed- or floating-point arithmetic used in the controller, 
+as well as the ADC/DAC conversions, 
+according to the IEEE standards.
 
 \subsection{Interval arithmetic over errors in numeric representation} 
-We use finite-precision arithmetic to model the plant. This is an approximation that speeds up each CEGIS
-iteration but necessitates a further stage where we verify that the errors introduced by the
-approximation have not caused us to generate a controller that is unsafe when executed with real numbers 
-for the plant. In this stage, we represent the plant using double precision floating point
+We use finite-precision arithmetic to model the plant. 
+This is an approximation that speeds up each CEGIS iteration, 
+however it necessitates a further stage where we verify that the errors introduced by the approximation have not resulted in a controller that is unsafe when executed on a plant expressed over real numbers.
+In this stage, we represent the plant using double-precision floating-point
 and we use the Boost interval arithmetic library~\cite{DBLP:journals/tcs/BronnimannMP06} to bound the error in this representation. 
-We use a compositional numeric library to model the fixed point arithmetic for the controller~\cite{} within
-double precision floating point numbers. We check the controller is safe starting from each vertex state, which we
-will show to be sufficient to prove safety from any initial state in the hypercube of possible initial states.
+We employ a compositional numeric library to model the fixed point arithmetic for the controller~\cite{} \note{fix} within double-precision floating-point numbers. 
+We check the controller is safe starting from each vertex of the set of initial states,  
+and show that this is sufficient to prove safety from any state in this set.
 

### 2019-01-19 automatica/paper.tex
section 5

@@
 
-We outline here the mathematics behind bounding the errors on the double precision floating point.
-Recall we use $\mathcal{F}_{\langle E,M \rangle}(x)$ denote a real number $x$
-represented in a floating point domain, with $E$ bits representing the exponent and $M$ bits representing the mantissa part. Any representation of a real number using the floating point domain will
-introduce an error, for which an upper bound can be given~\cite{DBLP:conf/arith/BrainTRW15}.
-For each number represented in floating point, we store an interval that encompasses this error.
-Further
-mathematical
-operations performed at the precision $\mathcal{F}_{\langle E,M \rangle}(x)$
-will propagate these errors forward and 
-introduce further errors for which bounds can be derived~\cite{DBLP:conf/arith/BrainTRW15}.
-
-The fixed point arithmetic of the digital controller is performed on the upper and lower limit of each interval independently. Since the precision of the floating point is greater than the precision
-of the controller, this is guaranteed to bound the real behaviour of the controller.
+We outline here the mathematics behind bounding the errors on the double-precision floating-point numbers. 
+Recall we use $\mathcal{F}_{\langle E,M \rangle}(x)$ denote a real number $x$ represented in a floating point domain, 
+with $E$ bits representing the exponent part, and $M$ bits representing the mantissa. 
+In general the representation of a real number using the floating-point domain introduces an error, 
+for which an upper bound can be given~\cite{DBLP:conf/arith/BrainTRW15}.
+For each number $x$ represented in the floating-point domain as $\mathcal{F}_{\langle E,M \rangle}(x)$, 
+we store an interval that encompasses this error. 
+Further mathematical operations performed at the precision $\mathcal{F}_{\langle E,M \rangle}(x)$ will propagate this error, 
+leading to further errors for which bounds can be derived~\cite{DBLP:conf/arith/BrainTRW15}.
+
+The fixed-point arithmetic of the digital controller is performed on the upper and lower limit of each interval independently \note{clarify what is meant by 'limit' and by 'each' (each amongst what?)} .
+Since the precision of the floating point domain is greater than the precision of the controller, this is guaranteed to bound the real behaviour of the controller.
 
@@
 
-\subsection{Effect on safety specification and stability}
+\subsection{Effect of precision arithmetic on safety specification and on stability}
 
 In this section we will quantify how the finite precision arithmetic in a digital controller affects the
-safety and stability properties of an LTI system
+safety and stability properties of an LTI model.
 
 \subsubsection{Safety of closed-loop models with finite precision controller error}
+
 Let us first consider the effect of the quantization errors on safety. 
 Within the controller, state values are manipulated at low precision,
-alongside the vector multiplication $Kx$.
-The inputs are computed using the following equation: 
+by means of the vector multiplication $Kx$.
+The inputs are thus computed using the following equation: 
 %
@@
 \end{align*}
-
-This induces two types of the errors detailed above: first, the truncation
-error due to representing $x_k$ as $\mathcal{F}_{\langle I_c,F_c
-\rangle}(x_{k})$; and second, the rounding error introduced by the
-multiplication operation. This error is behaviour modelled by the bounded model checking.
+This induces two types of the errors, 
+as detailed above: 
+first, the truncation error due to the representation of $x_k$ as $\mathcal{F}_{\langle I_c,F_c
+\rangle}(x_{k})$; and second, the rounding error introduced by the multiplication operation. 
+This error is modelled by the bounded model checking \note{clarify, elaborate (recall)}.
 
@@
 {\scriptsize
-\begin{equation}
+\begin{equation*}
 x_{k+1} =\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
-\end{equation}
+\end{equation*}
 }
-We address this error by use of interval
-arithmetic~\cite{moore1966interval} in the verification phase.
+We encompass this error using interval arithmetic~\cite{moore1966interval} in the verification phase \note{this statement might also need more details}.
 
@@
 \label{sec:stab_FWL}
-The proof of Jury's criterion~\cite{fadali} relies on the fact that the relationship between states and
-next states is defined by $x_{k+1} = (A_d - B_dK) x_k$, all computed
-at infinite precision.  When we employ a FWL digital controller, the
-operation becomes:
+The validity of Jury's criterion~\cite{fadali} relies on the representation of the closed-loop dynamics $x_{k+1} = (A_d - B_dK) x_k$ at infinite precision.  
+When we employ a FWL \note{did we define this acronym} digital controller, the operation above becomes:
 %
@@
 %
-where $\delta$ is the maximum error that can be introduced by the FWL
-controller in one step, i.e., by reading the states values once and
-multiplying by $K$ once.  We derive the closed form expression for $x_n$ as
-follows:
+where $\delta$ is the maximum error that can be introduced by the FWL controller in one step, 
+i.e., by reading the states values once and multiplying by $K$ once.  
+We derive the closed form expression for $x_n$ recursively, as follows:
 %
@@
 \normalsize
-The definition of asymptotic stability is that the system converges to a
-reference signal, in this case we use no reference signal so an
-asymptotically stable system will converge to the origin.  We know that the
-original system with an infinite-precision controller is stable, because we
-have synthesized it to meet Jury's criterion.  Hence, $(A_d - B_dK)^n x_0$ 
-must converge to zero.
-
+%The definition of asymptotic stability is that the system converges to a
+%reference signal, in this case we use no reference signal so 
+Recall that a closed-loop asymptotically stable system will converge to the origin.  
+We know that the original system with an infinite-precision controller is stable, 
+because we have synthesized it to meet Jury's criterion.  
+Hence, $(A_d - B_dK)^n x_0$  must converge to zero as $n \uparrow \infty$. 
 %T%o show that a fixed-point implementation of the same controller will
 %converge to a finite value, we need to show that the infinite sum converges. 
-The power series of matrices
-converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less
-than~1 as follows:
+Furthermore, the power series of a square matrix $T$ converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less
+than~1, and the limit results in 
 %
@@
 %
-where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge to the value 
+where $I$ is the identity matrix. 
+Thus, the closed-loop model converges to the value 
 %
@@
 %
-As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the
-safe space, then the synthesized fixed-point controller results in a safe
+As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the safe space \note{qualitative statement - is this a scalar or a vector, and what is the `safe space'? you mean safe set?}, 
+then the synthesized fixed-point controller results in a safe
 closed-loop model.  The convergence to a finite value, however, will not

### 2019-01-19 automatica/paper.tex
section 6

@@
 When we employ a FWL \note{did we define this acronym} digital controller, the operation above becomes: 
+\note{the first of the two equations is not clear}
 %
@@
 \else
-the instantiation of CEGIS we use to synthesise safe digital controllers, accounting for the precision issues detailed in previous sections. We use a multi-stage approach
-that unwinds the dynamics up to a completeness threshold, modelling finite-precision arithmetic using bit-precise bounded model checking, and then verifying soundness of the resulting controller using interval arithmetic.
+the CEGIS procedure that is used to synthesise safe digital controllers, 
+accounting for the precision issues detailed in the previous sections. 
+We employ a multi-stage approach that unwinds the dynamics of the model up to a completeness threshold, 
+modelling finite-precision arithmetic using bit-precise bounded model checking, 
+and then verifying soundness of the resulting controller using interval arithmetic. 
 \fi
@@
 \end{tikzpicture}
-\caption{CEGIS with multi-staged verification}
+\caption{CEGIS with multi-staged verification for digital controller synthesis}
 \label{fig:CEGIS-precision-increment}
@@
 \item The inductive synthesis phase ({\sc synthesize}) uses BMC to compute a
-candidate solution $K$ that satisfies both the stability criteria and the
-safety specification.
-
-To synthesize a controller that satisfies the 
-stability criteria, we require that a computed polynomial satisfies Jury's
-criterion~\cite{fadali} (see Section~\ref{ssec:stabspecification}).
+candidate solution $K$ that satisfies both the stability requirement and \note{next: already at this stage?} the safety specification.  
+In order to synthesize a controller that satisfies the stability requirement, 
+we need the computed characteristic polynomial to satisfy Jury's criterion~\cite{fadali} (see Section~\ref{ssec:stabspecification}).
 
@@
 This approach is sound if the current $k$ is greater than the completeness threshold (see later step).  
-We~also assume some (fixed or floating point) precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  
-The checks that these assumptions hold are performed by subsequent {\sc verify} stages.
+We~also assume some (fixed or floating point \note{both?}) precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  
+The checks that these assumptions hold are performed by the subsequent {\sc verify} stages.
 
@@
 \end{algorithmic}
-\caption{Safety check\label{alg:safetycheck}}
+\caption{Safety check ({\sc safety} stage in Fig.~\ref{fig:CEGIS-precision-increment})\label{alg:safetycheck}}
 \end{algorithm}
@@
 The algorithm checks that the candidate
-solution $K$, which we synthesized to be safe for at least one initial
-state, is safe for \emph{all} possible initial states, i.e., does not reach
-an unsafe state within $k$ steps.  After unfolding the transition system corresponding
+solution $K$, which we have synthesized to be safe for at least one initial
+state, is safe for \emph{all} possible initial states, i.e., it does not reach
+the (complement) unsafe state within $k$ steps.  After unfolding the transition system corresponding
 to the previously synthesized controller $k$ steps, we check that the safety
@@
 bound of the initial states. It is sufficient to verify that the controller is safe for all vertex
-states, and the proof is shown later in this section. We thus only need to iterate through the $2^{Num\_States}$ vertex
+states, and the proof is shown later in this section. We thus only need to iterate through the $2^{Num\_States}$ \note{new quantity, different than n?} vertex
 states, where $n$ is dimension of the state space (number of continuous variables).
@@
 \end{theorem}
-
-Thus we only need to check $2^n$ initial states, where $n$
-is the dimension of the state space, as before. 
 \begin{proof}
@@
 \begin{align*}
-x_k   &= (A_d - B_d K)^k x \\
-&= (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i \\
-      &= \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i \\
-      &= \sum_{i=1}^{2^n} \alpha_i x_k^i, 
+x_k   &= (A_d - B_d K)^k x = (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i \\
+      &= \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i = \sum_{i=1}^{2^n} \alpha_i x_k^i, 
  \end{align*}     
@@
 \end{proof}
+In conclusion, we only need to check $2^n$ initial states, 
+where $n$ is the dimension of the state space.
 
@@
 \item The third {\sc verify} stage, {\sc complete}, checks that the current
-$k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
-completeness threshold $\overline{k}$ for the current candidate controller $K$ and
+$k$ is large enough to ensure safety for any further time steps.  
+Here, we compute the completeness threshold $\overline{k}$ for the current candidate controller $K$ and
 check that $k{\geq}\overline{k}$.  This is done by computing the number of time steps
@@
 %\vspace{0.1cm}
-\caption{Completeness threshold for multi-staged verification. $T_s$ is the time step for the time discretization of the control matrices.}
+\caption{Completeness threshold for multi-staged verification (quantity $T_s$ is the time discretization step) }
 \label{fig:ct}

### 2019-01-20 automatica/paper.tex
section 7

@@
 
-The proposed synthesis methodology for closed-loop digital control
-systems is based on the Digital-System Synthesizer 
+The implementation of the proposed methodology for synthesis of digital controls for physical plants is based on the Digital-System Synthesizer 
 (DSSynth) tool~\cite{DBLP:conf/kbse/AbateBCCCDKKP17}, 
-which can be split into two main stages as follows: manual and 
-automated steps, as illustrated in Fig.~\ref{fig:synthesis-flow}.
-
-In Step~1, the user selects the closed-loop digital control
-system representation, which can be a transfer function or a state-space model.  
-In Step~2, the physical plant (e.g., in the form of Equation~\eqref{eq:ode1}) must be
-given~\cite{astrom1997computer}.  Finally, in Step~3, the numerical
-representation for the digital controller implementation must be set by the
-user, i.e., the FWL format that defines the number of bits of the integer
-and fractional parts when using fixed-point arithmetic or half- and single-precision 
-when using floating-point arithmetic as well as the dynamic range inputs.  The input 
-provided by the user is a specification of the physical plant.
-
-After that, the automated synthesis process starts with Step~A, where the
-\tool~translates the digital system specification into an ANSI-C program.  
-In Step~B, our CEGIS engine is invoked to
-synthesize the digital controller w.r.t.~the digital system specification. 
-Finally, in Step~C, the synthesized digital controller is produced.  The
-output generated by the \tool~is the synthesized digital controller
-represented either in transfer function or state-space equation.  The
-synthesis is considered to be \emph{successful} if a digital controller is
-correctly synthesized w.r.t.~FWL effects; otherwise, if any parameter is
-incorrectly defined in previous steps, or if there is no solution (no
-controller) for the respective physical plant (given the implementation
+which can be split into two main stages: manual and automated, as illustrated in Fig.~\ref{fig:synthesis-flow} and detailed next.
+
+In Step~1, the user selects the system representation, which can be a transfer function or a state-space model.  
+In Step~2, the physical plant (e.g., in the form of Equation~\eqref{eq:ode1}) is provided~\cite{astrom1997computer}.  
+Finally, in Step~3, the numerical representation for the digital controller implementation must be set by the user, i.e., 
+the FWL format that defines the number of bits of integer and fractional parts when using fixed-point arithmetic, 
+or half- and single-precision when using floating-point arithmetic, 
+as well as the input range.  
+% This input, provided by the user, is a specification of the physical plant.
+
+In the second stage, 
+the automated synthesis process starts with Step~A, where the
+\tool~translates the model specification into an ANSI-C program.  
+In Step~B, the proposed CEGIS engine is invoked to synthesize the digital controller w.r.t.~the specification on the digital model.  
+Finally, in Step~C, the synthesized digital controller is generated.  
+The output by \tool~is the synthesized digital controller represented either as a transfer function or in state-space form.  
+The synthesis is considered to be \emph{successful} if a digital controller is
+correctly synthesized w.r.t.~FWL effects; otherwise, \note{needed next?}if any parameter is
+incorrectly defined in previous steps, \note{next OK;} or if there is no solution (no
+controller) for the corresponding physical plant (given the implementation
 requirements), then the synthesis is considered to have \emph{failed}.
@@
 model checker (CBMC)~\cite{ClarkeKL04}.  CBMC transforms the ANSI-C representation
-of our closed-loop control system model into its internal representation (IR).  We
+of the closed-loop control model model into its internal representation (IR).  We
 instrument this IR for each synthesis or verification scenario accordingly,
 and use CBMC as an oracle to answer our queries.  CBMC itself relies on an
-underlying SAT or SMT solver to solve verification conditions.  We~model FWL
-effects, time discretization and the presence of quantization noise
+underlying SAT or SMT solver to address verification conditions.  We~model FWL
+effects, time discretization \note{keep time-d?}, and the presence of quantization noise
 explicitly using CBMC's nondeterminism API (e.g., \texttt{nondet},
@@
 including our MATLAB-generated benchmarks and benchmark shell script with
-instructions to run all benchmarks and reproduce our
+instructions to run all benchmarks and to reproduce our
 experiments.\footnote{\note{\url{XXXXXXXXXX}}}

### 2019-01-20 automatica/paper.tex
section 8

@@
 controller) for the corresponding physical plant (given the implementation
-requirements), then the synthesis is considered to have \emph{failed}.
+requirements), then the synthesis is considered to have \emph{failed} \note{we don't seem to have any such instance.}.
 
@@
 
-Our benchmark suite consists of 20 SISO models extracted from the 
+Our benchmark suite consists of \note{update} 20 SISO models extracted from the 
 control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal}.
 The models are discretized with sampling times ranging from 1.5s to 0.005s, and if CEGIS is unable to 
-synthesise a controller for a given sampling time, CEGIS heuristically selects a new sampling time.
+synthesise a controller for a given sampling time, CEGIS heuristically selects a new sampling time \note{do we, still?}.
 
@@
 
-\item[EG1] \textbf{(Performance)} Show that both the multi-staged and the abstraction-based
-CEGIS approaches are able to generate FWL digital controllers using floating-point arithmetic 
-in a reasonable amount of time.
-
-\item[EG2] \textbf{(Sanity check)} Confirm the stability and safety of the synthesized controllers outside 
+\item[EG1] \textbf{(Performance)} Show that the multi-staged 
+%and the abstraction-based 
+CEGIS approach is able to generate FWL digital controllers using floating-point arithmetic in a reasonable amount of time.
+
+\item[EG2] \textbf{(Sanity check)} Confirm the stability \note{also?} and safety of the synthesized controllers outside 
 of our model representation using MATLAB. 
@@
 
-We provide the results in Table~\ref{tab:results}, 
-where \textit{Benchmark} is the name of the respective benchmark; 
-\textit{Order} is the number of continuous variables of the model; \textcolor{blue}{ 
-$\mathcal{F}_{\langle I_p,F_p \rangle}$, where $I_p$ and $F_p$ indicate the integer and fractional parts,  
+We provide the results in Table~\ref{tab:results}, where: 
+\textit{Benchmark} is the name of the corresponding benchmark; 
+\textit{Order} is the number of continuous variables of the model; 
+\textcolor{blue}{$\mathcal{F}_{\langle I_p,F_p \rangle}$, where $I_p$ and $F_p$ indicate the integer and fractional parts,  
 and \textcolor{blue}{ $\mathcal{F}_{\langle W_p,F_p \rangle}$}, where $W_p$ and $F_p$ indicate the total word-length and fractional part, 
@@
 and \textit{Time} is the total time required to synthesize a controller for the given plant.    
-Timeouts are indicated by~\xmark, while failures to synthesise the digital controllers are indicated by $\dagger$.  
+Timeouts are indicated by~\xmark, while failures to synthesise the digital controllers are indicated by $\dagger$ \note{no such instances}.  
 The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
@@
 floating point controllers are at a higher precision than the fixed point. It may be that the precision of the fixed-point
-controllers is too low to be able to meet the safety specification. The floating point controllers take longer to synthesise
-than the fixed point controllers.
+controllers is too low to be able to meet the safety specification. The floating point controllers in general take longer to synthesise
+than the fixed point controllers \note{there is one surprising exception - check please}.
 %For the majority of the {\it fixed-point} benchmarks, we observe that the abstraction-based
@@
 
-The mean run-time for \textcolor{blue}{the successful} benchmarks is 152.6\,s for the fixed-point and 117.5\,s for floating-point implementations, respectively.
-The mean run-time for \textcolor{blue}{the successful} benchmarks is 16\,s for the fixed-point and 11\,s for floating-point implementations, respectively.
-We consider these times short enough to be of practical use to control engineers, and thus affirm the validity of EG1.
+The mean run-time for \textcolor{blue}{the successful} benchmarks is 152.6\,s for fixed-point and 117.5\,s for floating-point implementations, respectively.  
+\note{unclear repeat next:} The mean run-time for \textcolor{blue}{the successful} benchmarks is 16\,s for fixed-point and 11\,s for floating-point implementations, respectively.
+We consider these times to be short enough to be of practical use to control engineers, and thus affirm the validity of EG1.
 
 \textcolor{blue}{We fail to synthesise a controller for several instances.}  
-The completeness threshold may be too large, thus causing a timeout, or controller simply may not exist for these benchmarks at this given time discretisation and controller
-precision.
-Yet another source of incompleteness is the inability of the {\sc synthesize} phase to use a large enough precision for
-the plant model.
+The completeness threshold may be too large, thus causing a timeout \note{but timeouts are handled separately than failures?}, 
+or a controller simply may not exist for a benchmark at a given time discretisation and required controller precision. 
+Yet another source of incompleteness is the inability of the {\sc synthesize} phase to use a large enough precision for the plant model.
 
 \textcolor{blue}{The synthesized controllers are confirmed to be safe outside of our model
-representation using MATLAB, achieving EG2.  A~link to the full
-experimental environment, including scripts to reproduce the results, all
+representation using MATLAB, achieving EG2 \note{please explain how this check is performed - is the check itself sound?}.  
+A~link to the full experimental environment, including scripts to reproduce the results, all
 benchmarks and the tool, is provided in the
@@
 %-------------------------------
-\subsection{Threats to validity}
+\subsection{Threats to validity \note{generality?}}
 \label{exp:threats-to-validity}
@@
 %
-Our approach is novel within the control literature: we give a fully
+Our approach is novel within the digital control literature: we provide a fully
 automated synthesis method that is algorithmically and numerically sound,
@@
 Our experimental results show we are able to synthesize fully automatically 
-safe controllers for most benchmarks, which have been derived from the control literature, 
+safe controllers for diverse benchmarks from the control literature, 
 within a reasonable amount of time.

### 2019-01-20 automatica/paper.tex
section 8

@@
 describes the dynamics of the azimuth angle of an antenna 
-motion system composed by a gearbox, a DC motor and amplifiers~\cite{gajic2008optimal}. 
+motion system composed by a gearbox, a DC motor and amplifiers~\cite{gajic2008optimal}. \\
 %The \textit{ballmaglev}  plant corresponds to the model of a simple 
@@
 %identified by least squares 
-of the cell mass concentration controlled through the dilution rate of a bioreactor~\cite{bioreactor}.
-
+of the cell mass concentration controlled through the dilution rate of a bioreactor~\cite{bioreactor}.\\ 
+%
 The \textit{Chen\_ex1} and \textit{Chen\_ex3}
-benchmarks correspond to high-order control system 
+benchmarks correspond to higher-order control system 
 %discrete 
-models employed as case studies for model-order reduction techniques~\cite{CHEN1979389}. 
-The benchmarks \textit{Cruise}~\cite{Franklin15} and \textit{CruiseHSCC}~\cite{Astrom08} deal with 
-automotive cruise control models, where control is used to keep 
-constant the speed of an automobile, tracking a desired speed reference, and compensating disturbances and uncertainties. % related to relief and terrain.
-
+models employed as case studies for model-order reduction techniques~\cite{CHEN1979389}.  \\
+%
+The benchmarks \textit{Cruise}~\cite{Franklin15} and \textit{CruiseHSCC}~\cite{Astrom08} deal with automotive cruise control models, 
+where the control is used to maintain the speed of an automobile constant, 
+tracking a desired speed reference, and compensating disturbances and uncertainties. \\ % related to relief and terrain. 
 %There are two continuous stirred tank reactor models named 
-\textit{cstr}  and \textit{cstrtmp}  describe the PH dynamics of a reaction 
+\textit{cstr}  and \textit{cstrtmp}  describe the pH dynamics of a reaction 
 of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
@@
 %continuous flow stirred-
-tank reactor. The \textit{DC motor} plant  describes the velocity 
+tank reactor. \\ 
+The \textit{DC motor} plant  describes the velocity 
 dynamics of a 
 %basic brushed 
-direct-current electrical machine.
-
+direct-current electrical machine. \\ 
+%
 %The \textit{Flexbeam} benchmark  is 
@@
 model-order reduction techniques; it models a guidance control system, 
-which is used to determine the path of an autonomous vehicle. 
+which is used to determine the path of an autonomous vehicle \note{This is similar to the two benchmarks above?}. \\ 
 The \textit{helicopter} benchmark plant  describes the transitional and rotational dynamics 
 %of transitional motion with respect to a longitudinal plane and the rotational motion around the longitudinal axis for 
-of a coaxial helicopter.
-
+of a coaxial helicopter. \\ 
+%
 %\textit{Invpendulum\_cartpos}  and 
@@
 %plant composed by a point mass, which must be equilibrated above the pivot point and is mounted on an one degree of freedom cart that 
-which moves over a track through a DC motor.
-
+which moves over a track through a DC motor. \\ 
+%
 The \textit{magpointer}  describes a magnetic pointer, 
 % plant composed by a pointer employed in analogue gauges and indicators, 
-whose angular position dynamics is controlled by a magnetic field. 
-The \textit{magsuspension} describes  the dynamic of a magnetic car suspension system. 
-The \textit{pendulum}  plant consists of a swinging point mass suspended from a frictionless pivot by means of a rod with negligible mass.
-
+whose angular position dynamics is controlled by a magnetic field. \\ 
+%
+The \textit{magsuspension} describes  the dynamic of a magnetic car suspension system. \\
+The \textit{pendulum}  plant consists of a swinging point mass suspended from a frictionless pivot by means of a rod with negligible mass.  \\ 
+%
 The \textit{Regulator} consists of a linear model of a synchronous electrical machine% connected to an infinite bus
-~\cite{KOKOTOVIC198023}. 
-The \textit{springer-mass damper system} plant is a standard model for the dynamics of several mechanical systems. 
+~\cite{KOKOTOVIC198023}. \\
+The \textit{springer-mass damper system} plant is a standard model for the dynamics of several mechanical systems. \\ 
 %This benchmark describes a mass, which is fixed to a node by means of a springer and moves under the action of an input force, damping, and elastic force.
-The \textit{steam drum} benchmark describes a linear model for the level dynamics of a boiler steam drum~\cite{boiler}.
-
-The \textit{suspension} models a single-wheel suspension system of a car, 
-namely the relative motion dynamics of a mass springer damp model, which connects the car to one of its wheels.  
+The \textit{steam drum} benchmark describes a linear model for the level dynamics of a boiler steam drum~\cite{boiler}. \\ 
+%
+The \textit{suspension} models the single-wheel suspension system of a car, 
+namely the relative motion dynamics of a mass-spring-damper model, which connects the car to one of its wheels.  \\
 The \textit{tapedriver} benchmark models a computer tape driver, 
@@
 \vspace{0.05in}
-\caption{Experimental results\label{tab:results}}
+\caption{Experimental results \note{expand description (short, crisp)}\label{tab:results}}
 \end{table*}

### 2019-01-21 automatica/paper.tex
response
Newer CBMC ref

@@
 
-\note{Ref to Fig. \ref{fig:digitalsystem} anywhere?}
+\note{Ref to Fig. \ref{fig:digitalsystem} anywhere?. That figure is referred to in the section on errors. I think it is confusing to
+refer to it before we have explained the DAC, ADC and the errors shown in the figure.}
 
@@
 
-We employ the bounded model checker CBMC~\cite{ClarkeKL04} \note{newer reference?} to model the controller behavior on digital signals with finite bit-precision.  
+We employ the bounded model checker CBMC~\cite{DBLP:conf/tacas/KroeningT14} to model the controller behavior on digital signals with finite bit-precision.  
 We express the controller semantics as C programs, which is CBMC's preferable input language.  

### 2019-01-21 automatica/paper.tex
align dimensions

@@
 where 
-$\vec{x} \in \mathbb{R}^p$,  
-$\vec{u} \in \mathbb{R}^q$, 
-$\mat{A} \in \mathbb{R}^{p \times p}$, 
-$\mat{B} \in \mathbb{R}^{p \times q}$,
+$\vec{x} \in \mathbb{R}^n$,  
+$\vec{u} \in \mathbb{R}^p$, 
+$\mat{A} \in \mathbb{R}^{n \times n}$, 
+$\mat{B} \in \mathbb{R}^{n \times p}$,
 and $t \in \mathbb R_0^+$ denotes continuous time. 
@@
 where $u_k$ (notice we work with the discretized signal) is $u_k = r_{k} - K x_k$. 
-Here $K \in \mathbb{R}^{m \times n}$ \note{wrong dimensions?} is a state-feedback gain matrix, 
+Here $K \in \mathbb{R}^{p \times n}$ is a state-feedback gain matrix, 
 and $r_{k}$ is a reference signal (again digital). 
@@
 In this work we employ the notion of asymptotic stability within the CEGIS loop,  
-as a means for reducing the search space of possible safe controllers. 
-\note{next statement is not true - also, we have not defined safety} 
-As discussed later, a safe controller is necessarily asymptotically stable, although the reverse is not true. 
+as a means for reducing the search space of possible safe controllers, where the definition of a safe controller
+is defined in the following section. 
+As discussed later, for linear systems a safe controller is necessarily asymptotically stable, 
+although the reverse is not true. 
 %as an objective for guessing controllers that are later proven sound over safety requirements.  
@@
 for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ 
-\note{Fix/align dimensions of main model} 
 at the $k$-th instant, respectively.  This requires that the states will always be within an $n$-dimensional hyper-box.
@@
 which we assume have given bounds:
-$\phi_\mathit{input} = \{\forall k.\underline{u} \leq u_{k} \leq \overline{u}\} $, 
-\note{here you're assuming that u is 1-dim. This needs to be said somewhere. }
+$\phi_\mathit{input} = \{\forall k \geq 0.\bigwedge_{i=1}^{p} \underline{u} \leq u_{i} \leq \overline{u}\} $,
 and $\phi_\mathit{init} = \{ \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}\}$. 

### 2019-01-21 automatica/paper.tex
merge sentence

@@
 We express the controller semantics as C programs, which is CBMC's preferable input language.  
-CBMC symbolically executes every instruction in an input program by translating it to a boolean satisfiability problem \note{merge this sentence with next?}.  
-At the end of this process, the entire input program is translated to a boolean satisfiability formula which is satisfiable iff a certain property about the program holds.  
+CBMC symbolically executes every instruction in an input program by translating it to a boolean satisfiability problem,
+ which is satisfiable iff a certain property about the program holds.  
 CBMC's API allows to specify these properties in the form of assertions in the input program: 

### 2019-01-21 automatica/paper.tex
ref

@@
 Finite-precision arithmetic introduces errors, as shown in Figure~\ref{fig:digitalsystem}. 
-Details of how we model this arithmetic are in Section~\ref{sec:} \note{fix?}. 
+Details of how we model this arithmetic are in Section~\ref{sec:numeric_rep}. 
 These errors are present in the real world, and we must model them accurately in order to capture the full behaviour of the model:
@@
 \note{rephrase next:} Specifically, our model of the plant variables $x(t)$ and $u(t)$, which are, in reality, continuous quantities, with finite precision in our model. 
-We guarantee that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller and we use interval arithmetic to bound the errors, as detailed in Section~\ref{sec:} \note{fix?}.
+We guarantee that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller and we use interval arithmetic to bound the errors, as detailed in Section~\ref{sec:numeric_rep}.
 

### 2019-01-21 automatica/paper.tex
remove noise from diagram

@@
       \node[rectangle,dashed,draw,minimum width=3cm,minimum height=1.6cm,label=\textbf{DAC}] (dac) {};
-     \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
-     \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
-     \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
-     \node[fill=gray!20] (zoh) at ([xshift=.65cm]dac.center) {\sc ZOH};
+   %  \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
+   %  \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
+   %  \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
+     \node[fill=gray!20] (zoh) at ([xshift=.0cm]dac.center) {\sc ZOH};
    }
@@
      \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
-     \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
-     \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
-     \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
-     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]q1)  {$\vec{x}_k$};       
-     \coordinate (ykeast) at ([xshift=1.9cm]q1);
-     \coordinate (yksouth) at ([xshift=1.9cm,yshift=-3.5cm]q1);
+   %  \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
+   %  \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
+   %  \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
+     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]switch2)  {$\vec{x}_k$};       
+     \coordinate (ykeast) at ([xshift=2.9cm]switch2);
+     \coordinate (yksouth) at ([xshift=2.9cm,yshift=-3.5cm]switch2);
    } 
@@
 
-  \path[->] (v1) edge (q1.south);
-  \path[->] (v2) edge (q2.south);
+%  \path[->] (v1) edge (q1.south);
+%  \path[->] (v2) edge (q2.south);
   \path[->] (r) edge (circle.west);
-  \path[->] (circle.east) edge (q2.west);
-  \path       (q2.east) edge (zoh.west);
+  \path[->] (circle.east) edge (zoh.west);
+%  \path       (q2.east) edge (zoh.west);
   \path[->] (zoh.east) edge (B.west);
@@
    (int.east) edge (switch1.west)
-   (switch2) edge (q1.west);
+   (switch2) edge (ykeast);
   \path
-   (q1.east) edge (ykeast)
+ %  (q1.east) edge (ykeast)
    (ykeast) edge (yksouth)

### 2019-01-21 automatica/paper.tex
tweaks

@@
 and we use the Boost interval arithmetic library~\cite{DBLP:journals/tcs/BronnimannMP06} to bound the error in this representation. 
-We employ a compositional numeric library to model the fixed point arithmetic for the controller~\cite{} \note{fix} within double-precision floating-point numbers. 
+We employ a compositional numeric library to model the fixed point arithmetic for the controller~\cite{CNL} within double-precision floating-point numbers. 
 We check the controller is safe starting from each vertex of the set of initial states,  
@@
 
-The fixed-point arithmetic of the digital controller is performed on the upper and lower limit of each interval independently \note{clarify what is meant by 'limit' and by 'each' (each amongst what?)} .
+The fixed-point arithmetic of the digital controller is performed on the upper and lower bound of each interval independently and the upper and lower bound of the result taken as the interval result\note{clarify what is meant by 'limit' and by 'each' (each amongst what?)}.
 Since the precision of the floating point domain is greater than the precision of the controller, this is guaranteed to bound the real behaviour of the controller.
@@
 \rangle}(x_{k})$; and second, the rounding error introduced by the multiplication operation. 
-This error is modelled by the bounded model checking \note{clarify, elaborate (recall)}.
+Recall this error is modelled precisely by bounded model checking.
 
@@
 The validity of Jury's criterion~\cite{fadali} relies on the representation of the closed-loop dynamics $x_{k+1} = (A_d - B_dK) x_k$ at infinite precision.  
-When we employ a FWL \note{did we define this acronym} digital controller, the operation above becomes: 
+When we employ a fixed-point arithmetic digital controller, the operation above can be expressed as follows, where we use $\mathcal{F}_{\langle I_c,F_c \rangle}$ preceding a variable to indicate that variable is converted into the fixed-point precision given by $\mathcal{F}_{\langle I_c,F_c \rangle}$:
 \note{the first of the two equations is not clear}
@@
 %
-where $\delta$ is the maximum error that can be introduced by the FWL controller in one step, 
+where $\delta$ is the maximum error that can be introduced by the digital controller in one step, 
 i.e., by reading the states values once and multiplying by $K$ once.  
@@
 %
-As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the safe space \note{qualitative statement - is this a scalar or a vector, and what is the `safe space'? you mean safe set?}, 
+As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the safe set of states given by the safety specification
 then the synthesized fixed-point controller results in a safe
@@
 
+A similar argument can be made for floating-point arithmetic.
 We can thus disregard these steady-state errors (caused by
-FWL effects) when stability is ensured by synthesis, and then verify its
+finite-precision arithmetic) when stability is ensured by synthesis, and then verify its
 safety accounting for the finite-precision errors.
@@
 \item The inductive synthesis phase ({\sc synthesize}) uses BMC to compute a
-candidate solution $K$ that satisfies both the stability requirement and \note{next: already at this stage?} the safety specification.  
+candidate solution $K$ that satisfies both the stability requirement and the safety specification, 
+within a finite precision model.  
 In order to synthesize a controller that satisfies the stability requirement, 
@@
 This approach is sound if the current $k$ is greater than the completeness threshold (see later step).  
-We~also assume some (fixed or floating point \note{both?}) precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  
+We~also assume some finite precision for the plant and a sampling rate.
+We use a fixed-point precision in this description, given by $\langle I_p,F_p\rangle$, but if we are considering a floating-point controller we will instead model the plant with a floating-point precision, $\langle E_p,M_p\rangle$.
 The checks that these assumptions hold are performed by the subsequent {\sc verify} stages.
@@
 bound of the initial states. It is sufficient to verify that the controller is safe for all vertex
-states, and the proof is shown later in this section. We thus only need to iterate through the $2^{Num\_States}$ \note{new quantity, different than n?} vertex
+states, and the proof is shown later in this section. We thus only need to iterate through the $2^{n}$ vertex
 states, where $n$ is dimension of the state space (number of continuous variables).

### 2019-01-22 automatica/paper.tex
sections

@@
 is defined in the following section. 
-As discussed later, for linear systems a safe controller is necessarily asymptotically stable, 
+As discussed later, specifically for linear models a safe controller is necessarily asymptotically stable, 
 although the reverse is not true. 
@@
 Of interest for this work, 
-it can be shown that a discrete-time LTI system %as \eqref{eq:closedloopss} 
+it can be shown that a discrete-time LTI model %as \eqref{eq:closedloopss} 
 is asymptotically stable if all the roots of its characteristic polynomial (i.e., the
@@
 Details of how we model this arithmetic are in Section~\ref{sec:numeric_rep}. 
-These errors are present in the real world, and we must model them accurately in order to capture the full behaviour of the model:
+\note{[rephrase?] These errors are present in the real world}, and we must model them accurately in order to capture the full behaviour of the model:
 
@@
 However, we assume that the DAC converts numbers to analog signals with the same precision as the controller. 
+Again, this assumption is practically reasonable. 
 As a result we can ignore any additional errors introduced by the DAC. 
-Again, this assumption is practically reasonable. 
 It would, however, be straightforward to account for a DAC or ADC of different precision to the controller in our algorithm, if necessary. 
@@
 
+\note{[shouldn't this be a bullet point too?]}
 The representations used in the plant model and its arithmetic operations are also carried out at a finite precision, 
 thus we must account for the corresponding errors.  
-\note{rephrase next:} Specifically, our model of the plant variables $x(t)$ and $u(t)$, which are, in reality, continuous quantities, with finite precision in our model. 
-We guarantee that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller and we use interval arithmetic to bound the errors, as detailed in Section~\ref{sec:numeric_rep}.
+\note{rephrase next - main clause has no verb:} Specifically, our model of the plant variables $x(t)$ and $u(t)$, which are, in reality, continuous quantities, with finite precision in our model. 
+We \note{guarantee [?]} that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller and we use interval arithmetic to bound the errors, as detailed in Section~\ref{sec:numeric_rep}.
 
@@
 using $I$ bits to represent the integer part of the number and $F$ bits to represent its decimal part.  
-$\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ denotes a real number $x$ represented at the fixed-point precision of the controller, 
+In particular, $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ denotes a real number $x$ represented at the fixed-point precision of the controller, 
 and $\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ denotes a real number $x$
@@
 We start by describing the property that we pass to the synthesizer as the specification $\phi$. 
-Namely, as are interested in capturing safety (to be discussed in Section~\ref{ssec:safespecification}) \note{fix?},  
+Namely, as we are interested in capturing safety (to be discussed in Section~\ref{ssec:safespecification}\note{fix?}),  
 we use a stability specification to narrow the search space of possible controllers, as detailed in Section~\ref{ssec:stabspecification}.
@@
 as well as the behaviour of the limited-precision arithmetic used by the controller.
-We use interval arithmetic to bound the error introduced by the finite-precision plant, 
+
+We employ interval arithmetic to bound the error introduced by the finite-precision plant, 
 and bounded model checking to precisely model the error introduced by the ADC/DAC and the finite-precision controller.
@@
 We employ a compositional numeric library to model the fixed point arithmetic for the controller~\cite{CNL} within double-precision floating-point numbers. 
-We check the controller is safe starting from each vertex of the set of initial states,  
+We check that the controller is safe starting from each vertex of the set of initial states,  
 and show that this is sufficient to prove safety from any state in this set.
@@
 \end{align*}
-This induces two types of the errors, 
+This induces two types of errors, 
 as detailed above: 
@@
 When we employ a fixed-point arithmetic digital controller, the operation above can be expressed as follows, where we use $\mathcal{F}_{\langle I_c,F_c \rangle}$ preceding a variable to indicate that variable is converted into the fixed-point precision given by $\mathcal{F}_{\langle I_c,F_c \rangle}$:
-\note{the first of the two equations is not clear}
+\note{the first of the two equations is not clear - don't you miss a B matrix?}
 %
@@
 since in this paper we require stability only as a precursor to safety, it
-is sufficient to check that the (perturbed, noisy) model converges to a
+is sufficient to check that the perturbed model converges to a
 neighborhood of the equilibrium within the safe set.

### 2019-01-23 automatica/paper.tex
fixes

@@
 
-\note{[shouldn't this be a bullet point too?]}
+\note{[shouldn't this be a bullet point too?] It can't be in the previous list though because ti isn't an error introduced by the nature of digital control and that we need to model, it is an error introduced *by* our modelling}
 The representations used in the plant model and its arithmetic operations are also carried out at a finite precision, 
 thus we must account for the corresponding errors.  
-\note{rephrase next - main clause has no verb:} Specifically, our model of the plant variables $x(t)$ and $u(t)$, which are, in reality, continuous quantities, with finite precision in our model. 
-We \note{guarantee [?]} that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller and we use interval arithmetic to bound the errors, as detailed in Section~\ref{sec:numeric_rep}.
+Specifically, we must account for the error introduced by our model using finite-precision arithmetic for the plant variables $x(t)$ and $u(t)$, which are, in reality, continuous quantities. 
+We guarantee that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller and we use interval arithmetic to bound the errors, as detailed in Section~\ref{sec:numeric_rep}.
 

### 2019-01-23 automatica/paper.tex
add B matrix to equation
fix mean/median typo

@@
 When we employ a fixed-point arithmetic digital controller, the operation above can be expressed as follows, where we use $\mathcal{F}_{\langle I_c,F_c \rangle}$ preceding a variable to indicate that variable is converted into the fixed-point precision given by $\mathcal{F}_{\langle I_c,F_c \rangle}$:
-\note{the first of the two equations is not clear - don't you miss a B matrix?}
 %
 \begin{align*}
-x_{k+1} &= A_d \cdot x_{k} -(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
+x_{k+1} &= A_d \cdot x_{k} -B_d(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
 x_{k+1} &= (A_d  - B_dK) \cdot x_k + B_dK\delta, 
@@
 
-The mean run-time for \textcolor{blue}{the successful} benchmarks is 152.6\,s for fixed-point and 117.5\,s for floating-point implementations, respectively.  
-\note{unclear repeat next:} The mean run-time for \textcolor{blue}{the successful} benchmarks is 16\,s for fixed-point and 11\,s for floating-point implementations, respectively.
+The mean run-time for the successful benchmarks is 152.6\,s for fixed-point and 117.5\,s for floating-point implementations, respectively.  
+The median run-time for the successful benchmarks is 16\,s for fixed-point and 11\,s for floating-point implementations, respectively.
 We consider these times to be short enough to be of practical use to control engineers, and thus affirm the validity of EG1.

### 2019-01-23 automatica/paper.tex
is this better for the fixed point arithmetic on intervals?

@@
 
-The fixed-point arithmetic of the digital controller is performed on the upper and lower bound of each interval independently and the upper and lower bound of the result taken as the interval result\note{clarify what is meant by 'limit' and by 'each' (each amongst what?)}.
+The fixed-point arithmetic of the digital controller is performed on the upper and lower bound of the intervals independently and the upper and lower bound of the result taken as the interval result\note{Would an example make this clearer?, e.g., consider the conversion from plant precision to controller precision performed by the ADC on a single state value.
+The state value is represented as an interval $\{x.high, x.low\}$, and the result of the conversion is an interval where the upper bound is the conversion of $x.high$ and the lower bound is the conversion of $x.low$?}.
 Since the precision of the floating point domain is greater than the precision of the controller, this is guaranteed to bound the real behaviour of the controller.

### 2019-01-23 automatica/paper.tex
comment on time disc

@@
 The models are discretized with sampling times ranging from 1.5s to 0.005s, and if CEGIS is unable to 
-synthesise a controller for a given sampling time, CEGIS heuristically selects a new sampling time \note{do we, still?}.
+synthesise a controller for a given sampling time, CEGIS heuristically selects a new sampling time \note{do we, still?
+Yes, each benchmark has up to 8 time discretisations, that we run through in the order they are written in the benchmark.
+``heuristically'' is a euphemism for the fact the order is not consistent for each benchmark and we dont run through them in e.g., increasing order.}.
 

### 2019-01-23 automatica/paper.tex
fix section label

@@
 \subsection{Safety of closed-loop systems}
+\label{sec:safety}
 
@@
 We start by describing the property that we pass to the synthesizer as the specification $\phi$. 
-Namely, as we are interested in capturing safety (to be discussed in Section~\ref{ssec:safespecification}\note{fix?}),  
+Namely, as we are interested in capturing safety (as discussed in Section~\ref{sec:safety}),  
 we use a stability specification to narrow the search space of possible controllers, as detailed in Section~\ref{ssec:stabspecification}.

### 2019-01-23 automatica/paper.tex
comment on exception in results

@@
 controllers is too low to be able to meet the safety specification. The floating point controllers in general take longer to synthesise
-than the fixed point controllers \note{there is one surprising exception - check please}.
+than the fixed point controllers. There is one exception to this, which is due to the fact that it is not guaranteed that a controller
+exists for all the time discretizations we give the algorithm and, in this case, the fixed-point algorithm was forced to try more time discretizations
+than the floating-point algorithm
+because a fixed-point controller lacked the precision to control the system under the first few time discretizations. 
 %For the majority of the {\it fixed-point} benchmarks, we observe that the abstraction-based

### 2019-01-23 automatica/paper.tex
misaligned notation

@@
 \textcolor{blue}{$\mathcal{F}_{\langle I_p,F_p \rangle}$, where $I_p$ and $F_p$ indicate the integer and fractional parts,  
-and \textcolor{blue}{ $\mathcal{F}_{\langle W_p,F_p \rangle}$}, where $W_p$ and $F_p$ indicate the total word-length and fractional part, 
+and \note[make this align with the notation earlier in the paper]}\textcolor{blue}{ $\mathcal{F}_{\langle W_p,F_p \rangle}$}, where $W_p$ and $F_p$ indicate the total word-length and fractional part, 
 are the fixed- and floating-point precisions used to model the plant, respectively; } 

### 2019-01-23 automatica/paper.tex
align notation for floating point and fixed point

--- 2019-01-23 automatica/paper.tex
@@
 \textcolor{blue}{$\mathcal{F}_{\langle I_p,F_p \rangle}$, where $I_p$ and $F_p$ indicate the integer and fractional parts,  
-and \textcolor{blue}{ $\mathcal{F}_{\langle W_p,F_p \rangle}$}, where $W_p$ and $F_p$ indicate the total word-length and fractional part, 
-are the fixed- and floating-point precisions used to model the plant, respectively; } 
+and $\mathcal{F}_{\langle E_p,M_p \rangle}$}, where $E_p$ and $M_p$ indicate the exponent and mantissa part, 
+are the fixed- and floating-point precisions used to model the plant, respectively; 
 and \textit{Time} is the total time required to synthesize a controller for the given plant.    
@@
 chosen to be $I_c = 8$, $F_c = 8$ for fixed-point, \textcolor{blue}{whereas  
-$\mathcal{F}_{\langle W_c, F_c \rangle}$ is chosen to be $W_c = 16$ and $F_c = 10$
+$\mathcal{F}_{\langle E_c, M_c \rangle}$ is chosen to be $W_c = 6$ and $F_c = 10$
 for half-precision floating-point format}.
@@
 %   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
-%1  & Acrobot     & 4 & 16,8 & 61959.4\,s &  & ~\xmark & & ~\xmark &  & ~\xmark \\
+%1  & Acrobot     & 4 & 8,8 & 61959.4\,s &  & ~\xmark & & ~\xmark &  & ~\xmark \\
 %2  & Antenna     & 6 &  & ~\xmark &  & ~\xmark & & ~\xmark & & 2903s~\xmark\\
 %3  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark & & ~\xmark & & ~\xmark\\
-%4  & Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &14.6\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
-%5  & Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 9.2\,s & & ~\xmark & 16,10 & 1.4\,s\\
+%4  & Bioreact    & 3 & 8,8 & 11.5\,s & 6,10 &14.6\,s & 24,14 & 0.4\,s & 6,10 & 0.5\,s\\
+%5  & Chen\_ex1   & 3 & 8,8 & 10.3\,s  & 6,10 & 9.2\,s & & ~\xmark & 6,10 & 1.4\,s\\
 %6  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 4683.8\,s &  & ~\xmark & & ~\xmark\\
@@
 %8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-%9  & Cruise      & 1 & 16,8 & 9.6\,s & 16,10 & 6.5\,s & 24,14 & 0.3\,s& 16,10 & 0.3\,s\\
-%10 & CruiseHSCC & 1 & 16,8 & 9.6\,s & 16,10 & 6.6\,s &  24,14 & 0.3\,s & 16,10 & 0.3\,s \\
+%9  & Cruise      & 1 & 8,8 & 9.6\,s & 6,10 & 6.5\,s & 24,14 & 0.3\,s& 6,10 & 0.3\,s\\
+%10 & CruiseHSCC & 1 & 8,8 & 9.6\,s & 6,10 & 6.6\,s &  24,14 & 0.3\,s & 6,10 & 0.3\,s \\
 %11 & Cstr & 3 & & ~\xmark & & ~\xmark & & ~\xmark & & 181s~\xmark\\
 %12 & Cstrtmp  & 3 &  & ~\xmark & & ~\xmark & 24,14 & 0.5\,s & & ~\xmark\\
-%13 & DCmotor   & 2 & 16,8  & 11.3\,s & 16,10 & 7.8\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s (4.0\,s) \\
+%13 & DCmotor   & 2 & 8,8  & 11.3\,s & 6,10 & 7.8\,s & 24,14 & 0.4\,s & 6,10 & 0.5\,s (4.0\,s) \\
 %14 & Flexbeam   & 6 & & ~\xmark & & ~\xmark & 24,14 & 72.1\,s & & ~\xmark\\
 %15 & Guidance chen  & 5 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-%16 & Helicopter   & 3 & 16,8 & 13.8\,s & 32,23 & 148\,s & 24,14 & 0.8\,s& 16,10 & 1.1\,s (56.6\,s)\\
+%16 & Helicopter   & 3 & 8,8 & 13.8\,s & 32,23 & 148\,s & 24,14 & 0.8\,s& 6,10 & 1.1\,s (56.6\,s)\\
 %17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-%18 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 16,10 & 28.2\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s\\
-%19 & Magpointer   & 2 & 16,8 & 10.1\,s & 16,10 & 20.4\,s & 24,14  & 1\,s& 16,10 & 1.3\,s (\xmark)\\
-%20 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 34.8\,s & 24,14 & 0.5\,s & 16,10 & 0.6\,s (\xmark)\\
-%21 & Pendulum   & 2 & 16,8 & 8.5\,s & 32,23 & 24\,s & 24,14 & 0.4\,s & 16,10 & 0.5\,s (2.4\,s)\\
+%18 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 6,10 & 28.2\,s & 24,14 & 0.4\,s & 6,10 & 0.5\,s\\
+%19 & Magpointer   & 2 & 8,8 & 10.1\,s & 6,10 & 20.4\,s & 24,14  & 1\,s& 6,10 & 1.3\,s (\xmark)\\
+%20 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 6,10 & 34.8\,s & 24,14 & 0.5\,s & 6,10 & 0.6\,s (\xmark)\\
+%21 & Pendulum   & 2 & 8,8 & 8.5\,s & 32,23 & 24\,s & 24,14 & 0.4\,s & 6,10 & 0.5\,s (2.4\,s)\\
 %22 & Regulator   & 5 & & ~\xmark & & ~\xmark & &~\xmark  & & 529s~\xmark\\
 %23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & 14.1s~\xmark\\
-%24 & streamdrum   & 3 & 16,8  & 332.5\,s & 16,10 & 590.5\,s & 24,14 & 0.7\,s & 16,10 &1.3\,s\\
-%25 & Suspension  & 4 & 16,8  & 17.2\,s & 16,10 &1373\,s & 56,30 & 15.3\,s & 16,10 & 4.4\,s (313.6\,s)\\
-%26 & Tapedriver   & 3 & 16,8  & 8.2\,s & & ~\xmark & 64,22 & 2.1\,s & 16,10 & 1.1\,s (6.0\,s)\\
+%24 & streamdrum   & 3 & 8,8  & 332.5\,s & 6,10 & 590.5\,s & 24,14 & 0.7\,s & 6,10 &1.3\,s\\
+%25 & Suspension  & 4 & 8,8  & 17.2\,s & 6,10 &1373\,s & 56,30 & 15.3\,s & 6,10 & 4.4\,s (313.6\,s)\\
+%26 & Tapedriver   & 3 & 8,8  & 8.2\,s & & ~\xmark & 64,22 & 2.1\,s & 6,10 & 1.1\,s (6.0\,s)\\
 %\hline
@@
  Benchmark  &  Order  & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Time & $\mathcal{F}_{\langle E_p, M_p \rangle}$ & Time \\\hline
-%1  & Acrobot     & 4 & 16,8 & 61529.8\,s &  & ~\xmark \\
- Antenna     & 6 &  & ~\xmark & 16,10 & 817.4\,s \\
+%1  & Acrobot     & 4 & 8,8 & 61529.8\,s &  & ~\xmark \\
+ Antenna     & 6 &  & ~\xmark & 6,10 & 817.4\,s \\
 %2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
- Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &23.6\,s \\
- Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 12.7\,s \\
+ Bioreact    & 3 & 8,8 & 11.5\,s & 6,10 &23.6\,s \\
+ Chen\_ex1   & 3 & 8,8 & 10.3\,s  & 6,10 & 12.7\,s \\
 %4  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 3535s.1\,s \\
- Chen\_ex3   & 7 & 16,8  & 11.4\,s & 16,10 & 59.1\,s \\
+ Chen\_ex3   & 7 & 8,8  & 11.4\,s & 6,10 & 59.1\,s \\
 %8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
- Cruise      & 1 & 16,8 & 9.7\,s & 16,10 & 10.3\,s \\
- CruiseHSCC & 1 & 16,8 & 9.7\,s & 16,10 & 10.3\,s  \\
- Cstr & 3 & & ~\xmark & 16,10 & 21.4\,s \\
- Cstrtmp  & 3 & 16,8 & 12.5\,s &16,10 & 15.4\,s \\
- DCmotor   & 2 & 16,8  & 10.0\,s & 16,10 & 11.4\,s  \\
+ Cruise      & 1 & 8,8 & 9.7\,s & 6,10 & 10.3\,s \\
+ CruiseHSCC & 1 & 8,8 & 9.7\,s & 6,10 & 10.3\,s  \\
+ Cstr & 3 & & ~\xmark & 6,10 & 21.4\,s \\
+ Cstrtmp  & 3 & 8,8 & 12.5\,s &6,10 & 15.4\,s \\
+ DCmotor   & 2 & 8,8  & 10.0\,s & 6,10 & 11.4\,s  \\
 %11 & Flexbeam   & 6 & & ~\xmark & 16, 10 & 10916.1\,s \\
 %12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
- Helicopter   & 3 &  & ~\xmark & 16,10 & 32.0\,s \\
+ Helicopter   & 3 &  & ~\xmark & 6,10 & 32.0\,s \\
 %17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
- Invpendulum\_pendang & 2 & 16,8  & 10.7 & 16,10 & 14.8\,s\\
- Magpointer   & 2 &  & ~\xmark & 16,10 & 86.0\,s \\
- Magsuspension  & 2 & 12,12  & 39.0\,s  & 16,10 & 43.2\,s \\
- Pendulum   & 2 & 16,8 & 13.2\,s & 16,10 & 16.6\,s\\
- Regulator   & 5 & 16,8 & 1532.7\,s & 16,10 & 999.6\,s\\
- Springmassdamper & 2 & & ~\xmark &16,10 & 24.2s \\
- Steamdrum   & 3 & 16,8  & 700.9s & 16,10 & 24.4\,s \\
- Suspension  & 4 & 16,8  & 11.4\,s & 16,10 &15.4\,s \\
- Tapedriver   & 3 & 16,8  & 11.4\,s &16,10 & 13.3\,s \\
+ Invpendulum\_pendang & 2 & 8,8  & 10.7 & 6,10 & 14.8\,s\\
+ Magpointer   & 2 &  & ~\xmark & 6,10 & 86.0\,s \\
+ Magsuspension  & 2 & 12,12  & 39.0\,s  & 6,10 & 43.2\,s \\
+ Pendulum   & 2 & 8,8 & 13.2\,s & 6,10 & 16.6\,s\\
+ Regulator   & 5 & 8,8 & 1532.7\,s & 6,10 & 999.6\,s\\
+ Springmassdamper & 2 & & ~\xmark &6,10 & 24.2s \\
+ Steamdrum   & 3 & 8,8  & 700.9s & 6,10 & 24.4\,s \\
+ Suspension  & 4 & 8,8  & 11.4\,s & 6,10 &15.4\,s \\
+ Tapedriver   & 3 & 8,8  & 11.4\,s &6,10 & 13.3\,s \\
 \hline

### 2019-01-23 automatica/paper.tex
decided I didn't like experimental goal 2
seems silly because Matlab isn’t sound

@@
 Using the state-space models described in Section~\ref{exp:benchmarks}, 
-the evaluation study has the following two experimental goals:
+the evaluation study has the following experimental goal:
 
@@
 
-\item[EG2] \textbf{(Sanity check)} Confirm the stability \note{also?} and safety of the synthesized controllers outside 
-of our model representation using MATLAB. 
+%\item[EG2] \textbf{(Sanity check)} Confirm the stability \note{also?} and safety of the synthesized controllers outside 
+%of our model representation using MATLAB. 
 %\note{Where is this done?}
@@
 
-\textcolor{blue}{The synthesized controllers are confirmed to be safe outside of our model
-representation using MATLAB, achieving EG2 \note{please explain how this check is performed - is the check itself sound?}.  
+%\textcolor{blue}{The synthesized controllers are confirmed to be safe outside of our model
+%representation using MATLAB, achieving EG2 \note{please explain how this check is performed - is the check itself sound?}.  
 A~link to the full experimental environment, including scripts to reproduce the results, all
@@
 The provided experimental environment runs multiple discretisations for each
-benchmark, and lists the fastest as the result synthesis time.}
+benchmark, and lists the fastest as the result synthesis time.
 

### 2019-01-23 automatica/paper.tex
remove some blue

@@
 The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
-chosen to be $I_c = 8$, $F_c = 8$ for fixed-point, \textcolor{blue}{whereas  
+chosen to be $I_c = 8$, $F_c = 8$ for fixed-point, whereas  
 $\mathcal{F}_{\langle E_c, M_c \rangle}$ is chosen to be $W_c = 6$ and $F_c = 10$
-for half-precision floating-point format}.
+for half-precision floating-point format.
 

### 2019-01-24 automatica/paper.tex
remove "FWL" acronym

@@
 Recent results in digital control, however, have focused on separate aspects of discretization, 
-including delayed response~\cite{Duggirala2015} and finite word length (FWL) semantics, 
+including delayed response~\cite{Duggirala2015} and finite-precision arithmetic, 
 with the goal either to verify~\cite{daes20161} the correctness of the implementation or to optimize~\cite{oudjida2014design} the design.
 
-There are two different problems that arise from FWL semantics in digital controllers.  The first
+There are two different problems that arise from finite-precision arithmetic in digital controllers.  The first
 is the error caused by the inability to represent the exact
@@
 In~\cite{fialho1994stability}, a stability measure based on the error of the digital dynamics ensures that
-the deviation introduced by FWL does not lead to instability.  
+the deviation introduced by finite-precision arithmetic does not lead to instability.  
 \cite{DBLP:journals/automatica/WuLCC09} uses $\mu$-calculus to directly model the digital controller so that selected
@@
 %
-\item Division: the operations performed by the controllers in the FWL
+\item Division: the operations performed by the controllers in the finite-precision
 domain do not include division.  However, we do use division in computations within the plant.  
@@
 Finally, in Step~3, the numerical representation for the digital controller implementation must be set by the user, i.e., 
-the FWL format that defines the number of bits of integer and fractional parts when using fixed-point arithmetic, 
+the finite-precision arithmetic that defines the number of bits of integer and fractional parts when using fixed-point arithmetic, 
 or half- and single-precision when using floating-point arithmetic, 
@@
 The synthesis is considered to be \emph{successful} if a digital controller is
-correctly synthesized w.r.t.~FWL effects; otherwise, \note{needed next?}if any parameter is
-incorrectly defined in previous steps, \note{next OK;} or if there is no solution (no
+correctly synthesized w.r.t. effects of finite-precision arithmetic; or if there is no solution (no
 controller) for the corresponding physical plant (given the implementation
@@
 and use CBMC as an oracle to answer our queries.  CBMC itself relies on an
-underlying SAT or SMT solver to address verification conditions.  We~model FWL
-effects, time discretization \note{keep time-d?}, and the presence of quantization noise
+underlying SAT or SMT solver to address verification conditions.  We~model
+effects of finite-precision arithmetic 
 explicitly using CBMC's nondeterminism API (e.g., \texttt{nondet},
@@
 %and the abstraction-based 
-CEGIS approach is able to generate FWL digital controllers using floating-point arithmetic in a reasonable amount of time.
+CEGIS approach is able to generate finite-precision digital controllers using fixed-point and floating-point arithmetic in a reasonable amount of time.
 
@@
 \textit{Plant precision and discretization heuristics:} Our algorithm to
-select suitable FWL word widths to model the plant behavior 
+select suitable finite-precision arithmetic to model the plant behavior 
 increases the precision by 8 bits at each step 

### 2019-01-24 benchmarks/matlab/headerfiles/acrobot/acrobot_ss_disc.h

@@ -1,0 +1,27 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.500  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 4 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(3.743724e+00),  interval(-3.438393e+00),  interval(8.690112e-01),  interval(-4.326137e-01)},
+{ interval(-3.973071e+00),  interval(8.369377e+00),  interval(-4.998862e-01),  interval(1.451004e+00)},
+{ interval(1.712252e+01),  interval(-2.359894e+01),  interval(3.743724e+00),  interval(-3.438393e+00)},
+{ interval(-2.726863e+01),  interval(4.887006e+01),  interval(-3.973071e+00),  interval(8.369377e+00)}};
+const __plant_typet _controller_B[NSTATES] = {interval(-7.710746e-01), interval(1.523697e+00), interval(-5.176683e+00), interval(1.016667e+01)};
+const __plant_typet __char_poly_const[5][5] = 
+ {{ 1,  0,  0,  0,  0},
+{ -2.422620e+01,  1.016667e+01,  -5.176683e+00,  1.523697e+00,  -7.710746e-01},
+{ 7.268661e+01,  -4.515438e+01,  2.191392e+01,  -3.757837e+00,  1.657612e+00},
+{ -2.422620e+01,  4.515438e+01,  -2.191392e+01,  -3.757837e+00,  1.657612e+00},
+{ 1.000000e+00,  -1.016667e+01,  5.176683e+00,  1.523697e+00,  -7.710746e-01}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/acrobot/acrobot_ss_disc1.h

@@ -1,0 +1,27 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.100  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 4 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.063874e+00),  interval(-6.491412e-02),  interval(1.021100e-01),  interval(-2.134125e-03)},
+{ interval(-7.500843e-02),  interval(1.151202e+00),  interval(-2.465987e-03),  interval(1.049811e-01)},
+{ interval(1.306278e+00),  interval(-1.343118e+00),  interval(1.063874e+00),  interval(-6.491412e-02)},
+{ interval(-1.551976e+00),  interval(3.113168e+00),  interval(-7.500843e-02),  interval(1.151202e+00)}};
+const __plant_typet _controller_B[NSTATES] = {interval(-1.537333e-02), interval(3.082272e-02), interval(-3.170500e-01), interval(6.351355e-01)};
+const __plant_typet __char_poly_const[5][5] = 
+ {{ 1,  0,  0,  0,  0},
+{ -4.430152e+00,  6.351355e-01,  -3.170500e-01,  3.082272e-02,  -1.537333e-02},
+{ 6.879459e+00,  -1.938980e+00,  9.645688e-01,  -3.245398e-02,  1.602064e-02},
+{ -4.430152e+00,  1.938980e+00,  -9.645688e-01,  -3.245398e-02,  1.602064e-02},
+{ 1.000000e+00,  -6.351355e-01,  3.170500e-01,  3.082272e-02,  -1.537333e-02}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/ballmaglev/ballmaglev_ss_disc6.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.000  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.000002e+00),  interval(5.000004e-05),  interval(-4.256136e-08)},
+{ interval(8.761068e-02),  interval(1.000002e+00),  interval(-1.701912e-03)},
+{ interval(0),  interval(0),  interval(9.980884e-01)}};
+const __plant_typet _controller_B[NSTATES] = {interval(-1.364363e-12), interval(-8.184877e-08), interval(9.606191e-05)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -2.998093e+00,  9.606191e-05,  -8.184877e-08,  -1.364363e-12},
+{ 2.996181e+00,  -1.921242e-04,  5.218819e-11,  -5.454845e-12},
+{ -9.980884e-01,  9.606191e-05,  8.179658e-08,  -1.363059e-12}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/ballmaglev/ballmaglev_ss_disc7.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.000  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.000000e+00),  interval(1.000000e-05),  interval(-1.703323e-09)},
+{ interval(1.752212e-02),  interval(1.000000e+00),  interval(-3.406428e-04)},
+{ interval(0),  interval(0),  interval(9.996174e-01)}};
+const __plant_typet _controller_B[NSTATES] = {interval(-1.091908e-14), interval(-3.275620e-09), interval(1.922709e-05)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -2.999618e+00,  1.922709e-05,  -3.275620e-09,  -1.091908e-14},
+{ 2.999235e+00,  -3.845418e-05,  4.178249e-13,  -4.367215e-14},
+{ -9.996174e-01,  1.922709e-05,  3.275202e-09,  -1.091699e-14}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/ballmaglev/ballmaglev_ss_disc9.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.000  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.000000e+00),  interval(1.000000e-06),  interval(-1.703518e-11)},
+{ interval(1.752212e-03),  interval(1.000000e+00),  interval(-3.407014e-05)},
+{ interval(0),  interval(0),  interval(9.999617e-01)}};
+const __plant_typet _controller_B[NSTATES] = {interval(-1.092002e-17), interval(-3.275996e-11), interval(1.923040e-06)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -2.999962e+00,  1.923040e-06,  -3.275996e-11,  -1.092002e-17},
+{ 2.999923e+00,  -3.846080e-06,  4.178969e-16,  -4.367967e-17},
+{ -9.999617e-01,  1.923040e-06,  3.275955e-11,  -1.091981e-17}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/bioreact/bioreact_ss_disc1.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.800  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(4.788130e-01),  interval(7.892941e-01),  interval(-2.349702e-01)},
+{ interval(1),  interval(0),  interval(0)},
+{ interval(0),  interval(1.250000e-01),  interval(0)}};
+const __plant_typet _controller_B[NSTATES] = {interval(2), interval(0), interval(0)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -4.788130e-01,  2,  0,  0},
+{ -7.892941e-01,  0,  2,  0},
+{ 2.937127e-02,  0,  0,  2.500000e-01}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/bioreact/bioreact_ss_disc2.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.500  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.088597e+00),  interval(0),  interval(0)},
+{ interval(1),  interval(0),  interval(0)},
+{ interval(0),  interval(1),  interval(0)}};
+const __plant_typet _controller_B[NSTATES] = {interval(1), interval(0), interval(0)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -1.088597e+00,  1,  0,  0},
+{ 0,  0,  1,  0},
+{ 0,  0,  0,  1}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/bioreact/bioreact_ss_disc4.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 1.200  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.135064e+00),  interval(4.458085e-01)},
+{ interval(2.500000e-01),  interval(0)}};
+const __plant_typet _controller_B[NSTATES] = {interval(2), interval(0)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -1.135064e+00,  2,  0},
+{ -1.114521e-01,  0,  5.000000e-01}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/bioreact/bioreact_ss_disc5.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 1.500  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.090034e+00),  interval(5.160138e-01)},
+{ interval(5.000000e-01),  interval(0)}};
+const __plant_typet _controller_B[NSTATES] = {interval(2), interval(0)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -1.090034e+00,  2,  0},
+{ -2.580069e-01,  0,  1}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/bioreact/bioreact_ss_disc6.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 1.800  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.071729e+00),  interval(7.756817e-01)},
+{ interval(5.000000e-01),  interval(0)}};
+const __plant_typet _controller_B[NSTATES] = {interval(2), interval(0)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -1.071729e+00,  2,  0},
+{ -3.878408e-01,  0,  1}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/bioreact/bioreact_ss_disc7.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 2.000  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.070994e+00),  interval(4.681092e-01)},
+{ interval(1),  interval(0)}};
+const __plant_typet _controller_B[NSTATES] = {interval(2), interval(0)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -1.070994e+00,  2,  0},
+{ -4.681092e-01,  0,  2}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/bioreact/bioreact_ss_disc8.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 2.200  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.077832e+00),  interval(5.448118e-01)},
+{ interval(1),  interval(0)}};
+const __plant_typet _controller_B[NSTATES] = {interval(2), interval(0)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -1.077832e+00,  2,  0},
+{ -5.448118e-01,  0,  2}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/bioreact/bioreact_ss_disc9.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 2.500  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.100175e+00),  interval(6.551771e-01)},
+{ interval(1),  interval(0)}};
+const __plant_typet _controller_B[NSTATES] = {interval(2), interval(0)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -1.100175e+00,  2,  0},
+{ -6.551771e-01,  0,  2}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/chen_ex1/chen_ex1_ss_disc1.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.100  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(5.111777e-01),  interval(-2.091381e-01),  interval(-1.107232e-01)},
+{ interval(2.952619e-01),  interval(9.540705e-01),  interval(-2.458240e-02)},
+{ interval(1.638827e-02),  interval(9.839786e-02),  interval(9.991382e-01)}};
+const __plant_typet _controller_B[NSTATES] = {interval(3.690773e-02), interval(8.194133e-03), interval(2.872615e-04)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -2.464386e+00,  2.872615e-04,  8.194133e-03,  3.690773e-02},
+{ 2.017669e+00,  9.902295e-04,  -1.485344e-03,  -7.383402e-02},
+{ -5.488116e-01,  2.128085e-04,  -6.708788e-03,  3.692628e-02}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/chen_ex1/chen_ex1_ss_disc9.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.000  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(9.999940e-01),  interval(-2.749993e-06),  interval(-1.499996e-06)},
+{ interval(3.999988e-06),  interval(1.000000e+00),  interval(-2.999994e-12)},
+{ interval(1.999996e-12),  interval(1.000000e-06),  interval(1)}};
+const __plant_typet _controller_B[NSTATES] = {interval(4.999985e-07), interval(9.999980e-13), interval(3.333328e-19)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -2.999994e+00,  3.333328e-19,  9.999980e-13,  4.999985e-07},
+{ 2.999988e+00,  1.333329e-18,  -1.999994e-18,  -9.999970e-07},
+{ -9.999940e-01,  3.333318e-19,  -9.999960e-13,  4.999985e-07}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/cruise/cruise_ss_disc.h

@@ -1,0 +1,21 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.500  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 1 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = { interval(9.753099e-01)};
+ const __plant_typet _controller_B[NSTATES] = {interval(1.543130e-02)};
+const __plant_typet __char_poly_const[2][2] = 
+ {{ 1,  0},
+{ -9.753099e-01,  1.543130e-02}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/cruise/cruise_ss_disc2.h

@@ -1,0 +1,21 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.050  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 1 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = { interval(9.975031e-01)};
+ const __plant_typet _controller_B[NSTATES] = {interval(1.560549e-03)};
+const __plant_typet __char_poly_const[2][2] = 
+ {{ 1,  0},
+{ -9.975031e-01,  1.560549e-03}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/cstr/cstr_ss_disc.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.500  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(7.677953e-01),  interval(-4.455178e-02),  interval(-8.776488e-03)},
+{ interval(5.494095e-02),  interval(9.985473e-01),  interval(-2.863273e-04)},
+{ interval(4.481034e-04),  interval(1.561727e-02),  interval(9.999985e-01)}};
+const __plant_typet _controller_B[NSTATES] = {interval(1.373524e-02), interval(4.481034e-04), interval(2.384262e-06)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -2.766341e+00,  2.384262e-06,  4.481034e-04,  1.373524e-02},
+{ 2.535476e+00,  8.941536e-06,  -3.752793e-05,  -2.747049e-02},
+{ -7.691264e-01,  2.091059e-06,  -4.105754e-04,  1.373525e-02}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/cstr/cstr_ss_disc2.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.050  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(9.740760e-01),  interval(-4.994912e-03),  interval(-9.854047e-04)},
+{ interval(6.168649e-03),  interval(9.999843e-01),  interval(-3.092870e-06)},
+{ interval(4.840354e-06),  interval(1.562492e-03),  interval(1.000000e+00)}};
+const __plant_typet _controller_B[NSTATES] = {interval(1.542162e-03), interval(4.840354e-06), interval(2.526525e-09)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -2.974060e+00,  2.526525e-09,  4.840354e-06,  1.542162e-03},
+{ 2.948152e+00,  1.004011e-08,  -4.216817e-08,  -3.084325e-03},
+{ -9.740915e-01,  2.493582e-09,  -4.798186e-06,  1.542162e-03}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/cstr/cstr_ss_disc7.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.000  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(9.999948e-01),  interval(-1.011997e-06),  interval(-1.996795e-07)},
+{ interval(1.249997e-06),  interval(1.000000e+00),  interval(-1.247998e-13)},
+{ interval(1.953122e-13),  interval(3.125000e-07),  interval(1)}};
+const __plant_typet _controller_B[NSTATES] = {interval(3.124992e-07), interval(1.953122e-13), interval(2.034503e-20)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -2.999995e+00,  2.034503e-20,  1.953122e-13,  3.124992e-07},
+{ 2.999990e+00,  8.137999e-20,  -3.417960e-19,  -6.249984e-07},
+{ -9.999948e-01,  2.034497e-20,  -1.953118e-13,  3.124992e-07}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/cstr/cstr_ss_disc9.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.000  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(9.999995e-01),  interval(-1.012000e-07),  interval(-1.996799e-08)},
+{ interval(1.250000e-07),  interval(1.000000e+00),  interval(-1.248000e-15)},
+{ interval(1.953125e-15),  interval(3.125000e-08),  interval(1)}};
+const __plant_typet _controller_B[NSTATES] = {interval(3.124999e-08), interval(1.953125e-15), interval(2.034505e-23)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -2.999999e+00,  2.034505e-23,  1.953125e-15,  3.124999e-08},
+{ 2.999999e+00,  8.138019e-23,  -3.417968e-22,  -6.249998e-08},
+{ -9.999995e-01,  2.034504e-23,  -1.953124e-15,  3.124999e-08}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/cstrtemp/cstrtemp_ss_disc.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.500  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(9.763909e-01),  interval(2.655164e-02)},
+{ interval(3.087745e-02),  interval(1.000417e+00)}};
+const __plant_typet _controller_B[NSTATES] = {interval(2.470196e-01), interval(3.875051e-03)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -1.976807e+00,  3.875051e-03,  2.470196e-01},
+{ 9.759777e-01,  3.843771e-03,  -2.470196e-01}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/cstrtemp/cstrtemp_ss_disc1.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.100  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(9.951654e-01),  interval(5.361383e-03)},
+{ interval(6.234862e-03),  interval(1.000017e+00)}};
+const __plant_typet _controller_B[NSTATES] = {interval(4.987890e-02), interval(1.559975e-04)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -1.995182e+00,  1.559975e-04,  4.987890e-02},
+{ 9.951487e-01,  1.557448e-04,  -4.987890e-02}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/cstrtemp/cstrtemp_ss_disc4.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.001  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(9.999757e-01),  interval(2.687167e-05)},
+{ interval(3.124962e-05),  interval(1.000000e+00)}};
+const __plant_typet _controller_B[NSTATES] = {interval(2.499970e-04), interval(3.906218e-09)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -1.999976e+00,  3.906218e-09,  2.499970e-04},
+{ 9.999757e-01,  3.906187e-09,  -2.499970e-04}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/cstrtemp/cstrtemp_ss_disc6.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.000  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(9.999976e-01),  interval(2.687197e-06)},
+{ interval(3.124996e-06),  interval(1.000000e+00)}};
+const __plant_typet _controller_B[NSTATES] = {interval(2.499997e-05), interval(3.906247e-11)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -1.999998e+00,  3.906247e-11,  2.499997e-05},
+{ 9.999976e-01,  3.906244e-11,  -2.499997e-05}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/cstrtemp/cstrtemp_ss_disc9.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.000  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.000000e+00),  interval(5.374400e-08)},
+{ interval(6.250000e-08),  interval(1.000000e+00)}};
+const __plant_typet _controller_B[NSTATES] = {interval(5.000000e-07), interval(1.562500e-14)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -2.000000e+00,  1.562500e-14,  5.000000e-07},
+{ 1.000000e+00,  1.562500e-14,  -5.000000e-07}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/dcmotor/dcmotor_ss_disc.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.500  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(-9.874124e-05),  interval(-9.874085e-02)},
+{ interval(9.494312e-04),  interval(9.494274e-01)}};
+const __plant_typet _controller_B[NSTATES] = {interval(9.494312e-04), interval(4.862749e-04)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -9.493287e-01,  4.862749e-04,  9.494312e-04},
+{ 2.826151e-21,  9.494350e-07,  -9.494312e-04}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/dcmotor/dcmotor_ss_disc1.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.100  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(-1.029355e-04),  interval(-1.029351e-01)},
+{ interval(9.897607e-04),  interval(9.897568e-01)}};
+const __plant_typet _controller_B[NSTATES] = {interval(9.897607e-04), interval(9.849243e-05)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -9.896539e-01,  9.849243e-05,  9.897607e-04},
+{ -2.853564e-20,  9.897647e-07,  -9.897607e-04}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/dcmotor/dcmotor_ss_disc2.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.050  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(-1.034722e-04),  interval(-1.034718e-01)},
+{ interval(9.949209e-04),  interval(9.949169e-01)}};
+const __plant_typet _controller_B[NSTATES] = {interval(9.949209e-04), interval(4.887550e-05)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -9.948135e-01,  4.887550e-05,  9.949209e-04},
+{ -1.795973e-20,  9.949249e-07,  -9.949209e-04}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/dcmotor/dcmotor_ss_disc3.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.001  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(3.678152e-01),  interval(-6.573667e-02)},
+{ interval(6.320834e-04),  interval(9.999617e-01)}};
+const __plant_typet _controller_B[NSTATES] = {interval(6.320834e-04), interval(3.678661e-07)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -1.367777e+00,  3.678661e-07,  6.320834e-04},
+{ 3.678427e-01,  2.642226e-07,  -6.320834e-04}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/dcmotor/dcmotor_ss_disc4.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.001  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(6.064910e-01),  interval(-4.091970e-02)},
+{ interval(3.934586e-04),  interval(9.999889e-01)}};
+const __plant_typet _controller_B[NSTATES] = {interval(3.934586e-04), interval(1.065288e-07)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -1.606480e+00,  1.065288e-07,  3.934586e-04},
+{ 6.065003e-01,  9.020093e-08,  -3.934586e-04}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/dcmotor/dcmotor_ss_disc6.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.000  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(9.512245e-01),  interval(-5.072127e-03)},
+{ interval(4.877045e-05),  interval(9.999999e-01)}};
+const __plant_typet _controller_B[NSTATES] = {interval(4.877045e-05), interval(1.229422e-09)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -1.951224e+00,  1.229422e-09,  4.877045e-05},
+{ 9.512247e-01,  1.209100e-09,  -4.877045e-05}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/dcmotor/dcmotor_ss_disc7.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.000  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(9.900488e-01),  interval(-1.034817e-03)},
+{ interval(9.950161e-06),  interval(1.000000e+00)}};
+const __plant_typet _controller_B[NSTATES] = {interval(9.950161e-06), interval(4.983373e-11)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -1.990049e+00,  4.983373e-11,  9.950161e-06},
+{ 9.900488e-01,  4.966788e-11,  -9.950161e-06}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/dcmotor/dcmotor_ss_disc8.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.000  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(9.950120e-01),  interval(-5.187020e-04)},
+{ interval(4.987520e-06),  interval(1.000000e+00)}};
+const __plant_typet _controller_B[NSTATES] = {interval(4.987520e-06), interval(1.247919e-11)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -1.995012e+00,  1.247919e-11,  4.987520e-06},
+{ 9.950120e-01,  1.245841e-11,  -4.987520e-06}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/helicopter/helicopter_ss_disc.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.500  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(8.096392e-01),  interval(-1.552869e-02),  interval(-1.785605e-01)},
+{ interval(2.254552e-01),  interval(9.990216e-01),  interval(-2.310399e-02)},
+{ interval(2.917170e-02),  interval(2.499594e-01),  interval(9.980414e-01)}};
+const __plant_typet _controller_B[NSTATES] = {interval(7.214566e+00), interval(9.334945e-01), interval(7.913591e-02)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -2.806702e+00,  7.913591e-02,  9.334945e-01,  7.214566e+00},
+{ 2.628450e+00,  3.006669e-01,  -6.272694e-02,  -1.443657e+01},
+{ -8.105842e-01,  7.126433e-02,  -8.707676e-01,  7.222003e+00}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/helicopter/helicopter_ss_disc1.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.100  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(9.588945e-01),  interval(6.689355e-04),  interval(-3.878030e-02)},
+{ interval(4.896503e-02),  interval(1.000025e+00),  interval(-9.762895e-04)},
+{ interval(1.232689e-03),  interval(5.000049e-02),  interval(9.999837e-01)}};
+const __plant_typet _controller_B[NSTATES] = {interval(1.566881e+00), interval(3.944604e-02), interval(6.597273e-04)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -2.958903e+00,  6.597273e-04,  3.944604e-02,  1.566881e+00},
+{ 2.917870e+00,  2.611445e-03,  -5.482598e-04,  -3.133775e+00},
+{ -9.588698e-01,  6.460186e-04,  -3.889778e-02,  1.566894e+00}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/invpendulum_cartpos/invpendulum_cartpos_ss_disc3.h

@@ -1,0 +1,27 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.001  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 4 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.000001e+00),  interval(1.000000e-03),  interval(0),  interval(0)},
+{ interval(1.000000e-03),  interval(1.000001e+00),  interval(0),  interval(0)},
+{ interval(5.000000e-07),  interval(1.000000e-03),  interval(1),  interval(0)},
+{ interval(1.666667e-10),  interval(5.000000e-07),  interval(1.000000e-03),  interval(1)}};
+const __plant_typet _controller_B[NSTATES] = {interval(1.000000e-03), interval(5.000000e-07), interval(1.666667e-10), interval(4.166667e-14)};
+const __plant_typet __char_poly_const[5][5] = 
+ {{ 1,  0,  0,  0,  0},
+{ -4.000001e+00,  4.166667e-14,  1.666667e-10,  5.000000e-07,  1.000000e-03},
+{ 6.000002e+00,  4.583334e-13,  5.000001e-10,  -5.000000e-07,  -3.000001e-03},
+{ -4.000001e+00,  4.583334e-13,  -5.000001e-10,  -5.000000e-07,  3.000001e-03},
+{ 1.000000e+00,  4.166667e-14,  -1.666667e-10,  5.000000e-07,  -1.000000e-03}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/invpendulum_pendang/invpendulum_pendang_ss_disc1.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.100  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.005004e+00),  interval(1.001668e-01)},
+{ interval(1.001668e-01),  interval(1.005004e+00)}};
+const __plant_typet _controller_B[NSTATES] = {interval(1.001668e-01), interval(5.004168e-03)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -2.010008e+00,  5.004168e-03,  1.001668e-01},
+{ 1.000000e+00,  5.004168e-03,  -1.001668e-01}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/invpendulum_pendang/invpendulum_pendang_ss_disc3.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.001  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.000001e+00),  interval(1.000000e-03)},
+{ interval(1.000000e-03),  interval(1.000001e+00)}};
+const __plant_typet _controller_B[NSTATES] = {interval(1.000000e-03), interval(5.000000e-07)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -2.000001e+00,  5.000000e-07,  1.000000e-03},
+{ 1.000000e+00,  5.000000e-07,  -1.000000e-03}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/invpendulum_pendang/invpendulum_pendang_ss_disc5.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.000  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.000000e+00),  interval(1.000000e-04)},
+{ interval(1.000000e-04),  interval(1.000000e+00)}};
+const __plant_typet _controller_B[NSTATES] = {interval(1.000000e-04), interval(5.000000e-09)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -2.000000e+00,  5.000000e-09,  1.000000e-04},
+{ 1.000000e+00,  5.000000e-09,  -1.000000e-04}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/invpendulum_pendang/invpendulum_pendang_ss_disc7.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.000  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.000000e+00),  interval(1.000000e-05)},
+{ interval(1.000000e-05),  interval(1.000000e+00)}};
+const __plant_typet _controller_B[NSTATES] = {interval(1.000000e-05), interval(5.000000e-11)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -2.000000e+00,  5.000000e-11,  1.000000e-05},
+{ 1,  5.000000e-11,  -1.000000e-05}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/magneticpointer/magneticpointer_ss_disc1.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.100  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(9.732557e-01),  interval(-3.290424e-04),  interval(0)},
+{ interval(4.932844e-02),  interval(9.999917e-01),  interval(0)},
+{ interval(2.477565e-03),  interval(9.999972e-02),  interval(1)}};
+const __plant_typet _controller_B[NSTATES] = {interval(2.466422e-02), interval(6.193914e-04), interval(2.069293e-05)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -2.973247e+00,  2.069293e-05,  6.193914e-04,  2.466422e-02},
+{ 2.946511e+00,  8.221391e-05,  -5.569946e-06,  -4.932844e-02},
+{ -9.732639e-01,  2.041443e-05,  -6.138214e-04,  2.466422e-02}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/magneticpointer/magneticpointer_ss_disc2.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.050  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(9.865393e-01),  interval(-1.656362e-04),  interval(0)},
+{ interval(2.483137e-02),  interval(9.999979e-01),  interval(0)},
+{ interval(6.221864e-04),  interval(4.999997e-02),  interval(1)}};
+const __plant_typet _controller_B[NSTATES] = {interval(1.241569e-02), interval(1.555466e-04), interval(2.595368e-06)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -2.986537e+00,  2.595368e-06,  1.555466e-04,  1.241569e-02},
+{ 2.973079e+00,  1.034640e-05,  -7.009671e-07,  -2.483137e-02},
+{ -9.865414e-01,  2.577844e-06,  -1.548456e-04,  1.241569e-02}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/magneticpointer/magneticpointer_ss_disc5.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.000  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(9.999729e-01),  interval(-3.335175e-07),  interval(0)},
+{ interval(4.999932e-05),  interval(1.000000e+00),  interval(0)},
+{ interval(2.499977e-09),  interval(1.000000e-04),  interval(1)}};
+const __plant_typet _controller_B[NSTATES] = {interval(2.499966e-05), interval(6.249944e-10), interval(2.083319e-14)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -2.999973e+00,  2.083319e-14,  6.249944e-10,  2.499966e-05},
+{ 2.999946e+00,  8.333220e-14,  -5.645757e-15,  -4.999932e-05},
+{ -9.999729e-01,  2.083291e-14,  -6.249887e-10,  2.499966e-05}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/magsuspension/magsuspension_ss_disc1.h

@@ -1,0 +1,23 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.100  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 2 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.183334e+01),  interval(1.165201e+01)},
+{ interval(1.193166e+01),  interval(1.183334e+01)}};
+const __plant_typet _controller_B[NSTATES] = {interval(2.982915e+00), interval(2.773334e+00)};
+const __plant_typet __char_poly_const[3][3] = 
+ {{ 1,  0,  0},
+{ -2.366667e+01,  2.773334e+00,  2.982915e+00},
+{ 1.000000e+00,  2.773334e+00,  -2.982915e+00}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/regulator/regulator_ss_disc.h

@@ -1,0 +1,29 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.500  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 5 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(9.048374e-01),  interval(2.100611e-01),  interval(2.066266e-02),  interval(6.504802e-02),  interval(3.755344e-01)},
+{ interval(0),  interval(7.788008e-01),  interval(9.033475e-02),  interval(3.156122e-01),  interval(2.396729e+00)},
+{ interval(0),  interval(0),  interval(7.927521e-04),  interval(6.308523e-03),  interval(5.637409e-01)},
+{ interval(0),  interval(0),  interval(0),  interval(3.726653e-06),  interval(3.367110e-02)},
+{ interval(0),  interval(0),  interval(0),  interval(0),  interval(6.737947e-03)}};
+const __plant_typet _controller_B[NSTATES] = {interval(1.985159e+00), interval(2.332613e+01), interval(5.222808e+01), interval(8.898953e+00), interval(2.979786e+00)};
+const __plant_typet __char_poly_const[6][6] = 
+ {{ 1,  0,  0,  0,  0,  0},
+{ -1.691173e+00,  2.979786e+00,  8.898953e+00,  5.222808e+01,  2.332613e+01,  1.985159e+00},
+{ 7.173787e-01,  -5.019255e+00,  -1.494930e+01,  -8.654934e+01,  -6.613733e+00,  6.115953e+00},
+{ -5.318461e-03,  2.103816e+00,  6.214860e+00,  3.447484e+01,  -1.298350e+01,  9.231013e-01},
+{ 3.783917e-06,  -1.672477e-03,  2.353222e-02,  9.747704e-01,  -1.175831e-01,  4.032023e-03},
+{ -1.402752e-11,  6.203523e-09,  -2.255354e-05,  1.759881e-04,  -1.129200e-05,  2.214606e-07}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/steamdrum/steamdrum_ss_disc2.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.200  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.494719e+00),  interval(-2.187014e-01),  interval(-5.520347e-01)},
+{ interval(1),  interval(0),  interval(0)},
+{ interval(0),  interval(5.000000e-01),  interval(0)}};
+const __plant_typet _controller_B[NSTATES] = {interval(1.250000e-01), interval(0), interval(0)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -1.494719e+00,  1.250000e-01,  0,  0},
+{ 2.187014e-01,  0,  1.250000e-01,  0},
+{ 2.760174e-01,  0,  0,  6.250000e-02}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/steamdrum/steamdrum_ss_disc3.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.250  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(1.361328e+00),  interval(-2.279994e-02),  interval(-6.770571e-01)},
+{ interval(1),  interval(0),  interval(0)},
+{ interval(0),  interval(5.000000e-01),  interval(0)}};
+const __plant_typet _controller_B[NSTATES] = {interval(1.250000e-01), interval(0), interval(0)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -1.361328e+00,  1.250000e-01,  0,  0},
+{ 2.279994e-02,  0,  1.250000e-01,  0},
+{ 3.385285e-01,  0,  0,  6.250000e-02}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/steamdrum/steamdrum_ss_disc4.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.600  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(8.534849e-01),  interval(5.520655e-01),  interval(-8.111009e-01)},
+{ interval(1),  interval(0),  interval(0)},
+{ interval(0),  interval(5.000000e-01),  interval(0)}};
+const __plant_typet _controller_B[NSTATES] = {interval(2.500000e-01), interval(0), interval(0)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -8.534849e-01,  2.500000e-01,  0,  0},
+{ -5.520655e-01,  0,  2.500000e-01,  0},
+{ 4.055505e-01,  0,  0,  1.250000e-01}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/steamdrum/steamdrum_ss_disc8.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 1.750  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(2.999769e-01),  interval(8.711493e-01),  interval(-3.422525e-01)},
+{ interval(1),  interval(0),  interval(0)},
+{ interval(0),  interval(5.000000e-01),  interval(0)}};
+const __plant_typet _controller_B[NSTATES] = {interval(1), interval(0), interval(0)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ -2.999769e-01,  1,  0,  0},
+{ -8.711493e-01,  0,  1,  0},
+{ 1.711262e-01,  0,  0,  5.000000e-01}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/suspension/suspension_ss_disc.h

@@ -1,0 +1,27 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.500  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 4 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)1000000
+#define INPUT_LOWERBOUND (__plant_precisiont)-1000000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(2.377293e-05),  interval(4.660464e-05),  interval(7.174996e-05),  interval(2.199300e-05)},
+{ interval(-1.702991e-04),  interval(-3.195749e-04),  interval(-4.044589e-04),  interval(1.495685e-04)},
+{ interval(-2.895396e-04),  interval(-6.263289e-04),  interval(-1.324175e-03),  interval(-1.530528e-03)},
+{ interval(1.481423e-03),  interval(2.950573e-03),  interval(4.826849e-03),  interval(2.367931e-03)}};
+const __plant_typet _controller_B[NSTATES] = {interval(-5.321847e-06), interval(-3.619246e-05), interval(3.703558e-04), interval(2.414061e-01)};
+const __plant_typet __char_poly_const[5][5] = 
+ {{ 1,  0,  0,  0,  0},
+{ -7.479541e-04,  2.414061e-01,  3.703558e-04,  -3.619246e-05,  -5.321847e-06},
+{ 3.237226e-06,  3.927452e-04,  -3.702221e-04,  3.599650e-05,  5.337985e-06},
+{ -7.089229e-26,  3.859157e-08,  -1.337612e-07,  1.959521e-07,  -1.613850e-08},
+{ -6.172801e-47,  1.307296e-28,  -3.000352e-28,  -5.102908e-28,  1.784983e-27}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/suspension/suspension_ss_disc3.h

@@ -1,0 +1,27 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.001  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 4 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)1000000
+#define INPUT_LOWERBOUND (__plant_precisiont)-1000000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(5.764526e-01),  interval(-1.739824e-01),  interval(-6.215555e-02),  interval(-2.558090e-02)},
+{ interval(1.980814e-01),  interval(9.758136e-01),  interval(-8.657244e-03),  interval(-3.572299e-03)},
+{ interval(6.915374e-03),  interval(6.346275e-02),  interval(9.998075e-01),  interval(-7.951762e-05)},
+{ interval(7.696640e-05),  interval(1.019597e-03),  interval(3.199842e-02),  interval(9.999993e-01)}};
+const __plant_typet _controller_B[NSTATES] = {interval(6.190044e-03), interval(8.644217e-04), interval(1.924160e-05), interval(1.578795e-07)};
+const __plant_typet __char_poly_const[5][5] = 
+ {{ 1,  0,  0,  0,  0},
+{ -3.552073e+00,  1.578795e-07,  1.924160e-05,  8.644217e-04,  6.190044e-03},
+{ 4.702000e+00,  1.570568e-06,  4.855536e-05,  -1.001009e-03,  -1.857082e-02},
+{ -2.746737e+00,  1.416656e-06,  -5.293103e-05,  -5.912467e-04,  1.857149e-02},
+{ 5.968238e-01,  1.158396e-07,  -1.486592e-05,  7.278342e-04,  -6.190719e-03}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 benchmarks/matlab/headerfiles/tapedriver/tapedriver_ss_disc2.h

@@ -1,0 +1,25 @@
+#ifndef BENCHMARK_H_ 
+#define BENCHMARK_H_ 
+
+// time discretisation 0.050  
+#ifndef INT_BITS 
+#define INT_BITS 8
+#define FRAC_BITS 8
+#endif
+#define NSTATES 3 
+#include "control_types.h"
+#define NINPUTS 1 
+#define NOUTPUTS 1
+#define INPUT_UPPERBOUND (__plant_precisiont)10000
+#define INPUT_LOWERBOUND (__plant_precisiont)-10000
+const __plant_typet _controller_A[NSTATES][NSTATES] = {{ interval(5.490058e-09),  interval(8.317668e-09),  interval(5.773992e-09)},
+{ interval(-1.291620e-08),  interval(-1.670966e-08),  interval(-8.000363e-09)},
+{ interval(8.948255e-09),  interval(8.921712e-09),  interval(3.577775e-10)}};
+const __plant_typet _controller_B[NSTATES] = {interval(-1.009078e-10), interval(1.398165e-10), interval(1.747627e-02)};
+const __plant_typet __char_poly_const[4][4] = 
+ {{ 1,  0,  0,  0},
+{ 1.086183e-08,  1.747627e-02,  1.398165e-10,  -1.009078e-10},
+{ 3.139133e-17,  1.960768e-10,  -1.398165e-10,  1.009078e-10},
+{ -6.070745e-39,  2.743016e-19,  -5.357453e-19,  5.231888e-19}};
+
+#endif /*BENCHMARK_H_*/

### 2019-01-24 automatica/paper.tex
new template

@@
-% autosam.tex
-% Annotated sample file for the preparation of LaTeX files
-% for the final versions of papers submitted to or accepted for 
-% publication in AUTOMATICA.
-
-% See also the Information for Authors.
-
-% Make sure that the zip file that you send contains all the 
-% files, including the files for the figures and the bib file.
-
-% Output produced with the elsart style file does not imitate the
-% AUTOMATICA style. The style file is generic for all Elsevier
-% journals and the output is laid out for easy copy editing. The
-% final document is produced from the source file in the
-% AUTOMATICA style at Elsevier.
-
-% You may use the style file autart.cls to obtain a two-column 
-% document (see below) that more or less imitates the printed 
-% Automatica style. This may helpful to improve the formatting 
-% of the equations, tables and figures, and also serves to check 
-% whether the paper satisfies the length requirements.
-
-% Please note: Authors must not create their own macros.
-
-% For further information regarding the preparation of LaTeX files 
-% for Elsevier, please refer to the "Full Instructions to Authors" 
-% from Elsevier's anonymous ftp server on ftp.elsevier.nl in the
-% directory pub/styles, or from the internet (CTAN sites) on
-% ftp.shsu.edu, ftp.dante.de and ftp.tex.ac.uk in the directory
-% tex-archive/macros/latex/contrib/supported/elsevier.
-
-%\documentclass{elsart}               % The use of LaTeX2e is preferred.
-
-\documentclass[twocolumn]{autart}    % Enable this line and disable the 
-                                     % preceding line to obtain a two-column 
-                                     % document whose style resembles the
-                                     % printed Automatica style.
+%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% This is a general template file for the LaTeX package SVJour3
+% for Springer journals.          Springer Heidelberg 2010/09/16
+%
+% Copy it to a new file with a new name and use it as the basis
+% for your article. Delete % signs as needed.
+%
+% This template includes a few options for different layouts and
+% content for various journals. Please consult a previous issue of
+% your journal as needed.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% First comes an example EPS file -- just ignore it and
+% proceed on the \documentclass line
+% your LaTeX will extract the file if required
+\begin{filecontents*}{example.eps}
+%!PS-Adobe-3.0 EPSF-3.0
+%%BoundingBox: 19 19 221 221
+%%CreationDate: Mon Sep 29 1997
+%%Creator: programmed by hand (JK)
+%%EndComments
+gsave
+newpath
+  20 20 moveto
+  20 220 lineto
+  220 220 lineto
+  220 20 lineto
+closepath
+2 setlinewidth
+gsave
+  .4 setgray fill
+grestore
+stroke
+grestore
+\end{filecontents*}
+%
+\RequirePackage{fix-cm}
+%
+%\documentclass{svjour3}                     % onecolumn (standard format)
+%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
+\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+%\documentclass[twocolumn]{svjour3}          % twocolumn
+%
+\smartqed  % flush right qed marks, e.g. at end of proof
+%
 
@@
 \newcommand{\comment}[1]{}
-\newtheorem{lemma}{Lemma}
-\newtheorem{theorem}{Theorem}
-\newtheorem{corollary}{Corollary}
-\newtheorem{proof}{Proof}
+%\newtheorem{lemma}{Lemma}
+%\newtheorem{theorem}{Theorem}
+%\newtheorem{corollary}{Corollary}
+%\newtheorem{proof}{Proof}
 
@@
 \newcommand\tool{{\sf DSSynth}}
-\begin{frontmatter}
 
@@
 
-%\thanks[footnoteinfo]{This paper was not presented at any IFAC 
-%meeting. Corresponding author M.~T.~Cicero. Tel. +XXXIX-VI-mmmxxi. 
-%Fax +XXXIX-VI-mmmxxv.}
-
-\author[oxford]{Alessandro Abate}\ead{alessandro.abate@cs.ox.ac.uk},
-\author[manaus]{Iury Bessa}\ead{iurybessa@ufam.edu.br},
-\author[oxford]{Dario Cattaruzza}\ead{dario.cattaruzza@cs.ox.ac.uk},
-\author[manchester]{Lucas Cordeiro}\ead{lucas.cordeiro@manchester.ac.uk},
-\author[cambridge]{Cristina David}\ead{cd652@cam.ac.uk},
-\author[oxford]{Pascal Kessel}\ead{pascal.kesseli@cs.ox.ac.uk},
-\author[oxford]{Daniel Kroening}\ead{kroening@cs.ox.ac.uk},
-\author[oxford]{Elizabeth Polgreen}\ead{elizabeth.polgreen@cs.ox.ac.uk}
-
-\address[oxford]{University of Oxford, UK}
-\address[cambridge]{University of Cambridge, UK}
-\address[manchester]{University of Manchester, UK}
-\address[manaus]{Federal University of Amazonas, Brazil}
-
-\begin{keyword}                           % Five to ten keywords,  
-Digital control synthesis; Safety requirements; Analog/Digital conversion; Quantization errors; Time sampling.               % chosen from the IFAC 
-\end{keyword}                             % keyword list or with the 
+\author{Alessandro Abate         \and
+        Iury Bessa \and
+        Dario Cattaruzza \and
+        Lucas Cordeiro \and
+        Cristina David \and
+        Pascal Kesseli \and
+        Daniel Kroening \and
+        Elizabeth Polgreen
+}
+
+\authorrunning{Abate et al.} % if too long for running head
+
+%\institute{F. Author \at
+%              first address \\
+%
+%              \email{fauthor@example.com}           %  \\
+%%             \emph{Present address:} of F. Author  %  if needed
+%           \and
+%           S. Author \at
+%              second address
+%}
+
+\maketitle
+%\author[oxford]{Alessandro Abate}\ead{alessandro.abate@cs.ox.ac.uk},
+%\author[manaus]{Iury Bessa}\ead{iurybessa@ufam.edu.br},
+%\author[oxford]{Dario Cattaruzza}\ead{dario.cattaruzza@cs.ox.ac.uk},
+%\author[manchester]{Lucas Cordeiro}\ead{lucas.cordeiro@manchester.ac.uk},
+%\author[cambridge]{Cristina David}\ead{cd652@cam.ac.uk},
+%\author[oxford]{Pascal Kessel}\ead{pascal.kesseli@cs.ox.ac.uk},
+%\author[oxford]{Daniel Kroening}\ead{kroening@cs.ox.ac.uk},
+%\author[oxford]{Elizabeth Polgreen}\ead{elizabeth.polgreen@cs.ox.ac.uk}
+%
+%\address[oxford]{University of Oxford, UK}
+%\address[cambridge]{University of Cambridge, UK}
+%\address[manchester]{University of Manchester, UK}
+%\address[manaus]{Federal University of Amazonas, Brazil}
+
+\keywords{                        % Five to ten keywords,  
+Digital control synthesis \and Safety requirements \and Analog/Digital conversion \and Quantization errors \and Time sampling              % chosen from the IFAC 
+}                            % keyword list or with the 
                                           % help of the Automatica 
@@
 \end{abstract}
-
-\end{frontmatter}
 
@@
 
-\bibliographystyle{plain}        % Include this if you use bibtex 
+\bibliographystyle{spbasic}       % Include this if you use bibtex 
 \bibliography{paper}           % and a bib file to produce the 

### 2019-01-24 automatica/paper.tex
section 1

@@
 \title{Automated Formal Synthesis\\ 
-of Safe Digital Controllers 
+of Provably Safe Digital Controllers 
 for Continuous Plants}
@@
 We present a sound and automated approach to synthesizing safe,
-digital controllers for physical plants represented as linear,
-time-invariant models. Models are defined as differential equations
-with inputs, evolving over a continuous state space. The synthesis
-accounts for errors caused by the digitization effects introduced by
-the controller. Our approach uses counterexample-guided inductive
-synthesis (CEGIS): an inductive generalization phase produces a
-possible solution that is known to stabilize the system but that may
-not be safe for all initial conditions. 
+digital controllers for physical plants represented as time-invariant models. 
+Models are linear differential equations with inputs, evolving over a continuous state space. 
+The synthesis accounts for errors caused by the digitization effects introduced by the controller. 
+The approach uses counterexample-guided inductive synthesis (CEGIS): 
+an inductive generalization phase produces a controller that is known to stabilize the system but that may
+not be safe for all initial conditions of the model.  
 \ifx\axelerator
@@
 \else
-Safety is then verified via Bounded Model Checking;
+Safety is then verified via Bounded Model Checking: 
 \fi 
-if the verification step fails, a
-counterexample is provided to the inductive generalization and the
-process iterates until a safe controller is obtained.  We demonstrate
-the practical value of this approach by automatically synthesizing
-safe controllers for physical plant models from the digital control
-literature.
+if the verification step fails, 
+a counterexample is provided to the inductive generalization and the process iterates until a safe controller is obtained.  
+We demonstrate the practical value of this approach by automatically synthesizing safe controllers for physical plant models from the digital control literature.
 \end{abstract}
@@
 non-trivial control tasks, with significant impact in numerous
-application areas such as the life sciences, high-precision control, 
+application areas such as process and industrial engineering, high-precision control, 
 automotive and robotics~\cite{astrom1997computer, Franklin15}.  
-Provably correct synthesis of control software for such platforms is non-trivial, 
-even in cases with unsophisticated dynamics.
-
-In this paper, we examine the case of Linear Time Invariant (LTI)
-models, for which the synthesis of controllers is well understood.
+However, provably correct synthesis of control software for such platforms, 
+needed if certification is in order, is non-trivial even in cases with unsophisticated dynamics.
+
+In this paper, we examine the case of physical systems (plants) described mathematically as 
+Linear Time Invariant (LTI) models, for which the classical synthesis of controllers is well understood.
 However, the use of digital control architectures adds new challenges
@@
 Given an LTI model, we develop an automatic technique for generating
-correct-by-construction digital controllers that addresses all these
-challenges. Specifically, we automatically synthesize %stable and 
+correct-by-design digital controllers that addresses these challenges. 
+Specifically, we automatically synthesize %stable and 
 safe,
-software-implemented embedded controllers.  
+software-implemented embedded controllers for physical plants.   
 %Due to the complexity of
@@
 
-Our work addresses challenging aspects of the control synthesis problem:  
-we perform digital control synthesis over a ``hybrid model'',
+Our work addresses challenging aspects of control synthesis:  
+we perform automated control synthesis over a ``hybrid model'', 
 namely a model encompassing a plant exhibiting continuous behavior, 
@@
 In particular, our model evaluates the effects of the quantizers (A/D and D/A
-converters), as well as representation
-errors introduced by the controller working  %% artifacts such as an
+converters), as well as representation errors introduced by the controller working  %% artifacts such as an
 %% observer~\cite{astrom1997computer}
 in a finite-precision domain. Our model also accounts for representation errors introduced
-by our modelling of the plant using finite precision arithmetic. 
-We reason about safety requirements, which are frequently overlooked in conventional feedback control synthesis, but
-play a key role in systems engineering, particularly for safety-critical applications of clear concern in modern autonomy contexts.
+by our modelling of the plant using finite-precision arithmetic. 
+We reason about safety requirements, which are frequently overlooked in conventional feedback control synthesis, 
+but which nevertheless play a key role in safety-critical applications, of clear concern in numerous modern contexts, 
+e.g. autonomy in robotics, avionics, and automotive.
 
@@
 \else
-In this paper we present a novel approach for the synthesis of digital controllers,
-making 
+We present a novel approach for the synthesis of digital controllers making 
 \fi
-use of the framework known as counterexample guided
+use of a recently investigated framework known as counterexample-guided
 inductive synthesis (CEGIS)~\cite{jha-icse10, 
@@
   a technique from formal methods that has recently shown much promise and which we 
-  export in this work to a control-theoretical setup.  
+  export in this work to a control engineering setup.  
 CEGIS is an iterative process, where each iteration performs inductive

### 2019-01-24 automatica/paper.tex
section 1

@@
 use of a recently investigated framework known as counterexample-guided 
-inductive synthesis (CEGIS)~\cite{jha-icse10, 
-  DBLP:conf/asplos/Solar-LezamaTBSS06}, 
+inductive synthesis (CEGIS)~\cite{jha-icse10, DBLP:conf/asplos/Solar-LezamaTBSS06},  
 a technique from formal methods that has recently shown much promise and which we 
@@
 about a limited number of inputs to compute a candidate solution
-for the entire range of possible inputs. Our two instantiations of CEGIS are described next.
+for the entire range of possible inputs. 
+%Our two instantiations of CEGIS are described next.
 
@@
 \fi
-uses a multi-staged technique that starts by devising a
+uses a multi-staged \note{we should state what we mean by `stage' in multi-stage?} technique that starts by devising a
 digital controller that stabilizes the plant model while remaining safe for a
@@
 full set of initial states, and checking a \emph{completeness
-threshold}~\cite{DBLP:conf/vmcai/KroeningS03}, i.e., the number of
-iterations required to sufficiently unwind the closed-loop state-space
-model such that the safety boundaries are not violated for any larger number of
-iterations.
+threshold}~\cite{DBLP:conf/vmcai/KroeningS03}, i.e., 
+the number of iterations\note{stages?} required to sufficiently unwind the closed-loop model, 
+such that the safety boundaries are not violated for any larger number of iterations.  
+\note{we do not state the contribution about errors - this should be briefly mentioned here, before the item below. }
 
@@
   their effect on safety.  We provide bounds that ensure the
-  safety of our controllers in a hybrid (i.e., continuous/digital) domain.
+  safety of our controllers in a hybrid (i.e., continuous/digital) domain \note{keep? needed?}.
 
@@
 for the synthesis of switching controllers for stabilizing continuous-time
-plants with polynomial dynamics.  The work extends to affine systems, but is
+plants with polynomial dynamics.  The work extends to affine systems \note{extension or restriction?}, but is
 limited by the capacity of the state-of-the-art SMT solvers for solving
@@
 However, both approaches are unsuitable for the kind of controllers that we seek to
-synthesize.
+synthesize \note{why?}.
 
@@
 While this work also uses CEGIS, the approach is restricted to digital
-controllers for stable closed-loop systems given as transfer function
+controllers for stable closed-loop systems expressed as transfer function
 models: this results in a static check on their coefficients.  By contrast,
@@
 traces of the model, alongside the numerical soundness required by the
-effects of discretisation and finite-precision errors.
+effects of discretisation and the errors related to finite-precision arithmetic.
 
@@
 which is by and large overlooked in the standard (digital) control literature, 
-by default focussed on stability properties.  
+by default focussed on stability/regulation/tracking properties.  
 Moreover, our work integrates an abstraction-refinement (CEGAR) step inside the main CEGIS loop.
 
-The technique underpinning tools such as Pessoa~\cite{mazo2010pessoa}, related extensions \cite{Anta2010,liu16}, and applications \cite{zamani2014}
+The technique underpinning tools such as Pessoa~\cite{mazo2010pessoa}, related extensions \cite{Anta2010,liu16} and applications \cite{zamani2014}
 synthesizes correct-by-design embedded control software for LTI models.    
-It is based on the abstraction of the model to a finite-state machine, 
+It is based on the abstraction of the model as a finite-state machine, 
 and on the formal control synthesis over safety- and reachability-based temporal properties thereon.  
@@
 including delayed response~\cite{Duggirala2015} and finite-precision arithmetic, 
-with the goal either to verify~\cite{daes20161} the correctness of the implementation or to optimize~\cite{oudjida2014design} the design.
+with the goal either to verify~\cite{daes20161} the correctness of the implementation or to optimize~\cite{oudjida2014design} its design.
 
@@
 \cite{DBLP:journals/automatica/WuLCC09} uses $\mu$-calculus to directly model the digital controller so that selected
-parameters result by design in stable dynamics.  
+parameters result by design in stable dynamics \note{unclear}.  
 The analyses in~\cite{DBLP:conf/hybrid/RouxJG15, DBLP:conf/hybrid/WangGRJF16} rely on an
@@
 %This technique works for both linear and non-linear systems.
-
-%\note{Add note explaining relationship of this work with previously published papers. }
+\note{Add note explaining relationship of this work with previously published reviewed literature?}
 

### 2019-01-25 automatica/paper.tex
affiliations
overall paper

@@
 
-\title{Automated Formal Synthesis\\ 
+\title{Automated Formal Synthesis 
 of Provably Safe Digital Controllers 
@@
 
-%\institute{F. Author \at
-%              first address \\
+\institute{A. Abate \at
+              University of Oxford
+              \and
+              I. Bessa \at University of Manaus
+              \and
+              L. Cordeiro \at University of Manchester
+              \and
+              C. David \at University of Cambridge
+              \and
+              P. Kesseli \at DiffBlue 
+              \and
+              D. Kroening \at University of Oxford
+              \and
+              E. Polgreen \at University of Oxford 
+}
+
 %
@@
 \keywords{                        % Five to ten keywords,  
-Digital control synthesis \and Safety requirements \and Analog/Digital conversion \and Quantization errors \and Time sampling              % chosen from the IFAC 
+Formal Verification \and Safety requirements \and Dynamical models \and Digital control synthesis \and Analog/Digital conversion \and Time sampling \and Quantization errors \\
+            % chosen from the IFAC 
 }                            % keyword list or with the 
@@
 
-In this paper, we examine the case of physical systems (plants) described mathematically as 
+In this paper, we examine the case of physical systems (a.k.a. plants in control literature) described mathematically as 
 Linear Time Invariant (LTI) models, for which the classical synthesis of controllers is well understood.
@@
 Our work addresses challenging aspects of control synthesis:  
-we perform automated control synthesis over a ``hybrid model'', 
-namely a model encompassing a plant exhibiting continuous behavior, 
+we perform automated control synthesis over a model encompassing both a plant exhibiting continuous behavior  
 and a controller operating in discrete time and over a quantized domain.  
@@
 \else
-We present a novel approach for the synthesis of digital controllers making 
+We further present a novel approach for the synthesis of digital controllers making 
 \fi
@@
 \fi
-uses a multi-staged \note{we should state what we mean by `stage' in multi-stage?} technique that starts by devising a
+uses a multi-staged technique that starts by devising a
 digital controller that stabilizes the plant model while remaining safe for a
@@
 threshold}~\cite{DBLP:conf/vmcai/KroeningS03}, i.e., 
-the number of iterations\note{stages?} required to sufficiently unwind the closed-loop model, 
+the number of stages required to sufficiently unwind the closed-loop model, 
 such that the safety boundaries are not violated for any larger number of iterations.
-\note{we do not state the contribution about errors - this should be briefly mentioned here, before the item below. }
 
@@
 This paper is an extension of~\cite{DBLP:conf/cav/AbateBCCDKKP17}
-and makes the following contributions (the fourth is a 
-specific extension to~\cite{DBLP:conf/cav/AbateBCCDKKP17}): 
+and puts forward the following contributions: 
+% (the fourth is a  specific extension to~\cite{DBLP:conf/cav/AbateBCCDKKP17}): 
 %
@@
   the physical system. Such a representation requires ensuring the
-  specification over actual traces of the model, alongside the
+  specification over actual traces of the state-space model, alongside the
   numerical soundness required by the effects of discretisation and
@@
 \item We present a novel multi-staged approach to synthesizing digital controllers, using 
-  an unfolding of the dynamics up to a completeness threshold, and bit precise Bounded Model
-  Checking to account for fixed-point arithmetic used in the implementation of the digital control algorithm
+  an unfolding of the dynamics up to a completeness threshold. 
+  We employ bit-precise Bounded Model Checking to account for fixed-point arithmetic used in the implementation of the digital control algorithm, 
   and interval arithmetic to account for the imprecision in the modelling of the plant. 
@@
   their effect on safety.  We provide bounds that ensure the 
-  safety of our controllers in a hybrid (i.e., continuous/digital) domain \note{keep? needed?}.
+  safety of our controllers in a hybrid (i.e., continuous/digital) domain. \note{is this point repeating the previous one?}
 
@@
 
-Program synthesizers are an ideal fit for the synthesis of digital controllers, since
-the semantics of programs precisely capture the effects of finite-precision arithmetic.  
-In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS 
-for the synthesis of switching controllers for stabilizing continuous-time
-plants with polynomial dynamics.  The work extends to affine systems \note{extension or restriction?}, but is
-limited by the capacity of the state-of-the-art SMT solvers for solving
-linear arithmetic.  Since this approach uses switching models instead of
-linear dynamics for the digital controller, it avoids problems related to
+Program synthesizers are an ideal fit for the synthesis of digital controllers, 
+since the semantics of programs precisely capture the effects of finite-precision arithmetic.  
+However the control literature has been oblivious to this relevant connection. 
+A relevant exception is~\cite{DBLP:conf/cdc/RavanbakhshS15}, 
+which employs CEGIS for the synthesis of switching controllers for stabilizing continuous-time
+plants.  
+%with polynomial dynamics.  
+The work 
+% extends to affine systems \note{extension or restriction?}, but 
+is limited by the capacity of the state-of-the-art SMT solvers for solving
+linear arithmetic.  Since this approach uses switching actions for the digital controller, it avoids problems related to
 finite precision arithmetic, but potentially suffers from state-space
@@
 However, both approaches are unsuitable for the kind of controllers that we seek to
-synthesize \note{why?}.
+synthesize, which are not switching in nature.
 
@@
 
-The technique underpinning tools such as Pessoa~\cite{mazo2010pessoa}, related extensions \cite{Anta2010,liu16} and applications \cite{zamani2014}
-synthesizes correct-by-design embedded control software for LTI models.    
-It is based on the abstraction of the model as a finite-state machine, 
+Beyond CEGIS-based architectures, 
+there is an important line of research on provably correct control synthesis for dynamical models, 
+which leverages formal abstractions. 
+The approach underpinning tools such as Pessoa~\cite{mazo2010pessoa}, related extensions \cite{Anta2010,liu16} and applications \cite{zamani2014} 
+synthesizes correct-by-design embedded control software by abstraction of the model as a finite-state machine, 
 and on the formal control synthesis over safety- and reachability-based temporal properties thereon.  
@@
 %properties.  
-The controller software can then be implemented over the concrete LTI model. 
+The obtained finite controller software can then be implemented over the concrete LTI model. 
 %can be more complicated than
 %the state-feedback control we synthesize, and the properties available cover more detail.  
-However, relying on state-space discretization, \mbox{Pessoa} is likely to incur scalability limitations.   
+However, relying on state-space discretization, this set of approaches is likely to incur scalability limitations.   
 %Along this research line, \cite{Anta2010,liu16} studies the synthesis of digital controllers for
 %continuous dynamics, and \cite{zamani2014} extends the approach to the Network Control Systems setup.
+
+\medskip
 
@@
 }
- \caption{Closed-loop digital control system 
+ \caption{Closed-loop digital control setup: 
+ the plant is intended to be an analogue model of the underlying real system, 
+ whereas the controller is digital. 
  \label{fig:digitalsystem}}
@@
 $k \in \mathbb N$ is a discrete counter and where $\vec{x}_{0}=\vec{x}(0)$ denotes the initial state. 
+\note{shall we add a note on time discretization errors? namely that we disregard them? }
 
@@
 Feedback architectures can be employed to manipulate properties and behaviors of the plant:    
-we are interested in the synthesis of digital feedback controllers $u_k$,  
-as practically implemented on Field-Programmable Gate Arrays or Digital Signal Processors,  
+we are interested in the synthesis of digital feedback controllers $u_k$, as in Fig. \ref{fig:digitalsystem},  
+as practically implemented on Field-Programmable Gate Arrays or Digital Signal Processors   
 %This requires us to consider the errors introduced by, we will address the issue of variable quantization, 
@@
 
-\note{Ref to Fig. \ref{fig:digitalsystem} anywhere?. That figure is referred to in the section on errors. I think it is confusing to
-refer to it before we have explained the DAC, ADC and the errors shown in the figure.}
-
-\subsection{Stability of closed-loop systems}
+\subsection{Stability of closed-loop models}
 
 In this work we employ the notion of asymptotic stability within the CEGIS loop,  
-as a means for reducing the search space of possible safe controllers, where the definition of a safe controller
+as a means for reducing the search space of possible safe controllers, where the notion of a safe controller
 is defined in the following section. 
@@
 
-\subsection{Safety of closed-loop systems}
+\subsection{Safety of closed-loop models}
 \label{sec:safety}
@@
 \centering
-\resizebox{.48\textwidth}{!}{
+\resizebox{.8\textwidth}{!}{
  \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto,
@@
 }
- \caption{The CEGIS framework\label{fig:CEGIS}}
+ \caption{The general CEGIS framework\label{fig:CEGIS}}
 \end{figure}
@@
 }
-We encompass this error using interval arithmetic~\cite{moore1966interval} in the verification phase \note{this statement might also need more details}.
+We encompass this error using interval arithmetic~\cite{moore1966interval} in the verification phase \note{please add more details here}.
 
@@
 we describe in detail the different phases in Fig.~\ref{fig:CEGIS-precision-increment} (shaded blocks 1 to 4).
+
+\note{Please turn itemisation below into sub(sub?)sections.}
 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{figures/synthesis-flow.pdf}
+\includegraphics[width=0.9\textwidth]{figures/synthesis-flow.pdf}
 \caption{Phases of the controller synthesis}

### 2019-01-25 automatica/paper.tex
sections

@@
 
-\institute{A. Abate \at
-              University of Oxford
-              \and
-              I. Bessa \at University of Manaus
-              \and
-              L. Cordeiro \at University of Manchester
-              \and
-              C. David \at University of Cambridge
-              \and
-              P. Kesseli \at DiffBlue 
-              \and
-              D. Kroening \at University of Oxford
-              \and
-              E. Polgreen \at University of Oxford 
-}
+\institute{}
+%A. Abate \at
+%              University of Oxford
+%              \and
+%              I. Bessa \at University of Manaus
+%              \and
+%              L. Cordeiro \at University of Manchester
+%              \and
+%              C. David \at University of Cambridge
+%              \and
+%              P. Kesseli \at DiffBlue 
+%              \and
+%              D. Kroening \at University of Oxford
+%              \and
+%              E. Polgreen \at University of Oxford 
+%}
 
@@
 %the state-feedback control we synthesize, and the properties available cover more detail.  
-However, relying on state-space discretization, this set of approaches is likely to incur scalability limitations.   
+However, relying on state-space discretization, this class of approaches is likely to incur scalability limitations.   
 %Along this research line, \cite{Anta2010,liu16} studies the synthesis of digital controllers for
@@
 \textbf{Discretization Effects in Control Design --}
-Classical work in control synthesis has often disregarded digitalization effects.
-Recent results in digital control, however, have focused on separate aspects of discretization, 
-including delayed response~\cite{Duggirala2015} and finite-precision arithmetic, 
+%Classical work in control synthesis has often disregarded digitalization effects.
+Recent results in digital control have focused on separate aspects of discretization, 
+e.g. delayed response~\cite{Duggirala2015} and finite-precision arithmetic, 
 with the goal either to verify~\cite{daes20161} the correctness of the implementation or to optimize~\cite{oudjida2014design} its design.
 
-There are two different problems that arise from finite-precision arithmetic in digital controllers.  The first
-is the error caused by the inability to represent the exact
-state of the physical system, while the second relates to rounding and
-saturation errors during mathematical operations.  
+There are two different problems that arise from finite-precision arithmetic in digital controllers.  
+The first is the error caused by the inability to represent the exact state of the physical system, 
+while the second relates to rounding and saturation errors during mathematical operations.  
 In~\cite{fialho1994stability}, a stability measure based on the error of the digital dynamics ensures that
 the deviation introduced by finite-precision arithmetic does not lead to instability.  
-\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$-calculus to directly model the digital controller so that selected
-parameters result by design in stable dynamics \note{unclear}.  
+\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$-calculus to synthesise directly a digital controller, 
+so that selected parameters result in stable model dynamics.  
 The analyses in~\cite{DBLP:conf/hybrid/RouxJG15, DBLP:conf/hybrid/WangGRJF16} rely on an
 invariant computation on the discrete dynamics using Semi-Definite
-Programming (SDP):  while the former contribution uses bounded-input and bounded-output
-(BIBO) properties to determine stability, the latter uses Lyapunov-based
+Programming (SDP):  while the former contribution a uses bounded-input and bounded-output
+(BIBO) notion of stability, the latter employs Lyapunov-based
 quadratic invariants.  In both cases, the SDP solver uses floating-point
-arithmetic and soundness is checked by bounding the error.  
+arithmetic and soundness is checked by bounding the obtained error.  
 An alternative is~\cite{park2016scalable}, where the verification of given control code is
-performed against a known model by extracting an LTI model of the code by
-symbolic execution: to account for rounding errors, an upper bound is
+performed against a known model by extracting an LTI model of the code via 
+symbolic execution: to account for rounding errors, upper bounds of their values are 
 introduced in the verification phase.  
@@
 \cite{liberzon2003hybrid} evaluates the quantization error dynamics and calculates an upper and lower
-bound for the possible trajectory of the system up to a finite time. 
+bound for the possible trajectory of the system, up to a finite time. 
+The last two approaches can be placed within the research area known as ``hybrid systems theory.''  
 %This technique works for both linear and non-linear systems.
-\note{Add note explaining relationship of this work with previously published reviewed literature?}
+The present contribution distances itself from all these cognate results.
 
@@
 meets a given safety specification.  
-A safety specification gives rise to a requirement on the states of the model, such
-that the feedback controller (namely the choice of the gain matrix~$K$)
+A safety specification gives rise to a requirement on the states of the model, 
+namely that they remain within the safe set at all times (that is, over an infinite number of time steps).  
+So the feedback controller (namely the choice of the gain matrix~$K$)
 must ensure that the state never violates the requirement.  Note that an asymptotically 
@@
 
-Furthermore, it is practically relevant to consider the 
+\medskip
+
+Beyond the main requirement on safety, it is practically relevant to consider the 
 constraints $\phi_\mathit{input}$ on the input
@@
 We employ the bounded model checker CBMC~\cite{DBLP:conf/tacas/KroeningT14} to model the controller behavior on digital signals with finite bit-precision.  
-We express the controller semantics as C programs, which is CBMC's preferable input language.  
+We express the controller semantics as C programs, which is CBMC's preferred input language.  
 CBMC symbolically executes every instruction in an input program by translating it to a boolean satisfiability problem,
@@
 Details of how we model this arithmetic are in Section~\ref{sec:numeric_rep}. 
-\note{[rephrase?] These errors are present in the real world}, and we must model them accurately in order to capture the full behaviour of the model:
+\note{[rephrase?] These errors are present in the real world [as opposed to being absent? vacuous statement?]}, and we must model them accurately in order to capture the full behaviour of the model:
 
@@
 Again, this assumption is practically reasonable. 
-As a result we can ignore any additional errors introduced by the DAC. 
-It would, however, be straightforward to account for a DAC or ADC of different precision to the controller in our algorithm, if necessary. 
+As a result we can ignore possible additional errors introduced by the DAC. 
+It would, however, be straightforward to account for a DAC or ADC of different precision than the controller in our algorithm, if necessary. 
 \end{itemize}
 
-\note{[shouldn't this be a bullet point too?] It can't be in the previous list though because ti isn't an error introduced by the nature of digital control and that we need to model, it is an error introduced *by* our modelling}
+We furthermore encompass the following error that is due to modelling (as opposed to the nature of the digital control).  
+\begin{itemize} 
+\item
 The representations used in the plant model and its arithmetic operations are also carried out at a finite precision, 
@@
 We guarantee that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller and we use interval arithmetic to bound the errors, as detailed in Section~\ref{sec:numeric_rep}.
+\end{itemize}
 
@@
 \end{equation*}
-\note{clarify degree $N$ vs model dimensions} 
-An closed-loop LTI model is stable~\cite{astrom1997computer} \note{asymptotically?} if \note{make sure: only sufficient condition?}all the roots of its characteristic polynomial $S(z)$ (i.e., the 
+Here $N$ corresponds to the dimensions of the state variables (above $n$ ). 
+A sufficient condition for asymptotic stability of the closed-loop LTI model~\cite{astrom1997computer} 
+is when all the roots of its characteristic polynomial $S(z)$ (which correspond to the 
 eigenvalues of the matrix $A_d-B_dK$) are inside the unit circle in the complex plane, 
@@
 
-The \note{asympt?} stability property is finally encoded by a constraint expressed as the following formula: 
+In conclusion, 
+the asymptotic stability property is finally encoded by a constraint expressed as the following formula: 
 $

### 2019-01-25 automatica/paper.tex
sections

@@
 and we use the Boost interval arithmetic library~\cite{DBLP:journals/tcs/BronnimannMP06} to bound the error in this representation. 
-We employ a compositional numeric library to model the fixed point arithmetic for the controller~\cite{CNL} within double-precision floating-point numbers. 
+We employ a compositional numerical library to model the fixed point arithmetic for the controller~\cite{CNL} within double-precision floating-point numbers. 
 We check that the controller is safe starting from each vertex of the set of initial states,  
-and show that this is sufficient to prove safety from any state in this set.
+and show that this is sufficient to prove safety from any state in this set. \note{add forward reference to proof.}
 
@@
 
-The fixed-point arithmetic of the digital controller is performed on the upper and lower bound of the intervals independently and the upper and lower bound of the result taken as the interval result\note{Would an example make this clearer?, e.g., consider the conversion from plant precision to controller precision performed by the ADC on a single state value.
+The fixed-point arithmetic of the digital controller is performed on the upper and lower bound of the intervals from above independently, [I DO NOT UNDERSTAND THE REMAINING PART OF THE SENTENCE.] and the upper and lower bound of the result taken as the interval result\note{Would an example make this clearer?, e.g., consider the conversion from plant precision to controller precision performed by the ADC on a single state value.
 The state value is represented as an interval $\{x.high, x.low\}$, and the result of the conversion is an interval where the upper bound is the conversion of $x.high$ and the lower bound is the conversion of $x.low$?}.
@@
 }
-We encompass this error using interval arithmetic~\cite{moore1966interval} in the verification phase \note{please add more details here}.
+We encompass this error using interval arithmetic~\cite{moore1966interval} in the verification phase \note{please add more details here on the ``verification phase''}.
 
@@
 \begin{align*}
-x_{k+1} &= A_d \cdot x_{k} -B_d(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  \\
+x_{k+1} &= A_d \cdot x_{k} -B_d(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  
+\end{align*}
+This translates to 
+\begin{align*}
 x_{k+1} &= (A_d  - B_dK) \cdot x_k + B_dK\delta, 
@@
 
-\note{Please turn itemisation below into sub(sub?)sections.}
-
 %\note{we need to refer to the parts of Algorithm 1 more closely - point to specific lines in the explanation below.}
@@
 %\todo{please eventually itemize next}
-\begin{enumerate}
-
-\item The inductive synthesis phase ({\sc synthesize}) uses BMC to compute a
+\subsubsection{Block 1}
+
+The inductive synthesis phase ({\sc synthesize}) uses BMC to compute a
 candidate solution $K$ that satisfies both the stability requirement and the safety specification, 
@@
 
-\item The first {\sc verify} stage, {\sc safety} is shown in Alg.~\ref{alg:safetycheck}. 
+\subsubsection{Block 2}
+
+The first {\sc verify} stage, {\sc safety} is shown in Alg.~\ref{alg:safetycheck}. 
 The algorithm checks that the candidate
@@
 
-\item The second {\sc verify} stage, {\sc precision}, 
+\subsubsection{Block 3}
+
+The second {\sc verify} stage, {\sc precision}, 
  restores soundness with respect to the plant precision
@@
 
-\item The third {\sc verify} stage, {\sc complete}, checks that the current
+\subsubsection{Block 4}
+
+The third {\sc verify} stage, {\sc complete}, checks that the current
 $k$ is large enough to ensure safety for any further time steps.  
@@
 \end{proof}
-
-\end{enumerate}
 
@@
 %-------------------------------
-\section{DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants}
+\section{DSSynth: A Software Tool for Automated Digital Controller Synthesis over Physical Plants}
 \label{sec:dssynthtool}

### 2019-01-26 automatica/paper.tex
sections

@@
 in view of its efficiency and ease of integration within our implementation.  
-This method checks the stability working in the complex domain of the characteristic polynomial $S(z)$ \note{could be better and formally introduced in earlier section?},  
+This method checks the stability working in the complex domain of the characteristic polynomial $S(z)$,  
 %
@@
 \end{equation*}
-Here $N$ corresponds to the dimensions of the state variables (above $n$ ). 
+This polynomial is obtained as a function of the state-space matrices $A,B$~\cite{Astrom08}, 
+and in particular its order $N$ corresponds to the dimensions of the state variables (above $n$).  
 A sufficient condition for asymptotic stability of the closed-loop LTI model~\cite{astrom1997computer} 
@@
 
-We have that $S(z)$ is the characteristic polynomial of a stable system if and only if the following four conditions $R_i, i = 1,2,3,4,$ hold~\cite{astrom1997computer}:
+We have that $S(z)$ is the characteristic polynomial of an asymptotically stable system if and only if the following four conditions $R_i, i = 1,2,3,4,$ hold~\cite{astrom1997computer}: 
 %\begin{itemize}
@@
 the considered models must account for errors deriving from several sources: 
-we must bound the numerical error introduced by the finite-precision representation of the plant (and its operations), 
+we formally bound the numerical error introduced by the finite-precision representation of the plant (and its operations), 
 and precisely model the error introduced by the ADC/DAC conversions, 
@@
 
-We employ interval arithmetic to bound the error introduced by the finite-precision plant, 
-and bounded model checking to precisely model the error introduced by the ADC/DAC and the finite-precision controller.
+Technically, we employ interval arithmetic to bound the error introduced by the finite-precision plant, 
+and we use bounded model checking to precisely model the error introduced by the ADC/DAC and the finite-precision controller.
 
 \subsection{Bit-precise symbolic model checking}
-As described in section~\ref{sec:BMC}, we use CBMC, a bit-precise bounded model checker to synthesise and verify candidate controllers. 
+As described in Section~\ref{sec:BMC}, we use CBMC, a bit-precise bounded model checker to synthesise and verify candidate controllers. 
 CBMC manipulates precisely the fixed- or floating-point arithmetic used in the controller, 
@@
 
-\subsection{Interval arithmetic over errors in numeric representation} 
+\subsection{Interval arithmetic for errors in the numerical representation}
+
 We use finite-precision arithmetic to model the plant. 
@@
 however it necessitates a further stage where we verify that the errors introduced by the approximation have not resulted in a controller that is unsafe when executed on a plant expressed over real numbers.
-In this stage, we represent the plant using double-precision floating-point
+In this stage, we represent the plant using double-precision floating-point numbers 
 and we use the Boost interval arithmetic library~\cite{DBLP:journals/tcs/BronnimannMP06} to bound the error in this representation. 
@@
 closed-loop model.  The convergence to a finite value, however, will not
-make it asymptomatically stable.
+make it asymptotically stable.
 However,
@@
 An overview of the algorithm for controller synthesis is given in Figure~\ref{fig:CEGIS-precision-increment}.   
-One important point is that we formally synthesize a controller over a finite number ($k$) of time steps.  
+One important point is that we formally synthesize a controller over a finite number ($k$) of time steps (i.e., it is multi-stage).  
 We then compute a completeness threshold $\overline{k}$~\cite{DBLP:conf/vmcai/KroeningS03} for this controller, 
@@
 candidate solution $K$ that satisfies both the stability requirement and the safety specification, 
-within a finite precision model.  
+within a finite-precision model.  
 In order to synthesize a controller that satisfies the stability requirement, 
@@
 unfolding the transition system $k$ steps and by selecting a controller $K$ and a single initial state, 
-such that the states at each step do not violate the safety criteria (see Section~\ref{ssec:safespecification}).    
+such that the states at each step do not violate the safety criteria (see Section~\ref{ssec:safespecification} \note{fix}).    
 That is, we ask the bounded model checker~\cite{ClarkeKL04} if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states, and a given fixed point precision for the controller, and where the input signal remains within the specified bounds.
@@
 plant precision. A \emph{vertex state} is defined as a state where all values are either equal to the upper or lower
-bound of the initial states. It is sufficient to verify that the controller is safe for all vertex
-states, and the proof is shown later in this section. We thus only need to iterate through the $2^{n}$ vertex
-states, where $n$ is dimension of the state space (number of continuous variables).
+bound of the initial states. It is sufficient to verify that the controller is safe for all vertex states, as shown next. 
+%We thus only need to iterate through the $2^{n}$ vertex
+%states, where $n$ is dimension of the state space (number of continuous variables).
 
@@
 In conclusion, we only need to check $2^n$ initial states, 
-where $n$ is the dimension of the state space.
+where $n$ is the dimension of the state space (number of continuous variables).
 
@@
 \begin{theorem} There exists a finite $\overline{k}$ such that it is
-sufficient to unwind the closed-loop state-space system up to $\overline{k}$
+sufficient to unwind the closed-loop state-space model up to $\overline{k}$
 in order to ensure that $\phi_\mathit{safety}$ holds. 
@@
 %
-A stable control system is known to have converging dynamics.  Assume the
+An asymptotically stable model is known to have converging dynamics.  Assume the
 closed-loop matrix eigenvalues are not repeated (which is sensible to do,
@@
 In Step~1, the user selects the system representation, which can be a transfer function or a state-space model.  
-In Step~2, the physical plant (e.g., in the form of Equation~\eqref{eq:ode1}) is provided~\cite{astrom1997computer}.  
+In Step~2, the plant (e.g., in the form of Equation~\eqref{eq:ode1}) is provided~\cite{astrom1997computer}.  
 Finally, in Step~3, the numerical representation for the digital controller implementation must be set by the user, i.e., 
@@
 \textit{Order} is the number of continuous variables of the model; 
-\textcolor{blue}{$\mathcal{F}_{\langle I_p,F_p \rangle}$, where $I_p$ and $F_p$ indicate the integer and fractional parts,  
-and $\mathcal{F}_{\langle E_p,M_p \rangle}$}, where $E_p$ and $M_p$ indicate the exponent and mantissa part, 
+$\mathcal{F}_{\langle I_p,F_p \rangle}$, where $I_p$ and $F_p$ indicate the integer and fractional parts,  
+and $\mathcal{F}_{\langle E_p,M_p \rangle}$, where $E_p$ and $M_p$ indicate the exponent and mantissa part, 
 are the fixed- and floating-point precisions used to model the plant, respectively; 
@@
 We separate our evaluation into two sets of results: fixed- and floating-point. 
-We are able to synthesise more floating point controllers than fixed point controllers, likely because the
-floating point controllers are at a higher precision than the fixed point. It may be that the precision of the fixed-point
-controllers is too low to be able to meet the safety specification. The floating point controllers in general take longer to synthesise
-than the fixed point controllers. There is one exception to this, which is due to the fact that it is not guaranteed that a controller
-exists for all the time discretizations we give the algorithm and, in this case, the fixed-point algorithm was forced to try more time discretizations
-than the floating-point algorithm
-because a fixed-point controller lacked the precision to control the system under the first few time discretizations. 
+We are able to synthesise more floating-point controllers than fixed-point controllers, likely because the
+floating-point controllers are at a higher precision than the fixed-point ones. It may be that the precision of the fixed-point
+controllers is too low to be able to meet the safety specification. The floating-point controllers in general take longer to synthesise
+than the fixed-point ones. There is one exception to this, which is due to the fact that it is not guaranteed that a controller
+exists for all the time discretizations we give the algorithm and, in this case, the fixed-point algorithm might be forced to try more time discretizations
+than the floating-point algorithm because a fixed-point controller lacks the precision to control the system under the first (larger) time discretizations. 
 %For the majority of the {\it fixed-point} benchmarks, we observe that the abstraction-based
@@
 %closed-loop model.  The convergence to a finite value, however, will not
-%make it asymptomatically stable.
+%make it asymptotically stable.
 %

### 2019-01-28 automatica/paper.tex
remove duplicate point in intro
tweaks

@@
 
-%\runtitle{Insert a suggested running title}  % Running title for regular 
+%\runtitle{Automated Synthesis of Safe Digital Controllers}  % Running title for regular 
                                               % papers but only if the title  
@@
 Models are linear differential equations with inputs, evolving over a continuous state space. 
-The synthesis accounts for errors caused by the digitization effects introduced by the controller. 
+The synthesis precisely accounts for the effects of finite-precision arithmetic introduced by the controller. 
 The approach uses counterexample-guided inductive synthesis (CEGIS): 
@@
 caused by artefacts specific to digital control, such as the effects
-of finite-precision arithmetic, time discretization and quantization
+of finite-precision arithmetic and quantization
 errors introduced by A/D and D/A conversion.
@@
 %
-\item We develop a model for different sources of quantization error and account for 
-  their effect on safety.  We provide bounds that ensure the 
-  safety of our controllers in a hybrid (i.e., continuous/digital) domain. \note{is this point repeating the previous one?}
+%\item We develop a model for different sources of quantization error and account for 
+%  their effect on safety.  We provide bounds that ensure the 
+%  safety of our controllers in a hybrid (i.e., continuous/digital) domain. \note{is this point repeating the previous one?}
 
@@
 $k \in \mathbb N$ is a discrete counter and where $\vec{x}_{0}=\vec{x}(0)$ denotes the initial state.
-\note{shall we add a note on time discretization errors? namely that we disregard them? }
+\reply{This time discretization introduces errors that fall outside the scope of this work.}
+%\note{shall we add a note on time discretization errors? namely that we disregard them? }
 
@@
 %-------------------------------s
-\subsection{Errors from finite-precision arithmetics}
+\subsection{Semantics of finite-precision arithmetics}
 \label{sec:errors}
 
-A key contribution of this work is that, when synthesizing controllers, it precisely models the finite-precision arithmetic in the digital controller, guaranteeing that these controllers implemented with finite-precision arithmetic are safe.
-Finite-precision arithmetic introduces errors, as shown in Figure~\ref{fig:digitalsystem}. 
-Details of how we model this arithmetic are in Section~\ref{sec:numeric_rep}. 
-\note{[rephrase?] These errors are present in the real world [as opposed to being absent? vacuous statement?]}, and we must model them accurately in order to capture the full behaviour of the model:
+A key contribution of this work is that, when synthesizing controllers, it precisely replicates the finite-precision arithmetic in the digital controller, guaranteeing that these controllers implemented with finite-precision arithmetic are safe.
+The specific components of the system, shown in Figure~\ref{fig:digitalsystem}, we are concerned with are the ADC, digital controller and DAC.
+Details of how we model the behaviour of the finite-precision arithmetic in these components are in Section~\ref{sec:numeric_rep}.
+We must model the semantics precisely in order to capture the full behaviour of the system:
 
@@
 
-\item The ADC introduces quantisation errors when it converts the analog signal $x(t)$ into a digital signal $x_k$, which is then fed into the controller.  
+\item The ADC converts the analog signal $x(t)$ into a digital signal $x_k$, which is then fed into the controller, converting a real value to a finite-precision value.  
 % cf. Figure~\ref{fig:digitalsystem}.
 
-\item The controller block performs arithmetic at finite precision, 
-which introduces additional errors on top of that introduced by the ADC. 
+\item The controller block performs arithmetic at finite precision. 
 We assume the ADC represents numbers with at least the same precision as the controller, 
@@
 
-\item The DAC can potentially introduce further errors. 
-However, we assume that the DAC converts numbers to analog signals with the same precision as the controller. 
-Again, this assumption is practically reasonable. 
-As a result we can ignore possible additional errors introduced by the DAC. 
+\item The DAC converts finite-precision values back to real values. 
+We assume that the input to the DAC is the same precision as the output of the controller. 
 It would, however, be straightforward to account for a DAC or ADC of different precision than the controller in our algorithm, if necessary. 
@@
 
-We furthermore encompass the following error that is due to modelling (as opposed to the nature of the digital control).  
+\subsection{Soundness of modelling}
+
+In addition to precisely replicating the finite-precision arithmetic of the digital controller, we must consider that our \emph{model} itself uses finite-precision arithmetic to model the behaviour of the system.
+In order to guarantee soundness, we therefore encompass the following error that is due to modelling (as opposed to the nature of the digital control).
 \begin{itemize} 
@@
 As discussed in Section~\ref{sec:errors}, 
-the considered models must account for errors deriving from several sources: 
+the considered models must account for finite-precision arithmetic semantics deriving from several sources: 
 we formally bound the numerical error introduced by the finite-precision representation of the plant (and its operations), 
-and precisely model the error introduced by the ADC/DAC conversions, 
+and precisely model the behaviour introduced by the ADC/DAC conversions, 
 as well as the behaviour of the limited-precision arithmetic used by the controller.
@@
 Technically, we employ interval arithmetic to bound the error introduced by the finite-precision plant, 
-and we use bounded model checking to precisely model the error introduced by the ADC/DAC and the finite-precision controller.
+and we use bounded model checking to precisely model the semantics of finite-precision arithmetic introduced by the ADC/DAC and the finite-precision controller.
 
@@
 
-The fixed-point arithmetic of the digital controller is performed on the upper and lower bound of the intervals from above independently, [I DO NOT UNDERSTAND THE REMAINING PART OF THE SENTENCE.] and the upper and lower bound of the result taken as the interval result\note{Would an example make this clearer?, e.g., consider the conversion from plant precision to controller precision performed by the ADC on a single state value.
-The state value is represented as an interval $\{x.high, x.low\}$, and the result of the conversion is an interval where the upper bound is the conversion of $x.high$ and the lower bound is the conversion of $x.low$?}.
+The fixed-point arithmetic of the digital controller is performed on the upper and lower bound of the intervals from above independently, and the upper and lower bound of the result taken as the interval result.
+For example,
+consider consider the conversion from plant precision to controller precision performed by the ADC on a single state value.
+The state value is represented as an interval $\{x.high, x.low\}$, and the result of the conversion is an interval where the upper bound is the conversion of $x.high$ and the lower bound is the conversion of $x.low$.
 Since the precision of the floating point domain is greater than the precision of the controller, this is guaranteed to bound the real behaviour of the controller.
@@
 }
-We encompass this error using interval arithmetic~\cite{moore1966interval} in the verification phase \note{please add more details here on the ``verification phase''}.
+We encompass this error using interval arithmetic~\cite{moore1966interval} in the precision check shown in Figure~\ref{fig:CEGIS-precision-increment} and detailed in the following section.
 

### 2019-01-30 automatica/paper.tex
results and tweaks

@@
 
-Our benchmark suite consists of \note{update} 20 SISO models extracted from the 
+Our benchmark suite consists of 19 SISO case studies extracted from the 
 control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal}. 
-The models are discretized with sampling times ranging from 1.5s to 0.005s, and if CEGIS is unable to 
-synthesise a controller for a given sampling time, CEGIS heuristically selects a new sampling time \note{do we, still?
-Yes, each benchmark has up to 8 time discretisations, that we run through in the order they are written in the benchmark.
-``heuristically'' is a euphemism for the fact the order is not consistent for each benchmark and we dont run through them in e.g., increasing order.}.
+The models are discretized with sampling times ranging from 1s to 0.0001s.
+CEGIS initially starts with the coarsest discretisation (i.e., 1s sampling time), and if it fails to find a controller, reduces the sampling time.
 
@@
 %linearized by partial feedback linearization~\cite{acrobot}.
-The \textit{antenna} benchmark (\#2) 
-describes the dynamics of the azimuth angle of an antenna 
-motion system composed by a gearbox, a DC motor and amplifiers~\cite{gajic2008optimal}. \\
+%The \textit{antenna} benchmark (\#2) 
+%describes the dynamics of the azimuth angle of an antenna 
+%motion system composed by a gearbox, a DC motor and amplifiers~\cite{gajic2008optimal}. \\
 %The \textit{ballmaglev}  plant corresponds to the model of a simple 
@@
 %
-The \textit{Chen\_ex1} and \textit{Chen\_ex3}
-benchmarks correspond to higher-order control system 
+The \textit{Chen}
+benchmark correspond to a higher-order control system 
 %discrete 
-models employed as case studies for model-order reduction techniques~\cite{CHEN1979389}.  \\
-%
-The benchmarks \textit{Cruise}~\cite{Franklin15} and \textit{CruiseHSCC}~\cite{Astrom08} deal with automotive cruise control models, 
+model employed as a case study for model-order reduction techniques~\cite{CHEN1979389}.  \\
+%
+The benchmarks \textit{Cruise 1}~\cite{Franklin15} and \textit{Cruise 2}~\cite{Astrom08} deal with automotive cruise control models, 
 where the control is used to maintain the speed of an automobile constant, 
@@
 %a flexible metallic structure with sensors and actuators. 
-The \textit{guidance chen} benchmark ( is a high-order system model used by Chen et al.~\cite{CHEN1979389} to evaluate 
-model-order reduction techniques; it models a guidance control system, 
-which is used to determine the path of an autonomous vehicle \note{This is similar to the two benchmarks above?}. \\ 
+%The \textit{guidance chen} benchmark ( is a high-order system model used by Chen et al.~\cite{CHEN1979389} to evaluate 
+%model-order reduction techniques; it models a guidance control system, 
+%which is used to determine the path of an autonomous vehicle \note{This is similar to the two benchmarks above?}. \\ 
 The \textit{helicopter} benchmark plant  describes the transitional and rotational dynamics 
@@
 %\textit{Invpendulum\_cartpos}  and 
-The \textit{Invpendulum\_pendang}  
+The \textit{inverted pendulum} benchmark  
 describes a model for the cart position and the angle of an inverted pendulum placed on the cart,  
@@
 %
-The \textit{magpointer}  describes a magnetic pointer, 
+The \textit{magnetic pointer} benchmark  describes a magnetic pointer, 
 % plant composed by a pointer employed in analogue gauges and indicators, 
@@
 ~\cite{KOKOTOVIC198023}. \\
+The \textit{satellite attitude control system} plant describes the dynamics of a satellite 
+attitude, {\it i.e.}, the orientation angles. An attitude control system must maintain the desired 
+orientation of a satellite with respect to an 
+inertial frame during all the excursion. 
 The \textit{springer-mass damper system} plant is a standard model for the dynamics of several mechanical systems. \\ 
@@
 
-%The \textit{USCG cutter tampa heading angle} plant describes the heading angle dynamics of a Coast 
-%Guard cutter. The \textit{satellite attitude control system} plant describes the dynamics of a satellite 
-%attitude, {\it i.e.}, the orientation angles. An attitude control system must maintain the desired 
-%orientation of a satellite with respect to an 
-%inertial frame during all the excursion.
+The \textit{USCG cutter tampa heading angle} plant describes the heading angle dynamics of a Coast 
+Guard cutter.
 
@@
 and \textit{Time} is the total time required to synthesize a controller for the given plant.    
-Timeouts are indicated by~\xmark, while failures to synthesise the digital controllers are indicated by $\dagger$ \note{no such instances}.  
+Timeouts are indicated by~\xmark.  
 The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
@@
 We separate our evaluation into two sets of results: fixed- and floating-point. 
-We are able to synthesise more floating-point controllers than fixed-point controllers, likely because the
-floating-point controllers are at a higher precision than the fixed-point ones. It may be that the precision of the fixed-point
-controllers is too low to be able to meet the safety specification. The floating-point controllers in general take longer to synthesise
-than the fixed-point ones. There is one exception to this, which is due to the fact that it is not guaranteed that a controller
-exists for all the time discretizations we give the algorithm and, in this case, the fixed-point algorithm might be forced to try more time discretizations
-than the floating-point algorithm because a fixed-point controller lacks the precision to control the system under the first (larger) time discretizations. 
+We present a selection of case-studies that we are able to solve either for floating-point or fixed-point. 
+Given a time discretisation, the floating-point controllers in general take longer to synthesise
+than the fixed-point ones. However, the fixed-point algorithm is often forced to try more time discretisations, because the fixed-point controller
+lacks the precision to control the system at the coarser time discretisation.
 %For the majority of the {\it fixed-point} benchmarks, we observe that the abstraction-based
@@
 
-%\begin{table*}
-%\centering
-%\begin{tabular}{| r | l | c | c | r | c | r | c | r | c | r |}
-%%
-%\hline
-%\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                 & \multicolumn{4}{|c|}{Abstraction} \\
-%   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
-%1  & Acrobot     & 4 & 8,8 & 61959.4\,s &  & ~\xmark & & ~\xmark &  & ~\xmark \\
-%2  & Antenna     & 6 &  & ~\xmark &  & ~\xmark & & ~\xmark & & 2903s~\xmark\\
-%3  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark & & ~\xmark & & ~\xmark\\
-%4  & Bioreact    & 3 & 8,8 & 11.5\,s & 6,10 &14.6\,s & 24,14 & 0.4\,s & 6,10 & 0.5\,s\\
-%5  & Chen\_ex1   & 3 & 8,8 & 10.3\,s  & 6,10 & 9.2\,s & & ~\xmark & 6,10 & 1.4\,s\\
-%6  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 4683.8\,s &  & ~\xmark & & ~\xmark\\
-%7  & Chen\_ex3   & 7 &   & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-%8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-%9  & Cruise      & 1 & 8,8 & 9.6\,s & 6,10 & 6.5\,s & 24,14 & 0.3\,s& 6,10 & 0.3\,s\\
-%10 & CruiseHSCC & 1 & 8,8 & 9.6\,s & 6,10 & 6.6\,s &  24,14 & 0.3\,s & 6,10 & 0.3\,s \\
-%11 & Cstr & 3 & & ~\xmark & & ~\xmark & & ~\xmark & & 181s~\xmark\\
-%12 & Cstrtmp  & 3 &  & ~\xmark & & ~\xmark & 24,14 & 0.5\,s & & ~\xmark\\
-%13 & DCmotor   & 2 & 8,8  & 11.3\,s & 6,10 & 7.8\,s & 24,14 & 0.4\,s & 6,10 & 0.5\,s (4.0\,s) \\
-%14 & Flexbeam   & 6 & & ~\xmark & & ~\xmark & 24,14 & 72.1\,s & & ~\xmark\\
-%15 & Guidance chen  & 5 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-%16 & Helicopter   & 3 & 8,8 & 13.8\,s & 32,23 & 148\,s & 24,14 & 0.8\,s& 6,10 & 1.1\,s (56.6\,s)\\
-%17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
-%18 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 6,10 & 28.2\,s & 24,14 & 0.4\,s & 6,10 & 0.5\,s\\
-%19 & Magpointer   & 2 & 8,8 & 10.1\,s & 6,10 & 20.4\,s & 24,14  & 1\,s& 6,10 & 1.3\,s (\xmark)\\
-%20 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 6,10 & 34.8\,s & 24,14 & 0.5\,s & 6,10 & 0.6\,s (\xmark)\\
-%21 & Pendulum   & 2 & 8,8 & 8.5\,s & 32,23 & 24\,s & 24,14 & 0.4\,s & 6,10 & 0.5\,s (2.4\,s)\\
-%22 & Regulator   & 5 & & ~\xmark & & ~\xmark & &~\xmark  & & 529s~\xmark\\
-%23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & 14.1s~\xmark\\
-%24 & streamdrum   & 3 & 8,8  & 332.5\,s & 6,10 & 590.5\,s & 24,14 & 0.7\,s & 6,10 &1.3\,s\\
-%25 & Suspension  & 4 & 8,8  & 17.2\,s & 6,10 &1373\,s & 56,30 & 15.3\,s & 6,10 & 4.4\,s (313.6\,s)\\
-%26 & Tapedriver   & 3 & 8,8  & 8.2\,s & & ~\xmark & 64,22 & 2.1\,s & 6,10 & 1.1\,s (6.0\,s)\\
-%\hline
-%%
-%\end{tabular}
-%\vspace{0.05in}
-%\caption{Experimental results\label{tab:results}}
-%\end{table*}
-
 \begin{table*}
@@
 % \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Run-time} \\
- Benchmark  &  Order  & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Time & $\mathcal{F}_{\langle E_p, M_p \rangle}$ & Time \\\hline
-%1  & Acrobot     & 4 & 8,8 & 61529.8\,s &  & ~\xmark \\
- Antenna     & 6 &  & ~\xmark & 6,10 & 817.4\,s \\
-%2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
- Bioreact    & 3 & 8,8 & 11.5\,s & 6,10 &23.6\,s \\
- Chen\_ex1   & 3 & 8,8 & 10.3\,s  & 6,10 & 12.7\,s \\
-%4  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 3535s.1\,s \\
- Chen\_ex3   & 7 & 8,8  & 11.4\,s & 6,10 & 59.1\,s \\
-%8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
- Cruise      & 1 & 8,8 & 9.7\,s & 6,10 & 10.3\,s \\
- CruiseHSCC & 1 & 8,8 & 9.7\,s & 6,10 & 10.3\,s  \\
- Cstr & 3 & & ~\xmark & 6,10 & 21.4\,s \\
- Cstrtmp  & 3 & 8,8 & 12.5\,s &6,10 & 15.4\,s \\
- DCmotor   & 2 & 8,8  & 10.0\,s & 6,10 & 11.4\,s  \\
-%11 & Flexbeam   & 6 & & ~\xmark & 16, 10 & 10916.1\,s \\
-%12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
- Helicopter   & 3 &  & ~\xmark & 6,10 & 32.0\,s \\
-%17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
- Invpendulum\_pendang & 2 & 8,8  & 10.7 & 6,10 & 14.8\,s\\
- Magpointer   & 2 &  & ~\xmark & 6,10 & 86.0\,s \\
- Magsuspension  & 2 & 12,12  & 39.0\,s  & 6,10 & 43.2\,s \\
- Pendulum   & 2 & 8,8 & 13.2\,s & 6,10 & 16.6\,s\\
- Regulator   & 5 & 8,8 & 1532.7\,s & 6,10 & 999.6\,s\\
- Springmassdamper & 2 & & ~\xmark &6,10 & 24.2s \\
- Steamdrum   & 3 & 8,8  & 700.9s & 6,10 & 24.4\,s \\
- Suspension  & 4 & 8,8  & 11.4\,s & 6,10 &15.4\,s \\
- Tapedriver   & 3 & 8,8  & 11.4\,s &6,10 & 13.3\,s \\
+ Benchmark  &  Order  & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Time(s) & $\mathcal{F}_{\langle E_p, M_p \rangle}$ & Time(s) \\\hline
+Bioreact	&	2	&	8,8	&	15.35	&	10,6	&	23.76	\\
+Chen	&	3	&	8,8	&	11.24	&	10,6	&	14.25	\\
+Cruise 2	&	1	&	8,8	&	11.03	&	10,6	&	11.17	\\
+Cruise 2	&	1	&	8,8	&	9.93	&	10,6	&	10.54	\\
+cstrtmp	&	3	&	12,12	&	90.03	&	10,6	&	321.12	\\
+Cstrtmp	&	2	&	8,8	&	18.56	&	10,6	&	16.99	\\
+DC motor	&	2	&	8,8	&	10.34	&	10,6	&	12.32	\\
+Helicopter	&	3	&	16,16	&	1116.08	&	10,6	&	168.43	\\
+Inverted pendulum	&	2	&	12,12	&	16.01	&	10,6	&	18.73	\\
+Magnetic pointer	&	3	&	12,12	&	1071.02	&	10,6	&	207.60	\\
+Magnetic suspension	&	3	&	20,20	&	56.9	&	10,6	&	998.3	\\
+Pendulum	&	2	&	8,8	&	11.74	&	10,6	&	13.69	\\
+Regulator	&	5	&	10,16	&	190.28	&		&	~\xmark	\\
+Satellite	&	2	&	8,8	&	13.91	&	10,6	&	16.92	\\
+Spring-mass-damper	&	2	&	12,12	&	16.09	&	10,6	&	23.21	\\
+Steam drum	&	3	&		&	~\xmark	&	10,16	&	21.16	\\
+Supension	&	4	&	8,8	&	12.40	&	10,6	&	17.03	\\
+Tape driver	&	3	&	8,8	&	12.18	&	10,6	&	14.34	\\
+USCG tampa	&	3	&	12,12	&	1143.35	&	10,6	&	210.70	\\
+% 
+%%1  & Acrobot     & 4 & 8,8 & 61529.8\,s &  & ~\xmark \\
+%% Antenna     & 6 &  & ~\xmark & 6,10 & 817.4\,s \\
+%%2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
+% Bioreact    & 3 & 8,8 & 15.3\,s & 6,10 &23.6\,s \\
+%% 
+% Chen\_ex1   & 3 & 8,8 & 10.3\,s  & 6,10 & 14.3\,s \\
+%%4  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 3535s.1\,s \\
+%% Chen\_ex3   & 7 & 8,8  & 11.4\,s & 6,10 & 59.1\,s \\
+%%8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+% Cruise      & 1 & 8,8 & 9.7\,s & 6,10 & 10.3\,s \\
+%% CruiseHSCC & 1 & 8,8 & 9.7\,s & 6,10 & 10.3\,s  \\
+% Cstr & 3 & & ~\xmark & 6,10 & 21.4\,s \\
+% Cstrtmp  & 3 & 8,8 & 12.5\,s &6,10 & 15.4\,s \\
+% DCmotor   & 2 & 8,8  & 10.0\,s & 6,10 & 11.4\,s  \\
+%%11 & Flexbeam   & 6 & & ~\xmark & 16, 10 & 10916.1\,s \\
+%%12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
+% Helicopter   & 3 &  & ~\xmark & 6,10 & 32.0\,s \\
+%%17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
+% Invpendulum\_pendang & 2 & 8,8  & 10.7 & 6,10 & 14.8\,s\\
+% Magpointer   & 2 &  & ~\xmark & 6,10 & 86.0\,s \\
+% Magsuspension  & 2 & 12,12  & 39.0\,s  & 6,10 & 43.2\,s \\
+% Pendulum   & 2 & 8,8 & 13.2\,s & 6,10 & 16.6\,s\\
+% Regulator   & 5 & 8,8 & 1532.7\,s & 6,10 & 999.6\,s\\
+% Springmassdamper & 2 & & ~\xmark &6,10 & 24.2s \\
+% Steamdrum   & 3 & 8,8  & 700.9s & 6,10 & 24.4\,s \\
+% Suspension  & 4 & 8,8  & 11.4\,s & 6,10 &15.4\,s \\
+% Tapedriver   & 3 & 8,8  & 11.4\,s &6,10 & 13.3\,s \\
 \hline
@@
 \vspace{0.05in}
-\caption{Experimental results \note{expand description (short, crisp)}\label{tab:results}}
+\caption{Synthesis times for fixed- and floating-point controllers\label{tab:results}}
 \end{table*}
 
-The mean run-time for the successful benchmarks is 152.6\,s for fixed-point and 117.5\,s for floating-point implementations, respectively.  
-The median run-time for the successful benchmarks is 16\,s for fixed-point and 11\,s for floating-point implementations, respectively.
+The mean run-time for the successful benchmarks is 225\,s for fixed-point and 125\,s for floating-point implementations, respectively.  
+The median run-time for the successful benchmarks is 15.7\,s for fixed-point and 17.8\,s for floating-point implementations, respectively.
 We consider these times to be short enough to be of practical use to control engineers, and thus affirm the validity of EG1.
 
-\textcolor{blue}{We fail to synthesise a controller for several instances.}  
-The completeness threshold may be too large, thus causing a timeout \note{but timeouts are handled separately than failures?}, 
+We present in this paper a selection of case studies for which we are able to synthesise controllers. In the full experimental environment, 
+which is available to download, we include further case studies that we were unable to synthesise controllers for. This is in many cases
+due to timeouts, especially when the completeness threshold is too large, 
 or a controller simply may not exist for a benchmark at a given time discretisation and required controller precision. 
@@
 %-------------------------------
-\subsection{Threats to validity \note{generality?}}
+\subsection{Threats to generality}
 \label{exp:threats-to-validity}
@@
 in order to be compliant with the CBMC type API. 
-Similarly, for discretization, we run multiple discretizations for each
-benchmark and retain the fastest run.
+Similarly, for time-discretization, we try a set of pre-defined time discretisations.
 This works sufficiently well for our benchmarks, but

### 2019-01-30 automatica/paper.tex
removed unnecessary level of indirection in sec 6
fixed wrong reference

@@
 %\todo{please eventually itemize next}
-\subsubsection{Block 1}
+\subsection{Block 1}
 
@@
 unfolding the transition system $k$ steps and by selecting a controller $K$ and a single initial state, 
-such that the states at each step do not violate the safety criteria (see Section~\ref{ssec:safespecification} \note{fix}).    
+such that the states at each step do not violate the safety criteria (see Section~\ref{sec:safety}).    
 That is, we ask the bounded model checker~\cite{ClarkeKL04} if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states, and a given fixed point precision for the controller, and where the input signal remains within the specified bounds.
@@
 
-\subsubsection{Block 2}
+\subsection{Block 2}
 
@@
 
-\subsubsection{Block 3}
+\subsection{Block 3}
 
@@
 
-\subsubsection{Block 4}
+\subsection{Block 4}
 

### 2019-01-30 automatica/paper.tex
added forward reference to safety theorem

@@
 We check that the controller is safe starting from each vertex of the set of initial states,  
-and show that this is sufficient to prove safety from any state in this set. \note{add forward reference to proof.}
+and show that this is sufficient to prove safety from any state in this set (see Theorem~\ref{th:safety}). %\note{add forward reference to proof.}
 
@@
 \begin{theorem}
+  \label{th:safety}
 If a controller is safe for each of the corner cases of our hypercube of

### 2019-01-30 automatica/paper.tex
typo
+ comments

@@
 The former constraint expresses that control input, possibly shaped via state-feedback, 
-might saturates in view of physical constraints.
+might saturate in view of physical constraints.
 
@@
 Notice that the physical plant model operates over real-valued signals, 
-which means that our verification phase must also account for the numerical error, 
+which means that our verification phase \note{I'm not sure that it's clear at this point what the verification phase consists of} must also account for the numerical error, 
 as well as quantization errors caused by representing the physical plant at finite 
-precision $\mathcal{F}_{\langle I_p,F_p \rangle}$.
+precision $\mathcal{F}_{\langle I_p,F_p \rangle}$. \note{Also, isn't this paragraph redundant after sec 3.7?}
 

### 2019-01-30 automatica/paper.tex
typo

@@
 represented at the floating-point precision of the controller, 
-whereas $\mathcal{F}_{\langle E_p,M_p \rangle}(x)$ denotes a real number represented at the fixed-point precision of the plant model.
+whereas $\mathcal{F}_{\langle E_p,M_p \rangle}(x)$ denotes a real number represented at the floating-point precision of the plant model.
 

### 2019-01-30 automatica/paper.tex
floating point -> floating-point for consistency

@@
 
-We further employ $\mathcal{F}_{\langle E,M \rangle}(x)$ to denote a real number $x$ represented in a floating point domain, 
+We further employ $\mathcal{F}_{\langle E,M \rangle}(x)$ to denote a real number $x$ represented in a floating-point domain, 
 with $E$ bits representing the exponent part and $M$ bits representing the mantissa part. 
@@
 We outline here the mathematics behind bounding the errors on the double-precision floating-point numbers. 
-Recall we use $\mathcal{F}_{\langle E,M \rangle}(x)$ denote a real number $x$ represented in a floating point domain, 
+Recall we use $\mathcal{F}_{\langle E,M \rangle}(x)$ denote a real number $x$ represented in a floating-point domain, 
 with $E$ bits representing the exponent part, and $M$ bits representing the mantissa. 
@@
 The state value is represented as an interval $\{x.high, x.low\}$, and the result of the conversion is an interval where the upper bound is the conversion of $x.high$ and the lower bound is the conversion of $x.low$.
-Since the precision of the floating point domain is greater than the precision of the controller, this is guaranteed to bound the real behaviour of the controller.
+Since the precision of the floating-point domain is greater than the precision of the controller, this is guaranteed to bound the real behaviour of the controller.
 

### 2019-01-30 automatica/paper.tex
typo
finite precision -> finite-precision for consistency

@@
 linear arithmetic.  Since this approach uses switching actions for the digital controller, it avoids problems related to
-finite precision arithmetic, but potentially suffers from state-space
+finite-precision arithmetic, but potentially suffers from state-space
 explosion.  Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same
@@
 of the controller, which manipulates quantised signals as discrete quantities represented with
-finite precision. The new approach is fully automated and leverages an approach based on CEGIS.
+finite-precision. The new approach is fully automated and leverages an approach based on CEGIS.
 
@@
 
-\item The controller block performs arithmetic at finite precision. 
+\item The controller block performs arithmetic at finite-precision. 
 We assume the ADC represents numbers with at least the same precision as the controller, 
@@
 \item
-The representations used in the plant model and its arithmetic operations are also carried out at a finite precision, 
+The representations used in the plant model and its arithmetic operations are also carried out at a finite-precision, 
 thus we must account for the corresponding errors.  
@@
 which means that our verification phase \note{I'm not sure that it's clear at this point what the verification phase consists of} must also account for the numerical error, 
-as well as quantization errors caused by representing the physical plant at finite 
-precision $\mathcal{F}_{\langle I_p,F_p \rangle}$. \note{Also, isn't this paragraph redundant after sec 3.7?}
+as well as quantization errors caused by representing the physical plant at finite-precision $\mathcal{F}_{\langle I_p,F_p \rangle}$. \note{Also, isn't this paragraph redundant after sec 3.7?}
 
@@
 For example,
-consider consider the conversion from plant precision to controller precision performed by the ADC on a single state value.
+consider the conversion from plant precision to controller precision performed by the ADC on a single state value.
 The state value is represented as an interval $\{x.high, x.low\}$, and the result of the conversion is an interval where the upper bound is the conversion of $x.high$ and the lower bound is the conversion of $x.low$.
@@
 
-\subsection{Effect of precision arithmetic on safety specification and on stability}
-
-In this section we will quantify how the finite precision arithmetic in a digital controller affects the
+\subsection{Effect of finite-precision arithmetic on safety specification and on stability}
+
+In this section we will quantify how the finite-precision arithmetic in a digital controller affects the
 safety and stability properties of an LTI model.
 
-\subsubsection{Safety of closed-loop models with finite precision controller error}
+\subsubsection{Safety of closed-loop models with finite-precision controller error}
 
@@
 \label{sec:stab_FWL}
-The validity of Jury's criterion~\cite{fadali} relies on the representation of the closed-loop dynamics $x_{k+1} = (A_d - B_dK) x_k$ at infinite precision.  
+The validity of Jury's criterion~\cite{fadali} relies on the representation of the closed-loop dynamics $x_{k+1} = (A_d - B_dK) x_k$ at infinite-precision.  
 When we employ a fixed-point arithmetic digital controller, the operation above can be expressed as follows, where we use $\mathcal{F}_{\langle I_c,F_c \rangle}$ preceding a variable to indicate that variable is converted into the fixed-point precision given by $\mathcal{F}_{\langle I_c,F_c \rangle}$:
@@
 This approach is sound if the current $k$ is greater than the completeness threshold (see later step).  
-We~also assume some finite precision for the plant and a sampling rate.
+We~also assume some finite-precision for the plant and a sampling rate.
 We use a fixed-point precision in this description, given by $\langle I_p,F_p\rangle$, but if we are considering a floating-point controller we will instead model the plant with a floating-point precision, $\langle E_p,M_p\rangle$.

### 2019-01-31 automatica/paper.tex
+comment

@@
 }
-We encompass this error using interval arithmetic~\cite{moore1966interval} in the precision check shown in Figure~\ref{fig:CEGIS-precision-increment} and detailed in the following section.
+We encompass this error using interval arithmetic~\cite{moore1966interval} in the precision check shown in Figure~\ref{fig:CEGIS-precision-increment} and detailed in the following section \note{previous section?}.
 

### 2019-01-31 automatica/paper.tex
switched to finite precision overall instead of finite-precision

--- 2019-01-30 automatica/paper.tex
@@
 Models are linear differential equations with inputs, evolving over a continuous state space. 
-The synthesis precisely accounts for the effects of finite-precision arithmetic introduced by the controller. 
+The synthesis precisely accounts for the effects of finite precision arithmetic introduced by the controller. 
 The approach uses counterexample-guided inductive synthesis (CEGIS): 
@@
 caused by artefacts specific to digital control, such as the effects
-of finite-precision arithmetic and quantization
+of finite precision arithmetic and quantization
 errors introduced by A/D and D/A conversion.
@@
 %% observer~\cite{astrom1997computer}
-in a finite-precision domain. Our model also accounts for representation errors introduced
-by our modelling of the plant using finite-precision arithmetic. 
+in a finite precision domain. Our model also accounts for representation errors introduced
+by our modelling of the plant using finite precision arithmetic. 
 We reason about safety requirements, which are frequently overlooked in conventional feedback control synthesis, 
@@
   numerical soundness required by the effects of discretisation and
-  finite-precision errors.
+  finite precision errors.
 
@@
 Program synthesizers are an ideal fit for the synthesis of digital controllers, 
-since the semantics of programs precisely capture the effects of finite-precision arithmetic.  
+since the semantics of programs precisely capture the effects of finite precision arithmetic.  
 However the control literature has been oblivious to this relevant connection. 
@@
 traces of the model, alongside the numerical soundness required by the
-effects of discretisation and the errors related to finite-precision arithmetic.
+effects of discretisation and the errors related to finite precision arithmetic.
 
@@
 Recent results in digital control have focused on separate aspects of discretization, 
-e.g. delayed response~\cite{Duggirala2015} and finite-precision arithmetic, 
+e.g. delayed response~\cite{Duggirala2015} and finite precision arithmetic, 
 with the goal either to verify~\cite{daes20161} the correctness of the implementation or to optimize~\cite{oudjida2014design} its design.
 
-There are two different problems that arise from finite-precision arithmetic in digital controllers.  
+There are two different problems that arise from finite precision arithmetic in digital controllers.  
 The first is the error caused by the inability to represent the exact state of the physical system, 
@@
 In~\cite{fialho1994stability}, a stability measure based on the error of the digital dynamics ensures that
-the deviation introduced by finite-precision arithmetic does not lead to instability.  
+the deviation introduced by finite precision arithmetic does not lead to instability.  
 \cite{DBLP:journals/automatica/WuLCC09} uses $\mu$-calculus to synthesise directly a digital controller, 
@@
 %-------------------------------s
-\subsection{Semantics of finite-precision arithmetics}
+\subsection{Semantics of finite precision arithmetics}
 \label{sec:errors}
 
-A key contribution of this work is that, when synthesizing controllers, it precisely replicates the finite-precision arithmetic in the digital controller, guaranteeing that these controllers implemented with finite-precision arithmetic are safe.
+A key contribution of this work is that, when synthesizing controllers, it precisely replicates the finite precision arithmetic in the digital controller, guaranteeing that these controllers implemented with finite precision arithmetic are safe.
 The specific components of the system, shown in Figure~\ref{fig:digitalsystem}, we are concerned with are the ADC, digital controller and DAC.
-Details of how we model the behaviour of the finite-precision arithmetic in these components are in Section~\ref{sec:numeric_rep}.
+Details of how we model the behaviour of the finite precision arithmetic in these components are in Section~\ref{sec:numeric_rep}.
 We must model the semantics precisely in order to capture the full behaviour of the system:
@@
 
-\item The ADC converts the analog signal $x(t)$ into a digital signal $x_k$, which is then fed into the controller, converting a real value to a finite-precision value.  
+\item The ADC converts the analog signal $x(t)$ into a digital signal $x_k$, which is then fed into the controller, converting a real value to a finite precision value.  
 % cf. Figure~\ref{fig:digitalsystem}.
@@
 
-\item The DAC converts finite-precision values back to real values. 
+\item The DAC converts finite precision values back to real values. 
 We assume that the input to the DAC is the same precision as the output of the controller. 
@@
 
-In addition to precisely replicating the finite-precision arithmetic of the digital controller, we must consider that our \emph{model} itself uses finite-precision arithmetic to model the behaviour of the system.
+In addition to precisely replicating the finite precision arithmetic of the digital controller, we must consider that our \emph{model} itself uses finite precision arithmetic to model the behaviour of the system.
 In order to guarantee soundness, we therefore encompass the following error that is due to modelling (as opposed to the nature of the digital control).
@@
 thus we must account for the corresponding errors.  
-Specifically, we must account for the error introduced by our model using finite-precision arithmetic for the plant variables $x(t)$ and $u(t)$, which are, in reality, continuous quantities. 
+Specifically, we must account for the error introduced by our model using finite precision arithmetic for the plant variables $x(t)$ and $u(t)$, which are, in reality, continuous quantities. 
 We guarantee that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller and we use interval arithmetic to bound the errors, as detailed in Section~\ref{sec:numeric_rep}.
@@
 which means that our verification phase \note{I'm not sure that it's clear at this point what the verification phase consists of} must also account for the numerical error, 
-as well as quantization errors caused by representing the physical plant at finite 
-precision $\mathcal{F}_{\langle I_p,F_p \rangle}$. \note{Also, isn't this paragraph redundant after sec 3.7?}
+as well as quantization errors caused by representing the physical plant at finite precision $\mathcal{F}_{\langle I_p,F_p \rangle}$. \note{Also, isn't this paragraph redundant after sec 3.7?}
 
@@
 As discussed in Section~\ref{sec:errors}, 
-the considered models must account for finite-precision arithmetic semantics deriving from several sources: 
-we formally bound the numerical error introduced by the finite-precision representation of the plant (and its operations), 
+the considered models must account for finite precision arithmetic semantics deriving from several sources: 
+we formally bound the numerical error introduced by the finite precision representation of the plant (and its operations), 
 and precisely model the behaviour introduced by the ADC/DAC conversions, 
@@
 
-Technically, we employ interval arithmetic to bound the error introduced by the finite-precision plant, 
-and we use bounded model checking to precisely model the semantics of finite-precision arithmetic introduced by the ADC/DAC and the finite-precision controller.
+Technically, we employ interval arithmetic to bound the error introduced by the finite precision plant, 
+and we use bounded model checking to precisely model the semantics of finite precision arithmetic introduced by the ADC/DAC and the finite precision controller.
 
@@
 
-We use finite-precision arithmetic to model the plant. 
+We use finite precision arithmetic to model the plant. 
 This is an approximation that speeds up each CEGIS iteration, 
@@
 %
-\item Division: the operations performed by the controllers in the finite-precision
+\item Division: the operations performed by the controllers in the finite precision
 domain do not include division.  However, we do use division in computations within the plant.  
@@
 
-\subsection{Effect of precision arithmetic on safety specification and on stability}
+\subsection{Effect of finite precision arithmetic on safety specification and on stability}
 
@@
 Recall that a closed-loop asymptotically stable system will converge to the origin.  
-We know that the original system with an infinite-precision controller is stable, 
+We know that the original system with an infinite precision controller is stable, 
 because we have synthesized it to meet Jury's criterion.  
@@
 We can thus disregard these steady-state errors (caused by
-finite-precision arithmetic) when stability is ensured by synthesis, and then verify its
-safety accounting for the finite-precision errors.
+finite precision arithmetic) when stability is ensured by synthesis, and then verify its
+safety accounting for the finite precision errors.
 
@@
 We employ a multi-stage approach that unwinds the dynamics of the model up to a completeness threshold, 
-modelling finite-precision arithmetic using bit-precise bounded model checking, 
+modelling finite precision arithmetic using bit-precise bounded model checking, 
 and then verifying soundness of the resulting controller using interval arithmetic. 
@@
 candidate solution $K$ that satisfies both the stability requirement and the safety specification, 
-within a finite-precision model.  
+within a finite precision model.  
 In order to synthesize a controller that satisfies the stability requirement, 
@@
 Finally, in Step~3, the numerical representation for the digital controller implementation must be set by the user, i.e., 
-the finite-precision arithmetic that defines the number of bits of integer and fractional parts when using fixed-point arithmetic, 
+the finite precision arithmetic that defines the number of bits of integer and fractional parts when using fixed-point arithmetic, 
 or half- and single-precision when using floating-point arithmetic, 
@@
 The synthesis is considered to be \emph{successful} if a digital controller is
-correctly synthesized w.r.t. effects of finite-precision arithmetic; or if there is no solution (no
+correctly synthesized w.r.t. effects of finite precision arithmetic; or if there is no solution (no
 controller) for the corresponding physical plant (given the implementation
@@
 underlying SAT or SMT solver to address verification conditions.  We~model
-effects of finite-precision arithmetic 
+effects of finite precision arithmetic 
 explicitly using CBMC's nondeterminism API (e.g., \texttt{nondet},
@@
 %and the abstraction-based 
-CEGIS approach is able to generate finite-precision digital controllers using fixed-point and floating-point arithmetic in a reasonable amount of time.
+CEGIS approach is able to generate finite precision digital controllers using fixed-point and floating-point arithmetic in a reasonable amount of time.
 
@@
 \textit{Plant precision and discretization heuristics:} Our algorithm to
-select suitable finite-precision arithmetic to model the plant behavior 
+select suitable finite precision arithmetic to model the plant behavior 
 increases the precision by 8 bits at each step 
@@
 %asymptotically stable system will converge to the origin.  We know that the
-%original system with an infinite-precision controller is stable, because we
+%original system with an infinite precision controller is stable, because we
 %have synthesized it to meet Jury's criterion.  Hence, $(A_d - B_dK)^n x_0$ 

### 2019-01-31 automatica/paper.tex
overall paper

@@
 
-%\runtitle{Automated Synthesis of Safe Digital Controllers}  % Running title for regular 
-                                              % papers but only if the title  
-                                              % is over 5 words. Running title 
-                                              % is not shown in output.
-
 %\thanksref{footnoteinfo}
@@
 \authorrunning{Abate et al.} % if too long for running head
+
+\titlerunning{Automated Synthesis of Safe Digital Controllers}  % Running title for regular 
+                                              % papers but only if the title  
+                                              % is over 5 words. Running title 
+                                              % is not shown in output
 
@@
 $k \in \mathbb N$ is a discrete counter and where $\vec{x}_{0}=\vec{x}(0)$ denotes the initial state. 
-\reply{This time discretization introduces errors that fall outside the scope of this work.}
-%\note{shall we add a note on time discretization errors? namely that we disregard them? }
+We assume that specifications on the model concern \eqref{eq:plant}, 
+and plan to devise controllers $\vec{u}_k$ to meet them. 
+(The more general problem of synthesising controllers $u(t)$ for \eqref{eq:ode1} fall outside the scope of the present work.)
 

### 2019-01-31 automatica/paper.tex
overall paper

@@
 %-------------------------------s
-\subsection{Semantics of finite precision arithmetics}
+\subsection{Semantics of finite-precision arithmetics}
 \label{sec:errors}
 
-A key contribution of this work is that, when synthesizing controllers, it precisely replicates the finite precision arithmetic in the digital controller, guaranteeing that these controllers implemented with finite precision arithmetic are safe.
-The specific components of the system, shown in Figure~\ref{fig:digitalsystem}, we are concerned with are the ADC, digital controller and DAC.
-Details of how we model the behaviour of the finite precision arithmetic in these components are in Section~\ref{sec:numeric_rep}.
-We must model the semantics precisely in order to capture the full behaviour of the system:
+A key contribution of this work is that, when synthesizing controllers, it precisely replicates the finite-precision arithmetic within the digital controller, 
+thus guaranteeing that controllers implemented with finite-precision arithmetic are safe. 
+The specific components of the model, shown in Figure~\ref{fig:digitalsystem}, we are concerned with are the ADC, digital controller and DAC.
+Details of how we model the behaviour of the finite-precision arithmetic in these components are in Section~\ref{sec:numeric_rep}. 
+We must model the semantics precisely, in order to capture the full behaviour of the model. 
+More specifically, we encompass the following features:
 
@@
 
-\item The ADC converts the analog signal $x(t)$ into a digital signal $x_k$, which is then fed into the controller, converting a real value to a finite precision value.  
+\item The ADC converts the analog signal $x(t)$ into a digital signal $x_k$, which is then fed into the controller, converting a real value to a finite-precision value.  
 % cf. Figure~\ref{fig:digitalsystem}.
@@
 We assume the ADC represents numbers with at least the same precision as the controller, 
-and thus focus on the precision limited by the controller. 
+and thus focus on the precision as limited by the controller. 
 This is a reasonable assumption based on commonly available hardware.
 
-\item The DAC converts finite precision values back to real values. 
-We assume that the input to the DAC is the same precision as the output of the controller. 
+\item The DAC converts finite-precision values back to real values. 
+We assume that the input to the DAC has the same precision as the output of the controller. 
 It would, however, be straightforward to account for a DAC or ADC of different precision than the controller in our algorithm, if necessary. 
@@
 
-In addition to precisely replicating the finite precision arithmetic of the digital controller, we must consider that our \emph{model} itself uses finite precision arithmetic to model the behaviour of the system.
-In order to guarantee soundness, we therefore encompass the following error that is due to modelling (as opposed to the nature of the digital control).
+In addition to precisely replicating the finite-precision arithmetic of the digital controller, 
+we must consider that our \emph{model} itself in \eqref{eq:plant} employs finite-precision arithmetic to represent the behaviour of the real system. 
+In order to guarantee soundness, we therefore encompass the error that is due to modelling (as opposed to the nature of the digital controller):   
+the representations used in the plant model and its arithmetic operations are carried out at finite precision.  
 \begin{itemize} 
 \item
-The representations used in the plant model and its arithmetic operations are also carried out at a finite precision, 
-thus we must account for the corresponding errors.  
-Specifically, we must account for the error introduced by our model using finite precision arithmetic for the plant variables $x(t)$ and $u(t)$, which are, in reality, continuous quantities. 
-We guarantee that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller and we use interval arithmetic to bound the errors, as detailed in Section~\ref{sec:numeric_rep}.
+We account for the error introduced by finite precision arithmetic applied over the plant variables $x_k$ and $u_k$ \note{here I have replaced the continuous-time signals with discrete-time ones}, which are actually continuous quantities.
+We guarantee that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller, 
+and we use interval arithmetic to bound the incurred errors, as further detailed in Section~\ref{sec:numeric_rep}. 
 \end{itemize}

### 2019-01-31 automatica/paper.tex
overall paper

@@
 Notice that the physical plant model operates over real-valued signals, 
-which means that our verification phase \note{I'm not sure that it's clear at this point what the verification phase consists of} must also account for the numerical error, 
+which means that our verification \note{also called validation below ...
+} phase \note{I'm not sure that it's clear at this point what the verification phase consists of} must also account for the numerical error,
 as well as quantization errors caused by representing the physical plant at finite precision $\mathcal{F}_{\langle I_p,F_p \rangle}$. \note{Also, isn't this paragraph redundant after sec 3.7?}
@@
 Figure~\ref{fig:CEGIS}) and a validation phase (denoted by {\sc
-  Verify}), which interact via a finite set of tests {\sc
+  Verify}) \note{why do we use validation-VERIFY; this can be confusing, if you regard validation as a form of soft verification via data ... }, which interacts via a finite set of tests {\sc
   inputs} that is updated incrementally.
@@
 
-\note{reminder AA: check throughout use of 'model vs system'}
+%\note{reminder AA: check throughout use of 'model vs system'}
 
@@
 This polynomial is obtained as a function of the state-space matrices $A,B$~\cite{Astrom08}, 
-and in particular its order $N$ corresponds to the dimensions of the state variables (above $n$).  
+and in particular its order $N$ corresponds to the dimensions of the state variables (above, $n$).  
 A sufficient condition for asymptotic stability of the closed-loop LTI model~\cite{astrom1997computer} 

### 2019-01-31 automatica/paper.tex
overall paper

@@
 
+\note{throughout the article, we mix the notions of system, plant, and model. 
+I propose to clarify throughout as follows: \\ 
+we do not use the term plant (eliminate from text). \\ 
+we have an underlying physical/real/actual system. \\ 
+we have an analogue model of it (1), with continuous variables and continuous time. \\ 
+we discretise time, obtain the reference model for this article (2).  \\ 
+we define specs and properties over this discrete-time model. and we synthesise controllers $u_k$ (not $u(t)$) on it. 
+}
+
 We consider models of physical plants expressed as ordinary differential
@@
 As discussed in Section~\ref{sec:errors}, 
-the considered models must account for finite precision arithmetic semantics deriving from several sources: 
+the considered models must account for the semantics of finite-precision arithmetic, 
+deriving from several sources: 
 we formally bound the numerical error introduced by the finite precision representation of the plant (and its operations), 
@@
 
-Technically, we employ interval arithmetic to bound the error introduced by the finite precision plant, 
-and we use bounded model checking to precisely model the semantics of finite precision arithmetic introduced by the ADC/DAC and the finite precision controller.
-
-\subsection{Bit-precise symbolic model checking}
-As described in Section~\ref{sec:BMC}, we use CBMC, a bit-precise bounded model checker to synthesise and verify candidate controllers. 
+Technically, we employ interval arithmetic to bound the error introduced by the finite-precision plant model, 
+and we use bounded model checking to precisely model the semantics of finite-precision arithmetic, 
+as introduced by the ADC/DAC blocks and by the finite-precision controller.
+
+\subsection{Bit-precise bounded model checking}
+
+As described in Section~\ref{sec:BMC}, we use CBMC, a bit-precise bounded model checker, 
+to synthesise and verify candidate controllers. 
 CBMC manipulates precisely the fixed- or floating-point arithmetic used in the controller, 
-as well as the ADC/DAC conversions, 
-according to the IEEE standards.
-
-\subsection{Interval arithmetic for errors in the numerical representation}
-
-We use finite precision arithmetic to model the plant. 
+as well as the ADC/DAC conversions, according to the IEEE standards.
+
+\subsection{Interval arithmetic for errors in numerical representations}
+
+We use finite-precision arithmetic to model the plant. 
 This is an approximation that speeds up each CEGIS iteration, 

### 2019-01-31 automatica/paper.tex
overall paper

@@
 }
- \caption{Closed-loop digital control setup: 
- the plant is intended to be an analogue model of the underlying real system, 
- whereas the controller is digital. 
+ \caption{Closed-loop digital control setup, 
+ comprising an analogue model of the underlying real system, 
+ alongside a digital controller. 
  \label{fig:digitalsystem}}
@@
 \end{equation*}
-This polynomial is obtained as a function of the state-space matrices $A,B$~\cite{Astrom08}, 
+This polynomial is obtained as a function of the state-space matrices $A_d,B_d$~\cite{Astrom08}, 
 and in particular its order $N$ corresponds to the dimensions of the state variables (above, $n$).  
@@
 
-The fixed-point arithmetic of the digital controller is performed on the upper and lower bound of the intervals from above independently, and the upper and lower bound of the result taken as the interval result.
-For example,
-consider the conversion from plant precision to controller precision performed by the ADC on a single state value.
+The fixed-point arithmetic of the digital controller is performed on the upper and lower bound of the intervals from above independently, 
+and the upper and lower bound of the result is taken as the interval result. For example,
+consider the conversion from the model precision to controller precision performed by the ADC on a single state value.
 The state value is represented as an interval $\{x.high, x.low\}$, and the result of the conversion is an interval where the upper bound is the conversion of $x.high$ and the lower bound is the conversion of $x.low$.
@@
 %
-{\scriptsize
+%{\scriptsize
 \begin{equation*}
@@
 \end{equation*}
-}
+%}
 We encompass this error using interval arithmetic~\cite{moore1966interval} in the precision check shown in Figure~\ref{fig:CEGIS-precision-increment} and detailed in the following section \note{previous section?}.
@@
 %
-\small
 \begin{align*}
@@
 &\phantom{{}=1} ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
-  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{i=n-1}(A_d - B_dK)^iB_dk\delta. 
+  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{n-1}(A_d - B_dK)^iB_dk\delta. 
 \end{align*}
-\normalsize
 %The definition of asymptotic stability is that the system converges to a
@@
 We employ a multi-stage approach that unwinds the dynamics of the model up to a completeness threshold, 
-modelling finite precision arithmetic using bit-precise bounded model checking, 
+encompassing finite precision arithmetic using bit-precise bounded model checking, 
 and then verifying soundness of the resulting controller using interval arithmetic. 
@@
 %\todo{please eventually itemize next}
-\subsection{Block 1}
+\subsection{{\sc synthesize} Block}
 
@@
 candidate solution $K$ that satisfies both the stability requirement and the safety specification, 
-within a finite precision model.  
+within a finite-precision model.  
 In order to synthesize a controller that satisfies the stability requirement, 
-we need the computed characteristic polynomial to satisfy Jury's criterion~\cite{fadali} (see Section~\ref{ssec:stabspecification}).
+we need the characteristic polynomial of the closed-loop model to satisfy Jury's criterion~\cite{fadali} (see Section~\ref{ssec:stabspecification}).
 
@@
 and we synthesize a safe controller by
-unfolding the transition system $k$ steps and by selecting a controller $K$ and a single initial state, 
+unfolding the transition system (.e., the closed-loop model) $k$ steps and by selecting a controller $K$ and a single initial state, 
 such that the states at each step do not violate the safety criteria (see Section~\ref{sec:safety}).    
-That is, we ask the bounded model checker~\cite{ClarkeKL04} if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states, and a given fixed point precision for the controller, and where the input signal remains within the specified bounds.
-This approach is sound if the current $k$ is greater than the completeness threshold (see later step).  
-We~also assume some finite precision for the plant and a sampling rate.
+That is, we ask the bounded model checker~\cite{ClarkeKL04} if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states, and a given fixed-point precision for the controller, and where the input signal remains within the specified bounds.
+This approach is sound \note{you mean complete?} if the current $k$ is greater than the completeness threshold (see later step).  
+We also assume some finite precision for the plant and a given sampling time \note{sampling time comes out of nowhere - also not in the algorithm}.  
 We use a fixed-point precision in this description, given by $\langle I_p,F_p\rangle$, but if we are considering a floating-point controller we will instead model the plant with a floating-point precision, $\langle E_p,M_p\rangle$.
@@
 
-\subsection{Block 2}
+\subsection{{\sc safety} Block}
 

### 2019-01-31 automatica/paper.tex
overall paper

@@
 I propose to clarify throughout as follows: \\ 
-we do not use the term plant (eliminate from text). \\ 
-we have an underlying physical/real/actual system. \\ 
+the term plant is the underlying physical/real/actual system. \\ 
 we have an analogue model of it (1), with continuous variables and continuous time. \\ 
@@
 state, is safe for \emph{all} possible initial states, i.e., it does not reach
-the (complement) unsafe state within $k$ steps.  After unfolding the transition system corresponding
+the (complement) unsafe set within $k$ steps.  After unfolding the transition system corresponding
 to the previously synthesized controller $k$ steps, we check that the safety
@@
 plant precision. A \emph{vertex state} is defined as a state where all values are either equal to the upper or lower
-bound of the initial states. It is sufficient to verify that the controller is safe for all vertex states, as shown next. 
+bound of the states in the initial set. It is sufficient to verify that the controller is safe for all vertex states, as shown next.  
 %We thus only need to iterate through the $2^{n}$ vertex
@@
   \label{th:safety}
-If a controller is safe for each of the corner cases of our hypercube of
-allowed initial states, i.e., the vertex states, it is safe for any initial state in the hypercube. 
+If a controller is safe for each of the corner cases of the hypercube of allowed initial states, 
+i.e., the vertex states, then it is safe for any initial state in the hypercube. 
 \end{theorem}
@@
 
-\subsection{Block 3}
+\subsection{{\sc precision} Block}
 
@@
 
-\subsection{Block 4}
-
-The third {\sc verify} stage, {\sc complete}, checks that the current
+\subsection{{\sc complete} Block}
+
+The third and last {\sc verify} stage, {\sc complete}, checks that the current
 $k$ is large enough to ensure safety for any further time steps.  

### 2019-01-31 automatica/paper.tex
some responses

@@
 \item
-We account for the error introduced by finite precision arithmetic applied over the plant variables $x_k$ and $u_k$ \note{here I have replaced the continuous-time signals with discrete-time ones}, which are actually continuous quantities.
+We account for the error introduced by finite precision arithmetic applied over the plant variables $x_k$ and $u_k$, 
+%\note{here I have replaced the continuous-time signals with discrete-time ones}, 
+which are actually continuous quantities. 
 We guarantee that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller, 
@@
 That is, we ask the bounded model checker~\cite{ClarkeKL04} if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states, and a given fixed-point precision for the controller, and where the input signal remains within the specified bounds.
-This approach is sound \note{you mean complete?} if the current $k$ is greater than the completeness threshold (see later step).  
-We also assume some finite precision for the plant and a given sampling time \note{sampling time comes out of nowhere - also not in the algorithm}.  
+This approach is sound, i.e., the controller produced is guaranteed to be safe, \note{you mean complete?
+No, i mean sound} if the current $k$ is greater than the completeness threshold (see later step).
+We also assume some finite precision for the plant and a given time discretisation, as described in section~\ref{sec:model}.  
 We use a fixed-point precision in this description, given by $\langle I_p,F_p\rangle$, but if we are considering a floating-point controller we will instead model the plant with a floating-point precision, $\langle E_p,M_p\rangle$.
@@
 \includegraphics[width=0.9\textwidth]{figures/synthesis-flow.pdf}
-\caption{Phases of the controller synthesis}
+\caption{The Digital-System Synthesizer (\tool) tool - distinct phases of the controller synthesis }
 \label{fig:synthesis-flow}
@@
 The implementation of the proposed methodology for synthesis of digital controls for physical plants is based on the Digital-System Synthesizer 
-(DSSynth) tool~\cite{DBLP:conf/kbse/AbateBCCCDKKP17}, 
+(\tool) tool~\cite{DBLP:conf/kbse/AbateBCCCDKKP17}, 
 which can be split into two main stages: manual and automated, as illustrated in Fig.~\ref{fig:synthesis-flow} and detailed next.
 
-In Step~1, the user selects the system representation, which can be a transfer function or a state-space model.  
+The first stage comprises the following steps. 
+In Step~1, the user selects the system representation, which can be a transfer function or a state-space model (we focus on the latter in this article).   
 In Step~2, the plant (e.g., in the form of Equation~\eqref{eq:ode1}) is provided~\cite{astrom1997computer}.  
-Finally, in Step~3, the numerical representation for the digital controller implementation must be set by the user, i.e., 
-the finite precision arithmetic that defines the number of bits of integer and fractional parts when using fixed-point arithmetic, 
-or half- and single-precision when using floating-point arithmetic, 
-as well as the input range.  
-% This input, provided by the user, is a specification of the physical plant.
+Finally, in Step~3, the numerical representation for the digital controller implementation must be set by the user: 
+this is the finite-precision arithmetic that defines the number of bits of integer and fractional parts when using fixed-point arithmetic, 
+or half- and single-precision when using floating-point arithmetic. 
+The user also specifies the input range.
 
@@
 \tool~translates the model specification into an ANSI-C program.  
-In Step~B, the proposed CEGIS engine is invoked to synthesize the digital controller w.r.t.~the specification on the digital model.  
+In Step~B, the discussed CEGIS engine is invoked, 
+in order to synthesize the digital controller w.r.t.~the specification given on the model.  
 Finally, in Step~C, the synthesized digital controller is generated.  
-The output by \tool~is the synthesized digital controller represented either as a transfer function or in state-space form.  
+The output of \tool~is the synthesized digital controller \note{you mean: the closed-loop model}, 
+which is represented either as a transfer function or in state-space form (in this article we consider the latter case).  
 The synthesis is considered to be \emph{successful} if a digital controller is
-correctly synthesized w.r.t. effects of finite precision arithmetic; or if there is no solution (no
-controller) for the corresponding physical plant (given the implementation
-requirements), then the synthesis is considered to have \emph{failed} \note{we don't seem to have any such instance.}.
+correctly synthesized with respect to the effects of finite-precision arithmetic; 
+otherwise, if there is no solution (no controller) for the corresponding physical plant (given the implementation requirements), 
+then the synthesis is considered to have \emph{failed}.
 
@@
 and use CBMC as an oracle to answer our queries.  CBMC itself relies on an
-underlying SAT or SMT solver to address verification conditions.  We~model
+underlying SAT/SMT solver to address verification checks.  We~model the 
 effects of finite precision arithmetic 
@@
 download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}
-We further created a VirtualBox OVA image with our tool pre-installed,
-including our MATLAB-generated benchmarks and benchmark shell script with
-instructions to run all benchmarks and to reproduce our
+We have further created a VirtualBox OVA image with our tool pre-installed,
+including our MATLAB-generated benchmarks and benchmark shell script, 
+with instructions to run all benchmarks and to reproduce our
 experiments.\footnote{\note{\url{XXXXXXXXXX}}}
@@
 
-Our benchmark suite consists of 19 SISO case studies extracted from the 
-control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal}. 
-The models are discretized with sampling times ranging from 1s to 0.0001s.
+Our benchmark suite consists of 19 case studies extracted from the control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal}.
+These case studies comprise control models, which we represent in state space form as in \eqref{eq:ode1}.
+The models are time discretized, with sampling times ranging from 1s to 0.0001s. 
 CEGIS initially starts with the coarsest discretisation (i.e., 1s sampling time), and if it fails to find a controller, reduces the sampling time. 
+\note{we need to at least qualitatively mention input selection, initial conditions, and also safe sets. how much can you say? }
 
@@
 The \textit{tapedriver} benchmark models a computer tape driver, 
-that is a computer storage device used to read and write data on magnetic tapes.
-
+that is a computer storage device used to read and write data on magnetic tapes. \\ 
 The \textit{USCG cutter tampa heading angle} plant describes the heading angle dynamics of a Coast 
@@
 the evaluation study has the following experimental goal:  
-
 \begin{enumerate}
-
-\item[EG1] \textbf{(Performance)} Show that the multi-staged 
+\item[] 
+%[EG1] \textbf{(Performance)} 
+Show that the multi-staged 
 %and the abstraction-based 
 CEGIS approach is able to generate finite precision digital controllers using fixed-point and floating-point arithmetic in a reasonable amount of time.
-
 %\item[EG2] \textbf{(Sanity check)} Confirm the stability \note{also?} and safety of the synthesized controllers outside 
@@
 %\note{Where is this done?}
-
 \end{enumerate}
@@
 and \textit{Time} is the total time required to synthesize a controller for the given plant.    
-Timeouts are indicated by~\xmark.  
+Timeouts \note{above: failures} are indicated by~\xmark.  
 The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
@@
 The median run-time for the successful benchmarks is 15.7\,s for fixed-point and 17.8\,s for floating-point implementations, respectively.
-We consider these times to be short enough to be of practical use to control engineers, and thus affirm the validity of EG1.
-
-We present in this paper a selection of case studies for which we are able to synthesise controllers. In the full experimental environment, 
-which is available to download, we include further case studies that we were unable to synthesise controllers for. This is in many cases
-due to timeouts, especially when the completeness threshold is too large, 
-or a controller simply may not exist for a benchmark at a given time discretisation and required controller precision. 
-Yet another source of incompleteness is the inability of the {\sc synthesize} phase to use a large enough precision for the plant model.
+We consider these times to be short enough to be of practical use to control engineers, and thus affirm the validity of 
+%EG1. 
+the objective we have raised.
+
+\smallskip
 
@@
 %representation using MATLAB, achieving EG2 \note{please explain how this check is performed - is the check itself sound?}.  
-A~link to the full experimental environment, including scripts to reproduce the results, all
-benchmarks and the tool, is provided in the
+A~link to the full experimental environment, including scripts to reproduce the results, all benchmarks and the tool, is provided in the
 footnote as an Open Virtual Appliance (OVA).\footnote{\url{XXXX}} 
-The provided experimental environment runs multiple discretisations for each
-benchmark, and lists the fastest as the result synthesis time.
+The provided experimental environment runs multiple discretisations for each benchmark, and lists the fastest as the result synthesis time.
+
+In this article we have presented a selection of case studies for which we have been able to automatically synthesise safe controllers. 
+In the full experimental environment we have included further case studies that we have been unable to synthesise controllers for. 
+This is in many cases due to timeouts, 
+especially when the set completeness threshold is too large, 
+or when a controller simply may not exist for a benchmark at a given time discretisation and required controller precision. 
+Yet another source of incompleteness is the inability of the {\sc synthesize} phase to employ a large-enough precision for the plant model.
 
@@
 
+We identify the following factors as potential limits to the generality of the obtained results.
+
+\begin{itemize}
+
+\item[] 
 \textit{Benchmark selection:} We report an assessment of both our approaches
@@
 
-\textit{Plant precision and discretization heuristics:} Our algorithm to
-select suitable finite precision arithmetic to model the plant behavior 
-increases the precision by 8 bits at each step 
+\item[]
+\textit{Plant model precision and discretization heuristics:} Our algorithm to
+select suitable finite-precision arithmetic to model the plant behavior 
+increases the precision by 8 bits at each step,  
 in order to be compliant with the CBMC type API. 
@@
 
-%\note{So, what about EG2? Shall we assert it? }
+\end{itemize}
 
@@
 
-We have presented an automated approach to synthesize digital
-state-feedback controllers that ensure both stability and safety over state-space models.   
+We have presented an automated approach to synthesize provably-correct digital state-feedback controllers that ensure both stability and safety over state-space models.   
 %The first approach relies on unfolding of the closed-loop model dynamics up to a completeness threshold, while the second
@@
 %
-Our approach is novel within the digital control literature: we provide a fully
-automated synthesis method that is algorithmically and numerically sound,
-considering various error sources in the implementation of the digital
-control algorithm and in the computational modeling of plant dynamics.
-%
-Our experimental results show we are able to synthesize fully automatically 
-safe controllers for diverse benchmarks from the control literature, 
+Our approach is novel within the digital control literature: 
+we provide a fully automated synthesis method that is algorithmically and numerically sound,
+considering various error sources in the implementation of the digital control algorithm and in the computational modeling of plant dynamics.
+%
+Our experimental results show we are able to synthesize fully automatically safe controllers for diverse benchmarks from the control literature, 
 within a reasonable amount of time.  
-
 %

### 2019-01-31 automatica/paper.tex
overall paper

--- 2019-01-31 automatica/paper.tex
@@
 \item
-We account for the error introduced by finite precision arithmetic applied over the plant variables $x_k$ and $u_k$, 
-%\note{here I have replaced the continuous-time signals with discrete-time ones}, 
-which are actually continuous quantities. 
+We account for the error introduced by finite precision arithmetic applied over the plant variables $x_k$ and $u_k$ \note{here I have replaced the continuous-time signals with discrete-time ones}, which are actually continuous quantities.
 We guarantee that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller, 
@@
 That is, we ask the bounded model checker~\cite{ClarkeKL04} if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states, and a given fixed-point precision for the controller, and where the input signal remains within the specified bounds.
-This approach is sound, i.e., the controller produced is guaranteed to be safe, \note{you mean complete?
-No, i mean sound} if the current $k$ is greater than the completeness threshold (see later step).
-We also assume some finite precision for the plant and a given time discretisation, as described in section~\ref{sec:model}.  
+This approach is sound \note{you mean complete?} if the current $k$ is greater than the completeness threshold (see later step).  
+We also assume some finite precision for the plant and a given sampling time \note{sampling time comes out of nowhere - also not in the algorithm}.  
 We use a fixed-point precision in this description, given by $\langle I_p,F_p\rangle$, but if we are considering a floating-point controller we will instead model the plant with a floating-point precision, $\langle E_p,M_p\rangle$.
@@
 \item[]
-\textit{Plant model precision and discretization heuristics:} Our algorithm to
+\textit{Plant precision and discretization heuristics:} Our algorithm to
 select suitable finite-precision arithmetic to model the plant behavior 
@@
 
-We have presented an automated approach to synthesize provably-correct digital state-feedback controllers that ensure both stability and safety over state-space models.   
+We have presented an automated approach to synthesize digital
+state-feedback controllers that ensure both stability and safety over state-space models.   
 %The first approach relies on unfolding of the closed-loop model dynamics up to a completeness threshold, while the second
@@
 %
-Our approach is novel within the digital control literature: 
-we provide a fully automated synthesis method that is algorithmically and numerically sound,
-considering various error sources in the implementation of the digital control algorithm and in the computational modeling of plant dynamics.
-%
-Our experimental results show we are able to synthesize fully automatically safe controllers for diverse benchmarks from the control literature, 
+Our approach is novel within the digital control literature: we provide a fully
+automated synthesis method that is algorithmically and numerically sound,
+considering various error sources in the implementation of the digital
+control algorithm and in the computational modeling of plant dynamics.
+%
+Our experimental results show we are able to synthesize fully automatically 
+safe controllers for diverse benchmarks from the control literature, 
 within a reasonable amount of time.
+
 %

### 2019-01-31 automatica/paper.tex
overall paper

@@
 \item[]
-\textit{Plant precision and discretization heuristics:} Our algorithm to
+\textit{Plant model precision and discretization heuristics:} Our algorithm to
 select suitable finite-precision arithmetic to model the plant behavior 

### 2019-01-31 automatica/paper.tex
responses

@@
 
-Notice that the physical plant model operates over real-valued signals, 
-which means that our verification \note{also called validation below ...
-} phase \note{I'm not sure that it's clear at this point what the verification phase consists of} must also account for the numerical error,
-as well as quantization errors caused by representing the physical plant at finite precision $\mathcal{F}_{\langle I_p,F_p \rangle}$. \note{Also, isn't this paragraph redundant after sec 3.7?}
-
 We further employ $\mathcal{F}_{\langle E,M \rangle}(x)$ to denote a real number $x$ represented in a floating-point domain, 
@@
 an inductive synthesis phase (denoted by {\sc Synthesize} in
-Figure~\ref{fig:CEGIS}) and a validation phase (denoted by {\sc
-  Verify}) \note{why do we use validation-VERIFY; this can be confusing, if you regard validation as a form of soft verification via data ... }, which interacts via a finite set of tests {\sc
+Figure~\ref{fig:CEGIS}) and a verification phase (denoted by {\sc
+  Verify}), which interacts via a finite set of tests {\sc
   inputs} that is updated incrementally.
@@
 candidate solution to the full synthesis formula.  We pass this candidate
-solution to the validation phase, which checks whether it is a full solution
+solution to the verification phase, which checks whether it is a full solution
 (i.e., $P$ satisfies the specification $\phi(a, P)$ for all
@@
 That is, we ask the bounded model checker~\cite{ClarkeKL04} if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states, and a given fixed-point precision for the controller, and where the input signal remains within the specified bounds.
-This approach is sound \note{you mean complete?} if the current $k$ is greater than the completeness threshold (see later step).  
-We also assume some finite precision for the plant and a given sampling time \note{sampling time comes out of nowhere - also not in the algorithm}.  
+This approach is sound, i.e., the controller produced is guaranteed to be safe, if the current $k$ is greater than the completeness threshold (see later step).  
+We also assume some finite precision for the plant and a given time discretisation, as described in section~\ref{sec:model}.  
 We use a fixed-point precision in this description, given by $\langle I_p,F_p\rangle$, but if we are considering a floating-point controller we will instead model the plant with a floating-point precision, $\langle E_p,M_p\rangle$.

### 2019-01-31 automatica/paper.tex
comment on initial states etc

@@
 CEGIS initially starts with the coarsest discretisation (i.e., 1s sampling time), and if it fails to find a controller, reduces the sampling time.
-\note{we need to at least qualitatively mention input selection, initial conditions, and also safe sets. how much can you say? }
+The initial states are bounded between $0.5$ and $-0.5$ for all states, and the safety specification requires that the states remain between $-1.5$ and $1.5$.
+The input bounds are selected individually for each benchmark.
+%\note{we need to at least qualitatively mention input selection, initial conditions, and also safe sets. how much can you say? }
 

### 2019-01-31 automatica/paper.tex
responses

@@
 Finally, in Step~C, the synthesized digital controller is generated.  
-The output of \tool~is the synthesized digital controller \note{you mean: the closed-loop model}, 
+The output of \tool~is the closed-loop model with the synthesized digital controller, 
 which is represented either as a transfer function or in state-space form (in this article we consider the latter case).  
@@
 and \textit{Time} is the total time required to synthesize a controller for the given plant.    
-Timeouts \note{above: failures} are indicated by~\xmark.  
+Timeouts \note{above: failures. No, these are timeouts. I can't find any mention of failures} are indicated by~\xmark.  
 The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is

### 2019-01-31 automatica/paper.tex
overall paper

--- 2019-01-31 automatica/paper.tex
@@
 \keywords{                        % Five to ten keywords,  
-Formal Verification \and Safety requirements \and Dynamical models \and Digital control synthesis \and Analog/Digital conversion \and Time sampling \and Quantization errors \\
+Formal Verification \and Safety requirements \and Dynamical models \and Digital control synthesis \and Analog/Digital conversion 
+%\and Time sampling 
+\and Quantization errors \\
             % chosen from the IFAC 
@@
 
+Notice that the physical plant model operates over real-valued signals, 
+which means that our verification \note{also called validation below ...
+} phase \note{I'm not sure that it's clear at this point what the verification phase consists of} must also account for the numerical error,
+as well as quantization errors caused by representing the physical plant at finite precision $\mathcal{F}_{\langle I_p,F_p \rangle}$. \note{Also, isn't this paragraph redundant after sec 3.7?}
+
 We further employ $\mathcal{F}_{\langle E,M \rangle}(x)$ to denote a real number $x$ represented in a floating-point domain, 
@@
 an inductive synthesis phase (denoted by {\sc Synthesize} in
-Figure~\ref{fig:CEGIS}) and a verification phase (denoted by {\sc
-  Verify}), which interacts via a finite set of tests {\sc
+Figure~\ref{fig:CEGIS}) and a validation phase (denoted by {\sc
+  Verify}) \note{why do we use validation-VERIFY; this can be confusing, if you regard validation as a form of soft verification via data ... }, which interacts via a finite set of tests {\sc
   inputs} that is updated incrementally.
@@
 candidate solution to the full synthesis formula.  We pass this candidate
-solution to the verification phase, which checks whether it is a full solution
+solution to the validation phase, which checks whether it is a full solution
 (i.e., $P$ satisfies the specification $\phi(a, P)$ for all
@@
 That is, we ask the bounded model checker~\cite{ClarkeKL04} if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states, and a given fixed-point precision for the controller, and where the input signal remains within the specified bounds.
-This approach is sound, i.e., the controller produced is guaranteed to be safe, if the current $k$ is greater than the completeness threshold (see later step).  
-We also assume some finite precision for the plant and a given time discretisation, as described in section~\ref{sec:model}.  
+This approach is sound \note{you mean complete?} if the current $k$ is greater than the completeness threshold (see later step).  
+We also assume some finite precision for the plant and a given sampling time \note{sampling time comes out of nowhere - also not in the algorithm}.  
 We use a fixed-point precision in this description, given by $\langle I_p,F_p\rangle$, but if we are considering a floating-point controller we will instead model the plant with a floating-point precision, $\langle E_p,M_p\rangle$.

### 2019-02-01 automatica/paper.tex
URL for ova

--- 2019-01-31 automatica/paper.tex
@@
 caused by artefacts specific to digital control, such as the effects
-of finite precision arithmetic and quantization
+of finite-precision arithmetic and quantization 
 errors introduced by A/D and D/A conversion. 
@@
 
-A~state-space model has known advantages over the transfer function
+A~state-space model has well known advantages over the transfer function
 representation~\cite{Franklin15}, as 
@@
 \item
-We account for the error introduced by finite precision arithmetic applied over the plant variables $x_k$ and $u_k$, 
+We account for the error introduced by finite precision arithmetic applied over the model variables $x_k$ and $u_k$, 
 %\note{here I have replaced the continuous-time signals with discrete-time ones}, 
 which are actually continuous quantities. 
-We guarantee that the precision we use to represent the plant variables is at least as precise as the precision used in the digital controller, 
+We guarantee that the precision we use to represent the model variables is at least as precise as the precision used in the digital controller, 
 and we use interval arithmetic to bound the incurred errors, as further detailed in Section~\ref{sec:numeric_rep}. 
@@
 such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$, so that our controller 
-can be represented accurately in the plant domain.    
+can be represented accurately in the model domain.    
 Thus any mathematical operations in our modelled digital controller will be in the
@@
 This is an approximation that speeds up each CEGIS iteration, 
-however it necessitates a further stage where we verify that the errors introduced by the approximation have not resulted in a controller that is unsafe when executed on a plant expressed over real numbers.
-In this stage, we represent the plant using double-precision floating-point numbers 
+however it necessitates a further stage where we verify that the errors introduced by the approximation have not resulted in a controller that is unsafe when executed on a model expressed over real numbers.
+In this stage, we represent the plant model using double-precision floating-point numbers 
 and we use the Boost interval arithmetic library~\cite{DBLP:journals/tcs/BronnimannMP06} to bound the error in this representation. 
@@
 \item Division: the operations performed by the controllers in the finite precision
-domain do not include division.  However, we do use division in computations within the plant.  
+domain do not include division.  However, we do use division in computations within the model.  
 Here the error depends on whether the divisor is greater or smaller than the dividend:  $\mathcal{F}_{\langle I,F
@@
 The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
-the state of the plant at integer multiples of the sample time.  
+the state of the model at integer multiples of the sample time.  
 %\note{Unlike the CAV18 paper, these gain matrices have not been discussed yet. }
@@
 % $\mat{K}$, 
-we must be able to ensure that the safety of the plant holds at any continuous point in time.  
-In order to do so, we accelerate the dynamics of the plant according to the continuous-time model
+we must be able to ensure that the safety of the model holds at any continuous point in time.  
+In order to do so, we accelerate the dynamics of the model according to the continuous-time model
 semantics in Sec.~\ref{sec:model}.
@@
 We analyze the case of hybrid-time models, 
-namely where the plant dynamics evolve in continuous time, 
+namely where the model dynamics evolve in continuous time, 
 while the feedback dynamics evolve in discrete time.  
-A new input value is accepted by the plant only at sample times $T_s$.
+A new input value is accepted by the model only at sample times $T_s$.
 %but implemented over the continuous-time plant dynamics.
@@
 \eqref{eq:continuous_tube_param}, and where $\mat{A}_d=\mat{A}_{T_s}$,
-$\mat{B}_d=\mat{B}_{T_s}$ describe the discretized plant dynamics with
+$\mat{B}_d=\mat{B}_{T_s}$ describe the discretized model dynamics with
 sample time $T_s$, is the state of the model
@@
 This approach is sound, i.e., the controller produced is guaranteed to be safe, if the current $k$ is greater than the completeness threshold (see later step).  
-We also assume some finite precision for the plant and a given time discretisation, as described in section~\ref{sec:model}.  
+We also assume some finite precision for the model and a given time discretisation, as described in section~\ref{sec:model}.  
 We use a fixed-point precision in this description, given by $\langle I_p,F_p\rangle$, but if we are considering a floating-point controller we will instead model the plant with a floating-point precision, $\langle E_p,M_p\rangle$.
@@
 cast or conversion to the controller precision, and $(plant\_typet)$ to denote a cast or conversion to the 
-plant precision. A \emph{vertex state} is defined as a state where all values are either equal to the upper or lower
+model precision. A \emph{vertex state} is defined as a state where all values are either equal to the upper or lower
 bound of the states in the initial set. It is sufficient to verify that the controller is safe for all vertex states, as shown next.  
@@
 The second {\sc verify} stage, {\sc precision}, 
- restores soundness with respect to the plant precision
+ restores soundness with respect to the plant model precision
 by using interval arithmetic \cite{moore1966interval} to validate the 
@@
 \centering
-\includegraphics[width=\columnwidth]{figures/ct.eps}
+\includegraphics[width=.7\columnwidth]{figures/ct.eps}
 %\vspace{0.1cm}
@@
 with instructions to run all benchmarks and to reproduce our
-experiments.\footnote{\note{\url{XXXXXXXXXX}}}
+experiments.\footnote{\url{http://www.cprover.org/synthesis/}}
 %
@@
 are the fixed- and floating-point precisions used to model the plant, respectively; 
-and \textit{Time} is the total time required to synthesize a controller for the given plant.    
-Timeouts \note{above: failures. No, these are timeouts. I can't find any mention of failures} are indicated by~\xmark.  
+and \textit{Time} is the total time required to synthesize a controller for the given model.    
+Timeouts \note{above: failures. No, these are timeouts. I can't find any mention of failures; 
+From Section 7: ``
+otherwise, if there is no solution (no controller) for the corresponding physical plant (given the implementation requirements), 
+then the synthesis is considered to have \emph{failed}
+''} are indicated by~\xmark.  
 The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is

### 2019-02-01 automatica/paper.tex
overall paper

@@
 and \textit{Time} is the total time required to synthesize a controller for the given plant.    
-Timeouts \note{above: failures. No, these are timeouts. I can't find any mention of failures} are indicated by~\xmark.  
+Timeouts \note{above: failures. No, these are timeouts. I can't find any mention of failures; 
+From Section 7: ``
+otherwise, if there is no solution (no controller) for the corresponding physical plant (given the implementation requirements), 
+then the synthesis is considered to have \emph{failed}
+''} are indicated by~\xmark.  
 The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is

### 2019-02-01 automatica/paper.tex
overall paper

--- 2019-02-01 automatica/paper.tex
@@
 \centering
-\includegraphics[width=.7\columnwidth]{figures/ct.eps}
+\includegraphics[width=\columnwidth]{figures/ct.eps}
 %\vspace{0.1cm}
@@
 with instructions to run all benchmarks and to reproduce our
-experiments.\footnote{\url{http://www.cprover.org/synthesis/}}
+experiments.\footnote{\note{\url{XXXXXXXXXX}}}
 %

### 2019-02-01 automatica/paper.tex
overall paper
tweaks

@@
 The approach uses counterexample-guided inductive synthesis (CEGIS): 
-an inductive generalization phase produces a controller that is known to stabilize the system but that may
+an inductive generalization phase produces a controller that is known to stabilize the model but that may
 not be safe for all initial conditions of the model.  
@@
 
-\note{throughout the article, we mix the notions of system, plant, and model. 
-I propose to clarify throughout as follows: \\ 
-the term plant is the underlying physical/real/actual system. \\ 
-we have an analogue model of it (1), with continuous variables and continuous time. \\ 
-we discretise time, obtain the reference model for this article (2).  \\ 
-we define specs and properties over this discrete-time model. and we synthesise controllers $u_k$ (not $u(t)$) on it. 
-}
-
 We consider models of physical plants expressed as ordinary differential
@@
 
-Models \eqref{eq:ode1} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t)$ and  $u_k$, respectively. 
+Models \eqref{eq:ode1} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u(t)$ and  $u_k$, respectively. 
 Feedback architectures can be employed to manipulate properties and behaviors of the plant:    
@@
 and we use the Boost interval arithmetic library~\cite{DBLP:journals/tcs/BronnimannMP06} to bound the error in this representation. 
-We employ a compositional numerical library to model the fixed point arithmetic for the controller~\cite{CNL} within double-precision floating-point numbers. 
+We employ a compositional numerical library to model the fixed point arithmetic for the controller\footnote{\url{https://github.com/johnmcfarlane/cnl}} within double-precision floating-point numbers. 
 We check that the controller is safe starting from each vertex of the set of initial states,  
@@
 %}
-We encompass this error using interval arithmetic~\cite{moore1966interval} in the precision check shown in Figure~\ref{fig:CEGIS-precision-increment} and detailed in the following section \note{previous section?}.
+We encompass this error using interval arithmetic~\cite{moore1966interval} in the precision check shown in Figure~\ref{fig:CEGIS-precision-increment} and detailed in the previous section.
 
@@
   %consisting of evaluating the
-  progression of the system from $\phi_\mathit{init}$ over time,
+  progression of the model from $\phi_\mathit{init}$ over time,
 $x_{k} \models \phi_\mathit{safety}$. 
@@
 $z^n+\sum_{i=1}^n(a_i-k_i)z^{n-i}=\prod_{i=1}^n (z-\lambda_i) \text{ where } |\lambda_i|<1 \wedge \lambda_i \models \phi_{\Lambda}$.
-These constraints correspond to specific iterations for which the system may be unsafe.
+These constraints correspond to specific iterations for which the model may be unsafe.
 \item Pass the refined abstraction $\phi(K)$ with the new constraints and the list of iterations $k$ to the {\sc synthesize} phase (step (2)).
@@
 The synthesis is considered to be \emph{successful} if a digital controller is
-correctly synthesized with respect to the effects of finite-precision arithmetic; 
-otherwise, if there is no solution (no controller) for the corresponding physical plant (given the implementation requirements), 
-then the synthesis is considered to have \emph{failed}.
+correctly synthesized with respect to the effects of finite-precision arithmetic within the 5 hour time-out.
 
@@
 with instructions to run all benchmarks and to reproduce our
-experiments.\footnote{\note{\url{XXXXXXXXXX}}}
+experiments.\footnote{\url{http://www.cprover.org/DSSynth/}}
 %
@@
 
-Our benchmark suite consists of 19 case studies extracted from the control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal}.
+Our benchmark suite consists of 19 case studies extracted from the control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, gajic2008optimal}.
 These case studies comprise control models, which we represent in state space form as in \eqref{eq:ode1}.
@@
 %identified by least squares 
-of the cell mass concentration controlled through the dilution rate of a bioreactor~\cite{bioreactor}.\\ 
-%
+of the cell mass concentration controlled through the dilution rate of a bioreactor~\cite{bioreactor}.
 The \textit{Chen}
@@
 %discrete 
-model employed as a case study for model-order reduction techniques~\cite{CHEN1979389}.  \\
+model employed as a case study for model-order reduction techniques~\cite{CHEN1979389}.  
 %
@@
 where the control is used to maintain the speed of an automobile constant, 
-tracking a desired speed reference, and compensating disturbances and uncertainties. \\ % related to relief and terrain. 
+tracking a desired speed reference, and compensating disturbances and uncertainties.  % related to relief and terrain. 
 %There are two continuous stirred tank reactor models named 
@@
 %continuous flow stirred-
-tank reactor. \\ 
+tank reactor. 
 The \textit{DC motor} plant  describes the velocity 
@@
 %basic brushed 
-direct-current electrical machine. \\ 
+direct-current electrical machine. 
 %
@@
 %of transitional motion with respect to a longitudinal plane and the rotational motion around the longitudinal axis for 
-of a coaxial helicopter. \\ 
+of a coaxial helicopter. 
 %
@@
 %plant composed by a point mass, which must be equilibrated above the pivot point and is mounted on an one degree of freedom cart that 
-which moves over a track through a DC motor. \\ 
+which moves over a track through a DC motor.  
 %
@@
 % plant composed by a pointer employed in analogue gauges and indicators, 
-whose angular position dynamics is controlled by a magnetic field. \\ 
-%
-The \textit{magsuspension} describes  the dynamic of a magnetic car suspension system. \\
-The \textit{pendulum}  plant consists of a swinging point mass suspended from a frictionless pivot by means of a rod with negligible mass.  \\ 
+whose angular position dynamics is controlled by a magnetic field. 
+%
+The \textit{magsuspension} describes  the dynamic of a magnetic car suspension system. 
+The \textit{pendulum}  plant consists of a swinging point mass suspended from a frictionless pivot by means of a rod with negligible mass.  
 %
 The \textit{Regulator} consists of a linear model of a synchronous electrical machine% connected to an infinite bus
-~\cite{KOKOTOVIC198023}. \\
+~\cite{KOKOTOVIC198023}. 
 The \textit{satellite attitude control system} plant describes the dynamics of a satellite 
@@
 inertial frame during all the excursion. 
-The \textit{springer-mass damper system} plant is a standard model for the dynamics of several mechanical systems. \\ 
+The \textit{springer-mass damper system} plant is a standard model for the dynamics of several mechanical systems. 
 %This benchmark describes a mass, which is fixed to a node by means of a springer and moves under the action of an input force, damping, and elastic force.
-The \textit{steam drum} benchmark describes a linear model for the level dynamics of a boiler steam drum~\cite{boiler}. \\ 
+The \textit{steam drum} benchmark describes a linear model for the level dynamics of a boiler steam drum~\cite{boiler}. 
 %
 The \textit{suspension} models the single-wheel suspension system of a car, 
-namely the relative motion dynamics of a mass-spring-damper model, which connects the car to one of its wheels.  \\
+namely the relative motion dynamics of a mass-spring-damper model, which connects the car to one of its wheels.  
 The \textit{tapedriver} benchmark models a computer tape driver, 
-that is a computer storage device used to read and write data on magnetic tapes. \\ 
+that is a computer storage device used to read and write data on magnetic tapes. 
 The \textit{USCG cutter tampa heading angle} plant describes the heading angle dynamics of a Coast 
@@
 and \textit{Time} is the total time required to synthesize a controller for the given model.    
-Timeouts \note{above: failures. No, these are timeouts. I can't find any mention of failures; 
-From Section 7: ``
-otherwise, if there is no solution (no controller) for the corresponding physical plant (given the implementation requirements), 
-then the synthesis is considered to have \emph{failed}
-''} are indicated by~\xmark.  
+Time-outs are indicated by~\xmark, where the time-out used is 5 hours.  
 The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
@@
 A~link to the full experimental environment, including scripts to reproduce the results, all benchmarks and the tool, is provided in the
-footnote as an Open Virtual Appliance (OVA).\footnote{\url{XXXX}} 
+footnote as an Open Virtual Appliance (OVA).\footnote{\url{www.cprover.org/DSSynth}} 
 The provided experimental environment runs multiple discretisations for each benchmark, and lists the fastest as the result synthesis time.

### 2019-07-05 automatica/response.tex
response to reviews

\documentclass{article}

\setlength\parindent{0pt}

\usepackage{amssymb,latexsym,amsfonts,amsmath, amsthm,color,mathrsfs}
\usepackage[dvipsnames]{xcolor}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{mathtools}
\usepackage{todonotes}
%\usepackage{utf8}
\usepackage{fullpage}
\def\SS#1{{\textcolor{red}{ {\bf SS:} #1}}}
\renewcommand{\b}{\textcolor{blue}}
%\newcommand{\red}{\textcolor{red}}
%
\newcommand{\vold}[1]{\colorbox{red!20}{\bfseries #1}}
\newcommand{\vnew}[1]{\colorbox{blue!30}{\bfseries #1}}

\renewcommand{\t}{\new{(t)}}
\newcommand{\tp}{\new{(t+1)}}
\newcommand{\fei}[1]{{\color{purple}#1 \color{black}}}

\begin{document}
\begin{center}
{\Large Responses to the Comments}\\\vspace{0.3cm}
\today
\end{center}
\vspace{1cm}
Dear Associate Editor and Reviewers,\vspace{0.3cm}
\\
We would like to deeply thank you for reviewing our paper and providing us with the constructive comments and suggestions. We have carefully addressed
all the comments and incorporated them in the revised manuscript.

We present below a detailed discussion of all comments, questions, and concerns raised by the reviewers. The major modifications are highlighted in
blue in the revised manuscript. For clarity,  we also use \vold{v1} and \vnew{v2} in the response letter for referring respectively to the previous
and current versions of the manuscript.
%I do not like color coding that much. And definitely not with red and blue.
\\
\\
With kind regards,\vspace{0.1cm}
\\

%The Authors
%
\newpage

\section{General response}

\section{Response to Reviewer (1)}
\bigskip

{\bf Comment: }{\itshape This paper presents an approach for synthesizing 
digital/software controllers for continuous plants (linear time invariant / LTI) 
such that they satisfy safety/stability requirements, as would show up in closed-loop 
control of cyber-physical systems (CPS). The approach extends earlier work of the authors, 
the primary of which in my view is toward floating-point implementation as opposed to only fixed-point. 
I did not entirely buy that using CEGIS is a contribution, as from looking over the earlier related publications 
(e.g., ASE'17, CAV'17, HSCC'17, SYNT'18 abstract), all of them use CEGIS.}

\vspace{1em}

{\bf Response: }

Do we actually say that CEGIS is a contribution? We should change that

\todo[inline]{check that we don't say CEGIS is a contribution}

\vspace{2em}
{\bf Comment: } {\itshape he results are evaluated on about a dozen and a half examples from the controls literature all with relatively small
dimensionality (2 to 5 real variables in the continuous state space), and while the authors claim the software artifacts and benchmarks are available
for evaluation, when this reviewer browsed to the link (http://www.cprover.org/DSSynth/), a page with "TBD" was shown. I did a little digging and
eventually found what I presume is the same / similar artifacts here: https://github.com/ssvlab/dsverifier and/or http://dsverifier.org/}

\vspace{1em}
{\bf Response: }

Fixed this now

\todo[inline]{Elizabeth: fix this}
\vspace{2em}
{\bf Comment: } {\itshape On the control theory side, the approach uses standard results to synthesize stabilizing controllers for LTI systems,
specifically linear state feedback controllers (u=Kx with a possible reference signal to track), under the assumption the plant is controllable. It
seems the approach requires full-state observability as well, which is a fairly standard assumption as one can typically implement various filters /
estimators (Kalman, Leuenberger, etc.) to ensure state observability assuming detectability of the plant, but the authors should clarify this point to
make the assumptions more precise.}
\vspace{1em}
{\bf Response: }

We have clarified this on page [X] as follows:

\todo[inline]{fix this}
\vspace{2em}
{\bf Comment: } {\itshape Theorem 2 states completeness of the approach, specifically that there exists a finite k for which BMC can be done up-to to
provide a guarantee of future safety for all larger k' > k. Assuming the benchmarks all work up to some completeness threshold, I would like to see
the completeness threshold for each benchmark in table 1. The reason being, I find this result a bit surprising in the given context (albeit not
unbelievable given the focus on LTI) and would like to see further evidence illustrating the point beyond the fairly informal proof, and it would
greatly enhance the existing discussion of timeouts, etc. related to completeness thresholds being too high for some cases.}

\vspace{1em}

{\bf Response: }

We have added the completeness threshold for each benchmark in the table. Note that the completeness threshold is dependent on the controller, 
and a controller with a smaller completeness threshold may exist.

The proof has been elaborated on as follows:

\todo[inline]{Elizabeth: add completeness thresholds to table}
\todo[inline]{Alessandro: Elaborate and make more formal Theorem 2}

\vspace{2em}

{\bf Comment: }
{\itshape I would like to see some additional discussion and/or comparison to hybrid systems reachability. While the focus of this work is on lower-level
software synthesis, if the approach is to be believed in the context of closed-loop systems satisfying specifications, then I would like some
discussion/comparison to that vast existing literature. Specifically, I presume the reason the benchmarks are not scalable beyond ~n=4 dimensionality
(as the n=5 benchmark appears to timeout), which is trivially small at this stage for linear systems (e.g., given a recent HSCC'19 paper on verifying
$R^{billion}$ linear systems, or at least n=100 to n=1000 with standard approaches like SpaceEx), is due to overapproximation error growth with the
interval representation of plant behaviors, whereas most scalable approaches utilize better data structures for representing geometric sets
(zonotopes, support functions, star sets, Taylor models, etc.). This likewise limits the possible applicability of the
approach for nonlinear plants, although there are a host of technical issues in that potential extension. }

\vspace{1em}
{\bf Response: }

\vspace{2em}
{\bf Comment: }
{\itshape Finally, while checking the $2^n$ vertices
are sufficient (theorem 1), I doubt this is necessary, as e.g. the star set approaches avoid this blow-up that would also limit the dimensionality
the approach can work toward.}
\vspace{1em}

{\bf Response: }
\todo[inline]{Alessandro: response to this (Theorem 1)}

\vspace{2em}

{\bf Comment: }
{\itshape While I may have missed it, I didn't see how the controller gain K is initially selected. I presume under the given assumptions a standard approach
such as pole placement, but this should be clarified}
\vspace{1em}
{\bf Response: }

The controller gain is initially nondeterministically selected by the bounded model checking synthesis step, i.e., the SAT solver returns the first assignment to the controller
values it finds
that satisfies the boolean formula which encodes the specification, by using Conflict Driven Clause Learning.
We have added the following sentence to clarify this:
\todo[inline]{add this}

\vspace{2em}
\todo[inline]{fix reviewer 1 typos}

\section{Response to Reviewer (3)}

{\bf Comment: }{\itshape
The verification condition, given in Theorem 1, is wrong. Here is an example system, with dynamics, initial set, and unsafe set.

\begin{verbatim}
x+ = -0.5*y
y+ = 0.5*x
\end{verbatim}

Rotation by 90 degrees in counterclock wise and shrinking it to the origin by 0.5.
\begin{verbatim}
initial set is 0 <= x <= 1 and 0 <= y <= 1.
unsafe set -3/20 <= x <= -2/20 and -3/20 <= y <= -2/20.
\end{verbatim}

It is easy to see that after two transformations, the initial set would be
\begin{verbatim}
-0.25 <= x <= 0 and -0.25 <= y <= 0.
\end{verbatim}
The unsafe set lies completely within the reachable set, but none of the edges in the hyperrectangle is unsafe. The next time the initial set reaches
this quadrant, the reachable set is
\begin{verbatim}
-1/(2^6) <= x <= 0
-1/(2^6) <= y <= 0.
\end{verbatim}

I believe that for this case, the K returned from completeness is 4 or 5.

The same theorem is also present in [1]. The proof, upon careful inspection, is not a proof of the statement given in the theorem. It only proves
that the reachable set is the convex set obtained by the trajectories of the corner states. However, it does not prove that if the trajectories are
safe, their convex combination is also safe. In fact, as given in the above counterexample, the vertices of polytope are safe does not mean that the
convex combination is safe.

I think this bug needs to be fixed in the BMC part of the verifier. Instead of checking the individual trajectories, you should in fact compute the
convex combination of trajectories (reachable set) and then perform the verification.}
\vspace{1em}
{\bf Response: }
\todo[inline]{Alessandro: Response to this (Theorem 1)}
\vspace{2em}

\section{Response to Reviewer (4)}

{\bf Comment:  } {\itshape The safety property in Eqn 3 focuses on interval constraints. One can generate auxiliary variables such that range constraints over them can encode
more complex safety properties. It would be nice to bring this up in the discussion after equation 3 that $x_i$ need not be just $i$-th component of the
state.  Can these also incorporate temporal properties (say STL properties with bounded time-horizon) without having to unroll the transition and
create auxiliary variables that track history explicitly?}
\vspace{1em}
{\bf Response: }

\vspace{2em}
{\bf Comment: } {\itshape The paper would benefit with a restructuring of the discussion. Figure 2 and 3 will be more useful
earlier in the paper (Section 1 or 3).}

\vspace{1em}
{\bf Response: }
We have moved these figures to [] 
\todo[inline]{move figure}
\vspace{2em}

{\bf Comment: } {\itshape
Some other relevant applications of CEGIS to CPS/dynamical systems include: Synthesizing switching logic for
safety and dwell-time requirements in ICCPS, 2010; Synthesis of optimal switching logic for hybrid systems in EMSOFT, 2011, Synthesis of Optimal
Fixed-Point Implementation of Numerical Software Routines in NSV'13, Bridging boolean and quantitative synthesis using smoothed proof search,
POPL'14, Synthesis of fixed-point programs in EMSOFT'13}

\vspace{1em}
{\bf Response: }
We have added a discussion about these applications and results to the related work as follows:
\todo[inline]{add discussion}

\vspace{2em}
{\bf Comment: } {\itshape Could you add one example to the end of Section 4 to show $R_1$, $R_2$, $R_3$, $R_4$ for a simple LTI system? Section 4 is one the most interesting parts
of the paper and its current presentation is a bit sketchy. What are $m_{ij}$?}
\vspace{1em}
{\bf Response: }

\bibliographystyle{alpha}
\bibliography{}

\end{document}

### 2019-07-08 automatica/paper.tex
manuscript

@@
 \newcommand{\reply}[1]{\textcolor{blue}{[#1]}}
+\newcommand{\rev}[1]{\textcolor{blue}{#1}}
 
@@
 by our modelling of the plant using finite precision arithmetic. 
-We reason about safety requirements, which are frequently overlooked in conventional feedback control synthesis, 
+We reason about \rev{specific} safety requirements, which are frequently overlooked in conventional feedback control synthesis, 
 but which nevertheless play a key role in safety-critical applications, of clear concern in numerous modern contexts, 
@@
 the number of stages required to sufficiently unwind the closed-loop model, 
-such that the safety boundaries are not violated for any larger number of iterations.
+such that the safety boundaries \rev{(assumed to be a compact set)} are not violated for any larger number of iterations.
 
@@
 later in this work, we will target a less standard objective,
-namely a quantitative safety requirement, which opens up to more complex specifications \cite{BYG16, Tab09}. 
+namely a quantitative safety requirement \rev{over a convex set around the origin}, 
+which opens up to more complex specifications \cite{BYG16, Tab09}. 
 This is not typical in the digital control literature. We will further precisely account for the digital nature
@@
 %\eqref{eq:closedloopss} 
-meets a given safety specification.  
+meets a given safety specification \rev{that depends on a given set around the origin}.  
 A safety specification gives rise to a requirement on the states of the model, 
@@
 might saturate in view of physical constraints.
+\rev{Notice that we will assume that the set of initial states lies within the safe set, since the contrary leads to dynamics that are trivially unsafe. 
+Furthermore, whilst the problem can handle general hyper-boxes, we will in practice work with set that contain the origin. }
 
@@
 
-We outline here the mathematics behind bounding the errors on the double-precision floating-point numbers. 
+We describe here the mathematics behind bounding the errors on the double-precision floating-point numbers. 
 Recall we use $\mathcal{F}_{\langle E,M \rangle}(x)$ denote a real number $x$ represented in a floating-point domain, 
@@
 \rangle}(x_{k})$; and second, the rounding error introduced by the multiplication operation. 
-Recall this error is modelled precisely by bounded model checking.
+Recall that this error is modelled precisely by bounded model checking.
 
@@
   \label{th:safety}
-If a controller is safe for each of the corner cases of the hypercube of allowed initial states, 
+\rev{Assuming that the initial state is in the safe set, }
+if a controller is safe for each of the corner cases of the hypercube of allowed initial states, 
 i.e., the vertex states, then it is safe for any initial state in the hypercube. 
@@
 \begin{proof}
-Consider the set of initial states, $X_0$, which we assume to be convex since it is a hypercube. 
+Consider the set of initial states, $X_0$, which we note is convex since it is a hypercube. 
 Name $v_i$ its vertices, where $i=1,\ldots, 2^n$.  
@@
 convex set, by those generated from the vertices. 
+\rev{Recall that we have assumed that the initial set lies within the safe set, and that both are (convex) hyper-boxes. The conclusion follows. }
 \qed
 \end{proof}
-In conclusion, we only need to check $2^n$ initial states, 
+Summarising, we only need to check $2^n$ initial states, 
 where $n$ is the dimension of the state space (number of continuous variables).
@@
 since we select them).  The distance of the trajectory from the reference
-point (origin) decreases over time within subspaces related to real-valued
+point (which, for linear models, is the origin) decreases over time within subspaces related to real-valued
 eigenvalues; however, this is not the case in general when dealing with
@@
 CEGIS initially starts with the coarsest discretisation (i.e., 1s sampling time), and if it fails to find a controller, reduces the sampling time.
-The initial states are bounded between $0.5$ and $-0.5$ for all states, and the safety specification requires that the states remain between $-1.5$ and $1.5$.
+The initial states are bounded between $0.5$ and $-0.5$ for all states, and the safety specification requires that the states remain between $-1.5$ and $1.5$ \rev{(as remarked above, the initial set lies within the safe set and contains the origin)}.
 The input bounds are selected individually for each benchmark.

### 2019-07-08 automatica/response.tex
response

@@
 \newcommand{\fei}[1]{{\color{purple}#1 \color{black}}}
+\newcommand{\rev}[1]{\textcolor{blue}{#1}}
 
@@
 make the assumptions more precise.}
+
 \vspace{1em}
 {\bf Response: }
-
-We have clarified this on page [X] as follows:
+We do need full observability of the (states of the) model, and have clarified this on page [X] as follows: \ldots
 
@@
 \todo[inline]{Alessandro: response to this (Theorem 1)}
+
+\rev{It is probably true that the check on all vertices might not be necessary and could be simplified in special cases or under some conditions.
+The check however, as it currently is implemented, does not represent the bottleneck of our overall method, so we can safely reply on it as it stands.
+}
 
@@
 convex combination of trajectories (reachable set) and then perform the verification.}
+
 \vspace{1em}
@@
 \vspace{2em}
+
+\rev{We have emphasised that the initial set is assumed to lie within the safe set - the contrary would trivially result in an unsafe condition. 
+Recall further that the sets are hyper-boxes, thus convex. In view of the linear dynamics of the considered models, in practice both are assumed to contain the origin.  }
 

### 2019-07-09 automatica/response.tex
response

@@
 \begin{center}
-{\Large Responses to the Comments}\\\vspace{0.3cm}
+{\Large Responses to the Reviews}\\\vspace{0.3cm}
 \today
@@
 \\
-
-%The Authors
+The Authors
 %
@@
 
-Do we actually say that CEGIS is a contribution? We should change that
+This journal submission encompasses and summarises the mentioned conference articles (CAV, HSCC, ASE) or workshop abstract (SYNTH). 
+It is a more mature, complete, and comprehensive presentation of the conference material. 
+Of these conference articles, the CAV/HSCC contributions presented the theory underlying the approach, 
+whereas the ASE is a tool paper. 
+The application of the CEGIS architecture to the synthesis of digital controllers for continuous plants is indeed a novel contribution of this line of work.
 
-\todo[inline]{check that we don't say CEGIS is a contribution}
+\todo[inline]{Do we actually say that CEGIS is a contribution?
+We should change that.
+Check that we don't say CEGIS is a contribution.
+AA: I think the reviewers complain about our earlier conference publications.
+We should rectify this view.
+I've added the text above.
+}
 

### 2019-07-09 automatica/response.tex
response

@@
 
-\todo[inline]{Elizabeth: fix this}
+\todo[inline]{Elizabeth: say what the problem was, fix this if possible, then thank the reviewer for pointing this out. }
+
 \vspace{2em}
@@
 {\bf Response: }
-We do need full observability of the (states of the) model, and have clarified this on page [X] as follows: \ldots
+We do need full observability of the (states of the) model, and have clarified this in Section 3.1, as follows: {\it We assume full observability of the states of the model, namely the output states correspond with the model variables.
+} We recall this assumption later in the text.
 
-\todo[inline]{fix this}
 \vspace{2em}
 {\bf Comment: } {\itshape Theorem 2 states completeness of the approach, specifically that there exists a finite k for which BMC can be done up-to to
-provide a guarantee of future safety for all larger k' > k. Assuming the benchmarks all work up to some completeness threshold, I would like to see
+provide a guarantee of future safety for all larger k' greater than k. Assuming the benchmarks all work up to some completeness threshold, I would like to see
 the completeness threshold for each benchmark in table 1. The reason being, I find this result a bit surprising in the given context (albeit not

### 2019-07-09 automatica/paper.tex
response

@@
 We denote with $x(0)$ the model initial condition, which can be non-deterministic.  
+\rev{ We assume full observability of the states of the model, namely the output states correspond with the model variables.  }
 
@@
 
+\rev{ Recall that the states of the model are fully accessible (namely, observable). } 
 We consider state feedback control architectures, 
@@
 in a point closer to the origin.  The synthesized $\overline{k}$ is the completeness threshold. 
+\rev{[I will try to spin this more formally. ]}
 \qed 

### 2019-07-09 automatica/paper.tex
response

@@
   \label{th:safety}
-\rev{Assuming that the initial state is in the safe set, }
+\rev{Assuming that the initial set is included within the safe set, }
 if a controller is safe for each of the corner cases of the hypercube of allowed initial states, 
@@
 %
-An asymptotically stable model is known to have converging dynamics.  Assume the
-closed-loop matrix eigenvalues are not repeated (which is sensible to do,
-since we select them).  The distance of the trajectory from the reference
+An asymptotically stable model is known to have converging dynamics.  
+Assume that the eigenvalues of the closed-loop matrix are not repeated: this is sensible assumption to raise, 
+since the eigenvalues are selected by the user. \rev{ The distance of the trajectory from the reference
 point (which, for linear models, is the origin) decreases over time within subspaces related to real-valued
-eigenvalues; however, this is not the case in general when dealing with
-complex eigenvalues.  Consider the closed-loop matrix that updates the
+eigenvalues (say, $\theta < 0$): this can be shown considering the exponential $e^{\theta t} x_0$ ($x_0$ being the initial condition), 
+which envelops the model dynamics within subspaces and is monotonically decreasing. } 
+\rev{ However, this monotonic decrease cannot be ensured in general when dealing with complex eigenvalues. } 
+Consider the closed-loop matrix that updates the
 states in every discrete time step, and select the eigenvalue $\vartheta$ 
-with the smallest (non-trivial) imaginary value.  Between every pair of
-consecutive time steps $k\,T_s$ and $(k+1)\,T_s$, the dynamics projected on
-the corresponding eigenspace rotate $\vartheta T_s$ radians.  Thus, taking
+with the smallest (non-zero) imaginary part.  
+Between any pair of consecutive time steps $k\,T_s$ and $(k+1)\,T_s$, the dynamics projected on
+the corresponding eigenspace rotate of $\vartheta T_s$ radians.  Thus, taking
 $\overline{k}$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, after
-$k{\geq}\overline{k}$ steps we have completed a full rotation, which results
-in a point closer to the origin.  The synthesized $\overline{k}$ is the completeness threshold. 
-\rev{[I will try to spin this more formally. ]}
+$k{\geq}\overline{k}$ steps the model trajectory has completed a full rotation \rev{within the relevant eigenspace}: 
+this results in a point closer to the origin, \rev{as shown in Fig. \ref{fig:ct}}.  The synthesized $\overline{k}$ is thus a completeness threshold: 
+\rev{indeed, since we have selected $\vartheta$ to be the complex eigenvalue with smallest imaginary part, 
+any other pair of complex eigenvalues will correspond to dynamics that rotate faster within the corresponding eigenspace. 
+Hence, $\overline{k}$ will again represent a completeness threshold. }
 \qed 

### 2019-07-09 automatica/response.tex
response
response and manuscript

@@
 
-The proof has been elaborated on as follows:
+The proof of Theorem 2 has been elaborated and made more comprehensive and detailed.
 
 \todo[inline]{Elizabeth: add completeness thresholds to table}
-\todo[inline]{Alessandro: Elaborate and make more formal Theorem 2}
 
@@
 
+We have reviewed relevant literature on controller synthesis based on finite abstractions, cf. Belta and Tabuada.
+
+Literature on reachability analysis tackles a different problem, namely one of verification, rather than one of control synthesis (which this work focuses on).
+
+Admittedly reachability analysis tool scale quite well (as the reviewer points out), however this is under clear assumptions on model dynamics.
+
+One might argue that reachability analysis tools could be embedded within the CEGIS framework, however they currently lack full soundness: namely they are algorithmically sound, but not numerically sound.
+On the contrary our work is sound on both sides.
+(Shall we mention that indeed we do reachability analysis via Axelerator in CAV17?)
+
 \vspace{2em}
@@
 {\bf Response: }
-\todo[inline]{Alessandro: response to this (Theorem 1)}
 
-\rev{It is probably true that the check on all vertices might not be necessary and could be simplified in special cases or under some conditions.
-The check however, as it currently is implemented, does not represent the bottleneck of our overall method, so we can safely reply on it as it stands.
+\rev{It is probably true that the check on all vertices might not be necessary in general, that that this check might be simplified in special cases or under special conditions.
+The check however, as it currently is implemented, does not represent the bottleneck of our overall method, so we can safely rely on its current form, as it stands.
 }
@@
 
-\rev{We have emphasised that the initial set is assumed to lie within the safe set - the contrary would trivially result in an unsafe condition. 
-Recall further that the sets are hyper-boxes, thus convex. In view of the linear dynamics of the considered models, in practice both are assumed to contain the origin.  }
+\rev{
+Many thanks for this note. 
+Notice that in the submitted manuscript we had focused on special shapes of initial and safe sets, namely (convex) hyper-boxes, which included the origin. 
+In the amended draft, we have better clarified these assumptions, and 
+we have emphasised that the initial set is assumed to lie within the safe set: indeed, the contrary would trivially result in an unsafe condition. 
+In conclusion, recall that the sets are hyper-boxes, thus convex, and that in view of the linear dynamics of the considered models, in practice both are assumed to contain the origin.  }
 
@@
 create auxiliary variables that track history explicitly?}
+
 \vspace{1em}
 {\bf Response: }
+
+\todo[inline]{Eli: can we generalise according to the suggestion of the reviewer?}
 
@@
 \vspace{2em}
-{\bf Comment: } {\itshape Could you add one example to the end of Section 4 to show $R_1$, $R_2$, $R_3$, $R_4$ for a simple LTI system? Section 4 is one the most interesting parts
-of the paper and its current presentation is a bit sketchy. What are $m_{ij}$?}
+{\bf Comment: } {\itshape Could you add one example to the end of Section 4 to show $R_1$, $R_2$, $R_3$, $R_4$ for a simple LTI system?
+
 \vspace{1em}
 {\bf Response: }
+
+\todo[inline]{Eli: can you clarify?}
+
+\vspace{2em}
+{\bf Comment: } {\itshape 
+Section 4 is one the most interesting parts
+of the paper and its current presentation is a bit sketchy. What are $m_{ij}$?} }
+
+\vspace{1em}
+{\bf Response: }
+
+\todo[inline]{Eli: can we elaborate?}
 

### 2019-07-10 automatica/response.tex
wrap
move figures

@@
 whereas the ASE is a tool paper. 
-The application of the CEGIS architecture to the synthesis of digital controllers for continuous plants is indeed a novel contribution of this line of work.
-
-\todo[inline]{Do we actually say that CEGIS is a contribution?
-We should change that.
-Check that we don't say CEGIS is a contribution.
-AA: I think the reviewers complain about our earlier conference publications.
-We should rectify this view.
-I've added the text above.
-}
+The application of the CEGIS architecture to the synthesis of digital controllers for continuous plants is indeed a novel contribution of this line of
+work.
 
 \vspace{2em}
-{\bf Comment: } {\itshape he results are evaluated on about a dozen and a half examples from the controls literature all with relatively small
+{\bf Comment: } {\itshape The results are evaluated on about a dozen and a half examples from the controls literature all with relatively small
 dimensionality (2 to 5 real variables in the continuous state space), and while the authors claim the software artifacts and benchmarks are available
@@
 {\bf Response: }
-We do need full observability of the (states of the) model, and have clarified this in Section 3.1, as follows: {\it We assume full observability of the states of the model, namely the output states correspond with the model variables.
-} We recall this assumption later in the text.
+We do need full observability of the (states of the) model, and have clarified this in Section 3.1, as follows: {\it We assume full observability of
+the states of the model, namely the output states correspond with the model variables.  } We recall this assumption later in the text.
 
@@
 {\bf Comment: } {\itshape Theorem 2 states completeness of the approach, specifically that there exists a finite k for which BMC can be done up-to to
-provide a guarantee of future safety for all larger k' greater than k. Assuming the benchmarks all work up to some completeness threshold, I would like to see
+provide a guarantee of future safety for all larger k' greater than k. Assuming the benchmarks all work up to some completeness threshold, I would
+like to see
 the completeness threshold for each benchmark in table 1. The reason being, I find this result a bit surprising in the given context (albeit not
@@
 {\bf Comment: }
-{\itshape I would like to see some additional discussion and/or comparison to hybrid systems reachability. While the focus of this work is on lower-level
+{\itshape I would like to see some additional discussion and/or comparison to hybrid systems reachability. While the focus of this work is on
+lower-level
 software synthesis, if the approach is to be believed in the context of closed-loop systems satisfying specifications, then I would like some
@@
 
-Literature on reachability analysis tackles a different problem, namely one of verification, rather than one of control synthesis (which this work focuses on).
+Literature on reachability analysis tackles a different problem, namely one of verification, rather than one of control synthesis (which this work
+focuses on).
 
@@
 
-One might argue that reachability analysis tools could be embedded within the CEGIS framework, however they currently lack full soundness: namely they are algorithmically sound, but not numerically sound.
-On the contrary our work is sound on both sides.
-(Shall we mention that indeed we do reachability analysis via Axelerator in CAV17?)
+One might argue that reachability analysis tools could be embedded within the CEGIS framework, however they currently lack full soundness: namely they
+are algorithmically sound, but not numerically sound. On the contrary our work is sound on both sides. (Shall we mention that indeed we do
+reachability analysis via Axelerator in CAV17?)
 
@@
 
-\rev{It is probably true that the check on all vertices might not be necessary in general, that that this check might be simplified in special cases or under special conditions.
-The check however, as it currently is implemented, does not represent the bottleneck of our overall method, so we can safely rely on its current form, as it stands.
-}
+\rev{It is probably true that the check on all vertices might not be necessary in general, that that this check might be simplified in special cases
+or under special conditions. The check however, as it currently is implemented, does not represent the bottleneck of our overall method, so we can
+safely rely on its current form, as it stands. }
 
@@
 {\bf Comment: }
-{\itshape While I may have missed it, I didn't see how the controller gain K is initially selected. I presume under the given assumptions a standard approach
+{\itshape While I may have missed it, I didn't see how the controller gain K is initially selected. I presume under the given assumptions a standard
+approach
 such as pole placement, but this should be clarified}
@@
 
-The controller gain is initially nondeterministically selected by the bounded model checking synthesis step, i.e., the SAT solver returns the first assignment to the controller
+The controller gain is initially nondeterministically selected by the bounded model checking synthesis step, i.e., the SAT solver returns the first
+assignment to the controller
 values it finds
@@
 Many thanks for this note. 
-Notice that in the submitted manuscript we had focused on special shapes of initial and safe sets, namely (convex) hyper-boxes, which included the origin. 
+Notice that in the submitted manuscript we had focused on special shapes of initial and safe sets, namely (convex) hyper-boxes, which included the
+origin. 
 In the amended draft, we have better clarified these assumptions, and 
 we have emphasised that the initial set is assumed to lie within the safe set: indeed, the contrary would trivially result in an unsafe condition. 
-In conclusion, recall that the sets are hyper-boxes, thus convex, and that in view of the linear dynamics of the considered models, in practice both are assumed to contain the origin.  }
+In conclusion, recall that the sets are hyper-boxes, thus convex, and that in view of the linear dynamics of the considered models, in practice both
+are assumed to contain the origin.  }
 
@@
 
-{\bf Comment:  } {\itshape The safety property in Eqn 3 focuses on interval constraints. One can generate auxiliary variables such that range constraints over them can encode
-more complex safety properties. It would be nice to bring this up in the discussion after equation 3 that $x_i$ need not be just $i$-th component of the
+{\bf Comment:  } {\itshape The safety property in Eqn 3 focuses on interval constraints. One can generate auxiliary variables such that range
+constraints over them can encode
+more complex safety properties. It would be nice to bring this up in the discussion after equation 3 that $x_i$ need not be just $i$-th component of
+the
 state.  Can these also incorporate temporal properties (say STL properties with bounded time-horizon) without having to unroll the transition and
@@
 \vspace{1em}
-{\bf Response: }
+{\bf Response:}
+ It is true that we would be able to encode more complex properties by introducing auxiliary variables; however theorem 2 is dependent on the safe set being convex, and 
+so this proof would not necessarily hold with more complex properties. It would be possible to construct time-bounded properties as automata that track history explicitly, but I can't see how
+it would be possible to avoid unwinding the transition relation using this method. In the case of the example given by the reviewer, an STL property with bounded time-horizon, unwinding
+the transition relation would not pose much of a problem anyway as a time-bounded property would only require unwinding up to the time-bound.
 
-\todo[inline]{Eli: can we generalise according to the suggestion of the reviewer?}
+%\todo[inline]{Eli: can we generalise according to the suggestion of the reviewer?}
 
@@
 {\bf Response: }
-We have moved these figures to [] 
-\todo[inline]{move figure}
+We have moved these figures to section 1 and incorporated them into the introduction. We are still referring back to these figures from section 5.
+
 \vspace{2em}

### 2019-07-10 automatica/paper.tex
move figures

@@
 \else
-Our approach
-\fi
-uses a multi-staged technique that starts by devising a
-digital controller that stabilizes the plant model while remaining safe for a
-pre-selected time horizon and a single initial state; then, it verifies
-unbounded-time safety by unfolding the model dynamics, considering the 
-full set of initial states, and checking a \emph{completeness
-threshold}~\cite{DBLP:conf/vmcai/KroeningS03}, i.e., 
-the number of stages required to sufficiently unwind the closed-loop model, 
-such that the safety boundaries \rev{(assumed to be a compact set)} are not violated for any larger number of iterations.
-
-\ifx\axelerator
-Instead of unfolding the dynamics, \emph{the second approach}
-employs \emph{abstract acceleration}~\cite{cattaruzza2015unbounded} to
-evaluate all possible progressions of the model simultaneously. 
-Additionally, this approach uses the \emph{abstraction-refinement} template \cite{DBLP:conf/cav/ClarkeGJLV00},
-enabling one to start with a very simple (abstract) description of the model 
-regardless of the complexity of its dynamics, and to refine to more complex models only 
-when a solution cannot be found.
-\fi
-
-We provide experimental results showing that we are able to
-efficiently synthesize safe controllers for a set of intricate physical
-plant models taken from the digital control literature.
-%\addtodo{add more here once we have the experimental results ready}
-
-%% \addtodo{CD: the novelty compared to CAV'17 needs to be clarified}
-This paper is an extension of~\cite{DBLP:conf/cav/AbateBCCDKKP17}
-and puts forward the following contributions: 
-% (the fourth is a  specific extension to~\cite{DBLP:conf/cav/AbateBCCDKKP17}): 
-%
-\begin{enumerate}
-
-  % Additions from CAV:
-  % continuous time
-  % floating point 
-\item We automatically generate \emph{correct-by-construction} digital
-  controllers using an inductive synthesis approach (CEGIS).  
-  %% This application is non-trivial and addresses challenges specific to digital control
-  %% systems, such as the presence of A/D quantizers and FWL operations.  
-  The automatically computed state-feedback
-  controllers guarantee a given safety specification.
-  The implication is that, as opposed to existing
-  methods for controller synthesis which rely on transfer function
-  representations, we must consider a state-space representation of
-  the physical system. Such a representation requires ensuring the
-  specification over actual traces of the state-space model, alongside the
-  numerical soundness required by the effects of discretisation and
-  finite precision errors.
-
-%%   \note{[this statement is way too broad] Existing methods for controller synthesis rely on transfer 
-%%   function representations, which are inadequate to prove safety requirements. } 
-%% %
-\ifx\axelerator
-\item We provide two novel algorithms: the first, a multi-staged approach, relies on 
-  an unfolding of the dynamics up to a completeness threshold, while the
-  second one is abstraction-based and leverages abstraction/refinement and
-  acceleration to improve scalability while retaining soundness.  %% A third
-  %% algorithm evaluates systems using transfer functions where no state-space
-  %% description is given.
-  Both approaches provide sound synthesis of 
-  feedback controllers and consider the various sources of imprecision in
-  the implementation of the control algorithm and in the modeling of the
-  plant. 
-\else  
-\item We present a novel multi-staged approach to synthesizing digital controllers, using 
-  an unfolding of the dynamics up to a completeness threshold. 
-  We employ bit-precise Bounded Model Checking to account for fixed-point arithmetic used in the implementation of the digital control algorithm, 
-  and interval arithmetic to account for the imprecision in the modelling of the plant. 
-  \fi
-
-%
-%\item We develop a model for different sources of quantization error and account for 
-%  their effect on safety.  We provide bounds that ensure the 
-%  safety of our controllers in a hybrid (i.e., continuous/digital) domain. \note{is this point repeating the previous one?}
-
-%\item While~\cite{DBLP:conf/cav/AbateBCCDKKP17} is restricted to models in discrete 
-%time, \note{in the current paper we present an approach for
-%  soundly evaluating safety in combined continuous-discrete time and space. [this is via the AA-based back-end. However this part is not in the experiments, afaik.]}
-
-\item A limitation of the work in~\cite{DBLP:conf/cav/AbateBCCDKKP17} 
-  is its restriction to fixed-point arithmetic, meaning that fixed-point
-  numbers are employed for the representation of both the plant and the
-  controller, as well as for the operations performed by each of them. 
-  Conversely, in the current paper we also make use of floating-point
-  arithmetic.  
-  %\note{Additionally, we enhance the
-  %implementation with an SMT back-end, allowing us to also use reals in order
-  %to represent the states of the plant.}
-
-\end{enumerate}
-
-%-------------------------------
-\section{Related Work}
-\label{sec:relw}
-%-------------------------------
-
-\textbf{CEGIS --} Program synthesis is the problem of computing
-correct-by-design programs from high-level specifications. Algorithms
-for this problem have made substantial progress in recent years, in
-particular CEGIS, which is a recent approach to inductive synthesis.
-%% borrowing ideas from counterexample guided abstraction refinement
-%% (CEGAR)~\cite{DBLP:conf/cav/ClarkeGJLV00} and
-%% superoptimisation~\cite{DBLP:conf/iclp/BrainCVF06,
-%%   DBLP:conf/asplosss/Massalin87}.  
-%% \note{might be confusing that we relate the CEGAR architecture also to Abstract Acceleration?}   
-%% This approach uses an iterative
-%% process (see Section~\ref{ssec:cegis}), where each iteration performs inductive generalization based
-%% on counterexamples provided by a verification oracle.  In the absence
-%% of complete specifications, oracles are queried to distinguish between
-%% non-equivalent
-%% programs~\cite{jha-icse10,DBLP:conf/fmcad/AlurBJMRSSSTU13}.
-
-%% for instance~\cite{itzhaky2010simple} 
-%% to inductively synthesize invariants for the generation of desired programs.
-
-Program synthesizers are an ideal fit for the synthesis of digital controllers, 
-since the semantics of programs precisely capture the effects of finite precision arithmetic.  
-However the control literature has been oblivious to this relevant connection. 
-A relevant exception is~\cite{DBLP:conf/cdc/RavanbakhshS15}, 
-which employs CEGIS for the synthesis of switching controllers for stabilizing continuous-time
-plants.  
-%with polynomial dynamics.  
-The work 
-% extends to affine systems \note{extension or restriction?}, but 
-is limited by the capacity of the state-of-the-art SMT solvers for solving
-linear arithmetic.  Since this approach uses switching actions for the digital controller, it avoids problems related to
-finite precision arithmetic, but potentially suffers from state-space
-explosion.  Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same
-authors use a CEGIS-based approach for synthesizing continuous-time
-switching controllers that guarantee \emph{reach-while-stay} properties of
-closed-loop systems, i.e., properties that specify a set of goal states and
-safe states (constrained reachability).  This solution is based on
-synthesizing control Lyapunov functions for switched systems that yield
-switching controllers with a guaranteed minimum dwell time in each mode. 
-However, both approaches are unsuitable for the kind of controllers that we seek to
-synthesize, which are not switching in nature.
-
-The work in~\cite{hscc-paper} synthesizes stabilizing controllers for
-continuous plants given as transfer functions by exploiting bit-accurate
-verification of software-implemented digital controllers~\cite{Bessa16}. 
-While this work also uses CEGIS, the approach is restricted to digital
-controllers for stable closed-loop systems expressed as transfer function
-models: this results in a static check on their coefficients.  By contrast,
-in the current paper we consider a state-space representation of the
-physical system, which requires ensuring the specification over actual
-traces of the model, alongside the numerical soundness required by the
-effects of discretisation and the errors related to finite precision arithmetic.
-
-A~state-space model has well known advantages over the transfer function
-representation~\cite{Franklin15}, as 
-% it naturally generalizes to multivariate systems (i.e., with multiple inputs and outputs); and 
-it allows synthesis of controllers with guarantees on the internal dynamics, e.g., 
-%to synthesize controllers that make the closed-loop model 
-\emph{safety}.  Our work indeed focuses on the safety of internal states, 
-which is by and large overlooked in the standard (digital) control literature, 
-by default focussed on stability/regulation/tracking properties.  
-Moreover, our work integrates an abstraction-refinement (CEGAR) step inside the main CEGIS loop.
-
-Beyond CEGIS-based architectures, 
-there is an important line of research on provably correct control synthesis for dynamical models, 
-which leverages formal abstractions. 
-The approach underpinning tools such as Pessoa~\cite{mazo2010pessoa}, related extensions \cite{Anta2010,liu16} and applications \cite{zamani2014} 
-synthesizes correct-by-design embedded control software by abstraction of the model as a finite-state machine, 
-and on the formal control synthesis over safety- and reachability-based temporal properties thereon.  
-%Based on this safety specification, \mbox{Pessoa} can synthesize embedded controller software for a range of
-%properties.  
-The obtained finite controller software can then be implemented over the concrete LTI model. 
-%can be more complicated than
-%the state-feedback control we synthesize, and the properties available cover more detail.  
-However, relying on state-space discretization, this class of approaches is likely to incur scalability limitations.   
-%Along this research line, \cite{Anta2010,liu16} studies the synthesis of digital controllers for
-%continuous dynamics, and \cite{zamani2014} extends the approach to the Network Control Systems setup.
-
-\medskip
-
-\textbf{Discretization Effects in Control Design --}
-%Classical work in control synthesis has often disregarded digitalization effects.
-Recent results in digital control have focused on separate aspects of discretization, 
-e.g. delayed response~\cite{Duggirala2015} and finite precision arithmetic, 
-with the goal either to verify~\cite{daes20161} the correctness of the implementation or to optimize~\cite{oudjida2014design} its design.
-
-There are two different problems that arise from finite precision arithmetic in digital controllers.  
-The first is the error caused by the inability to represent the exact state of the physical system, 
-while the second relates to rounding and saturation errors during mathematical operations.  
-In~\cite{fialho1994stability}, a stability measure based on the error of the digital dynamics ensures that
-the deviation introduced by finite precision arithmetic does not lead to instability.  
-\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$-calculus to synthesise directly a digital controller, 
-so that selected parameters result in stable model dynamics.  
-The analyses in~\cite{DBLP:conf/hybrid/RouxJG15, DBLP:conf/hybrid/WangGRJF16} rely on an
-invariant computation on the discrete dynamics using Semi-Definite
-Programming (SDP):  while the former contribution a uses bounded-input and bounded-output
-(BIBO) notion of stability, the latter employs Lyapunov-based
-quadratic invariants.  In both cases, the SDP solver uses floating-point
-arithmetic and soundness is checked by bounding the obtained error.  
-An alternative is~\cite{park2016scalable}, where the verification of given control code is
-performed against a known model by extracting an LTI model of the code via 
-symbolic execution: to account for rounding errors, upper bounds of their values are 
-introduced in the verification phase.  
-The work in~\cite{picasso2003stabilization} introduces invariant sets as a mechanism to
-bound the quantization error effect on stabilization.  
-% as an invariant set that always converges toward the controllable set.  
-Similarly, 
-\cite{liberzon2003hybrid} evaluates the quantization error dynamics and calculates an upper and lower
-bound for the possible trajectory of the system, up to a finite time. 
-The last two approaches can be placed within the research area known as ``hybrid systems theory.''  
-%This technique works for both linear and non-linear systems.
-The present contribution distances itself from all these cognate results.
-
-%-------------------------------
-\section{Preliminaries}
-%\label{sec:preliminaries}
-\label{sec:model}
-%-------------------------------
-
-%-------------------------------
-%\subsection{State-space representations of LTI models}
-%\label{sec:model}
-%-------------------------------
-
-%% A dynamical system is a system in which a function describes the progression
-%% of a state over time.  In a continuous domain with linear dynamics, it is
-%% described by a first order Ordinary Differential Equation (ODE).
-%% \begin{equation}
-%% \dot{x}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)% +\vec{w}(t)
-%% \label{eq:dynamical}
-%% \end{equation}
-
-%-------------------------------
-\subsection{State-space representation of physical systems}
-\label{sec:model}
-%-------------------------------
-
-\begin{figure*}[htb]
-\centering
-
-\tikzset{add/.style n args={4}{
-    minimum width=6mm,
-    path picture={
-        \draw[circle] 
-            (path picture bounding box.south east) -- (path picture bounding box.north west)
-            (path picture bounding box.south west) -- (path picture bounding box.north east);
-        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
-        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
-        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
-        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
-        }
-    }
- }
-
-\resizebox{1.0\textwidth}{!}{
- \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
-     semithick, initial text=, ampersand replacement=\&,]
-
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
-    \node[draw=none] (r) {$r_k$};
-
-   \& \node[circle,add={-}{+}{}{}] (circle) {};
-   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$u_k$};
-   \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Kd) at ([xshift=0,yshift=-1.5cm]circle)  {\sc $\mat{K}$};
-   \coordinate (kdsouth) at ([yshift=-2cm]Kd);
-
-   \& complexnode/.pic={ 
-      \node[rectangle,dashed,draw,minimum width=3cm,minimum height=1.6cm,label=\textbf{DAC}] (dac) {};
-   %  \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
-   %  \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
-   %  \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
-     \node[fill=gray!20] (zoh) at ([xshift=.0cm]dac.center) {\sc ZOH};
-   }
-
-   \& complexnode/.pic={ 
-      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2.5cm,yshift=.5cm]plant.center)  {\sc $\mat{B}$};
-      \node[draw=none] (u) at ([xshift=-1cm,yshift=.15cm]B)  {$u(t)$};
-      \node[circle,add={+}{+}{}{}] (p1) at ([xshift=-1.3cm,yshift=.5cm]plant.center) {};
-      \node[draw=none] (xdot) at ([xshift=.85cm,yshift=.15cm]p1)  {$\dot{\vec{x}}(t)$};   
-      \node[rectangle,draw,minimum width=1cm] (int) at ([xshift=.5cm,yshift=.5cm]plant.center) {\sc $\int$};
-      \coordinate (xsouth) at ([xshift=1cm]int);
-      \node[draw=none] (x) at ([xshift=1cm,yshift=.15cm]int)  {$\vec{x}(t)$};
-      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (A) at ([xshift=.5cm,yshift=-1cm]plant.center)  {\sc $\mat{A}$};
-      \coordinate (aeast) at ([xshift=1cm]A);
-      \coordinate (awest) at ([xshift=-1.8cm]A);
-    }
-
-   \& complexnode/.pic={ 
-     \node[rectangle,dashed,draw,minimum width=3.5cm,minimum height=1.6cm,label=\textbf{ADC},] (adc) {};
-     \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
-     \coordinate (switch1) at ([xshift=-1cm]adc.center);
-     \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
-   %  \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
-   %  \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
-   %  \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
-     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]switch2)  {$\vec{x}_k$};       
-     \coordinate (ykeast) at ([xshift=2.9cm]switch2);
-     \coordinate (yksouth) at ([xshift=2.9cm,yshift=-3.5cm]switch2);
-   } 
-   \& \coordinate (aux1);
-   \& \\
-  };
-
-%  \path[->] (v1) edge (q1.south);
-%  \path[->] (v2) edge (q2.south);
-  \path[->] (r) edge (circle.west);
-  \path[->] (circle.east) edge (zoh.west);
-%  \path       (q2.east) edge (zoh.west);
-  \path[->] (zoh.east) edge (B.west);
-  \path
-   (B.east) edge (p1.west)
-   (p1.east) edge (int.west)
-   (xsouth) edge (aeast)
-   (aeast) edge (A.east)
-   (A.west) edge (awest)
-   (awest) edge (p1.south)
-   (int.east) edge (switch1.west)
-   (switch2) edge (ykeast);
-  \path
- %  (q1.east) edge (ykeast)
-   (ykeast) edge (yksouth)
-   (yksouth) edge (kdsouth);
-  \path[->]  (kdsouth) edge (Kd.south);
-  \path (Kd.north) edge (circle.south);
- \end{tikzpicture}
-}
- \caption{Closed-loop digital control setup, 
- comprising an analogue model of the underlying real system, 
- alongside a digital controller. 
- \label{fig:digitalsystem}}
-\end{figure*}
-
-We consider models of physical plants expressed as ordinary differential
-equations, which we assume are controllable~\cite{Astrom08}: 
-%
-\begin{align}
-\label{eq:ode1}
-\dot{x}(t) = \mat{A}\vec{x}(t)+ \mat{B} \vec{u}(t), 
-\end{align}
-%
-where 
-$\vec{x} \in \mathbb{R}^n$,  
-$\vec{u} \in \mathbb{R}^p$, 
-$\mat{A} \in \mathbb{R}^{n \times n}$, 
-$\mat{B} \in \mathbb{R}^{n \times p}$,
-and $t \in \mathbb R_0^+$ denotes continuous time. 
-%$\mat{A}$ and $\mat{B}$ are matrices that fully characterize the dynamics of the continuous plant,
-We denote with $x(0)$ the model initial condition, which can be non-deterministic.  
-\rev{ We assume full observability of the states of the model, namely the output states correspond with the model variables.  }
-
-Equation~\eqref{eq:ode1} is 
-%soundly 
-discretized in time~\cite{middleton1990digital,van1978computing} with constant sampling intervals, 
-each of duration $T_s$ (the sample time), 
-into the difference equation
-%
-\begin{align}
-\label{eq:plant}
-\vec{x}_{k+1} =& \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k, 
-\end{align} 
-where 
-$\mat{A}_d=e^{\mat{A}T_s}$ and 
-$\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$, 
-$k \in \mathbb N$ is a discrete counter and where $\vec{x}_{0}=\vec{x}(0)$ denotes the initial state. 
-We assume that specifications on the model concern \eqref{eq:plant}, 
-and plan to devise controllers $\vec{u}_k$ to meet them. 
-(The more general problem of synthesising controllers $u(t)$ for \eqref{eq:ode1} fall outside the scope of the present work.)
-
-\subsection{Digital control synthesis}
-
-Models \eqref{eq:ode1} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u(t)$ and  $u_k$, respectively. 
-Feedback architectures can be employed to manipulate properties and behaviors of the plant:    
-we are interested in the synthesis of digital feedback controllers $u_k$, as in Fig. \ref{fig:digitalsystem},  
-as practically implemented on Field-Programmable Gate Arrays or Digital Signal Processors   
-%This requires us to consider the errors introduced by, we will address the issue of variable quantization, 
-%introduced by ADC/DAC conversion blocks of Figure \ref{fig:digitalsystem}, 
-and as classically studied in \cite{astrom1997computer}.
-
-\rev{ Recall that the states of the model are fully accessible (namely, observable). } 
-We consider state feedback control architectures, 
-where $u_k$ (notice we work with the discretized signal) is $u_k = r_{k} - K x_k$. 
-Here $K \in \mathbb{R}^{p \times n}$ is a state-feedback gain matrix, 
-and $r_{k}$ is a reference signal (again digital). 
-We will assume $r_k=0$, thus obtaining the closed-loop model 
-$\vec{x}_{k+1}=(\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_k$.
-
-The gain matrix $K$ can be set so that the closed-loop discrete dynamics are
-shaped as desired, for instance according to a specific stability goal or
-around a dynamical behavior of interest \cite{astrom1997computer}.  As argued
-later in this work, we will target a less standard objective,
-namely a quantitative safety requirement \rev{over a convex set around the origin}, 
-which opens up to more complex specifications \cite{BYG16, Tab09}. 
-This is not typical in the digital control literature. We will further precisely account for the digital nature
-of the controller, which manipulates quantised signals as discrete quantities represented with
-finite precision. The new approach is fully automated and leverages an approach based on CEGIS.
-
-% Further, we will embrace the digital nature of the
-%controller, which manipulates quantized signals as discrete quantities represented with finite precision.
-
-\subsection{Stability of closed-loop models}
-
-In this work we employ the notion of asymptotic stability within the CEGIS loop,  
-as a means for reducing the search space of possible safe controllers, where the notion of a safe controller
-is defined in the following section. 
-As discussed later, specifically for linear models a safe controller is necessarily asymptotically stable, 
-although the reverse is not true. 
-%as an objective for guessing controllers that are later proven sound over safety requirements.  
-Qualitatively, (local) asymptotic stability is a property denoting the convergence of the model executions towards an equilibrium point, 
-starting from any states in a neighborhood of the point. 
-In the case of linear systems %as in~\eqref{eq:closedloopss}, 
-considered with a zero reference signal, 
-the equilibrium point of interest is the origin (see Figure~\ref{fig:ct} for the portrait of an asymptotically stable execution, converging to the origin).
-
-Of interest for this work, 
-it can be shown that a discrete-time LTI model %as \eqref{eq:closedloopss} 
-is asymptotically stable if all the roots of its characteristic polynomial (i.e., the
-eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
-circle of the complex plane, i.e., if their absolute values are strictly less than
-one~\cite{astrom1997computer}. 
-Whilst this simple sufficient condition can be either generalized or strengthen to be necessary, 
-this is not necessary in the context of this work.    
-What is technically key is that in this paper, 
-we shall express this asymptotic stability as a specification $\phi_\mathit{stability}$, 
-and encode it in terms of a check known as \emph{Jury's criterion}~\cite{fadali}: 
-this is an easy algebraic formula to check the entries of matrix $K$, 
-so that the closed-loop dynamics are shaped as desired.
-
-\subsection{Safety of closed-loop models}
-\label{sec:safety}
-
-We are not limited to the synthesis of digital stabilizing controllers -- a
-well known task in the literature on digital control systems -- but target
-safety requirements with an overall approach that is sound and automated. 
-More specifically, we require that the closed-loop model 
-%\eqref{eq:closedloopss} 
-meets a given safety specification \rev{that depends on a given set around the origin}.  
-A safety specification gives rise to a requirement on the states of the model, 
-namely that they remain within the safe set at all times (that is, over an infinite number of time steps).  
-So the feedback controller (namely the choice of the gain matrix~$K$)
-must ensure that the state never violates the requirement.  Note that an asymptotically 
-stable, closed-loop system is not necessarily a safe system: indeed, the 
-state values may leave the safe part of the state space while they converge
-to the equilibrium, which is typical in the case of oscillatory dynamics. 
-%However, a safe system will always be stable.  
-In~this work, the safety property is expressed as: 
-%
-\begin{equation}
-\label{eq:safetyliteral}
-\phi_\mathit{safety} = \left\{ \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}}\right\},
-\end{equation}
-%
-%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
-%
-where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
-for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ 
-at the $k$-th instant, respectively.  This requires that the states will always be within an $n$-dimensional hyper-box.
-
-\medskip
-
-Beyond the main requirement on safety, it is practically relevant to consider the 
-constraints $\phi_\mathit{input}$ on the input
-signal $u_{k}$ and $\phi_\mathit{init}$ on the initial states $x_0$,
-which we assume have given bounds:
-$\phi_\mathit{input} = \{\forall k \geq 0.\bigwedge_{i=1}^{p} \underline{u} \leq u_{i} \leq \overline{u}\} $,
-and $\phi_\mathit{init} = \{ \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}\}$. 
-The former constraint expresses that control input, possibly shaped via state-feedback, 
-might saturate in view of physical constraints.
-\rev{Notice that we will assume that the set of initial states lies within the safe set, since the contrary leads to dynamics that are trivially unsafe. 
-Furthermore, whilst the problem can handle general hyper-boxes, we will in practice work with set that contain the origin. }
-
-\subsection{Bounded Model Checking}
-\label{sec:BMC}
-
-We employ the bounded model checker CBMC~\cite{DBLP:conf/tacas/KroeningT14} to model the controller behavior on digital signals with finite bit-precision.  
-We express the controller semantics as C programs, which is CBMC's preferred input language.  
-CBMC symbolically executes every instruction in an input program by translating it to a boolean satisfiability problem,
- which is satisfiable iff a certain property about the program holds.  
-CBMC's API allows to specify these properties in the form of assertions in the input program: 
-we set these properties to express that our controllers generate (asymptotically stable and) safe dynamics. 
-%\note{Do we need more details here? Should we explain e.g. SSA or give examples of how assignments, loops,
-%etc. are turned into formulas? Part of Sec.~\ref{sec:errors} can probably be moved here.}
-
-%-------------------------------s
-\subsection{Semantics of finite-precision arithmetics}
-\label{sec:errors}
-
-A key contribution of this work is that, when synthesizing controllers, it precisely replicates the finite-precision arithmetic within the digital controller, 
-thus guaranteeing that controllers implemented with finite-precision arithmetic are safe. 
-The specific components of the model, shown in Figure~\ref{fig:digitalsystem}, we are concerned with are the ADC, digital controller and DAC.
-Details of how we model the behaviour of the finite-precision arithmetic in these components are in Section~\ref{sec:numeric_rep}. 
-We must model the semantics precisely, in order to capture the full behaviour of the model. 
-More specifically, we encompass the following features:
-
-\begin{itemize}
-
-\item The ADC converts the analog signal $x(t)$ into a digital signal $x_k$, which is then fed into the controller, converting a real value to a finite-precision value.  
-% cf. Figure~\ref{fig:digitalsystem}.
-
-\item The controller block performs arithmetic at finite precision. 
-We assume the ADC represents numbers with at least the same precision as the controller, 
-and thus focus on the precision as limited by the controller. 
-This is a reasonable assumption based on commonly available hardware.
-
-\item The DAC converts finite-precision values back to real values. 
-We assume that the input to the DAC has the same precision as the output of the controller. 
-It would, however, be straightforward to account for a DAC or ADC of different precision than the controller in our algorithm, if necessary. 
-\end{itemize}
-
-\subsection{Soundness of modelling}
-
-In addition to precisely replicating the finite-precision arithmetic of the digital controller, 
-we must consider that our \emph{model} itself in \eqref{eq:plant} employs finite-precision arithmetic to represent the behaviour of the real system. 
-In order to guarantee soundness, we therefore encompass the error that is due to modelling (as opposed to the nature of the digital controller):   
-the representations used in the plant model and its arithmetic operations are carried out at finite precision.  
-\begin{itemize} 
-\item
-We account for the error introduced by finite precision arithmetic applied over the model variables $x_k$ and $u_k$, 
-%\note{here I have replaced the continuous-time signals with discrete-time ones}, 
-which are actually continuous quantities. 
-We guarantee that the precision we use to represent the model variables is at least as precise as the precision used in the digital controller, 
-and we use interval arithmetic to bound the incurred errors, as further detailed in Section~\ref{sec:numeric_rep}. 
-\end{itemize}
-
-\subsection{Notation for fixed- and floating-point precision}
-
-In this paper we will use $\mathcal{F}_{\langle I,F \rangle}(x)$ to denote a real number $x$ expressed at a fixed-point precision, 
-using $I$ bits to represent the integer part of the number and $F$ bits to represent its decimal part.  
-In particular, $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ denotes a real number $x$ represented at the fixed-point precision of the controller, 
-and $\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ denotes a real number $x$
-represented at the fixed-point precision of the plant model. 
-$I_c$ and $F_c$ are determined by the controller.  We pick $I_p$ and $F_p$ for our synthesis
-such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$, so that our controller 
-can be represented accurately in the model domain.    
-Thus any mathematical operations in our modelled digital controller will be in the
-range of $\mathcal{F}_{\langle I_c,F_c \rangle}$, and all other calculations
-in our model will be carried out in the range of $\mathcal{F}_{\langle
-I_p,F_p \rangle}$.
-
-We further employ $\mathcal{F}_{\langle E,M \rangle}(x)$ to denote a real number $x$ represented in a floating-point domain, 
-with $E$ bits representing the exponent part and $M$ bits representing the mantissa part. 
-In particular, 
-we use $\mathcal{F}_{\langle E_c,M_c \rangle}(x)$ to denote a real number 
-represented at the floating-point precision of the controller, 
-whereas $\mathcal{F}_{\langle E_p,M_p \rangle}(x)$ denotes a real number represented at the floating-point precision of the plant model.
-
-%-------------------------------
-\subsection{Counterexample-Guided Inductive Synthesis} 
-\label{ssec:cegis}
-%-------------------------------
-
-\begin{figure}
-%\hspace{-2cm}
-\centering
-\resizebox{.8\textwidth}{!}{
- \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto,
- semithick, initial text=, ampersand replacement=\&,]
-
-  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
-},
-          row sep=1cm, column sep=2cm] {
-   \node[fill=gray!20,minimum height=1cm] (synth) {{\sc Synthesize}};
-   \&
-   \node[fill=gray!20,minimum height=1cm] (verif) {{\sc Verify}};
-   \&
-   \node[ellipse,fill=gray!20] (done) {{\sc Done}}; 
-    \\
-  };
-
-   \path
-   ([yshift=2em]synth.east) edge node[align=center] {Candidate} ([yshift=2em]verif.west)
-    ([yshift=-2em]verif.west) edge node[align=center] {Counterex} ([yshift=-2em]synth.east)
-    (verif) edge node {} (done);
- \end{tikzpicture}
-}
- \caption{The general CEGIS framework\label{fig:CEGIS}}
-\end{figure}
-
-In this section, we give a brief description of the CEGIS framework~\cite{jha-icse10,
-  DBLP:conf/asplos/Solar-LezamaTBSS06}, which is illustrated in Figure~\ref{fig:CEGIS}. 
-  CEGIS has been recently developed for the automated synthesis of software programs, 
-  and its setup is naturally that of mathematical logic. We consider an input specification of the form 
-$$
-\exists P .\, \forall a.\, \phi(a, P),
-$$  
-where $P$ ranges over functions (where a function is represented by the program computing it),
-$a$ ranges over ground terms, 
-and $\phi$ is a quantifier-free logical formula. 
-We~interpret the ground terms over some domain~$\mathcal{D}$. 
-This is a design problem, where the objective is to synthesise a valid $P$ that satisfies $\phi$ over all the $a$ terms.
-
-CEGIS breaks down this generally hard synthesis problem into two easier parts:
-%The design consists of two phases,
-an inductive synthesis phase (denoted by {\sc Synthesize} in
-Figure~\ref{fig:CEGIS}) and a verification phase (denoted by {\sc
-  Verify}), which interacts via a finite set of tests {\sc
-  inputs} that is updated incrementally.
-Given the specification $\phi$, the inductive synthesis procedure tries to
-find an existential witness $P$ satisfying the specification
-$\phi(a, P)$ for all $a$ in {\sc inputs} (as opposed to all $a \in
-\mathcal{D}$).
-%
-If the synthesis phase succeeds in finding a witness~$P$, this witness is a
-candidate solution to the full synthesis formula.  We pass this candidate
-solution to the verification phase, which checks whether it is a full solution
-(i.e., $P$ satisfies the specification $\phi(a, P)$ for all
-$a\in\mathcal{D}$).  If this is the case, then the algorithm terminates. 
-Otherwise, additional information is provided to the inductive synthesis
-phase in the form of a new counterexample that is added to the {\sc inputs}
-set and the loop iterates again.  %% More details about the general
-%% architecture of the synthesizer can be found
-%% in~\cite{DBLP:conf/lpar/DavidKL15}.
-If the solution space is finite then the CEGIS loop is guaranteed to
-terminate by either finding a solution or showing that no solution
-exists.
-
-In the context of the formal synthesis of safe controllers, 
-the set of possible {\sc inputs} corresponds to the set of possible initial states and the 
-candidate program $P$ is a candidate controller $K$. The synthesis block generates a candidate
-controller that works for a subset of the possible initial states, and the verifier checks whether 
-the controller works for all possible initial states.
-
-%-------------------------------
-\section{Formal specification of properties on a model} 
-\label{sec:specification}
-%-------------------------------
-
-%While in the previous section we have discussed the generic CEGIS framework, 
-We are now equipped to apply the general CEGIS framework to the synthesis of digital controllers. 
-We start by describing the property that we pass to the synthesizer as the specification $\phi$. 
-Namely, as we are interested in capturing safety (as discussed in Section~\ref{sec:safety}),  
-we use a stability specification to narrow the search space of possible controllers, as detailed in Section~\ref{ssec:stabspecification}.
-
-%-------------------------------
-\subsection{Jury's stability criterion} 
-\label{ssec:stabspecification}
-%-------------------------------
-
-%\note{reminder AA: check throughout use of 'model vs system'}
-
-There are a number of well known procedures to perform stability analysis of dynamical models~\cite{Astrom08}. 
-%which can fit our automatic verification engine.  
-%one based on Schur's decomposition
-%and another one based on Jury's criterion~\cite{astrom1997computer}.  
-Here we select the Jury stability criterion~\cite{astrom1997computer}, 
-in view of its efficiency and ease of integration within our implementation.  
-This method checks the stability working in the complex domain of the characteristic polynomial $S(z)$,  
-%
-% of the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$, where $Y(z)$ is the closed-loop system output and U(z) is the controller output. 
-%% \red{[unclear: what matrix? We need to clarify the relationship
-%% between the char. poly. $S(z)$ and the later quantities $\Delta
-%% N_{G}(z), \Delta D_{G}(z)$ and corresponding controller's
-%% structure.]}.
-%
-considered in its general form as 
-% for $S(z)$:
-%
-\begin{equation*}
-S(z) = a_0z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N,\,\, a_0\neq0. 
-\end{equation*}
-This polynomial is obtained as a function of the state-space matrices $A_d,B_d$~\cite{Astrom08}, 
-and in particular its order $N$ corresponds to the dimensions of the state variables (above, $n$).  
-A sufficient condition for asymptotic stability of the closed-loop LTI model~\cite{astrom1997computer} 
-is when all the roots of its characteristic polynomial $S(z)$ (which correspond to the 
-eigenvalues of the matrix $A_d-B_dK$) are inside the unit circle in the complex plane, 
-i.e., if their absolute values are less than one.
-
-%\note{The characteristic polynomial $S(z)$ represents the dynamical model in \ldots [clarify whether we use the CPol to describe the open- or closed-loop model.
-Relate parameters to matrices A,B,K.
-Notice that these parameters are used later in the Section where AA-based backend is explained.]}
-
-The following matrix $M$ with dimension $(2N-2)\times N$ and elements $m_{(\cdot),(\cdot)}$ is built from the coefficients of $S(z)$ as:  
-%
-$$
-M=\left( 
-\begin{array}{c}
-V^{(0)}\\
-V^{(1)}\\
-\vdots\\
-V^{(N-2)}
-\end{array}
-\right), 
-$$
-%
-where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ is such that:
-%
-$$
-v_{ij}^{(0)}=\left\{
-\begin{array}{ll}
-a_{j-1}, & \mbox{if}~i=1\\
-v_{(1)(N-j+1)}^{0},&\mbox{if}~i=2
-\end{array}
-\right.
-$$
-%
-$$
-v_{ij}^{(k)}=\left\{
-\begin{array}{ll}
-0,&\mbox{if}~j>n-k\\
-v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \mbox{if}~j\leq n-k ~\mbox{and}~i=1\\
-v_{(1)(N-j+1)}^{k},& \mbox{if}~j\leq n-k ~\mbox{and}~i=2\\
-\end{array}
-\right.
-$$
-%
-and where $k \in \mathbb{Z}$ is such that $0 < k < N - 2$.
-
-We have that $S(z)$ is the characteristic polynomial of an asymptotically stable system if and only if the following four conditions $R_i, i = 1,2,3,4,$ hold~\cite{astrom1997computer}: 
-%\begin{itemize}
-%\item 
-$R_1: S(1) > 0$;
-%\item 
-$R_2: (-1)^N S(-1) > 0$;
-%\item 
-$R_3: |a_0| < a_N$;
-%\item 
-$R_4: m_{11} > 0 \wedge\allowbreak
-      m_{31}>0 \wedge\allowbreak
-      m_{51}>0 \wedge \ldots \wedge\allowbreak
-      m_{(2N{-}3)(1)}>0$.
-%\end{itemize}
-
-In conclusion, 
-the asymptotic stability property is finally encoded by a constraint expressed as the following formula: 
-$
-\phi_\mathit{stability} = \{R_1 \wedge R_2 \wedge R_3 \wedge R_4\}.
-$
-
-\ifx\safetyrep
-%-------------------------------
-\subsection{Formal specification of safety} 
-\label{ssec:safespecification}
-%-------------------------------
-
-%We are not limited to the synthesis of digital stabilizing controllers -- a
-%well known task in the literature on digital control systems -- but target
-%safety requirements with an overall approach that is sound and automated. 
-%More specifically, we require that the closed-loop system meets given safety specifications.  
-We target synthesis of safe digital controllers with an overall approach that is sound and automated.
-A safety specification translates into a requirement on the states of the closed-loop model, 
-which hinges on the choice of the feedback controller (namely the choice of the gains in the matrix~$K$):  
-we must ensure that the states of the closed-loop model never violate this requirement, expressed as a given subset of the state space.
-
-Note that a stable closed-loop model is not necessarily a safe model: 
-indeed, the state values may leave the safe part of the state space while they converge
-to the equilibrium, which is typical in the case of oscillatory and convergent dynamics. 
-%However, a safe system will always be stable.  
-In~this work, the safety property is expressed as the formula:
-%
-\begin{equation}
-\label{eq:safetyliteral}
-\phi_\mathit{safety} := \forall k\ge 0,\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
-\end{equation}
-%
-%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
-%
-where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
-for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$, ranging over the $k$-th time step.  
-This means that the states are required to remain within an $n$-dimensional hyper-box at any point in time.
-
-Furthermore, it is practically relevant to consider constraints $\phi_\mathit{input}$ on the input
-signal $u_{k}$ and requirements $\phi_\mathit{init}$ on the initial states $x_0$, 
-both of which we be expressed via given bounds as: 
-$\phi_\mathit{input} := {\forall k\ge 0, \underline{u} \leq u_{k} \leq \overline{u}} $, 
-and $\phi_\mathit{init} := \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}$. 
-For the input signal, these requirements practically mean that the control input saturates in view of physical constraints. 
-\fi
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Numerical representation and soundness} 
-\label{sec:numeric_rep}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-As discussed in Section~\ref{sec:errors}, 
-the considered models must account for the semantics of finite-precision arithmetic, 
-deriving from several sources: 
-we formally bound the numerical error introduced by the finite precision representation of the plant (and its operations), 
-and precisely model the behaviour introduced by the ADC/DAC conversions, 
-as well as the behaviour of the limited-precision arithmetic used by the controller.
-
-Technically, we employ interval arithmetic to bound the error introduced by the finite-precision plant model, 
-and we use bounded model checking to precisely model the semantics of finite-precision arithmetic, 
-as introduced by the ADC/DAC blocks and by the finite-precision controller.
-
-\subsection{Bit-precise bounded model checking}
-
-As described in Section~\ref{sec:BMC}, we use CBMC, a bit-precise bounded model checker, 
-to synthesise and verify candidate controllers. 
-CBMC manipulates precisely the fixed- or floating-point arithmetic used in the controller, 
-as well as the ADC/DAC conversions, according to the IEEE standards.
-
-\subsection{Interval arithmetic for errors in numerical representations}
-
-We use finite-precision arithmetic to model the plant. 
-This is an approximation that speeds up each CEGIS iteration, 
-however it necessitates a further stage where we verify that the errors introduced by the approximation have not resulted in a controller that is unsafe when executed on a model expressed over real numbers.
-In this stage, we represent the plant model using double-precision floating-point numbers 
-and we use the Boost interval arithmetic library~\cite{DBLP:journals/tcs/BronnimannMP06} to bound the error in this representation. 
-We employ a compositional numerical library to model the fixed point arithmetic for the controller\footnote{\url{https://github.com/johnmcfarlane/cnl}} within double-precision floating-point numbers. 
-We check that the controller is safe starting from each vertex of the set of initial states,  
-and show that this is sufficient to prove safety from any state in this set (see Theorem~\ref{th:safety}). %\note{add forward reference to proof.}
-
-We describe here the mathematics behind bounding the errors on the double-precision floating-point numbers. 
-Recall we use $\mathcal{F}_{\langle E,M \rangle}(x)$ denote a real number $x$ represented in a floating-point domain, 
-with $E$ bits representing the exponent part, and $M$ bits representing the mantissa. 
-In general the representation of a real number using the floating-point domain introduces an error, 
-for which an upper bound can be given~\cite{DBLP:conf/arith/BrainTRW15}.
-For each number $x$ represented in the floating-point domain as $\mathcal{F}_{\langle E,M \rangle}(x)$, 
-we store an interval that encompasses this error. 
-Further mathematical operations performed at the precision $\mathcal{F}_{\langle E,M \rangle}(x)$ will propagate this error, 
-leading to further errors for which bounds can be derived~\cite{DBLP:conf/arith/BrainTRW15}.
-
-The fixed-point arithmetic of the digital controller is performed on the upper and lower bound of the intervals from above independently, 
-and the upper and lower bound of the result is taken as the interval result. For example,
-consider the conversion from the model precision to controller precision performed by the ADC on a single state value.
-The state value is represented as an interval $\{x.high, x.low\}$, and the result of the conversion is an interval where the upper bound is the conversion of $x.high$ and the lower bound is the conversion of $x.low$.
-Since the precision of the floating-point domain is greater than the precision of the controller, this is guaranteed to bound the real behaviour of the controller.
-
-\ifx\axelerator
-
-\begin{enumerate}
-
-\item {\bf Truncation:} Let $x$ be a real number, and $\mathcal{F}_{\langle
-I,F \rangle}(x)$ be the same number represented in a fixed-point domain as
-above.  Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the
-error $ \delta_T=x\ \%_{c_m}\ \tilde x$ \note{define tilde x}, and $\%_{c_m}$ is the modulus
-operation performed on the last bit. 
-Thus, $\delta_T$ is the truncation error and it will propagate across
-operations.
-%
-\item {\bf Rounding:} The following errors are due to basic arithmetic operations.  
-Let $c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be
-the truncation errors caused by representing $c_1$ and $c_2$ in a fixed-point domain.
-%
-\begin{enumerate}
-%
-\item Addition/Subtraction: these operations only propagate errors coming
-from truncation of the operands, namely $\mathcal{F}_{\langle I,F
-\rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3$
-with $|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
-%
-\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) \cdot
-\mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3|
-\leq |\delta_{T1}\cdot\mathcal{F}_{\langle I,F \rangle}(c_2)|\allowbreak +
-|\delta_{T2}\cdot\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where
-$c_m=2^{-F}$ as above.
-%
-\item Division: the operations performed by the controllers in the finite precision
-domain do not include division.  However, we do use division in computations within the model.  
-Here the error depends on whether the divisor is greater or smaller than the dividend:  $\mathcal{F}_{\langle I,F
-\rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_{T3}$, 
-where $\delta_{T3}$ is $(\delta_{T2}\cdot c_1 - \delta_{T1}\cdot
-c_2)/(\delta_{T2}^2 - \delta_{T2} c_2)$,
-%
-%$\mathcal{F}_{\langle I,F \rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) =  (c_1 - \delta_{T1})/ (c_2 + \delta_{T2}) + c_m $, where $c_m=2^{-F}$ as above.
-\end{enumerate}
-
-\item {\bf Overflow:}
-The maximum size of a real number $x$ that can be represented in a fixed
-point domain as $\mathcal{F}_{\langle I,F \rangle}(x)$ is $\pm
-(2^{I-1}+1-2^{-F})$.  Numbers outside this range cannot be represented by
-the domain.  If overflow occurs, the interval bound becomes infinite.
-
-\end{enumerate}
-
-Similar bounds for errors introduced by 
-performing basic mathematical operators in floating-point precision can be derived~\cite{DBLP:conf/arith/BrainTRW15}.
-
-\subsection{ADC/DAC quantization errors modelled as noise} 
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-In this section we describe how quantization errors can be modelled as noise. 
-Note that this is only applicable to the acceleration back end, as the multi-stage back 
-end makes use of CBMC's bit-precise model checking capabilities to account 
-for these deterministic errors.
-
-During any given ADC conversion, the continuous signal will be sampled in
-the real domain and transformed by $\mathcal{F}_{\langle I_{c},F_{c} \rangle}
-(x)$ (assuming the ADC discretization is the same as the digital
-implementation).  This sampling uses a threshold which is defined by the
-less significant bit ($q_{c}=c_{m_c}=2^{-F_c}$) 
-%\blue{[this quantity was named $c_m$ above and in other parts of the paper - please uniformise notations]}
-of the ADC and some non-linearities of the circuitry.  The overall conversion is
-%
-$$\mathcal{F}_{\langle I_{c},F_{c} \rangle}(x(t)) = x_k :
-(x_k)_i \in \left[x_i(t)-\frac{q_{c}}{2}\ \ \ \ x_i(t)+\frac{q_{c}}{2}\right] \,.$$
-%
-\reply{where $x_i$ is the $i^{th}$ component of the vector $x$.}
-If we denote the error in the conversion by $\nu_k=x_k-x(t)$ where $t = nk$,
-and $n$ is the sampling time and $k$ the number of steps, then we may define
-some bounds for it $(\nu_k)_i \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
-
-As stated before, we assume that the domain of the
-ADC is that of the digital controller (i.e, the quantizer includes any
-digital gain added in the code).  The process of quantization in the DAC is
-similar except that it is calculating $\mathcal{F}_{\langle I_{dac},F_{dac}
-\rangle} (\mathcal{F}_{\langle I_{c},F_{c} \rangle }(x)) $.  If these domains
-are the same ($I_{c}=I_{dac},\allowbreak F_{c}=F_{dac}$), or if the DAC
-resolution in higher than the ADC, then the DAC quantization error is equal
-to zero.  From the above equations we can now define the ADC and DAC
-quantization noises ${\nu_1}_k \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}]$ and
-${\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}]$, where $q_1=q_{c}$ and 
-$q_2=q_\mathit{dac}$.  This is illustrated in
-Fig.~\ref{fig:digitalsystem} where $Q_1$ is the quantizer of the ADC
-and $Q_2$ the quantizer for the DAC.  These bounds hold irrespective of
-whether the noise is correlated, hence we may use them to over-approximate
-the noise effect on the state space progression over time.  The
-resulting dynamics are
-%
-\begin{align*}
-%\label{eq:pre_quantization}
-{x}_{k+1} = {A}_d{x}_k+{B}_d({u}_k+{{\nu}_2}_k), \quad u_k = -K{x}_{k}+{{\nu}_1}_k, 
-\end{align*}
-%
-which result in the following closed-loop dynamics:
-%
-\begin{align*}
-%\label{eq:quantization}
-{x}_{k+1} &= ({A}_d-{B}_d{K}_d) {x}_k+{B}_d{{\nu}_2}_k +{{\nu}_1}_k \,. 
-\end{align*}
-
-\fi
-
-\subsection{Effect of finite precision arithmetic on safety specification and on stability}
-
-In this section we will quantify how the finite precision arithmetic in a digital controller affects the
-safety and stability properties of an LTI model.
-
-\subsubsection{Safety of closed-loop models with finite precision controller error}
-
-Let us first consider the effect of the quantization errors on safety. 
-Within the controller, state values are manipulated at low precision,
-by means of the vector multiplication $Kx$.
-The inputs are thus computed using the following equation: 
-%
-\begin{align*}
-u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})). 
-\end{align*}
-This induces two types of errors, 
-as detailed above: 
-first, the truncation error due to the representation of $x_k$ as $\mathcal{F}_{\langle I_c,F_c
-\rangle}(x_{k})$; and second, the rounding error introduced by the multiplication operation. 
-Recall that this error is modelled precisely by bounded model checking.
-
-An additional error is due to the representation of the plant dynamics, namely 
-%
-%{\scriptsize
-\begin{equation*}
-x_{k+1} =\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
-\end{equation*}
-%}
-We encompass this error using interval arithmetic~\cite{moore1966interval} in the precision check shown in Figure~\ref{fig:CEGIS-precision-increment} and detailed in the previous section.
-
-\subsubsection{Stability of closed-loop models with fixed-point controller error}
-%-------------------------------
-\label{sec:stab_FWL}
-The validity of Jury's criterion~\cite{fadali} relies on the representation of the closed-loop dynamics $x_{k+1} = (A_d - B_dK) x_k$ at infinite precision.  
-When we employ a fixed-point arithmetic digital controller, the operation above can be expressed as follows, where we use $\mathcal{F}_{\langle I_c,F_c \rangle}$ preceding a variable to indicate that variable is converted into the fixed-point precision given by $\mathcal{F}_{\langle I_c,F_c \rangle}$:
-%
-\begin{align*}
-x_{k+1} &= A_d \cdot x_{k} -B_d(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  
-\end{align*}
-This translates to 
-\begin{align*}
-x_{k+1} &= (A_d  - B_dK) \cdot x_k + B_dK\delta, 
-%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
-\end{align*}
-%
-where $\delta$ is the maximum error that can be introduced by the digital controller in one step, 
-i.e., by reading the states values once and multiplying by $K$ once.  
-We derive the closed form expression for $x_n$ recursively, as follows:
-%
-\begin{align*}
-x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
-x_{2} %&= (A_d  - B_dK)((A_d  - B_dK)x_0 + B_dK\delta ) + B_dK\delta \\
- &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
-%x_{3}  &=(A_d  - B_dK)^3x_0 + (A_d  - B_dK)^2B_dK\delta + (A_d  - B_dK)B_dK\delta + B_dK\delta\\
-x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta +\\
-&\phantom{{}=1} ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
-  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{n-1}(A_d - B_dK)^iB_dk\delta. 
-\end{align*}
-%The definition of asymptotic stability is that the system converges to a
-%reference signal, in this case we use no reference signal so 
-Recall that a closed-loop asymptotically stable system will converge to the origin.  
-We know that the original system with an infinite precision controller is stable, 
-because we have synthesized it to meet Jury's criterion.  
-Hence, $(A_d - B_dK)^n x_0$  must converge to zero as $n \uparrow \infty$. 
-%T%o show that a fixed-point implementation of the same controller will
-%converge to a finite value, we need to show that the infinite sum converges. 
-Furthermore, the power series of a square matrix $T$ converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less
-than~1, and the limit results in 
-%
-%\begin{align*}
-$\sum_{i=0}^{\infty}T^i  = (I - T)^{-1}$, 
-%\end{align*}
-%
-where $I$ is the identity matrix. 
-Thus, the closed-loop model converges to the value 
-%
-\begin{align*}
-0 + (I - A_d + B_dK)^{-1}B_dk\delta \,. 
-\end{align*}
-%
-As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the safe set of states given by the safety specification
-then the synthesized fixed-point controller results in a safe
-closed-loop model.  The convergence to a finite value, however, will not
-make it asymptotically stable.
-However,
-since in this paper we require stability only as a precursor to safety, it
-is sufficient to check that the perturbed model converges to a
-neighborhood of the equilibrium within the safe set.
-
-A similar argument can be made for floating-point arithmetic.
-We can thus disregard these steady-state errors (caused by
-finite precision arithmetic) when stability is ensured by synthesis, and then verify its
-safety accounting for the finite precision errors.
-
-%-------------------------------
-\ifx\axelerator
-\subsection{Abstract acceleration of linear dynamics \note{Shall we move the material on AAccel to the Preliminaries?}} 
-\label{ssec:aa}
-%-------------------------------
-
-We recall a technique called \emph{Abstract Acceleration}~\cite{JSS14,cattaruzza2015unbounded}, 
-which will be key in this work for abstraction-based synthesis.  
-Abstract Acceleration allows one to perform reachability analysis of dynamical models, 
-and as such can be employed for safety verification. 
-% 
-Given an autonomous model of an iterative program with dynamics 
-%
-$\vec{x}_{k+1}=\mat{A_d}\vec{x}_k$, 
-where $\vec{x}_k \in \mathbb{R}^p$, $\mat{A_d} \in \mathbb{R}^{p \times p}$ and $k \in \mathbb N_0$, 
-%\end{equation}
-%
-we want to find all possible states visited over an infinite time horizon starting at a given initial set $X_0$.  
-This set is known as the \emph{reach tube} of the model: 
-%
-\begin{equation}
-\hat{X} = \{ \vec{x}_k: k \in \mathbb N_0, \vec{x}_0 \in X_0 \text{ and } \vec{x}_{k+1}=\mat{A_d}\vec{x}_k\}.
-\end{equation}
-%
-Using Abstract Acceleration we transform this sequential reachability problem into a one-step problem. 
-This has a lot of benefits ~\cite{JSS14}, not least in terms of numerical error propagation.   
-In order to attain this, 
-the problem statement is modified 
-%, by means of acceleration, 
-into 
-%
-\begin{equation}
-\hat{X} = \{ \vec{x}_k=\mat{A_d}^k\vec{x}_0: k \in N_0 \text{ and } \vec{x}_0 \in X_0 \}, 
-\end{equation}
-%
-and a new 
-%model semantics and corresponding 
-set $\hat{X}^\sharp$ is further defined as 
-%
-\begin{equation}\label{eq:aa_reachtube}
-\hat{X} \subseteq \hat{X}^\sharp = \mathcal{A}X_0, \text{ such that } \bigcup_{k \in [0\ \infty)} \mat{A_d}^k \subseteq \mathcal{A}, 
-\end{equation}
-%
-where the newly introduced \emph{abstract reach tube} $\hat{X}^\sharp$ is an
-over-approximation of the reach tube of the model: 
-\cite{JSS14} details algorithms to compute such set, 
-whereas \cite{cattaruzza2015unbounded} extends this to LTI models with inputs as in Eqn. \eqref{eq:plant}.  
-In view of the overall goal of this work, 
-we extend the algorithm to continuous-time models.  
-% and  For this reason we must first look at the acceleration of continuous-time dynamics.
-
-The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
-the state of the model at integer multiples of the sample time.  
-%\note{Unlike the CAV18 paper, these gain matrices have not been discussed yet. }
-However, in order to synthesize a soundly safe controller, 
-% $\mat{K}$, 
-we must be able to ensure that the safety of the model holds at any continuous point in time.  
-In order to do so, we accelerate the dynamics of the model according to the continuous-time model
-semantics in Sec.~\ref{sec:model}.
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Accelerated\! dynamics\! for\! continuous-time\! models\! with\! parametric\! inputs}\label{sec:real_discrete_param_inputs}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-% 
-Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a
-linear function of initial state $\vec{x}_0$ and parametric input $\vec{u}$ as follows.
-
-\begin{lemma}
-The solution to the differential equation $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where
-$\forall t\geq 0\,\vec{u}(t)=\vec{u}$, $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, and $\mat{S}$ are the generalized eigenvectors of $\mat{A}$,
-evaluated at time $T$ is
-%
-\begin{align}
-\label{eq:continuous_tube_param}
-\vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u}\\
- \mat{A}_{T}&= \mat{S}
- \left [ \begin{array}{cccc}
- e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(2)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
-0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
-\vdots & & \ddots & \vdots \\
-0 & \cdots & 0  &e^{T\lambda_i} \\
-\end{array} \right ]
- \mat{S}^{-1}
- \label{eq:continuous_tube_dyn2}\\
- \mat{B}_T&=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}
- \footnote{When $\mat{A}$ is not invertible,
-we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\
-0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$.}\\
- &\text{where } s_i=\left\{\begin{array}{cc}1&\quad gm(\lambda_i)>1\\0&\quad gm(\lambda_i)=1\end{array}\right.,\nonumber
-\end{align}
-%
-$\lambda_i$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.
-%
-
-If $\mat{J}$ is diagonal and there exists a sampling time $T_s$ such that $A_d=e^{\mat{A} T_s}$, 
-then $\forall T \in \mathbb{R}_0^+$ we obtain the known expression 
-$$
-\vec{x}_T=A_d^{\frac{T}{T_s}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_s}})\mat{B}_d\vec{u}, 
-$$
-where $\mat{A}_d^{\frac{T}{T_s}} =e^{log(\mat{A}_d) \frac{T}{T_s}} = e^{\mat{A} T}$. 
-%is the state of the system at time $t=T$. 
-\end{lemma}
-
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\subsubsection{Accelerated dynamics for models with a sampled-time feedback}\label{sec:real_discrete_feedback_inputs}
-%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-We analyze the case of hybrid-time models, 
-namely where the model dynamics evolve in continuous time, 
-while the feedback dynamics evolve in discrete time.  
-A new input value is accepted by the model only at sample times $T_s$.
-%but implemented over the continuous-time plant dynamics.
-%
-%\note{Matrix K has not been introduced yet. }
-\begin{theorem}
-The expression
-%
- \begin{align}
- \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0, 
- \label{eq:cyber_feedback}
- \end{align}
-%
-with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, $\mat{B}_T$ as in
-\eqref{eq:continuous_tube_param}, and where $\mat{A}_d=\mat{A}_{T_s}$,
-$\mat{B}_d=\mat{B}_{T_s}$ describe the discretized model dynamics with
-sample time $T_s$, is the state of the model
-%
-\begin{align*}
- \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
- \vec{u}(t)=\mat{K}\vec{x}_k,  \,
- kT_s \leq t < (k+1)T_s \,. 
-\end{align*}
-%
-\end{theorem}
-\begin{proof}
-\note{let us not number the proofs.}
-%
-Let $\mat{K}$ be a feedback controller such that
-$\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$.  Let the output of the
-feedback system be a zero order holder such that
-$\vec{u}(t'+kT_s)=\vec{u}(kT_s), \text{ for } 0 \leq t' < T_s$.  The closed
-loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
-%
-\begin{align*}
-\vec{x}_{k,t'}=\mat{A}_{t'}\vec{x}_k-\mat{B}_{t'}\mat{K}\vec{x}_k = (\mat{A}_{t'}-\mat{B}_{t'}\mat{K})\vec{x}_k,
-\end{align*}
-where $0 \leq t' < T_s$
-We further explore the dynamics across discrete time boundaries. Let $\mat{A}_d=\mat{A}_{T_s}$ and $\mat{B}_d=\mat{B}_{T_s}$
-\begin{align*}
-\vec{x}_{k}&=\vec{x}_{k-1,T_s}= (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}\\
-\vec{x}_{k,T_s} &= (\mat{A}_d-\mat{B}_d\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}
-\end{align*}
-which accelerating results and setting $T=kT_s+t'$ becomes
-\begin{align}
-\label{eq:feedback_sampled_cont}
-\vec{x}_{k} &= (\mat{A}_d-\mat{B}_d\mat{K}) ^k\vec{x}_0\\
-\vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
-\label{eq:feedback_cont}
-\end{align}
-\end{proof}
-
-%-------------------------------
- \subsubsection{Abstract supports for continuous-time models}
- \label{sec:cont_aasup}
-%-------------------------------
-
-Just as the accelerated dynamics in Eqn.
-\eqref{eq:feedback_sampled_cont} can be abstracted using \eqref{eq:aa_reachtube} (where $\bigcup_{k \in N_0} (\mat{A}_d-\mat{B}_d\mat{K}) ^k \subseteq \mathcal{A}$),
-we use the same principle on Eqn. \eqref{eq:feedback_cont} to obtain 
-\begin{equation}\label{eq:aa_cont_amatrix}
-\bigcup_{T \in [0, T_s], k \in N_0} (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k \subseteq \mathcal{A}.
-\end{equation}
-
-We next describe how to obtain an over-approximation of such a set. 
-This is defined as a polyhedron, expressed as an intersection of hyperplanes. 
-A tight polyhedron can be obtained with hyperplanes that are tangent to the set,  
-which is achieved by selecting a number of points on the boundary of the set, 
-and finding corresponding hyperplanes that are tangent to those points with respect to the dynamics.  
-\note{[you are essentially taking the Lie derivative of the set wrt the dynamics at the selected point?]}
-In order to simplify this procedure, we look at two-dimensional cuts \note{projection?} of the space, one at a time (i.e., for every pair
-of eigenvalues of the closed-loop dynamics, we find a hyperplane tangent to
-the progression of that pair in a two dimensional space and use it as a face of
-the polyhedron).  The difference with~\cite{cattaruzza2015unbounded} is that
-in the continuous case, the tangent is found by derivation \note{cf. `Lie derivative' above} rather than
-differentialtion, thus including all intermediate points \note{[?] in the arc}.
-
-\note{So the case study section should emphasise that the AA-based back-end can handle continuous-time benchmarks/models? 
-It seems like the discussion in this section is not reflected on the case study section yet. }
-
-\fi
-%-------------------------------
-\section{Synthesis of digital controllers with CEGIS} 
-\label{sssec:cegisdig}
-%-------------------------------
-
-In this section we discuss 
-\ifx\axelerator
-two instantiations of CEGIS: 
-the first one,
-named {\it multi-stage} approach, 
-relies on an unfolding of the dynamics up to a completeness threshold; 
-the second one is {\it abstraction-based}, 
-and it leverages abstraction-refinement \cite{DBLP:conf/cav/ClarkeGJLV00} and abstract acceleration (cf. Sec.~\ref{ssec:aa}) to improve scalability,  
-while retaining soundness. 
-\else
-the CEGIS procedure that is used to synthesise safe digital controllers, 
-accounting for the precision issues detailed in the previous sections. 
-We employ a multi-stage approach that unwinds the dynamics of the model up to a completeness threshold, 
-encompassing finite precision arithmetic using bit-precise bounded model checking, 
-and then verifying soundness of the resulting controller using interval arithmetic. 
-\fi
-
-\ifx\axelerator
-%-------------------------------
-\subsection{Multi-stage CEGIS} 
-\label{sssec:naive}
-%-------------------------------
-\fi
-
 \begin{figure*}[htb]
@@
 \end{figure*}
+Our approach
+\fi
+uses a multi-staged technique\rev{, shown in Figure~\ref{fig:CEGIS-precision-increment}}, that starts by devising a
+digital controller that stabilizes the plant model while remaining safe for a
+pre-selected time horizon and a single initial state; then, it verifies
+unbounded-time safety by unfolding the model dynamics, considering the 
+full set of initial states, and checking a \emph{completeness
+threshold}~\cite{DBLP:conf/vmcai/KroeningS03}, i.e., 
+the number of stages required to sufficiently unwind the closed-loop model 
+such that the safety boundaries \rev{(assumed to be a compact set)} are not violated for any 
+larger number of iterations\rev{, illustrated in Figure~\ref{fig:ct}}.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=.7\columnwidth]{figures/ct.eps}
+%\vspace{0.1cm}
+\caption{Completeness threshold for multi-staged verification (quantity $T_s$ is the time discretization step) }
+\label{fig:ct}
+\end{figure}
+
+\ifx\axelerator
+Instead of unfolding the dynamics, \emph{the second approach}
+employs \emph{abstract acceleration}~\cite{cattaruzza2015unbounded} to
+evaluate all possible progressions of the model simultaneously. 
+Additionally, this approach uses the \emph{abstraction-refinement} template \cite{DBLP:conf/cav/ClarkeGJLV00},
+enabling one to start with a very simple (abstract) description of the model 
+regardless of the complexity of its dynamics, and to refine to more complex models only 
+when a solution cannot be found.
+\fi
+
+We provide experimental results showing that we are able to
+efficiently synthesize safe controllers for a set of intricate physical
+plant models taken from the digital control literature.
+%\addtodo{add more here once we have the experimental results ready}
+
+%% \addtodo{CD: the novelty compared to CAV'17 needs to be clarified}
+This paper is an extension of~\cite{DBLP:conf/cav/AbateBCCDKKP17}
+and puts forward the following contributions: 
+% (the fourth is a  specific extension to~\cite{DBLP:conf/cav/AbateBCCDKKP17}): 
+%
+\begin{enumerate}
+
+  % Additions from CAV:
+  % continuous time
+  % floating point 
+\item We automatically generate \emph{correct-by-construction} digital
+  controllers using an inductive synthesis approach (CEGIS).  
+  %% This application is non-trivial and addresses challenges specific to digital control
+  %% systems, such as the presence of A/D quantizers and FWL operations.  
+  The automatically computed state-feedback
+  controllers guarantee a given safety specification.
+  The implication is that, as opposed to existing
+  methods for controller synthesis which rely on transfer function
+  representations, we must consider a state-space representation of
+  the physical system. Such a representation requires ensuring the
+  specification over actual traces of the state-space model, alongside the
+  numerical soundness required by the effects of discretisation and
+  finite precision errors.
+
+%%   \note{[this statement is way too broad] Existing methods for controller synthesis rely on transfer 
+%%   function representations, which are inadequate to prove safety requirements. } 
+%% %
+\ifx\axelerator
+\item We provide two novel algorithms: the first, a multi-staged approach, relies on 
+  an unfolding of the dynamics up to a completeness threshold, while the
+  second one is abstraction-based and leverages abstraction/refinement and
+  acceleration to improve scalability while retaining soundness.  %% A third
+  %% algorithm evaluates systems using transfer functions where no state-space
+  %% description is given.
+  Both approaches provide sound synthesis of 
+  feedback controllers and consider the various sources of imprecision in
+  the implementation of the control algorithm and in the modeling of the
+  plant. 
+\else  
+\item We present a novel multi-staged approach to synthesizing digital controllers, using 
+  an unfolding of the dynamics up to a completeness threshold. 
+  We employ bit-precise Bounded Model Checking to account for fixed-point arithmetic used in the implementation of the digital control algorithm, 
+  and interval arithmetic to account for the imprecision in the modelling of the plant. 
+  \fi
+
+%
+%\item We develop a model for different sources of quantization error and account for 
+%  their effect on safety.  We provide bounds that ensure the 
+%  safety of our controllers in a hybrid (i.e., continuous/digital) domain. \note{is this point repeating the previous one?}
+
+%\item While~\cite{DBLP:conf/cav/AbateBCCDKKP17} is restricted to models in discrete 
+%time, \note{in the current paper we present an approach for
+%  soundly evaluating safety in combined continuous-discrete time and space. [this is via the AA-based back-end. However this part is not in the experiments, afaik.]}
+
+\item A limitation of the work in~\cite{DBLP:conf/cav/AbateBCCDKKP17} 
+  is its restriction to fixed-point arithmetic, meaning that fixed-point
+  numbers are employed for the representation of both the plant and the
+  controller, as well as for the operations performed by each of them. 
+  Conversely, in the current paper we also make use of floating-point
+  arithmetic.  
+  %\note{Additionally, we enhance the
+  %implementation with an SMT back-end, allowing us to also use reals in order
+  %to represent the states of the plant.}
+
+\end{enumerate}
+
+%-------------------------------
+\section{Related Work}
+\label{sec:relw}
+%-------------------------------
+
+\textbf{CEGIS --} Program synthesis is the problem of computing
+correct-by-design programs from high-level specifications. Algorithms
+for this problem have made substantial progress in recent years, in
+particular CEGIS, which is a recent approach to inductive synthesis.
+%% borrowing ideas from counterexample guided abstraction refinement
+%% (CEGAR)~\cite{DBLP:conf/cav/ClarkeGJLV00} and
+%% superoptimisation~\cite{DBLP:conf/iclp/BrainCVF06,
+%%   DBLP:conf/asplosss/Massalin87}.  
+%% \note{might be confusing that we relate the CEGAR architecture also to Abstract Acceleration?}   
+%% This approach uses an iterative
+%% process (see Section~\ref{ssec:cegis}), where each iteration performs inductive generalization based
+%% on counterexamples provided by a verification oracle.  In the absence
+%% of complete specifications, oracles are queried to distinguish between
+%% non-equivalent
+%% programs~\cite{jha-icse10,DBLP:conf/fmcad/AlurBJMRSSSTU13}.
+
+%% for instance~\cite{itzhaky2010simple} 
+%% to inductively synthesize invariants for the generation of desired programs.
+
+Program synthesizers are an ideal fit for the synthesis of digital controllers, 
+since the semantics of programs precisely capture the effects of finite precision arithmetic.  
+However the control literature has been oblivious to this relevant connection. 
+A relevant exception is~\cite{DBLP:conf/cdc/RavanbakhshS15}, 
+which employs CEGIS for the synthesis of switching controllers for stabilizing continuous-time
+plants.  
+%with polynomial dynamics.  
+The work 
+% extends to affine systems \note{extension or restriction?}, but 
+is limited by the capacity of the state-of-the-art SMT solvers for solving
+linear arithmetic.  Since this approach uses switching actions for the digital controller, it avoids problems related to
+finite precision arithmetic, but potentially suffers from state-space
+explosion.  Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same
+authors use a CEGIS-based approach for synthesizing continuous-time
+switching controllers that guarantee \emph{reach-while-stay} properties of
+closed-loop systems, i.e., properties that specify a set of goal states and
+safe states (constrained reachability).  This solution is based on
+synthesizing control Lyapunov functions for switched systems that yield
+switching controllers with a guaranteed minimum dwell time in each mode. 
+However, both approaches are unsuitable for the kind of controllers that we seek to
+synthesize, which are not switching in nature.
+
+The work in~\cite{hscc-paper} synthesizes stabilizing controllers for
+continuous plants given as transfer functions by exploiting bit-accurate
+verification of software-implemented digital controllers~\cite{Bessa16}. 
+While this work also uses CEGIS, the approach is restricted to digital
+controllers for stable closed-loop systems expressed as transfer function
+models: this results in a static check on their coefficients.  By contrast,
+in the current paper we consider a state-space representation of the
+physical system, which requires ensuring the specification over actual
+traces of the model, alongside the numerical soundness required by the
+effects of discretisation and the errors related to finite precision arithmetic.
+
+A~state-space model has well known advantages over the transfer function
+representation~\cite{Franklin15}, as 
+% it naturally generalizes to multivariate systems (i.e., with multiple inputs and outputs); and 
+it allows synthesis of controllers with guarantees on the internal dynamics, e.g., 
+%to synthesize controllers that make the closed-loop model 
+\emph{safety}.  Our work indeed focuses on the safety of internal states, 
+which is by and large overlooked in the standard (digital) control literature, 
+by default focussed on stability/regulation/tracking properties.  
+Moreover, our work integrates an abstraction-refinement (CEGAR) step inside the main CEGIS loop.
+
+Beyond CEGIS-based architectures, 
+there is an important line of research on provably correct control synthesis for dynamical models, 
+which leverages formal abstractions. 
+The approach underpinning tools such as Pessoa~\cite{mazo2010pessoa}, related extensions \cite{Anta2010,liu16} and applications \cite{zamani2014} 
+synthesizes correct-by-design embedded control software by abstraction of the model as a finite-state machine, 
+and on the formal control synthesis over safety- and reachability-based temporal properties thereon.  
+%Based on this safety specification, \mbox{Pessoa} can synthesize embedded controller software for a range of
+%properties.  
+The obtained finite controller software can then be implemented over the concrete LTI model. 
+%can be more complicated than
+%the state-feedback control we synthesize, and the properties available cover more detail.  
+However, relying on state-space discretization, this class of approaches is likely to incur scalability limitations.   
+%Along this research line, \cite{Anta2010,liu16} studies the synthesis of digital controllers for
+%continuous dynamics, and \cite{zamani2014} extends the approach to the Network Control Systems setup.
+
+\medskip
+
+\textbf{Discretization Effects in Control Design --}
+%Classical work in control synthesis has often disregarded digitalization effects.
+Recent results in digital control have focused on separate aspects of discretization, 
+e.g. delayed response~\cite{Duggirala2015} and finite precision arithmetic, 
+with the goal either to verify~\cite{daes20161} the correctness of the implementation or to optimize~\cite{oudjida2014design} its design.
+
+There are two different problems that arise from finite precision arithmetic in digital controllers.  
+The first is the error caused by the inability to represent the exact state of the physical system, 
+while the second relates to rounding and saturation errors during mathematical operations.  
+In~\cite{fialho1994stability}, a stability measure based on the error of the digital dynamics ensures that
+the deviation introduced by finite precision arithmetic does not lead to instability.  
+\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$-calculus to synthesise directly a digital controller, 
+so that selected parameters result in stable model dynamics.  
+The analyses in~\cite{DBLP:conf/hybrid/RouxJG15, DBLP:conf/hybrid/WangGRJF16} rely on an
+invariant computation on the discrete dynamics using Semi-Definite
+Programming (SDP):  while the former contribution a uses bounded-input and bounded-output
+(BIBO) notion of stability, the latter employs Lyapunov-based
+quadratic invariants.  In both cases, the SDP solver uses floating-point
+arithmetic and soundness is checked by bounding the obtained error.  
+An alternative is~\cite{park2016scalable}, where the verification of given control code is
+performed against a known model by extracting an LTI model of the code via 
+symbolic execution: to account for rounding errors, upper bounds of their values are 
+introduced in the verification phase.  
+The work in~\cite{picasso2003stabilization} introduces invariant sets as a mechanism to
+bound the quantization error effect on stabilization.  
+% as an invariant set that always converges toward the controllable set.  
+Similarly, 
+\cite{liberzon2003hybrid} evaluates the quantization error dynamics and calculates an upper and lower
+bound for the possible trajectory of the system, up to a finite time. 
+The last two approaches can be placed within the research area known as ``hybrid systems theory.''  
+%This technique works for both linear and non-linear systems.
+The present contribution distances itself from all these cognate results.
+
+%-------------------------------
+\section{Preliminaries}
+%\label{sec:preliminaries}
+\label{sec:model}
+%-------------------------------
+
+%-------------------------------
+%\subsection{State-space representations of LTI models}
+%\label{sec:model}
+%-------------------------------
+
+%% A dynamical system is a system in which a function describes the progression
+%% of a state over time.  In a continuous domain with linear dynamics, it is
+%% described by a first order Ordinary Differential Equation (ODE).
+%% \begin{equation}
+%% \dot{x}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)% +\vec{w}(t)
+%% \label{eq:dynamical}
+%% \end{equation}
+
+%-------------------------------
+\subsection{State-space representation of physical systems}
+\label{sec:model}
+%-------------------------------
+
+\begin{figure*}[htb]
+\centering
+
+\tikzset{add/.style n args={4}{
+    minimum width=6mm,
+    path picture={
+        \draw[circle] 
+            (path picture bounding box.south east) -- (path picture bounding box.north west)
+            (path picture bounding box.south west) -- (path picture bounding box.north east);
+        \node[draw=none] at ($(path picture bounding box.south)+(0,0.13)$)     {\small #1};
+        \node[draw=none] at ($(path picture bounding box.west)+(0.13,0)$)      {\small #2};
+        \node[draw=none] at ($(path picture bounding box.north)+(0,-0.13)$)    {\small #3};
+        \node[draw=none] at ($(path picture bounding box.east)+(-0.13,0)$)     {\small #4};
+        }
+    }
+ }
+
+\resizebox{1.0\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.6,-,>=stealth',shorten >=.2pt,auto,
+     semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.6cm] {
+    \node[draw=none] (r) {$r_k$};
+
+   \& \node[circle,add={-}{+}{}{}] (circle) {};
+   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$u_k$};
+   \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (Kd) at ([xshift=0,yshift=-1.5cm]circle)  {\sc $\mat{K}$};
+   \coordinate (kdsouth) at ([yshift=-2cm]Kd);
+
+   \& complexnode/.pic={ 
+      \node[rectangle,dashed,draw,minimum width=3cm,minimum height=1.6cm,label=\textbf{DAC}] (dac) {};
+   %  \node[circle,add={+}{+}{}{},fill=gray!20] (q2) at ([xshift=-.65cm]dac.center) {};
+   %  \node[draw=none] (q2t)  at ([yshift=.55cm]q2) {{\sc Q2}};
+   %  \node[draw=none] (v2)  at ([yshift=-1.5cm]q2) {$\nu_2$};
+     \node[fill=gray!20] (zoh) at ([xshift=.0cm]dac.center) {\sc ZOH};
+   }
+
+   \& complexnode/.pic={ 
+      \node[rectangle,dashed,draw,minimum width=8cm,minimum height=3.5cm,label=\textbf{Plant}] (plant)  at ([yshift=-.5cm]dac.center) {};
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (B) at ([xshift=-2.5cm,yshift=.5cm]plant.center)  {\sc $\mat{B}$};
+      \node[draw=none] (u) at ([xshift=-1cm,yshift=.15cm]B)  {$u(t)$};
+      \node[circle,add={+}{+}{}{}] (p1) at ([xshift=-1.3cm,yshift=.5cm]plant.center) {};
+      \node[draw=none] (xdot) at ([xshift=.85cm,yshift=.15cm]p1)  {$\dot{\vec{x}}(t)$};   
+      \node[rectangle,draw,minimum width=1cm] (int) at ([xshift=.5cm,yshift=.5cm]plant.center) {\sc $\int$};
+      \coordinate (xsouth) at ([xshift=1cm]int);
+      \node[draw=none] (x) at ([xshift=1cm,yshift=.15cm]int)  {$\vec{x}(t)$};
+      \node[rectangle,draw,minimum width=1cm,minimum height=1cm] (A) at ([xshift=.5cm,yshift=-1cm]plant.center)  {\sc $\mat{A}$};
+      \coordinate (aeast) at ([xshift=1cm]A);
+      \coordinate (awest) at ([xshift=-1.8cm]A);
+    }
+
+   \& complexnode/.pic={ 
+     \node[rectangle,dashed,draw,minimum width=3.5cm,minimum height=1.6cm,label=\textbf{ADC},] (adc) {};
+     \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
+     \coordinate (switch1) at ([xshift=-1cm]adc.center);
+     \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
+   %  \node[circle,add={+}{+}{}{},fill=gray!20] (q1) at ([xshift=.6cm]adc.center) {};
+   %  \node[draw=none] (q2t)  at ([yshift=.55cm]q1) {\sc Q1};
+   %  \node[draw=none] (v1)  at ([yshift=-1.5cm]q1) {$\nu_1$};
+     \node[draw=none] (y) at ([xshift=.85cm,yshift=.15cm]switch2)  {$\vec{x}_k$};       
+     \coordinate (ykeast) at ([xshift=2.9cm]switch2);
+     \coordinate (yksouth) at ([xshift=2.9cm,yshift=-3.5cm]switch2);
+   } 
+   \& \coordinate (aux1);
+   \& \\
+  };
+
+%  \path[->] (v1) edge (q1.south);
+%  \path[->] (v2) edge (q2.south);
+  \path[->] (r) edge (circle.west);
+  \path[->] (circle.east) edge (zoh.west);
+%  \path       (q2.east) edge (zoh.west);
+  \path[->] (zoh.east) edge (B.west);
+  \path
+   (B.east) edge (p1.west)
+   (p1.east) edge (int.west)
+   (xsouth) edge (aeast)
+   (aeast) edge (A.east)
+   (A.west) edge (awest)
+   (awest) edge (p1.south)
+   (int.east) edge (switch1.west)
+   (switch2) edge (ykeast);
+  \path
+ %  (q1.east) edge (ykeast)
+   (ykeast) edge (yksouth)
+   (yksouth) edge (kdsouth);
+  \path[->]  (kdsouth) edge (Kd.south);
+  \path (Kd.north) edge (circle.south);
+ \end{tikzpicture}
+}
+ \caption{Closed-loop digital control setup, 
+ comprising an analogue model of the underlying real system, 
+ alongside a digital controller. 
+ \label{fig:digitalsystem}}
+\end{figure*}
+
+We consider models of physical plants expressed as ordinary differential
+equations, which we assume are controllable~\cite{Astrom08}: 
+%
+\begin{align}
+\label{eq:ode1}
+\dot{x}(t) = \mat{A}\vec{x}(t)+ \mat{B} \vec{u}(t), 
+\end{align}
+%
+where 
+$\vec{x} \in \mathbb{R}^n$,  
+$\vec{u} \in \mathbb{R}^p$, 
+$\mat{A} \in \mathbb{R}^{n \times n}$, 
+$\mat{B} \in \mathbb{R}^{n \times p}$,
+and $t \in \mathbb R_0^+$ denotes continuous time. 
+%$\mat{A}$ and $\mat{B}$ are matrices that fully characterize the dynamics of the continuous plant,
+We denote with $x(0)$ the model initial condition, which can be non-deterministic.  
+\rev{ We assume full observability of the states of the model, namely the output states correspond with the model variables.  }
+
+Equation~\eqref{eq:ode1} is 
+%soundly 
+discretized in time~\cite{middleton1990digital,van1978computing} with constant sampling intervals, 
+each of duration $T_s$ (the sample time), 
+into the difference equation
+%
+\begin{align}
+\label{eq:plant}
+\vec{x}_{k+1} =& \mat{A}_d \vec{x}_k+ \mat{B}_d \vec{u}_k, 
+\end{align} 
+where 
+$\mat{A}_d=e^{\mat{A}T_s}$ and 
+$\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$, 
+$k \in \mathbb N$ is a discrete counter and where $\vec{x}_{0}=\vec{x}(0)$ denotes the initial state. 
+We assume that specifications on the model concern \eqref{eq:plant}, 
+and plan to devise controllers $\vec{u}_k$ to meet them. 
+(The more general problem of synthesising controllers $u(t)$ for \eqref{eq:ode1} fall outside the scope of the present work.)
+
+\subsection{Digital control synthesis}
+
+Models \eqref{eq:ode1} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u(t)$ and  $u_k$, respectively. 
+Feedback architectures can be employed to manipulate properties and behaviors of the plant:    
+we are interested in the synthesis of digital feedback controllers $u_k$, as in Fig. \ref{fig:digitalsystem},  
+as practically implemented on Field-Programmable Gate Arrays or Digital Signal Processors   
+%This requires us to consider the errors introduced by, we will address the issue of variable quantization, 
+%introduced by ADC/DAC conversion blocks of Figure \ref{fig:digitalsystem}, 
+and as classically studied in \cite{astrom1997computer}.
+
+\rev{ Recall that the states of the model are fully accessible (namely, observable). } 
+We consider state feedback control architectures, 
+where $u_k$ (notice we work with the discretized signal) is $u_k = r_{k} - K x_k$. 
+Here $K \in \mathbb{R}^{p \times n}$ is a state-feedback gain matrix, 
+and $r_{k}$ is a reference signal (again digital). 
+We will assume $r_k=0$, thus obtaining the closed-loop model 
+$\vec{x}_{k+1}=(\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_k$.
+
+The gain matrix $K$ can be set so that the closed-loop discrete dynamics are
+shaped as desired, for instance according to a specific stability goal or
+around a dynamical behavior of interest \cite{astrom1997computer}.  As argued
+later in this work, we will target a less standard objective,
+namely a quantitative safety requirement \rev{over a convex set around the origin}, 
+which opens up to more complex specifications \cite{BYG16, Tab09}. 
+This is not typical in the digital control literature. We will further precisely account for the digital nature
+of the controller, which manipulates quantised signals as discrete quantities represented with
+finite precision. The new approach is fully automated and leverages an approach based on CEGIS.
+
+% Further, we will embrace the digital nature of the
+%controller, which manipulates quantized signals as discrete quantities represented with finite precision.
+
+\subsection{Stability of closed-loop models}
+
+In this work we employ the notion of asymptotic stability within the CEGIS loop,  
+as a means for reducing the search space of possible safe controllers, where the notion of a safe controller
+is defined in the following section. 
+As discussed later, specifically for linear models a safe controller is necessarily asymptotically stable, 
+although the reverse is not true. 
+%as an objective for guessing controllers that are later proven sound over safety requirements.  
+Qualitatively, (local) asymptotic stability is a property denoting the convergence of the model executions towards an equilibrium point, 
+starting from any states in a neighborhood of the point. 
+In the case of linear systems %as in~\eqref{eq:closedloopss}, 
+considered with a zero reference signal, 
+the equilibrium point of interest is the origin (see Figure~\ref{fig:ct} for the portrait of an asymptotically stable execution, converging to the origin).
+
+Of interest for this work, 
+it can be shown that a discrete-time LTI model %as \eqref{eq:closedloopss} 
+is asymptotically stable if all the roots of its characteristic polynomial (i.e., the
+eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
+circle of the complex plane, i.e., if their absolute values are strictly less than
+one~\cite{astrom1997computer}. 
+Whilst this simple sufficient condition can be either generalized or strengthen to be necessary, 
+this is not necessary in the context of this work.    
+What is technically key is that in this paper, 
+we shall express this asymptotic stability as a specification $\phi_\mathit{stability}$, 
+and encode it in terms of a check known as \emph{Jury's criterion}~\cite{fadali}: 
+this is an easy algebraic formula to check the entries of matrix $K$, 
+so that the closed-loop dynamics are shaped as desired.
+
+\subsection{Safety of closed-loop models}
+\label{sec:safety}
+
+We are not limited to the synthesis of digital stabilizing controllers -- a
+well known task in the literature on digital control systems -- but target
+safety requirements with an overall approach that is sound and automated. 
+More specifically, we require that the closed-loop model 
+%\eqref{eq:closedloopss} 
+meets a given safety specification \rev{that depends on a given set around the origin}.  
+A safety specification gives rise to a requirement on the states of the model, 
+namely that they remain within the safe set at all times (that is, over an infinite number of time steps).  
+So the feedback controller (namely the choice of the gain matrix~$K$)
+must ensure that the state never violates the requirement.  Note that an asymptotically 
+stable, closed-loop system is not necessarily a safe system: indeed, the 
+state values may leave the safe part of the state space while they converge
+to the equilibrium, which is typical in the case of oscillatory dynamics. 
+%However, a safe system will always be stable.  
+In~this work, the safety property is expressed as: 
+%
+\begin{equation}
+\label{eq:safetyliteral}
+\phi_\mathit{safety} = \left\{ \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}}\right\},
+\end{equation}
+%
+%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
+%
+where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
+for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ 
+at the $k$-th instant, respectively.  This requires that the states will always be within an $n$-dimensional hyper-box.
+
+\medskip
+
+Beyond the main requirement on safety, it is practically relevant to consider the 
+constraints $\phi_\mathit{input}$ on the input
+signal $u_{k}$ and $\phi_\mathit{init}$ on the initial states $x_0$,
+which we assume have given bounds:
+$\phi_\mathit{input} = \{\forall k \geq 0.\bigwedge_{i=1}^{p} \underline{u} \leq u_{i} \leq \overline{u}\} $,
+and $\phi_\mathit{init} = \{ \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}\}$. 
+The former constraint expresses that control input, possibly shaped via state-feedback, 
+might saturate in view of physical constraints.
+\rev{Notice that we will assume that the set of initial states lies within the safe set, since the contrary leads to dynamics that are trivially unsafe. 
+Furthermore, whilst the problem can handle general hyper-boxes, we will in practice work with set that contain the origin. }
+
+\subsection{Bounded Model Checking}
+\label{sec:BMC}
+
+We employ the bounded model checker CBMC~\cite{DBLP:conf/tacas/KroeningT14} to model the controller behavior on digital signals with finite bit-precision.  
+We express the controller semantics as C programs, which is CBMC's preferred input language.  
+CBMC symbolically executes every instruction in an input program by translating it to a boolean satisfiability problem,
+ which is satisfiable iff a certain property about the program holds.  
+CBMC's API allows to specify these properties in the form of assertions in the input program: 
+we set these properties to express that our controllers generate (asymptotically stable and) safe dynamics. 
+%\note{Do we need more details here? Should we explain e.g. SSA or give examples of how assignments, loops,
+%etc. are turned into formulas? Part of Sec.~\ref{sec:errors} can probably be moved here.}
+
+%-------------------------------s
+\subsection{Semantics of finite-precision arithmetics}
+\label{sec:errors}
+
+A key contribution of this work is that, when synthesizing controllers, it precisely replicates the finite-precision arithmetic within the digital controller, 
+thus guaranteeing that controllers implemented with finite-precision arithmetic are safe. 
+The specific components of the model, shown in Figure~\ref{fig:digitalsystem}, we are concerned with are the ADC, digital controller and DAC.
+Details of how we model the behaviour of the finite-precision arithmetic in these components are in Section~\ref{sec:numeric_rep}. 
+We must model the semantics precisely, in order to capture the full behaviour of the model. 
+More specifically, we encompass the following features:
+
+\begin{itemize}
+
+\item The ADC converts the analog signal $x(t)$ into a digital signal $x_k$, which is then fed into the controller, converting a real value to a finite-precision value.  
+% cf. Figure~\ref{fig:digitalsystem}.
+
+\item The controller block performs arithmetic at finite precision. 
+We assume the ADC represents numbers with at least the same precision as the controller, 
+and thus focus on the precision as limited by the controller. 
+This is a reasonable assumption based on commonly available hardware.
+
+\item The DAC converts finite-precision values back to real values. 
+We assume that the input to the DAC has the same precision as the output of the controller. 
+It would, however, be straightforward to account for a DAC or ADC of different precision than the controller in our algorithm, if necessary. 
+\end{itemize}
+
+\subsection{Soundness of modelling}
+
+In addition to precisely replicating the finite-precision arithmetic of the digital controller, 
+we must consider that our \emph{model} itself in \eqref{eq:plant} employs finite-precision arithmetic to represent the behaviour of the real system. 
+In order to guarantee soundness, we therefore encompass the error that is due to modelling (as opposed to the nature of the digital controller):   
+the representations used in the plant model and its arithmetic operations are carried out at finite precision.  
+\begin{itemize} 
+\item
+We account for the error introduced by finite precision arithmetic applied over the model variables $x_k$ and $u_k$, 
+%\note{here I have replaced the continuous-time signals with discrete-time ones}, 
+which are actually continuous quantities. 
+We guarantee that the precision we use to represent the model variables is at least as precise as the precision used in the digital controller, 
+and we use interval arithmetic to bound the incurred errors, as further detailed in Section~\ref{sec:numeric_rep}. 
+\end{itemize}
+
+\subsection{Notation for fixed- and floating-point precision}
+
+In this paper we will use $\mathcal{F}_{\langle I,F \rangle}(x)$ to denote a real number $x$ expressed at a fixed-point precision, 
+using $I$ bits to represent the integer part of the number and $F$ bits to represent its decimal part.  
+In particular, $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ denotes a real number $x$ represented at the fixed-point precision of the controller, 
+and $\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ denotes a real number $x$
+represented at the fixed-point precision of the plant model. 
+$I_c$ and $F_c$ are determined by the controller.  We pick $I_p$ and $F_p$ for our synthesis
+such that $I_p \geq I_c$ and $\allowbreak F_p \geq F_c$, so that our controller 
+can be represented accurately in the model domain.    
+Thus any mathematical operations in our modelled digital controller will be in the
+range of $\mathcal{F}_{\langle I_c,F_c \rangle}$, and all other calculations
+in our model will be carried out in the range of $\mathcal{F}_{\langle
+I_p,F_p \rangle}$.
+
+We further employ $\mathcal{F}_{\langle E,M \rangle}(x)$ to denote a real number $x$ represented in a floating-point domain, 
+with $E$ bits representing the exponent part and $M$ bits representing the mantissa part. 
+In particular, 
+we use $\mathcal{F}_{\langle E_c,M_c \rangle}(x)$ to denote a real number 
+represented at the floating-point precision of the controller, 
+whereas $\mathcal{F}_{\langle E_p,M_p \rangle}(x)$ denotes a real number represented at the floating-point precision of the plant model.
+
+%-------------------------------
+\subsection{Counterexample-Guided Inductive Synthesis} 
+\label{ssec:cegis}
+%-------------------------------
+
+\begin{figure}
+%\hspace{-2cm}
+\centering
+\resizebox{.8\textwidth}{!}{
+ \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto,
+ semithick, initial text=, ampersand replacement=\&,]
+
+  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
+},
+          row sep=1cm, column sep=2cm] {
+   \node[fill=gray!20,minimum height=1cm] (synth) {{\sc Synthesize}};
+   \&
+   \node[fill=gray!20,minimum height=1cm] (verif) {{\sc Verify}};
+   \&
+   \node[ellipse,fill=gray!20] (done) {{\sc Done}}; 
+    \\
+  };
+
+   \path
+   ([yshift=2em]synth.east) edge node[align=center] {Candidate} ([yshift=2em]verif.west)
+    ([yshift=-2em]verif.west) edge node[align=center] {Counterex} ([yshift=-2em]synth.east)
+    (verif) edge node {} (done);
+ \end{tikzpicture}
+}
+ \caption{The general CEGIS framework\label{fig:CEGIS}}
+\end{figure}
+
+In this section, we give a brief description of the CEGIS framework~\cite{jha-icse10,
+  DBLP:conf/asplos/Solar-LezamaTBSS06}, which is illustrated in Figure~\ref{fig:CEGIS}. 
+  CEGIS has been recently developed for the automated synthesis of software programs, 
+  and its setup is naturally that of mathematical logic. We consider an input specification of the form 
+$$
+\exists P .\, \forall a.\, \phi(a, P),
+$$  
+where $P$ ranges over functions (where a function is represented by the program computing it),
+$a$ ranges over ground terms, 
+and $\phi$ is a quantifier-free logical formula. 
+We~interpret the ground terms over some domain~$\mathcal{D}$. 
+This is a design problem, where the objective is to synthesise a valid $P$ that satisfies $\phi$ over all the $a$ terms.
+
+CEGIS breaks down this generally hard synthesis problem into two easier parts:
+%The design consists of two phases,
+an inductive synthesis phase (denoted by {\sc Synthesize} in
+Figure~\ref{fig:CEGIS}) and a verification phase (denoted by {\sc
+  Verify}), which interacts via a finite set of tests {\sc
+  inputs} that is updated incrementally.
+Given the specification $\phi$, the inductive synthesis procedure tries to
+find an existential witness $P$ satisfying the specification
+$\phi(a, P)$ for all $a$ in {\sc inputs} (as opposed to all $a \in
+\mathcal{D}$).
+%
+If the synthesis phase succeeds in finding a witness~$P$, this witness is a
+candidate solution to the full synthesis formula.  We pass this candidate
+solution to the verification phase, which checks whether it is a full solution
+(i.e., $P$ satisfies the specification $\phi(a, P)$ for all
+$a\in\mathcal{D}$).  If this is the case, then the algorithm terminates. 
+Otherwise, additional information is provided to the inductive synthesis
+phase in the form of a new counterexample that is added to the {\sc inputs}
+set and the loop iterates again.  %% More details about the general
+%% architecture of the synthesizer can be found
+%% in~\cite{DBLP:conf/lpar/DavidKL15}.
+If the solution space is finite then the CEGIS loop is guaranteed to
+terminate by either finding a solution or showing that no solution
+exists.
+
+In the context of the formal synthesis of safe controllers, 
+the set of possible {\sc inputs} corresponds to the set of possible initial states and the 
+candidate program $P$ is a candidate controller $K$. The synthesis block generates a candidate
+controller that works for a subset of the possible initial states, and the verifier checks whether 
+the controller works for all possible initial states.
+
+%-------------------------------
+\section{Formal specification of properties on a model} 
+\label{sec:specification}
+%-------------------------------
+
+%While in the previous section we have discussed the generic CEGIS framework, 
+We are now equipped to apply the general CEGIS framework to the synthesis of digital controllers. 
+We start by describing the property that we pass to the synthesizer as the specification $\phi$. 
+Namely, as we are interested in capturing safety (as discussed in Section~\ref{sec:safety}),  
+we use a stability specification to narrow the search space of possible controllers, as detailed in Section~\ref{ssec:stabspecification}.
+
+%-------------------------------
+\subsection{Jury's stability criterion} 
+\label{ssec:stabspecification}
+%-------------------------------
+
+%\note{reminder AA: check throughout use of 'model vs system'}
+
+There are a number of well known procedures to perform stability analysis of dynamical models~\cite{Astrom08}. 
+%which can fit our automatic verification engine.  
+%one based on Schur's decomposition
+%and another one based on Jury's criterion~\cite{astrom1997computer}.  
+Here we select the Jury stability criterion~\cite{astrom1997computer}, 
+in view of its efficiency and ease of integration within our implementation.  
+This method checks the stability working in the complex domain of the characteristic polynomial $S(z)$,  
+%
+% of the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$, where $Y(z)$ is the closed-loop system output and U(z) is the controller output. 
+%% \red{[unclear: what matrix? We need to clarify the relationship
+%% between the char. poly. $S(z)$ and the later quantities $\Delta
+%% N_{G}(z), \Delta D_{G}(z)$ and corresponding controller's
+%% structure.]}.
+%
+considered in its general form as 
+% for $S(z)$:
+%
+\begin{equation*}
+S(z) = a_0z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N,\,\, a_0\neq0. 
+\end{equation*}
+This polynomial is obtained as a function of the state-space matrices $A_d,B_d$~\cite{Astrom08}, 
+and in particular its order $N$ corresponds to the dimensions of the state variables (above, $n$).  
+A sufficient condition for asymptotic stability of the closed-loop LTI model~\cite{astrom1997computer} 
+is when all the roots of its characteristic polynomial $S(z)$ (which correspond to the 
+eigenvalues of the matrix $A_d-B_dK$) are inside the unit circle in the complex plane, 
+i.e., if their absolute values are less than one.
+
+%\note{The characteristic polynomial $S(z)$ represents the dynamical model in \ldots [clarify whether we use the CPol to describe the open- or closed-loop model.
+Relate parameters to matrices A,B,K.
+Notice that these parameters are used later in the Section where AA-based backend is explained.]}
+
+The following matrix $M$ with dimension $(2N-2)\times N$ and elements $m_{(\cdot),(\cdot)}$ is built from the coefficients of $S(z)$ as:  
+%
+$$
+M=\left( 
+\begin{array}{c}
+V^{(0)}\\
+V^{(1)}\\
+\vdots\\
+V^{(N-2)}
+\end{array}
+\right), 
+$$
+%
+where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ is such that:
+%
+$$
+v_{ij}^{(0)}=\left\{
+\begin{array}{ll}
+a_{j-1}, & \mbox{if}~i=1\\
+v_{(1)(N-j+1)}^{0},&\mbox{if}~i=2
+\end{array}
+\right.
+$$
+%
+$$
+v_{ij}^{(k)}=\left\{
+\begin{array}{ll}
+0,&\mbox{if}~j>n-k\\
+v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \mbox{if}~j\leq n-k ~\mbox{and}~i=1\\
+v_{(1)(N-j+1)}^{k},& \mbox{if}~j\leq n-k ~\mbox{and}~i=2\\
+\end{array}
+\right.
+$$
+%
+and where $k \in \mathbb{Z}$ is such that $0 < k < N - 2$.
+
+We have that $S(z)$ is the characteristic polynomial of an asymptotically stable system if and only if the following four conditions $R_i, i = 1,2,3,4,$ hold~\cite{astrom1997computer}: 
+%\begin{itemize}
+%\item 
+$R_1: S(1) > 0$;
+%\item 
+$R_2: (-1)^N S(-1) > 0$;
+%\item 
+$R_3: |a_0| < a_N$;
+%\item 
+$R_4: m_{11} > 0 \wedge\allowbreak
+      m_{31}>0 \wedge\allowbreak
+      m_{51}>0 \wedge \ldots \wedge\allowbreak
+      m_{(2N{-}3)(1)}>0$.
+%\end{itemize}
+
+In conclusion, 
+the asymptotic stability property is finally encoded by a constraint expressed as the following formula: 
+$
+\phi_\mathit{stability} = \{R_1 \wedge R_2 \wedge R_3 \wedge R_4\}.
+$
+
+\ifx\safetyrep
+%-------------------------------
+\subsection{Formal specification of safety} 
+\label{ssec:safespecification}
+%-------------------------------
+
+%We are not limited to the synthesis of digital stabilizing controllers -- a
+%well known task in the literature on digital control systems -- but target
+%safety requirements with an overall approach that is sound and automated. 
+%More specifically, we require that the closed-loop system meets given safety specifications.  
+We target synthesis of safe digital controllers with an overall approach that is sound and automated.
+A safety specification translates into a requirement on the states of the closed-loop model, 
+which hinges on the choice of the feedback controller (namely the choice of the gains in the matrix~$K$):  
+we must ensure that the states of the closed-loop model never violate this requirement, expressed as a given subset of the state space.
+
+Note that a stable closed-loop model is not necessarily a safe model: 
+indeed, the state values may leave the safe part of the state space while they converge
+to the equilibrium, which is typical in the case of oscillatory and convergent dynamics. 
+%However, a safe system will always be stable.  
+In~this work, the safety property is expressed as the formula:
+%
+\begin{equation}
+\label{eq:safetyliteral}
+\phi_\mathit{safety} := \forall k\ge 0,\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
+\end{equation}
+%
+%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
+%
+where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
+for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$, ranging over the $k$-th time step.  
+This means that the states are required to remain within an $n$-dimensional hyper-box at any point in time.
+
+Furthermore, it is practically relevant to consider constraints $\phi_\mathit{input}$ on the input
+signal $u_{k}$ and requirements $\phi_\mathit{init}$ on the initial states $x_0$, 
+both of which we be expressed via given bounds as: 
+$\phi_\mathit{input} := {\forall k\ge 0, \underline{u} \leq u_{k} \leq \overline{u}} $, 
+and $\phi_\mathit{init} := \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}$. 
+For the input signal, these requirements practically mean that the control input saturates in view of physical constraints. 
+\fi
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{Numerical representation and soundness} 
+\label{sec:numeric_rep}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+As discussed in Section~\ref{sec:errors}, 
+the considered models must account for the semantics of finite-precision arithmetic, 
+deriving from several sources: 
+we formally bound the numerical error introduced by the finite precision representation of the plant (and its operations), 
+and precisely model the behaviour introduced by the ADC/DAC conversions, 
+as well as the behaviour of the limited-precision arithmetic used by the controller.
+
+Technically, we employ interval arithmetic to bound the error introduced by the finite-precision plant model, 
+and we use bounded model checking to precisely model the semantics of finite-precision arithmetic, 
+as introduced by the ADC/DAC blocks and by the finite-precision controller.
+
+\subsection{Bit-precise bounded model checking}
+
+As described in Section~\ref{sec:BMC}, we use CBMC, a bit-precise bounded model checker, 
+to synthesise and verify candidate controllers. 
+CBMC manipulates precisely the fixed- or floating-point arithmetic used in the controller, 
+as well as the ADC/DAC conversions, according to the IEEE standards.
+
+\subsection{Interval arithmetic for errors in numerical representations}
+
+We use finite-precision arithmetic to model the plant. 
+This is an approximation that speeds up each CEGIS iteration, 
+however it necessitates a further stage where we verify that the errors introduced by the approximation have not resulted in a controller that is unsafe when executed on a model expressed over real numbers.
+In this stage, we represent the plant model using double-precision floating-point numbers 
+and we use the Boost interval arithmetic library~\cite{DBLP:journals/tcs/BronnimannMP06} to bound the error in this representation. 
+We employ a compositional numerical library to model the fixed point arithmetic for the controller\footnote{\url{https://github.com/johnmcfarlane/cnl}} within double-precision floating-point numbers. 
+We check that the controller is safe starting from each vertex of the set of initial states,  
+and show that this is sufficient to prove safety from any state in this set (see Theorem~\ref{th:safety}). %\note{add forward reference to proof.}
+
+We describe here the mathematics behind bounding the errors on the double-precision floating-point numbers. 
+Recall we use $\mathcal{F}_{\langle E,M \rangle}(x)$ denote a real number $x$ represented in a floating-point domain, 
+with $E$ bits representing the exponent part, and $M$ bits representing the mantissa. 
+In general the representation of a real number using the floating-point domain introduces an error, 
+for which an upper bound can be given~\cite{DBLP:conf/arith/BrainTRW15}.
+For each number $x$ represented in the floating-point domain as $\mathcal{F}_{\langle E,M \rangle}(x)$, 
+we store an interval that encompasses this error. 
+Further mathematical operations performed at the precision $\mathcal{F}_{\langle E,M \rangle}(x)$ will propagate this error, 
+leading to further errors for which bounds can be derived~\cite{DBLP:conf/arith/BrainTRW15}.
+
+The fixed-point arithmetic of the digital controller is performed on the upper and lower bound of the intervals from above independently, 
+and the upper and lower bound of the result is taken as the interval result. For example,
+consider the conversion from the model precision to controller precision performed by the ADC on a single state value.
+The state value is represented as an interval $\{x.high, x.low\}$, and the result of the conversion is an interval where the upper bound is the conversion of $x.high$ and the lower bound is the conversion of $x.low$.
+Since the precision of the floating-point domain is greater than the precision of the controller, this is guaranteed to bound the real behaviour of the controller.
+
+\ifx\axelerator
+
+\begin{enumerate}
+
+\item {\bf Truncation:} Let $x$ be a real number, and $\mathcal{F}_{\langle
+I,F \rangle}(x)$ be the same number represented in a fixed-point domain as
+above.  Then $\mathcal{F}_{\langle I,F \rangle}(x) = x-\delta_T$ where the
+error $ \delta_T=x\ \%_{c_m}\ \tilde x$ \note{define tilde x}, and $\%_{c_m}$ is the modulus
+operation performed on the last bit. 
+Thus, $\delta_T$ is the truncation error and it will propagate across
+operations.
+%
+\item {\bf Rounding:} The following errors are due to basic arithmetic operations.  
+Let $c_1, c_2$ and $c_3$ be real numbers, and $\delta_{T1}$ and $\delta_{T2}$ be
+the truncation errors caused by representing $c_1$ and $c_2$ in a fixed-point domain.
+%
+\begin{enumerate}
+%
+\item Addition/Subtraction: these operations only propagate errors coming
+from truncation of the operands, namely $\mathcal{F}_{\langle I,F
+\rangle}(c_1) \pm \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_3$
+with $|\delta_3| \leq |\delta_{T1}| + |\delta_{T2}|$.
+%
+\item Multiplication: $\mathcal{F}_{\langle I,F \rangle}(c_1) \cdot
+\mathcal{F}_{\langle I,F \rangle}(c_2) =  c_3 + \delta_3$ with $|\delta_3|
+\leq |\delta_{T1}\cdot\mathcal{F}_{\langle I,F \rangle}(c_2)|\allowbreak +
+|\delta_{T2}\cdot\mathcal{F}_{\langle I,F \rangle}(c_1)| + c_m$, where
+$c_m=2^{-F}$ as above.
+%
+\item Division: the operations performed by the controllers in the finite precision
+domain do not include division.  However, we do use division in computations within the model.  
+Here the error depends on whether the divisor is greater or smaller than the dividend:  $\mathcal{F}_{\langle I,F
+\rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) = c_3 + \delta_{T3}$, 
+where $\delta_{T3}$ is $(\delta_{T2}\cdot c_1 - \delta_{T1}\cdot
+c_2)/(\delta_{T2}^2 - \delta_{T2} c_2)$,
+%
+%$\mathcal{F}_{\langle I,F \rangle}(c_1) / \mathcal{F}_{\langle I,F \rangle}(c_2) =  (c_1 - \delta_{T1})/ (c_2 + \delta_{T2}) + c_m $, where $c_m=2^{-F}$ as above.
+\end{enumerate}
+
+\item {\bf Overflow:}
+The maximum size of a real number $x$ that can be represented in a fixed
+point domain as $\mathcal{F}_{\langle I,F \rangle}(x)$ is $\pm
+(2^{I-1}+1-2^{-F})$.  Numbers outside this range cannot be represented by
+the domain.  If overflow occurs, the interval bound becomes infinite.
+
+\end{enumerate}
+
+Similar bounds for errors introduced by 
+performing basic mathematical operators in floating-point precision can be derived~\cite{DBLP:conf/arith/BrainTRW15}.
+
+\subsection{ADC/DAC quantization errors modelled as noise} 
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+In this section we describe how quantization errors can be modelled as noise. 
+Note that this is only applicable to the acceleration back end, as the multi-stage back 
+end makes use of CBMC's bit-precise model checking capabilities to account 
+for these deterministic errors.
+
+During any given ADC conversion, the continuous signal will be sampled in
+the real domain and transformed by $\mathcal{F}_{\langle I_{c},F_{c} \rangle}
+(x)$ (assuming the ADC discretization is the same as the digital
+implementation).  This sampling uses a threshold which is defined by the
+less significant bit ($q_{c}=c_{m_c}=2^{-F_c}$) 
+%\blue{[this quantity was named $c_m$ above and in other parts of the paper - please uniformise notations]}
+of the ADC and some non-linearities of the circuitry.  The overall conversion is
+%
+$$\mathcal{F}_{\langle I_{c},F_{c} \rangle}(x(t)) = x_k :
+(x_k)_i \in \left[x_i(t)-\frac{q_{c}}{2}\ \ \ \ x_i(t)+\frac{q_{c}}{2}\right] \,.$$
+%
+\reply{where $x_i$ is the $i^{th}$ component of the vector $x$.}
+If we denote the error in the conversion by $\nu_k=x_k-x(t)$ where $t = nk$,
+and $n$ is the sampling time and $k$ the number of steps, then we may define
+some bounds for it $(\nu_k)_i \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
+
+As stated before, we assume that the domain of the
+ADC is that of the digital controller (i.e, the quantizer includes any
+digital gain added in the code).  The process of quantization in the DAC is
+similar except that it is calculating $\mathcal{F}_{\langle I_{dac},F_{dac}
+\rangle} (\mathcal{F}_{\langle I_{c},F_{c} \rangle }(x)) $.  If these domains
+are the same ($I_{c}=I_{dac},\allowbreak F_{c}=F_{dac}$), or if the DAC
+resolution in higher than the ADC, then the DAC quantization error is equal
+to zero.  From the above equations we can now define the ADC and DAC
+quantization noises ${\nu_1}_k \in [-\frac{q_1}{2}\ \ \frac{q_1}{2}]$ and
+${\nu_2}_k \in [-\frac{q_2}{2}\ \ \frac{q_2}{2}]$, where $q_1=q_{c}$ and 
+$q_2=q_\mathit{dac}$.  This is illustrated in
+Fig.~\ref{fig:digitalsystem} where $Q_1$ is the quantizer of the ADC
+and $Q_2$ the quantizer for the DAC.  These bounds hold irrespective of
+whether the noise is correlated, hence we may use them to over-approximate
+the noise effect on the state space progression over time.  The
+resulting dynamics are
+%
+\begin{align*}
+%\label{eq:pre_quantization}
+{x}_{k+1} = {A}_d{x}_k+{B}_d({u}_k+{{\nu}_2}_k), \quad u_k = -K{x}_{k}+{{\nu}_1}_k, 
+\end{align*}
+%
+which result in the following closed-loop dynamics:
+%
+\begin{align*}
+%\label{eq:quantization}
+{x}_{k+1} &= ({A}_d-{B}_d{K}_d) {x}_k+{B}_d{{\nu}_2}_k +{{\nu}_1}_k \,. 
+\end{align*}
+
+\fi
+
+\subsection{Effect of finite precision arithmetic on safety specification and on stability}
+
+In this section we will quantify how the finite precision arithmetic in a digital controller affects the
+safety and stability properties of an LTI model.
+
+\subsubsection{Safety of closed-loop models with finite precision controller error}
+
+Let us first consider the effect of the quantization errors on safety. 
+Within the controller, state values are manipulated at low precision,
+by means of the vector multiplication $Kx$.
+The inputs are thus computed using the following equation: 
+%
+\begin{align*}
+u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})). 
+\end{align*}
+This induces two types of errors, 
+as detailed above: 
+first, the truncation error due to the representation of $x_k$ as $\mathcal{F}_{\langle I_c,F_c
+\rangle}(x_{k})$; and second, the rounding error introduced by the multiplication operation. 
+Recall that this error is modelled precisely by bounded model checking.
+
+An additional error is due to the representation of the plant dynamics, namely 
+%
+%{\scriptsize
+\begin{equation*}
+x_{k+1} =\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
+\end{equation*}
+%}
+We encompass this error using interval arithmetic~\cite{moore1966interval} in the precision check shown in Figure~\ref{fig:CEGIS-precision-increment} and detailed in the previous section.
+
+\subsubsection{Stability of closed-loop models with fixed-point controller error}
+%-------------------------------
+\label{sec:stab_FWL}
+The validity of Jury's criterion~\cite{fadali} relies on the representation of the closed-loop dynamics $x_{k+1} = (A_d - B_dK) x_k$ at infinite precision.  
+When we employ a fixed-point arithmetic digital controller, the operation above can be expressed as follows, where we use $\mathcal{F}_{\langle I_c,F_c \rangle}$ preceding a variable to indicate that variable is converted into the fixed-point precision given by $\mathcal{F}_{\langle I_c,F_c \rangle}$:
+%
+\begin{align*}
+x_{k+1} &= A_d \cdot x_{k} -B_d(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  
+\end{align*}
+This translates to 
+\begin{align*}
+x_{k+1} &= (A_d  - B_dK) \cdot x_k + B_dK\delta, 
+%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
+\end{align*}
+%
+where $\delta$ is the maximum error that can be introduced by the digital controller in one step, 
+i.e., by reading the states values once and multiplying by $K$ once.  
+We derive the closed form expression for $x_n$ recursively, as follows:
+%
+\begin{align*}
+x_{1} &= (A_d  - B_dK)x_0 + B_dK\delta \\
+x_{2} %&= (A_d  - B_dK)((A_d  - B_dK)x_0 + B_dK\delta ) + B_dK\delta \\
+ &=(A_d  - B_dK)^2x_0 + (A_d  - B_dK)B_dK\delta + B_dK\delta \\
+%x_{3}  &=(A_d  - B_dK)^3x_0 + (A_d  - B_dK)^2B_dK\delta + (A_d  - B_dK)B_dK\delta + B_dK\delta\\
+x_{n} &= (A_d  - B_dK)^nx_0 + (A_d  - B_dK)^{n-1}B_dK\delta +\\
+&\phantom{{}=1} ... + (A_d  - B_dK)^1B_dK \delta + B_dK\delta \\
+  &= (A_d - B_dK)^nx_0 + \sum_{i=0}^{n-1}(A_d - B_dK)^iB_dk\delta. 
+\end{align*}
+%The definition of asymptotic stability is that the system converges to a
+%reference signal, in this case we use no reference signal so 
+Recall that a closed-loop asymptotically stable system will converge to the origin.  
+We know that the original system with an infinite precision controller is stable, 
+because we have synthesized it to meet Jury's criterion.  
+Hence, $(A_d - B_dK)^n x_0$  must converge to zero as $n \uparrow \infty$. 
+%T%o show that a fixed-point implementation of the same controller will
+%converge to a finite value, we need to show that the infinite sum converges. 
+Furthermore, the power series of a square matrix $T$ converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less
+than~1, and the limit results in 
+%
+%\begin{align*}
+$\sum_{i=0}^{\infty}T^i  = (I - T)^{-1}$, 
+%\end{align*}
+%
+where $I$ is the identity matrix. 
+Thus, the closed-loop model converges to the value 
+%
+\begin{align*}
+0 + (I - A_d + B_dK)^{-1}B_dk\delta \,. 
+\end{align*}
+%
+As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the safe set of states given by the safety specification
+then the synthesized fixed-point controller results in a safe
+closed-loop model.  The convergence to a finite value, however, will not
+make it asymptotically stable.
+However,
+since in this paper we require stability only as a precursor to safety, it
+is sufficient to check that the perturbed model converges to a
+neighborhood of the equilibrium within the safe set.
+
+A similar argument can be made for floating-point arithmetic.
+We can thus disregard these steady-state errors (caused by
+finite precision arithmetic) when stability is ensured by synthesis, and then verify its
+safety accounting for the finite precision errors.
+
+%-------------------------------
+\ifx\axelerator
+\subsection{Abstract acceleration of linear dynamics \note{Shall we move the material on AAccel to the Preliminaries?}} 
+\label{ssec:aa}
+%-------------------------------
+
+We recall a technique called \emph{Abstract Acceleration}~\cite{JSS14,cattaruzza2015unbounded}, 
+which will be key in this work for abstraction-based synthesis.  
+Abstract Acceleration allows one to perform reachability analysis of dynamical models, 
+and as such can be employed for safety verification. 
+% 
+Given an autonomous model of an iterative program with dynamics 
+%
+$\vec{x}_{k+1}=\mat{A_d}\vec{x}_k$, 
+where $\vec{x}_k \in \mathbb{R}^p$, $\mat{A_d} \in \mathbb{R}^{p \times p}$ and $k \in \mathbb N_0$, 
+%\end{equation}
+%
+we want to find all possible states visited over an infinite time horizon starting at a given initial set $X_0$.  
+This set is known as the \emph{reach tube} of the model: 
+%
+\begin{equation}
+\hat{X} = \{ \vec{x}_k: k \in \mathbb N_0, \vec{x}_0 \in X_0 \text{ and } \vec{x}_{k+1}=\mat{A_d}\vec{x}_k\}.
+\end{equation}
+%
+Using Abstract Acceleration we transform this sequential reachability problem into a one-step problem. 
+This has a lot of benefits ~\cite{JSS14}, not least in terms of numerical error propagation.   
+In order to attain this, 
+the problem statement is modified 
+%, by means of acceleration, 
+into 
+%
+\begin{equation}
+\hat{X} = \{ \vec{x}_k=\mat{A_d}^k\vec{x}_0: k \in N_0 \text{ and } \vec{x}_0 \in X_0 \}, 
+\end{equation}
+%
+and a new 
+%model semantics and corresponding 
+set $\hat{X}^\sharp$ is further defined as 
+%
+\begin{equation}\label{eq:aa_reachtube}
+\hat{X} \subseteq \hat{X}^\sharp = \mathcal{A}X_0, \text{ such that } \bigcup_{k \in [0\ \infty)} \mat{A_d}^k \subseteq \mathcal{A}, 
+\end{equation}
+%
+where the newly introduced \emph{abstract reach tube} $\hat{X}^\sharp$ is an
+over-approximation of the reach tube of the model: 
+\cite{JSS14} details algorithms to compute such set, 
+whereas \cite{cattaruzza2015unbounded} extends this to LTI models with inputs as in Eqn. \eqref{eq:plant}.  
+In view of the overall goal of this work, 
+we extend the algorithm to continuous-time models.  
+% and  For this reason we must first look at the acceleration of continuous-time dynamics.
+
+The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
+the state of the model at integer multiples of the sample time.  
+%\note{Unlike the CAV18 paper, these gain matrices have not been discussed yet. }
+However, in order to synthesize a soundly safe controller, 
+% $\mat{K}$, 
+we must be able to ensure that the safety of the model holds at any continuous point in time.  
+In order to do so, we accelerate the dynamics of the model according to the continuous-time model
+semantics in Sec.~\ref{sec:model}.
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsubsection{Accelerated\! dynamics\! for\! continuous-time\! models\! with\! parametric\! inputs}\label{sec:real_discrete_param_inputs}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+% 
+Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a
+linear function of initial state $\vec{x}_0$ and parametric input $\vec{u}$ as follows.
+
+\begin{lemma}
+The solution to the differential equation $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where
+$\forall t\geq 0\,\vec{u}(t)=\vec{u}$, $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$, and $\mat{S}$ are the generalized eigenvectors of $\mat{A}$,
+evaluated at time $T$ is
+%
+\begin{align}
+\label{eq:continuous_tube_param}
+\vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u}\\
+ \mat{A}_{T}&= \mat{S}
+ \left [ \begin{array}{cccc}
+ e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(2)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
+0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
+\vdots & & \ddots & \vdots \\
+0 & \cdots & 0  &e^{T\lambda_i} \\
+\end{array} \right ]
+ \mat{S}^{-1}
+ \label{eq:continuous_tube_dyn2}\\
+ \mat{B}_T&=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}
+ \footnote{When $\mat{A}$ is not invertible,
+we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\
+0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$.}\\
+ &\text{where } s_i=\left\{\begin{array}{cc}1&\quad gm(\lambda_i)>1\\0&\quad gm(\lambda_i)=1\end{array}\right.,\nonumber
+\end{align}
+%
+$\lambda_i$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.
+%
+
+If $\mat{J}$ is diagonal and there exists a sampling time $T_s$ such that $A_d=e^{\mat{A} T_s}$, 
+then $\forall T \in \mathbb{R}_0^+$ we obtain the known expression 
+$$
+\vec{x}_T=A_d^{\frac{T}{T_s}}\vec{x}_0+(\mat{I}-\mat{A}_d^{\frac{T}{T_s}})\mat{B}_d\vec{u}, 
+$$
+where $\mat{A}_d^{\frac{T}{T_s}} =e^{log(\mat{A}_d) \frac{T}{T_s}} = e^{\mat{A} T}$. 
+%is the state of the system at time $t=T$. 
+\end{lemma}
+
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\subsubsection{Accelerated dynamics for models with a sampled-time feedback}\label{sec:real_discrete_feedback_inputs}
+%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
+
+We analyze the case of hybrid-time models, 
+namely where the model dynamics evolve in continuous time, 
+while the feedback dynamics evolve in discrete time.  
+A new input value is accepted by the model only at sample times $T_s$.
+%but implemented over the continuous-time plant dynamics.
+%
+%\note{Matrix K has not been introduced yet. }
+\begin{theorem}
+The expression
+%
+ \begin{align}
+ \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0, 
+ \label{eq:cyber_feedback}
+ \end{align}
+%
+with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn2}, $\mat{B}_T$ as in
+\eqref{eq:continuous_tube_param}, and where $\mat{A}_d=\mat{A}_{T_s}$,
+$\mat{B}_d=\mat{B}_{T_s}$ describe the discretized model dynamics with
+sample time $T_s$, is the state of the model
+%
+\begin{align*}
+ \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
+ \vec{u}(t)=\mat{K}\vec{x}_k,  \,
+ kT_s \leq t < (k+1)T_s \,. 
+\end{align*}
+%
+\end{theorem}
+\begin{proof}
+\note{let us not number the proofs.}
+%
+Let $\mat{K}$ be a feedback controller such that
+$\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$.  Let the output of the
+feedback system be a zero order holder such that
+$\vec{u}(t'+kT_s)=\vec{u}(kT_s), \text{ for } 0 \leq t' < T_s$.  The closed
+loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
+%
+\begin{align*}
+\vec{x}_{k,t'}=\mat{A}_{t'}\vec{x}_k-\mat{B}_{t'}\mat{K}\vec{x}_k = (\mat{A}_{t'}-\mat{B}_{t'}\mat{K})\vec{x}_k,
+\end{align*}
+where $0 \leq t' < T_s$
+We further explore the dynamics across discrete time boundaries. Let $\mat{A}_d=\mat{A}_{T_s}$ and $\mat{B}_d=\mat{B}_{T_s}$
+\begin{align*}
+\vec{x}_{k}&=\vec{x}_{k-1,T_s}= (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}\\
+\vec{x}_{k,T_s} &= (\mat{A}_d-\mat{B}_d\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}
+\end{align*}
+which accelerating results and setting $T=kT_s+t'$ becomes
+\begin{align}
+\label{eq:feedback_sampled_cont}
+\vec{x}_{k} &= (\mat{A}_d-\mat{B}_d\mat{K}) ^k\vec{x}_0\\
+\vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
+\label{eq:feedback_cont}
+\end{align}
+\end{proof}
+
+%-------------------------------
+ \subsubsection{Abstract supports for continuous-time models}
+ \label{sec:cont_aasup}
+%-------------------------------
+
+Just as the accelerated dynamics in Eqn.
+\eqref{eq:feedback_sampled_cont} can be abstracted using \eqref{eq:aa_reachtube} (where $\bigcup_{k \in N_0} (\mat{A}_d-\mat{B}_d\mat{K}) ^k \subseteq \mathcal{A}$),
+we use the same principle on Eqn. \eqref{eq:feedback_cont} to obtain 
+\begin{equation}\label{eq:aa_cont_amatrix}
+\bigcup_{T \in [0, T_s], k \in N_0} (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k \subseteq \mathcal{A}.
+\end{equation}
+
+We next describe how to obtain an over-approximation of such a set. 
+This is defined as a polyhedron, expressed as an intersection of hyperplanes. 
+A tight polyhedron can be obtained with hyperplanes that are tangent to the set,  
+which is achieved by selecting a number of points on the boundary of the set, 
+and finding corresponding hyperplanes that are tangent to those points with respect to the dynamics.  
+\note{[you are essentially taking the Lie derivative of the set wrt the dynamics at the selected point?]}
+In order to simplify this procedure, we look at two-dimensional cuts \note{projection?} of the space, one at a time (i.e., for every pair
+of eigenvalues of the closed-loop dynamics, we find a hyperplane tangent to
+the progression of that pair in a two dimensional space and use it as a face of
+the polyhedron).  The difference with~\cite{cattaruzza2015unbounded} is that
+in the continuous case, the tangent is found by derivation \note{cf. `Lie derivative' above} rather than
+differentialtion, thus including all intermediate points \note{[?] in the arc}.
+
+\note{So the case study section should emphasise that the AA-based back-end can handle continuous-time benchmarks/models? 
+It seems like the discussion in this section is not reflected on the case study section yet. }
+
+\fi
+%-------------------------------
+\section{Synthesis of digital controllers with CEGIS} 
+\label{sssec:cegisdig}
+%-------------------------------
+
+In this section we discuss 
+\ifx\axelerator
+two instantiations of CEGIS: 
+the first one,
+named {\it multi-stage} approach, 
+relies on an unfolding of the dynamics up to a completeness threshold; 
+the second one is {\it abstraction-based}, 
+and it leverages abstraction-refinement \cite{DBLP:conf/cav/ClarkeGJLV00} and abstract acceleration (cf. Sec.~\ref{ssec:aa}) to improve scalability,  
+while retaining soundness. 
+\else
+the CEGIS procedure that is used to synthesise safe digital controllers, 
+accounting for the precision issues detailed in the previous sections. 
+We employ a multi-stage approach that unwinds the dynamics of the model up to a completeness threshold, 
+encompassing finite precision arithmetic using bit-precise bounded model checking, 
+and then verifying soundness of the resulting controller using interval arithmetic. 
+\fi
+
+\ifx\axelerator
+%-------------------------------
+\subsection{Multi-stage CEGIS} 
+\label{sssec:naive}
+%-------------------------------
+\fi
+
+%\begin{figure*}[htb]
+%\scriptsize\centering
+%\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
+%  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},
+%          row sep=.6cm, column sep=.9cm] {
+%   \coordinate (aux1);
+%   \& \coordinate (aux2);
+%   \&;\\
+%   \coordinate (aux3);
+%   \& \coordinate (aux4);
+%   \&;\\
+%   \coordinate (aux5);
+%   \& \coordinate (aux6);
+%   \&;\\
+%   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc 1.Synthesize}};
+%   \&
+%   complexnode/.pic={ 
+%     \node[rectangle,draw,dotted,
+%	minimum width=6cm,
+%	minimum height=1cm,
+%        pattern=north west lines, pattern color=gray!20,
+%	label={\sc ~~~~~~~~~~~~Verify},] (verif) {};
+%     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc 2.Safety}};
+%     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=0cm]verif.center) {{\sc 3.Precision}};
+%     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=2cm]verif.center) {{\sc 4.Complete}};
+%     %\node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc 5.Sampling}};
+%   } 
+%   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
+%   \& \\
+%   \node[minimum height=0cm] (gp) {\sf Program Search};
+%   \&
+%   complexnode/.pic={ 
+%     \coordinate (aux);
+%   \node (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based \\ \sf Verifier};
+%   \node (fp)  at ([xshift=0cm]aux.center) {\sf Fixed-point \\ \sf Arithmetic\\ \sf Verifier};
+%   \node (sv)  at ([xshift=2cm]aux.center) {\sf Completeness\\ \sf Verifier};
+%   %\node (cv)  at ([xshift=3.1cm]aux.center) {\sf Sampling\\Verifier};
+%   }   
+%    \\
+%  };
+%
+%   \path
+%    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$K$} ([yshift=2em]verif1.west)
+%    ([yshift=-2em]verif1.west) edge node {C-ex} ([yshift=-2em]synth.east)
+%    ([xshift=-5em]fp.north) edge node[align=center]  {T/F} ([xshift=-5em]verif2.south)
+%    ([xshift=-5em]sv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif3.south)
+%    %([xshift=-5em]cv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif4.south)
+%    ([xshift=5em]verif1.south) edge node[align=center] {$K$} ([xshift=5em]bmc.north)
+%    ([xshift=5em]verif2.south) edge node[align=center] {$K$} ([xshift=5em]fp.north)
+%    ([xshift=5em]verif3.south) edge node[align=center] {$K$} ([xshift=5em]sv.north)
+%    %([xshift=5em]verif4.south) edge node[align=center] {$K$} ([xshift=5em]cv.north)
+%    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
+%    (verif) edge node {PASS} (done)
+%    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
+%    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$K$} ([xshift=-5em]synth.south)
+%    (aux3) edge (synth.north);
+%   \path[-]
+%   (verif2.north) edge node[align=center] {} ([xshift=0cm]aux6)
+%   ([xshift=0cm]aux6) edge node[align=center] {Increase Precision} (aux5)
+%   (verif3.north) edge node[align=center] {} ([xshift=6.7cm]aux4)
+%   ([xshift=6.7cm]aux4) edge node[align=center] {Increase Unfolding Bound} (aux3);
+%   %(verif4.north) edge node[align=center] {} ([xshift=10.5cm]aux2)
+%   %([xshift=10.5cm]aux2) edge node[align=center] {Increase Sampling Rate} (aux1);
+%\end{tikzpicture}
+%\caption{CEGIS with multi-staged verification for digital controller synthesis}
+%\label{fig:CEGIS-precision-increment}
+%\end{figure*}
 
@@
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=.7\columnwidth]{figures/ct.eps}
-%\vspace{0.1cm}
-\caption{Completeness threshold for multi-staged verification (quantity $T_s$ is the time discretization step) }
-\label{fig:ct}
-\end{figure}
+%\begin{figure}[t]
+%\centering
+%\includegraphics[width=.7\columnwidth]{figures/ct.eps}
+%%\vspace{0.1cm}
+%\caption{Completeness threshold for multi-staged verification (quantity $T_s$ is the time discretization step) }
+%\label{fig:ct}
+%\end{figure}
 

### 2019-07-18 automatica/response.tex
move figures
jury

@@
 \vspace{2em}
-{\bf Comment: } {\itshape Could you add one example to the end of Section 4 to show $R_1$, $R_2$, $R_3$, $R_4$ for a simple LTI system?
+{\bf Comment: } {\itshape 
+Could you add one example to the end of Section 4 to show $R_1$, $R_2$, $R_3$, $R_4$ for a simple LTI system?
 
@@
 
-\todo[inline]{Eli: can you clarify?}
+\todo[inline]{Eli: can you clarify? Again, this is just Jury's criteria, we don't really have space to go over examples of basic control theory }
 
@@
 {\bf Response: }
+We apologise for leaving the relatively brief presentation of Jury's criteria in section 4. This is standard
+work in the control literature, and so, given the space restrictions, we prioritised our contributions in the write up. 
+We have added a brief clarification of the notation $m_{ij}$ as follows:
 
-\todo[inline]{Eli: can we elaborate?}
+\rev{where $m_{ij}$ denotes the element in position $(i,j)$ of the matrix $M$, as defined previously}.
 

### 2019-07-19 automatica/paper.tex
jury
intro

@@
 Models are linear differential equations with inputs, evolving over a continuous state space. 
-The synthesis precisely accounts for the effects of finite precision arithmetic introduced by the controller. 
+The synthesis precisely accounts for the effects of finite-precision arithmetic introduced by the controller. 
 The approach uses counterexample-guided inductive synthesis (CEGIS): 
@@
 if the verification step fails, 
-a counterexample is provided to the inductive generalization and the process iterates until a safe controller is obtained.  
+a counterexample is provided to the inductive generalization, and the process further iterates until a safe controller is obtained.  
 We demonstrate the practical value of this approach by automatically synthesizing safe controllers for physical plant models from the digital control literature.
@@
 However, provably correct synthesis of control software for such platforms, 
-needed if certification is in order, is non-trivial even in cases with unsophisticated dynamics.
-
-In this paper, we examine the case of physical systems (a.k.a. plants in control literature) described mathematically as 
+needed if certification is in order, is non-trivial even in cases with unsophisticated system dynamics.
+
+In this paper, we examine the case of physical systems (known as `plants' in the control literature) that are mathematically described as 
 Linear Time Invariant (LTI) models, for which the classical synthesis of controllers is well understood. 
 However, the use of digital control architectures adds new challenges
-caused by artefacts specific to digital control, such as the effects
+caused by artefacts that are specific to digital control, such as the effects 
 of finite-precision arithmetic and quantization 
@@
 correct-by-design digital controllers that addresses these challenges. 
-Specifically, we automatically synthesize %stable and 
+Specifically, \rev{moving beyond classical literature in digital control~\cite{astrom1997computer, Franklin15}}, 
+we automatically synthesize %stable and 
 safe,
@@
 %% observer~\cite{astrom1997computer}
-in a finite precision domain. Our model also accounts for representation errors introduced
-by our modelling of the plant using finite precision arithmetic. 
+in a finite-precision domain. Our model also accounts for representation errors introduced
+by our modelling of the plant using finite-precision arithmetic. 
 We reason about \rev{specific} safety requirements, which are frequently overlooked in conventional feedback control synthesis, 
@@
 \else
-We further present a novel approach for the synthesis of digital controllers making 
+We present a novel approach for the synthesis of digital controllers that makes  
 \fi
@@
 \fi
-uses a multi-staged technique\rev{, shown in Figure~\ref{fig:CEGIS-precision-increment}}, that starts by devising a
+uses a multi-staged technique\rev{, shown in Figure~\ref{fig:CEGIS-precision-increment}}: 
+it starts by devising a
 digital controller that stabilizes the plant model while remaining safe for a
 pre-selected time horizon and a single initial state; then, it verifies
-unbounded-time safety by unfolding the model dynamics, considering the 
+an unbounded-time safety requirement by unfolding the model dynamics, considering the 
 full set of initial states, and checking a \emph{completeness
-threshold}~\cite{DBLP:conf/vmcai/KroeningS03}, i.e., 
-the number of stages required to sufficiently unwind the closed-loop model 
-such that the safety boundaries \rev{(assumed to be a compact set)} are not violated for any 
-larger number of iterations\rev{, illustrated in Figure~\ref{fig:ct}}.
+threshold}~\cite{DBLP:conf/vmcai/KroeningS03}: 
+\rev{this is the number of stages required to sufficiently unwind the closed-loop model}  
+such that the safety boundaries \rev{(which are assumed to be a compact set)} are not violated for any 
+larger number of iterations\rev{, as illustrated in Figure~\ref{fig:ct}}.
 
@@
 
+\medskip
+
 %% \addtodo{CD: the novelty compared to CAV'17 needs to be clarified}
-This paper is an extension of~\cite{DBLP:conf/cav/AbateBCCDKKP17}
-and puts forward the following contributions: 
+In summary this paper, which is an extension of~\cite{DBLP:conf/cav/AbateBCCDKKP17}, 
+puts forward the following contributions: 
 % (the fourth is a  specific extension to~\cite{DBLP:conf/cav/AbateBCCDKKP17}): 
@@
   The automatically computed state-feedback
-  controllers guarantee a given safety specification.
-  The implication is that, as opposed to existing
-  methods for controller synthesis which rely on transfer function
-  representations, we must consider a state-space representation of
-  the physical system. Such a representation requires ensuring the
+  controllers guarantee the validity of a given safety specification. 
+  This objective, unlike existing methods for controller synthesis that rely on transfer function
+  representations, requires to consider a state-space representation of
+  the physical system. Such a representation ensures the validity of the 
   specification over actual traces of the state-space model, alongside the
   numerical soundness required by the effects of discretisation and 
-  finite precision errors.
+  finite-precision errors.
 
@@
 
-\item A limitation of the work in~\cite{DBLP:conf/cav/AbateBCCDKKP17} 
+\item A limitation of the work in~\cite{DBLP:conf/cav/AbateBCCDKKP17}, which this contribution extends,  
   is its restriction to fixed-point arithmetic, meaning that fixed-point
@@
 correct-by-design programs from high-level specifications. Algorithms
-for this problem have made substantial progress in recent years, in
-particular CEGIS, which is a recent approach to inductive synthesis.
+for this task have made substantial progress over recent years, in
+particular the architecture known as CEGIS, which is a recent approach to inductive synthesis.
 %% borrowing ideas from counterexample guided abstraction refinement
@@
 Program synthesizers are an ideal fit for the synthesis of digital controllers, 
-since the semantics of programs precisely capture the effects of finite precision arithmetic.  
+since the semantics of programs precisely capture the effects of finite-precision arithmetic.  
 However the control literature has been oblivious to this relevant connection. 
@@
 traces of the model, alongside the numerical soundness required by the
-effects of discretisation and the errors related to finite precision arithmetic.
+effects of discretisation and the errors related to finite-precision arithmetic.
 
@@
 Recent results in digital control have focused on separate aspects of discretization, 
-e.g. delayed response~\cite{Duggirala2015} and finite precision arithmetic, 
+e.g. delayed response~\cite{Duggirala2015} and finite-precision arithmetic, 
 with the goal either to verify~\cite{daes20161} the correctness of the implementation or to optimize~\cite{oudjida2014design} its design.
 
-There are two different problems that arise from finite precision arithmetic in digital controllers.  
+There are two different problems that arise from finite-precision arithmetic in digital controllers.  
 The first is the error caused by the inability to represent the exact state of the physical system, 
@@
 In~\cite{fialho1994stability}, a stability measure based on the error of the digital dynamics ensures that
-the deviation introduced by finite precision arithmetic does not lead to instability.  
+the deviation introduced by finite-precision arithmetic does not lead to instability.  
 \cite{DBLP:journals/automatica/WuLCC09} uses $\mu$-calculus to synthesise directly a digital controller, 
@@
 \item
-We account for the error introduced by finite precision arithmetic applied over the model variables $x_k$ and $u_k$, 
+We account for the error introduced by finite-precision arithmetic applied over the model variables $x_k$ and $u_k$, 
 %\note{here I have replaced the continuous-time signals with discrete-time ones}, 
@@
       m_{51}>0 \wedge \ldots \wedge\allowbreak
-      m_{(2N{-}3)(1)}>0$.
+      m_{(2N{-}3)(1)}>0$, \rev{where $m_{ij}$ denotes the element in position $(i,j)$ of the matrix $M$, as defined previously}.
 %\end{itemize}
@@
 deriving from several sources: 
-we formally bound the numerical error introduced by the finite precision representation of the plant (and its operations), 
+we formally bound the numerical error introduced by the finite-precision representation of the plant (and its operations), 
 and precisely model the behaviour introduced by the ADC/DAC conversions, 
@@
 %
-\item Division: the operations performed by the controllers in the finite precision
+\item Division: the operations performed by the controllers in the finite-precision
 domain do not include division.  However, we do use division in computations within the model.  
@@
 
-\subsection{Effect of finite precision arithmetic on safety specification and on stability}
-
-In this section we will quantify how the finite precision arithmetic in a digital controller affects the
+\subsection{Effect of finite-precision arithmetic on safety specification and on stability}
+
+In this section we will quantify how the finite-precision arithmetic in a digital controller affects the
 safety and stability properties of an LTI model.
 
-\subsubsection{Safety of closed-loop models with finite precision controller error}
+\subsubsection{Safety of closed-loop models with finite-precision controller error}
 
@@
 Recall that a closed-loop asymptotically stable system will converge to the origin.  
-We know that the original system with an infinite precision controller is stable, 
+We know that the original system with an infinite-precision controller is stable, 
 because we have synthesized it to meet Jury's criterion.  
@@
 We can thus disregard these steady-state errors (caused by
-finite precision arithmetic) when stability is ensured by synthesis, and then verify its
-safety accounting for the finite precision errors.
+finite-precision arithmetic) when stability is ensured by synthesis, and then verify its
+safety accounting for the finite-precision errors.
 
@@
 We employ a multi-stage approach that unwinds the dynamics of the model up to a completeness threshold, 
-encompassing finite precision arithmetic using bit-precise bounded model checking, 
+encompassing finite-precision arithmetic using bit-precise bounded model checking, 
 and then verifying soundness of the resulting controller using interval arithmetic. 
@@
 underlying SAT/SMT solver to address verification checks.  We~model the 
-effects of finite precision arithmetic 
+effects of finite-precision arithmetic 
 explicitly using CBMC's nondeterminism API (e.g., \texttt{nondet},
@@
 %and the abstraction-based 
-CEGIS approach is able to generate finite precision digital controllers using fixed-point and floating-point arithmetic in a reasonable amount of time.
+CEGIS approach is able to generate finite-precision digital controllers using fixed-point and floating-point arithmetic in a reasonable amount of time.
 %\item[EG2] \textbf{(Sanity check)} Confirm the stability \note{also?} and safety of the synthesized controllers outside 
@@
 %
-Our experimental results show we are able to synthesize fully automatically safe controllers for diverse benchmarks from the control literature, 
+Our experimental results show that we are able to synthesize automatically safe controllers for diverse benchmarks from the digital control literature, 
 within a reasonable amount of time.  
@@
 
-\bibliographystyle{spbasic}       % Include this if you use bibtex 
+\bibliographystyle{plain}       % Include this if you use bibtex 
 \bibliography{paper}           % and a bib file to produce the 

### 2019-07-19 automatica/paper.tex
sec 2, 3

@@
 since the semantics of programs precisely capture the effects of finite-precision arithmetic.  
-However the control literature has been oblivious to this relevant connection. 
+Surprisingly,  the control literature has been oblivious to this relevant connection. 
 A relevant exception is~\cite{DBLP:conf/cdc/RavanbakhshS15}, 
-which employs CEGIS for the synthesis of switching controllers for stabilizing continuous-time
+which employs CEGIS on the synthesis of switching controllers for stabilizing continuous-time
 plants.  
 %with polynomial dynamics.  
-The work 
+This work hinges on and  
 % extends to affine systems \note{extension or restriction?}, but 
-is limited by the capacity of the state-of-the-art SMT solvers for solving
-linear arithmetic.  Since this approach uses switching actions for the digital controller, it avoids problems related to
-finite-precision arithmetic, but potentially suffers from state-space
+is limited by the capacity of the state-of-the-art SMT solvers to reason over 
+linear arithmetic \rev{problems}.  Since this contribution employs \rev{finite} switching actions for the digital controller, it avoids problems related to
+finite-precision arithmetic, but potentially suffers from the state-space 
 explosion.  Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same
@@
 switching controllers that guarantee \emph{reach-while-stay} properties of
-closed-loop systems, i.e., properties that specify a set of goal states and
-safe states (constrained reachability).  This solution is based on
+closed-loop systems, i.e., properties that specify both a set of goal states and
+safe states \rev{(this specification is also known as constrained reachability)}.  This solution is based on
 synthesizing control Lyapunov functions for switched systems that yield
@@
 However, both approaches are unsuitable for the kind of controllers that we seek to
-synthesize, which are not switching in nature.
+synthesize, which are not switching in nature but rather continuous (as further detailed later).
 
 The work in~\cite{hscc-paper} synthesizes stabilizing controllers for
-continuous plants given as transfer functions by exploiting bit-accurate
+continuous plants given as transfer functions, by exploiting bit-accurate
 verification of software-implemented digital controllers~\cite{Bessa16}.  
@@
 effects of discretisation and the errors related to finite-precision arithmetic.  
-
+%The new approach also ensures safety specifications, as opposed to stability ones as in~\cite{hscc-paper}.
+
+\rev{Furthermore, unlike the approach in~\cite{hscc-paper}, this work reasons over state-space models. }
 A~state-space model has well known advantages over the transfer function
@@
 %to synthesize controllers that make the closed-loop model 
-\emph{safety}.  Our work indeed focuses on the safety of internal states, 
+\emph{safety}.  Our work indeed focuses on the safety of internal states \rev{(which we assume to fully observe)}, 
 which is by and large overlooked in the standard (digital) control literature, 
@@
 The approach underpinning tools such as Pessoa~\cite{mazo2010pessoa}, related extensions \cite{Anta2010,liu16} and applications \cite{zamani2014} 
-synthesizes correct-by-design embedded control software by abstraction of the model as a finite-state machine, 
+synthesizes correct-by-design embedded control software by formally abstracting the model to a finite-state machine, 
 and on the formal control synthesis over safety- and reachability-based temporal properties thereon.  
+\rev{Whilst in principle this formal abstraction can account for the errors that we can deal with, 
+it is expected to provide a controller of different nature than the one we generate. }
 %Based on this safety specification, \mbox{Pessoa} can synthesize embedded controller software for a range of
 %properties.  
-The obtained finite controller software can then be implemented over the concrete LTI model. 
+The obtained finite controller software can then be implemented \rev{(refined)} over the concrete LTI model. 
 %can be more complicated than
@@
 invariant computation on the discrete dynamics using Semi-Definite
-Programming (SDP):  while the former contribution a uses bounded-input and bounded-output
+Programming (SDP):  while the former contribution uses a bounded-input and bounded-output
 (BIBO) notion of stability, the latter employs Lyapunov-based
@@
 The work in~\cite{picasso2003stabilization} introduces invariant sets as a mechanism to
-bound the quantization error effect on stabilization.  
+bound the effect of quantization error on stabilization.  
 % as an invariant set that always converges toward the controllable set.  
 Similarly, 
-\cite{liberzon2003hybrid} evaluates the quantization error dynamics and calculates an upper and lower
-bound for the possible trajectory of the system, up to a finite time. 
+\cite{liberzon2003hybrid} evaluates the quantization error dynamics and calculates upper and lower
+bounds for the possible trajectory of the system, up to a finite time. 
 The last two approaches can be placed within the research area known as ``hybrid systems theory.''  
@@
  comprising an analogue model of the underlying real system, 
- alongside a digital controller. 
+ alongside a digital controller  
  \label{fig:digitalsystem}}
@@
 We consider models of physical plants expressed as ordinary differential
-equations, which we assume are controllable~\cite{Astrom08}: 
+equations, which we assume to be controllable~\cite{Astrom08}: 
 %
@@
 $\mat{A}_d=e^{\mat{A}T_s}$ and 
-$\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$, 
-$k \in \mathbb N$ is a discrete counter and where $\vec{x}_{0}=\vec{x}(0)$ denotes the initial state. 
-We assume that specifications on the model concern \eqref{eq:plant}, 
-and plan to devise controllers $\vec{u}_k$ to meet them. 
+$\mat{B}_d = \int_{t = 0}^{T_s} e^{\mat{A} t} dt\ \mat{B}$, and where 
+$k \in \mathbb N$ is a discrete counter and $\vec{x}_{0}=\vec{x}(0)$ denotes the initial state. 
+We assume that specifications concern the model in \eqref{eq:plant}, 
+and we plan to devise controllers $\vec{u}_k$ to meet them. 
 (The more general problem of synthesising controllers $u(t)$ for \eqref{eq:ode1} fall outside the scope of the present work.)
@@
 we are interested in the synthesis of digital feedback controllers $u_k$, as in Fig. \ref{fig:digitalsystem},  
-as practically implemented on Field-Programmable Gate Arrays or Digital Signal Processors   
+as practically implemented on Field-Programmable Gate Arrays or on Digital Signal Processors,    
 %This requires us to consider the errors introduced by, we will address the issue of variable quantization, 
@@
 and $r_{k}$ is a reference signal (again digital). 
-We will assume $r_k=0$, thus obtaining the closed-loop model 
+We will assume $r_k=0$ \rev{(meaning that the reference signal is just the origin)}, thus obtaining the closed-loop model 
 $\vec{x}_{k+1}=(\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_k$.
@@
 later in this work, we will target a less standard objective,
-namely a quantitative safety requirement \rev{over a convex set around the origin}, 
+namely a quantitative safety requirement \rev{defined over a convex set around the origin}, 
 which opens up to more complex specifications \cite{BYG16, Tab09}. 
@@
 of the controller, which manipulates quantised signals as discrete quantities represented with
-finite precision. The new approach is fully automated and leverages an approach based on CEGIS.
+finite precision. The new approach is fully automated and leverages an approach based on CEGIS, 
+to be introduced shortly.
 
@@
 is defined in the following section. 
-As discussed later, specifically for linear models a safe controller is necessarily asymptotically stable, 
+As discussed later, for linear models a safe controller is necessarily asymptotically stable, 
 although the reverse is not true. 
@@
 In the case of linear systems %as in~\eqref{eq:closedloopss}, 
-considered with a zero reference signal, 
+considered with a zero reference signal \rev{(as assumed above)}, 
 the equilibrium point of interest is the origin (see Figure~\ref{fig:ct} for the portrait of an asymptotically stable execution, converging to the origin).
@@
 is asymptotically stable if all the roots of its characteristic polynomial (i.e., the
-eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
-circle of the complex plane, i.e., if their absolute values are strictly less than
+eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unit 
+circle on the complex plane, i.e., if their absolute values are strictly less than
 one~\cite{astrom1997computer}. 
@@
 this is not necessary in the context of this work.    
-What is technically key is that in this paper, 
+What is technically key is that in this paper  
 we shall express this asymptotic stability as a specification $\phi_\mathit{stability}$, 
@@
 so that the closed-loop dynamics are shaped as desired.  
+\rev{We refer the interested reader to~\cite{fadali} for further details about Jury's criterion, which we omit for the sake of space and since it is a standard result in the control literature that we just leverage for our overall approach.
+}
 
@@
 %\eqref{eq:closedloopss} 
-meets a given safety specification \rev{that depends on a given set around the origin}.  
+meets a given safety specification \rev{that is characterised by a given set around the origin}.  
 A safety specification gives rise to a requirement on the states of the model, 
@@
 \label{eq:safetyliteral}
-\phi_\mathit{safety} = \left\{ \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}}\right\},
+\phi_\mathit{safety} = \left\{ \forall k\ge 0,\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}}\right\},
 \end{equation}
@@
 which we assume have given bounds:
-$\phi_\mathit{input} = \{\forall k \geq 0.\bigwedge_{i=1}^{p} \underline{u} \leq u_{i} \leq \overline{u}\} $,
+$\phi_\mathit{input} = \{\forall k \geq 0,\bigwedge_{i=1}^{p} \underline{u} \leq u_{i} \leq \overline{u}\} $,
 and $\phi_\mathit{init} = \{ \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}\}$. 
-The former constraint expresses that control input, possibly shaped via state-feedback, 
+The former constraint expresses that the control input, possibly shaped via state-feedback, 
 might saturate in view of physical constraints.
 \rev{Notice that we will assume that the set of initial states lies within the safe set, since the contrary leads to dynamics that are trivially unsafe. 
-Furthermore, whilst the problem can handle general hyper-boxes, we will in practice work with set that contain the origin. }
+Furthermore, whilst the problem can handle general hyper-boxes, we will in practice work with sets that contain the origin, particularly in view of the choice of the reference signal $r_k = 0$. }
 
@@
 
-We employ the bounded model checker CBMC~\cite{DBLP:conf/tacas/KroeningT14} to model the controller behavior on digital signals with finite bit-precision.  
+We employ the bounded model checking software tool CBMC~\cite{DBLP:conf/tacas/KroeningT14} to model the controller behavior on digital signals with finite-bit precision.  
 We express the controller semantics as C programs, which is CBMC's preferred input language.  
-CBMC symbolically executes every instruction in an input program by translating it to a boolean satisfiability problem,
+CBMC symbolically executes every instruction in an input program by translating it to a Boolean satisfiability problem,
  which is satisfiable iff a certain property about the program holds.  
@@
 %-------------------------------s
-\subsection{Semantics of finite-precision arithmetics}
+\subsection{Semantics of finite-precision arithmetic}
 \label{sec:errors}
 
-A key contribution of this work is that, when synthesizing controllers, it precisely replicates the finite-precision arithmetic within the digital controller, 
+A key contribution of this work is that 
+%, when synthesizing controllers, 
+\rev{it precisely replicates the finite-precision arithmetic within the digital controller it synthesizes,  } 
 thus guaranteeing that controllers implemented with finite-precision arithmetic are safe. 
-The specific components of the model, shown in Figure~\ref{fig:digitalsystem}, we are concerned with are the ADC, digital controller and DAC.
+The specific components of the model we are concerned with, shown in Figure~\ref{fig:digitalsystem}, are the ADC, the digital controller and the DAC. 
 Details of how we model the behaviour of the finite-precision arithmetic in these components are in Section~\ref{sec:numeric_rep}. 
@@
 In order to guarantee soundness, we therefore encompass the error that is due to modelling (as opposed to the nature of the digital controller):   
-the representations used in the plant model and its arithmetic operations are carried out at finite precision.  
+the representations used in the plant model and its arithmetic operations are carried out at finite precision.  More specifically: 
 \begin{itemize} 
@@
 
-In this paper we will use $\mathcal{F}_{\langle I,F \rangle}(x)$ to denote a real number $x$ expressed at a fixed-point precision, 
+In this paper we will use $\mathcal{F}_{\langle I,F \rangle}(x)$ to denote a real number $x$ expressed with a fixed-point precision, 
 using $I$ bits to represent the integer part of the number and $F$ bits to represent its decimal part.  
@@
 \end{figure}
+
+\todo{Elizabeth: please make sure this section on CEGIS is perfect.}
 
@@
 In the context of the formal synthesis of safe controllers, 
+of interest or this work, 
 the set of possible {\sc inputs} corresponds to the set of possible initial states and the 

### 2019-07-20 automatica/paper.tex
sec 4

@@
 %-------------------------------
-\subsection{Counterexample-Guided Inductive Synthesis} 
+\subsection{Counterexample-Guided Inductive Synthesis (CEGIS)} 
 \label{ssec:cegis}
@@
 Figure~\ref{fig:CEGIS}) and a verification phase (denoted by {\sc
-  Verify}), which interacts via a finite set of tests {\sc
+  Verify} in Figure~\ref{fig:CEGIS}), which interacts via a finite set of tests {\sc
   inputs} that is updated incrementally.
@@
 In the context of the formal synthesis of safe controllers, 
-of interest or this work, 
+of interest for this work, 
 the set of possible {\sc inputs} corresponds to the set of possible initial states and the 
@@
 %-------------------------------
-\section{Formal specification of properties on a model} 
+\section{Formal specification of \rev{stability on a model}} 
 \label{sec:specification}
@@
 
-%While in the previous section we have discussed the generic CEGIS framework, 
-We are now equipped to apply the general CEGIS framework to the synthesis of digital controllers. 
-We start by describing the property that we pass to the synthesizer as the specification $\phi$. 
-Namely, as we are interested in capturing safety (as discussed in Section~\ref{sec:safety}),  
+\todo{I feel that this section had an overtly general title and intro, but was actually limited to discussing the encoding of stability - I have focussed this.}
+
+%While in the previous section we have discussed the generic CEGIS framework, We are now equipped to apply the general CEGIS framework to the synthesis of digital controllers.
+We start by describing the property that we pass to the synthesizer as a specification $\phi$.
+Since we are interested in capturing safety (as encoded in Equation~\eqref{eq:safetyliteral} in Section~\ref{sec:safety}),  
 we use a stability specification to narrow the search space of possible controllers, as detailed in Section~\ref{ssec:stabspecification}. 
+\rev{Essentially, we employ stability as a precursor to safety.}
 
@@
 %and another one based on Jury's criterion~\cite{astrom1997computer}.  
-Here we select the Jury stability criterion~\cite{astrom1997computer}, 
+Here we select the classical {\it Jury's stability criterion}~\cite{astrom1997computer}, 
 in view of its efficiency and ease of integration within our implementation.  
-This method checks the stability working in the complex domain of the characteristic polynomial $S(z)$,  
+This method checks the stability \rev{of a model} working over the complex domain of its characteristic polynomial $S(z)$,   
 %
@@
 \end{equation*}
-This polynomial is obtained as a function of the state-space matrices $A_d,B_d$~\cite{Astrom08}, 
+\rev{A standard result in Control theory~\cite{Astrom08} states that }
+this polynomial can be obtained as a function of the state-space matrices $A_d,B_d$,  
 and in particular its order $N$ corresponds to the dimensions of the state variables (above, $n$).  
@@
 eigenvalues of the matrix $A_d-B_dK$) are inside the unit circle in the complex plane, 
-i.e., if their absolute values are less than one.
+i.e., when the absolute values of the roots are less than one.
 
@@
 
-The following matrix $M$ with dimension $(2N-2)\times N$ and elements $m_{(\cdot),(\cdot)}$ is built from the coefficients of $S(z)$ as:  
+\rev{Skipping the full algebraic derivation for the sake of space (this can be found in~\cite{astrom1997computer}), }
+the following matrix $M$ with dimension $(2N-2)\times N$ and elements $m_{(\cdot),(\cdot)}$ is built from the coefficients of $S(z)$ as:  
 %
@@
 
-In conclusion, 
+Finally, 
 the asymptotic stability property is finally encoded by a constraint expressed as the following formula: 
@@
 
+\todo{This Section seems coherent. However, Elizabeth can you carefully check it once again?}
+
 As discussed in Section~\ref{sec:errors}, 
@@
 and precisely model the behaviour introduced by the ADC/DAC conversions, 
-as well as the behaviour of the limited-precision arithmetic used by the controller.
+as well as the behaviour of the limited-precision arithmetic used in the controller.
 
@@
 and we use the Boost interval arithmetic library~\cite{DBLP:journals/tcs/BronnimannMP06} to bound the error in this representation. 
-We employ a compositional numerical library to model the fixed point arithmetic for the controller\footnote{\url{https://github.com/johnmcfarlane/cnl}} within double-precision floating-point numbers. 
+We employ a compositional numerical library to model the fixed-point arithmetic for the controller\footnote{\url{https://github.com/johnmcfarlane/cnl}} within double-precision floating-point numbers. 
 We check that the controller is safe starting from each vertex of the set of initial states,  
@@
 \rangle}(x_{k})$; and second, the rounding error introduced by the multiplication operation. 
-Recall that this error is modelled precisely by bounded model checking.
+Recall that this error \rev{[CLARIFY WHICH OF THE PREVIOUS TWO]} is modelled precisely by bounded model checking.
 
@@
 The validity of Jury's criterion~\cite{fadali} relies on the representation of the closed-loop dynamics $x_{k+1} = (A_d - B_dK) x_k$ at infinite precision.  
-When we employ a fixed-point arithmetic digital controller, the operation above can be expressed as follows, where we use $\mathcal{F}_{\langle I_c,F_c \rangle}$ preceding a variable to indicate that variable is converted into the fixed-point precision given by $\mathcal{F}_{\langle I_c,F_c \rangle}$:
+\rev{When we employ a digital controller with fixed-point arithmetic}, the operation above can be expressed as follows, where we use $\mathcal{F}_{\langle I_c,F_c \rangle}$ preceding a variable to indicate that variable is converted into the fixed-point precision given by $\mathcal{F}_{\langle I_c,F_c \rangle}$:
 %
@@
 %
-As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the safe set of states given by the safety specification
+As a result, if the value $(I - A_d + B_dK)^{-1}B_dk\delta$ is within the safe set of states given by the safety specification, 
 then the synthesized fixed-point controller results in a safe
@@
 make it asymptotically stable.
-However,
-since in this paper we require stability only as a precursor to safety, it
-is sufficient to check that the perturbed model converges to a
+Since in this paper we require stability only as a precursor to safety, it
+is thus sufficient to check that the perturbed model converges to a
 neighborhood of the equilibrium within the safe set.

### 2019-07-20 automatica/paper.tex
all sections

@@
 A similar argument can be made for floating-point arithmetic.
-We can thus disregard these steady-state errors (caused by
-finite-precision arithmetic) when stability is ensured by synthesis, and then verify its
+In conclusion, we can thus disregard these steady-state errors (caused by
+finite-precision arithmetic) when stability is ensured by synthesis, and then verify  
 safety accounting for the finite-precision errors.
@@
 and we synthesize a safe controller by
-unfolding the transition system (.e., the closed-loop model) $k$ steps and by selecting a controller $K$ and a single initial state, 
-such that the states at each step do not violate the safety criteria (see Section~\ref{sec:safety}).    
+unfolding the transition system (i.e., the closed-loop model) $k$ steps and by selecting a controller $K$ and a single initial state, 
+such that the states at each step do not violate the safety requirement (see Section~\ref{sec:safety}).    
 That is, we ask the bounded model checker~\cite{ClarkeKL04} if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states, and a given fixed-point precision for the controller, and where the input signal remains within the specified bounds.
@@
 
-The first {\sc verify} stage, {\sc safety} is shown in Alg.~\ref{alg:safetycheck}. 
+The first {\sc verify} stage, {\sc safety} is shown in Algorithm~\ref{alg:safetycheck}. 
 The algorithm checks that the candidate
@@
 \rev{Assuming that the initial set is included within the safe set, }
-if a controller is safe for each of the corner cases of the hypercube of allowed initial states, 
-i.e., the vertex states, then it is safe for any initial state in the hypercube. 
+if a controller is safe for each of the corner cases of the hyper-box of allowed initial states, 
+i.e., the vertex states, then it is safe for any initial state in the hyper-box. 
 \end{theorem}
 \begin{proof}
-Consider the set of initial states, $X_0$, which we note is convex since it is a hypercube. 
+Consider the set of initial states, $X_0$, which we note is convex since it is a hyper-box. 
 Name $v_i$ its vertices, where $i=1,\ldots, 2^n$.  
@@
 Summarising, we only need to check $2^n$ initial states, 
-where $n$ is the dimension of the state space (number of continuous variables).
+where $n$ is the dimension of the state space (number of continuous variables). \todo{Add remark from reviewer that this number can be lower in actuality?}
 
@@
 \rev{ However, this monotonic decrease cannot be ensured in general when dealing with complex eigenvalues. } 
-Consider the closed-loop matrix that updates the
-states in every discrete time step, and select the eigenvalue $\vartheta$ 
+In this second instance, consider the closed-loop matrix that updates the
+states at each discrete time step, and select the eigenvalue $\vartheta$ 
 with the smallest (non-zero) imaginary part.  
@@
 any other pair of complex eigenvalues will correspond to dynamics that rotate faster within the corresponding eigenspace. 
-Hence, $\overline{k}$ will again represent a completeness threshold. }
+Hence, $\overline{k}$ will again represent a global completeness threshold. }
 \qed 
@@
 The synthesis is considered to be \emph{successful} if a digital controller is
-correctly synthesized with respect to the effects of finite-precision arithmetic within the 5 hour time-out.
-
-Our CEGIS engine is implemented as an integrated module within the C bounded
+correctly synthesized with respect to the effects of finite-precision arithmetic within a time-out set to 5 hours.
+
+The CEGIS engine is implemented as an integrated module within the C bounded
 model checker (CBMC)~\cite{ClarkeKL04}.  CBMC transforms the ANSI-C representation
@@
 Our benchmark suite consists of 19 case studies extracted from the control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, gajic2008optimal}.
-These case studies comprise control models, which we represent in state space form as in \eqref{eq:ode1}.
+These case studies comprise control models, which we represent in state space form as in Equation \eqref{eq:ode1}.
 The models are time discretized, with sampling times ranging from 1s to 0.0001s. 
-CEGIS initially starts with the coarsest discretisation (i.e., 1s sampling time), and if it fails to find a controller, reduces the sampling time.
+CEGIS initially starts with the coarsest discretisation (i.e., 1s sampling time), and if it fails to find a controller, it reduces the sampling time. 
 The initial states are bounded between $0.5$ and $-0.5$ for all states, and the safety specification requires that the states remain between $-1.5$ and $1.5$ \rev{(as remarked above, the initial set lies within the safe set and contains the origin)}.
@@
 The benchmarks \textit{Cruise 1}~\cite{Franklin15} and \textit{Cruise 2}~\cite{Astrom08} deal with automotive cruise control models, 
-where the control is used to maintain the speed of an automobile constant, 
-tracking a desired speed reference, and compensating disturbances and uncertainties.  % related to relief and terrain. 
+where the control is used to maintain the speed of an automobile at a constant value (after tracking a desired speed reference), 
+and compensating disturbances and uncertainties.  % related to relief and terrain. 
 %There are two continuous stirred tank reactor models named 
-\textit{cstr}  and \textit{cstrtmp}  describe the pH dynamics of a reaction 
+The models \textit{cstr}  and \textit{cstrtmp}  describe the pH dynamics of a reaction 
 of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
@@
 The \textit{inverted pendulum} benchmark  
-describes a model for the cart position and the angle of an inverted pendulum placed on the cart,  
+describes a model for the cart position and for the angle of an inverted pendulum placed on the cart,  
 %plant composed by a point mass, which must be equilibrated above the pivot point and is mounted on an one degree of freedom cart that 
-which moves over a track through a DC motor.  
+which moves over a track by means of a DC motor.  
 %
@@
 %
-The \textit{magsuspension} describes  the dynamic of a magnetic car suspension system. 
+The \textit{magsuspension} describes  the dynamics of a magnetic car suspension system. 
 The \textit{pendulum}  plant consists of a swinging point mass suspended from a frictionless pivot by means of a rod with negligible mass.  
@@
 attitude, {\it i.e.}, the orientation angles. An attitude control system must maintain the desired 
-orientation of a satellite with respect to an 
-inertial frame during all the excursion. 
+orientation of a satellite with respect to an inertial frame. % during all the excursion. 
 The \textit{springer-mass damper system} plant is a standard model for the dynamics of several mechanical systems. 
@@
 Using the state-space models described in Section~\ref{exp:benchmarks}, 
-the evaluation study has the following experimental goal:  
+the evaluation study has the following overall experimental goal:  
 \begin{enumerate}
@@
 The median run-time for the successful benchmarks is 15.7\,s for fixed-point and 17.8\,s for floating-point implementations, respectively.
-We consider these times to be short enough to be of practical use to control engineers, and thus affirm the validity of 
+We consider these times to be short enough to be of practical use to control engineers, and thus assert the success of 
 %EG1. 
-the objective we have raised.
-
-\smallskip
+the overall objective of the study that we have raised above.
 
@@
 footnote as an Open Virtual Appliance (OVA).\footnote{\url{www.cprover.org/DSSynth}} 
-The provided experimental environment runs multiple discretisations for each benchmark, and lists the fastest as the result synthesis time.
+The provided experimental environment runs multiple discretisations for each benchmark, and lists the fastest as the resulting synthesis time.
+
+\smallskip
 
@@
 
+\item[]
 \item[]
@@
 
-We have presented an automated approach to synthesize provably-correct digital state-feedback controllers that ensure both stability and safety over state-space models.   
+We have presented an automated approach to synthesize provably-correct digital state-feedback controllers that ensure 
+%both stability and 
+safety over state-space models.   
 %The first approach relies on unfolding of the closed-loop model dynamics up to a completeness threshold, while the second

### 2019-07-20 automatica/response.tex
response

@@
 We present below a detailed discussion of all comments, questions, and concerns raised by the reviewers. The major modifications are highlighted in
-blue in the revised manuscript. For clarity,  we also use \vold{v1} and \vnew{v2} in the response letter for referring respectively to the previous
+blue in the revised manuscript. 
+\todo{keep next?} For clarity,  we also use \vold{v1} and \vnew{v2} in the response letter for referring respectively to the previous
 and current versions of the manuscript.
@@
 \\
-With kind regards,\vspace{0.1cm}
+Best regards,\vspace{0.1cm}
 \\
@@
 It is a more mature, complete, and comprehensive presentation of the conference material. 
-Of these conference articles, the CAV/HSCC contributions presented the theory underlying the approach, 
-whereas the ASE is a tool paper. 
+Of these conference articles, the CAV/HSCC contributions provided an early presentation of the theory underlying the approach, 
+whereas the ASE was a tool paper.  
+The present contribution has new or updated experimental outcomes. 
 The application of the CEGIS architecture to the synthesis of digital controllers for continuous plants is indeed a novel contribution of this line of
@@
 We do need full observability of the (states of the) model, and have clarified this in Section 3.1, as follows: {\it We assume full observability of
-the states of the model, namely the output states correspond with the model variables.  } We recall this assumption later in the text.
+the states of the model, namely the output states correspond with the model variables.  } We recall this assumption later, throughout the manuscript.
 
@@
 
-The proof of Theorem 2 has been elaborated and made more comprehensive and detailed.
+The proof of Theorem 2 has been elaborated and has been made more detailed.
 
@@
 
-We have reviewed relevant literature on controller synthesis based on finite abstractions, cf. Belta and Tabuada.
+We have reviewed relevant literature on controller synthesis based on finite abstractions, cf. Belta, Tabuada, Zamani, et al.. We have clarified the differences with our approach in the manuscript.
 
-Literature on reachability analysis tackles a different problem, namely one of verification, rather than one of control synthesis (which this work
-focuses on).
+Furthermore, most literature on reachability analysis tackles a different problem, namely one of verification, rather than one of control synthesis (which this work
+focuses on). Admittedly, reachability analysis tool scale quite well (as the reviewer points out), however this is under clear assumptions on model dynamics. 
+Whilst algorithmically very advanced, notice that only a few of the available software tools for reachability analysis are actually numerically sound.
 
-Admittedly reachability analysis tool scale quite well (as the reviewer points out), however this is under clear assumptions on model dynamics.
-
-One might argue that reachability analysis tools could be embedded within the CEGIS framework, however they currently lack full soundness: namely they
-are algorithmically sound, but not numerically sound. On the contrary our work is sound on both sides. (Shall we mention that indeed we do
-reachability analysis via Axelerator in CAV17?)
+So one might argue that reachability analysis tools could be embedded within the CEGIS framework (incidentally, this was partly attempted in our CAV17 contribution), 
+however they currently lack full soundness: namely they 
+are algorithmically sound, but not numerically sound. On the contrary our work is sound on both sides.
 
@@
 
-\rev{It is probably true that the check on all vertices might not be necessary in general, that that this check might be simplified in special cases
+It is probably true that the check on all vertices might not be necessary in general, that that this check might be simplified in special cases
 or under special conditions. The check however, as it currently is implemented, does not represent the bottleneck of our overall method, so we can
-safely rely on its current form, as it stands. }
+safely rely on its current form, as it stands.  \todo{Add note to manuscript?}
 
@@
 
-\rev{
 Many thanks for this note. 
-Notice that in the submitted manuscript we had focused on special shapes of initial and safe sets, namely (convex) hyper-boxes, which included the
+Notice that already in the previous manuscript we had focused on special shapes of initial and safe sets, namely (convex) hyper-boxes, which include the
 origin. 
@@
 In conclusion, recall that the sets are hyper-boxes, thus convex, and that in view of the linear dynamics of the considered models, in practice both 
-are assumed to contain the origin.  }
+are assumed to contain the origin.
 
@@
 {\bf Response:}
- It is true that we would be able to encode more complex properties by introducing auxiliary variables; however theorem 2 is dependent on the safe set being convex, and 
-so this proof would not necessarily hold with more complex properties. It would be possible to construct time-bounded properties as automata that track history explicitly, but I can't see how
+ It is true that we would be able to encode more complex properties by introducing auxiliary variables; 
+ however,  Theorem 2 is dependent on the safe set being convex, and so this proof would not necessarily hold with more complex properties. 
+ It would be possible to construct time-bounded properties as automata that track history explicitly, but we can't see how
 it would be possible to avoid unwinding the transition relation using this method. In the case of the example given by the reviewer, an STL property with bounded time-horizon, unwinding
@@
 {\bf Response: }
-We have moved these figures to section 1 and incorporated them into the introduction. We are still referring back to these figures from section 5.
+We have moved these figures to Section 1 and incorporated them into the Introduction. We are still referring back to these figures from Section 5.
 
@@
 
+\todo{can we at least say that the values can be obtained form the SW tool, and say where in the tool they are computed? }
+
 \vspace{2em}

### 2019-07-23 automatica/response.tex
temporary commit

@@
 
-Fixed this now
+We apologise for this error and thank the reviewer for pointing it out. The DSSynth download from http://dsverifier.org/ is indeed the same code 
+as our implementation for this paper, but without the experimental results and benchmarks. The correct link is now functional: http://www.cprover.org/DSSynth/.
 
-\todo[inline]{Elizabeth: say what the problem was, fix this if possible, then thank the reviewer for pointing this out. }
+\todo[inline]{fix link }
 
@@
 We have added the following sentence to clarify this:
-\todo[inline]{add this}
+
+\rev{The bounded model checker selects the controller $K$ values using a satisfiability solver, i.e.,
+by constraint solving. As such, we do not need to consider traditional control approaches such as pole placement.}
 

### 2019-07-23 automatica/paper.tex
temporary commit

@@
 
+A large body of work exists on evaluating fixed-point errors and bridging the gap between real value
+and fixed-point values in synthesis in other application areas and using other
+algorithmic techniques; 
+Genetic programming has been used to minimise the error in synthesised fixed-point programs~\cite{Darulova};
+Smoothed proof search reduces the problem of boolean  a sequence of optimization problems
+
 %-------------------------------
@@
 such that the states at each step do not violate the safety requirement (see Section~\ref{sec:safety}).    
-That is, we ask the bounded model checker~\cite{ClarkeKL04} if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states, and a given fixed-point precision for the controller, and where the input signal remains within the specified bounds.
-This approach is sound, i.e., the controller produced is guaranteed to be safe, if the current $k$ is greater than the completeness threshold (see later step).  
+That is, we ask the bounded model checker~\cite{ClarkeKL04} if there exists a $K$ that is safe for at least 
+one $x_0$ in our set of all possible initial states, and a given fixed-point precision for 
+the controller, and where the input signal remains within the specified bounds. 
+\rev{The bounded model checker selects the controller $K$ values using a satisfiability solver, i.e.,
+by constraint solving. As such, we do not need to consider traditional control approaches such as pole placement.}
+This approach is sound, i.e., the controller produced is guaranteed to be safe, if the 
+current $k$ is greater than the completeness threshold (see later step).  
 We also assume some finite precision for the model and a given time discretisation, as described in section~\ref{sec:model}.  

### 2019-07-23 automatica/response.tex
more response

@@
 We have added a discussion about these applications and results to the related work as follows:
-\todo[inline]{add discussion}
+
+\vskip{2em}
+Similarly, 
+\cite{liberzon2003hybrid} evaluates the quantization error dynamics and calculates upper and lower
+bounds for the possible trajectory of the system, up to a finite time. \rev{Considering the problem of multi-modal
+dynamics,~\cite{DBLP:conf/emsoft/JhaST11} uses numerical optimization techniques to learn optimal switching logic for hybrid systems.
+The last three} approaches can be placed within the research area known as ``hybrid systems theory.''  
+%This technique works for both linear and non-linear systems.
+The present contribution distances itself from all these cognate results.
+
+\rev{A large body of work exists on evaluating fixed-point errors and bridging the gap between real value
+and fixed-point values in synthesis in other application areas and using other
+algorithmic techniques:
+Genetic programming has been used to minimise the error in synthesised fixed-point programs~\cite{DBLP:conf/emsoft/DarulovaKMS13};
+Smoothed proof search reduces the problem of parameter synthesis under boolean and quantitative 
+objectives to a sequence of optimisation problems~\cite{DBLP:conf/popl/ChaudhuriCS14}; Synthesis of 
+optimal fixed-point implementations of floating-point numerical software can be done using testing and induction~\cite{DBLP:journals/corr/abs-1302-1920}.
+All of these works present potential future applications for CEGIS in synthesising implementations in fixed-point arithmetic.}
 
@@
 Could you add one example to the end of Section 4 to show $R_1$, $R_2$, $R_3$, $R_4$ for a simple LTI system?
-
-\vspace{1em}
-{\bf Response: }
-
-\todo[inline]{Eli: can you clarify? Again, this is just Jury's criteria, we don't really have space to go over examples of basic control theory }
-
-\todo{can we at least say that the values can be obtained form the SW tool, and say where in the tool they are computed? }
 
@@
 work in the control literature, and so, given the space restrictions, we prioritised our contributions in the write up. 
+The values for $R_1$, $R_2$, $R_3$, $R_4$, and the corresponding values in the matrix $M$ are outputted in the counterexample
+trace obtained from the synthesis phase in the software tool 
+if it is run with full verbosity.
+
 We have added a brief clarification of the notation $m_{ij}$ as follows:
@@
 
-\bibliographystyle{alpha}
+\bibliographystyle{plain}
 \bibliography{}

### 2019-07-23 automatica/paper.tex
more response

@@
 \cite{liberzon2003hybrid} evaluates the quantization error dynamics and calculates upper and lower
-bounds for the possible trajectory of the system, up to a finite time. 
-The last two approaches can be placed within the research area known as ``hybrid systems theory.''  
+bounds for the possible trajectory of the system, up to a finite time. \rev{Considering the problem of multi-modal
+dynamics,~\cite{DBLP:conf/emsoft/JhaST11} uses numerical optimization techniques to learn optimal switching logic for hybrid systems.
+The last three} approaches can be placed within the research area known as ``hybrid systems theory.''  
 %This technique works for both linear and non-linear systems.
@@
 
-A large body of work exists on evaluating fixed-point errors and bridging the gap between real value
+\rev{A large body of work exists on evaluating fixed-point errors and bridging the gap between real value
 and fixed-point values in synthesis in other application areas and using other
-algorithmic techniques; 
-Genetic programming has been used to minimise the error in synthesised fixed-point programs~\cite{Darulova};
-Smoothed proof search reduces the problem of boolean  a sequence of optimization problems
+algorithmic techniques:
+Genetic programming has been used to minimise the error in synthesised fixed-point programs~\cite{DBLP:conf/emsoft/DarulovaKMS13};
+Smoothed proof search reduces the problem of parameter synthesis under boolean and quantitative 
+objectives to a sequence of optimisation problems~\cite{DBLP:conf/popl/ChaudhuriCS14}; Synthesis of 
+optimal fixed-point implementations of floating-point numerical software can be done using testing and induction~\cite{DBLP:journals/corr/abs-1302-1920}.
+All of these works present potential future applications for CEGIS in synthesising implementations in fixed-point arithmetic.}
 

### 2019-07-23 automatica/paper.tex
paper

@@
 We denote with $x(0)$ the model initial condition, which can be non-deterministic.  
-\rev{ We assume full observability of the states of the model, namely the output states correspond with the model variables.  }
+\rev{ We assume full observability of the states of the model, namely the output states correspond with the model variables, which we can thus fully access.  }
 
@@
 and $r_{k}$ is a reference signal (again digital). 
-We will assume $r_k=0$ \rev{(meaning that the reference signal is just the origin)}, thus obtaining the closed-loop model 
-$\vec{x}_{k+1}=(\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_k$.
+We will assume $r_k=0$ \rev{(meaning that the reference signal is just a zero signal)}, thus obtaining the closed-loop model 
+$\vec{x}_{k+1}=(\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_k$ \rev{with the origin as its equilibrium point}.
 

### 2019-07-23 automatica/paper.tex
paper

@@
 Summarising, we only need to check $2^n$ initial states, 
-where $n$ is the dimension of the state space (number of continuous variables). \todo{Add remark from reviewer that this number can be lower in actuality?}
+where $n$ is the dimension of the state space (number of continuous variables). 
+%\todo{Add remark from reviewer that this number can be lower in actuality?} 
+\rev{Whilst this full check on all vertices might not be necessary in general  
+(it might be simplified in special cases or under special conditions), 
+it does not represent the bottleneck of our overall method, so we can
+safely rely on its current form. }
 

### 2019-07-23 automatica/response.tex
more response
letter

@@
 blue in the revised manuscript. 
-\todo{keep next?} For clarity,  we also use \vold{v1} and \vnew{v2} in the response letter for referring respectively to the previous
-and current versions of the manuscript.
 %I do not like color coding that much. And definitely not with red and blue.
@@
 or under special conditions. The check however, as it currently is implemented, does not represent the bottleneck of our overall method, so we can
-safely rely on its current form, as it stands.  \todo{Add note to manuscript?}
+safely rely on its current form, as it stands.   
+We have added a note to the manuscript.
 
@@
 {\bf Response: }
-\todo[inline]{Alessandro: Response to this (Theorem 1)}
-\vspace{2em}
-
+%\todo[inline]{Alessandro: Response to this (Theorem 1)}
+%\vspace{2em} 
 Many thanks for this note. 
@@
 
-\vskip{2em}
+\vspace{2em}
 Similarly, 
@@
 
-\vspace{2em}
+%\vspace{2em}
 {\bf Comment: } {\itshape 

### 2019-08-05 automatica/response.tex
completeess thresholds and link

@@
 We apologise for this error and thank the reviewer for pointing it out. The DSSynth download from http://dsverifier.org/ is indeed the same code 
-as our implementation for this paper, but without the experimental results and benchmarks. The correct link is now functional: http://www.cprover.org/DSSynth/.
-
-\todo[inline]{fix link }
+as our implementation for this paper, but without the experimental results and benchmarks. The correct link is now functional: http://www.cprover.org/DSSynth/journal.tar.gz.
 
@@
 We have added the completeness threshold for each benchmark in the table. Note that the completeness threshold is dependent on the controller, 
-and a controller with a smaller completeness threshold may exist.
+and controllers with larger or smaller completeness thresholds may exist. Completeness thresholds of zero indicate that the the system, with the controller
+selected, has only real eigenvalues.
 
 The proof of Theorem 2 has been elaborated and has been made more detailed.
-
-\todo[inline]{Elizabeth: add completeness thresholds to table}
 
@@
 \vspace{2em}
+
 Similarly, 

### 2019-08-05 automatica/paper.tex
completeess thresholds and link

@@
 so that the closed-loop dynamics are shaped as desired.  
-\rev{We refer the interested reader to~\cite{fadali} for further details about Jury's criterion, which we omit for the sake of space and since it is a standard result in the control literature that we just leverage for our overall approach.
-}
+\rev{We refer the interested reader to~\cite{fadali} for further details about Jury's criterion, 
+which we omit for the sake of space and since it is a standard result in the control literature that we just leverage for our overall approach. }
 
@@
 with instructions to run all benchmarks and to reproduce our
-experiments.\footnote{\url{http://www.cprover.org/DSSynth/}}
+experiments.\footnote{\url{http://www.cprover.org/DSSynth/journal.tar.gz}}
 %
@@
 \centering
-\begin{tabular}{| l | c | c | r | c | r |}
+\begin{tabular}{| l | c | c | c| r | c | r | c |}
 %
@@
 % \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Run-time} \\
- Benchmark  &  Order  & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Time(s) & $\mathcal{F}_{\langle E_p, M_p \rangle}$ & Time(s) \\\hline
-Bioreact	&	2	&	8,8	&	15.35	&	10,6	&	23.76	\\
-Chen	&	3	&	8,8	&	11.24	&	10,6	&	14.25	\\
-Cruise 2	&	1	&	8,8	&	11.03	&	10,6	&	11.17	\\
-Cruise 2	&	1	&	8,8	&	9.93	&	10,6	&	10.54	\\
-cstrtmp	&	3	&	12,12	&	90.03	&	10,6	&	321.12	\\
-Cstrtmp	&	2	&	8,8	&	18.56	&	10,6	&	16.99	\\
-DC motor	&	2	&	8,8	&	10.34	&	10,6	&	12.32	\\
-Helicopter	&	3	&	16,16	&	1116.08	&	10,6	&	168.43	\\
-Inverted pendulum	&	2	&	12,12	&	16.01	&	10,6	&	18.73	\\
-Magnetic pointer	&	3	&	12,12	&	1071.02	&	10,6	&	207.60	\\
-Magnetic suspension	&	3	&	20,20	&	56.9	&	10,6	&	998.3	\\
-Pendulum	&	2	&	8,8	&	11.74	&	10,6	&	13.69	\\
-Regulator	&	5	&	10,16	&	190.28	&		&	~\xmark	\\
-Satellite	&	2	&	8,8	&	13.91	&	10,6	&	16.92	\\
-Spring-mass-damper	&	2	&	12,12	&	16.09	&	10,6	&	23.21	\\
-Steam drum	&	3	&		&	~\xmark	&	10,16	&	21.16	\\
-Supension	&	4	&	8,8	&	12.40	&	10,6	&	17.03	\\
-Tape driver	&	3	&	8,8	&	12.18	&	10,6	&	14.34	\\
-USCG tampa	&	3	&	12,12	&	1143.35	&	10,6	&	210.70	\\
+ Benchmark  &  Order  & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Time(s) & k & $\mathcal{F}_{\langle E_p, M_p \rangle}$ & Time(s)  & k\\\hline
+Bioreact	&	2	&	8,8	&	15.35 & 4	&	10,6	&	23.76 & 2	\\
+Chen	    &	3	&	8,8	& 	11.24& 0	&	10,6	&	14.25 & 0	\\
+%Chen 2	    &	3	&	8,8	&	11.24	&	10,6	&	14.25	\\
+Cruise    	&	1	&	8,8	&	11.03	& 0&	10,6	&	11.17& 0	\\
+Cruise 2	&	1	&	8,8	&	9.93 & 0	&	10,6	&	10.54 & 0	\\
+Cst  	&	3	&	12,12	&	90.03 & 2	&	10,6	&	321.12 & 2	\\
+Cstrtmp	    &	2	&	8,8	&	18.56 & 2	&	10,6	&	16.99 & 2	\\
+DC motor	&	2	&	8,8	&	10.34 & 0	&	10,6	&	12.32 & 0	\\
+Helicopter	&	3	&	16,16	&	1116.08 & 2	&	10,6	&	168.43 & 38	\\
+Inverted %
+pendulum	&	2	&	12,12 &	16.01&	2 &	10,6	&	18.73 &0	\\
+Magnetic %
+pointer	    &	3	&	12,12	&	1071.02	 & 10 &	10,6	&	207.60 & 9	\\
+Magnetic %
+suspension	&	3	&	20,20	&	56.9 & 2	&	10,6	&	998.3 & 6	\\
+Pendulum	&	2	&	8,8	&	11.74 & 0	&	10,6	&	13.69 & 0	\\
+Regulator	&	5	&		&	~\xmark	&  & 10,16	&	190.28	& 2 	\\
+Satellite	&	2	&	8,8	&	13.91 & 3	&	10,6	&	16.92	& 7\\
+Spring-%
+mass-damper	&	2	&	12,12	&	16.09&	0  &	10,6	&	23.21 & 4	\\
+Steam drum	&	3	&		&	~\xmark	&	& 10,16	&	21.16	& 4\\
+Supension	&	4	&	8,8	&	12.40	& 5 &	10,6	&	17.03 & 5	\\
+Tape driver	&	3	&	8,8	&	12.18 & 0	&	10,6	&	14.34	& 0\\
+USCG tampa	&	3	&	12,12	&	1143.35 & 10 	&	10,6	&	210.70 & 9	\\
 % 
@@
 %EG1. 
-the overall objective of the study that we have raised above.
+the overall objective of the study that we have raised above. \rev{The completeness threshold depends upon the controller
+selected, and the SAT/SMT solver picks a controller with a low completeness threshold for all the time discretisations that we solve.
+The completeness threshold is zero where the controller synthesised results in a system with real valued eigenvalues.}
 

### 2019-08-05 automatica/paper.tex
completeess thresholds and link

@@
 \end{tikzpicture}
-\caption{CEGIS with multi-staged verification for digital controller synthesis}
+\caption{CEGIS with multi-staged verification for digital controller synthesis. We synthesise $K$}
 \label{fig:CEGIS-precision-increment}
@@
 
-\todo{Elizabeth: please make sure this section on CEGIS is perfect.}
-
 In this section, we give a brief description of the CEGIS framework~\cite{jha-icse10,
@@
 %-------------------------------
-
-\todo{I feel that this section had an overtly general title and intro, but was actually limited to discussing the encoding of stability - I have focussed this.}
 
@@
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-\todo{This Section seems coherent. However, Elizabeth can you carefully check it once again?}
 
@@
 \rangle}(x_{k})$; and second, the rounding error introduced by the multiplication operation. 
-Recall that this error \rev{[CLARIFY WHICH OF THE PREVIOUS TWO]} is modelled precisely by bounded model checking.
+Recall that both these errors are modelled precisely by bounded model checking.
 
